\begin{proof}[Proof of \cref{obj:lem:admissible-swaps-preserve-direction}]
Let \(\pi\in G_m\), and extend it to the full source-label set by fixing \(0\) and \(m+1\).  For either arrow, the loading vector after relabeling at label \(j\) is exactly the old loading vector at label \(\pi(j)\), where \(\pi(j)=j\) on the two boundary labels.  Therefore each coordinate of the relabeled cumulant map is obtained from the original coordinate by replacing the finite sum over source labels by the same sum indexed through this permutation.  Finite sums are invariant under such a bijective reindexing, so
\[
\Phi^{\mathrm{right}}_{m,L}(\pi\theta^{\mathbb C})
=\Phi^{\mathrm{right}}_{m,L}(\theta^{\mathbb C}),
\qquad
\Phi^{\mathrm{left}}_{m,L}(\pi\eta^{\mathbb C})
=\Phi^{\mathrm{left}}_{m,L}(\eta^{\mathbb C}).
\]
% lean: forwardLoading_admissibleSourceSwap reverseLoading_admissibleSourceSwap sum_permMiddle forwardCumulantMap_admissibleSourceSwap reverseCumulantMap_admissibleSourceSwap

The same relabeling preserves the real feasible regions.  The nonzero direct edge is unchanged, and the tuple consisting of the direct slope and the middle slopes remains injective because it has only been composed with a permutation on the middle coordinates.  The source-cumulant and real-realizability witnesses required in \cref{obj:def:real-feasible-regions} are transported by using, for the new label \(j\), the old witness attached to \(\pi(j)\).  Hence \(\theta\in F^{\mathrm{right}}_{m,L}\) implies \(\pi\theta\in F^{\mathrm{right}}_{m,L}\), and similarly for the left parametrization.
% lean: finCons_comp_perm_injective realFeasibleRegion_admissibleSourceSwap

For the forward witness statement, put \(S'_j=S_{\pi(j)}\), with the boundary labels fixed.  Mutual independence is preserved because the relabeling is injective on the full source-label set; centering, non-Gaussianity, and the finite-moment condition are obtained by applying the corresponding original hypothesis to the source \(S_{\pi(j)}\).  The forward axis equations remain the same equations for \((X,Y)\), since the relabeled loading at \(j\) equals the old loading at \(\pi(j)\) and the resulting source sum is just a reindexing of the original one.  Forward noncollinearity is preserved by the same injectivity argument for the slope tuple, and the nonzero forward edge is unchanged.  Finally, for every \(2\le r\le L\),
\[
\operatorname{Cum}_r(S'_j)
=\operatorname{Cum}_r(S_{\pi(j)})
=c_{\pi(j),r}
=(\pi c)_{jr}.
\]
Thus the relabeled data satisfy every clause of \cref{obj:def:forward-lvlingam-class} with the same observed variables and the same pushforward law \(P_{\mathrm{right}}\), so \(P_{\mathrm{right}}\in\mathcal P^{\mathrm{right}}_{m,2m+2}\).
% lean: permMiddleEquiv forwardAxisModel_admissibleSourceSwap finCons_comp_perm_injective

The reverse witness statement is identical with the reverse loadings.  With \(S'_j=S_{\pi(j)}\), independence, centering, non-Gaussianity, and finite moments are transported exactly as above; the reverse axis equations are preserved by the reverse loading identity and reindexing of the source sum; reverse noncollinearity is preserved by permuting the middle slopes; and the reverse direct edge is unchanged.  The cumulant relation becomes
\[
\operatorname{Cum}_r(S'_j)
=\operatorname{Cum}_r(S_{\pi(j)})
=d_{\pi(j),r}
=(\pi d)_{jr},
\qquad 2\le r\le L.
\]
Consequently the same observed law \(P_{\mathrm{left}}\) has a valid reverse representation in the sense of \cref{obj:def:reverse-lvlingam-class}.
% lean: permMiddleEquiv reverseAxisModel_admissibleSourceSwap finCons_comp_perm_injective

Now let \(M\) be a structural model.  If \(D(M)=X\to Y\) and its parameter is \(\theta\), take the forward representation contained in \(M\), relabel its sources as above, and keep the same observed variables and law.  The preceding forward argument supplies a valid forward representation with parameter \(\pi\theta\), the feasible-region preservation supplies feasibility of \(\pi\theta\), and the cumulant-map equality gives the same truncated cumulant data.  Defining \(M'\) with this relabeled representation, the same law, and the forward arrow gives \(P_{M'}=P_M\), \(D(M')=X\to Y\), and parameter \(\pi\theta\).  The reverse case is the same construction using the reverse representation and gives \(D(M')=Y\to X\) with parameter \(\pi\eta\).
% lean: realFeasibleRegion_admissibleSourceSwap forwardAxisModel_admissibleSourceSwap reverseAxisModel_admissibleSourceSwap forwardCumulantMap_admissibleSourceSwap reverseCumulantMap_admissibleSourceSwap

For the orbit assertions, the definition of the action gives directly
\[
(\pi c^{\mathbb C})_{jr}=c^{\mathbb C}_{\pi(j),r},
\qquad
(\pi d^{\mathbb C})_{jr}=d^{\mathbb C}_{\pi(j),r}.
\]
For \(j=0\) and \(j=m+1\), the extended permutation fixes \(j\), so the forward boundary loading vectors are unchanged.  The action on arrow-tagged parameters changes only the parameter coordinates and leaves the tag itself fixed; hence a right-tagged parameter remains right-tagged and a left-tagged parameter remains left-tagged.  Therefore the right-tagged and left-tagged \(G_m\)-orbits are disjoint.
% lean: forwardLoading_admissibleSourceSwap admissibleSourceSwapTagged arrowTaggedOrbit_right_left_disjoint

The first cumulant-map argument did not use any special property of \(\pi\) beyond \(\pi\in G_m\).  Repeating it with an arbitrary \(\sigma\in G_m\) gives, for every admissible relabeling,
\[
\Phi^{\mathrm{right}}_{m,L}(\sigma\theta^{\mathbb C})
=\Phi^{\mathrm{right}}_{m,L}(\theta^{\mathbb C}),
\qquad
\Phi^{\mathrm{left}}_{m,L}(\sigma\eta^{\mathbb C})
=\Phi^{\mathrm{left}}_{m,L}(\eta^{\mathbb C}).
\]
% lean: forwardCumulantMap_admissibleSourceSwap reverseCumulantMap_admissibleSourceSwap
\end{proof}
