\begin{proof}[Proof of \cref{obj:thm:generic-apolar-arrow-recovery}]
Put \(K=2m+2\) and \(n=m+2\).  We argue in nine steps.

\begin{enumerate}
\item The truncated Hamburger moment interior theorem gives, at order \(K\), a nonempty Euclidean open set of admissible centered non-Gaussian one-dimensional source cumulant vectors, realized by laws with finite \(K\)-th moment.  This is the real feasibility input used below to make prescribed nonvanishing polynomial conditions hold inside the feasible region of \cref{obj:def:real-feasible-regions}.%
% lean: truncatedMomentInterior

\item On the forward side, choose a nonzero determinant polynomial \(M_{\mathrm r}\) whose nonvanishing makes the forward weighted contraction map injective; on the reverse side choose the analogous nonzero determinant polynomial \(M_{\mathrm l}\).  In each case the determinant is nonzero at an explicit parameter whose source-cumulant coordinates vanish outside the orders \(2,\ldots,K\), so the same determinant remains nonzero after restricting to the truncated coordinate chart.%
% lean: forward_contraction_injective_of_generic_and_minor

\item Let \(\Delta_{\mathrm{gen}}\) be the polynomial cutting out the complement of the generic locus of \cref{obj:def:generic-parameter-loci}: it is the product of the direct slope, all direct-versus-latent slope differences, all latent slope differences, and all retained source-cumulant coordinates.  Let
\[
\Delta_\rho=\prod_{i=1}^m \rho_i
\]
in the forward chart, and use the identical product in the reverse chart with the reverse finite slopes.  Define
\[
R_{\mathrm r}:=\Delta_{\mathrm{gen}}\Delta_\rho M_{\mathrm r},
\qquad
R_{\mathrm l}:=\Delta_{\mathrm{gen}}\Delta_\rho M_{\mathrm l}.
\]
The preceding step and the explicit nonzero factors show that both \(R_{\mathrm r}\) and \(R_{\mathrm l}\) are nonzero after restriction to the truncated chart.%
% lean: pinSubst_ne_zero_of_pinned_witness

\item Define \(U_m^{\mathrm{right}}\) to be the truncated forward parameter space cut by \(R_{\mathrm r}\ne0\), and \(U_m^{\mathrm{left}}\) to be the truncated reverse parameter space cut by \(R_{\mathrm l}\ne0\).  A principal nonvanishing locus whose truncated restriction is not the zero polynomial is relatively Zariski open and relatively Zariski dense.  Since \(R_{\mathrm r}\) and \(R_{\mathrm l}\) contain \(\Delta_{\mathrm{gen}}\), these loci are contained in the corresponding generic parameter loci; since they contain \(\Delta_\rho\), all finite latent slopes are nonzero on them; and since they contain the determinant factors, the corresponding weighted contraction maps are injective.%
% lean: isZariskiOpenIn_denseIn_of_pinSubst_ne_zero

\item Set
\[
O^{\mathrm{right}}=\{\theta\in\Theta^{\mathrm{right}}_{m,K}(\mathbb R):
R_{\mathrm r}(\theta_{\mathbb C})\ne0\},
\qquad
O^{\mathrm{left}}=\{\eta\in\Theta^{\mathrm{left}}_{m,K}(\mathbb R):
R_{\mathrm l}(\eta_{\mathbb C})\ne0\}.
\]
These are Euclidean open by continuity.  Applying the moment-interior nonvanishing statement to \(R_{\mathrm r}\) and \(R_{\mathrm l}\) gives feasible real points in each open set.  If a feasible real parameter lies in the appropriate open set, then its coordinatewise complexification satisfies the truncated support equations and the same nonvanishing condition, hence belongs to the corresponding \(U\)-locus.%
% lean: exists_feasible_nonvanishing

\item Fix \(\theta\in U_m^{\mathrm{right}}\).  From the construction, \(\theta\) is generic, \(\gamma\ne0\), all \(\rho_i\ne0\), the finite forward loading slopes are pairwise distinct and nonzero, and the forward weighted contraction map is injective.  Suppose that a reverse parameter \(\eta\) had the same truncated cumulants.  Its reverse support-annihilator is homogeneous of degree \(n\), annihilates the reverse divided-power blocks, and therefore, by equality of cumulants, annihilates the forward blocks.  The forward apolar kernel identity then forces it to be a scalar multiple of the forward support-annihilator.  The scalar is nonzero because a support-annihilator of the loading directions is nonzero.  But the reverse support-annihilator is divisible by \(y\), whereas the forward support-annihilator is not divisible by \(y\), since \(\gamma\) and all \(\rho_i\) are nonzero.  This contradiction proves
\[
R^{\mathrm{left}}_{m,K}\!\left(\Phi^{\mathrm{right}}_{m,K}(\theta)\right)=\varnothing .
\]%
% lean: forward_reverse_fiber_empty

\item For the same \(\theta\), take
\[
Q(z)=\prod_{r\in\{\gamma,\rho_1,\ldots,\rho_m\}}(z-r),
\]
with the multiset interpretation of the product.  Genericity makes the entries \(\gamma,\rho_1,\ldots,\rho_m\) pairwise distinct, and the extra factor \(\Delta_\rho\) together with genericity excludes \(0\); hence \(Q\ne0\), \(Q\) is squarefree, \(Q(0)\ne0\), and its root multiset is exactly \(\{\gamma,\rho_1,\ldots,\rho_m\}\).  If another generic forward parameter \(\theta''\) has the same forward cumulants, its own support-annihilator lies in the same forward apolar kernel; the kernel identity makes it a nonzero scalar multiple of the support-annihilator of \(\theta\), and dehomogenizing in the \(x\)-chart gives the same root multiset.%
% lean: forward_slopes_determined_by_cumulants

\item Let \(D\) be the forward loading-direction support and let \(Q_D\) be its homogeneous support-annihilator as in \cref{obj:def:apolar-notation}.  Each loading direction has at least one nonzero coordinate, so \(Q_D\ne0\).  The fixed vertical loading direction contributes the factor \(x\), while the nonzero finite slopes and \(\gamma\ne0\) exclude a factor \(y\).  Finally, the forward apolar kernel identity gives, for every homogeneous binary form \(q\) of degree \(n\),
\[
\bigl[q(\partial)f_{n+k}=0\ \text{for all }0\le k\le m\bigr]
\Longleftrightarrow
\exists c\in\mathbb C:\ q=cQ_D .
\]%
% lean: forward_apolar_kernel_identity

\item The reverse proof is the same argument with \(x\) and \(y\), and right and left, interchanged.  For \(\eta\in U_m^{\mathrm{left}}\), genericity and \(R_{\mathrm l}\ne0\) give \(\delta\ne0\), all \(\sigma_i\ne0\), distinct nonzero reverse finite loading coordinates, and injectivity of the reverse weighted contraction map.  A hypothetical forward parameter with the same cumulants would have a forward support-annihilator lying in the reverse apolar kernel; hence it would be a nonzero scalar multiple of the reverse support-annihilator.  This contradicts divisibility by \(x\), because the forward support-annihilator is divisible by \(x\) and the reverse one is not.  Thus the forward fiber is empty.  The univariate polynomial
\[
Q(z)=\prod_{r\in\{\delta,\sigma_1,\ldots,\sigma_m\}}(z-r)
\]
is nonzero, squarefree, nonzero at \(0\), and has the stated root multiset; the same dehomogenized-kernel argument shows that every generic reverse parameter with the same cumulants has that multiset.  For the reverse loading-direction support \(D\), the homogeneous \(Q_D\) is nonzero, is divisible by \(y\), is not divisible by \(x\), and its degree-\(n\) common apolar kernel is exactly the line \(\mathbb C Q_D\).%
% lean: reverse_forward_fiber_empty
\end{enumerate}
\end{proof}
