\begin{proof}[Proof of \cref{obj:thm:improved-real-information-order}]
Fix \(m\ge 3\), and put \(L=2m+1\).

\begin{enumerate}
\item The separation input at this order is obtained by the lower-order apolar
calculation.  On the forward parameter space, let
\[
\Delta^{\mathrm{right}}_m
  =
  \Bigl(\prod_{i=1}^{m}\rho_i\Bigr)\cdot
  \bigl(\text{the forward lower-order contraction-rank determinant}\bigr),
\]
and on the reverse parameter space let
\[
\Delta^{\mathrm{left}}_m
  =
  \Bigl(\prod_{i=1}^{m}\sigma_i\Bigr)\cdot
  \bigl(\text{the reverse lower-order contraction-rank determinant}\bigr).
\]
The explicit pinned determinant witnesses show that both determinant factors are
nonzero polynomials; hence \(\Delta^{\mathrm{right}}_m\) and
\(\Delta^{\mathrm{left}}_m\) are nonzero real polynomials.  Define
\[
E^{\mathrm{right}}
  :=\{\theta:\Delta^{\mathrm{right}}_m(\theta)=0\},
\qquad
E^{\mathrm{left}}
  :=\{\eta:\Delta^{\mathrm{left}}_m(\eta)=0\}.
\]
Thus both sets are proper real algebraic subsets of their respective real
parameter spaces.  The truncated-moment interior fact at order \(L\), together
with the pinned nonvanishing witnesses, gives feasible real points outside each
zero locus:
\[
F^{\mathrm{right}}_{m,L}\setminus E^{\mathrm{right}}\ne\varnothing,
\qquad
F^{\mathrm{left}}_{m,L}\setminus E^{\mathrm{left}}\ne\varnothing .
\]
% lean: lowerOrderApolarSeparation

\item Let \(\theta\in F^{\mathrm{right}}_{m,L}\setminus E^{\mathrm{right}}\).
After viewing \(\theta\) as a complex parameter, the nonvanishing of
\(\Delta^{\mathrm{right}}_m(\theta)\) gives all \(\rho_i\ne0\) and
nonvanishing of the forward contraction-rank determinant.  Feasibility gives
\(\gamma\ne0\) and the required distinctness of the forward loading slopes, so
the forward loading directions used in the lower-order apolar blocks are
injectively indexed and, together with the nonzero \(\rho_i\)'s, have the needed
nonzero second coordinates.  The determinant condition gives injectivity of the
associated lower-order weighted contraction map.  Suppose, toward a
contradiction, that some \(\eta\in F^{\mathrm{left}}_{m,L}\) satisfies
\[
\Phi^{\mathrm{right}}_{m,L}(\theta)
 =
\Phi^{\mathrm{left}}_{m,L}(\eta).
\]
The equality remains true after complexification, since the cumulant maps of
\cref{obj:def:forward-cumulant-map} and
\cref{obj:def:reverse-cumulant-map} have real polynomial coordinates.
% lean: lowerOrderApolarSeparation

\item Let \(Q_{\mathrm{left}}\) be the degree-\(m+2\) support-annihilator
polynomial of the reverse loading directions, and let \(Q_{\mathrm{right}}\) be
the corresponding support-annihilator polynomial of the forward loading
directions, in the notation of \cref{obj:def:apolar-notation}.
The polynomial \(Q_{\mathrm{left}}\) annihilates the reverse divided-power
cumulant blocks in orders \(m+2,\ldots,2m+1\); by the assumed equality of
cumulants, it also annihilates the corresponding forward blocks.  The forward
lower-order apolar kernel identity, applied with the slope and rank conditions
from the previous step, therefore yields a scalar \(c\) such that
\[
Q_{\mathrm{left}}=c\,Q_{\mathrm{right}}.
\]
But every reverse support annihilator is divisible by the horizontal-axis
factor, whereas the forward support annihilator is not divisible by that factor
when \(\gamma\ne0\) and all \(\rho_i\ne0\).  If \(c=0\), then
\(Q_{\mathrm{left}}=0\), contradicting nonzero support annihilation.  If
\(c\ne0\), divisibility transfers from \(Q_{\mathrm{left}}\) to
\(Q_{\mathrm{right}}\), again a contradiction.  Hence no such reverse
\(\eta\) exists.
% lean: lowerForwardReverseImpossible

\item The reverse argument is identical with the roles interchanged.  For
\(\eta\in F^{\mathrm{left}}_{m,L}\setminus E^{\mathrm{left}}\), the
nonvanishing of \(\Delta^{\mathrm{left}}_m(\eta)\) gives all
\(\sigma_i\ne0\) and nonvanishing of the reverse contraction-rank determinant.
Feasibility gives \(\delta\ne0\) and injectivity of the relevant reverse loading
slopes; together with the nonzero \(\sigma_i\)'s this gives the needed nonzero
first coordinates.  The determinant condition gives injectivity of the reverse
lower-order weighted contraction map.  If
\[
\Phi^{\mathrm{left}}_{m,L}(\eta)
 =
\Phi^{\mathrm{right}}_{m,L}(\theta)
\]
for some \(\theta\in F^{\mathrm{right}}_{m,L}\), then the forward support
annihilator annihilates the reverse lower-order blocks and must be a scalar
multiple of the reverse support annihilator.  The forward support annihilator is
divisible by the vertical-axis factor, while the reverse one is not divisible by
that factor under \(\delta\ne0\) and all \(\sigma_i\ne0\).  The same scalar
case split gives a contradiction.  Thus no such forward \(\theta\) exists.
% lean: lowerReverseForwardImpossible

\item The preceding four steps prove generic real separation at order
\(L=2m+1\), with the theorem-local exceptional sets
\(E^{\mathrm{right}}\) and \(E^{\mathrm{left}}\).  Since \(m\ge3\), also
\(2\le 2m+1\).  Therefore \(2m+1\) is an admissible element in the set whose
infimum defines \(K^\star(m)\) in \cref{obj:def:information-order},
and hence
\[
K^\star(m)\le 2m+1 .
\]
% lean: improvedRealInformationOrder

\item Finally, if \(K^\star(m)=2m+2\), the just-proved inequality would give
\(2m+2\le 2m+1\) after comparing the corresponding finite elements of
\(\mathbb N_\infty\), which is impossible.  Hence
\[
K^\star(m)\ne 2m+2 .
\]
% lean: improvedRealInformationOrder
\end{enumerate}
\end{proof}
