\begin{proof}[Proof of \cref{obj:thm:exceptional-locus-codimension-one}]
Fix \(m\ge 1\) and set \(K=2m+2\).  Let
\[
D_m:=\frac{3(m+2)^2+(m+2)}{2}-5 .
\]
\begin{enumerate}
\item The argument first reduces the theorem to the following auxiliary geometric fact: in the finite coordinate space consisting of cumulant coordinates of orders \(2,\ldots,K\), the common-axis image closure is a proper irreducible component of \(\overline E_m\) and lies one irreducible step below each of the two arrow image varieties of \cref{obj:def:image-varieties}.  Once this is known, the codimension-one assertions follow from the principal-equation component argument, while the preimage and low-dimensional assertions are obtained by unpacking \cref{obj:def:generic-full-fiber-compatibility}. % lean: exceptionalLocusCodimensionOne_of_commonAxis_certificates

\item For the common-axis image, the selected \(D_m\times D_m\) Jacobian minor is evaluated at the explicit pinned common-axis witness.  Its matrix is block upper triangular: the ordinary-order block is Vandermonde-type, the top-order block is the augmented confluent block, and the lower-left block vanishes because differentiating an order-\(r\) cumulant coordinate with respect to a source cumulant of a different order gives zero.  The two diagonal determinants are nonzero, so the minor is nonzero.  Together with the matching transcendence-degree upper bound, the finite-coordinate common-axis image has dimension \(D_m\). % lean: restrict_forwardCommonAxisImageClosure_dimension_expected

\item For the full forward arrow image, the analogous \((D_m+1)\times(D_m+1)\) Jacobian minor is evaluated at the forward witness.  The same order separation gives a block upper triangular matrix, now with the ordinary-order block and the top augmented confluent block on the diagonal.  Their determinants are nonzero, hence the polynomial image has dimension at least \(D_m+1\); the coordinate-algebra upper bound gives equality. % lean: restrict_forwardCumulantImageVariety_dimension_expected

\item Let \(C\) be the finite-coordinate common-axis image closure and let \(X^{\mathrm{right}}\) be the finite-coordinate forward arrow image variety.  The inclusions \(C\subseteq \overline E_m\subseteq X^{\mathrm{right}}\) hold by construction.  The inclusion \(C\subsetneq X^{\mathrm{right}}\) is proper: otherwise the finite-coordinate restriction of \(\overline E_m\) would equal that of \(X^{\mathrm{right}}\), contradicting the explicit horizontal contraction equation, which vanishes on the reverse arrow variety but is nonzero at the forward witness.  Since \(X^{\mathrm{right}}\) is irreducible and the dimensions from the previous two steps are \(D_m\) and \(D_m+1\), there is no irreducible closed set strictly between \(C\) and \(X^{\mathrm{right}}\).  Coordinate reversal gives the same no-intermediate statement for the reverse arrow variety. % lean: commonAxisFiniteHeightOneCertificates_of_exact_forward_dimensions

\item The finite-coordinate restriction is injective on the band-supported sets under consideration, so the finite-dimensional chain-codimension statement transfers back to the ambient cumulant space.  The forward and reverse arrow image varieties are irreducible polynomial-image closures, and \(\overline E_m\) is contained in both.  For the common-axis component, the corresponding horizontal or vertical contraction equation supplies a principal minimal-prime component, ruling out a three-term irreducible chain from that component to the ambient arrow variety.  Every irreducible component of \(\overline E_m\) still has the two-term chain from the component to the ambient irreducible arrow variety.  Hence \(\overline E_m\) has codimension exactly \(1\) in both \(C^{\mathrm{right}}_{m,K}\) and \(C^{\mathrm{left}}_{m,K}\). % lean: exceptionalCodimensionOne_of_finite_certificates

\item If \(m\ge 2\), exact codimension \(1\) excludes exact codimension \(m\): any irreducible chain of length \(m+1\) would contain, by taking its first two steps and its endpoint, a three-term chain from the codimension-one witness component to the ambient arrow variety, contradicting the preceding no-three-chain conclusion. % lean: HasCodimensionIn.not_of_one

\item For the forward preimage, \cref{obj:def:generic-full-fiber-compatibility} identifies \(H^{\mathrm{right}}_m\) with the parameters whose forward image lies in the generic full-fiber compatibility locus.  Unpacking this definition, and using \cref{obj:def:generic-parameter-loci} and \cref{obj:def:fiber-correspondences}, gives exactly
\[
\theta\in H^{\mathrm{right}}_m
\quad\Longleftrightarrow\quad
\theta\in\Theta^{\mathrm{right},\circ}_{m,K}
\ \text{and}\
R^{\mathrm{left}}_{m,K}\!\left(\Phi^{\mathrm{right}}_{m,K}(\theta)\right)\neq\varnothing .
\]
The finite-band equalities outside orders \(2,\ldots,K\) are automatic from the band-support conditions. % lean: genericCompatibilityPreimageRight_iff

\item The reverse preimage is identical with the two arrows interchanged.  Thus \cref{obj:def:generic-full-fiber-compatibility}, \cref{obj:def:generic-parameter-loci}, and \cref{obj:def:fiber-correspondences} give
\[
\eta\in H^{\mathrm{left}}_m
\quad\Longleftrightarrow\quad
\eta\in\Theta^{\mathrm{left},\circ}_{m,K}
\ \text{and}\
R^{\mathrm{right}}_{m,K}\!\left(\Phi^{\mathrm{left}}_{m,K}(\eta)\right)\neq\varnothing .
\] % lean: genericCompatibilityPreimageLeft_iff

\item Finally, for \(m=1\) and \(m=2\), the worked compatibility systems of \cref{obj:def:worked-compatibility-instances} are exactly the finite incidence presentations of the generic full-fiber compatibility locus.  In one direction, a point of \(E_m\) provides forward and reverse fiber witnesses with one generic side, and equality of their cumulant coordinates gives a point satisfying \(A_m\).  In the other direction, a solution \(p=(p^{\mathrm{right}},p^{\mathrm{left}})\) of \(A_m\) gives the self-fiber witness on the forward side and the opposite-arrow fiber witness on the reverse side; the coordinates outside the finite band vanish by band support.  Taking \(m=1\) gives the displayed formula with \(A_1\), and taking \(m=2\) gives the displayed formula with \(A_2\). % lean: genericFullFiberCompatibility_eq_worked_projection
\end{enumerate}
\end{proof}
