\begin{proof}[Proof of \cref{obj:prop:symmetry-reduction}]
For the relaxed matrix assertion, let \(u\) and \(v\) be the averages of the off-diagonal entries of \(X\) over, respectively, within-community pairs and across-community pairs, and replace \(X\) by the block matrix \(X(u,v)\).  The unit diagonal is built into \(X(u,v)\), and the same two block sums are preserved by the definitions of \(u\) and \(v\).  To verify membership in the block elliptope, positivity and the unit diagonal first give \(|X_{ij}|\le 1\) for every pair \((i,j)\), by testing the two vectors \(e_i-e_j\) and \(e_i+e_j\).  Averaging this upper bound over the within-community off-diagonal pairs gives \(1-u\ge0\).  The remaining two inequalities follow by applying positive semidefiniteness of \(X\) to the block-sign vector and to the all-ones vector, which give the nonnegativity of \(1+(m-1)u-mv\) and \(1+(m-1)u+mv\), respectively.  Together with the standing two-block homophily assumption, this proves \(X(u,v)\in\mathcal E_m^{\mathrm{blk}}\).

The trace terms in \(F_{r,\kappa}\) are unchanged by this replacement: \(L_m\), \(L_m^\dagger\), and \(J_n\) are block-constant, so their traces against a unit-diagonal symmetric matrix depend only on the diagonal sum and on the within- and across-community off-diagonal sums.  The Frobenius norm of \(X(u,v)\) is no larger than that of \(X\), by Cauchy--Schwarz applied separately to the two families of off-diagonal entries.  Since \(\kappa\ge0\),
\[
F_{r,\kappa}(X(u,v))\le F_{r,\kappa}(X).
\]
% lean: symmetrize_objective_le

For an assignment law \(P\in\mathcal P_m^{\mathrm{bal}}\), take its orbit average under the full two-block automorphism group.  The averaged law remains sign-symmetric and is invariant under permutations within the two communities and under swapping the communities, hence lies in \(\mathcal P_m^{\mathrm{sym}}\).  Sign-symmetry gives zero one-point margins for the averaged law.  Its second-moment matrix is the corresponding orbit average of the original second-moment matrix.  Because the automorphisms permute the within-community and across-community pair sets, the two block sums of this second-moment matrix agree with those of the original one.  Its Frobenius norm is no larger, by the same square-sum averaging argument together with invariance of the total square sum under simultaneous row-column permutations.  Therefore the trace terms in \(F_{r,\kappa}\) are unchanged, the Frobenius term weakly decreases, and
\[
F_{r,\kappa}\bigl(X(P^{\mathrm{orb}})\bigr)\le F_{r,\kappa}\bigl(X(P)\bigr).
\]
% lean: design_symmetrize

It remains to pass from pointwise reduction to the two infimum identities.  On the relaxed side, the block elliptope is contained in the unit-diagonal positive semidefinite elliptope, it is nonempty because \(X(0,0)\) belongs to it, the objective is bounded below on the relaxed elliptope, and every feasible relaxed matrix has the block-averaged representative above with no larger objective.  The elementary infimum-reduction principle therefore gives equality of the relaxed infima. % lean: sInf_image_reduce
On the implementable side, \(\mathcal P_m^{\mathrm{sym}}\subseteq\mathcal P_m^{\mathrm{bal}}\), the iid design supplies a nonempty symmetric class, assignment second moments are positive semidefinite with unit diagonal and hence inherit the same lower bound, and every balanced design is dominated by its orbit average as above.  Applying the same infimum-reduction principle gives the implementable infimum identity. % lean: sInf_image_reduce
\end{proof}
