\begin{proof}[Proof of \cref{obj:thm:sharp-rho-star}]
\textbf{1. Equality and range.}
By definition, \(\rho_\star(m,a,b,r,\kappa)\) is the difference between the implementable reduced value and the relaxed reduced value.  The reduced gap identity \cref{obj:lem:rounding-gap-reduction} identifies this same difference with \(\Delta_m^{\pm}(r,\kappa)\).  Hence
\[
\rho_\star(m,a,b,r,\kappa)=\Delta_m^{\pm}(r,\kappa).
\]
The nonnegativity of \(\rho_\star\) is the constrained-infimum comparison for the reduced problem: the implementable feasible set is the parity-truncated subset of \(T_m\), while the relaxed feasible set is all of \(T_m\).  The objective is bounded below using \(r\ge0\), \(\kappa\ge0\), the nonnegative reduced coordinates, and \(a>b>0\).  Applying the same reduced identity gives the nonnegativity of \(\Delta_m^{\pm}(r,\kappa)\). % lean: hGapEq, roundingLossCertificate_nonneg, implementabilityGap_nonneg

\textbf{2. Zero loss.}
Again using the definition of \(\rho_\star\) together with \cref{obj:lem:rounding-gap-reduction}, zero rounding loss is exactly zero reduced implementability gap.  The zero-gap criterion says that this happens precisely when some relaxed minimizer over \(T_m\) also belongs to the parity-truncated slice, namely when there is
\((x,y,z_{\mathrm{sp}})\in T_m\) minimizing \(\phi_{r,\kappa}\) over all of \(T_m\) and satisfying
\[
d_m\le y+z_{\mathrm{sp}}.
\]
This is the stated zero-loss equivalence. % lean: sharp_roundingLoss_zero_iff_argmin_meets_slice

\textbf{3. Strict robustness.}
Assume \(\kappa>0\).  Since \(m\ge2\) under \cref{obj:ass:two-block-homophily}, we have \(q=2(m-1)>0\).  Under the change of variables
\[
t=(qx,y,z_{\mathrm{sp}}),
\qquad
\alpha^\sharp=\Bigl(\frac{c_x}{q},c_y,c_z\Bigr),
\qquad
\beta^\sharp=\Bigl(\frac1q,1,1\Bigr),
\]
the reduced triangle \(T_m\) is the simplex of total mass \(2m\), and \(\phi_{r,\kappa}\) becomes the weighted-simplex objective.  The positive-robustness part of \cref{obj:lem:weighted-simplex-active-set} gives a unique weighted-simplex minimizer, hence a unique relaxed minimizer of \(\phi_{r,\kappa}\) on \(T_m\).  With uniqueness in hand, the zero-gap criterion from Step 2 is equivalent to saying that every relaxed minimizer satisfies \(d_m\le y+z_{\mathrm{sp}}\). % lean: sharp_reduced_active_set_and_unique, sharp_roundingLoss_zero_iff_unique_argmin_subset_slice

\textbf{4. Linear case.}
Assume \(\kappa=0\), and fix \((x,y,z_{\mathrm{sp}})\in T_m\).  Passing to \(t=(qx,y,z_{\mathrm{sp}})\), the reduced objective is the linear weighted-simplex objective with coefficients \(\alpha^\sharp\).  The zero-robustness part of \cref{obj:lem:weighted-simplex-active-set} identifies the minimizers with the exposed face supported only on coordinates whose \(\alpha^\sharp\)-coefficient is minimal.  Translating this exposed-face condition back to \((x,y,z_{\mathrm{sp}})\) gives exactly the three displayed implications:
positive \(x\)-mass requires \(c_x/q\le c_y,c_z\), positive \(y\)-mass requires \(c_y\le c_x/q,c_z\), and positive \(z_{\mathrm{sp}}\)-mass requires \(c_z\le c_x/q,c_y\). % lean: sharp_kappa_zero_reduced_min_iff

\textbf{5. Active-set formula.}
Assume \(\kappa>0\).  The same active-set construction from Step 3 supplies an admissible support \(S\subseteq\{x,y,z_{\mathrm{sp}}\}\) and multiplier \(\lambda\) for \(\alpha^\sharp,\beta^\sharp,\kappa\).  The corresponding simplex point \(t^{S,\lambda}\) has mass \(2m\); therefore
\[
\Bigl(\frac{t_x^{S,\lambda}}{q},t_y^{S,\lambda},t_z^{S,\lambda}\Bigr)\in T_m .
\]
The weighted-simplex strict minimizer property transfers back through \(t=(qx,y,z_{\mathrm{sp}})\), so this reduced point minimizes \(\phi_{r,\kappa}\) over \(T_m\).  The value formula in \cref{obj:lem:weighted-simplex-active-set} gives the relaxed reduced value \(2m\,\lambda\). % lean: sharp_reduced_active_set_and_unique

\textbf{6. Truncation correction.}
Suppose no relaxed minimizer in \(T_m\) satisfies \(d_m\le y+z_{\mathrm{sp}}\).  Choose a relaxed minimizer and pass to \(t=(qx,y,z_{\mathrm{sp}})\).  Its weighted-simplex coordinates minimize the unconstrained simplex problem but fail the truncated condition \(t_y+t_z\ge d_m\).  The truncation \cref{obj:lem:weighted-simplex-truncation} then puts the constrained minimizer on the boundary segment
\[
H_{d_m}=\{(2m-d_m,s,d_m-s):0\le s\le d_m\}
\]
at
\[
s_\star=\operatorname{truncSelector}(2m,d_m,\alpha^\sharp,\beta^\sharp,\kappa).
\]
Converting the resulting constrained weighted-simplex optimum back to the reduced notation gives
\[
\operatorname{val}_{\mathrm{impl}}(m,a,b,r,\kappa)
=
\Phi_{\alpha^\sharp,\beta^\sharp,\kappa}
(2m-d_m,s_\star,d_m-s_\star).
\]
 % lean: sharp_truncation_value_of_no_reduced_argmin_in_slice

\textbf{7. Even block size.}
If \(m\) is even, then \(d_m=0\).  A relaxed minimizer exists, and every point of \(T_m\) has \(y,z_{\mathrm{sp}}\ge0\), hence \(0=d_m\le y+z_{\mathrm{sp}}\).  The zero-loss criterion from Step 2 therefore gives
\[
\rho_\star(m,a,b,r,\kappa)=0 .
\]
 % lean: sharp_roundingLoss_zero_of_even
\end{proof}
