% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_proximal\_null\_realizability, specialization=v1
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_proximal\_null\_realizability} / \texttt{v1}%
  \\ \large\textit{Quotient-equivalent proximal tables can have different latent-realizable ATE sets}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional}).
\]
Here \(\texttt{qid}=\texttt{pid\_proximal\_null\_realizability}\) and \(\texttt{specialization}=\texttt{v1}\). The observable distribution \(P\) is a strictly positive finite law of \(O=(Y,A,W,Z)\), with \(A\in\{0,1\}\), \(Y\in[0,1]\), \(W\in\mathcal W\), and \(Z\in\mathcal Z\). The target parameter is the proximal average treatment effect \(\theta=\E\{Y(1)-Y(0)\}\). The identifying restrictions are consistency, treatment positivity, existence of a finite latent variable \(U\in\mathcal U\), negative-control exclusions \(Z\perp Y(a,w)\mid(A,U)\) and \(W\perp A\mid U\), and the finite latent completion constraints stated in Assumption~\ref{ass:latent-completion}. For each treatment arm \(a\), the observed bridge operator is \(T_{a,P}\in\mathbb R^{|\mathcal Z|\times |\mathcal W|}\) with entries \(T_{a,P}(z,w)=P(W=w\mid A=a,Z=z)\); the bridge equation is \(T_{a,P}h_a=m_{a,P}\), where \(m_{a,P}(z)=E_P(Y\mid A=a,Z=z)\). The algebraic bridge-null cone is \(K_P=\ker(T_{1,P})\times\ker(T_{0,P})\). The latent-realizable null cone \(R_P\subseteq K_P\) contains exactly those null perturbations \(r=(r_1,r_0)\) for which a one-dimensional signed path of finite latent completions preserves the observed law \(P(Y,A,W,Z)\) to first order and changes the latent bridge by \(r_a\) in arm \(a\). The sharp ATE set is
\[
\Theta_I(P)=\{L_P(h_1,h_0): (h_1,h_0)\text{ is induced by a finite latent completion of }P\},
\quad
L_P(h_1,h_0)=q_{1,P}^{\transpose}h_1-q_{0,P}^{\transpose}h_0,
\]
where \(q_{a,P}(w)=P(W=w\mid A=a)\). The bounding functional is the pair of support functions \(\underline\theta(P)=\inf\Theta_I(P)\) and \(\overline\theta(P)=\sup\Theta_I(P)\), computed over the latent completion polytope rather than over all algebraic bridge solutions.

\begin{abstract}
Finite proximal bridge equations can have nonunique bridge solutions even when an algebraic quotient certifies that a linear functional is invariant on the observed bridge fiber. This proposal asks whether that quotient certificate preserves the sharp causal set once bridge-null directions must be realized by a finite negative-control latent law. The flagship conjecture states that two strictly positive finite observed laws can have the same bridge-operator nullspace and the same null-annihilator quotient certificate, but different sharp ATE sets because their latent-realizable null cones differ. The focal object is the latent-realizable null cone \(R_P\), a Farkas-type cone cut out by nonnegative latent strata and negative-control exclusions. Resolving the conjecture would separate algebraic proximal bridge fibers from causal latent-model fibers and would give partial-identification proximal analyses a finite witness check before optimizing over bridge-null directions.
\end{abstract}

\section{Introduction}
Finite negative-control models impose restrictions that are not visible in the observed bridge equation alone. The main claim is a non-equivalence conjecture: quotient-equivalent observed bridge tables can have different sharp ATE sets because the same algebraic null direction is latent-realizable in one table and spurious in another.

The closest comparator is \citet[p. 2 and Theorem 1]{zhang2023proximalNonunique}, where bridge nonuniqueness is allowed but the counterfactual mean remains a functional of the observed bridge equation. The second comparator is the finite categorical negative-control model of \citet[Section 2.2]{shi2020multiplyRobustDNC}, where latent-class and proxy restrictions enter as genuine stochastic constraints. The gap is that neither paper characterizes which observed bridge-null directions lift to a valid finite latent negative-control law. The kernel is a partial-identification theorem for finite proximal negative-control laws.

The concrete consumer is \citet{ghassami2023partialProxy}, whose proxy partial-identification bounds are the right target when completeness fails but do not distinguish algebraic bridge endpoints from endpoints attained by latent negative-control completions. A reader should optimize the ATE over the latent completion polytope, or certify the relevant null ray as realizable, before treating an observed bridge fiber endpoint as sharp.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the latent-realizable null cone is a finitely generated projection cone and has a Farkas dual certificate. Gap: \citet{zhang2023proximalNonunique} gives an algebraic null-annihilator condition, not a latent stochastic lifting criterion. Consumer: finite proximal sensitivity analyses in \citet{zivich2023introducingPCI}.
\item Conjecture 1: there exist two strictly positive finite laws with identical \(K_P\), identical algebraic quotient certificate for \(L_P\), and different sharp ATE sets because \(R_P\) differs. Gap: \citet{zhang2023proximalNonunique} and \citet{shi2020multiplyRobustDNC} do not give a quotient-equivalent non-equivalence witness. Consumer: bridge-free partial-ID bounds in \citet{ghassami2023partialProxy}.
\item Conjecture 2: on a fixed support stratum, equality of the latent-realizable support function in the target direction is necessary and sufficient for sharp-set invariance among quotient-equivalent finite laws. Gap: quotient invariance is only algebraic in \citet{zhang2023proximalNonunique}. Consumer: finite categorical proximal estimators in \citet{shi2020multiplyRobustDNC}.
\end{itemize}

\section{Related work}
\citet{miao2018proxyVariables} establish proxy-variable identification using two conditionally independent proxies and rank-style restrictions, which is the finite negative-control substrate behind the present latent completion model. \citet{miao2018confoundingBridge} formulate outcome confounding bridges for double negative controls; their bridge equation supplies the operator \(T_{a,P}\). \citet{shi2020multiplyRobustDNC} give categorical double-negative-control identification formulas and are the closest finite latent-class comparator. \citet{zhang2023proximalNonunique} show that a counterfactual mean can be identified even when bridges are nonunique; this proposal does not revisit that algebraic quotient criterion. \citet{cui2024semiparametricProximal} develop semiparametric proximal ATE theory under bridge conditions, motivating why a finite sharp-set distinction matters for inference. \citet{ghassami2023partialProxy} derive partial-identification bounds without completeness; the present proposal asks when bridge-fiber endpoints are actually attainable by latent negative-control laws. \citet{zivich2023introducingPCI} emphasize that negative-control validity and completeness are hard to justify in applications, making observable finite diagnostics valuable. The in-catalogue prior art in \texttt{doc/API.md}, Section 3, records no active PartialID proximal theorem; \texttt{eid\_proximal\_bridge\_quotient} is banked as already solved by the null-annihilator criterion, while \texttt{eid\_proximal\_phase} and \texttt{eid\_proximal\_completeness} were downgraded or failed because they lacked finite latent realization or valid observed-law witnesses.

\section{Formal setup}
Let \(\mathcal A=\{0,1\}\), \(\mathcal W=\{1,2,3\}\), and \(\mathcal Z=\{1,2\}\) for the focal witness class, with the general statements allowing arbitrary finite \(\mathcal W\) and \(\mathcal Z\). An observed law \(P\) assigns strictly positive probabilities to \((Y,A,W,Z)\), with \(Y\in[0,1]\). For each arm \(a\), define \(T_{a,P}(z,w)=P(W=w\mid A=a,Z=z)\), \(m_{a,P}(z)=E_P(Y\mid A=a,Z=z)\), and \(q_{a,P}(w)=P(W=w\mid A=a)\). A bridge pair \(h=(h_1,h_0)\in[0,1]^{|\mathcal W|}\times[0,1]^{|\mathcal W|}\) is algebraically feasible when \(T_{a,P}h_a=m_{a,P}\) for \(a=0,1\); its ATE loading is \(L_P(h)=q_{1,P}^{\transpose}h_1-q_{0,P}^{\transpose}h_0\).

A finite latent completion of \(P\) consists of a finite set \(\mathcal U\), probabilities \(\pi_u\), treatment propensities \(p_a(u)\), proxy kernels \(g_z(z\mid a,u)\) and \(g_w(w\mid u)\), and outcome means \(\mu_a(u,w)\in[0,1]\) such that the implied marginal law of \((Y,A,W,Z)\) equals \(P\) and the negative-control exclusions in Assumption~\ref{ass:latent-completion} hold. The induced bridge is \(h_a(w)=E\{\mu_a(U,w)\mid W=w,A=a\}\) whenever it solves the observed bridge equation. The latent-realizable null cone \(R_P\) is the set of signed directions \(r\in K_P\) for which there exist a completion \(\eta\) of \(P\) and a signed first-order perturbation \(\dot\eta\) preserving the observed law and the exclusion restrictions such that the induced bridge derivative is \(r\). The latent sharp ATE set \(\Theta_I(P)\) is the image of all finite latent completions of \(P\) under \(L_P\).

\begin{center}
\fbox{\begin{minipage}{0.92\linewidth}
Locked parameters: \((\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional})=(\texttt{pid\_proximal\_null\_realizability},\texttt{v1},P(Y,A,W,Z),\E\{Y(1)-Y(0)\},\text{finite latent negative-control completions},(\underline\theta(P),\overline\theta(P)))\). The bridge operator is \(T_{a,P}(z,w)=P(W=w\mid A=a,Z=z)\); \(K_P=\ker(T_{1,P})\times\ker(T_{0,P})\); \(R_P\subseteq K_P\) is the cone of bridge-null directions induced by signed finite latent-completion paths; \(\Theta_I(P)\) is optimized over latent completions, not over the full algebraic bridge fiber.
\end{minipage}}
\end{center}

\section{Assumptions}
\begin{assumption}[Finite strict positivity]\label{ass:finite-positive}
The supports \(\mathcal W\), \(\mathcal Z\), and \(\mathcal U\) are finite, \(A\in\{0,1\}\), \(Y\in[0,1]\), and all observed cells \(P(A=a,W=w,Z=z)\) are strictly positive.
\end{assumption}

\begin{assumption}[Observed bridge equation]\label{ass:bridge-equation}
For each \(a\in\{0,1\}\), the equation \(T_{a,P}h_a=m_{a,P}\) has at least one solution \(h_a\in[0,1]^{|\mathcal W|}\). The algebraic nullspace \(K_P\) is nonzero in at least one arm.
\end{assumption}

\begin{assumption}[Finite latent negative-control completion]\label{ass:latent-completion}
A completion has finite \(U\) and satisfies consistency, treatment positivity \(0<P(A=a\mid U=u)<1\), proxy relevance, \(Z\perp Y(a,w)\mid(A,U)\), and \(W\perp A\mid U\). Its induced marginal law of \((Y,A,W,Z)\) equals \(P\).
\end{assumption}

\begin{assumption}[Fixed support stratum]\label{ass:fixed-stratum}
Comparisons between observed laws keep \(|\mathcal W|=3\), \(|\mathcal Z|=2\), the rank of each \(T_{a,P}\), the sign pattern of positive latent strata, and the algebraic target loading \(q_{1,P},q_{0,P}\) fixed unless stated otherwise.
\end{assumption}

\begin{assumption}[Quotient-equivalent pair]\label{ass:quotient-equivalent}
Two laws \(P\) and \(P'\) are quotient-equivalent when \(K_P=K_{P'}\), \(q_{1,P}^{\transpose}r_1-q_{0,P}^{\transpose}r_0=q_{1,P'}^{\transpose}r_1-q_{0,P'}^{\transpose}r_0\) for every \(r\in K_P\), and the null-annihilator certificate for algebraic functional invariance has the same truth value for \(P\) and \(P'\).
\end{assumption}

\begin{assumption}[Nondegenerate witness]\label{ass:nondegenerate-witness}
The witness laws have \(Y\) nonconstant in both treatment arms, all \((A,W,Z)\) cells positive, and at least two latent strata with distinct \((Z,W)\) proxy kernels. No bridge-null direction used in the witness is supported on a zero-probability observed cell.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: projected Farkas certificate for latent-realizable null directions]\label{thm:farkas-cone}
Under Assumptions~\ref{ass:finite-positive}--\ref{ass:latent-completion}, for fixed finite \(|\mathcal U|\), the set \(R_P^{|\mathcal U|}\) of first-order latent-realizable bridge-null directions is a finitely generated projection cone. A direction \(r\in K_P\) fails to lie in \(R_P^{|\mathcal U|}\) if and only if there is a Farkas multiplier \(\lambda\) separating \(r\) from the linearized latent-completion cone while satisfying all homogeneous constraints that preserve \(P(Y,A,W,Z)\) and the negative-control exclusions.
\end{theorem}
Proof sketch. After fixing support and active positivity pattern, a signed latent path is a finite vector constrained by linear equalities for observed-law preservation and linear inequalities for nonnegative latent atoms. Fourier--Motzkin projection or Farkas separation gives the stated projected cone and dual certificate.

\begin{conjecture}[Conjecture 1: quotient-equivalent laws with different sharp ATE sets (NOT YET PROVED)]\label{conj:nonequivalence}
Under Assumptions~\ref{ass:finite-positive}--\ref{ass:nondegenerate-witness}, there exist two strictly positive finite laws \(P^A\) and \(P^B\) on \(|\mathcal W|=3\), \(|\mathcal Z|=2\) such that \(P^A\) and \(P^B\) are quotient-equivalent, but
\[
R_{P^A}\cap\{r:L_{P^A}(r)>0\}\ne\varnothing,
\qquad
R_{P^B}\cap\{r:L_{P^B}(r)>0\}=\varnothing,
\]
and consequently \(\Theta_I(P^A)\ne\Theta_I(P^B)\). In the proposed witness, \(P^A\) has endpoint-attaining latent completions along the nonzero bridge-null ray, while \(P^B\) has a Farkas certificate excluding that ray although \(K_{P^A}=K_{P^B}\).
\end{conjecture}

\begin{conjecture}[Conjecture 2: support-function frontier for sharp-set invariance (NOT YET PROVED)]\label{conj:support-frontier}
Under Assumptions~\ref{ass:finite-positive}--\ref{ass:fixed-stratum}, let \(\sigma_P(v)=\sup_{r\in R_P,\|r\|_1\le1} v^{\transpose}r\) be the support function of the latent-realizable cone in direction \(v=(q_{1,P},-q_{0,P})\). Within a fixed quotient-equivalence stratum, equality of \(\sigma_P(v)\) and \(\sigma_{P'}(v)\) together with equality of the base bridge value is necessary and sufficient for equality of the local sharp ATE intervals generated by bridge-null perturbations. If \(K_P=K_{P'}\) but \(\sigma_P(v)\ne\sigma_{P'}(v)\), the algebraic quotient certificate cannot determine the sharp ATE set.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Unique-bridge reduction]\label{cor:unique}
Under Assumptions~\ref{ass:finite-positive} and \ref{ass:bridge-equation}, if \(\ker(T_{1,P})=\ker(T_{0,P})=\{0\}\), then \(K_P=R_P=\{0\}\) and \(\Theta_I(P)\) is a singleton whenever a finite latent completion exists. This collapses to the usual complete-rank proximal bridge case because there is no bridge-null direction to certify.
\end{corollary}

\begin{corollary}[Algebraic quotient reduction]\label{cor:quotient}
If Assumptions~\ref{ass:finite-positive}--\ref{ass:bridge-equation} hold and \(R_P=K_P\), then \(\Theta_I(P)\) has the same local width as the algebraic bridge fiber in the target direction. This is the Zhang--Li--Miao--Tchetgen quotient case because every observed null perturbation is causally liftable.
\end{corollary}

\paragraph{Exhibit 9.1: focal cone on a worked \(2\times3\) instance.}
Let both treatment arms share
\[
T=\begin{pmatrix}1/2&1/3&1/6\\1/3&1/2&1/6\end{pmatrix},
\qquad k=(1,1,-5)^{\transpose},
\]
so \(Tk=0\). Let \(q_1=(1/2,1/3,1/6)\) and \(q_0=(1/3,1/2,1/6)\), hence \((q_1-q_0)^{\transpose}k=0\) and the algebraic quotient certifies no ATE movement along the common within-arm ray. For the non-equivalence witness, replace the arm-one loading by \(q_1^\epsilon=q_1+\epsilon(1,-1,0)\) inside an observed law with the same conditional \(T\), and pair two latent completions with identical \(T\) but different tangent cones: completion A splits the third proxy cell across two positive latent strata so \(k\) is generated by moving mass between strata, whereas completion B forces the third proxy cell to be proportional in every positive latent stratum. The internal check is that all displayed probabilities are positive for \(|\epsilon|<1/6\), \(T\) has rank two, \(k\ne0\), no denominator is zero, and the proposed Farkas multiplier for completion B only uses the observed-law preservation rows and nonnegativity rows. Conjecture~\ref{conj:nonequivalence} asserts that this sketch can be completed with explicit \(Y\)-means in \([0,1]\) so that A attains a nonzero ATE endpoint and B excludes it.

\section{Proof-sketch route}
Theorem~\ref{thm:farkas-cone} follows by writing every latent completion parameter as a finite vector, linearizing the observed-law equations, adding tangent inequalities for nonnegative active atoms, projecting onto the induced bridge derivative, and applying Farkas separation. Conjecture~\ref{conj:nonequivalence} has reduction chain: headline \(<-\) unfold \(K_P,R_P,\Theta_I(P)\) \(<-\) substitute Assumptions~\ref{ass:finite-positive}--\ref{ass:nondegenerate-witness} \(<-\) construct two rational \(2\times3\) observed laws with common \(T\) and common algebraic null ray \(<-\) solve the linearized latent-completion equations for law A and exhibit an endpoint path \(<-\) solve the dual Farkas system for law B excluding the same ray \(<-\) compute the target support values and show unequal local sharp intervals. The count is \(k=4\): common-nullspace construction, endpoint latent path, dual obstruction, and support-value comparison. Conjecture~\ref{conj:support-frontier} has reduction chain: headline \(<-\) unfold support functions and local sharp intervals \(<-\) substitute fixed-stratum assumptions \(<-\) prove local equivalence between latent-completion paths and \(R_P\) by a tangent-cone lemma \(<-\) apply convex support-function equality for compact slices \(<-\) verify endpoint attainment for the finite latent polytope \(<-\) separate unequal support functions by a target-loading hyperplane. The count is \(k=4\).

\section{Honest scope flags}
Theorem~\ref{thm:farkas-cone} is a finite convex-analytic theorem conditional on a fixed support size and active positivity pattern. Conjectures~\ref{conj:nonequivalence} and \ref{conj:support-frontier} are not yet proved; the explicit rational endpoint witness and the dual multiplier are the main open calculations. The proposal does not claim a new algebraic null-annihilator criterion, does not optimize over all bridge solutions, and does not claim that every algebraic endpoint is sharp. The support-size bound for the smallest witness may be \(3\times3\) rather than \(2\times3\) if the displayed exhibit cannot be completed with bounded outcome means.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the non-equivalence witness angle; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Cui et~al.(2024)]{cui2024semiparametricProximal}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. (2024). Semiparametric proximal causal inference. \emph{Journal of the American Statistical Association}.

\bibitem[Ghassami et~al.(2024)]{ghassami2023partialProxy}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. (2024). Partial identification with proxy variables. \emph{arXiv:2304.04374}.

\bibitem[Miao et~al.(2018)]{miao2018proxyVariables}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E. (2018). Identifying causal effects with proxy variables of an unmeasured confounder. \emph{Biometrika} 105(4), 987--993.

\bibitem[Miao et~al.(2024)]{miao2018confoundingBridge}
Miao, W., Shi, X., Li, W., and Tchetgen Tchetgen, E. (2024). A confounding bridge approach for double negative control inference on causal effects. \emph{Statistical Theory and Related Fields}.

\bibitem[Shi et~al.(2020)]{shi2020multiplyRobustDNC}
Shi, X., Miao, W., Nelson, J. C., and Tchetgen Tchetgen, E. (2020). Multiply robust causal inference with double-negative control adjustment for categorical unmeasured confounding. \emph{Journal of the Royal Statistical Society: Series B} 82(2), 521--540.

\bibitem[Zhang et~al.(2023)]{zhang2023proximalNonunique}
Zhang, B., Li, W., Miao, W., and Tchetgen Tchetgen, E. (2023). Proximal causal inference without uniqueness assumptions. \emph{Statistics \& Probability Letters} 198, 109836.

\bibitem[Zivich et~al.(2023)]{zivich2023introducingPCI}
Zivich, P. N., Cole, S. R., Edwards, J. K., Mulholland, G. E., Shook-Sa, B. E., and Tchetgen Tchetgen, E. (2023). Introducing proximal causal inference for epidemiologists. \emph{American Journal of Epidemiology} 192(7), 1224--1233.
\end{thebibliography}

\end{document}
