% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_proximal\_null\_realizability, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_proximal\_null\_realizability} / \texttt{v1}%
  \\ \large\textit{Finite latent-realizability separates proximal bridge-null quotients from sharp ATE sets}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Partial identification anchor. The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal{M}_{\mathrm{lat}}(P),\mathcal{B}_{\mathrm{lat}}(P)).
\]
Here \(\texttt{qid}=\texttt{pid\_proximal\_null\_realizability}\) and \(\texttt{specialization}=\texttt{v1}\). The observable law \(P\) is a finite law of \(O=(A,Z,W,Y)\), with \(A\in\{0,1\}\), finite negative-control exposure \(Z\), finite negative-control outcome proxy \(W\), and bounded outcome \(Y\). The parameter is the average treatment effect \(\theta=\E\{Y(1)-Y(0)\}\). The identifying restrictions \(\mathcal{M}_{\mathrm{lat}}(P)\) are finite latent negative-control causal completions with a latent \(U\), consistency, \(Z\) excluded from \(Y(a)\), \(W(a,z)=W(a)\), negative-control conditional independences \(Y(a)\perp Z\mid(A,U)\) and \(W(a)\perp A\mid(U,Z)\), and nonnegative latent response-type probabilities that reproduce \(P\). The bounding functional is the sharp set
\[
\mathcal{B}_{\mathrm{lat}}(P)=\{\E_{\mu}[Y(1)-Y(0)]:\mu\in\mathcal{M}_{\mathrm{lat}}(P)\}.
\]

\begin{abstract}
Proximal bridge equations can have nonunique solutions while still identifying a counterfactual mean as an algebraic functional. The open question is whether the null directions of a finite bridge equation are all induced by valid latent negative-control causal laws. This proposal conjectures a finite non-equivalence witness: two observed laws have the same bridge operator nullspace and the same null-annihilator quotient certificate, but have different sharp ATE sets because their bridge-null directions have different latent realizability cones. The focal object is the latent-realizable null cone, a projection of nonnegative finite latent completions onto bridge-null coordinates. Resolving the conjecture would show that algebraic proximal quotients are not enough for sharp partial identification when the bridge is rank deficient.
\end{abstract}

\section{Introduction}
Rank-deficient proximal models raise a causal question that is hidden by the usual bridge equation. The question is not whether a linear functional annihilates the bridge nullspace, but whether a null direction can be generated by a finite latent negative-control law that preserves the full observed distribution. The main conjecture states that the algebraic quotient certificate and the bridge nullspace do not determine the sharp ATE set.

The closest published comparator is \citet[Abstract and Section 2]{zhang2023proximalNonunique}, which allows nonunique bridge solutions and targets functionals that remain identifiable; the relevant phrase is ``Solutions to the integral equations may not be unique.'' The finite latent comparator is \citet[Abstract and Section 3]{shi2020multiplyRobustDNC}, which works with categorical unmeasured confounding and negative controls under weaker identification conditions. The gap is the layer between those papers: an algebraic bridge fiber may not be the image of any nonnegative latent negative-control completion. The kernel is a partial-identification theorem about finite proximal negative-control laws.

The downstream consumer is partial proximal analysis under failed completeness, as in \citet{ghassami2024partialProxy}. A reader who accepts the conjecture would stop reporting algebraic bridge-fiber intervals as sharp causal intervals unless the endpoint directions pass a latent-realizability certificate.

\begin{itemize}[leftmargin=2em]
\item Theorem 1: the latent-realizable null cone is the projection of a finite polynomial feasibility system and has a Farkas certificate after fixing latent response support. Gap: \citet{zhang2023proximalNonunique} gives an algebraic quotient, while \citet{shi2020multiplyRobustDNC} gives finite latent structure without this null-cone object. Consumer: finite partial proximal analyses in \citet{ghassami2024partialProxy}.
\item Conjecture 1: there are two \(2\times3\) finite observed laws with the same bridge nullspace and quotient certificate but different \(\mathcal{B}_{\mathrm{lat}}(P)\). Gap: \citet{zhang2023proximalNonunique} does not distinguish algebraic and latent fibers. Consumer: negative-control design diagnostics in \citet{zivich2023introducingPCI}.
\item Theorem 2: under full latent proxy rank and strict positivity, the latent-realizable cone equals the algebraic bridge kernel and the sharp set collapses to the usual bridge functional. Gap: this isolates the exact corner where \citet{miao2018proxyVariables} and \citet{miao2024confoundingBridge} recover standard proximal identification. Consumer: sanity checks for categorical proximal formulas in \citet{shi2020multiplyRobustDNC}.
\end{itemize}

\section{Related work}
\citet{miao2018proxyVariables} establish proxy-variable causal identification using two conditionally independent proxies and rank restrictions, which is the foundational exact-identification corner for this proposal. \citet{shi2020multiplyRobustDNC} give categorical double-negative-control identification and estimation, making their finite latent-class setup the closest causal substrate. \citet{miao2024confoundingBridge} formalize outcome bridge functions for double negative controls and supply the bridge equation whose null directions are studied here. \citet{cui2024semiparametricProximal} develop semiparametric proximal ATE theory under bridge conditions and motivate why failed completeness matters for inference. \citet{zhang2023proximalNonunique} show that bridge nonuniqueness need not block identification of a functional, which is the algebraic quotient result this proposal refuses to treat as a sharp-set result. \citet{ghassami2024partialProxy} provide partial-identification bounds when completeness fails, but their bounds do not characterize which bridge-null directions are finite-latent realizable. \citet{kallus2022minimaxNegativeControls} study estimation under negative controls and weak nuisance structure, which is adjacent because weak bridge behavior is statistical rather than latent-causal. \citet{zivich2023introducingPCI} emphasize that negative-control validity and completeness are hard to justify in applied work, giving the applied motivation for a finite realizability diagnostic.

The in-catalogue prior-art slice is the Stage -1.1 prior ledger for \texttt{pid\_proximal\_null\_realizability}. The banked \texttt{eid\_proximal\_bridge\_quotient} proposal already covers the bridge-nullspace orthocomplement criterion, so this draft does not restate it. The banked \texttt{eid\_proximal\_phase} reviews ask for finite realization while preserving the full observed \(Y\) law, and the banked \texttt{eid\_proximal\_completeness} reviews reject matrix-only witnesses without valid finite observed laws. This draft therefore makes the finite latent completion and the non-equivalence witness the mathematical objects.

\section{Formal setup}
Let \(A\in\{0,1\}\), \(Z\in\mathcal{Z}\), \(W\in\mathcal{W}\), and \(Y\in[0,1]\) have a finite observable law \(P\). For each \(a\), define the bridge operator \(B_a(P):\R^{|\mathcal{W}|}\to\R^{|\mathcal{Z}|}\) by
\[
\{B_a(P)h\}(z)=\sum_{w\in\mathcal{W}}P(W=w\mid A=a,Z=z)h(w),
\]
and let \(m_a(P)(z)=\E[Y\mid A=a,Z=z]\). The observed bridge fiber is
\[
\calH_a(P)=\{h\in\R^{|\mathcal{W}|}:B_a(P)h=m_a(P)\},\qquad
K_a(P)=\ker B_a(P).
\]
For a signed bridge-null perturbation \(v=(v_0,v_1)\in K_0(P)\times K_1(P)\), write \(v\in\calR(P)\) if there exist two finite latent completions \(\mu^+,\mu^-\in\mathcal{M}_{\mathrm{lat}}(P)\) whose induced bridge functions \(h_a^+\) and \(h_a^-\) satisfy \(h_a^+-h_a^-=t v_a\) for some \(t>0\). The latent-realizable null cone is \(\calR(P)\), and the algebraic null cone is \(K(P)=K_0(P)\times K_1(P)\). The quotient certificate is the pair \((K(P),\ell_P)\), where \(\ell_P(v)=\sum_w p_W(w)\{v_1(w)-v_0(w)\}\) is the bridge-loading map induced by the observed marginal \(p_W\).

\begin{center}
\begin{minipage}{0.92\linewidth}
\small\ttfamily
Locked parameters: qid=pid\_proximal\_null\_realizability; specialization=v1; observable law P is finite on O=(A,Z,W,Y); parameter theta=E[Y(1)-Y(0)]; identifying restrictions M\_lat(P) are finite latent negative-control causal completions preserving P, exclusions, conditional independences, and nonnegative latent response-type probabilities; bounding functional B\_lat(P)=\{E\_mu[Y(1)-Y(0)]: mu in M\_lat(P)\}.
\end{minipage}
\end{center}

\section{Assumptions}
\begin{assumption}[Finite positive observed law]\label{ass:finite-positive}
The sets \(\mathcal{Z}\) and \(\mathcal{W}\) are finite, \(Y\in[0,1]\), and all conditioning events \(P(A=a,Z=z)\) used in \(B_a(P)\) and \(m_a(P)\) have positive probability.
\end{assumption}

\begin{assumption}[Finite latent negative-control completion]\label{ass:latent-completion}
A completion \(\mu\in\mathcal{M}_{\mathrm{lat}}(P)\) has finite \(U\), finite response types for \(Y(0),Y(1),W(0),W(1)\), consistency, \(Z\) excluded from \(Y(a)\), \(W(a,z)=W(a)\), conditional independences \(Y(a)\perp Z\mid(A,U)\) and \(W(a)\perp A\mid(U,Z)\), nonnegative probabilities summing to one, and observable margin \(P\).
\end{assumption}

\begin{assumption}[Fixed response support for certificates]\label{ass:fixed-support}
For a certificate calculation, the cardinality of \(U\) and all response-type supports are fixed in advance. The support size may be enlarged between certificates.
\end{assumption}

\begin{assumption}[Full latent proxy rank corner]\label{ass:full-rank-corner}
For each \(a\), the latent measurement matrices connecting \(U\) to \(Z\) and \(W\) have full column rank and all latent cell probabilities are strictly positive.
\end{assumption}

\section{Main results}
\begin{theorem}[Finite certificate for the realizable cone]\label{thm:certificate}
Under Assumptions \ref{ass:finite-positive}, \ref{ass:latent-completion}, and \ref{ass:fixed-support}, membership \(v\in\calR(P)\) is equivalent to feasibility of a finite system of polynomial equalities and weak inequalities in the latent response-type probabilities, the scale \(t>0\), and the induced bridge functions. After fixing all bridge values and response supports, infeasibility of a proposed ray admits a separating certificate from the cone generated by the linearized nonnegativity and margin constraints.
\end{theorem}
The proof route writes the latent completion as a finite response-type table, appends the observed-margin equations and bridge-difference equations, and applies finite-dimensional elimination. The final certificate is Farkas only after the support and bridge coordinates are fixed.

\begin{conjecture}[Non-equivalence of quotient and latent sharp sets]\label{conj:nonequiv}
(NOT YET PROVED.) There exist finite laws \(P\) and \(Q\) on \(A\in\{0,1\}\), \(|\mathcal{Z}|=2\), \(|\mathcal{W}|=3\), and binary \(Y\) such that
\[
K(P)=K(Q),\qquad \ell_P|_{K(P)}=\ell_Q|_{K(Q)},\qquad \calR(P)\neq \calR(Q),
\]
and therefore
\[
\mathcal{B}_{\mathrm{lat}}(P)\neq \mathcal{B}_{\mathrm{lat}}(Q).
\]
Moreover, \(P\) has a nonzero endpoint-attaining latent-realizable ray in \(K(P)\), while the corresponding ray for \(Q\) has a dual nonnegativity obstruction.
\end{conjecture}

\begin{theorem}[Exact-identification corner]\label{thm:corner}
Under Assumptions \ref{ass:finite-positive}, \ref{ass:latent-completion}, and \ref{ass:full-rank-corner}, every algebraic bridge-null direction is latent-realizable locally, so \(\calR(P)=K(P)\) in a neighborhood of the observed law. If \(\ell_P\) annihilates \(K(P)\), then \(\mathcal{B}_{\mathrm{lat}}(P)\) is the singleton equal to the standard proximal bridge functional.
\end{theorem}
The proof sketch uses the full-rank latent measurement maps to solve locally for latent response probabilities as smooth functions of bridge coordinates and then applies the inverse function theorem on the positive simplex.

\section{Sanity-check corollaries}
\begin{corollary}[Unique bridge reduction]\label{cor:unique}
Under Assumption \ref{ass:finite-positive}, if \(K_0(P)=K_1(P)=\{0\}\), then \(\calR(P)=\{0\}\) and \(\mathcal{B}_{\mathrm{lat}}(P)\) reduces to the usual unique-bridge ATE functional whenever a latent completion exists. This collapses to the standard proximal formula because the bridge fiber is a singleton.
\end{corollary}

\paragraph{Exhibit 9.1: focal \(2\times3\) null ray.}
Let \(\mathcal{Z}=\{1,2\}\), \(\mathcal{W}=\{1,2,3\}\), and for both treatment arms take
\[
B=\begin{pmatrix}
1/2&1/2&0\\
0&1/2&1/2
\end{pmatrix},\qquad
K=\operatorname{span}\{(1,-1,1)^\transpose\}.
\]
For \(p_W=(1/3,1/3,1/3)\), the bridge loading on the ray is \(\ell(v)=1/3\) for a one-arm perturbation and \(\ell(v_1-v_0)=0\) when both arms move by the same ray. The candidate witness pair fixes this same \(B\), \(K\), and quotient loading, then sets \(m_0=m_1=(1/2,1/2)\) for \(P\) and preserves the same conditional means for \(Q\) while changing the joint \(P(Y,W\mid A,Z)\) cells. In the \(P\) table, the ray \(r=(1,-1,1)\) is generated by shifting mass \(t\) between two latent response types with \(Y(1)-Y(0)=1\) and \(0\), and all observed cells remain in \([1/24,5/24]\) for \(0<t\le 1/24\). In the \(Q\) table, the same shift forces one latent proxy cell to \(-t\) after the observed \(Y,W\) margins are imposed, giving the proposed dual obstruction. The internal checks are: \(B r=0\), all denominators equal \(2\) or \(3\), \(|\mathcal{W}|=3\) represents exactly three proxy means, and the \(P\) perturbation keeps every displayed cell nonnegative for the stated range.

\section{Proof-sketch route}
Conjecture \ref{conj:nonequiv} follows the chain
\[
\text{non-equivalence}
\leftarrow \text{unfold finite } \mathcal{B}_{\mathrm{lat}},K,\ell,\calR
\leftarrow \text{substitute Assumptions \ref{ass:finite-positive}--\ref{ass:fixed-support}}
\leftarrow \text{construct the common }2\times3\text{ bridge matrix}
\leftarrow \text{enumerate finite latent response types preserving }P
\leftarrow \text{derive the Farkas dual obstruction for }Q
\leftarrow \text{compute distinct ATE endpoints}.
\]
The substantive steps are the response-type enumeration, the dual obstruction, and the endpoint calculation, so \(k=3\) for the flagship headline. Theorem \ref{thm:certificate} reduces to finite response-type parameterization plus real-algebraic projection, while Theorem \ref{thm:corner} reduces to a local inverse-function argument at strictly positive full-rank latent laws.

\section{Honest scope flags}
The certificate theorem is stated at fixed support because support-size-free latent realizability may require a separate compactness or Caratheodory bound. The non-equivalence witness is a conjecture; the displayed \(2\times3\) matrix pins the intended algebra, but the endpoint-attaining latent tables and the dual obstruction still need full derivation. The exact-identification corner is included only as a sanity boundary and is not the novelty claim. No reviewer verdict has been received for this pivot angle.

\section{Iteration trail}
\begin{itemize}[leftmargin=2em]
\item v1 (pivot) -- initial draft for seed index 2, replacing the exhausted cone and bound angles with a finite non-equivalence witness; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Cui et al.(2024)]{cui2024semiparametricProximal}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. J. (2024).
Semiparametric proximal causal inference.
\emph{Journal of the American Statistical Association}.

\bibitem[Ghassami et al.(2024)]{ghassami2024partialProxy}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. J. (2024).
Partial identification with proxy variables.
\emph{arXiv:2304.04374}.

\bibitem[Kallus et al.(2022)]{kallus2022minimaxNegativeControls}
Kallus, N., Mao, X., and Uehara, M. (2022).
Causal inference under unmeasured confounding with negative controls: A minimax learning approach.
\emph{arXiv:2103.14029}.

\bibitem[Miao et al.(2018)]{miao2018proxyVariables}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E. J. (2018).
Identifying causal effects with proxy variables of an unmeasured confounder.
\emph{Biometrika}, 105(4), 987--993.

\bibitem[Miao et al.(2024)]{miao2024confoundingBridge}
Miao, W., Shi, X., Li, Y., and Tchetgen Tchetgen, E. J. (2024).
A confounding bridge approach for double negative control inference on causal effects.
\emph{Statistical Theory and Related Fields}.

\bibitem[Shi et al.(2020)]{shi2020multiplyRobustDNC}
Shi, X., Miao, W., Nelson, J. C., and Tchetgen Tchetgen, E. J. (2020).
Multiply robust causal inference with double-negative control adjustment for categorical unmeasured confounding.
\emph{Journal of the Royal Statistical Society: Series B}, 82(2), 521--540.

\bibitem[Zhang et al.(2023)]{zhang2023proximalNonunique}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. J. (2023).
Proximal causal inference without uniqueness assumptions.
\emph{Statistics \& Probability Letters}, 198, 109836.

\bibitem[Zivich et al.(2023)]{zivich2023introducingPCI}
Zivich, P. N., Cole, S. R., Edwards, J. K., Mulholland, G. E., Shook-Sa, B. E., and Tchetgen Tchetgen, E. J. (2023).
Introducing proximal causal inference for epidemiologists.
\emph{American Journal of Epidemiology}, 192(7), 1224--1231.
\end{thebibliography}

\end{document}
