% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_approx\_nbhd\_interference, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{panel\_approx\_nbhd\_interference} / \texttt{v1}%
  \\ \large\textit{A spectral frontier for ANI, network-cluster-robust, and randomization-test interference functionals}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
(qid, specialization, p, assignment, target, regression)
= (panel_approx_nbhd_interference, v1,
   p = (r, rho, epsilon_M, eta, b_n, design_orbits),
   assignment = triangular-array randomized network experiment with
      bounded expected degree law rho, known graph G_n, treatment vector
      Z_n, and a design group Omega_n whose orbits describe the valid
      randomization permutations,
   target = finite-population direct-plus-spillover exposure contrast
      tau_ds(r) between e_1=(own treated, radius-r exposure s_1) and
      e_0=(own control, radius-r exposure s_0), where each exposure-label
      potential outcome is averaged over the assignment law conditional on
      that label,
   regression = exposure-score projection on M_r(i,Z_n), with the ANI
      point-score projection P_ANI(r), the design-orbit point-score
      projection P_RT(Omega_n), and first-order covariance operators
      V_HAC(r), V_NCR(b_n), and V_RT(Omega_n).)
\end{verbatim}
The proposal is a free-form panel/network-interference anchor, not a Q1
pool-mode instance.  The symbols \(r\), \(\rho\), \(\epsilon_M\), \(\eta\),
\(b_n\), and \(\Omega_n\) are fixed throughout the proposal.

\begin{abstract}
This proposal asks when three leading ways of working under SUTVA violations
identify the same direct-plus-spillover object: Leung's approximate
neighborhood interference exposure estimator, Leung's network-cluster-robust
inference, and Basse--Ding--Feller--Toulis randomization tests for
design-compatible peer effects.  The benchmark theorem records the oracle case
where the point-score projection and covariance operators collapse to the same
exposure contrast and first-order law.  The
flagship conjecture is a sharp spectral frontier: uniform equality of the
limiting functional and first-order variance over a declared misspecification
class holds if and only if an observable finite-dimensional optimization
\(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)\) is zero.  The unobserved
omitted-tail score then enters only as a sensitivity analysis inside that
observable cone, after vectorization into the common score space.  Above that
boundary, the proposal predicts strict separation: ANI carries
exposure-misspecification bias,
network-cluster-robust inference remains a covariance procedure for the
exposure-score estimator but has a contrast-specific scalar efficiency gap,
and the randomization procedure targets the design-orbit efficient null.
Resolving the conjecture would tell applied network experiments when exposure
maps, graph-distance covariance estimates, and exact randomization
restrictions are interchangeable rather than merely adjacent.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Network experiments now face three different prescriptions when treatment
effects spill across units.  Exposure-mapping estimators define a causal
contrast through local treatment summaries; network HAC and
cluster-robust procedures protect inference against graph dependence; exact
randomization tests protect finite-sample validity by respecting the design
orbit.  These objects are often used as if they were alternative implementations
of the same direct-plus-spillover estimand, but the literatures control
different sigma-fields: radius-\(r\) exposure cells, low-conductance graph
blocks, and design-compatible permutations.

\paragraph{The main finding (proposed).}
Theorem~\ref{thm:oracle-collapse} states the safe benchmark: when the exposure,
cluster, and randomization-orbit projections coincide on the active score
space, the ANI exposure-score estimator, the network-cluster-robust covariance
operator, and the randomization-test covariance operator deliver the same
direct-plus-spillover contrast and the same first-order variance.
Conjecture~\ref{conj:spectral-frontier} is the flagship claim: away from that
oracle cell, uniform equivalence over a declared ANI misspecification class is
governed by the observable cone program
\(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)\), with the cone-restricted singular
value \(\mu_\star(\eta)\) turning nonzero compatibility violations into sharp
lower bounds.  The unobserved true tail has its own sensitivity distance
\(\mu_{\perp}\), but it no longer defines the flagship frontier.

\paragraph{What is new.}
The novelty kernel is not another exposure estimator and not a looser
regularity condition.  The closest published results are
\citet{Leung2022ANI}, \citet{Leung2023NCRI},
\citet{BasseDingFellerToulis2024}, \citet{GaoDing2025Network},
\citet{PuelzBasseFellerToulis2022}, and \citet{WeinsteinNevo2026};
each gives validity for one mathematical object, but none characterizes the
necessary-and-sufficient frontier at which exposure point-scores,
network-robust covariance objects, and design-orbit randomization objects
coincide.  The epsilon-gap is the design-observable cone program induced by
the compatibility kernel
\[
  \mathcal A_{r,b,\Omega}
  =
  \begin{bmatrix}
  P_{\mathrm{ANI}}(r)-P_{\mathrm{RT}}(\Omega)\\
  V_{\mathrm{HAC}}(r)-V_{\mathrm{NCR}}(b)\\
  V_{\mathrm{HAC}}(r)-V_{\mathrm{RT}}(\Omega)
  \end{bmatrix} W_\rho^{1/2},
\]
plus the sensitivity-indexed omitted-tail distance to its common-null cone.
Unlike \citet{GaoDing2025Network}, which studies regression-based point
estimators and network-HAC covariance inside a single exposure-analysis
workflow, this proposal asks when that exposure-analysis workflow is also
equivalent to Leung-style cluster robustness and exact design-orbit
randomization.  Unlike \citet{PuelzBasseFellerToulis2022}, which constructs
valid graph-theoretic randomization tests from biclique conditioning, the
frontier here asks whether the randomization null, exposure estimand, and
network covariance law are the same limiting object.  Unlike
\citet{WeinsteinNevo2026}, which quantifies bias from using a misspecified
network, the proposed threshold also contains the randomization-orbit and
cluster-bandwidth coordinates.

\paragraph{How it positions in the literature.}
This is a panel / linear-projection proposal in the network-interference
frontier, with a partial-identification flavor only through exposure
misspecification.  It uses the same residual-score and spectral language that
appears in panel FWL and network covariance work, but the target is the
interference direct-plus-spillover contrast rather than a two-way fixed effect
coefficient.  The proposal deliberately treats SCM and graph semantics as
infrastructure: the theorem-level question is about equality of estimator
maps and their first-order covariance operators.

\paragraph{Implications for the community.}
The concrete downstream consumer is the design choice in
\citet{BasseDingFellerToulis2024}: if Conjecture~\ref{conj:spectral-frontier}
is true, a group-formation experimenter can report whether the exact
randomization target is also the Leung ANI exposure target and whether the
network-cluster-robust variance is paying only an efficiency cost rather than
estimating a different first-order law.

\paragraph{How research benefits from the conclusion.}
Researchers should report the observable compatibility program
\(\Delta_\eta\) and the cone-restricted compatibility value \(\mu_\star\) before
substituting exposure-IPW, network-cluster, and randomization-test analyses for
one another.

\section{Related work}
\citet{Leung2022ANI} is the closest exposure-estimation anchor: it introduces
approximate neighborhood interference, proves consistency and asymptotic
normality for inverse-probability exposure estimators, and uses a network HAC
variance estimator, but it does not compare that functional to
cluster-robust or exact randomization targets.  \citet{Leung2023NCRI} is the
closest cluster-robust anchor: it ties valid cluster-robust inference to
low-conductance graph partitions and spectral clustering, but its validity
condition is partition geometry rather than exposure-radius correctness.
\citet{BasseDingFellerToulis2024} is the closest randomization anchor: it gives
exact permutation tests for peer effects in group-formation experiments under
design-compatible exposure restrictions, but it does not state a sharp
ANI/HAC/randomization equivalence frontier.

\citet{Savje2024MisspecifiedExposure} separates exposure definitions from
assumptions on the full interference structure, which motivates treating
\(\epsilon_M\) as a real estimand/structure gap rather than a nuisance label.
\citet{AronowSamii2017Exposure} supplies the exposure-mapping framework and
Horvitz--Thompson logic for arbitrary interference under a specified exposure
map.  \citet{BasseFellerToulis2019} develops conditioning mechanisms for
valid randomization tests under general interference, providing the
design-orbit object used here.  \citet{HudgensHalloran2008} fixes the direct
and indirect effect terminology under partial interference; its no-cross-group
restriction is one corner case of the present compatibility problem.
\citet{KojevnikovMarmerSong2021} is the network HAC comparator: it shows how
HAC consistency depends on dependence decay and network denseness, matching
the \(\rho\) axis in this proposal.  \citet{GaoDing2025Network} is the
closest network-experiment regression/HAC paper: it recovers exposure
estimators through weighted least squares, develops design-based properties,
and studies network-robust covariance, but it does not compare the resulting
point-score and covariance law to low-conductance network clustering or exact
partial-interference randomization orbits.  \citet{Conley1999Spatial} is the older
spatial-dependence ancestor for distance-based covariance estimation, useful
because the proposed bandwidth \(b_n\) is a graph-distance analogue.
\citet{PuelzBasseFellerToulis2022} is the closer randomization-test comparator
missed in v3: it uses graph-theoretic biclique conditioning to construct valid
randomization tests under general interference, but it does not compare the
resulting test orbit to ANI exposure point scores or network-cluster covariance
operators.  \citet{WeinsteinNevo2026} is the closer misspecification comparator
missed in v3: it derives bias from misspecified network interference and
constructs network-misspecification-robust estimators, but it does not give a
three-procedure equivalence frontier involving design orbits and
cluster-bandwidth scaling.  The 2026 misspecified-exposure
partial-identification line is therefore orthogonal rather than duplicative:
it bounds what can be learned under a wrong network or exposure model, while
the present proposal asks when three named procedure maps collapse to the same
limiting point/covariance object.

In-catalogue prior art is adjacent but not duplicate.  \texttt{doc/API.md}
Section~1 records Q1 panel theorems about residualized score geometry and
minimal clean nuisance bases; these are algebraic analogues, not network
interference estimator comparisons.  The banked \texttt{pid\_network\_exposure}
proposal, ``Sharp ADE bounds from shared local-network completions under
misspecified exposure maps,'' proves a sharp finite joint-completion projection
and a strict cellwise-relaxation gap, but its own scope flags state that it does
not claim statistical inference, asymptotic coverage, or an efficient
estimator.  The failed \texttt{panel\_honest\_did\_phase} proposal supplies a
warning rather than prior art: its reviewer asked for named estimator-map
comparisons, exactly what the present proposal builds into the kernel.

\paragraph{Named literature checklist for the flagship conjectures.}
The reviewer-facing prior-art checklist is:
\begin{center}
\small
\begin{tabular}{p{0.18\linewidth}p{0.10\linewidth}p{0.20\linewidth}p{0.30\linewidth}p{0.14\linewidth}}
Author/year & Venue & Bibkey & Claim that threatens novelty & Most relevant result\\
\hline
Leung 2022 & Econometrica & \texttt{Leung2022ANI} &
ANI IPW consistency and asymptotic normality with network HAC under approximate neighborhood interference. &
Theorem 1; Conjecture 1\\
Leung 2023 & Econometrica & \texttt{Leung2023NCRI} &
Network cluster-robust validity is governed by low-conductance clusters and spectral partitions. &
Theorem 1; Conjecture 1\\
Basse--Ding--Feller--Toulis 2024 & Econometrica & \texttt{BasseDingFellerToulis2024} &
Exact group-formation permutation tests are valid for design-compatible exposure restrictions. &
Theorem 1; Conjectures 1--2\\
Gao--Ding 2025 & Journal of Econometrics & \texttt{GaoDing2025Network} &
Network-experiment WLS/Hajek analysis recovers exposure estimators and studies network-robust covariance. &
Conjecture 1\\
Puelz--Basse--Feller--Toulis 2022 & JRSSB & \texttt{PuelzBasseFellerToulis2022} &
Biclique conditioning gives graph-theoretic randomization tests under general interference. &
Conjectures 1--2\\
Weinstein--Nevo 2026 & Biometrics & \texttt{WeinsteinNevo2026} &
Misspecified network interference creates bias and motivates robust multi-network estimators. &
Conjectures 1--2\\
Savje 2024 & Biometrika & \texttt{Savje2024MisspecifiedExposure} &
Misspecified exposure mappings can define estimable contrasts without validating the causal exposure model. &
Conjecture 2
\end{tabular}
\end{center}
The checklist gap is the same for every flagship entry: none of these papers
gives a single if-and-only-if comparison of the ANI exposure point-score map,
the Leung network-cluster covariance map, and the design-orbit randomization
map indexed simultaneously by \((\rho,\epsilon_M,\eta,r,b_n,\Omega_n)\).

\section{Formal setup}
For each \(n\), let \(G_n=(V_n,E_n)\) be a known undirected network with
\(|V_n|=n\), graph distance \(d_n(\cdot,\cdot)\), empirical degree law
\(\rho_n\Rightarrow\rho\), and treatment assignment \(Z_n\in\{0,1\}^n\).
The potential outcome for unit \(i\) is \(Y_{i,n}(z)\).  For a fixed radius
\(r\), the analyst observes an exposure map \(M_{r,i}(z)=(z_i,S_{r,i}(z))\),
where \(S_{r,i}(z)\) is a known additive summary of treatments within
distance \(r\).  For an exposure label \(e\), define the exposure fiber
\(\Gamma_{i,n}(e)=\{z:M_{r,i}(z)=e\}\) and the exposure-label potential outcome
\[
  \bar Y_{i,n}(e)=
  \sum_{z\in\Gamma_{i,n}(e)}
  Y_{i,n}(z)\Pr_n(Z_n=z\mid Z_n\in\Gamma_{i,n}(e)),
\]
with the analogous orbit-averaged version when the conditioning is restricted
to a valid \(\Omega_n\)-orbit.  The target is the finite-population
direct-plus-spillover contrast
\[
  \tau_{ds,n}(r)=
  \frac1n \sum_{i\in V_n}
  \{\bar Y_{i,n}(e_{1,i})-\bar Y_{i,n}(e_{0,i})\},
\]
where \(e_{1,i}\) and \(e_{0,i}\) are the two locked exposure labels
\((1,s_1)\) and \((0,s_0)\).

Let \(\hat\tau_{\mathrm{IPW},n}\) be the residualized exposure-IPW point
estimator associated with the radius-\(r\) map, and let
\(\hat\tau_{\mathrm{RT},n}\) be the design-orbit linear contrast tested by the
randomization procedure.  Network cluster-robust inference does not introduce a
new point estimator in this proposal: it supplies a covariance operator for the
same exposure-score estimator.  Write \(P_{\mathrm{ANI},n}(r)\) for the
radius-\(r\) point-score projection, \(P_{\mathrm{RT},n}(\Omega_n)\) for the
design-orbit point-score projection, \(V_{\mathrm{HAC},n}(r)\) for the network
HAC covariance operator attached to \(\hat\tau_{\mathrm{IPW},n}\),
\(V_{\mathrm{NCR},n}(b_n)\) for Leung-style low-conductance
network-cluster-robust covariance with bandwidth/partition scale \(b_n\), and
\(V_{\mathrm{RT},n}(\Omega_n)\) for the design-orbit randomization covariance.
Let \(\mathcal H_n\) be the finite-dimensional real Hilbert space of weighted
residual score directions with inner product
\(\langle u,v\rangle_{\rho,n}=u^{\transpose}W_{\rho,n}v\), where
\(W_{\rho,n}\) is the diagonal degree-weight matrix induced by the empirical
degree law.  Covariance-operator differences are evaluated as linear maps on
\(\mathcal H_n\), and the stacked range of point-score and covariance
differences is denoted \(\mathcal K_n\).  All norms and distances below are
the induced Hilbert norms unless a display says otherwise.  Define the
observable compatibility operator \(\mathcal A_n:\mathcal H_n\to\mathcal K_n\)
by
\[
  \mathcal A_n =
  \begin{bmatrix}
  P_{\mathrm{ANI},n}(r)-P_{\mathrm{RT},n}(\Omega_n)\\
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{NCR},n}(b_n)\\
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{RT},n}(\Omega_n)
  \end{bmatrix} W_{\rho,n}^{1/2}.
\]
Write its point-score row block and covariance row block as
\[
  \mathcal A^P_n
  =
  \{P_{\mathrm{ANI},n}(r)-P_{\mathrm{RT},n}(\Omega_n)\}W_{\rho,n}^{1/2},
  \qquad
  \mathcal A^V_n
  =
  \begin{bmatrix}
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{NCR},n}(b_n)\\
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{RT},n}(\Omega_n)
  \end{bmatrix} W_{\rho,n}^{1/2}.
\]
The sensitivity object is finite-dimensional.  Let
\(\mathcal B_n=\{h_{1,n},\ldots,h_{m_n,n}\}\) be the observed residual-score
basis induced by the exposure labels, design orbits, and cluster/HAC score
products; every \(u\in\mathcal H_n\) is identified with its coordinate vector
in \(\R^{m_n}\).  Let \(\theta\in\R^{q_n}\) denote omitted-tail additive
response coefficients on the analyst-declared outside-radius atoms.  The
primitive data maps are
\[
  B^u_n\in\R^{m_n\times q_n},\quad
  R^{\mathrm{add}}_n\in\R^{a_n\times q_n},\quad
  R^{\Omega}_n\in\R^{o_n\times q_n},\quad
  B^{M}_n\in\R^{s_n\times q_n},\quad
  B^{\mathrm{tail}}_n\in\R^{t_n\times q_n}.
\]
Here \(B^u_n\) vectorizes omitted-tail coefficients into the common score
space; \(R^{\mathrm{add}}_n\theta=0\) imposes additive ANI response structure;
\(R^\Omega_n\theta=0\) imposes any analyst-declared design-orbit symmetry;
\(B^M_n\theta\) extracts the score mass on exposure labels declared
misspecified; and \(B^{\mathrm{tail}}_n\theta\) extracts the weighted
outside-radius tail.  The entries of \(B^u_n\), \(R^\Omega_n\), \(B^M_n\),
\(B^{\mathrm{tail}}_n\), \(W_{\rho,n}\), and \(\mathcal A_n\) are computed
from the observed graph \(G_n\), exposure map \(M_r\), assignment
probabilities, design-orbit incidence matrix, degree weights, and bandwidth
\(b_n\).  The matrix \(R^{\mathrm{add}}_n\) is determined by the declared
additive ANI response class.  The scalars \(\epsilon_M\) and \(\eta\) are
analyst-declared sensitivity radii; \(\theta\) and the realized omitted tail
are not observed.

Define \(\mathcal C_n(\eta)\subseteq\mathcal H_n\) by the explicit second-order
cone system
\[
\begin{aligned}
\mathcal C_n(\eta)=\{u\in\R^{m_n}:&\ \exists \theta\in\R^{q_n}\text{ with }
u=B^u_n\theta,\quad
R^{\mathrm{add}}_n\theta=0,\quad R^\Omega_n\theta=0,\\
&\ \|B^M_n\theta\|_{1,\rho,n}
     \le \epsilon_M\|u\|_{\rho,n},\quad
   \|B^{\mathrm{tail}}_n\theta\|_{2,\rho,n}
     \le \eta\|u\|_{\rho,n}\}.
\end{aligned}
\]
Thus \(\mathcal C_n(\eta)\) is design-observable after the analyst declares
\((\epsilon_M,\eta)\), while the true omitted-tail score need not be observed;
it is assumed to belong to one such finite cone.  Let
\(\mathcal N_n(\eta)=\ker(\mathcal A_n)\cap\mathcal C_n(\eta)\).
Also let
\(\mathcal N^P_n(\eta)=\ker(\mathcal A^P_n)\cap\mathcal C_n(\eta)\) and
\(\mathcal N^V_n(\eta)=\ker(\mathcal A^V_n)\cap\mathcal C_n(\eta)\).
Let \(S_n(\eta)=\{u\in\mathcal C_n(\eta):\|u\|_{\rho,n}=1\}\), and define the
observable finite-dimensional programs
\[
  \Delta_{\eta,n}=
  \sup_{u\in S_n(\eta)} \|\mathcal A_n u\|,
  \qquad
  \Delta^P_{\eta,n}=
  \sup_{u\in S_n(\eta)} \|\mathcal A^P_n u\|,
  \qquad
  \Delta^V_{\eta,n}=
  \sup_{u\in S_n(\eta)} \|\mathcal A^V_n u\|,
  \qquad
  \mu_{\star,n}(\eta)=
  \inf_{\substack{u\in S_n(\eta)\\
  \operatorname{dist}(u,\mathcal N_n(\eta))>0}}
  \frac{\|\mathcal A_n u\|}
       {\operatorname{dist}(u,\mathcal N_n(\eta))}.
\]
The limits \(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)=\limsup_n
\Delta_{\eta,n}\), \(\Delta^P_\eta=\limsup_n\Delta^P_{\eta,n}\),
\(\Delta^V_\eta=\limsup_n\Delta^V_{\eta,n}\), and
\(\mu_\star(\eta)=\liminf_n\mu_{\star,n}(\eta)\) are the observable
compatibility thresholds and cone-restricted singular value; if
the infimum set is empty because \(S_n(\eta)\subseteq\mathcal N_n(\eta)\), set
\(\mu_{\star,n}(\eta)=+\infty\) and \(\Delta_{\eta,n}=0\).
When the cones converge, write their limit as \(\mathcal C(\eta)\).  Define the
observable diagnostic envelope
\[
  \underline d_{\eta,n}=
  \inf_{u\in\mathcal C_n(\eta)}
  \operatorname{dist}(u,\mathcal N_n(\eta)),
  \qquad
  \overline d_{\eta,n}=
  \sup_{u\in\mathcal C_n(\eta)}
  \operatorname{dist}(u,\mathcal N_n(\eta)),
\]
with limits \(\underline d_\eta\) and \(\overline d_\eta\) when they exist.
Let
\(R_{M,n}=(I-\Pi_{M_r})T_n\) be the omitted-tail operator for the true
interference response \(T_n:z\mapsto (Y_{i,n}(z))_{i\le n}\), where
\(\Pi_{M_r}\) is the weighted projection onto the sigma-field generated by the
radius-\(r\) exposure map.  Let
\(\operatorname{vec}_{\rho,n}(R_{M,n})\in\mathcal H_n\) be the Riesz
representer of the linear score functional induced by this omitted-tail
operator; this is the common score-space vectorization used to compare
operators, cone elements, and covariance differences.  Set
\(U_{M,n}=\operatorname{vec}_{\rho,n}(R_{M,n})\), and define the true-tail
sensitivity distance
\[
  \mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)
  =
  \limsup_n \operatorname{dist}(U_{M,n},\mathcal N_n(\eta)).
\]
This \(\mu_{\perp}\) is a sensitivity parameter for the realized omitted tail,
not the flagship frontier; the observable statement is that any
analyst-declared \(\eta\)-cone implies
\(\underline d_\eta\le \mu_{\perp}\le \overline d_\eta\), while uniform
equivalence over the whole declared class is governed by \(\Delta_\eta=0\).

\begin{example}[Two-score design-orbit computation]\label{ex:two-score-orbit}
Take a toy design with two residual score coordinates: \(u_1\) is the
radius-\(r\) exposure score on a within-orbit edge, and \(u_2\) is the
cross-orbit leakage score.  Set \(W_{\rho,n}=I_2\), let the declared cone be
\(\mathcal C_n(\eta)=\R^2_+\) after the finite system above is evaluated, and
suppose the observed point and covariance row blocks reduce to
\[
  \mathcal A^P_n=\begin{bmatrix}1&-1\end{bmatrix},
  \qquad
  \mathcal A^V_n=\begin{bmatrix}0&1\\1&0\end{bmatrix},
  \qquad
  \mathcal A_n u=(u_1-u_2,u_2,u_1).
\]
Then
\(\mathcal N_n(\eta)=\ker(\mathcal A_n)\cap\R^2_+=\{0\}\),
\(S_n(\eta)=\{u\ge0:u_1^2+u_2^2=1\}\),
\[
  \Delta_{\eta,n}=\sup_{u\in S_n(\eta)}
     \{(u_1-u_2)^2+u_1^2+u_2^2\}^{1/2}=\sqrt2,
\]
while \(\Delta^P_{\eta,n}=1\) and \(\Delta^V_{\eta,n}=1\).  The example is
not a proposed theorem; it records the intended audit trail for Stage~0:
construct \(B^u_n\) and the cone, stack the point and covariance row blocks,
compute \(\mathcal N_n(\eta)\), and check whether the violation is a
point-score violation, a covariance-only violation, or both.
\end{example}
When \(b_n\) has an asymptotic scaling limit, write that limit as \(b\).  The design-orbit
variance bound is the variance of the \(V_{\mathrm{RT}}(\Omega)\) projected
score under the randomization law restricted to valid \(\Omega\)-orbits.  For
the direct-plus-spillover target contrast \(a_{ds}\), define the scalar
network-cluster efficiency gap
\[
  L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)
  =
  a_{ds}^{\transpose}\{V_{\mathrm{NCR}}(b)-V_{\mathrm{RT}}(\Omega)\}a_{ds}.
\]
When the design-orbit covariance is the efficient covariance in the active
score class, this scalar is nonnegative; otherwise the proposal treats its
positive part as the loss and its sign as evidence that the two procedures are
ranking different score classes.

\begin{verbatim}
(qid, specialization, p, assignment, target, regression)
= (panel_approx_nbhd_interference, v1,
   p = (r, rho, epsilon_M, eta, b_n, design_orbits),
   assignment = triangular-array randomized network experiment with
      bounded expected degree law rho, known graph G_n, treatment vector
      Z_n, and a design group Omega_n whose orbits describe the valid
      randomization permutations,
   target = finite-population direct-plus-spillover exposure contrast
      tau_ds(r) between e_1=(own treated, radius-r exposure s_1) and
      e_0=(own control, radius-r exposure s_0), where each exposure-label
      potential outcome is averaged over the assignment law conditional on
      that label,
   regression = exposure-score projection on M_r(i,Z_n), with the ANI
      point-score projection P_ANI(r), the design-orbit point-score
      projection P_RT(Omega_n), and first-order covariance operators
      V_HAC(r), V_NCR(b_n), and V_RT(Omega_n).)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Bounded degree-law limit]\label{ass:degree-law}
The graph sequence satisfies \(\rho_n\Rightarrow\rho\), uniformly bounded
\((2+\xi)\)-moments of degrees for some \(\xi>0\), and no single unit carries
positive asymptotic degree mass after \(W_{\rho,n}\) normalization.
\end{assumption}

\begin{assumption}[Additive ANI response]\label{ass:additive-ani}
Potential outcomes admit an additive own-treatment plus spillover
decomposition with a tail operator \(T_n\) whose contribution outside radius
\(r\) is \(R_{M,n}=(I-\Pi_{M_r})T_n\).  The direct-plus-spillover contrast
\(\tau_{ds,n}(r)\), using the exposure-fiber averaging convention in
Section~6, is uniformly bounded.
\end{assumption}

\begin{assumption}[Exposure misspecification profile and sensitivity cone]\label{ass:misspec-profile}
The radius-\(r\) exposure map misses an asymptotic fraction
\(\epsilon_M\in[0,1)\) of interference-relevant assignments, and the weighted
omitted-tail score \(U_{M,n}\) belongs to an admissible cone
\(\mathcal C_n(\eta)\) for a declared sensitivity radius \(\eta\).  The
cone \(\mathcal C_n(\eta)\) is exactly the finite constraint system in
Section~6 with variables \((u,\theta)\), matrix blocks
\((B^u_n,R^{\mathrm{add}}_n,R^\Omega_n,B^M_n,B^{\mathrm{tail}}_n)\),
misspecification inequality \(\|B^M_n\theta\|_{1,\rho,n}\le
\epsilon_M\|u\|_{\rho,n}\), and tail-radius inequality
\(\|B^{\mathrm{tail}}_n\theta\|_{2,\rho,n}\le\eta\|u\|_{\rho,n}\).  Its
unit slice \(S_n(\eta)\), compatibility program \(\Delta_{\eta,n}\), and
common-null cell \(\mathcal N_n(\eta)\) are computed from the observed graph,
exposure map, assignment law, design orbits, degree weights, bandwidth, and
declared radii.  The null-distance limit
\(\mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)\) exists for the true
unobserved tail, and the design-observable envelope
\([\underline d_\eta,\overline d_\eta]\) brackets all such tails in
\(\mathcal C_n(\eta)\).
\end{assumption}

\begin{assumption}[Randomization positivity and design orbits]\label{ass:design-orbits}
The assignment law gives exposure propensities for \(e_0\) and \(e_1\) bounded
away from zero on the active risk set, and the valid randomization permutations
form a design group \(\Omega_n\) with point-score projection
\(P_{\mathrm{RT},n}(\Omega_n)\) and covariance operator
\(V_{\mathrm{RT},n}(\Omega_n)\).
\end{assumption}

\begin{assumption}[Design-based LLN and point-functional consistency]\label{ass:design-lln}
The residualized exposure-IPW estimator \(\hat\tau_{\mathrm{IPW},n}\) and the
design-orbit linear contrast \(\hat\tau_{\mathrm{RT},n}\) obey triangular-array
laws of large numbers for their respective finite-population point
functionals.  Under correct exposure and equality of the active point-score
projections, these two limiting point functionals both equal
\(\lim_n\tau_{ds,n}(r)\).  More generally, when
\(\mathcal A^P_n U_{M,n}\) has a nonzero limit, the two probability limits
differ by the limiting point-score functional applied to the vectorized
omitted-tail score.
\end{assumption}

\begin{assumption}[Cluster bandwidth and conductance]\label{ass:cluster-bandwidth}
The network-cluster procedure uses bandwidth \(b_n\) and a partition whose
within-cluster conductance and between-cluster edge mass converge to limits
that determine the covariance operator \(V_{\mathrm{NCR},n}(b_n)\) for the
exposure-score estimator.
\end{assumption}

\begin{assumption}[Score and covariance convergence]\label{ass:kernel-convergence}
The point-score projections \(P_{\mathrm{ANI},n}(r)\) and
\(P_{\mathrm{RT},n}(\Omega_n)\), and the covariance operators
\(V_{\mathrm{HAC},n}(r)\), \(V_{\mathrm{NCR},n}(b_n)\), and
\(V_{\mathrm{RT},n}(\Omega_n)\), after degree weighting by \(W_{\rho,n}\),
act on the common Hilbert score space \(\mathcal H_n\) and converge in
operator norm on each active score cone \(\mathcal C_n(\eta)\).  The
omitted-tail operator \(R_{M,n}\) is compared to cone elements only through the
vector \(U_{M,n}=\operatorname{vec}_{\rho,n}(R_{M,n})\in\mathcal H_n\).  The
limits define \(\mathcal A\), its row blocks \(\mathcal A^P\) and
\(\mathcal A^V\), \(\mathcal N(\eta)\), \(\mathcal N^P(\eta)\),
\(\mathcal N^V(\eta)\), \(\Delta_\eta\), \(\Delta^P_\eta\),
\(\Delta^V_\eta\), \(\mu_\star(\eta)\), \(\underline d_\eta\),
\(\overline d_\eta\), and the three limiting variance functionals.
\end{assumption}

\begin{assumption}[Nondegenerate active signal class]\label{ass:nondegenerate-signal}
The omitted-tail directions considered in the strict-separation claim form an
open subset of the active score cone \(\mathcal C_n(\eta)\), and whenever
\(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)>0\) their compatibility violation is
bounded away from zero on at least one row block of \(\mathcal A\).  For
true-tail statements, the vectorized omitted-tail score \(U_{M,n}\) has
positive limiting distance from \(\mathcal N_n(\eta)\) exactly when
\(\mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)>0\).
\end{assumption}

\begin{assumption}[Contrast-specific design efficiency]\label{ass:contrast-efficiency}
For the target contrast vector \(a_{ds}\), \(V_{\mathrm{RT}}(\Omega)\) is the
design-orbit efficient covariance on the active randomization score class, so
\(L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)\ge0\) whenever
\(V_{\mathrm{NCR}}(b)\) and \(V_{\mathrm{RT}}(\Omega)\) target the same
point-score law.  If this ordering fails, the signed scalar
\(a_{ds}^{\transpose}\{V_{\mathrm{NCR}}(b)-V_{\mathrm{RT}}(\Omega)\}a_{ds}\)
is still the reported covariance separation for the \(a_{ds}\) contrast.
\end{assumption}

\begin{assumption}[Oracle exposure/design compatibility]\label{ass:oracle-compatibility}
The exposure map is correct \((\epsilon_M=0)\), \(b_n\ge r\) eventually, and on
the active score cone \(\mathcal C_n(\eta)\) the exposure, cluster, and orbit sigma-fields generate
the same projection: \(P_{\mathrm{ANI},n}=P_{\mathrm{RT},n}\) and
\(V_{\mathrm{HAC},n}=V_{\mathrm{NCR},n}=V_{\mathrm{RT},n}\) after degree
weighting.
\end{assumption}

\begin{assumption}[Partial-interference design corner]\label{ass:partial-interference-corner}
The graph is a disjoint union of design groups, radius \(r\) contains each
group, there are no cross-group tail effects, and the design group
\(\Omega_n\) is the direct product of the within-group design-compatible
permutation groups.  Equivalently, the valid \(\Omega_n\)-orbits coincide with
the within-group exposure fibers used by the partial-interference
randomization test.
\end{assumption}

\section{Main results}
\begin{theorem}[Oracle projection and covariance collapse]\label{thm:oracle-collapse}
Under Assumptions~\ref{ass:degree-law}, \ref{ass:additive-ani},
\ref{ass:misspec-profile}, \ref{ass:design-orbits}, \ref{ass:design-lln},
\ref{ass:cluster-bandwidth}, \ref{ass:kernel-convergence}, and
\ref{ass:oracle-compatibility},
\[
  \plim_n \hat\tau_{\mathrm{IPW},n}
  =
  \plim_n \hat\tau_{\mathrm{RT},n}
  =
  \lim_n \tau_{ds,n}(r),
\]
and the three first-order covariance operators
\(V_{\mathrm{HAC}}\), \(V_{\mathrm{NCR}}\), and \(V_{\mathrm{RT}}\) are
identical on the active score cone.
\end{theorem}

\paragraph{Why this is new and worth studying.}
The closest paper is \citet{Leung2022ANI}, which proves ANI consistency and
uses network HAC, but does not include the equality-of-projections and
equality-of-covariance conditions needed to compare against
\citet{Leung2023NCRI} and \citet{BasseDingFellerToulis2024}.  This theorem is
mainly a sanity benchmark: it gives users of the Basse--Ding--Feller--Toulis
group-formation tests the exact corner in which the Leung ANI exposure
contrast and the network-cluster covariance law are the same objects, without
misstating network cluster-robust inference as a separate point estimator.

\begin{conjecture}[Spectral equivalence frontier (NOT YET PROVED)]\label{conj:spectral-frontier}
Under Assumptions~\ref{ass:degree-law}--\ref{ass:nondegenerate-signal}, the
ANI exposure-IPW point functional, the design-orbit randomization point
functional, and the HAC/network-cluster/randomization first-order covariance
operators are uniformly equivalent over the declared sensitivity class
\(\mathcal C(\eta)\) if and only if the observable compatibility program
\[
  \Delta_\eta(\rho,\epsilon_M,r,b,\Omega)=0.
\]
Equivalently, every admissible omitted-tail score direction lies in the common
null cell \(\mathcal N(\eta)\).  When \(\Delta_\eta>0\), the sharp detectable
gap over the declared class is conjectured to satisfy
\[
  \mu_\star(\eta)
  \sup_{u\in S(\eta)}\operatorname{dist}(u,\mathcal N(\eta))
  \le
  \Delta_\eta
  \le
  \|\mathcal A\|
  \sup_{u\in S(\eta)}\operatorname{dist}(u,\mathcal N(\eta)).
\]
For the realized, unobserved omitted tail, true-tail equivalence is instead
the sensitivity statement \(U_M\in\mathcal N(\eta)\), or equivalently
\(\mu_{\perp}=0\).  If \(\mu_{\perp}>0\) and \(\mu_\star(\eta)>0\), the
combined point-score/covariance procedure-object gap for that true tail is
conjectured to be bounded below by \(\mu_\star(\eta)\mu_{\perp}\) up to a
vanishing triangular-array error; point probability limits differ only when
the point-score row block satisfies \(\mathcal A^P U_M\ne0\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
The closest published results are \citet{Leung2022ANI},
\citet{Leung2023NCRI}, \citet{BasseDingFellerToulis2024}, and
\citet{GaoDing2025Network}, with \citet{PuelzBasseFellerToulis2022} and
\citet{WeinsteinNevo2026} as the closest randomization and misspecification
comparators.  The precise epsilon-gap is that those papers give one-sided
validity or bias statements for exposure IPW/regression/HAC, cluster-robust
inference, graph-theoretic randomization tests, or misspecified-network
estimation, but none defines the joint compatibility operator \(\mathcal A\),
its sensitivity common-null cell \(\mathcal N(\eta)\), or the observable
finite program \(\Delta_\eta\) whose zero/nonzero value is an if-and-only-if
equivalence frontier indexed by
\((\rho,\epsilon_M,\eta,r,b_n,\Omega_n)\).  Proving the conjecture would
give the Leung 2023 spectral-clustering workflow and the Gao--Ding WLS/Hajek
workflow a direct diagnostic for when a network-robust standard error is merely
a variance implementation for the ANI estimand and when it is attached to a
different first-order law.

\begin{conjecture}[Strict separation above the frontier (NOT YET PROVED)]\label{conj:strict-separation}
Under Assumptions~\ref{ass:degree-law}--\ref{ass:contrast-efficiency}, if
\(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)>0\),
\(\mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)>0\), and
\(\mu_\star(\eta)>0\), then there is an open set of graph/design/outcome
triangular arrays with the same limit tuple
\((\rho,\epsilon_M,\eta,r,b,\Omega)\)
on which at least one named procedure object separates: either the ANI and
randomization point functionals differ, or their first-order covariance
operators differ, or both.

More sharply, if the realized tail has a nonzero point-row violation,
\[
  \liminf_n \|\mathcal A^P_n U_{M,n}\|>0,
\]
then
\[
  \plim_n \hat\tau_{\mathrm{IPW},n}
  \ne
  \plim_n \hat\tau_{\mathrm{RT},n},
\]
and ANI differs from \(\tau_{ds}(r)\) by a linear functional of \(R_M\).  If
instead \(\lim_n\|\mathcal A^P_n U_{M,n}\|=0\) but
\(\liminf_n\|\mathcal A^V_n U_{M,n}\|>0\), then the conjectured separation is
covariance-only: the two point limits may agree, while network-cluster-robust
inference supplies a covariance law for the exposure-score estimator that
differs from the HAC or design-orbit covariance law.  For the target contrast,
the reported scalar separation is
\(L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)\) when that quadratic form is
nonzero; otherwise the nonzero covariance row identifies a different contrast
or score direction whose first-order law separates.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
The closest negative comparator is the invalid-permutation phenomenon in
\citet{BasseDingFellerToulis2024} and the biclique-conditioning construction
in \citet{PuelzBasseFellerToulis2022}; the epsilon-gap is that their
obstructions concern randomization validity for a chosen null, whereas this
conjecture promotes incompatibility to an open class of graph sequences and
compares three named procedure objects.  \citet{WeinsteinNevo2026} is the
closest bias comparator, but its network-misspecification bias and robust
multi-network estimator do not include the cluster-bandwidth or design-orbit
frontier.  Resolving this conjecture would tell analysts using
\citet{Savje2024MisspecifiedExposure} style misspecified exposure contrasts
when estimability is not enough: the exposure estimand can be estimable while
the design-based randomization null and cluster covariance target are
different objects.

\section{Sanity-check corollaries}
\begin{corollary}[Correct-exposure ANI reduction]\label{cor:ani-reduction}
Under Assumptions~\ref{ass:degree-law}--\ref{ass:kernel-convergence},
\ref{ass:design-lln}, and \ref{ass:oracle-compatibility}, if
\(P_{\mathrm{ANI}}(r)=P_{\mathrm{RT}}(\Omega)\) and
\(V_{\mathrm{HAC}}(r)=V_{\mathrm{NCR}}(b)=V_{\mathrm{RT}}(\Omega)\) on
\(\mathcal C(\eta)\), then
Theorem~\ref{thm:oracle-collapse} reduces to the Leung ANI exposure contrast
with network HAC variance.
\end{corollary}

\begin{corollary}[Partial-interference randomization reduction]\label{cor:partial-interference}
Under Assumptions~\ref{ass:design-orbits} and \ref{ass:kernel-convergence}, if
Assumption~\ref{ass:partial-interference-corner} also holds, then
\(P_{\mathrm{RT}}(\Omega)\) equals the exposure-orbit projection and the
randomization component reduces to the Hudgens--Halloran/Basse--Ding--Feller--
Toulis partial-interference null because the valid permutations are exactly
the within-group design-compatible orbit permutations.
\end{corollary}

\section{Proof-sketch route}
The proof route is finite-dimensional score algebra followed by operator
limits.  First write the exposure-IPW and randomization-test point contrasts as
linear functionals of the same finite-population potential-outcome vector under
the exposure-fiber averaging convention, and write HAC, network-cluster, and
randomization inference as covariance operators for the corresponding
residualized scores.  The oracle theorem follows by the strengthened hypothesis
that the exposure, cluster, and orbit projections and covariance operators
coincide on the active score cone.  The spectral frontier would then reduce to a
finite-dimensional cone program for \(\mathcal A_n\):
\(\Delta_{\eta,n}=0\) exactly when every admissible omitted-tail score
direction is annihilated by the pairwise point-score and covariance
differences, while a realized tail with positive sensitivity null-distance
creates a nonzero pairwise procedure-object gap of order at least
\(\mu_\star(\eta)\mu_{\perp}\).  The point-limit claim is checked only through
the point row \(\mathcal A^P_n\); if that row vanishes while
\(\mathcal A^V_n\) does not, the proof route yields covariance-only
separation rather than unequal probability limits.  The covariance separation
is checked through the scalar quadratic form
\(L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)\), avoiding any claim that a
raw covariance-operator difference is itself a scalar loss.  The boundary
cases to compute explicitly are a
three-block graph with one cross-block leakage edge, a star-like high-degree
exposure misspecification sequence, and a group-formation design where one
exposure permutation is infeasible; these small examples should identify the
right cone \(\mathcal C(\eta)\) and the exact common-null certificate.

\section{Honest scope flags}
Theorem~\ref{thm:oracle-collapse} is intended as a routine benchmark theorem,
not the novelty-bearing contribution.  Conjectures~\ref{conj:spectral-frontier}
and \ref{conj:strict-separation} are not yet proved; in particular, the exact
form of \(\mu_\star(\eta)\) may need additional cone-regularity conditions if
the active omitted-tail directions are not a full linear subspace.  Version 4
separates the observable frontier \(\Delta_\eta\) from the true-tail
sensitivity distance \(\mu_{\perp}\); the former is the flagship threshold and
the latter is reported only after the analyst declares \(\eta\).  The proposal
does not claim a new finite-sample
randomization test, a new cluster algorithm, or a new exposure-IPW estimator.
It treats network cluster-robust inference as a covariance operator for a named
exposure-score estimator, not as a distinct point estimator.  It also does not
claim that Basse--Ding--Feller--Toulis randomization tests estimate an average
effect in every ANI model; the point is to characterize precisely when their
design-orbit null coincides with the ANI contrast.  Version 2 withdraws the v1
phrasing that treated network-cluster-robust inference as a separate point
estimator and replaces the norm-only threshold with a common-null-distance
frontier.  Version 3 recasts that frontier as sensitivity-indexed, adds the
Gao--Ding network-regression/HAC comparison, and scalarizes the covariance
separation through \(L_{\mathrm{NCR}\to\mathrm{RT}}\).  Version 4 adds the
Puelz--Basse--Feller--Toulis and Weinstein--Nevo comparators, defines the
common score Hilbert space, replaces ordinary estimator limits in the strict
separation claim with probability limits, and strengthens the
partial-interference corner by requiring design-compatible within-group
orbits.  Version 5 adds an explicit design-based LLN and point-functional
consistency assumption, splits the compatibility operator into point-score and
covariance row blocks, and weakens Conjecture~\ref{conj:strict-separation} so
covariance-only violations imply covariance separation rather than unequal
point probability limits.  Version 2 of angle 1 replaces the informal
sensitivity-cone description with an explicit finite-dimensional cone system
and adds a two-score design-orbit computation of \(\mathcal A_n\),
\(\mathcal N_n(\eta)\), \(\Delta_{\eta,n}\), \(\Delta^P_{\eta,n}\), and
\(\Delta^V_{\eta,n}\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft proposing a spectral frontier for
ANI, network-cluster-robust, and design-orbit randomization functionals; prior
verdict: none.
\item v2 (revise) -- defined exposure-fiber averaging, recast NCR as a
covariance operator for the exposure-score estimator, strengthened oracle
projection equality, and replaced the norm-only threshold with a common-null
distance frontier; prior verdict: REVISE.
\item v3 (revise) -- recast \(\mu_{\perp}\) as a sensitivity parameter with an
observable cone envelope, added the Gao--Ding network-regression/HAC comparison,
and defined strict covariance separation by the scalar
\(L_{\mathrm{NCR}\to\mathrm{RT}}\); prior verdict: REVISE.
\item v4 (revise) -- replaced the unobserved frontier by the observable
\(\Delta_\eta\) cone program, added Puelz--Basse--Feller--Toulis 2022 and
Weinstein--Nevo 2026, unified all tail/operator comparisons in
\(\mathcal H_n\), used probability limits for random estimators, and tightened
the partial-interference design-orbit reduction; prior verdict: REVISE.
\item v5 (revise) -- added the design-based LLN/point-consistency assumption,
defined the point and covariance row blocks \(\mathcal A^P\) and
\(\mathcal A^V\), split strict separation into point-functional and
covariance-only cases, and added the misspecified-exposure
partial-identification comparator note; prior verdict: REVISE.
\item v1 (revise, angle 1) -- added the named literature checklist mapping
Leung 2022, Leung 2023, Basse--Ding--Feller--Toulis 2024, Gao--Ding 2025,
Puelz--Basse--Feller--Toulis 2022, Weinstein--Nevo 2026, and Savje 2024 to the
specific \S8 results they threaten; prior verdict: REVISE.
\item v2 (revise, angle 1) -- defined \(\mathcal C_n(\eta)\) as a finite
constraint system with variables, observed matrix blocks, and declared
sensitivity radii, and added a two-score design-orbit calculation for
\(\mathcal A_n\), \(\mathcal N_n(\eta)\), and the point/covariance row split;
prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Aronow and Samii(2017)]{AronowSamii2017Exposure}
Aronow, P. M. and C. Samii (2017).
Estimating average causal effects under general interference, with application
to a social network experiment.
\emph{Annals of Applied Statistics} 11(4), 1912--1947.
doi:10.1214/16-AOAS1005.

\bibitem[Basse, Ding, Feller, and Toulis(2024)]{BasseDingFellerToulis2024}
Basse, G., P. Ding, A. Feller, and P. Toulis (2024).
Randomization tests for peer effects in group formation experiments.
\emph{Econometrica} 92(2), 567--590.
doi:10.3982/ECTA20134.

\bibitem[Basse, Feller, and Toulis(2019)]{BasseFellerToulis2019}
Basse, G. W., A. Feller, and P. Toulis (2019).
Randomization tests of causal effects under interference.
\emph{Biometrika} 106(2), 487--494.
doi:10.1093/biomet/asy072.

\bibitem[Conley(1999)]{Conley1999Spatial}
Conley, T. G. (1999).
GMM estimation with cross sectional dependence.
\emph{Journal of Econometrics} 92(1), 1--45.
doi:10.1016/S0304-4076(98)00084-0.

\bibitem[Gao and Ding(2025)]{GaoDing2025Network}
Gao, Mengsi and P. Ding (2025).
Causal inference in network experiments: regression-based analysis and
design-based properties.
\emph{Journal of Econometrics} 252, 106119.
doi:10.1016/j.jeconom.2025.106119.

\bibitem[Hudgens and Halloran(2008)]{HudgensHalloran2008}
Hudgens, M. G. and M. E. Halloran (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.
doi:10.1198/016214508000000292.

\bibitem[Kojevnikov, Marmer, and Song(2021)]{KojevnikovMarmerSong2021}
Kojevnikov, D., V. Marmer, and K. Song (2021).
Limit theorems for network dependent random variables.
\emph{Journal of Econometrics} 222(2), 882--908.
doi:10.1016/j.jeconom.2020.05.019.

\bibitem[Leung(2022)]{Leung2022ANI}
Leung, M. P. (2022).
Causal inference under approximate neighborhood interference.
\emph{Econometrica} 90(1), 267--293.
doi:10.3982/ECTA17841.

\bibitem[Leung(2023)]{Leung2023NCRI}
Leung, M. P. (2023).
Network cluster-robust inference.
\emph{Econometrica} 91(2), 641--667.
doi:10.3982/ECTA19816.

\bibitem[Puelz, Basse, Feller, and Toulis(2022)]{PuelzBasseFellerToulis2022}
Puelz, D., G. Basse, A. Feller, and P. Toulis (2022).
A graph-theoretic approach to randomization tests of causal effects under
general interference.
\emph{Journal of the Royal Statistical Society: Series B} 84(1), 174--204.
doi:10.1111/rssb.12478.

\bibitem[Savje(2024)]{Savje2024MisspecifiedExposure}
Savje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions
and assumptions.
\emph{Biometrika} 111(1), 1--15.
doi:10.1093/biomet/asad019.

\bibitem[Weinstein and Nevo(2026)]{WeinsteinNevo2026}
Weinstein, B. and D. Nevo (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.
doi:10.1093/biomtc/ujag023.
\end{thebibliography}

\end{document}
