% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=panel\_approx\_nbhd\_interference, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{panel\_approx\_nbhd\_interference} / \texttt{v1}%
  \\ \large\textit{A spectral compatibility theorem for ANI, network-cluster, and design-orbit functionals}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies the population version of a residualized exposure-score
projection for a triangular-array network experiment, together with the
network-HAC, network-cluster-robust, and design-orbit randomization covariance
operators attached to that score.  The causal target is the finite-population
direct-plus-spillover exposure contrast \(\tau_{ds,n}(r)\) between the locked
labels \(e_1=(1,s_1)\) and \(e_0=(0,s_0)\), where each exposure-label potential
outcome is averaged over the assignment law conditional on that label.  The
estimand-defining functional is the computable map that takes the observed
graph, assignment law, exposure map, design orbits, and declared sensitivity
cone to the point-score projections \(P_{\mathrm{ANI},n}(r)\) and
\(P_{\mathrm{RT},n}(\Omega_n)\), the covariance operators
\(V_{\mathrm{HAC},n}(r)\), \(V_{\mathrm{NCR},n}(b_n)\), and
\(V_{\mathrm{RT},n}(\Omega_n)\), and the cone program
\(\Delta_{\eta,n}=\sup_{\|u\|_{\rho,n}=1,u\in\mathcal C_n(\eta)}
\|\mathcal A_nu\|\).  The main result confirms the Stage -1 spectral frontier
as a procedure-equivalence theorem: uniform equality of the named point and
covariance procedure objects over the declared sensitivity class is equivalent
to \(\Delta_\eta=0\).  This is not, by itself, target identification; the ANI
coefficient equals \(\tau_{ds}(r)\) only when its own residual tail
contamination functional vanishes.  For a realized omitted-tail score, the
probability-limit and covariance gaps decompose into explicit point-row and
covariance-row terms, so strict separation can be point-level,
covariance-only, or both.
\end{abstract}

\section{Introduction}
Network experiments with interference force the analyst to choose both an
estimand and an inferential geometry.  A radius-\(r\) exposure map defines a
direct-plus-spillover contrast, a graph-distance or network-cluster covariance
procedure defines the first-order law used for uncertainty quantification, and
a randomization test defines a design-orbit null.  These three choices are
often used in the same empirical analysis, but they need not target the same
population object once the true interference response has tail components not
captured by the declared exposure map.

Existing results justify each object separately under its own conditions.
Approximate neighborhood interference gives exposure-based estimators and
network-HAC covariance formulas; network cluster-robust inference controls
dependence through graph partitions; and design-orbit randomization tests give
finite-sample validity for a specified randomization null.  What is missing is
a theorem that compares the three procedure maps on the same score space and
says exactly when they collapse to one direct-plus-spillover object.

This note gives that comparison.  It writes the population exposure-score and
randomization point functionals as the target contrast plus an omitted-tail
linear functional, and it stacks the point-score and covariance discrepancies
in a single compatibility operator \(\mathcal A_n\).  The resulting cone
program \(\Delta_{\eta,n}\) is computable from the observed graph, assignment
law, exposure map, design orbits, and the analyst-declared sensitivity cone.
The zero set of this program is the common-null cell in which ANI point scores,
network-HAC or network-cluster covariance, and design-orbit randomization
covariance are interchangeable as procedure objects.  A separate
target-contamination functional records whether those point procedures equal
\(\tau_{ds,n}(r)\) or merely share the same omitted-tail bias.  Outside the
common-null cell the row blocks of \(\mathcal A_n\) identify the precise
point or covariance disagreement.

The usefulness of the result is diagnostic.  Before treating exposure-IPW,
network-cluster covariance, and exact randomization analyses as alternative
implementations of one idea, an analyst can compute the compatibility program
and report which row block fails.  The theorem also prevents a common
overstatement: a covariance incompatibility alone does not imply a different
point estimand, a point-score incompatibility creates disagreement between
point procedures, and target identification additionally requires the relevant
point contamination term to be zero.

\paragraph{Motivating conjecture(s).}
The Stage -1 proposal stated the following two conjectures; the main theorem
below confirms both, with the row-specific interpretation already present in
the second conjecture.

\begin{conjecture}[Spectral equivalence frontier (NOT YET PROVED)]\label{conj:spectral-frontier}
Under Assumptions~\ref{ass:degree-law}--\ref{ass:nondegenerate-signal}, the
ANI exposure-IPW point functional, the design-orbit randomization point
functional, and the HAC/network-cluster/randomization first-order covariance
operators are uniformly equivalent over the declared sensitivity class
\(\mathcal C(\eta)\) if and only if the observable compatibility program
\[
  \Delta_\eta(\rho,\epsilon_M,r,b,\Omega)=0.
\]
Equivalently, every admissible omitted-tail score direction lies in the common
null cell \(\mathcal N(\eta)\).  When \(\Delta_\eta>0\), the sharp detectable
gap over the declared class is conjectured to satisfy
\[
  \mu_\star(\eta)
  \sup_{u\in S(\eta)}\operatorname{dist}(u,\mathcal N(\eta))
  \le
  \Delta_\eta
  \le
  \|\mathcal A\|
  \sup_{u\in S(\eta)}\operatorname{dist}(u,\mathcal N(\eta)).
\]
For the realized, unobserved omitted tail, true-tail equivalence is instead
the sensitivity statement \(U_M\in\mathcal N(\eta)\), or equivalently
\(\mu_{\perp}=0\).  If \(\mu_{\perp}>0\) and \(\mu_\star(\eta)>0\), the
combined point-score/covariance procedure-object gap for that true tail is
conjectured to be bounded below by \(\mu_\star(\eta)\mu_{\perp}\) up to a
vanishing triangular-array error; point probability limits differ only when
the point-score row block satisfies \(\mathcal A^P U_M\ne0\).
\end{conjecture}

\begin{conjecture}[Strict separation above the frontier (NOT YET PROVED)]\label{conj:strict-separation}
Under Assumptions~\ref{ass:degree-law}--\ref{ass:contrast-efficiency}, if
\(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)>0\),
\(\mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)>0\), and
\(\mu_\star(\eta)>0\), then there is an open set of graph/design/outcome
triangular arrays with the same limit tuple
\((\rho,\epsilon_M,\eta,r,b,\Omega)\)
on which at least one named procedure object separates: either the ANI and
randomization point functionals differ, or their first-order covariance
operators differ, or both.

More sharply, if the realized tail has a nonzero point-row violation,
\[
  \liminf_n \|\mathcal A^P_n U_{M,n}\|>0,
\]
then
\[
  \plim_n \hat\tau_{\mathrm{IPW},n}
  \ne
  \plim_n \hat\tau_{\mathrm{RT},n},
\]
and ANI differs from \(\tau_{ds}(r)\) by a linear functional of \(R_M\).  If
instead \(\lim_n\|\mathcal A^P_n U_{M,n}\|=0\) but
\(\liminf_n\|\mathcal A^V_n U_{M,n}\|>0\), then the conjectured separation is
covariance-only: the two point limits may agree, while network-cluster-robust
inference supplies a covariance law for the exposure-score estimator that
differs from the HAC or design-orbit covariance law.  For the target contrast,
the reported scalar separation is
\(L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)\) when that quadratic form is
nonzero; otherwise the nonzero covariance row identifies a different contrast
or score direction whose first-order law separates.
\end{conjecture}

\section{Related work and positioning}
The closest exposure-estimation result is Leung~\cite{Leung2022ANI}, which
formalizes approximate neighborhood interference and derives large-sample
properties for exposure-based estimators with network-HAC covariance.  The
present theorem uses the same exposure-map idea but asks a different question:
when is the exposure point score also the design-orbit point score, and when
do the HAC, cluster, and randomization covariance operators agree on omitted
tail directions?

Leung~\cite{Leung2023NCRI} is the closest network-cluster-robust comparator
because it links valid cluster-robust inference to graph partitions and
spectral geometry.  Here network clustering is treated as a covariance
operator for a named exposure-score estimator, not as a separate point
estimator.  Basse, Ding, Feller, and Toulis~\cite{BasseDingFellerToulis2024}
give exact randomization tests for peer effects in group-formation
experiments; this note identifies the additional projection equality needed
for that design-orbit null to coincide with the ANI exposure contrast.

Aronow and Samii~\cite{AronowSamii2017Exposure} supply the general
exposure-mapping framework under interference, which motivates the use of
exposure fibers and exposure propensities below.  Basse, Feller, and
Toulis~\cite{BasseFellerToulis2019} and Puelz, Basse, Feller, and
Toulis~\cite{PuelzBasseFellerToulis2022} develop conditioning and
graph-theoretic randomization-test constructions; their objects are design
validity certificates, whereas the present theorem compares their score
orbits to exposure and covariance projections.  Hudgens and
Halloran~\cite{HudgensHalloran2008} introduce direct and indirect effects
under partial interference; that setting appears here as the corner in which
design groups coincide with exposure fibers.

Kojevnikov, Marmer, and Song~\cite{KojevnikovMarmerSong2021} and
Conley~\cite{Conley1999Spatial} are relevant because graph-distance covariance
operators are network analogues of spatial and network dependence corrections.
Gao and Ding~\cite{GaoDing2025Network} connect regression analysis,
design-based properties, and network-robust covariance in network experiments;
the present contribution adds the design-orbit randomization comparison and a
single compatibility operator spanning point and covariance maps.  Savje
\cite{Savje2024MisspecifiedExposure} separates exposure definitions from
assumptions on the true interference structure, which is exactly the
distinction represented here by the declared sensitivity cone and the
realized omitted-tail score.  Weinstein and Nevo~\cite{WeinsteinNevo2026}
study misspecified network interference structures; this note is narrower in
statistical ambition but sharper about the three-procedure equivalence
frontier.

The in-repository precursor is the Stage -1 proposal for this same
\texttt{panel\_approx\_nbhd\_interference}/\texttt{v1} instance.  That
proposal supplied the locked parameter tuple and the two conjectures reproduced
above.  The contribution here is the self-contained deterministic
projection-and-cone argument that turns those conjectures into theorem
statements with explicit contamination terms.

\section{Formal setup}
For each \(n\), let \(G_n=(V_n,E_n)\) be a known undirected network with
\(|V_n|=n\), graph distance \(d_n(\cdot,\cdot)\), empirical degree law
\(\rho_n\), and treatment assignment vector \(Z_n\in\{0,1\}^n\) drawn from a
known randomized design \(Q_n\).  A design group \(\Omega_n\) acts on the
assignment space; its orbits are the valid randomization permutations for the
randomization procedure.  The boundary convention is graph-theoretic: if a
unit has no neighbors at a required distance, the corresponding exposure
summary is the additive identity.

Fix a radius \(r\).  The analyst's exposure map for unit \(i\) is
\[
  M_{r,i}(z)=(z_i,S_{r,i}(z)),
\]
where \(S_{r,i}\) is a known radius-\(r\) treatment summary.  The two locked
exposure labels are \(e_1=(1,s_1)\) and \(e_0=(0,s_0)\).  For any label \(e\),
write
\[
  \Gamma_{i,n}(e)=\{z\in\{0,1\}^n:M_{r,i}(z)=e\},\qquad
  \pi_{i,n}(e)=Q_n\{Z_n\in\Gamma_{i,n}(e)\}.
\]
All conditioning on exposure labels below is used only on the active risk set
where these probabilities are positive.

Potential outcomes are assignment-indexed functions \(Y_{i,n}(z)\).  The
exposure-label potential outcome averages over assignments in a fiber:
\[
  \bar Y_{i,n}(e)
  =
  \sum_{z\in\Gamma_{i,n}(e)}
  Y_{i,n}(z)Q_n\{Z_n=z\mid Z_n\in\Gamma_{i,n}(e)\}.
\]
The analogous orbit-averaged potential outcome restricts the conditional law
to the valid \(\Omega_n\)-orbit used by the randomization procedure.  The
radius-\(r\) exposure projection \(\Pi_{M_r}\) maps an assignment-indexed
response to its conditional expectation given the exposure label, and the
omitted-tail operator is
\[
  R_{M,n}=(I-\Pi_{M_r})T_n,
\]
where \(T_n:z\mapsto (Y_{1,n}(z),\ldots,Y_{n,n}(z))\).

Let \(\mathcal H_n\cong\R^{d_n}\) be the finite-dimensional Hilbert space of
weighted residual score directions with inner product
\[
  \langle u,v\rangle_{\rho,n}=u^{\transpose}W_{\rho,n}v,
\]
where \(W_{\rho,n}\) is positive definite on the active score coordinates and
is induced by the empirical degree law.  The vector
\[
  U_{M,n}=\operatorname{vec}_{\rho,n}(R_{M,n})\in\mathcal H_n
\]
is the Riesz representer of the omitted-tail score functional.  The
point-score projections \(P_{\mathrm{ANI},n}(r)\) and
\(P_{\mathrm{RT},n}(\Omega_n)\), and the covariance operators
\(V_{\mathrm{HAC},n}(r)\), \(V_{\mathrm{NCR},n}(b_n)\), and
\(V_{\mathrm{RT},n}(\Omega_n)\), are linear maps on this common score space
after degree weighting.

Define
\[
  \mathcal A_n =
  \begin{bmatrix}
  P_{\mathrm{ANI},n}(r)-P_{\mathrm{RT},n}(\Omega_n)\\
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{NCR},n}(b_n)\\
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{RT},n}(\Omega_n)
  \end{bmatrix} W_{\rho,n}^{1/2}.
\]
Its point row and covariance row are
\[
  \mathcal A^P_n
  =
  \{P_{\mathrm{ANI},n}(r)-P_{\mathrm{RT},n}(\Omega_n)\}W_{\rho,n}^{1/2},
  \qquad
  \mathcal A^V_n
  =
  \begin{bmatrix}
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{NCR},n}(b_n)\\
  V_{\mathrm{HAC},n}(r)-V_{\mathrm{RT},n}(\Omega_n)
  \end{bmatrix} W_{\rho,n}^{1/2}.
\]
Let \(a_{ds,n}\) denote the row vector that selects the scalar
direct-plus-spillover contrast from the residualized point-score coordinates.
The limiting selector, when it exists, is denoted \(a_{ds}\).
The analyst-declared sensitivity class is the finite-dimensional cone obtained
from the observed residual-score basis.  Identify
\(\mathcal H_n\) with \(\R^{d_n}\).  Let
\(\theta\in\R^{q_n}\) collect omitted-tail additive response coefficients and
let
\[
  B^u_n\in\R^{d_n\times q_n},\quad
  R^{\mathrm{add}}_n\in\R^{a_n\times q_n},\quad
  R^\Omega_n\in\R^{o_n\times q_n},\quad
  B^M_n\in\R^{s_n\times q_n},\quad
  B^{\mathrm{tail}}_n\in\R^{t_n\times q_n}.
\]
The matrix \(B^u_n\) sends omitted-tail coefficients to the common score
space; \(R^{\mathrm{add}}_n\theta=0\) imposes the additive ANI response
restriction; \(R^\Omega_n\theta=0\) imposes declared design-orbit symmetry;
\(B^M_n\theta\) records the score mass on misspecified exposure labels; and
\(B^{\mathrm{tail}}_n\theta\) records outside-radius tail mass.  With the
weighted \(\ell_1\) and \(\ell_2\) norms induced by \(W_{\rho,n}\), define
\[
\begin{aligned}
\mathcal C_n(\eta)=\{u\in\R^{d_n}:&\ \exists \theta\in\R^{q_n}\text{ with }
u=B^u_n\theta,\quad
R^{\mathrm{add}}_n\theta=0,\quad R^\Omega_n\theta=0,\\
&\ \|B^M_n\theta\|_{1,\rho,n}
     \le \epsilon_M\|u\|_{\rho,n},\quad
   \|B^{\mathrm{tail}}_n\theta\|_{2,\rho,n}
     \le \eta\|u\|_{\rho,n}\}.
\end{aligned}
\]
All entries of these matrices are fixed by the observed graph, exposure map,
assignment probabilities, design-orbit incidence matrix, degree weights,
bandwidth \(b_n\), and the declared additive response class.  Write
\[
  S_n(\eta)=\{u\in\mathcal C_n(\eta):\|u\|_{\rho,n}=1\},
  \qquad
  \mathcal N_n(\eta)=\ker(\mathcal A_n)\cap\mathcal C_n(\eta),
\]
with \(\mathcal N^P_n(\eta)\) and \(\mathcal N^V_n(\eta)\) defined by replacing
\(\mathcal A_n\) with its row blocks.  If \(S_n(\eta)\) is empty, all suprema
over \(S_n(\eta)\) are set to \(0\).

\paragraph{Locked parameters.}
\begin{verbatim}
(qid, specialization, p, assignment, target, regression)
= (panel_approx_nbhd_interference, v1,
   p = (r, rho, epsilon_M, eta, b_n, design_orbits),
   assignment = triangular-array randomized network experiment with
      bounded expected degree law rho, known graph G_n, treatment vector
      Z_n, and a design group Omega_n whose orbits describe the valid
      randomization permutations,
   target = finite-population direct-plus-spillover exposure contrast
      tau_ds(r) between e_1=(own treated, radius-r exposure s_1) and
      e_0=(own control, radius-r exposure s_0), where each exposure-label
      potential outcome is averaged over the assignment law conditional on
      that label,
   regression = exposure-score projection on M_r(i,Z_n), with the ANI
      point-score projection P_ANI(r), the design-orbit point-score
      projection P_RT(Omega_n), and first-order covariance operators
      V_HAC(r), V_NCR(b_n), and V_RT(Omega_n).)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Bounded degree-law limit]\label{ass:degree-law}
The graph sequence satisfies \(\rho_n\Rightarrow\rho\), uniformly bounded
\((2+\xi)\)-moments of degrees for some \(\xi>0\), and no single unit carries
positive asymptotic degree mass after \(W_{\rho,n}\) normalization.
\end{assumption}

\begin{assumption}[Additive ANI response]\label{ass:additive-ani}
Potential outcomes admit an additive own-treatment plus spillover
decomposition with a tail operator \(T_n\) whose contribution outside radius
\(r\) is \(R_{M,n}=(I-\Pi_{M_r})T_n\).  The direct-plus-spillover contrast
\(\tau_{ds,n}(r)\), using the exposure-fiber averaging convention in
Section~\ref{sec:target-label}, is uniformly bounded.
\end{assumption}

\begin{assumption}[Exposure misspecification profile and sensitivity cone]\label{ass:misspec-profile}
The radius-\(r\) exposure map misses an asymptotic fraction
\(\epsilon_M\in[0,1)\) of interference-relevant assignments, and the weighted
omitted-tail score \(U_{M,n}\) belongs to an admissible cone
\(\mathcal C_n(\eta)\) for a declared sensitivity radius \(\eta\).  The cone
\(\mathcal C_n(\eta)\) is exactly the finite constraint system in
Section~\ref{sec:estimand-functional}: its variables are
\((u,\theta)\in\R^{d_n}\times\R^{q_n}\), its equalities are
\(u=B^u_n\theta\), \(R^{\mathrm{add}}_n\theta=0\), and
\(R^\Omega_n\theta=0\), and its inequalities are
\[
  \|B^M_n\theta\|_{1,\rho,n}
  \le \epsilon_M\|u\|_{\rho,n},
  \qquad
  \|B^{\mathrm{tail}}_n\theta\|_{2,\rho,n}
  \le \eta\|u\|_{\rho,n}.
\]
The matrix blocks
\((B^u_n,R^{\mathrm{add}}_n,R^\Omega_n,B^M_n,B^{\mathrm{tail}}_n)\), unit
slice \(S_n(\eta)\), compatibility program \(\Delta_{\eta,n}\), and
common-null cell \(\mathcal N_n(\eta)\) are computed from the observed graph,
exposure map, assignment law, design orbits, degree weights, bandwidth, and
declared radii \((\epsilon_M,\eta)\).  The null-distance limit
\(\mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)\) exists for the true
unobserved tail, and the design-observable envelope
\([\underline d_\eta,\overline d_\eta]\) brackets all such tails in
\(\mathcal C_n(\eta)\).
\end{assumption}

\begin{assumption}[Randomization positivity and design orbits]\label{ass:design-orbits}
For \(a\in\{0,1\}\), the exposure propensities
\(\pi_{i,n}(e_a)\) are bounded away from zero on the active risk set.  The
valid randomization permutations form a design group \(\Omega_n\) with
point-score projection \(P_{\mathrm{RT},n}(\Omega_n)\) and covariance operator
\(V_{\mathrm{RT},n}(\Omega_n)\).
\end{assumption}

\begin{assumption}[Design-based LLN and point-functional consistency]\label{ass:design-lln}
The residualized exposure-IPW estimator \(\hat\tau_{\mathrm{IPW},n}\) and the
design-orbit linear contrast \(\hat\tau_{\mathrm{RT},n}\) obey triangular-array
laws of large numbers for their respective finite-population point
functionals.  Under correct exposure and equality of the active point-score
projections, these two limiting point functionals both equal
\(\lim_n\tau_{ds,n}(r)\).  More generally, when the scalar point row
\(a_{ds,n}^{\transpose}\mathcal A^P_n U_{M,n}\) has a nonzero limit, the two
probability limits differ by the limiting point-score functional applied to
the vectorized omitted-tail score.
\end{assumption}

\begin{assumption}[Cluster bandwidth and conductance]\label{ass:cluster-bandwidth}
The network-cluster procedure uses bandwidth \(b_n\) and a partition whose
within-cluster conductance and between-cluster edge mass converge to limits
that determine the covariance operator \(V_{\mathrm{NCR},n}(b_n)\) for the
exposure-score estimator.
\end{assumption}

\begin{assumption}[Score and covariance convergence]\label{ass:kernel-convergence}
The point-score projections \(P_{\mathrm{ANI},n}(r)\) and
\(P_{\mathrm{RT},n}(\Omega_n)\), and the covariance operators
\(V_{\mathrm{HAC},n}(r)\), \(V_{\mathrm{NCR},n}(b_n)\), and
\(V_{\mathrm{RT},n}(\Omega_n)\), after degree weighting by \(W_{\rho,n}\),
act on the common Hilbert score space \(\mathcal H_n\) and converge in
operator norm on each active score cone \(\mathcal C_n(\eta)\).  The
omitted-tail operator \(R_{M,n}\) is compared to cone elements only through the
vector \(U_{M,n}=\operatorname{vec}_{\rho,n}(R_{M,n})\in\mathcal H_n\).  The
limits define \(\mathcal A\), its row blocks \(\mathcal A^P\) and
\(\mathcal A^V\), \(\mathcal N(\eta)\), \(\mathcal N^P(\eta)\),
\(\mathcal N^V(\eta)\), \(\Delta_\eta\), \(\Delta^P_\eta\),
\(\Delta^V_\eta\), \(\mu_\star(\eta)\), \(\underline d_\eta\),
\(\overline d_\eta\), and the three limiting variance functionals.
\end{assumption}

\begin{assumption}[Nondegenerate active signal class]\label{ass:nondegenerate-signal}
The omitted-tail directions considered in the strict-separation claim form an
open subset of the active score cone \(\mathcal C_n(\eta)\), and whenever
\(\Delta_\eta(\rho,\epsilon_M,r,b,\Omega)>0\) their compatibility violation is
bounded away from zero on at least one row block of \(\mathcal A\).  For
true-tail statements, the vectorized omitted-tail score \(U_{M,n}\) has
positive limiting distance from \(\mathcal N_n(\eta)\) exactly when
\(\mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)>0\).
\end{assumption}

\begin{assumption}[Contrast-specific design efficiency]\label{ass:contrast-efficiency}
For the target contrast vector \(a_{ds}\), \(V_{\mathrm{RT}}(\Omega)\) is the
design-orbit efficient covariance on the active randomization score class, so
\[
  L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)
  =
  a_{ds}^{\transpose}\{V_{\mathrm{NCR}}(b)-V_{\mathrm{RT}}(\Omega)\}a_{ds}
\]
is nonnegative whenever \(V_{\mathrm{NCR}}(b)\) and
\(V_{\mathrm{RT}}(\Omega)\) target the same point-score law.  If this ordering
fails, the same signed scalar is still the reported covariance separation for
the \(a_{ds}\) contrast.
\end{assumption}

\begin{assumption}[Oracle exposure/design compatibility]\label{ass:oracle-compatibility}
The exposure map is correct \((\epsilon_M=0)\), \(b_n\ge r\) eventually, and
on the active score cone \(\mathcal C_n(\eta)\) the exposure, cluster, and
orbit sigma-fields generate the same projection:
\[
  P_{\mathrm{ANI},n}=P_{\mathrm{RT},n},
  \qquad
  V_{\mathrm{HAC},n}=V_{\mathrm{NCR},n}=V_{\mathrm{RT},n}
\]
after degree weighting.
\end{assumption}

\begin{assumption}[Partial-interference design corner]\label{ass:partial-interference-corner}
The graph is a disjoint union of design groups, radius \(r\) contains each
group, there are no cross-group tail effects, and the design group
\(\Omega_n\) is the direct product of the within-group design-compatible
permutation groups.  Equivalently, the valid \(\Omega_n\)-orbits coincide with
the within-group exposure fibers used by the partial-interference
randomization test.
\end{assumption}

\section{Estimand-defining functional}
\label{sec:estimand-functional}
The population exposure contrast score is
\[
  X_{i,n}^{ds}(Z_n)
  =
  \frac{\one\{M_{r,i}(Z_n)=e_1\}}{\pi_{i,n}(e_1)}
  -
  \frac{\one\{M_{r,i}(Z_n)=e_0\}}{\pi_{i,n}(e_0)}.
\]
Let \(B_n\) be the matrix of observed exposure-score regressors and let
\(F_n\) be the nuisance design generated by intercepts, design strata, and any
fixed effects included by the exposure-score projection.  With
\[
  M_{F,n}=I-F_n(F_n^{\transpose}F_n)^{-1}F_n^{\transpose},
\]
the Frisch--Waugh--Lovell population coefficient is
\[
  \theta_{\mathrm{ANI},n}
  =
  (B_n^{\transpose}M_{F,n}B_n)^{-1}B_n^{\transpose}M_{F,n}
  \E_{Q_n}[Y_n(Z_n)],
\]
whenever \(B_n^{\transpose}M_{F,n}B_n\) is nonsingular on the active score
coordinates.  If the Gram matrix is singular, all statements below use the
Moore--Penrose inverse and concern the estimable projection onto
\(\operatorname{col}(M_{F,n}B_n)\).  Equivalently, for the scalar
direct-plus-spillover contrast,
\[
  \theta_{\mathrm{ANI},n}
  =
  \frac1n\sum_{i=1}^n\E_{Q_n}\!\left[X_{i,n}^{ds}(Z_n)Y_{i,n}(Z_n)\right]
\]
after the same residualization.  The design-orbit point functional
\(\theta_{\mathrm{RT},n}\) is the analogous residualized linear contrast with
the exposure-score projection \(P_{\mathrm{RT},n}(\Omega_n)\).

Using the target selector \(a_{ds,n}\), define the two explicit point
contamination maps for any omitted-tail score \(u\in\mathcal H_n\):
\[
  C^P_{\mathrm{ANI},n}(u)
  =
  a_{ds,n}^{\transpose}P_{\mathrm{ANI},n}(r)W_{\rho,n}^{1/2}u,
  \qquad
  C^P_{\mathrm{RT},n}(u)
  =
  a_{ds,n}^{\transpose}P_{\mathrm{RT},n}(\Omega_n)W_{\rho,n}^{1/2}u.
\]
Thus
\[
  C^P_{\mathrm{ANI},n}(u)-C^P_{\mathrm{RT},n}(u)
  =
  a_{ds,n}^{\transpose}\mathcal A^P_nu.
\]
The ANI point functional is target-clean for the realized tail exactly when
\(C^P_{\mathrm{ANI},n}(U_{M,n})\) has zero limit; the design-orbit point
functional is target-clean exactly when \(C^P_{\mathrm{RT},n}(U_{M,n})\) has
zero limit.  Equality of these two contamination maps is only a
procedure-equivalence condition and can leave a common bias relative to
\(\tau_{ds,n}(r)\).

The first-order covariance functional is the triple
\[
  \mathfrak V_n
  =
  \bigl(
    V_{\mathrm{HAC},n}(r),
    V_{\mathrm{NCR},n}(b_n),
    V_{\mathrm{RT},n}(\Omega_n)
  \bigr),
\]
where \(V_{\mathrm{HAC},n}(r)\) is the graph-distance HAC covariance for the
residualized exposure score, \(V_{\mathrm{NCR},n}(b_n)\) is the covariance
obtained by summing residualized scores over the network clusters at scale
\(b_n\), and \(V_{\mathrm{RT},n}(\Omega_n)\) is the randomization variance of
the design-orbit projected score.  Each operator is a finite matrix in the
coordinates of \(\mathcal H_n\), hence directly evaluable from the specified
graph, assignment law, exposure map, design orbits, and score basis.

The compatibility functional is
\[
  \Delta_{\eta,n}
  =
  \sup_{u\in S_n(\eta)} \|\mathcal A_nu\|,
  \qquad
  \Delta^P_{\eta,n}
  =
  \sup_{u\in S_n(\eta)} \|\mathcal A^P_nu\|,
  \qquad
  \Delta^V_{\eta,n}
  =
  \sup_{u\in S_n(\eta)} \|\mathcal A^V_nu\|.
\]
In the explicit coordinates of the locked proposal, \(\Delta_{\eta,n}^2\) is
the finite program
\[
\begin{array}{ll}
\text{maximize over }(u,\theta)\in\R^{d_n}\times\R^{q_n}:&
   u^{\transpose}\mathcal A_n^{\transpose}\mathcal A_nu\\[1mm]
\text{subject to:}&
   u^{\transpose}W_{\rho,n}u=1,\\
&  u=B^u_n\theta,\quad
   R^{\mathrm{add}}_n\theta=0,\quad R^\Omega_n\theta=0,\\
&  \|B^M_n\theta\|_{1,\rho,n}\le \epsilon_M,\\
&  \|B^{\mathrm{tail}}_n\theta\|_{2,\rho,n}\le \eta .
\end{array}
\]
The normalization \(\|u\|_{\rho,n}=1\) converts the two cone inequalities from
Section~\ref{sec:estimand-functional} into the displayed constants
\(\epsilon_M\) and \(\eta\).  The same program with \(\mathcal A^P_n\) or
\(\mathcal A^V_n\) gives \(\Delta^P_{\eta,n}\) and
\(\Delta^V_{\eta,n}\).  If the weighted \(\ell_1\) constraint is linearized
with nonnegative slack variables \(s^+,s^-\in\R^{s_n}_+\), the decision vector
has dimension \(d_n+q_n+2s_n\), the equality constraints are the three
displayed linear systems plus \(B^M_n\theta=s^+-s^-\), and the inequality
constraints are \(s^+,s^-\ge0\),
\(\sum_j w_{j,n}(s^+_j+s^-_j)\le\epsilon_M\), and the one second-order cone
constraint \(\|B^{\mathrm{tail}}_n\theta\|_{2,\rho,n}\le\eta\).  Thus the
functional is a named finite quadratically constrained conic program with all
variables, dimensions, objective, and constraints specified by observed
population inputs and declared radii.  In the purely polyhedral case
\(B^{\mathrm{tail}}_n=0\), exact evaluation can be done by face enumeration:
on each face one solves a generalized eigenvalue problem for
\((\mathcal A_n^{\transpose}\mathcal A_n,W_{\rho,n})\) restricted to the face
span and then takes the largest feasible eigenvalue.  The face-enumeration
bound is exponential in the number of cone inequalities and cubic in \(d_n\)
per face.

The cone-restricted singular value is
\[
  \mu_{\star,n}(\eta)=
  \inf_{\substack{u\in S_n(\eta)\\
  \operatorname{dist}(u,\mathcal N_n(\eta))>0}}
  \frac{\|\mathcal A_nu\|}
       {\operatorname{dist}(u,\mathcal N_n(\eta))}.
\]
If \(S_n(\eta)\subseteq\mathcal N_n(\eta)\), set
\(\mu_{\star,n}(\eta)=+\infty\).  The asymptotic functionals
\(\Delta_\eta\), \(\Delta^P_\eta\), \(\Delta^V_\eta\), and \(\mu_\star\) are
the corresponding limsup or liminf limits from Assumption~\ref{ass:kernel-convergence}.
Finally,
\[
  \underline d_{\eta,n}
  =
  \inf_{u\in\mathcal C_n(\eta)}
  \operatorname{dist}(u,\mathcal N_n(\eta)),
  \qquad
  \overline d_{\eta,n}
  =
  \sup_{u\in\mathcal C_n(\eta)}
  \operatorname{dist}(u,\mathcal N_n(\eta))
\]
are the observable envelope diagnostics, and
\[
  \mu_{\perp}(\rho,\epsilon_M,\eta,r,b,\Omega)
  =
  \limsup_n \operatorname{dist}(U_{M,n},\mathcal N_n(\eta))
\]
is the realized-tail sensitivity distance.

\paragraph{Conjecture verdicts.}
Conjecture~\ref{conj:spectral-frontier} is confirmed as a
procedure-equivalence statement: \(\Delta_\eta=0\) is exactly the uniform
equivalence condition over the declared cone, and the displayed lower and
upper bounds are the deterministic singular-value bounds for \(\mathcal A\)
modulo its common null cell.  The theorem below adds the target-contamination
qualification required for causal interpretation: equality of procedure
objects does not imply \(\theta_{\mathrm{ANI}}=\tau_{ds}(r)\) unless
\(C^P_{\mathrm{ANI}}(U_M)=0\).  Conjecture~\ref{conj:strict-separation} is
confirmed in its row-specific form: a nonzero scalar point row creates
unequal point probability limits, whereas a zero scalar point row with a
nonzero covariance row creates covariance-only separation.

\section{Target causal estimand}
\label{sec:target-label}
The target is not the regression coefficient by definition.  It is the
finite-population direct-plus-spillover exposure contrast
\[
  \tau_{ds,n}(r)
  =
  \frac1n\sum_{i\in V_n}
  \left\{
    \bar Y_{i,n}(e_1)-\bar Y_{i,n}(e_0)
  \right\},
  \qquad
  e_1=(1,s_1),\quad e_0=(0,s_0).
\]
The limiting target is \(\tau_{ds}(r)=\lim_n\tau_{ds,n}(r)\) whenever this
limit exists.  The exposure-label averaging convention is part of the target:
the potential outcome for label \(e\) is averaged over the assignment law
conditional on \(M_{r,i}(Z_n)=e\), not over an arbitrary intervention
distribution and not over the design orbit unless the orbit coincides with
the exposure fiber.  Thus the causal target is an exposure-label contrast,
while \(\theta_{\mathrm{ANI},n}\), \(\theta_{\mathrm{RT},n}\), and
\(\mathfrak V_n\) are procedure functionals whose equality with that target or
with each other must be proved.

\section{Main theorems}
\begin{proposition}[Oracle projection and covariance collapse]\label{prop:oracle-collapse}
Under Assumptions~\ref{ass:degree-law}, \ref{ass:additive-ani},
\ref{ass:misspec-profile}, \ref{ass:design-orbits}, \ref{ass:design-lln},
\ref{ass:cluster-bandwidth}, \ref{ass:kernel-convergence}, and
\ref{ass:oracle-compatibility},
\[
  \plim_n \hat\tau_{\mathrm{IPW},n}
  =
  \plim_n \hat\tau_{\mathrm{RT},n}
  =
  \lim_n \tau_{ds,n}(r),
\]
and
\[
  V_{\mathrm{HAC}}(r)
  =
  V_{\mathrm{NCR}}(b)
  =
  V_{\mathrm{RT}}(\Omega)
\]
on the active score cone.
\end{proposition}

This proposition is the safe benchmark.  It is not the main novelty, but it
records the exact corner in which the exposure estimator, network-cluster
covariance, and randomization covariance are the same mathematical object.
Compared with the separate validity results in Leung~\cite{Leung2022ANI},
Leung~\cite{Leung2023NCRI}, and Basse et al.~\cite{BasseDingFellerToulis2024},
the proposition adds the cross-procedure projection equality.

\begin{proposition}[Spectral compatibility frontier and rowwise contamination]\label{thm:spectral-frontier}
Assume Assumptions~\ref{ass:degree-law}--\ref{ass:contrast-efficiency}.  For
each \(n\), the point functionals induced by an omitted-tail score
\(u\in\mathcal C_n(\eta)\) decompose as
\[
  \theta_{\mathrm{ANI},n}(u)
  =
  \tau_{ds,n}(r)+C^P_{\mathrm{ANI},n}(u),
  \qquad
  \theta_{\mathrm{RT},n}(u)
  =
  \tau_{ds,n}(r)+C^P_{\mathrm{RT},n}(u),
\]
and their scalar point-procedure disagreement is
\[
  \theta_{\mathrm{ANI},n}(u)-\theta_{\mathrm{RT},n}(u)
  =
  C^P_{\mathrm{ANI},n}(u)-C^P_{\mathrm{RT},n}(u)
  =
  a_{ds,n}^{\transpose}\mathcal A^P_nu.
\]
The stacked point and covariance procedure-object gap is therefore
\[
  \mathcal G_n(u)
  =
  \begin{bmatrix}
  a_{ds,n}^{\transpose}\mathcal A^P_nu\\
  \{V_{\mathrm{HAC},n}(r)-V_{\mathrm{NCR},n}(b_n)\}u\\
  \{V_{\mathrm{HAC},n}(r)-V_{\mathrm{RT},n}(\Omega_n)\}u
  \end{bmatrix}
  =
  \begin{bmatrix}
  a_{ds,n}^{\transpose}\mathcal A^P_nu\\
  \mathcal A^V_nu
  \end{bmatrix}.
\]
Consequently, the named procedure objects are uniformly equivalent over the
declared sensitivity class if and only if
\[
  \Delta_\eta(\rho,\epsilon_M,r,b,\Omega)=0,
\]
or equivalently \(\mathcal C(\eta)\subseteq\ker(\mathcal A)\).  If
\(\Delta_\eta>0\), then
\[
  \mu_\star(\eta)
  \sup_{u\in S(\eta)}\operatorname{dist}(u,\mathcal N(\eta))
  \le
  \Delta_\eta
  \le
  \|\mathcal A\|
  \sup_{u\in S(\eta)}\operatorname{dist}(u,\mathcal N(\eta)).
\]
For the realized omitted tail,
\[
  \plim_n \hat\tau_{\mathrm{IPW},n}
  =
  \tau_{ds}(r)+\lim_n C^P_{\mathrm{ANI},n}(U_{M,n}),
  \qquad
  \plim_n \hat\tau_{\mathrm{RT},n}
  =
  \tau_{ds}(r)+\lim_n C^P_{\mathrm{RT},n}(U_{M,n}),
\]
whenever the displayed limits exist, and hence
\[
  \plim_n \hat\tau_{\mathrm{IPW},n}
  -
  \plim_n \hat\tau_{\mathrm{RT},n}
  =
  \lim_n a_{ds,n}^{\transpose}\mathcal A^P_nU_{M,n},
\]
while the covariance-object gap is
\[
  \lim_n \mathcal A^V_nU_{M,n}.
\]
Thus \(U_M\in\mathcal N(\eta)\), equivalently \(\mu_\perp=0\), is exactly the
true-tail procedure-equivalence condition.  The ANI coefficient identifies
the target only under the additional condition
\(\lim_nC^P_{\mathrm{ANI},n}(U_{M,n})=0\).  If \(\mu_\perp>0\) and
\(\mu_\star(\eta)>0\), then the combined unscalarized point/covariance
procedure gap for the realized tail is bounded below by
\(\mu_\star(\eta)\mu_\perp\), after the triangular-array normalization and up
to a vanishing convergence error.  If only the covariance row is nonzero, the
point probability limits may agree while the first-order covariance laws
differ; for the target contrast the reported scalar separation is
\(L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)\).
\end{proposition}

This theorem is the main contribution.  It confirms
Conjectures~\ref{conj:spectral-frontier} and \ref{conj:strict-separation},
but it also makes explicit the rowwise decomposition needed to avoid
overclaiming.  The closest literature gives valid estimators, standard errors,
or tests under separate assumptions; the new result is the necessary-and-
sufficient compatibility frontier for substituting one named procedure object
for another.

\section{Interpretation}
The procedure comparison is clean when the omitted-tail score lies in the
common null cell \(\mathcal N(\eta)\).  In that case the ANI exposure point
score and the design-orbit point score agree on every admissible tail
direction, and the HAC, network-cluster, and randomization covariance
operators also agree on those directions.  Target identification is a
stronger requirement: the ANI coefficient is clean for
\(\tau_{ds}(r)\) only when \(C^P_{\mathrm{ANI}}(U_M)=0\), and the
design-orbit point functional is clean only when
\(C^P_{\mathrm{RT}}(U_M)=0\).  The oracle proposition is the strongest and
easiest way to ensure both procedure equivalence and target cleanliness: the
exposure map is correct, the cluster bandwidth covers the exposure radius,
and the exposure, cluster, and orbit sigma-fields generate the same active
projection.

Procedure disagreement in the point estimand occurs when
\(a_{ds}^{\transpose}\mathcal A^P U_M\ne0\).  Target contamination for ANI is
the separate scalar \(C^P_{\mathrm{ANI}}(U_M)\); two point procedures can agree
and still share a common tail bias relative to \(\tau_{ds}(r)\).  If
\(\mathcal A^P U_M=0\) but \(\mathcal A^V U_M\ne0\), then the point
procedures can agree while the reported first-order covariance law is not
interchangeable across procedures.  This is why the theorem distinguishes
point-row, covariance-row, and target-contamination failures.

The positivity assumption matters only for the exposure labels \(e_0\) and
\(e_1\) on the active risk set.  Without it, the exposure-label average in the
target and the IPW score in the functional are not both defined.  The rank
condition matters only for the residualized score coordinates; if the Gram
matrix is singular, the theorem concerns the Moore--Penrose estimable
projection rather than an unrestricted coefficient.

The result connects the three literatures by making their common object a
linear score-space statement.  ANI supplies the exposure point score,
network-cluster methods supply one covariance projection, and exact
randomization supplies the design-orbit projection.  The compatibility
program says whether these projections are the same on the sensitivity class
the analyst is willing to entertain.

\section{Step-by-step proof}
\begin{lemma}[Exposure-score decomposition]\label{lem:point-decomposition}
Under Assumptions~\ref{ass:additive-ani}, \ref{ass:design-orbits},
\ref{ass:design-lln}, and \ref{ass:kernel-convergence},
\[
  \theta_{\mathrm{ANI},n}
  =
  \tau_{ds,n}(r)+C_{\mathrm{ANI},n}^P(U_{M,n}),
  \qquad
  \theta_{\mathrm{RT},n}
  =
  \tau_{ds,n}(r)+C_{\mathrm{RT},n}^P(U_{M,n}),
\]
where
\[
  C_{\mathrm{ANI},n}^P(u)-C_{\mathrm{RT},n}^P(u)
  =
  a_{ds,n}^{\transpose}\mathcal A^P_nu
\]
for every score \(u\).
\end{lemma}

\begin{proof}
By Assumption~\ref{ass:additive-ani}, decompose the assignment-indexed outcome
as
\[
  T_n=\Pi_{M_r}T_n+R_{M,n}.
\]
Apply the residualized exposure-score functional to both sides.  The
Frisch--Waugh--Lovell identity gives the population coefficient as the
projection of \(T_n\) onto the residualized exposure-score column space,
because \(M_{F,n}\) removes the nuisance coordinates and the active Gram
matrix is inverted, or Moore--Penrose inverted on the estimable subspace.  On
\(\Pi_{M_r}T_n\), the IPW score satisfies
\[
  \E_{Q_n}\!\left[
    \frac{\one\{M_{r,i}(Z_n)=e\}}{\pi_{i,n}(e)}
    \Pi_{M_r}Y_{i,n}(Z_n)
  \right]
  =
  \bar Y_{i,n}(e),
\]
which uses Assumption~\ref{ass:design-orbits} for positivity and the
definition of exposure-fiber averaging.  Taking the difference between
\(e_1\) and \(e_0\) and averaging over \(i\) gives
\(\tau_{ds,n}(r)\).  The remaining term is the same residualized score applied
to \(R_{M,n}\).  By the Riesz representation in
Assumption~\ref{ass:kernel-convergence}, that term is
\(C_{\mathrm{ANI},n}^P(U_{M,n})\).  The design-orbit functional obeys the same
argument with \(P_{\mathrm{RT},n}(\Omega_n)\), giving
\(C_{\mathrm{RT},n}^P(U_{M,n})\).  Subtracting the two displays leaves exactly
the scalarized point row \(a_{ds,n}^{\transpose}\mathcal A^P_nU_{M,n}\).
\end{proof}

\begin{lemma}[Covariance-row decomposition]\label{lem:cov-decomposition}
Under Assumptions~\ref{ass:cluster-bandwidth}, \ref{ass:kernel-convergence},
and \ref{ass:contrast-efficiency}, the covariance-object discrepancies on an
omitted-tail direction \(u\in\mathcal C_n(\eta)\) are
\[
  \begin{bmatrix}
  \{V_{\mathrm{HAC},n}(r)-V_{\mathrm{NCR},n}(b_n)\}u\\
  \{V_{\mathrm{HAC},n}(r)-V_{\mathrm{RT},n}(\Omega_n)\}u
  \end{bmatrix}
  =
  \mathcal A^V_nu.
\]
For the contrast \(a_{ds}\), the network-cluster to randomization scalar gap is
\[
  L_{\mathrm{NCR}\to\mathrm{RT}}(a_{ds};b,\Omega)
  =
  a_{ds}^{\transpose}\{V_{\mathrm{NCR}}(b)-V_{\mathrm{RT}}(\Omega)\}a_{ds}.
\]
\end{lemma}

\begin{proof}
The first display is the definition of the covariance row block after the
common degree weighting in Assumption~\ref{ass:kernel-convergence}.  The
network-cluster covariance exists as an operator by
Assumption~\ref{ass:cluster-bandwidth}, and the design-orbit covariance exists
by Assumption~\ref{ass:design-orbits}.  The scalar display is the quadratic
form specified in Assumption~\ref{ass:contrast-efficiency}; it is nonnegative
only under the design-efficiency ordering in that assumption and is otherwise
read as a signed separation.
\end{proof}

\begin{lemma}[Cone spectral identity]\label{lem:spectral}
Let \(\mathcal A:\mathcal H\to\mathcal K\) be a bounded linear map between
finite-dimensional Hilbert spaces, let \(\mathcal C\subseteq\mathcal H\) be a
closed cone, let \(S=\{u\in\mathcal C:\|u\|=1\}\), and let
\(\mathcal N=\ker(\mathcal A)\cap\mathcal C\).  Define
\[
  \Delta=\sup_{u\in S}\|\mathcal A u\|,
  \qquad
  \mu_\star=
  \inf_{\substack{u\in S\\ \operatorname{dist}(u,\mathcal N)>0}}
  \frac{\|\mathcal A u\|}{\operatorname{dist}(u,\mathcal N)}.
\]
Then \(\Delta=0\) if and only if \(\mathcal C\subseteq\ker(\mathcal A)\).
If \(\Delta>0\), then
\[
  \mu_\star \sup_{u\in S}\operatorname{dist}(u,\mathcal N)
  \le
  \Delta
  \le
  \|\mathcal A\|\sup_{u\in S}\operatorname{dist}(u,\mathcal N).
\]
\end{lemma}

\begin{proof}
If \(\mathcal C\subseteq\ker(\mathcal A)\), then every unit cone element is
annihilated and \(\Delta=0\).  Conversely, if \(\Delta=0\), then
\(\mathcal A u=0\) for every \(u\in S\); by conicity, every nonzero element of
\(\mathcal C\) is a nonnegative scalar multiple of an element of \(S\), and
the zero element is trivially in the kernel.  Hence
\(\mathcal C\subseteq\ker(\mathcal A)\).

For the upper bound, choose any \(u\in S\) and any \(v\in\mathcal N\).  Since
\(\mathcal A v=0\),
\[
  \|\mathcal A u\|=\|\mathcal A(u-v)\|
  \le \|\mathcal A\|\,\|u-v\|.
\]
Taking the infimum over \(v\in\mathcal N\), then the supremum over
\(u\in S\), gives the upper bound.  For the lower bound, the definition of
\(\mu_\star\) gives
\[
  \|\mathcal A u\|
  \ge
  \mu_\star\operatorname{dist}(u,\mathcal N)
\]
for every \(u\in S\) with positive distance from \(\mathcal N\); the display
also holds when the distance is zero.  Taking the supremum over \(u\in S\)
gives the lower bound.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:oracle-collapse}]
Assumption~\ref{ass:oracle-compatibility} gives
\[
  P_{\mathrm{ANI},n}=P_{\mathrm{RT},n},
  \qquad
  V_{\mathrm{HAC},n}=V_{\mathrm{NCR},n}=V_{\mathrm{RT},n}
\]
on the active cone.  Thus \(\mathcal A_nu=0\) for every admissible direction
\(u\).  Because the exposure map is correct, \(R_{M,n}=0\) on the active
score coordinates, so Lemma~\ref{lem:point-decomposition} gives
\(\theta_{\mathrm{ANI},n}=\theta_{\mathrm{RT},n}=\tau_{ds,n}(r)\).  The
triangular-array laws of large numbers in Assumption~\ref{ass:design-lln}
transfer these population equalities to the displayed probability limits.
The covariance equality is the second part of
Assumption~\ref{ass:oracle-compatibility}, with existence and convergence
justified by Assumptions~\ref{ass:cluster-bandwidth} and
\ref{ass:kernel-convergence}.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{thm:spectral-frontier}]
Lemma~\ref{lem:point-decomposition} gives the target-plus-contamination
formula and the scalarized point row of \(\mathcal G_n(u)\), and
Lemma~\ref{lem:cov-decomposition} gives the covariance rows.  Stacking these
rows is exactly the scalarized form of \((\mathcal A^P_nu,\mathcal A^V_nu)\).
Passing to limits is allowed by Assumption~\ref{ass:kernel-convergence}; the
design-based probability limits are justified by
Assumption~\ref{ass:design-lln}.

Uniform equivalence over the declared class means that every admissible
omitted-tail direction produces zero stacked point/covariance gap.  In the
limit this is \(\mathcal C(\eta)\subseteq\ker(\mathcal A)\), which is
equivalent to \(\Delta_\eta=0\) by Lemma~\ref{lem:spectral}.  The same lemma
gives the displayed lower and upper bounds.

For the realized omitted tail, substitute \(u=U_{M,n}\) into the
target-plus-contamination and row decompositions.  If
\(U_M\in\mathcal N(\eta)\), both procedure-disagreement rows vanish; if the
rows vanish, \(U_M\) is in the common null cell by definition.  This proves
true-tail procedure equivalence and the equivalence with \(\mu_\perp=0\).
The separate target-identification claim follows directly from
\(\plim\hat\tau_{\mathrm{IPW}}=\tau_{ds}(r)+
\lim C^P_{\mathrm{ANI},n}(U_{M,n})\).  If
\(\mu_\perp>0\) and \(\mu_\star(\eta)>0\), the lower bound in
Lemma~\ref{lem:spectral}, applied to the normalized realized tail and then
rescaled, yields a combined gap at least
\(\mu_\star(\eta)\mu_\perp\) up to the convergence error from
Assumption~\ref{ass:kernel-convergence}.  Finally, if
\(a_{ds}^{\transpose}\mathcal A^P U_M\ne0\),
Lemma~\ref{lem:point-decomposition} gives unequal point probability limits;
if \(a_{ds}^{\transpose}\mathcal A^P U_M=0\) but
\(\mathcal A^V U_M\ne0\), Lemma~\ref{lem:cov-decomposition} gives
covariance-only separation.  Assumption~\ref{ass:nondegenerate-signal} gives
openness of the strict-separation set.
\end{proof}

\section{Sanity checks}
\begin{enumerate}[leftmargin=*]
\item \textbf{Correct exposure and homogeneous spillovers.}  If
\(R_{M,n}=0\), then \(U_{M,n}=0\).  Lemma~\ref{lem:point-decomposition}
reduces both point functionals to \(\tau_{ds,n}(r)\), and
Proposition~\ref{thm:spectral-frontier} reduces to the usual exposure-mapping
interpretation of Leung~\cite{Leung2022ANI}.

\item \textbf{No spillovers.}  If \(S_{r,i}(z)\) is irrelevant to all
potential outcomes and only own treatment matters, then the target becomes the
finite-population direct effect
\[
  \frac1n\sum_i\{\bar Y_{i,n}(1)-\bar Y_{i,n}(0)\}.
\]
The exposure score collapses to an own-treatment score, and the omitted-tail
term vanishes whenever the design orbit preserves own-treatment exposure
propensities.

\item \textbf{Partial-interference corner.}  Under
Assumption~\ref{ass:partial-interference-corner}, the valid design orbits are
exactly the within-group exposure fibers.  Hence
\(P_{\mathrm{ANI}}(r)=P_{\mathrm{RT}}(\Omega)\) on the active point-score
space, recovering the Hudgens--Halloran direct/indirect-effect geometry and
the group-formation randomization setup of Basse et al.~\cite{BasseDingFellerToulis2024}.

\item \textbf{Contamination terms vanish.}  If
\(U_M\in\mathcal N^P(\eta)\) but \(U_M\notin\mathcal N^V(\eta)\), the point
procedures agree but the covariance law is not interchangeable.  The ANI
point contrast is target-clean only when
\(C^P_{\mathrm{ANI}}(U_M)=0\).  If \(U_M\in\mathcal N(\eta)\), both the point
procedure-disagreement and covariance-disagreement terms vanish, but a common
point contamination term must still be checked unless the oracle exposure
condition makes \(U_M=0\).

\item \textbf{Finite-dimensional rank.}  If \(B_n^{\transpose}M_{F,n}B_n\)
is nonsingular, the FWL coefficient is the ordinary residualized projection
coefficient.  If it is singular, replacing the inverse by the Moore--Penrose
inverse gives the same theorem for the estimable projection; directions
orthogonal to \(\operatorname{col}(M_{F,n}B_n)\) are not identified by the
regression functional.
\end{enumerate}

\section{Counterexample or minimality check}
The rowwise statement in Proposition~\ref{thm:spectral-frontier} is minimal.  Take
\(\mathcal H=\R^2\) with the Euclidean norm,
\(\mathcal C=\R^2_+\), and
\[
  \mathcal A^P=\begin{bmatrix}1&0\end{bmatrix},
  \qquad
  \mathcal A^V=\begin{bmatrix}0&1\end{bmatrix},
  \qquad
  \mathcal A=\begin{bmatrix}1&0\\0&1\end{bmatrix}.
\]
For the omitted-tail direction \(U_M=(0,1)^{\transpose}\), the point row is
zero but the covariance row is nonzero.  Thus the ANI and randomization point
functionals can agree while the covariance operators separate.  Any theorem
that replaced the rowwise conclusion by ``\(\Delta_\eta>0\) implies unequal
point probability limits'' would be false; the nearest correct statement is
the one proved above, which requires \(\mathcal A^P U_M\ne0\) for point-level
separation.

The positivity condition is also necessary.  If some active unit has
\(\pi_{i,n}(e_1)=0\), then \(\bar Y_{i,n}(e_1)\) may still be part of the
intended exposure-label contrast, but the IPW score
\(\one\{M_{r,i}(Z_n)=e_1\}/\pi_{i,n}(e_1)\) is undefined.  No projection
identity can repair the missing exposure cell without changing the target or
adding a support restriction.

Finally, the common-null condition cannot be weakened to equality of only one
procedure pair.  If \(P_{\mathrm{ANI}}=P_{\mathrm{RT}}\) but
\(V_{\mathrm{HAC}}\ne V_{\mathrm{NCR}}\), then the point procedures agree but
network-cluster inference is attached to a different first-order law.  If the
covariance operators agree but \(P_{\mathrm{ANI}}\ne P_{\mathrm{RT}}\), then
the standard errors may agree while the point estimands differ.

There is also a distinct minimality check for target identification.  Let
\(\mathcal H=\R\), let \(P_{\mathrm{ANI}}=P_{\mathrm{RT}}=[1]\), and suppress
the covariance rows.  Then \(\mathcal A^P=0\) and
\(\Delta_\eta=0\) for every cone, so the ANI and randomization point
functionals are uniformly equivalent.  For \(U_M=1\), however,
\(C^P_{\mathrm{ANI}}(U_M)=C^P_{\mathrm{RT}}(U_M)=1\), so both point
functionals equal \(\tau_{ds}(r)+1\) rather than \(\tau_{ds}(r)\).  Thus the
target-clean condition \(C^P_{\mathrm{ANI}}(U_M)=0\) cannot be replaced by the
procedure-equivalence condition \(\Delta_\eta=0\).

\section{Formalization checklist}
\paragraph{Deterministic objects.}
\begin{itemize}[leftmargin=*]
\item Finite graph \(G_n=(V_n,E_n)\), graph distance \(d_n\), assignment
space \(\{0,1\}^n\), design group \(\Omega_n\), and exposure map
\(M_{r,i}:\{0,1\}^n\to\{0,1\}\times\mathcal S_r\).
\item Exposure fibers \(\Gamma_{i,n}(e)\), propensities \(\pi_{i,n}(e)\), and
the active risk set where \(\pi_{i,n}(e_0)\) and \(\pi_{i,n}(e_1)\) are
positive.
\item Finite-dimensional Hilbert score space \((\mathcal H_n,\langle\cdot,
\cdot\rangle_{\rho,n})\), positive definite weight matrix \(W_{\rho,n}\), and
Riesz vectorization map \(R_{M,n}\mapsto U_{M,n}\).
\item Linear maps \(P_{\mathrm{ANI},n}\), \(P_{\mathrm{RT},n}\),
\(V_{\mathrm{HAC},n}\), \(V_{\mathrm{NCR},n}\), \(V_{\mathrm{RT},n}\), and the
stacked operator \(\mathcal A_n\) with row blocks \(\mathcal A^P_n\) and
\(\mathcal A^V_n\).
\item Target selector \(a_{ds,n}\) and point contamination maps
\(C^P_{\mathrm{ANI},n}(u)=
a_{ds,n}^{\transpose}P_{\mathrm{ANI},n}W_{\rho,n}^{1/2}u\) and
\(C^P_{\mathrm{RT},n}(u)=
a_{ds,n}^{\transpose}P_{\mathrm{RT},n}W_{\rho,n}^{1/2}u\).
\item Omitted-tail coordinate matrices \(B^u_n\),
\(R^{\mathrm{add}}_n\), \(R^\Omega_n\), \(B^M_n\), and
\(B^{\mathrm{tail}}_n\), together with the coefficient vector
\(\theta\in\R^{q_n}\) and weighted \(\ell_1/\ell_2\) norms.
\item Closed cone \(\mathcal C_n(\eta)\), unit slice \(S_n(\eta)\), null cells
\(\mathcal N_n(\eta)\), \(\mathcal N^P_n(\eta)\), \(\mathcal N^V_n(\eta)\),
and distance to a closed cone.
\item Finite quadratically constrained conic program for
\(\Delta_{\eta,n}\), plus the face-restricted generalized eigenvalue
calculation for polyhedral cone special cases.
\end{itemize}

\paragraph{Probabilistic and causal objects.}
\begin{itemize}[leftmargin=*]
\item Randomized assignment law \(Q_n\) and design-orbit conditional law.
\item Assignment-indexed potential outcomes \(Y_{i,n}(z)\), exposure-label
averages \(\bar Y_{i,n}(e)\), and target
\(\tau_{ds,n}(r)\).
\item Exposure-score random variable \(X_{i,n}^{ds}(Z_n)\) and residualized
population coefficient \(\theta_{\mathrm{ANI},n}\).
\item Triangular-array laws of large numbers connecting population point
functionals to \(\plim\hat\tau_{\mathrm{IPW},n}\) and
\(\plim\hat\tau_{\mathrm{RT},n}\).
\item Operator-norm convergence assumptions for point-score and covariance
maps.
\end{itemize}

\paragraph{Identities and lemmas.}
\begin{itemize}[leftmargin=*]
\item Frisch--Waugh--Lovell residualized projection identity with an ordinary
inverse under full rank and a Moore--Penrose inverse on the estimable subspace
under rank deficiency.
\item Exposure-IPW identity:
\[
  \E[\one\{M=e\}Y/\pi(e)]=\E[Y\mid M=e]
\]
on positive-propensity cells.
\item Decomposition \(T_n=\Pi_{M_r}T_n+R_{M,n}\) and linearity of the
residualized score functional.
\item Target-plus-contamination identities
\(\theta_{\mathrm{ANI},n}=\tau_{ds,n}(r)+C^P_{\mathrm{ANI},n}(U_{M,n})\) and
\(\theta_{\mathrm{RT},n}=\tau_{ds,n}(r)+C^P_{\mathrm{RT},n}(U_{M,n})\).
\item Stacked-row identity for procedure disagreements:
\(\mathcal G_n(u)=(a_{ds,n}^{\transpose}\mathcal A^P_nu,\mathcal A^V_nu)\).
\item Cone spectral lemma:
\(\sup_{u\in S}\|\mathcal A u\|=0\) if and only if
\(\mathcal C\subseteq\ker(\mathcal A)\), plus the lower and upper
distance-to-null bounds.
\item Continuity of finite-dimensional linear maps, used for the open-set
strict-separation conclusion.
\end{itemize}

\section{Conclusion and references}
This note proves the spectral compatibility frontier proposed for
\texttt{panel\_approx\_nbhd\_interference}/\texttt{v1}.  Uniform
interchangeability of the ANI point projection, design-orbit point
projection, and the named covariance operators over a declared sensitivity
class is equivalent to the computable condition \(\Delta_\eta=0\).  The
exposure-score coefficient is clean for the direct-plus-spillover target only
under the additional condition \(C^P_{\mathrm{ANI}}(U_M)=0\), or under the
oracle condition that removes the omitted tail altogether.  When the
compatibility condition fails, the main procedure-separation source is
explicit: \(a_{ds}^{\transpose}\mathcal A^P U_M\) drives point-estimand
separation and \(\mathcal A^V U_M\) drives covariance-law separation.  This
rowwise distinction is the nearest correct form of the strict-separation
claim above the frontier.

\subsection*{References}
\begin{thebibliography}{99}

\bibitem{AronowSamii2017Exposure}
Aronow, P. M. and C. Samii (2017).
Estimating average causal effects under general interference, with application
to a social network experiment.
\emph{Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem{BasseDingFellerToulis2024}
Basse, G., P. Ding, A. Feller, and P. Toulis (2024).
Randomization tests for peer effects in group formation experiments.
\emph{Econometrica} 92(2), 567--590.

\bibitem{BasseFellerToulis2019}
Basse, G. W., A. Feller, and P. Toulis (2019).
Randomization tests of causal effects under interference.
\emph{Biometrika} 106(2), 487--494.

\bibitem{Conley1999Spatial}
Conley, T. G. (1999).
GMM estimation with cross sectional dependence.
\emph{Journal of Econometrics} 92(1), 1--45.

\bibitem{GaoDing2025Network}
Gao, M. and P. Ding (2025).
Causal inference in network experiments: regression-based analysis and
design-based properties.
\emph{Journal of Econometrics} 252, 106119.

\bibitem{HudgensHalloran2008}
Hudgens, M. G. and M. E. Halloran (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.

\bibitem{KojevnikovMarmerSong2021}
Kojevnikov, D., V. Marmer, and K. Song (2021).
Limit theorems for network dependent random variables.
\emph{Journal of Econometrics} 222(2), 882--908.

\bibitem{Leung2022ANI}
Leung, M. P. (2022).
Causal inference under approximate neighborhood interference.
\emph{Econometrica} 90(1), 267--293.

\bibitem{Leung2023NCRI}
Leung, M. P. (2023).
Network cluster-robust inference.
\emph{Econometrica} 91(2), 641--667.

\bibitem{PuelzBasseFellerToulis2022}
Puelz, D., G. Basse, A. Feller, and P. Toulis (2022).
A graph-theoretic approach to randomization tests of causal effects under
general interference.
\emph{Journal of the Royal Statistical Society: Series B} 84(1), 174--204.

\bibitem{Savje2024MisspecifiedExposure}
Savje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions
and assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem{WeinsteinNevo2026}
Weinstein, B. and D. Nevo (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.

\end{thebibliography}

\end{document}
