\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\section*{exp_ego_cluster_exposure_clt (ego_cluster_polynomial_clt)}

\paragraph{TL;DR.} The proposal studies finite-population Horvitz-Thompson exposure contrasts in ego-cluster experiments when analyst-defined exposure labels are encoded by signed incidence polynomials over cluster treatment indicators. The main technical contribution is not a new generic dependency-graph CLT, but an explicit reduction from signed ego-cluster exposure supports to a computable dependency graph and overlap screen Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1), together with exact inclusion-exclusion formulas for the first and joint target-exposure probabilities. On the explicitly assumed variance-regular regime ass:variance-nondegenerate and the induced rate Delta_n=o(n^(1/4)), Chin's Stein bound then yields the design-based Horvitz-Thompson CLT and oracle Wald coverage. The feasible conservative Wald interval is a sharp complementary add-on built on that kernel: for the fixed HT contrast, Vbar_n = max_{y in F_n^obs} Q_n(y) is completion-sharp and pointwise shortest within the observed-data variance-envelope Wald family. Harshaw-Middleton-Savje (2112.01709) instead optimize over the class of quadratic-form variance estimators to obtain the minimally-conservative estimable upper bound of the unknown design variance, so the two optimizations are complementary rather than nested.

\section{Project justification}

\paragraph{Gap.} The literature has either the exposure-mapping HT architecture without ego-cluster probability algebra, generic dependency-graph CLTs that do not show how ego-cluster supports generate the required graph and degree inputs, model-based ego-cluster asymptotics without fixed-potential-outcome HT contrasts, or estimator-class conservative-variance programs that optimize a different object. The missing kernel is an explicit reduction from signed-incidence ego-cluster exposure supports to an overlap-derived dependency graph with an exact inclusion-exclusion algebra for the first and joint target-exposure probabilities, so that a variance-regular ego-cluster HT contrast can be checked against an existing dependency-graph CLT.

\paragraph{Niche.} This opens a design-based inference niche for platform-style ego experiments where the analyst wants exact exposure contrasts under user-defined local rules rather than regression coefficients under a working model.

\paragraph{Fill.} The project fills the gap by deriving exact first and joint exposure probabilities for signed incidence-polynomial labels, translating the same exposure supports into an explicit overlap-derived dependency graph with screen Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1), applying Chin's dependency-graph CLT on the explicitly assumed variance-regular regime ass:variance-nondegenerate, and adding a computable completion-sharp variance envelope as a sharp complementary observed-data Wald add-on.

\section{Related work}

Aronow and Samii (2017) provide the exposure-mapping Horvitz-Thompson architecture, randomization-based variance decomposition, and local-dependence asymptotics that this proposal keeps, but they leave the exposure probabilities and the dependence neighborhood abstract; the present contribution is to make both concrete for signed-incidence ego-cluster exposure rules by deriving exact first and joint target-exposure probabilities and the overlap-based dependency graph screen Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1). Ugander, Karrer, Backstrom, and Kleinberg (2013) compute exact probabilities for several graph-cluster exposure conditions and show that suitable clustering can sharply improve variance, but they do not give a signed incidence-polynomial algebra for ego-cluster exposure labels. Chin (2018) already proves Stein-method Horvitz-Thompson CLTs for dependency-graph sequences with maximal degree o(n^(1/4)); the present note does not strengthen that abstract CLT, but verifies its hypotheses for the ego-cluster HT contrast by deriving G_n^dep and the computable overlap screen from the contrast support geometry B_in and the overlap index omega_n, on the explicitly assumed variance-regular regime ass:variance-nondegenerate. Leung (2019) moves to approximate neighborhood interference and network HAC inference in a superpopulation framework, which is complementary but not a fixed finite-population HT Wald result for analyst-specified exposure labels. Chattopadhyay, Imai, and Zubizarreta (2023) develop design-based unbiased estimation and conservative variance estimators for stochastic-intervention estimands in generalized network experiments, but their estimand class differs from fixed exposure-label HT contrasts and does not supply the ego-incidence probability algebra or the same observed-data variance-envelope Wald family. Kung and Sussman (2022) characterize linear unbiased estimators under additive exposure models and identify optimal affine-basis estimators, but the additive restriction changes the estimand class and does not answer the nonadditive conservative-envelope question for Horvitz-Thompson exposure contrasts. Harshaw-Middleton-Savje (2112.01709) optimize over the class of quadratic-form variance estimators to obtain the minimally-conservative estimable upper bound of the unknown design variance. The feasible-Wald envelope here is a different optimization: for the fixed Horvitz-Thompson contrast variance, Vbar_n = max_{y in F_n^obs} Q_n(y) is the sharp upper envelope over the unknown bounded target-potential completions consistent with the realized exposure data. The two optimize over different domains (estimator class vs completion class), so the completion-sharp envelope is complementary to, not a special case of, the HMS estimator-optimization program. Gao and Ding (2023) show that regression-based network-robust covariances can be anti-conservative, which is why the proposal keeps the CLT and the conservative variance scope separate. Liu, Hu, and Zhang (2026) are the closest ego-cluster comparator, but their estimators and asymptotics are model-based and do not deliver exact exposure-weighted design-based inference.

\section{Setup}

Target estimand: tau_n = n^(-1) sum_{i=1}^n { Y_in(h_n^+) - Y_in(h_n^-) }.
Estimand-defining functional: hat_tau_HT_n = n^(-1) sum_{i=1}^n [ 1{E_ih_n^+n = 1} Y_in^obs / pi_ih_n^+n - 1{E_ih_n^-n = 1} Y_in^obs / pi_ih_n^-n ].
\begin{itemize}
  \item $n$ --- sample_size; N; design_size $:= Number of units in the finite population.$
  \item $m_n$ --- number_of_ego_clusters; N; design_size $:= Number of ego-clusters randomized at stage n.$
  \item $U_n$ --- finite_population; subsets of N; population_index $:= Unit index set U_n = {1, ..., n}.$
  \item $W_n$ --- cluster_assignment_vector; {0,1}^{m_n}; randomization $:= Ego-cluster treatment vector W_n = (W_cn)_{c=1}^{m_n}.$
  \item $p_n$ --- cluster_treatment_rate; (0,1); design_parameter $:= Bernoulli treatment probability for each ego-cluster.$
  \item $H_n$ --- exposure_label_set; finite set; exposure_codomain $:= Finite set of analyst-specified exposure labels.$
  \item $h_n^+$ --- target_exposure_label; H_n; target_label $:= Treated exposure label in the target contrast.$
  \item $h_n^-$ --- target_exposure_label; H_n; target_label $:= Reference exposure label in the target contrast.$
  \item $Y_in(h)$ --- potential_outcome; R; causal_primitive $:= Potential outcome for unit i in stage n under exposure label h.$
  \item $Y_in^obs$ --- observed_outcome; R; observed_outcome $:= Observed outcome for unit i in stage n under the realized exposure label.$
  \item $M_ihn$ --- signed_monomial_family; finite subsets of P({1,...,m_n} x {-1,1}); exposure_primitive $:= Family of signed cluster-index monomials defining exposure h for unit i at stage n.$
  \item $P_ihn(W_n)$ --- incidence_polynomial; {0,1,...,|M_ihn|}; exposure_map $:= Incidence polynomial whose positivity defines exposure label h for unit i.$
  \item $E_ihn$ --- exposure_event_indicator; {0,1}; exposure_event $:= Indicator that W_n places unit i in exposure label h.$
  \item $pi_ihn$ --- first_exposure_probability; (0,1]; known_design_probability $:= pi_ihn = Pr_pi(E_ihn = 1).$
  \item $pi_ij(h,h',n)$ --- joint_exposure_probability; [0,1]; known_design_probability $:= pi_ij(h,h',n) = Pr_pi(E_ihn = 1, E_jh'n = 1).$
  \item $B_ihn$ --- cluster_support; subsets of {1,...,m_n}; dependency_support $:= Set of ego-cluster indices appearing in at least one monomial in M_ihn.$
  \item $B_in$ --- contrast_support; subsets of {1,...,m_n}; dependency_support $:= Contrast support B_in = B_ih_n^+n union B_ih_n^-n.$
  \item $chi(A)$ --- literal_consistency_indicator; probability_algebra $:= chi(A) equals one when the union of signed literals in A contains no cluster index with both signs.$
  \item $u(A)$ --- treated_literal_count; probability_algebra $:= Number of distinct cluster indices that appear with sign +1 in the consistent union of A.$
  \item $v(A)$ --- control_literal_count; probability_algebra $:= Number of distinct cluster indices that appear with sign -1 in the consistent union of A.$
  \item $q_n$ --- max_monomial_degree; N; complexity_index $:= Maximum cardinality of any signed monomial in any M_ihn used by the target contrast.$
  \item $kappa_n$ --- max_monomial_count; N; complexity_index $:= Maximum number of signed monomials in any M_ihn used by the target contrast.$
  \item $omega_n$ --- max_ego_overlap; N; overlap_index $:= omega_n = max_c |{ i in U_n : c in B_in }|, the largest number of target-contrast units whose exposure supports involve the same ego-cluster c.$
  \item $b_n$ --- max_support_size; N; support_index $:= b_n = max_i |B_in|.$
  \item $M_Y$ --- outcome_bound; R_+; regularity_constant $:= Uniform bound on absolute potential outcomes.$
  \item $pi_min$ --- positivity_constant; (0,1); regularity_constant $:= Lower bound on target exposure probabilities pi_ih_n^+n and pi_ih_n^-n.$
  \item $c_sigma$ --- variance_constant; R_+; regularity_constant $:= Positive constant lower bounding n sigma_n^2.$
  \item $tau_n$ --- finite_population_exposure_contrast; R; target_estimand $:= tau_n = n^(-1) sum_{i=1}^n { Y_in(h_n^+) - Y_in(h_n^-) }.$
  \item $hat_tau_HT_n$ --- Horvitz_Thompson_exposure_contrast; R; design_based_estimator $:= Horvitz-Thompson estimator for tau_n using the two target exposure labels and their known design probabilities.$
  \item $psi_in$ --- raw_HT_summand; R; dependency_graph_node $:= psi_in = 1{E_ih_n^+n = 1} Y_in^obs / pi_ih_n^+n - 1{E_ih_n^-n = 1} Y_in^obs / pi_ih_n^-n.$
  \item $G_n^dep$ --- dependency_graph; graphs on U_n; dependence_object $:= Graph whose vertices are units and whose edges connect i and j whenever B_in and B_jn intersect.$
  \item $Delta_n$ --- max_dependency_degree; N; dependence_index $:= Maximum degree of G_n^dep.$
  \item $sigma_n^2$ --- design_variance; R_+; normalization $:= sigma_n^2 = Var_pi(hat_tau_HT_n).$
  \item $alpha$ --- coverage_level; (0,1); inference_parameter $:= Nominal miscoverage level for Wald intervals.$
  \item $CI_n^orc(1-alpha)$ --- oracle_Wald_interval; intervals in R; inference_object $:= CI_n^orc(1-alpha) = [hat_tau_HT_n - z_(1-alpha/2) sigma_n, hat_tau_HT_n + z_(1-alpha/2) sigma_n].$
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:bernoulli-ego-design]\label{ass:bernoulli-ego-design}
The ego-cluster assignments W_1n, ..., W_m_nn are mutually independent Bernoulli(p_n) random variables.
\par\smallskip\noindent\emph{Standard} (Bernoulli treatment assignment specialized to ego-clusters, \cite{AronowSamii2017}).
\end{assumption}

\begin{assumption}[ass:exposure-consistency]\label{ass:exposure-consistency}
For every i in U_n, the observed outcome satisfies Y_in^obs = sum_{h in H_n} 1{E_ihn = 1} Y_in(h), and at most one label h has E_ihn = 1.
\par\smallskip\noindent\emph{Standard} (Exposure-mapping consistency, \cite{AronowSamii2017}).
\end{assumption}

\begin{assumption}[ass:bounded-outcomes]\label{ass:bounded-outcomes}
max_{i in U_n, h in H_n} |Y_in(h)| <= M_Y.
\par\smallskip\noindent\emph{Standard} (Uniformly bounded potential outcomes, \cite{AronowSamii2017}).
\end{assumption}

\begin{assumption}[ass:positivity]\label{ass:positivity}
min_{i in U_n} { pi_ih_n^+n, pi_ih_n^-n } >= pi_min.
\par\smallskip\noindent\emph{Standard} (Exposure positivity, \cite{AronowSamii2017}).
\end{assumption}

\begin{assumption}[ass:variance-nondegenerate]\label{ass:variance-nondegenerate}
n sigma_n^2 >= c_sigma.
\par\smallskip\noindent\emph{Standard} (Nondegenerate design variance, \cite{Chin2018}).
\end{assumption}

\begin{assumption}[ass:primitive-degree-rate]\label{ass:primitive-degree-rate}
Delta_n / n^(1/4) -> 0 as n -> infinity (equivalently Delta_n = o(n^(1/4))).
\par\smallskip\noindent\emph{Novel.} The CLT needs the induced ego-overlap dependency degree to satisfy Delta_n=o(n^(1/4)); prop:dependency-degree gives the primitive sufficient screen Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1), so analysts may verify the stronger support-level bound when convenient.
\end{assumption}

\begin{assumption}[ass:uniform-primitive-degree-rate]\label{ass:uniform-primitive-degree-rate}
For any subclass C of def:clt-qualified-ego-incidence-array-class over which uniform coverage is claimed, rho_n^Delta(C):=sup_{array in C} Delta_n(array) / n^(1/4) -> 0 as n -> infinity.
\par\smallskip\noindent\emph{Novel.} standard: uniform version of a pointwise asymptotic sparsity condition used to convert a pointwise Berry-Stein bound into a uniform CLT. A sufficient support-level screen is sup_{array in C} b_n(array)(omega_n(array)-1)/n^(1/4) -> 0, via the prop:dependency-degree chain.
\end{assumption}

\section{Definitions}

\begin{definition}[def:ego-incidence-array-class]\label{def:ego-incidence-array-class}
$Positive-probability ego-incidence Bernoulli arrays := { ((Y_in(h))_{i in U_n, h in H_n}, (W_n)_{n>=1}, (M_ihn)_{i in U_n, h in {h_n^+, h_n^-}}) : ass:bernoulli-ego-design and ass:exposure-consistency and ass:bounded-outcomes and ass:positivity }$ --- the class of all objects satisfying: ass:bernoulli-ego-design; ass:exposure-consistency; ass:bounded-outcomes; ass:positivity.
\end{definition}

\begin{definition}[def:clt-qualified-ego-incidence-array-class]\label{def:clt-qualified-ego-incidence-array-class}
$Variance-regular CLT-qualified positive-probability ego-incidence Bernoulli arrays := { ((Y_in(h))_{i in U_n, h in H_n}, (W_n)_{n>=1}, (M_ihn)_{i in U_n, h in {h_n^+, h_n^-}}) : ass:bernoulli-ego-design and ass:exposure-consistency and ass:bounded-outcomes and ass:positivity and ass:variance-nondegenerate and ass:primitive-degree-rate }$ --- the class of all objects satisfying: ass:bernoulli-ego-design; ass:exposure-consistency; ass:bounded-outcomes; ass:positivity; ass:variance-nondegenerate; ass:primitive-degree-rate.
\end{definition}

\begin{definition}[def:literal-map]\label{def:literal-map}
$Signed cluster literal := For each cluster index c and sign sigma in {-1,1}, L_csigma_n(W_n) = W_cn if sigma = 1 and L_csigma_n(W_n) = 1 - W_cn if sigma = -1.$ \quad (\text{inputs: } W_n)
\end{definition}

\begin{definition}[def:incidence-polynomial]\label{def:incidence-polynomial}
$Signed incidence polynomial := P_ihn(W_n) = sum_{A in M_ihn} prod_{(c,sigma) in A} L_csigma_n(W_n).$ \quad (\text{inputs: } M_ihn, W_n)
\end{definition}

\begin{definition}[def:exposure-event]\label{def:exposure-event}
$Exposure event := E_ihn = 1{ P_ihn(W_n) >= 1 }.$ \quad (\text{inputs: } P_ihn(W_n))
\end{definition}

\begin{definition}[def:consistency-indicator]\label{def:consistency-indicator}
$Literal consistency indicator := chi(A) = 1 if no cluster index c appears with both signs +1 and -1 in the union of the signed monomials in A, and chi(A) = 0 otherwise.$ \quad (\text{inputs: } M_ihn)
\end{definition}

\begin{definition}[def:treated-literal-count]\label{def:treated-literal-count}
$Treated literal count := u(A) = |{ c : (c,1) appears in the union of A and (c,-1) does not appear in the union of A }|.$ \quad (\text{inputs: } chi(A))
\end{definition}

\begin{definition}[def:control-literal-count]\label{def:control-literal-count}
$Control literal count := v(A) = |{ c : (c,-1) appears in the union of A and (c,1) does not appear in the union of A }|.$ \quad (\text{inputs: } chi(A))
\end{definition}

\begin{definition}[def:ht-contrast]\label{def:ht-contrast}
$Horvitz-Thompson exposure contrast := hat_tau_HT_n = n^(-1) sum_{i=1}^n [ 1{E_ih_n^+n = 1} Y_in^obs / pi_ih_n^+n - 1{E_ih_n^-n = 1} Y_in^obs / pi_ih_n^-n ].$ \quad (\text{inputs: } n, E_ihn, Y_in^obs, pi_ihn, h_n^+, h_n^-)
\end{definition}

\begin{definition}[def:dependency-graph]\label{def:dependency-graph}
$Ego-overlap dependency graph := G_n^dep has vertex set U_n and edge set { {i,j} : i != j and B_in intersect B_jn is nonempty }.$ \quad (\text{inputs: } U_n, B_in)
\end{definition}

\begin{definition}[def:oracle-ci]\label{def:oracle-ci}
$Oracle Wald interval := CI_n^orc(1-alpha) = [hat_tau_HT_n - z_(1-alpha/2) sigma_n, hat_tau_HT_n + z_(1-alpha/2) sigma_n].$ \quad (\text{inputs: } hat_tau_HT_n, sigma_n^2, alpha)
\end{definition}

\begin{definition}[def:variance-envelope-handle]\label{def:variance-envelope-handle}
$Dual upper-envelope variance handle := Let R={+,-}, h_+=h_n^+, h_-=h_n^-, s_+=1, s_-=-1, pi_{ir}=pi_{i h_r n}, and E_{ir}=E_{i h_r n}. For i!=j set pi_{ij}^{rs}=pi_ij(h_r,h_s,n); for i=j set pi_{ii}^{rr}=pi_{ir} and pi_{ii}^{rs}=Pr_pi(E_{ir}=1,E_{is}=1), equal to 0 for distinct labels under exposure consistency and to pi_{ir} if the two labels coincide. Define Gamma_{ij}^{rs}=pi_{ij}^{rs}/(pi_{ir}pi_{js})-1 and Q_n(y)=n^{-2} sum_{i,j} sum_{r,s in R} s_r s_s Gamma_{ij}^{rs} y_{ir} y_{js}. Given realized exposure indicators and outcomes, let F_n^{obs}={y in [-M_Y,M_Y]^{2n}: E_{ir}=1 implies y_{ir}=Y_in^obs for every i,r}. Set Vbar_n=max_{y in F_n^{obs}} Q_n(y).$ \quad (\text{inputs: } pi_ihn, pi_ij(h,h',n), Y_in(h), M_Y)
\end{definition}

\section{Main results}

\begin{proposition}[prop:incidence-probabilities]\label{prop:incidence-probabilities}
Under ass:bernoulli-ego-design, for every unit i in U_n and target exposure label h in {h_n^+, h_n^-}, pi_ihn = sum_{emptyset != A subseteq M_ihn} (-1)^(|A|+1) chi(A) p_n^(u(A)) (1-p_n)^(v(A)). For every pair i != j and labels h, h' in {h_n^+, h_n^-}, pi_ij(h,h',n) = sum_{emptyset != A subseteq M_ihn} sum_{emptyset != B subseteq M_jh'n} (-1)^(|A|+|B|) chi(A union B) p_n^(u(A union B)) (1-p_n)^(v(A union B)).
\end{proposition}
Fix n, a unit i, and a target label h. For a monomial a in M_ihn, let C_a be the event that every signed literal in a is satisfied by W_n. By def:literal-map, def:incidence-polynomial, and def:exposure-event, E_ihn=1 exactly when at least one C_a with a in M_ihn occurs, because P_ihn(W_n) is the sum of the literal products and each product is a 0-1 indicator. Hence pi_ihn=Pr_pi(union_{a in M_ihn} C_a). Since M_ihn is finite, the ordinary inclusion-exclusion identity gives pi_ihn=sum_{emptyset != A subseteq M_ihn} (-1)^(|A|+1) Pr_pi(intersection_{a in A} C_a). The event intersection_{a in A} C_a is the event that every literal appearing in the union of the monomials in A is satisfied. By lem:literal-conjunction-probability, its probability is chi(A) p_n^(u(A)) (1-p_n)^(v(A)). Substitution gives the displayed first-exposure formula. For the joint formula, fix i != j and labels h,h'. Write C_a for monomials a in M_ihn and D_b for monomials b in M_jh'n. The event {E_ihn=1,E_jh'n=1} is (union_a C_a) intersect (union_b D_b). Expanding both union indicators by inclusion-exclusion and multiplying gives the coefficient (-1)^(|A|+1)(-1)^(|B|+1)=(-1)^(|A|+|B|) for each nonempty A subseteq M_ihn and nonempty B subseteq M_jh'n. The intersection event requires all literals in A union B. Applying lem:literal-conjunction-probability to A union B gives chi(A union B) p_n^(u(A union B)) (1-p_n)^(v(A union B)). Summing over A and B proves the joint formula.
\par\smallskip\noindent \textit{Justification.} Exact HT weighting and any design-based variance calculation require first and joint exposure probabilities, and the gap is algebraic rather than conceptual. \textit{Gap.} UganderKarrerBackstromKleinberg2013 gives exact probabilities for selected neighborhood-exposure conditions under graph-cluster randomization, but not a closed signed-incidence polynomial formula for ego-cluster exposure labels with both treated and control literals. \textit{Consumer.} This proposition turns analyst-chosen ego exposure rules into computable HT weights and computable joint probability inputs for the downstream CLT and variance question.

\begin{proposition}[prop:dependency-degree]\label{prop:dependency-degree}
Under ass:bernoulli-ego-design and ass:exposure-consistency, let G_n^dep be as in def:dependency-graph. Then the centered raw summands psi_in - E_pi[psi_in] admit G_n^dep as a dependency graph, and Delta_n <= b_n (omega_n - 1) <= 2 q_n kappa_n (omega_n - 1).
\end{proposition}
Let X_in=psi_in-E_pi[psi_in]. By ass:exposure-consistency, on the event E_ihn=1 the observed outcome equals Y_in(h), so the two target terms in psi_in can be written as E_ih_n^+n Y_in(h_n^+)/pi_ih_n^+n and E_ih_n^-n Y_in(h_n^-)/pi_ih_n^-n. The potential outcomes and probabilities are fixed finite-population constants. By def:incidence-polynomial and def:exposure-event, E_ihn is a measurable function only of the cluster assignments W_cn with c in B_ihn. Therefore X_in is measurable with respect to the sigma-field generated by {W_cn: c in B_in}. If two disjoint vertex sets A and C in U_n have no edge between them in G_n^dep, then B_in intersect B_jn is empty for every i in A and j in C, so the two unions of cluster supports are disjoint. Under ass:bernoulli-ego-design the assignment variables on disjoint cluster sets are independent, hence {X_in: i in A} and {X_jn: j in C} are independent. This is exactly the dependency-graph property for G_n^dep. For the degree bound, fix i. Every neighbor j of i shares at least one cluster c in B_in. For a fixed c, at most omega_n target-contrast units have c in their contrast support, so at most omega_n-1 of them are neighbors of i through c. A union bound over c in B_in gives deg(i) <= |B_in|(omega_n-1) <= b_n(omega_n-1). Taking the maximum over i gives Delta_n <= b_n(omega_n-1). Finally, for each target label h, B_ihn is the union of the cluster indices appearing in at most kappa_n monomials, each of cardinality at most q_n, so |B_ihn| <= q_n kappa_n. Since B_in = B_ih_n^+n union B_ih_n^-n, |B_in| <= 2 q_n kappa_n, hence b_n <= 2 q_n kappa_n and Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1). This is the concrete ego-support-to-dependency-graph reduction consumed downstream: once the support geometry is known, the abstract dependency degree entering Chin's Stein bound is directly screenable from b_n, omega_n, q_n, and kappa_n.
\par\smallskip\noindent \textit{Justification.} This is the load-bearing bridge from signed ego-cluster exposure primitives to an abstract dependency-graph CLT: it constructs the graph from support overlap and gives the computable screens Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1). \textit{Gap.} Chin2018 takes a dependency graph and its maximal degree as abstract inputs. This proposition derives both from the signed ego-support geometry B_in, with the extra factor two coming from the union of the treated-label and reference-label supports inside each contrast support. \textit{Consumer.} It is the exact handoff that lets analysts verify Chin's o(n^(1/4)) degree condition using the primitive overlap screens b_n(omega_n-1) or 2 q_n kappa_n(omega_n-1).

\begin{theorem}[thm:ego-overlap-clt]\label{thm:ego-overlap-clt}
Under ass:bernoulli-ego-design, ass:exposure-consistency, ass:bounded-outcomes, ass:positivity, ass:variance-nondegenerate, and ass:primitive-degree-rate, (hat_tau_HT_n - tau_n) / sigma_n converges in distribution to N(0,1). Consequently, for every fixed alpha in (0,1), Pr_pi{ tau_n in CI_n^orc(1-alpha) } -> 1 - alpha.
\end{theorem}
Let X_in=n^(-1)(psi_in-E_pi[psi_in]) and S_n=sum_{i=1}^n X_in. By lem:ht-unbiased-bounded and def:ht-contrast, S_n=hat_tau_HT_n-tau_n and Var_pi(S_n)=sigma_n^2. The same lemma gives |psi_in-E_pi[psi_in]| <= C_Y with C_Y=4 M_Y/pi_min, hence |X_in| <= C_Y/n, sum_i E_pi[X_in^4] <= C_Y^4 n^(-3), and sum_i E_pi[|X_in|^3] <= C_Y^3 n^(-2). By prop:dependency-degree, the X_in have dependency graph G_n^dep with maximum degree Delta_n, so the ego-cluster problem has been reduced to the abstract dependency-graph setup of lem:dependency-graph-normal-bound. Apply that cited normal-approximation bound with d=Delta_n, S=S_n, and sigma^2=sigma_n^2. Since ass:variance-nondegenerate gives n sigma_n^2 >= c_sigma, the first Stein term is at most K_1 Delta_n^(3/2) n^(-1/2), and the second is at most K_2 Delta_n^2 n^(-1/2), where K_1,K_2 depend only on M_Y, pi_min, c_sigma, and the universal constants in lem:dependency-graph-normal-bound. By ass:primitive-degree-rate, Delta_n=o(n^(1/4)); therefore Delta_n^(3/2)n^(-1/2)=o(n^(-1/8)) and Delta_n^2 n^(-1/2)=o(1). Thus d_W((hat_tau_HT_n-tau_n)/sigma_n,Z) -> 0 for Z standard normal. A standard Lipschitz smoothing of half-lines yields convergence in distribution to N(0,1): for any continuity point t of the normal cdf and any epsilon>0, approximate 1{x<=t} from above and below by 1/epsilon-Lipschitz functions that differ only on [t-epsilon,t+epsilon], use the Wasserstein bound, and then let epsilon down to zero. This proves (hat_tau_HT_n-tau_n)/sigma_n => N(0,1). For coverage, set z=z_(1-alpha/2). By def:oracle-ci, the event {tau_n in CI_n^orc(1-alpha)} is {|(hat_tau_HT_n-tau_n)/sigma_n| <= z}. Since z is a continuity point of the standard normal law, the just-proved convergence gives Pr_pi{|(hat_tau_HT_n-tau_n)/sigma_n| <= z} -> Phi(z)-Phi(-z)=1-alpha. This proves oracle Wald coverage.
\par\smallskip\noindent \textit{Justification.} This is an application theorem on a variance-regular subclass: prop:dependency-degree supplies the dependency graph and computable degree bound from ego-support overlap, prop:incidence-probabilities supplies the design probabilities, and Chin's dependency-graph Stein bound then yields the standardized HT CLT under Delta_n=o(n^(1/4)). \textit{Gap.} Chin2018 already provides the generic Horvitz-Thompson dependency-graph CLT under maximal degree o(n^(1/4)). The contribution here is to show that the ego-cluster HT contrast fits that substrate: signed-incidence exposure supports induce the dependency graph G_n^dep, the computable bound Delta_n <= b_n(omega_n-1) <= 2 q_n kappa_n(omega_n-1), and the exact exposure-probability inputs, on the explicitly assumed variance-regular regime ass:variance-nondegenerate. Relative to Aronow-Samii, the gain is this concrete ego-support reduction rather than a new abstract CLT. \textit{Consumer.} Once an ego design passes the overlap screens and the sequence is variance-regular, the theorem certifies that the standardized HT contrast inherits Chin's Gaussian limit and oracle Wald coverage.

\begin{lemma}[lem:variance-envelope-dominates]\label{lem:variance-envelope-dominates}
For every realized assignment and observed target-exposure dataset generated by an admissible finite-population array, the dual upper-envelope handle of def:variance-envelope-handle satisfies Vbar_n >= sigma_n^2 (pathwise).
\end{lemma}
Let y^0_{i+}=Y_in(h_n^+) and y^0_{i-}=Y_in(h_n^-). By ass:bounded-outcomes, y^0 lies in [-M_Y,M_Y]^(2n). By ass:exposure-consistency, whenever E_{ir}=1 for r in {+,-}, the observed outcome equals the corresponding target potential outcome, so y^0 satisfies all equality constraints defining F_n^obs. Hence y^0 in F_n^obs for every realized assignment and observed target-exposure dataset generated by the array. By lem:variance-quadratic-exact, Q_n(y^0)=sigma_n^2. Since Vbar_n is the maximum of Q_n over F_n^obs in def:variance-envelope-handle, Vbar_n >= Q_n(y^0)=sigma_n^2 pathwise.
\par\smallskip\noindent \textit{Justification.} The realized bounded target-potential completion is feasible for F_n^obs, so the envelope maximum dominates the realized design variance. \textit{Gap.} This records the pathwise completion argument needed by the feasible Wald theorem instead of leaving it implicit in proof prose. \textit{Consumer.} supporting lemma for thm:feasible-conservative-wald

\begin{lemma}[lem:variance-envelope-computable-attained]\label{lem:variance-envelope-computable-attained}
Given the realized exposure indicators and outcomes, F_n^obs is a finite-dimensional box with equality constraints and Vbar_n = max_{y in F_n^obs} Q_n(y) is an observed-data functional whose maximum is attained and computable from observed-population inputs.
\end{lemma}
Conditional on the realized exposure indicators and outcomes, F_n^obs is the subset of R^(2n) defined by the coordinate bounds -M_Y <= y_{ir} <= M_Y and the linear equalities y_{ir}=Y_in^obs for coordinates with E_{ir}=1. Thus it is a closed bounded finite-dimensional box with equality constraints; in particular it is compact, and it is nonempty for generated datasets because the true bounded target-potential vector is feasible by ass:exposure-consistency and ass:bounded-outcomes. The objective Q_n(y) in def:variance-envelope-handle is a finite quadratic polynomial in y whose coefficients are the design probabilities pi_{ir}, pi_{ij}^{rs} and signs s_r. The probabilities entering those coefficients are computable from the signed incidence families and p_n by prop:incidence-probabilities, with the diagonal convention stated in def:variance-envelope-handle. Hence Vbar_n is an explicit observed-data quadratic optimization problem with 2n variables, box constraints, and equality constraints. Continuity of Q_n on the compact feasible set gives attainment by Weierstrass' theorem, and the displayed finite-dimensional optimization is the claimed computable observed-data functional.
\par\smallskip\noindent \textit{Justification.} The feasible set is a closed bounded finite-dimensional polytope and Q_n uses only observed outcomes and design probabilities. \textit{Gap.} This makes the existence and computability of the variance-envelope optimizer explicit for the solver. \textit{Consumer.} supporting lemma for thm:feasible-conservative-wald

\begin{lemma}[lem:variance-envelope-sharp]\label{lem:variance-envelope-sharp}
Vbar_n is the pointwise smallest observed-data upper envelope for sigma_n^2 over all bounded target-potential completions consistent with the realized target-exposure data.
\end{lemma}
Fix a realized observed target-exposure dataset and consider the bounded completion class F_n^obs from def:variance-envelope-handle. For each completion y in F_n^obs, lem:variance-quadratic-exact identifies Q_n(y) as the design variance that the HT contrast would have if y were the vector of target potential outcomes. By definition Vbar_n=max_{y in F_n^obs} Q_n(y). Therefore Vbar_n itself dominates the variance for every bounded completion. Conversely, let U be any observed-data upper envelope that dominates sigma_n^2 for every bounded target-potential completion consistent with the same observed data. Applying this domination property to each y in F_n^obs gives U >= Q_n(y) for all y in F_n^obs, hence U >= sup_{y in F_n^obs} Q_n(y)=Vbar_n. Thus no smaller observed-data upper envelope can dominate all completions, and Vbar_n is pointwise smallest.
\par\smallskip\noindent \textit{Justification.} Since Vbar_n is the supremum of Q_n over the completion class, any observed-data upper envelope over that class must be at least Vbar_n. \textit{Gap.} This isolates the theorem's sharpness claim within the observed-data variance-envelope family. \textit{Consumer.} supporting lemma for thm:feasible-conservative-wald

\begin{lemma}[lem:uniform-oracle-wald-coverage]\label{lem:uniform-oracle-wald-coverage}
Under ass:bernoulli-ego-design, ass:exposure-consistency, ass:bounded-outcomes, ass:positivity, ass:variance-nondegenerate, and ass:uniform-primitive-degree-rate, for any subclass C of def:clt-qualified-ego-incidence-array-class over which uniform coverage is claimed, liminf_n inf_{A in C} Pr_{pi,A}{ |hat_tau_HT_n - tau_n| <= z_(1-alpha/2) sigma_n(A) } >= 1 - alpha (uniform oracle Wald coverage).
\end{lemma}
For an array A in the subclass C, set X_i(A)=n^(-1)(psi_i(A)-E_{pi,A} psi_i(A)) and S_A=sum_i X_i(A). The proof of thm:ego-overlap-clt, using lem:ht-unbiased-bounded, prop:dependency-degree, ass:variance-nondegenerate, and lem:dependency-graph-normal-bound, gives constants K_1,K_2 independent of A such that d_W(S_A/sigma_n(A),Z) <= K_1 Delta_n(A)^(3/2)n^(-1/2)+K_2 Delta_n(A)^2 n^(-1/2). Let rho_n^Delta(C)=sup_{A in C} Delta_n(A)/n^(1/4). Taking suprema over A in C yields sup_A d_W(S_A/sigma_n(A),Z) <= K_1 (rho_n^Delta(C))^(3/2)n^(-1/8)+K_2 (rho_n^Delta(C))^2, which tends to zero by ass:uniform-primitive-degree-rate. Let z=z_(1-alpha/2). For epsilon in (0,z), choose a Lipschitz function f_epsilon with 0 <= f_epsilon <= 1{|x|<=z}, f_epsilon(x)=1 for |x|<=z-epsilon, and Lipschitz constant at most 1/epsilon. Then uniformly in A, Pr_{pi,A}{|S_A| <= z sigma_n(A)} >= E f_epsilon(S_A/sigma_n(A)) >= E f_epsilon(Z)-epsilon^(-1) sup_A d_W(S_A/sigma_n(A),Z) >= Pr{|Z|<=z-epsilon}-epsilon^(-1) sup_A d_W(S_A/sigma_n(A),Z). Taking infimum over A, then liminf_n, gives at least Pr{|Z|<=z-epsilon}. Finally let epsilon down to zero and use continuity of the normal cdf to obtain liminf_n inf_{A in C} Pr_{pi,A}{|hat_tau_HT_n-tau_n| <= z sigma_n(A)} >= Pr{|Z|<=z}=1-alpha. The identity S_A=hat_tau_HT_n-tau_n follows from def:ht-contrast and lem:ht-unbiased-bounded.
\par\smallskip\noindent \textit{Justification.} The same dependency-graph Stein bound used pointwise becomes uniform after taking the degree-rate supremum over a variance-regular subclass. \textit{Gap.} This separates uniform oracle Wald coverage from thm:ego-overlap-clt so the feasible theorem has an explicit uniform coverage input. \textit{Consumer.} supporting lemma for thm:feasible-conservative-wald

\begin{theorem}[thm:feasible-conservative-wald]\label{thm:feasible-conservative-wald}
Under ass:bernoulli-ego-design, ass:exposure-consistency, ass:bounded-outcomes, ass:positivity, ass:variance-nondegenerate, and ass:primitive-degree-rate, with Vbar_n the computable functional of def:variance-envelope-handle, for every fixed alpha in (0,1), liminf_n Pr_pi{ tau_n in [hat_tau_HT_n - z_(1-alpha/2) sqrt(Vbar_n), hat_tau_HT_n + z_(1-alpha/2) sqrt(Vbar_n)] } >= 1 - alpha for each sequence in def:clt-qualified-ego-incidence-array-class, and uniformly over any subclass satisfying ass:uniform-primitive-degree-rate. Moreover Vbar_n is the pointwise smallest observed-data upper envelope for sigma_n^2 over bounded target-potential completions consistent with the realized target-exposure data, so this feasible Wald interval is the sharp conservative one in that class.
\end{theorem}
First fix a single sequence in def:clt-qualified-ego-incidence-array-class and write z=z_(1-alpha/2). By lem:variance-envelope-computable-attained, Vbar_n is an observed-data computable maximum. By lem:variance-envelope-dominates, Vbar_n >= sigma_n^2 pathwise for every realized assignment, so sqrt(Vbar_n) >= sigma_n. Therefore the oracle event {|hat_tau_HT_n-tau_n| <= z sigma_n} is pathwise contained in the feasible event {|hat_tau_HT_n-tau_n| <= z sqrt(Vbar_n)}. Taking probabilities and then liminf gives liminf_n Pr_pi{|hat_tau_HT_n-tau_n| <= z sqrt(Vbar_n)} >= liminf_n Pr_pi{|hat_tau_HT_n-tau_n| <= z sigma_n}. The right side equals 1-alpha by thm:ego-overlap-clt. This proves pointwise conservative coverage. For a subclass C satisfying ass:uniform-primitive-degree-rate, the same pathwise containment holds for every array A in C, hence inf_A Pr_A(feasible event) >= inf_A Pr_A(oracle event). Taking liminf and applying lem:uniform-oracle-wald-coverage gives the uniform lower bound 1-alpha. Finally, lem:variance-envelope-sharp states that Vbar_n is the pointwise smallest observed-data upper envelope for sigma_n^2 over bounded target-potential completions consistent with the realized target-exposure data. Since the Wald half-length z sqrt(V) is increasing in any nonnegative variance envelope V, Vbar_n gives the pointwise shortest conservative Wald interval within the observed-data variance-envelope Wald family for this fixed HT contrast. This is the asserted sharp conservative interpretation, and it is distinct from any claim of global minimality over all variance procedures.
\par\smallskip\noindent \textit{Justification.} The feasible conservative variance is a sharp complementary add-on to the variance-regular CLT kernel: because Vbar_n >= sigma_n^2 pathwise for the fixed HT contrast, the oracle confidence interval is contained in the feasible one, so coverage transfers from thm:ego-overlap-clt by monotonicity with no extra assumption; sharpness is only within the observed-data variance-envelope Wald family. \textit{Gap.} Harshaw-Middleton-Savje (2112.01709) optimize over the class of quadratic-form variance estimators to obtain the minimally-conservative estimable upper bound of the unknown design variance. The feasible-Wald envelope here is a different optimization: for the fixed Horvitz-Thompson contrast variance, Vbar_n = max_{y in F_n^obs} Q_n(y) is the sharp upper envelope over the unknown bounded target-potential completions consistent with the realized exposure data. The two optimize over different domains (estimator class vs completion class), so the completion-sharp envelope is complementary to, not a special case of, the HMS estimator-optimization program. The theorem does not claim global minimal conservativeness over all variance procedures or all conservative intervals; it claims pointwise shortest Wald half-length only within the observed-data variance-envelope Wald family for the fixed HT contrast. \textit{Consumer.} The theorem turns the oracle CLT on the variance-regular overlap-screened class into an operational confidence interval for platform ego experiments, as a completion-sharp add-on to the signed-incidence dependency-graph kernel and without importing model-based regression assumptions.

\begin{lemma}[lem:literal-conjunction-probability]\label{lem:literal-conjunction-probability}
Under ass:bernoulli-ego-design, for any finite nonempty collection C of signed monomials, the probability that every literal appearing in the union of C is satisfied equals chi(C) p_n^(u(C)) (1-p_n)^(v(C)).
\end{lemma}
If the union of literals in C contains both (c,+1) and (c,-1) for some cluster c, then the event requires W_cn=1 and W_cn=0 simultaneously, so its probability is zero. In this case chi(C)=0, and the displayed expression is zero. If the union is consistent, it requires W_cn=1 for exactly u(C) distinct clusters and W_cn=0 for exactly v(C) distinct clusters, with no other restrictions. By ass:bernoulli-ego-design the W_cn are mutually independent Bernoulli(p_n), so the probability is p_n^(u(C))(1-p_n)^(v(C)). Since chi(C)=1 in the consistent case, this is chi(C) p_n^(u(C))(1-p_n)^(v(C)).

\begin{lemma}[lem:ht-unbiased-bounded]\label{lem:ht-unbiased-bounded}
Under ass:exposure-consistency, ass:bounded-outcomes, and ass:positivity, E_pi[psi_in] = Y_in(h_n^+) - Y_in(h_n^-) for every i, hat_tau_HT_n is unbiased for tau_n, and |psi_in - E_pi[psi_in]| <= 4 M_Y / pi_min.
\end{lemma}
On the event E_ihn=1, ass:exposure-consistency gives Y_in^obs=Y_in(h), because at most one exposure label is realized. Therefore E_pi[1{E_ihn=1}Y_in^obs/pi_ihn]=Y_in(h) Pr_pi(E_ihn=1)/pi_ihn=Y_in(h). Applying this identity to h_n^+ and h_n^- gives E_pi[psi_in]=Y_in(h_n^+)-Y_in(h_n^-). Averaging over i and using def:ht-contrast gives E_pi[hat_tau_HT_n]=tau_n. For boundedness, ass:bounded-outcomes and ass:positivity imply |psi_in| <= 2 M_Y/pi_min, while |E_pi psi_in| <= |Y_in(h_n^+)|+|Y_in(h_n^-)| <= 2 M_Y. Since pi_min <= 1, |psi_in-E_pi psi_in| <= 2 M_Y/pi_min+2 M_Y <= 4 M_Y/pi_min.

\begin{lemma}[lem:dependency-graph-normal-bound]\label{lem:dependency-graph-normal-bound}
Let X_1,...,X_N be centered random variables with dependency graph of maximum degree d, let S=sum_i X_i, and let sigma^2=Var(S)>0. There are universal constants C_1,C_2 such that, for Z standard normal, d_W(S/sigma,Z) <= C_1 d^(3/2) sigma^(-2) (sum_i E[X_i^4])^(1/2) + C_2 d^2 sigma^(-3) sum_i E[|X_i|^3].
\end{lemma}
Let X_1,...,X_N be centered random variables with dependency graph of maximum degree d, let S=sum_i X_i, and let sigma^2=Var(S)>0. There are universal constants C_1,C_2 such that, for Z standard normal, d_W(S/sigma,Z) <= C_1 d^(3/2) sigma^(-2) (sum_i E[X_i^4])^(1/2) + C_2 d^2 sigma^(-3) sum_i E[|X_i|^3].

\begin{lemma}[lem:variance-quadratic-exact]\label{lem:variance-quadratic-exact}
For the notation in def:variance-envelope-handle, define T_n(y)=n^(-1) sum_i sum_{r in {+,-}} s_r E_{ir} y_{ir}/pi_{ir}. For every fixed y in R^(2n), Var_pi(T_n(y))=Q_n(y). For the true target vector y^0_{i+}=Y_in(h_n^+) and y^0_{i-}=Y_in(h_n^-), T_n(y^0)=hat_tau_HT_n and Q_n(y^0)=sigma_n^2.
\end{lemma}
For fixed y, expand the variance of T_n(y). The covariance between E_{ir}y_{ir}/pi_{ir} and E_{js}y_{js}/pi_{js} is y_{ir}y_{js}[E_pi(E_{ir}E_{js})/(pi_{ir}pi_{js})-1]. By the definition of pi_{ij}^{rs}, including the diagonal convention for i=j in def:variance-envelope-handle, E_pi(E_{ir}E_{js})=pi_{ij}^{rs}. Multiplying by n^(-2)s_r s_s and summing over i,j,r,s gives exactly Q_n(y). For the true vector y^0, ass:exposure-consistency gives E_{ir}Y_in^obs=E_{ir}y^0_{ir}, so T_n(y^0) is the Horvitz-Thompson contrast in def:ht-contrast. Therefore Q_n(y^0)=Var_pi(T_n(y^0))=Var_pi(hat_tau_HT_n)=sigma_n^2.

\section{Honest scope}

Settled target: exact first and joint exposure probabilities for the signed incidence-polynomial class, an overlap-derived dependency graph with growing-degree condition Delta_n=o(n^(1/4)) and sufficient screens b_n(omega_n-1)=o(n^(1/4)) or 2 q_n kappa_n(omega_n-1)=o(n^(1/4)), together with the explicit variance-regular regime assumption ass:variance-nondegenerate under which Chin's dependency-graph Horvitz-Thompson CLT yields oracle Wald coverage. The feasible conservative Wald interval is a sharp complementary add-on: for the fixed HT contrast, Vbar_n = max_{y in F_n^obs} Q_n(y) is a computable completion-sharp variance envelope delivering at-least-nominal coverage only within the observed-data variance-envelope Wald family. Harshaw-Middleton-Savje (2112.01709) optimize over quadratic-form variance estimators rather than bounded target-potential completions, so this proposal is complementary to their estimator-optimization program. The proposal deliberately does not claim to derive ass:variance-nondegenerate from the primitive overlap conditions, to improve Chin's generic o(n^(1/4)) CLT, to be a first design-based inference object, to be a new general conservative-variance framework, to be globally minimally conservative over all intervals, to be optimal for HT relative to alternative linear estimators, or to solve a general design problem over all clusterings.

\begin{thebibliography}{99}

  \bibitem{AronowSamii2017} Aronow, Peter M., and Cyrus Samii (2017). "Estimating Average Causal Effects Under General Interference, with Application to a Social Network Experiment." Annals of Applied Statistics 11(4): 1912-1947.

  \bibitem{UganderKarrerBackstromKleinberg2013} Ugander, Johan, Brian Karrer, Lars Backstrom, and Jon Kleinberg (2013). "Graph Cluster Randomization: Network Exposure to Multiple Universes." Proceedings of KDD 2013.

  \bibitem{Chin2018} Chin, Alex (2018). "Central Limit Theorems via Stein's Method for Randomized Experiments under Interference." arXiv:1804.03105.

  \bibitem{Leung2019ANI} Leung, Michael P. (2019). "Causal Inference Under Approximate Neighborhood Interference." arXiv:1911.07085.

  \bibitem{GaoDing2023} Gao, Mengsi, and Peng Ding (2023). "Causal Inference in Network Experiments: Regression-Based Analysis and Design-Based Properties." arXiv:2309.07476.

  \bibitem{ChattopadhyayImaiZubizarreta2023} Chattopadhyay, Ambarish, Kosuke Imai, and Jose R. Zubizarreta (2023). "Design-Based Inference for Generalized Network Experiments with Stochastic Interventions." arXiv:2312.03268.

  \bibitem{KungSussman2022} Kung, Kelly, and Daniel L. Sussman (2022). "Unbiased Estimation for Additive Exposure Models." arXiv:2209.01053.

  \bibitem{HarshawMiddletonSavje2026} Harshaw, Christopher, Joel A. Middleton, and Fredrik Sävje (2026). "Optimized Variance Estimation under Interference and Complex Experimental Designs." Journal of the American Statistical Association. arXiv:2112.01709.

  \bibitem{SavjeAronowHudgens2021} Sävje, Fredrik, Peter M. Aronow, and Michael G. Hudgens (2021). "Average Treatment Effects in the Presence of Unknown Interference." Annals of Statistics 49(2): 673-701.

  \bibitem{AronowEcklesSamiiZonszein2021} Aronow, Peter M., Dean Eckles, Cyrus Samii, and Stephanie Zonszein (2021). "Spillover Effects in Experimental Data." In Handbook of Research Methods in Health Social Sciences.

  \bibitem{LiuHuZhang2026} Liu, Xiao, Feifang Hu, and Jingfei Zhang (2026). "Estimating Treatment and Spillover Effects with the Ego-Cluster Experimental Design." arXiv:2605.00534.

\end{thebibliography}

\end{document}