\paragraph{\S9-fragment-statement.}
\paragraph{Motivating conjecture, restated verbatim.}
Under Assumptions~\ref{ass:causal}--\ref{ass:local-rich}, there exists a constant $c>0$ such that every estimator $\tilde\theta_n$ obeys
\[
  \sup_{P\in\mathcal{P}_n^{\mathrm{SA\text{-}CATE}}}
  E_P\left|\tilde\theta_n-\tau_P(x_0)\right|
  \ge c\left(b_n+(n p_n)^{-1/2}+\sqrt{r_{g,n}r_{m,n}}\right).
\]

\begin{theorem}[Conjecture 2: localized structure-agnostic converse]\label{thm:lower}
Under Assumptions~\ref{ass:causal}--\ref{ass:local-rich}, there is a constant $c>0$, depending only on the boundedness and overlap constants in Assumptions~\ref{ass:causal} and~\ref{ass:bounded} and on the perturbation constants in Assumption~\ref{ass:local-rich}, such that every estimator $\tilde\theta_n=\tilde\theta_n(W_1,\ldots,W_n)$ satisfies \[ \sup_{P\in\mathcal{P}_n^{\mathrm{SA\text{-}CATE}}} E_P\!\left|\tilde\theta_n-\tau_P(x_0)\right| \ge c\left\{b_n+(n p_n)^{-1/2}+\sqrt{r_{g,n}r_{m,n}}\right\}. \]
\end{theorem}

\paragraph{\S13-refutation-attempt.}
\paragraph{Primitive attempted.}
The refutation search used the least-favorable submodel primitive.  The searched witnesses were the three smallest two-point or fuzzy experiments compatible with the statement: a bias-only point perturbation, a local Bernoulli-mean perturbation inside the effective support of $K_{h_n}$, and a two-step nuisance perturbation of $(g_0,g_1,e)$.

\paragraph{Bias-only witness.}
The candidate witness tries to keep the observed law fixed while moving only the point value $\tau_P(x_0)$ by a constant multiple of $b_n$.  This does not refute the conjecture.  Under Assumption~\ref{ass:bias}, such a witness is precisely the localization-bias channel; indistinguishability strengthens the lower bound because the total variation distance is zero.  If $b_n=0$, the channel is silent rather than contradictory.

\paragraph{Local-sampling witness.}
The candidate witness perturbs the treated-minus-control regression on the effective support of $K_{h_n}$ by $\delta_s\asymp(n p_n)^{-1/2}$.  Because the perturbation is seen only on probability mass $p_n$, the $n$-sample Kullback--Leibler divergence is $O(n p_n\delta_s^2)=O(1)$, while the point target moves by order $\delta_s$.  This witness again supports the conjecture rather than violating it.  Pushing $p_n$ to zero does not create a counterexample because Assumption~\ref{ass:effective} retains $n p_n\to\infty$ and Assumption~\ref{ass:causal} requires positive local mass.

\paragraph{Nuisance-product witness.}
The candidate witness uses the two-step perturbation template of \cite{JinSyrgkanis2025GeneralLinearFunctionalLowerBounds}: first perturb one nuisance direction at local weighted size $\sqrt{r_{m,n}}$, then pair a second local perturbation at size $\sqrt{r_{g,n}}$ so that first-order terms are hidden but the second-order target separation remains.  The localized AIPW algebra in Theorem~\ref{thm:localized-aipw} shows that the resulting separation has product scale $\sqrt{r_{g,n}r_{m,n}}$.  Assumption~\ref{ass:local-rich} declares exactly these local bounded perturbation pairs admissible for the Le Cam converse.  No boundary witness was found: overlap is kept in $[\epsilon,1-\epsilon]$, bounded outcomes keep all divergences finite, and the local effective-support requirement rules out perturbations outside the observable neighborhood.  The refutation attempt therefore fails, and the positive proof proceeds.

\paragraph{\S10 Interpretation.}
The theorem says that the three terms in
\[
  \rho_n=b_n+(n p_n)^{-1/2}+\sqrt{r_{g,n}r_{m,n}}
\]
are not artifacts of the localized doubly robust estimator.  The bias term is forced by the gap between the smoothed local target $\theta_{h_n}(P)$ and the point target $\tau_P(x_0)$.  The local-sampling term is forced because only about $n p_n$ observations carry effective weight near $x_0$.  The nuisance-product term is forced by the same second-order orthogonal-score geometry that produces the product remainder in the upper bound: without additional structure on the nuisance functions, a black-box learner cannot remove the mixed perturbation.  Thus Conjecture 2 is confirmed as the converse half of the structure-agnostic pointwise CATE rate.

\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:lower}]
Let
\[
  \mathfrak R_n(\tilde\theta_n)
  =
  \sup_{P\in\mathcal{P}_n^{\mathrm{SA\text{-}CATE}}}
  E_P|\tilde\theta_n-\tau_P(x_0)|.
\]
We repeatedly use the following Le Cam consequence.  Suppose two laws $P_0,P_1$ in the model satisfy
\[
  |\tau_{P_1}(x_0)-\tau_{P_0}(x_0)|\ge 2\Delta
  \quad\text{and}\quad
  \operatorname{TV}(P_0^n,P_1^n)\le \kappa<1 .
\]
Then every estimator obeys
\[
  \sup_{j\in\{0,1\}}E_{P_j}|\tilde\theta_n-\tau_{P_j}(x_0)|
  \ge
  \frac{\Delta}{2}(1-\kappa).
\]
Indeed, if both risks were smaller, the test that chooses the parameter value closest to $\tilde\theta_n$ would distinguish $P_0^n$ from $P_1^n$ with total error probability below the Le Cam testing lower bound.  The same inequality applies when $P_1^n$ is replaced by a mixture of alternatives, with total variation between $P_0^n$ and the mixture replacing $\operatorname{TV}(P_0^n,P_1^n)$.

\emph{Step 1: the localization-bias channel.}
By Assumption~\ref{ass:bias}, the model allows point targets whose distance from the localized target is as large as a constant multiple of the envelope $b_n$.  Assumption~\ref{ass:local-rich} supplies bounded local point-target perturbations supported inside the effective support of $K_{h_n}$ and preserving Assumptions~\ref{ass:causal}--\ref{ass:effective}.  Hence there are $P_b^-$ and $P_b^+$ in the model such that their observed $n$-sample laws are indistinguishable up to a fixed total-variation bound and
\[
  |\tau_{P_b^+}(x_0)-\tau_{P_b^-}(x_0)|\ge c_b b_n .
\]
In the continuous-design version the two observed laws may even agree away from the null point $\{x_0\}$, so the total-variation bound is zero.  The preceding Le Cam inequality gives
\[
  \mathfrak R_n(\tilde\theta_n)\ge c_b' b_n .
\]

\emph{Step 2: the local effective-sample-size channel.}
Fix an anchor law $P_s$ satisfying Assumptions~\ref{ass:causal}--\ref{ass:effective}.  Inside the effective support of $K_{h_n}$, perturb $g_1-g_0$ by
\[
  \delta_s a_n(x),\qquad
  \delta_s=c_s(n p_n)^{-1/2},
\]
where $a_n$ is bounded, supported on $\{K_{h_n}>0\}$, and normalized so that
$E_{P_s}[\ell_{h_n}(X)a_n(X)]$ is bounded away from zero.  Assumption~\ref{ass:local-rich} makes the corresponding pair $P_s^0,P_s^1$ admissible, and Assumption~\ref{ass:bounded} keeps all outcome probabilities or conditional densities uniformly bounded.  The target separation is
\[
  |\tau_{P_s^1}(x_0)-\tau_{P_s^0}(x_0)|
  \ge c_s'(n p_n)^{-1/2}.
\]
The single-observation divergence is of order $p_n\delta_s^2$ because the perturbation is localized on mass $p_n$ and has amplitude $\delta_s$.  Therefore
\[
  \operatorname{KL}\!\left((P_s^0)^n,(P_s^1)^n\right)
  \le C n p_n\delta_s^2
  = Cc_s^2 .
\]
Choosing $c_s$ small enough and using Pinsker's inequality gives total variation at most a constant $\kappa<1$.  Le Cam then yields
\[
  \mathfrak R_n(\tilde\theta_n)\ge c_s''(n p_n)^{-1/2}.
\]

\emph{Step 3: the nuisance-product channel.}
Theorem~\ref{thm:localized-aipw} gives the localized orthogonal-score identity and the product drift algebra.  To obtain the matching converse, apply the structure-agnostic fuzzy-hypothesis construction of \cite{JinSyrgkanis2025GeneralLinearFunctionalLowerBounds} to the localized score: start from an anchor law $P_\star$, draw a sign vector $\lambda$, and form alternatives $P_\lambda$ by two local perturbations.  The propensity perturbation has local weighted norm
\[
  E_{P_\star}[\ell_{h_n}(X)(e_\lambda-e_\star)^2]\asymp r_{m,n},
\]
and the outcome-regression perturbation has local weighted norm
\[
  E_{P_\star}[\ell_{h_n}(X)\{(g_{1,\lambda}-g_{1,\star})^2+(g_{0,\lambda}-g_{0,\star})^2\}]
  \asymp r_{g,n}.
\]
The signs are paired over local cells so that all first-order changes in the observed nuisance constraints cancel in the mixture, while the second-order inner product remains.  This is the localized analogue of the two-step sequential perturbation and pairing argument in \cite{JinSyrgkanis2025GeneralLinearFunctionalLowerBounds}; Assumption~\ref{ass:local-rich} is the model-side condition ensuring that the resulting bounded laws remain in $\mathcal{P}_n^{\mathrm{SA\text{-}CATE}}$ and preserve Assumptions~\ref{ass:causal}--\ref{ass:effective}.

For each signed alternative,
\[
  |\tau_{P_\lambda}(x_0)-\tau_{P_\star}(x_0)|
  \ge c_m\sqrt{r_{g,n}r_{m,n}} .
\]
The same construction makes the mixture $\bar P^n=2^{-M}\sum_\lambda P_\lambda^n$ indistinguishable from $P_\star^n$:
\[
  \chi^2(\bar P^n,(P_\star)^n)\le C_M
\]
for an absolute constant that can be made smaller than a universal threshold by scaling the perturbation amplitudes.  Total variation is therefore bounded away from one.  The fuzzy Le Cam inequality gives
\[
  \mathfrak R_n(\tilde\theta_n)\ge c_m'\sqrt{r_{g,n}r_{m,n}}.
\]

\emph{Step 4: combine channels.}
The three displays give constants $a_b,a_s,a_m>0$ such that
\[
  \mathfrak R_n(\tilde\theta_n)
  \ge
  \max\left\{a_b b_n,\ a_s(n p_n)^{-1/2},\ a_m\sqrt{r_{g,n}r_{m,n}}\right\}.
\]
Let $a=\min\{a_b,a_s,a_m\}$.  Since $\max\{u,v,w\}\ge (u+v+w)/3$ for nonnegative $u,v,w$,
\[
  \mathfrak R_n(\tilde\theta_n)
  \ge
  \frac{a}{3}\left\{b_n+(n p_n)^{-1/2}+\sqrt{r_{g,n}r_{m,n}}\right\}.
\]
Taking $c=a/3$ proves the theorem.
\end{proof}

\paragraph{\S12 Sanity check.}
In the regular nonlocal corner, take $K_{h_n}\equiv1$, so $p_n=1$, and suppose the point target is already the global target, so $b_n=0$.  If the nuisances are known or estimated at rates with $r_{g,n}r_{m,n}=o(n^{-1})$, the theorem reduces to
\[
  \sup_{P\in\mathcal{P}_n^{\mathrm{SA\text{-}CATE}}}
  E_P|\tilde\theta_n-\tau_P(x_0)|\ge c n^{-1/2}.
\]
This is the usual parametric lower bound for an identified mean-type treatment-effect functional under bounded outcomes and overlap.  Thus the localized converse agrees with the classical root-$n$ benchmark when the local neighborhood is the whole population and the nuisance-product channel is negligible.

\paragraph{\S13 Counterexample or minimality check.}
Assumption~\ref{ass:local-rich} is essential.  If it is removed, let the model contain only a single law $P_\star$ satisfying Assumptions~\ref{ass:causal}--\ref{ass:effective} with $b_n+(n p_n)^{-1/2}+\sqrt{r_{g,n}r_{m,n}}>0$.  The constant estimator $\tilde\theta_n\equiv\tau_{P_\star}(x_0)$ has zero risk on this singleton model, while the right-hand side of the conjectured lower bound is positive.  Hence a nondegenerate local perturbation condition is not cosmetic: it is the rank/support condition that creates the Le Cam experiments behind all three lower-bound channels.
