% file-plan: bypass-justified: the substrate survey found no direct fixed-policy MSM-CVaR primitive; this fragment works at the paper-level observable-law, marginal-sensitivity, and finite response-type LP layer and cites no implementation files.

\paragraph{\S9-fragment-statement: Refutation note for the labelled solve target \texttt{noncommutation}.}\label{prop:noncommutation-refuted}
\paragraph{Conjecture restated verbatim.}\label{conj:noncommutation}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail},
\[
\Delta_{\mathrm{nc}}(\pi;P)=
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
-\underline W_{\tau,\Gamma}(\pi;P)\geq 0.
\]
Moreover, there is a two-action, three-outcome, one-covariate-cell class satisfying strict overlap and \(1<\Gamma<\infty\) on which \(\Delta_{\mathrm{nc}}(\pi;P)>0\).  Equality holds when the same monotone least-favorable MSM tilt is simultaneously optimal for all \(\eta\) in the active subgradient set of \(\mathcal C_\eta(P,\pi)\).

\textbf{Verdict.} Refuted: the strict-existence clause is false under the shared pointwise-CDF band definition. In the two-action, three-outcome, one-covariate-cell MSM response-type LP with strict overlap and any \(1<\Gamma<\infty\), the monotone upper-tail MSM tilt is a common first-order-stochastically maximal vertex for every threshold and every generated loss \((Y-\eta)_+\). Hence \(W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)=\underline W_{\tau,\Gamma}(\pi;P)\) and \(\Delta_{\mathrm{nc}}(\pi;P)=0\) throughout that proposed witness class, so no member of that class can witness \(\Delta_{\mathrm{nc}}(\pi;P)>0\).

\paragraph{\S13-refutation-attempt and generic-class certificate.}
\textbf{Primitive executed.}  I used the prescribed two-action, three-outcome, one-covariate-cell response-type LP.  Let
\[
\mathcal A=\{0,1\},\qquad X=x_0\ \text{a.s.},\qquad
Y\in\{0,1,2\},
\]
and write \(e_a=P(A=a\mid X=x_0)\), with \(0<e_a<1\).  For a fixed
\(1<\Gamma<\infty\), Assumption~\ref{ass:msm} is equivalent in each observed cell to a bounded
tilting representation
\[
q_{aj}=p_{aj}r_{aj},\qquad
p_{aj}=P(Y=j\mid A=a,X=x_0),\qquad
\ell_a\le r_{aj}\le u_a,\qquad
\sum_{j=0}^2 p_{aj}r_{aj}=1,
\]
where
\[
\ell_a=e_a+\frac{1-e_a}{\Gamma},\qquad
u_a=e_a+\Gamma(1-e_a).
\]
Strict overlap gives \(0<\ell_a\le1\le u_a<\infty\).  Thus the finite LP variables are the
actionwise tilted probabilities \(q_{aj}\).  For policy weights
\(\pi_a=\pi(a\mid x_0)\), the feasible policy-outcome mass is
\[
q^\pi_j=\sum_{a\in\{0,1\}}\pi_a q_{aj}.
\]

The vertex enumeration has a common monotone solution.  For each action \(a\), start from the lower
face \(q_{aj}=\ell_a p_{aj}\) and distribute the remaining mass
\[
1-\ell_a\sum_{j=0}^2p_{aj}=1-\ell_a
\]
greedily from the largest outcome downward, respecting the caps
\((u_a-\ell_a)p_{aj}\).  Denote the resulting vertex by \(q_a^\star\).  Explicitly,
\[
q^\star_{a2}=\min\{u_ap_{a2},\,1-\ell_a(p_{a0}+p_{a1})\},
\]
\[
q^\star_{a1}=\min\{u_ap_{a1},\,1-q^\star_{a2}-\ell_ap_{a0}\},
\qquad
q^\star_{a0}=1-q^\star_{a1}-q^\star_{a2}.
\]
This is the usual rearrangement vertex for the marginal-sensitivity density-ratio LP used in the
direct sharp analysis of \cite{DornGuo2021QuantileBalancing}: all mass that can be moved upward is
moved to the largest outcomes first.  The exchange argument is finite-dimensional.  If a feasible
vertex \(q_a\) assigns extra mass above the lower face to a smaller outcome while a larger outcome
has not reached its cap, shifting an \(\varepsilon\)-unit of mass from the smaller to the larger
outcome preserves the normalization and box constraints, weakly decreases every lower CDF
\(\sum_{j\le k}q_{aj}\), and weakly increases every increasing objective.  Repeating the exchange
terminates at \(q_a^\star\).  Hence \(q_a^\star\) simultaneously minimizes
\[
F_a(0)=q_{a0},\qquad F_a(1)=q_{a0}+q_{a1},
\]
and maximizes
\[
\sum_{j=0}^2 q_{aj}(j-\eta)_+
\]
for every \(\eta\in[0,2]\).

Mixing the two actionwise vertices with the fixed policy preserves this first-order stochastic
dominance.  The pointwise sharp lower policy CDF envelope is therefore the CDF of the single
policy distribution
\[
q^{\pi,\star}_j=\sum_{a\in\{0,1\}}\pi_a q^\star_{aj}.
\]
Consequently the band set
\(\mathcal F_{\Gamma}^{\mathrm{pt}}(P,\pi)\) contains a first-order-stochastically maximal element,
namely the CDF \(F^\star_\pi\) associated with \(q^{\pi,\star}\).  Since
\((y-\eta)_+\) is increasing in \(y\), the inner band optimization is
\[
\sup_{F\in\mathcal F_{\Gamma}^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)
=
\sum_{j=0}^2 q^{\pi,\star}_j(j-\eta)_+.
\]
The right-hand side is also the nested MSM generated-loss endpoint:
\[
\sum_{a\in\{0,1\}}\pi_a
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,x_0\}
=
\sum_{j=0}^2 q^{\pi,\star}_j(j-\eta)_+.
\]
Thus, for every \(\eta\in[0,2]\),
\[
\sup_{F\in\mathcal F_{\Gamma}^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)
=
\E_P\left[
\sum_{a\in\{0,1\}}\pi_a
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right].
\]
Taking the same operation \(\inf_{\eta\in[0,2]}\{\eta+\tau^{-1}(\cdot)\}\) on both sides gives
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
=
\underline W_{\tau,\Gamma}(\pi;P)
\]
for every observable law in the proposed two-action, three-outcome, one-cell strict-overlap class.

A concrete vertex check illustrates the certificate.  Take \(e_0=e_1=1/2\), \(\Gamma=2\),
\(\pi_0=\pi_1=1/2\), and
\[
P(Y=0\mid A=a)=P(Y=1\mid A=a)=P(Y=2\mid A=a)=1/3,\qquad a=0,1.
\]
Then \(\ell_a=3/4\) and \(u_a=3/2\).  The common upper-tail vertex is
\[
q_a^\star=(1/4,1/4,1/2),\qquad a=0,1,
\]
so \(F^\star_\pi(0)=1/4\) and \(F^\star_\pi(1)=1/2\).  For example, at
\(\tau=1/2\),
\[
\inf_{\eta\in[0,2]}
\left\{\eta+2\sum_{j=0}^2q^{\pi,\star}_j(j-\eta)_+\right\}
=2
\]
for both the band comparator and the nested endpoint.  The same calculation at the LP vertices is
not a special symmetry of the uniform law; it is the finite rearrangement argument above.  The
refutation primitive therefore finds no strict witness.  Instead it gives a generic certificate
that the conjecture's asserted strict two-action, three-outcome class cannot exist under the
shared definitions.  The nonnegativity inequality itself is not the failed part; the failed part
is the promised strict non-commutation witness.
