\section{Setup and Assumptions}

Consider a finite-\(N\) panel with units \(i=1,\ldots,N\) observed over calendar periods \(t=1,\ldots,T\). Each unit belongs to an adoption cohort \(G_i\) in the finite support \(\mathcal C\); the never-treated cohort is denoted by \(\infty\). Treatment is absorbing: \(D_{gt}\) indicates whether cohort \(g\) is treated in period \(t\), and \(D_{it}=D_{G_i t}\). Let \(I_{gN}=\{i:G_i=g\}\) and \(n_{gN}=|I_{gN}|\). Expectations under the triangular-array population law are written \(E_{\mathcal P_N}\).

The first restrictions keep the large-array design stable and impose the multiplicative untreated mean structure. Potential outcomes are \(Y_{it}(0)\) and \(Y_{it}(1)\). The untreated mean has a positive unit baseline \(b_{iN}\) and a calendar component \(\gamma_{t0}\); \(\bar b_{gN}\) is the within-cohort average baseline and \(\bar b_g\) its limit.

\begin{center}
\begin{tabular}{ll}
\hline
Notation & Economic object\\
\hline
\(D_{gt}\) & treatment status of cohort \(g\) in period \(t\)\\
\(B_{gt}=\bar b_g\exp(\gamma_{t0})\) & untreated cohort-time mean\\
\(\delta_{gt}\) & treated-cell log proportional effect\\
\(m_{gt}(\delta)=B_{gt}\exp(D_{gt}\delta_{gt})\) & observed cohort-time mean\\
\(\beta_N^\star(\delta)\) & finite-array population PPML treatment coordinate\\
\(\beta^\star(\delta)\) & limiting collapsed population PPML treatment coordinate\\
\(\widetilde W_{gt}(\delta)\) & fitted-mean-weighted residualized treatment\\
\(\Phi(\delta)\) & primitive index with the sign of \(\beta^\star(\delta)\)\\
\hline
\end{tabular}
\end{center}

\begin{assumptionv}{ass:cohort-share-limit}[Cohort share limits]
For every \(N\ge |\mathcal C|\) and every \(g\in\mathcal C\),
\[
n_{gN}>0
\quad\text{and}\quad
\frac{n_{gN}}{N}\to \pi_g\in(0,1).
\]
\end{assumptionv}

\cref{obj:ass:cohort-share-limit} is the positive limiting cohort shares condition: every cohort remains represented asymptotically and contributes positive mass to the collapsed comparison \citep{deChaisemartinDHaultfoeuille2020TWFE}. The limit share is denoted \(\pi_g\).

\begin{assumptionv}{ass:unit-untreated-exponential-mean}[Untreated exponential mean]
For every unit \(i=1,\ldots,N\) and period \(t=1,\ldots,T\),
\[
E_{\mathcal P_N}\!\left[Y_{it}(0)\right]
=
b_{iN}\exp(\gamma_{t0}),
\]
with the normalization \(\gamma_{10}=0\).
\end{assumptionv}

\cref{obj:ass:unit-untreated-exponential-mean} is a unit-fixed-effect multiplicative parallel-trends restriction in an exponential mean model \citep{Wooldridge2023NonlinearDiD}. The normalization fixes the location of the time effects and has no substantive content.

\begin{assumptionv}{ass:within-cohort-baseline-limit}[Within-cohort baseline limits]
For every \(g\in\mathcal C\), the deterministic triangular-array average
\[
\bar b_{gN}
=
n_{gN}^{-1}\sum_{i\in I_{gN}} b_{iN}
\]
satisfies
\[
\bar b_{gN}\to \bar b_g\in(0,\infty).
\]
\end{assumptionv}

\cref{obj:ass:within-cohort-baseline-limit} is specific to this analysis. It is the condition that makes the cohort-time collapse deterministic: after averaging within a cohort, the only limiting untreated heterogeneity that remains is the cohort baseline \(\bar b_g\).

\begin{assumptionv}{ass:proportional-effects}[Proportional treatment effects]
For every unit \(i=1,\ldots,N\) and period \(t=1,\ldots,T\) with \(D_{it}=1\),
\[
E_{\mathcal P_N}\!\left[Y_{it}(1)\right]
=
E_{\mathcal P_N}\!\left[Y_{it}(0)\right]\exp(\delta_{G_i t}).
\]
\end{assumptionv}

\cref{obj:ass:proportional-effects} is the cohort-time proportional treatment effects condition \citep{MoreauKastler2025PTT}. The log multiplier \(\delta_{G_i t}\) may vary across treated cohorts and calendar periods, so the pooled coefficient below is not imposed to equal a common structural effect.

These assumptions induce a collapsed cohort-by-time representation. Define the untreated cohort-time mean \(B_{gt}=\bar b_g\exp(\gamma_{t0})\), the collapsed cell mass \(q_{gt}=\pi_g/T\), and the observed collapsed mean \(m_{gt}(\delta)=B_{gt}\exp(D_{gt}\delta_{gt})\), where \(\delta_{gt}\) denotes the cohort-time log multiplier on treated cells. Let \(r_{gt}\) collect the collapsed fixed-effect regressors and the treatment indicator, and let \(X_{gt}\) be the same vector with the treatment coordinate removed.

\begin{assumptionv}{ass:collapsed-design-rank}[Collapsed design rank]
The collapsed second-moment matrix
\[
\sum_{g\in\mathcal C}\sum_{t=1}^T q_{gt} r_{gt} r_{gt}'
\]
is positive definite.
\end{assumptionv}

\cref{obj:ass:collapsed-design-rank} is the full-rank Poisson fixed-effect design condition \citep{White1982MisspecifiedML}. It rules out exact collinearity in the collapsed regressors, so the population projection has a well-defined treatment coordinate rather than an unidentified linear combination of fixed effects and treatment.

The population object is a Poisson pseudo-likelihood projection defined through the conditional-mean criterion. For a finite array, let \(v_{itN}\) be the unit-time regressor vector containing unit effects, time effects, and treatment; let \(\theta_N\) be the corresponding coefficient vector; and let \(m_{itN}(\delta)\) be the observed unit-time mean generated by the untreated mean and proportional effects.

\begin{definitionv}{def:unit-fe-population-projection}[Unit-FE Projection \(\beta_N^\star(\delta)\)]
Define \(\beta_N^\star(\delta)\) as the last coordinate of a maximizer over \(\theta_N\in\mathbb R^{N+T}\) of
\[
L_N(\theta_N;\delta)
=
(NT)^{-1}\sum_{i=1}^N\sum_{t=1}^T
\left\{
m_{itN}(\delta)\,v_{itN}'\theta_N-\exp(v_{itN}'\theta_N)
\right\}.
\]
\end{definitionv}

\cref{obj:def:unit-fe-population-projection} is the finite-array population analogue of the unit fixed-effect PPML regression. The criterion \(L_N(\theta_N;\delta)\) is evaluated at means rather than realized outcomes, and \(\beta_N^\star(\delta)\) is the treatment coordinate of that population projection.

\begin{definitionv}{def:sample-unit-fe-ppml}[Sample PPML Coefficient \(\hat\beta_N\)]
Let \(A_N\) be the set of admissible extended maximizers of
\[
\sum_{i=1}^N\sum_{t=1}^T
\left\{
Y_{it}\,v_{itN}'\theta_N-\exp(v_{itN}'\theta_N)
\right\}
\]
over unit-effect coordinates in \(\mathbb R\cup\{-\infty\}\), time-effect coordinates in \(\mathbb R\) satisfying the period-1 normalization, and \(\beta\in\mathbb R\), with the convention \(\exp(-\infty)=0\). Admissibility means that the period-1 time effect is normalized to zero and that a unit-effect coordinate may equal \(-\infty\) only for a unit whose whole observed outcome path satisfies \(Y_{it}=0\) for every \(t\); for such a unit the extended objective contribution is defined to be zero. If \(A_N\) contains an element whose squared Euclidean norm over the finite time-effect and \(\beta\) coordinates is no larger than that of every element of \(A_N\), then \(\hat\beta_N\) is the \(\beta\)-coordinate of such a selected element. If no such minimum-finite-coordinate-norm admissible extended maximizer exists, set \(\hat\beta_N=0\).
\end{definitionv}

The limiting projection works directly with the collapsed cohort-time cells. With \(\theta\) denoting the collapsed coefficient vector, write the limiting collapsed Poisson criterion as \(L(\theta;\delta)\). The finite collapsed analogue, used only to connect the array to this limit, is denoted \(L_{Nc}(\theta;\delta)\).

\begin{definitionv}{def:collapsed-population-projection}[Collapsed Projection \(\theta^\star(\delta)\)]
Define
\[
\theta^\star(\delta)\in
\arg\max_{\theta\in\mathbb R^{|\mathcal C|+T}} L(\theta;\delta),
\]
where
\[
L(\theta;\delta)
=
\sum_{g\in\mathcal C}\sum_{t=1}^T
q_{gt}
\left\{
m_{gt}(\delta)\,r_{gt}'\theta-\exp(r_{gt}'\theta)
\right\}.
\]
The coefficient \(\beta^\star(\delta)\) is the last coordinate of \(\theta^\star(\delta)\), and the fitted collapsed mean is
\[
\mu^\star_{gt}(\delta)=\exp\{r_{gt}'\theta^\star(\delta)\}.
\]
\end{definitionv}

\cref{obj:def:collapsed-population-projection} gives the main object studied in the paper. The maximizer \(\theta^\star(\delta)\), its treatment coordinate \(\beta^\star(\delta)\), and the fitted mean \(\mu^\star_{gt}(\delta)\) are pseudo-true quantities in the sense of misspecified likelihood theory \citep{White1982MisspecifiedML,GourierouxMonfortTrognon1984Theory,GourierouxMonfortTrognon1984Poisson}. The target is therefore a deterministic population projection defined by the Poisson mean criterion.

The analysis centers on this deterministic population projection. A sample fixed-effect PPML regression replaces the means by observed outcomes and may also confront separation \citep{SantosSilvaTenreyro2006,SantosSilvaTenreyro2011,CorreiaGuimaraesZylkin2020}; its sampling theory is a distinct extension. Accordingly, references below to a ``pooled coefficient'' mean the population coordinate \(\beta^\star(\delta)\), unless explicitly stated otherwise.

The sign analysis uses the residualized treatment after partialling out the collapsed fixed effects with weights given by the fitted PPML mean. Let \(\rho^\star(\delta)\) be the weighted least-squares coefficient from that auxiliary projection.

\begin{definitionv}{def:weighted-fwl-residual}[Weighted Residual \(\widetilde W_{gt}(\delta)\)]
Define
\[
\rho^\star(\delta)
\in
\arg\min_{\rho\in\mathbb R^{|\mathcal C|+T-1}}
\sum_{g\in\mathcal C}\sum_{t=1}^T
q_{gt}\,\mu^\star_{gt}(\delta)\{D_{gt}-X_{gt}'\rho\}^2.
\]
The weighted Frisch--Waugh--Lovell residualized treatment is
\[
\widetilde W_{gt}(\delta)=D_{gt}-X_{gt}'\rho^\star(\delta).
\]
\end{definitionv}

\cref{obj:def:weighted-fwl-residual} gives the comparison weights that enter the local sign formula in the next section. The residual \(\widetilde W_{gt}(\delta)\) is the fixed-effect projection residual of treatment under the curvature weights of the Poisson criterion and serves as a projection comparison weight.

The sign-reversal result is stated on designs with at least the four adoption statuses needed for the explicit construction. The next two assumptions isolate that scope and the positive-effect case of interest.

\begin{assumptionv}{ass:multicohort-frontier-scope}[Multicohort frontier scope]
The cohort set satisfies
\[
\{2,3,4,\infty\}\subseteq \mathcal C.
\]
\end{assumptionv}

\cref{obj:ass:multicohort-frontier-scope} is specific to this analysis. It ensures that the design contains early, middle, late, and never-treated cohorts, the minimal structure used by the four-cohort construction.

\begin{assumptionv}{ass:strict-positive-effects}[Strict Positive Effects]
For every cohort-period cell \((g,t)\) with \(D_{gt}=1\),
\[
\delta_{gt}>0.
\]
\end{assumptionv}

\cref{obj:ass:strict-positive-effects} is also specific to this analysis. It deliberately restricts attention to the strongest sign benchmark: every treated cell has a positive proportional effect, so any negative pooled coefficient is a property of the projection rather than a mixture of positive and negative underlying effects.

The global parameter region collects the maintained restrictions under which the limiting PPML treatment coordinate is negative despite those positive cell-level effects.

\begin{definitionv}{def:global-sign-reversal-region}[Sign-Reversal Region \(\mathcal R_T\)]
Define \(\mathcal R_T\) as the set of all triples
\[
\left((\pi_g)_{g\in\mathcal C},(B_{gt})_{g\in\mathcal C,\ 1\le t\le T},(\delta_{gt})_{(g,t):D_{gt}=1}\right)
\]
with \(T\ge 4\), indexed by a cohort support \(\mathcal C\) that contains \(\{2,3,4,\infty\}\) and contains no first-period finite cohort, such that
\[
0<\pi_g<1\quad(g\in\mathcal C),\qquad \sum_{g\in\mathcal C}\pi_g=1,
\]
there exist \(\bar b_g>0\) for \(g\in\mathcal C\) with \(B_{gt}=\bar b_g\exp(\gamma_{t0})\) for every supported cell \((g,t)\), \(\delta_{gt}>0\) for every treated supported cell \((g,t)\) with \(D_{gt}=1\), the collapsed design has full weighted rank in the sense that
\[
\forall a\ne 0,\qquad
0<\sum_{g\in\mathcal C}\sum_{t=1}^T \frac{\pi_g}{T}\,(r_{gt}'a)^2,
\]
and
\[
\beta^\star(\delta)<0.
\]
\end{definitionv}

\cref{obj:def:global-sign-reversal-region} names the population configurations in which the pooled limiting coefficient has the opposite sign from every granular proportional treatment effect. The notation \(\mathcal R_T\) is only a shorthand for this primitive set of shares, untreated means, and treated-cell multipliers.

The paper uses one explicit triangular array to show that this region is nonempty. Its role is evidentiary rather than calibrational: all baselines and untreated time effects are set to one, and the only large treated multiplier is placed in the period-4 cell of the cohort first treated in period 2.

\begin{definitionv}{def:four-cohort-witness}[Four-cohort witness $W_4$]
Let $W_4$ be the cofinal triangular subsequence indexed by $N=4m$, $m=1,2,\ldots$, with $T=4$ and
\[
\mathcal C=\{2,3,4,\infty\}.
\]
For each such $N$,
\[
n_{2N}=n_{3N}=n_{4N}=n_{\infty N}=m,
\]
$b_{iN}=1$ for every $i$, and $\gamma_{t0}=0$ for every $t$. The treatment effects satisfy
\[
\delta_{gt}=\log(101/100)
\]
for every treated cell $(g,t)\ne(2,4)$, while
\[
\delta_{2,4}=\log(4).
\]
\end{definitionv}

\cref{obj:def:four-cohort-witness} defines the witness \(W_4\). Equal cohort shares and flat untreated means remove scale and composition as explanations for the sign reversal; the later result depends only on the staggered treatment pattern and the heterogeneous positive proportional effects encoded here.

Finally, the primitive sign characterization uses an algebraic index based on observed mean components. Let \(H\) denote the set of treated cohort-time cells when that notation is needed later.

\begin{definitionv}{def:frontier-elimination-handle}[Frontier-elimination polynomial $\Phi(\delta)$]
Define
\[
\Phi(\delta)
=
M A
-
\sum_{g,t} D_{gt} R_g C_t,
\]
where
\[
h_{gt}
=
\pi_g B_{gt}\exp(D_{gt}\delta_{gt}),\qquad
R_g=\sum_t h_{gt},\qquad
C_t=\sum_g h_{gt},
\]
and
\[
M=\sum_g R_g,\qquad
A=\sum_{g,t}D_{gt}h_{gt}.
\]
The relation between $\Phi(\delta)$ and $\beta^\star(\delta)$ is stated separately.
\end{definitionv}

\cref{obj:def:frontier-elimination-handle} introduces the scalar \(\Phi(\delta)\) used by the primitive sign result. The component \(h_{gt}\) is the cohort-share-weighted observed collapsed mean, equivalently \(Tq_{gt}m_{gt}(\delta)\), while \(R_g\), \(C_t\), \(M\), and \(A\) are its cohort sums, period sums, grand sum, and treated-cell sum. The main theorem in the next section supplies the sign relation for this scalar.
