\section{Appendix: Proofs, Auxiliary Lemmas, and Verification Note}

This appendix records the two auxiliary population results used to connect the unit-level fixed-effect regression to the collapsed cohort-time analysis. The ordering mirrors the logic of the main text. The collapse result first justifies replacing the finite-\(N\) unit fixed-effect projection by its cohort-time counterpart. The projection result then gives the first-order conditions for the limiting collapsed pseudo-true parameter. The main theorem proofs use these statements before establishing the primitive sign characterization in \cref{obj:thm:primitive-global-frontier}; the four-cohort sign-reversal result in \cref{obj:prop:four-cohort-sign-reversal} is then read as a consequence of that characterization together with the explicit witness construction.

The first lemma formalizes the reduction from a unit fixed-effect PPML population criterion to a collapsed criterion. Its role is to show that, under the same cohort-share, untreated-mean, baseline-limit, proportional-effect, and rank restrictions used in \cref{obj:ass:cohort-share-limit}, the treatment coordinate is invariant to within-cohort rearrangements of unit baselines that leave cohort averages unchanged. Thus the finite-array object in \cref{obj:def:unit-fe-population-projection} and the limiting object in \cref{obj:def:collapsed-population-projection} are linked through the cohort-time means that drive the sign analysis.

\begin{lemmav}{lem:unit-fe-collapse}[Unit FE Collapse]
Let $T$ be a number of periods and let $\mathcal C$ be a finite cohort set. Suppose:
\begin{itemize}
\item \textbf{(Horizon.)} $T\ge 4$.
\item \textbf{(Cohort support.)} The never-treated cohort belongs to $\mathcal C$, and every finite cohort in $\mathcal C$ is dated after the first period.
\item \textbf{(Array support.)} For every $N$ and every unit $i$, the cohort label $G_i$ belongs to $\mathcal C$.
\item \textbf{(Positive primitives.)} The unit baselines $b_{iN}$ and the limiting within-cohort baselines $\bar b_g$ are strictly positive, and each limiting cohort share satisfies $\pi_g\in(0,1)$.
\item \textbf{(Share limits.)} \cref{obj:ass:cohort-share-limit} holds for $G_i$ and $\pi_g$.
\item \textbf{(Untreated means.)} \cref{obj:ass:unit-untreated-exponential-mean} holds for $Y_{it}(d)$, $\mathcal P_N$, $b_{iN}$, and $\gamma_{t0}$.
\item \textbf{(Baseline limits.)} \cref{obj:ass:within-cohort-baseline-limit} holds for $G_i$, $b_{iN}$, and $\bar b_g$.
\item \textbf{(Proportional effects.)} \cref{obj:ass:proportional-effects} holds for $Y_{it}(d)$, $\mathcal P_N$, $G_i$, and $\delta_{gt}$.
\item \textbf{(Collapsed rank.)} \cref{obj:ass:collapsed-design-rank} holds for $\mathcal C$ and $\pi_g$.
\end{itemize}
Then, for every $N$ with $|\mathcal C|\le N$, the finite-array unit-FE population criterion $L_N(\theta_N;\delta)$ of \cref{obj:def:unit-fe-population-projection} has a unique global maximizer, the collapsed finite-array criterion $L_{Nc}(\theta;\delta)$ has a unique global maximizer, and
\[
\beta_N^\star(\delta)
=
\text{the treatment coordinate of the unique maximizer of }L_{Nc}(\theta;\delta).
\]
Moreover,
\[
\beta_N^\star(\delta)\longrightarrow \beta^\star(\delta)
\qquad\text{as }N\to\infty .
\]
Finally, for every $N$ with $|\mathcal C|\le N$ and every alternative positive baseline array $b'_{iN}$, if
\[
\bar b'_{gN}=\bar b_{gN}
\qquad\text{for every }g\in\mathcal C,
\]
then replacing $b_{iN}$ by $b'_{iN}$ leaves the finite-array unit-FE coefficient unchanged:
\[
\beta_N^\star(\delta;b')=\beta_N^\star(\delta;b).
\]
\end{lemmav}

The uniqueness clauses are population pseudo-likelihood statements in the usual misspecified-likelihood sense \citep{White1982MisspecifiedML,GourierouxMonfortTrognon1984Theory,GourierouxMonfortTrognon1984Poisson}. The final invariance clause is specific to the cohort-time collapse used here: once unit effects absorb individual baseline levels, only the within-cohort baseline average enters the collapsed mean relevant for the treatment coordinate. This is why the later sign results can be stated in terms of cohort shares, untreated cohort-time means, and proportional-effect multipliers rather than the full list of unit baselines.

The second auxiliary lemma records the first-order conditions for the collapsed pseudo-true PPML projection. These score equations are the fixed-effect and treatment equations behind the derivative formula in \cref{obj:thm:sharp-ppml-forbidden-sign} and the algebraic sign calculation in \cref{obj:thm:primitive-global-frontier}.

\begin{lemmav}{lem:pseudo-true-ppml-projection}[Unique PPML Projection]
Fix a number of periods \(T\), a finite cohort set \(\mathcal C\), cohort shares \(\pi_g\in(0,1)\), positive limiting baseline means \(\bar b_g>0\), time components \(\gamma_{t0}\), and proportional-effect log multipliers \(\delta_{gt}\). Suppose the collapsed design rank condition in \cref{obj:ass:collapsed-design-rank} holds for \((T,\mathcal C,\pi)\). Let \(\theta^\star(\delta)\), \(L(\theta;\delta)\), \(m_{gt}(\delta)\), and \(\mu^\star_{gt}(\delta)\) be as in \cref{obj:def:collapsed-population-projection}. Then \(\theta^\star(\delta)\) is the unique global maximizer of \(L(\theta;\delta)\). Moreover, for every collapsed nuisance regressor index \(j\),
\[
\sum_{g\in\mathcal C}\sum_{t=1}^T
q_{gt} X_{gt,j}\{m_{gt}(\delta)-\mu^\star_{gt}(\delta)\}=0,
\]
and the treatment score also vanishes:
\[
\sum_{g\in\mathcal C}\sum_{t=1}^T
q_{gt} D_{gt}\{m_{gt}(\delta)-\mu^\star_{gt}(\delta)\}=0.
\]
\end{lemmav}

\cref{obj:lem:pseudo-true-ppml-projection} is the collapsed analogue of the pseudo-true score condition for a Poisson quasi-likelihood projection. The rank condition rules out flat directions in the fixed-effect and treatment regressors, while positivity of the cell means keeps the exponential criterion strictly concave on the relevant design span. The argument uses the mean criterion characteristic of standard pseudo-maximum-likelihood analysis \citep{White1982MisspecifiedML,GourierouxMonfortTrognon1984Poisson}.

Combining \cref{obj:lem:unit-fe-collapse} and \cref{obj:lem:pseudo-true-ppml-projection} fixes the population target before the sign results are applied. The derivative result in \cref{obj:thm:sharp-ppml-forbidden-sign} uses the score equations to express the response of the treatment coordinate through the weighted residualized treatment. The homogeneous benchmark in \cref{obj:prop:homogeneous-effect-reduction} then identifies the correctly specified common-effect case. The primitive sign theorem, \cref{obj:thm:primitive-global-frontier}, comes next because it supplies the global sign criterion used to place the explicit four-cohort construction in \(\mathcal R_4\). With that ordering, \cref{obj:prop:four-cohort-sign-reversal} becomes the concrete specialization of the sign frontier to the witness in \cref{obj:def:four-cohort-witness}.

\paragraph{Reproducibility note.}
The formal supplement verifies the displayed population claims in Lean 4 and records the correspondence between mathematical statements and declarations. Its deterministic scope covers the finite-dimensional projection, collapse, derivative-sign, primitive-sign, and four-cohort calculations. Sampling consistency, inference, and empirical identification of the primitive means and proportional effects form the natural empirical extension.
