The active-pair products and their cardinalities are computable without expansion. Under the hypothesis their total cardinality is \(r\), so all active words can then be listed in polynomial time. Let \(R_\mu\in\{0,1\}^{r\times r}\) be the matrix whose rows are these restricted active normals. Since \(\mu\) is a vertex and there are exactly \(r\) active rows, the active-rank criterion implies that \(R_\mu\) is nonsingular. Therefore
\[T_\mu=\{h:R_\mu h\ge0\}.\tag{1}\]
The invertible linear map \(h\mapsto R_\mu h\) carries this cone bijectively onto \(\mathbb R_+^r\). Its extreme rays are consequently
\[h_i=R_\mu^{-1}e_i,\qquad i=1,\ldots,r.\tag{2}\]
Here \(e_i\) is the \(i\)-th standard basis vector. Since the active-normal sum is \(s_\mu=R_\mu^{\mathsf T}\mathbf1\), every ray in (2) is already normalized:
\[s_\mu^{\mathsf T}h_i=\mathbf1^{\mathsf T}R_\mu R_\mu^{-1}e_i=1.\tag{3}\]
Exact inversion has polynomial bit complexity because \(R_\mu\) is an \(r\)-dimensional zero--one matrix. Apply the compressed ray verifier and exact line search to each of the \(r\) vectors in (2). Discard recession rays and finite endpoints \(\nu\) for which \(P(\nu)\ne\mu\), and output all remaining endpoints. Distinct extreme rays at a vertex determine distinct incident edges and hence distinct neighboring endpoints. Conversely every adjacent child determines one of the extreme rays in (2), so the list is sound and complete. There are only \(r=O(nl)\) candidates and every test is polynomial; therefore the entire list, including exhaustion, is produced in polynomial total time.