Write \(u_{y,z}=\lambda_{(y,0,z)}\) and \(v_{y,z}=\lambda_{(y,1,z)}\), and order every arm block as \((u_{0,z},u_{1,z},v_{0,z},v_{1,z})\). For \(n=2\), \(a=1\), and \(s=(2,3)\), direct substitution in the definition of \(w(a,s)\), followed by treatment swapping and negation, gives
\[\rho=\Gamma(\bar w(1,(2,3)))=\bigl((1,0,1,1),(0,0,-1,0),(0,0,0,0)\bigr).\]
Interchanging arms two and three in the indexing word gives the distinct gauge-fixed vector
\[\xi=\Gamma(\bar w(1,(3,2)))=\bigl((1,0,1,1),(0,0,0,0),(0,0,-1,0)\bigr).\]
Both displayed vectors satisfy \(u_{0,2}=u_{0,3}=0\), so the displayed applications of \(\Gamma\) do not change them.

Let \(\eta=(a,b)\in\{0,1\}^2\). By the definitions of \(A_{2,3}\) and \(c_{2,3}\), the slack of the type \((\delta,\eta)\) at a vector \(\alpha\in\{\rho,\xi\}\) is
\[s^{\alpha}_{\delta,ab}=\sum_{z=1}^3\alpha_{(\eta(\delta(z)),\delta(z),z)}-(b-a).\]
Substitution of the two displayed coefficient vectors gives all thirty-two slacks in each case: 
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&1&0&1&0\\ 001&1&0&1&0\\ 010&0&0&0&0\\ 011&0&0&0&0\\ 100&1&0&2&1\\ 101&1&0&2&1\\ 110&0&0&1&1\\ 111&0&0&1&1\end{array}\qquad(\alpha=\rho),\]
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&1&0&1&0\\ 001&0&0&0&0\\ 010&1&0&1&0\\ 011&0&0&0&0\\ 100&1&0&2&1\\ 101&0&0&1&1\\ 110&1&0&2&1\\ 111&0&0&1&1\end{array}\qquad(\alpha=\xi).\]
Every entry is nonnegative. Hence \(A_{2,3}^{\mathsf T}\rho\ge c_{2,3}\) and \(A_{2,3}^{\mathsf T}\xi\ge c_{2,3}\); together with the gauge equalities, this proves \(\rho,\xi\in\mathcal H^0_{2,3}\). The zero entries in the tables are precisely their complete signatures.

For the canonical-basis calculation, scan those zero entries in the handle's prescribed lexicographic type order, retaining an equation exactly when its row normal increases the rank in the gauge coordinates. Exact elimination gives the successive ranks
\[(1,2,3,4,5,6,7,7,8,8,8,8,9,9,10,10,10,10)\]
for \(\rho\), and
\[(1,2,3,4,5,5,6,7,8,8,8,8,9,10,10,10,10,10)\]
for \(\xi\). Writing \(\delta/ab\) for \((\delta,(a,b))\), the retained lists are therefore
\[\begin{aligned}B_{\rho}=(&000/01,000/11,001/01,001/11,010/00,010/01,\\&010/10,011/00,100/01,110/00),\end{aligned}\]
\[\begin{aligned}B_{\xi}=(&000/01,000/11,001/00,001/01,001/10,010/01,\\&010/11,011/00,100/01,101/00).\end{aligned}\]
Here the gauge section has dimension \(r=2\cdot2\cdot3-3+1=10\). In the reduced coordinate order
\[x=(u_{0,1},u_{1,1},v_{0,1},v_{1,1},u_{1,2},v_{0,2},v_{1,2},u_{1,3},v_{0,3},v_{1,3}),\]
the row-normal matrices of these two retained systems are
\[R_{\rho}=\begin{pmatrix}1&0&0&0&0&0&0&0&0&0\\0&1&0&0&1&0&0&1&0&0\\1&0&0&0&0&0&0&0&0&1\\0&1&0&0&1&0&0&0&0&1\\1&0&0&0&0&1&0&0&0&0\\1&0&0&0&0&0&1&0&0&0\\0&1&0&0&0&1&0&1&0&0\\1&0&0&0&0&1&0&0&1&0\\0&0&0&1&0&0&0&0&0&0\\0&0&1&0&0&1&0&0&0&0\end{pmatrix},\qquad\det(R_{\rho})=-1,\]
\[R_{\xi}=\begin{pmatrix}1&0&0&0&0&0&0&0&0&0\\0&1&0&0&1&0&0&1&0&0\\1&0&0&0&0&0&0&0&1&0\\1&0&0&0&0&0&0&0&0&1\\0&1&0&0&1&0&0&0&1&0\\1&0&0&0&0&0&1&0&0&0\\0&1&0&0&0&0&1&1&0&0\\1&0&0&0&0&1&0&0&1&0\\0&0&0&1&0&0&0&0&0&0\\0&0&1&0&0&0&0&0&1&0\end{pmatrix},\qquad\det(R_{\xi})=1.\]
Thus each vector has ten linearly independent tight inequalities in the ten-dimensional gauge section. If either vector were the midpoint of two distinct feasible section points, every inequality tight at the midpoint would be tight at both endpoints, so their difference would lie in the null space of the corresponding matrix \(R_{\rho}\) or \(R_{\xi}\). The displayed nonzero determinants force that difference to vanish. Hence both vectors are vertices of \(\mathcal H^0_{2,3}\), in particular \(\xi\in\mathcal V_{2,3}\).

It remains to verify that the retained lists are the canonical bases, rather than merely bases. For any linearly ordered finite list of row vectors, the greedy scan that retains the first row increasing the span returns the lexicographically least full-rank sublist: at the first position where another full-rank sublist differs, omitting the greedy row cannot permit an earlier replacement, while the greedy row is independent of all preceding rows and therefore must be replaced only by a later row. Applying this elementary argument successively to the two ordered signatures proves that \(B_{\rho}\) and \(B_{\xi}\) are exactly the canonical bases specified by the reverse-search handle.

The first two entries of these bases agree. Their third entries are respectively \(001/01\) and \(001/00\), and the prescribed lexicographic type order has \(001/00\prec001/01\). Consequently
\[B_{\xi}\prec B_{\rho}.\]
Every parent edge under the proposed rule strictly decreases the canonical basis. Inductively, every vertex reached after at least one parent step from \(\xi\) has canonical basis strictly smaller than \(B_{\xi}\), and hence cannot be \(\rho\), whose basis is strictly larger. Therefore no parent chain from \(\xi\) reaches the proposed root \(\rho\). Root reachability fails already at \((n,l)=(2,3)\), so this decreasing-canonical-basis construction does not establish the claimed rooted reverse search or a polynomial-delay enumerator. The calculation concerns only this parent rule and supplies no obstruction to a different global orientation or enumeration algorithm.