A vertex in the \(r\) free gauge coordinates is the unique solution of \(r\) independent active type equations. Their coefficient matrix is zero--one and their right-hand sides have absolute value at most \(n-1\). By the Leibniz determinant formula, every denominator in Cramer's rule is at most \(r!\) in absolute value, and every numerator is at most \((n-1)r!\). Thus each reduced rational coordinate has
\[O(r\log r+\log n)\tag{1}\]
bits, and a canonical self-delimiting encoding of the complete vertex has length bounded by a polynomial \(L(n,l)\). The compressed verification lemma decides in polynomial time whether a canonically encoded rational vector is a vertex and, for a nonroot vertex, computes its parent. The inverse-child relation is therefore polynomial-time decidable, and (1) proves polynomial balance.

Fix \(\mu\). Pad every canonical child encoding, after a delimiter, to length exactly \(L(n,l)\). For a binary prefix \(\sigma\), consider the language asking whether there exists a completion \(\omega\) such that \(\sigma\omega\) is the padded canonical encoding of a vertex \(\nu\) satisfying \(P(\nu)=\mu\). This language is in \(\mathsf{NP}\): the completion has polynomial length and the relation is polynomial-time decidable. With an oracle for this prefix language, traverse the binary prefix tree depth first, pruning a prefix whenever the oracle says that it has no completion. At depth \(L(n,l)\), output the uniquely decoded child. Canonical padding prevents duplicates. Between two output leaves, the traversal ascends and descends at most \(2L(n,l)\) edges whose surviving subtrees are certified by oracle calls; empty subtrees are pruned by one call. The same bound gives polynomial exhaustion after the last leaf, including the case of no child. This is a polynomial-delay local child iterator relative to an \(\mathsf{NP}\) oracle.

The global-parent theorem makes these child relations a finite rooted tree spanning \(\mathcal V_{n,l}\). Applying the parity Euler delay-transfer lemma to the oracle-assisted local iterators gives exact-once global enumeration, polynomial delay, and polynomial final termination relative to the same oracle. No step removes the existential prefix oracle, so the argument does not prove the deterministic claim posed by the open-ended question.