For a type \(\tau=(\delta,\eta)\), define its slack at \(\lambda^\dagger\) by
\[s_{\delta,\eta}=\sum_{z=1}^{3}\lambda^\dagger_{(\eta(\delta(z)),\delta(z),z)}-\bigl(\eta(1)-\eta(0)\bigr).\]
Using the coordinate order \(((0,0),(1,0),(0,1),(1,1))\) within each arm, direct substitution gives
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&2&1&1&0\\ 001&2&2&0&0\\ 010&0&1&1&2\\ 011&0&2&0&2\\ 100&2&0&2&0\\ 101&2&1&1&0\\ 110&0&0&2&2\\ 111&0&1&1&2\end{array}.\]
Every entry is nonnegative, and the fixed coordinates in arms two and three are zero. Thus \(\lambda^\dagger\in\mathcal H^0_{2,3}\). Reading off all zero entries gives exactly
\[\begin{split}\operatorname{Sig}(\lambda^\dagger)=\{&((000),(11)),((001),(10)),((001),(11)),((010),(00)),\\ &((011),(00)),((011),(10)),((100),(01)),((100),(11)),\\ &((101),(11)),((110),(00)),((110),(01)),((111),(00))\}.\end{split}\]
This proves both feasibility and completeness of the stated signature.

Stack the ten coefficient rows indexed, in their displayed order, by \(B^\dagger\), and append the two gauge rows. In the ambient coordinate order obtained by concatenating the three arm blocks, the resulting matrix is
\[M^\dagger=\left(\begin{array}{rrrrrrrrrrrr}0&1&0&0&0&1&0&0&0&1&0&0\\ 0&1&0&0&0&1&0&0&0&0&1&0\\ 0&1&0&0&0&1&0&0&0&0&0&1\\ 1&0&0&0&0&0&1&0&1&0&0&0\\ 1&0&0&0&0&0&1&0&0&0&1&0\\ 0&1&0&0&0&0&1&0&0&0&1&0\\ 0&0&0&1&1&0&0&0&1&0&0&0\\ 0&0&0&1&0&1&0&0&0&1&0&0\\ 0&0&1&0&0&0&1&0&1&0&0&0\\ 0&0&0&1&0&0&0&1&1&0&0&0\\ 0&0&0&0&1&0&0&0&0&0&0&0\\ 0&0&0&0&0&0&0&0&1&0&0&0\end{array}\right).\]
Integer elimination gives \(\det(M^\dagger)=1\). Hence the first ten rows have rank \(10\), while all twelve rows have rank \(12\). Since the gauge section has dimension \(10\), these ten tight equations isolate \(\lambda^\dagger\) in the section. If a feasible point isolated by its active equalities were a nontrivial midpoint of two feasible points, every active inequality would be an equality at both endpoints and the endpoints would lie in that same isolated affine solution set. They would therefore coincide. Thus \(\lambda^\dagger\) is extreme and belongs to \(\mathcal V_{2,3}\).

We next analyze the literal comparator family. By the gauge-transversal lemma, an element \(v\in K_{2,3}\) is constant within each arm. Therefore
\[I_z(\lambda+v)=\lambda_{(1,1,z)}+a_z-\lambda_{(0,1,z)}-a_z=I_z(\lambda),\]
which proves gauge invariance of \(I\). At \(n=2\), an admissible index \((a,s)\) has \(s=(s_0,s_1)\), where \(a,s_0,s_1\) are the three distinct arms. From the definition of the treatment-swapped negative,
\[I_z(\bar w(a,s))=-w(a,s)_{1,0,z}+w(a,s)_{0,0,z}=\mathbf1\{z=s_0\}.\]
The correction made by \(\Gamma\) is constant within each arm, so \(I(\Gamma(\bar w(a,s)))=e_{s_0}\).

It remains to establish that all six such comparators are distinct vertices. For \(a=1\) and \(s=(2,3)\), the gauge-fixed representative has blocks
\[\mu^0=\bigl((1,0,1,1),(0,0,-1,0),(0,0,0,0)\bigr).\]
Its complete slack table is
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&1&0&1&0\\ 001&1&0&1&0\\ 010&0&0&0&0\\ 011&0&0&0&0\\ 100&1&0&2&1\\ 101&1&0&2&1\\ 110&0&0&1&1\\ 111&0&0&1&1\end{array}.\]
Thus \(\mu^0\) is feasible. In the reduced coordinate order
\[x=(u_{0,1},u_{1,1},v_{0,1},v_{1,1},u_{1,2},v_{0,2},v_{1,2},u_{1,3},v_{0,3},v_{1,3}),\]
the tight types \(000/01,000/11,001/01,001/11,010/00,010/01,010/10,011/00,100/01,110/00\) have row-normal matrix
\[R_0=\begin{pmatrix}1&0&0&0&0&0&0&0&0&0\\ 0&1&0&0&1&0&0&1&0&0\\ 1&0&0&0&0&0&0&0&0&1\\ 0&1&0&0&1&0&0&0&0&1\\ 1&0&0&0&0&1&0&0&0&0\\ 1&0&0&0&0&0&1&0&0&0\\ 0&1&0&0&0&1&0&1&0&0\\ 1&0&0&0&0&1&0&0&1&0\\ 0&0&0&1&0&0&0&0&0&0\\ 0&0&1&0&0&1&0&0&0&0\end{pmatrix},\qquad\det(R_0)=-1.\]
The preceding active-rank argument shows that \(\mu^0\) is a vertex. Every admissible ordered triple \((a,s_0,s_1)\) is an arm permutation of \((1,2,3)\). An arm permutation merely relabels treatment words in the incidence inequalities and leaves the ATE right-hand side unchanged, so it is a linear automorphism of \(\mathcal H_{2,3}\) preserving \(K_{2,3}\). It therefore induces an automorphism of the quotient polyhedron, and the gauge-transversal lemma carries every permuted comparator to a vertex of \(\mathcal H^0_{2,3}\).

Define also the gauge-invariant contrast
\[J_z(\lambda)=\lambda_{(1,0,z)}-\lambda_{(0,0,z)}.\]
Direct substitution in the literal comparator formula gives
\[J(\Gamma(\bar w(a,s)))=-e_a,\qquad I(\Gamma(\bar w(a,s)))=e_{s_0}.\]
Thus a comparator vector recovers the ordered pair \((a,s_0)\), and \(s_1\) is the remaining arm. The six admissible indices consequently give six distinct comparator vertices.

Finally, direct evaluation gives
\[I(\lambda^\dagger)=(1-2,\,0-(-2),\,1-0)=(-1,2,1).\]
Let \(\sigma=(1\ 2\ 3)\), let \(P_\sigma\) permute the arm blocks, and for \(j=0,1,2\) define \(\lambda^{\dagger,j}=\Gamma(P_{\sigma^j}\lambda^\dagger)\). The quotient-automorphism argument just used shows that all three vectors are vertices. Gauge invariance of \(I\) and arm relabeling give the three cyclic coordinate permutations of \((-1,2,1)\) as their invariant vectors. Those vectors are pairwise distinct, so the three vertices are distinct; none is a comparator because no cyclic permutation of \((-1,2,1)\) is a standard basis vector. Hence the six comparator vertices and these three omitted vertices are pairwise disjoint. Therefore
\[|\mathcal V_{2,3}\setminus\mathcal F^{\mathrm{BBAK}}_{2,3}|\ge3,\qquad |\mathcal V_{2,3}|\ge6+3=9,\]
and strict inclusion follows.