Compute the active outcome-pair set and the armwise minimizer sets \(R_{ab,z}(\mu)\) from (5) of the facet-reduction lemma. For a fixed active pair, a coordinate selected at arm \(z\) occurs in exactly
\[\prod_{j\ne z}|R_{ab,j}(\mu)|\tag{1}\]
active words. Summing these multiplicities over the active pairs computes \(s_\mu\) in \(O(n^2l)\) arithmetic operations. The integers in (1) have at most \(l+1\) bits, so this computation has polynomial bit complexity despite an exponentially large signature.

Given rational \(h\), define for every active pair
\[\phi_{ab}(h)=\sum_{z=1}^l\min_{d\in R_{ab,z}(\mu)}h_{(\eta(d),d,z)}.\tag{2}\]
The same separability identity as in the global-parent theorem gives
\[h\in T_\mu\quad\Longleftrightarrow\quad \phi_{ab}(h)\ge0\text{ for every active }(a,b).\tag{3}\]
The algorithm first checks (3) and \(s_\mu^{\mathsf T}h=1\). For a pair with \(\phi_{ab}(h)=0\), put
\[Q_{ab,z}(h)=\operatorname*{argmin}_{d\in R_{ab,z}(\mu)}h_{(\eta(d),d,z)}.\tag{4}\]
Subtracting the separable minimum in (2) expresses the value of an active type row at \(h\) as a sum of nonnegative armwise gaps. Hence that row vanishes at \(h\) if and only if its treatment word belongs to \(\prod_zQ_{ab,z}(h)\). Pairs with \(\phi_{ab}(h)>0\) contribute no zero row.

Choose one base word from every nonempty product in (4). For every arm at which \(|Q_{ab,z}(h)|=2\), also form the word obtained by flipping only that arm. If \(\alpha^0\) is the base row and \(\alpha^z\) is its one-arm flip, every product row has the form
\[\alpha^0+\sum_{z\in J}(\alpha^z-\alpha^0)\tag{5}\]
for a subset \(J\) of the tied arms. Conversely each difference in (5) belongs to the span of the base and flip rows. Thus one base row and at most \(l\) flip rows span the entire exponentially large product. Over all pairs, at most \(n^2(l+1)\) rows suffice to compute the rank of every zero active normal.

All active normals annihilate \(h\), whereas \(s_\mu^{\mathsf T}h=1\), so \(s_\mu\) is not in their span. The affine point \(h\) is a vertex of \(\mathcal K_\mu\) if and only if its zero active normals have rank \(r-1\). If the rank is \(r-1\), those equations together with \(s_\mu^{\mathsf T}x=1\) have the unique solution \(h\). If the rank is smaller, choose a nonzero vector annihilated by the zero rows and by \(s_\mu\); finiteness of the type system and strict positivity of all other slacks allow sufficiently small perturbations in both signs, so \(h\) is not a vertex. Exact elimination on the compressed rows therefore decides extremality in polynomial bit time.

For a certified extreme ray, use the exact line search from the global-parent theorem. For each outcome pair define
\[f_{ab}(t)=\sum_{z=1}^l\min\{u^\mu_{a,z}+t h_{(a,0,z)},v^\mu_{b,z}+t h_{(b,1,z)}\}-(b-a).\tag{6}\]
Every summand has at most one rational breakpoint, so sorting at most \(l\) breakpoints and inspecting the affine pieces decides whether all the inequalities remain nonnegative for arbitrarily large \(t\). If not, it computes the exact positive endpoint \(t_\mu\). The extreme tangent ray then determines a one-dimensional incident face; a finite endpoint \(\nu=\mu+t_\mu h\) is its other vertex. Evaluation of the explicit parent map at \(\nu\), followed by exact comparison with \(\mu\), decides the child condition in polynomial bit time.

Finally, a supplied rational \(x\) belongs to \(\mathcal H^0_{n,l}\) exactly when it satisfies the gauge equations and the \(n^2\) separable-minimum inequalities. At every equality pair, the span of all active type rows is computed by the same base-plus-one-flip construction (5). Since the section is full-dimensional, \(x\) is a vertex exactly when the union of those compressed generators has rank \(r\). This gives polynomial-time membership in \(\mathcal V_{n,l}\). Combining that test with polynomial-time evaluation of \(P\) proves the final assertion.