Write \(u_{y,z}=\lambda_{(y,0,z)}\) and \(v_{y,z}=\lambda_{(y,1,z)}\), ordering each arm as \((u_{0,z},u_{1,z},v_{0,z},v_{1,z})\). For \(n=2\), \(a=1\), and \(s=(2,3)\), the literal comparator definition gives
\[\rho=\Gamma(\bar w(1,(2,3)))=\bigl((1,0,1,1),(0,0,-1,0),(0,0,0,0)\bigr).\]
Interchanging arms two and three gives the second gauge-fixed vector
\[\xi=\Gamma(\bar w(1,(3,2)))=\bigl((1,0,1,1),(0,0,0,0),(0,0,-1,0)\bigr).\]
For \(\alpha\in\{\rho,\xi\}\), define
\[s^\alpha_{\delta,ab}=\sum_{z=1}^3\alpha_{(\eta(\delta(z)),\delta(z),z)}-(b-a),\qquad \eta=(a,b).\]
Direct substitution gives all thirty-two slacks for each vector:
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&1&0&1&0\\ 001&1&0&1&0\\ 010&0&0&0&0\\ 011&0&0&0&0\\ 100&1&0&2&1\\ 101&1&0&2&1\\ 110&0&0&1&1\\ 111&0&0&1&1\end{array}\qquad(\alpha=\rho),\]
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&1&0&1&0\\ 001&0&0&0&0\\ 010&1&0&1&0\\ 011&0&0&0&0\\ 100&1&0&2&1\\ 101&0&0&1&1\\ 110&1&0&2&1\\ 111&0&0&1&1\end{array}\qquad(\alpha=\xi).\]
Both vectors are feasible and satisfy the gauges. Scan the zero entries in the handle's lexicographic type order, retaining a row exactly when it increases rank in the gauge coordinates. The cumulative ranks for \(\rho\) are
\[(1,2,3,4,5,6,7,7,8,8,8,8,9,9,10,10,10,10),\]
and those for \(\xi\) are
\[(1,2,3,4,5,5,6,7,8,8,8,8,9,10,10,10,10,10).\]
The greedy scans therefore return
\[\begin{aligned}B_\rho=(&000/01,000/11,001/01,001/11,010/00,010/01,\\&010/10,011/00,100/01,110/00),\\ B_\xi=(&000/01,000/11,001/00,001/01,001/10,010/01,\\&010/11,011/00,100/01,101/00).\end{aligned}\]
Here \(\delta/ab\) abbreviates \((\delta,(a,b))\). In the reduced coordinate order
\[x=(u_{0,1},u_{1,1},v_{0,1},v_{1,1},u_{1,2},v_{0,2},v_{1,2},u_{1,3},v_{0,3},v_{1,3}),\]
the corresponding row-normal matrices are
\[R_\rho=\begin{pmatrix}1&0&0&0&0&0&0&0&0&0\\ 0&1&0&0&1&0&0&1&0&0\\ 1&0&0&0&0&0&0&0&0&1\\ 0&1&0&0&1&0&0&0&0&1\\ 1&0&0&0&0&1&0&0&0&0\\ 1&0&0&0&0&0&1&0&0&0\\ 0&1&0&0&0&1&0&1&0&0\\ 1&0&0&0&0&1&0&0&1&0\\ 0&0&0&1&0&0&0&0&0&0\\ 0&0&1&0&0&1&0&0&0&0\end{pmatrix},\qquad\det(R_\rho)=-1,\]
\[R_\xi=\begin{pmatrix}1&0&0&0&0&0&0&0&0&0\\ 0&1&0&0&1&0&0&1&0&0\\ 1&0&0&0&0&0&0&0&1&0\\ 1&0&0&0&0&0&0&0&0&1\\ 0&1&0&0&1&0&0&0&1&0\\ 1&0&0&0&0&0&1&0&0&0\\ 0&1&0&0&0&0&1&1&0&0\\ 1&0&0&0&0&1&0&0&1&0\\ 0&0&0&1&0&0&0&0&0&0\\ 0&0&1&0&0&0&0&0&1&0\end{pmatrix},\qquad\det(R_\xi)=1.\]
Thus each feasible vector is isolated by ten tight equations in the ten-dimensional gauge section and is a vertex. The cumulative-rank scans also certify the canonical-basis claim: at each scan position a dependent row cannot enlarge the independent prefix, whereas the first independent row must occur in every lexicographically least full-rank extension. Induction over the ordered signatures therefore proves that \(B_\rho\) and \(B_\xi\) are exactly the canonical bases specified by the handle.

The first two entries agree, but their third entries are respectively \(001/01\) and \(001/00\), with \(001/00\prec001/01\). Hence \(B_\xi\prec B_\rho\). Every parent edge prescribed by the proposed rule strictly decreases the canonical basis. It follows inductively that every basis after \(B_\xi\) on a parent chain beginning at \(\xi\) is strictly smaller than \(B_\xi\), and therefore cannot equal the larger basis \(B_\rho\). No such chain reaches the proposed root \(\rho\). The required root-reachability property fails, so this decreasing-basis rule does not define the claimed reverse-search tree and cannot establish polynomial-delay enumeration. The argument uses no property of other possible parent maps and therefore does not rule out a different polynomial-delay algorithm.