Put \(m=n-1\). By the incidence-matrix and ATE-loading definitions, dual feasibility for \(\lambda\in\mathcal H_{n,2}\) is equivalent to\n\[\n\sum_{z=1}^{2}\Bigl(\lambda_{(a,0,z)}\mathbf 1\{\delta(z)=0\}+\lambda_{(b,1,z)}\mathbf 1\{\delta(z)=1\}\Bigr)\ge b-a\n\]\nfor every \(a,b\in\mathcal Y_n\) and every \(\delta\in\mathcal D^{\mathcal Z_2}\). Call the set of arms having nonconstant blocks the essential-arm support. The description of \(K_{n,l}\) in the gauge-transversal lemma shows that adding an element of \(K_{n,l}\) adds a constant to each arm block. It therefore leaves the essential-arm support unchanged. In particular, essential-arm support is well defined on M-classes and is preserved by \(\Gamma\).\n\nThe binary-instrument count and the gauge-transversal bijection give\n\[\n|\mathcal V_{n,2}|=N_n.\n\]\nWe bound the number of these vertices that fail to have two essential arms. Suppose first that only arm one is essential. The arm-two block is constant, and the gauge equation \(\lambda_{(0,0,2)}=0\) makes that block identically zero. Taking \(\delta(1)=0\) in the dual inequalities and maximizing over \(b\) gives, for every \(a\in\mathcal Y_n\),\n\[\n\lambda_{(a,0,1)}\ge\max_{b\in\mathcal Y_n}(b-a)=m-a.\n\]\nLikewise, taking \(\delta(1)=1\) and maximizing over \(a\) gives, for every \(b\in\mathcal Y_n\),\n\[\n\lambda_{(b,1,1)}\ge\max_{a\in\mathcal Y_n}(b-a)=b.\n\]\nConversely, these \(2n\) coordinatewise inequalities imply every dual inequality when the second block is zero. If any one of them were strict, every dual inequality involving that coordinate would have strictly positive slack, while inequalities not involving it would be unchanged. Because the defining system is finite, a sufficiently small positive and negative perturbation of that coordinate would preserve feasibility and the gauge equations. The point would then be the midpoint of two distinct feasible section points and could not be a vertex. Hence a vertex whose essential-arm support is \(\{1\}\), if it exists, is uniquely forced to satisfy\n\[\n\lambda_{(a,0,1)}=m-a,\qquad \lambda_{(b,1,1)}=b,\qquad \lambda_{(y,d,2)}=0.\n\]\nThus there is at most one such vertex. Interchanging the two instrument arms is an automorphism of the inequality system: it merely permutes treatment-response words and leaves the right side \(b-a\) unchanged. It consequently induces a bijection of quotient vertices, and the gauge-transversal map chooses their unique section representatives. Since arm interchange also interchanges essential-arm supports, there is at most one vertex whose support is \(\{2\}\).\n\nThere is no vertex with empty essential-arm support. Indeed, if both blocks are constant, the second is identically zero by the gauge equation and the first equals some constant \(c\). Every dual left side then equals \(c\), so feasibility requires \(c\ge m\). If \(c>m\), no dual inequality is tight. If \(c=m\), an inequality is tight only when \(b-a=m\), which on \(\mathcal Y_n=\{0,\ldots,m\}\) means \((a,b)=(0,m)\). The tightness graph therefore has no edges in the first case and only the edge \(U_0V_m\) in the second. Since \(n\ge2\), it is disconnected in either case, whereas the zero-arm vertex-lifting lemma proves that the tightness graph of every vertex is connected. Thus at most two of the \(N_n\) binary-instrument vertices fail to have both arms essential, and at least\n\[\nN_n-2\n\]\nof them have essential-arm support \(\{1,2\}\).\n\nFix \(l\ge3\), and let \(\mathcal W_n\subseteq\mathcal V_{n,2}\) be any collection of \(N_n-2\) vertices having both arms essential. Repeated application of the zero-arm lifting lemma gives an injective map \(\iota_{2\to l}\) that copies the two binary blocks to arms one and two and puts zero blocks on all remaining arms. For each unordered pair \(\{i,j\}\subseteq\mathcal Z_l\), with \(i<j\), choose an arm permutation \(\Pi_{ij}\) sending arms one and two to \(i\) and \(j\), and define\n\[\n\Phi_{ij}(\lambda)=\Gamma\bigl(\Pi_{ij}\iota_{2\to l}(\lambda)\bigr),\qquad \lambda\in\mathcal W_n.\n\]\nArm permutation is an automorphism of \(\mathcal H_{n,l}\) and hence of its quotient by \(K_{n,l}\). The lifted point is a section vertex, so the gauge-transversal bijection shows that \(\Phi_{ij}(\lambda)\in\mathcal V_{n,l}\). Its essential-arm support is exactly \(\{i,j\}\): lifting adds only constant zero blocks, permutation relabels the support, and gauge fixing adds only armwise constants. Images belonging to different unordered pairs are therefore distinct.\n\nFor injectivity at a fixed pair, suppose \(\Phi_{ij}(\lambda)=\Phi_{ij}(\mu)\). The two pre-gauge vectors then differ by an element of \(K_{n,l}\), so their difference is armwise constant. It vanishes on every arm outside \(\{i,j\}\), because both pre-gauge vectors have zero blocks there. The two remaining arm constants consequently sum to zero. After applying \(\Pi_{ij}^{-1}\) and restricting to the first two arms, \(\lambda-\mu\in K_{n,2}\). Since \(\lambda,\mu\in\mathcal G_{n,2}\), uniqueness of the gauge representative gives \(\lambda=\mu\). Hence every \(\Phi_{ij}\) is injective. We have constructed pairwise disjoint sets of \(N_n-2\) vertices for all \(\binom l2\) unordered arm pairs. Therefore\n\[\n|\{\lambda\in\mathcal V_{n,l}:\lambda\text{ has exactly two essential arm blocks}\}|\ge\binom l2(N_n-2),\n\]\nand the asserted lower bound on \(|\mathcal V_{n,l}|\) follows.