Call arm \(z\) essential for \(\lambda\) if the block \(\{\lambda_{(y,d,z)}:y\in\mathcal Y_n,d\in\mathcal D\}\) is nonconstant. Adding an element of \(K_{n,l}\) adds one constant to each arm block, so essential-arm support is invariant under M-equivalence and under gauge fixing. By the cited binary-instrument count and the gauge-transversal bijection,\n\[\n|\mathcal V_{n,2}|=N_n.\n\]\nWe determine how many of these vertices have two essential arms. Put \(m=n-1\). Suppose first that only arm one is essential. The arm-two block is constant, and the gauge equation \(\lambda_{(0,0,2)}=0\) makes that entire block zero. Choosing the treatment response on arm one to be zero shows, for every \(a,b\), that \(\lambda_{(a,0,1)}\ge b-a\), and choosing it to be one shows that \(\lambda_{(b,1,1)}\ge b-a\). Maximizing over the unused outcome gives\n\[\n\lambda_{(a,0,1)}\ge m-a,\qquad \lambda_{(b,1,1)}\ge b.\n\]\nConversely, these coordinatewise inequalities imply every two-arm dual constraint when the second block is zero. If any displayed inequality were strict, that coordinate could be perturbed in both directions by a sufficiently small amount while preserving all inequalities, contradicting vertexhood. Thus there is at most one such vertex, namely\n\[\nu^{(1)}_{(a,0,1)}=m-a,\qquad u^{(1)}_{(b,1,1)}=b,\qquad u^{(1)}_{(y,d,2)}=0.\n\]\nIt is indeed a vertex. For each \(a\), the two rows with outcomes \((a,m)\), arm-one response zero, and either arm-two response are active; for each \(b\), the two rows with outcomes \((0,b)\), arm-one response one, and either arm-two response are active. If a gauge direction annihilates these rows, subtracting each pair first forces all treatment-one coordinates of arm two to equal its fixed \((0,0)\) coordinate and then forces all treatment-zero coordinates of arm two to equal them. Hence the second block of the direction is zero. The remaining active equations separately force every coordinate in the first block to be zero. The active-normal criterion therefore proves vertexhood. Arm interchange followed by gauge fixing supplies exactly one analogous vertex with only arm two essential.\n\nThere is no vertex with zero essential arms. If both blocks are constant, every type has the same left side \(c\), independent of its treatment word and outcomes. Feasibility requires \(c\ge m\). When \(c>m\), no inequality is active; when \(c=m\), active outcome pairs consist only of \((a,b)=(0,m)\). In either case the tightness graph is disconnected because \(n\ge2\), contradicting Lemma~\(\text{lem:zero-arm-vertex-lifting}\). It follows that exactly \(N_n-2\) binary-instrument vertices have both arms essential.\n\nFix an unordered pair \(\{i,j\}\subseteq\mathcal Z_l\), ordered by \(i<j\). Place the two blocks of any one of these \(N_n-2\) vertices on arms \(i,j\), put zero blocks on every other arm, and apply the canonical gauge map. Repeated zero-arm lifting proves vertexhood for the embedding on the first two arms; arm permutation is an automorphism of the dual system, and the gauge-transversal lemma carries the permuted M-class to a vertex of \(\mathcal H^0_{n,l}\). The resulting essential-arm support is exactly \(\{i,j\}\), so embeddings attached to different unordered pairs are distinct. For a fixed pair, two embedded vertices could be M-equivalent only if their restrictions to that pair differed by armwise constants summing to zero; gauge transversality for the original binary-instrument section then says that the original vertices were equal. Thus the construction is injective on the product of the \(\binom l2\) arm pairs and the \(N_n-2\) two-essential binary vertices. This proves both displayed lower bounds.