For a type \(\tau=(\delta,\eta)\), define its slack at \(\lambda^\dagger\) by
\[
s_{\delta,\eta}=\sum_{z=1}^{3}\lambda^\dagger_{(\eta(\delta(z)),\delta(z),z)}-\bigl(\eta(1)-\eta(0)\bigr).
\]
Using the coordinate order \(((0,0),(1,0),(0,1),(1,1))\) within each arm, direct substitution of the three blocks in the definition of \(\lambda^\dagger\) gives
\[
\begin{array}{c|rrrr}
\delta\backslash\eta&00&01&10&11\\ \hline
000&2&1&1&0\\
001&2&2&0&0\\
010&0&1&1&2\\
011&0&2&0&2\\
100&2&0&2&0\\
101&2&1&1&0\\
110&0&0&2&2\\
111&0&1&1&2
\end{array}.
\]
Every entry is nonnegative. Moreover, the first coordinate in each of the second and third arm blocks is zero, so the two gauge equations hold. Thus \(\lambda^\dagger\in\mathcal H^0_{2,3}\). Reading off the zero entries of the table gives exactly
\[
\begin{split}
\operatorname{Sig}(\lambda^\dagger)=\{&((000),(11)),((001),(10)),((001),(11)),((010),(00)),\\
&((011),(00)),((011),(10)),((100),(01)),((100),(11)),\\
&((101),(11)),((110),(00)),((110),(01)),((111),(00))\}.
\end{split}
\]
This proves both feasibility and completeness of the asserted signature.

We next certify extremality. Stack the ten coefficient rows indexed, in their displayed order, by \(B^\dagger\), and then append the two gauge rows. In the ambient coordinate order formed by concatenating the three arm blocks, the resulting matrix is
\[
M^\dagger=\left(\begin{array}{rrrrrrrrrrrr}
0&1&0&0&0&1&0&0&0&1&0&0\\
0&1&0&0&0&1&0&0&0&0&1&0\\
0&1&0&0&0&1&0&0&0&0&0&1\\
1&0&0&0&0&0&1&0&1&0&0&0\\
1&0&0&0&0&0&1&0&0&0&1&0\\
0&1&0&0&0&0&1&0&0&0&1&0\\
0&0&0&1&1&0&0&0&1&0&0&0\\
0&0&0&1&0&1&0&0&0&1&0&0\\
0&0&1&0&0&0&1&0&1&0&0&0\\
0&0&0&1&0&0&0&1&1&0&0&0\\
0&0&0&0&1&0&0&0&0&0&0&0\\
0&0&0&0&0&0&0&0&1&0&0&0
\end{array}\right).
\]
Integer elimination gives \(\det(M^\dagger)=1\). Hence the first ten rows have rank \(10\), while all twelve rows have rank \(12\). The two independent gauge equations make \(\mathcal G_{2,3}\) ten-dimensional, and the ten tight type equations therefore isolate \(\lambda^\dagger\) in that affine space. A feasible point isolated by active inequalities is an extreme point. Consequently \(\lambda^\dagger\in\mathcal V_{2,3}\).

It remains to compare this vertex with the literal family \(\mathcal F^{\mathrm{BBAK}}_{2,3}\). By the gauge-transversal lemma, every \(v\in K_{2,3}\) has coordinates \(v_{(y,d,z)}=a_z\). Therefore, for each arm \(z\),
\[
I_z(\lambda+v)=\lambda_{(1,1,z)}+a_z-\lambda_{(0,1,z)}-a_z=I_z(\lambda),
\]
which proves gauge invariance of \(I\). For a comparator indexed by \((a,s)\), with \(s=(s_0,s_1)\), treatment swapping and sign reversal yield
\[
I_z(\bar w(a,s))=-w(a,s)_{1,0,z}+w(a,s)_{0,0,z}.
\]
At \(n=2\), nonconstancy and \(s_j
e a\) imply that \(a,s_0,s_1\) are the three distinct arms. Substitution into the defining coefficients gives
\[
-w(a,s)_{1,0,z}+w(a,s)_{0,0,z}=\mathbf 1\{z=s_0\}.
\]
Since the correction made by \(\Gamma\) is constant within each arm,
\[
I\bigl(\Gamma(\bar w(a,s))\bigr)=e_{s_0}.
\]
Thus every member of the comparator family has the standard-basis invariant asserted in the theorem.

We must also verify that the literal comparator family is contained in the vertex set. Consider first \(a=1\) and \(s=(2,3)\). Its gauge-fixed upper-dual representative has blocks
\[
\mu^0=\bigl((1,0,1,1),(0,0,-1,0),(0,0,0,0)\bigr).
\]
Its complete slack table is
\[
\begin{array}{c|rrrr}
\delta\backslash\eta&00&01&10&11\\ \hline
000&1&0&1&0\\
001&1&0&1&0\\
010&0&0&0&0\\
011&0&0&0&0\\
100&1&0&2&1\\
101&1&0&2&1\\
110&0&0&1&1\\
111&0&0&1&1
\end{array}.
\]
It is therefore feasible. The ten tight types
\[
\begin{split}
\{&((000),(01)),((000),(11)),((001),(01)),((001),(11)),((010),(00)),\\
&((010),(01)),((010),(10)),((011),(00)),((100),(01)),((110),(00))\}
\end{split}
\]
together with the two gauge rows form a \(12\times12\) matrix of determinant \(1\). The same active-rank argument proves \(\mu^0\in\mathcal V_{2,3}\). Every admissible triple \((a,s_0,s_1)\) is an arm permutation of \((1,2,3)\). Arm permutations preserve the incidence inequalities and the ATE right-hand side; on the quotient by \(K_{2,3}\), they therefore preserve extreme points. Applying the unique gauge representative map \(\Gamma\) shows that all six literal comparators belong to \(\mathcal V_{2,3}\).

For completeness, these six vertices are distinct. Introduce the within-arm treatment-zero contrast
\[
J_z(\lambda)=\lambda_{(1,0,z)}-\lambda_{(0,0,z)}.
\]
It too is invariant under addition of \(K_{2,3}\), and direct substitution gives
\[
J\bigl(\Gamma(\bar w(a,s))\bigr)=-e_a,\qquad I\bigl(\Gamma(\bar w(a,s))\bigr)=e_{s_0}.
\]
Thus a representative recovers the ordered pair \((a,s_0)\), and \(s_1\) is the remaining arm. There are consequently exactly six distinct comparator vertices, in agreement with \(3(3-1)^{2-1}=6\) from the corrected literal family definition.

Finally, direct evaluation at the displayed witness gives
\[
I(\lambda^\dagger)=(1-2,\,0-(-2),\,1-0)=(-1,2,1),
\]
which is not a standard basis vector. Hence \(\lambda^\dagger\notin\mathcal F^{\mathrm{BBAK}}_{2,3}\), whereas \(\lambda^\dagger\) and all six members of \(\mathcal F^{\mathrm{BBAK}}_{2,3}\) lie in \(\mathcal V_{2,3}\). Therefore
\[
\mathcal F^{\mathrm{BBAK}}_{2,3}\subsetneq\mathcal V_{2,3},\qquad |\mathcal V_{2,3}|\ge 7,
\]
as claimed.