Work in the \(r=2nl-l+1\) free coordinates of \(\mathcal G_{n,l}\), inserting the fixed zero coordinates when evaluating a type row. First validate and deduplicate the explicitly encoded list \(B\). For every \(\tau\in B\), form its zero--one normal \(\alpha_\tau\) and right-hand side \((c_{n,l})_\tau\). Perform exact elimination on
\[
\alpha_\tau^{\mathsf T}x=(c_{n,l})_\tau,\qquad \tau\in B.
\]
If the system is inconsistent or its row rank is smaller than \(r\), reject. A complete signature of a vertex must have rank \(r\), because a feasible point of a full-dimensional polyhedron is a vertex exactly when its active normals span the ambient space. Here full dimensionality follows, for example, by assigning a common constant \(C>n-1\) to all four coordinates in arm \(1\), assigning zero to the gauged coordinates, and choosing all remaining free coordinates positive and sufficiently small: every type sum contains the contribution \(C\) from arm \(1\), so every inequality is strict.

If the rank is \(r\), exact elimination produces the unique rational candidate \(\lambda\). For \((a,b)\in\mathcal Y_n^2\), define
\[
m_{ab}(\lambda)=\sum_{z=1}^l\min\{\lambda_{(a,0,z)},\lambda_{(b,1,z)}\}.
\]
For a type with \(\eta(0)=a\) and \(\eta(1)=b\), separability over the treatment word gives the identity
\[
\min_{\delta\in\mathcal D^{\mathcal Z_l}}\left[\sum_{z=1}^l\lambda_{(\eta(\delta(z)),\delta(z),z)}-(b-a)\right]=m_{ab}(\lambda)-(b-a).
\]
Therefore \(\lambda\in\mathcal H^0_{n,l}\) if and only if \(m_{ab}(\lambda)\ge b-a\) for all \(n^2\) pairs. Reject if any inequality fails.

Suppose feasibility holds. If \(m_{ab}(\lambda)>b-a\), no type with outcome pair \((a,b)\) is tight. If equality holds, set
\[
R_{ab,z}=\operatorname*{argmin}_{d\in\{0,1\}}\lambda_{(\eta(d),d,z)}.
\]
A treatment word is tight exactly when \(\delta(z)\in R_{ab,z}\) for every arm, because every summand exceeds its armwise minimum by a nonnegative amount. Hence the tight words for \((a,b)\) are the explicit Cartesian product \(\prod_z R_{ab,z}\), whose cardinality is \(2^{t_{ab}}\), with
\[
t_{ab}=|\{z:\lambda_{(a,0,z)}=\lambda_{(b,1,z)}\}|.
\]
Check that every listed type belongs to the appropriate product and that the number of distinct listed words for each \((a,b)\) is zero in the strict case and \(2^{t_{ab}}\) in the equality case. Subset inclusion plus equality of these finite cardinalities is equivalent to \(B=\operatorname{Sig}(\lambda)\), without expanding any unlisted treatment word. Accept exactly in this case. Since the equations indexed by \(B\) have rank \(r\), the accepted feasible point is a vertex. Conversely, the true complete signature of any vertex passes every step, so the algorithm is sound and complete.

It remains to check complexity. There are \(O(nl)\) variables, \(|B|\) explicit zero--one rows, and \(n^2l\) armwise comparisons. Exact Gaussian or fraction-free elimination is polynomial in these dimensions and in the coefficient bit lengths. Hadamard's determinant bound gives polynomial bit length for the unique rational candidate because the equation coefficients are zero--one and the right-hand sides have magnitude at most \(n-1\). Each integer \(2^{t_{ab}}\) has at most \(l+1\) bits. Thus all validation, feasibility, completeness, and rank computations take time polynomial in \(n+l+\operatorname{enc}(B)\).