Use the within-arm coordinate order \((u_{0,z},u_{1,z},v_{0,z},v_{1,z})\). For a type \((\delta,\eta)\), direct substitution in the definitions of \(A_{2,3}\) and \(c_{2,3}\) gives the slack at \(\mu\). With columns ordered by \(\eta=00,01,10,11\), the complete table is
\[\begin{array}{c|rrrr}\delta\backslash\eta&00&01&10&11\\ \hline 000&2&1&1&0\\ 001&1&1&0&0\\ 010&1&1&1&1\\ 011&0&1&0&1\\ 100&2&0&2&0\\ 101&1&0&1&0\\ 110&1&0&2&1\\ 111&0&0&1&1\end{array}.\tag{1}\]
Every entry is nonnegative and the two gauge coordinates are zero, so \(\mu\in\mathcal H^0_{2,3}\). The zero entries in (1) give the complete signature
\[\begin{split}\operatorname{Sig}(\mu)=\{&000/11,001/10,001/11,011/00,011/10,100/01,100/11,\\&101/01,101/11,110/01,111/00,111/01\}.\end{split}\tag{2}\]
Here \(\delta/ab\) abbreviates the type with treatment word \(\delta\) and outcome pair \((a,b)\).

Eliminate the gauge coordinates and use the reduced order
\[x=(u_{0,1},u_{1,1},v_{0,1},v_{1,1},u_{1,2},v_{0,2},v_{1,2},u_{1,3},v_{0,3},v_{1,3}).\]
The first ten independent rows obtained by a greedy scan of (2) are
\[B_\mu=(000/11,001/10,001/11,011/00,011/10,100/01,100/11,101/01,110/01,111/00).\]
Their row-normal matrix is
\[R_\mu=\begin{pmatrix}0&1&0&0&1&0&0&1&0&0\\0&1&0&0&1&0&0&0&1&0\\0&1&0&0&1&0&0&0&0&1\\1&0&0&0&0&1&0&0&1&0\\0&1&0&0&0&1&0&0&1&0\\0&0&0&1&0&0&0&0&0&0\\0&0&0&1&1&0&0&1&0&0\\0&0&0&1&0&0&0&0&0&1\\0&0&0&1&0&0&1&0&0&0\\0&0&1&0&0&1&0&0&1&0\end{pmatrix},\qquad\det(R_\mu)=-1.\tag{3}\]
Thus the active normals at \(\mu\) span all ten gauge coordinates. The active-rank vertex criterion gives \(\mu\in\mathcal V_{2,3}\).

The already certified signature of \(\lambda^\dagger\) and (2) have the following ten common types:
\[\mathcal C=\{000/11,001/10,001/11,011/00,011/10,100/01,100/11,101/11,110/01,111/00\}.\tag{4}\]
The first nine displayed types in (4) after omitting \(101/11\) have rank nine. An exact minor certificate, obtained by deleting the tenth reduced coordinate, is
\[\det\begin{pmatrix}0&1&0&0&1&0&0&1&0\\0&1&0&0&1&0&0&0&1\\0&1&0&0&1&0&0&0&0\\1&0&0&0&0&1&0&0&1\\0&1&0&0&0&1&0&0&1\\0&0&0&1&0&0&0&0&0\\0&0&0&1&1&0&0&1&0\\0&0&0&1&0&0&1&0&0\\0&0&1&0&0&1&0&0&1\end{pmatrix}=-1.\tag{5}\]
On the other hand, the nonzero reduced direction from \(\lambda^\dagger\) to \(\mu\) is
\[d=\mu-\lambda^\dagger=(0,0,0,0,1,1,0,-1,-1,-1).\tag{6}\]
Every common active row annihilates \(d\), because it is tight at both endpoints. Hence the common active rank is at most nine; (5) makes it exactly nine. The smallest face containing the two vertices is the intersection of their common supporting hyperplanes, so its dimension is \(10-9=1\). It is therefore the bounded edge \([\lambda^\dagger,\mu]\).

Finally, evaluate the rows of the frozen canonical basis \(B^\dagger\) on (6), in the order specified in its definition. The resulting directional products are
\[\bigl(\alpha_\tau^{\mathsf T}d\bigr)_{\tau\in B^\dagger}=(0,0,0,1,0,0,0,0,1,0).\tag{7}\]
The two nonzero entries correspond to \(010/00\) and \(110/00\). Thus \(\mu\) fails both of those equations, with slack one in table (1). Deleting any single equation from \(B^\dagger\) leaves at least one of these two failed equations in the retained nine-equation system. Adding one new type equation cannot remove that retained failure. Consequently no one-type-equation exchange from the canonical basis \(B^\dagger\) reconstructs the adjacent vertex \(\mu\), proving the claim.