% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_proximal\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_proximal\_phase} / \texttt{v1}%
  \\ \large\textit{Functional-null proximal phase transition for weak negative-control completeness}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization}, P, \theta, \text{identifying restrictions}, \text{bounding functional}).
\]
Here \(\texttt{qid}=\texttt{eid\_proximal\_phase}\) and
\(\texttt{specialization}=\texttt{v1}\).  The observable distribution \(P\) is
the joint law of \(O=(Y,A,W,Z,X)\), where \(A\in\{0,1\}\), \(Y\in[0,1]\), and
\((W,Z,X)\) have finite supports.  The target parameter is
\(\theta=\E\{Y(1)-Y(0)\}\).  The identifying restrictions are consistency,
positivity for both treatment arms, the negative-control exclusion and latent
exchangeability restrictions that justify the proximal outcome-bridge moment,
bounded potential outcomes in \([0,1]\), and the finite bridge-envelope
realizability restriction stated in Assumption~\ref{ass:finite-realization}.
The bounding functional is the sharp support interval
\[
\Theta_I(P)=
\left[
\inf_{h\in\calH(P)} L_P(h),\,
\sup_{h\in\calH(P)} L_P(h)
\right],
\quad
L_P(h)=\E_P\{h(W,1,X)-h(W,0,X)\},
\]
where \(\calH(P)=\{h\in[0,1]^{\mathcal W\times\{0,1\}\times\mathcal X}:T_Ph=m_P\}\),
\((T_Ph)(z,a,x)=\E_P\{h(W,a,x)\mid Z=z,A=a,X=x\}\), and
\(m_P(z,a,x)=\E_P(Y\mid Z=z,A=a,X=x)\).

\begin{abstract}
Proximal causal inference identifies average treatment effects by solving an
outcome-bridge equation, but the standard completeness condition can fail in
empirically plausible negative-control designs.  This proposal asks for the
sharp finite-state ATE identified set when the bridge operator has weak or
rank-deficient proxy information.  The proposed kernel has two non-routine
pieces: a generic finite response-type realization theorem for the observable
bridge envelope, and a sharp residual-tolerance modulus describing how fast
the identified set inflates as bridge moments are allowed to fail.  Conditional
on realization, point identification holds when the ATE loading annihilates
every attainable bridge-null direction, a nontrivial interval appears when
some bounded null direction changes the loading, and the interval becomes
Manski-trivial only when the two observable endpoint LP certificate problems
are feasible.  The flagship conjecture therefore replaces a scalar ``smallest
singular value'' story by a computable support-function threshold that can
distinguish weak bridge identification from weak causal-effect
identification.  If resolved, the result would turn proximal completeness
failure into a reportable finite LP diagnostic rather than an all-or-nothing
modeling assumption.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Negative controls have made unmeasured-confounding adjustment possible in
settings where ordinary covariate adjustment is scientifically implausible.
The price is an inverse problem: the researcher must believe that the outcome
bridge equation has enough proxy variation to identify the causal contrast.
Completeness is a mathematical condition rather than an empirical diagnostic,
so applied proximal analyses need a sharp answer to what remains identified
when the bridge function is weakly identified, nonunique, or not identified at
all.

\paragraph{The main finding (proposed).}
The headline claims are Conjectures~\ref{conj:realization}
and~\ref{conj:residual-modulus}.  The first asserts that, on a generic
finite negative-control class, every rational point of the observable bridge
envelope is realized by a finite latent response-type model with an explicit
support-size bound.  The second asserts that the proximal ATE has a
first-order residual-tolerance phase modulus: after the sharp exact-moment
interval is known, the rate at which it expands under
\(\|T_Ph-m_P\|_2\le\varepsilon\) is the value of a finite tangent-cone support
problem, bounded by the active singular-value scale and attained on an open
class of proxy laws.

\paragraph{What is new.}
The closest point-identification papers, \citet{MiaoGengTchetgen2018Biometrika}
and \citet{CuiPuShiMiaoTchetgen2024JASA}, assume bridge/completeness
conditions under which the proximal formula returns a single ATE.  The closest
partial-identification paper, \citet{GhassamiShpitserTchetgen2023ProxyPI},
drops completeness and derives proxy bounds, but it does not prove that a
finite bridge-null envelope is generically realized by actual
negative-control causal models with a support-size certificate.  The closest
functional-identification papers,
\citet{ZhangLiMiaoTchetgen2023SPL},
\citet{BennettKallusMaoNeweySyrgkanisUehara2023COLT}, and
\citet{Santos2011JoE}, explain when a linear functional is identified despite
nonunique nuisances; they do not characterize the sharp interval or its
residual-tolerance modulus once that condition fails.  The novel epsilon gap
is the combination of finite bridge-envelope realization and a tangent-cone
phase constant, not the deterministic observation that a compact interval has
zero, intermediate, or full width.

\paragraph{How it positions in the literature.}
The proposal sits at the intersection of exact proximal identification and
partial identification.  It treats the bridge equation as the exact-ID
object, but its main result is an identified-set theorem in the
Manski/Balke--Pearl spirit: the causal parameter is the image of an observable
feasible set under a linear functional.  The finite-state restriction is
deliberate; it creates an observable matrix operator \(T_P\), singular
subspaces, and LP support functions that can be checked directly.

\paragraph{Implications for the community.}
The concrete consumer is the proximal semiparametric workflow of
\citet{CuiPuShiMiaoTchetgen2024JASA}: when completeness is doubtful, an
analysis could report the null-loading phase and the sharp interval
\(\Theta_I(P)\) before applying OR, IPW, or doubly robust estimators.  If the
realization and residual-modulus conjectures resolve favorably, empirical PCI
papers can replace an untestable ``assume completeness'' sentence by a finite
proxy-strength diagnostic, a sharp fallback bound, and a first-order
fragility calculation.

\paragraph{How research benefits from the conclusion.}
A researcher should check whether the ATE loading annihilates the estimated
bridge-null directions, report the resulting sharp interval whenever it does
not, and use \(\Gamma_P\) as the sensitivity scale for small bridge-moment
misspecification.

\section{Related work}
\citet{MiaoGengTchetgen2018Biometrika} is the foundational two-proxy point
identification paper: it establishes nonparametric causal-effect
identification under rank/completeness-type proxy conditions, leaving
rank-deficient failure regimes outside the theorem.  \citet{CuiPuShiMiaoTchetgen2024JASA}
develop semiparametric proximal OR/IPW/DR identification and efficiency under
bridge assumptions; this proposal asks what sharp identified set the same
observable law supports when those bridge assumptions are not strong enough
for point identification.  \citet{TchetgenYingCuiShiMiao2024StatSci} gives
the current statistical overview of proximal causal inference and motivates
proxy bridge assumptions as a replacement for measured exchangeability.
\citet{GhassamiShpitserTchetgen2023ProxyPI} is the closest partial-ID anchor:
it obtains proxy-based causal-effect bounds without completeness, but does
not supply a finite singular-subspace phase transition for the ATE loading.
\citet{Manski1990AER} is the canonical partial-identification reference for
bounded-outcome treatment-effect intervals; it motivates using the full
\([-1,1]\) ATE range as the fallback rather than forcing point identification.
\citet{BalkePearl1997JASA} gives sharp finite response-type LP bounds for
binary instrumental-variable models; Conjecture~\ref{conj:realization} is
intended as a proximal analogue only after proving a new negative-control
response-type realization step, not as a routine restatement of their IV LP.
\citet{ZhangLiMiaoTchetgen2023SPL} shows that proximal bridges may be
nonunique while counterfactual means can still be identified, directly
motivating the null-annihilation criterion in
Theorem~\ref{thm:phase-classification}.
\citet{BennettKallusMaoNeweySyrgkanisUehara2023COLT} studies strongly
identified linear functionals of weakly identified nuisance functions,
including proximal examples; this proposal treats their strong-identification
principle as prior art and asks for the finite sharp identified set when the
functional is not strongly identified.  \citet{Santos2011JoE}
separates recovery of linear functionals from full NPIV structural-function
identification, providing the adjoint-range analogy for \(L_P\in\operatorname{range}(T_P^*)\).
\citet{CanaySantosShaikh2013Econometrica} shows that completeness and related
identification hypotheses can be non-testable in nonparametric endogenous
models, which is why the present proposal locks finite supports and observable
matrices rather than claiming a universal diagnostic.  \citet{Andrews2017JoECompleteness}
provides econometric examples of \(L^2\)-complete and boundedly-complete
distributions, but not sharp rank-deficient causal-effect intervals.
\citet{DarollesFanFlorensRenault2011Econometrica} is the inverse-problem
estimation anchor: it treats NPIV as an ill-posed integral equation, whereas
the current proposal isolates the identification set before regularization.
\citet{Fiacco1983Sensitivity} and \citet{BonnansShapiro2000Perturbation}
are the standard optimization references for value-function and active-set
sensitivity; Conjecture~\ref{conj:residual-modulus} uses that calculus only
after adding the proximal-specific facts that the perturbed LP is generated
by the observable bridge operator and that its support-function derivative is
sharp for an actual negative-control causal model.

\begin{center}
\begin{tabular}{p{0.24\linewidth}p{0.32\linewidth}p{0.34\linewidth}}
\textbf{Thread} & \textbf{What is already settled} & \textbf{Gap used here}\\
Miao--Geng--Tchetgen and Cui--Pu--Shi--Miao--Tchetgen &
Proximal ATE point identification and efficient estimation under bridge
conditions &
No sharp finite fallback set when the bridge operator is rank deficient.\\
Ghassami--Shpitser--Tchetgen &
Proxy-based partial identification without completeness &
No generic response-type realization theorem for the finite bridge envelope.\\
Zhang--Li--Miao--Tchetgen, Bennett et al., Santos &
Functional identification can survive nonunique nuisance functions &
No sharp residual-tolerance modulus after functional identification fails.\\
Balke--Pearl &
Finite IV response-type LP sharpness &
No negative-control bridge-array realization preserving proxy exclusions.
\\
Fiacco and Bonnans--Shapiro &
Parametric optimization value sensitivity under active-set regularity &
No causal sharpness or weak-proxy singular-value lower-bound class.
\end{tabular}
\end{center}

In the ThmSmith catalogue, \texttt{pid\_mediation\_proxy} is the closest
failed proxy partial-ID artifact: its reviewer record warns that a full
bridge-null interval can collapse to a projection identity if finite
realization is not proved.  The downgraded \texttt{eid\_frontdoor\_multi\_mediator}
proposal supplies a related bridge-envelope/nonrectangular LP geometry and
the same realization obstruction.  The \texttt{q1\_spectral\_phase\_transition}
proposal is an in-repository singular-value analogue in panel/FWL algebra,
but it does not concern proximal bridges or causal-effect identified sets.
The project API describes the PartialID family as the repository home for
Manski and Balke--Pearl style bounds; this proposal belongs there
mathematically even though its qid prefix is \texttt{eid}.

\section{Formal setup}
All variables are finite except the bounded outcome \(Y\in[0,1]\).  The
observed law \(P\) is over \(O=(Y,A,W,Z,X)\), with binary treatment \(A\),
outcome-confounding proxy \(W\), treatment-confounding proxy \(Z\), and
covariates \(X\).  A latent proximal model augments \(P\) with an unobserved
confounder \(U\), potential outcomes \(Y(0),Y(1)\), consistency
\(Y=Y(A)\), latent exchangeability \(Y(a)\perp A\mid U,X\), negative-control
exclusions for \(W\) and \(Z\), and overlap \(0<P(A=a\mid X)<1\).  The
target is \(\theta=\E\{Y(1)-Y(0)\}\).

For a candidate bridge \(h:\mathcal W\times\{0,1\}\times\mathcal X\to[0,1]\),
define the observable bridge operator and right-hand side by
\[
(T_Ph)(z,a,x)=\sum_w h(w,a,x)P(W=w\mid Z=z,A=a,X=x),\qquad
m_P(z,a,x)=\E_P(Y\mid Z=z,A=a,X=x).
\]
The observable bridge fiber is
\[
\calH(P)=\{h\in[0,1]^{\mathcal W\times\{0,1\}\times\mathcal X}:T_Ph=m_P\}.
\]
The ATE loading is the linear functional
\[
L_P(h)=\sum_{x,w}\{h(w,1,x)-h(w,0,x)\}P(W=w\mid X=x)P(X=x).
\]
Let \(N_P=\{r:T_Pr=0\}\) be the bridge-null space, let
\(\calR_P(h)=\{r\in N_P:h+r\in[0,1]^{\mathcal W\times\{0,1\}\times\mathcal X}\}\)
be the attainable null directions at \(h\).  Define the sharp LP endpoints and width
\[
\underline\theta_P=\min_{h\in\calH(P)}L_P(h),\qquad
\overline\theta_P=\max_{h\in\calH(P)}L_P(h),\qquad
\Delta_P=\overline\theta_P-\underline\theta_P.
\]
Equivalently, \(\Delta_P\) is the two-sided support-function width of
\(\calH(P)\) in the direction \(L_P\), so \(0\le\Delta_P\le2\) because
\(Y(a)\in[0,1]\).  For \(s\in\{-1,1\}\), let
\[
\mathsf{Cert}_s(P)=
\left\{h\in[0,1]^{\mathcal W\times\{0,1\}\times\mathcal X}:
T_Ph=m_P,\ L_P(h)=s\right\}
\]
be the observable endpoint LP certificate set.  The smallest positive singular value of \(T_P\) on the orthogonal
complement of \(N_P\) is denoted by \(\sigma_+(P)\); if no positive singular
value exists, \(\sigma_+(P)=0\).  For \(\varepsilon\ge0\), the
residual-tolerance fiber is
\[
\calH_\varepsilon(P)=\{h\in[0,1]^{\mathcal W\times\{0,1\}\times\mathcal X}:
\|T_Ph-m_P\|_2\le\varepsilon\}.
\]
Define the perturbed endpoints and width by
\[
\underline\theta_{P,\varepsilon}=\min_{h\in\calH_\varepsilon(P)}L_P(h),
\quad
\overline\theta_{P,\varepsilon}=\max_{h\in\calH_\varepsilon(P)}L_P(h),
\quad
\Delta_{P,\varepsilon}=\overline\theta_{P,\varepsilon}
-\underline\theta_{P,\varepsilon}.
\]
Let \(\ell_P\) be the vector representing \(L_P\) under the Euclidean inner
product on bridge arrays.  The estimand-active row space is the span of the
right singular directions \(v\) of \(T_P\) with positive singular value and
\(\langle \ell_P,v\rangle\neq0\).  Let \(\sigma_{\mathrm{act}}(P)\) be the
minimum positive singular value among these active directions; if there are no
active directions, set \(\sigma_{\mathrm{act}}(P)=+\infty\), so
\(\varepsilon/\sigma_{\mathrm{act}}(P)=0\).  Let
\(\Pi_{\mathrm{act},P}\ell_P\) be the projection of \(\ell_P\) onto this
active row space and define \(C_P=2\|\Pi_{\mathrm{act},P}\ell_P\|_2\).  The
residual-tolerance width inflation is
\[
I_P(\varepsilon)=\Delta_{P,\varepsilon}-\Delta_P.
\]
Let \(\calH_P^+\) and \(\calH_P^-\) denote the upper and lower endpoint
optimizer sets for \(L_P\) over \(\calH(P)\).  When these optimizers are
unique, write them as \(h_P^+\) and \(h_P^-\).  For any bridge array \(h\),
let \(\mathcal T_{\Box}(h)\) be the tangent cone of the box
\([0,1]^{\mathcal W\times\{0,1\}\times\mathcal X}\) at \(h\).  The candidate
first-order residual modulus is
\[
\Gamma_P=
\sup_{\substack{d\in\mathcal T_{\Box}(h_P^+)\\ \|T_Pd\|_2\le1}}L_P(d)
-
\inf_{\substack{d\in\mathcal T_{\Box}(h_P^-)\\ \|T_Pd\|_2\le1}}L_P(d),
\]
whenever \(h_P^+\) and \(h_P^-\) are unique.  This is a finite conic LP
quantity; under strict complementarity it is the directional derivative
candidate for \(\Delta_{P,\varepsilon}\) at \(\varepsilon=0\).
No perturbation claim below divides by \(\sigma_+(P)\) when
\(\sigma_+(P)=0\).
The finite realization support-size bound used in
Conjecture~\ref{conj:realization} is
\[
B_P
=1+
|\mathcal A||\mathcal W||\mathcal Z||\mathcal X|
+2|\mathcal W||\mathcal A||\mathcal X|
+|\mathcal Z||\mathcal A||\mathcal X|.
\]
The identified set is the set of all ATE values compatible with \(P\) and the
restrictions in Section 7, denoted \(\Theta_I(P)\).

To make the genericity language in Conjecture~\ref{conj:realization}
concrete, identify \(T_P\) with its finite matrix and \(m_P\) with its vector.
Let
\[
\mathcal M(T_P)=\{T_Ph:0\le h\le1\}
\]
be the observable bridge-moment polytope, and let \(F_P\) be the minimal face
of \(\mathcal M(T_P)\) containing \(m_P\).  The phrase ``\(P\) belongs to the
relative interior of the observable bridge-feasibility stratum'' means the
following three observable quantities are held fixed in a local cell:
\begin{enumerate}[label=(\alph*)]
\item the zero pattern of \(P(W=w,Z=z,A=a,X=x)\), so all conditioning rows used
in \(T_P\) remain either positive or structurally absent;
\item \(\operatorname{rank}(T_P)\) and the ranks of the submatrices of \(T_P\)
whose columns define the face \(F_P\); and
\item the face itself, with \(m_P\in\operatorname{relint}(F_P)\).
\end{enumerate}
Thus the local stratum is a relative-interior cell of the finite observable
simplex crossed with a fixed-rank matrix cell; the polyhedral object is the
face \(F_P\subseteq\mathcal M(T_P)\), and the rank data state exactly which
singular directions and zero cells are not allowed to change during the
generic realization claim.

\begin{verbatim}
qid = eid_proximal_phase
specialization = v1
observable distribution P = law of (Y,A,W,Z,X), with finite W,Z,X,A and Y in [0,1]
parameter theta = E[Y(1)-Y(0)]
identifying restrictions = consistency, positivity, latent proximal exchangeability,
  negative-control exclusions, bounded potential outcomes, and finite bridge-envelope
  realizability
bounding functional = sharp support interval of L_P(h) over h in H(P), where
  H(P) = {h in [0,1]^(W x {0,1} x X) : T_P h = m_P}
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite observable support and bounded outcomes]\label{ass:finite-bounded}
The supports of \(W,Z,X,A\) are finite, \(A\in\{0,1\}\), and \(Y\in[0,1]\)
almost surely.
\end{assumption}

\begin{assumption}[Treatment positivity]\label{ass:positivity}
For each \(x\) with \(P(X=x)>0\), \(0<P(A=a\mid X=x)<1\) for \(a=0,1\).
All conditional probabilities used in \(T_P\) are evaluated only on cells with
positive \(P(Z=z,A=a,X=x)\).
\end{assumption}

\begin{assumption}[Proximal negative-control validity]\label{ass:proximal-valid}
There exists a latent variable \(U\) such that consistency holds,
\(Y=Y(A)\), \(Y(a)\perp A\mid U,X\), \(Z\) has no direct effect on \(Y\)
given \(A,U,X\), and \(W\) is not affected by \(A\) or \(Z\) except through
\((U,X)\).  These restrictions are the finite negative-control restrictions
that justify the outcome-bridge moment when an outcome bridge is present.
\end{assumption}

\begin{assumption}[Nonempty bounded bridge fiber]\label{ass:bridge-nonempty}
The observable bridge fiber \(\calH(P)\) is nonempty.
\end{assumption}

\begin{assumption}[Finite bridge-envelope realization]\label{ass:finite-realization}
Every \(h\in\calH(P)\) that satisfies the boundedness restriction is
attainable by at least one finite latent proximal model obeying
Assumptions~\ref{ass:finite-bounded}--\ref{ass:proximal-valid} and inducing
the observed law \(P\); conversely, every compatible latent proximal model
induces an element of \(\calH(P)\) whose ATE is \(L_P(h)\).
\end{assumption}

\begin{assumption}[Endpoint attainability]\label{ass:endpoint-attain}
The extrema of \(L_P(h)\) over \(\calH(P)\) are attained.  Under
Assumption~\ref{ass:finite-bounded}, this holds because \(\calH(P)\) is a
closed bounded polytope.
\end{assumption}

\begin{assumption}[Endpoint LP certificates]\label{ass:endpoint-certificates}
The phrase ``Manski-trivial'' means \(\Theta_I(P)=[-1,1]\), the full ATE
range implied only by \(Y(a)\in[0,1]\).  The endpoint certificates are the two
finite feasibility problems
\[
\mathsf{Cert}_{-1}(P)\neq\emptyset,\qquad
\mathsf{Cert}_{1}(P)\neq\emptyset,
\]
where \(\mathsf{Cert}_s(P)\) is defined in Section~6 by the observable
constraints \(T_Ph=m_P\), \(0\le h\le1\), and \(L_P(h)=s\).  This condition is
independent of the label ``Manski-trivial'': it can be checked by two linear
program feasibility calls before invoking any causal sharpness conclusion.
\end{assumption}

\begin{assumption}[Observable support-rank genericity]\label{ass:generic-stratum}
The observed law \(P\) lies in the relative interior of the observable
bridge-feasibility stratum defined in Section~6: the zero pattern of
\(P(W,Z,A,X)\), the rank of \(T_P\), the ranks of the submatrices defining
the bridge-moment face \(F_P\), and the condition
\(m_P\in\operatorname{relint}(F_P)\) are all fixed in the local cell.
\end{assumption}

\begin{assumption}[Generic endpoint regularity]\label{ass:generic-endpoint}
The endpoint LPs defining \(\underline\theta_P\) and \(\overline\theta_P\)
have unique optimizers \(h_P^-\) and \(h_P^+\), and the active box constraints
at those optimizers satisfy strict complementarity for the finite LP pair.
This is the generic finite-dimensional regularity condition used only for
the first-order residual-tolerance statement.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: bridge-envelope support interval]\label{thm:support-interval}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:endpoint-attain},
\[
\Theta_I(P)=
\left[
\min_{h\in\calH(P)} L_P(h),\,
\max_{h\in\calH(P)} L_P(h)
\right].
\]
Equivalently, for any \(h_0\in\calH(P)\),
\[
\Theta_I(P)=L_P(h_0)+
\left[
\min_{r\in N_P:\,h_0+r\in[0,1]}L_P(r),\,
\max_{r\in N_P:\,h_0+r\in[0,1]}L_P(r)
\right].
\]
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The algebraic support interval is routine once
Assumption~\ref{ass:finite-realization} is granted; the closest published
comparison is \citet{GhassamiShpitserTchetgen2023ProxyPI}, which gives proxy
bounds without packaging the finite bridge fiber as this null-space support
functional.  The epsilon gap is not the LP itself but the bridge-envelope
realization needed to make it sharp for causal models.  (b) The concrete
consumer is the proximal DR estimator setup in \citet{CuiPuShiMiaoTchetgen2024JASA}:
Theorem~\ref{thm:support-interval} supplies the finite fallback interval to
report when its point-identifying bridge conditions are not defensible.

\begin{conjecture}[Conjecture 1: generic finite proximal realization theorem (NOT YET PROVED)]\label{conj:realization}
For every rational finite observed law \(P\) satisfying
Assumptions~\ref{ass:finite-bounded}--\ref{ass:bridge-nonempty} and
Assumption~\ref{ass:generic-stratum}, every rational \(h\in\calH(P)\) is
realized by a finite latent proximal model
obeying Assumptions~\ref{ass:finite-bounded}--\ref{ass:proximal-valid} and
inducing the same observed law \(P\).  Moreover the latent support can be
chosen with at most
\[
B_P
=1+
|\mathcal A||\mathcal W||\mathcal Z||\mathcal X|
+2|\mathcal W||\mathcal A||\mathcal X|
+|\mathcal Z||\mathcal A||\mathcal X|
\]
response types, where the two potential-outcome coordinates are real values
in \([0,1]\) rather than finite outcome categories.  The construction is
locally stable: there is a nonempty
open neighborhood of such \(P\)'s inside the finite observable simplex on
which the same support bound realizes all rational bridge-envelope points.
Consequently the interval in Theorem~\ref{thm:support-interval} is the sharp
proximal ATE identified set on this generic class, not merely an outer
relaxation.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest project prior is the failed \texttt{pid\_mediation\_proxy}
angle, whose reviewer rejected a full-fiber sharpness claim because no finite
model realized each bridge-null array.  The closest published anchor,
\citet{MiaoGengTchetgen2018Biometrika}, uses rank/completeness for point
identification and does not construct rank-deficient response-type models
realizing every bounded bridge solution.  The epsilon gap is the missing
Balke--Pearl-style finite realization theorem for proximal bridge fibers:
\citet{BalkePearl1997JASA} supplies sharp finite IV response-type LP bounds,
but its response table is tied to instrument/treatment monotone types rather
than negative-control bridge arrays constrained by \(T_Ph=m_P\).
(b) Resolving it would unblock \citet{GhassamiShpitserTchetgen2023ProxyPI}
style proxy bounds in finite negative-control designs by certifying when the
computed LP is sharp rather than conservative.

\begin{theorem}[Theorem 2: conditional finite LP-width phase classification]\label{thm:phase-classification}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:endpoint-certificates}, the
following three regimes are sharp and exhaustive.
\begin{enumerate}[label=(\roman*)]
\item Point regime: \(\Theta_I(P)\) is a singleton if and only if
\(\Delta_P=0\), equivalently \(L_P(r)=0\) for every feasible difference
\(r=h'-h\) with \(h,h'\in\calH(P)\).
\item Nontrivial interval regime: \(\Theta_I(P)\) is a strict subset of
\([-1,1]\) with positive width if and only if \(0<\Delta_P<2\).  Its width is
the computable LP support-function width
\[
\max_{h\in\calH(P)}L_P(h)-\min_{h\in\calH(P)}L_P(h).
\]
\item Manski-trivial regime: \(\Theta_I(P)=[-1,1]\) if and only if
\(\mathsf{Cert}_{-1}(P)\neq\emptyset\) and
\(\mathsf{Cert}_{1}(P)\neq\emptyset\), equivalently
\(\underline\theta_P=-1\), \(\overline\theta_P=1\), and
\(\Delta_P=2\).  This can occur when \(\sigma_+(P)=0\), but
\(\sigma_+(P)=0\) alone is not sufficient because the ATE loading and the box
constraints may still exclude one or both endpoints.
\end{enumerate}
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is intentionally conditional: after
Assumption~\ref{ass:finite-realization}, the trichotomy is the exact finite
LP classification needed to state the non-tautological conjectures cleanly.
The closest published comparison is
\citet{GhassamiShpitserTchetgen2023ProxyPI}, which supplies proxy bounds but
not the endpoint certificate formulation separating point, interval, and
Manski-trivial phases.  (b) The concrete consumer is the proximal OR/IPW/DR
workflow of \citet{CuiPuShiMiaoTchetgen2024JASA}; analysts using that
workflow could report whether bridge nonuniqueness is harmless for the ATE,
forces a nontrivial interval, or leaves only the full Manski range.

\begin{conjecture}[Conjecture 2: sharp residual-tolerance phase modulus (NOT YET PROVED)]\label{conj:residual-modulus}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:generic-endpoint}, and
on the generic realization class of Conjecture~\ref{conj:realization}, the
residual-tolerance width has the one-sided expansion
\[
\Delta_{P,\varepsilon}
=\Delta_P+\varepsilon\Gamma_P+o(\varepsilon)
\qquad\text{as }\varepsilon\downarrow0.
\]
The constant \(\Gamma_P\) is the finite tangent-cone support value defined in
Section~6 and satisfies
\[
0\le\Gamma_P\le C_P/\sigma_{\mathrm{act}}(P)
\]
with the convention that the right side is \(0\) when
\(\sigma_{\mathrm{act}}(P)=+\infty\).  The bound is sharp on an open class of
finite proxy laws with a one-dimensional active singular direction: for those
laws \(\Gamma_P=C_P/\sigma_{\mathrm{act}}(P)\), so the
\(1/\sigma_{\mathrm{act}}\) inflation is an identification phenomenon rather
than an artifact of regularized bridge estimation.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{ZhangLiMiaoTchetgen2023SPL} and
\citet{BennettKallusMaoNeweySyrgkanisUehara2023COLT} show that functionals
can be identified when nuisance bridges are not unique, and
\citet{Santos2011JoE} gives the NPIV adjoint-range analogue.  This proposal
therefore does not claim the null-annihilation principle as new.  The epsilon
gap is the first-order \(\Gamma_P\) formula and the matching lower-bound
class showing when weak proxy singular values genuinely inflate the sharp ATE
set.  This is not a restatement of the deterministic LP trichotomy in
Theorem~\ref{thm:phase-classification}, and it is not covered by standard
LP perturbation theory alone: \citet{Fiacco1983Sensitivity} and
\citet{BonnansShapiro2000Perturbation} justify directional value derivatives
under active-set regularity, but they do not prove that the perturbed
finite program is the sharp causal identified set for a negative-control
law or that a weak-proxy singular direction yields a matching open-class
lower bound.  (b) The concrete consumer is the
proximal OR/IPW/DR workflow of \citet{CuiPuShiMiaoTchetgen2024JASA}; the
modulus tells analysts when a reported point estimate is fragile to a small
bridge-moment violation even if the exact-moment interval is narrow.  The
overview of \citet{TchetgenYingCuiShiMiao2024StatSci} motivates the
bridge-assumption setting but is not treated here as recommending this
diagnostic.

\section{Sanity-check corollaries}
\begin{corollary}[Completeness collapse]\label{cor:complete-collapse}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:endpoint-attain}, if
\(T_P\) is injective on the bridge domain, then \(N_P=\{0\}\),
\(\Delta_P=0\), and Theorem~\ref{thm:support-interval} collapses to the usual
proximal point formula
\[
\Theta_I(P)=\{L_P(h_0)\},
\qquad T_Ph_0=m_P.
\]
This is the finite-support reduction to the point-identification regime of
\citet{MiaoGengTchetgen2018Biometrika} and
\citet{CuiPuShiMiaoTchetgen2024JASA}.
\end{corollary}

\begin{corollary}[Nonunique harmless bridge]\label{cor:nonunique-harmless}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:endpoint-attain}, if
\(N_P\neq\{0\}\) but \(L_P(r)=0\) for every attainable \(r\in N_P\), then
\(\Theta_I(P)\) is still a singleton.  The reduction is clean because the
second display in Theorem~\ref{thm:support-interval} has zero radius even
though the bridge fiber contains more than one element.
\end{corollary}

\begin{example}[Binary-proxy nontrivial interval check]\label{ex:binary-nontrivial}
Take no \(X\), a constant \(Z\), \(W\in\{0,1\}\), and
\(P(W=1)=1/2\).  Let
\(P(W=1\mid A=1)=0.8\), \(P(W=1\mid A=0)=0.2\), and
\(m_P(Z,A=a)=1/2\) for both treatment arms.  For each arm, the bridge
constraint leaves a one-dimensional box segment, and direct substitution
gives
\[
\min_{h\in\calH(P)} L_P(h)=-3/8,\qquad
\max_{h\in\calH(P)} L_P(h)=3/8 .
\]
Thus the reduction is neither point identified nor Manski-trivial; it is the
finite nontrivial interval phase that Theorem~\ref{thm:phase-classification}
must reproduce.
\end{example}

\begin{corollary}[Manski endpoint certificate]\label{cor:manski-cert}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:endpoint-certificates},
if both endpoint LP certificate sets \(\mathsf{Cert}_{-1}(P)\) and
\(\mathsf{Cert}_{1}(P)\) are nonempty, then
\(\underline\theta_P=-1\), \(\overline\theta_P=1\), and
\(\Theta_I(P)=[-1,1]\).  The reduction is a direct endpoint substitution:
the lower and upper support LPs attain the bounded-outcome extremes, so the
finite bridge interval coincides with Manski's full ATE range.
\end{corollary}

\section{Proof-sketch route}
The proof route is finite-dimensional convex geometry.  First rewrite the
bridge equation as a matrix system \(T_Ph=m_P\) and express every bridge as
\(h_0+r\), \(r\in N_P\), with box constraints \(0\le h_0+r\le1\).  Theorem
1 is then the image of a compact polytope under a linear functional, with
endpoints obtained by primal LP or by the dual support function.  Conjecture
1 is the hard step: construct a finite latent response-type distribution
realizing each rational feasible bridge array, using a Caratheodory or
Balke--Pearl table argument while preserving the negative-control exclusions.
Theorem~\ref{thm:phase-classification} then follows by decomposing \(L_P\)
into components on \(\operatorname{range}(T_P^*)\) and \(N_P\), then checking
the boundary cases: injective \(T_P\), nontrivial null space with
\(L_P\)-annihilation, active null directions with interior box slack, and
endpoint bridge arrays that solve the two endpoint LP certificate problems
for \(\theta=-1\) and \(\theta=1\).
Conjecture~\ref{conj:residual-modulus} requires directional sensitivity
analysis of the two endpoint LPs: identify the tangent cone at the upper and
lower optimizers, compute the conic support value \(\Gamma_P\), and prove
that strict complementarity and the fixed support-rank stratum make the
\(o(\varepsilon)\) remainder uniform on a small observable neighborhood.  The matching lower-bound class should be
obtained from a two-proxy finite matrix with one active singular direction
and endpoint optimizers in the relative interior of their active faces.  This
is not asymptotic distribution theory.

\section{Honest scope flags}
Theorem~\ref{thm:support-interval} is only routine conditional on
Assumption~\ref{ass:finite-realization}; it should not be marketed as a
published novelty by itself.  Conjecture~\ref{conj:realization} is the main
sharpness risk, because prior ThmSmith proxy proposals failed precisely when
LP arrays were not shown to correspond to actual causal models.
Theorem~\ref{thm:phase-classification} is a conditional classification, not
the flagship novelty by itself.  Conjecture~\ref{conj:residual-modulus} is
the flagship phase-transition statement and is not yet proved.  The draft
intentionally withdraws the stronger scalar claim that a
positive critical value \(\sigma_\star\) alone separates point, interval, and
Manski regimes; the proposed boundary also depends on the ATE loading and on
attainable box-constrained null directions.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft; prior verdict: none.
\item v2 (revise) -- normalized the phase conjecture by LP width,
replaced circular Manski visibility with endpoint LP certificates, and
narrowed the Santos/Bennett novelty comparison; prior verdict: REVISE.
\item v3 (revise) -- added Manski and Balke--Pearl sharp-bounds anchors,
removed the overstated StatSci diagnostic attribution, and made the
residual-tolerance width functional well posed; prior verdict: REVISE.
\item v4 (revise) -- upgraded the flagship kernel by adding a generic
response-type support bound, splitting the deterministic LP trichotomy into a
conditional theorem, isolating the residual-tolerance modulus conjecture, and
adding a comparison table plus a nontrivial finite interval example; prior
verdict: REVISE.
\item v5 (revise) -- defined the observable bridge-feasibility stratum as a
fixed zero-pattern, fixed-rank, relative-interior face condition and added
the missing optimization sensitivity comparison for the residual-modulus
conjecture; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Andrews(2017)]{Andrews2017JoECompleteness}
Andrews, D. W. K. (2017).
Examples of \(L^2\)-complete and boundedly-complete distributions.
\textit{Journal of Econometrics} 199(2), 213--220.

\bibitem[Balke and Pearl(1997)]{BalkePearl1997JASA}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\textit{Journal of the American Statistical Association} 92(439), 1171--1176.

\bibitem[Bennett et~al.(2023)]{BennettKallusMaoNeweySyrgkanisUehara2023COLT}
Bennett, A., Kallus, N., Mao, X., Newey, W., Syrgkanis, V., and Uehara, M. (2023).
Inference on strongly identified functionals of weakly identified functions.
\textit{Proceedings of Thirty Sixth Conference on Learning Theory}, PMLR 195.

\bibitem[Canay et~al.(2013)]{CanaySantosShaikh2013Econometrica}
Canay, I. A., Santos, A., and Shaikh, A. M. (2013).
On the testability of identification in some nonparametric models with endogeneity.
\textit{Econometrica} 81(6), 2535--2559.

\bibitem[Cui et~al.(2024)]{CuiPuShiMiaoTchetgen2024JASA}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. J. (2024).
Semiparametric proximal causal inference.
\textit{Journal of the American Statistical Association}.

\bibitem[Darolles et~al.(2011)]{DarollesFanFlorensRenault2011Econometrica}
Darolles, S., Fan, Y., Florens, J.-P., and Renault, E. (2011).
Nonparametric instrumental regression.
\textit{Econometrica} 79(5), 1541--1565.

\bibitem[Fiacco(1983)]{Fiacco1983Sensitivity}
Fiacco, A. V. (1983).
\textit{Introduction to Sensitivity and Stability Analysis in Nonlinear Programming}.
Academic Press.

\bibitem[Ghassami et~al.(2023)]{GhassamiShpitserTchetgen2023ProxyPI}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
Partial identification of causal effects using proxy variables.
arXiv:2304.04374.

\bibitem[Miao et~al.(2018)]{MiaoGengTchetgen2018Biometrika}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E. J. (2018).
Identifying causal effects with proxy variables of an unmeasured confounder.
\textit{Biometrika} 105(4), 987--993.

\bibitem[Manski(1990)]{Manski1990AER}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\textit{American Economic Review} 80(2), 319--323.

\bibitem[Bonnans and Shapiro(2000)]{BonnansShapiro2000Perturbation}
Bonnans, J. F. and Shapiro, A. (2000).
\textit{Perturbation Analysis of Optimization Problems}.
Springer.

\bibitem[Santos(2011)]{Santos2011JoE}
Santos, A. (2011).
Instrumental variable methods for recovering continuous linear functionals.
\textit{Journal of Econometrics} 161(2), 129--146.

\bibitem[Tchetgen Tchetgen et~al.(2024)]{TchetgenYingCuiShiMiao2024StatSci}
Tchetgen Tchetgen, E. J., Ying, A., Cui, Y., Shi, X., and Miao, W. (2024).
An introduction to proximal causal inference.
\textit{Statistical Science} 39(3).

\bibitem[Zhang et~al.(2023)]{ZhangLiMiaoTchetgen2023SPL}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. J. (2023).
Proximal causal inference without uniqueness assumptions.
\textit{Statistics and Probability Letters} 198, 109836.
\end{thebibliography}

\end{document}
