% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=eid\_proximal\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{eid\_proximal\_phase} / \texttt{v1}%
  \\ \large\textit{Proximal bridge fibers, sharp ATE ranges, and quadratic selector artifacts}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies the finite-support proximal average treatment effect
\(\theta=\E\{Y(1)-Y(0)\}\) when the observable bridge equation
\(T_Ph=m_P\) has multiple bounded solutions.  The estimand-defining
functional is the sharp bridge-fiber range
\(\Theta_I(P)=\{\ell_P(h):h\in\calH_P\}\), with
\(\ell_P(h)=\E_P\{h(W,1,X)-h(W,0,X)\}\) and
\(\calH_P=\{h\in[0,1]^d:T_Ph=m_P\}\).  Under finite bridge-fiber
sharpness, \(\Theta_I(P)\) is exactly the identified set for the causal
ATE, and it collapses to a point if and only if the ATE loading annihilates
every feasible bridge-null direction.  For any symmetric positive-definite
quadratic penalty \(Q\), the residual-penalized population bridge converges
to the exact-fiber minimizer \(h_Q=\arg\min_{h\in\calH_P}h^\transpose Qh\),
so \(\theta_Q(P)=\ell_P(h_Q)\) is a computable selector inside the sharp
interval, not a new identifying formula.  The Stage -1 conjectures are
resolved as follows: the SPD-exposed and one-dimensional nonradial selector
claims are proved, the unqualified one-dimensional claim is refuted by a
radial fiber counterexample, and the proposed two-by-two negative-control
witness is constructed explicitly.
\end{abstract}

\section{Introduction}
Negative-control proxies are used when measured covariates are not enough to
justify ordinary exchangeability.  In the proximal ATE setup, the outcome
bridge \(h(W,A,X)\) turns the proxy law into an identifying formula only when
the bridge equation carries enough information about the causal loading.
Finite samples and finite dictionaries often make the bridge equation
ill-conditioned or nonunique, so applied analyses commonly stabilize the
bridge by ridge or Tikhonov penalties.  The causal question is whether that
regularized point is invariant over all data-compatible bridges, or whether
it is a penalty-selected value inside a partially identified causal range.

The standard point-identification theorem says that, under proximal
negative-control assumptions and a completeness condition, an outcome bridge
identifies \(\E\{Y(a)\}\) through \(\E\{h(W,a,X)\}\).  Later work shows that
the bridge itself need not be unique if the target functional is still
constant on the bridge fiber.  This note isolates the finite-dimensional
linear-algebra boundary between those two cases.  Once the exact bounded
bridge fiber \(\calH_P\) is fixed, the causal ATE is point identified exactly
when the linear loading \(\ell_P\) is constant on \(\calH_P\); otherwise the
sharp identified set is the interval obtained by optimizing the same loading
over the fiber.

The new content is the selector geometry.  A quadratic regularizer does not
change the causal restrictions; it chooses the unique bridge point closest to
the origin in the inner product induced by \(Q\).  The resulting selected
ATEs are characterized by a normal-cone condition, and in a one-dimensional
nonradial fiber their closure fills the sharp interval.  The note also gives
a concrete binary-\(W\), binary-\(Z\), no-covariate observable law for which
diagonal penalties move the selected proximal ATE over a positive-length
subinterval while the observed law and maintained restrictions are held
fixed.

These formulas are useful because they turn the qualitative warning
"regularization can matter" into computable diagnostics.  An analyst can
evaluate the sharp bridge-fiber interval by a finite linear program, test the
null-annihilator criterion by linear algebra, and evaluate a proposed
quadratic selector by a finite strictly convex quadratic program.

\paragraph{Motivating conjecture(s).}
\begin{conjecture}[Conjecture 1: generic quadratic-selection range for proximal ATEs (NOT YET PROVED)]\label{conj:penalty-separation}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:active-nonunique}, there
is a nonempty open class of finite negative-control laws \(P\) such that the
quadratic-regularizer selection range
\[
\mathcal S_Q(P)=\{\theta_Q(P):Q=Q^\transpose\succ0\}
\]
has nonempty relative interior inside \(\Theta_I(P)\).  More sharply,
\(\overline{\mathcal S_Q(P)}\) contains every ATE value \(\ell_P(h^\star)\)
of an SPD-exposed bridge point \(h^\star\in\calH_P\); in
the one-dimensional bridge-fiber case,
\[
\overline{\mathcal S_Q(P)}=\Theta_I(P).
\]
The range characterization is stable on a neighborhood \(\mathcal U\) of
\(P\) with the same finite proxy stratum and active bridge-face pattern.
Consequently a regularized proximal OR/IPW/DR or minimax bridge point value
whose finite population bridge step has the residual-plus-SPD-quadratic form
can be a genuine regularization artifact: it is a well-defined limit of a
named bridge-solving workflow but not a point-identified causal estimand.
\end{conjecture}

\begin{conjecture}[Conjecture 2: nondegenerate two-by-two negative-control witness (NOT YET PROVED)]\label{conj:binary-witness}
There exists a binary-\(W\), binary-\(Z\), no-covariate finite proximal law
satisfying Assumptions~\ref{ass:finite-bounded}--\ref{ass:generic-stratum}
with \(\Pr_P(A=a,W=w,Z=z)>0\) for all \(a,w,z\),
\(0<\E_P(Y\mid Z=z,A=a)<1\) for all \(z,a\), nonconstant conditional outcome
means across proxy-treatment cells, \(\calH_P\) a one-dimensional line
segment, and \(\ell_P\) nonconstant on that segment.  For this law, diagonal
admissible regularizers
\[
Q_\lambda=\operatorname{diag}(\lambda,1,1,\ldots,1),\qquad \lambda>0,
\]
select a continuous nonconstant curve
\(\lambda\mapsto\theta_{Q_\lambda}(P)\) whose image has positive length
inside \(\Theta_I(P)\).
\end{conjecture}

\section{Related work and positioning}
Miao, Geng, and Tchetgen Tchetgen \cite{MiaoGengTchetgen2018Biometrika}
give the foundational proximal ATE identification theorem with proxy
variables and completeness; this note keeps the same bridge equation but
studies what remains when the bridge is not unique.  Cui, Pu, Shi, Miao, and
Tchetgen Tchetgen \cite{CuiPuShiMiaoTchetgen2024JASA} develop proximal
outcome-regression, inverse-probability, and doubly robust estimators; the
population bridge selector analyzed here is the target those workflows can
approach when their bridge step uses a quadratic residual penalty.  Zhang,
Li, Miao, and Tchetgen Tchetgen \cite{ZhangLiMiaoTchetgen2023SPL} show that
nonunique proximal bridges can still identify counterfactual means; the
null-annihilator criterion below is the finite bridge-fiber version of that
functional-invariance phenomenon.

Bennett, Kallus, Mao, Newey, Syrgkanis, and Uehara
\cite{BennettKallusMaoNeweySyrgkanisUehara2023COLT} study inference on
strongly identified linear functionals of weakly identified nuisance
functions; the present note gives the complementary finite diagnostic for
when the proximal ATE loading is not strongly identified.  Kallus, Mao, and
Uehara \cite{KallusMaoUehara2021MinimaxNC} motivate finite-class
negative-control bridge learning without strong uniqueness assumptions; the
quadratic-selector results apply only to the population special case where
the bridge-solving objective reduces to an SPD quadratic selector on exact
bridge coordinates.  Darolles, Fan, Florens, and Renault
\cite{DarollesFanFlorensRenault2011Econometrica} and Horowitz
\cite{Horowitz2014ARE} provide the inverse-problem background for Tikhonov
regularization; here the penalty is interpreted as a causal selector only
after taking the exact-fiber limit.

Manski \cite{Manski1990AER} is the benchmark for bounded-outcome partial
identification: if proxy restrictions are removed, the ATE falls back to the
natural bounded range.  Ghassami, Shpitser, and Tchetgen Tchetgen
\cite{GhassamiShpitserTchetgen2023ProxyPI} develop proxy-variable partial
identification without completeness; this note is narrower because it
conditions on the exact bridge fiber and asks how regularizers select points
inside its sharp interval.  Canay, Santos, and Shaikh
\cite{CanaySantosShaikh2013Econometrica} motivate reporting such diagnostics
because completeness-type hypotheses are generally not testable in broad
nonparametric classes.  The local project catalogue treats ExactID and
PartialID theorem families as separate theorem substrates; this qid sits at
their boundary by proving exact point identification only in the
null-annihilator case and otherwise exposing a sharp partially identified
bridge-fiber interval.

\section{Formal setup}
Let \(O=(Y,A,W,Z,X)\) have observed law \(P\).  The treatment is binary,
\(\mathcal A=\{0,1\}\); \(Y\in[0,1]\); and \(W,Z,X\) have finite supports.
The latent proximal model contains an unobserved confounder \(U\), potential
outcomes \(Y(0),Y(1)\), consistency \(Y=Y(A)\), latent exchangeability
\((Y(0),Y(1))\perp A\mid(U,X)\), and negative-control exclusions assigning
\(Z\) the treatment-proxy role and \(W\) the outcome-proxy role.

Index the bridge coordinates by \(j=(w,a,x)\) and write
\[
  d=|\mathcal W|\,|\mathcal A|\,|\mathcal X|,
  \qquad
  h=(h(w,a,x))_{(w,a,x)}\in\R^d .
\]
For each \((z,a,x)\) with positive \(P(z,a,x)\), define the observable bridge
operator and moment vector by
\[
  (T_Ph)(z,a,x)=\sum_{w\in\mathcal W} h(w,a,x)P(w\mid z,a,x),
  \qquad
  m_P(z,a,x)=\E_P(Y\mid Z=z,A=a,X=x).
\]
The exact bounded bridge fiber is the compact polytope
\[
  \calH_P=\{h\in[0,1]^d:T_Ph=m_P\}.
\]
The ATE loading is the observable linear functional
\[
  \ell_P(h)
  =
  \sum_{w,x} h(w,1,x)P(w,x)
  -
  \sum_{w,x} h(w,0,x)P(w,x).
\]
Let \(c_P\in\R^d\) denote the coefficient vector for this linear functional,
so that \(\ell_P(h)=c_P^\transpose h\).  The bridge-fiber identified set is
\[
  \Theta_I(P)=\{\ell_P(h):h\in\calH_P\}.
\]
For a symmetric positive-definite matrix \(Q\), define the exact-fiber
quadratic selector
\[
  h_Q(P)=\operatorname*{arg\,min}_{h\in\calH_P}h^\transpose Qh,
  \qquad
  \theta_Q(P)=\ell_P(h_Q(P)),
\]
and the selector range
\[
  \mathcal S_Q(P)=\{\theta_Q(P):Q=Q^\transpose\succ0\}.
\]

\paragraph{Locked parameters.}
This is a partial-identification / exact-functional-identification proposal
with locked tuple
\[
(\texttt{qid},\texttt{specialization}, P, \theta, \text{identifying restrictions},
\text{bounding and selection-range functionals}).
\]
Here \(\texttt{qid}=\texttt{eid\_proximal\_phase}\) and
\(\texttt{specialization}=\texttt{v1}\).  The observable distribution \(P\)
is the finite-support joint law of \(O=(Y,A,W,Z,X)\), with
\(A\in\{0,1\}\), \(Y\in[0,1]\), finite proxy supports for \(W\) and \(Z\),
and finite covariate support for \(X\).  The target parameter is the proximal
average treatment effect \(\theta=\E\{Y(1)-Y(0)\}\).  The identifying
restrictions are consistency, positivity for both treatment arms, latent
proximal exchangeability, negative-control exclusions, existence of a bounded
outcome bridge \(h(W,A,X)\), and the finite bridge-fiber sharpness condition
stated in Assumption~\ref{ass:fiber-sharp}.  The bounding functional is
\[
\Theta_I(P)=\{\ell_P(h):h\in\calH_P\},\qquad
\ell_P(h)=\E_P\{h(W,1,X)-h(W,0,X)\},
\]
where \(\calH_P=\{h\in[0,1]^d:T_Ph=m_P\}\),
\((T_Ph)(z,a,x)=\E_P\{h(W,a,x)\mid Z=z,A=a,X=x\}\), and
\(m_P(z,a,x)=\E_P(Y\mid Z=z,A=a,X=x)\).  The selection functional for an
admissible quadratic regularizer \(Q\succ0\) is
\[
\theta_Q(P)=\ell_P(h_Q),\qquad
h_Q=\operatorname*{arg\,min}_{h\in\calH_P} h^\transpose Qh.
\]
The selection-range functional is
\[
\mathcal S_Q(P)=\{\theta_Q(P):Q=Q^\transpose\succ0\}.
\]
The novelty question is whether \(\mathcal S_Q(P)\) collapses to a singleton
because the ATE is identified, or instead forms a nontrivial subset of the
sharp interval \(\Theta_I(P)\) selected only by the regularization workflow.

\section{Assumptions}
\begin{assumption}[Finite bounded observable law]\label{ass:finite-bounded}
The supports of \(W,Z,X\) are finite, \(A\in\{0,1\}\), and \(Y\in[0,1]\).
Every observable cell \((z,a,x)\) used in \(T_P\) has \(P(z,a,x)>0\), so
\(P(w\mid z,a,x)\) and \(m_P(z,a,x)\) are well defined.  The marginal
probabilities \(P(w,x)\) used in \(\ell_P\) are the observed marginals under
the same law \(P\).
\end{assumption}

\begin{assumption}[Treatment-arm positivity]\label{ass:positivity}
For each \(a\in\{0,1\}\), the proximal latent model has
\(\Pr(A=a\mid U,X)>0\) almost surely on the strata relevant to
\(\E\{Y(a)\}\).  Observable cells with \(P(z,a,x)>0\) are the only cells used
in the finite bridge equations.
\end{assumption}

\begin{assumption}[Proximal negative-control validity]\label{ass:proximal-valid}
There exists a latent variable \(U\) and potential outcomes \(Y(0),Y(1)\)
such that consistency \(Y=Y(A)\), latent exchangeability
\((Y(0),Y(1))\perp A\mid(U,X)\), the outcome-proxy exclusion
\(Y\perp Z\mid(A,U,X)\), and the treatment-proxy exclusion
\(W\perp(A,Z)\mid(U,X)\) hold.  These are the causal restrictions that make
an outcome bridge interpretable as a proximal bridge rather than merely an
observable regression equation.
\end{assumption}

\begin{assumption}[Bounded bridge existence]\label{ass:bridge-exists}
The exact bounded bridge fiber
\[
  \calH_P=\{h\in[0,1]^d:T_Ph=m_P\}
\]
is nonempty.
\end{assumption}

\begin{assumption}[Finite bridge-fiber sharpness]\label{ass:fiber-sharp}
Every \(h\in\calH_P\) is attained by at least one finite latent proximal
model satisfying Assumptions~\ref{ass:finite-bounded}--\ref{ass:proximal-valid}
and inducing the same observed law \(P\); conversely every compatible finite
latent proximal model induces an ATE value \(\ell_P(h)\) for some
\(h\in\calH_P\).
\end{assumption}

\begin{assumption}[Admissible quadratic regularizers]\label{ass:admissible-Q}
The regularizer \(Q\) ranges over symmetric positive-definite \(d\times d\)
matrices.  The choice of \(Q\) is part of the bridge-solving workflow and is
not an additional causal identifying restriction.
\end{assumption}

\begin{assumption}[Generic finite proxy stratum]\label{ass:generic-stratum}
In a neighborhood of the observed law under consideration, the matrix rank of
\(T_P\), the active zero/one box constraints defining the face of
\(\calH_P\), and the support pattern of the finite observable cells are
constant.  The polytope \(\calH_P\) has nonempty relative interior in its
affine hull.
\end{assumption}

\begin{assumption}[ATE-active bridge nonuniqueness]\label{ass:active-nonunique}
There exist \(h_1,h_2\in\calH_P\) such that
\(\ell_P(h_1)\neq\ell_P(h_2)\).  Equivalently, the bridge-fiber sharp
interval \(\Theta_I(P)\) is not a singleton.
\end{assumption}

\section{Estimand-defining functional}
The object evaluated from the observed law is the finite bridge-fiber
bounding functional
\[
  \Theta_I(P)=[\theta_L(P),\theta_U(P)].
\]
Let \(B=[0,1]^d\), let \(T\) be the matrix representation of \(T_P\), let
\(m\) be the vector representation of \(m_P\), and let \(c=c_P\) represent
\(\ell_P(h)=c^\transpose h\).  The endpoints are computed by the two finite
linear programs
\[
\begin{array}{ll}
\theta_L(P)=\min_h & c^\transpose h\\
\text{subject to} & T h=m,\quad 0\le h_j\le 1,\ j=1,\ldots,d,
\end{array}
\qquad
\begin{array}{ll}
\theta_U(P)=\max_h & c^\transpose h\\
\text{subject to} & T h=m,\quad 0\le h_j\le 1,\ j=1,\ldots,d.
\end{array}
\]
Equivalently, enumerate candidate vertices by choosing \(d\) linearly
independent active constraints from the rows of \(T h=m\), the lower bounds
\(h_j=0\), and the upper bounds \(h_j=1\); solve the resulting square linear
systems; retain the feasible solutions; and take the minimum and maximum of
\(c^\transpose h\).  This gives a finite algorithm whose naive enumeration
cost is at most \(\binom{r+2d}{d}\) linear solves of dimension \(d\), where
\(r=\operatorname{rank}(T)\).  Any standard linear-programming method is an
equivalent evaluation procedure with the same decision variables and
constraints.

For a fixed admissible quadratic regularizer \(Q\), the selected point is
computed by the strictly convex quadratic program
\[
\begin{array}{ll}
h_Q(P)=\operatorname*{arg\,min}_h & h^\transpose Qh\\
\text{subject to} & T h=m,\quad 0\le h_j\le 1,\ j=1,\ldots,d,
\end{array}
\qquad
\theta_Q(P)=c^\transpose h_Q(P).
\]
The active-set form is explicit: for each proposed lower-bound set \(L\) and
upper-bound set \(U\), solve the KKT system for the free coordinates
\[
  2Q_{FF}h_F+2Q_{F,L}0+2Q_{F,U}\mathbf 1 + T_F^\transpose\lambda=0,
  \qquad
  T_Fh_F+T_U\mathbf 1=m,
\]
check the free-coordinate inequalities and the complementary normal-cone
inequalities at active bounds, and retain the unique feasible KKT solution.
Strict convexity of \(Q\) makes the retained solution unique.

\paragraph{Verdict on the motivating conjectures.}
Conjecture~\ref{conj:penalty-separation} is confirmed for the
null-annihilator boundary, the exact-fiber Tikhonov limit, the SPD-exposed
point characterization, and the existence of a nonempty open nonradial
one-dimensional class whose selector closure fills the sharp interval.  It
is refuted as written for the unqualified phrase ``in the one-dimensional
bridge-fiber case'': a one-dimensional radial fiber through the origin has a
nontrivial sharp interval but every SPD quadratic selector chooses the same
nearest-to-origin point.  Conjecture~\ref{conj:binary-witness} is confirmed
by the explicit binary-\(W\), binary-\(Z\), no-covariate law in
Proposition~\ref{prop:binary-witness}.

\section{Target causal estimand}
The causal target is the proximal average treatment effect
\[
  \theta=\E\{Y(1)-Y(0)\}.
\]
This is a counterfactual parameter of the latent proximal model, not a
definition in terms of the observed bridge equation.  Under
Assumption~\ref{ass:fiber-sharp}, every compatible latent proximal model with
observed law \(P\) has \(\theta=\ell_P(h)\) for at least one
\(h\in\calH_P\), and every \(h\in\calH_P\) is realized by some compatible
latent proximal model.  Thus the theorem below is a containment and
sharpness statement for \(\theta\): the causal target belongs to
\(\Theta_I(P)\), and every value in that interval is attainable by a
compatible model.  Point identification is the special case in which
\(\Theta_I(P)\) has zero width.

\section{Main theorems}
\begin{proposition}[Sharp bridge-fiber interval and null-annihilator]\label{prop:sharp-null}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:fiber-sharp},
\[
  \Theta_I(P)=\{\ell_P(h):h\in\calH_P\}
  =[\theta_L(P),\theta_U(P)]
\]
is the sharp identified set for \(\theta=\E\{Y(1)-Y(0)\}\), where
\(\theta_L(P)\) and \(\theta_U(P)\) are the finite LP endpoints displayed in
Section~7.  Moreover the following are equivalent:
\[
  \theta_L(P)=\theta_U(P),
  \qquad
  \ell_P(h')=\ell_P(h)\ \text{for all }h,h'\in\calH_P,
  \qquad
  \ell_P(r)=0\ \text{for every feasible difference }r=h'-h .
\]
If \(\ker(T_P)=\{0\}\), the condition holds automatically.  If
\(\ker(T_P)\neq\{0\}\), it can still hold when the ATE loading annihilates
all bridge-null directions that are feasible inside the box.
\end{proposition}
\paragraph{Contribution.}
This proposition is the finite bridge-fiber version of proximal functional
identification under bridge nonuniqueness.  It differs from the classical
complete-bridge theorem by not requiring uniqueness of \(h\); it identifies
the causal ATE exactly when the causal loading is invariant over the
nonunique bridge fiber.

\begin{proposition}[Quadratic selectors and exact-fiber Tikhonov limits]\label{prop:selector-kkt}
Under Assumptions~\ref{ass:finite-bounded}, \ref{ass:bridge-exists}, and
\ref{ass:admissible-Q}, each admissible \(Q\) has a unique selector
\[
  h_Q(P)=\arg\min_{h\in\calH_P}h^\transpose Qh.
\]
Let
\[
  h_{\alpha,Q}(P)=\operatorname*{arg\,min}_{h\in[0,1]^d}
  \{\|T_Ph-m_P\|_2^2+\alpha h^\transpose Qh\}.
\]
Then \(h_{\alpha,Q}(P)\to h_Q(P)\) and
\(\ell_P(h_{\alpha,Q}(P))\to\theta_Q(P)\) as \(\alpha\downarrow0\).  A point
\(h^\star\in\calH_P\) is selected by \(Q\) if and only if
\[
  -2Qh^\star\in N_{\calH_P}(h^\star),
  \qquad
  N_{\calH_P}(h^\star)=\{n:n^\transpose(v-h^\star)\le0
  \text{ for all }v\in\calH_P\}.
\]
Consequently every SPD-exposed bridge point belongs to the exact quadratic
selector range, and its ATE value belongs to \(\mathcal S_Q(P)\).
\end{proposition}
\paragraph{Contribution.}
This proposition identifies the population object selected by a
residual-plus-quadratic bridge workflow.  The conclusion is not that
\(\theta_Q(P)\) is causally identified; it is that the selected value is a
computable point in the sharp bridge-fiber interval and is governed by a
normal-cone certificate.

\begin{proposition}[One-dimensional selector phase]\label{prop:onedim}
Suppose \(\calH_P=\{h_0+tr:t\in[L,U]\}\) with \(L<U\), \(r\neq0\), and
\(\ell_P(r)\neq0\).  For each admissible \(Q\), the selected coordinate is
\[
  t_Q
  =
  \Pi_{[L,U]}
  \left(-\frac{r^\transpose Qh_0}{r^\transpose Qr}\right),
\]
where \(\Pi_{[L,U]}\) is Euclidean projection onto the interval.  If the
affine line \(\{h_0+tr:t\in\R\}\) is not contained in \(\operatorname{span}(r)\),
then every interior \(t\in(L,U)\) is selected by some SPD \(Q\), and
\[
  \overline{\mathcal S_Q(P)}=\Theta_I(P).
\]
If the affine line is contained in \(\operatorname{span}(r)\), the selected
coordinate \(t_Q\) is independent of \(Q\), so the selector range can be a
singleton even when \(\Theta_I(P)\) has positive length.
\end{proposition}
\paragraph{Contribution.}
This is the nearest correct one-dimensional version of
Conjecture~\ref{conj:penalty-separation}.  It proves the generic nonradial
case and gives the precise radial obstruction, so the original unqualified
one-dimensional statement is only partially correct.

\begin{proposition}[Binary negative-control witness]\label{prop:binary-witness}
There is a binary-\(W\), binary-\(Z\), no-covariate finite observable law
satisfying the support and generic-stratum conditions of
Conjecture~\ref{conj:binary-witness} such that, conditional on the maintained
finite bridge-fiber sharpness restriction, the exact bridge fiber is
\[
  \calH_P=\{(t,1-t,1/5,4/5):0\le t\le1\},
\]
in coordinate order \((h(0,0),h(1,0),h(0,1),h(1,1))\).  Its sharp ATE
interval is
\[
  \Theta_I(P)=\left[-\frac1{40},\,\frac1{10}\right].
\]
For diagonal penalties
\[
  Q_\lambda=\operatorname{diag}(\lambda,1,1,1),\qquad \lambda>0,
\]
the selected coordinate is \(t_\lambda=1/(1+\lambda)\) and
\[
  \theta_{Q_\lambda}(P)
  =
  -\frac1{40}+\frac{1}{8(1+\lambda)}.
\]
Thus \(\lambda\mapsto\theta_{Q_\lambda}(P)\) is continuous and nonconstant,
with positive-length image inside \(\Theta_I(P)\), and Conjecture~\ref{conj:binary-witness}
is confirmed.
\end{proposition}
\paragraph{Contribution.}
The witness shows that penalty dependence is not an infinite-dimensional
pathology.  It occurs in the smallest proxy table with binary treatment,
binary treatment proxy, binary outcome proxy, and no covariates.

\section{Interpretation}
The bridge equation \(T_Ph=m_P\) is an observable restriction.  The causal
interpretation of its solutions comes from the proximal validity assumptions
and, for sharpness, from Assumption~\ref{ass:fiber-sharp}.  If those
assumptions hold and the ATE loading is constant on \(\calH_P\), then every
compatible latent model gives the same ATE, even when several bridges solve
the equation.  This is exact identification of the target, not merely a
choice of bridge norm.

If the ATE loading is not constant on \(\calH_P\), the sharp interval
\(\Theta_I(P)\) is the correct causal object.  A quadratic regularizer then
selects one point in that interval by choosing a bridge closest to zero in a
chosen inner product.  Changing \(Q\) can move the reported ATE without
changing the observed law or the proximal restrictions.  In that case the
selected value \(\theta_Q(P)\) is a well-defined population output of a
workflow, but it is not a point-identified causal estimand.

The key support conditions are the positivity of the treatment arms and the
observable support needed to define \(P(w\mid z,a,x)\) and
\(\E(Y\mid z,a,x)\).  If observable proxy cells are missing, the finite
operator \(T_P\) is not defined on those rows, and any formula using them is
a different estimand.  If proximal negative-control validity fails, the same
linear algebra still describes bridge solutions, but it no longer carries
the causal interpretation \(Y(a)\mapsto h(W,a,X)\).  If finite
bridge-fiber sharpness fails, the LP interval remains an outer bridge range,
but it need not be the sharp causal identified set.

The bound collapses to point identification under completeness
\(\ker(T_P)=\{0\}\) or, more generally, under the null-annihilator condition.
It widens toward the natural Manski bounded-outcome range when the bridge
equation supplies little information about the ATE loading.  The tightening
work is done by the observable bridge equations and the box restriction
\([0,1]^d\), while the selection of a point inside the tightened interval is
done by \(Q\), not by an additional identifying assumption.

\section{Step-by-step proof}
\begin{lemma}[Bridge-fiber image is an interval]\label{lem:image-interval}
Under Assumptions~\ref{ass:finite-bounded} and \ref{ass:bridge-exists},
\(\calH_P\) is a nonempty compact convex polytope and
\(\ell_P(\calH_P)\) is a compact interval.
\end{lemma}
\begin{proof}
The set \([0,1]^d\) is compact and convex.  The equation \(T_Ph=m_P\) is a
finite system of linear equalities, so its intersection with \([0,1]^d\) is
a compact convex polytope; nonemptiness is Assumption~\ref{ass:bridge-exists}.
The linear map \(\ell_P\) is continuous, so its image is compact.  The image
of a convex set under a linear map into \(\R\) is convex, hence an interval.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:sharp-null}]
By Assumption~\ref{ass:fiber-sharp}, every compatible latent proximal model
with observed law \(P\) induces an ATE value \(\ell_P(h)\) for some
\(h\in\calH_P\), and every \(h\in\calH_P\) is realized by such a model.  The
set of all compatible causal ATE values is therefore exactly
\(\{\ell_P(h):h\in\calH_P\}\).  By Lemma~\ref{lem:image-interval}, this set
is the compact interval \([\theta_L(P),\theta_U(P)]\).  The endpoint formulas
in Section~7 are precisely the finite LPs that minimize and maximize the
linear functional \(\ell_P(h)=c^\transpose h\) over the same feasible set.

The interval is a singleton if and only if \(\ell_P(h')=\ell_P(h)\) for all
feasible \(h,h'\).  Since \(\ell_P\) is linear, this is equivalent to
\(\ell_P(h'-h)=0\) for every feasible difference \(h'-h\).  If
\(\ker(T_P)=\{0\}\), the affine equation \(T_Ph=m_P\) has at most one
solution, so the condition holds automatically.  If the kernel is nontrivial,
the same equivalence shows that point identification still holds exactly
when the ATE loading vanishes on all kernel directions that are feasible
inside the box.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:selector-kkt}]
Fix \(Q\succ0\).  The map \(h\mapsto h^\transpose Qh\) is continuous and
strictly convex.  Since \(\calH_P\) is nonempty and compact, a minimizer over
\(\calH_P\) exists; strict convexity makes it unique.

For the residual-penalized problem, the feasible set \([0,1]^d\) is compact,
so \(h_{\alpha,Q}\) exists.  Let \(h_Q\) be the exact-fiber minimizer.  Since
\(h_Q\in\calH_P\),
\[
  \|T_Ph_{\alpha,Q}-m_P\|_2^2+\alpha h_{\alpha,Q}^\transpose Qh_{\alpha,Q}
  \le
  \alpha h_Q^\transpose Qh_Q .
\]
Thus \(\|T_Ph_{\alpha,Q}-m_P\|_2^2\le\alpha h_Q^\transpose Qh_Q\to0\), and
also \(h_{\alpha,Q}^\transpose Qh_{\alpha,Q}\le h_Q^\transpose Qh_Q\).  Any
sequence \(\alpha_n\downarrow0\) has a convergent subsequence because
\([0,1]^d\) is compact.  If the subsequential limit is \(h^\star\), the
residual convergence gives \(T_Ph^\star=m_P\), so \(h^\star\in\calH_P\).  By
continuity of the quadratic form,
\[
  (h^\star)^\transpose Qh^\star\le h_Q^\transpose Qh_Q.
\]
Uniqueness of the exact-fiber minimizer forces \(h^\star=h_Q\).  Every
subsequence has the same limit, hence \(h_{\alpha,Q}\to h_Q\), and continuity
of \(\ell_P\) gives convergence of selected ATEs.

For the normal-cone statement, the differentiable convex first-order
condition for minimizing \(h^\transpose Qh\) over the convex set \(\calH_P\)
is
\[
  (2Qh^\star)^\transpose(v-h^\star)\ge0
  \quad\text{for every }v\in\calH_P.
\]
This is exactly \(-2Qh^\star\in N_{\calH_P}(h^\star)\) under the displayed
definition of the normal cone.  Strict convexity again gives uniqueness.  If
an SPD-exposed point satisfies this condition for some \(Q\), it is therefore
the selected point for that \(Q\), and its ATE value is in
\(\mathcal S_Q(P)\).
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:onedim}]
On the line \(h(t)=h_0+tr\),
\[
  h(t)^\transpose Qh(t)
  =
  h_0^\transpose Qh_0+2t\,r^\transpose Qh_0+t^2 r^\transpose Qr .
\]
Since \(Q\succ0\) and \(r\neq0\), \(r^\transpose Qr>0\).  The unconstrained
minimizer is
\[
  t^\circ_Q=-\frac{r^\transpose Qh_0}{r^\transpose Qr},
\]
and the constrained minimizer over \([L,U]\) is its projection
\(\Pi_{[L,U]}(t^\circ_Q)\).

Fix an interior \(t\in(L,U)\) and write \(x=h_0+tr\).  This \(t\) is the
unconstrained minimizer exactly when \(r^\transpose Qx=0\).  If the affine
line is not contained in \(\operatorname{span}(r)\), then \(x\) and \(r\) are
linearly independent for every \(t\).  Choose an inner product in which
\(x\) is orthogonal to \(r\), and represent that inner product by an SPD
matrix \(Q\); then \(r^\transpose Qx=0\), so the chosen interior \(t\) is
selected.  Because every interior \(t\) is selected and endpoint values are
limits of interior values, the closure of selected ATE values is the full
interval \(\ell_P(\calH_P)=\Theta_I(P)\).

If the affine line is contained in \(\operatorname{span}(r)\), then
\(h_0=s_0r\) for some scalar \(s_0\).  The objective becomes
\((s_0+t)^2 r^\transpose Qr\), so the constrained minimizer is the projection
of \(-s_0\) onto \([L,U]\), independent of \(Q\).  When
\(\ell_P(r)\neq0\) and \(L<U\), the sharp interval has positive length, but
the selector range is a singleton.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:binary-witness}]
Define the observable law as follows.  Let \(P(A=0)=P(A=1)=1/2\).  Given
\(A=0\), let \(P(Z=0\mid A=0)=1/2\) and
\[
  P(W=0\mid Z=0,A=0)=P(W=0\mid Z=1,A=0)=1/2 .
\]
Given \(A=1\), let \(P(Z=0\mid A=1)=3/4\) and
\[
  P(W=0\mid Z=0,A=1)=1/4,\qquad
  P(W=0\mid Z=1,A=1)=3/4 .
\]
Let \(Y\) be Bernoulli conditional on \((Z,A)\), with conditional means
\[
  m_P(z,0)=1/2,\qquad
  m_P(0,1)=13/20,\qquad
  m_P(1,1)=7/20 .
\]
All joint cells \((A,W,Z)\) have positive probability, all outcome means lie
strictly between zero and one, and the conditional outcome means are
nonconstant.

In coordinate order \((h(0,0),h(1,0),h(0,1),h(1,1))\), the bridge equations
are
\[
  \frac12 h(0,0)+\frac12 h(1,0)=\frac12,
\]
for both \(z\) in arm \(A=0\), and
\[
  \frac14 h(0,1)+\frac34 h(1,1)=\frac{13}{20},
  \qquad
  \frac34 h(0,1)+\frac14 h(1,1)=\frac{7}{20}.
\]
The arm \(A=1\) equations have the unique solution
\((h(0,1),h(1,1))=(1/5,4/5)\), while the arm \(A=0\) equation gives
\((h(0,0),h(1,0))=(t,1-t)\) with \(0\le t\le1\).  Hence
\[
  \calH_P=\{(t,1-t,1/5,4/5):0\le t\le1\}.
\]
The unconditional proxy marginal is
\[
  P(W=0)=\frac{7}{16},\qquad P(W=1)=\frac{9}{16}.
\]
Therefore
\[
  \ell_P(h(t))
  =
  \frac{7}{16}\frac15+\frac{9}{16}\frac45
  -
  \left\{\frac{7}{16}t+\frac{9}{16}(1-t)\right\}
  =
  -\frac1{40}+\frac{t}{8}.
\]
The sharp interval over \(t\in[0,1]\) is
\([-1/40,1/10]\).

For \(Q_\lambda=\operatorname{diag}(\lambda,1,1,1)\), only the first two
coordinates vary along the fiber, and the objective is
\[
  \lambda t^2+(1-t)^2+\text{constant}.
\]
Its unique minimizer is \(t_\lambda=1/(1+\lambda)\).  Substitution gives
\[
  \theta_{Q_\lambda}(P)
  =
  -\frac1{40}+\frac{1}{8(1+\lambda)}.
\]
As \(\lambda\) ranges over \((0,\infty)\), \(t_\lambda\) ranges over
\((0,1)\), so the selected ATEs form the positive-length open interval
\((-1/40,1/10)\).  The maintained finite bridge-fiber sharpness assumption
then gives the causal sharpness interpretation claimed in the proposition.
\end{proof}

\section{Sanity checks}
\begin{itemize}[leftmargin=*]
\item \textbf{Completeness corner.}  If \(T_P\) has full column rank on the
bridge coordinates, then \(\calH_P\) is a singleton whenever it is nonempty.
The sharp interval collapses and every quadratic selector returns the same
ATE.  This is the finite-support reduction of the classical complete
proximal bridge theorem.

\item \textbf{Strong functional identification with nonunique bridges.}  If
there exists a vector \(\varphi\) such that
\(\ell_P(h)=\varphi^\transpose T_Ph\) on the affine hull of \(\calH_P\),
then \(\ell_P\) is constant over all solutions to \(T_Ph=m_P\).  Thus the
bridge may be nonunique while the ATE is point identified.

\item \textbf{Random-treatment special case.}  If treatment is randomized
relative to the latent confounder so that the ordinary arm means identify the
counterfactual means, and the bridge fiber forces
\(h(W,a,X)\) to have observed mean \(\E(Y\mid A=a)\), then the formula
reduces to the usual ATE
\(\E(Y\mid A=1)-\E(Y\mid A=0)\).  This is a corner case in which the proxy
bridge is unnecessary.

\item \textbf{Null-effect corner.}  If \(\ell_P(h)=0\) for every
\(h\in\calH_P\), then the sharp interval is \(\{0\}\).  The causal null is
identified even if the bridge itself is not unique.

\item \textbf{No-restriction bounded-outcome fallback.}  If the bridge
equation is removed and the only remaining information is \(0\le h\le1\),
then \(\ell_P([0,1]^d)=[-1,1]\).  This matches the natural bounded-outcome
Manski fallback for an ATE with both potential-outcome means in \([0,1]\).

\item \textbf{Binary witness corner.}  The witness in
Proposition~\ref{prop:binary-witness} has one-dimensional nonradial fiber,
so Proposition~\ref{prop:onedim} predicts that the closure of SPD-selected
ATEs fills the sharp interval.  The diagonal subfamily already fills the
open interval.
\end{itemize}

\section{Counterexample or minimality check}
The unqualified one-dimensional part of Conjecture~\ref{conj:penalty-separation}
fails without the nonradial condition.  Consider the bridge fiber
\[
  C=\{tr:0\le t\le1\}\subset[0,1]^d
\]
for a nonzero vector \(r\ge0\), and take an ATE loading with
\(\ell(r)\neq0\).  This is a one-dimensional bridge fiber with a
positive-length sharp interval \(\ell(C)\).  For any \(Q\succ0\),
\[
  (tr)^\transpose Q(tr)=t^2 r^\transpose Qr
\]
is minimized at \(t=0\), independent of \(Q\).  Hence
\(\mathcal S_Q(P)\) is a singleton although \(\Theta_I(P)\) is not.

The nearest correct statement is Proposition~\ref{prop:onedim}: a
one-dimensional fiber has full selector closure when its affine hull is not
the radial line through the origin.  This condition is generic in the
fixed-rank, fixed-face class because a small perturbation of a nonradial
affine line remains nonradial, and the property \(\ell_P(r)\neq0\) is also
open.  The binary witness in Proposition~\ref{prop:binary-witness} lies in
that stable nonradial class.

The other minimality conditions have distinct roles.  Without
Assumption~\ref{ass:bridge-exists}, the bridge-fiber functional is empty.
Without the support part of Assumption~\ref{ass:finite-bounded}, the
conditional rows of \(T_P\) may be undefined.  Without
Assumption~\ref{ass:proximal-valid}, the same LP remains a bridge-equation
calculation but does not identify or bound a causal ATE.  Without
Assumption~\ref{ass:fiber-sharp}, \(\Theta_I(P)\) is at most an outer bridge
range; sharp causal attainability is no longer guaranteed.

\section{Formalization checklist}
\paragraph{Observable finite objects.}
\begin{itemize}[leftmargin=*]
\item Finite supports \(\mathcal W,\mathcal Z,\mathcal X\) and binary
\(\mathcal A=\{0,1\}\).
\item Observed law \(P\) on \((Y,A,W,Z,X)\), with \(Y\in[0,1]\).
\item Conditional probability rows \(P(w\mid z,a,x)\) and conditional means
\(m_P(z,a,x)=\E_P(Y\mid z,a,x)\) on positive observable cells.
\item Matrix \(T_P:\R^d\to\R^r\), vector \(m_P\in\R^r\), box
\([0,1]^d\), bridge polytope \(\calH_P=\{h:T_Ph=m_P,0\le h\le1\}\).
\item Loading vector \(c_P\) for \(\ell_P(h)=c_P^\transpose h\), with
coordinates \(+P(w,x)\) on arm \(a=1\) and \(-P(w,x)\) on arm \(a=0\).
\end{itemize}

\paragraph{Probabilistic and causal assumptions.}
\begin{itemize}[leftmargin=*]
\item Consistency \(Y=Y(A)\).
\item Latent exchangeability \((Y(0),Y(1))\perp A\mid(U,X)\).
\item Negative-control exclusions \(Y\perp Z\mid(A,U,X)\) and
\(W\perp(A,Z)\mid(U,X)\).
\item Treatment-arm positivity \(\Pr(A=a\mid U,X)>0\).
\item Bounded bridge existence \(\calH_P\neq\emptyset\).
\item Finite bridge-fiber sharpness: compatible causal ATE values are
exactly \(\ell_P(h)\) for \(h\in\calH_P\).
\end{itemize}

\paragraph{Deterministic identities and lemmas.}
\begin{itemize}[leftmargin=*]
\item Compact-convex polytope lemma: intersection of a box with finitely
many affine equalities is compact and convex.
\item Linear-image lemma: the image of a compact convex set under a real
linear functional is a compact interval.
\item LP endpoint identity: minimizing and maximizing \(c^\transpose h\)
over \(T h=m,0\le h\le1\) gives the sharp interval endpoints.
\item Null-annihilator equivalence:
\(\ell\) is constant on \(\calH\) if and only if
\(\ell(h'-h)=0\) for all feasible pairs \(h,h'\in\calH\).
\item Strict convexity: \(Q\succ0\) implies \(h^\transpose Qh\) has a unique
minimizer over a nonempty compact convex set.
\item Exact-fiber limit: minimizers of
\(\|Th-m\|^2+\alpha h^\transpose Qh\) over the box converge to the
minimum-\(Q\)-norm point in the exact fiber as \(\alpha\downarrow0\).
\item Normal-cone KKT identity:
\(h^\star\) minimizes \(h^\transpose Qh\) over \(\calH\) if and only if
\(-2Qh^\star\in N_{\calH}(h^\star)\).
\item One-dimensional quadratic identity:
on \(h(t)=h_0+tr\), the selected coordinate is
\(\Pi_{[L,U]}[-(r^\transpose Qh_0)/(r^\transpose Qr)]\).
\item SPD orthogonalization fact: for linearly independent \(x,r\in\R^d\),
there exists \(Q\succ0\) with \(r^\transpose Qx=0\).
\end{itemize}

\paragraph{Witness arithmetic.}
\begin{itemize}[leftmargin=*]
\item Binary witness bridge equations, solution fiber
\(\{(t,1-t,1/5,4/5):0\le t\le1\}\), and marginal proxy weights
\(P(W=0)=7/16\), \(P(W=1)=9/16\).
\item Witness loading identity
\(\ell_P(h(t))=-1/40+t/8\).
\item Diagonal selector identity
\(t_\lambda=1/(1+\lambda)\) for \(Q_\lambda=\operatorname{diag}(\lambda,1,1,1)\).
\end{itemize}

\section{Conclusion and references}
The proximal ATE is point identified from a nonunique finite bridge equation
exactly when the ATE loading annihilates all feasible bridge-null directions.
When that condition fails, the sharp causal object under finite
bridge-fiber sharpness is the computable LP interval
\(\Theta_I(P)\), not the point selected by a bridge penalty.  Quadratic
regularization selects the unique minimum-\(Q\)-norm bridge, and its value is
governed by a normal-cone certificate.  The one-dimensional selector range
fills the sharp interval in the stable nonradial case, but a radial fiber
shows that the unqualified version of that claim is false.  The binary proxy
witness demonstrates concretely that changing a diagonal bridge penalty can
move the selected proximal ATE over a positive-length interval without
changing the observed law.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{BennettKallusMaoNeweySyrgkanisUehara2023COLT}
Bennett, A., Kallus, N., Mao, X., Newey, W., Syrgkanis, V., and Uehara, M.
(2023).
Inference on strongly identified functionals of weakly identified functions.
\emph{Proceedings of Machine Learning Research}, 195:2265--2265.

\bibitem{CanaySantosShaikh2013Econometrica}
Canay, I. A., Santos, A., and Shaikh, A. M. (2013).
On the testability of identification in some nonparametric models with
endogeneity.
\emph{Econometrica}, 81(6):2535--2559.

\bibitem{CuiPuShiMiaoTchetgen2024JASA}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. J. (2024).
Semiparametric proximal causal inference.
\emph{Journal of the American Statistical Association}, 119(546):1348--1359.

\bibitem{DarollesFanFlorensRenault2011Econometrica}
Darolles, S., Fan, Y., Florens, J.-P., and Renault, E. (2011).
Nonparametric instrumental regression.
\emph{Econometrica}, 79(5):1541--1565.

\bibitem{GhassamiShpitserTchetgen2023ProxyPI}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
Partial identification of causal effects using proxy variables.
\emph{arXiv:2304.04374}.

\bibitem{Horowitz2014ARE}
Horowitz, J. L. (2014).
Ill-posed inverse problems in economics.
\emph{Annual Review of Economics}, 6:21--51.

\bibitem{KallusMaoUehara2021MinimaxNC}
Kallus, N., Mao, X., and Uehara, M. (2021).
Causal inference under unmeasured confounding with negative controls: A
minimax learning approach.
\emph{arXiv:2103.14029}.

\bibitem{Manski1990AER}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review}, 80(2):319--323.

\bibitem{MiaoGengTchetgen2018Biometrika}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E. J. (2018).
Identifying causal effects with proxy variables of an unmeasured confounder.
\emph{Biometrika}, 105(4):987--993.

\bibitem{ZhangLiMiaoTchetgen2023SPL}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. J. (2023).
Proximal causal inference without uniqueness assumptions.
\emph{Statistics \& Probability Letters}, 198:109836.
\end{thebibliography}

\end{document}
