% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_dose\_response\_iv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_dose\_response\_iv} / \texttt{v1}%
  \\ \large\textit{Adjacent-rank copula tubes for continuous-IV derivative-sign partial identification}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification anchor.  The locked tuple is
\[
(\texttt{pid\_dose\_response\_iv},\texttt{v1},
P,\theta,\mathcal R_{\Gamma,\rho,\eta}^{\mathrm{iv\text{-}tube}},B_{\Gamma,\rho,\eta}^{\mathrm{slope}}).
\]
Here \(P\) is the observable law of \((Y,A,Z,X)\), with bounded outcome \(Y\in[0,1]\), continuous dose \(A\in[a_0,a_2]\), continuous instrument \(Z\in\mathcal Z\subset\mathbb R\), and observed covariates \(X\).  The parameter is the adjacent-dose rank-slice finite-difference
\[
\theta_{\tau,h}=\frac{\E\{Y(a_1)-Y(a_0)\mid R_{01}\in\tau\}}{h},
\quad a_1=a_0+h,
\]
where \(R_{01}:=U_{a_0}\) is the baseline adjacent-dose rank coordinate, \(U_a=F^-_{a,X}\{Y(a)\}+V_a(F_{a,X}\{Y(a)\}-F^-_{a,X}\{Y(a)\})\) is the randomized conditional probability-integral-transform rank with an independent tie-breaker \(V_a\sim\mathrm{Unif}(0,1)\), and \(\tau\subset[0,1]\) is a fixed interval with positive length.  Equivalently, when \(Y(a)\mid X\) is continuous, \(U_a=F_{a,X}\{Y(a)\}\).  The identifying restrictions \(\mathcal R_{\Gamma,\rho,\eta}^{\mathrm{iv\text{-}tube}}\) are consistency, positivity for \(A\) and \(Z\), well-defined randomized ranks, exclusion and conditional independence of \(Z\) from the latent potential-outcome array, a continuous-treatment marginal sensitivity bound \(\Gamma\) on dose-specific hidden-confounding tilts, a finite vector \(m(Y(a_j),X)\in\mathbb R^K\) of IV moment-balance restrictions with tolerance \(\eta\), and an adjacent-rank copula tube requiring the copula of \((U_{a_0},U_{a_1})\) within \(X\)-strata to lie within sup-norm distance \(\rho\) of the comonotone copula on \(\tau\times[0,1]\).  Thus the target conditions on the explicitly pinned coordinate \(R_{01}=U_{a_0}\), while the copula \(C_{01,x}\) controls how the adjacent rank \(U_{a_1}\) can be paired with it.  The bounding functional is the sharp interval
\[
B_{\Gamma,\rho,\eta}^{\mathrm{slope}}(P;\tau,h)=
\left[\inf_{Q\in\mathcal M(P,\mathcal R_{\Gamma,\rho,\eta}^{\mathrm{iv\text{-}tube}})}\theta_{\tau,h}(Q),
\sup_{Q\in\mathcal M(P,\mathcal R_{\Gamma,\rho,\eta}^{\mathrm{iv\text{-}tube}})}\theta_{\tau,h}(Q)\right],
\]
where \(\mathcal M(P,\mathcal R_{\Gamma,\rho,\eta}^{\mathrm{iv\text{-}tube}})\) is the set of full-data laws with observed margin \(P\) satisfying the stated restrictions.

\begin{abstract}
Continuous-dose sensitivity analyses now give sharp pointwise bands for average potential outcomes under hidden confounding, but local scientific questions often concern the sign of a marginal dose-response derivative.  This proposal asks whether a continuous instrument plus a bounded adjacent-rank copula tube can certify the sign of a baseline-rank-slice finite difference even when the two one-dose rank-slice marginal bands overlap enough to leave the ordinary marginal slope sign ambiguous.  The routine theorem is a finite sharp-bounds representation: after discretizing the adjacent rank slice and the instrument support, the identified slope interval is the projection of one joint coupling problem rather than a product of dosewise rank-slice intervals.  The flagship conjecture is that the adjacent-rank copula creates a strict sign phase transition: for small enough copula radius \(\rho\) and informative enough IV moment tolerance \(\eta\), the sharp lower slope bound is positive although the one-dose rank-slice slope interval straddles zero.  Resolving this would turn rank-dependence information into an auditable local derivative-sign certificate for continuous treatments under unmeasured confounding.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Many continuous-treatment decisions are local: whether one more unit of exposure helps or harms a clinically relevant subgroup, whether a policy subsidy has a positive marginal return near the current level, or whether a regulator can certify that a small exposure increase is damaging.  Pointwise sensitivity bands for the dose-response curve are useful, but they can be inconclusive for derivatives because two dosewise adversaries can be chosen independently.  If adjacent potential-outcome ranks cannot be paired arbitrarily, and if an instrument supplies extra marginal-distribution information, the local derivative sign may be more identifiable than the dosewise mean envelope suggests.

\paragraph{The main finding (proposed).}
Theorem~\ref{thm:finite-coupling-bound} states the bookkeeping result: for fixed adjacent doses, rank bins, instrument bins, and IV moment functions, sharp partial identification of the baseline-rank-slice slope is a finite linear-programming projection over one joint coupling of \(Y(a_0)\), \(Y(a_1)\), latent confounding tilts, and IV-compatible margins.  Conjecture~\ref{conj:sign-certificate} is the novelty kernel: there are observable laws for which the one-dose rank-slice sensitivity intervals imply a finite-difference interval containing zero, while the adjacent-rank copula tube and IV moment restrictions force the sharp baseline-rank-slice finite-difference interval to be strictly positive.  Conjecture~\ref{conj:rho-threshold} records the expected boundary form: the lower slope endpoint is monotone nondecreasing as the copula tube tightens, and crosses zero at a finite critical radius in a two-rank-bin witness.

\paragraph{What is new.}
The closest published comparator is \citet{BaitairianSebastienJreichKatsahianGuilloux2025}, which establishes sharp APO bounds under a continuous sensitivity model, together with continuous-dose hidden-confounding methods such as \citet{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022}, \citet{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023}, and \citet{DalalTchetgenTchetgen2025}.  The closest derivative-target comparator is \citet{Zhang2025ADE}, which gives sensitivity bounds for the average derivative effect under an odds-ratio restriction on the latent versus observed generalized propensity score.  \citet{ChernozhukovFernandezValHanWuthrich2024} is the closest IV-plus-copula comparator: it uses local copula invariance to point-identify average and quantile effects for discrete and continuous treatments with a binary instrument.  Those papers do not study a partially identified target whose value depends on the joint law of adjacent potential-outcome ranks after conditioning on the pinned baseline rank \(R_{01}=U_{a_0}\).  The proposed gap is not a generic shape restriction or an ADE sensitivity band: it is the incompatibility of independently sharp one-dose rank-slice adversaries with a single adjacent-rank copula tube and IV-compatible moment margins.

\paragraph{How it positions in the literature.}
This is a partial-identification proposal in the continuous-treatment sensitivity, IV, and copula-bounds cluster.  It uses the continuous-IV literature as marginal information about potential-outcome distributions, and the treatment-effect-distribution literature as the warning that pointwise sharp bounds need not be uniformly or jointly sharp.  It deliberately avoids the panel / linear-projection cluster: the object is a sharp identified interval for a continuous-dose rank-slice derivative, not a regression coefficient.

\section{Related work}
\citet{BaitairianSebastienJreichKatsahianGuilloux2025} is the closest continuous-sensitivity comparator because it gives sharp bounds for the average potential outcome under a continuous sensitivity model; this proposal changes the target from a pointwise APO to a baseline-rank finite-difference requiring one cross-dose copula.  \citet{Zhang2025ADE} is the closest derivative-target sensitivity comparator because it derives closed-form bounds for the average derivative effect under a generalized-propensity odds-ratio sensitivity model; this proposal instead asks for a rank-slice adjacent finite-difference sign under IV-compatible copula tubes, so an ADE band can remain ambiguous while the baseline-rank-slice sign is certified.  \citet{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022} introduces the continuous-treatment marginal sensitivity model and scalable bounds for continuous-valued interventions; the present proposal borrows the hidden-confounding radius idea but adds IV moment margins and rank-copula dependence restrictions.  \citet{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023} develops partial identification for average and conditional average continuous-dose effects under hidden confounding; the gap is that their dose-response envelope does not characterize rank-slice slopes.  \citet{DalalTchetgenTchetgen2025} extends Rosenbaum and marginal sensitivity frameworks to endogenous continuous exposures with dose-varying sensitivity functions; the proposed result asks whether a local sign can be certified by rank compatibility even when their global curve envelope remains sign-ambiguous.

\citet{Kasy2014} studies continuous IV triangular systems with unrestricted heterogeneity and states a rich-support point-identification theorem plus partial identification under insufficient support, but the corrigendum by \citet{HoderleinHolzmannKasyMeister2017} explains that the central theorem needs the stronger one-dimensional monotone first-stage heterogeneity condition used by \citet{ImbensNewey2009}; this proposal works in the insufficient-support / hidden-confounding regime and asks for a derivative-sign partial-ID certificate rather than relying on that point-ID claim.  \citet{Torgovitsky2015} shows that scalar heterogeneity restrictions can point-identify nonseparable continuous-treatment models with small-support instruments; the contrast here is that no scalar heterogeneity point-identification assumption is imposed.  \citet{DHaultfoeuilleFevrier2015} provides a discrete-instrument triangular point-identification route under monotonicity and support/intersection conditions; the present proposal treats failures of such point-ID conditions as a partial-ID problem with copula dependence restrictions.  \citet{ChernozhukovHansen2005} is the quantile-IV benchmark; it motivates rank-sensitive IV targets, while this proposal bounds a rank-slice potential-outcome derivative rather than point-identifying a structural quantile function.  \citet{ChernozhukovFernandezValHanWuthrich2024} is especially close because it combines binary instruments with a local copula invariance restriction to identify average and quantile treatment effects for discrete and continuous treatments; the distinction is that this proposal keeps the continuous-IV sensitivity model partially identified and studies an adjacent-rank slope sign under a copula tube, not point identification under invariance.  Average-derivative estimands for continuous treatments motivate the local sign target, but the object here is a bounded partial-ID finite difference inside a baseline rank slice, not an average derivative point estimand.

\citet{FirpoRidder2019} proves that pointwise Makarov bounds for treatment-effect distribution objects are not uniformly sharp; this is the main conceptual warning behind the proposal's claim that dosewise sharp APO intervals may be jointly nonsharp for slopes.  \citet{FanGuerreZhu2017} studies partial identification of functionals of the joint distribution of potential outcomes and shows how copula information can matter for non-ATE targets; the present proposal moves that logic to adjacent continuous doses and an IV/sensitivity setting.  \citet{DornGuo2023} develops sharp marginal-sensitivity bounds via quantile balancing, relevant because it shows how quantile restrictions can sharpen sensitivity analysis; this proposal uses a different quantile object, namely an adjacent-dose rank-copula tube.

The in-catalogue ThmSmith prior art is thin for this anchor.  \texttt{doc/API.md} section 3 records \texttt{ThmSmith/PartialID/} as an empty seed area for Manski-family bounds, IV bounds, sensitivity analysis, and shape restrictions, so the live catalogue does not already contain a continuous-dose IV copula-slope theorem.  The closest banked proposal is \texttt{pid\_dose\_response\_shape}: shape-closed sensitivity bounds for monotone-concave continuous dose response; its kernel is finite-grid monotone-concave curve closure without an IV and without a rank-slice derivative.  The present kernel is therefore not a relabelling of that banked angle: it replaces shape closure of marginal means by joint sharpness and sign certification for an adjacent-rank slope under IV-compatible margins.

\section{Formal setup}
Let \(P\) denote the observable law of \((Y,A,Z,X)\).  Potential outcomes are \(\{Y(a):a\in[a_0,a_2]\}\), with \(Y=Y(A)\) under consistency.  The two adjacent design doses are \(a_0<a_1\), \(h=a_1-a_0\), and \(\tau\subset[0,1]\) is a fixed rank slice.  For any full-data law \(Q\), let \(F_{a,x}\) be the conditional distribution function of \(Y(a)\mid X=x\), let \(F^-_{a,x}(y)=\Pr_Q(Y(a)<y\mid X=x)\), and introduce tie-breakers \(V_a\sim\mathrm{Unif}(0,1)\) independent conditional on \(\{Y(a),X\}\).  The randomized conditional rank is
\[
U_a=F^-_{a,X}(Y(a))+V_a\{F_{a,X}(Y(a))-F^-_{a,X}(Y(a))\},
\]
so \(U_a\mid X\sim\mathrm{Unif}(0,1)\) even when \(Y(a)\mid X\) has atoms; when the conditional margin is continuous this agrees with \(F_{a,X}\{Y(a)\}\).  Set the target coordinate to \(R_{01}:=U_{a_0}\), and let \(C_{01,x}\) be the conditional copula of \((U_{a_0},U_{a_1})\mid X=x\).  For \(j=0,1\), define the one-dose rank-slice marginal endpoints
\[
L_j^\tau(P,\Gamma,\eta)=\inf_Q \E_Q\{Y(a_j)\mid R_{01}\in\tau\},\quad
U_j^\tau(P,\Gamma,\eta)=\sup_Q \E_Q\{Y(a_j)\mid R_{01}\in\tau\},
\]
where the infimum and supremum range over the corresponding one-dose finite-grid sensitivity model with the same observed margin \(P\), the same baseline-rank slice \(R_{01}\), the \(\Gamma\)-tilt bound, and the IV moment tolerance \(\eta\), but without a cross-dose copula-tube constraint.  The rank-slice finite difference is
\[
\theta_{\tau,h}(Q)=
\frac{\E_Q[Y(a_1)-Y(a_0)\mid R_{01}\in\tau]}{h}.
\]
The identified set is
\[
\Theta_I(P)=\{\theta_{\tau,h}(Q): Q\in\mathcal M(P,\mathcal R_{\Gamma,\rho,\eta}^{\mathrm{iv\text{-}tube}})\}.
\]
The bounding functional \(B_{\Gamma,\rho,\eta}^{\mathrm{slope}}(P;\tau,h)\) is the interval hull of \(\Theta_I(P)\).

\begin{verbatim}
qid=pid_dose_response_iv
specialization=v1
observable distribution P=law(Y,A,Z,X), Y in [0,1], A in [a0,a2], continuous Z
parameter theta=baseline-rank-slice adjacent finite difference theta_{tau,h},
  with R_{01}:=U_{a0} defined by the randomized conditional PIT rank
restrictions R=consistency, positivity, randomized rank well-definedness,
  IV exclusion/conditional independence,
  CMSM Gamma, finite IV moment tolerance eta for m(Y(a_j),X) in R^K,
  adjacent-rank copula tube radius rho for C_{01,x} on tau x [0,1]
bounding functional B=sharp lower/upper envelope over full-data laws with observed margin P
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Bounded adjacent-dose setup]\label{ass:bounded-setup}
The outcome satisfies \(Y(a)\in[0,1]\) for \(a\in\{a_0,a_1\}\), the observed dose support contains neighborhoods of \(a_0\) and \(a_1\), \(h=a_1-a_0>0\), and the rank slice \(\tau=[\tau_L,\tau_U]\subset(0,1)\) has \(\tau_L<\tau_U\).
\end{assumption}

\begin{assumption}[Randomized conditional ranks]\label{ass:randomized-ranks}
For each adjacent dose \(a\in\{a_0,a_1\}\), the full-data law includes an auxiliary tie-breaker \(V_a\sim\mathrm{Unif}(0,1)\), independent conditional on \(\{Y(a),X\}\), and defines
\[
U_a=F^-_{a,X}(Y(a))+V_a\{F_{a,X}(Y(a))-F^-_{a,X}(Y(a))\}.
\]
The target event \(R_{01}\in\tau\) means \(U_{a_0}\in\tau\), and the conditional copula \(C_{01,x}\) is the copula of the randomized rank pair \((U_{a_0},U_{a_1})\mid X=x\).  If the conditional outcome margins are continuous, this assumption reduces to the ordinary probability-integral-transform ranks.
\end{assumption}

\begin{assumption}[Consistency and positivity]\label{ass:consistency-positivity}
The observed outcome is \(Y=Y(A)\).  Conditional treatment and instrument densities are positive on the dose and instrument bins used in the finite approximation, conditional on \(X\).
\end{assumption}

\begin{assumption}[IV margin restriction]\label{ass:iv-margin}
The instrument \(Z\) is excluded from the potential-outcome equation and is independent of the latent potential-outcome array conditional on \(X\).  Fix a known finite moment vector \(m(Y(a_j),X)\in\mathbb R^K\).  In the finite relaxation, IV compatibility is encoded by the linear inequalities
\[
\left|\E_Q[m_k(Y(a_j),X)\mid Z\in z_b]-\E_Q[m_k(Y(a_j),X)]\right|\le \eta
\]
for every moment coordinate \(k\), adjacent dose \(j=0,1\), and instrument bin \(z_b\).
\end{assumption}

\begin{assumption}[Continuous-treatment sensitivity radius]\label{ass:cmsm}
For each adjacent dose \(a_j\), hidden confounding is bounded by a continuous marginal sensitivity radius \(\Gamma\): the complete-data density tilt that maps the observed conditional law near \(A=a_j\) to the potential-outcome margin for \(Y(a_j)\) lies in a known closed interval of likelihood ratios with ratio at most \(\Gamma\).
\end{assumption}

\begin{assumption}[Adjacent-rank copula tube]\label{ass:copula-tube}
Within each \(X\)-stratum, \(R_{01}:=U_{a_0}\) is the randomized rank coordinate from Assumption~\ref{ass:randomized-ranks} that defines the target slice.  The copula \(C_{01,x}\) of \((U_{a_0},U_{a_1})\) satisfies
\[
\sup_{(u,v)\in\tau\times[0,1]}|C_{01,x}(u,v)-\min(u,v)|\le\rho.
\]
Thus conditioning in \(\theta_{\tau,h}\) is always conditioning on \(U_{a_0}\in\tau\), while the tube restricts the conditional distribution of the adjacent rank \(U_{a_1}\) paired with that baseline rank.
\end{assumption}

\begin{assumption}[Finite grid regularity]\label{ass:finite-grid}
For the finite theorem, \(X\), \(Z\), \(Y(a_0)\), \(Y(a_1)\), \(U_{a_0}\), and \(U_{a_1}\) are represented on fixed finite partitions, the moment vector \(m\) has finite dimension \(K\), and the feasible set defined by Assumptions~\ref{ass:bounded-setup}--\ref{ass:copula-tube} is nonempty and closed.
\end{assumption}

\begin{assumption}[Two-bin sign-witness regularity]\label{ass:two-bin-witness}
For Conjecture~\ref{conj:sign-certificate} and Conjecture~\ref{conj:rho-threshold}, the finite approximation has two baseline-rank bins inside \(\tau\), two instrument bins, nondegenerate IV-induced moment variation, and one-dose rank-slice marginal sensitivity intervals whose finite-difference interval contains zero.
\end{assumption}

\begin{assumption}[Observed-confounder rank identification corner]\label{ass:rank-id-corner}
For the unconfounded sanity corner, the observed-confounder law identifies \(F_{a_0,x}\), \(F_{a_1,x}\), the randomized rank construction in Assumption~\ref{ass:randomized-ranks}, and the adjacent copula \(C_{01,x}\), and this identified copula satisfies Assumption~\ref{ass:copula-tube}.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite sharp coupling projection]\label{thm:finite-coupling-bound}
Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:finite-grid}, the finite-grid sharp identified set for \(\theta_{\tau,h}\) is the projection of a nonempty compact polytope whose variables are the joint cell probabilities of \((Y(a_0),Y(a_1),U_{a_0},U_{a_1},Z,X)\) and the dose-specific sensitivity tilts.  The linear IV moment inequalities in Assumption~\ref{ass:iv-margin} and the copula-tube inequalities in Assumption~\ref{ass:copula-tube} are part of the finite constraint system defining this polytope.  The lower and upper endpoints of \(B_{\Gamma,\rho,\eta}^{\mathrm{slope}}(P;\tau,h)\) are attained by linear programs over this polytope.
\end{theorem}

\paragraph{Why this is new and worth studying.}
This theorem is not the field-level novelty claim: it is the finite sharpness object needed before testing the conjectured sign phenomenon.  Its closest prior art is the pointwise sharp APO construction in \citet{BaitairianSebastienJreichKatsahianGuilloux2025} and the finite-dimensional joint-distribution bounds in \citet{FirpoRidder2019} and \citet{FanGuerreZhu2017}; the difference is that the variables include one adjacent-dose rank coupling plus IV-compatible potential-outcome margins.  Formalizing this projection would give the repository a clean partial-ID target for continuous-dose IV sensitivity problems.

\begin{conjecture}[Conjecture 1: adjacent-rank sign certificate (NOT YET PROVED)]\label{conj:sign-certificate}
Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:two-bin-witness}, there exist observable laws \(P\), sensitivity radii \(\Gamma>1\), IV moment tolerances \(\eta>0\), and copula radii \(\rho>0\) such that the one-dose baseline-rank-slice marginal sensitivity interval
\[
\left[\frac{L_1^\tau(P,\Gamma,\eta)-U_0^\tau(P,\Gamma,\eta)}{h},
\frac{U_1^\tau(P,\Gamma,\eta)-L_0^\tau(P,\Gamma,\eta)}{h}\right]
\]
contains zero, while the sharp rank-slice interval \(B_{\Gamma,\rho,\eta}^{\mathrm{slope}}(P;\tau,h)\) is strictly positive.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
The closest sensitivity paper is \citet{BaitairianSebastienJreichKatsahianGuilloux2025}: their APO bounds can be sharp at each dose, but they do not ask whether two independently sharp dose adversaries can be pasted through one adjacent-rank copula.  The closest derivative sensitivity paper is \citet{Zhang2025ADE}, whose ADE bounds average the derivative over the exposure distribution under a generalized-propensity sensitivity model; it does not condition on a pinned baseline potential-outcome rank or use a continuous instrument and adjacent-rank copula tube to rule out sign-reversing cross-dose couplings.  The closest IV-copula paper is \citet{ChernozhukovFernandezValHanWuthrich2024}, which uses local copula invariance for point identification with a binary instrument; it does not give a partial-ID sign certificate for an adjacent baseline-rank slope under a sensitivity radius and copula tube.  Resolving this conjecture would let analysts report a local derivative-sign certificate under hidden confounding, instead of stopping at an inconclusive difference of pointwise or ADE bands.

\begin{conjecture}[Conjecture 2: two-bin copula-radius phase transition (NOT YET PROVED)]\label{conj:rho-threshold}
In the two-rank-bin witness of Assumption~\ref{ass:two-bin-witness}, holding \(P\), \(\Gamma\), the IV moment vector \(m\), and \(\eta\) fixed, the lower endpoint
\[
\underline\theta(\rho)=\inf B_{\Gamma,\rho,\eta}^{\mathrm{slope}}(P;\tau,h)
\]
is nonincreasing in \(\rho\).  Moreover, for some nonempty open set of witness laws there is a critical radius \(\rho^\star\in(0,1)\) such that \(\underline\theta(\rho)>0\) for \(\rho<\rho^\star\), \(\underline\theta(\rho)=0\) at \(\rho=\rho^\star\), and the one-dose baseline-rank-slice marginal finite-difference interval remains sign-ambiguous throughout.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
\citet{FirpoRidder2019} shows that pointwise sharp bounds can fail to be jointly sharp for process functionals; this conjecture proposes a concrete continuous-dose analogue where the boundary is governed by a copula-radius parameter.  The gap to standard copula-bounds work such as \citet{FanGuerreZhu2017} and IV local-copula work such as \citet{ChernozhukovFernandezValHanWuthrich2024} is the sensitivity-margin plus copula-radius phase boundary for a local derivative target.  A phase-transition theorem would give practitioners a transparent robustness curve: how close adjacent ranks must be before a derivative sign becomes certified.

\begin{theorem}[Theorem 2: no-tube reduction to one-dose rank-slice bounds]\label{thm:no-tube-reduction}
Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:finite-grid}, if \(\rho=1\) imposes no effective restriction on the adjacent copula and \(\eta\) is set large enough that the IV moment inequalities in Assumption~\ref{ass:iv-margin} are vacuous, then \(B_{\Gamma,\rho,\eta}^{\mathrm{slope}}(P;\tau,h)\) contains the one-dose rank-slice finite-difference interval
\[
\left[\frac{L_1^\tau(P,\Gamma,\eta)-U_0^\tau(P,\Gamma,\eta)}{h},
\frac{U_1^\tau(P,\Gamma,\eta)-L_0^\tau(P,\Gamma,\eta)}{h}\right],
\]
where \(L_j^\tau,U_j^\tau\) are the rank-slice marginal endpoints defined in Section~6.
\end{theorem}

\paragraph{Why this is new and worth studying.}
This is a sanity theorem rather than the novelty kernel.  It checks that the proposed object does not create derivative-sign information by notation alone: when the cross-dose copula and IV moment restrictions are removed, the proposal collapses back to the product of one-dose rank-slice sensitivity envelopes, the rank-slice analogue of the pointwise continuous-sensitivity bounds studied by \citet{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022}, \citet{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023}, and \citet{BaitairianSebastienJreichKatsahianGuilloux2025}.

\section{Sanity-check corollaries}
\begin{corollary}[Unconfounded adjacent-rank collapse]\label{cor:gamma-one-collapse}
Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:copula-tube} and Assumption~\ref{ass:rank-id-corner}, if \(\Gamma=1\) and \(\eta=0\), then \(B_{1,\rho,0}^{\mathrm{slope}}(P;\tau,h)\) is the singleton containing the corresponding observed-confounder rank-slice finite difference.
\end{corollary}

Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:copula-tube} and Assumption~\ref{ass:rank-id-corner}, the statement collapses cleanly because \(\Gamma=1\) removes hidden-confounding tilts, \(\eta=0\) makes the finite IV moment margins exact, and the known adjacent copula fixes the joint mean difference conditional on the pinned event \(R_{01}=U_{a_0}\in\tau\).

\begin{corollary}[No shared-rank information gives no sign certificate]\label{cor:no-rank-no-sign}
Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:finite-grid}, if \(\rho=1\), \(\eta\) is large enough to make Assumption~\ref{ass:iv-margin} vacuous, and the one-dose rank-slice finite-difference interval in Theorem~\ref{thm:no-tube-reduction} contains zero, then the proposed rank-slice analysis cannot certify a strictly positive derivative sign.
\end{corollary}

Under Assumptions~\ref{ass:bounded-setup}--\ref{ass:finite-grid}, this is the direct sanity check for Theorem~\ref{thm:no-tube-reduction}: without the copula tube or finite IV moment restrictions, independent one-dose rank-slice endpoint choices remain feasible in the product relaxation, so a positive sign cannot be forced when that product interval contains zero.

\section{Proof-sketch route}
The mathematical route is finite-dimensional convex analysis plus a two-bin witness calculation.  Theorem~\ref{thm:finite-coupling-bound} follows by writing the observed margins, randomized-rank bin masses, sensitivity-ratio bounds, finite IV moment inequalities, copula-tube inequalities, and probability normalization constraints as linear equalities and inequalities on a finite joint table; compactness gives attained extrema.  Theorem~\ref{thm:no-tube-reduction} is proved by constructing product couplings that attain the one-dose rank-slice marginal endpoints when the cross-dose and IV moment constraints are vacuous.  The conjectural work is the explicit two-baseline-rank-bin algebra: write a \(2\times2\) table \(p_{rs}\) for baseline rank bin \(r\in\{L,H\}\) and adjacent rank bin \(s\in\{L,H\}\), impose fixed row and column margins, impose \(|p_{LL}-(p_{L\cdot}\wedge p_{\cdot L})|\le\rho\) as the local copula-radius inequality, and add one signed IV moment inequality that prevents the low-slope cell from absorbing all baseline-low mass.  Solving that four-cell linear program should expose the threshold at which the lower finite difference crosses zero.

\section{Honest scope flags}
The finite LP representation and the no-tube reduction are labelled as theorems because they are routine once the finite partitions and restrictions are fixed.  The sign certificate and the critical-radius phase transition are labelled as conjectures because the two-bin witness has not yet been algebraically enumerated.  The copula-tube restriction is deliberately local to adjacent doses and a baseline rank slice \(R_{01}=U_{a_0}\in\tau\); the proposal does not claim point identification of the full dose-response curve or the full treatment-effect distribution.  The IV tolerance \(\eta\) is now fixed as a finite vector of linear moment inequalities; variants based on full conditional distributions or Wasserstein distance are outside this locked proposal.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for the adjacent-rank copula-tube angle after the dynamic-IV compliance seed was burned; prior verdict: none.
\item v2 (revise) --- pinned \(R_{01}=U_{a_0}\), defined one-dose rank-slice marginal endpoints, fixed \(\eta\) as finite IV moment inequalities, and repaired the no-tube sanity reduction; prior verdict: REVISE.
\item v3 (revise) --- replaced ordinary ranks by randomized conditional ranks to make copulas well-defined under atoms, narrowed the Kasy comparison with the 2017 corrigendum, and added a two-by-two witness-table route; prior verdict: REVISE.
\item v4 (revise) --- added the local-copula binary-IV comparator of Chernozhukov, Fernandez-Val, Han, and Wuthrich (2024) and distinguished point identification under copula invariance from the rank-slice partial-ID slope kernel; prior verdict: REVISE.
\item v5 (revise) --- added Zhang (2025) as the closest average-derivative sensitivity comparator and separated ADE bounds from the baseline-rank-slice IV/copula sign certificate; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Baitairian et~al.(2025)]{BaitairianSebastienJreichKatsahianGuilloux2025}
Baitairian, J.-B., B. Sebastien, R. Jreich, S. Katsahian, and A. Guilloux (2025).
\newblock Sharp bounds for continuous-valued treatment effects with unobserved confounders.
\newblock \emph{Biometrical Journal} 67(5), e70084. \url{https://arxiv.org/abs/2411.02231}.

\bibitem[Chernozhukov and Hansen(2005)]{ChernozhukovHansen2005}
Chernozhukov, V. and C. Hansen (2005).
\newblock An IV model of quantile treatment effects.
\newblock \emph{Econometrica} 73(1), 245--261.

\bibitem[Chernozhukov et~al.(2024)]{ChernozhukovFernandezValHanWuthrich2024}
Chernozhukov, V., I. Fernandez-Val, S. Han, and K. Wuthrich (2024).
\newblock Estimating causal effects of discrete and continuous treatments with binary instruments.
\newblock arXiv:2403.05850. \url{https://arxiv.org/abs/2403.05850}.

\bibitem[Dalal and Tchetgen Tchetgen(2025)]{DalalTchetgenTchetgen2025}
Dalal, A. and E. J. Tchetgen Tchetgen (2025).
\newblock Partial identification of causal effects for endogenous continuous treatments.
\newblock arXiv:2508.13946. \url{https://ideas.repec.org/p/arx/papers/2508.13946.html}.

\bibitem[D'Haultfoeuille and Fevrier(2015)]{DHaultfoeuilleFevrier2015}
D'Haultfoeuille, X. and P. Fevrier (2015).
\newblock Identification of nonseparable triangular models with discrete instruments.
\newblock \emph{Econometrica} 83(3), 1199--1210.

\bibitem[Dorn and Guo(2023)]{DornGuo2023}
Dorn, J. and K. Guo (2023).
\newblock Sharp sensitivity analysis for inverse propensity weighting via quantile balancing.
\newblock \emph{Journal of the American Statistical Association} 118(544), 2645--2657.

\bibitem[Fan et~al.(2017)]{FanGuerreZhu2017}
Fan, Y., E. Guerre, and D. Zhu (2017).
\newblock Partial identification of functionals of the joint distribution of potential outcomes.
\newblock \emph{Journal of Econometrics} 197(1), 42--59.

\bibitem[Firpo and Ridder(2019)]{FirpoRidder2019}
Firpo, S. and G. Ridder (2019).
\newblock Partial identification of the treatment effect distribution and its functionals.
\newblock \emph{Journal of Econometrics} 213(1), 210--234.

\bibitem[Jesson et~al.(2022)]{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022}
Jesson, A., A. Douglas, P. Manshausen, M. Solal, N. Meinshausen, P. Stier, Y. Gal, and U. Shalit (2022).
\newblock Scalable sensitivity and uncertainty analyses for causal-effect estimates of continuous-valued interventions.
\newblock \emph{NeurIPS 2022}. \url{https://arxiv.org/abs/2204.10022}.

\bibitem[Kasy(2014)]{Kasy2014}
Kasy, M. (2014).
\newblock Instrumental variables with unrestricted heterogeneity and continuous treatment.
\newblock \emph{Review of Economic Studies} 81(4), 1614--1636.

\bibitem[Hoderlein et~al.(2017)]{HoderleinHolzmannKasyMeister2017}
Hoderlein, S., H. Holzmann, M. Kasy, and A. Meister (2017).
\newblock Corrigendum: Instrumental variables with unrestricted heterogeneity and continuous treatment.
\newblock \emph{Review of Economic Studies} 84(2), 964--968. \url{https://doi.org/10.1093/restud/rdw027}.

\bibitem[Imbens and Newey(2009)]{ImbensNewey2009}
Imbens, G. W. and W. K. Newey (2009).
\newblock Identification and estimation of triangular simultaneous equations models without additivity.
\newblock \emph{Econometrica} 77(5), 1481--1512.

\bibitem[Marmarelis et~al.(2023)]{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023}
Marmarelis, M. G., E. Haddad, A. Jesson, N. Jahanshad, A. Galstyan, and G. Ver Steeg (2023).
\newblock Partial identification of dose responses with hidden confounders.
\newblock \emph{Proceedings of the Thirty-Ninth Conference on Uncertainty in Artificial Intelligence}, PMLR 216:1368--1379.

\bibitem[Torgovitsky(2015)]{Torgovitsky2015}
Torgovitsky, A. (2015).
\newblock Identification of nonseparable models using instruments with small support.
\newblock \emph{Econometrica} 83(3), 1185--1197.

\bibitem[Zhang(2025)]{Zhang2025ADE}
Zhang, J. (2025).
\newblock A sensitivity analysis for the average derivative effect.
\newblock arXiv:2511.06243. \url{https://arxiv.org/abs/2511.06243}.
\end{thebibliography}

\end{document}
