% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_dose\_response\_iv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_dose\_response\_iv} / \texttt{v1}%
  \\ \large\textit{Quantile-copula sign certificates for local dose-response slopes under continuous-IV sensitivity bounds}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
(\texttt{pid\_dose\_response\_iv},\texttt{v1},
P,\theta_{\tau,h},\mathcal R_{\Gamma,\rho}^{\mathrm{cIV+cop}},
B_{\Gamma,\rho}^{\mathrm{slope}}).
\]
Here \(P\) is the observable law of \(O=(Y,A,Z,X)\), where \(Y\in[0,1]\), \(A\in\mathcal A\subset\mathbb R\), \(Z\in\mathcal Z\subset\mathbb R\) is a continuous instrument, and \(X\) is a measured covariate vector.  Fix three doses \(a_-<a_0<a_+\) with \(h=a_+-a_->0\) and a rank slice \(S_\tau=[\tau_L,\tau_U]\) with \(0\le \tau_L<\tau_U\le 1\).  The primary local target uses an interior slice \(S_\tau\subset(0,1)\); the boundary convention \(S_\tau=[0,1]\) is reserved for the full-population sanity theorem.  The parameter is the rank-slice local dose-response slope
\[
\theta_{\tau,h}
=\E\!\left[\frac{Y(a_+)-Y(a_-)}{h}\ \middle|\ U_0\in S_\tau\right],
\]
where \(U_j=F_{Y(a_j)}(Y(a_j))\) is the latent quantile rank of the potential outcome at \(a_j\), with \(j\in\{-,0,+\}\), under the continuous-rank convention in Assumption~\ref{ass:continuous-ranks}.  If atoms are later allowed, the same notation must be replaced by the randomized probability-integral transform \(F_{Y(a_j)}(Y(a_j)-)+V_j\Delta F_{Y(a_j)}(Y(a_j))\).  The identifying restrictions \(\mathcal R_{\Gamma,\rho}^{\mathrm{cIV+cop}}\) are consistency, exclusion of \(Z\) except through \(A\), continuous-IV relevance, a dosewise marginal-sensitivity model indexed by \(\Gamma\) using normalized outcome-density tilts \(\omega_j\) with \(\E[\omega_j\mid A=a_j,Z,X]=1\) and odds-ratio diameter at most \(\Gamma\), and an adjacent-dose quantile-copula tube indexed by \(\rho\) requiring \(|U_--U_0|\le\rho\) and \(|U_+-U_0|\le\rho\) almost surely.  The full-data law class is \(\mathfrak M_{\Gamma,\rho}(P)\), the set of laws over \((O,\{Y(a):a\in\mathcal A\})\) with observed marginal \(P\) that satisfy these restrictions and the normalization in Assumption~\ref{ass:msm}.  The bounding functional is
\[
B_{\Gamma,\rho}^{\mathrm{slope}}(P,\tau,h)
=\left[
\inf_{\vartheta\in\Theta_{\Gamma,\rho}(P;\tau,h)}\vartheta,\,
\sup_{\vartheta\in\Theta_{\Gamma,\rho}(P;\tau,h)}\vartheta
\right],
\]
where \(\Theta_{\Gamma,\rho}(P;\tau,h)\) is the set of all values of the displayed rank-slice slope over dosewise quantile functions and rank couplings satisfying \(\mathcal R_{\Gamma,\rho}^{\mathrm{cIV+cop}}\).

\begin{abstract}
Continuous instruments can reveal or bound dose-response marginals, but local causal slopes for units at a given potential-outcome rank also depend on how nearby potential outcomes are coupled across doses.  This proposal asks for sharp partial identification of a rank-slice marginal dose-response derivative when dosewise continuous-IV sensitivity bounds are combined with an explicit quantile-copula tube.  The proposed kernel is a sign-certification phenomenon: a narrow adjacent-dose rank tube can force a positive lower bound on a local slope even when every dosewise marginal mean band and every unrestricted-copula slope band still contains zero.  The routine part is a finite lifted optimal-transport relaxation that is a valid outer envelope; the open part is the continuous-IV sensitivity pasting theorem showing when the envelope is sharp for one full-data law rather than only for separately optimized dose marginals.  If resolved, the result would give practitioners a checkable certificate for local dose-response monotonicity under bounded unmeasured confounding.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Many continuous-treatment questions are local: a clinician changes a dose slightly, a regulator changes an exposure threshold, or a price changes at the margin.  Continuous-IV and continuous-treatment sensitivity papers usually report bounds on dose-response levels or on dosewise potential-outcome distributions.  Those objects do not answer whether a local dose increase helps the units sitting at a particular latent outcome rank, because that derivative depends on the cross-dose dependence of \(Y(a_-)\), \(Y(a_0)\), and \(Y(a_+)\).  The methodological question is whether a transparent rank-copula restriction can turn IV-assisted sensitivity bands into sharp local slope bounds.

\paragraph{The main finding (proposed).}
Theorem~\ref{thm:transport-outer} states the finite lifted optimal-transport relaxation: after discretizing ranks, the products between rank-cell masses and dosewise quantile values are represented by lifted outcome-mass variables, yielding a linear-program outer bound.  Conjecture~\ref{conj:pasting-sharpness} is the main novelty-bearing statement: feasible continuous objects satisfying the common \(\Gamma\)-sensitivity and \(\rho\)-copula restrictions can be pasted into one full-data continuous-IV law.  Conjecture~\ref{conj:sign-phase} isolates the publishable phenomenon: for three adjacent doses, the copula tube can certify a strictly positive rank-slice slope even when unrestricted dependence cannot.

\paragraph{What is new.}
The closest continuous-IV paper, \citet{Kasy2014}, identifies or partially identifies potential-outcome distributions under a continuous instrument, but it does not bound local derivative functionals that depend on the joint law of adjacent potential outcomes.  \citet{Chesher2003} and \citet{Jun2009} are the closest local-derivative comparators: they identify structural derivatives or local structural quantile effects in nonseparable triangular models under local rank, order, control-variable, and relevance restrictions.  This proposal is different because the target is not point identification of a structural derivative at a latent coordinate; it is a partial-identification sign certificate for a rank-slice finite-difference slope under a named bounded-confounding model and a cross-dose copula tube.  The IV quantile-treatment-effect literature, especially \citet{ChernozhukovHansen2005}, \citet{ChernozhukovHansen2006}, and \citet{ImbensNewey2009}, is closer in its use of ranks, but it targets structural quantile or control-function effects under rank restrictions rather than partial-identification bounds for a rank-slice slope under bounded confounding and a copula tube.  \citet{Kline2016} is the closest IV comparator on the sign question because it identifies the existence and direction of a causal effect, but it is not a continuous-dose partial-identification result and does not use cross-dose rank-copula restrictions.  The closest continuous-treatment sensitivity papers, including \citet{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022}, \citet{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023}, \citet{BaitairianSebastienJreichKatsahianGuilloux2025}, and \citet{DalalTchetgenTchetgen2025}, provide dosewise hidden-confounding bounds but do not add a continuous instrument plus a cross-dose rank-copula sharpness theorem.  The closest copula and treatment-effect-distribution work, especially \citet{FirpoRidder2019} and \citet{MadigasekaraPoskittZhangZhao2024}, shows that joint potential-outcome dependence matters, but not for IV-assisted local continuous-dose derivative signs.  The novelty kernel is therefore not ``add a copula''; it is the sign-certification boundary created when a continuous-IV marginal envelope is intersected with an adjacent-dose rank-coupling tube.

\paragraph{How it positions in the literature.}
This is a partial-identification proposal in the continuous-IV, bounded-confounding, and copula-restricted potential-outcome-dependence cluster.  It uses continuous-IV results as marginal-information sources, sensitivity-analysis papers as dosewise envelope sources, and copula/optimal-transport ideas as the cross-dose compatibility layer.  It is not an SCM axiomatics proposal and not a panel regression proposal.

\section{Related work}
\citet{Kasy2014} studies continuous triangular systems with unrestricted heterogeneity and shows that rich continuous instruments can identify potential-outcome distributions, with partial identification when support is insufficient; this proposal takes that marginal-distribution frontier as the closest IV anchor.  \citet{Torgovitsky2015} and \citet{DHaultfoeuilleFevrier2015} show that scalar heterogeneity and monotone triangular structure can restore point identification with small-support instruments; the present proposal instead keeps a bounded-confounding partial-ID envelope and asks what copula restrictions add.  \citet{Ishihara2021} studies partial identification of nonseparable models with continuous endogenous variables and binary instruments under monotonicity or concavity; it is relevant because it shows that point identification can fail while shape restrictions still carry identifying power.  \citet{Chesher2003} identifies local structural derivatives and quantiles of policy impacts in nonseparable models using local rank/order and quantile-insensitivity restrictions; it is the closest derivative paper, but it is a point-identification framework rather than a bounded-confounding partial-ID copula-tube bound.  \citet{Jun2009} develops local structural quantile effects in a semiparametric nonseparable triangular model with a control variable and local instrument relevance; it is adjacent because the estimand is local and rank-indexed, but it does not produce sharp partial-ID intervals from continuous-IV sensitivity envelopes.  \citet{ChernozhukovHansen2005} develops an IV model of quantile treatment effects using rank restrictions, \citet{ChernozhukovHansen2006} gives IV quantile-regression inference for structural and treatment-effect models, and \citet{ImbensNewey2009} identifies nonadditive triangular models through control variables; these are the closest rank-based IV comparators, but none states a copula-sensitivity bound for local dose-response slopes.  \citet{Kline2016} identifies the existence and direction of a causal effect using IV variation in a generalized nonparametric nonseparable model; it is the closest sign/direction comparator, while the present proposal asks for a partial-ID sign certificate for a continuous-dose rank-slice slope under a copula tube.

\citet{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022} propose continuous-treatment marginal sensitivity bounds for continuous-valued interventions; the present proposal uses such dosewise envelopes but studies their cross-dose sharpness.  \citet{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023} derives hidden-confounding dose-response bounds for continuous treatments, again without the continuous-IV copula derivative target.  \citet{BaitairianSebastienJreichKatsahianGuilloux2025} gives sharp APO bounds under a continuous sensitivity model and is the closest pointwise-sharp sensitivity comparator.  \citet{DalalTchetgenTchetgen2025} bounds dose-response curves for endogenous continuous treatments under Rosenbaum and marginal sensitivity models; this proposal differs by adding a continuous instrument and targeting rank-slice local slopes.

\citet{FirpoRidder2019} shows that Makarov-style pointwise bounds on treatment-effect distributions are not uniformly sharp for functionals of the whole process; this motivates treating the derivative bound as a joint coupling problem rather than as two separately optimized dose marginals.  \citet{FanPark2010} gives sharp Makarov-type bounds for treatment-effect distributions from known marginals, and \citet{MadigasekaraPoskittZhangZhao2024} uses copula equality assumptions in panel data to sharpen distributional treatment-effect bounds.  \citet{BaiocchiChengSmall2023} is relevant because it warns that sensitivity models for continuous IVs must incorporate dose information; here the copula tube explicitly keeps adjacent-dose rank information.

The ThmSmith catalogue currently has no populated ExactID or PartialID theorem stack; `doc/API.md' records those catalogues as seed areas.  The closest banked proposal is \texttt{pid\_dose\_response\_shape\_v1}, which studies monotone-concave closure of continuous-treatment sensitivity intervals without an instrument and without copula-dependent derivative targets.  The accepted \texttt{pid\_dynamic\_iv\_compliance\_v2} proposal studies dynamic binary-IV response-contribution memory bounds; it is IV partial-ID prior art, but its kernel is finite compliance memory rather than continuous-dose rank dependence.

\section{Formal setup}
Let \(P\) be the observable law of \(O=(Y,A,Z,X)\), with \(Y\in[0,1]\), continuous dose \(A\), continuous instrument \(Z\), and covariates \(X\).  Potential outcomes are \(\{Y(a):a\in\mathcal A\}\).  Fix the local grid \(a_-<a_0<a_+\), write \(h=a_+-a_-\), and let \(F_j\) and \(Q_j\) denote the marginal distribution and quantile function of \(Y(a_j)\) for \(j\in\{-,0,+\}\).  Under the continuous-rank convention, \(U_j=F_j(Y(a_j))\) is uniform on \([0,1]\).  If \(F_j\) has atoms, the replacement object is the tie-broken rank \(F_j(Y(a_j)-)+V_j\{F_j(Y(a_j))-F_j(Y(a_j)-)\}\), with \(V_j\sim\mathrm{Unif}(0,1)\) independent of the potential outcomes.  Let \(S_\tau=[\tau_L,\tau_U]\) be the target rank slice; the main local problem uses \(S_\tau\subset(0,1)\), while \(S_\tau=[0,1]\) is an explicit boundary extension for Theorem~\ref{thm:mean-collapse}.

The continuous-IV/sensitivity layer is summarized by closed dosewise quantile-envelope sets
\[
\mathcal Q_j(P,\Gamma)=
\{q_j:[0,1]\to[0,1]\ \text{nondecreasing and left-continuous}:
Q^-_j(u;P,\Gamma)\le q_j(u)\le Q^+_j(u;P,\Gamma)\ \forall u\}.
\]
The proposal treats these envelopes as the output of a named marginal sensitivity model, not as free primitives.  For each \(j\), let \(R_j(dy\mid z,x)\) be the local regular conditional law of \(Y\) given \(A=a_j,Z=z,X=x\).  A full-data law belongs to \(\mathfrak M_{\Gamma,\rho}(P)\) only if there are measurable tilts \(\omega_j(y,z,x)\) such that
\[
dF_{Y(a_j)\mid Z=z,X=x}(y)=\omega_j(y,z,x)\,dR_j(y\mid z,x),\qquad
\int\omega_j(y,z,x)\,dR_j(y\mid z,x)=1,
\]
and
\[
\frac{\omega_j(y,z,x)}{\omega_j(y',z,x)}\le\Gamma
\quad\text{for }R_j(\cdot\mid z,x)\otimes R_j(\cdot\mid z,x)\text{-a.e. }(y,y').
\]
This is the odds-ratio-diameter normalization of a marginal sensitivity model; \(\Gamma=1\) forces no hidden-confounding tilt at the local dose.  The continuous-IV part of \(\mathfrak M_{\Gamma,\rho}(P)\) further requires observed marginal \(P\), consistency, exclusion of \(Z\) from \(Y(a)\) except through the dose rule, and first-stage relevance sufficient to define the local conditionals \(R_j\).  The derivation of \(Q_j^\pm\) from this law class is prior-art input, not the novelty claim.

For a rank-coupling law \(\pi\) on \([0,1]^3\), write \(U=(U_-,U_0,U_+)\sim\pi\).  Define the adjacent-dose copula class
\[
\Pi_\rho(S_\tau)=
\left\{\pi:
\pi_j=\mathrm{Unif}(0,1)\ \forall j,\ 
|U_--U_0|\le\rho,\ |U_+-U_0|\le\rho\ \pi\text{-a.s.},\
\Pr_\pi(U_0\in S_\tau)>0
\right\}.
\]
For \(q=(q_-,q_0,q_+)\) and \(\pi\in\Pi_\rho(S_\tau)\), the induced local rank-slice slope is
\[
\theta(q,\pi)
=
\frac{
\int \one\{u_0\in S_\tau\}\{q_+(u_+)-q_-(u_-)\}\,d\pi(u_-,u_0,u_+)
}{
h\,\pi(U_0\in S_\tau)
}.
\]
The identified set and bounding functional are
\[
\Theta_{\Gamma,\rho}(P;\tau,h)
=
\{\theta(q,\pi): q_j\in\mathcal Q_j(P,\Gamma),\ \pi\in\Pi_\rho(S_\tau)\},
\qquad
B_{\Gamma,\rho}^{\mathrm{slope}}(P,\tau,h)
=
[\inf\Theta_{\Gamma,\rho},\sup\Theta_{\Gamma,\rho}].
\]

\begin{verbatim}
Locked parameters:
(qid, specialization, P, theta, identifying restrictions, bounding functional)
=(pid_dose_response_iv, v1, P_{Y,A,Z,X}, theta_{tau,h},
  R^{cIV+cop}_{Gamma,rho}, B^{slope}_{Gamma,rho})
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Observed support and consistency]\label{ass:support}
\(Y\in[0,1]\), \(a_-<a_0<a_+\) are interior points of \(\mathcal A\), \(0\le\tau_L<\tau_U\le1\), the primary local target has \(0<\tau_L<\tau_U<1\), and the observed outcome satisfies \(Y=Y(A)\).  The boundary choice \(S_\tau=[0,1]\) is permitted only for full-population collapse and sanity-check statements.
\end{assumption}

\begin{assumption}[Continuous potential-outcome ranks]\label{ass:continuous-ranks}
For \(j\in\{-,0,+\}\), the marginal distribution \(F_j\) of \(Y(a_j)\) is continuous, so \(U_j=F_j(Y(a_j))\) is uniform on \([0,1]\).  If this assumption is removed, every rank statement must instead use the randomized probability-integral transform defined in Section 6.
\end{assumption}

\begin{assumption}[Continuous-IV marginal sensitivity envelope]\label{ass:msm}
For each \(j\in\{-,0,+\}\), the law class \(\mathfrak M_{\Gamma,\rho}(P)\) uses the normalized local marginal-sensitivity tilts defined in Section 6: \(dF_{Y(a_j)\mid Z=z,X=x}=\omega_j\,dR_j\), \(\int\omega_j\,dR_j=1\), and \(\omega_j(y,z,x)/\omega_j(y',z,x)\le\Gamma\) almost surely under the local reference law.  The same full-data law must have observed marginal \(P\), satisfy consistency, satisfy exclusion of \(Z\) from potential outcomes apart from the dose rule, and have continuous-IV relevance sufficient for the local regular conditional laws \(R_j\) at \(a_-,a_0,a_+\).
\end{assumption}

\begin{assumption}[Closed dosewise quantile envelope]\label{ass:civ-envelope}
For each \(j\in\{-,0,+\}\), the full-data laws satisfying Assumption~\ref{ass:msm} induce the nonempty closed quantile-envelope set \(\mathcal Q_j(P,\Gamma)\) defined in Section 6.
\end{assumption}

\begin{assumption}[Adjacent quantile-copula tube]\label{ass:copula}
The joint rank law of \((U_-,U_0,U_+)\) belongs to \(\Pi_\rho(S_\tau)\) for a known \(\rho\in[0,1]\).
\end{assumption}

\begin{assumption}[Nonempty feasible slope set]\label{ass:nonempty}
\(\Theta_{\Gamma,\rho}(P;\tau,h)\) is nonempty and \(\Pr_\pi(U_0\in S_\tau)=\tau_U-\tau_L>0\) for every feasible rank coupling.
\end{assumption}

\begin{assumption}[Finite rank grid approximation]\label{ass:grid}
For computational statements, ranks are restricted to a grid \(0=r_0<\cdots<r_M=1\) with cells \(I_b=(r_{b-1},r_b]\) and lengths \(\Delta_b=r_b-r_{b-1}\).  The target rank slice is grid-aligned: there is an index set \(\mathcal B_\tau\subseteq\{1,\ldots,M\}\) such that \(S_\tau=\bigcup_{b\in\mathcal B_\tau} I_b\) up to endpoints and \(\sum_{b\in\mathcal B_\tau}\Delta_b=\tau_U-\tau_L\).  A rank cell \((a,b,c)\) is \(\rho\)-admissible under the outer-bound convention when the product cell \(I_a\times I_b\times I_c\) intersects the continuous tube \(\{(u_-,u_0,u_+): |u_--u_0|\le\rho,\ |u_+-u_0|\le\rho\}\); equivalently, both interval distances \(\mathrm{dist}(I_a,I_b)\) and \(\mathrm{dist}(I_c,I_b)\) are at most \(\rho\).  Non-\(\rho\)-admissible cells are assigned zero mass, while admissible cells are retained even if only part of the product cell lies inside the tube.  The quantile functions are represented by step values on the grid cells, and the copula law \(\pi\) is represented by a nonnegative mass array \(m_{abc}\) on the \(M^3\) rank cells with uniform one-dimensional marginals \(\sum_{a,c}m_{abc}=\Delta_b\), \(\sum_{b,c}m_{abc}=\Delta_a\), and \(\sum_{a,b}m_{abc}=\Delta_c\).  The lifted relaxation additionally uses outcome-mass variables \(w^-_{abc}\) and \(w^+_{abc}\), interpreted as \(m_{abc}q_-(I_a)\) and \(m_{abc}q_+(I_c)\) for an exact grid object but constrained only by the linear envelope inequalities stated in Theorem~\ref{thm:transport-outer}.
\end{assumption}

\begin{assumption}[Sign-separation witness]\label{ass:sign-witness}
There exist \(\varepsilon>0\) and a rank slice \(S_\tau\) such that for all feasible \(q_-\in\mathcal Q_-(P,\Gamma)\), \(q_+\in\mathcal Q_+(P,\Gamma)\), and all \(u_0\in S_\tau\), every \(u_-,u_+\) satisfying \(|u_--u_0|\le\rho\) and \(|u_+-u_0|\le\rho\) obeys \(q_+(u_+)-q_-(u_-)\ge\varepsilon h\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite transport envelope is a valid outer bound]\label{thm:transport-outer}
Under Assumptions~\ref{ass:support}--\ref{ass:grid}, define a finite lifted transport relaxation with variables \(m_{abc}\ge0\), \(w^-_{abc}\), and \(w^+_{abc}\).  The mass variables have uniform one-dimensional marginals, non-\(\rho\)-admissible cells in the any-point sense of Assumption~\ref{ass:grid} have zero mass, and the lifted variables satisfy the linear inequalities
\[
Q^-_-(I_a;P,\Gamma)m_{abc}\le w^-_{abc}\le Q^+_-(I_a;P,\Gamma)m_{abc},\qquad
Q^-_+(I_c;P,\Gamma)m_{abc}\le w^+_{abc}\le Q^+_+(I_c;P,\Gamma)m_{abc}.
\]
Here \(Q^\pm_j(I_b;P,\Gamma)\) denotes the lower or upper envelope value assigned to grid cell \(I_b\).
The lower and upper endpoints of the lifted finite-grid outer interval are attained by linear programs with objective
\[
\frac{1}{h(\tau_U-\tau_L)}
\sum_{b\in\mathcal B_\tau}\sum_{a,c}(w^+_{abc}-w^-_{abc}).
\]
Every exact finite-grid law satisfying \(\mathcal R_{\Gamma,\rho}^{\mathrm{cIV+cop}}\) maps to this lifted polytope by setting \(w^-_{abc}=m_{abc}q_-(I_a)\) and \(w^+_{abc}=m_{abc}q_+(I_c)\).  Because grid alignment gives \(\Pr(U_0\in S_\tau)=\sum_{b\in\mathcal B_\tau}\Delta_b=\tau_U-\tau_L\), the displayed objective is the exact rank-slice slope for that finite law; hence the resulting interval is a valid outer bound for \(\theta_{\tau,h}\).  Exactness of this lifted relaxation is not asserted.
\end{theorem}

\paragraph{Why this is new and worth studying.}
The closest papers split the ingredients: \citet{Kasy2014} supplies continuous-IV marginal information, the continuous-treatment sensitivity papers supply dosewise envelopes, and \citet{FirpoRidder2019} warns that pointwise coupling bounds need not be uniformly sharp for functionals.  This theorem records a checkable lifted outer object that combines those ingredients for a rank-slice local slope without falsely treating products of masses and quantile values as linear.  Its value is diagnostic: it makes clear when a derivative-sign claim is already certified by a conservative transport relaxation and when a sharper nonlinear or pasting argument is needed.

\begin{conjecture}[Conjecture 1: continuous-IV sensitivity/copula pasting sharpness (NOT YET PROVED)]\label{conj:pasting-sharpness}
Under Assumptions~\ref{ass:support}--\ref{ass:nonempty}, every feasible pair \((q,\pi)\) in the definition of \(\Theta_{\Gamma,\rho}(P;\tau,h)\) that is compatible with the dosewise envelopes \(\mathcal Q_j(P,\Gamma)\) is induced by at least one full-data law in \(\mathfrak M_{\Gamma,\rho}(P)\).  Equivalently, one can choose normalized tilts \(\omega_j\) satisfying Assumption~\ref{ass:msm}, potential outcomes \(\{Y(a):a\in\mathcal A\}\) agreeing with \(q_j\) at \(a_j\), observed law \(P\), continuous-IV exclusion and relevance, and joint rank law \(\pi\) satisfying Assumption~\ref{ass:copula}.  Consequently \(B_{\Gamma,\rho}^{\mathrm{slope}}(P,\tau,h)\) is the sharp partial-identification interval for \(\theta_{\tau,h}\) relative to \(\mathfrak M_{\Gamma,\rho}(P)\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
Pointwise sharpness in \citet{BaitairianSebastienJreichKatsahianGuilloux2025} and the pseudo-outcome envelopes of \citet{DalalTchetgenTchetgen2025} do not imply this statement, because one latent full-data law must rationalize all adjacent doses and their rank dependence simultaneously.  Copula-restricted distributional-treatment-effect papers such as \citet{MadigasekaraPoskittZhangZhao2024} impose dependence restrictions but do not include a continuous-IV sensitivity envelope or local derivative target.  Proving or refuting this conjecture would identify whether the finite transport interval is a sharp causal bound or only a conservative diagnostic.

\begin{conjecture}[Conjecture 2: copula-tube sign-certification phase transition (NOT YET PROVED)]\label{conj:sign-phase}
Under Assumptions~\ref{ass:support}--\ref{ass:nonempty} and Assumption~\ref{ass:sign-witness}, the lower endpoint of \(B_{\Gamma,\rho}^{\mathrm{slope}}(P,\tau,h)\) is at least \(\varepsilon\); this certificate clause is routine once the witness assumption is granted.  The conjectural phase-transition claim is that there exist observable laws \(P\), sensitivity levels \(\Gamma>1\), and adjacent-dose envelopes \(\mathcal Q_-(P,\Gamma),\mathcal Q_+(P,\Gamma)\) for which the same rank-slice lower endpoint is strictly positive for some \(\rho<1/2\), while the unrestricted-copula endpoint at \(\rho=1\) is nonpositive and the full-population average-slope interval contains zero.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
The sign-separation witness is not a generic ``stronger assumption tightens bounds'' claim.  It says the tightening appears only after the derivative target is localized by rank and after the adjacent-dose copula tube prevents the lower dose from borrowing high ranks while the upper dose borrows low ranks.  \citet{Chesher2003} and \citet{Jun2009} are the closest local-derivative comparators, but their local structural derivative objects are point identified under local rank/control restrictions rather than bounded as a copula-restricted partial-ID interval.  \citet{Kline2016} is the closest IV sign comparator because it identifies the direction of a causal effect in a broad nonseparable IV model; the present conjecture differs by making the sign a partial-identification lower-endpoint statement for a local continuous-dose rank-slice derivative under bounded confounding and cross-dose rank dependence.  IV quantile-regression papers such as \citet{ChernozhukovHansen2005} and \citet{ChernozhukovHansen2006} use rank restrictions to identify structural quantile effects, but they do not study partial-ID sign certification created by intersecting a bounded-confounding envelope with a cross-dose copula tube.  That phenomenon is also absent from dosewise continuous-treatment sensitivity bands and from continuous-IV marginal distribution results, and it would give an interpretable certificate for local monotonicity under hidden confounding.

\begin{theorem}[Theorem 2: full-population mean slope ignores the copula]\label{thm:mean-collapse}
Under Assumptions~\ref{ass:support}--\ref{ass:nonempty} and the boundary convention \(S_\tau=[0,1]\), for every feasible \(q\) and every feasible \(\pi\),
\[
\theta(q,\pi)=\frac{\int_0^1 q_+(u)\,du-\int_0^1 q_-(u)\,du}{h}.
\]
Thus the copula restriction can affect the proposed slope bound only through rank-slice or other non-marginal derivative targets, not through the full-population average dose-response slope.
\end{theorem}

\paragraph{Why this is new and worth studying.}
This is a sanity theorem rather than the flagship contribution.  It prevents the proposal from claiming copula-based gains for an estimand where linearity of expectation makes the copula irrelevant.  The theorem also clarifies why the target is \(\theta_{\tau,h}\), a rank-slice marginal derivative, instead of the ordinary average derivative.

\section{Sanity-check corollaries}
\begin{corollary}[Full-population unrestricted copula reduces to marginal mean logic]\label{cor:frechet}
Under Assumptions~\ref{ass:support}, \ref{ass:civ-envelope}, \ref{ass:copula}, \ref{ass:nonempty}, the boundary convention \(S_\tau=[0,1]\), and \(\rho=1\), the copula tube imposes no adjacent-rank restriction and the slope envelope reduces to the mean-difference functional in Theorem~\ref{thm:mean-collapse}.  This is the full-population Fréchet/Makarov-style corner: arbitrary couplings are allowed, but the average finite-difference slope depends only on the marginal quantile envelopes.
\end{corollary}
Under the named assumptions, the reduction is immediate because \(|U_j-U_0|\le1\) is vacuous on \([0,1]\) and \(S_\tau=[0,1]\) removes the selected-subcoupling denominator.  For an interior rank slice this corollary is deliberately not claimed: conditioning on \(U_0\in S_\tau\) can skew the selected \(U_-\) and \(U_+\) marginals even when \(\rho=1\).

\begin{corollary}[No hidden confounding and comonotonic ranks]\label{cor:point-collapse}
Under Assumptions~\ref{ass:support}--\ref{ass:nonempty}, if \(\Gamma=1\) makes each \(\mathcal Q_j(P,1)\) a singleton \(\{Q_j^0\}\) and \(\rho=0\), then
\[
B_{1,0}^{\mathrm{slope}}(P,\tau,h)
=
\left\{
\frac{1}{h(\tau_U-\tau_L)}
\int_{\tau_L}^{\tau_U}\{Q_+^0(u)-Q_-^0(u)\}\,du
\right\}.
\]
\end{corollary}
Under the named assumptions, this collapses cleanly because \(\rho=0\) forces \(U_-=U_0=U_+\) and singleton quantile envelopes remove all marginal uncertainty.

\section{Proof-sketch route}
The mathematical route is finite convex analysis and a continuous-measure pasting argument.  Theorem~\ref{thm:transport-outer} follows by replacing the three rank variables by an \(M^3\)-cell probability table, imposing uniform one-dimensional marginals, zeroing out only cells whose product interval does not intersect the \(\rho\)-tube, using grid alignment so the selected \(U_0\)-cells have total mass \(\tau_U-\tau_L\), and lifting the bilinear products \(m_{abc}q_-(I_a)\) and \(m_{abc}q_+(I_c)\) to variables \(w^-_{abc}\) and \(w^+_{abc}\) bounded by linear envelope inequalities.  This proves a linear-program outer relaxation, not exact finite-grid sharpness; exactness would require additional nonlinear sharing constraints or a separate argument.  Theorem~\ref{thm:mean-collapse} and Corollary~\ref{cor:frechet} follow from the marginal constraints on \(\pi\) and Fubini's theorem under the explicit boundary convention \(S_\tau=[0,1]\).  For Conjecture~\ref{conj:pasting-sharpness}, the hard step is to construct one latent variable that simultaneously realizes the selected normalized sensitivity tilts \(\omega_j\) and the selected copula for \((U_-,U_0,U_+)\), while preserving the observed \(P_{Y,A,Z,X}\), the local reference laws \(R_j\), and continuous-IV first-stage restrictions.  The smallest useful witness for Conjecture~\ref{conj:sign-phase} is a two-rank-bin or three-rank-bin discretization in which \(q_+\) dominates \(q_-\) on the \(\rho\)-tube over \(S_\tau\), but the unrestricted coupling can pair low upper-dose ranks with high lower-dose ranks and pull the slope below zero.

\section{Honest scope flags}
The finite lifted transport relaxation and the full-population mean-slope collapse are routine mathematical claims once the envelope primitives are accepted.  Theorem~\ref{thm:transport-outer} is deliberately only an outer-bound theorem after v2, v3 adds the grid-alignment convention needed for its finite-slice denominator, and v4 fixes the finite-cell tube rule to the any-point admissibility convention appropriate for an outer bound; exact finite-grid sharpness remains part of the nonlinear/pasting problem.  The pasting theorem is open and is the main risk: dosewise sharp sensitivity envelopes may contain marginal quantile functions that cannot be induced jointly with the same continuous-IV full-data law, the same normalized marginal-sensitivity tilts, and the same rank copula.  The sign-certification phase transition is also conjectural at the field level until a concrete finite-rank witness is constructed and checked.  This v5 proposal deliberately avoids claiming that copulas sharpen the ordinary average derivative, because Theorem~\ref{thm:mean-collapse} says they do not, and restricts the \(\rho=1\) Fréchet/Makarov sanity reduction to the full-population slice \(S_\tau=[0,1]\).

\section{Iteration trail}
\begin{itemize}[leftmargin=2em]
\item v1 (cold-start) -- initial draft proposing quantile-copula sign certificates for rank-slice local dose-response slopes under continuous-IV sensitivity bounds; prior verdict: none.
\item v2 (revise) -- corrected the finite LP claim to a lifted outer relaxation, added the continuous-rank and full-population boundary conventions, corrected the Ishihara citation, and added IV quantile-regression prior art; prior verdict: REVISE.
\item v3 (revise) -- added a grid-alignment convention so Theorem~\ref{thm:transport-outer}'s finite-slice denominator matches selected rank mass, and corrected the Marmarelis et al.\ venue metadata; prior verdict: REVISE.
\item v4 (revise) -- defined finite-grid \(\rho\)-tube admissibility by any-point cell intersection for the outer-bound theorem, and added \citet{Kline2016} as the closest IV sign/direction comparator for Conjecture~\ref{conj:sign-phase}; prior verdict: REVISE.
\item v5 (revise) -- added \citet{Chesher2003} and \citet{Jun2009} as local-derivative comparators, pinned the \(\Gamma\)-sensitivity metric to normalized marginal-sensitivity tilts in the full-data law class, and restricted the \(\rho=1\) sanity reduction to \(S_\tau=[0,1]\); prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Baiocchi et~al.(2023)]{BaiocchiChengSmall2023}
Baiocchi, M., J. Cheng, and D. S. Small (2023).
\newblock Instrumental variables: to strengthen or not to strengthen?
\newblock \emph{Journal of the Royal Statistical Society: Series A} 186(4), 852--875.

\bibitem[Baitairian et~al.(2025)]{BaitairianSebastienJreichKatsahianGuilloux2025}
Baitairian, J.-B., B. Sebastien, R. Jreich, S. Katsahian, and A. Guilloux (2025).
\newblock Sharp bounds for continuous-valued treatment effects with unobserved confounders.
\newblock \emph{Biometrical Journal} 67(5), e70084.

\bibitem[Chernozhukov and Hansen(2005)]{ChernozhukovHansen2005}
Chernozhukov, V. and C. Hansen (2005).
\newblock An IV model of quantile treatment effects.
\newblock \emph{Econometrica} 73(1), 245--261.
\newblock doi: \href{https://doi.org/10.1111/j.1468-0262.2005.00570.x}{10.1111/j.1468-0262.2005.00570.x}.

\bibitem[Chernozhukov and Hansen(2006)]{ChernozhukovHansen2006}
Chernozhukov, V. and C. Hansen (2006).
\newblock Instrumental quantile regression inference for structural and treatment effect models.
\newblock \emph{Journal of Econometrics} 132(2), 491--525.
\newblock doi: \href{https://doi.org/10.1016/j.jeconom.2005.02.009}{10.1016/j.jeconom.2005.02.009}.

\bibitem[Chesher(2003)]{Chesher2003}
Chesher, A. (2003).
\newblock Identification in nonseparable models.
\newblock \emph{Econometrica} 71(5), 1405--1441.

\bibitem[D'Haultfoeuille and Fevrier(2015)]{DHaultfoeuilleFevrier2015}
D'Haultfoeuille, X. and P. Fevrier (2015).
\newblock Identification of nonseparable triangular models with discrete instruments.
\newblock \emph{Econometrica} 83(3), 1199--1210.

\bibitem[Dalal and Tchetgen Tchetgen(2025)]{DalalTchetgenTchetgen2025}
Dalal, A. and E. J. Tchetgen Tchetgen (2025).
\newblock Partial identification of causal effects for endogenous continuous treatments.
\newblock arXiv:2508.13946.

\bibitem[Fan and Park(2010)]{FanPark2010}
Fan, Y. and S. S. Park (2010).
\newblock Sharp bounds on the distribution of treatment effects and their statistical inference.
\newblock \emph{Econometric Theory} 26(3), 931--951.

\bibitem[Firpo and Ridder(2019)]{FirpoRidder2019}
Firpo, S. and G. Ridder (2019).
\newblock Partial identification of the treatment effect distribution and its functionals.
\newblock \emph{Journal of Econometrics} 213(1), 210--234.

\bibitem[Jesson et~al.(2022)]{JessonDouglasManshausenSolalMeinshausenStierGalShalit2022}
Jesson, A., A. Douglas, P. Manshausen, M. Solal, N. Meinshausen, C. Stier, Y. Gal, and U. Shalit (2022).
\newblock Scalable sensitivity and uncertainty analysis for causal-effect estimates of continuous-valued interventions.
\newblock \emph{Advances in Neural Information Processing Systems} 35.

\bibitem[Jun(2009)]{Jun2009}
Jun, S. J. (2009).
\newblock Local structural quantile effects in a model with a nonseparable control variable.
\newblock \emph{Journal of Econometrics} 151(1), 82--97.

\bibitem[Imbens and Newey(2009)]{ImbensNewey2009}
Imbens, G. W. and W. K. Newey (2009).
\newblock Identification and estimation of triangular simultaneous equations models without additivity.
\newblock \emph{Econometrica} 77(5), 1481--1512.
\newblock doi: \href{https://doi.org/10.3982/ECTA7108}{10.3982/ECTA7108}.

\bibitem[Ishihara(2021)]{Ishihara2021}
Ishihara, T. (2021).
\newblock Partial identification of nonseparable models using binary instruments.
\newblock \emph{Econometric Theory} 37, 817--848.
\newblock doi: \href{https://doi.org/10.1017/S0266466620000353}{10.1017/S0266466620000353}.

\bibitem[Kasy(2014)]{Kasy2014}
Kasy, M. (2014).
\newblock Instrumental variables with unrestricted heterogeneity and continuous treatment.
\newblock \emph{Review of Economic Studies} 81(4), 1614--1636.

\bibitem[Kline(2016)]{Kline2016}
Kline, B. (2016).
\newblock Identification of the direction of a causal effect by instrumental variables.
\newblock \emph{Journal of Business \& Economic Statistics} 34(2), 176--184.
\newblock doi: \href{https://doi.org/10.1080/07350015.2015.1021925}{10.1080/07350015.2015.1021925}.

\bibitem[Madigasekara et~al.(2024)]{MadigasekaraPoskittZhangZhao2024}
Madigasekara, H., D. S. Poskitt, L. Zhang, and X. Zhao (2024).
\newblock Partial identification of distributional treatment effects in panel data using copula equality assumptions.
\newblock arXiv:2411.04450.

\bibitem[Marmarelis et~al.(2023)]{MarmarelisHaddadJessonJahanshadGalstyanVerSteeg2023}
Marmarelis, M., E. Haddad, A. Jesson, N. Jahanshad, Y. Galstyan, and G. Ver Steeg (2023).
\newblock Partial identification of dose responses with hidden confounders.
\newblock \emph{Proceedings of the 39th Conference on Uncertainty in Artificial Intelligence}, PMLR 216.

\bibitem[Torgovitsky(2015)]{Torgovitsky2015}
Torgovitsky, A. (2015).
\newblock Identification of nonseparable models using instruments with small support.
\newblock \emph{Econometrica} 83(3), 1185--1197.
\end{thebibliography}

\end{document}
