% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_mediation\_proxy, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_mediation\_proxy} / \texttt{v1}%
  \\ \large\textit{Joint sharp proxy-null geometry for natural mediation effects when proximal completeness fails}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid = pid_mediation_proxy
specialization = v1
anchor_cluster = PartialID / mediation bounds with negative-control proxies
observable distribution P = law(A,M,Y,Z,W,X) with A,M,Y,Z,W binary and X finite
parameter theta = (PNDE,TNIE), where
  PNDE = E[Y(1,M(0))-Y(0,M(0))]
  TNIE = E[Y(1,M(1))-Y(1,M(0))]
identifying restrictions =
  consistency and bounded outcomes; randomized single binary treatment A;
  finite latent post-treatment mediator-outcome confounder U;
  negative-control proxy exclusions for binary treatment-inducing proxy Z
    and binary outcome-inducing proxy W;
  latent mediator-outcome exchangeability given (A,U,X);
  positivity for all observed (A,M,Z,W,X) cells used in the bridge equations;
  existence of finite outcome-confounding bridge arrays h_{a,m,x}(w);
  proxy-rank regime rank(K_{a,m,x}) in {1,2}, where
    K_{a,m,x}(z,w)=P(W=w | A=a,M=m,Z=z,X=x).
bounding functional =
  the sharp joint projection of the finite latent/proxy-response feasible
  set onto (PNDE,TNIE); in the rank-one proxy-null regime the proposed
  closed form is the two-dimensional affine zonotope generated by the
  bridge-null intervals and their PNDE/TNIE loading vectors, with
  observable proxy-separation inequalities certifying strict improvement
  over no-proxy mediation bounds.
\end{verbatim}

\begin{abstract}
This proposal asks for sharp partial-identification bounds for natural direct and indirect effects in a single-binary-treatment mediation design when the mediator-outcome confounder is latent but two negative-control proxies are observed.  The closest point-identification result is proximal mediation analysis, which uses completeness of proxy bridge equations to identify natural effects.  The proposed kernel is the boundary case deliberately left outside that point-identification theorem: when the binary proxy bridge matrix has rank one, the natural direct and indirect effects need not both explode to the no-proxy Manski bounds.  I conjecture a finite proxy-null phase diagram in which the joint PNDE/TNIE set is a sharp affine zonotope, with coordinate intervals as projections and with a sign-agreement criterion for when coordinate endpoints are jointly attainable.  A second conjecture gives observable proxy-separation inequalities that certify and quantify strict improvement over no-proxy mediation bounds.  Resolving these claims would turn weak or collinear negative controls from a qualitative failure of proximal assumptions into an auditable sharp-bound calculation.
\end{abstract}

\section{Introduction}
Natural mediation effects are attractive because they decompose a treatment effect into pathways through and around a mediator, but they are fragile when the mediator-outcome relation is confounded.  Negative-control and proximal methods offer a way to use proxy variables for latent confounding rather than assuming it away.  In applications, however, proxy variables are often weak, redundant, or nearly collinear, so the practical question is not only whether a bridge equation is invertible but what remains sharply learnable when it is not.

The main finding proposed here is Conjecture~\ref{conj:joint-null}: in the minimal binary-proxy mediation design, failure of proximal completeness has a structured sharp joint identified set.  When the bridge matrix has rank two, the standard proximal mediation formula is recovered as a singleton.  When the bridge matrix has rank one, all bridge solutions differ by one null direction, and the joint PNDE/TNIE set is conjectured to be the two-dimensional affine zonotope generated by the cell-specific bridge-null intervals and the paired natural-effect loading vectors.

What is new is the proxy-null joint geometry, not the existence of an LP or the standard proximal point-identification formula.  \citet{DukesShpitserTchetgen2023} establish point identification of natural effects under proximal bridge conditions, \citet{GhassamiShpitserTchetgen2023} develop proxy-based partial-identification bounds without completeness for total-effect and hidden-mediator settings, and \citet{ZhangLiMiaoTchetgen2023} studies proximal inference when bridge solutions are nonunique.  The proposed gap is the rank-deficient natural-mediation middle regime: a proxy pair that fails completeness may still impose a coupled two-dimensional sharp set, make some coordinate endpoints mutually unattainable, and strictly improve on no-proxy bounds through observable proxy-separation inequalities rather than through completeness.

This proposal sits in the partial-identification cluster, specifically mediation bounds and proximal negative-control inference.  It uses finite response-type and projection logic in the spirit of Manski and Balke--Pearl bounds, but the kernel is mediation-specific: the same proxy-null direction feeds PNDE and TNIE through different cross-world mediator weights.  It is not a graphical-identification or panel-regression proposal.

\section{Related work}
\citet{RobinsGreenland1992} and \citet{Pearl2001} introduce the counterfactual direct and indirect effects whose natural versions are targeted here.  \citet{AvinShpitserPearl2005} show that path-specific effects can fail to be identified under exposure-induced intermediate confounding, motivating an explicitly partial-identification target.  \citet{ImaiKeeleYamamoto2010} give a widely used identification and sensitivity-analysis framework for mediation under sequential ignorability; the present proposal replaces sequential ignorability for the mediator-outcome relation by proxy restrictions.  \citet{TchetgenShpitser2012} develop semiparametric theory for marginal natural effects under observed confounding control; their estimands and robustness perspective are inherited but the latent-confounding problem is different.

\citet{MiaoShiLiTchetgen2024} and \citet{PenningDeVriesGroenwold2023} summarize how double negative controls can correct, rather than merely detect, unmeasured confounding through bridge functions.  \citet{DukesShpitserTchetgen2023} is the closest proximal-mediation paper: it gives proximal identification results and efficient estimation for natural direct and indirect effects using proxies, but its positive result assumes sufficient bridge uniqueness rather than classifying sharp sets when uniqueness fails.  \citet{GhassamiShpitserTchetgen2023} is the closest proxy partial-identification preprint because it bounds causal effects using proxies without completeness; the proposed contribution is a closed-form binary natural-mediation joint-set geometry rather than a generic proxy-bound construction for total effects and hidden-mediator targets.  \citet{ZhangLiMiaoTchetgen2023} is the closest bridge-nonuniqueness paper because it permits nonunique proximal bridge solutions while targeting counterfactual outcome means; the proposed contribution tracks how two natural-mediation functionals load jointly on the same finite bridge-null coordinates.  \citet{SunYe2021} identifies natural effects with unmeasured mediator-outcome confounding through heteroskedasticity restrictions; it is relevant as a different point-identification route that does not study proxy-rank failure.  \citet{DingVanderWeele2016} provide sharp sensitivity bounds for mediation under unmeasured mediator-outcome confounding, giving a no-proxy comparator for the proposed proxy-tightening statement.

\citet{MilesKankiMeloniTchetgen2017} derive partial-identification bounds for the natural indirect effect when key cross-world or exposure-induced-confounding assumptions are relaxed; the proposed TNIE bridge-null interval is narrower only when negative-control proxy restrictions add information.  The companion direct-effect comparator is \citet{MilesKankiMeloniTchetgen2015}, which treats partial identification of the pure natural direct effect in an arXiv preprint.  \citet{CaiKurokiPearlTian2008} apply Balke--Pearl symbolic LP methods to direct-effect bounds with a confounded intermediate variable; the present proposal follows the same finite-sharpness philosophy but with proxy equations and natural-effect targets.  \citet{LuoGeng2016} give no-proxy bounds for direct and indirect effects on a continuous endpoint, making them the direct ancestor for the no-proxy comparator that \citet{HanLuoZhangGu2026} identify and extend under partially observed mediator-endpoint confounders; the proposed setting instead observes proxies for the latent confounder and asks what happens at proxy rank deficiency.  \citet{GabrielSachsSjolander2023} show that sharp bounds for decomposition effects with multiple binary mediators cannot generally be obtained by separately combining sharp bounds for components; this is a caution for the PNDE/TNIE pair here, where the same proxy-null coordinate couples both intervals.

Named literature checklist for Stage -0.5 review: \citet{DukesShpitserTchetgen2023} is the point-identification comparator for Theorem~\ref{thm:complete-collapse} and Conjecture~\ref{conj:joint-null}; \citet{GhassamiShpitserTchetgen2023} is the closest proxy partial-identification comparator for Conjectures~\ref{conj:joint-null} and \ref{conj:tightening}; \citet{ZhangLiMiaoTchetgen2023} is the bridge-nonuniqueness comparator for Conjecture~\ref{conj:joint-null}; \citet{MilesKankiMeloniTchetgen2017} is the no-proxy TNIE partial-identification comparator for Conjecture~\ref{conj:tightening}; \citet{CaiKurokiPearlTian2008} is the finite LP direct-effect-bound comparator for Conjecture~\ref{conj:tightening}; \citet{LuoGeng2016} is the no-proxy direct/indirect-bound ancestor for Conjecture~\ref{conj:tightening}; \citet{GabrielSachsSjolander2023} is the decomposition-bounds warning against rectangularizing jointly coupled effects in Conjecture~\ref{conj:joint-null}; \citet{DingVanderWeele2016} is the sharp sensitivity-bound comparator for no-proxy unmeasured mediator-outcome confounding in Conjecture~\ref{conj:tightening}; and \citet{HanLuoZhangGu2026} is the partially observed mediator-endpoint-confounder comparator for Conjecture~\ref{conj:tightening}.

The in-catalogue ThmSmith prior art is sparse for this anchor.  \texttt{doc/API.md} Section 3 records \texttt{ThmSmith/PartialID/} as an empty seed catalogue for Manski-family bounds, Balke--Pearl bounds, IV bounds, sensitivity analysis, shape restrictions, and missing-data bounds.  The closest banked PartialID artifacts are dynamic IV compliance and long-term surrogate proposals, but they target compliance-memory or surrogate-index drift rather than natural mediation effects with a negative-control proxy pair.

\section{Formal setup}
The observed law is \(P=P_{A,M,Y,Z,W,X}\), where \(A\in\{0,1\}\) is the randomized treatment, \(M\in\{0,1\}\) is the mediator, \(Y\in[0,1]\) is the outcome, \(Z\in\{0,1\}\) is a treatment-inducing negative-control proxy, \(W\in\{0,1\}\) is an outcome-inducing negative-control proxy, and \(X\) is a finite baseline covariate.  The latent variable \(U\) is a finite post-treatment mediator-outcome confounder that may be associated with \(M\), \(Y\), \(Z\), and \(W\).  The target is \(\theta(P^\star)=(\mathrm{PNDE}(P^\star),\mathrm{TNIE}(P^\star))\) for latent causal laws \(P^\star\) compatible with \(P\):
\[
\mathrm{PNDE}=\E\{Y(1,M(0))-Y(0,M(0))\},\qquad
\mathrm{TNIE}=\E\{Y(1,M(1))-Y(1,M(0))\}.
\]

For each \((a,m,x)\), define the binary proxy bridge matrix
\[
K_{a,m,x}(z,w)=P(W=w\mid A=a,M=m,Z=z,X=x),
\]
and the observed outcome vector \(q_{a,m,x}(z)=\E(Y\mid A=a,M=m,Z=z,X=x)\).  A bridge vector \(h_{a,m,x}\in\R^2\) satisfies \(K_{a,m,x}h_{a,m,x}=q_{a,m,x}\).  If \(K_{a,m,x}\) has rank one and the bridge equation is feasible, fix a nonzero null vector \(\nu_{a,m,x}\) with \(K_{a,m,x}\nu_{a,m,x}=0\), a reference solution \(h^0_{a,m,x}\), and the bounded bridge interval
\[
T_{a,m,x}(P)=\{t\in\R: 0\le h^0_{a,m,x}(w)+t\nu_{a,m,x}(w)\le 1\text{ for }w=0,1\}.
\]
Let \(\mathcal N=\{(a,m,x):\operatorname{rank}(K_{a,m,x})=1\}\) be the set of proxy-null cells.  For a reference bridge array \(h^0\), define \(\theta^0_D=\mathrm{PNDE}(h^0)\) and \(\theta^0_I=\mathrm{TNIE}(h^0)\).
For \(r,a\in\{0,1\}\), define the observed mediator and proxy weights
\[
\pi_{r,m,x}=P(M=m\mid A=r,X=x),\qquad
\omega_{a,m,x}(w)=P(W=w\mid A=a,M=m,X=x),
\]
and for any bridge array \(h\) define
\[
\Psi_a(r;h)=\sum_x P(X=x)\sum_{m\in\{0,1\}}\pi_{r,m,x}
\sum_{w\in\{0,1\}}\omega_{a,m,x}(w)h_{a,m,x}(w).
\]
The finite proximal mediation functional is
\(\mathrm{PNDE}(h)=\Psi_1(0;h)-\Psi_0(0;h)\) and
\(\mathrm{TNIE}(h)=\Psi_1(1;h)-\Psi_1(0;h)\).  Let \(\Theta_{\mathrm{joint}}(P)\) be the set of all \((\mathrm{PNDE},\mathrm{TNIE})\) generated by finite latent laws and bridge arrays satisfying Assumptions~\ref{ass:data}--\ref{ass:rank}.  Its coordinate projections are denoted
\[
\Theta_D(P)=\{d:\exists n,\ (d,n)\in\Theta_{\mathrm{joint}}(P)\},\qquad
\Theta_{\mathrm{NIE}}(P)=\{n:\exists d,\ (d,n)\in\Theta_{\mathrm{joint}}(P)\}.
\]
The bounding functional is the joint set \(\Theta_{\mathrm{joint}}(P)\) together with its coordinate projections \((\Theta_D(P),\Theta_{\mathrm{NIE}}(P))\).
For \(j=(a,m,x)\in\mathcal N\), write \(T_j(P)=[\ell_j,u_j]\) and \(\lambda_j(P)=(\lambda^D_j(P),\lambda^I_j(P))\), with \(\lambda^{\mathrm{NIE}}_j\) used interchangeably for \(\lambda^I_j\).  The proposed joint proxy-null set is
\[
Z(P)=\left\{(\theta^0_D,\theta^0_I)+\sum_{j\in\mathcal N}t_j\lambda_j(P):t_j\in[\ell_j,u_j]\right\}.
\]
For \(E\in\{D,\mathrm{NIE}\}\) and endpoint \(s\in\{\min,\max\}\), define the endpoint selector
\[
\tau^{E,s}_j=
\begin{cases}
u_j,& s=\max\text{ and }\lambda^E_j\ge0,\\
\ell_j,& s=\max\text{ and }\lambda^E_j<0,\\
\ell_j,& s=\min\text{ and }\lambda^E_j\ge0,\\
u_j,& s=\min\text{ and }\lambda^E_j<0.
\end{cases}
\]

For Conjecture~\ref{conj:tightening}, let \(\mathcal L^0(P)\) be the no-proxy finite response-type polytope obtained by dropping \(Z,W\) and matching only the observed law of \((A,M,Y,X)\).  Let \(\mathcal L^{\mathrm{proxy}}(P)\) be the proxy-response polytope matching \(P\) and satisfying the proxy exclusions, and let \(\rho:\mathcal L^{\mathrm{proxy}}(P)\to\mathcal L^0(P)\) forget the proxy response coordinates.  For \(E\in\{D,\mathrm{NIE}\}\) and endpoint \(s\in\{\min,\max\}\), write \(F^0_{E,s}(P)\) for the exposed face of \(\mathcal L^0(P)\) attaining the no-proxy endpoint for effect \(E\).  The endpoint is called proxy-compatible when \(\rho(\mathcal L^{\mathrm{proxy}}(P))\cap F^0_{E,s}(P)\neq\varnothing\).
Let \(b^{\mathrm{proxy}}(P)\) collect the observed proxy cell probabilities \(P(Y=y,M=m,Z=z,W=w,A=a,X=x)\) and \(b^0(P)\) collect the observed no-proxy cell probabilities \(P(Y=y,M=m,A=a,X=x)\).  Let \(C_{E,s}(P)\) be the convex hull of proxy cell-probability vectors \(b^{\mathrm{proxy}}\) generated by no-proxy endpoint-completing response types in \(F^0_{E,s}(P)\).  Define the observable separation margin
\[
\Delta_{E,s}(P)=\sup_{\alpha:\|\alpha\|_1\le1}
\left\{\alpha^\transpose b^{\mathrm{proxy}}(P)-
\sup_{c\in C_{E,s}(P)}\alpha^\transpose c\right\}_+.
\]
The width reduction at endpoint \(s\) is
\[
R_{E,s}(P)=
\begin{cases}
\sup_{\ell\in F^0_{E,\max}(P)}E(\ell)-\sup_{r\in\mathcal L^{\mathrm{proxy}}(P)}E(\rho r),&s=\max,\\
\inf_{r\in\mathcal L^{\mathrm{proxy}}(P)}E(\rho r)-\inf_{\ell\in F^0_{E,\min}(P)}E(\ell),&s=\min,
\end{cases}
\]
where \(E(\cdot)\) is the PNDE or TNIE linear functional.
Let \(L_{E,s}(P)\) be the smallest finite constant such that changing the proxy cell-probability vector by \(v\) within the endpoint-face relaxation can change the endpoint value of \(E\) by at most \(L_{E,s}(P)\|v\|_\infty\); because all response spaces are finite and \(Y\in[0,1]\), this constant is finite whenever the endpoint face is nonempty.  The numeric ratio certificate in Conjecture~\ref{conj:tightening} is asserted only on nonempty endpoint faces with \(L_{E,s}(P)>0\).  If \(L_{E,s}(P)=0\), the quotient \(\Delta_{E,s}(P)/L_{E,s}(P)\) is not formed; the conjecture retains only the qualitative endpoint-incompatibility claim and the exact LP definition of \(R_{E,s}(P)\).  If \(F^0_{E,s}(P)\) or \(C_{E,s}(P)\) is empty, endpoint \(s\) is treated as a vacuous boundary case and is excluded from the strict-tightening equivalence.

\begin{verbatim}
qid = pid_mediation_proxy
specialization = v1
anchor_cluster = PartialID / mediation bounds with negative-control proxies
observable distribution P = law(A,M,Y,Z,W,X) with A,M,Y,Z,W binary and X finite
parameter theta = (PNDE,TNIE), where
  PNDE = E[Y(1,M(0))-Y(0,M(0))]
  TNIE = E[Y(1,M(1))-Y(1,M(0))]
identifying restrictions =
  consistency and bounded outcomes; randomized single binary treatment A;
  finite latent post-treatment mediator-outcome confounder U;
  negative-control proxy exclusions for binary treatment-inducing proxy Z
    and binary outcome-inducing proxy W;
  latent mediator-outcome exchangeability given (A,U,X);
  positivity for all observed (A,M,Z,W,X) cells used in the bridge equations;
  existence of finite outcome-confounding bridge arrays h_{a,m,x}(w);
  proxy-rank regime rank(K_{a,m,x}) in {1,2}, where
    K_{a,m,x}(z,w)=P(W=w | A=a,M=m,Z=z,X=x).
bounding functional =
  the sharp joint projection of the finite latent/proxy-response feasible
  set onto (PNDE,TNIE); in the rank-one proxy-null regime the proposed
  closed form is the two-dimensional affine zonotope generated by the
  bridge-null intervals and their PNDE/TNIE loading vectors, with
  observable proxy-separation inequalities certifying strict improvement
  over no-proxy mediation bounds.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Observed finite bounded data]\label{ass:data}
The variables have the domains stated in Section 3, \(X\) has finite support, and \(0\le Y\le1\).  All conditional probabilities and conditional means appearing in \(K_{a,m,x}\), \(q_{a,m,x}\), and the mediator weights below are defined on positive-probability cells.
\end{assumption}

\begin{assumption}[Consistency and randomized treatment]\label{ass:consistency}
Observed \(M,Y,Z,W\) equal their factual potential values under the realized treatment, and \(A\) is randomized conditional on \(X\): \(A\) is independent of all potential mediator, outcome, proxy, and latent-confounder response types given \(X\).
\end{assumption}

\begin{assumption}[Latent mediator-outcome exchangeability]\label{ass:latent-exchange}
There exists a finite latent \(U\) such that, conditional on \((A,U,X)\), the mediator assignment is unconfounded for the nested outcome response and, conditional on \((A,M,U,X)\), the outcome response is independent of the observed proxy \(Z\).  This is the latent exchangeability condition that the negative-control proxies are intended to operationalize.
\end{assumption}

\begin{assumption}[Negative-control proxy exclusions]\label{ass:proxy-exclusion}
The proxy \(Z\) has no direct effect on \(Y\) after conditioning on \((A,M,U,X)\), and the proxy \(W\) is not affected by interventions on \(M\) after conditioning on \((A,U,X)\).  Conditional on \((A,M,U,X)\), \(Z\) and \(W\) are independent except through their common dependence on \(U\).
\end{assumption}

\begin{assumption}[Bridge feasibility and boundedness]\label{ass:bridge}
For every positive-probability \((a,m,x)\), the equation \(K_{a,m,x}h_{a,m,x}=q_{a,m,x}\) has at least one solution \(h_{a,m,x}\in[0,1]^2\).  In the rank-one case, \(h^0_{a,m,x}\), \(\nu_{a,m,x}\), and \(T_{a,m,x}(P)\) are defined as in Section 3.
\end{assumption}

\begin{assumption}[Proxy-rank regime]\label{ass:rank}
For each \((a,m,x)\), the matrix \(K_{a,m,x}\) has rank two or rank one.  The rank-two cells are called complete cells, and the rank-one cells are called proxy-null cells.
\end{assumption}

\begin{assumption}[Natural-effect loading definitions]\label{ass:loadings}
For each proxy-null cell, define
\[
\eta_{a,m,x}(P)=\sum_{w\in\{0,1\}}\omega_{a,m,x}(w)\nu_{a,m,x}(w).
\]
The bridge-null coefficient in PNDE is
\[
\lambda^{D}_{a,m,x}(P)=P(X=x)\pi_{0,m,x}\eta_{a,m,x}(P)\{\one(a=1)-\one(a=0)\},
\]
and the bridge-null coefficient in TNIE is
\[
\lambda^{I}_{a,m,x}(P)=P(X=x)\one(a=1)(\pi_{1,m,x}-\pi_{0,m,x})\eta_{1,m,x}(P).
\]
These coefficients are exactly the scalar multipliers of the null parameter \(t\) after replacing \(h_{a,m,x}\) by \(h^0_{a,m,x}+t\nu_{a,m,x}\) in the finite proximal mediation functional defined in Section 3.
\end{assumption}

\begin{assumption}[No-proxy endpoint faces]\label{ass:endpoint-faces}
The no-proxy and proxy response-type polytopes \(\mathcal L^0(P)\) and \(\mathcal L^{\mathrm{proxy}}(P)\), the forgetting map \(\rho\), the endpoint faces \(F^0_{E,s}(P)\), the proxy endpoint hulls \(C_{E,s}(P)\), the observable separation margins \(\Delta_{E,s}(P)\), the width reductions \(R_{E,s}(P)\), and the finite constants \(L_{E,s}(P)\) are the finite objects defined in Section 3.  An endpoint-completing latent response type means a response type with positive mass in at least one point of \(F^0_{E,s}(P)\).  Such a type is endpoint-compatible when it appears with the same no-proxy response coordinates in some element of \(\rho(\mathcal L^{\mathrm{proxy}}(P))\cap F^0_{E,s}(P)\).  The ratio certificate in Conjecture~\ref{conj:tightening} additionally assumes \(F^0_{E,s}(P)\neq\varnothing\), \(C_{E,s}(P)\neq\varnothing\), and \(L_{E,s}(P)>0\); when \(L_{E,s}(P)=0\), no division by \(L_{E,s}(P)\) is made.
\end{assumption}

\begin{assumption}[Sequential-ignorability corner]\label{ass:seq-ignorability}
There is no latent mediator-outcome confounding given \((A,M,X)\), so the usual mediation formula under sequential ignorability is valid for PNDE and TNIE.  This assumption is used only for the sanity-check reduction, not for the main proxy-null conjectures.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: complete-proxy collapse]\label{thm:complete-collapse}
Under Assumptions~\ref{ass:data}--\ref{ass:rank}, if every \(K_{a,m,x}\) has rank two, then every bridge vector \(h_{a,m,x}\) is unique.  Consequently \(\Theta_{\mathrm{joint}}(P)\) is a singleton for the two natural-effect coordinates and equals the proximal mediation functional obtained by plugging the unique bridge arrays into the mediation formula.
\end{theorem}

\paragraph{Why this is new and worth studying.}
This theorem is not the novelty claim; it is the sanity-preserving corner that recovers \citet{DukesShpitserTchetgen2023} in the finite binary-proxy notation used here.  Its value is to force the partial-identification proposal to agree with the closest point-identification result before moving to the rank-deficient boundary.

\begin{conjecture}[Conjecture 1: joint rank-one proxy-null zonotope (NOT YET PROVED)]\label{conj:joint-null}
Assume Assumptions~\ref{ass:data}--\ref{ass:loadings}.  Suppose the only non-complete bridge cells are rank-one proxy-null cells.  Then the sharp joint identified set is
\[
\Theta_{\mathrm{joint}}(P)=Z(P)
=\left\{(\theta^0_D,\theta^0_I)+\sum_{j\in\mathcal N}t_j\lambda_j(P):t_j\in T_j(P)\right\}.
\]
Consequently the previously advertised coordinate intervals are only the projections of this two-dimensional affine zonotope:
\[
\Theta_D(P)=\theta^0_D+\sum_{j\in\mathcal N}\lambda^D_j(P)T_j(P),\qquad
\Theta_{\mathrm{NIE}}(P)=\theta^0_I+\sum_{j\in\mathcal N}\lambda^I_j(P)T_j(P).
\]
For any two coordinate endpoints \((D,s_D)\) and \((\mathrm{NIE},s_I)\), the two endpoint values are jointly attainable if and only if the endpoint selectors agree on every nondegenerate cell with \(\lambda^D_j\lambda^I_j\neq0\):
\[
\tau^{D,s_D}_j=\tau^{\mathrm{NIE},s_I}_j
\quad\text{for all }j\in\mathcal N\text{ with }u_j>\ell_j\text{ and }\lambda^D_j\lambda^I_j\neq0.
\]
Thus two sharp coordinate bounds can be individually valid but cannot generally be combined into a rectangle; sign-discordant loading vectors carve out missing corners of the joint PNDE/TNIE set.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
The closest papers are \citet{DukesShpitserTchetgen2023}, which treats the complete-proxy mediation case, \citet{GhassamiShpitserTchetgen2023}, which gives proxy partial-identification bounds without completeness for related causal-effect targets, and \citet{ZhangLiMiaoTchetgen2023}, which studies nonunique bridge solutions for counterfactual means.  The gap is not another coordinate interval: the conjecture gives the coupled joint geometry, including the exact missing-corner criterion induced by sign-discordant PNDE and TNIE loadings.  Proving it would prevent the common but invalid practice of pairing separately sharp PNDE and TNIE endpoints, while still giving applied proximal mediation a diagnostic for which weak proxy dimensions matter for each effect.

\begin{conjecture}[Conjecture 2: strict proxy tightening over no-proxy bounds (NOT YET PROVED)]\label{conj:tightening}
Under Assumptions~\ref{ass:data}--\ref{ass:endpoint-faces}, compare the coordinate projections from Conjecture~\ref{conj:joint-null} with the corresponding no-proxy finite mediation bounds obtained after dropping \(Z,W\) and retaining only the observed law of \((A,M,Y,X)\).  For \(E\in\{D,\mathrm{NIE}\}\) and \(s\in\{\min,\max\}\), the proxy-null bound is strictly tighter than the no-proxy endpoint \(s\) for effect \(E\) if and only if there exists an observable proxy-separation contrast \(\alpha\) with
\[
\alpha^\transpose b^{\mathrm{proxy}}(P)>
\sup_{c\in C_{E,s}(P)}\alpha^\transpose c,
\]
equivalently \(\Delta_{E,s}(P)>0\).  Moreover \(R_{E,s}(P)\) is the exact endpoint width reduction.  On the nonempty-face branch where \(C_{E,s}(P)\neq\varnothing\) and \(L_{E,s}(P)>0\), every separating contrast supplies a computable lower certificate
\[
R_{E,s}(P)\ge
\Delta_{E,s}(P)/L_{E,s}(P),
\]
where \(L_{E,s}(P)\) is the finite Lipschitz constant of the effect functional over the endpoint face in the norm dual to the contrast class.  If \(L_{E,s}(P)=0\), the quotient is undefined and is deliberately not used; the conjecture then claims only the qualitative equivalence \(\Delta_{E,s}(P)>0\) and the exact LP-computed reduction \(R_{E,s}(P)\).  In particular, a rank-one proxy pair can fail point identification and still strictly shorten a no-proxy natural-effect interval by violating an observable probability inequality that every no-proxy endpoint-completing latent response type must satisfy.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
\citet{GhassamiShpitserTchetgen2023} show that proxies can yield partial-identification bounds without completeness, while \citet{CaiKurokiPearlTian2008}, \citet{LuoGeng2016}, \citet{MilesKankiMeloniTchetgen2017}, and \citet{GabrielSachsSjolander2023} establish sharp-bounds traditions for direct, indirect, and decomposition effects.  They do not give an observable separator for when weak proxies exclude a natural-mediation endpoint face, nor do they quantify the endpoint width reduction from that exclusion.  This conjecture is worth studying because it separates informative weak proxies from decorative negative controls: a proxy can fail point identification and still certify, through a finite probability inequality, the exact loss of no-proxy endpoint attainability.

\section{Sanity-check corollaries}
\begin{corollary}[Sequential-ignorability corner]\label{cor:ignorability}
If Assumptions~\ref{ass:data}, \ref{ass:consistency}, and \ref{ass:seq-ignorability} hold, then \(K_{a,m,x}\) is irrelevant to the target and the formula reduces to the usual mediation formula under sequential ignorability.
\end{corollary}

\begin{corollary}[Complete-proxy corner]\label{cor:complete}
Under Assumptions~\ref{ass:data}--\ref{ass:rank}, if all \(K_{a,m,x}\) have rank two, Conjecture~\ref{conj:joint-null} reduces to Theorem~\ref{thm:complete-collapse} because \(\mathcal N\) is empty and \(Z(P)=\{(\theta^0_D,\theta^0_I)\}\).
\end{corollary}

\begin{corollary}[No-proxy fallback]\label{cor:noproxy}
If the proxy restrictions in Assumption~\ref{ass:proxy-exclusion} are dropped, the bounding functional is the finite response-type projection for natural direct and indirect effects with observed law \((A,M,Y,X)\), matching the Manski-style no-proxy partial-identification problem.  Under Assumption~\ref{ass:endpoint-faces}, this is exactly the optimization of the PNDE and TNIE linear functionals over \(\mathcal L^0(P)\), so the endpoint faces \(F^0_{E,s}(P)\) reduce to the usual no-proxy LP faces.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is finite-dimensional linear algebra, convex geometry, and finite-support sharpness.  First write the proximal mediation functional as a linear map from the bridge array \(h\) to \((\mathrm{PNDE},\mathrm{TNIE})\), with all mediator weights expanded as observed finite sums over \((m,x,w)\).  In full rank, invert each \(2\times2\) bridge matrix.  In rank one, solve each bridge equation as an affine line \(h^0+t\nu\), intersect that line with the unit square to obtain \(T_j(P)\), and map the product box \(\prod_jT_j(P)\) through the paired loading vectors \(\lambda_j(P)\).  The joint-set claim then becomes the assertion that this affine image is sharp, not merely outer, for the finite latent/proxy response model; the nonrectangular corner criterion follows from coordinate-wise linear optimization over a box.  The strict-tightening claim should follow from finite-dimensional separation: an endpoint face survives exactly when the observed proxy probability vector lies in the convex hull generated by endpoint-completing response types, and otherwise a Farkas separating contrast gives both the observable inequality and the endpoint-width lower certificate.  The delicate boundary cases are zero mediator weights, singleton bridge-null intervals, sign-discordant loadings, empty endpoint faces, and separating contrasts with zero Lipschitz denominator.

\section{Honest scope flags}
The complete-proxy collapse is labelled as a theorem because it is routine matrix inversion once the finite bridge notation is accepted, and it is not claimed as novel.  The joint rank-one zonotope and observable strict-tightening certificate are conjectures and are the novelty-bearing claims.  The strongest assumption is the finite binary proxy setup: it is intentionally narrow so that sharpness can be checked exactly before asking for continuous or multi-category proxies.  The phrase ``post-treatment confounder'' is implemented here as a latent variable measured after treatment but before mediator and outcome; if the reviewer requires fully exposure-induced \(U(a)\) response types, the bridge equations should be lifted to the corresponding response-type table rather than weakened silently.  No statements were withdrawn in v1 or v2.  Revision v3 withdraws the weaker coordinate-only reading of Conjecture 1 as the flagship kernel and replaces it with a joint-set conjecture; the coordinate intervals remain only as projections.  Revision v4 does not change the kernel; it adds the reviewer-requested named literature checklist and makes Conjecture~\ref{conj:tightening}'s lower certificate inactive when \(L_{E,s}(P)=0\) or endpoint hulls are empty.
Revision v2 changes notation only where the reviewer found clashes: \(\Theta_{\mathrm{joint}}(P)\) denotes the joint set, while \(\Theta_D(P)\) and \(\Theta_{\mathrm{NIE}}(P)\) denote coordinate intervals.  It also makes Conjecture~\ref{conj:tightening}'s endpoint language an LP face condition rather than an informal response-type phrase.

\section{Iteration trail}
\begin{itemize}
\item v1 (cold-start) --- initial draft proposing the rank-deficient proximal-mediation proxy-null phase diagram; prior verdict: none.
\item v2 (revise) --- added closer proxy partial-identification literature, corrected the Miles et al. comparator, separated joint and coordinate identified-set notation, made the loading formulas explicit, and formalized endpoint compatibility as an LP face condition; prior verdict: REVISE.
\item v3 (revise) --- upgraded Conjecture 1 from coordinate intervals to a joint affine-zonotope sharp-set claim, replaced Conjecture 2's generic face-emptiness statement by observable proxy-separation inequalities with width-reduction certificates, and corrected the Ghassami--Shpitser--Tchetgen citation to a preprint; prior verdict: REVISE.
\item v4 (revise) --- added the named literature checklist including Luo--Geng as the no-proxy direct/indirect-bound ancestor, and guarded Conjecture 2's lower certificate against \(L_{E,s}=0\) and empty endpoint-hull boundary cases; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Avin, Shpitser, and Pearl(2005)]{AvinShpitserPearl2005}
Avin, C., Shpitser, I., and Pearl, J. (2005).
Identifiability of path-specific effects.
In \emph{Proceedings of the Nineteenth International Joint Conference on Artificial Intelligence}, 357--363.

\bibitem[Cai, Kuroki, Pearl, and Tian(2008)]{CaiKurokiPearlTian2008}
Cai, Z., Kuroki, M., Pearl, J., and Tian, J. (2008).
Bounds on direct effects in the presence of confounded intermediate variables.
\emph{Biometrics}, 64(3), 695--701.

\bibitem[Ding and VanderWeele(2016)]{DingVanderWeele2016}
Ding, P. and VanderWeele, T. J. (2016).
Sharp sensitivity bounds for mediation under unmeasured mediator-outcome confounding.
\emph{Biometrika}, 103(2), 483--490.

\bibitem[Dukes, Shpitser, and Tchetgen Tchetgen(2023)]{DukesShpitserTchetgen2023}
Dukes, O., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
Proximal mediation analysis.
\emph{Biometrika}, 110(4), 973--987.

\bibitem[Gabriel, Sachs, and Sjolander(2023)]{GabrielSachsSjolander2023}
Gabriel, E. E., Sachs, M. C., and Sjolander, A. (2023).
Sharp nonparametric bounds for decomposition effects with two binary mediators.
\emph{Journal of the American Statistical Association}, 118(544), 2446--2453.

\bibitem[Ghassami, Shpitser, and Tchetgen Tchetgen(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. (2023).
Partial identification of causal effects using proxy variables.
arXiv:2304.04374.

\bibitem[Han, Luo, Zhang, and Gu(2026)]{HanLuoZhangGu2026}
Han, Y., Luo, P., Zhang, W., and Gu, X. (2026).
Bounds and identification on direct and indirect effects under partially observed mediator-endpoint confounders.
\emph{Journal of Multivariate Analysis}, 213, 105565.

\bibitem[Imai, Keele, and Yamamoto(2010)]{ImaiKeeleYamamoto2010}
Imai, K., Keele, L., and Yamamoto, T. (2010).
Identification, inference and sensitivity analysis for causal mediation effects.
\emph{Statistical Science}, 25(1), 51--71.

\bibitem[Luo and Geng(2016)]{LuoGeng2016}
Luo, P. and Geng, Z. (2016).
Bounds on direct and indirect effects of treatment on a continuous endpoint.
\emph{ACM Transactions on Intelligent Systems and Technology}, 7(2), Article 20, 1--18.

\bibitem[Miao, Shi, Li, and Tchetgen Tchetgen(2024)]{MiaoShiLiTchetgen2024}
Miao, W., Shi, X., Li, Y., and Tchetgen Tchetgen, E. (2024).
A confounding bridge approach for double negative control inference on causal effects.
\emph{Statistical Theory and Related Fields}, published online.

\bibitem[Miles, Kanki, Meloni, and Tchetgen Tchetgen(2017)]{MilesKankiMeloniTchetgen2017}
Miles, C. H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E. J. (2017).
On partial identification of the natural indirect effect.
\emph{Journal of Causal Inference}, 5(2).

\bibitem[Miles, Kanki, Meloni, and Tchetgen Tchetgen(2015)]{MilesKankiMeloniTchetgen2015}
Miles, C. H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E. J. (2015).
On partial identification of the pure direct effect.
arXiv:1509.01652.

\bibitem[Pearl(2001)]{Pearl2001}
Pearl, J. (2001).
Direct and indirect effects.
In \emph{Proceedings of the Seventeenth Conference on Uncertainty in Artificial Intelligence}, 411--420.

\bibitem[Penning de Vries and Groenwold(2023)]{PenningDeVriesGroenwold2023}
Penning de Vries, B. B. L. and Groenwold, R. H. H. (2023).
Negative controls: Concepts and caveats.
\emph{Statistical Methods in Medical Research}, 32(8), 1543--1553.

\bibitem[Robins and Greenland(1992)]{RobinsGreenland1992}
Robins, J. M. and Greenland, S. (1992).
Identifiability and exchangeability for direct and indirect effects.
\emph{Epidemiology}, 3(2), 143--155.

\bibitem[Sun and Ye(2021)]{SunYe2021}
Sun, B. and Ye, T. (2021).
Semiparametric causal mediation analysis with unmeasured mediator-outcome confounding.
arXiv:2012.06762.

\bibitem[Tchetgen Tchetgen and Shpitser(2012)]{TchetgenShpitser2012}
Tchetgen Tchetgen, E. J. and Shpitser, I. (2012).
Semiparametric theory for causal mediation analysis: Efficiency bounds, multiple robustness and sensitivity analysis.
\emph{Annals of Statistics}, 40(3), 1816--1845.

\bibitem[Zhang, Li, Miao, and Tchetgen Tchetgen(2023)]{ZhangLiMiaoTchetgen2023}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. (2023).
Proximal causal inference without uniqueness assumptions.
\emph{Statistics \& Probability Letters}, 198, 109836.
\end{thebibliography}

\end{document}
