% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_mediation\_proxy, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_mediation\_proxy} / \texttt{v1}%
  \\ \large\textit{Shared Proxy-Null Mediation Bounds and Sharpness Criterion}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies a partial-identification problem for the joint natural-effect
target \(\theta=(\mathrm{PNDE}(1,0),\mathrm{TNIE}(1,0))\) in a binary mediation
design with binary negative-control proxies.  There is no regression estimator
in this anchor; the estimand-defining object is the affine bridge-fiber bound
\[
  B(P)=\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\}.
\]
The main conclusion is an outer-bound and sharpness characterization:
\(\Theta_I(P)\subseteq B(P)\), while equality holds if and only if the primitive
mean-kernel projection fills the whole observable interval.  Thus Stage -1
Conjecture 1 is confirmed for containment but refuted as a sharpness theorem
under the named assumptions alone.  The corrected sharp object is the affine
image of the attainable scalar set \(E(P)\), not necessarily the whole line
segment \(B(P)\).
\end{abstract}

\section{Introduction}
Natural direct and indirect effects are used to separate a treatment effect into
the part acting outside a mediator and the part transmitted through that
mediator.  The decomposition is most delicate when the mediator-outcome
relationship is confounded by post-treatment latent states.  Negative-control
or proximal methods try to use observed proxies to learn enough about the latent
state to recover a bridge function, but weak or redundant proxies can make the
bridge equations rank deficient.

The Stage -1 proposal asks whether that rank deficiency has a clean joint
geometry.  Its locked setup is a binary proxy mediation problem in which all
admissible bridge solutions relevant for the PNDE and TNIE share one scalar
null coordinate \(\eta\).  The proposed bounding functional is the line segment
\(B(P)\), the affine image of the observable interval \([\ell(P),u(P)]\) induced
by rank-deficient bridge equations and outcome-range constraints.

This note proves the exact algebra behind that proposal and separates the part
that is a theorem from the part that is an additional sharpness requirement.
Under the named bridge-fiber assumptions, every compatible primitive
mean-kernel model has a coordinate \(\eta(Q)\in[\ell(P),u(P)]\), so its
natural-effect vector lies in \(B(P)\).  However, the assumptions do not imply
that every observable bridge coordinate is attainable by a primitive latent
mean-kernel model.  The sharp joint identified set is the affine image of
\[
  E(P)=\{\eta(Q):Q\in\mathcal L(P)\},
\]
and \(B(P)\) is sharp exactly when \(E(P)=[\ell(P),u(P)]\).

The result is useful for downstream formula design because it gives a precise
diagnostic for proxy-null mediation bounds.  Reporting the whole shared-null
segment is justified as an outer bound.  Reporting it as a sharp bound requires
a separate endpoint and interior realisability argument, or equivalently a
finite linear-programming projection proof.

\section{Related work and positioning}
Robins and Greenland \cite{RobinsGreenland1992} and Pearl \cite{Pearl2001}
introduced the counterfactual direct and indirect effects that motivate the
PNDE and TNIE coordinates.  Avin, Shpitser, and Pearl
\cite{AvinShpitserPearl2005} showed that path-specific effects can fail to be
identified in graphs with intermediate confounding, which is the
nonidentification regime studied here.  Imai, Keele, and Yamamoto
\cite{ImaiKeeleYamamoto2010} give the standard mediation formula under
sequential ignorability; the present note replaces mediator-outcome
ignorability by negative-control bridge restrictions.

Dukes, Shpitser, and Tchetgen Tchetgen \cite{DukesShpitserTchetgen2023} develop
proximal mediation identification using bridge functions, and their work is the
closest point-identification comparator.  Zhang, Li, Miao, and Tchetgen
Tchetgen \cite{ZhangLiMiaoTchetgen2023} show that bridge nonuniqueness does not
always destroy identification when the target is invariant across bridge
solutions.  Ghassami, Shpitser, and Tchetgen Tchetgen
\cite{GhassamiShpitserTchetgen2023} study partial identification using proxies
when proximal point-identification conditions fail.  This note differs from all
three by targeting the joint PNDE/TNIE geometry generated by a shared
one-dimensional bridge-null coordinate.

Manski \cite{Manski1990} and Balke and Pearl \cite{BalkePearl1997} provide the
finite linear-programming template for sharp partial-identification bounds:
write all observational and structural restrictions as linear constraints and
project the feasible polytope onto the target.  Cai, Kuroki, Pearl, and Tian
\cite{CaiKurokiPearlTian2008} use related symbolic bounding ideas for direct
effects with confounded intermediate variables.  Miles, Kanki, Meloni, and
Tchetgen Tchetgen \cite{MilesKankiMeloniTchetgen2015} bound the pure natural
direct effect, while Miles, Kanki, Meloni, and Tchetgen Tchetgen
\cite{MilesKankiMeloniTchetgen2017} bound the natural indirect effect.  Gabriel,
Sachs, and Sjolander \cite{GabrielSachsSjolander2023} emphasize that separately
sharp bounds for decomposition components need not combine sharply; the present
line-segment analysis gives a proxy-null version of that joint-attainability
issue.

\section{Formal setup}
Let \(P\) denote the observable law of
\[
  O=(X,A,M,Y,W,Z),
\]
where \(A,M,W,Z\in\{0,1\}\), \(Y\in[0,1]\), and \(X\) has finite support
\(\mathcal X\).  The latent causal law is represented by an element
\(Q\) of a finite mean-kernel model.  It contains mediator potential outcomes
\(M(a)\), outcome potential outcomes \(Y(a,m)\), history-indexed latent
mediator-outcome confounder states \(U(a,m)\), and proxy response variables
\(W(a,m)\) and \(Z(a,m)\).  Factual variables are generated by the consistency
relations
\[
  M=M(A),\qquad Y=Y(A,M(A)),\qquad
  W=W(A,M(A)),\qquad Z=Z(A,M(A)).
\]

The causal target attached to \(Q\) is
\[
  \theta(Q)=(\theta_D(Q),\theta_I(Q)),
\]
with
\[
  \theta_D(Q)=\E_Q\{Y(1,M(0))-Y(0,M(0))\},
  \qquad
  \theta_I(Q)=\E_Q\{Y(1,M(1))-Y(1,M(0))\}.
\]
The identified set is the set of all target values attainable by primitive
models that reproduce \(P\) and satisfy the maintained restrictions:
\[
  \Theta_I(P)=\{\theta(Q):Q\in\mathcal L(P)\}.
\]
Here \(\mathcal L(P)\) is the finite mean-kernel latent polytope defined by
matching the observable law of \((X,A,M,W,Z)\), matching the conditional
outcome means \(r_c(z)=\E[Y\mid X=x,A=a,M=m,Z=z]\), and imposing the
consistency, positivity, negative-control, and shared-null bridge restrictions
listed in Section 4.

For each stratum \(c=(x,a,m)\), define the observable proxy matrix
\[
  K_c(z,w)=P(W=w\mid X=x,A=a,M=m,Z=z),
\]
and the observable outcome-mean vector
\[
  r_c(z)=\E[Y\mid X=x,A=a,M=m,Z=z].
\]
The bridge equation is \(K_ch_c=r_c\), where \(h_c\in[0,1]^2\) is indexed by
\(w\in\{0,1\}\).  In a rank-deficient binary bridge cell, the solution set has
the form
\[
  h_c=h_c^0+\eta_c n_c,
\]
where \(n_c\ne0\) spans the null space of \(K_c\).  The shared-null restriction
reparameterizes these stratum coordinates as
\[
  \eta_c=s_c\eta+t_c
\]
for observable signs and scales \(s_c,t_c\).  The interval
\([\ell(P),u(P)]\) is the intersection of all outcome-range constraints
\[
  0\le h_c^0(w)+(s_c\eta+t_c)n_c(w)\le1
\]
over all \(c,w\) used by the bridge formulas.

The Stage -1 bridge loading assumption states that the PNDE and TNIE induced by
this bridge family are affine in the same scalar:
\[
  \theta_D(\eta)=\theta_D^0+\beta_D\eta,\qquad
  \theta_I(\eta)=\theta_I^0+\beta_I\eta,
\]
with \((\beta_D,\beta_I)\ne(0,0)\).  For a primitive model
\(Q\in\mathcal L(P)\), let \(\eta(Q)\) be its induced shared-null coordinate
and define
\[
  E(P)=\{\eta(Q):Q\in\mathcal L(P)\}.
\]
Assumption \ref{ass:latent-polytope} gives \(E(P)\subseteq[\ell(P),u(P)]\).

\paragraph{Locked parameters.}
\begin{quote}
\textbf{Partial identification tuple.}
\texttt{qid = pid\_mediation\_proxy};
\texttt{specialization = v1};
observable distribution \(P\) is the law of \(O=(X,A,M,Y,W,Z)\), where
\(A\in\{0,1\}\) is a single binary treatment, \(M\in\{0,1\}\) is a mediator,
\(Y\in[0,1]\) is an outcome, and \(W,Z\in\{0,1\}\) are negative-control
proxies for treatment- and mediator-history-indexed unobserved
mediator--outcome confounders \(U(a,m)\);
parameter \(\theta=(\theta_D,\theta_I)\), where
\(\theta_D=\mathrm{PNDE}(1,0)\) and \(\theta_I=\mathrm{TNIE}(1,0)\);
identifying restrictions are consistency, treatment ignorability conditional
on \(X\), mediator/proxy positivity, negative-control exclusion and relevance,
and the one-dimensional shared proxy-null bridge-fiber restriction in
Assumption~\ref{ass:shared-null};
the bounding functional is the affine image
\[
  B(P)=\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\},
\]
where \([\ell(P),u(P)]\) is the observable feasibility interval induced by
the rank-deficient bridge equations and the outcome-range constraints.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite binary mediation system]\label{ass:finite}
The variables satisfy \(A,M,W,Z\in\{0,1\}\), \(Y\in[0,1]\), and \(X\) has finite
support.  Every cell used to define a conditional probability, conditional
expectation, bridge matrix, mediator law, or proxy law has strictly positive
probability.  The interval endpoints \(\ell(P)\) and \(u(P)\) are finite and
obey \(\ell(P)\le u(P)\).
\end{assumption}

\begin{assumption}[Consistency and treatment ignorability]\label{ass:consistency}
Observed \(M\) and \(Y\) equal their corresponding factual potential outcomes,
and \(A\) is conditionally independent of the relevant treatment-indexed
potential outcomes, treatment- and mediator-history-indexed latent confounder
states, and proxy response types given \(X\).  Factual consistency also sets
\(U=U(A,M(A))\), \(W=W(A,M(A))\), and \(Z=Z(A,M(A))\).
\end{assumption}

\begin{assumption}[Negative-control exclusion]\label{ass:negative-control}
For each realised history \(c=(x,a,m)\), conditional on
\((X=x,A=a,M=m,U(a,m))\), \(Z(a,m)\) carries no direct information about the
outcome bridge other than through \(U(a,m)\), and \(W(a,m)\) is an
outcome-inducing proxy for \(U(a,m)\) with no direct treatment or mediator
effect except through the history-indexed bridge relation encoded by
\(K_ch_c=r_c\).  Relevance means the proxy law supplies the bridge matrices
appearing in Assumption \ref{ass:rank-def}.
\end{assumption}

\begin{assumption}[Rank-deficient binary bridge]\label{ass:rank-def}
For each \(c=(x,a,m)\), the observed \(2\times2\) matrix
\(K_c(z,w)=P(W=w\mid X=x,A=a,M=m,Z=z)\) has rank one, the equation
\(K_ch_c=r_c\) is feasible, and its solution set is
\(\{h_c^0+\eta_c n_c:\eta_c\in I_c(P)\}\) for a nonzero null vector \(n_c\).
\end{assumption}

\begin{assumption}[Shared proxy-null coordinate]\label{ass:shared-null}
The feasible bridge solutions relevant to \(\theta_D\) and \(\theta_I\) are
indexed by a single scalar \(\eta\), so \(\eta_c=s_c\eta+t_c\) for known
observable signs/scales \(s_c,t_c\).  The common feasible interval
\([\ell(P),u(P)]\) is the intersection of the stratum intervals after this
reparameterisation.
\end{assumption}

\begin{assumption}[Affine natural-effect loading]\label{ass:affine-loading}
The PNDE and TNIE functionals induced by the bridge family are
\(\theta_D(\eta)=\theta_D^0+\beta_D\eta\) and
\(\theta_I(\eta)=\theta_I^0+\beta_I\eta\), with
\((\beta_D,\beta_I)\neq(0,0)\).  The constants
\(\theta_D^0,\theta_I^0,\beta_D,\beta_I,\ell(P),u(P)\) are observable
functionals of \(P\) under Assumptions~\ref{ass:finite}--\ref{ass:shared-null}.
\end{assumption}

\begin{assumption}[Primitive mean-kernel feasibility]\label{ass:latent-polytope}
The finite mean-kernel latent polytope \(\mathcal L(P)\) defined in the formal
setup is nonempty.  Every \(Q\in\mathcal L(P)\) reproduces
\(P_{X,A,M,W,Z}\) and the observable conditional outcome means \(r_c(z)\),
satisfies Assumptions~\ref{ass:finite}--\ref{ass:affine-loading}, indexes all
latent confounder and proxy response types by \((a,m)\), and induces a
well-defined shared-null scalar \(\eta(Q)\in[\ell(P),u(P)]\).  This assumption
does not assert that every \(\eta\in[\ell(P),u(P)]\) is attainable.
\end{assumption}

\begin{assumption}[Total-effect bridge compatibility]\label{ass:total-effect}
The total effect \(\theta_T=\E\{Y(1,M(1))-Y(0,M(0))\}\) is identified from
\(P\) under the same consistency and treatment-ignorability conditions, and for
every primitive mean-kernel model \(Q\in\mathcal L(P)\) the natural-effect
decomposition holds:
\[
  \theta_D(Q)+\theta_I(Q)=\theta_T.
\]
This assumption fixes the total effect but does not separately impose any
value on the affine loading \(\beta_D+\beta_I\).
\end{assumption}

\section{Regression estimator}
This section title is fixed by the skeleton.  In this partial-identification
anchor there is no regression estimator; the estimand-defining functional is
the bounding functional \(B(P)\) and its coordinate projections.

\begin{definition}[Shared-null bounding functional]\label{def:bound}
Under Assumptions \ref{ass:rank-def}--\ref{ass:affine-loading}, define
\[
  B(P)=\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\}.
\]
The coordinate lower and upper functionals are
\[
  \theta_D^L(P)=\min_{\eta\in[\ell(P),u(P)]}
       \{\theta_D^0+\beta_D\eta\},
  \qquad
  \theta_D^U(P)=\max_{\eta\in[\ell(P),u(P)]}
       \{\theta_D^0+\beta_D\eta\},
\]
and
\[
  \theta_I^L(P)=\min_{\eta\in[\ell(P),u(P)]}
       \{\theta_I^0+\beta_I\eta\},
  \qquad
  \theta_I^U(P)=\max_{\eta\in[\ell(P),u(P)]}
       \{\theta_I^0+\beta_I\eta\}.
\]
These are observable functionals of \(P\).  The set \(B(P)\) is an outer bound
unless every point on the line segment is attainable by a primitive model.
\end{definition}

\begin{definition}[Primitive projection functional]\label{def:primitive-proj}
The sharp primitive shared-null set is
\[
  B_{\mathrm{sh}}(P)=
  \{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):\eta\in E(P)\},
\]
where \(E(P)=\{\eta(Q):Q\in\mathcal L(P)\}\).  Equivalently, a finite
linear-programming representation of \(\mathcal L(P)\) gives the sharp set by
projecting that polytope onto \((\theta_D,\theta_I)\).  The interval
\([\ell(P),u(P)]\) uses only observable bridge feasibility and outcome range;
the set \(E(P)\) additionally uses primitive latent mean-kernel feasibility.
\end{definition}

\section{Target causal estimand}
The intended causal target is the vector
\[
  \theta(Q)=
  \bigl(
  \E_Q\{Y(1,M(0))-Y(0,M(0))\},
  \E_Q\{Y(1,M(1))-Y(1,M(0))\}
  \bigr).
\]
The first coordinate is \(\mathrm{PNDE}(1,0)\): it compares treatment levels
while holding the mediator at the value it would have taken under \(A=0\).  The
second coordinate is \(\mathrm{TNIE}(1,0)\): it compares the mediator under
\(A=1\) to the mediator under \(A=0\), holding the outcome treatment level at
\(A=1\).  The target is not defined to be the bridge formula.  The bridge
formula supplies a bound, and the proof must show which target values are
compatible with the observed law and restrictions.

\section{Main theorems}
\begin{proposition}[Outer bound and exact sharpness criterion]\label{thm:outer-sharp}
Under Assumptions \ref{ass:finite}--\ref{ass:latent-polytope},
\[
  \Theta_I(P)=B_{\mathrm{sh}}(P)
  =\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):\eta\in E(P)\}
  \subseteq B(P).
\]
Consequently,
\[
  \Theta_I(P)\subseteq
  [\theta_D^L(P),\theta_D^U(P)]\times
  [\theta_I^L(P),\theta_I^U(P)].
\]
Because \((\beta_D,\beta_I)\ne(0,0)\), the affine map
\(\eta\mapsto(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta)\) is injective.
Therefore \(B(P)\) is the sharp joint identified set if and only if
\[
  E(P)=[\ell(P),u(P)].
\]
\end{proposition}

This proposition is the central contribution.  It confirms the containment part
of the Stage -1 proposal and gives the exact missing condition for sharpness.
It also explains why marginal PNDE and TNIE intervals should not be multiplied
into a rectangle: the joint outer bound is a line segment, and the sharp joint
set is a possibly smaller subset of that same line.

\paragraph{Verdict on Stage -1 Conjecture 1.}
Conjecture 1 is \emph{partial}.  The theorem confirms the outer-bound claim
\(\Theta_I(P)\subseteq B(P)\).  The theorem refutes the claim that the named
assumptions alone imply sharpness: sharpness is equivalent to the extra
realisability statement \(E(P)=[\ell(P),u(P)]\), which is not contained in
Assumption \ref{ass:latent-polytope}.

\begin{proposition}[Failure of sharpness without full-fiber realisability]\label{thm:sharp-fails}
There are finite shared-null bridge instances satisfying Assumptions
\ref{ass:finite}--\ref{ass:latent-polytope} for which
\[
  E(P)\subsetneq[\ell(P),u(P)].
\]
In such instances \(B(P)\) is a valid outer bound but is not sharp.  In
particular, if \(E(P)=\{0\}\), \([\ell(P),u(P)]=[-1,1]\),
\(\theta_D^0=\theta_I^0=0\), \(\beta_D=1\), and \(\beta_I=-1\), then
\[
  \Theta_I(P)=\{(0,0)\}
  \quad\text{while}\quad
  B(P)=\{(\eta,-\eta):\eta\in[-1,1]\}.
\]
\end{proposition}

This proposition is not a new causal model for mediation; it is the minimal
logical counterexample to the sharpness inference.  The nearest correct
statement is Proposition \ref{thm:outer-sharp}: the primitive projection \(E(P)\)
must be computed or proved full before the observable bridge interval can be
reported as sharp.

\begin{proposition}[Total-effect compatibility]\label{thm:total-effect}
Assume Assumptions \ref{ass:finite}--\ref{ass:total-effect}.  If \(E(P)\)
contains at least two distinct values, then
\[
  \beta_D+\beta_I=0
  \quad\text{and}\quad
  \theta_D^0+\theta_I^0=\theta_T.
\]
Consequently,
\[
  \theta_D(\eta)+\theta_I(\eta)=\theta_T
\]
for every \(\eta\in E(P)\).  If the Stage -1 sharpness conclusion
\(E(P)=[\ell(P),u(P)]\) also holds and \(\ell(P)<u(P)\), then the entire
segment \(B(P)\) lies in the hyperplane \(\theta_D+\theta_I=\theta_T\).
\end{proposition}

This is the corrected version of the Stage -1 total-effect theorem.  The
decomposition restriction need only be checked on attainable primitive points;
two attainable shared-null values are enough to force the slope restriction.
If the full observable interval is attainable, the same algebra holds on the
whole line segment.

\section{Interpretation}
The line segment \(B(P)\) is an observable sensitivity curve indexed by the
shared proxy-null coordinate.  It is narrower than the coordinate rectangle
whenever \(\ell(P)<u(P)\) and both loadings are nonzero, because direct and
indirect effects must move together along the same scalar coordinate.  This is
the sense in which the shared-null restriction does real tightening work.

The bound collapses to point identification when the affine image is a
singleton.  This happens if \(\ell(P)=u(P)\), or more generally if the primitive
projection \(E(P)\) is a singleton.  If one loading vanishes but the other does
not, one component is point identified along the shared-null fiber while the
other remains partially identified.  If both loadings vanished, the bridge
fiber would be irrelevant for this target, but Assumption \ref{ass:affine-loading}
rules out that degenerate case.

The bound widens toward a Manski-style no-restriction bound when the proxy,
negative-control, and bridge restrictions are removed.  In that case the finite
mean-kernel polytope permits all bounded counterfactual completions consistent
with the observed factual distribution, and the sharp set is obtained by a
generic response-type linear program.  The proxy restrictions tighten the bound
only through constraints on feasible bridge coordinates and through any
additional primitive feasibility restrictions that shrink \(E(P)\).

The main caution is sharpness.  Outcome-range constraints on observable bridge
solutions produce \([\ell(P),u(P)]\), but primitive latent feasibility can
exclude some of those bridge coordinates.  Therefore a published formula should
label \(B(P)\) as an outer bound unless it also proves
\(E(P)=[\ell(P),u(P)]\) by an endpoint and mixture construction or by a finite
linear-programming projection argument.

\section{Step-by-step proof}
\paragraph{Proof of Proposition \ref{thm:outer-sharp}.}
By definition of the identified set,
\[
  \Theta_I(P)=\{\theta(Q):Q\in\mathcal L(P)\}.
\]
Assumption \ref{ass:latent-polytope} says that every \(Q\in\mathcal L(P)\)
induces a scalar \(\eta(Q)\in[\ell(P),u(P)]\).  Assumption
\ref{ass:affine-loading} says that the PNDE and TNIE attached to that bridge
coordinate are
\[
  \theta_D(Q)=\theta_D^0+\beta_D\eta(Q),
  \qquad
  \theta_I(Q)=\theta_I^0+\beta_I\eta(Q).
\]
Substituting these two equalities into the definition of \(\Theta_I(P)\) gives
\[
  \Theta_I(P)
  =\{(\theta_D^0+\beta_D\eta(Q),\theta_I^0+\beta_I\eta(Q)):
       Q\in\mathcal L(P)\}.
\]
Replacing the image of \(Q\) by the set of all induced scalars gives
\[
  \Theta_I(P)
  =\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):\eta\in E(P)\}
  =B_{\mathrm{sh}}(P).
\]
Since \(E(P)\subseteq[\ell(P),u(P)]\), the displayed set is contained in
\[
  B(P)=\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\}.
\]
This proves \(\Theta_I(P)\subseteq B(P)\).

The coordinate rectangle follows by projecting the same containment onto the
two axes.  For example,
\[
  \theta_D^0+\beta_D\eta\in
  [\theta_D^L(P),\theta_D^U(P)]
\]
for every \(\eta\in[\ell(P),u(P)]\), and the same argument applies to the
indirect coordinate.

It remains to characterize sharpness of the full line segment.  The affine map
\[
  f(\eta)=(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta)
\]
is injective because \((\beta_D,\beta_I)\ne(0,0)\): if
\(f(\eta_1)=f(\eta_2)\), then
\[
  (\beta_D,\beta_I)(\eta_1-\eta_2)=(0,0),
\]
which forces \(\eta_1=\eta_2\).  Hence
\[
  f(E(P))=f([\ell(P),u(P)])
\]
if and only if \(E(P)=[\ell(P),u(P)]\).  Since
\(\Theta_I(P)=f(E(P))\) and \(B(P)=f([\ell(P),u(P)])\), the outer bound is sharp
if and only if the primitive projection fills the whole observable interval.

\paragraph{Proof of Proposition \ref{thm:sharp-fails}.}
The proof uses the extreme-point view of a finite mean-kernel model.  Consider
a finite instance with one baseline stratum and bridge equations whose
observable feasibility interval is \([-1,1]\).  Let the affine natural-effect
loading be
\[
  f(\eta)=(\eta,-\eta).
\]
Let the primitive mean-kernel polytope be nonempty but have the additional
observable-matching linear restriction that its bridge representative has
\(\eta(Q)=0\).  Equivalently, the polytope projection onto the shared-null
coordinate is the singleton
\[
  E(P)=\{0\}.
\]
This satisfies Assumption \ref{ass:latent-polytope}, which only requires
nonemptiness and \(E(P)\subseteq[\ell(P),u(P)]\), not the reverse inclusion.
All bridge, shared-null, and affine-loading assumptions are satisfied by
construction.  Proposition \ref{thm:outer-sharp} then yields
\[
  \Theta_I(P)=f(E(P))=\{(0,0)\}
\]
while
\[
  B(P)=f([-1,1])=\{(\eta,-\eta):\eta\in[-1,1]\}.
\]
Thus the observable line segment is an outer bound but is not sharp.  The only
missing step is full-fiber realisability, exactly the equality
\(E(P)=[\ell(P),u(P)]\).

\paragraph{Proof of Proposition \ref{thm:total-effect}.}
By Assumption \ref{ass:total-effect}, for every \(Q\in\mathcal L(P)\),
\[
  \theta_D(Q)+\theta_I(Q)=\theta_T.
\]
Using Assumption \ref{ass:affine-loading}, this is
\[
  \theta_D^0+\theta_I^0+(\beta_D+\beta_I)\eta(Q)=\theta_T
\]
for every \(\eta(Q)\in E(P)\).  If \(E(P)\) contains two distinct values
\(\eta_1\ne\eta_2\), subtracting the two equalities gives
\[
  (\beta_D+\beta_I)(\eta_1-\eta_2)=0.
\]
Therefore \(\beta_D+\beta_I=0\).  Substituting this back into the equality at
any attainable point gives
\[
  \theta_D^0+\theta_I^0=\theta_T.
\]
Consequently \(\theta_D(\eta)+\theta_I(\eta)=\theta_T\) for every
\(\eta\in E(P)\).  If \(E(P)=[\ell(P),u(P)]\), the same identity holds on the
whole segment \(B(P)\).

\section{Sanity checks}
\paragraph{No-proxy fallback.}
If the proxy variables and bridge restrictions are removed, the sharp object is
the projection of the finite response-type polytope that matches only the
observable law of \((X,A,M,Y)\).  With \(Y\in[0,1]\), each natural-effect
coordinate lies within the natural Manski range \([-1,1]\), with sharper
endpoints obtained by the finite linear program when the factual distribution
imposes additional constraints.

\paragraph{Zero-width and point-identification corners.}
If \(\ell(P)=u(P)\), then \(B(P)\) is a singleton and the shared-null bridge
fiber gives point identification for the two coordinates under the affine
loading.  The same collapse occurs when \(E(P)\) is a singleton, even if the
observable interval is wider.  Full-rank proximal bridge conditions are one
standard route to this kind of collapse, as in proximal mediation
identification \cite{DukesShpitserTchetgen2023}.

\paragraph{Monotone-treatment-response specialization.}
Monotone treatment response is not part of the locked parameter block.  If it
were added as a new restriction, it would enter the primitive finite program as
linear inequalities such as \(Y(1,m)\ge Y(0,m)\).  Such inequalities can only
shrink \(E(P)\) and the resulting sharp set, so they tighten rather than
invalidate the outer-bound argument.

\paragraph{Total-effect sanity check.}
When the total effect is fixed and at least two shared-null values are
attainable, Proposition \ref{thm:total-effect} forces
\(\beta_D+\beta_I=0\).  Hence variation along the line segment reallocates
effect between the direct and indirect components without changing the total
effect.

\paragraph{Balke--Pearl finite-LP special case.}
If the mediation target is replaced by a binary treatment effect with a binary
instrument and finite response types, the primitive polytope projection reduces
to the Balke--Pearl linear-programming construction \cite{BalkePearl1997}.  The
same extreme-point logic underlies the present sharpness criterion, but the
coordinates here are PNDE and TNIE rather than a single treatment effect.

\section{Counterexample or minimality check}
The minimality issue is full-fiber realisability.  The named assumptions imply
\[
  E(P)\subseteq[\ell(P),u(P)],
\]
but they do not imply the reverse inclusion.  Proposition
\ref{thm:sharp-fails} gives the simplest possible counterexample: the
observable bridge equations allow \(\eta\in[-1,1]\), but the primitive
mean-kernel polytope projects only to \(\eta=0\).  Then the sharp set is the
single point \((0,0)\), while the proposed line segment contains many
unattainable values.

The nearest correct statement is therefore
\[
  \Theta_I(P)=
  \{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):\eta\in E(P)\}.
\]
The Stage -1 formula \(B(P)\) becomes sharp only after proving
\[
  E(P)=[\ell(P),u(P)].
\]
That equality can be established by an endpoint construction plus convex
mixture argument, or by solving the finite latent mean-kernel linear program and
showing that its projection onto \(\eta\) is the whole interval.  Without that
step, the interval endpoints \(\ell(P)\) and \(u(P)\) are boundary conditions
for bridge functions, not automatically attainable causal models.

\section{Formalization checklist}
\paragraph{Probabilistic assumptions and objects.}
\begin{itemize}[leftmargin=*]
\item Observable law \(P\) of \(O=(X,A,M,Y,W,Z)\), with \(A,M,W,Z\) binary,
\(Y\in[0,1]\), and finite \(\mathcal X\).  Role: supplies bridge matrices,
conditional means, mediator laws, and all observable constants.
\item Primitive finite mean-kernel polytope \(\mathcal L(P)\).  Type:
nonempty compact convex set of finite latent response-type and outcome-mean
kernels matching \(P\).  Dependencies: Assumptions \ref{ass:finite},
\ref{ass:consistency}, \ref{ass:negative-control}, and
\ref{ass:latent-polytope}.  Role: defines the sharp identified set.
\item Potential-outcome target maps
\[
  \theta_D(Q)=\E_Q\{Y(1,M(0))-Y(0,M(0))\},
  \quad
  \theta_I(Q)=\E_Q\{Y(1,M(1))-Y(1,M(0))\}.
\]
Role: causal estimand coordinates.
\item Shared-null coordinate map \(Q\mapsto\eta(Q)\).  Dependencies:
Assumptions \ref{ass:rank-def}, \ref{ass:shared-null}, and
\ref{ass:latent-polytope}.  Role: projects primitive models onto the bridge
fiber.
\end{itemize}

\paragraph{Deterministic identities and convex arguments.}
\begin{itemize}[leftmargin=*]
\item Bridge equation \(K_ch_c=r_c\), rank-one solution representation
\(h_c=h_c^0+\eta_cn_c\), and shared reparameterisation
\(\eta_c=s_c\eta+t_c\).  Role: constructs the observable interval
\([\ell(P),u(P)]\).
\item Outcome-range interval identity:
\[
  [\ell(P),u(P)]
  =\{\eta:0\le h_c^0(w)+(s_c\eta+t_c)n_c(w)\le1
       \text{ for all used }c,w\}.
\]
Role: boundary condition for the outer bound.
\item Affine loading map
\[
  f(\eta)=(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta).
\]
Dependencies: Assumption \ref{ass:affine-loading}.  Role: maps scalar bridge
coordinates to natural-effect coordinates.
\item Primitive projection \(E(P)=\{\eta(Q):Q\in\mathcal L(P)\}\).  Role:
distinguishes sharp attainable coordinates from observable bridge coordinates.
\item Containment identity:
\[
  \Theta_I(P)=f(E(P))\subseteq f([\ell(P),u(P)])=B(P).
\]
Dependencies: definitions of \(\Theta_I(P)\), \(E(P)\), and Assumptions
\ref{ass:affine-loading}--\ref{ass:latent-polytope}.  Role: main outer-bound
proof.
\item Injectivity lemma for \(f\): if \((\beta_D,\beta_I)\ne(0,0)\), then
\(f(\eta_1)=f(\eta_2)\) implies \(\eta_1=\eta_2\).  Role: proves that
sharpness of \(B(P)\) is equivalent to \(E(P)=[\ell(P),u(P)]\).
\item Total-effect slope identity:
\[
  \theta_D^0+\theta_I^0+(\beta_D+\beta_I)\eta=\theta_T
\]
on attainable \(\eta\).  Role: derives \(\beta_D+\beta_I=0\) when at least two
attainable coordinates exist.
\item Finite LP projection principle: a compact finite mean-kernel polytope
projected by a linear map has a compact sharp identified set with endpoints
attained at faces.  Role: supplies the standard route for proving or refuting
full-fiber realisability.
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a corrected joint partial-identification
statement for the Stage -1 shared proxy-null proposal.  The affine segment
\(B(P)\) is a valid observable outer bound for the joint PNDE/TNIE target, and
it is sharper than the naive coordinate rectangle because both effects move
with the same scalar.  It is sharp exactly when the primitive mean-kernel
projection fills the entire observable bridge interval.  The main source of
non-sharpness is failure of full-fiber realisability: bridge functions may
satisfy the outcome-range constraints at values of \(\eta\) that no compatible
latent mean-kernel model attains.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem[Avin, Shpitser, and Pearl(2005)]{AvinShpitserPearl2005}
Avin, C., Shpitser, I., and Pearl, J. (2005).
Identifiability of path-specific effects.
In \emph{Proceedings of the Nineteenth International Joint Conference on Artificial Intelligence},
357--363.

\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association}, 92(439), 1171--1176.

\bibitem[Cai, Kuroki, Pearl, and Tian(2008)]{CaiKurokiPearlTian2008}
Cai, Z., Kuroki, M., Pearl, J., and Tian, J. (2008).
Bounds on direct effects in the presence of confounded intermediate variables.
\emph{Biometrics}, 64(3), 695--701.

\bibitem[Ding and VanderWeele(2016)]{DingVanderWeele2016}
Ding, P. and VanderWeele, T. J. (2016).
Sharp sensitivity bounds for mediation under unmeasured mediator-outcome
confounding.
\emph{Biometrika}, 103(2), 483--490.

\bibitem[Dukes, Shpitser, and Tchetgen Tchetgen(2023)]{DukesShpitserTchetgen2023}
Dukes, O., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
Proximal mediation analysis.
\emph{Biometrika}, 110(4), 973--987.

\bibitem[Gabriel, Sachs, and Sjolander(2023)]{GabrielSachsSjolander2023}
Gabriel, E. E., Sachs, M. C., and Sjolander, A. (2023).
Sharp nonparametric bounds for decomposition effects with two binary mediators.
\emph{Journal of the American Statistical Association}, 118(544), 2446--2453.

\bibitem[Ghassami, Shpitser, and Tchetgen Tchetgen(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. (2023).
Partial identification of causal effects using proxy variables.
arXiv:2304.04374.

\bibitem[Imai, Keele, and Yamamoto(2010)]{ImaiKeeleYamamoto2010}
Imai, K., Keele, L., and Yamamoto, T. (2010).
Identification, inference and sensitivity analysis for causal mediation effects.
\emph{Statistical Science}, 25(1), 51--71.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{The American Economic Review}, 80(2), 319--323.

\bibitem[Miles, Kanki, Meloni, and Tchetgen Tchetgen(2015)]{MilesKankiMeloniTchetgen2015}
Miles, C. H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E. J. (2015).
On partial identification of the pure direct effect.
\emph{Harvard University Biostatistics Working Paper Series}, Working Paper 196.

\bibitem[Miles, Kanki, Meloni, and Tchetgen Tchetgen(2017)]{MilesKankiMeloniTchetgen2017}
Miles, C. H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E. J. (2017).
On partial identification of the natural indirect effect.
\emph{Journal of Causal Inference}, 5(2).

\bibitem[Pearl(2001)]{Pearl2001}
Pearl, J. (2001).
Direct and indirect effects.
In \emph{Proceedings of the Seventeenth Conference on Uncertainty in Artificial Intelligence},
411--420.

\bibitem[Robins and Greenland(1992)]{RobinsGreenland1992}
Robins, J. M. and Greenland, S. (1992).
Identifiability and exchangeability for direct and indirect effects.
\emph{Epidemiology}, 3(2), 143--155.

\bibitem[Zhang, Li, Miao, and Tchetgen Tchetgen(2023)]{ZhangLiMiaoTchetgen2023}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. (2023).
Proximal causal inference without uniqueness assumptions.
\emph{Statistics \& Probability Letters}, 198, 109836.
\end{thebibliography}

\end{document}
