% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_mediation\_proxy, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_mediation\_proxy} / \texttt{v1}%
  \\ \large\textit{Sharp joint PNDE/TNIE partial identification under a shared proxy-null bridge fiber}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{quote}
\textbf{Partial identification tuple.}
\texttt{qid = pid\_mediation\_proxy};
\texttt{specialization = v1};
observable distribution \(P\) is the law of \(O=(X,A,M,Y,W,Z)\), where
\(A\in\{0,1\}\) is a single binary treatment, \(M\in\{0,1\}\) is a mediator,
\(Y\in[0,1]\) is an outcome, and \(W,Z\in\{0,1\}\) are negative-control
proxies for treatment- and mediator-history-indexed unobserved
mediator--outcome confounders \(U(a,m)\);
parameter \(\theta=(\theta_D,\theta_I)\), where
\(\theta_D=\mathrm{PNDE}(1,0)\) and \(\theta_I=\mathrm{TNIE}(1,0)\);
identifying restrictions are consistency, treatment ignorability conditional
on \(X\), mediator/proxy positivity, negative-control exclusion and relevance,
and the one-dimensional shared proxy-null bridge-fiber restriction in
Assumption~\ref{ass:shared-null};
the bounding functional is the affine image
\[
  B(P)=\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\},
\]
where \([\ell(P),u(P)]\) is the observable feasibility interval induced by
the rank-deficient bridge equations and the outcome-range constraints.
\end{quote}

\begin{abstract}
This proposal asks whether negative-control proxies can deliver a sharp
\emph{joint} partial-identification statement for the pure natural direct
effect and total natural indirect effect when bridge equations are rank
deficient.  Existing proximal mediation work emphasizes bridge existence and
uniqueness for point identification, while mediation-bounds work warns that
separately sharp decompositions need not combine sharply.  The proposed kernel
is that, with binary proxies and a one-dimensional shared bridge null fiber,
the joint identified set for \((\mathrm{PNDE},\mathrm{TNIE})\) is a line
segment, not the rectangle obtained by multiplying the two marginal intervals.
This would turn weak or redundant negative controls from a nuisance failure of
point identification into a testable geometry for mediation decompositions.
Sharpness is left as a conjecture; it is not assumed as a bridge
realisability condition, but posed as a finite mean-kernel projection claim.
The affine and non-rectangular consequences are routine finite-dimensional
algebra once the shared-null setup is fixed.
\end{abstract}

\section{Introduction}
Mediation analysis is often used to separate a treatment's effect into a
path operating directly on the outcome and a path operating through an
intermediate mediator.  The decomposition is fragile when a post-treatment
latent confounder process \(U(a,m)\) can vary with treatment and mediator
histories: graphical identification can fail, sensitivity parameters are hard
to calibrate, and point-identifying proximal bridge equations can lose
uniqueness when the negative controls are weak.

The main proposed finding is Conjecture~\ref{conj:sharp-joint}: under a
binary-proxy rank-deficient bridge equation whose null direction is shared
across the two natural-effect functionals, the sharp joint identified set for
\((\mathrm{PNDE},\mathrm{TNIE})\) is the one-dimensional affine image of the
observable bridge-feasibility interval.  The accompanying algebraic theorem
states that the marginal PNDE and TNIE formulas are affine projections of the
same coordinate, so the Cartesian product of the two marginal ranges is
generally too large if the sharpness conjecture holds.

What is new is the joint-geometry claim.  Proximal mediation results such as
\citet{DukesShpitserTchetgen2023} target point identification under bridge
conditions; partial-identification mediation results such as
\citet{MilesKankiMeloniTchetgen2015} and
\citet{MilesKankiMeloniTchetgen2017} give no-proxy pure-direct and
natural-indirect bounds; and \citet{GabrielSachsSjolander2023} show that
decomposed effect bounds can lose sharpness when combined.  Proxy
partial-identification results such as
\citet{ZhangLiMiaoTchetgen2023} and
\citet{GhassamiShpitserTchetgen2023} show that nonunique bridges can still
carry causal information, but they do not formulate a mediation decomposition
in which the same bridge-null coordinate moves PNDE and TNIE together.  The
proposed kernel says that rank-deficient proxies create a \emph{common} latent
coordinate that couples the direct and indirect effect intervals, yielding a
non-rectangular sharp set with an observable slope.

The proposal sits in the partial-identification cluster: it is closest to
Manski/Balke--Pearl style latent-table sharpness, modern proximal partial
identification with negative controls, and mediation bounds under unmeasured
mediator--outcome confounding.  It does not propose a new do-calculus rule or
SCM axiom; the SCM and potential-outcome machinery are treated as background
language for a finite-dimensional identified-set statement.

\section{Related work}
\citet{AvinShpitserPearl2005} show that path-specific effects, including
natural effects, can be unidentified in graphs with intermediate confounding;
this is the nonidentification regime in which the present proposal works.
\citet{CaiKurokiPearlTian2008} derive bounds for direct effects with a
confounded intermediate variable; their target is controlled/direct-effect
bounds, whereas this proposal targets the joint geometry of natural direct and
indirect effects.  \citet{ImaiKeeleYamamoto2010} frame mediator--outcome
confounding through sensitivity analysis, motivating why an observable
negative-control coordinate would be useful.  \citet{DingVanderWeele2016}
develop sharp or interpretable sensitivity bounds for mediation effects; this
proposal replaces part of the sensitivity region by a proxy-constrained bridge
fiber.

\citet{MilesKankiMeloniTchetgen2015} give partial-identification bounds for
the pure natural direct effect when cross-world independence and
no-exposure-induced confounding assumptions are relaxed; their bounds are
componentwise and do not use negative-control bridge equations.
\citet{MilesKankiMeloniTchetgen2017} give partial-identification results for
natural indirect effects under relaxed mediation assumptions; together with
the pure-direct-effect paper, this is the closest no-proxy mediation-bounds
thread.  \citet{MilesShpitserKankiMeloniTchetgen2017Path} develop
semiparametric estimation of a path-specific effect under
mediator-outcome confounding, clarifying the adjacent path-specific-effects
literature but not supplying a proxy-null joint identified set.
\citet{DukesShpitserTchetgen2023}
develop proximal mediation identification using negative controls and bridge
functions; the present proposal is about what remains sharply identified when
the relevant finite bridge system is not unique.
\citet{ZhangLiMiaoTchetgen2023} show that proximal causal effects can remain
point identified without uniqueness of the bridge solution when all admissible
bridges agree on the target functional; this proposal instead studies the
case where admissible bridges disagree on each mediation component but agree
on a one-dimensional joint geometry.
\citet{GhassamiShpitserTchetgen2023} develop partial identification of causal
effects using proxy variables when proximal point-identification conditions
fail; their target is a proxy-bounded causal effect rather than the coupled
PNDE/TNIE decomposition line segment proposed here.
\citet{MiaoShiLiTchetgen2024} study double-negative-control bridge correction
in related causal-effect settings; they motivate the rank/completeness issue
but do not state a joint PNDE/TNIE partial-identification geometry.
\citet{PenningDeVriesGroenwold2023} survey negative-control caveats,
including weak or redundant controls; the proposal gives one formal
target-loading-specific sense in which redundancy is not all-or-nothing.
\citet{GabrielSachsSjolander2023} warn that separately sharp decomposition
bounds for mediation effects require careful joint construction rather than
naive combination; this is the closest published decomposition-bounds novelty
axis, and the proposed line segment is a positive joint sharpness conjecture
in a proxy-constrained model.

In-repo, `ThmSmith/doc/API.md' reports that the ThmSmith ExactID and PartialID
catalogues are empty at seed time, so there is no existing ThmSmith proposal
whose kernel coincides with this one.  The promoted AutoID catalogue in
`../doc/API.md' contains partial-identification infrastructure for Manski
bounds, Balke--Pearl sharp latent-table bounds, and proximal proxy bounds for
ATE-style targets; these are relevant substrate and comparison points, but
none records a mediation-specific joint PNDE/TNIE proxy-null identified set.

\section{Formal setup}
Let \(O=(X,A,M,Y,W,Z)\sim P\), with \(A,M,W,Z\in\{0,1\}\) and
\(Y\in[0,1]\).  The latent variables
\(\{U(a,m):a,m\in\{0,1\}\}\) are unobserved treatment- and
mediator-history-specific mediator--outcome confounder states.  They allow the
confounder process to be post-treatment while keeping each cross-world object
indexed by the intervention history under which it is evaluated.  The
observed latent state is \(U=U(A,M)\), and the observed proxies are
\(W=W(A,M)\) and \(Z=Z(A,M)\).  The targets are
\[
  \theta_D=\E\{Y(1,M(0))-Y(0,M(0))\}, \qquad
  \theta_I=\E\{Y(1,M(1))-Y(1,M(0))\}.
\]
When a total-effect compatibility check is invoked, write
\(\theta_T=\E\{Y(1,M(1))-Y(0,M(0))\}\).
For each finite stratum \(c=(x,a,m)\), write \(r_c(z)=\E[Y\mid
X=x,A=a,M=m,Z=z]\), \(h_c(w)\in[0,1]\) for an outcome bridge indexed by
\(W=w\), and \(K_c(z,w)=P(W=w\mid X=x,A=a,M=m,Z=z)\).  The observable bridge
equation is
\[
  K_c h_c = r_c.
\]
The proposal studies the rank-deficient binary-proxy case where every
solution can be written \(h_c(\eta)=h_c^0+\eta n_c\) with a single scalar
\(\eta\) shared across the natural-effect functionals.  Outcome-range and
observable compatibility constraints restrict the scalar to an interval
\([\ell(P),u(P)]\).  The natural-effect functionals are known affine maps of
the bridge family:
\[
  \theta_D(\eta)=\theta_D^0+\beta_D\eta,\qquad
  \theta_I(\eta)=\theta_I^0+\beta_I\eta,
\]
where the constants are computed from \(P\), the mediator distributions
\(P(M=m\mid A=a,X=x)\), and the chosen bridge representatives
\(\{h_c^0,n_c\}\).  The candidate affine bound is
\[
  B(P)=\{(\theta_D(\eta),\theta_I(\eta)):
      \eta\in[\ell(P),u(P)]\}.
\]
The notation \(\Theta_D(P)\) and \(\Theta_I(P)\) is reserved for the marginal
PNDE and TNIE intervals, respectively; only \(\Theta_{D,I}(P)\) denotes the
sharp joint identified set.

For the sharpness question, let \(\mathcal{L}(P)\) denote the finite
mean-kernel latent polytope of nonnegative masses over binary response types
for
\[
  \{M(a),U(a,m),W(a,m),Z(a,m):a,m\in\{0,1\}\}
\]
together with bounded outcome mean kernels
\(\mu_{a,m,u}\in[0,1]\).  Elements of \(\mathcal{L}(P)\) reproduce the
observable law of \((X,A,M,W,Z)\) and the observable conditional outcome means
\(r_c(z)=\E[Y\mid X=x,A=a,M=m,Z=z]\) through
\((A,M(A),W(A,M(A)),Z(A,M(A)))\); they do not attempt to encode the full
conditional distribution of the bounded outcome \(Y\).  When \(Y\) is binary,
this mean-kernel convention coincides with a standard binary
outcome-response-type polytope.  The polytope also obeys the exclusion,
consistency, positivity, and shared-null bridge restrictions.
For \(Q\in\mathcal{L}(P)\), let \(\eta(Q)\) be the scalar shared-null
coordinate induced by its bridge representative, write
\(\theta_D(Q)=\theta_D(\eta(Q))\) and
\(\theta_I(Q)=\theta_I(\eta(Q))\), and define the primitive projection
\[
  E(P)=\{\eta(Q):Q\in\mathcal{L}(P)\}.
\]
The observable bridge equations imply \(E(P)\subseteq[\ell(P),u(P)]\).  The
nontrivial sharpness question is whether the reverse inclusion holds.

\begin{quote}
\textbf{Locked parameters repeated.}
\texttt{qid = pid\_mediation\_proxy};
\texttt{specialization = v1};
observable distribution \(P\) is the law of \(O=(X,A,M,Y,W,Z)\), where
\(A\in\{0,1\}\) is a single binary treatment, \(M\in\{0,1\}\) is a mediator,
\(Y\in[0,1]\) is an outcome, and \(W,Z\in\{0,1\}\) are negative-control
proxies for treatment- and mediator-history-indexed unobserved
mediator--outcome confounders \(U(a,m)\);
parameter \(\theta=(\theta_D,\theta_I)\), where
\(\theta_D=\mathrm{PNDE}(1,0)\) and \(\theta_I=\mathrm{TNIE}(1,0)\);
identifying restrictions are consistency, treatment ignorability conditional
on \(X\), mediator/proxy positivity, negative-control exclusion and relevance,
and the one-dimensional shared proxy-null bridge-fiber restriction in
Assumption~\ref{ass:shared-null};
the bounding functional is the affine image
\[
  B(P)=\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\},
\]
where \([\ell(P),u(P)]\) is the observable feasibility interval induced by
the rank-deficient bridge equations and the outcome-range constraints.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite binary mediation system]\label{ass:finite}
The variables satisfy \(A,M,W,Z\in\{0,1\}\), \(Y\in[0,1]\), and \(X\) has
finite support.  All cells used in conditional probabilities below have
strictly positive probability.
\end{assumption}

\begin{assumption}[Consistency and treatment ignorability]\label{ass:consistency}
Observed \(M\) and \(Y\) equal their corresponding factual potential outcomes,
and \(A\) is conditionally independent of the relevant treatment-indexed
potential outcomes, treatment- and mediator-history-indexed latent confounder
states, and proxy response types given \(X\).  Factual consistency also sets
\(U=U(A,M(A))\), \(W=W(A,M(A))\), and \(Z=Z(A,M(A))\).
\end{assumption}

\begin{assumption}[Negative-control exclusion]\label{ass:negative-control}
For each realised history \(c=(x,a,m)\), conditional on
\((X=x,A=a,M=m,U(a,m))\), \(Z(a,m)\) carries no direct information about the
outcome bridge other than through \(U(a,m)\), and \(W(a,m)\) is an
outcome-inducing proxy for \(U(a,m)\) with no direct treatment or mediator
effect except through the history-indexed bridge relation encoded by
\(K_c h_c=r_c\).
\end{assumption}

\begin{assumption}[Rank-deficient binary bridge]\label{ass:rank-def}
For each \(c=(x,a,m)\), the observed \(2\times2\) matrix
\(K_c(z,w)=P(W=w\mid X=x,A=a,M=m,Z=z)\) has rank one, the equation
\(K_c h_c=r_c\) is feasible, and its solution set is
\(\{h_c^0+\eta_c n_c:\eta_c\in I_c(P)\}\) for a nonzero null vector \(n_c\).
\end{assumption}

\begin{assumption}[Shared proxy-null coordinate]\label{ass:shared-null}
The feasible bridge solutions relevant to \(\theta_D\) and \(\theta_I\) are
indexed by a single scalar \(\eta\), so \(\eta_c=s_c\eta+t_c\) for known
observable signs/scales \(s_c,t_c\).  The common feasible interval
\([\ell(P),u(P)]\) is the intersection of the stratum intervals after this
reparameterisation.
\end{assumption}

\begin{assumption}[Affine natural-effect loading]\label{ass:affine-loading}
The PNDE and TNIE functionals induced by the bridge family are
\(\theta_D(\eta)=\theta_D^0+\beta_D\eta\) and
\(\theta_I(\eta)=\theta_I^0+\beta_I\eta\), with
\((\beta_D,\beta_I)\neq(0,0)\).  The constants
\(\theta_D^0,\theta_I^0,\beta_D,\beta_I,\ell(P),u(P)\) are observable
functionals of \(P\) under Assumptions~\ref{ass:finite}--\ref{ass:shared-null}.
\end{assumption}

\begin{assumption}[Primitive mean-kernel feasibility]\label{ass:latent-polytope}
The finite mean-kernel latent polytope \(\mathcal{L}(P)\) defined in the
formal setup is nonempty.  Every \(Q\in\mathcal{L}(P)\) reproduces
\(P_{X,A,M,W,Z}\) and the observable conditional outcome means \(r_c(z)\),
satisfies Assumptions~\ref{ass:finite}--\ref{ass:affine-loading}, indexes all
latent confounder and proxy response types by \((a,m)\), and induces a
well-defined shared-null scalar \(\eta(Q)\in[\ell(P),u(P)]\).  This assumption
does not assert that every \(\eta\in[\ell(P),u(P)]\) is attainable.
\end{assumption}

\begin{assumption}[Total-effect bridge compatibility]\label{ass:total-effect}
The total effect \(\theta_T=\E\{Y(1,M(1))-Y(0,M(0))\}\) is identified from
\(P\) under the same consistency and treatment-ignorability conditions, and
for every primitive mean-kernel model \(Q\in\mathcal{L}(P)\) the natural-effect
decomposition holds:
\[
  \theta_D(Q)+\theta_I(Q)=\theta_T.
\]
This assumption fixes the total effect but does not separately impose any
value on the affine loading \(\beta_D+\beta_I\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: affine marginal proxy-null intervals]\label{thm:affine-marginals}
Under Assumptions~\ref{ass:finite}--\ref{ass:affine-loading}, the candidate
marginal ranges generated by the shared bridge fiber are
\[
  \Theta_D(P)=
  [\min_{\eta\in[\ell(P),u(P)]}\theta_D(\eta),
   \max_{\eta\in[\ell(P),u(P)]}\theta_D(\eta)]
\]
and
\[
  \Theta_I(P)=
  [\min_{\eta\in[\ell(P),u(P)]}\theta_I(\eta),
   \max_{\eta\in[\ell(P),u(P)]}\theta_I(\eta)].
\]
If both \(\beta_D\) and \(\beta_I\) are nonzero and \(\ell(P)<u(P)\), then
the affine image \(B(P)\) is a line segment and is a strict subset of
\(\Theta_D(P)\times\Theta_I(P)\).
\end{theorem}

\paragraph{Why this is new and worth studying.}
The closest published warning is \citet{GabrielSachsSjolander2023}, which
shows that separately sharp decomposed bounds need not combine sharply; this
theorem identifies a concrete proxy-null mechanism that explains why the
product of candidate marginal PNDE and TNIE intervals is too large.  It advances the
field by giving a finite-dimensional diagnostic: compute the two loadings
\(\beta_D,\beta_I\) and the shared feasibility interval before reporting
separate mediation bounds as if they were jointly attainable.

\begin{conjecture}[Conjecture 1: sharp joint proxy-null mediation set (NOT YET PROVED)]\label{conj:sharp-joint}
Under Assumptions~\ref{ass:finite}--\ref{ass:affine-loading} and
Assumption~\ref{ass:latent-polytope}, the primitive mean-kernel projection
satisfies \(E(P)=[\ell(P),u(P)]\).  Consequently, the sharp joint identified
set for \((\mathrm{PNDE}(1,0),\mathrm{TNIE}(1,0))\) is exactly
\[
  \Theta_{D,I}(P)=B(P)
  =\{(\theta_D^0+\beta_D\eta,\theta_I^0+\beta_I\eta):
       \eta\in[\ell(P),u(P)]\}.
\]
Equivalently, every point on the line segment is attainable by a model with
observable \((X,A,M,W,Z)\) law and conditional outcome means matching \(P\),
and no point off the segment is attainable.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
\citet{DukesShpitserTchetgen2023} focus on proximal mediation identification
when bridge conditions are strong enough for point identification, while
\citet{MilesKankiMeloniTchetgen2015},
\citet{MilesKankiMeloniTchetgen2017}, and
\citet{DingVanderWeele2016} bound natural effects without exploiting a
proxy-null bridge fiber.
\citet{ZhangLiMiaoTchetgen2023} and
\citet{GhassamiShpitserTchetgen2023} are the closest proxy-based
nonuniqueness and partial-identification comparators, but they treat target
functionals whose bridge-null disagreement is either eliminated or bounded
directly rather than a pair of natural-effect components that share the same
null coordinate.  The conjecture is not a weaker-assumption variant of those
papers or of the no-proxy pure-direct/natural-indirect bounds: it asserts that
primitive mean-kernel feasibility fills the whole observable proxy-null
interval and therefore creates a new sharp joint geometry in mediation.
Resolving it would make weak negative
controls operational, because the remaining unidentified direction would be an
observable one-dimensional sensitivity coordinate rather than an analyst-chosen
sensitivity parameter.

\begin{theorem}[Theorem 2: total-effect hyperplane compatibility]\label{thm:te-plane}
Under Assumptions~\ref{ass:finite}--\ref{ass:affine-loading},
Assumption~\ref{ass:latent-polytope}, Assumption~\ref{ass:total-effect}, and
the sharpness conclusion \(E(P)=[\ell(P),u(P)]\) from
Conjecture~\ref{conj:sharp-joint}, if \(\ell(P)<u(P)\), then
\[
  \beta_D+\beta_I=0
  \quad\text{and}\quad
  \theta_D(\eta)+\theta_I(\eta)=\theta_T
  \quad\text{for all }\eta\in[\ell(P),u(P)].
\]
\end{theorem}

\paragraph{Why this is new and worth studying.}
The closest decomposition literature treats the direct and indirect pieces as
separate bounded targets and then asks how they add up.  This theorem is no
longer an assumption in disguise: Assumption~\ref{ass:total-effect} fixes the
primitive-model decomposition on attainable points, while
Conjecture~\ref{conj:sharp-joint} supplies enough attainable shared-null
variation to force the affine slope restriction.  The result would give a
proxy-null falsification check: if an estimated shared-null model with a
nondegenerate interval produces a nonzero total-effect loading, the locked
assumptions are incoherent.

\section{Sanity-check corollaries}
\begin{corollary}[Full-rank proxy reduction]\label{cor:full-rank}
If Assumption~\ref{ass:rank-def} is replaced by full column rank of every
\(K_c\), then \(\ell(P)=u(P)\), so \(B(P)\) collapses to a singleton.  This is
the proximal point-identification corner case studied by
\citet{DukesShpitserTchetgen2023}.
\end{corollary}

\begin{corollary}[Total-effect sanity check]\label{cor:te}
Under Assumption~\ref{ass:total-effect} and the conclusion of
Theorem~\ref{thm:te-plane}, the line segment \(B(P)\) lies in the observable
affine hyperplane \(\theta_D+\theta_I=\theta_T\).  Thus the
proposal cannot create spurious variation in the total effect while varying
the direct and indirect pieces.
\end{corollary}

\section{Proof-sketch route}
The algebraic theorem reduces to two facts from finite-dimensional linear
programming: a rank-one \(2\times2\) bridge equation has a one-dimensional
affine solution fiber, and a linear functional maps a compact interval to a
compact interval whose endpoints occur at the scalar endpoints.  The sharpness
conjecture should be attacked by a finite latent-type construction: enumerate
binary response types for
\(\{M(a),U(a,m),W(a,m),Z(a,m):a,m\in\{0,1\}\}\), add bounded outcome mean
kernels \(\mu_{a,m,u}\in[0,1]\), impose the observed cell-probability,
conditional-mean, and bridge equations as linear constraints, and show that
the resulting polytope projection \(E(P)\) equals the whole observable interval
\([\ell(P),u(P)]\).  Equivalently, fixing
\(\eta\in[\ell(P),u(P)]\) should admit a nonnegative latent mean-kernel table
that reproduces \(P_{X,A,M,W,Z}\), the observed conditional outcome means, and
attains \((\theta_D(\eta),\theta_I(\eta))\).  The boundary cases needing
explicit algebra are the two endpoint tables
\(\eta=\ell(P)\) and \(\eta=u(P)\), plus the degeneracies \(\beta_D=0\),
\(\beta_I=0\), and \(\ell(P)=u(P)\).  The total-effect compatibility theorem
is then routine algebra: once at least two values of \(\eta\) are attainable
and all attainable primitive models share the same \(\theta_T\), the affine
function \(\theta_D(\eta)+\theta_I(\eta)\) must have zero slope.

\section{Honest scope flags}
Theorems~\ref{thm:affine-marginals} and \ref{thm:te-plane} are routine algebra
statements conditional on the locked shared-null setup and, for
Theorem~\ref{thm:te-plane}, on the sharpness conclusion of
Conjecture~\ref{conj:sharp-joint}.  Conjecture~\ref{conj:sharp-joint} is not
yet proved; its hard part is the mean-kernel latent sharpness construction,
specifically the equality
\(E(P)=[\ell(P),u(P)]\), not the affine projection algebra.  The strongest
scope restriction is Assumption~\ref{ass:shared-null}: if the PNDE and TNIE
depend on independent bridge-null coordinates, the joint set can become
higher-dimensional and the proposed line segment is false.  This version also
withdraws the v1--v2 formulation that assumed endpoint bridge realisability;
attainability is now the open content of Conjecture~\ref{conj:sharp-joint}.
This angle withdraws any claim that proxy rank deficiency by itself
point-identifies a single natural effect; the kernel is joint geometry under a
shared null coordinate.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 2: joint PNDE/TNIE sharp set as
a shared proxy-null line segment; prior verdict: none.
\item v2 (revise) --- corrected the Miles et al. bibliography title, reserved
\(\Theta_I(P)\) for the TNIE marginal interval while naming the joint set
\(\Theta_{D,I}(P)\), and added the missing Zhang et al. and Ghassami et al.
proxy partial-identification comparisons; prior verdict: REVISE.
\item v3 (revise) --- replaced sharp bridge realisability by primitive
latent-table feasibility, made endpoint/interior attainability the explicit
content of Conjecture~\ref{conj:sharp-joint}, and added the missing pure
direct-effect and path-specific-effect mediation comparisons; prior verdict:
REVISE.
\item v4 (revise) --- indexed the post-treatment mediator--outcome confounder
and proxy response types by treatment/mediator histories throughout the setup
and latent polytope; prior verdict: REVISE.
\item v5 (revise) --- replaced the bounded-outcome binary response-type
polytope by a bounded mean-kernel latent polytope, weakened total-effect
compatibility, and relabelled the hyperplane result as conditional algebra in
Theorem~\ref{thm:te-plane};
prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Avin et~al.(2005)]{AvinShpitserPearl2005}
Avin, C., Shpitser, I., and Pearl, J. (2005).
Identifiability of path-specific effects.
In \emph{Proceedings of IJCAI}.

\bibitem[Cai et~al.(2008)]{CaiKurokiPearlTian2008}
Cai, Z., Kuroki, M., Pearl, J., and Tian, J. (2008).
Bounds on direct effects in the presence of confounded intermediate variables.
\emph{Biometrics}.

\bibitem[Ding and VanderWeele(2016)]{DingVanderWeele2016}
Ding, P. and VanderWeele, T. J. (2016).
Sharp sensitivity bounds for mediation under unmeasured mediator--outcome confounding.
\emph{Biometrika}.

\bibitem[Dukes et~al.(2023)]{DukesShpitserTchetgen2023}
Dukes, O., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
Proximal mediation analysis.
\emph{Biometrika}.

\bibitem[Gabriel et~al.(2023)]{GabrielSachsSjolander2023}
Gabriel, E. E., Sachs, M. C., and Sjolander, A. (2023).
Sharp nonparametric bounds for decomposition effects with two binary mediators.
\emph{Journal of the American Statistical Association}.

\bibitem[Ghassami et~al.(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
Partial identification of causal effects using proxy variables.
\emph{arXiv preprint arXiv:2304.04374}.

\bibitem[Imai et~al.(2010)]{ImaiKeeleYamamoto2010}
Imai, K., Keele, L., and Yamamoto, T. (2010).
Identification, inference and sensitivity analysis for causal mediation effects.
\emph{Statistical Science}.

\bibitem[Miao et~al.(2024)]{MiaoShiLiTchetgen2024}
Miao, W., Shi, X., Li, W., and Tchetgen Tchetgen, E. J. (2024).
A confounding bridge approach for double negative control inference.
\emph{Statistical Theory and Related Fields}.

\bibitem[Miles et~al.(2017)]{MilesKankiMeloniTchetgen2017}
Miles, C. H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E. J. (2017).
On partial identification of the natural indirect effect.
\emph{Journal of Causal Inference}.

\bibitem[Miles et~al.(2015)]{MilesKankiMeloniTchetgen2015}
Miles, C. H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E. J. (2015).
On partial identification of the pure direct effect.
\emph{Harvard University Biostatistics Working Paper Series}, Working Paper
196; arXiv:1509.01652.

\bibitem[Miles et~al.(2017)]{MilesShpitserKankiMeloniTchetgen2017Path}
Miles, C. H., Shpitser, I., Kanki, P., Meloni, S., and Tchetgen Tchetgen,
E. J. (2017).
On semiparametric estimation of a path-specific effect in the presence of
mediator-outcome confounding.
\emph{arXiv preprint arXiv:1710.02011}.

\bibitem[Penning de Vries et~al.(2023)]{PenningDeVriesGroenwold2023}
Penning de Vries, B. B. L., Groenwold, R. H. H., and colleagues (2023).
Negative controls in epidemiological studies: caveats, weak controls, and design guidance.
\emph{Statistical Methods in Medical Research}.

\bibitem[Zhang et~al.(2023)]{ZhangLiMiaoTchetgen2023}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. J. (2023).
Proximal causal inference without uniqueness assumptions.
\emph{Statistics \& Probability Letters}, 198, 109836.
\end{thebibliography}

\end{document}
