\begin{abstract}
This paper studies lower bounds for estimating an interior continuous-treatment dose-response partial mean. The target is
\[
\theta_P(t_0)=\int \mu_P(t_0,x)p_{X,P}(x)\,dx,
\]
interpretable as a causal dose-response mean under consistency, no unmeasured confounding, and local positivity. Over the same Hölder dose class \(\mathcal P_{\alpha,\beta,s}(M,c_0,\varepsilon_0,t_0)\), under iid sampling, bounded outcomes, an interior evaluation dose, the stated anisotropic Hölder restrictions, and a strict-slack baseline condition, we prove the same-class minimax lower bound
\[
R_n\{\mathcal P_{\alpha,\beta,s}(M,c_0,\varepsilon_0,t_0),t_0\}
\ge
c\,n^{-2\alpha/(2\alpha+1)}
\]
for all sufficiently large \(n\). The lower-bound exponent is the one-dimensional treatment-regression exponent and holds for every fixed \(\beta>0\), although the constant and slack-baseline feasibility may depend on \(\beta\). We compare this lower floor with the published higher-order influence-function benchmark
\[
\rho_n=
n^{-2\alpha/(2\alpha+1)}
\vee
n^{-2/(1+d/(4s)+1/\alpha)}.
\]
When \(d\le 4s\), the lower-bound exponent equals the exponent of this published comparator, whose upper theorem concerns a distinct localized-regularity class. When \(4s<d\), the benchmark is governed by the covariate-smoothness term and has a strictly smaller exponent than the same-class lower-floor exponent. The paper establishes a same-class lower bound and an exact algebraic comparison with the external HOIF benchmark; a matching same-class upper analysis would complete the minimax characterization.
\end{abstract}

\section{Introduction}

Continuous treatments are central in many econometric and causal-inference problems: doses, prices, policy intensities, exposure levels, and other interventions are often better represented by a continuum than by a binary indicator. In the potential-outcome framework of \citet{rubin1974} and \citet{robins1986}, the object of interest is commonly a dose-specific mean \(E\{Y(t)\}\). Under consistency, conditional ignorability, and positivity, this causal object is identified by an observed-data partial mean, averaging the conditional regression of \(Y\) on \((A,X)\) at dose \(t\) over the marginal distribution of covariates. This paper studies the difficulty of estimating that fixed-dose partial mean at an interior dose.

The formal target is \cref{obj:def:theta-functional},
\[
\theta_P(t_0)=\int_{[0,1]^d}\mu_P(t_0,x)p_{X,P}(x)\,dx,
\]
where \(A\in[0,1]\), \(X\in[0,1]^d\), and \(\mu_P(a,x)=E_P[Y\mid A=a,X=x]\). The model class in \cref{obj:def:holder-dose-class} imposes iid sampling, bounded outcomes, an interior evaluation dose, local positivity, Hölder smoothness of the outcome regression and treatment density in the treatment coordinate, and Hölder smoothness of the relevant covariate functions. The causal assumptions supply the interpretation of the same observed-data functional as a dose-response mean; the lower bound itself is a statement about the observed-data experiment and the minimax risk in \cref{obj:def:minimax-risk}.

The continuous-treatment literature provides both the identification background and the estimator benchmarks for this problem. Early formulations include the generalized propensity-score and propensity-function approaches of \citet{imbens2000}, \citet{hirano2004}, and \citet{imai2004}, with comparisons developed by \citet{zhao2013}. Semiparametric efficiency and influence-function methods provide the language for regular estimation and orthogonalization \citep{bickel1993,vanderVaart1998,vanderLaan2003,chernozhukov2018}. For nonparametric dose-response curves, \citet{kennedy2017}, \citet{lee2018}, and \citet{colangelo2020} are direct antecedents. The closest upper-side benchmark for this paper is \citet{bonvini2022}, which builds on higher-order influence-function methods \citep{robins2008,robins2015} and reports the rate recorded here as \cref{obj:def:published-hoif-rate}.

The main result is a same-class lower bound. Under the hypotheses of \cref{obj:thm:sharp-pointwise-lower-bound}, including positive smoothness \(\alpha,\beta,s\), the stated interior and boundedness constants, and the strict-slack baseline condition in \cref{obj:ass:baseline-submodel-slack}, there is a constant \(c>0\) such that, for all sufficiently large \(n\),
\[
c\,n^{-2\alpha/(2\alpha+1)}
\le
R_n\!\left(
\mathcal P_{\alpha,\beta,s}(M,c_0,\varepsilon_0,t_0),
t_0
\right).
\]
This theorem establishes the lower half of the minimax analysis for the original Hölder dose class and fixes the treatment-regression obstruction at exponent \(2\alpha/(2\alpha+1)\).

The comparison sequence is
\[
\rho_n=
n^{-2\alpha/(2\alpha+1)}
\vee
n^{-2/(1+d/(4s)+1/\alpha)}.
\]
In the smooth-covariate regime \(d\le 4s\), \cref{obj:prop:oracle-regime-reduction} and \cref{obj:thm:sharp-minimax-smooth-covariate} show that the lower-bound exponent equals the exponent of \(\rho_n\), giving an exact exponent comparison with the published benchmark. In the deficient-covariate regime \(4s<d\), \cref{obj:thm:frontier-bracket-deficient} shows that \(\rho_n\) is governed by the covariate-smoothness expression and has a strictly smaller exponent than the certified same-class lower floor. This ordering isolates the same-class upper behavior as the remaining question in that regime.

The lower-bound construction can be viewed as embedding the classical one-dimensional pointwise nonparametric regression obstruction inside the continuous-treatment partial-mean experiment. The embedding must preserve the observed-data restrictions of \cref{obj:def:holder-dose-class}: bounded outcomes, local positivity around \(t_0\), smooth covariate density, treatment-density smoothness, and the causal dose-response interpretation. The strict-slack baseline condition in \cref{obj:ass:baseline-submodel-slack} is used to keep the least favorable alternatives inside the class while perturbing only the treatment regression. This is why the resulting lower exponent is insensitive to the fixed treatment-density smoothness index \(\beta\) at the exponent level, while constants and feasibility may still depend on \(\beta\).

The scope is deliberately narrower than neighboring continuous-exposure problems. Recent work studies modified treatment policies, weak-overlap or alternative identification regimes, nonparametric inference for dose-response curves, and incremental continuous-exposure interventions \citep{hejazi2022,doss2022,hudson2023,shi2024,zhang2024,schindl2024,bonvini2024}. Those estimands or positivity structures can change the role of the treatment density and the smoothing built into the target. The present paper concerns the fixed interior partial mean in \cref{obj:def:theta-functional} under the same-class Hölder restrictions in \cref{obj:def:holder-dose-class}.

The formal statements used in the paper are accompanied by Lean~4 verification artifacts; the precise verification scope is summarized in the verification appendix. The mathematical contribution is the same-class lower bound, the two algebraic comparisons with the published HOIF benchmark, and the explicit separation between those lower-bound statements and upper results proved for other localized-regularity classes.
