% Stage 0.k fragment for Conjecture 2 (label=phase).
% Contains this conjecture's contributions to Sections 9--13.

\paragraph{Conjecture 2 (verbatim).}
Under Assumptions~\ref{ass:heap}--\ref{ass:equal-grid}, the integer
\[
\tau^\star(G,W,L;q^0)=\operatorname{rank}(R^{\mathrm{feas}}_{G,W,L}(q^0))
\]
is well typed and computable from \(A_G\), \(S_W\), \(C_{G,W,L}\), \(\ell_{G,W,L}\), and the face \(\mathcal{D}_G(q^0)\).  The equal-grid design is point-informative for the bunching mass on the observed feasible face exactly when \(\tau^\star(G,W,L;q^0)=0\).  When \(\tau^\star(G,W,L;q^0)=1\), the row \(r_{G,W,L}^{\transpose}\) has one independent loading on feasible heap contrasts, and an aliasing certificate \(Z_G\alpha\) exists for some \(\alpha\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)\) with \(\ell_{G,W,L}^{\transpose}Z_G\alpha\neq0\).  If Assumption~\ref{ass:face} also holds, this criterion equals the full-nullspace screen \(\operatorname{rank}(R^{\mathrm{full}}_{G,W,L})=0\).

\begin{theorem}[Equal-grid phase screen]\label{thm:phase}
Under Assumptions~\ref{ass:heap}--\ref{ass:equal-grid}, the feasible-loading rank
\[
\tau^\star(G,W,L;q^0)=\operatorname{rank}(R^{\mathrm{feas}}_{G,W,L}(q^0))
\]
is a computable integer in \(\{0,1\}\), and the equal-grid design is point-informative for \(\theta_B\) on the observed feasible face if and only if \(\tau^\star(G,W,L;q^0)=0\).  If \(\tau^\star(G,W,L;q^0)=1\), there are two feasible contrast points whose difference \(\alpha\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)\) gives a signed heap-null aliasing certificate \(Z_G\alpha\) with \(\ell_{G,W,L}^{\transpose}Z_G\alpha\neq0\).  Under Assumption~\ref{ass:face}, this feasible-face criterion is equivalent to the full-nullspace screen \(\operatorname{rank}(R^{\mathrm{full}}_{G,W,L})=0\).
\end{theorem}

\paragraph{Refutation attempt before proof.}
The relevant refutation primitive is vertex enumeration of the feasible contrast polytope.  In the heaping design, the smallest response-type LP analogue has latent masses \(q_j\) as the unknown types, heap equations \(A_Gq=P^H\), simplex constraints \(q\ge0\) and \(\one^{\transpose}q=1\), and the known continuation operator \(C_{G,W,L}\).  After fixing \(q^0\), every observationally equivalent candidate in the observed feasible face has the form \(q^0+Z_G\alpha\) with \(\alpha\in\mathcal{A}_G(q^0)\).  Thus a refuting witness must be one of the following:
\[
\begin{array}{ll}
\text{false positive:} & \operatorname{rank}(R^{\mathrm{feas}}_{G,W,L}(q^0))=0
\text{ but } r_{G,W,L}^{\transpose}(\alpha-\alpha')\ne0
\text{ for feasible }\alpha,\alpha',\\[3pt]
\text{false negative:} & \operatorname{rank}(R^{\mathrm{feas}}_{G,W,L}(q^0))=1
\text{ but } r_{G,W,L}^{\transpose}(\alpha-\alpha')=0
\text{ for every feasible }\alpha,\alpha',\\[3pt]
\text{face mismatch:} &
\mathcal{D}_G(q^0)=\mathbb{R}^{d_G}
\text{ but the feasible screen and full-nullspace screen disagree.}
\end{array}
\]
Enumerating vertex differences is enough, because a linear loading reaches its extrema on vertices of the finite contrast polytope, and every feasible contrast difference lies in the span of such differences.  The false-positive case cannot occur: a nonzero loading on a feasible vertex difference is a nonzero loading on \(\mathcal{D}_G(q^0)\), so the restricted row has rank one.  The false-negative case cannot occur: if all feasible vertex differences have zero loading, then by linearity all of \(\mathcal{D}_G(q^0)\) is annihilated and the restricted rank is zero.  The face-mismatch case cannot occur under Assumption~\ref{ass:face}, because the feasible direction span is the full nullspace coordinate space.  The refutation search therefore finds no witness under the stated assumptions.

\paragraph{Interpretation.}
The theorem says that heaping creates a precise linear-algebraic phase frontier.  The observed heap histogram fixes totals within heap cells, but it does not generally fix how mass is allocated within a cell.  The matrix \(Z_G\) lists exactly those within-fiber reallocations that preserve the observed histogram, while \(r_{G,W,L}^{\transpose}=\ell_{G,W,L}^{\transpose}Z_G\) measures how each such reallocation changes latent excess bunching mass.  The feasible face \(\mathcal{D}_G(q^0)\) removes directions blocked by nonnegativity, summability, or continuation feasibility at the observed law.  Therefore \(\tau^\star=0\) means every feasible observational alias leaves \(\theta_B\) unchanged, so the bound collapses to a point on that face.  The value \(\tau^\star=1\) means that one scalar degree of observable aliasing remains for the scalar bunching target, so the observed heap histogram cannot distinguish two latent densities with different excess mass.  Equal-grid geometry matters because it makes \(S_W\), \(C_{G,W,L}\), and hence \(\ell_{G,W,L}\), a known finite-dimensional map of the design rather than an unspecified smoothness extrapolation.

\subsubsection*{Proof of Conjecture 2}
\begin{proof}
We use finite-dimensional linear algebra and the standard extreme-point logic for linear optimization over a compact polytope.  Assumption~\ref{ass:heap} gives the known incidence matrix \(A_G\).  Choose a column basis \(Z_G\in\mathbb{R}^{J\times d_G}\) for \(\operatorname{Null}(A_G)\), so
\[
A_GZ_G=0
\quad\text{and}\quad
\operatorname{range}(Z_G)=\operatorname{Null}(A_G).
\]
Assumption~\ref{ass:fiber} supplies a nonempty compact feasible set and a reference point \(q^0\in\mathcal{F}(P^H)\).  Hence every feasible \(q\in\mathcal{F}(P^H)\) with the same observed histogram satisfies
\[
A_G(q-q^0)=P^H-P^H=0,
\]
so \(q-q^0=Z_G\alpha\) for a unique coordinate vector \(\alpha\in\mathbb{R}^{d_G}\).  By definition of the contrast set, this vector belongs to \(\mathcal{A}_G(q^0)\) exactly when \(q^0+Z_G\alpha\in\mathcal{F}(P^H)\).

Assumption~\ref{ass:linear-cont} gives the known scalar loading \(\ell_{G,W,L}\), and Assumption~\ref{ass:equal-grid} makes \(S_W\) and \(C_{G,W,L}\) known design matrices with
\[
\ell_{G,W,L}^{\transpose}=\one^{\transpose}S_W-\one^{\transpose}C_{G,W,L}.
\]
Define
\[
r_{G,W,L}^{\transpose}=\ell_{G,W,L}^{\transpose}Z_G .
\]
For any two feasible contrast coordinates \(\alpha,\alpha'\in\mathcal{A}_G(q^0)\), the corresponding target difference is
\[
\theta_B(q^0+Z_G\alpha)-\theta_B(q^0+Z_G\alpha')
=\ell_{G,W,L}^{\transpose}Z_G(\alpha-\alpha')
=r_{G,W,L}^{\transpose}(\alpha-\alpha').
\]
The first equality uses the linear target representation in Assumption~\ref{ass:linear-cont}; the second is the definition of \(r_{G,W,L}\).

Now let \(B_G(q^0)\in\mathbb{R}^{d_G\times k}\) be any matrix whose columns form a basis for the feasible direction span
\[
\mathcal{D}_G(q^0)=\operatorname{span}\{\alpha-\alpha':\alpha,\alpha'\in\mathcal{A}_G(q^0)\}.
\]
This basis is computable from the supplied face \(\mathcal{D}_G(q^0)\) by row reduction; if the face is represented by vertices of \(\mathcal{A}_G(q^0)\), it is obtained by row-reducing all vertex differences.  Define the feasible-loading matrix
\[
R^{\mathrm{feas}}_{G,W,L}(q^0)=r_{G,W,L}^{\transpose}B_G(q^0).
\]
This is a \(1\times k\) matrix, with \(k=\dim\mathcal{D}_G(q^0)\), so its rank is well typed and belongs to \(\{0,1\}\).  Each ingredient is computable from \(A_G\), \(S_W\), \(C_{G,W,L}\), \(\ell_{G,W,L}\), and \(\mathcal{D}_G(q^0)\): compute \(Z_G\) from \(A_G\), compute \(r_{G,W,L}^{\transpose}\) from \(\ell_{G,W,L}^{\transpose}Z_G\), compute \(B_G(q^0)\) from the face, and compute the row rank of \(r_{G,W,L}^{\transpose}B_G(q^0)\) by Gaussian elimination.

We next prove the point-informativeness criterion.  The design is point-informative for \(\theta_B\) on the observed feasible face exactly when the value of \(\theta_B(q^0+Z_G\alpha)\) is the same for all \(\alpha\in\mathcal{A}_G(q^0)\).  By the displayed target-difference identity, this is equivalent to
\[
r_{G,W,L}^{\transpose}(\alpha-\alpha')=0
\quad\text{for all }\alpha,\alpha'\in\mathcal{A}_G(q^0).
\]
Because \(\mathcal{D}_G(q^0)\) is the linear span of these feasible differences, the preceding condition is equivalent to
\[
r_{G,W,L}^{\transpose}d=0
\quad\text{for all }d\in\mathcal{D}_G(q^0).
\]
Writing \(d=B_G(q^0)t\), this is equivalent to
\[
r_{G,W,L}^{\transpose}B_G(q^0)t=0
\quad\text{for all }t\in\mathbb{R}^k,
\]
which is equivalent to \(R^{\mathrm{feas}}_{G,W,L}(q^0)=0\), and hence to
\[
\operatorname{rank}(R^{\mathrm{feas}}_{G,W,L}(q^0))=0.
\]
This proves that point-informativeness on the observed feasible face holds exactly when \(\tau^\star(G,W,L;q^0)=0\).

If instead \(\tau^\star(G,W,L;q^0)=1\), then the row \(r_{G,W,L}^{\transpose}\) does not annihilate \(\mathcal{D}_G(q^0)\).  Therefore there is some \(d\in\mathcal{D}_G(q^0)\) with \(r_{G,W,L}^{\transpose}d\ne0\).  Since \(\mathcal{D}_G(q^0)\) is the span of feasible differences, at least one feasible difference \(\alpha-\alpha'\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)\) must satisfy
\[
r_{G,W,L}^{\transpose}(\alpha-\alpha')\ne0;
\]
otherwise every linear combination of feasible differences would have zero loading, contradicting the choice of \(d\).  Set \(\bar\alpha=\alpha-\alpha'\).  Then
\[
A_GZ_G\bar\alpha=0
\]
and
\[
\ell_{G,W,L}^{\transpose}Z_G\bar\alpha
=r_{G,W,L}^{\transpose}\bar\alpha\ne0.
\]
Thus \(Z_G\bar\alpha\) is a signed heap-null aliasing certificate that changes latent excess bunching mass while preserving the observed heap equations.  This proves the certificate claim.

Finally impose Assumption~\ref{ass:face}.  Then \(\mathcal{D}_G(q^0)=\mathbb{R}^{d_G}\).  We may choose \(B_G(q^0)\) to be any invertible \(d_G\times d_G\) basis matrix, and the full-nullspace loading is
\[
R^{\mathrm{full}}_{G,W,L}=r_{G,W,L}^{\transpose}.
\]
Because right multiplication by an invertible basis matrix does not change whether a row is zero,
\[
\operatorname{rank}(R^{\mathrm{feas}}_{G,W,L}(q^0))=0
\quad\Longleftrightarrow\quad
r_{G,W,L}^{\transpose}=0
\quad\Longleftrightarrow\quad
\operatorname{rank}(R^{\mathrm{full}}_{G,W,L})=0.
\]
Therefore, on the full affine face, the feasible-face point-informativeness criterion and the full-nullspace screen coincide.
\end{proof}

\paragraph{Sanity check.}
Consider the corner case in which every heap cell is a singleton, so \(h_G\) is one-to-one and \(A_G\) is a permutation of the identity matrix.  Then \(\operatorname{Null}(A_G)=\{0\}\), hence \(d_G=0\), \(Z_G\) is the empty \(J\times0\) basis, and \(r_{G,W,L}^{\transpose}\) is the empty row.  The feasible direction span is \(\mathcal{D}_G(q^0)=\{0\}\), so \(R^{\mathrm{feas}}_{G,W,L}(q^0)\) is a \(1\times0\) zero matrix and
\[
\tau^\star(G,W,L;q^0)=0.
\]
The heap histogram now directly reveals the latent density \(q\), so \(\theta_B(q)=\ell_{G,W,L}^{\transpose}q\) is point-informative.  This is exactly the zero-aliasing special case predicted by the theorem.

\paragraph{Counterexample or minimality check.}
The restriction to the observed feasible face is essential.  Take three equally spaced latent support points in a single heap cell, so \(A_G=(1\ \ 1\ \ 1)\), and let the continuation-feasibility part of \(\mathcal{Q}_{G,W,L}\) restrict the observed feasible face to
\[
\mathcal{F}(P^H)=\{(t,1-t,0)^{\transpose}:0\le t\le1\}.
\]
This satisfies nonemptiness and compactness in Assumption~\ref{ass:fiber}.  Choose \(q^0=(1/2,1/2,0)^{\transpose}\) and \(\ell_{G,W,L}=(0,0,1)^{\transpose}\).  Then \(\theta_B(q)=0\) for every \(q\in\mathcal{F}(P^H)\), so the feasible-face screen has rank zero and the target is point-informative on the observed feasible face.  However, the full heap nullspace of \(A_G\) contains directions such as \((1,0,-1)^{\transpose}\), and
\[
\ell_{G,W,L}^{\transpose}(1,0,-1)^{\transpose}=-1\ne0.
\]
The full-nullspace screen therefore has nonzero rank even though no feasible contrast on the observed face changes \(\theta_B\).  Thus replacing \(R^{\mathrm{feas}}\) by the full-nullspace screen without Assumption~\ref{ass:face} gives a false negative for point-informativeness.  Assumption~\ref{ass:face} is precisely the support condition that makes the two screens equivalent.
