% --- S9-fragment-statement ---
\begin{theorem}[Conjecture 1: sharp aliasing frontier]\label{thm:frontier}
\paragraph{Conjecture restated verbatim.}
Under Assumptions~\ref{ass:heap}, \ref{ass:fiber}, and \ref{ass:linear-cont},
\[
B_{G,W,E,L}(P^H)=
\ell_{G,W,L}^{\transpose}q^0+
\left[
\min_{\alpha\in\mathcal{A}_G(q^0)} r_{G,W,L}^{\transpose}\alpha,
\max_{\alpha\in\mathcal{A}_G(q^0)} r_{G,W,L}^{\transpose}\alpha
\right],
\]
and \(\theta_B\) is point identified if and only if
\[
r_{G,W,L}^{\transpose}\alpha=0
\quad\text{for every }\alpha\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0).
\]
If the condition fails, an extreme point of the normalized contrast polytope gives a finite signed-nullspace certificate \(Z_G\alpha\) and two feasible latent densities \(q^-,q^+\) with \(A_Gq^-=A_Gq^+=P^H\) and \(\theta_B(q^-)\neq\theta_B(q^+)\).

Equivalently, the endpoint map is the linear image of the feasible contrast polytope, and point identification holds exactly when \(r_{G,W,L}^{\transpose}\) vanishes on \(\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)\).
\end{theorem}

% --- S13-refutation-attempt ---
\paragraph{Refutation attempt before proof.}
The appropriate primitive is vertex enumeration of the finite feasible fiber.  A counterexample to the frontier formula would have to be one of three algebraic vertex patterns.

First, there could be a feasible latent density \(q\in\mathcal{F}(P^H)\) that is not represented by any contrast \(\alpha\in\mathcal{A}_G(q^0)\).  The search over this pattern is empty.  Since \(q,q^0\in\mathcal{F}(P^H)\), Assumption~\ref{ass:heap} gives
\[
A_G(q-q^0)=P^H-P^H=0,
\]
so \(q-q^0\in\operatorname{Null}(A_G)\).  The columns of \(Z_G\) span this nullspace, hence \(q=q^0+Z_G\alpha\) for some \(\alpha\).  Because \(q\) is feasible, that \(\alpha\) lies in \(\mathcal{A}_G(q^0)\).

Second, there could be a represented contrast \(\alpha\in\mathcal{A}_G(q^0)\) whose endpoint value differs from the displayed linear contrast value.  This search also has no witness: Assumption~\ref{ass:linear-cont} gives \(\theta_B(q)=\ell_{G,W,L}^{\transpose}q\), so for \(q=q^0+Z_G\alpha\),
\[
\theta_B(q)=\ell_{G,W,L}^{\transpose}q^0+
\ell_{G,W,L}^{\transpose}Z_G\alpha
=\ell_{G,W,L}^{\transpose}q^0+r_{G,W,L}^{\transpose}\alpha .
\]

Third, there could be a point-identification failure not detected by the difference polytope.  Vertex enumeration again gives no such witness.  The set \(\mathcal{A}_G(q^0)\) is compact by Assumption~\ref{ass:fiber} and the affine map \(\alpha\mapsto q^0+Z_G\alpha\).  Thus the image of \(\mathcal{A}_G(q^0)\) under the linear row \(r_{G,W,L}^{\transpose}\) is a compact interval.  That interval is a singleton exactly when the row is constant on \(\mathcal{A}_G(q^0)\), equivalently when it vanishes on every difference \(\alpha-\alpha'\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)\).  Therefore no finite vertex of the searched contrast polytope violates the conjectured criterion.  The proof below records this finite-dimensional argument as the sharp identified-set calculation.

% --- S10 Interpretation ---
\paragraph{Interpretation.}
The theorem says that heaping creates aliasing only through within-fiber movements of latent probability mass.  The observable histogram \(P^H\) fixes the heap totals \(A_Gq=P^H\), but it does not generally fix how mass is distributed across latent support points inside a heap fiber.  The basis \(Z_G\) lists exactly those heap-preserving redistributions, and the row
\[
r_{G,W,L}^{\transpose}=\ell_{G,W,L}^{\transpose}Z_G
\]
measures how each such redistribution changes the latent excess mass after the order-\(L\) continuation rule is applied.

The causal target is the latent scalar \(\theta_B(q)\), not the observed heap histogram itself.  The computable identifying functional is the interval obtained by optimizing the explicit linear map \(r_{G,W,L}^{\transpose}\alpha\) over the finite contrast polytope \(\mathcal{A}_G(q^0)\).  Hence the result gives a sharp partial-identification statement:
\[
\Theta_I(P^H)=B_{G,W,E,L}(P^H).
\]
Point identification occurs precisely when every feasible within-fiber contrast has zero loading under \(r_{G,W,L}^{\transpose}\).  If any feasible contrast has nonzero loading, the observed heap histogram admits two latent density completions with different bunching mass, and the obstruction is the signed-nullspace certificate \(Z_G(\alpha-\alpha')\).

This differs from ordinary extrapolation uncertainty in bunching designs.  The continuation rule is held fixed and linear; the theorem isolates the additional loss from deterministic rounding or heaping.  The endpoint calculation is evaluable from \(P^H\), \(A_G\), \(Z_G\), \(q^0\), and \(\ell_{G,W,L}\) by a finite linear program with \(d_G\) decision variables, constraints \(q^0+Z_G\alpha\in\Delta(\mathcal{X})\), \(A_G(q^0+Z_G\alpha)=P^H\), and the continuation-feasibility constraints in \(\mathcal{Q}_{G,W,L}\).

% --- S11 Proof ---
\begin{proof}
Write \(\ell=\ell_{G,W,L}\), \(r=r_{G,W,L}\), \(A=A_G\), \(Z=Z_G\), and \(\mathcal{A}=\mathcal{A}_G(q^0)\) for readability.

First, establish the exact reparameterization of the feasible fiber.  Let \(q\in\mathcal{F}(P^H)\).  Since \(q^0\in\mathcal{F}(P^H)\) by Assumption~\ref{ass:fiber}, both \(q\) and \(q^0\) satisfy the observed heap equations.  Assumption~\ref{ass:heap} therefore gives
\[
A(q-q^0)=Aq-Aq^0=P^H-P^H=0.
\]
Thus \(q-q^0\in\operatorname{Null}(A)\).  By the definition of the nullspace basis \(Z\), there is \(\alpha\in\mathbb{R}^{d_G}\) such that
\[
q-q^0=Z\alpha.
\]
Because \(q\in\mathcal{F}(P^H)\), this \(\alpha\) satisfies \(q^0+Z\alpha\in\mathcal{F}(P^H)\), hence \(\alpha\in\mathcal{A}\).  Conversely, if \(\alpha\in\mathcal{A}\), then \(q^0+Z\alpha\in\mathcal{F}(P^H)\) by the definition of \(\mathcal{A}\).  Therefore
\[
\mathcal{F}(P^H)=\{q^0+Z\alpha:\alpha\in\mathcal{A}\}.
\]

Second, translate the target functional through this parameterization.  Assumption~\ref{ass:linear-cont} gives \(\theta_B(q)=\ell^{\transpose}q\) on the feasible fiber.  Hence, for every \(\alpha\in\mathcal{A}\),
\[
\theta_B(q^0+Z\alpha)
=\ell^{\transpose}(q^0+Z\alpha)
=\ell^{\transpose}q^0+\ell^{\transpose}Z\alpha
=\ell^{\transpose}q^0+r^{\transpose}\alpha,
\]
where the last equality is the definition \(r^{\transpose}=\ell^{\transpose}Z\).

Third, compute the identified set.  By definition,
\[
\Theta_I(P^H)=\{\theta_B(q):q\in\mathcal{F}(P^H)\}.
\]
Combining the previous two displays yields
\[
\Theta_I(P^H)
=
\left\{\ell^{\transpose}q^0+r^{\transpose}\alpha:
\alpha\in\mathcal{A}\right\}.
\]
Assumption~\ref{ass:fiber} gives compactness and nonemptiness of \(\mathcal{F}(P^H)\).  Since the map \(\alpha\mapsto q^0+Z\alpha\) is continuous and \(\mathcal{A}\) is the inverse image of \(\mathcal{F}(P^H)\) under this affine map restricted to the finite-dimensional contrast coordinates, the relevant feasible contrast image is compact and nonempty.  A continuous linear functional attains its minimum and maximum on this compact set, so
\[
\Theta_I(P^H)=
\ell^{\transpose}q^0+
\left[
\min_{\alpha\in\mathcal{A}}r^{\transpose}\alpha,
\max_{\alpha\in\mathcal{A}}r^{\transpose}\alpha
\right].
\]
This is the claimed formula for \(B_{G,W,E,L}(P^H)\), and it is sharp because every value in the interval is attained by a convex mixture of endpoint contrasts whenever \(\mathcal{A}\) is convex, and by the displayed image set in the general compact finite-dimensional formulation.  In the maintained algebraic heaping setup, \(\mathcal{A}\) is a polytope because it is cut out by the simplex constraints, the affine heap equations, and the linear continuation rule, so its linear image is exactly the closed interval between the two endpoint values.

Fourth, prove the point-identification criterion.  The target is point identified from \(P^H\) exactly when \(\Theta_I(P^H)\) is a singleton.  By the formula above, this is equivalent to
\[
\min_{\alpha\in\mathcal{A}}r^{\transpose}\alpha
=
\max_{\alpha\in\mathcal{A}}r^{\transpose}\alpha,
\]
that is, \(r^{\transpose}\alpha\) is constant on \(\mathcal{A}\).  A linear functional is constant on \(\mathcal{A}\) if and only if it vanishes on all pairwise differences:
\[
r^{\transpose}(\alpha-\alpha')=0
\quad\text{for all }\alpha,\alpha'\in\mathcal{A}.
\]
This is exactly
\[
r_{G,W,L}^{\transpose}\beta=0
\quad\text{for every }\beta\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0).
\]

Finally, suppose the condition fails.  Then there are \(\alpha^+,\alpha^-\in\mathcal{A}\) with
\[
r^{\transpose}(\alpha^+-\alpha^-)\ne 0.
\]
Set
\[
q^+=q^0+Z\alpha^+,\qquad q^-=q^0+Z\alpha^-.
\]
By the definition of \(\mathcal{A}\), both \(q^+\) and \(q^-\) lie in \(\mathcal{F}(P^H)\), and since \(AZ=0\),
\[
Aq^+=Aq^-=Aq^0=P^H.
\]
Their bunching masses differ because
\[
\theta_B(q^+)-\theta_B(q^-)
=\ell^{\transpose}Z(\alpha^+-\alpha^-)
=r^{\transpose}(\alpha^+-\alpha^-)
\ne0.
\]
Equivalently, maximizing \(|r^{\transpose}\beta|\) over the compact normalized difference polytope
\[
\mathcal{C}_G(q^0)=\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)
\]
attains a nonzero value at an extreme point \(\beta^\star\).  The signed vector \(Z_G\beta^\star\) is a finite nullspace certificate: \(A_GZ_G\beta^\star=0\), but \(\ell_{G,W,L}^{\transpose}Z_G\beta^\star\ne0\).  Choosing any representation \(\beta^\star=\alpha^+-\alpha^-\) with \(\alpha^\pm\in\mathcal{A}_G(q^0)\) gives the displayed feasible densities \(q^\pm\).  This proves the conjecture.
\end{proof}

% --- S12 Sanity check ---
\paragraph{Sanity check.}
Consider the no-heaping corner case in which every heap fiber is a singleton.  Then \(A_G\) is a permutation of the identity matrix, \(\operatorname{Null}(A_G)=\{0\}\), and \(d_G=0\).  The contrast polytope is \(\mathcal{A}_G(q^0)=\{0\}\), so
\[
r_{G,W,L}^{\transpose}\alpha=0
\quad\text{for every }\alpha\in\mathcal{A}_G(q^0)-\mathcal{A}_G(q^0)=\{0\}.
\]
The theorem reduces to
\[
B_{G,W,E,L}(P^H)=\left[\ell_{G,W,L}^{\transpose}q^0,\ell_{G,W,L}^{\transpose}q^0\right],
\]
which is exactly the ordinary fully observed finite-grid bunching functional under the fixed continuation rule.  Thus deterministic heaping is the only source of the aliasing interval in this corner case.

% --- S13 Counterexample or minimality check ---
\paragraph{Minimality check.}
The known-heap-map and linear-continuation assumptions are both essential.  If Assumption~\ref{ass:heap} is dropped, then \(A_G\) and its nullspace are not observed-population inputs, so the contrast set \(\mathcal{A}_G(q^0)\) is not an evaluable map from \(P^H\).  The same observed histogram could be generated by two different heap maps with different nullspaces, producing different rows \(r_{G,W,L}^{\transpose}\).

If Assumption~\ref{ass:linear-cont} is dropped, the equality
\[
\theta_B(q^0+Z_G\alpha)
=\ell_{G,W,L}^{\transpose}q^0+r_{G,W,L}^{\transpose}\alpha
\]
need not hold.  Then a heap-preserving direction \(Z_G\alpha\) may have a nonlinear or undefined effect on the counterfactual continuation term, and optimizing the linear row \(r_{G,W,L}^{\transpose}\alpha\) is only a relaxation.  Thus the sharp frontier is not a generic Manski bound over latent histograms; it is the exact linear image of the observed feasible face under the maintained continuation operator.
