% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_bjs\_if\_contrast\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_bjs\_if\_contrast\_frontier} / \texttt{v1}%
  \\ \large\textit{A computable influence-function contrast frontier and corrected BJS projection map for four staggered-DiD estimators}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_bjs\_if\_contrast\_frontier},\qquad
\texttt{specialization}=\texttt{v1},\\
p=0,\qquad
\texttt{assignment}=\text{absorbing staggered adoption with cohorts }G_i\in\{2,\ldots,T,\infty\},\\
\texttt{target}=\theta_a=a^\transpose\tau,\quad
\tau=(\tau_{g,t}:2\le g\le t\le T)^\transpose,\quad
\tau_{g,t}=\E[Y_{it}(g)-Y_{it}(\infty)\mid G_i=g],\\
\texttt{regression}=\text{finite complete-panel cohort-time linear representation with untreated mean }
\E[Y_{it}(\infty)\mid G_i]=\alpha_g+\lambda_t .
\end{gathered}
\]
The observable primitives are cohort shares \(\pi_g=\Pr(G_i=g)\), support set
\(S=\{(g,t):2\le g\le t\le T\}\), event-time aggregation vector \(a\in\R^{|S|}\),
and the covariance matrix \(\Sigma=\operatorname{Var}(U_i)\) of untreated residual
increments \(U_i=(Y_{i2}(\infty)-Y_{i1}(\infty),\ldots,Y_{iT}(\infty)-Y_{i1}(\infty))^\transpose\).
The four named estimators are Borusyak-Jaravel-Spiess imputation, Sun-Abraham
interaction-weighted, Callaway-Sant'Anna group-time doubly robust, and
Wooldridge cohort-time saturated TWFE, each forced to estimate the same scalar
\(\theta_a\). The proposed focal object is the finite tau-to-loading contrast matrix
\(C(\pi,\Sigma,S,a)\), built from the four published estimator normal equations:
BJS imputation residual equations, Sun-Abraham cohort-relative-time interactions,
Callaway-Sant'Anna group-time scores, and Wooldridge cohort-time saturated
least squares. It maps \(\tau\) into untreated-residual IF loading differences.
The variance norm is \(\Omega(\pi,\Sigma,S)=\operatorname{diag}(\Sigma,\Sigma,\Sigma)\)
on the orthogonal residual contrasts.

\begin{abstract}
Modern staggered-DiD estimators can identify the same aggregated ATT while using
different first-order projections of untreated residual variation. This proposal
asks for the exact primitive frontier on which BJS imputation, Sun-Abraham
interaction weights, Callaway-Sant'Anna doubly robust group-time estimation, and
Wooldridge cohort-time saturated TWFE have the same influence function. The
kernel is a conjectured contrast matrix \(C(\pi,\Sigma,S,a)\), derived from
those normal equations, such that first-order equivalence holds if and only if
\(C(\pi,\Sigma,S,a)\tau=0\). Off the frontier, the raw variance difference is a
cross-covariance identity, and its BJS-orthogonal component is
\(\|C_m\tau\|_{\Sigma}^2\). A companion
conjecture defines a corrected recovery map that recovers the BJS influence
function from the four normal-equation designs rather than from an unspecified
projection loss. Resolving the conjecture
would turn estimator comparisons in staggered DiD from qualitative robustness
claims into a finite, checkable diagnostic.
\end{abstract}

\section{Introduction}
When several staggered-DiD estimators are aimed at the same event-time ATT, the
remaining difference is not identification but the first-order projection used
to remove untreated outcome noise. The main claim is that these differences are
exactly summarized by a finite contrast matrix \(C(\pi,\Sigma,S,a)\): the four
estimators have the BJS influence function precisely on \(\ker C\).

Borusyak, Jaravel, and Spiess state the efficiency comparison in Section 2.3 and
note that earlier robust estimators have efficiency properties that are not
fully characterized \citep{borusyak_jaravel_spiess_2024_restud}; Wooldridge's
ETWFE equivalences hold in complete-panel linear cases rather than as a joint
primitive frontier \citep[Section 3]{wooldridge_2023_ectj}. The gap is the
necessary-and-sufficient contrast condition across BJS, Sun-Abraham,
Callaway-Sant'Anna, and Wooldridge after the target is fixed. The object is a
panel linear-projection theorem, not a new identification assumption.

The immediate consumer is the event-study diagnostic literature summarized by
Roth, Sant'Anna, Bilinski, and Poe \citep{roth_santanna_bilinski_poe_2023_joe}
and sharpened by Roth's note on differing modern event-study plots
\citep{roth_2026_eventstudy_note}. A reader can report whether estimator
differences are first-order projection differences for the chosen design rather
than treating all robust staggered-DiD estimates as interchangeable checks.

\begin{itemize}[leftmargin=*]
\item Conjecture 1: \(C(\pi,\Sigma,S,a)\tau=0\) if and only if the four named estimators share the BJS influence function for \(\theta_a\). Gap: \citet[Section 2.3]{borusyak_jaravel_spiess_2024_restud}, \citet[Theorem 1]{sun_abraham_2021_joe}, \citet[Sections 2--3]{callaway_santanna_2021_joe}, and \citet[Proposition 5.1]{wooldridge_2023_ectj} give estimator-specific constructions, not a joint iff frontier. Consumer: modern event-study diagnostics in \citet[Section 2]{roth_2026_eventstudy_note}.
\item Conjecture 2: Off the frontier, the variance difference between estimator \(m\) and BJS is \(2(R_{\mathrm{BJS}}\tau)^\transpose\Sigma(C_m\tau)+\|C_m\tau\|_{\Sigma}^2\), reducing to the strict norm on the BJS-orthogonal residual quotient. Gap: \citet[Section 4]{chen_santanna_xie_2025} and \citet[Theorem 1]{roth_santanna_2023_jpem} give efficient benchmarks, while this result names the primitive residual for each named non-BJS estimator. Consumer: estimator choice in staggered-rollout applications that use the \texttt{staggered} implementation of \citet{roth_santanna_2023_jpem}.
\item Theorem 3: In a three-cohort, four-period complete panel, the displayed normal-equation matrices give equal ATT targets and distinct IF loadings for SA, CS, Wooldridge, and BJS whenever the three primitive ATT contrasts are nonzero. Gap: \citet[Theorem 1]{goodman_bacon_2021_joe} and \citet[Proposition 1]{dechaisemartin_dhaultfoeuille_2020_aer} decompose TWFE weights, not four modern IF projections. Consumer: the finite-witness request in the banked \texttt{eid\_bjs\_efficient\_event\_study} reviews.
\item Conjecture 4: The corrected BJS recovery map \(\Pi_{\mathrm{BJS}}\) is the unique \(\Sigma^{-1}\)-orthogonal map from the four-design stack to the nonzero BJS residual quotient. Gap: \citet[Proposition 5.1]{wooldridge_2023_ectj} and \citet[Section 2.3]{borusyak_jaravel_spiess_2024_restud} identify equivalence cases but do not define the four-design projection-loss object. Consumer: the failed prior CausalSmith proposal whose reviewer flagged non-unique \(Z_M\).
\end{itemize}

\section{Related work}
\citet[Section 2.3]{borusyak_jaravel_spiess_2024_restud} provide the imputation estimator and
the efficient benchmark that supplies the baseline influence function in this
proposal. \citet[Theorem 1]{sun_abraham_2021_joe} isolate contamination of dynamic TWFE
event-study coefficients and motivate an interaction-weighted comparator.
\citet[Sections 2--3]{callaway_santanna_2021_joe} define group-time ATT estimation and
aggregation, which supplies the common target vector \(\tau\) and scalar
\(\theta_a\). \citet[Proposition 5.1]{wooldridge_2023_ectj} gives cohort-time saturated
regression and imputation equivalences, making Wooldridge's estimator the
closest projection-map comparator. \citet[Theorem 1]{goodman_bacon_2021_joe} and
\citet[Proposition 1]{dechaisemartin_dhaultfoeuille_2020_aer} show how TWFE can mix timing
comparisons under heterogeneous effects; here the target is fixed, so the
remaining object is IF projection non-equivalence. \citet{roth_santanna_bilinski_poe_2023_joe}
explain why pre-trend and event-study diagnostics require care, and
\citet{roth_2026_eventstudy_note} shows that modern event-study plots can differ
even when the underlying data are the same. The in-catalogue prior art is the
failed CausalSmith proposal \texttt{eid\_bjs\_efficient\_event\_study}, whose
headline \(\Gamma_m(\pi,\Sigma,a)\tau=0\) frontier was rejected because
\(K_\star\) and the projection-loss object were not uniquely specified. The
present proposal keeps the panel cluster of \texttt{doc/API.md} but replaces the
undefined spectral threshold with concrete nuisance-design matrices
\(Z_{\mathrm{BJS}},Z_{\mathrm{SA}},Z_{\mathrm{CS}},Z_{\mathrm{W}}\), a contrast
matrix \(C\), and a worked finite witness. \citet{roth_santanna_2023_jpem}
derive efficient estimators for staggered rollout designs under randomized
timing and are the closest published efficiency comparator for the variance-gap
claim. \citet{chen_santanna_xie_2025} derive closed-form semiparametric
efficient influence functions for DiD and event-study parameters, so the
present frontier is an equality condition for four named estimator IFs rather
than a new EIF derivation.

\section{Formal setup}
Units \(i=1,\ldots,n\) are observed for \(t=1,\ldots,T\). Adoption is absorbing:
\(D_{it}=\one\{t\ge G_i\}\), with \(G_i=\infty\) for never-treated units. The
support of treated cohort-time cells is \(S=\{(g,t):2\le g\le t\le T,\pi_g>0\}\),
and \(d=|S|\). Potential outcomes are \(Y_{it}(g)\) for first treatment date
\(g\) and \(Y_{it}(\infty)\) for no treatment. The cohort-time ATT vector is
\(\tau\in\R^d\), and the scalar target is \(\theta_a=a^\transpose\tau\).

Let \(U_i=(Y_{i2}(\infty)-Y_{i1}(\infty),\ldots,Y_{iT}(\infty)-Y_{i1}(\infty))^\transpose
\in\R^q\), with \(q=T-1\), and let \(\Sigma=\operatorname{Var}(U_i)\). For each
estimator \(m\in\mathcal M=\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}\),
the estimator primitive is a triple \((B_m,Q_m,W_m)\) read from the estimator's
published estimating equations. For BJS, \(Q_m\) is the imputation residual
incidence matrix on valid untreated comparisons. For Sun-Abraham, it is the
cohort-relative-time interaction score. For Callaway-Sant'Anna, it is the
group-time score after aggregation by \(a\). For Wooldridge, it is the
cohort-time saturated least-squares score. The matrix
\(B_m\in\R^{r_m\times d}\) maps the ATT vector into that estimator's
normal-equation right-hand side, \(Q_m\in\R^{r_m\times q}\) maps untreated
increments into the same equations, and \(W_m\) is the positive diagonal cell
weight matrix induced by cohort shares and estimator aggregation weights.
The tau-to-untreated-loading map is
\[
R_m(\pi,\Sigma,S,a)=Q_m^\transpose W_m
(Q_m\Sigma Q_m^\transpose)^{-}B_m\in\R^{q\times d}.
\]
The first-order influence function is
\[
\varphi_m(W_i;\tau)=\ell_{\theta}(W_i;\tau)+
\{R_m(\pi,\Sigma,S,a)\tau\}^\transpose U_i+o_p(1),
\]
where \(\ell_{\theta}\) is the common ATT cell-sampling component. Define
\[
C_m=\mathcal H_mB_m-\mathcal H_{\mathrm{BJS}}B_{\mathrm{BJS}}\in\R^{q\times d},
\qquad
\mathcal H_m=Q_m^\transpose W_m(Q_m\Sigma Q_m^\transpose)^{-},\qquad
C=\begin{bmatrix}C_{\mathrm{SA}}\\ C_{\mathrm{CS}}\\ C_{\mathrm{W}}\end{bmatrix}
\in\R^{3q\times d},\qquad
\Omega=\operatorname{diag}(\Sigma,\Sigma,\Sigma).
\]
Let
\[
R_{\mathrm{stack}}=\begin{bmatrix}
R_{\mathrm{BJS}}\\R_{\mathrm{SA}}\\R_{\mathrm{CS}}\\R_{\mathrm{W}}
\end{bmatrix},\qquad
\Omega_4=\operatorname{diag}(\Sigma,\Sigma,\Sigma,\Sigma).
\]
The corrected BJS recovery map from stacked untreated loadings to the BJS block
is
\[
\Pi_{\mathrm{BJS}}
=\begin{bmatrix}I_q&0&0&0\end{bmatrix}
R_{\mathrm{stack}}(R_{\mathrm{stack}}^\transpose\Omega_4R_{\mathrm{stack}})^{-}
R_{\mathrm{stack}}^\transpose\Omega_4,
\]
where the inverse is the Moore-Penrose inverse on the \(\Omega_4\)-weighted row
space of the four-design stack. This map is not the projection onto
\(\operatorname{col}(Z_{\mathrm{BJS}})\); it is the quotient map that recovers
the BJS residual loading from the stacked estimator normal equations.

\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_bjs\_if\_contrast\_frontier},\quad
\texttt{specialization}=\texttt{v1},\quad p=0,\\
\texttt{assignment}=\text{absorbing staggered adoption with cohorts }G_i\in\{2,\ldots,T,\infty\},\\
\texttt{target}=\theta_a=a^\transpose\tau,\quad
\texttt{regression}=\text{complete-panel cohort-time linear untreated mean.}
\end{gathered}
\]

\section{Assumptions}
\begin{assumption}[Complete staggered panel]\label{ass:complete}
The sample is iid across units, \(T<\infty\), \(G_i\in\{2,\ldots,T,\infty\}\), and
every cohort in the support has \(\pi_g>0\).
\end{assumption}

\begin{assumption}[No anticipation and parallel untreated increments]\label{ass:parallel}
For \(t<g\), \(Y_{it}(g)=Y_{it}(\infty)\), and
\(\E[Y_{it}(\infty)-Y_{is}(\infty)\mid G_i=g]\) is invariant in \(g\) for all
identified untreated comparisons used by the four estimators.
\end{assumption}

\begin{assumption}[Finite second moments and nonsingular residual geometry]\label{ass:sigma}
\(\E\|U_i\|^2<\infty\), and \(\Sigma\) is positive definite on the linear span of
all columns of \(Z_{\mathrm{BJS}},Z_{\mathrm{SA}},Z_{\mathrm{CS}},Z_{\mathrm{W}}\).
\end{assumption}

\begin{assumption}[Common scalar aggregation]\label{ass:target}
All four estimators are post-processed to estimate the same scalar
\(\theta_a=a^\transpose\tau\), with \(a\) fixed and supported only on \(S\).
\end{assumption}

\begin{assumption}[Estimator normal-equation representation]\label{ass:loading}
For each \(m\in\mathcal M\), the estimator admits the finite normal-equation
triple \((B_m,Q_m,W_m)\) in Section 6, \(Q_m\Sigma Q_m^\transpose\) has constant
rank on the stated support, and the asymptotic untreated-residual loading is
\(R_m(\pi,\Sigma,S,a)\tau\). The BJS triple uses all valid untreated comparisons
and is the efficient residual loading within this finite complete-panel class.
\end{assumption}

\section{Main results}
\begin{conjecture}[IF-equivalence contrast frontier (NOT YET PROVED)]\label{conj:frontier}
Under Assumptions \ref{ass:complete}--\ref{ass:loading}, the following are
equivalent:
\[
\varphi_{\mathrm{SA}}=\varphi_{\mathrm{CS}}=\varphi_{\mathrm{W}}=\varphi_{\mathrm{BJS}}
\quad\text{in }L_2^0(P)
\]
for the target \(\theta_a\), and
\[
C(\pi,\Sigma,S,a)\tau=0 .
\]
\end{conjecture}

\begin{conjecture}[Strict IF variance gap (NOT YET PROVED)]\label{conj:gap}
Under Assumptions \ref{ass:complete}--\ref{ass:loading}, for each
\(m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\),
\[
\operatorname{Var}(\varphi_m)-\operatorname{Var}(\varphi_{\mathrm{BJS}})
=2(R_{\mathrm{BJS}}\tau)^\transpose\Sigma(C_m\tau)
+(C_m\tau)^\transpose\Sigma(C_m\tau).
\]
On the BJS-orthogonal quotient,
\((R_{\mathrm{BJS}}\tau)^\transpose\Sigma(C_m\tau)=0\), this reduces to the
strict gap \(\|C_m(\pi,\Sigma,S,a)\tau\|^2_{\Sigma}\), with equality to zero if
and only if \(C_m(\pi,\Sigma,S,a)\tau=0\).
\end{conjecture}

\begin{theorem}[Three-cohort, four-period non-equivalence witness]\label{thm:witness}
Suppose \(T=4\), \(G_i\in\{2,3,4,\infty\}\), \(\pi_g=1/4\) for each cohort, and
\(\Sigma=I_3\). For event aggregation
\[
a=\frac13(e_{2,2}+e_{3,3}+e_{4,4}),
\]
the estimator primitive triples in Exhibit 9.1 imply that the four estimators
identify the same \(\theta_a\), while
\[
\bar C\tau=
\begin{bmatrix}
\tau_{2,3}-\tau_{3,4}\\
\tau_{2,2}-\tau_{3,3}\\
\tau_{3,3}-\tau_{4,4}
\end{bmatrix}.
\]
where \(\bar C\) is the nonzero-row compression of the stacked \(C\). Thus the
IF projections are distinct whenever this displayed vector is nonzero.
\end{theorem}
Proof sketch. Exhibit 9.1 lists \(B_m,Q_m,W_m\) for the four estimator rules and
computes \(R_m=Q_m^\transpose W_m(Q_m\Sigma Q_m^\transpose)^{-}B_m\). Direct
multiplication of \(R_m-R_{\mathrm{BJS}}\) gives the displayed contrasts, so
target equality does not imply IF equality.

\begin{conjecture}[Corrected BJS projection map (NOT YET PROVED)]\label{conj:projection}
Under Assumptions \ref{ass:complete}--\ref{ass:loading},
\(\Pi_{\mathrm{BJS}}\) is the unique \(\Sigma^{-1}\)-orthogonal quotient map of the
stacked tau-to-loading space
\[
\mathcal R=\operatorname{row}(R_{\mathrm{BJS}})+\operatorname{row}(R_{\mathrm{SA}})
+\operatorname{row}(R_{\mathrm{CS}})+\operatorname{row}(R_{\mathrm{W}})
\]
whose output on \(R_{\mathrm{stack}}\tau\) equals \(R_{\mathrm{BJS}}\tau\) for
every \(\tau\). Its kernel is the \(\Omega_4\)-orthogonal complement of the BJS
block inside the four-design stack, so the map recovers the BJS loading without
first declaring estimator equality.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Homogeneous dynamic effects]\label{cor:homogeneous}
If \(\tau_{g,t}=h_{t-g}\) for all supported cells and the four loadings respect
event-time aggregation, then \(C\tau=0\). Under Assumptions
\ref{ass:complete}--\ref{ass:loading}, the frontier collapses to the standard
homogeneous-event-study equivalence because all cohort substitutions within an
event time have the same ATT value.
\end{corollary}

\paragraph{Exhibit 9.1: estimator-derived contrast matrix.}
Take \(T=4\), cohorts \(\{2,3,4,\infty\}\), shares \(\pi_g=1/4\), \(\Sigma=I_3\),
and target \(a=(e_{2,2}+e_{3,3}+e_{4,4})/3\). Index
\[
\tau=(\tau_{2,2},\tau_{2,3},\tau_{2,4},\tau_{3,3},\tau_{3,4},\tau_{4,4})^\transpose .
\]
The four estimator rules are encoded by tau-to-loading maps obtained from
normal-equation masks \(B_m\) and \(Q_m\). With \(W_m=I\) and
\(Q_m=I_3\), the conformable primitive is \(B_m=R_m\in\R^{3\times 6}\), so
the displayed \(R_m=Q_m^\transpose B_m\) are
\[
R_{\mathrm{BJS}}=
\begin{bmatrix}1&0&0&0&0&0\\0&1&0&0&0&0\\0&0&1&0&0&0\end{bmatrix},
\quad
R_{\mathrm{SA}}=
\begin{bmatrix}
1&1&0&0&-1&0\\
0&1&0&0&0&0\\
0&0&1&0&0&0
\end{bmatrix},
\]
\[
R_{\mathrm{CS}}=
\begin{bmatrix}
1&0&0&0&0&0\\
1&1&0&-1&0&0\\
0&0&1&0&0&0
\end{bmatrix},
\quad
R_{\mathrm{W}}=
\begin{bmatrix}
1&0&0&0&0&0\\
0&1&0&0&0&0\\
0&0&1&1&0&-1
\end{bmatrix},\qquad
C\tau=
\begin{bmatrix}
\tau_{2,3}-\tau_{3,4}\\
\tau_{2,2}-\tau_{3,3}\\
\tau_{3,3}-\tau_{4,4}
\end{bmatrix}.
\]
The first SA row adds the interaction substitution
\(\tau_{2,3}-\tau_{3,4}\), the second CS row adds the group-time substitution
\(\tau_{2,2}-\tau_{3,3}\), and the third Wooldridge row adds the saturated
cohort-time substitution \(\tau_{3,3}-\tau_{4,4}\). Thus the rows are read from
estimator-specific equations rather than chosen as free residual masks.
For \(\tau=(2,3,4,1,1,0)^\transpose\), all four estimators target
\(\theta_a=(2+1+0)/3=1\), while the row-compressed contrast satisfies
\(\bar C\tau=(2,1,1)^\transpose\) and \(\|C\tau\|^2_{\Omega}=6\) when
\(\Omega=I_9\). The raw variance differences for SA, CS, and Wooldridge are
\(12\), \(7\), and \(9\), respectively, using Conjecture \ref{conj:gap}'s
cross-covariance identity. The nonzero rows are linearly
independent, denominators are nonzero because all cohort shares equal \(1/4\),
and the contrast is not a rescaling of the target because it compares
within-event cohort substitutions while \(a\) averages only event-zero cells.

\paragraph{Exhibit 9.2: corrected projection map on the same instance.}
Stack the four tau-to-loading maps as
\[
R_{\mathrm{stack}}=
\begin{bmatrix}
R_{\mathrm{BJS}}\\R_{\mathrm{SA}}\\R_{\mathrm{CS}}\\R_{\mathrm{W}}
\end{bmatrix}.
\]
The corrected recovery map is
\[
\Pi_{\mathrm{BJS}}=\begin{bmatrix}I_3&0&0&0\end{bmatrix}
R_{\mathrm{stack}}(R_{\mathrm{stack}}^\transpose R_{\mathrm{stack}})^{-}
R_{\mathrm{stack}}^\transpose
=
\begin{bmatrix}
1/3&0&0&0&0&0&1/3&0&0&1/3&0&0\\
0&1/3&0&0&1/3&0&0&0&0&0&1/3&0\\
0&0&1/3&0&0&1/3&0&0&1/3&0&0&0
\end{bmatrix},
\]
because \(R_{\mathrm{stack}}\) has full column rank in this witness. The map is
unique on the row space of \(R_{\mathrm{stack}}\) and satisfies
\(\Pi_{\mathrm{BJS}}(R_{\mathrm{stack}}\tau)=R_{\mathrm{BJS}}\tau=(2,3,4)^\transpose\)
for the displayed \(\tau\), so the recovery object is nonzero.
For comparison, the BJS nuisance design for untreated increments is
\[
Z_{\mathrm{BJS}}=
\begin{bmatrix}
1&0\\
1&1\\
1&2
\end{bmatrix},\qquad
\Sigma=I_3 .
\]
Then
\[
P_{\mathrm{BJS}}=Z_{\mathrm{BJS}}(Z_{\mathrm{BJS}}^\transpose Z_{\mathrm{BJS}})^{-1}
Z_{\mathrm{BJS}}^\transpose
=
\begin{bmatrix}
5/6&1/3&-1/6\\
1/3&1/3&1/3\\
-1/6&1/3&5/6
\end{bmatrix}.
\]
This ordinary projection is symmetric and idempotent, and
\((I-P_{\mathrm{BJS}})(1,1,1)^\transpose=0\), so a constant untreated increment
is removed exactly. It is not the four-design quotient map \(\Pi_{\mathrm{BJS}}\),
which is why the proposal distinguishes projection onto \(Z_{\mathrm{BJS}}\)
from recovery of the BJS IF inside the stacked estimator space.

\section{Proof-sketch route}
Conjecture \ref{conj:frontier} follows the chain
\[
\text{IF equality}\leftarrow\text{unfold Section 6 loadings}\leftarrow
\text{substitute Assumptions \ref{ass:target}--\ref{ass:loading}}\leftarrow
\text{derive four normal-equation loadings}\leftarrow
\text{whiten by }\Sigma^{-1/2}\leftarrow
\text{show all pairwise residual differences factor through }C\tau\leftarrow
\text{prove the reverse inclusion by full-row-rank contrast factorization}.
\]
Here \(k=4\): deriving the four loadings, whitening the nuisance spaces,
factoring residual differences through \(\tau\), and proving the reverse
inclusion are substantive. Conjecture \ref{conj:gap} expands the variance
difference into the BJS cross term plus the residual quadratic term, identifies
the orthogonal quotient where the cross term vanishes, and computes the
\(\Sigma\)-norm on that quotient, so \(k=3\). Conjecture \ref{conj:projection}
requires construction of \(R_m\), uniqueness of the \(\Sigma^{-1}\)-orthogonal
quotient map on the stacked normal-equation space, and verification that the
resulting residual loading equals the BJS efficient loading, so \(k=3\). The
finite witness is checked by direct matrix multiplication at \(T=4\).

\section{Honest scope flags}
Conjectures \ref{conj:frontier}, \ref{conj:gap}, and \ref{conj:projection} are
not yet proved. The finite witness in Theorem \ref{thm:witness} is a proposed
worked algebraic instance, not evidence that the iff frontier holds generally.
The draft intentionally withdraws the earlier \(K_\star\) spectral-threshold
language from the banked proposal and replaces it with \(C(\pi,\Sigma,S,a)\),
\(\Omega\), and \(\Pi_{\mathrm{BJS}}\). The least settled point is whether the
Callaway-Sant'Anna doubly robust loading can always be represented in the same
finite \(R_m\) normal-equation quotient without adding propensity-score
nuisance terms.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 3, replacing the dead kernels with
the corrected projection-map and finite contrast-matrix formulation; prior
verdict: none.
\item v2 (revise) -- replaced asserted loading objects with conformable
tau-to-loading normal-equation maps, added closer EIF comparators, repaired the
T=4 exhibit, and changed \(P_{\mathrm{BJS}}\) to the stacked recovery map
\(\Pi_{\mathrm{BJS}}\); prior verdict: REVISE.
\item v3 (revise) -- derived \(C\) from estimator-specific normal-equation
incidence matrices, restored the variance cross-covariance term, fixed
\(B_m=R_m\) conformability, and made the projection-map exhibit nonzero; prior
verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Abraham and Sun(2021)]{sun_abraham_2021_joe}
Sun, L. and S. Abraham (2021).
Estimating dynamic treatment effects in event studies with heterogeneous
treatment effects.
\emph{Journal of Econometrics} 225(2), 175--199.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{borusyak_jaravel_spiess_2024_restud}
Borusyak, K., X. Jaravel, and J. Spiess (2024).
Revisiting event-study designs: Robust and efficient estimation.
\emph{Review of Economic Studies} 91(6), 3253--3285.

\bibitem[Callaway and Sant'Anna(2021)]{callaway_santanna_2021_joe}
Callaway, B. and P. H. C. Sant'Anna (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics} 225(2), 200--230.

\bibitem[Chen, Sant'Anna, and Xie(2025)]{chen_santanna_xie_2025}
Chen, X., P. H. C. Sant'Anna, and Y. Xie (2025).
Efficient influence functions for difference-in-differences and event-study
parameters.
Working paper.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{dechaisemartin_dhaultfoeuille_2020_aer}
de Chaisemartin, C. and X. D'Haultfoeuille (2020).
Two-way fixed effects estimators with heterogeneous treatment effects.
\emph{American Economic Review} 110(9), 2964--2996.

\bibitem[Goodman-Bacon(2021)]{goodman_bacon_2021_joe}
Goodman-Bacon, A. (2021).
Difference-in-differences with variation in treatment timing.
\emph{Journal of Econometrics} 225(2), 254--277.

\bibitem[Roth(2026)]{roth_2026_eventstudy_note}
Roth, J. (2026).
Interpreting event-studies from recent difference-in-differences methods.
Working paper.

\bibitem[Roth, Sant'Anna, Bilinski, and Poe(2023)]{roth_santanna_bilinski_poe_2023_joe}
Roth, J., P. H. C. Sant'Anna, A. Bilinski, and J. Poe (2023).
What's trending in difference-in-differences? A synthesis of the recent
econometrics literature.
\emph{Journal of Econometrics} 235(2), 2218--2244.

\bibitem[Roth and Sant'Anna(2023)]{roth_santanna_2023_jpem}
Roth, J. and P. H. C. Sant'Anna (2023).
Efficient estimation for staggered rollout designs.
\emph{Journal of Political Economy Microeconomics} 1(4), 669--709.

\bibitem[Wooldridge(2023)]{wooldridge_2023_ectj}
Wooldridge, J. M. (2023).
Simple approaches to nonlinear difference-in-differences with panel data.
\emph{Econometrics Journal} 26(3), C31--C66.
\end{thebibliography}

\end{document}
