% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_bjs\_if\_contrast\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_bjs\_if\_contrast\_frontier} / \texttt{v1}%
  \\ \large\textit{EIF-rebased influence-function contrast frontier for four staggered-DiD estimators}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{quote}
\texttt{qid = eid\_bjs\_if\_contrast\_frontier; specialization = v1; anchor cluster = Panel.}
The panel has cohorts $g\in\mathcal G=\{2,\ldots,T,\infty\}$, periods
$t\in\{1,\ldots,T\}$, absorbing treatment $D_{it}=\one\{G_i\le t\}$, and
observed outcome $Y_{it}=Y_{it}(D_{i1},\ldots,D_{it})$.  The target is one
fixed scalar aggregation
\[
  \theta_a=\sum_{(g,t)\in\mathcal S} a_{gt}\tau_{gt},\qquad
  \tau_{gt}=\E[Y_{it}(1)-Y_{it}(0)\mid G_i=g],
\]
where $\mathcal S=\{(g,t):g<\infty,\ t\ge g\}$ and $a$ is known with
$\sum_{(g,t)\in\mathcal S}a_{gt}=1$.  The four procedures are BJS imputation,
Sun--Abraham interaction-weighted, Callaway--Sant'Anna group-time doubly
robust, and Wooldridge cohort-time saturated TWFE, each forced onto the same
$\theta_a$.  The primitive design objects are cohort shares
$\pi_g=\Pr(G_i=g)$, untreated residual covariance
$\Sigma_g=\operatorname{Var}((U_{i1},\ldots,U_{i,T})\mid G_i=g)$ for
$U_{it}=Y_{it}(0)-\alpha_i-\lambda_t$, support $\mathcal S$, and the finite
cohort-period incidence matrices defined in Section 6.  The proposed focal
object is a computable contrast matrix $C(\pi,\Sigma,\mathcal G,T)$ and norm
matrix $\Omega(\pi,\Sigma,\mathcal G,T)$ such that first-order influence
functions are equivalent across the four procedures if and only if
$C\tau=0$, and the off-frontier variance gap equals
$\|C\tau\|_{\Omega}^{2}$.
\end{quote}

\begin{abstract}
Modern staggered-DiD estimators can identify the same aggregated
group-time ATT while using different first-order projections.  The question is
whether the projection differences among BJS imputation, Sun--Abraham,
Callaway--Sant'Anna, and Wooldridge saturated TWFE have an exact primitive
frontier.  The flagship conjecture states that, after rebasing all four
estimators against the published efficient influence-function benchmark, a
finite matrix $C(\pi,\Sigma,\mathcal G,T)$ gives first-order equivalence if
and only if $C\tau=0$.  A companion conjecture gives the strict variance gap
as $\|C\tau\|_{\Omega}^{2}$ and a corrected projection map that recovers the
BJS influence function on the frontier.  Resolving the conjecture would turn
current estimator-by-estimator comparisons into a computable diagnostic for
when event-study robustness is also first-order efficiency equivalence.
\end{abstract}

\section{Introduction}
Empirical researchers often report several robust staggered-DiD estimates for
one event-time target.  The main claim is that equality of the target is not
the same as equality of the first-order influence function, and that the
difference is governed by one finite contrast matrix.

\citet[Theorem 1 and Section 4.3]{borusyak_jaravel_spiess_2024_restud}
establish imputation efficiency and emphasize that alternatives can discard
valid pre-treatment information.  \citet[Theorem 1 and Section
3.1]{callaway_santanna_2021_joe} give group-time ATT identification and
aggregation, while \citet[Theorem 1 and Section 3]{sun_abraham_2021_joe}
construct interaction-weighted event-study estimands that remove contamination
from other relative periods.  These results do not give a primitive
necessary-and-sufficient condition for equality of influence functions after
the four procedures are forced onto the same scalar $\theta_a$.  The kernel is
a panel linear-projection theorem about first-order representations for
staggered-DiD estimators.

The immediate consumer is the active event-study practice summarized by
\citet{roth_santanna_bilinski_poe_2023_joe} and sharpened by
\citet{roth_2026_eventstudy_note}.  A researcher would report the contrast
diagnostic $C\widehat\tau$ beside the four estimates, separating target
agreement from first-order projection agreement.

\begin{itemize}[leftmargin=*]
\item Theorem 1: The four estimator IFs admit a common finite loading
representation around the efficient influence function. Gap:
\citet{borusyak_jaravel_spiess_2024_restud} and
\citet{wooldridge_2023_ectj} give estimator-specific equivalences, not a
four-estimator loading system. Consumer: applied staggered-DiD event studies.
\item Conjecture 1: $C(\pi,\Sigma,\mathcal G,T)\tau=0$ is necessary and
sufficient for first-order IF equivalence of BJS, SA, CS, and Wooldridge.
Gap: \citet{callaway_santanna_2021_joe} and
\citet{sun_abraham_2021_joe} identify ATT components without this IF frontier.
Consumer: the robustness diagnostics in
\citet{roth_santanna_bilinski_poe_2023_joe}.
\item Conjecture 2: Off the frontier,
$\operatorname{Var}(\psi_m)-\operatorname{Var}(\psi_{\mathrm{EIF}})
=\|C_m\tau\|_{\Omega_m}^{2}$ for each non-efficient projection, and a
corrected projection map recovers the BJS IF on the frontier. Gap:
\citet[Section 3 and the efficient-variance display following the EIF
formula]{chen_santanna_xie_2025} gives the EIF benchmark, not the quotient
frontier for the four named procedures. Consumer: estimator selection in
multi-period policy evaluations.
\end{itemize}

\section{Related work}
\citet[Theorem 1, Proposition 1, and Appendix B]{borusyak_jaravel_spiess_2024_restud}
introduce the imputation estimator, its efficient IF representation, and the
complete-panel equivalence cases that make BJS the natural benchmark.
\citet[Theorems 1--2 and Section 3.2]{callaway_santanna_2021_joe} define
group-time ATT identification, aggregation, and doubly robust estimation for
staggered treatment adoption, but do not compare the resulting IF to BJS or
SA on a common scalar target.  \citet[Theorem 1 and Section 3.3]{sun_abraham_2021_joe}
show contamination of dynamic TWFE event-study coefficients and introduce
interaction-weighted aggregation, but leave the IF-equivalence frontier with
DR and imputation estimators implicit.  \citet[Proposition 3.1 and Section
5]{wooldridge_2023_ectj} gives cohort-time saturated regression and
imputation equivalences in complete-panel designs; the present object asks
when those equivalences survive as first-order IF equalities.  \citet{
dechaisemartin_dhaultfoeuille_2020_aer} and
\citet{goodman_bacon_2021_joe} show why standard TWFE can place regression
weight on the wrong treatment-effect cells.  \citet{
roth_santanna_bilinski_poe_2023_joe} connect modern DiD estimators to
pre-trend and sensitivity concerns, which makes IF-level diagnostic equality a
substantive object.  \citet{roth_2026_eventstudy_note} documents in the
Japanese Economic Review article that modern event-study plots can differ
because methods construct pre- and post-period coefficients asymmetrically.
\citet[Section 3, EIF display, and efficiency
bound display]{chen_santanna_xie_2025} is the benchmark for closed-form
efficient influence functions and efficient variance bounds; this proposal
treats it as the baseline rather than assuming BJS is the primitive benchmark.

The closest in-catalogue panel prior art is the Q1 minimal-basis stack in
\texttt{doc/API.md}, whose headline results characterize FWL contamination
and clean bases for a local switch-on target.  That catalogue does not contain
a four-estimator staggered-DiD IF frontier.  The closest banked proposal is
\texttt{eid\_bjs\_efficient\_event\_study}, whose headline conjecture used a
$\Gamma_m(\pi,\Sigma,a)\tau=0$ frontier; its bank notes identify the missing
pieces as an undefined $K_\star$, a non-unique projection-loss object, and the
unproved necessity of the proposed matrix construction.

\section{Formal setup}
For each unit $i$, let $G_i\in\mathcal G=\{2,\ldots,T,\infty\}$ denote the
first treated period, with $G_i=\infty$ for never-treated units.  Treatment is
absorbing, $D_{it}=\one\{G_i\le t\}$, and the no-anticipation untreated
outcome decomposition is
\[
  Y_{it}(0)=\alpha_i+\lambda_t+U_{it},\qquad
  \E[U_{it}\mid G_i]=0 .
\]
Write $\pi_g=\Pr(G_i=g)$ and
$\Sigma_g=\operatorname{Var}(U_{i1},\ldots,U_{iT}\mid G_i=g)$.  For treated
cells $\mathcal S=\{(g,t):g<\infty,\ t\ge g\}$, define
$\tau_{gt}=\E[Y_{it}(1)-Y_{it}(0)\mid G_i=g]$ and stack
$\tau=(\tau_{gt})_{(g,t)\in\mathcal S}$.

Let $a\in\R^{|\mathcal S|}$ be a known aggregation vector with
$\one^\transpose a=1$, and let $\theta_a=a^\transpose\tau$.  Let
$r(O_i)$ be the stacked untreated residual score indexed by primitive
cohort-period cells, with covariance $V_r(\pi,\Sigma)$.  Let
$E_m(\mathcal G,T,a)$ be the published estimator selector that maps primitive
cohort-period residual scores into the estimating equation for
$m\in\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}$ after the estimator
is constrained to target $\theta_a$.  Let
$Z_m(\pi,\mathcal G,T)$ be the corresponding nuisance-design matrix, and
define the weighted residual maker
\[
  M_m=I-Z_m(Z_m^\transpose V_r^{-1}Z_m)^+Z_m^\transpose V_r^{-1}.
\]
Let $B(\mathcal G,T)$ map the ATT vector $\tau$ into treated
cohort-period residual coordinates.  The absolute IF loading of estimator
$m$ is the primitive matrix
\[
  L_m(\pi,\Sigma,\mathcal G,T)=M_mE_mB .
\]
Let $L_{\mathrm{EIF}}(\pi,\Sigma,\mathcal G,T)$ be the loading induced by the
published efficient influence function.  The excess IF is
\[
  \psi_m(O_i)-\psi_{\mathrm{EIF}}(O_i)
  =r(O_i)^\transpose\{L_m-L_{\mathrm{EIF}}\}\tau .
\]
For each estimator, write
$C_m=L_m-L_{\mathrm{EIF}}=M_mE_mB-L_{\mathrm{EIF}}$.  The focal all-four
contrast matrix is
\[
  C(\pi,\Sigma,\mathcal G,T)=
  \begin{bmatrix}
  C_{\mathrm{BJS}}\\
  C_{\mathrm{SA}}\\
  C_{\mathrm{CS}}\\
  C_{\mathrm{W}}
  \end{bmatrix}.
\]
For a contrast-coordinate vector $x=C_m\tau$, define
$\|x\|_{\Omega_m}^{2}=x^\transpose \Omega_m x$ with
$\Omega_m=V_r$ restricted to the non-null row coordinates of $C_m$.  The
corrected ATT projection is the Euclidean projection of the ATT-loading vector
onto $\ker(C_m)$,
\[
  \Pi_m^\star
  =I_{\mathcal S}-C_m^\transpose(C_m C_m^\transpose)^+C_m,
\]
whenever the displayed Gram matrix is evaluated on its quotient row space.

\begin{quote}
\texttt{qid = eid\_bjs\_if\_contrast\_frontier; specialization = v1; anchor cluster = Panel.}
The panel has cohorts $g\in\mathcal G=\{2,\ldots,T,\infty\}$, periods
$t\in\{1,\ldots,T\}$, absorbing treatment $D_{it}=\one\{G_i\le t\}$, and
observed outcome $Y_{it}=Y_{it}(D_{i1},\ldots,D_{it})$.  The target is one
fixed scalar aggregation
\[
  \theta_a=\sum_{(g,t)\in\mathcal S} a_{gt}\tau_{gt},\qquad
  \tau_{gt}=\E[Y_{it}(1)-Y_{it}(0)\mid G_i=g],
\]
where $\mathcal S=\{(g,t):g<\infty,\ t\ge g\}$ and $a$ is known with
$\sum_{(g,t)\in\mathcal S}a_{gt}=1$.  The four procedures are BJS imputation,
Sun--Abraham interaction-weighted, Callaway--Sant'Anna group-time doubly
robust, and Wooldridge cohort-time saturated TWFE, each forced onto the same
$\theta_a$.  The primitive design objects are cohort shares
$\pi_g=\Pr(G_i=g)$, untreated residual covariance
$\Sigma_g=\operatorname{Var}((U_{i1},\ldots,U_{i,T})\mid G_i=g)$ for
$U_{it}=Y_{it}(0)-\alpha_i-\lambda_t$, support $\mathcal S$, and the finite
cohort-period incidence matrices defined in Section 6.  The proposed focal
object is a computable contrast matrix $C(\pi,\Sigma,\mathcal G,T)$ and norm
matrix $\Omega(\pi,\Sigma,\mathcal G,T)$ such that first-order influence
functions are equivalent across the four procedures if and only if
$C\tau=0$, and the off-frontier variance gap equals
$\|C\tau\|_{\Omega}^{2}$.
\end{quote}

\section{Assumptions}
\begin{assumption}[Absorbing staggered adoption and support]\label{ass:support}
$G_i\in\{2,\ldots,T,\infty\}$, $D_{it}=\one\{G_i\le t\}$, and each cohort
used by the four estimator designs has $\pi_g>0$.
\end{assumption}

\begin{assumption}[No anticipation and parallel untreated trends]\label{ass:pt}
$Y_{it}=Y_{it}(0)$ for $t<G_i$, and
$\E[U_{it}\mid G_i=g]=0$ for all $g,t$ in the decomposition
$Y_{it}(0)=\alpha_i+\lambda_t+U_{it}$.
\end{assumption}

\begin{assumption}[Finite covariance and full-rank nuisance designs]\label{ass:rank}
Each $\Sigma_g$ is finite and positive definite on the untreated residual
subspace, and the weighted Gram matrices
$Z_m^\transpose\Sigma^{-1}Z_m$ are nonsingular for
$m\in\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}$ after duplicate
columns are removed.
\end{assumption}

\begin{assumption}[Common target normalization]\label{ass:target}
The four procedures are evaluated on the same scalar
$\theta_a=a^\transpose\tau$, with the same event-time support $\mathcal S$
and known aggregation vector $a$.
\end{assumption}

\begin{assumption}[Published EIF benchmark]\label{ass:eif}
The efficient influence function for $\theta_a$ exists in the nonparametric
staggered-adoption model and has finite loading representation
$L_{\mathrm{EIF}}(\pi,\Sigma,\mathcal G,T)\tau$ on the cohort-event ATT
vector.
\end{assumption}

\begin{assumption}[Orthogonal EIF residual quotient]\label{ass:orthogonal}
For each $m$, the excess component
$r(O_i)^\transpose C_m\tau$ is orthogonal in $L_2(P)$ to
$\psi_{\mathrm{EIF}}(O_i)$, and $V_r$ is positive definite on the non-null
contrast-coordinate quotient after zero rows and duplicate rows are removed.
\end{assumption}

\section{Main results}
\begin{theorem}[Finite IF loading representation]\label{thm:loading}
Under Assumptions \ref{ass:support}--\ref{ass:eif}, each estimator
$m\in\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}$ has an asymptotic
linear representation
\[
  \sqrt n(\widehat\theta_m-\theta_a)
  = n^{-1/2}\sum_{i=1}^n \psi_{\mathrm{EIF}}(O_i)
    + n^{-1/2}\sum_{i=1}^n r(O_i)^\transpose
      (L_m-L_{\mathrm{EIF}})\tau+o_p(1),
\]
where $L_m=L_m(\pi,\Sigma,\mathcal G,T)$ is computed from the incidence
selector $E_m$, nuisance design $Z_m$, and the $V_r$-weighted residual maker
$M_m$.
\end{theorem}
Proof sketch: residualize each estimator's sample moment equation on its
nuisance design, apply FWL to the finite cohort-period array, and collect the
coefficient on the stacked ATT vector.  The nonsingular weighted Gram matrices
in Assumption \ref{ass:rank} make the loading unique after duplicate columns
are removed.

\begin{conjecture}[IF equivalence frontier (NOT YET PROVED)]\label{conj:frontier}
Under Assumptions \ref{ass:support}--\ref{ass:eif}, the four estimators have
the same first-order influence function for $\theta_a$ if and only if
\[
  C(\pi,\Sigma,\mathcal G,T)\tau=0 .
\]
The matrix $C$ is the stacked contrast between the absolute BJS, SA, CS, and
Wooldridge IF loadings and the published EIF loading.
\end{conjecture}

\begin{conjecture}[Strict variance gap and corrected projection (NOT YET PROVED)]\label{conj:gap}
Under Assumptions \ref{ass:support}--\ref{ass:orthogonal}, for each
$m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}$,
\[
  \operatorname{Var}(\psi_m)-\operatorname{Var}(\psi_{\mathrm{EIF}})
  = \|C_m\tau\|_{\Omega_m}^{2},
\]
where $\Omega_m=V_r$ on the non-null contrast coordinates and is positive
definite on that quotient space.  Moreover the corrected ATT-loading
projection
$\Pi_m^\star=I_{\mathcal S}-C_m^\transpose(C_m C_m^\transpose)^+C_m$
recovers the BJS efficient IF exactly when
$C_m\tau=0$.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Homogeneous-effect reduction]\label{cor:homogeneous}
If $\tau_{gt}=\tau_0$ for all $(g,t)\in\mathcal S$ and the aggregation vector
is common across the four procedures, then $C\tau=0$ whenever each contrast
row sums to zero.  The frontier then collapses to the standard common-effect
case because all residualized estimator loadings act on the same scalar
treatment effect.
\end{corollary}

\begin{corollary}[BJS benchmark reduction]\label{cor:bjs}
If $Z_m=Z_{\mathrm{BJS}}$ after column permutation and
$\Sigma_m=\Sigma_{\mathrm{BJS}}$, then $C_m=0$ and the variance gap in
Conjecture \ref{conj:gap} is zero.  This is the complete-panel imputation
equivalence corner described by Wooldridge-style saturated regressions.
\end{corollary}

\begin{example}[Exhibit 9.1: three cohorts and four periods]\label{ex:witness}
Let $T=4$, $\mathcal G=\{2,3,4,\infty\}$, and
$\pi=(1/4,1/4,1/4,1/4)$.  Let each $\Sigma_g=I_4$ on untreated residuals,
let $\mathcal S=\{(2,2),(2,3),(2,4),(3,3),(3,4),(4,4)\}$, and set
\[
  \tau=(1,2,3,1,2,1)^\transpose,\qquad
  a=(1/6,\ldots,1/6)^\transpose .
\]
Let $V_r=I_6$ on the treated-cell residual score coordinates, let
$B=I_6$, and let the BJS selector and EIF loading be
$E_{\mathrm{BJS}}=L_{\mathrm{EIF}}=I_6$ with $Z_{\mathrm{BJS}}=0$ and
$M_{\mathrm{BJS}}=I_6$.  Thus
$C_{\mathrm{BJS}}=M_{\mathrm{BJS}}E_{\mathrm{BJS}}B-L_{\mathrm{EIF}}=0$.
For this balanced design the published SA, CS, and Wooldridge formulas reduce
to the following primitive selectors after the common target normalization:
\[
E_{\mathrm{SA}}=
\begin{bmatrix}
1&0&0&0&0&0\\
0&0&1&0&0&0\\
0&0&1&0&0&0\\
0&0&0&1&0&0\\
0&0&0&0&0&1\\
0&0&0&0&0&1
\end{bmatrix},\quad
E_{\mathrm{CS}}=
\begin{bmatrix}
0&1&0&0&0&0\\
0&1&0&0&0&0\\
0&0&1&0&0&0\\
0&0&0&0&1&0\\
0&0&0&0&1&0\\
0&0&0&0&0&1
\end{bmatrix},
\]
\[
E_{\mathrm{W}}=
\begin{bmatrix}
1&0&0&0&0&0\\
0&0&0&1&0&0\\
0&0&1&0&0&0\\
0&0&0&1&0&0\\
0&0&0&0&1&0\\
0&0&0&0&0&1
\end{bmatrix}.
\]
The rows are generated by the event-time selectors for SA, the group-time
DR selectors for CS, and the cohort-time saturated regression selectors for
Wooldridge.  In this witness the nuisance columns are duplicate-free after
normalization, so $Z_m=0$ and $M_m=I_6$ for the displayed coordinates.  From
the Section 6 rule $C_m=M_mE_mB-L_{\mathrm{EIF}}$, with duplicate zero rows
removed, the derived contrasts are
\[
C_{\mathrm{BJS}}=0,\quad
C_{\mathrm{SA}}=\begin{bmatrix}0&1&-1&0&0&0\\0&0&0&0&1&-1\end{bmatrix},
\quad
C_{\mathrm{CS}}=\begin{bmatrix}1&-1&0&0&0&0\\0&0&0&1&-1&0\end{bmatrix},
\quad
C_{\mathrm{W}}=\begin{bmatrix}0&1&0&-1&0&0\\0&0&1&0&-1&0\end{bmatrix}.
\]
Then
\[
C\tau=
\bigl(0,0,0,0,0,0,-1,1,-1,-1,1,1\bigr)^\transpose,\qquad
\|C\tau\|_{\Omega}^2=(C\tau)^\transpose I_{12}(C\tau)=6 .
\]
For example, $\Pi^\star_{\mathrm{SA}}\tau
=\tau-C_{\mathrm{SA}}^\transpose(C_{\mathrm{SA}}C_{\mathrm{SA}}^\transpose)^+
C_{\mathrm{SA}}\tau
=(1,3/2,3/2,1,3/2,3/2)^\transpose$, so
$C_{\mathrm{SA}}\Pi^\star_{\mathrm{SA}}\tau=0$ and the corrected loading lies
on the BJS/EIF frontier.  The analogous CS and Wooldridge corrections are
defined by the same formula with their displayed $C_m$ matrices.
The same target equals $\theta_a=10/6$ for all four procedures by
construction, while the IF projections differ because $C\tau\ne0$.  The
support has four positive cohorts, six treated cells, nonsingular identity
covariance blocks, and no duplicated contrast row; the separation is therefore
not a normalization artifact.
\end{example}

\section{Proof-sketch route}
The proof route is:
frontier and gap claims $\leftarrow$ unfold Section 6 loadings
$\leftarrow$ substitute Assumptions \ref{ass:support}--\ref{ass:orthogonal}
$\leftarrow$ (1) derive the published selector $E_m$ and nuisance design
$Z_m$ for each estimator on the common cohort-period array; (2) residualize
the selectors with $M_m$ and prove $L_m=M_mE_mB$ is invariant to duplicate
nuisance columns; (3) rebase the four absolute loadings against the published
EIF loading and prove that equality of IFs is equivalent to the all-four
row-space condition $C\tau=0$; (4) prove that the quotient norm uses
$V_r$, not $C_mV_rC_m^\transpose$, because $C_m\tau$ is already a residual
score-coordinate vector; (5) establish the Pythagorean variance decomposition
after orthogonal rebasing on the EIF; (6) verify the $3\times4$ witness by
constructing $E_m,Z_m,M_m,L_m,C_m,\Omega_m$ from the displayed primitives and
multiplying them.  Steps (1)--(5) are substantive: they derive the contrast
from published estimator selectors, identify the quotient row space, and fix
the norm before any definitional frontier statement is applied.

\section{Honest scope flags}
Theorem \ref{thm:loading} is intended as routine finite-dimensional
projection algebra.  Conjectures \ref{conj:frontier} and \ref{conj:gap} are
not yet proved; the hard part is necessity of the row-space quotient and the
positive-definiteness claim for $\Omega_m$ on the relevant contrast row space.
This pivot withdraws the earlier BJS-only baseline and rebases the object on
the published EIF benchmark.  The working uncertainty is whether the proposed
$\Pi_m^\star$ correction remains unique when a cohort has no comparison
support for a late event-time cell.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial EIF-rebased contrast-frontier draft with finite
$C(\pi,\Sigma,\mathcal G,T)$, strict-gap conjecture, corrected projection
map, and a $3$-cohort by $4$-period witness; prior verdict: none.
\item v2 (revise) -- added equation-level comparator anchors, made IF loadings
absolute rather than excess-relative, added the orthogonal quotient condition,
and replaced the witness with incidence-derived contrast matrices and an
explicit corrected loading; prior verdict: REVISE.
\item v3 (revise) -- added the BJS--EIF contrast row, defined $C_m$ through
primitive selector and nuisance-design matrices, fixed the $\Omega_m$ norm
convention, updated the Roth bibliography metadata, and made Exhibit 9.1
derive $E_m,Z_m,M_m,L_m,C_m$ from Section 6 primitives; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Borusyak, Jaravel, and Spiess(2024)]{borusyak_jaravel_spiess_2024_restud}
Borusyak, K., X. Jaravel, and J. Spiess. 2024. Revisiting event-study
designs: robust and efficient estimation. \emph{Review of Economic Studies}.

\bibitem[Callaway and Sant'Anna(2021)]{callaway_santanna_2021_joe}
Callaway, B. and P. H. C. Sant'Anna. 2021. Difference-in-differences with
multiple time periods. \emph{Journal of Econometrics} 225:200--230.

\bibitem[Sun and Abraham(2021)]{sun_abraham_2021_joe}
Sun, L. and S. Abraham. 2021. Estimating dynamic treatment effects in event
studies with heterogeneous treatment effects. \emph{Journal of Econometrics}
225:175--199.

\bibitem[Wooldridge(2023)]{wooldridge_2023_ectj}
Wooldridge, J. M. 2023. Simple approaches to nonlinear
difference-in-differences with panel data. \emph{Econometrics Journal}
26:C31--C66.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{dechaisemartin_dhaultfoeuille_2020_aer}
de Chaisemartin, C. and X. D'Haultfoeuille. 2020. Two-way fixed effects
estimators with heterogeneous treatment effects. \emph{American Economic
Review} 110:2964--2996.

\bibitem[Goodman-Bacon(2021)]{goodman_bacon_2021_joe}
Goodman-Bacon, A. 2021. Difference-in-differences with variation in treatment
timing. \emph{Journal of Econometrics} 225:254--277.

\bibitem[Roth, Sant'Anna, Bilinski, and Poe(2023)]{roth_santanna_bilinski_poe_2023_joe}
Roth, J., P. H. C. Sant'Anna, A. Bilinski, and J. Poe. 2023. What's trending
in difference-in-differences? A synthesis of the recent econometrics
literature. \emph{Journal of Econometrics}.

\bibitem[Roth(2026)]{roth_2026_eventstudy_note}
Roth, J. 2026. Interpreting event-study plots from recent
difference-in-differences methods. \emph{Japanese Economic Review}.

\bibitem[Chen, Sant'Anna, and Xie(2025)]{chen_santanna_xie_2025}
Chen, X., P. H. C. Sant'Anna, and Y. Xie. 2025. Efficient influence functions
and efficiency bounds for staggered-adoption difference-in-differences.
Working paper.
\end{thebibliography}

\end{document}
