\section{Main Results}

The setup in \cref{obj:def:rollout-law-class} reduces the identification problem to a polynomial endpoint problem. The first result records the corresponding identity for the target contrast: under the static rollout interpretation and the degree-\(\beta\) rollout mean restriction, the estimand is the sum of the nonconstant coefficients of the rollout mean curve.

\begin{lemmav}{prop:rollout-polynomial-identity}[Rollout Polynomial Identity]
For any finite assignment space $\Omega$, population size $n$, number of rollout intervals $k$, polynomial order $\beta$, contemporaneous assignment vectors $Z_j$, potential outcomes $Y_i(Z_j)$, round means $\bar Y_j$, rollout mean curve $m_P$, and polynomial coefficients $(a_{P,\ell})_{\ell\ge 0}$, suppose \cref{obj:ass:static-rollout-consistency} and \cref{obj:ass:beta-order-polynomial} hold. Then
\[
m_P(1)-m_P(0)=\sum_{\ell=1}^{\beta} a_{P,\ell}.
\]
Thus the endpoint treatment contrast satisfies
\[
\tau_P=m_P(1)-m_P(0)=\sum_{\ell=1}^{\beta} a_{P,\ell}.
\]
\end{lemmav}

\cref{obj:prop:rollout-polynomial-identity} identifies the polynomial target: any design-unbiased estimator of the nonconstant polynomial coefficients is also unbiased for the endpoint contrast. The subsequent results add sampling variability and optimize the placement of rollout measurements.

The next theorem turns this identity into a design criterion under the variance envelope in \cref{obj:ass:round-mean-variance-envelope}. The point is that, once cross-round covariances are left unrestricted except for positive semidefiniteness and the diagonal envelope, the worst-case variance of a linear unbiased estimator is governed by the squared \(\ell^1\) norm of its weights.

\begin{theoremv}{thm:tv-envelope-design}[TV Envelope Design Bound]
Let \(n,k,\beta\) be integers, let \(q\in\mathbb R\), and let \(\sigma_0^2\in\mathbb R\). Fix a finite assignment space \(\Omega\), a finite design \(\pi\) on \(\Omega\), rollout assignment vectors \(Z_0,\ldots,Z_k\), round means \(\bar Y_0,\ldots,\bar Y_k\), a rollout mean curve \(m_P\), polynomial coefficients \(a_{P,\ell}\), and a schedule \(p=(p_0,\ldots,p_k)\). Suppose that
\begin{itemize}
\item \textbf{(Order.)} \(1\le \beta\le k\).
\item \textbf{(Envelope scale.)} \(\sigma_0^2\ge 0\).
\item \textbf{(Schedule.)} \(p\in S_{k,q}\), in the sense of \cref{obj:def:budgeted-schedule-class}.
\item \textbf{(Law class.)} The design, rollout variables, round means, mean curve, coefficients, envelope scale, and schedule satisfy the rollout law-class restrictions \(\mathcal P_\beta\) in \cref{obj:def:rollout-law-class}.
\end{itemize}
Then \(W_\beta(p)\), as defined in \cref{obj:def:unbiased-weight-set}, is nonempty. Moreover, for every \(w\in W_\beta(p)\),
\[
\mathbb E_\pi\!\left[\sum_{j=0}^k w_j\bar Y_j\right]=m_P(1)-m_P(0)
\]
and
\[
\operatorname{Var}_\pi\!\left(\sum_{j=0}^k w_j\bar Y_j\right)
\le
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2 .
\]
For every such \(w\), there also exists a positive semidefinite \((k+1)\times(k+1)\) matrix \(\Gamma\) such that
\[
\Gamma_{jj}\le \frac{\sigma_0^2}{n}\quad\text{for every }j=0,\ldots,k,
\]
and
\[
\sum_{i=0}^k\sum_{j=0}^k w_i\Gamma_{ij}w_j
=
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2 .
\]
Consequently, with \(A_\beta(\cdot)\) and \(M_{\beta,k,q}\) as in \cref{obj:def:amplification-criterion},
\[
\inf\left\{
v:\ \exists w\in W_\beta(p)\text{ with }
v=\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2
\right\}
=
\frac{\sigma_0^2}{n}A_\beta(p),
\]
and
\[
\inf\left\{
v:\ \exists p'\in S_{k,q}\text{ with }
v=\frac{\sigma_0^2}{n}A_\beta(p')
\right\}
=
\frac{\sigma_0^2}{n}M_{\beta,k,q}.
\]
Finally, if \(p^\star\in S_{k,q}\) satisfies
\[
A_\beta(p^\star)=M_{\beta,k,q},
\]
then for every \(p'\in S_{k,q}\),
\[
\frac{\sigma_0^2}{n}A_\beta(p^\star)
\le
\frac{\sigma_0^2}{n}A_\beta(p').
\]
\end{theoremv}

\cref{obj:thm:tv-envelope-design} separates three roles that are otherwise easy to conflate. The law class determines which linear combinations are unbiased; the envelope scale contributes the common factor \(\sigma_0^2/n\); and the schedule affects risk only through the feasible set of polynomial-exact weights. Thus the schedule problem is the minimization of \(A_\beta(p)\) over \(S_{k,q}\), a finite-dimensional optimal-design problem in the tradition of polynomial extrapolation and minimax design \citep{smith1918,kiefer1959,kiefer1974,pukelsheim1993,karlin1966}.

A simple benchmark uses the minimal \(\beta+1\) equally spaced measurements on \([0,q]\). It establishes feasibility of unbiased extrapolation and displays the large amplification cost of naive spacing when \(q\) is small.

\begin{lemmav}{prop:equal-spacing-benchmark}[Equal-Spacing Amplification Bound]
For every integer $\beta\ge 1$ and every $q\in(0,1]$, let
\[
p^{\mathrm{eq}}(\beta,q)_j=\frac{qj}{\beta},
\qquad j=0,\ldots,\beta .
\]
Then $p^{\mathrm{eq}}(\beta,q)_j\in[0,1]$ for every $j=0,\ldots,\beta$, and, with $A_\beta$ as in \cref{obj:def:amplification-criterion},
\[
A_\beta\!\left(p^{\mathrm{eq}}(\beta,q)\right)
\le
9\left(\frac{\beta}{q}\right)^{2\beta}.
\]
\end{lemmav}

\cref{obj:prop:equal-spacing-benchmark} provides a universal feasibility scale for equal spacing. The base of its exponential upper bound grows with \(\beta/q\), reflecting the instability of extrapolating from \([0,q]\) to \(1\) using evenly spaced nodes; the Chebyshev result below supplies the minimax comparison.

The full-budget boundary is qualitatively different. When \(q=1\), the observed target endpoint permits direct estimation.

\begin{lemmav}{prop:no-extrapolation-boundary}[Full-Budget Endpoint Rule]
For every polynomial order \(\beta\ge 1\), take \(k=\beta\) and use the equal-spacing schedule \(p^{\mathrm{eq}}(\beta,1)\). Define the weight vector \(w=(w_0,\ldots,w_\beta)\) by
\[
w_0=-1,\qquad w_\beta=1,\qquad w_j=0 \quad\text{for } 1\le j\le \beta-1 .
\]
Then \(w\in W_\beta(p^{\mathrm{eq}}(\beta,1))\), where \(W_\beta(\cdot)\) is the unbiased weight set in \cref{obj:def:unbiased-weight-set}. Consequently, for the amplification criterion in \cref{obj:def:amplification-criterion},
\[
A_\beta\!\left(p^{\mathrm{eq}}(\beta,1)\right)\le 4 .
\]
\end{lemmav}

\cref{obj:prop:no-extrapolation-boundary} explains why the low-budget assumption is imposed separately in \cref{obj:ass:low-budget-cap}. At full rollout, the endpoint contrast can be estimated by the difference between the final and baseline round means, with amplification bounded independently of \(\beta\). The exponential behavior in the next theorem is therefore specific to endpoint extrapolation.

Chebyshev-Lobatto placement is the schedule that controls this extrapolation cost. The theorem below compares every admissible schedule to the shifted Chebyshev-Lobatto schedule from \cref{obj:def:chebyshev-schedule}, uniformly over budgets bounded away from one. The oversampling ratio \leanref{sym:c}{$c$} permits more than the minimum \(\beta+1\) measurements, which is the regime in which the discrete Lobatto grid norms the relevant continuous polynomial problem.

\begin{theoremv}{thm:chebyshev-minimax}[Chebyshev Minimax Amplification]
Fix a budget cap \(q_{\max}\in(0,1)\). There exists a constant
\(C_-(q_{\max})>0\) such that, for every oversampling ratio \(c>1\), there
exists a constant \(C_+(c,q_{\max})>0\) with the following property.

For every pair of integers \(\beta,k\), every rollout budget \(q\), and every
schedule \(p\), suppose that
\begin{itemize}
\item \textbf{(Order and oversampling.)} \(\beta\ge 1\) and \(k\ge c\beta\).
\item \textbf{(Low-budget regime.)} \(q>0\) and the low-budget cap condition of
\cref{obj:ass:low-budget-cap} holds for \((q,q_{\max})\).
\item \textbf{(Admissible schedule.)} When \(p\) is used below, \(p\in S_{k,q}\)
as in \cref{obj:def:budgeted-schedule-class}.
\end{itemize}
Then, with \(A_\beta(\cdot)\) and \(M_{\beta,k,q}\) as in
\cref{obj:def:amplification-criterion} and
\(p^{\mathrm{Ch}}(k,q)\) as in \cref{obj:def:chebyshev-schedule},
\[
A_\beta(p)
\ge
C_-(q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta},
\]
and
\[
A_\beta\!\left(p^{\mathrm{Ch}}(k,q)\right)
\le
C_+(c,q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}.
\]
Moreover, the minimax amplification satisfies the matching two-sided bound
\[
C_-(q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}
\le
M_{\beta,k,q}
\le
C_+(c,q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}.
\]
\end{theoremv}

\cref{obj:thm:chebyshev-minimax} gives the main schedule result. For fixed \(q\le q_{\max}<1\) and \(k\ge c\beta\), every admissible schedule incurs the displayed Chebyshev amplification exponent, while the shifted Chebyshev-Lobatto schedule attains that rate up to constants depending only on \(q_{\max}\) and \(c\). In economic terms, the theorem says that the experimenter should spend rollout measurements where polynomial extrapolation is hardest: near the untreated baseline and near the budget endpoint. The low-budget cost remains exponential in the polynomial order, but Chebyshev-Lobatto placement controls the exponent that the total-variation variance envelope makes unavoidable.
