\section{Discussion and Extensions}

The envelope result in \cref{obj:thm:tv-envelope-design} is deliberately conservative about the covariance structure of a nested rollout. It permits any positive semidefinite covariance matrix whose diagonal entries satisfy the round-mean variance envelope, and it therefore turns the schedule problem into a polynomial amplification problem. The exact finite-population problem in \cref{obj:def:exact-nested-risk} is narrower: the covariance matrix must arise from the same monotone Bernoulli rollout law that generates the observed round means. That extra structure may matter for finite-sample optimality, even though the envelope criterion already gives a sharp and interpretable design rule.

\subsection{Exact-covariance scope and limitations}

The distinction is important for the status of Chebyshev-Lobatto placement. \Cref{obj:thm:chebyshev-minimax} proves minimax optimality for the total-variation envelope criterion \(A_\beta(p)\) and \(M_{\beta,k,q}\). Exact optimality with \(\Gamma_P(p)\) left inside the minimax risk is the stronger covariance-specific question recorded separately below.

\begin{remarkv}{oeq:exact-nested-minimax}[Exact nested optimality]
Fix a finite assignment space \(\Omega\) with rollout randomization \(\pi\), population size \(n\), and variance-envelope scale \(\sigma_0^2\). Fix a budget cap \(q_{\max}\) with \(0<q_{\max}<1\), let \(c>1\), let \(\beta\ge 1\), set \(k=\lceil c\beta\rceil\), and take \(q\) with \(0<q\le q_{\max}\). Under these hypotheses the shifted Chebyshev-Lobatto schedule \(p^{\mathrm{Ch}}(k,q)\) is admissible, so that
\[
p^{\mathrm{Ch}}(k,q)\in S_{k,q}.
\]
For the exact finite-population nested-rollout minimax problem
\[
R_{\mathrm{exact}}(\beta,k,q)
=
\inf_{p\in S_{k,q}}
\inf_{w\in W_\beta(p)}
\sup_{P\in\mathcal P_\beta}
w^\prime \Gamma_P(p) w,
\]
where \(\Gamma_P(p)\) is the true design covariance matrix of the monotone Bernoulli rollout and \(\mathcal P_\beta\) includes the static-rollout, \(\beta\)-polynomial, variance-envelope, and mean-curve-pinning restrictions, the open question is whether the fixed Chebyshev-Lobatto exact risk attains the nested infimum:
\[
\inf_{w\in W_\beta(p^{\mathrm{Ch}}(k,q))}
\sup_{P\in\mathcal P_\beta}
w^\prime \Gamma_P(p^{\mathrm{Ch}}(k,q)) w
=
R_{\mathrm{exact}}(\beta,k,q).
\]
This statement is only the exact-optimality question for \(p^{\mathrm{Ch}}(k,q)\); it does not assert the separate rate-feasibility bound.
\end{remarkv}

\cref{obj:oeq:exact-nested-minimax} keeps exact optimality separate from rate feasibility. The equality displayed there characterizes the optimizer of the true nested covariance problem and is stronger than achieving the same exponential order as the envelope benchmark. Establishing such an equality calls for the covariance restrictions implied by monotone Bernoulli rollout designs in addition to the diagonal variance envelope. Related finite-population interference designs suggest that these restrictions can be substantive, especially when exposure mappings, clustered assignments, or dependency neighborhoods impose additional structure on covariances \citep{cortezrodriguez2024,eichhorn2024,jiang2023,cai2023}.

The results below state the rate implication delivered by the one-sided envelope comparison. The exact nested risk is bounded above by the envelope amplification criterion at every admissible schedule. Therefore any schedule that is good for the envelope problem is automatically feasible for the exact finite-population risk.

\begin{lemmav}{lem:exact-risk-envelope-upper}[Exact Risk Envelope Bound]
Let $\Omega$ be a finite assignment space equipped with rollout randomization $\pi$. For any population size $n$, any integers $k$ and $\beta$, any real numbers $q$ and $\sigma_0^2$, and any schedule $p=(p_0,\ldots,p_k)$, suppose that
\begin{itemize}
\item \textbf{(Order.)} $\beta\ge 1$.
\item \textbf{(Number of rollout intervals.)} $k\ge \beta$.
\item \textbf{(Budget.)} $0<q\le 1$.
\item \textbf{(Variance scale.)} $\sigma_0^2\ge 0$.
\item \textbf{(Budgeted schedule.)} $p\in S_{k,q}$, as in \cref{obj:def:budgeted-schedule-class}.
\end{itemize}
Then
\[
\inf_{w\in W_\beta(p)}
\sup_{P\in\mathcal P_\beta}
w^\prime \Gamma_P(p) w
\le
\frac{\sigma_0^2}{n}\,A_\beta(p),
\]
with $W_\beta(p)$ as in \cref{obj:def:unbiased-weight-set}, $\mathcal P_\beta$ as in \cref{obj:def:rollout-law-class}, and $A_\beta(p)$ as in \cref{obj:def:amplification-criterion}. Consequently,
\[
R_{\mathrm{exact}}(\beta,k,q)
\le
\frac{\sigma_0^2}{n}\,M_{\beta,k,q},
\]
where $R_{\mathrm{exact}}(\beta,k,q)$ is as in \cref{obj:def:exact-nested-risk} and $M_{\beta,k,q}$ is as in \cref{obj:def:amplification-criterion}.
\end{lemmav}

\cref{obj:lem:exact-risk-envelope-upper} is a one-sided comparison. It places the exact covariance minimax risk below the envelope risk because the envelope allows a larger class of covariance matrices than those generated by the rollout law. A matching lower bound and characterization of the exact-risk minimizing schedule constitute the remaining exact-covariance problem.

Combining this comparison with the Chebyshev upper bound gives the finite-population feasibility statement relevant for low-budget rollout design. With \(k=\lceil c\beta\rceil\), the shifted Chebyshev-Lobatto schedule attains the same exponential rate for the exact risk upper bound as it does for the envelope criterion.

\begin{lemmav}{lem:exact-chebyshev-rate-feasible}[Feasible Chebyshev Rate]
Fix an oversampling constant \(c\) and a budget cap \(q_{\max}\) such that \(c>1\) and \(0<q_{\max}<1\). Then there exists a constant \(C_+(c,q_{\max})>0\) such that, for every population size \(n\), polynomial order \(\beta\), number of rollout intervals \(k\), finite assignment space \(\Omega\), finite design \(\pi\) on \(\Omega\), rollout budget \(q\), and variance-envelope scale \(\sigma_0^2\), the following conditions imply the stated bound:
\begin{itemize}
\item \textbf{(Order.)} \(\beta\ge 1\).
\item \textbf{(Budget.)} \(q>0\) and \(q\) satisfies the low-budget cap with \(q_{\max}\) in \cref{obj:ass:low-budget-cap}.
\item \textbf{(Variance scale.)} \(\sigma_0^2\ge 0\).
\item \textbf{(Chebyshev size.)} \(k=\lceil c\beta\rceil\).
\item \textbf{(Schedule.)} \(p=p^{\mathrm{Ch}}(k,q)\) is the shifted Chebyshev-Lobatto schedule of \cref{obj:def:chebyshev-schedule}.
\end{itemize}
Under these conditions,
\[
\inf_{w\in W_\beta(p^{\mathrm{Ch}}(k,q))}
\sup_{P\in\mathcal P_\beta}
\operatorname{Var}_\pi\!\left(\sum_{j=0}^k w_j\bar Y_j\right)
\le
\frac{\sigma_0^2}{n}\,
C_+(c,q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta},
\]
where \(W_\beta(p^{\mathrm{Ch}}(k,q))\) is the unbiased weight set of \cref{obj:def:unbiased-weight-set}, and the supremum ranges over rollout laws \(P\in\mathcal P_\beta\) satisfying \cref{obj:def:rollout-law-class} at the schedule \(p^{\mathrm{Ch}}(k,q)\) with variance-envelope scale \(\sigma_0^2\).
\end{lemmav}

\cref{obj:lem:exact-chebyshev-rate-feasible} gives a practical interpretation of the main theorem for the original rollout experiment. Independently of exact nested optimality, the Chebyshev-Lobatto schedule delivers an unbiased linear estimator whose worst-case exact variance is bounded by the displayed low-budget exponential rate. Thus the envelope solution provides a feasible design with controlled finite-population risk under the stated law class.

\subsection{Future work}

Several extensions are natural. Clustered rollouts would replace unit-level monotone Bernoulli assignment with group-level assignment and would require tracking how cluster size and within-cluster exposure affect the round-mean covariance matrix. Mixed designs that combine rollout fractions with saturation, encouragement, or exposure-based randomization would add further design variables beyond the treated-fraction schedule, connecting the present extrapolation problem to recent work on clustered and network experiments \citep{roth2021,chen2025,fan2025,bhadra2025,schroder2026}. The Chebyshev argument suggests that endpoint placement should remain central whenever the estimand extrapolates beyond the observed rollout range, with a design-specific minimax object for each extension.
