\section{Appendix: Proofs and Verification}

This appendix collects the auxiliary statements that support the envelope design result and the low-budget Chebyshev rate. The first part translates the rollout-weight problem into a real-polynomial optimal-recovery problem; the second part records the Chebyshev approximation inequalities; the final part returns these inequalities to the admissible rollout schedules and to the variance envelope. The appendix states the mathematical ingredients under the modeling assumptions introduced in the main text.

The bridge from rollout weights to approximation is the duality between minimum \(\ell^1\) norm weights and bounded polynomial extrapolation. In the notation of \cref{obj:def:unbiased-weight-set}, the moment equations make each admissible weight vector a linear functional on degree-\(\beta\) polynomials. The dual norm of this functional is exactly the largest endpoint contrast among polynomials bounded at the chosen schedule nodes.

\begin{lemmav}{lem:amplification-dual-norm}[Dual Norm Amplification]
Let \(\beta,k\in\mathbb N\) and let \(p=(p_0,\ldots,p_k)\) be a real-valued schedule whose nodes are distinct. Suppose that the unbiased weight set \(W_\beta(p)\) in \cref{obj:def:unbiased-weight-set} is nonempty. Then
\[
\inf_{w\in W_\beta(p)} \sum_{j=0}^k |w_j|
=
\sup\left\{
|r(1)-r(0)|:
r\in\mathbb R[x],\ \deg(r)\le \beta,\ \max_{0\le j\le k}|r(p_j)|\le 1
\right\}.
\]
Consequently, for the amplification criterion \(A_\beta(p)\) in \cref{obj:def:amplification-criterion},
\[
A_\beta(p)
=
\left(
\sup\left\{
|r(1)-r(0)|:
r\in\mathbb R[x],\ \deg(r)\le \beta,\ \max_{0\le j\le k}|r(p_j)|\le 1
\right\}
\right)^2 .
\]
\end{lemmav}

\cref{obj:lem:amplification-dual-norm} is the point at which the econometric design problem becomes the \leanref{S-2}{real polynomial optimal-recovery problem}. The schedule affects the right-hand side only through the locations at which the polynomial is constrained. Hence minimax placement of rollout fractions is equivalent, under the envelope criterion, to choosing nodes that make bounded interpolation on \([0,q]\) as stable as possible for the endpoint contrast \(r(1)-r(0)\).

The approximation bounds used for that comparison are standard Chebyshev facts adapted to the extrapolation geometry. The first is the exterior extremal property: among degree-\(\beta\) polynomials bounded by one on \([-1,1]\), the Chebyshev polynomial controls growth outside the interval \citep{karlin1966,pukelsheim1993}.

\begin{lemmav}{lem:chebyshev-exterior-extremal}[Exterior Chebyshev Extremal Bound]
Let $\beta$ be a positive integer. For every real polynomial $P$ and every exterior point $x_0$, suppose that
\begin{itemize}
\item \textbf{(Degree bound.)} $\deg(P)\le \beta$.
\item \textbf{(Unit interval bound.)} For every $x\in[-1,1]$, $|P(x)|\le 1$.
\item \textbf{(Exterior point.)} $x_0>1$.
\end{itemize}
Then
\[
|P(x_0)|\le T_\beta(x_0),
\]
where $T_\beta$ is the Chebyshev polynomial of the first kind of degree $\beta$.
\end{lemmav}

For the rollout application, the polynomial is controlled at the finite set of measurement nodes. Oversampled Chebyshev-Lobatto grids pass from this nodewise control to uniform control on the interval. The next statement records the required discrete norming step, conditional on the Ehlich--Zeller mesh inequality.

\begin{lemmav}{lem:oversampled-chebyshev-lobatto-norming}[Oversampled Lobatto Norming]
Suppose the Ehlich--Zeller Chebyshev--Lobatto mesh inequality holds: for every pair of nonnegative integers $\beta,k$ and every real polynomial $R$ with $\deg(R)\le \beta$ and $\beta<k$,
\[
 |R(x)|
 \le
 \frac{1}{\cos(\pi\beta/(2k))}
 \max_{0\le j\le k}\left|R\!\left(-\cos\!\left(\frac{\pi j}{k}\right)\right)\right|
\]
for every $x\in[-1,1]$.  Then, for every real oversampling ratio $c$ with $c>1$, there exists a real constant $K(c)>0$ such that the following holds.  For every pair of nonnegative integers $\beta,k$ and every real polynomial $R$ satisfying
\begin{itemize}
\item \textbf{(Positive order.)} $\beta\ge 1$,
\item \textbf{(Oversampling.)} $k\ge c\beta$,
\item \textbf{(Degree bound.)} $\deg(R)\le \beta$,
\end{itemize}
one has, for every $x\in[-1,1]$,
\[
 |R(x)|
 \le
 K(c)
 \max_{0\le j\le k}\left|R\!\left(-\cos\!\left(\frac{\pi j}{k}\right)\right)\right|.
\]
\end{lemmav}

\cref{obj:lem:oversampled-chebyshev-lobatto-norming} explains why the main theorem imposes \(k\ge c\beta\) with \(c>1\). Oversampling prevents a degree-\(\beta\) polynomial from taking large values between adjacent Lobatto nodes while remaining small at the nodes. The constant \(K(c)\) is allowed to depend on the oversampling ratio, but not on \(\beta\), \(k\), or the rollout budget.

The affine map from \([0,q]\) to \([-1,1]\) sends the target endpoint \(u=1\) to the exterior point \(x_q=2/q-1\). The corresponding Chebyshev multiplier \(\lambda(q)=x_q+\sqrt{x_q^2-1}\) gives the low-budget exponential base. Uniformity over \(q\le q_{\max}<1\) is recorded next.

\begin{lemmav}{lem:continuous-chebyshev-endpoint-bound}[Continuous Chebyshev Endpoint Bound]
Fix \(q_{\max}\) with \(0<q_{\max}<1\). Then there exist constants \(C(q_{\max})>0\) and \(c(q_{\max})>0\) such that, for every \(\beta\in\mathbb N\) and every \(q\in\mathbb R\), if
\begin{itemize}
\item \textbf{(Degree.)} \(1\le \beta\),
\item \textbf{(Budget.)} \(0<q\le q_{\max}\),
\item \textbf{(Exterior notation.)} \(x_q=2/q-1\) and \(\lambda(q)=x_q+\sqrt{x_q^2-1}\),
\end{itemize}
then both of the following hold:
\[
\text{for every real polynomial }R\text{ with }\deg(R)\le \beta
\text{ and }\sup_{x\in[-1,1]}|R(x)|\le 1,\qquad
|R(x_q)-R(-1)|\le C(q_{\max})\,\lambda(q)^\beta,
\]
and
\[
T_\beta(x_q)-1\ge c(q_{\max})\,\lambda(q)^\beta .
\]
\end{lemmav}

\cref{obj:lem:continuous-chebyshev-endpoint-bound} supplies the continuous upper and lower endpoint calculations behind \cref{obj:thm:chebyshev-minimax}. The first inequality controls the extrapolation contrast for every bounded polynomial; the second shows that the Chebyshev polynomial itself has the corresponding order of growth. After rescaling from \([-1,1]\) back to \([0,q]\), this is the source of the factor \(((1+\sqrt{1-q})^2/q)^{2\beta}\) in the amplification criterion.

The remaining deterministic ingredients connect the approximation statements to the rollout schedule class. First, the shifted Chebyshev-Lobatto nodes used in \cref{obj:def:chebyshev-schedule} are admissible budgeted schedules.

\begin{lemmav}{lem:chebyshev-schedule-admissible}[Chebyshev Schedule Admissibility]
For every integer $k \ge 1$ and every $q \in (0,1]$, the shifted Chebyshev--Lobatto schedule $p^{\mathrm{Ch}}(k,q)$ of \cref{obj:def:chebyshev-schedule} is an element of the budgeted schedule class $S_{k,q}$ of \cref{obj:def:budgeted-schedule-class}. Equivalently, its coordinates all lie in $[0,1]$, it starts at $0$, is strictly increasing across the rollout measurement indices, and ends at $q$.
\end{lemmav}

The admissibility statement matters because \cref{obj:thm:chebyshev-minimax} compares the Chebyshev schedule to all elements of \(S_{k,q}\). It verifies that endpoint clustering at \(0\) and \(q\) is compatible with the strict monotonicity imposed by \cref{obj:def:budgeted-schedule-class}.

A separate feasibility issue is the existence of polynomially unbiased weights. Distinct budgeted nodes provide enough interpolation information once the number of rollout intervals is at least the polynomial order.

\begin{lemmav}{lem:unbiased-weight-set-nonempty}[Nonempty Unbiased Weights]
Let \(q\in\mathbb R\), let \(\beta\) and \(k\) be integers, and let \(p=(p_0,\ldots,p_k)\) be a rollout schedule. Suppose that
\begin{itemize}
\item \textbf{(Order.)} \(\beta\ge 1\).
\item \textbf{(Enough nodes.)} \(k\ge \beta\).
\item \textbf{(Budgeted schedule.)} \(p\in S_{k,q}\), with \(S_{k,q}\) as in \cref{obj:def:budgeted-schedule-class}.
\end{itemize}
Then the unbiased weight set \(W_\beta(p)\) of \cref{obj:def:unbiased-weight-set} is nonempty. Equivalently, there exists a weight vector \(w=(w_0,\ldots,w_k)\) such that \(w\in W_\beta(p)\).
\end{lemmav}

\cref{obj:lem:unbiased-weight-set-nonempty} justifies the infima over \(W_\beta(p)\) in \cref{obj:def:amplification-criterion} for the schedules used in the main results. Econometrically, \(k\ge\beta\) gives at least \(\beta+1\) distinct measurements, which is the finite-dimensional requirement for exactness on the monomial basis \(1,u,\ldots,u^\beta\).

The last auxiliary statement is the variance-envelope calculation. It establishes the squared \(\ell^1\) norm as the sharp worst-case envelope over positive semidefinite covariance matrices with the stated diagonal bound.

\begin{lemmav}{lem:variance-envelope-sharpness}[Sharp Variance Envelope]
For any population size $n$, final rollout index $k$, finite assignment space $\Omega$ with rollout randomization $\pi$, rollout-round statistics $X_0,\ldots,X_k$, variance scale $\sigma_0^2$, and weight vector $w=(w_0,\ldots,w_k)$, suppose that
\begin{itemize}
\item \textbf{(Nonnegative scale.)} $\sigma_0^2\ge 0$.
\item \textbf{(Round variance envelope.)} \cref{obj:ass:round-mean-variance-envelope} holds for $X_0,\ldots,X_k$ with scale $\sigma_0^2/n$.
\end{itemize}
Then
\[
\operatorname{Var}_\pi\!\left(\sum_{j=0}^k w_j X_j\right)
\le
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2 .
\]
Moreover, there exists a positive semidefinite matrix
$\Gamma\in\mathbb R^{(k+1)\times(k+1)}$ such that
\[
\Gamma_{jj}\le \frac{\sigma_0^2}{n}\quad\text{for every }j=0,\ldots,k,
\]
and
\[
\sum_{i=0}^k\sum_{j=0}^k w_i\,\Gamma_{ij}\,w_j
=
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2 .
\]
\end{lemmav}

\cref{obj:lem:variance-envelope-sharpness} completes the connection between approximation and variance. The upper bound follows from the diagonal variance envelope and positive semidefiniteness; the sharpness clause establishes \(A_\beta(p)\) as the smallest uniform envelope criterion when cross-round covariances are otherwise unrestricted. \Cref{obj:thm:tv-envelope-design} therefore optimizes this sharp criterion directly.

\paragraph{Verification note.}
The theorem statements and proofs for the formal results displayed in this paper are machine-checked in Lean 4. The checked development covers the finite-design variance algebra over a finite assignment space, the \(\ell^1/\ell^\infty\) dual amplification calculation, the positive-semidefinite variance-envelope sharpness argument, and the real-polynomial approximation objects used in the Chebyshev and Lobatto bounds. The potential-outcome consistency restriction in \cref{obj:ass:static-rollout-consistency}, the polynomial rollout restriction in \cref{obj:ass:beta-order-polynomial}, the law-class pinning in \cref{obj:def:rollout-law-class}, and the round-mean variance envelope in \cref{obj:ass:round-mean-variance-envelope} enter as hypotheses. The Ehlich--Zeller mesh inequality enters as the explicit classical input stated in \cref{obj:lem:oversampled-chebyshev-lobatto-norming}.
