% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orth\_uniform, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_dml\_orth\_uniform} / \texttt{v1}%
  \\ \large\textit{Spectral local-misspecification frontier for DML, LRO, and ADML ATE inference}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This proposal uses the ExactID/free-form convention
\[
(\texttt{qid},\texttt{specialization},\text{SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
The locked tuple is
\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_dml\_orth\_uniform},\qquad
\texttt{specialization}=\texttt{v1},\\
\text{SWIG/DAG}=X\to D\to Y,\; X\to Y,\quad
\text{treatment }D\in\{0,1\},\\
\text{target } \theta_0=\E[Y(1)-Y(0)],\\
\text{identifying assumptions}=\text{consistency, unconfoundedness }
(Y(1),Y(0))\perp D\mid X,\text{ overlap } \epsilon\le p_0(X)\le 1-\epsilon,\\
\text{and the local nuisance-rate experiment in Assumptions \ref{ass:rates}--\ref{ass:spectral-kernel}.}
\end{gathered}
\]
The estimators compared are the cross-fit DML AIPW estimator of
\citet{ChernozhukovEtAl2018DML}, the locally robust semiparametric GMM estimator
of \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} specialized to the
ATE moment and Jacobian normalization in Assumption \ref{ass:eif-normalization},
and the automatic debiased ML/Riesz estimator of
\citet{ChernozhukovNeweySingh2022ADML}.  Nuisance rates are exponent rates
\(\delta_{g,n}=n^{-r_g}\) for outcome-regression error and
\(\delta_{p,n}=n^{-r_p}\) for propensity/Riesz error.

\begin{abstract}
This proposal asks when three leading orthogonal ATE estimators that share the
same efficient influence function still separate uniformly over local
misspecification sequences.  The proposed kernel is a spectral frontier:
cross-fit DML, locally robust semiparametric GMM (LRO), and automatic debiased
ML (ADML) are uniformly first-order equivalent if and only if the joint nuisance
rate exponent \(r_g+r_p\) exceeds a threshold \(\rho_\star(K_n)\) determined by
the smallest nonzero eigenvalue of a population covariance kernel whose
cross-fitted plug-in version is observable.
Below that frontier, the conjectured local experiment has rate-scaled pairwise
influence-remainder gaps, with DML weakly dominated by the orthogonalized
estimators and ADML attaining the smallest tangent-cone risk envelope when the
LRO moment omits a residual Riesz direction.  Resolving the conjecture would turn
the current collection of pointwise validity theorems into an estimator-choice
diagnostic: report the plug-in spectral kernel, the rate exponents, and the
implied equivalence or separation regime.  The proposal is deliberately stated as a
research question, not as a completed proof.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied users often treat DML, LRO, and ADML as interchangeable ways to obtain
orthogonal ATE inference under unconfoundedness.  That practice is justified by
their common efficient influence function under correct specification and
sufficiently fast nuisance learning, but it is not a uniform-in-DGP comparison:
near weak overlap, Riesz instability, or joint outcome-propensity
misspecification, the leading remainder can be the object that determines
whether two Wald intervals are practically identical.

\paragraph{The main finding (proposed).}
Conjecture \ref{conj:spectral-frontier} proposes a necessary-and-sufficient
frontier for uniform equivalence.  Let \(K_n\) be the covariance kernel of the
outcome-residual channel and the propensity/Riesz-representer channel after the
estimator-specific first-step projections have been put on one common EIF
normalization.  If the smallest nonzero eigenvalue satisfies
\(\lambda_{\min}^+(K_n)\asymp n^{-2\kappa}\), define
\(\rho_\star(K_n)=1/2-\kappa\).  The conjecture says that the
supremum of \(\sqrt n\) pairwise estimator differences vanishes exactly when
\(r_g+r_p>\rho_\star(K_n)\); when \(\rho_\star(K_n)<0\) this condition is
automatic for nonnegative rate exponents.  Otherwise an open set of local DGP
sequences generates pairwise tangent-cone risk-envelope gaps of order
\(s_{mm',n}^2n^{1-2(r_g+r_p)}\lambda_{\min}^+(K_n)\), where the active
projection-gap singular values \(s_{mm',n}\) certify which estimator pairs
actually separate.

\paragraph{What is new.}
The closest published results prove validity, robustness, or efficiency for one
construction at a time: \citet{ChernozhukovEtAl2018DML} for DML,
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} for LRO, and
\citet{ChernozhukovNeweySingh2022ADML},
\citet{ChernozhukovNeweySingh2022RR},
\citet{ChernozhukovNeweyQuintasMartinezSyrgkanis2024RieszRegression}, and
\citet{Singh2024KRRR} for ADML/Riesz debiasing and effective-dimension
analysis, while \citet{Velez2024DML} separates DML1 and DML2 under growing
cross-fitting fold counts.  The epsilon-gap is the absence of a single plug-in spectral
diagnostic that classifies pairwise non-equivalence among the three named
estimators over local nuisance-rate sequences.  This proposal makes the
comparison against one fixed ATE EIF rather than assigning each estimator its
own canonical gradient.

\paragraph{How it positions in the literature.}
The anchor cluster is ExactID semiparametric ATE under unconfoundedness.  The
proposal consumes the usual exact-identification statement
\(\theta_0=\E[g_{1,0}(X)-g_{0,0}(X)]\) and studies the inferential consequences of
estimating the nuisance functions, not a new do-calculus rule or a new
identification formula.  It sits at the boundary between the DML product-rate
literature, locally robust semiparametric GMM, and Riesz-representer debiasing.

\paragraph{Implications for the community.}
The concrete downstream consumer is empirical ATE work that follows the ADML
standard-error practice in \citet{ChernozhukovNeweySingh2022ADML}: the proposed
frontier would say when ADML's Riesz-based studentization is a harmless
implementation choice and when it gives a strictly sharper tangent-cone risk
diagnostic than the original DML or a locally robust moment with an incomplete
Riesz projection.

\paragraph{How research benefits from the conclusion.}
If the conjecture resolves favorably, researchers should report the estimated
Riesz-overlap spectral kernel before treating DML, LRO, and ADML confidence
intervals as equivalent.

\section{Related work}
\citet{ChernozhukovEtAl2018DML} is the baseline DML paper: it gives cross-fit
orthogonal-score ATE inference under product-rate and overlap conditions, but
does not classify uniform pairwise equivalence against LRO or ADML.
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} constructs locally
robust semiparametric moments by adding first-step influence adjustments; the
present proposal asks which ATE specialization and Jacobian normalization share
the global ATE EIF and which retain a residual projection loss.
\citet{ChernozhukovNeweySingh2022ADML} develops ADML for causal and structural
effects using automatic bias correction and misspecification-robust standard
errors; the present proposal treats that robust studentization as one endpoint
of the pairwise frontier.
\citet{ChernozhukovNeweySingh2022RR} gives regularized Riesz representers for
global and local functionals and is the closest published source for the
spectral Riesz-instability channel, but it does not compare DML, LRO, and ADML
over a single local nuisance experiment.
\citet{ChernozhukovNeweyQuintasMartinezSyrgkanis2024RieszRegression} is closer
than generic DML references on the automatic side: it learns Riesz
representers by Riesz regression and gives end-to-end automatic debiasing
theory, while the present proposal asks whether that automatic Riesz route is
uniformly equivalent to two named nonautomatic ATE estimators.
\citet{Singh2024KRRR} is the closest kernel/effective-dimension reference: it
interprets kernel balancing weights as kernel ridge Riesz representers and
analyzes misspecification and counterfactual effective dimension, but it does
not supply a DML-LRO-ADML pairwise frontier.
\citet{Velez2024DML} is the closest estimator-frontier paper missed in the
previous version: it shows that DML2 can dominate DML1 in bias, MSE, and
inference when the number of cross-fitting folds grows with sample size, while
the present proposal holds the original cross-fit DML route fixed and compares
it with LRO and ADML through nuisance-misspecification and Riesz-projection
geometry.
\citet{NeweyRobins2018CrossFit} studies cross-fitting and fast remainder rates,
which supplies the mathematical template for turning nuisance error products
into first-order equivalence or separation statements.
\citet{AvagyanVansteelandt2022PBR} extends uniform ATE inference to regimes
where one nuisance need not converge to truth, making it a close prior-art
candidate for one-sided misspecification boundaries rather than triple
estimator comparison.
\citet{DukesVansteelandtWhitney2024DRDML} proves doubly robust DML inference in
semiparametric regression and notes nonregularity when only one nuisance is
consistent; that nonregularity motivates the local-to-misspecification
experiment used here.
\citet{vanDerLaanLuedtkeCarone2024CDML} introduces calibrated DML for automatic
doubly robust inference on linear functionals, allowing one nuisance to be slow
or inconsistent after calibration; it is the closest one-slow-nuisance
comparator, but it does not classify the pairwise DML-LRO-ADML spectral
frontier or give an iff variance-separation threshold among the three named
estimators.
\citet{BrunsSmithDukesFellerOgburn2024ABW} characterizes augmented balancing
weights and AutoDML-style estimators through algebraic equivalences and
tuning-dependent behavior; it is the nearest algebraic-equivalence thread, but
not a sharp uniform tangent-cone risk frontier for the three named estimators.
\citet{ChernozhukovNeweySingh2023Biometrika} gives a finite-sample debiased ML
theorem for global and local functionals; it provides a general robustness
benchmark but not an iff comparison between DML, LRO, and ADML.

In-repo prior art is currently negative rather than duplicative.  The active
\texttt{eid\_dml\_orth\_uniform} catalogue entry has only state and pipeline
metadata before this proposal.  The closest banked ThmSmith analogue is
\texttt{eid\_bjs\_efficient\_event\_study}, whose rejected proposal asked for
an influence-function equivalence frontier between named estimators and whose
reviewer requested a gap matrix to one fixed efficient EIF.  The downgraded
\texttt{eid\_lp\_svar\_nonequiv} proposal is relevant because its non-equivalence
margin was assumed rather than derived from primitive finite-support
conditions.  The downgraded
\texttt{pid\_offline\_policy\_joint\_misspec} proposal is relevant only as an
analogy for joint nuisance envelopes: it warns that rectangular one-nuisance
bounds can miss compatibility restrictions.

\section{Formal setup}
Let \(W=(Y,D,X)\sim P\), with \(D\in\{0,1\}\), outcome \(Y\in\R\), and
covariates \(X\in\mathcal{X}\).  The SWIG has baseline covariates \(X\), treatment
node \(D\), and potential outcomes \(Y(1),Y(0)\).  Define
\[
g_{d,0}(x)=\E[Y\mid D=d,X=x],\qquad p_0(x)=\Pr(D=1\mid X=x),
\]
\[
\theta_0=\E[Y(1)-Y(0)]=\E[g_{1,0}(X)-g_{0,0}(X)].
\]
The efficient ATE influence function under the nonparametric unconfoundedness
model is
\[
\phi_0(W)=g_{1,0}(X)-g_{0,0}(X)-\theta_0+
\frac{D}{p_0(X)}\{Y-g_{1,0}(X)\}
-\frac{1-D}{1-p_0(X)}\{Y-g_{0,0}(X)\}.
\]
For a local law \(P_n\), \(\phi_n\) denotes the same formula with
\((g_{1,n},g_{0,n},p_n,\theta_n)\) in place of
\((g_{1,0},g_{0,0},p_0,\theta_0)\), and \(\mathcal{P}_n\) denotes the local DGP
class satisfying the assumptions below.  The notation \(g_{D,n}^\star(X)\)
means \(Dg_{1,n}^\star(X)+(1-D)g_{0,n}^\star(X)\).
Let \(\hat\theta_D\), \(\hat\theta_L\), and \(\hat\theta_A\) denote,
respectively, the DML, LRO, and ADML estimators after cross-fitting on the same
fold partition.  For a local sequence \(P_n\), write
\(\Delta_{g,n}=(\hat g_1-g_{1,n}^\star,\hat g_0-g_{0,n}^\star)\) and
\(\Delta_{p,n}=\hat p-p_n^\star\), where starred limits may equal the truth
or a pseudo-truth under misspecification.  The pairwise first-order remainders
are modeled as bilinear forms
\[
B_m(\Delta_g,\Delta_p)=
\E\!\left[\langle \Delta_g(X),\, T_m\Delta_p(X)\rangle\right],
\qquad m\in\{D,L,A\},
\]
where \(T_D\) is the DML propensity channel, \(T_L\) is the LRO channel after
its moment/Jacobian projection, and \(T_A\) is the minimal Riesz projection
channel.

To put the three channels in one coordinate system, fix a finite
gap-coordinate dictionary \(b_n(X)\in\R^{q_n}\).  The dictionary is either
fixed ex ante or selected by a training-fold-only rule; the observable version
\(\hat b_n\) converges in \(L^2(P_n)\) to \(b_n\).  Its span contains the
projected propensity/Riesz directions used by \(T_D,T_L,T_A\) and the pairwise
gap directions \(T_m-T_{m'}\).  Let
\(\Pi_{D,n},\Pi_{L,n},\Pi_{A,n}\) be the population limits of the
estimator-specific coordinate projection matrices, with observable
cross-fitted analogues \(\hat\Pi_{D,n},\hat\Pi_{L,n},\hat\Pi_{A,n}\).  The
coordinate form of \(T_m\Delta_p\) is \(\Pi_{m,n}\beta_p\) when
\(\Delta_p(X)=b_n(X)^\transpose\beta_p\).  For the LRO estimator,
\(\Pi_{L,n}=J_{L,n}^{-1}G_{L,n}\) is the ATE-specialized Jacobian/GMM
projection matrix; the exact LRO--ADML collapse condition is
\(\operatorname{span}(\Pi_{L,n})=\operatorname{span}(\Pi_{A,n})\) on the
pairwise gap subspace.  The finite gap-coordinate selection rule keeps the
union of estimated singular directions of
\(\hat\Pi_{D,n}-\hat\Pi_{L,n}\), \(\hat\Pi_{L,n}-\hat\Pi_{A,n}\), and
\(\hat\Pi_{D,n}-\hat\Pi_{A,n}\) whose singular values exceed a deterministic
tolerance \(\tau_n\downarrow0\).  Define the population residual and Riesz
coordinate vectors
\[
Z_{g,n}(W)=b_n(X)\{Y-g_{D,n}^\star(X)\},\qquad
Z_{p,n}(W)=b_n(X)\left\{\frac{D}{p_n^\star(X)}
-\frac{1-D}{1-p_n^\star(X)}\right\}.
\]
Both vectors lie in \(\R^{q_n}\).  The spectral covariance kernel is the
\(q_n\times q_n\) population target
\[
K_n=\E_{P_n}\!\left[
Z_{g,n}(W)Z_{g,n}(W)^\transpose+
Z_{p,n}(W)Z_{p,n}(W)^\transpose\right],
\]
and the actual diagnostic is the cross-fitted plug-in
\[
\hat K_n=\frac1n\sum_{i=1}^n
\left[
\hat Z_{g,n}(W_i)\hat Z_{g,n}(W_i)^\transpose+
\hat Z_{p,n}(W_i)\hat Z_{p,n}(W_i)^\transpose
\right],
\]
where \(\hat Z_{g,n}\) and \(\hat Z_{p,n}\) replace
\((g_{D,n}^\star,p_n^\star,b_n)\) by their training-fold estimates.  The
frontier uses \(K_n\), while observability means
\(\|\hat K_n-K_n\|_{\mathrm{op}}=o_P(\lambda_{\min}^+(K_n))\) on the selected
gap span.  Let
\(\lambda_{\min}^+(K_n)\) be the smallest positive eigenvalue on the span of the
coordinate gap directions
\(\operatorname{range}(\Pi_{D,n}-\Pi_{L,n})+
\operatorname{range}(\Pi_{L,n}-\Pi_{A,n})+
\operatorname{range}(\Pi_{D,n}-\Pi_{A,n})\).  If
\(\lambda_{\min}^+(K_n)\asymp n^{-2\kappa}\), set
\[
\rho_\star(K_n)=1/2-\kappa.
\]
For each active pair \(m,m'\), let
\[
s_{mm',n}=\sigma_{\min}^+\!\left((\Pi_{m,n}-\Pi_{m',n})\big|_{\mathcal{G}_{mm',n}}\right)
\]
be the smallest nonzero singular value of the pairwise projection gap on its
selected coordinate gap span \(\mathcal{G}_{mm',n}\).  The observable diagnostic
therefore consists of \((\hat K_n,\hat s_{DL,n},\hat s_{LA,n},\hat s_{DA,n})\);
\(\lambda_{\min}^+(K_n)\) measures the size of perturbations in the selected
coordinates, while the \(s_{mm',n}\)'s measure whether a given estimator pair
actually loads on those perturbations.
Let \(\mathcal{T}_n\) be the set of local tangent directions generated by the
normalized outcome-regression and propensity/Riesz perturbations, with
\(\mathcal{T}\) used as shorthand when \(n\) is clear.  For
\(m\in\{D,L,A\}\), let \(\mathfrak V_{m,n}\) denote the local
tangent-cone asymptotic risk envelope
\[
\mathfrak V_{m,n}
=\sup_{h\in\mathcal{T}_n:\|h\|_{K_n}\le 1}
\operatorname{Var}_{\Omega_n(h)}\!\left(Z_{0,n}+G_{m,n}(h)\right),
\]
where \(G_{m,n}(h)\) is the Gaussian limit of
\(\sqrt n\,B_m(\Delta_{g,n},\Delta_{p,n})\) along tangent direction \(h\) and
\(\|h\|_{K_n}\) is the norm induced by the selected gap-coordinate kernel.  More
precisely, \((Z_{0,n},G_{D,n}(h),G_{L,n}(h),G_{A,n}(h))\) denotes the joint
Gaussian limit of the EIF empirical process and the three rate-scaled bilinear
channels, with \(Z_{0,n}\sim N(0,\E_{P_n}[\phi_n(W)^2])\).  Cross-fitting
removes own-fold empirical-process products but does not by itself force
\(\operatorname{Cov}(Z_{0,n},G_{m,n}(h))=0\); the covariance blocks are part of
the local Gaussian experiment below and enter every displayed variance envelope.

\begin{verbatim}
qid=eid_dml_orth_uniform
specialization=v1
cluster=ExactID semiparametric ATE under unconfoundedness
SWIG/DAG=X -> D -> Y with X -> Y
treatment=D in {0,1}
target=theta_0 = E[Y(1)-Y(0)]
estimators=DML cross-fit AIPW, LRO ATE-specialized semiparametric GMM, ADML Riesz debiased ML
nuisance_rates=||g_hat-g_star||_2=O_P(n^{-r_g}), ||p_hat-p_star||_2=O_P(n^{-r_p})
frontier_index=rho_star(K_n)=1/2-kappa, lambda_min^+(K_n) asymp n^{-2 kappa}
gap_coordinates=b_n(X) in R^{q_n}; observable plug-in K_hat,n estimates population K_n
projection matrices Pi_D,n, Pi_L,n, Pi_A,n are population limits of cross-fitted estimator matrices
active_pair_singular_values=s_DL,n, s_LA,n, s_DA,n for projection gaps on selected coordinates
identifying_assumptions=consistency, unconfoundedness, overlap, local nuisance-rate experiment
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Exact ATE identification]\label{ass:identification}
The observed law \(P_n\) satisfies consistency \(Y=DY(1)+(1-D)Y(0)\),
unconfoundedness \((Y(1),Y(0))\perp D\mid X\), and positivity
\(\epsilon_n\le p_n(X)\le 1-\epsilon_n\) almost surely, with
\(\epsilon_n>0\).  The phrase ``bounded-overlap corner'' means
\(\inf_n\epsilon_n>0\).  The target is
\(\theta_n=\E_{P_n}[Y(1)-Y(0)]\).
\end{assumption}

\begin{assumption}[Common EIF normalization]\label{ass:eif-normalization}
The DML, LRO, and ADML estimators are all centered at the same ATE functional
\(\theta_n\) and are normalized so that, under correct specification and
bounded overlap, their asymptotic linear term is the single efficient influence
function \(\phi_n\) defined in \S6.  In the LRO estimator, the Jacobian and GMM
weight induce the coordinate projection
\(\Pi_{L,n}=J_{L,n}^{-1}G_{L,n}\) in the common basis \(b_n\), so the ATE moment
is compared to \(\phi_n\), not to an estimator-specific canonical gradient.
\end{assumption}

\begin{assumption}[Cross-fitting and local nuisance rates]\label{ass:rates}
All nuisance estimates are cross-fitted on folds independent of the evaluation
fold.  Along \(P_n\),
\[
\|\Delta_{g,n}\|_{2,P_n}=O_P(n^{-r_g}),\qquad
\|\Delta_{p,n}\|_{2,P_n}=O_P(n^{-r_p}),
\]
with deterministic exponents \(r_g,r_p\ge 0\).  The normalized errors have
weak limits in a fixed tangent cone \(\mathcal{T}\), so local risk envelopes can
be formed by taking suprema over \(\mathcal{T}\).
\end{assumption}

\begin{assumption}[Second-order expansion]\label{ass:second-order}
For \(m\in\{D,L,A\}\),
\[
\sqrt n(\hat\theta_m-\theta_n)=n^{-1/2}\sum_{i=1}^n\phi_n(W_i)
\;+\;
\sqrt n\,B_m(\Delta_{g,n},\Delta_{p,n})+o_P(1)
\]
uniformly over the local DGP class.  The maps \(B_m\) are the bilinear
remainder maps defined in \S6 and have finite operator norm on \(\mathcal{T}\).
\end{assumption}

\begin{assumption}[Spectral kernel and eigengap]\label{ass:spectral-kernel}
The dictionary \(b_n(X)\), observable dictionary \(\hat b_n(X)\), projection
matrices \(\Pi_{D,n},\Pi_{L,n},\Pi_{A,n}\), observable projections
\(\hat\Pi_{D,n},\hat\Pi_{L,n},\hat\Pi_{A,n}\), coordinate vectors
\(Z_{g,n}(W),Z_{p,n}(W)\), population kernel \(K_n\), plug-in kernel
\(\hat K_n\), tolerance \(\tau_n\), selected gap-coordinate span, and active
pairwise singular values \(s_{DL,n},s_{LA,n},s_{DA,n}\) are as
defined in \S6.  The kernel is finite and has a positive eigenvalue on at least
one pairwise estimator-gap direction.  The plug-in diagnostic is consistent on
the selected span:
\(\|\hat K_n-K_n\|_{\mathrm{op}}=o_P(\lambda_{\min}^+(K_n))\).  The smallest
positive population eigenvalue on that span satisfies
\(\lambda_{\min}^+(K_n)\asymp n^{-2\kappa}\) for some \(\kappa\ge 0\), and
\(\rho_\star(K_n)=1/2-\kappa\).
\end{assumption}

\begin{assumption}[Local Gaussian experiment]\label{ass:gaussian-experiment}
For each \(h\in\mathcal{T}_n\), the vector
\[
\left(n^{-1/2}\sum_{i=1}^n\phi_n(W_i),\;
\sqrt n B_D(\Delta_{g,n},\Delta_{p,n}),\;
\sqrt n B_L(\Delta_{g,n},\Delta_{p,n}),\;
\sqrt n B_A(\Delta_{g,n},\Delta_{p,n})\right)
\]
converges jointly to a centered Gaussian vector
\((Z_{0,n},G_{D,n}(h),G_{L,n}(h),G_{A,n}(h))\) with covariance matrix
\(\Omega_n(h)\).  Its upper-left entry is \(\E_{P_n}[\phi_n(W)^2]\), and the
off-diagonal blocks between \(Z_{0,n}\) and the \(G_{m,n}(h)\)'s are retained
unless an auxiliary-sample design or an explicit orthogonality calculation makes
them zero.  The risk envelope \(\mathfrak V_{m,n}\) is
\(\sup_{\|h\|_{K_n}\le1}\operatorname{Var}_{\Omega_n(h)}(Z_{0,n}+G_{m,n}(h))\).
\end{assumption}

\begin{assumption}[Primitive finite-support inequalities]\label{ass:primitive-open}
For any candidate three-point witness law \(P^\circ\), write its covariate
support as \(\{x_1,x_2,x_3\}\), cell probabilities as \(\pi_j=P^\circ(X=x_j)\),
propensities as \(p_j=P^\circ(D=1\mid X=x_j)\), conditional means as
\(\mu_{dj}=E_{P^\circ}[Y\mid D=d,X=x_j]\), conditional residual variances as
\(\sigma^2_{dj}=\operatorname{Var}_{P^\circ}(Y\mid D=d,X=x_j)\), let
\(u_{DL}\) be the coordinate vector of the DML propensity channel after
orthogonal projection away from the LRO span, and let \(u_{LA}\) be the
coordinate vector of the ADML Riesz direction after orthogonal projection away
from the LRO span.  The primitive witness
inequalities are
\[
\pi_j>0,\qquad 0<\epsilon<p_j<1-\epsilon<1,\qquad
\max_{d,j}\sigma^2_{dj}<\infty,\qquad
\sum_{d,j}\sigma^2_{dj}>0,\qquad
\|u_{DL}\|_{K^\circ}>0,\qquad
\|u_{LA}\|_{K^\circ}>0,
\]
where \(K^\circ\) is the finite-support version of the covariance kernel in
\S6.  These are pointwise inequalities for a proposed law, not an existential
or open-neighborhood condition.
\end{assumption}

\begin{assumption}[Moment regularity]\label{ass:moments}
For some \(q>4\), \(\sup_n\E_{P_n}[|Y|^q]<\infty\) after weighting by the
inverse-overlap factors appearing in \(\phi_n\), and the fold-level empirical
process remainders are \(o_P(1)\) uniformly over the local class.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: common EIF corner case]\label{thm:common-eif}
Under Assumptions \ref{ass:identification}, \ref{ass:eif-normalization},
\ref{ass:rates}, \ref{ass:second-order}, and \ref{ass:moments}, if
\(p_n^\star=p_n\), \(g_{d,n}^\star=g_{d,n}\), overlap is bounded away from zero,
and \(r_g+r_p>1/2\), then
\[
\sqrt n(\hat\theta_D-\theta_n),\quad
\sqrt n(\hat\theta_L-\theta_n),\quad
\sqrt n(\hat\theta_A-\theta_n)
\]
have the same first-order limit \(N(0,\E[\phi_n(W)^2])\), and every pairwise
difference is \(o_P(1)\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
This theorem is not the flagship novelty; it is a required sanity anchor.  The
closest result is \citet{ChernozhukovEtAl2018DML}, with supporting comparisons
in \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} and
\citet{ChernozhukovNeweySingh2022ADML}.  The epsilon-gap is only the common
normalization across the three named estimators.  Its concrete consumer is
Conjecture \ref{conj:spectral-frontier}: the conjectured frontier must reduce
to this textbook product-rate equivalence when \(K_n\) is bounded away from
singularity.

\begin{conjecture}[Conjecture 1: spectral uniform non-equivalence frontier (NOT YET PROVED)]\label{conj:spectral-frontier}
Under Assumptions \ref{ass:identification}--\ref{ass:moments}, the following
are equivalent:
\[
\sup_{P_n\in\mathcal{P}_n}\max_{m\ne m'}\left|
\sqrt n\{(\hat\theta_m-\theta_n)-(\hat\theta_{m'}-\theta_n)\}\right|
\stackrel{P}{\longrightarrow}0
\]
for \(m,m'\in\{D,L,A\}\), and
\[
r_g+r_p>\rho_\star(K_n).
\]
If \(r_g+r_p\le \rho_\star(K_n)\), then necessarily \(\kappa\le 1/2\), and
there is an open set of local DGP sequences satisfying Assumption
\ref{ass:primitive-open} and active pairwise singular values
\(s_{DL,n},s_{LA,n}\) bounded below on the selected spans for which the pairwise
tangent-cone risk envelopes are strictly ordered:
\[
\mathfrak V_{D,n}-\mathfrak V_{L,n}
\ge c_{DL} s_{DL,n}^2 n^{1-2(r_g+r_p)}\lambda_{\min}^+(K_n),\qquad
\mathfrak V_{L,n}-\mathfrak V_{A,n}
\ge c_{LA} s_{LA,n}^2 n^{1-2(r_g+r_p)}\lambda_{\min}^+(K_n),
\]
for constants \(c_{DL},c_{LA}>0\) determined by the tangent-cone normalization.
Equivalently, the strict risk-envelope separation is governed by the normalized
local amplitude
\(a_n(r_g,r_p,K_n)=n^{1-2(r_g+r_p)}\lambda_{\min}^+(K_n)\), which vanishes
if and only if \(r_g+r_p>1/2-\kappa=\rho_\star(K_n)\), including the
automatic-equivalence case \(\kappa>1/2\).  If only one active singular value is
bounded below, the same frontier gives strict separation only for that active
pair and not a universal \(D>L>A\) ordering.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
The closest papers are \citet{ChernozhukovEtAl2018DML},
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO},
\citet{ChernozhukovNeweySingh2022ADML}, and
\citet{ChernozhukovNeweySingh2022RR}, with the nearest automatic-Riesz
extensions \citet{ChernozhukovNeweyQuintasMartinezSyrgkanis2024RieszRegression}
and \citet{Singh2024KRRR}, and the nearest calibrated doubly robust comparator
\citet{vanDerLaanLuedtkeCarone2024CDML}; the closest estimator-frontier
comparator is \citet{Velez2024DML}.  The latter separates DML1 and DML2 under a
growing-\(K\) asymptotic experiment, whereas this conjecture fixes the DML
cross-fitting convention and asks for a DML-LRO-ADML nuisance-rate and
projection-gap threshold.  Each of the other papers establishes validity,
orthogonality, robust standard errors, Riesz construction, Riesz-regression
learning, effective-dimension control, or one-slow-nuisance asymptotic
linearity for its own estimator class; none gives an iff, uniform-in-DGP,
closed-form spectral boundary for pairwise non-equivalence among all three
named ATE estimators.  The epsilon-gap to calibrated DML is especially narrow:
C-DML uses calibration to restore doubly robust asymptotic linearity when one
nuisance is slow or inconsistent, while this conjecture compares three named
uncalibrated/calibrated-adjacent estimator routes against one fixed ATE EIF and
asks when their variance envelopes coincide or separate.
Resolving the conjecture would give applied users of
\citet{ChernozhukovNeweySingh2022ADML} a computable diagnostic for when ADML
standard errors are first-order interchangeable with DML/LRO standard errors
and when the ADML tangent-cone risk envelope is strictly smaller.

\begin{center}
\begin{tabular}{lll}
\hline
Gap & Projection difference & Main consumer \\
\hline
\(D-L\) & \(\Pi_{D,n}-\Pi_{L,n}\) & \citet{ChernozhukovEtAl2018DML} product-rate diagnostics \\
\(L-A\) & \(\Pi_{L,n}-\Pi_{A,n}\) & \citet{ChernozhukovNeweySingh2022ADML} Riesz studentization \\
\(D-A\) & \(\Pi_{D,n}-\Pi_{A,n}\) & \citet{vanDerLaanLuedtkeCarone2024CDML} one-slow-nuisance comparison \\
\hline
\end{tabular}
\end{center}

\begin{conjecture}[Conjecture 2: primitive finite-support witness (NOT YET PROVED)]\label{conj:witness}
There exists a three-point covariate support, binary treatment, and bounded
outcome law whose cell probabilities, treatment propensities, residual
variances, DML--LRO coordinate gap, and LRO--ADML residual Riesz coordinate
satisfy the pointwise primitive
inequalities in Assumption \ref{ass:primitive-open}, and whose induced local
DGP class satisfies Assumptions \ref{ass:identification},
\ref{ass:eif-normalization}, \ref{ass:rates}, \ref{ass:second-order},
\ref{ass:spectral-kernel}, \ref{ass:gaussian-experiment}, and
\ref{ass:moments}, with
\(\lambda_{\min}^+(K_n)>0\), such that the inequalities in Conjecture
\ref{conj:spectral-frontier} are strict.  Moreover the primitive inequalities
and the strict risk-envelope inequalities persist on an open neighborhood of
the cell probabilities, treatment propensities, conditional residual variances,
conditional outcome means, and DML/LRO/ADML projection coordinates.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
This statement responds to the recurring ThmSmith failure mode visible in the
banked \texttt{eid\_lp\_svar\_nonequiv} and
\texttt{eid\_bjs\_efficient\_event\_study} proposals: a non-equivalence margin
should not be hidden inside an assumption.  The closest published thread is
\citet{BrunsSmithDukesFellerOgburn2024ABW}, which gives concrete algebraic
equivalences for augmented balancing weights and AutoDML-style estimators, but
not a finite-support witness for strict DML-LRO-ADML risk separation.  The
concrete consumer is Conjecture \ref{conj:spectral-frontier}: a finite-support
witness would make the spectral frontier falsifiable rather than merely formal.

\section{Sanity-check corollaries}
\begin{corollary}[Bounded-overlap product-rate reduction]\label{cor:product-rate}
Under Assumptions \ref{ass:identification}--\ref{ass:moments}, if
\(\lambda_{\min}^+(K_n)\) is bounded away from zero, then
\(\rho_\star(K_n)=1/2\).  Conjecture \ref{conj:spectral-frontier} therefore
collapses to the standard product-rate condition \(r_g+r_p>1/2\), the usual
\(n^{-1/4}\)-by-\(n^{-1/4}\) DML boundary.
\end{corollary}

\begin{corollary}[Fast spectral decay]\label{cor:fast-spectral-decay}
Under Assumptions \ref{ass:rates} and \ref{ass:spectral-kernel}, if
\(\kappa>1/2\), then \(\rho_\star(K_n)<0\).  Since \(r_g,r_p\ge0\), the
condition \(r_g+r_p>\rho_\star(K_n)\) holds automatically and the normalized
amplitude \(a_n(r_g,r_p,K_n)\) vanishes even at \(r_g+r_p=0\).
\end{corollary}

\begin{corollary}[No residual Riesz direction]\label{cor:no-gap}
Under Assumptions \ref{ass:eif-normalization} and \ref{ass:spectral-kernel}, if
the LRO projection span equals the ADML minimal Riesz span on the pairwise
gap directions, then \(K_n\) has no positive eigenvalue on the \(L-A\) gap
subspace and Conjecture \ref{conj:spectral-frontier} predicts no strict
LRO-ADML tangent-cone risk separation.
\end{corollary}

\begin{corollary}[Correct specification]\label{cor:correct-spec}
Under Assumptions \ref{ass:identification}, \ref{ass:eif-normalization},
\ref{ass:rates}, \ref{ass:second-order}, and \ref{ass:gaussian-experiment}, if
\(\Delta_{g,n}=0\) or \(\Delta_{p,n}=0\) on every evaluation fold, all bilinear
remainders \(B_m(\Delta_{g,n},\Delta_{p,n})\) vanish, the Gaussian channels
\(G_{m,n}(h)\) are zero, and the three estimators share the same first-order
law with variance \(\E_{P_n}[\phi_n(W)^2]\).
\end{corollary}

\section{Proof-sketch route}
The mathematical route is to put the three estimators on one ATE EIF
normalization, derive their cross-fitted von Mises expansions, and isolate the
pairwise bilinear remainder maps \(B_D-B_L\), \(B_L-B_A\), and \(B_D-B_A\).
Those maps should reduce to compact quadratic forms on the finite-dimensional
tangent span generated by the outcome-regression and propensity/Riesz
perturbations in the common \(b_n\)-coordinate basis.  The spectral threshold
follows by comparing the rate-scaled amplitude
\(n^{1-2(r_g+r_p)}\lambda_{\min}^+(K_n)\) with zero: if it vanishes, pairwise
remainders are first-order negligible, while if it is bounded away from zero
the local experiment should deliver a nonzero tangent-cone risk-envelope gap.  The
hard boundary cases are (i) weak-overlap
local sequences where the Riesz norm diverges, (ii) LRO Jacobian choices that
project away only part of the Riesz direction, and (iii) a three-point
finite-support enumeration proving a strict open-set gap rather than a
hand-tuned equality failure.  The covariance matrix \(\Omega_n(h)\) must be
carried through the comparison, because cross-fitting alone does not eliminate
all covariance between the empirical EIF process and nuisance-remainder limits.
No Lean or formalization substrate is needed to
judge this route at the proposal stage.

\section{Honest scope flags}
Theorem \ref{thm:common-eif} is a routine corner-case theorem conditional on
the common normalization and second-order expansion.  Conjectures
\ref{conj:spectral-frontier} and \ref{conj:witness} are not yet proved and are
the actual research kernel.  The most fragile modeling choice is the exact
definition of the LRO projection channel \(T_L\): if the intended LRO
specialization already spans the same minimal Riesz direction as ADML, the
strict \(L-A\) part should be withdrawn and replaced by a DML-versus-common
orthogonal frontier.  The second fragile choice is the scaling convention for
\(\rho_\star(K_n)\); this draft defines it without max-truncation as
\(1/2-\kappa\) through
\(\lambda_{\min}^+(K_n)\asymp n^{-2\kappa}\) and the normalized amplitude
\(n^{1-2(r_g+r_p)}\lambda_{\min}^+(K_n)\), so that the bounded-overlap case
recovers the textbook product-rate boundary and the \(\kappa>1/2\) case becomes
automatic equivalence for all nonnegative nuisance-rate exponents.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft of a spectral local-misspecification
frontier with common EIF normalization, primitive witness conjecture, and
named DML/LRO/ADML prior-art checklist; prior verdict: none.
\item v2 (revise) -- pinned the spectral kernel to common finite
gap-coordinate projections and inserted the rate-scaled separation amplitude
requested by the soundness review; prior verdict: REVISE.
\item v3 (revise) -- removed the max-truncated frontier, made the spectral
kernel observable through an explicit cross-fitted plug-in diagnostic, replaced
estimator-specific lower-bound language with tangent-cone risk envelopes, and
added the closer Riesz-regression/effective-dimension references; prior
verdict: REVISE.
\item v4 (revise) -- added calibrated DML as the close one-slow-nuisance
comparator, inserted a D-L/L-A/D-A gap table, and replaced the existential
primitive witness assumption with pointwise finite-support inequalities; prior
verdict: REVISE.
\item v5 (revise) -- added the Velez DML1/DML2 growing-\(K\) comparator,
defined the joint local Gaussian experiment behind the risk envelopes, and made
strict separation depend on active D-L and L-A projection singular values; prior
verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., D.~Chetverikov, M.~Demirer, E.~Duflo, C.~Hansen,
W.~Newey, and J.~Robins (2018).
\newblock Double/debiased machine learning for treatment and structural
parameters.
\newblock \emph{The Econometrics Journal} 21(1), C1--C68.
\newblock \url{https://doi.org/10.1111/ectj.12097}.

\bibitem[Chernozhukov et~al.(2022a)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
Chernozhukov, V., J.~C. Escanciano, H.~Ichimura, W.~K. Newey, and J.~M. Robins
(2022).
\newblock Locally robust semiparametric estimation.
\newblock \emph{Econometrica} 90(4), 1501--1535.
\newblock \url{https://doi.org/10.3982/ECTA16294}.

\bibitem[Chernozhukov et~al.(2022b)]{ChernozhukovNeweySingh2022ADML}
Chernozhukov, V., W.~K. Newey, and R.~Singh (2022).
\newblock Automatic debiased machine learning of causal and structural effects.
\newblock \emph{Econometrica} 90(3), 967--1027.
\newblock \url{https://doi.org/10.3982/ECTA18515}.

\bibitem[Chernozhukov et~al.(2022c)]{ChernozhukovNeweySingh2022RR}
Chernozhukov, V., W.~K. Newey, and R.~Singh (2022).
\newblock Debiased machine learning of global and local parameters using
regularized Riesz representers.
\newblock \emph{The Econometrics Journal} 25(3), 576--601.
\newblock \url{https://doi.org/10.1093/ectj/utac002}.

\bibitem[Chernozhukov et~al.(2024)]{ChernozhukovNeweyQuintasMartinezSyrgkanis2024RieszRegression}
Chernozhukov, V., W.~K. Newey, V.~Quintas-Martinez, and V.~Syrgkanis (2024).
\newblock Automatic debiased machine learning via Riesz regression.
\newblock arXiv:2104.14737.
\newblock \url{https://arxiv.org/abs/2104.14737}.

\bibitem[Chernozhukov et~al.(2023)]{ChernozhukovNeweySingh2023Biometrika}
Chernozhukov, V., W.~K. Newey, and R.~Singh (2023).
\newblock A simple and general debiased machine learning theorem with
finite-sample guarantees.
\newblock \emph{Biometrika} 110(1), 257--264.
\newblock \url{https://doi.org/10.1093/biomet/asac033}.

\bibitem[Newey and Robins(2018)]{NeweyRobins2018CrossFit}
Newey, W.~K. and J.~M. Robins (2018).
\newblock Cross-fitting and fast remainder rates for semiparametric estimation.
\newblock arXiv:1801.09138.
\newblock \url{https://arxiv.org/abs/1801.09138}.

\bibitem[Avagyan and Vansteelandt(2022)]{AvagyanVansteelandt2022PBR}
Avagyan, V. and S.~Vansteelandt (2022).
\newblock High-dimensional inference for the average treatment effect under
model misspecification using penalized bias reduction.
\newblock \emph{Biostatistics and Epidemiology} 6(2), 323--341.
\newblock \url{https://doi.org/10.1080/24709360.2021.1898730}.

\bibitem[Dukes et~al.(2024)]{DukesVansteelandtWhitney2024DRDML}
Dukes, O., S.~Vansteelandt, and D.~Whitney (2024).
\newblock On doubly robust inference for double machine learning in
semiparametric regression.
\newblock \emph{Journal of Machine Learning Research} 25(279), 1--46.
\newblock \url{https://jmlr.org/papers/v25/22-1233.html}.

\bibitem[van der Laan et~al.(2024)]{vanDerLaanLuedtkeCarone2024CDML}
van der Laan, L., A.~Luedtke, and M.~Carone (2024).
\newblock Automatic doubly robust inference for linear functionals via
calibrated debiased machine learning.
\newblock arXiv:2411.02771.
\newblock \url{https://arxiv.org/abs/2411.02771}.

\bibitem[Bruns-Smith et~al.(2024)]{BrunsSmithDukesFellerOgburn2024ABW}
Bruns-Smith, D., O.~Dukes, A.~Feller, and E.~L. Ogburn (2024).
\newblock Augmented balancing weights as linear regression.
\newblock arXiv:2304.14545.
\newblock \url{https://arxiv.org/abs/2304.14545}.

\bibitem[Singh(2024)]{Singh2024KRRR}
Singh, R. (2024).
\newblock Kernel ridge Riesz representers: generalization, mis-specification,
and the counterfactual effective dimension.
\newblock arXiv:2102.11076.
\newblock \url{https://arxiv.org/abs/2102.11076}.

\bibitem[Velez(2024)]{Velez2024DML}
Velez, A. (2024).
\newblock On the asymptotic properties of debiased machine learning estimators.
\newblock arXiv:2411.01864, updated March 20, 2026.
\newblock \url{https://arxiv.org/abs/2411.01864}.
\end{thebibliography}

\end{document}
