% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orth\_uniform, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_dml\_orth\_uniform} / \texttt{v1}%
  \\ \large\textit{Weak-overlap studentization frontier for DML, LRO, and ADML ATE inference}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This proposal uses the ExactID/free-form convention
\[
(\texttt{qid},\texttt{specialization},\text{SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
The locked tuple is
\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_dml\_orth\_uniform},\qquad
\texttt{specialization}=\texttt{v1},\\
\text{SWIG/DAG}=X\to D\to Y,\; X\to Y,\quad
\text{treatment }D\in\{0,1\},\\
\text{target } \theta_0=\E[Y(1)-Y(0)],\\
\text{identifying assumptions}=\text{consistency, unconfoundedness }
(Y(1),Y(0))\perp D\mid X,\\
\text{local weak overlap } \ell_n\le p_0(X)\le 1-\ell_n
\text{ with }\ell_n=n^{-\omega},\;0\le \omega<1,\\
\text{and Assumptions \ref{ass:eif}--\ref{ass:student-kernel} below.}
\end{gathered}
\]
The compared procedures are the original cross-fit DML AIPW estimator
\(\widehat\theta_D\) of \citet{ChernozhukovEtAl2018DML}, the ATE-specialized
locally robust semiparametric GMM estimator \(\widehat\theta_L\) of
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}, and the automatic
debiased ML/Riesz estimator \(\widehat\theta_A\) of
\citet{ChernozhukovNeweySingh2022ADML}.  The estimator-specific standard-error
estimators are \(\widehat V_D\) (empirical DML score variance),
\(\widehat V_L\) (the LRO sandwich variance for the ATE moment
\[
  \varphi_L(W;\theta,\eta)=g_1(X)-g_0(X)-\theta
  +\frac{D}{p(X)}(Y-g_1(X))
  -\frac{1-D}{1-p(X)}(Y-g_0(X)),
  \quad J_L=-\E[\partial_\theta\varphi_L]=1,
\]
with sandwich normalization \(J_L^{-1}\E[\varphi_L^2]J_L^{-1}\)), and
\(\widehat V_A\) (ADML misspecification-robust Riesz variance).
Outcome-regression and propensity/Riesz \(L^2(P)\) errors have exponent rates
\(\delta_{g,n}=n^{-r_g}\) and \(\delta_{\alpha,n}=n^{-r_\alpha}\).

\begin{abstract}
This proposal asks whether three orthogonal ATE point estimators can be
first-order equivalent while their Wald studentizations are not.  The proposed
kernel is a local-to-weak-overlap frontier: after normalizing all three
estimators to the same ATE efficient influence function, the point estimates
remain mutually equivalent over a region of \((r_g,r_\alpha,\omega)\), but the
studentized statistics separate whenever a named covariance-kernel eigenvalue
dominates the nuisance-rate product.  The novel object is the studentization
gap kernel \(S_n\), built from the observable variance-score summands used by
the DML empirical score variance, the LRO sandwich variance, and the ADML
misspecification-robust Riesz variance.  Conjecture
\ref{conj:student-frontier} gives the
sharp iff boundary for \(\widehat T_D-\widehat T_A\) and
\(\widehat T_L-\widehat T_A\), while Theorem \ref{thm:common-eif} records the
standard common-EIF collapse under fixed overlap and product rates.  Resolving
the conjecture would tell applied users when DML, LRO, and ADML confidence
intervals can be reported interchangeably and when ADML's robust
studentization is the first object that detects weak-overlap fragility.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
The ATE under unconfoundedness is a canonical exact-identification target, and
DML, LRO, and ADML are three leading ways to build orthogonal inference for it.
Under fixed overlap and fast nuisance learning, the three routes are usually
treated as first-order interchangeable.  Weak overlap challenges that practice:
the inverse propensity/Riesz representer can grow with \(n\), so a point
estimator comparison can be silent precisely when the variance estimator and
Wald interval are doing the inferential work.

\paragraph{The main finding (proposed).}
The headline conjecture is that studentization has a sharper uniform frontier
than point-estimator equivalence.  Let \(V_n=\operatorname{Var}_P(\psi_0(W))\)
be the ATE EIF variance, let \(S_n\) be the covariance kernel of the
estimator-specific variance-correction residuals \(h_{m,n}\), and write
\(\lambda_{\min}^+(S_n)\asymp n^{-2\zeta}\).  In the local weak-overlap
experiment with \(V_n\asymp n^\omega\), the conjectured boundary is
\[
  r_g+r_\alpha+\zeta > \rho_{\mathrm{stud}}(\omega)
  \qquad\text{where}\qquad
  \rho_{\mathrm{stud}}(\omega)=\frac{1+\omega}{2}.
\]
Above the boundary, the studentized statistics
\(\widehat T_m=\sqrt n(\widehat\theta_m-\theta_0)/\widehat V_m^{1/2}\) are
uniformly pairwise equivalent.  At and below the boundary, the point estimates
can still be equivalent after \(V_n\)-normalization, but the variance
estimators either have finite nonzero pairwise local limits on boundary
alternatives or diverging unscaled gaps strictly below the boundary; in the
active residual Riesz direction the ordering is DML most fragile, LRO
intermediate, and ADML least fragile.

\paragraph{What is new.}
\citet{ChernozhukovEtAl2018DML} gives product-rate DML inference,
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} gives a general
locally robust moment construction, and
\citet{ChernozhukovNeweySingh2022ADML} gives ADML with
misspecification-robust standard errors.  The epsilon-gap is not another proof
of asymptotic normality for one estimator: it is a necessary-and-sufficient
comparison of the three named studentized statistics over a local weak-overlap
sequence in which the point estimates may already agree.  The closest
weak-overlap inference papers, \citet{Dorn2025WeakOverlapTStats},
\citet{Rothe2017LimitedOverlapCI}, \citet{ArmstrongKolesar2021ATE}, and
\citet{HeilerKazak2021ExtremePS}, study robust ATE confidence intervals,
doubly robust \(t\)-statistics, and irregular propensity-score limits.
\citet{MaSantAnnaSasakiUra2026WeakOverlapDR} is especially close because it
constructs trimmed, bias-corrected doubly robust estimators for weak overlap,
but it changes the estimator class rather than giving an iff frontier for the
three fixed DML/LRO/ADML studentizations under one common EIF normalization.

\paragraph{How it positions in the literature.}
The anchor cluster is ExactID semiparametric ATE.  The proposal takes the
standard SWIG/DAG identification formula as given and studies the inferential
frontier induced by nuisance estimation and local overlap.  It is adjacent to
the DML product-rate literature, LRO semiparametric GMM, ADML/Riesz
debiasing, and the weak-overlap support-condition literature.

\paragraph{Implications for the community.}
The concrete downstream consumer is empirical work using the ADML robust
standard errors of \citet{ChernozhukovNeweySingh2022ADML} or the software
practice surveyed by \citet{AhrensHansenSchafferWiemann2024DDML}: the proposal
would supply a diagnostic for when the original DML standard error is
uniformly interchangeable with the ADML Riesz variance and when the latter is
the relevant weak-overlap safeguard.

\paragraph{How research benefits from the conclusion.}
If the conjecture resolves favorably, researchers should check and report the
studentization gap kernel \(S_n\) before treating DML, LRO, and ADML Wald
intervals as equivalent.

\section{Related work}
\citet{ChernozhukovEtAl2018DML} is the baseline DML source: it gives
cross-fitted orthogonal-score ATE inference under nuisance product-rate and
overlap conditions, but does not compare studentized DML to LRO or ADML under
weak overlap.
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} constructs locally
robust semiparametric moments; here it is the LRO comparator whose sandwich
variance may omit or retain residual Riesz directions depending on the chosen
ATE moment and Jacobian normalization.
\citet{ChernozhukovNeweySingh2022ADML} develops ADML for causal and structural
effects and introduces misspecification-robust standard errors; this proposal
tests whether that robust studentization is uniformly equivalent to the older
DML and LRO standard errors.
\citet{ChernozhukovNeweySingh2022RR} provides the regularized Riesz framework
for global and local functionals, making it the closest source for the
Riesz-instability channel behind \(S_n\).
\citet{ChernozhukovNeweyQuintasMartinezSyrgkanis2022RieszNet} gives neural-net
and forest Riesz learners, showing that the automatic Riesz route is not a
purely abstract construction but a practical estimator family whose variance
diagnostics matter.
\citet{ChernozhukovNeweyQuintasMartinezSyrgkanis2024RieszRegression} studies
automatic debiasing through Riesz regression; it supplies a close ADML
implementation thread but not a three-estimator weak-overlap studentization
frontier.
\citet{CrumpHotzImbensMitnik2009Overlap} develops optimal trimming for limited
overlap, identifying the practical problem of imprecise ATE estimation under
thin propensity support that this proposal turns into a local studentization
comparison.
\citet{Dorn2025WeakOverlapTStats} gives the closest weak-overlap
doubly robust \(t\)-statistic result: thresholded AIPW can retain calibrated
Wald inference under weak overlap, but the paper does not compare the DML,
LRO, and ADML variance channels.
\citet{MaSantAnnaSasakiUra2026WeakOverlapDR} is the closest weak-overlap DR
estimator paper: it shows that trimming extreme propensity scores requires a
bias correction to retain double robustness, whereas this proposal keeps the
three named DML/LRO/ADML estimators fixed and asks when their studentizations
are equivalent or separated.
\citet{Rothe2017LimitedOverlapCI} shows that limited overlap can distort
traditional ATE confidence intervals because local sample sizes drive coverage
error; this proposal asks which of three orthogonal studentizations absorbs
that problem.
\citet{ArmstrongKolesar2021ATE} derives finite-sample optimal ATE confidence
intervals under unconfoundedness and allows valid inference when root-\(n\)
inference fails, but it is an optimal-CI result rather than a DML/LRO/ADML
equivalence frontier.
\citet{HeilerKazak2021ExtremePS} studies IPW and doubly robust inference with
many extreme propensity scores and alpha-stable limits; the present proposal
keeps the three named orthogonal estimators fixed and asks when their
studentized laws separate.
\citet{KhanTamer2010Irregular} proves that inverse-weight estimators can be
irregular without strong support conditions; it is the closest econometric
warning that point identification need not imply regular inference, but it does
not distinguish DML, LRO, and ADML standard-error routes.
\citet{PetersenPorterGruberWangVanDerLaan2012Positivity} treats positivity
violations as an inferential diagnostic problem; the proposed \(S_n\) is meant
to be the DML/Riesz analogue of such diagnostics.
\citet{VanDerLaanLuedtkeCarone2024CDML} gives calibrated DML with doubly robust
asymptotic linearity when one nuisance is slow or inconsistent, making it a
nearby one-slow-nuisance result rather than a comparison of the three named
studentized statistics.
\citet{Velez2024DML} separates DML1 and DML2 when the number of cross-fitting
folds grows; it is a different estimator-frontier problem because the present
proposal fixes the original DML construction and compares it with LRO and
ADML under weak overlap.
The ThmSmith in-catalogue ExactID/PartialID section of \texttt{doc/API.md}
states that \texttt{ThmSmith/ExactID} is empty at seed time; hence there is no
active exact-ID ThmSmith proposal whose kernel duplicates this DML/LRO/ADML
studentization question.  The closest archived project analogue is
\texttt{eid\_bjs\_efficient\_event\_study}, an estimator-frontier proposal for
staggered event studies, but its reviewer asked for EIF-baseline
normalization in a panel design rather than an ATE weak-overlap
studentization kernel.

\section{Formal setup}
Let \(W=(Y,D,X)\) be observed data, \(D\in\{0,1\}\), and \(Y=DY(1)+(1-D)Y(0)\).
The DAG/SWIG is \(X\to D\to Y\) and \(X\to Y\).  The target is
\(\theta_0=\E[Y(1)-Y(0)]\).  Write
\[
  p_0(x)=\Pr(D=1\mid X=x),\quad
  g_{d,0}(x)=\E[Y\mid D=d,X=x],\quad
  \tau_0(x)=g_{1,0}(x)-g_{0,0}(x),
\]
\[
  \alpha_0(W)=\frac{D}{p_0(X)}-\frac{1-D}{1-p_0(X)},\quad
  \varepsilon_0(W)=Y-g_{D,0}(X),
\]
and define the normalized ATE efficient influence function
\[
  \psi_0(W)=\tau_0(X)-\theta_0+\alpha_0(W)\varepsilon_0(W),\qquad
  V_n=\E[\psi_0(W)^2].
\]
For \(m\in\{D,L,A\}\), let \(\widehat\theta_m\) denote the DML, LRO, and ADML
point estimators, and let \(\widehat V_m\) denote their associated
estimator-specific variance estimators.  The studentized statistics are
\(\widehat T_m=\sqrt n(\widehat\theta_m-\theta_0)/\widehat V_m^{1/2}\).
The LRO member is locked to the ATE moment \(\varphi_L\), scalar Jacobian
\(J_L=1\), and sandwich variance
\(\widehat V_L=\widehat J_L^{-1}\widehat\Omega_L\widehat J_L^{-1}\) with
\(\widehat\Omega_L\) the cross-fitted empirical variance of the locally robust
ATE moment plus the first-step influence adjustment of
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}.
The local weak-overlap sequence has a propensity floor
\(\ell_n=n^{-\omega}\), \(0\le\omega<1\), and \(V_n\asymp n^\omega\).

The variance-score construction is locked as follows.  Each variance estimator
is written as a cross-fitted sample average
\(\widehat V_m=\mathbb P_n\widehat v_{m,n}\): for DML,
\(\widehat v_{D,n}=\widehat\psi_D^2\), with
\[
  \widehat\psi_D(W_i)=
  \widehat g_1(X_i)-\widehat g_0(X_i)-\widehat\theta_D
  +\widehat\alpha(W_i)\{Y_i-\widehat g_{D_i}(X_i)\},
\]
the squared DML AIPW score; for LRO,
\(\widehat v_{L,n}=\widehat\chi_L^2\), where \(\widehat\chi_L\) is the
locally robust ATE moment plus its published first-step influence adjustment
under \(J_L=1\); and for ADML,
\(\widehat v_{A,n}=\widehat\chi_A^2+\widehat\kappa_A\), where
\(\widehat\chi_A\) is the ADML Riesz score for the ATE functional and
\(\widehat\kappa_A\) is the ADML robust-variance augmentation.  This is the
misspecification-robust Riesz variance summand of
\citet{ChernozhukovNeweySingh2022ADML}, including its robust correction
\(\widehat\kappa_A\).  Let \(v_{m,n}\) be the population limit of
\(\widehat v_{m,n}\) along the local sequence.  If
\(\Delta_{g,n}\) and \(\Delta_{\alpha,n}\) are the normalized local
outcome-regression and propensity/Riesz perturbation directions, define
\[
  h_{m,n}(W)=
  \frac{\dot v_{m,n}[\Delta_{g,n},\Delta_{\alpha,n}](W)
        -\E[\dot v_{m,n}[\Delta_{g,n},\Delta_{\alpha,n}](W)]}
       {V_n},
  \qquad m\in\{D,L,A\},
\]
where \(\dot v_{m,n}\) is the Gateaux derivative of the named variance
summand \(v_{m,n}\) in the two nuisance directions.  The sample plug-in
diagnostic used by the conjecture is
\[
  \widehat S_n=
  \mathbb P_n\left[
     \begin{pmatrix}\widehat\Delta v_{D A,i}\\
                    \widehat\Delta v_{L A,i}\end{pmatrix}
     \begin{pmatrix}\widehat\Delta v_{D A,i}&
                    \widehat\Delta v_{L A,i}\end{pmatrix}
  \right],
\]
where
\[
  \widehat\Delta v_{m A,i}
  =
  \frac{\widehat v_{m,n}(W_i)/\widehat V_m
        -\widehat v_{A,n}(W_i)/\widehat V_A
        -\mathbb P_n(\widehat v_{m,n}/\widehat V_m
        -\widehat v_{A,n}/\widehat V_A)}
       {\widehat a_n},\qquad m\in\{D,L\}.
\]
Here \(\widehat a_n\) is any rate-consistent plug-in for
\(a_n=n^{(1+\omega)/2-r_g-r_\alpha}\); the population statements below use
the deterministic \(a_n\).
Thus \(S_n\) is the population target of a computable pairwise variance-score
contrast, not an abstract unanchored residual.  With
\(\mathbb G_n f=n^{-1/2}\sum_{i=1}^n(f(W_i)-\E f(W))\), the pairwise local
limits are carried by \(\mathbb G_n(h_{m,n}-h_{A,n})\).  The kernel
\[
  S_n=\E\left[
     \begin{pmatrix}h_{D,n}-h_{A,n}\\ h_{L,n}-h_{A,n}\end{pmatrix}
     \begin{pmatrix}h_{D,n}-h_{A,n}& h_{L,n}-h_{A,n}\end{pmatrix}
  \right]
\]
has smallest nonzero eigenvalue \(\lambda_{\min}^+(S_n)\) when nonzero.  The
zero-kernel convention is \(\lambda_{\min}^+(S_n)=0\), \(\zeta=+\infty\), and
no active pairwise gap.  The active singular values \(s_{DA,n}\) and
\(s_{LA,n}\) denote the standard deviations of
\(\mathbb G_n(h_{D,n}-h_{A,n})\) and \(\mathbb G_n(h_{L,n}-h_{A,n})\).
Define the studentization boundary shorthand
\(\rho_{\mathrm{stud}}(\omega)=(1+\omega)/2\).  For
\(m\in\{D,L\}\), \(Z_{mA}^\circ\) denotes the standardized centered Gaussian
local-limit variable for the active empirical-process contrast
\(\mathbb G_n(h_{m,n}-h_{A,n})/s_{mA,n}\); its variance is one whenever the
active singular value is positive.  The tangent-cone studentization risk is
the boundary local-limit expected absolute separation from the ADML
studentizer:
\[
  \mathfrak R_A^{\mathrm{tc}}=0,\qquad
  \mathfrak R_m^{\mathrm{tc}}
  =
  \lim_{\gamma_{mA,n}\to c_{mA}\in(0,\infty)}
  \E\!\left[|\widehat T_m-\widehat T_A|\right]
  =
  c_{mA}\E|Z_{mA}^\circ|,\quad m\in\{D,L\},
\]
whenever the displayed limit exists along the local sequence.  For
strict-below-boundary alternatives with \(\gamma_{mA,n}\to\infty\), the
associated scale risk is the coefficient of divergence,
\[
  \mathfrak r_m^{\mathrm{tc}}
  =
  \lim \E\!\left[
    \frac{|\widehat T_m-\widehat T_A|}{\gamma_{mA,n}}
  \right]
  =
  \E|Z_{mA}^\circ|,\quad m\in\{D,L\},
\]
with ADML again normalized to zero as the reference studentizer.

\begin{quote}
\begin{verbatim}
Locked parameters:
qid = eid_dml_orth_uniform
specialization = v1
SWIG/DAG = X -> D -> Y and X -> Y
treatment = binary D
target estimand = theta_0 = E[Y(1)-Y(0)]
identifying assumptions = consistency, unconfoundedness,
  local weak overlap ell_n <= p_0(X) <= 1-ell_n with ell_n=n^{-omega},
  the LRO comparator is the ATE moment varphi_L with J_L=1 sandwich variance,
  and Assumptions 1--5 in the proposal.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Exact ATE identification]\label{ass:eif}
Consistency holds, \((Y(1),Y(0))\perp D\mid X\), and the local weak-overlap
bound \(\ell_n\le p_0(X)\le 1-\ell_n\) holds with
\(\ell_n=n^{-\omega}\) and \(0\le\omega<1\).  The second moments defining
\(\theta_0\), \(\psi_0\), and \(V_n\) are finite for each \(n\), and
\(V_n\asymp n^\omega\).
\end{assumption}

\begin{assumption}[Common EIF normalization]\label{ass:normalization}
The three estimators admit cross-fitted asymptotic expansions around the same
\(\psi_0\):
\[
  \widehat\theta_m-\theta_0
  = n^{-1}\sum_{i=1}^n \psi_0(W_i)+R_{m,n},\qquad m\in\{D,L,A\}.
\]
All estimator-specific differences are therefore carried by the remainders
\(R_{m,n}\) and by the variance-estimator residuals \(h_{m,n}\), not by
changing the target EIF.
\end{assumption}

\begin{assumption}[Nuisance rates]\label{ass:rates}
The cross-fitted outcome-regression error satisfies
\(\|\widehat g-g_0\|_{2,n}=O_P(n^{-r_g})\), and the propensity/Riesz error
satisfies \(\|\widehat\alpha-\alpha_0\|_{2,n}=O_P(n^{-r_\alpha})\).  The same
rates govern the LRO and ADML nuisance channels after their estimator-specific
projections are expressed on the common EIF scale.
\end{assumption}

\begin{assumption}[Point-equivalence window]\label{ass:point-window}
The nuisance rates satisfy the point-equivalence inequality
\[
  r_g+r_\alpha>\frac{1-\omega}{2}.
\]
Under this condition,
\(\max_{m,m'}\sqrt{n/V_n}\,|\widehat\theta_m-\widehat\theta_{m'}|=o_P(1)\).
\end{assumption}

\begin{assumption}[Studentization gap kernel]\label{ass:student-kernel}
Let \(a_n=n^{(1+\omega)/2-r_g-r_\alpha}\).  The variance-score summands
\(\widehat v_{D,n}\), \(\widehat v_{L,n}\), and \(\widehat v_{A,n}\) are the
locked summands from Section 3, and \(h_{m,n}\) is their centered Gateaux
derivative channel in the local nuisance directions.  There is a centered
square-integrable common score \(q_{0,n}\) such that the variance estimators
have the joint stochastic expansion
\[
  \frac{\widehat V_m}{V_n}-1
  = n^{-1}\sum_{i=1}^n q_{0,n}(W_i)
    +a_n\,\mathbb G_n h_{m,n}+b_{m,n}+o_P(a_n),
  \qquad m\in\{D,L,A\},
\]
where \(b_{m,n}\) is a deterministic local drift and the common empirical
component \(q_{0,n}\) is the same for \(m=D,L,A\).  Pairwise drifts satisfy
\(b_{D,n}-b_{A,n}=o(a_n s_{DA,n})\) and
\(b_{L,n}-b_{A,n}=o(a_n s_{LA,n})\) whenever the corresponding active singular
value is positive.  The two-dimensional kernel \(S_n\) defined in Section 3 is
the covariance matrix of
\((\mathbb G_n(h_{D,n}-h_{A,n}),\mathbb G_n(h_{L,n}-h_{A,n}))\).  If
\(S_n\ne0\), then \(\lambda_{\min}^+(S_n)\asymp n^{-2\zeta}\); if \(S_n=0\),
the zero-kernel convention from Section 3 applies.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: fixed-overlap common-EIF sanity collapse]\label{thm:common-eif}
Under Assumptions \ref{ass:eif}--\ref{ass:student-kernel} with \(\omega=0\)
and \(r_g+r_\alpha>1/2\), if the variance residuals coincide
\(h_{D,n}=h_{L,n}=h_{A,n}\) in \(L^2(P)\) and
\(b_{D,n}=b_{L,n}=b_{A,n}\), then
\[
  \max_{m,m'\in\{D,L,A\}}
  \left|\widehat T_m-\widehat T_{m'}\right|=o_P(1).
\]
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is explicitly not the flagship novelty claim; it is the
known sanity anchor from \citet{ChernozhukovEtAl2018DML},
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}, and
\citet{ChernozhukovNeweySingh2022ADML}, restated only after pinning the common
EIF and the locked LRO sandwich normalization.  (b) It is useful because it
keeps the proposed weak-overlap result from contradicting the ADML
standard-error practice in \citet{ChernozhukovNeweySingh2022ADML} in the
well-overlapped equal-channel regime.

\begin{conjecture}[Conjecture 1: weak-overlap studentization frontier (NOT YET PROVED)]\label{conj:student-frontier}
Under Assumptions \ref{ass:eif}--\ref{ass:student-kernel}, suppose
\(S_n\ne0\) and \(\lambda_{\min}^+(S_n)\asymp n^{-2\zeta}\).  Then the
following are equivalent:
\[
  \max_{m\in\{D,L\}}|\widehat T_m-\widehat T_A|=o_P(1)
  \quad\Longleftrightarrow\quad
  r_g+r_\alpha+\zeta>\rho_{\mathrm{stud}}(\omega)=\frac{1+\omega}{2}.
\]
If \(r_g+r_\alpha+\zeta\le (1+\omega)/2\) and \(s_{mA,n}>0\), there exist
nondegenerate local weak-overlap DGP sequences satisfying the point-equivalence
window of Assumption \ref{ass:point-window} and the drift restriction in
Assumption \ref{ass:student-kernel}.  Write
\(\gamma_{mA,n}=a_n s_{mA,n}\).  On boundary/local alternatives with
\(\gamma_{mA,n}\to c_{mA}\in(0,\infty)\),
\[
  |\widehat T_m-\widehat T_A|
  \Rightarrow
  c_{mA}|Z_{mA}^\circ|,\qquad
  \operatorname{Var}(Z_{mA}^\circ)=1.
\]
On strict-below-boundary alternatives with
\(\gamma_{mA,n}\to\infty\),
\[
  \frac{|\widehat T_m-\widehat T_A|}{\gamma_{mA,n}}
  \Rightarrow |Z_{mA}^\circ|,
  \qquad
  |\widehat T_m-\widehat T_A|\to\infty \text{ in probability}.
\]
In boundary residual Riesz directions where both \(s_{DA,n}\) and
\(s_{LA,n}\) are active and
\(\gamma_{DA,n}\to c_{DA}>\gamma_{LA,n}\to c_{LA}>0\), the tangent-cone
studentization risk defined in Section 3 is strictly ordered
\[
  \mathfrak R_D^{\mathrm{tc}}>
  \mathfrak R_L^{\mathrm{tc}}>
  \mathfrak R_A^{\mathrm{tc}}=0.
\]
Strictly below the boundary, the unscaled DML and LRO gaps both diverge when
active, while their divergence coefficients are compared by
\(\gamma_{DA,n}/\gamma_{LA,n}\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest papers are \citet{Dorn2025WeakOverlapTStats}, which studies
how much weak overlap doubly robust \(t\)-statistics can tolerate,
\citet{MaSantAnnaSasakiUra2026WeakOverlapDR}, which gives bias-corrected
trimmed DR estimators under weak overlap, \citet{Rothe2017LimitedOverlapCI},
which gives robust CIs under limited overlap,
\citet{ArmstrongKolesar2021ATE}, which gives optimal CIs when root-\(n\)
inference may fail, and \citet{HeilerKazak2021ExtremePS}, which derives
nonstandard limits under many extreme propensity scores.  None gives an iff
boundary where the three named DML/LRO/ADML point estimates are equivalent but
their studentized statistics separate through the computable variance-score
kernel \(S_n\).
(b) Resolving this conjecture would give users of ADML standard errors and
\texttt{ddml}-style DML implementations a named diagnostic: estimate \(S_n\)
and report whether the Wald interval is in the common-studentization or
ADML-favored weak-overlap regime.

\begin{conjecture}[Conjecture 2: finite-support nonvacuity witness (NOT YET PROVED)]\label{conj:witness}
There is a three-point covariate support
\(\mathcal X=\{x_0,x_1,x_2\}\), with cell probabilities bounded away from zero,
propensity values
\[
  p_0(x_0)=\ell_n,\qquad p_0(x_1)=1/2,\qquad p_0(x_2)=1-\ell_n,
\]
and residual variances positive in both treatment arms at each support point,
such that Assumptions \ref{ass:eif}--\ref{ass:student-kernel} hold,
\(\lambda_{\min}^+(S_n)>0\), \(s_{DA,n}>s_{LA,n}>0\), and the strict
DML \(>\) LRO \(>\) ADML studentization ordering in Conjecture
\ref{conj:student-frontier} persists on an open neighborhood of the cell
probabilities and residual variances.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) Prior ThmSmith non-equivalence proposals were weakened when the strict
gap was placed directly into an assumption; this conjecture demands a
primitive finite-support witness instead.  The closest published algebraic
equivalence paper, \citet{BrunsSmithDukesFellerOgburn2024ABW}, studies
augmented balancing/AutoDML equivalences in linear models, not a primitive
weak-overlap witness for three different studentizations.  (b) The concrete
consumer is the diagnostic workflow of \citet{PetersenPorterGruberWangVanDerLaan2012Positivity}:
the witness would show that the proposed \(S_n\) check is not vacuous and can
flag real positivity-driven interval separation.

\section{Sanity-check corollaries}
\begin{corollary}[Fixed strong overlap and equal variance channels]\label{cor:fixed-overlap}
Under Assumptions \ref{ass:eif}--\ref{ass:student-kernel}, if
\(\omega=0\), \(r_g+r_\alpha>1/2\),
\(h_{D,n}=h_{L,n}=h_{A,n}\) in \(L^2(P)\), and
\(b_{D,n}=b_{L,n}=b_{A,n}\), then \(S_n=0\).  By the zero-kernel convention
\(\lambda_{\min}^+(S_n)=0\), \(\zeta=+\infty\), and there is no active pairwise
gap, so the studentization claim reduces to Theorem \ref{thm:common-eif}
rather than to the nonzero-kernel branch of Conjecture
\ref{conj:student-frontier}.
\end{corollary}

\begin{corollary}[Point-equivalence but not interval-equivalence window]\label{cor:window}
If \(0<\omega<1\) and
\[
  \frac{1-\omega}{2}<r_g+r_\alpha\le \frac{1+\omega}{2}-\zeta,
\]
then Assumption \ref{ass:point-window} permits normalized point-estimator
equivalence while Conjecture \ref{conj:student-frontier} predicts a
nonvanishing studentization gap whenever \(S_n\) has an active pairwise
eigen-direction.
\end{corollary}

\section{Proof-sketch route}
The proof route is classical semiparametric expansion plus a finite-dimensional
local experiment.  First, put DML, LRO, and ADML on the same ATE EIF scale and
separate the point-estimator remainders from the variance-estimator
remainders.  Second, in the weak-overlap sequence, compute the order of
\(V_n\), of the product nuisance remainder, and of the linearized
studentization terms; this should yield the two competing inequalities
\((1-\omega)/2\) for point equivalence and \((1+\omega)/2-\zeta\) for
studentization equivalence.  Third, diagonalize the two-dimensional
studentization gap kernel \(S_n\) and reduce strict pairwise separation to the
active singular values \(s_{DA,n}\) and \(s_{LA,n}\), with a separate local
limit calculation for \(\gamma_{mA,n}\to c\in(0,\infty)\) and a rescaled
divergence calculation for \(\gamma_{mA,n}\to\infty\).  Finally, verify
Conjecture \ref{conj:witness} by direct three-support enumeration of
propensity cells, residual variances, and the DML/LRO/ADML variance-score
summands; this is the boundary case that should expose any missing
normalization.

\section{Honest scope flags}
Theorem \ref{thm:common-eif} is intended as a routine collapse of known
orthogonal-score expansions under strong overlap and equal variance channels.
Conjectures \ref{conj:student-frontier} and \ref{conj:witness} are not yet
proved and are the actual research kernel.  The proposed boundary assumes that
the linearized variance residuals \(h_{m,n}\) can be defined on one common
scale; this revision locks LRO to the ATE moment, scalar Jacobian, and
sandwich normalization in the locked parameters rather than comparing all
possible LRO moments.  No claim is made that ADML always
dominates DML in point-estimator risk; the strict ordering is only for
the tangent-cone studentization risk defined in Section 3 along active
weak-overlap residual Riesz directions.
The plug-in \(\widehat S_n\) is proposed as a diagnostic target derived from
the three named variance estimators; its sampling accuracy is not asserted
outside the same local expansion and rate conditions used in Conjecture
\ref{conj:student-frontier}.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the structurally new weak-overlap
studentization angle; prior verdict: none.
\item v2 (revise) -- added weak-overlap inference prior art, locked the LRO
ATE sandwich object, rewrote the studentization expansion, and added the
zero-kernel convention; prior verdict: REVISE.
\item v3 (revise) -- fixed Conjecture 1's scaling convention by treating
\(s_{mA,n}\) as the standard deviation of the active empirical-process
loading and removing the duplicate \(\lambda_{\min}^+(S_n)\) variance factor;
prior verdict: REVISE.
\item v4 (revise) -- added Ma--Sant'Anna--Sasaki--Ura weak-overlap DR prior
art, split Conjecture 1 into finite-boundary and divergent-below-boundary
regimes, and defined \(h_{D,n}\), \(h_{L,n}\), \(h_{A,n}\), \(S_n\), and
\(\widehat S_n\) from the named variance estimators; prior verdict: REVISE.
\item v5 (revise) -- defined tangent-cone studentization risk as the
boundary expected absolute ADML-reference separation and restated the
DML/LRO/ADML ordering in that metric; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Ahrens et~al.(2024)]{AhrensHansenSchafferWiemann2024DDML}
Ahrens, A., C.~B. Hansen, M.~E. Schaffer, and T.~Wiemann (2024).
\newblock \textit{ddml: Double/debiased machine learning in Stata}.
\newblock The Stata Journal 24, 3--45.

\bibitem[Bruns-Smith et~al.(2024)]{BrunsSmithDukesFellerOgburn2024ABW}
Bruns-Smith, D., O.~Dukes, A.~Feller, and E.~L. Ogburn (2024).
\newblock \textit{Augmented balancing weights as linear regression}.
\newblock arXiv:2304.14545.

\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., D.~Chetverikov, M.~Demirer, E.~Duflo, C.~Hansen,
W.~Newey, and J.~Robins (2018).
\newblock Double/debiased machine learning for treatment and structural parameters.
\newblock \textit{The Econometrics Journal} 21(1), C1--C68.

\bibitem[Chernozhukov et~al.(2022a)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
Chernozhukov, V., J.~C. Escanciano, H.~Ichimura, W.~K. Newey, and J.~M. Robins (2022).
\newblock Locally robust semiparametric estimation.
\newblock \textit{Econometrica} 90(4), 1501--1535.

\bibitem[Chernozhukov et~al.(2022b)]{ChernozhukovNeweySingh2022ADML}
Chernozhukov, V., W.~K. Newey, and R.~Singh (2022).
\newblock Automatic debiased machine learning of causal and structural effects.
\newblock \textit{Econometrica} 90(3), 967--1027.

\bibitem[Chernozhukov et~al.(2022c)]{ChernozhukovNeweySingh2022RR}
Chernozhukov, V., W.~K. Newey, and R.~Singh (2022).
\newblock Debiased machine learning of global and local parameters using regularized Riesz representers.
\newblock \textit{The Econometrics Journal} 25(3), 576--601.

\bibitem[Chernozhukov et~al.(2022d)]{ChernozhukovNeweyQuintasMartinezSyrgkanis2022RieszNet}
Chernozhukov, V., W.~Newey, V.~Quintas-Martinez, and V.~Syrgkanis (2022).
\newblock RieszNet and ForestRiesz: Automatic debiased machine learning with neural nets and random forests.
\newblock \textit{Proceedings of Machine Learning Research} 162, 3901--3914.

\bibitem[Chernozhukov et~al.(2024)]{ChernozhukovNeweyQuintasMartinezSyrgkanis2024RieszRegression}
Chernozhukov, V., W.~Newey, V.~Quintas-Martinez, and V.~Syrgkanis (2024).
\newblock Automatic debiased machine learning via Riesz regression.
\newblock arXiv:2104.14737.

\bibitem[Crump et~al.(2009)]{CrumpHotzImbensMitnik2009Overlap}
Crump, R.~K., V.~J. Hotz, G.~W. Imbens, and O.~A. Mitnik (2009).
\newblock Dealing with limited overlap in estimation of average treatment effects.
\newblock \textit{Biometrika} 96(1), 187--199.

\bibitem[Dorn(2025)]{Dorn2025WeakOverlapTStats}
Dorn, J. (2025).
\newblock How much weak overlap can doubly robust t-statistics handle?
\newblock arXiv:2504.13273.

\bibitem[Armstrong and Kolesar(2021)]{ArmstrongKolesar2021ATE}
Armstrong, T.~B. and M.~Kolesar (2021).
\newblock Finite-sample optimal estimation and inference on average treatment effects under unconfoundedness.
\newblock \textit{Econometrica} 89(3), 1141--1177.

\bibitem[Heiler and Kazak(2021)]{HeilerKazak2021ExtremePS}
Heiler, P. and E.~Kazak (2021).
\newblock Valid inference for treatment effect parameters under irregular identification and many extreme propensity scores.
\newblock \textit{Journal of Econometrics} 222(2), 1083--1108.

\bibitem[Khan and Tamer(2010)]{KhanTamer2010Irregular}
Khan, S. and E.~Tamer (2010).
\newblock Irregular identification, support conditions, and inverse weight estimation.
\newblock \textit{Econometrica} 78(6), 2021--2042.

\bibitem[Ma et~al.(2026)]{MaSantAnnaSasakiUra2026WeakOverlapDR}
Ma, Y., P.~H.~C. Sant'Anna, Y.~Sasaki, and T.~Ura (2026).
\newblock Doubly robust estimators with weak overlap.
\newblock arXiv:2304.08974, revised April 2026.

\bibitem[Petersen et~al.(2012)]{PetersenPorterGruberWangVanDerLaan2012Positivity}
Petersen, M.~L., K.~E. Porter, S.~Gruber, Y.~Wang, and M.~J. van~der Laan (2012).
\newblock Diagnosing and responding to violations in the positivity assumption.
\newblock \textit{Statistical Methods in Medical Research} 21(1), 31--54.

\bibitem[Rothe(2017)]{Rothe2017LimitedOverlapCI}
Rothe, C. (2017).
\newblock Robust confidence intervals for average treatment effects under limited overlap.
\newblock \textit{Econometrica} 85(2), 645--660.

\bibitem[van der Laan et~al.(2024)]{VanDerLaanLuedtkeCarone2024CDML}
van der Laan, L., A.~Luedtke, and M.~Carone (2024).
\newblock Automatic doubly robust inference for linear functionals via calibrated debiased machine learning.
\newblock arXiv:2411.02771.

\bibitem[Velez(2026)]{Velez2024DML}
Velez, A. (2026).
\newblock On the asymptotic properties of debiased machine learning estimators.
\newblock Working paper, Cornell University.
\end{thebibliography}

\end{document}
