\begin{theorem}[Conjecture 1: studentization frontier]\label{thm:student-frontier}
Under Assumptions~\ref{ass:exact-ate}--\ref{ass:kernel-observable}, including the standardized EIF central limit condition in Assumption~\ref{ass:eif-clt}, the centered point estimators are uniformly equivalent:
\[
  \max_{m,m'\in\mathcal M}|Z_{m,n}-Z_{m',n}|\to_p0.
\]
For any \(m,m'\in\mathcal M\), their studentized statistics are asymptotically equivalent,
\[
  T_{m,n}-T_{m',n}\to_p0,
\]
if and only if
\[
  \Delta_{m,n}-\Delta_{m',n}\to0.
\]
If \(\Delta_{m,n}\to\delta_m\) and \(\Delta_{m',n}\to\delta_{m'}\) with \(\delta_m\ne\delta_{m'}\), then the studentized statistics have different scale limits:
\[
  T_{m,n}\Rightarrow N(0,(1+\delta_m)^{-1}),\qquad
  T_{m',n}\Rightarrow N(0,(1+\delta_{m'})^{-1}),
\]
even though their centered point estimates share the same \(N(0,1)\) limit after normalization by \(V_n^{1/2}\).  In the canonical ordering where ADML absorbs the full weak-overlap Riesz direction and DML/LRO leave progressively larger residual projections, \(\delta_{\mathrm{ADML}}=0<\delta_{\mathrm{LRO}}<\delta_{\mathrm{DML}}\), so Wald intervals separate first through studentization, not through the point estimate.  Moreover, a single estimator \(m\) has ratio-consistent studentization relative to the efficient variance \(V_n\) if and only if \(\Delta_{m,n}\to0\).
\end{theorem}

\paragraph{Front-loaded refutation attempt.}
The smallest exact-ID search space for this conjecture is the three-node
back-door SWIG with \(X\), \(D\), and \(Y\), finite \(X\)-support, binary
treatment, consistency, conditional exchangeability, and local overlap
\(\kappa_n\le e_n(X)\le1-\kappa_n\).  In that search space the causal
identifying formula is fixed by Assumption~\ref{ass:exact-ate}; possible
refutations must therefore come from the statistic layer, not from a failure
of back-door identification.

The first candidate witness is a finite-support weak-overlap law with one
small-propensity cell.  Assumption~\ref{ass:common-eif} rules out a centered
point-estimator witness, because for every \(m,m'\in\mathcal M\),
\[
  Z_{m,n}-Z_{m',n}
  =
  \frac{R_{m,n}-R_{m',n}}{V_n^{1/2}}
  =o_p(1).
\]
The second candidate witness tries to make studentized statistics agree while
the projection indices differ.  Writing
\[
  b_{m,n}=(1+\Delta_{m,n})^{-1/2},
\]
Assumption~\ref{ass:variance-linear} reduces any such witness to the scalar
condition
\[
  \{b_{m,n}-b_{m',n}\}
  V_n^{-1/2}n^{-1/2}\sum_{i=1}^n\psi_n(W_i)\to_p0
\]
while \(\Delta_{m,n}-\Delta_{m',n}\not\to0\).  This cannot occur inside the
stated projection-index regime.  Indeed, the projection definition gives
\[
  0\le \Delta_{m,n}
  =
  \frac{\|(I-\Pi_{m,n})\alpha_n\|_{K_n}^2}{V_n}
  \le
  \frac{\|\alpha_n\|_{K_n}^2}{V_n}
  =
  \frac{L_n^2}{V_n}
  =O(1)
\]
by Assumption~\ref{ass:local-overlap}.  On any bounded interval the map
\(d\mapsto(1+d)^{-1/2}\) is one-to-one with continuous inverse.  Hence no
bounded finite-support witness can have \(b_{m,n}-b_{m',n}\to0\) but
\(\Delta_{m,n}-\Delta_{m',n}\not\to0\).  The tempting divergent-index
construction \((\Delta_{m,n},\Delta_{m',n})=(n,2n)\) would break the
``only if'' direction algebraically, but it is outside the conjecture's own
projection-index support bound because \(\Delta_{m,n}\le L_n^2/V_n=O(1)\).
Thus the mandated refutation attempt finds no witness under
Assumptions~\ref{ass:exact-ate}--\ref{ass:kernel-observable}.

\paragraph{Interpretation.}
The theorem separates two layers of weak-overlap behavior.  The point
estimators remain first-order equivalent after the common efficient
standard-deviation normalization because all three estimators have the same
efficient influence-function expansion.  Studentization depends on a different
object: the observable residual projection index \(\Delta_{m,n}\) attached to
the variance rule.  Equal limiting projection loss gives equal Wald scaling;
unequal finite projection losses give distinct Gaussian scale limits even
though the centered numerators share the same limit.

The last clause is the ratio-consistency special case.  A variance rule is
studentized as if it used the efficient variance \(V_n\) exactly when its
reported variance is first-order ratio-consistent for \(V_n\), and under the
linearization in Assumption~\ref{ass:variance-linear} this is equivalent to
the residual projection index vanishing.

\begin{proof}
Let
\[
  S_n=V_n^{-1/2}n^{-1/2}\sum_{i=1}^n\psi_n(W_i).
\]
By Assumption~\ref{ass:eif-clt}, \(S_n\Rightarrow N(0,1)\), so \(S_n=O_p(1)\)
and the limiting law is nondegenerate.  Assumption~\ref{ass:common-eif} gives,
uniformly over the finite set \(\mathcal M\),
\[
  Z_{m,n}=S_n+\frac{R_{m,n}}{V_n^{1/2}}
  =S_n+o_p(1).
\]
Therefore
\[
  \max_{m,m'\in\mathcal M}|Z_{m,n}-Z_{m',n}|
  \le
  2\max_{m\in\mathcal M}|R_{m,n}|/V_n^{1/2}
  \to_p0,
\]
which proves centered point-estimator equivalence.  The same display and the
central limit theorem give \(Z_{m,n}\Rightarrow N(0,1)\) for every
\(m\in\mathcal M\).

Next, Assumption~\ref{ass:variance-linear} gives
\[
  \frac{\hat V_{m,n}}{V_n}=1+\Delta_{m,n}+\rho_{m,n},
  \qquad
  \max_{m\in\mathcal M}|\rho_{m,n}|\to_p0,
\]
where \(\rho_{m,n}\) absorbs \(\xi_{m,n}\) and the displayed \(o_p(1)\) term.
Because \(\Pi_{m,n}\) is a \(K_n\)-orthogonal projection,
\[
  0\le\Delta_{m,n}
  \le \|\alpha_n\|_{K_n}^2/V_n
  =L_n^2/V_n.
\]
Assumption~\ref{ass:local-overlap} states \(V_n\asymp L_n^2\), so the
deterministic sequence \(\{\Delta_{m,n}:m\in\mathcal M\}\) is uniformly
bounded.  Since \(d\mapsto(1+d)^{-1/2}\) is continuously differentiable on
\([0,C]\) for any finite \(C\), the continuous mapping theorem and the
uniform \(o_p(1)\) remainder imply
\[
  \left(\frac{V_n}{\hat V_{m,n}}\right)^{1/2}
  =
  (1+\Delta_{m,n})^{-1/2}+o_p(1)
\]
uniformly over \(m\in\mathcal M\).  Hence
\[
  T_{m,n}
  =
  Z_{m,n}\left(\frac{V_n}{\hat V_{m,n}}\right)^{1/2}
  =
  S_n(1+\Delta_{m,n})^{-1/2}+o_p(1)
\]
uniformly over \(m\).

Fix \(m,m'\).  The preceding expansion yields
\[
  T_{m,n}-T_{m',n}
  =
  S_n\left\{(1+\Delta_{m,n})^{-1/2}
      -(1+\Delta_{m',n})^{-1/2}\right\}
  +o_p(1).
\]
If \(\Delta_{m,n}-\Delta_{m',n}\to0\), then the bracketed deterministic
difference tends to zero by continuity, and \(T_{m,n}-T_{m',n}\to_p0\)
because \(S_n=O_p(1)\).

Conversely suppose \(T_{m,n}-T_{m',n}\to_p0\).  If the bracketed deterministic
difference did not converge to zero, a subsequence would have absolute value
at least some \(\varepsilon>0\).  Along that subsequence,
\(\varepsilon S_n+o_p(1)\) could not converge to zero in probability because
\(S_n\Rightarrow N(0,1)\) is nondegenerate.  Therefore
\[
  (1+\Delta_{m,n})^{-1/2}
      -(1+\Delta_{m',n})^{-1/2}\to0.
\]
The indices are bounded and the inverse map \(b\mapsto b^{-2}-1\) is
continuous on the corresponding compact range bounded away from zero, so
\(\Delta_{m,n}-\Delta_{m',n}\to0\).  This proves the stated if and only if.

If \(\Delta_{m,n}\to\delta_m\), then the expansion above and Slutsky's theorem
give
\[
  T_{m,n}
  \Rightarrow
  (1+\delta_m)^{-1/2}N(0,1)
  =
  N(0,(1+\delta_m)^{-1}).
\]
The same argument applies to \(m'\).  If \(\delta_m\ne\delta_{m'}\), the
limiting variances \((1+\delta_m)^{-1}\) and \((1+\delta_{m'})^{-1}\) are
different.  In the canonical ordering
\(\delta_{\mathrm{ADML}}=0<\delta_{\mathrm{LRO}}<\delta_{\mathrm{DML}}\), this
means the ADML Wald denominator has the efficient first-order scale, while
LRO and DML have progressively larger reported variance ratios and therefore
different studentized Gaussian scales.  The centered numerators still share
the \(N(0,1)\) limit by the first part of the proof.

Finally, for one estimator \(m\),
\[
  \frac{\hat V_{m,n}}{V_n}
  =
  1+\Delta_{m,n}+o_p(1).
\]
If \(\Delta_{m,n}\to0\), then \(\hat V_{m,n}/V_n\to_p1\).  Conversely, if
\(\hat V_{m,n}/V_n\to_p1\), then the deterministic nonnegative term
\(\Delta_{m,n}\) must converge to zero; otherwise a subsequence bounded away
from zero would force the variance ratio away from one in probability.  Thus
ratio-consistent studentization relative to \(V_n\) holds if and only if
\(\Delta_{m,n}\to0\).
\end{proof}

\paragraph{Sanity check.}
In the fixed-overlap corner, Assumption~\ref{ass:fixed-overlap} states that
each named variance estimator is ratio-consistent for \(V_n\).  The final part
of Theorem~\ref{thm:student-frontier} then gives
\(\Delta_{m,n}\to0\) for every \(m\in\mathcal M\), and the pairwise
studentized differences converge to zero.  This recovers the fixed-overlap
equivalence stated in Theorem~\ref{thm:fixed-overlap}.  In the known-propensity
common-score corner, Assumption~\ref{ass:known-propensity} puts
\(\alpha_n\) in every variance-rule adjoint range, so
\((I-\Pi_{m,n})\alpha_n=0\), \(\Delta_{m,n}=0\), and the same collapse occurs.

\paragraph{Counterexample/minimality check.}
The bounded projection-index condition is essential.  If one dropped the
support bound \(\Delta_{m,n}\le L_n^2/V_n=O(1)\) supplied by
Assumption~\ref{ass:local-overlap} and the projection definition, the
``only if'' direction would fail algebraically: take deterministic indices
\(\Delta_{m,n}=n\) and \(\Delta_{m',n}=2n\).  Then
\[
  (1+\Delta_{m,n})^{-1/2}
  -(1+\Delta_{m',n})^{-1/2}\to0
\]
and hence the leading approximation to \(T_{m,n}-T_{m',n}\) vanishes, while
\(\Delta_{m,n}-\Delta_{m',n}=-n\not\to0\).  This is not a counterexample to
the theorem because such indices cannot arise from the stated
\(K_n\)-orthogonal projection functional under \(V_n\asymp L_n^2\), but it
shows why the overlap/variance-scale bound cannot be omitted from the proof.
