\paragraph{\S9-fragment-statement.}
\begin{theorem}[Conjecture 2: two-cell weak-overlap witness]\label{thm:two-cell-witness}
\paragraph{Motivating claim, restated verbatim.}
Under Assumptions~\ref{ass:exact-ate}--\ref{ass:kernel-observable} and \ref{ass:two-cell}, there is a nonempty open set of finite-support triangular arrays for which
\[
  \Delta_{\mathrm{ADML},n}=0,\qquad
  0<\liminf_n\Delta_{\mathrm{LRO},n}
  \le \limsup_n\Delta_{\mathrm{LRO},n}
  < \liminf_n\Delta_{\mathrm{DML},n}.
\]
On this open set,
\[
  \max_{m,m'\in\mathcal M}|Z_{m,n}-Z_{m',n}|\to_p0
\]
but the three Wald half-lengths based on \(\hat V_{m,n}^{1/2}/\sqrt n\) have strict limiting ratios.  The witness is nondegenerate on the observable law: both treatment states occur with positive probability in each \(n\), residual variances are bounded away from zero on the weak-overlap cell, and the strict gaps persist under sufficiently small perturbations of the two cell probabilities and residual variances.  For the displayed two-cell matrices, the indices are computed directly as
\[
  \Delta_{\mathrm{ADML},n}=0,\qquad
  \Delta_{\mathrm{DML},n}=a_{A,n}^2/V_n,\qquad
  \Delta_{\mathrm{LRO},n}
  =
  \frac{(a_{A,n}-\lambda a_{B,n})^2}{(1+\lambda^2)V_n},
\]
so strict separation follows whenever \(0< (a_{A,n}-\lambda a_{B,n})^2/(1+\lambda^2)<a_{A,n}^2\) eventually.
Because \(a_{B,n}/a_{A,n}\to0\), the displayed LRO index converges to \(\eta_A/(1+\lambda^2)\) while the DML index converges to \(\eta_A\), giving strict separation for every fixed \(\lambda>0\).

\paragraph{Headline.}
Under Assumptions~\ref{ass:exact-ate}--\ref{ass:kernel-observable} and \ref{ass:two-cell}, the two-cell matrices yield \(\Delta_{\mathrm{ADML},n}=0\), \(0<\lim_{n\to\infty}\Delta_{\mathrm{LRO},n}=\eta_A/(1+\lambda^2)<\eta_A=\lim_{n\to\infty}\Delta_{\mathrm{DML},n}\), centered point-statistic equivalence, and strict Wald half-length ratios.
\end{theorem}

\paragraph{\S13-refutation-attempt.}
The required refutation-first check was run inside the exact-identification regime stated in Assumptions~\ref{ass:exact-ate}--\ref{ass:kernel-observable} and the finite-support two-cell regime stated in Assumption~\ref{ass:two-cell}.  The first primitive was the three-node back-door/SWIG check with variables \(X,D,Y\).  For a candidate law satisfying consistency, \((Y(1),Y(0))\perp D\mid X\), and \(0<e_n(X)<1\) on the two cells, the standard adjustment trace gives
\[
  \E_n[Y(d)]
  =\E_n\{\E_n[Y(d)\mid X]\}
  =\E_n\{\E_n[Y(d)\mid D=d,X]\}
  =\E_n\{\E_n[Y\mid D=d,X]\},
\]
where the second equality uses Assumption~\ref{ass:exact-ate}, the third uses consistency in Assumption~\ref{ass:exact-ate}, and local overlap from Assumption~\ref{ass:local-overlap} makes the conditional means observable.  Thus no finite two-cell law satisfying the stated assumptions can refute the target-functional equality.

The second primitive was the finite-support overlap-violation check.  Setting \(e_n(x_A)=0\) would make the treated weak-overlap cell unobserved and would obstruct the conditional mean \(g_{1,n}(x_A)\), but that candidate violates Assumptions~\ref{ass:local-overlap} and \ref{ass:two-cell}, which require \(e_n(x_A)=\kappa_n>0\).  It is therefore outside the conjecture's regime and is not a refutation.

The third check was the two-dimensional projection algebra itself.  Potential refutations would require one of the displayed residual norms to be zero or ordered incorrectly while the two-cell hypotheses remain true.  The equality \(a_{A,n}-\lambda a_{B,n}=0\) would force \(a_{B,n}/a_{A,n}=1/\lambda\), contradicting \(a_{B,n}/a_{A,n}\to0\) for fixed \(\lambda>0\).  The equality \(\lambda=0\) would collapse LRO to the DML column space, but Assumption~\ref{ass:two-cell} fixes \(\lambda\in(0,\infty)\).  No admissible witness was found, so the derivation proceeds to the positive proof.

\paragraph{\S10 Interpretation.}
The theorem is a finite-dimensional certificate for the studentization frontier.  The point estimators remain equivalent because Assumption~\ref{ass:common-eif} gives all three estimators the same efficient influence-function expansion after scaling by \(V_n^{1/2}\).  The reported Wald denominators can still separate because Assumption~\ref{ass:variance-linear} lets each variance rule leave a different covariance-kernel residual of the ATE Riesz representer.

In the two-cell basis, ADML spans both weak- and strong-overlap cell directions, so its residual index is zero.  DML spans only the \(q_B\) direction and leaves the entire weak-overlap component \(a_{A,n}q_A\).  LRO spans the tilted line \((\lambda,1)\), so it captures a fixed positive fraction of \(q_A\) but not all of it.  Since the weak-overlap coefficient dominates, \(a_{B,n}/a_{A,n}\to0\), the LRO residual limit is exactly \(1/(1+\lambda^2)\) of the DML residual limit.

\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:two-cell-witness}]
Let
\[
  U_n=V_n^{-1/2}n^{-1/2}\sum_{i=1}^n\psi_n(W_i).
\]
Assumption~\ref{ass:common-eif} gives, uniformly over \(m\in\mathcal M\),
\[
  Z_{m,n}=U_n+R_{m,n}/V_n^{1/2}=U_n+o_p(1).
\]
Therefore, for any \(m,m'\in\mathcal M\),
\[
  Z_{m,n}-Z_{m',n}
  =(R_{m,n}-R_{m',n})/V_n^{1/2}
  =o_p(1),
\]
and hence
\[
  \max_{m,m'\in\mathcal M}|Z_{m,n}-Z_{m',n}|\to_p0.
\]
Assumption~\ref{ass:eif-clt} also gives \(U_n\Rightarrow N(0,1)\), so the common point-estimator numerator is nondegenerate.

It remains to compute the observable variance indices.  By Assumption~\ref{ass:two-cell}, \(q_A,q_B\) are \(K_n\)-orthonormal and
\[
  \alpha_n=a_{A,n}q_A+a_{B,n}q_B.
\]
For ADML, the displayed matrix \(B_{\mathrm{ADML},n}=I_2\) has column space \(\mathbb R^2\).  Thus \(\Pi_{\mathrm{ADML},n}\alpha_n=\alpha_n\), so
\[
  (I-\Pi_{\mathrm{ADML},n})\alpha_n=0,
  \qquad
  \Delta_{\mathrm{ADML},n}=0.
\]

For DML, \(B_{\mathrm{DML},n}=(0,1)^\transpose\), so the projection range is \(\operatorname{span}\{q_B\}\).  Orthogonality of \(q_A,q_B\) gives
\[
  \Pi_{\mathrm{DML},n}\alpha_n=a_{B,n}q_B,\qquad
  (I-\Pi_{\mathrm{DML},n})\alpha_n=a_{A,n}q_A.
\]
Since \(\|q_A\|_{K_n}=1\),
\[
  \Delta_{\mathrm{DML},n}
  =
  \frac{\|(I-\Pi_{\mathrm{DML},n})\alpha_n\|_{K_n}^2}{V_n}
  =
  \frac{a_{A,n}^2}{V_n}.
\]

For LRO, \(B_{\mathrm{LRO},n}=(\lambda,1)^\transpose\), so the projection range is the line spanned by \(v=(\lambda,1)^\transpose\).  In the \(K_n\)-orthonormal coordinates \((q_A,q_B)\), the squared distance from \(a=(a_{A,n},a_{B,n})^\transpose\) to this line is
\[
  \|a\|^2-\frac{(a^\transpose v)^2}{v^\transpose v}
  =
  a_{A,n}^2+a_{B,n}^2
  -
  \frac{(\lambda a_{A,n}+a_{B,n})^2}{1+\lambda^2}
  =
  \frac{(a_{A,n}-\lambda a_{B,n})^2}{1+\lambda^2}.
\]
Dividing by \(V_n\) yields
\[
  \Delta_{\mathrm{LRO},n}
  =
  \frac{(a_{A,n}-\lambda a_{B,n})^2}{(1+\lambda^2)V_n}.
\]

Assumption~\ref{ass:two-cell} gives \(a_{A,n}^2/V_n\to\eta_A>0\), \(a_{B,n}/a_{A,n}\to0\), and fixed \(\lambda\in(0,\infty)\).  Hence
\[
  \Delta_{\mathrm{DML},n}\to\eta_A
\]
and
\[
  \Delta_{\mathrm{LRO},n}
  =
  \frac{a_{A,n}^2}{V_n}
  \frac{(1-\lambda a_{B,n}/a_{A,n})^2}{1+\lambda^2}
  \to
  \frac{\eta_A}{1+\lambda^2}.
\]
Because \(\lambda>0\),
\[
  0<\frac{\eta_A}{1+\lambda^2}<\eta_A.
\]
The displayed liminf--limsup ordering follows because the three sequences converge to the displayed limits.

Assumption~\ref{ass:variance-linear} gives, uniformly over \(m\in\mathcal M\),
\[
  \frac{\hat V_{m,n}}{V_n}=1+\Delta_{m,n}+o_p(1),
\]
where Assumption~\ref{ass:kernel-observable} makes the indices computable from the observable law and the named variance rule.  Therefore a Wald half-length of the form \(c_\gamma\hat V_{m,n}^{1/2}/\sqrt n\), for any fixed normal critical value \(c_\gamma>0\), satisfies
\[
  \frac{c_\gamma\hat V_{m,n}^{1/2}/\sqrt n}{c_\gamma V_n^{1/2}/\sqrt n}
  \to_p
  (1+\delta_m)^{1/2},
\]
where
\[
  \delta_{\mathrm{ADML}}=0,\qquad
  \delta_{\mathrm{LRO}}=\frac{\eta_A}{1+\lambda^2},\qquad
  \delta_{\mathrm{DML}}=\eta_A.
\]
Thus the limiting half-length ratios are strict:
\[
  1
  <
  \sqrt{1+\eta_A/(1+\lambda^2)}
  <
  \sqrt{1+\eta_A}.
\]

Finally, the witness is nonempty and open in the finite-support parameterization.  One concrete member is obtained by taking two cells with positive probabilities, \(e_n(x_A)=\kappa_n\), \(e_n(x_B)=1/2\), residual variances in a compact interval \([c,C]\), fixed \(\lambda>0\), \(a_{A,n}^2/V_n\to\eta_A>0\), and \(a_{B,n}/a_{A,n}\to0\), as stipulated by Assumption~\ref{ass:two-cell}.  Both treatment states occur on each cell because \(\kappa_n>0\) and \(1/2\in(0,1)\), and the residual variances are bounded away from zero by the same assumption.  The formulas above are continuous functions of the cell probabilities, residual variances, \(\lambda\), and normalized coefficient ratio \(a_{B,n}/a_{A,n}\) wherever \(V_n>0\) and the displayed projection matrices keep their ranks.  Since the strict inequality \(0<\eta_A/(1+\lambda^2)<\eta_A\) has positive margin, sufficiently small perturbations preserving positivity, \(\lambda>0\), and \(|a_{B,n}/a_{A,n}|\) small enough preserve the same strict ordering.  This proves the claimed nonempty open set and completes the proof.
\end{proof}

\paragraph{\S12 Sanity check.}
Take the clean corner \(\lambda=1\) and \(a_{B,n}/a_{A,n}\to0\).  Then
\[
  \Delta_{\mathrm{ADML},n}\to0,\qquad
  \Delta_{\mathrm{LRO},n}\to\eta_A/2,\qquad
  \Delta_{\mathrm{DML},n}\to\eta_A.
\]
The limiting Wald half-length multipliers relative to the efficient scale are
\[
  1,\qquad \sqrt{1+\eta_A/2},\qquad \sqrt{1+\eta_A},
\]
which are strictly ordered for every \(\eta_A>0\).  This matches the intended weak-overlap picture: all three centered point estimates have the same \(V_n^{1/2}\)-normalized numerator, but the denominator reports differ.

In the fixed-overlap corner, Theorem~\ref{thm:fixed-overlap} gives equality of the named first-order Wald statistics.  The two-cell witness does not contradict that result because Assumption~\ref{ass:two-cell} instead places nonvanishing normalized Riesz energy in the weak-overlap \(q_A\) direction.

\paragraph{\S13 Counterexample or minimality check.}
The restriction \(\lambda>0\) is necessary for strict DML--LRO separation in the displayed two-cell certificate.  If \(\lambda=0\), then
\[
  B_{\mathrm{LRO},n}=(0,1)^\transpose=B_{\mathrm{DML},n},
\]
so
\[
  \Delta_{\mathrm{LRO},n}=\Delta_{\mathrm{DML},n}=a_{A,n}^2/V_n,
\]
and the strict inequality \(\limsup_n\Delta_{\mathrm{LRO},n}<\liminf_n\Delta_{\mathrm{DML},n}\) fails.

The dominance condition \(a_{B,n}/a_{A,n}\to0\) is also necessary for the advertised LRO limit.  If instead \(a_{B,n}/a_{A,n}\to1/\lambda\), then
\[
  \Delta_{\mathrm{LRO},n}
  =
  \frac{a_{A,n}^2}{V_n}
  \frac{(1-\lambda a_{B,n}/a_{A,n})^2}{1+\lambda^2}
  \to0,
\]
so the claimed positive LRO limit disappears.  This shows that the two-cell theorem is not merely a consequence of weak overlap; it depends on the weak-overlap Riesz direction being asymptotically aligned with \(q_A\) and only tilted, not fully absorbed, by the LRO certificate.
