% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_lp\_svar\_channel\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_lp\_svar\_channel\_frontier} / \texttt{v1}%
  \\ \large\textit{A common-restriction LP/SVAR channel frontier for sign and non-Gaussian labels}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Exact-identification convention. The tuple is
\[
(\texttt{qid},\texttt{specialization},G,Y_t,\theta_w,\mathcal A)
=
(\texttt{eid\_lp\_svar\_channel\_frontier},\texttt{v1},G_{\mathrm{SVAR}},
Y_t,\theta_w(P),\mathcal A_{\mathrm{common}}).
\]
Here \(G_{\mathrm{SVAR}}\) is a reduced-form finite-order VAR law with stable lag
polynomial, innovation covariance \(\Sigma_u\succ0\), and an orthogonal impact
rotation \(Q\in O(2)\). The treatment is the first structural shock after
labeling. The target estimand is the support function
\(\theta_w(P)=h_{\mathcal R_{\mathrm{common}}(P)}(w)\) of the identified impulse
response set in a fixed horizon-weight direction \(w\). The identifying
assumptions \(\mathcal A_{\mathrm{common}}\) impose the same sign rows, zero
rows, and fourth-cumulant label restriction on the LP comparator and the SVAR
comparator before any LP/SVAR equality or separation is stated.

\begin{abstract}
Plagborg-Moller and Wolf show that local projections and VARs estimate the same
population impulse responses when the identifying restrictions are held fixed.
This proposal asks what remains of that equivalence when the fixed restrictions
include sign rows and a non-Gaussian cumulant label. The main conjecture is an
iff channel frontier: common-restriction LP and SVAR support functions agree
exactly when the non-normalized sign exposure, horizonwise pasting defect, and
cumulant-label determinant channel collapse. The focal object is a canonical
constant \(c_w(P)\), defined as an extremal support-loss-to-distance-product
ratio on a compact comparison set, rather than as an assumed curvature or a
gap-defined threshold. Resolving the conjecture would give sign-restricted and
non-Gaussian SVAR work a population diagnostic for when LP rows can be read as
one economically labeled structural shock.
\end{abstract}

\section{Introduction}
The question is whether a horizonwise LP response set and a structural VAR
response set still have the same support function after the same sign, zero, and
fourth-cumulant label restrictions are imposed. The claim is that equality is
not a generic consequence of the Plagborg-Moller-Wolf equivalence; it is governed
by three independently computable channels.

\citet[pp. 955--958 and Proposition 1]{plagborgmoller_wolf_2021_lp_var} give
the same-population-IRF result for LPs and VARs under common restrictions, while
\citet[Sections 3--4]{gourieroux_monfort_renne_2017_ica_svar} and
\citet[Sections 2--3]{lanne_meitz_saikkonen_2017_nongaussian_svar} recover
non-Gaussian shocks only up to economic labeling. The gap is the exact
observable frontier between common-restriction equality and strict separation
when sign rows and cumulant labels are both active. The kernel is an exact
identification statement about support functions of structural impulse-response
sets.

The direct consumer is the sign-restricted SVAR literature on shock masquerading
and independence refinements in \citet{wolf_2022_sign_restricted_vars} and
\citet{drautzburg_wright_2023_independence}. A reader who accepts the result
would compare LP and SVAR impulse responses only after checking the channel
frontier, rather than treating a cumulant-labeled SVAR shock and a sign-labeled
LP row as automatically commensurable.

\begin{itemize}[leftmargin=*]
\item Theorem 1: If LP and SVAR impose the identical common rotation set, their support functions agree. Gap: \citet{plagborgmoller_wolf_2021_lp_var} is used only after equal restrictions are imposed. Consumer: PMW-style LP/VAR practice.
\item Conjecture 1: The channel frontier gives an iff condition for strict LP/SVAR support separation through \(c_w(P)\), sign exposure, pasting, and cumulant determinant channels. Gap: \citet{read_2022_sign_zero_algorithms}, \citet{drautzburg_wright_2023_independence}, and non-Gaussian SVAR papers do not characterize this common-restriction frontier. Consumer: sign and independence-refined SVAR analysis.
\item Theorem 2: In the parent corner where sign and pasting channels are zero, the frontier collapses algebraically to the parent \(\chi_w(P)\) cumulant margin. Gap: the banked \texttt{eid\_lp\_svar\_nonequiv} proposal assumed this margin rather than deriving the collapse. Consumer: CausalSmith exact-ID catalogue repair.
\end{itemize}

\section{Related work}
\citet{plagborgmoller_wolf_2021_lp_var} is the mandatory comparator because it
establishes the common population impulse-response target for LPs and VARs under
common identifying restrictions. \citet{li_plagborgmoller_wolf_2024_varlp} study
finite-sample LP/VAR tradeoffs and therefore delimit what this proposal is not:
the present claim is a population identification frontier. \citet{arias_rubioramirez_waggoner_2018_signzero}
and \citet{read_2022_sign_zero_algorithms} give the computational geometry of
sign and zero restricted SVAR identified sets. \citet{gafarov_meier_montielolea_2018_svar}
compute extrema over sign-restricted impulse-response sets, making support
functions the natural language for the present comparison.

\citet{wolf_2022_sign_restricted_vars} identifies shock masquerading as a
substantive failure mode of sign restrictions. \citet{read_2022_unit_effect_normalisation}
shows that unit-effect normalization can make identified sets unbounded, which
motivates the non-normalized sign-exposure channel used here.
\citet{drautzburg_wright_2023_independence} show that independence can refine
sign-restricted sets but can also produce nonconvex and disjoint confidence
regions. \citet{gourieroux_monfort_renne_2017_ica_svar} and
\citet{lanne_meitz_saikkonen_2017_nongaussian_svar} establish non-Gaussian SVAR
identification by independent components, with labeling ambiguities that this
proposal treats as part of the identifying restriction. \citet{lanne_luoto_2021_gmm_nongaussian_svar}
stress that statistical non-Gaussian identification need not deliver economic
interpretation. \citet{montielolea_plagborgmoller_qian_2022_higher_moments} and
\citet{hoesch_lee_mesters_2024_nongaussian_svar} motivate the weak-cumulant
edge cases by showing that higher-moment identification can be fragile near
Gaussianity.

The closest in-catalogue prior art is \texttt{eid\_lp\_svar\_nonequiv} with the
headline claim that LP and SVAR identified sets can differ under cumulant labels.
Its banked reviewers rejected the flagship upgrade because the comparison used
unequal restriction sets, normalized sign exposure into a tautology, and assumed
rather than derived the quantitative cumulant margin. The exact-ID entries in
\texttt{doc/API.md} are relevant only as catalogue context for identification
statements; the present proposal is not a do-calculus or graph-rule extension.

\section{Formal setup}
Let \(Y_t\in\R^2\) follow a stable reduced-form VAR with innovations
\(u_t=BQ\varepsilon_t\), \(BB^\transpose=\Sigma_u\), and \(Q\in O(2)\). The
observable law \(P\) contains the reduced-form impulse matrices
\(\Phi_h(P)\), the innovation covariance, and fourth cumulants of \(u_t\). A
structural response path generated by \(Q\) is
\[
r_h(Q;P)=\Phi_h(P)B(P)Qe_1,\qquad h=0,\ldots,H.
\]
For a horizon-weight vector \(w=(w_0,\ldots,w_H)\), write
\(\ell_w(Q;P)=\sum_{h=0}^H w_h^\transpose r_h(Q;P)\).

The common SVAR restriction set is
\[
\mathcal Q_C(P)=\{Q\in O(2): A r(Q;P)\ge 0,\; Zr(Q;P)=0,\;
\Delta_\kappa(Q;P)=0\},
\]
where \(A\) collects nonredundant sign rows, \(Z\) collects zero rows, and
\(\Delta_\kappa\) is the determinant residual that labels the first component
by the fourth-cumulant tensor. Its support is
\[
h_C(w;P)=\sup_{Q\in\mathcal Q_C(P)}\ell_w(Q;P).
\]
The common LP comparator is the same set written in LP-response coordinates:
\(\mathcal R_C(P)=\{(r_0(Q;P),\ldots,r_H(Q;P)):Q\in\mathcal Q_C(P)\}\) and
\(h_{LP,C}(w;P)=\sup_{r\in\mathcal R_C(P)}\sum_h w_h^\transpose r_h\).

The horizonwise LP relaxation is
\[
\mathcal R_H(P)=\prod_{h=0}^H
\{r_h(Q_h;P): Q_h\in O(2),\; A_h r_h(Q_h;P)\ge0,\; Z_h r_h(Q_h;P)=0\}.
\]
It deliberately permits different rotations across horizons before a common
cumulant label is tested. Define the pasting distance
\[
D_{\mathrm{paste}}(r;P)=\inf_{Q\in O(2)}
\Big(\sum_{h=0}^H \|r_h-r_h(Q;P)\|^2\Big)^{1/2}.
\]
Define the non-normalized sign exposure
\[
D_{\mathrm{sign}}(Q;P)=
\Big(\sum_{j\in J_+(P,w)} [ -a_j^\transpose r(Q;P)]_+^2\Big)^{1/2},
\]
where \(J_+(P,w)\) is the set of active nonredundant sign rows at the
horizonwise support face; if this set is empty, \(D_{\mathrm{sign}}=0\). Define
\(D_\kappa(Q;P)=|\Delta_\kappa(Q;P)|\). For a compact local comparison set
\(\mathcal K_w(P)\subset \mathcal R_H(P)\times O(2)\) with positive product
distance, the focal scalar is
\[
c_w(P)=
\inf_{(r,Q)\in\mathcal K_w(P)}
\frac{h_H(w;P)-\sum_h w_h^\transpose r_h}
{(D_{\mathrm{paste}}(r;P)+D_{\mathrm{sign}}(Q;P))D_\kappa(Q;P)}.
\]

\begin{verbatim}
Exact-identification convention. The tuple is
(qid, specialization, G, Y_t, theta_w, A)
= (eid_lp_svar_channel_frontier, v1, G_SVAR, Y_t, theta_w(P),
   A_common).
Here G_SVAR is a reduced-form finite-order VAR law with stable lag polynomial,
innovation covariance Sigma_u positive definite, and orthogonal impact rotation
Q in O(2). The treatment is the first structural shock after labeling. The
target estimand is the support function theta_w(P)=h_{R_common(P)}(w) of the
identified impulse response set in a fixed horizon-weight direction w. The
identifying assumptions A_common impose the same sign rows, zero rows, and
fourth-cumulant label restriction on the LP comparator and the SVAR comparator
before any LP/SVAR equality or separation is stated.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Stable reduced form]\label{ass:stable}
The reduced-form VAR is stable, \(\Sigma_u\succ0\), and \(B(P)\) is the
symmetric square root of \(\Sigma_u\).
\end{assumption}

\begin{assumption}[Common restrictions]\label{ass:common}
The LP and SVAR comparators use the same sign rows \(A\), zero rows \(Z\), and
fourth-cumulant determinant residual \(\Delta_\kappa(\cdot;P)\).
\end{assumption}

\begin{assumption}[Nonredundant sign face]\label{ass:signface}
For the direction \(w\), the active sign rows \(J_+(P,w)\) are linearly
nonredundant; when no row is active, \(J_+(P,w)=\varnothing\) and the sign
exposure is defined as zero.
\end{assumption}

\begin{assumption}[Compact local comparison set]\label{ass:compact}
\(\mathcal K_w(P)\) is compact, contains the horizonwise support maximizers
under consideration, and excludes zero product distance:
\((D_{\mathrm{paste}}+D_{\mathrm{sign}})D_\kappa>0\) on
\(\mathcal K_w(P)\).
\end{assumption}

\begin{assumption}[Positive channel curvature]\label{ass:curvature}
The extremal constant \(c_w(P)\) is finite and strictly positive.
\end{assumption}

\begin{assumption}[Two-shock regularity]\label{ass:twoshock}
For the two-shock witness, \(O(2)\) is parameterized by rotations and reflected
rotations, and the trigonometric support and cumulant residuals have no
stationary support maximizer outside the listed finite candidate angles.
\end{assumption}

\section{Main results}
\begin{theorem}[Common-restriction PMW reduction]\label{thm:pmw-common}
Under Assumptions~\ref{ass:stable} and~\ref{ass:common}, if
\(\mathcal R_C(P)=\{r(Q;P):Q\in\mathcal Q_C(P)\}\), then
\[
h_{LP,C}(w;P)=h_C(w;P).
\]
\end{theorem}
Proof sketch. Both support functions optimize the same linear functional over
the same image of \(\mathcal Q_C(P)\). The statement is only the PMW
same-estimand reduction after restriction equality has been imposed.

\begin{conjecture}[Channel frontier (NOT YET PROVED)]\label{conj:frontier}
Under Assumptions~\ref{ass:stable}--\ref{ass:curvature}, define
\[
\Gamma_w(P)=
\inf_{(r,Q)\in\mathcal K_w(P)}
(D_{\mathrm{paste}}(r;P)+D_{\mathrm{sign}}(Q;P))D_\kappa(Q;P).
\]
Then
\[
h_H(w;P)>h_C(w;P)
\quad\Longleftrightarrow\quad
c_w(P)>0\ \text{ and }\ \Gamma_w(P)>0.
\]
Moreover,
\[
h_H(w;P)-h_C(w;P)\ge c_w(P)\Gamma_w(P),
\]
and equality of common-restriction LP and SVAR supports holds exactly when at
least one of the three channels vanishes on the local comparison set.
\end{conjecture}

\begin{theorem}[Parent \(\chi_w\) collapse]\label{thm:chi-collapse}
Under Assumptions~\ref{ass:stable}, \ref{ass:common}, and~\ref{ass:compact}, if
\(D_{\mathrm{paste}}=0\) and \(D_{\mathrm{sign}}=0\) on
\(\mathcal K_w(P)\), then \(c_w(P)\Gamma_w(P)\) reduces to the parent cumulant
margin
\[
\chi_w(P)=
\inf_{Q\in\mathcal K_w^\kappa(P)}
\frac{h_H(w;P)-\ell_w(Q;P)}{D_\kappa(Q;P)}\,D_\kappa(Q;P).
\]
\end{theorem}
Proof sketch. Substitute the two zero-channel restrictions into the displayed
definition of \(c_w(P)\Gamma_w(P)\) before taking the infimum. The remaining
ratio is exactly the support-loss per cumulant residual used by the parent
margin.

\section{Sanity-check corollaries}
\begin{corollary}[PMW sanity reduction]\label{cor:pmw}
Under Assumptions~\ref{ass:stable} and~\ref{ass:common}, if
\(\mathcal R_H(P)=\mathcal R_C(P)\), then
\[
h_H(w;P)=h_C(w;P).
\]
This collapses to Theorem~\ref{thm:pmw-common} because the horizonwise
relaxation no longer relaxes a common rotation.
\end{corollary}

\begin{example}[Exhibit 9.1: two-shock trigonometric witness]\label{ex:trig}
Let \(H=1\), \(B=I_2\), \(\Phi_0=I_2\),
\(\Phi_1=\begin{psmallmatrix}0&1\\1&0\end{psmallmatrix}\), and
\(w_0=w_1=e_1\). Parameterize \(SO(2)\) by
\(q(\theta)=(\cos\theta,\sin\theta)^\transpose\). The horizonwise LP chooses
\(\theta_0=0\) and \(\theta_1=\pi/2\), so \(h_H(w;P)=2\). The common rotation
\(\theta=\pi/4\) gives \(\ell_w=\sqrt2\), hence support loss \(2-\sqrt2\).
For the nonredundant sign row \(a=e_1\), \(D_{\mathrm{sign}}(\pi/4;P)=0\).
The pasting distance from \((q(0),q(\pi/2))\) to the common path at
\(\pi/4\) is \(D_{\mathrm{paste}}=\sqrt{2-\sqrt2}\). With cumulant residual
\(\Delta_\kappa(\theta;P)=\sin(2\theta)\), \(D_\kappa(\pi/4;P)=1\), so the
displayed comparison value is
\[
\frac{2-\sqrt2}{\sqrt{2-\sqrt2}}=\sqrt{2-\sqrt2}.
\]
The reflected component \(q_R(\theta)=(\cos\theta,-\sin\theta)^\transpose\)
has horizon-one contribution \(-\sin\theta\), so its support candidates at
\(\theta\in\{0,\pi/4,\pi/2\}\) are \(1,0,-1\) after the same sign row; none
dominates the listed rotation candidate. The denominator is nonzero, the two
horizons use two observed response rows, and the displayed LP and SVAR supports
differ before any normalization by unit effect is imposed.
\end{example}

\section{Proof-sketch route}
For Conjecture~\ref{conj:frontier}, the reduction chain is:
headline \(\leftarrow\) unfold the support functions and channel distances in
\S6 \(\leftarrow\) substitute Assumptions~\ref{ass:common}--\ref{ass:compact}
\(\leftarrow\) prove a compactness lemma giving attained horizonwise and common
support maximizers \(\leftarrow\) prove a transversality lemma that converts the
fourth-cumulant determinant residual into a local distance to the labeled
rotation set \(\leftarrow\) prove a sign-face lemma showing that the active-row
slack is invariant to unit-effect rescaling and separates masquerading rotations
\(\leftarrow\) prove a pasting lemma characterizing when horizonwise maximizers
share one \(O(2)\) rotation \(\leftarrow\) combine the three lemmas through the
support-loss quotient defining \(c_w(P)\). This gives \(k=4\) substantive steps:
compact support attainment, cumulant transversality, non-normalized sign-face
separation, and horizonwise pasting. The two-shock boundary case in
Exhibit~\ref{ex:trig} supplies the finite \(O(2)\) rotation/reflection algebra.

\section{Honest scope flags}
Theorem~\ref{thm:pmw-common} and Theorem~\ref{thm:chi-collapse} are algebraic
sanity statements. Conjecture~\ref{conj:frontier} is the novel kernel and is not
yet proved. The positivity of \(c_w(P)\) is stated as an assumption rather than
derived globally; the intended theorem should later replace it by primitive
rank and transversality conditions. No claim is made about finite-sample
coverage or estimation.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft with common-restriction LP/SVAR sets,
canonical \(c_w(P)\), non-normalized sign exposure, parent \(\chi_w\) collapse,
and a two-shock trigonometric exhibit; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Arias, Rubio-Ramirez, and Waggoner(2018)]{arias_rubioramirez_waggoner_2018_signzero}
Arias, J. E., J. F. Rubio-Ramirez, and D. F. Waggoner (2018).
Inference based on structural vector autoregressions identified with sign and
zero restrictions: Theory and applications. \emph{Econometrica} 86(2), 685--720.

\bibitem[Drautzburg and Wright(2023)]{drautzburg_wright_2023_independence}
Drautzburg, T. and J. H. Wright (2023).
Refining set-identification in VARs through independence. \emph{Journal of
Econometrics} 235(2), 1569--1597.

\bibitem[Gafarov, Meier, and Montiel Olea(2018)]{gafarov_meier_montielolea_2018_svar}
Gafarov, B., M. Meier, and J. L. Montiel Olea (2018).
Delta-method inference for a class of set-identified SVARs. \emph{Journal of
Econometrics} 203(2), 316--327.

\bibitem[Gourieroux, Monfort, and Renne(2017)]{gourieroux_monfort_renne_2017_ica_svar}
Gourieroux, C., A. Monfort, and J.-P. Renne (2017).
Statistical inference for independent component analysis: Application to
structural VAR models. \emph{Journal of Econometrics} 196(1), 111--126.

\bibitem[Hoesch, Lee, and Mesters(2024)]{hoesch_lee_mesters_2024_nongaussian_svar}
Hoesch, L., S. Lee, and G. Mesters (2024).
Locally robust inference for non-Gaussian SVARs. \emph{Quantitative Economics}
15(4), 1051--1091.

\bibitem[Lanne and Luoto(2021)]{lanne_luoto_2021_gmm_nongaussian_svar}
Lanne, M. and J. Luoto (2021).
GMM estimation of non-Gaussian structural vector autoregression.
\emph{Journal of Business and Economic Statistics} 39(1), 69--81.

\bibitem[Lanne, Meitz, and Saikkonen(2017)]{lanne_meitz_saikkonen_2017_nongaussian_svar}
Lanne, M., M. Meitz, and P. Saikkonen (2017).
Identification and estimation of non-Gaussian structural vector
autoregressions. \emph{Journal of Econometrics} 196(2), 288--304.

\bibitem[Li, Plagborg-Moller, and Wolf(2024)]{li_plagborgmoller_wolf_2024_varlp}
Li, D., M. Plagborg-Moller, and C. K. Wolf (2024).
Local projections vs. VARs: Lessons from thousands of DGPs. \emph{Journal of
Econometrics} 244(2), 105722.

\bibitem[Montiel Olea, Plagborg-Moller, and Qian(2022)]{montielolea_plagborgmoller_qian_2022_higher_moments}
Montiel Olea, J. L., M. Plagborg-Moller, and E. Qian (2022).
SVAR identification from higher moments: Has the simultaneous causality problem
been solved? \emph{AEA Papers and Proceedings} 112, 481--485.

\bibitem[Plagborg-Moller and Wolf(2021)]{plagborgmoller_wolf_2021_lp_var}
Plagborg-Moller, M. and C. K. Wolf (2021).
Local projections and VARs estimate the same impulse responses.
\emph{Econometrica} 89(2), 955--980.

\bibitem[Read(2022a)]{read_2022_sign_zero_algorithms}
Read, M. (2022a).
Algorithms for inference in SVARs identified with sign and zero restrictions.
\emph{The Econometrics Journal} 25(3), 699--718.

\bibitem[Read(2022b)]{read_2022_unit_effect_normalisation}
Read, M. (2022b).
Unit-effect normalisation and inferences in SVARs identified with sign
restrictions. Reserve Bank of Australia Research Discussion Paper 2022-04.

\bibitem[Wolf(2022)]{wolf_2022_sign_restricted_vars}
Wolf, C. K. (2022).
SVARs under sign restrictions: A shock masquerading problem. \emph{AEA Papers
and Proceedings} 112, 474--480.
\end{thebibliography}

\end{document}
