% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_sdid\_mc\_id, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{panel\_sdid\_mc\_id} / \texttt{v1}%
  \\ \large\textit{Strict lattice for convex SCM, ridge ASCM, SDiD, and matrix completion under bounded-rank IFE}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{quote}
\begin{verbatim}
(qid, specialization, p, assignment, target, regression)
= (panel_sdid_mc_id, v1, unrestricted pre-period length T0 >= 2,
   single treated block after T0 with N0 >= 2 donor units and one treated
   aggregate row, ATT over post periods T1 >= 1,
   finite-dimensional population identifying functionals generated by
   convex SCM, affine/ridge ASCM, two-sided SDiD, and rank-R matrix completion).
\end{verbatim}
\end{quote}
The proposal is a free-form panel anchor, not the Q1 pool-mode.  Untreated potential outcomes are restricted to bounded-rank interactive fixed effects,
\[
Y^0_{it}=\alpha_i+\lambda_t+u_i^\transpose v_t,\qquad u_i,v_t\in\R^R,
\]
with deterministic population matrices and no sampling noise in the identification comparison.  Regularization parameters are part of the functional definitions and are held fixed or taken along an explicitly declared sequence before any asymptotic comparison is made.

\begin{abstract}
Synthetic-control practice now offers several nearby estimators--convex SCM, signed or ridge augmented SCM, synthetic DiD, and nuclear-norm matrix completion--but the literature usually compares them by robustness or asymptotic consistency rather than by an exact hierarchy of the ATT functionals they identify. This proposal asks for the sharp strict-extension lattice among those four functional classes under one bounded-rank interactive-fixed-effect panel model. The kernel conjecture is that convex SCM is strictly contained in affine/ridge ASCM, which is strictly contained in exact two-sided SDiD balance, which is strictly contained in rank-\(R\) matrix-completion uniqueness, with every strict separation witnessed by a minimal nondegenerate rank-\(R\) panel. A second conjecture asks for an observable Schur-complement certificate deciding lattice membership and producing the separating witness when membership fails. Resolving the conjectures would turn the current menu of synthetic-control estimators into a diagnostic rule: before choosing an estimator, applied researchers could report which identifying geometry their donor panel actually supports.
\end{abstract}

\section{Introduction}

\paragraph{Why the problem is important.}
Synthetic-control and causal-panel estimators are often presented as variations on a common pre-treatment matching idea, but applied conclusions can change when convex donor weights, signed ridge weights, time weights, or global low-rank completion extrapolate in different directions. The scientific question is whether these methods are merely computationally different implementations of the same bounded-rank identifying restriction, or whether each method genuinely expands the set of panels for which the ATT is pinned down.

\paragraph{The main finding (proposed).}
The proposed flagship result is Conjecture~\ref{conj:strict-lattice}: under the locked single-shock bounded-rank panel convention, the exact-identification domains form the strict lattice
\[
\calF_{\mathrm{convex}}(R,\rho)\subsetneq
\calF_{\mathrm{affine}}(R,\rho)\subsetneq
\calF_{\mathrm{sdid}}(R,\rho)\subsetneq
\calF_{\mathrm{mc}}(R,\rho),
\]
after quotienting out the common additive two-way-fixed-effect component. The strictness is not a generic ``more assumptions versus fewer assumptions'' statement: each gap is conjectured to have a minimal rank and dimension witness, with the ATT limits of the two adjacent methods written in closed form.

\paragraph{What is new.}
The closest published papers define, analyze, or compare individual estimators: \citet{DoudchenkoImbens2016} synthesize SCM, regression, DiD, intercepts, negative weights, and regularization; \citet{BenMichaelFellerRothstein2021} show ridge ASCM debiases imperfect SCM fit; \citet{ArkhangelskyAtheyHirshbergImbensWager2021} prove SDiD consistency and asymptotic normality under latent factors; \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} connect low-rank matrix completion to causal panels; and \citet{AtheyBayatiImbensQu2019} compare regression, synthetic-control, and matrix-completion predictors by ensemble weighting. None gives a necessary-and-sufficient lattice comparing the population ATT functional domains across all four methods. The novelty kernel is the strict-extension frontier itself, including adjacent ATT-projected Schur/Riesz certificates \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\) that should be zero exactly when the higher estimator's extra moments add no new ATT-relevant information beyond the lower estimator.

\paragraph{How it positions in the literature.}
This is a panel / linear-projection proposal. It sits between the design geometry of synthetic controls, the two-sided balancing geometry of SDiD, and the low-rank recovery geometry of matrix completion. It deliberately does not propose a new estimator or a new structural causal calculus; it asks for the exact identification relation among named published panel estimators under a shared bounded-rank interactive-fixed-effect model.

\paragraph{Implications for the community.}
The direct downstream consumer is the estimator-choice guidance in \citet{Abadie2021}: the proposed lattice would replace the current qualitative advice about convex-hull fit, extrapolation, and data requirements with a finite-dimensional certificate showing whether an applied panel needs convex SCM, ridge ASCM, SDiD, or matrix completion to identify the same ATT.

\paragraph{How research benefits from the conclusion.}
If the conjecture resolves favorably, empirical researchers should report the adjacent-pair certificates \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\) before treating SDiD, ASCM, and matrix completion as robustness checks for the same causal estimand.

\section{Related work}

\citet{AbadieDiamondHainmueller2010} establish the canonical convex synthetic-control design, where donor weights are nonnegative and sum to one; this is the baseline geometry represented by \(\calF_{\mathrm{convex}}(R,\rho)\). \citet{Abadie2021} surveys feasibility, data requirements, and practical diagnostics for synthetic controls, making it the applied guidance that would consume the proposed lattice certificate. \citet{DoudchenkoImbens2016} explicitly relax the Abadie--Diamond--Hainmueller restrictions by allowing intercepts, non-unit-sum weights, negative weights, and regularization; this is the closest published ancestor of the inclusion \(\calF_{\mathrm{convex}}(R,\rho)\subseteq\calF_{\mathrm{affine}}(R,\rho)\). \citet{AbadieLHour2021} show that penalization changes the donor-weight geometry in disaggregated synthetic-control settings; this motivates treating regularization as part of the identifying functional, not as a harmless computational detail. \citet{FermanPinto2021} analyze bias from imperfect pre-treatment fit, which is the empirical phenomenon that makes strict separation between convex and signed/augmented weights relevant.

\citet{BenMichaelFellerRothstein2021} introduce augmented SCM and show that ridge augmentation can be interpreted as a modified synthetic-control problem allowing negative weights while controlling extrapolation; this paper is the closest prior art for the affine/ridge node of the lattice. It also relates ASCM to constrained outcome-regression adjustments, so the proposed affine--SDiD comparison is not merely restating that relationship: the new object is the ATT-projected equality certificate deciding when time reweighting adds estimand information beyond the ASCM normal equations. \citet{ArkhangelskyAtheyHirshbergImbensWager2021} introduce SDiD with unit and time weights and prove consistency/asymptotic normality under latent-factor outcome models; this is the closest prior art for the SDiD node, but it does not characterize when its population functional equals ASCM or matrix completion. \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} develop nuclear-norm matrix completion for causal panel data and emphasize that causal-panel methods differ in how they impose identification restrictions; this is the closest prior art for \(\calF_{\mathrm{mc}}(R)\). \citet{AtheyBayatiImbensQu2019} compare regression, synthetic-control, and matrix-completion predictors through cross-validated ensembles; it is the closest published multi-method comparison, but it chooses among or averages prediction rules rather than giving necessary-and-sufficient equality domains for their ATT functionals. \citet{Xu2017} and \citet{BaiNg2021} provide adjacent factor-imputation routes under interactive fixed effects, helping fix the rank-\(R\) nuisance model used here but not comparing the synthetic-weight functional domains. \citet{ArkhangelskyImbens2022} study double-robust identification for causal panel data, which reinforces that assignment and outcome restrictions are distinct routes; this proposal instead holds the outcome-rank route fixed and compares the estimator geometries inside it.

In-repo prior art is adjacent but not duplicative. The ThmSmith catalogue's Q1\_MinimalBasis entry proves exact plim formulas for panel regression bases under iid Bernoulli assignment, and Q1\_StaggeredMinimalBasis records staggered closed forms for a switch-on target; both are finite-history regression-basis results rather than synthetic-control lattice results. The Q1\_SpectralThreshold entry refutes a Markov spectral-sign threshold for Q1 FWL weights; it supplies useful panel-spectral caution but concerns treatment-history regressions, not donor-weight synthetic controls. The banked \texttt{pid\_synth\_control\_factor\_misspec} proposal studies partial-identification intervals under factor misspecification and scalar diagnostic nonsharpness; it does not compare convex, signed, time-weighted, and low-rank identifying functional classes.

\section{Formal setup}

There is one treated aggregate row \(i=0\), \(N_0\) donor rows \(i=1,\ldots,N_0\), \(T_0\) pre-treatment periods, and \(T_1\) post-treatment periods. Write \(X_0\in\R^{T_0}\) for the treated pre-period untreated path, \(X\in\R^{N_0\times T_0}\) for the donor pre-period matrix with row \(X_i^\transpose\), \(Z_0\in\R^{T_1}\) for the unobserved treated post-period untreated path, and \(Z\in\R^{N_0\times T_1}\) for the observed donor post-period matrix. The observed treated post outcome is \(Y^{\mathrm{obs}}_{0,\mathrm{post}}=Z_0+\tau\one_{T_1}\), and the target is \(\tau_{\mathrm{ATT}}=T_1^{-1}\one_{T_1}^\transpose(Y^{\mathrm{obs}}_{0,\mathrm{post}}-Z_0)\). The observable panel law is
\[
P_{\mathrm{obs}}=(X_0,X,Z,Y^{\mathrm{obs}}_{0,\mathrm{post}}),
\]
and the estimator design package is \(\mathcal P=(P_{\mathrm{obs}},\rho)\), where \(\rho=(\rho_{\mathrm{scm}},\rho_{\mathrm{ascm}},\rho_{\mathrm{sdid},u},\rho_{\mathrm{sdid},t},\rho_{\mathrm{mc}})\) records the fixed or limiting regularization constants. Let \(\Delta_d=\{v\in\R^d:v_j\ge0,\ \one^\transpose v=1\}\), \(\bar Y^{\mathrm{obs}}_0=T_1^{-1}\one_{T_1}^\transpose Y^{\mathrm{obs}}_{0,\mathrm{post}}\), and \(\bar Z(w)=T_1^{-1}\one_{T_1}^\transpose Z^\transpose w\).

The rank-\(R\) untreated panel restriction is imposed on the full matrix
\[
M^0=\begin{pmatrix}
X_0^\transpose & Z_0^\transpose\\
X & Z
\end{pmatrix}
\]
after removing additive unit and time effects. Let \(Q_u\) and \(Q_t\) denote the population demeaning projections that remove those additive effects, and define the residual matrix \(\widetilde M=Q_uM^0Q_t\). The class \(\calM_R(P_{\mathrm{obs}})\) contains all completions of the missing treated-post block with \(\operatorname{rank}(\widetilde M)\le R\) and the same observed blocks \(P_{\mathrm{obs}}\).

The four population functionals are fixed by explicit optimization problems. Convex SCM solves
\[
w_{\mathrm{cvx}}\in\arg\min_{w\in\Delta_{N_0}}
\|X_0-X^\transpose w\|_2^2+\rho_{\mathrm{scm}}\|w\|_2^2,\qquad
\phi_{\mathrm{convex}}(\mathcal P)=\bar Y^{\mathrm{obs}}_0-\bar Z(w_{\mathrm{cvx}}),
\]
with deterministic tie-breaking by minimum Euclidean norm. The affine/ridge ASCM node solves the signed affine ridge problem
\[
(\gamma_{\mathrm{a}},w_{\mathrm{a}})\in\arg\min_{\gamma\in\R,\ w\in\R^{N_0}}
\|X_0-\gamma\one_{T_0}-X^\transpose w\|_2^2+\rho_{\mathrm{ascm}}\|w\|_2^2,
\]
and evaluates
\[
\phi_{\mathrm{affine}}(\mathcal P)
=\bar Y^{\mathrm{obs}}_0
-T_1^{-1}\one_{T_1}^\transpose(\gamma_{\mathrm{a}}\one_{T_1}+Z^\transpose w_{\mathrm{a}}).
\]
The two-sided SDiD node solves
\[
(w_{\mathrm{s}},\lambda_{\mathrm{s}},\mu_{\mathrm{s}},\nu_{\mathrm{s}})
\in\arg\min_{\substack{w\in\Delta_{N_0},\ \lambda\in\Delta_{T_0}\\ \mu,\nu\in\R}}
\|X_0-\mu\one_{T_0}-X^\transpose w\|_2^2+\rho_{\mathrm{sdid},u}\|w\|_2^2
+\|T_1^{-1}Z\one_{T_1}-X\lambda-\nu\one_{N_0}\|_2^2
+\rho_{\mathrm{sdid},t}\|\lambda\|_2^2
\]
and evaluates
\[
\phi_{\mathrm{sdid}}(\mathcal P)
=\bar Y^{\mathrm{obs}}_0-\bar Z(w_{\mathrm{s}})
-\lambda_{\mathrm{s}}^\transpose(X_0-X^\transpose w_{\mathrm{s}}).
\]
Finally, the rank-\(R\) matrix-completion node chooses the minimum-nuclear-norm residual completion
\[
M_{\mathrm{mc}}\in\arg\min_{M}
\frac12\|\Pi_{\Omega}(M)-\Pi_{\Omega}(M^{\mathrm{obs}})\|_F^2
+\rho_{\mathrm{mc}}\|Q_uMQ_t\|_*
\quad\text{subject to}\quad \operatorname{rank}(Q_uMQ_t)\le R,
\]
where \(M^{\mathrm{obs}}\) is the array of observed untreated blocks and \(\Omega\) contains the treated pre-period block and all donor blocks but excludes the treated post-period untreated block. It then sets
\[
\phi_{\mathrm{mc}}(\mathcal P)=
T_1^{-1}\one_{T_1}^\transpose
\{Y^{\mathrm{obs}}_{0,\mathrm{post}}-(M_{\mathrm{mc}})_{0,\mathrm{post}}\}.
\]
Thus \(\phi_{\mathrm{affine}}\) is the ASCM/ridge population normal-equation functional, \(\phi_{\mathrm{sdid}}\) is the two-sided SDiD unit--time normal-equation functional, and \(\phi_{\mathrm{mc}}\) is the rank-\(R\) completion functional; the comparison is not made by evaluating all methods at externally chosen weights. The exact-identification domain is
\[
\calF_m(R,\rho)
=\{\mathcal P:\phi_m(\mathcal P)=T_1^{-1}\one^\transpose(Y^{\mathrm{obs}}_{0,\mathrm{post}}-Z_0)
\text{ for every } Z_0 \text{ with } (X_0,X,Z,Z_0)\in\calM_R(P_{\mathrm{obs}})\}.
\]
Thus \(\calF_{\mathrm{convex}}\) and \(\calF_{\mathrm{affine}}\) are not merely pre-period balance domains: they are the laws on which the resulting convex or affine counterfactual post mean is invariant over all admissible rank-\(R\) completions. The pre-period balance rules define \(\phi_m\); exact identification requires equality to the ATT across \(\calM_R(P_{\mathrm{obs}})\).

The adjacent-pair certificates use one common normal-equation notation obtained from these objectives. For convex SCM and SDiD, first restrict to a fixed active simplex face and eliminate the affine equality constraint; the resulting local coefficient spaces are \(E_{\mathrm{convex}}\subseteq\R^{N_0}\) and \(E_{\mathrm{sdid}}\subseteq\R^{N_0+T_0+2}\). For affine/ridge ASCM, \(E_{\mathrm{affine}}=\R^{N_0+1}\). For matrix completion, \(E_{\mathrm{mc}}\) is the finite-dimensional tangent-coordinate space of \(Q_uM_{\mathrm{mc}}Q_t\) in the rank-\(R\) factor chart. In every case the local population problem has the form
\[
\beta_m^\star\in\arg\min_{\beta\in E_m}
\frac12\|B_m\beta-r_m\|_2^2+\frac12\rho_m\beta^\transpose D_m\beta,\qquad
\phi_m(\mathcal P)=\bar Y^{\mathrm{obs}}_0-\ell_m^\transpose\beta_m^\star,
\]
where \(B_m\) is exactly the residualized design matrix appearing in the displayed objective for method \(m\), \(r_m\) is the corresponding treated or donor target vector, \(D_m\) is the displayed penalty matrix after constraint elimination, and \(\ell_m\) is the post-period ATT evaluation vector. For \(a\prec b\), write the higher method's residualized and penalized population system, after ordering coefficients as lower coordinates followed by additional higher coordinates, as
\[
G_b(\mathcal P)=
\begin{pmatrix}
G_a & H_{a,b}\\
H_{a,b}^\transpose & K_{a,b}
\end{pmatrix},\qquad
c_b(\mathcal P)=\binom{c_a}{d_{a,b}},\qquad
\ell_b(\mathcal P)=\binom{\ell_a}{e_{a,b}}.
\]
Here \(G_a=B_a^\transpose B_a+\rho_aD_a\), \(c_a=B_a^\transpose r_a\), and \(\ell_a\) is the linear post-period evaluation vector for the lower functional; \(B_a,r_a,D_a,\ell_a\) are respectively the lower method's residualized moment matrix, target-moment vector, penalty matrix, and post-period evaluation vector. The Moore--Penrose inverse convention is used throughout. Define
\[
\Omega_{a,b}=K_{a,b}-H_{a,b}^\transpose G_a^\dagger H_{a,b},\quad
\kappa^{\mathrm{mom}}_{a,b}=d_{a,b}-H_{a,b}^\transpose G_a^\dagger c_a,\quad
\kappa^{\mathrm{att}}_{a,b}=e_{a,b}-H_{a,b}^\transpose G_a^\dagger \ell_a,
\]
and set
\[
S^{\mathrm{raw}}_{a,b,R}(\mathcal P)=
\begin{pmatrix}
\Omega_{a,b} & \kappa^{\mathrm{mom}}_{a,b} & \kappa^{\mathrm{att}}_{a,b}\\
(\kappa^{\mathrm{mom}}_{a,b})^\transpose & 0 & 0\\
(\kappa^{\mathrm{att}}_{a,b})^\transpose & 0 & 0
\end{pmatrix},
\]
with \(R\) entering through the rank-\(R\) completion restriction and through the matrix-completion block \(B_{\mathrm{mc}}\). This raw Schur block is only the computational input. Let \(\calH^{\mathrm{att}}_{a,b,R}(\mathcal P)\) be the quotient subspace of added higher-method coordinates that are reachable by rank-\(R\) untreated-completion perturbations after the lower method's fitted counterfactual is held fixed and that can affect the post-period ATT evaluation. Let \(\Pi^{\mathrm{att}}_{a,b,R}\) denote the orthogonal projection onto this subspace, and define the ATT-projected Riesz certificate
\[
C^{\mathrm{att}}_{a,b,R}(\mathcal P)
=\Pi^{\mathrm{att}}_{a,b,R}
\Bigl(\kappa^{\mathrm{att}}_{a,b}-\Omega_{a,b}^{\dagger}\kappa^{\mathrm{mom}}_{a,b}\Bigr).
\]
Residual variance in added coordinates is therefore harmless unless it changes this projected Riesz representer. The adjacent pairs are convex--affine, affine--SDiD, and SDiD--MC.

It remains to pin down the projection space as finite-dimensional linear algebra rather than as a verbal ``ATT-relevant quotient.'' Fix an admissible completion \(M^\star\in\calM_R(P_{\mathrm{obs}})\), let \(\widetilde M^\star=U\Sigma V^\transpose\) have residual rank \(r\le R\), and define the linearized rank-\(R\) completion tangent space
\[
\mathfrak T_R(M^\star)=\{\Delta\in\R^{(N_0+1)\times(T_0+T_1)}:
\Delta_{\mathrm{obs}}=0,
(I-UU^\transpose)Q_u\Delta Q_t(I-VV^\transpose)=0\}.
\]
Here \(\Delta_{\mathrm{obs}}=0\) means that the treated pre-period block and all donor blocks are held fixed. The local tangent span is \(\mathfrak T_R(\mathcal P)=\operatorname{span}_{M^\star\in\calM_R(P_{\mathrm{obs}})}\mathfrak T_R(M^\star)\). For each adjacent pair \(a\prec b\), let \(E_a=\R^{q_a}\) and \(E_b=\R^{q_{a,b}}\) be the lower-coordinate and added-coordinate Euclidean spaces in the block normal equations. Let \(J_b:\mathfrak T_R(\mathcal P)\to E_b\) map an untreated-completion perturbation to the induced perturbation of the higher method's added coordinates, and let \(A_a:\mathfrak T_R(\mathcal P)\to E_a\) map it to the lower method's fitted counterfactual coordinates. The ATT-relevant added-coordinate quotient is the concrete Euclidean quotient
\[
\calH^{\mathrm{att}}_{a,b,R}(\mathcal P)
=J_b\bigl(\ker A_a\bigr)\big/
\{h\in J_b(\ker A_a):(\kappa^{\mathrm{att}}_{a,b})^\transpose h=0\}.
\]
We identify this quotient with the orthogonal complement of the null subspace inside \(J_b(\ker A_a)\subseteq E_b\), using the Euclidean inner product on the added-coordinate space \(E_b\). The projection \(\Pi^{\mathrm{att}}_{a,b,R}\) is the Euclidean orthogonal projection onto this representative subspace; equivalently, it is the projection that discards exactly those rank-\(R\) completion directions that are invisible both to the lower fitted counterfactual and to the ATT evaluation.

Equivalently, the certificate is a finite algorithm. Its inputs are \(X_0,X,Z,Y^{\mathrm{obs}}_{0,\mathrm{post}}\), \(R\), the active simplex faces for the convex and SDiD programs, and \(\rho\). Step 1 forms the four objective-specific triples \((B_m,r_m,D_m)\) and evaluation vectors \(\ell_m\) with dimensions \(B_m\in\R^{s_m\times q_m}\), \(r_m\in\R^{s_m}\), \(D_m\in\R^{q_m\times q_m}\), and \(\ell_m\in\R^{q_m}\). Step 2 embeds the lower coordinates in the higher coordinates for each adjacent pair and computes \(G_a,H_{a,b},K_{a,b},c_a,d_{a,b},\ell_a,e_{a,b}\). Step 3 enumerates the rank-\(R\) completion tangent span \(\mathfrak T_R(\mathcal P)\), pushes it through \(A_a\) and \(J_b\), and constructs the Euclidean representative of \(\calH^{\mathrm{att}}_{a,b,R}(\mathcal P)\). Step 4 returns \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\) and declares equality exactly when its Euclidean norm is zero; if a Schur block is singular, all inverses in Step 2 are Moore--Penrose inverses and the zero test is still the projected norm, not raw Schur rank.

\begin{quote}
\begin{verbatim}
(qid, specialization, p, assignment, target, regression)
= (panel_sdid_mc_id, v1, unrestricted pre-period length T0 >= 2,
   single treated block after T0 with N0 >= 2 donor units and one treated
   aggregate row, ATT over post periods T1 >= 1,
   finite-dimensional population identifying functionals generated by
   convex SCM, affine/ridge ASCM, two-sided SDiD, and rank-R matrix completion).
\end{verbatim}
\end{quote}

\section{Assumptions}

\begin{assumption}[Panel dimensions and nondegenerate design]\label{ass:panel-dimensions}
The panel has \(N_0\ge2\), \(T_0\ge2\), and \(T_1\ge1\). The observed donor pre-period matrix \(X\), donor post-period matrix \(Z\), and treated pre-period vector \(X_0\) are finite real arrays, and all Gram and Schur-complement matrices named in the results use Moore--Penrose inverses when singular.
\end{assumption}

\begin{assumption}[Bounded-rank interactive fixed effects]\label{ass:rank-r-ife}
After additive unit and time effects are removed by \(Q_u\) and \(Q_t\), every admissible untreated completion satisfies \(\operatorname{rank}(\widetilde M)\le R\) for a fixed integer \(R\ge0\).
\end{assumption}

\begin{assumption}[Common ATT target and no anticipation]\label{ass:common-att}
Treatment starts only in the post-period block for the treated aggregate row, donor rows are untreated in all periods, observed pre-period outcomes equal untreated outcomes, and the target is \(\tau_{\mathrm{ATT}}=T_1^{-1}\one_{T_1}^\transpose(Y^{\mathrm{obs}}_{0,\mathrm{post}}-Z_0)\).
\end{assumption}

\begin{assumption}[Declared regularization paths]\label{ass:regularization-paths}
The convex-SCM, ridge-ASCM, SDiD unit-quadratic, SDiD time-quadratic, and nuclear-norm matrix-completion functionals use deterministic penalty sequences \(\eta_{\mathrm{scm}},\eta_{\mathrm{ascm}},\eta_{\mathrm{sdid},u},\eta_{\mathrm{sdid},t},\eta_{\mathrm{mc}}\) with fixed limits \(\rho_{\mathrm{scm}},\rho_{\mathrm{ascm}},\rho_{\mathrm{sdid},u},\rho_{\mathrm{sdid},t},\rho_{\mathrm{mc}}\). A limiting functional is compared only after these limits are fixed in the design package \(\mathcal P=(P_{\mathrm{obs}},\rho)\); the observable panel law remains \(P_{\mathrm{obs}}\).
\end{assumption}

\begin{assumption}[Exact-balance corner]\label{ass:exact-balance-corner}
There exists \(w\in\Delta_{N_0}\) such that \(X_0=X^\transpose w\), and the common-corner donor post relation is valid: every admissible rank-\(R\) completion used for the comparison has \(Z_0=Z^\transpose w\). In this corner the convex SCM counterfactual is \(Z^\transpose w\).
\end{assumption}

\begin{assumption}[Common-corner normal equations]\label{ass:common-corner-normal-equations}
At the exact-balance corner in Assumption~\ref{ass:exact-balance-corner}, the declared ASCM/ridge, SDiD, and matrix-completion population optimization problems have the common counterfactual \(Z^\transpose w\) as their ATT-evaluation solution: the ASCM residual correction is zero at the affine extension of \(w\), the SDiD unit--time normal equations admit unit weights \(w\) and time weights with total post contrast one, and the rank-\(R\) completion rule uniquely evaluates the treated post block as \(Z^\transpose w\).
\end{assumption}

\begin{assumption}[Additive zero-rank corner]\label{ass:additive-corner}
The de-meaned untreated matrix is zero, \(\widetilde M=0\), equivalently \(Y^0_{it}=\alpha_i+\lambda_t\) for all units and periods.
\end{assumption}

\begin{assumption}[Observable lattice certificate]\label{ass:lattice-certificate}
For each adjacent pair \(a\prec b\) in \(\{\mathrm{convex},\mathrm{affine},\mathrm{sdid},\mathrm{mc}\}\), the block matrices \(G_a,H_{a,b},K_{a,b},c_a,d_{a,b},\ell_a,e_{a,b}\) are the residualized population moment, penalty, and post-evaluation matrices defined in Section~3 from \(\mathcal P\). The raw Schur input \(S^{\mathrm{raw}}_{a,b,R}(\mathcal P)\), the linearized rank-\(R\) completion space \(\mathfrak T_R(\mathcal P)\), the maps \(J_b\) and \(A_a\), the ATT-relevant quotient representative \(\calH^{\mathrm{att}}_{a,b,R}(\mathcal P)\), the Euclidean projection \(\Pi^{\mathrm{att}}_{a,b,R}\), and the projected certificate \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\) are exactly the objects displayed in Section~3, using Moore--Penrose inverses and the declared penalty limits.
\end{assumption}

\begin{assumption}[Minimal witness class]\label{ass:minimal-witness}
A strict-separation witness is nondegenerate if the observed donor pre-period covariance has positive rank, the treated pre-period vector is not identically zero after demeaning, the target ATT contrast is finite, and the two adjacent functionals have different finite limits on an open neighborhood of the displayed observable law.
\end{assumption}

\begin{assumption}[Adjacent witness dimensions]\label{ass:adjacent-witness-dimensions}
The three adjacent strict-inclusion claims use separate minimal dimension requirements. For the convex--affine witness, \(N_0\ge2\), \(T_0\ge2\), \(T_1\ge1\), and the treated pre-period vector lies in the affine donor span but outside the convex donor hull. For the affine--SDiD witness, \(N_0\ge2\), \(T_0\ge3\), \(T_1\ge1\), and the residualized pre-period time span has at least one direction orthogonal to the affine donor normal equations but not orthogonal to the SDiD time-weight normal equations. For the SDiD--MC witness, \(R\ge1\), \(N_0+1\ge R+2\), \(T_0+T_1\ge R+2\), \(T_0\ge R+1\), and \(T_1\ge1\), so that a rank-\(R\) completion determinant can identify the treated post block while two-sided SDiD balance leaves an ATT-relevant tangent direction unresolved.
\end{assumption}

\section{Main results}

\begin{theorem}[Theorem 1: convex exact balance is the common corner]\label{thm:convex-corner}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:common-att}, \ref{ass:regularization-paths}, \ref{ass:exact-balance-corner}, and \ref{ass:common-corner-normal-equations}, the declared convex SCM, affine/ridge ASCM, two-sided SDiD, and rank-\(R\) matrix-completion population functionals all identify the same ATT functional:
\[
\phi_{\mathrm{convex}}(\mathcal P)=\phi_{\mathrm{affine}}(\mathcal P)
=\phi_{\mathrm{sdid}}(\mathcal P)=\phi_{\mathrm{mc}}(\mathcal P)=
\tau_{\mathrm{ATT}}
=T_1^{-1}\one^\transpose\{Y^{\mathrm{obs}}_{0,\mathrm{post}}-Z^\transpose w\}.
\]
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is not the flagship novelty; it is the sanity anchor tying the proposed lattice to \citet{AbadieDiamondHainmueller2010}, \citet{DoudchenkoImbens2016}, \citet{BenMichaelFellerRothstein2021}, \citet{ArkhangelskyAtheyHirshbergImbensWager2021}, and \citet{AtheyBayatiDoudchenkoImbensKhosravi2021}. The epsilon-gap is that those papers do not state the exact-balance corner as a common solution of the ASCM, SDiD, and matrix-completion normal equations inside a four-node functional lattice. (b) The concrete consumer is \citet{Abadie2021}: this theorem identifies the regime where the usual convex-hull diagnostic is enough and the more elaborate methods should reduce to a robustness check rather than a different estimand.

\begin{conjecture}[Conjecture 1: strict four-node identifying-functional lattice (NOT YET PROVED)]\label{conj:strict-lattice}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:rank-r-ife}, \ref{ass:common-att}, \ref{ass:regularization-paths}, \ref{ass:minimal-witness}, and \ref{ass:adjacent-witness-dimensions}, the exact-identification domains satisfy
\[
\calF_{\mathrm{convex}}(R,\rho)\subsetneq
\calF_{\mathrm{affine}}(R,\rho)\subsetneq
\calF_{\mathrm{sdid}}(R,\rho)\subsetneq
\calF_{\mathrm{mc}}(R,\rho)
\]
whenever the corresponding adjacent-pair dimension clause in Assumption~\ref{ass:adjacent-witness-dimensions} is satisfied. Moreover, each strict inclusion has a minimal nondegenerate witness: convex--affine at the affine-outside-hull clause, affine--SDiD at the extra time-span clause, and SDiD--MC at the rank-\(R\) determinant-completion clause. In each case the adjacent ATT functionals differ by an explicit determinant ratio of the appropriate pre-period Gram or Schur-complement block.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest papers are \citet{DoudchenkoImbens2016} for relaxing SCM restrictions, \citet{BenMichaelFellerRothstein2021} for ridge signed-weight augmentation, \citet{ArkhangelskyAtheyHirshbergImbensWager2021} for two-sided SDiD, \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} for nuclear-norm matrix completion, and \citet{AtheyBayatiImbensQu2019} for comparing regression, synthetic-control, and matrix-completion predictors by ensembling. The flagship epsilon-gap is that each paper establishes, compares, or combines nodes of the diagram, while the conjecture asserts all inclusions, all strict separations, and minimal rank witnesses in one common bounded-rank IFE model. (b) Resolving it would give the \citet{DoudchenkoImbens2016} synthesis a theorem-level hierarchy rather than a menu of estimator restrictions, and would tell users of ASCM and SDiD when disagreement is estimand-level rather than finite-sample noise.

\begin{conjecture}[Conjecture 2: Schur-complement certificate for equality and separation (NOT YET PROVED)]\label{conj:certificate}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:rank-r-ife}, \ref{ass:common-att}, \ref{ass:regularization-paths}, \ref{ass:lattice-certificate}, and \ref{ass:minimal-witness}, an adjacent pair of functionals \(a\prec b\) agrees on the ATT for every rank-\(R\) completion compatible with \(P_{\mathrm{obs}}\) if and only if
\[
C^{\mathrm{att}}_{a,b,R}(\mathcal P)=0.
\]
If \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\ne0\), then the normalized projected Riesz vector
\[
v_{a,b,R}(\mathcal P)
=C^{\mathrm{att}}_{a,b,R}(\mathcal P)/
\|C^{\mathrm{att}}_{a,b,R}(\mathcal P)\|_2
\]
selects a direction in \(J_b(\ker A_a)\). Any tangent perturbation \(\Delta\in\ker A_a\) with \(J_b\Delta=v_{a,b,R}(\mathcal P)\) and satisfying the nondegeneracy conditions in Assumption~\ref{ass:minimal-witness} produces a local path of observable laws on which the two adjacent ATT functionals differ to first order. A nonzero raw Schur block \(S^{\mathrm{raw}}_{a,b,R}(\mathcal P)\) by itself is not a separation witness unless it has nonzero projection through \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{AbadieLHour2021} and \citet{BenMichaelFellerRothstein2021} show that penalties and signed extrapolation change weight geometry, \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} show that nuclear-norm recovery changes identification restrictions, and \citet{AtheyBayatiImbensQu2019} shows that cross-validated ensembles can outperform individual causal-panel predictors. The epsilon-gap is the proposed ATT-projected equality/separation certificate \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\): it is not a predictive model-selection criterion, because it ignores harmless residual higher-coordinate variance and tests only whether the higher method's extra Riesz representer changes the ATT functional. (b) The concrete consumer is empirical robustness reporting based on \citet{Abadie2021}: instead of reporting several synthetic-control estimates as if they targeted the same ATT, a paper could report whether \(C^{\mathrm{att}}_{a,b,R}(\mathcal P)\) certifies equality or flags estimand separation.

\section{Sanity-check corollaries}

\begin{corollary}[Zero-rank affine/SDiD/MC collapse, with convex only under hull support]\label{cor:additive-collapse}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:common-att}, and \ref{ass:additive-corner}, the affine/ridge ASCM, SDiD, and rank-\(R\) matrix-completion functionals collapse to the same two-way-fixed-effect DiD counterfactual because the de-meaned rank component is zero and the remaining additive row and column effects are removed by the common affine or double-difference normalization. The convex SCM functional joins this collapse only under the additional convex-hull part of Assumption~\ref{ass:exact-balance-corner}, since additive zero rank alone does not imply that the treated row lies in the donor convex hull.
\end{corollary}

\begin{corollary}[Exact convex balance recovers the SCM corner]\label{cor:convex-scm-corner}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:common-att}, \ref{ass:regularization-paths}, \ref{ass:exact-balance-corner}, and \ref{ass:common-corner-normal-equations}, Conjecture~\ref{conj:strict-lattice} must reduce to Theorem~\ref{thm:convex-corner}: the first lattice inclusion is equality at \(\mathcal P\) because \(X_0=X^\transpose w\) with \(w\in\Delta_{N_0}\), the declared higher-method normal equations select the common ATT evaluation, and \(Z_0=Z^\transpose w\) for every admissible completion make signed extrapolation, time reweighting, and rank completion unnecessary for the missing treated post mean.
\end{corollary}

\begin{corollary}[Exact convex balance zeros the adjacent certificates]\label{cor:convex-certificate-zero}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:common-att}, \ref{ass:regularization-paths}, \ref{ass:exact-balance-corner}, \ref{ass:common-corner-normal-equations}, and \ref{ass:lattice-certificate}, the exact convex-balance corner has
\[
C^{\mathrm{att}}_{\mathrm{convex},\mathrm{affine},R}(\mathcal P)
=C^{\mathrm{att}}_{\mathrm{affine},\mathrm{sdid},R}(\mathcal P)
=C^{\mathrm{att}}_{\mathrm{sdid},\mathrm{mc},R}(\mathcal P)=0.
\]
The reduction is concrete: \(A_a\Delta=0\) and the common counterfactual \(Z^\transpose w\) make \((\kappa^{\mathrm{att}}_{a,b})^\transpose J_b\Delta=0\) for every rank-\(R\) tangent perturbation, so \(\calH^{\mathrm{att}}_{a,b,R}(\mathcal P)\) is the zero representative subspace and the Euclidean projection of the Riesz vector vanishes.
\end{corollary}

\begin{corollary}[Harmless higher-coordinate variance]\label{cor:harmless-extra-coordinate}
Under Assumptions~\ref{ass:panel-dimensions}, \ref{ass:rank-r-ife}, \ref{ass:common-att}, \ref{ass:regularization-paths}, and \ref{ass:lattice-certificate}, if \(S^{\mathrm{raw}}_{a,b,R}(\mathcal P)\ne0\) but \(\Pi^{\mathrm{att}}_{a,b,R}\bigl(\kappa^{\mathrm{att}}_{a,b}-\Omega_{a,b}^{\dagger}\kappa^{\mathrm{mom}}_{a,b}\bigr)=0\), then Conjecture~\ref{conj:certificate} predicts equality of the adjacent ATT functionals despite residual variance in the added higher-method coordinates.
\end{corollary}

\section{Proof-sketch route}

The mathematical route is finite-dimensional linear algebra. First quotient the observed panel by additive unit and time effects, so each estimator becomes one of the explicit optimization problems in Section~3: a constrained convex-weight quadratic program, an affine ridge quadratic program, a two-sided SDiD quadratic program, or a rank-constrained nuclear-norm completion. Theorem~\ref{thm:convex-corner} is the direct substitution identity \(X_0=X^\transpose w\), the common-corner normal-equation check for the declared ASCM/SDiD/MC functionals, and preservation of the donor post linear relation. For Conjecture~\ref{conj:strict-lattice}, the weak-inclusion algebra should be proved pairwise on fixed active faces: if \(\beta_a^\star=G_a^\dagger c_a\) is the lower solution, the higher KKT equations reduce after Schur elimination to
\[
\Omega_{a,b}h=\kappa^{\mathrm{mom}}_{a,b},\qquad
\phi_b-\phi_a
=-\bigl(\kappa^{\mathrm{att}}_{a,b}-\Omega_{a,b}^\dagger\kappa^{\mathrm{mom}}_{a,b}\bigr)^\transpose h
\]
modulo directions orthogonal to \(J_b(\ker A_a)\). Thus lower exact identification can force higher exact identification only when the ATT-projected Riesz residual vanishes; strictness comes from enumerating the smallest nondegenerate cases: convex versus affine at \(N_0=2,T_0=2\), affine versus SDiD at \(N_0=2,T_0=3\) where time reweighting removes a row-span defect, and SDiD versus rank-\(R\) completion at \(R=1\) with a missing treated-post block uniquely determined by a low-rank determinant identity but not by two-sided balance. For Conjecture~\ref{conj:certificate}, compute the displayed block normal equations for each adjacent pair, form the raw Schur input \(S^{\mathrm{raw}}_{a,b,R}(\mathcal P)\), build the local rank-\(R\) tangent span \(\mathfrak T_R(\mathcal P)\), and project the induced Riesz vector onto the Euclidean quotient representative \(\calH^{\mathrm{att}}_{a,b,R}(\mathcal P)\); equality is the vanishing of this projected vector, while the smallest witnesses come from lifting the normalized projected Riesz vector through \(J_b(\ker A_a)\).

\section{Honest scope flags}

Theorem~\ref{thm:convex-corner} is intended as routine algebra and a sanity anchor, not the contribution. Conjectures~\ref{conj:strict-lattice} and \ref{conj:certificate} are the open kernel: the determinant-ratio formulas and the minimality of the three adjacent dimension clauses may need adjustment after small-case enumeration. The proposal intentionally withdraws the archived angle-0 claim that a single spectral threshold \(R_\star\) simultaneously decides equality among SDiD, ASCM, and matrix completion; this pivot replaces that threshold object with adjacent-pair Schur/Riesz projections and a strict lattice. The regularization-path normalization is a genuine risk: if two published papers use incompatible penalty scaling, the lattice must state separate fixed-penalty and vanishing-penalty versions rather than one universal statement. The matrix-completion node is stated as uniqueness over rank-\(R\) completions, not as a claim that a particular nuclear-norm algorithm always finds the correct completion.

\section{Iteration trail}

\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial strict-lattice draft after archived angle 0 rejected the single spectral-threshold kernel; prior verdict: none.
\item v2 (revise) --- redefined the lattice nodes as exact-identification domains over rank-\(R\) completions, made the Schur certificate an explicit block matrix on \(\mathcal P=(P_{\mathrm{obs}},\rho)\), and repaired the zero-rank collapse corollary; prior verdict: REVISE.
\item v3 (revise) --- restated Theorem~\ref{thm:convex-corner} for the declared ASCM/SDiD/MC normal-equation functionals and replaced the raw Schur iff in Conjecture~\ref{conj:certificate} with an ATT-projected Riesz certificate; prior verdict: REVISE.
\item v4 (revise) --- pinned down the rank-\(R\) tangent quotient, replaced the singular-direction language by a normalized Riesz-vector lift, split the witness dimension clauses by adjacent pair, and added the exact-balance zero-certificate corollary; prior verdict: REVISE.
\item v5 (revise) --- added the omitted ensemble-methods comparison, replaced generic method-function prose with explicit population optimization problems, stated the certificate as a finite-dimensional algorithm, and inserted the Schur-elimination identity in the proof sketch; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Abadie(2021)]{Abadie2021}
Abadie, Alberto. 2021. ``Using Synthetic Controls: Feasibility, Data Requirements, and Methodological Aspects.'' \emph{Journal of Economic Literature} 59(2): 391--425.

\bibitem[Abadie, Diamond, and Hainmueller(2010)]{AbadieDiamondHainmueller2010}
Abadie, Alberto, Alexis Diamond, and Jens Hainmueller. 2010. ``Synthetic Control Methods for Comparative Case Studies: Estimating the Effect of California's Tobacco Control Program.'' \emph{Journal of the American Statistical Association} 105(490): 493--505.

\bibitem[Abadie and L'Hour(2021)]{AbadieLHour2021}
Abadie, Alberto, and Jeremy L'Hour. 2021. ``A Penalized Synthetic Control Estimator for Disaggregated Data.'' \emph{Journal of the American Statistical Association} 116(536): 1817--1834.

\bibitem[Arkhangelsky and Imbens(2022)]{ArkhangelskyImbens2022}
Arkhangelsky, Dmitry, and Guido W. Imbens. 2022. ``Double-Robust Identification for Causal Panel Data Models.'' \emph{The Econometrics Journal} 25(3): 649--674.

\bibitem[Arkhangelsky et~al.(2021)]{ArkhangelskyAtheyHirshbergImbensWager2021}
Arkhangelsky, Dmitry, Susan Athey, David A. Hirshberg, Guido W. Imbens, and Stefan Wager. 2021. ``Synthetic Difference-in-Differences.'' \emph{American Economic Review} 111(12): 4088--4118.

\bibitem[Athey et~al.(2019)]{AtheyBayatiImbensQu2019}
Athey, Susan, Mohsen Bayati, Guido W. Imbens, and Zhaonan Qu. 2019. ``Ensemble Methods for Causal Effects in Panel Data Settings.'' \emph{AEA Papers and Proceedings} 109: 65--70.

\bibitem[Athey et~al.(2021)]{AtheyBayatiDoudchenkoImbensKhosravi2021}
Athey, Susan, Mohsen Bayati, Nikolay Doudchenko, Guido W. Imbens, and Khashayar Khosravi. 2021. ``Matrix Completion Methods for Causal Panel Data Models.'' \emph{Journal of the American Statistical Association} 116(536): 1716--1730.

\bibitem[Bai and Ng(2021)]{BaiNg2021}
Bai, Jushan, and Serena Ng. 2021. ``Matrix Completion, Counterfactuals, and Factor Analysis of Missing Data.'' \emph{Journal of the American Statistical Association} 116(536): 1746--1763.

\bibitem[Ben-Michael, Feller, and Rothstein(2021)]{BenMichaelFellerRothstein2021}
Ben-Michael, Eli, Avi Feller, and Jesse Rothstein. 2021. ``The Augmented Synthetic Control Method.'' \emph{Journal of the American Statistical Association} 116(536): 1789--1803.

\bibitem[Doudchenko and Imbens(2016)]{DoudchenkoImbens2016}
Doudchenko, Nikolay, and Guido W. Imbens. 2016. ``Balancing, Regression, Difference-in-Differences and Synthetic Control Methods: A Synthesis.'' NBER Working Paper 22791.

\bibitem[Ferman and Pinto(2021)]{FermanPinto2021}
Ferman, Bruno, and Cristine Pinto. 2021. ``Synthetic Controls with Imperfect Pretreatment Fit.'' \emph{Quantitative Economics} 12(4): 1197--1221.

\bibitem[Xu(2017)]{Xu2017}
Xu, Yiqing. 2017. ``Generalized Synthetic Control Method: Causal Inference with Interactive Fixed Effects Models.'' \emph{Political Analysis} 25(1): 57--76.
\end{thebibliography}

\end{document}
