% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_sdid\_mc\_id, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{panel\_sdid\_mc\_id} / \texttt{v1}%
  \\ \large\textit{A spectral rank certificate for equality and separation of SDiD, ASCM, and matrix-completion ATT functionals}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form panel anchor, not Q1 pool-mode.  The locked tuple is
\[
(qid,\ specialization,\ p,\ assignment,\ target,\ regression)
=
(\texttt{panel\_sdid\_mc\_id},\ \texttt{v1},\ p_{\mathrm{IFE}},\ \mathcal A_{\mathrm{cohort}},\ \tau_{\mathrm{ATT}},\ \mathcal R_{\mathrm{spec}}).
\]
Here \(p_{\mathrm{IFE}}=(T_0,T_1,N_0,C,R,\rho_N,\rho_T,\lambda_{\mathrm{ascm}},\lambda_{\mathrm{mc}})\) fixes \(T_0\ge 2\) pre-periods, \(T_1\ge 1\) post-periods, \(N_0\ge 2\) donor units, \(C\ge 1\) treated adoption cohorts, untreated-factor rank bound \(R\), SDiD unit/time ridge sequences \(\rho_N,\rho_T\ge 0\), ASCM donor-side ridge augmentation sequence \(\lambda_{\mathrm{ascm}}\ge 0\), and matrix-completion nuclear-norm sequence \(\lambda_{\mathrm{mc}}\ge 0\).  The SDiD ridges \(\rho_N,\rho_T\) enter only the two-sided SDiD balancing equations; ASCM uses \(\lambda_{\mathrm{ascm}}\) for donor-weight regression augmentation and does not use \(\rho_N,\rho_T\).  The assignment \(\mathcal A_{\mathrm{cohort}}\) is absorbing cohort adoption: donor units are never treated and treated units in cohort \(c\) are untreated for \(t<T_c\) and treated for \(t\ge T_c\), with the single-cohort case \(C=1\) reproducing the original one-shock SDiD design.  The target \(\tau_{\mathrm{ATT}}\) is the cohort-size-weighted average of \(Y_{it}(1)-Y_{it}(0)\) over treated post-treatment cells.  The regression convention \(\mathcal R_{\mathrm{spec}}\) compares four population identifying functionals: two-sided SDiD weights chosen by quadratic balancing, ridge ASCM donor-side augmentation as in Ben-Michael--Feller--Rothstein with weights normalized to sum to one after the intercept correction, nuclear-norm matrix completion on the full observed untreated block with an explicit subgradient certificate, and staggered-SDiD cohort-time weighting, with all limits taken after centering by additive unit and time effects.

\begin{abstract}
Synthetic difference-in-differences, augmented synthetic control, and nuclear-norm matrix completion are often motivated by the same low-rank interactive fixed-effects model, but the literature does not give a sharp condition under which they define the same ATT functional or the same first-order estimator.  This proposal asks whether equality is governed by an observable finite-dimensional spectral certificate built from donor pre-period covariances, cohort-time regression contrasts, regularization strengths, and the matrix-completion subgradient block.  The flagship conjecture is a necessary-and-sufficient rank/span theorem: the ATT-residual certificate vanishes on the rank-\(R\) tangent cone exactly when SDiD, ASCM, MC, and staggered SDiD identify the same ATT, have the same influence function, and attain the same semiparametric variance bound.  A companion conjecture states that, outside the equality frontier, the first-order bias and influence-function directions differ in a computable way rather than merely producing different finite-sample algorithms.  Resolving the conjecture would give applied researchers a pre-analysis diagnostic for when SDiD, ASCM, and matrix completion are genuine robustness checks rather than three implementations of the same identifying restriction.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Low-rank panel methods are used precisely in applications where plain parallel trends is not credible and where the donor pool is rich enough to support synthetic comparisons.  In that regime, the empirical practice of reporting SDiD, ASCM, and matrix-completion estimates side by side is only informative if the methods are known to target different limits when their identifying restrictions fail differently.  At present, the leading papers prove consistency or asymptotic normality under method-specific sufficient conditions, but they do not characterize the finite-dimensional frontier at which the population identifying functionals coincide.

\paragraph{The main finding (proposed).}
The proposed headline result is Conjecture~\ref{conj:spectral-frontier}: after additive fixed effects are removed, estimator-level equality of SDiD, ridge ASCM, nuclear-norm matrix completion, and staggered SDiD is equivalent to the vanishing of an ATT-residual certificate on the rank-\(R\) untreated-factor tangent cone.  The same pulled-back kernel gives a sharp threshold \(R_\star(P_{\mathrm{obs}};\rho,\lambda)\) such that all rank-\(R\) untreated IFE completions share the same ATT functional, influence function, and asymptotic variance for \(R\le R_\star\), while for \(R>R_\star\) there is an open set of panels on which the limiting functionals or influence functions are pairwise distinct.

\paragraph{What is new.}
The novelty kernel is not another consistency theorem for one estimator.  Relative to \citet{ArkhangelskyAtheyHirshbergImbensWager2021}, \citet{AtheyBayatiDoudchenkoImbensKhosravi2021}, and \citet{BenMichaelFellerRothstein2021}, the proposal asks for a necessary-and-sufficient equality certificate for the induced ATT functionals and their first-order influence functions, expressed in primitive second moments, assignment weights, and penalty sequences.  The epsilon-gap is the move from separate sufficient assumptions to a sharp estimator-level equality/separation boundary, including strict-separation witnesses outside the boundary.

\paragraph{How it positions in the literature.}
This is a panel and linear-projection-methods proposal.  It lives at the intersection of synthetic control, SDiD, augmented SCM, matrix completion, staggered adoption, and interactive fixed effects, not in graphical exact-ID or partial-ID calculus.  It uses the panel-spectral language suggested by the ThmSmith catalogue but targets the low-rank causal-panel frontier opened by \citet{Xu2017}, \citet{AtheyBayatiDoudchenkoImbensKhosravi2021}, \citet{ArkhangelskyAtheyHirshbergImbensWager2021}, and \citet{ArkhangelskyImbensLeiLuo2024}.

\paragraph{Implications for the community.}
The concrete consumer is the applied synthetic-control workflow codified in \citet{Abadie2021}: researchers who currently treat ASCM, SDiD, and matrix completion as robustness checks would get a computable diagnostic saying when disagreement is expected from rank/span geometry rather than tuning noise.  If the conclusion is correct, empirical researchers should report the spectral equality certificate before interpreting cross-estimator agreement as design robustness.

\paragraph{How research benefits from the conclusion.}
Researchers should treat SDiD, ASCM, and matrix completion as distinct identifying checks only when the reported certificate fails; inside the equality region, they should report one common ATT functional and spend robustness effort on rank/span and penalty-path sensitivity instead.

\section{Related work}
\citet{AbadieDiamondHainmueller2010} and \citet{AbadieDiamondHainmueller2015} supply the convex-weight synthetic-control benchmark whose geometry later work relaxes.  \citet{Abadie2021} is the applied-methods reference that treats SCM diagnostics and donor-pool fit as central reporting objects, making a spectral equality diagnostic directly useful.  \citet{DoudchenkoImbens2016} rewrites SCM, DiD, and regression estimators as choices of intercept, sum, sign, and regularization restrictions; it motivates a hierarchy question but does not compare SDiD, ASCM, and matrix-completion population limits.  \citet{Xu2017} and \citet{GobillonMagnac2016} place synthetic controls inside interactive fixed-effects models, making rank and pre-period span the natural primitives for this proposal.

\citet{ArkhangelskyAtheyHirshbergImbensWager2021} introduces SDiD, combining unit and time weights and proving IFE consistency and asymptotic normality; it is the closest SDiD anchor, but it does not give a necessary-and-sufficient equality frontier against ASCM or matrix completion.  \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} develops nuclear-norm matrix completion for causal panels and explicitly notes that methods differ in how they impose identification, but it does not characterize when those different restrictions produce the same ATT functional.  \citet{BenMichaelFellerRothstein2021} introduces ASCM and ridge ASCM, exposing the signed-weight extrapolation route that must be compared against SDiD time weights and matrix-completion shrinkage.  \citet{AbadieLHour2021} shows that penalization changes synthetic-control geometry, supporting the proposal's focus on penalty-dependent population limits.

\citet{BaiNg2021} gives factor-imputation distribution theory for average and individual ATT under factor structure; it is adjacent because it supplies a matrix-completion-like inference route without the SDiD/ASCM equality question.  \citet{ArkhangelskyImbens2022} is a closer panel-identification comparator because it contrasts outcome-model and assignment-model routes and proves double-robust identification, but it does not compare SDiD, ASCM, and matrix-completion functionals through a common spectral equality frontier.  \citet{FermanPinto2021} shows that imperfect pre-treatment fit can bias SCM-type estimators and that demeaning can improve bias/variance, making strict separation outside the equality frontier empirically meaningful.  \citet{BenMichaelFellerRothstein2022} extends synthetic controls to staggered adoption with partial pooling, and \citet{ArkhangelskyImbensLeiLuo2024} develops design-robust panel weights for general treatment paths; these papers motivate the cohort-time part of the locked assignment but do not solve the rank/span equality certificate.  \citet{ArkhangelskySamkov2024} proposes Sequential SDiD and proves oracle-OLS equivalence under a linear IFE route; it is orthogonal to the present frontier because oracle OLS equivalence is within one sequential estimator, whereas the proposed certificate compares SDiD, ASCM, MC, and staggered population functionals.  \citet{ClarkePailanirAtheyImbens2024} documents SDiD and staggered-SDiD implementation in Stata, making clear why applied workflows need an estimator-comparison diagnostic; it is computational and expository rather than a necessary-and-sufficient equivalence theorem.  The in-repository prior art is ThmSmith `doc/API.md` Section 1 on panel theorems, especially Q1 minimal-basis, Q1 staggered minimal-basis, and Q1 spectral-threshold/phase-transition entries; those catalogue entries analyze residualized regression bases and panel spectral thresholds, but none states an equality/separation theorem for SDiD, ASCM, and nuclear-norm matrix completion.
\citet{BorusyakJaravelSpiess2024} derives robust and efficient imputation estimators for staggered DiD and event studies under additive parallel-trends restrictions; it is the closest efficiency-frontier comparator, but it does not handle the bounded-rank IFE geometry or cross-estimator SDiD/ASCM/MC equality.

\section{Formal setup}
There are \(N_0\) donor units and treated cohorts \(c=1,\ldots,C\).  Time is split into \(T_0\) pre-periods and \(T_1\) post-periods.  Untreated potential outcomes satisfy
\[
Y_{it}(0)=\alpha_i+\delta_t+\ell_i^\transpose f_t+\varepsilon_{it},
\qquad
\ell_i,f_t\in\R^R,
\]
with rank bound \(R\) after removing additive unit and time effects.  Treatment is absorbing by cohort: \(D_{it}=1\{t\ge T_c\}\) for treated cohort \(c\), and \(D_{it}=0\) for donors.  The target is
\[
\tau_{\mathrm{ATT}}
=\sum_{c=1}^C \pi_c\,\frac{1}{|\mathcal T_c^+|}\sum_{t\in\mathcal T_c^+}
\E[Y_{it}(1)-Y_{it}(0)\mid i\in c],
\]
where \(\pi_c\) is the treated cohort share and \(\mathcal T_c^+=\{t:t\ge T_c\}\).  The cohort-specific target is
\[
\tau_{\mathrm{ATT},c}
=\frac{1}{|\mathcal T_c^+|}\sum_{t\in\mathcal T_c^+}
\E[Y_{it}(1)-Y_{it}(0)\mid i\in c].
\]

Let \(M_{\mathrm{pre}}\in\R^{N_0\times T_0}\) be the additive-FE-residualized donor pre-period outcome matrix.  Let \(g_c\in\R^{T_0}\) be the residualized pre-period treated-cohort mean for cohort \(c\), and let \(h_c\in\R^{T_0}\) be the Riesz representer, in the Hilbert space \(\calH_{\mathrm{pre}}=\operatorname{span}\{M_{i,\mathrm{pre}}:i\le N_0\}\) with inner product induced by donor pre-period second moments, of the residualized post-period cohort-time regression contrast whose donor prediction is needed for \(\tau_{\mathrm{ATT}}\).  Define the donor pre-period covariance \(S=M_{\mathrm{pre}}^\transpose M_{\mathrm{pre}}/N_0\), the donor-unit covariance \(\Sigma_N=M_{\mathrm{pre}}M_{\mathrm{pre}}^\transpose/T_0\), the pre-time covariance \(\Sigma_T=M_{\mathrm{pre}}^\transpose M_{\mathrm{pre}}/N_0\), the cohort contrast matrix \(G=[g_1,\ldots,g_C]\), the post-regression loading target \(H=[h_1,\ldots,h_C]\), and the mismatch matrix \(B=G-H\).  The cohort-specific single-shock functionals are \(\phi_{\mathrm{sdid},c}(Q)\), \(\phi_{\mathrm{ascm},c}(Q)\), and \(\phi_{\mathrm{mc},c}(Q)\); their pooled versions are \(\phi_{\mathrm{sdid}}(Q)=\sum_c\pi_c\phi_{\mathrm{sdid},c}(Q)\), \(\phi_{\mathrm{ascm}}(Q)=\sum_c\pi_c\phi_{\mathrm{ascm},c}(Q)\), and \(\phi_{\mathrm{mc}}(Q)=\sum_c\pi_c\phi_{\mathrm{mc},c}(Q)\).  The staggered functional \(\phi_{\mathrm{stag}}(Q)\) is defined separately by the cohort-time weights in \(\mathcal R_{\mathrm{spec}}\) and is not assumed to equal the pooled single-shock SDiD functional when \(C>1\).

For each cohort \(c\), let \(r^N_c\in\R^{N_0}\) be the donor-side representer of the treated pre-period profile and let \(r^T_c\in\R^{T_0}\) be the time-side representer of the donor post-period contrast.  The population SDiD weights \((\omega_{\mathrm{sdid},c},\lambda_{\mathrm{sdid},c})\) are the selected minimum-norm solutions to
\[
\begin{bmatrix}
\Sigma_N+\rho_N I_{N_0} & \one\\
\one^\transpose & 0
\end{bmatrix}
\begin{bmatrix}\omega_{\mathrm{sdid},c}\\ \nu_c\end{bmatrix}
=
\begin{bmatrix}r^N_c\\ 1\end{bmatrix},
\qquad
\begin{bmatrix}
\Sigma_T+\rho_T I_{T_0} & \one\\
\one^\transpose & 0
\end{bmatrix}
\begin{bmatrix}\lambda_{\mathrm{sdid},c}\\ \kappa_c\end{bmatrix}
=
\begin{bmatrix}r^T_c\\ 1\end{bmatrix}.
\]
These equations are the population version of the quadratic unit-weight and time-weight balancing convention in \(\mathcal R_{\mathrm{spec}}\), and they induce the contrast row \(c_{\mathrm{sdid},c}\in\R^{1\times d}\).  For staggered SDiD, each eligible cohort-time cell \((c,t)\) has an admissible comparison set \(\mathcal E_{ct}\) of never-treated and not-yet-treated units, assignment weight \(a_{ct}\), and KKT systems of the same form with \(\Sigma_N,\Sigma_T,r^N_c,r^T_c\) replaced by \(\Sigma_{N,ct},\Sigma_{T,ct},r^N_{ct},r^T_{ct}\) computed on \(\mathcal E_{ct}\).  The staggered row is \(c_{\mathrm{stag}}=\sum_{c,t}a_{ct}c_{\mathrm{stag},ct}\), so later-treated controls enter through explicit off-diagonal comparison-set blocks rather than through an unstated convention.

For each cohort \(c\), the ASCM population weights solve
\[
\omega_{\mathrm{ascm},c}
\in\arg\min_{\omega:\one^\transpose\omega=1}
\|g_c-M_{\mathrm{pre}}^\transpose\omega\|_2^2+\lambda_{\mathrm{ascm}}\|\omega\|_2^2,
\]
with the intercept-corrected outcome regression augmentation evaluated at the same centered coordinates.  Let \(Y\) be the additive-FE-centered observed outcome matrix, let \(\Omega\) be the mask of observed untreated donor, pre-treatment treated, and eligible not-yet-treated cells, and let \(\mathcal P_\Omega\) be the coordinate projection onto that mask.  Let \(\Theta\) be the additive-FE-centered untreated mean matrix.  The matrix-completion population limit is the selected pair \((\widehat \Theta_{\mathrm{mc}},Z_{\mathrm{mc}})\) satisfying
\[
\widehat \Theta_{\mathrm{mc}}
\in\arg\min_{\Theta}
\frac12\|\mathcal P_\Omega(\Theta-Y)\|_F^2+\lambda_{\mathrm{mc}}\|\Theta\|_*,
\qquad
0\in\mathcal P_\Omega(\widehat \Theta_{\mathrm{mc}}-Y)+\lambda_{\mathrm{mc}} Z_{\mathrm{mc}},
\quad
Z_{\mathrm{mc}}\in\partial\|\widehat \Theta_{\mathrm{mc}}\|_* .
\]
If the nuclear-norm objective has multiple minimizers, \(\widehat \Theta_{\mathrm{mc}}\) is the unique minimizer with smallest Frobenius norm.  Given this \(\widehat \Theta_{\mathrm{mc}}\), \(Z_{\mathrm{mc}}\) is the unique minimum-Frobenius-norm element of the closed convex set of subgradients satisfying the displayed KKT inclusion; when \(\lambda_{\mathrm{mc}}=0\), set \(Z_{\mathrm{mc}}=0\).  This selection is part of the population functional, not an extra estimator.

Let \(d=(N_0+C)(T_0+T_1)-N_0-C-T_0-T_1+1\) be the dimension of the additive-FE-centered untreated-cell coordinate vector \(x=\operatorname{vec}_{0}(\Theta)\).  Let \(a_{\mathrm{att}}\in\R^{1\times d}\) be the row vector that extracts the target ATT contrast from \(x\), and let \(c_{\mathrm{sdid}},c_{\mathrm{ascm}},c_{\mathrm{stag}}\in\R^{1\times d}\) be the row vectors induced by the selected SDiD, ASCM, and staggered weights.  Under the active-face regularity assumption below, the selected MC map is directionally linear at \(Y\): for centered perturbations \(u\in\R^d\),
\[
\operatorname{vec}_{0}\{D\widehat \Theta_{\mathrm{mc}}[u]\}
=D_{\mathrm{mc}}u,\qquad
D_{\mathrm{mc}}
=\left(\mathcal P_\Omega+\lambda_{\mathrm{mc}}\mathcal H_{Z_{\mathrm{mc}}}\right)^{\dagger}\mathcal P_\Omega,
\]
where \(\mathcal H_{Z_{\mathrm{mc}}}\in\R^{d\times d}\) is the active-face derivative of the selected nuclear-norm subgradient and the Moore--Penrose inverse uses the same minimum-norm selection rule.  Define \(c_{\mathrm{mc}}=a_{\mathrm{att}}D_{\mathrm{mc}}\).  For each method \(m\in\{\mathrm{sdid},\mathrm{ascm},\mathrm{mc},\mathrm{stag}\}\), let \(\psi_m\) be the influence-function row obtained by applying \(c_m\) to the observed-cell score after the same additive-FE residualization, and let \(\psi_{\mathrm{eff}}\) be the canonical gradient for \(\tau_{\mathrm{ATT}}\) in the rank-\(R\) IFE completion model when it exists.  The ATT-residual and comparison certificate is the explicit block matrix
\[
C^{\mathrm{att}}_{\rho,\lambda}
=
\begin{bmatrix}
c_{\mathrm{sdid}}-a_{\mathrm{att}}\\
c_{\mathrm{ascm}}-a_{\mathrm{att}}\\
c_{\mathrm{mc}}-a_{\mathrm{att}}\\
c_{\mathrm{stag}}-a_{\mathrm{att}}\\
c_{\mathrm{sdid}}-c_{\mathrm{ascm}}\\
c_{\mathrm{sdid}}-c_{\mathrm{mc}}\\
c_{\mathrm{sdid}}-c_{\mathrm{stag}}\\
\mathcal P_\Omega D_{\mathrm{mc}}-\mathcal P_\Omega\\
\lambda_{\mathrm{mc}}\mathcal H_{Z_{\mathrm{mc}}}D_{\mathrm{mc}}
\end{bmatrix}
\in \R^{(7+2d)\times d}.
\]
The first four rows compare each induced functional to the target ATT row, the next three rows compare methods to each other, and the last two blocks are the differentiated MC mask and subgradient KKT equations, so the MC contribution is pinned to the selected nuclear-norm certificate rather than an arbitrary completion.  This is the certificate used below; the earlier pairwise-only certificate is intentionally not sufficient for equality to \(\tau_{\mathrm{ATT}}\).  Let \(P_{\mathrm{obs}}\) denote the observed law of outcomes and cohort assignment.  For each integer \(r\), let \(\mathcal C_r(P_{\mathrm{obs}})\) be the class of full potential-outcome laws \(Q\) that agree with \(P_{\mathrm{obs}}\) on observed cells, satisfy no anticipation and the locked cohort assignment, and have additive-FE-residualized untreated mean rank at most \(r\).

For a completion \(Q\) and integer \(r\), let \(\mathcal T_r(Q)\subset\R^d\) be the additive-FE-centered tangent cone generated by rank-at-most-\(r\) first-order perturbations \(L F^\transpose\), and let \(\Pi_r(Q)\) be any matrix with orthonormal columns spanning the linear hull of \(\mathcal T_r(Q)\).  The pulled-back rank-\(r\) certificate is
\[
K^{(r)}_{\rho,\lambda}(Q)
=
\Pi_r(Q)^\transpose
(C^{\mathrm{att}}_{\rho,\lambda})^\transpose C^{\mathrm{att}}_{\rho,\lambda}
\Pi_r(Q).
\]
The rank threshold is the maximal rank budget whose entire admissible tangent class is annihilated by this pullback,
\[
R_\star(P_{\mathrm{obs}};\rho,\lambda)
=
\max\{r:\ K^{(r)}_{\rho,\lambda}(Q)=0
\text{ for every }Q\in\mathcal C_r(P_{\mathrm{obs}})\},
\]
with \(R_\star=-1\) if the set is empty.  This definition compares matrices inside the same tangent coordinate space and therefore does not subtract unrelated kernels such as \(\ker(S+\rho_N I_{T_0})\) from \(\ker(C^{\mathrm{att}}_{\rho,\lambda})\).
Equality is therefore a statement about identified functionals over \(\mathcal C_R(P_{\mathrm{obs}})\), while \(C^{\mathrm{att}}_{\rho,\lambda}\), \(K^{(r)}_{\rho,\lambda}(Q)\), and \(R_\star(P_{\mathrm{obs}};\rho,\lambda)\) are computed from the observed moments, selected first-order certificate blocks, and the rank-\(r\) tangent pullback.

The separation region is the set of nondegenerate observed laws for which \(R>R_\star(P_{\mathrm{obs}};\rho,\lambda)\) and \(C^{\mathrm{att}}_{\rho,\lambda}\) has a nonzero restriction to \(\mathcal T_R(Q)\) for some admissible \(Q\).  Let \(\mathcal V_{\max}(K^{(R)}_{\rho,\lambda}(Q))\) be the unit sphere in the leading nonzero singular subspace of \(K^{(R)}_{\rho,\lambda}(Q)\); if the leading singular value has multiplicity greater than one, the whole leading subspace is retained.  For a direction \(v\in\mathcal T_R(Q)\), \(b_{\mathrm{sdid},\mathrm{mc}}(v;\rho_N,\rho_T,\lambda_{\mathrm{mc}})\) denotes the directional derivative at \(\eta=0\) of \(\phi_{\mathrm{sdid}}(Q_\eta)-\phi_{\mathrm{mc}}(Q_\eta)\), with analogous definitions for the other pairwise gaps and influence-function gaps.  A local submodel \(Q_\eta\) induces the perturbed observed law \(P_{\mathrm{obs},\eta}\) by applying the observation mask and cohort assignment to \(Q_\eta\).

\begin{quote}
Locked parameters: \((qid,\ specialization,\ p,\ assignment,\ target,\ regression)=(\texttt{panel\_sdid\_mc\_id},\ \texttt{v1},\ p_{\mathrm{IFE}},\ \mathcal A_{\mathrm{cohort}},\ \tau_{\mathrm{ATT}},\ \mathcal R_{\mathrm{spec}})\), where \(p_{\mathrm{IFE}}=(T_0,T_1,N_0,C,R,\rho_N,\rho_T,\lambda_{\mathrm{ascm}},\lambda_{\mathrm{mc}})\), \(\mathcal A_{\mathrm{cohort}}\) is absorbing cohort adoption with never-treated donors, \(\tau_{\mathrm{ATT}}\) is the cohort-size-weighted treated post-cell ATT, and \(\mathcal R_{\mathrm{spec}}\) compares additive-FE-centered population SDiD, ridge ASCM, nuclear-norm MC with subgradient certificate, and staggered-SDiD functionals.
\end{quote}

\section{Assumptions}
\begin{assumption}[Bounded-rank IFE]\label{ass:rank}
After additive unit and time effects are removed, untreated potential outcomes have interactive fixed-effects rank at most \(R\): the residualized untreated mean matrix factors as \(L F^\transpose\) with \(L\in\R^{N\times R}\) and \(F\in\R^{T\times R}\).
\end{assumption}

\begin{assumption}[Absorbing cohort support]\label{ass:cohort}
The assignment law is \(\mathcal A_{\mathrm{cohort}}\): donors are never treated, each treated unit belongs to exactly one cohort \(c\), and every cohort has positive limiting share \(\pi_c>0\) and at least one pre-period and one post-period.
\end{assumption}

\begin{assumption}[Overlap and nondegenerate donor moments]\label{ass:overlap}
The donor pre-period covariance \(S\), the donor-unit covariance \(\Sigma_N\), the pre-time covariance \(\Sigma_T\), and the regularized matrices \(\Sigma_N+\rho_N I_{N_0}\), \(\Sigma_T+\rho_T I_{T_0}\), and \(S+\lambda_{\mathrm{ascm}} I_{T_0}\) have stable Moore--Penrose limits, and all cohort pre-period contrasts \(g_c\) are observed in the same centered coordinate system as \(M_{\mathrm{pre}}\).
\end{assumption}

\begin{assumption}[Penalty-path regularity]\label{ass:penalty}
The penalty sequences \(\rho_N,\rho_T,\lambda_{\mathrm{ascm}},\lambda_{\mathrm{mc}}\) converge to finite nonnegative constants or vanish at rates for which the population SDiD, ASCM, and matrix-completion objectives have unique limiting minimizers after additive-FE centering.  The sequences \(\rho_N,\rho_T\) are SDiD-only; \(\lambda_{\mathrm{ascm}}\) is the ASCM ridge sequence; and \(\lambda_{\mathrm{mc}}\) is the matrix-completion nuclear-norm sequence.
\end{assumption}

\begin{assumption}[Selected MC active-face regularity]\label{ass:mc-active}
The selected matrix-completion solution in Section~6 has a locally constant nuclear-norm active face, so the minimum-norm subgradient representative \(Z_{\mathrm{mc}}\), its active-face derivative \(\mathcal H_{Z_{\mathrm{mc}}}\), and the selected derivative matrix \(D_{\mathrm{mc}}\) are unique finite matrices on the observed law under study.
\end{assumption}

\begin{assumption}[No anticipation and stable cohort ATT]\label{ass:att}
For \(t<T_c\), treated cohort \(c\) has observed outcomes equal to \(Y_{it}(0)\).  For \(t\ge T_c\), the cohort ATT contribution is the mean difference between \(Y_{it}(1)\) and \(Y_{it}(0)\), with the target weights \(\pi_c/|\mathcal T_c^+|\) fixed by the locked parameters.
\end{assumption}

\begin{assumption}[Observable spectral certificate]\label{ass:kernel}
The matrices \(S\), \(\Sigma_N\), \(\Sigma_T\), \(G\), \(H\), \(B\), the SDiD and staggered KKT representers \(r^N_c,r^T_c,r^N_{ct},r^T_{ct}\), the ASCM weights \(\omega_{\mathrm{ascm},c}\), the MC certificate pair \((\widehat\Theta_{\mathrm{mc}},Z_{\mathrm{mc}})\), the ATT-residual certificate map \(C^{\mathrm{att}}_{\rho,\lambda}\), the pulled-back kernels \(K^{(r)}_{\rho,\lambda}(Q)\), the threshold \(R_\star(P_{\mathrm{obs}};\rho,\lambda)\), and the influence rows \(\psi_m\) are defined as in Section~6, and equality of population functionals is evaluated only for nondegenerate observed laws \(P_{\mathrm{obs}}\) and admissible completions \(Q\in\mathcal C_R(P_{\mathrm{obs}})\) for which these objects are finite.
\end{assumption}

\begin{assumption}[Regular first-order panel model]\label{ass:if}
At the observed law under study, the rank-\(R\) IFE completion model admits quadratic-mean differentiable local submodels with finite-variance scores.  The canonical gradient \(\psi_{\mathrm{eff}}\), when referenced in a result, exists as an element of the same first-order tangent space as \(\psi_{\mathrm{sdid}}\), \(\psi_{\mathrm{ascm}}\), \(\psi_{\mathrm{mc}}\), and \(\psi_{\mathrm{stag}}\); a regular score direction means an element of this finite-variance tangent space.
\end{assumption}

\begin{assumption}[Completion-class semantics]\label{ass:completion}
For each observed law \(P_{\mathrm{obs}}\), the admissible class \(\mathcal C_R(P_{\mathrm{obs}})\) consists of full potential-outcome laws \(Q\) matching observed cells, satisfying Assumptions~\ref{ass:rank}--\ref{ass:att} and Assumption~\ref{ass:if}, and inducing the same observed matrices \(S\), \(\Sigma_N\), \(\Sigma_T\), \(G\), \(H\), \(B\), \(C^{\mathrm{att}}_{\rho,\lambda}\), and pulled-back rank certificate \(K^{(R)}_{\rho,\lambda}(Q)\).  The target \(\tau_{\mathrm{ATT}}(Q)\), the cohort-specific functionals \(\phi_{\mathrm{sdid},c}(Q)\), \(\phi_{\mathrm{ascm},c}(Q)\), and \(\phi_{\mathrm{mc},c}(Q)\), the pooled single-shock functionals \(\phi_{\mathrm{sdid}}(Q)\), \(\phi_{\mathrm{ascm}}(Q)\), and \(\phi_{\mathrm{mc}}(Q)\), and the staggered functional \(\phi_{\mathrm{stag}}(Q)\) are defined on \(Q\), not directly on \(P_{\mathrm{obs}}\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: population comparison objects are well defined]\label{thm:functionals}
Under Assumptions~\ref{ass:rank}--\ref{ass:completion}, for every \(Q\in\mathcal C_R(P_{\mathrm{obs}})\) the additive-FE-centered population objectives defining \(\phi_{\mathrm{sdid},c}(Q)\), \(\phi_{\mathrm{ascm},c}(Q)\), \(\phi_{\mathrm{mc},c}(Q)\), and \(\phi_{\mathrm{stag}}(Q)\) are finite-dimensional convex programs or first-order certificate systems in the objects of Section~6.  The SDiD block is determined by the displayed \((\Sigma_N+\rho_N I,\Sigma_T+\rho_T I)\) KKT equations, the ASCM block by the normalized ridge problem with \(\lambda_{\mathrm{ascm}}\), the MC block by the observed-mask nuclear-norm problem and subgradient \(Z_{\mathrm{mc}}\), and the staggered block by the displayed cohort-time KKT systems on \(\mathcal E_{ct}\).  The rows \(a_{\mathrm{att}},c_{\mathrm{sdid}},c_{\mathrm{ascm}},c_{\mathrm{mc}},c_{\mathrm{stag}}\), the ATT-residual certificate \(C^{\mathrm{att}}_{\rho,\lambda}\), and the pulled-back kernels \(K^{(r)}_{\rho,\lambda}(Q)\) are therefore well-defined finite-dimensional objects.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest papers are \citet{ArkhangelskyAtheyHirshbergImbensWager2021}, \citet{BenMichaelFellerRothstein2021}, and \citet{AtheyBayatiDoudchenkoImbensKhosravi2021}; each defines one objective, while this theorem puts the four population comparison objects in one centered certificate notation.  This part is routine algebra, not the flagship novelty.  (b) The concrete consumer is Conjecture~\ref{conj:spectral-frontier}: without a common finite-dimensional notation, the spectral equality certificate cannot even be stated.

\begin{conjecture}[Conjecture 1: sharp estimator-level spectral equality frontier (NOT YET PROVED)]\label{conj:spectral-frontier}
Under Assumptions~\ref{ass:rank}--\ref{ass:completion}, the following are equivalent for every nondegenerate observed law \(P_{\mathrm{obs}}\) and its admissible completion class \(\mathcal C_R(P_{\mathrm{obs}})\):
\begin{enumerate}[label=(\roman*)]
\item for every \(Q\in\mathcal C_R(P_{\mathrm{obs}})\) and every cohort \(c\), the cohort-specific single-shock population functionals satisfy \(\phi_{\mathrm{sdid},c}(Q)=\phi_{\mathrm{ascm},c}(Q)=\phi_{\mathrm{mc},c}(Q)=\tau_{\mathrm{ATT},c}(Q)\), and hence their pooled versions satisfy \(\phi_{\mathrm{sdid}}(Q)=\phi_{\mathrm{ascm}}(Q)=\phi_{\mathrm{mc}}(Q)=\tau_{\mathrm{ATT}}(Q)\);
\item for every \(Q\in\mathcal C_R(P_{\mathrm{obs}})\), the separately defined staggered functional also collapses to the cohort-size-weighted pooled single-shock functional, \(\phi_{\mathrm{stag}}(Q)=\sum_c \pi_c \phi_{\mathrm{sdid},c}(Q)=\tau_{\mathrm{ATT}}(Q)\);
\item the first-order rows agree on the rank-\(R\) tangent model, \(\psi_{\mathrm{sdid}}=\psi_{\mathrm{ascm}}=\psi_{\mathrm{mc}}=\psi_{\mathrm{stag}}=\psi_{\mathrm{eff}}\), so the four estimators have the same asymptotic variance and attain the same semiparametric efficiency bound whenever that bound is regular;
\item the pulled-back spectral threshold satisfies \(R\le R_\star(P_{\mathrm{obs}};\rho,\lambda)\), equivalently \(K^{(R)}_{\rho,\lambda}(Q)=0\) for every \(Q\in\mathcal C_R(P_{\mathrm{obs}})\).
\end{enumerate}
If \(R>R_\star(P_{\mathrm{obs}};\rho,\lambda)\), then there is an open set of nondegenerate observed laws \(P_{\mathrm{obs}}\) and completions \(Q\in\mathcal C_R(P_{\mathrm{obs}})\) for which either the pooled functionals \(\phi_{\mathrm{sdid}}(Q)\), \(\phi_{\mathrm{ascm}}(Q)\), \(\phi_{\mathrm{mc}}(Q)\), and \(\phi_{\mathrm{stag}}(Q)\) are pairwise distinct, or their influence rows are pairwise distinct with strictly ordered asymptotic variance along at least one regular score direction.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published result is \citet{ArkhangelskyImbens2022}, which unifies outcome-model and assignment-model routes through double-robust panel identification; the epsilon-gap is that it does not give a necessary-and-sufficient equality theorem for SDiD, ASCM, MC, and staggered-SDiD functionals or influence functions under one spectral certificate.  \citet{BorusyakJaravelSpiess2024} gives an efficiency frontier for staggered imputation under additive parallel trends, but not for bounded-rank IFE or the SDiD/ASCM/MC triple.  (b) The concrete consumer is the robustness-check workflow in \citet{Abadie2021}: the result would tell applied users when cross-estimator agreement is an identification and efficiency fact and when estimator disagreement is predicted by a rank/span obstruction.

\begin{conjecture}[Conjecture 2: first-order separation geometry outside the frontier (NOT YET PROVED)]\label{conj:bias-geometry}
Under Assumptions~\ref{ass:rank}--\ref{ass:completion} and \(R>R_\star(P_{\mathrm{obs}};\rho,\lambda)\), for every nondegenerate observed law \(P_{\mathrm{obs}}\) in the separation region and every \(Q\in\mathcal C_R(P_{\mathrm{obs}})\), let \(v\in\mathcal V_{\max}(K^{(R)}_{\rho,\lambda}(Q))\).  There exists a smooth local completion submodel \(Q_\eta\in\mathcal C_R(P_{\mathrm{obs},\eta})\) perturbing the untreated factor surface in direction \(v\) such that the functional gaps obey
\[
\phi_{\mathrm{sdid}}(Q_\eta)-\phi_{\mathrm{mc}}(Q_\eta)
=\eta\, b_{\mathrm{sdid},\mathrm{mc}}(v;\rho_N,\rho_T,\lambda_{\mathrm{mc}})+o(\eta),
\]
and analogous formulas hold for SDiD versus ASCM and staggered-SDiD versus the cohort-weighted single-shock functional.  The corresponding influence-function gaps \(\psi_m-\psi_{m'}\) have nonzero covariance with at least one regular score direction.  Equivalently, the maximum absolute pairwise derivative over \(v\in\mathcal V_{\max}(K^{(R)}_{\rho,\lambda}(Q))\) is strictly positive on an open dense subset of the separation region.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{FermanPinto2021} shows that imperfect pre-treatment fit can bias SCM-type estimators, and \citet{BenMichaelFellerRothstein2021} analyzes ridge augmentation, but neither gives pairwise first-order bias directions among SDiD, ASCM, MC, and staggered weighting under one bounded-rank nuisance model.  The epsilon-gap is the open-set directional separation formula, not another example with poor fit.  (b) The concrete consumer is \citet{BenMichaelFellerRothstein2022}: their staggered-adoption partial-pooling logic would gain a diagnostic for whether later-treated cohorts create a new population functional or simply average single-cohort SDiD/ASCM limits.

\section{Sanity-check corollaries}
\begin{corollary}[Low-rank perfect-span collapse]\label{cor:perfect-span}
Under Assumptions~\ref{ass:rank}--\ref{ass:completion}, if \(R=0\) after additive-FE centering, \(B=G-H=0\), the penalty path satisfies \(\rho_N=\rho_T=\lambda_{\mathrm{ascm}}=\lambda_{\mathrm{mc}}=0\) at the population limit, and the Section~6 minimum-Frobenius MC tie-break is used, then the selected centered missing untreated residual is zero, \(D_{\mathrm{mc}}\) is the identity on the additive residual class, the ATT-residual rows of \(C^{\mathrm{att}}_{\rho,\lambda}\) vanish on \(\mathcal T_0(Q)\), \(R_\star(P_{\mathrm{obs}};\rho,\lambda)\ge 0\), and Conjecture~\ref{conj:spectral-frontier} reduces to the standard equality of correctly specified additive DiD, SDiD, ASCM, and MC ATT functionals and influence rows.  This reduction does not appeal to an arbitrary \(\lambda_{\mathrm{mc}}=0\) missing-cell completion; the tie-break pins the MC functional before the collapse is taken.
\end{corollary}

\begin{corollary}[Single-cohort reduction]\label{cor:single-cohort}
Under Assumptions~\ref{ass:cohort}, \ref{ass:att}, and \ref{ass:completion}, if \(C=1\) then \(\phi_{\mathrm{stag}}(Q)=\phi_{\mathrm{sdid},1}(Q)\) whenever the cohort-time weighting normalization in \(\mathcal R_{\mathrm{spec}}\) equals the original SDiD normalization.  Thus Conjecture~\ref{conj:spectral-frontier} collapses to a three-way SDiD--ASCM--MC equality statement in the original one-shock design.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is finite-dimensional linear algebra after additive fixed effects are projected out.  First derive the contrast rows \(c_{\mathrm{sdid}},c_{\mathrm{ascm}},c_{\mathrm{stag}}\) from their displayed KKT systems: SDiD gives the two ridge-balanced normal equations in \(\Sigma_N+\rho_N I\) and \(\Sigma_T+\rho_T I\), ASCM gives the affine ridge equation with \(\lambda_{\mathrm{ascm}}\), and staggered SDiD gives the same rows plus off-diagonal later-treated-control blocks on \(\mathcal E_{ct}\).  Second linearize the selected MC KKT system
\[
\mathcal P_\Omega(d\Theta-dY)+\lambda_{\mathrm{mc}}\mathcal H_{Z_{\mathrm{mc}}}(d\Theta)=0
\]
on the active face, giving \(D_{\mathrm{mc}}=(\mathcal P_\Omega+\lambda_{\mathrm{mc}}\mathcal H_{Z_{\mathrm{mc}}})^\dagger\mathcal P_\Omega\) and hence \(c_{\mathrm{mc}}=a_{\mathrm{att}}D_{\mathrm{mc}}\).  Third stack the four ATT residual rows, the three pairwise contrast-row differences, and the two MC KKT derivative blocks into \(C^{\mathrm{att}}_{\rho,\lambda}\).  The missing algebraic lemma is the tangent-space pullback theorem: equality of the four functionals and their influence rows on every rank-\(R\) completion is equivalent to \(C^{\mathrm{att}}_{\rho,\lambda}\Pi_R(Q)=0\) for every admissible \(Q\), where \(\Pi_R(Q)\) spans the rank-\(R\) factor tangent directions.  The iff threshold then follows from the finite list of rank-\(r\) pulled-back matrices \(K^{(r)}_{\rho,\lambda}(Q)=\Pi_r(Q)^\transpose(C^{\mathrm{att}}_{\rho,\lambda})^\transpose C^{\mathrm{att}}_{\rho,\lambda}\Pi_r(Q)\), not from subtracting nullities in different spaces.  Strictness outside the frontier should follow by taking a leading right singular vector of \(K^{(R)}_{\rho,\lambda}(Q)\), computing the corresponding pairwise derivative \(b_{\cdot,\cdot}\) and influence-function covariance, and promoting the minimal \(T_0=2,N_0=2,C=1\) witness to an open set by singular-value continuity.  The staggered extension is checked by showing that the off-diagonal later-treated-control blocks vanish exactly in the single-cohort or no-later-treated-support case.

\section{Honest scope flags}
Theorem~\ref{thm:functionals} is intended as routine algebra once the population objectives are fixed.  Conjectures~\ref{conj:spectral-frontier} and \ref{conj:bias-geometry} are the novel kernel and are not yet proved.  The displayed pulled-back kernel \(K^{(r)}_{\rho,\lambda}(Q)\) is now tied to ATT residual rows, selected SDiD and staggered KKT systems, a selected MC minimizer, a selected subgradient representative, and an active-face derivative; if active-face regularity fails, the proposal should be restated as a set-valued certificate rather than a single matrix theorem.  The efficiency claim is conditional on existence of the regular canonical gradient in the bounded-rank IFE completion model and is part of the conjecture, not a proved fact.  No claim is made here that Sequential SDiD is subsumed; this proposal only asks for equality and first-order separation of population functionals and influence rows across the named SDiD, ASCM, MC, and staggered-weight objects.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft around an observable spectral rank certificate for SDiD--ASCM--MC--staggered equality; prior verdict: none.
\item v2 (revise) -- patched reviewer flags by adding the sixth introduction paragraph, Arkhangelsky--Imbens double-robust and Stata SDiD comparators, completion-class semantics, full assumption coverage, subspace tie handling, and a valid perfect-span sanity reduction; prior verdict: REVISE.
\item v3 (revise) -- patched well-posedness and coherence flags by adding the ASCM ridge penalty, replacing the MC projection shortcut with an explicit nuclear-norm certificate, and separating cohort-specific, pooled, and staggered functionals; prior verdict: REVISE.
\item v4 (revise) -- patched MC/certificate soundness flags by defining the selected MC minimizer and subgradient, giving explicit \(C_{\rho,\lambda}\) blocks, repairing the \(\lambda_{\mathrm{mc}}=0\) perfect-span collapse with the tie-break, and adding the concrete KKT linearization route; prior verdict: REVISE.
\item v5 (revise) -- patched flagship and well-posedness flags by adding ATT-residual rows, replacing nullity subtraction with a tangent-cone pullback threshold, displaying SDiD and staggered KKT systems, and upgrading the frontier to equality of influence functions and asymptotic variance; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Abadie(2021)]{Abadie2021}
Abadie, Alberto. 2021. ``Using Synthetic Controls: Feasibility, Data Requirements, and Methodological Aspects.'' \emph{Journal of Economic Literature} 59(2): 391--425.

\bibitem[Abadie, Diamond, and Hainmueller(2010)]{AbadieDiamondHainmueller2010}
Abadie, Alberto, Alexis Diamond, and Jens Hainmueller. 2010. ``Synthetic Control Methods for Comparative Case Studies: Estimating the Effect of California's Tobacco Control Program.'' \emph{Journal of the American Statistical Association} 105(490): 493--505.

\bibitem[Abadie, Diamond, and Hainmueller(2015)]{AbadieDiamondHainmueller2015}
Abadie, Alberto, Alexis Diamond, and Jens Hainmueller. 2015. ``Comparative Politics and the Synthetic Control Method.'' \emph{American Journal of Political Science} 59(2): 495--510.

\bibitem[Abadie and L'Hour(2021)]{AbadieLHour2021}
Abadie, Alberto, and Jeremy L'Hour. 2021. ``A Penalized Synthetic Control Estimator for Disaggregated Data.'' \emph{Journal of the American Statistical Association} 116(536): 1817--1834.

\bibitem[Arkhangelsky et~al.(2021)]{ArkhangelskyAtheyHirshbergImbensWager2021}
Arkhangelsky, Dmitry, Susan Athey, David A. Hirshberg, Guido W. Imbens, and Stefan Wager. 2021. ``Synthetic Difference-in-Differences.'' \emph{American Economic Review} 111(12): 4088--4118.

\bibitem[Arkhangelsky et~al.(2024)]{ArkhangelskyImbensLeiLuo2024}
Arkhangelsky, Dmitry, Guido W. Imbens, Lihua Lei, and Xiaoman Luo. 2024. ``Design-Robust Two-Way Fixed Effects Regression for Panel Data.'' \emph{Quantitative Economics} 15(4): 999--1034.

\bibitem[Arkhangelsky and Imbens(2022)]{ArkhangelskyImbens2022}
Arkhangelsky, Dmitry, and Guido W. Imbens. 2022. ``Doubly Robust Identification for Causal Panel Data Models.'' \emph{The Econometrics Journal} 25(3): 649--674.

\bibitem[Arkhangelsky and Samkov(2024)]{ArkhangelskySamkov2024}
Arkhangelsky, Dmitry, and Aleksei Samkov. 2024. ``Sequential Synthetic Difference in Differences.'' arXiv:2404.00164.

\bibitem[Athey et~al.(2021)]{AtheyBayatiDoudchenkoImbensKhosravi2021}
Athey, Susan, Mohsen Bayati, Nikolay Doudchenko, Guido W. Imbens, and Khashayar Khosravi. 2021. ``Matrix Completion Methods for Causal Panel Data Models.'' \emph{Journal of the American Statistical Association} 116(536): 1716--1730.

\bibitem[Bai and Ng(2021)]{BaiNg2021}
Bai, Jushan, and Serena Ng. 2021. ``Matrix Completion, Counterfactuals, and Factor Analysis of Missing Data.'' \emph{Journal of the American Statistical Association} 116(536): 1746--1763.

\bibitem[Ben-Michael, Feller, and Rothstein(2021)]{BenMichaelFellerRothstein2021}
Ben-Michael, Eli, Avi Feller, and Jesse Rothstein. 2021. ``The Augmented Synthetic Control Method.'' \emph{Journal of the American Statistical Association} 116(536): 1789--1803.

\bibitem[Ben-Michael, Feller, and Rothstein(2022)]{BenMichaelFellerRothstein2022}
Ben-Michael, Eli, Avi Feller, and Jesse Rothstein. 2022. ``Synthetic Controls with Staggered Adoption.'' \emph{Journal of the Royal Statistical Society: Series B} 84(2): 351--381.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{BorusyakJaravelSpiess2024}
Borusyak, Kirill, Xavier Jaravel, and Jann Spiess. 2024. ``Revisiting Event-Study Designs: Robust and Efficient Estimation.'' \emph{Review of Economic Studies} 91(6): 3253--3285.

\bibitem[Clarke et~al.(2024)]{ClarkePailanirAtheyImbens2024}
Clarke, Damian, Daniel Pailanir, Susan Athey, and Guido Imbens. 2024. ``On Synthetic Difference-in-Differences and Related Estimation Methods in Stata.'' \emph{The Stata Journal} 24(4): 557--598.

\bibitem[Doudchenko and Imbens(2016)]{DoudchenkoImbens2016}
Doudchenko, Nikolay, and Guido W. Imbens. 2016. ``Balancing, Regression, Difference-in-Differences and Synthetic Control Methods: A Synthesis.'' NBER Working Paper 22791.

\bibitem[Ferman and Pinto(2021)]{FermanPinto2021}
Ferman, Bruno, and Cristine Pinto. 2021. ``Synthetic Controls with Imperfect Pretreatment Fit.'' \emph{Quantitative Economics} 12(4): 1197--1221.

\bibitem[Gobillon and Magnac(2016)]{GobillonMagnac2016}
Gobillon, Laurent, and Thierry Magnac. 2016. ``Regional Policy Evaluation: Interactive Fixed Effects and Synthetic Controls.'' \emph{Review of Economics and Statistics} 98(3): 535--551.

\bibitem[Xu(2017)]{Xu2017}
Xu, Yiqing. 2017. ``Generalized Synthetic Control Method: Causal Inference with Interactive Fixed Effects Models.'' \emph{Political Analysis} 25(1): 57--76.
\end{thebibliography}

\end{document}
