% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=q1\_spectral\_phase\_transition, specialization=p1\_markov
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `tools/thmsmith/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block VERBATIM from
%    `doc/ThmSmith/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{q1\_spectral\_phase\_transition} / \texttt{p1\_markov}%
  \\ \large\textit{A Bojinov--Rambachan--Shephard interpretability frontier for Markov distributed-lag TWFE}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid = q1_spectral_phase_transition
specialization = p1_markov
p = 1
assignment = stationary two-state first-order Markov treatment path with
  transition probabilities a_T = Pr(D_t=1 | D_{t-1}=0) and
  b_T = Pr(D_t=0 | D_{t-1}=1), independently across units.
  The spectral gap is gamma_T = a_T+b_T, the second eigenvalue is
  rho_T = 1-gamma_T, and pi_T(1)=a_T/(a_T+b_T).
target = dynamic Q1 ATT profile theta=(theta_on, theta_surv), where
  theta_on = m(01)-m(00) is the switch-on effect and
  theta_surv = m(11)-m(00) is the one-period treated-survivor effect.
  Linear functionals ell' theta are interpreted as causal dynamic ATT
  directions only when ell is visible in the retained FWL row space.
regression = TWFE/FWL distributed-lag regression with unit and calendar
  fixed effects, current and lagged treatment columns (D_t, D_{t-1}),
  and the Q1 clean-history nuisance columns 1{H=(1,0)} and 1{H=(1,1)}
  when they are retained by the deterministic threshold kappa_T.  The
  spectral innovation mass is
  Xi_T = n_T*pi_T(0)*pi_T(1)*(1-rho_T^2), with n_T=T-1.
  Singular directions with Gram singular value below kappa_T are not
  treated as regular identifying moments; bounded-response affine fibers
  define the partial-identification fallback.
\end{verbatim}

\begin{abstract}
\citet{bojinov2021panel} show that serially correlated assignments can make common fixed-effect estimators fail to recover a causally interpretable dynamic effect.
This proposal asks for the sharp spectral version of that warning in the Q1 Markov panel: which dynamic ATT directions are point identified, partially identified, or nonidentified by a TWFE/FWL distributed-lag specification?
The proposed kernel is a phase transition in the spectral innovation mass \(\Xi_T=n_T\pi_T(0)\pi_T(1)(1-\rho_T^2)\), where \(\rho_T=1-a_T-b_T\).
Above the threshold, the current/lag distributed-lag basis and the clean Q1 history basis are regularly equivalent and the two-dimensional dynamic ATT profile is interpretable.
At the boundary only the threshold-retained eigen-directions are interpretable, and below it Bojinov--Rambachan--Shephard's qualitative non-interpretability becomes a row-space nonidentification statement.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Dynamic panel experiments and switchback designs are increasingly used when treatment can turn on and off over time.
The applied question is rarely just whether a scalar TWFE coefficient is biased; researchers want to know whether a reported current effect and a reported carryover effect correspond to any causal dynamic ATT coordinates.
\citet{bojinov2021panel} establish that serial correlation can destroy the causal interpretation of common fixed-effect estimators, but their warning is not an identification frontier telling a researcher which dynamic directions remain visible as the assignment chain becomes persistent or nearly alternating.

\paragraph{The main finding (proposed).}
The flagship conjecture is Conjecture~\ref{conj:brs-frontier}: for a stationary two-state Markov assignment, the retained row space of the TWFE/FWL distributed-lag moment system changes at the threshold
\[
\Xi_T/\kappa_T
= n_T\pi_T(0)\pi_T(1)(1-\rho_T^2)/\kappa_T .
\]
If this ratio diverges, the dynamic Q1 profile \((\theta_{\mathrm{on}},\theta_{\mathrm{surv}})\) is regularly point identified.
If the ratio converges to a finite positive constant, only eigen-directions whose limiting Gram constants exceed the threshold are regular and the orthogonal dynamic ATT directions are bounded through an affine fiber.
If the ratio vanishes, no nonzero contrast separating switch-on from treated-survivor effects is regularly identified without additional shape restrictions.

\paragraph{What is new.}
The closest published result is \citet{bojinov2021panel}, whose Proposition 4.1 characterizes a fixed-effect probability limit under dynamic causal effects and serially correlated assignment.
The epsilon-gap is that Bojinov--Rambachan--Shephard diagnose non-interpretability of a conventional estimator, while this proposal conjectures an if-and-only-if spectral row-space frontier for the augmented distributed-lag and clean-history specifications themselves.
The proposed theorem is not merely ``iid to Markov'': it predicts two structurally different failures, near persistence \(\rho_T\to1\) and near alternation \(\rho_T\to-1\), both governed by the same innovation eigenvalue \(1-\rho_T^2\).

\paragraph{How it positions in the literature.}
The proposal sits in the panel and linear-projection cluster, with a partial-identification fallback when the regular row space loses directions.
\citet{bojinov2021panel}, \citet{bojinov2023switchback}, and \citet{hu2022switchback} make serial dependence and carryover first-order design features.
\citet{sunabraham2021eventstudy}, \citet{dechaisemartin2020twfe}, and \citet{goodmanbacon2021timing} explain why TWFE/event-study coefficients can mix the wrong causal objects under heterogeneous effects.
The present proposal contributes a different object: a spectral support threshold for whether the dynamic ATT coordinates are in the FWL row space at all.

\paragraph{Implications for the community.}
The immediate consumer is the panel-experiment workflow in \citet{bojinov2021panel}: before reporting fixed-effect or distributed-lag causal summaries under serially correlated assignment, the analyst would report \(\Xi_T\) and the retained eigen-directions, not just the coefficient vector.
\paragraph{How research benefits from the conclusion.}
Researchers should treat a dynamic TWFE profile under Markov assignment as a spectral row-space object and report which current/carryover directions are point identified, bounded, or not identified.

\section{Related work}
\citet{bojinov2021panel} provide the primary anchor: they develop finite-population panel-experiment estimands and show that fixed-effect estimators need not recover causally interpretable dynamic effects under serially correlated assignment.
\citet{bojinov2023switchback} derive design and inference results for switchback experiments with carryover, motivating why treatment-path dependence is a design primitive rather than a nuisance detail.
\citet{hu2022switchback} show that geometric mixing changes switchback estimation rates; this is the closest spectral-rate precedent, but it does not state a TWFE/FWL dynamic-ATT row-space frontier.
\citet{sunabraham2021eventstudy} show that event-study coefficients can be contaminated by effects from other relative periods; the present proposal studies row-space visibility rather than contamination conditional on fixed support.
\citet{dechaisemartin2020twfe} show that TWFE estimators are weighted averages with potentially negative weights; here the issue is whether the current/carryover basis has enough spectral innovation to be invertible at all.
\citet{goodmanbacon2021timing} decomposes staggered TWFE into two-by-two comparisons; the proposed Markov frontier is not a comparison decomposition, because recurrent treatment makes the relevant object a lag covariance operator.
\citet{callaway2021multiple} identify group-time ATT components before aggregation in staggered designs; this proposal asks for the analogous visibility check for Markov history-time ATT directions.
\citet{schmidheiny2023event} establish identification and equivalence results for event-study and distributed-lag TWFE specifications; the new question is when the distributed-lag Gram itself loses regular rank as \(|\rho_T|\to1\).
\citet{dechaisemartin2024intertemporal} study nonabsorbing and lagged treatment effects in DiD; the present proposal is narrower but sharper about the Markov spectral boundary separating full, partial, and no regular interpretation.
\citet{manski2003partial} and \citet{tamer2010partial} provide the partial-identification language used for bounded affine fibers after row-space loss.
The in-repository panel catalogue in \texttt{doc/API.md} records \texttt{Q1\_MinimalBasis} for iid Bernoulli clean-history identification, \texttt{Q1\_StaggeredMinimalBasis} for absorbing staggered adoption, \texttt{Q1\_SignFlip} for sign-of-bias thresholds, and \texttt{Q1\_SpectralThreshold} for a refuted Markov sign-lock conjecture.
The closest repository entry is \texttt{Q1\_SpectralThreshold}, but it studies signs of saturated-clean FWL weights; it does not classify interpretability of the dynamic ATT vector through the singular row space of the distributed-lag and clean-history designs.

\section{Formal setup}
Let \(i=1,\ldots,N\), \(t=1,\ldots,T\), and \(D_{it}\in\{0,1\}\).
Set \(H_{it}=(D_{i,t-1},D_{it})\in\{00,01,10,11\}\), with \(t=2,\ldots,T\) used for the Q1 interior panel and \(n_T=T-1\).
Potential outcomes have memory \(p=1\), so \(Y_{it}=Y_{it}(H_{it})\).
Write \(m(h)=\E[Y_{it}(h)]\) for the time-homogeneous response surface after the untreated baseline has been absorbed by fixed effects.
The dynamic Q1 ATT profile is
\[
\theta =
\begin{pmatrix}
\theta_{\mathrm{on}}\\
\theta_{\mathrm{surv}}
\end{pmatrix}
=
\begin{pmatrix}
m(01)-m(00)\\
m(11)-m(00)
\end{pmatrix}.
\]
The treatment path is stationary Markov with transition matrix
\[
M_T=
\begin{pmatrix}
1-a_T & a_T\\
b_T & 1-b_T
\end{pmatrix},
\qquad
\rho_T=1-a_T-b_T,\qquad
\pi_T(1)=\frac{a_T}{a_T+b_T}.
\]
Let \(\pi_T(0)=1-\pi_T(1)=b_T/(a_T+b_T)\) and define the spectral innovation mass
\[
\Xi_T=n_T\pi_T(0)\pi_T(1)(1-\rho_T^2).
\]
The distributed-lag TWFE design contains unit fixed effects, calendar fixed effects, and \(X_t=(D_{it},D_{i,t-1})\).
The clean-history design augments the target switch-on column \(C_{01}=\one\{H=01\}\) with \(C_{10}=\one\{H=10\}\) and \(C_{11}=\one\{H=11\}\).
After FWL residualization against unit and calendar fixed effects, write \(Z_T\) for the retained design matrix, \(G_T=\E[Z_T^\transpose Z_T]\) for its population Gram, and \(A_T=\E[Z_T^\transpose \Phi]\) for the moment map from the local history response vector \(m=(m(00),m(01),m(10),m(11))\).
Let \(G_T=U_T\Sigma_TU_T^\transpose\) be an orthonormal singular decomposition.
Given a deterministic threshold \(\kappa_T>0\), define
\[
J_T^{\mathrm{reg}}=\{j:\Sigma_{T,jj}\ge \kappa_T\},
\qquad
\mathcal V_T^{\mathrm{reg}}=\operatorname{span}\{u_{T,j}^\transpose A_T:j\in J_T^{\mathrm{reg}}\}.
\]
For any target loading \(\ell\in\R^2\), let \(\bar \ell\in\R^4\) be its induced row on \(m\):
\[
\bar\ell^\transpose m
=
\ell_1(m(01)-m(00))+\ell_2(m(11)-m(00)).
\]
The retained affine fiber under bounds \(L<U\) is
\[
\calF_T^{\mathrm{reg}}(z;L,U)=
\{m'\in[L,U]^4: (u_{T,j}^\transpose A_Tm')_{j\in J_T^{\mathrm{reg}}}=z\}.
\]
Let \(\Pi_T^{\mathrm{reg}}\) denote Euclidean projection of response rows onto \(\mathcal V_T^{\mathrm{reg}}\).
At a boundary sequence with \(\Xi_T/\kappa_T\to\lambda\in(0,\infty)\), let \(s_j=\lim_T \Sigma_{T,jj}/\Xi_T\) when the limit exists and \(J^{\mathrm{bdry}}(\lambda)=\{j:s_j\lambda\ge1\}\).

Locked parameters for Stage 0:
\begin{verbatim}
qid = q1_spectral_phase_transition
specialization = p1_markov
p = 1
assignment = stationary two-state first-order Markov treatment path with
  transition probabilities a_T = Pr(D_t=1 | D_{t-1}=0) and
  b_T = Pr(D_t=0 | D_{t-1}=1), independently across units.
  The spectral gap is gamma_T = a_T+b_T, the second eigenvalue is
  rho_T = 1-gamma_T, and pi_T(1)=a_T/(a_T+b_T).
target = dynamic Q1 ATT profile theta=(theta_on, theta_surv), where
  theta_on = m(01)-m(00) is the switch-on effect and
  theta_surv = m(11)-m(00) is the one-period treated-survivor effect.
  Linear functionals ell' theta are interpreted as causal dynamic ATT
  directions only when ell is visible in the retained FWL row space.
regression = TWFE/FWL distributed-lag regression with unit and calendar
  fixed effects, current and lagged treatment columns (D_t, D_{t-1}),
  and the Q1 clean-history nuisance columns 1{H=(1,0)} and 1{H=(1,1)}
  when they are retained by the deterministic threshold kappa_T.  The
  spectral innovation mass is
  Xi_T = n_T*pi_T(0)*pi_T(1)*(1-rho_T^2), with n_T=T-1.
  Singular directions with Gram singular value below kappa_T are not
  treated as regular identifying moments; bounded-response affine fibers
  define the partial-identification fallback.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite memory and consistency]\label{ass:finite-memory}
For every unit and interior period, \(Y_{it}=Y_{it}(H_{it})\), where \(H_{it}=(D_{i,t-1},D_{it})\).
\end{assumption}

\begin{assumption}[Untreated TWFE baseline]\label{ass:untreated-twfe}
\(\E[Y_{it}(00)\mid D_i]=\alpha_i+\lambda_t\), so unit and calendar fixed effects absorb the untreated response.
\end{assumption}

\begin{assumption}[Stationary Markov assignment]\label{ass:stationary-markov}
For each \(T\), \(D_{i1},\ldots,D_{iT}\) are independent across units and follow the stationary two-state Markov law with \(0<a_T<1\), \(0<b_T<1\), transition matrix \(M_T\), stationary probabilities \(\pi_T(0),\pi_T(1)\), and second eigenvalue \(\rho_T=1-a_T-b_T\).
\end{assumption}

\begin{assumption}[Regular row-space threshold]\label{ass:regular-threshold}
A deterministic threshold \(\kappa_T>0\) is fixed before outcomes are observed.
Only Gram singular directions at least \(\kappa_T\) are interpreted as regular identifying moments.
\end{assumption}

\begin{assumption}[Boundary singular-value limits]\label{ass:boundary-limits}
For boundary statements with \(\Xi_T/\kappa_T\to\lambda\in(0,\infty)\), every normalized singular value \(\Sigma_{T,jj}/\Xi_T\) along the nonzero distributed-lag and clean-history block has a finite limit \(s_j\).
\end{assumption}

\begin{assumption}[Bounded response surface]\label{ass:bounded-response}
For partial-identification statements, \(m(h)\in[L,U]\) for every \(h\in\{00,01,10,11\}\), where \(L<U\) are known finite constants.
\end{assumption}

\begin{assumption}[Nondegenerate dynamic target loading]\label{ass:nondegenerate-loading}
The target loading \(\ell\in\R^2\) is nonzero and its induced row \(\bar\ell\) is supported only on \((m(00),m(01),m(11))\) as defined in the formal setup.
\end{assumption}

\begin{assumption}[Admissible basis comparison class]\label{ass:basis-class}
The admissible basis class consists of subcollections and nonsingular finite linear recombinations of the distributed-lag columns \((D_t,D_{t-1})\) and clean-history columns \((C_{01},C_{10},C_{11})\), with no external shape restriction on \(m\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: retained row-space identification trichotomy]\label{thm:row-space-trichotomy}
Assume Assumptions~\ref{ass:regular-threshold}, \ref{ass:bounded-response}, and \ref{ass:nondegenerate-loading}.
Fix \(T\), retained moments \(z\), and target loading \(\ell\).
If \(\bar\ell\in\mathcal V_T^{\mathrm{reg}}\), then \(\ell^\transpose\theta\) is regularly point identified from \(z\).
If \(0\ne\Pi_T^{\mathrm{reg}}\bar\ell\ne\bar\ell\), then \((\Pi_T^{\mathrm{reg}}\bar\ell)^\transpose m\) is regularly point identified and the sharp bounded interval for \(\ell^\transpose\theta\) is
\[
\left[
\inf_{m'\in\calF_T^{\mathrm{reg}}(z;L,U)}\bar\ell^\transpose m',
\sup_{m'\in\calF_T^{\mathrm{reg}}(z;L,U)}\bar\ell^\transpose m'
\right].
\]
If \(\Pi_T^{\mathrm{reg}}\bar\ell=0\), then no nonzero component of \(\ell^\transpose\theta\) is regularly identified; without Assumption~\ref{ass:bounded-response}, the target is not point identified whenever the retained affine fiber contains a direction \(v\) with \(A_T^{\mathrm{reg}}v=0\) and \(\bar\ell^\transpose v\ne0\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is a deterministic row-space theorem, not the flagship novelty; its closest published analogues are the row-span support logic behind \citet{borusyak2024eventstudy} and the partial-identification logic of \citet{manski2003partial}, but it is phrased for Bojinov-style dynamic panel fixed-effect moments.
(b) It is worth isolating because Conjecture~\ref{conj:brs-frontier} would feed this theorem directly into \citet{bojinov2021panel}'s applied panel-experiment workflow.

\begin{conjecture}[Conjecture 1: Bojinov--Rambachan--Shephard spectral interpretability frontier (NOT YET PROVED)]\label{conj:brs-frontier}
Under Assumptions~\ref{ass:finite-memory}--\ref{ass:boundary-limits}, \ref{ass:bounded-response}, and \ref{ass:nondegenerate-loading}, the nonzero singular values of the residualized distributed-lag/clean-history Gram block that separate \(\theta_{\mathrm{on}}\) from \(\theta_{\mathrm{surv}}\) are all of order \(\Xi_T\):
there exist constants \(0<c<C<\infty\), independent of \(T\), such that each such singular value lies between \(c\Xi_T\) and \(C\Xi_T\), while all rows orthogonal to the Markov innovation span have singular value \(o(\Xi_T)\).
Consequently, if \(\Xi_T/\kappa_T\to\infty\), then every \(\ell^\transpose\theta\) is regularly point identified.
If \(\Xi_T/\kappa_T\to\lambda\in(0,\infty)\), then \(\ell^\transpose\theta\) is regularly point identified if and only if \(\bar\ell\) lies in the span of the boundary-retained directions \(J^{\mathrm{bdry}}(\lambda)\), and otherwise it is sharply partially identified by Theorem~\ref{thm:row-space-trichotomy}.
If \(\Xi_T/\kappa_T\to0\), then no nonzero contrast separating \(\theta_{\mathrm{on}}\) from \(\theta_{\mathrm{surv}}\) is regularly identified.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{bojinov2021panel} show that serial correlation and dynamic effects can make fixed-effect estimators noncausal; the epsilon-gap is the proposed if-and-only-if spectral frontier for the entire dynamic ATT row space.
\citet{hu2022switchback} give a geometric-mixing rate result, but not a TWFE/FWL row-space trichotomy for current and carryover ATT directions.
(b) Resolving the conjecture would give users of the panel-experiment methods in \citet{bojinov2021panel} a concrete diagnostic: report \(\Xi_T\) and the retained eigenvectors before claiming that a dynamic fixed-effect coefficient is interpretable.

\begin{conjecture}[Conjecture 2: minimal-basis structural change across the spectral boundary (NOT YET PROVED)]\label{conj:minimal-basis-change}
Under Assumptions~\ref{ass:finite-memory}--\ref{ass:basis-class}, the clean Q1 history basis \((C_{01},C_{10},C_{11})\) and the distributed-lag basis \((D_t,D_{t-1})\) are regularly equivalent for identifying \(\theta\) when \(\Xi_T/\kappa_T\to\infty\).
On a boundary sequence, the minimal regular basis is any basis of the boundary-retained innovation subspace \(\operatorname{span}\{u_j^\transpose A_T:j\in J^{\mathrm{bdry}}(\lambda)\}\).
When \(\Xi_T/\kappa_T\to0\), no admissible recombination of \((D_t,D_{t-1},C_{01},C_{10},C_{11})\) restores regular identification of both \(\theta_{\mathrm{on}}\) and \(\theta_{\mathrm{surv}}\) without an external shape restriction on \(m\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The repository's \texttt{Q1\_MinimalBasis} proves a static iid clean-basis result, and \texttt{Q1\_SpectralThreshold} refutes a Markov sign-lock conjecture; neither says that the minimal basis changes with the Markov innovation eigenvalue.
\citet{schmidheiny2023event} compare event-study and distributed-lag parametrizations, but do not classify basis minimality after Markov spectral row loss.
(b) This would give the \citet{schmidheiny2023event} distributed-lag practice a sharp warning: near \(|\rho_T|=1\), formula equivalence does not imply regular causal-equivalence of the dynamic ATT coordinates.

\section{Sanity-check corollaries}
\begin{corollary}[IID fixed-gap reduction]\label{cor:iid-fixed-gap}
If \(a_T=a\), \(b_T=b\), \(0<a,b<1\), and \(|1-a-b|<1\) is bounded away from \(1\), then \(\Xi_T\asymp T\).
For any \(\kappa_T=o(T)\), Conjecture~\ref{conj:brs-frontier} reduces to regular point identification of the two-dimensional Q1 dynamic ATT profile.
\end{corollary}
Under Assumptions~\ref{ass:stationary-markov} and \ref{ass:regular-threshold}, the reduction is immediate because \(\pi_T(0)\pi_T(1)(1-\rho_T^2)\) is a fixed positive constant; this matches the existing Q1 iid clean-basis result in the catalogue.

\begin{corollary}[Persistent rare-switch collapse]\label{cor:persistent-collapse}
If \(a_T=\alpha/T^2\), \(b_T=b\in(0,1)\), then \(\rho_T\to1\) and \(\Xi_T\to0\).
Conjecture~\ref{conj:brs-frontier} predicts that the switch-on and treated-survivor contrast cannot be regularly separated.
\end{corollary}
Under Assumption~\ref{ass:stationary-markov}, \(\pi_T(1)\sim a_T/b\) and \(1-\rho_T^2\sim2b\), so \(n_T\pi_T(0)\pi_T(1)(1-\rho_T^2)\asymp T\cdot T^{-2}\to0\).

\begin{corollary}[Near-alternation collapse]\label{cor:alternating-collapse}
If \(a_T=1-\alpha/T^2\) and \(b_T=1-\beta/T^2\), then \(\rho_T\to-1\) and \(\Xi_T\to0\).
Conjecture~\ref{conj:brs-frontier} predicts the same nonregular separation of dynamic ATT directions, despite frequent treatment changes.
\end{corollary}
The algebra differs from Corollary~\ref{cor:persistent-collapse}: here \(\pi_T(0)\pi_T(1)\to1/4\), but \(1-\rho_T^2\sim2(\alpha+\beta)/T^2\), so the lag design is nearly deterministic alternating and the innovation mass still vanishes.

\section{Why feasible}
The mathematical route is finite-dimensional.
First, compute the two-by-two Markov lag covariance matrix after fixed-effect residualization; before residualization the lag block has Toeplitz entries proportional to \(\pi_T(0)\pi_T(1)\rho_T^{|j-k|}\), whose determinant is proportional to \(\pi_T(0)^2\pi_T(1)^2(1-\rho_T^2)\).
Second, show that unit and calendar FWL residualization changes this block only by lower-order boundary terms under the stationary interior convention.
Third, transport the distributed-lag block to the Q1 clean-history response map and identify which singular directions load on \((m(01)-m(00),m(11)-m(00))\).
The boundary cases needing explicit algebra are \(\rho_T\to1\), \(\rho_T\to-1\), balanced versus unbalanced stationary shares, and the exact two-direction projection on the \(\Xi_T/\kappa_T\to\lambda\) frontier.

\section{Honest scope flags}
Theorem~\ref{thm:row-space-trichotomy} is labelled as a theorem because it is routine finite-dimensional linear algebra with box bounds.
Conjectures~\ref{conj:brs-frontier} and \ref{conj:minimal-basis-change} are not yet proved.
The proposal does not claim that finite-\(T\) algebraic point identification fails when \(0<a_T,b_T<1\); the point/partial/nonidentified trichotomy is a regular-identification convention after imposing the deterministic threshold \(\kappa_T\).
The hardest open issue is whether the FWL residualization and clean-history transformation preserve the exact \(\Xi_T\) singular-value order uniformly when the stationary share \(\pi_T(1)\) also approaches zero or one.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 2, replacing the exhausted event-window rank-collapse angle with a Bojinov--Rambachan--Shephard distributed-lag interpretability frontier; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bojinov, Rambachan, and Shephard(2021)]{bojinov2021panel}
Iavor Bojinov, Ashesh Rambachan, and Neil Shephard.
\newblock Panel experiments and dynamic causal effects: A finite population perspective.
\newblock \emph{Quantitative Economics}, 12(4):1171--1196, 2021.

\bibitem[Bojinov, Simchi-Levi, and Zhao(2023)]{bojinov2023switchback}
Iavor Bojinov, David Simchi-Levi, and Jinglong Zhao.
\newblock Design and analysis of switchback experiments.
\newblock \emph{Management Science}, 69(7):3759--3777, 2023.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{borusyak2024eventstudy}
Kirill Borusyak, Xavier Jaravel, and Jann Spiess.
\newblock Revisiting event-study designs: Robust and efficient estimation.
\newblock \emph{Review of Economic Studies}, 91(6):3253--3285, 2024.

\bibitem[Callaway and Sant'Anna(2021)]{callaway2021multiple}
Brantly Callaway and Pedro H. C. Sant'Anna.
\newblock Difference-in-differences with multiple time periods.
\newblock \emph{Journal of Econometrics}, 225(2):200--230, 2021.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{dechaisemartin2020twfe}
Clement de Chaisemartin and Xavier D'Haultfoeuille.
\newblock Two-way fixed effects estimators with heterogeneous treatment effects.
\newblock \emph{American Economic Review}, 110(9):2964--2996, 2020.

\bibitem[de Chaisemartin and D'Haultfoeuille(2024)]{dechaisemartin2024intertemporal}
Clement de Chaisemartin and Xavier D'Haultfoeuille.
\newblock Difference-in-differences estimators of intertemporal treatment effects.
\newblock \emph{Review of Economics and Statistics}, 2024.

\bibitem[Goodman-Bacon(2021)]{goodmanbacon2021timing}
Andrew Goodman-Bacon.
\newblock Difference-in-differences with variation in treatment timing.
\newblock \emph{Journal of Econometrics}, 225(2):254--277, 2021.

\bibitem[Hu and Wager(2022)]{hu2022switchback}
Yuchen Hu and Stefan Wager.
\newblock Switchback experiments under geometric mixing.
\newblock arXiv:2209.00197, 2022.

\bibitem[Manski(2003)]{manski2003partial}
Charles F. Manski.
\newblock \emph{Partial Identification of Probability Distributions}.
\newblock Springer, 2003.

\bibitem[Schmidheiny and Siegloch(2023)]{schmidheiny2023event}
Kurt Schmidheiny and Sebastian Siegloch.
\newblock On event studies and distributed-lags in two-way fixed effects models: Identification, equivalence, and generalization.
\newblock \emph{Journal of Applied Econometrics}, 38(5):695--713, 2023.

\bibitem[Sun and Abraham(2021)]{sunabraham2021eventstudy}
Liyang Sun and Sarah Abraham.
\newblock Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\newblock \emph{Journal of Econometrics}, 225(2):175--199, 2021.

\bibitem[Tamer(2010)]{tamer2010partial}
Elie Tamer.
\newblock Partial identification in econometrics.
\newblock \emph{Annual Review of Economics}, 2:167--195, 2010.
\end{thebibliography}

\end{document}
