\paragraph{Section 9 fragment statement.}
\paragraph{Motivating conjecture restated verbatim.}
Under Assumptions~\ref{ass:finite-memory}--\ref{ass:clean-window}, \ref{ass:regular-row}, \ref{ass:boundary-limits}, \ref{ass:minimal-class}, \ref{ass:bounded-response}, and \ref{ass:nondegenerate-target}, the Q1 nuisance basis \(\{C_{10},C_{11}\}\) is minimal in \(\mathfrak B(K)\) for regular point identification of all causal finite-window switch-on event contrasts when \(\Lambda_T(K)/\kappa_T\to\infty\).
On the boundary \(\Lambda_T(K)/\kappa_T\to\lambda\in(0,\infty)\), the minimal regular nuisance basis is any basis of the active subspace \(N_T^{\mathrm{act}}(K,\lambda)\); nuisance contrasts in \(\operatorname{span}\{C_{10},C_{11}\}\cap N_T^{\mathrm{act}}(K,\lambda)^\perp\) are nonregular and are omitted from the regular comparison.
Below the boundary, no finite augmentation by relative-time columns alone restores regular identification of the full causal event-window profile unless it adds an external shape restriction on \(m_K\).

\paragraph{Refutation note.}
The finite-T rank/support witness \(T=2\), \(K=\{-1,0\}\), \(a=b=1/2\), and \(B^\star=\{C_{10}+C_{11}\}\) refutes Conjecture 2's claim that \(\{C_{10},C_{11}\}\) is minimal in \(\mathfrak B(K)\).

\paragraph{Section 13 refutation attempt and counterexample.}
I used the prescribed finite-\(T\) grid and rank/support primitive.
The candidate grid point is \(T=2\), \(K_- =1\), \(K_+=0\), \(K=\{-1,0\}\), and the stationary Markov assignment with \(a_T=b_T=1/2\).
Then the valid-origin set is \(\mathcal S_2(K)=\{2\}\), the only non-omitted relative-time column is \(E_0\), and the only causal target coordinate is
\[
\theta_0=m_2(01)-m_2(00).
\]
The clean-window probability is \(p_2(K)=\phi_2=1/4\), so \(\Lambda_2(K)=1/4\).
Choosing any deterministic threshold \(\kappa_2<0.044\) retains both positive residualized Gram directions for the two-column design \((E_0,L)\), where
\[
L=C_{10}+C_{11}=D_{i,t-1}.
\]
This \(L\) is an admissible nuisance basis element under Assumption~\ref{ass:minimal-class}, because it is a finite linear recombination of \(C_{10}\) and \(C_{11}\).

Write the local effect-coordinate vector as
\[
m_K=
\bigl(
\tau_1(01),\tau_1(10),\tau_1(11),
\tau_2(01),\tau_2(10),\tau_2(11)
\bigr)^\transpose,
\qquad
\tau_t(h)=m_t(h)-m_t(00).
\]
After residualizing against the path fixed effects and calendar-time fixed effects, the retained FWL moment map for \(X=(E_0,L)\) is
\[
A_{B^\star}=
\begin{pmatrix}
1/16 & 0 & 0 & 3/32 & -1/32 & -1/32\\
-1/8 & 0 & 0 & -1/16 & 1/16 & 1/16
\end{pmatrix}.
\]
The two positive eigenvalues of the residualized Gram matrix \(X^\transpose M_FX\) are approximately \(0.04495\) and \(0.17380\), so both rows are regular under the displayed threshold.
The target row for \(\theta_0\) is
\[
\ell=(0,0,0,1,0,0).
\]
It is in the row space of the one-nuisance-column design, because
\[
16(1/16,0,0,3/32,-1/32,-1/32)
+8(-1/8,0,0,-1/16,1/16,1/16)
=(0,0,0,1,0,0).
\]
Therefore
\[
\theta_0=\ell^\transpose m_K
=16 z_{E_0}+8 z_L,
\qquad
z=A_{B^\star}m_K,
\]
which is a computable regular identifying functional of the retained observed moments.
No shape restriction on \(m_K\) is used; the identity holds for every value of the six local response coordinates.

This contradicts the first sentence of Conjecture~2.
For this admissible finite-window target, the one-column nuisance basis \(B^\star=\{C_{10}+C_{11}\}\) regularly point identifies all causal switch-on event contrasts, because there is only the \(k=0\) contrast.
Thus the two-column basis \(\{C_{10},C_{11}\}\) is not minimal in \(\mathfrak B(K)\).
As a check on the primitive, dropping to the literal one-column bases \(\{C_{10}\}\) or \(\{C_{11}\}\) leaves target-row residual norm \(1/\sqrt{3}\) in the same finite row-space calculation; the failure of the conjecture is specifically caused by the proposal's admission of finite linear recombinations, not by an omitted-variable-free literal subcollection.
