\begin{proof}[Proof of \cref{obj:oeq:feasible-upper}]
\begin{enumerate}
\item The clipping and localization schedules are those of \cref{obj:def:feasible-rate}: for \(\gamma>0\),
\[
q_n=q_0n^{-s_{\mathrm{feas}}},\qquad
u_n=\bar u\,n^{-t_{\mathrm{feas}}},
\]
while for \(\gamma=0\) the clipping schedule is fixed, \(q_n=q_0\).  The input restrictions in \cref{obj:def:feasible-rate} give \(q_0>0\); when \(\gamma>0\) they also give \(\bar u>0\), \(q_0\le 1/2\), and the eventual admissibility
\[
q_n\le c_o u_n^\gamma .
\]
Thus \(q_n>0\) for all sufficiently large \(n\). % lean: qSched

\item We first dispose of the exceptional strict-overlap case in which \(\gamma=0\) and the law-class part of the domain is empty.  Then the set over which the conditional upper risk in \cref{obj:def:upper-risk} takes its supremum is empty, so \(U_n=0\).  Taking \(C=1\) and \(p=0\), the desired inequality holds for all sufficiently large \(n\), since the right-hand side is nonnegative. % lean: feasible_upper

\item In the remaining cases the schedule is in the clipping range needed by the master bound.  If \(\gamma=0\), non-emptiness supplies a law in \(\mathcal P_{\alpha,\gamma}\); the strict-overlap endpoint condition in \cref{obj:def:law-class} gives \(\underline p\le 1/2\), and the input restriction gives
\[
q_n=q_0\le \underline p/2\le 1/2 .
\]
If \(\gamma>0\), feasibility of the selected maximizer gives \(s_{\mathrm{feas}}\ge0\), hence \(n^{-s_{\mathrm{feas}}}\le1\) for \(n\ge1\), and therefore
\[
q_n=q_0n^{-s_{\mathrm{feas}}}\le q_0\le 1/2 .
\]
For \(\gamma=0\) we also record that \(q_n\) is eventually equal to the fixed value \(q_0\). % lean: feasibleMaximizer_mem

\item Apply \cref{obj:lem:crude-localized-master-bound} with these schedules.  It gives constants \(C_{\mathrm M}>0\) and \(p_{\mathrm M}\ge0\) such that, for all sufficiently large \(n\), every law \(P\) in the side-condition domain of \cref{obj:def:upper-risk} satisfies the corresponding master inequality.  Apply \cref{obj:lem:clip-balance-exponent} to the same schedules and nuisance-rate exponents.  It gives constants \(C_{\mathrm B}>0\) and \(p_{\mathrm B}\ge0\) such that the deterministic bracket in the master bound is at most
\[
C_{\mathrm B}n^{-r_{\mathrm{feas}}}(\log n)^{p_{\mathrm B}},
\]
with \(r_{\mathrm{feas}}=r_{\mathrm{up}}\) by \cref{obj:def:feasible-rate}. % lean: crude_localized_master_bound

\item Suppose first that \(\gamma=0\).  For every \(P\) in the upper-risk domain and all sufficiently large \(n\), \cref{obj:lem:crude-localized-master-bound} gives
\[
\mathbb E_{P^{\otimes n}} R_P(\widehat\pi_n)
\le
C_{\mathrm M}\{n^{-A_\alpha}+r_{\mu,n}r_{e,n}\}(\log n)^{p_{\mathrm M}} .
\]
The \(\gamma=0\) branch of \cref{obj:lem:clip-balance-exponent} bounds the brace by
\[
C_{\mathrm B}n^{-r_{\mathrm{feas}}}(\log n)^{p_{\mathrm B}} .
\]
Since \(\log n>0\) for large \(n\), the logarithmic powers combine, and hence
\[
\mathbb E_{P^{\otimes n}} R_P(\widehat\pi_n)
\le
C_{\mathrm M}C_{\mathrm B}
n^{-r_{\mathrm{feas}}}(\log n)^{p_{\mathrm M}+p_{\mathrm B}} .
\]
Taking the supremum over \(P\) in \cref{obj:def:upper-risk} preserves this bound. % lean: clip_balance_exponent

\item Now suppose \(\gamma>0\).  For all sufficiently large \(n\), we have \(u_n>0\), \(u_n\le u_0\), and \(q_n\le c_o u_n^\gamma\); the bound \(u_n\le u_0\) follows from \(\bar u\le u_0\), \(t_{\mathrm{feas}}\ge0\), and \(n^{-t_{\mathrm{feas}}}\le1\).  Thus \cref{obj:lem:crude-localized-master-bound} yields, for each \(P\) in the upper-risk domain,
\[
\mathbb E_{P^{\otimes n}} R_P(\widehat\pi_n)
\le
C_{\mathrm M}
\left\{
n^{-r_\star}
+(nq_n^2)^{-A_\alpha}
+\frac{r_{\mu,n}r_{e,n}}{q_n}
+r_{\mu,n}u_n^{\alpha/2}q_n^{1/(2\gamma)}
+\frac{r_{\mu,n}^2}{u_n}
\right\}
(\log n)^{p_{\mathrm M}} .
\]
The positive-\(\gamma\) branch of \cref{obj:lem:clip-balance-exponent} bounds the brace by
\[
C_{\mathrm B}n^{-r_{\mathrm{feas}}}(\log n)^{p_{\mathrm B}} .
\]
Combining the two displays and then taking the supremum in \cref{obj:def:upper-risk} gives
\[
U_n(\alpha,\gamma,a,c;\widehat\eta)
\le
C_{\mathrm M}C_{\mathrm B}
n^{-r_{\mathrm{feas}}}(\log n)^{p_{\mathrm M}+p_{\mathrm B}} .
\]
With \(C=C_{\mathrm M}C_{\mathrm B}\), \(p=p_{\mathrm M}+p_{\mathrm B}\), and \(r_{\mathrm{feas}}=r_{\mathrm{up}}\), this is the claimed bound. % lean: feasible_upper
\end{enumerate}
\end{proof}
