% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_mc\_estimation\_duality, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{panel\_mc\_estimation\_duality} / \texttt{v1}%
  \\ \large\textit{Projected Riesz--Schur certificates for a strict SCM/ASCM/SDiD/matrix-completion exact-identification lattice}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\textbf{Tuple:} $(qid,\ specialization,\ p,\ assignment,\ target,\ regression)$.
Here $qid=\texttt{panel\_mc\_estimation\_duality}$ and
$specialization=\texttt{v1}$. The memory length is $p=0$: units follow
absorbing staggered adoption $D_{it}=\one\{t\ge G_i\}$ over
$t=1,\ldots,T$, with $G_i\in\mathcal G\subseteq\{2,\ldots,T,\infty\}$.
The assignment convention is deterministic in the proposal: the cohort sizes,
the treated cells $\mathcal A=\{(i,t):t\ge G_i,\ G_i<\infty\}$, and the
donor pre-adoption cells $\mathcal O_0=\{(i,t):t<G_i\}$ are fixed design
objects; randomness enters through outcomes only. The target is the fixed
weighted ATT
\[
  \theta(M^0,Y)=\sum_{(i,t)\in\mathcal A}q_{it}\{Y_{it}-M^0_{it}\},
  \qquad q_{it}>0,\quad \sum_{(i,t)\in\mathcal A}q_{it}=1,
\]
where $M^0$ is the untreated mean matrix and $Y_{it}$ is observed. The
regression / estimator convention is the ordered lattice of four population
counterfactual functionals: convex SCM, affine ridge ASCM, staggered SDiD, and
rank-$r$ matrix completion, each defined by the optimization problems in
Section~\ref{sec:setup}. The low-rank untreated surface is
$M^0=A+B+L^0$, where $A_{it}=\alpha_i$, $B_{it}=\lambda_t$ and
$\operatorname{rank}(L^0)\le r$ after additive effects are removed.

\begin{abstract}
This proposal asks whether the leading synthetic-control and matrix-completion
identification domains form a strict lattice in staggered-treatment panels.
The proposed focal object is an adjacent projected Riesz--Schur certificate
$\Delta_{a,b,r}(P,D)$ computed from each lower method's normal equations, each
higher method's admissible tangent directions, and the ATT linear functional.
The flagship conjecture is that, for each adjacent pair
convex SCM $\subset$ affine ASCM $\subset$ staggered SDiD $\subset$ rank-$r$
matrix completion, exact ATT equality holds for all compatible rank-$r$
untreated matrices if and only if the corresponding certificate vanishes, and
strict separation occurs on a relative-open fixed-rank chart whenever it does
not vanish. This is a proposal, not a proof: the certificate theorem, plug-in
diagnostic law, and minimal witnesses are labelled as Conjectures. If resolved,
the result would turn the current
``compare SDiD, augmented SCM, and matrix completion'' practice into a finite
diagnostic for when the methods identify the same ATT and when disagreement is
structural rather than tuning noise.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied staggered-adoption studies often report synthetic-control,
augmented-synthetic-control, SDiD, and matrix-completion estimates as
robustness checks for the same ATT. The estimators are built from different
restrictions: convex donor weights, signed or ridge-corrected weights, joint
unit--time balancing, and low-rank completion. Without a theorem that compares
their exact-identification domains, disagreement is hard to interpret: it may
reflect finite-sample tuning, or it may prove that the observed panel does not
contain enough untreated information for the claimed counterfactual.

\paragraph{The main finding (proposed).}
The proposed main finding is the projected Riesz--Schur lattice in
Conjecture~\ref{conj:lattice}. For each adjacent pair of estimator classes
$(a,b)$ in the ordered list
\[
  \mathrm{SCM}_{+}\prec \mathrm{ASCM}_{\rho}\prec
  \mathrm{SDID}_{\rho_N,\rho_T}\prec \mathrm{MC}_{r,\lambda},
\]
define $\Delta_{a,b,r}(P,D)$ as the norm of the ATT Riesz representer after
projecting it onto the quotient of the higher method's tangent space by the
lower method's normal-equation tangent space. The conjecture says that
$\Delta_{a,b,r}(P,D)=0$ is exactly the equality frontier; when it is positive,
there is a rank-$r$ untreated matrix compatible with the observed donor cells
on which the two methods give different ATT functionals.

\paragraph{What is new.}
The closest published comparators are \citet{AbadieDiamondHainmueller2010}
for convex SCM, \citet{DoudchenkoImbens2016} for relaxed regression-style
synthetic controls, \citet{BenMichaelFellerRothstein2021} for augmented SCM,
\citet{ArkhangelskyAtheyHirshbergImbensWager2021} for SDiD, and
\citet{AtheyBayatiDoudchenkoImbensKhosravi2021} and
\citet{AtheyBayatiImbensQu2019} for matrix-completion / ensemble panel
predictors, and \citet[arXiv v3 abstract and Section~2 estimator definition]{AtheyImbensQuViviano2025}
for a combined low-rank, unit-weight, and time-weight estimator. Those papers define methods and
consistency or performance regimes, but do not give an adjacent-pair
necessary-and-sufficient certificate for equality of the ATT functional over a
common bounded-rank completion class. The new object is not a relabelled
spectral gap: $\Delta_{a,b,r}(P,D)$ is an ATT-projected Riesz residual built
from explicit normal-equation matrices, so its zero test compares the estimand
delivered by two named methods rather than the numerical conditioning of one
estimator.

\paragraph{How it positions in the literature.}
The kernel lives in the panel / linear-projection cluster. It borrows the
modern staggered target language of \citet{CallawaySantAnna2021} and
\citet{BorusyakJaravelSpiess2024}, the synthetic-control geometry of
\citet{AbadieDiamondHainmueller2010} and \citet{DoudchenkoImbens2016}, the
augmented and staggered synthetic-control comparisons of
\citet{BenMichaelFellerRothstein2021} and
\citet{BenMichaelFellerRothstein2022}, the SDiD weighting system of
\citet{ArkhangelskyAtheyHirshbergImbensWager2021}, and the causal-panel
matrix-completion framework of
\citet{AtheyBayatiDoudchenkoImbensKhosravi2021}. The proposal is deliberately
orthogonal to Q1 history-regression sign-flip results in the CausalSmith
catalogue: the object here is a cross-estimator ATT equality certificate, not
a coefficient contamination formula for a particular treatment-history basis.

\paragraph{Implications for the community.}
The concrete downstream consumer is the staggered synthetic-control workflow
of \citet{BenMichaelFellerRothstein2022}. If the conjecture is true, analysts
can compute $\Delta_{\mathrm{ASCM},\mathrm{SDID},r}$ and
$\Delta_{\mathrm{SDID},\mathrm{MC},r}$ before treating ASCM, SDiD, and matrix
completion as interchangeable ATT estimators; positive certificates warn that
the methods identify different counterfactual functionals on admissible
low-rank panels. The companion sample diagnostic in
Conjecture~\ref{conj:plugin} makes this operational: the same active-set
matrices define a plug-in $\widehat\Delta_{a,b,r}$ whose first-order law is
conjectured to be valid when the estimated active set is stable.

\paragraph{How research benefits from the conclusion.}
Researchers should report the adjacent Riesz--Schur certificates alongside
SCM/ASCM/SDiD/MC estimates and avoid interpreting agreement or disagreement
without first checking the exact-identification lattice node they occupy.

\section{Related work}
\citet[Section~2, donor-weight program]{AbadieDiamondHainmueller2010} define
the convex synthetic-control estimator under exact donor balancing; this is
the bottom node of the proposed lattice.
\citet[Sections~2--3, restriction map between SC, DID, and regression]{DoudchenkoImbens2016}
show how synthetic controls, difference in differences, and linear regression
are connected through restrictions on weights and intercepts; this motivates
the affine/relaxed node but does not state adjacent exact-ID certificates.
\citet[Sections~2--3, bias-correction formula after imperfect SC fit]{BenMichaelFellerRothstein2021}
develop augmented synthetic control, using an outcome model to correct
imperfect synthetic-control fit; this is the closest ASCM comparator for the
affine ridge node.
\citet[Section~2, unit/time weighting objective and ATT estimator]{ArkhangelskyAtheyHirshbergImbensWager2021}
introduce synthetic DiD with unit and time weights and prove
consistency/asymptotic normality under latent-factor structure; this is the
SDiD node of the proposed lattice.
\citet[Sections~2--3, nuclear-norm objective and causal-panel setup]{AtheyBayatiDoudchenkoImbensKhosravi2021}
propose nuclear-norm matrix completion for causal panels and discuss links to
synthetic controls; this is the matrix-completion node, but the paper does not
give a finite adjacent equality certificate against SDiD or ASCM.
\citet[Section~2, completion-matrix construction and local/global uniqueness tests]{SingerCucuringu2010}
give deterministic low-rank completion certificates via a completion matrix
adapted from rigidity theory; this is a close finite-certificate precedent,
but its certificate concerns uniqueness of a low-rank completion under an
observation mask, not equality of adjacent causal ATT functionals after SDiD
or ASCM normal equations are imposed.
\citet[main theorem and graph-limit solvability criterion]{Chatterjee2020}
gives a deterministic asymptotic theory for arbitrary low-rank matrix
completion masks; it is a closer mask-design comparator than random-mask
phase-transition papers, but it does not include staggered causal estimators,
ATT Riesz rows, or adjacent SCM/SDiD/MC equality frontiers.
\citet[Section~2, ensemble comparison of panel estimators]{AtheyBayatiImbensQu2019}
compare ensemble methods for causal effects in panel settings, including
regression, synthetic control, and matrix completion; it is a close
multi-method comparator, but it treats combination and prediction performance
rather than a necessary-and-sufficient ATT identification lattice.
\citet[Sections~2--3, interactive-fixed-effect counterfactual estimator]{Xu2017}
develop the generalized synthetic-control method by imputing counterfactuals
with interactive fixed effects; it is a close low-rank/SC unification
comparator, but it does not give an adjacent active-set certificate comparing
GSC/MC with SDiD or ASCM on the same ATT functional.
\citet[arXiv v3 abstract and Section~2 estimator definition]{AtheyImbensQuViviano2025}
introduce the Triply RObust Panel (TROP) estimator, combining a low-rank
outcome model with unit and time weights; it is the closest 2025 comparator,
but it targets estimator performance against TWFE, SC, MC, and SDiD rather
than an observable adjacent-pair equality certificate.
\citet{BenMichaelFellerRothstein2022} extend synthetic controls to staggered
adoption and emphasize individual and pooled treated-unit imbalance; this
supplies the staggered-design consumer of the proposed certificates.
\citet{BaiNg2021} give factor-imputation theory for counterfactuals under
interactive fixed effects; their rank and factor-strength restrictions are the
background low-rank regime for the matrix-completion node.
\citet{ChoiKwonLiao2024} develop inference after low-rank completion without
sample splitting and apply it to ATE estimation; it is adjacent to the
matrix-completion node but does not compare exact-ID domains across
SCM/ASCM/SDiD/MC.
\citet{CallawaySantAnna2021} and \citet{BorusyakJaravelSpiess2024} provide
staggered-adoption ATT notation and imputation estimators; they anchor the
target parameter but not the synthetic-control / matrix-completion lattice.
In-catalogue prior art is doc/API.md Section~1: Q1\_MinimalBasis,
Q1\_StaggeredMinimalBasis, Q1\_SignFlip, and Q1\_SpectralThreshold give
FWL, clean-basis, staggered-basis, and Markov spectral sign-threshold panel
results. Those entries do not define synthetic-control, augmented-control,
SDiD, or matrix-completion population optimizers and therefore do not contain
the proposed Riesz--Schur lattice. The failed banked proposal
\texttt{panel\_sdid\_mc\_id\_v1} is the nearest in-repo signal: its reviewer
asked for explicit finite-dimensional observable computation after earlier
spectral-frontier and lattice drafts left the certificate underdefined.

\section{Formal setup}\label{sec:setup}
Let $I=\{1,\ldots,N\}$ and $T=\{1,\ldots,\bar T\}$ be fixed finite sets.
The observed outcome matrix is $Y\in\R^{N\times \bar T}$ and the untreated
mean matrix is $M^0\in\R^{N\times\bar T}$. Write $P$ for the finite
observable law consisting of $(Y_{it},D_{it},G_i)$ and the fixed design
weights $q_{it}$. For proposal purposes all estimator functionals are
population maps of $(P,D)$; the sample diagnostic is defined after the
population certificate.

Let $\mathcal O_0=\{(i,t):t<G_i\}$ be untreated observed cells and
$\mathcal A=\{(i,t):t\ge G_i,\ G_i<\infty\}$ be target cells. Let
$\ell_q(H)=\sum_{(i,t)\in\mathcal A}q_{it}H_{it}$ be the ATT linear
functional on counterfactual matrices. Let $\Pi_{\alpha,\lambda}$ be the
orthogonal residual-maker that removes unit and time additive effects on the
ambient Frobenius space. The admissible rank-$r$ completion class is
\[
  \mathcal C_r(P,D)=
  \{M:\ M_{\mathcal O_0}=\E[Y_{\mathcal O_0}\mid D],\
        \operatorname{rank}(\Pi_{\alpha,\lambda}M)\le r\}.
\]
For a candidate counterfactual $\widehat M^m(P,D)$ produced by method $m$,
the method's ATT functional is
$\phi_m(P,D)=\ell_q(Y-\widehat M^m)$. For the lattice conjecture the
completion must also be allowed to vary. Define
\[
  \widehat M^m(P,D;M)=\mathcal A_m(P,D)M+\mathcal B_m(P,D)Y
  \quad\text{and}\quad
  \phi_m(P,D;M)=\ell_q\{Y-\widehat M^m(P,D;M)\},
\]
where $\mathcal A_m(P,D)$ and $\mathcal B_m(P,D)$ are the finite matrices
obtained by freezing method $m$'s active set and differentiating its displayed
population normal equations with respect to the compatible completion
$M\in\mathcal C_r(P,D)$. Thus $\phi_m(P,D)=\phi_m(P,D;M^0)$ at the true
untreated matrix, while $\phi_m(P,D;M)$ is a linear functional on the local
rank-$r$ completion class.

The four population optimizers are fixed as follows. Convex SCM solves, for
each target row/cohort block $c$, a donor-weight problem
\[
  \min_{w\in\Delta_c}\|X_c-X_D^\transpose w\|_{V_c}^2
  \quad\text{and sets}\quad \widehat M^{+}_{ct}=Y_{Dt}^\transpose w_c
  \ \text{on target post cells},
\]
where $\Delta_c=\{w\ge0:\one^\transpose w=1,\ w_i=0\text{ if }i\text{ is not a
donor for }c\}$, $X_c\in\R^{T_c^-}$ is the vector of cohort-$c$
pre-adoption outcomes, $X_D\in\R^{n_c(D)\times T_c^-}$ stacks the corresponding
donor pre-adoption rows, and $V_c\in\R^{T_c^-\times T_c^-}$ is a fixed
positive semidefinite pre-period weighting matrix. Affine ASCM solves
\[
  \min_{w\in\Delta_c^{\mathrm{aff}},\,\beta\in\R^{d_\mu}}
  \|X_c-X_D^\transpose w-Z_c^\transpose\beta+
      \sum_{i\in D_c}w_i Z_i^\transpose\beta\|_{V_c}^2
  +\rho_{\mathrm A}\|w\|_2^2+\rho_\mu\|\beta\|_2^2,
\]
where $\Delta_c^{\mathrm{aff}}=\{w:\one^\transpose w=1,\ w_i=0\text{ off }
D_c\}$, $Z_i\in\R^{d_\mu\times T_c^-}$ are the pre-period regressors for the
ridge outcome model, and
$\widehat\mu_{it}=z_{it}^\transpose\widehat\beta_c$. The ASCM target-cell
counterfactual is
\[
  \widehat M^{\mathrm A}_{ct}
  =Y_{D_ct}^\transpose \widehat w_c+
    \widehat\mu_{ct}-\sum_{i\in D_c}\widehat w_{ci}\widehat\mu_{it}.
\]
Thus the ASCM KKT block entering $J_m$ contains derivatives with respect to
both $w_c$ and $\beta_c$, and its target-cell Riesz row includes the explicit
outcome-model correction above.

For staggered SDiD, let $C$ index treated cohorts, let $D_C$ be their
not-yet-treated donor risk set, let $\mathcal T_C^-$ be the pre-adoption
periods used for time balancing, and let $\mathcal T_C^+$ be the target
post-periods. Define
$X_T^{C}\in\R^{|C|\times |\mathcal T_C^-|}$ as the matrix of cohort-average
treated outcomes before adoption and
$X_D^{C}\in\R^{|D_C|\times |\mathcal T_C^-|}$ as the donor pre-adoption matrix.
The donor target-period vector is
$Y_{D_C,\mathcal T_C^+}\in\R^{|D_C|\times |\mathcal T_C^+|}$ and the treated
target-period vector is
$Y_{C,\mathcal T_C^+}\in\R^{|C|\times |\mathcal T_C^+|}$. Staggered SDiD solves
\[
  \min_{\omega,\lambda}
  \| (X_T^{C})^\transpose\pi_C-(X_D^{C})^\transpose\omega\|_{\lambda}^2+
  \rho_N\|\omega\|_2^2+\rho_T\|\lambda\|_2^2
\]
subject to donor-risk-set support,
$\one^\transpose\omega=1$, $\omega\ge0$, $\one^\transpose\lambda=1$,
$\lambda\ge0$, where $\pi_C$ are the fixed cohort aggregation weights and
$\|v\|_\lambda^2=\sum_{t\in\mathcal T_C^-}\lambda_t v_t^2$. Its target
functional is the weighted double contrast
\[
  \phi_{\mathrm{SDID}}=
  \sum_{t\in\mathcal T_C^+}\nu_t
  \{Y_{C,t}^\transpose\pi_C-Y_{D_C,t}^\transpose\omega\}
  -\sum_{t\in\mathcal T_C^-}\lambda_t
  \{Y_{C,t}^\transpose\pi_C-Y_{D_C,t}^\transpose\omega\},
\]
with fixed post weights $\nu_t$. The SDiD KKT block entering $J_m$ therefore
has columns for the active donor weights $\omega$, active pre-period time
weights $\lambda$, and the simplex multipliers. Rank-$r$ MC solves
\[
  \min_{M}\ \|P_{\mathcal O_0}(Y-M)\|_F^2+\lambda_{\mathrm{MC}}\|M\|_\*
  \quad\text{subject to}\quad
  \operatorname{rank}(\Pi_{\alpha,\lambda}M)\le r
\]
with the deterministic tie-breaker choosing the minimum Frobenius norm among
population minimizers.

For each method $m$, let $J_m(P,D)$ be the active-set Jacobian of the frozen
normal equations with columns indexed by local perturbations of $M$. Define
\[
  N_m(P,D)=\operatorname{rowspan}\{J_m(P,D)\},\qquad
  R_m(P,D)=\mathcal A_m(P,D)^\transpose \ell_q,
\]
the normal-equation tangent row space and Frobenius Riesz row for
$M\mapsto\phi_m(P,D;M)$. For adjacent $a\prec b$, define
the common row space
\[
  H_{a,b}(P,D)=N_a(P,D)\cap N_b(P,D),
\]
and the higher-method quotient slice
\[
  K_{a\to b}(P,D)=N_b(P,D)\cap H_{a,b}(P,D)^\perp,
\]
where the orthogonal complement is taken in the ambient Frobenius row space
after both systems are embedded in the same tangent coordinates for
$\mathcal C_r(P,D)$. Thus $K_{a\to b}$ is the canonical representative of
the quotient $N_b/H_{a,b}$ and does not require $N_a\subseteq N_b$ or
$N_b\subseteq N_a$. Define the independent
focal object
\[
  \Delta_{a,b,r}(P,D)=
  \left\|(I-\Pi_{\overline{N_a+K_{a\to b}}})\{R_b-R_a\}\right\|_F,
\]
where $\overline{N_a+K_{a\to b}}$ is its closed finite-dimensional
span and $\Pi_{\overline{N_a+K_{a\to b}}}$ is the Frobenius projection. This
definition does not mention equality of $\phi_a$ and $\phi_b$; equality is the
nontrivial claim of Conjecture~\ref{conj:lattice}. Let $c_{a,b}>0$ denote the
smallest singular value of the quotient evaluation map from
$K_{a\to b}(P,D)$ modulo the null directions annihilated by $R_b-R_a$ to the
ATT contrast row on the fixed active-set chart; Assumption~\ref{ass:nongenerate}
requires this finite constant to be well-defined whenever a positive-margin
separation is stated.

For a random panel sequence indexed by $s=1,\ldots,n_{\mathrm{eff}}$, let
$\widehat P$ denote the empirical analogue of the finite moments entering the
four active-set normal equations. The sample diagnostic is
$\widehat\Delta_{a,b,r}=\Delta_{a,b,r}(\widehat P,D)$ computed after replacing
population Gram matrices, Riesz rows, and rank-$r$ completion Jacobians by
their sample analogues on the selected active-set chart. Let
$g_{a,b,r}(P,D)$ be the vector of all finite moments entering
$\Delta_{a,b,r}$, and let $\Gamma_{a,b,r}(P,D)$ be the derivative of the map
$g\mapsto\Delta_{a,b,r}$ on the region where the projection residual is
nonzero. Define
\[
  \sigma^2_{a,b,r}(P,D)=
  \Gamma_{a,b,r}(P,D)\,\Omega_{a,b,r}(P,D)\,
  \Gamma_{a,b,r}(P,D)^\transpose,
\]
where $\Omega_{a,b,r}$ is the long-run covariance matrix of
$\sqrt{n_{\mathrm{eff}}}\{g_{a,b,r}(\widehat P,D)-g_{a,b,r}(P,D)\}$.

\begin{verbatim}
Locked parameters:
qid = panel_mc_estimation_duality
specialization = v1
p = 0
assignment = fixed absorbing staggered adoption mask D with cohort risk sets
target = weighted ATT theta(M0,Y)=sum_{(i,t) in A} q_it (Y_it-M0_it)
regression = additive effects plus rank-r untreated matrix; estimator lattice
             convex SCM -> affine ridge ASCM -> staggered SDiD -> rank-r MC
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Staggered overlap and target support]\label{ass:overlap}
Every target cell $(i,t)\in\mathcal A$ has a nonempty not-yet-treated donor
risk set at $t$, and every cohort block appearing in $q$ has at least one
pre-adoption cell and one donor row outside the treated cohort.
\end{assumption}

\begin{assumption}[Rank-$r$ untreated completion class]\label{ass:rank}
The untreated mean matrix satisfies $M^0\in\mathcal C_r(P,D)$ and the tangent
cone of $\mathcal C_r(P,D)$ at $M^0$ is generated by first-order perturbations
$UV^\transpose+U_\perp V^\transpose+UV_\perp^\transpose$ after additive effects
are residualized.
\end{assumption}

\begin{assumption}[Unique population optimizers]\label{ass:unique}
The four population optimization problems defining
$\mathrm{SCM}_{+}$, $\mathrm{ASCM}_{\rho}$,
$\mathrm{SDID}_{\rho_N,\rho_T}$, and $\mathrm{MC}_{r,\lambda}$ have unique
solutions under the stated tie-breaker, and their active constraints are
locally constant on the neighborhood under study.
\end{assumption}

\begin{assumption}[Regular normal-equation linearization]\label{ass:linear}
The KKT systems for the four optimizers are differentiable at $(P,D)$ after
conditioning on the active set, and their derivative matrices have Moore--Penrose
inverses on the orthogonal complement of their null spaces.
\end{assumption}

\begin{assumption}[Nondegenerate observed design]\label{ass:nongenerate}
The donor pre-period Gram matrices, SDiD unit/time Gram matrices, and the
rank-$r$ observed-cell completion Jacobian all have positive smallest
nonzero singular values. Let $\kappa_{\min}(P,D)$ be the minimum of these
singular values.
\end{assumption}

\begin{assumption}[Bounded certificate margin]\label{ass:margin}
For any positive-margin statement, the displayed margin satisfies
$0<\delta\le \kappa_{\min}(P,D)/4$. This prevents separation claims from
using a free tuning parameter unrelated to the observable design.
\end{assumption}

\begin{assumption}[Sampling and active-set stability]\label{ass:sampling}
For the growing-panel sequence used to estimate
$\widehat\Delta_{a,b,r}$, fixed rank $r$ is maintained, the selected active
sets of the four optimizers equal their population active sets with
probability tending to one, and
\[
  \sqrt{n_{\mathrm{eff}}}\{g_{a,b,r}(\widehat P,D)-g_{a,b,r}(P,D)\}
  \rightsquigarrow N(0,\Omega_{a,b,r}(P,D)).
\]
The matrix $\Omega_{a,b,r}(P,D)$ is positive semidefinite and consistently
estimable on the fixed active-set chart.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: explicit adjacent certificate construction]\label{thm:construction}
Under Assumptions~\ref{ass:overlap}, \ref{ass:rank}, \ref{ass:unique},
\ref{ass:linear}, and \ref{ass:nongenerate}, the quantity
$\Delta_{a,b,r}(P,D)$ is a finite-dimensional computable scalar for every
adjacent pair
$a\prec b$ in
$\mathrm{SCM}_{+}\prec \mathrm{ASCM}_{\rho}\prec
\mathrm{SDID}_{\rho_N,\rho_T}\prec \mathrm{MC}_{r,\lambda}$. Its inputs are
the four displayed population optimization systems, the active constraint
sets, the rank-$r$ completion Jacobian, the ATT row vector $\ell_q$, and
Moore--Penrose inverses of the resulting normal-equation matrices.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The construction is closest to \citet{DoudchenkoImbens2016},
\citet{BenMichaelFellerRothstein2021},
\citet{ArkhangelskyAtheyHirshbergImbensWager2021}, and
\citet{AtheyBayatiDoudchenkoImbensKhosravi2021}: respectively, their
restriction-map sections, ASCM bias-correction sections, SDiD Section~2
weighting objective, and MC Sections~2--3 nuclear-norm objective define the
individual optimizers but do not assemble their active-set normal equations
into one adjacent Riesz--Schur zero-test. The deterministic completion
certificates of \citet[Section~2]{SingerCucuringu2010} and the arbitrary-mask
solvability criterion of \citet[main theorem]{Chatterjee2020} are closer to
the $J_{\mathrm{MC}}$ block, but they test low-rank completion uniqueness or
asymptotic solvability rather than whether an ATT Riesz row is already
spanned by SDiD/ASCM normal equations. The in-repo Q1 panel entries in doc/API.md
contain Gram/FWL computations for treatment-history regressions, not these
synthetic-control and matrix-completion normal equations. (b) Resolving this
construction gives Stage~0 a concrete object to verify for the
\texttt{panel\_sdid\_mc\_id\_v1} reviewer request for an explicit finite
observable computation.

\begin{conjecture}[Conjecture 1: strict adjacent exact-identification lattice (NOT YET PROVED)]\label{conj:lattice}
Under Assumptions~\ref{ass:overlap}--\ref{ass:margin}, for each adjacent
pair $a\prec b$ and every $(P,D)$ in the locally fixed active-set region,
\[
  \phi_a(P,D;M)=\phi_b(P,D;M)\ \text{for all }M\in\mathcal C_r(P,D)
  \quad\Longleftrightarrow\quad
  \Delta_{a,b,r}(P,D)=0.
\]
If $\Delta_{a,b,r}(P,D)\ge\delta$ for
$0<\delta\le\kappa_{\min}(P,D)/4$, then there is a relative-open
neighborhood in the fixed-rank completion manifold, with the observed donor
cells and active-set chart fixed, on which the adjacent ATT functionals differ
by at least $c_{a,b}\delta$ for a method-specific positive constant $c_{a,b}$.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Sections~2--3]{AtheyBayatiDoudchenkoImbensKhosravi2021} state that
causal-panel matrix completion, synthetic controls, and related methods differ
in restrictions; \citet[Section~2]{AtheyBayatiImbensQu2019} compare ensembles
of such predictors; \citet[Sections~2--3]{Xu2017} imputes counterfactuals
with interactive fixed effects; \citet[arXiv v3 abstract and Section~2 estimator definition]{AtheyImbensQuViviano2025}
combine low-rank outcome structure with unit and time weights in TROP. None
gives an iff frontier for ATT equality over a common rank-$r$ completion
class. The proposed epsilon-gap is the adjacent-pair iff certificate plus
relative-open strict separation, not another consistency theorem for one
method. \citet{SingerCucuringu2010} and \citet{Chatterjee2020} supply
deterministic low-rank completion comparators, but their null object is
completion uniqueness or solvability of the whole missing matrix; the proposed
certificate allows completion nonuniqueness in directions orthogonal to the
ATT contrast.
(b) The concrete consumer is the staggered synthetic-control
analysis of \citet{BenMichaelFellerRothstein2022}: the conjecture would tell
when pooled SCM imbalance can be corrected by SDiD or MC without changing the
identified ATT.

\begin{conjecture}[Conjecture 2: plug-in diagnostic and first-order law (NOT YET PROVED)]\label{conj:plugin}
Under Assumptions~\ref{ass:overlap}--\ref{ass:sampling}, fix an adjacent
pair $a\prec b$ with $\Delta_{a,b,r}(P,D)>0$. The plug-in diagnostic
$\widehat\Delta_{a,b,r}=\Delta_{a,b,r}(\widehat P,D)$ is locally regular on
the fixed active-set chart and satisfies
\[
  \sqrt{n_{\mathrm{eff}}}
  \{\widehat\Delta_{a,b,r}-\Delta_{a,b,r}(P,D)\}
  \rightsquigarrow
  N(0,\sigma^2_{a,b,r}(P,D)).
\]
When $\Delta_{a,b,r}(P,D)=0$, the squared diagnostic
$n_{\mathrm{eff}}\widehat\Delta_{a,b,r}^{\,2}$ has the corresponding
projected quadratic-form limit determined by the same quotient projection.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Section~2]{ArkhangelskyAtheyHirshbergImbensWager2021} prove
large-sample theory for SDiD itself, \citet[Sections~2--3]{ChoiKwonLiao2024}
study low-rank completion inference, and \citet[Sections~2--3]{Xu2017}
estimate interactive-fixed-effect counterfactuals. None derives a sampling
law for an adjacent-pair equality diagnostic whose null is that two named
panel estimators identify the same ATT functional. (b) The concrete consumer
is the \citet{BenMichaelFellerRothstein2022} staggered-SCM workflow: analysts
would have a rate-calibrated test statistic for deciding whether ASCM, SDiD,
and MC agreement is an identification fact or a finite-sample accident.

\begin{conjecture}[Conjecture 3: minimal noncorner witnesses (NOT YET PROVED)]\label{conj:witnesses}
Under Assumptions~\ref{ass:overlap}--\ref{ass:margin}, each strict adjacent
inclusion in Conjecture~\ref{conj:lattice} has a concrete noncorner witness:
\begin{enumerate}[label=(\roman*)]
\item a $3\times3$ donor-pre-period block for
$\mathrm{SCM}_{+}\prec\mathrm{ASCM}_{\rho}$ with one negative affine weight
direction and nonzero ATT projection;
\item a $3\times4$ staggered block for
$\mathrm{ASCM}_{\rho}\prec\mathrm{SDID}_{\rho_N,\rho_T}$ where time weights
remove a cohort shock that affine unit weights cannot remove;
\item a $4\times4$ rank-one-plus-additive block for
$\mathrm{SDID}_{\rho_N,\rho_T}\prec\mathrm{MC}_{1,\lambda}$ where the
rank-one completion tangent contains a treated-post direction orthogonal to
all SDiD unit/time balancing equations.
\end{enumerate}
In each witness the observable donor cells are nonconstant, each target and
donor risk set is nonempty, and the determinant-ratio ATT gap is bounded below
by a positive $\delta\le\kappa_{\min}(P,D)/4$.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The nearest negative examples in
\citet[Sections~2--3, bias correction after imperfect pretreatment fit]{BenMichaelFellerRothstein2021}
and
\citet[Sections~2--3, penalized donor-choice objective for disaggregated data]{AbadieLHour2021}
show that penalization or imperfect fit matters for synthetic controls, but
do not give minimal staggered rank-$r$ witnesses for each adjacent pair in
the SCM/ASCM/SDiD/MC lattice. (b) The consumer is the
\citet{AtheyBayatiDoudchenkoImbensKhosravi2021} matrix-completion user: the
witnesses would identify the smallest panel sizes where agreement with SDiD
is mathematically impossible rather than empirically accidental.

\section{Sanity-check corollaries}
\begin{corollary}[Additive exact-balance collapse]\label{cor:additive}
Under Assumptions~\ref{ass:overlap}, \ref{ass:unique}, and
\ref{ass:linear}, if $r=0$ and each target cohort's additive untreated profile
lies in the convex hull of its donor profiles with exact pre-period balance,
then all three adjacent certificates vanish and all four method functionals
equal the same ATT.
\end{corollary}
The reduction is: under $r=0$ the completion tangent contains only additive
unit and time directions; exact convex pre-period balance makes the SCM
normal equations already span the affine, SDiD, and MC ATT Riesz directions,
so $\Delta_{a,b,0}(P,D)=0$ for every adjacent pair.

\begin{corollary}[One-treated-cohort nonstaggered corner]\label{cor:single}
If there is one treated cohort, a never-treated donor pool, and exactly one
pre-period enters the SDiD time-weight program, then the
$\mathrm{ASCM}_{\rho}\prec\mathrm{SDID}_{\rho_N,\rho_T}$ certificate reduces
to the affine-weight residual direction in \citet{DoudchenkoImbens2016}.
\end{corollary}
The reduction is: with one pre-period the SDiD time-weight simplex is the
singleton $\lambda_1=1$, so the time-weight normal equation contributes no
quotient direction over affine ASCM; only the affine donor-weight residual
remains.

\begin{corollary}[Pure completion-matrix corner]\label{cor:completion}
Suppress the lower estimator constraints by taking
$N_{\mathrm{SDID}}=\{0\}$, remove additive effects before forming the rank-$r$
tangent chart, and let $J_{\mathrm{MC}}$ be the local completion matrix for
the observed untreated mask in the sense of \citet{SingerCucuringu2010}. Then
the MC part of $\Delta_{\mathrm{SDID},\mathrm{MC},r}$ reduces to
\[
  \left\|(I-\Pi_{\operatorname{rowspan}(J_{\mathrm{MC}})})R_{\mathrm{MC}}\right\|_F,
\]
the ATT-projected completion residual. This vanishes whenever the standard
completion-matrix rank test gives local uniqueness, but it can also vanish
when the completion is nonunique and all nonunique tangent directions have
zero ATT projection.
\end{corollary}
The reduction is: with the lower SDiD row space set to zero,
$H_{\mathrm{SDID},\mathrm{MC}}=\{0\}$ and
$K_{\mathrm{SDID}\to\mathrm{MC}}=\operatorname{rowspan}(J_{\mathrm{MC}})$,
so the certificate is exactly the projection of the ATT Riesz row onto the
orthogonal complement of the completion-matrix row space. This is weaker than
full local completion uniqueness and explains why the proposed causal
certificate is not subsumed by a standard completion-matrix rank test.

\begin{example}[Concrete witness route for the SCM--ASCM gap]\label{ex:scm-ascm}
Take three units and three periods, with unit 1 treated only in period 3 and
units 2 and 3 never treated. Let the pre-period donor profiles be
$X_2=(0,2)^\transpose$, $X_3=(2,0)^\transpose$, and target profile
$X_1=(-\eta,2+\eta)^\transpose$ with $0<\eta<1/4$. Convex SCM projects
$X_1$ to donor 2 and leaves residual $(-\eta,\eta)$, whereas affine ASCM can
match the target profile exactly with weights
$w_2=1+\eta/2$ and $w_3=-\eta/2$, which satisfy
$w_2+w_3=1$ but violate convexity through one negative weight. Assign post
outcomes so this affine direction has ATT projection $\eta$. The determinant
route is to write the $2\times2$ donor Gram matrix and check that the
projected SCM residual row is not in the affine normal-equation row space for
$\eta\ne0$, giving
$\Delta_{\mathrm{SCM}_{+},\mathrm{ASCM}_{\rho},r}>0$ on a nonconstant
observable law.
\end{example}

\begin{example}[Concrete witness route for the ASCM--SDiD gap]\label{ex:ascm-sdid}
Take three units and four periods, with unit 1 treated from period 4 and
units 2 and 3 never treated. Let pre-period residualized outcomes be
\[
  \begin{pmatrix}
  0&1&1+\eta\\
  0&1&1\\
  1&0&1
  \end{pmatrix}
\]
for periods 1--3, and set the target-period untreated donor outcomes to
$(1,0)$. Affine ASCM can only choose one signed unit-weight vector across all
pre-periods, so the residualized cohort shock in period 3 leaves a nonzero ATT
Riesz row. SDiD adds a time-weight normal equation that places positive mass
on periods 2 and 3 and removes that shock before the post-period contrast.
The explicit Stage~0 route is to compute the $3\times3$ block Gram matrix for
unit and time weights and verify that the SDiD time row is linearly independent
of the affine unit rows when $\eta\ne0$.
\end{example}

\begin{example}[Concrete witness route for the SDiD--MC gap]\label{ex:witness}
Take four units and four periods, cohorts $G=(3,4,\infty,\infty)$, and
untreated residual matrix
\[
  L^0(\eta)=
  \begin{pmatrix}
  0&1&\eta&2\eta\\
  1&0&2\eta&\eta\\
  0&1&0&1\\
  1&0&1&0
  \end{pmatrix}
  - \Pi_{\alpha,\lambda}
  \begin{pmatrix}
  0&1&\eta&2\eta\\
  1&0&2\eta&\eta\\
  0&1&0&1\\
  1&0&1&0
  \end{pmatrix}.
\]
For small nonzero $\eta$, the Stage~0 calculation should check that the
rank-one tangent direction generated by the treated-post block has nonzero
ATT projection while satisfying the SDiD unit/time balance equations only at
$\eta=0$. This is the noncorner witness attached to
Conjecture~\ref{conj:witnesses}(iii).
\end{example}

\section{Proof-sketch route}
The verification route is finite-dimensional. First write the KKT systems for
convex SCM, affine ridge ASCM, staggered SDiD, and rank-$r$ MC after active
sets are fixed; this gives four block normal-equation matrices and four ATT
Riesz rows. Second, for each adjacent pair, form the Schur complement of the
lower method's normal equations inside the higher method's tangent system and
project the ATT Riesz difference onto the resulting quotient space. The
``if'' direction of Conjecture~\ref{conj:lattice} should follow by showing
that a zero projected Riesz residual makes the two ATT rows equal on every
rank-$r$ feasible perturbation. The ``only if'' direction should follow by
choosing the Moore--Penrose least-norm perturbation in the quotient direction
and using Assumption~\ref{ass:margin} to keep the witness inside the local
active-set and rank-$r$ neighborhood. Boundary cases are the $3\times3$
SCM--ASCM determinant in Example~\ref{ex:scm-ascm}, the $3\times4$
ASCM--SDiD block in Example~\ref{ex:ascm-sdid}, the $4\times4$ SDiD--MC
determinant in Example~\ref{ex:witness}, plus the $r=0$ additive collapse in
Corollary~\ref{cor:additive}. For Conjecture~\ref{conj:plugin}, the route is
the delta method on the fixed active-set chart; the zero-certificate boundary
uses the quadratic-form expansion of the projected residual norm.

\section{Honest scope flags}
Theorem~\ref{thm:construction} is intended as routine finite-dimensional
linear algebra once the four population optimizers and active sets are fixed.
Conjectures~\ref{conj:lattice}, \ref{conj:plugin}, and
\ref{conj:witnesses} are not proved:
the hard part is showing that the rank-$r$ tangent cone and active-set KKT
linearizations are sufficient for global equality over the compatible
completion class, not merely first-order equality at one base point; for the
plug-in diagnostic, the hard part is proving active-set stability and the
nonregular zero-boundary limit under staggered masks. The proposal deliberately
does not claim semiparametric efficiency or tuning-path optimality. Earlier
spectral-threshold and penalty-stability angles for this topic were exhausted
by the orchestrator; this pivot keeps the strict adjacent-lattice kernel and
adds the sample diagnostic needed to use the certificate.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial angle-2 draft proposing the projected
Riesz--Schur strict SCM/ASCM/SDiD/MC exact-identification lattice; prior
verdict: none.
\item v2 (revise) -- defined completion-dependent functionals and finite
maps $N_m,R_m,K_b$, added rank to Theorem~1, anchored flagship comparators
including TROP, and supplied concrete witnesses for all three adjacent gaps;
prior verdict: REVISE.
\item v3 (revise) -- added the plug-in $\widehat\Delta_{a,b,r}$ diagnostic
and first-order-law conjecture, repaired the relative-open manifold wording,
strengthened Xu/Abadie--L'Hour/Ben-Michael--Feller--Rothstein anchors, and
fixed the one-cohort SDiD sanity reduction; prior verdict: REVISE.
\item v4 (revise) -- pinned the ASCM ridge outcome-model objective and SDiD
matrix dimensions for Theorem~1, replaced the invalid SCM--ASCM witness with
affine weights summing to one, and gave TROP a section-level anchor; prior
verdict: REVISE.
\item v5 (revise) -- replaced the ambiguous informal quotient by the
orthogonal quotient slice $K_{a\to b}=N_b\cap(N_a\cap N_b)^\perp$, added
Singer--Cucuringu and Chatterjee deterministic completion comparators, and
added the pure completion-matrix sanity corner; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Abadie, Diamond, and Hainmueller(2010)]{AbadieDiamondHainmueller2010}
Abadie, A., A. Diamond, and J. Hainmueller (2010).
Synthetic control methods for comparative case studies: Estimating the effect
of California's tobacco control program.
\emph{Journal of the American Statistical Association} 105(490), 493--505.

\bibitem[Abadie and L'Hour(2021)]{AbadieLHour2021}
Abadie, A. and J. L'Hour (2021).
A penalized synthetic control estimator for disaggregated data.
\emph{Journal of the American Statistical Association} 116(536), 1817--1834.

\bibitem[Arkhangelsky, Athey, Hirshberg, Imbens, and Wager(2021)]{ArkhangelskyAtheyHirshbergImbensWager2021}
Arkhangelsky, D., S. Athey, D. A. Hirshberg, G. W. Imbens, and S. Wager
(2021). Synthetic difference-in-differences.
\emph{American Economic Review} 111(12), 4088--4118.

\bibitem[Athey, Bayati, Doudchenko, Imbens, and Khosravi(2021)]{AtheyBayatiDoudchenkoImbensKhosravi2021}
Athey, S., M. Bayati, N. Doudchenko, G. Imbens, and K. Khosravi (2021).
Matrix completion methods for causal panel data models.
\emph{Journal of the American Statistical Association} 116(536), 1716--1730.

\bibitem[Athey, Bayati, Imbens, and Qu(2019)]{AtheyBayatiImbensQu2019}
Athey, S., M. Bayati, G. W. Imbens, and Z. Qu (2019).
Ensemble methods for causal effects in panel data settings.
\emph{AEA Papers and Proceedings} 109, 65--70.

\bibitem[Athey, Imbens, Qu, and Viviano(2025)]{AtheyImbensQuViviano2025}
Athey, S., G. W. Imbens, Z. Qu, and D. Viviano (2025).
Triply robust panel estimators.
arXiv:2508.21536.

\bibitem[Bai and Ng(2021)]{BaiNg2021}
Bai, J. and S. Ng (2021).
Matrix completion, counterfactuals, and factor analysis of missing data.
\emph{Journal of the American Statistical Association} 116(536), 1746--1763.

\bibitem[Ben-Michael, Feller, and Rothstein(2021)]{BenMichaelFellerRothstein2021}
Ben-Michael, E., A. Feller, and J. Rothstein (2021).
The augmented synthetic control method.
\emph{Journal of the American Statistical Association} 116(536), 1789--1803.

\bibitem[Ben-Michael, Feller, and Rothstein(2022)]{BenMichaelFellerRothstein2022}
Ben-Michael, E., A. Feller, and J. Rothstein (2022).
Synthetic controls with staggered adoption.
\emph{Journal of the Royal Statistical Society: Series B} 84(2), 351--381.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{BorusyakJaravelSpiess2024}
Borusyak, K., X. Jaravel, and J. Spiess (2024).
Revisiting event-study designs: Robust and efficient estimation.
\emph{Review of Economic Studies} 91(6), 3253--3285.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and P. H. C. Sant'Anna (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics} 225(2), 200--230.

\bibitem[Choi, Kwon, and Liao(2024)]{ChoiKwonLiao2024}
Choi, J., S. Kwon, and Z. Liao (2024).
Inference for low-rank completion without sample splitting with application to
treatment effect estimation.
\emph{Journal of Econometrics} 240(2), 105682.

\bibitem[Chatterjee(2020)]{Chatterjee2020}
Chatterjee, S. (2020).
A deterministic theory of low rank matrix completion.
\emph{IEEE Transactions on Information Theory} 66(12), 8046--8058.

\bibitem[Doudchenko and Imbens(2016)]{DoudchenkoImbens2016}
Doudchenko, N. and G. W. Imbens (2016).
Balancing, regression, difference-in-differences and synthetic control methods:
A synthesis.
NBER Working Paper No. 22791.

\bibitem[Singer and Cucuringu(2010)]{SingerCucuringu2010}
Singer, A. and M. Cucuringu (2010).
Uniqueness of low-rank matrix completion by rigidity theory.
\emph{SIAM Journal on Matrix Analysis and Applications} 31(4), 1621--1641.

\bibitem[Xu(2017)]{Xu2017}
Xu, Y. (2017).
Generalized synthetic control method: Causal inference with interactive fixed
effects models.
\emph{Political Analysis} 25(1), 57--76.
\end{thebibliography}

\end{document}
