% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_ida\_selective\_pivot, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one stage-1 placeholder
%    placeholder. Replace each placeholder with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_ida\_selective\_pivot} / \texttt{v1}%
  \\ \large\textit{Selective regions for deduplicated IDA possible effects and the minimum-absolute score}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form exact-identification/inference anchor. The locked tuple is
\[
(\texttt{qid},\texttt{specialization},\text{graph/MPDAG},\text{treatment},\text{target estimand},\text{identifying assumptions})
\]
with
\begin{quote}
\texttt{qid}=\texttt{eid\_ida\_selective\_pivot}; \texttt{specialization}=\texttt{v1}; graph/MPDAG is a selected CPDAG or MPDAG $\widehat{\mathcal G}$ on variables $V=(X,Y,Z_1,\ldots,Z_{p-2})$ produced by a fixed Gaussian conditional-independence screen and background-knowledge rule; treatment is a scalar node $X$ and outcome is a scalar node $Y$; the target estimand is the selected deduplicated IDA/MPDAG possible-effect set $\Theta_{\widehat s}=\{\theta_m:m\in M_{\widehat s}\}$ and its lower-bound score $L_{\widehat s}=\min_{m\in M_{\widehat s}}|\theta_m|$ after minimal enumeration; identifying assumptions are linear Gaussian SEM, acyclicity, causal sufficiency, faithfulness away from the declared local-boundary faces, consistency of total effects with parent-adjustment regressions for each DAG completion represented by $m$, and a selection event $\widehat s$ that records the selected graph, the minimally enumerated branch list, duplicate-merge tolerances, and the signed branch attaining $\min_m|\widehat\theta_m|$.
\end{quote}

\begin{abstract}
IDA and MPDAG methods report a set of possible total effects when a causal graph is only known up to an equivalence class. Empirical practice often compresses this set to the minimum absolute possible effect, but the same sample usually learns the graph, enumerates the branches, merges duplicates, and estimates the effects. This draft asks for selective confidence regions for the selected deduplicated possible-effect set and for the selected lower-bound score. The main conjecture is that, under a local Gaussian experiment and a fixed finite branch catalogue, the joint event selecting the graph screen, duplicate partition, and signed minimum branch has an explicit polyhedral tangent certificate, which yields a simultaneous truncated-Gaussian pivot. A proof would turn IDA lower-bound summaries from descriptive post-discovery scores into conditionally valid selective inference targets.
\end{abstract}

\section{Introduction}
IDA-style analysis replaces a single causal effect by a multiset of possible total effects when the CPDAG or MPDAG does not orient all relevant arrows. The question here is whether the reported deduplicated set and its lower-bound score can receive selective confidence regions after the data have selected the graph and the effect branches.

\citet{MaathuisKalischBuhlmann2009IDA} introduce IDA possible-effect multisets and lower-bound summaries; \citet{GuoPerkovic2021MinimalEnumeration} remove duplicate possible-effect functionals by minimal enumeration. Neither paper gives the conditioning event required by \citet[Section 2, Theorem 1]{LeeSunSunTaylor2016Polyhedral} for exact selective inference after the reported IDA set has been chosen. The kernel lives in exact identification and post-selection inference: the causal object is a selected possible-effect set, and the mathematical object is a polyhedral tangent certificate for its selection map.

The direct consumer is high-dimensional gene-regulatory IDA screening as studied by \citet{MaathuisKalischBuhlmann2009IDA}. A reader who accepts the result would report a selective lower confidence bound for the IDA lower-bound score rather than a naive Wald interval around the branch that happens to be smallest.

\begin{itemize}[leftmargin=*]
\item Theorem 1: conditional on a fixed selected MPDAG and fixed duplicate partition, the event that a signed branch attains the minimum absolute possible effect is a finite affine system in the branch estimator vector. Gap: \citet{GuoPerkovic2021MinimalEnumeration} deduplicate the functionals but do not derive the min-score selection geometry. Consumer: IDA lower-bound screening in \citet{MaathuisKalischBuhlmann2009IDA}.
\item Conjecture 1: in the local Gaussian IDA experiment, the full selected graph, duplicate partition, and signed-minimum event admits a polyhedral tangent certificate whose truncation limits give simultaneous selective confidence regions for $\Theta_{\widehat s}$ and $L_{\widehat s}$. Gap: \citet{LeeSunSunTaylor2016Polyhedral} require an explicit affine selection event, while IDA/MPDAG selection includes graph discovery and minimal enumeration. Consumer: post-causal-discovery inference in \citet{ChangGuoMalinsky2026PostSelectionCausalDiscovery} and \citet{GraduZrnicWangJordan2025ValidInference}.
\item Conjecture 2: a two-completion local experiment has first-order undercoverage for the naive Wald interval centered at the selected minimum branch, while the selective lower-bound pivot has exact conditional coverage in the tangent experiment. Gap: \citet{LeeSunSunTaylor2016Polyhedral} show exactness after conditioning but do not address IDA lower-bound selection; \citet{MaathuisKalischBuhlmann2009IDA} report the score without selective calibration. Consumer: empirical IDA screening where near-ties between possible effects drive reported importance.
\end{itemize}

\section{Related work}
\citet{MaathuisKalischBuhlmann2009IDA} introduce IDA for estimating possible total causal effects from an estimated CPDAG and motivate lower-bound summaries such as the minimum absolute possible effect.
\citet{NandyMaathuisRichardson2017JointIDA} extend IDA to simultaneous interventions and provide asymptotic theory for joint possible effects, which marks the nearest vector-effect analogue but not the selected lower-bound score.
\citet{PerkovicKalischMaathuis2017MPDAG} adapt IDA and joint-IDA to MPDAGs with background knowledge, making the selected graph object in this draft an MPDAG rather than only a CPDAG.
\citet{GuoPerkovic2021MinimalEnumeration} give minimal enumeration of distinct possible total-effect functionals, which is the comparator for the duplicate partition $M_{\widehat s}$.
\citet{GuoPerkovic2022EfficientLS} provide efficient recursive least-squares estimation of total effects when the MPDAG is known, which supplies the branch-estimation analogue but not post-selection calibration.
\citet{LeeSunSunTaylor2016Polyhedral} prove exact Gaussian selective inference for a linear contrast after an affine selection event $Ay\le b$; this draft asks for the missing affine certificate for the selected IDA possible-effect report.
\citet{TibshiraniTaylorLockhartTibshirani2016Sequential} show that tractable selective inference depends on an explicit selection geometry beyond the lasso, which is the methodological template for deriving IDA-specific conditioning events.
\citet{GraduZrnicWangJordan2025ValidInference} study valid inference after causal discovery and randomized graph selection, but their target is graph-aware inference rather than selective regions for the deduplicated possible-effect set and lower-bound score.
\citet{ChangGuoMalinsky2026PostSelectionCausalDiscovery} emphasize double dipping and selected-functional mismatch after causal discovery, which motivates treating $\Theta_{\widehat s}$ and $L_{\widehat s}$ as selected targets.
The in-catalogue prior-proposal map reports no direct CausalSmith proposal for IDA, MPDAG, CPDAG, possible-effect selective pivots, or this qid; the nearest analogues are \texttt{eid\_proximal\_phase}, \texttt{eid\_dml\_orthogonality\_frontier}, and \texttt{pid\_dose\_response\_iv}, none of which concerns IDA/MPDAG possible-effect selection.

\section{Formal setup}
Let $V=(X,Y,Z_1,\ldots,Z_{p-2})$ follow a linear Gaussian SEM associated with an unknown DAG $\mathcal D_0$ in a Markov equivalence class represented by a CPDAG or MPDAG. The selected state is
\[
\widehat s=(\widehat{\mathcal G},M_{\widehat s},\Pi_{\widehat s},j_{\widehat s},\sigma_{\widehat s}),
\]
where $\widehat{\mathcal G}$ is the selected MPDAG, $M_{\widehat s}=\{1,\ldots,K_{\widehat s}\}$ indexes the minimally enumerated possible-effect functionals, $\Pi_{\widehat s}$ is the duplicate partition used by minimal enumeration, $j_{\widehat s}$ is the branch selected by the minimum absolute estimated effect, and $\sigma_{\widehat s}\in\{-1,1\}$ is the selected sign.

For branch $m$, let $P_m$ be the parent set of $X$ in the corresponding completion or local MPDAG adjustment rule. The branch estimand is
\[
\theta_m=\beta_{X\mid P_m}^{Y},
\]
the coefficient on $X$ in the population least-squares regression of $Y$ on $(X,P_m)$. Let $\widehat\theta=(\widehat\theta_1,\ldots,\widehat\theta_K)^\transpose$ denote the post-enumeration vector of branch estimates on the selected branch list. The selected possible-effect set is $\Theta_{\widehat s}=\{\theta_m:m\in M_{\widehat s}\}$, and the lower-bound score is $L_{\widehat s}=\min_{m\in M_{\widehat s}}|\theta_m|$.

The local Gaussian experiment assumes
\[
\sqrt n(\widehat\theta-\theta)\rightsquigarrow Z,\qquad Z\sim N(0,\Sigma_s),
\]
conditional on the selected finite branch catalogue. The selection certificate is a pair $(A_s,b_s)$ such that the tangent selection event is $\{A_s Z\le b_s\}$.

\begin{quote}
\texttt{qid}=\texttt{eid\_ida\_selective\_pivot}; \texttt{specialization}=\texttt{v1}; graph/MPDAG is a selected CPDAG or MPDAG $\widehat{\mathcal G}$ on variables $V=(X,Y,Z_1,\ldots,Z_{p-2})$ produced by a fixed Gaussian conditional-independence screen and background-knowledge rule; treatment is a scalar node $X$ and outcome is a scalar node $Y$; the target estimand is the selected deduplicated IDA/MPDAG possible-effect set $\Theta_{\widehat s}=\{\theta_m:m\in M_{\widehat s}\}$ and its lower-bound score $L_{\widehat s}=\min_{m\in M_{\widehat s}}|\theta_m|$ after minimal enumeration; identifying assumptions are linear Gaussian SEM, acyclicity, causal sufficiency, faithfulness away from the declared local-boundary faces, consistency of total effects with parent-adjustment regressions for each DAG completion represented by $m$, and a selection event $\widehat s$ that records the selected graph, the minimally enumerated branch list, duplicate-merge tolerances, and the signed branch attaining $\min_m|\widehat\theta_m|$.
\end{quote}

\section{Assumptions}
\begin{assumption}[Linear Gaussian SEM]\label{ass:linear-gaussian}
$V$ is generated by an acyclic linear SEM with jointly independent Gaussian errors and positive definite covariance matrix.
\end{assumption}

\begin{assumption}[IDA parent-adjustment validity]\label{ass:ida-valid}
For every branch $m\in M_{\widehat s}$, the parent set $P_m$ is a valid adjustment set for the total effect of $X$ on $Y$ in the corresponding DAG completion represented by $\widehat{\mathcal G}$.
\end{assumption}

\begin{assumption}[Fixed finite selected catalogue]\label{ass:finite-catalogue}
Conditional on $\widehat s$, the selected branch list $M_{\widehat s}$ is finite, nonempty, and has no zero-variance branch estimator.
\end{assumption}

\begin{assumption}[Local Gaussian branch experiment]\label{ass:local-gaussian}
There is a nonsingular matrix $\Sigma_s$ such that $\sqrt n(\widehat\theta-\theta)\rightsquigarrow N(0,\Sigma_s)$ on the selected branch coordinates.
\end{assumption}

\begin{assumption}[Duplicate partition margin]\label{ass:duplicate-margin}
The duplicate partition $\Pi_{\widehat s}$ is locally stable: within-block differences are identified as the same functional, and between-block population effects differ by more than a tolerance $\delta_s>0$ on the tangent scale unless a declared boundary face is conditioned on.
\end{assumption}

\begin{assumption}[Polyhedral tangent selection]\label{ass:polyhedral-tangent}
For the selected state $\widehat s$, there exists an explicit finite matrix-vector pair $(A_s,b_s)$, computable from the Gaussian screen, background-knowledge rule, duplicate partition, and signed-minimum inequalities, such that the tangent event is $\{A_s Z\le b_s\}$.
\end{assumption}

\begin{assumption}[Unique signed minimum or declared tie face]\label{ass:unique-min}
Either $j_{\widehat s}$ is the unique signed minimizer of $|\widehat\theta_m|$, or the selected state records a tie face and the tied branches are all conditioned on.
\end{assumption}

\section{Main results}
\begin{theorem}[Signed lower-bound branch is affine after the catalogue is fixed]\label{thm:min-poly}
Assume \ref{ass:finite-catalogue} and \ref{ass:unique-min}. Conditional on $(\widehat{\mathcal G},M_{\widehat s},\Pi_{\widehat s})$, the event that branch $j$ with sign $\sigma\in\{-1,1\}$ attains the lower-bound score is
\[
\sigma \widehat\theta_j\ge 0,\qquad
\sigma \widehat\theta_j\le \widehat\theta_k,\qquad
\sigma \widehat\theta_j\le -\widehat\theta_k\quad\text{for all }k\ne j,
\]
with equalities added for declared tie branches. Hence this part of the IDA lower-bound selection event is a finite affine system in $\widehat\theta$.
\end{theorem}
The proof is the identity $|\widehat\theta_j|\le|\widehat\theta_k|$ with the sign of $\widehat\theta_j$ fixed, split into the two half-spaces $\sigma\widehat\theta_j\le \widehat\theta_k$ and $\sigma\widehat\theta_j\le-\widehat\theta_k$.

\begin{conjecture}[Polyhedral tangent pivot for the selected possible-effect set (NOT YET PROVED)]\label{conj:set-pivot}
Under Assumptions \ref{ass:linear-gaussian}--\ref{ass:polyhedral-tangent}, for every contrast vector $\eta$ in the selected branch span, the conditional law of $\eta^\transpose Z$ given $A_sZ\le b_s$ and the nuisance component orthogonal to $\eta$ is Gaussian with truncation limits
\[
L_s(\eta,Z)\le \eta^\transpose Z\le U_s(\eta,Z),
\]
where $L_s$ and $U_s$ are computed from $(A_s,b_s,\Sigma_s,\eta)$. Inverting these pivots over $\eta=e_m$ for $m\in M_{\widehat s}$ and over the signed minimum contrast $\eta=\sigma_{\widehat s}e_{j_{\widehat s}}$ gives simultaneous selective confidence regions for $\Theta_{\widehat s}$ and $L_{\widehat s}$ with conditional coverage $1-\alpha$ in the tangent experiment.
\end{conjecture}

\begin{conjecture}[Naive lower-bound Wald intervals undercover near branch ties (NOT YET PROVED)]\label{conj:wald-fail}
Under Assumptions \ref{ass:local-gaussian} and \ref{ass:unique-min}, consider two branches with independent tangent errors of variance one and local means $\theta_1=\mu/\sqrt n$, $\theta_2=(\mu+c)/\sqrt n$ for fixed $c>0$. The ordinary Wald interval centered at $\widehat\theta_{j_{\widehat s}}$ after selecting $j_{\widehat s}=\arg\min_m|\widehat\theta_m|$ has conditional coverage strictly below its nominal level for an open set of $(\mu,c,\alpha)$, while the truncated pivot from Conjecture \ref{conj:set-pivot} has exact conditional coverage in the same tangent experiment.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Singleton IDA class]\label{cor:singleton}
Under Assumptions \ref{ass:finite-catalogue} and \ref{ass:local-gaussian}, if $K_{\widehat s}=1$ and the graph screen is not conditioned on, Theorem \ref{thm:min-poly} adds only the sign half-space for the lower-bound report. If the sign is also not selected, the confidence region in Conjecture \ref{conj:set-pivot} collapses to the ordinary Gaussian interval for the unique parent-adjustment regression coefficient.
\end{corollary}

\begin{corollary}[Known MPDAG catalogue]\label{cor:known-catalogue}
If $\widehat{\mathcal G}$, $M_{\widehat s}$, and $\Pi_{\widehat s}$ are fixed by design and only the signed minimum is selected, the selection matrix $A_s$ is exactly the matrix of inequalities in Theorem \ref{thm:min-poly}. Thus the proposal reduces to ordinary Lee-style selective inference for a finite family of regression contrasts.
\end{corollary}

\paragraph{Exhibit 9.1: two-branch lower-bound certificate.}
Let $K=2$, $\widehat\theta=(a,b)^\transpose$, and suppose the selected report is $j=1$, $\sigma=1$. The lower-bound event is $0\le a\le b$ and $a\le -b$, hence
\[
A_{\min}\widehat\theta\le 0,\qquad
A_{\min}=
\begin{pmatrix}
-1&0\\
1&-1\\
1&1
\end{pmatrix}.
\]
No denominator appears, the three inequalities are compatible whenever $b\ge a\ge0$ and $b\le -a$, and the nonempty instance $(a,b)=(0.2,-0.4)$ satisfies all inequalities. This computes the constructive certificate from the branch estimates defined in Section 6.

\paragraph{Exhibit 9.2: deduplicated set and score on a small MPDAG catalogue.}
Take three branch estimates $(0.40,0.40,-0.15)$ where branches 1 and 2 belong to one duplicate block and branch 3 belongs to a second block, so $M_{\widehat s}=\{[1,2],[3]\}$ and the deduplicated reported set is $\{0.40,-0.15\}$. The lower-bound score is $L_{\widehat s}=0.15$, attained by branch 3 with sign $-1$, and Theorem \ref{thm:min-poly} gives $-\widehat\theta_3\ge0$, $-\widehat\theta_3\le \widehat\theta_1$, and $-\widehat\theta_3\le-\widehat\theta_1$ after duplicate merging. The inequalities are internally consistent because $0.15\le0.40$ and $0.15\le0.40$.

\section{Proof-sketch route}
For Theorem \ref{thm:min-poly}, the route is: signed minimum headline $<-$ unfold $L_{\widehat s}=\min_m|\widehat\theta_m|$ $<-$ condition on $(j,\sigma)$ $<-$ split each absolute-value comparison into two linear inequalities. For Conjecture \ref{conj:set-pivot}, the route is: selective region headline $<-$ unfold the selected state $\widehat s$ $<-$ substitute Assumptions \ref{ass:local-gaussian} and \ref{ass:polyhedral-tangent} $<-$ step 1, derive the Jacobian of each parent-adjustment coefficient as a linear functional of the covariance tangent; $<-$ step 2, intersect the Gaussian-screen inequalities, duplicate-margin faces, and signed-minimum inequalities into one finite matrix $(A_s,b_s)$; $<-$ step 3, project the polyhedron along $\eta^\transpose Z$ to compute truncation limits; $<-$ step 4, invert the truncated-Gaussian pivot jointly over branch and lower-bound contrasts; $<-$ classical Gaussian selective-inference theorem. For Conjecture \ref{conj:wald-fail}, the route is: undercoverage headline $<-$ unfold the two-branch selection event $<-$ step 1, compute the conditional density of the selected branch in the wedge from Exhibit 9.1; $<-$ step 2, compare the naive untruncated Gaussian quantiles with the wedge-truncated quantiles; $<-$ step 3, show strict inequality on an open local-mean set by continuity from one explicit numerical point; $<-$ classical conditioning identity.

\section{Honest scope flags}
Theorem \ref{thm:min-poly} is elementary once the catalogue is fixed. Conjecture \ref{conj:set-pivot} carries the main burden: the graph-screen and duplicate-partition parts of $(A_s,b_s)$ must be derived rather than assumed. Conjecture \ref{conj:wald-fail} is included to prevent the project from becoming only a formal rephrasing of Lee-style inference; it requires an explicit two-branch calculation. The draft does not claim finite-sample exactness for ordinary PC-style conditional-independence graph learning unless that learning rule is represented by the declared affine tangent certificate.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the deduplicated-set and lower-bound-score angle; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chang, Guo, and Malinsky(2026)]{ChangGuoMalinsky2026PostSelectionCausalDiscovery}
Chang, T.-H., Z. Guo, and D. Malinsky (2026).
\newblock Post-selection inference for causal discovery.
\newblock \emph{Biometrika}.

\bibitem[Gradu, Zrnic, Wang, and Jordan(2025)]{GraduZrnicWangJordan2025ValidInference}
Gradu, P., T. Zrnic, Y. Wang, and M. I. Jordan (2025).
\newblock Valid inference after causal discovery.
\newblock \emph{Journal of the American Statistical Association}.

\bibitem[Guo and Perkovic(2021)]{GuoPerkovic2021MinimalEnumeration}
Guo, R. and E. Perkovic (2021).
\newblock Minimal enumeration of all possible total effects in a Markov equivalence class.
\newblock \emph{Proceedings of AISTATS}.

\bibitem[Guo and Perkovic(2022)]{GuoPerkovic2022EfficientLS}
Guo, R. and E. Perkovic (2022).
\newblock Efficient least squares for estimating total effects under linearity and causal sufficiency.
\newblock \emph{Journal of Machine Learning Research}.

\bibitem[Lee, Sun, Sun, and Taylor(2016)]{LeeSunSunTaylor2016Polyhedral}
Lee, J. D., D. L. Sun, Y. Sun, and J. E. Taylor (2016).
\newblock Exact post-selection inference, with application to the lasso.
\newblock \emph{Annals of Statistics} 44(3), 907--927.

\bibitem[Maathuis, Kalisch, and Buhlmann(2009)]{MaathuisKalischBuhlmann2009IDA}
Maathuis, M. H., M. Kalisch, and P. Buhlmann (2009).
\newblock Estimating high-dimensional intervention effects from observational data.
\newblock \emph{Annals of Statistics} 37(6A), 3133--3164.

\bibitem[Nandy, Maathuis, and Richardson(2017)]{NandyMaathuisRichardson2017JointIDA}
Nandy, P., M. H. Maathuis, and T. S. Richardson (2017).
\newblock Estimating the effect of joint interventions from observational data in sparse high-dimensional settings.
\newblock \emph{Annals of Statistics} 45(2), 647--674.

\bibitem[Perkovic, Kalisch, and Maathuis(2017)]{PerkovicKalischMaathuis2017MPDAG}
Perkovic, E., M. Kalisch, and M. H. Maathuis (2017).
\newblock Interpreting and using CPDAGs with background knowledge.
\newblock \emph{Proceedings of UAI}.

\bibitem[Tibshirani, Taylor, Lockhart, and Tibshirani(2016)]{TibshiraniTaylorLockhartTibshirani2016Sequential}
Tibshirani, R. J., J. Taylor, R. Lockhart, and R. Tibshirani (2016).
\newblock Exact post-selection inference for sequential regression procedures.
\newblock \emph{Journal of the American Statistical Association} 111(514), 600--620.
\end{thebibliography}

\end{document}
