% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_proximal\_completeness, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_proximal\_completeness} / \texttt{v1}%
  \\ \large\textit{A common-kernel bridge-compatibility threshold for long-term proximal ATE identification}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form ExactID/PartialID proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization}, P, \theta_{\mathrm{LT}},
\text{identifying restrictions},\text{bounding functional}).
\]
Here \(\texttt{qid}=\texttt{eid\_proximal\_completeness}\) and
\(\texttt{specialization}=\texttt{v1}\).  The observable distribution \(P\)
is the finite-support law of two samples \(G\in\{E,B\}\): a short-run
experimental sample \(E\), in which \(A\in\{0,1\}\), \(X\), and proxy panels
\((W,Z)\) are observed but the terminal outcome \(Y\) is not; and a long-run
observational sample \(B\), in which \((Y,A,X,W,Z)\) are observed but
treatment assignment may be persistently confounded.  The target estimand is
\[
\theta_{\mathrm{LT}}=\E\{Y(1)-Y(0)\}
\]
for the experimental target population.  The identifying restrictions are
finite-support consistency, experimental random assignment in sample \(E\),
proxy transport stability between \(E\) and \(B\), negative-control exclusion
restrictions, existence of at least one bounded observational outcome bridge
\(h(W,A,X)\), and the finite bridge-realization condition in
Assumption~\ref{ass:realization}.  The observational bridge operator is the
matrix \(T_B(P):\R^d\to\R^r\) with
\[
(T_Bh)(z,a,x)=\E_B\{h(W,a,x)\mid Z=z,A=a,X=x\},
\qquad
m_B(z,a,x)=\E_B(Y\mid Z=z,A=a,X=x),
\]
and the bridge fiber is \(\calH_B(P)=\{h\in[0,1]^d:T_B(P)h=m_B(P)\}\).
The experimental long-term loading is the observable vector
\(\lambda_E(P)\in\R^d\) satisfying
\[
\lambda_E(P)^\transpose h
=\E_E\{h(W,1,X)\mid A=1\}-\E_E\{h(W,0,X)\mid A=0\}.
\]
The named focal object is the common-kernel bridge-compatibility index
\[
\Delta_{\mathrm{CK}}(P)=
\left\|\Pi_{\ker T_B(P)}\lambda_E(P)\right\|_2,
\]
where the projection uses the Euclidean inner product on the finite bridge
coordinates.  The bounding functional is the bridge-fiber support width
\[
W_{\mathrm{LT}}(P)
=\sup_{h\in\calH_B(P)}\lambda_E(P)^\transpose h
-\inf_{h\in\calH_B(P)}\lambda_E(P)^\transpose h.
\]
The novelty question is whether \(\Delta_{\mathrm{CK}}(P)=0\) is the sharp
observable iff frontier for long-term proximal ATE point identification, and
whether \(\Delta_{\mathrm{CK}}(P)>0\) forces a non-singleton sharp bridge
envelope rather than merely nonunique nuisance bridges.

\begin{abstract}
Long-term causal inference increasingly uses short-run experimental proxies
and long-run observational outcomes to identify terminal treatment effects
under persistent unobserved confounding.  Existing proximal and surrogate-index
results give sufficient bridge, surrogacy, or sequential proxy conditions, but
do not state a sharp observable frontier for when the early experimental proxy
panel spans exactly the confounding direction needed for the terminal outcome.
This proposal introduces the common-kernel bridge-compatibility index
\(\Delta_{\mathrm{CK}}(P)\), the norm of the experimental ATE loading projected
onto the observational bridge null space.  The flagship conjecture is that,
under finite bridge realization, \(\Delta_{\mathrm{CK}}(P)=0\) is necessary and
sufficient for point identification of the long-term ATE, while positive
\(\Delta_{\mathrm{CK}}(P)\) produces a sharp non-singleton bridge envelope.
Resolving the conjecture would turn completeness from an untestable global
condition into a target-specific compatibility report for proximal surrogate
analyses.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Short-run experiments are often too short to observe the outcome that policy
makers care about, while long-run observational data often contain persistent
unmeasured confounding.  Surrogate-index methods and newer persistent-confounding
methods use short-term outcomes or proxies to bridge the two data sources.
Their practical weak point is that a global completeness or surrogacy condition
can fail in directions irrelevant to the terminal ATE, and can also hold for
bridge uniqueness without revealing whether the experimental target loading is
compatible with the observational bridge equation.

\paragraph{The main finding (proposed).}
The proposed main result is Conjecture~\ref{conj:ck-frontier}.  It states that
the common-kernel bridge-compatibility index
\(\Delta_{\mathrm{CK}}(P)\) is the exact threshold for long-term proximal ATE
point identification in the finite two-sample setting: zero iff the experimental
loading annihilates every observationally invisible bridge perturbation, and
positive iff the same observed law admits at least two latent negative-control
models with different long-term ATEs.  Theorem~\ref{thm:fiber-algebra} is a
support theorem giving the bridge-fiber algebra, and
Conjecture~\ref{conj:positive-width} promotes the positive-threshold side to a
sharp-width statement with a concrete minimal noisy-panel witness.

\paragraph{What is new.}
The closest proximal papers separate bridge existence, bridge uniqueness, and
target-functional identification: \citet{MiaoGengTchetgen2018} use proxy
rank/completeness for point identification, \citet{YingMiaoShiTchetgen2023}
extend bridge ideas longitudinally, and \citet{ZhangLiMiaoTchetgen2023} show
that a target mean can remain identified without unique bridge functions.  The
closest long-term papers, \citet{AtheyChettyImbensKang2019} and
\citet{ImbensKallusMaoWang2025}, use surrogate or sequential proxy structure
to identify terminal effects.  The epsilon gap is that none of these papers
names the cross-sample row-space object \(\Delta_{\mathrm{CK}}(P)\), nor proves
that the experimental proxy loading lies in the observational bridge row space
iff the long-term ATE is point identified.  This proposal is therefore not a
new bridge estimator and not another sufficient completeness assumption; it is
a target-specific necessary-and-sufficient compatibility frontier.

\paragraph{How it positions in the literature.}
The kernel lives between exact identification and partial identification.  On
the exact-ID side, \(\Delta_{\mathrm{CK}}(P)=0\) gives a bridge formula for the
long-term ATE even when \(T_B(P)\) has a nontrivial null space.  On the
partial-ID side, \(\Delta_{\mathrm{CK}}(P)>0\) makes the identified set a
support interval over the observational bridge fiber.  The proposal uses
proximal causal inference as the identification language and long-term
surrogate-index work as the applied data-combination motivation.

\paragraph{Implications for the community.}
The concrete downstream consumer is the persistent-confounding long-term ATE
design of \citet{ImbensKallusMaoWang2025}: before treating the sequential proxy
conditions as sufficient for a terminal effect, analysts could compute the
common-kernel compatibility index for the finite proxy basis actually used.
The same diagnostic also tells users of the surrogate-index design in
\citet{AtheyChettyImbensKang2019} when additional short-term proxy waves span
the terminal bridge loading rather than merely improving prediction.

\paragraph{How research benefits from the conclusion.}
Researchers should report \(\Delta_{\mathrm{CK}}(P)\) and
\(W_{\mathrm{LT}}(P)\) as the target-specific proxy-richness diagnostic before
claiming point identification of a long-term proximal ATE.

\section{Related work}
\citet{AtheyChettyImbensKang2019} develop the surrogate-index approach for
estimating long-term treatment effects from multiple short-term proxies under
surrogacy; this proposal replaces global surrogacy with a proximal row-space
compatibility condition for the terminal ATE loading.  \citet{ImbensKallusMaoWang2025}
study long-term causal inference under persistent confounding by combining
short-run experiments and long-run observational data; their sequential proxy
structure motivates the two-sample setup, but they do not state a sharp
bridge-null threshold.  \citet{MiaoGengTchetgen2018} establish negative-control
proximal point identification through outcome bridge functions and
rank/completeness conditions; the proposed index asks which rank failures are
irrelevant to the target.  \citet{YingMiaoShiTchetgen2023} extend proximal
bridge identification to complex longitudinal studies, making clear that
time-ordered proxy panels are natural bridge variables but leaving the
finite target-specific row-space boundary implicit.  \citet{CuiPuShiMiaoTchetgen2024}
develop semiparametric proximal OR/IPW/DR inference under bridge conditions;
the present proposal is a population identification question that precedes
their regular asymptotics.  \citet{ZhangLiMiaoTchetgen2023} show that
counterfactual means can be identified without unique bridge functions; the
present conjecture specializes that insight to a two-sample long-term ATE and
names the observable common-kernel index.  \citet{GhassamiShpitserTchetgen2023}
derive proxy-based partial-identification bounds when completeness fails; the
positive-\(\Delta_{\mathrm{CK}}\) side here is a sharper bridge-fiber support
width for the long-term ATE.  \citet{CanaySantosShaikh2013} show that
completeness-type identifying hypotheses can be empirically untestable in
nonparametric endogenous models, which motivates reporting a target-specific
sensitivity frontier rather than pretesting global completeness.

In-catalogue CausalSmith prior art does not already contain this kernel.
\texttt{doc/API.md} records the promoted ExactID and PartialID catalogues as
empty seed areas, while the populated Q1 entries are panel/FWL theorems rather
than proximal identification results.  The banked \texttt{eid\_proximal\_phase}
proposal studied finite OR/DR-versus-minimax bridge-selector equivalence near
nonunique bridges; it did not address two-sample long-term ATE compatibility or
an experimental loading versus observational bridge row-space threshold.  The
failed \texttt{pid\_long\_term\_surrogate} proposal collapsed to generic
surrogate-panel partial identification; the reviewer explicitly named a
common-kernel bridge-compatibility statement as the missing non-generic repair
direction.

\section{Formal setup}
All variables have finite support.  Let \(G=E\) denote the short-run
experimental sample and \(G=B\) the long-run observational sample.  In the
experimental sample, treatment \(A\) is randomized conditional on \(X\), the
proxy panel \((W,Z)\) is observed after treatment, and the long-term outcome
\(Y\) is missing.  In the observational sample, \((Y,A,X,W,Z)\) are observed
and \(A\) may be confounded by an unobserved \(U\).  The negative-control
interpretation is that \(Z\) carries treatment-confounding information and
\(W\) carries outcome-confounding information, with the exclusion restrictions
specified in Assumption~\ref{ass:proximal-structure}.

Index the finite bridge coordinates by \(j=(w,a,x)\), so \(h\in\R^d\) is the
array \(h(w,a,x)\).  Index the observational bridge equations by
\(k=(z,a,x)\), so \(T_B(P)\in\R^{r\times d}\) and \(m_B(P)\in\R^r\).  The
observable bridge fiber is
\[
\calH_B(P)=\{h\in[0,1]^d:T_B(P)h=m_B(P)\}.
\]
The experimental loading \(\lambda_E(P)\in\R^d\) is defined by
\[
\lambda_{E,(w,a,x)}(P)=
\one\{a=1\}\Pr_E(W=w,X=x\mid A=1)
-\one\{a=0\}\Pr_E(W=w,X=x\mid A=0).
\]
For any bridge \(h\), the candidate long-term ATE value is
\(\theta(h)=\lambda_E(P)^\transpose h\), and the bridge-fiber identified set
is
\[
\Theta_I(P)=\{\theta(h):h\in\calH_B(P)\}
=[\underline\theta(P),\overline\theta(P)].
\]
The common-kernel bridge-compatibility index and support width are
\[
\Delta_{\mathrm{CK}}(P)=
\left\|\Pi_{\ker T_B(P)}\lambda_E(P)\right\|_2,\qquad
W_{\mathrm{LT}}(P)=\overline\theta(P)-\underline\theta(P).
\]
Let \(r_{\mathrm{int}}(P)>0\) denote the bridge-interior radius in
Assumption~\ref{ass:interior-radius}; it bounds how far a bridge can move in
any unit null direction while remaining in the bounded bridge cube.

\begin{quote}
Locked parameters: \((\texttt{qid},\texttt{specialization}, P,
\theta_{\mathrm{LT}},\text{identifying restrictions},\text{bounding
functional})\) with \(\texttt{qid}=\texttt{eid\_proximal\_completeness}\),
\(\texttt{specialization}=\texttt{v1}\), \(P\) the finite two-sample law of
\((G,Y,A,X,W,Z)\), \(\theta_{\mathrm{LT}}=\E\{Y(1)-Y(0)\}\), identifying
restrictions given by Assumptions~\ref{ass:sampling}--\ref{ass:realization},
and bounding functional \(W_{\mathrm{LT}}(P)\) over \(\calH_B(P)\).
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite two-sample support and overlap]\label{ass:sampling}
The observed law \(P\) has finite support.  In sample \(E\), treatment
\(A\in\{0,1\}\) is randomized conditional on \(X\), and
\(0<\Pr_E(A=a\mid X=x)<1\) for every \(a,x\) used by the target population.
The proxy cells entering \(T_B(P)\) and \(\lambda_E(P)\) have positive
probability whenever their corresponding rows or columns are retained.
\end{assumption}

\begin{assumption}[Proximal negative-control structure]\label{ass:proximal-structure}
There exists a latent variable \(U\) such that consistency holds, the
experimental target population and the observational bridge population share
the same terminal outcome bridge after conditioning on \((A,X,U)\), \(Z\) has
no direct effect on \(Y\) given \((A,X,U)\), and \(W\) is excluded from the
treatment assignment mechanism given \((X,U,Z)\).  These restrictions are
only used to interpret a realized bridge-fiber value as a causal long-term ATE.
\end{assumption}

\begin{assumption}[Bounded observational outcome bridge]\label{ass:bridge-existence}
The bridge fiber \(\calH_B(P)=\{h\in[0,1]^d:T_B(P)h=m_B(P)\}\) is nonempty.
Every \(h\in\calH_B(P)\) is an admissible bounded outcome bridge for the
observational terminal outcome equation.
\end{assumption}

\begin{assumption}[Proxy transport stability]\label{ass:transport}
For each \(a\in\{0,1\}\), the experimental proxy distribution
\(\Pr_E(W=w,X=x\mid A=a)\) equals the target-population distribution of the
outcome-inducing proxy \(W(a)\) and covariates \(X\) under intervention \(A=a\).
Consequently \(\lambda_E(P)^\transpose h\) is the long-term ATE implied by
bridge \(h\).
\end{assumption}

\begin{assumption}[Finite latent law class]\label{ass:realization}
The admissible causal model class consists of finite latent
negative-control laws for \((Y(0),Y(1),A,X,W(0),W(1),Z,U,G)\) satisfying
Assumptions~\ref{ass:sampling}, \ref{ass:proximal-structure}, and
\ref{ass:transport} and inducing the observed law \(P\).  No sharpness or
endpoint-attainability property of \(\calH_B(P)\) is assumed here; proving
which bridge-fiber values are realized by this finite law class is the open
content of Conjecture~\ref{conj:ck-frontier}.
\end{assumption}

\begin{assumption}[Interior bridge radius]\label{ass:interior-radius}
There exists \(h^\circ\in\calH_B(P)\) and a known structural radius
\(r_{\mathrm{int}}(P)>0\) such that
\(h^\circ+t v\in[0,1]^d\) for every \(v\in\ker T_B(P)\) with
\(\|v\|_2=1\) and every \(|t|\le r_{\mathrm{int}}(P)\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: bridge-fiber algebra]\label{thm:fiber-algebra}
Under Assumptions~\ref{ass:sampling}, \ref{ass:bridge-existence}, and
\ref{ass:transport}, the bridge-fiber values satisfy
\[
\Theta_I(P)=
\{\lambda_E(P)^\transpose h:h\in\calH_B(P)\}.
\]
Moreover \(\Theta_I(P)\) is a singleton iff
\(\lambda_E(P)\in\operatorname{row}(T_B(P))\), equivalently iff
\(\Delta_{\mathrm{CK}}(P)=0\).  If \(\Delta_{\mathrm{CK}}(P)=0\) and
\(\lambda_E(P)=T_B(P)^\transpose q\), then every bridge in \(\calH_B(P)\)
gives the same formula \(\theta_{\mathrm{LT}}=q^\transpose m_B(P)\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) As linear algebra, this is routine and deliberately labeled a theorem,
but the precise cross-sample loading \(\lambda_E(P)\) is not named in
\citet{AtheyChettyImbensKang2019}, \citet{ImbensKallusMaoWang2025}, or
\citet{ZhangLiMiaoTchetgen2023}.  The gap is that those papers do not state
the row-space equality between an experimental long-term loading and an
observational proximal bridge operator.  (b) This theorem gives users of
\citet{ImbensKallusMaoWang2025} a computable finite diagnostic for whether a
chosen proxy panel can identify the terminal ATE before any asymptotic
estimator is discussed.

\begin{conjecture}[Conjecture 1: common-kernel frontier (NOT YET PROVED)]\label{conj:ck-frontier}
Under Assumptions~\ref{ass:sampling}--\ref{ass:realization}, the terminal
long-term ATE is point identified from \(P\) if and only if
\[
\Delta_{\mathrm{CK}}(P)=0.
\]
If \(\Delta_{\mathrm{CK}}(P)>0\), then there exist two finite latent
negative-control causal laws inducing the same observable \(P\) and satisfying
the same proxy transport restrictions but yielding distinct terminal ATEs.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest comparator chain is
\citet{MiaoGengTchetgen2018} for sufficient proxy rank/completeness,
\citet{ZhangLiMiaoTchetgen2023} for target identification without unique
bridges, and \citet{ImbensKallusMaoWang2025} for long-term ATE identification
under persistent confounding.  None proves the iff statement that the
experimental loading must annihilate the observational bridge null space; the
epsilon gap is the independent focal object
\(\Delta_{\mathrm{CK}}(P)\), which can be positive even when bridges exist and
can be zero even when bridges are nonunique.  (b) Resolving it would directly
close the reviewer-identified gap in the banked
\texttt{pid\_long\_term\_surrogate} run: a common-kernel bridge compatibility
theorem coupling the experimental measurement kernel to the long-run
observational bridge law.

\begin{conjecture}[Conjecture 2: positive-threshold sharp width (NOT YET PROVED)]\label{conj:positive-width}
Under Assumptions~\ref{ass:sampling}--\ref{ass:interior-radius}, if
\(\Delta_{\mathrm{CK}}(P)>0\), then the bridge-fiber support width obeys
\[
W_{\mathrm{LT}}(P)\ge 2\,r_{\mathrm{int}}(P)\,\Delta_{\mathrm{CK}}(P).
\]
On an open finite-support class containing the two-wave binary noisy-panel
witness in Corollary~\ref{cor:witness}, this lower bound is strict whenever
the earlier proxy wave loads on a terminal-confounding direction not spanned by
the later wave alone.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{GhassamiShpitserTchetgen2023} study proxy partial-identification
bounds after completeness fails, but do not give this target-specific
long-term bridge-width modulus.  The prior
\texttt{pid\_long\_term\_surrogate} reviewer rejected generic LP containment
and requested a minimal \(K=2,J=1\) noisy-panel theorem; this conjecture names
the width modulus and the non-corner witness class.  (b) Resolving it would
give analysts using the surrogate-index design of
\citet{AtheyChettyImbensKang2019} a reason to collect an additional early
proxy wave: it can shrink \(W_{\mathrm{LT}}(P)\) exactly when it reduces
\(\Delta_{\mathrm{CK}}(P)\), not merely when it improves prediction of \(Y\).

\section{Sanity-check corollaries}
\begin{corollary}[Full-rank proximal completeness corner]\label{cor:full-rank}
If Assumptions~\ref{ass:sampling}--\ref{ass:transport} hold and
\(\ker T_B(P)=\{0\}\), then \(\Delta_{\mathrm{CK}}(P)=0\),
\(W_{\mathrm{LT}}(P)=0\), and Theorem~\ref{thm:fiber-algebra} reduces to the
usual finite proximal bridge formula.  This is the
\citet{MiaoGengTchetgen2018} completeness corner because no invisible bridge
direction remains for \(\lambda_E(P)\) to load on.
\end{corollary}

\begin{corollary}[Surrogacy corner]\label{cor:surrogacy}
If the short-term proxy panel is a sufficient surrogate in the sense that the
terminal conditional mean is an observed function \(g(W,A,X)\) common to both
samples, then \(g\in\calH_B(P)\) and \(\lambda_E(P)^\transpose g\) is the
surrogate-index long-term ATE.  Under Assumption~\ref{ass:transport}, if every
other bridge differs from \(g\) only by directions orthogonal to
\(\lambda_E(P)\), then \(\Delta_{\mathrm{CK}}(P)=0\) and the proposal reduces
to the \citet{AtheyChettyImbensKang2019} point-ID logic.
\end{corollary}

\begin{corollary}[Concrete two-wave noisy-panel witness]\label{cor:witness}
Consider \(X\) absent, \(A\in\{0,1\}\), binary \(W_1,W_2,Z\), and a bridge
dictionary \(h(W_1,W_2,A)\) with one observational null vector
\(v(W_1,W_2,A)=(-1)^{W_1}\one\{A=1\}\) generated by symmetric measurement
noise in \(W_1\) conditional on \((Z,A)\).  If the experimental loading has
\(\lambda_E^\transpose v\ne0\), then
\(\Delta_{\mathrm{CK}}(P)>0\) and Conjecture~\ref{conj:positive-width}
predicts a nonzero long-term ATE width; if the earlier wave \(W_1\) is added
to the observational bridge rows so that \(v\notin\ker T_B(P)\), then the
same target loading can have \(\Delta_{\mathrm{CK}}(P)=0\).  This is the
minimal non-corner \(K=2,J=1\) proxy-panel reduction requested by the prior
reviewer.
\end{corollary}

\section{Proof-sketch route}
Theorem~\ref{thm:fiber-algebra} reduces to the fundamental theorem of linear
algebra: an affine fiber \(h_0+\ker T_B\) has constant value under
\(\lambda_E^\transpose h\) exactly when \(\lambda_E\) is orthogonal to
\(\ker T_B\), equivalently lies in \(\operatorname{row}(T_B)\).  The hard part
of Conjecture~\ref{conj:ck-frontier} is the finite causal-realization step:
given two bounded bridges in the same observable fiber, construct finite
latent response-type laws that preserve the observed \((Y,A,X,W,Z,G)\) law and
negative-control exclusions while assigning the two bridge-implied terminal
means.  Conjecture~\ref{conj:positive-width} then follows by moving from an
interior bridge \(h^\circ\) in the normalized null direction
\(\Pi_{\ker T_B}\lambda_E/\Delta_{\mathrm{CK}}\), plus an explicit
small-support enumeration for the binary two-wave witness in
Corollary~\ref{cor:witness}.  Boundary cases needing algebra are rows of
\(T_B\) with zero proxy support, non-interior bridge fibers where the lower
bound becomes one-sided, and the comparison between the \(W_2\)-only and
\((W_1,W_2)\)-row operators in the witness.

\section{Honest scope flags}
Theorem~\ref{thm:fiber-algebra} is routine finite-dimensional algebra once the
bridge-fiber convention is accepted.  Conjecture~\ref{conj:ck-frontier} is the
novel kernel and is not yet proved because Assumption~\ref{ass:realization}
may fail for some negative-control exclusion graphs; a counterexample would
turn the proposal into a characterization of which bridge fibers are causally
realizable.  Conjecture~\ref{conj:positive-width} is also open: the lower
bound is plausible under the interior-radius assumption, but sharpness at the
boundary of the bounded bridge cube may require replacing the Euclidean
projection norm by a polyhedral gauge.  The pivot intentionally withdraws the
archived scalar singular-value threshold from the previous angle and does not
claim any OR/DR-versus-minimax selector-equivalence result.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the common-kernel bridge-compatibility
angle after exhausting the target-active null-score angle; prior verdict:
none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Athey et~al.(2019)]{AtheyChettyImbensKang2019}
Athey, S., Chetty, R., Imbens, G.~W., and Kang, H. (2019).
\newblock The surrogate index: Combining short-term proxies to estimate
long-term treatment effects more rapidly and precisely.
\newblock \emph{NBER Working Paper} 26463. doi:10.3386/w26463.

\bibitem[Canay et~al.(2013)]{CanaySantosShaikh2013}
Canay, I.~A., Santos, A., and Shaikh, A.~M. (2013).
\newblock On the testability of identification in some nonparametric models
with endogeneity.
\newblock \emph{Econometrica} 81(6), 2535--2559. doi:10.3982/ECTA10851.

\bibitem[Cui et~al.(2024)]{CuiPuShiMiaoTchetgen2024}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. (2024).
\newblock Semiparametric proximal causal inference.
\newblock \emph{Journal of the American Statistical Association} 119(546),
1348--1359. doi:10.1080/01621459.2023.2191817.

\bibitem[Ghassami et~al.(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. (2023).
\newblock Partial identification of causal effects using proxy variables.
\newblock \emph{arXiv preprint} arXiv:2304.04374.

\bibitem[Imbens et~al.(2025)]{ImbensKallusMaoWang2025}
Imbens, G., Kallus, N., Mao, X., and Wang, Y. (2025).
\newblock Long-term causal inference under persistent confounding via data
combination.
\newblock \emph{Journal of the Royal Statistical Society: Series B} 87(2),
362--388. doi:10.1093/jrsssb/qkae095.

\bibitem[Miao et~al.(2018)]{MiaoGengTchetgen2018}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E. (2018).
\newblock Identifying causal effects with proxy variables of an unmeasured
confounder.
\newblock \emph{Biometrika} 105(4), 987--993. doi:10.1093/biomet/asy038.

\bibitem[Ying et~al.(2023)]{YingMiaoShiTchetgen2023}
Ying, A., Miao, W., Shi, X., and Tchetgen Tchetgen, E.~J. (2023).
\newblock Proximal causal inference for complex longitudinal studies.
\newblock \emph{Journal of the Royal Statistical Society: Series B} 85(3),
684--704. doi:10.1093/jrsssb/qkad020.

\bibitem[Zhang et~al.(2024)]{ZhangLiMiaoTchetgen2023}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. (2024).
\newblock Proximal causal inference without uniqueness assumptions.
\newblock \emph{Statistics and Probability Letters} 204, 109836.
doi:10.1016/j.spl.2023.109836.
\end{thebibliography}

\end{document}
