% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_proximal\_completeness, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_proximal\_completeness} / \texttt{v1}%
  \\ \large\textit{A target-active null-score threshold for long-term proximal ATE identification}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Exact-identification tuple:
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions})
\]
is fixed as follows.  \(\texttt{qid}=\texttt{eid\_proximal\_completeness}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph/SWIG is a two-sample
long-term proximal negative-control design with baseline covariates \(X\),
binary treatment \(A\in\{0,1\}\), short-term proxy history \(S\), treatment
negative-control proxy \(Z\), outcome negative-control proxy \(W\), latent
confounder \(U\), and terminal outcome \(Y^L\); sample \(E\) is randomized or
short-term experimental and supplies the target loading on \((W,S,X,A)\), while
sample \(B\) is the bridge-learning sample with \(Y^L\).  The treatment is the
binary intervention \(A=a\).  The target estimand is the long-term average
treatment effect
\[
\theta(P)=\E_E\{Y^L(1)-Y^L(0)\}.
\]
Identifying assumptions are consistency and positivity, negative-control
exclusions for \(Z,W\), existence of bounded outcome bridges
\(h_a(W,S,X)\in[0,1]\) satisfying the observed bridge equation in sample \(B\),
and cross-sample transport of the bridge equation to the experimental loading.
Completeness of the full bridge operator is not locked in, and
\(\alpha_{\mathrm{LT}}(P)=0\) is the tested frontier condition rather than a
locked identifying assumption; the question is the sharp boundary at which the
target remains identified as completeness approaches failure.

\begin{abstract}
Proximal long-term treatment-effect analyses use negative-control proxies to
solve outcome-bridge equations, but standard point-identification statements
typically impose completeness or rank conditions that make the bridge unique.
Recent proximal work shows that the causal functional may remain identified even
when bridge functions are nonunique, while proxy partial-identification work
studies what happens after completeness is abandoned.  This proposal asks for
the sharp critical boundary between those regimes in a two-sample long-term ATE
setting.  The proposed focal object is the target-active null score
\(\alpha_{\mathrm{LT}}(P)\), the component of the experimental long-term ATE
loading that lies in the null space of the observed bridge operator.  The
headline conjecture is that \(\alpha_{\mathrm{LT}}(P)\) and a finite bridge-LP
support function yield both the exact point-identification frontier and a
local-to-incomplete phase diagram for regularized bridge estimators when the
smallest target-relevant singular values shrink.  If resolved, the result would
tell analysts when a weak or nonunique
proximal bridge still identifies the long-term ATE and when it must be reported
as a sharp proxy-sensitive interval.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Proximal causal inference is attractive precisely in settings where ordinary
selection-on-observables is not credible but proxy variables for the hidden
confounder are available.  Long-term ATE problems sharpen the issue: short-term
experimental data may contain rich proxy histories, while terminal outcomes are
observed only in a bridge-learning sample.  The practical question is not
whether an analyst can invoke a global completeness condition, but whether the
specific long-term ATE loading is orthogonal to the directions of the bridge
equation that the data cannot see.

\paragraph{The main finding (proposed).}
The main finding proposed here is a sharp target-specific completeness
frontier.  Proposition~\ref{prop:null-annihilator} records the routine finite
linear-algebra backbone: if every observed bridge-null direction is annihilated
by the long-term ATE loading, then all bounded bridge solutions deliver the
same ATE.  Conjecture~\ref{conj:critical-frontier} is the flagship claim: on a
finite positive-cell class with nondegenerate bridge fibers, the target-active
null score \(\alpha_{\mathrm{LT}}(P)\) is the sharp critical completeness
threshold, with \(\alpha_{\mathrm{LT}}(P)=0\) giving point identification and
\(\alpha_{\mathrm{LT}}(P)>0\) giving a sharp non-singleton bridge envelope whose
width is the value of a finite support-function LP over the bounded bridge
fiber, not a one-dimensional radius unless the fiber is exposed and
one-dimensional.  Conjecture~\ref{conj:local-weak} adds the
local-to-incomplete phase diagram for regularized outcome-bridge estimators.

\paragraph{What is new.}
What is new is the long-term target-loading threshold and its support-function
width object, not the generic fact that linear functionals are constant on a
null space.  \citet[Sections 2--4]{MiaoGengTchetgen2018} and
\citet[Theorem 3.1 and equation (9)]{CuiPuShiMiaoTchetgen2024} give proximal
point-identification and semiparametric proximal inference under bridge
conditions.  \citet[Section 2 and Section 3]{ZhangLiMiaoTchetgen2023} separate
bridge uniqueness from target-functional identification, and
\citet[Abstract and Sections 2--3]{Santos2011JoE} gives the NPIV predecessor
where a continuous linear functional is recoverable even when the nuisance
structural function is not identified.  \citet[Abstract and Section
4]{KallusMaoUehara2021} gives the minimax negative-control bridge-learning
comparator whose finite selector behavior is not characterized at the boundary.
\citet[Abstract and Theorem 2.1]{BennettKallusMaoNeweySyrgkanisUehara2023}
studies strong functionals of weakly identified functions.  This proposal
targets the missing two-sample long-term boundary: an experimentally weighted
terminal ATE loading can be target-inactive even when the bridge operator is
incomplete, or target-active even when a bridge equation still has many bounded
solutions.

\paragraph{How it positions in the literature.}
This is an ExactID proposal with a proximal/negative-control bridge substrate
and a PartialID boundary corollary.  It is informed by the long-term surrogate
and persistent-confounding literature of \citet{AtheyChettyImbensKang2019} and
\citet{ImbensKallusMaoWang2025}, but it does not use a panel or surrogate-index
estimand.  The proposed conjecture consumes the observed two-sample law and asks
whether the long-term ATE functional is invariant over the outcome-bridge fiber.

\paragraph{Implications for the community.}
The concrete downstream consumer is the long-term data-combination analysis of
\citet{ImbensKallusMaoWang2025}: a resolved threshold would distinguish cases
where their sufficient bridge/proxy structure can be relaxed from cases where
the terminal ATE is necessarily interval-valued.

\paragraph{How research benefits from the conclusion.}
Before reporting a proximal long-term point estimate, analysts should report
the target-active null score and the support-function bridge-envelope width,
then switch to a bridge-envelope interval whenever the score is positive.

\section{Related work}
\citet[Sections 2--4, especially the categorical rank result in Section
2 and the nonparametric completeness discussion in Section 3]{MiaoGengTchetgen2018}
is the point-identification anchor: it uses proxy rank/completeness conditions
for causal-effect identification with negative controls, and when proxy
information is insufficient it turns to testing rather than a sharp
target-specific boundary.  \citet[Theorem 3.1 and influence-function equation
(9)]{CuiPuShiMiaoTchetgen2024} develops semiparametric proximal estimation and
double robustness under bridge equations; the present proposal asks what its
outcome-bridge workflow identifies when the bridge equation is weak or
nonunique.  \citet[Section 2, Theorem 2.1, and Section 3's solution-set
construction]{ZhangLiMiaoTchetgen2023} is the closest bridge-nonuniqueness
paper because it shows counterfactual means may be identified without unique
bridge functions; the proposed gap is a named long-term target-loading score
with a critical-completeness phase diagram.  \citet[Abstract and Section
3 bound construction]{GhassamiShpitserTchetgen2023} is the closest
no-completeness partial-identification comparator; it gives proxy partial-ID
bounds rather than the exact row-space frontier separating point ID from a
bridge-envelope interval.  \citet[Theorem 1 and Section 4]{CanaySantosShaikh2013}
motivates a threshold/sensitivity object because it shows completeness-type
identification conditions in nonparametric endogenous models may be
nontrivially untestable.  \citet[Abstract, Theorem 2.1, and Section 4 proximal
example]{BennettKallusMaoNeweySyrgkanisUehara2023} gives the strongest
functional inference comparator: strong identification of a functional despite
weak identification of a nuisance; this proposal specializes the issue to
long-term proximal ATE loadings and asks for a finite observable threshold and
sharp envelope.  \citet[Abstract and Sections 2--3]{Santos2011JoE} is the NPIV
ancestor for recovering a continuous linear functional when the underlying
structural function is not identified; the present proposal differs by adding
bounded negative-control bridge fibers, long-term experimental loadings, and
sharp bridge-envelope endpoints.  \citet[Chapter 77, Sections 1 and 3]{CarrascoFlorensRenault2007}
and \citet[Abstract plus Sections 2--3 on approximation numbers and link
conditions]{ChenReiss2011} supply the inverse-problem and singular-value
language for the local weak-completeness conjecture.  \citet[Abstract and
Section 4's minimax bridge-learning construction]{KallusMaoUehara2021} and
\citet{MastouriZhuGultchinEtAl2021} study bridge learning through minimax or
kernel inverse-problem methods; they are relevant because regularized bridge
selection can mask target-active null directions.  \citet{AtheyChettyImbensKang2019}
and \citet{ImbensKallusMaoWang2025} motivate the long-term ATE setting with
short-term proxies and persistent confounding, but they use sufficient surrogate
or sequential proxy structures rather than a sharp critical-completeness
frontier.  \citet{YingMiaoShiTchetgen2023} extends proximal inference to
longitudinal treatment regimes and shows why bridge equations and
regularization become central in time-indexed settings.

The in-catalogue prior-work substrate is the archived
\texttt{eid\_proximal\_phase}/\texttt{v1} proposal, especially the reviewer
request to strengthen a finite diagnostic taxonomy into a generic-class
proximal obstruction or theorem.  That banked run proposed scalar singular-value
and native-selector thresholds but was downgraded because its accepted content
was finite taxonomy and selector-range geometry.  The failed
\texttt{pid\_long\_term\_surrogate}/\texttt{v1} run is relevant only as a
warning: prevalence dilation and generic LP containment did not prove the
reviewer-requested common-kernel bridge compatibility theorem.  The failed
\texttt{pid\_mediation\_proxy}/\texttt{v1} run is relevant because reviewers
flagged bridge-envelope realizability as a hard sharpness step.  This proposal
therefore avoids a generic LP endpoint theorem and makes the exact focal object
the target-active null score for a long-term proximal ATE loading.

\section{Formal setup}
All variables have finite support.  Let \(P=(P_E,P_B)\) denote the observed
two-sample law.  Sample \(E\) supplies the experimental loading distribution
for \((A,W,S,X)\), and sample \(B\) supplies the terminal outcome regression and
the bridge conditional law for \((Y^L,A,Z,W,S,X)\).  For each treatment value
\(a\), write \(h_a\in\R^{d_a}\) for the vector of bounded outcome-bridge values
\(h_a(w,s,x)\), and stack \(h=(h_0,h_1)\in[0,1]^d\).  The observed bridge
operator \(K_P:\R^d\to\R^q\) and right-hand side \(m_P\in\R^q\) encode the
conditional moment equations
\[
  \E_B\{Y^L-h_A(W,S,X)\mid Z=z,A=a,S=s,X=x\}=0
\]
over the positive cells.  The bridge fiber is
\[
  \calH(P)=\{h\in[0,1]^d:K_P h=m_P\}.
\]
The long-term experimental ATE loading is the vector \(c_P\in\R^d\) satisfying
\[
  \theta_h(P)=c_P^\transpose h
  =\E_E\{h_1(W,S,X)-h_0(W,S,X)\}.
\]
Let \(N_P=\ker(K_P)\), let \(\Pi_{N_P}\) be the Euclidean projection onto
\(N_P\), and define the target-active null score
\[
  \alpha_{\mathrm{LT}}(P)=\|\Pi_{N_P}c_P\|_2.
\]
For local sequences, let \(K_{P_n}=U_n \Sigma_n V_n^\transpose\) be a singular
value decomposition and let \(a_{j,n}=c_{P_n}^\transpose v_{j,n}\) be the
long-term loading on the \(j\)-th right singular vector.  The target-relevant
weak-completeness index is
\[
  \omega_n=\min_{j:a_{j,n}\neq 0}\sqrt{n}\,\sigma_{j,n}/|a_{j,n}|.
\]
The sharp bridge-envelope set is
\[
  \Theta_I(P)=\{c_P^\transpose h:h\in\calH(P)\}.
\]
Let \(h_P^\star\) denote the lexicographically selected Chebyshev center of
\(\calH(P)\), i.e. a bridge solution maximizing the minimum coordinate slack
\(\min_j\{h_j,1-h_j\}\), with lexicographic tie-breaking.  Define the bounded
null-displacement polytope and its support function by
\[
  \mathcal{D}_P=N_P\cap\{u\in\R^d:0\le h_P^\star+u\le1\},\qquad
  \psi_P(g)=\sup_{u\in\mathcal{D}_P}g^\transpose u .
\]
The bridge-envelope support half-width is
\[
  R_{\mathrm{LT}}(P)=\frac12\left\{\sup_{h\in\calH(P)}c_P^\transpose h
  -\inf_{h\in\calH(P)}c_P^\transpose h\right\}.
\]
Equivalently, when \(h_P^\star\in\calH(P)\),
\[
  R_{\mathrm{LT}}(P)=\{\psi_P(c_P)+\psi_P(-c_P)\}/2 .
\]
For the concrete witness in Section~\ref{ex:witness}, \(X\) and \(S\) are
degenerate, \(A\sim\operatorname{Bernoulli}(1/2)\), \(Z\) is binary, \(W\) has
three values, and the bridge matrix has \(q=2<d=3\) with a one-dimensional
target-active null space on an open positive-cell stratum.

\[
\boxed{\begin{minipage}{0.94\linewidth}
Exact-identification tuple:
\((\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions})\) is fixed as follows.
\(\texttt{qid}=\texttt{eid\_proximal\_completeness}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph/SWIG is a two-sample
long-term proximal negative-control design with baseline covariates \(X\),
binary treatment \(A\in\{0,1\}\), short-term proxy history \(S\), treatment
negative-control proxy \(Z\), outcome negative-control proxy \(W\), latent
confounder \(U\), and terminal outcome \(Y^L\); sample \(E\) is randomized or
short-term experimental and supplies the target loading on \((W,S,X,A)\), while
sample \(B\) is the bridge-learning sample with \(Y^L\).  The treatment is the
binary intervention \(A=a\).  The target estimand is
\(\theta(P)=\E_E\{Y^L(1)-Y^L(0)\}\).  Identifying assumptions are consistency
and positivity, negative-control exclusions for \(Z,W\), existence of bounded
outcome bridges \(h_a(W,S,X)\in[0,1]\) satisfying the observed bridge equation
in sample \(B\), and cross-sample transport of the bridge equation to the
experimental loading.  The condition \(\alpha_{\mathrm{LT}}(P)=0\) is the
tested frontier object, not a locked assumption.  Completeness of the full
bridge operator is not locked in; the question is the sharp boundary at which
the target remains identified as completeness approaches failure.
\end{minipage}}
\]

\section{Assumptions}
\begin{assumption}[Finite positive cells]\label{ass:finite-positive}
The support of \((A,W,Z,S,X,Y^L)\) used in the bridge equations is finite, and
every conditioning cell \((Z=z,A=a,S=s,X=x)\) appearing in \(K_P\) has positive
probability in sample \(B\).  The experimental loading cells used in \(c_P\)
have positive probability in sample \(E\).
\end{assumption}

\begin{assumption}[Negative-control proximal restrictions]\label{ass:proximal}
The SWIG obeys consistency, no interference, the standard negative-control
exclusion restrictions for \(Z\) and \(W\) relative to \(U\), and overlap for
the interventions \(A=0,1\).  Under these restrictions, any bounded outcome
bridge \(h\in\calH(P)\) evaluates the long-term intervention mean through
\(c_P^\transpose h\) when the target-active null-score condition holds.
\end{assumption}

\begin{assumption}[Bounded bridge fiber]\label{ass:bounded-fiber}
The bridge fiber \(\calH(P)=\{h\in[0,1]^d:K_Ph=m_P\}\) is nonempty and contains
at least one relative-interior point \(h^\circ\) satisfying
\(\varepsilon_P\le h^\circ_j\le 1-\varepsilon_P\) for all coordinates, where
\(\varepsilon_P\in(0,1/2]\) is a named slack constant.  The Chebyshev center
\(h_P^\star\), the null-displacement polytope \(\mathcal{D}_P\), the support function
\(\psi_P\), and the support half-width \(R_{\mathrm{LT}}(P)\) are defined as in
Section 6.
\end{assumption}

\begin{assumption}[Target-active null score]\label{ass:null-score}
The target-active null score is \(\alpha_{\mathrm{LT}}(P)=\|\Pi_{N_P}c_P\|_2\),
where \(N_P=\ker(K_P)\).  The point-identifying threshold condition is
\(\alpha_{\mathrm{LT}}(P)=0\), but this condition is not assumed unless a
statement explicitly invokes the point-identification side of the frontier.
\end{assumption}

\begin{assumption}[Open bounded bridge class]\label{ass:open-bridge}
The law \(P\) belongs to a finite-support open neighborhood in which the bridge
fiber remains nonempty, the relative-interior slack in
Assumption~\ref{ass:bounded-fiber} remains bounded below by
\(\underline{\varepsilon}>0\), and the maps \(P\mapsto K_P\), \(P\mapsto m_P\),
and \(P\mapsto c_P\) are continuously differentiable on the positive-cell
simplex.  The rank of \(K_P\) is locally constant on the considered stratum, so
the null dimension of the bridge fiber does not appear only at a rank-drop
boundary.
\end{assumption}

\begin{assumption}[Open one-dimensional weak-completeness class]\label{ass:open-weak}
For the local weak-completeness statement, \(P_n\) lies in a finite-support
open class in which exactly one right singular direction \(v_{*,n}\) is
target-active and weak, \(a_{*,n}=c_{P_n}^\transpose v_{*,n}\neq0\),
\(\sigma_{*,n}\downarrow0\), all other target-active singular directions are
bounded away from zero by \(\underline{\sigma}>0\), and the bridge slack obeys
\(\varepsilon_{P_n}\ge\underline{\varepsilon}>0\).  The loading is bounded and
bounded away from zero, \(\underline a\le |a_{*,n}|\le\overline a\), and the
local sequence is restricted to exactly one of the three named regimes:
\(\omega_n\to\infty\), \(\omega_n\to\tau\in(0,\infty)\), or
\(\omega_n\to0\), where
\(\omega_n=\sqrt{n}\sigma_{*,n}/|a_{*,n}|\).  No additional free threshold is
allowed.
\end{assumption}

\begin{assumption}[Regularized bridge workflow]\label{ass:regularized}
Let \((\widehat K,\widehat m,\widehat c,\widehat V)\) be finite-dimensional
estimators satisfying a joint central limit theorem for
\(\sqrt n\,\mathrm{vec}(\widehat K-K_P,\widehat m-m_P,\widehat c-c_P)\), with
\(\widehat V\) consistently estimating the covariance of
\(\sqrt n(\widehat K h-\widehat m)\) uniformly over bounded \(h\), and with
\(\widehat V\) positive definite on the residual span with probability tending
to one.  The
regularized bridge estimator is the concrete Tikhonov selector
\[
  \widehat h_{\lambda_n}\in\arg\min_{h\in[0,1]^d}
  \{ \|\widehat K h-\widehat m\|_{\widehat V^{-1}}^2
     +\lambda_n\|h-h_P^\star\|_2^2\},
  \qquad
  \widehat\theta_{\lambda_n}=\widehat c^\transpose\widehat h_{\lambda_n},
\]
with \(\lambda_n\asymp n^{-1/2}\sigma_{*,n}\) in the local weak-completeness
class.  For nominal level \(1-\gamma\), the projection confidence set is
\[
  C_n(\gamma)=\{\widehat c^\transpose h:h\in[0,1]^d,\,
  n\|\widehat K h-\widehat m\|_{\widehat V^{-1}}^2
  \le \chi^2_{q,1-\gamma}\}.
\end{assumption}

\section{Main results}
\begin{proposition}[Support Proposition: null-annihilator point-identification criterion]\label{prop:null-annihilator}
Under Assumptions~\ref{ass:finite-positive}--\ref{ass:null-score}, if
\(\alpha_{\mathrm{LT}}(P)=0\), then \(c_P^\transpose h\) is constant over
\(\calH(P)\).  Hence the long-term ATE is point identified by any bounded
outcome bridge in \(\calH(P)\).  If Assumption~\ref{ass:bounded-fiber} also
holds and \(\alpha_{\mathrm{LT}}(P)>0\), then there exist two bridge solutions
in the affine hull of \(\calH(P)\) that disagree on \(c_P^\transpose h\).
\end{proposition}

\paragraph{Why this is new and worth studying.}
(a) This support proposition is not claimed as the flagship novelty.  It is the finite
linear-algebra backbone behind \citet{ZhangLiMiaoTchetgen2023} and
\citet{BennettKallusMaoNeweySyrgkanisUehara2023}: target functionals can be
identified even when nuisance bridges are not.  The difference is that the
functional here is the two-sample long-term ATE loading \(c_P\), which is the
object needed by \citet{ImbensKallusMaoWang2025}.  (b) Recording the criterion
makes the proposed bridge threshold auditable: the consumer is the
\citet{ImbensKallusMaoWang2025} long-term data-combination design, where the
analyst needs to know whether weak proxies still suffice for the terminal ATE.

\begin{conjecture}[Conjecture 1: sharp critical-completeness frontier (NOT YET PROVED)]\label{conj:critical-frontier}
Under Assumptions~\ref{ass:finite-positive}--\ref{ass:open-bridge}, the
following hold on an open neighborhood of every law in that class.
\begin{enumerate}[label=(\roman*)]
\item \(\alpha_{\mathrm{LT}}(P)=0\) if and only if \(\Theta_I(P)\) is a
singleton equal to the proximal long-term ATE.
\item If \(\alpha_{\mathrm{LT}}(P)>0\), then \(\Theta_I(P)\) is a non-singleton
compact interval and its half-width is the finite support-function LP
\[
  R_{\mathrm{LT}}(P)=\{\psi_P(c_P)+\psi_P(-c_P)\}/2>0,
  \qquad
  \psi_P(g)=\sup_{u\in N_P,\;0\le h_P^\star+u\le1}g^\transpose u .
\]
On a one-dimensional exposed-null subclass this reduces to the two endpoint
radii along the exposed null direction; in higher-dimensional fibers the LP,
not a single radius, is the claimed width object.
\item The interval endpoints are attained by bounded bridge solutions that can
be represented by a finite proximal negative-control mean law, not merely by an
abstract bridge array.
\end{enumerate}
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet[Sections 2--4]{MiaoGengTchetgen2018} gives point identification
under proxy rank/completeness; \citet[Abstract and Section 3]{GhassamiShpitserTchetgen2023}
gives partial-ID bounds when completeness is not available; and
\citet[Section 2 and Section 3]{ZhangLiMiaoTchetgen2023} shows nonunique
bridges need not destroy target identification.  None gives an open
finite-support critical threshold for the long-term ATE loading, a finite
support-function LP \(R_{\mathrm{LT}}(P)\), and a bridge-envelope realization
clause.  This is also the exact gap flagged by the archived
\texttt{eid\_proximal\_phase} reviewers: strengthen the finite diagnostic
taxonomy into a generic-class theorem or obstruction.  (b) Resolving the
conjecture gives the \citet[Theorem 3.1 and equation (9)]{CuiPuShiMiaoTchetgen2024}
proximal OR/DR workflow a concrete warning label: when
\(\alpha_{\mathrm{LT}}(P)>0\), the reported point estimate is a
selector-dependent element of a sharp interval, not an identified long-term ATE.

\begin{conjecture}[Conjecture 2: local weak-completeness phase diagram (NOT YET PROVED)]\label{conj:local-weak}
Under Assumptions~\ref{ass:finite-positive}--\ref{ass:regularized}, let the
single target-active singular value \(\sigma_{*,n}\) approach zero and write
\(\omega_n=\sqrt{n}\sigma_{*,n}/|a_{*,n}|\).  The regularized proximal
long-term ATE estimator has three regimes:
\begin{enumerate}[label=(\roman*)]
\item if \(\omega_n\to\infty\), the target is locally regular and the usual
proximal influence-function limit from the strong-completeness regime is
recovered;
\item if \(\omega_n\to\tau\in(0,\infty)\), the limit experiment is a Gaussian
shift inverse problem in the active bridge-null coordinate, truncated only when
the box constraint binds at a bridge-envelope endpoint, and the projection
confidence set \(C_n(\gamma)\) has nondegenerate random length;
\item if \(\omega_n\to0\), no regular point estimator is uniformly valid and
the projection confidence set converges to the sharp bridge-envelope interval
from Conjecture~\ref{conj:critical-frontier}.
\end{enumerate}
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet[Chapter 77, Sections 1 and 3]{CarrascoFlorensRenault2007} describes
spectral regularization for econometric inverse problems,
\citet[Sections 2--3]{ChenReiss2011} separates rate behavior by approximation
numbers and link conditions, and
\citet[Abstract and Sections 2--3]{Santos2011JoE} recovers continuous linear
functionals in NPIV even when the nuisance function is only partially
identified.  In addition,
\citet[Abstract, Theorem 2.1, and Section 4]{BennettKallusMaoNeweySyrgkanisUehara2023}
studies strongly identified functionals of weakly identified functions.  The
proposed gap is the explicit proximal long-term ATE phase diagram indexed by
\(\omega_n=\sqrt{n}\sigma_{*,n}/|a_{*,n}|\), with a bridge-envelope endpoint
when completeness fails and the concrete \(C_n(\gamma)\) projection set when it
nearly fails.  (b) The concrete consumer is the negative-control bridge learning
workflow of \citet[Abstract and Section 4]{KallusMaoUehara2021}: the phase
diagram would tell when minimax or Tikhonov bridge learning can support ordinary
point inference and when only projection inference is defensible.

\section{Sanity-check corollaries}
\begin{corollary}[Complete-operator reduction]\label{cor:complete}
If \(K_P\) has full column rank, then \(N_P=\{0\}\),
\(\alpha_{\mathrm{LT}}(P)=0\), and Proposition~\ref{prop:null-annihilator} collapses
to the standard proximal point-identification corner of
\citet{MiaoGengTchetgen2018} and \citet{CuiPuShiMiaoTchetgen2024}.
\end{corollary}

\begin{corollary}[Nonunique but target-inactive reduction]\label{cor:nonunique}
If \(K_P\) is rank deficient but \(c_P\in\operatorname{Row}(K_P)\), then
\(\calH(P)\) can contain many bridges while \(\Theta_I(P)\) remains a
singleton.  This is the long-term two-sample analogue of the
\citet{ZhangLiMiaoTchetgen2023} nonunique-bridge identification phenomenon.
\end{corollary}

\begin{example}[Concrete open-stratum incomplete witness]\label{ex:witness}
Let \(X\) and \(S\) be degenerate, let \(A\sim\operatorname{Bernoulli}(1/2)\),
let \(Z\in\{0,1\}\), and let \(W\in\{0,1,2\}\).  For a fixed treatment arm,
take the bridge conditional matrix
\[
K=
\begin{pmatrix}
1/2&3/10&1/5\\
1/5&3/10&1/2
\end{pmatrix},
\qquad
h^\star=(2/5,1/2,3/5)^\transpose,\qquad
m=Kh^\star .
\]
All entries of \(K\) are strictly positive, \(q=2<d=3\), and
\(\ker(K)=\operatorname{span}\{(3,-7,3)^\transpose\}\) on an open neighborhood
of positive matrices with rank two.  Let the experimental long-term loading for
this arm be \(c=(0,0,1)^\transpose\).  Then
\[
\alpha_{\mathrm{LT}}(P)=|c^\transpose(3,-7,3)|/\sqrt{67}=3/\sqrt{67}>0,
\]
and the bounded bridge fiber is
\[
  h(t)=h^\star+t(3,-7,3)^\transpose,\qquad -1/14\le t\le1/14.
\]
Thus
\[
\Theta_I(P)=\{3/5+3t:-1/14\le t\le1/14\}
=[27/70,57/70],\qquad R_{\mathrm{LT}}(P)=3/14.
\]
The two endpoint bridge arrays are strictly inside \([0,1]^3\) except for the
exposed middle-coordinate constraint, and the same rank-two, target-active
null geometry persists under small positive-cell perturbations.  This supplies
a non-corner witness for Conjecture~\ref{conj:critical-frontier}; replacing the
fixed nonzero singular value by \(\sigma_{*,n}\downarrow0\) along the same
right-null direction supplies the one-dimensional local witness for
Conjecture~\ref{conj:local-weak}.
\end{example}

\section{Proof-sketch route}
Proposition~\ref{prop:null-annihilator} is finite-dimensional linear algebra:
two bridge solutions differ by an element of \(\ker(K_P)\), and a linear
functional is constant on an affine fiber exactly when its loading lies in the
row space of the operator.  Conjecture~\ref{conj:critical-frontier} would be
attacked by combining that row-space identity with support-function calculus
for the bounded bridge fiber: the width calculation is the finite linear
program defining \(\psi_P(c_P)\) and \(\psi_P(-c_P)\) over
\(N_P\cap([0,1]^d-h_P^\star)\), with the one-dimensional exposed-null formula
as a corollary rather than an assumption.  The remaining step is a finite
latent mean-law realization for the endpoint bridge arrays; the explicit
open-stratum algebra is the observable ternary-\(W\) law in
Example~\ref{ex:witness}.  The local weak-completeness conjecture studies the
concrete Tikhonov estimator \(\widehat h_{\lambda_n}\) and projection set
\(C_n(\gamma)\), reducing the bridge residual process along the target-active
singular vector to a one-dimensional Gaussian shift inverse problem, with the
strong, weak, and failed regimes separated by
\(\omega_n=\sqrt{n}\sigma_{*,n}/|a_{*,n}|\).  The main mathematical risk is the
realization clause: the endpoint bridge arrays must be completed to an actual
negative-control mean law rather than only to an abstract solution of
\(K_Ph=m_P\).

\section{Honest scope flags}
Proposition~\ref{prop:null-annihilator} is routine and included only to make the
focal threshold precise.  Conjectures~\ref{conj:critical-frontier} and
\ref{conj:local-weak} are not yet proved; they are the proposed research
kernel.  The largest open soundness issue is finite bridge-envelope
realization, because prior CausalSmith proxy proposals failed when they assumed
endpoint attainability instead of proving it.  The local weak-completeness
phase diagram is now restricted to the concrete finite-dimensional Tikhonov
selector and projection confidence set in Assumption~\ref{ass:regularized}, but
its covariance regularity may still need to be narrowed after the mathematical
proof attempt.  The v1 reviewer rejected the support proposition as
novelty-bearing and requested a support-function width object, location-level
anchors, and a concrete finite-law witness; v2 patched those items without
changing the kernel.  The v2 reviewer found that the witness was only a
rank-drop boundary, the width formula was under-specified in higher-dimensional
null spaces, Santos (2011) was missing, and Conjecture~\ref{conj:local-weak}
needed a concrete estimator and confidence set; v3 narrows the width claim to a
finite support-function LP, adds an open-stratum \(q<d\) witness, and specifies
the Tikhonov/projection workflow.

\section{Iteration trail}
\begin{itemize}[leftmargin=1.5em]
\item v1 (cold-start) --- initial draft proposing the target-active null-score
threshold and local weak-completeness phase diagram; prior verdict: none.
\item v2 (revise) --- demoted the null-annihilator theorem to a support
proposition, rewrote the width claim using support-function radii, added
location-level comparator anchors, and replaced the abstract matrix witness by
an observable binary-cell law; prior verdict: REVISE.
\item v3 (revise) --- replaced the one-dimensional radius formula by a finite
support-function LP, added an open-stratum ternary-\(W\) incomplete witness,
added Santos (2011) and location-level Kallus--Mao--Uehara anchors, and made
the weak-completeness estimator/confidence set concrete; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Athey et~al.(2019)]{AtheyChettyImbensKang2019}
Athey, S., Chetty, R., Imbens, G.~W., and Kang, H. (2019).
\newblock The surrogate index: Combining short-term proxies to estimate
long-term treatment effects more rapidly and precisely.
\newblock \emph{NBER Working Paper} 26463.
\newblock \url{https://doi.org/10.3386/w26463}.

\bibitem[Bennett et~al.(2023)]{BennettKallusMaoNeweySyrgkanisUehara2023}
Bennett, A., Kallus, N., Mao, X., Newey, W., Syrgkanis, V., and Uehara, M.
(2023).
\newblock Inference on strongly identified functionals of weakly identified
functions.
\newblock \emph{Proceedings of Machine Learning Research}, 195:2265--2265.
\newblock \url{https://proceedings.mlr.press/v195/bennett23a.html}.

\bibitem[Canay et~al.(2013)]{CanaySantosShaikh2013}
Canay, I.~A., Santos, A., and Shaikh, A.~M. (2013).
\newblock On the testability of identification in some nonparametric models
with endogeneity.
\newblock \emph{Econometrica}, 81(6):2535--2559.
\newblock \url{https://doi.org/10.3982/ECTA10851}.

\bibitem[Carrasco et~al.(2007)]{CarrascoFlorensRenault2007}
Carrasco, M., Florens, J.-P., and Renault, E. (2007).
\newblock Linear inverse problems in structural econometrics: Estimation based
on spectral decomposition and regularization.
\newblock In Heckman, J.~J. and Leamer, E.~E., editors, \emph{Handbook of
Econometrics}, volume 6B, pages 5633--5751. Elsevier.
\newblock \url{https://doi.org/10.1016/S1573-4412(07)06077-1}.

\bibitem[Chen and Reiss(2011)]{ChenReiss2011}
Chen, X. and Reiss, M. (2011).
\newblock On rate optimality for ill-posed inverse problems in econometrics.
\newblock \emph{Econometric Theory}, 27(3):497--521.
\newblock \url{https://doi.org/10.1017/S0266466610000381}.

\bibitem[Cui et~al.(2024)]{CuiPuShiMiaoTchetgen2024}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. (2024).
\newblock Semiparametric proximal causal inference.
\newblock \emph{Journal of the American Statistical Association}.
\newblock \url{https://doi.org/10.1080/01621459.2023.2191817}.

\bibitem[Ghassami et~al.(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. (2023).
\newblock Partial identification of causal effects using proxy variables.
\newblock \emph{arXiv preprint}.
\newblock \url{https://doi.org/10.48550/arXiv.2304.04374}.

\bibitem[Imbens et~al.(2025)]{ImbensKallusMaoWang2025}
Imbens, G., Kallus, N., Mao, X., and Wang, Y. (2025).
\newblock Long-term causal inference under persistent confounding via data
combination.
\newblock \emph{Journal of the Royal Statistical Society Series B},
87(2):362--392.
\newblock \url{https://doi.org/10.1093/jrsssb/qkae095}.

\bibitem[Kallus et~al.(2021)]{KallusMaoUehara2021}
Kallus, N., Mao, X., and Uehara, M. (2021).
\newblock Causal inference under unmeasured confounding with negative controls:
A minimax learning approach.
\newblock \emph{arXiv preprint}.
\newblock \url{https://doi.org/10.48550/arXiv.2103.14029}.

\bibitem[Mastouri et~al.(2021)]{MastouriZhuGultchinEtAl2021}
Mastouri, A., Zhu, Y., Gultchin, L., Korba, A., Silva, R., Kusner, M.~J.,
Gretton, A., and Muandet, K. (2021).
\newblock Proximal causal learning with kernels: Two-stage estimation and
moment restriction.
\newblock \emph{Proceedings of the 38th International Conference on Machine
Learning}.
\newblock \url{https://proceedings.mlr.press/v139/mastouri21a.html}.

\bibitem[Miao et~al.(2018)]{MiaoGengTchetgen2018}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E.~J. (2018).
\newblock Identifying causal effects with proxy variables of an unmeasured
confounder.
\newblock \emph{Biometrika}, 105(4):987--993.
\newblock \url{https://doi.org/10.1093/biomet/asy038}.

\bibitem[Santos(2011)]{Santos2011JoE}
Santos, A. (2011).
\newblock Instrumental variable methods for recovering continuous linear
functionals.
\newblock \emph{Journal of Econometrics}, 161(2):129--146.
\newblock \url{https://doi.org/10.1016/j.jeconom.2010.11.014}.

\bibitem[Ying et~al.(2023)]{YingMiaoShiTchetgen2023}
Ying, A., Miao, W., Shi, X., and Tchetgen Tchetgen, E.~J. (2023).
\newblock Proximal causal inference for complex longitudinal studies.
\newblock \emph{Journal of the Royal Statistical Society Series B},
85(3):684--704.
\newblock \url{https://doi.org/10.1093/jrsssb/qkad020}.

\bibitem[Zhang et~al.(2023)]{ZhangLiMiaoTchetgen2023}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. (2023).
\newblock Proximal causal inference without uniqueness assumptions.
\newblock \emph{Statistics and Probability Letters}, 198:109836.
\newblock \url{https://doi.org/10.1016/j.spl.2023.109836}.
\end{thebibliography}

\end{document}
