% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_proximal\_completeness, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_proximal\_completeness} / \texttt{v1}%
  \\ \large\textit{Finite bridge-envelope realization and nonrealization for proximal ATE}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID / proximal-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional}).
\]
Here \(\texttt{qid}=\texttt{eid\_proximal\_completeness}\) and
\(\texttt{specialization}=\texttt{v1}\).  The observable distribution \(P\) is
a finite-support law of \((Y,A,W,Z,X)\), where \(A\in\{0,1\}\), \(Y\in[0,1]\),
and \(W,Z,X\) are finite.  The causal parameter is the long-run proximal ATE
\(\theta=\E[Y(1)-Y(0)]\).  The identifying restrictions are finite latent
negative-control models with consistency, positivity, \(W,Z\) unaffected by
treatment, no direct effect of \(Z\) on \(Y(a)\) after the latent state
\(U\) and \(X\), and an outcome-bridge equation
\(\E\{Y\mid Z,A=a,X\}=\E\{h_a(W,X)\mid Z,A=a,X\}\).  The bounding functional is
the pair of support functions of (i) the observable bounded bridge envelope
\(\Theta_{\mathrm{br}}(P)\) and (ii) the causally realizable latent envelope
\(\Theta_{\mathrm{lat}}(P)\), with the bridge-realization defect
\(\Delta_{\mathrm{BR}}(P)\) defined as their two-sided support-function gap.

\begin{abstract}
Proximal identification papers often use completeness to move from an
outcome-bridge equation to a point-identified ATE, while partial-identification
papers use the same bridge equation to construct observable bounds when
completeness fails.  This proposal asks whether every bounded observable bridge
endpoint is actually induced by a finite latent negative-control causal model.
The kernel claim is a finite realization frontier: a computable
bridge-realization defect \(\Delta_{\mathrm{BR}}(P)\) is zero exactly when the
observable bridge envelope and the latent negative-control ATE envelope agree,
and is generically positive on a nondegenerate binary-proxy boundary class.  The
main nonrealization conjecture is intentionally labelled open; it would turn a
reviewer warning from prior CausalSmith proximal runs into a sharp theorem.
If resolved, proximal analysts would know when bridge-envelope endpoints are
causal bounds and when they are only algebraic artifacts of a weak bridge
operator.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Completeness is the load-bearing condition that turns negative-control proxies
into a proximal adjustment formula.  Near completeness failure, however, the
observable bridge equation may have many bounded solutions.  A researcher can
then compute a bridge-envelope interval for the ATE, but it is not automatic
that each algebraic bridge endpoint corresponds to any latent negative-control
causal law.  This matters for long-term ATE work because short-term proxies are
often noisy measurements of persistent unobserved confounding: the empirical
question is not just whether a bridge equation has solutions, but whether its
extreme solutions are causally attainable.

\paragraph{The main finding (proposed).}
The proposed main result is Conjecture~\ref{conj:generic-nonrealization}.  It
states that on an open class of finite binary-proxy laws with a nonunique
bounded outcome-bridge fiber, the observable bridge envelope strictly contains
the latent negative-control envelope.  The named focal object is the
bridge-realization defect \(\Delta_{\mathrm{BR}}(P)\), a support-function gap
computed by a finite bridge LP and a finite response-type feasibility LP.
Theorem~\ref{thm:farkas-frontier} supplies the routine algebraic frontier:
\(\Delta_{\mathrm{BR}}(P)=0\) if and only if every bridge-envelope extreme point
passes the finite Farkas realization inequalities.

\paragraph{What is new.}
The novelty kernel is not another sufficient completeness assumption and not a
generic LP restatement of partial identification.  \citet[Sections 2--3]{MiaoGengTchetgen2018}
and \citet[Section 3]{CuiPuShiMiaoTchetgen2024} work with bridge equations and
completeness or semiparametric regularity; \citet[abstract and Sections
3--4]{GhassamiShpitserTchetgen2023} moves to partial identification when
completeness fails; \citet[abstract and Sections 2--3]{ZhangLiMiaoTchetgen2023}
separates bridge uniqueness from target-functional identification.  None of
these papers asks the finite sharpness question isolated here: whether a
bounded observable bridge endpoint is realizable by an actual latent
negative-control causal model.  The prior CausalSmith
\texttt{eid\_proximal\_phase} angle explicitly conjectured universal finite
realization and flagged it as the main sharpness risk; this proposal reverses
that direction and asks for a generic nonrealization theorem.

\paragraph{How it positions in the literature.}
The proposal is in the PartialID cluster, with proximal exact identification as
the source of the bridge equations.  It uses the Balke--Pearl finite
response-type style as a causal-realization benchmark, the proximal bridge
literature as the observable-equation substrate, and the no-completeness
proximal bounds literature as the closest partial-identification neighbor.  The
contribution is a non-LP sharpness diagnostic layered on top of the bridge
envelope: the bridge envelope is easy to compute, while the latent envelope is
the causal object whose equality to that bridge envelope is open.

\paragraph{Implications for the community.}
The concrete downstream consumer is the proxy partial-identification program of
\citet{GhassamiShpitserTchetgen2023}: if Conjecture~\ref{conj:generic-nonrealization}
is true, bridge-envelope bounds need a realization check before they can be
reported as sharp causal bounds.  The conclusion changes research practice by
making analysts report \(\Delta_{\mathrm{BR}}(P)\), not just a bridge residual
or a bridge-envelope width, when completeness is weak or fails.

\section{Related work}
\citet[Sections 2--3]{MiaoGengTchetgen2018} give a Biometrika negative-control
identification framework using proxy rank and completeness conditions; this
proposal studies the finite boundary where those conditions no longer deliver a
unique bridge.  \citet[Section 3 and equation (9)]{CuiPuShiMiaoTchetgen2024}
develop proximal double robustness and semiparametric efficiency; their bridge
regularity assumptions motivate why a weak bridge operator needs a separate
sharpness diagnostic.  \citet[abstract and Sections 2--3]{ZhangLiMiaoTchetgen2023}
show that counterfactual means can remain identified without unique bridge
functions, which is the target-functional distinction sharpened here into a
realization question for bridge endpoints.  \citet[abstract and Sections
3--4]{GhassamiShpitserTchetgen2023} develop proximal partial-identification
bounds when completeness fails; their bounds are the closest published
consumer, but they do not characterize when an observable bridge endpoint is
latent-realizable.  \citet[Theorem 1 and Section 4]{CanaySantosShaikh2013}
show that completeness-type assumptions can be strongly untestable, motivating
observable sensitivity and sharpness diagnostics rather than completeness
pretesting.  \citet{BalkePearl1997} use finite response-type linear programming
to obtain sharp causal bounds with imperfect compliance; this proposal imports
that realization discipline into proximal negative-control bridge arrays.
\citet{Manski1990} is the bounded-outcome partial-identification baseline:
when proxies carry no target-relevant information, any proximal bridge envelope
should reduce to a Manski-style interval rather than overclaim point
identification.  \citet[Sections 2--3]{AtheyChettyImbensKang2019} and
\citet[Sections 2--4]{ImbensKallusMaoWang2025} motivate the long-term ATE
setting in which short-term outcomes or proxies stand in for persistent
unobserved confounding; they do not provide a bridge-realization frontier.

In-catalogue CausalSmith prior art is thin for this exact question.  The
\texttt{doc/API.md} ExactID / PartialID catalogue records only seed-time empty
ExactID and PartialID trees plus a Manski bounded-outcome study entry, whose
headline is selected-cell mean-dominance tightening rather than proximal bridge
realization.  The banked \texttt{eid\_proximal\_phase} proposal conjectured
that every rational bounded bridge endpoint is realized by a finite latent
proximal model and recorded realization as the main sharpness risk; the
present proposal is a structurally different nonrealization and frontier
proposal.  The failed \texttt{pid\_mediation\_proxy} reviewer warned that
``sharp bridge realisability'' had been assumed rather than proved, which is
exactly the hidden step isolated here.

\section{Formal setup}
All spaces are finite.  Let \(P\) denote the observable law of
\((Y,A,W,Z,X)\), with \(A\in\{0,1\}\), \(Y\in[0,1]\), and finite supports
\(\mathcal W,\mathcal Z,\mathcal X\).  For each treatment arm \(a\), define the
conditional bridge operator
\[
  (T_{a,x}h)(z)=\sum_{w\in\mathcal W}h(w,x)\,P(W=w\mid Z=z,A=a,X=x)
\]
and the observed outcome regression
\[
  m_{a,x}(z)=\E_P[Y\mid Z=z,A=a,X=x].
\]
The bounded observable bridge fiber is
\[
  \mathcal H_a(P)=\{h_a:\mathcal W\times\mathcal X\to[0,1]:
    T_{a,x}h_a(\cdot,x)=m_{a,x}\ \text{for all }x\}.
\]
Let \(\lambda_x(w)=P(W=w\mid X=x)\) and define the native bridge loading
\[
  L_a(h_a)=\sum_{x,w}P(X=x)\lambda_x(w)h_a(w,x),\qquad
  L(h_1,h_0)=L_1(h_1)-L_0(h_0).
\]
The observable bridge envelope is
\[
  \Theta_{\mathrm{br}}(P)=\{L(h_1,h_0):h_a\in\mathcal H_a(P),\ a=0,1\}.
\]

A finite latent negative-control model consists, conditional on \(X=x\), of a
finite latent state \(U\), potential outcomes \(Y(0),Y(1)\in[0,1]\), proxies
\((W,Z)\) unaffected by \(A\), consistency \(Y=Y(A)\), and the exclusion that
\(Z\) has no direct effect on \(Y(a)\) after \((U,X)\).  For a candidate bridge
pair \(h=(h_1,h_0)\), realization means that there is a nonnegative finite
latent table \(\pi\) matching the observed \(P\) and satisfying, for every
\((u,a,x)\),
\[
  \E_\pi[Y(a)\mid U=u,X=x]
  =
  \sum_{w} h_a(w,x)\Pr_\pi(W=w\mid U=u,X=x).
\]
The latent envelope is
\[
  \Theta_{\mathrm{lat}}(P)=\{\E_\pi[Y(1)-Y(0)]:\pi\ \text{is a finite latent
  negative-control model matching }P\}.
\]
For \(s\in\{-1,1\}\), let
\(\sigma_{\mathrm{br}}(s;P)=\sup_{\theta\in\Theta_{\mathrm{br}}(P)}s\theta\)
and \(\sigma_{\mathrm{lat}}(s;P)=\sup_{\theta\in\Theta_{\mathrm{lat}}(P)}s\theta\).
The bridge-realization defect is the named focal object
\[
  \Delta_{\mathrm{BR}}(P)=
  \max_{s\in\{-1,1\}}\{\sigma_{\mathrm{br}}(s;P)-\sigma_{\mathrm{lat}}(s;P)\}.
\]

\begin{verbatim}
Locked parameters:
qid = eid_proximal_completeness
specialization = v1
P = finite observable law of (Y,A,W,Z,X), A binary, Y in [0,1]
theta = E[Y(1)-Y(0)]
identifying restrictions = finite latent negative-control model plus
  consistency, positivity, W/Z unaffected by A, no direct Z->Y(a) effect
  after (U,X), and the outcome-bridge equation
bounding functional = support-function pair of Theta_br(P) and
  Theta_lat(P), summarized by Delta_BR(P)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite positive observable law]\label{ass:finite-positive}
The supports of \(Y,A,W,Z,X\) are finite, \(A\in\{0,1\}\), \(Y\in[0,1]\), and
all conditional probabilities used in \(T_{a,x}\), \(m_{a,x}\), and
\(\lambda_x\) are well-defined on the support under study.
\end{assumption}

\begin{assumption}[Nonempty bounded bridge fiber]\label{ass:bridge-nonempty}
For each \(a\in\{0,1\}\), the set \(\mathcal H_a(P)\) is nonempty and compact
in the finite-dimensional cube \([0,1]^{|\mathcal W||\mathcal X|}\).
\end{assumption}

\begin{assumption}[Finite latent negative-control class]\label{ass:latent-class}
The admissible causal laws are finite latent tables satisfying consistency,
\(W,Z\) unaffected by treatment, no direct \(Z\to Y(a)\) effect after
\((U,X)\), and the bridge-realization equations displayed in Section~6.
The latent support size is bounded by the Caratheodory bound associated with
the linear constraints, so feasibility is finite-dimensional.
\end{assumption}

\begin{assumption}[Constant-rank binary-proxy boundary]\label{ass:binary-boundary}
For the generic-class conjecture, \(X\) is degenerate,
\(\mathcal W=\mathcal Z=\{0,1\}\), each \(T_a\) has rank one, and the observed
law lies in a constant-rank neighborhood with nonempty bridge fiber and
strictly positive treatment, proxy, and outcome cell probabilities.
\end{assumption}

\begin{assumption}[Noncorner witness margin]\label{ass:witness-margin}
The witness law in Section~9 has a bridge-realization support gap at least
\(\eta_{\mathrm{BR}}>0\), where \(\eta_{\mathrm{BR}}\) is bounded above by the
minimum of the positive cell-probability margin and the constant-rank
singular-gap margin from Assumption~\ref{ass:binary-boundary}.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite Farkas bridge-realization frontier]\label{thm:farkas-frontier}
Under Assumptions~\ref{ass:finite-positive}, \ref{ass:bridge-nonempty}, and
\ref{ass:latent-class}, the following are equivalent.
\begin{enumerate}[label=(\roman*)]
\item \(\Theta_{\mathrm{br}}(P)=\Theta_{\mathrm{lat}}(P)\).
\item \(\Delta_{\mathrm{BR}}(P)=0\).
\item Every extreme point \(h\) of the bounded bridge polytope
\(\mathcal H_1(P)\times\mathcal H_0(P)\) satisfies the finite Farkas dual
inequalities for the latent negative-control feasibility system
\(A_{\mathrm{NC}}(h)\pi=b(P,h)\), \(\pi\ge 0\).
\end{enumerate}
Here \(A_{\mathrm{NC}}(h)\) is the response-type constraint matrix implied by
Assumption~\ref{ass:latent-class}.  This theorem is a proposed routine
finite-dimensional algebra statement, not the flagship novelty claim.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest published comparator is \citet{BalkePearl1997}, which uses
finite response-type LPs for imperfect compliance, and
\citet[abstract and Sections 3--4]{GhassamiShpitserTchetgen2023}, which studies
proximal bounds after completeness failure.  The epsilon-gap is the bridge
realization layer: neither paper states the Farkas test for whether bounded
proximal bridge endpoints themselves are latent negative-control causal laws.
(b) This theorem gives the reviewer-checkable decision procedure needed by
\citet{GhassamiShpitserTchetgen2023}: a bridge endpoint is reportable as a
sharp causal bound only after passing the finite realization inequalities.

\begin{conjecture}[Conjecture 1: generic bridge-envelope nonrealization (NOT YET PROVED)]\label{conj:generic-nonrealization}
Under Assumptions~\ref{ass:finite-positive}, \ref{ass:bridge-nonempty},
\ref{ass:latent-class}, \ref{ass:binary-boundary}, and
\ref{ass:witness-margin}, there exists an open set \(\mathcal O_{\mathrm{BR}}\)
of binary-proxy observable laws such that
\[
  \Delta_{\mathrm{BR}}(P)\ge \eta_{\mathrm{BR}}>0
  \quad\text{for every }P\in\mathcal O_{\mathrm{BR}}.
\]
Equivalently, on this open class, at least one extreme bounded solution of the
observable proximal outcome-bridge equations is not induced by any finite
latent negative-control causal model, and
\(\Theta_{\mathrm{lat}}(P)\subsetneq\Theta_{\mathrm{br}}(P)\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest prior CausalSmith comparator is
\texttt{eid\_proximal\_phase}, Section 8 Conjecture 1, which conjectured that
every rational \(h\in\mathcal H(P)\) is realized by a finite latent proximal
model and then marked realization as the main sharpness risk.  The closest
published comparators are \citet[abstract and Sections 2--3]{ZhangLiMiaoTchetgen2023},
which shows target means can be identified despite nonunique bridges, and
\citet[abstract and Sections 3--4]{GhassamiShpitserTchetgen2023}, which gives
partial-identification bounds after completeness failure.  The precise
flagship gap is the open-set nonrepresentability claim: neither published line
proves that observable bridge endpoints can be algebraically feasible yet
causally unattainable over a nondegenerate class of laws.  (b) Resolving this
would directly change the proximal partial-ID workflow of
\citet{GhassamiShpitserTchetgen2023} by requiring a realization defect report
before interpreting bridge-envelope bounds as sharp causal bounds.

\begin{conjecture}[Conjecture 2: binary witness generates a stable support gap (NOT YET PROVED)]\label{conj:binary-witness}
In the concrete binary law of Example~\ref{ex:binary-witness}, the upper
bridge-envelope endpoint violates a Farkas realization inequality by the margin
\(\eta_{\mathrm{BR}}\).  Moreover, every sufficiently small perturbation that
preserves Assumptions~\ref{ass:finite-positive}, \ref{ass:bridge-nonempty},
\ref{ass:latent-class}, \ref{ass:binary-boundary}, and
\ref{ass:witness-margin} keeps
\(\sigma_{\mathrm{br}}(1;P)-\sigma_{\mathrm{lat}}(1;P)>0\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) This is the concrete-witness counterpart to Conjecture~\ref{conj:generic-nonrealization}.
\citet{MiaoGengTchetgen2018} and \citet{CuiPuShiMiaoTchetgen2024} use
completeness or bridge regularity to avoid this boundary; \citet{BalkePearl1997}
supplies response-type sharpness logic in another causal design but not a
proximal bridge witness.  The epsilon-gap is a named finite law with a stable
support-function separation, not a hand-tuned degenerate bridge example.
(b) The consumer is the prior \texttt{pid\_mediation\_proxy} reviewer warning:
the witness gives a template for replacing assumed bridge realisability with a
primitive finite feasibility check.

\section{Sanity-check corollaries}
\begin{corollary}[Completeness singleton reduction]\label{cor:singleton}
If, in addition to Assumptions~\ref{ass:finite-positive} and
\ref{ass:bridge-nonempty}, each \(T_{a,x}\) is injective on bounded bridge
arrays, then \(\mathcal H_a(P)\) is a singleton for each arm.  In that case
\(\Theta_{\mathrm{br}}(P)\) is a singleton and Theorem~\ref{thm:farkas-frontier}
reduces to the usual proximal point-identification check: if the unique bridge
is realized by a finite negative-control model, then
\(\Delta_{\mathrm{BR}}(P)=0\) and
\(\Theta_{\mathrm{lat}}(P)=\Theta_{\mathrm{br}}(P)=\{\theta\}\).
\end{corollary}

\begin{corollary}[Manski no-proxy corner]\label{cor:manski}
If \(W\) and \(Z\) are independent of \(Y,A\) conditional on \(X\), the bridge
equations impose no target-relevant proxy restriction beyond \(Y\in[0,1]\).
Under Assumption~\ref{ass:latent-class}, the latent envelope then collapses to
the bounded-outcome Manski interval of \citet{Manski1990}, while any wider
bridge envelope has \(\Delta_{\mathrm{BR}}(P)>0\).  Thus the proposed frontier
does not create identification from irrelevant proxies.
\end{corollary}

\begin{example}[Concrete noncorner binary witness route]\label{ex:binary-witness}
Take \(X\) degenerate, \(P(A=1)=1/2\), and \(P(Z=z,W=w\mid A=a)=1/4\) for all
\((z,w,a)\), so \(T_a\) has rank one.  Let
\(m_1(0)=m_1(1)=1/2\), \(m_0(0)=m_0(1)=1/4\), and let the bridge-envelope upper
endpoint use \(h_1(1)=1,h_1(0)=0\) and \(h_0(1)=h_0(0)=1/4\).  The bridge
equations hold because only the proxy averages are observed.  The conjectured
Farkas certificate says that, after imposing the latent negative-control
bridge-realization equations, this \(h_1\) endpoint forces incompatible
conditional means for a shared latent proxy distribution, leaving a positive
support gap.  This is the explicit finite-support instance to be checked in
Stage 0 before promoting the generic open-class claim.
\end{example}

\section{Proof-sketch route}
Theorem~\ref{thm:farkas-frontier} reduces to finite-dimensional convex duality:
the bridge envelope is the image of a bounded polytope under \(L\), the latent
negative-control envelope is the image of a finite response-type polytope, and
Farkas' lemma characterizes when a bridge extreme point has a nonnegative
latent completion.  Conjecture~\ref{conj:binary-witness} requires an explicit
small-support enumeration for the binary witness in Example~\ref{ex:binary-witness},
including the dual certificate that separates the upper bridge endpoint from
the latent response-type polytope.  Conjecture~\ref{conj:generic-nonrealization}
then follows, if the witness certificate is strict, by continuity of support
functions and constant-rank perturbation of the bridge and response-type
constraint matrices.  The boundary cases that need explicit algebra are
rank changes in \(T_a\), zero proxy cells, and endpoints where the bounded
bridge polytope changes its active face.

\section{Honest scope flags}
Theorem~\ref{thm:farkas-frontier} is proposed as routine finite-dimensional
algebra once the latent feasibility matrix \(A_{\mathrm{NC}}(h)\) is written
out.  Conjectures~\ref{conj:generic-nonrealization} and
\ref{conj:binary-witness} are not proved; the main risk is that the binary
witness can be completed by a richer latent table, collapsing the support gap.
The proposal deliberately avoids claiming universal bridge realization, because
that was the hidden sharpness assumption flagged in prior reviews.  It also
does not claim a closed-form formula for \(\Delta_{\mathrm{BR}}(P)\) beyond the
finite support-function and Farkas-dual characterization.  The long-term ATE
language is represented here through persistent finite proxies and the terminal
outcome \(Y\); a fully longitudinal multi-wave theorem would be a later
extension, not part of this v1 kernel.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 3, replacing the exhausted
target-active-null, common-kernel, and selector-equivalence angles with a
finite bridge-envelope realization / nonrealization kernel; prior verdict:
none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Athey et~al.(2019)]{AtheyChettyImbensKang2019}
Athey, S., Chetty, R., Imbens, G., and Kang, H. (2019).
\newblock The surrogate index: Combining short-term proxies to estimate
long-term treatment effects more rapidly and precisely.
\newblock \emph{NBER Working Paper} No. 26463.

\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
\newblock Bounds on treatment effects from studies with imperfect compliance.
\newblock \emph{Journal of the American Statistical Association} 92(439),
1171--1176.

\bibitem[Canay et~al.(2013)]{CanaySantosShaikh2013}
Canay, I. A., Santos, A., and Shaikh, A. M. (2013).
\newblock On the testability of identification in some nonparametric models
with endogeneity.
\newblock \emph{Econometrica} 81(6), 2535--2559.

\bibitem[Cui et~al.(2024)]{CuiPuShiMiaoTchetgen2024}
Cui, Y., Pu, H., Shi, X., Miao, W., and Tchetgen Tchetgen, E. J. (2024).
\newblock Semiparametric proximal causal inference.
\newblock \emph{Journal of the American Statistical Association} 119(546),
1348--1359.

\bibitem[Ghassami et~al.(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E. J. (2023).
\newblock Partial identification with proxy variables.
\newblock \emph{arXiv preprint} arXiv:2304.04374.

\bibitem[Imbens et~al.(2025)]{ImbensKallusMaoWang2025}
Imbens, G., Kallus, N., Mao, X., and Wang, Y. (2025).
\newblock Long-term causal inference under persistent confounding via data
combination.
\newblock \emph{Journal of the Royal Statistical Society: Series B}.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review Papers and Proceedings} 80(2),
319--323.

\bibitem[Miao et~al.(2018)]{MiaoGengTchetgen2018}
Miao, W., Geng, Z., and Tchetgen Tchetgen, E. J. (2018).
\newblock Identifying causal effects with proxy variables of an unmeasured
confounder.
\newblock \emph{Biometrika} 105(4), 987--993.

\bibitem[Zhang et~al.(2024)]{ZhangLiMiaoTchetgen2023}
Zhang, J., Li, W., Miao, W., and Tchetgen Tchetgen, E. J. (2024).
\newblock Proximal causal inference without uniqueness of bridge functions.
\newblock \emph{Statistics and Probability Letters} 204, 110055.
\end{thebibliography}

\end{document}
