% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_bjs\_efficient\_event\_study, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_bjs\_efficient\_event\_study} / \texttt{v1}%
  \\ \large\textit{A spectral active-rank frontier for influence-function equivalence across BJS, Sun--Abraham, Callaway--Sant'Anna, and Wooldridge staggered-DiD estimators}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form panel anchor with tuple
\[
(\texttt{qid},\texttt{specialization},p,\text{assignment},\text{target},\text{regression})
\]
defined as follows.  \texttt{qid}=\texttt{eid\_bjs\_efficient\_event\_study};
\texttt{specialization}=\texttt{v1}; \(p=0\) absorbing-treatment event-study design
with no post-treatment carry-over beyond the event-time treatment effect matrix;
assignment is staggered adoption with first-treatment cohort \(G_i\in\mathcal G\),
never-treated or not-yet-treated controls allowed, cohort shares
\(\pi=(\pi_g)_{g\in\mathcal G}\), no anticipation, and unconditional parallel
trends for untreated outcomes; the target is a fixed scalar ATT aggregation
\(\theta_a=\sum_{g\in\mathcal G}\sum_{\ell\in\mathcal L}a_{g\ell}\tau_{g\ell}\)
over cohort-event cells with \(a_{g\ell}\ge 0\) and
\(\sum_{g,\ell}a_{g\ell}=1\); regression means the four named first-order
linear estimators: Borusyak--Jaravel--Spiess imputation, Sun--Abraham
interaction-weighted event-study, Callaway--Sant'Anna doubly robust group-time
ATT aggregation, and Wooldridge cohort-time-saturated TWFE/Mundlak regression.
The spectral boundary object is the integer active rank
\[
K_\star(\pi,\Sigma,a)=\operatorname{rank}\{H(\pi,\Sigma,a)\},
\]
where \(H(\pi,\Sigma,a)\) is the covariance-whitened observable pre-period
contrast kernel defined in Section~\ref{sec:setup}; equivalently
\(\sigma_{K_\star}(H)>0=\sigma_{K_\star+1}(H)\).  Thus \(K_\star\) is determined
by singular values, but is an integer rank threshold rather than a raw singular
value.

\begin{abstract}
Modern staggered-DiD papers now agree on how to identify interpretable
group-time and event-study ATT parameters under no anticipation and parallel
trends, but they do not give a sharp frontier for when the leading robust
estimators have the same first-order influence function.  This proposal asks
for a closed-form spectral condition under which the BJS imputation estimator,
Sun--Abraham interaction-weighted estimator, Callaway--Sant'Anna group-time
doubly robust aggregation, and Wooldridge saturated-TWFE implementation have
the same canonical normalized influence function for one fixed ATT aggregation.
The flagship
conjecture is that equivalence is governed by the row-space of an explicit
covariance-whitened pre-period contrast kernel \(H(\pi,\Sigma,a)\): rows of the
residualized heterogeneity matrix outside this active row-space force strict
first-order variance separation, while rows inside it collapse the four
estimators to the same canonical score.  The proposal deliberately formulates the rank
boundary as an integer active-rank certificate, avoiding the ill-posed shortcut
``rank less than a singular value.''  Resolving the conjecture would turn the
current estimator-choice discussion into a computable diagnostic based on
canonical normalized influence functions, cohort shares, pre-period covariance,
and the observed event-study design.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied researchers routinely choose among the BJS imputation estimator, the
Sun--Abraham interaction-weighted event-study estimator, Callaway--Sant'Anna
group-time ATT estimators, and Wooldridge saturated-regression implementations
after agreeing on the same no-anticipation and parallel-trends identifying
logic.  Point-identification agreement is not enough for inference: two
estimators can target the same written ATT aggregation while using different
nuisance projections, comparison sets, and estimated weights.  The methodological
question is therefore whether estimator choice is only a matter of presentation
or whether it changes the first-order variance in identifiable regions of
cohort-event treatment-effect heterogeneity.

\paragraph{The main finding (proposed).}
The headline result is Conjecture~\ref{conj:if-frontier}: the four canonical
normalized influence functions are equal if and only if every row of the
residualized heterogeneity matrix \(\Delta_\tau\) lies in the row-space admitted
by the covariance-whitened pre-period kernel \(H(\pi,\Sigma,a)\).  A companion
variance-gap conjecture states that outside this row-space, BJS attains the
fixed-design linear imputation benchmark while the other three estimator
classes pay an explicit projection-quadratic penalty in the heterogeneity
component orthogonal to \(\operatorname{row}(H)\).  The familiar
homogeneous-effects case appears as the rank-zero corner in
Theorem~\ref{thm:homogeneous-collapse}.

\paragraph{What is new.}
The novelty kernel is not another contamination decomposition and not another
proof that all four estimators identify ATT under parallel trends.  The proposed
object is an equality-of-influence-functions frontier: a necessary-and-sufficient
spectral certificate, computable from \(\pi\), \(\Sigma\), and the target
aggregation \(a\), that separates equivalence from strict variance
non-equivalence.  The closest published result is \citet{BorusyakJaravelSpiess2024},
which derives an efficient imputation estimator and restricted imputation/regression
equivalences, but it does not characterize when BJS has the same influence
function as Sun--Abraham, Callaway--Sant'Anna, or Wooldridge.  The precise
epsilon-gap is the passage from ``one estimator is efficient in its event-study
model'' to ``the four named estimators have equal canonical normalized influence
functions exactly on a computable active row-space, and strict variance
separation off it.''

\paragraph{How it positions in the literature.}
This is a panel and linear-projection methods proposal in the staggered-DiD
frontier.  It sits after the negative-weight and contamination results of
\citet{deChaisemartinDHaultfoeuille2020}, \citet{GoodmanBacon2021}, and
\citet{SunAbraham2021}, and after the interpretable group-time ATT framework of
\citet{CallawaySantAnna2021}.  It uses the efficiency perspective of
\citet{SantAnnaZhao2020}, \citet{RothSantAnna2023Efficient},
\citet{BorusyakJaravelSpiess2024}, and \citet{ChenSantAnnaXie2025}, but asks a
different question: when does the efficient score for a chosen ATT aggregation
coincide with the scores delivered by other robust staggered-DiD
implementations?

\paragraph{Implications for the community.}
The concrete downstream consumer is the estimator-choice guidance in
\citet{RothSantAnnaBilinskiPoe2023}: if the conjecture is resolved, their
recommendation to report robust DiD estimators can be sharpened into a diagnostic
that says when BJS, Sun--Abraham, Callaway--Sant'Anna, and Wooldridge are
first-order interchangeable and when an efficiency gap must be reported.

\paragraph{How research benefits from the conclusion.}
Researchers would report the active-rank residual
\(\|\Delta_\tau(I-\Pi_{\calH})\|_{\Sigma,\pi}\) before treating staggered-DiD
estimators as interchangeable for inference.

\section{Related work}
\citet{BorusyakJaravelSpiess2024} is the efficiency anchor: it develops robust
and efficient imputation for staggered event-study designs with unrestricted
treatment-effect heterogeneity and includes restricted equivalences between
imputation and Wooldridge-style regression implementations, but it does not give
an if-and-only-if four-estimator influence-function equivalence frontier across
BJS, Sun--Abraham, Callaway--Sant'Anna, and Wooldridge.  \citet{SunAbraham2021} is the
contamination anchor: it shows that lead-lag TWFE coefficients can load on
other-period effects and proposes interaction-weighted estimators, but it does
not compare their orthogonal-score subspace to BJS or CS.  \citet{CallawaySantAnna2021}
is the group-time ATT anchor: it separates identification of \(\operatorname{ATT}(g,t)\)
from aggregation and inference, but leaves equality of its influence function
with imputation and saturated-regression estimators unresolved.
\citet{Wooldridge2021} supplies the saturated TWFE/Mundlak implementation route
for staggered entry and heterogeneous effects, making it the regression
implementation comparator in this proposal.

\citet{GoodmanBacon2021} and \citet{deChaisemartinDHaultfoeuille2020} explain why
ordinary TWFE can produce nonconvex or misleading weighted averages under
heterogeneous treatment effects; their results motivate robust estimators but
do not settle efficiency equivalence among robust alternatives.
\citet{SantAnnaZhao2020} derives semiparametric efficiency bounds for two-period
DiD ATT parameters, which is the lower-dimensional efficiency benchmark for the
multi-period frontier considered here.  \citet{ChenSantAnnaXie2025} derives
closed-form efficient influence functions for modern DiD and event-study
parameters and emphasizes overidentification restrictions from multiple
pre-periods; this proposal asks when those restrictions change the efficient
score relative to named staggered-DiD implementations.
\citet{RothSantAnnaBilinskiPoe2023} synthesizes modern DiD practice and
foregrounds estimator-choice issues, which this proposal would convert into a
spectral diagnostic.  \citet{RothSantAnna2023Efficient} is the closest
published efficiency comparator: it studies staggered-rollout designs with
as-good-as-random rollout timing and derives a feasible efficient estimator,
using an optimal pre-treatment adjustment \(\beta^\star\), that weakly
dominates existing approaches, but it does not give an if-and-only-if row-space
frontier across the four parallel-trends estimators studied here.
\citet{Gardner2022} is the closest untreated-first construction comparator:
its two-stage DiD estimator estimates group and period effects from untreated
observations before estimating treatment effects, but it does not characterize
when that imputation-style projection shares the same canonical influence
function as BJS, Sun--Abraham, Callaway--Sant'Anna, and Wooldridge for a fixed
ATT aggregation.  \citet{BelleGoBenatiaDortetBernadet2025} extends efficiency
questions to unbalanced staggered panels; it is adjacent because unbalanced
missingness changes the same covariance and comparison-set objects that enter
\(H(\pi,\Sigma,a)\).

In-catalogue prior art is closest in the banked ThmSmith proposals
\texttt{panel\_honest\_did\_phase} and
\texttt{q1\_spectral\_phase\_transition}.  The former proposed a cohort-vs-aggregate
row-space frontier for Honest-DiD sensitivity and its reviewer requested a
generic computable operator certificate; the latter proposed a singular-value
phase-transition template for event-window visibility.  Neither proposal states
an asymptotic influence-function equivalence theorem across BJS, Sun--Abraham,
Callaway--Sant'Anna, and Wooldridge.  The relevant catalogue family is the
ThmSmith Panel section of \texttt{doc/API.md}, not AutoID SCM or graph
infrastructure.

\section{Formal setup}\label{sec:setup}
There are units \(i=1,\ldots,n\), periods \(t\in\{1,\ldots,T\}\), and absorbing
treatment \(D_{it}=\one\{t\ge G_i\}\) for first-treatment cohort
\(G_i\in\mathcal G\subseteq\{2,\ldots,T\}\cup\{\infty\}\).  Event time is
\(\ell=t-G_i\), and the target event window is a finite set \(\mathcal L\).
Potential outcomes satisfy no anticipation, so \(Y_{it}(0)\) is observed for
\(t<G_i\), and post-treatment causal effects are
\(\tau_{g\ell}=\E[Y_{i,g+\ell}(1)-Y_{i,g+\ell}(0)\mid G_i=g]\).  Let
\(\mathcal T=(\tau_{g\ell})_{g\in\mathcal G,\ell\in\mathcal L}\) and
\(\theta_a=\langle a,\mathcal T\rangle\) for fixed aggregation weights \(a\).

Let \(q\) be the number of treated cohorts entering \(a\), let \(r=|\mathcal L|\),
and let \(m\) be the number of untreated pre-period residual increments used by
the comparison system.  Let \(X_i\in\R^m\) be the vector of those untreated
pre-period residual increments after removing cohort and calendar means.  Write
\(\Sigma=\operatorname{Var}(X_i\mid D_i=0)\), assumed positive definite on its
support, and \(\pi_g=\Pr(G_i=g)\), normalized over the \(q\) treated cohorts in
the target.  Define \(R_\pi=I_q-\mathbf 1\pi^\transpose\), the cohort
residualizer.  The event-to-precontrast alignment map is
\(A_a\in\R^{r\times m}\); its \(j\)-th column records the signed event-time
weights induced by the target aggregation \(a\) for the \(j\)-th untreated
pre-period contrast.  Thus
\[
\Delta_\tau=R_\pi\mathcal T A_a\in\R^{q\times m}.
\]

The comparison-set convention is fixed once for all four estimators.  BJS uses
all untreated observations, including never-treated and not-yet-treated units,
to fit the untreated outcome path before imputation.  Sun--Abraham uses the
same never-treated/not-yet-treated comparison eligibility for each cohort-event
cell before applying the target weights \(a\).  Callaway--Sant'Anna uses the
same eligibility set for each group-time ATT and then aggregates with \(a\).
Wooldridge uses the cohort-time-saturated/Mundlak regression with the same
support and target weights.  Under this convention, the pre-period contrast
matrix is \(C_a\in\R^{q\times m}\), with row \(g\) equal to the signed
comparison weights that map \(X_i\) into the untreated counterfactual contrast
for cohort \(g\) and aggregation \(a\).  The observable pre-period contrast
kernel is
\[
H(\pi,\Sigma,a)=\operatorname{diag}(\pi)^{1/2} R_\pi C_a\Sigma^{-1/2}
\in\R^{q\times m}.
\]
Let \(\calH=\operatorname{row}\{H(\pi,\Sigma,a)\}\subseteq\R^m\), let
\(\Pi_{\calH}\) denote the Euclidean projection onto \(\calH\), and let
\[
K_\star(\pi,\Sigma,a)=\operatorname{rank}\{H(\pi,\Sigma,a)\}.
\]
For the smallest nontrivial three-period, two-treated-cohort design with one
post-treatment event cell and one pre-period residual contrast,
\[
\mathcal T=\begin{bmatrix}\tau_{2,0}\\ \tau_{3,0}\end{bmatrix},\quad
A_a=\begin{bmatrix}1\end{bmatrix},\quad
C_a=\begin{bmatrix}c_2\\ c_3\end{bmatrix},\quad
R_\pi=\begin{bmatrix}1-\pi_2&-\pi_3\\ -\pi_2&1-\pi_3\end{bmatrix},
\]
so \(H=\operatorname{diag}(\pi)^{1/2}R_\pi C_a\sigma^{-1/2}\) and the proposed
row-space condition is already a concrete one-dimensional contrast test.

For each estimator \(M\in\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}\),
let \(\widetilde\psi_M(\theta_a)\) be its canonical normalized influence
function for \(\theta_a\): \(\E[\widetilde\psi_M]=0\) and its pathwise
derivative with respect to the scalar target \(\theta_a\) is normalized to one.
Let \(\mathcal S_M=\operatorname{span}\{\widetilde\psi_M(\theta_a)\}\); equality
of \(\mathcal S_M\)'s below always means equality of the canonical normalized
scores, not equality up to an arbitrary nonzero scalar.  Write
\(V_M(a,\mathcal T)=\operatorname{Var}\{\widetilde\psi_M(\theta_a)\}\).

The efficiency benchmark used in Conjecture~\ref{conj:variance-gap} is not the
fully unrestricted semiparametric tangent model.  It is the fixed-design linear
parallel-trends benchmark \(\mathcal M_{\mathrm{LPT}}(a)\): iid unit-level
panels with finite cohort and time support, known event window, fixed
aggregation vector \(a\), fixed cohort shares \(\pi\), known comparison
covariance \(\Sigma\), absorbing adoption, no anticipation, unconditional
parallel trends for untreated increments, and the common comparison-support
convention above.  Admissible first-order perturbations vary the untreated
linear projections and cohort-event treatment-effect matrix while preserving
the fixed \((a,\pi,\Sigma,C_a)\) design.  Let
\(\psi_{\mathrm{BJS}\text{-}\mathrm{lin}}(\theta_a)\) be the canonical
influence function of the BJS generalized least-squares imputation estimator in
this benchmark, and define
\[
V_{\mathrm{BJS}\text{-}\mathrm{lin}}(a,\mathcal T)
=\operatorname{Var}\{\psi_{\mathrm{BJS}\text{-}\mathrm{lin}}(\theta_a)\}.
\]
This is the common known-covariance linear-efficiency object to which the BJS
Section~5.3 efficiency comparisons and the Roth--Sant'Anna optimal
pre-treatment adjustment benchmark are mapped below; it deliberately does not
assert a full unrestricted EIF bound.  For a conformable matrix \(B\), define
\(\|B\|_{\Sigma,\pi}^2=\operatorname{tr}\{B^\transpose \operatorname{diag}(\pi)B\Sigma^{-1}\}\)
after restriction to the support of \(\Sigma\).

Define the computable projection-loss term as follows.  Vectorize each
heterogeneity residual in row-major order, so
\(\operatorname{vec}(\Delta_\tau)\in\R^{qm}\), and let
\(\Omega_{\pi,\Sigma}=\operatorname{diag}(\pi)\otimes\Sigma^{-1}\in\R^{qm\times qm}\).
For each \(M\), let
\(Z_M(a,\pi,\Sigma)\in\R^{qm\times d_M}\) be the estimator-specific design
matrix, formed from that estimator's stated first-stage equations, whose
columns span the nuisance score directions used by estimator \(M\) under the
comparison-set convention above after vectorization.  Define the
\(\Omega_{\pi,\Sigma}\)-orthogonal projection \(P_M\in\R^{qm\times qm}\) by
\[
P_M=Z_M(Z_M^\transpose\Omega_{\pi,\Sigma}Z_M)^\dagger
Z_M^\transpose\Omega_{\pi,\Sigma}.
\]
With \(P_{\mathrm{BJS}}\) defined analogously, set
\[
\rho_M(a,\pi,\Sigma,\Delta_\tau)
=
\operatorname{vec}(\Delta_\tau)^\transpose
(P_M-P_{\mathrm{BJS}})^\transpose\Omega_{\pi,\Sigma}
(P_M-P_{\mathrm{BJS}})
\operatorname{vec}(\Delta_\tau).
\]
This is nonnegative by construction and is computable from the estimator design
matrices, \(\pi\), \(\Sigma\), and \(\Delta_\tau\); it is not defined by the
desired variance decomposition.

\begin{quote}
\begin{verbatim}
Locked parameters:
(qid, specialization, p, assignment, target, regression)
= (eid_bjs_efficient_event_study, v1, 0,
   absorbing staggered adoption with no anticipation and unconditional
   parallel trends, fixed scalar ATT aggregation theta_a over cohort-event
   cells, BJS / Sun-Abraham / Callaway-Sant'Anna / Wooldridge first-order
   linear staggered-DiD estimators).
K_star(pi,Sigma,a) = rank H(pi,Sigma,a), where H is the covariance-whitened
observable pre-period contrast kernel.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Absorbing staggered adoption and overlap]\label{ass:adoption}
Each unit has a first-treatment cohort \(G_i\), treatment is absorbing, and
\(\pi_g>0\) for every treated cohort entering the aggregation \(a\).  At every
cohort-event cell used by \(a\), there is a nonempty never-treated or
not-yet-treated comparison set.
\end{assumption}

\begin{assumption}[No anticipation]\label{ass:no-anticipation}
For all \(g\in\mathcal G\) and all \(t<g\), observed outcomes equal untreated
potential outcomes: \(Y_{it}=Y_{it}(0)\) conditional on \(G_i=g\).
\end{assumption}

\begin{assumption}[Unconditional parallel trends]\label{ass:parallel}
For all cohorts \(g,g'\) used in the comparison system and all untreated
pre/post increments needed by \(C_a\),
\[
\E\{Y_{it}(0)-Y_{i,t-1}(0)\mid G_i=g\}
=
\E\{Y_{it}(0)-Y_{i,t-1}(0)\mid G_i=g'\}.
\]
\end{assumption}

\begin{assumption}[Finite second moments and regular covariance]\label{ass:covariance}
The pre-period residual vector \(X_i\) has finite second moments, and
\(\Sigma=\operatorname{Var}(X_i\mid D_i=0)\) is positive definite on the support
used to form \(H(\pi,\Sigma,a)\).
\end{assumption}

\begin{assumption}[Common target aggregation]\label{ass:common-target}
All four estimators are evaluated for the same fixed scalar target
\(\theta_a=\sum_{g,\ell}a_{g\ell}\tau_{g\ell}\), with nonnegative weights
\(a_{g\ell}\) summing to one over identified cohort-event cells.
\end{assumption}

\begin{assumption}[Common comparison support and fixed design maps]\label{ass:design-maps}
The matrices \(A_a\), \(C_a\), and \(Z_M(a,\pi,\Sigma)\) are formed from the
comparison-set convention in Section~\ref{sec:setup}: never-treated and
not-yet-treated observations are eligible exactly when untreated for the
cohort-event cell, and all four estimators impose the same fixed aggregation
weights \(a\) after their estimator-specific first-stage projections.
\end{assumption}

\begin{assumption}[First-order linear regularity]\label{ass:regular}
The BJS, Sun--Abraham, Callaway--Sant'Anna, and Wooldridge implementations admit
asymptotically linear representations for \(\theta_a\) under the same sampling
sequence, and their nuisance estimators are regular enough that first-order
comparisons reduce to their orthogonal-score projections.
\end{assumption}

\begin{assumption}[Common linear-efficiency benchmark]\label{ass:eif-model}
The benchmark variance \(V_{\mathrm{BJS}\text{-}\mathrm{lin}}(a,\mathcal T)\)
is computed in the fixed-design linear parallel-trends model
\(\mathcal M_{\mathrm{LPT}}(a)\) from Section~\ref{sec:setup}.  Claims that BJS
attains the benchmark, or that another implementation has a variance gap
relative to it, are interpreted after expressing all four estimators'
influence functions in the same known-\((\pi,\Sigma,C_a,a)\) linear projection
quotient.  They are not claims about the fully unrestricted semiparametric
tangent space with unknown covariance or arbitrary distributional
perturbations.
\end{assumption}

\begin{assumption}[Homogeneous-effects corner]\label{ass:homogeneous}
For the sanity-check theorem only, \(\tau_{g\ell}=\tau_0\) for all
\((g,\ell)\) with \(a_{g\ell}>0\), so \(\Delta_\tau=0\).
\end{assumption}

\begin{assumption}[Homogeneous canonical weight equivalence]\label{ass:homogeneous-weights}
For the sanity-check theorem only, when Assumption~\ref{ass:homogeneous} holds,
the four implementations use the same fixed aggregation \(a\) and common
comparison support in a way that reduces their canonical normalized influence
functions to the common homogeneous ATT score \(\psi_0(a)\).  Equivalently, any
differences among their nuisance projections lie in the null space of the
homogeneous target score.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: homogeneous-effect target collapse]\label{thm:homogeneous-collapse}
Under Assumptions~\ref{ass:adoption}--\ref{ass:eif-model} and
Assumptions~\ref{ass:homogeneous}--\ref{ass:homogeneous-weights}, the
residualized heterogeneity component
\(\Delta_\tau\) is zero.  Consequently
\[
\mathcal S_{\mathrm{BJS}}=\mathcal S_{\mathrm{SA}}=\mathcal S_{\mathrm{CS}}=\mathcal S_{\mathrm{W}},
\]
with equality understood for canonical normalized influence functions, and the
four estimators have the same first-order asymptotic variance for \(\theta_a\).
Without Assumption~\ref{ass:homogeneous-weights}, the theorem records only the
target-side collapse \(\Delta_\tau=0\), not equality of implementation-specific
canonical scores.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is not the flagship advance; it records the required corner case after
making the homogeneous projection/weight-equivalence convention explicit.
\citet{SunAbraham2021}, \citet{CallawaySantAnna2021}, and \citet{Wooldridge2021}
all contain homogeneous-effect or saturation regimes in which robust
implementations agree, but they do not express that agreement as the rank-zero
limit of a spectral IF-frontier.  (b) The concrete consumer is
\citet{RothSantAnnaBilinskiPoe2023}: their applied guidance needs this reduction
so that the proposed diagnostic does not contradict the familiar homogeneous
benchmark.

\begin{conjecture}[Conjecture 1: spectral IF-equivalence frontier (NOT YET PROVED)]\label{conj:if-frontier}
Under Assumptions~\ref{ass:adoption}--\ref{ass:eif-model}, the following are
equivalent:
\begin{enumerate}[label=(\roman*)]
\item
\(\mathcal S_{\mathrm{BJS}}=\mathcal S_{\mathrm{SA}}=\mathcal S_{\mathrm{CS}}=\mathcal S_{\mathrm{W}}\)
for the common ATT aggregation \(\theta_a\), equivalently
\(\widetilde\psi_{\mathrm{BJS}}=\widetilde\psi_{\mathrm{SA}}
=\widetilde\psi_{\mathrm{CS}}=\widetilde\psi_{\mathrm{W}}\) almost surely under
the canonical normalization in Section~\ref{sec:setup};
\item
\(\Delta_\tau(I-\Pi_{\calH})=0\), where
\(\calH=\operatorname{row}\{H(\pi,\Sigma,a)\}\subseteq\R^m\), so
\(\Pi_{\calH}\) projects each row of \(\Delta_\tau\) in \(\R^m\);
\item
the covariance-whitened residual matrix
\(\operatorname{diag}(\pi)^{1/2}\Delta_\tau\) has no singular direction outside
the active row-space of \(H(\pi,\Sigma,a)\).
\end{enumerate}
In particular, if \(\operatorname{rank}(\Delta_\tau)>K_\star(\pi,\Sigma,a)\),
then the four canonical normalized influence functions cannot all be equal.  If
\(\operatorname{rank}(\Delta_\tau)\le K_\star(\pi,\Sigma,a)\), equivalence
requires the additional sharp alignment condition
\(\operatorname{row}(\Delta_\tau)\subseteq\calH\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest published paper is \citet{BorusyakJaravelSpiess2024}: it gives
an efficient imputation estimator, but not a necessary-and-sufficient equality
criterion comparing BJS with Sun--Abraham, Callaway--Sant'Anna, and Wooldridge.
\citet{ChenSantAnnaXie2025} gives closed-form EIFs for DiD/event-study
parameters, \citet{RothSantAnna2023Efficient} gives an efficient estimator for
staggered rollouts, and \citet{Gardner2022} gives an untreated-first two-stage
construction, but none collapses these four named parallel-trends
implementations to a single row-space certificate.  The epsilon-gap is the exact
operator frontier \(\Delta_\tau(I-\Pi_{\calH})=0\), not merely another estimator
or another ATT aggregation.  (b) The concrete consumer is the estimator-choice
problem in \citet{RothSantAnnaBilinskiPoe2023}: a resolved theorem would tell
applied researchers when reporting any one of the four estimators is
first-order equivalent and when estimator-specific variance reporting is
mandatory.

\begin{conjecture}[Conjecture 2: strict variance gap off the active row-space (NOT YET PROVED)]\label{conj:variance-gap}
Under Assumptions~\ref{ass:adoption}--\ref{ass:eif-model}, suppose
\(\Delta_\tau(I-\Pi_{\calH})\ne 0\).  Then BJS attains the fixed-design
linear imputation benchmark for \(\theta_a\),
\(V_{\mathrm{BJS}}(a,\mathcal T)
=V_{\mathrm{BJS}\text{-}\mathrm{lin}}(a,\mathcal T)\), while each
non-imputation implementation
\(M\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\) has asymptotic variance
\[
V_M(a,\mathcal T)-V_{\mathrm{BJS}}(a,\mathcal T)
=
\left\|\Delta_\tau(I-\Pi_{\calH})\right\|_{\Sigma,\pi}^2
\;+\;
\rho_M(a,\pi,\Sigma,\Delta_\tau),
\]
where \(\rho_M(a,\pi,\Sigma,\Delta_\tau)\ge 0\) is the projection quadratic form
defined in Section~\ref{sec:setup}.  It vanishes exactly when \(M\)'s nuisance
projection agrees with the BJS projection on the heterogeneity direction
\(\operatorname{vec}(\Delta_\tau)\).  Hence the variance gap is strictly
positive on an open set of heterogeneous-effect matrices with rank exceeding
\(K_\star(\pi,\Sigma,a)\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{SantAnnaZhao2020} provides two-period DiD efficiency bounds,
\citet{BorusyakJaravelSpiess2024} provides an efficient imputation benchmark,
and \citet{RothSantAnna2023Efficient} proves weak efficiency dominance in
staggered rollout designs through an optimal pre-treatment adjustment
\(\beta^\star\), but none gives a computable rank-gap variance formula for
these four parallel-trends estimators under the common
\(\mathcal M_{\mathrm{LPT}}(a)\) known-covariance linear benchmark.
\citet{Gardner2022} is close in projection geometry because it estimates
untreated fixed effects first, but it does not state the off-row-space loss
\(\rho_M(a,\pi,\Sigma,\Delta_\tau)\).  Relative to BJS Section~5.3 efficiency
comparisons and the Roth--Sant'Anna weak-dominance result, the new object is an
if-and-only-if active-row-space formula for when the comparator projection loss
is zero.  The epsilon-gap is strict non-equivalence on an open heterogeneity
class, with the magnitude tied to a computable residual norm and projection
quadratic form.  (b) The concrete consumer is BJS-style event-study practice in
\citet{BorusyakJaravelSpiess2024}: the theorem would justify when imputation is
not just robust but first-order more efficient than alternative robust
implementations for the same ATT aggregation.

\section{Sanity-check corollaries}
\begin{corollary}[Homogeneous ATT reduction]\label{cor:homogeneous}
Under Assumptions~\ref{ass:adoption}--\ref{ass:eif-model} and
Assumptions~\ref{ass:homogeneous}--\ref{ass:homogeneous-weights},
Conjecture~\ref{conj:if-frontier} reduces to
Theorem~\ref{thm:homogeneous-collapse}: since \(\Delta_\tau=0\),
\(\Delta_\tau(I-\Pi_{\calH})=0\) for every \(\pi\), \(\Sigma\), and \(a\), and
Assumption~\ref{ass:homogeneous-weights} supplies the implementation-side
canonical score equality.
\end{corollary}

\begin{corollary}[Two-period one-cohort neutrality]\label{cor:two-period}
In the two-period, one-treated-cohort design satisfying
Assumptions~\ref{ass:adoption}--\ref{ass:eif-model} and
Assumption~\ref{ass:homogeneous-weights}, with a single scalar post-treatment
cell, the treated-cohort residualizer is \(R_\pi=0\).  Hence
\(\Delta_\tau=0\) regardless of the scalar post-treatment ATT, and
Conjecture~\ref{conj:if-frontier} reduces to the canonical-score equality in
Theorem~\ref{thm:homogeneous-collapse}; the off-row-space premise of
Conjecture~\ref{conj:variance-gap} is absent rather than a disguised two-period
efficiency comparison.
\end{corollary}

\section{Proof-sketch route}
The verification route is finite-dimensional.  First express each estimator's
asymptotic linear representation for the same aggregation \(a\) as a common
ATT score plus an estimator-specific projection of untreated pre-period
residual moments.  Second, whiten the residual moments by \(\Sigma^{-1/2}\) and
apply the Frisch--Waugh--Lovell projection identity to identify the row-space
of nuisance scores retained by each estimator.  Third, show that all four
canonical normalized scores are equal exactly when every row of the residualized
heterogeneity matrix \(\Delta_\tau\) lies in the row-space of the common
pre-period contrast kernel \(H(\pi,\Sigma,a)\).  Fourth, compute the variance difference as the
\(\Omega_{\pi,\Sigma}\)-quadratic form generated by the difference between the
BJS projection \(P_{\mathrm{BJS}}\) and each comparator projection \(P_M\).  The
boundary cases needing explicit algebra are the smallest nontrivial staggered
design with three periods and two treated cohorts, and the singular design
where \(H\) loses one row because the pre-period covariance has a near-null
contrast.

\section{Honest scope flags}
Theorem~\ref{thm:homogeneous-collapse} is intended as routine algebra and a
sanity anchor.  Conjectures~\ref{conj:if-frontier} and
\ref{conj:variance-gap} are the novel kernel and are not yet proved.  The
proposal intentionally withdraws the literal phrase ``rank is less than the
smallest singular value'' because that is dimensionally ill-posed; the retained
claim is an integer active-rank boundary defined by the singular-value pattern
of \(H(\pi,\Sigma,a)\).  Version 2 narrows the equality language to canonical
normalized influence functions and defines the projection-loss term as an
explicit quadratic form.  Version 3 corrects the active-row-space residual to
the right projection \(\Delta_\tau(I-\Pi_{\calH})\) and pins the vectorized
dimensions of \(Z_M\) and \(P_M\).  Version 4 makes the homogeneous
projection/weight-equivalence condition explicit and defines the common
efficiency convention used before comparing BJS, Chen--Sant'Anna--Xie, and
Roth--Sant'Anna efficiency claims.  Version 5 narrows
Conjecture~\ref{conj:variance-gap} to the fixed-design linear parallel-trends
benchmark \(\mathcal M_{\mathrm{LPT}}(a)\) with known
\((\pi,\Sigma,C_a,a)\), withdrawing the stronger unrestricted semiparametric
EIF-bound reading.  The largest mathematical uncertainty is whether the
Sun--Abraham, Callaway--Sant'Anna, and Wooldridge nuisance projections require
extra regularity conditions on estimated aggregation weights or covariates even
after fixing the common comparison-support convention.

\section{Iteration trail}
\begin{itemize}
\item v1 (cold-start) --- initial draft with the flagship spectral
IF-equivalence frontier stated as Conjectures~\ref{conj:if-frontier} and
\ref{conj:variance-gap}; prior verdict: none.
\item v2 (revise) --- added Roth--Sant'Anna efficient-rollout and Gardner
two-stage comparisons, pinned \(A_a\), \(C_a\), canonical IF normalization, and
the projection-quadratic loss, and replaced the invalid two-period efficiency
corollary with a one-cohort neutrality reduction; prior verdict: REVISE.
\item v3 (revise) --- corrected active-row-space projection orientation to
\(\Delta_\tau(I-\Pi_{\calH})\), pinned \(Z_M\) and \(P_M\) dimensions after
vectorization, and clarified the gap beyond BJS restricted imputation/regression
equivalences; prior verdict: REVISE.
\item v4 (revise) --- added the homogeneous canonical weight-equivalence
condition and the common semiparametric tangent-space model for
\(V_{\mathrm{EIF}}\); prior verdict: REVISE.
\item v5 (revise) --- narrowed Conjecture~\ref{conj:variance-gap} from an
unrestricted semiparametric EIF-bound claim to the fixed-design
known-\((\pi,\Sigma,C_a,a)\) linear imputation benchmark
\(\mathcal M_{\mathrm{LPT}}(a)\); prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Belle'go, Benatia, and Dortet-Bernadet(2025)]{BelleGoBenatiaDortetBernadet2025}
Belle'go, C., D. Benatia, and V. Dortet-Bernadet.
\newblock Chained difference-in-differences.
\newblock \emph{Journal of Econometrics}, 2025.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{BorusyakJaravelSpiess2024}
Borusyak, K., X. Jaravel, and J. Spiess.
\newblock Revisiting event-study designs: robust and efficient estimation.
\newblock \emph{Review of Economic Studies}, 2024.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and P. H. C. Sant'Anna.
\newblock Difference-in-differences with multiple time periods.
\newblock \emph{Journal of Econometrics}, 225(2):200--230, 2021.

\bibitem[Chen, Sant'Anna, and Xie(2025)]{ChenSantAnnaXie2025}
Chen, X., P. H. C. Sant'Anna, and H. Xie.
\newblock Efficient difference-in-differences and event study estimators.
\newblock Cowles Foundation Discussion Paper / arXiv working paper, 2025.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{deChaisemartinDHaultfoeuille2020}
de Chaisemartin, C. and X. D'Haultfoeuille.
\newblock Two-way fixed effects estimators with heterogeneous treatment effects.
\newblock \emph{American Economic Review}, 110(9):2964--2996, 2020.

\bibitem[Gardner(2022)]{Gardner2022}
Gardner, J.
\newblock Two-stage differences in differences.
\newblock arXiv:2207.05943, 2022.  \url{https://arxiv.org/abs/2207.05943}.

\bibitem[Goodman-Bacon(2021)]{GoodmanBacon2021}
Goodman-Bacon, A.
\newblock Difference-in-differences with variation in treatment timing.
\newblock \emph{Journal of Econometrics}, 225(2):254--277, 2021.

\bibitem[Roth and Sant'Anna(2023)]{RothSantAnna2023Efficient}
Roth, J. and P. H. C. Sant'Anna.
\newblock Efficient estimation for staggered rollout designs.
\newblock \emph{Journal of Political Economy Microeconomics}, 1(4):669--709,
2023.  \url{https://doi.org/10.1086/726581}.

\bibitem[Roth, Sant'Anna, Bilinski, and Poe(2023)]{RothSantAnnaBilinskiPoe2023}
Roth, J., P. H. C. Sant'Anna, A. Bilinski, and J. Poe.
\newblock What's trending in difference-in-differences? A synthesis of the recent econometrics literature.
\newblock \emph{Journal of Econometrics}, 235(2):2218--2244, 2023.

\bibitem[Sant'Anna and Zhao(2020)]{SantAnnaZhao2020}
Sant'Anna, P. H. C. and J. Zhao.
\newblock Doubly robust difference-in-differences estimators.
\newblock \emph{Journal of Econometrics}, 219(1):101--122, 2020.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021}
Sun, L. and S. Abraham.
\newblock Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\newblock \emph{Journal of Econometrics}, 225(2):175--199, 2021.

\bibitem[Wooldridge(2021)]{Wooldridge2021}
Wooldridge, J. M.
\newblock Two-way fixed effects, the two-way Mundlak regression, and difference-in-differences estimators.
\newblock SSRN working paper 3906345, 2021.
\end{thebibliography}

\end{document}
