% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_bjs\_efficient\_event\_study, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_bjs\_efficient\_event\_study} / \texttt{v1}%
  \\ \large\textit{Aggregation-equivalent staggered DiD estimators need not be influence-function equivalent}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form panel / linear-projection proposal, not a Q1 pool-mode instance.
The locked tuple is
\[
  (\texttt{qid},\texttt{specialization},p,\texttt{assignment},\texttt{target},\texttt{regression})
\]
with \texttt{qid}=\texttt{eid\_bjs\_efficient\_event\_study}, \texttt{specialization}=\texttt{v1},
\(p=0\) (absorbing staggered adoption with no carry-over beyond exposure status), assignment
given by first-treatment cohort \(G_i\in\mathcal G\cup\{\infty\}\) and event time \(e=t-G_i\),
target \(\theta_a=\sum_{(g,t)\in\mathcal C} a_{gt}\operatorname{ATT}(g,t)\) for a fixed known
aggregation vector \(a\) over treated cohort-time cells \(\mathcal C=\{(g,t):t\ge g,\ g<\infty\}\),
and regression/estimation class equal to the four named staggered-DiD implementations:
Borusyak--Jaravel--Spiess imputation, Sun--Abraham interaction-weighted event study,
Callaway--Sant'Anna group-time doubly robust aggregation, and Wooldridge cohort-time-saturated
TWFE/Mundlak regression.  Untreated potential outcomes satisfy
\(\E[Y_{it}(0)\mid G_i]=\alpha_{G_i}+\lambda_t\) after conditioning on the cohort cells used by the
estimators.  Residual coordinates are embedded in the fixed coordinate set
\(\mathcal P=\{(h,s):h\in\mathcal G\cup\{\infty\},\ s\in\mathcal T_0(h)\}\), where
\(\mathcal T_0(h)=\{s:s<h\}\) for treated cohorts and \(\mathcal T_0(\infty)=\{1,\ldots,T\}\) for
never-treated cohorts, with finite covariance matrix \(\Sigma=\operatorname{Var}(R_i)\) for the
common vector \(R_i=(\one\{G_i=h\}(Y_{is}(0)-\alpha_h-\lambda_s))_{(h,s)\in\mathcal P}\).

\begin{abstract}
Modern staggered DiD papers give several estimators that can be written as targeting the same
aggregate ATT, but equality of the written estimand does not settle equality of their first-order
influence functions.  This proposal asks for a sharp finite-dimensional frontier separating
aggregation-equivalence from influence-function-equivalence for BJS imputation, Sun--Abraham
interaction-weighting, Callaway--Sant'Anna group-time aggregation, and Wooldridge saturated TWFE.
The kernel conjecture is that the boundary is a quotient row-space condition: after removing the
null directions of the target aggregation \(a\), the estimator-specific nuisance projection operators
must agree on the BJS efficient influence function, i.e. the canonical gradient.  The diagnostic is
not design-only: the operator
\(\Gamma_m(\pi,\Sigma,a)\) is built from observable design and covariance objects, while the boundary
condition also uses the identified population ATT vector \(\tau\).  Off this quotient-zero set, two
estimators can report the same \(\theta_a\) while having strictly different canonical influence
functions and asymptotic variances.  Resolving the conjecture would turn the current estimator-choice
discussion in staggered DiD into a computable plug-in diagnostic for when point-identification-equivalent
procedures are also efficiency-equivalent.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied researchers increasingly choose among robust staggered-DiD estimators by asking whether they
target the same ATT aggregation, but first-order inference depends on the influence function, not only
on the estimand label.  If two implementations agree on \(\theta_a\) while using different nuisance
projections, then equal point identification can mask unequal precision and different standard-error
behavior.

\paragraph{The main finding (proposed).}
The headline result is Conjecture~\ref{conj:quotient-frontier}: BJS, SA, CS, and Wooldridge are
influence-function equivalent for a fixed aggregate ATT if and only if their covariance-weighted
nuisance-loading differences vanish in the quotient by the target null space.  The proposal also
contains the routine linear-algebra theorem that aggregation equality alone is insufficient whenever
one of those quotient loadings is nonzero.

\paragraph{What is new.}
The novelty kernel is not another proof that the four estimators can identify interpretable
cohort-time ATTs.  The proposed advance is the missing \(\varepsilon\)-gap left by the restricted
equivalence statements already surrounding \citet{BorusyakJaravelSpiess2024}: BJS relates imputation
to familiar robust event-study, group-time, and regression implementations in special aligned designs,
while \citet{CallawaySantAnna2021} separates identification of \(\operatorname{ATT}(g,t)\) from
aggregation.  The new claim is that those boundary cases are shadows of a single quotient-IF
frontier: even when the aggregation vector \(a\) is fixed and all procedures target the same
\(\theta_a\), their canonical gradients coincide only under an additional identified row-space
restriction.

\paragraph{How it positions in the literature.}
This is a panel / linear-projection methods proposal in the modern staggered-DiD cluster.  It uses the
contamination and interaction-weighted estimand analysis of \citet{SunAbraham2021}, the group-time
ATT aggregation framework of \citet{CallawaySantAnna2021}, the imputation efficiency benchmark of
\citet{BorusyakJaravelSpiess2024}, and the cohort-time saturated regression implementation route of
\citet{Wooldridge2021}.  It is adjacent to recent semiparametric efficiency work by
\citet{SantAnnaZhao2020}, \citet{RothSantAnna2021Efficient}, and
\citet{ChenSantAnnaXie2025}, but asks a different comparison question: when do named estimators
for the same aggregate parameter share the same canonical influence function under the parallel-trends
staggered-DiD model rather than the randomized-rollout model?

\paragraph{Implications for the community.}
The direct consumer is the estimator-choice guidance synthesized by
\citet{RothSantAnnaBilinskiPoe2023}: their practitioner-facing distinction between assumptions,
estimands, and implementation would gain a fourth diagnostic, namely whether a chosen implementation
keeps or discards tangent-space directions that affect the variance of the reported aggregate ATT.

\paragraph{How research benefits from the conclusion.}
Researchers should report a quotient-projection diagnostic before treating BJS, SA, CS, and saturated
TWFE estimates for the same aggregate ATT as inferentially interchangeable.

\section{Related work}
\citet{BorusyakJaravelSpiess2024} derive a robust and efficient imputation estimator for staggered
event-study designs with unrestricted treatment-effect heterogeneity and discuss restricted
connections to other modern event-study implementations; they are the closest boundary-case anchor,
but they do not give necessary and sufficient conditions for BJS, Sun--Abraham, Callaway--Sant'Anna,
and Wooldridge influence functions to coincide for an arbitrary fixed aggregate ATT.
\citet{SunAbraham2021} show that conventional event-study TWFE coefficients can be contaminated by
effects from other relative periods and propose interaction-weighted estimands; their contribution
settles a point-identification and weighting problem rather than the IF-equivalence problem here.
\citet{CallawaySantAnna2021} identify group-time average treatment effects and aggregate them into
policy-relevant summaries; this proposal starts from their separation of \(\operatorname{ATT}(g,t)\)
and aggregation and asks whether equal aggregation implies equal canonical gradients.
\citet{Wooldridge2021} establishes saturated TWFE/Mundlak/pooled-OLS implementation equivalences for
staggered-entry designs; together with BJS's restricted regression equivalence discussion, it marks
the closest published implementation boundary, while the proposed theorem tests when such regression
equivalence is also influence-function equivalence.
\citet{AguilarLoyo2025} gives the most direct recent estimator-comparison paper: it connects the
extended TWFE estimand introduced by BJS and Wooldridge to a difference-in-differences estimand and
decomposes its meaningful-comparison and residual components.  That closes part of the estimand and
implementation comparison gap, but it does not derive equality of canonical gradients or a
semiparametric variance frontier across BJS, SA, CS, and Wooldridge for a fixed aggregate ATT.
\citet{GoodmanBacon2021} and \citet{deChaisemartinDHaultfoeuille2020} explain why ordinary TWFE can
use nonconvex or negative comparisons under heterogeneous effects; their weight-decomposition
warnings motivate, but do not subsume, a variance-frontier theorem for robust estimators.
\citet{SantAnnaZhao2020} derive semiparametric efficiency bounds for two-period DiD ATTs and show
when doubly robust estimators attain them; their two-period benchmark is a required sanity reduction
for the present staggered-panel proposal.
\citet{RothSantAnna2021Efficient} derive efficient estimators for staggered rollout designs under
as-if random treatment timing and show efficiency gains over popular alternatives; they are a close
efficiency-frontier comparator, but their rollout assignment model and estimator class do not give
the parallel-trends four-estimator quotient IF boundary proposed here.
\citet{ChenSantAnnaXie2025} derive closed-form efficient influence functions for modern DiD and
event-study parameters under sequential moment restrictions; their overidentification insight is the
closest published efficiency thread, but they do not compare BJS, SA, CS, and Wooldridge quotient
canonical-gradient subspaces for a fixed \(\theta_a\).
\citet{RothSantAnnaBilinskiPoe2023} synthesize modern DiD practice and highlight unresolved
implementation choices; this proposal supplies a candidate algebraic rule for one such choice.
\citet{Roth2026Interpreting} shows that modern DiD event-study plots can have different
pre-treatment visual behavior from traditional TWFE plots even in non-staggered timing; that plot
interpretation issue is separate from the canonical-gradient equality frontier, but it reinforces
that modern DiD procedures are not automatically interchangeable because their reported objects look
similar.
\citet{BellegoBenatiaDortetBernadet2025} study chained DiD in unbalanced panels and emphasize
efficiency gains from available comparison information; their setting is not the balanced-panel
kernel here, but it is a natural downstream stress test for the quotient-IF frontier.

In the ThmSmith catalogue, the Stage -1.1 gap scan reports no active proposal for
\texttt{eid\_bjs\_efficient\_event\_study}.  The closest in-repo prior proposal is
\texttt{panel\_honest\_did\_phase}, whose rejected angle asked for rank-phase and operator-certificate
frontiers for cohort-vs-aggregate sensitivity rather than for named estimator influence functions.
The downgraded \texttt{q1\_spectral\_phase\_transition} proposal gives a spectral row-space template
for event-window visibility, but it does not formulate a semiparametric efficiency or IF-equivalence
claim.  The \texttt{doc/API.md} panel entries therefore provide catalogue context, not a duplicate of
the proposed quotient-IF theorem.

\section{Formal setup}
Let \(i=1,\ldots,n\) index units and \(t=1,\ldots,T\) index periods.  Treatment is absorbing:
\(D_{it}=\one\{t\ge G_i\}\) for first-treatment cohort \(G_i\in\mathcal G\cup\{\infty\}\), where
\(\infty\) denotes never-treated units.  For treated cohort-time cells
\(\mathcal C=\{(g,t):g\in\mathcal G,\ t\ge g\}\), define
\[
  \tau_{gt}=\operatorname{ATT}(g,t)=\E[Y_{it}(1)-Y_{it}(0)\mid G_i=g],
  \qquad
  \theta_a=\sum_{(g,t)\in\mathcal C}a_{gt}\tau_{gt}.
\]
Write \(\tau\in\R^{|\mathcal C|}\) for the stacked heterogeneity vector and
\(\pi_g=\Pr(G_i=g)\) for cohort shares.  The untreated response surface is
\(\E[Y_{it}(0)\mid G_i=g]=\alpha_g+\lambda_t\).  To make cohort-specific pre-period lengths
comparable, define the fixed residual coordinate set
\[
  \mathcal P=\{(h,s):h\in\mathcal G\cup\{\infty\},\ s\in\mathcal T_0(h)\},
  \qquad
  \mathcal T_0(h)=\{s:s<h\},\quad
  \mathcal T_0(\infty)=\{1,\ldots,T\}.
\]
The common residual vector is
\[
  R_i=\bigl(\one\{G_i=h\}(Y_{is}(0)-\alpha_h-\lambda_s)\bigr)_{(h,s)\in\mathcal P}
  \in\R^{|\mathcal P|},
\]
so never-treated and not-yet-treated comparison residuals occupy named coordinates and unavailable
cohort-period cells are absent rather than padded ambiguously.  Let
\(\Sigma=\operatorname{Var}(R_i)\), interpreted on its active pre-period residual span.  Each estimator
\(m\in\mathcal M=\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}\) is represented by an
asymptotically linear influence function
\[
  \psi_m(W_i;\theta_a)
    = \psi_{\mathrm{BJS}}(W_i;\theta_a)
      + \langle \Gamma_m(\pi,\Sigma,a),\,\tau\rangle_{\Sigma^{-1}}(R_i),
\]
where \(\Gamma_{\mathrm{BJS}}=0\), and
\(\Gamma_m(\pi,\Sigma,a)\in\R^{|\mathcal P|\times|\mathcal C|}\) is the design-and-covariance
nuisance-loading contrast between estimator \(m\)'s canonical gradient and the BJS canonical gradient
after quotienting
by the null space of the target aggregation \(a\) and projecting onto the active residual span.  The
proposal uses a raw-loading convention: \(\Gamma_m\tau\) is expressed in the same coordinates as
\(R_i\), and all covariance weighting enters through \(\Sigma^{+}\), not through a transformed
version of \(\Gamma_m\).  Here
\(\langle \Gamma_m,\tau\rangle_{\Sigma^{-1}}(R_i)\) denotes the scalar residual loading
\((\Gamma_m\tau)^\transpose \Sigma^{+}R_i\), where \(\Sigma^{+}\) is the inverse on the active span
and zero on its orthogonal complement.  Let
\(\mathcal V_m=\operatorname{Var}(\psi_m(W_i;\theta_a))\).  The exact construction of
\(\Gamma_m\) is the conjectural object of the proposal: it should be computable from cohort shares,
pre-period covariance blocks, the aggregation vector, and the published estimator comparison sets.
The intended Stage~0 recipe is concrete.  Form the comparison-set incidence matrix \(B_m\) for
estimator \(m\), residualize \(B_m\) against unit, time, cohort, and event-time nuisance columns using
the FWL projection \(M_m\), pass the treated-cell loadings through the target quotient
\(Q_a=I-a(a^\transpose a)^{+}a^\transpose\), project the resulting residual loading onto the active
span of \(R_i\), and set \(\Gamma_m\) to that raw loading difference relative to BJS.  No additional
covariance transform is folded into \(\Gamma_m\); the IF scalar is always
\((\Gamma_m\tau)^\transpose\Sigma^{+}R_i\) and the variance norm is
\((\Gamma_m\tau)^\transpose\Sigma^{+}(\Gamma_m\tau)\).
The smallest worked check is the three-period, two-treated-cohort design, where the single
post-treatment late-cohort cell produces one nontrivial FWL residual column and the condition
\(\Gamma_m\tau=0\) can be verified by direct \(2\times 2\) block algebra.
The frontier condition \(\Gamma_m(\pi,\Sigma,a)\tau=0\) is therefore an identified population
condition, using the ATT vector \(\tau\) identified under the DiD assumptions; empirical use would
replace \((\pi,\Sigma,\tau)\) by consistent plug-in estimates.  For later reductions,
define the active column support
\[
  \mathcal C_\Gamma=\{c\in\mathcal C:\text{some entry of the \(c\)-th column of }
  \Gamma_m(\pi,\Sigma,a)\text{ is nonzero for some }m\}.
\]

\begin{quote}
\begin{verbatim}
Locked tuple:
qid = eid_bjs_efficient_event_study
specialization = v1
p = 0
assignment = absorbing staggered adoption by cohort G_i and event time e=t-G_i
target = theta_a = sum_(g,t in C) a_gt ATT(g,t), fixed known aggregation a
regression = BJS imputation, SA interaction-weighted, CS group-time DR aggregation,
             and Wooldridge cohort-time-saturated TWFE/Mundlak regression
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Absorbing staggered adoption]\label{ass:absorbing}
For each unit \(i\), \(D_{it}=\one\{t\ge G_i\}\) with \(G_i\in\mathcal G\cup\{\infty\}\), and every
treated cohort \(g\in\mathcal G\) has \(\pi_g=\Pr(G_i=g)>0\).
\end{assumption}

\begin{assumption}[No anticipation]\label{ass:no-anticipation}
For all \(g\in\mathcal G\) and \(t<g\), \(Y_{it}=Y_{it}(0)\) for units with \(G_i=g\).
\end{assumption}

\begin{assumption}[Cohort parallel trends]\label{ass:parallel}
There exist \((\alpha_g)_{g\in\mathcal G\cup\{\infty\}}\) and \((\lambda_t)_{t=1}^T\) such that
\(\E[Y_{it}(0)\mid G_i=g]=\alpha_g+\lambda_t\) for all cohorts and periods used in the four
estimators.
\end{assumption}

\begin{assumption}[Overlap for comparison cells]\label{ass:overlap}
Every cohort-time contrast used by BJS, SA, CS, or Wooldridge has a comparison cohort with positive
probability and well-defined untreated potential-outcome mean under Assumptions~\ref{ass:no-anticipation}
and~\ref{ass:parallel}.
\end{assumption}

\begin{assumption}[Regular covariance]\label{ass:regular-covariance}
The fixed-coordinate residual vector \(R_i\in\R^{|\mathcal P|}\) has finite second moments, and
\(\Sigma=\operatorname{Var}(R_i)\) is positive definite on the active residual span generated by the
comparison cells used by BJS, SA, CS, and Wooldridge.  All products
\(\Gamma_m(\pi,\Sigma,a)\tau\) are elements of this same coordinate space.
\end{assumption}

\begin{assumption}[Common target aggregation]\label{ass:common-target}
The four estimator implementations are normalized to the same fixed aggregation vector
\(a\in\R^{|\mathcal C|}\), so their probability limits equal \(\theta_a\) whenever the identifying
assumptions hold.
\end{assumption}

\begin{assumption}[Canonical asymptotic linearity]\label{ass:asym-linear}
For each \(m\in\mathcal M\), the estimator admits a first-order influence function
\(\psi_m(W_i;\theta_a)\) in the finite-dimensional panel model above.  The representative is fixed
by the canonical quotient normalization used in the setup: residual-loading components are projected
onto the active span of \(R_i\), target-null directions are removed, and no additional mean-zero null
component may be added after this normalization.  Two estimators are influence-function equivalent when
these canonical representatives are equal in \(L_2(P)\).
\end{assumption}

\begin{assumption}[BJS canonical-gradient orthogonality]\label{ass:bjs-orthogonality}
The BJS influence function \(\psi_{\mathrm{BJS}}(W_i;\theta_a)\) is the efficient influence
function, equivalently the canonical gradient, for \(\theta_a\) in the tangent space of the model
under consideration.  Its residual component is the tangent-space projection orthogonal in \(L_2(P)\)
to the quotient nuisance-loading contrasts
\(\langle \Gamma_m(\pi,\Sigma,a),\tau\rangle_{\Sigma^{-1}}(R_i)\) for
\(m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).
\end{assumption}

\begin{assumption}[Active-column homogeneous corner]\label{ass:active-column-homogeneous}
For each \(m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\),
\(\Gamma_m(\pi,\Sigma,a)\mathbf 1_{\mathcal C}=0\), where
\(\mathbf 1_{\mathcal C}\in\R^{|\mathcal C|}\) is the constant-effect vector over all cohort-time
effect cells.  Zero-weight cells with \(a_{gt}=0\) are not silently ignored: if such a cell has a
nonzero column in any \(\Gamma_m\), it is part of the active homogeneous-effect support.
\end{assumption}

\begin{assumption}[Homogeneous active effects]\label{ass:homogeneous-active-effects}
For the homogeneous-effect reduction only, there exists a scalar \(\theta\) such that
\(\tau_{gt}=\theta\) for every \((g,t)\in\mathcal C_\Gamma\), and the common target aggregation is
normalized by \(\sum_{(g,t)\in\mathcal C}a_{gt}=1\).
\end{assumption}

\begin{assumption}[Two-period canonical reduction]\label{ass:two-period-canonical}
For the two-period sanity reduction only, \(T=2\), each treated group has one post-treatment cell,
and the four implementations reduce to the same two-period ATT contrast under no anticipation and
parallel trends.
\end{assumption}

\section{Main results}
\begin{theorem}[Aggregation equality is not an IF equality certificate]\label{thm:aggregation-not-if}
Under Assumptions~\ref{ass:absorbing}--\ref{ass:bjs-orthogonality}, suppose two estimators
\(m,m'\in\mathcal M\) have the same probability limit \(\theta_a\).  Define
\[
  \delta_m(W_i)=\langle \Gamma_m(\pi,\Sigma,a),\tau\rangle_{\Sigma^{-1}}(R_i),
  \qquad
  \delta_{m'}(W_i)=\langle \Gamma_{m'}(\pi,\Sigma,a),\tau\rangle_{\Sigma^{-1}}(R_i).
\]
If
\[
  \operatorname{Var}\!\left(
    \delta_m(W_i)-\delta_{m'}(W_i)
  \right)>0,
\]
then the canonical representatives fixed by Assumption~\ref{ass:asym-linear} are not equal in
\(L_2(P)\), so \(m\) and \(m'\) are not influence-function equivalent.  Their variance difference is exactly
\[
  \mathcal V_m-\mathcal V_{m'}
    =\operatorname{Var}(\delta_m)-\operatorname{Var}(\delta_{m'})
      +2\operatorname{Cov}\!\left(\psi_{\mathrm{BJS}},\delta_m-\delta_{m'}\right),
\]
so strict variance inequality holds if and only if the right-hand side is nonzero.  In the special
comparison \(m'=\mathrm{BJS}\), Assumption~\ref{ass:bjs-orthogonality} gives
\(\mathcal V_m-\mathcal V_{\mathrm{BJS}}=\operatorname{Var}(\delta_m)>0\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest published paper is \citet{BorusyakJaravelSpiess2024}, which directly motivates
efficient imputation and gives restricted equivalence and precision comparisons against familiar
robust event-study and regression alternatives, but does not state an exact canonical
variance-difference identity for BJS, SA, CS, and Wooldridge after a common \(\theta_a\)
normalization.  The \(\varepsilon\)-gap is that BJS establishes an efficiency benchmark and special
implementation coincidences, whereas this result isolates the quotient-IF term that makes
aggregation-equivalent estimators first-order different outside those coincidences.  (b) Resolving
and using this theorem gives the
\citet{RothSantAnnaBilinskiPoe2023} estimator-choice synthesis a concrete warning: identical reported
ATT weights do not by themselves justify treating robust staggered-DiD standard errors as
interchangeable.

\begin{conjecture}[Quotient row-space IF frontier (NOT YET PROVED)]\label{conj:quotient-frontier}
Under Assumptions~\ref{ass:absorbing}--\ref{ass:bjs-orthogonality}, there exist explicit
design-and-covariance matrices
\[
  \Gamma_m(\pi,\Sigma,a),\qquad m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\},
\]
constructed from cohort shares, pre-period covariance blocks, comparison-set incidence matrices, and
the aggregation vector \(a\).  For the identified population ATT vector \(\tau\), BJS and estimator
\(m\) are influence-function equivalent for \(\theta_a\) if and only if
\[
  \Gamma_m(\pi,\Sigma,a)\tau=0.
\]
All four estimators are influence-function equivalent if and only if
\[
  \tau\in
  \bigcap_{m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}}\ker \Gamma_m(\pi,\Sigma,a).
\]
When this condition fails for at least one \(m\), the asymptotic variance gap relative to BJS is the
raw-loading covariance squared quotient norm
\[
  \mathcal V_m-\mathcal V_{\mathrm{BJS}}
    =
    \|\Gamma_m(\pi,\Sigma,a)\tau\|_{\Sigma^{-1}}^2
    + 2\,\operatorname{Cov}\!\left(\psi_{\mathrm{BJS}},
      \langle \Gamma_m(\pi,\Sigma,a),\tau\rangle_{\Sigma^{-1}}(R_i)\right),
\]
with the covariance term vanishing under the canonical-gradient orthogonality normalization.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published efficiency and comparison anchors are \citet{BorusyakJaravelSpiess2024},
\citet{AguilarLoyo2025}, \citet{RothSantAnna2021Efficient}, and \citet{ChenSantAnnaXie2025}.
BJS gives an efficient imputation estimator and restricted equivalence statements tying imputation to
other implementations in special cases; Aguilar-Loyo gives a direct extended-TWFE versus DiD
estimand decomposition, but not a canonical-gradient comparison; Roth--Sant'Anna derive efficient
staggered-rollout estimators under as-if random timing; and Chen--Sant'Anna--Xie derive closed-form
EIFs for modern DiD/event-study parameters.  None states the necessary and sufficient identified
quotient row-space condition under which SA, CS, and Wooldridge share BJS's canonical influence
function for the same parallel-trends aggregate \(\theta_a\).  The \(\varepsilon\)-gap is the
cross-estimator IF-equivalence frontier beyond BJS's restricted equivalence cases and
Aguilar-Loyo's estimand decomposition, not another derivation of a single estimator's EIF, a
randomized-rollout efficiency bound, or an implementation-equivalence formula.  (b) The concrete
consumer is empirical staggered-DiD practice in the style surveyed by
\citet{RothSantAnnaBilinskiPoe2023}: the matrices \(\Gamma_m\) would let applied researchers diagnose
whether switching among BJS, SA, CS, and saturated TWFE is merely a weighting convention or an
efficiency-relevant change.

\begin{theorem}[Homogeneous-effect reduction]\label{thm:homogeneous-reduction}
Under Assumptions~\ref{ass:absorbing}--\ref{ass:bjs-orthogonality},
Assumption~\ref{ass:active-column-homogeneous}, and
Assumption~\ref{ass:homogeneous-active-effects}, every
quotient-loading contrast annihilates the heterogeneity vector:
\[
  \Gamma_m(\pi,\Sigma,a)\tau=0\quad\text{for all }m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}.
\]
Consequently, Conjecture~\ref{conj:quotient-frontier} recovers the standard homogeneous-effects
equivalence corner case.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) Homogeneous-effect equivalence is not new; it is the sanity corner implicit in
\citet{SunAbraham2021}, \citet{CallawaySantAnna2021}, and \citet{Wooldridge2021}.  Its role here is to
pin the quotient operator so that the proposed frontier does not create artificial non-equivalence
when no heterogeneity direction exists.  (b) The concrete consumer is the
\citet{GoodmanBacon2021} and \citet{deChaisemartinDHaultfoeuille2020} warning literature: the theorem
shows that the proposed diagnostic switches on only when heterogeneous-effect tangent-space directions are
actually present.

\section{Sanity-check corollaries}
\begin{corollary}[Homogeneous-effects corner]\label{cor:homogeneous}
Under Assumptions~\ref{ass:absorbing}--\ref{ass:bjs-orthogonality},
Assumption~\ref{ass:active-column-homogeneous}, and
Assumption~\ref{ass:homogeneous-active-effects}, Conjecture~\ref{conj:quotient-frontier} reduces to
equality of the four IFs because \(\tau=\theta\mathbf 1_{\mathcal C}\) on
\(\mathcal C_\Gamma\) and \(\Gamma_m(\pi,\Sigma,a)\mathbf 1_{\mathcal C}=0\).
\end{corollary}

\begin{corollary}[Two-period DiD corner]\label{cor:two-period}
Under Assumptions~\ref{ass:no-anticipation}, \ref{ass:parallel}, \ref{ass:asym-linear}, and
\ref{ass:two-period-canonical}, the fixed residual coordinate set \(\mathcal P\) can still be nonempty,
but the active quotient-loading columns vanish: \(\Gamma_m(\pi,\Sigma,a)\tau=0\) for every
\(m\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).  In the one-post-cell quotient, each implementation
places the same canonical coefficient on the treated-minus-comparison change, and the remaining
pre-period residual direction is target-null and removed by Assumption~\ref{ass:asym-linear}.  The
remaining canonical gradient is the usual two-period ATT influence function, so the frontier collapses to the
\citet{SantAnnaZhao2020} two-period ATT efficiency comparison.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is finite-dimensional Hilbert-space projection algebra.  First write each
published estimator's first-order expansion as a common cohort-time ATT influence function plus an
estimator-specific projection of the pre-period residual coordinates.  Then quotient the tangent
space by the null space of the
fixed aggregation \(a\), apply the \(\Sigma^{+}\) inner product on the fixed residual coordinates,
and identify the loading contrasts
\(\Gamma_m\) by FWL residualization of the comparison-set incidence matrices.  The non-equivalence
part follows from positive definiteness of the covariance inner product, while the sharp frontier
requires checking that the constructed quotient loadings are not merely sufficient but necessary for
IF equality.  The boundary cases needing explicit algebra are the smallest nontrivial staggered design
with three periods and two treated cohorts, the homogeneous-effect rank-zero corner, and the two-period
collapse to the classical ATT DiD influence function.

\section{Honest scope flags}
Conjecture~\ref{conj:quotient-frontier} is not yet proved; the main open issue is necessity of the
specific \(\Gamma_m(\pi,\Sigma,a)\) construction for all three non-BJS estimators.  The diagnostic is
identified-plug-in rather than design-only: \(\Gamma_m\) uses design and covariance inputs, while
membership in \(\ker\Gamma_m\) also requires the identified ATT vector \(\tau\).  Theorem~\ref{thm:aggregation-not-if}
is routine once the canonical influence-function representation is accepted, and
Theorem~\ref{thm:homogeneous-reduction} is a normalization sanity check rather than a new published
claim.  This pivot deliberately withdraws the earlier spectral-threshold-only \(K_\star\) framing:
a bare singular-value boundary risks duplicating generic trust-region or row-space geometry unless it
is tied to named estimator influence functions.  The proposal assumes balanced panels and known
aggregation weights; unbalanced panels and estimated data-adaptive weights are left for a separate
frontier, with \citet{BellegoBenatiaDortetBernadet2025} as the natural stress test.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for seed index 2, reframing the angle around aggregation-equivalent
but IF-non-equivalent staggered-DiD estimators; prior verdict: none.
\item v2 (revise) -- patched fixed residual coordinates, exact variance-difference identity,
active-column homogeneous reduction, and Roth--Sant'Anna efficiency-frontier comparison; prior
verdict: REVISE.
\item v3 (revise) -- fixed canonical IF equivalence modulo null components, foregrounded BJS restricted
equivalence as closest prior art, clarified the identified plug-in status of the \(\Gamma_m\tau\)
frontier, and replaced the two-period zero-row claim by a zero-active-loading reduction; prior
verdict: REVISE.
\item v4 (revise) -- added Aguilar-Loyo's 2025 TWFE comparison and Roth's 2026 event-study
interpretation note to the literature separation, replaced efficient-influence-function language with
canonical-gradient / tangent-space projection language, and made the \(\Gamma_m\) recipe more
concrete; prior verdict: REVISE.
\item v5 (revise) -- fixed the \(\Gamma_m\) scaling convention by choosing raw residual loadings with
all covariance weighting carried by \(\Sigma^{+}\), so the IF scalar and variance norm use the same
coordinate system, and made the sanity-reduction hypotheses explicit in §7; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Borusyak, Jaravel, and Spiess(2024)]{BorusyakJaravelSpiess2024}
Borusyak, K., Jaravel, X., and Spiess, J. (2024).
Revisiting event-study designs: Robust and efficient estimation.
\emph{Review of Economic Studies}, 91(6):3253--3285.
\url{https://doi.org/10.1093/restud/rdae007}.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021}
Sun, L. and Abraham, S. (2021).
Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\emph{Journal of Econometrics}, 225(2):175--199.
\url{https://doi.org/10.1016/j.jeconom.2020.09.006}.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and Sant'Anna, P. H. C. (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics}, 225(2):200--230.
\url{https://doi.org/10.1016/j.jeconom.2020.12.001}.

\bibitem[Wooldridge(2021)]{Wooldridge2021}
Wooldridge, J. M. (2021).
Two-way fixed effects, the two-way Mundlak regression, and difference-in-differences estimators.
SSRN working paper.
\url{https://doi.org/10.2139/ssrn.3906345}.

\bibitem[Aguilar-Loyo(2025)]{AguilarLoyo2025}
Aguilar-Loyo, J. (2025).
A comparative analysis of two-way fixed effects estimators in staggered treatment designs.
\emph{Journal of Econometrics}, 251:106059.
\url{https://doi.org/10.1016/j.jeconom.2025.106059}.

\bibitem[Goodman-Bacon(2021)]{GoodmanBacon2021}
Goodman-Bacon, A. (2021).
Difference-in-differences with variation in treatment timing.
\emph{Journal of Econometrics}, 225(2):254--277.
\url{https://doi.org/10.1016/j.jeconom.2021.03.014}.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{deChaisemartinDHaultfoeuille2020}
de Chaisemartin, C. and D'Haultfoeuille, X. (2020).
Two-way fixed effects estimators with heterogeneous treatment effects.
\emph{American Economic Review}, 110(9):2964--2996.
\url{https://doi.org/10.1257/aer.20181169}.

\bibitem[Sant'Anna and Zhao(2020)]{SantAnnaZhao2020}
Sant'Anna, P. H. C. and Zhao, J. (2020).
Doubly robust difference-in-differences estimators.
\emph{Journal of Econometrics}, 219(1):101--122.
\url{https://doi.org/10.1016/j.jeconom.2020.06.003}.

\bibitem[Roth and Sant'Anna(2023)]{RothSantAnna2021Efficient}
Roth, J. and Sant'Anna, P. H. C. (2023).
Efficient estimation for staggered rollout designs.
\emph{Journal of Political Economy Microeconomics}, 1(4):669--709.
\url{https://doi.org/10.1086/726581}.

\bibitem[Chen, Sant'Anna, and Xie(2025)]{ChenSantAnnaXie2025}
Chen, X., Sant'Anna, P. H. C., and Xie, H. (2025).
Efficient difference-in-differences and event study estimators.
arXiv:2506.17729.
\url{https://arxiv.org/abs/2506.17729}.

\bibitem[Roth, Sant'Anna, Bilinski, and Poe(2023)]{RothSantAnnaBilinskiPoe2023}
Roth, J., Sant'Anna, P. H. C., Bilinski, A., and Poe, J. (2023).
What's trending in difference-in-differences? A synthesis of the recent econometrics literature.
\emph{Journal of Econometrics}, 235(2):2218--2244.
\url{https://doi.org/10.1016/j.jeconom.2023.03.008}.

\bibitem[Roth(2026)]{Roth2026Interpreting}
Roth, J. (2026).
Interpreting event-studies from recent difference-in-differences methods.
\emph{The Japanese Economic Review}, 77(2):275--288.
\url{https://doi.org/10.1007/s42973-026-00235-x}.

\bibitem[Bellego, Benatia, and Dortet-Bernadet(2025)]{BellegoBenatiaDortetBernadet2025}
Bellego, C., Benatia, D., and Dortet-Bernadet, V. (2025).
The chained difference-in-differences.
\emph{Journal of Econometrics}, 247:105783.
\url{https://doi.org/10.1016/j.jeconom.2024.105783}.
\end{thebibliography}

\end{document}
