% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_bjs\_efficient\_event\_study, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_bjs\_efficient\_event\_study} / \texttt{v1}%
  \\ \large\textit{Estimator-specific score-certificate ranks as the efficiency boundary in staggered DiD event studies}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form panel / linear-projection proposal, not a Q1 pool-mode
instance.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},p,\texttt{assignment},\texttt{target},
\texttt{regression})
\]
with the following meanings.  \texttt{qid} is
\texttt{eid\_bjs\_efficient\_event\_study}; \texttt{specialization} is
\texttt{v1}.  The memory parameter is \(p=T-1\): every pre-treatment outcome
period available before a cohort's adoption date is admissible as a
pre-period moment, and no post-treatment outcome is used to estimate untreated
potential-outcome trends for treated cells.  The assignment is absorbing
staggered adoption with cohort \(G_i\in\{2,\ldots,T,\infty\}\), fixed cohort
share vector \(\pi=(\pi_g)_{g\in\mathcal G}\) with \(\pi_g>0\) on every
treated cohort used by the target, and a nonempty not-yet-treated or
never-treated comparison set for every target cell.  The target is the fixed
known aggregation
\[
  \theta_a=\sum_{(g,t)\in\mathcal T_a} a_{gt}\tau_{gt},\qquad
  \sum_{(g,t)\in\mathcal T_a}a_{gt}=1,
\]
where \(\tau_{gt}=\E[Y_{it}(g)-Y_{it}(\infty)\mid G_i=g]\) and
\(\mathcal T_a=\{(g,t):t\ge g,\ a_{gt}\ne0\}\).  The regression convention is
finite-dimensional semiparametric GMM / linear projection: BJS uses the full
valid sequential pre-period moment block \(\mathcal M_{\mathrm{all}}\), while
the canonical SA, CS, and Wooldridge implementations use estimator-specific
comparison blocks
\(\mathcal M_{\mathrm{SA}},\mathcal M_{\mathrm{CS}},\mathcal M_{\mathrm{W}}
\subseteq\mathcal M_{\mathrm{all}}\) that identify the same \(\theta_a\) but
need not optimally combine every pre-period covariance direction.  From v4
onward the common-baseline shortcut is withdrawn: the three spans are defined separately
by the finite contrast matrices
\(B_{\mathrm{SA}},B_{\mathrm{CS}},B_{\mathrm{W}}\) in Section 6, and equality
with BJS is tested estimator-by-estimator through the two-block score
certificate \(K_e=(D_e;H_{\mathrm{pre},e})\) for
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\), where \(D_e\) records
canonical/post-period score-loading differences not absorbed by the full BJS
pre-period span.  The pre-period residual covariance matrix is
\(\Sigma\succ0\), estimated from untreated observations and treated as the
inner product defining efficiency projections.  The active-rank diagnostic is
\(K_e(a,\pi,\Sigma)\), an observable population function of the target
weights, cohort shares, estimator-specific comparison-support matrices, and
pre-period covariance; \(\tau\) enters the estimand value but is not a
primitive argument of the diagnostic.

\begin{abstract}
Modern staggered DiD estimators often agree on the group-time ATT target while
using different pre-period information to remove untreated-outcome nuisance
variation.  This proposal asks for the sharp boundary at which additional
pre-treatment periods change the efficient influence function rather than
serving only as diagnostics or finite-sample stabilizers.  The flagship
conjecture is an estimator-specific active-score-rank theorem: after separating
canonical post-period score-loading differences from residual pre-period
projection differences, the BJS full-preperiod influence function equals that
estimator's influence function if and only if the corresponding observable
two-block score certificate \(K_e=(D_e;H_{\mathrm{pre},e})\) has rank zero.
Off this rank-zero set, the variance gap is the squared \(\Sigma^{-1}\)-norm
of the full score residual within the maintained sequential-moment model, so
efficiency loss is a computable projection quantity rather than a vague
estimator-choice warning.  A companion comparison theorem maps this diagnostic
to the extra pre-period weight component in \citet{ChenSantAnnaXie2025}.
Resolving the conjecture would turn the recent efficient-DiD literature into a
diagnostic for when empirical researchers should exploit all pre-periods in an
imputation score.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
The recent staggered-DiD literature has largely settled how to avoid forbidden
comparisons and how to write interpretable group-time ATT aggregations.  It has
not settled the more operational question of when two identification-equivalent
procedures have the same first-order precision.  In applications with several
pre-treatment periods, researchers must decide whether extra pre-periods should
enter the estimating score, be reserved for pre-trend tests, or be ignored to
match a simpler event-study implementation.

\paragraph{The main finding (proposed).}
The proposed flagship result is Conjecture 1, the estimator-specific active
pre-period score-rank boundary.  Fixing the target \(\theta_a\), cohort shares
\(\pi\), estimator comparison support, and pre-period covariance \(\Sigma\),
form the BJS canonical score loading and full pre-period projection, then
compare them separately with the SA, CS, and Wooldridge canonical score
loadings and score projections.  The claim is that BJS and estimator \(e\)
have the same first-order influence function exactly when the observable
residualized score certificate \(K_e(a,\pi,\Sigma)\) has rank zero, and that
the strict variance gap off that set is the projection norm of this same
certificate.

\paragraph{What is new.}
The nearest published frontiers are \citet{EgamiYamauchi2023}, which show how
multiple pre-treatment periods can improve DiD and staggered-adoption designs
through GMM-style use of extra information, \citet{ChenSantAnnaXie2025}, which
derive closed-form efficient influence functions and emphasize that modern DiD
assumptions impose overidentifying restrictions, and
\citet{RothSantAnna2023Efficient}, which builds feasible efficient estimators
for staggered rollout designs under as-good-as-random rollout timing.  The
epsilon-gap here is the necessary-and-sufficient observable classifier saying
when those efficiency gains are score-changing for a particular
parallel-trends staggered ATT aggregation and when they are redundant relative
to each named estimator's actual comparison block.  The closest BJS result,
\citet{BorusyakJaravelSpiess2024}, shows efficient imputation and documents
large precision gains under its maintained error-structure conditions, but it
does not give an if-and-only-if active-rank condition separating equality and
strict non-equality of influence functions for the four named estimators.

\paragraph{How it positions in the literature.}
This is a panel / linear-projection proposal in the modern staggered-DiD and
event-study cluster.  It consumes the ATT identification results of
\citet{CallawaySantAnna2021}, the contamination-free event-study estimands of
\citet{SunAbraham2021}, the imputation-efficiency benchmark of
\citet{BorusyakJaravelSpiess2024}, and the semiparametric efficiency logic of
\citet{SantAnnaZhao2020}, \citet{RothSantAnna2023Efficient}, and
\citet{ChenSantAnnaXie2025}.  Its contribution is not a new estimand and not
another implementation recipe; it is a row-space boundary for when additional
pre-period moment restrictions alter a named estimator's influence function
for a fixed estimand.

\paragraph{Implications for the community.}
The direct consumer is the efficient DiD / event-study program of
\citet{ChenSantAnnaXie2025}: the conjecture would supply a transparent
observable diagnostic for deciding whether their extra pre-period EIF weights
are active for a given event-study aggregation or whether a named BJS, SA, CS,
or Wooldridge implementation already has the same first-order score.

\paragraph{How research benefits from the conclusion.}
Empirical researchers should report the estimator-specific score-certificate
ranks before treating extra pre-treatment periods as merely diagnostic rather
than efficiency-relevant.

\section{Related work}
\citet{BorusyakJaravelSpiess2024} derive the robust and efficient imputation
estimator for staggered event-study designs and show that alternative robust
estimators can be less precise; this proposal tries to characterize exactly
when that precision difference vanishes.  \citet{ChenSantAnnaXie2025} derive
closed-form EIFs for DiD and event-study parameters under modern DiD
assumptions; this proposal asks for the finite-dimensional rank certificate
that decides whether the extra pre-period restrictions appearing in those EIFs
are active.  \citet{SantAnnaZhao2020} derive the semiparametric efficiency
bound for two-period ATT DiD; this proposal isolates the additional active-rank
phenomenon that has no analogue when only one pre-period contrast is available.
\citet{EgamiYamauchi2023} study how multiple pre-treatment periods can improve
DiD and staggered-adoption designs through GMM; this proposal turns that
intuition into an influence-function equality boundary rather than an
estimator-specific efficiency comparison.
\citet{RothSantAnna2023Efficient} is the closest efficient-staggered-rollout
comparator: it derives feasible efficient estimators and optimal pre-treatment
adjustments under as-good-as-random rollout timing, while the present proposal
targets the separate parallel-trends question of when BJS and each of SA, CS,
and Wooldridge have identical or strictly different first-order scores for a
common ATT aggregation.

\citet{CallawaySantAnna2021} identify and aggregate group-time ATTs in
multi-period DiD and provide inference for those aggregations; this proposal
holds the aggregation fixed and compares nuisance-score projections around it.
\citet{SunAbraham2021} show that dynamic TWFE coefficients can be contaminated
by other-period heterogeneous effects and propose interaction-weighted
estimators; this proposal separates contamination-free point identification
from efficiency equivalence.  \citet{Wooldridge2021} gives saturated
regression and Mundlak-style implementation equivalences for staggered entry
with heterogeneous effects; this proposal asks when such implementation
equivalences also preserve the efficient influence-function subspace.
\citet{RothSantAnnaBilinskiPoe2023} synthesize the modern DiD literature and
highlight the difficulty of matching estimator choices to empirical designs;
the active-rank diagnostic would be a concrete answer for the pre-period
efficiency dimension.  \citet{BellegoBenatiaDortetBernadet2025} develop chained
DiD for unbalanced panels and discuss efficiency gains from overlapping
incomplete panels; their results are adjacent because missing pre-period
directions change the same score geometry studied here.

The in-catalogue prior art supplied by the Stage -1.1 scout is
\texttt{panel\_honest\_did\_phase}, whose failed banked proposal and reviewer
logs identify row-space and operator-certificate gaps for staggered-DiD
sensitivity frontiers, and
\texttt{q1\_spectral\_phase\_transition}/\texttt{p1\_markov}, which proposes
singular values of event-window FWL Gram blocks as visibility diagnostics.
Those artefacts are relevant as warnings: a bare spectral threshold can look
like generic linear algebra unless it is tied to a named econometric score or
frontier.  No active ThmSmith proposal in the Stage -1.1 prior-proposal map
states an active pre-period EIF rank boundary for BJS, SA, CS, and Wooldridge
around a common staggered ATT target.

\section{Formal setup}
There are \(n\) independent units observed for \(t=1,\ldots,T\).  Cohort
\(G_i=g\) means unit \(i\) first receives treatment in period \(g\), with
\(G_i=\infty\) for never-treated units, and \(D_{it}=\one\{t\ge G_i\}\).  The
untreated potential-outcome mean has the additive panel form
\[
  \E[Y_{it}(\infty)\mid G_i=g]=\alpha_g+\lambda_t
\]
after conditioning on the finite cohort cells used in this proposal.  The
group-time treatment effect is
\(\tau_{gt}=\E[Y_{it}(g)-Y_{it}(\infty)\mid G_i=g]\) for \(t\ge g\), and the
target is \(\theta_a=\sum_{(g,t)\in\mathcal T_a}a_{gt}\tau_{gt}\).

Let
\[
  \mathcal J=\{(h,r): h\in\mathcal G,\ r<h\ \text{or}\ h=\infty\}
\]
be the set of observed untreated cohort-period cells, ordered once and for all,
and write \(q=|\mathcal J|\).  For \(j=(h,r)\in\mathcal J\), \(U_j\) is the
cohort-share normalized untreated residual cell score after removing cohort
and calendar means; \(U=(U_j)_{j\in\mathcal J}\in\R^q\) and
\(\Sigma=\operatorname{Var}(U)\succ0\).  For a closed linear subspace
\(\mathcal L\subseteq\R^q\), \(P_{\mathcal L}^{\Sigma}\) denotes orthogonal
projection under
\(\langle x,y\rangle_{\Sigma}=x^{\transpose}\Sigma^{-1}y\).

For each target cell \(k=(g,t)\in\mathcal T_a\), let
\(\mathcal C^e_{gt}\subseteq\{c\in\mathcal G:c>t\ \text{or}\ c=\infty\}\)
be the comparison cohorts used by estimator
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\), and let
\(w^e_{gtc}\) be its population comparison weights, normalized to sum to one
over \(c\in\mathcal C^e_{gt}\) for SA and CS.  SA uses the not-yet-treated
cohorts entering the interaction-weighted cohort-by-event contrast, and CS
uses the group-time ATT comparison set in its doubly-robust score.  The
Wooldridge object in this proposal is the cohort-time-saturated
Mundlak/TWFE implementation whose residual-regression comparison weights
\(w^{\mathrm W}_{gtc}\) are induced by the population normal equations after
excluding already-treated comparison outcomes; these weights may be signed
residual-regression weights, but their contrast is normalized to have unit
loading on the missing untreated mean for cell \((g,t)\).  The BJS comparison
support \(\mathcal C^{\mathrm{BJS}}_{gt}\) is the full admissible
not-yet-treated or never-treated support used by the efficient imputation
score, with population imputation weights \(w^{\mathrm{BJS}}_{gtc}\).  For a
pre-period edge \(2\le r<g\), define the elementary comparison column
\(v^e_{gt,r}\in\R^q\) by
\[
  v^e_{gt,r}(h,s)=
  \frac{\one\{h=g,s=r\}-\one\{h=g,s=r-1\}}{\sqrt{\pi_g}}
  -\sum_{c\in\mathcal C^e_{gt}}w^e_{gtc}
   \frac{\one\{h=c,s=r\}-\one\{h=c,s=r-1\}}{\sqrt{\pi_c}}.
\]
The finite matrix \(B_e\in\R^{q\times m_e}\) has columns
\(\{v^e_{gt,r}:(g,t)\in\mathcal T_a,\ 2\le r<g\}\) after dropping duplicate
or zero columns, and
\[
  \mathcal M_e=\operatorname{col}(B_e),\qquad
  e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}.
\]
The full BJS sequential-preperiod matrix
\(B_{\mathrm{all}}\in\R^{q\times m_{\mathrm{all}}}\) contains the union of
all such valid columns over every admissible comparison cohort and pre-period
edge for the target cells, and
\(\mathcal M_{\mathrm{all}}=\operatorname{col}(B_{\mathrm{all}})\).
Thus \(\mathcal M_e\subseteq\mathcal M_{\mathrm{all}}\), but the three
baseline spans need not coincide.

The estimator-specific ATT score loadings \(b_a^e(a,\pi)\in\R^q\), for
\(e\in\{\mathrm{BJS},\mathrm{SA},\mathrm{CS},\mathrm{W}\}\), are defined by
the same indexed coordinates.  Let
\[
  \omega_{gt}^{e}(h,s)=
  \frac{\one\{h=g,s=t\}}{\sqrt{\pi_g}}
  -\sum_{c\in\mathcal C^e_{gt}}w^e_{gtc}
   \frac{\one\{h=c,s=t\}}{\sqrt{\pi_c}}
\]
denote the post-period untreated counterfactual loading that would enter the
first-order expansion of the \(gt\) ATT contrast if untreated outcomes at
period \(t\) were observed for cohort \(g\).  Its restriction to the untreated
score coordinates is the vector \(\omega_{gt}^e\in\R^q\), and
\[
  b_a^e(a,\pi)=\sum_{(g,t)\in\mathcal T_a}a_{gt}\omega_{gt}^{e}.
\]
For \(e=\mathrm{BJS}\) this formula uses
\(\mathcal C^{\mathrm{BJS}}_{gt}\) and \(w^{\mathrm{BJS}}_{gtc}\).  The
canonical score-loading residual for estimator \(e\) is
\[
  d_e(a,\pi)=b_a^{\mathrm{BJS}}(a,\pi)-b_a^e(a,\pi).
\]
These loadings are functions of \(a\), \(\pi\), and comparison support, not of
the unknown treatment-effect vector \(\tau\).

For each \(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\), define the residual
active pre-period score, canonical residual, and total score certificate
\[
  h_{\mathrm{pre},e}(a,\pi,\Sigma)=
  \left(P_{\mathcal M_{\mathrm{all}}}^{\Sigma}
       -P_{\mathcal M_e}^{\Sigma}\right)b_a^e(a,\pi),
\]
\[
  D_e(a,\pi,\Sigma)=
  \Sigma^{-1/2}(I-P_{\mathcal M_{\mathrm{all}}}^{\Sigma})d_e(a,\pi),\qquad
  H_{\mathrm{pre},e}(a,\pi,\Sigma)
  =\Sigma^{-1/2} h_{\mathrm{pre},e}(a,\pi,\Sigma).
\]
For scalar \(\theta_a\), \(D_e\) and \(H_{\mathrm{pre},e}\) are \(q\)-vectors.
For an \(m\)-dimensional vector event-study target
\(A=(a_1,\ldots,a_m)\), define
\[
  D_e(A,\pi,\Sigma)=
  \begin{bmatrix}D_e(a_1,\pi,\Sigma)&\cdots&D_e(a_m,\pi,\Sigma)\end{bmatrix},
\quad
  H_{\mathrm{pre},e}(A,\pi,\Sigma)=
  \begin{bmatrix}
    H_{\mathrm{pre},e}(a_1,\pi,\Sigma)&\cdots&
    H_{\mathrm{pre},e}(a_m,\pi,\Sigma)
  \end{bmatrix}.
\]
The total whitened score certificate is the vertical block
\[
  K_e(a,\pi,\Sigma)=
  \begin{bmatrix}
    D_e(a,\pi,\Sigma)\\
    H_{\mathrm{pre},e}(a,\pi,\Sigma)
  \end{bmatrix},
\]
with the same vertical stacking applied columnwise to \(A\).
Because \(H_{\mathrm{pre},e}\) lies in the whitened full-preperiod span and
\(D_e\) lies in its \(\Sigma\)-orthogonal complement, \(\operatorname{rank}K_e=0\)
is equivalent to both the unabsorbed canonical residual and the active
pre-period residual being zero.  For scalar \(\theta_a\),
\(\operatorname{rank}K_e\) is zero or positive; for a vector event-study target
\(A=(a_1,\ldots,a_m)\), the target-dimensional variance-gap matrix is
\[
  \Delta_{\mathrm{EIF},e}(A,\pi,\Sigma)
  =
  D_e(A,\pi,\Sigma)^{\transpose}D_e(A,\pi,\Sigma)
  +H_{\mathrm{pre},e}(A,\pi,\Sigma)^{\transpose}
   H_{\mathrm{pre},e}(A,\pi,\Sigma)
  =K_e(A,\pi,\Sigma)^{\transpose}K_e(A,\pi,\Sigma).
\]
These population objects are observable from the design matrices, \(a\), \(\pi\),
the estimator-specific comparison weights, and \(\Sigma\).  Their sample
analogues
\(\widehat K_e=K_e(a,\widehat\pi,\widehat\Sigma)\) use cohort shares and
untreated pre-period residual covariance estimated from the pre-treatment
sample.

\begin{quote}\small
\begin{verbatim}
Locked parameters:
qid = eid_bjs_efficient_event_study
specialization = v1
p = T - 1
assignment = absorbing staggered adoption with fixed positive cohort shares pi
target = theta_a = sum_{(g,t) in T_a} a_gt tau_gt
regression = finite-dimensional EIF/GMM projection:
  BJS uses M_all;
  canonical SA/CS/Wooldridge use estimator-specific spans
    M_SA = col(B_SA), M_CS = col(B_CS), M_W = col(B_W);
  no common-baseline or common-canonical-loading equality is assumed from v4 onward;
  Sigma is the untreated pre-period residual covariance inner product;
  d_e = b_BJS - b_e captures canonical/post-score loading differences;
  K_e = [D_e; H_pre,e] is observable and does not depend on tau
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Absorbing staggered panel and support]\label{ass:panel-support}
Treatment is absorbing, cohort shares \(\pi_g\) are fixed and strictly positive
for every treated cohort entering \(\mathcal T_a\), and each target cell
\((g,t)\in\mathcal T_a\) has at least one valid not-yet-treated or
never-treated comparison cohort in each estimator-specific comparison support
\(\mathcal C^{\mathrm{BJS}}_{gt}\), \(\mathcal C^{\mathrm{SA}}_{gt}\),
\(\mathcal C^{\mathrm{CS}}_{gt}\), and \(\mathcal C^{\mathrm{W}}_{gt}\).
\end{assumption}

\begin{assumption}[No anticipation and additive untreated trends]\label{ass:pt-na}
For every cohort \(g\) and period \(t<g\), observed outcomes equal untreated
potential outcomes, and
\(\E[Y_{it}(\infty)\mid G_i=g]=\alpha_g+\lambda_t\).  The implied sequential
parallel-trend moment restrictions are exactly the finite-dimensional span
\(\mathcal M_{\mathrm{all}}\) defined in Section 6.
\end{assumption}

\begin{assumption}[Pinned estimator-specific moment spans]\label{ass:nested-moments}
The canonical SA, CS, and Wooldridge implementations being compared use the
finite contrast matrices \(B_{\mathrm{SA}},B_{\mathrm{CS}},B_{\mathrm{W}}\)
from Section 6, with
\(\mathcal M_e=\operatorname{col}(B_e)\) for
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).  The full BJS imputation score
uses \(B_{\mathrm{all}}\) and \(\mathcal M_{\mathrm{all}}\), and each named
baseline span is nested,
\[
  \mathcal M_e\subseteq\mathcal M_{\mathrm{all}}\subseteq\R^q.
\]
No equality among
\(\mathcal M_{\mathrm{SA}},\mathcal M_{\mathrm{CS}},\mathcal M_{\mathrm{W}}\)
is assumed.
\end{assumption}

\begin{assumption}[Regular covariance and fixed target]\label{ass:regular-covariance}
The pre-period residual covariance \(\Sigma=\operatorname{Var}(U)\) is positive
definite, the aggregation weights \(a\) are fixed and nonrandom, and
\(\theta_a\), \(b_a^{\mathrm{BJS}}(a,\pi)\), \(b_a^e(a,\pi)\), \(d_e\),
\(h_{\mathrm{pre},e}\), \(D_e\), \(H_{\mathrm{pre},e}\), and \(K_e\) are the
objects defined in Section 6.
\end{assumption}

\begin{assumption}[Observable plug-in rank regularity]\label{ass:plugin-rank}
The plug-in estimates \(\widehat\pi\) and \(\widehat\Sigma\) are
\(\sqrt n\)-consistent for \(\pi\) and \(\Sigma\), the comparison weights
\(w^e_{gtc}\), design matrices
\(B_{\mathrm{all}},B_{\mathrm{SA}},B_{\mathrm{CS}},B_{\mathrm{W}}\), and
target weights \(a\) are fixed, and the nonzero singular values of each
\(K_e(a,\pi,\Sigma)\) are separated from zero by a population
gap \(\gamma_e>0\).  The rank selector uses a deterministic threshold
\(\lambda_n\downarrow0\) with \(\sqrt n\,\lambda_n\to\infty\).
\end{assumption}

\begin{assumption}[Regular asymptotic linearity]\label{ass:regular-if}
The BJS, SA, CS, and Wooldridge implementations are evaluated under the common
finite-cell convention of Section 6 and admit first-order asymptotic linear
representations whose canonical score loadings are
\(b_a^{\mathrm{BJS}}\) and \(b_a^e\), and whose nuisance-score components are
the \(\Sigma\)-orthogonal projections onto their stated moment spans.
\end{assumption}

\begin{assumption}[BJS full-preperiod score correctness]\label{ass:bjs-full-score}
The BJS implementation being compared is in the error-structure regime where
its imputation score uses the full valid sequential pre-period span
\(\mathcal M_{\mathrm{all}}\).  The resulting variance is the full-preperiod
sequential-moment bound in this proposal, not a claim that BJS attains every
arbitrary-\(\Sigma\) semiparametric bound outside its maintained efficient
imputation setup.
\end{assumption}

\begin{assumption}[Single-preperiod sanity corner]\label{ass:single-preperiod}
For the two-period sanity reduction, every target cell has only one usable
pre-treatment contrast, so
\(\mathcal M_{\mathrm{all}}=\mathcal M_{\mathrm{SA}}=\mathcal M_{\mathrm{CS}}
=\mathcal M_{\mathrm{W}}\), and
\((I-P_{\mathcal M_{\mathrm{all}}}^{\Sigma})d_e(a,\pi)=0\) for every
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).
\end{assumption}

\begin{assumption}[Redundant-diagnostic sanity corner]\label{ass:redundant-diagnostic}
For the redundant-diagnostics sanity reduction, every extra pre-period moment
in \(\mathcal M_{\mathrm{all}}\ominus_{\Sigma}\mathcal M_e\), for each
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\), is \(\Sigma\)-orthogonal to
\(b_a^e(a,\pi)\), and
\((I-P_{\mathcal M_{\mathrm{all}}}^{\Sigma})d_e(a,\pi)=0\).
\end{assumption}

\begin{assumption}[Homogeneous treatment effects]\label{ass:homogeneous-effect}
For the homogeneous-effect sanity reduction, treatment effects are constant on
\(\mathcal T_a\), so the scalar target value is a common ATT across all
treated cohort-period cells entering the aggregation.
\end{assumption}

\begin{assumption}[Common loading and span sanity corner]\label{ass:common-loading-span}
For the homogeneous-effect sanity reduction, the common-ATT contrast design
also makes the canonical score loading satisfy
\(b_a^{\mathrm{BJS}}(a,\pi)=b_a^e(a,\pi)\in
\mathcal M_{\mathrm{SA}}\cap\mathcal M_{\mathrm{CS}}\cap\mathcal M_{\mathrm{W}}\)
for every \(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).
\end{assumption}

\section{Main results}
\begin{conjecture}[Conjecture 1: estimator-specific active pre-period EIF boundary (NOT YET PROVED)]\label{conj:active-preperiod-boundary}
Under Assumptions \ref{ass:panel-support}--\ref{ass:bjs-full-score}, fix
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).  The full-preperiod BJS
influence function obtained from \(\mathcal M_{\mathrm{all}}\) equals
estimator \(e\)'s influence function obtained from its canonical loading
\(b_a^e\) and moment span \(\mathcal M_e\) if and only if
\[
  \operatorname{rank}K_e(a,\pi,\Sigma)=0.
\]
Equivalently, both the unabsorbed canonical score residual \(D_e\) and the
active pre-period residual \(H_{\mathrm{pre},e}\) vanish.  When
\(\operatorname{rank}K_e>0\), the full-preperiod influence
function has strictly smaller asymptotic variance than estimator \(e\)'s
score within the maintained sequential-moment model, with variance improvement
\[
  \Delta_{\mathrm{EIF},e}(a,\pi,\Sigma)
  =
  \|(I-P_{\mathcal M_{\mathrm{all}}}^{\Sigma})d_e(a,\pi)\|_{\Sigma}^{2}
  +\|h_{\mathrm{pre},e}(a,\pi,\Sigma)\|_{\Sigma}^{2}>0
\]
in the scalar target case, and the analogous positive semidefinite Loewner gap
\[
  D_e(A,\pi,\Sigma)^{\transpose}D_e(A,\pi,\Sigma)
  +H_{\mathrm{pre},e}(A,\pi,\Sigma)^{\transpose}
   H_{\mathrm{pre},e}(A,\pi,\Sigma)
  =K_e(A,\pi,\Sigma)^{\transpose}K_e(A,\pi,\Sigma)
\]
for vector event-study targets \(A=(a_1,\ldots,a_m)\).  The four named
implementations have a common influence function if
and only if this rank-zero condition holds for all
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest papers are \citet{EgamiYamauchi2023},
\citet{ChenSantAnnaXie2025}, and \citet{RothSantAnna2023Efficient}.  Egami and
Yamauchi show how multiple pre-treatment periods can improve DiD and
staggered-adoption designs through GMM-style use of extra pre-period
information, but they do not give an if-and-only-if condition under which BJS,
SA, CS, and Wooldridge have the same influence function for a fixed target.
Chen, Sant'Anna, and Xie give closed-form EIFs and overidentification
restrictions, and Roth and Sant'Anna give feasible efficient
staggered-rollout estimators, but neither paper states the observable
rank-zero classifier relative to each named estimator's actual comparison
block.  The epsilon gap is the equality frontier \(K_e=0\), including both
canonical loading residuals and active pre-period GMM residuals; it is not the
existence of GMM efficiency gains, an EIF, or an efficient estimator.  The v5
statement also avoids the vector-target well-posedness gap by defining
\(K_e\) as a vertical score block whose Gram is target-dimensional.  (b)
Resolving this would give the
\citet{ChenSantAnnaXie2025} efficient-estimation program and the
\citet{RothSantAnnaBilinskiPoe2023} estimator-choice guidance a one-number
score-certificate diagnostic for when all pre-periods must enter the score for
each named implementation.

\begin{theorem}[Theorem 1: relation to closed-form EIF weights]\label{thm:csx-comparison}
Under Assumptions \ref{ass:panel-support}--\ref{ass:regular-if}, suppose a
closed-form event-study EIF weight vector \(q_{\mathrm{EIF}}\in\R^q\) is
written in the finite-cell coordinates \(\mathcal J\) of Section 6, and the
score used by estimator \(e\) has nuisance weight
\(q_e=P_{\mathcal M_e}^{\Sigma}b_a^e(a,\pi)\).  If the full-preperiod efficient
weight is
\(q_{\mathrm{EIF}}=P_{\mathcal M_{\mathrm{all}}}^{\Sigma}
b_a^{\mathrm{BJS}}(a,\pi)\), then
\[
  q_{\mathrm{EIF}}-q_e
  =P_{\mathcal M_{\mathrm{all}}}^{\Sigma}d_e(a,\pi)
   +h_{\mathrm{pre},e}(a,\pi,\Sigma).
\]
If \(\varphi_{\mathrm{BJS}}\) and \(\varphi_e\) denote the corresponding
finite-cell influence functions, their score-coordinate difference is
\[
  \varphi_{\mathrm{BJS}}-\varphi_e
  =(I-P_{\mathcal M_{\mathrm{all}}}^{\Sigma})d_e(a,\pi)
   -h_{\mathrm{pre},e}(a,\pi,\Sigma).
\]
Hence the difference between the full-preperiod EIF and estimator \(e\)'s
influence function is zero exactly when
\(\operatorname{rank}K_e(a,\pi,\Sigma)=0\).
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) \citet{ChenSantAnnaXie2025} give closed-form EIFs and identify
overidentification restrictions, but they do not turn their extra pre-period
weight vector into a named-estimator equality classifier for BJS, SA, CS, and
Wooldridge.  This theorem states the precise algebraic bridge: their EIF
weights correspond to the \(\mathcal M_{\mathrm{all}}\) projection, while the
new object is the residual of that weight and the associated canonical
post-period loading against each published estimator's finite comparison
block.  (b) The concrete consumer is the empirical
diagnostic implied by \citet{ChenSantAnnaXie2025}: researchers can ask whether
the EIF's extra score component is zero for their chosen SA, CS, or Wooldridge
implementation.

\begin{theorem}[Theorem 2: plug-in rank selection]\label{thm:plugin-rank}
Under Assumptions \ref{ass:panel-support}--\ref{ass:plugin-rank}, let
\(\widehat r_{e,n}\) be the number of singular values of
\(\widehat K_e=K_e(a,\widehat\pi,\widehat\Sigma)\)
exceeding \(\lambda_n\).  Then, for each
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\),
\[
  \Pr\{\widehat r_{e,n}=\operatorname{rank}K_e(a,\pi,\Sigma)\}
  \to 1.
\]
Consequently the equality region in Conjecture~\ref{conj:active-preperiod-boundary}
is testable estimator-by-estimator at the population rank-selection level
whenever the spectral gap condition in Assumption~\ref{ass:plugin-rank} holds.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is a routine perturbation result once the observable object
\(K_e(a,\pi,\Sigma)\) is defined, but it is absent from
\citet{ChenSantAnnaXie2025}, \citet{RothSantAnna2023Efficient}, and
\citet{BorusyakJaravelSpiess2024} because those papers do not define this
four-estimator equality frontier.  The epsilon gap is not rank consistency by
itself; it is rank consistency for the proposed equality/non-equality
certificate.  (b) The concrete consumer is empirical work following
\citet{RothSantAnnaBilinskiPoe2023}: the theorem says the proposed diagnostic
can be reported from observable cohort shares and untreated covariance rather
than from the unknown treatment-effect matrix.

\begin{conjecture}[Conjecture 2: named-estimator implication (NOT YET PROVED)]\label{conj:named-estimator-implication}
Under Assumptions \ref{ass:panel-support}--\ref{ass:bjs-full-score}, the BJS
imputation estimator, SA interaction-weighted estimator, CS group-time
doubly-robust estimator, and Wooldridge cohort-time-saturated regression have
identical first-order influence functions for \(\theta_a\) if and only if
\[
  \operatorname{rank}K_{\mathrm{SA}}
  =\operatorname{rank}K_{\mathrm{CS}}
  =\operatorname{rank}K_{\mathrm{W}}=0.
\]
If the rank is positive for estimator \(e\), then BJS and estimator \(e\) have
strictly different influence functions, and estimator \(e\)'s asymptotic
variance exceeds the full-preperiod sequential-moment bound by
\(\Delta_{\mathrm{EIF},e}\) for scalar targets.  This is a claim about the
explicit finite matrices and canonical loadings in Section 6, not about
stipulated common spans or common post-period loadings.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{BorusyakJaravelSpiess2024} prove efficient imputation and compare
precision to other robust estimators, while \citet{SunAbraham2021},
\citet{CallawaySantAnna2021}, and \citet{Wooldridge2021} provide
contamination-free or saturated-regression routes to interpretable ATT
parameters.  \citet{RothSantAnna2023Efficient} is a closer efficiency
comparator, but its rollout-timing framework and optimal adjustment result do
not give a necessary-and-sufficient score-certificate condition under which
these four parallel-trends implementations have the same influence-function
subspace for the same target, and \citet{ChenSantAnnaXie2025} does not assert
that BJS
attains their full bound outside the BJS error-structure regime.  (b)
Resolving this would let users of the BJS,
\texttt{did}, interaction-weighted, and saturated-regression workflows decide
whether a reported standard-error difference is an implementation artifact or
a genuine semiparametric efficiency gap.

\section{Sanity-check corollaries}
\begin{corollary}[Two-period collapse]\label{cor:two-period-collapse}
Under Assumptions \ref{ass:panel-support}--\ref{ass:single-preperiod},
\(\mathcal M_{\mathrm{all}}=\mathcal M_e\) for every
\(e\in\{\mathrm{SA},\mathrm{CS},\mathrm{W}\}\), hence
\(h_{\mathrm{pre},e}=0\), \(D_e=0\), \(\operatorname{rank}K_e=0\), and
the proposal collapses to the two-period ATT efficiency comparison of
\citet{SantAnnaZhao2020}.
\end{corollary}

\begin{corollary}[Redundant diagnostics]\label{cor:redundant-diagnostics}
Under Assumptions \ref{ass:nested-moments} and
\ref{ass:redundant-diagnostic}, \(K_e=0\) for every
\(e\).  Thus additional pre-periods may remain useful for testing parallel
trends without changing the first-order efficient score for \(\theta_a\).
\end{corollary}

\begin{corollary}[Homogeneous-effect corner]\label{cor:homogeneous-corner}
Under Assumptions \ref{ass:nested-moments},
\ref{ass:regular-covariance}, \ref{ass:homogeneous-effect}, and
\ref{ass:common-loading-span}, the active score-certificate rank is zero for
each named estimator.  Homogeneity supplies a common ATT value, while
Assumption~\ref{ass:common-loading-span} supplies the additional design
condition that makes the canonical loadings and pre-period spans coincide;
together they recover the standard equivalence intuition that robust
staggered-DiD implementations differ in presentation rather than first-order
score for the common ATT.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is a finite-dimensional Hilbert-space projection
argument.  First write each estimator's first-order expansion as an
estimator-specific canonical ATT score plus a nuisance correction in the span
of valid pre-period moments.  Second decompose the BJS-minus-estimator score
difference into the \(\Sigma\)-orthogonal direct sum of the unabsorbed
canonical residual \((I-P_{\mathcal M_{\mathrm{all}}}^{\Sigma})d_e\) and the
active pre-period projection residual \(h_{\mathrm{pre},e}\).  Third apply the
standard semiparametric projection identity: the variance drop from replacing
estimator \(e\)'s score by the full-preperiod BJS score is the squared norm of
that direct-sum residual.  The nonroutine algebra is to verify, for the SA,
CS, and Wooldridge comparison conventions separately, that the indexed
matrices \(B_{\mathrm{SA}},B_{\mathrm{CS}},B_{\mathrm{W}}\) and loadings
\(b_a^e\) reproduce the published first-order scores and are nested in
\(B_{\mathrm{all}}\).  The smallest nontrivial designs \(T=3\) and \(T=4\)
should then be computed explicitly to confirm that \(D_e\) and
\(H_{\mathrm{pre},e}\) separate post-period loading differences from
residualized pre-period row-space differences.  The comparison with
\citet{ChenSantAnnaXie2025} reduces to writing their closed-form EIF weights
in the same \(\mathcal J\) coordinates and subtracting the estimator-specific
projection \(P_{\mathcal M_e}^{\Sigma}b_a^e\).  The plug-in theorem follows by
Davis--Kahan or Weyl singular value perturbation after \(\widehat\pi\) and
\(\widehat\Sigma\) are substituted.  The boundary cases are singular
comparison support, nearly collinear pre-period covariance, BJS error
structures outside Assumption~\ref{ass:bjs-full-score}, and vector event-study
targets where rank may exceed one.

\section{Honest scope flags}
Conjectures \ref{conj:active-preperiod-boundary} and
\ref{conj:named-estimator-implication} are not yet proved.  Theorem
\ref{thm:csx-comparison} is an algebraic positioning statement conditional on
expressing \citet{ChenSantAnnaXie2025}'s EIF weights in the finite-cell
coordinates of Section 6.  Theorem
\ref{thm:plugin-rank} is intended as a routine perturbation result conditional
on Assumption~\ref{ass:plugin-rank}, not as the flagship mathematical novelty.
The projection-norm formula is routine once the estimator-specific first-order
spans have been identified.  The v3 draft withdraws the v2 common-baseline
shortcut and makes the named SA, CS, and Wooldridge implementations separate
finite matrices \(B_{\mathrm{SA}},B_{\mathrm{CS}},B_{\mathrm{W}}\).  It also
limits the BJS efficiency claim to the full-preperiod sequential-moment bound
under Assumption~\ref{ass:bjs-full-score}, avoiding the stronger and
unsupported claim that BJS attains every arbitrary-\(\Sigma\) bound.  The v4
draft withdraws the v3 claim that \(H_{\mathrm{pre},e}\) alone classifies full
influence-function equality; equality is now classified by the full two-block
certificate \(K_e=(D_e;H_{\mathrm{pre},e})\).  The
proposal deliberately withdraws the earlier angle's stronger claim that the
four estimators are classified by a heterogeneity-matrix rank threshold alone;
the present angle makes observable pre-period score activity, not
treatment-effect rank by itself, the primitive.  The v5 draft separates
homogeneity from the extra loading/span equality needed for the homogeneous
sanity corner, and replaces the vector-target variance gap by the
target-dimensional matrix \(D_e^{\transpose}D_e+
H_{\mathrm{pre},e}^{\transpose}H_{\mathrm{pre},e}\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 1, replacing the exhausted
four-estimator \(K_\star\) rank-threshold angle with an active pre-period
score-rank frontier anchored to \citet{ChenSantAnnaXie2025}; prior verdict:
none.
\item v2 (revise) --- added \citet{RothSantAnna2023Efficient}, made
\(H_{\mathrm{pre}}(a,\pi,\Sigma)\) observable with a plug-in rank-selection
theorem, and pinned SA/CS/Wooldridge baseline spans by explicit matrices;
prior verdict: REVISE.
\item v3 (revise) --- replaced the common-baseline shortcut by
estimator-specific matrices and \(H_{\mathrm{pre},e}\), added the
\citet{ChenSantAnnaXie2025} EIF-weight comparison theorem, and restricted the
BJS efficiency claim to the maintained full-preperiod score regime; prior
verdict: REVISE.
\item v4 (revise) --- added estimator-specific canonical score loadings
\(b_a^e\), the unabsorbed loading residual \(D_e\), and the total certificate
\(K_e=(D_e;H_{\mathrm{pre},e})\); clarified Wooldridge as signed
residual-regression weights from the saturated normal equations; prior
verdict: REVISE.
\item v5 (revise) --- made the vector-target variance gap target-dimensional,
added the load-bearing comparison to \citet{EgamiYamauchi2023}, and separated
homogeneity from loading/span equality in the sanity corner; prior verdict:
REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Belle'go et~al.(2025)]{BellegoBenatiaDortetBernadet2025}
Belle'go, C., Benatia, D., and Dortet-Bernadet, V. (2025).
The chained difference-in-differences.
\emph{Journal of Econometrics}, 248, 105783.
\url{https://doi.org/10.1016/j.jeconom.2024.105783}.

\bibitem[Borusyak et~al.(2024)]{BorusyakJaravelSpiess2024}
Borusyak, K., Jaravel, X., and Spiess, J. (2024).
Revisiting event-study designs: robust and efficient estimation.
\emph{Review of Economic Studies}, 91(6), 3253--3285.
\url{https://doi.org/10.1093/restud/rdae007}.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and Sant'Anna, P. H. C. (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics}, 225(2), 200--230.
\url{https://doi.org/10.1016/j.jeconom.2020.12.001}.

\bibitem[Chen et~al.(2025)]{ChenSantAnnaXie2025}
Chen, X., Sant'Anna, P. H. C., and Xie, H. (2025).
Efficient difference-in-differences and event study estimators.
arXiv:2506.17729.
\url{https://arxiv.org/abs/2506.17729}.

\bibitem[Egami and Yamauchi(2023)]{EgamiYamauchi2023}
Egami, N. and Yamauchi, S. (2023).
Using multiple pretreatment periods to improve difference-in-differences and
staggered adoption designs.
\emph{Political Analysis}, 31(2), 195--212.
\url{https://doi.org/10.1017/pan.2022.8}.

\bibitem[Roth et~al.(2023)]{RothSantAnnaBilinskiPoe2023}
Roth, J., Sant'Anna, P. H. C., Bilinski, A., and Poe, J. (2023).
What's trending in difference-in-differences? A synthesis of the recent
econometrics literature.
\emph{Journal of Econometrics}, 235(2), 2218--2244.
\url{https://doi.org/10.1016/j.jeconom.2023.03.008}.

\bibitem[Roth and Sant'Anna(2023)]{RothSantAnna2023Efficient}
Roth, J. and Sant'Anna, P. H. C. (2023).
Efficient estimation for staggered rollout designs.
\emph{Journal of Political Economy Microeconomics}, 1(4), 669--709.
\url{https://doi.org/10.1086/726581}.

\bibitem[Sant'Anna and Zhao(2020)]{SantAnnaZhao2020}
Sant'Anna, P. H. C. and Zhao, J. (2020).
Doubly robust difference-in-differences estimators.
\emph{Journal of Econometrics}, 219(1), 101--122.
\url{https://doi.org/10.1016/j.jeconom.2020.06.003}.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021}
Sun, L. and Abraham, S. (2021).
Estimating dynamic treatment effects in event studies with heterogeneous
treatment effects.
\emph{Journal of Econometrics}, 225(2), 175--199.
\url{https://doi.org/10.1016/j.jeconom.2020.09.006}.

\bibitem[Wooldridge(2021)]{Wooldridge2021}
Wooldridge, J. M. (2021).
Two-way fixed effects, the two-way Mundlak regression, and difference-in-
differences estimators.
SSRN working paper 3906345.
\url{https://doi.org/10.2139/ssrn.3906345}.
\end{thebibliography}

\end{document}
