% S9-fragment-statement
\begin{theorem}[Conjecture 2: \(m_n\)-out-of-\(n\) bootstrap law for the Spearman-band endpoints]\label{thm:inference}\label{prop:inference}
\paragraph{Motivating conjecture (verbatim).}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:sampling}--\ref{ass:regular}, \ref{ass:stable-dual}, and \ref{ass:finite-cell}, if \(b_{K_n}=o(n^{-1/2})\), the root-\(n\) local sieve remainder in Assumption~\ref{ass:finite-cell} holds, \(\log K_n/n\to0\), and \(m_n\to\infty\) with \(m_n/n\to0\), then \(\sqrt n(\widehat L_\rho-L_\rho(P),\widehat U_\rho-U_\rho(P))\) converges to a directional endpoint limit law and the \(m_n\)-out-of-\(n\) bootstrap estimates it consistently.

\paragraph{Operational statement.}
For \(K=K_n\), put \(u_\ell=\ell/(K+1)\) and \(a_\pm=(\rho_\pm+3)/12\).  Let
\[
\Pi_K(a_-,a_+)=\left\{\pi\in\mathbb R_+^{K\times K}:
\sum_{m=1}^K\pi_{\ell m}=K^{-1},\
\sum_{\ell=1}^K\pi_{\ell m}=K^{-1},\
a_-\le\sum_{\ell,m=1}^K u_\ell u_m\pi_{\ell m}\le a_+
\right\}.
\]
For each cell \(x_j\), let \(\widehat p_j=n^{-1}\sum_{i=1}^n\one\{X_i=x_j\}\), let \(\widehat Q_d(\cdot\mid x_j)\) be the within-cell treatment-\(d\) empirical quantile, and define the computable endpoint estimators
\[
\widehat L_\rho=\sum_{j=1}^J\widehat p_j
\min_{\pi\in\Pi_{K_n}(a_-,a_+)}
\sum_{\ell,m=1}^{K_n}
\one\{\widehat Q_1(u_\ell\mid x_j)>\widehat Q_0(u_m\mid x_j)\}\pi_{\ell m},
\]
\[
\widehat U_\rho=\sum_{j=1}^J\widehat p_j
\max_{\pi\in\Pi_{K_n}(a_-,a_+)}
\sum_{\ell,m=1}^{K_n}
\one\{\widehat Q_1(u_\ell\mid x_j)>\widehat Q_0(u_m\mid x_j)\}\pi_{\ell m}.
\]
Let \(O_1^*,\ldots,O_{m_n}^*\) be drawn with replacement from the empirical law and let \(\widehat L_\rho^*,\widehat U_\rho^*\) be the same two programs recomputed on the bootstrap sample with the same grid \(K_n\).  Write \(\eta_0=\eta(P)\), let \(\widehat\eta_n\) collect the empirical cell weights and empirical conditional quantiles, and set
\[
\Phi_{\rho,K}(\eta)=(L_{\rho,K}(\eta),U_{\rho,K}(\eta)),\qquad
\Phi_\rho(\eta)=(L_\rho(\eta),U_\rho(\eta)),\qquad
e_K(\eta)=\Phi_{\rho,K}(\eta)-\Phi_\rho(\eta).
\]
Read the root-\(n\) local sieve remainder clause in Assumption~\ref{ass:finite-cell} as the first-order local condition
\[
\sqrt n\{e_{K_n}(\widehat\eta_n)-e_{K_n}(\eta_0)\}=o_p(1).
\]
Under Assumptions~\ref{ass:sampling}--\ref{ass:regular}, \ref{ass:stable-dual}, and \ref{ass:finite-cell}, if \(b_{K_n}=o(n^{-1/2})\), this root-\(n\) local sieve remainder holds, \(\log K_n/n\to0\), and \(m_n\to\infty\) with \(m_n/n\to0\), then
\[
Z_n=\sqrt n\bigl(\widehat L_\rho-L_\rho(P),\,\widehat U_\rho-U_\rho(P)\bigr)
\rightsquigarrow \dot\Phi_{\rho,P}(\mathbb G_P),
\]
and, with
\[
Z_n^*=\sqrt{m_n}\bigl(\widehat L_\rho^*-\widehat L_\rho,\,
\widehat U_\rho^*-\widehat U_\rho\bigr),
\]
\[
d_{\mathrm{BL}}\!\left(\mathcal L^*(Z_n^*\mid O_1,\ldots,O_n),\,
\mathcal L\{\dot\Phi_{\rho,P}(\mathbb G_P)\}\right)\to_p0.
\]
Here \(d_{\mathrm{BL}}\) is the bounded-Lipschitz metric, \(\mathbb G_P\) is the finite-cell empirical-weight and conditional-quantile Gaussian limit, and \(\dot\Phi_{\rho,P}\) is the directional derivative of the endpoint map at \(\eta(P)\).

\paragraph{Stitch headline.}
Theorem 2 (\texttt{inference}) is confirmed: under Assumptions~\ref{ass:sampling}--\ref{ass:regular}, \ref{ass:stable-dual}, and \ref{ass:finite-cell}, define \(\widehat L_\rho=\sum_{j=1}^J\widehat p_j\min_{\pi\in\Pi_{K_n}(a_-,a_+)}\sum_{\ell,m}\one\{\widehat Q_1(u_\ell\mid x_j)>\widehat Q_0(u_m\mid x_j)\}\pi_{\ell m}\) and \(\widehat U_\rho=\sum_{j=1}^J\widehat p_j\max_{\pi\in\Pi_{K_n}(a_-,a_+)}\sum_{\ell,m}\one\{\widehat Q_1(u_\ell\mid x_j)>\widehat Q_0(u_m\mid x_j)\}\pi_{\ell m}\), where \(\Pi_{K_n}(a_-,a_+)=\{\pi\in\mathbb R_+^{K_n\times K_n}:\sum_m\pi_{\ell m}=K_n^{-1},\sum_\ell\pi_{\ell m}=K_n^{-1},a_-\le\sum_{\ell,m}u_\ell u_m\pi_{\ell m}\le a_+\}\) and \(a_\pm=(\rho_\pm+3)/12\). Let \(O_1^*,\ldots,O_{m_n}^*\) be drawn with replacement from the empirical law and let \(\widehat L_\rho^*,\widehat U_\rho^*\) be the same two programs recomputed on the bootstrap sample with the same grid \(K_n\). If \(b_{K_n}=o(n^{-1/2})\), the root-\(n\) local sieve remainder clause holds, meaning with \(e_K(\eta)=\Phi_{\rho,K}(\eta)-\Phi_\rho(\eta)\), \(\eta_0=\eta(P)\), and \(\widehat\eta_n\) the empirical finite-cell summary, \(\sqrt n\{e_{K_n}(\widehat\eta_n)-e_{K_n}(\eta_0)\}=o_p(1)\), \(\log K_n/n\to0\), and \(m_n\to\infty\) with \(m_n/n\to0\), then \(Z_n=\sqrt n(\widehat L_\rho-L_\rho(P),\widehat U_\rho-U_\rho(P))\rightsquigarrow\dot\Phi_{\rho,P}(\mathbb G_P)\) and \(d_{\mathrm{BL}}(\mathcal L^*(Z_n^*\mid O_1,\ldots,O_n),\mathcal L\{\dot\Phi_{\rho,P}(\mathbb G_P)\})\to_p0\) for \(Z_n^*=\sqrt{m_n}(\widehat L_\rho^*-\widehat L_\rho,\widehat U_\rho^*-\widehat U_\rho)\), where \(\mathbb G_P\) is the joint finite-cell empirical-weight and conditional-quantile Gaussian limit and \(\dot\Phi_{\rho,P}\) is the directional derivative of \(\Phi_\rho(\eta)=(L_\rho(\eta),U_\rho(\eta))\) at \(\eta(P)\).
\end{theorem}

% S13-refutation-attempt
\paragraph{Refutation attempt before proof.}
The required finite response-type primitive was checked on the smallest checkerboard transport face.  Take one covariate cell, \(K=2\), \(u_1=1/3\), and \(u_2=2/3\).  Every feasible \(2\times2\) plan with uniform margins has the form
\[
\pi(t)=
\begin{pmatrix}
t & 1/2-t\\
1/2-t & t
\end{pmatrix},
\qquad 0\le t\le 1/2.
\]
Its Spearman moment is
\[
\sum_{\ell,m=1}^2u_\ell u_m\pi_{\ell m}(t)=\frac{2}{9}+\frac{t}{9},
\]
so the band restricts \(t\) to
\[
I_\rho=\left[0,\frac12\right]\cap[9a_- -2,\,9a_+ -2].
\]
For an arbitrary binary benefit table \(h=(h_{\ell m})_{\ell,m\le2}\), the lower objective is
\[
q_h(t)=\sum_{\ell,m=1}^2 h_{\ell m}\pi_{\ell m}(t)
=\frac{h_{12}+h_{21}}{2}
+t(h_{11}-h_{12}-h_{21}+h_{22}).
\]
Enumerating all \(2^4\) benefit tables gives either a nonzero slope, in which case the optimum is a vertex of \(I_\rho\), or a zero slope, in which case the value is constant over \(I_\rho\).  Thus the vertex search produces no finite-face witness against the endpoint map: the local value is piecewise linear, and under a fixed active face its directional derivative is exactly the slope selected by the stable dual face.

This search is not a proof of the asymptotic claim by itself.  It only verifies that the smallest transport face does not contradict the conjecture once the conjecture is read with its root-\(n\) local sieve remainder clause.  The known possible obstruction is the centered checkerboard residual
\[
\sqrt n\{[\Phi_{\rho,K_n}(\widehat\eta_n)-\Phi_\rho(\widehat\eta_n)]
-[\Phi_{\rho,K_n}(\eta_0)-\Phi_\rho(\eta_0)]\},
\]
which is exactly the residual the corrected conjecture assumes away.  No counterexample is produced under the stated active-face, finite-cell, local-sieve-remainder, and \(m_n/n\to0\) regime, so the derivation proceeds to the positive proof.

% S10 Interpretation
\paragraph{Interpretation.}
The theorem is an endpoint-law result for the observable outer-envelope functional \(\mathcal B_\rho(P)=[L_\rho(P),U_\rho(P)]\).  It is not a sharpness theorem for the latent scalar \(\theta\), and it does not require endpoint-attaining copula selectors or a no-gap continuous transport dual.  The sample statistic and the bootstrap statistic are explicit maps from the data through finite-dimensional transport programs.  The role of Stoye's interval-identification analysis is methodological: one first obtains a valid law for estimated lower and upper endpoints, then uses interval-width-aware calibration for a partially identified scalar \cite{Stoye2009MoreCI}.  The \(m_n/n\to0\) condition makes the bootstrap evaluate the same directional derivative as the sample statistic at a nonregular face rather than at a random empirical face.

% S11 Proof
\begin{proof}[Proof of Theorem~\ref{thm:inference}]
Let
\[
\eta_0=\eta(P)=\Bigl((p_j)_{j\le J},\{Q_d(\cdot\mid x_j):d\in\{0,1\},1\le j\le J\}\Bigr),
\]
where \(p_j=\Pr(X=x_j)\).  Let \(\widehat\eta_n\) be the same vector with \(p_j\) and \(Q_d(\cdot\mid x_j)\) replaced by the sample cell frequencies and within-cell treatment-specific empirical quantiles.  Let \(\widehat\eta_{m,n}^*\) be the corresponding vector computed from the \(m_n\)-out-of-\(n\) bootstrap sample.

Assumptions~\ref{ass:sampling}, \ref{ass:unconf}, \ref{ass:continuous}, and \ref{ass:finite-cell} give i.i.d. sampling, finitely many \(X\)-cells with positive masses, propensities bounded away from zero and one, compact conditional supports, and densities bounded above and away from zero.  The finite-dimensional multinomial central limit theorem and the finite collection of conditional quantile Bahadur expansions therefore give
\[
H_n:=\sqrt n(\widehat\eta_n-\eta_0)\rightsquigarrow\mathbb G_P.
\]
The same primitive conditions and the bootstrap grid condition in Assumption~\ref{ass:finite-cell} give
\[
d_{\mathrm{BL}}\!\left(
\mathcal L^*\{\sqrt{m_n}(\widehat\eta_{m,n}^*-\widehat\eta_n)\mid O_1,\ldots,O_n\},
\mathcal L(\mathbb G_P)
\right)\to_p0.
\]
This is the finite-cell empirical-process input for the endpoint-first inference program used in Stoye's interval analysis \cite{Stoye2009MoreCI}.

The displayed programs in the theorem are exactly
\[
(\widehat L_\rho,\widehat U_\rho)=\Phi_{\rho,K_n}(\widehat\eta_n),
\qquad
(\widehat L_\rho^*,\widehat U_\rho^*)=\Phi_{\rho,K_n}(\widehat\eta_{m,n}^*).
\]
With \(e_K(\eta)=\Phi_{\rho,K}(\eta)-\Phi_\rho(\eta)\),
\[
\begin{aligned}
Z_n
&=\sqrt n\{\Phi_{\rho,K_n}(\widehat\eta_n)-\Phi_\rho(\eta_0)\}\\
&=\sqrt n\{\Phi_\rho(\widehat\eta_n)-\Phi_\rho(\eta_0)\}
+\sqrt n\{e_{K_n}(\widehat\eta_n)-e_{K_n}(\eta_0)\}
+\sqrt n\,e_{K_n}(\eta_0).
\end{aligned}
\]
The final term is \(o(1)\) because \(b_{K_n}=o(n^{-1/2})\) controls the pointwise checkerboard bias at \(\eta_0\).  The middle term is \(o_p(1)\) by the root-\(n\) local sieve remainder clause in Assumption~\ref{ass:finite-cell}.  Assumption~\ref{ass:regular} gives directional Hadamard differentiability of \(\Phi_\rho\), hence
\[
\sqrt n\{\Phi_\rho(\widehat\eta_n)-\Phi_\rho(\eta_0)\}
=\dot\Phi_{\rho,P}(H_n)+o_p(1).
\]
Combining the last three displays yields
\[
Z_n=\dot\Phi_{\rho,P}(H_n)+o_p(1)
\rightsquigarrow \dot\Phi_{\rho,P}(\mathbb G_P)
\]
by the continuous mapping theorem for the directional derivative on the stable tangent set.

For the bootstrap statistic, write
\[
H_n^*=\sqrt{m_n}(\widehat\eta_{m,n}^*-\widehat\eta_n),
\qquad
R_n=\sqrt{m_n}(\widehat\eta_n-\eta_0)=\sqrt{\frac{m_n}{n}}\,H_n.
\]
Since \(H_n=O_p(1)\) and \(m_n/n\to0\), \(R_n=o_p(1)\).  The bootstrap path is therefore
\[
\widehat\eta_{m,n}^*=\eta_0+m_n^{-1/2}(R_n+H_n^*),
\qquad
\widehat\eta_n=\eta_0+m_n^{-1/2}R_n.
\]
Decompose
\[
\begin{aligned}
Z_n^*
&=\sqrt{m_n}\{\Phi_{\rho,K_n}(\widehat\eta_{m,n}^*)-\Phi_{\rho,K_n}(\widehat\eta_n)\}\\
&=\sqrt{m_n}\{\Phi_\rho(\widehat\eta_{m,n}^*)-\Phi_\rho(\widehat\eta_n)\}
+\sqrt{m_n}\{e_{K_n}(\widehat\eta_{m,n}^*)-e_{K_n}(\widehat\eta_n)\}.
\end{aligned}
\]
The two bootstrap arguments lie in the deterministic neighborhood \(\mathcal N\) with conditional probability tending to one because Assumption~\ref{ass:stable-dual} gives a neighborhood whose radius dominates \(m_n^{-1/2}\) and Assumption~\ref{ass:finite-cell} gives the bootstrap quantile grid control.  On that event,
\[
\left\|e_{K_n}(\widehat\eta_{m,n}^*)-e_{K_n}(\widehat\eta_n)\right\|
\le 2\sup_{\eta\in\mathcal N_{\mathrm{cb}}}\|e_{K_n}(\eta)\|
=o(m_n^{-1/2})
\]
by the local-uniform checkerboard approximation in Assumption~\ref{ass:finite-cell}.  Hence the second bootstrap term is \(o_p^*(1)\).

For the first bootstrap term, the local drift must be kept explicit.  Put \(t_n=m_n^{-1/2}\).  Assumption~\ref{ass:regular} gives directional Hadamard differentiability of \(\Phi_\rho\) at \(\eta_0\), and Assumption~\ref{ass:stable-dual} keeps the same active face in the neighborhood \(\mathcal N\).  Hence, on every compact tangent set \(C\) on which the derivative is evaluated, the ordinary expansion at the population base is uniform:
\[
\sup_{h\in C}
\left\|t_n^{-1}\{\Phi_\rho(\eta_0+t_n h)-\Phi_\rho(\eta_0)\}
-\dot\Phi_{\rho,P}(h)\right\|\to0 .
\]
This display is only the population-base expansion from Assumption~\ref{ass:regular}; no shifted differentiability assertion is being assumed.  Applying it twice, with \(h=R_n+H_n^*\) and \(h=R_n\), gives conditionally in probability
\[
\begin{aligned}
&\sqrt{m_n}\{\Phi_\rho(\eta_0+t_n(R_n+H_n^*))
-\Phi_\rho(\eta_0+t_nR_n)\}\\
&\qquad =
\dot\Phi_{\rho,P}(R_n+H_n^*)-\dot\Phi_{\rho,P}(R_n)+o_p^*(1).
\end{aligned}
\]
The term suppressed in a naive shifted-delta argument is therefore
\[
A_n^*=
\dot\Phi_{\rho,P}(R_n+H_n^*)-\dot\Phi_{\rho,P}(R_n)
-\dot\Phi_{\rho,P}(H_n^*).
\]
The conditional bootstrap CLT above makes \(H_n^*\) conditionally tight, while \(R_n=o_p(1)\).  Since \(\dot\Phi_{\rho,P}\) is continuous on the stable tangent face and \(\dot\Phi_{\rho,P}(0)=0\), for every compact \(C\) and every \(\varepsilon>0\),
\[
\sup_{\substack{h\in C\\ \|r\|\le\delta}}
\|\dot\Phi_{\rho,P}(r+h)-\dot\Phi_{\rho,P}(h)\|
+\sup_{\|r\|\le\delta}\|\dot\Phi_{\rho,P}(r)\|
\to0
\qquad(\delta\downarrow0).
\]
On the event \(H_n^*\in C\) and \(\|R_n\|\le\delta\), this bound makes \(\|A_n^*\|\) arbitrarily small; the complement has conditional probability tending to zero by tightness and \(m_n/n\to0\).  Thus \(A_n^*=o_p^*(1)\), and
\[
\sqrt{m_n}\{\Phi_\rho(\eta_0+t_n(R_n+H_n^*))
-\Phi_\rho(\eta_0+t_nR_n)\}
=\dot\Phi_{\rho,P}(H_n^*)+o_p^*(1).
\]
Consequently
\[
Z_n^*=\dot\Phi_{\rho,P}(H_n^*)+o_p^*(1)
\]
conditionally in probability.  The conditional bootstrap CLT for \(H_n^*\), followed by the directional continuous mapping theorem on the stable face, gives
\[
d_{\mathrm{BL}}\!\left(\mathcal L^*(Z_n^*\mid O_1,\ldots,O_n),\,
\mathcal L\{\dot\Phi_{\rho,P}(\mathbb G_P)\}\right)\to_p0.
\]
This proves consistency of the \(m_n\)-out-of-\(n\) bootstrap for the directional endpoint law and confirms the conjecture as stated with its root-\(n\) local sieve remainder clause.
\end{proof}

% S12 Sanity check
\paragraph{Sanity check.}
In the regular corner where each endpoint has a unique active optimizer, the Spearman moment binding status is unchanged in the neighborhood from Assumption~\ref{ass:stable-dual}, and the root-\(n\) local sieve remainder is automatic, the derivative \(\dot\Phi_{\rho,P}\) is linear.  If \(A_P\) denotes the corresponding sensitivity operator for the lower and upper endpoints, then
\[
\dot\Phi_{\rho,P}(\mathbb G_P)=A_P\mathbb G_P,
\]
so \(Z_n\) has an ordinary bivariate normal limit with covariance \(A_P\Sigma_PA_P^{\transpose}\).  The \(m_n\)-out-of-\(n\) bootstrap conclusion then reduces to the classical plug-in endpoint bootstrap for two smooth bound estimators.  This is exactly the endpoint-law input used before applying the Imbens--Manski/Stoye interval-width calibration for a scalar lying in \([L_\rho(P),U_\rho(P)]\) \cite{Stoye2009MoreCI}.

% S13 Counterexample or minimality check
\paragraph{Minimality check.}
The condition \(m_n/n\to0\) cannot be replaced by the ordinary \(n\)-out-of-\(n\) bootstrap in a genuinely directional problem.  The scalar analogue is \(\phi(t)=|t|\), with \(W_i\) i.i.d. mean zero and variance one and \(\widehat t_n=n^{-1}\sum_iW_i\).  Then
\[
\sqrt n\{\phi(\widehat t_n)-\phi(0)\}\rightsquigarrow |Z|,
\qquad Z\sim N(0,1).
\]
The ordinary bootstrap has conditional local form
\[
\sqrt n\{|\widehat t_n^*|-|\widehat t_n|\}
=|Z^*+\sqrt n\,\widehat t_n|-|\sqrt n\,\widehat t_n|+o_p^*(1),
\]
whose conditional limit is the random law of \(|Z^*+Z_0|-|Z_0|\) given the realized local drift \(Z_0\), not the fixed law of \(|Z|\).  If \(m_n/n\to0\), then \(\sqrt{m_n}\widehat t_n\to_p0\), and the bootstrap derivative is evaluated at the population face.

The root-\(n\) local sieve remainder is also load-bearing.  Pointwise checkerboard bias at \(\eta_0\) and bootstrap-scale local bias do not imply the sample root-\(n\) expansion.  For the scalar approximation \(\phi(t)=t\), \(\phi_K(t)=t+K^{-1/2}\sin(Kt)\), and \(K_n=n\), one has \(\phi_{K_n}(0)-\phi(0)=0\) and \(\sup_{|t|\le c m_n^{-1/2}}|\phi_{K_n}(t)-\phi(t)|=O(n^{-1/2})=o(m_n^{-1/2})\) whenever \(m_n/n\to0\).  Nevertheless,
\[
\sqrt n\{\phi_{K_n}(h/\sqrt n)-\phi_{K_n}(0)-h/\sqrt n\}
=\sin(\sqrt n\,h),
\]
which need not converge to zero.  This example explains why the corrected theorem explicitly includes the root-\(n\) local sieve remainder; without it, the endpoint expansion can contain an additional first-order approximation term.
