% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_shift\_share\_design, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_shift\_share\_design} / \texttt{v1}%
  \\ \large\textit{A spectral frontier for equivalence and strict separation of Bartik, recentered, and design-based formula IV}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This proposal uses the ExactID tuple
\[
(\texttt{qid},\texttt{specialization},\text{formula-IV DGP},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
The locked convention is:
\begin{quote}
\begin{verbatim}
qid = eid_shift_share_design
specialization = v1
formula-IV DGP = finite-shock linear shift-share design with n units,
  K shock cells, exposure matrix S in R^{n x K}, shock vector G in R^K,
  formula instrument Z = S G, observed covariates C, treatment X, and
  outcome Y = beta_exp X + U.
treatment = the scalar exposure-induced treatment X generated by the same
  shock vector G and exposure matrix S, with nonzero first stage for each
  instrument considered.
target estimand = beta_exp, the structural exposure coefficient in the
  linear outcome equation.
identifying assumptions = consistency, exposure additivity, shock-design
  first-stage relevance, common-support/finite second moments, and the
  three distortion primitives (Omega, Pi, epsilon) defined in Section 6:
  Omega is the shock cross-correlation operator relative to the design law,
  Pi is the residual exposure-share covariance after the locked controls C,
  and epsilon is the covariate-conditional shock-mean leakage vector.
\end{verbatim}
\end{quote}

\begin{abstract}
This proposal asks when three leading formula-IV estimators--canonical Bartik-style shift-share IV, Borusyak--Hull recentered IV, and design-based formula IV--identify the same structural exposure coefficient on a common shift-share DGP.  Existing work gives estimator-specific sufficient conditions, but not a necessary-and-sufficient frontier over the joint geometry of shock dependence, exposure covariance, and covariate-conditional leakage.  The flagship conjecture is a closed-form spectral boundary: the three population moments are equivalent exactly when the spectral radius of $\Pi^{1/2}\Omega\Pi^{1/2}$ is below a threshold $\lambda_\star(\Pi,\epsilon)$ built from the observable residual exposure kernel and the leakage direction.  Above the threshold, canonical Bartik IV has a nonzero limit distortion while recentered and design-based moments remain separated by the leakage projection, with design IV attaining the efficient projection in the correctly specified design class.  Resolving the conjecture would turn the current menu of shift-share validity checks into a single diagnostic that says when correlated shocks are harmless for identification rather than only for inference.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Shift-share and formula-IV designs are used when a scalar treatment or instrument is assembled from many common shocks and predetermined exposure shares.  The empirical question is usually the same--the structural coefficient on exposure--but the current econometric literature offers three nearby routes to it: shock-level SSIV orthogonality, recentering against counterfactual shock realizations, and design-based formula-IV conditioning.  Applied researchers therefore face a practical identification question that is not answered by separate sufficient conditions: whether a given pattern of shock correlation, exposure concentration, and covariate leakage merely changes inference, or actually moves the population estimand.

\paragraph{The main finding (proposed).}
The proposed flagship result is Conjecture~1, a spectral non-equivalence theorem.  Under the locked linear shift-share DGP, let $\rho_{\Omega,\Pi}=\lambda_{\max}(\Pi^{1/2}\Omega\Pi^{1/2})$ and let $\lambda_\star(\Pi,\epsilon)$ be the smallest positive singular value of the observable kernel $K_\epsilon=\Pi^{1/2}M_{\mathcal{D},\epsilon}\Pi^{1/2}$, where $M_{\mathcal{D},\epsilon}$ removes the design-conditioned recentering and leakage-null directions.  The conjecture states that Bartik SSIV, recentered IV, and design-based formula IV have the same identifying moment for $\beta_{\exp}$ if and only if $\rho_{\Omega,\Pi}\leq \lambda_\star(\Pi,\epsilon)$; when the inequality fails, the three limit functionals separate in a direction witnessed by the leading eigenvector of $\Pi^{1/2}\Omega\Pi^{1/2}$.

\paragraph{What is new.}
The novelty kernel is not another sufficient validity condition for shift-share IV.  \citet{BorusyakHullJaravel2022REStud} reduce canonical SSIV orthogonality to shock-level orthogonality under many-shock weak-dependence conditions, \citet{BorusyakHull2023Econometrica} show how recentering removes nonrandom exposure to exogenous shocks, and \citet{BorusyakHullJaravel2025ECTJ} review design-based formula-IV moments.  None of these papers gives an iff boundary comparing all three population moments on the same DGP, and none defines a threshold $\lambda_\star(\Pi,\epsilon)$ that separates inference-only correlation from identifying-moment distortion.

\paragraph{How it positions in the literature.}
This is an exact-identification proposal in the econometric IV family, specialized to formula instruments.  It sits at the frontier between the shock-exogeneity view of \citet{BorusyakHullJaravel2022REStud}, the exposure-share interpretation of \citet{GoldsmithPinkhamSorkinSwift2020AER}, the correlated-residual inference warning of \citet{AdaoKolesarMorales2019QJE}, and the design-based recentering program of \citet{BorusyakHull2023Econometrica,BorusyakHullJaravel2025ECTJ}.  The proposal deliberately treats the SCM/DAG layer as infrastructure and asks a theorem-level econometric question: equality versus strict separation of named IV moments.

\paragraph{Implications for the community.}
If the spectral frontier is correct, users of the China-shock and immigration-style Bartik designs discussed by \citet{BorusyakHullJaravel2022REStud} and \citet{JaegerRuistStuhler2018NBER} would get a computable pre-analysis diagnostic: report $\rho_{\Omega,\Pi}$, $\lambda_\star(\Pi,\epsilon)$, and the leading separation direction before deciding whether canonical SSIV is an identifying design or only a descriptive shift-share regression requiring recentering.

\paragraph{How research benefits from the conclusion.}
A reader should stop treating correlated shocks as only a standard-error issue and instead check the $\Omega$--$\Pi$--$\epsilon$ spectral frontier before choosing canonical Bartik IV over recentered or design-based formula IV.

\section{Related work}
\citet{BorusyakHullJaravel2022REStud} is the canonical shock-level SSIV reference: it shows how shift-share orthogonality can be represented at the shock level and gives sufficient many-shock conditions for consistency.  \citet{AdaoKolesarMorales2019QJE} shows that residual correlation induced by common exposure shares can make conventional shift-share inference overreject, which motivates separating inference distortions from identifying-moment distortions.  \citet{GoldsmithPinkhamSorkinSwift2020AER} gives the leading exposure-share and Rotemberg-weight interpretation of Bartik instruments, providing the closest alternative route to Bartik validity.  \citet{BorusyakHull2023Econometrica} introduces recentered instruments for nonrandom exposure to exogenous shocks and is the closest published paper to the $\epsilon$-null-space part of this proposal.  \citet{BorusyakHullJaravel2025ECTJ} reviews design-based formula instruments, including recentering, controls, heterogeneous effects, multiple instruments, and open inference extensions; it is the closest published paper to the proposed triple-comparison.  \citet{JaegerRuistStuhler2018NBER} gives an applied shift-share warning in immigration designs, where serially stable exposure patterns can conflate short- and long-run responses; this is a concrete consumer of a dependence-frontier diagnostic.  \citet{BlandholBonneyMogstadTorgovitsky2022NBER} studies when IV estimands are weakly causal under flexible controls, which is relevant because residualization changes the effective exposure covariance $\Pi$.

On the in-repository axis, \texttt{doc/API.md} reports that the seed-time \texttt{ThmSmith/ExactID/} and \texttt{ThmSmith/PartialID/} catalogues are empty, so there is no in-catalogue shift-share theorem with the same kernel.  The Stage -1.1 prior-proposal map names \texttt{eid\_lp\_svar\_nonequiv\_v1} as the nearest non-equivalence template, but that proposal concerns row-space and singular-subspace boundaries for local-projection/SVAR objects rather than formula-IV shift-share moments.  It also names \texttt{q1\_spectral\_phase\_transition\_p1\_markov} as a cautionary failed spectral-threshold proposal and \texttt{eid\_dml\_orth\_uniform\_v1} as a warning that orthogonalization separations can collapse at the truth unless the finite-support covariance diagnostic is explicit.  The present proposal responds to those repository signals by making the primitive observable objects $\Omega$, $\Pi$, $\epsilon$, $K_\epsilon$, and $\lambda_\star$ part of the theorem statement.

\section{Formal setup}
There are $n$ observational units and $K$ shock cells.  Let $S\in\R^{n\times K}$ be the exposure-share matrix, $G\in\R^K$ the realized shock vector, $C\in\R^{n\times d}$ observed controls, $X\in\R^n$ the endogenous exposure-induced treatment, and $Y\in\R^n$ the outcome.  The structural equation is
\[
Y_i=\beta_{\exp}X_i+U_i,\qquad i=1,\ldots,n,
\]
and the canonical shift-share instrument is $Z=SG$.  Let $M_C=I-P_C$ be the residual-maker for the locked controls $C$, and define the residual exposure covariance
\[
\Pi=\plim n^{-1}S^\transpose M_C S.
\]
The design law $\mathcal{D}$ specifies the counterfactual distribution of $G$ conditional on the predetermined formula inputs; write $m_{\mathcal{D}}=\E_{\mathcal{D}}[G\mid S,C]$, $\mu=S m_{\mathcal{D}}$, and $\widetilde Z_R=M_C S(G-m_{\mathcal{D}})$ for the recentered instrument.  The design-based shock residual is $\widetilde G_D=M_{\mathcal{D},\epsilon}(G-m_{\mathcal{D}})$, and the design-based instrument is $\widetilde Z_D=M_C S\widetilde G_D$, where $M_{\mathcal{D},\epsilon}$ is the $K\times K$ orthogonal projector that removes the span of the design mean and the leakage direction defined below.

The shock cross-correlation operator is
\[
\Omega=\plim \E[(G-m_{\mathcal{D}})(G-m_{\mathcal{D}})^\transpose\mid S,C]
\]
after normalization to unit marginal shock scale.  The covariate-conditional shock-mean leakage vector is
\[
\epsilon=\plim \Pi^{1/2}\E[G-m_{\mathcal{D}}\mid C],
\]
with $\epsilon=0$ in the correctly centered design.  The central spectral quantities are
\[
\rho_{\Omega,\Pi}=\lambda_{\max}(\Pi^{1/2}\Omega\Pi^{1/2}),\qquad
K_\epsilon=\Pi^{1/2}M_{\mathcal{D},\epsilon}\Pi^{1/2},\qquad
\lambda_\star(\Pi,\epsilon)=\sigma_{\min}^{+}(K_\epsilon),
\]
where $\sigma_{\min}^{+}$ denotes the smallest strictly positive singular value.  For $j\in\{B,R,D\}$, the population IV functional is
\[
\beta_j=\frac{\plim n^{-1}\widetilde Z_j^\transpose Y}{\plim n^{-1}\widetilde Z_j^\transpose X},
\]
with $\widetilde Z_B=M_CSG$, $\widetilde Z_R=M_C S(G-m_{\mathcal{D}})$, and $\widetilde Z_D=M_CSM_{\mathcal{D},\epsilon}(G-m_{\mathcal{D}})$.  For any unit vector $v\in\R^K$, let $L_{\Pi,\epsilon}(v)=v^\transpose \Pi^{1/2}\epsilon$ denote the signed leakage loading used in the local excess-correlation expansion.
Let $\mathcal A_\epsilon=\operatorname{range}(I-M_{\mathcal{D},\epsilon})\cap\operatorname{range}(\Pi)$; this is the finite-dimensional leakage subspace that recentering can leave active but design projection removes.

The locked parameters are reproduced verbatim:
\begin{quote}
\begin{verbatim}
qid = eid_shift_share_design
specialization = v1
formula-IV DGP = finite-shock linear shift-share design with n units,
  K shock cells, exposure matrix S in R^{n x K}, shock vector G in R^K,
  formula instrument Z = S G, observed covariates C, treatment X, and
  outcome Y = beta_exp X + U.
treatment = the scalar exposure-induced treatment X generated by the same
  shock vector G and exposure matrix S, with nonzero first stage for each
  instrument considered.
target estimand = beta_exp, the structural exposure coefficient in the
  linear outcome equation.
identifying assumptions = consistency, exposure additivity, shock-design
  first-stage relevance, common-support/finite second moments, and the
  three distortion primitives (Omega, Pi, epsilon) defined in Section 6:
  Omega is the shock cross-correlation operator relative to the design law,
  Pi is the residual exposure-share covariance after the locked controls C,
  and epsilon is the covariate-conditional shock-mean leakage vector.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Linear formula-IV structural equation]\label{ass:linear}
The observed outcome satisfies $Y_i=\beta_{\exp}X_i+U_i$ for a scalar structural coefficient $\beta_{\exp}$, and the treatment $X_i$ is generated by the same shock vector $G$ and exposure row $S_i$ used to construct $Z_i=S_i^\transpose G$.
\end{assumption}

\begin{assumption}[Exposure additivity]\label{ass:additive}
The formula instrument is additive in shocks, $Z=SG$, and the residualized first stage for each $\widetilde Z_j$, $j\in\{B,R,D\}$, has a nonzero probability limit $\Gamma_j=\plim n^{-1}\widetilde Z_j^\transpose X$ whenever the corresponding functional $\beta_j$ is invoked.
\end{assumption}

\begin{assumption}[Design law and recentering]\label{ass:design}
The counterfactual shock design $\mathcal{D}$ is known, $m_{\mathcal{D}}=\E_{\mathcal{D}}[G\mid S,C]$ exists, and the recentered instrument uses $\mu=S m_{\mathcal{D}}$ before residualizing by $C$.
\end{assumption}

\begin{assumption}[Finite operator limits]\label{ass:limits}
The limits $\Pi$, $\Omega$, $\epsilon$, $\Gamma_B$, $\Gamma_R$, and $\Gamma_D$ exist, $\Pi$ is positive semidefinite on the residual exposure span, and all second moments needed for the displayed population IV functionals are finite.
\end{assumption}

\begin{assumption}[Design projection]\label{ass:projection}
$M_{\mathcal{D},\epsilon}$ is the $K\times K$ orthogonal projector onto the complement of the span generated by the design mean direction and the normalized leakage direction $\epsilon$; when $\epsilon=0$, it reduces to the design-mean residualizer.
\end{assumption}

\begin{assumption}[Nondegenerate spectral kernel]\label{ass:nondegenerate}
Whenever the spectral-frontier conjectures are invoked, $K_\epsilon$ has at least one positive singular value, the first-stage limits $\Gamma_B,\Gamma_R,\Gamma_D$ are nonzero, and any strict-separation sequence has a well-defined leading eigendirection $v_{\max}$ of $\Pi^{1/2}\Omega\Pi^{1/2}$ outside the range of $K_\epsilon$.
\end{assumption}

\begin{assumption}[Correct linear design class]\label{ass:efficient-class}
For efficiency comparisons, the design law $\mathcal{D}$ and the projection $M_{\mathcal{D},\epsilon}$ correctly specify the closed linear span of admissible shock functions available to formula-IV estimators.
\end{assumption}

\begin{assumption}[No omitted non-formula shock channel]\label{ass:no-omitted}
Conditional on $(S,C)$ and the distortion primitives $(\Omega,\epsilon)$, the only violation of the canonical Bartik moment $\plim n^{-1}Z^\transpose U=0$ enters through shock correlation transmitted by $\Pi$ or through the covariate-conditional leakage vector $\epsilon$.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: zero-distortion equivalence]\label{thm:zero-distortion}
Under Assumptions~\ref{ass:linear}--\ref{ass:no-omitted}, if $\Omega=0$ and $\epsilon=0$, then $\beta_B=\beta_R=\beta_D=\beta_{\exp}$.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is not the flagship novelty claim; it is the required anchor showing that the proposed notation reduces to the classical consistency region in \citet{BorusyakHullJaravel2022REStud} and the recentering argument in \citet{BorusyakHull2023Econometrica}.  (b) It makes \citet{BorusyakHullJaravel2022REStud} a sanity-check corollary of the proposed frontier, so applied SSIV users can see that the new diagnostic does not move the accepted uncorrelated-shock benchmark.

\begin{conjecture}[Conjecture 1: spectral equivalence frontier (NOT YET PROVED)]\label{conj:spectral-frontier}
Under Assumptions~\ref{ass:linear}--\ref{ass:no-omitted},
\[
\beta_B=\beta_R=\beta_D=\beta_{\exp}
\quad\Longleftrightarrow\quad
\rho_{\Omega,\Pi}\leq \lambda_\star(\Pi,\epsilon).
\]
Moreover, $\lambda_\star(\Pi,\epsilon)$ is sharp: for every $\delta>0$ there exists a nondegenerate finite-support design with the same $(\Pi,\epsilon)$ and $\rho_{\Omega,\Pi}\in(\lambda_\star,\lambda_\star+\delta)$ for which at least one equality among $\beta_B$, $\beta_R$, $\beta_D$, and $\beta_{\exp}$ fails.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{BorusyakHullJaravel2022REStud}, which gives sufficient shock-level orthogonality and weak-dependence conditions, and \citet{BorusyakHull2023Econometrica}, which gives recentering validity under a specified counterfactual design.  The $\epsilon$-gap is that neither paper states an iff operator boundary comparing canonical, recentered, and design-based formula-IV moments; the proposed advance is the explicit threshold $\lambda_\star(\Pi,\epsilon)$ and the strict finite-support witness just above it.  (b) Resolving this would directly give the design diagnostic requested by the formula-IV review of \citet{BorusyakHullJaravel2025ECTJ}: when a non-iid covariance or leakage pattern requires recentering/design conditioning for identification rather than only different inference.

\begin{conjecture}[Conjecture 2: excess-correlation bias and efficient design separation (NOT YET PROVED)]\label{conj:strict-separation}
Under the hypotheses of Conjecture~\ref{conj:spectral-frontier}, if $\rho_{\Omega,\Pi}>\lambda_\star(\Pi,\epsilon)$, then the canonical Bartik functional satisfies
\[
\beta_B-\beta_{\exp}
=\frac{\rho_{\Omega,\Pi}-\lambda_\star(\Pi,\epsilon)}{\Gamma_B}
\cdot L_{\Pi,\epsilon}(v_{\max})+o(\rho_{\Omega,\Pi}-\lambda_\star(\Pi,\epsilon)),
\]
for the observable signed loading $L_{\Pi,\epsilon}$ defined in the formal setup.  In the same local sequence, $\beta_R-\beta_D$ is exactly the projection of $\epsilon$ onto $\mathcal A_\epsilon$, and $\beta_D$ attains the semiparametric efficiency bound within the correctly specified linear design class of Assumption~\ref{ass:efficient-class}.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{AdaoKolesarMorales2019QJE} treats exposure-induced correlation as an inference problem, while \citet{BorusyakHullJaravel2025ECTJ} discusses optimal formula-instrument construction without a three-way excess-correlation expansion.  The $\epsilon$-gap is the proposed signed excess-bias formula and the identification of the precise leakage projection separating recentered and design IV.  (b) If true, this gives users of the \citet{JaegerRuistStuhler2018NBER} immigration-style shift-share designs a quantitative warning: the leading eigenvector of observed exposure persistence is the direction along which canonical Bartik IV ceases to target the short-run structural effect.

\section{Sanity-check corollaries}
\begin{corollary}[Classical uncorrelated-shock reduction]\label{cor:bhj}
Under Assumptions~\ref{ass:linear}--\ref{ass:no-omitted}, if $\Omega=0$ and $\epsilon=0$, then $\rho_{\Omega,\Pi}=0$ and the proposed frontier collapses to Theorem~\ref{thm:zero-distortion}.
\end{corollary}
This reduction uses Assumptions~\ref{ass:design} and \ref{ass:limits}: with zero shock correlation and zero leakage, $K_\epsilon$ is only a residual exposure kernel and no distortion vector remains for any of the three instruments.

\begin{corollary}[Pure recentering benchmark]\label{cor:recenter}
Under Assumptions~\ref{ass:linear}--\ref{ass:no-omitted}, if $\Omega=0$ and $\epsilon$ lies entirely in the design-mean span removed by $M_{\mathcal{D},\epsilon}$, then $\beta_R=\beta_D=\beta_{\exp}$ and any remaining difference between $\beta_B$ and $\beta_{\exp}$ is the canonical nonrandom-exposure component removed by recentering.
\end{corollary}
This reduction uses Assumptions~\ref{ass:design} and \ref{ass:projection}: when leakage is in the removed design span, $M_{\mathcal{D},\epsilon}$ and recentering annihilate the same direction.

\section{Proof-sketch route}
The mathematical route is finite-dimensional linear IV algebra plus operator perturbation.  First, write each population numerator as a bilinear form in $(S,G,U)$ after residualizing by $C$, and decompose it into an $\Omega$ term, a design-mean term, and an $\epsilon$ term by the law of iterated expectations.  Second, express equality of the three IV functionals as equality of three normalized bilinear forms on the residual exposure span, reduce that system to a null-space condition for $K_\epsilon$, and apply the min--max characterization of singular values to obtain the candidate threshold.  Third, check sharpness by two-by-two and three-by-three finite-support matrices whose leading eigenvector crosses the range of $K_\epsilon$, then paste those witnesses into open neighborhoods of observable $(\Omega,\Pi,\epsilon)$ without changing the first-stage signs.  The efficiency component in Conjecture~\ref{conj:strict-separation} should reduce to the usual linear IV tangent-space projection after conditioning on the design sigma-field.

\section{Honest scope flags}
Theorem~\ref{thm:zero-distortion} is intended as routine algebra and a benchmark, not a new flagship contribution.  Conjectures~\ref{conj:spectral-frontier} and \ref{conj:strict-separation} are not yet proved; their sharpness and efficiency clauses are the main research risk.  The definition of $M_{\mathcal{D},\epsilon}$ may need refinement if the design mean direction and leakage direction are not linearly independent, though the current statement handles this by using the span and $\sigma_{\min}^{+}$.  No v1 material has been withdrawn because this is the initial draft.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft of the spectral equivalence frontier for canonical Bartik, recentered, and design-based formula IV; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Adao, Kolesar, and Morales(2019)]{AdaoKolesarMorales2019QJE}
Adao, Rodrigo, Michal Kolesar, and Eduardo Morales. 2019.
``Shift-Share Designs: Theory and Inference.''
\emph{Quarterly Journal of Economics} 134(4): 1949--2010.

\bibitem[Blandhol, Bonney, Mogstad, and Torgovitsky(2022)]{BlandholBonneyMogstadTorgovitsky2022NBER}
Blandhol, Christine, John Bonney, Magne Mogstad, and Alexander Torgovitsky. 2022.
``When Is TSLS Actually LATE?''
NBER Working Paper 29709.

\bibitem[Borusyak, Hull, and Jaravel(2022)]{BorusyakHullJaravel2022REStud}
Borusyak, Kirill, Peter Hull, and Xavier Jaravel. 2022.
``Quasi-Experimental Shift-Share Research Designs.''
\emph{Review of Economic Studies} 89(1): 181--213.

\bibitem[Borusyak and Hull(2023)]{BorusyakHull2023Econometrica}
Borusyak, Kirill, and Peter Hull. 2023.
``Nonrandom Exposure to Exogenous Shocks.''
\emph{Econometrica} 91(6): 2155--2185.

\bibitem[Borusyak, Hull, and Jaravel(2025)]{BorusyakHullJaravel2025ECTJ}
Borusyak, Kirill, Peter Hull, and Xavier Jaravel. 2025.
``Design-Based Identification with Formula Instruments: A Review.''
\emph{Econometrics Journal} 28(1): 83--108.

\bibitem[Goldsmith-Pinkham, Sorkin, and Swift(2020)]{GoldsmithPinkhamSorkinSwift2020AER}
Goldsmith-Pinkham, Paul, Isaac Sorkin, and Henry Swift. 2020.
``Bartik Instruments: What, When, Why, and How.''
\emph{American Economic Review} 110(8): 2586--2624.

\bibitem[Jaeger, Ruist, and Stuhler(2018)]{JaegerRuistStuhler2018NBER}
Jaeger, David A., Joakim Ruist, and Jan Stuhler. 2018.
``Shift-Share Instruments and the Impact of Immigration.''
NBER Working Paper 24285.
\end{thebibliography}

\end{document}
