Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). If \(k_a\le M\), the order-statistic identity gives
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.\tag{1}
\]
Indeed, the \(k_a\)-th calibration order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by strict comparison and the event depends on \(s_a\) only through its total preorder. If \(k_a=M+1\), then \(Q_{k_a}=+\infty\) by \(\texttt{def:rank-inversion}\), so that arm's event is certain.

Conversely, let a total preorder have ordered nonempty tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\). If \(d_a=1\), assign score zero. If \(d_a>1\), assign \((j-1)K/(d_a-1)\) to class \(C_{a,j}\). Since \(K>0\), this defines a map into \([0,K]\), realizes exactly the chosen preorder, and uses at most \(d_a\le m_a\) levels. Therefore finite enumeration of the relevant total preorders attains the maximum in \(\texttt{def:coverage-frontier}\). This establishes exactness for the declared bounded orbit-constant score class only; it does not identify a supremum over all laws in \(\mathcal P_{\mathcal G,K}\).

Suppose first that \(k_0,k_1\le M\). Apply \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). It retains the coherent common-target law
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}\tag{2}
\]
and the full joint calibration law
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).\tag{3}
\]
Thus neither the target lifts nor the calibration selectors are factorized. For each preorder pair \(C\), the lemma pushes (2) to \(P_T^C\), forms the exact prefix-table vectors \(\pi^C(j,\ell)\), and proves that the coupled recurrence value depends only on \(\pi^C(j,\ell)\) and \(M,k_0,k_1\). With \(L_C=|\operatorname{supp}(P_T^C)|\) and \(U_C\) the number of distinct supported exact vectors, it gives \(U_C\le L_C\le\min\{L,d_0d_1\}\) and the exact representation
\[
\Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).\tag{4}
\]
A balanced tree keyed by three independent exact coordinates groups the \(L_C\) supported pairs in \(O(L_C\log(1+L_C))\) comparisons, with \(O(L_C)\) mass-aggregation arithmetic, after which (4) uses one recurrence for each of the \(U_C\) keys. Summing the lemma's per-preorder cost over the \(F_{m_0}F_{m_1}\) preorder pairs proves
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)+\sum_{C\in\mathfrak C}\left[L_C\log(1+L_C)+L_C+U_C\{1+Mk_0k_1\}\right]
\right).\tag{5}
\]
Putting \(L_{\max}=\max_C L_C\) and \(U_{\max}=\max_C U_C\) gives the asserted uniform bound
\[
O\!\left(|\mathcal V|+F_{m_0}F_{m_1}\left[m_0m_1+L+L_{\max}\log(1+L_{\max})+L_{\max}+U_{\max}\{1+Mk_0k_1\}\right]\right),\tag{6}
\]
and the exact-key table contributes \(O(U_{\max})\) to the lemma's working-memory bound
\[
O(m_0m_1+L+k_0k_1+U_{\max}).\tag{7}
\]
Equations (2)--(4) show directly that this caching preserves both kinds of dependence required by the theorem.

Suppose next that exactly one rank \(k_b=M+1\), and put \(c=1-b\). By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), the boundary-arm event is certain and disappears from the conjunction. Conditional on \(O_{T,c}=O_t\), (1) is the event that a binomial random variable with success probability
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O}\tag{8}
\]
is smaller than \(k_c\). Averaging over the target orbit yields
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}\Pr\!\left\{\operatorname{Bin}\bigl(M,\theta(O_t)\bigr)<k_c\right\}.\tag{9}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), put
\[
q_j=q_c(C_j),\qquad p_j=p_c(C_j),\qquad \theta_j=\sum_{\ell<j}q_\ell.\tag{10}
\]
All target orbits in \(C_j\) share \(\theta_j\), so (9) becomes
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}.\tag{11}
\]
One ordered-class scan forms (10). For \(0<\theta<1\), consecutive binomial masses satisfy
\[
t_0=(1-\theta)^M,\qquad t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},\quad 0\le r<k_c-1,\tag{12}
\]
and
\[
u_M=\theta^M,\qquad u_{r-1}=u_r\frac{r}{M-r+1}\frac{1-\theta}{\theta},\quad k_c<r\le M.\tag{13}
\]
Exponentiation by squaring initializes either endpoint in \(O(\log M)\) operations. The exact evaluator \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\) then sums the shorter lower or complementary upper tail in \(O(\min\{k_c,M-k_c+1\})\) operations and constant memory. At \(\theta=0\), the probability is one; at \(\theta=1\), it is zero because \(k_c\le M\). Hence no endpoint division occurs. Enumerating the \(F_{m_c}\) nonboundary preorders proves the stated one-boundary cost and the absence of any boundary-arm preorder, member, or orbit-table factor.

If both ranks equal \(M+1\), both rank events are certain. Therefore the probability in \(\texttt{def:coverage-frontier}\) is one and
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=[(1-\alpha)-1]_+=0.\tag{14}
\]

It remains to verify the nonbinary witness. Take four pair blocks, \(\mathcal G=S_2^4\), independent fair within-pair assignments, and a singleton selector library. In either arm let the selector choose blocks with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)\tag{15}
\]
and then choose the unique member observed in that arm. This kernel is observable and equivariant under every within-pair swap. Give the common target block probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\qquad q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2}.\tag{16}
\]
For \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=3\). Put \(s_0\equiv0\) and order the arm-one blocks as \(1\prec3\prec2\prec4\). Arm zero never fails, whereas arm one fails exactly when all three calibration blocks lie strictly below the target block. Its failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.\tag{17}
\]
The frontier objective is therefore
\[
\frac{104957}{160000}-\frac12=\frac{24957}{160000}.\tag{18}
\]
For binary maps let \(H_a\) be the high-score block set and put \(A_a=(1-q(H_a))^3\). Conditional on the common target block, arm \(a\) fails exactly when that block is in \(H_a\) and all calibration blocks are outside \(H_a\). Inclusion--exclusion gives
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\tag{19}
\]
Order the sixteen subsets as
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.
\]
For each fixed \(H_0\), exact substitution of all sixteen choices of \(H_1\) into (19) gives the following row maxima, with denominator \(320000000\):
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}\tag{20}
\]
This exhausts all \(16^2\) binary pairs. Their maximum failure probability is \(208582976/320000000=3259109/5000000\), so their maximum frontier objective is \(759109/5000000\). The four-level improvement is
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\tag{21}
\]
Thus binary maps need not attain the frontier.

Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Assign score \(K\) to every target-supported arm-\(a\) orbit, score zero to all other arm-\(a\) orbits, and score zero in the other arm. The target score in arm \(a\) is always \(K\), every calibration score there is zero, and its rank threshold is zero. Thus the joint rank event has probability zero and
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha,\tag{22}
\]
the largest value permitted by its definition. If one rank is at the boundary, (8)--(13) give the exact reduction to the other arm. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), and \(\texttt{def:coverage-frontier}\) gives \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w)\). Hence the symmetric frontier theorem is recovered.