For \(w\in\Delta(\mathcal H)\), define
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|(Aw-b_{\mathrm{LP}})_{a,O}|.
\tag{1}
\]
The row identities proved in \(\texttt{thm:common-selector-lp}\) imply
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|\delta_{a,O}(w)|=\Delta_0(w)+\Delta_1(w).
\tag{2}
\]
Because \(\mathcal H\) is finite and nonempty, \(\Delta(\mathcal H)\) is a nonempty compact simplex. The continuous function \(d\) attains its minimum, so \(D_*\) is attained and \(\mathcal W_*\ne\varnothing\).

For fixed \(w\), the two-sided constraints in the displayed absolute-value program are equivalent to
\[
t_{a,O}\ge |(Aw-b_{\mathrm{LP}})_{a,O}|.
\tag{3}
\]
Thus every feasible \((w,t)\) has objective at least \(d(w)\), while choosing equality in (3) makes the objective exactly \(d(w)\). It follows that the primal value is \(D_*\), and its optimizing \(w\)-coordinates are precisely \(\mathcal W_*\).

For the quantitative dual, put
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\},\qquad b=b_{\mathrm{LP}}.
\]
Then
\[
D_*=\min_{c\in C}\frac12\lVert c-b\rVert_1.
\tag{4}
\]
For every \(y\) with \(\lVert y\rVert_\infty\le1/2\) and every \(c\in C\), finite-dimensional H"older inequality gives
\[
y^\top(c-b)\le\lVert y\rVert_\infty\lVert c-b\rVert_1\le\frac12\lVert c-b\rVert_1.
\tag{5}
\]
Taking first the minimum over \(c\) and then the maximum over \(y\) proves weak duality. If \(D_*=0\), the feasible vector \(y=0\) proves equality. Assume henceforth that \(D_*>0\). For \(n\ge2\), set \(r_n=(1-1/n)D_*\) and
\[
B_n=\{x:\tfrac12\lVert x-b\rVert_1\le r_n\}.
\]
By (4), the nonempty compact convex sets \(B_n\) and \(C\) are disjoint. Choose a Euclidean closest pair \((c_n,x_n)\in C\times B_n\) and set \(v_n=c_n-x_n\ne0\). Directional differentiation along line segments in the two convex sets yields
\[
\min_{c\in C}v_n^\top c\ge v_n^\top c_n>v_n^\top x_n\ge\max_{x\in B_n}v_n^\top x.
\tag{6}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). Then \(\lVert y_n\rVert_\infty=1/2\). The support function of \(B_n\) is
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b+2r_n\lVert y_n\rVert_\infty=y_n^\top b+r_n.
\tag{7}
\]
Indeed, H"older inequality gives the upper bound, and equality is attained by moving from \(b\) a signed distance \(2r_n\) in a coordinate on which \(|(y_n)_j|=1/2\). Equations (6)--(7) imply
\[
\min_{c\in C}y_n^\top c-y_n^\top b\ge r_n.
\tag{8}
\]
The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact. Along a convergent subsequence, \(y_n\to y_*\). Since \(\mathcal H\) is finite,
\[
\min_{c\in C}y^\top c=\min_{h\in\mathcal H}y^\top A_{\cdot h}
\tag{9}
\]
is continuous in \(y\). Letting \(n\to\infty\) in (8) and combining with weak duality proves the attained identity
\[
D_*=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.
\tag{10}
\]
If \(D_*>0\) and \(y\) maximizes (10), then \(y^\top A_{\cdot h}\ge y^\top b_{\mathrm{LP}}+D_*\) for every \(h\). Hence \(z=-y\) satisfies
\[
z^\top b_{\mathrm{LP}}\ge\max_{h\in\mathcal H}z^\top A_{\cdot h}+D_*,
\tag{11}
\]
which is the asserted Farkas separating direction and margin.

By nonnegativity of (1), \(D_*=0\) exactly when some \(w\in\Delta(\mathcal H)\) satisfies \(Aw=b_{\mathrm{LP}}\). The common-selector theorem identifies this with feasibility of the exact joint-balance LP. Every entry of \(A\) is computed from the known assignment law and selector kernels, and \(b_{\mathrm{LP}}\) is computed from the prespecified target rule. Thus any optimizer \(w_*\) can be chosen before scores are observed and is prespecified.

Fix such a \(w_*\), condition on \(\mathcal T\), and apply \(\texttt{prop:asymmetric-finite-rank-orbit-gap-bound}\). By (2) and optimality, \(\Delta_0(w_*)+\Delta_1(w_*)=D_*\), so
\[
\Pr_P\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right)\ge\max\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\right\}.
\tag{12}
\]
For arbitrary \(w\in\Delta(\mathcal H)\), optimality gives \(D_*\le\Delta_0(w)+\Delta_1(w)\). Since \(x\mapsto\max\{0,c-x\}\) is nonincreasing, (12) weakly dominates the certificate for \(w\). If the imbalance inequality is strict and the untruncated right side of (12) is positive, this dominance is strict, including when the comparator is truncated at zero. Finally, when \(\varepsilon_0=\varepsilon_1=\alpha/2\), the definitions give \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\) and \(\mathcal C^{\boldsymbol\varepsilon}_{w_*}=\mathcal C_{w_*}\); substituting these identities in (12) proves the equal-split formula.