Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\), \(k_0=k_1=k\), and by \(\texttt{def:coverage-frontier}\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
The exactness and preorder-attainment assertions now follow from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\): on the diagonal it maximizes the same objective over the same bounded orbit-constant score maps. In particular, the rank event depends on each score map only through its total preorder, and a preorder with \(d_a\) nonempty ordered tie classes is represented in \([0,K]\) by assigning zero when \(d_a=1\), and by assigning \((j-1)K/(d_a-1)\) to the \(j\)-th class when \(d_a>1\). This uses at most \(d_a\le m_a\) levels. Hence the finite enumeration attains the maximum; it does not enlarge the declared score class or identify a supremum over \(P\in\mathcal P_{\mathcal G,K}\).

We next specialize the cached evaluator. For an orbit \(O\in\mathcal O_a\), write
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z).
\]
For \(v\in\mathcal V\), let \(O_a(v)\) denote the orbit containing \((v,a)\). The shared assignment induces the joint calibration-orbit law
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z),
\tag{2}
\]
whereas the one common target induces
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}.
\tag{3}
\]
Thus neither the two target lifts nor the two calibration selectors have been replaced by independent marginals. Let \(L=|\operatorname{supp}(P_T)|\). For a preorder pair \(C=(c_0,c_1)\), push (3) forward to its ordered class indices, obtaining \(P_T^C\), and put \(L_C=|\operatorname{supp}(P_T^C)|\). For every supported class pair \((j,\ell)\), the two-dimensional prefix table of (2) gives the exact four-cell vector
\[
\pi^C_{xy}(j,\ell)=\sum_{O_0,O_1}R_w(O_0,O_1)\mathbf 1\!\left\{\mathbf 1\{c_0(O_0)<j\}=x,\ \mathbf 1\{c_1(O_1)<\ell\}=y\right\},
\qquad (x,y)\in\{0,1\}^2.
\tag{4}
\]
Let \(\Pi_C\) be the set of distinct vectors in (4) on \(\operatorname{supp}(P_T^C)\), and let \(U_C=|\Pi_C|\). The exact-vector-cached construction of \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) gives
\[
U_C\le L_C\le\min\{L,d_0d_1\}
\tag{5}
\]
and, for the fixed preorder pair,
\[
\Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k,k}(\pi),
\tag{6}
\]
where \(\omega_C(\pi)\) is the total coherent target mass of the supported class pairs having key \(\pi\), and \(D_{M,k,k}(\pi)\) is the coupled two-count recurrence value. Equation (6) proves that one recurrence per distinct exact vector is sufficient, while (2) and (3) show that caching preserves shared-assignment dependence and common-target coherence.

Let \(\mathfrak C\) denote the \(F_{m_0}F_{m_1}\) preorder pairs. When \(k\le M\), substitute \(k_0=k_1=k\) into the instance-adaptive bound in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). Building (3), constructing each prefix table, grouping the \(L_C\) supported pairs by three independent exact coordinates in a deterministic balanced tree, aggregating their masses, and running the \(U_C\) recurrences require
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)+\sum_{C\in\mathfrak C}\left[L_C\log(1+L_C)+L_C+U_C\{1+Mk^2\}\right]
\right)
\tag{7}
\]
unit-cost exact comparisons and arithmetic operations after \(R_w\) is tabulated. With \(L_{\max}=\max_C L_C\) and \(U_{\max}=\max_C U_C\), (7) is at most
\[
O\!\left(|\mathcal V|+F_{m_0}F_{m_1}\left[m_0m_1+L+L_{\max}\log(1+L_{\max})+L_{\max}+U_{\max}\{1+Mk^2\}\right]\right).
\tag{8}
\]
The prefix and target tables, two-count recurrence arrays, and current exact-key table use
\[
O(m_0m_1+L+k^2+U_{\max})
\tag{9}
\]
working memory. This is precisely the diagonal of the accepted cached asymmetric evaluator.

If \(k=M+1\), both armwise order-statistic operators equal \(+\infty\) by \(\texttt{def:rank-inversion}\). Both rank events are therefore certain, and (1) gives
\[
\Gamma_{M,\alpha}(w)=[(1-\alpha)-1]_+=0,
\tag{10}
\]
which is evaluated in constant time. This also agrees with \(\texttt{prop:rank-boundary}\).

The admissible four-pair construction in \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\) already has \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so it lies on the diagonal (1). The asymmetric theorem's exhaustive evaluation gives the four-level objective, largest binary objective, and their difference as
\[
\frac{24957}{160000},\qquad \frac{759109}{5000000},\qquad \frac{83189}{20000000}>0,
\tag{11}
\]
respectively. Hence binary scores need not attain the symmetric frontier. Finally, if target and calibration orbit supports are disjoint in one arm and \(k\le M\), the diagonal specialization of the asymmetric theorem assigns score \(K\) to target-supported orbits and zero to calibration-supported orbits in that arm, with score zero in the other arm. The joint rank event then has probability zero, so
\[
\Gamma_{M,\alpha}(w)=[(1-\alpha)-0]_+=1-\alpha.
\tag{12}
\]
Equations (1)--(12) prove every assertion of the proposed synchronized statement.