First suppose \(\mathcal H=\varnothing\). By \(\texttt{def:minimum-imbalance-common-selector}\), \(\Delta(\mathcal H)=\varnothing\), so no selector mixture, implemented kernel, selector-indexed procedure, imbalance minimum, optimizer set, or selected optimizer exists. This case is distinct from an empty active-arm set with a finite nonempty library.

Now suppose \(\mathcal H\) is finite and nonempty. For a row set \(\mathcal I\), write \(A_{\mathcal I}\) and \(b_{\mathcal I}\) for the corresponding restrictions and put
\[
d_{\mathcal I}(w)=\frac12\lVert A_{\mathcal I}w-b_{\mathcal I}\rVert_1.
\tag{1}
\]
Let \(\mathcal I_{\mathrm{all}}\) contain every pair \((a,O)\), and let \(\mathcal I_{\mathcal A}=\{(a,O):a\in\mathcal A_{\boldsymbol\varepsilon},\ O\in\mathcal O\}\). The row identity in \(\texttt{thm:common-selector-lp}\) gives
\[
d_{\mathcal I_{\mathrm{all}}}(w)=\Delta_0(w)+\Delta_1(w),\qquad d_{\mathcal I_{\mathcal A}}(w)=\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w).
\tag{2}
\]
Because \(\Delta(\mathcal H)\) is a nonempty compact simplex and (1) is continuous, both the full and active-row minima are attained. Consequently \(\mathcal W_*\) and \(\mathcal W_{*,\mathcal A}\) are nonempty. If \(\mathcal I_{\mathcal A}=\varnothing\), the active objective is identically zero, and therefore
\[
D_{*,\mathcal A}=0,\qquad \mathcal W_{*,\mathcal A}=\Delta(\mathcal H).
\tag{3}
\]
For either nonempty row set, the two-sided slack constraints are equivalent to \(t_j\ge |(A_{\mathcal I}w-b_{\mathcal I})_j|\). Minimization over the slacks makes equality hold coordinatewise, so the declared absolute-value programs have values \(D_*\) and \(D_{*,\mathcal A}\).

We derive the dual for an arbitrary nonempty row set \(\mathcal I\). Define
\[
C_{\mathcal I}=\operatorname{conv}\{(A_{\cdot h})_{\mathcal I}:h\in\mathcal H\},\qquad D_{\mathcal I}=\min_{c\in C_{\mathcal I}}\frac12\lVert c-b_{\mathcal I}\rVert_1.
\tag{4}
\]
For every \(y\) with \(\lVert y\rVert_\infty\le1/2\), Hölder's inequality gives
\[
\min_{c\in C_{\mathcal I}}y^\top(c-b_{\mathcal I})\le D_{\mathcal I}.
\tag{5}
\]
If \(D_{\mathcal I}=0\), equality is attained at \(y=0\). Suppose \(D_{\mathcal I}>0\). For \(n\ge2\), put \(r_n=(1-1/n)D_{\mathcal I}\) and
\[
B_n=\left\{x:\frac12\lVert x-b_{\mathcal I}\rVert_1\le r_n\right\}.
\]
The compact convex sets \(B_n\) and \(C_{\mathcal I}\) are disjoint. Choose a Euclidean closest pair \((c_n,x_n)\) and set \(v_n=c_n-x_n\ne0\). Minimality along line segments implies
\[
\min_{c\in C_{\mathcal I}}v_n^\top c=v_n^\top c_n>v_n^\top x_n=\max_{x\in B_n}v_n^\top x.
\tag{6}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). The support function of the displayed \(\ell_1\)-ball is
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b_{\mathcal I}+2r_n\lVert y_n\rVert_\infty=y_n^\top b_{\mathcal I}+r_n.
\tag{7}
\]
It follows from (6)--(7) that \(\min_{c\in C_{\mathcal I}}y_n^\top c-y_n^\top b_{\mathcal I}>r_n\). The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact. Along a convergent subsequence, continuity of the minimum of the finitely many linear forms and (5) yield
\[
D_{\mathcal I}=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top(A_{\cdot h})_{\mathcal I}-y^\top b_{\mathcal I}\right\}.
\tag{8}
\]
The full-row choice gives the displayed dual for \(D_*\). For active rows, extend \(y\) by zero on inactive rows; this gives the displayed dual for \(D_{*,\mathcal A}\). When the active set is empty, the only admissible supported vector is zero and the dual value is zero, consistently with (3).

If \(D_*>0\) and \(y^*\) maximizes the full dual, then \((y^*)^\top A_{\cdot h}\ge(y^*)^\top b_{\mathrm{LP}}+D_*\) for every \(h\). Thus \(z=-y^*\) satisfies
\[
z^\top b_{\mathrm{LP}}\ge\max_{h\in\mathcal H}z^\top A_{\cdot h}+D_*,
\]
so \(z\) is a Farkas separating direction with margin \(D_*\). Nonnegativity and attainment show that \(D_*=0\) exactly when some \(w\in\Delta(\mathcal H)\) satisfies \(Aw=b_{\mathrm{LP}}\), which \(\texttt{thm:common-selector-lp}\) identifies with exact joint balance. The same argument on active rows shows that \(D_{*,\mathcal A}=0\) exactly when one common selector balances all active rows; this is a joint two-arm characterization only when both arms are active.

The matrix \(A\) depends only on the known assignment law and selector library, \(b_{\mathrm{LP}}\) only on the target rule, and \(\mathcal A_{\boldsymbol\varepsilon}\) only on \(M\) and the prespecified error allocation. Thus deterministic tie-breaking makes both \(w_*\) and \(w_{*,\mathcal A}\) prespecified. By (2) and active-row optimality,
\[
\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w_{*,\mathcal A})=D_{*,\mathcal A}.
\tag{9}
\]
Apply \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) to \(w_{*,\mathcal A}\). Equation (9) gives
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_{*,\mathcal A}}\mid\mathcal T\right\}\ge\max\!\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\rho_{M,\varepsilon_a}-D_{*,\mathcal A}\right\}.
\tag{10}
\]
For any fixed common \(w\), optimality gives \(D_{*,\mathcal A}\le\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w)\). Monotonicity of \(x\mapsto\max\{0,x\}\) proves weak dominance, and dominance is strict when the active imbalance is strictly smaller and the optimized untruncated bound is positive. With exactly one boundary arm, only the other arm's rows and rank penalty occur. If no arm is active, (3) holds, no LP need be solved, and coverage is one.

For the unchanged full diagnostic, any \(w_*\in\mathcal W_*\) satisfies \(\Delta_0(w_*)+\Delta_1(w_*)=D_*\) by (2). Applying \(\texttt{prop:asymmetric-finite-rank-orbit-gap-bound}\), or equivalently adding the nonnegative inactive penalties to its sharper active-arm bound, gives
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right\}\ge\max\!\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\right\}.
\tag{11}
\]
The optimality of \(D_*\) proves its stated weak and strict dominance claims relative to every fixed common selector. On the finite-rank equal-split diagonal, both arms are active, so \(D_{*,\mathcal A}=D_*\), \(\mathcal W_{*,\mathcal A}=\mathcal W_*\), and (10)--(11) reduce to \(\max\{0,1-2\rho_{M,\alpha}-D_*\}\). At the two-boundary elbow coverage is one.