Condition throughout on \(\mathcal T\), so the trained maps are fixed. By \(\texttt{lem:orbit-score-factorization}\), for each arm \(a\) there are orbit-specific probability laws \(F_{a,O}\) such that, for every Borel set \(C\), a calibration orbit--score pair and the independent target orbit--score pair satisfy
\[
\Pr(O_{i,a}=O,S_{i,a}\in C\mid\mathcal T)=q_{a,O}F_{a,O}(C),\qquad \Pr(O_{T,a}=O,S_{0,a}\in C\mid\mathcal T)=p_{a,O}F_{a,O}(C).
\tag{1}
\]
The same lemma states that the \(M\) calibration pairs are conditionally independent and identically distributed and are independent of the target pair, separately for each arm.

Suppose joint orbit balance holds. Then \(q_{a,O}=p_{a,O}\) for every arm and orbit. Summing the two identities in (1) over \(O\) gives, for every Borel set \(C\),
\[
\Pr(S_{i,a}\in C\mid\mathcal T)=\sum_Oq_{a,O}F_{a,O}(C)=\sum_Op_{a,O}F_{a,O}(C)=\Pr(S_{0,a}\in C\mid\mathcal T).
\tag{2}
\]
Combining (2) with the independence conclusion of the factorization lemma shows that \(S_{1,a},\ldots,S_{M,a},S_{0,a}\) are conditionally independent and identically distributed for each fixed arm \(a\). This argument is armwise only: it neither factors the two lifts of the common target nor removes the within-replicate dependence induced by the common assignment.

Conversely, suppose that for some arm \(a\) and orbit \(O\), one has \(q_{a,O}\ne p_{a,O}\). Use \(\texttt{def:orbit-separating-law}\), take a fixed covariate value, and set both trained maps equal to zero. All outcomes lie in \(\{0,K\}\), so \(\texttt{ass:bounded-potential-outcomes}\) holds. Because \(O\) is a \(\mathcal G\)-orbit,
\[
\mathbf 1\{g\cdot(v,a)\in O\}=\mathbf 1\{(v,a)\in O\}\qquad\text{for every }g\in\mathcal G.
\tag{3}
\]
Thus the orbit-constant prototype is invariant under every group relabelling; its stated uniform symmetrization is therefore invariant as well. The constructed law consequently belongs to \(\mathcal P_{\mathcal G,K}\), and the known invariant randomization and observable selector generate the declared experiment. For this law the arm \(a\) score is exactly
\[
S=K\mathbf 1\{\text{the selected arm-}a\text{ state lies in }O\}.
\tag{4}
\]
The definitions of the calibration and target orbit masses therefore give
\[
\Pr(S_{i,a}=K\mid\mathcal T)=q_{a,O},\qquad \Pr(S_{0,a}=K\mid\mathcal T)=p_{a,O}.
\tag{5}
\]
These score laws differ. Hence equality of calibration and target score laws for every bounded invariant law and every fixed measurable trained map forces every orbit equation \(q_{a,O}=p_{a,O}\). Applying the argument in both arms gives joint orbit balance. Equations (2) and (5) establish the claimed equivalence and the explicit bounded witness.