Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\), \(k_0=k_1=k\), and by \(\texttt{def:coverage-frontier}\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w). \tag{1}
\]
The exactness and preorder-attainment assertions follow from the diagonal section of \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). Explicitly, when \(k\le M\),
\[
s_a(O_{T,a})\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\Longleftrightarrow\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k. \tag{2}
\]
Thus only total preorders matter. Assigning score zero to a one-class preorder, and \((j-1)K/(d_a-1)\) to class \(j\) when there are \(d_a>1\) classes, realizes every preorder in \([0,K]\). This proves attainment over the declared bounded orbit-constant score class and makes no law-level sharpness claim.

The coherent evaluator uses
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z) \tag{3}
\]
and
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}. \tag{4}
\]
The first is the unchanged full shared-assignment calibration law; the second is the unchanged coherent law of the two lifts of the single target. For each preorder pair \(C\), its prefix table of (3) gives exact vectors \(\pi^C(j,\ell)\), while the pushforward of (4) gives local weights
\[
\omega_C(\pi)=\sum_{(j,\ell):\pi^C(j,\ell)=\pi}P_T^C(j,\ell). \tag{5}
\]
Consequently, with \(D_{M,k,k}(\pi)\) denoting the coupled recurrence value, the exact rank-event probability is
\[
\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k,k}(\pi). \tag{6}
\]
This displays separately the source of calibration dependence and the source of target coherence.

The local per-preorder cache gives the instance-adaptive and uniform bounds stated before the global refinement. For the refinement, define
\[
\Pi_\star=\bigcup_{C\in\mathfrak C}\Pi_C,\qquad G=|\Pi_\star|. \tag{7}
\]
Use one global memo keyed exactly by
\[
(M,k,k,\pi_{00},\pi_{01},\pi_{10}),\qquad \pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10}. \tag{8}
\]
The recurrence in \(\texttt{lem:four-cell-rank-event-dynamic-program}\) uses only this key. It never uses the local weight (5), which is multiplied only when (6) is formed. Therefore the \(G\) globally distinct vectors require \(GMk^2\) recurrence operations, and the \(\sum_CU_C\) local occurrences require deterministic balanced-tree lookup cost \(O((\sum_CU_C)\log(1+G))\). Adding the unchanged prefix, pushforward, and local-grouping costs proves
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)+\sum_{C\in\mathfrak C}\left[L_C\log(1+L_C)+L_C+U_C\right]+\left\{\sum_{C\in\mathfrak C}U_C\right\}\log(1+G)+GMk^2
\right), \tag{9}
\]
and the uniform bound
\[
O\!\left(|\mathcal V|+F_{m_0}F_{m_1}\left[m_0m_1+L+L_{\max}\log(1+L_{\max})+L_{\max}+U_{\max}\{1+\log(1+G)\}\right]+GMk^2\right). \tag{10}
\]
The orbit tables, coherent target table, rolling recurrence arrays, current local weight table, and global memo use respectively \(O(m_0m_1)\), \(O(L)\), \(O(k^2)\), \(O(U_{\max})\), and \(O(G)\) memory. This proves
\[
O(m_0m_1+L+k^2+U_{\max}+G). \tag{11}
\]
Equations (3)--(8) show that the global memo changes only computational reuse.

If \(k=M+1\), both rank events are certain, so
\[
\Gamma_{M,\alpha}(w)=[(1-\alpha)-1]_+=0. \tag{12}
\]
The four-pair construction in the asymmetric theorem has \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), and hence lies on the diagonal (1). Its four-level objective, best binary objective, and strict difference are
\[
\frac{24957}{160000},\qquad \frac{759109}{5000000},\qquad \frac{83189}{20000000}>0. \tag{13}
\]
Thus binary maps need not attain the symmetric frontier. Finally, under disjoint target and calibration orbit support in arm \(a\) and \(k\le M\), give score \(K\) to the target-supported orbits and zero to the calibration-supported orbits in that arm, with the other-arm score identically zero. The joint rank event then has probability zero, so
\[
\Gamma_{M,\alpha}(w)=1-\alpha. \tag{14}
\]
This proves every assertion of the revised equal-split theorem.
\paragraph{Diagonal corner-oriented refinement.}
Set
\[
\bar k=\min\{k,M-k+1\},\qquad
C_{M,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2. \tag{15}
\]
The diagonal specialization of \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) evaluates every exact key (8) in \(O(C_{M,k})\) recurrence operations and \(O(\bar k^2)\) recurrence workspace. Thus the recurrence terms \(GMk^2\) in (9)--(10) are superseded by \(GC_{M,k}\), and the \(k^2\) component of (11) is superseded by \(\bar k^2\). These sharper bounds imply the frozen ones because
\[
C_{M,k}\le M\bar k^2\le Mk^2. \tag{16}
\]

Let \(\mathsf B\) be the non-evaluator part of (9), let
\(\mathsf T=\mathsf T_{M,k,k}\), and partition the exact keys into
\(\Pi_{\mathrm{MS}}\) and \(\Pi_{\mathrm{DP}}\). The selected-branch charge is
\[
O\!\left(
\mathsf B+M+
\sum_{\pi\in\Pi_{\mathrm{MS}}}(M+\mathsf T)
+|\Pi_{\mathrm{DP}}|C_{M,k}
\right), \tag{17}
\]
and time selection gives
\[
O\!\left(
\mathsf B+M+
G\min\{M+\mathsf T,C_{M,k}\}
\right). \tag{18}
\]
Sequential processing uses
\[
O\!\left(
m_0m_1+L+U_{\max}+G+
\max\{M,\bar k^2\}
\right) \tag{19}
\]
working memory. The coherent weights, full shared-assignment law, exact-key memo, and common-target pushforward are the same as in (3)--(8). In particular, when \(k=M\), the recurrence width is one in each coordinate and its per-key cost is \(O(M)\).
