Define the realized events
\[
E_{\mathrm{joint}}=\{Y_{0T}(1)\in I^{\boldsymbol\varepsilon}_{1,w},\ Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{0,w}\},\qquad
E_{\mathrm{eff}}=\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\}.
\]
By \(\texttt{def:rank-inversion}\), \(\mathcal C^{\boldsymbol\varepsilon}_w=I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}\). On \(E_{\mathrm{joint}}\), put \(y_1=Y_{0T}(1)\) and \(y_0=Y_{0T}(0)\). Then the definition of the Minkowski difference gives
\[
\tau_T=y_1-y_0\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{A}
\]
Thus \(E_{\mathrm{joint}}\subseteq E_{\mathrm{eff}}\), and monotonicity of conditional probability yields the displayed inequality. The reverse containment is false in general: if both intervals are \(\{0\}\) and \(Y_{0T}(0)=Y_{0T}(1)=K\), then \(\tau_T=0\in\mathcal C^{\boldsymbol\varepsilon}_w=\{0\}\) although neither armwise outcome lies in its interval. Consequently the probability in \(\texttt{def:coverage-frontier}\) is a joint-armwise-inclusion probability, and its maximized shortfall is exactly a certificate deficit for that sufficient event, not the actual effect-set coverage deficit.

For a finite rank \(k_a\), the order-statistic identity
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\quad\Longleftrightarrow\quad
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a
\tag{1}
\]
shows that the event depends on \(s_a\) only through its total preorder on \(\mathcal O_a\). Conversely, for ordered nonempty classes \(C_{a,1}\prec\cdots\prec C_{a,d_a}\), assign score zero if \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes the preorder in \([0,K]\) with at most \(m_a\) levels. Thus the maximum in \(\texttt{def:coverage-frontier}\) is attained over the finite set of \(F_{m_0}F_{m_1}\) preorder pairs. This proves exactness over the declared bounded orbit-constant score class; it asserts neither equality with actual effect-set coverage nor equality with a supremum over latent laws.

When both ranks are finite, \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) gives
\[
\Pr\{\text{both rank events under }C\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
That lemma integrates total selector kernels only through assignments in \(\operatorname{supp}(\nu)\); every off-support term has zero \(\nu\)-weight. It proves the displayed seven-way partition, the branch sum \(\mathsf B\), both enumeration bounds, and memory \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\), including constant workspace and absence of factorial preprocessing for face and rank-one keys. It also proves the three strict identities and resource comparisons for the edge, face, and rank-one audits, together with all displayed ranks and budgets.

If exactly one rank \(k_b=M+1\), \(\texttt{prop:asymmetric-rank-boundary}\) makes its event certain. With \(c=1-b\), conditioning on \(O_{T,c}=O_t\) in (1) gives a binomial count with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over the target orbit yields the stated one-arm formula. The ordered-class scan and exact shorter-tail recurrence in \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) give the asserted \(F_{m_c}\)-preorder time and constant auxiliary distribution-function memory. If both ranks are \(M+1\), both events are certain, so the positive-part certificate deficit is zero.

We next verify binary nonattainment by an explicit admissible four-pair construction. Take four pair blocks under the product swap group, independent fair one-treated--one-control assignment in each block, and label the four arm-specific block orbits by \(1,2,3,4\) in both arms. Let the selector first choose a block with calibration masses
\[
q=(13/20,1/20,1/4,1/20)
\]
and then select that block's unique observed member in the requested arm. The two auxiliary arm draws are independent conditional on the assignment, as required by \(\texttt{ass:selector-auxiliary-randomization}\). Let the common target choose one fixed member in each block with block masses
\[
p=(1/20,1/10,1/4,3/5).
\]
These kernels are legal and equivariant on the invariant assignment support and may be extended arbitrarily off it. Take arm \(0\) constant and order arm \(1\) as \(1\prec3\prec2\prec4\). For \(M=3\) and \(k_0=k_1=3\), the joint-event failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\]
Because \(1-\alpha=1/2\), the four-level certificate objective is \(24957/160000\).

For binary high-score sets \(H_0,H_1\), an arm fails exactly when the common target lies in its high set and all three calibration draws lie outside it. Inclusion--exclusion, common-target coherence, and independent auxiliary arm draws give joint-event failure probability
\[
p(H_0)\{1-q(H_0)\}^3+p(H_1)\{1-q(H_1)\}^3-p(H_0\cap H_1)\{1-q(H_0)\}^3\{1-q(H_1)\}^3.
\tag{3}
\]
Order the sixteen subsets as \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\). Exact substitution in (3), maximizing over \(H_1\) for each successive \(H_0\), gives the following failure-probability numerators over denominator \(320000000\):
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\]
Subtracting \(1/2\), the largest binary certificate objective is \(759109/5000000\), and
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.
\]
Thus binary scores are not universally extremal.

Finally, suppose target and calibration orbit supports are disjoint in a finite-rank arm. Give score \(K\) to every target-supported orbit and zero to every calibration-supported orbit in that arm, and use zero scores in the other arm. The adverse event in (1) fails surely, while the other arm's event holds surely. Thus the joint rank-event probability is zero and the certificate objective is \(1-\alpha\). No objective can exceed \(1-\alpha\), proving equality. Setting \(\varepsilon_0=\varepsilon_1=\alpha/2\) gives \(k_0=k_1=k\) by \(\texttt{lem:armwise-finite-rank-staircase}\), which proves the equal-split specialization. Every computational prepass changes only the exact evaluation of (2), so it changes none of the stated active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit semantics.