The generator \(s_b\) interchanges the two members of block \(b\) and preserves the arm label. Therefore, directly from \(\texttt{def:pair-action}\), \[s_b(v_{b,r},a)=(v_{b,1-r},a),\qquad r,a\in\{0,1\},\] while all outside members are fixed and complete records are relabelled according to \(\texttt{def:group-action}\). The two points \((v_{b,0},a)\) and \((v_{b,1},a)\) are mutually reachable and no point with the other arm label is reachable. Thus the two arm-specific orbits are exactly \(O_{b,0}\) and \(O_{b,1}\) displayed in the proposition.

For the proposed exclusive mate rule, the target arm \(1\) orbit vector assigns mass one to \(O_{b,1}\), whereas the mate's control state belongs to the disjoint orbit \(O_{b,0}\). Hence the candidate calibration vector has zero mass in the \((1,O_{b,1})\) row and cannot equal the target vector in that row. It is therefore not jointly orbit balancing and cannot satisfy the corresponding stacked LP equations. Moreover, an arm \(1\) calibration analogue made exclusively from an arm \(0\) state is not legal because an arm \(1\) calibration law is supported on \(\mathcal U_1\). Thus the mate-control proposal is excluded before outcomes are used.

For any legal implemented arm \(1\) calibration law satisfying \(q^{\mathrm{obs}}_{w,1}(O_{b,1})=0\), while the target is supported on \(O_{b,1}\), the disjoint-orbit premise does hold. If \(k\le M\), \(\texttt{prop:disjoint-orbit-witness}\) then supplies the bounded invariant zero-coverage law. If \(k=M+1\), \(\texttt{prop:rank-boundary}\) instead gives \(\mathcal C_w=\mathbb R\) and coverage one. These cases exhaust the possible values of \(k\).