Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\), \(k_0=k_1=k\), and \(\texttt{def:coverage-frontier}\) gives
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
All exactness, attainment, and coherence claims now follow from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\) on this diagonal. In detail, when \(k\le M\), each rank event is equivalent to a strict-below count smaller than \(k\), so only a total preorder matters and every preorder has a representative in \([0,K]\). For each preorder pair the exact probability is
\[
\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k,k}(\pi),
\]
where each \(\pi\) comes from the unchanged full \(R_w\) and each weight from the coherent pushforward of the one common target. The key \((M,k,k,\pi_{00},\pi_{01},\pi_{10})\) therefore permits exactly the claimed global reuse. The coherent evaluator supplies the two displayed time bounds and the displayed memory bound.

For the directive's sharper diagonal certificate, put
\[
\bar k=\min\{k,M-k+1\},\qquad C_{M,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2.
\]
For every exact key, compare the permuted zero-cell-safe multinomial branch \(M+\mathsf T_{M,\bar k,\bar k}\), the rolling branch \(C_{M,k}\), and the positive-corner coefficient branch \(\mathsf C_+(\pi)\). The latter minimizes over all orientations with positive base atom and includes the marginal tails required to reconstruct the original lower--lower event. The three-way sequential charge and its branch-conditional workspace are exactly equations (7)--(8) of \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) with \(k_0=k_1=k\). Since \(C_{M,k}\le M\bar k^2\le Mk^2\), these sharper bounds imply the coarser resource displays in the theorem. In particular, at \(k=M\), the rolling width is one in each coordinate.

If \(k=M+1\), both rank events are certain and (1) makes the frontier zero. The four-pair construction and exhaustive binary calculation in the asymmetric theorem lie on the diagonal and give respectively \(24957/160000\), \(759109/5000000\), and the positive gap \(83189/20000000\). The same theorem's disjoint-support score construction makes one rank event fail surely when \(k\le M\), giving frontier \(1-\alpha\). This proves all assertions.