For a finite rank \(k_a\), the order-statistic identity
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\quad\Longleftrightarrow\quad
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a
\tag{1}
\]
shows that the event depends on \(s_a\) only through its total preorder on \(\mathcal O_a\). Conversely, for ordered nonempty classes \(C_{a,1}\prec\cdots\prec C_{a,d_a}\), assign score zero if \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes the preorder in \([0,K]\) with at most \(m_a\) levels. Thus the maximum in \(\texttt{def:coverage-frontier}\) is attained over the finite set of \(F_{m_0}F_{m_1}\) preorder pairs. This proves exactness over the declared orbit-constant score class; it does not assert equality with a supremum over latent laws.

When both ranks are finite, \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) gives
\[
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
That lemma integrates the total selector kernels only through assignments in \(\operatorname{supp}(\nu)\); every off-support term has zero \(\nu\)-weight. Its three witness lookup tables are complete on their respective supports. It proves the displayed seven-way partition, the branch sum \(\mathsf B\), both enumeration bounds, and memory \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\), including the constant workspace and absence of factorial preprocessing for face and rank-one keys. It also proves the three strict identities and resource comparisons for the edge, face, and rank-one audits, together with all displayed ranks and budgets.

If exactly one rank \(k_b=M+1\), \(\texttt{prop:asymmetric-rank-boundary}\) makes its event certain. With \(c=1-b\), conditioning on \(O_{T,c}=O_t\) in (1) gives a binomial count with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over the target orbit yields the stated one-arm formula. The ordered-class scan and exact shorter-tail recurrence in \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) give the asserted \(F_{m_c}\)-preorder time and constant auxiliary distribution-function memory. If both ranks are \(M+1\), both events are certain, and the positive-part deficit is zero.

We next verify binary nonattainment. Use four orbit labels with calibration masses
\[
q=(13/20,1/20,1/4,1/20)
\]
and common-target masses
\[
p=(1/20,1/10,1/4,3/5).
\]
These masses are realized on invariant one-treated--one-control assignment support by kernels that, on every supported assignment and in each arm, first choose a block with law \(q\) and then choose its unique observed arm member; extend the kernels arbitrarily off support. Take arm \(0\) constant and order arm \(1\) as \(1\prec3\prec2\prec4\). For \(M=3\) and \(k_0=k_1=3\), the failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\]
Because \(1-\alpha=1/2\), the four-level objective is \(24957/160000\). For binary high-score sets \(H_0,H_1\), inclusion--exclusion and the independent auxiliary selector draws give failure probability
\[
p(H_0)\{1-q(H_0)\}^3+p(H_1)\{1-q(H_1)\}^3
-p(H_0\cap H_1)\{1-q(H_0)\}^3\{1-q(H_1)\}^3.
\tag{3}
\]
Ordering the sixteen subsets as \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\), exact maximization of (3) over \(H_1\) for each successive \(H_0\) gives, over denominator \(320000000\),
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\]
The largest binary objective is therefore \(759109/5000000\), and
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\]
Thus binary scores are not universally extremal.

Finally, suppose target and calibration orbit supports are disjoint in a finite-rank arm. Give score \(K\) to every target-supported orbit and zero to every calibration-supported orbit in that arm, and use zero scores in the other arm. The adverse event in (1) fails surely, so the joint rank-event probability is zero and the frontier objective is \(1-\alpha\). No objective can exceed \(1-\alpha\), proving equality. Setting \(\varepsilon_0=\varepsilon_1=\alpha/2\) gives \(k_0=k_1=k\) by \(\texttt{lem:armwise-finite-rank-staircase}\), and hence yields \(\texttt{thm:sharp-orbit-coverage-frontier}\). Since every computational prepass changes only the exact evaluation of (2), it changes none of the stated active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit semantics.