Write \(p_{xy}=\pi_{xy}\). Since the four masses sum to one, the determinant identity gives
\[
\begin{aligned}
\theta_0\theta_1
&=(p_{10}+p_{11})(p_{01}+p_{11})\\
&=p_{10}p_{01}+p_{11}(p_{10}+p_{01}+p_{11})\\
&=p_{00}p_{11}+p_{11}(1-p_{00})=p_{11}.
\end{aligned}
\tag{1}
\]
It follows successively that
\[
p_{10}=\theta_0(1-\theta_1),\qquad
p_{01}=(1-\theta_0)\theta_1,\qquad
p_{00}=(1-\theta_0)(1-\theta_1).
\tag{2}
\]
Substitution of (1)--(2) into the one-draw generating function proves
\[
p_{00}+p_{10}x+p_{01}y+p_{11}xy
=\{(1-\theta_0)+\theta_0x\}\{(1-\theta_1)+\theta_1y\}.
\tag{3}
\]
Independence of the \(M\) draws raises (3) to the \(M\)-th power. The resulting bivariate generating function is the product of the generating functions of \(\operatorname{Bin}(M,\theta_0)\) and \(\operatorname{Bin}(M,\theta_1)\). Hence \(R\) and \(S\) are independent with the asserted marginals, and
\[
\Pr\{R<k_0,S<k_1\}
=H_{M,k_0}(\theta_0)H_{M,k_1}(\theta_1).
\tag{4}
\]
The equality \(p_{00}p_{11}=p_{01}p_{10}\) is checked by two exact products and one exact comparison, without tolerance or approximation. By \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), factor \(a\) in (4) costs
\[
O\!\left(1+\lceil\log_2M\rceil+\bar k_a\right)
\]
exact operations and constant workspace. Sequentially evaluating the two factors and multiplying them gives the stated \(O(\mathsf R_{M,k_0,k_1})\) time and \(O(1)\) workspace.

We verify the design witness. Take
\[
\mathcal V_1=\{v_{1,0},v_{1,1}\},\qquad
\mathcal V_2=\{v_{2,0},v_{2,1}\},\qquad
\mathcal G=\{e\}.
\]
In each block independently, assign exactly one member to treatment, choosing either member with probability \(1/2\). The resulting four-point assignment law is known and invariant under the trivial group, as required by \(\texttt{ass:known-matched-randomization}\). Let \(\mathcal H=\{h\}\) and \(w_h=1\). For every supported assignment, \(\kappa_{h,0}\) is the point mass on block \(1\)'s unique control and \(\kappa_{h,1}\) is the point mass on block \(2\)'s unique treated member. These kernels select only observed arm states, so \(\texttt{ass:observable-selector-kernel}\) holds; equivariance is automatic for the trivial group. Because the kernels are point masses, their conditional product is exactly the auxiliary law in \(\texttt{ass:selector-auxiliary-randomization}\).

Set \(q_{\mathrm{tar}}=\delta_{v_{2,0}}\), independently of the calibration records, as required by \(\texttt{ass:prespecified-target}\). Every arm-labelled state is a singleton orbit. In arm \(0\), place \((v_{1,0},0)\) strictly below the target orbit \((v_{2,0},0)\) and place \((v_{1,1},0)\) in the target tie class. Then the arm-\(0\) strict-prefix indicator is Bernoulli \(1/2\) and depends only on block \(1\)'s assignment. In arm \(1\), place the mate-treatment state \((v_{2,1},1)\) strictly below the target state \((v_{2,0},1)\). Then the arm-\(1\) strict-prefix indicator is Bernoulli \(1/2\) and depends only on block \(2\)'s assignment. Independence of the two block assignments therefore gives
\[
\pi_{00}=\pi_{01}=\pi_{10}=\pi_{11}=\frac14.
\tag{5}
\]
This proves both the exact determinant identity and the displayed product formula for the witness.

Put \(N=M+1=2n+1\). Direct calculation gives
\[
\left\lceil N(1-\varepsilon_0)\right\rceil
=\lceil n\rceil=n,
\qquad
\left\lceil N(1-\varepsilon_1)\right\rceil
=\lceil n+2\rceil=n+2.
\tag{6}
\]
Moreover, \(\varepsilon_0,\varepsilon_1>0\) for \(n\ge3\), their sum is \(2n/(2n+1)=\alpha<1\), and both ranks are at most \(M=2n\). Thus every rank and budget condition is satisfied.

For this witness,
\[
\bar k_0=n,qquad \bar k_1=n-1.
\tag{7}
\]
The prescribed shorter-tail recurrences evaluate respectively \(n\) and \(n-1\) nonzero terms, so the rank-one branch takes \(\Theta(n)=\Theta(M)\) arithmetic and constant workspace. The rolling charge contains \(\Theta(n)\) terminal stages with \(n(n-1)\) retained states and is \(\Theta(n^3)\), with \(\Theta(n^2)\) workspace. The multinomial term count has \(\Theta(n^2)\) pairs \((r,s)\) for which the inner range has \(\Theta(n)\) values, so it is \(\Theta(n^3)\), with \(\Theta(n)\) power-table workspace. Finally, every cell in (5) is positive after every corner orientation, while each transformed threshold is \(\Theta(n)\). Hence every positive-corner coefficient rectangle has \(\Theta(n^2)\) entries and \(\Theta(n)\) rolling width. The least former branch is therefore the coefficient branch with \(\Theta(M^2)\) time and \(\Theta(M)\) workspace, and every former branch has time at least \(\Omega(M^2)\). This proves the strict resource separation.