Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). For \(k_a\le M\), \[s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\Longleftrightarrow\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.\tag{1}\] Indeed, the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Hence ties are handled by the strict comparison and the event depends only on the score map's total preorder. Conversely, if the ordered nonempty classes are \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). Every preorder is therefore represented in \([0,K]\) with at most \(m_a\) levels, so the finite maximum is attained. This is exactness for the declared orbit-constant class only. Suppose first that both ranks are finite. By \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\), the unchanged shared-assignment law \(R_w\) and coherent common-target law \(P_T\) give, for every preorder pair, \[U_C\le L_C\le\min\{L,d_0d_1\},\qquad \Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).\tag{2}\] Thus the exact key \((M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10})\) determines the count probability, while \(\omega_C\) is applied only when the preorder objective is formed. The local grouping, global lookup, one computation per one of the \(G\) keys, and table costs in that lemma prove both time displays and the memory display. Because every \(\pi\) is made from the full \(R_w\) and every weight from the pushforward of the one \(P_T\), memoization changes no probability law. The same proof records the three exact per-key alternatives: zero-cell-safe multinomial summation, corner-oriented rolling recurrence, and positive-base coefficient recurrence. Selecting among them changes only arithmetic, and branch-conditional workspace is the workspace of the actual selected branch; the displayed coarser bounds follow from the rolling option. Now suppose exactly one rank \(k_b=M+1\) and put \(c=1-b\). The boundary event is certain. Conditional on \(O_{T,c}=O_t\), (1) counts iid Bernoulli trials with success probability \[\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.\tag{3}\] Target independence therefore gives \[\sum_{O_t}p_{c,O_t}\Pr\{\operatorname{Bin}(M,\theta(O_t))<k_c\}.\tag{4}\] Grouping a preorder into ordered tie classes gives the stated \(\sum_jp_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}\) and one cumulative scan forms all masses. For \(0<\theta<1\), ratios of consecutive binomial probabilities yield the two displayed recurrences. Exponentiation by squaring initializes an endpoint in \(O(\log M)\), and choosing the shorter tail gives \(O(\min\{k_c,M-k_c+1\})\) further operations. Degeneracy gives probabilities one and zero at \(\theta=0,1\), respectively. Since (4) contains only the nonboundary preorder, \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) gives exactly the asserted one-arm complexity. If both ranks equal \(M+1\), both events are certain and \([(1-\alpha)-1]_+=0\). For nonbinary attainment, specialize to four pair blocks with \(\mathcal G=S_2^4\), so all local swap subgroups required by the corrected pair definition are present. Use fair independent pair assignment, an equivariant selector choosing blocks with probabilities \(q=(13/20,1/20,1/4,1/20)\), and target block probabilities \(p=(1/20,1/10,1/4,3/5)\), split equally within each pair. With \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), one has \(k_0=k_1=3\). Taking \(s_0\equiv0\) and ordering arm one as \(1\prec3\prec2\prec4\) gives failure probability \[\frac14(13/20)^3+\frac1{10}(18/20)^3+\frac35(19/20)^3=\frac{104957}{160000},\] hence objective \(24957/160000\). For a binary pair let \(H_a\) be arm \(a\)'s high-score block set and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion gives the exact joint failure probability \[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\tag{5}\] Enumerate the sixteen subsets in the order \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\). Exact substitution in (5), maximizing over \(H_1\) for each successive \(H_0\), gives row maxima with common denominator \(320000000\): \[(164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).\] Thus the largest binary failure probability is \(3259109/5000000\), the largest binary frontier objective is \(759109/5000000\), and its gap below the four-level objective is \(83189/20000000>0\). Finally, if target and calibration supports are disjoint in an arm with finite rank, assign score \(K\) to its target-supported orbits and zero elsewhere and assign zero throughout the other arm. One rank event then fails surely, so the frontier reaches its maximal possible value \(1-\alpha\). At a boundary rank, (4) is exactly the remaining arm's event. On the equal-split diagonal, \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), yielding \(\texttt{thm:sharp-orbit-coverage-frontier}\).