Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values of \(s_a\) outside \(\mathcal O_a\) are irrelevant. If \(k_a\le M\), define the total preorder \(O\preceq_a O'\) if and only if \(s_a(O)\le s_a(O')\). Then
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\#\{i:s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Thus the joint event depends only on the two induced total preorders. Conversely, if a preorder has ordered tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). This is a representative in \([0,K]\) with \(d_a\le m_a\) levels. If \(k_a=M+1\), its armwise event is identically true, so the same finite reduction applies. The number of total preorders on an \(m\)-element labelled set is the ordered Bell number
\[
F_m=\sum_{d=1}^m d!\left\{\begin{matrix}m\\d\end{matrix}\right\}.
\tag{2}
\]
Hence a maximum is attained after checking \(F_{m_0}F_{m_1}\) preorder pairs. Since this is exactly the maximizing class in \(\texttt{def:coverage-frontier}\), the enumeration is exact within that class and does not enlarge it to arbitrary invariant latent laws.

For evaluability, define the proof intermediate
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z)
\]
and the joint calibration orbit mass
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).
\tag{3}
\]
The auxiliary-product assumption makes the two selector draws conditionally independent given their shared assignment, so \((3)\) is their joint orbit law. Across replicates these orbit pairs are independent and identically distributed. If \(O_a(v)\) denotes the orbit containing \((v,a)\), a fixed preorder pair has joint rank-event probability
\[
\begin{aligned}
&\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\sum_{((O_{i,0},O_{i,1}))_{i=1}^M\in(\mathcal O_0\times\mathcal O_1)^M}
\left\{\prod_{i=1}^M R_w(O_{i,0},O_{i,1})\right\}\\
&\quad\times\prod_{a=0}^1
\mathbf 1\!\left\{s_a(O_a(v))\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\right\}.
\end{aligned}
\tag{4}
\]
This finite sum preserves the common target member and the within-replicate cross-arm coupling. It assumes neither target-arm nor calibration-arm independence.

Let \(n=m_0m_1\). After the \(n^M\) configuration weights in \((4)\) are tabulated, enumerate configurations in reflected \(n\)-ary order so consecutive configurations change one replicate coordinate. For each target and preorder pair, the two strict-lower counts in \((1)\) then update in constant time after an \(O(M)\) initialization. When \(n\ge2\), \(M=O(n^M)\); when \(n=1\), the sum is immediate. Multiplying by the numbers of targets and preorder pairs gives
\[
O\!\left(F_{m_0}F_{m_1}|\mathcal V|(m_0m_1)^M\right).
\tag{5}
\]

To disprove binary attainment in the generalized family, use its symmetric subcase. Take four pair blocks, group \(S_2^4\), and the invariant assignment law that treats exactly one member per pair, equiprobably within each pair. Let the selector library be a singleton. Given an assignment, in either arm choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\]
and select that block's unique observed arm member. This selector is observable and equivariant, its block law is \(q\), and \(R_w(b_0,b_1)=q_{b_0}q_{b_1}\). Let
\[
q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},
\qquad
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right).
\]
Set \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Set \(s_0\equiv0\), and order the arm-one blocks as \(1\prec 3\prec 2\prec 4\), represented by \(0,K/3,2K/3,K\). Arm one fails exactly when all three calibration blocks lie strictly below the target, with probability
\[
F_{\mathrm{multi}}
=\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\tag{6}
\]
Arm zero never fails, so the frontier objective is \(F_{\mathrm{multi}}-\alpha=24957/160000\).

For a binary map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be its high-score blocks and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion conditional on the common target block gives the probability that at least one arm fails:
\[
F_{\mathrm{bin}}(H_0,H_1)
=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{7}
\]
In the row order
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
exhaustive rational substitution of all sixteen choices for the other arm yields row maxima, over denominator \(320000000\),
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{8}
\]
Thus all \(16^2\) binary pairs are exhausted and
\[
\max_{H_0,H_1}F_{\mathrm{bin}}(H_0,H_1)=\frac{3259109}{5000000}.
\]
The largest binary objective is \(759109/5000000\), and the strict gap is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\tag{9}
\]

Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Put score \(K\) on target-supported orbits in that arm and zero elsewhere, and put zero in the other arm. The arm-\(a\) target score is always \(K\), while all its calibration scores are zero, so its rank event is impossible. The joint event in \((4)\) has probability zero and the objective equals its universal upper bound \(1-\alpha\). Hence \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha\).

If \(k_a=M+1\), then \(Q_{k_a}=+\infty\), so that arm's indicator in \((4)\) is one for every score map. Removing this factor gives exactly the other arm's frontier. If both ranks equal \(M+1\), the joint event has probability one and the frontier is zero. This proves the exact one-arm and two-arm boundary clauses. The diagonal identities in the four corrected definitions recover every formula and conclusion of the symmetric frontier theorem.