Fix an arm \(a\in\{0,1\}\) and work conditionally on \(\mathcal T\). By \(\texttt{lem:orbit-score-factorization}\), for every Borel set \(C\subseteq[0,\infty)\),
\[
\Pr(S_{i,a}\in C\mid\mathcal T)=\sum_{O\subseteq\mathcal U_a}q_{a,O}F_{a,O}(C),\qquad\Pr(S_{0,a}\in C\mid\mathcal T)=\sum_{O\subseteq\mathcal U_a}p_{a,O}F_{a,O}(C).\tag{1}
\]
If joint orbit balance holds, then \(q_{a,O}=p_{a,O}\) for every arm and orbit by \(\texttt{def:joint-orbit-balance}\). Substitution in \( (1) \) proves equality of the calibration and target score laws for every \(P\in\mathcal P_{\mathcal G,K}\) and every fixed measurable predictor map. The same factorization lemma states that the \(M\) calibration orbit--score pairs are iid and independent of the target pair. Their score marginals now agree, so \(S_{1,a},\ldots,S_{M,a},S_{0,a}\) are iid conditionally on \(\mathcal T\).

For the converse, suppose joint orbit balance fails. Since the action preserves arms, there are an arm \(a\) and an orbit \(O_\star\subseteq\mathcal U_a\) such that
\[
q_{a,O_\star}\ne p_{a,O_\star}.\tag{2}
\]
Apply \(\texttt{def:orbit-separating-law}\) to \(a\) and \(O_\star\), and take the fixed measurable maps \(\widehat m_0=\widehat m_1=0\). Thus \(Y_v(a)=K\mathbf 1\{\iota_a(v)\in O_\star\}\) and \(Y_v(1-a)=0\). The outcomes are bounded by \(K\). Let \(L^\star\) denote the prototype and let \(G_0\) be uniform on the finite group \(\mathcal G\). For every \(h\in\mathcal G\), left multiplication sends the uniform random element \(G_0\) to another uniform random element, and hence
\[
h(G_0L^\star)\stackrel{d}{=}G_0L^\star.\tag{3}
\]
Therefore the symmetrized latent law is \(\mathcal G\)-invariant. Together with boundedness, it belongs to \(\mathcal P_{\mathcal G,K}\) by \(\texttt{def:invariant-laws}\). Taking iid copies and drawing assignments according to the known randomization law gives the replicated experiment in \(\texttt{def:observable-replicated-experiment}\).

On every assignment having positive \(\nu\)-mass, \(\texttt{ass:observable-selector-kernel}\) gives \(Z_{iJ_{i,a}}=a\) almost surely. Because \(O_\star\) is an orbit, its indicator is unchanged by the symmetrization in \( (3) \). Consequently,
\[
S_{i,a}=K\mathbf 1\{U_{i,a}\in O_\star\},\qquad S_{0,a}=K\mathbf 1\{T^a\in O_\star\}.\tag{4}
\]
The definitions of the integrated calibration law and the target lift, together with the selector auxiliary-draw and prespecified-target assumptions, now yield
\[
\Pr(S_{i,a}=K\mid\mathcal T)=q_{a,O_\star},\qquad\Pr(S_{0,a}=K\mid\mathcal T)=p_{a,O_\star}.\tag{5}
\]
Since \(K>0\), equations \( (2) \) and \( (5) \) show that the two score laws differ. Thus equality of the score laws uniformly over the declared invariant class and all fixed measurable predictors forces equality of every orbit mass, proving necessity.

Finally, invariance of \(\nu\) keeps its positive-mass assignment support invariant. Assignments outside that support have zero integrated weight, so arbitrary total kernel extensions there do not alter any selector mixture. Every argument above was carried out for one fixed arm; it asserts neither independence nor joint exchangeability across arms.