Assume \(\mathcal H\) is finite and nonempty, fix \(w\in\Delta(\mathcal H)\), condition on \(\mathcal T\), and fix an arm \(a\). By \(\texttt{lem:orbit-score-factorization}\), the \(M\) calibration orbit--score pairs are independent and identically distributed with law
\[
\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),
\tag{1}
\]
and the independent target orbit--score pair has law
\[
\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).
\tag{2}
\]
Orbit overlap implies \(\mathsf P_a\ll\mathsf Q_a\). Because the conditional score kernel \(F_{a,O}\) is identical in (1) and (2), its factor cancels and
\[
\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\frac{p_{a,O}}{q_{a,O}}=\lambda_{a,O}
\quad\mathsf Q_a\text{-almost surely on target-supported orbits}.
\tag{3}
\]
Thus only quotient-orbit overlap is needed. The selector may be singular among member labels inside an orbit, because member identity does not appear in the quotient laws (1)--(3).

Since \(0<\epsilon_a<1\), apply \(\texttt{lem:finite-support-weighted-rank-validity}\) to (1)--(3), with \(R_i=S_{i,a}\). The target orbit has \(p_{a,O_{T,a}}>0\) almost surely, so overlap makes \(\lambda_{a,O_{T,a}}>0\); consequently the normalized infinity-augmented measure has positive total mass. Its left-continuous \((1-\epsilon_a)\)-quantile is exactly \(r^{\mathrm W}_{a,w}\). Therefore
\[
\Pr_P\!\left(S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\right)\le\epsilon_a.
\tag{4}
\]
This one-arm step is precisely the finite-support likelihood-ratio weighted-exchangeability validity argument, including the target-weight atom at \(+\infty\), weak inclusion, ties, and zero calibration weights. The design-specific reduction is (3): invariant matched-block laws make the likelihood ratio constant on each finite orbit, so quotient overlap replaces member-level overlap.

Let \(E_a=\{S_{0,a}\le r^{\mathrm W}_{a,w}\}\). On \(E_a\), the definition of the residual score gives
\[
Y_{0T}(a)\in[\widehat m_a(X_{0T})-r^{\mathrm W}_{a,w},\widehat m_a(X_{0T})+r^{\mathrm W}_{a,w}].
\tag{5}
\]
The bounded-outcome assumption also gives \(Y_{0T}(a)\in[-K,K]\), so (5) implies \(Y_{0T}(a)\in I^{\mathrm W}_{a,w}\), including when the radius is infinite. Applying (4) to the two arms and using the union bound, without arm independence, yields
\[
\Pr_P(E_0\cap E_1\mid\mathcal T)\ge1-\epsilon_0-\epsilon_1\ge1-\alpha.
\tag{6}
\]
The same common target \(T\) and common selector mixture \(w\) occur in both events. On their intersection,
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.
\tag{7}
\]
Equations (6)--(7) prove the coverage assertion for every declared law and every fixed measurable trained map.

Under joint orbit balance, \(p_{a,O}=q_{a,O}\) for every orbit, so every orbit having positive mass has \(\lambda_{a,O}=1\); zero-mass orbits are never drawn. The normalized weighted measure then has \(M+1\) equal-mass atoms, one at each calibration score and one at \(+\infty\). Its left-continuous \((1-\epsilon_a)\)-quantile is the \(k_a\)-th ordered atom, where
\[
k_a=\left\lceil(M+1)(1-\epsilon_a)\right\rceil.
\tag{8}
\]
If \(k_a\le M\), this is the \(k_a\)-th calibration order statistic; if \(k_a=M+1\), it is \(+\infty\). Hence
\[
r^{\mathrm W}_{a,w}=r_{a,(k_a)},\qquad I^{\mathrm W}_{a,w}=I^{\boldsymbol\varepsilon}_{a,w},\qquad\mathcal C^{\mathrm W}_w=\mathcal C^{\boldsymbol\varepsilon}_w,
\tag{9}
\]
where the ordinary procedure uses \(\varepsilon_a=\epsilon_a\). Only on taking \(\epsilon_0=\epsilon_1=\alpha/2\) do (8)--(9) reduce to \(k_0=k_1=\lceil(M+1)(1-\alpha/2)\rceil\), \(I^{\mathrm W}_{a,w}=I_{a,w}\), and \(\mathcal C^{\mathrm W}_w=\mathcal C_w\). This proves both the asymmetric and symmetric reductions.