For \(w\in\Delta(\mathcal H)\), write
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|(Aw-b_{\mathrm{LP}})_{a,O}|.
\tag{1}
\]
The row identities used in \(\texttt{thm:common-selector-lp}\) give
\[
(Aw)_{a,O}=q^{\mathrm{obs}}_{w,a}(O),\qquad (b_{\mathrm{LP}})_{a,O}=q_{\mathrm{tar},a}(O).
\tag{2}
\]
Consequently,
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|\delta_{a,O}(w)|=\Delta_0(w)+\Delta_1(w).
\tag{3}
\]
Because \(\mathcal H\) is finite and nonempty, \(\Delta(\mathcal H)\) is a nonempty compact simplex. The function \(d\) is continuous, so it attains its minimum. Thus \(D_*\) is finite and \(\mathcal W_*\) is nonempty and compact.

We next verify the explicit primal program. For fixed \(w\), its inequalities imply
\[
t_{a,O}\ge |(Aw-b_{\mathrm{LP}})_{a,O}|
\tag{4}
\]
for every row. Hence every feasible \((w,t)\) has objective at least \(d(w)\). Conversely, choosing
\[
t_{a,O}=|(Aw-b_{\mathrm{LP}})_{a,O}|
\tag{5}
\]
makes \((w,t)\) feasible and gives objective \(d(w)\). Minimizing first over \(t\) and then over \(w\) proves that the finite absolute-value linear program has value \(D_*\), and its optimizing \(w\)-coordinates are exactly \(\mathcal W_*\).

We now prove the quantitative dual and its attainment directly. Let
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\subset\mathbb R^{2|\mathcal O|},\qquad b=b_{\mathrm{LP}}.
\]
Since \(Aw\) ranges over \(C\) as \(w\) ranges over the simplex,
\[
D_*=\min_{c\in C}\frac12\lVert c-b\rVert_1.
\tag{6}
\]
For every \(y\) with \(\lVert y\rVert_\infty\le1/2\) and every \(c\in C\), H"older's finite-sum inequality gives
\[
y^\top(c-b)\le\lVert y\rVert_\infty\lVert c-b\rVert_1\le\frac12\lVert c-b\rVert_1.
\tag{7}
\]
Taking the minimum over \(c\), then the maximum over \(y\), proves weak duality:
\[
\max_{\lVert y\rVert_\infty\le1/2}\min_{c\in C}y^\top(c-b)\le D_*.
\tag{8}
\]
If \(D_*=0\), the choice \(y=0\) makes the left side of \((8)\) at least zero, so equality holds. Suppose henceforth that \(D_*>0\). For integers \(n\ge2\), put \(r_n=(1-1/n)D_*\) and define the closed convex set
\[
B_n=\{x:\tfrac12\lVert x-b\rVert_1\le r_n\}.
\]
By \((6)\), \(B_n\cap C=\varnothing\). Both sets are compact. Choose \((c_n,x_n)\in C\times B_n\) minimizing the Euclidean distance between them, and put \(v_n=c_n-x_n\ne0\). For \(c\in C\), minimality along the segment from \(c_n\) to \(c\) gives
\[
0\le\left.\frac{d}{dt}\lVert c_n+t(c-c_n)-x_n\rVert_2^2\right|_{t=0+}=2v_n^\top(c-c_n).
\tag{9}
\]
Likewise, for \(x\in B_n\), minimality along the segment from \(x_n\) to \(x\) gives
\[
0\le\left.\frac{d}{dt}\lVert c_n-x_n-t(x-x_n)\rVert_2^2\right|_{t=0+}=-2v_n^\top(x-x_n).
\tag{10}
\]
Equations \((9)\)--\((10)\) imply
\[
\min_{c\in C}v_n^\top c\ge v_n^\top c_n\ge v_n^\top x_n\ge\max_{x\in B_n}v_n^\top x.
\tag{11}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). Then \(\lVert y_n\rVert_\infty=1/2\). The support function of the \(\ell_1\)-ball is explicit: choosing a coordinate on which \(|(y_n)_j|=1/2\) and moving \(2r_n\) in its signed coordinate direction shows
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b+2r_n\lVert y_n\rVert_\infty=y_n^\top b+r_n.
\tag{12}
\]
Combining \((11)\)--\((12)\) yields
\[
\min_{c\in C}y_n^\top c-y_n^\top b\ge r_n.
\tag{13}
\]
The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact, so a subsequence converges to some \(y_*\) in that cube. Since \(C\) is the convex hull of finitely many columns,
\[
\min_{c\in C}y^\top c=\min_{h\in\mathcal H}y^\top A_{\cdot h}
\tag{14}
\]
is a continuous function of \(y\). Letting \(n\to\infty\) in \((13)\) and using \((14)\) gives
\[
\min_{h\in\mathcal H}y_*^\top A_{\cdot h}-y_*^\top b_{\mathrm{LP}}\ge D_*.
\tag{15}
\]
Weak duality \((8)\) forces equality in \((15)\). The dual objective is continuous on the compact cube, so its maximum is attained; the preceding construction identifies a maximizer. Together with primal attainment, this proves finite-dimensional strong linear-programming duality. If \(D_*>0\), equality in \((15)\) says
\[
y_*^\top A_{\cdot h}\ge y_*^\top b_{\mathrm{LP}}+D_*\quad\forall h\in\mathcal H.
\tag{16}
\]
Thus \(z_*=-y_*\) satisfies
\[
z_*^\top b_{\mathrm{LP}}\ge\max_{h\in\mathcal H}z_*^\top A_{\cdot h}+D_*,
\tag{17}
\]
so it is precisely the existing Farkas separating direction, now with the quantitative margin \(D_*\).

By nonnegativity in \((1)\), \(D_*=0\) holds if and only if some \(w\in\Delta(\mathcal H)\) satisfies \(Aw=b_{\mathrm{LP}}\). This is exactly feasibility of \(\texttt{def:common-selector-feasibility-lp}\), equivalently exact joint balance by \(\texttt{thm:common-selector-lp}\). Moreover, the entries of \(A\) are obtained by integrating the allowed kernels against the known assignment law \(\nu\), and \(b_{\mathrm{LP}}\) is obtained from the prespecified target law. Therefore the primal program uses only the known randomization, target rule, and selector library. Solving it before scored outcomes are observed produces a prespecified \(w_*\); neither the scores nor the trained residuals enter \((1)\)--\((5)\).

Fix such a \(w_*\) and a prespecified budget \(\boldsymbol\varepsilon\). Proposition \(\texttt{prop:asymmetric-finite-rank-orbit-gap-bound}\) gives
\[
\Pr_P\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right)\ge\max\!\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-\Delta_0(w_*)-\Delta_1(w_*)\right\}.
\tag{18}
\]
By \((3)\) and the definition of \(\mathcal W_*\), \(\Delta_0(w_*)+\Delta_1(w_*)=D_*\), which turns \((18)\) into the claimed certificate. For any fixed \(w\), optimality gives
\[
D_*\le\Delta_0(w)+\Delta_1(w).
\tag{19}
\]
Since \(x\mapsto\max\{0,c-x\}\) is nonincreasing for fixed \(c\), equation \((19)\) proves weak dominance. If the inequality in \((19)\) is strict and
\[
1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*>0,
\]
then the optimized certificate is positive and either the comparator is also positive but smaller, or it is truncated to zero. In both cases the dominance is strict. Finally, on \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{def:finite-rank-error}\) gives \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\), and \(\texttt{def:rank-inversion}\) gives \(\mathcal C^{\boldsymbol\varepsilon}_{w_*}=\mathcal C_{w_*}\). Substitution in \((18)\) proves the displayed equal-split corollary.