Put \(N=M+1\). Since \(k_c=\lceil N(1-\varepsilon_c)\rceil\), the elementary equivalence \(\lceil x\rceil\le n\) if and only if \(x\le n\), for integral \(n\), yields
\[
k_c\le M
\iff N(1-\varepsilon_c)\le N-1
\iff \varepsilon_c\ge\frac1N.
\tag{1}
\]

Under \(\texttt{def:disjoint-orbit-law}\), the arm-\(a\) potential outcome is \(K\) on target-supported arm-\(a\) orbits and zero elsewhere, while every arm-\(1-a\) potential outcome is zero. These coordinates are constant on each \(\mathcal G\)-orbit. Complete the prototype with any fixed covariate array and let \(G\) be uniform on the finite group, as the definition prescribes. For any fixed \(g\in\mathcal G\), the product \(gG\) is again uniform; hence \(g(GL^*)\) and \(GL^*\) have the same law. The construction satisfies finite-group latent invariance. Its potential outcomes lie in \(\{0,K\}\subseteq[-K,K]\), so it satisfies boundedness and belongs to \(\mathcal P_{\mathcal G,K}\) by \(\texttt{def:invariant-laws}\). Independent copies, the known assignment law, and the stipulated auxiliary draws furnish the replicated experiment.

If \(q^{\mathrm{obs}}_{w,a}(O)>0\), the disjoint-support premise says that \(O\) is not target-supported, and the construction assigns outcome zero there. The predictor is identically zero, while the observable-selector condition forces \(J_{i,a}\) to be observed in arm \(a\). Thus every selected arm-\(a\) calibration score is zero. All outcomes and the predictor in arm \(1-a\) are also zero, so its calibration scores are zero as well. Consequently,
\[
r_{c,(k_c)}=0\quad\hbox{if }k_c\le M,
\qquad
r_{c,(k_c)}=+\infty\quad\hbox{if }k_c=M+1.
\tag{2}
\]
If both ranks are finite, clipping leaves the two singleton intervals \(\{0\}\), so \(\mathcal C^{\boldsymbol\varepsilon}_w=\{0\}\). Target independence puts the selected target in a target-supported orbit almost surely, whence \(Y_{0T}(a)=K\), \(Y_{0T}(1-a)=0\), and
\[
\tau_T=\begin{cases}K,&a=1,\\-K,&a=0.\end{cases}
\tag{3}
\]
Since \(K>0\), \((3)\) is not in \(\{0\}\), proving zero conditional coverage.

If exactly one rank is at the boundary, \((2)\) and \(\texttt{prop:asymmetric-rank-boundary}\) give one arm interval \([-K,K]\) and the other \(\{0\}\). Either ordering of the Minkowski difference is \([-K,K]\), which contains both possible values in \((3)\), including its closed endpoints. If both ranks are at the boundary, the effect set is \([-2K,2K]\), also containing \((3)\). This proves the two coverage-one boundary clauses. Finally, on the symmetric diagonal the two ranks coincide, so the only possibilities are the both-finite zero-coverage case and the both-boundary coverage-one case, exactly as in the frozen symmetric proposition.