For a finite rank \(k_a\), the elementary order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Thus ties are governed by strict prefixes and the event depends on \(s_a\) only through its total preorder. Conversely, if a preorder has ordered nonempty tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes it in \([0,K]\) with at most \(m_a\) levels. The finite set of \(F_{m_0}F_{m_1}\) preorder pairs therefore attains the maximum in the definition, proving exactness over the declared orbit-constant score class and making no assertion about a supremum over latent laws.

Suppose first that both ranks are finite. By \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\), for every preorder pair \(C\),
\[
\Pr\{\text{both rank events}\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi),
\qquad U_C\le L_C\le\min\{L,d_0d_1\}.
\tag{2}
\]
The exact memo key contains no target weight, so every \(\omega_C\) remains local. If \(\pi_{xy}=1\), all \(M\) strict-prefix indicator pairs equal \((x,y)\), and hence
\[
D_{M,k_0,k_1}(\pi)=\mathbf 1\{Mx<k_0\ \text{and}\ My<k_1\}.
\tag{3}
\]
This proves the constant-time, constant-workspace vertex prepass. The coherent evaluator then partitions only the nonvertex keys among the three exact branches, yielding
\[
\Pi_\star=\Pi_{\mathrm{vert}}\mathbin{\dot\cup}\Pi_{\mathrm{roll}}\mathbin{\dot\cup}\Pi_{\mathrm{MS}}\mathbin{\dot\cup}\Pi_+
\tag{4}
\]
and
\[
\begin{aligned}
\mathsf B={}&|\Pi_{\mathrm{vert}}|+M\mathbf 1\{\Pi_{\mathrm{MS}}\ne\varnothing\}
+\sum_{\pi\in\Pi_{\mathrm{roll}}}\mathsf C_{M,k_0,k_1}\\
&+\sum_{\pi\in\Pi_{\mathrm{MS}}}(M+\mathsf T_{M,\bar k_0,\bar k_1})
+\sum_{\pi\in\Pi_+}\mathsf C_+(\pi).
\end{aligned}
\tag{5}
\]
The vertex workspace is constant, and the factorial preprocessing in (5) occurs exactly when the nonvertex multinomial branch is nonempty. Substitution of (5) into the evaluator's grouping and memo accounting proves both displayed time bounds and the stated \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\) memory bound. Since the construction of each key uses the unchanged full \(R_w\), and its local weight uses the unchanged coherent \(P_T^C\), the prepass and dispatcher preserve calibration-arm dependence, the common target, and the common selector.

The strict improvement is witnessed by one audited pair orbit in each arm, fair pair randomization, and the legal selector choosing the unique observed member in the requested arm. Then \(R_w\) and \(P_T\) are point masses and the unique strict-prefix key is \(\pi_{00}=1\). For \(M\ge2\), \(\alpha=2/(M+1)\) and \(\varepsilon_0=\varepsilon_1=1/(M+1)\) imply \(k_0=k_1=M\). Equation (3) gives \(D_{M,M,M}(\pi)=1\). The former rolling and multinomial charges are \(M\) and \(M+1\), respectively. Only the lower--lower orientation has positive base mass, so \(\mathsf C_+(\pi)=\Theta(M^2)\). The former least-charge dispatcher therefore paid \(\Theta(M)\), while the vertex prepass pays \(\Theta(1)\). This is a statement about the exact key value, not the frontier deficit.

If exactly one rank \(k_b=M+1\), the boundary-arm event is certain by \(\texttt{prop:asymmetric-rank-boundary}\). Put \(c=1-b\). Conditional on target orbit \(O_t\), (1) is a binomial strict-prefix count with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
The calibration orbits are iid and independent of the target by the known randomization, auxiliary-selector, and target assumptions. Averaging gives
\[
\sum_{O_t}p_{c,O_t}\Pr\{\operatorname{Bin}(M,\theta(O_t))<k_c\}.
\tag{6}
\]
Grouping target orbits by ordered tie class turns (6) into the displayed cumulative-class formula. The lower and upper binomial recurrences, their endpoint clauses, the shorter-tail complexity, and the absence of the other arm's preorder follow exactly from \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) and \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\). If both ranks equal \(M+1\), both events are certain and the defining positive part is zero.

For binary nonattainment, use four audited pair blocks with fair independent assignment. Let the selector's block probabilities in each arm be
\[
q=(13/20,1/20,1/4,1/20)
\]
and let the common target's block probabilities be
\[
p=(1/20,1/10,1/4,3/5).
\]
With \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), both ranks equal three. Set \(s_0\equiv0\) and order the arm-one blocks as \(1\prec3\prec2\prec4\). The failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000},
\]
so this four-level frontier objective is \(24957/160000\). For a binary pair, if \(H_a\) is the high-score block set and \(A_a=(1-q(H_a))^3\), inclusion--exclusion gives failure probability
\[
p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{7}
\]
In the row order
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
exact substitution in (7), maximizing over the sixteen choices in the other arm, gives the row maxima with common denominator \(320000000\):
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{8}
\]
Thus the maximum failure probability in (7) is \(208582976/320000000\), so every binary objective is at most \(759109/5000000\). The difference is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\]
Finally, if target and calibration supports are disjoint in a finite-rank arm, assign score \(K\) to its target-supported orbits and zero elsewhere, and assign zero in the other arm. The adverse rank event fails surely, so the deficit is at least \(1-\alpha\); the positive-part definition gives the reverse inequality. A boundary arm is certain and reduces to (6). On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), the armwise staircase gives \(k_0=k_1=k\), yielding the symmetric theorem.