Condition throughout on \(\mathcal T\), and fix an arm \(a\). Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). By \(\texttt{lem:orbit-score-factorization}\), a calibration score and the target score have conditional laws
\[
\mathsf Q_a=\sum_{O\in\mathcal O_a}q_{a,O}F_{a,O},\qquad \mathsf P_a=\sum_{O\in\mathcal O_a}p_{a,O}F_{a,O},
\tag{1}
\]
and the \(M\) calibration scores are independent and identically distributed from \(\mathsf Q_a\), independently of the target score from \(\mathsf P_a\).

For a measurable \(f:[0,\infty)\to[0,1]\), put \(h_O=\int f\,dF_{a,O}\) and \(d_O=p_{a,O}-q_{a,O}\). Both orbit-mass vectors are probability vectors, so \(\sum_Od_O=0\). Therefore the positive and negative parts of \((d_O)_O\) have the same total mass, namely
\[
\frac12\sum_{O\in\mathcal O_a}|d_O|=\Delta_a(w).
\]
It follows that
\[
\left|\int f\,d(\mathsf P_a-\mathsf Q_a)\right|=\left|\sum_{O\in\mathcal O_a}d_Oh_O\right|\le \Delta_a(w).
\tag{2}
\]
Thus the common orbit-specific score kernels contract the total variation between the orbit mixing laws.

On an auxiliary product extension, let \(S'_{0,a}\sim\mathsf Q_a\) be independent of the calibration scores. Append the independent continuous tie-breakers prescribed by \(\texttt{def:rank-inversion}\). The augmented rank of \(S'_{0,a}\) among the \(N=M+1\) independent and identically distributed augmented scores is uniform on \(\{1,\ldots,N\}\). If the unaugmented comparison score strictly exceeds the reported \(k_a\)-th calibration order statistic, its augmented rank exceeds \(k_a\), regardless of its tie-breaker. Hence
\[
\Pr\{S'_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le\frac{N-k_a}{N}=\rho_{M,\varepsilon_a}.
\tag{3}
\]
This includes \(k_a=N\), because then the threshold is \(+\infty\) and the event is empty.

For each fixed calibration realization, apply (2) to \(f(s)=\mathbf 1\{s>r_{a,(k_a)}\}\). The actual target is independent of the calibration sample and has law \(\mathsf P_a\). Averaging the conditional comparison and using (3) yields
\[
\Pr_P\{S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le \rho_{M,\varepsilon_a}+\Delta_a(w).
\tag{4}
\]
Let \(\widetilde I^{\boldsymbol\varepsilon}_{a,w}\) denote the un-clipped residual interval. On \(\{S_{0,a}\le r_{a,(k_a)}\}\), the target outcome belongs to that interval. The bounded-outcome assumption also gives \(Y_{0T}(a)\in[-K,K]\). Since
\[
I^{\boldsymbol\varepsilon}_{a,w}=\widetilde I^{\boldsymbol\varepsilon}_{a,w}\cap[-K,K],
\]
we obtain
\[
\{Y_{0T}(a)\notin I^{\boldsymbol\varepsilon}_{a,w}\}\subseteq\{S_{0,a}>r_{a,(k_a)}\}.
\tag{5}
\]
If neither arm fails in (5), then
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{6}
\]
The union bound applied to (4)--(6), without any cross-arm independence, gives
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right\}\ge 1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-\Delta_0(w)-\Delta_1(w).
\]
Taking the maximum with zero proves the displayed bound. The coordinate elbows follow from \(\texttt{lem:armwise-finite-rank-staircase}\).

Finally, \(\sum_O\delta_{a,O}(w)=0\). Hence the sum of the positive coordinates and the absolute sum of the negative coordinates both equal \(\Delta_a(w)\), so every coordinate obeys \(|\delta_{a,O}(w)|\le\Delta_a(w)\). On the diagonal, \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\), while \(\texttt{def:rank-inversion}\) identifies \(\mathcal C^{\boldsymbol\varepsilon}_w\) with \(\mathcal C_w\). This yields the asserted symmetric specialization.