Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,
\]
and the definition gives \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w)\). Thus \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\) applies on the diagonal. Its preorder argument proves exactness and attainment over the bounded orbit-constant score class, with at most \(m_a\) levels, while preserving the coherent \(P_T^C\), the full joint \(R_w\), and the local weights.

Suppose \(k\le M\). For a vertex key \(\pi_{xy}=1\), the diagonal specialization of the deterministic-count identity is
\[
D_{M,k,k}(\pi)=\mathbf 1\{Mx<k\ \text{and}\ My<k\}.
\tag{1}
\]
It costs constant exact time and workspace. Only the nonvertex keys enter the deterministically tie-broken three-way dispatcher, so
\[
\Pi_\star=\Pi_{\mathrm{vert}}\mathbin{\dot\cup}\Pi_{\mathrm{roll}}\mathbin{\dot\cup}\Pi_{\mathrm{MS}}\mathbin{\dot\cup}\Pi_+,
\tag{2}
\]
and the asymmetric charge specializes to
\[
\begin{aligned}
\mathsf B_{\mathrm{sym}}={}&|\Pi_{\mathrm{vert}}|+M\mathbf 1\{\Pi_{\mathrm{MS}}\ne\varnothing\}
+\sum_{\pi\in\Pi_{\mathrm{roll}}}\mathsf C_{M,k,k}\\
&+\sum_{\pi\in\Pi_{\mathrm{MS}}}(M+\mathsf T_{M,\bar k,\bar k})
+\sum_{\pi\in\Pi_+}\mathsf C_+(\pi).
\end{aligned}
\tag{3}
\]
The vertex branch adds no nonconstant workspace, and the factorial term in (3) is present if and only if the nonvertex multinomial branch is nonempty. Substituting (3) and the diagonal workspace \(\mathsf W_{\mathrm{sym}}\) into the asymmetric evaluator gives the two displayed time bounds and
\[
O(m_0m_1+L+U_{\max}+G+\mathsf W_{\mathrm{sym}})
\]
memory. Each exact key still comes from \(R_w\), and each local weight still comes from \(P_T^C\), so computation changes no probability object.

For the strict witness, take the admissible one-orbit-per-arm pair design from the asymmetric theorem. Then \(\pi_{00}=1\). If \(M\ge2\) and \(\alpha=2/(M+1)\), the equal split gives \(k=M\), and (1) yields \(D_{M,M,M}(\pi)=1\). The prior dispatcher paid \(\Theta(M)\), whereas the vertex prepass pays \(\Theta(1)\). If \(k=M+1\), both rank events are certain by \(\texttt{prop:rank-boundary}\), hence \(\Gamma_{M,\alpha}(w)=0\). The four-pair construction and exact binary enumeration in the asymmetric theorem already lie on the equal-split diagonal, so they give the stated four-level value, binary upper bound, and positive gap. Its disjoint-support construction likewise specializes to \(\Gamma_{M,\alpha}(w)=1-\alpha\) whenever \(k\le M\).