Assume that \(\mathcal H\) is finite and nonempty. For \(w\in\Delta(\mathcal H)\), define
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|(Aw-b_{\mathrm{LP}})_{a,O}|.\tag{1}
\]
The row identities from \(\texttt{thm:common-selector-lp}\) give
\[
(Aw)_{a,O}=q^{\mathrm{obs}}_{w,a}(O),\qquad (b_{\mathrm{LP}})_{a,O}=q_{\mathrm{tar},a}(O),
\]
and therefore
\[
d(w)=\Delta_0(w)+\Delta_1(w).\tag{2}
\]
The simplex is nonempty and compact and \(d\) is continuous, so the minimum is attained. Hence \(D_*\) is finite and \(\mathcal W_*\) is nonempty.

For fixed \(w\), the two-sided slack constraints in the displayed primal program imply
\[
t_{a,O}\ge |(Aw-b_{\mathrm{LP}})_{a,O}|.\tag{3}
\]
Conversely, equality in \((3)\) defines feasible slacks. Minimizing over the slacks and then over \(w\) shows that the absolute-value program has value \(D_*\), with optimizer set \(\mathcal W_*\).

Put \(C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\) and \(b=b_{\mathrm{LP}}\). Since \(Aw\) ranges over \(C\),
\[
D_*=\min_{c\in C}\frac12\lVert c-b\rVert_1.\tag{4}
\]
For \(\lVert y\rVert_\infty\le1/2\), finite-dimensional Holder inequality gives
\[
y^\top(c-b)\le\lVert y\rVert_\infty\lVert c-b\rVert_1\le\frac12\lVert c-b\rVert_1.
\]
Thus
\[
\max_{\lVert y\rVert_\infty\le1/2}\min_{c\in C}y^\top(c-b)\le D_*.\tag{5}
\]
We prove the reverse inequality and attainment. If \(D_*=0\), \(y=0\) gives equality in \((5)\). Suppose \(D_*>0\). For \(n\ge2\), set \(r_n=(1-1/n)D_*\) and
\[
B_n=\{x:\tfrac12\lVert x-b\rVert_1\le r_n\}.
\]
By \((4)\), the compact convex sets \(B_n\) and \(C\) are disjoint. Choose a closest pair \((c_n,x_n)\in C\times B_n\), put \(v_n=c_n-x_n\ne0\), and vary each coordinate of the closest pair along line segments in its convex set. The resulting first-order inequalities are
\[
v_n^\top(c-c_n)\ge0\quad(c\in C),\qquad v_n^\top(x-x_n)\le0\quad(x\in B_n).\tag{6}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). Then \(\lVert y_n\rVert_\infty=1/2\), and \((6)\) implies
\[
\min_{c\in C}y_n^\top c\ge\max_{x\in B_n}y_n^\top x.\tag{7}
\]
The support function of the displayed \(\ell_1\)-ball is
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b+2r_n\lVert y_n\rVert_\infty=y_n^\top b+r_n.\tag{8}
\]
Indeed, Holder gives the upper bound, and equality follows by moving \(2r_n\) in a signed coordinate attaining \(\lVert y_n\rVert_\infty\). Equations \((7)\)--\((8)\) yield
\[
\min_{c\in C}y_n^\top c-y_n^\top b\ge r_n.\tag{9}
\]
The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact. Along a convergent subsequence, \(y_n\to y_*\). Because the library is finite,
\[
\min_{c\in C}y^\top c=\min_{h\in\mathcal H}y^\top A_{\cdot h}\tag{10}
\]
is continuous in \(y\). Letting \(n\to\infty\) in \((9)\) and combining with weak duality \((5)\) proves
\[
D_*=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.\tag{11}
\]
Continuity on the compact cube also proves dual attainment. If \(D_*>0\) and \(y_*\) is any maximizer, \((11)\) implies
\[
y_*^\top A_{\cdot h}\ge y_*^\top b_{\mathrm{LP}}+D_*\quad\forall h\in\mathcal H.
\]
Thus \(-y_*\) separates \(b_{\mathrm{LP}}\) from every column, and hence from their convex hull, with margin \(D_*\).

Nonnegativity in \((1)\) shows that \(D_*=0\) exactly when some \(w\in\Delta(\mathcal H)\) has \(Aw=b_{\mathrm{LP}}\), which is feasibility of the exact-balance program. Every entry of \(A\) integrates a declared selector kernel against the known assignment law, and \(b_{\mathrm{LP}}\) depends only on the prespecified target rule. Hence the finite program can be solved before scores are observed, and any selected \(w_*\in\mathcal W_*\) is prespecified.

Fix such a \(w_*\) and condition on \(\mathcal T\). Proposition \(\texttt{prop:asymmetric-finite-rank-orbit-gap-bound}\), followed by \((2)\), gives
\[
\Pr_P\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right)\ge\max\!\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\right\}.\tag{12}
\]
For any fixed \(w\in\Delta(\mathcal H)\), optimality gives \(D_*\le\Delta_0(w)+\Delta_1(w)\). Since \(x\mapsto\max\{0,c-x\}\) is nonincreasing, the certificate in \((12)\) weakly dominates the corresponding fixed-\(w\) certificate. If the imbalance inequality is strict and the optimized expression before truncation is positive, the dominance is strict. On the equal-split diagonal, \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\) and \(\mathcal C^{\boldsymbol\varepsilon}_{w_*}=\mathcal C_{w_*}\), so \((12)\) becomes the asserted symmetric bound.