First suppose \(\mathcal H=\varnothing\). By \(\texttt{def:minimum-imbalance-common-selector}\), \(\Delta(\mathcal H)=\varnothing\); hence no selector mixture, implemented kernel, selector-indexed procedure, \(D_*\), \(D_{*,\mathcal A}\), optimizer set, or selected optimizer exists. This is distinct from an empty active-arm set when \(\mathcal H\ne\varnothing\).

Now suppose that \(\mathcal H\) is finite and nonempty. The compactness, absolute-value primal representation, attained dual representations, and separation statements are supplied by \(\texttt{thm:active-arm-minimum-imbalance-selector-certificate}\). We record how those conclusions yield every certificate here. For the full row set, that theorem gives a nonempty optimizer set \(\mathcal W_*\) and
\[
D_*=\min_{w\in\Delta(\mathcal H)}\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|(Aw-b_{\mathrm{LP}})_{a,O}|
=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.
\tag{1}
\]
The minimum is attained because the simplex is compact and the objective is continuous; the slack-variable program is exact because, at a minimum, each slack equals the absolute value of its residual. If \(y^*\) maximizes (1) and \(D_*>0\), then for every \(h\),
\[
(y^*)^\top A_{\cdot h}-(y^*)^\top b_{\mathrm{LP}}\ge D_*.
\]
Thus \(-y^*\) strictly separates \(b_{\mathrm{LP}}\) from every column and hence from their convex hull, with margin \(D_*\). Also, \(D_*=0\) holds exactly when some simplex point has zero residual, that is, when the exact joint-balance program is feasible.

For the active row set \(\mathcal A_{\boldsymbol\varepsilon}=\{a:k_a\le M\}\), the same theorem gives a nonempty \(\mathcal W_{*,\mathcal A}\) and
\[
D_{*,\mathcal A}=\min_{w\in\Delta(\mathcal H)}\frac12\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\sum_O|(Aw-b_{\mathrm{LP}})_{a,O}|
=\max_{\substack{\lVert y\rVert_\infty\le1/2\\y_{a,O}=0\ \mathrm{for}\ a\notin\mathcal A_{\boldsymbol\varepsilon}}}\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.
\tag{2}
\]
It also gives \(D_{*,\mathcal A}=0\) exactly when one common selector balances all active rows. This is equivalent to full joint balance only when both arms are active. Since \(A\), \(b_{\mathrm{LP}}\), and the ranks are determined by the known design, target rule, selector library, and prespecified error allocation, a deterministic tie-break chooses \(w_{*,\mathcal A}\) before any score is observed.

Row by row, the definitions of \(A\), \(b_{\mathrm{LP}}\), and \(\Delta_a\) give
\[
\frac12\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\sum_O|(Aw-b_{\mathrm{LP}})_{a,O}|
=\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w).
\tag{3}
\]
Apply \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) to \(w_{*,\mathcal A}\), and use (2)--(3). This yields
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_{*,\mathcal A}}\mid\mathcal T\right\}
\ge\max\!\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\rho_{M,\varepsilon_a}-D_{*,\mathcal A}\right\}.
\tag{4}
\]
For every fixed \(w\), optimality implies \(D_{*,\mathcal A}\le\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w)\). Monotonicity of \(x\mapsto\max\{0,x\}\) proves weak dominance of (4); the dominance is strict when this inequality is strict and the untruncated optimized bound is positive. If exactly one arm is at the boundary, (2)--(4) contain only the other arm's rows and rank penalty. If no arm is active, the objective in (2) is identically zero, so \(D_{*,\mathcal A}=0\), \(\mathcal W_{*,\mathcal A}=\Delta(\mathcal H)\), and both arm intervals are \([-K,K]\), giving coverage one without optimization.

For completeness, take any \(w_*\in\mathcal W_*\). Equation (3) with both arms, together with (1), gives \(\Delta_0(w_*)+\Delta_1(w_*)=D_*\). The asymmetric orbit-gap bound therefore gives
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right\}
\ge\max\!\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\right\}.
\tag{5}
\]
Optimality of \(D_*\) proves the stated weak and strict dominance comparisons against every fixed common \(w\). On the equal-split diagonal with finite ranks, the active rows are all rows, so \(D_{*,\mathcal A}=D_*\), \(\mathcal W_{*,\mathcal A}=\mathcal W_*\), and (5) becomes
\[
\Pr_P(\tau_T\in\mathcal C_{w_*}\mid\mathcal T)\ge\max\{0,1-2\rho_{M,\alpha}-D_*\}.
\]
At the two-boundary elbow the active set is empty and the sharper conclusion is coverage one.