For a finite rank \(k_a\), the order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Thus ties are handled by strict prefixes, and the event depends on \(s_a\) only through its total preorder on \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). Conversely, if a total preorder has ordered nonempty classes \(C_{a,1}\prec\cdots\prec C_{a,d_a}\), assign score \(0\) when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(C_{a,j}\). This realizes the preorder in \([0,K]\) using \(d_a\le m_a=|\mathcal O_a|\) levels. There are exactly \(F_{m_0}F_{m_1}\) preorder pairs. Hence the finite maximum in \(\texttt{def:coverage-frontier}\) is attained by their enumeration. This proves exactness over the declared bounded orbit-constant score class and, as stated, makes no assertion about a supremum over latent laws.

Suppose first that \(k_0,k_1\le M\). By \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\), for each preorder pair \(C\),
\[
\Pr\{\text{both rank events under }C\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
That lemma constructs every key from the unchanged joint calibration law \(R_w\), keeps the coherent common-target weights \(\omega_C\) local to \(P_T^C\), and memoizes only \((M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10})\). Its support-one and support-two prepasses followed by the least-charge support-at-least-three dispatcher give exactly the displayed partition of \(\Pi_\star\), the charges \(\mathsf B\) and \(\mathsf W\), both time bounds, and the memory bound. In particular, \(\texttt{def:simplex-vertex-key-prepass}\) and \(\texttt{lem:four-cell-rank-event-dynamic-program}\) show that an edge is an affine-binomial interval and uses only constant workspace; it therefore creates no additional term in \(\mathsf W\). The multinomial factorial table is needed exactly when a support-at-least-three key is assigned to \(\Pi_{\mathrm{MS}}\). This proves every two-finite-rank computational assertion.

The strict edge witness is also audited in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). Namely, when \(M=2n\ge4\), \(k_0=n\), \(k_1=M\), and \(\pi=(1/2,1/2,0,0)\), a variable \(N\sim\operatorname{Bin}(M,1/2)\) satisfies \((R_M,S_M)=(0,N)\), and hence
\[
D_{M,n,M}(\pi)=\Pr\{N<M\}=1-2^{-M}.
\tag{3}
\]
The one-point complementary tail costs \(\Theta(\log M)\) exact arithmetic and constant workspace, whereas the least of the former rolling, multinomial-sum, and positive-corner charges is \(\Theta(M)\). The cited lemma supplies the two audited pair blocks, invariant randomization, legal equivariant selector, common target, and preorders. It also verifies directly that
\[
\varepsilon_0=\frac{n+1}{2n+1},\qquad \varepsilon_1=\frac1{2n+1},\qquad \alpha=\frac{n+2}{2n+1}
\tag{4}
\]
are positive, obey the budget, and yield \(k_0=n\) and \(k_1=M\).

Suppose next that exactly one rank \(k_b=M+1\), and put \(c=1-b\). By \(\texttt{prop:asymmetric-rank-boundary}\), the boundary-arm event is certain. Conditional on \(O_{T,c}=O_t\), (1) and iid calibration orbits make the strict-prefix count binomial with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\tag{5}
\]
Averaging over the target-orbit mass gives
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}\Pr\!\left\{\operatorname{Bin}(M,\theta(O_t))<k_c\right\}.
\tag{6}
\]
The ordered-class scan and shorter-tail recurrence in \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), with endpoint handling from \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), evaluate all \(F_{m_c}\) preorders in
\[
O\!\left(F_{m_c}m_c[1+\log M+\min\{k_c,M-k_c+1\}]\right)
\tag{7}
\]
arithmetic operations and constant auxiliary CDF memory after the two marginal vectors are tabulated. If both ranks equal \(M+1\), both rank events are certain, so the probability in \(\texttt{def:coverage-frontier}\) equals one and the positive-part deficit is zero.

We now prove the binary nonattainment assertion by an exact finite witness. Take four audited pair blocks under \(S_2^4\), independent fair one-treated--one-control assignments, and selector kernels which, independently across arms conditional on assignment, choose a block with probabilities
\[
q=(13/20,1/20,1/4,1/20)
\tag{8}
\]
and then select that block's unique observed member in the requested arm. These kernels are observable and equivariant. Let the common target choose a block with probabilities
\[
p=(1/20,1/10,1/4,3/5)
\tag{9}
\]
and then a prespecified member of that block. Thus both arm lifts have the coherent block-orbit law (9). At \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), both ranks equal three. Take \(s_0\equiv0\) and give arm \(1\) the four-level order \(1\prec3\prec2\prec4\). The probability that the arm-\(1\) rank event fails is
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\tag{10}
\]
The arm-\(0\) event is certain, so the frontier objective is \(104957/160000-1/2=24957/160000\).

For arbitrary binary score maps, let \(H_a\) be arm \(a\)'s high-score block set and put \(A_a=(1-q(H_a))^3\). The rank event in arm \(a\) fails precisely when the common target lies in \(H_a\) and all three arm-\(a\) calibration blocks lie outside \(H_a\). Conditional independence of the two selector draws within each replicate and inclusion--exclusion therefore give joint failure probability
\[
p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{11}
\]
For \(H_0\) in the order
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
maximization of (11) over the sixteen choices of \(H_1\) gives, with common denominator \(320000000\), the exact numerators
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{12}
\]
Thus the largest binary failure probability is \(208582976/320000000\), and every binary frontier objective is at most
\[
\frac{208582976}{320000000}-\frac12=\frac{759109}{5000000}.
\tag{13}
\]
Subtracting (13) from the four-level value gives the strictly positive gap
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}.
\tag{14}
\]
This proves that binary scores are not universally extremal.

Finally, suppose target and calibration orbit supports are disjoint in a finite-rank arm \(a\). Assign score \(K\) to every target-supported arm-\(a\) orbit and score zero to all other arm-\(a\) orbits, and assign zero in the other arm. Every adverse-arm calibration score is zero and the target score is \(K>0\), so its finite-rank event fails surely. The joint event therefore has probability zero, and the frontier objective is \(1-\alpha\). Since \([(1-\alpha)-p]_+\le1-\alpha\) for every probability \(p\), this is the exact maximum. This score construction is the score-level counterpart of \(\texttt{prop:asymmetric-disjoint-orbit-witness}\). On setting \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\) and the definition gives \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w)\), yielding the equal-split theorem. All prepasses merely evaluate the same probabilities in (2) or (6); they alter none of the selector, common-target, active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit definitions.