Condition throughout on \(\mathcal T\), and fix \(a\in\{0,1\}\). Let \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). By \(\texttt{lem:orbit-score-factorization}\), the conditional laws of a calibration score and the target score are, respectively,
\[
\mathsf Q_a=\sum_{O\in\mathcal O_a}q_{a,O}F_{a,O},\qquad \mathsf P_a=\sum_{O\in\mathcal O_a}p_{a,O}F_{a,O}.
\tag{1}
\]
For any measurable \(f:[0,\infty)\to[0,1]\), put \(h_O=\int f\,dF_{a,O}\in[0,1]\). Both \((p_{a,O})_{O\in\mathcal O_a}\) and \((q_{a,O})_{O\in\mathcal O_a}\) are probability vectors, so the coordinates of \(d_O=p_{a,O}-q_{a,O}\) sum to zero. The positive and negative parts of \((d_O)_O\) therefore have the same total mass, equal to \(\frac12\sum_O|d_O|=\Delta_a(w)\). It follows that
\[
\left|\int f\,d(\mathsf P_a-\mathsf Q_a)\right|
=\left|\sum_{O\in\mathcal O_a}d_Oh_O\right|
\le \Delta_a(w).
\tag{2}
\]
Thus mixing through the common orbit-specific score laws contracts the total variation distance between the two orbit-mass vectors.

The factorization lemma, using the iid arrays and the product auxiliary selector draws, also states that \(S_{1,a},\ldots,S_{M,a}\) are conditionally iid with law \(\mathsf Q_a\). On an auxiliary product extension, introduce an independent comparison score \(S'_{0,a}\sim\mathsf Q_a\). Append independent continuous tie-breakers as prescribed by \(\texttt{def:rank-inversion}\). The rank of the augmented \(S'_{0,a}\) among the \(M+1\) iid augmented scores is uniform on \(\{1,\ldots,M+1\}\). If the unaugmented comparison score strictly exceeds the reported \(k\)-th calibration order statistic, then its augmented rank is greater than \(k\), irrespective of how ties are broken. Hence weak inclusion at the reported threshold gives
\[
\Pr_{\mathsf Q_a^{M+1}}\!\left\{S'_{0,a}>r_{a,(k)}\mid\mathcal T\right\}
\le \frac{M+1-k}{M+1}
=\rho_{M,\alpha}.
\tag{3}
\]
This also covers \(k=M+1\), because then \(r_{a,(k)}=+\infty\) and the event on the left is empty.

By \(\texttt{lem:orbit-score-factorization}\), the actual target score is independent of all calibration scores and has conditional law \(\mathsf P_a\). For each fixed calibration realization, apply (2) to the measurable function \(f(s)=\mathbf 1\{s>r_{a,(k)}\}\). Comparison with an independent \(\mathsf Q_a\)-distributed target and then averaging over the calibration scores yields, by (3),
\[
\Pr_P\!\left\{S_{0,a}>r_{a,(k)}\mid\mathcal T\right\}
\le \rho_{M,\alpha}+\Delta_a(w).
\tag{4}
\]

It remains to connect score success to the clipped interval. Define the un-clipped residual set
\[
\widetilde I_{a,w}=\left\{y\in\mathbb R:\left|y-\widehat m_a(X_{0T})\right|\le r_{a,(k)}\right\}.
\]
On \(\{S_{0,a}\le r_{a,(k)}\}\), the definition of \(S_{0,a}\) gives \(Y_{0T}(a)\in\widetilde I_{a,w}\). Since \(P\in\mathcal P_{\mathcal G,K}\), the bounded-potential-outcomes assumption also gives \(Y_{0T}(a)\in[-K,K]\). The clipped construction in \(\texttt{def:rank-inversion}\) has \(I_{a,w}=\widetilde I_{a,w}\cap[-K,K]\); consequently,
\[
\{Y_{0T}(a)\notin I_{a,w}\}\subseteq\{S_{0,a}>r_{a,(k)}\}.
\tag{5}
\]
If (5) does not fail for either arm, then
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I_{1,w}-I_{0,w}=\mathcal C_w.
\tag{6}
\]
Combining (4)--(6) for \(a=0,1\) and applying the union bound, with no independence assumption between arms, gives
\[
\Pr_P\!\left\{\tau_T\in\mathcal C_w\mid\mathcal T\right\}
\ge 1-2\rho_{M,\alpha}-\Delta_0(w)-\Delta_1(w).
\]
A probability is nonnegative, so replacing the right-hand side by its maximum with zero proves the displayed coverage bound. By \(\texttt{lem:finite-rank-staircase}\), \(\rho_{M,\alpha}=j/(M+1)\) whenever \(\alpha\in[2j/(M+1),2(j+1)/(M+1))\) and the interval intersects \((0,1)\); hence the staircase elbows occur at \(\alpha=2j/(M+1)\).

Finally, for each arm, \(\sum_{O\in\mathcal O}\delta_{a,O}(w)=0\), since both orbit-mass vectors have total mass one. Thus the sum of the positive coordinates of \((\delta_{a,O}(w))_O\), and also the absolute sum of its negative coordinates, equals
\[
\frac12\sum_{O\in\mathcal O}|\delta_{a,O}(w)|=\Delta_a(w).
\]
Every positive coordinate is at most the positive-coordinate sum, and the absolute value of every negative coordinate is at most the absolute negative-coordinate sum. Therefore \(|\delta_{a,O}(w)|\le\Delta_a(w)\) for every \(a\in\{0,1\}\) and \(O\in\mathcal O\), as claimed.