Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,\qquad \Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
The deterministic-preorder interpretation, coherent common-target calculation, full-model disclaimer, binary counterexample, disjoint-support value, and comparator scope therefore specialize from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). In particular, its bounded common-Bernoulli construction proves that the diagonal functional is not a uniform full-model joint-inclusion or causal effect-set coverage certificate.

The pointwise implication specializes to
\[
\{Y_{0T}(1)\in I_{1,w},Y_{0T}(0)\in I_{0,w}\}\subseteq\{\tau_T\in I_{1,w}-I_{0,w}\}=\{\tau_T\in\mathcal C_w\}.
\tag{2}
\]
If both intervals are \(\{0\}\) and both outcomes equal \(K\), the right event holds while the left event fails.

When \(k\le M\), substitute \(\bar k_0=\bar k_1=\bar k=\min\{k,M-k+1\}\) into the asymmetric seven-way partition. The rolling charge becomes \(\mathsf C_{M,k,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2\), the branch sum becomes exactly \(\mathsf B_{\mathrm{sym}}\), and the maximum live workspace becomes \(\mathsf W_{\mathrm{sym}}\). The adaptive, uniform, and memory bounds follow from \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). Vertex, edge, face, and rank-one keys use constant auxiliary workspace, and rank-one keys do not trigger factorial preprocessing.

For every \(M\ge2\), \(\alpha=2/(M+1)\) gives \(k=M\). The audited edge key \(\pi=(1/2,1/2,0,0)\) has \(D_{M,M,M}(\pi)=1-2^{-M}\), with \(\Theta(\log M)\) time rather than \(\Theta(M)\). The audited face key \(\pi=(1/3,1/3,1/3,0)\) has \(D_{M,M,M}(\pi)=1-2\cdot3^{-M}\), with the same strict resource improvement. The off-diagonal rank-one audit remains a strict certificate for the common evaluator, while the diagonal charge is \(\mathsf R_{M,k,k}=1+2\lceil\log_2M\rceil+2\bar k\). If \(k=M+1\), both rank events are certain and \(\Gamma_{M,\alpha}(w)=0\).

Equation (1) also transfers the exact four-level and binary values and their positive gap, as well as the value \(1-\alpha\) under disjoint support. The full-model guarantees remain those in \(\texttt{thm:common-selector-lp}\) and \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\). The literature comparison likewise specializes only as a comparison of different optimized objects. Therefore no branch change affects the common-target, active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit semantics.