Assume that \(\mathcal H\) is finite and nonempty, fix \(w\in\Delta(\mathcal H)\), condition on \(\mathcal T\), and fix an arm \(a\). By \(\texttt{lem:orbit-score-factorization}\), the \(M\) calibration orbit--score pairs are independent and identically distributed with law
\[
\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),
\tag{1}
\]
and the independent target orbit--score pair has law
\[
\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).
\tag{2}
\]
Orbit overlap implies \(\mathsf P_a\ll\mathsf Q_a\). Because the same conditional score kernel \(F_{a,O}\) occurs in (1) and (2), it cancels from the likelihood ratio, giving
\[
\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\frac{p_{a,O}}{q_{a,O}}=\lambda_{a,O}
\quad\text{for }\mathsf Q_a\text{-almost every target-relevant }(O,s).
\tag{3}
\]
Thus quotient-orbit overlap suffices: arbitrary singularity among member labels inside a common orbit disappears after the common kernel is factored out.

Apply \(\texttt{lem:finite-support-weighted-rank-validity}\) to (1)--(3), with \(R_i=S_{i,a}\) and \(\epsilon=\epsilon_a\). The target has \(p_{a,O_{T,a}}>0\) almost surely, so overlap implies \(\lambda_{a,O_{T,a}}>0\). The infinity-augmented weighted measure is therefore well defined, and its stated left-continuous quantile is exactly \(r^{\mathrm W}_{a,w}\). The lemma gives
\[
\Pr_P\!\left(S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\right)\le\epsilon_a.
\tag{4}
\]
This is the finite-support likelihood-ratio weighted-rank step; equation (3) is the design-specific orbit-quotient reduction.

Let \(E_a=\{S_{0,a}\le r^{\mathrm W}_{a,w}\}\). On \(E_a\), the score definition gives
\[
Y_{0T}(a)\in[\widehat m_a(X_{0T})-r^{\mathrm W}_{a,w},\widehat m_a(X_{0T})+r^{\mathrm W}_{a,w}].
\tag{5}
\]
The bounded-outcome assumption also gives \(Y_{0T}(a)\in[-K,K]\), so (5) implies \(Y_{0T}(a)\in I^{\mathrm W}_{a,w}\), including when the radius is infinite. Applying (4) to both arms and using the union bound, without arm independence, yields
\[
\Pr_P(E_0\cap E_1\mid\mathcal T)\ge1-\epsilon_0-\epsilon_1\ge1-\alpha.
\tag{6}
\]
The same common target \(T\) and common selector mixture \(w\) occur in both events. On their intersection,
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.
\tag{7}
\]
Equations (6)--(7) prove the asserted coverage uniformly over the declared laws and fixed measurable trained maps.

Under joint orbit balance, \(p_{a,O}=q_{a,O}\) for every orbit. Hence \(\lambda_{a,O}=1\) on every orbit that can be drawn; zero-mass orbits are irrelevant. The normalized weighted measure then has \(M+1\) equal-mass atoms, one at each calibration score and one at \(+\infty\). Its left-continuous \((1-\epsilon_a)\)-quantile is the \(k_a\)-th ordered atom, where
\[
k_a=\left\lceil(M+1)(1-\epsilon_a)\right\rceil.
\tag{8}
\]
If \(k_a\le M\), this is the \(k_a\)-th calibration order statistic; if \(k_a=M+1\), it is \(+\infty\). Therefore
\[
r^{\mathrm W}_{a,w}=r_{a,(k_a)},
\tag{9}
\]
so weighted inversion is exactly the ordinary arm-specific rank inversion with arm level \(\epsilon_a\). Taking \(\epsilon_0=\epsilon_1=\alpha/2\) in (8)--(9) gives the common rank \(\lceil(M+1)(1-\alpha/2)\rceil\) and the symmetric intervals and effect set. This also identifies precisely which part of the argument is the general weighted-rank inequality and which parts are the matched-block orbit reduction, common-target coupling, clipping, and Bonferroni deductions.