Use the corrected likelihood-ratio convention in the proposed symbol replacement. Fix an arm \(a\), condition on \(\mathcal T\), and put \(\varepsilon=\alpha/2\). By \(\texttt{lem:orbit-score-factorization}\), the calibration pair has law \[\mathsf Q_a(O,ds)=q_{a,O}F_{a,O}(ds),\] and the independent target pair has law \[\mathsf P_a(O,ds)=p_{a,O}F_{a,O}(ds).\] Orbit overlap gives \(\mathsf P_a\ll\mathsf Q_a\), with \[\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\lambda_{a,O}.\] Thus member-level singularity is immaterial: conditional on the orbit, both selectors induce the same score law \(F_{a,O}\).

We prove the required weighted-rank inequality directly. Given \(M+1\) orbit-score pairs \(X_j=(O_j,S_j)\), put \(\ell_j=\lambda_{a,O_j}\) and \(W=\sum_{j=0}^M\ell_j\). For candidate target index \(j\), let \(r_j\) be the left-continuous \((1-\varepsilon)\)-quantile obtained by placing weight \(\ell_j\) at \(+\infty\) and weight \(\ell_i\) at \(S_i\) for \(i\ne j\), normalized by \(W\), and set \(\phi_j=\mathbf 1\{S_j>r_j\}\). On the irrelevant event \(W=0\), set every \(\phi_j=0\). Deterministically, \[\sum_{j=0}^M\ell_j\phi_j\le\varepsilon W.\] Indeed, if there is a failing index, choose one, say \(j_*\), with the smallest score among failing indices. Since \(S_{j_*}>r_{j_*}\), the quantile definition implies that indices with score strictly below \(S_{j_*}\) have total weight at least \((1-\varepsilon)W\). None of those indices fails by the choice of \(j_*\). Hence all failing indices together have weight at most \(\varepsilon W\). Ties do not alter the argument because failure is the strict event \(S_j>r_j\).

Under \(\mathsf Q_a^{M+1}\), the pairs are exchangeable. Changing coordinate zero from \(\mathsf Q_a\) to \(\mathsf P_a\) gives \[\Pr_{\mathsf P_a\otimes\mathsf Q_a^M}(S_0>r_0)=\mathbb E_{\mathsf Q_a^{M+1}}[\ell_0\phi_0]=\frac1{M+1}\mathbb E_{\mathsf Q_a^{M+1}}\!\left[\sum_{j=0}^M\ell_j\phi_j\right].\] Also, overlap and the corrected convention give \[\mathbb E_{\mathsf Q_a}\lambda_{a,O}=\sum_{O:q_{a,O}>0}q_{a,O}\frac{p_{a,O}}{q_{a,O}}=\sum_Op_{a,O}=1.\] The deterministic inequality therefore yields \[\Pr(S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T)\le\frac{\varepsilon}{M+1}\mathbb E\sum_{j=0}^M\ell_j=\varepsilon=\frac\alpha2.\]

The event \(S_{0,a}\le r^{\mathrm W}_{a,w}\) is exactly \(Y_{0T}(a)\in I^{\mathrm W}_{a,w}\). Applying the armwise inequality twice and using Bonferroni gives probability at least \(1-\alpha\) that both potential outcomes lie in their respective intervals. On that event, \[\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.\] This proves the asserted conditional coverage without any cross-arm independence. Finally, under joint orbit balance, every orbit that can be realized has \(p_{a,O}=q_{a,O}>0\), hence weight one. The weighted empirical measure then has \(M\) unit atoms at the calibration scores and one unit atom at \(+\infty\); its \((1-\alpha/2)\)-quantile is exactly the order statistic in \(\texttt{def:rank-inversion}\), including the \(k=M+1\) convention. Thus weighted rank inversion recovers ordinary rank inversion.