Fix an arm \(a\) and condition on \(\mathcal T\). By \(\texttt{ass:external-observed-training}\), the fitted map \(\widehat m_a\) is then fixed and the conditional law of every experimental replicate is unchanged. For \(v\in\mathcal V\), put \[R_{v,a}=|Y_v(a)-\widehat m_a(X_v)|,\qquad F_{v,a}(C)=\Pr_P\{R_{v,a}\in C\mid\mathcal T\}\] for every Borel set \(C\subseteq[0,\infty)\). If \(v'=\pi_g(v)\), invariance of \(P\) under the action in \(\texttt{def:group-action}\) gives \(F_{v',a}=F_{v,a}\). Hence there is a well-defined probability kernel \(F_{a,O}\) for every orbit \(O\in\mathcal O\), equal to \(F_{v,a}\) whenever \(\iota_a(v)\in O\).

The design and selector symmetries also imply that the integrated selector law is constant along member orbits. Indeed, using the bijection \(z=gy\), \(\nu(gy)=\nu(y)\), and selector equivariance, \[q^{\mathrm{obs}}_{h,a}(\pi_gv,a)=\sum_y\nu(gy)\kappa_{h,a}(\pi_gv\mid gy)=\sum_y\nu(y)\kappa_{h,a}(v\mid y)=q^{\mathrm{obs}}_{h,a}(v,a).\] More importantly, randomization is independent of the latent array and the auxiliary selector draw uses only \(Z_i\). Therefore, for \(i\ge1\), \[\Pr(S_{i,a}\in C\mid\mathcal T)=\sum_{v\in\mathcal V}q^{\mathrm{obs}}_{w,a}(v,a)F_{v,a}(C)=\sum_{O\in\mathcal O}q^{\mathrm{obs}}_{w,a}(O)F_{a,O}(C).\tag{1}\] Independence of \(T\) and \(L_0\) similarly gives \[\Pr(S_{0,a}\in C\mid\mathcal T)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)F_{v,a}(C)=\sum_{O\in\mathcal O}q_{\mathrm{tar},a}(O)F_{a,O}(C).\tag{2}\] Thus joint orbit balance makes (1) and (2) equal for every \(P\in\mathcal P_{\mathcal G,K}\), every fixed measurable fitted map, and both arms.

Conversely, suppose the masses differ for an arm \(a\) and orbit \(O_*\). Use \(\texttt{def:orbit-separating-law}\) with \(\widehat m_0=\widehat m_1=0\). Its outcome prototype is constant on every orbit, and averaging its complete latent prototype over a uniform element of the finite group makes the latent law invariant. Its outcomes lie in \([-K,K]\), so the resulting law belongs to \(\mathcal P_{\mathcal G,K}\). Under this law the arm-\(a\) score is \(K\) exactly on \(O_*\) and is zero elsewhere. Consequently, \[\Pr(S_{i,a}=K\mid\mathcal T)=q^{\mathrm{obs}}_{w,a}(O_*),\qquad \Pr(S_{0,a}=K\mid\mathcal T)=q_{\mathrm{tar},a}(O_*),\] which are unequal because \(K>0\). Universal equality of score laws therefore forces equality of every orbit mass in each arm.

Finally, under balance, \(\texttt{ass:independent-replicated-arrays}\), the product randomization law, and \(\texttt{ass:selector-auxiliary-randomization}\) make \(S_{1,a},\ldots,S_{M,a}\) independent and identically distributed. The independent target draw and replicate \(L_0\) make \(S_{0,a}\) independent of them; equations (1)--(2) give the common marginal law. This argument is armwise. Since the two scores of a replicate and the two lifts of \(T\) can be dependent, it asserts no exchangeability across arms.