Put \(N=M+1\). The claimed rank equivalence follows directly from the ceiling identity: 
\[k\le M\iff \left\lceil N(1-\alpha/2)\right\rceil\le N-1\iff N(1-\alpha/2)\le N-1\iff \alpha\ge\frac{2}{M+1}.\]
Fix the adverse arm \(a\). Under \(\texttt{def:disjoint-orbit-law}\), the arm-\(a\) potential outcome is \(K\) on target-supported arm-\(a\) orbits and zero on every other arm-\(a\) orbit, while every arm-\((1-a)\) potential outcome is zero. The premise that every target-supported arm-\(a\) orbit has zero calibration mass makes these prescriptions consistent. Complete the prototype by taking a common fixed covariate value at every member. The resulting latent prototype is constant on every \(\mathcal G\)-orbit, so relabelling it by any \(g\in\mathcal G\) leaves it unchanged; in particular, its uniform group randomization satisfies \(\texttt{ass:finite-group-latent-invariance}\). All its outcome coordinates lie in \(\{0,K\}\subseteq[-K,K]\), so \(\texttt{ass:bounded-potential-outcomes}\) also holds. Therefore the resulting law belongs to \(\mathcal P_{\mathcal G,K}\) by \(\texttt{def:invariant-laws}\); independent replication, the known assignment law, and the stipulated auxiliary selector draws give the declared experiment.

Let \(O\) have \(q^{\mathrm{obs}}_{w,a}(O)>0\). It cannot be target-supported, so the construction assigns outcome zero to arm \(a\) throughout \(O\). The construction also fixes \(\widehat m_a=0\), and \(\texttt{ass:observable-selector-kernel}\) forces \(J_{i,a}\) to be observed in arm \(a\). Thus every selected adverse-arm calibration score is zero almost surely. Since \(k\le M\),
\[r_{a,(k)}=0.\]
All outcomes and the predictor in arm \(1-a\) are also zero, hence that arm's calibration scores and threshold are zero. It follows from \(\texttt{def:rank-inversion}\) that
\[I_{0,w}=I_{1,w}=\{0\},\qquad \mathcal C_w=\{0\}-\{0\}=\{0\}.\]
By \(\texttt{ass:prespecified-target}\), the selected member lies in a target-supported orbit almost surely. Hence \(Y_{0T}(a)=K\) and \(Y_{0T}(1-a)=0\). Therefore \(\tau_T=K\) if \(a=1\), whereas \(\tau_T=-K\) if \(a=0\). Since \(K>0\), neither value belongs to \(\{0\}\), and consequently
\[\Pr_P(\tau_T\in\mathcal C_w\mid\mathcal T)=0.\]