For each assignment \(z\), aggregate the legal selector within orbits:
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z).
\tag{1}
\]
Conditional on \(Z_i=z\), \(\texttt{ass:selector-auxiliary-randomization}\) makes the two selected members independent with their armwise kernels. Integrating over \(\nu\) gives the full joint law \(R_w\). Across replicates these pairs are iid by the product auxiliary draws and known replicated design. The common target has joint orbit law \(P_T\) because one member \(T\) supplies both lifts. Its support is an image of \(\mathcal V\), hence
\[
L\le\min\{|\mathcal V|,m_0m_1\}.
\tag{2}
\]
Pushing through preorder classes cannot increase support and has range \(d_0d_1\), so
\[
L_C\le\min\{L,d_0d_1\}.
\tag{3}
\]

For a target class pair \((j,\ell)\), a two-dimensional strict-prefix table of \(R_w\) gives the four probabilities that neither, only arm zero, only arm one, or both calibration scores are strictly below their target scores. Call this vector \(\pi^C(j,\ell)\). The strict prefix is required because
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{4}
\]
Conditioning on the target class and grouping equal four-cell vectors yields
\[
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi),
\qquad U_C\le L_C.
\tag{5}
\]
The value \(D\) depends only on \(M,k_0,k_1\) and three cells of \(\pi\). Therefore the global memo key is exact, while keeping \(\omega_C\) local preserves \(P_T^C\). Equations (1) and (5) show that \(R_w\) is never factorized and the common target is never replaced by two targets.

By \(\texttt{lem:four-cell-rank-event-dynamic-program}\), support-one keys cost constant time and support-two keys cost \(\mathsf E_M(\pi)\) time with constant workspace. By the three frozen exact evaluators, every remaining key has charges \(\mathsf C_{M,k_0,k_1}\), \(M+\mathsf T_{M,\bar k_0,\bar k_1}\), and \(\mathsf C_+(\pi)\). Deterministic least-charge selection therefore gives the five-way disjoint partition and exactly \(\mathsf B\). Only the multinomial branch uses factorials. Sequential key evaluation gives the maximum live workspace \(\mathsf W\); support-one and support-two keys are absorbed by its constant term.

The target scan costs \(O(|\mathcal V|)\). Per preorder pair, class aggregation, the prefix table, and target pushforward cost \(O(m_0m_1+L)\). A local balanced tree costs \(O(L_C\log(1+L_C))\) comparisons and \(O(L_C)\) aggregation, forming (5) costs \(O(U_C)\), and the global memo costs
\[
O\!\left(\Bigl(\sum_CU_C\Bigr)\log(1+G)\right).
\]
Adding \(\mathsf B\) proves the adaptive time formula. Substitution of \(L_{\max}\) and \(U_{\max}\) proves the uniform formula. The live orbit table, target table, local grouping table, \(G\) scalar memo entries, and exact evaluator prove the memory formula.

We finally audit the strict witness. Let \(M=2n\) with \(n\ge2\), \(k_0=n\), \(k_1=M\), and let the edge support be \(u=(0,0)\), \(v=(0,1)\), each with mass \(1/2\). If \(N\sim\operatorname{Bin}(M,1/2)\), then
\[
R_M=0,\qquad S_M=N.
\tag{6}
\]
Thus
\[
D_{M,n,M}(\pi)=\Pr\{N<M\}=1-2^{-M}.
\tag{7}
\]
The interval is \([0,M-1]\); its complement is the single endpoint \(M\). Exponentiation by squaring evaluates \(2^{-M}\) in \(\Theta(\log M)\) exact arithmetic and constant workspace. For the former dispatcher, the rolling charge is \(\Theta(M^2)\). The multinomial charge is \(M+\mathsf T_{M,n,1}=\Theta(M)\). In the positive-corner branch, the only positive-base orientations have either an \(n\times M\) coefficient rectangle or an \(n\times1\) rectangle plus an arm-zero marginal of width \(n\), so \(\mathsf C_+(\pi)=\Theta(M)\). Hence its least charge is \(\Theta(M)\), proving strict improvement.

For admissibility, take two pair blocks and \(\mathcal G=S_2^2\), so each pure local swap is audited by \(\texttt{def:pair-action}\) and each \(O_{b,a}\) is a global orbit. In each block independently assign exactly one treated member with probability \(1/2\) to each member. This law is invariant under both swaps and satisfies \(\texttt{ass:known-matched-randomization}\). Let the selector library be a singleton. Its arm-\(1\) kernel first chooses block \(1\) or \(2\) with probability \(1/2\), independently of labels, then chooses the unique member observed in arm \(1\); define the arm-\(0\) kernel analogously. The kernels select observed-arm members, are equivariant under both swaps, and their auxiliary draws obey the declared product law. Put the target law on a fixed member of block \(2\), independently of calibration data. The two target lifts therefore lie in the block-\(2\) orbits. Order block \(2\) lowest in arm \(0\); then the strict-below arm-zero indicator is always zero. Order block \(1\) below block \(2\) in arm \(1\); then the arm-one indicator equals one exactly when the selector chooses block \(1\), with probability \(1/2\). Thus the induced key is exactly \((1/2,1/2,0,0)\). The construction uses only selector and target rules fixed before scores, so external training and score values do not affect the audit.

Finally, with \(M+1=2n+1\),
\[
\left\lceil(2n+1)\left(1-\frac{n+1}{2n+1}\right)\right\rceil=n,
\qquad
\left\lceil(2n+1)\left(1-\frac1{2n+1}\right)\right\rceil=2n=M.
\tag{8}
\]
The two levels are positive, their sum is \((n+2)/(2n+1)=\alpha\), and \(\alpha<1\) because \(n\ge2\). This verifies every rank and budget condition and completes the proof.