Condition throughout on \(\mathcal T\), and fix an arm \(a\in\{0,1\}\). The trained map \(\widehat m_a\) is then fixed. By \(\texttt{lem:orbit-score-factorization}\), there are probability laws \(F_{a,O}\) such that the \(M\) calibration orbit--score pairs are independent and identically distributed with law
\[
\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),
\]
whereas the independent target orbit--score pair has law
\[
\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).
\]
Assumption \(\texttt{ass:orbit-overlap}\) gives \(\mathsf P_a\ll\mathsf Q_a\). On every orbit fibre with positive \(\mathsf P_a\)-mass,
\[
\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\frac{p_{a,O}}{q_{a,O}}=\lambda_{a,O}.
\tag{1}
\]
Thus the likelihood ratio depends only on the orbit: the common conditional score law \(F_{a,O}\) cancels. This also proves that no member-level overlap inside an orbit is needed.

Because \(\epsilon_a>0\) and \(\epsilon_0+\epsilon_1\le\alpha<1\), one has \(0<\epsilon_a<1\). Apply \(\texttt{lem:finite-support-weighted-rank-validity}\), conditionally on \(\mathcal T\), with \(\mathscr E=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\), \(q_O=q_{a,O}\), \(p_O=p_{a,O}\), \(R_i=S_{i,a}\), and \(\varepsilon=\epsilon_a\). The target draw satisfies \(p_{a,O_{T,a}}>0\) almost surely. Orbit overlap therefore gives \(q_{a,O_{T,a}}>0\) and \(\lambda_{a,O_{T,a}}>0\), so the infinity-augmented measure has strictly positive total mass. Its left-continuous \((1-\epsilon_a)\)-quantile is exactly \(r^{\mathrm W}_{a,w}\) from \(\texttt{def:weighted-rank-inversion}\). Consequently,
\[
\Pr_P\!\left(S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\right)\le\epsilon_a.
\tag{2}
\]

Let \(E_a=\{S_{0,a}\le r^{\mathrm W}_{a,w}\}\), and define the unclipped interval
\[
\widetilde I^{\mathrm W}_{a,w}=\left[\widehat m_a(X_{0T})-r^{\mathrm W}_{a,w},\,\widehat m_a(X_{0T})+r^{\mathrm W}_{a,w}\right].
\]
On \(E_a\), the identity \(S_{0,a}=|Y_{0T}(a)-\widehat m_a(X_{0T})|\) implies \(Y_{0T}(a)\in\widetilde I^{\mathrm W}_{a,w}\). Assumption \(\texttt{ass:bounded-potential-outcomes}\) also gives \(Y_{0T}(a)\in[-K,K]\). Since
\[
I^{\mathrm W}_{a,w}=\widetilde I^{\mathrm W}_{a,w}\cap[-K,K],
\]
we have \(Y_{0T}(a)\in I^{\mathrm W}_{a,w}\) on \(E_a\), including when \(r^{\mathrm W}_{a,w}=+\infty\).

Applying \((2)\) to the two arms and using the union bound, with no cross-arm independence assumption, gives
\[
\Pr_P(E_0\cap E_1\mid\mathcal T)\ge 1-\epsilon_0-\epsilon_1\ge1-\alpha.
\tag{3}
\]
On \(E_0\cap E_1\), set subtraction yields
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.
\]
Combining this inclusion with \((3)\) proves
\[
\Pr_P(\tau_T\in\mathcal C^{\mathrm W}_w\mid\mathcal T)\ge1-\epsilon_0-\epsilon_1\ge1-\alpha.
\]
The argument is conditional on any fixed or prespecified \(w\) and applies to every declared law and every fixed measurable trained predictor map.

It remains to prove the reduction under joint orbit balance. By \(\texttt{thm:orbit-balance-iff}\), balance gives \(p_{a,O}=q_{a,O}\) for every arm and orbit. Hence \(\lambda_{a,O}=1\) on every orbit that can be drawn; orbits with zero mass under both laws are irrelevant. For arm \(a\), the normalized weighted measure therefore has \(M+1\) equal-mass atoms: one at each of the \(M\) calibration scores and one at \(+\infty\). Its left-continuous \((1-\epsilon_a)\)-quantile is the \(k_a\)-th order statistic of these atoms, where
\[
k_a=\left\lceil(M+1)(1-\epsilon_a)\right\rceil.
\]
If \(k_a\le M\), this is the \(k_a\)-th order statistic of the calibration scores; if \(k_a=M+1\), it is \(+\infty\). These are exactly the two clauses defining \(r_{a,(k_a)}\) in \(\texttt{def:rank-inversion}\). Therefore \(r^{\mathrm W}_{a,w}=r_{a,(k_a)}\), \(I^{\mathrm W}_{a,w}=I_{a,w}\), and \(\mathcal C^{\mathrm W}_w=\mathcal C_w\). Finally, setting \(\epsilon_0=\epsilon_1=\alpha/2\) gives \(k_0=k_1=\lceil(M+1)(1-\alpha/2)\rceil\), so the symmetric construction and every conclusion of the original theorem are recovered.