Condition throughout on \(\mathcal T\), so the trained maps are fixed. By \(\texttt{lem:orbit-score-factorization}\), for each arm \(a\) there are orbit-specific laws \(F_{a,O}\) such that a calibration orbit--score pair has law
\[
\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),
\tag{1}
\]
whereas the independent target orbit--score pair has law
\[
\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).
\tag{2}
\]
The \(M\) calibration pairs are independent and identically distributed and are independent of the target pair, separately for each arm.

Suppose joint orbit balance holds. Then \(q_{a,O}=p_{a,O}\) for every arm and orbit. Summing (1) and (2) over \(O\) shows that \(S_{i,a}\) and \(S_{0,a}\) have the same conditional law. The independence assertion in the factorization lemma then implies that
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are conditionally independent and identically distributed for each fixed \(a\). This is only an armwise conclusion: neither the common target nor the selectors' common within-replicate assignment has been factored across arms.

Conversely, suppose that for some arm \(a\) and orbit \(O\), one has \(q_{a,O}\ne p_{a,O}\). Apply \(\texttt{def:orbit-separating-law}\), take constant covariates, and fix \(\widehat m_0=\widehat m_1=0\). Its outcomes belong to \(\{0,K\}\), so boundedness holds. Moreover, membership of \((v,a)\) in the \(\mathcal G\)-orbit \(O\) is unchanged by every group element. Hence the orbit-constant prototype is invariant; equivalently, its uniform group symmetrization is invariant. Thus the constructed law belongs to \(\mathcal P_{\mathcal G,K}\). The arm-\(a\) score is exactly
\[
K\mathbf 1\{\text{the selected arm-}a\text{ state lies in }O\}.
\tag{3}
\]
Using the calibration and target orbit masses in (1)--(2), respectively, gives
\[
\Pr(S_{i,a}=K\mid\mathcal T)=q_{a,O},\qquad
\Pr(S_{0,a}=K\mid\mathcal T)=p_{a,O}.
\tag{4}
\]
The two score laws therefore differ. Taking the contrapositive, equality of the calibration and target score laws for every bounded invariant law and every fixed measurable trained map forces \(q_{a,O}=p_{a,O}\) for every orbit. Applying this argument to both arms proves joint orbit balance.

The forward direction is precisely the elementary equality of two finite mixtures with common kernels \(F_{a,O}\), once orbit-score factorization is known. The necessity direction is also a finite-partition separation, but (3)--(4) verify that every failed orbit equation has a realizable bounded invariant matched-randomization witness; no generic priority claim for mixture identities is needed.