Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). Suppose first that \(k_a\le M\). For a fixed target orbit, the elementary order-statistic identity is
\[
s_a(O_{T,a})
\le
Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M
\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}
<k_a.
\tag{1}
\]
Indeed, the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by the strict comparison in (1), and the event depends on \(s_a\) only through its total preorder. Conversely, if a total preorder has ordered nonempty classes
\[
C_{a,1}\prec_a\cdots\prec_a C_{a,d_a},
\]
assign score zero if \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). Every preorder has a representative in \([0,K]\) with at most \(m_a\) levels. The declared finite maximum is therefore attained by preorder enumeration. This proves exactness over the score-map class in \(\texttt{def:coverage-frontier}\); it does not identify that maximum with a supremum over latent laws.

Assume first that \(k_0,k_1\le M\). By \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\), the unchanged shared-assignment law \(R_w\) and coherent common-target law \(P_T\) give, for every preorder pair \(C\),
\[
U_C\le L_C\le\min\{L,d_0d_1\},
\qquad
\Pr\{\text{both rank events}\}
=
\sum_{\pi\in\Pi_C}
\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
The exact key \((M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10})\) determines the count probability in (2), while \(\omega_C\) is applied only when the preorder objective is formed. The local grouping, global lookup, single recurrence computation for each of the \(G\) keys, and table-construction charges proved in that lemma yield the stated instance-adaptive time bound, its uniform specialization, and the memory bound. Every \(\pi\) is formed from the full \(R_w\), and every \(\omega_C\) from the pushforward of the single \(P_T\), so memoization changes computation but neither law. The zero-cell-safe multinomial summation and corner-oriented recurrence supplied by \(\texttt{lem:four-cell-multinomial-sum-alternative}\) and \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) are exact alternatives for each key. Selecting the rolling recurrence always proves the displayed coarser charges \(GMk_0k_1\) and \(O(k_0k_1)\).

Suppose next that exactly one rank, \(k_b\), equals \(M+1\), and put \(c=1-b\). By \(\texttt{def:rank-inversion}\), the boundary event is certain. Conditional on \(O_{T,c}=O_t\), (1) counts iid Bernoulli trials with success probability
\[
\theta(O_t)
=
\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}
q_{c,O}.
\tag{3}
\]
The calibration orbit draws are iid by \(\texttt{ass:known-matched-randomization}\) and \(\texttt{ass:selector-auxiliary-randomization}\), and independent of the target by \(\texttt{ass:prespecified-target}\). Hence the exact joint rank-event probability is
\[
\sum_{O_t\in\mathcal O_c}
p_{c,O_t}
\Pr\!\left\{
\operatorname{Bin}\bigl(M,\theta(O_t)\bigr)<k_c
\right\}.
\tag{4}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), put
\[
q_j=q_c(C_j),\qquad
p_j=p_c(C_j),\qquad
\theta_j=\sum_{\ell<j}q_\ell.
\tag{5}
\]
Every target orbit in class \(j\) has the same strict-prefix probability, so (4) becomes
\[
\sum_{j=1}^d
p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}.
\tag{6}
\]
One cumulative ordered-class scan forms all quantities in (5).

For \(0<\theta<1\), successive binomial probabilities give
\[
t_0=(1-\theta)^M,\qquad
t_{r+1}
=
t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},
\quad 0\le r<k_c-1,
\tag{7}
\]
and, from the upper endpoint,
\[
u_M=\theta^M,\qquad
u_{r-1}
=
u_r\frac r{M-r+1}\frac{1-\theta}{\theta},
\quad k_c<r\le M.
\tag{8}
\]
Exponentiation by squaring initializes (7) or (8) in \(O(\log M)\) operations. Summing the shorter of the lower tail and complementary upper tail takes
\[
O(\min\{k_c,M-k_c+1\})
\tag{9}
\]
additional operations. At \(\theta=0\), the probability in (6) is one, and at \(\theta=1\) it is zero, without division. By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) and \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), enumeration of only the \(F_{m_c}\) nonboundary preorders therefore costs
\[
O\!\left(
F_{m_c}m_c
[1+\log M+\min\{k_c,M-k_c+1\}]
\right)
\tag{10}
\]
arithmetic operations and \(O(1)\) auxiliary CDF memory after the marginal vectors are tabulated. Formula (6) has no boundary-arm preorder, member-level scan, or cross-arm table.

If both ranks equal \(M+1\), both rank events are certain. Thus the expression in \(\texttt{def:coverage-frontier}\) equals
\[
[(1-\alpha)-1]_+=0,
\tag{11}
\]
which proves the two-boundary claim.

It remains to prove that binary attainment is false. Consider four pair blocks with \(\mathcal G=S_2^4\). This product contains every pure local swap used below, so the sufficient audit in \(\texttt{def:pair-action}\) makes each arm-specific pair cell a global orbit. Randomize treatment fairly and independently within pairs. Let an equivariant selector first choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{12}
\]
and then choose the unique member observed in the requested arm. Let the common target choose a block with probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right)
\tag{13}
\]
and choose either member of that block with equal probability. These rules satisfy \(\texttt{ass:observable-selector-kernel}\) and \(\texttt{ass:selector-equivariance}\); the two armwise auxiliary block draws are independent conditional on assignment as required by \(\texttt{ass:selector-auxiliary-randomization}\). Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Set \(s_0\equiv0\) and order the arm-one blocks as
\[
1\prec3\prec2\prec4.
\tag{14}
\]
The arm-zero event is certain. Direct strict-prefix evaluation of the arm-one failure event gives
\[
\frac14\left(\frac{13}{20}\right)^3
+
\frac1{10}\left(\frac{18}{20}\right)^3
+
\frac35\left(\frac{19}{20}\right)^3
=
\frac{104957}{160000}.
\tag{15}
\]
Consequently the frontier objective is
\[
\frac{104957}{160000}-\frac12
=
\frac{24957}{160000}.
\tag{16}
\]

For a binary score pair, let \(H_a\) be arm \(a\)'s high-score block set and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion, retaining the common target and the independent auxiliary block choices, gives exact joint failure probability
\[
F_{\mathrm{bin}}(H_0,H_1)
=
p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{17}
\]
There are sixteen subsets. In the order
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
exact substitution in (17), maximizing over \(H_1\) in each successive \(H_0\)-row, gives the numerators
\[
\begin{gathered}
164616000,\ 165302000,\ 192052000,\ 198366000,\\
207906936,\ 165912000,\ 164712000,\ 165787368,\\
203032000,\ 208582976,\ 208582976,\ 164632000,\\
165793875,\ 164631423,\ 202894331,\ 164616000
\end{gathered}
\tag{18}
\]
over the common denominator \(320000000\). The maximum is \(3259109/5000000\). Hence every binary pair has frontier objective at most
\[
\frac{3259109}{5000000}-\frac12
=
\frac{759109}{5000000}.
\tag{19}
\]
The four-level objective exceeds (19) by
\[
\frac{24957}{160000}
-
\frac{759109}{5000000}
=
\frac{83189}{20000000}
>0.
\tag{20}
\]

Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Assign score \(K\) to target-supported arm-\(a\) orbits and zero to calibration-supported and remaining arm-\(a\) orbits; assign score zero throughout the other arm. Then the arm-\(a\) rank event fails surely, so the joint event has probability zero. The deficit equals \(1-\alpha\), and no positive-part deficit can exceed \(1-\alpha\); therefore
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha.
\tag{21}
\]
If \(k_a=M+1\), that arm's event is certain and (4)--(6) give exactly the other arm's rank event. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), yielding \(\texttt{thm:sharp-orbit-coverage-frontier}\).