For \(h\in\mathcal H\), write \(A_{\cdot h}\) for column \(h\) of \(A\). For every \(w\in\Delta(\mathcal H)\), the definitions of \(A\), \(b_{\mathrm{LP}}\), and the integrated selector law give, row by row,
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_hq^{\mathrm{obs}}_{h,a}(O)=q^{\mathrm{obs}}_{w,a}(O),\qquad (b_{\mathrm{LP}})_{a,O}=q_{\mathrm{tar},a}(O).
\tag{1}
\]
Consequently, \(Aw=b_{\mathrm{LP}}\) is equivalent to joint orbit balance. If \(\mathcal H\ne\varnothing\), then
\[
\{Aw:w\in\Delta(\mathcal H)\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\tag{2}
\]
Equations (1)--(2) prove the convex-hull and stacked-LP equivalences for a nonempty library. If \(\mathcal H=\varnothing\), the adopted conventions make both \(\Delta(\mathcal H)\) and the displayed convex hull empty, so both sides of the existence equivalence are false. The LP is infeasible for the explicit normalization contradiction
\[
\sum_{h\in\varnothing}w_h=0\ne1.
\tag{3}
\]
There is then no mixture \(w\), hence no implemented mixture kernel or selector-indexed ordinary or weighted procedure. By the frozen definitions of the corresponding symbols, \(D_*\), \(\mathcal W_*\), and \(w_*\) are not instantiated in this case.

Suppose now that \(\mathcal H\ne\varnothing\) and that \(b_{\mathrm{LP}}\) does not belong to the convex hull \(C\) in (2). The set \(C\) is nonempty, compact, and convex. Choose \(c^*\in C\) minimizing \(\lVert b_{\mathrm{LP}}-c\rVert_2\), and put \(y=b_{\mathrm{LP}}-c^*\ne0\). For every \(c\in C\) and \(t\in(0,1]\), minimality along the segment \(c^*+t(c-c^*)\) gives
\[
0\le -2t y^\top(c-c^*)+t^2\lVert c-c^*\rVert_2^2.
\tag{4}
\]
After division by \(t\) and passage to \(t\downarrow0\), one obtains \(y^\top c\le y^\top c^*\) for every \(c\in C\). Moreover,
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\lVert y\rVert_2^2>\sup_{c\in C}y^\top c=\max_{h\in\mathcal H}y^\top A_{\cdot h}.
\tag{5}
\]
Thus (5) is a strict Farkas separating certificate. No separation assertion is needed for the empty hull, for which (3) is the complete certificate.

It remains to prove coverage. Condition on \(\mathcal T\), fix a feasible common \(w\), and put \(N=M+1\). Feasibility and (1) imply joint orbit balance. By \(\texttt{thm:orbit-balance-iff}\), for each arm \(a\),
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\tag{6}
\]
are conditionally independent and identically distributed. Append independent continuous uniforms and rank the augmented pairs lexicographically, as prescribed for proof ranks in \(\texttt{def:rank-inversion}\). Exchangeability and absence of augmented ties make the target rank \(R_{0,a}\) uniform on \(\{1,\ldots,N\}\). If \(k_a\le M\) and \(S_{0,a}>r_{a,(k_a)}\), at least \(k_a\) calibration scores are strictly smaller, so \(R_{0,a}>k_a\). If \(k_a=N\), the threshold is \(+\infty\) and the exceedance event is empty. Hence in both cases
\[
\Pr\!\left(S_{0,a}>r_{a,(k_a)}\mid\mathcal T\right)\le\frac{N-k_a}{N}.
\tag{7}
\]
The elementary identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\), with \(x=N\varepsilon_a\), yields
\[
\frac{N-k_a}{N}=\frac{\lfloor N\varepsilon_a\rfloor}{N}=\rho_{M,\varepsilon_a}\le\varepsilon_a.
\tag{8}
\]
The bounded-outcome assumption gives \(Y_{0T}(a)\in[-K,K]\). Therefore
\[
S_{0,a}\le r_{a,(k_a)}\quad\Longrightarrow\quad Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w},
\tag{9}
\]
including the infinite-radius case. If (9) holds in both arms, then
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{10}
\]
The conditional union bound, which requires no arm independence, and (7)--(10) give
\[
\Pr\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right)\ge1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\ge1-\varepsilon_0-\varepsilon_1\ge1-\alpha.
\tag{11}
\]
On the equal-split diagonal, \(k_0=k_1=\lceil(M+1)(1-\alpha/2)\rceil=k\), and \(\texttt{def:rank-inversion}\) identifies \(I^{\boldsymbol\varepsilon}_{a,w}=I_{a,w}\) and \(\mathcal C^{\boldsymbol\varepsilon}_w=\mathcal C_w\). Equations (7)--(11) then give the symmetric formulas.