Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values of \(s_a\) outside \(\mathcal O_a\) are irrelevant. The phrase "exact finite worst-coverage deficit" refers precisely to the maximum over the bounded orbit-constant score class in \(\texttt{def:coverage-frontier}\); the argument below neither enlarges that class nor identifies it with all laws in \(\mathcal P_{\mathcal G,K}\).

First suppose \(k\le M\). Given a score map \(s_a\), define \(O\preceq_a O'\) if and only if \(s_a(O)\le s_a(O')\). This is a total preorder. For any target orbit and calibration configuration,
\[s_a(O_{T,a})\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\iff \#\{i:s_a(O_{i,a})<s_a(O_{T,a})\}<k.\tag{1}\]
Indeed, the \(k\)-th order statistic is strictly below the target score exactly when at least \(k\) calibration scores are strictly below it. Thus the joint rank event depends only on the pair of total preorders induced by \(s_0\) and \(s_1\). Conversely, if a total preorder on \(\mathcal O_a\) has ordered equivalence classes
\[C_{a,1}\prec_a\cdots\prec_a C_{a,d_a},\]
assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). Since \(K>0\), this gives a representative in \([0,K]\) with \(d_a\le m_a\) levels. When \(k=M+1\), the order statistic is \(+\infty\) by definition, so the rank event is identically true and the same finite reduction is immediate.

The number of total preorders on an \(m\)-element labelled set is
\[F_m=\sum_{d=1}^m d!\left\{\begin{matrix}m\\d\end{matrix}\right\},\tag{2}\]
where the braces denote a Stirling number of the second kind: first partition the set into \(d\) nonempty tie classes and then order those classes. Hence only \(F_{m_0}F_{m_1}\) preorder pairs need be checked. This proves that the maximum is attained.

We next give the exact finite objective. For \(O\in\mathcal O_a\), define the orbit-level selector probability
\[\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),\]
and define the joint calibration-orbit mass
\[R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).\tag{3}\]
The product in (3) follows from \(\texttt{ass:selector-auxiliary-randomization}\), which makes the two selector draws conditionally independent given their shared assignment. Independence across replicated arrays makes the \(M\) calibration orbit pairs iid with mass function \(R_w\). If \(O_a(v)\) is the orbit containing \((v,a)\), then for a fixed preorder pair the joint rank-event probability equals
\[\begin{aligned}&\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\!\sum_{((O_{i,0},O_{i,1}))_{i=1}^M\in(\mathcal O_0\times\mathcal O_1)^M}\!\left\{\prod_{i=1}^M R_w(O_{i,0},O_{i,1})\right\}\\&\qquad\times\prod_{a=0}^1\mathbf 1\!\left\{s_a(O_a(v))\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\right\}.\end{aligned}\tag{4}\]
Formula (4) retains the coherent common target member and the within-replicate cross-arm selector coupling; it invokes no independence between target arms or calibration arms. Substituting (4) into \(\texttt{def:coverage-frontier}\) gives the asserted evaluable finite maximum.

Let \(n=m_0m_1\). Once \(R_w\) has been tabulated, the \(n^M\) configuration weights in (4) can be enumerated by a depth-\(M\), \(n\)-ary recursion using \(O(n^M)\) arithmetic operations. For \(n\ge2\), use reflected \(n\)-ary order, in which successive configurations change one coordinate. For each target member and preorder pair, the two counts in (1) can then be updated in constant time after an \(O(M)\) initialization; because \(M=O(n^M)\) for \(n\ge2\), this does not alter the order. The case \(n=1\) is immediate. Multiplication by the number of preorder pairs and target members yields
\[O\!\left(F_{m_0}F_{m_1}|\mathcal V|(m_0m_1)^M\right).\tag{5}\]

It remains to establish the strict failure of binary attainment. Consider four pair blocks with \(\mathcal G=S_2^4\), and assign exactly one treated member per pair by independent fair within-pair randomization. Let \(\mathcal H\) be a singleton and \(w=1\). Given any assignment, each arm-\(a\) kernel first chooses a block with probabilities
\[q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)\]
and then selects that block's unique observed arm-\(a\) member. The kernel is observable; swapping names within any pair simply relabels the unique selected member, so it is equivariant. The selected block law is \(q\), independently of the realized member labels, and the auxiliary product rule gives \(R_w(b_0,b_1)=q_{b_0}q_{b_1}\). Define the target law by
\[q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},\qquad p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right).\]
Thus the two target lifts share a block having law \(p\). Take \(M=3\) and \(\alpha=1/2\), so \(k=3\). Put \(s_0\equiv0\), and order the arm-\(1\) blocks as \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Arm \(1\) fails exactly when all three calibration blocks are strictly below the target. Its failure probability is
\[F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.\tag{6}\]
Arm zero never fails. Therefore this four-level pair has frontier objective
\[F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.\tag{7}\]

For a binary map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be the blocks assigned the high score \(K\), and put \(A_a=(1-q(H_a))^3\). Conditional on the common target block, inclusion--exclusion gives the exact probability that at least one arm fails:
\[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\tag{8}\]
Indeed, arm \(a\) fails precisely when the target block is in \(H_a\) and all three arm-\(a\) calibration blocks lie outside \(H_a\); the intersection of the two failures has the last probability in (8). In the row order
\[\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,\]
direct rational substitution of all sixteen choices for \(H_1\) into (8), for each displayed choice of \(H_0\), gives the row maxima with common denominator \(320000000\):
\[\begin{split}(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).\end{split}\tag{9}\]
This finite table exhausts all \(16^2\) binary pairs. Hence
\[\max_{H_0,H_1}F_{\mathrm{bin}}(H_0,H_1)=\frac{3259109}{5000000},\]
attained, for example, by \(H_0=\{2,4\}\) and \(H_1=\{3,4\}\). The largest binary frontier objective is consequently \(759109/5000000\), and (7)--(9) give the strict gap
\[\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\]
Thus binary attainment is false.

Finally, suppose target and calibration orbit supports are disjoint in one arm and \(k\le M\). Assign score \(K\) to the target-supported orbits in that arm and zero elsewhere, and assign zero in the other arm. The adverse target score is always \(K\), every adverse calibration score is zero, and the joint rank event has probability zero. The frontier objective is always at most \(1-\alpha\) by its definition and attains that value here. Therefore \(\Gamma_{M,\alpha}(w)=1-\alpha\), consistently with \(\texttt{prop:disjoint-orbit-witness}\). If \(k=M+1\), both rank thresholds in the frontier definition are \(+\infty\), so the joint event has probability one for every score pair and \(\Gamma_{M,\alpha}(w)=0\), consistently with \(\texttt{prop:rank-boundary}\).