By \texttt{def:pair-action}, the nonidentity element \(s_b\) interchanges the two members of block \(b\) without changing the arm label and fixes every member outside that block. Hence, for \(r,a\in\{0,1\}\),
\[s_b(v_{b,r},a)=(v_{b,1-r},a),\]
and the two arm-specific orbits in block \(b\) are exactly
\[O_{b,0}=\{(v_{b,0},0),(v_{b,1},0)\},\qquad O_{b,1}=\{(v_{b,0},1),(v_{b,1},1)\}.\]
The action on complete records is the relabelling in \texttt{def:group-action}.

Suppose the target arm-\(1\) lift is supported on \(O_{b,1}\). Its orbit-mass vector assigns its supported mass to \(O_{b,1}\). An exclusive mate-control analogue instead takes values in \(O_{b,0}\), so it assigns the corresponding mass to a distinct orbit and zero to \(O_{b,1}\). The two orbit-mass vectors differ. Therefore the equality constraints defining joint orbit balance, equivalently the corresponding rows of the stacked feasibility system in \texttt{def:common-selector-feasibility-lp}, cannot hold for that analogue. Moreover, the failure is categorical: by \texttt{ass:observable-selector-kernel}, an arm-\(1\) selector must be supported on realized arm-\(1\) members, hence on \(\mathcal U_1\), whereas the mate-control state lies in \(\mathcal U_0\). It is thus not a legal arm-\(1\) selector.

Now consider separately a legal implemented arm-\(1\) selector with \(q^{\mathrm{obs}}_{w,1}(O_{b,1})=0\). Because the target arm-\(1\) law is supported on \(O_{b,1}\), every target-supported arm-\(1\) orbit has zero calibration mass. This is exactly the premise of \texttt{prop:disjoint-orbit-witness} with \(a=1\). When \(k\le M\), that proposition gives its zero-coverage construction. When \(k=M+1\), the corrected \texttt{prop:rank-boundary} instead gives \(I_{0,w}=I_{1,w}=[-K,K]\), \(\mathcal C_w=[-2K,2K]\), and coverage one. These two cases exhaust the possible rank regimes.