Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). If \(k_a\le M\), then
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Hence ties are handled by strict comparison and the event depends on \(s_a\) only through its total preorder. Conversely, if a preorder has ordered nonempty classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes the preorder in \([0,K]\) with \(d_a\le m_a\) levels. Thus the maximum in \(\texttt{def:coverage-frontier}\) is attained by finite enumeration of the \(F_{m_0}F_{m_1}\) preorder pairs whenever both ranks are finite. Its exactness is exactness for the score class appearing in that definition; it makes no assertion about a supremum over latent laws.

Assume first that \(k_0,k_1\le M\). The coherent evaluator retains the full calibration law
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z)
\tag{2}
\]
and the common-target law
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}.
\tag{3}
\]
For every preorder pair \(C\), \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) constructs each exact vector \(\pi^C(j,\ell)\) from a prefix table of (2), pushes (3) to \(P_T^C\), and proves
\[
U_C\le L_C\le\min\{L,d_0d_1\},\qquad
\Pr\{\text{both rank events under }C\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{4}
\]
Thus every \(\pi\) preserves shared-assignment dependence and every \(\omega_C\) preserves the one common target. With \(\Pi_\star=\bigcup_C\Pi_C\) and \(G=|\Pi_\star|\), the exact key
\[
(M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10}),\qquad \pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10},
\tag{5}
\]
determines the recurrence but contains no coherent weight. Local grouping, global lookup, and one computation per distinct key therefore yield the two displayed time bounds and the displayed memory bound in the theorem by the coherent evaluator lemma.

The synchronized corner-oriented certificate is sharper. Put
\[
\bar k_a=\min\{k_a,M-k_a+1\},\qquad
C_{M,k_0,k_1}=\sum_{i=0}^{M-1}\min\{\bar k_0,i+1\}\min\{\bar k_1,i+1\}.
\tag{6}
\]
For each exact key, complement coordinate \(a\) precisely when \(M-k_a+1<k_a\), thereby merely permuting its four cells. The multinomial formula is applied to that permuted law at thresholds \((\bar k_0,\bar k_1)\), and the four identities in the corner-oriented evaluator reconstruct the requested lower--lower probability using exact binomial marginals. Consequently its key charge is \(M+\mathsf T_{M,\bar k_0,\bar k_1}\), while the corner recurrence charge is \(C_{M,k_0,k_1}\). If \(\mathsf B\) denotes all non-evaluator terms in the theorem's instance-adaptive display, the canonical hybrid charge is
\[
O\!\left(\mathsf B+M+G\min\{M+\mathsf T_{M,\bar k_0,\bar k_1},C_{M,k_0,k_1}\}\right),
\tag{7}
\]
with working memory
\[
O\!\left(m_0m_1+L+U_{\max}+G+\max\{M,\bar k_0\bar k_1\}\right).
\tag{8}
\]
Factorials are shared once, probability power tables are rebuilt per multinomial key, and exact keys are processed sequentially. Since \(C_{M,k_0,k_1}\le Mk_0k_1\), (7)--(8) imply the theorem's coarser displayed resource bounds. Nothing in this computation changes (2)--(4).

Suppose exactly one rank \(k_b=M+1\) and put \(c=1-b\). The boundary-arm event is certain. By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), conditional on \(O_{T,c}=O_t\), the remaining count is binomial with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O},
\tag{9}
\]
and averaging over the target gives exactly
\[
\sum_{O_t}p_{c,O_t}\Pr\{\operatorname{Bin}(M,\theta(O_t))<k_c\}.
\tag{10}
\]
For ordered classes \(C_1\prec\cdots\prec C_d\), grouping target and calibration masses gives \(q_j=q_c(C_j)\), \(p_j=p_c(C_j)\), and \(\theta_j=\sum_{\ell<j}q_\ell\), so (10) equals \(\sum_jp_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}\). A single ordered-class scan forms these masses. For \(0<\theta<1\), the ratios of consecutive binomial terms give
\[
t_0=(1-\theta)^M,\qquad t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},
\tag{11}
\]
and
\[
u_M=\theta^M,\qquad u_{r-1}=u_r\frac{r}{M-r+1}\frac{1-\theta}{\theta}.
\tag{12}
\]
The exact shorter-tail lemma proves the claimed operation and memory bounds. At \(\theta=0\) and \(\theta=1\), the probabilities are one and zero, respectively. Enumeration is only over the \(F_{m_c}\) nonboundary preorders, yielding the stated one-boundary complexity and excluding every boundary-arm or joint-table factor. If both ranks are \(M+1\), both events are certain and \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=[(1-\alpha)-1]_+=0\).

It remains to establish the two extremal assertions. For nonbinary attainment, use four pair blocks with \(\mathcal G=S_2^4\), fair independent within-pair assignment, and an equivariant kernel that first chooses a block with calibration probabilities
\[
q=(13/20,1/20,1/4,1/20)
\tag{13}
\]
and then selects that block's member observed in the requested arm. Choose the common target block probabilities
\[
p=(1/20,1/10,1/4,3/5),\qquad q_{\mathrm{tar}}(v_{b,r})=p_b/2.
\tag{14}
\]
This obeys observability, equivariance, invariant randomization, and the prespecified common-target condition. With \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), both ranks equal three. Take \(s_0\equiv0\) and order the arm-one block orbits as \(1\prec3\prec2\prec4\). Arm zero always succeeds, and direct substitution gives arm-one failure probability
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\tag{15}
\]
The resulting objective is \(24957/160000\). For a binary map let \(H_a\) be its high-score block set and \(A_a=(1-q(H_a))^3\). Inclusion--exclusion conditional on the common target block gives joint failure
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{16}
\]
Order the sixteen subsets as \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\). For each fixed \(H_0\), exact substitution of all sixteen choices of \(H_1\) in (16) gives the following row maxima, in that order, with common denominator \(320000000\):
\[
(164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\]
This finite table exhausts all \(16^2\) binary pairs. Its maximum is \(208582976/320000000=3259109/5000000\), hence the maximum binary objective is \(759109/5000000\). Therefore the four-level gain is
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.
\tag{17}
\]
Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Give target-supported orbits score \(K\), every other orbit in that arm score zero, and the other arm score zero. The arm-\(a\) rank event fails surely, so the joint event has probability zero. The frontier objective is therefore \(1-\alpha\), its largest possible value. If one arm is at the boundary, (9)--(12) give exactly the other-arm reduction. Setting \(\varepsilon_0=\varepsilon_1=\alpha/2\) yields \(k_0=k_1=k\) by the armwise staircase lemma and gives the symmetric theorem.