For \(w\in\Delta(\mathcal H)\), define
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|(Aw-b_{\mathrm{LP}})_{a,O}|.
\tag{1}
\]
The row identities established in \(\texttt{thm:common-selector-lp}\) give
\[
(Aw)_{a,O}=q^{\mathrm{obs}}_{w,a}(O),\qquad (b_{\mathrm{LP}})_{a,O}=q_{\mathrm{tar},a}(O).
\tag{2}
\]
Consequently, by the definitions of \(\delta_{a,O}(w)\) and \(\Delta_a(w)\),
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|\delta_{a,O}(w)|=\Delta_0(w)+\Delta_1(w).
\tag{3}
\]
Because \(\mathcal H\) is finite and nonempty, \(\Delta(\mathcal H)\) is a nonempty compact simplex. The function \(d\) is continuous, so it attains its minimum. Hence \(D_*\) is finite, \(\mathcal W_*\) is nonempty, and indeed \(\mathcal W_*\) is compact.

We next verify the displayed absolute-value primal program. For fixed \(w\), its two-sided constraints imply
\[
t_{a,O}\ge |(Aw-b_{\mathrm{LP}})_{a,O}|
\tag{4}
\]
for every row \((a,O)\). Thus every feasible pair \((w,t)\) has objective at least \(d(w)\). Conversely, for any \(w\in\Delta(\mathcal H)\), choosing
\[
t_{a,O}=|(Aw-b_{\mathrm{LP}})_{a,O}|
\tag{5}
\]
makes \((w,t)\) feasible and gives objective exactly \(d(w)\). Minimizing first over \(t\) and then over \(w\) proves that the primal program has value \(D_*\), and that its optimizing \(w\)-coordinates are exactly the elements of \(\mathcal W_*\).

We prove the quantitative dual identity and attainment directly. Put
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\subset\mathbb R^{2|\mathcal O|},\qquad b=b_{\mathrm{LP}}.
\]
As \(Aw\) ranges over \(C\) when \(w\) ranges over the simplex,
\[
D_*=\min_{c\in C}\frac12\lVert c-b\rVert_1.
\tag{6}
\]
For every \(y\) satisfying \(\lVert y\rVert_\infty\le1/2\) and every \(c\in C\), the finite-sum H\"older inequality gives
\[
y^\top(c-b)\le\lVert y\rVert_\infty\lVert c-b\rVert_1\le\frac12\lVert c-b\rVert_1.
\tag{7}
\]
Taking the minimum over \(c\), followed by the maximum over \(y\), proves weak duality:
\[
\max_{\lVert y\rVert_\infty\le1/2}\min_{c\in C}y^\top(c-b)\le D_*.
\tag{8}
\]
If \(D_*=0\), the feasible choice \(y=0\) makes the left-hand side of \((8)\) at least zero, so equality holds. Suppose now that \(D_*>0\). For every integer \(n\ge2\), put \(r_n=(1-1/n)D_*\) and define the compact convex set
\[
B_n=\{x:\tfrac12\lVert x-b\rVert_1\le r_n\}.
\]
Equation \((6)\) implies \(B_n\cap C=\varnothing\). Choose \((c_n,x_n)\in C\times B_n\) minimizing their Euclidean distance and put \(v_n=c_n-x_n\ne0\). For every \(c\in C\), minimality along the segment from \(c_n\) to \(c\) yields
\[
0\le\left.\frac{d}{dt}\lVert c_n+t(c-c_n)-x_n\rVert_2^2\right|_{t=0+}=2v_n^\top(c-c_n).
\tag{9}
\]
Likewise, for every \(x\in B_n\), minimality along the segment from \(x_n\) to \(x\) yields
\[
0\le\left.\frac{d}{dt}\lVert c_n-x_n-t(x-x_n)\rVert_2^2\right|_{t=0+}=-2v_n^\top(x-x_n).
\tag{10}
\]
It follows that
\[
\min_{c\in C}v_n^\top c\ge v_n^\top c_n\ge v_n^\top x_n\ge\max_{x\in B_n}v_n^\top x.
\tag{11}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\), so \(\lVert y_n\rVert_\infty=1/2\). The support function of this \(\ell_1\)-ball is explicit. Indeed, the upper bound follows from the finite-sum H\"older inequality, and equality is obtained by moving \(2r_n\) from \(b\) in a signed coordinate direction on which \(|(y_n)_j|=1/2\). Therefore
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b+2r_n\lVert y_n\rVert_\infty=y_n^\top b+r_n.
\tag{12}
\]
Combining \((11)\) and \((12)\) gives
\[
\min_{c\in C}y_n^\top c-y_n^\top b\ge r_n.
\tag{13}
\]
The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact, so a subsequence of \((y_n)\) converges to some \(y_*\) in that cube. Since \(C\) is the convex hull of finitely many columns,
\[
\min_{c\in C}y^\top c=\min_{h\in\mathcal H}y^\top A_{\cdot h}
\tag{14}
\]
is a continuous function of \(y\). Letting \(n\to\infty\) along the subsequence in \((13)\), and using \((14)\), gives
\[
\min_{h\in\mathcal H}y_*^\top A_{\cdot h}-y_*^\top b_{\mathrm{LP}}\ge D_*.
\tag{15}
\]
Weak duality \((8)\) forces equality. The dual objective in \((14)\), minus \(y^\top b_{\mathrm{LP}}\), is continuous on the compact cube, so its maximum is attained. We have therefore proved
\[
D_*=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.
\tag{16}
\]
If \(D_*>0\) and \(y\) is any maximizing dual vector, then \((16)\) implies
\[
y^\top A_{\cdot h}\ge y^\top b_{\mathrm{LP}}+D_*\qquad\forall h\in\mathcal H.
\tag{17}
\]
Thus \(z=-y\) satisfies
\[
z^\top b_{\mathrm{LP}}\ge\max_{h\in\mathcal H}z^\top A_{\cdot h}+D_*,
\tag{18}
\]
so the negative of every dual maximizer is a Farkas separating direction with margin \(D_*\).

By nonnegativity in \((1)\), \(D_*=0\) if and only if some \(w\in\Delta(\mathcal H)\) satisfies \(Aw=b_{\mathrm{LP}}\). This is exactly feasibility of \(\texttt{def:common-selector-feasibility-lp}\), and it is equivalent to exact joint balance by \(\texttt{thm:common-selector-lp}\). Moreover, every entry of \(A\) is obtained by integrating an allowed selector kernel against the known assignment law \(\nu\), while \(b_{\mathrm{LP}}\) is obtained from the prespecified target law. Hence the finite primal program uses only the known randomization law, target rule, and selector library. Solving it before scores are observed produces any desired \(w_*\in\mathcal W_*\) as a prespecified selector; neither scored outcomes nor trained residuals enter the program.

Fix such a \(w_*\), a prespecified budget \(\boldsymbol\varepsilon=(\varepsilon_0,\varepsilon_1)\), a law \(P\in\mathcal P_{\mathcal G,K}\), and the trained predictor maps, and condition on \(\mathcal T\). Proposition \(\texttt{prop:asymmetric-finite-rank-orbit-gap-bound}\) gives
\[
\Pr_P\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right)\ge\max\!\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-\Delta_0(w_*)-\Delta_1(w_*)\right\}.
\tag{19}
\]
By \((3)\) and \(w_*\in\mathcal W_*\),
\[
\Delta_0(w_*)+\Delta_1(w_*)=D_*.
\tag{20}
\]
Substitution of \((20)\) into \((19)\) proves the asserted optimized coverage certificate. For every fixed common \(w\in\Delta(\mathcal H)\), optimality gives
\[
D_*\le\Delta_0(w)+\Delta_1(w).
\tag{21}
\]
For fixed \(c=1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\), the map \(x\mapsto\max\{0,c-x\}\) is nonincreasing. Equation \((21)\) therefore proves weak dominance of the optimized numerical certificate. If the inequality in \((21)\) is strict and \(c-D_*>0\), then the optimized certificate is positive and is strictly larger than \(\max\{0,c-\Delta_0(w)-\Delta_1(w)\}\), whether or not the latter expression is truncated at zero. This proves the stated strict-dominance clause.

Finally, on the equal-split diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{def:finite-rank-error}\) gives \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\), while \(\texttt{def:rank-inversion}\) gives \(\mathcal C^{\boldsymbol\varepsilon}_{w_*}=\mathcal C_{w_*}\). Substitution in \((19)\)--\((20)\) yields
\[
\Pr_P(\tau_T\in\mathcal C_{w_*}\mid\mathcal T)\ge\max\{0,1-2\rho_{M,\alpha}-D_*\},
\]
which is the claimed equal-split conclusion.