Let \(N_{xy}\) count draws equal to \((x,y)\), and put
\[
R=N_{10}+N_{11},\qquad S=N_{01}+N_{11}.
\]
If \(R=r\), \(S=s\), and \(N_{11}=t\), then necessarily
\[
(N_{00},N_{01},N_{10},N_{11})
=(M-r-s+t,s-t,r-t,t).
\tag{1}
\]
Conversely, (1) is a nonnegative integer vector of total \(M\) exactly when
\[
\max\{0,r+s-M\}\le t\le\min\{r,s\}.
\tag{2}
\]
The multinomial probability of (1) is the displayed summand. Summing over (2), then over \(r<k_0\) and \(s<k_1\), proves the formula. The conventions \(0^0=1\) and \(0^j=0\) for \(j>0\) make it valid on every simplex face.

For each \((r,s)\), the number of feasible \(t\)'s is at most
\(\min\{r,s\}+1\le\min\{k_0,k_1\}\). Hence
\[
\mathsf T_{M,k_0,k_1}\le k_0k_1\min\{k_0,k_1\}.
\tag{3}
\]
Factorials through \(M!\) require \(O(M)\) shared arithmetic and memory. For each key, its four probability-specific power tables require \(O(M)\) time and memory, and each feasible summand thereafter has constant cost. This proves the multinomial charge. The retained convolution in
\(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) proves the rolling alternative and its stated memory.

We now justify the refined partition. A support-one key has deterministic counts by \(\texttt{def:simplex-vertex-key-prepass}\). A support-two key has the exact affine-binomial interval formula there, with charge \(\mathsf E_M(\pi)\) and constant workspace. For a remaining support-three key, the face set is selected precisely when some orientation satisfies
\(\pi^\sigma_{11}=0\) and \(t_0^\sigma+t_1^\sigma>M\). The last part of
\(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) then gives its exact value with charge \(\mathsf F_M(\pi)\) and constant workspace. Therefore no vertex, edge, or face key is assigned to either generic branch. Every key assigned to \(\Pi_{\mathrm{MS}}\) or \(\Pi_{\mathrm{DP}}\) has support at least three and is not face-admissible.

Sequentially adding the exact per-key charges gives the displayed aggregate operation bound. The shared factorial table is built exactly when
\(\Pi_{\mathrm{MS}}\ne\varnothing\); neither an edge nor a face computation uses it. Probability-specific power tables are rebuilt for each multinomial key, as claimed. Retaining one scalar answer per key and taking the maximum live workspace gives the displayed memory bound because vertices, edges, and face keys each use \(O(1)\) auxiliary storage. The same argument permits the remaining nonface keys to be compared with the positive-corner coefficient evaluator without changing any probability.