For \(i\in\{0,\ldots,M\}\), define the two partial counts
\[
R_i=\sum_{j=1}^i b_0(E_{j,0}),\qquad S_i=\sum_{j=1}^i b_1(E_{j,1}).
\]
We prove by induction that every retained entry satisfies
\[
d_i(r,s)=\Pr\{R_i=r,S_i=s\},\qquad 0\le r<k_0,\quad 0\le s<k_1.
\tag{1}
\]
For \(i=0\), both counts are zero, so (1) is exactly the initialization. Suppose it holds at \(i\). Independence of the next pair from the first \(i\) pairs and the definition of \(\pi_{xy}\) give, for any retained \((r,s)\),
\[
\Pr\{R_{i+1}=r,S_{i+1}=s\}
=\sum_{x=0}^1\sum_{y=0}^1\pi_{xy}\Pr\{R_i=r-x,S_i=s-y\}.
\tag{2}
\]
If an index in (2) is negative, its probability is zero. Nor can a previously discarded state contribute: both counts have nonnegative increments, so a state with first coordinate at least \(k_0\) or second coordinate at least \(k_1\) can never return to the retained rectangle. Substitution of the induction hypothesis into (2) proves (1) at \(i+1\). Summing (1) at \(i=M\) over the retained rectangle proves the displayed probability identity.

Computing the four values \(\pi_{xy}\) takes one scan through the \(|\mathscr E_0||\mathscr E_1|\) cells of \(R\). At each of \(M\) stages, every one of the at most \(k_0k_1\) retained states receives four constant-time contributions. Keeping only the current and next arrays proves the stated arithmetic and memory bounds. If, say, the first rank equals \(M+1\), its rank event is certain. Replace the four-cell law by the marginal \(\pi_{\cdot y}=\pi_{0y}+\pi_{1y}\) and repeat the same induction for \(S_i\), retaining only \(0\le s<k_1\). This gives the one-dimensional bounds. The other case is symmetric. If both ranks equal \(M+1\), both events are certain and their conjunction has probability one.