Write
\(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and aggregate the implemented selector by
\[
\kappa_{w,a}(O\mid z)=
\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z).
\tag{1}
\]
Conditional on \(Z_i=z\), \(\texttt{ass:selector-auxiliary-randomization}\) makes the two selector draws independent with the two kernels in (1). Integrating over \(\nu\) gives the stated \(R_w\), while independence across replicated arrays makes the calibration orbit pairs iid. The independent common target has joint orbit law
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}.
\tag{2}
\]
Its support is an image of \(\mathcal V\), so
\(L\le\min\{|\mathcal V|,m_0m_1\}\).

Fix a preorder pair \(C=(c_0,c_1)\) with \(d_a\) ordered nonempty classes, and push (2) through the class maps. Pushforward cannot enlarge support and its range has size \(d_0d_1\), whence
\[
L_C\le\min\{L,d_0d_1\}.
\tag{3}
\]
Condition on a supported target class pair \((j,\ell)\), and for calibration replicate \(i\) put
\[
B_{i0}=\mathbf 1\{c_0(O_{i,0})<j\},\qquad
B_{i1}=\mathbf 1\{c_1(O_{i,1})<\ell\}.
\tag{4}
\]
The strict prefix is forced by
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{5}
\]
A two-dimensional prefix table of the unchanged law \(R_w\) gives the four-cell law \(\pi^C(j,\ell)\) in constant time. The pairs in (4) are iid, but their coordinates need not be independent. Grouping target class pairs with the same four-cell vector yields
\[
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi),
\qquad U_C\le L_C.
\tag{6}
\]
The value \(D\) depends only on \(M,k_0,k_1\) and three independent cells of \(\pi\); the local weights remain outside the key. This proves the global memo specification and preserves \(R_w\), \(P_T^C\), the common selector, the common target, and within-replicate cross-arm dependence.

By \(\texttt{lem:four-cell-rank-event-dynamic-program}\), vertices and edges have the exact prepass formulas and charges in the statement. By
\(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), an eligible support-three face key has exact charge \(\mathsf F_M(\pi)\) and constant workspace. The rank-one calculation in \(\texttt{lem:four-cell-rank-event-dynamic-program}\) next evaluates every remaining support-four determinant-zero key with charge \(\mathsf R_{M,k_0,k_1}\) and constant workspace. Every residual key is evaluated exactly by one of the rolling,
zero-cell-safe multinomial, or positive-corner coefficient branches, using
\(\texttt{lem:four-cell-multinomial-sum-alternative}\) and
\(\texttt{lem:positive-corner-coefficient-recurrence}\). Deterministic least-charge selection gives the displayed seven-way disjoint partition and the sum \(\mathsf B\), including the rank-one charge. Only \(\Pi_{\mathrm{MS}}\) uses the shared factorial table. Sequential evaluation uses the maximum live branch workspace: the three nonzero terms in \(\mathsf W\) are exactly the rolling, multinomial, and positive-corner requirements; vertices, edges, faces, and rank-one keys are constant-space strata.

The target pushforward costs \(O(|\mathcal V|)\). Per preorder pair, class aggregation, the prefix table, and target pushforward cost
\(O(m_0m_1+L)\). A balanced tree groups \(L_C\) local keys in
\(O(L_C\log(1+L_C))\) comparisons and \(O(L_C)\) arithmetic; forming (6) costs \(O(U_C)\). The global tree adds
\[
O\!\left(\left(\sum_CU_C\right)\log(1+G)\right).
\]
Adding \(\mathsf B\) proves the adaptive bound. Replacing \(L_C,U_C\) by their maxima proves the uniform bound. The joint orbit table, coherent target table, local grouping table, memoized scalars, and selected evaluator workspace prove the memory bound.

The edge strictness audit is unchanged. For \(M=2n\), \(k_0=n\), \(k_1=M\), and \(\pi=(1/2,1/2,0,0)\), one count is zero and the other is
\(\operatorname{Bin}(M,1/2)\), so
\[
D_{M,n,M}(\pi)=1-2^{-M}.
\]
The exact edge tail costs \(O(\log M)\). In the binary-multiplication exact-arithmetic model, producing the degree-\(M\) monomial \(2^{-M}\) from \(1/2\) needs at least \(\lceil\log_2 M\rceil\) multiplications because one multiplication can at most double degree; hence the charge is \(\Theta(\log M)\). The former least-charge dispatcher costs \(\Theta(M)\).

For the design audit, take two pair blocks with the product group \(S_2^2\) generated by the two pure local swaps, and independently assign exactly one treated member per block with probability \(1/2\) for either member. The known law is invariant under both swaps. Use a singleton selector library. In each arm, its kernel chooses block \(1\) or block \(2\) equiprobably by auxiliary randomization and then selects that block's unique observed arm-\(a\) member. The rule is observable; relabelling a pair sends its unique observed member to the correspondingly relabelled member while leaving the block coin fixed, so it is equivariant. Put the independent common target on a fixed member of block \(2\). In arm \(0\), place the block-\(2\) orbit at the target's lowest level and block \(1\) above it, making the first strict-prefix indicator identically zero. In arm \(1\), place block \(1\) below the target's block-\(2\) orbit, making the second indicator equal the block-\(1\) selector coin. Thus the induced key is \((1/2,1/2,0,0)\). Finally,
\[
\varepsilon_0=\frac{n+1}{2n+1},\qquad
\varepsilon_1=\frac1{2n+1},\qquad
\alpha=\frac{n+2}{2n+1}
\]
are positive, sum to \(\alpha<1\), and satisfy
\[
\left\lceil(2n+1)(1-\varepsilon_0)\right\rceil=n,\qquad
\left\lceil(2n+1)(1-\varepsilon_1)\right\rceil=2n=M.
\]
This proves every legality, invariance, common-target, common-selector, preorder, rank, and resource assertion for the edge witness.

We now give the new strict face audit. Let
\[
\mathcal V_1=\{v_{1,0},v_{1,1}\},\qquad
\mathcal V_2=\{v_{2,0},v_{2,1}\},\qquad
\mathcal G=\{e\}.
\]
The group is finite and all equivariance and design-invariance conditions under it are automatic. In member order
\((v_{1,0},v_{1,1},v_{2,0},v_{2,1})\), let \(\nu\) be uniform on
\[
z^A=(1,0,1,0),\qquad
z^B=(1,0,0,1),\qquad
z^C=(0,1,1,0).
\tag{7}
\]
Every vector assigns exactly one treated and one control member in each pair. Let the selector library be the singleton \(\{h\}\), with \(w_h=1\). On \(z^A\), both arm kernels select the unique member of their arm in block \(2\). On \(z^B\), the arm-\(0\) kernel selects block \(2\) and the arm-\(1\) kernel selects block \(1\). On \(z^C\), the arm-\(0\) kernel selects block \(1\) and the arm-\(1\) kernel selects block \(2\). These deterministic lookups select only observed arm-\(a\) members on the assignment support, hence are legal observable kernels. Under the trivial group they are equivariant. The auxiliary product condition holds because each kernel is a point mass.

Set \(q_{\mathrm{tar}}=\delta_{v_{2,0}}\), independently of the calibration records. Under the trivial group every arm-labelled state is a singleton orbit. In each arm, put both block-\(1\) singleton orbits strictly below the target orbit and put both block-\(2\) singleton orbits in the target tie class. The strict-prefix pairs induced by (7) are respectively
\[
(0,0),\qquad(0,1),\qquad(1,0).
\]
Consequently the unique target prefix key is
\[
\pi=(1/3,1/3,1/3,0).
\tag{8}
\]
For \(k_0=k_1=M\), the \(LL\) orientation has zero \(11\) cell and
\(t_0+t_1=2M>M\). Moreover, \(R=M\) occurs only when every draw is \(10\), and \(S=M\) only when every draw is \(01\). These events are disjoint, each has probability \(3^{-M}\), and hence
\[
D_{M,M,M}(\pi)=1-2\cdot3^{-M}.
\tag{9}
\]
Exponentiation by squaring evaluates \(3^{-M}\) in \(O(\log M)\) exact multiplications. Conversely, starting from \(1/3\), one multiplication can at most double the largest available exponent, so producing the degree-\(M\) monomial requires at least \(\lceil\log_2 M\rceil\) multiplications. Thus the face branch costs
\(\Theta(\log M)\) exact arithmetic and constant workspace. Since
\(\bar k_0=\bar k_1=1\), the rolling charge is \(M\), and the multinomial charge is \(M+\mathsf T_{M,1,1}=M+1\). Among positive-base orientations, \(LL\) has an \(M\)-by-\(M\) coefficient rectangle, \(LU\) and \(UL\) have an \(M\)-by-\(1\) rectangle, and \(UU\) has zero base atom and is forbidden. Thus every allowed coefficient orientation costs \(\Theta(M)\). Finally,
\[
\varepsilon_0=\varepsilon_1=\frac1{M+1},\qquad
\alpha=\frac2{M+1}
\]
are admissible for \(M\ge2\), and
\[
k_a=\left\lceil(M+1)\left(1-\frac1{M+1}\right)\right\rceil=M.
\]
This verifies the assignment support, selector legality, common selector, common target, preorder, rank, value, and strict resource improvement.

We finally audit the strict rank-one witness. Let \(M=2n\) with \(n\ge3\), take two blocks \(\mathcal V_1=\{v_{1,0},v_{1,1}\}\) and \(\mathcal V_2=\{v_{2,0},v_{2,1}\}\), and take \(\mathcal G=\{e\}\). Independently within each block, assign exactly one treated member, with either member chosen with probability \(1/2\). The four-point law is known and invariant under the trivial group. Let the selector library be the singleton \(\{h\}\). Its arm-\(0\) kernel is the point mass on block \(1\)'s unique observed control, and its arm-\(1\) kernel is the point mass on block \(2\)'s unique observed treated member. Both kernels satisfy observability; equivariance is automatic, and their point-mass product is the auxiliary selector law.

Put \(q_{\mathrm{tar}}=\delta_{v_{2,0}}\). Under the trivial group every state is a singleton orbit. In arm \(0\), put exactly one of the two block-\(1\) control states strictly below \((v_{2,0},0)\), and tie the other with the target. The resulting strict-prefix indicator is a fair Bernoulli variable determined by block \(1\). In arm \(1\), put the mate-treatment state \((v_{2,1},1)\) strictly below \((v_{2,0},1)\). Its strict-prefix indicator is a fair Bernoulli variable determined by block \(2\). The block assignments are independent, so the exact prefix key is
\[
\pi=(1/4,1/4,1/4,1/4).
\tag{10}
\]
The determinant vanishes and (R3) gives
\[
D_{2n,n,n+2}(\pi)=H_{2n,n}(1/2)H_{2n,n+2}(1/2).
\tag{11}
\]
For \(N=2n+1\), the proposed levels satisfy
\[
\left\lceil N(1-\varepsilon_0)\right\rceil=n,
\qquad
\left\lceil N(1-\varepsilon_1)\right\rceil=n+2,
\qquad
\varepsilon_0+\varepsilon_1=\alpha=\frac{2n}{2n+1}<1.
\tag{12}
\]
Thus the ranks and budget are legal.

Here \(\bar k_0=n\) and \(\bar k_1=n-1\). The two exact shorter-tail recurrences process \(n\) and \(n-1\) nonzero terms, so the rank-one branch takes \(\Theta(M)\) time and constant workspace. The rolling charge is \(\Theta(n^3)\) with \(\Theta(n^2)\) workspace. The multinomial branch has \(\Theta(n^2)\) retained pairs and \(\Theta(n)\) feasible inner counts on a fixed positive fraction of them, so it takes \(\Theta(n^3)\) time and \(\Theta(n)\) workspace. All four cells in (10) remain positive under every orientation, while both transformed thresholds are \(\Theta(n)\); every positive-corner coefficient rectangle therefore costs \(\Theta(n^2)\) time and \(\Theta(n)\) workspace. The least former branch is consequently \(\Theta(M^2)\) in time with \(\Theta(M)\) workspace, proving strictness.