Put
\[
J(s_0,s_1)=\Pr\!\left\{s_1(O_{T,1})\le Q_{k_1}(s_1(O_{1,1}),\ldots,s_1(O_{M,1}))\ \text{ and }\ s_0(O_{T,0})\le Q_{k_0}(s_0(O_{1,0}),\ldots,s_0(O_{M,0}))\right\}.
\]
By \(\texttt{def:coverage-frontier}\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\max_{s_0,s_1}[(1-\alpha)-J(s_0,s_1)]_+.
\tag{1}
\]
This is exactly the worst deficit over the declared deterministic maps \(s_a:\mathcal O\to[0,K]\). It is not a full-model statement: with fixed covariates, zero predictors, a nondegenerate Bernoulli variable \(\xi_i\), and \(Y_{iv}(a)=K\xi_i\) for every member and arm, the bounded latent law is invariant but the residual score remains nondegenerate conditional on every orbit. Thus the optimization domain in (1) is genuinely narrower than \(\mathcal P_{\mathcal G,K}\).

Let \(E_{\mathrm{joint}}\) denote simultaneous armwise inclusion and \(E_{\mathrm{eff}}\) effect-set inclusion. On \(E_{\mathrm{joint}}\),
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w,
\tag{2}
\]
so \(E_{\mathrm{joint}}\subseteq E_{\mathrm{eff}}\) and the probability inequality follows. If both intervals are \(\{0\}\) and both outcomes are \(K\), the left event fails while \(\tau_T=0\) belongs to the effect set, proving strictness can occur.

Assume first \(k_0,k_1\le M\). For either arm,
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\iff\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{3}
\]
Thus only the total preorder of each score map matters. Conversely, every total preorder with ordered nonempty classes \(C_{a,1}\prec\cdots\prec C_{a,d_a}\) has a representative in \([0,K]\): use zero if \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). Hence the maximum is attained among the \(F_{m_0}F_{m_1}\) preorder pairs.

For every pair \(C\), \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) proves
\[
J(C)=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi),
\tag{4}
\]
while preserving \(R_w\), the coherent target pushforward \(P_T^C\), and the within-replicate cross-arm coupling. That lemma, together with \(\texttt{lem:four-cell-rank-event-dynamic-program}\), \(\texttt{lem:four-cell-multinomial-sum-alternative}\), and \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), establishes the seven disjoint strata and every displayed exact evaluator. Summing their exact per-key charges is precisely \(\mathsf B\); taking the largest live branch workspace gives \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\). The coherent evaluator proves both displayed time bounds, the factorial-trigger condition, constant workspace for the first four strata, and the edge, face, and rank-one audit identities and resource separations. All audited selector lookups are normalized and realized-arm supported on assignments of positive design mass; off-support extensions have zero integrated weight.

If exactly one rank \(k_b=M+1\), that arm's event is certain. For \(c=1-b\), conditioning (3) on \(O_{T,c}=O_t\) gives a binomial count with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over \(p_{c,O_t}\) proves the displayed one-boundary formula. The class scan and exact shorter-tail evaluation in \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) give its time and memory bounds. If both ranks equal \(M+1\), both events are certain and (1) equals zero.

For the binary-attainment claim, take four two-member blocks with \(\mathcal G=S_2^4\), audit each pure local swap by \(\texttt{def:pair-action}\), and assign independently and fairly one treated and one control member per block. In each arm, choose a block with probabilities \(q=(13/20,1/20,1/4,1/20)\) and select its unique member observed in the requested arm. This kernel is normalized and realized-arm supported on every supported assignment. Give the common target block probabilities \(p=(1/20,1/10,1/4,3/5)\). Use an arm-zero constant score and order arm-one blocks as \(1\prec3\prec2\prec4\). At \(M=3\) and \(k_0=k_1=3\), the joint-event failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000},
\]
so the objective at \(1-\alpha=1/2\) is \(24957/160000\). For binary high-score sets \(H_0,H_1\), conditional independence of the two auxiliary draws gives failure probability
\[
p(H_0)\{1-q(H_0)\}^3+p(H_1)\{1-q(H_1)\}^3-p(H_0\cap H_1)\{1-q(H_0)\}^3\{1-q(H_1)\}^3.
\tag{5}
\]
The \(16^2=256\) pairs form an explicit finite enumeration. The maximum is attained by \((H_0,H_1)=(\{2,4\},\{3,4\})\) and its transpose. For the displayed ordering of the arms, \(q(H_0)=1/10\), \(p(H_0)=7/10\), \(q(H_1)=3/10\), \(p(H_1)=17/20\), and \(p(H_0\cap H_1)=3/5\). Substitution in (5) gives failure probability \(3259109/5000000\), hence objective \(759109/5000000\); direct substitution for each of the remaining \(254\) pairs gives no larger numerator. Therefore
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.
\]
Thus binary maps do not attain the frontier. If target and calibration orbit supports are disjoint in a finite-rank arm, give every target-supported orbit score \(K\), every calibration-supported orbit score zero, and use zero in the other arm. Then \(J=0\), so (1) equals \(1-\alpha\), its largest possible value.

The comparator leaves delimit different objects. \(\texttt{lem:lebrun-rectangular-probability-comparator}\) concerns arbitrary rectangles for several discrete count laws; \(\texttt{lem:timans-max-rank-comparator}\) concerns dependence-aware simultaneous family-wise error control; \(\texttt{lem:schlembach-multi-target-allocation-comparator}\) concerns multi-target level allocation for hyperrectangle volume; and \(\texttt{lem:structured-volume-dynamic-program-comparator}\) concerns near-optimal structured prediction-set volume. In contrast, (1)--(4) exactly evaluate this paper's restricted deterministic joint-armwise rank-inclusion certificate audit with one coherent target. This is a distinction of optimized objects, not a priority claim or a general coverage claim.

Finally, \(\texttt{thm:common-selector-lp}\) gives the full-model guarantee under exact balance, and \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) gives the full-model total-variation guarantee under imbalance; neither follows from (1). Setting \(\varepsilon_0=\varepsilon_1=\alpha/2\) gives the equal-split theorem. Since every computational branch evaluates the same probability in (4), none changes the active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit semantics.