Let \(N_{xy}\) be the number of draws in cell \((x,y)\), and put \(R=\sum_iX_i\), \(S=\sum_iY_i\). For fixed margins \(R=r\), \(S=s\), write \(t=N_{11}\). The margin equations force
\[
(N_{00},N_{01},N_{10},N_{11})
=(M-r-s+t,s-t,r-t,t). \tag{1}
\]
Conversely, (1) is a nonnegative integer count vector with the required margins exactly when
\[
\max\{0,r+s-M\}\le t\le\min\{r,s\}. \tag{2}
\]
Thus (1)--(2) give a bijection between feasible count vectors and the inner summation indices. The multinomial mass of (1) is
\[
\frac{M!}{(M-r-s+t)!(s-t)!(r-t)!t!}
\pi_{00}^{M-r-s+t}\pi_{01}^{s-t}\pi_{10}^{r-t}\pi_{11}^{t}. \tag{3}
\]
Summing (3) over (2), then over \(0\le r<k_0\) and \(0\le s<k_1\), proves the displayed formula. The zero-power conventions make (3) valid on every face of the probability simplex.

For each \((r,s)\), the number of feasible values of \(t\) is the displayed positive part and is at most
\[
\min\{r,s\}+1\le\min\{k_0,k_1\}.
\]
There are \(k_0k_1\) margin pairs, proving
\[
\mathsf T_{M,k_0,k_1}
\le k_0k_1\min\{k_0,k_1\}. \tag{4}
\]
The factorial table is formed once in \(O(M)\) operations. For each exact key, four power tables are rebuilt by repeated multiplication in \(O(M)\) operations and \(O(M)\) memory. Factorial and power lookups make each term in (3) constant-cost, proving the multinomial branch charge
\[
O(M+\mathsf T_{M,k_0,k_1}). \tag{5}
\]

For the recurrence alternative, define
\[
h_a=M-k_a+1,\qquad
\bar k_a=\min\{k_a,h_a\},\qquad
C_{M,k_0,k_1}=\sum_{i=0}^{M-1}
\min\{\bar k_0,i+1\}\min\{\bar k_1,i+1\}. \tag{6}
\]
By \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), an appropriate coordinatewise complementation permutes the four cells and computes the smallest corner in \(O(C_{M,k_0,k_1})\) operations and \(O(\bar k_0\bar k_1)\) workspace. The lemma's marginal inclusion--exclusion formulas recover the desired lower--lower probability exactly, including zero-cell cases. Therefore the sharper time-selecting hybrid charge for one key is
\[
O\!\left(
\min\{M+\mathsf T_{M,k_0,k_1},C_{M,k_0,k_1}\}
\right), \tag{7}
\]
with conditional workspace \(O(M)\) on the multinomial branch and \(O(\bar k_0\bar k_1)\) on the recurrence branch. Since
\[
C_{M,k_0,k_1}
\le M\bar k_0\bar k_1
\le Mk_0k_1, \tag{8}
\]
(7) implies the recurrence and hybrid time bounds printed in the statement. It also sharpens the unconditional per-key workspace from \(O(\max\{M,k_0k_1\})\) to
\[
O(\max\{M,\bar k_0\bar k_1\}). \tag{9}
\]

For a finite key set processed sequentially, let \(\Pi_{\mathrm{MS}}\) and \(\Pi_{\mathrm{DP}}\) denote the branches actually selected. Sharing factorial preprocessing, rebuilding powers for every multinomial key, and reusing the rolling recurrence arrays gives
\[
O\!\left(
M+\sum_{\pi\in\Pi_{\mathrm{MS}}}
(M+\mathsf T_{M,k_0,k_1})
+|\Pi_{\mathrm{DP}}|C_{M,k_0,k_1}
\right). \tag{10}
\]
When one scalar answer per key is retained, the memory is
\[
O\!\left(
|\Pi|+\max\{M,\bar k_0\bar k_1\}
\right). \tag{11}
\]
Replacing \(C_{M,k_0,k_1}\) and \(\bar k_0\bar k_1\) by the upper bounds in (8) yields exactly the aggregate time and memory claims in the frozen statement, while (6)--(11) establish the directive's sharper branch accounting.
