Write \(\operatorname{supp}(\nu)=\{z:\nu(z)>0\}\). By \(\texttt{ass:known-matched-randomization}\), \(\nu(gz)=\nu(z)\), so this support is \(\mathcal G\)-invariant. For a supported assignment define the orbit-aggregated kernel
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z).
\tag{1}
\]
By \(\texttt{ass:observable-selector-kernel}\), (1) is a probability mass function on \(\mathcal O_a\). Conditional on \(Z_i=z\), \(\texttt{ass:selector-auxiliary-randomization}\) makes the two arm selectors independent with these kernels. Hence their joint orbit law is
\[
R_w(O_0,O_1)=\sum_{z\in\operatorname{supp}(\nu)}\nu(z)
\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).
\tag{2}
\]
This equals the unrestricted displayed sum because every omitted assignment has \(\nu(z)=0\). Any total probability-kernel extension off the support is therefore immaterial. Independence across replicates makes the calibration orbit pairs iid with law (2). By \(\texttt{ass:prespecified-target}\), the independent common target has coherent joint law
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}.
\tag{3}
\]
Its support is an image of \(\mathcal V\), so \(L\le\min\{|\mathcal V|,m_0m_1\}\).

Fix a preorder pair \(C=(c_0,c_1)\) with \(d_a\) nonempty ordered classes and push (3) through the two class maps. Pushforward cannot enlarge support and the range has size \(d_0d_1\), whence
\[
L_C\le\min\{L,d_0d_1\}.
\tag{4}
\]
Condition on a target class pair \((j,\ell)\) in this support and define
\[
B_{i0}=\mathbf 1\{c_0(O_{i,0})<j\},\qquad
B_{i1}=\mathbf 1\{c_1(O_{i,1})<\ell\}.
\tag{5}
\]
For each arm, the order-statistic identity
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\quad\Longleftrightarrow\quad
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a
\tag{6}
\]
uses a strict prefix and is valid with ties. A two-dimensional prefix table of (2) supplies the four-cell law \(\pi^C(j,\ell)\) of (5) in constant time. Across \(i\), these pairs are iid, although their two coordinates need not be independent. Grouping target class pairs that yield the same four-cell vector gives
\[
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi),\qquad U_C\le L_C.
\tag{7}
\]
The value \(D_{M,k_0,k_1}(\pi)\) depends only on the two ranks and three independent cells, since \(\pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10}\). Local weights therefore remain outside the global memo key. Equations (2), (3), and (7) preserve the common selector, common target, and within-replicate cross-arm dependence.

The frozen exact evaluators now apply key by key. By \(\texttt{lem:four-cell-rank-event-dynamic-program}\), support-one and support-two keys have the stated deterministic and affine-binomial formulas. By \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), every eligible support-three face key has charge \(\mathsf F_M(\pi)\) and constant workspace, and every remaining support-four determinant-zero key factors into two strict binomial distribution functions with charge \(\mathsf R_{M,k_0,k_1}\) and constant workspace. By \(\texttt{lem:four-cell-multinomial-sum-alternative}\) and \(\texttt{lem:positive-corner-coefficient-recurrence}\), every residual key is evaluated exactly by the rolling, zero-cell-safe multinomial, or positive-corner branch. Prespecified least-charge selection and tie-breaking give the displayed seven disjoint strata and exactly the sum \(\mathsf B\). Only \(\Pi_{\mathrm{MS}}\) builds the factorial table. Sequential processing uses the largest live branch workspace, namely \(\mathsf W\); the first four strata use only constant auxiliary space.

Constructing (3) costs \(O(|\mathcal V|)\). For each preorder pair, class aggregation, the prefix table of (2), and target pushforward cost \(O(m_0m_1+L)\). A balanced tree groups its \(L_C\) local keys in \(O(L_C\log(1+L_C))\) comparisons and \(O(L_C)\) arithmetic, and (7) costs \(O(U_C)\). The global memo tree adds
\[
O\!\left(\Bigl(\sum_CU_C\Bigr)\log(1+G)\right).
\]
Adding \(\mathsf B\) proves the adaptive bound; replacing \(L_C,U_C\) by \(L_{\max},U_{\max}\) proves the uniform bound. The joint table, target table, largest local grouping table, \(G\) memoized answers, and selected branch workspace give \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\) memory.

For the edge audit, use two pair blocks, \(S_2^2\), and the four supported assignments generated by independent fair one-treated--one-control assignments. On every supported assignment and in each arm, choose either block with probability \(1/2\), then select its unique observed arm \(a\) member. This kernel is normalized, has realized-arm support, and is equivariant on the invariant support. Extend it to a total Markov kernel off support by any fixed probability law; the extension has zero weight in (2). Put the target in block \(2\), place block \(2\) lowest in arm \(0\), and place block \(1\) below block \(2\) in arm \(1\). Then \(B_{i0}=0\) and \(B_{i1}\) is fair, so \(\pi=(1/2,1/2,0,0)\) and
\[
D_{M,n,M}(\pi)=\Pr\{\operatorname{Bin}(M,1/2)<M\}=1-2^{-M}.
\]
The edge charge is \(\Theta(\log M)\) with constant workspace, while each former nonvertex charge is \(\Theta(M)\). Direct substitution gives ranks \(n\) and \(M\) from the displayed positive levels, whose sum is \(\alpha\).

For the face audit, take the trivial group on two pair blocks and let \(\nu\) be uniform on
\[
z^A=(1,0,1,0),\qquad z^B=(1,0,0,1),\qquad z^C=(0,1,1,0),
\tag{8}
\]
in member order \((v_{1,0},v_{1,1},v_{2,0},v_{2,1})\). Define both selector kernels on every supported assignment: on \(z^A\), select the requested arm in block \(2\); on \(z^B\), select block \(2\) in arm \(0\) and block \(1\) in arm \(1\); on \(z^C\), select block \(1\) in arm \(0\) and block \(2\) in arm \(1\). These are complete point-mass lookups on \(\operatorname{supp}(\nu)\), and equivariance is automatic for the trivial group. Extend them arbitrarily as total probability kernels off support. With target \(v_{2,0}\), put both block \(1\) singleton orbits below the target in each arm and tie the block \(2\) singleton orbits with it. The three strict-prefix pairs are \(00,01,10\), so \(\pi=(1/3,1/3,1/3,0)\). At \(k_0=k_1=M\), failure means that all draws are \(10\) or all are \(01\); these events are disjoint. Hence
\[
D_{M,M,M}(\pi)=1-2\cdot3^{-M}.
\]
The face charge is \(\Theta(\log M)\) with constant workspace. The rolling and multinomial charges are \(\Theta(M)\); direct inspection of the positive-base orientations gives rectangles of dimensions \(M\) by \(M\), \(M\) by \(1\), or \(1\) by \(M\), so their least charge is also \(\Theta(M)\). The displayed levels give \(k_0=k_1=M\) and sum to \(\alpha\).

For the rank-one audit, retain the trivial group and use all four independent fair one-treated--one-control assignments. On each supported assignment, arm \(0\) selects block \(1\)'s unique control and arm \(1\) selects block \(2\)'s unique treated member. This is a complete legal lookup table on the support; extend it arbitrarily as a total kernel elsewhere. With target \(v_{2,0}\), put one block \(1\) control singleton orbit below the arm \(0\) target orbit and the block \(2\) mate-treatment singleton orbit below the arm \(1\) target orbit. The prefix indicators are independent fair Bernoulli variables, so \(\pi=(1/4,1/4,1/4,1/4)\). Its determinant vanishes, and therefore
\[
D_{2n,n,n+2}(\pi)=H_{2n,n}(1/2)H_{2n,n+2}(1/2).
\]
The displayed levels give ranks \(n,n+2\), are positive for \(n\ge3\), and sum to \(2n/(2n+1)\). Here \(\bar k_0=n\) and \(\bar k_1=n-1\), so the rank-one charge is \(\Theta(M)\) with constant workspace. Each former branch has two widths of order \(M\), hence least time \(\Theta(M^2)\) and workspace \(\Theta(M)\). This proves all three admissible strict improvements and the lemma.