Condition throughout on \(\mathcal T\), and fix an arm \(a\in\{0,1\}\). The trained map \(\widehat m_a\) is then fixed. By \(\texttt{lem:orbit-score-factorization}\), there are probability laws \(F_{a,O}\) such that the \(M\) calibration orbit--score pairs are independent and identically distributed with law
\[
\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),
\]
whereas the independent target orbit--score pair has law
\[
\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).
\]
Assumption \(\texttt{ass:orbit-overlap}\) gives \(\mathsf P_a\ll\mathsf Q_a\). On every orbit fibre with positive target mass,
\[
\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\frac{p_{a,O}}{q_{a,O}}=\lambda_{a,O}.
\tag{1}
\]
Thus the likelihood ratio depends only on the orbit: the common conditional score law \(F_{a,O}\) cancels. In particular, no member-level overlap within an orbit is required.

Because \(\epsilon_a>0\) and \(\epsilon_0+\epsilon_1\le\alpha<1\), one has \(0<\epsilon_a<1\). Apply \(\texttt{lem:finite-support-weighted-rank-validity}\), conditionally on \(\mathcal T\), with \(\mathscr E=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\), \(q_O=q_{a,O}\), \(p_O=p_{a,O}\), \(R_i=S_{i,a}\), and \(\varepsilon=\epsilon_a\). The target draw satisfies \(p_{a,O_{T,a}}>0\) almost surely. Orbit overlap therefore gives \(q_{a,O_{T,a}}>0\) and \(\lambda_{a,O_{T,a}}>0\), so the infinity-augmented measure has positive total mass. Its left-continuous \((1-\epsilon_a)\)-quantile is exactly \(r^{\mathrm W}_{a,w}\) from \(\texttt{def:weighted-rank-inversion}\). Consequently,
\[
\Pr_P\!\left(S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\right)\le\epsilon_a.
\tag{2}
\]

Let \(E_a=\{S_{0,a}\le r^{\mathrm W}_{a,w}\}\), and define the unclipped interval
\[
\widetilde I^{\mathrm W}_{a,w}=\left[\widehat m_a(X_{0T})-r^{\mathrm W}_{a,w},\,\widehat m_a(X_{0T})+r^{\mathrm W}_{a,w}\right].
\]
On \(E_a\), the identity \(S_{0,a}=|Y_{0T}(a)-\widehat m_a(X_{0T})|\) implies \(Y_{0T}(a)\in\widetilde I^{\mathrm W}_{a,w}\). Assumption \(\texttt{ass:bounded-potential-outcomes}\) also gives \(Y_{0T}(a)\in[-K,K]\). Since
\[
I^{\mathrm W}_{a,w}=\widetilde I^{\mathrm W}_{a,w}\cap[-K,K],
\]
we have \(Y_{0T}(a)\in I^{\mathrm W}_{a,w}\) on \(E_a\), including when \(r^{\mathrm W}_{a,w}=+\infty\). Applying \((2)\) to both arms and using the union bound, without any cross-arm independence assumption, gives
\[
\Pr_P(E_0\cap E_1\mid\mathcal T)\ge1-\epsilon_0-\epsilon_1\ge1-\alpha.
\tag{3}
\]
On \(E_0\cap E_1\), set subtraction yields
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.
\]
Combining this inclusion with \((3)\) proves
\[
\Pr_P(\tau_T\in\mathcal C^{\mathrm W}_w\mid\mathcal T)\ge1-\epsilon_0-\epsilon_1\ge1-\alpha.
\]
The argument is conditional on any fixed or prespecified \(w\), and it applies to every declared law and every fixed measurable trained predictor map.

It remains to identify the balanced specialization. By joint orbit balance, \(p_{a,O}=q_{a,O}\) for every arm and orbit; equivalently, this is the balance side of \(\texttt{thm:orbit-balance-iff}\). Hence \(\lambda_{a,O}=1\) on every orbit that can be drawn, while orbits having zero mass under both laws are irrelevant. For arm \(a\), the normalized weighted measure therefore has \(M+1\) equal-mass atoms: one at each of the \(M\) calibration scores and one at \(+\infty\). Its left-continuous \((1-\epsilon_a)\)-quantile is the \(k_a\)-th order statistic of these atoms, where
\[
k_a=\left\lceil(M+1)(1-\epsilon_a)\right\rceil.
\]
If \(k_a\le M\), this is the \(k_a\)-th calibration-score order statistic; if \(k_a=M+1\), it is \(+\infty\). These are exactly the two clauses defining \(r_{a,(k_a)}\) in \(\texttt{def:rank-inversion}\). Therefore
\[
r^{\mathrm W}_{a,w}=r_{a,(k_a)},\qquad I^{\mathrm W}_{a,w}=I^{\boldsymbol\varepsilon}_{a,w},\qquad \mathcal C^{\mathrm W}_w=\mathcal C^{\boldsymbol\varepsilon}_w,
\tag{4}
\]
where the ordinary construction in \((4)\) uses the same arm levels \(\varepsilon_a=\epsilon_a\). This is the ordinary arm-specific rank inversion for an arbitrary prespecified allocation; it is not yet the legacy symmetric notation. Only after taking \(\epsilon_0=\epsilon_1=\alpha/2\) do we obtain \(k_0=k_1=k=\lceil(M+1)(1-\alpha/2)\rceil\) and, by \(\texttt{def:rank-inversion}\),
\[
I^{\mathrm W}_{a,w}=I^{\boldsymbol\varepsilon}_{a,w}=I_{a,w},\qquad \mathcal C^{\mathrm W}_w=\mathcal C^{\boldsymbol\varepsilon}_w=\mathcal C_w.
\]
This proves both the general balanced reduction and its equal-split symmetric corollary.