Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,
\qquad
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
The corrected scope, exact deterministic-preorder interpretation, common-target coherence, binary counterexample, and disjoint-support value therefore follow from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). In particular, the example with common nondegenerate bounded outcomes shows that an arbitrary invariant law can have stochastic residual scores conditional on an orbit; consequently the diagonal functional in (1) is not a uniform full-model joint-inclusion or effect-coverage certificate.

The pointwise event containment specializes to
\[
\{Y_{0T}(1)\in I_{1,w},\ Y_{0T}(0)\in I_{0,w}\}
\subseteq
\{\tau_T\in I_{1,w}-I_{0,w}\}
=\{\tau_T\in\mathcal C_w\}.
\tag{2}
\]
Conditional probability is monotone, proving the stated inequality. When both intervals are \(\{0\}\) and both potential outcomes equal \(K\), the right event in (2) holds and the left event fails, so equality need not hold. As in the asymmetric theorem, (2) is algebraic and does not extend the deterministic optimization in (1) to stochastic conditional score laws.

Assume \(k\le M\). Specializing the asymmetric seven-way partition gives the displayed disjoint strata. Since
\[
\bar k_0=\bar k_1=\bar k=\min\{k,M-k+1\},
\]
the rolling charge is \(\mathsf C_{M,k,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2\). Substitution in the asymmetric branch sum gives exactly \(\mathsf B_{\mathrm{sym}}\), including the face and rank-one terms. The same substitution gives \(\mathsf W_{\mathrm{sym}}\); the vertex, edge, face, and rank-one evaluators use constant workspace, and the rank-one evaluator does not trigger factorial preprocessing. Substitution in the adaptive, uniform, and memory bounds of \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) proves all displayed diagonal resource bounds.

For every \(M\ge2\), taking \(\alpha=2/(M+1)\) gives \(k=M\). The audited edge construction in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) realizes \(\pi=(1/2,1/2,0,0)\), and hence
\[
D_{M,M,M}(\pi)=1-2^{-M}.
\]
Its edge charge is \(\Theta(\log M)\), while the former dispatcher charge is \(\Theta(M)\). At the same diagonal rank, the audited face construction realizes \(\pi=(1/3,1/3,1/3,0)\) and gives
\[
D_{M,M,M}(\pi)=1-2\cdot3^{-M},
\]
again with \(\Theta(\log M)\) time and constant workspace versus \(\Theta(M)\) for every former branch. The off-diagonal rank-one audit remains a strict certificate of the common evaluator's computational improvement; on the diagonal, the same determinant test has charge
\[
\mathsf R_{M,k,k}=1+2\lceil\log_2M\rceil+2\bar k.
\]
If \(k=M+1\), \(\texttt{prop:rank-boundary}\) makes both deterministic rank events certain, and thus \(\Gamma_{M,\alpha}(w)=0\).

Within the deterministic submodel, the exact four-level and binary values and their positive gap, as well as the value \(1-\alpha\) under disjoint support, follow through (1) from the asymmetric theorem. For the full stochastic model, \(\texttt{thm:common-selector-lp}\) supplies the exact-balance Bonferroni guarantee, and \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) supplies the active-arm total-variation bound. Neither follows from \(\Gamma_{M,\alpha}(w)\). Because every computational branch evaluates the same strict-prefix probability within the deterministic submodel, the common-target, active-arm, pair-audit, empty-library, ordinary-rank, and weighted-orbit semantics remain unchanged.