Condition throughout on \(\mathcal T\). First consider the feasibility claim. Write \(A_{\cdot h}\) for column \(h\) of \(A\). For any \(w\in\Delta(\mathcal H)\) and every row \((a,O)\), the definitions of \(A\) and the integrated mixture law give
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=\sum_{u\in O}q^{\mathrm{obs}}_{w,a}(u)=q^{\mathrm{obs}}_{w,a}(O).
\tag{1}
\]
The corresponding coordinate of the target vector is
\[
(b_{\mathrm{LP}})_{a,O}=\sum_{u\in O}q_{\mathrm{tar},a}(u)=q_{\mathrm{tar},a}(O).
\tag{2}
\]
Consequently, \(Aw=b_{\mathrm{LP}}\) holds if and only if \(w\) jointly orbit-balances both arms. Moreover,
\[
\{Aw:w\in\Delta(\mathcal H)\}=\left\{\sum_{h\in\mathcal H}w_hA_{\cdot h}:w_h\ge0,\ \sum_{h\in\mathcal H}w_h=1\right\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\tag{3}
\]
Thus a jointly balancing \(w\) exists exactly when \(b_{\mathrm{LP}}\) belongs to the displayed convex hull, and the coordinate equations in \((1)\)--\((2)\), together with \(w_h\ge0\) and \(\sum_h w_h=1\), are exactly the stacked program in \(\texttt{def:common-selector-feasibility-lp}\). If \(\mathcal H=\varnothing\), both the simplex and the convex hull in this equivalence are empty and the normalization equation \(\sum_h w_h=1\) is inconsistent. Hence the equivalence remains valid in that degenerate case. In what follows, for the nonvacuous geometric certificate, suppose \(\mathcal H\ne\varnothing\).

Let
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\]
Because \(\mathcal H\) is finite and nonempty, \(C\) is compact. If \(b_{\mathrm{LP}}\notin C\), choose \(c^*\in C\) minimizing \(\lVert b_{\mathrm{LP}}-c\rVert_2\), and put \(y=b_{\mathrm{LP}}-c^*\ne0\). For any \(c\in C\) and \(t\in(0,1]\), convexity gives \(c^*+t(c-c^*)\in C\). Minimality of \(c^*\) therefore yields
\[
0\le\lVert b_{\mathrm{LP}}-c^*-t(c-c^*)\rVert_2^2-\lVert b_{\mathrm{LP}}-c^*\rVert_2^2=-2t y^\top(c-c^*)+t^2\lVert c-c^*\rVert_2^2.
\]
Divide by \(t\) and let \(t\downarrow0\). Then \(y^\top c\le y^\top c^*\) for every \(c\in C\), while
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\lVert y\rVert_2^2>y^\top c^*=\sup_{c\in C}y^\top c=\max_{h\in\mathcal H}y^\top A_{\cdot h}.
\tag{4}
\]
Thus \(y\), together with any scalar strictly between the last two sides of \((4)\), is the asserted strict separating, equivalently Farkas, certificate. When \(\mathcal H=\varnothing\), infeasibility is already certified by the contradictory normalization equation, and separation from the empty convex hull is vacuous.

Now fix a feasible \(w\), let \(N=M+1\), and take the prespecified levels \(\varepsilon_0,\varepsilon_1>0\) satisfying \(\varepsilon_0+\varepsilon_1\le\alpha\). Since \(0<\alpha<1\), each \(\varepsilon_a\in(0,1)\), and hence
\[
k_a=\left\lceil N(1-\varepsilon_a)\right\rceil\in\{1,\ldots,N\}.
\tag{5}
\]
Equations \((1)\)--\((2)\) prove joint orbit balance, so \(\texttt{thm:orbit-balance-iff}\) implies that, for each fixed arm \(a\),
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are independent and identically distributed conditional on \(\mathcal T\). Append independent \(\operatorname{Unif}(0,1)\) variables \(V_{0,a},\ldots,V_{M,a}\) solely for lexicographic tie-breaking. The \(N\) pairs \((S_{i,a},V_{i,a})\) are conditionally iid and almost surely distinct. Exchangeability and uniqueness of the ranks imply that the lexicographic rank \(R_{0,a}\) of the target pair is uniform on \(\{1,\ldots,N\}\): for every rank, each of the \(N\) indices has the same conditional probability of occupying it, and those \(N\) probabilities sum to one.

If \(k_a\le M\) and \(S_{0,a}>r_{a,(k_a)}\), at least \(k_a\) calibration scores are strictly smaller than \(S_{0,a}\), so \(R_{0,a}>k_a\). If \(k_a=N=M+1\), then \(r_{a,(k_a)}=+\infty\) by \(\texttt{def:rank-inversion}\), so the same exceedance event is empty. Therefore both cases satisfy
\[
\Pr(S_{0,a}>r_{a,(k_a)}\mid\mathcal T)\le\Pr(R_{0,a}>k_a\mid\mathcal T)=\frac{N-k_a}{N}.
\tag{6}
\]
The elementary integer identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\), applied with \(x=N\varepsilon_a\), and \(\texttt{def:finite-rank-error}\) give
\[
\frac{N-k_a}{N}=\frac{\lfloor N\varepsilon_a\rfloor}{N}=\rho_{M,\varepsilon_a}\le\varepsilon_a.
\tag{7}
\]
This also covers the boundary \(k_a=N\), where both sides of \((6)\) before the last inequality equal zero.

Under the arm-specific construction in \(\texttt{def:rank-inversion}\),
\[
I_{a,w}=\bigl[\widehat m_a(X_{0T})-r_{a,(k_a)},\widehat m_a(X_{0T})+r_{a,(k_a)}\bigr]\cap[-K,K].
\tag{8}
\]
Assumption \(\texttt{ass:bounded-potential-outcomes}\) gives \(Y_{0T}(a)\in[-K,K]\). Consequently, including when \(r_{a,(k_a)}=+\infty\),
\[
Y_{0T}(a)\in I_{a,w}\quad\Longleftrightarrow\quad |Y_{0T}(a)-\widehat m_a(X_{0T})|\le r_{a,(k_a)}\quad\Longleftrightarrow\quad S_{0,a}\le r_{a,(k_a)}.
\tag{9}
\]
On the intersection of the two armwise events in \((9)\), set subtraction yields
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I_{1,w}-I_{0,w}=\mathcal C_w.
\]
The conditional union bound, which requires no independence between arms, together with \((6)\)--\((7)\), now gives
\[
\begin{aligned}
\Pr(\tau_T\in\mathcal C_w\mid\mathcal T)
&\ge1-\sum_{a=0}^1\Pr(S_{0,a}>r_{a,(k_a)}\mid\mathcal T)\\
&\ge1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\\
&\ge1-\varepsilon_0-\varepsilon_1\ge1-\alpha.
\end{aligned}
\tag{10}
\]
Finally, set \(\varepsilon_0=\varepsilon_1=\alpha/2\). Then \(k_0=k_1=\lceil(M+1)(1-\alpha/2)\rceil=k\), \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\), \(r_{a,(k_a)}=r_{a,(k)}\), and \((6)\)--\((10)\) reduce exactly to
\[
\Pr(S_{0,a}>r_{a,(k)}\mid\mathcal T)\le\frac{M+1-k}{M+1}=\rho_{M,\alpha}\le\frac{\alpha}{2},\qquad \Pr(\tau_T\in\mathcal C_w\mid\mathcal T)\ge1-2\rho_{M,\alpha}\ge1-\alpha.
\]
Thus the former symmetric theorem and all of its formulas are recovered as a corollary.