Fix \(a\in\{0,1\}\) and condition on \(\mathcal T\). By \(\texttt{lem:orbit-score-factorization}\), for every Borel set \(C\subseteq[0,\infty)\), \[\Pr(S_{i,a}\in C\mid\mathcal T)=\sum_{O\subseteq\mathcal U_a}q_{a,O}F_{a,O}(C),\qquad \Pr(S_{0,a}\in C\mid\mathcal T)=\sum_{O\subseteq\mathcal U_a}p_{a,O}F_{a,O}(C).\tag{1}\] Under joint orbit balance, \(q_{a,O}=p_{a,O}\) for every arm and orbit by \(\texttt{def:joint-orbit-balance}\), so (1) proves equality in law for every declared invariant law and every fixed measurable predictor. The factorization lemma also makes the calibration pairs iid and independent of the target pair. Their score marginals now agree, so \(S_{1,a},\ldots,S_{M,a},S_{0,a}\) are iid conditional on \(\mathcal T\), arm by arm.
Conversely, suppose balance fails. Then for some arm \(a\) and orbit \(O_\star\subseteq\mathcal U_a\), \[q_{a,O_\star}\ne p_{a,O_\star}.\tag{2}\] Invoke \(\texttt{def:orbit-separating-law}\) with \(\widehat m_0=\widehat m_1=0\). Its arm \(a\) outcomes are \(Y_v(a)=K\mathbf 1\{(v,a)\in O_\star\}\), and the other-arm outcomes are zero. All outcomes lie in \([-K,K]\). If \(L^\star\) is the prototype and \(G_0\) is uniform on \(\mathcal G\), then \(hG_0L^\star\) and \(G_0L^\star\) have the same law for every \(h\in\mathcal G\); thus the symmetrized law is invariant and belongs to \(\mathcal P_{\mathcal G,K}\). Independent symmetrized copies supply the replicated law. On every supported assignment the selector chooses only an actually observed arm \(a\) member, so \[S_{i,a}=K\mathbf 1\{U_{i,a}\in O_\star\},\qquad S_{0,a}=K\mathbf 1\{T^a\in O_\star\}.\tag{3}\] Because \(K>0\), (2)--(3) imply \[\Pr(S_{i,a}=K\mid\mathcal T)=q_{a,O_\star}\ne p_{a,O_\star}=\Pr(S_{0,a}=K\mid\mathcal T).\] Hence uniform equality of the score laws implies balance.
The support-only repair causes no hidden restriction. If \(\nu(z)>0\), invariance of \(\nu\) implies \(\nu(gz)>0\), so every use of selector equivariance stays on the supported domain. Assignments outside that domain receive zero weight in all integrated selector laws, and arbitrary total extensions there change neither (1) nor (3). The proof is strictly armwise: the common target, assignment, and selector mixture may couple the two arms, and no cross-arm exchangeability is claimed.