Condition throughout on \(\mathcal T\), and fix an arm \(a\in\{0,1\}\). The trained map \(\widehat m_a\) is then fixed. By \(\texttt{lem:orbit-score-factorization}\), there are probability laws \(F_{a,O}\) such that the \(M\) calibration orbit--score pairs are independent and identically distributed with law
\[
\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),
\]
whereas the independent target orbit--score pair has law
\[
\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).
\]
Assumption \(\texttt{ass:orbit-overlap}\) gives \(\mathsf P_a\ll\mathsf Q_a\). On every orbit fibre with positive \(\mathsf P_a\)-mass, the Radon--Nikodym derivative is
\[
\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\frac{p_{a,O}}{q_{a,O}}=\lambda_{a,O}.
\]
Thus the derivative depends only on the orbit: the common conditional score kernel \(F_{a,O}\) cancels. In particular, member-level overlap within an orbit is unnecessary.

Apply \(\texttt{lem:finite-support-weighted-rank-validity}\), conditionally on \(\mathcal T\), with \(\mathscr E=\mathcal O_a\), \(q_O=q_{a,O}\), \(p_O=p_{a,O}\), \(R_i=S_{i,a}\), and \(\varepsilon=\alpha/2\). The target draw satisfies \(p_{a,O_{T,a}}>0\) almost surely; orbit overlap therefore gives \(q_{a,O_{T,a}}>0\) and \(\lambda_{a,O_{T,a}}>0\), so the infinity-augmented measure has positive total mass. The quantile in that lemma is exactly \(r^{\mathrm W}_{a,w}\) from \(\texttt{def:weighted-rank-inversion}\). Consequently,
\[
\Pr_P\!\left(S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\right)\le\frac{\alpha}{2}.
\tag{1}
\]

Let \(E_a=\{S_{0,a}\le r^{\mathrm W}_{a,w}\}\), and define the untrimmed residual interval
\[
\widetilde I^{\mathrm W}_{a,w}=\left[\widehat m_a(X_{0T})-r^{\mathrm W}_{a,w},\widehat m_a(X_{0T})+r^{\mathrm W}_{a,w}\right].
\]
On \(E_a\), the identity \(S_{0,a}=|Y_{0T}(a)-\widehat m_a(X_{0T})|\) implies \(Y_{0T}(a)\in\widetilde I^{\mathrm W}_{a,w}\). Assumption \(\texttt{ass:bounded-potential-outcomes}\) also gives \(Y_{0T}(a)\in[-K,K]\). Since the reported interval is
\[
I^{\mathrm W}_{a,w}=\widetilde I^{\mathrm W}_{a,w}\cap[-K,K],
\]
we have \(Y_{0T}(a)\in I^{\mathrm W}_{a,w}\) on \(E_a\), including when \(r^{\mathrm W}_{a,w}=+\infty\).

Applying \((1)\) to both arms and using the union bound, with no cross-arm independence assumption, yields
\[
\Pr_P(E_0\cap E_1\mid\mathcal T)\ge 1-\Pr_P(E_0^c\mid\mathcal T)-\Pr_P(E_1^c\mid\mathcal T)\ge1-\alpha.
\]
On \(E_0\cap E_1\), set subtraction gives
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.
\]
This proves the asserted conditional coverage for every law, fixed or prespecified mixture, and trained predictor map in the theorem.

Finally, suppose joint orbit balance holds. By \(\texttt{thm:orbit-balance-iff}\), \(p_{a,O}=q_{a,O}\) for every arm and orbit. Hence \(\lambda_{a,O}=1\) on every orbit that can be drawn; orbits having zero mass under both laws are irrelevant. The normalized weighted measure therefore assigns equal mass to each of the \(M\) calibration scores and to \(+\infty\). Its left-continuous \(1-\alpha/2\) quantile is the \(k\)-th order statistic among those \(M+1\) atoms: it is \(r_{a,(k)}\) when \(k\le M\) and \(+\infty\) when \(k=M+1\). Thus \(r^{\mathrm W}_{a,w}=r_{a,(k)}\). The weighted and ordinary constructions then intersect the same residual-centred interval with \([-K,K]\) in each arm, so \(I^{\mathrm W}_{a,w}=I_{a,w}\) and \(\mathcal C^{\mathrm W}_w=\mathcal C_w\). This proves the claimed reduction to ordinary rank inversion.