Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). If \(k_a\le M\), the order-statistic identity gives
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\quad\Longleftrightarrow\quad\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a. \tag{1}
\]
Indeed, the \(k_a\)-th calibration order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by strict comparison and the event depends on \(s_a\) only through its total preorder. If \(k_a=M+1\), then \(Q_{k_a}=+\infty\) by \(\texttt{def:rank-inversion}\), so that arm's event is certain.

Conversely, let a total preorder have ordered nonempty tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\). Assign score zero if \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(C_{a,j}\). Since \(K>0\), this realizes the preorder in \([0,K]\) with at most \(d_a\le m_a\) levels. Hence finite preorder enumeration attains the maximum in \(\texttt{def:coverage-frontier}\). This proves exactness for the declared bounded orbit-constant score class, without asserting a supremum over all \(P\in\mathcal P_{\mathcal G,K}\).

Suppose first that \(k_0,k_1\le M\). Apply \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). It retains the coherent common-target law
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\} \tag{2}
\]
and the full joint calibration law
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z). \tag{3}
\]
For each preorder pair \(C\), the lemma pushes (2) to \(P_T^C\), obtains every exact vector \(\pi^C(j,\ell)\) from a prefix table of the unchanged law (3), and aggregates the unchanged coherent target masses into
\[
\omega_C(\pi)=\sum_{(j,\ell):\pi^C(j,\ell)=\pi}P_T^C(j,\ell). \tag{4}
\]
It proves \(U_C\le L_C\le\min\{L,d_0d_1\}\) and the exact identity
\[
\Pr\{\text{both rank events under }C\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi). \tag{5}
\]
Thus \(\pi\) contains the full shared-assignment calibration dependence from \(R_w\), while \(\omega_C\) contains the one-common-member coherence from \(P_T^C\). Neither object is factorized.

The local grouping calculation in that lemma gives the displayed local-cache instance-adaptive and uniform bounds in the theorem. For the global refinement, put
\[
\Pi_\star=\bigcup_{C\in\mathfrak C}\Pi_C,\qquad G=|\Pi_\star|. \tag{6}
\]
The coupled recurrence depends only on the key
\[
(M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10}),\qquad \pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10}. \tag{7}
\]
It does not depend on \(C\) or on \(\omega_C(\pi)\). A global balanced-tree memo therefore computes the recurrence once for each of the \(G\) keys and performs one lookup for each of the \(\sum_CU_C\) local occurrences. Multiplication by the local weight occurs only in (5). The lemma consequently gives the exact total
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)+\sum_{C\in\mathfrak C}\left[L_C\log(1+L_C)+L_C+U_C\right]+\left\{\sum_{C\in\mathfrak C}U_C\right\}\log(1+G)+GMk_0k_1
\right), \tag{8}
\]
its uniform version
\[
O\!\left(|\mathcal V|+F_{m_0}F_{m_1}\left[m_0m_1+L+L_{\max}\log(1+L_{\max})+L_{\max}+U_{\max}\{1+\log(1+G)\}\right]+GMk_0k_1\right), \tag{9}
\]
and working memory
\[
O(m_0m_1+L+k_0k_1+U_{\max}+G). \tag{10}
\]
Equations (2)--(7) explicitly prove that global memoization changes only recurrence reuse, not the target or calibration probability objects.

Suppose next that exactly one rank \(k_b=M+1\), and put \(c=1-b\). By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), the boundary-arm event is certain and disappears. Conditional on \(O_{T,c}=O_t\), (1) is the event that a binomial variable with success probability
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O} \tag{11}
\]
is below \(k_c\). Averaging gives
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}\Pr\!\left\{\operatorname{Bin}(M,\theta(O_t))<k_c\right\}. \tag{12}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), put \(q_j=q_c(C_j)\), \(p_j=p_c(C_j)\), and \(\theta_j=\sum_{\ell<j}q_\ell\). Then (12) is
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}. \tag{13}
\]
One cumulative class scan forms these masses. For \(0<\theta<1\), the lower-tail terms obey
\[
t_0=(1-\theta)^M,\qquad t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta}, \tag{14}
\]
and the upper-tail terms obey
\[
u_M=\theta^M,\qquad u_{r-1}=u_r\frac{r}{M-r+1}\frac{1-\theta}{\theta}. \tag{15}
\]
By \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), exponentiation by squaring and the shorter tail require \(O(\log M+\min\{k_c,M-k_c+1\})\) operations and constant auxiliary memory. At \(\theta=0\) and \(\theta=1\), the probabilities are one and zero without division. Enumerating the \(F_{m_c}\) nonboundary preorders proves the stated one-boundary complexity and the absence of every boundary-arm factor.

If both ranks equal \(M+1\), both events are certain, and therefore
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=[(1-\alpha)-1]_+=0. \tag{16}
\]

It remains to verify the nonbinary witness. Take four pair blocks, \(\mathcal G=S_2^4\), independent fair within-pair assignments, and a singleton selector library. In either arm let the selector choose blocks with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right) \tag{17}
\]
and then choose the unique member observed in that arm. The kernel is observable and equivariant. Give the common target block probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\qquad q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2}. \tag{18}
\]
For \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=3\). Put \(s_0\equiv0\) and order arm-one blocks as \(1\prec3\prec2\prec4\). Arm zero never fails, while arm one fails precisely when all three calibration blocks lie below the target block. Hence its failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}, \tag{19}
\]
and the frontier objective is \(24957/160000\). For binary maps let \(H_a\) be the high-score block set and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion conditional on the common target block gives
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1. \tag{20}
\]
Order the sixteen subsets as \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\). Exact substitution of all sixteen choices of \(H_1\) for each fixed \(H_0\) gives the row maxima, with denominator \(320000000\),
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split} \tag{21}
\]
This exhausts all \(16^2\) binary pairs. Their largest failure probability is \(3259109/5000000\), so the largest binary frontier objective is \(759109/5000000\). The four-level advantage is
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0. \tag{22}
\]

Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Assign score \(K\) to every target-supported arm-\(a\) orbit and zero to all other orbits in that arm, and use the zero score in the other arm. The arm-\(a\) target score is always \(K\), every calibration score is zero, and the joint rank event has probability zero. Therefore
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha. \tag{23}
\]
If one rank is at the boundary, (11)--(15) give the exact reduction to the other arm. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), the armwise staircase gives \(k_0=k_1=k\), so all assertions specialize to the equal-split theorem.