Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\).  If \(k_a\le M\), the elementary order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a. \tag{1}
\]
Indeed, the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it.  Thus ties are handled by strict comparison, and the event depends on \(s_a\) only through its total preorder.  If \(k_a=M+1\), then \(Q_{k_a}=+\infty\) by \(\texttt{def:rank-inversion}\), and that arm's event is certain.

Conversely, suppose a total preorder has ordered nonempty classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\).  Assign score \(0\) if \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(C_{a,j}\).  Because \(K>0\), this realizes the preorder in \([0,K]\) using \(d_a\le m_a\) levels.  The score domain and preorder set are finite, so enumerating all preorder pairs attains the maximum in \(\texttt{def:coverage-frontier}\).  This establishes exactness for the declared orbit-constant score class and does not assert sharpness over all laws in \(\mathcal P_{\mathcal G,K}\).

Assume first that \(k_0,k_1\le M\).  The coherent evaluator retains
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z) \tag{2}
\]
and
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}. \tag{3}
\]
For each preorder pair \(C\), \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) forms every exact vector \(\pi^C(j,\ell)\) from a prefix table of the unchanged full calibration law (2), pushes the unchanged coherent target law (3) to \(P_T^C\), and aggregates only identical vectors:
\[
\omega_C(\pi)=\sum_{(j,\ell):\pi^C(j,\ell)=\pi}P_T^C(j,\ell). \tag{4}
\]
It proves
\[
U_C\le L_C\le\min\{L,d_0d_1\},\qquad
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi). \tag{5}
\]
Thus \(\pi\) preserves the shared-assignment dependence, and \(\omega_C\) preserves the common target.

With \(\Pi_\star=\bigcup_C\Pi_C\) and \(G=|\Pi_\star|\), the key
\[
(M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10}),\qquad
\pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10}, \tag{6}
\]
determines the complete recurrence input and excludes the local weight.  Hence each recurrence value is computed once, the weights are applied only in (5), and the lemma gives exactly the two displayed recurrence-only time bounds and the displayed memory bound in the theorem.

The same values also admit the exact multinomial formula of \(\texttt{lem:four-cell-multinomial-sum-alternative}\).  Let \(\mathsf T=\mathsf T_{M,k_0,k_1}\) and let \(\Pi_{\mathrm{MS}}\sqcup\Pi_{\mathrm{DP}}=\Pi_\star\) be the actual branch partition.  If \(\mathsf B\) denotes all non-evaluator terms in the theorem's instance-adaptive bound, the synchronized exact alternative is
\[
O\!\left(
\mathsf B+M+\sum_{\pi\in\Pi_{\mathrm{MS}}}(M+\mathsf T)
+|\Pi_{\mathrm{DP}}|Mk_0k_1
\right), \tag{7}
\]
with the one-time \(O(M)\) factorial table shared across all \(G\) keys and four \(\pi\)-specific power tables rebuilt on each multinomial call.  The time-selecting specialization is
\[
O\!\left(\mathsf B+M+G\min\{M+\mathsf T,Mk_0k_1\}\right). \tag{8}
\]
Keys are processed sequentially.  Consequently the multinomial branch uses \(O(M)\) workspace, the recurrence branch uses \(O(k_0k_1)\), and the unconditional hybrid memory is
\[
O\!\left(m_0m_1+L+U_{\max}+G+\max\{M,k_0k_1\}\right). \tag{9}
\]
The recurrence-only claims in the theorem follow by taking \(\Pi_{\mathrm{DP}}=\Pi_\star\).  Equations (2)--(6) show that neither computational branch changes the probability objects.

Suppose exactly one rank \(k_b=M+1\), and put \(c=1-b\).  By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), the boundary-arm event is certain and disappears.  Conditional on \(O_{T,c}=O_t\), (1) counts iid calibration orbits below the target, with probability
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over the target gives
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}
\Pr\{\operatorname{Bin}(M,\theta(O_t))<k_c\}. \tag{10}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), put \(q_j=q_c(C_j)\), \(p_j=p_c(C_j)\), and \(\theta_j=\sum_{\ell<j}q_\ell\).  Then (10) is
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}. \tag{11}
\]
A single ordered-class scan forms all masses.  For \(0<\theta<1\), the exact lower-tail terms satisfy
\[
t_0=(1-\theta)^M,\qquad
t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta}, \tag{12}
\]
and the exact upper-tail terms satisfy
\[
u_M=\theta^M,\qquad\nu_{r-1}=u_r\frac{r}{M-r+1}\frac{1-\theta}{\theta}. \tag{13}
\]
By \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), exponentiation by squaring and the shorter tail cost
\[
O(\log M+\min\{k_c,M-k_c+1\})
\]
operations and constant CDF workspace.  At \(\theta=0\) and \(\theta=1\), the probabilities are respectively one and zero without division.  Enumerating only the \(F_{m_c}\) nonboundary preorders gives the stated one-boundary complexity and removes every boundary-arm factor.  If both ranks equal \(M+1\), both events are certain, and
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=[(1-\alpha)-1]_+=0. \tag{14}
\]

We next prove the nonbinary assertion.  Take four pair blocks, \(\mathcal G=S_2^4\), independent fair within-pair assignments, and a singleton selector library.  In either arm choose blocks with calibration probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\]
and then select the unique member observed in that arm.  This kernel is observable and equivariant.  Give the common target block probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\qquad
q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2}. \tag{15}
\]
For \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=3\).  Put \(s_0\equiv0\) and order arm-one blocks as \(1\prec3\prec2\prec4\).  Arm zero always succeeds, while arm one fails exactly when all three calibration blocks are below the target.  The failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+
\frac1{10}\left(\frac{18}{20}\right)^3+
\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}. \tag{16}
\]
The frontier objective is therefore \(24957/160000\).

For binary maps let \(H_a\) be the high-score block set and put \(A_a=(1-q(H_a))^3\).  Inclusion--exclusion conditional on the common target block gives
\[
F_{\mathrm{bin}}(H_0,H_1)
=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1. \tag{17}
\]
Order the sixteen subsets as
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.
\]
Exact substitution of all sixteen \(H_1\) for every fixed \(H_0\) gives the row maxima, with denominator \(320000000\),
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split} \tag{18}
\]
This finite enumeration exhausts all \(16^2\) binary pairs.  Its largest failure probability is \(3259109/5000000\), so its largest frontier objective is \(759109/5000000\).  The four-level improvement is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0. \tag{19}
\]

Finally suppose the target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\).  Assign score \(K\) to every target-supported orbit and zero to all other arm-\(a\) orbits, and use the zero score in the other arm.  The arm-\(a\) target score is always \(K\), all its calibration scores are zero, and the joint rank event has probability zero.  Since the positive-part objective can never exceed \(1-\alpha\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha. \tag{20}
\]
If an arm is at the boundary, (10)--(13) give the exact reduction to the other arm.  On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), the staircase gives \(k_0=k_1=k\), so every assertion specializes to \(\texttt{thm:sharp-orbit-coverage-frontier}\).