Condition throughout on \(\mathcal T\), so the trained maps are fixed. We first dispose of the empty-library case. By convention \(\Delta(\varnothing)=\varnothing\). If \(\mathcal H=\varnothing\), then a vector indexed by \(\mathcal H\) has
\[
\sum_{h\in\mathcal H}w_h=0,
\]
which contradicts the normalization \(\sum_h w_h=1\) in \(\texttt{def:common-selector-feasibility-lp}\). Thus the feasibility program is infeasible by an explicit normalization certificate. There is no \(w\), hence no mixture kernel \(\kappa_{w,a}\), no integrated calibration law \(q^{\mathrm{obs}}_{w,a}\), and no weighted procedure. Under the corrected nonempty-domain definition \(\texttt{def:minimum-imbalance-common-selector}\), the objects \(D_*\), \(\mathcal W_*\), and \(w_*\) are likewise not defined in this case. No separating-hyperplane assertion is made for the empty convex hull.

Now assume that \(\mathcal H\) is finite and nonempty. For every \(w\in\Delta(\mathcal H)\), the definitions of \(A\), \(q^{\mathrm{obs}}_{w,a}\), and \(b_{\mathrm{LP}}\) give, row by row,
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=\sum_{u\in O}q^{\mathrm{obs}}_{w,a}(u)=q^{\mathrm{obs}}_{w,a}(O),\tag{1}
\]
and
\[
(b_{\mathrm{LP}})_{a,O}=\sum_{u\in O}q_{\mathrm{tar},a}(u)=q_{\mathrm{tar},a}(O).\tag{2}
\]
Consequently \(Aw=b_{\mathrm{LP}}\) is equivalent to all of the joint-orbit-balance equations in \(\texttt{def:joint-orbit-balance}\). Moreover,
\[
\{Aw:w\in\Delta(\mathcal H)\}=\left\{\sum_{h\in\mathcal H}w_hA_{\cdot h}:w_h\ge0,\ \sum_{h\in\mathcal H}w_h=1\right\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.\tag{3}
\]
Equations \((1)\)--\((3)\) prove the balance, convex-hull, and LP-feasibility equivalences.

Suppose that \(b_{\mathrm{LP}}\) does not belong to the convex hull \(C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\). Because the library is finite and nonempty, \(C\) is nonempty and compact. Let \(c^*\in C\) minimize \(\lVert b_{\mathrm{LP}}-c\rVert_2\), and put \(y=b_{\mathrm{LP}}-c^*\ne0\). For any \(c\in C\) and \(0<t\le1\), convexity puts \(c^*+t(c-c^*)\) in \(C\). Minimality gives
\[
0\le-2t y^\top(c-c^*)+t^2\lVert c-c^*\rVert_2^2.
\]
After division by \(t\) and passage to \(t\downarrow0\),
\[
y^\top c\le y^\top c^*\quad\forall c\in C.
\]
Since \(y=b_{\mathrm{LP}}-c^*\),
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\lVert y\rVert_2^2>y^\top c^*=\max_{h\in\mathcal H}y^\top A_{\cdot h}.\tag{4}
\]
Thus \(y\), together with a scalar strictly between the two sides of \((4)\), is a strict separating hyperplane and hence a Farkas infeasibility certificate. The nonemptiness restriction is essential to this construction.

Fix a feasible common \(w\), write \(N=M+1\), and fix \(\boldsymbol\varepsilon=(\varepsilon_0,\varepsilon_1)\) as in the statement. Feasibility and \((1)\)--\((2)\) imply joint orbit balance. Therefore \(\texttt{thm:orbit-balance-iff}\) implies, separately for each arm \(a\), that
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are conditionally independent and identically distributed. Append independent continuous tie breakers and let \(R_{0,a}\) be the target's lexicographic rank among the \(N\) augmented scores. Conditional exchangeability makes \(R_{0,a}\) uniform on \(\{1,\ldots,N\}\). If \(k_a\le M\) and \(S_{0,a}>r_{a,(k_a)}\), at least \(k_a\) calibration scores are strictly smaller, so \(R_{0,a}>k_a\). If \(k_a=N\), the threshold is \(+\infty\) and the exceedance event is empty. Hence in both cases
\[
\Pr\!\left(S_{0,a}>r_{a,(k_a)}\mid\mathcal T\right)\le\Pr(R_{0,a}>k_a\mid\mathcal T)=\frac{N-k_a}{N}.\tag{5}
\]
The identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\), applied with \(x=N\varepsilon_a\), and \(\texttt{def:finite-rank-error}\) yield
\[
\frac{N-k_a}{N}=\frac{\lfloor N\varepsilon_a\rfloor}{N}=\rho_{M,\varepsilon_a}\le\varepsilon_a.\tag{6}
\]
By bounded potential outcomes, \(Y_{0T}(a)\in[-K,K]\). Therefore the clipping in \(\texttt{def:rank-inversion}\) does not remove the true outcome when its residual is within the radius, and
\[
S_{0,a}\le r_{a,(k_a)}\quad\Longrightarrow\quad Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w}.\tag{7}
\]
On the intersection of the two events in \((7)\),
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\]
The conditional union bound, which requires no arm independence, and \((5)\)--\((7)\) give
\[
\Pr\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right)\ge1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\ge1-\varepsilon_0-\varepsilon_1\ge1-\alpha.\tag{8}
\]
Finally, if \(\varepsilon_0=\varepsilon_1=\alpha/2\), then the definitions give \(k_0=k_1=k\), \(I^{\boldsymbol\varepsilon}_{a,w}=I_{a,w}\), and \(\mathcal C^{\boldsymbol\varepsilon}_w=\mathcal C_w\). Equations \((5)\)--\((8)\) then give the symmetric formulas.