Condition throughout on \(\mathcal T\). First consider feasibility. Let \(A_{\cdot h}\) denote column \(h\) of \(A\). For every \(w\in\Delta(\mathcal H)\) and every row \((a,O)\), the definitions of \(A\) and the integrated mixture law give
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=\sum_{u\in O}q^{\mathrm{obs}}_{w,a}(u)=q^{\mathrm{obs}}_{w,a}(O).
\]
By the definition of \(b_{\mathrm{LP}}\), its same coordinate is
\[
(b_{\mathrm{LP}})_{a,O}=q_{\mathrm{tar},a}(O).
\]
Consequently \(Aw=b_{\mathrm{LP}}\) is equivalent, coordinate by coordinate and simultaneously for both arms, to joint orbit balance. Moreover,
\[
\{Aw:w\in\Delta(\mathcal H)\}=\left\{\sum_{h\in\mathcal H}w_hA_{\cdot h}:w_h\ge0,\ \sum_{h\in\mathcal H}w_h=1\right\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\]
This proves both the convex-hull criterion and its equivalence to feasibility of the stacked linear program in \(\texttt{def:common-selector-feasibility-lp}\).

For completeness, the failure certificate can be obtained directly. Put \(C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\). Because \(\mathcal H\) is finite, \(C\) is compact. If \(b_{\mathrm{LP}}\notin C\), choose \(c^*\in C\) minimizing \(\|b_{\mathrm{LP}}-c\|_2\) and set \(y=b_{\mathrm{LP}}-c^*\ne0\). For any \(c\in C\) and \(t\in[0,1]\), the point \(c^*+t(c-c^*)\) belongs to \(C\). Minimality of \(c^*\) yields
\[
0\le \|b_{\mathrm{LP}}-c^*-t(c-c^*)\|_2^2-\|b_{\mathrm{LP}}-c^*\|_2^2=-2t\,y^\top(c-c^*)+t^2\|c-c^*\|_2^2.
\]
After division by \(t>0\) and passage to \(t\downarrow0\), this gives \(y^\top c\le y^\top c^*\). Hence
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\|y\|_2^2>y^\top c^*=\sup_{c\in C}y^\top c=\max_{h\in\mathcal H}y^\top A_{\cdot h}.
\]
Thus \(y\), together with any threshold strictly between the two displayed sides, is the asserted Farkas separating-hyperplane certificate.

Now fix a feasible \(w\). The preceding equivalence gives joint orbit balance. The iid-array, independent-target, and selector-auxiliary-randomization assumptions are precisely the sampling hypotheses used by \(\texttt{thm:orbit-balance-iff}\); that theorem therefore implies that, for each fixed arm \(a\),
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are iid conditional on \(\mathcal T\). No assertion about independence between the two arms is needed. Write \(N=M+1\), and append independent \(\operatorname{Unif}(0,1)\) variables \(V_{0,a},\ldots,V_{M,a}\) solely to break ties lexicographically. The \(N\) pairs \((S_{i,a},V_{i,a})\) are iid and almost surely have no ties, so permutation symmetry makes the lexicographic rank \(R_{0,a}\) of the target pair uniform on \(\{1,\ldots,N\}\).

If \(k\le M\) and \(S_{0,a}>r_{a,(k)}\), at least \(k\) calibration scores are strictly smaller than \(S_{0,a}\). Their lexicographic pairs precede the target pair, and therefore \(R_{0,a}>k\). It follows that
\[
\Pr(S_{0,a}>r_{a,(k)}\mid\mathcal T)\le\Pr(R_{0,a}>k\mid\mathcal T)=\frac{N-k}{N}=\frac{M+1-k}{M+1}.
\]
If \(k=M+1=N\), the definition sets \(r_{a,(k)}=+\infty\), so the left side is zero and the same display remains valid. Finally, using \(k=\lceil N(1-\alpha/2)\rceil\) and the integer identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\),
\[
\frac{N-k}{N}=\frac{\lfloor N\alpha/2\rfloor}{N}=\rho_{M,\alpha}\le\frac{\alpha}{2},
\]
where the middle equality is exactly \(\texttt{def:finite-rank-error}\).

For each arm, the closed interval in \(\texttt{def:rank-inversion}\) satisfies
\[
Y_{0T}(a)\in I_{a,w}\quad\Longleftrightarrow\quad S_{0,a}\le r_{a,(k)}.
\]
On the intersection of these two armwise events,
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I_{1,w}-I_{0,w}=\mathcal C_w.
\]
The conditional union bound, which does not require arm independence, therefore gives
\[
\Pr(\tau_T\in\mathcal C_w\mid\mathcal T)\ge1-\sum_{a=0}^1\Pr(S_{0,a}>r_{a,(k)}\mid\mathcal T)\ge1-2\rho_{M,\alpha}\ge1-\alpha.
\]
This proves every assertion.