Fix a pair block \(b\). By \(\texttt{def:pair-action}\), the nonidentity element \(s_b\) interchanges the two members of block \(b\), preserves the arm coordinate, fixes every member outside that block, and applies the declared complete-record relabelling. Hence, for \(r,a\in\{0,1\}\),\[s_b(v_{b,r},a)=(v_{b,1-r},a).\]For a fixed arm \(a\), each of \( (v_{b,0},a)\) and \( (v_{b,1},a)\) is reachable from the other by \(s_b\), while arm preservation prevents either state from reaching a state with arm label \(1-a\). Therefore the two arm-specific pair orbits are exactly\[O_{b,0}=\{(v_{b,0},0),(v_{b,1},0)\},\qquad O_{b,1}=\{(v_{b,0},1),(v_{b,1},1)\}.\]
Now suppose the lifted target selector is supported on \(O_{b,1}\). Its arm \(1\) orbit-mass vector consequently satisfies\[q_{\mathrm{tar},1}(O_{b,1})=1,\qquad q_{\mathrm{tar},1}(O)=0\quad(O\ne O_{b,1}).\]An exclusive mate-control proposal is instead supported on a state in \(O_{b,0}\). Its proposed orbit-mass vector therefore assigns zero mass to \(O_{b,1}\) and unit mass to \(O_{b,0}\). In particular, it differs from the target vector in the \((1,O_{b,1})\) coordinate. By \(\texttt{def:joint-orbit-balance}\), equality of every arm-orbit coordinate is necessary for exact joint balance, so this proposed rule is not jointly orbit balancing. Equivalently, its candidate weight vector cannot satisfy the \((1,O_{b,1})\) row of \(Aw=b_{\mathrm{LP}}\) in \(\texttt{def:common-selector-feasibility-lp}\). Notice also that the proposal changes the arm label: a control state in \(O_{b,0}\) cannot itself serve as an observed arm \(1\) calibration state. Thus it is ruled out as an arm \(1\) selector before outcomes are inspected.
At the level of orbit masses, the same comparison gives the disjointness condition: the only target-supported arm \(1\) orbit is \(O_{b,1}\), and the exclusive mate-control proposal assigns it calibration mass zero. Accordingly, for any legal implemented arm \(1\) calibration selector with this same zero mass on \(O_{b,1}\), every target-supported arm \(1\) orbit has zero calibration mass, which is exactly the premise of \(\texttt{prop:disjoint-orbit-witness}\). If \(k\le M\), that proposition supplies a bounded invariant law for which \(\mathcal C_w=\{0\}\) and the common-target effect has conditional coverage zero. If \(k=M+1\), \(\texttt{prop:rank-boundary}\) instead gives \(\mathcal C_w=\mathbb R\) and conditional coverage one. Since \(k\in\{1,\ldots,M+1\}\), these two cases exhaust the rank boundary and establish the claimed qualification.