Fix an orientation \(\sigma=(\sigma_0,\sigma_1)\) and define \(B_{ia}^{\sigma}=B_{ia}\) under \(L\), while \(B_{ia}^{\sigma}=1-B_{ia}\) under \(U\). This transformation merely permutes the four atoms of \(\pi\), so its pushforward \(\pi^\sigma\) is again a probability mass function, with no positivity requirement. Let \(T_{ia}=\sum_{j=1}^iB_{ja}^{\sigma}\). On the rectangle \(0\le r<t_0\), \(0\le s<t_1\), initialize \(d_0(0,0)=1\) and update
\[
d_{i+1}(r,s)=\sum_{x,y\in\{0,1\}}\pi^\sigma_{xy}d_i(r-x,s-y). \tag{1}
\]
Induction on \(i\) gives \(d_i(r,s)=\Pr\{T_{i0}=r,T_{i1}=s\}\) on the retained rectangle. Nonnegative increments ensure that discarded states never return. At stage \(i\), each count is at most \(i\), so at most
\[
\min\{t_0,i+1\}\min\{t_1,i+1\}
\]
states are active. Summing these charges for \(i=0,\ldots,M-1\) and using two rolling arrays proves the stated time and memory bounds.

If \(\sigma=(L,L)\), the retained event is \(\{R<k_0,S<k_1\}\), hence the answer is \(J_{LL}\). If \(\sigma=(L,U)\), then
\[
\sum_i(1-B_{i1})<h_1=M-k_1+1
\quad\Longleftrightarrow\quad S\ge k_1. \tag{2}
\]
Thus \(J_{LU}=\Pr\{R<k_0,S\ge k_1\}\), and partitioning \(\{R<k_0\}\) gives
\[
\Pr\{R<k_0,S<k_1\}=\Pr\{R<k_0\}-J_{LU}. \tag{3}
\]
The \((U,L)\) identity is symmetric. Under \((U,U)\), (2) in both coordinates gives \(J_{UU}=\Pr\{R\ge k_0,S\ge k_1\}\); two-event inclusion--exclusion yields
\[
\Pr\{R<k_0,S<k_1\}
=1-\Pr\{R\ge k_0\}-\Pr\{S\ge k_1\}+J_{UU}. \tag{4}
\]

The marginal success probabilities are \(\pi_{10}+\pi_{11}\) and \(\pi_{01}+\pi_{11}\). Therefore \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\) evaluates every required lower tail, and an upper tail is its complement, in
\[
O\!\left(\log M+\min\{k_a,M-k_a+1\}\right)
\]
operations and constant memory. Choose \(L\) when \(k_a\le h_a\) and \(U\) otherwise. Then \(t_a=\bar k_a\). The recurrence sum is at least \(M\), because each of its \(M\) summands is at least one, so it absorbs both marginal costs. Substitution in (1)--(4) proves the final complexity and exact recovery claims.