Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,\qquad \Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
The deterministic-preorder interpretation, coherent common-target calculation, full-model disclaimer, binary counterexample, disjoint-support value, and comparator scope therefore specialize directly from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). In particular, the bounded common-Bernoulli example shows that an arbitrary invariant law can have a stochastic residual score conditional on its orbit, so the diagonal functional is not a uniform full-model joint-inclusion or effect-coverage certificate.

The pointwise inclusion specializes to
\[
\{Y_{0T}(1)\in I_{1,w},\ Y_{0T}(0)\in I_{0,w}\}\subseteq\{\tau_T\in I_{1,w}-I_{0,w}\}=\{\tau_T\in\mathcal C_w\}.
\tag{2}
\]
Monotonicity of conditional probability proves the displayed inequality. If both intervals are \(\{0\}\) and both potential outcomes equal \(K\), the right event in (2) holds and the left event fails. Thus equality need not hold, and the algebraic containment does not enlarge the deterministic domain in (1).

Assume \(k\le M\). Specializing the asymmetric seven-way partition gives the displayed disjoint strata. Since
\[
\bar k_0=\bar k_1=\bar k=\min\{k,M-k+1\},
\]
the rolling charge is \(\mathsf C_{M,k,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2\). Substitution in the asymmetric branch sum gives \(\mathsf B_{\mathrm{sym}}\), including the face and rank-one terms. The same substitution gives \(\mathsf W_{\mathrm{sym}}\). The vertex, edge, face, and rank-one evaluators use constant workspace, the rank-one evaluator does not trigger factorial preprocessing, and the adaptive, uniform, and memory bounds follow from \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). These steps use only normalization, realized-arm support on \(\operatorname{supp}(\nu)\), conditional selector draws, and the off-support zero-weight fact.

For every \(M\ge2\), taking \(\alpha=2/(M+1)\) gives \(k=M\). The audited edge construction in the coherent evaluator realizes \(\pi=(1/2,1/2,0,0)\), and hence
\[D_{M,M,M}(\pi)=1-2^{-M}.\]
Its edge charge is \(\Theta(\log M)\), while the former dispatcher charge is \(\Theta(M)\). At the same diagonal rank, the audited face construction realizes \(\pi=(1/3,1/3,1/3,0)\) and gives
\[D_{M,M,M}(\pi)=1-2\cdot3^{-M},\]
again with \(\Theta(\log M)\) time and constant workspace versus \(\Theta(M)\) for every former branch. The off-diagonal rank-one audit remains a strict certificate for the common evaluator; on the diagonal its charge is
\[\mathsf R_{M,k,k}=1+2\lceil\log_2M\rceil+2\bar k.\]
If \(k=M+1\), \(\texttt{prop:rank-boundary}\) makes both deterministic rank events certain, so \(\Gamma_{M,\alpha}(w)=0\).

The exact four-level and binary values, their positive gap, and the value \(1-\alpha\) under disjoint support follow from the asymmetric theorem through (1). For the full stochastic model, \(\texttt{thm:common-selector-lp}\) supplies the exact-balance Bonferroni guarantee and \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) supplies the active-arm total-variation bound. Neither follows from \(\Gamma_{M,\alpha}(w)\). The literature comparison is likewise the equal-split specialization: the deliverable is an exact evaluator for the paper-defined deterministic audit functional, not a general discrete-rectangle algorithm, simultaneous-conformal error-control theorem, error-allocation theorem, or structured-volume theorem. Because each branch evaluates the same strict-prefix probability, the common-target, active-arm, pair-audit, empty-library, ordinary-rank, and weighted-orbit semantics are unchanged.