Condition throughout on \(\mathcal T\). Fix an active arm \(a\in\mathcal A_{\boldsymbol\varepsilon}\), and write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). By \(\texttt{lem:orbit-score-factorization}\), a calibration score and the independent target score have conditional laws
\[
\mathsf Q_a=\sum_{O\in\mathcal O_a}q_{a,O}F_{a,O},\qquad
\mathsf P_a=\sum_{O\in\mathcal O_a}p_{a,O}F_{a,O},
\tag{1}
\]
and the \(M\) calibration scores are independent and identically distributed from \(\mathsf Q_a\), independently of the target score from \(\mathsf P_a\).

For a measurable \(f:[0,\infty)\to[0,1]\), put \(h_O=\int f\,dF_{a,O}\) and \(d_O=p_{a,O}-q_{a,O}\). Both orbit-mass vectors are probability vectors, so \(\sum_Od_O=0\). The positive and negative parts of \((d_O)_O\) therefore have common mass
\[
\frac12\sum_{O\in\mathcal O_a}|d_O|=\Delta_a(w).
\]
Since \(0\le h_O\le1\),
\[
\left|\int f\,d(\mathsf P_a-\mathsf Q_a)\right|
=\left|\sum_{O\in\mathcal O_a}d_Oh_O\right|
\le\Delta_a(w).
\tag{2}
\]
Thus the orbit-specific score kernel contracts total variation.

On an auxiliary product extension, let \(S'_{0,a}\sim\mathsf Q_a\) be independent of the calibration scores. Append the independent continuous tie-breakers prescribed by \(\texttt{def:rank-inversion}\). With \(N=M+1\), the augmented rank of \(S'_{0,a}\) among the \(N\) independent and identically distributed augmented scores is uniform on \(\{1,\ldots,N\}\). Because \(a\) is active, \(k_a\le M\). If the unaugmented comparison score exceeds the reported \(k_a\)-th calibration order statistic, its augmented rank exceeds \(k_a\). Hence
\[
\Pr\{S'_{0,a}>r_{a,(k_a)}\mid\mathcal T\}
\le\frac{N-k_a}{N}=\rho_{M,\varepsilon_a}.
\tag{3}
\]
For each fixed calibration realization, apply (2) to \(f(s)=\mathbf1\{s>r_{a,(k_a)}\}\). Independence of the actual target from the calibration sample and (3) give
\[
\Pr_P\{S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}
\le\rho_{M,\varepsilon_a}+\Delta_a(w).
\tag{4}
\]
The score definition and bounded outcomes imply
\[
\{Y_{0T}(a)\notin I^{\boldsymbol\varepsilon}_{a,w}\}
\subseteq\{S_{0,a}>r_{a,(k_a)}\}.
\tag{5}
\]

Now fix a boundary arm \(a\notin\mathcal A_{\boldsymbol\varepsilon}\). Since \(k_a\in\{1,\ldots,M+1\}\), nonmembership means \(k_a=M+1\). By \(\texttt{prop:asymmetric-rank-boundary}\),
\[
I^{\boldsymbol\varepsilon}_{a,w}=[-K,K].
\tag{6}
\]
The bounded-outcome assumption gives \(Y_{0T}(a)\in[-K,K]\) surely. Thus the failure event in (5) is empty for a boundary arm; no rank or imbalance comparison is needed there.

If every active-arm outcome lies in its interval, then (6) supplies the same conclusion for every inactive arm, and hence
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)
\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}
=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{7}
\]
The union bound over only \(a\in\mathcal A_{\boldsymbol\varepsilon}\), which uses no cross-arm independence, and (4)--(7) yield
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right\}
\ge 1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\bigl(\rho_{M,\varepsilon_a}+\Delta_a(w)\bigr).
\tag{8}
\]
Taking the maximum with zero proves the main display.

For every arm, \(\sum_O\delta_{a,O}(w)=0\). The positive and negative coordinate sums therefore both equal \(\Delta_a(w)\), which proves \(|\delta_{a,O}(w)|\le\Delta_a(w)\). The staircase and its coordinate elbows follow from \(\texttt{lem:armwise-finite-rank-staircase}\). If exactly one rank is \(M+1\), (8) contains only the other arm. If both ranks equal \(M+1\), the active set is empty; \(\texttt{prop:asymmetric-rank-boundary}\) gives \(\mathcal C^{\boldsymbol\varepsilon}_w=[-2K,2K]\), which contains the bounded effect surely, and (8) equals one. On the equal-split diagonal the ranks coincide. When \(k\le M\), both arms are active and the stated symmetric expression follows; when \(k=M+1\), both are inactive and coverage is one.