For any \(w\in\Delta(\mathcal H)\), the row definitions give \[(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=q^{\mathrm{obs}}_{w,a}(O).\tag{1}\] Hence \(Aw=b_{\mathrm{LP}}\) is exactly joint orbit balance. When \(\mathcal H\ne\varnothing\), the set of all \(Aw\) with \(w\in\Delta(\mathcal H)\) is precisely \(\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\), proving the convex-hull and LP equivalences. If \(\mathcal H=\varnothing\), the adopted simplex is empty and the equality constraint \(\sum_{h\in\varnothing}w_h=1\) reads \(0=1\); the nonexistence conclusions then follow from the definitions. If the nonempty convex hull \(C\) does not contain \(b_{\mathrm{LP}}\), let \(c_\star\in C\) minimize Euclidean distance to \(b_{\mathrm{LP}}\) and put \(x=b_{\mathrm{LP}}-c_\star\ne0\). For \(c\in C\), differentiating the squared distance along \(c_\star+t(c-c_\star)\) at \(t=0+\) gives \(x^\top(c-c_\star)\le0\). Therefore \[x^\top b_{\mathrm{LP}}-\sup_{c\in C}x^\top c\ge\|x\|_2^2>0,\] which is the asserted strict Farkas hyperplane.
Now fix a feasible \(w\). By \(\texttt{thm:orbit-balance-iff}\), conditional on \(\mathcal T\), the \(M+1\) scores in each arm are iid. Append independent continuous uniforms and rank score--uniform pairs lexicographically. If \(k_a\le M\), the strict event \(S_{0,a}>r_{a,(k_a)}\) implies that the target pair has rank greater than \(k_a\). Its rank is uniform on \(\{1,\ldots,M+1\}\), whence \[\Pr(S_{0,a}>r_{a,(k_a)}\mid\mathcal T)\le\frac{M+1-k_a}{M+1}.\tag{2}\] If \(k_a=M+1\), the threshold is \(+\infty\) and (2) remains true with both sides zero. Writing \(N=M+1\), the integer identity \(\lceil N-N\varepsilon_a\rceil=N-\lfloor N\varepsilon_a\rfloor\) gives \[\frac{M+1-k_a}{M+1}=\rho_{M,\varepsilon_a}=\frac{\lfloor N\varepsilon_a\rfloor}{N}\le\varepsilon_a.\tag{3}\]
Because \(Y_{0T}(a)\in[-K,K]\), clipping does not change whether that outcome belongs to its residual interval: \(Y_{0T}(a)\notin I^{\boldsymbol\varepsilon}_{a,w}\) exactly when \(S_{0,a}>r_{a,(k_a)}\). If both arm outcomes are covered, their difference belongs to \(\mathcal C^{\boldsymbol\varepsilon}_w\). The union bound and (2)--(3), without cross-arm independence, yield \[\Pr(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T)\ge1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\ge1-\varepsilon_0-\varepsilon_1\ge1-\alpha.\] On the equal-split diagonal, \(\texttt{def:rank-inversion}\) gives \(k_0=k_1=k\), the stated interval identities, and the symmetric corollary.