Set \(\varepsilon_0=\varepsilon_1=\alpha/2\).  By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,
\]
and by \(\texttt{def:coverage-frontier}\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w). \tag{1}
\]
The exactness and preorder-attainment assertions are therefore the diagonal specialization of \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\).  Explicitly, for \(k\le M\),
\[
s_a(O_{T,a})\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k. \tag{2}
\]
Hence only total preorders matter.  A one-class preorder is represented by score zero; a preorder with \(d_a>1\) ordered classes is represented by assigning \((j-1)K/(d_a-1)\) to class \(j\).  This proves finite attainment over the stated score class without asserting law-level sharpness.

The coherent evaluator uses the unchanged probability objects
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z) \tag{3}
\]
and
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}. \tag{4}
\]
For each preorder \(C\), prefix tables of (3) give exact vectors \(\pi^C(j,\ell)\), while the pushforward of (4) supplies the local coherent weights
\[
\omega_C(\pi)=\sum_{(j,\ell):\pi^C(j,\ell)=\pi}P_T^C(j,\ell). \tag{5}
\]
Consequently the rank-event probability is
\[
\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k,k}(\pi). \tag{6}
\]
With \(\Pi_\star=\bigcup_C\Pi_C\) and \(G=|\Pi_\star|\), the exact key is
\[
(M,k,k,\pi_{00},\pi_{01},\pi_{10}),\qquad
\pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10}. \tag{7}
\]
Neither \(C\) nor the local weight occurs in the evaluator.  Thus the recurrence is run once for every one of the \(G\) keys, global lookup costs \(O((\sum_CU_C)\log(1+G))\), and the unchanged construction and grouping costs give the two displayed time bounds and the displayed \(O(m_0m_1+L+k^2+U_{\max}+G)\) memory bound.

The exact multinomial alternative also specializes diagonally.  Put \(\mathsf T=\mathsf T_{M,k,k}\), partition \(\Pi_\star=\Pi_{\mathrm{MS}}\sqcup\Pi_{\mathrm{DP}}\), and let \(\mathsf B\) be the symmetric theorem's non-evaluator instance-adaptive terms.  By \(\texttt{lem:four-cell-multinomial-sum-alternative}\), the selected-branch charge is
\[
O\!\left(
\mathsf B+M+\sum_{\pi\in\Pi_{\mathrm{MS}}}(M+\mathsf T)
+|\Pi_{\mathrm{DP}}|Mk^2
\right), \tag{8}
\]
and time selection yields
\[
O\!\left(\mathsf B+M+G\min\{M+\mathsf T,Mk^2\}\right). \tag{9}
\]
The \(O(M)\) factorial table is shared once, the four probability-specific power tables are rebuilt for each multinomial key, and keys are processed sequentially.  Conditional workspace is \(O(M)\) for the multinomial sum and \(O(k^2)\) for the rolling recurrence; the valid unconditional hybrid memory is
\[
O(m_0m_1+L+U_{\max}+G+\max\{M,k^2\}), \tag{10}
\]
not an independent minimum.  Taking every key through the recurrence recovers the formal recurrence-only bounds in the theorem.  Equations (3)--(7) are unchanged under both evaluators.

If \(k=M+1\), both rank events are certain, so
\[
\Gamma_{M,\alpha}(w)=[(1-\alpha)-1]_+=0. \tag{11}
\]
The four-pair construction in the asymmetric theorem has \(M=3\), \(\alpha=1/2\), and equal arm budgets \(1/4\), so it is on the diagonal (1).  Its four-level objective, largest binary objective, and difference are
\[
\frac{24957}{160000},\qquad
\frac{759109}{5000000},\qquad
\frac{83189}{20000000}>0. \tag{12}
\]
Thus binary maps need not attain the symmetric frontier.  Under disjoint target and calibration orbit support in arm \(a\) with \(k\le M\), assign score \(K\) on the target-supported arm-\(a\) orbits and zero on the calibration-supported orbits, with the other-arm score identically zero.  The joint rank event has probability zero, and therefore
\[
\Gamma_{M,\alpha}(w)=1-\alpha. \tag{13}
\]
This proves every symmetric assertion.