Let \(N_{xy}\) be the number of the \(M\) draws equal to \((x,y)\), and put \(R=N_{10}+N_{11}\) and \(S=N_{01}+N_{11}\). If \(R=r\), \(S=s\), and \(N_{11}=t\), then necessarily
\[
(N_{00},N_{01},N_{10},N_{11})=(M-r-s+t,s-t,r-t,t).
\tag{1}
\]
Conversely, (1) is a nonnegative integer vector of total \(M\) with margins \((r,s)\) exactly when
\[
\max\{0,r+s-M\}\le t\le\min\{r,s\}.
\tag{2}
\]
The multinomial probability of (1) is
\[
\frac{M!}{(M-r-s+t)!(s-t)!(r-t)!t!}
\pi_{00}^{M-r-s+t}\pi_{01}^{s-t}\pi_{10}^{r-t}\pi_{11}^{t}.
\tag{3}
\]
Summing (3) over (2), and then over \(0\le r<k_0\) and \(0\le s<k_1\), proves the displayed formula. The conventions \(0^0=1\) and \(0^j=0\) for \(j>0\) make (3) valid on every face of the simplex. For each \((r,s)\), the number of feasible \(t\)'s is at most \(\min\{r,s\}+1\le\min\{k_0,k_1\}\), whence
\[
\mathsf T_{M,k_0,k_1}\le k_0k_1\min\{k_0,k_1\}.
\tag{4}
\]
Precomputing the factorials through \(M!\) takes \(O(M)\) arithmetic operations. For a fixed key, repeated multiplication constructs the four power tables in \(O(M)\) operations and \(O(M)\) memory, after which each feasible summand in (3) costs constant time. This proves the multinomial charge. The elementary two-count convolution, retaining only \(r<k_0\) and \(s<k_1\), is exact by induction on the number of draws and uses \(O(Mk_0k_1)\) operations and \(O(k_0k_1)\) rolling memory. Thus the per-key minimum and branch-conditional memory bounds follow.

It remains to justify the prepass and aggregate charge. Let \(\pi\in\Pi_{\mathrm{vert}}\). Since the four nonnegative cells sum to one, the cell \((x,y)\) satisfying \(\pi_{xy}=1\) is unique and every other cell is zero. Every draw therefore equals \((x,y)\) almost surely, so
\[
(R,S)=(Mx,My)\quad\text{almost surely},
\qquad
D_{M,k_0,k_1}(\pi)=\mathbf 1\{Mx<k_0\ \text{and}\ My<k_1\}.
\tag{5}
\]
Checking four cells and the two inequalities in (5) costs \(O(1)\) time and workspace and uses neither factorials nor power tables. Apply this test before partitioning the remaining keys into \(\Pi_{\mathrm{MS}}\) and \(\Pi_{\mathrm{DP}}\). Sequentially summing their certified charges gives
\[
O\!\left(|\Pi_{\mathrm{vert}}|+M\mathbf 1\{\Pi_{\mathrm{MS}}\ne\varnothing\}+\sum_{\pi\in\Pi_{\mathrm{MS}}}(M+\mathsf T_{M,k_0,k_1})+|\Pi_{\mathrm{DP}}|Mk_0k_1\right).
\tag{6}
\]
The factorial table in (6) is built if and only if the nonvertex multinomial branch is used. Only one branch workspace is live at a time, and retaining one answer per key adds \(O(|\Pi|)\) storage, proving the proposed memory statement. Coordinate complementation only permutes the four cells, so it preserves vertex status; consequently the same prepass is valid before the downstream corner-oriented three-way dispatcher.