Let \(N_{xy}\) be the number of the \(M\) draws equal to \((x,y)\), and let \(R=N_{10}+N_{11}\) and \(S=N_{01}+N_{11}\). For fixed margins \(R=r\) and \(S=s\), put \(t=N_{11}\). The margin equations force
\[
(N_{00},N_{01},N_{10},N_{11})=(M-r-s+t,s-t,r-t,t).
\tag{1}
\]
Conversely, the vector in (1) is a nonnegative integer vector with total \(M\) and margins \((r,s)\) if and only if
\[
\max\{0,r+s-M\}\le t\le\min\{r,s\}.
\tag{2}
\]
The multinomial probability of (1) is
\[
\frac{M!}{(M-r-s+t)!(s-t)!(r-t)!t!}\pi_{00}^{M-r-s+t}\pi_{01}^{s-t}\pi_{10}^{r-t}\pi_{11}^{t}.
\tag{3}
\]
Summing (3) over (2), and then over \(0\le r<k_0\) and \(0\le s<k_1\), proves the displayed formula for \(Q_{M,k_0,k_1}(\pi)\). The conventions concerning zero powers make (3) valid on every face of the probability simplex. For a fixed \((r,s)\), the number of feasible values of \(t\) is the displayed positive part and is at most \(\min\{r,s\}+1\le\min\{k_0,k_1\}\). There are \(k_0k_1\) margin pairs, so
\[
\mathsf T_{M,k_0,k_1}\le k_0k_1\min\{k_0,k_1\}.
\tag{4}
\]
Factorials through \(M!\) are precomputed once in \(O(M)\) arithmetic operations. For a given exact key, the four power tables are rebuilt by repeated multiplication in \(O(M)\) operations and \(O(M)\) memory. Every summand in (3) is then obtained in constant time, proving the stated multinomial charge \(O(M+\mathsf T_{M,k_0,k_1})\). The lower-left orientation of \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) gives the stated exact recurrence alternative with at most \(O(Mk_0k_1)\) time and \(O(k_0k_1)\) memory. Choosing the cheaper time branch proves the hybrid and aggregate bounds printed in the statement.

We now prove the directive-level corner refinement. Define
\[
h_a=M-k_a+1,\qquad \bar k_a=\min\{k_a,h_a\},\qquad
C_{M,k_0,k_1}=\sum_{i=0}^{M-1}\min\{\bar k_0,i+1\}\min\{\bar k_1,i+1\}.
\tag{5}
\]
Complement coordinate \(a\) precisely when \(h_a<k_a\). This merely permutes the four atoms of \(\pi\); call the resulting law \(\pi^\sigma\). The selected corner event is a retained lower-left rectangle with thresholds \((\bar k_0,\bar k_1)\). Applying the already proved multinomial formula to \(\pi^\sigma\) evaluates that corner in
\[
O\!\left(M+\mathsf T_{M,\bar k_0,\bar k_1}\right)
\tag{6}
\]
operations and \(O(M)\) workspace. By \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), the desired untransformed lower--lower probability is recovered exactly as one of
\[
J_{LL},\quad \Pr\{R<k_0\}-J_{LU},\quad \Pr\{S<k_1\}-J_{UL},
\tag{7}
\]
or
\[
1-\Pr\{R\ge k_0\}-\Pr\{S\ge k_1\}+J_{UU}.
\tag{8}
\]
The needed marginals are binomial laws with success probabilities \(\pi_{10}+\pi_{11}\) and \(\pi_{01}+\pi_{11}\). The same corner-oriented lemma evaluates them in \(O(\log M+\bar k_a)\) operations and constant memory, so their cost is absorbed by the \(O(M)\) term in (6). Thus the corner-oriented multinomial branch has precisely the charge in (6), including when some cells vanish. The corner recurrence from the same lemma costs \(O(C_{M,k_0,k_1})\) operations and \(O(\bar k_0\bar k_1)\) workspace. Hence the sharpened per-key hybrid is
\[
O\!\left(\min\left\{M+\mathsf T_{M,\bar k_0,\bar k_1},C_{M,k_0,k_1}\right\}\right),
\tag{9}
\]
with conditional workspaces \(O(M)\) and \(O(\bar k_0\bar k_1)\), respectively. For a finite exact-key set \(\Pi=\Pi_{\mathrm{MS}}\sqcup\Pi_{\mathrm{DP}}\), sequential processing therefore costs
\[
O\!\left(M+\sum_{\pi\in\Pi_{\mathrm{MS}}}\{M+\mathsf T_{M,\bar k_0,\bar k_1}\}+|\Pi_{\mathrm{DP}}|C_{M,k_0,k_1}\right)
\tag{10}
\]
and uses \(O(|\Pi|+\max\{M,\bar k_0\bar k_1\})\) memory when one answer per key is retained. The factorial table in (10) is shared, but the four probability-specific power tables are rebuilt for every multinomial key. Finally, \(\bar k_a\le k_a\), \(\mathsf T_{M,\bar k_0,\bar k_1}\le\mathsf T_{M,k_0,k_1}\), and
\[
C_{M,k_0,k_1}\le M\bar k_0\bar k_1\le Mk_0k_1.
\tag{11}
\]
Thus (9)--(11) imply all of the coarser resource bounds in the formal statement and establish the required corner-oriented replacement.