Write \(b=b_{\mathrm{LP}}\), \(A_h=A_{\cdot h}\), \(r(w)=Aw-b\), and \[\Phi(w)=\frac12\sum_{a=0}^1\sum_O|r_{a,O}(w)|,\qquad \Phi_{\mathcal A}(w)=\frac12\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\sum_O|r_{a,O}(w)|.\] The constraints \(-t_j\le r_j(w)\le t_j\), \(t_j\ge0\), minimize at \(t_j=|r_j(w)|\). Thus the displayed full and active-row programs have values \(D_*\) and \(D_{*,\mathcal A}\). Since the finite nonempty simplex is compact and both objectives are continuous, both minima and both optimizer sets are attained.
We derive the full dual directly. Let \(C=\operatorname{conv}\{A_h:h\in\mathcal H\}\). Then \[D_*=\min_{c\in C}\frac12\|c-b\|_1.\tag{1}\] For \(\|y\|_\infty\le1/2\) and \(c=Aw\), \[\min_hy^\top A_h-y^\top b\le y^\top(c-b)\le\frac12\|c-b\|_1,\tag{2}\] so the proposed dual is at most \(D_*\). Suppose \(D_*>0\) and fix \(0<d<D_*\). The compact convex set \(C_d=C+\{u:\|u\|_1\le2d\}\) does not contain \(b\). Let \(z_d\) minimize Euclidean distance from \(b\) to \(C_d\), and put \(q_d=b-z_d\ne0\). Minimality along \(z_d+t(z-z_d)\) gives \(q_d^\top(z-z_d)\le0\) for all \(z\in C_d\). Hence \[q_d^\top b-\sup_{z\in C_d}q_d^\top z\ge\|q_d\|_2^2>0.\tag{3}\] The support function of the Minkowski sum equals \(\max_hq_d^\top A_h+2d\|q_d\|_\infty\). Set \(x_d=q_d/(2\|q_d\|_\infty)\) and \(y_d=-x_d\). Dividing (3) gives \[\min_hy_d^\top A_h-y_d^\top b=x_d^\top b-\max_hx_d^\top A_h>d,\qquad\|y_d\|_\infty=1/2.\] Letting \(d\uparrow D_*\) and using (2) proves equality. If \(D_*=0\), \(y=0\) proves equality. The dual cube is compact and its objective is continuous, so the maximum is attained. Repeating the same argument after projecting onto active rows, then extending the dual vector by zero, proves the active-row dual. If there are no active rows, both sides are identically zero.
For any full dual maximizer \(y^*\), \[\min_h(y^*)^\top A_h-(y^*)^\top b=D_*.\] If \(D_*>0\), \(x^*=-y^*\) satisfies \[(x^*)^\top b-\max_h(x^*)^\top A_h=D_*>0,\] so it separates \(b\) from the convex hull with the asserted margin. Primal attainment gives \(D_*=0\) exactly when some \(w\) satisfies \(Aw=b\), which is feasibility of the joint-balance program. The identical argument on active rows proves that \(D_{*,\mathcal A}=0\) exactly when one selector balances every active row; omitted rows are unrestricted.
The coefficients are known before scores: \(b\) is fixed by the target rule, while \(A_{(a,O),h}=\sum_{u\in O}\sum_z\nu(z)\kappa_{h,a}(u\mid z)\). By \(\texttt{lem:null-support-kernel-extensions}\), arbitrary total extensions off \(\operatorname{supp}(\nu)\) cannot alter these coefficients. Deterministic tie-breaking therefore makes \(w_*\) and \(w_{*,\mathcal A}\) prespecified. Moreover, \[\frac12\sum_O|(Aw-b)_{a,O}|=\Delta_a(w).\tag{4}\] Applying \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) to \(w_{*,\mathcal A}\) and using (4) proves \[\Pr_P(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_{*,\mathcal A}}\mid\mathcal T)\ge\max\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\rho_{M,\varepsilon_a}-D_{*,\mathcal A}\right\}.\tag{5}\] Optimality gives \(D_{*,\mathcal A}\le\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w)\) for every fixed \(w\). Monotonicity of \(x\mapsto\max\{0,x\}\) proves weak dominance; if the imbalance inequality is strict and the optimized untruncated bound is positive, the resulting numerical bound is strictly larger.
With one boundary arm, only the other arm's rows remain. With no active arms, the objective is empty, every mixture is optimal, and coverage is one by \(\texttt{prop:asymmetric-rank-boundary}\). On the equal-split finite-rank diagonal all rows are active, so the active and full optima coincide; at the two-boundary elbow coverage is one. Finally, applying the active-arm bound to any \(w_*\in\mathcal W_*\) and adding the nonnegative omitted rank and gap penalties gives \[\Pr_P(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T)\ge\max\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\}.\] Since \(D_*\le\Delta_0(w)+\Delta_1(w)\), its weak and strict dominance claims follow identically. The empty-library conclusion is exactly the convention in \(\texttt{def:minimum-imbalance-common-selector}\).