Condition throughout on \(\mathcal T\), so the trained maps are fixed. We first prove the feasibility equivalence. For \(h\in\mathcal H\), write \(A_{\cdot h}\) for column \(h\) of \(A\). If \(w\in\Delta(\mathcal H)\), then the definitions of \(A\) and the integrated mixture law give, for every row \((a,O)\),
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=\sum_{u\in O}q^{\mathrm{obs}}_{w,a}(u)=q^{\mathrm{obs}}_{w,a}(O).
\tag{1}
\]
On the other hand,
\[
(b_{\mathrm{LP}})_{a,O}=\sum_{u\in O}q_{\mathrm{tar},a}(u)=q_{\mathrm{tar},a}(O).
\tag{2}
\]
Thus \(Aw=b_{\mathrm{LP}}\) is equivalent to joint orbit balance. Moreover,
\[
\{Aw:w\in\Delta(\mathcal H)\}=\left\{\sum_{h\in\mathcal H}w_hA_{\cdot h}:w_h\ge0,\ \sum_{h\in\mathcal H}w_h=1\right\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\tag{3}
\]
Equations \((1)\)--\((3)\) prove both the convex-hull characterization and its equivalence to the constraints in \(\texttt{def:common-selector-feasibility-lp}\). This also covers \(\mathcal H=\varnothing\): the simplex and convex hull are empty, while the normalization equation is inconsistent.

For completeness, suppose first that \(\mathcal H\neq\varnothing\) and the condition fails. Let
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\]
The set \(C\) is compact because \(\mathcal H\) is finite. Choose \(c^*\in C\) minimizing \(\lVert b_{\mathrm{LP}}-c\rVert_2\), and set \(y=b_{\mathrm{LP}}-c^*\neq0\). For \(c\in C\) and \(t\in(0,1]\), convexity gives \(c^*+t(c-c^*)\in C\). Hence minimality of \(c^*\) implies
\[
0\le \lVert b_{\mathrm{LP}}-c^*-t(c-c^*)\rVert_2^2-\lVert b_{\mathrm{LP}}-c^*\rVert_2^2=-2t y^\top(c-c^*)+t^2\lVert c-c^*\rVert_2^2.
\]
After division by \(t\) and passage to \(t\downarrow0\), one obtains \(y^\top c\le y^\top c^*\) for all \(c\in C\). Therefore
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\lVert y\rVert_2^2>y^\top c^*=\sup_{c\in C}y^\top c=\max_{h\in\mathcal H}y^\top A_{\cdot h}.
\tag{4}
\]
Thus \(y\), together with any scalar strictly between the two sides of \((4)\), is a strict separating hyperplane, equivalently a Farkas infeasibility certificate. If \(\mathcal H=\varnothing\), infeasibility is already certified by the contradictory normalization equation, and separation from the empty convex hull is vacuous.

Now fix one feasible common vector \(w\), put \(N=M+1\), and fix the prespecified budget \(\boldsymbol\varepsilon=(\varepsilon_0,\varepsilon_1)\) with \(\varepsilon_a>0\) and \(\varepsilon_0+\varepsilon_1\le\alpha\). Since \(0<\alpha<1\), one has \(0<\varepsilon_a<1\), and therefore
\[
k_a=\left\lceil N(1-\varepsilon_a)\right\rceil\in\{1,\ldots,N\}.
\tag{5}
\]
By \((1)\)--\((2)\), feasibility of \(w\) gives joint orbit balance. The theorem \(\texttt{thm:orbit-balance-iff}\), using the iid arrays, the one independent common target, and the selector auxiliary draws, then implies that for each fixed arm \(a\),
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are iid conditional on \(\mathcal T\). Append independent \(\operatorname{Unif}(0,1)\) variables \(V_{0,a},\ldots,V_{M,a}\) only to break ties lexicographically. The \(N\) pairs \((S_{i,a},V_{i,a})\) are conditionally iid and almost surely distinct. Consequently, exchangeability makes the lexicographic rank \(R_{0,a}\) of the target pair uniform on \(\{1,\ldots,N\}\): for each rank, all \(N\) indices have the same conditional probability of occupying that rank, and those probabilities sum to one.

If \(k_a\le M\) and \(S_{0,a}>r_{a,(k_a)}\), at least \(k_a\) calibration scores are strictly smaller than \(S_{0,a}\), whence \(R_{0,a}>k_a\). If \(k_a=N=M+1\), the definition of rank inversion sets \(r_{a,(k_a)}=+\infty\), so the exceedance event is empty. Both cases therefore give
\[
\Pr\!\left(S_{0,a}>r_{a,(k_a)}\mid\mathcal T\right)\le\Pr(R_{0,a}>k_a\mid\mathcal T)=\frac{N-k_a}{N}.
\tag{6}
\]
The integer identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\), with \(x=N\varepsilon_a\), and \(\texttt{def:finite-rank-error}\) yield
\[
\frac{N-k_a}{N}=\frac{\lfloor N\varepsilon_a\rfloor}{N}=\rho_{M,\varepsilon_a}\le\varepsilon_a.
\tag{7}
\]
This includes the boundary case \(k_a=N\), in which the first two quantities in \((7)\) vanish.

The arm-specific interval is
\[
I^{\boldsymbol\varepsilon}_{a,w}=\left[\widehat m_a(X_{0T})-r_{a,(k_a)},\widehat m_a(X_{0T})+r_{a,(k_a)}\right]\cap[-K,K].
\tag{8}
\]
By \(\texttt{ass:bounded-potential-outcomes}\), \(Y_{0T}(a)\in[-K,K]\). Thus, also when the radius is \(+\infty\), clipping in \((8)\) gives the exact equivalence
\[
Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w}\quad\Longleftrightarrow\quad |Y_{0T}(a)-\widehat m_a(X_{0T})|\le r_{a,(k_a)}\quad\Longleftrightarrow\quad S_{0,a}\le r_{a,(k_a)}.
\tag{9}
\]
On the intersection of the two events in \((9)\), set subtraction gives
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\]
The conditional union bound, which uses no independence between the arms, and \((6)\)--\((7)\) now imply the exact finite-rank guarantee
\[
\begin{aligned}
\Pr\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right)
&\ge 1-\sum_{a=0}^1\Pr\!\left(S_{0,a}>r_{a,(k_a)}\mid\mathcal T\right)\\
&\ge 1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\\
&\ge 1-\varepsilon_0-\varepsilon_1\ge1-\alpha.
\end{aligned}
\tag{10}
\]
The same common \(T\) and common feasible \(w\) are used in both arms throughout; possible cross-arm dependence is absorbed by the union bound.

Finally, if \(\varepsilon_0=\varepsilon_1=\alpha/2\), then \(k_0=k_1=\lceil(M+1)(1-\alpha/2)\rceil=k\), \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\), \(r_{a,(k_a)}=r_{a,(k)}\), \(I^{\boldsymbol\varepsilon}_{a,w}=I_{a,w}\), and \(\mathcal C^{\boldsymbol\varepsilon}_w=\mathcal C_w\). Hence \((6)\)--\((10)\) specialize to
\[
\Pr(S_{0,a}>r_{a,(k)}\mid\mathcal T)\le\frac{M+1-k}{M+1}=\rho_{M,\alpha}\le\frac{\alpha}{2},\qquad \Pr(\tau_T\in\mathcal C_w\mid\mathcal T)\ge1-2\rho_{M,\alpha}\ge1-\alpha,
\]
which is the equal-split statement as a corollary.