Let \(N_{xy}\) count draws equal to \((x,y)\), and put
\[
R=N_{10}+N_{11},\qquad S=N_{01}+N_{11}.
\]
If \(R=r\), \(S=s\), and \(N_{11}=t\), the four counts must be
\[
(N_{00},N_{01},N_{10},N_{11})
=(M-r-s+t,s-t,r-t,t).
\tag{1}
\]
Conversely, (1) is a nonnegative integer vector of total \(M\) exactly when
\[
\max\{0,r+s-M\}\le t\le\min\{r,s\}.
\tag{2}
\]
Its multinomial probability is the summand displayed in the proposed statement. Summing over (2), then over \(r<k_0\) and \(s<k_1\), proves the formula. The zero-power conventions make it valid on every simplex face.

For each \((r,s)\), the number of feasible \(t\)'s is at most \(\min\{r,s\}+1\le\min\{k_0,k_1\}\), so
\[
\mathsf T_{M,k_0,k_1}\le k_0k_1\min\{k_0,k_1\}.
\tag{3}
\]
Factorials through \(M!\) require \(O(M)\) shared arithmetic and memory. For each key, four probability-specific power tables require \(O(M)\) time and memory, and each feasible term thereafter costs constant arithmetic. This proves the multinomial charge. The rolling alternative follows from the retained convolution in \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), giving its stated charge and branch-conditional memory.

It remains to justify the refined partition. A support-one key has deterministic counts by the vertex calculation in \(\texttt{def:simplex-vertex-key-prepass}\). A support-two key has, by the affine-binomial calculation there, the exact interval probability
\[
\Pr\{L_\pi\le\operatorname{Bin}(M,p)\le U_\pi\}
\]
with charge \(\mathsf E_M(\pi)\) and constant workspace. Therefore neither kind needs formula (1) or a two-count recurrence. Only support-at-least-three keys are assigned to \(\Pi_{\mathrm{MS}}\) or \(\Pi_{\mathrm{DP}}\). Adding the certified charges over sequentially processed keys gives the displayed operation bound. Factorials are needed exactly when \(\Pi_{\mathrm{MS}}\) is nonempty; edge evaluation uses no table of length depending on \(M\). Retaining one answer per key and taking the maximum live branch workspace yields the stated memory bound. Since the later positive-corner branch is another exact evaluator of the same support-at-least-three key, the vertex-and-edge prepass may precede that three-way comparison without changing any probability.