For each arm, two score maps induce the same event in \(\texttt{def:coverage-frontier}\) whenever they induce the same weak ordering of the finite set \(\mathcal O\): the event uses only comparisons of a target score with an order statistic of calibration scores. Every weak ordering is an ordered partition, and there are finitely many ordered partitions of a finite set. Conversely, if an ordered partition has \(d\) nonempty levels, it can be represented by the values \(0,K/(d-1),\ldots,K\) when \(d>1\), and by zero when \(d=1\). Thus the objective is constant on each pair of armwise total preorders and its maximum is attained after a finite enumeration. Each representative uses at most \(|\mathcal O|\) levels.

The two boundary claims follow directly. Under disjoint support and \(k\le M\), choose the adverse-arm map to be \(K\) on target-supported orbits and zero on calibration-supported orbits, and choose the other-arm map to be zero. The joint coverage event then has probability zero, so \(\Gamma_{M,\alpha}(w)=1-\alpha\), its largest possible value. If \(k=M+1\), then \(Q_k=+\infty\) for both arms, the joint coverage event has probability one for every score pair, and \(\Gamma_{M,\alpha}(w)=0\).

It remains to explain why the stronger binary claim must be removed. Consider four pair blocks with group \(S_2^4\), one treated member per pair under the invariant fair within-pair randomization, and selectors that independently choose a block in each arm and then take that block's unique observed arm member. Let the common target's block probabilities and each calibration selector's block probabilities be \[p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\qquad q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right).\tag{5}\] These kernels are observable and equivariant, and the auxiliary draws make the two arms' calibration block sequences independent. Take \(M=3\), \(\alpha=1/2\), so \(k=3\). Set \(s_0\equiv0\), and order the arm-\(1\) blocks as \(1<3<2<4\), represented, for example, by \(0,K/3,2K/3,K\). Since failure means that all three calibration scores are strictly below the target score, its probability is \[F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.\tag{6}\] The resulting frontier objective is \[F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.\tag{7}\]

For binary maps, let \(H_a\subseteq\{1,2,3,4\}\) be the set assigned score \(K\) in arm \(a\), and put \(A_a=(1-q(H_a))^3\). Conditional independence of the two arm selectors gives the exact union-of-failures probability \[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\tag{8}\] Evaluating (8) over the \(16^2\) subset pairs is a finite exact certificate. To display the complete check compactly, in the row order \[\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,\] the numerators of \(\max_{H_1}F_{\mathrm{bin}}(H_0,H_1)\), over the common denominator \(320000000\), are \[164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000.\] Therefore \[\max_{H_0,H_1}F_{\mathrm{bin}}(H_0,H_1)=\frac{3259109}{5000000},\] attained, for example, at \((H_0,H_1)=(\{2,4\},\{3,4\})\). Its largest frontier objective is \(759109/5000000\), and \[\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\] Thus a multilevel score pair is strictly more adverse than every binary pair in this admissible instance. Finite total-preorder enumeration is valid, but universal binary attainment is false.