Fix \(a\in\{0,1\}\) and suppose \(k_a=M+1\). By \(\texttt{def:rank-inversion}\), the reported order statistic is then defined to be \(+\infty\), so
\[
r_{a,(k_a)}=+\infty.
\]
The corresponding un-clipped interval is all of \(\mathbb R\). Therefore the prescribed clipping gives
\[
I^{\boldsymbol\varepsilon}_{a,w}=\mathbb R\cap[-K,K]=[-K,K].
\tag{1}
\]
By \(\texttt{ass:bounded-potential-outcomes}\), \(Y_{0T}(a)\in[-K,K]\) almost surely. Combining this fact with (1) yields the support-clipping implication
\[
\Pr\!\left\{Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w}\mid\mathcal T\right\}=1.
\tag{2}
\]
In particular, a boundary arm cannot cause effect-set miscoverage. More explicitly, if \(k_0=M+1\) and \(k_1\le M\), then the definition of the Minkowski difference and (1) give
\[
\mathcal C^{\boldsymbol\varepsilon}_w=I^{\boldsymbol\varepsilon}_{1,w}-[-K,K].
\tag{3}
\]
Whenever \(Y_{0T}(1)\in I^{\boldsymbol\varepsilon}_{1,w}\), boundedness gives \(Y_{0T}(0)\in[-K,K]\), and hence
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-[-K,K]=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{4}
\]
Thus only the nonboundary arm can fail in this regime. Symmetrically, if \(k_1=M+1\) and \(k_0\le M\), then
\[
\mathcal C^{\boldsymbol\varepsilon}_w=[-K,K]-I^{\boldsymbol\varepsilon}_{0,w},
\tag{5}
\]
and \(Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{0,w}\) implies \(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\).

If both \(k_0=k_1=M+1\), applying (1) to both arms gives
\[
\mathcal C^{\boldsymbol\varepsilon}_w=[-K,K]-[-K,K]=[-2K,2K].
\tag{6}
\]
Again by \(\texttt{ass:bounded-potential-outcomes}\),
\[
-2K\le Y_{0T}(1)-Y_{0T}(0)=\tau_T\le2K
\]
almost surely. Hence (6) has conditional coverage one for every admissible law and every fixed trained predictor map. This also exhibits the two-boundary case as trivial and exact.

Finally, on the symmetric diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\). Consequently either both arms have rank \(M+1\) or neither does; an exactly-one-boundary regime is impossible on that diagonal. When the common rank is \(M+1\), (6) and its coverage conclusion are precisely \(\texttt{prop:rank-boundary}\). This proves every assertion.