First, the claimed rank equivalence is exact. With \(N=M+1\),
\[k\le M\iff \left\lceil N(1-\alpha/2)\right\rceil\le N-1\iff N(1-\alpha/2)\le N-1\iff \alpha\ge\frac{2}{M+1}.\]
Fix the adverse arm \(a\). Under \(\texttt{def:disjoint-orbit-law}\), the potential-outcome array is constant on every \(\mathcal G\)-orbit: its arm-\(a\) value is \(K\) on target-supported arm-\(a\) orbits and zero elsewhere, while every arm-\(1-a\) value is zero. Consequently relabelling by any \(g\in\mathcal G\) leaves the prototype unchanged. The optional uniform group randomization therefore also has an invariant law. All coordinates belong to \(\{0,K\}\subseteq[-K,K]\). Thus the construction satisfies \(\texttt{ass:finite-group-latent-invariance}\) and \(\texttt{ass:bounded-potential-outcomes}\), and hence belongs to \(\mathcal P_{\mathcal G,K}\) by \(\texttt{def:invariant-laws}\). Independent copies of this array, followed by the known assignment law and the stipulated auxiliary selector draws, satisfy the replicated experiment assumptions.

Let \(O\) be an orbit with positive calibration mass \(q^{\mathrm{obs}}_{w,a}(O)>0\). By hypothesis, no such orbit is target-supported. The construction therefore assigns value zero to arm \(a\) on \(O\). Since the predictor is identically zero and an observable selector chooses a realized arm-\(a\) member, every adverse-arm calibration score is zero almost surely. Because \(k\le M\), its \(k\)-th order statistic is therefore
\[r_{a,(k)}=0.\]
Every potential outcome and predictor in arm \(1-a\) is also zero, so all calibration scores in that arm are zero and \(r_{1-a,(k)}=0\). It follows from \(\texttt{def:rank-inversion}\) that both reported arm intervals are the singleton \(\{0\}\), whence
\[\mathcal C_w=\{0\}-\{0\}=\{0\}.\]

By \(\texttt{ass:prespecified-target}\), the selected member lies almost surely in a target-supported orbit. Hence \(Y_{0T}(a)=K\) and \(Y_{0T}(1-a)=0\). If \(a=1\), then \(\tau_T=K\); if \(a=0\), then \(\tau_T=-K\). Since \(K>0\), neither value belongs to \(\{0\}\). Thus
\[\Pr_P(\tau_T\in\mathcal C_w\mid\mathcal T)=0.\]