Condition throughout on \(\mathcal T\). Fix \(a\in\mathcal A_{\boldsymbol\varepsilon}\). By \(\texttt{lem:orbit-score-factorization}\), the calibration and target score laws are
\[
\mathsf Q_a=\sum_{O\in\mathcal O_a}q_{a,O}F_{a,O},\qquad \mathsf P_a=\sum_{O\in\mathcal O_a}p_{a,O}F_{a,O}.
\tag{1}
\]
For measurable \(f:[0,\infty)\to[0,1]\), put \(h_O=\int f\,dF_{a,O}\) and \(d_O=p_{a,O}-q_{a,O}\). Since \(\sum_Od_O=0\), the positive and negative parts each have mass \(\Delta_a(w)\), and therefore
\[
\left|\int f\,d(\mathsf P_a-\mathsf Q_a)\right|=\left|\sum_Od_Oh_O\right|\le\Delta_a(w).
\tag{2}
\]
This is total-variation contraction through the common orbit score kernel. Let \(S'_{0,a}\sim\mathsf Q_a\) be independent of the calibration scores. With the prescribed continuous tie-breakers, its rank among the \(M+1\) iid augmented scores is uniform. Since \(k_a\le M\),
\[
\Pr\{S'_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le\frac{M+1-k_a}{M+1}=\rho_{M,\varepsilon_a}.
\tag{3}
\]
For each calibration realization apply (2) to \(f(s)=\mathbf1\{s>r_{a,(k_a)}\}\). Target independence and (3) give
\[
\Pr_P\{S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le\rho_{M,\varepsilon_a}+\Delta_a(w).
\tag{4}
\]
Because outcomes are in \([-K,K]\), failure of \(Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w}\) implies the event in (4). If \(a\notin\mathcal A_{\boldsymbol\varepsilon}\), then \(k_a=M+1\), and \(\texttt{prop:asymmetric-rank-boundary}\) gives \(I^{\boldsymbol\varepsilon}_{a,w}=[-K,K]\), which contains \(Y_{0T}(a)\) surely. If all active-arm outcomes lie in their intervals, all inactive-arm outcomes do as well, and hence \(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\). A union bound only over active arms yields
\[
\Pr_P\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\}\ge\max\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}(\rho_{M,\varepsilon_a}+\Delta_a(w))\right\}.
\tag{5}
\]
For every arm, \(\sum_O\delta_{a,O}(w)=0\), so each positive or negative coordinate has magnitude at most the common positive-part sum \(\Delta_a(w)\). The staircase assertions follow from \(\texttt{lem:armwise-finite-rank-staircase}\). Exactly one boundary rank leaves only the other arm in (5). Two boundary ranks give an empty sum and, by the boundary proposition, effect set \([-2K,2K]\) and coverage one. On the equal-split diagonal, either both arms are active and (5) is \(\max\{0,1-2\rho_{M,\alpha}-\Delta_0(w)-\Delta_1(w)\}\), or both are boundary arms and coverage is one.