For \(w\in\Delta(\mathcal H)\), define
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|(Aw-b_{\mathrm{LP}})_{a,O}|.
\tag{1}
\]
The row identities in the proof of \(\texttt{thm:common-selector-lp}\) give
\[
d(w)=\frac12\sum_{a=0}^1\sum_{O\in\mathcal O}|\delta_{a,O}(w)|=\Delta_0(w)+\Delta_1(w).
\tag{2}
\]
Because \(\mathcal H\) is finite and nonempty, \(\Delta(\mathcal H)\) is a nonempty compact simplex. The continuous function \(d\) attains its minimum, so \(D_*\) is attained and \(\mathcal W_*\ne\varnothing\).

For fixed \(w\), the two-sided constraints in the displayed absolute-value program are equivalent to
\[
t_{a,O}\ge |(Aw-b_{\mathrm{LP}})_{a,O}|.
\tag{3}
\]
Every feasible \((w,t)\) therefore has objective at least \(d(w)\), while equality in (3) makes its objective exactly \(d(w)\). Hence the primal value is \(D_*\), and its optimizing \(w\)-coordinates are precisely \(\mathcal W_*\).

For the quantitative dual, put
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\},\qquad b=b_{\mathrm{LP}}.
\]
Then
\[
D_*=\min_{c\in C}\frac12\lVert c-b\rVert_1.
\tag{4}
\]
For every \(y\) with \(\lVert y\rVert_\infty\le1/2\) and every \(c\in C\), the dual-norm inequality gives
\[
y^\top(c-b)\le\lVert y\rVert_\infty\lVert c-b\rVert_1\le\frac12\lVert c-b\rVert_1.
\tag{5}
\]
Taking the minimum over \(c\) and then the maximum over \(y\) proves weak duality. If \(D_*=0\), the feasible vector \(y=0\) proves equality and attainment. Suppose \(D_*>0\). For \(n\ge2\), set \(r_n=(1-1/n)D_*\) and
\[
B_n=\{x:\tfrac12\lVert x-b\rVert_1\le r_n\}.
\]
By (4), the nonempty compact convex sets \(B_n\) and \(C\) are disjoint. Choose a Euclidean closest pair \((c_n,x_n)\in C\times B_n\) and put \(v_n=c_n-x_n\ne0\). Directional differentiation along line segments in the two convex sets gives
\[
\min_{c\in C}v_n^\top c=v_n^\top c_n>v_n^\top x_n=\max_{x\in B_n}v_n^\top x.
\tag{6}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). Then \(\lVert y_n\rVert_\infty=1/2\). The support function of \(B_n\) is
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b+2r_n\lVert y_n\rVert_\infty=y_n^\top b+r_n.
\tag{7}
\]
Indeed, the dual-norm inequality gives the upper bound, and equality is attained by moving from \(b\) a signed \(\ell_1\)-distance \(2r_n\) in a coordinate on which \(|(y_n)_j|=1/2\). Equations (6)--(7) imply
\[
\min_{c\in C}y_n^\top c-y_n^\top b>r_n.
\tag{8}
\]
The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact, so a subsequence converges to some \(y_*\). Since \(\mathcal H\) is finite,
\[
\min_{c\in C}y^\top c=\min_{h\in\mathcal H}y^\top A_{\cdot h}
\tag{9}
\]
is continuous in \(y\). Letting \(n\to\infty\) in (8) and combining with weak duality proves the attained identity
\[
D_*=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.
\tag{10}
\]
If \(D_*>0\) and \(y\) maximizes (10), then \(y^\top A_{\cdot h}\ge y^\top b_{\mathrm{LP}}+D_*\) for every \(h\). Thus \(z=-y\) satisfies
\[
z^\top b_{\mathrm{LP}}\ge\max_{h\in\mathcal H}z^\top A_{\cdot h}+D_*,
\tag{11}
\]
which is the asserted Farkas separating direction with margin \(D_*\).

By nonnegativity of (1), \(D_*=0\) exactly when some \(w\in\Delta(\mathcal H)\) satisfies \(Aw=b_{\mathrm{LP}}\). The common-selector theorem identifies this with feasibility of the exact joint-balance LP. Every entry of \(A\) is computed from the known assignment law and selector kernels, and \(b_{\mathrm{LP}}\) is computed from the prespecified target rule. Thus the finite LP computes an optimizer \(w_*\) before any scores are observed, making it prespecified.

Fix \(w_*\in\mathcal W_*\), condition on \(\mathcal T\), and apply \(\texttt{prop:asymmetric-finite-rank-orbit-gap-bound}\). By (2) and optimality, \(\Delta_0(w_*)+\Delta_1(w_*)=D_*\), whence
\[
\Pr_P\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_*}\mid\mathcal T\right)\ge\max\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\right\}.
\tag{12}
\]
For arbitrary \(w\in\Delta(\mathcal H)\), optimality gives \(D_*\le\Delta_0(w)+\Delta_1(w)\). Since \(x\mapsto\max\{0,c-x\}\) is nonincreasing, (12) weakly dominates the corresponding certificate for \(w\). If the imbalance inequality is strict and the untruncated right side of (12) is positive, the dominance is strict, whether or not the comparator certificate is truncated at zero. Finally, when \(\varepsilon_0=\varepsilon_1=\alpha/2\), the definitions give \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\) and \(\mathcal C^{\boldsymbol\varepsilon}_{w_*}=\mathcal C_{w_*}\). Substitution in (12) proves the equal-split formula.