For \(h\in\mathcal H\), write \(A_{\cdot h}\) for column \(h\) of \(A\). For every \(w\in\Delta(\mathcal H)\), the definitions of \(A\), the integrated selector law, and \(b_{\mathrm{LP}}\) give, row by row,
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_hq^{\mathrm{obs}}_{h,a}(O)=q^{\mathrm{obs}}_{w,a}(O),\qquad
(b_{\mathrm{LP}})_{a,O}=q_{\mathrm{tar},a}(O).
\tag{1}
\]
Consequently, \(Aw=b_{\mathrm{LP}}\) is equivalent to joint orbit balance. If \(\mathcal H\ne\varnothing\), then
\[
\{Aw:w\in\Delta(\mathcal H)\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\tag{2}
\]
Thus (1)--(2) prove the convex-hull and stacked-LP equivalences for a nonempty library. If \(\mathcal H=\varnothing\), the adopted conventions make both \(\Delta(\mathcal H)\) and the displayed convex hull empty, so both sides of the existence equivalence are false. The LP is infeasible for the explicit reason
\[
\sum_{h\in\varnothing}w_h=0\ne1.
\tag{3}
\]
There is then no mixture \(w\), hence no implemented selector kernel or selector-indexed ordinary or weighted procedure; the minimum-imbalance objects, whose definition requires a nonempty library, are not instantiated.

Suppose next that \(\mathcal H\ne\varnothing\) and \(b_{\mathrm{LP}}\) does not belong to the convex hull \(C\) in (2). The set \(C\) is nonempty, compact, and convex. Choose \(c^*\in C\) minimizing \(\lVert b_{\mathrm{LP}}-c\rVert_2\), and put \(y=b_{\mathrm{LP}}-c^*\ne0\). For every \(c\in C\) and \(t\in(0,1]\), minimality along the segment \(c^*+t(c-c^*)\) gives
\[
0\le-2t y^\top(c-c^*)+t^2\lVert c-c^*\rVert_2^2.
\tag{4}
\]
Divide by \(t\) and let \(t\downarrow0\). Then \(y^\top c\le y^\top c^*\) for every \(c\in C\), while
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\lVert y\rVert_2^2>\sup_{c\in C}y^\top c=\max_{h\in\mathcal H}y^\top A_{\cdot h}.
\tag{5}
\]
Thus (5) is a strict Farkas separating certificate. No separation assertion is made for the empty convex hull; (3) is its complete infeasibility certificate.

It remains to prove coverage. Condition on \(\mathcal T\), fix a feasible common \(w\), and put \(N=M+1\). Feasibility implies that the library is nonempty and, by (1), that joint orbit balance holds. The theorem \(\texttt{thm:orbit-balance-iff}\) therefore implies that, for each arm \(a\),
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\tag{6}
\]
are conditionally independent and identically distributed. Append independent continuous uniforms \(V_{0,a},\ldots,V_{M,a}\) and rank the pairs \((S_{i,a},V_{i,a})\) lexicographically. Exchangeability and almost-sure absence of augmented ties make the target rank \(R_{0,a}\) uniform on \(\{1,\ldots,N\}\). If \(k_a\le M\) and \(S_{0,a}>r_{a,(k_a)}\), at least \(k_a\) calibration scores are strictly smaller, so \(R_{0,a}>k_a\). If \(k_a=N\), the threshold equals \(+\infty\) and the exceedance event is empty. Hence in both cases
\[
\Pr\!\left(S_{0,a}>r_{a,(k_a)}\mid\mathcal T\right)
\le\frac{N-k_a}{N}.
\tag{7}
\]
The identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\), applied to \(x=N\varepsilon_a\), yields
\[
\frac{N-k_a}{N}=\frac{\lfloor N\varepsilon_a\rfloor}{N}=\rho_{M,\varepsilon_a}\le\varepsilon_a.
\tag{8}
\]

The bounded-outcome assumption gives \(Y_{0T}(a)\in[-K,K]\). Therefore the definition of the clipped interval implies
\[
S_{0,a}\le r_{a,(k_a)}
\quad\Longrightarrow\quad
Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w},
\tag{9}
\]
including the case \(r_{a,(k_a)}=+\infty\). If (9) holds for both arms, then
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{10}
\]
The conditional union bound, which requires no arm independence, and (7)--(10) give
\[
\begin{aligned}
\Pr\!\left(\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right)
&\ge1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}\\
&\ge1-\varepsilon_0-\varepsilon_1\ge1-\alpha.
\end{aligned}
\tag{11}
\]
On the equal-split diagonal, \(k_0=k_1=\lceil(M+1)(1-\alpha/2)\rceil=k\), and \(\texttt{def:rank-inversion}\) gives \(I^{\boldsymbol\varepsilon}_{a,w}=I_{a,w}\) and \(\mathcal C^{\boldsymbol\varepsilon}_w=\mathcal C_w\). Equations (7)--(11) then give the symmetric formulas.