Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values assigned by \(s_a\) outside \(\mathcal O_a\) are immaterial. We first prove the finite total-preorder reduction. For a score map \(s_a\), define \(O\preceq_a O'\) if and only if \(s_a(O)\le s_a(O')\). This is a total preorder on \(\mathcal O_a\). If \(\widetilde s_a\) induces the same total preorder, then for every target orbit and every calibration-orbit vector,\[s_a(O_{T,a})\le Q_k\bigl(s_a(O_{1,a}),\ldots,s_a(O_{M,a})\bigr)\]holds if and only if\[\widetilde s_a(O_{T,a})\le Q_k\bigl(\widetilde s_a(O_{1,a}),\ldots,\widetilde s_a(O_{M,a})\bigr).\]Indeed, the first event says that fewer than \(k\) calibration scores are strictly below the target score, and that count depends only on the preorder. Hence the joint event in \(\texttt{def:coverage-frontier}\) is pointwise unchanged when either score map is replaced by another representative of the same preorder.\n\nConversely, let a total preorder on \(\mathcal O_a\) have the ordered nonempty equivalence classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\). If \(d_a=1\), assign score zero to its only class. If \(d_a>1\), assign the value \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). Because \(K>0\), this score map takes values in \([0,K]\) and induces exactly the prescribed preorder. It uses \(d_a\le m_a\) levels. There are\[F_{m_a}=\sum_{d=1}^{m_a}d!\left\{\begin{matrix}m_a\\ d\end{matrix}\right\}\]total preorders on an \(m_a\)-element set, where the braces denote a Stirling number of the second kind. The objective is therefore constant on each of the \(F_{m_0}F_{m_1}\) pairs of total preorders. This proves both attainment and the exact finite reduction.\n\nFor completeness, the probability attached to each preorder pair is directly computable from the design. Put\[\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),\qquad R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).\]By the replicated randomization and auxiliary-selector construction, the \(M\) calibration orbit pairs are iid with mass function \(R_w\). If \(O_a(v)\) is the orbit containing \((v,a)\), the joint coverage probability for a fixed score pair is the finite sum\[\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\!\sum_{((O_{i,0},O_{i,1}))_{i=1}^M\in(\mathcal O_0\times\mathcal O_1)^M}\!\left\{\prod_{i=1}^M R_w(O_{i,0},O_{i,1})\right\}\prod_{a=0}^1\mathbf 1\!\left\{s_a(O_a(v))\le Q_k\bigl(s_a(O_{1,a}),\ldots,s_a(O_{M,a})\bigr)\right\}.\]Thus brute-force evaluation, after tabulating \(R_w\), uses at most \(O\!\left(F_{m_0}F_{m_1}|\mathcal V|(m_0m_1)^M\right)\) arithmetic operations. This is an exact ordered-partition algorithm; repeated orbit-pair counts may equivalently be aggregated into multinomial cells.\n\nWe next disprove binary attainment by an admissible instance. Take four pair blocks, \(\mathcal G=S_2^4\), and independent fair within-pair assignments with exactly one treated member per pair. Let \(\mathcal H\) be a singleton and \(w=1\). Conditional on assignment, its arm-\(a\) kernel first chooses a block with probabilities\[q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)\]and then selects that block's unique observed arm-\(a\) member. This kernel is observable and equivariant, and its selected orbit is precisely the chosen block. Let\[q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},\qquad p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\qquad r\in\{0,1\}.\]The two target lifts consequently have the same target block, with law \(p\). The auxiliary selector draws make the two arms' calibration block sequences independent, each with law \(q\). Take \(M=3\) and \(\alpha=1/2\), so \(k=\lceil4(1-1/4)\rceil=3\). Set \(s_0\equiv0\), and give the arm-\(1\) blocks the strict order \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Since \(k=3\), arm \(1\) fails exactly when all three calibration blocks lie strictly below the target block. Therefore its failure probability is\[F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.\]Arm \(0\) never fails, so the frontier objective of this multilevel pair is\[F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.\]\n\nIt remains to compare all binary pairs, including pairs that use both arms adversely. For a binary arm-\(a\) map, let \(H_a\subseteq\{1,2,3,4\}\) be the blocks assigned score \(K\), and write \(A_a=(1-q(H_a))^3\). The arm fails exactly when the common target block lies in \(H_a\) and all three arm-\(a\) calibration blocks lie outside \(H_a\). Conditional independence of the two calibration sequences and the common target block give the exact union probability\[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\]This formula permits a finite exact certificate. Using concatenation to denote a subset, for example \(12=\{1,2\}\), take the row order\[\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.\]The numerators of \(\max_{H_1}F_{\mathrm{bin}}(H_0,H_1)\), all over the common denominator \(320000000\), are\[\begin{split}(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).\end{split}\]These sixteen row maxima exhaust all \(16^2\) binary pairs. Hence\[\max_{H_0,H_1}F_{\mathrm{bin}}(H_0,H_1)=\frac{3259109}{5000000},\]attained, for example, by \(H_0=\{2,4\}\) and \(H_1=\{3,4\}\). The largest binary frontier objective is consequently \(759109/5000000\), and the strict gap is\[\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\]Thus the asserted universal binary reduction is false, even for observable equivariant selectors under ordinary matched-pair randomization.\n\nFinally, suppose that in one arm every target-supported orbit has zero calibration mass and \(k\le M\). Assign score \(K\) to precisely those target-supported orbits in that arm and zero to all its other orbits, and assign zero in the other arm. The target score in the adverse arm is \(K\) almost surely, every adverse-arm calibration score is zero almost surely, and its \(k\)-th order statistic is zero. The other-arm inequality holds, so the joint coverage event has probability zero. Since the frontier objective can never exceed \(1-\alpha\), it follows that \(\Gamma_{M,\alpha}(w)=1-\alpha\), consistently with \(\texttt{prop:disjoint-orbit-witness}\). If \(k=M+1\), then \(Q_k=+\infty\); both arm inequalities hold for every score configuration, so the joint coverage probability is one and \(\Gamma_{M,\alpha}(w)=0\), consistently with \(\texttt{prop:rank-boundary}\).