Let \(N=M+1\). Since \(k=\lceil N(1-\alpha/2)\rceil\), the elementary equivalence \(\lceil x\rceil\le n\) if and only if \(x\le n\), for integral \(n\), gives
\[
\begin{aligned}
k\le M
&\iff \left\lceil N\left(1-\frac{\alpha}{2}\right)\right\rceil\le N-1\\
&\iff N\left(1-\frac{\alpha}{2}\right)\le N-1\\
&\iff \alpha\ge\frac{2}{M+1}.
\end{aligned}
\]
Fix the arm \(a\) in the premise. Under \(\texttt{def:disjoint-orbit-law}\), the arm-\(a\) potential outcome is \(K\) on target-supported arm-\(a\) orbits and zero elsewhere, while every arm-\(1-a\) potential outcome is zero. These outcome coordinates are constant on every \(\mathcal G\)-orbit. Complete the prototype with any fixed covariate array and let \(G\) be uniform on the finite group \(\mathcal G\), as prescribed by the definition. For each fixed \(g\in\mathcal G\), \(gG\) is again uniform on \(\mathcal G\); hence \(g(GL^*)\) and \(GL^*\) have the same law. The constructed latent law therefore satisfies \(\texttt{ass:finite-group-latent-invariance}\). Every potential-outcome coordinate belongs to \(\{0,K\}\subseteq[-K,K]\), so it also satisfies \(\texttt{ass:bounded-potential-outcomes}\). Consequently it is a member of \(\mathcal P_{\mathcal G,K}\) by \(\texttt{def:invariant-laws}\). Independent copies, the known assignment law, and the stipulated auxiliary draws give the experiment required by the remaining assumptions.

If an orbit \(O\) has \(q^{\mathrm{obs}}_{w,a}(O)>0\), the disjoint-support premise says that \(O\) is not target-supported. The construction therefore assigns outcome zero on \(O\). The predictor is identically zero, and \(\texttt{ass:observable-selector-kernel}\) forces \(J_{i,a}\) to be observed in arm \(a\). Thus each selected arm-\(a\) calibration score is zero almost surely. Since \(k\le M\),
\[
r_{a,(k)}=0.
\]
All potential outcomes and the predictor in arm \(1-a\) are also zero, so all calibration scores in that arm are zero and \(r_{1-a,(k)}=0\). The two raw residual intervals are \(\{0\}\), and clipping to \([-K,K]\) leaves them unchanged because \(K>0\). Hence
\[
I_{0,w}=I_{1,w}=\{0\},\qquad \mathcal C_w=\{0\}-\{0\}=\{0\}.
\]
By \(\texttt{ass:prespecified-target}\), the selected target belongs almost surely to a target-supported orbit. Therefore \(Y_{0T}(a)=K\) and \(Y_{0T}(1-a)=0\). It follows that \(\tau_T=K\) when \(a=1\) and \(\tau_T=-K\) when \(a=0\). Since \(K>0\), neither value belongs to \(\{0\}\), and thus
\[
\Pr_P\{\tau_T\in\mathcal C_w\mid\mathcal T\}=0.
\]