For a finite rank \(k_a\), the order-statistic identity
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a
\tag{1}
\]
shows that the event depends on \(s_a\) only through its total preorder on \(\mathcal O_a\). Conversely, if a preorder has ordered nonempty classes \(C_{a,1}\prec\cdots\prec C_{a,d_a}\), assign score \(0\) when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes the preorder in \([0,K]\) with at most \(m_a\) levels. Hence the maximum in \(\texttt{def:coverage-frontier}\) is attained by the finite collection of \(F_{m_0}F_{m_1}\) preorder pairs. This proves exactness over the declared orbit-constant score class and does not identify it with a supremum over latent laws.

When both ranks are finite, \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) gives
\[
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
Its proof integrates the selector kernels only over \(\operatorname{supp}(\nu)\), so arbitrary off-support extensions do not affect \(R_w\), \(P_T^C\), any local weight, or any exact key. The vertex, edge, face, and rank-one prepasses followed by the deterministic least-charge residual dispatcher give exactly the displayed seven-way partition. The same lemma proves the sum \(\mathsf B\), both enumeration-time bounds, and the memory bound \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\). In particular, face and rank-one keys have constant auxiliary workspace and do not trigger factorial preprocessing.

The edge, face, and rank-one strict comparisons follow directly from the three complete support-domain kernel audits in that lemma. They respectively yield
\[
D_{M,n,M}(1/2,1/2,0,0)=1-2^{-M},
\]
\[
D_{M,M,M}(1/3,1/3,1/3,0)=1-2\cdot3^{-M},
\]
and
\[
D_{2n,n,n+2}(1/4,1/4,1/4,1/4)
=H_{2n,n}(1/2)H_{2n,n+2}(1/2),
\]
with precisely the asserted ranks, budgets, time charges, and workspace charges. Because each lookup is specified on every point of its finite assignment support, the corrected selector-domain assumptions are fully met.

Suppose next that exactly one rank \(k_b=M+1\), and put \(c=1-b\). By \(\texttt{prop:asymmetric-rank-boundary}\), the boundary-arm event is certain. Conditional on \(O_{T,c}=O_t\), (1) is a binomial strict-prefix event with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over the target orbit gives the displayed one-arm formula. The ordered-class scan and \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), as assembled in \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), prove the stated \(F_{m_c}\)-preorder time bound and constant auxiliary distribution-function memory. If both ranks equal \(M+1\), both rank events are certain, so the positive-part deficit is zero.

We verify the binary nonattainment certificate exactly. Take four pair-block orbits, calibration block probabilities
\[
q=(13/20,1/20,1/4,1/20),
\]
and common-target block probabilities
\[
p=(1/20,1/10,1/4,3/5).
\]
This is realized on the invariant support of independent one-treated--one-control assignments by complete kernels which, in each arm and on every supported assignment, select a block according to \(q\) and then its unique observed arm member; the auxiliary product draws make the two selected block labels independent conditional on the assignment. Let arm \(0\) be constant and order arm \(1\) as \(1\prec3\prec2\prec4\). For \(M=3\) and \(k_0=k_1=3\), the failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+
\frac1{10}\left(\frac{18}{20}\right)^3+
\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\]
Since \(1-\alpha=1/2\), the frontier objective is \(24957/160000\).

For binary high-score sets \(H_0,H_1\), inclusion--exclusion and the independent arm-selector draws give the failure probability
\[
p(H_0)\{1-q(H_0)\}^3+p(H_1)\{1-q(H_1)\}^3
-p(H_0\cap H_1)\{1-q(H_0)\}^3\{1-q(H_1)\}^3.
\tag{3}
\]
Order the sixteen subsets as
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.
\]
Exact maximization of (3) over the sixteen choices of \(H_1\), for each listed \(H_0\), gives numerators over the common denominator \(320000000\)
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\]
Thus the largest binary objective is \(759109/5000000\), and subtraction gives
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\]
Therefore binary scores are not universally extremal.

Finally, if target and calibration orbit supports are disjoint in a finite-rank arm, assign score \(K\) to target-supported orbits and \(0\) to calibration-supported orbits in that arm, and assign \(0\) in the other arm. The adverse rank event then fails surely, so the joint event has probability zero and the frontier objective is \(1-\alpha\). No objective can exceed \(1-\alpha\), proving equality. Setting \(\varepsilon_0=\varepsilon_1=\alpha/2\) gives \(k_0=k_1=k\) by \(\texttt{lem:armwise-finite-rank-staircase}\), and hence yields \(\texttt{thm:sharp-orbit-coverage-frontier}\). All prepasses evaluate the same probabilities in (2), so none changes the active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit semantics.