Put \(N=M+1\). Since \(k=\lceil N(1-\alpha/2)\rceil\), the elementary equivalence \(\lceil x\rceil\le n\Longleftrightarrow x\le n\) for integral \(n\) gives
\[
k\le M\Longleftrightarrow N(1-\alpha/2)\le N-1\Longleftrightarrow \alpha\ge \frac{2}{M+1}.
\tag{1}
\]
Fix the adverse arm \(a\). Under \texttt{def:disjoint-orbit-law}, the arm-\(a\) potential outcome is \(K\) on every target-supported arm-\(a\) orbit and is zero on every orbit having positive calibration mass and on every remaining orbit. These prescriptions are consistent because the hypothesis says that each target-supported adverse-arm orbit has zero \(q^{\mathrm{obs}}_{w,a}\)-mass. Every arm-\((1-a)\) potential outcome is zero, and both trained predictors are zero. Complete the prototype with a common fixed covariate. The prototype is constant on every actual \(\mathcal G\)-orbit. Equivalently, under the uniform group randomization in \texttt{def:disjoint-orbit-law}, left multiplication by any fixed \(g_0\in\mathcal G\) preserves the uniform group element. Hence the resulting latent law satisfies \texttt{ass:finite-group-latent-invariance}. All outcomes lie in \(\{0,K\}\subseteq[-K,K]\), so \texttt{ass:bounded-potential-outcomes} and \texttt{def:invariant-laws} imply that the law belongs to \(\mathcal P_{\mathcal G,K}\). Independent replication, the known randomization law, and the auxiliary selector draws give the experiment required by \texttt{ass:independent-replicated-arrays}, \texttt{ass:known-matched-randomization}, and \texttt{ass:selector-auxiliary-randomization}.

If \(q^{\mathrm{obs}}_{w,a}(O)>0\), then \(O\) is not target-supported, so its arm-\(a\) outcome and predictor are both zero. By \texttt{ass:observable-selector-kernel} and \texttt{def:observable-selector-mixture}, every selected adverse-arm calibration score therefore equals zero. Every arm-\((1-a)\) selected score is also zero. Since \(k\le M\), the two \(k\)-th order statistics are zero, and \texttt{def:rank-inversion} yields
\[
r_{0,(k)}=r_{1,(k)}=0,\qquad I_{0,w}=I_{1,w}=\{0\},\qquad \mathcal C_w=\{0\}.
\tag{2}
\]
By \texttt{ass:prespecified-target}, \(T^a\) lies in a target-supported arm-\(a\) orbit almost surely. Thus \(Y_{0T}(a)=K\) and \(Y_{0T}(1-a)=0\), so
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)=\begin{cases}K,&a=1,\\-K,&a=0.\end{cases}
\tag{3}
\]
Because \(K>0\), (2) and (3) imply \(\Pr_P(\tau_T\in\mathcal C_w\mid\mathcal T)=0\). The proof uses the actual quotient \(\mathcal U/\mathcal G\); a two-state pair cell may instantiate an orbit in this argument only under the local subgroup condition in \texttt{def:pair-action}.