Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values of \(s_a\) outside \(\mathcal O_a\) are irrelevant. First suppose \(k\le M\). Given \(s_a\), define the total preorder \(O\preceq_a O'\) if and only if \(s_a(O)\le s_a(O')\). Then
\[
s_a(O_{T,a})\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff \#\{i:s_a(O_{i,a})<s_a(O_{T,a})\}<k.
\tag{1}
\]
Thus the joint rank event depends only on the pair of total preorders induced by \(s_0\) and \(s_1\). Conversely, if a total preorder on \(\mathcal O_a\) has ordered equivalence classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). Because \(K>0\), this is a representative in \([0,K]\) with \(d_a\le m_a\) levels. If \(k=M+1\), the rank event is identically true and the same finite reduction is immediate. The number of total preorders on an \(m\)-element labelled set is the ordered Bell number
\[
F_m=\sum_{d=1}^m d!\left\{\begin{matrix}m\\d\end{matrix}\right\},
\tag{2}
\]
because one first partitions the set into \(d\) nonempty tie classes and then orders those classes. Hence only \(F_{m_0}F_{m_1}\) preorder pairs need be checked. This proves finite attainment and, together with the maximizing definition of \(\Gamma_{M,\alpha}(w)\), proves exactness over the stated orbit-constant score class. No step enlarges that class to all laws in \(\mathcal P_{\mathcal G,K}\).

We next write the exact objective. For an orbit \(O\in\mathcal O_a\), define the proof intermediate
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),
\]
and define
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).
\tag{3}
\]
By \(\texttt{ass:selector-auxiliary-randomization}\), the two selector draws are conditionally independent given their shared assignment, so \(R_w\) is their joint orbit law. Independence across replicates makes the \(M\) calibration orbit pairs iid with mass \(R_w\). If \(O_a(v)\) is the orbit containing \((v,a)\), then a fixed preorder pair has joint rank-event probability
\[
\begin{aligned}
&\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\!\sum_{((O_{i,0},O_{i,1}))_{i=1}^M\in(\mathcal O_0\times\mathcal O_1)^M}\!\left\{\prod_{i=1}^M R_w(O_{i,0},O_{i,1})\right\}\\
&\quad\times\prod_{a=0}^1\mathbf 1\!\left\{s_a(O_a(v))\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\right\}.
\end{aligned}
\tag{4}
\]
This sum retains the one coherent target member and the within-replicate cross-arm selector coupling; it assumes neither target-arm nor calibration-arm independence. Substitution into \(\texttt{def:coverage-frontier}\) gives the asserted evaluable finite maximum.

Let \(n=m_0m_1\). After tabulating the \(n^M\) configuration weights in \((4)\), enumerate configurations in reflected \(n\)-ary order, so successive configurations change one replicate coordinate. For each target member and preorder pair, the two counts in \((1)\) can then be updated in constant time after an \(O(M)\) initialization. When \(n\ge2\), \(M=O(n^M)\), and when \(n=1\) the sum is immediate. Multiplication by the numbers of preorder pairs and target members yields
\[
O\!\left(F_{m_0}F_{m_1}|\mathcal V|(m_0m_1)^M\right)
\tag{5}
\]
arithmetic operations after the joint calibration law is tabulated.

It remains to disprove binary attainment. Take four pair blocks, \(\mathcal G=S_2^4\), and an invariant assignment law giving exactly one treated member per pair, with the two assignments equiprobable within each pair. Let \(\mathcal H\) be a singleton and \(w=1\). Given any assignment, let each arm-\(a\) kernel choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\]
and then select that block's unique observed arm-\(a\) member. This is an observable equivariant selector. Its block law is \(q\), independent of the assignment, and the auxiliary product rule gives \(R_w(b_0,b_1)=q_{b_0}q_{b_1}\). Set
\[
q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},\qquad p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right).
\]
Thus the two target lifts share a block with law \(p\). Take \(M=3\) and \(\alpha=1/2\), so \(k=3\). Set \(s_0\equiv0\), and order the arm-\(1\) blocks as \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Arm \(1\) fails exactly when all three calibration blocks are strictly below the target. Its failure probability is
\[
F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\tag{6}
\]
Arm \(0\) never fails, so the resulting frontier objective is \(F_{\mathrm{multi}}-\alpha=24957/160000\).

Every binary score map is rank-equivalent either to a constant map or to a map taking values zero and \(K\). For such a map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be the blocks assigned the high score, and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion, conditional on the common target block, gives the probability that at least one arm fails as
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{7}
\]
In the row order \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\), exhaustive rational substitution of all sixteen choices for the other arm into \((7)\) gives the following row maxima, over the common denominator \(320000000\):
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{8}
\]
The table exhausts all \(16^2\) binary pairs. Therefore
\[
\max_{H_0,H_1}F_{\mathrm{bin}}(H_0,H_1)=\frac{3259109}{5000000},
\]
attained, for example, by \(H_0=\{2,4\}\) and \(H_1=\{3,4\}\). The largest binary frontier objective is consequently \(759109/5000000\), and \((6)\)--\((8)\) give the strict objective gap
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.
\]
This proves that binary scores need not attain the frontier.

Finally, suppose target and calibration orbit supports are disjoint in one arm and \(k\le M\). Assign score \(K\) to target-supported orbits in that arm and zero to all other orbits; assign zero in the other arm. Every adverse target score is \(K\), every adverse calibration score is zero, and the joint rank event has probability zero. Since any value of the objective is at most \(1-\alpha\), this construction proves \(\Gamma_{M,\alpha}(w)=1-\alpha\), consistently with \(\texttt{prop:disjoint-orbit-witness}\). If \(k=M+1\), both order-statistic operators in the frontier definition equal \(+\infty\), so the joint rank event has probability one for every score pair and \(\Gamma_{M,\alpha}(w)=0\), consistently with \(\texttt{prop:rank-boundary}\).