Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\), \(k_0=k_1=k\), and by \(\texttt{def:coverage-frontier}\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w). \tag{1}
\]
The exactness and preorder-attainment assertions follow by taking this diagonal section of \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). For completeness, the rank event depends on each score map only through its total preorder: when \(k\le M\),
\[
s_a(O_{T,a})\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\quad\Longleftrightarrow\quad
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k. \tag{2}
\]
If a preorder has ordered nonempty tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to \(C_{a,j}\). Since \(K>0\), this realizes the preorder in \([0,K]\) with at most \(d_a\le m_a\) levels. Thus enumeration of the \(F_{m_0}F_{m_1}\) preorder pairs attains the maximum. This is an exact maximum only over the bounded orbit-constant score class declared in \(\texttt{def:coverage-frontier}\); no law-level supremum has been introduced.

We next specialize the exact cached evaluator. For \(O\in\mathcal O_a\), write
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z).
\]
The common assignment and the one common target induce, respectively,
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z), \tag{3}
\]
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}. \tag{4}
\]
Hence \(R_w\) retains the within-replicate cross-arm dependence created by the shared assignment, while \(P_T\) retains the dependence between the two arm lifts of the same selected member. Let \(L=|\operatorname{supp}(P_T)|\). For a preorder pair \(C=(c_0,c_1)\), push (4) forward to ordered class indices to obtain \(P_T^C\), and let \(L_C=|\operatorname{supp}(P_T^C)|\). For every supported class pair \((j,\ell)\), the two-dimensional prefix table of (3) gives the four-cell vector
\[
\pi^C_{xy}(j,\ell)=\sum_{O_0,O_1}R_w(O_0,O_1)\mathbf 1\!\left\{\mathbf 1\{c_0(O_0)<j\}=x,\ \mathbf 1\{c_1(O_1)<\ell\}=y\right\},
\qquad (x,y)\in\{0,1\}^2. \tag{5}
\]
Let \(\Pi_C\) be the set of distinct vectors in (5) on \(\operatorname{supp}(P_T^C)\), and put \(U_C=|\Pi_C|\). By \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\),
\[
U_C\le L_C\le\min\{L,d_0d_1\}, \tag{6}
\]
and the probability of both rank events for this preorder pair is
\[
\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k,k}(\pi), \tag{7}
\]
where \(\omega_C(\pi)\) aggregates exactly the coherent target mass of class pairs with key \(\pi\), and \(D_{M,k,k}(\pi)\) is the coupled two-count recurrence value. Therefore class pairs sharing an exact key require only one recurrence, without factorizing either (3) or (4).

Let \(\mathfrak C\) be the set of all preorder pairs. When \(k\le M\), the same lemma, with \(k_0=k_1=k\), shows that tabulating the target pushforward, constructing each prefix table, grouping the \(L_C\) supported class pairs by three independent exact coordinates in a deterministic balanced tree, aggregating their masses, and running the \(U_C\) recurrences costs
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)+\sum_{C\in\mathfrak C}\left[L_C\log(1+L_C)+L_C+U_C\{1+Mk^2\}\right]
\right). \tag{8}
\]
Putting \(L_{\max}=\max_C L_C\) and \(U_{\max}=\max_C U_C\) in (8) gives
\[
O\!\left(|\mathcal V|+F_{m_0}F_{m_1}\left[m_0m_1+L+L_{\max}\log(1+L_{\max})+L_{\max}+U_{\max}\{1+Mk^2\}\right]\right), \tag{9}
\]
and the orbit tables, coherent-target table, two recurrence arrays, and current exact-key table use
\[
O(m_0m_1+L+k^2+U_{\max}) \tag{10}
\]
working memory. These are precisely the asserted instance-adaptive, uniform, and memory bounds after \(R_w\) is tabulated.

If \(k=M+1\), \(\texttt{def:rank-inversion}\) makes both order-statistic operators equal to \(+\infty\). Both rank events are certain, so (1) gives
\[
\Gamma_{M,\alpha}(w)=[(1-\alpha)-1]_+=0, \tag{11}
\]
which is evaluable in constant time and agrees with \(\texttt{prop:rank-boundary}\).

The admissible four-pair construction proved in \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\) uses \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so it lies on the diagonal (1). Its exhaustive evaluation gives, respectively, the four-level frontier objective, the largest binary objective, and their difference as
\[
\frac{24957}{160000},\qquad \frac{759109}{5000000},\qquad \frac{83189}{20000000}>0. \tag{12}
\]
Thus binary score maps do not always attain the symmetric frontier. Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k\le M\). Give score \(K\) to every target-supported orbit and score zero to every calibration-supported orbit in arm \(a\), and use the zero score in the other arm. Then the target score in arm \(a\) is always \(K\), every calibration score there is zero, and the joint rank event has probability zero. Consequently
\[
\Gamma_{M,\alpha}(w)=[(1-\alpha)-0]_+=1-\alpha. \tag{13}
\]
Equations (1)--(13) prove every assertion.