For a finite rank \(k_a\), the order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Hence ties are handled by strict prefixes and the event depends on \(s_a\) only through its total preorder. Conversely, if a preorder has ordered classes \(C_{a,1}\prec\cdots\prec C_{a,d_a}\), assign zero when \(d_a=1\) and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes every preorder in \([0,K]\) with at most \(m_a\) levels. The finite preorder collection therefore attains the maximum defining \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)\). This proves exactness over the declared score class and makes no claim about all invariant latent laws.

When both ranks are finite, \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) gives
\[
\Pr\{\text{both rank events under }C\}
=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
Its proof preserves the full \(R_w\), coherent \(P_T^C\), and local weights. The vertex-and-edge prepass and the three support-at-least-three branches give the asserted partition, \(\mathsf B\), \(\mathsf W\), both time bounds, and the memory bound. Since edge evaluation stores only a current binomial term and running sum, it adds no nonconstant workspace. Because no edge reaches the multinomial branch, the shared factorial table is present exactly under the displayed indicator.

For the strict witness, the full legality, invariance, support, selector, target, and rank audit is proved in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). In particular, with \(N\sim\operatorname{Bin}(M,1/2)\),
\[
(R_M,S_M)=(0,N),\qquad
D_{M,n,M}(\pi)=\Pr\{N<M\}=1-2^{-M}.
\tag{3}
\]
The endpoint \(2^{-M}\) takes \(\Theta(\log M)\) exact arithmetic, whereas the old least charge is \(\Theta(M)\). The error levels sum to \(\alpha\) and equation (8) of that lemma gives \(k_0=n\) and \(k_1=M\).

Suppose exactly one rank \(k_b=M+1\). By \(\texttt{prop:asymmetric-rank-boundary}\), that arm's rank event is certain. For \(c=1-b\), condition on \(O_{T,c}=O_t\). By (1) and iid calibration orbits, the strict-prefix count is binomial with parameter
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over \(p_{c,O_t}\) gives the displayed one-arm formula. Grouping by ordered tie classes and applying \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\) yields
\[
O\!\left(F_{m_c}m_c[1+\log M+\min\{k_c,M-k_c+1\}]\right)
\]
operations and constant CDF workspace, exactly as \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) proves. If both ranks equal \(M+1\), both events are certain and the positive-part deficit is zero.

For binary nonattainment, use four audited pair blocks with independent fair within-pair assignment, calibration block probabilities
\[
q=(13/20,1/20,1/4,1/20)
\]
in each arm, and common-target block probabilities
\[
p=(1/20,1/10,1/4,3/5).
\]
At \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), both ranks are three. Taking \(s_0\equiv0\) and arm-one order \(1\prec3\prec2\prec4\) gives failure probability
\[
\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000},
\]
hence objective \(24957/160000\). For binary high-score sets \(H_0,H_1\), put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion gives failure probability
\[
p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{4}
\]
In the subset order
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
maximizing (4) over the other arm gives the following row numerators with common denominator \(320000000\):
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\]
This exhaustive exact table has maximum \(208582976/320000000\), so every binary objective is at most \(759109/5000000\). Subtraction gives
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\tag{5}
\]

If target and calibration orbit supports are disjoint in a finite-rank arm, assign score \(K\) to target-supported orbits and zero elsewhere, and assign zero in the other arm. The adverse event fails surely, so the deficit is at least \(1-\alpha\); the defining positive part is never larger than \(1-\alpha\), proving equality. Equal splitting gives \(k_0=k_1=k\) by \(\texttt{lem:armwise-finite-rank-staircase}\) and yields the symmetric theorem. Finally, the new branches only compute the same probabilities in (2); they do not modify selectors, intervals, active-arm boundaries, pair audits, the empty-library convention, or weighted inversion.