Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values of \(s_a\) outside \(\mathcal O_a\) are irrelevant. Given \(s_a\), define \(O\preceq_aO'\) if and only if \(s_a(O)\le s_a(O')\). For \(k\le M\), the armwise rank event is equivalent to \[\#\{i:s_a(O_{i,a})<s_a(O_{T,a})\}<k,\] and for \(k=M+1\) it holds identically. It therefore depends only on the induced total preorder. If a prescribed preorder has ordered equivalence classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) on \(C_{a,j}\). Because \(K>0\), this is a representative in \([0,K]\) with \(d_a\le m_a\) levels. The number of total preorders on an \(m\)-element labelled set is \[F_m=\sum_{d=1}^m d!\left\{\begin{matrix}m\\d\end{matrix}\right\},\] because one first partitions the set into \(d\) nonempty tie classes and then orders those classes. Thus the objective is constant on each of the \(F_{m_0}F_{m_1}\) preorder pairs, proving attainment by finite enumeration.

For explicit evaluation, define \[\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),\qquad R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).\] The shared assignment is integrated in \(R_w\); no general cross-arm independence is asserted. Conditional independence of auxiliary selector draws given \(Z_i\), together with independence across replicates, makes the \(M\) calibration orbit pairs iid with mass \(R_w\). If \(O_a(v)\) denotes the orbit containing \((v,a)\), the joint coverage probability for a fixed score pair is the finite sum \[\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\!\sum_{((O_{i,0},O_{i,1}))_{i=1}^M\in(\mathcal O_0\times\mathcal O_1)^M}\!\left\{\prod_{i=1}^MR_w(O_{i,0},O_{i,1})\right\}\prod_{a=0}^1\mathbf 1\!\left\{s_a(O_a(v))\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\right\}.\] This is the claimed exact finite objective after applying the positive part in \(\texttt{def:coverage-frontier}\). Let \(n=m_0m_1\). The \(n^M\) configuration weights can be generated once by a depth-\(M\), \(n\)-ary recursion in \(O(n^M)\) arithmetic operations when \(n\ge2\); the case \(n=1\) is immediate. For each preorder pair and target member, enumerate the configurations in reflected \(n\)-ary order, reversing successive sublists recursively. Consecutive configurations then change one coordinate, so the two below-target counts update in constant time. Initialization costs \(O(M)=O(n^M)\). The total cost is therefore \[O\!\left(F_{m_0}F_{m_1}|\mathcal V|(m_0m_1)^M\right).\]

We next give the strict binary counterexample. Take four pair blocks, \(\mathcal G=S_2^4\), and independent fair assignments with exactly one treated member per pair. Let \(\mathcal H\) be a singleton and \(w=1\). Given any assignment, each arm-\(a\) kernel chooses a block with probabilities \[q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)\] and then selects that block's unique observed arm-\(a\) member. The kernel is observable and equivariant. Its block law is \(q\), independent of the assignment, and the auxiliary product rule gives \(R_w(b_0,b_1)=q_{b_0}q_{b_1}\). Choose \[q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},\qquad p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right).\] The two target lifts share a block with law \(p\). Take \(M=3\) and \(\alpha=1/2\), so \(k=3\). Put \(s_0\equiv0\), and order the arm-\(1\) blocks as \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Arm \(1\) fails exactly when all three calibration blocks are strictly below the target, with probability \[F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.\] Arm zero never fails, so the frontier objective is \[F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.\]

For a binary map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be the blocks receiving score \(K\), and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion, conditional on the common target block, gives the exact joint failure probability \[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\] In the row order \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\), the numerators of \(\max_{H_1}F_{\mathrm{bin}}(H_0,H_1)\), over the common denominator \(320000000\), are \[\begin{split}(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).\end{split}\] These sixteen row maxima are obtained by direct substitution in the displayed rational formula and exhaust all \(16^2\) binary pairs. Hence \[\max_{H_0,H_1}F_{\mathrm{bin}}(H_0,H_1)=\frac{3259109}{5000000},\] attained, for example, by \(H_0=\{2,4\}\) and \(H_1=\{3,4\}\). The largest binary frontier objective is \(759109/5000000\), and the strict gap is \[\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\] This admissible matched-pair instance disproves binary attainment.

Finally, under disjoint target and calibration support in one arm with \(k\le M\), assign \(K\) to the target-supported orbits in that arm and zero elsewhere, and assign zero in the other arm. The adverse target score is \(K\), all adverse calibration scores are zero, and joint coverage is zero. Since the frontier objective is never greater than \(1-\alpha\), it equals \(1-\alpha\), in agreement with \(\texttt{prop:disjoint-orbit-witness}\). If \(k=M+1\), then \(Q_k=+\infty\), every joint rank event holds, and the frontier is zero, in agreement with \(\texttt{prop:rank-boundary}\).