Complement coordinate \(a\) when the upper-tail width \(h_a\) is smaller than \(k_a\). This operation permutes the four atoms and changes the retained corner width to \(\bar k_a\). By the four corner identities in \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\), the original lower--lower probability is recovered exactly from the selected transformed-corner probability and, when required, one or two exact binomial marginal tails.

For the first branch, \(\texttt{lem:four-cell-multinomial-sum-alternative}\) applies to the permuted four-cell law without requiring a positive base atom. For one key it rebuilds the four probability-power tables in \(O(M)\) operations and sums \(\mathsf T_{M,\bar k_0,\bar k_1}\) feasible terms. Factorials through \(M!\) are independent of the key and cost \(O(M)\) once whenever \(\Pi_{\mathrm{MS}}\ne\varnothing\). Sequential processing uses \(O(M)\) workspace.

For the second branch, the rolling recurrence in \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) visits exactly
\[
\mathsf C_{M,k_0,k_1}=\sum_{i=0}^{M-1}\min\{\bar k_0,i+1\}\min\{\bar k_1,i+1\}
\]
active states up to a fixed four-transition factor and uses two \(\bar k_0\) by \(\bar k_1\) arrays. Its time and workspace are therefore \(O(\mathsf C_{M,k_0,k_1})\) and \(O(\bar k_0\bar k_1)\).

For the third branch, the four atoms sum to one, so at least one orientation has a positive lower-left atom. The coefficient recurrence and corner reconstruction in \(\texttt{lem:positive-corner-coefficient-recurrence}\) have exact charge \(\mathsf C_+(\pi)\), including every required binomial tail, and rolling width \(u_+(\pi)\). Hence each of the three branches computes the same original retained-rectangle probability.

Summing the appropriate per-key charge over the disjoint partition gives the displayed time bound. At most one key workspace is live because keys are processed sequentially. Retaining the answers adds \(O(|\Pi|)\) memory, and the largest workspace among branches that are actually used gives the displayed maximum. This is the memory of the time-selected partition itself, not a separate optimization, proving the claim.