Condition throughout on \(\mathcal T\), put \(N=M+1\), and let \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). By \(\texttt{lem:orbit-score-factorization}\), the calibration-score and target-score laws in arm \(a\) are respectively
\[
Q_a=\sum_{O\in\mathcal O_a}q_{a,O}F_{a,O},\qquad P_a=\sum_{O\in\mathcal O_a}p_{a,O}F_{a,O}.
\]
For any measurable \(f:[0,\infty)\to[0,1]\), set \(h_O=\int f\,dF_{a,O}\) and \(d_O=p_{a,O}-q_{a,O}\). Since both orbit-mass vectors are probability mass functions, \(\sum_Od_O=0\). Hence the positive and negative parts of \(d=(d_O)_O\) both have mass \(\Delta_a(w)\), and
\[
\left|\int f\,d(P_a-Q_a)\right|=\left|\sum_Od_Oh_O\right|\le\Delta_a(w).
\tag{1}
\]
This is the required total-variation contraction through the common orbit-score kernel.

Fix an active arm \(a\in\mathcal A_{\boldsymbol\varepsilon}\), so \(k_a\le M\). Let \(\widetilde S_{0,a}\sim Q_a\) be independent of the calibration scores. Conditional on the calibration scores, apply (1) to \(f(s)=\mathbf 1\{s>r_{a,(k_a)}\}\). Target independence and the factorization lemma give
\[
\Pr\{S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le\Pr\{\widetilde S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}+\Delta_a(w).
\tag{2}
\]
The \(M+1\) variables \(S_{1,a},\ldots,S_{M,a},\widetilde S_{0,a}\) are iid. Append independent continuous uniforms and use the lexicographic proof ranks prescribed by \(\texttt{def:rank-inversion}\). The rank of the appended target pair is uniform on \(\{1,\ldots,N\}\). Strict exceedance of the \(k_a\)-th calibration order statistic forces this rank to exceed \(k_a\), so
\[
\Pr\{\widetilde S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le\frac{N-k_a}{N}=\rho_{M,\varepsilon_a}.
\tag{3}
\]
Combining (2) and (3),
\[
\Pr\{S_{0,a}>r_{a,(k_a)}\mid\mathcal T\}\le\rho_{M,\varepsilon_a}+\Delta_a(w),\qquad a\in\mathcal A_{\boldsymbol\varepsilon}.
\tag{4}
\]
By \(\texttt{ass:bounded-potential-outcomes}\), the implication \(S_{0,a}\le r_{a,(k_a)}\Rightarrow Y_{0T}(a)\in I^{\boldsymbol\varepsilon}_{a,w}\) holds for every active arm after clipping. If \(a\notin\mathcal A_{\boldsymbol\varepsilon}\), then \(k_a=M+1\), and \(\texttt{prop:asymmetric-rank-boundary}\) gives \(I^{\boldsymbol\varepsilon}_{a,w}=[-K,K]\), which contains \(Y_{0T}(a)\) surely. Thus inactive arms contribute neither a rank penalty nor an imbalance penalty. If both arm outcomes belong to their intervals, then
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\]
A conditional union bound over active arms only, together with (4), proves
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\mid\mathcal T\right\}\ge\max\!\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\bigl(\rho_{M,\varepsilon_a}+\Delta_a(w)\bigr)\right\}.
\tag{5}
\]
If exactly one arm is at the boundary, only the other arm occurs in (5). If both arms are at the boundary, the sum is empty and \(\texttt{prop:asymmetric-rank-boundary}\) gives \(\mathcal C^{\boldsymbol\varepsilon}_w=[-2K,2K]\) and coverage one.

By \(\texttt{lem:armwise-finite-rank-staircase}\), \(\rho_{M,\varepsilon_a}=j/(M+1)\) exactly for \(\varepsilon_a\in[j/(M+1),(j+1)/(M+1))\), so the coordinate elbows are \(j/(M+1)\). Moreover, \(d_O=-\delta_{a,O}(w)\), and zero total mass gives
\[
\Delta_a(w)=\frac12\sum_O|d_O|=\sum_{d_O>0}d_O=\sum_{d_O<0}(-d_O).
\]
Each coordinate is bounded by the corresponding one-sided sum, proving \(|\delta_{a,O}(w)|\le\Delta_a(w)\). On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(k_0=k_1=k\) and \(\rho_{M,\varepsilon_0}=\rho_{M,\varepsilon_1}=\rho_{M,\alpha}\). If \(k\le M\), both arms are active and (5) is \(\max\{0,1-2\rho_{M,\alpha}-\Delta_0(w)-\Delta_1(w)\}\); if \(k=M+1\), coverage is one.