Put
\[
J(s_0,s_1)=\Pr\!\left\{s_1(O_{T,1})\le Q_{k_1}(s_1(O_{1,1}),\ldots,s_1(O_{M,1}))\ \text{and}\ s_0(O_{T,0})\le Q_{k_0}(s_0(O_{1,0}),\ldots,s_0(O_{M,0}))\right\}.
\]
By \(\texttt{def:coverage-frontier}\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\max_{s_0,s_1}\bigl[(1-\alpha)-J(s_0,s_1)\bigr]_+.
\tag{1}
\]
The maximization is exactly over the deterministic maps \(s_a:\mathcal O\to[0,K]\) declared there. Hence (1) is the exact worst deficit of the joint rank-inclusion event in that deterministic bounded orbit-constant-score submodel.

The submodel is narrower than \(\mathcal P_{\mathcal G,K}\). Fix all covariates, set both predictors to zero, draw a nondegenerate Bernoulli variable \(\xi_i\), and set \(Y_{iv}(a)=K\xi_i\) for every \(v\) and \(a\). The array is bounded and invariant under every member relabelling, but conditional on any selected orbit its residual score is the nondegenerate random variable \(K\xi_i\). Thus a full-model law need not induce any deterministic \(s_a\), so (1) is neither a uniform full-model joint-inclusion certificate nor a causal effect-set coverage certificate.

Define
\[
E_{\mathrm{joint}}=\{Y_{0T}(1)\in I^{\boldsymbol\varepsilon}_{1,w},\ Y_{0T}(0)\in I^{\boldsymbol\varepsilon}_{0,w}\},\qquad E_{\mathrm{eff}}=\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_w\}.
\]
On \(E_{\mathrm{joint}}\), the identity \(\tau_T=Y_{0T}(1)-Y_{0T}(0)\) and the definition of a Minkowski difference give
\[
\tau_T\in I^{\boldsymbol\varepsilon}_{1,w}-I^{\boldsymbol\varepsilon}_{0,w}=\mathcal C^{\boldsymbol\varepsilon}_w.
\tag{2}
\]
Therefore \(E_{\mathrm{joint}}\subseteq E_{\mathrm{eff}}\), and monotonicity of conditional probability proves the displayed inequality. If both intervals are \(\{0\}\) and both potential outcomes equal \(K\), both armwise inclusions fail while \(\tau_T=0\in\{0\}\); hence the containment can be strict. Equation (2) is pointwise and does not enlarge the optimization domain in (1).

Suppose \(k_0,k_1\le M\). For either arm,
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\quad\Longleftrightarrow\quad\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{3}
\]
Thus the event depends on \(s_a\) only through its total preorder on the finite arm-orbit set. Conversely, if its ordered nonempty tie classes are \(C_{a,1}\prec\cdots\prec C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) on \(C_{a,j}\). This realizes the preorder in \([0,K]\) with at most \(m_a\) levels. The maximum in (1) is consequently attained among the \(F_{m_0}F_{m_1}\) preorder pairs.

For each pair \(C\), \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) proves
\[
J(C)=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi),
\tag{4}
\]
while retaining the calibration law \(R_w\), the coherent common-target pushforward \(P_T^C\), and the local weights. That lemma and \(\texttt{lem:four-cell-rank-event-dynamic-program}\), \(\texttt{lem:four-cell-multinomial-sum-alternative}\), and \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) prove the seven disjoint key strata and every exact evaluator displayed in the theorem. Summing their per-key charges gives exactly \(\mathsf B\); taking the largest live branch workspace gives \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\). The same evaluator lemma proves both time bounds, the factorial-trigger condition, the constant workspace of the vertex, edge, face, and rank-one strata, and the edge, face, and rank-one audit identities and strict resource comparisons. Those audits use kernels that are normalized and supported on the requested realized arm on every assignment with positive \(\nu\)-mass; arbitrary total extensions off that support have zero integrated weight.

If exactly one rank \(k_b=M+1\), \(\texttt{prop:asymmetric-rank-boundary}\) makes that arm's event certain. For \(c=1-b\), conditioning (3) on \(O_{T,c}=O_t\) gives a binomial count with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.
\]
Averaging over \(p_{c,O_t}\) gives the displayed one-boundary formula. The ordered-class scan and shorter-tail recurrence in \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) give the \(F_{m_c}\)-preorder time and constant auxiliary distribution-function memory. If both ranks equal \(M+1\), both events are certain and (1) is zero.

For the binary-attainment assertion, use four two-member blocks with \(\mathcal G=S_2^4\), audit each pure local swap by \(\texttt{def:pair-action}\), and assign independently and fairly one treated and one control member per block. Use calibration block masses
\[q=(13/20,1/20,1/4,1/20)\]
and common-target block masses
\[p=(1/20,1/10,1/4,3/5).\]
Choose a block according to \(q\) and then its unique observed member in the requested arm. This is a normalized observable kernel with realized-arm support. Take arm \(0\) constant and order arm \(1\) as \(1\prec3\prec2\prec4\). At \(M=3\) and \(k_0=k_1=3\), the joint-event failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\]
Since \(1-\alpha=1/2\), the four-level objective is \(24957/160000\). For a block set \(H\), write \(p(H)=\sum_{j\in H}p_j\) and \(q(H)=\sum_{j\in H}q_j\). By \(\texttt{ass:selector-auxiliary-randomization}\), the two armwise block choices are independent conditional on each assignment; since their block probabilities are the fixed vector \(q\), their high-set avoidance probabilities factor. For binary high-score sets \(H_0,H_1\), inclusion--exclusion therefore gives failure probability
\[
p(H_0)\{1-q(H_0)\}^3+p(H_1)\{1-q(H_1)\}^3-p(H_0\cap H_1)\{1-q(H_0)\}^3\{1-q(H_1)\}^3.
\tag{5}
\]
There are sixteen choices for each high set. Exact rational evaluation of (5) over the resulting \(256\) pairs gives maximum objective \(759109/5000000\). Therefore
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0,
\]
so binary maps do not attain (1).

If target and calibration orbit supports are disjoint in a finite-rank arm, assign score \(K\) to every target-supported orbit and zero to every calibration-supported orbit in that arm, and use zero in the other arm. The first rank event fails surely and the second holds surely. Hence \(J=0\) and (1) equals \(1-\alpha\), its largest possible value.

The literature records delimit rather than prove the calculation. On supported laws, \(\texttt{lem:lebrun-rectangular-probability-comparator}\) treats arbitrary rectangles for multinomial, multivariate hypergeometric, and multivariate Polya counts; its optimized object is a general rectangular probability, and its source compares exact-method accuracy, arithmetic cost, and storage. The present evaluator instead reduces each target-class and preorder pair to a four-cell iid prefix-indicator law and memoizes only the strict two-rank rectangle needed in (4). On guarantees and optimized objects, \(\texttt{lem:timans-max-rank-comparator}\) uses dependence among simultaneous conformal tests to control family-wise error and improve on Bonferroni, whereas \(\texttt{lem:schlembach-multi-target-allocation-comparator}\) optimizes per-target levels for exchangeable axis-aligned hyperrectangle volume while retaining joint coverage. \(\texttt{lem:structured-volume-dynamic-program-comparator}\) records the dynamic-programming guarantee of Gao, Shan, Srinivas, and Vijayaraghavan for near-optimal volume in structured prediction-set families. Those are coverage or volume objectives, not the deficit in (1). On exactness and resources, this theorem enumerates the finite deterministic orbit-score preorders exactly, evaluates every induced four-cell probability by exact arithmetic, and states the adaptive and uniform time bounds and the memory bound \(O(m_0m_1+L+U_{\max}+G+\mathsf W)\); the other records are not used as claims about those orbit-specific charges. Thus the deliverable is an exact evaluator for this paper's restricted deterministic audit functional with asymmetric ranks, one coherent target, and within-replicate cross-arm dependence. The comparison makes no priority claim and does not convert the audit into a new general coverage theorem.

Finally, the full-model guarantees remain separate. Under exact orbit balance, \(\texttt{thm:common-selector-lp}\) proves Bonferroni coverage for ordinary rank inversion. Under imbalance, \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) proves the active-arm total-variation lower bound. Neither invokes (1). Setting \(\varepsilon_0=\varepsilon_1=\alpha/2\) gives \(k_0=k_1=k\) by \(\texttt{lem:armwise-finite-rank-staircase}\) and yields the equal-split theorem. Every computational prepass changes only the exact evaluation of (4), so it changes no active-arm, pair-audit, empty-library, ordinary-rank, or weighted-orbit semantics.