For a row set \(\mathcal I\), let \(A_{\mathcal I}\) and \(b_{\mathcal I}\) be the corresponding restrictions and define
\[
d_{\mathcal I}(w)=\frac12\lVert A_{\mathcal I}w-b_{\mathcal I}\rVert_1.
\tag{1}
\]
Let \(\mathcal I_{\mathrm{all}}\) contain all rows and \(\mathcal I_{\mathcal A}=\{(a,O):a\in\mathcal A_{\boldsymbol\varepsilon},\ O\in\mathcal O\}\). The row identities in \(\texttt{thm:common-selector-lp}\) imply
\[
d_{\mathcal I_{\mathrm{all}}}(w)=\Delta_0(w)+\Delta_1(w),\qquad d_{\mathcal I_{\mathcal A}}(w)=\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w).
\tag{2}
\]
Because \(\mathcal H\) is finite and nonempty, \(\Delta(\mathcal H)\) is a nonempty compact simplex. The functions in (1) are continuous, so both minima are attained and both optimizer sets are nonempty. If \(\mathcal I_{\mathcal A}=\varnothing\), the active objective is identically zero, whence
\[
D_{*,\mathcal A}=0,\qquad \mathcal W_{*,\mathcal A}=\Delta(\mathcal H).
\tag{3}
\]
For either nonempty row set, the two-sided constraints are equivalent to \(t_j\ge |(A_{\mathcal I}w-b_{\mathcal I})_j|\). Minimizing over \(t\) gives equality coordinatewise, so the full and active absolute-value programs have values \(D_*\) and \(D_{*,\mathcal A}\), with exactly the declared optimizing \(w\)-coordinates.

We prove the dual formula for an arbitrary nonempty \(\mathcal I\). Put
\[
C_{\mathcal I}=\operatorname{conv}\{(A_{\cdot h})_{\mathcal I}:h\in\mathcal H\},\qquad D_{\mathcal I}=\min_{c\in C_{\mathcal I}}\frac12\lVert c-b_{\mathcal I}\rVert_1.
\tag{4}
\]
If \(\lVert y\rVert_\infty\le1/2\), then
\[
\min_{c\in C_{\mathcal I}}y^\top(c-b_{\mathcal I})\le D_{\mathcal I},
\tag{5}
\]
by Hölder's inequality, proving weak duality. If \(D_{\mathcal I}=0\), \(y=0\) attains equality. Suppose \(D_{\mathcal I}>0\). For \(n\ge2\), let \(r_n=(1-1/n)D_{\mathcal I}\) and
\[
B_n=\{x:\tfrac12\lVert x-b_{\mathcal I}\rVert_1\le r_n\}.
\]
The compact convex sets \(B_n\) and \(C_{\mathcal I}\) are disjoint. Choose a Euclidean closest pair \((c_n,x_n)\) and set \(v_n=c_n-x_n\ne0\). Minimality along segments gives
\[
\min_{c\in C_{\mathcal I}}v_n^\top c=v_n^\top c_n>v_n^\top x_n=\max_{x\in B_n}v_n^\top x.
\tag{6}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). The support function of the \(\ell_1\)-ball is
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b_{\mathcal I}+2r_n\lVert y_n\rVert_\infty=y_n^\top b_{\mathcal I}+r_n.
\tag{7}
\]
Thus \(\min_{c\in C_{\mathcal I}}y_n^\top c-y_n^\top b_{\mathcal I}>r_n\). Compactness of the cube gives a convergent subsequence. Because \(\mathcal H\) is finite, the minimum of the finitely many linear forms is continuous. Passing to the limit and using (5) yields the attained identity
\[
D_{\mathcal I}=\max_{\lVert y\rVert_\infty\le1/2}\left\{\min_{h\in\mathcal H}y^\top(A_{\cdot h})_{\mathcal I}-y^\top b_{\mathcal I}\right\}.
\tag{8}
\]
The full-row choice is the displayed dual for \(D_*\). For active rows, extend \(y\) by zero on inactive rows; (8) is the displayed dual for \(D_{*,\mathcal A}\). If the active set is empty, the only such vector is zero and the same dual value is zero.

If \(D_*>0\) and \(y\) maximizes the full dual, then \(y^\top A_{\cdot h}\ge y^\top b_{\mathrm{LP}}+D_*\) for every \(h\). Hence \(z=-y\) satisfies
\[
z^\top b_{\mathrm{LP}}\ge\max_h z^\top A_{\cdot h}+D_*,
\]
the claimed Farkas separation. Nonnegativity and attainment show that \(D_*=0\) exactly when some \(w\) satisfies every row of \(Aw=b_{\mathrm{LP}}\), which \(\texttt{thm:common-selector-lp}\) identifies with exact joint balance. The analogous argument shows that \(D_{*,\mathcal A}=0\) exactly when all active rows can be balanced, a joint two-arm characterization only when both arms are active.

The entries of \(A\) depend only on the known assignment law and selector library; \(b_{\mathrm{LP}}\) depends only on the prespecified target rule; and the active set depends only on \(M\) and the prespecified error budget. Therefore deterministically tie-broken choices \(w_*\) and \(w_{*,\mathcal A}\) are prespecified. Apply \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) to \(w_{*,\mathcal A}\). By (2) and optimality,
\[
\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w_{*,\mathcal A})=D_{*,\mathcal A},
\]
which gives
\[
\Pr_P\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_{*,\mathcal A}}\mid\mathcal T\}\ge\max\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\rho_{M,\varepsilon_a}-D_{*,\mathcal A}\right\}.
\tag{9}
\]
For any fixed \(w\), optimality gives \(D_{*,\mathcal A}\le\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w)\). Hence (9) weakly dominates its fixed-\(w\) counterpart, strictly if the inequality is strict and the optimized untruncated bound is positive. Applying the same proposition to \(w_*\), and then adding the omitted inactive nonnegative penalties, recovers
\[
\max\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\},
\]
together with the original full-object dominance and strictness claims.

With exactly one boundary arm, only the other arm's rows occur in the active program. If no arm is active, (3) holds, no optimization is needed, and \(\texttt{prop:asymmetric-rank-boundary}\) gives coverage one. On the finite-rank equal-split diagonal both arms are active, so \(D_{*,\mathcal A}=D_*\), \(\mathcal W_{*,\mathcal A}=\mathcal W_*\), and (9) becomes \(\max\{0,1-2\rho_{M,\alpha}-D_*\}\); at the two-boundary elbow coverage is one. Finally, if \(\mathcal H=\varnothing\), then \(\Delta(\mathcal H)=\varnothing\), so no selector-indexed object exists.