Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values of \(s_a\) outside \(\mathcal O_a\) are irrelevant. If \(k_a\le M\), then for every target orbit and calibration-orbit vector,
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\quad\Longleftrightarrow\quad
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the left event fails exactly when at least \(k_a\) calibration scores are strictly smaller than the target score. Thus ties are handled by the strict comparison in \((1)\), and the event depends on \(s_a\) only through its induced total preorder. If \(k_a=M+1\), then \(Q_{k_a}=+\infty\), so the event is identically true.

Conversely, let a total preorder on \(\mathcal O_a\) have ordered nonempty tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\). If \(d_a=1\), assign score zero to its sole class. If \(d_a>1\), assign score \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). Since \(K>0\), this map takes values in \([0,K]\), induces the prescribed preorder, and has \(d_a\le m_a\) levels. There are finitely many such preorders, namely \(F_{m_a}\).

Suppose first that \(k_0,k_1\le M\). Both events in \((1)\) may then vary. The objective in \(\texttt{def:coverage-frontier}\) is constant on each pair of total preorders, every pair has an admissible representative by the preceding construction, and the maximum is attained by enumerating the \(F_{m_0}F_{m_1}\) preorder pairs. This proves exact maximization over the declared bounded orbit-constant score class; it does not identify the maximum with a supremum over all laws in \(\mathcal P_{\mathcal G,K}\).

Define the orbit-level selector kernels and the one-replicate joint calibration-orbit law by
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),
\qquad
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).
\tag{2}
\]
By \(\texttt{ass:selector-auxiliary-randomization}\), the two arm selectors are conditionally independent given their shared assignment. By \(\texttt{ass:known-matched-randomization}\), assignments are independent across replicates with law \(\nu\). Hence the \(M\) calibration orbit pairs are iid with mass function \(R_w\), which preserves their within-replicate cross-arm dependence.

Fix a target member \(v\) and a preorder pair. Let \(O_a(v)\) be the orbit containing \((v,a)\), and put \(b_a(O;v)=\mathbf 1\{s_a(O)<s_a(O_a(v))\}\). Collapse \(R_w\) to
\[
\pi_{xy}(v)=\sum_{O_0\in\mathcal O_0}\sum_{O_1\in\mathcal O_1}R_w(O_0,O_1)
\mathbf 1\{b_0(O_0;v)=x,\ b_1(O_1;v)=y\},
\qquad (x,y)\in\{0,1\}^2.
\tag{3}
\]
Initialize \(d_0(0,0)=1\), set all other entries to zero, and update
\[
d_{i+1}(r,s)=\sum_{x=0}^1\sum_{y=0}^1\pi_{xy}(v)d_i(r-x,s-y),
\qquad 0\le r<k_0,\quad 0\le s<k_1,
\tag{4}
\]
with out-of-range entries zero. By \(\texttt{lem:four-cell-rank-event-dynamic-program}\),
\[
\sum_{r=0}^{k_0-1}\sum_{s=0}^{k_1-1}d_M(r,s)
=
\Pr\!\left\{\sum_{i=1}^M b_0(O_{i,0};v)<k_0,\ \sum_{i=1}^M b_1(O_{i,1};v)<k_1\right\}.
\tag{5}
\]
By \((1)\), this is the joint rank-event probability conditional on target member \(v\). Since \(T\sim q_{\mathrm{tar}}\) by \(\texttt{ass:prespecified-target}\), the frontier probability is
\[
\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\sum_{r=0}^{k_0-1}\sum_{s=0}^{k_1-1}d_M^{(v)}(r,s).
\tag{6}
\]
The single member sum preserves coherence of the target's two arm lifts, and \(R_w\) preserves calibration-arm coupling. For each member and preorder pair, forming \((3)\) scans \(m_0m_1\) cells and \((4)\) takes \(O(Mk_0k_1)\) operations. Two rolling arrays use \(O(k_0k_1)\) memory. After tabulating \(R_w\), enumeration therefore costs
\[
O\!\left(F_{m_0}F_{m_1}|\mathcal V|\{m_0m_1+Mk_0k_1\}\right)
\tag{7}
\]
operations and \(O(k_0k_1)\) working memory.

Now suppose exactly one rank equals \(M+1\). Write \(b\) for the boundary arm and \(c=1-b\), so \(k_c\le M\). By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), the boundary-arm event is certain and its score map, preorder, target lift, and calibration coordinate are irrelevant. Exact maximization therefore enumerates only total preorders of \(\mathcal O_c\). For fixed \(s_c\), define
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O}.
\tag{8}
\]
The same lemma gives the exact remaining rank-event probability
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}
\Pr\!\left\{\operatorname{Bin}\bigl(M,\theta(O_t)\bigr)<k_c\right\}.
\tag{9}
\]
Conditionally on \(O_{T,c}=O_t\), this follows because the number of calibration scores strictly below the target is binomial with parameters \(M\) and \(\theta(O_t)\), while \((1)\) requires this count to be less than \(k_c\). Averaging over the target orbit yields \((9)\). After the marginal \(q_c\) is tabulated, \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) shows that exact maximization enumerates only the \(F_{m_c}\) nonboundary preorders and takes
\[
O\!\left(F_{m_c}m_c\{m_c+Mk_c\}\right)
\tag{10}
\]
operations and \(O(k_c)\) rolling memory. Thus there is no factor \(F_{m_{1-c}}\), \(|\mathcal V|\), or per-case \(m_0m_1\) scan. If both ranks equal \(M+1\), both events are certain, so the frontier is \([(1-\alpha)-1]_+=0\), computable in constant time.

It remains to verify the binary obstruction. Take four pair blocks, let \(\mathcal G=S_2^4\), and use independent fair within-pair assignments with exactly one treated member per pair. Let \(\mathcal H\) be a singleton and \(w=1\). Conditional on assignment, the selector in either arm first chooses a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{11}
\]
and then chooses that block's unique observed member in the requested arm. This is an observable selector and is equivariant under every pair swap. Let
\[
q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},
\qquad
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),
\qquad r\in\{0,1\}.
\tag{12}
\]
The common target block has law \(p\), whereas the two auxiliary block choices are independent and each has law \(q\). Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\). By \(\texttt{lem:armwise-finite-rank-staircase}\), \(k_0=k_1=3\). Let \(s_0\equiv0\), and order the arm-one blocks as \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Arm one fails exactly when all three calibration blocks lie strictly below the target block, with probability
\[
F_{\mathrm{multi}}
=\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\tag{13}
\]
Arm zero never fails, so the four-level frontier objective is
\[
F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.
\tag{14}
\]
For a binary map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be its high-score blocks and set \(A_a=(1-q(H_a))^3\). Conditional on the common target block, inclusion--exclusion and independence of the auxiliary block choices give
\[
F_{\mathrm{bin}}(H_0,H_1)
=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{15}
\]
Ordering the sixteen possible choices of \(H_0\) as
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
exact substitution of all sixteen \(H_1\) choices in each row of \((15)\) gives row maxima, with denominator \(320000000\),
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{16}
\]
This exhausts all \(16^2\) binary pairs. The maximum failure probability is \(208582976/320000000=3259109/5000000\), so the largest binary objective is \(759109/5000000\). Its gap below \((14)\) is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\tag{17}
\]
Thus binary score pairs need not attain the frontier.

Finally, suppose target and calibration orbit supports are disjoint in an arm \(a\) with \(k_a\le M\). Give target-supported orbits in that arm score \(K\), all other orbits in that arm score zero, and every orbit in the other arm score zero. The target score in arm \(a\) is always \(K\), while all its calibration scores are zero. Its rank event is impossible, so the joint event has probability zero and the frontier objective is \(1-\alpha\). Since the positive-part deficit in \(\texttt{def:coverage-frontier}\) cannot exceed \(1-\alpha\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha.
\]
If \(k_a=M+1\), that event is certain and the frontier is exactly the other arm's optimization in \((8)\)--\((10)\). On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), and \(\texttt{def:coverage-frontier}\) identifies \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)\) with \(\Gamma_{M,\alpha}(w)\). The conclusions then specialize to \(\texttt{thm:sharp-orbit-coverage-frontier}\).