Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). If \(k_a\le M\), the elementary order-statistic identity gives
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Hence ties are handled by strict comparison, and the event depends on \(s_a\) only through its total preorder on \(\mathcal O_a\). If \(k_a=M+1\), then \(Q_{k_a}=+\infty\) by \(\texttt{def:rank-inversion}\), so that arm's event is certain.

Conversely, let a total preorder have ordered nonempty tie classes
\[
C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}.
\tag{2}
\]
If \(d_a=1\), assign score zero. If \(d_a>1\), assign \((j-1)K/(d_a-1)\) to class \(C_{a,j}\). Since \(K>0\), this is a score map into \([0,K]\), induces exactly the chosen preorder, and uses at most \(d_a\le m_a\) levels. Therefore the maximum in \(\texttt{def:coverage-frontier}\) is attained by finite enumeration of the relevant total preorders. This proves exactness for the declared bounded orbit-constant score class only; it does not identify a supremum over all \(P\in\mathcal P_{\mathcal G,K}\).

Suppose first that \(k_0,k_1\le M\). Apply \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). It tabulates the coherent common-target law
\[
P_T(O_0,O_1)=\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\mathbf 1\{O_0(v)=O_0,\ O_1(v)=O_1\}
\tag{3}
\]
and retains the full joint calibration law
\[
R_w(O_0,O_1)=\sum_z\nu(z)
\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).
\tag{4}
\]
Thus neither the two target lifts nor the two calibration selectors are factorized. For each preorder pair with class maps \(c_0,c_1\), the lemma pushes (3) forward to
\[
P_T^C(j,\ell)=
\sum_{\substack{O_0,O_1\\c_0(O_0)=j,\ c_1(O_1)=\ell}}
P_T(O_0,O_1)
\tag{5}
\]
and proves
\[
L_C(c_0,c_1):=|\operatorname{supp}(P_T^C)|
\le\min\{L,d_0d_1\}.
\tag{6}
\]
Its prefix-table formulas show that every supported target-orbit pair mapped to \((j,\ell)\) has the same four strict-below cell probabilities. The coupled recurrence in \(\texttt{lem:four-cell-rank-event-dynamic-program}\) is a function only of those four probabilities, \(M\), \(k_0\), and \(k_1\). Consequently all such orbit pairs have the same dynamic-program value, and their contributions aggregate exactly to \(P_T^C(j,\ell)\) times one run.

Let \(\mathfrak C\) denote all \(F_{m_0}F_{m_1}\) preorder pairs and let \(L_C=\max_{\mathfrak C}L_C(c_0,c_1)\). The cited lemma gives the exact instance-adaptive arithmetic bound
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)
+\{1+Mk_0k_1\}
\sum_{(c_0,c_1)\in\mathfrak C}L_C(c_0,c_1)
\right),
\tag{7}
\]
and hence
\[
O\!\left(|\mathcal V|+F_{m_0}F_{m_1}
\left[m_0m_1+L+L_C\{1+Mk_0k_1\}\right]\right).
\tag{8}
\]
The same lemma gives \(O(m_0m_1+L+k_0k_1)\) working memory. This proves every two-finite-rank assertion in the proposed statement.

Suppose next that exactly one rank \(k_b=M+1\), and put \(c=1-b\). By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), the boundary-arm event is certain and may be removed from the conjunction. Conditional on \(O_{T,c}=O_t\), (1) is the event that a binomial variable with success probability
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O}
\tag{9}
\]
is smaller than \(k_c\). Averaging over the target marginal proves
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}
\Pr\!\left\{\operatorname{Bin}(M,\theta(O_t))<k_c\right\}.
\tag{10}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), put
\[
q_j=q_c(C_j),\qquad p_j=p_c(C_j),\qquad
\theta_j=\sum_{\ell<j}q_\ell.
\tag{11}
\]
Every target orbit in \(C_j\) has the same value \(\theta_j\), so (10) becomes
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}.
\tag{12}
\]
A single ordered-class scan forms (11). For \(0<\theta<1\), the binomial mass ratios are
\[
t_0=(1-\theta)^M,\qquad
t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},
\tag{13}
\]
and
\[
u_M=\theta^M,\qquad
u_{r-1}=u_r\frac{r}{M-r+1}\frac{1-\theta}{\theta}.
\tag{14}
\]
These identities follow by dividing consecutive binomial probability masses. Exponentiation by squaring initializes \(t_0\) or \(u_M\) in \(O(\log M)\) operations. Summing the lower tail through \(k_c-1\), or subtracting the upper tail from one, and choosing the shorter calculation costs
\[
O\!\left(\log M+\min\{k_c,M-k_c+1\}\right)
\tag{15}
\]
with constant auxiliary memory, exactly as formalized in \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\). At \(\theta=0\), the binomial count is zero and the probability is one; at \(\theta=1\), it is \(M\) and the probability is zero because \(k_c\le M\). Thus no endpoint division occurs. Enumerating the \(F_{m_c}\) preorders proves the stated one-boundary complexity and the absence of every boundary-arm enumeration factor.

If both ranks equal \(M+1\), both events are certain. The probability inside \(\texttt{def:coverage-frontier}\) is one, and therefore
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=[(1-\alpha)-1]_+=0.
\tag{16}
\]

We next prove that binary maps need not attain the frontier. Take four pair blocks, \(\mathcal G=S_2^4\), independent fair within-pair assignments, and a singleton selector library. In each arm the selector chooses block \(b\) with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{17}
\]
and then chooses the unique member observed in that arm. This is an observable kernel by \(\texttt{ass:observable-selector-kernel}\), and swapping member labels within a pair swaps the selected observed member without changing the chosen block, so the kernel is equivariant. Let the common target block probabilities be
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),
\qquad q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2}.
\tag{18}
\]
For \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=3\).

Put \(s_0\equiv0\) and order the arm-one blocks as \(1\prec3\prec2\prec4\). Failure of arm one's rank event requires all three calibration blocks to lie strictly below the target block. Hence its failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\tag{19}
\]
Arm zero never fails, so the frontier objective is
\[
\frac{104957}{160000}-\frac12=\frac{24957}{160000}.
\tag{20}
\]

For binary maps let \(H_a\) be the high-score block set and write
\[
A_a=(1-q(H_a))^3.
\tag{21}
\]
Conditional on the common target block, arm \(a\) fails exactly when that block lies in \(H_a\) and all three independently selected calibration blocks lie outside \(H_a\). Inclusion--exclusion gives the probability of failure in at least one arm:
\[
F_{\mathrm{bin}}(H_0,H_1)
=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{22}
\]
Order the sixteen subsets as
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.
\]
For each fixed \(H_0\), exact substitution of all sixteen values of \(H_1\) into (22) gives the following row maxima, with common denominator \(320000000\):
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{23}
\]
This exhausts all \(16^2\) binary pairs. Their maximum failure probability is
\[
\frac{208582976}{320000000}=\frac{3259109}{5000000},
\]
so their maximum frontier objective is \(759109/5000000\). The four-level improvement is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\tag{24}
\]
Thus binary attainment is false.

Finally, suppose the target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Assign score \(K\) to every target-supported arm-\(a\) orbit, score zero to all remaining arm-\(a\) orbits, and score zero in the other arm. Every target score in arm \(a\) is \(K\), every calibration score there is zero, and \(Q_{k_a}=0\). Thus arm \(a\)'s rank event is impossible and the joint event has probability zero. By the positive-part definition,
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha,
\tag{25}
\]
which is the largest possible value. If one rank is at the boundary, equations (9)--(15) give the exact reduction to the other arm. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), and \(\texttt{def:coverage-frontier}\) gives \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w)\). This is precisely the symmetric specialization.