Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). The armwise staircase lemma gives \(k_0=k_1=k\), and the definition gives
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
Thus exactness over bounded orbit-constant score maps, finite total-preorder attainment, the coherent laws \(R_w\) and \(P_T\), the support inequalities, and exact-key global memoization all follow from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\) on this diagonal. In particular, when \(k\le M\), every score event is
\[
s_a(O_{T,a})\le Q_k(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k,
\tag{2}
\]
so only total preorders matter, and every preorder has the bounded representative constructed in the asymmetric proof. For each preorder pair, its exact rank-event probability is
\[
\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k,k}(\pi),
\tag{3}
\]
where every \(\pi\) is obtained from the unchanged full shared-assignment law and every \(\omega_C\) from the unchanged pushforward of the one common target. The key
\[
(M,k,k,\pi_{00},\pi_{01},\pi_{10}),\qquad \pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10},
\tag{4}
\]
therefore permits exactly the global reuse claimed in the theorem, and the coherent evaluator lemma yields its two displayed time bounds and memory bound.

For the synchronized sharper resource certificate, put
\[
\bar k=\min\{k,M-k+1\},\qquad C_{M,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2.
\tag{5}
\]
Complement each coordinate precisely when \(M-k+1<k\). For every exact key (4), the multinomial branch applies the feasible-count formula to the permuted four-cell law at thresholds \((\bar k,\bar k)\) and reconstructs the requested probability with the corner identities and exact binomial marginals. It costs \(M+\mathsf T_{M,\bar k,\bar k}\). The corner recurrence costs \(C_{M,k}\). If \(\mathsf B\) denotes the non-evaluator part of the theorem's instance-adaptive bound, the canonical diagonal hybrid therefore costs
\[
O\!\left(\mathsf B+M+G\min\{M+\mathsf T_{M,\bar k,\bar k},C_{M,k}\}\right)
\tag{6}
\]
and uses
\[
O\!\left(m_0m_1+L+U_{\max}+G+\max\{M,\bar k^2\}\right)
\tag{7}
\]
working memory. Factorials are shared once, multinomial power tables are rebuilt per key, and keys are processed sequentially. Since \(C_{M,k}\le M\bar k^2\le Mk^2\), (6)--(7) imply the formal theorem's coarser bounds. In particular, at \(k=M\), one has \(\bar k=1\), so the recurrence is linear in \(M\) per key.

If \(k=M+1\), both rank events are certain, and (1) gives \(\Gamma_{M,\alpha}(w)=0\). The four-pair construction in the asymmetric proof lies on the diagonal and establishes the four-level objective \(24957/160000\), the best binary objective \(759109/5000000\), and their positive gap \(83189/20000000\). Likewise, the disjoint-support construction in that proof gives a surely false rank event in one arm when \(k\le M\), and hence \(\Gamma_{M,\alpha}(w)=1-\alpha\). This proves every symmetric assertion.