Put \(N=M+1\). For any \(w\in\Delta(\mathcal H)\), the definition of \(A\) gives, for every arm--orbit row \((a,O)\),
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h A_{(a,O),h}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=q^{\mathrm{obs}}_{w,a}(O).
\]
The corresponding coordinate of \(b_{\mathrm{LP}}\) is \(q_{\mathrm{tar},a}(O)\). Hence \(Aw=b_{\mathrm{LP}}\) is equivalent, row by row and simultaneously for both arms, to joint orbit balance. Moreover, \(w\in\Delta(\mathcal H)\) is equivalent to \(w_h\ge 0\) for every \(h\) and \(\sum_h w_h=1\). Thus a jointly balancing common mixture exists if and only if the stacked linear program is feasible. Since
\[
Aw=\sum_{h\in\mathcal H}w_hA_{\cdot h},
\]
this is further equivalent to
\[
b_{\mathrm{LP}}\in\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\]

For completeness, the failure of feasibility has an explicit separating certificate. Let \(C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}\). Because \(\mathcal H\) is finite, \(C\) is compact. If \(b_{\mathrm{LP}}\notin C\), choose \(x_*\in C\) minimizing \(\lVert b_{\mathrm{LP}}-x\rVert_2\) over \(x\in C\), and set \(y=b_{\mathrm{LP}}-x_*\ne0\). For every \(x\in C\), the function \(t\mapsto\lVert b_{\mathrm{LP}}-[x_*+t(x-x_*)]\rVert_2^2\) has a right derivative at zero that is nonnegative. Therefore \(y^\top(x-x_*)\le0\), and consequently
\[
\max_{h\in\mathcal H}y^\top A_{\cdot h}=\sup_{x\in C}y^\top x\le y^\top x_*<y^\top b_{\mathrm{LP}},
\]
where the final strict gap is \(y^\top(b_{\mathrm{LP}}-x_*)=\lVert y\rVert_2^2>0\). Thus \(y\) is the asserted finite Farkas separating hyperplane.

Now fix a feasible \(w\) and condition throughout on \(\mathcal T\). Feasibility gives joint orbit balance, so \(\texttt{thm:orbit-balance-iff}\) implies that, for each arm \(a\) separately,
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are iid. Attach iid continuous auxiliary uniforms and order the resulting score--uniform pairs lexicographically, as permitted by \(\texttt{def:rank-inversion}\). Iid symmetry implies that the rank \(R_{0,a}\) of the target pair among these \(N\) pairs is uniform on \(\{1,\ldots,N\}\): indeed, almost surely every rank is occupied once, while permutation invariance gives the same probability to every labelled observation at every rank. If \(S_{0,a}>r_{a,(k)}\), at least \(k\) calibration scores are strictly smaller than \(S_{0,a}\), and hence \(R_{0,a}>k\). Therefore
\[
\Pr\{S_{0,a}>r_{a,(k)}\mid\mathcal T\}
\le \Pr\{R_{0,a}>k\mid\mathcal T\}
=\frac{N-k}{N}.
\]
This argument also covers \(k=N\): then \(r_{a,(k)}=+\infty\), both probabilities in the first display are zero, and the right side is zero.

By \(k=\lceil N(1-\alpha/2)\rceil\) and the integer identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\), the exact finite-rank error is
\[
\rho_{M,\alpha}:=\frac{N-k}{N}=\frac{\lfloor N\alpha/2\rfloor}{N}\le\frac{\alpha}{2}.
\]
Thus each armwise failure probability is at most \(\rho_{M,\alpha}\), retaining the exact rank count rather than replacing it immediately by \(\alpha/2\). If neither armwise failure occurs, then \(Y_{0T}(a)\in I_{a,w}\) for both \(a=0,1\), and hence
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I_{1,w}-I_{0,w}=\mathcal C_w.
\]
The union bound, which requires no independence between arms, now yields the strengthened staircase guarantee
\[
\Pr_P\{\tau_T\in\mathcal C_w\mid\mathcal T\}
\ge 1-2\rho_{M,\alpha}
=1-\frac{2\lfloor(M+1)\alpha/2\rfloor}{M+1}
\ge1-\alpha.
\]
Finally, if \(j=\lfloor N\alpha/2\rfloor\), then on every interval \(\alpha\in[2j/N,2(j+1)/N)\cap(0,1)\) the bound is the constant \(1-2j/N\). Its elbows occur at \(\alpha=2j/(M+1)\). In the \(j=0\) regime, namely \(0<\alpha<2/(M+1)\), one has \(k=M+1\), both reported intervals are \(\mathbb R\), and coverage is exactly one. This is the finite-rank boundary regime.