Condition on \(\mathcal T\) and fix an arm \(a\in\{0,1\}\). By \(\texttt{lem:orbit-score-factorization}\), define probability laws on orbit--score pairs by
\[
Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),\qquad
P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C)\tag{1}
\]
for Borel \(C\subseteq[0,\infty)\). Orbit overlap implies \(P_a\ll Q_a\). On every \(Q_a\)-supported orbit, a version of the likelihood ratio is
\[
\frac{dP_a}{dQ_a}(O,s)=\lambda_{a,O}.\tag{2}
\]
Indeed, when \(q_{a,O}>0\), the common conditional score factor \(F_{a,O}\) in equation \(1\) cancels and the ratio is \(p_{a,O}/q_{a,O}\); if \(q_{a,O}=0\), overlap gives \(p_{a,O}=0\). Thus the quotient likelihood ratio depends only on the orbit even when the target and calibration selector laws are mutually singular at the member level. The same factorization lemma gives iid calibration pairs from \(Q_a\), independently of the target pair from \(P_a\).

Apply \(\texttt{lem:finite-support-weighted-rank-validity}\) on the orbit--score space with \(X=(O,S)\), score map \(R(O,S)=S\), and likelihood ratio \(2\). Its augmented empirical measure is exactly the measure in \(\texttt{def:weighted-rank-inversion}\): calibration observation \(i\) receives mass \(\lambda_{a,O_{i,a}}\) at \(S_{i,a}\), and the target receives mass \(\lambda_{a,O_{T,a}}\) at \(+\infty\). Therefore
\[
\Pr\{S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\}\le\epsilon_a.\tag{3}
\]
Because \(Y_{0T}(a)\in[-K,K]\), clipping does not remove the target outcome when the un-clipped residual inequality holds, and in fact
\[
S_{0,a}\le r^{\mathrm W}_{a,w}\quad\Longleftrightarrow\quad Y_{0T}(a)\in I^{\mathrm W}_{a,w}.\tag{4}
\]
If both armwise events in \(4\) occur, then by the definition of a Minkowski difference,
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.\tag{5}
\]
The union bound applied to \(3\)--\(5\), without any cross-arm independence assumption, gives
\[
\Pr_P(\tau_T\in\mathcal C^{\mathrm W}_w\mid\mathcal T)\ge1-\epsilon_0-\epsilon_1\ge1-\alpha.\tag{6}
\]

Under joint orbit balance, \(p_{a,O}=q_{a,O}\) for every orbit. Hence \(\lambda_{a,O}=1\) on every orbit that can appear under either law; zero--zero orbits are never sampled. The normalized augmented measure consequently consists of \(M\) equal atoms at the calibration scores and one equal atom at \(+\infty\). Put \(N=M+1\) and \(k_a=\lceil N(1-\epsilon_a)\rceil\). Its left-continuous \((1-\epsilon_a)\)-quantile is the \(k_a\)-th calibration order statistic when \(k_a\le M\), and is \(+\infty\) when \(k_a=N\). Thus \(r^{\mathrm W}_{a,w}=r_{a,(k_a)}\), so the weighted procedure equals ordinary arm-specific rank inversion. Setting \(\epsilon_0=\epsilon_1=\alpha/2\) gives the stated common rank and the symmetric construction.

\paragraph{Comparator scope.} The one-arm weighted quantile inequality is the inherited likelihood-ratio weighted-exchangeability result of \cite{TibshiraniBarberCandesRamdas2019}, including the test-point mass at \(+\infty\); no new general weighted-exchangeability theorem is claimed. The design-specific deductions proved above are the finite orbit-quotient likelihood ratio, quotient overlap despite member-level singularity, and the combination of two armwise guarantees for one common causal target through clipping and Bonferroni. The causal and counterfactual target in \cite{LeiCandes2021}, the cluster-randomized target and design in \cite{WangLiYu2025}, and the general beyond-exchangeability setting of \cite{BarberCandesRamdasTibshirani2023} are scope comparators only; no priority assertion is made.