Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values assigned by \(s_a\) outside \(\mathcal O_a\) are immaterial. For a score map \(s_a\), define \(O\preceq_a O'\) if and only if \(s_a(O)\le s_a(O')\). This is a total preorder on \(\mathcal O_a\). For any fixed target orbit and calibration-orbit vector,
\[s_a(O_{T,a})\le Q_k\bigl(s_a(O_{1,a}),\ldots,s_a(O_{M,a})\bigr)\]
holds exactly when fewer than \(k\) calibration scores are strictly below the target score. That count depends only on \(\preceq_a\). Consequently the joint event in \(\texttt{def:coverage-frontier}\), and hence its probability, is unchanged when either score map is replaced by a map inducing the same total preorder.

Conversely, let a total preorder on \(\mathcal O_a\) have ordered nonempty equivalence classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\). If \(d_a=1\), assign score zero to its sole class. If \(d_a>1\), assign \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). Because \(K>0\), this is a map into \([0,K]\) inducing precisely the prescribed preorder, with \(d_a\le m_a\) levels. There are finitely many total preorders, namely
\[F_{m_a}=\sum_{d=1}^{m_a}d!\left\{\begin{matrix}m_a\\ d\end{matrix}\right\},\]
where the braces denote Stirling numbers of the second kind. Thus the objective is constant on each of the \(F_{m_0}F_{m_1}\) preorder pairs, every pair has an admissible representative, and enumeration attains the exact maximum defining \(\Gamma_{M,\alpha}(w)\). This proves exactness only for the bounded orbit-constant class appearing in \(\texttt{def:coverage-frontier}\); no passage to a supremum over invariant latent laws has been made.

The probability for a fixed preorder pair is an explicit finite sum. Define the orbit-level kernel and the joint calibration-orbit mass by
\[\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),\qquad R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).\]
The product auxiliary-selector law and independent replicated randomization make the \(M\) calibration orbit pairs iid with mass function \(R_w\). If \(O_a(v)\) denotes the orbit containing \((v,a)\), the joint coverage probability equals
\[\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)\!\sum_{((O_{i,0},O_{i,1}))_{i=1}^M\in(\mathcal O_0\times\mathcal O_1)^M}\!\left\{\prod_{i=1}^M R_w(O_{i,0},O_{i,1})\right\}\prod_{a=0}^1\mathbf 1\!\left\{s_a(O_a(v))\le Q_k\bigl(s_a(O_{1,a}),\ldots,s_a(O_{M,a})\bigr)\right\}.\]
This sum preserves the coherence of the two target lifts by summing over their one common base member \(v\), and it preserves the within-replicate cross-arm coupling through \(R_w\). For a fixed preorder and target member, a depth-\(M\) enumeration can maintain the running product and the two counts of calibration orbits strictly below the target, requiring constant arithmetic per tree edge. Hence, after tabulating \(R_w\), brute-force evaluation over all preorder pairs uses
\[O\!\left(F_{m_0}F_{m_1}|\mathcal V|(m_0m_1)^M\right)\]
arithmetic operations; the degenerate case \(m_0m_1=1\) is evaluated directly in constant time.

We next give the finite certificate disproving binary attainment. Take four pair blocks, \(\mathcal G=S_2^4\), and independent fair within-pair assignments having exactly one treated member in every pair. Let \(\mathcal H\) be a singleton and \(w=1\). Conditional on assignment, the arm-\(a\) kernel first chooses a block with probabilities
\[q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)\]
and then selects that block's unique observed arm-\(a\) member. This kernel is observable and equivariant, and its selected orbit is the chosen block. Set
\[q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},\qquad p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\qquad r\in\{0,1\}.\]
Thus the two target lifts share one target block with law \(p\). The product auxiliary randomization makes the two arms' calibration block sequences independent, each with law \(q\). Take \(M=3\) and \(\alpha=1/2\), so \(k=\lceil4(1-1/4)\rceil=3\). Put \(s_0\equiv0\), and order the arm-\(1\) blocks as \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Arm one fails exactly when all three calibration blocks lie strictly below the target block. Its failure probability is therefore
\[F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.\]
Arm zero never fails, so this four-level pair has frontier objective
\[F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.\]
For a binary map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be the blocks receiving the high score and put \(A_a=(1-q(H_a))^3\). Conditional independence of the armwise calibration sequences, together with the common target block, gives the exact union-of-failures probability
\[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\]
Using concatenation for subsets, take the row order
\[\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.\]
Direct exact substitution of all sixteen choices of \(H_1\) in each row gives the following numerators of \(\max_{H_1}F_{\mathrm{bin}}(H_0,H_1)\), over the common denominator \(320000000\):
\[\begin{split}(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).\end{split}\]
This table exhausts all \(16^2\) binary pairs. Its largest entry is \(208582976/320000000=3259109/5000000\), attained, for example, at \(H_0=\{2,4\}\) and \(H_1=\{3,4\}\). Hence the largest binary frontier objective is
\[\frac{3259109}{5000000}-\frac12=\frac{759109}{5000000},\]
and the strict advantage of the four-level pair is
\[\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\]
This admissible matched-pair instance proves that binary attainment is false.

Finally, suppose target and calibration orbit supports are disjoint in one arm and \(k\le M\). Assign score \(K\) to precisely the target-supported orbits in that arm and zero to all its other orbits; assign zero throughout the other arm. The adverse-arm target score is \(K\) almost surely, all adverse-arm calibration scores are zero, and their \(k\)-th order statistic is zero. The other-arm inequality always holds, so the joint coverage event has probability zero. The frontier objective is then \(1-\alpha\), and it cannot exceed \(1-\alpha\) because a probability is nonnegative. Therefore \(\Gamma_{M,\alpha}(w)=1-\alpha\), in agreement with \(\texttt{prop:disjoint-orbit-witness}\). If \(k=M+1\), then \(Q_k=+\infty\); both inequalities hold for every bounded score configuration, so their joint probability is one and \(\Gamma_{M,\alpha}(w)=[(1-\alpha)-1]_+=0\), in agreement with \(\texttt{prop:rank-boundary}\).