Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,
\qquad
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
Therefore the exact score-class interpretation, preorder attainment, unchanged coherent laws, local weights, exact memo keys, binary counterexample, and disjoint-support value follow from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). Its support-domain proof also shows that all integrated selector laws ignore arbitrary off-support kernel extensions.

Assume \(k\le M\). Specializing the asymmetric partition gives the displayed seven disjoint strata. Since
\[
\bar k_0=\bar k_1=\bar k=\min\{k,M-k+1\},
\]
the rolling charge becomes
\[
\mathsf C_{M,k,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2.
\]
Substitution into the asymmetric branch sum gives exactly \(\mathsf B_{\mathrm{sym}}\), including the face and rank-one charges. The same substitution gives \(\mathsf W_{\mathrm{sym}}\); vertex, edge, face, and rank-one branches have constant workspace and do not trigger the factorial table. Substitution in the adaptive, uniform, and memory formulas proves all displayed diagonal resource bounds.

For every \(M\ge2\), taking \(\alpha=2/(M+1)\) gives \(k=M\). The complete support-domain edge audit in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) realizes \(\pi=(1/2,1/2,0,0)\), and
\[
D_{M,M,M}(\pi)=1-2^{-M}.
\]
The edge charge is \(\Theta(\log M)\), whereas the former dispatcher charge is \(\Theta(M)\). At the same diagonal rank, the complete three-point-support face audit realizes \(\pi=(1/3,1/3,1/3,0)\) and gives
\[
D_{M,M,M}(\pi)=1-2\cdot3^{-M},
\]
with \(\Theta(\log M)\) face cost and constant workspace versus \(\Theta(M)\) for every former branch. The off-diagonal rank-one audit is a strict certificate for the common evaluator; on the diagonal the identical determinant test has charge
\[
\mathsf R_{M,k,k}=1+2\lceil\log_2M\rceil+2\bar k.
\]
If \(k=M+1\), \(\texttt{prop:rank-boundary}\) makes both events certain, so \(\Gamma_{M,\alpha}(w)=0\). The exact binary values and positive gap, and the value \(1-\alpha\) under disjoint support, follow from the asymmetric theorem through (1). Because each computational branch changes only the evaluation of a fixed strict-prefix probability, all common-target, active-arm, pair-audit, empty-library, ordinary-rank, and weighted-orbit semantics are preserved.