Assume \(\mathcal V_b=\{v_{b,0},v_{b,1}\}\) and \(\langle s_b\rangle\le\mathcal G\). By \texttt{def:pair-action}, the nonidentity element satisfies
\[
s_b(v_{b,r},a)=(v_{b,1-r},a),\qquad r,a\in\{0,1\},
\tag{1}
\]
fixes every member outside block \(b\), and acts on complete records through \texttt{def:group-action}. Every element of \(\mathcal G\) preserves blocks. Since block \(b\) contains exactly the two displayed members, the orbit of either \((v_{b,r},a)\) cannot leave their two-state pair cell; (1) shows that it reaches both states. Therefore, under this local specialization and only under it,
\[
\operatorname{Orb}_{\mathcal G}(v_{b,r},a)=O_{b,a}=\{(v_{b,0},a),(v_{b,1},a)\},\qquad a\in\{0,1\}.
\tag{2}
\]
Suppose the target arm-\(1\) lifted law is supported on \(O_{b,1}\). Its arm-one orbit vector consequently assigns mass one to the row \((1,O_{b,1})\). An exclusive mate-control analogue is supported on a control-labelled state in the distinct arm-zero cell \(O_{b,0}\), because the group action preserves arm labels. Its mass in row \((1,O_{b,1})\) is therefore zero. Thus the analogue's stacked orbit vector differs from the target vector, and the equations in \texttt{def:joint-orbit-balance}, equivalently the relevant equations in \texttt{def:common-selector-feasibility-lp}, cannot hold. Independently, \texttt{ass:observable-selector-kernel} requires an arm-one selector to put mass only on members with \(z_v=1\); a mate's control-labelled state is not a legal arm-one selection.

Now consider a legal implemented arm-one selector with \(q^{\mathrm{obs}}_{w,1}(O_{b,1})=0\). Since the target arm-one lift is supported on the single orbit \(O_{b,1}\), every target-supported arm-one orbit has zero calibration mass. Hence \texttt{prop:disjoint-orbit-witness} applies with \(a=1\) and gives zero coverage when \(k\le M\). If \(k=M+1\), \texttt{prop:rank-boundary} instead gives \(\mathcal C_w=[-2K,2K]\) and coverage one.