Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). If \(k_a\le M\), the elementary order-statistic identity gives
\[s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\iff\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.\tag{1}\]
Thus ties are handled by strict comparison and the event depends on \(s_a\) only through its total preorder. Conversely, if the ordered nonempty tie classes are \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes the preorder in \([0,K]\) with at most \(m_a\) levels. Since there are finitely many preorder pairs, the maximum in \(\texttt{def:coverage-frontier}\) is attained and is exactly the declared worst deficit over bounded orbit-constant maps. No law-level supremum is introduced.

Suppose first that \(k_0,k_1\le M\). Apply \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). For every preorder pair \(C\),
\[U_C\le L_C\le\min\{L,d_0d_1\},\qquad \Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).\tag{2}\]
Put \(h_a=M-k_a+1\), \(\bar k_a=\min\{k_a,h_a\}\), and define \(\mathsf C_{M,k_0,k_1}\), the deterministically tie-broken partition \(\Pi_\star=\Pi_{\mathrm{roll}}\mathbin{\dot\cup}\Pi_{\mathrm{MS}}\mathbin{\dot\cup}\Pi_+\), the charge \(\mathsf B\), and the actual-branch workspace \(\mathsf W\) exactly as in that lemma. Equation (2), local grouping, global exact-key lookup, and its three-way evaluator prove the proposed instance-adaptive time bound with terminal term \(\mathsf B\), its uniform specialization, and memory
\[O(m_0m_1+L+U_{\max}+G+\mathsf W).\tag{3}\]
The multinomial factorial cost occurs once if and only if \(\Pi_{\mathrm{MS}}\ne\varnothing\), since its factorial table is shared while its probability-specific power tables are rebuilt per assigned key. Empty branch sums are zero and the singleton \(\{0\}\) in the definition of \(\mathsf W\) makes every empty-branch case well-defined. Every \(\pi\) is formed from the unchanged full \(R_w\), and every local \(\omega_C\) from the unchanged coherent \(P_T^C\); consequently neither memoization nor branch selection changes shared-assignment dependence, the common target, the common selector, or the frontier probability. At \(k_0=k_1=M\), \(\bar k_0=\bar k_1=1\) and the rolling per-key charge is \(\mathsf C_{M,M,M}=M\), strictly improving the coarse \(\Theta(M^3)\) charge to \(\Theta(M)\); the positive-corner branch can be smaller when its minimizing positive-base orientation permits it.

Suppose exactly one rank \(k_b=M+1\), and put \(c=1-b\). The boundary-arm event is certain by \(\texttt{prop:asymmetric-rank-boundary}\). Conditional on \(O_{T,c}=O_t\), (1) is a binomial count with parameter
\[\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O}.\]
Target independence therefore gives
\[\sum_{O_t\in\mathcal O_c}p_{c,O_t}\Pr\{\operatorname{Bin}(M,\theta(O_t))<k_c\}.\tag{4}\]
By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), for ordered tie classes \(C_1\prec\cdots\prec C_d\), (4) equals \(\sum_jp_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}\), where \(q_j=q_c(C_j)\), \(p_j=p_c(C_j)\), and \(\theta_j=\sum_{\ell<j}q_\ell\). One scan forms these quantities. For \(0<\theta<1\), consecutive lower-tail terms and upper-tail terms obey
\[t_0=(1-\theta)^M,\qquad t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},\tag{5}\]
\[u_M=\theta^M,\qquad u_{r-1}=u_r\frac r{M-r+1}\frac{1-\theta}{\theta}.\tag{6}\]
The first power costs \(O(\log M)\) by exponentiation by squaring, and summing the shorter tail costs \(O(\min\{k_c,M-k_c+1\})\). At \(\theta=0\) and \(1\), the answers are one and zero without division. Enumerating only the \(F_{m_c}\) nonboundary preorders proves the proposed one-boundary time and memory bound. If both ranks equal \(M+1\), both events are certain, and the frontier is \([(1-\alpha)-1]_+=0\).

It remains to verify the two sharpness assertions about the score class. For the nonbinary certificate, use four pair blocks, \(\mathcal G=S_2^4\), fair independent within-pair assignment, and a singleton selector. Let each arm choose a block with calibration probabilities
\[q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right),\]
and let the common target choose a block with probabilities
\[p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),\]
splitting equally within the chosen pair. These rules are observable and equivariant. Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Put \(s_0\equiv0\) and order arm-one blocks as \(1\prec3\prec2\prec4\). The failure probability is
\[\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000},\]
so the frontier objective is \(24957/160000\). For a binary score pair, let \(H_a\) be arm \(a\)'s high-score block set and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion gives
\[F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.\tag{7}\]
In the row order \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\), exhaustive exact substitution of the sixteen choices for the other row gives maximum numerators
\[\begin{split}(164616000,&165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000)\end{split}\]
over denominator \(320000000\). Hence every binary pair has objective at most \(759109/5000000\), and the four-level gap is
\[\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.\tag{8}\]
Finally, if target and calibration supports are disjoint in an active arm, assign score \(K\) to its target-supported orbits and zero elsewhere, and assign zero throughout the other arm. The active-arm rank event then fails surely, so the deficit reaches its maximum possible value \(1-\alpha\). At a boundary rank that arm's event is certain and (4) is exactly the remaining arm's event. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), proving the asserted reduction to \(\texttt{thm:sharp-orbit-coverage-frontier}\).