Put \(R_i=\sum_{j=1}^i b_0(E_{j,0})\) and \(S_i=\sum_{j=1}^i b_1(E_{j,1})\). At \(i=0\), \(d_0(0,0)=1\). If the retained entries at stage \(i\) equal the corresponding probabilities, independence of draw \(i+1\) and the definition of \(\pi\) give
\[
\Pr\{R_{i+1}=r,S_{i+1}=s\}
=\sum_{x,y\in\{0,1\}}\pi_{xy}
 \Pr\{R_i=r-x,S_i=s-y\}.
\tag{1}
\]
Both increments are nonnegative, so a state discarded after reaching either strict threshold cannot return. Induction proves the recurrence and the terminal rectangle sum. Forming \(\pi\) scans \(R\) once; each of \(M\) stages has at most \(k_0k_1\) retained states and two rolling arrays suffice. This proves the generic time and memory bounds. A rank \(M+1\) is never reached by a count of \(M\) Bernoulli increments. Deleting one such coordinate gives the one-dimensional recurrence, and deleting both makes the event certain.

If \(\pi\) has support one at \(u=(x,y)\), every increment equals \(u\), so
\[
(R_M,S_M)=(Mx,My)
\]
almost surely, proving the vertex formula. If its support is \(\{u,v\}\), orient it deterministically and let \(I_i\) indicate the atom \(v\). Then
\(N=\sum_i I_i\sim\operatorname{Bin}(M,\pi_v)\), and
\[
R_M=Mu_0+(v_0-u_0)N,\qquad
S_M=Mu_1+(v_1-u_1)N.
\tag{2}
\]
For coordinate \(a\), the inequality is an upper bound on \(N\) when
\(d_a=1\), a lower bound when \(d_a=-1\), automatic or impossible when
\(d_a=0\). Intersecting those conditions with \(0\le N\le M\) gives exactly
\([L_\pi,U_\pi]\), including its empty convention. The three interval evaluators in
\(\texttt{def:simplex-vertex-key-prepass}\), together with
\(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), prove the exact charge
\(\mathsf E_M(\pi)\) and constant workspace. Reversing the support orientation replaces \(N\) by \(M-N\), so deterministic least-charge choice and tie-breaking preserve the answer.

Finally let a remaining support-three key have an admissible face orientation. Since \(\pi^\sigma_{11}=0\), every transformed increment satisfies \(B_{i0}^\sigma+B_{i1}^\sigma\le1\), and hence
\(T_0^\sigma+T_1^\sigma\le M\). The inequality
\(t_0^\sigma+t_1^\sigma>M\) makes the two transformed upper-tail events disjoint. Thus
\[
J_\sigma=1-\Pr\{T_0^\sigma\ge t_0^\sigma\}
-\Pr\{T_1^\sigma\ge t_1^\sigma\}.
\tag{3}
\]
The two marginals are binomial. Exact shorter-tail evaluation, complementation, and the four corner identities give the original lower--lower probability with the charge \(\mathsf F_M(\pi)\) and constant workspace proved in
\(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\). Reconstruction introduces no duplicate marginal evaluation. Therefore only support-at-least-three keys not selected by the face prepass can reach a generic bivariate evaluator.