Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). Suppose first that \(k_a\le M\). For a fixed target orbit, the order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\Longleftrightarrow
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by the strict comparison in (1), and the event depends on \(s_a\) only through its total preorder. Conversely, if a total preorder has ordered nonempty classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). Hence every preorder has a representative in \([0,K]\) with at most \(m_a\) levels. The finite maximum in \(\texttt{def:coverage-frontier}\) is therefore attained by preorder enumeration. This proves exactness over the declared score-map class and makes no assertion about a supremum over latent laws.

Assume \(k_0,k_1\le M\). By \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\), the unchanged shared-assignment law \(R_w\) and coherent common-target law \(P_T\) give, for every preorder pair \(C\),
\[
U_C\le L_C\le\min\{L,d_0d_1\},\qquad
\Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
The exact key \((M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10})\) determines the recurrence probability in (2), while \(\omega_C\) is applied only when the preorder objective is formed. The local grouping, global lookup, one recurrence computation for each of the \(G\) keys, and table-construction charges in that lemma give the stated instance-adaptive time bound, its uniform specialization, and the memory bound. Every \(\pi\) is formed from the full \(R_w\), and every \(\omega_C\) from the pushforward of the single \(P_T\), so memoization changes computation but neither law. The exact alternatives in \(\texttt{lem:four-cell-multinomial-sum-alternative}\) and \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) compute the same per-key probability. Selecting the rolling recurrence for every key proves the displayed coarser charges \(GMk_0k_1\) and \(O(k_0k_1)\).

Suppose exactly one rank \(k_b=M+1\), and put \(c=1-b\). The boundary event is certain by \(\texttt{def:rank-inversion}\). Conditional on \(O_{T,c}=O_t\), (1) counts iid Bernoulli trials with success probability
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O}.
\tag{3}
\]
The calibration orbit draws are iid by \(\texttt{ass:known-matched-randomization}\) and \(\texttt{ass:selector-auxiliary-randomization}\), and are independent of the target by \(\texttt{ass:prespecified-target}\). Consequently the exact rank-event probability is
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}\Pr\!\left\{\operatorname{Bin}(M,\theta(O_t))<k_c\right\}.
\tag{4}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), put \(q_j=q_c(C_j)\), \(p_j=p_c(C_j)\), and \(\theta_j=\sum_{\ell<j}q_\ell\). Every target orbit in class \(j\) has the same strict-prefix probability, so (4) becomes
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}.
\tag{5}
\]
One cumulative ordered-class scan forms all these quantities. For \(0<\theta<1\), the exact lower-tail terms satisfy
\[
t_0=(1-\theta)^M,\qquad t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},\quad 0\le r<k_c-1,
\tag{6}
\]
and the exact upper-tail terms satisfy
\[
u_M=\theta^M,\qquad u_{r-1}=u_r\frac r{M-r+1}\frac{1-\theta}{\theta},\quad k_c<r\le M.
\tag{7}
\]
Exponentiation by squaring initializes (6) or (7) in \(O(\log M)\) operations, and summing the shorter tail costs \(O(\min\{k_c,M-k_c+1\})\) further operations. At \(\theta=0\) and \(\theta=1\), the probabilities in (5) are respectively one and zero without division. By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) and \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\), enumeration of only the \(F_{m_c}\) nonboundary preorders therefore costs
\[
O\!\left(F_{m_c}m_c[1+\log M+\min\{k_c,M-k_c+1\}]\right)
\tag{8}
\]
operations and \(O(1)\) auxiliary CDF memory after the marginal vectors are tabulated. Formula (5) has no boundary-arm preorder, member-level scan, or cross-arm table.

If both ranks equal \(M+1\), both rank events are certain, and thus
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=[(1-\alpha)-1]_+=0.
\tag{9}
\]

It remains to disprove binary attainment. Consider four pair blocks with \(\mathcal G=S_2^4\), which contains every audited pure local swap. Randomize treatment fairly and independently within pairs. Let an equivariant selector first choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{10}
\]
and then choose the unique member observed in the requested arm. Let the common target choose a block with probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right)
\tag{11}
\]
and choose either member of that block with equal probability. These rules obey selector observability and equivariance, and the two auxiliary arm draws are independent conditional on assignment. Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Set \(s_0\equiv0\) and order the arm-one blocks as \(1\prec3\prec2\prec4\). The arm-zero event is certain. Direct strict-prefix evaluation gives joint failure probability
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\tag{12}
\]
Therefore the frontier objective is
\[
\frac{104957}{160000}-\frac12=\frac{24957}{160000}.
\tag{13}
\]
For a binary score pair, let \(H_a\) be arm \(a\)'s high-score block set and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion, retaining the common target and independent auxiliary block choices, gives exact joint failure probability
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{14}
\]
There are sixteen subsets. In the order \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\), exact substitution in (14), maximizing over \(H_1\) in each successive \(H_0\)-row, gives the numerators
\[
\begin{gathered}
164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000
\end{gathered}
\tag{15}
\]
over the common denominator \(320000000\). Hence the largest binary failure probability is \(3259109/5000000\), and every binary objective is at most
\[
\frac{3259109}{5000000}-\frac12=\frac{759109}{5000000}.
\tag{16}
\]
The difference between (13) and (16) is \(83189/20000000>0\), proving the claimed failure of binary attainment.

Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Assign score \(K\) to target-supported arm-\(a\) orbits and zero to calibration-supported and remaining arm-\(a\) orbits; assign score zero throughout the other arm. The arm-\(a\) rank event fails surely, so the joint event has probability zero. The deficit equals \(1-\alpha\), and no positive-part deficit can exceed \(1-\alpha\). Therefore \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha\). If \(k_a=M+1\), that arm's event is certain, and (4)--(5) give exactly the other arm's rank event. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), yielding \(\texttt{thm:sharp-orbit-coverage-frontier}\).