Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). Suppose first that \(k_a\le M\). For any fixed target orbit, the elementary order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))\Longleftrightarrow\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by the strict comparison in (1), and the event depends on \(s_a\) only through its total preorder. Conversely, if a total preorder has ordered nonempty classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). Every preorder therefore has a representative in \([0,K]\) with at most \(m_a\) levels. The declared finite maximum is consequently attained by preorder enumeration. This establishes exactness over the score-map class in \texttt{def:coverage-frontier}; it does not identify the maximum with a supremum over latent laws.

Assume first that \(k_0,k_1\le M\). By \texttt{lem:coherent-two-finite-rank-frontier-evaluator}, the unchanged shared-assignment law \(R_w\) and coherent common-target law \(P_T\) give, for every preorder pair \(C\),
\[
U_C\le L_C\le\min\{L,d_0d_1\},\qquad \Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
The exact key \((M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10})\) determines the count probability in (2), while \(\omega_C\) is applied only when the preorder objective is formed. The local grouping, global lookup, one recurrence computation for each of the \(G\) keys, and table-construction charges established in that lemma yield the stated instance-adaptive time bound, its uniform specialization, and the memory bound. Every \(\pi\) is formed from the full \(R_w\), and every \(\omega_C\) from the pushforward of the one \(P_T\), so memoization changes computation but not either probability law. The zero-cell-safe multinomial summation, corner-oriented rolling recurrence, and positive-base coefficient recurrence supplied by \texttt{lem:four-cell-multinomial-sum-alternative} and \texttt{lem:corner-oriented-four-cell-rank-evaluator} are exact alternatives for each key; always choosing the rolling recurrence proves the coarser displayed charges \(GMk_0k_1\) and \(O(k_0k_1)\).

Suppose next that exactly one rank, \(k_b\), equals \(M+1\), and put \(c=1-b\). By \texttt{def:rank-inversion}, the boundary event is certain. Conditional on \(O_{T,c}=O_t\), (1) counts iid Bernoulli trials with success probability
\[
\theta(O_t)=\sum_{O\in\mathcal O_c:s_c(O)<s_c(O_t)}q_{c,O}.
\tag{3}
\]
The calibration orbit draws are iid by \texttt{ass:known-matched-randomization} and \texttt{ass:selector-auxiliary-randomization}, and are independent of the target by \texttt{ass:prespecified-target}. Hence the exact joint rank-event probability is
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}\Pr\!\left\{\operatorname{Bin}(M,\theta(O_t))<k_c\right\}.
\tag{4}
\]
For ordered tie classes \(C_1\prec\cdots\prec C_d\), let \(q_j=q_c(C_j)\), \(p_j=p_c(C_j)\), and \(\theta_j=\sum_{\ell<j}q_\ell\). Every target orbit in class \(j\) has the same strict-prefix probability, so (4) becomes
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}.
\tag{5}
\]
One ordered-class scan forms all three sequences. For \(0<\theta<1\), consecutive binomial probabilities give
\[
t_0=(1-\theta)^M,\qquad t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},
\tag{6}
\]
and, from the upper endpoint,
\[
u_M=\theta^M,\qquad u_{r-1}=u_r\frac r{M-r+1}\frac{1-\theta}{\theta}.
\tag{7}
\]
Exponentiation by squaring initializes (6) or (7) in \(O(\log M)\) operations. Summing the shorter of the lower tail and complementary upper tail takes \(O(\min\{k_c,M-k_c+1\})\) further operations. At \(\theta=0\), the probability in (5) is one, and at \(\theta=1\) it is zero, with no division. By \texttt{lem:one-boundary-orbit-frontier-evaluator}, enumerating only the \(F_{m_c}\) nonboundary preorders therefore has exactly the asserted time and memory bounds and introduces no factor from the boundary arm.

If both ranks equal \(M+1\), both rank events are certain. Therefore the expression in \texttt{def:coverage-frontier} is \([(1-\alpha)-1]_+=0\), proving the two-boundary claim.

It remains to prove that binary attainment is false. Consider four pair blocks with \(\mathcal G=S_2^4\), so every local subgroup required by \texttt{def:pair-action} is present. Randomize treatment fairly and independently within pairs. Let an equivariant selector first choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{8}
\]
and then choose the unique member observed in the requested arm. Let the common target choose a block with probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right)
\tag{9}
\]
and choose either member of that block with equal probability. These rules are legal and equivariant, and the two armwise auxiliary block draws are independent conditional on assignment as required. Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Set \(s_0\equiv0\) and order arm-one blocks as \(1\prec3\prec2\prec4\). The arm-zero event is certain, and direct strict-prefix evaluation gives failure probability
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\tag{10}
\]
Thus the frontier objective is \(104957/160000-1/2=24957/160000\). For a binary score pair, let \(H_a\) be arm \(a\)'s high-score block set and put \(A_a=(1-q(H_a))^3\). Inclusion--exclusion, using the one common target and independent auxiliary block draws, gives the exact joint failure probability
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{11}
\]
There are only sixteen subsets. Enumerate them in the order \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\). Exact substitution in (11), maximizing over \(H_1\) in each successive row \(H_0\), gives, with common denominator \(320000000\),
\[
(164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\tag{12}
\]
The maximum in (12) is \(3259109/5000000\). Therefore every binary pair has objective at most \(759109/5000000\), and the four-level objective exceeds it by
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.
\tag{13}
\]
Finally, suppose target and calibration orbit supports are disjoint in arm \(a\) and \(k_a\le M\). Assign score \(K\) to target-supported arm-\(a\) orbits and zero to all calibration-supported or remaining orbits, and assign score zero throughout the other arm. The arm-\(a\) rank event fails surely, so the joint event has probability zero. Since a positive-part deficit cannot exceed \(1-\alpha\), the frontier equals \(1-\alpha\). If \(k_a=M+1\), that arm's event is certain and (4)--(5) give exactly the other arm's rank event. On the diagonal, \texttt{lem:armwise-finite-rank-staircase} gives \(k_0=k_1=k\), yielding \texttt{thm:sharp-orbit-coverage-frontier}.