Condition throughout on \(\mathcal T\), and fix an arm \(a\in\{0,1\}\). The trained map \(\widehat m_a\) is then fixed. By \(\texttt{lem:orbit-score-factorization}\), the calibration orbit--score pairs are independent and identically distributed with law
\[\mathsf Q_a(\{O\}\times C)=q_{a,O}F_{a,O}(C),\]
and the independent target pair has law
\[\mathsf P_a(\{O\}\times C)=p_{a,O}F_{a,O}(C).\]
Orbit overlap gives \(\mathsf P_a\ll\mathsf Q_a\), and their Radon--Nikodym derivative is constant on each orbit fibre:
\[\frac{d\mathsf P_a}{d\mathsf Q_a}(O,s)=\lambda_{a,O}.\]
Thus \(\texttt{lem:finite-support-weighted-rank-validity}\), with \(\varepsilon=\alpha/2\), applies to the \(M\) calibration pairs and the target pair. Its infinity-augmented weighted quantile is exactly \(r^{\mathrm W}_{a,w}\) from \(\texttt{def:weighted-rank-inversion}\). Indeed, the target draw has \(p_{a,O_{T,a}}>0\) almost surely, so overlap implies \(q_{a,O_{T,a}}>0\) and hence \(\lambda_{a,O_{T,a}}>0\); consequently the normalizing total weight is positive. The lemma yields
\[\Pr\{S_{0,a}>r^{\mathrm W}_{a,w}\mid\mathcal T\}\le \frac{\alpha}{2}.\]
This argument uses only the orbit-level derivative. Therefore it remains valid even if the implemented selector and the target selector are mutually singular at the member level inside an orbit: the common conditional score kernel \(F_{a,O}\) supplied by orbit invariance cancels from the likelihood ratio.

Define \(E_a=\{S_{0,a}\le r^{\mathrm W}_{a,w}\}\). On \(E_a\), the definition of the absolute residual gives
\[Y_{0T}(a)\in I^{\mathrm W}_{a,w}.\]
No independence between \(E_0\) and \(E_1\) is required. The union bound and the two armwise inequalities give
\[\Pr(E_0\cap E_1\mid\mathcal T)\ge 1-\Pr(E_0^c\mid\mathcal T)-\Pr(E_1^c\mid\mathcal T)\ge1-\alpha.\]
On \(E_0\cap E_1\), set subtraction implies
\[\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I^{\mathrm W}_{1,w}-I^{\mathrm W}_{0,w}=\mathcal C^{\mathrm W}_w.\]
This proves the asserted conditional coverage uniformly over the stated invariant law class and the arbitrary fixed measurable trained maps.

Finally, suppose joint orbit balance holds. By \(\texttt{thm:orbit-balance-iff}\), \(p_{a,O}=q_{a,O}\) for every arm and orbit. Hence \(\lambda_{a,O}=1\) on every orbit that can actually be drawn by either the calibration or target selector; orbits with \(p_{a,O}=q_{a,O}=0\) are irrelevant. The normalized weighted measure therefore has unit mass at each of the \(M\) calibration scores and unit mass at \(+\infty\). Its left-continuous \((1-\alpha/2)\)-quantile is the \(k\)-th order statistic for \(k=\lceil(M+1)(1-\alpha/2)\rceil\): it equals \(r_{a,(k)}\) when \(k\le M\) and \(+\infty\) when \(k=M+1\). Thus \(r^{\mathrm W}_{a,w}=r_{a,(k)}\) in both arms, and the weighted construction reduces exactly to the ordinary rank inversion in \(\texttt{def:rank-inversion}\).