Set \(\varepsilon_0=\varepsilon_1=\alpha/2\). By \(\texttt{lem:armwise-finite-rank-staircase}\),
\[
k_0=k_1=k,\qquad
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=\Gamma_{M,\alpha}(w).
\tag{1}
\]
Therefore the exact score-class interpretation, preorder attainment, unchanged coherent laws, local weights, exact memo keys, binary counterexample, and disjoint-support value follow from \(\texttt{thm:asymmetric-sharp-orbit-coverage-frontier}\). Its proof and \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) also show explicitly that arbitrary total kernel extensions off \(\operatorname{supp}(\nu)\) disappear from every integrated selector law.

Assume \(k\le M\). Specializing the asymmetric partition yields the displayed seven disjoint strata. Since
\[
\bar k_0=\bar k_1=\bar k=\min\{k,M-k+1\},
\]
the rolling charge becomes
\[
\mathsf C_{M,k,k}=\sum_{i=0}^{M-1}\min\{\bar k,i+1\}^2.
\]
Substitution in the asymmetric branch sum gives exactly \(\mathsf B_{\mathrm{sym}}\), including the face and rank-one terms. The same substitution gives \(\mathsf W_{\mathrm{sym}}\); the vertex, edge, face, and rank-one evaluators use constant workspace and do not trigger factorial preprocessing. Substitution in the adaptive, uniform, and memory formulas proves all displayed diagonal resource bounds.

For every \(M\ge2\), taking \(\alpha=2/(M+1)\) gives \(k=M\). The complete supported-assignment edge audit in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) realizes \(\pi=(1/2,1/2,0,0)\), and hence
\[
D_{M,M,M}(\pi)=1-2^{-M}.
\]
Its edge charge is \(\Theta(\log M)\), whereas the former dispatcher charge is \(\Theta(M)\). At the same diagonal rank, the complete three-point-support face audit realizes \(\pi=(1/3,1/3,1/3,0)\) and gives
\[
D_{M,M,M}(\pi)=1-2\cdot3^{-M},
\]
with \(\Theta(\log M)\) time and constant workspace versus \(\Theta(M)\) for every former branch. The off-diagonal rank-one audit remains a strict certificate for the common evaluator; on the diagonal the same determinant test has charge
\[
\mathsf R_{M,k,k}=1+2\lceil\log_2M\rceil+2\bar k.
\]
If \(k=M+1\), \(\texttt{prop:rank-boundary}\) makes both rank events certain, so \(\Gamma_{M,\alpha}(w)=0\). The exact binary values and their positive gap, and the value \(1-\alpha\) under disjoint support, follow from the asymmetric theorem through (1). Every branch computes the same strict-prefix probability, so the common-target, active-arm, pair-audit, empty-library, ordinary-rank, and weighted-orbit semantics are unchanged.