Under \(\mathcal G=S_2\times S_2\), the first factor swaps only the two members of block one and the second swaps only the two members of block two. By \(\texttt{def:pair-action}\), the action preserves arm labels and cannot move a state between blocks. Its orbits are therefore exactly\n\[O_{1,0},\ O_{1,1},\ O_{2,0},\ O_{2,1}.\]\nIf \(q_{\mathrm{tar}}\) concentrates on \(v_{1,0}\), then \(T^1=(v_{1,0},1)\in O_{1,1}\) almost surely, so the arm-\(1\) target orbit vector has value one on \(O_{1,1}\) and zero on the other arm-\(1\) orbit. The exclusive mate-control state \((v_{1,1},0)\) lies in \(O_{1,0}\), so its vector has value zero on \(O_{1,1}\). Hence the target equation for the \((1,O_{1,1})\) row of the stacked system in \(\texttt{def:common-selector-feasibility-lp}\) fails. In addition, \(\texttt{ass:observable-selector-kernel}\) rules out a control-labelled state as the output of an arm-\(1\) selector. Thus the mate-control analogue cannot be both jointly balancing and a legal arm-\(1\) selector.\n\nSuppose instead that a legal implemented arm-\(1\) selector has \(q^{\mathrm{obs}}_{w,1}(O_{1,1})=0\). Since \(O_{1,1}\) is the sole target-supported arm-\(1\) orbit, the premise of \(\texttt{prop:disjoint-orbit-witness}\) holds. If \(k\le M\), that proposition gives \(\mathcal C_w=\{0\}\) and conditional coverage zero. If \(k=M+1\), \(\texttt{prop:rank-boundary}\) gives\n\[I_{0,w}=I_{1,w}=[-K,K],\qquad \mathcal C_w=[-2K,2K],\]\nand conditional coverage one. This proves every assertion in the finite sanity check.