Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\) and \(m_a=|\mathcal O_a|\). Values of \(s_a\) outside \(\mathcal O_a\) are irrelevant. If \(k_a\le M\), define \(O\preceq_a O'\) if and only if \(s_a(O)\le s_a(O')\). For every target orbit and calibration-orbit vector, the order-statistic identity
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\quad\Longleftrightarrow\quad
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a
\tag{1}
\]
holds: the \(k_a\)-th order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by strict comparison on the right of \((1)\), and the rank event depends only on the total preorder induced by \(s_a\). If \(k_a=M+1\), then \(Q_{k_a}=+\infty\), so the event is identically true and imposes no restriction on the score map in that arm.

Conversely, let a total preorder on \(\mathcal O_a\) have ordered nonempty tie classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\). If \(d_a=1\), assign score zero to its only class. If \(d_a>1\), assign score \((j-1)K/(d_a-1)\) to every orbit in \(C_{a,j}\). Since \(K>0\), this is a map into \([0,K]\) that induces exactly the prescribed preorder and has \(d_a\le m_a\) levels. The number of total preorders on an \(m_a\)-element labelled set is
\[
F_{m_a}=\sum_{d=1}^{m_a}d!\left\{\begin{matrix}m_a\\ d\end{matrix}\right\},
\tag{2}
\]
where the braces denote Stirling numbers of the second kind. Hence, when both ranks are finite, the objective in \(\texttt{def:coverage-frontier}\) is constant on each of the finitely many \(F_{m_0}F_{m_1}\) preorder pairs, and every such pair has an admissible representative. This proves attainment and exactness over the declared class of bounded orbit-constant score maps. It does not assert equality with a supremum over all laws in \(\mathcal P_{\mathcal G,K}\).

We next derive the evaluator when both ranks are finite. Define the orbit-level selector kernel and its one-replicate joint orbit law by
\[
\kappa_{w,a}(O\mid z)=\sum_{v:(v,a)\in O}\kappa_{w,a}(v\mid z),
\qquad
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z).
\tag{3}
\]
The product kernel in \(\texttt{ass:selector-auxiliary-randomization}\) makes the two auxiliary draws conditionally independent given their shared assignment. The product assignment law in \(\texttt{ass:known-matched-randomization}\) then implies that the calibration orbit pairs are independent and identically distributed across replicates with mass function \(R_w\). Formula \((3)\) retains the within-replicate cross-arm dependence generated by the common assignment.

Fix a target member \(v\) and a preorder pair. Let \(O_a(v)\) be the orbit containing \((v,a)\), and put
\[
b_a(O;v)=\mathbf 1\{s_a(O)<s_a(O_a(v))\}.
\]
Collapse \(R_w\) to
\[
\pi_{xy}(v)=\sum_{O_0\in\mathcal O_0}\sum_{O_1\in\mathcal O_1}R_w(O_0,O_1)
\mathbf 1\{b_0(O_0;v)=x,\ b_1(O_1;v)=y\},
\qquad (x,y)\in\{0,1\}^2.
\tag{4}
\]
For \(k_0,k_1\le M\), initialize \(d_0(0,0)=1\), set the other entries to zero, and update
\[
d_{i+1}(r,s)=\sum_{x=0}^1\sum_{y=0}^1\pi_{xy}(v)d_i(r-x,s-y),
\qquad 0\le r<k_0,\quad 0\le s<k_1,
\tag{5}
\]
where out-of-range entries are zero. By \(\texttt{lem:four-cell-rank-event-dynamic-program}\),
\[
\sum_{r=0}^{k_0-1}\sum_{s=0}^{k_1-1}d_M(r,s)
=\Pr\!\left\{\sum_{i=1}^M b_0(O_{i,0};v)<k_0,\ \sum_{i=1}^M b_1(O_{i,1};v)<k_1\right\}.
\tag{6}
\]
By \((1)\), this is the conditional joint rank-event probability for target member \(v\). Since the one common target satisfies \(T\sim q_{\mathrm{tar}}\), the probability in the frontier is
\[
\sum_{v\in\mathcal V}q_{\mathrm{tar}}(v)
\sum_{r=0}^{k_0-1}\sum_{s=0}^{k_1-1}d_M^{(v)}(r,s).
\tag{7}
\]
The single sum over \(v\) preserves coherence of the two target-arm lifts, and the four-cell law preserves calibration-arm coupling. For every target and preorder pair, constructing \((4)\) scans \(m_0m_1\) cells and \((5)\) uses \(O(Mk_0k_1)\) arithmetic operations. Rolling two arrays gives \(O(k_0k_1)\) memory. Consequently, after \(R_w\) is tabulated, exact enumeration takes
\[
O\!\left(F_{m_0}F_{m_1}|\mathcal V|\{m_0m_1+Mk_0k_1\}\right)
\tag{8}
\]
arithmetic operations and \(O(k_0k_1)\) working memory.

Now suppose exactly one rank is \(M+1\), and let \(c\) denote the other arm, with \(k_c\le M\). Lemma \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\) proves that the boundary-arm event, score map, preorder, target lift, and calibration coordinate are all irrelevant. For a fixed nonboundary preorder it gives the exact probability
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}
\Pr\!\left\{\operatorname{Bin}\bigl(M,\theta(O_t)\bigr)<k_c\right\},
\qquad
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O},
\tag{9}
\]
and exact evaluation time
\[
O\!\left(F_{m_c}m_c\{m_c+Mk_c\}\right)
\tag{10}
\]
with \(O(k_c)\) memory after the marginal \(q_c\) is tabulated. This is sharper than the theorem's printed one-boundary upper bound and, in particular, proves it: \(F_{m_{1-c}}\ge1\), \(m_{1-c}\ge1\), and \(|\mathcal V|\ge m_c\), so the order in \((10)\) is bounded by
\[
O\!\left(F_{m_0}F_{m_1}|\mathcal V|\{m_0m_1+Mk_c\}\right).
\]
If both ranks equal \(M+1\), both events are identically true. Their joint probability is one, so the frontier objective is \([(1-\alpha)-1]_+=0\), obtained in constant time.

It remains to prove that binary maps need not attain the maximum. Take four pair blocks, \(\mathcal G=S_2^4\), and independent fair within-pair assignments with exactly one treated member per pair. Let \(\mathcal H\) be a singleton and \(w=1\). Conditional on assignment, let each arm selector first choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{11}
\]
and then select that block's unique observed member in the requested arm. The kernel is observable and equivariant under every pair swap. Put
\[
q_{\mathrm{tar}}(v_{b,r})=\frac{p_b}{2},
\qquad
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right),
\qquad r\in\{0,1\}.
\tag{12}
\]
Thus the common target block has law \(p\), while the two auxiliary block choices are independent and each has law \(q\). Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Let \(s_0\equiv0\), and order the arm-one blocks as \(1\prec_1 3\prec_1 2\prec_1 4\), represented by \(0,K/3,2K/3,K\). Arm one fails exactly when all three calibration blocks are strictly below the target block. Hence
\[
F_{\mathrm{multi}}=\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\tag{13}
\]
Arm zero never fails, so the four-level frontier objective is
\[
F_{\mathrm{multi}}-\alpha=\frac{24957}{160000}.
\tag{14}
\]
For a binary map in arm \(a\), let \(H_a\subseteq\{1,2,3,4\}\) be its high-score blocks and set \(A_a=(1-q(H_a))^3\). Conditional on the common target block, inclusion--exclusion gives the exact probability of at least one arm failure:
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{15}
\]
Order the sixteen possible \(H_0\) as
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234.
\]
Exact substitution of all sixteen possibilities for \(H_1\) yields the row maxima, with common denominator \(320000000\),
\[
\begin{split}
(&164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,\\
&203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\end{split}
\tag{16}
\]
This exhausts all \(16^2\) binary pairs. The largest failure probability is \(208582976/320000000=3259109/5000000\), so the largest binary objective is
\[
\frac{3259109}{5000000}-\frac12=\frac{759109}{5000000}.
\]
Its gap below \((14)\) is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\tag{17}
\]
Thus binary attainment is false in an admissible asymmetric instance.

Finally, suppose target and calibration orbit supports are disjoint in an arm \(a\) with \(k_a\le M\). Assign score \(K\) to the target-supported orbits of arm \(a\), score zero to its other orbits, and score zero throughout the other arm. The target score in arm \(a\) is always \(K\), all its calibration scores are zero, and its rank event is impossible. The joint rank event therefore has probability zero and the frontier objective equals \(1-\alpha\). Since the positive-part objective can never exceed \(1-\alpha\),
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)=1-\alpha.
\]
This is consistent with \(\texttt{prop:asymmetric-disjoint-orbit-witness}\). If \(k_a=M+1\), its event is identically true and the frontier is exactly the other arm's rank-event optimization, as made explicit by \((9)\). On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), lemma \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), and \(\texttt{def:coverage-frontier}\) identifies \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)\) with \(\Gamma_{M,\alpha}(w)\). All conclusions then specialize to \(\texttt{thm:sharp-orbit-coverage-frontier}\).