Fix the adverse arm \(a\). Under \(\texttt{def:disjoint-orbit-law}\), the arm-\(a\) outcome equals \(K\) on every target-supported arm-\(a\) orbit and zero on every orbit with positive calibration mass and on all remaining orbits; the other-arm outcome and both predictors are zero. The prescriptions are consistent by the disjoint-support premise. The prototype is constant on every actual \(\mathcal G\)-orbit, and left multiplication preserves its uniform group randomizer. Hence latent invariance holds. All outcomes lie in \(\{0,K\}\subseteq[-K,K]\), so
\[
P\in\mathcal P_{\mathcal G,K}.
\tag{1}
\]
The known design, iid replication, and auxiliary product draws supply the declared experiment. By selector observability and \(\texttt{def:observable-selector-mixture}\), a selected calibration state has positive integrated calibration mass. Its outcome is zero in the adverse arm, and every outcome is zero in the other arm. Thus
\[
S_{i,0}=S_{i,1}=0\qquad(1\le i\le M).
\tag{2}
\]
Target prespecification puts \(T^a\) in a target-supported orbit almost surely, whence
\[
\tau_T=\begin{cases}K,&a=1,\\-K,&a=0.\end{cases}
\tag{3}
\]
If both ranks are at most \(M\), (2) makes both thresholds zero, so both intervals and the effect set equal \(\{0\}\); (3) proves zero coverage. If exactly one rank equals \(M+1\), \(\texttt{prop:asymmetric-rank-boundary}\) makes that interval \([-K,K]\), while (2) makes the finite-rank interval \(\{0\}\). Their Minkowski difference is \([-K,K]\), which contains both values in (3), so this witness has coverage one. If both ranks equal \(M+1\), the effect set is \([-2K,2K]\) and coverage is one. With \(N=M+1\),
\[
k_c\le M\iff \lceil N(1-\varepsilon_c)\rceil\le N-1\iff \varepsilon_c\ge N^{-1}.
\]
On the equal-split diagonal the ranks coincide, recovering \(\texttt{prop:disjoint-orbit-witness}\) in the finite-rank regime and the boundary result otherwise.