Condition throughout on \(\mathcal T\). Write \(A_{\cdot h}\) for column \(h\) of \(A\). For any \(w\in\Delta(\mathcal H)\) and every row \((a,O)\), the definitions of \(A\) and the integrated mixture law give
\[
(Aw)_{a,O}=\sum_{h\in\mathcal H}w_h\sum_{u\in O}q^{\mathrm{obs}}_{h,a}(u)=\sum_{u\in O}q^{\mathrm{obs}}_{w,a}(u)=q^{\mathrm{obs}}_{w,a}(O).
\]
The corresponding coordinate of the target vector is
\[
(b_{\mathrm{LP}})_{a,O}=\sum_{u\in O}q_{\mathrm{tar},a}(u)=q_{\mathrm{tar},a}(O).
\]
Consequently, \(Aw=b_{\mathrm{LP}}\) holds if and only if \(w\) jointly orbit-balances both arms. Moreover,
\[
\{Aw:w\in\Delta(\mathcal H)\}=\left\{\sum_{h\in\mathcal H}w_hA_{\cdot h}:w_h\ge0,\ \sum_{h\in\mathcal H}w_h=1\right\}=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\]
Thus a jointly balancing \(w\) exists exactly when \(b_{\mathrm{LP}}\) belongs to the displayed convex hull, and the coordinate conditions together with \(w_h\ge0\) and \(\sum_h w_h=1\) are exactly the stacked program in \(\texttt{def:common-selector-feasibility-lp}\).

We next construct the asserted infeasibility certificate. Let
\[
C=\operatorname{conv}\{A_{\cdot h}:h\in\mathcal H\}.
\]
Because \(\mathcal H\) is finite, \(C\) is compact. If \(b_{\mathrm{LP}}\notin C\), choose \(c^*\in C\) minimizing \(\lVert b_{\mathrm{LP}}-c\rVert_2\), and put \(y=b_{\mathrm{LP}}-c^*\ne0\). For any \(c\in C\) and \(t\in(0,1]\), convexity gives \(c^*+t(c-c^*)\in C\). Minimality of \(c^*\) therefore yields
\[
0\le\lVert b_{\mathrm{LP}}-c^*-t(c-c^*)\rVert_2^2-\lVert b_{\mathrm{LP}}-c^*\rVert_2^2=-2t y^\top(c-c^*)+t^2\lVert c-c^*\rVert_2^2.
\]
After division by \(t\) and passage to \(t\downarrow0\), this gives \(y^\top c\le y^\top c^*\). Hence
\[
y^\top b_{\mathrm{LP}}=y^\top c^*+\lVert y\rVert_2^2>y^\top c^*=\sup_{c\in C}y^\top c=\max_{h\in\mathcal H}y^\top A_{\cdot h}.
\]
Thus \(y\), together with any threshold strictly between the last two quantities, is the claimed Farkas separating hyperplane.

Now fix a feasible \(w\). The first part proves joint orbit balance, so \(\texttt{thm:orbit-balance-iff}\) implies that, for each fixed arm \(a\),
\[
S_{1,a},\ldots,S_{M,a},S_{0,a}
\]
are independent and identically distributed conditional on \(\mathcal T\). Put \(N=M+1\), and append independent \(\operatorname{Unif}(0,1)\) variables \(V_{0,a},\ldots,V_{M,a}\) solely for lexicographic tie-breaking. The \(N\) pairs \((S_{i,a},V_{i,a})\) are conditionally independent and identically distributed and almost surely distinct. Permutation symmetry then makes the target pair's lexicographic rank \(R_{0,a}\) uniform on \(\{1,\ldots,N\}\).

If \(k\le M\) and \(S_{0,a}>r_{a,(k)}\), at least \(k\) calibration scores are strictly smaller than \(S_{0,a}\), so \(R_{0,a}>k\). If \(k=N=M+1\), then \(r_{a,(k)}=+\infty\) and the event is empty. Therefore, in both cases,
\[
\Pr(S_{0,a}>r_{a,(k)}\mid\mathcal T)\le\Pr(R_{0,a}>k\mid\mathcal T)=\frac{N-k}{N}=\frac{M+1-k}{M+1}.
\]
Since \(k=\lceil N(1-\alpha/2)\rceil\), the integer identity \(N-\lceil N-x\rceil=\lfloor x\rfloor\) gives
\[
\frac{N-k}{N}=\frac{\lfloor N\alpha/2\rfloor}{N}=\rho_{M,\alpha}\le\frac{\alpha}{2},
\]
where the middle equality is \(\texttt{def:finite-rank-error}\).

Under the bounded-support construction in \(\texttt{def:rank-inversion}\),
\[
I_{a,w}=\bigl[\widehat m_a(X_{0T})-r_{a,(k)},\widehat m_a(X_{0T})+r_{a,(k)}\bigr]\cap[-K,K].
\]
By \(\texttt{ass:bounded-potential-outcomes}\), \(Y_{0T}(a)\in[-K,K]\). Consequently, including when \(r_{a,(k)}=+\infty\),
\[
Y_{0T}(a)\in I_{a,w}\quad\Longleftrightarrow\quad |Y_{0T}(a)-\widehat m_a(X_{0T})|\le r_{a,(k)}\quad\Longleftrightarrow\quad S_{0,a}\le r_{a,(k)}.
\]
On the intersection of the two armwise inclusion events,
\[
\tau_T=Y_{0T}(1)-Y_{0T}(0)\in I_{1,w}-I_{0,w}=\mathcal C_w.
\]
The conditional union bound, which requires no independence between arms, now yields
\[
\Pr(\tau_T\in\mathcal C_w\mid\mathcal T)\ge1-\sum_{a=0}^1\Pr(S_{0,a}>r_{a,(k)}\mid\mathcal T)\ge1-2\rho_{M,\alpha}\ge1-\alpha.
\]
This proves every assertion.