Write \(\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}\). When \(k_a\le M\), the order-statistic identity is
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the \(k_a\)-th calibration order statistic is strictly below the target score exactly when at least \(k_a\) calibration scores are strictly below it. Thus ties are handled by strict comparison, and the event depends on \(s_a\) only through its total preorder. Conversely, if a preorder has ordered nonempty classes \(C_{a,1}\prec_a\cdots\prec_a C_{a,d_a}\), assign score zero when \(d_a=1\), and otherwise assign \((j-1)K/(d_a-1)\) to class \(j\). This realizes it in \([0,K]\) with at most \(m_a\) levels. Consequently the maximum defining \(\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)\) is attained by finite preorder enumeration. This is exactness for the declared orbit-constant score class, not for all invariant latent laws.

Suppose first that both ranks are finite. The coherent evaluator forms the unchanged laws
\[
R_w(O_0,O_1)=\sum_z\nu(z)\kappa_{w,0}(O_0\mid z)\kappa_{w,1}(O_1\mid z),
\qquad
P_T(O_0,O_1)=\sum_vq_{\mathrm{tar}}(v)\mathbf 1\{O_0(v)=O_0,O_1(v)=O_1\}.
\tag{2}
\]
For every preorder pair it proves
\[
U_C\le L_C\le\min\{L,d_0d_1\},\qquad
\Pr\{\text{both rank events}\}=\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{3}
\]
Thus the exact key \((M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10})\) determines the count probability, while the local coherent weight never enters that computation. The local grouping and global lookup bounds, one computation for each of the \(G\) keys, and the table work in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\) give both displayed time bounds and the memory bound in the theorem. Equation (2) shows that neither calibration dependence nor common-target coherence is altered.

The synchronized exact evaluator is stronger. Define
\[
C_{M,k_0,k_1}=\sum_{i=0}^{M-1}\min\{\bar k_0,i+1\}\min\{\bar k_1,i+1\}.
\]
For each exact key, compare the zero-cell-safe permuted multinomial cost \(M+\mathsf T_{M,\bar k_0,\bar k_1}\), the rolling-corner cost \(C_{M,k_0,k_1}\), and the positive-corner coefficient cost \(\mathsf C_+(\pi)\). The last is finite because some four-cell atom is positive, and it includes precisely the exact marginal tails required by the selected corner identity. With \(\mathsf B\) denoting the non-evaluator portion and with the same three-way partition of distinct keys as in the coherent lemma, the exact time is the charge in its equation (7). Its equation (8) gives the workspace of the branch partition actually selected. In particular, one may use the simpler safe bounds in the theorem because the rolling branch has \(C_{M,k_0,k_1}\le Mk_0k_1\), the coefficient width is at most \(M\), and keys are processed sequentially.

Suppose exactly one rank \(k_b=M+1\), and put \(c=1-b\). The boundary event is certain. By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), conditional on \(O_{T,c}=O_t\), the remaining strict-below count is binomial with success probability
\[
\theta(O_t)=\sum_{O:s_c(O)<s_c(O_t)}q_{c,O},
\]
so the exact event probability is
\[
\sum_{O_t}p_{c,O_t}\Pr\{\operatorname{Bin}(M,\theta(O_t))<k_c\}.
\tag{4}
\]
Grouping an ordered preorder into classes gives exactly the displayed sum \(\sum_jp_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}\). One scan forms the cumulative masses. For \(0<\theta<1\), ratios of consecutive binomial probabilities give the stated \(t_r\) and \(u_r\) recurrences; exponentiation by squaring and \(\texttt{lem:exact-binomial-shorter-tail-evaluator}\) give \(O(\log M+\min\{k_c,M-k_c+1\})\) time and constant CDF memory. At \(0\) and \(1\), degeneracy gives probabilities one and zero. Because only the nonboundary preorder appears in (4), enumeration has precisely the claimed one-arm complexity. If both ranks equal \(M+1\), both events are certain, and the positive part of \((1-\alpha)-1\) is zero.

It remains to verify the extremal assertions. For nonbinary attainment, take four pair blocks with \(\mathcal G=S_2^4\). This product contains \(\langle s_b\rangle\) for every invoked block, so \(\texttt{def:pair-action}\) identifies the displayed pair cells with global orbits. Use fair independent within-pair assignment, and an equivariant kernel that first selects a block with probabilities
\[
q=(13/20,1/20,1/4,1/20)
\]
and then selects that block's member observed in the requested arm. Let the common target block probabilities be
\[
p=(1/20,1/10,1/4,3/5),\qquad q_{\mathrm{tar}}(v_{b,r})=p_b/2.
\]
These choices satisfy observability, equivariance, invariant randomization, and common-target selection. Put \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\), so \(k_0=k_1=3\). Take \(s_0\equiv0\) and order the arm-one block orbits as \(1\prec3\prec2\prec4\). Arm zero succeeds surely and direct substitution gives arm-one failure probability
\[
\frac14\left(\frac{13}{20}\right)^3+\frac1{10}\left(\frac{18}{20}\right)^3+\frac35\left(\frac{19}{20}\right)^3=\frac{104957}{160000}.
\tag{5}
\]
Thus the frontier objective is \(24957/160000\). For binary maps, let \(H_a\) be the high-score block set and \(A_a=(1-q(H_a))^3\). Conditional inclusion--exclusion gives joint failure
\[
F_{\mathrm{bin}}(H_0,H_1)=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{6}
\]
Order the sixteen subsets as \(\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234\). Exhaustive exact substitution over \(H_1\) gives, for these successive \(H_0\), row maxima with denominator \(320000000\):
\[
(164616000,165302000,192052000,198366000,207906936,165912000,164712000,165787368,203032000,208582976,208582976,164632000,165793875,164631423,202894331,164616000).
\]
Hence the largest binary failure is \(3259109/5000000\), the largest binary objective is \(759109/5000000\), and the four-level advantage is
\[
\frac{24957}{160000}-\frac{759109}{5000000}=\frac{83189}{20000000}>0.
\]
Finally, if target and calibration supports are disjoint in arm \(a\) and \(k_a\le M\), give target-supported orbits score \(K\), all other arm-\(a\) orbits score zero, and every orbit in the other arm score zero. The arm-\(a\) rank event then fails surely, so the joint event has probability zero and the frontier equals its maximal possible value \(1-\alpha\). The one-boundary reduction was already proved in (4). On the diagonal, the armwise staircase gives \(k_0=k_1=k\), proving the asserted reduction to the symmetric theorem.