Fix an arm \(a\in\{0,1\}\) and condition on \(\mathcal T\). By \(\texttt{lem:orbit-score-factorization}\), for every Borel set \(C\subseteq[0,\infty)\),
\[
\Pr(S_{i,a}\in C\mid\mathcal T)=\sum_{O\subseteq\mathcal U_a}q_{a,O}F_{a,O}(C),\qquad\Pr(S_{0,a}\in C\mid\mathcal T)=\sum_{O\subseteq\mathcal U_a}p_{a,O}F_{a,O}(C).
\tag{1}
\]
If joint orbit balance holds, then \(q_{a,O}=p_{a,O}\) for every arm and orbit by \(\texttt{def:joint-orbit-balance}\), so (1) proves equality of the two score laws for every \(P\in\mathcal P_{\mathcal G,K}\) and every fixed measurable predictor. The same factorization lemma states that the \(M\) calibration orbit--score pairs are iid and independent of the target pair. Their score marginals now coincide, hence \(S_{1,a},\ldots,S_{M,a},S_{0,a}\) are iid conditional on \(\mathcal T\). This is an armwise assertion and gives no cross-arm independence or exchangeability.

Conversely, suppose balance fails. Then for some arm \(a\) and orbit \(O_\star\subseteq\mathcal U_a\),
\[
q_{a,O_\star}\ne p_{a,O_\star}.
\tag{2}
\]
Use \(\texttt{def:orbit-separating-law}\) with \(\widehat m_0=\widehat m_1=0\). Its arm-\(a\) outcome is \(Y_v(a)=K\mathbf 1\{(v,a)\in O_\star\}\), and its other-arm outcome is zero. All outcomes lie in \([-K,K]\). If \(L^\star\) is the prototype and \(G_0\) is uniform on the finite group, then for every \(h\in\mathcal G\), \(hG_0L^\star\) and \(G_0L^\star\) have the same law because left multiplication permutes the uniform group law. Thus the symmetrized law is \(\mathcal G\)-invariant and belongs to \(\mathcal P_{\mathcal G,K}\). Independent copies and the known assignment law give the declared replicated experiment.

On every assignment with positive \(\nu\)-mass, \(\texttt{ass:observable-selector-kernel}\) selects a member observed in arm \(a\). Assignments outside the support have zero contribution to the integrated selector law. Therefore
\[
S_{i,a}=K\mathbf 1\{U_{i,a}\in O_\star\},\qquad S_{0,a}=K\mathbf 1\{T^a\in O_\star\}.
\tag{3}
\]
Since \(K>0\), (2)--(3) imply
\[
\Pr(S_{i,a}=K\mid\mathcal T)=q_{a,O_\star}\ne p_{a,O_\star}=\Pr(S_{0,a}=K\mid\mathcal T).
\]
Thus universal equality of the armwise score laws forces every orbit mass to agree. Together with the first implication, this proves the equivalence and the stated witness.