For any row set \(\mathcal I\subseteq\{(a,O):a\in\{0,1\},\ O\in\mathcal O\}\), let \(A_{\mathcal I}\) and \(b_{\mathcal I}\) denote the corresponding restrictions of \(A\) and \(b_{\mathrm{LP}}\), and define
\[
d_{\mathcal I}(w)=\frac12\lVert A_{\mathcal I}w-b_{\mathcal I}\rVert_1.
\tag{1}
\]
Take \(\mathcal I_{\mathrm{all}}\) to be all rows and \(\mathcal I_{\mathcal A}=\{(a,O):a\in\mathcal A_{\boldsymbol\varepsilon},\ O\in\mathcal O\}\). The row identities in \(\texttt{thm:common-selector-lp}\) give
\[
d_{\mathcal I_{\mathrm{all}}}(w)=\Delta_0(w)+\Delta_1(w),\qquad
d_{\mathcal I_{\mathcal A}}(w)=\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w).
\tag{2}
\]
Because \(\mathcal H\) is finite and nonempty, \(\Delta(\mathcal H)\) is a nonempty compact simplex. Each function in (1) is continuous, so both minima are attained. This proves nonemptiness of \(\mathcal W_*\) and \(\mathcal W_{*,\mathcal A}\). If \(\mathcal I_{\mathcal A}=\varnothing\), then the second function in (1) is identically zero, and therefore
\[
D_{*,\mathcal A}=0,\qquad \mathcal W_{*,\mathcal A}=\Delta(\mathcal H).
\tag{3}
\]
No optimization is needed in this case.

For either nonempty row set \(\mathcal I\), the two-sided absolute-value constraints are equivalent to
\[
t_j\ge |(A_{\mathcal I}w-b_{\mathcal I})_j|\qquad(j\in\mathcal I).
\tag{4}
\]
Thus every feasible objective is at least \(d_{\mathcal I}(w)\), while equality in (4) attains exactly that value. The full and active-row primal programs consequently have values \(D_*\) and \(D_{*,\mathcal A}\), respectively, and their optimizing \(w\)-coordinates are precisely the declared optimizer sets.

We next prove both dual identities without assuming strong duality. Fix a nonempty \(\mathcal I\), and put
\[
C_{\mathcal I}=\operatorname{conv}\{(A_{\cdot h})_{\mathcal I}:h\in\mathcal H\},\qquad b=b_{\mathcal I},\qquad D_{\mathcal I}=\min_{c\in C_{\mathcal I}}\frac12\lVert c-b\rVert_1.
\tag{5}
\]
For every \(y\) with \(\lVert y\rVert_\infty\le1/2\), every \(c\in C_{\mathcal I}\) satisfies
\[
y^\top(c-b)\le\lVert y\rVert_\infty\lVert c-b\rVert_1\le\frac12\lVert c-b\rVert_1.
\tag{6}
\]
Taking the minimum over \(c\) and then the maximum over \(y\) proves weak duality. If \(D_{\mathcal I}=0\), the feasible vector \(y=0\) attains equality. Suppose \(D_{\mathcal I}>0\). For \(n\ge2\), let \(r_n=(1-1/n)D_{\mathcal I}\) and
\[
B_n=\{x:\tfrac12\lVert x-b\rVert_1\le r_n\}.
\]
The nonempty compact convex sets \(B_n\) and \(C_{\mathcal I}\) are disjoint. Choose a Euclidean closest pair \((c_n,x_n)\in C_{\mathcal I}\times B_n\) and put \(v_n=c_n-x_n\ne0\). Minimality along line segments in the two sets gives
\[
\min_{c\in C_{\mathcal I}}v_n^\top c=v_n^\top c_n>v_n^\top x_n=\max_{x\in B_n}v_n^\top x.
\tag{7}
\]
Normalize \(y_n=v_n/(2\lVert v_n\rVert_\infty)\). The support function of the \(\ell_1\)-ball is
\[
\max_{x\in B_n}y_n^\top x=y_n^\top b+2r_n\lVert y_n\rVert_\infty=y_n^\top b+r_n.
\tag{8}
\]
Equations (7)--(8) imply
\[
\min_{c\in C_{\mathcal I}}y_n^\top c-y_n^\top b>r_n.
\tag{9}
\]
The cube \(\{y:\lVert y\rVert_\infty\le1/2\}\) is compact, so a subsequence converges to \(y_*\). Because \(\mathcal H\) is finite, \(y\mapsto\min_h y^\top(A_{\cdot h})_{\mathcal I}\) is continuous. Letting \(n\to\infty\) in (9) and combining with (6) proves the attained identity
\[
D_{\mathcal I}=\max_{\lVert y\rVert_\infty\le1/2}
\left\{\min_{h\in\mathcal H}y^\top(A_{\cdot h})_{\mathcal I}-y^\top b_{\mathcal I}\right\}.
\tag{10}
\]
For the full row set, (10) is the displayed dual for \(D_*\). For the active row set, extend \(y\) by zero on inactive rows; (10) becomes exactly
\[
D_{*,\mathcal A}=\max_{\substack{\lVert y\rVert_\infty\le1/2\\y_{a,O}=0\ \mathrm{for}\ a\notin\mathcal A_{\boldsymbol\varepsilon}}}
\left\{\min_{h\in\mathcal H}y^\top A_{\cdot h}-y^\top b_{\mathrm{LP}}\right\}.
\tag{11}
\]
When the active set is empty, the only permitted embedded vector is zero, so (11) also has value zero and agrees with (3).

If \(D_*>0\) and \(y\) maximizes the full dual, then \(y^\top A_{\cdot h}\ge y^\top b_{\mathrm{LP}}+D_*\) for every \(h\). Thus \(z=-y\) satisfies
\[
z^\top b_{\mathrm{LP}}\ge\max_{h\in\mathcal H}z^\top A_{\cdot h}+D_*,
\tag{12}
\]
which is the Farkas separation with margin \(D_*\). Nonnegativity and attainment in (1) show that \(D_*=0\) exactly when some \(w\) satisfies all rows of \(Aw=b_{\mathrm{LP}}\), which \(\texttt{thm:common-selector-lp}\) identifies with exact joint balance. Likewise, \(D_{*,\mathcal A}=0\) exactly when some \(w\) satisfies only the active rows. The latter is a two-arm balance characterization only when both arms are active.

All entries of \(A\) are determined by the known assignment law and selector kernels, while \(b_{\mathrm{LP}}\) is determined by the prespecified target rule. The ranks and hence \(\mathcal A_{\boldsymbol\varepsilon}\) are fixed by \(M\) and the prespecified budget. Therefore any deterministic tie-broken choices \(w_*\in\mathcal W_*\) and \(w_{*,\mathcal A}\in\mathcal W_{*,\mathcal A}\) are computable before scores are observed.

Apply \(\texttt{prop:active-arm-finite-rank-orbit-gap-bound}\) to \(w_{*,\mathcal A}\). Equations (1)--(2) and optimality give
\[
\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w_{*,\mathcal A})=D_{*,\mathcal A},
\]
so
\[
\Pr_P\!\left\{\tau_T\in\mathcal C^{\boldsymbol\varepsilon}_{w_{*,\mathcal A}}\mid\mathcal T\right\}
\ge\max\!\left\{0,1-\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\rho_{M,\varepsilon_a}-D_{*,\mathcal A}\right\}.
\tag{13}
\]
For every fixed \(w\), optimality gives \(D_{*,\mathcal A}\le\sum_{a\in\mathcal A_{\boldsymbol\varepsilon}}\Delta_a(w)\). Since \(x\mapsto\max\{0,c-x\}\) is nonincreasing, (13) weakly dominates the corresponding fixed-\(w\) certificate, and the dominance is strict when the imbalance inequality is strict and the optimized untruncated bound is positive.

For the unchanged full optimizer \(w_*\), the same proposition and (2) give a bound at least
\[
\max\!\left\{0,1-\rho_{M,\varepsilon_0}-\rho_{M,\varepsilon_1}-D_*\right\},
\tag{14}
\]
because omitting inactive nonnegative terms can only increase the right side. The full optimality inequality \(D_*\le\Delta_0(w)+\Delta_1(w)\) proves the frozen weak-dominance claim, and it is strict under the frozen strictness conditions.

If exactly one arm is inactive, (11) has nonzero coordinates only on the other arm's rows, and (13) charges only that arm. If both are inactive, (3) applies and \(\texttt{prop:asymmetric-rank-boundary}\) gives coverage one without solving an LP. On the equal-split diagonal the ranks coincide. In the finite-rank regime both arms are active, so \(D_{*,\mathcal A}=D_*\), \(\mathcal W_{*,\mathcal A}=\mathcal W_*\), and (13) becomes
\[
\Pr_P(\tau_T\in\mathcal C_{w_*}\mid\mathcal T)\ge\max\{0,1-2\rho_{M,\alpha}-D_*\}.
\]
At the two-boundary elbow, coverage is one. Finally, if \(\mathcal H=\varnothing\), then \(\Delta(\mathcal H)=\varnothing\) by definition, so none of the selector-indexed objects exists.