For \(0\le i\le M\), put
\[
R_i=\sum_{j=1}^i b_0(E_{j,0}),\qquad S_i=\sum_{j=1}^i b_1(E_{j,1}).
\]
We prove by induction that every retained entry satisfies \(d_i(r,s)=\Pr\{R_i=r,S_i=s\}\). This is the initialization at \(i=0\). If it holds at \(i\), independence of the next draw and the definition of \(\pi_{xy}\) give
\[
\Pr\{R_{i+1}=r,S_{i+1}=s\}=\sum_{x,y\in\{0,1\}}\pi_{xy}\Pr\{R_i=r-x,S_i=s-y\}.
\tag{1}
\]
Negative indices have probability zero, and a discarded state cannot re-enter the retained rectangle because the increments are nonnegative. Thus (1) is exactly the asserted recurrence. Summing at \(i=M\) over \(r<k_0,s<k_1\) proves the probability identity. One scan of the table of \(R\) forms the four cells in \(O(|\mathscr E_0||\mathscr E_1|)\) operations. Each of the \(M\) updates visits at most \(k_0k_1\) entries and two rolling arrays suffice, proving the two-finite-rank resource bounds.

If, for example, \(k_0=M+1\), then \(R_i<k_0\) holds surely. Marginalizing the four cells over the first coordinate and applying the same induction to \(S_i\) gives \(O(Mk_1)\) time and \(O(k_1)\) memory after the common table scan. The other one-boundary case is symmetric, and with two boundary ranks the event is certain.

For the synchronized exact refinement, set
\[
C_{M,k_0,k_1}=\sum_{i=0}^{M-1}\min\{\bar k_0,i+1\}\min\{\bar k_1,i+1\}.
\]
The four corner identities in \(\texttt{lem:corner-oriented-four-cell-rank-evaluator}\) permit the rolling computation on the independently smallest corner in \(O(C_{M,k_0,k_1})\) time and \(O(\bar k_0\bar k_1)\) memory. The exact multinomial alternative in \(\texttt{lem:four-cell-multinomial-sum-alternative}\) works on the same width-minimizing permuted law even when its base atom is zero. Finally, through the positive-corner refinement of the corner lemma, a coefficient recurrence is available for every key after choosing any orientation with positive base atom. Hence all three branches compute the same probability; choosing their least operation count preserves exactness, while the memory charge is conditional on the selected branch rather than minimized independently. Since \(C_{M,k_0,k_1}\le M\bar k_0\bar k_1\le Mk_0k_1\), these refinements imply the coarser bounds in the statement.