Write
\[
\mathcal O_a=\{O\in\mathcal O:O\subseteq\mathcal U_a\}.
\]
If \(k_a\le M\), the elementary order-statistic identity gives
\[
s_a(O_{T,a})\le Q_{k_a}(s_a(O_{1,a}),\ldots,s_a(O_{M,a}))
\iff
\sum_{i=1}^M\mathbf 1\{s_a(O_{i,a})<s_a(O_{T,a})\}<k_a.
\tag{1}
\]
Indeed, the \(k_a\)-th calibration order statistic is strictly below the target score if and only if at least \(k_a\) calibration scores are strictly below it. Therefore ties are handled by the strict comparison in (1), and the event depends on \(s_a\) only through its total preorder. Conversely, if the ordered nonempty tie classes are
\[
C_{a,1}\prec_a\cdots\prec_a C_{a,d_a},
\]
assign score zero when \(d_a=1\), and otherwise assign
\[
\frac{(j-1)K}{d_a-1}
\]
to class \(C_{a,j}\). This realizes the preorder in \([0,K]\) with at most \(m_a\) levels. There are only \(F_{m_0}F_{m_1}\) preorder pairs. Hence the maximum in \(\texttt{def:coverage-frontier}\) is attained and is exactly the stated worst deficit over bounded orbit-constant score maps. This argument introduces no supremum over latent laws.

Suppose first that \(k_0,k_1\le M\). Apply \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). For every preorder pair \(C\),
\[
U_C\le L_C\le\min\{L,d_0d_1\},
\qquad
\Pr\{\text{both rank events}\}
 =\sum_{\pi\in\Pi_C}\omega_C(\pi)D_{M,k_0,k_1}(\pi).
\tag{2}
\]
The lemma also proves that the exact recurrence value is keyed by
\[
(M,k_0,k_1,\pi_{00},\pi_{01},\pi_{10}),
\qquad
\pi_{11}=1-\pi_{00}-\pi_{01}-\pi_{10},
\tag{3}
\]
whereas the local coherent weights never enter the key. Consequently each exact four-cell probability is computed once globally and then multiplied by the appropriate local \(\omega_C\).

Put \(h_a=M-k_a+1\), \(\bar k_a=\min\{k_a,h_a\}\), and define \(\mathsf C_{M,k_0,k_1}\), the deterministically tie-broken partition
\[
\Pi_\star
 =\Pi_{\mathrm{roll}}\mathbin{\dot\cup}\Pi_{\mathrm{MS}}\mathbin{\dot\cup}\Pi_+,
\]
the total charge \(\mathsf B\), and the actual-branch workspace \(\mathsf W\) exactly as in \(\texttt{lem:coherent-two-finite-rank-frontier-evaluator}\). That lemma compares, for every key, the exact corner-oriented rolling charge \(\mathsf C_{M,k_0,k_1}\), the zero-cell-safe multinomial charge \(M+\mathsf T_{M,\bar k_0,\bar k_1}\), and the positive-corner coefficient charge \(\mathsf C_+(\pi)\). Its complexity calculation applied to (2) gives
\[
O\!\left(
|\mathcal V|+F_{m_0}F_{m_1}(m_0m_1+L)
+\sum_{C\in\mathfrak C}\!\left[L_C\log(1+L_C)+L_C+U_C\right]
+\left\{\sum_{C\in\mathfrak C}U_C\right\}\log(1+G)+\mathsf B
\right),
\tag{4}
\]
and replacing \(L_C,U_C\) by \(L_{\max},U_{\max}\) gives the stated uniform specialization. Its memory calculation gives
\[
O(m_0m_1+L+U_{\max}+G+\mathsf W).
\tag{5}
\]
The factorial table is built once if and only if \(\Pi_{\mathrm{MS}}\ne\varnothing\); probability-specific power tables remain included in each multinomial key's charge. Empty branch sums vanish, and the singleton \(\{0\}\) in \(\mathsf W\) handles empty branches. Since every \(\pi\) is formed from the unchanged full \(R_w\), every \(\omega_C\) is formed from the unchanged coherent \(P_T^C\), and the three branches merely evaluate the same value in (2), neither memoization nor branch selection changes shared-assignment dependence, the common target, or the common selector. If \(k_0=k_1=M\), then \(\bar k_0=\bar k_1=1\) and
\[
\mathsf C_{M,M,M}=M,
\]
so the rolling charge is \(\Theta(M)\) per key rather than the coarse \(\Theta(M^3)\); the positive-corner branch may be smaller.

Suppose next that exactly one rank satisfies \(k_b=M+1\), and put \(c=1-b\). By \(\texttt{prop:asymmetric-rank-boundary}\), the boundary-arm rank event is certain. Conditional on \(O_{T,c}=O_t\), (1) is a binomial count with parameter
\[
\theta(O_t)=\sum_{\substack{O\in\mathcal O_c\\s_c(O)<s_c(O_t)}}q_{c,O}.
\tag{6}
\]
The calibration orbits are iid and independent of the target by the known randomization, target prespecification, and auxiliary-selector assumptions. Hence the exact remaining rank-event probability is
\[
\sum_{O_t\in\mathcal O_c}p_{c,O_t}
 \Pr\!\left\{\operatorname{Bin}\bigl(M,\theta(O_t)\bigr)<k_c\right\}.
\tag{7}
\]
By \(\texttt{lem:one-boundary-orbit-frontier-evaluator}\), if
\[
C_1\prec\cdots\prec C_d
\]
are the nonboundary preorder's ordered tie classes and
\[
q_j=q_c(C_j),\qquad p_j=p_c(C_j),\qquad
\theta_j=\sum_{\ell<j}q_\ell,
\]
then (7) is
\[
\sum_{j=1}^d p_j\Pr\{\operatorname{Bin}(M,\theta_j)<k_c\}.
\tag{8}
\]
One cumulative scan forms these quantities. For \(0<\theta<1\), the lower-tail terms satisfy
\[
t_0=(1-\theta)^M,\qquad
t_{r+1}=t_r\frac{M-r}{r+1}\frac{\theta}{1-\theta},
\quad 0\le r<k_c-1,
\tag{9}
\]
whereas the upper-tail terms satisfy
\[
u_M=\theta^M,\qquad\nu_{r-1}=u_r\frac r{M-r+1}\frac{1-\theta}{\theta},
\quad k_c<r\le M.
\tag{10}
\]
Exponentiation by squaring initializes the selected endpoint in \(O(\log M)\) operations, and summing the shorter tail costs
\[
O(\min\{k_c,M-k_c+1\}).
\]
At \(\theta=0\) and \(\theta=1\), the probabilities are one and zero, respectively, without division. Thus enumerating only the \(F_{m_c}\) nonboundary preorders costs
\[
O\!\left(
F_{m_c}m_c
\left[1+\log M+\min\{k_c,M-k_c+1\}\right]
\right)
\tag{11}
\]
operations and \(O(1)\) auxiliary CDF memory after \(q_c,p_c\) are tabulated. Formula (8) contains neither the other arm's preorder nor a member-level or cross-orbit scan, proving every asserted absence in the one-boundary bound. If both ranks equal \(M+1\), both rank events are certain and
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)
 =[(1-\alpha)-1]_+=0.
\tag{12}
\]

We now prove that binary scores need not attain the maximum. Take four pair blocks, \(\mathcal G=S_2^4\), fair independent within-pair assignment, and a singleton selector library. In either arm let the selector first choose a block with probabilities
\[
q=\left(\frac{13}{20},\frac1{20},\frac14,\frac1{20}\right)
\tag{13}
\]
and then select that block's unique observed arm-\(a\) member. Let the common target choose a block with probabilities
\[
p=\left(\frac1{20},\frac1{10},\frac14,\frac35\right)
\tag{14}
\]
and choose either member of that block with equal probability. These kernels are observable and equivariant under \(S_2^4\), and the two auxiliary block choices are independent conditional on the assignment. Take \(M=3\), \(\alpha=1/2\), and \(\varepsilon_0=\varepsilon_1=1/4\). Then \(k_0=k_1=3\). Set \(s_0\equiv0\) and order the four arm-one block orbits as
\[
1\prec3\prec2\prec4.
\]
The arm-zero event is certain. The arm-one event fails exactly when all three calibration blocks precede the target block. Its failure probability is
\[
\frac14\left(\frac{13}{20}\right)^3
+\frac1{10}\left(\frac{18}{20}\right)^3
+\frac35\left(\frac{19}{20}\right)^3
=\frac{104957}{160000}.
\tag{15}
\]
Consequently the frontier objective of this four-level pair is
\[
\frac{104957}{160000}-\frac12
=\frac{24957}{160000}.
\tag{16}
\]

For a binary score pair let \(H_a\) be arm \(a\)'s high-score block set and put
\[
A_a=(1-q(H_a))^3.
\]
The common target block and conditionally independent auxiliary block choices give, by inclusion--exclusion,
\[
F_{\mathrm{bin}}(H_0,H_1)
=p(H_0)A_0+p(H_1)A_1-p(H_0\cap H_1)A_0A_1.
\tag{17}
\]
There are only sixteen possible high sets in each arm. In the row order
\[
\varnothing,1,2,3,4,12,13,14,23,24,34,123,124,134,234,1234,
\]
exact substitution in (17), maximizing over the sixteen choices for the other arm, gives the following row maxima over the common denominator \(320000000\):
\[
\begin{split}
(164616000,&165302000,192052000,198366000,207906936,165912000,\\
&164712000,165787368,203032000,208582976,208582976,164632000,\\
&165793875,164631423,202894331,164616000).
\end{split}
\tag{18}
\]
The largest failure probability in (18) is \(208582976/320000000\). Subtracting \(1/2\), every binary pair therefore has frontier objective at most
\[
\frac{759109}{5000000}.
\tag{19}
\]
The strict gap between (16) and (19) is
\[
\frac{24957}{160000}-\frac{759109}{5000000}
=\frac{83189}{20000000}>0.
\tag{20}
\]
This establishes the claimed failure of binary attainment within an admissible symmetric instance.

Finally, suppose target and calibration orbit supports are disjoint in an arm \(a\) with \(k_a\le M\). Assign score \(K\) to every target-supported orbit in that arm and zero to every other orbit, and assign score zero throughout the other arm. Every adverse-arm calibration score is then zero while its target score is \(K\); its rank event fails surely. Therefore the joint event has probability zero and
\[
\Gamma_{M,\alpha,\boldsymbol\varepsilon}(w)\ge1-\alpha.
\]
The reverse inequality follows immediately from the positive-part definition, so equality holds. If \(k_a=M+1\), its event is certain and (7)--(8) show that the frontier reduces exactly to the other arm's event. On the diagonal \(\varepsilon_0=\varepsilon_1=\alpha/2\), \(\texttt{lem:armwise-finite-rank-staircase}\) gives \(k_0=k_1=k\), and the asymmetric definition becomes \(\Gamma_{M,\alpha}(w)\), proving the asserted reduction.