% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_anchor\_icp\_dantzig\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_anchor\_icp\_dantzig\_frontier} / \texttt{v1}%
  \\ \large\textit{A covariance-pencil frontier for ICP, anchor regression, and Causal Dantzig}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\texttt{qid} is \texttt{eid\_anchor\_icp\_dantzig\_frontier}. \texttt{specialization} is \texttt{v1}. The graph/SWIG is a linear Gaussian SEM with centered anchors $A\in\R^q$, covariates $X\in\R^p$, outcome $Y\in\R$, and exogenous Gaussian noise independent of anchor shocks after conditioning on the SEM parents named in Assumption~\ref{ass:sem}. The treatment is the coordinate vector $X$ as a candidate direct-cause set for $Y$. The target estimand is the covariance-level agreement frontier among three population procedures: ICP accepted sets $\mathcal I_{\mathrm{ICP}}$, the $\gamma=\infty$ anchor-regression solution set $\mathcal B_{\mathrm{AR}}^\infty$, and the Causal-Dantzig solution set $\mathcal B_{\mathrm{CD}}$. Identifying assumptions are linear Gaussianity, finite nonsingular covariance for $(A,X,Y)$, additive anchor shifts, and the moment/conditional-law invariance definitions in Section~\ref{sec:setup}. The decision functional is the primitive covariance pencil $K(\Sigma_{AXY};S,\beta)$ in Definition~\ref{def:pencil}, together with its rank and kernel zero sets.

\begin{abstract}
Invariant causal prediction, anchor regression, and Causal Dantzig use different invariance equations on the same environment-indexed linear SEM. The question is whether their population outputs can be compared by a primitive covariance object rather than by solving the three procedures and checking equality afterward. The central conjecture is an if-and-only-if rank and kernel frontier for a covariance pencil $K(\Sigma_{AXY};S,\beta)$ whose blocks are derived from the conditional-law, anchor normal-equation, and residual-moment equations. A second conjecture gives two $q=p=2$ Gaussian SEM witness families separating conditional-distribution invariance from residual-moment invariance in both directions. If resolved, the result would turn a verbal distinction among three invariance methods into a finite certificate for when the methods agree, strictly include one another, or conflict.
\end{abstract}

\section{Introduction}
Invariant methods differ in the object they keep stable across environments. The main claim is that, in linear Gaussian SEMs with anchors, three named procedures have an exact covariance-level agreement frontier described by a single pencil $K(\Sigma_{AXY};S,\beta)$ and not by a post hoc equality test between their fitted coefficients.

The closest comparators are \citet[Section~2, equations (2.3)--(2.6)]{RothenhauslerMeinshausenBuhlmannPeters2021Anchor}, who derive the anchor path and its $\gamma\to\infty$ endpoint, and \citet[Section~2.1, equations (1)--(2)]{PetersBuhlmannMeinshausen2016ICP}, who define ICP through equality of conditional distributions. The gap is that neither paper, nor \citet[Sections~1--2]{RothenhauslerBuhlmannMeinshausen2019CausalDantzig}, gives a sharp finite covariance certificate comparing conditional-law invariance, anchor normal equations, and Causal-Dantzig residual moments on the same SEM. The kernel lives in exact identification for linear Gaussian SEMs with multiple environments.

The direct consumer is the robustness and invariance literature that extends anchor regression beyond mean-squared residual stability, including \citet{KookSickBuhlmann2022DistributionalAnchor} and recent invariant probabilistic prediction. A reader who takes the conclusion away would check rank and kernel conditions on covariance blocks before treating ICP acceptance, anchor stability, and Causal-Dantzig feasibility as interchangeable evidence.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the three population procedures can be written as three explicit zero equations in covariance blocks. Gap: \citet{PetersBuhlmannMeinshausen2016ICP}, \citet{RothenhauslerMeinshausenBuhlmannPeters2021Anchor}, and \citet{RothenhauslerBuhlmannMeinshausen2019CausalDantzig} state separate equations but do not assemble a common certificate. Consumer: distributional anchor diagnostics in \citet{KookSickBuhlmann2022DistributionalAnchor}.
\item Conjecture 1: the affine operator $\mathfrak K_S=(M_S,h_S)$ has $h_S$ in the common image and kernel $N_S$ exactly when ICP acceptance, the anchor $\gamma=\infty$ coefficient, and Causal-Dantzig feasibility agree at $(S,\beta)$. Gap: anchor regression gives interpolation and robustness, while Causal Dantzig gives residual invariance, but neither gives the three-way iff frontier. Consumer: the distributional-anchor diagnostic of \citet{KookSickBuhlmann2022DistributionalAnchor} and the environment-IV workflow of \citet{LongZhuDoHa2023IVEnvironments}.
\item Conjecture 2: two $2$-anchor by $2$-covariate Gaussian SEM strata separate residual-moment invariance from ICP conditional-law invariance in both directions. Gap: \citet[Section~2]{RothenhauslerBuhlmannMeinshausen2019CausalDantzig} motivates inner-product invariance as different from ICP, and \citet[Section~3]{KookSickBuhlmann2022DistributionalAnchor} separates score and distributional stability, but neither classifies the smallest covariance witnesses. Consumer: ICP screening in \citet{HeinzeDemlPetersMeinshausen2018NonlinearICP} when residual diagnostics are used as a computational proxy.
\end{itemize}

\section{Related work}
\citet{PetersBuhlmannMeinshausen2016ICP} introduce invariant causal prediction and base acceptance on equality of the conditional distribution of $Y$ given a selected covariate set across environments. \citet{HeinzeDemlPetersMeinshausen2018NonlinearICP} show that accepted-set behavior depends on model structure and power, which makes support comparisons across methods nonautomatic. \citet{RothenhauslerBuhlmannMeinshausen2019CausalDantzig} introduce Causal Dantzig for linear SEMs with hidden variables and additive interventions, replacing conditional-law invariance by residual inner-product invariance. \citet{RothenhauslerMeinshausenBuhlmannPeters2021Anchor} define anchor regression and show that its population path interpolates between partialling out, OLS, and IV-like limits with robustness to anchor-span perturbations. \citet{KookSickBuhlmann2022DistributionalAnchor} separates residual mean or score invariance from distributional residual invariance, which is the closest published warning that first-moment stability and full conditional stability need not coincide. \citet{LongZhuDoHa2023IVEnvironments} relate environment-based restrictions to instrumental variables and hidden confounding, but do not provide a three-estimator equality frontier. \citet{HenziShenLawBuhlmann2025IPP} and \citet{ShenBuhlmannTaeb2026Robustness} broaden anchor-style robustness beyond the original shift span, making the exact conflict set among invariance procedures more salient. In the CausalSmith catalogue, \texttt{doc/API.md} reports no existing ExactID entry for anchor regression, ICP, or Causal Dantzig; the nearest in-repo prior signals are the downgraded \texttt{eid\_dml\_orth\_uniform} triple-frontier attempt and \texttt{eid\_lp\_svar\_nonequiv} low-dimensional non-equivalence attempt described in the Stage -1.1 gaps payload.

\section{Formal setup}\label{sec:setup}
Let $Z=(A\transpose,X\transpose,Y)\transpose$ be centered jointly Gaussian with covariance $\Sigma$. Write $\Sigma_{UV}=\E[UV\transpose]$ for subvectors $U,V$ and assume $\Sigma_{AA}\succ0$ and $\Sigma_{XX}\succ0$. For $S\subseteq\{1,\ldots,p\}$, let $X_S$ be the selected covariates and $\beta_S^{\mathrm{ols}}=\Sigma_{X_SX_S}^{-1}\Sigma_{X_SY}$. The ICP population acceptance equation for $S$ is the Gaussian conditional-law equation
\[
  k_{\mathrm{ICP}}(S)=\Sigma_{AY}-\Sigma_{AX_S}\beta_S^{\mathrm{ols}}=0,
\]
which is equivalent to zero coefficient on $A$ in the population regression of $Y$ on $(X_S,A)$ when the conditional residual variance is environment-stable. The anchor $\gamma=\infty$ solution set is
\[
  \mathcal B_{\mathrm{AR}}^\infty=\arg\min_{b\in\R^p}\E\{[\E(Y-X\transpose b\mid A)]^2\},
\]
with normal equation $G_A b=g_A$, where $G_A=\Sigma_{XA}\Sigma_{AA}^{-1}\Sigma_{AX}$ and $g_A=\Sigma_{XA}\Sigma_{AA}^{-1}\Sigma_{AY}$. The Causal-Dantzig population feasibility set is written as
\[
  \mathcal B_{\mathrm{CD}}=\{b\in\R^p: C_A b=d_A\},\qquad C_A=\Sigma_{AX},\quad d_A=\Sigma_{AY},
\]
so that residuals are orthogonal to the additive anchor shifts. For a selected set $S$ and a full coefficient vector $b$ supported on $S$, define the covariance pencil
\begin{definition}[Covariance conflict pencil]\label{def:pencil}
Let $R_{S^c}$ select the coordinates outside $S$ and let $\iota_S:\R^{|S|}\to\R^p$ insert zeros outside $S$. Define the affine operator
\[
  \mathfrak K_S(\Sigma)=(M_S(\Sigma),h_S(\Sigma)),\qquad
  K(\Sigma;S,b)=M_S(\Sigma)b-h_S(\Sigma),
\]
where
\[
M_S=
\begin{bmatrix}
0_{q\times p}\\
G_A\\
C_A\\
R_{S^c}\Sigma_{XX}
\end{bmatrix},\qquad
h_S=
\begin{bmatrix}
-k_{\mathrm{ICP}}(S)\\
g_A\\
d_A\\
R_{S^c}\Sigma_{XY}
\end{bmatrix}.
\]
The first block is a primitive conditional-law obstruction independent of the chosen coefficient; the remaining blocks are the anchor endpoint, Causal-Dantzig, and omitted-coordinate affine equations. Let
\[
  r_S=\operatorname{rank}M_S,\qquad
  N_S=\ker M_S\cap\operatorname{range}(\iota_S),\qquad
  I_S=\operatorname{im}M_S .
\]
The frontier object is the triple $(r_S,N_S,I_S)$ together with the membership predicate $h_S\in I_S$.
\end{definition}
The locked parameters are reproduced verbatim: \texttt{qid=eid\_anchor\_icp\_dantzig\_frontier; specialization=v1; graph/SWIG=linear Gaussian SEM with centered anchors A, covariates X, outcome Y; treatment=X; target=agreement frontier among ICP accepted sets, anchor gamma-infinity coefficients, and Causal-Dantzig coefficients; assumptions=linear Gaussianity, nonsingular covariance, additive anchor shifts, and the Section 6 invariance equations; decision functional=K(Sigma;S,b) with rank/kernel zero sets}.

\section{Assumptions}
\begin{assumption}[Linear Gaussian anchor SEM]\label{ass:sem}
$(A,X,Y)$ is generated by an acyclic linear SEM with jointly Gaussian exogenous noise, centered variables, finite second moments, and additive anchor shifts that enter through $A$ and its descendants.
\end{assumption}

\begin{assumption}[Nonsingular covariance blocks]\label{ass:nonsing}
$\Sigma_{AA}\succ0$, $\Sigma_{XX}\succ0$, and $\Sigma_{X_SX_S}\succ0$ for every selected set $S$ used in a result.
\end{assumption}

\begin{assumption}[Gaussian ICP acceptance]\label{ass:icp}
For a selected set $S$, population ICP accepts $S$ exactly when the Gaussian conditional law of $Y$ given $X_S$ is invariant across anchors, equivalently $k_{\mathrm{ICP}}(S)=0$ together with invariant conditional residual variance.
\end{assumption}

\begin{assumption}[Anchor and Dantzig population equations]\label{ass:arcd}
The $\gamma=\infty$ anchor coefficient set and Causal-Dantzig coefficient set are the population solution sets defined in Section~\ref{sec:setup}; nonunique solutions are allowed.
\end{assumption}

\begin{assumption}[Frontier regularity]\label{ass:frontier}
The rank of $G_A$ and $C_A$ is locally constant on the covariance stratum under consideration, unless the result explicitly names a rank-change boundary.
\end{assumption}

\begin{assumption}[Coefficient support convention]\label{ass:support}
A coefficient $b$ agrees with support $S$ when $b\in\operatorname{range}(\iota_S)$ and the omitted-coordinate block $R_{S^c}(\Sigma_{XX}b-\Sigma_{XY})$ is evaluated against the full covariance matrix, not against the restricted regression alone.
\end{assumption}

\section{Main results}
\begin{theorem}[Population equations for the three invariance procedures]\label{thm:equations}
Under Assumptions~\ref{ass:sem}--\ref{ass:arcd}, ICP acceptance, the anchor $\gamma=\infty$ endpoint, and Causal-Dantzig feasibility are respectively equivalent to $k_{\mathrm{ICP}}(S)=0$, $G_A b=g_A$, and $C_A b=d_A$ with the objects defined in Section~\ref{sec:setup}.
\end{theorem}
The proof is a direct population calculation: Gaussian conditional-law invariance is zero anchor coefficient in the regression on $(X_S,A)$, anchor $\gamma=\infty$ is the normal equation for the projected residual loss, and Causal Dantzig is residual orthogonality to additive anchor shifts.

\begin{conjecture}[Three-way covariance-pencil frontier (NOT YET PROVED)]\label{conj:frontier}
Under Assumptions~\ref{ass:sem}--\ref{ass:support}, for any support $S$, the following are equivalent: (i) $S\in\mathcal I_{\mathrm{ICP}}$ and there exists $b\in\operatorname{range}(\iota_S)$ such that $b\in\mathcal B_{\mathrm{AR}}^\infty\cap\mathcal B_{\mathrm{CD}}$ with no omitted-coordinate normal-equation conflict; (ii) $k_{\mathrm{ICP}}(S)=0$, $h_S\in I_S$, and the affine fiber $\{b:M_Sb=h_S\}$ intersects $\operatorname{range}(\iota_S)$ in the coset $b_0+N_S$ for some $b_0$ whose restricted coordinates equal $\beta_S^{\mathrm{ols}}$. On rank-change boundaries, the same equivalence holds after replacing $N_S$ by the upper semicontinuous limit of $\ker M_S\cap\operatorname{range}(\iota_S)$ along the covariance stratum.
\end{conjecture}

\begin{conjecture}[Minimal two-by-two non-equivalence witnesses (NOT YET PROVED)]\label{conj:witness}
Under Assumptions~\ref{ass:sem}--\ref{ass:arcd}, there are two non-corner $q=p=2$ Gaussian SEM covariance strata with positive conditional noise variances. On the first, $C_A b=d_A$ and $G_A b=g_A$ hold for a supported coefficient $b$ while $k_{\mathrm{ICP}}(S)\ne0$. On the second, $k_{\mathrm{ICP}}(S)=0$ but $\mathcal B_{\mathrm{AR}}^\infty\cap\mathcal B_{\mathrm{CD}}$ contains coefficients with a different support from the ICP regression coefficient. The separating strata are semi-algebraic and can be written by nonvanishing determinants and one rank-one anchor-covariate minor in Definition~\ref{def:pencil}.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[No-anchor collapse]
If $\Sigma_{AX}=0$ and $\Sigma_{AY}=0$, then $k_{\mathrm{ICP}}(S)=0$, $G_A=0$, $g_A=0$, $C_A=0$, and $d_A=0$ for every $S$. The pencil reduces to the ordinary omitted-coordinate normal-equation block, so the frontier does not create spurious conflict when environments carry no covariance information.
\end{corollary}

\begin{corollary}[Full-rank valid-anchor collapse]
If $C_A=\Sigma_{AX}$ has full column rank and $\Sigma_{AY}=\Sigma_{AX}\beta^0$, then $\mathcal B_{\mathrm{CD}}=\{\beta^0\}$ and $\mathcal B_{\mathrm{AR}}^\infty=\{\beta^0\}$. If additionally $\Sigma_{AY}-\Sigma_{AX_S}\beta_S^{\mathrm{ols}}=0$ for $S=\operatorname{supp}(\beta^0)$, then $K(\Sigma;S,\beta^0)=0$.
\end{corollary}

\paragraph{Exhibit 9.1: hand-derived pencil on a $2$-anchor by $2$-covariate covariance.}
First let $A_1,A_2,U_1,U_2,V$ be independent standard Gaussians, set $X_1=A_1+U_1$, $X_2=A_2+U_2$, and $Y=X_1+U_1+V$. Then
\[
\Sigma_{AA}=I_2,\quad
\Sigma_{AX}=\begin{psmallmatrix}1&0\\0&1\end{psmallmatrix},\quad
\Sigma_{XX}=\begin{psmallmatrix}2&0\\0&2\end{psmallmatrix},\quad
\Sigma_{AY}=\binom{1}{0},\quad
\Sigma_{XY}=\binom{3}{0}.
\]
For $S=\{1\}$, $b=(1,0)\transpose$, and $\beta_1^{\mathrm{ols}}=3/2$, the affine operator in Definition~\ref{def:pencil} is
\[
M_S=
\begin{bmatrix}
0&0\\0&0\\
1&0\\0&1\\
1&0\\0&1\\
0&2
\end{bmatrix},\qquad
h_S=
\begin{bmatrix}
1/2\\0\\
1\\0\\
1\\0\\
0
\end{bmatrix},\qquad
K(\Sigma;S,b)=
\begin{bmatrix}
-1/2\\0\\
0\\0\\
0\\0\\
0
\end{bmatrix}.
\]
Thus $\operatorname{rank}M_S=2$, $N_S=\{0\}$, $h_S\notin I_S$ because of the first ICP row, and the residual-moment and anchor rows are exactly satisfied. The covariance is positive definite because it is generated by the displayed SEM with independent positive-variance noises.

\paragraph{Exhibit 9.2: ICP acceptance with residual-moment nonuniqueness.}
Let $A_1,A_2,U_1,U_2,V$ be independent standard Gaussians, set $X_1=A_1+A_2+U_1$, $X_2=A_1+A_2+U_2$, and $Y=X_1+V$. Then
\[
\Sigma_{AA}=I_2,\quad
\Sigma_{AX}=\begin{psmallmatrix}1&1\\1&1\end{psmallmatrix},\quad
\Sigma_{XX}=\begin{psmallmatrix}3&2\\2&3\end{psmallmatrix},\quad
\Sigma_{AY}=\binom{1}{1},\quad
\Sigma_{XY}=\binom{3}{2}.
\]
For $S=\{1\}$, $\beta_1^{\mathrm{ols}}=1$ and $k_{\mathrm{ICP}}(S)=0$. The anchor and Dantzig equations are both $b_1+b_2=1$, so $(1,0)\transpose$ and $(0,1)\transpose$ are feasible; hence the residual-moment criteria contain a coefficient with support $\{2\}$ although ICP accepts the restricted coefficient on $X_1$. Here $\operatorname{rank}M_S=2$, $N_S=\{0\}$ after support restriction, and the unrestricted residual fiber has direction $(1,-1)\transpose$, which is the named rank-one boundary in Conjecture~\ref{conj:witness}.

\section{Proof-sketch route}
For Conjecture~\ref{conj:frontier}, the reduction chain is: headline $\leftarrow$ unfold Definition~\ref{def:pencil} $\leftarrow$ substitute Assumptions~\ref{ass:icp}, \ref{ass:arcd}, and \ref{ass:support} $\leftarrow$ prove a Schur-complement lemma identifying Gaussian conditional-law invariance with the zero first block while keeping it independent of $b$ $\leftarrow$ prove an affine-image lemma for $h_S\in I_S$ that separates existence of a common coefficient from equality of any pre-solved estimators $\leftarrow$ prove a kernel-fiber lemma showing that $N_S$ is the exact nonuniqueness direction on a fixed support $\leftarrow$ prove a support-pasting lemma showing that $R_{S^c}(\Sigma_{XX}b-\Sigma_{XY})$ rules out false support equality $\leftarrow$ apply rank-nullity and upper-semicontinuity of kernels on rank strata. Thus $k=4$ substantive steps: the Schur-complement lemma, the affine-image lemma, the kernel-fiber lemma, and the support-pasting lemma. For Conjecture~\ref{conj:witness}, solve the two displayed $q=p=2$ systems, then perturb within the stated covariance stratum and verify the determinant signs and positive conditional variances away from the rank-one boundary.

\section{Honest scope flags}
Theorem~\ref{thm:equations} is a routine population translation of the three published definitions. Conjectures~\ref{conj:frontier} and \ref{conj:witness} are not yet proved; the main risk is that the support-pasting block is too strong for some accepted-set comparisons or too weak on rank-change boundaries. The v1 open-set wording for the second witness was withdrawn; v2 states non-corner covariance strata because one separation necessarily uses a nonunique residual-moment fiber.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft of a covariance-pencil frontier and two-by-two witness programme; prior verdict: none.
\item v2 (revise) --- made the pencil an affine operator with rank, image, and kernel objects; repaired the two witness exhibits; fixed named consumers and bibliography metadata; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Long, Zhu, Do, and Ha(2023)]{LongZhuDoHa2023IVEnvironments}
Long, Q., Y. Zhu, K. A. Do, and W. Ha (2023). Estimating causal effects with hidden confounding using instrumental variables and environments. Methodological article.

\bibitem[Heinze-Deml, Peters, and Meinshausen(2018)]{HeinzeDemlPetersMeinshausen2018NonlinearICP}
Heinze-Deml, C., J. Peters, and N. Meinshausen (2018). Invariant causal prediction for nonlinear models. \emph{Journal of Causal Inference} 6(2).

\bibitem[Henzi, Shen, Law, and Buhlmann(2025)]{HenziShenLawBuhlmann2025IPP}
Henzi, A., X. Shen, M. Law, and P. Buhlmann (2025). Invariant probabilistic prediction. \emph{Biometrika}.

\bibitem[Kook, Sick, and Buhlmann(2022)]{KookSickBuhlmann2022DistributionalAnchor}
Kook, L., B. Sick, and P. Buhlmann (2022). Distributional anchor regression. \emph{Statistics and Computing} 32, 39.

\bibitem[Peters, Buhlmann, and Meinshausen(2016)]{PetersBuhlmannMeinshausen2016ICP}
Peters, J., P. Buhlmann, and N. Meinshausen (2016). Causal inference using invariant prediction: identification and confidence intervals. \emph{Journal of the Royal Statistical Society: Series B} 78(5), 947--1012.

\bibitem[Rothenhausler, Buhlmann, and Meinshausen(2019)]{RothenhauslerBuhlmannMeinshausen2019CausalDantzig}
Rothenhausler, D., P. Buhlmann, and N. Meinshausen (2019). Causal Dantzig: fast inference in linear structural equation models with hidden variables under additive interventions. \emph{Annals of Statistics} 47(3), 1688--1722.

\bibitem[Rothenhausler, Meinshausen, Buhlmann, and Peters(2021)]{RothenhauslerMeinshausenBuhlmannPeters2021Anchor}
Rothenhausler, D., N. Meinshausen, P. Buhlmann, and J. Peters (2021). Anchor regression: heterogeneous data meet causality. \emph{Journal of the Royal Statistical Society: Series B} 83(2), 215--246.

\bibitem[Shen, Buhlmann, and Taeb(2026)]{ShenBuhlmannTaeb2026Robustness}
Shen, X., P. Buhlmann, and A. Taeb (2026). Causality-oriented robustness: exploiting general noise interventions. \emph{Journal of the American Statistical Association}.
\end{thebibliography}

\end{document}
