% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_fragmented\_transport\_support, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_fragmented\_transport\_support} / \texttt{v1}%
  \\ \large\textit{Sharp support-fragmented multi-trial transport by an atom-cover certificate}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\[
\begin{array}{ll}
\text{qid} & \texttt{eid\_fragmented\_transport\_support},\\
\text{specialization} & \texttt{v1},\\
\text{graph / SWIG} & \text{finite-population transport SWIG with target domain } S=\star
  \text{ and trial domains } S\in\{1,\ldots,K\},\\
\text{treatment} & A\in\{0,1\}\text{ randomized within each observed source trial stratum},\\
\text{target estimand} & \theta_\star=\E_\star\{Y(1)-Y(0)\},\\
\text{identifying restrictions} & \text{finite target support, consistency, source-trial randomization,}
  \text{ observed target covariate law, and}\\
& \text{candidate atom-arm conditional mean invariance edges. The atom-cover certificate }C(P)
  \text{ is a testable candidate frontier,}\\
& \text{not an assumed identifying condition.}
\end{array}
\]

\begin{abstract}
Multi-trial transport can identify a target average treatment effect even when every source trial misses part of the target covariate support. The question is whether the identifying support condition is a pooled trial-level condition or a finer atom-arm condition. The flagship conjecture states that, on finite covariate support, point identification is equivalent to a computable atom-arm cover: each target atom and treatment arm must have at least one experimentally supported source cell with invariant conditional potential-outcome mean. This permits treated and untreated means for the same target atom to be transported from different source trials, a regime not stated by the pooled-source conditions in \citet[Sec. 3.4, Theorem 3]{DahabrehRobertsonPetitoHernanSteingrimsson2023}. Below the frontier, the usual bounded-outcome Manski rectangle gives a diagnostic interval for the remaining unsupported atom-arm means.
\end{abstract}

\section{Introduction}
Target populations are often wider than any one randomized trial. The question is whether several incomplete trials can jointly transport an average treatment effect without imposing a model for unsupported target strata. Conjecture 1 states that finite-support point identification is equivalent to an atom-arm cover certificate: each target covariate atom and treatment arm must be covered by an experimentally supported source cell whose conditional potential-outcome mean is invariant for that atom.

\citet[Sec. 2.4]{DahabrehPetitoRobertsonHernanSteingrimsson2020} and \citet[Sec. 3.4, Theorem 3]{DahabrehRobertsonPetitoHernanSteingrimsson2023} give multi-trial identification formulas under weaker overlap conditions over the collection of trials, while \citet[Sec. 3]{BareinboimLeeHonavarPearl2013} gives graphical multi-environment transportability criteria. The gap is the finite-support necessity statement for a stricter object: an atom-arm assignment frontier that allows the treated and untreated means at one target atom to be supplied by different source trials and proves nonidentification when any required atom-arm edge is absent. The kernel is an exact-identification frontier with a classical partial-identification corollary below it.

The immediate consumer is the causally interpretable meta-analysis program in \citet{DahabrehRobertsonPetitoHernanSteingrimsson2023}. A reader can report which target atoms are identified by which source trials, compute the target ATE when the cover holds, and report a sharp interval when it does not.

\begin{itemize}[leftmargin=*]
\item Conjecture 1: The target ATE is point identified if and only if the atom-arm cover certificate holds. Gap: \citet[Sec. 3.4, Theorem 3]{DahabrehRobertsonPetitoHernanSteingrimsson2023} identifies target means under pooled multi-trial overlap, but does not give an iff atom-arm assignment frontier or the missing-edge converse; \citet[Sec. 3]{BareinboimLeeHonavarPearl2013} gives a graphical transport algorithm rather than this finite econometric certificate. Consumer: multi-trial target-population meta-analysis in \citet{DahabrehRobertsonPetitoHernanSteingrimsson2023}.
\item Corollary 2: If the certificate fails and outcomes are bounded, the Manski rectangle specialization gives the atomwise interval in \eqref{eq:sharp-interval}. Gap: this is not claimed as new relative to \citet{Manski1990}, \citet{Robins1989}, or \citet{KlineTamer2018}; it records the exact below-frontier diagnostic attached to Conjecture 1. Consumer: nonpositive transport regions in \citet{ZivichEdwardsShookSaLofgrenLesslerCole2025}.
\item Theorem 3: In the two-source binary-atom design, neither source identifies the target ATE alone, the pair identifies it under the certificate, and one missing atom-arm invariance clause creates two observationally equivalent laws with different target ATEs. Gap: \citet{HotzImbensMortimer2005} and \citet{ColeStuart2010} motivate overlap diagnostics without this minimal finite witness. Consumer: finite-support diagnostics in trial generalizability studies.
\end{itemize}

\section{Related work}
\citet{HotzImbensMortimer2005} is the econometric ancestor for extrapolating experimental effects across sites; it makes covariate overlap and site comparability central to external validity. \citet{ColeStuart2010} gives an early standardization template for transporting trial evidence to a specified target population. \citet{WestreichEdwardsLeskoStuartCole2017} develops inverse odds of sampling weights for transportability and makes sampling positivity an operational condition. \citet{DahabrehPetitoRobertsonHernanSteingrimsson2020} states conditions for transporting inferences from one or more randomized trials to a target population. \citet[Sec. 3.4, Theorem 3]{DahabrehRobertsonPetitoHernanSteingrimsson2023} is the closest published comparator because it permits identification under weaker overlap over a collection of trials; the present qid asks for a finite atom-arm iff certificate and the missing-edge converse rather than another estimator for the same formula. \citet{SuRytgaardRavnEriksson2024} studies semiparametric efficiency for multiple source trials under effect-measure transportability, which is adjacent to estimation once the finite certificate is known. \citet{DegtiarRose2023} reviews generalizability and transportability assumptions, diagnostics, and heterogeneity tests. \citet{BareinboimLeeHonavarPearl2013} is the closest graphical multi-environment comparator; it addresses do-calculus transport formulas rather than finite potential-outcome support fragmentation. \citet{Manski1990} gives the classical bounded-outcome treatment-effect interval, and \citet{Robins1989} gives foundational nonparametric bounds for causal effects with incomplete information. \citet{KlineTamer2018} applies partial- and point-identification ideas to external validity under selective randomized-trial participation; Corollary 2 should be read as a Manski--Robins specialization attached to the atom-arm frontier, not as a new partial-ID theorem. \citet{ZivichEdwardsShookSaLofgrenLesslerCole2025} emphasizes that nonpositive transport regions are not nonparametrically identified without additional synthesis assumptions. The in-repository prior-art map lists \texttt{eid\_data\_fusion\_k\_source\_v1} as the closest banked proposal; its headline concerned source-law cover for general data fusion, while the present qid fixes randomized source trials, a target-population ATE, and an atom-arm certificate. The API catalogue section ``ExactID / PartialID catalogues'' records no promoted exact-ID or partial-ID entry for multi-source trial support fragmentation.

\section{Formal setup}
Let $X$ take values in a finite set $\calX$, and let $\calX_\star=\{x:\Pr_\star(X=x)>0\}$ be the target support. The observed domains are $S=\star$ for the target covariate sample and $S\in\{1,\ldots,K\}$ for randomized source trials. In a source trial, $A\in\{0,1\}$ and $Y=Y(A)$ are observed; in the target sample only $X$ is required. Write
\[
q_x=\Pr_\star(X=x),\qquad
\mu_{\star a}(x)=\E_\star\{Y(a)\mid X=x\},\qquad
\theta_\star=\sum_{x\in\calX_\star}q_x\{\mu_{\star 1}(x)-\mu_{\star 0}(x)\}.
\]
For each source $s$, define the observed support set
\[
\calC_{sa}(P)=\{x\in\calX_\star:\Pr(S=s,X=x)>0,\ \Pr(A=a\mid S=s,X=x)>0\}.
\]
When $x\in\calC_{sa}(P)$, define the observed source arm mean $m_{sa}(x)=\E(Y\mid S=s,X=x,A=a)$. The atom-cover graph has left nodes $\calD=\calX_\star\times\{0,1\}$ and right nodes $\calR=\{(s,a):s=1,\ldots,K,\ a\in\{0,1\}\}$, with edge $((x,a),(s,a))$ present when $x\in\calC_{sa}(P)$ and the atom-arm invariance restriction for $(s,a,x)$ is imposed. The certificate is
\[
C(P):\quad \forall (x,a)\in\calD,\ \exists s\in\{1,\ldots,K\}\text{ such that }((x,a),(s,a))\text{ is an edge.}
\]
Equivalently, for every $B\subseteq\calD$, the union of source-supported atom-arm cells adjacent to $B$ covers all elements of $B$; this is the Hall-type finite cover condition used here. Define the stronger common-source cover
\[
D(P):\quad \forall x\in\calX_\star,\ \exists s\in\{1,\ldots,K\}\text{ such that both }((x,0),(s,0))\text{ and }((x,1),(s,1))\text{ are edges.}
\]
The class $C(P)\wedge\neg D(P)$ is the arm-split regime: the treated and untreated target means for at least one target atom must be transported from different source trials. For bounded outcomes $Y\in[\underline y,\overline y]$, define
\[
\ell_a(x)=
\begin{cases}
m_{sa}(x), & \text{if some admissible }s\text{ covers }(x,a),\\
\underline y, & \text{otherwise,}
\end{cases}
\qquad
u_a(x)=
\begin{cases}
m_{sa}(x), & \text{if some admissible }s\text{ covers }(x,a),\\
\overline y, & \text{otherwise.}
\end{cases}
\]
The value is independent of the admissible source under Assumption \ref{ass:invariance}.

\[
\begin{array}{ll}
\text{qid} & \texttt{eid\_fragmented\_transport\_support},\\
\text{specialization} & \texttt{v1},\\
\text{graph / SWIG} & \text{finite-population transport SWIG with target domain } S=\star
  \text{ and trial domains } S\in\{1,\ldots,K\},\\
\text{treatment} & A\in\{0,1\}\text{ randomized within each observed source trial stratum},\\
\text{target estimand} & \theta_\star=\E_\star\{Y(1)-Y(0)\},\\
\text{identifying restrictions} & \text{finite target support, consistency, source-trial randomization,}
  \text{ observed target covariate law, and}\\
& \text{candidate atom-arm conditional mean invariance edges. The atom-cover certificate }C(P)
  \text{ is a testable candidate frontier,}\\
& \text{not an assumed identifying condition.}
\end{array}
\]

\section{Assumptions}
\begin{assumption}[Finite target support]\label{ass:finite}
$\calX_\star$ is finite, and $q_x>0$ is observed for every $x\in\calX_\star$.
\end{assumption}

\begin{assumption}[Consistency]\label{ass:consistency}
In each source trial, $Y=Y(A)$ almost surely.
\end{assumption}

\begin{assumption}[Source-trial randomization]\label{ass:randomization}
For every source $s$, treatment is randomized within observed covariate strata: $(Y(0),Y(1))\perp A\mid S=s,X$ whenever $\Pr(S=s,X=x)>0$.
\end{assumption}

\begin{assumption}[Atom-arm invariance]\label{ass:invariance}
For every edge $((x,a),(s,a))$ in the atom-cover graph,
\[
\E_s\{Y(a)\mid X=x\}=\E_\star\{Y(a)\mid X=x\}.
\]
If two sources cover the same atom-arm pair, their conditional means agree.
\end{assumption}

\begin{assumption}[Bounded outcomes]\label{ass:bounded}
For partial-identification statements, $Y(a)\in[\underline y,\overline y]$ almost surely for $a\in\{0,1\}$ in the target population.
\end{assumption}

\begin{assumption}[No latent cross-atom restrictions]\label{ass:no-cross}
Apart from Assumptions \ref{ass:finite}--\ref{ass:bounded}, the unobserved target conditional means $\{\mu_{\star a}(x)\}$ may vary freely across atom-arm pairs subject only to the stated bounds.
\end{assumption}

\section{Main results}
\begin{conjecture}[Atom-cover equivalence for fragmented transport (NOT YET PROVED)]\label{conj:cover-iff}
Under Assumptions \ref{ass:finite}--\ref{ass:invariance}, $\theta_\star$ is point identified from the observed target covariate law and source trial laws if and only if $C(P)$ holds. When $C(P)$ holds,
\[
\theta_\star=\sum_{x\in\calX_\star}q_x\{m_{s_1(x),1}(x)-m_{s_0(x),0}(x)\},
\]
where $s_a(x)$ is any source covering $(x,a)$.
The sufficiency direction includes arm-split laws satisfying $C(P)\wedge\neg D(P)$, where no common source trial supplies both potential-outcome means for at least one target atom.
\end{conjecture}

\begin{corollary}[Manski rectangle below the certificate]\label{cor:bounds}
Under Assumptions \ref{ass:finite}--\ref{ass:no-cross}, the identified set for $\theta_\star$ is the interval
\begin{equation}\label{eq:sharp-interval}
\Theta_I(P)=
\left[
\sum_{x\in\calX_\star}q_x\{\ell_1(x)-\nu_0(x)\},
\sum_{x\in\calX_\star}q_x\{\nu_1(x)-\ell_0(x)\}
\right].
\end{equation}
The proof is a direct product construction: identified atom-arm means are fixed by randomization and invariance, while each uncovered target atom-arm mean can be set independently anywhere in $[\underline y,\overline y]$. The endpoints are attained by setting uncovered treated means to their lower or upper bound and uncovered control means to the opposite bound.
\end{corollary}

\begin{theorem}[Two-source support-fragmentation witness]\label{thm:witness}
Let $\calX_\star=\{0,1\}$, $q_0,q_1\in(0,1)$, source 1 have $\Pr(X=0\mid S=1)=1$, and source 2 have $\Pr(X=1\mid S=2)=1$, with both treatment arms randomized in each source. Under Assumptions \ref{ass:finite}--\ref{ass:invariance}, neither source alone identifies $\theta_\star$, while the pair identifies it by
\[
\theta_\star=q_0\{m_{11}(0)-m_{10}(0)\}+q_1\{m_{21}(1)-m_{20}(1)\}.
\]
If the invariance edge for $(x=1,a=1)$ is removed and $Y\in[0,1]$, then two target laws with $\mu_{\star 1}(1)=0$ and $\mu_{\star 1}(1)=1$ are observationally equivalent but differ in $\theta_\star$ by $q_1$.
\end{theorem}

\section{Sanity-check corollaries}
\begin{corollary}[Single-source positivity reduction]\label{cor:single-source}
If $K=1$ and source 1 covers every $(x,a)\in\calX_\star\times\{0,1\}$, Conjecture \ref{conj:cover-iff} reduces to the standard trial-transport standardization formula
\[
\theta_\star=\sum_{x\in\calX_\star}q_x\{m_{11}(x)-m_{10}(x)\}.
\]
Under Assumptions \ref{ass:finite}--\ref{ass:invariance}, this collapses to the usual single-trial transport estimand because the cover graph has one source neighbor for every atom-arm pair.
\end{corollary}

\paragraph{Exhibit 9.1: computed atom-cover certificate.}
Let $\calX_\star=\{0,1\}$, $q_0=0.4$, $q_1=0.6$, and $Y\in[0,1]$. Source 1 observes $X=0$ with treatment probabilities $\Pr(A=1\mid S=1,X=0)=1/2$ and means $m_{11}(0)=0.7$, $m_{10}(0)=0.2$. Source 2 observes $X=1$ with treatment probabilities $\Pr(A=1\mid S=2,X=1)=1/2$ and means $m_{21}(1)=0.6$, $m_{20}(1)=0.4$. The left nodes are $(0,0),(0,1),(1,0),(1,1)$, and the right source-arm nodes are $(1,0),(1,1),(2,0),(2,1)$; the edge set is $((0,0),(1,0))$, $((0,1),(1,1))$, $((1,0),(2,0))$, $((1,1),(2,1))$. Every left node has a source-supported edge, all denominators are $1/2$, and the computed target ATE is $0.4(0.7-0.2)+0.6(0.6-0.4)=0.32$.

\paragraph{Exhibit 9.2: sharp failure interval.}
Remove only the edge $((1,1),(2,1))$ while keeping the observed source laws and target covariate law fixed. Then $\ell_1(1)=0$, $\nu_1(1)=1$, and all other atom-arm means are fixed, so Corollary \ref{cor:bounds} gives $\Theta_I(P)=[0.4(0.5)+0.6(0-0.4),\,0.4(0.5)+0.6(1-0.4)]=[-0.04,0.56]$. The construction is internally consistent because each atom-arm mean appears once, treatment propensities are nonzero in observed source cells, and no unobserved infinite-dimensional object is used.

\section{Proof-sketch route}
Conjecture \ref{conj:cover-iff}: headline $\leftarrow$ unfold the finite target ATE and cover graph definitions $\leftarrow$ substitute consistency, source randomization, and atom-arm invariance $\leftarrow$ step 1: prove source arm means are unique on overlapping admissible edges by Assumption \ref{ass:invariance} $\leftarrow$ step 2: construct the standardization functional by selecting one admissible edge for each atom-arm pair, including the arm-split class $C(P)\wedge\neg D(P)$ $\leftarrow$ step 3: prove necessity by choosing a failed atom-arm pair, holding all observed source and target covariate laws fixed, and varying only the missing target conditional potential-outcome mean $\leftarrow$ step 4: verify the two resulting laws satisfy all remaining restrictions and differ in $\theta_\star$ by $q_x\Delta$ $\leftarrow$ finite-support countermodel separation. Thus $k=4$ substantive non-definitional steps. Corollary \ref{cor:bounds}: headline $\leftarrow$ unfold $\Theta_I(P)$ $\leftarrow$ substitute boundedness and no-cross-atom restrictions $\leftarrow$ product rectangularity of uncovered atom-arm means $\leftarrow$ linear optimization over a rectangle $\leftarrow$ endpoint-attainment construction. Theorem \ref{thm:witness}: headline $\leftarrow$ instantiate the two-atom design $\leftarrow$ compute the cover graph and the standardization formula $\leftarrow$ remove one invariance edge $\leftarrow$ build the paired laws used in the necessity step.

\section{Honest scope flags}
Conjecture \ref{conj:cover-iff} is the open flagship claim; the sufficiency direction is routine, but the necessity direction must be checked against possible cross-source restrictions not encoded in Assumption \ref{ass:no-cross}. Corollary \ref{cor:bounds} is not claimed as novel relative to Manski--Robins bounded-outcome bounds; it is retained only as the below-frontier diagnostic attached to a failed atom-arm cover. The Hall terminology is used in the finite cover sense, not as a capacity-constrained matching theorem; a reviewer may prefer the name ``atom-cover certificate.''

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft; prior verdict: none.
\item v2 (revise) -- repositioned Conjecture 1 against Dahabreh et al. (2023) Sec. 3.4/Theorem 3, reworded $C(P)$ as a candidate frontier, and downgraded the bounded interval to a Manski--Robins corollary; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bareinboim, Lee, Honavar, and Pearl(2013)]{BareinboimLeeHonavarPearl2013}
Bareinboim, E., S. Lee, V. Honavar, and J. Pearl (2013).
\newblock Transportability from multiple environments with limited experiments.
\newblock \emph{Advances in Neural Information Processing Systems}.

\bibitem[Cole and Stuart(2010)]{ColeStuart2010}
Cole, S. R. and E. A. Stuart (2010).
\newblock Generalizing evidence from randomized clinical trials to target populations: The ACTG 320 trial.
\newblock \emph{American Journal of Epidemiology} 172(1), 107--115.

\bibitem[Dahabreh, Petito, Robertson, Hernan, and Steingrimsson(2020)]{DahabrehPetitoRobertsonHernanSteingrimsson2020}
Dahabreh, I. J., L. C. Petito, S. E. Robertson, M. A. Hernan, and J. A. Steingrimsson (2020).
\newblock Toward causally interpretable meta-analysis: Transporting inferences from multiple randomized trials to a new target population.
\newblock \emph{Epidemiology} 31(3), 334--344.

\bibitem[Dahabreh, Robertson, Petito, Hernan, and Steingrimsson(2023)]{DahabrehRobertsonPetitoHernanSteingrimsson2023}
Dahabreh, I. J., S. E. Robertson, L. C. Petito, M. A. Hernan, and J. A. Steingrimsson (2023).
\newblock Efficient and robust methods for causally interpretable meta-analysis: Transporting inferences from multiple randomized trials to a target population.
\newblock \emph{Biometrics} 79(2), 1057--1072.

\bibitem[Dahabreh and Stuart(2021)]{DahabrehStuart2021PCORI}
Dahabreh, I. J. and E. A. Stuart (2021).
\newblock Methods for extending causal inferences from a randomized trial to a target population.
\newblock \emph{PCORI Methods Report}.

\bibitem[Degtiar and Rose(2023)]{DegtiarRose2023}
Degtiar, I. and S. Rose (2023).
\newblock A review of generalizability and transportability.
\newblock \emph{Annual Review of Statistics and Its Application} 10, 501--524.

\bibitem[Hotz, Imbens, and Mortimer(2005)]{HotzImbensMortimer2005}
Hotz, V. J., G. W. Imbens, and J. H. Mortimer (2005).
\newblock Predicting the efficacy of future training programs using past experiences at other locations.
\newblock \emph{Journal of Econometrics} 125(1--2), 241--270.

\bibitem[Kline and Tamer(2018)]{KlineTamer2018}
Kline, B. and E. Tamer (2018).
\newblock Identification of treatment effects with selective participation in a randomized trial.
\newblock \emph{The Econometrics Journal} 21(3), 332--353.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review} 80(2), 319--323.

\bibitem[Robins(1989)]{Robins1989}
Robins, J. M. (1989).
\newblock The analysis of randomized and non-randomized AIDS treatment trials using a new approach to causal inference in longitudinal studies.
\newblock In \emph{Health Service Research Methodology: A Focus on AIDS}, 113--159.

\bibitem[Su, Rytgaard, Ravn, and Eriksson(2024)]{SuRytgaardRavnEriksson2024}
Su, Y., H. Rytgaard, H. Ravn, and F. Eriksson (2024).
\newblock Semiparametric efficient estimation of target average treatment effects using multiple source trials.
\newblock \emph{arXiv:2405.10769}.

\bibitem[Westreich, Edwards, Lesko, Stuart, and Cole(2017)]{WestreichEdwardsLeskoStuartCole2017}
Westreich, D., J. K. Edwards, C. R. Lesko, E. Stuart, and S. R. Cole (2017).
\newblock Transportability of trial results using inverse odds of sampling weights.
\newblock \emph{American Journal of Epidemiology} 186(8), 1010--1014.

\bibitem[Zivich, Edwards, Shook-Sa, Lofgren, Lessler, and Cole(2025)]{ZivichEdwardsShookSaLofgrenLesslerCole2025}
Zivich, P. N., J. K. Edwards, B. E. Shook-Sa, E. T. Lofgren, J. Lessler, and S. R. Cole (2025).
\newblock Positivity and transportability in causal inference.
\newblock \emph{Journal of the Royal Statistical Society: Series A}.
\end{thebibliography}

\end{document}
