\section{Main results}

This section characterizes the design-based variance of the Hájek linearization, then studies the graph-only envelope as a conservative allocation criterion. The outcome-agnostic criterion protects against the bounded potential-outcome schedules permitted by \cref{obj:ass:bounded-outcomes}. It provides an exploratory design-stage rule for reallocating a fixed expected treatment budget using observed overlap structure. Related design-based analyses under interference likewise distinguish the randomization distribution from an outcome model \citep{AronowSamii2017GeneralInterference,SavjeAronowHudgens2021}.

We first recover the familiar homogeneous Bernoulli expressions as a special case. When all intervention units receive the same probability, only the size of the shared neighborhood determines the same-exposure covariance loads.

\begin{theoremv}{prop:homogeneous-reduction}[Homogeneous Bernoulli Reduction]
Under \cref{obj:ass:independent-heterogeneous-bernoulli}, suppose that the assignment probabilities are constant, \(p_k=p\) for every \(k\in I_n\), for some \(p\in(0,1)\). Then, for every \(i,j\in O_n\),
\[
r_{ij}^1(G_n,p)=
\begin{cases}
p^{-|S_{ij}(G_n)|}-1, & |S_{ij}(G_n)|>0,\\
0, & |S_{ij}(G_n)|=0,
\end{cases}
\qquad
r_{ij}^0(G_n,p)=
\begin{cases}
(1-p)^{-|S_{ij}(G_n)|}-1, & |S_{ij}(G_n)|>0,\\
0, & |S_{ij}(G_n)|=0.
\end{cases}
\]
Moreover,
\[
\sigma_{G_n,p}^2(Y)
=
\frac{1}{n}\sum_{i\in O_n}\sum_{j\in O_n}
\left[
r_{ij}^1(G_n,p)(Y_i^1-\mu_1)(Y_j^1-\mu_1)
+r_{ij}^0(G_n,p)(Y_i^0-\mu_0)(Y_j^0-\mu_0)
+2r_{ij}^{10}(G_n)(Y_i^1-\mu_1)(Y_j^0-\mu_0)
\right].
\]
\end{theoremv}

\cref{obj:prop:homogeneous-reduction} shows that homogeneous assignment is governed by overlap counts beyond the marginal degrees of outcome units. It also supplies the benchmark against which the heterogeneous criterion below is compared.

\subsection{Variance representation and envelope optimization}

The next result gives the pairwise covariance representation under heterogeneous assignment and bounds the resulting variance scale by the graph envelope.

\begin{theoremv}{thm:hetero-envelope}[Heterogeneous envelope kernel]
Suppose that:
\begin{itemize}
\item \textbf{(Assignment probabilities.)} $0<p_k<1$ for every $k\in I_n$.
\item \textbf{(Design.)} \cref{obj:ass:independent-heterogeneous-bernoulli} holds with assignment-probability vector $p$.
\item \textbf{(Outcomes.)} \cref{obj:ass:bounded-outcomes} holds.
\end{itemize}
Then, for every $i,j\in O_n$,
\[
\mathbb E_p\!\left[\eta_i(p,Z)\eta_j(p,Z)\right]
=
r_{ij}^1(G_n,p)(Y_i^1-\mu_1)(Y_j^1-\mu_1)
+r_{ij}^0(G_n,p)(Y_i^0-\mu_0)(Y_j^0-\mu_0)
+r_{ij}^{10}(G_n)\!\left\{(Y_i^1-\mu_1)(Y_j^0-\mu_0)+(Y_i^0-\mu_0)(Y_j^1-\mu_1)\right\}.
\]
Moreover,
\[
\sigma^2_{G_n,p}(Y)\le V_{\mathrm{env}}(G_n,p).
\]
\end{theoremv}

\cref{obj:thm:hetero-envelope} separates the schedule-dependent covariance terms from their graph-and-design loads. Bounded outcomes make the displayed envelope uniform over the admissible schedule class and give it a conservative design interpretation.

The envelope's inputs are known before randomization, and its minimization has a convex formulation. The following result establishes existence and provides the corresponding optimality characterization.

\begin{theoremv}{thm:convex-design}[Convex feasible design]
Let $G_n$ be a bipartite experiment with intervention-unit set $I_n$, and let $\epsilon,B_n\in\mathbb R$. Suppose that
\begin{itemize}
\item \textbf{(Positivity margin.)} $0<\epsilon<1/2$;
\item \textbf{(Feasible budget.)} $m_n\epsilon\le B_n\le m_n(1-\epsilon)$.
\end{itemize}
Then $\mathcal P_{n,B_n,\epsilon}$ is nonempty, compact, and convex, and $p\mapsto V_{\mathrm{env}}(G_n,p)$ is convex on $\mathcal P_{n,B_n,\epsilon}$. Moreover, there exists a minimizer $p_n^*(G_n)\in\mathcal P_{n,B_n,\epsilon}$ such that
\[
V_{\mathrm{env}}(G_n,p_n^*(G_n))
\le V_{\mathrm{env}}(G_n,q)
\qquad\text{for every }q\in\mathcal P_{n,B_n,\epsilon}.
\]
For every such minimizer $p_n^*(G_n)$, there exist $\lambda_n\in\mathbb R$ and functions $\nu^+_{\cdot,n},\nu^-_{\cdot,n}:I_n\to\mathbb R$ such that, for every $k\in I_n$,
\[
\nu^+_{k,n}\ge0,\qquad \nu^-_{k,n}\ge0,\qquad
g_k(G_n,p_n^*(G_n))=\lambda_n-\nu^+_{k,n}+\nu^-_{k,n},
\]
and
\[
\nu^+_{k,n}\bigl((p_n^*(G_n))_k-(1-\epsilon)\bigr)=0,
\qquad
\nu^-_{k,n}\bigl(\epsilon-(p_n^*(G_n))_k\bigr)=0.
\]
\end{theoremv}

\cref{obj:thm:convex-design} places the allocation problem in a standard finite-dimensional convex-optimization form \citep[Chs.~4--5]{BoydVandenberghe2004}. Positivity makes every reciprocal-product term differentiable on the feasible box; convexity, the affine budget equality, and the two coordinate bounds supply the objective and constraint structure. At an interior coordinate, the envelope gradient score equals the common budget multiplier; at a probability bound, complementary slackness gives the corresponding one-sided condition. The formally verified statement covers feasible endpoint budgets directly. Because the objective couples probabilities across shared neighborhoods, the allocation depends on the full overlap score beyond \(s_k\), intervention degree, or any single local statistic.

\subsection{Large-sample inference and design-stage coverage}

We next turn to inference for the envelope-optimal design. The central-limit result combines the Hájek linearization with the bounded-degree dependency structure induced by overlapping neighborhoods.

\begin{theoremv}{thm:hetero-clt}[Heterogeneous Hájek CLT]
Consider a sequence of bipartite experiments indexed by $n$. Suppose:
\begin{itemize}
\item \textbf{(Outcome indexing.)} For all sufficiently large $n$, $|O_n|=n$.
\item \textbf{(Assignment and interference.)} \cref{obj:ass:independent-heterogeneous-bernoulli} and \cref{obj:ass:bipartite-interference} hold at every $n$ for the assignment design $D_n$ and probabilities $p_n$.
\item \textbf{(Outcome and graph regularity.)} \cref{obj:ass:bounded-outcomes}, \cref{obj:ass:bounded-outcome-degree}, and \cref{obj:ass:bounded-overlap-dependency} hold at every $n$, with constants $\bar d$ and $\bar D$, respectively.
\item \textbf{(Feasibility and optimality.)} For every $n$, $p_n\in\mathcal P_{n,B_n,\epsilon_n}$ as in \cref{obj:def:feasible-designs}, and
\[
p_n=p_n^*(G_n)
\]
as in \cref{obj:def:optimal-design}.
\item \textbf{(Uniform positivity.)} There exists $\epsilon_0>0$ such that $\epsilon_0\le\epsilon_n$ for all sufficiently large $n$.
\item \textbf{(Variance.)} \cref{obj:ass:variance-nondegenerate} holds for $\sigma^2_{G_n,p_n}(Y)$ as in \cref{obj:def:variance-scale}.
\end{itemize}
Then, for every $\delta>0$,
\[
\Pr_{D_n}\!\left(
\left|
\sqrt n\bigl\{\widehat\tau_H(p_n^*(G_n))-\tau_n\bigr\}
-n^{-1/2}\sum_{i\in O_n}\eta_i(p_n^*(G_n),Z)
\right|\ge\delta
\right)\longrightarrow 0,
\]
and, for every $s\in\mathbb R$,
\[
\Pr_{D_n}\!\left(
\frac{\sqrt n\bigl\{\widehat\tau_H(p_n^*(G_n))-\tau_n\bigr\}}
{\sqrt{\sigma^2_{G_n,p_n^*(G_n)}(Y)}}\le s
\right)
\longrightarrow
\Pr\!\left\{N(0,1)\le s\right\}.
\]
\end{theoremv}

\cref{obj:thm:hetero-clt} is a design-based result: the potential-outcome schedule remains fixed throughout. Uniform positivity and bounded outcome degree control inverse-probability weights, bounded overlap dependency limits the number of dependent exposure terms associated with any outcome, and nondegeneracy supplies positive fluctuation. These familiar dependency-graph conditions define a sparse local-dependence regime \citep{AronowSamii2017GeneralInterference,LuShiFangZhangDing2025BipartiteDesign}.

For applied use, the relevant graph diagnostics are the empirical distributions of \(d_i\), intervention incidences \(s_k\), and degrees in the outcome-overlap graph. Sequences with uniformly bounded values of the first and third quantities fall within the theorem's graph scope. These diagnostics therefore make the bounded-local-dependence requirement directly auditable.

The next result translates the same regularity conditions into a Wald interval based on the deterministic graph-only scale of \cref{obj:def:conservative-variance-estimator}.

\begin{theoremv}{thm:postdesign-wald}[Post-design Wald coverage]
For a sequence of bipartite experiments $G_n$ with outcome sets $O_n$, finite assignment designs, probability vectors $p_n$, positivity margins $\epsilon_n$, and budgets $B_n$, suppose:
\begin{itemize}
\item \textbf{(Outcome indexing.)} $|O_n|=n$ for all sufficiently large $n$.
\item \textbf{(Assignment law.)} The assignment design satisfies \cref{obj:ass:independent-heterogeneous-bernoulli} with $0\le p_{n,k}\le 1$ for every $n$ and $k\in I_n$.
\item \textbf{(Interference and boundedness.)} \cref{obj:ass:bipartite-interference}, \cref{obj:ass:bounded-outcomes}, \cref{obj:ass:bounded-outcome-degree}, and \cref{obj:ass:bounded-overlap-dependency} hold with constants $\bar d$ and $\bar D$.
\item \textbf{(Feasibility and optimality.)} For every $n$, $p_n$ is a feasible design in the sense of \cref{obj:def:feasible-designs}, $\epsilon_n\in(0,1/2)$, and
\[
p_n=p_n^*(G_n)
\]
in the sense of \cref{obj:def:optimal-design}.
\item \textbf{(Uniform positivity.)} There exists $\epsilon_0>0$ such that $\epsilon_0\le\epsilon_n$ for all sufficiently large $n$.
\item \textbf{(Nondegenerate variance.)} \cref{obj:ass:variance-nondegenerate} holds for $\sigma^2_{G_n,p_n}(Y)$.
\item \textbf{(Wald critical value.)} $\alpha_{\mathrm{cov}}\in(0,1)$, $z_{1-\alpha_{\mathrm{cov}}/2}\ge0$, and
\[
\Phi\!\left(z_{1-\alpha_{\mathrm{cov}}/2}\right)
=1-\frac{\alpha_{\mathrm{cov}}}{2}.
\]
\end{itemize}
Then, for every $n$,
\[
\sigma^2_{G_n,p_n}(Y)\le \widehat V_{\mathrm{cons}}(G_n,p_n),
\]
where $\sigma^2_{G_n,p_n}(Y)$ and $\widehat V_{\mathrm{cons}}(G_n,p_n)$ are as in \cref{obj:def:variance-scale} and \cref{obj:def:conservative-variance-estimator}, respectively; moreover,
\[
1-\alpha_{\mathrm{cov}}
\le
\liminf_{n\to\infty}
\Pr_{p_n}\!\left(
\left|\tau_n-\widehat\tau_H(p_n)\right|
\le
z_{1-\alpha_{\mathrm{cov}}/2}
\sqrt{\frac{\widehat V_{\mathrm{cons}}(G_n,p_n)}{n}}
\right).
\]
\end{theoremv}

\cref{obj:thm:postdesign-wald} yields asymptotically conservative coverage using a scale determined entirely by the graph and selected probabilities, giving an outcome-model-free guarantee.

\subsection{When heterogeneous probabilities improve on homogeneity}

The envelope can strictly favor heterogeneity even under a fixed expected treatment budget. To state a quantitative comparison, recall the directional curvature quantity introduced in \cref{sec:setup-and-assumptions}. Equivalently, along the budget-preserving direction from the highest-score coordinate \(a\) to the lowest-score coordinate \(b\),
\[
L_{ab}
=
\sup_{q\in\mathcal P_{n,B_n,\epsilon}}
(e_b-e_a)^\top
\operatorname{Hess}\!\left\{V_{\mathrm{env}}(G_n,q)/4\right\}
(e_b-e_a).
\]
The supremum ranges only over the feasible probability domain. Since the positivity floor makes that domain compact and keeps every reciprocal probability factor finite, \(L_{ab}\) admits finite graph-specific bounds whenever the displayed derivatives are evaluated on that domain.

\begin{theoremv}{thm:heterogeneity-separation}[Heterogeneity separation]
Let \(G_n\) be a bipartite experiment with \(m_n=|I_n|>0\), and let \(\epsilon\in(0,1/2)\). Suppose that:
\begin{itemize}
\item \textbf{(Admissible budget.)} \(m_n\epsilon\le B_n\le m_n(1-\epsilon)\).
\item \textbf{(Homogeneous rate.)} \(\rho=B_n/m_n\), with \(\epsilon<\rho<1-\epsilon\) and \(\rho\neq 1/2\).
\item \textbf{(Homogeneous design.)} \(p^{\mathrm{hom}}_k=\rho\) for every \(k\in I_n\).
\end{itemize}
Then all of the following hold:
\begin{itemize}
\item If there exist \(a,b\in I_n\) such that
\[
g_a(G_n,p^{\mathrm{hom}})\neq g_b(G_n,p^{\mathrm{hom}}),
\]
then \(p^{\mathrm{hom}}\) is not a minimizer of \(V_{\mathrm{env}}(G_n,\cdot)\) over \(\mathcal P_{n,B_n,\epsilon}\). Moreover, there exist \(a,b\in I_n\) attaining, respectively, the maximum and minimum homogeneous-point gradient scores, such that
\[
\Delta_g:=g_a(G_n,p^{\mathrm{hom}})-g_b(G_n,p^{\mathrm{hom}})>0.
\]
For every \(p_n^*(G_n)\in\operatorname{argmin}_{p\in\mathcal P_{n,B_n,\epsilon}}V_{\mathrm{env}}(G_n,p)\),
\[
p_n^*(G_n)\neq p^{\mathrm{hom}},\qquad
V_{\mathrm{env}}(G_n,p_n^*(G_n))<V_{\mathrm{env}}(G_n,p^{\mathrm{hom}}),
\]
and
\[
V_{\mathrm{env}}(G_n,p^{\mathrm{hom}})-V_{\mathrm{env}}(G_n,p_n^*(G_n))
\ge
2\Delta_g
\begin{cases}
\min\{\rho-\epsilon,\,1-\epsilon-\rho\}, & L_{ab}=0,\\
\min\!\left\{\min\{\rho-\epsilon,\,1-\epsilon-\rho\},\,\Delta_g/L_{ab}\right\}, & L_{ab}\neq0,
\end{cases}
\]
where \(L_{ab}\) is the directional modulus along \(e_b-e_a\).

\item If \(|N_i(G_n)|=1\) for every \(i\in O_n\), then, for every \(k\in I_n\),
\[
g_k(G_n,p^{\mathrm{hom}})
=
n^{-1}s_k^2\left((1-\rho)^{-2}-\rho^{-2}\right).
\]

\item If \(|N_i(G_n)|=1\) for every \(i\in O_n\) and there exist \(a,b\in I_n\) such that \(s_a^2\neq s_b^2\), then the preceding non-homogeneity, strict-improvement, and gap conclusions hold.
\end{itemize}
\end{theoremv}

The singleton-neighborhood case gives a transparent diagnostic: when \(\rho\neq 1/2\), heterogeneity in intervention-side incidence produces heterogeneous homogeneous-point scores and a strict envelope-improving direction away from homogeneous assignment. More generally, the score spread captures overlap patterns beyond \(s_k\) alone.

\subsection{A bounded-degree surrogate and its limitation}

The exact envelope couples probabilities across shared neighborhoods. The additive surrogate in \cref{obj:def:surrogate-design} removes that coupling and is therefore attractive for implementation. Under bounded outcome degree, its loss relative to the envelope optimum is uniformly controlled.

\begin{theoremv}{thm:surrogate-certificate}[Surrogate approximation certificate]
For a bipartite experiment on \(G_n\), suppose:
\begin{itemize}
\item \textbf{(Admissible floor.)} \(0<\epsilon<1/2\).
\item \textbf{(Bounded outcome degree.)} \cref{obj:ass:bounded-outcome-degree} holds with bound \(\bar d\).
\item \textbf{(Admissible budget.)} \(m_n\epsilon\le B_n\le m_n(1-\epsilon)\).
\end{itemize}
Then, for every \(p\in\mathcal P_{n,B_n,\epsilon}\) of \cref{obj:def:feasible-designs},
\[
\sum_{k\in I_n}h_k(G_n)\!\left\{p_k^{-1}+(1-p_k)^{-1}\right\}
\le \frac{V_{\mathrm{env}}(G_n,p)}{4}
\le
\max\!\left\{1,\epsilon^{-(\bar d-1)}\right\}
\sum_{k\in I_n}h_k(G_n)\!\left\{p_k^{-1}+(1-p_k)^{-1}\right\}.
\]
Moreover, the approximation ratio of \cref{obj:def:approximation-ratio} satisfies
\[
\alpha_{\mathrm{cert}}(G_n)\le
\max\!\left\{1,\epsilon^{-(\bar d-1)}\right\}.
\]
\end{theoremv}

The certificate constant deteriorates with the allowed outcome degree and with a small positivity floor. Reporting \(\max_i d_i\), \(\epsilon\), and the resulting bound therefore makes clear when the surrogate guarantee is informative and when it is effectively vacuous.

A natural conjecture is that broad dispersion in intervention-side degrees, combined with the one-sided conditional weight-ratio restriction used below, might itself control the surrogate's envelope approximation quality. The following result rules out such a conclusion; its counterexample can satisfy equal positive \(h\)-weights even though the formal condition is stated one-sidedly.

\begin{theoremv}{thm:dispersion-certificate-unbounded}[Unbounded dispersion certificate]
For every $\epsilon\in(0,1/2)$, $c_{\mathrm{disp}}>0$, and $C_{\mathrm{disp}}\geq 1$, there exist sequences of finite intervention-unit sets $I_n$, finite outcome-unit sets $O_n$, finite bipartite experiments $G_n$, and budgets $B_n$ such that, for every $n$,

\begin{itemize}

\item \textbf{(Admissible budget.)} With $m_n=|I_n|$,
\[
m_n\epsilon\leq B_n\leq m_n(1-\epsilon).
\]

\item \textbf{(Positive energy.)}
\[
0<\sum_{k\in I_n}s_k^2.
\]

\end{itemize}

Moreover, for all sufficiently large $n$,

\begin{itemize}

\item \textbf{(Degree dispersion.)} For every $k\in I_n$,
\[
s_k^2\leq c_{\mathrm{disp}}\sum_{l\in I_n}s_l^2.
\]

\item \textbf{($h$-weight ratio.)} For every $k,l\in I_n$,
\[
h_l(G_n)>0\ \Longrightarrow\ h_k(G_n)\leq C_{\mathrm{disp}}\,h_l(G_n).
\]

\end{itemize}

Finally, the approximation ratio of \cref{obj:def:approximation-ratio} satisfies
\[
\alpha_{\mathrm{cert}}(G_n)\longrightarrow\infty .
\]
\end{theoremv}

\cref{obj:thm:dispersion-certificate-unbounded} shows that degree dispersion and the conditional restriction
\[
h_l(G_n)>0\Longrightarrow h_k(G_n)\le C_{\mathrm{disp}}h_l(G_n)
\]
cannot replace the bounded-degree condition behind \cref{obj:thm:surrogate-certificate}. Thus, the separable rule is best treated as a bounded-degree approximation with an explicit certificate, not as a generally reliable proxy for the full overlap criterion.
