\section{Appendix: finite-design identities, optimization, and asymptotic arguments}

This appendix separates the finite-design calculations underlying the exposure-weighted estimator from the convex-optimization and asymptotic arguments used in the main text. The finite-design component uses independent Bernoulli randomization to obtain the exposure and covariance identities that underlie \cref{obj:thm:hetero-envelope} and~\cref{obj:prop:homogeneous-reduction}. The optimization component concerns the compact feasible class and reciprocal-product objective in \cref{obj:thm:convex-design}. The final component treats denominator events and normal approximation under bounded local dependence, extending familiar design-based arguments for ratio estimators and interference settings \citep{HorvitzThompson1952,Hajek1964,LiuHudgens2014}.

The random normalization in the Hájek estimator requires both exposure-weighted denominators to be positive with probability approaching one. The following lemma supplies that control uniformly over feasible probability vectors.

\begin{lemmav}{lem:denominator-positivity}[Denominator Degeneracy Bound]
Let $\epsilon\in(0,1/2)$, and let $(G_n)_{n\geq 0}$ be a sequence of bipartite experiments with intervention sets $I_n$ and outcome sets $O_n$. Suppose that:

\begin{itemize}

\item \textbf{(Outcome-population indexing.)} $|O_n|=n$ for every $n\geq 0$.

\item \textbf{(Admissible budgets.)} For every $n\geq 0$,
\[
|I_n|\epsilon\leq B_n\leq |I_n|(1-\epsilon).
\]

\item \textbf{(Bounded degrees.)} \cref{obj:ass:bounded-outcome-degree} holds with constant $\bar d$.

\item \textbf{(Bounded overlap dependency.)} \cref{obj:ass:bounded-overlap-dependency} holds with constant $\bar D$.
\end{itemize}

Then there exists a constant $C\geq 0$ such that, for all sufficiently large $n$, every $q=(q_k)_{k\in I_n}$ with $0\leq q_k\leq1$ for all $k\in I_n$ and $q\in\mathcal P_{n,B_n,\epsilon}$ as in \cref{obj:def:feasible-designs} satisfies
\[
\Pr_q\!\left(D_1(q,Z)=0\ \text{or}\ D_0(q,Z)=0\right)
\leq \frac{C}{n},
\]
where $Z$ has independent Bernoulli coordinates with assignment probabilities $q$, and $D_1(q,Z)$ and $D_0(q,Z)$ are as in \cref{obj:def:hajek-denominators}.
\end{lemmav}

\cref{obj:lem:denominator-positivity} combines the positivity floor with bounded outcome neighborhoods to keep each inverse-probability exposure contribution controlled. Bounded overlap dependency then limits the aggregate covariance among these contributions. Its uniformity over the feasible class supports evaluation at a graph-selected design as well as at fixed homogeneous probability vectors. In particular, the zero-denominator event in \cref{obj:def:hetero-hajek-estimator} has probability of order \(n^{-1}\) under the conditions used for \cref{obj:thm:hetero-clt}.

For the asymptotic argument, dependence is represented by the outcome-overlap graph. The next lemma gives the normal approximation invoked after the Hájek estimator has been linearized into the summands of \cref{obj:def:first-order-linearization}.

\begin{lemmav}{lem:bounded-degree-dependency-clt}[Bounded-Degree Dependency CLT]
Let \(\{X_{n,i}: i\in\iota_n\}\) be real-valued random variables, where \(|\iota_n|=n\), under the usual measurability and integrability conditions. Suppose:
\begin{itemize}
\item \textbf{(Centered summands.)} For every \(n\) and \(i\in\iota_n\), \(\mathbb E[X_{n,i}]=0\).
\item \textbf{(Dependency degree.)} The variables admit a dependency graph whose neighborhood of every \(i\in\iota_n\) has cardinality at most \(D\), for a fixed \(D\in\mathbb N\).
\item \textbf{(Uniform bound.)} There is an \(M\ge 0\) such that \(|X_{n,i}|\le M\) for every \(n\), \(i\in\iota_n\), and outcome.
\item \textbf{(Variance growth.)} Writing \(S_n=\sum_{i\in\iota_n}X_{n,i}\), suppose \(\mathbb E[S_n^2]=v_n\) for every \(n\), and, for some \(c>0\), \(v_n\ge cn\) for all sufficiently large \(n\).
\end{itemize}
Then, for every \(s\in\mathbb R\),
\[
\lim_{n\to\infty}\Pr\!\left(\frac{S_n}{\sqrt{v_n}}\le s\right)
=
\Pr\!\left(Z\le s\right),
\qquad Z\sim\mathcal N(0,1).
\]
\end{lemmav}

\cref{obj:lem:bounded-degree-dependency-clt} isolates the probabilistic ingredient needed for \cref{obj:thm:hetero-clt}. The uniform summand bound follows there from bounded potential outcomes, bounded outcome degree, and the positivity floor. The dependency-degree condition is supplied by the overlap bound, while nondegeneracy of the variance scale yields the required linear variance growth. Thus, the lemma addresses local dependence induced by shared intervention neighborhoods.

\subsection{Verification note}

The displayed theorem and lemma statements in this paper, together with their proofs, are machine-checked in Lean~4. The checked finite-design component covers the Bernoulli-randomization, exposure-probability, denominator, covariance, and optimization identities used in the stated results. The bipartite graph, fixed potential-outcome schedule, and bipartite-interference restriction enter as identification primitives; the positivity and budget restrictions, bounded outcomes, bounded outcome degree, bounded overlap dependency, and variance nondegeneracy conditions enter as stated hypotheses. Classical finite-set and real-number reasoning is used where required. The replication archive accompanying this paper records the permanent artifact location, exact source revision, Lean and library versions, one-command build instruction, and the correspondence between each displayed formal result and its checked declaration.
