\paragraph{Solve target restated.}
Is there a finite family of rational functions $\{v_j(\lambda)\}_{j\in J}$ of $(p_x,q_{m\mid x},r_{x,m},\lambda)$,
indexed by active-set cells of the lifted polytope of \S\ref{sec:setup}, with
\[
  L(\lambda)=\min_{j\in J}v_j(\lambda),\qquad U(\lambda)=\max_{j\in J}v_j(\lambda),
\]
and a closed-form threshold $\lambda^\star=\lambda^\star(P)>0$ at which the maximizing (resp.\ minimizing)
cell changes, so that $U(\cdot)$ (resp.\ $L(\cdot)$) is piecewise-rational with a kink at $\lambda^\star$?

\smallskip\noindent\textbf{No-kink convention.} Set
$\lambda^\star(P):=\inf\{\lambda>0:\text{the maximizing cell at }\lambda\text{ differs from the cell active at }0^+\}$,
with $\lambda^\star(P):=+\infty$ when no such switch occurs---a single cell is maximizing throughout, as on the
degenerate support $|\mathcal U|=1$ (Corollary~\ref{cor:degenerate}) or wherever one branch dominates for all
$\lambda$. The kink claim is scoped to the generic regime $\{P:0<\lambda^\star(P)<\infty\}$; on its complement
$U(\cdot)$ is a single rational branch with no interior kink and the construction returns that branch. The
symmetric convention defines the minimizing-cell threshold for $L(\cdot)$.

\smallskip\noindent\textbf{Handle:} lift the bilinear program with $g_{m,x,u}=\varphi(m,x,u)w_x(u)$ so the
compatibility equations \eqref{eq:compat} become linear; for fixed $(w_0,w_1)$ on the latent simplices,
enumerate the active-set cells of \S\ref{sec:setup} (which box bounds $g_{m,x,u}\in\{0,w_x(u)\}$ and which
leak bounds $|d(m,u)|\le\lambda$ bind), read each cell's vertex value of \eqref{eq:ace} as a rational
function $v_j$ of the data and $(w_0,w_1)$, optimize over $(w_0,w_1)$, and locate $\lambda^\star$ as the
smallest $\lambda$ solving the boundary equality $v_{j}(\lambda)=v_{j'}(\lambda)$ between the two adjacent
maximizing cells. Start from $|\mathcal U|=2$, the smallest support allowing $w_0\neq w_1$.
\textbf{Why it matters:} a closed-form vertex formula lets front-door software report the leak interval and
its kink directly from $(p_x,q_{m\mid x},r_{x,m})$ without solving a nonconvex program at every $\lambda$.

\begin{theorem}[Finite response-type basis for the leak endpoints]\label{thm:vertex}
Yes, with the no-kink convention applied to reduced value branches rather than to duplicate LP bases. For $\bar\lambda=\min\{\lambda,1\}$, the leak endpoint pair is computed by the finite response-type LP \eqref{eq:vlp}; its feasible-basis values are rational functions $v_B^U(P,\lambda)=c_B(P,\lambda)^\mathsf{T}A_B(\lambda)^{-1}b(P)$ and $v_B^L(P,\lambda)$, with $U(\lambda;P)=\max_B v_B^U(P,\lambda)$ and $L(\lambda;P)=\min_B v_B^L(P,\lambda)$. Quotient feasible bases whose value functions agree identically on each connected common-feasibility cell, order the remaining branches lexicographically, and define the maximizing branch at each $\lambda$ to be the first branch attaining the envelope. Then the first maximizing-cell threshold is the smallest positive point at which this canonical maximizing branch differs from the canonical branch active at $0^+$; it is found from the finite list of nonzero cleared-denominator branch equalities and feasibility-boundary equalities, and is $+\infty$ if that list produces no positive canonical switch. The minimizing threshold is defined analogously. Every feasible LP value is realized by a shared-$U$ completion with at most two latent atoms, obtained from the arm averages $\bar a^t=p_t^{-1}\sum_a\rho_{t,a}a$, so sharpness respects the locked support restriction $|\mathcal U|\le5$.

For $\bar\lambda=\min\{\lambda,1\}$, let
\[
  H_{\bar\lambda}
  :=\{(a,b)\in[0,1]^2: |b-a|\le \bar\lambda\}
\]
and let $V_{\bar\lambda}$ be the finite vertex set
\[
  \{(0,0),(1,1),(0,\bar\lambda),(\bar\lambda,0),(1-\bar\lambda,1),(1,1-\bar\lambda)\},
\]
with duplicate vertices removed. Let $\mathcal A_{\lambda}=V_{\bar\lambda}\times V_{\bar\lambda}$ index one
leak-feasible response type $a=((a_{0,0},a_{0,1}),(a_{1,0},a_{1,1}))$ for each mediator value. Define
\[
  \ell_a(P):=\sum_{m\in\{0,1\}}\{q_{m\mid1}a_{m,1}-q_{m\mid0}a_{m,0}\}.
\]
The endpoint pair is obtained by the finite linear programs
\begin{equation}
\begin{aligned}
  U(\lambda;P)
  &=\max_{\{\rho_{t,a}\ge0\}}\sum_{a\in\mathcal A_\lambda}
      (\rho_{0,a}+\rho_{1,a})\ell_a(P),\\
  L(\lambda;P)
  &=\min_{\{\rho_{t,a}\ge0\}}\sum_{a\in\mathcal A_\lambda}
      (\rho_{0,a}+\rho_{1,a})\ell_a(P),\\
  \text{subject to}\qquad
  &\sum_a\rho_{0,a}=p_0,\qquad
    \sum_a\rho_{1,a}=p_1,\\
  &\sum_a\rho_{0,a}a_{m,0}=p_0r_{0,m},\qquad
    \sum_a\rho_{1,a}a_{m,1}=p_1r_{1,m}\quad(m=0,1).
\end{aligned}
\tag{VLP}\label{eq:vlp}
\end{equation}
Equivalently, if $B$ ranges over the finitely many nonsingular bases of \eqref{eq:vlp}, and
\[
  v_B^U(P,\lambda)=c_B(P,\lambda)^\mathsf{T}A_B(\lambda)^{-1}b(P)
\]
when the basis is primal feasible (and is ignored otherwise), then
\[
  U(\lambda;P)=\max_{B}v_B^U(P,\lambda),\qquad
  L(\lambda;P)=\min_B v_B^L(P,\lambda),
\]
where $v_B^L$ is the analogous basis value for the minimization problem. Each retained $v_B^U$ and $v_B^L$ is
a rational function of $(p_x,q_{m\mid x},r_{x,m},\lambda)$ on each of the two regimes $0\le\lambda\le1$ and
$\lambda\ge1$. For the threshold construction, replace the basis list by the reduced branch list: two basis
records are identified when their feasibility cells have a connected overlap and their rational value functions
agree identically there after clearing denominators. Fix a deterministic lexicographic order of the reduced
branches, and let $\beta_U(\lambda;P)$ be the first feasible reduced branch attaining the upper envelope at
$\lambda$. After refining the positive line by all feasibility-boundary roots and all nonzero branch-crossing
roots, there is an $\varepsilon>0$ on which $\beta_U(\lambda;P)$ is constant; call that branch
$\beta_U(0^+;P)$. Define
\[
  \lambda_U^\star(P)
  :=\inf\{\lambda>0:\beta_U(\lambda;P)\ne\beta_U(0^+;P)\},
\]
with value $+\infty$ when the set is empty. Equivalently, $\lambda_U^\star(P)$ is the smallest positive
candidate root or feasibility-boundary point at which the canonical branch changes; identically zero equality
polynomials have already been removed by quotienting duplicate branches and hence do not create fake switches.
The minimizing threshold $\lambda_L^\star(P)$ is defined by the same construction with $v_B^L$. On the generic
regime where the active branch is unique on both sides of the first root and the crossing is transversal, the
corresponding endpoint is piecewise-rational and has the claimed active-cell kink.
\end{theorem}

\paragraph{Refutation-first attempt.}
The requested impossibility check was carried out in the smallest nontrivial latent class. Candidate A was the
degenerate one-state support. It produces $w_0=w_1$, hence a single response-type branch; the no-kink
convention returns $\lambda^\star=+\infty$, so it is not a witness against the claim. Candidate B was the
two-strata response-type search with one stratum selected only in arm $X=0$ and one stratum selected only in
arm $X=1$, and with each mediator pair placed on a box or leak face of
$H_{\bar\lambda}=\{(a,b)\in[0,1]^2:|b-a|\le\bar\lambda\}$. The Fréchet face check gives exactly the six
vertices listed in Theorem~\ref{thm:vertex}; every saturated leak face has coordinates affine in
$\bar\lambda$. Candidate C allowed an intermediate treatment propensity $e\in(0,1)$ on a two-strata support.
For a fixed structural vector $a$, its moment row splits as
\[
  (1,e,(1-e)a_{0,0},(1-e)a_{1,0},ea_{0,1},ea_{1,1},\ell_a)
  = (1-e)R_{0,a}+eR_{1,a},
\]
where $R_{0,a}$ and $R_{1,a}$ are the corresponding rows with deterministic propensities $0$ and $1$. Thus an
intermediate-propensity candidate is a convex combination of endpoint-propensity candidates and cannot create a
curved branch outside the finite basis envelope. Candidate D allowed duplicate LP bases and tied active values
over an interval. Such ties do not contradict the endpoint formula, but they make an unquotiented "first basis
switch" ambiguous. The reduced-branch and lexicographic convention in Theorem~\ref{thm:vertex} removes this
degeneracy: value-identical bases are the same branch, and a tied interval with no canonical branch change is
classified by the no-kink convention. The primitive therefore produces no counterexample to the reduced-branch
claim: the two-strata search collapses to the finite response-type LP \eqref{eq:vlp}.

\paragraph{Interpretation.}
The result replaces the informal instruction "optimize over $(w_0,w_1)$" by an evaluable Balke--Pearl-style
finite program. A response type records the four structural means
\((\varphi(0,0,u),\varphi(0,1,u),\varphi(1,0,u),\varphi(1,1,u))\). Because the outcome box and the leak budget
are polyhedral, only finitely many response types matter. The treatment propensity inside a latent type does
not add a new nonlinear cell: a type with propensity \(e\) is the convex mixture of the same response type used
only in arm \(0\) and only in arm \(1\). Consequently the shared-\(U\) endpoint is computed by a finite LP whose
bases are the active cells. The kink is not imposed by hand; after duplicate value branches are quotiented and
ties are broken deterministically, it is exactly the first parameter value at which a different feasible reduced
branch overtakes the branch active just to the right of the exclusion corner. If all apparent switches are only
duplicate-basis ties, the no-kink convention returns \(+\infty\).

\begin{proof}
The proof uses the finite latent-type enumeration technique of \citet{BalkePearl1997Bounds}, adapted from a
binary IV response-type LP to the present clean-mediator leak program. The secondary finite-constraint encoding
viewpoint is the same one used by \citet{FinkelsteinAdamsSariaShpitser2020MeasurementError} for discrete latent
and conditional-independence restrictions.

First fix \(\lambda\). Since \(Y\in[0,1]\) by Assumption~\ref{ass:bounded}, and
\(|\varphi(m,1,u)-\varphi(m,0,u)|\le\lambda\) by Assumption~\ref{ass:leak}, each mediator-specific pair
\((\varphi(m,0,u),\varphi(m,1,u))\) lies in the polygon \(H_{\bar\lambda}\), where
\(\bar\lambda=\min\{\lambda,1\}\). For \(0\le\bar\lambda\le1\), the only possible active intersections of the
box faces \(a=0,a=1,b=0,b=1\) and the leak faces \(b-a=\pm\bar\lambda\) are
\[
  (0,0),\ (1,1),\ (0,\bar\lambda),\ (\bar\lambda,0),\ (1-\bar\lambda,1),\ (1,1-\bar\lambda),
\]
with duplicates removed at \(\bar\lambda=0\) or \(\bar\lambda=1\). Therefore the product over the two mediator
values has the finite vertex set \(\mathcal A_\lambda\).

Now take any feasible completion
\((\pi,w_0,w_1,\varphi)\in\mathcal F(P,\lambda)\). Define the latent treatment propensity
\[
  e_u:=\Pr(X=1\mid U=u)=\frac{p_1w_1(u)}{\pi(u)}
\]
when \(\pi(u)>0\), with arbitrary value when \(\pi(u)=0\). Bayes consistency gives
\(\pi(u)e_u=p_1w_1(u)\) and \(\pi(u)(1-e_u)=p_0w_0(u)\). Decompose the structural vector
\[
  a_u=((\varphi(0,0,u),\varphi(0,1,u)),(\varphi(1,0,u),\varphi(1,1,u)))
\]
as a convex combination of vertices of \(\mathcal A_\lambda\), say
\(a_u=\sum_{a\in\mathcal A_\lambda}\eta_{u,a}a\). This is possible because
\(\mathcal A_\lambda\) is the vertex set of the product polytope. Set
\[
  \rho_{0,a}:=\sum_u\pi(u)(1-e_u)\eta_{u,a},\qquad
  \rho_{1,a}:=\sum_u\pi(u)e_u\eta_{u,a}.
\]
The mass constraints in \eqref{eq:vlp} follow from
\(\sum_u\pi(u)(1-e_u)=p_0\) and \(\sum_u\pi(u)e_u=p_1\). The moment constraints follow from
Assumption~\ref{ass:clean} and the compatibility equations \eqref{eq:compat}:
\[
  \sum_a\rho_{0,a}a_{m,0}
  =\sum_u p_0w_0(u)\varphi(m,0,u)=p_0r_{0,m},
  \qquad
  \sum_a\rho_{1,a}a_{m,1}
  =\sum_u p_1w_1(u)\varphi(m,1,u)=p_1r_{1,m}.
\]
Finally, using the causal functional \eqref{eq:ace} and Bayes consistency,
\[
\begin{aligned}
  \theta
  &=\sum_u\pi(u)\sum_m\{q_{m\mid1}\varphi(m,1,u)-q_{m\mid0}\varphi(m,0,u)\}\\
  =\sum_{t\in\{0,1\}}\sum_{a\in\mathcal A_\lambda}\rho_{t,a}\ell_a(P).
\end{aligned}
\]
Thus every feasible causal value is represented in the finite LP.

Conversely, let \(\rho\) satisfy the constraints of \eqref{eq:vlp}. Define the two arm-averaged structural
vectors
\[
  \bar a^0:=\frac{1}{p_0}\sum_{a\in\mathcal A_\lambda}\rho_{0,a}a,
  \qquad
  \bar a^1:=\frac{1}{p_1}\sum_{a\in\mathcal A_\lambda}\rho_{1,a}a.
\]
The divisions are valid by Assumption~\ref{ass:overlap}. Since \(\mathcal A_\lambda\) is the vertex set of the
product polytope \(H_{\bar\lambda}\times H_{\bar\lambda}\), both \(\bar a^0\) and \(\bar a^1\) lie in that
product polytope. Create two latent states \(u_0,u_1\) with marginal masses
\(\pi(u_0)=p_0\), \(\pi(u_1)=p_1\), deterministic treatment propensities
\(e_{u_0}=0\), \(e_{u_1}=1\), and hence conditional latent laws
\[
  w_0(u_0)=1,\quad w_0(u_1)=0,\qquad
  w_1(u_0)=0,\quad w_1(u_1)=1.
\]
Set \(\varphi(m,x,u_t):=\bar a^t_{m,x}\) for \(t\in\{0,1\}\). This two-atom construction satisfies
Assumption~\ref{ass:finite} because \(2\le5\), and it satisfies Assumptions~\ref{ass:bounded} and
\ref{ass:leak} because each \(\bar a^t\) lies in the product leak polytope. It satisfies the clean-mediator
restriction because \(w_x\) is a function of \(x\) only. The compatibility equations are
\[
  \sum_u p_0w_0(u)\varphi(m,0,u)
  =p_0\bar a^0_{m,0}
  =\sum_a\rho_{0,a}a_{m,0}
  =p_0r_{0,m},
\]
and similarly
\[
  \sum_u p_1w_1(u)\varphi(m,1,u)
  =p_1\bar a^1_{m,1}
  =\sum_a\rho_{1,a}a_{m,1}
  =p_1r_{1,m}.
\]
Finally, by linearity of \(\ell_a(P)\) in the structural vector,
\[
\begin{aligned}
  \theta
  &=p_0\ell_{\bar a^0}(P)+p_1\ell_{\bar a^1}(P)\\
  &=\sum_{a\in\mathcal A_\lambda}\rho_{0,a}\ell_a(P)
    +\sum_{a\in\mathcal A_\lambda}\rho_{1,a}\ell_a(P).
\end{aligned}
\]
Thus every feasible LP value is attained inside the locked shared-\(U\) support class. Hence \eqref{eq:vlp}
gives the sharp endpoint pair \(L(\lambda;P),U(\lambda;P)\).

It remains to justify the rational active-cell representation. The vector \(b(P)\) on the right side of
\eqref{eq:vlp} is
\[
  b(P)=(p_0,p_1,p_0r_{0,0},p_0r_{0,1},p_1r_{1,0},p_1r_{1,1})^\mathsf{T}.
\]
For \(0\le\lambda\le1\), every entry of the LP matrix \(A(\lambda)\) is either constant or affine in
\(\lambda\), and every entry of the objective vector \(c(P,\lambda)\) is affine in
\((q_{m\mid x},\lambda)\). For \(\lambda\ge1\), the leak constraint is inactive because both structural means
are already in \([0,1]\), so the coefficient matrix is constant after replacing \(\lambda\) by \(1\). Fix any
nonsingular basis \(B\). On the cell where \(A_B(\lambda)^{-1}b(P)\ge0\) and the usual reduced-cost
inequalities select \(B\), the basis value is
\[
  c_B(P,\lambda)^\mathsf{T}A_B(\lambda)^{-1}b(P),
\]
which is a rational function of the observable inputs and \(\lambda\). There are only finitely many bases, so
the upper endpoint is the maximum of finitely many such rational functions and the lower endpoint is the
minimum of finitely many such rational functions.

For the threshold, first remove duplicate branch records. Namely, on each connected common-feasibility cell,
declare two basis records equivalent when the cleared numerator of
\(v_B^U(P,\lambda)-v_{B'}^U(P,\lambda)\) is the zero polynomial; these records give the same endpoint value
throughout that cell and cannot be a genuine kink. The remaining reduced list is finite. Refine
\((0,\infty)\) by all real roots of denominators, all feasibility-boundary polynomials, and all nonzero cleared
equality polynomials between reduced branches. On every open interval in this finite partition, the feasibility
status and strict ordering of all nonidentical reduced branches are constant. With the fixed lexicographic
tie-break, the canonical maximizer \(\beta_U(\lambda;P)\) is therefore constant on each such interval. The first
positive boundary at which \(\beta_U\) changes is precisely
\(\lambda_U^\star(P)\); if no boundary changes the canonical maximizer, the no-kink convention gives
\(\lambda_U^\star(P)=+\infty\). The same argument with minimization branches gives
\(\lambda_L^\star(P)\). On the generic locus where the relevant branch is unique on both sides of the selected
root and the crossing is transversal, the endpoint changes rational branch there, so the claimed kink follows.
\end{proof}

\paragraph{Sanity check.}
At \(\lambda=0\), \(H_0=\{(a,a):0\le a\le1\}\), whose vertices are \((0,0)\) and \((1,1)\). Hence every
response type has \(a_{m,0}=a_{m,1}\). The LP objective becomes
\[
  \sum_{t,a}\rho_{t,a}\sum_m(q_{m\mid1}-q_{m\mid0})a_m
  =\sum_m(q_{m\mid1}-q_{m\mid0})
    \left\{\sum_a\rho_{0,a}a_m+\sum_a\rho_{1,a}a_m\right\}.
\]
The constraints give
\(\sum_a\rho_{0,a}a_m=p_0r_{0,m}\) and
\(\sum_a\rho_{1,a}a_m=p_1r_{1,m}\), so
\[
  U(0;P)=L(0;P)
  =\sum_m(q_{m\mid1}-q_{m\mid0})(p_0r_{0,m}+p_1r_{1,m})
  =\theta_{\mathrm{FD}},
\]
matching Theorem~\ref{thm:collapse}. On the one-state degenerate support, all feasible bases reduce to the
same value branch for all \(\lambda\), so the threshold rule returns \(+\infty\), exactly as required by the
no-kink convention.

\paragraph{Counterexample or minimality check.}
The finite rational conclusion is a consequence of the polyhedral restriction
\((\varphi(m,0,u),\varphi(m,1,u))\in H_{\bar\lambda}\). If the leak condition were replaced by a smooth
nonpolyhedral sensitivity set, for example
\[
  (\varphi(m,1,u)-\varphi(m,0,u))^2\le \lambda^2
\]
without the equivalent linear absolute-value faces used in Assumption~\ref{ass:leak}, the response-type set
would have a curved boundary rather than the six listed vertices. The active-cell enumeration would then no
longer reduce to finitely many LP bases, and the endpoint support function could contain square-root boundary
terms instead of rational basis values. Thus the minimality condition for this fragment is not merely finite
latent support; it is the combination of bounded outcome support and the linear absolute-value leak budget.
