% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_leaky\_frontdoor\_shared\_u, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_core.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_leaky\_frontdoor\_shared\_u} / \texttt{v1}%
  \\ \large\textit{Sharp partial identification of the average causal effect in the leaky front-door model with a clean mediator and a single bounded shared-confounder direct leak}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\theoremstyle{definition}
\newtheorem{openendedquestion}{Open-ended Question}

\paragraph{Locked parameters.}
This proposal anchors to the \emph{partial identification} cluster. The locked
tuple is $(\textsf{qid},\textsf{specialization},P,\theta,\text{restrictions},\text{bounding functional})$:
\begin{itemize}[leftmargin=1.5em,itemsep=1pt]
  \item \textbf{qid} $=$ \texttt{pid\_leaky\_frontdoor\_shared\_u}; \textbf{specialization} $=$ \texttt{v1}.
  \item \textbf{Observable distribution} $P$: the joint law of $(X,M,Y)$ with $X\in\{0,1\}$,
        $M\in\{0,1\}$, $Y\in[0,1]$, summarized by the sufficient statistics
        $p_x=\Pr(X=x)$, $q_{m\mid x}=\Pr(M=m\mid X=x)$, $r_{x,m}=\E[Y\mid X=x,M=m]$.
  \item \textbf{Parameter} $\theta=\mathrm{ACE}=\E[Y(\mathrm{do}\,X=1)]-\E[Y(\mathrm{do}\,X=0)]$
        in the graph $\mathcal G$ with edges $U\to X$, $U\to Y$, $X\to M$, $M\to Y$, $X\to Y$.
  \item \textbf{Identifying restrictions}: $U$ has finite support with
        $|\mathcal U|\le K:=|X|\,|M|+1=5$ (Carath\'eodory reduction); the mediator is
        \emph{clean}, $U\perp M\mid X$; the outcome structural mean
        $\varphi(m,x,u)=\E[Y\mid M=m,X=x,U=u]\in[0,1]$; the latent controlled direct
        effect $d(m,u)=\varphi(m,1,u)-\varphi(m,0,u)$ obeys the single scalar
        \emph{leak bound} $|d(m,u)|\le\lambda$, with $\lambda=0$ the Pearl exclusion restriction.
  \item \textbf{Bounding functional}: the sharp identified set
        $I(\lambda)=\{\,\mathrm{ACE}\;:\;\exists\,(\pi,w_0,w_1,\varphi)\text{ feasible}\,\}$
        with endpoint map $\lambda\mapsto[L(\lambda),U(\lambda)]$, where $\pi=\Pr(U=\cdot)$,
        $w_x=\Pr(U=\cdot\mid X=x)$, feasibility is the four clean-mediator compatibility
        equations $r_{x,m}=\sum_u\varphi(m,x,u)\,w_x(u)$, the Bayes consistency
        $\pi=\sum_x p_x w_x$, the box $\varphi\in[0,1]$, and $|d|\le\lambda$.
\end{itemize}

\begin{abstract}
Pearl's front-door functional point-identifies the average causal effect (ACE) of $X$ on $Y$ when
no direct $X\to Y$ path exists. We ask what set of ACE values is consistent with the data when the
mediator $M$ stays clean ($U\perp M\mid X$) but the exclusion restriction is relaxed to a single
bounded structural leak $|\varphi(m,1,u)-\varphi(m,0,u)|\le\lambda$, so that uncertainty arises
purely from a bounded confounded direct path rather than from a non-identified sensitivity
parameter. We characterize the sharp identified set $I(\lambda)$ and conjecture that it is strictly
smaller than two natural relaxations---the per-mediator controlled-direct-effect box and the generic
latent-confounding sensitivity interval---on the observable set where the front-door functional and the
unadjusted treatment contrast disagree and the treatment changes the mediator law, because the same
latent law couples all four clean-mediator compatibility equations and the effect itself. We pose, as a
construction question, a finite-vertex
characterization of the endpoints driven by a leak threshold $\lambda^\star$ at which the compatibility
constraints switch from slack to binding, together with a cross-fitted estimator with
$\sqrt n$ inference in the interior and a directional limit at the kink. Resolved, this gives applied
mediation analyses with a suspected residual direct path a sharp, leak-indexed interval that collapses
to Pearl's point estimate at $\lambda=0$.
\end{abstract}

\section{Introduction}
The front-door criterion of \citet{Pearl1995CausalDiagrams} point-identifies the average causal effect
of a treatment $X$ on an outcome $Y$ through a mediator $M$, by combining the $X\to M$ and $M\to Y$
links while ruling out any direct $X\to Y$ path. The exclusion of that direct path is the single most
demanding ingredient: in most applications a residual direct channel is plausible, and a binary
"front-door holds / fails" verdict discards the design entirely the moment exclusion is doubted. We
study the partial-identification problem that sits between these two regimes. The mediator stays clean
in the front-door sense ($U\perp M\mid X$), but the direct path is reopened by a single scalar
sensitivity radius: the latent controlled direct effect $d(m,u)=\varphi(m,1,u)-\varphi(m,0,u)$ is bounded
by $|d(m,u)|\le\lambda$, with $\lambda=0$ recovering Pearl exclusion. The question is what set of ACE
values, $I(\lambda)$, the observed law admits, and how that set behaves as $\lambda$ grows.

The closest published anchors are Pearl's front-door functional \citep[\S3.3.2, eq.~(3.42)]{Pearl1995CausalDiagrams},
which is the $\lambda=0$ corner of our set, and the generalized front-door of
\citet{FulcherShpitserMarealleTchetgen2017GeneralizedFrontDoor}, which permits a direct path but
re-targets the estimand to a population intervention indirect effect rather than delivering a sharp
total-effect interval indexed by a leak radius. The mediation sensitivity bounds of
\citet[\S2--3]{DingVanderWeele2016SharpMediationSensitivity} are a deliberate foil: they bound the
natural direct and indirect effects under unmeasured \emph{mediator--outcome} confounding, treating the
mediator as confounded with the outcome, whereas we keep the mediator clean ($U\perp M\mid X$) and bound
only the direct $X\to Y$ structural contrast. The two violations reopen different arrows, and the
resulting sets are generally incomparable. The
kernel lives in partial identification: $I(\lambda)$ is a set-valued causal estimand carved by the four
clean-mediator outcome-compatibility equations, the shared latent law, and the box-plus-leak
restrictions. The central question is whether $I(\lambda)$ decomposes into a Pearl point plus an
independent direct-effect band, or whether the shared latent law that appears in all four compatibility
equations and in the effect itself binds them together.

A concrete consumer is any front-door application where investigators currently abandon the design on
suspicion of a small direct path; the multi-mediator front-door proposal \texttt{eid\_frontdoor\_multi\_mediator}
flags the same non-rectangularity obstacle and asks for a sharp, non-decomposable set. A reader who takes
only the conclusion away stops reporting "front-door fails" and instead reports a leak-indexed interval
that contracts to Pearl's point estimate as the assumed direct path vanishes.

\paragraph{Results at a glance.}
\begin{itemize}[leftmargin=1.5em,itemsep=2pt]
  \item \textbf{Theorem 1} ($\lambda=0$ collapse): $I(0)$ is the singleton equal to Pearl's front-door
        functional $\theta_{\mathrm{FD}}=\sum_m(q_{m\mid1}-q_{m\mid0})(p_1 r_{1,m}+p_0 r_{0,m})$.
        \emph{Gap}: recovers \citet{Pearl1995CausalDiagrams} exactly at the exclusion corner, certifying
        the relaxation is a strict generalization. \emph{Consumer}: any front-door application
        (\texttt{eid\_frontdoor\_multi\_mediator}).
  \item \textbf{Theorem 2} (interval structure): for every $\lambda\ge0$, $I(\lambda)$ is compact with
        endpoints $L(\lambda)$ nonincreasing and $U(\lambda)$ nondecreasing, and the sets are nested in
        $\lambda$. \emph{Gap}: organizes the leak radius as a monotone sensitivity scale absent from
        \citet{Pearl1995CausalDiagrams}. \emph{Consumer}: sensitivity reporting in applied mediation.
  \item \textbf{Conjecture 3} (non-decomposition / strict inclusion): $[L(\lambda),U(\lambda)]$ is
        contained in the per-mediator controlled-direct-effect box $B_{\mathrm{box}}(\lambda)$ and in the
        generic latent-confounding sensitivity interval $B_{\mathrm{sens}}(\lambda)$, with the inclusion
        strict for small $\lambda>0$ on the observable set
        $\{P:\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$ where the unadjusted contrast and the
        front-door functional disagree and the mediator channel is active. \emph{Gap}: neither
        \citet{DingVanderWeele2016SharpMediationSensitivity} (mediator--outcome confounding, no
        clean-mediator equations) nor a rectangular relaxation captures the shared-latent coupling identified
        by \texttt{eid\_frontdoor\_multi\_mediator}. \emph{Consumer}: applied front-door analyses needing a
        non-conservative leak interval.
  \item \textbf{Open-ended Question 4} (finite-vertex endpoints with a kink): construct a finite family of
        explicit rational functions of $(p_x,q_{m\mid x},r_{x,m},\lambda)$ whose min and max give
        $L(\lambda),U(\lambda)$, indexed by active-set cells of a lifted polytope, with a closed-form
        threshold $\lambda^\star$ where the compatibility constraints switch from slack to binding.
        \emph{Gap}: extends the finite response-type LP geometry of \citet{BalkePearl1997Bounds} and
        \citet{FinkelsteinAdamsSariaShpitser2020MeasurementError} to a bilinear shared-$U$ program with no
        published vertex enumeration. \emph{Consumer}: software that reports front-door bounds.
  \item \textbf{Open-ended Question 5} (estimation and inference): construct a cross-fitted estimator of
        $(L(\lambda),U(\lambda))$ with $\sqrt n$ Gaussian inference in the interior of an active regime and
        a directional limit at $\lambda^\star$. \emph{Gap}: the endpoint map is nonsmooth, so neither the
        ordinary bootstrap \citep{FangSantos2019DirectionallyDifferentiable} nor pointwise plug-in suffices,
        and set-level coverage \citep{ChernozhukovHongTamer2007ParameterSets} is required. \emph{Consumer}:
        empirical mediation studies reporting confidence bands over $\lambda$.
\end{itemize}

\section{Related work}
\citet{Pearl1995CausalDiagrams} introduces the front-door criterion and its identifying functional; this
is the $\lambda=0$ face of $I(\lambda)$ and the result Theorem~1 must reproduce.
\citet{FulcherShpitserMarealleTchetgen2017GeneralizedFrontDoor} generalize front-door identification to
settings with a residual direct path, but their target is a population intervention indirect effect and
they deliver point identification of that re-defined estimand, not a sharp total-effect interval indexed
by a structural leak radius; our contribution is exactly the missing total-effect set.
\citet{DingVanderWeele2016SharpMediationSensitivity} give sharp nonparametric sensitivity bounds for the
natural direct and indirect effects under unmeasured mediator--outcome confounding; this is the closest
sensitivity-analysis foil. Their sensitivity parameter perturbs the mediator--outcome relationship (a
confounded mediator), whereas ours bounds the direct $X\to Y$ structural contrast under a clean mediator,
so the two sensitivity scales index different model classes and the resulting sets are generally
incomparable, as Conjecture~\ref{conj:nondecomp} makes precise.
\citet{BalkePearl1997Bounds} establish the finite response-type linear-programming template for sharp
discrete causal bounds, and \citet{FinkelsteinAdamsSariaShpitser2020MeasurementError} show that discrete
latent and conditional-independence assumptions can be encoded as linear constraints; both are the method
ancestors for the finite-vertex endpoint geometry of Open-ended Question~\ref{oeq:vertex}, with the caveat
that the clean-mediator compatibility equations make our program bilinear rather than linear.
\citet{GhassamiShpitserTchetgen2023ProxyPartialID} obtain partial-identification bounds from proxies
without completeness; their setting recovers or bounds \emph{hidden} confounders or mediators through
proxies, whereas we observe a clean mediator and bound only the direct structural contrast, so their
intervals are a distinct object (the comparison is a natural follow-on, recorded in \S\ref{sec:scope}).
\citet{ChernozhukovHongTamer2007ParameterSets} provide the criterion-based confidence-region framework
for set-identified parameters that Open-ended Question~5 must instantiate, and
\citet{FangSantos2019DirectionallyDifferentiable} supply the directional delta method needed at the kink
$\lambda^\star$ where the endpoint map is only directionally differentiable.
\citet{Manski1990NonparametricBounds} is the bounded-outcome partial-identification antecedent for the
$[0,1]$ box on $\varphi$.

\paragraph{In-repo prior art.} The downgraded proposal \texttt{eid\_frontdoor\_multi\_mediator} (front-door
with multiple mediators) records the same non-rectangularity obstacle---shared latent coordinates make an
outer product of marginal intervals nonsharp---and nearby records call for a rational small-instance
witness; our Conjecture~3 supplies that witness shape for the single-clean-mediator leak model. The
proximal-bridge proposals \texttt{pid\_proximal\_l2\_bridge} contribute the finite endpoint-formula and
collapse-regime concerns and the nonsmooth endpoint-inference gap that Open-ended Question~5 targets. We do
not draw kernel content from either; they are prior-art pointers.

\paragraph{Exemplars.} Writing exemplar: \citet{DingVanderWeele2016SharpMediationSensitivity} (arXiv
1601.05155) --- \S4 and \S6 mirror its arc from a familiar mediation estimand to sharp bounds under one
explicitly named violation. Method exemplars, per result: Theorem~1 and Conjecture~3 adapt
\citet{Pearl1995CausalDiagrams} (identification, DOI 10.1093/biomet/82.4.669), carrying over the front-door
functional as the $\lambda=0$ face and tracking how the latent-completion constraints perturb it;
Open-ended Question~4 adapts \citet{BalkePearl1997Bounds} (identification, DOI 10.1080/01621459.1997.10474074)
and \citet{FinkelsteinAdamsSariaShpitser2020MeasurementError} (identification, arXiv 2012.12449), carrying over
finite latent-type enumeration and the linear-constraint encoding, modified for the bilinear shared-$U$
coupling; Open-ended Question~5 adapts \citet{FangSantos2019DirectionallyDifferentiable} (estimation
/inference, arXiv 1404.3763) and \citet{ChernozhukovHongTamer2007ParameterSets} (estimation/inference, DOI
10.1111/j.1468-0262.2007.00773.x), carrying over the directional delta method and criterion-based set
coverage.

\section{Formal setup}
\label{sec:setup}
\paragraph{Variables and graph.} Let $X\in\{0,1\}$ be the treatment, $M\in\{0,1\}$ the mediator,
$Y\in[0,1]$ the bounded outcome, and $U$ a latent confounder with finite support $\mathcal U$. The causal
diagram $\mathcal G$ has edges $U\to X$, $U\to Y$, $X\to M$, $M\to Y$, and the \emph{leak} $X\to Y$. The
mediator is \emph{clean}: $U\perp M\mid X$, i.e.\ $U$ does not confound $X\to M$.

\paragraph{Structural objects.} Write the outcome structural mean
$\varphi(m,x,u)=\E[Y\mid M=m,X=x,U=u]\in[0,1]$ and the latent controlled direct effect
$d(m,u)=\varphi(m,1,u)-\varphi(m,0,u)$. Let $\pi(u)=\Pr(U=u)$ and $w_x(u)=\Pr(U=u\mid X=x)$ be the latent
marginal and treatment-arm-conditional laws, related by Bayes consistency $\pi(u)=\sum_x p_x\,w_x(u)$.

\paragraph{Observable law.} The data identify $p_x=\Pr(X=x)$, $q_{m\mid x}=\Pr(M=m\mid X=x)$, and
$r_{x,m}=\E[Y\mid X=x,M=m]$. Because $M$ is clean, $\Pr(U\mid X,M)=\Pr(U\mid X)$, which yields the four
\emph{outcome-compatibility equations}
\begin{equation}\label{eq:compat}
  r_{x,m}=\sum_{u}\varphi(m,x,u)\,w_x(u),\qquad (x,m)\in\{0,1\}^2 .
\end{equation}

\paragraph{Target and identified set.} Intervening $\mathrm{do}(X=x)$ cuts $U\to X$, so
\begin{equation}\label{eq:ace}
  \mathrm{ACE}=\sum_{m}\sum_{u}\bigl[\,q_{m\mid1}\varphi(m,1,u)-q_{m\mid0}\varphi(m,0,u)\,\bigr]\pi(u).
\end{equation}
The sharp identified set is
\begin{equation}\label{eq:idset}
  I(\lambda)=\Bigl\{\mathrm{ACE}\text{ as in \eqref{eq:ace}}\;:\;
   (\pi,w_0,w_1,\varphi)\text{ satisfy \eqref{eq:compat}, Bayes consistency, }
   \varphi\in[0,1],\ |d|\le\lambda\Bigr\},
\end{equation}
a function of $(P,\lambda)$ alone. Carath\'eodory reduction (Assumption~\ref{ass:finite}) lets every point
of $I(\lambda)$ be attained with $|\mathcal U|\le K=|X|\,|M|+1=5$. Note that \eqref{eq:compat} is
\emph{bilinear} in $(\varphi,w_x)$ and \eqref{eq:ace} bilinear in $(\varphi,\pi)$; the same $\pi$ and
$w_x$ appear in all four equations and in the target, which is the source of the non-decomposition in
Conjecture~\ref{conj:nondecomp}.

\paragraph{Observable confounding signature.} Let
\begin{equation}\label{eq:kappa}
  \kappa(P):=\Bigl(\E[Y\mid X{=}1]-\E[Y\mid X{=}0]\Bigr)-\theta_{\mathrm{FD}}(P)
  =\sum_m\bigl(q_{m\mid1}r_{1,m}-q_{m\mid0}r_{0,m}\bigr)-\sum_m\bigl(q_{m\mid1}-q_{m\mid0}\bigr)\bigl(p_1 r_{1,m}+p_0 r_{0,m}\bigr),
\end{equation}
the gap between the unadjusted treatment contrast and the front-door functional. This is a function of
observables alone. If the model were unconfounded ($U\perp X$, so $w_0=w_1$) at $\lambda=0$, then
$r_{1,m}=r_{0,m}$ for each $m$ and a direct computation gives $\kappa(P)=0$; hence $\kappa(P)\neq0$ is an
observable certificate that no unconfounded $\lambda=0$ completion explains $P$. The strict-inclusion
regime also requires an active mediator channel,
\begin{equation}\label{eq:active-mediator}
  q_{\cdot\mid1}\neq q_{\cdot\mid0},
\end{equation}
because if $q_{\cdot\mid1}=q_{\cdot\mid0}$ the mediator contributes no treatment variation to
\eqref{eq:ace} and the shared-$U$ constraints need not tighten the leak box.

\paragraph{Comparison sets.} Define two relaxations used in Conjecture~\ref{conj:nondecomp} as explicit
endpoint programs. Both are \emph{internal} comparison objects constructed here, not published estimators;
$B_{\mathrm{sens}}$ instantiates the generic latent-confounding sensitivity family of
\citet{FrauenMelnychukFeuerriegel2023SharpBounds}.

The \emph{per-mediator box} $B_{\mathrm{box}}(\lambda)$ keeps the within-mediator structure of
\eqref{eq:idset} but severs the latent law across mediators. For each $m$ introduce a separate arm-shared
pair $w_0^{(m)},w_1^{(m)}\in\Delta(\mathcal U)$ with its own Bayes-tied marginal
$\pi^{(m)}=p_1 w_1^{(m)}+p_0 w_0^{(m)}$, and set
\[
  B_{\mathrm{box}}(\lambda)=\Bigl[\min,\ \max\Bigr]\ \text{of}\
  \sum_{m}\sum_{u}\bigl[q_{m\mid1}\varphi(m,1,u)-q_{m\mid0}\varphi(m,0,u)\bigr]\pi^{(m)}(u)
\]
over $\bigl(\varphi,\{w_0^{(m)},w_1^{(m)}\}_m\bigr)$ subject to the per-mediator compatibility
$r_{x,m}=\sum_u\varphi(m,x,u)\,w_x^{(m)}(u)$, each $w_x^{(m)}\in\Delta(\mathcal U)$, $\varphi\in[0,1]$, and
$|d(m,u)|\le\lambda$. Thus the marginal that weights mediator $m$ in the effect is pinned to that mediator's
own Bayes-consistent latent law (there is no free $\pi$), and the only constraint dropped relative to
\eqref{eq:idset} is that the two mediators must share one latent law $w_x$.

The \emph{generic sensitivity interval} $B_{\mathrm{sens}}(\lambda)$ is the min/max of \eqref{eq:ace}
when the clean-mediator equations \eqref{eq:compat} are deleted entirely, retaining one shared arm-pair
$w_0,w_1$, the Bayes tie $\pi=\sum_x p_x w_x$, $\varphi\in[0,1]$, and $|d|\le\lambda$. Both programs drop
constraints present in \eqref{eq:idset}, so $I(\lambda)\subseteq B_{\mathrm{box}}(\lambda)$ and
$I(\lambda)\subseteq B_{\mathrm{sens}}(\lambda)$ by construction.

\paragraph{Lifted active-set object.} For the endpoint geometry (Open-ended
Question~\ref{oeq:vertex}), lift the bilinear monomials $g_{m,x,u}:=\varphi(m,x,u)\,w_x(u)\ge0$. Then
\eqref{eq:compat} is linear, $r_{x,m}=\sum_u g_{m,x,u}$, the box $\varphi\in[0,1]$ becomes
$0\le g_{m,x,u}\le w_x(u)$, and \eqref{eq:ace} is linear in $g$. Fix $(w_0,w_1)$ on the latent simplices
under Assumption~\ref{ass:finite}. An \emph{active-set cell} is a choice, for each $(m,x,u)$, of whether
the box bound is binding ($g_{m,x,u}\in\{0,w_x(u)\}$) or interior, together with which leak bounds
$|d(m,u)|\le\lambda$ are binding; within a cell the feasible $g$-set is a polytope and \eqref{eq:ace} is
linear, so its extremum is attained at a vertex of that polytope. The candidate endpoints $v_j(\lambda)$
are the values of these vertices optimized over $(w_0,w_1)$.

\begin{quote}\small\textbf{Locked parameters (reproduced).}
$(\textsf{qid},\textsf{specialization})=(\texttt{pid\_leaky\_frontdoor\_shared\_u},\texttt{v1})$;
$P=$ law of $(X,M,Y)$ with sufficient statistics $(p_x,q_{m\mid x},r_{x,m})$;
$\theta=\mathrm{ACE}$ in $\mathcal G=\{U\to X,U\to Y,X\to M,M\to Y,X\to Y\}$;
restrictions $=\{|\mathcal U|\le5,\ U\perp M\mid X,\ \varphi\in[0,1],\ |d(m,u)|\le\lambda\}$;
bounding functional $=I(\lambda)$ with endpoint map $\lambda\mapsto[L(\lambda),U(\lambda)]$.
\end{quote}

\section{Assumptions}
\label{sec:assumptions}
\begin{assumption}[Finite-support latent confounder]\label{ass:finite}
$U$ has finite support with $|\mathcal U|\le K=|X|\,|M|+1=5$. By a Carath\'eodory argument the bound is
without loss for the endpoints of $I(\lambda)$. \emph{Precedent:} discrete latent partial identification
\citep{FinkelsteinAdamsSariaShpitser2020MeasurementError}; response-type enumeration \citep{BalkePearl1997Bounds}.
\end{assumption}
\begin{assumption}[Clean mediator / front-door mediator exogeneity]\label{ass:clean}
$U\perp M\mid X$, so $\Pr(U\mid X,M)=\Pr(U\mid X)$ and \eqref{eq:compat} holds. \emph{Precedent:} the
mediator-isolation half of Pearl's front-door criterion \citep{Pearl1995CausalDiagrams}.
\end{assumption}
\begin{assumption}[Bounded outcome]\label{ass:bounded}
$Y\in[0,1]$, hence $\varphi(m,x,u)\in[0,1]$. \emph{Precedent:} bounded-outcome partial identification
\citep{Manski1990NonparametricBounds}.
\end{assumption}
\begin{assumption}[Bounded structural leak]\label{ass:leak}
There is a known $\lambda\ge0$ with $|d(m,u)|=|\varphi(m,1,u)-\varphi(m,0,u)|\le\lambda$ for all $(m,u)$;
$\lambda=0$ is Pearl exclusion. This is the scope/sensitivity parameter that indexes the model class.
\emph{Precedent:} a bounded direct-effect sensitivity parameter in the spirit of the bounded mediation
sensitivity radius of \citet{DingVanderWeele2016SharpMediationSensitivity}, here applied to the direct
$X\to Y$ contrast rather than to mediator--outcome confounding.
\end{assumption}
\begin{assumption}[Overlap]\label{ass:overlap}
$p_x>0$ and $q_{m\mid x}>0$ for all $(x,m)$, so all conditional means $r_{x,m}$ are well defined.
\emph{Precedent:} standard positivity for identification of $\mathrm{ACE}$.
\end{assumption}
\begin{assumption}[Active mediator channel]\label{ass:mediator-shift}
For strict-inclusion statements only, the treatment shifts the mediator law:
$q_{\cdot\mid1}\neq q_{\cdot\mid0}$, equivalently $q_{m\mid1}\neq q_{m\mid0}$ for some $m$.
\emph{Precedent:} the front-door relevance condition implicit in \citet{Pearl1995CausalDiagrams}; if the
mediator law is treatment-invariant, the $X\to M\to Y$ channel carries no treatment variation.
\end{assumption}
\begin{assumption}[Endpoint-inference regularity]\label{ass:inference-regularity}
For Open-ended Question~\ref{oeq:inference} only, $(X_i,M_i,Y_i)$ are i.i.d.; the four cell probabilities
$\rho_{xm}=\Pr(X=x,M=m)$ lie in the relative interior of the simplex; and the endpoint maps admit the
finite locally-$C^1$ active-branch representation constructed in Open-ended Question~\ref{oeq:vertex} on
the fixed $\lambda$ regime under study. \emph{Precedent:} finite-cell smoothness and active-set regularity
for set-identified endpoint inference in \citet{ChernozhukovHongTamer2007ParameterSets} and directional
differentiability in \citet{FangSantos2019DirectionallyDifferentiable}.
\end{assumption}
\section{Main results}
\label{sec:results}
Throughout, Assumptions~\ref{ass:finite}--\ref{ass:overlap} hold and $I(\lambda)$ is the set
\eqref{eq:idset}.

\begin{theorem}[Exclusion collapse]\label{thm:collapse}
At $\lambda=0$ the set $I(0)$ is the singleton
\[
  \theta_{\mathrm{FD}}=\sum_{m}\bigl(q_{m\mid1}-q_{m\mid0}\bigr)\bigl(p_1 r_{1,m}+p_0 r_{0,m}\bigr),
\]
Pearl's front-door functional.
\end{theorem}
\noindent\emph{Proof sketch.} At $\lambda=0$, Assumption~\ref{ass:leak} forces $\varphi(m,1,u)=\varphi(m,0,u)=:\varphi(m,u)$.
Then \eqref{eq:compat} gives $\sum_u\varphi(m,u)w_x(u)=r_{x,m}$, and Bayes consistency yields
$\sum_u\varphi(m,u)\pi(u)=p_1 r_{1,m}+p_0 r_{0,m}$. Substituting into \eqref{eq:ace} collapses the latent
sum, leaving $\theta_{\mathrm{FD}}$ regardless of the (still unidentified) $\varphi,\pi$. \hfill$\square$

\begin{theorem}[Interval structure and monotonicity]\label{thm:interval}
For every $\lambda\ge0$, $I(\lambda)$ is nonempty and compact; writing $L(\lambda)=\min I(\lambda)$ and
$U(\lambda)=\max I(\lambda)$, the map $\lambda\mapsto L(\lambda)$ is nonincreasing, $\lambda\mapsto U(\lambda)$
is nondecreasing, and $I(\lambda)\subseteq I(\lambda')$ whenever $\lambda\le\lambda'$ in the sense
$[L(\lambda),U(\lambda)]\subseteq[L(\lambda'),U(\lambda')]$. Moreover $L(0)=U(0)=\theta_{\mathrm{FD}}$.
\end{theorem}
\noindent\emph{Proof sketch.} The feasible $(\pi,w_0,w_1,\varphi)$ lie in a compact semialgebraic subset of a
Euclidean space (products of simplices and boxes intersected with the continuous equalities
\eqref{eq:compat}); \eqref{eq:ace} is continuous, so its image is compact and the extrema are attained
(Weierstrass). Enlarging $\lambda$ enlarges the feasible set, giving monotone endpoints; the corner value
follows from Theorem~\ref{thm:collapse}. \hfill$\square$

\begin{conjecture}[Non-decomposition / strict inclusion]\label{conj:nondecomp}
\textnormal{(NOT YET PROVED)} Let $\kappa(P)$ be the observable signature \eqref{eq:kappa}.
\begin{enumerate}[label=(\alph*),leftmargin=2em,itemsep=1pt]
  \item For all $\lambda\ge0$, $[L(\lambda),U(\lambda)]\subseteq B_{\mathrm{box}}(\lambda)\cap B_{\mathrm{sens}}(\lambda)$.
  \item Under Assumption~\ref{ass:mediator-shift}, on the relatively open observable set
        $\{P:\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$, there is $\lambda_0(P)>0$ such that
        for $0<\lambda<\lambda_0(P)$ the inclusion in (a) is \emph{strict} in both factors.
  \item At the exclusion corner the per-mediator box closes:
        $B_{\mathrm{box}}(0)=I(0)=\{\theta_{\mathrm{FD}}\}$, so the strict inclusion in (b) against
        $B_{\mathrm{box}}$ is necessarily a strictly-positive-$\lambda$ phenomenon. In mediator-stationary
        regimes $q_{\cdot\mid1}=q_{\cdot\mid0}$ the strict-inclusion assertion is not made.
\end{enumerate}
\end{conjecture}
\noindent The mechanism is that one latent law $(\pi,w_0,w_1)$ must simultaneously reconcile the four
equations \eqref{eq:compat} and weight the effect \eqref{eq:ace}; a relaxation that lets the two mediators
carry different latent laws, or that discards \eqref{eq:compat} altogether, severs that coupling and admits
ACE values no joint latent completion can realize. On
$\{\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$ the observed law has both a confounding signature
and a live mediator channel, which is when the cross-mediator coupling can tighten the natural relaxations.

\begin{openendedquestion}[Open-ended Question 4: finite-vertex endpoints with a kink]\label{oeq:vertex}
Is there a finite family of rational functions $\{v_j(\lambda)\}_{j\in J}$ of $(p_x,q_{m\mid x},r_{x,m},\lambda)$,
indexed by active-set cells of the lifted polytope of \S\ref{sec:setup}, with
\[
  L(\lambda)=\min_{j\in J}v_j(\lambda),\qquad U(\lambda)=\max_{j\in J}v_j(\lambda),
\]
and a closed-form threshold $\lambda^\star=\lambda^\star(P)>0$ at which the maximizing (resp.\ minimizing)
cell changes, so that $U(\cdot)$ (resp.\ $L(\cdot)$) is piecewise-rational with a kink at $\lambda^\star$?

\smallskip\noindent\textbf{No-kink convention.} Set
$\lambda^\star(P):=\inf\{\lambda>0:\text{the maximizing cell at }\lambda\text{ differs from the cell active at }0^+\}$,
with $\lambda^\star(P):=+\infty$ when no such switch occurs---a single cell is maximizing throughout, as on the
degenerate support $|\mathcal U|=1$ (Corollary~\ref{cor:degenerate}) or wherever one branch dominates for all
$\lambda$. The kink claim is scoped to the generic regime $\{P:0<\lambda^\star(P)<\infty\}$; on its complement
$U(\cdot)$ is a single rational branch with no interior kink and the construction returns that branch. The
symmetric convention defines the minimizing-cell threshold for $L(\cdot)$.

\smallskip\noindent\textbf{Handle:} lift the bilinear program with $g_{m,x,u}=\varphi(m,x,u)w_x(u)$ so the
compatibility equations \eqref{eq:compat} become linear; for fixed $(w_0,w_1)$ on the latent simplices,
enumerate the active-set cells of \S\ref{sec:setup} (which box bounds $g_{m,x,u}\in\{0,w_x(u)\}$ and which
leak bounds $|d(m,u)|\le\lambda$ bind), read each cell's vertex value of \eqref{eq:ace} as a rational
function $v_j$ of the data and $(w_0,w_1)$, optimize over $(w_0,w_1)$, and locate $\lambda^\star$ as the
smallest $\lambda$ solving the boundary equality $v_{j}(\lambda)=v_{j'}(\lambda)$ between the two adjacent
maximizing cells. Start from $|\mathcal U|=2$, the smallest support allowing $w_0\neq w_1$.
\textbf{Why it matters:} a closed-form vertex formula lets front-door software report the leak interval and
its kink directly from $(p_x,q_{m\mid x},r_{x,m})$ without solving a nonconvex program at every $\lambda$.
\end{openendedquestion}

\begin{openendedquestion}[Open-ended Question 5: cross-fitted endpoint inference]\label{oeq:inference}
Is there an estimator of $\bigl(L(\lambda),U(\lambda)\bigr)$ that is $\sqrt n$-consistent and asymptotically
Gaussian for fixed $\lambda$ in the interior of an active regime, and whose limit at the kink $\lambda^\star$
is the (non-Gaussian) directional law? Here $\lambda^\star=\lambda^\star(P)$ is the threshold of Open-ended
Question~\ref{oeq:vertex} under its no-kink convention; on $\{P:\lambda^\star(P)=+\infty\}$ the kink regime is
empty and only the interior Gaussian limit is in force.

\smallskip\noindent\textbf{Handle:} cross-fit the nuisances $(\hat p_x,\hat q_{m\mid x},\hat r_{x,m})$ on
held-out folds and plug them into the Open-ended Question~\ref{oeq:vertex} vertex map
$v_j(\cdot)$, then apply the directional delta method of \citet{FangSantos2019DirectionallyDifferentiable} to
the $\min/\max$ envelope; the active-set indicator at $\lambda^\star$ supplies the directional derivative
along the binding face.
\textbf{Case-split fallback:} if no single procedure is valid across regimes, deliver one per regime---(a)
interior active set: regular $\sqrt n$ Gaussian inference on the selected vertex; (b) kink
$\lambda=\lambda^\star$: a directional limit with a rescaled-bootstrap or numerical-derivative correction; (c)
collapse $\lambda=0$: the degenerate point limit at $\theta_{\mathrm{FD}}$, coordinated with set-level
coverage in the sense of \citet{ChernozhukovHongTamer2007ParameterSets}.
\textbf{Why it matters:} it turns the leak-indexed interval into a reportable confidence band over
$\lambda$ for empirical mediation studies, the inference object \citet{ChernozhukovHongTamer2007ParameterSets}
calls for in set-identified models.
\end{openendedquestion}

\section{Sanity-check corollaries}
\label{sec:sanity}
\begin{corollary}[Exclusion corner]\label{cor:corner}
Setting $\lambda=0$ in $I(\lambda)$ returns the singleton $\theta_{\mathrm{FD}}$ of
Theorem~\ref{thm:collapse}; the interval has zero width. This is the reduction the relaxation must satisfy.
\end{corollary}
\begin{corollary}[No spurious strict inclusion at the corner]\label{cor:noshift}
By Conjecture~\ref{conj:nondecomp}(c), $B_{\mathrm{box}}(0)=I(0)=\{\theta_{\mathrm{FD}}\}$, so the
strict-inclusion claim against the per-mediator box cannot fire at $\lambda=0$; it is a
strictly-positive-$\lambda$ phenomenon. This guards against reading the non-decomposition as an artifact of
the exclusion corner.
\end{corollary}
\begin{corollary}[Mediator-stationary boundary]\label{cor:stationary-mediator}
If $q_{\cdot\mid1}=q_{\cdot\mid0}$, then \eqref{eq:ace} reduces to
$\sum_{m,u}q_{m\mid1}d(m,u)\pi(u)$. The leak bound gives
$|\mathrm{ACE}|\le\lambda$ before any shared-$U$ tightening is considered. Thus
Conjecture~\ref{conj:nondecomp}(b) is scoped away from the mediator-stationary regime; the strictness
claim requires the active channel in Assumption~\ref{ass:mediator-shift}.
\end{corollary}
\begin{corollary}[Degenerate latent support]\label{cor:degenerate}
If $|\mathcal U|=1$ (no latent confounding), the compatibility equations \eqref{eq:compat} force
$\varphi(m,x)=r_{x,m}$, leaving no latent freedom. Then $I(\lambda)$ and $B_{\mathrm{box}}(\lambda)$ both
collapse to the single value $\sum_m\bigl[q_{m\mid1}r_{1,m}-q_{m\mid0}r_{0,m}\bigr]$ (the unadjusted
treatment contrast) whenever the leak bound $\max_m|r_{1,m}-r_{0,m}|\le\lambda$ holds, and are empty
otherwise. The interval has zero width: the partial-identification width of $I(\lambda)$ is a
latent-confounding phenomenon, not a product of the leak band alone. At $\lambda=0$ this forces
$r_{1,m}=r_{0,m}$ and the value equals $\theta_{\mathrm{FD}}$, consistent with Theorem~\ref{thm:collapse}.
\end{corollary}
\begin{example}[A rational witness in the strict-inclusion regime]\label{ex:kappa}
Take $p_1=p_0=\tfrac12$, $q_{1\mid1}=\tfrac23,\,q_{0\mid1}=\tfrac13$, $q_{1\mid0}=\tfrac13,\,q_{0\mid0}=\tfrac23$,
and $r_{1,1}=\tfrac34,\,r_{1,0}=\tfrac12,\,r_{0,1}=\tfrac12,\,r_{0,0}=\tfrac14$. Then
$\E[Y\mid X{=}1]-\E[Y\mid X{=}0]=\tfrac23-\tfrac13=\tfrac13$ and
$\theta_{\mathrm{FD}}=\tfrac{5}{24}-\tfrac{3}{24}=\tfrac1{12}$, so the observable signature is
$\kappa(P)=\tfrac13-\tfrac1{12}=\tfrac14\neq0$, and
$q_{\cdot\mid1}\neq q_{\cdot\mid0}$. This $P$ lies in the open regime
$\{\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$ of
Conjecture~\ref{conj:nondecomp}(b), where the conjecture predicts
$I(\lambda)\subsetneq B_{\mathrm{box}}(\lambda)$ for small $\lambda>0$. A $\lambda=0$ front-door completion
exists on $|\mathcal U|=2$ ($w_1=(1,0)$, $w_0=(0,1)$,
$\varphi(m,u_1)=r_{1,m}$, $\varphi(m,u_2)=r_{0,m}$), so $I(\lambda)$ is nonempty and nested for all
$\lambda\ge0$. We do not compute the endpoints; the witness certifies that the strict-inclusion regime is
nonempty over rational data and makes the route of \S\ref{sec:route} concrete.
\end{example}

\section{Proof-sketch route}
\label{sec:route}
Theorem~\ref{thm:collapse} is the substitution computation in its proof sketch and reduces to Pearl's
front-door derivation \citep{Pearl1995CausalDiagrams}. Theorem~\ref{thm:interval} reduces to the Weierstrass
extreme-value theorem on the compact semialgebraic feasible set together with monotonicity of the feasible
region in $\lambda$. For Conjecture~\ref{conj:nondecomp}, the inclusion (a) is definitional ($I(\lambda)$ adds
constraints to both relaxations); strictness (b) is the substance. The route is: (i) on
$\{\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$, parametrize at fixed $\lambda$ the feasible set with $|\mathcal U|=2$ (the smallest
support that admits $w_1\neq w_0$) and write the four equations \eqref{eq:compat} as a bilinear system in
$(\varphi,w_0,w_1)$; (ii) exhibit, for the rational $P$ of Example~\ref{ex:kappa} (where $\kappa(P)=\tfrac14$), a point of
$B_{\mathrm{box}}(\lambda)$ near its endpoint that requires the two mediators to carry different latent laws
$w_x^{(1)}\neq w_x^{(2)}$, violating the single shared $w_x$ of \eqref{eq:idset}, and certify it is not
attained by any feasible completion (a small finite enumeration, in the spirit of the rational $2\times2$
witness requested for \texttt{eid\_frontdoor\_multi\_mediator}); (iii) propagate the gap to the relatively
open set $\{\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$ by continuity. Part (c) is the corner computation: at $\lambda=0$ the leak
bound forces $\varphi(m,1,u)=\varphi(m,0,u)$, so the per-mediator box objective collapses to
$\theta_{\mathrm{FD}}$ exactly as in Theorem~\ref{thm:collapse}, giving $B_{\mathrm{box}}(0)=I(0)$. For
Open-ended Question~\ref{oeq:vertex}, the route adapts the finite response-type enumeration
of \citet{BalkePearl1997Bounds} and the linear-constraint encoding of
\citet{FinkelsteinAdamsSariaShpitser2020MeasurementError}: after the lift $g_{m,x,u}=\varphi(m,x,u)w_x(u)$
the compatibility equations become linear, and for fixed $(w_0,w_1)$ the extrema lie at vertices of the
active-set cells of \S\ref{sec:setup}; enumerating cells gives the finite family $\{v_j\}$, and the
threshold $\lambda^\star$ is the smallest $\lambda$ at which the maximizing cell changes, found by solving
the boundary equality of two adjacent branch formulas. The boundary algebra to check explicitly is the
two-point-support case (closed-form $v_j$ and $\lambda^\star$) and the switch between the leak-band-binding
and compatibility-binding branches. Open-ended Question~5 reduces the inference problem to the directional
delta method for $\min/\max$ of smooth plug-in functionals \citep{FangSantos2019DirectionallyDifferentiable}
over cross-fitted nuisances, with set-level coverage as in \citet{ChernozhukovHongTamer2007ParameterSets}.

\section{Honest scope flags}
\label{sec:scope}
\textbf{Proved vs.\ open.} Theorems~\ref{thm:collapse}--\ref{thm:interval} are routine
(substitution; Weierstrass plus monotonicity) and we treat them as established. Conjecture~\ref{conj:nondecomp}
and Open-ended Questions~\ref{oeq:vertex} and \ref{oeq:inference} are open.

\textbf{Known soft spots.} (i) The compatibility equations \eqref{eq:compat} are \emph{bilinear} in
$(\varphi,w_x)$, so the program is not a linear program and standard LP-duality sharpness arguments do not
apply directly; the finite-vertex characterization sought in Open-ended Question~\ref{oeq:vertex} rests on
the active-set/vertex structure of the lifted feasible set after Carath\'eodory reduction, which is left
open as a construction.
(ii) Theorem~\ref{thm:interval} asserts compactness and monotone endpoints but not that $I(\lambda)$ is the
\emph{full} interval $[L(\lambda),U(\lambda)]$; connectedness of $I(\lambda)$ is left open (plausible by a
convex-combination homotopy of feasible completions) and folded into Open-ended Question~\ref{oeq:vertex}.
(iii) The closed form for $\lambda^\star$ is sought only for $K\le5$; larger latent supports are reduced
to this by Carath\'eodory but the reduction is left to be checked at the boundary.
(iv) Strict non-decomposition is left open only on the active-mediator regime
$\{\kappa(P)\neq0,\ q_{\cdot\mid1}\neq q_{\cdot\mid0}\}$; mediator-stationary laws are outside that claim.

\textbf{Supplementary direction (not a numbered result).} The comparison with proxy/proximal partial-ID
intervals \citep{GhassamiShpitserTchetgen2023ProxyPartialID,GhassamiYangShpitserTchetgen2021HiddenMediators}---
necessary and sufficient conditions for equality, strict containment, or incomparability between those
intervals and $I(\lambda)$---is orthogonal to the headline and left as future work; the obstacle is that
their latent-information structure (hidden mediator measured by proxies) differs from our observed clean
mediator, so the two sets need not be nested.

\section{Iteration trail}
\label{sec:trail}
\begin{itemize}[leftmargin=1.5em,itemsep=1pt]
  \item \textbf{v1} (cold-start) --- initial draft; prior verdict: none.
  \item \textbf{v2} (revise) --- recast the non-decomposition regime on the observable signature
        $\kappa(P)$ with an explicit unconfounded submodel; defined $B_{\mathrm{box}},B_{\mathrm{sens}}$ as
        endpoint programs and a lifted active-set object; relabeled the finite-vertex endpoint claim as an
        Open-ended Question with the enumeration as its Handle; corrected the Ding--VanderWeele
        characterization; prior verdict: REVISE.
  \item \textbf{v3} (revise) --- fully specified $B_{\mathrm{box}}$ as a per-mediator Bayes-tied endpoint
        program (no free $\pi$) and labeled $B_{\mathrm{box}},B_{\mathrm{sens}}$ as internal relaxations with
        $B_{\mathrm{sens}}$ anchored to \citet{FrauenMelnychukFeuerriegel2023SharpBounds}; added a no-kink
        convention for $\lambda^\star$ (with $\lambda^\star=+\infty$ off the generic regime) and propagated it
        to Open-ended Question~\ref{oeq:inference}; recast Conjecture~\ref{conj:nondecomp}(c) as the
        provable corner collapse $B_{\mathrm{box}}(0)=I(0)$ and retired the unconfounded-submodel assumption;
        fixed the degenerate-support corollary to a singleton; added the rational witness
        Example~\ref{ex:kappa} with $\kappa(P)=\tfrac14$; corrected two Open-ended Question~4 mislabels;
        prior verdict: REVISE.
  \item \textbf{v4} (revise) --- split the strict non-decomposition regime by adding the active-mediator
        condition $q_{\cdot\mid1}\neq q_{\cdot\mid0}$, added the mediator-stationary sanity check, and
        propagated the regime through the abstract, P4, Conjecture~\ref{conj:nondecomp}, the witness, and
        the proof route; prior verdict: REJECT.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem{Pearl1995CausalDiagrams} Pearl, J. (1995). Causal diagrams for empirical research.
  \textit{Biometrika} 82(4), 669--688. DOI 10.1093/biomet/82.4.669.
\bibitem{FulcherShpitserMarealleTchetgen2017GeneralizedFrontDoor} Fulcher, I., Shpitser, I., Marealle, S.,
  and Tchetgen Tchetgen, E. (2017). Robust inference on indirect causal effects: a generalized front-door
  criterion. arXiv:1711.03611.
\bibitem{DingVanderWeele2016SharpMediationSensitivity} Ding, P., and VanderWeele, T.~J. (2016). Sharp
  sensitivity bounds for mediation under unmeasured mediator--outcome confounding. \textit{Biometrika}
  103(2), 483--490. arXiv:1601.05155.
\bibitem{BalkePearl1997Bounds} Balke, A., and Pearl, J. (1997). Bounds on treatment effects from studies
  with imperfect compliance. \textit{Journal of the American Statistical Association} 92(439), 1171--1176.
  DOI 10.1080/01621459.1997.10474074.
\bibitem{FinkelsteinAdamsSariaShpitser2020MeasurementError} Finkelstein, N., Adams, R., Saria, S., and
  Shpitser, I. (2020). Partial identifiability in discrete data with measurement error. arXiv:2012.12449.
\bibitem{GhassamiYangShpitserTchetgen2021HiddenMediators} Ghassami, A., Yang, A., Shpitser, I., and
  Tchetgen Tchetgen, E. (2021). Causal inference with hidden mediators. arXiv:2111.02927.
\bibitem{GhassamiShpitserTchetgen2023ProxyPartialID} Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E.
  (2023). Partial identification of causal effects using proximal causal inference. arXiv:2304.04374.
\bibitem{ChernozhukovHongTamer2007ParameterSets} Chernozhukov, V., Hong, H., and Tamer, E. (2007).
  Estimation and confidence regions for parameter sets in econometric models. \textit{Econometrica} 75(5),
  1243--1284. DOI 10.1111/j.1468-0262.2007.00773.x.
\bibitem{FangSantos2019DirectionallyDifferentiable} Fang, Z., and Santos, A. (2019). Inference on
  directionally differentiable functions. \textit{Review of Economic Studies} 86(1), 377--412.
  arXiv:1404.3763.
\bibitem{Manski1990NonparametricBounds} Manski, C.~F. (1990). Nonparametric bounds on treatment effects.
  \textit{American Economic Review} 80(2), 319--323.
\bibitem{FrauenMelnychukFeuerriegel2023SharpBounds} Frauen, D., Melnychuk, V., and Feuerriegel, S. (2023).
  Sharp bounds for generalized causal sensitivity analysis. \textit{Advances in Neural Information
  Processing Systems} 36, 19036--19071. arXiv:2305.16988.
\end{thebibliography}

\end{document}
