% file-plan: bypass-justified: the substrate survey found reusable finite-support partial-ID and potential-outcome endpoint patterns, but this fragment is an estimator-level result for the new leaky front-door active-branch endpoint map; reuse is analogy-level only.

\paragraph{\S9-fragment-statement.}
\paragraph{Motivating open-ended question (verbatim).}
Is there an estimator of $\bigl(L(\lambda),U(\lambda)\bigr)$ that is $\sqrt n$-consistent and asymptotically
Gaussian for fixed $\lambda$ in the interior of an active regime, and whose limit at the kink $\lambda^\star$
is the (non-Gaussian) directional law? Here $\lambda^\star=\lambda^\star(P)$ is the threshold of Open-ended
Question~\ref{oeq:vertex} under its no-kink convention; on $\{P:\lambda^\star(P)=+\infty\}$ the kink regime is
empty and only the interior Gaussian limit is in force.

\smallskip\noindent\textbf{Handle:} cross-fit the nuisances $(\hat p_x,\hat q_{m\mid x},\hat r_{x,m})$ on
held-out folds and plug them into the Open-ended Question~\ref{oeq:vertex} vertex map
$v_j(\cdot)$, then apply the directional delta method of \citet{FangSantos2019DirectionallyDifferentiable} to
the $\min/\max$ envelope; the active-set indicator at $\lambda^\star$ supplies the directional derivative
along the binding face.
\textbf{Case-split fallback:} if no single procedure is valid across regimes, deliver one per regime---(a)
interior active set: regular $\sqrt n$ Gaussian inference on the selected vertex; (b) kink
$\lambda=\lambda^\star$: a directional limit with a rescaled-bootstrap or numerical-derivative correction; (c)
collapse $\lambda=0$: the degenerate point limit at $\theta_{\mathrm{FD}}$, coordinated with set-level
coverage in the sense of \citet{ChernozhukovHongTamer2007ParameterSets}.
\textbf{Why it matters:} it turns the leak-indexed interval into a reportable confidence band over
$\lambda$ for empirical mediation studies, the inference object \citet{ChernozhukovHongTamer2007ParameterSets}
calls for in set-identified models.

\begin{proposition}[Active-branch endpoint inference]\label{prop:inference-active-branch}
\emph{Headline statement.} Inference construction under Assumption~\ref{ass:inference-regularity}. Let \(O_i=(X_i,M_i,Y_i)\) be i.i.d., define \(\widehat\rho_{xm}=n^{-1}\sum_i\one\{X_i=x,M_i=m\}\), \(\widehat\mu_{xm}=n^{-1}\sum_iY_i\one\{X_i=x,M_i=m\}\), \(\widehat p_x=\sum_m\widehat\rho_{xm}\), \(\widehat q_{m\mid x}=\widehat\rho_{xm}/\widehat p_x\), \(\widehat r_{x,m}=\widehat\mu_{xm}/\widehat\rho_{xm}\), and \(\widehat\eta_n=(\widehat\rho,\widehat\mu)\). For any fixed \(\lambda\), set \(\widehat L_n(\lambda)=\min_{j\in J_L}v^L_j(\widehat\eta_n,\lambda)\) and \(\widehat U_n(\lambda)=\max_{j\in J_U}v^U_j(\widehat\eta_n,\lambda)\), where the finite \(C^1\) branch maps \(v^L_j,v^U_j\) are the active-branch representation of \(L,U\). If \(\lambda\) is in an interior active regime with unique active indices \(j_L,j_U\), then \(\sqrt n((\widehat L_n,\widehat U_n)-(L,U))\Rightarrow \mathcal N(0,D_\lambda\Sigma_\eta D_\lambda^\transpose)\), where \(D_\lambda\) has rows \(\nabla_\eta v^L_{j_L}(\eta,\lambda)^\transpose\) and \(\nabla_\eta v^U_{j_U}(\eta,\lambda)^\transpose\). If \(\lambda=\lambda^\star(P)\) is a finite kink selected by the no-kink/tie convention, then \(\sqrt n((\widehat L_n,\widehat U_n)-(L,U))\Rightarrow(\min_{j\in A_L^\star}\nabla_\eta v^L_j(\eta,\lambda^\star)^\transpose Z_\eta,\max_{j\in A_U^\star}\nabla_\eta v^U_j(\eta,\lambda^\star)^\transpose Z_\eta)\), with \(Z_\eta\sim\mathcal N(0,\Sigma_\eta)\); the displayed directional law is genuinely non-Gaussian only when the relevant finite min/max envelope is not almost surely equal to a single linear form of \(Z_\eta\), and in a two-branch binding face it is non-Gaussian when the active gradients \(a,b\) for the same endpoint satisfy \((a-b)^\transpose\Sigma_\eta(a-b)>0\). For multiplier draws \(\xi_i\) that are i.i.d., independent of the sample, satisfy \(E[\xi_i]=0\), \(E[\xi_i^2]=1\), and \(E|\xi_i|^{2+\delta}<\infty\) for some \(\delta>0\), define \(\widehat Z_{\eta,n}^b=n^{-1/2}\sum_i\xi_i(\widehat\psi_{\eta,i}-\overline{\widehat\psi}_\eta)\). If \(t_n\downarrow0\) and \(\sqrt n\,t_n\to\infty\), the numerical-derivative bootstrap \(\widehat\Phi'_{\lambda,n}(h)=t_n^{-1}\{\Phi_\lambda(\widehat\eta_n+t_nh)-\Phi_\lambda(\widehat\eta_n)\}\), \(\widehat Z_n^b=\widehat\Phi'_{\lambda,n}(\widehat Z_{\eta,n}^b)\), consistently estimates the interior Gaussian law and the kink directional law. Thus \(C_{n,\alpha}(\lambda)=[\widehat L_n(\lambda)-\widehat c_{1-\alpha}/\sqrt n,\widehat U_n(\lambda)+\widehat c_{1-\alpha}/\sqrt n]\), with \(\widehat c_{1-\alpha}\) the conditional \((1-\alpha)\)-quantile of \(\max\{\widehat Z_{n,L}^b,-\widehat Z_{n,U}^b\}\), has asymptotic set coverage for \([L(\lambda),U(\lambda)]\) at continuity points of the limiting quantile. At \(\lambda=0\), use \(\widehat L_n(0)=\widehat U_n(0)=\widehat\theta_{\mathrm{FD}}\), where \(\widehat\theta_{\mathrm{FD}}=\sum_m(\widehat q_{m\mid1}-\widehat q_{m\mid0})(\widehat p_1\widehat r_{1,m}+\widehat p_0\widehat r_{0,m})\); the endpoint pair has the diagonal Gaussian limit for \(\theta_{\mathrm{FD}}\) and the estimated width is identically zero.
\end{proposition}

\paragraph{\S13-refutation-attempt.}
The refutation-first check used the partial-identification finite vertex primitive on
the smallest support capable of exposing the proposed obstruction: binary \(Y\),
binary \(X\), binary \(M\), and a two-point latent support
\(\mathcal U=\{u_0,u_1\}\).  On this support the sample-relevant observable vector is
\[
  \eta(P)=\bigl(\rho_{xm},\mu_{xm}\bigr)_{x,m\in\{0,1\}},
  \qquad
  \rho_{xm}=P(X=x,M=m),\quad
  \mu_{xm}=E[Y\one\{X=x,M=m\}],
\]
and Assumption~\ref{ass:overlap} places \(\eta(P)\) in the relative interior of the
four-cell probability simplex with well-defined cell means
\(r_{x,m}=\mu_{xm}/\rho_{xm}\).

The searched witnesses fall into four cases.  First, when a single branch of the
candidate endpoint map is active, every response-type vertex gives a smooth map of
\(\eta\).  The finite-dimensional central limit theorem and the ordinary delta method
therefore produce the stated Gaussian law, so no impossibility witness appears.
Second, when two response-type vertices tie at the convention-selected threshold
\(\lambda^\star\), the local model may reduce to
\(U(\eta)=\max\{a^\transpose\eta,b^\transpose\eta\}\).  If
\((a-b)^\transpose\Sigma_\eta(a-b)>0\), the ordinary linear Gaussian delta method
fails and the requested kink behavior is exactly the directional law
\(\max\{a^\transpose Z_\eta,b^\transpose Z_\eta\}\).  If the two induced linear
forms differ only in a \(\Sigma_\eta\)-null direction, or if two basis value
functions are identical after the no-kink/tie convention quotients them, the same
directional formula collapses to the common Gaussian linear form.  Neither case is a
counterexample to the open-ended question.  Third, at \(\lambda=0\), Theorem~\ref{thm:collapse}
collapses the identified set to the front-door point, so the endpoint-width process is
degenerate rather than impossible.  Fourth, witnesses with \(\rho_{xm}=0\) make
\(\widehat r_{x,m}\) undefined and can destroy root-\(n\) estimation, but those
witnesses violate Assumption~\ref{ass:overlap}.

The search therefore does not refute the existence of the requested estimator once the
finite active-branch representation and primitive sampling conditions in
Assumption~\ref{ass:inference-regularity} are supplied.  It also isolates the role of
the no-kink/tie convention from Open-ended Question~\ref{oeq:vertex}: the inference
argument takes \(\lambda^\star\) and the binding active face as convention-defined
inputs and does not require an unquotiented ``first positive root'' rule.

\paragraph{\S10 Interpretation.}
The construction is an inference layer on top of the leak-indexed partial-ID endpoint
map.  The causal object remains the identified interval
\([L(\lambda),U(\lambda)]\) for the total effect in \eqref{eq:ace}; the estimator first
estimates only the observable cell vector \(\eta(P)\), then evaluates the branch
envelope supplied by the finite-vertex representation.  Cross-fitting is
harmless in this finite-cell problem: replacing \(\widehat\eta_n\) by the fixed-fold
average of held-out-fold estimators has the same influence function, because each
fold estimator is a smooth cell-frequency and cell-mean functional under overlap.

The interior active-regime case is regular.  Once the same branch remains active in a
neighborhood of \(P\), an endpoint is a differentiable scalar function of the eight
observable moments \((\rho,\mu)\).  At a kink, the active set does not select a single
gradient; the endpoint is a min or max over several branchwise linearizations.  That is
the precise setting of the directional delta method of
\citet{FangSantos2019DirectionallyDifferentiable}.  The confidence interval
\(C_{n,\alpha}(\lambda)\) is a set-level interval in the sense of
\citet{ChernozhukovHongTamer2007ParameterSets}: it covers the whole population
identified interval, not merely one selected endpoint.

\paragraph{\S11 Proof.}
Work under Assumptions~\ref{ass:finite}--\ref{ass:overlap} and
Assumption~\ref{ass:inference-regularity}.  Let
\[
  \eta=\eta(P)=\bigl(\rho_{00},\rho_{01},\rho_{10},\rho_{11},
                    \mu_{00},\mu_{01},\mu_{10},\mu_{11}\bigr)^\transpose .
\]
The estimator in Proposition~\ref{prop:inference-active-branch} is the sample mean
of the bounded vector
\[
  S(O)=\bigl(\one\{X=0,M=0\},\ldots,\one\{X=1,M=1\},
             Y\one\{X=0,M=0\},\ldots,Y\one\{X=1,M=1\}\bigr)^\transpose .
\]
Thus
\[
  \widehat\eta_n-\eta=n^{-1}\sum_{i=1}^n\psi_\eta(O_i),
  \qquad
  \psi_\eta(O)=S(O)-\eta .
\]
Because \(Y\in[0,1]\) by Assumption~\ref{ass:bounded}, all coordinates of
\(\psi_\eta\) are bounded.  The finite-dimensional central limit theorem gives
\[
  \sqrt n(\widehat\eta_n-\eta)\Rightarrow Z_\eta,
  \qquad
  Z_\eta\sim\mathcal N(0,\Sigma_\eta),
  \qquad
  \Sigma_\eta=E[\psi_\eta(O)\psi_\eta(O)^\transpose].
\]
Assumption~\ref{ass:overlap} gives \(\rho_{xm}>0\), so the maps
\[
  p_x=\sum_m\rho_{xm},\qquad
  q_{m\mid x}={\rho_{xm}\over\sum_{m'}\rho_{xm'}},\qquad
  r_{x,m}={\mu_{xm}\over\rho_{xm}}
\]
are continuously differentiable in a neighborhood of \(\eta(P)\).  Every division in
the estimator is therefore justified on an event whose probability tends to one.

For a fixed \(\lambda\), Assumption~\ref{ass:inference-regularity} supplies finite
branch families
\[
  L(\lambda;\eta)=\min_{j\in J_L}v^L_j(\eta,\lambda),
  \qquad
  U(\lambda;\eta)=\max_{j\in J_U}v^U_j(\eta,\lambda),
\]
where each branch is \(C^1\) on a neighborhood of \(\eta(P)\).  Define
\[
  \Phi_\lambda(\eta)
  =
  \bigl(\min_{j\in J_L}v^L_j(\eta,\lambda),
        \max_{j\in J_U}v^U_j(\eta,\lambda)\bigr).
\]
The endpoint estimator is exactly
\[
  (\widehat L_n(\lambda),\widehat U_n(\lambda))
  =\Phi_\lambda(\widehat\eta_n).
\]

The map \(\Phi_\lambda\) is Hadamard directionally differentiable because it is a
finite minimum and maximum of continuously differentiable real maps.  Its directional
derivative at \(\eta\) in direction \(h\) is
\[
  \Phi'_{\lambda,\eta}(h)
  =
  \left(
    \min_{j\in A_L(\eta,\lambda)}
      \nabla_\eta v^L_j(\eta,\lambda)^\transpose h,\quad
    \max_{j\in A_U(\eta,\lambda)}
      \nabla_\eta v^U_j(\eta,\lambda)^\transpose h
  \right),
\]
where
\[
  A_L(\eta,\lambda)=\arg\min_{j\in J_L}v^L_j(\eta,\lambda),
  \qquad
  A_U(\eta,\lambda)=\arg\max_{j\in J_U}v^U_j(\eta,\lambda).
\]
This derivative formula is just the elementary first-order expansion of each active
branch plus the algebraic identities for finite min and max envelopes.

If \(\lambda\) lies in an interior active regime, the active sets are singletons
\(A_L=\{j_L\}\) and \(A_U=\{j_U\}\).  The displayed derivative is then linear:
\[
  \Phi'_{\lambda,\eta}(h)
  =
  D_\lambda h,\qquad
  D_\lambda=
  \begin{pmatrix}
    \nabla_\eta v^L_{j_L}(\eta,\lambda)^\transpose\\
    \nabla_\eta v^U_{j_U}(\eta,\lambda)^\transpose
  \end{pmatrix}.
\]
Combining the central limit theorem for \(\widehat\eta_n\) with the ordinary delta
method yields
\[
  \sqrt n\{(\widehat L_n,\widehat U_n)-(L,U)\}
  \Rightarrow
  D_\lambda Z_\eta
  \sim
  \mathcal N(0,D_\lambda\Sigma_\eta D_\lambda^\transpose).
\]
This proves the claimed regular Gaussian limit.

If \(\lambda=\lambda^\star(P)\) is finite and the no-kink/tie convention selects a
binding face, Assumption~\ref{ass:inference-regularity} states that the corresponding active
sets \(A_L^\star\) and \(A_U^\star\) are finite and locally exhaustive.  Applying the
directional delta method of \citet{FangSantos2019DirectionallyDifferentiable} to the
same endpoint map gives
\[
  \sqrt n\{(\widehat L_n(\lambda^\star),\widehat U_n(\lambda^\star))
          -(L(\lambda^\star),U(\lambda^\star))\}
  \Rightarrow
  \Phi'_{\lambda^\star,\eta}(Z_\eta),
\]
namely
\[
  \left(
    \min_{j\in A_L^\star}
      \nabla_\eta v^L_j(\eta,\lambda^\star)^\transpose Z_\eta,\quad
    \max_{j\in A_U^\star}
      \nabla_\eta v^U_j(\eta,\lambda^\star)^\transpose Z_\eta
  \right).
\]
This formula is the kink directional law.  It is genuinely non-Gaussian only when the
finite envelope is not almost surely equal to one linear form of \(Z_\eta\).  In
particular, for a two-branch upper-face tie with gradients \(a\) and \(b\),
\[
  \max\{a^\transpose Z_\eta,b^\transpose Z_\eta\}
  =
  { (a+b)^\transpose Z_\eta \over 2}
  +
  { |(a-b)^\transpose Z_\eta| \over 2},
\]
so the folded-normal term is nondegenerate, and the limit is not Gaussian, whenever
\((a-b)^\transpose\Sigma_\eta(a-b)>0\).  The same argument applies to a two-branch
lower-face tie with \(\min\) in place of \(\max\).  If distinct ambient gradients
differ only in a \(\Sigma_\eta\)-null direction, then their induced linear forms are
equal almost surely and the displayed directional law reduces to the corresponding
Gaussian linear form.  On the event
\(\lambda^\star(P)=+\infty\), the kink clause is empty by the no-kink convention, so
only the preceding interior branch law is asserted.

It remains to justify the bootstrap and the set-level interval.  Let
\(\xi_1,\ldots,\xi_n\) be independent multiplier draws with mean zero, variance one,
and finite \(2+\delta\) moment, independent of the sample.  Let
\[
  \widehat\psi_{\eta,i}=S(O_i)-\widehat\eta_n,\qquad
  \widehat Z_{\eta,n}^b
  =
  n^{-1/2}\sum_{i=1}^n\xi_i
  \bigl(\widehat\psi_{\eta,i}-n^{-1}\sum_{\ell=1}^n\widehat\psi_{\eta,\ell}\bigr).
\]
Since \(S(O)\) is bounded and finite-dimensional, the multiplier central limit theorem
gives conditional convergence of \(\widehat Z_{\eta,n}^b\) to \(Z_\eta\).  For any
sequence \(t_n\downarrow0\) with \(\sqrt n\,t_n\to\infty\), define
\[
  \widehat\Phi'_{\lambda,n}(h)
  =
  { \Phi_\lambda(\widehat\eta_n+t_nh)-\Phi_\lambda(\widehat\eta_n)\over t_n}.
\]
The branch maps are \(C^1\) and the envelope is a finite min/max, so
\(\widehat\Phi'_{\lambda,n}(h)\) converges to
\(\Phi'_{\lambda,\eta}(h)\) uniformly over compact subsets of the tangent space.  The
condition \(\sqrt n\,t_n\to\infty\) makes the centering error
\(\widehat\eta_n-\eta\) negligible relative to the numerical derivative step.  The
Fang--Santos numerical-derivative bootstrap therefore yields
\[
  \widehat Z_n^b
  =
  \widehat\Phi'_{\lambda,n}(\widehat Z_{\eta,n}^b)
  \rightsquigarrow_{\Pr}
  \Phi'_{\lambda,\eta}(Z_\eta)
\]
conditionally on the sample, both at interior points and at kink points.

Let
\[
  T_\lambda
  =
  \max\{Z_L,-Z_U\},
  \qquad
  \widehat T_\lambda^b
  =
  \max\{\widehat Z_{n,L}^b,-\widehat Z_{n,U}^b\}.
\]
At continuity points of the distribution of \(T_\lambda\), the conditional
\((1-\alpha)\)-quantile \(\widehat c_{1-\alpha}\) of
\(\widehat T_\lambda^b\) consistently estimates the corresponding population
quantile.  The event
\[
  [L(\lambda),U(\lambda)]
  \subseteq
  [\widehat L_n(\lambda)-\widehat c_{1-\alpha}/\sqrt n,
   \widehat U_n(\lambda)+\widehat c_{1-\alpha}/\sqrt n]
\]
is equivalent to
\[
  \max\{\sqrt n(\widehat L_n-L),\sqrt n(U-\widehat U_n)\}
  \le \widehat c_{1-\alpha}.
\]
The previous bootstrap convergence and quantile continuity therefore give asymptotic
coverage \(1-\alpha\) for the identified interval.  This is the endpoint version of
the set-coverage inversion principle in
\citet{ChernozhukovHongTamer2007ParameterSets}.

Finally take \(\lambda=0\).  Theorem~\ref{thm:collapse} gives
\[
  L(0)=U(0)=\theta_{\mathrm{FD}}
  =
  \sum_m(q_{m\mid1}-q_{m\mid0})(p_1r_{1,m}+p_0r_{0,m}).
\]
The plug-in estimator
\[
  \widehat\theta_{\mathrm{FD}}
  =
  \sum_m(\widehat q_{m\mid1}-\widehat q_{m\mid0})
        (\widehat p_1\widehat r_{1,m}+\widehat p_0\widehat r_{0,m})
\]
is a continuously differentiable function of \(\widehat\eta_n\) under overlap, so the
ordinary delta method gives a one-dimensional Gaussian limit for
\(\sqrt n(\widehat\theta_{\mathrm{FD}}-\theta_{\mathrm{FD}})\).  Setting
\(\widehat L_n(0)=\widehat U_n(0)=\widehat\theta_{\mathrm{FD}}\) places the endpoint
pair on the diagonal and makes the estimated width exactly zero, matching the collapse
of the identified set.

\paragraph{\S12 Sanity check.}
At the no-leak corner, the result reduces to the classical front-door plug-in
estimator.  Theorem~\ref{thm:collapse} states that
\([L(0),U(0)]=\{\theta_{\mathrm{FD}}\}\).  The estimator in the proposition gives
\[
  [\widehat L_n(0),\widehat U_n(0)]
  =
  \left[
    \sum_m(\widehat q_{m\mid1}-\widehat q_{m\mid0})
          (\widehat p_1\widehat r_{1,m}+\widehat p_0\widehat r_{0,m}),
    \sum_m(\widehat q_{m\mid1}-\widehat q_{m\mid0})
          (\widehat p_1\widehat r_{1,m}+\widehat p_0\widehat r_{0,m})
  \right],
\]
so the estimated interval is a singleton.  Its first-order law is the ordinary
finite-cell delta-method law for Pearl's front-door functional, while the width process
\(\sqrt n\{(\widehat U_n(0)-\widehat L_n(0))-(U(0)-L(0))\}\) is identically zero.

If the vertex threshold obeys \(\lambda^\star(P)=+\infty\), then by the no-kink/tie
convention there is no finite isolated switching threshold under consideration after
identical branches and persistent tie intervals have been quotiented.  On interior
regimes the active sets are singletons, and the formula in
Proposition~\ref{prop:inference-active-branch} reduces to the regular Gaussian branch
law.  If a non-quotiented tie remains at a fixed \(\lambda\), it is handled by the
directional formula rather than by the interior line.  Thus the finite-kink clause is
empty exactly in the convention-defined no-kink regime, as required by the motivating
question.

\paragraph{\S13 Counterexample or minimality check.}
The active-branch and directional-bootstrap conditions are minimal for the proof above.
Drop the kink treatment and consider the local two-branch endpoint
\[
  U(\eta)=\max\{\eta_1,\eta_2\},\qquad \eta(P)=(0,0),
\]
with \(\sqrt n\,\widehat\eta_n\Rightarrow (Z_1,Z_2)\), where
\((Z_1,Z_2)\) is a centered Gaussian vector satisfying
\(\Var(Z_1-Z_2)>0\).  Then
\[
  \sqrt n\{U(\widehat\eta_n)-U(\eta)\}
  \Rightarrow
  \max\{Z_1,Z_2\},
\]
which is not Gaussian because it contains the nondegenerate folded-normal term
\(|Z_1-Z_2|/2\).  A
procedure that reports the interior Gaussian law at this tie has the wrong limiting
distribution.  This is the finite-vertex witness that forces the
Fang--Santos directional derivative or numerical-derivative bootstrap at
\(\lambda^\star\).

The tie convention in Open-ended Question~\ref{oeq:vertex} is also load-bearing.  If
two basis value functions are identical over a positive \(\lambda\)-interval, the
unquotiented equation \(v_B^U(P,\lambda)=v_{B'}^U(P,\lambda)\) is identically zero and
has no smallest positive root.  The inference theorem therefore treats
\(\lambda^\star\) as the threshold supplied by the no-kink/tie convention, with
identical branches quotiented and persistent ties classified before the limit law is
applied.

Overlap is also not cosmetic.  If \(\rho_{x,m}=0\) for one observed cell, then
\(r_{x,m}=\mu_{xm}/\rho_{xm}\) and the plug-in branch maps involving that conditional
mean are not evaluable from \(P\).  No root-\(n\) estimator of the stated cell mean
exists without changing the target or imposing an extrapolation model.  This explains
why Assumption~\ref{ass:overlap} is used at the first division step in \S11.

The active-branch premise is not cosmetic.  Without a finite locally \(C^1\)
active-branch representation of the leaky front-door endpoints, the notation \(v_j\),
the active sets \(A_L,A_U\), and the kink threshold \(\lambda^\star\) are not
mathematical inputs for the delta-method argument.  Assumption~\ref{ass:inference-regularity}
is exactly the regularity condition that supplies those objects for this inference
layer.
