Let \(R_n=(P_0^\circ)^n\), and write \(L_{\theta,n}=dP_{\theta,n}/dP_0^\circ\) for the one-observation likelihood ratio.  Under the base law, conditional on \((X,A)\), the observed outcome is uniform on \(\{-B,B\}\).  Under \(P_{\theta,n}\), its conditional mean is \((2A-1)\Delta_{\theta,n}(X)/2\).  Hence
\[
 L_{\theta,n}(O)
 =1+\frac{(2A-1)Y\Delta_{\theta,n}(X)}{2B^2}.
\]
For two sign vectors \(\theta,\theta'\), independence and symmetry under the base law give
\[
 E_{P_0^\circ}[L_{\theta,n}L_{\theta',n}]
 =1+\frac1{4B^2}\int_{\mathcal X}
 \Delta_{\theta,n}(x)\Delta_{\theta',n}(x)\,dx
 =1+q_n\sum_{\ell=1}^{N_n}\theta_\ell\theta'_\ell,
\]
where
\[
 q_n=\frac{a_n^2h_n^dJ_2}{4B^2},
 \qquad
 J_2=\int_{[0,1]^d}\psi(z)^2\,dz.
\]
The cube supports are disjoint, which is exactly what removes all cross-cell integrals.

Squaring the mixture likelihood and using product sampling yields
\[
 1+\chi^2(\overline Q_n,R_n)
 =2^{-2N_n}\sum_{\theta,\theta'}
 \left(1+q_n\sum_{\ell=1}^{N_n}\theta_\ell\theta'_\ell\right)^n.
\]
If \(R_1,\ldots,R_{N_n}\) are independent Rademacher variables, the right-hand side equals
\[
 E\left(1+q_n\sum_{\ell=1}^{N_n}R_\ell\right)^n.
\]
The inner factor is positive because it is an integral of a product of nonnegative likelihoods.  Using \(1+x\le e^x\) and \(\cosh t\le e^{t^2/2}\),
\[
 \begin{aligned}
 1+\chi^2(\overline Q_n,R_n)
 &\le E\exp\!\left(nq_n\sum_{\ell=1}^{N_n}R_\ell\right)\\
 &=\{\cosh(nq_n)\}^{N_n}\\
 &\le\exp\!\left(\frac{N_nn^2q_n^2}{2}\right)\\
 &=\exp\!\left\{K n^2N_na_n^4h_n^{2d}\right\},
 \end{aligned}
\]
with \(K=J_2^2/(32B^4)\).  This proves the first displayed inequality in the theorem.

The calibration constraints used in the membership proof are compatible with the testing constraint.  Indeed,
\[
 n^2N_na_n^4h_n^{2d}
 \le c_Nc_a^4n^2h_n^{d+s_1\alpha+4s_1}
 =c_Nc_a^4c_h^{D}.
\]
Choose, for example, any fixed \(\varepsilon\in(0,1-2\gamma)\), then choose positive \(c_a,c_N,c_h\) small enough to satisfy the Hölder, margin, support, and variance calibrations in \(\mathrm{def:sparse-near-tie-family}\) and
\[
 Kc_Nc_a^4c_h^D\le\log(1+\varepsilon^2).
\]
The collection of \(N_n\) cubes exists eventually because \(N_nh_n^d\asymp h_n^{s_1\alpha}\to0\), whereas \([1/4,3/4]^d\) has fixed positive volume.  It follows that \(\chi^2(\overline Q_n,R_n)\le\varepsilon^2\) eventually.

It remains to transfer testing indistinguishability to interval length.  The base law satisfies the exact-tie conditions directly: its regressions vanish, its design density is one, its propensity is one half, and its conditional outcome variances equal \(B^2\).  Thus \(P_0^\circ\in\mathcal P_0\subset\mathcal U\).  By \(\mathrm{lem:sparse-family-membership}\), every alternative in the mixture belongs to \(\mathcal P_1\subset\mathcal U\), has value \(\delta_n\), and the base value is zero.

Fix any \((C_n)_n\in\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\).  Uniform asymptotic honesty gives a deterministic sequence \(r_n\downarrow0\) such that, eventually,
\[
 R_n\{0\in C_n\}\ge1-\gamma-r_n,
 \qquad
 \overline Q_n\{\delta_n\in C_n\}\ge1-\gamma-r_n.
\]
Cauchy--Schwarz gives the total-variation bound
\[
 \sup_E|\overline Q_n(E)-R_n(E)|
 \le\frac12\left\{\chi^2(\overline Q_n,R_n)\right\}^{1/2}
 \le\frac\varepsilon2.
\]
Consequently
\[
 R_n\{0\in C_n,\ \delta_n\in C_n\}
 \ge1-2\gamma-2r_n-\frac\varepsilon2.
\]
Because \(C_n\) is connected, the event on the left forces \(\operatorname{length}(C_n)\ge\delta_n\).  Therefore
\[
 \liminf_{n\to\infty}
 \frac{E_{R_n}[\operatorname{length}(C_n)]}{\delta_n}
 \ge1-2\gamma-\frac\varepsilon2
 =:c_{\gamma,\varepsilon}>0.
\]
Finally,
\[
 \xi-\frac12
 =\frac{3s_1\alpha-d}{2(d+s_1\alpha+4s_1)}.
\]
Thus \(3s_1\alpha<d\) implies \(\xi<1/2\) and
\[
 \frac{\delta_n}{n^{-1/2}}\asymp n^{1/2-\xi}\longrightarrow\infty.
\]
The lower bound is therefore strictly slower than root-\(n\) at \(P_0^\circ\), whereas \(\mathrm{prop:oracle-tie-rootn}\) supplies a root-\(n\) interval when only the exact-tie stratum must be covered.