% Section 9-fragment-statement
\begin{theorem}[Conjecture 1: critical leakage support frontier]\label{thm:critical-leakage-frontier}
\paragraph{Conjecture restatement.}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:regular-frontier}, fix a population law \(P\), report direction \(w\), and leakage radius \(\eta\) with \(\mathcal Q_\eta(P)\ne\emptyset\).  The support-function equality frontier is sharp:
\[
h_{\mathrm{LP}}(w;P)=h_\eta(w;P)
\quad\Longleftrightarrow\quad
\eta\ge \eta_w^*(P),
\]
where
\[
\eta_w^*(P)=
\inf\{\eta'\ge0:\mathcal M_w(P)\cap\mathcal Q_{\eta'}(P)\ne\emptyset\}.
\]
Consequently, for every \(\eta<\eta_w^*(P)\),
\[
\Delta_w^\eta(P)=h_{\mathrm{LP}}(w;P)-h_\eta(w;P)>0,
\]
while for every \(\eta\ge\eta_w^*(P)\) the exposed LP support value is attainable by a rotation whose fourth cumulants match \(K_u\) up to allowed co-kurtosis leakage.  On a nonempty open semi-algebraic class of observable objects, \(\eta_w^*(P)\) is positive and finite, so bounded dependence creates a genuine phase transition between parent-style non-equivalence and restored LP/SVAR equivalence.

\paragraph{Headline.}
Conjecture 1 is confirmed: under Assumptions~\ref{ass:finite-var}--\ref{ass:regular-frontier}, the equality \(h_{\mathrm{LP}}(w;P)=h_\eta(w;P)\) holds exactly for \(\eta\ge\eta_w^*(P)\), and the critical radius is positive and finite on a nonempty open semi-algebraic class.
\end{theorem}

% Section 13-refutation-attempt
\paragraph{Refutation attempt before proof.}
The exact-identification primitives were checked first against the locked parameters.  The three-node SWIG primitive does not instantiate: the observable input is the finite-dimensional VAR/cumulant tuple \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\), there is no treatment node \(A\), no adjustment covariate \(X\), and no do-calculus functional whose equality to a potential-outcome target could be falsified.  The finite-support overlap primitive also has no conditioning stratum to shrink, and the do-calculus rule trace has no intervention expression on which a rule can fail.  These attempts therefore produce no admissible witness inside the proposal's locked support-function substrate.

The smallest compatible refutation search is the two-shock rotation search.  Set \(n=2\), \(j=1\), \(\Sigma_u=I_2\), take no sign or zero rows, and choose a report direction with
\[
\theta_w(Q)=e_1^\transpose Qe_1 .
\]
Let \(\alpha=\pi/6\), \(c=\cos\alpha\), \(s=\sin\alpha\),
\[
v_1=(c,s)^\transpose,\qquad v_2=(-s,c)^\transpose,
\]
and let
\[
K_u=4\delta_4\,v_1^{\otimes4}+\delta_4\,v_2^{\otimes4}.
\]
The LP/sign problem maximizes \(e_1^\transpose Qe_1\) over \(O(2)\), so \(h_{\mathrm{LP}}(w;P)=1\), attained by the two orthogonal completions whose first column is \(e_1\).  At either LP support maximizer, the pure diagonal cumulant coordinates are
\[
\bar\kappa_1=4\delta_4c^4+\delta_4s^4,\qquad
\bar\kappa_2=4\delta_4s^4+\delta_4c^4,
\]
and
\[
\bar\kappa_1-\bar\kappa_2
=3\delta_4(c^4-s^4)
=\frac{3}{2}\delta_4 .
\]
Thus \((\bar\kappa_1,\bar\kappa_2)\in\mathcal K_{\delta_4}(1)\).  The off-diagonal fourth-cumulant coordinate
\[
K^I_{1112}
=4\delta_4c^3s-\delta_4s^3c
=\delta_4cs(4c^2-s^2)
\]
is strictly positive, so the LP support maximizer does not belong to \(\mathcal Q_0(P)\) but does belong to \(\mathcal Q_\eta(P)\) once \(\eta\) reaches its off-diagonal residual norm.  The tilted basis \(Q=[v_1\ v_2]\) has exact diagonal fourth-cumulant contact at \(\eta=0\), so the contact sets are nonempty.  This bounded search therefore finds no violation of the conjectured frontier: it produces \(\eta_w^*(P)\in(0,\infty)\), equality for all \(\eta\ge\eta_w^*(P)\), and strict inequality for all feasible \(\eta<\eta_w^*(P)\).  The general proof below explains why this is forced by closed nested contact sets, not by a special trigonometric accident.

% Section 10 Interpretation
\paragraph{Interpretation.}
The theorem says that the LP/sign report and the higher-cumulant SVAR/sign report agree in direction \(w\) exactly when at least one LP support maximizer is also compatible with the same bounded-leakage fourth-cumulant contact restriction.  The scalar \(\eta_w^*(P)\) is therefore not an additional identifying assumption; it is the observable finite-dimensional radius needed to paste an exposed LP maximizer into the higher-cumulant contact set.  Below that radius, every \(\eta\)-SVAR feasible rotation is a proper suboptimal point for the LP support problem, so the support gap is strictly positive whenever \(\mathcal Q_\eta(P)\) is nonempty.  At or above that radius, the same rotation attains both reports.

The phase transition is a partial-identification statement about support functions.  The causal target remains the labelled structural response \(\psi_j(Q)\) and scalar report \(\theta_w(Q)\) for admissible structural completions \(Q\).  The observable functionals \(h_{\mathrm{LP}}\), \(h_\eta\), and \(\eta_w^*\) summarize two feasible rotation sets and the first leakage level at which their exposed faces intersect.  The computable program in Section~7 evaluates \(\eta_w^*(P)\) using only \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\), with \(n^2+n+1\) scalar decision variables \((Q,\kappa,t)\) and the displayed orthogonality, sign-zero, exposed-face, diagonal-contact, and residual-bound constraints.

% Section 11 Proof
\begin{proof}
Write the pure diagonal coordinate map as
\[
\bar\kappa(Q;P)=\bigl(K^Q_{1111},\ldots,K^Q_{nnnn}\bigr).
\]
Define the extended residual radius
\[
\rho(Q;P)=
\begin{cases}
\|r_4(Q,\bar\kappa(Q;P);P)\|_{\mathrm{off}},
& \bar\kappa(Q;P)\in\mathcal K_{\delta_4}(j),\\
+\infty,
& \bar\kappa(Q;P)\notin\mathcal K_{\delta_4}(j).
\end{cases}
\]
By the coordinate equivalence in the formal setup, together with Assumptions~\ref{ass:cumulants}, \ref{ass:separated-target}, and \ref{ass:leakage-class},
\[
Q\in\mathcal Q_\eta(P)
\quad\Longleftrightarrow\quad
Q\in\mathcal Q_{\mathrm{LP}}(P)\ \text{and}\ \rho(Q;P)\le\eta .
\]
Indeed, \(d_4(Q,\kappa;P)=0\) fixes \(\kappa=\bar\kappa(Q;P)\), and the leakage tensor \(L\) can absorb exactly the off-diagonal residual coordinates whose Euclidean norm is at most \(\eta\).

Assumption~\ref{ass:sign-zero} makes \(\mathcal Q_{\mathrm{LP}}(P)\) a nonempty compact subset of \(O(n)\).  Assumptions~\ref{ass:finite-var} and \ref{ass:normalization} make \(Q\mapsto\theta_w(Q)\) continuous, so
\[
\mathcal M_w(P)=\arg\max_{Q\in\mathcal Q_{\mathrm{LP}}(P)}\theta_w(Q)
\]
is nonempty and compact.  For each finite \(\eta\), the set \(\mathcal Q_\eta(P)\) is closed in \(\mathcal Q_{\mathrm{LP}}(P)\): the maps \(Q\mapsto\bar\kappa(Q;P)\) and \(Q\mapsto r_4(Q,\bar\kappa(Q;P);P)\) are continuous, \(\mathcal K_{\delta_4}(j)\) is closed, and the leakage ball is closed by Assumption~\ref{ass:leakage-class}.  Hence \(\mathcal Q_\eta(P)\) is compact whenever it is nonempty.

The first key equivalence is
\[
h_{\mathrm{LP}}(w;P)=h_\eta(w;P)
\quad\Longleftrightarrow\quad
\mathcal M_w(P)\cap\mathcal Q_\eta(P)\ne\emptyset .
\]
If the intersection is nonempty, some \(Q^\star\in\mathcal Q_\eta(P)\) satisfies \(\theta_w(Q^\star)=h_{\mathrm{LP}}(w;P)\), so \(h_\eta(w;P)\ge h_{\mathrm{LP}}(w;P)\).  Theorem~\ref{thm:parent-corner} gives \(\mathcal Q_\eta(P)\subseteq\mathcal Q_{\mathrm{LP}}(P)\), hence \(h_\eta(w;P)\le h_{\mathrm{LP}}(w;P)\), and equality follows.  Conversely, if \(h_\eta(w;P)=h_{\mathrm{LP}}(w;P)\) and \(\mathcal Q_\eta(P)\ne\emptyset\), compactness gives \(Q_\eta^\star\in\mathcal Q_\eta(P)\) with
\[
\theta_w(Q_\eta^\star)=h_\eta(w;P)=h_{\mathrm{LP}}(w;P).
\]
Thus \(Q_\eta^\star\in\mathcal M_w(P)\cap\mathcal Q_\eta(P)\).

Now define
\[
S_w(P)=\{\eta'\ge0:\mathcal M_w(P)\cap\mathcal Q_{\eta'}(P)\ne\emptyset\}.
\]
Using the residual-radius representation,
\[
S_w(P)=\{\eta'\ge0:\inf_{Q\in\mathcal M_w(P)}\rho(Q;P)\le \eta'\}.
\]
The extended function \(\rho(\cdot;P)\) is lower semicontinuous on the compact set \(\mathcal M_w(P)\), because it is continuous on the closed separated-cumulant region and equals \(+\infty\) off that region.  Therefore the infimum is attained when finite.  With the convention that \(\inf\emptyset=+\infty\),
\[
\eta_w^*(P)
=\inf S_w(P)
=\min_{Q\in\mathcal M_w(P)}\rho(Q;P)
\]
in the extended real line, and \(S_w(P)=[\eta_w^*(P),\infty)\) when the minimum is finite, while \(S_w(P)=\emptyset\) when it is infinite.  Combining this description of \(S_w(P)\) with the preceding support-equality equivalence proves
\[
h_{\mathrm{LP}}(w;P)=h_\eta(w;P)
\quad\Longleftrightarrow\quad
\eta\ge\eta_w^*(P)
\]
for every finite \(\eta\) with \(\mathcal Q_\eta(P)\ne\emptyset\).

If \(\eta<\eta_w^*(P)\), then \(\mathcal M_w(P)\cap\mathcal Q_\eta(P)=\emptyset\).  Since \(\mathcal Q_\eta(P)\) is compact and nonempty by Assumption~\ref{ass:contact-nonempty} for the finite comparison under discussion, \(h_\eta(w;P)\) is attained.  If the attained value were \(h_{\mathrm{LP}}(w;P)\), the maximizer would belong to \(\mathcal M_w(P)\cap\mathcal Q_\eta(P)\), a contradiction.  Thus
\[
\Delta_w^\eta(P)=h_{\mathrm{LP}}(w;P)-h_\eta(w;P)>0 .
\]
If \(\eta\ge\eta_w^*(P)\), choose \(Q^\star\in\mathcal M_w(P)\cap\mathcal Q_\eta(P)\).  By the definition of \(\mathcal Q_\eta(P)\), there is a separated diagonal cumulant vector \(\kappa^\star\in\mathcal K_{\delta_4}(j)\) and a leakage tensor \(L^\star\in\mathcal L_\eta(Q^\star)\) such that
\[
K_u=D(Q^\star,\kappa^\star)+L^\star .
\]
The same \(Q^\star\) attains \(\theta_w(Q^\star)=h_{\mathrm{LP}}(w;P)\), proving the stated attainability by a rotation whose fourth cumulants match \(K_u\) up to allowed co-kurtosis leakage.

It remains to prove that the positive finite frontier occurs on a nonempty open semi-algebraic class.  Use the two-shock center from the refutation attempt:
\[
n=2,\quad j=1,\quad \Sigma_u=I_2,\quad
\theta_w(Q)=e_1^\transpose Qe_1,\quad
K_u^0=4\delta_4\,v_1^{\otimes4}+\delta_4\,v_2^{\otimes4},
\]
where \(v_1=(\cos(\pi/6),\sin(\pi/6))^\transpose\) and \(v_2=(-\sin(\pi/6),\cos(\pi/6))^\transpose\), and take \(A\) and \(Z\) empty.  Assumptions~\ref{ass:finite-var}--\ref{ass:leakage-class} hold, for example, for a stable finite-order VAR with these population response rows and cumulants.  Assumption~\ref{ass:generic-exposed} holds because the report is nonconstant and exposes only the two completions whose first column is \(e_1\).  Assumption~\ref{ass:regular-frontier} is satisfied at the center because the exposed face is zero-dimensional and the boundary condition is the scalar closed inequality \(\rho(Q;P)\le\eta\) at an isolated support maximizer.

At this center, the calculation in the refutation attempt gives
\[
\eta_w^*(P^0)=\rho(I_2;P^0)\in(0,\infty).
\]
The lower bound is strict because \(K^{I_2}_{1112}=\delta_4cs(4c^2-s^2)>0\).  The upper bound is finite because the pure diagonal coordinates at the LP maximizer lie in \(\mathcal K_{\delta_4}(1)\).  Small perturbations of \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,w)\) preserve the strict inequalities
\[
\bar\kappa_1(Q_{\mathrm{LP}};P)>\delta_4,\qquad
|\bar\kappa_1(Q_{\mathrm{LP}};P)-\bar\kappa_2(Q_{\mathrm{LP}};P)|>\delta_4,\qquad
\rho(Q_{\mathrm{LP}};P)>0,
\]
where \(Q_{\mathrm{LP}}\) is an LP support maximizer on each component.  They also preserve nonflat exposure of the LP support face and the regular isolated-boundary condition after removing the lower-dimensional algebraic exceptional set named in Assumption~\ref{ass:regular-frontier}.  These strict conditions define a nonempty open class containing the center.

The same class is semi-algebraic.  Orthogonality, sign-zero restrictions, exposed-face equations \(\theta_w(Q)=h_{\mathrm{LP}}(w;P)\), diagonal contact, separated cumulants, and residual inequalities are polynomial equalities and inequalities in the entries of \((Q,\kappa,t)\), the observed coefficients, and an auxiliary symmetric square root \(S\) constrained by \(S=S^\transpose\), \(S^2=\Sigma_u\), and positive principal minors.  The statement that the displayed strict inequalities hold at an exposed maximizer can be written with auxiliary variables for \(Q_{\mathrm{LP}}\), \(S\), and the support value; eliminating those variables preserves semi-algebraicity by the Tarski-Seidenberg projection theorem.  Hence on a nonempty open semi-algebraic class of observable objects, \(\eta_w^*(P)\) is positive and finite.  This proves the final phase-transition claim.
\end{proof}

% Section 12 Sanity check
\paragraph{Sanity check.}
At the parent independent-shock corner \(\eta=0\), Theorem~\ref{thm:parent-corner} identifies \(\mathcal Q_0(P)\) with the exact fourth-cumulant diagonalizing SVAR/sign set.  The frontier theorem reduces to
\[
h_{\mathrm{LP}}(w;P)=h_0(w;P)
\quad\Longleftrightarrow\quad
\mathcal M_w(P)\cap\mathcal Q_0(P)\ne\emptyset
\quad\Longleftrightarrow\quad
\eta_w^*(P)=0.
\]
Thus the parent corner has no LP/SVAR support gap exactly when an LP support maximizer already satisfies the independent-shock cumulant contact restriction.  If the LP side is restricted to the same \(\eta\)-contact set, both reports optimize \(\theta_w\) over the identical feasible set, and Theorem~\ref{thm:parent-corner} again gives equality for every \(w\).  This is the common-restriction special case: the gap is created by optimizing over the larger LP/sign relaxation, not by the response-row definition of \(\psi_j(Q)\).

% Section 13 Counterexample or minimality check
\paragraph{Minimality check.}
Closedness of the leakage class is essential for the boundary equality.  If Assumption~\ref{ass:leakage-class} were changed so that the off-diagonal leakage ball were open, \(\|r_4(Q,\kappa;P)\|_{\mathrm{off}}<\eta\), the two-shock center above would have
\[
S_w(P^0)=(\eta_w^*(P^0),\infty)
\]
instead of \(S_w(P^0)=[\eta_w^*(P^0),\infty)\).  Then the infimum defining \(\eta_w^*(P^0)\) would be unchanged, but the LP support maximizer would not be feasible at the boundary radius itself, so
\[
h_{\mathrm{LP}}(w;P^0)\ne h_{\eta_w^*(P^0)}(w;P^0)
\]
despite \(\eta=\eta_w^*(P^0)\).  This shows why the closed leakage ball and compact support-face attainment assumptions are not cosmetic regularity conditions: they are exactly what turns the infimum diagnostic into a sharp equality frontier.
