% =====================================================================
%  thmsmith Stage 0 derivation skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=eid\_lp\_svar\_nonequiv, specialization=upgrade2
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{eid\_lp\_svar\_nonequiv} / \texttt{upgrade2}%
  \\ \large\textit{Critical leakage radius for LP/sign and higher-cumulant SVAR support equivalence}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note sets up a support-function partial-identification problem for structural impulse responses in a finite-order VAR population.  The estimand-defining functional is the observable pair
\[
h_{\mathrm{LP}}(w;P)=\sup_{Q\in\mathcal Q_{\mathrm{LP}}(P)}\theta_w(Q),
\qquad
h_\eta(w;P)=\sup_{Q\in\mathcal Q_\eta(P)}\theta_w(Q),
\]
together with the computable critical-radius program defining \(\eta_w^*(P)\).  The target causal object is the labelled structural impulse-response path \(\psi_j(Q)\) and scalar report \(\theta_w(Q)=w^\transpose\psi_j(Q)\) for rotations satisfying the sign-zero and higher-cumulant contact restrictions.  The per-conjecture stages will verify whether the support-function equality frontier is exactly governed by \(\eta_w^*(P)\), and whether the two-shock case reduces to an explicit angular residual formula.
\end{abstract}

\section{Introduction}
Local projections and VARs can report the same impulse-response objects when they impose the same identifying restrictions, but non-Gaussian SVARs can impose additional restrictions through higher moments of reduced-form innovations.  The resulting econometric question is whether an LP/sign robustness report and a higher-cumulant SVAR/sign report are optimizing over the same response set, or whether the LP report is an outer relaxation that includes rotations incompatible with the shock label.

The parent setting asked this question at the exact independent-shock corner, where off-diagonal fourth cumulants in the structural basis must vanish.  The upgrade treated here allows a bounded amount of co-kurtosis leakage.  If the conjectured frontier is confirmed, the scalar \(\eta_w^*(P)\) will be the population diagnostic for the smallest leakage radius at which an LP support maximizer enters the higher-cumulant contact set.  If the conjectures fail, the failure will identify which boundary condition prevents a support-function equality from being reduced to cumulant residual distance.

The note targets two contributions.  First, the critical-frontier conjecture would turn the comparison between LP/sign and SVAR/sign reports into a computable support-face contact problem.  Second, the two-shock conjecture would reduce that problem to a closed-form angular formula on the two connected components of \(O(2)\), making the diagnostic auditable in the smallest nontrivial case.

\paragraph{Motivating conjecture(s).}
Conjecture 1. Under Assumptions~\ref{ass:finite-var}--\ref{ass:regular-frontier}, fix a population law \(P\), report direction \(w\), and leakage radius \(\eta\) with \(\mathcal Q_\eta(P)\ne\emptyset\).  The support-function equality frontier is sharp:
\[
h_{\mathrm{LP}}(w;P)=h_\eta(w;P)
\quad\Longleftrightarrow\quad
\eta\ge \eta_w^*(P),
\]
where
\[
\eta_w^*(P)=
\inf\{\eta'\ge0:\mathcal M_w(P)\cap\mathcal Q_{\eta'}(P)\ne\emptyset\}.
\]
Consequently, for every \(\eta<\eta_w^*(P)\),
\[
\Delta_w^\eta(P)=h_{\mathrm{LP}}(w;P)-h_\eta(w;P)>0,
\]
while for every \(\eta\ge\eta_w^*(P)\) the exposed LP support value is attainable by a rotation whose fourth cumulants match \(K_u\) up to allowed co-kurtosis leakage.  On a nonempty open semi-algebraic class of observable objects, \(\eta_w^*(P)\) is positive and finite, so bounded dependence creates a genuine phase transition between parent-style non-equivalence and restored LP/SVAR equivalence.

Conjecture 2. Under Assumptions~\ref{ass:finite-var}--\ref{ass:generic-exposed} and \ref{ass:two-shock}, parameterize the two components of \(O(2)\) by rotation/reflection angles \(\varphi\).  Let the LP/sign feasible set on a component be \(I_{\mathrm{LP}}\), and write the report objective as
\[
\theta_w(\varphi)=a_w\cos\varphi+b_w\sin\varphi=\rho_w\cos(\varphi-\varphi_w).
\]
Let \(r_4(\varphi,\kappa;P)\) be the vector of off-diagonal fourth-cumulant residual coordinates in the structural basis and \(d_4(\varphi,\kappa;P)\) the pure-diagonal residual.  If no \(\kappa\in\mathcal K_{\delta_4}(j)\) satisfies \(d_4(\varphi,\kappa;P)=0\) at any LP support angle on the component, set the component value of \(\eta_w^*(P)\) to \(+\infty\).  Otherwise the critical leakage radius on that component is
\[
\eta_w^*(P)=
\min_{\substack{\varphi\in\arg\max_{\phi\in I_{\mathrm{LP}}}\theta_w(\phi)\\
\kappa\in\mathcal K_{\delta_4}(j),\ d_4(\varphi,\kappa;P)=0}}
\|r_4(\varphi,\kappa;P)\|_{\mathrm{off}},
\]
with the global \(O(2)\) value obtained by taking the minimum over rotation and reflection components.  In the parent corner \(\eta=0\), this reduces to the parent two-shock witness: equality holds only when an LP support angle is one of the cumulant-contact angles; otherwise the support gap is at least \(\rho_w(1-\cos d_w)\) for the distance \(d_w\) to the nearest contact angle.

\section{Related work and positioning}
Jorda (2005) introduced local projections as direct population impulse-response regressions, motivating the treatment of \(\Gamma_h\) as the observed response-row input.  Plagborg-Moller and Wolf (2021) show that LPs and VARs estimate the same impulse responses under common identifying restrictions; this note differs by comparing an LP/sign relaxation with a stricter higher-cumulant contact set.  Rubio-Ramirez, Waggoner, and Zha (2010) and Arias, Rubio-Ramirez, and Waggoner (2018) provide the rotation geometry for sign and zero restrictions in SVARs, which is the finite-dimensional geometry used here.  Baumeister and Hamilton (2015) emphasize that sign-restricted conclusions depend on what remains in the identified set, motivating support functions rather than point estimates.

Drautzburg and Wright (2023) refine sign-restricted VAR sets through independence restrictions and document that the resulting sets can be nonconvex; the present setup asks for a radius at which an LP support face first intersects the higher-moment contact set.  Gourieroux, Monfort, and Renne (2017) and Lanne, Meitz, and Saikkonen (2017) show how non-Gaussian independent shocks can label SVARs, corresponding to the \(\eta=0\) parent corner.  Guay (2021) develops higher-moment rank conditions for SVAR identification, adjacent to the regular-contact and transversality conditions used by the frontier conjecture.  Lanne and Luoto (2021) study GMM estimation of non-Gaussian SVARs, which is related to implementation but not to the population equality frontier.

Hoesch, Lee, and Mesters (2024) develop locally robust inference for non-Gaussian SVARs near weak or local-to-Gaussian cases, making a population null for \(h_{\mathrm{LP}}(w;P)-h_\eta(w;P)\) useful.  Montiel Olea, Plagborg-Moller, and Qian (2022) caution that higher-moment SVAR identification can be empirically fragile, so an auditable leakage diagnostic is a natural population-level complement.  Lanne, Liu, and Luoto (2026) show that some non-Gaussian identification survives dependent shocks under co-moment restrictions; this note instead fixes a bounded co-kurtosis leakage class and compares the resulting support function with the LP/sign relaxation.  The discussion is targeted rather than exhaustive.

\section{Formal setup}
Let \(P\) denote the population law of a covariance-stationary finite-order VAR process \(Y_t\in\R^n\) with reduced-form innovation \(u_t\), innovation covariance \(\Sigma_u\succ0\), and finite fourth moments.  The observed population inputs are
\[
\Gamma_h=\E[Y_{t+h}u_t^\transpose]\Sigma_u^{-1},\qquad h=0,\ldots,H,
\]
the covariance \(\Sigma_u\), and the fourth cumulant tensor \(K_u=\operatorname{cum}_4(u_t)\).  Fix the symmetric square root \(\Sigma_u^{1/2}\).  Every unit-variance structural completion is written
\[
B(Q)=\Sigma_u^{1/2}Q,\qquad Q\in O(n),
\]
with labelled shock vector \(b_j(Q)=B(Q)e_j\).  The labelled impulse-response path and report are
\[
\psi_j(Q)=\left(e_y^\transpose\Gamma_h b_j(Q)\right)_{h=0}^H\in\R^{H+1},
\qquad
\theta_w(Q)=w^\transpose\psi_j(Q).
\]

Known sign and zero restrictions are encoded by matrices \(A\in\R^{m_A\times(H+1)}\) and \(Z\in\R^{m_Z\times(H+1)}\):
\[
\mathcal Q_{\mathrm{LP}}(P)=
\{Q\in O(n):A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0\}.
\]
For \(Q\in O(n)\) and diagonal cumulant vector \(\kappa\), define
\[
D(Q,\kappa)=\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4}.
\]
The admissible separated diagonal cumulant set is
\[
\mathcal K_{\delta_4}(j)=
\{\kappa\in\R^n:\ |\kappa_j|\ge\delta_4,\ 
|\kappa_\ell-\kappa_j|\ge\delta_4\text{ for all }\ell\ne j\},
\]
where \(\delta_4>0\).

Let \(c_a(Q)\) be the \(a\)-th column of \(B(Q)^{-\transpose}\), and write the structural-basis cumulant coordinates as
\[
K^Q_{abcd}=
\langle K_u,c_a(Q)\otimes c_b(Q)\otimes c_c(Q)\otimes c_d(Q)\rangle .
\]
Let \(\mathcal I_{\mathrm{off}}\) be the index set of fourth-order tuples \((a,b,c,d)\) that are not all equal.  Define the off-diagonal residual vector and pure-diagonal residual by
\[
r_4(Q,\kappa;P)=
\left(K^Q_{abcd}-\one_{\{a=b=c=d\}}\kappa_a\right)_{(a,b,c,d)\in\mathcal I_{\mathrm{off}}},
\]
\[
\|r_4(Q,\kappa;P)\|_{\mathrm{off}}=
\left(\sum_{(a,b,c,d)\in\mathcal I_{\mathrm{off}}}
|r_{4,abcd}(Q,\kappa;P)|^2\right)^{1/2},
\qquad
d_4(Q,\kappa;P)=\left(K^Q_{aaaa}-\kappa_a\right)_{a=1}^n.
\]
For a leakage radius \(\eta\ge0\), let \(\mathcal L_\eta(Q)\) be the set of symmetric fourth-order tensors whose \(B(Q)\)-basis coordinates have zero pure diagonal entries and off-diagonal Euclidean coefficient norm at most \(\eta\).  The leakage-adjusted mismatch is
\[
m_\eta(Q;P)=
\inf_{\kappa\in\mathcal K_{\delta_4}(j),\,L\in\mathcal L_\eta(Q)}
\|K_u-D(Q,\kappa)-L\|_F.
\]
Equivalently, \(m_\eta(Q;P)=0\) exactly when some \(\kappa\in\mathcal K_{\delta_4}(j)\) satisfies
\[
d_4(Q,\kappa;P)=0,\qquad
\|r_4(Q,\kappa;P)\|_{\mathrm{off}}\le\eta .
\]
The \(\eta\)-SVAR/sign contact set is therefore
\[
\mathcal Q_\eta(P)=
\{Q\in\mathcal Q_{\mathrm{LP}}(P):m_\eta(Q;P)=0\}.
\]

\paragraph{Locked parameters.}
\begin{itemize}[leftmargin=*]
  \item qid: eid\_lp\_svar\_nonequiv
  \item specialization: upgrade2
  \item anchor\_cluster: PartialID / support-function structural time-series identification with partial sign-zero restrictions and higher-cumulant contact restrictions defining the sharp response set
  \item observable distribution \(P\): the population law of a covariance-stationary finite-order VAR(p) process \(Y_t\), summarized by reduced-form response rows \(\Gamma_h = E[Y_{t+h} u_t'] \Sigma_u^{-1}\) for \(h=0,\ldots,H\), innovation covariance \(\Sigma_u\), and fourth cumulant tensor \(K_u = \operatorname{cum4}(u_t)\)
  \item parameter \(\theta\): the structural impulse-response vector \(\psi_j(Q)=(e_y' \Gamma_h b_j(Q))_{h=0}^H\) and its scalar report \(\theta_w(Q)=w' \psi_j(Q)\)
  \item identifying restrictions: finite-order LP/VAR population rows; unit-variance shocks; partial sign-zero restrictions \(A \psi_j(Q) \ge 0\) and \(Z \psi_j(Q)=0\); a fourth-cumulant structural representation whose off-diagonal co-kurtosis leakage is bounded by \(\eta \ge 0\); target cumulant separation \(\delta_4 > 0\); and the common-contact requirement that the same rotation generating an LP response lies inside the eta-leakage cumulant contact set
  \item upgrade axis: generalization of the parent v1 independent-shock cumulant diagonalization premise from \(\eta=0\) to eta-bounded dependent/non-diagonal fourth-cumulant leakage, with v1 recovered as the eta=0 corner
  \item operational quantity: \(\eta_w^*(P)\), the critical leakage radius at which a support-exposed LP/sign maximizer first enters the higher-cumulant SVAR contact set; strict non-equivalence is governed by \(\eta < \eta_w^*(P)\)
  \item bounding functional: support functions \(h_{\mathrm{LP}}(w;P)\) and \(h_\eta(w;P)\) over, respectively, the LP/sign relaxation and the eta-leakage higher-cumulant contact set; the non-equivalence gap is \(\Delta_w^\eta(P)=h_{\mathrm{LP}}(w;P)-h_\eta(w;P)\)
\end{itemize}

\section{Assumptions}
\begin{assumption}[Finite-order LP/VAR population environment]\label{ass:finite-var}
The population law \(P\) is generated by a covariance-stationary finite-order VAR(p) with innovation \(u_t\), \(\Sigma_u\succ0\), finite fourth moments, and response rows \(\Gamma_h\) equal to the unrestricted population VAR response rows for \(h=0,\ldots,H\).
\end{assumption}

\begin{assumption}[Rotation normalization and labelled shock]\label{ass:normalization}
Structural shocks have identity covariance and each impact matrix is \(B(Q)=\Sigma_u^{1/2}Q\) for \(Q\in O(n)\).  The shock label \(j\) is fixed after the usual sign and permutation normalization.
\end{assumption}

\begin{assumption}[Partial sign-zero restrictions]\label{ass:sign-zero}
The matrices \(A\in\R^{m_A\times(H+1)}\) and \(Z\in\R^{m_Z\times(H+1)}\) are known, and \(\mathcal Q_{\mathrm{LP}}(P)=\{Q:A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0\}\) is nonempty and compact as a closed subset of \(O(n)\).
\end{assumption}

\begin{assumption}[Observed fourth cumulants]\label{ass:cumulants}
The fourth cumulant tensor \(K_u=\operatorname{cum}_4(u_t)\) is observed at the population level.  For each \(Q\), \(D(Q,\kappa)=\sum_k\kappa_kb_k(Q)^{\otimes4}\) is the pure diagonal fourth-cumulant component in the \(B(Q)\) basis.
\end{assumption}

\begin{assumption}[Separated target cumulant]\label{ass:separated-target}
The admissible pure diagonal cumulants satisfy \(\kappa\in\mathcal K_{\delta_4}(j)\) for a fixed \(\delta_4>0\).  Gaussian and equal-target-kurtosis boundaries are excluded from strict-gap statements unless explicitly handled as limiting cases.
\end{assumption}

\begin{assumption}[Bounded co-kurtosis leakage class]\label{ass:leakage-class}
For every \(Q\), \(\mathcal L_\eta(Q)\) is the closed convex set of symmetric fourth-order tensors whose coordinates in the \(B(Q)\) structural basis have zero pure diagonal terms and Euclidean off-diagonal coefficient norm at most \(\eta\), using the coordinate convention \(r_4(Q,\kappa;P)\) from the formal setup.  The sets are nested in \(\eta\), contain only \(0\) when \(\eta=0\), and vary continuously with \(Q\).
\end{assumption}

\begin{assumption}[Nonempty contact at the evaluated leakage radius]\label{ass:contact-nonempty}
For every leakage radius \(\eta\) appearing in a finite support comparison, \(\mathcal Q_\eta(P)\) is nonempty.  Empty-contact cases are interpreted as failed higher-cumulant SVAR feasibility rather than finite LP/SVAR disagreement.
\end{assumption}

\begin{assumption}[Generic exposed report]\label{ass:generic-exposed}
The report direction \(w\in\R^{H+1}\) exposes a nonempty compact LP maximizer set \(\mathcal M_w(P)\), and \(\theta_w(Q)\) is not constant on any positive-dimensional feasible component that changes the leakage-adjusted mismatch \(m_\eta(Q;P)\).
\end{assumption}

\begin{assumption}[Regular cumulant-contact frontier]\label{ass:regular-frontier}
Near the boundary \(\eta=\eta_w^*(P)\), the zero set \(m_\eta(Q;P)=0\) intersects the exposed LP support face transversally, except on a lower-dimensional algebraic exceptional set.  This is the regularity condition whose necessity or sufficiency is part of Conjecture 1.
\end{assumption}

\begin{assumption}[Two-shock planar specialization]\label{ass:two-shock}
For the closed-form witness, \(n=2\), \(p=1\), \(H\ge1\), both rotation and reflection components of \(O(2)\) are included, the sign-zero restrictions leave a nondegenerate angular interval on at least one component, and the target and non-target pure cumulants are separated by \(\delta_4\).
\end{assumption}

\section{Estimand-defining functional}
For a report direction \(w\), the LP/sign outer support functional is
\[
h_{\mathrm{LP}}(w;P)=
\sup_{Q\in\mathcal Q_{\mathrm{LP}}(P)}\theta_w(Q),
\qquad
\theta_w(Q)=w^\transpose\left(e_y^\transpose\Gamma_h\Sigma_u^{1/2}Qe_j\right)_{h=0}^H .
\]
The \(\eta\)-leakage higher-cumulant support functional is
\[
h_\eta(w;P)=\sup_{Q\in\mathcal Q_\eta(P)}\theta_w(Q),
\qquad
\mathcal Q_\eta(P)=
\{Q\in\mathcal Q_{\mathrm{LP}}(P):m_\eta(Q;P)=0\}.
\]
The non-equivalence gap is the observed-population functional
\[
\Delta_w^\eta(P)=h_{\mathrm{LP}}(w;P)-h_\eta(w;P),
\]
with the convention \(\sup\emptyset=-\infty\).  The exposed LP support face is
\[
\mathcal M_w(P)=\arg\max_{Q\in\mathcal Q_{\mathrm{LP}}(P)}\theta_w(Q),
\]
and the critical leakage functional is
\[
\eta_w^*(P)=
\inf\{\eta'\ge0:\mathcal M_w(P)\cap\mathcal Q_{\eta'}(P)\ne\emptyset\}.
\]

The same quantity is computable from \(P\) by the finite-dimensional program
\[
\begin{aligned}
\eta_w^*(P)=\min_{Q,\kappa,t}\quad & t\\
\text{subject to}\quad
& Q^\transpose Q=I_n,\quad A\psi_j(Q)\ge0,\quad Z\psi_j(Q)=0,\\
& \theta_w(Q)=h_{\mathrm{LP}}(w;P),\quad \kappa\in\mathcal K_{\delta_4}(j),\\
& d_4(Q,\kappa;P)=0,\\
& \|r_4(Q,\kappa;P)\|_{\mathrm{off}}^2\le t^2,\quad t\ge0 .
\end{aligned}
\]
If this program is infeasible, \(\eta_w^*(P)=+\infty\).  Otherwise compactness of \(O(n)\), closed sign-zero constraints, and closed diagonal-contact constraints give an attained minimum.  The optimization has \(n^2+n+1\) scalar decision variables \((Q,\kappa,t)\), \(n(n+1)/2\) orthogonality equations, \(m_A\) sign inequalities, \(m_Z\) zero equations, one exposed-face equality, \(n\) pure-diagonal cumulant equations, and one quadratic residual bound.  All coefficients in these constraints are functions of the observed objects \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u)\).

\section{Target causal estimand}
For each admissible structural completion \(Q\), the causal target is the labelled structural impulse-response path
\[
\psi_j(Q)=\left(e_y^\transpose\Gamma_h b_j(Q)\right)_{h=0}^H,
\qquad b_j(Q)=\Sigma_u^{1/2}Qe_j,
\]
and the scalar report in direction \(w\) is
\[
\theta_w(Q)=w^\transpose\psi_j(Q).
\]
The LP/sign target set is \(\Theta_{\mathrm{LP}}(P)=\{\theta_w(Q):Q\in\mathcal Q_{\mathrm{LP}}(P)\}\).  The higher-cumulant \(\eta\)-SVAR target set is
\[
\Theta_\eta(P)=\{\theta_w(Q):Q\in\mathcal Q_\eta(P)\}.
\]
Thus \(h_{\mathrm{LP}}(w;P)\) and \(h_\eta(w;P)\) are support-function summaries of two target sets, not definitions of the causal effect itself.  The central identification question for the later theorem stages is whether the observable support-function equality \(h_{\mathrm{LP}}(w;P)=h_\eta(w;P)\) is exactly characterized by the critical leakage radius \(\eta_w^*(P)\), and how the target set changes when \(\eta\) moves from the parent independent-shock corner \(\eta=0\) to positive bounded co-kurtosis leakage.

\section{Main theorems}
\begin{theorem}[Conjecture 1: critical leakage support frontier]\label{thm:critical-leakage-frontier}
Conjecture 1 is confirmed: under Assumptions~\ref{ass:finite-var}--\ref{ass:regular-frontier}, the equality \(h_{\mathrm{LP}}(w;P)=h_\eta(w;P)\) holds exactly for \(\eta\ge\eta_w^*(P)\), and the critical radius is positive and finite on a nonempty open semi-algebraic class.
\end{theorem}
The theorem says that the LP/sign report and the higher-cumulant SVAR/sign report agree in direction \(w\) exactly when at least one LP support maximizer is also compatible with the same bounded-leakage fourth-cumulant contact restriction.  The scalar \(\eta_w^*(P)\) is therefore not an additional identifying assumption; it is the observable finite-dimensional radius needed to paste an exposed LP maximizer into the higher-cumulant contact set.

\begin{theorem}[Conjecture 2: two-shock angular critical-radius formula]\label{thm:two-shock-formula}
The two-shock critical leakage radius is the minimum off-diagonal fourth-cumulant residual over LP support angles satisfying pure-diagonal contact, with the global value obtained over both components.
\end{theorem}
The theorem says that the two-shock leakage diagnostic is not an optimization over the full angular contact set.  One first finds the LP/sign support angle or angles on each component, then checks whether those same angles have pure-diagonal fourth-cumulant contact.  If they do, the required leakage radius is exactly the off-diagonal fourth-cumulant residual norm at those angles; if they do not, no finite off-diagonal leakage radius can make that component attain the LP support value.

\section{Interpretation}
\paragraph{Interpretation for Conjecture 1.}
The theorem says that the LP/sign report and the higher-cumulant SVAR/sign report agree in direction \(w\) exactly when at least one LP support maximizer is also compatible with the same bounded-leakage fourth-cumulant contact restriction.  The scalar \(\eta_w^*(P)\) is therefore not an additional identifying assumption; it is the observable finite-dimensional radius needed to paste an exposed LP maximizer into the higher-cumulant contact set.  Below that radius, every \(\eta\)-SVAR feasible rotation is a proper suboptimal point for the LP support problem, so the support gap is strictly positive whenever \(\mathcal Q_\eta(P)\) is nonempty.  At or above that radius, the same rotation attains both reports.

The phase transition is a partial-identification statement about support functions.  The causal target remains the labelled structural response \(\psi_j(Q)\) and scalar report \(\theta_w(Q)\) for admissible structural completions \(Q\).  The observable functionals \(h_{\mathrm{LP}}\), \(h_\eta\), and \(\eta_w^*\) summarize two feasible rotation sets and the first leakage level at which their exposed faces intersect.  The computable program in Section~7 evaluates \(\eta_w^*(P)\) using only \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\), with \(n^2+n+1\) scalar decision variables \((Q,\kappa,t)\) and the displayed orthogonality, sign-zero, exposed-face, diagonal-contact, and residual-bound constraints.

\paragraph{Interpretation for Conjecture 2.}
The theorem says that the two-shock leakage diagnostic is not an optimization over the full angular contact set.  One first finds the LP/sign support angle or angles on each component, then checks whether those same angles have pure-diagonal fourth-cumulant contact.  If they do, the required leakage radius is exactly the off-diagonal fourth-cumulant residual norm at those angles; if they do not, no finite off-diagonal leakage radius can make that component attain the LP support value.  This is a computable observed-population map: on each component, the LP support angle is the projection of the report phase \(\varphi_{w,c}\) onto the closed feasible interval \(I_c\) together with any tied endpoint, and the residuals are polynomial-trigonometric functions of \((\Gamma_h,\Sigma_u,K_u)\).

The result connects the upgrade to the parent independent-shock corner.  At \(\eta=0\), equality of the LP/sign and higher-cumulant SVAR reports is not a generic consequence of sign restrictions; it requires that an exposed LP angle also diagonalize the fourth cumulant tensor with separated target cumulants.  Positive leakage widens the contact set by allowing off-diagonal co-kurtosis residuals, but it does not relax the pure-diagonal cumulant equations.

Together these interpretations connect back to the motivating conjectures: the scalar \(\eta_w^*(P)\) is the observable finite-dimensional radius needed to paste an exposed LP maximizer into the higher-cumulant contact set, and in the two-shock case this is a computable observed-population map whose residuals are polynomial-trigonometric functions of \((\Gamma_h,\Sigma_u,K_u)\).

\section{Step-by-step proof}
\subsection*{Supporting lemmas}
\begin{theorem}[Theorem 1: nesting and parent-corner reduction]\label{thm:parent-corner}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:leakage-class}, the contact sets are nested:
\[
\eta_1\le\eta_2\quad\Longrightarrow\quad
\mathcal Q_{\eta_1}(P)\subseteq \mathcal Q_{\eta_2}(P)\subseteq\mathcal Q_{\mathrm{LP}}(P),
\]
and therefore \(h_{\eta_1}(w;P)\le h_{\eta_2}(w;P)\le h_{\mathrm{LP}}(w;P)\) for every \(w\).  When \(\eta=0\), \(\mathcal L_0(Q)=\{0\}\) and \(\mathcal Q_0(P)\) is exactly the parent v1 independent-shock cumulant-diagonalizing SVAR/sign set.  If the LP side is restricted to the same \(\eta\)-contact set, the LP and \(\eta\)-SVAR support functions are equal for every \(w\).
\end{theorem}
\begin{proof}
Fix \(P\), \(w\), and \(\eta_1\le\eta_2\).  By Assumption~\ref{ass:leakage-class}, \(\mathcal L_{\eta_1}(Q)\subseteq\mathcal L_{\eta_2}(Q)\) for every rotation \(Q\).  Hence any \(Q\in\mathcal Q_{\eta_1}(P)\) has some \(\kappa\in\mathcal K_{\delta_4}(j)\) and \(L\in\mathcal L_{\eta_1}(Q)\) with \(K_u=D(Q,\kappa)+L\).  The same witness belongs to \(\mathcal L_{\eta_2}(Q)\), so \(Q\in\mathcal Q_{\eta_2}(P)\).  This proves \(\mathcal Q_{\eta_1}(P)\subseteq\mathcal Q_{\eta_2}(P)\).  The definition of \(\mathcal Q_\eta(P)\) includes the sign-zero condition \(Q\in\mathcal Q_{\mathrm{LP}}(P)\), so \(\mathcal Q_{\eta_2}(P)\subseteq\mathcal Q_{\mathrm{LP}}(P)\).  Taking suprema of the same real-valued report \(\theta_w\) over nested feasible sets gives \(h_{\eta_1}(w;P)\le h_{\eta_2}(w;P)\le h_{\mathrm{LP}}(w;P)\), with the stated empty-set convention.  At \(\eta=0\), Assumption~\ref{ass:leakage-class} gives \(\mathcal L_0(Q)=\{0\}\), so contact requires \(K_u=D(Q,\kappa)\) for an admissible separated \(\kappa\); that is precisely exact structural-basis fourth-cumulant diagonalization plus the common sign-zero restrictions.  Finally, if the LP report is itself restricted to \(\mathcal Q_\eta(P)\), both reports optimize \(\theta_w\) over the identical feasible set, so their support functions are equal for every \(w\).
\end{proof}

\subsubsection*{Proof of Conjecture 1}
\begin{proof}
Write the pure diagonal coordinate map as
\[
\bar\kappa(Q;P)=\bigl(K^Q_{1111},\ldots,K^Q_{nnnn}\bigr).
\]
Define the extended residual radius
\[
\rho(Q;P)=
\begin{cases}
\|r_4(Q,\bar\kappa(Q;P);P)\|_{\mathrm{off}},
& \bar\kappa(Q;P)\in\mathcal K_{\delta_4}(j),\\
+\infty,
& \bar\kappa(Q;P)\notin\mathcal K_{\delta_4}(j).
\end{cases}
\]
By the coordinate equivalence in the formal setup, together with Assumptions~\ref{ass:cumulants}, \ref{ass:separated-target}, and \ref{ass:leakage-class},
\[
Q\in\mathcal Q_\eta(P)
\quad\Longleftrightarrow\quad
Q\in\mathcal Q_{\mathrm{LP}}(P)\ \text{and}\ \rho(Q;P)\le\eta .
\]
Indeed, \(d_4(Q,\kappa;P)=0\) fixes \(\kappa=\bar\kappa(Q;P)\), and the leakage tensor \(L\) can absorb exactly the off-diagonal residual coordinates whose Euclidean norm is at most \(\eta\).

Assumption~\ref{ass:sign-zero} makes \(\mathcal Q_{\mathrm{LP}}(P)\) a nonempty compact subset of \(O(n)\).  Assumptions~\ref{ass:finite-var} and \ref{ass:normalization} make \(Q\mapsto\theta_w(Q)\) continuous, so
\[
\mathcal M_w(P)=\arg\max_{Q\in\mathcal Q_{\mathrm{LP}}(P)}\theta_w(Q)
\]
is nonempty and compact.  For each finite \(\eta\), the set \(\mathcal Q_\eta(P)\) is closed in \(\mathcal Q_{\mathrm{LP}}(P)\): the maps \(Q\mapsto\bar\kappa(Q;P)\) and \(Q\mapsto r_4(Q,\bar\kappa(Q;P);P)\) are continuous, \(\mathcal K_{\delta_4}(j)\) is closed, and the leakage ball is closed by Assumption~\ref{ass:leakage-class}.  Hence \(\mathcal Q_\eta(P)\) is compact whenever it is nonempty.

The first key equivalence is
\[
h_{\mathrm{LP}}(w;P)=h_\eta(w;P)
\quad\Longleftrightarrow\quad
\mathcal M_w(P)\cap\mathcal Q_\eta(P)\ne\emptyset .
\]
If the intersection is nonempty, some \(Q^\star\in\mathcal Q_\eta(P)\) satisfies \(\theta_w(Q^\star)=h_{\mathrm{LP}}(w;P)\), so \(h_\eta(w;P)\ge h_{\mathrm{LP}}(w;P)\).  Theorem~\ref{thm:parent-corner} gives \(\mathcal Q_\eta(P)\subseteq\mathcal Q_{\mathrm{LP}}(P)\), hence \(h_\eta(w;P)\le h_{\mathrm{LP}}(w;P)\), and equality follows.  Conversely, if \(h_\eta(w;P)=h_{\mathrm{LP}}(w;P)\) and \(\mathcal Q_\eta(P)\ne\emptyset\), compactness gives \(Q_\eta^\star\in\mathcal Q_\eta(P)\) with
\[
\theta_w(Q_\eta^\star)=h_\eta(w;P)=h_{\mathrm{LP}}(w;P).
\]
Thus \(Q_\eta^\star\in\mathcal M_w(P)\cap\mathcal Q_\eta(P)\).

Now define
\[
S_w(P)=\{\eta'\ge0:\mathcal M_w(P)\cap\mathcal Q_{\eta'}(P)\ne\emptyset\}.
\]
Using the residual-radius representation,
\[
S_w(P)=\{\eta'\ge0:\inf_{Q\in\mathcal M_w(P)}\rho(Q;P)\le \eta'\}.
\]
The extended function \(\rho(\cdot;P)\) is lower semicontinuous on the compact set \(\mathcal M_w(P)\), because it is continuous on the closed separated-cumulant region and equals \(+\infty\) off that region.  Therefore the infimum is attained when finite.  With the convention that \(\inf\emptyset=+\infty\),
\[
\eta_w^*(P)
=\inf S_w(P)
=\min_{Q\in\mathcal M_w(P)}\rho(Q;P)
\]
in the extended real line, and \(S_w(P)=[\eta_w^*(P),\infty)\) when the minimum is finite, while \(S_w(P)=\emptyset\) when it is infinite.  Combining this description of \(S_w(P)\) with the preceding support-equality equivalence proves
\[
h_{\mathrm{LP}}(w;P)=h_\eta(w;P)
\quad\Longleftrightarrow\quad
\eta\ge\eta_w^*(P)
\]
for every finite \(\eta\) with \(\mathcal Q_\eta(P)\ne\emptyset\).

If \(\eta<\eta_w^*(P)\), then \(\mathcal M_w(P)\cap\mathcal Q_\eta(P)=\emptyset\).  Since \(\mathcal Q_\eta(P)\) is compact and nonempty by Assumption~\ref{ass:contact-nonempty} for the finite comparison under discussion, \(h_\eta(w;P)\) is attained.  If the attained value were \(h_{\mathrm{LP}}(w;P)\), the maximizer would belong to \(\mathcal M_w(P)\cap\mathcal Q_\eta(P)\), a contradiction.  Thus
\[
\Delta_w^\eta(P)=h_{\mathrm{LP}}(w;P)-h_\eta(w;P)>0 .
\]
If \(\eta\ge\eta_w^*(P)\), choose \(Q^\star\in\mathcal M_w(P)\cap\mathcal Q_\eta(P)\).  By the definition of \(\mathcal Q_\eta(P)\), there is a separated diagonal cumulant vector \(\kappa^\star\in\mathcal K_{\delta_4}(j)\) and a leakage tensor \(L^\star\in\mathcal L_\eta(Q^\star)\) such that
\[
K_u=D(Q^\star,\kappa^\star)+L^\star .
\]
The same \(Q^\star\) attains \(\theta_w(Q^\star)=h_{\mathrm{LP}}(w;P)\), proving the stated attainability by a rotation whose fourth cumulants match \(K_u\) up to allowed co-kurtosis leakage.

It remains to prove that the positive finite frontier occurs on a nonempty open semi-algebraic class.  Use the two-shock center from the refutation attempt:
\[
n=2,\quad j=1,\quad \Sigma_u=I_2,\quad
\theta_w(Q)=e_1^\transpose Qe_1,\quad
K_u^0=4\delta_4\,v_1^{\otimes4}+\delta_4\,v_2^{\otimes4},
\]
where \(v_1=(\cos(\pi/6),\sin(\pi/6))^\transpose\) and \(v_2=(-\sin(\pi/6),\cos(\pi/6))^\transpose\), and take \(A\) and \(Z\) empty.  Assumptions~\ref{ass:finite-var}--\ref{ass:leakage-class} hold, for example, for a stable finite-order VAR with these population response rows and cumulants.  Assumption~\ref{ass:generic-exposed} holds because the report is nonconstant and exposes only the two completions whose first column is \(e_1\).  Assumption~\ref{ass:regular-frontier} is satisfied at the center because the exposed face is zero-dimensional and the boundary condition is the scalar closed inequality \(\rho(Q;P)\le\eta\) at an isolated support maximizer.

At this center, the calculation in the refutation attempt gives
\[
\eta_w^*(P^0)=\rho(I_2;P^0)\in(0,\infty).
\]
The lower bound is strict because \(K^{I_2}_{1112}=\delta_4cs(4c^2-s^2)>0\).  The upper bound is finite because the pure diagonal coordinates at the LP maximizer lie in \(\mathcal K_{\delta_4}(1)\).  Small perturbations of \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,w)\) preserve the strict inequalities
\[
\bar\kappa_1(Q_{\mathrm{LP}};P)>\delta_4,\qquad
|\bar\kappa_1(Q_{\mathrm{LP}};P)-\bar\kappa_2(Q_{\mathrm{LP}};P)|>\delta_4,\qquad
\rho(Q_{\mathrm{LP}};P)>0,
\]
where \(Q_{\mathrm{LP}}\) is an LP support maximizer on each component.  They also preserve nonflat exposure of the LP support face and the regular isolated-boundary condition after removing the lower-dimensional algebraic exceptional set named in Assumption~\ref{ass:regular-frontier}.  These strict conditions define a nonempty open class containing the center.

The same class is semi-algebraic.  Orthogonality, sign-zero restrictions, exposed-face equations \(\theta_w(Q)=h_{\mathrm{LP}}(w;P)\), diagonal contact, separated cumulants, and residual inequalities are polynomial equalities and inequalities in the entries of \((Q,\kappa,t)\), the observed coefficients, and an auxiliary symmetric square root \(S\) constrained by \(S=S^\transpose\), \(S^2=\Sigma_u\), and positive principal minors.  The statement that the displayed strict inequalities hold at an exposed maximizer can be written with auxiliary variables for \(Q_{\mathrm{LP}}\), \(S\), and the support value; eliminating those variables preserves semi-algebraicity by the Tarski-Seidenberg projection theorem.  Hence on a nonempty open semi-algebraic class of observable objects, \(\eta_w^*(P)\) is positive and finite.  This proves the final phase-transition claim.
\end{proof}

\subsubsection*{Proof of Conjecture 2}
\begin{proof}
Fix \(P\), \(w\), and a component \(c\in\{+,-\}\).  By Assumptions~\ref{ass:finite-var} and \ref{ass:normalization}, \(b_j(Q_c(\varphi))=\Sigma_u^{1/2}Q_c(\varphi)e_j\) is an affine trigonometric function of \((\cos\varphi,\sin\varphi)\).  Therefore
\[
\theta_w(Q_c(\varphi))
=w^\transpose\left(e_y^\transpose\Gamma_h b_j(Q_c(\varphi))\right)_{h=0}^H
=a_{w,c}\cos\varphi+b_{w,c}\sin\varphi .
\]
If \((a_{w,c},b_{w,c})\ne0\), write \(\rho_{w,c}=(a_{w,c}^2+b_{w,c}^2)^{1/2}\) and choose \(\varphi_{w,c}\) with \(a_{w,c}=\rho_{w,c}\cos\varphi_{w,c}\) and \(b_{w,c}=\rho_{w,c}\sin\varphi_{w,c}\), giving \(\theta_w(Q_c(\varphi))=\rho_{w,c}\cos(\varphi-\varphi_{w,c})\).  If \((a_{w,c},b_{w,c})=(0,0)\), the displayed linear form remains valid and every feasible angle is an LP maximizer on that component.

By Assumption~\ref{ass:sign-zero}, \(I_c\) is the closed angular feasible set cut out by \(A\psi_j(Q_c(\varphi))\ge0\) and \(Z\psi_j(Q_c(\varphi))=0\).  Since each component is compact and the constraints are closed, every nonempty \(I_c\) has a nonempty compact maximizer set \(M_{w,c}\).  Assumption~\ref{ass:generic-exposed} excludes the only problematic case for strict statements, namely a positive-dimensional support face on which the mismatch changes while the report is constant.

Next characterize component contact.  By the formal setup and Assumptions~\ref{ass:cumulants}--\ref{ass:leakage-class}, \(Q_c(\varphi)\in\mathcal Q_\eta(P)\) if and only if \(\varphi\in I_c\) and there exists \(\kappa\in\mathcal K_{\delta_4}(j)\) such that
\[
d_4(Q_c(\varphi),\kappa;P)=0,
\qquad
\|r_4(Q_c(\varphi),\kappa;P)\|_{\mathrm{off}}\le\eta .
\]
The implication from left to right is just the coordinate definition of \(m_\eta(Q;P)=0\): the leakage tensor can absorb exactly the off-diagonal residual and, by definition of \(\mathcal L_\eta(Q)\), cannot absorb any pure-diagonal residual.  The reverse implication holds by constructing the leakage tensor whose structural-basis off-diagonal coordinates equal \(r_4(Q_c(\varphi),\kappa;P)\) and whose pure diagonal coordinates are zero.

It follows that the first leakage radius at which the component support face meets the cumulant contact set is
\[
\inf\{\eta\ge0:
\exists \varphi\in M_{w,c},\ \exists\kappa\in\mathcal K_{\delta_4}(j)
\text{ with }d_4(Q_c(\varphi),\kappa;P)=0
\text{ and }\|r_4(Q_c(\varphi),\kappa;P)\|_{\mathrm{off}}\le\eta\}.
\]
If the displayed diagonal-contact feasibility condition is empty, no finite \(\eta\) can create contact at the component support face, proving the \(+\infty\) branch.  Otherwise the infimum equals the minimum of the off-diagonal residual norm over that feasible set.  Indeed, \(M_{w,c}\) is compact, \(d_4\) and \(r_4\) vary continuously in \(\varphi\), and \(d_4(Q_c(\varphi),\kappa;P)=0\) pins \(\kappa\) to the two observed diagonal structural-basis cumulants at \(\varphi\).  Thus there is no escaping sequence in the unbounded ambient \(\kappa\)-space, and the feasible residual image is compact.

The global statement is the same calculation over \(O(2)=O_+(2)\cup O_-(2)\).  Assumption~\ref{ass:normalization} fixes the shock label after sign and permutation normalization, and Assumption~\ref{ass:two-shock} includes both components.  For a fixed labelled shock, the labelled column \(Q_c(\varphi)e_j\) has the same image on the rotation and reflection components after angular relabelling.  Hence the report \(\theta_w\) and the sign-zero feasibility constraints have the same exposed support value on the two components, while the fourth-order reflection changes only signs or orderings of off-diagonal coordinates and preserves the norm used in Assumption~\ref{ass:leakage-class}.  Taking the minimum over the two component critical values is therefore exactly the definition
\[
\eta_w^*(P)=
\inf\{\eta'\ge0:\mathcal M_w(P)\cap\mathcal Q_{\eta'}(P)\ne\emptyset\}.
\]

Finally set \(\eta=0\).  By Theorem~\ref{thm:parent-corner}, \(\mathcal Q_0(P)\subseteq\mathcal Q_{\mathrm{LP}}(P)\) and \(\mathcal Q_0(P)\) is precisely the parent independent-shock cumulant-diagonalizing sign set.  Thus \(h_{\mathrm{LP}}(w;P)=h_0(w;P)\) holds if and only if some maximizer of \(\theta_w\) over \(\mathcal Q_{\mathrm{LP}}(P)\) belongs to \(\mathcal Q_0(P)\), which is exactly the condition that an LP support angle is a parent contact angle with \(d_4=0\) and \(r_4=0\).

If no exposed LP support angle is a parent contact angle, let \(\varphi^\star\) be an exposed support angle and let \(\varphi^0\) be a parent contact angle attaining \(h_0(w;P)\) on the same connected feasible angular interval.  Write \(\alpha=|\varphi^\star-\varphi_w|\) and \(d_w=|\varphi^0-\varphi^\star|\) along the monotone branch of the interval moving away from the report phase.  Since \(\varphi^\star\) maximizes \(\rho_w\cos(\varphi-\varphi_w)\) over the feasible interval, \(0\le\alpha\le\alpha+d_w\le\pi\).  Therefore
\[
\begin{aligned}
h_{\mathrm{LP}}(w;P)-h_0(w;P)
&\ge \rho_w\{\cos\alpha-\cos(\alpha+d_w)\}\\
&=2\rho_w\sin(d_w/2)\sin(\alpha+d_w/2)\\
&\ge 2\rho_w\sin^2(d_w/2)
=\rho_w(1-\cos d_w),
\end{aligned}
\]
which is the stated parent-corner witness.  The case \(\rho_w=0\) gives the limiting zero lower bound and no strict support gap, as expected.
\end{proof}

\section{Sanity checks}
\paragraph{Sanity check for Conjecture 1.}
At the parent independent-shock corner \(\eta=0\), Theorem~\ref{thm:parent-corner} identifies \(\mathcal Q_0(P)\) with the exact fourth-cumulant diagonalizing SVAR/sign set.  The frontier theorem reduces to
\[
h_{\mathrm{LP}}(w;P)=h_0(w;P)
\quad\Longleftrightarrow\quad
\mathcal M_w(P)\cap\mathcal Q_0(P)\ne\emptyset
\quad\Longleftrightarrow\quad
\eta_w^*(P)=0.
\]
Thus the parent corner has no LP/SVAR support gap exactly when an LP support maximizer already satisfies the independent-shock cumulant contact restriction.  If the LP side is restricted to the same \(\eta\)-contact set, both reports optimize \(\theta_w\) over the identical feasible set, and Theorem~\ref{thm:parent-corner} again gives equality for every \(w\).  This is the common-restriction special case: the gap is created by optimizing over the larger LP/sign relaxation, not by the response-row definition of \(\psi_j(Q)\).

\paragraph{Sanity check for Conjecture 2: parent contact at the LP support angle.}
Suppose the LP support angle on a component is unique, \(\varphi^\star=\varphi_w\in I_c\), and the observed cumulants satisfy \(d_4(Q_c(\varphi^\star),\kappa^\star;P)=0\) and \(r_4(Q_c(\varphi^\star),\kappa^\star;P)=0\) for some \(\kappa^\star\in\mathcal K_{\delta_4}(j)\).  The formula gives \(\eta_{w,c}^*(P)=0\).  By Theorem~\ref{thm:parent-corner}, the parent contact set is a subset of the LP/sign set, and because it contains the LP maximizer, \(h_0(w;P)=h_{\mathrm{LP}}(w;P)=\rho_w\).  This is exactly the parent independent-shock equality case.

If instead the nearest parent contact angle is \(\varphi^\star+d\) with \(0<d\le\pi\) and \(\varphi^\star=\varphi_w\), then \(h_0(w;P)\le\rho_w\cos d\), so the support gap is at least \(\rho_w(1-\cos d)\).  The displayed lower bound is therefore sharp in the interior-support corner.

\section{Counterexample or minimality check}
\paragraph{Refutation attempt before proof for Conjecture 1.}
The exact-identification primitives were checked first against the locked parameters.  The three-node SWIG primitive does not instantiate: the observable input is the finite-dimensional VAR/cumulant tuple \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\), there is no treatment node \(A\), no adjustment covariate \(X\), and no do-calculus functional whose equality to a potential-outcome target could be falsified.  The finite-support overlap primitive also has no conditioning stratum to shrink, and the do-calculus rule trace has no intervention expression on which a rule can fail.  These attempts therefore produce no admissible witness inside the proposal's locked support-function substrate.

The smallest compatible refutation search is the two-shock rotation search.  Set \(n=2\), \(j=1\), \(\Sigma_u=I_2\), take no sign or zero rows, and choose a report direction with
\[
\theta_w(Q)=e_1^\transpose Qe_1 .
\]
Let \(\alpha=\pi/6\), \(c=\cos\alpha\), \(s=\sin\alpha\),
\[
v_1=(c,s)^\transpose,\qquad v_2=(-s,c)^\transpose,
\]
and let
\[
K_u=4\delta_4\,v_1^{\otimes4}+\delta_4\,v_2^{\otimes4}.
\]
The LP/sign problem maximizes \(e_1^\transpose Qe_1\) over \(O(2)\), so \(h_{\mathrm{LP}}(w;P)=1\), attained by the two orthogonal completions whose first column is \(e_1\).  At either LP support maximizer, the pure diagonal cumulant coordinates are
\[
\bar\kappa_1=4\delta_4c^4+\delta_4s^4,\qquad
\bar\kappa_2=4\delta_4s^4+\delta_4c^4,
\]
and
\[
\bar\kappa_1-\bar\kappa_2
=3\delta_4(c^4-s^4)
=\frac{3}{2}\delta_4 .
\]
Thus \((\bar\kappa_1,\bar\kappa_2)\in\mathcal K_{\delta_4}(1)\).  The off-diagonal fourth-cumulant coordinate
\[
K^I_{1112}
=4\delta_4c^3s-\delta_4s^3c
=\delta_4cs(4c^2-s^2)
\]
is strictly positive, so the LP support maximizer does not belong to \(\mathcal Q_0(P)\) but does belong to \(\mathcal Q_\eta(P)\) once \(\eta\) reaches its off-diagonal residual norm.  The tilted basis \(Q=[v_1\ v_2]\) has exact diagonal fourth-cumulant contact at \(\eta=0\), so the contact sets are nonempty.  This bounded search therefore finds no violation of the conjectured frontier: it produces \(\eta_w^*(P)\in(0,\infty)\), equality for all \(\eta\ge\eta_w^*(P)\), and strict inequality for all feasible \(\eta<\eta_w^*(P)\).  The general proof above explains why this is forced by closed nested contact sets, not by a special trigonometric accident.

\paragraph{Minimality check for Conjecture 1.}
Closedness of the leakage class is essential for the boundary equality.  If Assumption~\ref{ass:leakage-class} were changed so that the off-diagonal leakage ball were open, \(\|r_4(Q,\kappa;P)\|_{\mathrm{off}}<\eta\), the two-shock center above would have
\[
S_w(P^0)=(\eta_w^*(P^0),\infty)
\]
instead of \(S_w(P^0)=[\eta_w^*(P^0),\infty)\).  Then the infimum defining \(\eta_w^*(P^0)\) would be unchanged, but the LP support maximizer would not be feasible at the boundary radius itself, so
\[
h_{\mathrm{LP}}(w;P^0)\ne h_{\eta_w^*(P^0)}(w;P^0)
\]
despite \(\eta=\eta_w^*(P^0)\).  This shows why the closed leakage ball and compact support-face attainment assumptions are not cosmetic regularity conditions: they are exactly what turns the infimum diagnostic into a sharp equality frontier.

\paragraph{Refutation attempt before proof for Conjecture 2.}
The shared setup locks this conjecture as a PartialID/support-function structural time-series problem, even though the run metadata names the exact-ID cluster.  The SWIG, overlap, and do-calculus refutation primitives therefore have no treatment, outcome, or adjustment variables to instantiate.  The corresponding finite-dimensional refutation search is over the two angular components of \(O(2)\).

First, consider a candidate LP support angle \(\varphi^\star\) for which no \(\kappa\in\mathcal K_{\delta_4}(j)\) satisfies \(d_4(Q_c(\varphi^\star),\kappa;P)=0\).  This does not refute the formula: by Assumption~\ref{ass:leakage-class}, leakage tensors have zero pure diagonal coordinates, so changing \(\eta\) can never repair pure-diagonal failure.  The component critical value is correctly \(+\infty\).

Second, try to produce a mismatch by putting a small residual on the reflection component and a large residual on the rotation component.  In the two-shock parametrization this does not produce a witness.  The labelled column \(Q_c(\varphi)e_j\) traces the same unit circle on the two components, up to the fixed sign normalization in Assumption~\ref{ass:normalization}.  Since \(\theta_w\), \(A\psi_j\), and \(Z\psi_j\) depend only on that labelled column, the LP support value is represented on both components after the angular relabelling.  The reflection only signed-permutes off-diagonal fourth-cumulant coordinates involving the non-target column, preserving the pure-diagonal equations and the Euclidean off-diagonal norm.  Hence a smaller reflection residual at a non-exposed report value cannot occur inside the locked two-shock geometry.

Third, in the parent corner, setting \(\eta=0\) forces \(r_4=0\) by Assumption~\ref{ass:leakage-class}.  A searched witness with \(r_4\ne0\) is infeasible, while a witness with \(r_4=0\) and \(d_4=0\) is exactly a parent contact angle.  Thus the bounded angular search finds no counterexample to the conjectured formula, and the proof above verifies the claim.

\paragraph{Minimality check for Conjecture 2: pure-diagonal contact cannot be dropped.}
The condition \(d_4(Q_c(\varphi),\kappa;P)=0\) is essential.  Consider a two-shock population and an LP support angle \(\varphi^\star\) for which every off-diagonal structural-basis cumulant coordinate vanishes, so \(r_4(Q_c(\varphi^\star),\kappa;P)=0\), but the pure diagonal coordinates are equal:
\[
K^{Q_c(\varphi^\star)}_{1111}
=K^{Q_c(\varphi^\star)}_{2222}.
\]
Then \(d_4=0\) forces \(\kappa_1=\kappa_2\), which violates the target separation requirement in \(\mathcal K_{\delta_4}(j)\) for every \(\delta_4>0\).  If one minimized only the off-diagonal residual, the reported leakage radius would be \(0\).  Under the actual assumptions, no finite off-diagonal leakage radius can repair the failed pure-diagonal separation, because Assumption~\ref{ass:leakage-class} allows leakage only in off-diagonal coordinates.  Thus the diagonal-contact and separated-cumulant clauses are not regularity decoration; they are necessary for the formula to define the same higher-cumulant SVAR contact set.

\paragraph{Substrate audit record.}
\texttt{bypass-justified}: the declaration-level audit did not surface reusable exact-identification adjustment primitives for this theorem, and the shared setup is algebraic over \(O(2)\) support functions and fourth-cumulant coordinates rather than an SCM adjustment formula.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
  \item \(\Gamma_h\): typed signature \(\R^{d_y\times n}\) for \(h=0,\ldots,H\); role: observed population response rows entering \(\psi_j(Q)\); dependencies: Assumption~\ref{ass:finite-var}.
  \item \(\Sigma_u\): typed signature symmetric positive definite \(n\times n\) matrix; role: innovation covariance and source of \(B(Q)=\Sigma_u^{1/2}Q\); dependencies: Assumptions~\ref{ass:finite-var} and \ref{ass:normalization}.
  \item \(K_u\): typed signature symmetric fourth-order tensor on \(\R^n\); role: observed fourth cumulant tensor to be decomposed into diagonal structural cumulants plus leakage; dependencies: Assumption~\ref{ass:cumulants}.
  \item \(O(n)\): typed signature set of real \(n\times n\) matrices satisfying \(Q^\transpose Q=I_n\); role: compact rotation/reflection parameter space; dependencies: Assumption~\ref{ass:normalization}.
  \item \(B(Q)\): typed signature \(O(n)\to\R^{n\times n}\), \(Q\mapsto\Sigma_u^{1/2}Q\); role: structural impact matrix; dependencies: \(\Sigma_u\succ0\).
  \item \(\psi_j(Q)\): typed signature \(O(n)\to\R^{H+1}\); role: labelled structural impulse-response path; dependencies: \(\Gamma_h\), \(B(Q)\), labelled shock \(j\).
  \item \(\theta_w(Q)\): typed signature \(O(n)\to\R\); role: scalar support report \(w^\transpose\psi_j(Q)\); dependencies: \(w\in\R^{H+1}\) and \(\psi_j\).
  \item \(\mathcal Q_{\mathrm{LP}}(P)\): typed signature subset of \(O(n)\); role: LP/sign outer feasible set; dependencies: \(A\psi_j(Q)\ge0\), \(Z\psi_j(Q)=0\), Assumption~\ref{ass:sign-zero}.
  \item \(D(Q,\kappa)\): typed signature \(O(n)\times\R^n\to\) symmetric fourth-order tensors; role: pure diagonal structural fourth-cumulant component; dependencies: \(b_k(Q)\) and \(\kappa\).
  \item \(\mathcal K_{\delta_4}(j)\): typed signature closed subset of \(\R^n\); role: separated target cumulant admissible set; dependencies: \(\delta_4>0\), Assumption~\ref{ass:separated-target}.
  \item \(K^Q_{abcd}\): typed signature \(O(n)\to\R\) for each fourth-order index tuple; role: structural-basis cumulant coordinate; dependencies: \(K_u\) and \(B(Q)^{-\transpose}\).
  \item \(r_4(Q,\kappa;P)\): typed signature \(O(n)\times\R^n\to\R^{|\mathcal I_{\mathrm{off}}|}\); role: off-diagonal residual whose norm defines the leakage radius; dependencies: \(K^Q_{abcd}\), \(\kappa\).
  \item \(d_4(Q,\kappa;P)\): typed signature \(O(n)\times\R^n\to\R^n\); role: pure-diagonal residual that leakage cannot absorb; dependencies: \(K^Q_{aaaa}\), \(\kappa\).
  \item \(\mathcal L_\eta(Q)\): typed signature closed convex subset of symmetric fourth-order tensors; role: bounded off-diagonal co-kurtosis leakage class; dependencies: Assumption~\ref{ass:leakage-class}.
  \item \(m_\eta(Q;P)\): typed signature \(O(n)\to[0,\infty]\); role: mismatch functional whose zero set defines higher-cumulant contact; dependencies: \(D(Q,\kappa)\), \(\mathcal K_{\delta_4}(j)\), \(\mathcal L_\eta(Q)\).
  \item \(\mathcal Q_\eta(P)\): typed signature subset of \(\mathcal Q_{\mathrm{LP}}(P)\); role: leakage-adjusted higher-cumulant SVAR/sign contact set; dependencies: \(m_\eta(Q;P)=0\).
  \item \(h_{\mathrm{LP}}(w;P)\) and \(h_\eta(w;P)\): typed signature real extended-valued functionals of \(P,w\); role: support functions over \(\mathcal Q_{\mathrm{LP}}(P)\) and \(\mathcal Q_\eta(P)\); dependencies: \(\theta_w\) and compactness/nonempty conventions.
  \item \(\mathcal M_w(P)\): typed signature compact subset of \(\mathcal Q_{\mathrm{LP}}(P)\); role: exposed LP support face; dependencies: continuity of \(\theta_w\) and compactness of \(\mathcal Q_{\mathrm{LP}}(P)\).
  \item \(\eta_w^*(P)\): typed signature extended nonnegative real functional; role: first leakage radius at which \(\mathcal M_w(P)\) intersects \(\mathcal Q_\eta(P)\); dependencies: \(\mathcal M_w(P)\), \(\mathcal Q_\eta(P)\).
  \item \(\rho(Q;P)\): typed signature \(O(n)\to[0,\infty]\); role: extended residual radius used to rewrite \(\eta_w^*(P)=\min_{Q\in\mathcal M_w(P)}\rho(Q;P)\); dependencies: \(\bar\kappa(Q;P)\), \(r_4\), \(\mathcal K_{\delta_4}(j)\).
  \item \(Q_c(\varphi)\): typed signature \(\{+,-\}\times\R\to O(2)\); role: angular parameterization of the two components in the two-shock specialization; dependencies: Assumption~\ref{ass:two-shock}.
  \item \(I_c\) and \(M_{w,c}\): typed signatures closed subsets of the angular circle; role: component LP/sign feasible angles and component support angles; dependencies: \(Q_c(\varphi)\), \(A\), \(Z\), \(\theta_w\).
  \item \(\eta_{w,c}^*(P)\): typed signature extended nonnegative real per component; role: component minimum off-diagonal residual over exposed pure-diagonal contact angles; dependencies: \(M_{w,c}\), \(d_4=0\), \(r_4\), \(\mathcal K_{\delta_4}(j)\).
  \item Tarski-Seidenberg projection theorem: typed signature preservation of semi-algebraicity under coordinate projection; role: certifies the nonempty open semi-algebraic class in Theorem~\ref{thm:critical-leakage-frontier}; dependencies: polynomial equalities and inequalities in observed coefficients and auxiliary variables.
\end{itemize}

\section{Conclusion and references}
Conjecture 1 (critical-leakage-frontier) is confirmed; Conjecture 1 is confirmed: under Assumptions~\ref{ass:finite-var}--\ref{ass:regular-frontier}, the equality \(h_{\mathrm{LP}}(w;P)=h_\eta(w;P)\) holds exactly for \(\eta\ge\eta_w^*(P)\), and the critical radius is positive and finite on a nonempty open semi-algebraic class.

Conjecture 2 (two-shock-formula) is confirmed; The two-shock critical leakage radius is the minimum off-diagonal fourth-cumulant residual over LP support angles satisfying pure-diagonal contact, with the global value obtained over both components.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AriasRubioRamirezWaggoner2018}
Arias, J. E., J. F. Rubio-Ramirez, and D. F. Waggoner (2018).  Inference based on structural vector autoregressions identified with sign and zero restrictions: theory and applications.  \emph{Econometrica} 86(2), 685--720.

\bibitem{BaumeisterHamilton2015}
Baumeister, C. and J. D. Hamilton (2015).  Sign restrictions, structural vector autoregressions, and useful prior information.  \emph{Econometrica} 83(5), 1963--1999.

\bibitem{DrautzburgWright2023}
Drautzburg, T. and J. H. Wright (2023).  Refining set-identification in VARs through independence.  \emph{Journal of Econometrics} 233(2), 443--465.

\bibitem{GourierouxMonfortRenne2017}
Gourieroux, C., A. Monfort, and J.-P. Renne (2017).  Statistical inference for independent component analysis: application to structural VAR models.  \emph{Journal of Econometrics} 196(1), 111--126.

\bibitem{Guay2021}
Guay, A. (2021).  Identification of structural vector autoregressions through higher unconditional moments.  \emph{Journal of Econometrics} 225(1), 27--46.

\bibitem{HoeschLeeMesters2024}
Hoesch, L., J. Lee, and G. Mesters (2024).  Locally robust inference for non-Gaussian SVARs.  Working paper.

\bibitem{Jorda2005}
Jorda, O. (2005).  Estimation and inference of impulse responses by local projections.  \emph{American Economic Review} 95(1), 161--182.

\bibitem{LanneLiuLuoto2026}
Lanne, M., K. Liu, and J. Luoto (2026).  Non-Gaussian structural vector autoregressions with dependent shocks.  Forthcoming or working paper.

\bibitem{LanneLuoto2021}
Lanne, M. and J. Luoto (2021).  GMM estimation of non-Gaussian structural vector autoregression.  \emph{Journal of Business \& Economic Statistics} 39(1), 69--81.

\bibitem{LanneMeitzSaikkonen2017}
Lanne, M., M. Meitz, and P. Saikkonen (2017).  Identification and estimation of non-Gaussian structural vector autoregressions.  \emph{Journal of Econometrics} 196(2), 288--304.

\bibitem{MontielOleaPlagborgMollerQian2022}
Montiel Olea, J. L., M. Plagborg-Moller, and E. Qian (2022).  SVAR identification from higher moments: has the simultaneous causality problem been solved?  \emph{AEA Papers and Proceedings} 112, 481--485.

\bibitem{PlagborgMollerWolf2021}
Plagborg-Moller, M. and C. K. Wolf (2021).  Local projections and VARs estimate the same impulse responses.  \emph{Econometrica} 89(2), 955--980.

\bibitem{RubioRamirezWaggonerZha2010}
Rubio-Ramirez, J. F., D. F. Waggoner, and T. Zha (2010).  Structural vector autoregressions: theory of identification and algorithms for inference.  \emph{Review of Economic Studies} 77(2), 665--696.

\bibitem{Tarski1951}
Tarski, A. (1951).  \emph{A Decision Method for Elementary Algebra and Geometry}.  University of California Press.
\end{thebibliography}

\end{document}
