% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_policy\_regret\_ch\_sensitivity, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_policy\_regret\_ch\_sensitivity} / \texttt{v1}%
  \\ \large\textit{Policy-score calibration frontiers across partial-$R^2$, marginal-sensitivity, and covariate-shift regret bounds}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form partial-identification proposal with locked tuple
\[
  (\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional})
  =
  (\texttt{pid\_policy\_regret\_ch\_sensitivity},\texttt{v1},P,\theta_{\pi,\pi_0},
  \mathcal C_{\kappa}\cup\mathcal M_{\Gamma}\cup\mathcal S_{\delta},B).
\]
Here $P$ is the observed law of $O=(X,A,Y)$ with binary action $A\in\{0,1\}$, bounded outcome $Y\in[\ell,u]$, known nominal propensity $e_0(a\mid X)\in[\underline e,1-\underline e]$, and a finite policy class $\Pi$ containing a status-quo rule $\pi_0$.  The parameter is the policy regret contrast
\[
  \theta_{\pi,\pi_0}=\E[Y(\pi_0)-Y(\pi)]
\]
under latent full-data laws compatible with $P$.  For each candidate policy $\pi$, the local policy score $W_{\pi}$ is the centered, bounded observed score that represents the first-order perturbation of $\theta_{\pi,\pi_0}$ under compatible latent confounding or target-population tilts.  The restriction $\mathcal C_{\kappa}$ is a Cinelli--Hazlett partial-$R^2$ budget represented locally as an $L^2(P)$ ellipsoid for mean-zero latent perturbations $h$: $\E h=0$ and $\E h^2\le \kappa^2$.  The restriction $\mathcal M_{\Gamma}$ is the marginal-sensitivity odds-ratio budget represented locally by mean-zero perturbations $h$ with $\|h\|_{\infty}\le b(\Gamma)$, where $b(1)=0$ and $b(\Gamma)$ is increasing.  The restriction $\mathcal S_{\delta}$ is a covariate-shift budget represented by mean-zero density tilts $g(X)$ with $\E g=0$ and $\E g^2\le\delta^2$.  The bounding functional $B_{\mathfrak A}(\pi)$ is the support-function regret penalty for ambiguity language $\mathfrak A\in\{\mathcal C_{\kappa},\mathcal M_{\Gamma},\mathcal S_{\delta}\}$; the proposed kernel concerns when there is, or is not, a positive scalar calibration among these $B_{\mathfrak A}$ values that preserves regret rankings over the active nonzero policy comparisons in $\Pi$.

\begin{abstract}
Sensitivity analyses for hidden confounding now use several incompatible languages: Cinelli--Hazlett partial-$R^2$ budgets, marginal-sensitivity odds-ratio budgets, and covariate-shift ambiguity sets.  This proposal asks when those languages can be calibrated to give the same robust policy-regret comparison over a finite offline policy class.  The routine piece is a support-function reduction: after local compatibility normalization, the three regret endpoints are different support functions of the same policy score.  The flagship conjecture is an observable all-pairs equivalence frontier for the local population criteria induced by the MSM robust-welfare objective in \citet{JinXuZhengZhou2025} and the covariate-shift policy-choice objective in \citet{AdjahoChristensen2025}: positive scalar bridges preserve all active robust-regret endpoints exactly when the finite policy-score matrix has a positive common scale across languages, equivalently vanishing cross-language $2\times2$ minors plus nonzero active columns.  Resolving the conjecture would tell policy-learning papers when a reported CH partial-$R^2$ sensitivity value can be a calibrated proxy for an MSM or covariate-shift regret curve, and when separate robustness curves are mathematically unavoidable.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Offline policy learning under hidden confounding is increasingly reported through sensitivity curves rather than through a single unconfoundedness assumption.  A practitioner may see a Cinelli--Hazlett robustness value in a regression analysis, a Kallus--Zhou or Zhao--Small--Bhattacharya marginal-sensitivity parameter in policy learning, and an Adjaho--Christensen covariate-shift radius in external-validity analysis.  These numbers are often interpreted informally as comparable amounts of ``robustness,'' but the underlying partial-identification problems constrain different latent objects.

\paragraph{The main finding (proposed).}
The proposed main result is Conjecture \ref{conj:calibration-frontier}: after reducing a policy-regret contrast to its local score $W_{\pi}$, exact positive scalar calibration across the partial-$R^2$, marginal-sensitivity, and covariate-shift languages is possible for the active policy comparisons exactly when the observable bridge-defect threshold $\tau_{\Pi_\ast}$ is zero.  The diagnostic compares the three score penalties $(\|W_{\pi}\|_2,D_1(W_{\pi}),\|M_{\pi}\|_2)$ for every active candidate policy and excludes the degenerate case in which one language has a zero column while another has positive penalties.  Away from the positive common-scale frontier, the proposed two-policy open-set witness is an internal sharpness lemma: it separates the CH penalty from the MSM or covariate-shift penalty, while Conjecture \ref{conj:calibration-frontier} supplies the additional nominal-regret perturbation needed to turn that penalty separation into different local population robust-regret rankings for the MSM robust-welfare criterion of \citet{JinXuZhengZhou2025} and the external-validity policy-choice criterion of \citet{AdjahoChristensen2025}.

\paragraph{What is new.}
The novelty kernel is not another robust policy learner and not a claim that one sensitivity parameter dominates another.  It is a theorem-level calibration boundary for policy regret: \citet{CinelliHazlett2020} calibrate omitted-variable bias by partial $R^2$, \citet{DiegertMastenPoirier2025} compare sensitivity parameters axiomatically, \citet{MastenPoirierRen2025} give a broad relaxation framework for unconfoundedness, \citet{SorianoBenMichaelBickelFellerPimentel2023} give interpretable sensitivity analysis for balancing weights, \citet{HuangPimentel2025} develop an $R^2$-parameterized variance-based sensitivity model for weighting estimators, \citet{ZhaoSmallBhattacharya2019} and \citet{KallusZhou2021} use odds-ratio propensity-weight ambiguity, and \citet{AdjahoChristensen2025} studies external validity under target-population shifts.  None gives the necessary and sufficient all-pairs policy-score diagnostic under which the same local robust-regret ordering survives translation between the MSM and covariate-shift population criteria after CH-style normalization.  The flagship epsilon-gap is the observable bridge-defect threshold $\tau_{\Pi_\ast}$: a policy class with two linearly independent centered scores can have equal variances but different centered absolute deviations or different covariate projections, so a CH partial-$R^2$ calibration cannot in general reproduce the robust-welfare ordering in \citet{JinXuZhengZhou2025} or the external-validity ordering in \citet{AdjahoChristensen2025}.

\paragraph{How it positions in the literature.}
This is a partial-identification and sensitivity-analysis proposal.  It sits between sharp hidden-confounding policy learning \citep{KallusZhou2021,JinXuZhengZhou2025}, marginal-sensitivity bounds \citep{ZhaoSmallBhattacharya2019,YadlowskyNamkoongBasuDuchiTian2022,DornGuoKallus2025,MastenPoirierRen2025}, interpretable and variance-based weighting sensitivity \citep{SorianoBenMichaelBickelFellerPimentel2023,HuangPimentel2025}, omitted-variable partial-$R^2$ sensitivity and parameter-comparison work \citep{CinelliHazlett2020,DiegertMastenPoirier2025}, and external-validity policy choice \citep{AdjahoChristensen2025,ChristensenConnault2023}.  The target is a population identified-set comparison, not an estimator or a panel regression identity.

\paragraph{Implications for the community.}
The concrete downstream consumer is robust policy learning under the marginal sensitivity model, especially the closed-form robust welfare criteria in \citet{JinXuZhengZhou2025}: the proposed frontier would say exactly when a CH-style robustness value can be used as a calibrated proxy for their MSM regret curve and when it cannot.  It also gives users of \citet{AdjahoChristensen2025} a diagnostic for whether external-validity robustness and hidden-confounding robustness are ranking the same policies.

\paragraph{How research benefits from the conclusion.}
Researchers should report the policy-score geometry behind a sensitivity value---rank-one, variance-only, absolute-deviation, or covariate-projection driven---before translating robustness claims across CH, MSM, and covariate-shift analyses.

\section{Related work}
\citet{CinelliHazlett2020} introduce the partial-$R^2$ omitted-variable-bias language and the robustness value; this proposal asks for the analogous calibration problem when the object is a policy-regret support function rather than a scalar regression coefficient.  \citet{DiegertMastenPoirier2025} are the closest sensitivity-parameter comparison paper because they give an axiomatic framework for choosing among omitted-variable sensitivity parameters; their comparison criterion is a covariate sampling distribution for scalar regression sensitivity, not an observable all-pairs frontier for robust policy rankings.  \citet{MastenPoirierRen2025} define a broad class of relaxations of unconfoundedness that includes the marginal sensitivity model and yields sharp bounds beyond average effects; their framework is a serious subsumption threat for pointwise effect-function bounds, but it does not isolate the finite policy-score threshold at which CH, MSM, and covariate-shift regret criteria agree.  \citet{SorianoBenMichaelBickelFellerPimentel2023} adapt interpretable sensitivity analysis to balancing-weight estimators; they are close because their workflow benchmarks a scalar amount of hidden confounding in a weighting problem, but they do not ask whether that scalar preserves rankings over a policy class.  \citet{HuangPimentel2025} introduce a variance-based weighting sensitivity model parameterized by an $R^2$ value and contrast it with marginal $L^\infty$ sensitivity; they are the closest calibration-adjacent prior art, but their object is a weighting-estimator interval, not a multi-policy regret frontier.  \citet{ZhaoSmallBhattacharya2019} define the marginal sensitivity model as an odds-ratio relaxation of no unmeasured confounding for IPW estimands; their model supplies the $\mathcal M_{\Gamma}$ side of the proposed bridge.  \citet{KallusZhou2021} formulate hidden-confounding policy learning as minimax regret over propensity-weight uncertainty sets, making them the closest policy-regret precursor.  \citet{YadlowskyNamkoongBasuDuchiTian2022} and \citet{DornGuoKallus2025} sharpen MSM partial-identification and estimation for treatment-effect bounds; they motivate why the support-function geometry should be sharp rather than a loose envelope.

\citet{JinXuZhengZhou2025} derive closed-form robust welfare criteria and asymptotic regret guarantees for policy learning under MSM; their criteria are the most direct consumer of a correct CH-to-MSM calibration theorem.  \citet{AdjahoChristensen2025} studies personalized policies that remain good under target-population shifts in characteristics and outcomes; this proposal isolates the covariate-score support function that such external-validity ambiguity shares with, or separates from, hidden-confounding sensitivity.  \citet{ChristensenConnault2023} develops counterfactual sensitivity and robustness under ambiguity over latent distributions, providing the broader econometric robustness language in which a no-universal-calibration result would live.  \citet{Manski1990} anchors the partial-identification perspective: when sensitivity restrictions do not point identify welfare or regret, the object is an interval or support function rather than a single value.

The closest in-repo prior proposal is \texttt{pid\_offline\_policy\_joint\_misspec\_v1}, whose accepted downgraded angle proposes a sharp joint-misspecification variational interval and an open-set non-rectangularity witness for offline policy value.  The present proposal uses that compatibility warning only as background; its kernel is a calibration frontier among three named sensitivity languages for policy regret, not a joint propensity/outcome-misspecification value interval.  \texttt{doc/API.md} \S3 says the ExactID and PartialID catalogues are empty at seed time for new \texttt{pid\_*} entries, and \S3.1 records only Manski bounded-outcome wrappers; those entries supply generic partial-ID context but do not contain a policy-score bridge theorem.

\section{Formal setup}
Let $O=(X,A,Y)\sim P$, with $A\in\{0,1\}$, $Y\in[\ell,u]$, and nominal propensity $e_0(a\mid X)$ bounded away from zero and one.  The policy class $\Pi$ is finite and contains a status quo $\pi_0$.  For each $\pi\in\Pi$, write $\theta_{\pi,\pi_0}$ for the regret contrast $\E[Y(\pi_0)-Y(\pi)]$ under a latent full-data law compatible with the observed law $P$.  Local perturbations away from the nominal compatible law are indexed by mean-zero scores $h\in L^2_0(P)$ or covariate-only scores $g\in L^2_0(P_X)$.

For each policy $\pi$, the centered policy score $W_{\pi}\in L^2_0(P)$ is the Gateaux derivative of $\theta_{\pi,\pi_0}$ with respect to a compatible latent perturbation $h$: the first-order regret change is $\E[hW_{\pi}]$.  To make observability explicit for the Jin--Xu--Zheng--Zhou and Adjaho--Christensen policy criteria, lock the diagnostic to the usual observable policy-value score whenever the nominal nuisance functions $m_a(x)=\E[Y\mid A=a,X=x]$ and $e_0(a\mid x)$ are identified from $P$:
\[
  \widetilde W_{\pi}(O)
  =
  m_{\pi_0(X)}(X)-m_{\pi(X)}(X)
  + \frac{\one\{A=\pi_0(X)\}}{e_0(A\mid X)}\{Y-m_A(X)\}
  - \frac{\one\{A=\pi(X)\}}{e_0(A\mid X)}\{Y-m_A(X)\},
  \qquad
  W_{\pi}=\widetilde W_{\pi}-\E[\widetilde W_{\pi}].
\]
Thus $W_{\pi}$, its covariate projection $M_{\pi}(X)=\E[W_{\pi}\mid X]$, and $Q_{\Pi_\ast}$ are computable from $P$ for a fixed finite policy class.  Define the CH, MSM, and covariate-shift support penalties
\[
  B_C(\pi;\kappa)=\sup_{\E h=0,\ \E h^2\le\kappa^2}\E[hW_{\pi}],
\]
\[
  B_M(\pi;\Gamma)=\sup_{\E h=0,\ \|h\|_{\infty}\le b(\Gamma)}\E[hW_{\pi}],
  \qquad b(1)=0,\quad b(\Gamma)>0\text{ for }\Gamma>1,
\]
and
\[
  B_S(\pi;\delta)=\sup_{\E g(X)=0,\ \E g(X)^2\le\delta^2}\E[g(X)W_{\pi}]
  = \sup_{\E g=0,\ \E g^2\le\delta^2}\E[g(X)M_{\pi}(X)].
\]
The identified robust-regret upper endpoint for ambiguity language $\mathfrak A$ is
\[
  R_{\mathfrak A}(\pi)=\theta^0_{\pi,\pi_0}+B_{\mathfrak A}(\pi),
\]
where $\theta^0_{\pi,\pi_0}$ is the nominal regret contrast.  Let $\Pi_\ast\subseteq\Pi\setminus\{\pi_0\}$ denote the active comparison set on which policy-score penalties are nonzero in every ambiguity language being bridged.  An exact scalar bridge from language $\mathfrak A$ to language $\mathfrak B$ on $\Pi_\ast$ is a parameter map $\varphi$ such that $B_{\mathfrak A}(\pi;t)=B_{\mathfrak B}(\pi;\varphi(t))$ for every $\pi\in\Pi_\ast$ and every $t$ in a non-degenerate interval.  A three-language positive bridge means that there are positive scale functions $s_C(t),s_M(t),s_S(t)$ and a positive common policy scale $\rho(\pi)$ such that $B_A(\pi;t_A)=s_A(t_A)\rho(\pi)$ for each $A\in\{C,M,S\}$ and $\pi\in\Pi_\ast$.
For each policy define the three observable score penalties
\[
  n_C(\pi)=\|W_{\pi}\|_2,\qquad
  n_M(\pi)=D_1(W_{\pi}),\qquad
  n_S(\pi)=\|M_{\pi}\|_2,
\]
where $D_1(W)=\inf_{c\in\R}\E|W-c|$.  The finite diagnostic matrix is
\[
  Q_{\Pi_\ast}=\bigl(n_C(\pi),n_M(\pi),n_S(\pi)\bigr)_{\pi\in\Pi_\ast}.
\]
For two ambiguity languages $A,B\in\{C,M,S\}$ and two policies $\pi,\pi'$, write the all-pairs calibration residual as
\[
  \Delta_{AB}(\pi,\pi')=n_A(\pi)n_B(\pi')-n_A(\pi')n_B(\pi).
\]
The positive common-scale frontier is the event that all such $2\times2$ minors of $Q_{\Pi_\ast}$ vanish and $n_C(\pi),n_M(\pi),n_S(\pi)$ are all strictly positive for every $\pi\in\Pi_\ast$; equivalently, the three columns of $Q_{\Pi_\ast}$ are positive scalar multiples of one common policy vector.  The observable bridge-defect threshold is
\[
  \tau_{\Pi_\ast}=\max_{A<B}\max_{\pi,\pi'\in\Pi_\ast}|\Delta_{AB}(\pi,\pi')|.
\]
For a fixed sensitivity radius, define the population robust-regret choice set
\[
  \mathcal A_A(t)=\arg\min_{\pi\in\Pi_\ast}\{\theta^0_{\pi,\pi_0}+B_A(\pi;t)\},
  \qquad A\in\{C,M,S\}.
\]
The revised flagship claim treats $\tau_{\Pi_\ast}=0$ as the exact local equivalence frontier for these robust-regret endpoints and choice sets after the published MSM and covariate-shift criteria are expressed in the support-function units above; $\tau_{\Pi_\ast}>0$ is the strict non-equivalence region.  This is not an estimator-equivalence claim about \citet{JinXuZhengZhou2025} or \citet{AdjahoChristensen2025}; it is a population identified-set statement for the local objectives their criteria induce.

\begin{quote}
\begin{verbatim}
(qid, specialization, observable distribution P, parameter theta,
 identifying restrictions, bounding functional)
= (pid_policy_regret_ch_sensitivity, v1, law of O=(X,A,Y),
   theta_{pi,pi0}=E[Y(pi0)-Y(pi)],
   local CH L2 partial-R^2 budget C_kappa,
   local MSM bounded-odds perturbation budget M_Gamma,
   local covariate-shift L2 budget S_delta,
   support-function regret penalty B_A(pi)).
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Bounded overlap and bounded outcomes]\label{ass:bounded-overlap}
The observed law $P$ satisfies $Y\in[\ell,u]$ almost surely and $e_0(a\mid X)\in[\underline e,1-\underline e]$ for some $\underline e>0$ and both $a\in\{0,1\}$.
\end{assumption}

\begin{assumption}[Finite policy class and local differentiability]\label{ass:finite-local}
The class $\Pi$ is finite, contains $\pi_0$, and for every $\pi\in\Pi$ the regret contrast $\theta_{\pi,\pi_0}$ is locally differentiable along compatible latent perturbation paths with centered derivative score $W_{\pi}\in L^2_0(P)\cap L^{\infty}(P)$.
\end{assumption}

\begin{assumption}[Support-function sensitivity budgets]\label{ass:support-budgets}
The CH, MSM, and covariate-shift ambiguity languages are represented locally by the support sets in Section 3: $\E h=0$, $\E h^2\le\kappa^2$ for $\mathcal C_{\kappa}$; $\E h=0$, $\|h\|_{\infty}\le b(\Gamma)$ for $\mathcal M_{\Gamma}$; and $\E g(X)=0$, $\E g(X)^2\le\delta^2$ for $\mathcal S_{\delta}$.  The calibration scale $b$ is continuous, strictly increasing, satisfies $b(1)=0$, and has range $[0,\infty)$.
\end{assumption}

\begin{assumption}[Active positive bridge domain]\label{ass:active-domain}
The three-language bridge is evaluated on a nonempty active subset $\Pi_\ast\subseteq\Pi\setminus\{\pi_0\}$ satisfying $n_C(\pi)>0$, $n_M(\pi)>0$, and $n_S(\pi)>0$ for every $\pi\in\Pi_\ast$.  A policy with $n_A(\pi)=0$ for some bridged language is not part of a non-degenerate three-language bridge unless all bridged penalties are zero for that policy, in which case it is an uninformative tie and is omitted from $\Pi_\ast$.
\end{assumption}

\begin{assumption}[Rank-one compatibility frontier]\label{ass:rank-one}
There exists a nonzero centered score $W_0\in L^2_0(P)\cap L^{\infty}(P)$ and constants $c_{\pi}\ne0$ such that $W_{\pi}=c_{\pi}W_0$ for every $\pi\in\Pi_\ast$.  For the three-language bridge, additionally $M_{\pi}(X)=d_{\pi}M_0(X)$ for a nonzero centered covariate score $M_0$ and constants $d_{\pi}\ne0$ with $|d_{\pi}|$ proportional to $|c_{\pi}|$ on $\Pi_\ast$.
\end{assumption}

\begin{assumption}[Two-score generic witness]\label{ass:two-score}
There exist $\pi_1,\pi_2\in\Pi_\ast$ such that $W_{\pi_1}$ and $W_{\pi_2}$ are linearly independent in $L^2_0(P)$, have non-degenerate distributions, and have strictly positive relevant penalties $n_A(\pi_j)>0$ for the languages $A$ being compared.  At least one all-pairs calibration residual is nonzero:
\[
  \Delta_{CM}(\pi_1,\pi_2)\ne0
  \quad\text{or}\quad
  \Delta_{CS}(\pi_1,\pi_2)\ne0
  \quad\text{or}\quad
  \Delta_{MS}(\pi_1,\pi_2)\ne0.
\]
This cross-product formulation is the locked convention for avoiding undefined norm ratios.
\end{assumption}

\begin{assumption}[Nominal-regret tie for the ranking witness]\label{ass:nominal-tie}
For the two witness policies in Conjecture \ref{conj:open-set-witness}, the nominal regrets are equal:
\[
  \theta^0_{\pi_1,\pi_0}=\theta^0_{\pi_2,\pi_0}.
\]
This assumption is used only for the optional robust-regret ranking conclusion of Conjecture \ref{conj:open-set-witness}; the penalty-level separation does not require it.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: local support-function reduction]\label{thm:support-reduction}
Under Assumptions \ref{ass:bounded-overlap}--\ref{ass:support-budgets}, for every $\pi\in\Pi$,
\[
  B_C(\pi;\kappa)=\kappa\|W_{\pi}\|_2,\qquad
  B_M(\pi;\Gamma)=b(\Gamma)D_1(W_{\pi}),\qquad
  B_S(\pi;\delta)=\delta\|M_{\pi}\|_2.
\]
Here $D_1(W)=\inf_{c\in\R}\E|W-c|$ is the centered $L^1$ support norm induced by the mean-zero bounded MSM perturbation.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This theorem is routine convex duality, not the flagship contribution.  The closest published inputs are \citet{CinelliHazlett2020} for partial-$R^2$ geometry, \citet{ZhaoSmallBhattacharya2019} for bounded odds-ratio perturbations, and \citet{AdjahoChristensen2025} for policy robustness under covariate shifts; the epsilon-gap is the single score-level display that puts the three policy-regret penalties in comparable support-function units.  (b) The concrete consumer is \citet{JinXuZhengZhou2025}: their MSM robust welfare score could be compared to a CH sensitivity report only after this norm-level reduction identifies which score functional is being calibrated.

\begin{conjecture}[Conjecture 1: observable scalar-calibration threshold (NOT YET PROVED)]\label{conj:calibration-frontier}
Under Assumptions \ref{ass:bounded-overlap}--\ref{ass:active-domain}, a non-degenerate three-language scalar bridge among $B_C$, $B_M$, and $B_S$ on the active finite class $\Pi_\ast$ exists on an interval of sensitivity values if and only if the observable bridge-defect threshold is zero: $\tau_{\Pi_\ast}=0$, with $n_C(\pi),n_M(\pi),n_S(\pi)>0$ for every $\pi\in\Pi_\ast$.  Equivalently, $Q_{\Pi_\ast}$ lies on the positive common-scale frontier, so there are positive constants $\alpha_C,\alpha_M,\alpha_S$ and positive policy weights $\rho(\pi)$ such that
\[
  \bigl(n_C(\pi),n_M(\pi),n_S(\pi)\bigr)
  = \rho(\pi)(\alpha_C,\alpha_M,\alpha_S)
  \qquad\text{for every }\pi\in\Pi_\ast.
\]
Assumption \ref{ass:rank-one} is a sufficient primitive condition for this positive common-scale frontier.  Conversely, under Assumption \ref{ass:two-score}, $\tau_{\Pi_\ast}>0$ and no scalar maps $\kappa\mapsto\Gamma(\kappa)$ and $\kappa\mapsto\delta(\kappa)$ can satisfy
\[
  B_C(\pi;\kappa)=B_M(\pi;\Gamma(\kappa))=B_S(\pi;\delta(\kappa))
\]
for all $\pi\in\Pi_\ast$ on any non-degenerate interval with $\kappa>0$.  If the positive common-scale condition holds, then for every nominal regret vector $(\theta^0_{\pi,\pi_0})_{\pi\in\Pi_\ast}$ the robust-regret endpoint vectors $(R_C(\pi))_{\pi\in\Pi_\ast}$, $(R_M(\pi))_{\pi\in\Pi_\ast}$, and $(R_S(\pi))_{\pi\in\Pi_\ast}$ agree up to the same positive radius normalization, so the local choice sets $\mathcal A_C(\kappa)$, $\mathcal A_M(\Gamma(\kappa))$, and $\mathcal A_S(\delta(\kappa))$ coincide.  Moreover, whenever one residual is nonzero for $\pi_1,\pi_2$, there is an open interval of nominal regret differences $\theta^0_{\pi_1,\pi_0}-\theta^0_{\pi_2,\pi_0}$ for which the CH-normalized ranking and at least one of the MSM robust-welfare ranking induced by \citet{JinXuZhengZhou2025} or the covariate-shift policy-choice ranking induced by \citet{AdjahoChristensen2025} choose different unique policies.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{KallusZhou2021} and \citet{JinXuZhengZhou2025} provide robust policy-regret criteria under MSM, while \citet{CinelliHazlett2020}, \citet{DiegertMastenPoirier2025}, \citet{MastenPoirierRen2025}, \citet{SorianoBenMichaelBickelFellerPimentel2023}, and \citet{HuangPimentel2025} provide scalar $R^2$, relaxation, or weighting-sensitivity comparison tools, and \citet{AdjahoChristensen2025} provides an external-validity policy language.  None states the necessary-and-sufficient finite-policy diagnostic for translating one local population robust-regret endpoint into another without changing policy rankings.  The flagship epsilon-gap is the observable threshold $\tau_{\Pi_\ast}$: it is a computable equality/non-equivalence frontier for robust-regret endpoints and choice sets induced by named published criteria, not a local norm-ratio slogan, estimator-equivalence claim, or axiomatic scalar-parameter comparison.  (b) The concrete consumer is \citet{JinXuZhengZhou2025}: if this frontier is true, their MSM robust welfare criterion can inherit a CH partial-$R^2$ calibration only when $Q_{\Pi_\ast}$ has a positive common scale, and otherwise must be reported as a separate robustness curve rather than as a CH-calibrated proxy.

\begin{conjecture}[Conjecture 2: supporting two-policy open-set penalty separation witness (NOT YET PROVED)]\label{conj:open-set-witness}
Under Assumptions \ref{ass:bounded-overlap}--\ref{ass:active-domain}, there is an open set of non-degenerate binary-action observable laws $P$ and two active policies $\pi_1,\pi_2\in\Pi_\ast$ for which
\[
  \|W_{\pi_1}\|_2=\|W_{\pi_2}\|_2
  \quad\text{but}\quad
  D_1(W_{\pi_1})\ne D_1(W_{\pi_2})
  \quad\text{or}\quad
  \|M_{\pi_1}\|_2\ne\|M_{\pi_2}\|_2.
\]
For those laws, CH partial-$R^2$ robustness ties the two penalty terms at every $\kappa$, while the MSM or covariate-shift penalty terms strictly separate at every positive calibrated radius.  If, in addition, Assumption \ref{ass:nominal-tie} holds, then the same witness gives a robust-regret ranking separation; without this nominal-regret equality, the conjecture is only a penalty-level sharpness witness and the ranking claim is supplied by Conjecture \ref{conj:calibration-frontier}.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) This is a supporting sharpness witness for Conjecture \ref{conj:calibration-frontier}, not a novelty-bearing refutation of \citet{CinelliHazlett2020}, \citet{SorianoBenMichaelBickelFellerPimentel2023}, \citet{HuangPimentel2025}, \citet{JinXuZhengZhou2025}, or \citet{AdjahoChristensen2025}.  The named workflow it targets is the informal cross-paper reporting practice motivated by scalar sensitivity comparisons in \citet{DiegertMastenPoirier2025} and by $R^2$-parameterized weighting sensitivity in \citet{HuangPimentel2025}; those papers do not endorse translating scalar $R^2$ values into policy rankings, and the witness tests exactly where such a translation would fail.  The epsilon-gap is the open-set promotion needed by Conjecture \ref{conj:calibration-frontier}: the separation is not a single hand-tuned degenerate law, but a stable region where policy-score distributional shape matters.  (b) The concrete consumer is \citet{AdjahoChristensen2025}: the witness would warn externally valid policy-choice users that a covariate-shift penalty comparison need not agree with a CH partial-$R^2$ penalty comparison even when both are normalized to the same local variance.

\section{Sanity-check corollaries}
\begin{corollary}[Zero-sensitivity point-regret corner]\label{cor:zero}
Under Assumptions \ref{ass:bounded-overlap}--\ref{ass:support-budgets}, if $\kappa=0$, $\Gamma=1$, and $\delta=0$, then $B_C(\pi;0)=B_M(\pi;1)=B_S(\pi;0)=0$ for every $\pi\in\Pi$, so all three robust regret endpoints reduce to the nominal regret $\theta^0_{\pi,\pi_0}$.
\end{corollary}

\begin{corollary}[Single-policy calibration is always possible]\label{cor:single-policy}
Under Assumptions \ref{ass:bounded-overlap}--\ref{ass:support-budgets}, if $\Pi=\{\pi_0,\pi\}$ and $n_C(\pi),n_M(\pi),n_S(\pi)$ are strictly positive, then for any fixed $\kappa>0$ one can choose $\Gamma$ and $\delta$ so that $B_C(\pi;\kappa)=B_M(\pi;\Gamma)=B_S(\pi;\delta)$.  The obstruction in Conjecture \ref{conj:calibration-frontier} is therefore a multi-policy ranking obstruction, not a failure to match one scalar number.
\end{corollary}

\section{Proof-sketch route}
The proof route is convex-analytic.  Theorem \ref{thm:support-reduction} follows from Cauchy--Schwarz for the $L^2$ ellipsoids, conditional projection for the covariate-shift score, and the dual formula for maximizing a linear functional over mean-zero $L^\infty$ perturbations, which yields the centered absolute-deviation norm.  The positive direction of Conjecture \ref{conj:calibration-frontier} reduces to substituting $W_{\pi}=c_{\pi}W_0$ and $M_{\pi}=d_{\pi}M_0$ into the three support functions and solving the resulting one-dimensional scale equations on the active set $\Pi_\ast$.  The all-pairs negative direction reduces to finite matrix algebra: a positive three-language scalar bridge requires every column of $Q_{\Pi_\ast}$ to be a positive multiple of one common policy vector, equivalently $\tau_{\Pi_\ast}=0$ together with the nonzero-column condition in Assumption \ref{ass:active-domain}; if any cross-product residual is nonzero, one scalar parameter map cannot make both policy equalities hold.  The ranking-separation clause then perturbs the two nominal regrets around equality until the two support penalties choose different unique minimizers.  Conjecture \ref{conj:open-set-witness} should be proved by a finite-support construction with two centered scores having equal variance but different centered absolute deviation or different conditional expectation norm, followed by a continuity argument showing the strict penalty inequalities persist under small perturbations of $P$; robust-regret ranking separation is then stated only under the additional equality $\theta^0_{\pi_1,\pi_0}=\theta^0_{\pi_2,\pi_0}$ or through the nominal-regret perturbation clause of Conjecture \ref{conj:calibration-frontier}.

\section{Honest scope flags}
\begin{itemize}[leftmargin=*]
\item Theorem \ref{thm:support-reduction} and Corollaries \ref{cor:zero}--\ref{cor:single-policy} are labelled as routine support-function facts.
\item Conjecture \ref{conj:calibration-frontier} is the novelty-bearing kernel and is not yet proved.  Conjecture \ref{conj:open-set-witness} is retained only as a supporting open-set witness for that kernel.
\item Version 2 for the current reviewer pass removes undefined variance-based ranking language, narrows the flagship frontier to local population robust-regret endpoints and choice sets, and replaces the overstrong claim that comparison papers license scalar-to-policy translation with a neutral motivation statement.
\item Version 3 reframes Conjecture \ref{conj:open-set-witness} as an internal penalty-level sharpness witness rather than an external negative result, and makes robust-regret ranking separation conditional on equal nominal regrets or on Conjecture \ref{conj:calibration-frontier}'s nominal-regret perturbation clause.
\item Version 4 adds the active positive-bridge domain $\Pi_\ast$, excludes zero-column degeneracies from Conjecture \ref{conj:calibration-frontier}, and reframes the kernel as an equivalence/non-equivalence frontier between the named MSM robust-welfare and external-validity policy-choice criteria.
\item Version 5 adds the missed sensitivity-parameter comparison papers \citet{DiegertMastenPoirier2025} and \citet{MastenPoirierRen2025}, makes the observable score formula and bridge-defect threshold $\tau_{\Pi_\ast}$ explicit, and demotes Conjecture \ref{conj:open-set-witness} to a supporting witness for the flagship frontier rather than a stand-alone negative result.
\item This pivot deliberately withdraws the dead angle's stronger claim of a universal CH-calibrated minimax-regret formula.  The new kernel allows calibration only under a rank-one score frontier and predicts generic non-equivalence otherwise.
\item The setup is local: it assumes the derivative scores $W_{\pi}$ correctly summarize compatible latent perturbations.  A later derivation must connect those scores back to a fully sharp finite latent law if the project wants a global, nonlocal version.
\end{itemize}

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 1, replacing the dead universal CH-regret formula with a calibration-frontier proposal across CH, MSM, and covariate-shift support functions; prior verdict: none.
\item v2 (revise) --- removed undefined variance-based ranking language, narrowed Conjecture 1 to local population robust-regret endpoint and choice-set equivalence, and neutralized the Diegert--Masten--Poirier / Huang--Pimentel comparison wording; prior verdict: REVISE.
\item v3 (revise) --- patched Conjecture 2 to be a penalty-level sharpness witness, added the missing nominal-regret equality condition for any ranking separation, and removed the unsupported external-splice framing; prior verdict: REVISE.
\item v4 (revise) --- added the positive common-scale/nonzero-column condition for the calibration frontier and lifted Conjecture 1 into an equivalence/non-equivalence diagnostic for named MSM and external-validity policy criteria; prior verdict: REVISE.
\item v5 (revise) --- added Diegert--Masten--Poirier and Masten--Poirier--Ren to the closest-literature comparison, replaced the flagship frontier with the observable threshold $\tau_{\Pi_\ast}$, made $W_\pi$ computable from $P$, and reframed Conjecture 2 as supporting rather than novelty-bearing; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Adjaho and Christensen(2025)]{AdjahoChristensen2025}
Adjaho, C. and T. Christensen (2025).
Externally valid policy choice.
\emph{arXiv:2205.05561}.

\bibitem[Christensen and Connault(2023)]{ChristensenConnault2023}
Christensen, T. and B. Connault (2023).
Counterfactual sensitivity and robustness.
\emph{Econometrica} 91(1), 263--298.

\bibitem[Cinelli and Hazlett(2020)]{CinelliHazlett2020}
Cinelli, C. and C. Hazlett (2020).
Making sense of sensitivity: extending omitted variable bias.
\emph{Journal of the Royal Statistical Society: Series B} 82(1), 39--67.

\bibitem[Dorn, Guo, and Kallus(2025)]{DornGuoKallus2025}
Dorn, J., K. Guo, and N. Kallus (2025).
Doubly-valid/doubly-sharp sensitivity analysis for causal inference with unmeasured confounding.
\emph{Journal of the American Statistical Association}.

\bibitem[Diegert, Masten, and Poirier(2025)]{DiegertMastenPoirier2025}
Diegert, P., M. A. Masten, and A. Poirier (2025).
An axiomatic approach to comparing sensitivity parameters.
\emph{arXiv:2504.21106}.

\bibitem[Huang and Pimentel(2025)]{HuangPimentel2025}
Huang, M. and S. D. Pimentel (2025).
Variance-based sensitivity analysis for weighting estimators results in more informative bounds.
\emph{Biometrika} 112(1), 235--240.

\bibitem[Jin, Xu, Zheng, and Zhou(2025)]{JinXuZhengZhou2025}
Jin, Z., G. Xu, X. Zheng, and Y. Zhou (2025).
Policy learning under unobserved confounding: a robust and efficient approach.
\emph{arXiv:2507.20550}.

\bibitem[Kallus and Zhou(2021)]{KallusZhou2021}
Kallus, N. and A. Zhou (2021).
Minimax-optimal policy learning under unobserved confounding.
\emph{Management Science} 67(5), 2870--2890.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Masten, Poirier, and Ren(2025)]{MastenPoirierRen2025}
Masten, M. A., A. Poirier, and M. Ren (2025).
A general approach to relaxing unconfoundedness.
\emph{arXiv:2501.15400}.

\bibitem[Soriano et~al.(2023)]{SorianoBenMichaelBickelFellerPimentel2023}
Soriano, D., E. Ben-Michael, P. J. Bickel, A. Feller, and S. D. Pimentel (2023).
Interpretable sensitivity analysis for balancing weights.
\emph{Journal of the Royal Statistical Society: Series A} 186(4), 707--721.

\bibitem[Yadlowsky et~al.(2022)]{YadlowskyNamkoongBasuDuchiTian2022}
Yadlowsky, S., H. Namkoong, S. Basu, J. Duchi, and L. Tian (2022).
Bounds on the conditional and average treatment effect with unobserved confounding factors.
\emph{Annals of Statistics} 50(5), 2587--2615.

\bibitem[Zhao, Small, and Bhattacharya(2019)]{ZhaoSmallBhattacharya2019}
Zhao, Q., D. S. Small, and B. B. Bhattacharya (2019).
Sensitivity analysis for inverse probability weighting estimators via the percentile bootstrap.
\emph{Journal of the Royal Statistical Society: Series B} 81(4), 735--761.
\end{thebibliography}

\end{document}
