% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_reversible\_dynamic\_spillover, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_reversible\_dynamic\_spillover} / \texttt{v1}%
  \\ \large\textit{Scalar-indexed sharp bounds for reversible dynamic treatment with bounded adjacent-spell carryover}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Partial-identification anchor.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R_\rho,B_\rho)
=
(\texttt{pid\_reversible\_dynamic\_spillover},\texttt{v1},P,
\theta^{LR},\mathcal R_\rho,[L_\rho(P),U_\rho(P)]).
\]
Here \(P_T\) is the observed law of a finite-support longitudinal panel
\((L_{it},A_{it},Y_{it})_{t=1}^T\), with \(A_{it}\in\{0,1\}\) reversible and
\(Y_{it}\in[0,1]\).  For finite-horizon statements write \(P=P_T\).  For the
long-run statement, \(P_\infty\) is either a stationary infinite-panel law whose
finite-dimensional marginals are \(P_T\), or a projectively compatible sequence
\((P_T)_{T\ge1}\) satisfying Assumption~\ref{ass:stationary}.  The parameter
\(\theta^{LR}\) is the Cesaro long-run average of the sustained-treatment contrast
\[
\theta_T = T^{-1}\sum_{t=1}^T
\left\{\E[Y_t(\bar 1_t)]-\E[Y_t(\bar 0_t)]\right\},
\qquad
\theta^{LR}=\lim_{T\to\infty}\theta_T
\]
when the limit exists.  The identifying restrictions \(\mathcal R_\rho\) are
consistency, Robins transition stability for covariates, finite-history
positivity on the reversible support, and a scalar adjacent-spell carryover
bound: latent conditional outcome means are \(\rho\)-Lipschitz in the
spell-boundary distance \(d_{\rm sp}\) defined in Section~\ref{sec:setup}.
The bounding functional \(B_\rho(P)=[L_\rho(P),U_\rho(P)]\) is the nested
lower/upper g-formula obtained by replacing each Robins outcome regression by
its McShane-Whitney lower or upper \(\rho\)-Lipschitz envelope over the
observed reversible support.  The endpoint convention is
\(\rho=0\) for the Robins g-formula point-identification regime and
\(\rho=\infty\) for the unrestricted bounded-outcome Manski regime that retains
factual consistency anchors at observed target-history nodes and otherwise lets
unobserved sustained-history outcomes range over \([0,1]\).

\begin{abstract}
This proposal asks for sharp bounds on a long-run average treatment effect when
the treatment process is reversible and adjacent treatment spells may contaminate
each other by at most a scalar amount \(\rho\).  The proposed kernel is a
closed-form sequence of lower and upper nested g-formulas: at each history node,
the usual Robins outcome regression is replaced by the smallest and largest
bounded \(\rho\)-Lipschitz extension compatible with the observed reversible
panel law.  The flagship conjecture is that these formulas are not merely outer
bounds, but the exact sharp identified interval, with extremal latent joint laws
attaining every lower and upper face.  The construction is designed to collapse
to the Robins \citep{Robins1986} g-formula when \(\rho=0\) and to the
bounded-outcome Manski interval when \(\rho=\infty\).  If resolved, the result
would give empirical researchers a sensitivity parameter for reversible
dynamic treatments that sits between full sequential point identification and
assumption-free dynamic bounds.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Many panel treatments are reversible: pollution exposure, medication use,
employment status, incarceration, price regulation, and policy intensity can all
turn on, turn off, and turn on again.  Standard longitudinal g-formula analyses
point-identify dynamic regimes under sequential exchangeability, while
assumption-free partial-identification analyses honestly report very wide
bounds.  The open methodological question is whether a single interpretable
carryover radius can interpolate between those two poles when the scientific
concern is contamination from adjacent treatment spells rather than arbitrary
latent confounding.

\paragraph{The main finding (proposed).}
Conjecture~\ref{conj:sharp-finite} states that, for each finite horizon \(T\)
and spillover radius \(\rho\), the identified set for
\(\theta_T\) is exactly the interval obtained from the lower and upper
nested g-formulas \(L_T(\rho;P)\) and \(U_T(\rho;P)\).  The same conjecture
includes the sharpness witness: two observed-law-compatible latent completions
attain each exposed and unexposed endpoint, so the ATE faces
\(L_T^1(\rho)-U_T^0(\rho)\) and \(U_T^1(\rho)-L_T^0(\rho)\) cannot be improved.
Conjecture~\ref{conj:longrun} then asks for the Cesaro-limit version under
stationary reversible dynamics.

\paragraph{What is new.}
The novelty kernel is the spell-boundary Lipschitz envelope, not a routine
extension from absorbing to nonabsorbing treatment paths.  \citet{KimKwonKwonLee2018}
show that smoothness restrictions can sharpen counterfactual-outcome bounds in
static treatment-response models; the strict dynamic extension proposed here is
that the Lipschitz metric is defined on reversible treatment-history boundary
vectors and then propagated through a Robins transition recursion, so a single
latent completion must satisfy all period and regime faces simultaneously.  Robins
\citep{Robins1986} gives point identification under the full longitudinal
assumptions; Diemer, Shi, and Swanson \citep{DiemerShiSwanson2024} give
assumption-free dynamic sustained-intervention bounds; de Chaisemartin and
d'Haultfoeuille \citep{DeChaisemartinDHaultfoeuille2024} handle nonabsorbing
treatment lags under a DID design.  None of those papers gives a scalar
closed-form, sharp partial-identification bridge in which repeated on-off
spells are retained as the state variable and the two endpoint regimes are
theorems of the same formula.

\paragraph{How it positions in the literature.}
This is a partial-identification proposal with a dynamic-panel interface.  It
uses the g-formula as the zero-radius exact-identification endpoint, uses
Manski-style bounded-outcome logic as the infinite-radius endpoint, and borrows
the sharpness standard of panel partial-identification papers such as
\citet{ChernozhukovFernandezValHahnNewey2013} and \citet{JunLeeShin2016}.  It does
not propose a new event-study estimand or a new two-way fixed-effects
regression; the panel feature is the reversible treatment-history support on
which the partial-identification envelope is built.

\paragraph{Implications for the community.}
The concrete downstream consumer is the treatment-history matching workflow of
\citet{ImaiKimWang2023}: their applied design already matches on finite
treatment histories and estimates short- and long-run effects, but it needs a
formal sensitivity target when exact no-carryover diagnostics fail.  A sharp
\(\rho\)-indexed interval would tell users of that workflow how much their
long-run conclusion can move as adjacent-spell contamination is relaxed.

\paragraph{How research benefits from the conclusion.}
Researchers studying reversible policies should report a spillover-radius
sensitivity curve \( \rho\mapsto [L_\rho(P),U_\rho(P)] \) rather than treating
Robins point identification and unrestricted dynamic bounds as unrelated
analyses.

\section{Related work}
\citet{Robins1986} introduces the g-formula for time-varying treatments under
sequential exchangeability, consistency, and positivity; it is the
\(\rho=0\) endpoint this proposal must recover.  \citet{Han2021} studies
nonparametric identification of finite dynamic treatment sequences and
emphasizes timing, state dependence, and endogenous dynamic choices; it is the
closest econometric dynamic-treatment identification paper, but it is not a
closed-form scalar partial-identification bridge for reversible spillovers.
\citet{DiemerShiSwanson2024} extends assumption-free partial-identification
bounds from time-fixed exposures to sustained static and dynamic interventions;
it supplies the wide \(\rho=\infty\) pole but intentionally does not impose a
bounded adjacent-spell structure.  \citet{KimKwonKwonLee2018} study sharp
counterfactual-outcome bounds under Lipschitz smoothness assumptions; this is
the closest smoothness partial-identification comparator, but their metric is a
static treatment-response smoothness condition rather than a reversible
treatment-history spell-boundary metric coupled through a dynamic g-recursion.
\citet{ChernozhukovFernandezValHahnNewey2013}
derive sharp bounds for average and quantile effects in nonseparable panel
models, including dynamic state-dependence bounds under time-homogeneity
conditions; their sharpness target motivates the extremal-law requirement here,
but their restrictions are not scalar spell-boundary contamination bounds.
\citet{JunLeeShin2016} give sharp identifiable bounds for potential-outcome
distributions in panels with dynamic treatment decisions using stationarity
restrictions; this proposal instead asks for a reversible-spell Lipschitz
restriction that nests Robins and Manski endpoints.  \citet{DeChaisemartinDHaultfoeuille2024}
allow nonbinary, nonabsorbing treatments and lags in a DID event-study design;
their estimands are parallel-trends weighted effects, not sharp
partial-identification intervals.  \citet{SunAbraham2021} and
\citet{CallawaySantAnna2021} show why absorbing adoption timing is a powerful
state compression in event-study and DID designs; reversible spells destroy
that compression.  \citet{BojinovRambachanShephard2021} define finite-population
dynamic causal effects for alternative treatment paths in panel experiments and
show why carryover makes conventional panel estimators hard to interpret; their
framework is design-based rather than a sharp observational partial-ID envelope.
\citet{ImaiKimWang2023} propose treatment-history matching
for time-series cross-sectional data and estimate long-run effects, making it a
natural empirical consumer of a reversible-spell sensitivity curve.
\citet{HanYang2024} represent a computational approach to policy-effect
identification under unobserved heterogeneity; the contrast here is analytic
closed-form envelopes indexed by one spillover radius.

In-repo prior art is closest in three places.  The generated catalogue
`doc/API.md' records only the generic PartialID/Manski seed section, so there
is no existing CausalSmith entry for this qid beyond scaffolding.  The candidate
proposal `pid\_dynamic\_iv\_compliance v2' develops memory-retaining dynamic IV
bounds and notes that retaining history constraints can shrink intervals, but
its object is compliance response types rather than reversible treatment-spell
carryover.  The downgraded `pid\_dynamic\_iv\_compliance v3' and failed
`pid\_long\_term\_surrogate v1' artifacts both expose the same missing
ingredient: exact endpoint-face witnesses for latent dynamic completions.  The
candidate `pid\_did\_anticipation\_bounded v1' studies bounded anticipation
with shared coordinates in DID aggregation; it is relevant as support-function
algebra, but its target is panel ATT aggregation, not a long-run dynamic ATE.

\section{Formal setup}
\label{sec:setup}
For each finite horizon \(T\), there are exchangeable units \(i\), periods
\(t=1,\ldots,T\), covariates
\(L_t\in\mathcal L_t\), reversible binary treatment \(A_t\in\{0,1\}\), and
bounded outcome \(Y_t\in[0,1]\).  Let
\(H_t=(L_1,A_1,Y_1,\ldots,L_t)\) denote the pre-treatment history at period
\(t\), and let \(P_T\) be the observed law of the full panel path.  Write
\(X_t=(L_1,Y_1,\ldots,Y_{t-1},L_t)\) for the non-treatment history component
used to index reversible-support strata, and write
\(\bar A_t=(A_1,\ldots,A_t)\).  For a
treatment path \(\bar a_t=(a_1,\ldots,a_t)\), \(Y_t(\bar a_t)\) denotes the
period-\(t\) potential outcome, and \(L_{t+1}(\bar a_t)\) denotes the next
covariate under the same path.

The two sustained regimes are \(\bar 1_t=(1,\ldots,1)\) and
\(\bar 0_t=(0,\ldots,0)\).  The finite-horizon target is
\[
\theta_T=T^{-1}\sum_{t=1}^T
\{\E[Y_t(\bar 1_t)]-\E[Y_t(\bar 0_t)]\},
\]
and the long-run target \(\theta^{LR}\) is the Cesaro limit of \(\theta_T\)
when it exists.  For a history-node \(v=(t,x_t,\bar a_t)\), define the
spell-boundary vector
\[
s(\bar a_t)=(\one\{a_2\ne a_1\},\ldots,\one\{a_t\ne a_{t-1}\})
\]
and the adjacent-spell distance
\[
d_{\rm sp}(\bar a_t,\bar b_t)
=\one\{a_t\ne b_t\}+\sum_{r=2}^t |s_r(\bar a_t)-s_r(\bar b_t)|.
\]
The first term separates current treatment effects; the summation measures
carryover from starts and endings of consecutive spells.

For any node \(v=(t,x_t,\bar a_t)\), let \(m_t(v)\) be the latent conditional
mean \(\E[Y_t(\bar a_t)\mid X_t=x_t]\).  The observed reversible-support set at
the non-treatment state \(x_t\) is
\[
\mathcal O_t(x_t)=
\{\bar b_t\in\{0,1\}^t:\Pr_{P_T}(X_t=x_t,\bar A_t=\bar b_t)>0\}.
\]
For \(\bar b_t\in\mathcal O_t(x_t)\), define the factual regression
\[
\mu_t^P(x_t,\bar b_t)=\E_{P_T}[Y_t\mid X_t=x_t,\bar A_t=\bar b_t].
\]
If \(v=(t,x_t,\bar a_t)\) is factual, meaning
\(\bar a_t\in\mathcal O_t(x_t)\), consistency anchors \(m_t(v)\) at
\(\mu_t^P(x_t,\bar a_t)\).  Given \(\rho\), the
candidate lower and upper outcome envelopes are
\[
\ell_t^\rho(v)=
\max\left\{0,\sup_{\bar b_t\in\mathcal O_t(x_t)}
[\mu_t^P(x_t,\bar b_t)-\rho d_{\rm sp}(\bar a_t,\bar b_t)]\right\},
\qquad
u_t^\rho(v)=
\min\left\{1,\inf_{\bar b_t\in\mathcal O_t(x_t)}
[\mu_t^P(x_t,\bar b_t)+\rho d_{\rm sp}(\bar a_t,\bar b_t)]\right\},
\]
with the convention that \(\rho=\infty\) drops the Lipschitz inequalities but
retains the factual anchor \(m_t(t,x_t,\bar a_t)=\mu_t^P(x_t,\bar a_t)\) when
\(\bar a_t\in\mathcal O_t(x_t)\); if \(\bar a_t\notin\mathcal O_t(x_t)\), the
nodewise envelope is the unrestricted range \([0,1]\).
The nested lower and upper g-formulas \(L_T^a(\rho;P)\) and \(U_T^a(\rho;P)\)
are obtained by running the Robins backward recursion for regime
\(\bar a\in\{\bar 0,\bar 1\}\), using the observed covariate transition kernel
and replacing the terminal outcome regression at each period by
\(\ell_t^\rho\) or \(u_t^\rho\).  The proposed ATE interval is
\[
B_T(\rho;P)=
[L_T^1(\rho;P)-U_T^0(\rho;P),\,
 U_T^1(\rho;P)-L_T^0(\rho;P)].
\]

\begin{quote}
Locked parameters: \(q=\texttt{pid\_reversible\_dynamic\_spillover}\),
specialization \(=\texttt{v1}\), observable distribution \(P\) is the
finite-support law \(P_T\) of \((L_t,A_t,Y_t)_{t=1}^T\) for finite-horizon
results and the stationary law \(P_\infty\) or compatible sequence
\((P_T)_{T\ge1}\) for the long-run result, parameter
\(\theta=\theta^{LR}\) is the Cesaro long-run sustained-regime ATE, identifying
restrictions \(\mathcal R_\rho\) are consistency, Robins transition stability,
reversible-support positivity, and \(\rho\)-bounded adjacent-spell Lipschitz
carryover, and bounding functional \(B_\rho(P)\) is the nested lower/upper
g-formula interval defined by the McShane-Whitney envelopes
\(\ell_t^\rho,u_t^\rho\).
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite reversible panel law]\label{ass:finite}
For each finite horizon \(T\), the observed panel law \(P\) has finite support,
\(A_t\in\{0,1\}\), and \(Y_t\in[0,1]\).  All conditional means and transition
kernels appearing in Section~\ref{sec:setup} are defined on positive-probability
histories.
\end{assumption}

\begin{assumption}[Consistency]\label{ass:consistency}
If the realized treatment prefix equals \(\bar a_t\), then the observed outcome
satisfies \(Y_t=Y_t(\bar a_t)\), and the realized covariate history satisfies
the corresponding potential-history consistency relation.
\end{assumption}

\begin{assumption}[Robins transition stability]\label{ass:transition}
For the two sustained regimes \(\bar 0\) and \(\bar 1\), the conditional law of
\(L_{t+1}(\bar a_t)\) given \(H_t=h_t\) is the observed conditional law
\(P(L_{t+1}\mid H_t=h_t,A_t=a_t)\) whenever the conditioning event has positive
probability.
\end{assumption}

\begin{assumption}[Reversible-support positivity]\label{ass:positivity}
For every history node used by the sustained-regime g-recursion, the observed
support contains a nonempty reversible-support set \(\mathcal O_t(x_t)\) and
the covariate transition probabilities in Assumption~\ref{ass:transition} are
strictly positive on their finite support.
\end{assumption}

\begin{assumption}[\(\rho\)-bounded adjacent-spell carryover]\label{ass:rho}
For every period \(t\), non-treatment history \(x_t\), and two treatment prefixes
\(\bar a_t,\bar b_t\) on the reversible support,
\[
|m_t(t,x_t,\bar a_t)-m_t(t,x_t,\bar b_t)|
\le \rho\,d_{\rm sp}(\bar a_t,\bar b_t).
\]
The conventions are \(\rho=0\) for exact spell-boundary invariance and
\(\rho=\infty\) for no restriction beyond \(Y_t\in[0,1]\), except that
factual consistency anchors are retained when the target treatment prefix is in
\(\mathcal O_t(x_t)\).
\end{assumption}

\begin{assumption}[Stationary finite-memory long-run law]\label{ass:stationary}
For the long-run result, either \(P_\infty\) is a stationary infinite-panel law
or \((P_T)_{T\ge1}\) is a projectively compatible finite-panel sequence whose
finite-dimensional marginals agree with \(P_\infty\).  The induced process is
stationary and geometrically ergodic on a finite \(M\)-memory state
\(S_t=(L_{t-M:t},A_{t-M:t},Y_{t-M:t-1})\), and the two sustained-regime
transition kernels induced by Assumption~\ref{ass:transition} have unique
invariant laws.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: Endpoint nesting of the candidate interval]\label{thm:endpoints}
Under Assumptions~\ref{ass:finite}--\ref{ass:rho}, the candidate interval
\(B_T(\rho;P)\) is nested and monotone in \(\rho\): if
\(0\le\rho\le\rho'\le\infty\), then
\[
B_T(\rho;P)\subseteq B_T(\rho';P).
\]
At \(\rho=0\), \(B_T(0;P)\) collapses to the Robins nested g-formula contrast
for the two sustained regimes whenever exact spell-boundary invariance makes
\(\ell_t^0=u_t^0=\mu_t^P\) at each node.  At \(\rho=\infty\),
unobserved sustained-history nodes have \(\ell_t^\infty=0\) and
\(u_t^\infty=1\), while factual sustained-history nodes retain their
consistency anchors.  Thus \(B_T(\infty;P)\) is the data-tightened
bounded-outcome Manski interval for the finite-horizon sustained-regime ATE,
and it equals \([-1,1]\) in the fully off-support sustained-regime case.
\end{theorem}
\paragraph{Why this is new and worth studying.}
The theorem itself is routine envelope algebra, but it is the necessary
calibration check for the proposal's novelty kernel.  The closest published
papers give one endpoint at a time: \citet{Robins1986} gives the
point-identification endpoint and \citet{DiemerShiSwanson2024} gives wide
assumption-free dynamic bounds.  The concrete consumer is
\citet{ImaiKimWang2023}, whose treatment-history matching users need a
reported sensitivity curve with interpretable endpoint diagnostics.

\begin{conjecture}[Conjecture 1: Sharp finite-horizon reversible-spell bounds (NOT YET PROVED)]\label{conj:sharp-finite}
Under Assumptions~\ref{ass:finite}--\ref{ass:rho}, the sharp identified set for
\(\theta_T\) over all latent joint laws satisfying the observed law \(P\) and
the \(\rho\)-bounded adjacent-spell carryover restriction is exactly
\[
\Theta_I^T(P,\rho)=B_T(\rho;P).
\]
Moreover, for every exposed-regime endpoint and unexposed-regime endpoint in
the definition of \(B_T(\rho;P)\), there exists an observed-law-compatible
latent completion satisfying Assumptions~\ref{ass:consistency}--\ref{ass:rho}
that attains that endpoint.  The extremal completions can be chosen as
McShane-type and Whitney-type spell-boundary extensions of the observed
outcome regressions, pasted with the observed Robins transition kernel.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
The closest published sharpness results are
\citet{KimKwonKwonLee2018}, \citet{ChernozhukovFernandezValHahnNewey2013}, and
\citet{JunLeeShin2016}.  \citet{KimKwonKwonLee2018} prove sharp bounds under
smoothness of treatment response functions, but not for a finite-state dynamic
treatment-history metric whose same extremal completion must be compatible with
Robins transition recursions across periods.  The panel sharpness papers give
sharp bounds driven by time-homogeneity or stationarity restrictions rather
than a scalar adjacent-spell Lipschitz radius on reversible treatment histories.
The epsilon gap is the exact face-attainment claim for a nonabsorbing
spell-boundary metric: no cited paper proves that the Lipschitz lower/upper
extensions remain globally pasteable after the same latent completion must
serve all periods and both sustained regimes.  Resolving this would give the
assumption-free dynamic bounds of \citet{DiemerShiSwanson2024} a one-parameter
frontier between Robins point identification and unrestricted bounds.

\begin{conjecture}[Conjecture 2: Long-run Cesaro limit of the sharp intervals (NOT YET PROVED)]\label{conj:longrun}
Under Assumptions~\ref{ass:finite}--\ref{ass:stationary} for the stationary law
\(P_\infty\) or compatible sequence \((P_T)_{T\ge1}\), the finite-horizon
sharp intervals \(B_T(\rho;P_T)\) converge in Hausdorff distance to a stationary
interval \(B_\rho(P)=[L_\rho(P),U_\rho(P)]\).  The limiting endpoints are the
solutions of the stationary lower and upper Bellman-g-formula equations on the
finite \(M\)-memory reversible-spell state space, and the long-run identified
set for \(\theta^{LR}\) is exactly \(B_\rho(P)\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
\citet{BojinovRambachanShephard2021} define dynamic causal effects for
alternative treatment paths in panel experiments, explicitly making carryover a
path-level object; \citet{Han2021} identifies finite dynamic treatment-sequence
means under
econometric dynamic-treatment assumptions, and \citet{HanYang2024} gives a
computational approach to policy-effect identification under unobserved
heterogeneity.  Neither states analytic conditions under which
horizon-normalized sharp bounds for reversible bounded-carryover regimes
converge to a closed-form stationary interval.  The concrete consumer is the
long-run effect estimand in \citet{ImaiKimWang2023}: the conjecture would tell
users when finite-history matching sensitivity intervals have a stable
long-run target rather than a horizon-specific interpretation.

\section{Sanity-check corollaries}
\begin{corollary}[Zero carryover reduction]\label{cor:zero}
Under Assumptions~\ref{ass:finite}--\ref{ass:rho} with \(\rho=0\), if every
regime node has zero spell-boundary distance from the relevant observed
Robins node, then \(B_T(0;P)\) is the singleton containing the standard Robins
g-formula contrast.
\end{corollary}

\begin{corollary}[Unrestricted bounded-outcome reduction]\label{cor:infty}
Under Assumptions~\ref{ass:finite}--\ref{ass:rho} with \(\rho=\infty\), the
period-specific sustained-regime means range over \([0,1]\) at target nodes
that are not factual under \(P_T\), while factual target nodes retain their
observed consistency anchors.  Hence the finite-horizon ATE interval is the
data-tightened Manski interval; in the fully off-support sustained-regime case,
it reduces to \([-1,1]\) after taking the exposed-minus-unexposed contrast.
\end{corollary}

\begin{corollary}[Absorbing-path reduction]\label{cor:absorbing}
If the observed support contains no \(1\to0\) reversals and only the first
switch-on boundary can occur, then \(d_{\rm sp}\) collapses to the Hamming
distance between absorbing switch-boundary vectors plus the current-treatment
mismatch term \(\one\{a_t\ne b_t\}\), not to the calendar distance between
adoption dates.  Under Assumptions~\ref{ass:finite}--\ref{ass:rho}, the
proposed state space reduces to the absorbing event-history state used by
\citet{SunAbraham2021} and \citet{CallawaySantAnna2021}, with no repeated-spell
carryover coordinates.
\end{corollary}

\section{Proof-sketch route}
The finite-horizon route is to view the latent conditional outcome means as a
finite metric-extension problem on the treatment-history graph whose edge
lengths are \(d_{\rm sp}\).  The candidate lower and upper node values are the
McShane and Whitney Lipschitz extensions of the observed regressions, clipped to
\([0,1]\); the Robins recursion then turns nodewise envelopes into lower and
upper regime means by monotonicity of finite sums and conditional expectations.
Sharpness requires the nontrivial step: prove that the nodewise extremal
extensions can be pasted into a single latent joint law with the observed
factual margins and transition kernel, or identify the additional coupling
faces if pasteability fails.  The smallest boundary case to enumerate is
\(T=3\) with paths \(010\) and \(101\), because this is the first horizon where
two spell boundaries can interact with the same endpoint.  The long-run route
then applies finite-state Markov reward arguments and support-function
continuity to exchange Cesaro limits with the finite-horizon lower and upper
recursions.

\section{Honest scope flags}
The endpoint nesting result is labelled as a theorem because it follows from
the definitions of the lower and upper envelopes.  The sharpness and long-run
claims are conjectures: the proposal has not proved global pasteability of the
McShane/Whitney extremal completions, and the \(T=3\) two-boundary case may
reveal additional coupling inequalities.  The phrase "Han-Yao-Hsu (2024)" in
the topic was not verified as a stable bibliographic anchor by the Stage -1.1
scout; this draft therefore cites the verified Han dynamic-treatment papers and
does not rely on an unverified paper claim.  The proposal assumes treatment
affects future covariates only through the Robins transition-stability
restriction; relaxing that would turn the current interval into an outer bound
unless transition laws are bounded as well.  No reviewer iterations have yet
withdrawn any claim.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft of the reversible-spell Lipschitz
  envelope proposal; prior verdict: none.
\item v2 (revise) --- added the Lipschitz partial-ID and dynamic path-effect
  comparators, repaired support/envelope typing, clarified the
  \(\rho=\infty\) endpoint, corrected the absorbing-path metric reduction, and
  typed the long-run law as \(P_\infty\) or a compatible sequence; prior
  verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and Sant'Anna, P. H. C. (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics}, 225(2), 200--230.
doi:10.1016/j.jeconom.2020.12.001.

\bibitem[Chernozhukov et~al.(2013)]{ChernozhukovFernandezValHahnNewey2013}
Chernozhukov, V., Fernandez-Val, I., Hahn, J., and Newey, W. (2013).
Average and quantile effects in nonseparable panel models.
\emph{Econometrica}, 81(2), 535--580.
doi:10.3982/ECTA8405.

\bibitem[de Chaisemartin and d'Haultfoeuille(2024)]{DeChaisemartinDHaultfoeuille2024}
de Chaisemartin, C. and d'Haultfoeuille, X. (2024).
Difference-in-differences estimators of intertemporal treatment effects.
\emph{Review of Economics and Statistics}, 1--45.
doi:10.1162/rest\_a\_01414.

\bibitem[Diemer et~al.(2024)]{DiemerShiSwanson2024}
Diemer, E. W., Shi, J., and Swanson, S. A. (2024).
Partial identification of the effects of sustained treatment strategies.
\emph{Epidemiology}, 35(3).
doi:10.1097/EDE.0000000000001721.

\bibitem[Bojinov et~al.(2021)]{BojinovRambachanShephard2021}
Bojinov, I., Rambachan, A., and Shephard, N. (2021).
Panel experiments and dynamic causal effects: A finite population perspective.
\emph{Quantitative Economics}, 12(4), 1171--1196.

\bibitem[Han(2021)]{Han2021}
Han, S. (2021).
Identification in nonparametric models for dynamic treatment effects.
\emph{Journal of Econometrics}, 225(1), 132--147.
doi:10.1016/j.jeconom.2019.08.014.

\bibitem[Han and Yang(2024)]{HanYang2024}
Han, S. and Yang, S. (2024).
A computational approach to identification of treatment effects for policy
evaluation.
\emph{Journal of Econometrics}, 240(1), 105680.
doi:10.1016/j.jeconom.2024.105680.

\bibitem[Imai et~al.(2023)]{ImaiKimWang2023}
Imai, K., Kim, I. S., and Wang, E. (2023).
Matching methods for causal inference with time-series cross-sectional data.
\emph{American Journal of Political Science}, 67(3), 587--605.

\bibitem[Jun et~al.(2016)]{JunLeeShin2016}
Jun, S. J., Lee, Y., and Shin, Y. (2016).
Treatment effects with unobserved heterogeneity: A set identification approach.
\emph{Journal of Business \& Economic Statistics}, 34(2), 302--311.
doi:10.1080/07350015.2015.1044008.

\bibitem[Kim et~al.(2018)]{KimKwonKwonLee2018}
Kim, W., Kwon, K., Kwon, S., and Lee, S. (2018).
The identification power of smoothness assumptions in models with
counterfactual outcomes.
\emph{Quantitative Economics}, 9(2), 617--642.

\bibitem[Robins(1986)]{Robins1986}
Robins, J. M. (1986).
A new approach to causal inference in mortality studies with a sustained
exposure period: Application to control of the healthy worker survivor effect.
\emph{Mathematical Modelling}, 7(9--12), 1393--1512.
doi:10.1016/0270-0255(86)90088-6.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021}
Sun, L. and Abraham, S. (2021).
Estimating dynamic treatment effects in event studies with heterogeneous
treatment effects.
\emph{Journal of Econometrics}, 225(2), 175--199.
doi:10.1016/j.jeconom.2020.09.006.
\end{thebibliography}

\end{document}
