\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{stat\_policy\_regret\_margin\_overlap} / \texttt{v1}%
  \\ \large\textit{Calibrated offline policy regret under margin and one-sided overlap decay}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---

\begin{abstract}
This note studies offline binary policy learning under unconfoundedness,
bounded outcomes, a Tsybakov decision-margin condition, one-sided polynomial
overlap decay near the decision boundary, and finite-VC policy complexity.
The causal estimand is welfare regret,
\[
R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)
      =E_P[|\tau_P(X)|\one\{\pi(X)\ne\pi_P^*(X)\}],
\]
where \(\tau_P(x)=E_P[Y(1)-Y(0)\mid X=x]\) and
\(\pi_P^*(x)=\one\{\tau_P(x)\ge0\}\).  Identification of \(\tau_P\) is taken
as given by consistency and unconfoundedness; the contribution is the
statistical rate for learning a low-regret policy from offline data.

The lower-bound layer optimizes an active block with contrast height \(h\),
covariate mass \(h^\alpha\), and weak-arm propensity \(h^\beta\).  Membership
in the one-sided overlap class forces
\[
\beta\le \beta_{\alpha,\gamma}:=
\begin{cases}
0, & \gamma=0,\\
\alpha\gamma/(\alpha+1), & \gamma>0.
\end{cases}
\]
The least informative admissible layer has one-observation information
\(h^{2+\alpha+\beta_{\alpha,\gamma}}\) and regret separation
\(h^{1+\alpha}\), giving the converse exponent
\[
r_*(\alpha,\gamma)=
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
The note proves a two-point lower bound at this exponent over the full
weak-overlap law class.  The construction explicitly perturbs the outcome
regression of the weak arm, so the chi-square information is
\(h^\alpha h^{\beta_{\alpha,\gamma}}h^2\), not \(h^\alpha h^2\).

The achievability theorem is stated in a primitive known-logging finite-cell
regime.  The logging propensity is known exactly on a known finite partition,
the outcome regressions are cell-constant, the estimator uses truncated
cross-fitted empirical cell means, and a displayed rare-arm cell-count
envelope makes the clipped-score drift a derived quantity.  This upper theorem
does not require the one-sided overlap-decay condition; the parameter
\(\gamma\) enters the statement only through the deterministic clipping
sequence \(q_n^*=q(h_n^*)\).  No high-level target-rate nuisance assumption
and no sup-norm propensity localization are assumed.  The resulting
data-and-design estimator is a target-preserving clipped-AIPW empirical
welfare maximizer with
\[
h_n^*=n^{-1/(2+\alpha+\beta_{\alpha,\gamma})},\qquad
q_n^*=q(h_n^*),
\]
and expected regret bounded by
\[
\bar\rho_n^*
=(h_n^*)^{1+\alpha}
\{\log(e/(h_n^*)^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}.
\]
Thus the upper theorem matches the lower polynomial exponent on any
uniform primitive finite-cell collection that is also rich enough to contain
the weak-overlap witnesses.  Over the larger weak-overlap class with unknown
nuisance functions, the exact data-only feasible rate remains open; in
particular, ordinary \(L_2(P_X)\) propensity control alone creates an
estimated-clipping variance term that is not removed by the primitive
assumptions of the full lower-bound class.
\end{abstract}

\section{Introduction}
Observational policy learning asks for a treatment rule that improves welfare
using fixed offline data.  In the binary-treatment setting the welfare
criterion is driven by the sign of the conditional causal contrast
\[
\tau_P(x)=E_P[Y(1)-Y(0)\mid X=x].
\]
Unconfoundedness identifies this contrast through observed conditional means.
The statistical problem is hardest where \(|\tau_P(x)|\) is small and the arm
that reveals the sign is rare.  A margin condition limits the mass near
\(\tau_P=0\), while the one-sided overlap condition limits how much of that
near-boundary mass can also have a small weak-arm propensity.

The weak-arm layer must be optimized under the overlap-tail constraint.  If
an active block has margin height \(h\), mass \(h^\alpha\), and weak-arm
propensity \(h^\beta\), then membership in the overlap class requires
\[
\beta\le \beta_{\alpha,\gamma}:=\alpha\gamma/(\alpha+1)
\quad(\gamma>0).
\]
Balancing
\[
n h^{2+\alpha+\beta_{\alpha,\gamma}}\asymp1
\]
gives the converse exponent
\[
r_*(\alpha,\gamma)=
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]

The upper theorem uses a cross-fitted clipped-AIPW welfare score.  Clipping
keeps the score variance at order \(q_n^{-1}\) when the logging propensity is
known exactly.  Because clipping is not fully orthogonal to arbitrary outcome
regression error on the clipped weak-arm layer, the outcome nuisance part
must be controlled by primitive sample-size information.  The primitive
finite-cell condition below provides this information directly: on a known
finite partition, the local rare-arm cell masses and arm probabilities imply
the \(L_1(P_X)\) clipped-layer accuracy of empirical cell means.  This is the
only nuisance input consumed by the upper proof.  The upper proof uses
causal sampling, boundedness, margin localization, finite VC complexity,
known logging, and this finite-cell envelope; it does not use the overlap-tail
inequality.

\paragraph{Motivating conjecture(s).}
Let \(\delta_{\alpha,\gamma}=(\gamma-\alpha)_+\).

\textbf{Conjecture 1.} (Upper-rate claim.) Under
Assumptions~\ref{ass:causal-sampling}--\ref{ass:nuisance}, the clipped-AIPW
ERM with \(t_n=n^{-s(\alpha,\gamma)}\) satisfies
\[
\sup_{P\in\mathcal{P}_{\alpha,\gamma}}
E_P R_P(\widehat\pi_{t_n})
\le C n^{-r(\alpha,\gamma)}
\]
for \(r(\alpha,\gamma)=(1+\alpha)/(2+\alpha+\delta_{\alpha,\gamma})\), where
\(\delta_{\alpha,\gamma}=(\gamma-\alpha)_+\).

\textbf{Conjecture 2.} (Calibrated lower claim.) Under
Assumptions~\ref{ass:causal-sampling}, \ref{ass:margin},
\ref{ass:overlap-decay}, \ref{ass:primitive-cube}, and
\ref{ass:calibrated-overlap-richness}, for
\(h_n=n^{-1/(2+\alpha+\delta_{\alpha,\gamma})}\) there exist paired laws
\(P_{n,+},P_{n,-}\) in a calibrated subclass with active-block mass
\(h_n^\alpha\), contrast height \(h_n\), weak-arm propensity
\(h_n^{\delta_{\alpha,\gamma}}\), one-observation Hellinger radius
\(h_n^{2+\alpha+\delta_{\alpha,\gamma}}\), and regret separation
\(h_n^{1+\alpha}\).

The verdict is as follows.  Conjecture 1 is false as a full-class no-log
claim whenever
\[
\frac{1+\alpha}{2+\alpha+\delta_{\alpha,\gamma}}
>
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
At \((\alpha,\gamma)=(2,2)\), it predicts \(3/4\), while the full-class
two-point witness forces \(9/16\).  The primitive finite-cell upper theorem
proved here is instead
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\le C\bar\rho_n^*
\]
for uniform known-logging finite-cell collections \(\mathcal Q\).  It matches
the lower polynomial exponent \(r_*(\alpha,\gamma)\) up to the finite-VC
logarithmic factor whenever such a collection contains the calibrated
weak-arm witnesses.  Conjecture 2 is valid after replacing
\(\delta_{\alpha,\gamma}\) by the largest overlap-admissible weak-arm exponent
\(\beta_{\alpha,\gamma}\) and placing the sign-varying regression on the weak
arm itself.

\section{Related work and positioning}
Athey and Wager (2021) provide the observational policy-learning template:
the causal target is a policy welfare, the empirical criterion is built from
doubly robust scores, and the policy search is restricted by a manageable
complexity condition.  Kitagawa and Tetenov (2018) give the empirical welfare
maximization perspective for treatment choice.  Luedtke and Chambaz (2017)
show how a margin condition can convert score accuracy into fast policy-regret
rates.  Chernozhukov et al. (2018) provide the cross-fitting and orthogonal
score template used to separate nuisance learning from validation-sample
empirical processes.

Ma, Sant'Anna, Sasaki, and Ura (2023) separate variance stabilization from
target-changing trimming for scalar causal estimands under weak overlap.  The
present note uses target-preserving clipping for policy regret.  Kallus
(2017) gives an alternative variance-stabilized policy-learning route.  Jin,
Ren, Yang, and Wang (2022) and Zhan, Ren, Athey, and Zhou (2021) show why
scarce treatment observations matter for policy learning, though their
scarcity mechanisms differ from the fixed offline overlap surface studied
here.  D'Amour, Ding, Feller, Lei, and Sekhon (2021) motivate replacing
strict overlap by tail and diagnostic conditions in observational studies.

Audibert and Tsybakov (2007) supply the lower-bound grammar: localized
finite-cell sign perturbations under a margin condition.  The additional
ingredient here is that the lower-bound cells must satisfy the same
one-sided overlap-decay envelope as every other member of the law class.
Standard VC maximal inequalities, as in Vapnik and Chervonenkis (1971) and
van der Vaart and Wellner (1996), supply the finite-VC localized empirical
process bound, with the logarithmic entropy factor retained.

\section{Formal setup}
Let \(O=(X,A,Y)\sim P\), where \(A\in\{0,1\}\) and \(Y\in[-1,1]\).  Potential
outcomes \(Y(0),Y(1)\) satisfy consistency and unconfoundedness.  Define
\[
e_P(x)=P(A=1\mid X=x),\qquad
\mu_a(x)=E_P[Y\mid A=a,X=x],
\]
\[
\tau_P(x)=\mu_1(x)-\mu_0(x)=E_P[Y(1)-Y(0)\mid X=x].
\]
A deterministic policy \(\pi:\mathcal X\to\{0,1\}\) has normalized welfare
\[
V_P(\pi)=E_P[\pi(X)\tau_P(X)].
\]
The optimal policy is
\[
\pi_P^*(x)=\one\{\tau_P(x)\ge0\},
\]
and its regret is \(R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)\).

Let
\[
p_P(x)=\min\{e_P(x),1-e_P(x)\}.
\]
For \(\gamma>0\) define
\[
\beta_{\alpha,\gamma}=\frac{\alpha\gamma}{\alpha+1},
\]
and set \(\beta_{\alpha,0}=0\).  Let
\[
D_{\alpha,\gamma}=2+\alpha+\beta_{\alpha,\gamma},\qquad
h_n^*=n^{-1/D_{\alpha,\gamma}},\qquad
r_*(\alpha,\gamma)=\frac{1+\alpha}{D_{\alpha,\gamma}}.
\]
Define
\[
L_n^*=\log\{e/(h_n^*)^{1+\alpha}\},\qquad
a_\alpha=\frac{1+\alpha}{2+\alpha},
\]
and
\[
\bar\rho_n^*=(h_n^*)^{1+\alpha}(L_n^*)^{a_\alpha}.
\]
Fix a strict-overlap clipping constant \(q_0\in(0,1/8]\).  For
\(h\in(0,1)\), define
\[
q(h)=
\begin{cases}
q_0, & \beta_{\alpha,\gamma}=0,\\
h^{\beta_{\alpha,\gamma}}, & \beta_{\alpha,\gamma}>0.
\end{cases}
\]
The overlap-calibrated lower display and the finite-cell upper display use
\[
q_n^*=q(h_n^*).
\]
This convention covers the strict-overlap case \(\gamma=0\) and the
\(\alpha=0,\gamma>0\) case, where \(\beta_{\alpha,\gamma}=0\).

For a nuisance tuple \(\eta=(\mu_0,\mu_1,e)\) and a lower clipping level
\(q\in(0,1/2]\), define
\[
e_q(x;\eta)=\min\{1-q,\max\{q,e(x)\}\}
\]
and the clipped AIPW score
\[
\Gamma_q(O;\eta)=\mu_1(X)-\mu_0(X)
+\frac{A}{e_q(X;\eta)}\{Y-\mu_1(X)\}
-\frac{1-A}{1-e_q(X;\eta)}\{Y-\mu_0(X)\}.
\]
The oracle nuisance tuple is \(\eta_P=(\mu_0,\mu_1,e_P)\).  Its score
\(\Gamma_q^\circ(O)=\Gamma_q(O;\eta_P)\) satisfies
\[
E_P[\Gamma_q^\circ(O)\mid X]=\tau_P(X)
\]
for every \(q\in(0,1/2]\).

The feasible score is formed from a fixed nonrandom \(K\)-fold partition
\(I_1,\ldots,I_K\) of \(\{1,\ldots,n\}\), with \(K\) fixed,
\(n_k=|I_k|\), \(w_k=n_k/n\), and \(c_Kn\le n_k\le C_Kn\).  For
\(i\in I_k\), let
\[
\widehat\eta^{(-k)}=(\widehat\mu_0^{(-k)},\widehat\mu_1^{(-k)},e_P)
\]
where \(e_P\) is known by design in the primitive finite-cell regime and the
outcome regressions are estimated from the training sigma-field
\(\mathcal T_k=\sigma(O_i:i\notin I_k)\), together with any independent
algorithmic randomization.  Define
\[
\widehat\Gamma_{q,k}(O)=\Gamma_q(O;\widehat\eta^{(-k)}).
\]
The known-logging clipped-AIPW empirical welfare maximizer is
\[
\widehat\pi_{n,q}\in\arg\max_{\pi\in\Pi}
\widehat V_{n,q}(\pi),\qquad
\widehat V_{n,q}(\pi)=
\sum_{k=1}^K w_k\, n_k^{-1}\sum_{i\in I_k}
\pi(X_i)\widehat\Gamma_{q,k}(O_i).
\]
The overlap-calibrated estimator uses \(q=q_n^*\) and writes
\[
\widehat\pi_{n}^{\mathsf F}:=\widehat\pi_{n,q_n^*}.
\]
Measurable selectors are assumed when an argmax is not unique.

The margin-overlap law class is
\[
\mathcal P_{\alpha,\gamma}
=\{P:\text{Assumptions~\ref{ass:causal-sampling},
\ref{ass:margin}, \ref{ass:overlap-decay}, and
\ref{ass:policy-class} hold with exponents }\alpha,\gamma\}.
\]
This class fixes the exponents \(\alpha,\gamma\) but not the numerical
margin, overlap, policy-complexity, fold, or nuisance-structure constants.

\begin{definition}[Uniform primitive finite-cell feasible collection]\label{def:uniform-feasible-collection}
Fix \(\alpha,\gamma\), the clipping sequence \(q_n^*\), the rate sequence
\(\bar\rho_n^*\), the policy class \(\Pi\), the fixed fold partition rule,
and the cell-mean nuisance learners.  A law collection \(\mathcal Q\) is
called \(\kappa\)-uniform primitive finite-cell feasible if every
\(P\in\mathcal Q\) satisfies Assumptions~\ref{ass:causal-sampling},
\ref{ass:margin}, \ref{ass:policy-class}, and \ref{ass:nuisance} with all
numerical constants bounded by a finite vector \(\kappa\), and the fold sizes
satisfy the same constants \(c_K,C_K,K\).  The one-sided overlap-decay
Assumption~\ref{ass:overlap-decay} is not part of this achievability-side
definition.
\end{definition}

For any law collection \(\mathcal Q\), define the policy-regret minimax risk
\[
\mathfrak M_n(\mathcal Q)
=\inf_{\widehat\pi}
\sup_{P\in\mathcal Q}E_P R_P(\widehat\pi),
\]
where the infimum ranges over measurable data-dependent policies taking
values in \(\Pi\).  The full weak-overlap risk is
\[
\mathfrak M_n(\alpha,\gamma)=\mathfrak M_n(\mathcal P_{\alpha,\gamma}).
\]
The upper theorem is stated for collections satisfying
Definition~\ref{def:uniform-feasible-collection}.  Such collections need not
be subsets of \(\mathcal P_{\alpha,\gamma}\).  The full weak-overlap class
\(\mathcal P_{\alpha,\gamma}\) is not itself an achievability class unless
these primitive nuisance-learnability conditions are also supplied.

\paragraph{Locked parameters.}
\begin{itemize}[leftmargin=*]
  \item \texttt{(qid, specialization) = (stat\_policy\_regret\_margin\_overlap, v1).}
  \item \texttt{Anchor cluster = Stat.}
  \item \texttt{Statistical model and causal estimand: iid observations O\_i=(X\_i,A\_i,Y\_i), A\_i in \{0,1\}, unconfoundedness, consistency, bounded outcomes, and known-or-estimable propensity e\_P(x)=P(A=1|X=x). The causal contrast is tau\_P(x)=E[Y(1)-Y(0)|X=x]. For a policy pi:X->\{0,1\}, V\_P(pi)=E[pi(X)tau\_P(X)] and R\_P(pi)=V\_P(pi\_P\textasciicircum{}*)-V\_P(pi), where pi\_P\textasciicircum{}*(x)=1\{tau\_P(x)>=0\}.}
  \item \texttt{Sampling model: iid draws from P in a fixed offline logging design; no adaptive exploration.}
  \item \texttt{Target object: the information-theoretic minimax expected welfare-regret exponent over the one-sided overlap-decay class, r\_*(alpha,gamma)=(1+alpha)/(2+alpha+beta\_{alpha,gamma}) with beta\_{alpha,gamma}=alpha gamma/(alpha+1) for gamma>0 and beta\_{alpha,0}=0.}
  \item \texttt{Estimator: a data-and-design cross-fitted target-preserving clipped-AIPW-score empirical welfare maximizer using the overlap-calibrated clipping level q\_n\textasciicircum{}*=q\_0 whenever beta\_{alpha,gamma}=0 and q\_n\textasciicircum{}*=(h\_n\textasciicircum{}*)\textasciicircum{}\{beta\_{alpha,gamma}\} otherwise, with known logging and finite-cell outcome learners under the primitive achievability theorem.}
  \item \texttt{Matching converse: a primitive localized two-point construction whose cube mass, contrast height, weak-arm propensity height, and chi-square divergence radius are calibrated to r\_*(alpha,gamma), with the sign-varying regression placed on the weak arm.}
\end{itemize}

\section{Assumptions}
\begin{assumption}[Causal sampling and bounded outcomes]\label{ass:causal-sampling}
The observations \(O_1,\ldots,O_n\) are iid from \(P\).  Consistency and
unconfoundedness hold, \(Y(a)\in[-1,1]\), and \(0<e_P(X)<1\) almost surely.
The conditional means \(\mu_a(x)=E_P[Y\mid A=a,X=x]\) exist as measurable
versions.
\end{assumption}

\begin{assumption}[Tsybakov decision margin and canonical zero-effect region]\label{ass:margin}
There are constants \(0<C_m<\infty\), \(u_0>0\), and \(\alpha\ge0\) such that
\[
P(0<|\tau_P(X)|\le u)\le C_m u^\alpha
\quad\text{for all }0<u\le u_0.
\]
In addition, either \(P_X\{\tau_P(X)=0\}=0\), or every
\(\pi\in\Pi\) satisfies \(\pi(x)=\pi_P^*(x)\) for \(P_X\)-almost every
\(x\) with \(\tau_P(x)=0\).
\end{assumption}

\begin{assumption}[One-sided polynomial overlap decay]\label{ass:overlap-decay}
Let \(p_P(x)=\min\{e_P(x),1-e_P(x)\}\).  There are constants
\(C_o,c_o>0\) and \(\gamma\ge0\) such that
\[
P\{p_P(X)\le v,\;0<|\tau_P(X)|\le u\}
  \le C_o u^\alpha v^{1/\gamma}
\]
for all \(0<v\le c_o u^\gamma\), with the convention that \(v^{1/\gamma}=1\)
when \(\gamma=0\).  In the \(\gamma=0\) case, the condition is read as a
strict-overlap condition on the strict-margin region.
\end{assumption}

\begin{assumption}[Calibrated overlap-richness for the delta witness]\label{ass:calibrated-overlap-richness}
Let \(\delta_{\alpha,\gamma}=(\gamma-\alpha)_+\).  When the
\(\delta_{\alpha,\gamma}\)-weak-arm witness in Conjecture 2 is considered,
the exponents satisfy
\[
(\gamma-\alpha)_+
\le \frac{\alpha\gamma}{\alpha+1}.
\]
Equivalently, when \(\gamma>\alpha\), this condition is
\(\gamma\le\alpha(\alpha+1)\).
\end{assumption}

\begin{remark}
Assumption~\ref{ass:calibrated-overlap-richness} is the exponent condition
under which the \(\delta_{\alpha,\gamma}\)-calibrated witness described in
Conjecture 2 is overlap-admissible.  The main lower theorem below does not
need this condition because it uses the largest admissible weak-arm exponent
\(\beta_{\alpha,\gamma}=\alpha\gamma/(\alpha+1)\) when \(\gamma>0\), and
\(\beta_{\alpha,0}=0\) when \(\gamma=0\).
\end{remark}

\begin{assumption}[Policy class entropy]\label{ass:policy-class}
The policy class \(\Pi\) consists of measurable deterministic policies, has
finite VC dimension \(d_\Pi<\infty\), and \(\pi_P^*\in\Pi\) for each law
\(P\) in the law collection to which the theorem is applied.
\end{assumption}

\begin{assumption}[Primitive known-logging finite-cell nuisance structure]\label{ass:nuisance}
Fix the sequence \(q_n^*\), the logarithmic scale \(L_n^*\), and
\(\bar\rho_n^*\).  For every \(n\) and every \(P\) in the upper-bound
collection there is a known finite measurable partition
\(\mathscr C_n\) of \(\mathcal X\), not depending on the outcomes in the
validation fold, such that:
\[
|\mathscr C_n|\le \exp(C_{\mathscr C}L_n^*).
\]
For each cell \(C\in\mathscr C_n\), the functions
\(e_P,\mu_0,\mu_1\) are constant on \(C\), and the logging propensity
\(e_P\) is known to the learning rule.  For \(a\in\{0,1\}\), write
\[
p_{a,P}(C)=P(A=a\mid X\in C),\qquad m_P(C)=P_X(C).
\]
The rare-arm cell-count envelope satisfies
\[
\Lambda_n(P):=
\sum_{a=0}^1
\sum_{\substack{C\in\mathscr C_n:\\
\min\{e_P(C),1-e_P(C)\}\le 2q_n^*}}
m_P(C)\,
\min\left\{1,
\sqrt{\frac{L_n^*}{n\,m_P(C)\,p_{a,P}(C)}}\right\}
\le C_\Lambda \bar\rho_n^*,
\]
where the summand is interpreted as \(m_P(C)\) if
\(m_P(C)p_{a,P}(C)=0\).  The learner sets
\(\widehat e^{(-k)}=e_P\) and estimates \(\mu_a\) on each cell by the
training-fold empirical mean among observations with \(A=a\), truncated to
\([-1,1]\); if the training-fold cell-arm count is zero, the truncated mean
is set to zero.
\end{assumption}

\begin{remark}
Assumption~\ref{ass:nuisance} is primitive in the sense used by the upper
proof: it specifies a known logging design, a finite cell structure, and an
explicit cell mass/sample-size envelope.  It does not assume a bound on an
estimator-determined empirical-process offset, does not impose
\(\|\widehat e-e_P\|_\infty\le c q_n\), and does not assume that an unknown
propensity estimator already attains the target regret rate.  The local
clipped-score drift is derived from the displayed cell-count envelope and
bounded-outcome concentration.
\end{remark}

\begin{assumption}[Endpoint primitive local policy richness with weak-arm perturbation]\label{ass:primitive-cube}
The policy class \(\Pi\) consists of measurable deterministic policies and has
finite VC dimension.  For each sufficiently small \(h\), there exist a
covariate probability law \(Q_h\), a measurable active block
\(B_h\subseteq\mathcal X\), a logging propensity
\(e_h:\mathcal X\to(0,1)\), a weak-arm label
\(a_h\in\{0,1\}\), and two bounded outcome regression systems indexed by
\(\sigma\in\{+,-\}\) such that
\[
c_B h^\alpha\le Q_h(B_h)\le C_B h^\alpha.
\]
The policy class \(\Pi\) can assign either treatment label on \(B_h\) while
agreeing with the common off-block label \(1\).  On \(B_h\), the weak arm has
logging probability comparable to the endpoint clipping layer \(q(h)\):
\[
c_Qq(h)\le
P(A=a_h\mid X=x)
\le C_Qq(h)
\quad\text{for all }x\in B_h.
\]
The two regression systems differ on \(B_h\) only through the weak-arm
outcome regression.  They induce treatment contrasts
\[
\tau_{h,+}(x)=h,\qquad \tau_{h,-}(x)=-h
\quad\text{for all }x\in B_h.
\]
Off \(B_h\), the propensities are bounded away from zero and one,
\[
4q_0\le e_h(x)\le 1-4q_0
\quad\text{for all }x\notin B_h,
\]
and both systems have a common off-block treatment contrast
\(\tau_0\in(0,1)\).  The witness constants can be chosen with
\(8C_BC_Q<\log 5\).
\end{assumption}

\begin{assumption}[Known-logging finite-cell witnesses]\label{ass:learnable-cube}
The witnesses in Assumption~\ref{ass:primitive-cube} can be chosen so that
\(B_h\) and \(B_h^c\) are atoms of an observed finite partition known to the
nuisance-learning procedure.  The logging propensity \(e_h\) is known by
design on this partition, and the procedure sets
\(\widehat e^{(-k)}=e_h\) on both atoms for every fold.  The outcome
regressions \(\mu_0\) and \(\mu_1\) are constant on each atom, and the
procedure uses foldwise empirical cell-mean estimators for
\(\mu_0,\mu_1\), truncated to \([-1,1]\).  The procedure is not supplied with
the sign index \(\sigma\); the active-block outcome contrast is learned only
from the training sample.
\end{assumption}

\begin{remark}
Assumption~\ref{ass:learnable-cube} is a local lower-bound witness condition.
Known logging propensities are compatible with fixed offline designs and do
not reveal the sign of the active-block treatment contrast.  The feasible
upper theorem uses Assumption~\ref{ass:nuisance}; it does not claim that
finite-cell structure is necessary for achievability.
\end{remark}

\section{Estimand-defining functional}
The causal functional is the policy welfare \(V_P(\pi)=E_P[\pi(X)\tau_P(X)]\)
and its regret
\[
R_P(\pi)=V_P(\pi_P^*)-V_P(\pi).
\]
The full-class minimax object is
\[
\mathfrak M_n(\alpha,\gamma)
=\inf_{\widehat\pi}
\sup_{P\in\mathcal P_{\alpha,\gamma}}E_P R_P(\widehat\pi).
\]
For a \(\kappa\)-uniform primitive finite-cell feasible collection
\(\mathcal Q\), the conditional achievability object is
\[
\sup_{P\in\mathcal Q}E_P R_P(\widehat\pi_n^{\mathsf F}),
\]
where \(\mathcal Q\) satisfies the common-constant requirements of
Definition~\ref{def:uniform-feasible-collection}.  The data-and-design
estimator is
\[
\widehat\pi_n^{\mathsf F}
\in\arg\max_{\pi\in\Pi}
\sum_{k=1}^K w_k\,n_k^{-1}\sum_{i\in I_k}
\pi(X_i)\Gamma_{q_n^*}(O_i;\widehat\eta^{(-k)}).
\]
The target rate object proved for this estimator under the primitive
finite-cell nuisance structure is
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\lesssim
\bar\rho_n^*.
\]
This upper object does not require \(P\in\mathcal P_{\alpha,\gamma}\); it
requires only the primitive finite-cell feasibility conditions.  The converse
object is
\[
\mathfrak M_n(\alpha,\gamma)
\gtrsim n^{-r_*(\alpha,\gamma)}.
\]
If a \(\kappa\)-uniform primitive finite-cell feasible collection
\(\mathcal Q\) contains the known-logging finite-cell witness sequence, then
the same polynomial lower exponent applies to \(\mathfrak M_n(\mathcal Q)\).

\section{Target causal estimand}
For each deterministic \(\pi\in\Pi\), the causal welfare increment is
\[
V_P(\pi)=E_P[Y(\pi(X))-Y(0)]
=E_P[\pi(X)\{Y(1)-Y(0)\}]
=E_P[\pi(X)\tau_P(X)].
\]
The optimal policy is \(\pi_P^*(x)=\one\{\tau_P(x)\ge0\}\), and the loss is
the welfare regret \(R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)\).  The clipping level,
cross-fitting scheme, known logging design, cell partition, empirical cell
means, empirical process, VC entropy factor, and weak-arm exponent are
statistical devices used to learn a good policy; they are not causal
estimands.

\section{Main theorems}
\begin{theorem}[Known-logging finite-cell clipped-score upper bound]\label{thm:feasible-upper-log}\label{conj:upper-rate}
Let \(\mathcal Q\) be a \(\kappa\)-uniform primitive finite-cell feasible
collection in the sense of Definition~\ref{def:uniform-feasible-collection},
and let the fold number \(K\) be fixed.  Set
\[
h_n^*=n^{-1/(2+\alpha+\beta_{\alpha,\gamma})},
\qquad q_n^*=q(h_n^*),
\qquad
L_n^*=\log\{e/(h_n^*)^{1+\alpha}\},
\]
and
\[
\bar\rho_n^*
=
(h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}.
\]
Let \(\widehat\pi_n^{\mathsf F}\) be the cross-fitted clipped-AIPW empirical
welfare maximizer defined in the formal setup, with known logging propensity
and truncated foldwise empirical cell-mean outcome regressions.  Then there
are constants \(C<\infty\) and \(N<\infty\), depending only on \(\kappa\),
\(\alpha\), and \(\gamma\), such that for all \(n\ge N\),
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\le
C\bar\rho_n^*.
\]
Equivalently,
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\le
C n^{-r_*(\alpha,\gamma)}
(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
The statement is an achievability theorem for primitive known-logging
finite-cell collections.  It does not impose the overlap-decay
Assumption~\ref{ass:overlap-decay} on \(\mathcal Q\), and it is not an upper
theorem over the larger class \(\mathcal P_{\alpha,\gamma}\) without the
nuisance structure in Assumption~\ref{ass:nuisance}.
\end{theorem}

\begin{theorem}[Weak-overlap margin converse]\label{thm:lower-full-class}\label{conj:lower-calibration}
Suppose Assumption~\ref{ass:primitive-cube} holds.  Let
\[
\beta=\beta_{\alpha,\gamma},\qquad
h_n=n^{-1/(2+\alpha+\beta)},\qquad
q_n=q(h_n).
\]
For all sufficiently large \(n\), there are paired laws
\(P_{n,+},P_{n,-}\in\mathcal P_{\alpha,\gamma}\) with common covariate law,
common logging propensity, common law off an active block \(B_n\), a weak-arm
label \(a_n\in\{0,1\}\), a fixed common off-block contrast \(\tau_0\in(0,1)\),
and
\[
P_X(B_n)\asymp h_n^\alpha,\qquad
\tau_{P_{n,+}}(x)=h_n,\qquad
\tau_{P_{n,-}}(x)=-h_n
\quad (x\in B_n),
\]
\[
\tau_{P_{n,+}}(x)=\tau_{P_{n,-}}(x)=\tau_0
\quad (x\notin B_n),
\]
\[
P_{n,\sigma}(A=a_n\mid X=x)\asymp q_n
\quad (x\in B_n,\ \sigma\in\{+,-\}).
\]
The two laws differ on \(B_n\) only in the weak-arm outcome regression.  They
satisfy
\[
n\,\chi^2(P_{n,+}\|P_{n,-})\le C_\chi,
\qquad
\chi^2(P_{n,+}\|P_{n,-})=O(h_n^{2+\alpha+\beta}),
\]
and
\[
\inf_{\pi\in\Pi}
\max_{\sigma\in\{+,-\}}R_{P_{n,\sigma}}(\pi)
\asymp h_n^{1+\alpha}.
\]
Consequently,
\[
\mathfrak M_n(\alpha,\gamma)\ge c n^{-r_*(\alpha,\gamma)}.
\]
If Assumption~\ref{ass:learnable-cube} also holds, then these same witness
laws satisfy the primitive known-logging finite-cell nuisance structure of
Assumption~\ref{ass:nuisance} with common constants.
\end{theorem}

\begin{corollary}[Primitive finite-cell feasible bracket]\label{cor:feasible-bracket}
Let \(\mathcal Q\) be a \(\kappa\)-uniform primitive finite-cell feasible
collection in the sense of Definition~\ref{def:uniform-feasible-collection}.
Then there are constants \(C<\infty\) and \(N<\infty\), depending only on
\(\kappa,\alpha,\gamma\), such that for all \(n\ge N\),
\[
\mathfrak M_n(\mathcal Q)
\le
C\bar\rho_n^*.
\]
If, in addition, Assumption~\ref{ass:primitive-cube} holds and \(\mathcal Q\)
contains the corresponding two witness laws for all sufficiently large \(n\),
then there are constants \(0<c\le C<\infty\) and \(N<\infty\) such that for all
\(n\ge N\),
\[
c n^{-r_*(\alpha,\gamma)}
\le
\mathfrak M_n(\mathcal Q)
\le
C n^{-r_*(\alpha,\gamma)}
(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
Thus the polynomial exponent \(r_*(\alpha,\gamma)\) is matched on primitive
known-logging finite-cell collections that contain the weak-overlap witnesses.
The logarithmic factor is the finite-VC achievability multiplier; a matching
logarithmic lower bound is not implied by finite VC dimension alone.
\end{corollary}

\section{Interpretation}
The full-class converse is controlled by the largest weak-arm exponent
compatible with the overlap tail.  A block with \(|\tau|\asymp h\), mass
\(h^\alpha\), and weak-arm propensity \(h^\beta\) is included in the event
\(\{p_P(X)\le v,0<|\tau_P(X)|\le u\}\) when
\[
v\asymp h^\beta,\qquad u\asymp h^{\beta/\gamma}.
\]
The overlap envelope then requires
\[
h^\alpha\lesssim u^\alpha v^{1/\gamma}
\asymp h^{(\alpha+1)\beta/\gamma},
\]
which is equivalent to
\(\beta\le\alpha\gamma/(\alpha+1)\).  The least informative admissible layer
uses equality.  It has one-observation information
\[
h^\alpha h^{\beta_{\alpha,\gamma}}h^2
=h^{2+\alpha+\beta_{\alpha,\gamma}}
\]
because the sign-varying outcome regression is placed on the weak arm.  Its
regret separation is \(h^{1+\alpha}\), giving \(r_*\).

For the upper theorem, known logging removes estimated-clipping instability:
with \(\widehat e=e_P\), the conditional score variance on a policy
disagreement set \(D\) is of order
\[
q_n^{-1}P_X(D).
\]
Margin localization gives
\[
P_X(D)\lesssim R_P(\pi)^{\alpha/(1+\alpha)}.
\]
The localized finite-VC fixed point is therefore
\[
\rho
\asymp
\sqrt{\frac{q_n^{-1}\rho^{\alpha/(1+\alpha)}
\log(e/\rho)}{n}},
\]
which closes at
\[
\rho=(h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}
=\bar\rho_n^*.
\]
The primitive finite-cell envelope in Assumption~\ref{ass:nuisance} supplies
the remaining ingredient: the clipped-score drift from outcome-regression
estimation on weak-arm cells is at most \(C\bar\rho_n^*\).  No step in this
upper argument uses the overlap-tail inequality
\(P\{p_P(X)\le v,0<|\tau_P(X)|\le u\}\le C_o u^\alpha v^{1/\gamma}\).

For the lower-bound witnesses compatible with the primitive finite-cell
upper regime, the active weak-arm training count is calibrated to be of
order \(h^{-2}\).  A cell-mean threshold of order
\(h\{\log(e/h^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}\) therefore has failure
probability no larger than the feasible scale, while multiplying by the
active mass \(h^\alpha\) gives the local \(L_1(P_X)\) contribution
\(\bar\rho_n^*\).

\section{Step-by-step proof}
\subsection*{Supporting lemmas}
\begin{lemma}[Welfare-regret identity]\label{lem:welfare-identity}
Under Assumption~\ref{ass:causal-sampling}, for every measurable
deterministic policy \(\pi\),
\[
R_P(\pi)=E_P[|\tau_P(X)|\one\{\pi(X)\ne\pi_P^*(X)\}].
\]
\end{lemma}
\begin{proof}
By definition,
\[
R_P(\pi)
=E_P[(\pi_P^*(X)-\pi(X))\tau_P(X)].
\]
If \(\tau_P(x)\ge0\), then \(\pi_P^*(x)=1\), and
\[
(1-\pi(x))\tau_P(x)
=|\tau_P(x)|\one\{\pi(x)\ne1\}.
\]
If \(\tau_P(x)<0\), then \(\pi_P^*(x)=0\), and
\[
-\pi(x)\tau_P(x)
=|\tau_P(x)|\one\{\pi(x)\ne0\}.
\]
If \(\tau_P(x)=0\), both sides are zero.  Taking expectations proves the
claim.
\end{proof}

\begin{lemma}[Margin localization]\label{lem:margin-localization}
Under Assumption~\ref{ass:margin}, for every measurable policy \(\pi\in\Pi\),
\[
P_X\{\pi(X)\ne\pi_P^*(X)\}
\le C_P R_P(\pi)^{\alpha/(1+\alpha)}.
\]
If the margin constants are common over a law collection, then \(C_P\) is
common over that collection.
\end{lemma}
\begin{proof}
Let \(D_\pi=\{x:\pi(x)\ne\pi_P^*(x)\}\).  The zero-effect clause in
Assumption~\ref{ass:margin} removes disagreements on \(\{\tau_P=0\}\).  For
any \(u\in(0,u_0]\),
\[
P_X(D_\pi)
\le
P(0<|\tau_P(X)|\le u)
+P(D_\pi\cap\{|\tau_P(X)|>u\})
\le C_m u^\alpha+\frac{R_P(\pi)}{u}.
\]
Choose \(u\asymp R_P(\pi)^{1/(1+\alpha)}\), truncated at \(u_0\).  Enlarging
the constant handles the truncation case.
\end{proof}

\begin{lemma}[Primitive cell means imply clipped-layer outcome accuracy]\label{lem:primitive-nuisance-derived}
Let Assumption~\ref{ass:nuisance} hold over a law collection \(\mathcal Q\)
with common constants.  Fix \(P\in\mathcal Q\) and a fold \(k\).  There is an
event \(G_{n,k}\in\mathcal T_k\) such that
\[
P^n(G_{n,k}^c)\le C\bar\rho_n^*
\]
and, on \(G_{n,k}\),
\[
|\widehat\mu_a^{(-k)}(x)|\le1,\qquad \widehat e^{(-k)}(x)=e_P(x),
\]
and
\[
\sum_{a=0}^1
E_{P_X}\!\left[
|\widehat\mu_a^{(-k)}(X)-\mu_a(X)|
\one\{p_P(X)\le2q_n^*\}
\,\middle|\,\mathcal T_k\right]
\le C\bar\rho_n^*.
\]
\end{lemma}
\begin{proof}
The truncation gives \(|\widehat\mu_a^{(-k)}|\le1\), and the known-logging
rule gives \(\widehat e^{(-k)}=e_P\).  It remains to prove the local
outcome-regression bound.

For each cell \(C\in\mathscr C_n\) and arm \(a\), let
\[
N_{a,k}(C)=\sum_{i\notin I_k}\one\{X_i\in C,A_i=a\}.
\]
Conditional on \(N_{a,k}(C)\), Bernstein's inequality for bounded outcomes
gives
\[
\Pr\!\left(
|\widehat\mu_a^{(-k)}(C)-\mu_a(C)|
>
B\min\left\{1,\sqrt{\frac{L_n^*}{n\,m_P(C)\,p_{a,P}(C)}}\right\}
\right)
\le 2\exp(-cB^2L_n^*)
\]
after increasing \(B\) to account for the fixed fold fraction constants.
The same bound is trivial when \(m_P(C)p_{a,P}(C)=0\), because the truncated
error is at most \(2\).  A union bound over
\(a\in\{0,1\}\) and \(C\in\mathscr C_n\), together with
\(|\mathscr C_n|\le\exp(C_{\mathscr C}L_n^*)\), gives an event \(G_{n,k}\)
with failure probability at most \(C\bar\rho_n^*\) for \(B\) large enough.
On this event,
\[
\begin{aligned}
&\sum_{a=0}^1
E_{P_X}\!\left[
|\widehat\mu_a^{(-k)}(X)-\mu_a(X)|
\one\{p_P(X)\le2q_n^*}
\,\middle|\,\mathcal T_k\right]\\
&\qquad\le
C
\sum_{a=0}^1
\sum_{\substack{C\in\mathscr C_n:\\
\min\{e_P(C),1-e_P(C)\}\le2q_n^*}}
m_P(C)\,
\min\left\{1,
\sqrt{\frac{L_n^*}{n\,m_P(C)\,p_{a,P}(C)}}\right\}\\
&\qquad\le C\bar\rho_n^*
\end{aligned}
\]
by Assumption~\ref{ass:nuisance}.
\end{proof}

\begin{lemma}[Primitive cell means imply clipped-score drift]\label{lem:drift-derived}
Fix a law collection \(\mathcal Q\) satisfying
Assumption~\ref{ass:nuisance}.  Fix \(P\in\mathcal Q\), a fold \(k\), and
write \(q=q_n^*\).  On \(G_{n,k}\), let
\[
b_k(x)=E_P[\widehat\Gamma_{q,k}(O)\mid X=x,\mathcal T_k]-\tau_P(x).
\]
Then
\[
\sup_{\pi\in\Pi}
\left|E_P[(\pi(X)-\pi_P^*(X))b_k(X)\mid\mathcal T_k]\right|
\le C\bar\rho_n^*.
\]
\end{lemma}
\begin{proof}
Write
\[
\delta_{a,k}(x)=\widehat\mu_a^{(-k)}(x)-\mu_a(x),
\qquad
e_{q,P}(x)=\min\{1-q,\max\{q,e_P(x)\}\}.
\]
Since the logging propensity is known, taking the conditional mean of the
score given \(X=x\) and \(\mathcal T_k\) gives
\[
b_k(x)
=
\delta_{1,k}(x)\left(1-\frac{e_P(x)}{e_{q,P}(x)}\right)
-\delta_{0,k}(x)\left(1-\frac{1-e_P(x)}{1-e_{q,P}(x)}\right).
\]
If \(p_P(x)>q\), both \(e_P(x)\) and \(1-e_P(x)\) lie in \([q,1-q]\), so the
two coefficients are zero.  If \(p_P(x)\le q\), the two coefficients are
bounded in absolute value by a universal constant.  Hence
\[
|b_k(x)|
\le C\{|\delta_{0,k}(x)|+|\delta_{1,k}(x)|\}\one\{p_P(x)\le q\}.
\]
Since \(|\pi-\pi_P^*|\le1\), Lemma~\ref{lem:primitive-nuisance-derived}
yields
\[
\sup_{\pi\in\Pi}
\left|E_P[(\pi-\pi_P^*)b_k\mid\mathcal T_k]\right|
\le E_P[|b_k(X)|\mid\mathcal T_k]
\le C\bar\rho_n^*.
\]
\end{proof}

\begin{lemma}[Known-logging finite-VC offset]\label{lem:feasible-vc-offset}
Let \(\mathcal Q\) satisfy the hypotheses of
Theorem~\ref{thm:feasible-upper-log}.  Fix \(P\in\mathcal Q\).  On
\(G_n=\cap_{k=1}^K G_{n,k}\), define
\[
\widehat f_{\pi,k,n}(O)=(\pi-\pi_P^*)(X)\widehat\Gamma_{q_n^*,k}(O),
\]
\[
\widehat Z_n(P)=
\sup_{\pi\in\Pi}
\left\{
\left|\sum_{k=1}^K w_k
(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}\right|
-\frac12R_P(\pi)
\right\}_+,
\]
where \(\mathbb P_{n,k}\) is the empirical measure on validation fold
\(I_k\).  Then
\[
E_P[\widehat Z_n(P)\one_{G_n}]
\le C\bar\rho_n^*
\]
uniformly over \(P\in\mathcal Q\).
\end{lemma}
\begin{proof}
Condition on \(\mathcal T_k\) and the event \(G_{n,k}\).  The validation
observations in fold \(k\) are iid from \(P\) and independent of
\(\widehat\eta^{(-k)}\).  The score envelope obeys
\[
|\widehat\Gamma_{q_n^*,k}(O)|\le C(q_n^*)^{-1},
\]
because the estimated outcome regressions are bounded by one and the known
propensity is clipped into \([q_n^*,1-q_n^*]\).

Let \(q=q_n^*\) and \(D\subseteq\mathcal X\) be measurable.  Since
\(\widehat e=e_P\),
\[
E_P\!\left[
\one_D\frac{A}{e_{q,P}(X)^2}\{Y-\widehat\mu_1^{(-k)}(X)\}^2
\,\middle|\,\mathcal T_k\right]
\le
C\int_D \frac{e_P(x)}{e_{q,P}(x)^2}\,dP_X(x)
\le Cq^{-1}P_X(D).
\]
The untreated residual term is identical with \(e_P\) replaced by
\(1-e_P\).  The regression part of the score is bounded and is also covered
by \(Cq^{-1}P_X(D)\).  Therefore
\[
E_P[\one_D\widehat\Gamma_{q,k}(O)^2\mid\mathcal T_k]
\le Cq^{-1}P_X(D).
\]

For policies with \(R_P(\pi)\le\rho\), Lemma~\ref{lem:margin-localization}
gives
\[
P_X\{\pi(X)\ne\pi_P^*(X)\}\le C\rho^{\alpha/(1+\alpha)}.
\]
Thus
\[
\operatorname{Var}_P\{\widehat f_{\pi,k,n}(O)\mid\mathcal T_k\}
\le
Cq^{-1}\rho^{\alpha/(1+\alpha)}.
\]
The class \(\{x\mapsto \pi(x)-\pi_P^*(x):\pi\in\Pi\}\) has finite VC
dimension depending only on \(d_\Pi\).  The finite-VC maximal inequality for
bounded classes yields, uniformly on \(G_{n,k}\),
\[
E_P\!\left[
\sup_{R_P(\pi)\le\rho}
|(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}|
\,\middle|\,\mathcal T_k\right]
\le C\left[
\sqrt{
\frac{
q^{-1}\rho^{\alpha/(1+\alpha)}
\log(e/\rho)}
{n_k}}
+
\frac{q^{-1}\log(e/\rho)}{n_k}
\right].
\]

Set \(\rho_n=\bar\rho_n^*\).  By construction,
\[
\rho_n
\ge
\left\{\frac{q^{-1}L_n^*}{n}\right\}^{(1+\alpha)/(2+\alpha)}.
\]
This implies
\[
\sqrt{\frac{q^{-1}\rho_n^{\alpha/(1+\alpha)}L_n^*}{n}}
\le C\rho_n.
\]
The linear VC term satisfies
\[
\frac{q^{-1}L_n^*}{n}
\le C\rho_n
\]
for all sufficiently large \(n\), because it is of smaller order than the
first fixed-point radius.  Since
\(\log(e/\rho_n)\le C L_n^*\) whenever \(\rho_n\le1/2\), the localized bound
at \(\rho=\rho_n\) is \(C\rho_n\).  If \(\rho_n>1/2\), the lemma is trivial
after increasing \(C\).

A dyadic peeling over regret shells
\[
\mathcal S_j=\{\pi:2^j\rho_n<R_P(\pi)\le2^{j+1}\rho_n\},\qquad j\ge0,
\]
and the base set \(\{R_P(\pi)\le\rho_n\}\), gives the offset form.  On
\(\mathcal S_j\), the localized empirical-process ratio is bounded by a
constant multiple of \(2^{-j(2+\alpha)/(2+2\alpha)}\), and the linear term by
a constant multiple of \(2^{-j}\).  Bernstein tails for bounded finite-VC
classes are summable over the same shells.  Hence, conditionally on
\(G_{n,k}\),
\[
E_P\!\left[
\sup_{\pi\in\Pi}
\left\{|(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}|
-\frac12R_P(\pi)\right\}_+
\,\middle|\,\mathcal T_k\right]
\le C\rho_n.
\]
Finally,
\[
\left|\sum_{k=1}^K w_k
(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}\right|
-\frac12R_P(\pi)
\le
\sum_{k=1}^K w_k
\left\{|(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}|
-\frac12R_P(\pi)\right\}_+.
\]
Taking the supremum over \(\pi\), then expectations, proves the lemma.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:feasible-upper-log}]
Let
\[
B_n(\pi)=
\sum_{k=1}^K w_k
E_P[(\pi(X)-\pi_P^*(X))b_k(X)\mid\mathcal T_k],
\]
with \(b_k\) as in Lemma~\ref{lem:drift-derived}.  On
\(G_n=\cap_{k=1}^K G_{n,k}\), Lemma~\ref{lem:drift-derived} gives
\[
\sup_{\pi\in\Pi}|B_n(\pi)|\le C\bar\rho_n^*.
\]
For each \(\pi\),
\[
\sum_{k=1}^K w_k
E_P[\widehat f_{\pi,k,n}(O)\mid\mathcal T_k]
=
-R_P(\pi)+B_n(\pi),
\]
by Lemma~\ref{lem:welfare-identity} and the definition of \(b_k\).

Since \(\widehat\pi_n^{\mathsf F}\) maximizes the feasible empirical welfare
criterion and \(\pi_P^*\in\Pi\),
\[
0\le
\sum_{k=1}^K w_k\mathbb P_{n,k}
\widehat f_{\widehat\pi_n^{\mathsf F},k,n}.
\]
Therefore, on \(G_n\),
\[
R_P(\widehat\pi_n^{\mathsf F})
\le
\sum_{k=1}^K w_k
(\mathbb P_{n,k}-P)\widehat f_{\widehat\pi_n^{\mathsf F},k,n}
+B_n(\widehat\pi_n^{\mathsf F}).
\]
By the definition of \(\widehat Z_n(P)\),
\[
R_P(\widehat\pi_n^{\mathsf F})
\le
\widehat Z_n(P)
+\frac12R_P(\widehat\pi_n^{\mathsf F})
+C\bar\rho_n^*.
\]
Thus
\[
R_P(\widehat\pi_n^{\mathsf F})\one_{G_n}
\le
2\widehat Z_n(P)\one_{G_n}+C\bar\rho_n^*.
\]
The regret is bounded by \(2\), and
\[
P^n(G_n^c)\le\sum_{k=1}^K P^n(G_{n,k}^c)
\le CK\bar\rho_n^*
\]
by Lemma~\ref{lem:primitive-nuisance-derived}.  Taking expectations and
applying Lemma~\ref{lem:feasible-vc-offset} gives
\[
E_P R_P(\widehat\pi_n^{\mathsf F})
\le C\bar\rho_n^*
\]
uniformly over \(P\in\mathcal Q\).  The displayed polynomial form follows
from
\[
(h_n^*)^{1+\alpha}=n^{-(1+\alpha)/(2+\alpha+\beta_{\alpha,\gamma})}
=n^{-r_*(\alpha,\gamma)}
\]
and \(L_n^*\asymp\log n\).  The proof uses only the assumptions built into
Definition~\ref{def:uniform-feasible-collection}; no overlap-tail bound is
invoked.
\end{proof}

\begin{lemma}[Endpoint primitive witnesses are overlap-class laws]\label{lem:witness-membership}
Suppose Assumption~\ref{ass:primitive-cube} holds.  Fix
\(\beta=\beta_{\alpha,\gamma}\) and a sufficiently small \(h\).  Define
\[
q_h=q(h).
\]
Then there are paired laws \(P_{h,+},P_{h,-}\in\mathcal P_{\alpha,\gamma}\)
with common covariate law \(Q_h\), common logging propensity, common law off
an active block \(B_h\), a weak-arm label \(a_h\), and
\[
Q_h(B_h)\asymp h^\alpha,\qquad
\tau_{P_{h,+}}=h,\quad \tau_{P_{h,-}}=-h\quad\text{on }B_h,
\]
\[
\tau_{P_{h,+}}=\tau_{P_{h,-}}=\tau_0\in(0,1)\quad\text{off }B_h,\qquad
P_{h,\sigma}(A=a_h\mid X)\asymp q_h\quad\text{on }B_h.
\]
The two laws differ on \(B_h\) only in the weak-arm outcome regression.
Moreover
\[
\chi^2(P_{h,+}\|P_{h,-})\le C h^{2+\alpha+\beta},
\]
and every deterministic \(\pi\in\Pi\) satisfies
\[
R_{P_{h,+}}(\pi)+R_{P_{h,-}}(\pi)\ge c h^{1+\alpha}.
\]
If Assumption~\ref{ass:learnable-cube} also holds and \(h=h_n\) with
\(n h_n^{2+\alpha+\beta}=1\), then the two laws satisfy
Assumption~\ref{ass:nuisance} with \(q_n^*=q(h_n)\) and
\(\bar\rho_n^*=h_n^{1+\alpha}\{\log(e/h_n^{1+\alpha})\}^{a_\alpha}\).
\end{lemma}

\begin{proof}
By Assumption~\ref{ass:primitive-cube}, choose \(Q_h\), \(B_h\),
\(e_h\), the weak-arm label \(a_h\), and the two bounded regression
systems.  Let
\[
m_h:=Q_h(B_h),\qquad c h^\alpha\le m_h\le C h^\alpha.
\]
On \(B_h\), the weak-arm probability is comparable to \(q_h\); off
\(B_h\), keep the propensities in \([4q_0,1-4q_0]\).  The paired laws have
\(X\sim Q_h\) and identical \(A\mid X\) distributions.  They differ only in
the weak-arm outcome regression on \(B_h\).  If \(a_h=1\), set the untreated
conditional mean to zero on \(B_h\) and set the treated mean to \(+h\) under
\(P_{h,+}\) and \(-h\) under \(P_{h,-}\).  If \(a_h=0\), set the treated
conditional mean to zero on \(B_h\) and set the untreated mean to \(-h\)
under \(P_{h,+}\) and \(+h\) under \(P_{h,-}\).  In both cases
\(\tau_{P_{h,+}}=h\) and \(\tau_{P_{h,-}}=-h\) on \(B_h\), and the
sign-varying arm is the weak arm.  Bounded Bernoulli outcomes with these
means can be chosen for all sufficiently small \(h\).  Off \(B_h\), choose a
common bounded regression system with contrast \(\tau_0\).

The laws satisfy Assumption~\ref{ass:causal-sampling} by construction.
Choose the margin scale \(u_0<\tau_0/2\).  There is no zero-effect region.
For \(0<u\le u_0\), the only possible strict effects below \(u\) are on
\(B_h\):
\[
P_{h,\pm}\{0<|\tau_{P_{h,\pm}}(X)|\le u\}=0
\quad (u<h),
\]
and for \(u\ge h\),
\[
P_{h,\pm}\{0<|\tau_{P_{h,\pm}}(X)|\le u\}=m_h
\le C h^\alpha\le C u^\alpha.
\]
The policy-class condition follows from the local label-flexibility in
Assumption~\ref{ass:primitive-cube}.

It remains to verify Assumption~\ref{ass:overlap-decay}.  If \(\gamma=0\),
choose the overlap constant \(c_o\) below the lower bound for the weak-arm
propensity on the strict-margin region; then the overlap event is empty in
the required range.  Let \(\gamma>0\).  If \(\beta=0\), then \(q_h=q_0\) and
the on-block weak arm is bounded away from zero, so the same empty-event
argument applies after choosing \(c_o u_0^\gamma\) below that bound.  Now
suppose \(\beta>0\).  For \(0<u\le u_0\), the off-block contrast \(\tau_0\)
is larger than \(u\), so the overlap event can only include \(B_h\).  It is
empty unless \(u\ge h\) and \(v\gtrsim h^\beta\).  In the required range
\(v\le c_o u^\gamma\), nonemptiness also implies
\[
u\gtrsim h^{\beta/\gamma}.
\]
Because \(\beta/\gamma=\alpha/(\alpha+1)\), this is the binding window for
small \(h\).  Hence
\[
u^\alpha v^{1/\gamma}
\gtrsim h^{\alpha\beta/\gamma}h^{\beta/\gamma}
=h^{(\alpha+1)\beta/\gamma}
=h^\alpha.
\]
Thus
\[
P_{h,\pm}\{p_{P_{h,\pm}}(X)\le v,\;0<|\tau_{P_{h,\pm}}(X)|\le u\}
\le m_h
\le C u^\alpha v^{1/\gamma}.
\]

The one-observation \(\chi^2\) divergence is concentrated on
\(\{X\in B_h,A=a_h\}\), which has probability \(m_h q_h\) up to constants.
The \(\chi^2\) divergence between Bernoulli laws with means differing by
\(2h\) and bounded away from \(\pm1\) is at most \(C h^2\) for
\(h\le1/2\).  Hence
\[
\chi^2(P_{h,+}\|P_{h,-})
\le C m_h q_h h^2
\le C h^{2+\alpha+\beta}.
\]

The optimal policies are opposite on \(B_h\).  By
Lemma~\ref{lem:welfare-identity}, every deterministic \(\pi\in\Pi\) satisfies
\[
R_{P_{h,+}}(\pi)+R_{P_{h,-}}(\pi)
\ge h Q_h(B_h)
\asymp h^{1+\alpha}.
\]

If Assumption~\ref{ass:learnable-cube} holds, the partition
\(\{B_h,B_h^c\}\) is known, the logging propensity is known, and the outcome
regressions are cell-constant.  The partition cardinality is two.  Let
\[
L_h=\log(e/h^{1+\alpha}),\qquad
\bar\rho_h=h^{1+\alpha}L_h^{a_\alpha}.
\]
On \(B_h\), the weak-arm cell contribution to the rare-arm envelope is
\[
m_h\sqrt{\frac{L_h}{n m_h q_h}}
\asymp
h^\alpha\sqrt{L_h\,h^2}
=
h^{1+\alpha}L_h^{1/2}
\le \bar\rho_h,
\]
because \(a_\alpha\ge1/2\).  The strong-arm contribution is no larger:
\[
m_h\sqrt{\frac{L_h}{n m_h}}
\asymp
h^\alpha h^{(2+\beta)/2}L_h^{1/2}
\le \bar\rho_h.
\]
Off \(B_h\), the weak-arm propensity is bounded away from zero and one, so
for sufficiently small \(h\) the off-block cell is not included in the
summation defining \(\Lambda_n(P)\).  Hence
Assumption~\ref{ass:nuisance} holds for the two witness laws with common
constants.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:lower-full-class}]
Apply Lemma~\ref{lem:witness-membership} with
\(\beta=\beta_{\alpha,\gamma}\) and \(h=h_n\).  The resulting laws are
members of \(\mathcal P_{\alpha,\gamma}\) and have the stated block mass,
contrast, weak-arm propensity, and one-observation divergence.  The same
lemma gives
\[
\inf_{\pi\in\Pi}\max_{\sigma\in\{+,-\}}R_{P_{n,\sigma}}(\pi)
\ge c h_n^{1+\alpha}.
\]
The local label-flexibility clause gives the reverse order: choose a policy
that uses the common off-block label \(1\) and either one of the two
active-block labels.  It makes no active-block mistakes under one sign and
pays at most \(h_nP_X(B_n)\le C h_n^{1+\alpha}\) under the other sign.  Hence
the deterministic two-law separation is \(\asymp h_n^{1+\alpha}\).

Since
\[
n h_n^{2+\alpha+\beta}=1,
\]
the lemma gives
\[
n\chi^2(P_{n,+}\|P_{n,-})\le C_\chi.
\]
Using the witness constants in Assumption~\ref{ass:primitive-cube}, calibrate
the construction so that
\[
n\chi^2(P_{n,+}\|P_{n,-})\le 8C_BC_Q<\log 5.
\]
Tensorization gives
\[
1+\chi^2(P_{n,+}^{\otimes n}\|P_{n,-}^{\otimes n})
=(1+\chi^2(P_{n,+}\|P_{n,-}))^n
\le \exp(8C_BC_Q)<5.
\]
For any data-dependent policy \(\widehat\pi\), define a test that reports
``+'' when the policy assigns treatment \(1\) to at least half of the active
block and reports ``-'' otherwise.  If this test is wrong, the corresponding
active-block regret is at least a fixed multiple of \(h_nP_X(B_n)\).  Le
Cam's two-point inequality and
\(\operatorname{TV}(P,Q)\le\tfrac12\sqrt{\chi^2(P\|Q)}\) yield a fixed
positive lower bound on the sum of the two testing error probabilities.
Integrating the active-block regret separation gives
\[
E_{P_{n,+}}R_{P_{n,+}}(\widehat\pi)
+E_{P_{n,-}}R_{P_{n,-}}(\widehat\pi)
\ge c h_n^{1+\alpha}.
\]
Taking the maximum over the two signs and then the infimum over all
measurable estimators proves
\[
\mathfrak M_n(\alpha,\gamma)\ge c h_n^{1+\alpha}
=c n^{-r_*(\alpha,\gamma)}.
\]
If Assumption~\ref{ass:learnable-cube} holds,
Lemma~\ref{lem:witness-membership} verifies the final primitive finite-cell
nuisance assertion for the same witness laws.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:feasible-bracket}]
Because \(\mathcal Q\) is \(\kappa\)-uniform primitive finite-cell feasible,
Theorem~\ref{thm:feasible-upper-log} applies to \(\mathcal Q\) with constants
depending only on \(\kappa,\alpha,\gamma\).  The minimax risk
\(\mathfrak M_n(\mathcal Q)\) is an infimum over all data-dependent policies,
so it is bounded above by the risk of \(\widehat\pi_n^{\mathsf F}\).  This
gives the displayed upper bound.  If \(\mathcal Q\) contains the two witness
laws from Theorem~\ref{thm:lower-full-class} for all large \(n\), the Le Cam
lower-bound argument in the proof of Theorem~\ref{thm:lower-full-class}
applies inside \(\mathcal Q\), giving
\(\mathfrak M_n(\mathcal Q)\ge c n^{-r_*(\alpha,\gamma)}\).
\end{proof}

\section{Sanity checks}
\paragraph{Strict overlap.}
If \(\gamma=0\), then \(\beta_{\alpha,0}=0\),
\[
r_*(\alpha,0)=\frac{1+\alpha}{2+\alpha}.
\]
The clipping level and the lower-bound weak-arm propensity are fixed
constants bounded away from zero.  The converse construction has information
\(h^{2+\alpha}\) and regret \(h^{1+\alpha}\), matching the standard
fast-margin polynomial exponent.  The finite-VC fixed point is
\[
\rho\asymp
\sqrt{\rho^{\alpha/(1+\alpha)}\log(e/\rho)/n},
\]
so the proved primitive feasible benchmark is
\[
n^{-(1+\alpha)/(2+\alpha)}
(\log n)^{(1+\alpha)/(2+\alpha)}.
\]

\paragraph{Zero-margin exponent with weak-overlap parameter.}
If \(\alpha=0\) and \(\gamma>0\), then
\(\beta_{\alpha,\gamma}=0\).  The clipping convention uses \(q(h)=q_0\),
not \(h^0=1\).  The overlap witness has constant weak-arm propensity and
therefore satisfies the overlap-tail condition by the empty-event argument
for \(v\le c_o u^\gamma\).  The converse exponent is
\(r_*(0,\gamma)=1/2\), and the finite-VC feasible upper benchmark is
\(n^{-1/2}(\log n)^{1/2}\).

\paragraph{Diagnostic point \((\alpha,\gamma)=(2,2)\).}
Here
\[
\beta_{2,2}=\frac{2\cdot2}{2+1}=\frac43,\qquad
D_{2,2}=2+2+\frac43=\frac{16}{3},
\]
so
\[
r_*(2,2)=\frac3{16/3}=\frac9{16}.
\]
The lower witness uses \(h_n=n^{-3/16}\), weak-arm propensity
\[
q_n=h_n^{4/3}=n^{-1/4},
\]
one-observation information \(h_n^{16/3}=n^{-1}\), and regret
\[
h_n^3=n^{-9/16}.
\]
The finite-VC feasible upper fixed point with \(q_n=n^{-1/4}\) solves
\[
\rho\asymp\sqrt{\rho^{2/3}\log(e/\rho)/(nq_n)}
=\sqrt{\rho^{2/3}\log(e/\rho)n^{-3/4}},
\]
giving
\[
\rho\asymp n^{-9/16}(\log n)^{3/4}.
\]
Thus a full-class \(n^{-3/4}\) rate is too fast, while the primitive
known-logging finite-cell upper theorem matches the polynomial lower exponent
at this diagnostic point for collections containing the witness laws.

\paragraph{Large \(\gamma\).}
As \(\gamma\) grows with \(\alpha>0\),
\(\beta_{\alpha,\gamma}=\alpha\gamma/(\alpha+1)\) grows linearly.  The
weak-arm layer can then be made rarer while staying in the overlap-tail
class, and the converse exponent \(r_*(\alpha,\gamma)\) decreases.  The
known-logging upper theorem uses the same deterministic calibration
\(q_n^*=h_n^{\beta_{\alpha,\gamma}}\), but its proof is driven by the
finite-cell nuisance envelope at that clipping level rather than by the
overlap-tail inequality.  The finite-VC fixed point remains
\(\bar\rho_n^*\), so the polynomial exponent continues to match on primitive
finite-cell feasible collections that contain the calibrated witnesses.

\paragraph{Known-logging cell means.}
For the lower witnesses with \(h=h_n\), the active weak-arm training count is
of order \(h^{-2}\).  A cell-mean threshold of order \(h\) has only constant
Bernstein exponent and is not enough for a good event whose failure
probability is of order the feasible scale.  The threshold
\[
h\{\log(e/h^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}
\]
has exponent
\[
\{\log(e/h^{1+\alpha})\}^{2(1+\alpha)/(2+\alpha)},
\]
which is at least linear in \(\log(e/h^{1+\alpha})\).  With a sufficiently
large constant, the failure probability is bounded by \(C\bar\rho_n^*\),
while the local \(L_1(P_X)\) contribution is \(h^\alpha\) times the threshold
and is no larger than \(\bar\rho_n^*\).

\paragraph{Common constants in uniform upper bounds.}
Membership in \(\mathcal P_{\alpha,\gamma}\) fixes only the exponents and
allows the margin constants, overlap constants, policy-complexity constants,
partition constants, and cell-count constants to vary with \(P\).  The upper
theorem itself is uniform over law collections whose causal-sampling, margin,
policy-complexity, partition, fold, and cell-count constants are bounded
uniformly.  It does not require a uniform overlap constant.  In
Corollary~\ref{cor:feasible-bracket}, membership
\(\mathcal Q\subseteq\mathcal P_{\alpha,\gamma}\) is not a mathematical
hypothesis for the bracket: the upper half uses only primitive finite-cell
feasibility, and the lower half uses explicit containment of the two witness
laws in \(\mathcal Q\).  If one additionally restricts attention to
collections \(\mathcal Q\subseteq\mathcal P_{\alpha,\gamma}\), the same
bracket has the interpretation of a primitive learnable subcollection inside
the full weak-overlap class.

\section{Counterexample or minimality check}
\paragraph{Why the faster \(r(\alpha,\gamma)\) claim fails.}
The two-point construction in Theorem~\ref{thm:lower-full-class} is a
counterexample whenever
\[
\frac{1+\alpha}{2+\alpha+\delta_{\alpha,\gamma}}
>
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
At \((\alpha,\gamma)=(2,2)\), \(\delta_{2,2}=0\), so Conjecture 1 predicts
\(3/4\).  But the weak-overlap laws with active mass \(h^2\), contrast
\(h\), and weak-arm propensity \(h^{4/3}\) satisfy the law-side assumptions
and force regret at least \(n^{-9/16}\).  No estimator can have uniformly
smaller expected regret on a class containing these laws.

\paragraph{Minimality of \(\beta_{\alpha,\gamma}\).}
Keep active mass \(h^\alpha\), contrast height \(h\), and weak-arm propensity
\(h^\beta\).  If \(\beta>\alpha\gamma/(\alpha+1)\), then at the tight window
\[
v\asymp h^\beta,\qquad u\asymp h^{\beta/\gamma},
\]
the overlap envelope is
\[
u^\alpha v^{1/\gamma}
\asymp h^{(\alpha+1)\beta/\gamma}
=o(h^\alpha).
\]
Thus the active block violates Assumption~\ref{ass:overlap-decay}.  At the
endpoint \(\beta=\beta_{\alpha,\gamma}\),
Lemma~\ref{lem:witness-membership} verifies membership for the primitive
witnesses used by the lower theorem.  The same exponent algebra shows why
smaller \(\beta\) layers are overlap-admissible, but the minimax converse only
needs the least informative endpoint layer.

\paragraph{Why the weak arm must be the perturbed arm.}
The lower-bound information calculation is
\[
Q_h(B_h)\,P(A=a_h\mid X\in B_h)\,h^2.
\]
If the sign-varying regression were placed on the strong arm when
\(P(A=a_h\mid X\in B_h)\asymp h^\beta\) is the weak-arm probability, the
information would instead be of order \(h^\alpha h^2\), and the calibration
\(n h^{2+\alpha+\beta}\asymp1\) would fail.  Assumption~\ref{ass:primitive-cube}
therefore requires the two laws to differ on \(B_h\) only through the
weak-arm outcome regression, and Lemma~\ref{lem:witness-membership} uses this
condition in the \(\chi^2\) calculation.

\paragraph{Why finite VC dimension gives a logarithmic upper factor.}
At the no-log oracle-score scale \(\rho_0=(h_n^*)^{1+\alpha}\), the localized
finite-VC maximal inequality gives
\[
E_P\sup_{R_P(\pi)\le\rho_0}
|(\mathbb P_n-P)f_{\pi,n}|
\lesssim
\sqrt{\frac{(q_n^*)^{-1}\rho_0^{\alpha/(1+\alpha)}
\log(e/\rho_0)}{n}}
+
\frac{(q_n^*)^{-1}\log(e/\rho_0)}{n}.
\]
The leading term equals
\[
(h_n^*)^{1+\alpha}\sqrt{\log(e/\rho_0)}
\]
up to constants, not \(O(\rho_0)\).  Therefore finite-VC entropy alone closes
the oracle-score fixed point at
\[
\rho_0\{\log(e/\rho_0)\}^{(1+\alpha)/(2+\alpha)}.
\]

\paragraph{Why finite VC dimension alone does not make the logarithm unavoidable.}
The preceding display is an achievability-side entropy calculation, not a
matching lower-bound theorem.  Assumption~\ref{ass:policy-class} is an upper
complexity condition and also permits finite or two-policy classes, for which
a logarithmic entropy lower bound is false.  A logarithmic lower bound would
need an additional lower-richness condition, such as \(M_h\) separated active
locations with \(\log M_h\asymp\log(1/h)\) and a policy class able to realize
the relevant labels on those locations, while keeping the same margin and
overlap calibration.  Assumption~\ref{ass:primitive-cube} supplies one
endpoint active block with two labels, so the Le Cam construction proves only
the polynomial lower exponent.

\paragraph{Why the full weak-overlap class is not an achievability class.}
The law class \(\mathcal P_{\alpha,\gamma}\) imposes margin, overlap, bounded
outcomes, positivity, and policy-class conditions.  It does not impose a
known logging design, a finite partition, cell-constant nuisance functions,
or a cell-count envelope.  A clipped-AIPW estimator needs such primitive
nuisance learnability to control the first-order clipping drift.  Therefore
Assumption~\ref{ass:nuisance} cannot be replaced by
Assumption~\ref{ass:overlap-decay}: the conditional upper theorem is an
upper bound over collections with primitive nuisance structure, while the
full-class theorem supplied by the primitive margin-overlap assumptions is
the converse.

\paragraph{Why ordinary \(L_2\) propensity control does not give the known-logging variance.}
Let \(D\) be a policy-disagreement set lying mostly where \(e_P>2q_n\), and
suppose an estimated propensity \(\widehat e\) falls below \(q_n\) on a small
subset of \(D\).  On that subset, the treated inverse weight in the feasible
score is \(q_n^{-1}\), while the true treated probability is of order
\(e_P\), not \(q_n\).  The contribution to the second moment is therefore of
order \(e_P q_n^{-2}\).  The event \(\widehat e<q_n<e_P/2\) forces
\(|\widehat e-e_P|\gtrsim e_P\), which gives the valid bound
\[
e_P q_n^{-2}\lesssim q_n^{-2}|\widehat e-e_P|,
\]
but not the sharper \(q_n^{-1}\) bound used by the known-logging proof.
An upper theorem based only on \(L_2(P_X)\) propensity estimation must account
for this extra term or prove a different stability argument.

\paragraph{Why a target-rate \(L_2\) nuisance assumption is not primitive.}
If an unknown logging propensity is required to satisfy
\[
\|\widehat e-e_P\|_{2,P_X}\lesssim n^{-r_*(\alpha,\gamma)}
\]
at the lower-bound scale, then in regimes with
\(r_*(\alpha,\gamma)>1/2\) the condition asks for faster-than-root-\(n\)
uniform \(L_2\) propensity accuracy.  Such a rate cannot be inferred from
bounded outcomes, margin, overlap decay, or finite VC policy complexity.  It
requires its own primitive smoothness, sparsity, finite-dimensional design,
known-logging, or other structural condition.  The upper theorem therefore
uses the explicit known-logging finite-cell structure of
Assumption~\ref{ass:nuisance}.

\paragraph{Why product-only nuisance control is insufficient.}
Suppose \(e_P\) is known exactly, so a propensity-estimation product is zero.
Let \(\widehat\mu_1-\mu_1\) be nonzero on the clipped weak-overlap region
\(\{p_P(X)<q_n^*,0<|\tau_P(X)|\le h_n^*\}\).  Even with known propensity, the
clipped treated-arm term has conditional mean contribution
\[
(\widehat\mu_1-\mu_1)(X)
\left\{1-\frac{e_P(X)}{e_{q_n^*}(X;\eta_P)}\right\},
\]
which is first order on the region \(e_P(X)<q_n^*\).  Therefore a
product-only remainder cannot imply the feasible clipped-score drift.  The
rare-arm local outcome-regression control derived from
Assumption~\ref{ass:nuisance} is needed.

\paragraph{Why bounded residual weighting cannot remove the bias.}
Consider any treated-arm score of the residual-weight form
\[
S_1(X,A,Y)=c_1(X)\widehat\mu_1(X)+w_1(X)A\{Y-\widehat\mu_1(X)\}.
\]
Conditional on \(X=x\),
\[
E_P[S_1\mid X=x]
=e_P(x)w_1(x)\mu_1(x)
+\{c_1(x)-e_P(x)w_1(x)\}\widehat\mu_1(x).
\]
For this conditional mean to equal \(\mu_1(x)\) for every value of
\(\widehat\mu_1(x)\), the coefficient of \(\widehat\mu_1(x)\) must be zero
and the coefficient of \(\mu_1(x)\) must be one.  Thus
\(w_1(x)=1/e_P(x)\).  The untreated arm gives
\(w_0(x)=1/\{1-e_P(x)\}\).  Exact first-order orthogonality for arbitrary
outcome-regression error therefore forces the unclipped inverse-propensity
weights.  A bounded clipped residual score can either control variance by
clipping or be fully orthogonal to arbitrary outcome error, but not both.

\paragraph{Open exact-value qualification.}
Corollary~\ref{cor:feasible-bracket} gives a primitive known-logging
finite-cell feasible upper theorem with the finite-VC logarithmic multiplier
and a polynomial lower exponent for collections containing the finite-cell
witnesses.  It does not prove a no-log upper bound under finite VC dimension
alone.  It also does not prove a matching logarithmic lower bound from finite
VC dimension alone, and it does not prove an upper bound over the larger
class \(\mathcal P_{\alpha,\gamma}\) without primitive nuisance learnability.
The exact data-only feasible minimax rate under unknown logging and only
ordinary \(L_2(P_X)\) propensity control remains open.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
\item \textbf{Causal objects.}  \(\tau_P:\mathcal X\to\mathbb R\),
\(\pi_P^*(x)=\one\{\tau_P(x)\ge0\}\), \(V_P(\pi)=E_P[\pi(X)\tau_P(X)]\),
and \(R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)\).  Role: target estimand and loss.
\item \textbf{Regret identity.}  Lemma~\ref{lem:welfare-identity} rewrites
\(R_P(\pi)\) as
\(E_P[|\tau_P(X)|\one\{\pi(X)\ne\pi_P^*(X)\}]\).  Role: connects causal
welfare regret to sign classification.
\item \textbf{Law classes.}  \(\mathcal P_{\alpha,\gamma}\) is carved by
Assumptions~\ref{ass:causal-sampling}, \ref{ass:margin},
\ref{ass:overlap-decay}, and \ref{ass:policy-class} and fixes only the
exponents \(\alpha,\gamma\); Definition~\ref{def:uniform-feasible-collection}
defines a \(\kappa\)-uniform primitive finite-cell feasible collection using
Assumptions~\ref{ass:causal-sampling}, \ref{ass:margin},
\ref{ass:policy-class}, and \ref{ass:nuisance}, without requiring
Assumption~\ref{ass:overlap-decay}.  Role: separates law-side lower-bound
classes from achievability-side nuisance structure and common constants.
\item \textbf{Primitive finite-cell nuisance structure.}
Assumption~\ref{ass:nuisance} gives the known finite partition
\(\mathscr C_n\), known logging propensity, cell-constant \(\mu_a\), empirical
cell-mean learners, and the rare-arm cell-count envelope \(\Lambda_n(P)\).
Role: primitive input from which Lemma~\ref{lem:primitive-nuisance-derived}
derives the local clipped-layer outcome accuracy.
\item \textbf{Delta-witness calibration.}
Assumption~\ref{ass:calibrated-overlap-richness} states
\((\gamma-\alpha)_+\le\alpha\gamma/(\alpha+1)\).  Role: verifies the
overlap admissibility of the \(\delta_{\alpha,\gamma}\)-weak-arm motivating
witness when that witness is considered; the main theorem uses
\(\beta_{\alpha,\gamma}\) instead.
\item \textbf{Overlap layer.}  \(\beta_{\alpha,\gamma}=0\) for \(\gamma=0\)
and \(\beta_{\alpha,\gamma}=\alpha\gamma/(\alpha+1)\) for \(\gamma>0\).
Role: optimized weak-arm exponent allowed by Assumption~\ref{ass:overlap-decay}.
\item \textbf{Clipping convention.}  \(q(h)=q_0\) whenever
\(\beta_{\alpha,\gamma}=0\), and
\(q(h)=h^{\beta_{\alpha,\gamma}}\) otherwise.  Role: keeps the clipping level
inside \((0,1/2]\), including the \(\alpha=0,\gamma>0\) case.
\item \textbf{Rate and logarithmic scale.}
\(D_{\alpha,\gamma}=2+\alpha+\beta_{\alpha,\gamma}\),
\(h_n^*=n^{-1/D_{\alpha,\gamma}}\),
\(q_n^*=q(h_n^*)\),
\(r_*(\alpha,\gamma)=(1+\alpha)/D_{\alpha,\gamma}\),
\(L_n^*=\log\{e/(h_n^*)^{1+\alpha}\}\), and
\(\bar\rho_n^*=(h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}\).
Role: lower-bound calibration and primitive finite-cell upper-bound
calibration.
\item \textbf{Clipped score.}  \(e_q(x;\eta)\), \(\Gamma_q(O;\eta)\), and
\(\widehat\Gamma_{q,k}(O)\).  Role: explicit data-and-design score used by
the estimator.
\item \textbf{Feasible estimator.}
\(\widehat\pi_n^{\mathsf F}\in\arg\max_{\pi\in\Pi}\sum_k w_k n_k^{-1}
\sum_{i\in I_k}\pi(X_i)\Gamma_{q_n^*}(O_i;\widehat\eta^{(-k)})\).  Role:
sample-to-policy map in Theorem~\ref{thm:feasible-upper-log}.
\item \textbf{Derived nuisance event.}
Lemma~\ref{lem:primitive-nuisance-derived} derives the foldwise good event
and the local weak-arm outcome \(L_1(P_X)\) bound from the primitive
cell-count envelope.  Role: prevents replacing primitive structure by a
target-rate nuisance assumption.
\item \textbf{Derived drift.}  Lemma~\ref{lem:drift-derived} derives the
policy-uniform clipped-score conditional-bias bound from known logging and
local cell-mean accuracy.  Role: controls first-order clipped weak-arm bias.
\item \textbf{VC localization.}  Lemma~\ref{lem:feasible-vc-offset} combines
finite VC complexity, the \(q^{-1}\) known-logging variance term, margin
localization, and the entropy multiplier \(\log(e/\rho)\).  Role: proves the
feasible fixed point \(\bar\rho_n^*\) without using the overlap-tail
assumption.
\item \textbf{Endpoint lower-bound witnesses.}  The witness covariate law
\(Q_h\), active block \(B_h\), \(m_h=Q_h(B_h)\), weak-arm label \(a_h\),
\(P_{h,+}\), \(P_{h,-}\), \(q_h=q(h)\), and the fixed off-block contrast
\(\tau_0>0\).  Assumption~\ref{ass:primitive-cube} supplies only the endpoint
witness needed for the lower theorem.  Lemma~\ref{lem:witness-membership}
verifies bounded outcomes, positivity, margin, overlap decay, policy
membership, divergence, and primitive finite-cell nuisance compatibility when
Assumption~\ref{ass:learnable-cube} is imposed.
\item \textbf{Weak-arm perturbation.}
Assumption~\ref{ass:primitive-cube} requires the paired laws to differ on
\(B_h\) only through the weak-arm outcome regression.  Role: makes the
one-observation divergence \(h^\alpha h^{\beta_{\alpha,\gamma}}h^2\).
\item \textbf{Known-logging witness learnability.}  In
Assumption~\ref{ass:learnable-cube}, \(\widehat e=e_h\) is known by
design on the finite witness partition.  Outcome regressions are empirical
cell means, and the active weak-arm cell has expected sample size of order
\(h^{-2}\).  Role: verifies Assumption~\ref{ass:nuisance} using the inflated
threshold \(h\{\log(e/h^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}\).
\item \textbf{Divergences.}  \(\chi^2(P\|Q)\) and total variation.  Role:
product-law indistinguishability and Le Cam testing lower bound.
\item \textbf{Abstraction record.}  The mathematical note is written over
generic probability laws, policies, finite partitions, and empirical cell
means; reuse of specialized implementation objects is bypass-justified
because the theorem's proof objects are rate-calibration and finite-cell
concentration identities rather than a pre-existing causal identification
functional.
\end{itemize}

\section{Conclusion and references}
The calibrated weak-arm exponent is
\[
\beta_{\alpha,\gamma}=
\begin{cases}
0,&\gamma=0,\\
\alpha\gamma/(\alpha+1),&\gamma>0,
\end{cases}
\]
and the polynomial converse exponent is
\[
r_*(\alpha,\gamma)=
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
A primitive two-point construction, with the sign-varying regression placed
on the weak arm, gives the full weak-overlap lower bound
\[
\mathfrak M_n(\alpha,\gamma)\ge c n^{-r_*(\alpha,\gamma)}.
\]
For any \(\kappa\)-uniform primitive known-logging finite-cell feasible law
collection, the cross-fitted clipped-AIPW empirical welfare maximizer is
explicit and satisfies
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\le
C n^{-r_*(\alpha,\gamma)}
(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
This upper bound does not require overlap decay.  If the collection contains
the known-logging finite-cell witnesses, the same collection has the matching
polynomial lower exponent.  Removing the finite-VC logarithmic factor
requires stronger local entropy structure, while proving an upper bound over
the larger weak-overlap class requires primitive nuisance learnability for
unknown outcome regressions and, if logging is unknown, a primitive solution
to estimated-clipping instability.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem[Athey and Wager(2021)]{AtheyWager2021PolicyLearning}
Athey, S. and Wager, S. (2021).
Policy learning with observational data.
\emph{Econometrica}, 89(1), 133--161.

\bibitem[Audibert and Tsybakov(2007)]{AudibertTsybakov2007PluginClassifiers}
Audibert, J.-Y. and Tsybakov, A. B. (2007).
Fast learning rates for plug-in classifiers.
\emph{Annals of Statistics}, 35(2), 608--633.

\bibitem[Chernozhukov et al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., Chetverikov, D., Demirer, M., Duflo, E., Hansen, C.,
Newey, W., and Robins, J. (2018).
Double/debiased machine learning for treatment and structural parameters.
\emph{The Econometrics Journal}, 21(1), C1--C68.

\bibitem[D'Amour et al.(2021)]{DAmourDingFellerLeiSekhon2017Overlap}
D'Amour, A., Ding, P., Feller, A., Lei, L., and Sekhon, J. (2021).
Overlap in observational studies with high-dimensional covariates.
\emph{Journal of Econometrics}, 221(2), 644--654.

\bibitem[Jin et al.(2022)]{JinRenYangWang2022PessimisticPolicy}
Jin, Y., Ren, Z., Yang, Z., and Wang, Z. (2022).
Policy learning ``without'' overlap: Pessimism and generalized empirical
Bernstein's inequality.
arXiv:2212.09900.

\bibitem[Kallus(2017)]{Kallus2017BalancedPolicy}
Kallus, N. (2017).
Balanced policy evaluation and learning.
arXiv:1705.07384.

\bibitem[Kitagawa and Tetenov(2018)]{KitagawaTetenov2018WhoShouldBeTreated}
Kitagawa, T. and Tetenov, A. (2018).
Who should be treated? Empirical welfare maximization methods for treatment
choice.
\emph{Econometrica}, 86(2), 591--616.

\bibitem[Luedtke and Chambaz(2017)]{LuedtkeChambaz2017FasterRates}
Luedtke, A. and Chambaz, A. (2017).
Faster rates for policy learning.
arXiv:1704.06431.

\bibitem[Ma et al.(2023)]{MaSantAnnaSasakiUra2023DRWeakOverlap}
Ma, Y., Sant'Anna, P. H. C., Sasaki, Y., and Ura, T. (2023).
Doubly robust estimators with weak overlap.
arXiv:2304.08974.

\bibitem[Vapnik and Chervonenkis(1971)]{VapnikChervonenkis1971}
Vapnik, V. N. and Chervonenkis, A. Y. (1971).
On the uniform convergence of relative frequencies of events to their
probabilities.
\emph{Theory of Probability and its Applications}, 16(2), 264--280.

\bibitem[van der Vaart and Wellner(1996)]{VanderVaartWellner1996}
van der Vaart, A. W. and Wellner, A. W. (1996).
\emph{Weak Convergence and Empirical Processes}.
Springer.

\bibitem[Zhan et al.(2021)]{ZhanRenAtheyZhou2021AdaptivePolicy}
Zhan, R., Ren, Athey, S., and Zhou, Z. (2021).
Policy learning with adaptively collected data.
arXiv:2105.02344.
\end{thebibliography}

\end{document}
