% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_policy\_commutator\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_policy\_commutator\_phase} / \texttt{v1}%
  \\ \large\textit{A representation certificate for the IPSI--LMTP policy commutator}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\texttt{qid} is \texttt{eid\_policy\_commutator\_phase}. \texttt{specialization} is \texttt{v1}. The anchor cluster is ExactID. The observed longitudinal law is
\[
P(a_1,\ell,a_2,y)=p_1(a_1)q_{\ell\mid a_1}r_{a_2\mid a_1,\ell}s_{y\mid a_1,\ell,a_2}
\]
on binary variables \(A_1,L_2,A_2,Y\). The treatment process is \(A=(A_1,A_2)\), the post-baseline covariate is \(L_2\), and the target estimands are ordered stochastic-policy means \(\psi_{I_\lambda\circ N_\eta}(P)\) and \(\psi_{N_\eta\circ I_\lambda}(P)\). \(I_\lambda\) is the odds-multiplier IPSI map \(x\mapsto \omega_\lambda(x)=\lambda x/(1-x+\lambda x)\), applied to the conditional law of \(A_2\) given \((A_1,L_2)\). \(N_\eta\) is the binary natural-value modified treatment policy that assigns the natural \(A_2\) value with probability \(\eta\in(0,1)\) and its complement with probability \(1-\eta\). The identifying assumptions are consistency, sequential exchangeability for the two ordered stochastic regimes, and positivity \(r_{1\mid a,\ell}\in(0,1)\).

\begin{abstract}
Support-preserving stochastic policies are often compared through their identified g-formula functionals. This proposal asks whether such a comparison remains meaningful after one policy is embedded inside a second longitudinal policy operator. The kernel is a representation certificate: in a two-time binary law, an odds-multiplier IPSI and a natural-value LMTP can agree with a static stochastic representation as standalone interventions but generate different commutators after composition. The main conjecture states that any equivalence relation that identifies policies only by their standalone observed-data functional is too coarse for ordered policy composition. A closed-form one-cell commutator coefficient gives a finite witness and isolates the algebraic source of the failure.
\end{abstract}

\section{Introduction}
Longitudinal stochastic interventions are usually identified one policy at a time. The question here is whether two support-preserving policies that are indistinguishable as standalone observed-data functionals remain interchangeable after another policy is composed with them. The conjecture is negative: natural-value semantics leave a measurable trace in the IPSI commutator even when the standalone stochastic kernel can be written without that semantics.

Kennedy's IPSI formula \citep[Sec.~2, Eq.~1]{Kennedy2019JASA} shifts the treatment odds inside the observed treatment mechanism, while longitudinal LMTPs in \citet[Sec.~2.1]{DiazWilliamsHoffmanSchenck2023JASA} let a policy depend on the natural treatment value. \citet[Sec.~2]{VanDerLaanLuedtkeDiaz2014EM} and \citet[Sec.~2.3]{WenMarcusYoung2023SMMR} warn that a single statistical estimand can have multiple causal interpretations. The gap is an ExactID statement showing that this representation choice is not harmless once policy operators are ordered.

The direct consumer is the longitudinal modified-treatment-policy literature using natural treatment values in realistic policy rules, including \citet{YoungHernanRobins2014EM} and \citet{StensrudLaurendeauSarvet2024Biometrika}. A reader who accepts the result should report the ordered operator semantics, not only the final g-formula functional, whenever an LMTP is combined with an IPSI or a resource-scaled stochastic intervention.

\begin{itemize}[leftmargin=*]
\item Theorem 1: The ordered IPSI--LMTP means are identified by two extended g-formulas and differ by a cellwise coefficient \(C_{\lambda,\eta}(r)\). Gap: \citet{Kennedy2019JASA} and \citet{DiazWilliamsHoffmanSchenck2023JASA} identify each class separately but do not compare ordered compositions. Consumer: LMTP analyses in \citet{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology}.
\item Conjecture 1: No quotient that identifies policies by their standalone observed-data functional can make the IPSI--LMTP commutator representation invariant on an open binary-law class. Gap: \citet{VanDerLaanLuedtkeDiaz2014EM} and \citet{WenMarcusYoung2023SMMR} name representation sensitivity but do not give an ordered-operator obstruction. Consumer: natural-value decision rules in \citet{StensrudLaurendeauSarvet2024Biometrika}.
\end{itemize}

\section{Related work}
\citet{DiazVanDerLaan2012Biometrics} establishes population intervention effects for stochastic interventions and supplies the statistical ancestor of IPSI-style g-formulas. \citet{HaneuseRotnitzky2013StatMed} introduces modified treatment policies that modify the received exposure, which is the point-treatment predecessor of the natural-value policy used here. \citet{Kennedy2019JASA} defines incremental propensity-score interventions as odds-scale shifts of the observed treatment process and gives longitudinal identification and efficiency theory for the resulting stochastic effects. \citet{DiazWilliamsHoffmanSchenck2023JASA} studies longitudinal modified treatment policies and gives sequential-regression identification for policies that may depend on natural treatment values. \citet{YoungHernanRobins2014EM} separates interventions depending on natural treatment values from ordinary dynamic regimes and clarifies why their counterfactual assumptions are not merely notation. \citet{VanDerLaanLuedtkeDiaz2014EM} emphasizes that distinct causal questions can share a statistical estimand, which is the representation issue used here. \citet{WenMarcusYoung2023SMMR} studies interventions depending on the observed treatment process and records that multiplicative-shift distributions can have multiple modified-policy representations. \citet{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics} introduces limited-resource IPSIs, making ordered composition important because the scaling law itself can be policy-dependent. \citet{YoungLoganRobinsHernan2019JASA} studies representative random dynamic interventions as realistic stochastic alternatives to deterministic regimes. \citet{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology} broadens LMTPs to binary and time-varying exposures, so the binary witness below is not a degenerate setting. \citet{StensrudLaurendeauSarvet2024Biometrika} treats the natural treatment intention as decision information, which is exactly the semantic feature the commutator preserves.

The Stage -1.1 catalogue map reports no completed \texttt{eid\_policy\_commutator\_phase} proposal. The nearest in-catalogue warnings are \texttt{eid\_compositional\_reallocation\_effect\_v1}, where an LMTP-adjacent rule-dependence idea collapsed to support-span geometry, and \texttt{eid\_proximal\_completeness\_v1} angle 2, where a commutator-zero-set frontier was abandoned because its boundary and rank cases were not derived. This proposal avoids both failures by exhibiting the operator coefficient directly from observed transition kernels.

\section{Formal setup}
Let \(A_1,L_2,A_2,Y\in\{0,1\}\). Write
\[
\pi=\Pr(A_1=1),\qquad q_a=\Pr(L_2=1\mid A_1=a),\qquad r_{a\ell}=\Pr(A_2=1\mid A_1=a,L_2=\ell),
\]
and \(m_{a\ell b}=\E[Y\mid A_1=a,L_2=\ell,A_2=b]\). Let \(\omega_\lambda(x)=\lambda x/(1-x+\lambda x)\) for \(\lambda>0\). The natural-value policy \(N_\eta\) assigns \(A_2^\star=A_2\) with probability \(\eta\) and \(A_2^\star=1-A_2\) with probability \(1-\eta\), conditional on the natural value of \(A_2\) generated under the preceding regime. Define \(n_\eta(r)=(1-\eta)+(2\eta-1)r\). The two ordered treatment probabilities at history \((a,\ell)\) are
\[
p^{IN}_{a\ell}=\omega_\lambda(n_\eta(r_{a\ell})),\qquad
p^{NI}_{a\ell}=n_\eta(\omega_\lambda(r_{a\ell})).
\]
The ordered means are
\[
\psi_{I_\lambda\circ N_\eta}(P)=\sum_{a,\ell}\Pr(A_1=a,L_2=\ell)\{p^{IN}_{a\ell}m_{a\ell1}+(1-p^{IN}_{a\ell})m_{a\ell0}\},
\]
\[
\psi_{N_\eta\circ I_\lambda}(P)=\sum_{a,\ell}\Pr(A_1=a,L_2=\ell)\{p^{NI}_{a\ell}m_{a\ell1}+(1-p^{NI}_{a\ell})m_{a\ell0}\}.
\]
The commutator coefficient is
\[
C_{\lambda,\eta}(r)=\omega_\lambda(n_\eta(r))-n_\eta(\omega_\lambda(r)).
\]

\begin{verbatim}
qid=eid_policy_commutator_phase
specialization=v1
cluster=ExactID
graph/SWIG=A1 -> L2 -> A2 -> Y with A1 -> A2, A1 -> Y, L2 -> Y allowed
treatment=(A1,A2), with the composed policies acting on A2 conditional on (A1,L2)
target estimand=(psi_{I_lambda o N_eta}(P), psi_{N_eta o I_lambda}(P), Delta_{lambda,eta}(P))
identifying assumptions=consistency, sequential exchangeability, positivity r_{a l} in (0,1)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Observed binary longitudinal law]\label{ass:binary-law}
The observed law factors as \(P(a_1,\ell,a_2,y)=p_1(a_1)q_{\ell\mid a_1}r_{a_2\mid a_1,\ell}s_{y\mid a_1,\ell,a_2}\) on \(\{0,1\}^4\), and all displayed conditional probabilities are well-defined.
\end{assumption}

\begin{assumption}[Sequential exchangeability]\label{ass:seq-exch}
For each ordered regime \(I_\lambda\circ N_\eta\) and \(N_\eta\circ I_\lambda\), the post-policy counterfactual outcome is conditionally independent of the assigned \(A_2\) mechanism given \((A_1,L_2)\), and the observed outcome regression \(m_{a\ell b}\) is invariant under the regime assignment.
\end{assumption}

\begin{assumption}[Positivity]\label{ass:positivity}
For every \((a,\ell)\in\{0,1\}^2\), \(r_{a\ell}\in(0,1)\), \(\lambda>0\), and \(\eta\in(0,1)\).
\end{assumption}

\begin{assumption}[Nondegenerate effect contrast]\label{ass:effect-contrast}
At least one history \((a,\ell)\) has \(m_{a\ell1}\ne m_{a\ell0}\) and \(\Pr(A_1=a,L_2=\ell)>0\).
\end{assumption}

\section{Main results}
\begin{theorem}[Identified commutator coefficient]\label{thm:coefficient}
Under Assumptions~\ref{ass:binary-law}--\ref{ass:positivity},
\[
\Delta_{\lambda,\eta}(P)=\psi_{I_\lambda\circ N_\eta}(P)-\psi_{N_\eta\circ I_\lambda}(P)
=\sum_{a,\ell}\Pr(A_1=a,L_2=\ell)C_{\lambda,\eta}(r_{a\ell})(m_{a\ell1}-m_{a\ell0}).
\]
The coefficient is
\[
C_{\lambda,\eta}(r)=
\frac{\lambda\{(1-\eta)+(2\eta-1)r\}}{1-(1-\eta)-(2\eta-1)r+\lambda\{(1-\eta)+(2\eta-1)r\}}
-(1-\eta)-(2\eta-1)\frac{\lambda r}{1-r+\lambda r}.
\]
\end{theorem}
The proof expands the two g-formulas after substituting the ordered treatment probabilities \(p^{IN}_{a\ell}\) and \(p^{NI}_{a\ell}\). The outcome-regression terms cancel history by history except for the displayed contrast.

\begin{conjecture}[Representation quotient obstruction (NOT YET PROVED)]\label{conj:quotient}
Under Assumptions~\ref{ass:binary-law}--\ref{ass:effect-contrast}, consider any policy equivalence relation \(\sim\) that identifies a natural-value policy \(N_\eta\) with the static stochastic policy \(S_{\eta,P}\) having \(S_{\eta,P}(A_2^\star=1\mid A_1=a,L_2=\ell)=n_\eta(r_{a\ell})\) whenever the two standalone g-formula means agree for all outcome regressions \(m\). On a nonempty open set of laws with \(\lambda\ne1\) and \(\eta\ne1/2\), the commutator map is not well-defined on the quotient: \(I_\lambda\circ N_\eta\) and \(I_\lambda\circ S_{\eta,P}\) can have different ordered means after replacing \(N_\eta\) by an equivalent representative. Equivalently, standalone observed-functional equivalence is strictly coarser than ordered-operator equivalence.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Null reductions]\label{cor:null}
Under Assumptions~\ref{ass:binary-law}--\ref{ass:positivity}, \(\Delta_{\lambda,\eta}(P)=0\) if \(\lambda=1\), if \(\eta=1/2\), or if \(m_{a\ell1}=m_{a\ell0}\) for all histories.
\end{corollary}
The first two cases collapse because \(C_{\lambda,\eta}(r)=0\) for every \(r\); the last collapses because each history-specific outcome contrast is zero.

\paragraph{Exhibit 9.1: finite representation certificate.}
Let \(\pi=1/2\), \(q_0=1/4\), \(q_1=3/4\), \(r_{00}=1/5\), \(r_{01}=1/2\), \(r_{10}=2/5\), \(r_{11}=7/10\), \(m_{a\ell b}=\ell b\), \(\lambda=2\), and \(\eta=3/4\). Then \(n_\eta(r)=1/4+r/2\). At history \((1,1)\),
\[
C_{2,3/4}(7/10)=\omega_2(3/5)-\{1/4+\omega_2(7/10)/2\}
=\frac{3}{4}-\left(\frac14+\frac{7}{17}\right)=\frac{3}{34}.
\]
The denominator is nonzero because all \(r_{a\ell}\in(0,1)\). Since \(\Pr(A_1=1,L_2=1)=3/8\) and \(m_{111}-m_{110}=1\), this single cell contributes \(9/272\) to \(\Delta_{2,3/4}(P)\). The static representative \(S_{\eta,P}\) has the same standalone one-step assigned probability \(n_\eta(r_{a\ell})\) at each history, but it does not carry the natural-value input whose odds are shifted before \(N_\eta\) in \(N_\eta\circ I_\lambda\).

\section{Proof-sketch route}
Theorem~\ref{thm:coefficient}: headline \(\leftarrow\) unfold \S6 ordered means \(\leftarrow\) substitute \(p^{IN}_{a\ell}\) and \(p^{NI}_{a\ell}\) \(\leftarrow\) collect \(m_{a\ell1}-m_{a\ell0}\) by history \(\leftarrow\) simplify the odds-ratio map. Here \(k=3\): historywise collection, nonlinear odds-map simplification, and null-factor verification are substantive algebraic steps. Conjecture~\ref{conj:quotient}: headline \(\leftarrow\) define standalone-functional equivalence \(\leftarrow\) build the static representative \(S_{\eta,P}\) \(\leftarrow\) prove equality against all \(m\) before composition \(\leftarrow\) apply \(I_\lambda\) on the natural-value input in one representative and on the assigned stochastic kernel in the other \(\leftarrow\) use Exhibit~9.1 and continuity to promote the witness to an open set. Here \(k=4\): constructing the representative, proving pre-composition equality uniformly in \(m\), separating the two post-composition operators, and promoting a rational witness by continuity.

\section{Honest scope flags}
Theorem~\ref{thm:coefficient} is routine algebra once the two ordered policies are fixed. Conjecture~\ref{conj:quotient} is the novel statement; the open work is to formalize the class of admissible equivalence relations without making the obstruction tautological. The draft does not claim a universal zero-set theorem for every accidental cancellation variety, and it does not treat resource-constrained IPSI multipliers.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 2, switching from direct zero-phase statements to a representation-quotient obstruction with an exhibited binary witness; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Diaz and van der Laan(2012)]{DiazVanDerLaan2012Biometrics}
Diaz, I. and van der Laan, M. J. (2012).
Population intervention causal effects based on stochastic interventions.
\emph{Biometrics}, 68(2), 541--549.

\bibitem[Diaz et~al.(2023)]{DiazWilliamsHoffmanSchenck2023JASA}
Diaz, I., Williams, N., Hoffman, K. L., and Schenck, E. J. (2023).
Non-parametric causal effects based on longitudinal modified treatment policies.
\emph{Journal of the American Statistical Association}, 118(542), 846--857.

\bibitem[Haneuse and Rotnitzky(2013)]{HaneuseRotnitzky2013StatMed}
Haneuse, S. and Rotnitzky, A. (2013).
Estimation of the effect of interventions that modify the received treatment.
\emph{Statistics in Medicine}, 32(30), 5260--5277.

\bibitem[Hoffman et~al.(2024)]{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology}
Hoffman, K. L., Salazar-Barreto, D., Williams, N., Rudolph, K. E., and Diaz, I. (2024).
A causal roadmap for longitudinal modified treatment policies with complex exposures.
\emph{Epidemiology}, 35(3), 329--338.

\bibitem[Kennedy(2019)]{Kennedy2019JASA}
Kennedy, E. H. (2019).
Nonparametric causal effects based on incremental propensity score interventions.
\emph{Journal of the American Statistical Association}, 114(526), 645--656.

\bibitem[Sarvet et~al.(2023)]{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics}
Sarvet, A. L., Wanis, K. N., Young, J. G., Hernandez-Alejandro, R., and Stensrud, M. J. (2023).
Causal effects of modified treatment policies for resource allocation.
\emph{Biometrics}, 79(4), 3392--3404.

\bibitem[Stensrud et~al.(2024)]{StensrudLaurendeauSarvet2024Biometrika}
Stensrud, M. J., Laurendeau, M., and Sarvet, A. L. (2024).
Interventions on treatment: natural treatment intention as decision information.
\emph{Biometrika}, 111(2), 597--613.

\bibitem[van der Laan et~al.(2014)]{VanDerLaanLuedtkeDiaz2014EM}
van der Laan, M. J., Luedtke, A. R., and Diaz, I. (2014).
Targeted learning of causal effects of realistic individualized treatment rules.
\emph{Epidemiologic Methods}, 3(1), 1--12.

\bibitem[Wen et~al.(2023)]{WenMarcusYoung2023SMMR}
Wen, C., Marcus, J. L., and Young, J. G. (2023).
Intervention treatment distributions that depend on the observed treatment process.
\emph{Statistical Methods in Medical Research}, 32(2), 295--314.

\bibitem[Young et~al.(2014)]{YoungHernanRobins2014EM}
Young, J. G., Hernan, M. A., and Robins, J. M. (2014).
Identification, estimation and approximation of risk under interventions that depend on the natural value of treatment using observational data.
\emph{Epidemiologic Methods}, 3(1), 1--19.

\bibitem[Young et~al.(2019)]{YoungLoganRobinsHernan2019JASA}
Young, J. G., Logan, R. W., Robins, J. M., and Hernan, M. A. (2019).
Inverse probability weighted estimation of risk under representative interventions in observational studies.
\emph{Journal of the American Statistical Association}, 114(526), 938--947.
\end{thebibliography}

\end{document}
