% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_policy\_commutator\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_policy\_commutator\_phase} / \texttt{v1}%
  \\ \large\textit{A two-time IPSI--LMTP commutator coefficient and its feedback phase}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is an ExactID proposal. The locked tuple is
\[
\begin{array}{ll}
\text{qid} & = \texttt{eid\_policy\_commutator\_phase},\\
\text{specialization} & = \texttt{v1},\\
\text{graph/SWIG} & = A_1 \to L_2 \to A_2 \to Y,\quad A_1 \to A_2,\quad A_1 \to Y,\quad L_2 \to Y,\\
\text{treatment} & = (A_1,A_2)\in\{0,1\}^2,\\
\text{target estimand} & =
\Delta_{\delta,\gamma}(P):=\psi_{\delta\circ\gamma}(P)-\psi_{\gamma\circ\delta}(P),\\
\text{identifying assumptions} & =
\text{consistency, sequential exchangeability, positivity, and the natural-value composition semantics in Assumption \ref{ass:natural-semantics}.}
\end{array}
\]
Here \(\delta>0\) is the incremental odds multiplier and \(\gamma\in(0,1/2)\) is the binary natural-value modification probability.

\begin{abstract}
Incremental propensity-score interventions and longitudinal modified treatment policies are both support-preserving stochastic policies. The question is whether these two policy operators commute when applied to the same longitudinal law. The proposed kernel defines a two-time binary transition model and a closed-form commutator coefficient \(\Delta_{\delta,\gamma}(P)\) for applying an odds-multiplier IPSI and a natural-value LMTP in opposite orders. The main conjecture is that \(\Delta_{\delta,\gamma}(P)\) factors into a treatment-confounder-feedback term, an effect-modification term, and positive policy-scale terms. A proof would give a finite witness that two identified policy effects can disagree solely because the policy order changes. It would also supply a phase boundary for realistic longitudinal interventions that use natural treatment values as decision information.
\end{abstract}

\section{Introduction}
Support-preserving longitudinal policies are often treated as modular pieces of one stochastic-intervention toolkit. The claim here is sharper: in the presence of treatment-confounder feedback, the IPSI operator of \citet[Section 2, ``multiply the odds'']{Kennedy2019JASA} and the natural-value LMTP operator of \citet[Section 2, ``longitudinal modified treatment policies'']{DiazWilliamsHoffmanSchenck2023JASA} need not commute.

\citet[Section 2]{Kennedy2019JASA} identifies odds-scale incremental interventions, and \citet[Section 3]{DiazWilliamsHoffmanSchenck2023JASA} identifies longitudinal modified treatment policies through sequential regression. Neither paper compares the causal operator obtained by first changing the treatment law and then reading a natural treatment value with the operator obtained in the reverse order. The kernel is an exact-identification statement for a finite longitudinal SWIG, not a new efficiency calculation or a positivity-free g-formula.

The immediate consumer is the natural-value policy literature surveyed by \citet{YoungHernanRobins2014EM} and extended by \citet{WenMarcusYoung2023SMMR}. A reader who takes the conclusion away should fix the causal representation of a support-preserving policy before composing it with another support-preserving policy.

\begin{itemize}[leftmargin=*]
\item Theorem 1: both ordered IPSI--LMTP estimands are identified by two finite g-formula sums. Gap: \citet{Kennedy2019JASA} and \citet{DiazWilliamsHoffmanSchenck2023JASA} identify each policy class separately, not their ordered composition. Consumer: \citet{WenMarcusYoung2023SMMR}.
\item Conjecture 1: the commutator coefficient factors as a positive policy scale times treatment-confounder feedback times effect modification. Gap: \citet{YoungHernanRobins2014EM} and \citet{WenMarcusYoung2023SMMR} discuss natural-value and representation-sensitive interventions without a zero-phase theorem. Consumer: longitudinal feasible-policy analyses using LMTP software.
\item Theorem 2: an explicit nondegenerate binary law gives \(\Delta_{\delta,\gamma}(P)\ne0\). Gap: existing IPSI and LMTP examples show identification, not noncommutation on one observed law. Consumer: \citet{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics}.
\end{itemize}

\section{Related work}
\citet{Kennedy2019JASA} introduces incremental propensity-score interventions as odds-multiplier stochastic interventions and gives longitudinal identification and efficiency theory. \citet{DiazVanDerLaan2012Biometrics} is the stochastic-intervention ancestor for population intervention causal effects. \citet{HaneuseRotnitzky2013StatMed} introduces modified treatment policies for modified exposure values and motivates natural-value policy semantics. \citet{YoungHernanRobins2014EM} formalizes interventions depending on natural treatment values and separates their identification conditions from ordinary dynamic regimes. \citet{VanDerLaanLuedtkeDiaz2014EM} emphasizes that distinct causal questions can share one statistical estimand, which is why operator representation matters here. \citet{YoungLoganRobinsHernan2019JASA} develops representative random dynamic interventions and provides a comparator class of realistic stochastic longitudinal policies. \citet{DiazWilliamsHoffmanSchenck2023JASA} gives longitudinal modified treatment policies, a sequential-regression identification formula, and efficient estimators. \citet{WenMarcusYoung2023SMMR} studies intervention distributions that depend on the observed treatment process and shows that representation can affect robustness. \citet{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics} develops limited-resource IPSIs and distinguishes natural from assigned treatment values in resource-constrained longitudinal settings. \citet{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology} broadens LMTPs to binary, multivariate, continuous, time-varying, and complex exposures, which makes a binary witness a relevant boundary case rather than a toy outside the literature.

The in-catalogue check used \texttt{CausalSmith/doc/API.md}, Section 3, which records that ExactID and PartialID catalogues are seed-level at present and do not contain a completed policy-commutator theorem. The closest banked in-repo prior art is \texttt{eid\_compositional\_reallocation\_effect\_v1}, whose rejected support-span kernel shows why a new order-sensitive operator coefficient is needed, and \texttt{eid\_proximal\_completeness\_v1} angle 2, whose abandoned row-commutator frontier warns against assuming a zero set instead of deriving it.

\section{Formal setup}
The observed data are \(O=(A_1,L_2,A_2,Y)\), with \(A_1,L_2,A_2\in\{0,1\}\) and \(Y\in\mathbb{R}\). Write
\[
p=\Pr(A_1=1),\qquad q_a=\Pr(L_2=1\mid A_1=a),\qquad r_{a\ell}=\Pr(A_2=1\mid A_1=a,L_2=\ell),
\]
and \(m_{a\ell b}=\E[Y\mid A_1=a,L_2=\ell,A_2=b]\). For \(u\in(0,1)\) define the IPSI odds-shift map
\[
\kappa_\delta(u)=\frac{\delta u}{1-u+\delta u}.
\]
For \(\gamma\in(0,1/2)\) define the binary natural-value modification map
\[
\mu_\gamma(u)=\Pr(\widetilde A=1\mid A^{\natural}\sim\mathrm{Bernoulli}(u))
=\gamma+(1-2\gamma)u.
\]
The ordered estimand \(\psi_{\delta\circ\gamma}(P)\) first shifts the first-period treatment law by \(\kappa_\delta\) and then applies the natural-value modification to the shifted first-period natural value before the second-period kernels are generated. The ordered estimand \(\psi_{\gamma\circ\delta}(P)\) first modifies the first-period natural value by \(\mu_\gamma\) and then applies the odds multiplier to that assigned first-period probability. In both orders, the second-period treatment kernel \(r_{a\ell}\) and outcome mean \(m_{a\ell b}\) are evaluated by the same downstream longitudinal g-formula.

The locked parameters are reproduced as
\[
\begin{array}{ll}
\text{qid} & = \texttt{eid\_policy\_commutator\_phase},\\
\text{specialization} & = \texttt{v1},\\
\text{graph/SWIG} & = A_1 \to L_2 \to A_2 \to Y,\quad A_1 \to A_2,\quad A_1 \to Y,\quad L_2 \to Y,\\
\text{treatment} & = (A_1,A_2)\in\{0,1\}^2,\\
\text{target estimand} & =
\Delta_{\delta,\gamma}(P):=\psi_{\delta\circ\gamma}(P)-\psi_{\gamma\circ\delta}(P),\\
\text{identifying assumptions} & =
\text{consistency, sequential exchangeability, positivity, and Assumption \ref{ass:natural-semantics}.}
\end{array}
\]

\section{Assumptions}
\begin{assumption}[Finite binary longitudinal law]\label{ass:finite-law}
The observed law of \(O=(A_1,L_2,A_2,Y)\) is Markov with the kernels and conditional means defined in Section 3, and \(Y\) has finite first moment in every cell.
\end{assumption}

\begin{assumption}[Sequential exchangeability and consistency]\label{ass:seq-exch}
For every ordered policy considered here, observed outcomes equal their counterfactual values under the observed treatment history, and the usual longitudinal exchangeability restrictions hold at \(A_1\) and \(A_2\) conditional on the measured past.
\end{assumption}

\begin{assumption}[Positivity]\label{ass:positivity}
There is \(\epsilon>0\) such that \(p,q_a,r_{a\ell}\in[\epsilon,1-\epsilon]\) for all \(a,\ell\in\{0,1\}\).
\end{assumption}

\begin{assumption}[Natural-value composition semantics]\label{ass:natural-semantics}
When an LMTP is applied after an IPSI, the natural value \(A_2^{\natural}\) is drawn from the treatment kernel generated under the prior IPSI history. When an IPSI is applied after an LMTP, the odds multiplier is applied to the assigned treatment probability induced by \(\mu_\gamma\).
\end{assumption}

\begin{assumption}[Nondegenerate policy scale]\label{ass:policy-scale}
\(\delta>0\), \(\delta\ne1\), and \(\gamma\in(0,1/2)\).
\end{assumption}

\begin{assumption}[Two-factor phase class]\label{ass:phase-class}
The conditional mean admits the contrast notation \(d_{a\ell}=m_{a\ell 1}-m_{a\ell 0}\). Treatment-confounder feedback is absent when \(q_1=q_0\), and second-time effect modification by \(L_2\) is absent when \(d_{a1}=d_{a0}\) for both \(a\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: ordered g-formula identification]\label{thm:ordered-id}
Under Assumptions \ref{ass:finite-law}--\ref{ass:natural-semantics}, both ordered estimands are identified from \(P\) by
\[
\psi_{\delta\circ\gamma}(P)=
\sum_{a,\ell,b} \mathrm{Bern}\{a;\mu_\gamma(\kappa_\delta(p))\}\,
\mathrm{Bern}\{\ell;q_a\}\,\mathrm{Bern}\{b;r_{a\ell}\}\,m_{a\ell b},
\]
\[
\psi_{\gamma\circ\delta}(P)=
\sum_{a,\ell,b} \mathrm{Bern}\{a;\kappa_\delta(\mu_\gamma(p))\}\,
\mathrm{Bern}\{\ell;q_a\}\,\mathrm{Bern}\{b;r_{a\ell}\}\,m_{a\ell b}.
\]
\end{theorem}
The proof is the finite longitudinal g-formula applied after fixing the ordered policy kernels. Assumption \ref{ass:natural-semantics} determines which kernel supplies the natural value.

\begin{conjecture}[Conjecture 1: commutator phase factorization (NOT YET PROVED)]\label{conj:phase}
Under Assumptions \ref{ass:finite-law}--\ref{ass:phase-class}, there are positive functions \(C_{\delta,\gamma}(p)\) and \(W_{a,\delta,\gamma}(r_{a0},r_{a1})\) such that
\[
\Delta_{\delta,\gamma}(P)
=
(\delta-1)\gamma(1-2\gamma)C_{\delta,\gamma}(p)\,
(q_1-q_0)\,
\sum_{a\in\{0,1\}} W_{a,\delta,\gamma}(r_{a0},r_{a1})\,(d_{a1}-d_{a0}).
\]
Moreover \(\Delta_{\delta,\gamma}(P)=0\) for all \((\delta,\gamma)\) in an open policy rectangle if and only if \(q_1=q_0\) or \(d_{a1}=d_{a0}\) for both \(a\), up to the cellwise accidental-cancellation variety where the displayed polynomial vanishes at isolated policy values.
\end{conjecture}

\begin{theorem}[Theorem 2: noncommuting finite witness]\label{thm:witness}
Under Assumptions \ref{ass:finite-law}--\ref{ass:policy-scale}, the law
\[
p=1/2,\quad q_0=1/4,\quad q_1=3/4,\quad
r_{00}=1/5,\ r_{01}=2/5,\ r_{10}=3/5,\ r_{11}=4/5,
\]
\[
m_{a\ell b}=b\ell
\]
has \(\Delta_{2,1/4}(P)\ne0\).
\end{theorem}
Direct substitution gives different first-period assignment probabilities because \(\mu_{1/4}(\kappa_2(1/2))\ne \kappa_2(\mu_{1/4}(1/2))\). Since \(q_1\ne q_0\) and \(m_{a\ell b}=b\ell\), the difference is not removed by downstream averaging over \(L_2\).

\section{Sanity-check corollaries}
\begin{corollary}[No-feedback reduction]\label{cor:no-feedback}
Under Assumptions \ref{ass:finite-law}--\ref{ass:phase-class}, if \(q_1=q_0\), then the conjectured phase formula collapses to \(\Delta_{\delta,\gamma}(P)=0\) for every \(\delta,\gamma\). The reduction follows because the \(L_2\) mixture is the same after either value of \(A_1\), so the natural-value order cannot change the distribution of histories entering the second treatment kernel.
\end{corollary}

\begin{corollary}[No-effect-modification reduction]\label{cor:no-em}
Under Assumptions \ref{ass:finite-law}--\ref{ass:phase-class}, if \(d_{a1}=d_{a0}\) for both \(a\), then the conjectured phase formula collapses to \(\Delta_{\delta,\gamma}(P)=0\). The reduction follows because the two ordered policies may change the distribution of \(A_2\), but the \(A_2\)-to-\(Y\) contrast no longer varies with the feedback covariate.
\end{corollary}

\paragraph{Exhibit 9.1: finite commutator coefficient.}
For the witness in Theorem \ref{thm:witness}, \(\kappa_2(1/2)=2/3\), \(\mu_{1/4}(u)=1/4+u/2\), and
\[
\mu_{1/4}(\kappa_2(1/2))=\frac{7}{12},\qquad
\kappa_2(\mu_{1/4}(1/2))=\frac{3}{5}.
\]
With \(m_{a\ell b}=b\ell\), only \(\ell=1\) cells contribute, and the two first-period weights multiply different downstream values because \(q_1r_{11}=3/5\) and \(q_0r_{01}=1/10\). All denominators are nonzero, every probability lies in \((0,1)\), and the four \(r_{a\ell}\) values are distinct observed treatment kernels rather than assumed frontier quantities.

\section{Proof-sketch route}
Theorem \ref{thm:ordered-id} follows from the finite longitudinal g-formula after replacing the second treatment kernel by the ordered policy kernel. Conjecture \ref{conj:phase} should be verified by the chain
\[
\text{phase factorization}
\leftarrow \text{unfold Section 3 definitions}
\leftarrow \text{substitute Assumptions \ref{ass:natural-semantics}--\ref{ass:phase-class}}
\leftarrow \text{isolate } \mu_\gamma(\kappa_\delta(p))-\kappa_\delta(\mu_\gamma(p))
\leftarrow \text{separate }L_2\text{-mixture differences by }q_1-q_0
\leftarrow \text{factor the outcome part into }d_{a1}-d_{a0}
\leftarrow \text{show the remaining policy factor is positive on the rectangle}
\leftarrow \text{use polynomial identity and open-set zero arguments}.
\]
This gives \(k=5\) substantive steps beyond definitions: noncommuting scalar-map isolation, mixture separation, outcome-contrast factorization, policy-factor positivity, and polynomial zero-set necessity. Theorem \ref{thm:witness} is a boundary check by direct rational substitution in the two finite sums.

\section{Honest scope flags}
Theorem \ref{thm:ordered-id} and Theorem \ref{thm:witness} are intended as routine finite-law algebra. Conjecture \ref{conj:phase} is the novel kernel and is not yet proved. The exact treatment of accidental cancellation varieties may need refinement; the current conjecture separates generic open rectangles from isolated policy values. No claims are made about efficient influence functions, resource-constrained multipliers, or continuous-treatment LMTPs in this version.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft of the two-time IPSI--LMTP commutator coefficient and feedback phase; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Diaz and van der Laan(2012)]{DiazVanDerLaan2012Biometrics}
Diaz, I. and van der Laan, M. J. (2012).
\newblock Population intervention causal effects based on stochastic interventions.
\newblock \emph{Biometrics}, 68(2), 541--549.

\bibitem[Diaz et al.(2023)]{DiazWilliamsHoffmanSchenck2023JASA}
Diaz, I., Williams, N., Hoffman, K. L., and Schenck, E. J. (2023).
\newblock Nonparametric causal effects based on longitudinal modified treatment policies.
\newblock \emph{Journal of the American Statistical Association}, 118(542), 846--857.

\bibitem[Haneuse and Rotnitzky(2013)]{HaneuseRotnitzky2013StatMed}
Haneuse, S. and Rotnitzky, A. (2013).
\newblock Estimation of the effect of interventions that modify the received treatment.
\newblock \emph{Statistics in Medicine}, 32(30), 5260--5277.

\bibitem[Hoffman et al.(2024)]{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology}
Hoffman, K. L., Salazar-Barreto, D., Williams, N., Rudolph, K. E., and Diaz, I. (2024).
\newblock Studying continuous, time-varying, and complex exposures using longitudinal modified treatment policies.
\newblock \emph{Epidemiology}.

\bibitem[Kennedy(2019)]{Kennedy2019JASA}
Kennedy, E. H. (2019).
\newblock Nonparametric causal effects based on incremental propensity score interventions.
\newblock \emph{Journal of the American Statistical Association}, 114(526), 645--656.

\bibitem[Sarvet et al.(2023)]{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics}
Sarvet, A. L., Wanis, K. N., Young, J. G., Hernandez-Alejandro, R., and Stensrud, M. J. (2023).
\newblock Longitudinal incremental propensity score interventions for limited resource settings.
\newblock \emph{Biometrics}, 79(4), 3418--3430.

\bibitem[van der Laan et al.(2014)]{VanDerLaanLuedtkeDiaz2014EM}
van der Laan, M. J., Luedtke, A. R., and Diaz, I. (2014).
\newblock Targeted learning of the mean outcome under an optimal dynamic treatment rule.
\newblock \emph{Epidemiologic Methods}, 3(1), 61--81.

\bibitem[Wen et al.(2023)]{WenMarcusYoung2023SMMR}
Wen, L., Marcus, J. L., and Young, J. G. (2023).
\newblock Intervention treatment distributions that depend on the observed treatment process and model double robustness in causal survival analysis.
\newblock \emph{Statistical Methods in Medical Research}, 32(3), 477--492.

\bibitem[Young et al.(2014)]{YoungHernanRobins2014EM}
Young, J. G., Hernan, M. A., and Robins, J. M. (2014).
\newblock Identification, estimation and approximation of risk under interventions that depend on the natural value of treatment.
\newblock \emph{Epidemiologic Methods}, 3(1), 1--19.

\bibitem[Young et al.(2019)]{YoungLoganRobinsHernan2019JASA}
Young, J. G., Logan, R. W., Robins, J. M., and Hernan, M. A. (2019).
\newblock Inverse probability weighted estimation of risk under representative interventions in observational studies.
\newblock \emph{Journal of the American Statistical Association}, 114(526), 938--947.
\end{thebibliography}

\end{document}
