% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_policy\_commutator\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section initially contains one stage-1 placeholder.
%    Replace each placeholder with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_policy\_commutator\_phase} / \texttt{v1}\\ \large\textit{A sharp zero phase for ordered IPSI--LMTP longitudinal policy operators}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
ExactID anchor. The locked tuple is $(qid, specialization, graph/SWIG, treatment, target estimand, identifying assumptions)$ with
\[
\begin{gathered}
qid=\texttt{eid\_policy\_commutator\_phase},\qquad specialization=\texttt{v1},\\
O=(A_1,L_2,A_2,Y),\quad A_1,L_2,A_2\in\{0,1\},\quad Y\in\mathbb R .
\end{gathered}
\]
The graph is the two-time longitudinal DAG $A_1\to L_2\to A_2\to Y$, $A_1\to A_2$, $A_1\to Y$, and $L_2\to Y$, with baseline suppressed as constant. The treatment is the ordered pair $(A_1,A_2)$. The target estimands are the two ordered stochastic-policy means $\psi_{I\circ M}(P;\delta)$ and $\psi_{M\circ I}(P;\delta)$ obtained by composing an odds-multiplier incremental propensity-score intervention $I_\delta$ with a natural-value longitudinal modified treatment policy $M$. The identifying assumptions are consistency, sequential exchangeability for the two policy orders, positivity of the observed binary kernels, and the natural-value compatibility condition stated in Assumptions 1--4. The focal bounding-free functional is the identified commutator $\Delta_\delta(P)=\psi_{I\circ M}(P;\delta)-\psi_{M\circ I}(P;\delta)$; $\mathcal C_\delta(P)$ is the closed-form product coefficient conjectured to equal it.

\begin{abstract}
Longitudinal stochastic policies are usually studied one intervention class at a time. This proposal asks whether two support-preserving classes, incremental propensity-score interventions and natural-value modified treatment policies, commute when both are applied to the same two-time law. The main conjecture gives a closed-form commutator coefficient and claims that its zero set is exactly a union of two phases: no treatment-confounder feedback and no $L_2$-modification of the $A_2$ outcome contrast. The claim is not an efficiency calculation or a new g-formula; it is an operator non-equivalence statement about two identified causal regimes. A proof would give applied longitudinal analyses a finite diagnostic for when the order of realistic policy definitions is causal content rather than notation.
\end{abstract}

\section{Introduction}
Support-preserving policy effects avoid the artificial positivity demands of deterministic regimes, but realistic policies may be composed in more than one order. In the two-time binary model below, the conjecture is that the IPSI--LMTP commutator has a sharp polynomial zero phase: it vanishes exactly when treatment does not move the intermediate covariate, or when the intermediate covariate does not modify the incremental $A_2$ outcome contrast.

Kennedy's incremental intervention identifies odds-shift policy means for longitudinal binary treatments \citep[p.~646, Sec.~2]{Kennedy2019JASA}, while Diaz, Williams, Hoffman, and Schenck identify longitudinal modified treatment policies whose rules can depend on natural treatment values \citep[Sec.~2]{DiazWilliamsHoffmanSchenck2023JASA}. Those papers do not compare the two ordered operators on one law. The kernel is an exact-identification statement because both ordered means are expressed as observed-kernel functionals under sequential exchangeability.

The concrete consumer is the natural-value intervention literature that treats assigned and natural treatment histories as distinct causal objects \citep{YoungHernanRobins2014EM}. A reader analyzing resource-preserving or feasibility-preserving longitudinal policies would record the operator order and check the commutator phase before interpreting two policy descriptions as interchangeable.

\begin{itemize}[leftmargin=*]
\item Theorem 1: Under sequential exchangeability and positivity, the two ordered regimes are explicit finite observed-kernel functionals $\psi_{I\circ M}$ and $\psi_{M\circ I}$. Gap: \citet{Kennedy2019JASA}, \citet{DiazWilliamsHoffmanSchenck2023JASA}, and \citet{YoungHernanRobins2014EM} supply the single-policy extended g-formula ingredients, but not the ordered-pair functional used below. Consumer: natural-value policy analyses in \citet{YoungHernanRobins2014EM}.
\item Conjecture 1: The independently defined commutator $\Delta_\delta(P)=\psi_{I\circ M}(P;\delta)-\psi_{M\circ I}(P;\delta)$ equals $\{s_\delta(e)-e\}(q_1-q_0)(r_1-r_0)$. Gap: \citet{WenMarcusYoung2023SMMR} studies representation-sensitive observed-treatment-process interventions without an operator non-equivalence certificate. Consumer: representation-sensitive policy reporting in longitudinal survival analyses.
\item Conjecture 2: For the open saturated binary class with active first-period odds shift, $\Delta_\delta(P)=0$ if and only if $q_1=q_0$ or $r_1=r_0$. Gap: \citet[p.~3420, Sec.~2.2]{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics} and \citet[Sec.~2]{WenMarcusYoung2023SMMR} treat realistic stochastic-policy representations, but neither gives a generic-class commutator zero phase. Consumer: limited-resource IPSI analyses and observed-treatment-process policy representations.
\end{itemize}

\section{Related work}
\citet{Kennedy2019JASA} defines incremental propensity-score interventions by multiplying the odds of treatment and gives identifying conditions and efficiency theory for longitudinal effects. \citet{DiazVanderLaan2012Biometrics} develops population intervention effects for stochastic interventions and supplies the broader statistical ancestor of IPSI-style g-formulas. \citet{HaneuseRotnitzky2013SIM} introduces modified treatment policies that modify the received exposure and motivates natural-value rules. \citet{YoungHernanRobins2014EM} separates interventions that depend on natural treatment values from ordinary dynamic-regime interventions. \citet{VanderLaanLuedtkeDiaz2014EM} emphasizes that different causal questions can share a statistical estimand, which is the representation warning behind an operator commutator. \citet{YoungLoganRobinsHernan2019JASA} develops representative random dynamic interventions as realistic longitudinal alternatives to deterministic regimes. \citet{DiazWilliamsHoffmanSchenck2023JASA} gives sequential-regression identification and efficiency theory for longitudinal modified treatment policies. \citet{WenMarcusYoung2023SMMR} shows that intervention distributions depending on the observed treatment process may need representation-specific derivations. \citet{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics} develops limited-resource IPSIs and distinguishes natural from assigned treatment values under regimes. \citet{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology} broadens LMTPs to binary, multivariate, continuous, time-varying, and complex exposures, making a binary transition-kernel witness a minimal test case.

The in-catalogue CausalSmith prior work has no completed ExactID entry for this qid. The closest banked artifacts are \texttt{eid\_compositional\_reallocation\_effect\_v1}, which collapsed to support-span geometry for rule-dependent modified policies, and \texttt{eid\_proximal\_completeness\_v1} angle 2, which used commutator-zero-set language but left rank-change boundary cases unresolved. The active CausalSmith catalogue in \texttt{doc/API.md} records ExactID and PartialID as staging clusters and has no policy-operator commutator theorem.

\section{Formal setup}
Let $P$ be the observed law of $O=(A_1,L_2,A_2,Y)$ with binary $A_1,L_2,A_2$. Define
\[
e=P(A_1=1),\quad q_a=P(L_2=1\mid A_1=a),\quad p_{a\ell}=P(A_2=1\mid A_1=a,L_2=\ell),
\]
and $\mu_{a\ell b}=\E[Y\mid A_1=a,L_2=\ell,A_2=b]$. For $\delta>0$, let $s_\delta(x)=\delta x/(1-x+\delta x)$ for $x\in(0,1)$. The IPSI operator $I_\delta$ replaces a binary treatment kernel $x$ by $s_\delta(x)$. The LMTP operator $M$ is the natural-value policy whose second-period assigned treatment has the same natural support but whose effective contrast is normalized by Definition 3.

\begin{definition}[Observed-kernel weights]
For $x\in(0,1)$, set
\[
w_1(x)=xq_1+(1-x)q_0,\qquad w_0(x)=1-w_1(x).
\]
Let
\[
m_\ell^0=(1-p_{1\ell})\mu_{1\ell0}+p_{1\ell}\mu_{1\ell1},\qquad
m_\ell^\delta=(1-s_\delta(p_{1\ell}))\mu_{1\ell0}+s_\delta(p_{1\ell})\mu_{1\ell1}.
\]
The common natural-value baseline is
\[
B_\delta(P)=w_0(e)m_0^0+w_1(e)m_1^0 .
\]
\end{definition}

\begin{definition}[Ordered policy means]
The two identified ordered means are the finite observed-kernel functionals
\[
\psi_{I\circ M}(P;\delta)=B_\delta(P)+w_0(s_\delta(e))(m_0^\delta-m_0^0)+w_1(s_\delta(e))(m_1^\delta-m_1^0),
\]
and
\[
\psi_{M\circ I}(P;\delta)=B_\delta(P)+w_0(e)(m_0^\delta-m_0^0)+w_1(e)(m_1^\delta-m_1^0).
\]
The first functional evaluates the natural-value second-period modification after the first-period odds-shifted history distribution. The second evaluates the same modification along the unshifted natural-value history distribution before the first-period odds shift is applied.
\end{definition}

\begin{definition}[Incremental second-period contrast]
For $\ell\in\{0,1\}$, set
\[
r_\ell=m_\ell^\delta-m_\ell^0=\{s_\delta(p_{1\ell})-p_{1\ell}\}\{\mu_{1\ell1}-\mu_{1\ell0}\}.
\]
The no-effect-modification phase is $r_1=r_0$.
\end{definition}

\begin{definition}[Commutator coefficient]
The independent focal object is the ordered-policy difference
\[
\Delta_\delta(P)=\psi_{I\circ M}(P;\delta)-\psi_{M\circ I}(P;\delta).
\]
The product coefficient whose equality to this difference is conjectured is
\[
\mathcal C_\delta(P)=\{s_\delta(e)-e\}(q_1-q_0)(r_1-r_0).
\]
\end{definition}

The locked parameters are reproduced here:
\begin{quote}\small
ExactID anchor. The locked tuple is $(qid, specialization, graph/SWIG, treatment, target estimand, identifying assumptions)$ with $qid=\texttt{eid\_policy\_commutator\_phase}$, $specialization=\texttt{v1}$, $O=(A_1,L_2,A_2,Y)$, $A_1,L_2,A_2\in\{0,1\}$, and $Y\in\mathbb R$. The graph is the two-time longitudinal DAG $A_1\to L_2\to A_2\to Y$, $A_1\to A_2$, $A_1\to Y$, and $L_2\to Y$. The treatment is $(A_1,A_2)$. The targets are $\psi_{I\circ M}(P;\delta)$, $\psi_{M\circ I}(P;\delta)$, $\Delta_\delta(P)$, and $\mathcal C_\delta(P)$ under consistency, sequential exchangeability, positivity, and natural-value compatibility.
\end{quote}

\section{Assumptions}
\begin{assumption}[Consistency]\label{ass:consistency}
Observed outcomes and covariates equal their counterfactual values under the observed treatment history.
\end{assumption}

\begin{assumption}[Sequential exchangeability]\label{ass:seqex}
For each ordered policy considered here, treatment assignment at $A_1$ and $A_2$ is conditionally independent of future counterfactual outcomes given the observed past in the two-time DAG.
\end{assumption}

\begin{assumption}[Kernel positivity]\label{ass:positivity}
There is $\epsilon>0$ such that $e,p_{a\ell}\in[\epsilon,1-\epsilon]$ and $P(A_1=a,L_2=\ell)>0$ for all $a,\ell\in\{0,1\}$.
\end{assumption}

\begin{assumption}[Natural-value compatibility]\label{ass:naturalcompat}
The LMTP natural value at time 2 is indexed by the assigned first-period history, so the extended g-formula evaluates the natural treatment kernel under the history generated by the earlier operator in the ordered composition.
\end{assumption}

\begin{assumption}[Nondegenerate phase screen]\label{ass:nondegenerate}
The odds shift is active, $\delta\ne1$, the first-period treatment is nondegenerate, $0<e<1$, and the first-period shift is nonzero, $s_\delta(e)\ne e$.
\end{assumption}

\section{Main results}
\begin{theorem}[Identification of the ordered means]\label{thm:identified}
Under Assumptions \ref{ass:consistency}--\ref{ass:naturalcompat}, $\psi_{I\circ M}(P;\delta)$ and $\psi_{M\circ I}(P;\delta)$ are identified by the two finite observed-kernel functionals in Definition 2. They use only $e,q_a,p_{a\ell}$ and $\mu_{a\ell b}$.
\end{theorem}
The proof is the standard extended g-formula with the two ordered policy kernels written in Definition 2. This theorem is bookkeeping rather than the novelty claim; its role is to put the two standard policy ingredients on one observed-kernel scale.

\begin{conjecture}[Commutator factorization (NOT YET PROVED)]\label{conj:factorization}
Under Assumptions \ref{ass:consistency}--\ref{ass:naturalcompat},
\[
\Delta_\delta(P)
=\mathcal C_\delta(P)
=\{s_\delta(e)-e\}(q_1-q_0)(r_1-r_0).
\]
This is a strict operator-comparison statement against \citet{Kennedy2019JASA} and \citet{DiazWilliamsHoffmanSchenck2023JASA}: the same observed law identifies both ordered regimes, but their difference is a feedback-by-effect-modification coefficient that neither single-policy theory contains.
\end{conjecture}

\begin{conjecture}[Sharp zero phase (NOT YET PROVED)]\label{conj:zerophase}
Under Assumptions \ref{ass:consistency}--\ref{ass:nondegenerate} and the factorization in Conjecture \ref{conj:factorization},
\[
\Delta_\delta(P)=0\quad\Longleftrightarrow\quad q_1=q_0\;\;\text{or}\;\; r_1=r_0.
\]
Thus commutation is equivalent to no first-period treatment-confounder feedback or no $L_2$-modification of the incremental second-period outcome contrast.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[No-feedback reduction]
Under Assumptions \ref{ass:consistency}--\ref{ass:nondegenerate} and Conjecture \ref{conj:factorization}, if $q_1=q_0$ then $\Delta_\delta(P)=0$ because the factor $(q_1-q_0)$ vanishes. This reduces to the single-policy g-formula setting where changing $A_1$ does not move the distribution of the intermediate covariate.
\end{corollary}

\begin{corollary}[No-modification reduction]
Under Assumptions \ref{ass:consistency}--\ref{ass:nondegenerate} and Conjecture \ref{conj:factorization}, if $r_1=r_0$ then $\Delta_\delta(P)=0$ because the second-period incremental contrast is invariant across $L_2$. This is the homogeneous-effect corner in which the natural-value normalization has no covariate-specific outcome contrast to reorder.
\end{corollary}

\begin{example}[Exhibit 9.1: computed ordered means and commutator]\label{ex:computed}
Take $\delta=2$, $e=1/2$, $q_0=1/5$, $q_1=4/5$, $p_{10}=1/4$, $p_{11}=3/5$, $(\mu_{100},\mu_{101})=(0,1)$, and $(\mu_{110},\mu_{111})=(0,3)$. Then $s_2(e)=2/3$, $s_2(p_{10})=2/5$, $s_2(p_{11})=3/4$, so $m_0^0=1/4$, $m_1^0=9/5$, $r_0=(2/5-1/4)\cdot1=3/20$, and $r_1=(3/4-3/5)\cdot3=9/20$. The common baseline is $B_2(P)=w_0(1/2)m_0^0+w_1(1/2)m_1^0=41/40$. Therefore
\[
\psi_{I\circ M}(P;2)=41/40+(2/5)(3/20)+(3/5)(9/20)=271/200,
\]
while
\[
\psi_{M\circ I}(P;2)=41/40+(1/2)(3/20)+(1/2)(9/20)=53/40.
\]
Their difference is $271/200-53/40=3/100$, and the product coefficient gives the same value:
\[
\mathcal C_2(P)=(2/3-1/2)(4/5-1/5)(9/20-3/20)=3/100.
\]
All denominators are positive, every binary kernel lies in $(0,1)$, and the two values are not related by a normalization because the displayed difference is on the common outcome-mean scale.
\end{example}

\section{Proof-sketch route}
For Conjecture \ref{conj:factorization}, the route is: headline $\leftarrow$ unfold the ordered extended-g-formulas $\leftarrow$ substitute Assumptions \ref{ass:consistency}--\ref{ass:naturalcompat} $\leftarrow$ derive the two explicit kernels in Definition 2 from the assigned-history SWIG $\leftarrow$ isolate the first-period odds-shift term in the $L_2$ mixture $\leftarrow$ collect the $L_2=1$ and $L_2=0$ second-period incremental contrasts $\leftarrow$ cancel common natural-value baseline terms $\leftarrow$ obtain the product form by binary-kernel algebra. This gives $k=5$ substantive steps after definitions. For Conjecture \ref{conj:zerophase}, the route is: zero phase for $\Delta_\delta(P)$ $\leftarrow$ Conjecture \ref{conj:factorization} $\leftarrow$ use Assumption \ref{ass:nondegenerate} to remove the active odds-shift factor $\leftarrow$ apply the integral-domain property of real numbers to the remaining product $\leftarrow$ map the two surviving factors to the feedback and effect-modification phases. This gives $k=3$ substantive steps after definitions.

\section{Honest scope flags}
The identification statement is a theorem conditional on the ordered-policy counterfactual semantics in Assumption \ref{ass:naturalcompat}. The factorization and the sharp zero-set theorem are conjectures. The main risk is that a fully expanded LMTP definition introduces an additional natural-value compatibility term; if so, Conjecture \ref{conj:factorization} should be weakened to include that term rather than forcing the two-factor phase. The previous angle's unequal-witness-only claim is not reused here; the present angle targets the exact zero set.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the sharp zero-set angle after the unequal-witness seed was exhausted; prior verdict: none.
\item v2 (revise) -- replaced prose-only ordered means with explicit finite functionals, computed both ordered means in Exhibit 9.1, corrected the van der Laan--Luedtke--Diaz bibliography entry, and rewrote the zero phase against $\Delta_\delta(P)$; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Diaz and van der Laan(2012)]{DiazVanderLaan2012Biometrics}
Diaz, I. and van der Laan, M. J. (2012). Population intervention causal effects based on stochastic interventions. \textit{Biometrics} 68, 541--549.

\bibitem[Diaz et~al.(2023)]{DiazWilliamsHoffmanSchenck2023JASA}
Diaz, I., Williams, N., Hoffman, K. L., and Schenck, E. J. (2023). Non-parametric causal effects based on longitudinal modified treatment policies. \textit{Journal of the American Statistical Association} 118, 846--857.

\bibitem[Haneuse and Rotnitzky(2013)]{HaneuseRotnitzky2013SIM}
Haneuse, S. and Rotnitzky, A. (2013). Estimation of the effect of interventions that modify the received treatment. \textit{Statistics in Medicine} 32, 5260--5277.

\bibitem[Hoffman et~al.(2024)]{HoffmanSalazarBarretoWilliamsRudolphDiaz2024Epidemiology}
Hoffman, K. L., Salazar-Barreto, D., Williams, N., Rudolph, K. E., and Diaz, I. (2024). Causal effects based on modified treatment policies for complex exposures. \textit{Epidemiology} 35, 271--280.

\bibitem[Kennedy(2019)]{Kennedy2019JASA}
Kennedy, E. H. (2019). Nonparametric causal effects based on incremental propensity score interventions. \textit{Journal of the American Statistical Association} 114, 645--656.

\bibitem[Sarvet et~al.(2023)]{SarvetWanisYoungHernandezAlejandroStensrud2023Biometrics}
Sarvet, A. L., Wanis, K. N., Young, J. G., Hernandez-Alejandro, R., and Stensrud, M. J. (2023). Longitudinal incremental propensity score interventions for limited resource settings. \textit{Biometrics} 79, 3418--3430.

\bibitem[van der Laan et~al.(2014)]{VanderLaanLuedtkeDiaz2014EM}
van der Laan, M. J., Luedtke, A. R., and Diaz, I. (2014). Discussion of ``Identification, estimation and approximation of risk under interventions that depend on the natural value of treatment using observational data,'' by Jessica Young, Miguel Hernan, and James Robins. \textit{Epidemiologic Methods} 3, 21--32.

\bibitem[Wen et~al.(2023)]{WenMarcusYoung2023SMMR}
Wen, L., Marcus, J. L., and Young, J. G. (2023). Intervention treatment distributions that depend on the observed treatment process and model double robustness in causal survival analysis. \textit{Statistical Methods in Medical Research} 32, 557--573.

\bibitem[Young et~al.(2014)]{YoungHernanRobins2014EM}
Young, J. G., Hernan, M. A., and Robins, J. M. (2014). Identification, estimation and approximation of risk under interventions that depend on the natural value of treatment using observational data. \textit{Epidemiologic Methods} 3, 1--19.

\bibitem[Young et~al.(2019)]{YoungLoganRobinsHernan2019JASA}
Young, J. G., Logan, R. W., Robins, J. M., and Hernan, M. A. (2019). Inverse probability weighted estimation of risk under representative interventions in observational studies. \textit{Journal of the American Statistical Association} 114, 938--947.
\end{thebibliography}

\end{document}
