% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_compositional\_reallocation\_effect, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_compositional\_reallocation\_effect} / \texttt{v1}%
  \\ \large\textit{Exact reallocation invariance for component effects on a simplex}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form ExactID convention. The tuple is
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
Here \texttt{qid} is \texttt{eid\_compositional\_reallocation\_effect} and \texttt{specialization} is \texttt{v1}. The graph/SWIG has baseline covariates \(X\), a simplex-valued treatment \(A=(A_1,\ldots,A_K)\in\Delta^{K-1}\), and outcome \(Y\), with potential outcomes \(Y(a)\) for every \(a\) in a relative open subset \(S\subseteq\Delta^{K-1}\). The treatment is the full composition \(A\), not a single component. The target estimand is the local component-\(j\) causal derivative at \(a\),
\[
\tau_j(a;q)=D_{h_j(q)} m(a),\qquad
h_j(q)=e_j-\sum_{\ell\neq j} q_\ell e_\ell,\quad
q\in\Delta_{-j},
\]
where \(m(a)=\E\{Y(a)\}\) and \(q\) is the reallocation rule over the displaced components. The identifying assumptions are consistency, conditional exchangeability \(Y(a)\perp A\mid X\), local overlap for every tangent segment used by \(h_j(q)\), and differentiability of the identified dose-response surface \(m\) on \(S\).
The focal object is the reallocation-invariance frontier
\[
\mathcal{R}_j(a)=\{\tau_j(a;q):q\in\mathcal{Q}_j(a)\},\qquad
\kappa_j(a)=\sup_{q,q'\in\mathcal{Q}_j(a)}|\tau_j(a;q)-\tau_j(a;q')|,
\]
where \(\mathcal{Q}_j(a)\subseteq\Delta_{-j}\) is the support-admissible set of reallocations. A reported component-\(j\) effect is policy-free exactly when \(\kappa_j(a)=0\).
The non-tautological certificate used below is the support-span condition
\[
\mathcal{L}_j(a)=\mathrm{span}\{q-q':q,q'\in\mathcal{Q}_j(a)\},\qquad
\Pi_{\mathcal{L}_j(a)}\gamma_{-j}(a)=0,
\]
where \(\gamma_{-j}(a)\) is the vector of displaced-component tangent derivatives and \(\Pi_{\mathcal{L}_j(a)}\) is Euclidean projection onto the linear subspace generated by admissible rule contrasts.

\begin{abstract}
Many empirical papers report the effect of increasing one component of a composition while the total is fixed. Such a phrase is incomplete unless it also states which other components are displaced. The main conjecture characterizes the exceptional case in which the phrase is nevertheless well-defined through a support-span restriction on the simplex gradient. When the restriction fails, the observational or randomized mixture law identifies a set of rule-specific substitution effects, not a component effect. A three-component exhibit shows why opposite signed rule-specific effects can arise under one mixture-response law.
\end{abstract}

\section{Introduction}
Empirical analyses of diets, pollution mixtures, time use, and budgets often ask for the causal effect of increasing one share. On a simplex, this question is not a one-coordinate intervention. Conjecture 1 states that the identified object is a reallocation-invariance frontier, and a component-\(j\) effect exists only when the displaced-component gradient is orthogonal to every supported contrast between reallocation rules.

\citet[][pp. 1310--1312]{ArnoldBerrieTennantGilthorpe2020} show that fixed-total compositional effects are joint relative effects, \citet[][pp. 1380--1384]{TomovaGilthorpeTennant2022} separate direct, inadvertent, and average-relative substitutions, and \citet[][Sec. 4]{VanderWeeleHernan2013} show that version distributions define different causal effects. The gap is that these papers classify or identify effects after a rule or version law has been chosen, while the present question gives the exact support-span condition under which all admissible versions collapse to one component estimand. The kernel is an exact-identification statement for a continuous, simplex-valued treatment.

The immediate consumer is nutritional substitution analysis, where \citet{TomovaGilthorpeTennant2022} show that multi-component substitutions can be obscure or biased if the estimand is not fixed before modeling. A reader would report a rule-specific effect unless the gradient-equality restriction is checked or imposed by design.

\begin{itemize}[leftmargin=1.8em]
\item Conjecture 1: The reallocation-invariance frontier \(\mathcal{R}_j(a)\) is point-identified as a compact set of path derivatives, and all admissible substitution versions collapse to one component effect exactly when \(\Pi_{\mathcal{L}_j(a)}\gamma_{-j}(a)=0\). Gap: ArnoldBerrieTennantGilthorpe2020 and TomovaGilthorpeTennant2022 define relative/substitution effects and VanderWeeleHernan2013 identifies version-specific effects, but they do not give the support-span collapse criterion. Consumer: dietary and environmental mixture studies.
\item Theorem 1: Conditional on the identified surface \(m\), the frontier endpoints are the extrema of an affine simplex-gradient map over the support-admissible reallocation set. Gap: HiranoImbens2004 is background for \(m\); the theorem is the simplex frontier map from \(m\) to all admissible substitution policies. Consumer: observed-support mixture policies.
\item Corollary 1: Under full displaced-component support, if the displaced components have a common zero ambient derivative in an unconstrained embedding, the invariant simplex effect collapses to the standard continuous-treatment partial derivative. Gap: HiranoImbens2004 and HinesDiazOrdazVansteelandt2026 are routine background; the new claim is only the full-support simplex-to-Euclidean recovery clause. Consumer: scalar continuous-treatment dose-response users.
\end{itemize}

\section{Related work}
\citet{ArnoldBerrieTennantGilthorpe2020} give the causal compositional-data warning that fixed-total relative effects are joint effects whose interpretation must be explicit. \citet{TomovaGilthorpeTennant2022} formalize substitution estimands in nutritional epidemiology and show that models can target different substitutions. \citet{Piepel2006} compares component-slope, Scheffe, and Cox parameterizations in mixture experiments, making clear that a component slope depends on a direction or reference composition. \citet{AitchisonBaconShone1984} develop log-contrast mixture models with zero-sum restrictions, which supply a statistical language for simplex coordinates but not potential-outcome identification.

\citet{VanderWeeleHernan2013} treat multiple versions of treatment and identify effects after the version or version distribution is specified; simplex reallocations are versions of a component increase, so the support-span condition is the proposed version-collapse frontier. \citet{Diaz2023LMTP} identifies longitudinal modified treatment policies after the policy map is specified, which parallels rule-specific reallocation effects rather than rule-invariant component effects. \citet{HiranoImbens2004} identify scalar continuous-treatment dose-response functions under weak unconfoundedness, and \citet{Cattaneo2010} studies semiparametric efficiency for multivalued treatments under ignorability. \citet{HinesDiazOrdazVansteelandt2026} derive efficient average derivative estimators for continuous treatments using local overlap; the present proposal moves the derivative to the simplex tangent space.

\citet{AntonelliZigler2024} emphasize that environmental-mixture estimands may require unsupported mixture values, and \citet{HuangDongLinAntonelli2026} frame positivity as a central obstacle for deterministic multivariate mixture interventions. \citet{DAmourDingFellerLeiSekhon2021} show that overlap restrictions become more demanding in high dimension, which motivates the local-overlap clause in this proposal. The Stage -1.1 catalogue scan reports no prior CausalSmith proposal on compositional treatments; the closest in-catalogue neighbors are \texttt{pid\_dose\_response\_iv} on dose-derivative signs under cross-dose coupling and \texttt{pid\_dose\_response\_shape} on joint-law restrictions for dosewise claims.

\section{Formal setup}
Let \(K\geq 3\), \(\Delta^{K-1}=\{a\in\R_+^K:\sum_k a_k=1\}\), and let \(S\) be a relative open subset of the simplex. The observed law is \(P\) for \(O=(Y,A,X)\), with \(A\in S\) on the support used below. Potential outcomes are \(\{Y(a):a\in S\}\), and the causal dose-response surface is \(m(a)=\E\{Y(a)\}\). The conditional response surface is \(\mu(a,x)=\E(Y\mid A=a,X=x)\), so under the assumptions \(m(a)=\int \mu(a,x)\,dP_X(x)\).

For component \(j\), define the admissible reallocation simplex \(\Delta_{-j}=\{q\in\R_+^{K-1}:\sum_{\ell\neq j}q_\ell=1\}\). A rule \(q\in\Delta_{-j}\) increases component \(j\) by one infinitesimal unit and removes shares from the remaining components according to \(q\), giving direction \(h_j(q)=e_j-\sum_{\ell\neq j}q_\ell e_\ell\). If \(\gamma(a)\in\R^K/\mathrm{span}\{\one\}\) is any tangent gradient satisfying \(D_v m(a)=\gamma(a)^\transpose v\) for all \(v\) with \(\one^\transpose v=0\), then
\[
\tau_j(a;q)=D_{h_j(q)}m(a)=\gamma_j(a)-\sum_{\ell\neq j}q_\ell\gamma_\ell(a).
\]
Let \(\mathcal{Q}_j(a)\) be the set of \(q\in\Delta_{-j}\) for which the segment \(a+t h_j(q)\) is supported for small \(|t|\). The reallocation-invariance frontier and diameter are
\[
\mathcal{R}_j(a)=\{\tau_j(a;q):q\in\mathcal{Q}_j(a)\},\qquad
\kappa_j(a)=\sup_{r,s\in\mathcal{R}_j(a)}|r-s|.
\]
Let \(\gamma_{-j}(a)\in\R^{K-1}\) collect the displaced-component coordinates of any tangent-gradient representative, and let
\[
\mathcal{L}_j(a)=\mathrm{span}\{q-q':q,q'\in\mathcal{Q}_j(a)\}\subseteq\{u:\one^\transpose u=0\}.
\]
The support-span certificate is \(\Pi_{\mathcal{L}_j(a)}\gamma_{-j}(a)=0\). This condition is independent of the definition of \(\kappa_j(a)\); it is stated only in terms of the identified tangent gradient and the observable local support geometry of admissible reallocations.

\begin{verbatim}
Locked parameters.
qid = eid_compositional_reallocation_effect
specialization = v1
graph/SWIG = X -> A -> Y with potential outcomes Y(a), a in S subset Delta^{K-1}
treatment = full composition A, not the coordinate A_j alone
target estimand = tau_j(a;q) = D_{h_j(q)} m(a), h_j(q)=e_j-sum_{l != j} q_l e_l
identifying assumptions = consistency, conditional exchangeability, local overlap, differentiability
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Consistency]\label{ass:consistency}
If \(A=a\), then \(Y=Y(a)\) almost surely.
\end{assumption}

\begin{assumption}[Conditional exchangeability]\label{ass:exchangeability}
For every \(a\in S\), \(Y(a)\perp A\mid X\).
\end{assumption}

\begin{assumption}[Local simplex overlap]\label{ass:overlap}
For every \(a\), \(j\), and \(q\) used in a result, there is \(\epsilon>0\) such that \(a+t h_j(q)\in S\) and the conditional density or mass of \(A\) given \(X=x\) is positive in a relative neighborhood of \(a+t h_j(q)\) for almost every \(x\) and all \(|t|<\epsilon\).
\end{assumption}

\begin{assumption}[Tangent differentiability]\label{ass:differentiability}
The identified surface \(m\) is Gateaux differentiable on \(S\) along every tangent vector \(v\) with \(\one^\transpose v=0\), and it admits a tangent-gradient representative \(\gamma(a)\in\R^K/\mathrm{span}\{\one\}\).
\end{assumption}

\begin{assumption}[Reallocation admissibility]\label{ass:admissibility}
For a fixed component \(j\), admissible component increases are exactly the directions \(h_j(q)\) with \(q\in\mathcal{Q}_j(a)\), where \(\mathcal{Q}_j(a)\subseteq\Delta_{-j}\) is nonempty, compact, and defined by Assumption \ref{ass:overlap}.
\end{assumption}

\begin{assumption}[Full displaced support]\label{ass:fullsupport}
For the component \(j\) and point \(a\) used in the ambient-recovery result, every displaced-component rule is locally supported: \(\mathcal{Q}_j(a)=\Delta_{-j}\).
\end{assumption}

\begin{assumption}[Ambient recovery]\label{ass:ambient}
There is an unconstrained response \(M\) on a product neighborhood of \(a\) whose restriction to the simplex is \(m\), with ambient gradient \(g=\nabla M(a)\). The displaced-component spread is \(\rho_j(a)=\max_{\ell,r\neq j}|g_\ell-g_r|\).
\end{assumption}

\section{Main results}
\begin{conjecture}[Reallocation-invariance frontier, NOT YET PROVED]\label{conj:invariance}
Under Assumptions \ref{ass:consistency}--\ref{ass:admissibility}, fix \(a\in S\) and component \(j\). The following are equivalent:
\[
\Pi_{\mathcal{L}_j(a)}\gamma_{-j}(a)=0,
\]
and
\[
\tau_j(a;q)=\tau_j(a;q')\quad\text{for all }q,q'\in\mathcal{Q}_j(a).
\]
Equivalently, all reallocation versions in the sense of \citet{VanderWeeleHernan2013} define the same component-\(j\) estimand exactly when the displaced-gradient vector has no component in the rule-contrast span generated by local support.
When \(\mathcal{Q}_j(a)=\Delta_{-j}\), the frontier is the interval
\[
\mathcal{R}_j(a)=
\left[\gamma_j(a)-\max_{\ell\neq j}\gamma_\ell(a),\,
\gamma_j(a)-\min_{\ell\neq j}\gamma_\ell(a)\right],
\]
and \(\kappa_j(a)=0\) if and only if \(\gamma_\ell(a)=\gamma_r(a)\) for all \(\ell,r\neq j\). When these conditions hold, the common component effect is \(\gamma_j(a)-c_j(a)\), where \(c_j(a)\) is the common non-\(j\) gradient coordinate.
\end{conjecture}

\begin{theorem}[Support-local frontier map]\label{thm:rulespecific}
Under Assumptions \ref{ass:consistency}--\ref{ass:admissibility}, for every \(q\in\mathcal{Q}_j(a)\),
\[
\tau_j(a;q)=\left.\frac{d}{dt}\int \E(Y\mid A=a+t h_j(q),X=x)\,dP_X(x)\right|_{t=0}.
\]
If \(\mathcal{Q}_j(a)\) is compact, the identified frontier is
\[
\mathcal{R}_j(a)=\left\{\gamma_j(a)-\sum_{\ell\neq j}q_\ell\gamma_\ell(a):q\in\mathcal{Q}_j(a)\right\},
\]
so its endpoints solve two linear programs over the support-admissible reallocation polytope. The adjustment formula identifies \(m\); compactness and tangent differentiability then turn the policy-indexed derivatives into the displayed frontier map.
\end{theorem}

\begin{corollary}[Unconstrained continuous-treatment recovery]\label{cor:ambient}
Under Assumptions \ref{ass:fullsupport} and \ref{ass:ambient}, the simplex component-\(j\) effect is invariant if and only if \(\rho_j(a)=0\). If in addition the common displaced-component derivative \(c_j(a)\) tends to zero along a sequence of ambient embeddings, the invariant simplex effect converges to the ordinary continuous-treatment derivative \(g_j(a)\). Without Assumption \ref{ass:fullsupport}, \(\rho_j(a)\) is replaced by the diameter of the projection of \(g_{-j}\) onto \(\mathcal{L}_j(a)\).
\end{corollary}

\section{Sanity-check corollaries}
\begin{corollary}[Two-component collapse]\label{cor:binary}
If \(K=2\), then \(\Delta_{-j}\) is a singleton. Under Assumptions \ref{ass:consistency}--\ref{ass:admissibility}, the rule-specific and invariant component effects coincide because there is only one possible reallocation direction.
\end{corollary}

\paragraph{Exhibit 9.1: computed focal object on a three-component law.}
Take \(A\) randomized uniformly on a small relative-open triangle around \(a_0=(1/3,1/3,1/3)\), no covariates, and \(Y=m(A)+\varepsilon\) with \(\E(\varepsilon\mid A)=0\) and \(m(a)=a_2-a_3\). The tangent-gradient class is represented by \(\gamma=(0,1,-1)\), and \(\mathcal{Q}_1(a_0)=\Delta_{-1}\). The focal object in Conjecture \ref{conj:invariance} is
\[
\mathcal{R}_1(a_0)=\{-q_2+q_3:(q_2,q_3)\in\Delta_{-1}\}=[-1,1],\qquad
\kappa_1(a_0)=2.
\]
The two rule values are \(-1\) and \(1\), so the sign reversal is not a normalization artifact; adding any constant multiple of \(\one\) to \(\gamma\) leaves both derivatives unchanged. The instance is internally consistent because \(A\) has support in the two-dimensional simplex neighborhood, both directions remain inside \(S\) for small \(|t|\), and no denominator or unobserved nuisance object is used.

\paragraph{Reduction.}
Under Assumption \ref{ass:ambient} with \(g_\ell=0\) for every \(\ell\neq j\), Corollary \ref{cor:ambient} collapses to the ordinary partial derivative \(g_j\) because the tangent derivative in direction \(e_j-\sum_{\ell\neq j}q_\ell e_\ell\) equals \(g_j\) for every \(q\).

\section{Proof-sketch route}
For Conjecture \ref{conj:invariance}, the reduction chain is: headline \(\leftarrow\) unfold \(\tau_j(a;q)\) and \(\mathcal{L}_j(a)\) \(\leftarrow\) substitute Assumptions \ref{ass:differentiability} and \ref{ass:admissibility} \(\leftarrow\) Step 1, identify \(m\) and its tangent derivative on every support-admissible segment \(\leftarrow\) Step 2, prove the support-admissible rule set is an observable compact convex subset of the local tangent cone \(\leftarrow\) Step 3, represent any difference of two version effects as \(-\gamma_{-j}(a)^\transpose(q-q')\) \(\leftarrow\) Step 4, apply finite-dimensional orthogonal decomposition to the rule-contrast span \(\mathcal{L}_j(a)\) \(\leftarrow\) Step 5, prove necessity by constructing two admissible rules whose contrast has nonzero inner product with \(\gamma_{-j}\) whenever \(\Pi_{\mathcal{L}_j(a)}\gamma_{-j}\neq0\) \(\leftarrow\) Step 6, specialize to \(\mathcal{Q}_j(a)=\Delta_{-j}\) and use the extreme points of the simplex to obtain the max--min gradient formula \(\leftarrow\) Step 7, verify the formula is invariant to the representative of \(\gamma\) in \(\R^K/\mathrm{span}\{\one\}\) \(\leftarrow\) Step 8, show boundary support restrictions can make \(\rho_j(a)\) irrelevant by shrinking \(\mathcal{L}_j(a)\). Theorem \ref{thm:rulespecific} uses the same first two steps but stops at the support-local linear-program representation. Corollary \ref{cor:ambient} follows by imposing full displaced support, restricting an ambient gradient to the simplex tangent space, and taking the displaced-component spread \(\rho_j\) to zero.

\section{Honest scope flags}
Conjecture \ref{conj:invariance} is the novel kernel and is not yet proved in the CausalSmith catalogue. Theorem \ref{thm:rulespecific} is no longer claimed as a strict advance over continuous-treatment adjustment; its non-routine role is the support-local map from \(m\) to the whole simplex reallocation frontier. The opposite-sign calculation in Exhibit 9.1 is only a sanity witness because Piepel2006 already makes direction dependence explicit in linear mixture models. Corollary \ref{cor:ambient} and Corollary \ref{cor:binary} are routine once the frontier is accepted. The proposal does not claim efficient estimation, partial identification under unsupported directions, or robustness to unmeasured confounding.

\section{Iteration trail}
\begin{itemize}[leftmargin=1.8em]
\item v1 (cold-start) -- initial draft of the exact reallocation-invariance conjecture; prior verdict: none.
\item v2 (revise) -- replaced the routine rule-specific derivative claim with a named support-local reallocation frontier, added the diameter diagnostic \(\kappa_j(a)\), and downgraded Hirano/Hines comparisons to background; prior verdict: REVISE.
\item v3 (revise) -- replaced the tautological diameter-zero iff with the support-span gradient certificate, moved the Piepel-style sign reversal out of the main results, and added full displaced support to the ambient recovery clause; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Aitchison and Bacon-Shone(1984)]{AitchisonBaconShone1984}
Aitchison, J. and J. Bacon-Shone (1984).
Log contrast models for experiments with mixtures.
\emph{Biometrika} 71(2), 323--330.

\bibitem[Antonelli and Zigler(2024)]{AntonelliZigler2024}
Antonelli, J. and C. Zigler (2024).
Causal inference for environmental mixtures.
\emph{American Journal of Epidemiology}.

\bibitem[Arnold et al.(2020)]{ArnoldBerrieTennantGilthorpe2020}
Arnold, K. F., L. Berrie, P. W. G. Tennant, and M. S. Gilthorpe (2020).
A causal inference perspective on the analysis of compositional data.
\emph{International Journal of Epidemiology} 49(4), 1307--1313.

\bibitem[Cattaneo(2010)]{Cattaneo2010}
Cattaneo, M. D. (2010).
Efficient semiparametric estimation of multi-valued treatment effects under ignorability.
\emph{Journal of Econometrics} 155(2), 138--154.

\bibitem[D'Amour et al.(2021)]{DAmourDingFellerLeiSekhon2021}
D'Amour, A., P. Ding, A. Feller, L. Lei, and J. Sekhon (2021).
Overlap in observational studies with high-dimensional covariates.
\emph{Journal of Econometrics} 221(2), 644--654.

\bibitem[Diaz(2023)]{Diaz2023LMTP}
Diaz, I. (2023).
Non-parametric causal effects based on longitudinal modified treatment policies.
\emph{Journal of the American Statistical Association} 118(542), 846--857.

\bibitem[Hines et al.(2026)]{HinesDiazOrdazVansteelandt2026}
Hines, O., K. Diaz-Ordaz, and S. Vansteelandt (2026).
Efficient estimation of average derivative effects.
\emph{Biometrika}.

\bibitem[Hirano and Imbens(2004)]{HiranoImbens2004}
Hirano, K. and G. W. Imbens (2004).
The propensity score with continuous treatments.
In \emph{Applied Bayesian Modeling and Causal Inference from Incomplete-Data Perspectives}, 73--84.

\bibitem[Huang et al.(2026)]{HuangDongLinAntonelli2026}
Huang, J., L. Dong, X. Lin, and J. Antonelli (2026).
Incremental propensity score interventions for multivariate exposure mixtures.
\emph{arXiv:2604.23534}.

\bibitem[Piepel(2006)]{Piepel2006}
Piepel, G. F. (2006).
A note comparing component-slope, Scheffe, and Cox parameterizations of the linear mixture experiment model.
\emph{Journal of Applied Statistics} 33(4), 397--403.

\bibitem[Tomova et al.(2022)]{TomovaGilthorpeTennant2022}
Tomova, G. D., M. S. Gilthorpe, and P. W. G. Tennant (2022).
Theory and performance of substitution models for estimating relative causal effects in nutritional epidemiology.
\emph{American Journal of Clinical Nutrition} 116(5), 1379--1388.

\bibitem[VanderWeele and Hernan(2013)]{VanderWeeleHernan2013}
VanderWeele, T. J. and M. A. Hernan (2013).
Causal inference under multiple versions of treatment.
\emph{Journal of Causal Inference} 1(1), 1--20.
\end{thebibliography}

\end{document}
