% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_iv\_bounded\_defier\_envelope, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_iv\_bounded\_defier\_envelope} / \texttt{v1}%
  \\ \large\textit{Non-rectangular ATE sign frontier for binary IV under joint c-dependence, defier caps, and never-taker caps}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a PartialID proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
\text{bounding functional})
\]
defined as follows.  The qid is
\(\texttt{pid\_iv\_bounded\_defier\_envelope}\) and the specialization is
\(\texttt{v1}\), interpreted in this pivot as the joint-sensitivity sign-frontier
angle.  The observable distribution is
\[
  P=P_{Y,D,Z}\quad\text{on}\quad [\ell,u]\times\{0,1\}\times\{0,1\},
\]
with \(\ell<u\), \(\Pr(Z=z)>0\), and conditional cell probabilities
\(q_{zd}:=\Pr(D=d\mid Z=z)\).  The target is the population average treatment
effect \(\theta:=\E[Y(1)-Y(0)]\) and the sign conclusion
\(\theta\ge 0\).  The identifying restrictions are consistency, exclusion of
the instrument from potential outcomes, bounded outcomes, a binary principal
strata representation \(S=(D(0),D(1))\in\{N,C,A,F\}\), Picchetti-style
\(c\)-dependence for the instrument, a defier-share cap
\(\Pr(S=F)\le \bar\delta\), and a never-taker-share cap
\(\Pr(S=N)\le \bar\nu\).  The bounding functional is the sharp lower endpoint
\[
  L(P;c,\bar\delta,\bar\nu)
  :=\inf\{\E_\mu[Y(1)-Y(0)]:\mu\in
  \Theta_I(P;c,\bar\delta,\bar\nu)\},
\]
and the associated breakdown surface
\(\mathcal B_0(P):=\{(c,\bar\delta,\bar\nu):L(P;c,\bar\delta,\bar\nu)=0\}\).

\begin{abstract}
This proposal asks whether binary-IV ATE sign conclusions have a genuinely
three-dimensional sensitivity frontier when monotonicity, instrument
independence, and the prevalence of never-takers are relaxed simultaneously.
Picchetti's 2026 frontier varies \(c\)-dependence and defier share, while the
bounded-never-taker idea varies a principal-stratum mass that is usually treated
as a nuisance component of the ATE.  The flagship conjecture is that these
relaxations are non-rectangular: on an open set of observable laws, the sharp
ATE lower endpoint under all three restrictions is strictly larger than every
endpoint obtained by intersecting the pairwise sensitivity analyses.  A second
conjecture asks for an observable criterion separating redundant never-taker
caps from caps that create a new mixed exposed face of the identified set.  If
resolved, the result would tell IV sensitivity analysts when a never-taker cap
is a real third sensitivity coordinate rather than cosmetic tightening of
existing defier or independence frontiers.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied IV papers often report that a sign conclusion is robust to some
monotonicity violation or some instrument-independence violation, but the
resulting sensitivity analysis usually has only one or two coordinates.  In
settings such as encouragement designs, access-to-treatment designs, and
eligibility instruments, the share of never-takers is itself scientifically
interpretable: it measures the population that cannot or will not take the
treatment under either instrument state.  The methodological question is
whether bounding this share contributes independent identifying power for ATE
sign conclusions once the analyst has already allowed defiers and
\(c\)-dependence.

\paragraph{The main finding (proposed).}
The headline result is Conjecture~\ref{conj:nonrectangular}: the lower endpoint
\(L(P;c,\bar\delta,\bar\nu)\) is not generally the rectangular combination of
Picchetti's \((c,\bar\delta)\) frontier and pairwise never-taker-cap frontiers.
Instead, there should be an open, nondegenerate region of binary-IV observable
laws on which \(c\)-dependence, the defier cap, and the never-taker cap bind in
the same endpoint-attaining latent law, producing a strictly stronger ATE sign
conclusion than every pairwise sensitivity analysis would report.

\paragraph{What is new.}
The novelty kernel is an equivalence/non-equivalence frontier, not another
finite-LP envelope.  \citet{Picchetti2026} derives identified sets and a LATE
breakdown frontier under joint monotonicity and independence relaxations but
does not introduce an independent never-taker-share coordinate.
\citet{BaiHuangMoonShaikhVytlacil2024} clarify when generalized monotonicity
restrictions have no identifying power for ATE; the present proposal asks when
principal-stratum mass caps escape that no-power logic by restricting the
composition of counterfactual support-fill-in terms.  The flagship epsilon-gap
is a strict non-rectangularity statement: pairwise robust-region diagnostics
can be conservative even when each pairwise bound is sharp.

\paragraph{How it positions in the literature.}
This is a partial-identification and IV-sensitivity proposal.  It sits after
Manski support bounds, Balke--Pearl binary-IV bounds, Imbens--Angrist LATE, and
recent monotonicity-relaxation sensitivity analyses by Noack, Yap, and
Picchetti.  Unlike the rejected static envelope angle for this qid, the target
is not a catalogue of all facets of the two-cap binary-IV polytope; the target
is the geometry of the sign breakdown surface when a third sensitivity
coordinate is added to an active two-coordinate frontier.

\paragraph{Implications for the community.}
The immediate downstream consumer is the breakdown-frontier workflow in
\citet{Picchetti2026}: if Conjecture~\ref{conj:nonrectangular} is true, an
analyst studying the Angrist--Evans family-size IV application with plausible
never-taker information should report a three-coordinate ATE frontier rather
than overlaying Picchetti's \((c,\bar\delta)\) frontier with a separate
never-taker cap.

\paragraph{How research benefits from the conclusion.}
Researchers should check whether their never-taker cap is pairwise redundant or
mixed-face active before declaring an IV sign conclusion sensitive to
monotonicity and independence alone.

\section{Related work}
\citet{Manski1990} gives the bounded-outcome support-bounds benchmark for ATEs
when counterfactual means are unrestricted.  \citet{ImbensAngrist1994} gives
the monotone-IV LATE point-identification corner that sensitivity frontiers
depart from.  \citet{AngristImbensRubin1996} supplies the principal-strata
language used here for compliers, always-takers, never-takers, and defiers.
\citet{BalkePearl1997} derives sharp binary-IV bounds through symbolic linear
programming; this proposal asks about a robustness frontier inside that
finite-type universe rather than the unrestricted bound itself.
\citet{DeChaisemartin2017} shows that IV estimands can remain valid under a
weaker condition than no defiers, making defier-sensitive IV analysis a live
econometric object.  \citet{Noack2021} parameterizes monotonicity violations by
defier share and outcome-distribution differences and derives robust regions
for LATE conclusions; it does not include a never-taker-share coordinate.
\citet{Yap2022} uses a defier-to-complier ratio as a sensitivity parameter for
policy-relevant treatment parameters; it does not ask whether never-taker mass
creates non-rectangular sign frontiers.  \citet{Picchetti2026} combines
defier-share relaxation with \(c\)-dependence and derives identified sets and
breakdown frontiers; it is the closest published comparator, with epsilon-gap
equal to the independent never-taker cap and the proposed strict
non-rectangularity of pairwise analyses.  \citet{BaiHuangMoonShaikhVytlacil2024}
show that generalized monotonicity restrictions can have no identifying power
for ATE; the present proposal isolates when a principal-stratum mass cap has
identifying power precisely because it restricts latent mixture shares, not
outcome ranks.

In the CausalSmith catalogue, the accepted study artifacts
\texttt{imbens\_angrist\_late\_v1} and
\texttt{manski\_nonparametric\_bounds\_v1} provide the LATE and support-bound
limit anchors.  The failed
\texttt{pid\_late\_bounded\_defiers\_one\_sided\_compliance} proposal is the
closest in-repo warning: its review rejected a formula that omitted the
\((Z=1,D=0)\) observed cell and requested a full four-cell principal-strata
mixture system.  The candidate
\texttt{pid\_dynamic\_iv\_compliance\_v2} records a pure-never-taker
mixture-subtraction phenomenon, but its target is dynamic compliance and it
does not characterize a static IV sign frontier under \(c\)-dependence.
According to \texttt{doc/API.md}, the PartialID catalogue is the intended home
for Manski-family bounds, Balke--Pearl bounds, IV sensitivity, and
shape-restricted partial-ID entries; no active catalogue entry already states
the three-coordinate non-rectangularity kernel proposed here.

\section{Formal setup}
Let \(Z,D\in\{0,1\}\), let \(Y\in[\ell,u]\), and let
\(P=P_{Y,D,Z}\) be the observable law.  A latent law \(\mu\) is a probability
measure over
\[
  (Y(0),Y(1),D(0),D(1),Z)
  \in [\ell,u]^2\times\{0,1\}^2\times\{0,1\}.
\]
Write \(S=(D(0),D(1))\), with \(N=(0,0)\), \(C=(0,1)\),
\(A=(1,1)\), and \(F=(1,0)\).  The latent law is observable-compatible when
\(D=D(Z)\), \(Y=Y(D)\), the marginal law of \((Y,D,Z)\) equals \(P\), and the
instrument has no direct effect on \((Y(0),Y(1))\) beyond the allowed
\(c\)-dependence inequality.

For \(c\in[0,1]\), \(\bar\delta\in[0,1]\), and
\(\bar\nu\in[0,1]\), define \(\Theta_I(P;c,\bar\delta,\bar\nu)\) as the set of
observable-compatible latent laws satisfying the assumptions in
Section~\ref{sec:assumptions}.  The ATE identified set is
\[
  \mathcal I_{\mathrm{ATE}}(P;c,\bar\delta,\bar\nu)
  :=\{\E_\mu[Y(1)-Y(0)]:\mu\in
  \Theta_I(P;c,\bar\delta,\bar\nu)\}.
\]
Its lower endpoint is \(L(P;c,\bar\delta,\bar\nu)\).  The pairwise-rectangular
lower diagnostic is
\[
L^\square(P;c,\bar\delta,\bar\nu)
:=\max\{L(P;c,\bar\delta,1),\,L(P;c,1,\bar\nu),\,
        L(P;0,\bar\delta,\bar\nu)\}.
\]
This is the strongest lower sign diagnostic obtained by keeping at most two of
the three relaxations active at a time.

\begin{quote}
\texttt{qid = pid\_iv\_bounded\_defier\_envelope;}\\
\texttt{specialization = v1;}\\
\texttt{observable distribution P = P\_\{Y,D,Z\} on [ell,u] x \{0,1\} x \{0,1\};}\\
\texttt{parameter theta = E[Y(1)-Y(0)] and sign conclusion theta >= 0;}\\
\texttt{identifying restrictions = consistency, exclusion, bounded outcomes, c-dependence, Pr(S=F)<=bar_delta, Pr(S=N)<=bar_nu;}\\
\texttt{bounding functional = L(P;c,bar\_delta,bar\_nu) and breakdown surface B0(P).}
\end{quote}

\section{Assumptions}\label{sec:assumptions}
\begin{assumption}[Binary IV observables and bounded support]\label{ass:observables}
The observable law \(P\) is defined on
\([\ell,u]\times\{0,1\}\times\{0,1\}\), where \(\ell<u\), and
\(\Pr_P(Z=z)>0\) for \(z=0,1\).
\end{assumption}

\begin{assumption}[Consistency and exclusion]\label{ass:consistency}
There exist potential outcomes \(Y(0),Y(1)\in[\ell,u]\) and potential
treatments \(D(0),D(1)\in\{0,1\}\) such that \(D=D(Z)\) and
\(Y=Y(D)\).  The instrument has no direct potential-outcome argument beyond
its effect through treatment and the allowed dependence in
Assumption~\ref{ass:cdep}.
\end{assumption}

\begin{assumption}[\(c\)-dependence]\label{ass:cdep}
Let \(\pi_Z:=\Pr_\mu(Z=1)\).  The latent law satisfies
\[
  \left|\Pr_\mu(Z=1\mid Y(0),Y(1),D(0),D(1))-\pi_Z\right|\le c
\]
almost surely.  The case \(c=0\) is latent instrument independence.
\end{assumption}

\begin{assumption}[Defier and never-taker caps]\label{ass:caps}
The principal-stratum masses satisfy
\[
  \Pr_\mu(S=F)\le \bar\delta,\qquad
  \Pr_\mu(S=N)\le \bar\nu,
\]
where \(F=(1,0)\) and \(N=(0,0)\).
\end{assumption}

\begin{assumption}[Nondegenerate frontier region]\label{ass:nondegenerate}
For the flagship non-rectangularity claim, the observable law and sensitivity
parameters satisfy
\(\Theta_I(P;c,\bar\delta,\bar\nu)\ne\varnothing\), all four conditional
\((Z,D)\) cells have positive probability, \(0<c<1\),
\(0<\bar\delta<1\), \(0<\bar\nu<1\), and the endpoint
\(L(P;c,\bar\delta,\bar\nu)\) is finite.
\end{assumption}

\begin{assumption}[Pairwise frontier compatibility]\label{ass:pairwise}
The three pairwise feasible sets used in \(L^\square\),
\(\Theta_I(P;c,\bar\delta,1)\), \(\Theta_I(P;c,1,\bar\nu)\), and
\(\Theta_I(P;0,\bar\delta,\bar\nu)\), are nonempty.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite sharp sign-endpoint polytope]\label{thm:polytope}
Under Assumptions~\ref{ass:observables}--\ref{ass:caps},
\(\Theta_I(P;c,\bar\delta,\bar\nu)\) is a compact convex set after replacing
the bounded outcomes by finite boundary response types at \(\ell\) and \(u\).
Consequently \(\mathcal I_{\mathrm{ATE}}(P;c,\bar\delta,\bar\nu)\) is a
closed interval and \(L(P;c,\bar\delta,\bar\nu)\) is attained by a boundary
latent law.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is a setup theorem rather than the flagship novelty: it specializes
the Balke--Pearl finite response-type logic to the joint
\((c,\bar\delta,\bar\nu)\) sensitivity model.  The gap to
\citet{BalkePearl1997} and \citet{Picchetti2026} is the simultaneous inclusion
of \(c\)-dependence and an independent never-taker cap.  (b) The concrete
consumer is Conjecture~\ref{conj:nonrectangular}: compactness and boundary
attainment are needed before the three-way mixed face can be stated and tested
without numerical-solver ambiguity.

\begin{conjecture}[Conjecture 1: non-rectangular ATE sign frontier (NOT YET PROVED)]\label{conj:nonrectangular}
Under Assumptions~\ref{ass:observables}--\ref{ass:pairwise}, there exists an
open set \(\mathcal U\) of observable laws \(P\) and sensitivity triples
\((c,\bar\delta,\bar\nu)\) such that
\[
  L(P;c,\bar\delta,\bar\nu) >
  L^\square(P;c,\bar\delta,\bar\nu).
\]
Equivalently, for \(P\in\mathcal U\), the robust ATE sign conclusion
\(\theta\ge 0\) can hold under the full three-coordinate model even though no
pairwise frontier among \((c,\bar\delta)\), \((c,\bar\nu)\), and
\((\bar\delta,\bar\nu)\) certifies it.  On \(\mathcal U\), every
relative-interior point of the optimal face for
\(L(P;c,\bar\delta,\bar\nu)\) has the \(c\)-dependence inequality, the defier
cap, and the never-taker cap all binding.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest published result is \citet{Picchetti2026}, which builds a
\((c,\bar\delta)\) breakdown frontier and derives ATE/LATE identified sets as
functions of those two sensitivity parameters; it has no independent
\(\bar\nu\) coordinate and therefore cannot distinguish a true mixed
never-taker face from pairwise tightening.  \citet{Noack2021} and
\citet{Yap2022} likewise vary defier-related parameters without the
never-taker-share coordinate.  (b) The concrete consumer is Picchetti's
breakdown-frontier reporting workflow: the conjecture says that in applications
such as Angrist--Evans family size, a never-taker cap can certify ATE sign
robustness that is invisible to the published two-coordinate frontier.

\begin{conjecture}[Conjecture 2: observable redundancy certificate (NOT YET PROVED)]\label{conj:certificate}
Under Assumptions~\ref{ass:observables}--\ref{ass:pairwise}, define the
never-taker slack
\[
  \rho_N(P;c,\bar\delta)
  :=\sup\{\Pr_\mu(S=N):\mu\in
       \arg\min_{\eta\in\Theta_I(P;c,\bar\delta,1)}
       \E_\eta[Y(1)-Y(0)]\}.
\]
Then the never-taker cap is lower-endpoint redundant,
\[
  L(P;c,\bar\delta,\bar\nu)=L(P;c,\bar\delta,1),
\]
if and only if \(\bar\nu\ge \rho_N(P;c,\bar\delta)\).  Moreover,
\(\rho_N(P;c,\bar\delta)\) admits an observable closed form using only the four
conditional cells of \(P_{Y,D\mid Z}\), \((\ell,u)\), \(c\), and
\(\bar\delta\), with no optimization over latent response types.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The first equivalence is the conceptual frontier missing from
\citet{BaiHuangMoonShaikhVytlacil2024}: their no-power result concerns
treatment-response monotonicity restrictions that do not restrict potential
outcomes, while this conjecture asks when a principal-stratum mass cap has
power by excluding endpoint-minimizing latent mixtures.  The observable
closed-form part is also absent from \citet{BalkePearl1997}, which certifies
sharpness by symbolic LP rather than a never-taker redundancy threshold.  (b)
The concrete consumer is the CausalSmith open question
\texttt{oq\_defiers}: it would let the pipeline decide before formalizing a
full envelope whether the never-taker cap is mathematically active for the
defier-relaxation problem at hand.

\section{Sanity-check corollaries}
\begin{corollary}[No never-taker cap reduces to Picchetti's frontier]\label{cor:picchetti}
Under Assumptions~\ref{ass:observables}--\ref{ass:caps}, setting
\(\bar\nu=1\) removes the never-taker cap, so
\(\Theta_I(P;c,\bar\delta,1)\) is the Picchetti-style
\((c,\bar\delta)\) latent model for ATE and \(L(P;c,\bar\delta,1)\) is the
corresponding two-coordinate lower endpoint.
\end{corollary}

Under \(\bar\nu=1\), the statement collapses to \citet{Picchetti2026} because
Assumption~\ref{ass:caps} leaves only the defier cap and
Assumption~\ref{ass:cdep} leaves only \(c\)-dependence as nonclassical
sensitivity coordinates.

\begin{corollary}[Classical independence corner]\label{cor:independence}
Under Assumptions~\ref{ass:observables}--\ref{ass:caps}, setting \(c=0\)
turns Assumption~\ref{ass:cdep} into latent instrument independence.  If also
\(\bar\delta=0\), the switcher-local component reduces to the
Imbens--Angrist monotone LATE corner whenever the first stage is positive,
while the population ATE can remain partially identified through always-taker
and never-taker counterfactual means.
\end{corollary}

Under \(c=0\) and \(\bar\delta=0\), the observed Wald numerator cancels the
always-taker and never-taker observed components and isolates the complier
contrast, exactly as in \citet{ImbensAngrist1994}; the population ATE remains
an interval unless the noncomplier counterfactual components are separately
restricted.

\section{Proof-sketch route}
The proof route is finite convex analysis.  First discretize endpoint-relevant
outcome completions to boundary values \(\ell\) and \(u\), then write the
observable equations, \(c\)-dependence inequalities, and stratum-share caps as
a finite linear system over principal-stratum/outcome-response types.  Theorem
1 follows from compactness and linear projection.  For
Conjecture~\ref{conj:nonrectangular}, one should construct a nondegenerate
binary-outcome observable law for which the lower-endpoint LP has a unique
optimal basis with the \(c\)-dependence, defier-cap, and never-taker-cap
constraints all binding, and then verify strict inequality against the three
pairwise LPs by direct basis substitution.  For
Conjecture~\ref{conj:certificate}, the expected route is to solve the
Picchetti-style lower-endpoint basis for the maximum never-taker mass among
minimizers, then eliminate latent variables using the four observed
\((Z,D)\) cells and the support endpoints; zero-cell and zero-first-stage
boundaries should be handled separately from the open-cell case.

\section{Honest scope flags}
Theorem~\ref{thm:polytope} is labelled theorem because it is routine finite-LP
partial identification once the setup is fixed.  Conjectures
\ref{conj:nonrectangular} and \ref{conj:certificate} are the novel kernel and
are not yet proved.  The proposal deliberately withdraws the rejected
facet-catalogue and active-knot framing from the previous angle: no claim is
made here that all two-cap ATE endpoints have a flagship-level closed-form
facet taxonomy.  The main uncertainty is whether the observable closed form
for \(\rho_N(P;c,\bar\delta)\) can be made simple enough to count as more than
an LP-value restatement; if not, Conjecture~\ref{conj:certificate} should be
downgraded to an algorithmic certificate while Conjecture~\ref{conj:nonrectangular}
remains the primary flagship target.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 2, replacing the rejected static
facet-envelope kernel with a three-coordinate non-rectangular sign-frontier
proposal anchored to \citet{Picchetti2026}; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Angrist, Imbens, and Rubin(1996)]{AngristImbensRubin1996}
Angrist, J. D., G. W. Imbens, and D. B. Rubin (1996).
Identification of causal effects using instrumental variables.
\emph{Journal of the American Statistical Association} 91(434), 444--455.

\bibitem[Bai et~al.(2024)]{BaiHuangMoonShaikhVytlacil2024}
Bai, Y., S. Huang, S. Moon, A. M. Shaikh, and E. J. Vytlacil (2024).
On the identifying power of generalized monotonicity for average treatment
effects.
NBER Working Paper 32983.

\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Balke, A. and J. Pearl (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association} 92(439), 1171--1176.

\bibitem[de Chaisemartin(2017)]{DeChaisemartin2017}
de Chaisemartin, C. (2017).
Tolerating defiance? Local average treatment effects without monotonicity.
\emph{Quantitative Economics} 8(2), 367--396.

\bibitem[Imbens and Angrist(1994)]{ImbensAngrist1994}
Imbens, G. W. and J. D. Angrist (1994).
Identification and estimation of local average treatment effects.
\emph{Econometrica} 62(2), 467--475.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Noack(2021)]{Noack2021}
Noack, C. (2021).
Sensitivity of LATE estimates to violations of the monotonicity assumption.
arXiv:2106.06421.

\bibitem[Picchetti(2026)]{Picchetti2026}
Picchetti, P. (2026).
Sensitivity analysis for instrumental variables under joint relaxations of
monotonicity and independence.
arXiv:2603.25529.

\bibitem[Yap(2022)]{Yap2022}
Yap, T. Y. (2022).
Bounds on policy-relevant treatment parameters without monotonicity.
Princeton Industrial Relations Section Working Paper.
\end{thebibliography}

\end{document}
