% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_iv\_bounded\_defier\_envelope, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_iv\_bounded\_defier\_envelope} / \texttt{v1}%
  \\ \large\textit{Four-cell sharp ATE envelope for binary IV with simultaneous defier and never-taker caps}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_iv\_bounded\_defier\_envelope},\texttt{v1},
  P_{Y,D,Z},\ \theta_{\mathrm{ATE}},\
  \calR_{\mathrm{IV+BDN}},\
  [\underline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu),
    \overline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)]) .
\end{gathered}
\]
Here \(Z,D\in\{0,1\}\), \(Y\in[0,1]\), and \(P_{Y,D,Z}\) is observed with
\(0<\Pr(Z=1)<1\).  The target is the population average treatment effect
\[
\theta_{\mathrm{ATE}}=\E[Y(1)-Y(0)].
\]
The restrictions \(\calR_{\mathrm{IV+BDN}}\) are consistency, exclusion of \(Z\)
except through \(D\), instrument independence
\(Z\perp (Y(0),Y(1),D(0),D(1))\), bounded potential outcomes, observational
compatibility with the binary-IV principal-strata mixture equations, a known
one-sided defier cap
\[
\Pr(D(1)=0,D(0)=1)\le \bar\delta,
\]
and a known never-taker cap
\[
\Pr(D(1)=0,D(0)=0)\le \bar\nu.
\]
The convention is restricted to cap-compatible observed laws:
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\ne\varnothing\).
The bounding functional is the projection of the resulting finite
principal-strata polytope onto \(\theta_{\mathrm{ATE}}\), with endpoints proposed
to equal the explicit max/min affine facet envelope in
Conjecture~\ref{conj:facet-envelope}.

\begin{abstract}
This proposal asks for sharp ATE bounds in the binary-instrument model when
monotonicity is relaxed by a defier-share cap and the never-taker share is also
bounded above.  The kernel claim is not a new generic linear program: it is the
conjecture that the full four-observed-cell principal-strata projection has a
closed polytopal endpoint formula whose facets split into Balke--Pearl,
defier-cap, never-taker-cap, joint-cap, and support-fill-in families.  The
second conjecture asks for a boundary-distribution certificate attaining every
facet, including cap-binding and zero-cell faces that defeated a prior
CausalSmith proposal.  The proposal also records exact face reductions: the
zero-defier face must recover the Imbens--Angrist complier LATE coordinate,
while the pure never-taker face must collapse to Manski's outcome-support ATE
interval.  If resolved, the result would turn monotonicity-violation sensitivity
from a numerical IV-bounds exercise into a facet-auditable theorem.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Binary instruments are used precisely where treatment receipt is imperfect.
The Imbens--Angrist LATE theorem gives a clean point estimand under no defiers,
whereas Balke--Pearl bounds give sharp nonparametric intervals when compliance
behavior is unrestricted.  Empirical researchers often want an intermediate
sensitivity analysis: allow a small defier population, also limit the population
share that can never take treatment, and report the sharp ATE region implied by
those two primitive caps.

\paragraph{The main finding (proposed).}
The flagship result is Conjecture~\ref{conj:facet-envelope}: after encoding the
four principal strata \(C,N,A,F\), their observed potential-outcome mixtures,
and the caps \(\pi_F\le\bar\delta\), \(\pi_N\le\bar\nu\), the sharp ATE
identified set is a single interval whose endpoints are max/mins over an
explicit finite catalogue of affine functions of the four observed cells and
the two caps.  Conjecture~\ref{conj:boundary-certificates} strengthens this by
asking for endpoint-attaining latent laws for each exposed facet.  Theorem~\ref{thm:polytope-wellposed}
and Theorem~\ref{thm:face-limits} are supporting
statements: the first fixes the exact polytope, and the second states the
required LATE and Manski face limits.

\paragraph{What is new.}
The closest published result is \citet{BalkePearl1997}, which gives tight
binary-IV ATE bounds by symbolic linear programming but does not isolate a
two-cap sensitivity envelope with independent restrictions on defiers and
never-takers.  The closest defier-geometry precedent is
\citet{RichardsonRobins2010}: if their fixed-defier bounds are available for
each \(t=\pi_F\), then the two-cap endpoint value should be compared with
optimizing those fixed-\(t\) bounds over
\[
\left[\max\{0,q_{10}-\bar\nu,q_{10}-q_{00}\},\
\min\{q_{01},q_{10},\bar\delta\}\right].
\]
The flagship epsilon-gap is not generic finite-LP existence.  It is the
eliminated observable frontier: explicit affine inequalities saying when
\(\bar\nu\) is redundant, when it strictly shrinks an endpoint on an open set,
and which active facet generates that shrinkage after all four observed
\(Z,D\) cells are imposed.

\paragraph{How it positions in the literature.}
The proposal lives in the partial-identification cluster: Manski support
bounds, Balke--Pearl IV bounds, LATE monotonicity, and recent monotonicity
sensitivity analysis.  It is not a graphical-identification or do-calculus
proposal.  It consumes the principal-strata IV setup as fixed and asks for a
sharp projected identified set under economically interpretable caps.

\paragraph{Implications for the community.}
The concrete downstream consumer is \citet{LevisBonviniZengKeeleKennedy2025}:
their covariate-assisted IV-bounds inference problem is nonsmooth because the
bound is a max/min functional, and an explicit two-cap facet catalogue would
identify which inequalities drive local nonsmoothness under monotonicity
relaxation.

\paragraph{How research benefits from the conclusion.}
A reader who takes only the conclusion away should report both the defier cap
and the never-taker cap, then diagnose whether the active endpoint lies on a
Balke--Pearl, defier-cap, never-taker-cap, or joint-cap facet instead of
treating IV sensitivity as an opaque solver output.

\section{Related work}
\citet{Manski1990} supplies the bounded-outcome support-fill-in benchmark that
the pure never-taker face of this proposal must recover.  \citet{ImbensAngrist1994}
identifies the local average treatment effect for compliers under instrument
independence and monotonicity; this proposal treats the zero-defier face as an
exact coordinate reduction rather than as an informal limiting check.
\citet{AngristImbensRubin1996} gives the principal-strata language
\((C,N,A,F)\) used to define the latent polytope.  \citet{BalkePearl1997}
derives sharp binary-IV ATE bounds through symbolic linear programming over
latent response types; the present proposal asks for the strictly more
structured two-cap envelope and its facet certificates.  Although the original
Balke--Pearl formulas are often presented for binary \(Y\), the convention here
uses bounded outcome-mass variables \(y_{ds}\in[0,\pi_s]\), so the no-cap
sanity reduction is to the bounded-outcome IV support-envelope analogue rather
than to a binary-response-type table.  \citet{RichardsonRobins2010}
develops binary-IV geometry under restrictions including defier proportions,
making it the closest geometry precedent for the defier cap but not for the
simultaneous never-taker cap.  \citet{SwansonHernanMillerRobinsRichardson2018}
reviews binary-IV partial-identification methods and motivates defier-proportion
sensitivity, but it leaves closed-form cap-specific ATE facets as an open
specialization.  \citet{ManskiPepper2000} shows how monotone restrictions can
tighten nonparametric bounds; the present proposal instead tightens by
principal-stratum mass restrictions.  \citet{MourifieWan2017} tests LATE
independence and monotonicity through conditional moment inequalities, while
this proposal quantifies the ATE set after monotonicity is allowed to fail by a
bounded amount.  \citet{Noack2021} and \citet{Yap2022} parameterize
monotonicity violations through defier shares or defier-to-complier ratios; the
epsilon-gap is the independent never-taker-share cap and the resulting joint
facet changes.  \citet{Picchetti2026} combines defier-share relaxation with IV
independence relaxation for breakdown frontiers; the present proposal keeps IV
independence but adds never-taker cap geometry.
\citet{DeChaisemartin2017} shows that a LATE-type interpretation can survive
defiers under compliers-defiers and stochastic-monotonicity conditions; this is
an estimand-interpretation result, whereas the present proposal gives a sharp
ATE identified set under primitive mass caps.  \citet{DahlHuberMellace2023}
identify LATEs with or without defiers under local monotonicity and local
compliers-defiers conditions; the proposed two-cap envelope is different
because it does not require the local cancellation structure and instead asks
when observed four-cell mixtures make a never-taker cap bind.
\citet{SachsJonzonSjolanderGabriel2023} gives a general symbolic-bound method
for causal effects that are linear in discrete latent distributions, and
\citet{GabrielSachsSjolander2023} warns in the decomposition-effects setting
that separately sharp componentwise bounds need not combine sharply.  Together
they make the non-subsumption issue explicit: the two-cap IV problem must show
joint sharpness and active-facet control, not only separate fixed-defier or
fixed-never-taker bounds.  \citet{DuarteFinkelsteinKnoxMummoloShpitser2024}
automates sharp or epsilon-sharp bounds for discrete causal problems through
constrained optimization.
These papers are closer generic precedents than a textbook LP
argument: the present proposal must therefore deliver a hand-eliminated
IV-specific facet catalogue and strict-shrinkage frontier, not merely a solver
or symbolic-bound existence claim.  \citet{LevisBonviniZengKeeleKennedy2025}
shows that covariate-assisted Balke--Pearl bounds produce nonsmooth max/min
functionals, making explicit facet control valuable for inference.  \citet{BaiHuangMoonShaikhVytlacil2024}
clarifies which generalized monotonicity restrictions identify ATE features,
including no-power regions for treatment-response-only restrictions; this
proposal complements that frontier by using compliance-stratum mass caps whose
binding status is constrained by the four observed \(Z,D\) cells.

In-catalogue prior art is thin but informative.  \texttt{doc/API.md} reports
that CausalSmith's ExactID and PartialID catalogues are seed-time empty except
for the Manski nonparametric-bounds study entries under
\texttt{CausalSmith/PartialID/ManskiNonparametricBounds\_Study/}.  The accepted
\texttt{manski\_nonparametric\_bounds} study supplies the support-bound face
that Theorem~\ref{thm:face-limits} must match.  The accepted
\texttt{imbens\_angrist\_late} study supplies the monotone LATE coordinate that
the zero-defier face must recover.  The failed
\texttt{pid\_late\_bounded\_defiers}/\texttt{one\_sided\_compliance} proposal is
the nearest in-repo attempt; its reviewer explicitly rejected a formula that
omitted the \(Z=1,D=0\) observed cell and recommended redrafting around the full
four-cell mixture system.  The candidate
\texttt{pid\_dynamic\_iv\_compliance\_v2} proposal supplies reusable language
about never-taker mixture subtraction, but its target is dynamic and it does
not solve the static two-cap binary-IV ATE envelope.

\section{Formal setup}
Let
\[
C=\{D(0)=0,D(1)=1\},\quad
N=\{D(0)=0,D(1)=0\},\quad
A=\{D(0)=1,D(1)=1\},\quad
F=\{D(0)=1,D(1)=0\}
\]
denote compliers, never-takers, always-takers, and defiers.  Write
\(\pi_s=\Pr(s)\) for \(s\in\{C,N,A,F\}\), and
\(y_{ds}=\E[Y(d)\one\{s\}]\) for \(d\in\{0,1\}\).  Thus
\(0\le y_{ds}\le \pi_s\).  Let
\[
q_{zd}=\Pr(D=d\mid Z=z),\qquad
r_{zd}=q_{zd}\E[Y\mid Z=z,D=d],
\]
with \(r_{zd}=0\) when \(q_{zd}=0\).

The observed first-stage and outcome-mixture equations are
\[
\begin{aligned}
q_{11}&=\pi_C+\pi_A,& q_{10}&=\pi_N+\pi_F,\\
q_{01}&=\pi_A+\pi_F,& q_{00}&=\pi_N+\pi_C,\\
r_{11}&=y_{1C}+y_{1A},& r_{10}&=y_{0N}+y_{0F},\\
r_{01}&=y_{1A}+y_{1F},& r_{00}&=y_{0N}+y_{0C}.
\end{aligned}
\]
The parameter is
\[
\theta_{\mathrm{ATE}}
=\sum_{s\in\{C,N,A,F\}}(y_{1s}-y_{0s}).
\]
The first-stage equations leave one scalar compliance-share degree of freedom:
with \(t=\pi_F\),
\[
\pi_A=q_{01}-t,\qquad
\pi_N=q_{10}-t,\qquad
\pi_C=q_{00}-q_{10}+t.
\]
Define the cap-compatible first-stage interval
\[
I_{\pi}(P,\bar\delta,\bar\nu)=
\left[
\max\{0,q_{10}-\bar\nu,q_{10}-q_{00}\},\
\min\{q_{01},q_{10},\bar\delta\}
\right].
\]
Nonemptiness of this interval is the first-stage part of capped feasibility;
the outcome equations and support inequalities then determine whether a
candidate \(t\) admits hidden outcome means.  Define the outcome-feasible
fixed-defier set
\[
I_{\pi}^{Y}(P,\bar\delta,\bar\nu)=
\left\{t\in I_{\pi}(P,\bar\delta,\bar\nu):
\begin{array}{l}
\text{there exist }(y_{ds})_{d,s}\text{ satisfying the four observed outcome}\\
\text{equations and }0\le y_{ds}\le\pi_s(t)\text{ for }
\pi_A(t)=q_{01}-t,\\
\pi_N(t)=q_{10}-t,\ \pi_C(t)=q_{00}-q_{10}+t,\ \pi_F(t)=t
\end{array}\right\}.
\]
For \(t\in I_{\pi}^{Y}(P,\bar\delta,\bar\nu)\), write \(B_L(t)\) and
\(B_U(t)\) for the sharp lower and upper ATE endpoints of the same four-cell
latent-outcome system after imposing \(\pi_F=t\) and \(\pi_N=q_{10}-t\), but
before optimizing over \(t\).  These are the fixed-defier endpoints used only
for comparison with Richardson--Robins-style geometry.
For observed \(P\) and caps \((\bar\delta,\bar\nu)\), define
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) to be the set of all
\((\pi_s,y_{ds})\) satisfying the display above, the simplex constraints
\(\pi_s\ge0\), \(\sum_s\pi_s=1\), the support constraints
\(0\le y_{ds}\le\pi_s\), and the cap constraints
\(\pi_F\le\bar\delta\), \(\pi_N\le\bar\nu\).  The identified set is
\[
\Theta_I(P,\bar\delta,\bar\nu)
=\{\theta_{\mathrm{ATE}}(\pi,y):(\pi,y)\in
\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\}.
\]
The proposed lower and upper affine endpoint catalogues are denoted
\(\mathfrak{L}_{\mathrm{BDN}}\) and \(\mathfrak{U}_{\mathrm{BDN}}\).  For an
exposed affine form \(f\) in either catalogue, \(\Gamma_f\) denotes the
candidate boundary-distribution map from observables and caps to a latent
vector \((\pi_s,y_{ds})_{s,d}\) attaining facet \(f\).

\begin{verbatim}
qid = pid_iv_bounded_defier_envelope
specialization = v1
observable distribution P = law of (Y,D,Z), with Z,D binary and Y in [0,1]
parameter theta = theta_ATE = E[Y(1)-Y(0)]
identifying restrictions = consistency, exclusion, instrument independence,
  bounded outcomes, four-cell principal-strata mixture equations,
  pi_F <= delta_bar, pi_N <= nu_bar, and cap-compatible nonemptiness
bounding functional = projection of P_BDN(P,delta_bar,nu_bar) onto theta_ATE;
  proposed closed form is max/min over the finite two-cap facet catalogue
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Binary IV support and bounded outcomes]\label{ass:support}
\(Z,D\in\{0,1\}\), \(0<\Pr(Z=1)<1\), and \(0\le Y(0),Y(1)\le1\) almost surely.
\end{assumption}

\begin{assumption}[IV independence, exclusion, and consistency]\label{ass:iv}
\(Z\perp (Y(0),Y(1),D(0),D(1))\).  The instrument affects \(Y\) only through
\(D\), and the realized variables satisfy \(D=D(Z)\) and \(Y=Y(D)\).
\end{assumption}

\begin{assumption}[Observed four-cell compatibility]\label{ass:compatibility}
The observed law \(P\) admits at least one latent vector
\((\pi_s,y_{ds})\) satisfying the mixture equations in Section 6, the support
constraints \(0\le y_{ds}\le\pi_s\), and the simplex constraints.  Cell
probabilities \(q_{zd}\) are allowed to be zero, with \(r_{zd}=0\) by convention.
\end{assumption}

\begin{assumption}[Defier and never-taker caps]\label{ass:caps}
The known sensitivity parameters satisfy \(0\le\bar\delta,\bar\nu\le1\), and
the maintained model imposes \(\pi_F\le\bar\delta\) and
\(\pi_N\le\bar\nu\).
\end{assumption}

\begin{assumption}[Cap-compatible feasibility]\label{ass:capped-feasible}
The capped polytope is nonempty:
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\ne\varnothing\).
Equivalently, the outcome-feasible fixed-defier set
\(I_{\pi}^{Y}(P,\bar\delta,\bar\nu)\) is nonempty.
\end{assumption}

\begin{assumption}[Face-limit regimes]\label{ass:faces}
For the zero-defier face, impose \(\bar\delta=0\) and observational
compatibility with \(\pi_F=0\).  For the pure never-taker face, impose
\(\bar\nu=1\) and \(\pi_N=1\), equivalently \(q_{10}=q_{00}=1\) and
\(q_{11}=q_{01}=0\), with the observed untreated mean
\(m_0=\E[Y\mid D=0]\) defined.  On this face the never-taker cap is saturated,
not imposed as a stricter bound.
\end{assumption}

\section{Main results}
\begin{theorem}[Finite four-cell cap polytope]\label{thm:polytope-wellposed}
Under Assumptions~\ref{ass:support}--\ref{ass:capped-feasible},
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) is a closed bounded
polytope, and \(\Theta_I(P,\bar\delta,\bar\nu)\) is the closed interval
\[
\left[
\min_{(\pi,y)\in\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)}
\theta_{\mathrm{ATE}}(\pi,y),\quad
\max_{(\pi,y)\in\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)}
\theta_{\mathrm{ATE}}(\pi,y)
\right].
\]
Moreover each endpoint is attained at a vertex of
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is the setup theorem, not the flagship novelty: \citet{BalkePearl1997}
already teaches that binary-IV bounds are linear-program projections.  The
epsilon-gap is the exact four-cell cap polytope with both
\(\pi_F\le\bar\delta\) and \(\pi_N\le\bar\nu\), which corrects the failed
CausalSmith one-sided-compliance proposal by including both \(Z=1,D=0\) and
\(Z=0,D=0\) mixtures.  (b) The concrete consumer is
\citet{MourifieWan2017}: their moment-inequality view of LATE violations gains
a finite feasibility object whose active inequalities can be tested or reported.

\begin{conjecture}[Closed-form simultaneous-cap facet envelope]\label{conj:facet-envelope}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:support}--\ref{ass:capped-feasible}, there
exist two explicit finite catalogues
\(\mathfrak{L}_{\mathrm{BDN}}\) and \(\mathfrak{U}_{\mathrm{BDN}}\) of affine
forms in
\[
(q_{11},q_{10},q_{01},q_{00},r_{11},r_{10},r_{01},r_{00},
  \bar\delta,\bar\nu)
\]
such that
\[
\underline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)
=\max_{\ell\in\mathfrak{L}_{\mathrm{BDN}}}\ell(P,\bar\delta,\bar\nu),
\qquad
\overline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)
=\min_{u\in\mathfrak{U}_{\mathrm{BDN}}}u(P,\bar\delta,\bar\nu).
\]
The catalogues can be partitioned into five nonredundant families:
Balke--Pearl base facets, defier-cap facets, never-taker-cap facets,
joint-cap facets where \(\pi_F=\bar\delta\) and \(\pi_N=\bar\nu\) both bind,
and support-fill-in facets where a hidden \(y_{ds}\) equals \(0\) or \(\pi_s\).
No additional facet family appears after projecting out the latent variables.

The same catalogue also yields a strict-shrinkage frontier relative to the
unrestricted Balke--Pearl endpoints: for each endpoint and each fixed
\(\bar\delta\), there is a finite list of observable affine inequalities in
\((q,r,\bar\nu)\) that is necessary and sufficient for lowering \(\bar\nu\) to
strictly move the endpoint inward.  Outside those regions the never-taker cap
is redundant after the four observed cells and the defier cap are imposed.
Equivalently, if \(B_L(t)\) and \(B_U(t)\) denote the sharp fixed-defier lower
and upper endpoints in the sense of Richardson--Robins, the conjectured
endpoints agree with
\[
\min_{t\in I_{\pi}^{Y}(P,\bar\delta,\bar\nu)}B_L(t),
\qquad
\max_{t\in I_{\pi}^{Y}(P,\bar\delta,\bar\nu)}B_U(t)
\]
whenever those fixed-\(t\) functions are evaluated with the same four observed
outcome equations.  The novel content is the closed-form elimination of \(t\)
and the necessary-and-sufficient observable classification of the open regions
where replacing \(I_{\pi}^{Y}(P,\bar\delta,1)\) by
\(I_{\pi}^{Y}(P,\bar\delta,\bar\nu)\) changes the endpoint and the active
normal.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{BalkePearl1997},
\citet{RichardsonRobins2010}, \citet{DeChaisemartin2017},
\citet{DahlHuberMellace2023}, \citet{SachsJonzonSjolanderGabriel2023},
\citet{GabrielSachsSjolander2023}, and
\citet{DuarteFinkelsteinKnoxMummoloShpitser2024}.  Balke--Pearl and the
symbolic/automated-bound papers imply that a finite LP or symbolic procedure
can bound the model; Richardson--Robins makes the fixed-defier sensitivity
comparison unavoidable because \(\pi_N=q_{10}-\pi_F\) turns a never-taker upper
cap into a lower truncation on the feasible defier-share interval.  The
de Chaisemartin and Dahl--Huber--Mellace comparisons are not subsuming because
their defier-tolerant conclusions target LATE interpretation under cancellation
or local monotonicity, while Conjecture~\ref{conj:facet-envelope} targets the
sharp ATE support projection under caps alone.  Gabriel--Sachs--Sjolander is
not subsuming because its warning is that separate sharp bounds need joint
construction, exactly the point of the proposed two-cap facet catalogue.  The
epsilon-gap is the observable strict-shrinkage frontier and active-facet
equivalence table after eliminating \(t\): none of those papers state
necessary and sufficient inequalities for when the never-taker cap is
redundant, when it strictly improves the endpoint on an open set, or which
joint-cap facet is responsible.  \citet{BaiHuangMoonShaikhVytlacil2024} is the
flagship frontier comparison: their no-power regions concern generalized
monotonicity restrictions on treatment response, whereas the proposed
strict-shrinkage frontier asks when compliance-stratum mass caps have
identifying power because the two untreated observed cells pin
\(\pi_N+\pi_F\) and \(\pi_N+\pi_C\) in different ways.  (b) The concrete consumer is
\citet{LevisBonviniZengKeeleKennedy2025}: resolving this conjecture would give
their nonsmooth IV-bound inference problem an explicit active-facet map for
monotonicity-violation sensitivity.

\begin{example}[Nondegenerate strict-shrinkage witness target]\label{ex:strict-shrinkage-target}
The Stage 0 endpoint catalogue should certify at least the following open-set
pattern, not only a boundary case.  Let
\[
q_{11}=q_{00}=0.6,\quad q_{10}=q_{01}=0.4,\quad
r_{11}=0.21,\quad r_{10}=0.14,\quad r_{01}=0.15,\quad r_{00}=0.24,
\]
so every observed \(Z,D\) cell has positive mass and an interior observed
conditional outcome mean.  With \(\bar\delta=0.4\), the lower endpoint of the
fixed-\(t\) outcome LP equals \(-0.43\) at the unconstrained lower face
\(t=0\), but after lowering the never-taker cap to \(\bar\nu=0.2\) the
first-stage interval is truncated to \(t\ge q_{10}-\bar\nu=0.2\), and the same
fixed-\(t\) endpoint at the new truncation face is \(-0.37\).  The proposed
facet catalogue must explain this inward movement by a never-taker lower
truncation/joint-support facet, and the same inequality pattern should persist
on a neighborhood of the displayed law.
\end{example}

\begin{conjecture}[Boundary-distribution sharpness certificate]\label{conj:boundary-certificates}
(NOT YET PROVED.)  For every exposed affine form in
\(\mathfrak{L}_{\mathrm{BDN}}\cup\mathfrak{U}_{\mathrm{BDN}}\), there is a
constructive boundary map
\[
\Gamma_f:(P,\bar\delta,\bar\nu)\mapsto(\pi_s,y_{ds})_{s,d}
\]
defined on the corresponding feasibility region such that
\(\Gamma_f(P,\bar\delta,\bar\nu)\in
\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) and attains the endpoint
facet \(f\).  The maps cover zero observed cells, cap-binding faces, and the
four-cell cases in which \(Z=1,D=0\) and \(Z=0,D=0\) impose distinct hidden
untreated mixtures.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{RichardsonRobins2010} and \citet{BalkePearl1997} certify sharpness
through latent response distributions, but the mined prior CausalSmith proposal
asserted sharpness before correcting the four-cell feasible system.  This
conjecture asks for primal certificates aligned with the two-cap facet list,
not merely a dual LP value.  (b) The concrete consumer is the
\texttt{oq\_defiers} open question in the study graph: it needs auditable
bounds when monotonicity is relaxed to a limited defier share, and boundary
laws are the evidence that the interval is sharp rather than conservative.

\begin{theorem}[Exact face-limit reductions]\label{thm:face-limits}
Under Assumptions~\ref{ass:support}--\ref{ass:faces}, the following reductions
must hold for the polytope in Theorem~\ref{thm:polytope-wellposed}.
\begin{enumerate}[label=(\roman*)]
\item On the zero-defier face \(\bar\delta=0\), the complier-coordinate
projection
\[
\theta_C=\E[Y(1)-Y(0)\mid C]
\]
is the Imbens--Angrist Wald/LATE estimand
\[
\frac{\E[Y\mid Z=1]-\E[Y\mid Z=0]}
     {\E[D\mid Z=1]-\E[D\mid Z=0]},
\]
whenever the denominator is positive.  The population ATE projection remains
an interval unless the always-taker and never-taker hidden counterfactual
components are also fixed.
\item On the pure never-taker face \(\bar\nu=1\) and \(\pi_N=1\), the ATE
identified set is the Manski support-fill-in interval
\[
[0-m_0,\ 1-m_0],
\qquad m_0=\E[Y\mid D=0].
\]
\end{enumerate}
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) \citet{ImbensAngrist1994} and \citet{Manski1990} are not new results, but
the epsilon-gap is equality of the proposed two-cap projected endpoints with
these two limiting objects.  This guards against a common false claim that
\(\bar\delta=0\) point-identifies the population ATE; it point-identifies only
the complier coordinate unless noncomplier counterfactuals are otherwise
restricted.  (b) The concrete consumers are the accepted
\texttt{imbens\_angrist\_late} and \texttt{manski\_nonparametric\_bounds}
study artifacts, which become formal sanity faces of the new envelope rather
than separate examples.

\section{Sanity-check corollaries}
\begin{corollary}[No-cap reduction]\label{cor:no-cap}
If \(\bar\delta\ge1\) and \(\bar\nu\ge1\), then
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) is the unrestricted
binary-IV principal-strata polytope, so Conjecture~\ref{conj:facet-envelope}
must reduce to the bounded-outcome Balke--Pearl IV ATE support envelope.
\end{corollary}

\begin{corollary}[Zero-defier LATE sanity]\label{cor:late}
Under Assumption~\ref{ass:faces} with \(\bar\delta=0\), the \(F\)-stratum is
removed from all four mixture equations.  The difference
\(\E[Y\mid Z=1]-\E[Y\mid Z=0]\) cancels the always-taker and never-taker
observed components, leaving \(\pi_C\theta_C\); the first-stage difference is
\(\pi_C\).  Hence the complier-coordinate reduction in
Theorem~\ref{thm:face-limits} is exactly the Wald ratio.
\end{corollary}

\begin{corollary}[Pure never-taker support sanity]\label{cor:never}
Under Assumption~\ref{ass:faces} with \(\bar\nu=1\) and \(\pi_N=1\), all
observed outcomes equal \(Y(0)\), so \(\E[Y(0)]=m_0\) and \(Y(1)\) is
constrained only by \([0,1]\).  Therefore the ATE interval is
\([0-m_0,1-m_0]\).
\end{corollary}

\section{Proof-sketch route}
The mathematical route is finite-dimensional convex analysis.  First write the
latent variables as the vector
\((\pi_C,\pi_N,\pi_A,\pi_F,y_{0C},y_{1C},y_{0N},y_{1N},y_{0A},y_{1A},y_{0F},y_{1F})\)
and assemble the equality constraints from the eight observed
\((q_{zd},r_{zd})\) equations plus the simplex.  Theorem~\ref{thm:polytope-wellposed}
then follows from compactness and linear projection.  The flagship work is to
enumerate all nondegenerate active bases involving support constraints and the
two caps, discard infeasible bases by sign conditions, and simplify the dual
endpoint forms into the five facet families in
Conjecture~\ref{conj:facet-envelope}.  Sharpness is checked by giving the
corresponding primal vertex maps and verifying that every observed mixture
equation is matched, including zero-cell limits.  The face reductions are
ordinary cancellations in the principal-strata equations.

\section{Honest scope flags}
Theorem~\ref{thm:polytope-wellposed} is routine once the setup is fixed.
Theorem~\ref{thm:face-limits} is labelled as a theorem-level requirement
because it is an algebraic face check, but the detailed equality with every
facet in Conjecture~\ref{conj:facet-envelope} remains part of the open work.
The genuinely novel kernel is Conjecture~\ref{conj:facet-envelope} together
with Conjecture~\ref{conj:boundary-certificates}.  The proposal deliberately
does not claim that zero defiers point-identify the population ATE.  It also
does not yet fix the final count of affine facets; Stage 0 must compute and
name the catalogue rather than hide behind a generic LP solver.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft around the full four-cell simultaneous
defier-cap and never-taker-cap ATE polytope; prior verdict: none.
\item v2 (revise) -- added the missing research-practice paragraph, a
cap-compatible nonemptiness assumption, a saturated \(\bar\nu=1\) pure
never-taker face, and a Bai-frontier strict-shrinkage clause for
Conjecture~\ref{conj:facet-envelope}; prior verdict: REVISE.
\item v3 (revise) -- added the Richardson--Robins fixed-defier optimization
comparison, generic symbolic/automated-bound precedents, and recentered
Conjecture~\ref{conj:facet-envelope} on the observable strict-shrinkage
frontier needed for flagship novelty; prior verdict: REVISE.
\item v4 (revise) -- restricted the Richardson--Robins fixed-defier comparison
in Conjecture~\ref{conj:facet-envelope} to the outcome-feasible set
\(I_{\pi}^{Y}(P,\bar\delta,\bar\nu)\); prior verdict: REVISE.
\item v5 (revise) -- added the missed defier/monotonicity and symbolic-bound
comparators, an explicit non-subsumption comparison for Conjecture~\ref{conj:facet-envelope},
and a nondegenerate strict-shrinkage witness target; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Angrist, Imbens, and Rubin(1996)]{AngristImbensRubin1996}
Angrist, J. D., G. W. Imbens, and D. B. Rubin (1996).
Identification of causal effects using instrumental variables.
\emph{Journal of the American Statistical Association} 91(434), 444--455.
\url{https://doi.org/10.1080/01621459.1996.10476902}.

\bibitem[Bai et al.(2024)]{BaiHuangMoonShaikhVytlacil2024}
Bai, Y., M. Huang, H. R. Moon, A. M. Shaikh, and E. Vytlacil (2024).
On the identifying power of generalized monotonicity restrictions.
\emph{NBER Working Paper}.

\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Balke, A. and J. Pearl (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association} 92(439), 1171--1176.
\url{https://doi.org/10.1080/01621459.1997.10474074}.

\bibitem[Duarte et al.(2024)]{DuarteFinkelsteinKnoxMummoloShpitser2024}
Duarte, G., N. Finkelstein, D. Knox, J. Mummolo, and I. Shpitser (2024).
An automated approach to causal inference in discrete settings.
\emph{Journal of the American Statistical Association} 119(547), 1778--1793.
\url{https://doi.org/10.1080/01621459.2023.2216909}.

\bibitem[Dahl, Huber, and Mellace(2023)]{DahlHuberMellace2023}
Dahl, C. M., M. Huber, and G. Mellace (2023).
It is never too LATE: a new look at local average treatment effects with or
without defiers.
\emph{The Econometrics Journal} 26(3), 378--404.
\url{https://doi.org/10.1093/ectj/utad013}.

\bibitem[de Chaisemartin(2017)]{DeChaisemartin2017}
de Chaisemartin, C. (2017).
Tolerating defiance? Local average treatment effects without monotonicity.
\emph{Quantitative Economics} 8(2), 367--396.
\url{https://doi.org/10.3982/QE601}.

\bibitem[Gabriel, Sachs, and Sjolander(2023)]{GabrielSachsSjolander2023}
Gabriel, E. E., M. C. Sachs, and A. Sjolander (2023).
Sharp nonparametric bounds for decomposition effects with two binary mediators.
\emph{Journal of the American Statistical Association}.

\bibitem[Imbens and Angrist(1994)]{ImbensAngrist1994}
Imbens, G. W. and J. D. Angrist (1994).
Identification and estimation of local average treatment effects.
\emph{Econometrica} 62(2), 467--475.
\url{https://www.jstor.org/stable/2951620}.

\bibitem[Levis et al.(2025)]{LevisBonviniZengKeeleKennedy2025}
Levis, A. W., M. Bonvini, J. Zeng, L. Keele, and E. H. Kennedy (2025).
Covariate-assisted bounds on causal effects with instrumental variables.
\emph{Journal of the Royal Statistical Society: Series B}.
\url{https://doi.org/10.1093/jrsssb/qkaf028}.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Manski and Pepper(2000)]{ManskiPepper2000}
Manski, C. F. and J. V. Pepper (2000).
Monotone instrumental variables: With an application to the returns to schooling.
\emph{Econometrica} 68(4), 997--1010.

\bibitem[Mourifie and Wan(2017)]{MourifieWan2017}
Mourifie, I. and Y. Wan (2017).
Testing local average treatment effect assumptions.
\emph{Review of Economics and Statistics} 99(2), 305--313.

\bibitem[Noack(2021)]{Noack2021}
Noack, C. (2021).
Sensitivity analysis without assumptions.
\emph{arXiv:2106.06421}.
\url{https://doi.org/10.48550/arXiv.2106.06421}.

\bibitem[Picchetti(2026)]{Picchetti2026}
Picchetti, F. (2026).
Monotonicity and independence relaxations in instrumental-variable bounds.
\emph{arXiv:2603.25529}.
\url{https://doi.org/10.48550/arXiv.2603.25529}.

\bibitem[Richardson and Robins(2010)]{RichardsonRobins2010}
Richardson, T. S. and J. M. Robins (2010).
Analysis of the binary instrumental variable model.
\emph{Heuristics, Probability and Causality / University of Washington Working Paper}.
\url{https://csss.uw.edu/files/working-papers/2010/wp99.pdf}.

\bibitem[Sachs et al.(2023)]{SachsJonzonSjolanderGabriel2023}
Sachs, M. C., G. Jonzon, A. Sjolander, and E. E. Gabriel (2023).
A general method for deriving tight symbolic bounds on causal effects.
\emph{Journal of Computational and Graphical Statistics} 32(2), 567--576.
\url{https://doi.org/10.1080/10618600.2022.2071905}.

\bibitem[Swanson et al.(2018)]{SwansonHernanMillerRobinsRichardson2018}
Swanson, S. A., M. A. Hernan, M. Miller, J. M. Robins, and T. S. Richardson (2018).
Partial identification of the average treatment effect using instrumental
variables: Review of methods for binary instruments, treatments, and outcomes.
\emph{Journal of the American Statistical Association} 113(522), 933--947.
\url{https://doi.org/10.1080/01621459.2018.1434530}.

\bibitem[Yap(2022)]{Yap2022}
Yap, R. (2022).
Bounds on policy relevant treatment effects without monotonicity.
\emph{Princeton Industrial Relations Section Working Paper}.
\url{http://arks.princeton.edu/ark:/88435/dsp015d86p341p}.
\end{thebibliography}

\end{document}
