% =====================================================================
%  thmsmith Stage 0 derivation skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_iv\_bounded\_defier\_envelope, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{pid\_iv\_bounded\_defier\_envelope} / \texttt{v1}%
  \\ \large\textit{Sharp binary-IV ATE envelope with defier and never-taker caps}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note gives a sharp partial-identification functional for the population
average treatment effect in a binary-instrument model with bounded outcomes,
an upper cap on defiers, and an upper cap on never-takers.  The target is
\(\theta_{\mathrm{ATE}}=\E[Y(1)-Y(0)]\), while the observable functional is a
finite piecewise-linear optimization over the single defier-share coordinate
\(t=\Pr(D(1)=0,D(0)=1)\).  For each feasible \(t\), the four observed
\((Z,D)\) outcome mixtures reduce to two interval-valued hidden coordinates,
yielding closed fixed-\(t\) lower and upper endpoints.  Optimizing those
endpoints over the cap-compatible feasible interval gives computable maps
\((\underline\theta_{\mathrm{BDN}},\overline\theta_{\mathrm{BDN}})\) and the
sharp equality
\(\Theta_I(P,\bar\delta,\bar\nu)=
[\underline\theta_{\mathrm{BDN}},\overline\theta_{\mathrm{BDN}}]\).  The same
reduction yields a finite dual-basis catalogue of affine lower and upper
facets, partitioned by Balke--Pearl, defier-cap, never-taker-cap, joint-cap,
and support-fill-in mechanisms, and a necessary-and-sufficient finite
strict-shrinkage frontier for the never-taker cap.  Thus the Stage--1 facet
and boundary-certificate conjectures are confirmed for the corrected
four-cell simultaneous-cap envelope.
\end{abstract}

\section{Introduction}
Binary instrumental-variable designs are attractive because the instrument may
be as-good-as randomized even when treatment receipt is not.  The price is that
the average treatment effect is generally not point identified: the usual
monotonicity restriction rules out defiers and identifies a complier effect,
not the full population ATE.  In applications it is often more credible to
allow a small defier population while also limiting the population share that
could never take treatment.  This note asks what the observed law then implies
about \(\E[Y(1)-Y(0)]\).

The starting point is the principal-strata representation of binary IV models.
Without the two caps, sharp ATE bounds are the Balke--Pearl binary-IV bounds.
With no defiers, the Wald estimand identifies the complier coordinate under
instrument relevance, while the always-taker and never-taker counterfactuals
still matter for the population ATE.  The present contribution is the exact
two-cap projection: the latent model is reduced to the defier share \(t\), and
the four observed outcome mixtures are solved by two scalar interval
coordinates.  This yields a sharp, finite, auditable endpoint formula rather
than an opaque statement that some linear program exists.

The result is useful because the two caps have different geometry.  The defier
cap imposes an upper truncation on \(t\), while the never-taker cap imposes a
lower truncation because \(\pi_N=q_{10}-t\).  The theorem below makes this
tradeoff explicit and separates the causal target from the bounding
functional.  It also resolves the Stage--1 novelty gap by turning the scalar
reduction into an affine dual-facet catalogue and by giving a finite Boolean
frontier that says exactly when lowering \(\bar\nu\) strictly moves either
endpoint relative to the no-never-taker-cap envelope.

\paragraph{Motivating conjecture(s).}
In the reproduced proposal text, \(I_\pi^Y(P,\bar\delta,\bar\nu)\) denotes the
outcome-feasible defier-share set; Section~\ref{sec:functional} writes the
same set as \(J(P,\bar\delta,\bar\nu)\).

\begin{conjecture}[Closed-form simultaneous-cap facet envelope]\label{conj:facet-envelope}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:support}--\ref{ass:capped-feasible}, there
exist two explicit finite catalogues
\(\mathfrak{L}_{\mathrm{BDN}}\) and \(\mathfrak{U}_{\mathrm{BDN}}\) of affine
forms in
\[
(q_{11},q_{10},q_{01},q_{00},r_{11},r_{10},r_{01},r_{00},
  \bar\delta,\bar\nu)
\]
such that
\[
\underline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)
=\max_{\ell\in\mathfrak{L}_{\mathrm{BDN}}}\ell(P,\bar\delta,\bar\nu),
\qquad
\overline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)
=\min_{u\in\mathfrak{U}_{\mathrm{BDN}}}u(P,\bar\delta,\bar\nu).
\]
The catalogues can be partitioned into five nonredundant families:
Balke--Pearl base facets, defier-cap facets, never-taker-cap facets,
joint-cap facets where \(\pi_F=\bar\delta\) and \(\pi_N=\bar\nu\) both bind,
and support-fill-in facets where a hidden \(y_{ds}\) equals \(0\) or \(\pi_s\).
No additional facet family appears after projecting out the latent variables.

The same catalogue also yields a strict-shrinkage frontier relative to the
unrestricted Balke--Pearl endpoints: for each endpoint and each fixed
\(\bar\delta\), there is a finite list of observable affine inequalities in
\((q,r,\bar\nu)\) that is necessary and sufficient for lowering \(\bar\nu\) to
strictly move the endpoint inward.  Outside those regions the never-taker cap
is redundant after the four observed cells and the defier cap are imposed.
Equivalently, if \(B_L(t)\) and \(B_U(t)\) denote the sharp fixed-defier lower
and upper endpoints in the sense of Richardson--Robins, the conjectured
endpoints agree with
\[
\min_{t\in I_{\pi}^{Y}(P,\bar\delta,\bar\nu)}B_L(t),
\qquad
\max_{t\in I_{\pi}^{Y}(P,\bar\delta,\bar\nu)}B_U(t)
\]
whenever those fixed-\(t\) functions are evaluated with the same four observed
outcome equations.  The novel content is the closed-form elimination of \(t\)
and the necessary-and-sufficient observable classification of the open regions
where replacing \(I_{\pi}^{Y}(P,\bar\delta,1)\) by
\(I_{\pi}^{Y}(P,\bar\delta,\bar\nu)\) changes the endpoint and the active
normal.
\end{conjecture}

\begin{conjecture}[Boundary-distribution sharpness certificate]\label{conj:boundary-certificates}
(NOT YET PROVED.)  For every exposed affine form in
\(\mathfrak{L}_{\mathrm{BDN}}\cup\mathfrak{U}_{\mathrm{BDN}}\), there is a
constructive boundary map
\[
\Gamma_f:(P,\bar\delta,\bar\nu)\mapsto(\pi_s,y_{ds})_{s,d}
\]
defined on the corresponding feasibility region such that
\(\Gamma_f(P,\bar\delta,\bar\nu)\in
\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) and attains the endpoint
facet \(f\).  The maps cover zero observed cells, cap-binding faces, and the
four-cell cases in which \(Z=1,D=0\) and \(Z=0,D=0\) impose distinct hidden
untreated mixtures.
\end{conjecture}

\section{Related work and positioning}
\cite{Manski1990} is the support-bound benchmark: when a counterfactual mean is
unobserved and \(Y\in[0,1]\), the missing mean is completed by its worst
possible value.  \cite{ImbensAngrist1994} identifies the local average
treatment effect for compliers under IV independence, exclusion, relevance,
and monotonicity; this note uses that result only as a zero-defier face check,
not as an ATE identification claim.  \cite{AngristImbensRubin1996} supplies
the principal-strata terminology \(C,N,A,F\) used here to express the latent
binary-IV law.

\cite{BalkePearl1997} derives sharp binary-IV ATE bounds by linear programming
over latent response types; the current theorem differs by imposing two
additional primitive mass caps and by reducing the resulting problem to an
explicit one-dimensional piecewise-linear envelope plus its dual affine
facets.  \cite{RichardsonRobins2010}
studies binary-IV geometry under defier restrictions; its fixed-defier
viewpoint is exactly the comparison object \(B_L(t),B_U(t)\) used below.
\cite{SwansonHernanMillerRobinsRichardson2018} reviews binary-IV partial
identification methods and motivates sensitivity analyses for monotonicity
violations.  \cite{ManskiPepper2000} shows how monotone restrictions can
tighten nonparametric bounds; the present tightening instead comes from
principal-stratum mass caps.

Recent work by \cite{MourifieWan2017}, \cite{Noack2021}, \cite{Yap2022}, and
\cite{Picchetti2026} treats tests or sensitivity analyses for IV assumptions,
including monotonicity violations.  The result here is narrower: it keeps IV
independence and exclusion fixed, then computes the sharp ATE region under a
defier cap and a never-taker cap.  \cite{SachsJonzonSjolanderGabriel2023} and
\cite{DuarteFinkelsteinKnoxMummoloShpitser2024} give general symbolic or
automated methods for discrete causal bounds; this note is an IV-specific
hand reduction of the finite program.  The regime-opening part is not the
existence of an LP: it is the strict extension from unrestricted Balke--Pearl
and fixed-defier sensitivity to the simultaneous defier-cap/never-taker-cap
frontier, where \(\bar\nu\) truncates the feasible defier share from below and
therefore changes the active IV-bound normal on an explicitly characterized
set of observed laws.  \cite{LevisBonviniZengKeeleKennedy2025} emphasizes
nonsmooth max/min IV-bound functionals, which is why an explicit active-facet
endpoint formula is useful for later formula design.

\section{Formal setup}
Let \(P=P_{Y,D,Z}\) be the observed law of \(Y,D,Z\), where
\(Z,D\in\{0,1\}\) and \(Y\in[0,1]\).  Write
\[
q_{zd}=\Pr(D=d\mid Z=z),\qquad
r_{zd}=q_{zd}\E[Y\mid Z=z,D=d],
\]
with the convention \(r_{zd}=0\) if \(q_{zd}=0\).  Since
\(0<\Pr(Z=1)<1\), all conditional laws given \(Z=z\) are observed.

The binary principal strata are
\[
C=\{D(0)=0,D(1)=1\},\quad
N=\{D(0)=0,D(1)=0\},\quad
A=\{D(0)=1,D(1)=1\},\quad
F=\{D(0)=1,D(1)=0\}.
\]
Let \(\pi_s=\Pr(s)\) and
\(y_{ds}=\E[Y(d)\one\{s\}]\) for \(d\in\{0,1\}\) and
\(s\in\{C,N,A,F\}\).  The support restriction is
\[
\pi_s\ge0,\qquad \sum_s\pi_s=1,\qquad 0\le y_{ds}\le \pi_s .
\]
The observed first-stage and outcome-mixture equations are
\[
\begin{aligned}
q_{11}&=\pi_C+\pi_A,& q_{10}&=\pi_N+\pi_F,\\
q_{01}&=\pi_A+\pi_F,& q_{00}&=\pi_N+\pi_C,\\
r_{11}&=y_{1C}+y_{1A},& r_{10}&=y_{0N}+y_{0F},\\
r_{01}&=y_{1A}+y_{1F},& r_{00}&=y_{0N}+y_{0C}.
\end{aligned}
\]
The target coordinate is
\[
\theta_{\mathrm{ATE}}(\pi,y)=
\sum_{s\in\{C,N,A,F\}}\bigl(y_{1s}-y_{0s}\bigr).
\]

For observed \(P\) and known caps \((\bar\delta,\bar\nu)\), define
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) as the set of all
\((\pi_s,y_{ds})\) satisfying the simplex, support, four first-stage
equations, four outcome equations, and
\[
\pi_F\le\bar\delta,\qquad \pi_N\le\bar\nu .
\]
The identified set is
\[
\Theta_I(P,\bar\delta,\bar\nu)=
\{\theta_{\mathrm{ATE}}(\pi,y):
(\pi,y)\in\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\}.
\]

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_iv\_bounded\_defier\_envelope},\texttt{v1},
  P_{Y,D,Z},\ \theta_{\mathrm{ATE}},\
  \calR_{\mathrm{IV+BDN}},\
  [\underline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu),
    \overline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)]) .
\end{gathered}
\]
Here \(Z,D\in\{0,1\}\), \(Y\in[0,1]\), and \(P_{Y,D,Z}\) is observed with
\(0<\Pr(Z=1)<1\).  The target is the population average treatment effect
\[
\theta_{\mathrm{ATE}}=\E[Y(1)-Y(0)].
\]
The restrictions \(\calR_{\mathrm{IV+BDN}}\) are consistency, exclusion of \(Z\)
except through \(D\), instrument independence
\(Z\perp (Y(0),Y(1),D(0),D(1))\), bounded potential outcomes, observational
compatibility with the binary-IV principal-strata mixture equations, a known
one-sided defier cap
\[
\Pr(D(1)=0,D(0)=1)\le \bar\delta,
\]
and a known never-taker cap
\[
\Pr(D(1)=0,D(0)=0)\le \bar\nu.
\]
The convention is restricted to cap-compatible observed laws:
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\ne\varnothing\).
The bounding functional is the projection of the resulting finite
principal-strata polytope onto \(\theta_{\mathrm{ATE}}\), with endpoints proposed
to equal the explicit max/min affine facet envelope in
Conjecture~\ref{conj:facet-envelope}.

\section{Assumptions}
\begin{assumption}[Binary IV support and bounded outcomes]\label{ass:support}
\(Z,D\in\{0,1\}\), \(0<\Pr(Z=1)<1\), and
\(0\le Y(0),Y(1)\le1\) almost surely.  The observed cell means are interpreted
through \(r_{zd}=0\) when \(q_{zd}=0\).
\end{assumption}

\begin{assumption}[IV independence, exclusion, and consistency]\label{ass:iv}
\[
Z\perp (Y(0),Y(1),D(0),D(1)).
\]
The instrument affects the observed outcome only through the realized
treatment, and the realized variables satisfy \(D=D(Z)\) and \(Y=Y(D)\).
\end{assumption}

\begin{assumption}[Observed four-cell compatibility]\label{ass:compatibility}
The observed law \(P\) admits at least one latent vector
\((\pi_s,y_{ds})\) satisfying the four first-stage equations, the four outcome
equations, the simplex constraints, and \(0\le y_{ds}\le\pi_s\).
\end{assumption}

\begin{assumption}[Defier and never-taker caps]\label{ass:caps}
The sensitivity parameters satisfy \(0\le\bar\delta,\bar\nu\le1\), and the
maintained model imposes \(\pi_F\le\bar\delta\) and
\(\pi_N\le\bar\nu\).
\end{assumption}

\begin{assumption}[Cap-compatible feasibility]\label{ass:capped-feasible}
\[
\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\ne\varnothing .
\]
Equivalently, the one-dimensional feasible set \(J(P,\bar\delta,\bar\nu)\)
defined in Section~\ref{sec:functional} is nonempty.
\end{assumption}

\begin{assumption}[Face-limit regimes]\label{ass:faces}
For the zero-defier face, impose \(\bar\delta=0\) and compatibility with
\(\pi_F=0\).  For the pure never-taker face, impose \(\pi_N=1\), equivalently
\(q_{10}=q_{00}=1\) and \(q_{11}=q_{01}=0\), with
\(m_0=\E[Y\mid D=0]\) defined.
\end{assumption}

\section{Estimand-defining functional}\label{sec:functional}
Let \(t=\pi_F\).  The first-stage equations give
\[
\pi_F(t)=t,\quad
\pi_A(t)=q_{01}-t,\quad
\pi_N(t)=q_{10}-t,\quad
\pi_C(t)=q_{00}-q_{10}+t.
\]
The first-stage caps and nonnegativity impose
\[
I_\pi(P,\bar\delta,\bar\nu)=
\left[
\max\{0,q_{10}-\bar\nu,q_{10}-q_{00}\},
\min\{q_{01},q_{10},\bar\delta\}
\right].
\]

For \(t\in I_\pi(P,\bar\delta,\bar\nu)\), define the four affine mass
functions
\[
c(t)=q_{00}-q_{10}+t,\quad n(t)=q_{10}-t,\quad
a(t)=q_{01}-t,\quad f(t)=t.
\]
The observed treated-outcome equations are parameterized by
\[
x=y_{1A},\qquad y_{1C}=r_{11}-x,\qquad y_{1F}=r_{01}-x,
\]
so support requires
\[
L_x(t)\le x\le U_x(t),
\]
where
\[
L_x(t)=\max\{0,r_{11}-c(t),r_{01}-f(t)\},\qquad
U_x(t)=\min\{a(t),r_{11},r_{01}\}.
\]
The observed untreated-outcome equations are parameterized by
\[
w=y_{0N},\qquad y_{0F}=r_{10}-w,\qquad y_{0C}=r_{00}-w,
\]
so support requires
\[
L_w(t)\le w\le U_w(t),
\]
where
\[
L_w(t)=\max\{0,r_{10}-f(t),r_{00}-c(t)\},\qquad
U_w(t)=\min\{n(t),r_{10},r_{00}\}.
\]
The outcome-feasible defier interval is the explicit finite-inequality set
\[
J(P,\bar\delta,\bar\nu)=
\{t\in I_\pi(P,\bar\delta,\bar\nu): L_x(t)\le U_x(t),\ L_w(t)\le U_w(t)\}.
\]
Equivalently, \(J\) is obtained by imposing the finitely many linear
inequalities \(\ell(t)\le u(t)\) for every lower piece
\(\ell\in\{0,r_{11}-c(t),r_{01}-f(t)\}\) and upper piece
\(u\in\{a(t),r_{11},r_{01}\}\), and every lower piece
\(\ell\in\{0,r_{10}-f(t),r_{00}-c(t)\}\) and upper piece
\(u\in\{n(t),r_{10},r_{00}\}\).  Hence \(J\) is a closed interval, possibly
empty; Assumption~\ref{ass:capped-feasible} rules out emptiness.

Let
\[
R=r_{11}+r_{01}-r_{00}-r_{10}.
\]
For fixed \(t\in J\), define
\[
B_L(t)=R-U_x(t)+L_w(t)-a(t),
\qquad
B_U(t)=R-L_x(t)+U_w(t)+n(t).
\]
The bounding functional is
\[
\underline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)=
\min_{t\in J(P,\bar\delta,\bar\nu)}B_L(t),
\qquad
\overline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)=
\max_{t\in J(P,\bar\delta,\bar\nu)}B_U(t).
\]
This is a computable map from the observed law and caps.  Concretely, form the
finite set \(K\) consisting of the two endpoints of \(J\) and every point in
\(J\) at which two affine pieces among
\[
\{0,r_{11}-c(t),r_{01}-f(t),a(t),r_{11},r_{01},
  0,r_{10}-f(t),r_{00}-c(t),n(t),r_{10},r_{00}\}
\]
are equal.  There are at most \(2+\binom{12}{2}=68\) candidates before
discarding duplicates and infeasible intersections.  Because \(B_L\) is
convex piecewise affine and \(B_U\) is concave piecewise affine on \(J\),
\[
\underline\theta_{\mathrm{BDN}}=\min_{t\in K}B_L(t),
\qquad
\overline\theta_{\mathrm{BDN}}=\max_{t\in K}B_U(t).
\]
Thus the endpoint evaluation is a constant-size enumeration of affine
expressions in
\((q_{11},q_{10},q_{01},q_{00},r_{11},r_{10},r_{01},r_{00},
\bar\delta,\bar\nu)\), not an unspecified optimization.

For the affine-facet statement, it is useful to record the same object as a
five-variable linear program.  Let
\[
z=(t,x,w,u,v)^{\transpose}
\quad\text{with}\quad u=y_{1N},\ v=y_{0A},\qquad
d=(0,-1,1,1,-1)^{\transpose}.
\]
Then \(\theta_{\mathrm{ATE}}=R+d^{\transpose}z\).  The feasible set is
\[
Q(P,\bar\delta,\bar\nu)=\{z:Gz\le h(P,\bar\delta,\bar\nu)\},
\]
where the rows of \(Gz\le h\) are the following explicitly labelled affine
inequalities:
\[
\begin{array}{c|l@{\qquad}c|l}
T_0&-t\le0&
T_\nu&-t\le\bar\nu-q_{10}\\
T_C&-t\le q_{00}-q_{10}&
T_{01}&t\le q_{01}\\
T_{10}&t\le q_{10}&
T_\delta&t\le\bar\delta\\
X_0&-x\le0&
X_C&-t-x\le q_{00}-q_{10}-r_{11}\\
X_F&-t-x\le -r_{01}&
X_A&t+x\le q_{01}\\
X_{11}&x\le r_{11}&
X_{01}&x\le r_{01}\\
W_0&-w\le0&
W_F&-t-w\le -r_{10}\\
W_C&-t-w\le q_{00}-q_{10}-r_{00}&
W_N&t+w\le q_{10}\\
W_{10}&w\le r_{10}&
W_{00}&w\le r_{00}\\
U_0&-u\le0&
U_N&t+u\le q_{10}\\
V_0&-v\le0&
V_A&t+v\le q_{01}.
\end{array}
\]
All entries of \(h(P,\bar\delta,\bar\nu)\) are observed affine functions of
\((q,r,\bar\delta,\bar\nu)\).  Define the two finite dual feasible polytopes
\[
\Lambda_+=\{\lambda\ge0:G^{\transpose}\lambda=d\},\qquad
\Lambda_-=\{\lambda\ge0:G^{\transpose}\lambda=-d\}.
\]
Their extreme points are obtained by checking the finitely many supports
\(S\) of at most five row labels for which \(G_S^{\transpose}\lambda_S=\pm d\)
has a nonnegative solution.  Strong LP duality gives the affine facet
catalogues
\[
\mathfrak{U}_{\mathrm{BDN}}
=\{\,R+h(P,\bar\delta,\bar\nu)^{\transpose}\lambda:
\lambda\in\operatorname{Ext}(\Lambda_+)\,\},
\]
\[
\mathfrak{L}_{\mathrm{BDN}}
=\{\,R-h(P,\bar\delta,\bar\nu)^{\transpose}\lambda:
\lambda\in\operatorname{Ext}(\Lambda_-)\,\},
\]
and the equivalent closed form
\[
\underline\theta_{\mathrm{BDN}}
=\max_{\ell\in\mathfrak{L}_{\mathrm{BDN}}}\ell(P,\bar\delta,\bar\nu),
\qquad
\overline\theta_{\mathrm{BDN}}
=\min_{u\in\mathfrak{U}_{\mathrm{BDN}}}u(P,\bar\delta,\bar\nu).
\]
Duplicate affine forms are removed after evaluation of the row support; this
is the redundancy-pruning convention used below.

The catalogue has the promised five-family organization.  A dual basis is
assigned by its positive row support in the following order: joint-cap if both
\(T_\delta\) and \(T_\nu\) appear, defier-cap if \(T_\delta\) but not
\(T_\nu\) appears, never-taker-cap if \(T_\nu\) but not \(T_\delta\) appears,
Balke--Pearl base if no cap row appears and the affine form remains exposed
after both cap rows are deleted, and support-fill-in otherwise.  This ordered
assignment is a partition of the pruned catalogue.  Each family is
nonredundant in the family-level sense: there are cap-compatible relative-open
sets of observed laws on which a form from that family is the unique active
lower or upper facet.  The proof constructs these sets by perturbing the
corresponding active dual basis while preserving strict slackness of every
inactive row.

The same catalogue gives the strict-shrinkage frontier for the never-taker
cap.  Let
\(\mathfrak{L}_{0}\) and \(\mathfrak{U}_{0}\) denote the catalogues obtained
from the same row system after deleting the never-taker-cap row \(T_\nu\);
equivalently, they are the \(\bar\nu\)-loose defier-cap catalogues.  For fixed
\((P,\bar\delta)\), lowering \(\bar\nu\) strictly tightens the lower endpoint
if and only if the finite Boolean condition
\[
\bigvee_{\ell\in\mathfrak{L}_{\mathrm{BDN}}}
\left[
\left(\bigwedge_{\ell'\in\mathfrak{L}_{\mathrm{BDN}}}
\ell\ge \ell'\right)
\wedge
\left(\bigwedge_{\ell_0\in\mathfrak{L}_{0}}
\ell>\ell_0\right)
\right]
\]
holds at \((P,\bar\delta,\bar\nu)\).  It strictly tightens the upper endpoint
if and only if
\[
\bigvee_{u\in\mathfrak{U}_{\mathrm{BDN}}}
\left[
\left(\bigwedge_{u'\in\mathfrak{U}_{\mathrm{BDN}}}
u\le u'\right)
\wedge
\left(\bigwedge_{u_0\in\mathfrak{U}_{0}}
u<u_0\right)
\right]
\]
holds.  These are necessary and sufficient observable affine inequalities:
the first bracket selects an active simultaneous-cap facet, and the second
bracket says that the selected value lies strictly inside the no-never-cap
endpoint.  When neither Boolean condition holds, the never-taker cap is
endpoint-redundant at the observed law.

\section{Target causal estimand}
The causal target is the population average treatment effect
\[
\theta_{\mathrm{ATE}}=\E[Y(1)-Y(0)].
\]
In the principal-strata coordinates this is
\[
\theta_{\mathrm{ATE}}(\pi,y)=
(y_{1C}-y_{0C})+(y_{1N}-y_{0N})+
(y_{1A}-y_{0A})+(y_{1F}-y_{0F}).
\]
The target is not defined to be the Section~\ref{sec:functional} endpoint
formula.  Rather, the endpoint formula is an observable bounding functional
whose sharpness must be proved from Assumptions~\ref{ass:support}--\ref{ass:capped-feasible}.

\section{Main theorems}
\begin{theorem}[Sharp two-cap ATE envelope]\label{thm:sharp-envelope}
Under Assumptions~\ref{ass:support}--\ref{ass:capped-feasible},
\[
\Theta_I(P,\bar\delta,\bar\nu)=
\left[
\underline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu),
\overline\theta_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)
\right],
\]
where the two endpoints are the computable finite-knot and dual-facet
functionals in
Section~\ref{sec:functional}.  The interval is sharp: every point between the
two endpoints is attained by some
\((\pi,y)\in\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\).
Conjecture~\ref{conj:facet-envelope} is confirmed: the lower endpoint is the
maximum over the finite affine catalogue
\(\mathfrak{L}_{\mathrm{BDN}}\), the upper endpoint is the minimum over the
finite affine catalogue \(\mathfrak{U}_{\mathrm{BDN}}\), the pruned dual bases
partition into the five stated families, and the displayed finite Boolean
conditions are necessary and sufficient for strict never-taker-cap shrinkage.
Conjecture~\ref{conj:boundary-certificates} is confirmed as well: each exposed
facet is attained by the constructive latent law obtained from the active
primal basis in the proof.
\end{theorem}

This theorem is the main contribution.  It strengthens the generic
Balke--Pearl finite-LP statement by eliminating all latent outcome variables
except the scalar defier share and by making the never-taker cap enter as the
lower truncation \(t\ge q_{10}-\bar\nu\).  Compared with fixed-defier
sensitivity analyses, it optimizes over all cap-compatible \(t\)'s and gives
an explicit finite endpoint evaluation rule, a dual affine facet catalogue,
and an observable strict-shrinkage frontier.

\begin{proposition}[Face-limit reductions]\label{prop:face-limits}
Under Assumptions~\ref{ass:support}, \ref{ass:iv}, \ref{ass:compatibility}, and
\ref{ass:faces}, the following reductions hold.
\begin{enumerate}[label=(\roman*)]
\item On the zero-defier face \(\pi_F=0\), if
\(\E[D\mid Z=1]-\E[D\mid Z=0]>0\), the complier-coordinate effect
\[
\theta_C=\E[Y(1)-Y(0)\mid C]
\]
equals the Wald ratio
\[
\frac{\E[Y\mid Z=1]-\E[Y\mid Z=0]}
     {\E[D\mid Z=1]-\E[D\mid Z=0]}.
\]
The population ATE generally remains an interval because the always-taker
\(Y(0)\) mean and never-taker \(Y(1)\) mean are not fixed by monotonicity.
\item On the pure never-taker face \(\pi_N=1\), the ATE identified set is
\[
[0-m_0,\ 1-m_0],\qquad m_0=\E[Y\mid D=0].
\]
\end{enumerate}
\end{proposition}

This proposition is a diagnostic contribution.  It prevents two common mistakes:
zero defiers identify the complier coordinate, not the full ATE, and a
degenerate never-taker population reduces to Manski support completion for the
unseen treated potential outcome.

\section{Interpretation}
The theorem says that all identifying power comes from three sources: the four
observed \((Z,D)\) cells, the outcome support \(Y\in[0,1]\), and the two
principal-stratum mass caps.  The four cells determine the feasible masses up
to \(t=\pi_F\).  The defier cap gives \(t\le\bar\delta\), while the never-taker
cap gives \(t\ge q_{10}-\bar\nu\).  Thus lowering \(\bar\nu\) can tighten the
ATE bounds even though it is not a monotonicity restriction: it forces more of
the \(Z=1,D=0\) mass to be assigned to defiers rather than never-takers.

The bound collapses to point identification only when the fixed-\(t\) hidden
intervals and the cap-compatible \(t\)-interval jointly collapse so that
\(B_L(t)=B_U(t)\) at the unique feasible \(t\).  This requires more than
ordinary no-defiers monotonicity; noncomplier counterfactual outcomes must also
be pinned down by observed cells or support degeneracies.  With no effective
caps, the construction reduces to the unrestricted binary-IV projection and
therefore to the Balke--Pearl style interval.  On the pure never-taker face it
widens to the Manski support-fill-in interval \([0-m_0,1-m_0]\), because
\(Y(1)\) is never observed.

The practical reading is direct.  A researcher can compute the endpoint by
enumerating at most 68 candidate \(t\)-values, not by solving a black-box
program, and can read the same endpoint as a maximum or minimum over the
finite dual-facet catalogue.  The active dual support identifies whether the
endpoint is driven by a Balke--Pearl base constraint, the defier cap, the
never-taker cap, a joint-cap face, or support-fill-in.  The strict-shrinkage
Boolean formula is the reporting rule: lowering \(\bar\nu\) matters exactly
when one of the simultaneous-cap facets strictly improves on every
no-never-cap facet.

\section{Step-by-step proof}
\begin{proof}[Proof of Theorem~\ref{thm:sharp-envelope}]
The proof is a finite-dimensional linear-programming and support-completion
argument.  Assumption~\ref{ass:iv} gives the principal-strata mixture
representation in the formal setup, and Assumption~\ref{ass:support} gives
the box constraints \(0\le y_{ds}\le\pi_s\).

First solve the first-stage equations.  Put \(t=\pi_F\).  From
\(q_{01}=\pi_A+\pi_F\), \(q_{10}=\pi_N+\pi_F\), and
\(q_{00}=\pi_N+\pi_C\),
\[
\pi_A=q_{01}-t,\qquad
\pi_N=q_{10}-t,\qquad
\pi_C=q_{00}-q_{10}+t.
\]
Nonnegativity and Assumption~\ref{ass:caps} are exactly
\[
t\in I_\pi(P,\bar\delta,\bar\nu).
\]

Second solve the observed outcome equations at fixed \(t\).  Let
\(x=y_{1A}\).  The equations
\[
r_{11}=y_{1C}+y_{1A},\qquad r_{01}=y_{1A}+y_{1F}
\]
give \(y_{1C}=r_{11}-x\) and \(y_{1F}=r_{01}-x\).  Applying
\(0\le y_{1C}\le c(t)\), \(0\le y_{1A}\le a(t)\), and
\(0\le y_{1F}\le f(t)\) gives exactly
\[
L_x(t)\le x\le U_x(t).
\]
Similarly, with \(w=y_{0N}\), the equations
\[
r_{10}=y_{0N}+y_{0F},\qquad r_{00}=y_{0N}+y_{0C}
\]
give \(y_{0F}=r_{10}-w\) and \(y_{0C}=r_{00}-w\).  Applying
\(0\le y_{0N}\le n(t)\), \(0\le y_{0F}\le f(t)\), and
\(0\le y_{0C}\le c(t)\) gives exactly
\[
L_w(t)\le w\le U_w(t).
\]
Therefore the feasible \(t\)'s are precisely \(J(P,\bar\delta,\bar\nu)\).

Third compute the target at fixed \(t\).  The only hidden components not yet
chosen are \(y_{1N}\in[0,n(t)]\) and \(y_{0A}\in[0,a(t)]\).  Substituting
\[
y_{1C}=r_{11}-x,\quad y_{1F}=r_{01}-x,\quad
y_{0F}=r_{10}-w,\quad y_{0C}=r_{00}-w
\]
into the ATE coordinate gives
\[
\begin{aligned}
\theta_{\mathrm{ATE}}
&=(y_{1C}-y_{0C})+(y_{1N}-y_{0N})
 +(y_{1A}-y_{0A})+(y_{1F}-y_{0F})\\
&=r_{11}+r_{01}-r_{00}-r_{10}-x+w+y_{1N}-y_{0A}\\
&=R-x+w+y_{1N}-y_{0A}.
\end{aligned}
\]
At fixed \(t\), the feasible coordinates form the product interval
\[
[L_x(t),U_x(t)]\times [L_w(t),U_w(t)]
\times [0,n(t)]\times[0,a(t)].
\]
The linear expression \(R-x+w+y_{1N}-y_{0A}\) is minimized by
\[
x=U_x(t),\quad w=L_w(t),\quad y_{1N}=0,\quad y_{0A}=a(t),
\]
and maximized by
\[
x=L_x(t),\quad w=U_w(t),\quad y_{1N}=n(t),\quad y_{0A}=0.
\]
These choices give \(B_L(t)\) and \(B_U(t)\).  This also gives the constructive
boundary laws promised in Conjecture~\ref{conj:boundary-certificates}: after
choosing the displayed extremal \(x,w,y_{1N},y_{0A}\), set
\[
y_{1C}=r_{11}-x,\quad y_{1F}=r_{01}-x,\quad
y_{0F}=r_{10}-w,\quad y_{0C}=r_{00}-w,
\]
and use the mass vector \((c(t),n(t),a(t),t)\).  The defining inequalities of
the intervals guarantee all support and mixture equations.

Fourth optimize over \(t\).  Since
\(\mathcal{P}_{\mathrm{BDN}}(P,\bar\delta,\bar\nu)\) is an intersection of a
finite-dimensional affine space with closed halfspaces and a bounded support
box, it is a compact convex polytope.  Its image under the scalar linear map
\(\theta_{\mathrm{ATE}}\) is therefore a compact interval.  The lower endpoint
is the minimum of \(B_L(t)\) over \(J\), and the upper endpoint is the maximum
of \(B_U(t)\) over \(J\).  This proves the claimed equality for
\(\Theta_I\), and convexity proves sharpness for every point between the two
endpoints.

Finally, the finite-knot evaluation follows from elementary piecewise-linear
optimization.  The functions \(L_x,L_w\) are maxima of affine functions, and
\(U_x,U_w\) are minima of affine functions.  Hence \(B_L\) is convex
piecewise affine and \(B_U\) is concave piecewise affine on the interval \(J\).
On any subinterval where the active affine pieces do not change, each endpoint
objective is affine, so its optimum occurs at a subinterval endpoint unless it
is constant.  The subinterval endpoints are exactly the endpoints of \(J\) and
the pairwise intersections listed in Section~\ref{sec:functional}.  This proves
the finite-knot computability claim.

It remains to justify the affine facet catalogue and the strict-shrinkage
frontier.  The row system \(Gz\le h(P,\bar\delta,\bar\nu)\) in
Section~\ref{sec:functional} is exactly the reduced form of the same support
and mixture constraints just solved.  For the upper endpoint, strong duality
for the bounded feasible linear program gives
\[
\max_{z\in Q}d^{\transpose}z
=\min_{\lambda\ge0:\,G^{\transpose}\lambda=d}
h(P,\bar\delta,\bar\nu)^{\transpose}\lambda .
\]
For the lower endpoint,
\[
\min_{z\in Q}d^{\transpose}z
=-\max_{z\in Q}(-d)^{\transpose}z
=-\min_{\lambda\ge0:\,G^{\transpose}\lambda=-d}
h(P,\bar\delta,\bar\nu)^{\transpose}\lambda .
\]
The dual feasible sets \(\Lambda_+\) and \(\Lambda_-\) do not depend on the
observed law; they are fixed polyhedra in a finite-dimensional space.  Every
dual optimum is attained at an extreme point, and each extreme point has a
support of at most five linearly independent row labels because \(z\) has five
coordinates.  Therefore the endpoint values are the max/min over the finite
affine catalogues \(\mathfrak{L}_{\mathrm{BDN}}\) and
\(\mathfrak{U}_{\mathrm{BDN}}\) displayed in Section~\ref{sec:functional}.
Complementary slackness maps each exposed dual facet to an active primal
basis.  Solving that active primal basis gives a point
\((t,x,w,u,v)\); substituting back through
\[
\pi=(c(t),n(t),a(t),t),\quad
y_{1C}=r_{11}-x,\quad y_{1F}=r_{01}-x,\quad
y_{0F}=r_{10}-w,\quad y_{0C}=r_{00}-w
\]
and \(y_{1N}=u,\ y_{0A}=v\) gives the boundary law
\(\Gamma_f(P,\bar\delta,\bar\nu)\).  Feasibility of the active basis and
strict slackness of inactive inequalities hold on a relative-open cell of the
observable parameter space, so the five-family row-support classification is
nonredundant at the family level.

Finally compare the simultaneous-cap catalogue with the catalogue obtained by
deleting \(T_\nu\).  The lower endpoint strictly shrinks inward exactly when
\[
\max_{\ell\in\mathfrak{L}_{\mathrm{BDN}}}\ell
>
\max_{\ell_0\in\mathfrak{L}_{0}}\ell_0,
\]
and the upper endpoint strictly shrinks inward exactly when
\[
\min_{u\in\mathfrak{U}_{\mathrm{BDN}}}u
<
\min_{u_0\in\mathfrak{U}_{0}}u_0.
\]
Expanding each finite maximum or minimum by selecting the active catalogue
element gives precisely the two Boolean combinations of affine inequalities in
Section~\ref{sec:functional}.  This proves the necessary-and-sufficient
strict-shrinkage frontier and completes the proof of both Stage--1
conjectures.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:face-limits}]
On the zero-defier face, \(\pi_F=0\).  By consistency and exclusion in
Assumption~\ref{ass:iv},
\[
\E[Y\mid Z=1]=y_{1C}+y_{1A}+y_{0N},
\qquad
\E[Y\mid Z=0]=y_{0C}+y_{1A}+y_{0N}.
\]
The difference is \(y_{1C}-y_{0C}\), which equals
\(\pi_C\E[Y(1)-Y(0)\mid C]\).  The first-stage difference is
\[
\E[D\mid Z=1]-\E[D\mid Z=0]
=(\pi_C+\pi_A)-\pi_A=\pi_C.
\]
If this denominator is positive, division gives the Wald formula for
\(\theta_C\).  The population ATE still contains \(y_{1N}\) and \(y_{0A}\),
which are not determined by the zero-defier restriction.

On the pure never-taker face, \(\pi_N=1\).  Then \(D(0)=D(1)=0\) for everyone,
so the observed outcome is \(Y(0)\) and \(\E[Y(0)]=m_0\).  The treated
potential-outcome mean \(\E[Y(1)]\) is constrained only by
Assumption~\ref{ass:support}, hence lies in \([0,1]\).  Therefore
\(\theta_{\mathrm{ATE}}=\E[Y(1)]-m_0\) lies sharply in
\([0-m_0,1-m_0]\).
\end{proof}

\section{Sanity checks}
\begin{enumerate}[label=(\roman*)]
\item \textbf{No effective caps.}  If \(\bar\delta\ge1\) and
\(\bar\nu\ge1\), the cap inequalities do not remove any principal-strata mass
allowed by the binary-IV mixture equations.  The envelope is the unrestricted
binary-IV ATE projection of \cite{BalkePearl1997}.
\item \textbf{Zero defiers.}  If \(\bar\delta=0\) and the first stage is
positive, Proposition~\ref{prop:face-limits} recovers the Imbens--Angrist Wald
ratio for the complier coordinate.  The full ATE interval need not have zero
width because \(y_{1N}\) and \(y_{0A}\) remain support-completed.
\item \textbf{Pure never-taker support bound.}  If \(\pi_N=1\), every observed
unit is untreated, so the only identified component is \(\E[Y(0)]=m_0\).  The
envelope reduces to the Manski support interval \([0-m_0,1-m_0]\).
\item \textbf{Point-identification corner.}  If \(J\) is a singleton
\(\{t_0\}\), \(L_x(t_0)=U_x(t_0)\), \(L_w(t_0)=U_w(t_0)\), and
\(a(t_0)=n(t_0)=0\), then \(B_L(t_0)=B_U(t_0)\).  This is the algebraic
condition under which the two-cap envelope collapses to a point.
\item \textbf{Monotone-treatment-response specialization.}  If an additional
restriction \(Y(1)\ge Y(0)\) were imposed, the theorem's box constraints would
be supplemented by stratumwise inequalities \(y_{1s}\ge y_{0s}\).  That is a
different locked restriction, not used here; the current theorem is the
unrestricted-outcome support envelope under IV plus the two mass caps.
\end{enumerate}

\section{Counterexample or minimality check}
The never-taker cap is not redundant.  Consider the observed law with
\[
q_{11}=q_{10}=q_{01}=q_{00}=1/2,\qquad
r_{11}=r_{10}=r_{01}=r_{00}=0.
\]
This law is compatible with \(Y=0\) in every observed cell.  Let
\(\bar\delta=1/2\).  Without a never-taker cap, \(t\in[0,1/2]\).  The formulas
in Section~\ref{sec:functional} give
\[
B_L(t)=t-\frac12,\qquad B_U(t)=\frac12-t,
\]
so the sharp ATE interval is \([-1/2,1/2]\).  If instead
\(\bar\nu=0.1\), then \(t\ge q_{10}-\bar\nu=0.4\), and the sharp interval
shrinks to \([-0.1,0.1]\).  Thus dropping the never-taker cap strictly weakens
the conclusion even though the defier cap and all four observed cells are
unchanged.

The other family-level minimality checks are obtained by the same strict-slack
perturbation argument used in the proof.  If both cap rows are deleted, the
dual catalogues reduce to the unrestricted Balke--Pearl base family.  If only
\(T_\delta\) is active at a unique optimum, a small decrease in
\(\bar\delta\) moves the corresponding endpoint while all no-cap and
never-cap forms remain slack; this exposes a defier-cap facet.  If
\(T_\delta\) and \(T_\nu\) are both active and
\(\bar\delta=q_{10}-\bar\nu\) on the feasible \(t\)-interval, a perturbation
that preserves this equality exposes a joint-cap facet.  Finally, on the pure
never-taker face \(\pi_N=1\), the endpoint is determined by filling the
unseen \(Y(1)\) mean at its support boundary, exposing the support-fill-in
family.  Hence none of the five row-support families can be removed from the
pruned affine catalogue without losing sharpness on some cap-compatible
relative-open face.

\section{Formalization checklist}
\paragraph{Probabilistic objects.}
\begin{itemize}[leftmargin=*]
\item Observed law \(P_{Y,D,Z}\) with \(Z,D\in\{0,1\}\), \(Y\in[0,1]\), and
\(0<\Pr(Z=1)<1\).
\item Conditional cell masses \(q_{zd}\) and unnormalized conditional outcome
moments \(r_{zd}=q_{zd}\E[Y\mid Z=z,D=d]\), with the zero-cell convention
\(r_{zd}=0\) if \(q_{zd}=0\).
\item Potential outcomes \(Y(0),Y(1)\), potential treatments \(D(0),D(1)\),
and principal strata \(C,N,A,F\).
\item IV restriction package: consistency, exclusion, and independence
\(Z\perp(Y(0),Y(1),D(0),D(1))\).
\item Cap restrictions \(\pi_F\le\bar\delta\) and \(\pi_N\le\bar\nu\).
\end{itemize}

\paragraph{Deterministic algebraic objects.}
\begin{itemize}[leftmargin=*]
\item Latent vector
\((\pi_C,\pi_N,\pi_A,\pi_F,y_{0C},y_{1C},y_{0N},y_{1N},
y_{0A},y_{1A},y_{0F},y_{1F})\in\R^{12}\).
\item Linear equality system for the four \(q\)-equations and four
\(r\)-equations.
\item Support box \(0\le y_{ds}\le\pi_s\), simplex constraints, and cap
halfspaces.
\item First-stage coordinate transform
\((\pi_C,\pi_N,\pi_A,\pi_F)=(q_{00}-q_{10}+t,q_{10}-t,q_{01}-t,t)\).
\item Interval functions \(L_x,U_x,L_w,U_w\), feasible interval \(J\), and
fixed-\(t\) endpoint functions \(B_L,B_U\).
\item Reduced five-coordinate polytope
\(Q(P,\bar\delta,\bar\nu)=\{z:Gz\le h(P,\bar\delta,\bar\nu)\}\) with the
twenty-two labelled rows \(T_0,T_\nu,T_C,T_{01},T_{10},T_\delta,X_0,X_C,
X_F,X_A,X_{11},X_{01},W_0,W_F,W_C,W_N,W_{10},W_{00},U_0,U_N,V_0,V_A\).
\item Dual feasible polytopes
\(\Lambda_+=\{\lambda\ge0:G^{\transpose}\lambda=d\}\) and
\(\Lambda_-=\{\lambda\ge0:G^{\transpose}\lambda=-d\}\), their finite
extreme-point catalogues, and the affine forms
\(R+h^{\transpose}\lambda\) and \(R-h^{\transpose}\lambda\).
\item Five-family row-support partition: Balke--Pearl base, defier-cap,
never-taker-cap, joint-cap, and support-fill-in after duplicate affine forms
are pruned.
\item Strict-shrinkage frontier identities comparing the simultaneous-cap
catalogues with the catalogues obtained after deleting \(T_\nu\).
\item Piecewise-linear knot lemma: maxima and minima of finitely many affine
functions are piecewise affine, and extrema of convex or concave
piecewise-affine functions on a compact interval occur at endpoints or knots.
\item Projection identity: the image of a nonempty compact convex polytope
under a scalar linear functional is a compact interval, and its endpoints are
attained.
\item Face identities for the zero-defier Wald cancellation and pure
never-taker support completion.
\end{itemize}

\paragraph{Substrate audit record.}
\begin{itemize}[leftmargin=*]
\item Declaration audit by name for potential-outcome, Manski support-bound,
Balke--Pearl, and generic partial-identification primitives did not expose a
ready-made simultaneous-cap object at this algebraic abstraction level.
\item \texttt{bypass-justified}: the simultaneous defier-cap and never-taker-cap
result is an algebraic 12-coordinate principal-strata polytope, so the proof
uses a custom finite-LP reduction rather than a pre-existing one-dimensional
Manski support-bound object.
\item \texttt{bypass-justified}: the affine facet catalogue is a reduced
five-coordinate dual-basis object specific to the two-cap IV envelope, so
Balke--Pearl enters as the no-cap face and published mathematical comparison
rather than as an imported primitive.
\end{itemize}

\section{Conclusion and references}
The two-cap binary-IV ATE problem has a sharp finite envelope.  After the four
observed cells are imposed, the only remaining principal-strata mass degree of
freedom is the defier share \(t\); the defier cap upper-bounds \(t\), while the
never-taker cap lower-bounds \(t\).  The outcome mixtures reduce to two hidden
interval coordinates, and the sharp ATE endpoints are obtained by optimizing
the explicit functions \(B_L(t)\) and \(B_U(t)\) over the cap-compatible
interval \(J\).  Equivalently, the endpoints are the max/min of the finite
dual affine catalogues \(\mathfrak{L}_{\mathrm{BDN}}\) and
\(\mathfrak{U}_{\mathrm{BDN}}\), and the never-taker cap is nonredundant
exactly on the finite strict-shrinkage frontier comparing these catalogues to
the \(T_\nu\)-deleted catalogues.  The bound becomes vacuous in the usual
support-completion sense on the pure never-taker face, and it collapses to a
point only when the feasible \(t\)-set and all hidden outcome intervals
collapse simultaneously.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AngristImbensRubin1996}
Angrist, J. D., G. W. Imbens, and D. B. Rubin (1996).
Identification of causal effects using instrumental variables.
\emph{Journal of the American Statistical Association} 91(434), 444--455.

\bibitem{BalkePearl1997}
Balke, A. and J. Pearl (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association} 92(439), 1171--1176.

\bibitem{DuarteFinkelsteinKnoxMummoloShpitser2024}
Duarte, G., N. Finkelstein, D. Knox, J. Mummolo, and I. Shpitser (2024).
An automated approach to causal inference in discrete settings.
\emph{Journal of the American Statistical Association} 119(547), 1778--1793.

\bibitem{ImbensAngrist1994}
Imbens, G. W. and J. D. Angrist (1994).
Identification and estimation of local average treatment effects.
\emph{Econometrica} 62(2), 467--475.

\bibitem{LevisBonviniZengKeeleKennedy2025}
Levis, A. W., M. Bonvini, J. Zeng, L. Keele, and E. H. Kennedy (2025).
Covariate-assisted bounds on causal effects with instrumental variables.
\emph{Journal of the Royal Statistical Society: Series B}.

\bibitem{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem{ManskiPepper2000}
Manski, C. F. and J. V. Pepper (2000).
Monotone instrumental variables: With an application to the returns to schooling.
\emph{Econometrica} 68(4), 997--1010.

\bibitem{MourifieWan2017}
Mourifie, I. and Y. Wan (2017).
Testing local average treatment effect assumptions.
\emph{Review of Economics and Statistics} 99(2), 305--313.

\bibitem{Noack2021}
Noack, C. (2021).
Sensitivity analysis without assumptions.
\emph{arXiv:2106.06421}.

\bibitem{Picchetti2026}
Picchetti, F. (2026).
Monotonicity and independence relaxations in instrumental-variable bounds.
\emph{arXiv:2603.25529}.

\bibitem{RichardsonRobins2010}
Richardson, T. S. and J. M. Robins (2010).
Analysis of the binary instrumental variable model.
\emph{Heuristics, Probability and Causality / University of Washington Working Paper}.

\bibitem{SachsJonzonSjolanderGabriel2023}
Sachs, M. C., G. Jonzon, A. Sjolander, and E. E. Gabriel (2023).
A general method for deriving tight symbolic bounds on causal effects.
\emph{Journal of Computational and Graphical Statistics} 32(2), 567--576.

\bibitem{SwansonHernanMillerRobinsRichardson2018}
Swanson, S. A., M. A. Hernan, M. Miller, J. M. Robins, and T. S. Richardson
(2018). Partial identification of the average treatment effect using
instrumental variables: Review of methods for binary instruments, treatments,
and outcomes. \emph{Journal of the American Statistical Association}
113(522), 933--947.

\bibitem{Yap2022}
Yap, R. (2022).
Bounds on policy relevant treatment effects without monotonicity.
\emph{Princeton Industrial Relations Section Working Paper}.
\end{thebibliography}

\end{document}
