% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_dynamic\_iv\_compliance, specialization=v3
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_dynamic\_iv\_compliance} / \texttt{v3}%
  \\ \large\textit{Bounded-defier assignment-memory bounds for dynamic IV effects}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_dynamic\_iv\_compliance},\texttt{v3},
  P_{Y,D_1,D_2,Z_1,Z_2,X},\ \theta_{C,0}^{(2)},\
  \mathcal{R}_{\mathrm{2stageIV+memory+bd}},\
  [\underline\theta_{\mathrm{bd}}(P,e,\kappa),\overline\theta_{\mathrm{bd}}(P,e,\kappa)]) .
\end{gathered}
\]
Here \(X\) has finite support, \(Z_t,D_t\in\{0,1\}\), and \(Y\in[0,1]\).  The first-stage encouragement \(Z_1\) is randomized within \(X\); the second-stage encouragement follows the known adaptive law
\[
e_2(z\mid x,z_1,d_1)=\Pr(Z_2=z\mid X=x,Z_1=z_1,D_1=d_1),
\]
which may depend on the retained assignment-memory label \(Z_1\) after conditioning on \((X,D_1)\).  The target remains the first-stage-complier, first-stage-untreated second-period effect
\[
\theta_{C,0}^{(2)}
=\E\!\left[Y(0,1)-Y(0,0)\mid D_1(1)=1,\ D_1(0)=0\right].
\]
The restrictions \(\mathcal{R}_{\mathrm{2stageIV+memory+bd}}\) are consistency, exclusion of \(Z_1,Z_2\) except through \(D_1,D_2\), randomized \(Z_1\) within \(X\), sequential randomization of \(Z_2\) given \((X,Z_1,D_1)\), positivity of all reachable encouragement cells, one-sided second-stage compliance within each retained history, no direct assignment-memory effect within the \(D_1=0\) state, and a bounded first-stage defier restriction
\[
0\le q_F(x)=\Pr(D_1(1)=0,D_1(0)=1\mid X=x)\le\kappa(x),
\]
with all induced first-stage stratum shares nonnegative, including \(q_A(x)=\Pr(D_1=1\mid Z_1=0,X=x)-q_F(x)\ge0\).  The analyst specifies \(\kappa(x)\), and \(\kappa(x)=0\) reproduces the parent \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v2} one-sided first-stage model.  The bounding functional is the sharp interval obtained by the finite latent-response linear program retaining \(Z_1\) as an assignment-memory label while allowing first-stage strata \(C,N,A,F\).

\begin{abstract}
The parent \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v2} result shows that a remembered first-stage assignment can tighten dynamic IV bounds because one observed history is a pure never-taker branch.  This proposal asks whether the same memory mechanism survives when first-stage monotonicity fails but defier mass is bounded.  The flagship conjecture is that the sharp two-stage bound is the projection of a defier-trimmed response-contribution prism: the parent response-contribution subtraction is recovered at \(\kappa=0\), while positive \(\kappa\) opens an interval fan for the never-taker contribution.  A second conjecture states a phase transition: retained assignment memory gives strict endpoint gain below an observable defier-budget threshold and can lose all strict gain above it.  Resolving this would turn a fragile one-sided-compliance theorem into a sensitivity theorem for dynamic IV experiments whose monotonicity assumption is credible only approximately.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Sequential encouragement designs often rely on monotonicity to interpret compliance strata, but monotonicity is exactly the behavioral assumption applied researchers worry about when advice, reminders, eligibility letters, or digital recommendations can backfire for some units.  The parent v2 theorem used one-sided first-stage compliance to make \((Z_1,D_1)=(1,0)\) a pure never-taker branch and then subtracted its response contribution from the mixed untreated branch.  If even a small defier population is allowed, that cell is no longer pure; it is a never-taker/defier mixture.  The methodological question is whether assignment memory still has theorem-level identifying content when the branch that drove the parent formula is contaminated in a bounded but nonzero way.

\paragraph{The main finding (proposed).}
Theorem~\ref{thm:corner-nesting} records the upgrade-axis corner case: the bounded-defier feasible set is monotone in \(\kappa\), and at \(\kappa=0\) it reduces to the parent one-sided memory bound.  Conjecture~\ref{conj:defier-prism} is the flagship upgrade delta: under bounded first-stage defiers, the sharp cellwise memory bound for \(\theta_{C,0}^{(2)}(x)\) equals a union over feasible defier shares of response-contribution prisms that trim the never-taker contribution out of the contaminated \((Z_1,D_1)=(1,0)\) branch.  Conjecture~\ref{conj:phase-transition} states that strict memory gain has an observable threshold in the defier budget: below the threshold the retained \(Z_1\) label still tightens at least one endpoint, while above it the coarsened relaxation can match the memory endpoints for an open set of laws.

\paragraph{What is new.}
Relative to the parent \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v2}, the new contribution is the bounded-defier generalization: v2 assumes \(q_F(x)=0\) and therefore has a pure never-taker memory branch; v3 lets \(0\le q_F(x)\le\kappa(x)\), enforces the induced always-taker and never-taker nonnegativity constraints, and asks for the sharp interval fan created by contaminating that branch with defiers.  Relative to published work, the closest dynamic comparator is \citet{SojitraSyrgkanis2024}, which identifies dynamic LATEs under one-sided noncompliance and additional cross-period restrictions; the epsilon-gap is the nonparametric partial-ID regime with two-sided first-stage compliance and retained non-Markov assignment memory.  The closest static defier sensitivity comparator is \citet{Noack2021}, which indexes sharp static monotonicity-violation bounds by defier share and outcome-distribution distance; the epsilon-gap is that no retained dynamic assignment-memory branch can be activated or absorbed in her one-period sensitivity region.  The closest static defier identification comparators are \citet{DeChaisemartin2017} and \citet{DahlHuberMellace2023}; the epsilon-gap is a dynamic response-contribution bound where defiers contaminate the memory branch that previously supplied the subtraction term.  The closest generic computation result is \citet{DuarteFinkelsteinKnoxMummoloShpitser2024}, which can encode such discrete bounds, but does not state a reusable bounded-defier prism or a memory-gain threshold.

\paragraph{How it positions in the literature.}
The proposal lives in the partial-identification cluster: IV bounds, Balke--Pearl response types, sensitivity to monotonicity, and dynamic treatment timing.  It is not a new do-calculus rule and not a panel regression decomposition.  It uses the parent v2 response-contribution formula as the zero-defier corner and asks whether the same algebra can be made robust to bounded violations of first-stage monotonicity.

\paragraph{Implications for the community.}
The concrete downstream consumer is the dynamic-LATE and SMART literature represented by \citet{SojitraSyrgkanis2024} and \citet{ArtmanBhattacharyaErtefaieLynchMcKayJohnson2024}: their one-sided or modeled-compliance analyses would gain a nonparametric sensitivity bound showing how much monotonicity violation is needed before retained assignment memory stops tightening the target dynamic effect.

\paragraph{How research benefits from the conclusion.}
Readers should report a defier-budget sensitivity curve for retained-memory dynamic IV bounds, rather than treating the one-sided memory formula as either valid or unusable.

\section{Related work}
\citet{AngristImbensRubin1996} define the static principal-strata IV benchmark and the monotonicity condition that rules out defiers; this proposal weakens that premise in a dynamic memory-bound setting.  \citet{BalkePearl1997} [reused from parent] derive sharp static binary-IV bounds under imperfect compliance; the proposed theorem uses the same finite response-type logic inside retained histories.  \citet{SwansonHernanMillerRobinsRichardson2018} [reused from parent] review static binary-IV partial identification and supply the vocabulary for bounded-outcome IV intervals.  \citet{BugniGaoObradovicVelez2024} [reused from parent] characterize ATE and ATT identified sets under covariate-adaptive randomization with imperfect compliance; their strata are pre-treatment assignment strata rather than post-baseline memory labels contaminated by defiers.  \citet{DuarteFinkelsteinKnoxMummoloShpitser2024} [reused from parent] provide generic Autobounds machinery for discrete sharp bounds; this proposal seeks the analytic prism and threshold that a generic polynomial program would not expose.  \citet{SojitraSyrgkanis2024} [reused from parent] identify dynamic LATEs under one-sided noncompliance plus cross-period restrictions; the present proposal studies partial identification when first-stage one-sidedness is relaxed.

\citet{MourifieWan2017} give conditional inequality tests for the static LATE assumptions, showing that monotonicity and related IV restrictions have observable implications; this motivates treating defier mass as a sensitivity parameter rather than a background nuisance.  \citet{Kitagawa2015} develops a specification test for instrument validity and monotonicity in heterogeneous treatment-effect models; it is the closest flagship-venue source for observable monotonicity restrictions, but it is static and not a dynamic assignment-memory bound.  \citet{Noack2021} derives sharp static sensitivity bounds indexed by the defier share and complier/defier outcome-distribution distance; v3 differs because retained assignment memory creates an additional branch equation whose endpoint influence can disappear at a design-specific threshold.  \citet{DeChaisemartin2017} weakens monotonicity through compliers-defiers and stochastic-monotonicity style conditions under which an IV estimand remains interpretable for a complier subset; that is an estimand-interpretation result, not a sharp dynamic memory-bound sensitivity formula.  \citet{DahlHuberMellace2023} study LATEs with or without defiers under weaker local monotonicity and local compliers-defiers conditions; the proposal differs by bounding a two-stage dynamic principal-stratum contrast when defiers contaminate the branch used by the parent memory subtraction.  \citet{ArtmanBhattacharyaErtefaieLynchMcKayJohnson2024} [reused from parent] model partial compliance in SMARTs with principal-strata marginal structural models; the proposed result supplies a nonparametric sensitivity target for the same applied design class.

In-catalogue prior art is limited.  The relevant \texttt{ThmSmith/doc/API.md} section says the PartialID catalogue is empty at seed time and will be populated by \texttt{pid\_*} qids.  The banked parent \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v2}: ``Sharp memory-retaining dynamic IV bounds as LP projections; marginal mixture subtraction is only an outer relaxation'' is the closest in-repo result and is the required corner case.  The downgraded \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v1}: ``Full-history IV bounds for dynamic treatment effects under adaptive noncompliance'' is burned for the Bellman/non-pasteability angle and is not reused as the kernel here.  The present v3 proposal differs from both by replacing the pure never-taker branch with a bounded never-taker/defier mixture and asking for the resulting sensitivity threshold.

\section{Formal setup}
Let \(O=(Y,D_1,D_2,Z_1,Z_2,X)\) have observed law \(P\), with finite \(X\), binary \(Z_t,D_t\), and \(Y\in[0,1]\).  Write \(p_1(z\mid x)=\Pr(Z_1=z\mid X=x)\) and
\[
e_2(z\mid x,z_1,d_1)=\Pr(Z_2=z\mid X=x,Z_1=z_1,D_1=d_1).
\]
First-stage principal strata are
\[
C=(D_1(1),D_1(0))=(1,0),\quad
N=(0,0),\quad
A=(1,1),\quad
F=(0,1),
\]
with shares \(q_s(x)=\Pr(S=s\mid X=x)\).  The observable first-stage contrast is
\[
\Delta_D(x)=\Pr(D_1=1\mid Z_1=1,X=x)-\Pr(D_1=1\mid Z_1=0,X=x)=q_C(x)-q_F(x).
\]
The bounded-defier sensitivity parameter \(\kappa(x)\) restricts \(q_F(x)\in[0,\kappa(x)]\).  A feasible defier share \(f\) in cell \(x\) determines
\[
q_F(f)=f,\qquad
q_C(f)=\Delta_D(x)+f,\qquad
q_N(f)=\Pr(D_1=0\mid Z_1=1,X=x)-f,\qquad
q_A(f)=\Pr(D_1=1\mid Z_1=0,X=x)-f.
\]
All four shares \(q_C(f),q_N(f),q_A(f),q_F(f)\) must be nonnegative, and \(q_C(f)>0\) is required for target cells.

For \(s\in\{C,N,A,F\}\) and \(d_1\in\{0,1\}\), let \(D_2^{s,d_1}(z_2)\) be the second-stage potential treatment and let \(Y(d_1,d_2)\) be the potential outcome.  The target cell effect is
\[
\theta_{C,0}^{(2)}(x)
=\E[Y(0,1)-Y(0,0)\mid S=C,X=x],
\]
and the aggregate target is
\[
\theta_{C,0}^{(2)}
=\sum_x w_C(x)\theta_{C,0}^{(2)}(x),\qquad
w_C(x)=\frac{\Pr(X=x)q_C(x)}{\sum_{x'}\Pr(X=x')q_C(x')}.
\]
Unlike the parent, the weights \(w_C(x)\) may vary over the feasible defier-share set because \(q_C(x)=\Delta_D(x)+q_F(x)\).

The retained-memory LP \(\mathcal{L}_{\mathrm{bd}}(P,e,\kappa)\) has finite latent variables for \(S\in\{C,N,A,F\}\), one-sided second-stage response types in the \(D_1=0\) branch, and bounded potential-outcome contribution variables.  It reproduces all observed probabilities and \(Y\)-first moments under \(P\), obeys the known assignment probabilities \(p_1,e_2\), and imposes \(0\le q_F(x)\le\kappa(x)\).  The sharp bounded-defier memory set is
\[
\Theta_{\mathrm{bd}}(P,e,\kappa)
=\{\theta_{C,0}^{(2)}(\ell):\ell\in\mathcal{L}_{\mathrm{bd}}(P,e,\kappa)\},
\]
with endpoints \(\underline\theta_{\mathrm{bd}}(P,e,\kappa)\) and \(\overline\theta_{\mathrm{bd}}(P,e,\kappa)\).  The coarsened set \(\Theta_{\mathrm{bd,coarse}}(A P,e,\kappa)\) is defined by summing the retained-memory observed equations over \(Z_1\) inside \(D_1=0\), keeping the original \(e_2(z\mid x,z_1,d_1)\) inside the summed equations.  Let \(\Theta_{\mathrm{mem}}^{\mathrm{parent}}(P,e)\) denote the parent v2 sharp memory-retaining identified set under the same observed law and assignment law with the additional first-stage one-sided restriction \(q_F(x)=0\) for every \(x\).

A finite retained-memory system is any finite-support extension of this LP with finitely many retained assignment-history branch equations, the same bounded-outcome contribution variables, and the same known assignment probabilities; the two-stage \((M,H)\) equations below must appear as one active submodel.  Its endpoint \(b\in\{\inf,\sup\}\) is the lower or upper scalar LP endpoint for the target contrast after choosing a retained-memory cell \(x\).

For the conjectured analytic formula, define unnormalized retained-memory response-contribution summaries in each \(x\) cell.  In the mixed branch \((Z_1,D_1)=(0,0)\),
\[
M_0(x)=\Pr(D_1=0\mid Z_1=0,X=x)\E[Y\mid Z_1=0,D_1=0,Z_2=0,X=x],
\]
\[
M_\rho(x)=\Pr(D_1=0\mid Z_1=0,X=x)\Pr(D_2=1\mid Z_1=0,D_1=0,Z_2=1,X=x),
\]
\[
M_\gamma(x)=\Pr(D_1=0\mid Z_1=0,X=x)
\E[Y\one\{D_2=1\}\mid Z_1=0,D_1=0,Z_2=1,X=x].
\]
In the contaminated branch \((Z_1,D_1)=(1,0)\), define \(H_0(x),H_\rho(x),H_\gamma(x)\) analogously.  Let \(a_s=(\mu_{s,0},\rho_s,\gamma_s)\in[0,1]^3\) denote a stratum's baseline mean, second-stage response rate, and observed responder contribution, with \(0\le\gamma_s\le\rho_s\le1\).  The memory equations have the schematic form
\[
M=q_C a_C+q_N a_N,\qquad H=q_N a_N+q_F a_F,
\]
coordinatewise for \(M=(M_0,M_\rho,M_\gamma)\) and \(H=(H_0,H_\rho,H_\gamma)\).  The parent v2 formula is the special case \(q_F=0\), where \(H\) is a pure never-taker contribution.

\begin{verbatim}
qid=pid_dynamic_iv_compliance
specialization=v3
P=P_{Y,D1,D2,Z1,Z2,X}, a finite-support observed law with Y in [0,1]
theta=theta_C0^(2)=E[Y(0,1)-Y(0,0) | D1(1)=1,D1(0)=0]
identifying restrictions=R_2stageIV+memory+bd: consistency, exclusion,
  randomized Z1 within X, sequentially randomized Z2 given (X,Z1,D1),
  positivity, one-sided second-stage compliance, no direct assignment-memory
  effect in the D1=0 state, bounded first-stage defier mass q_F(x)<=kappa(x),
  and nonnegative induced C,N,A,F first-stage stratum shares
bounding functional=[theta_bd_lower(P,e,kappa), theta_bd_upper(P,e,kappa)],
  the sharp interval over finite first-stage strata C,N,A,F, second-stage
  response types, and bounded outcome contribution tables retaining Z1
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite support and bounded outcomes]\label{ass:finite-bounded}
\(X\) has finite support; \(Z_1,Z_2,D_1,D_2\in\{0,1\}\); and \(0\le Y(d_1,d_2)\le1\) almost surely for all \(d_1,d_2\in\{0,1\}\).
\end{assumption}

\begin{assumption}[First-stage random encouragement]\label{ass:first-rand}
For every \(x\) used in the target, \(0<p_1(1\mid x)<1\), and \(Z_1\) is independent of first-stage stratum, second-stage response types, and potential outcomes conditional on \(X=x\).
\end{assumption}

\begin{assumption}[Sequential second-stage random encouragement]\label{ass:second-rand}
For every reachable \((x,z_1,d_1)\), \(0<e_2(1\mid x,z_1,d_1)<1\), and \(Z_2\) is independent of the latent first-stage stratum, second-stage response type, and potential outcomes conditional on \((X,Z_1,D_1)=(x,z_1,d_1)\).
\end{assumption}

\begin{assumption}[Consistency and exclusion]\label{ass:consistency}
The realized treatments satisfy \(D_1=D_1(Z_1)\) and \(D_2=D_2^{S,D_1}(Z_2)\).  The realized outcome is \(Y=Y(D_1,D_2)\), and \(Z_1,Z_2\) affect \(Y\) only through \(D_1,D_2\).
\end{assumption}

\begin{assumption}[Second-stage one-sided compliance]\label{ass:stage2-one-sided}
For each first-stage stratum \(s\) and first-stage treatment \(d_1\), second-stage compliance in the \(D_1=0\) branch is one-sided:
\[
D_2^{s,0}(0)=0\le D_2^{s,0}(1)
\]
almost surely.  No one-sided restriction is imposed on first-stage compliance beyond Assumption~\ref{ass:bounded-defiers}.
\end{assumption}

\begin{assumption}[Bounded first-stage defiers]\label{ass:bounded-defiers}
For every target cell \(x\), the first-stage defier share \(q_F(x)=\Pr(S=F\mid X=x)\) satisfies \(0\le q_F(x)\le\kappa(x)\), where \(\kappa(x)\) is known and \(0\le\kappa(x)<1\).  The feasible defier-share set also satisfies \(q_C(x)=\Delta_D(x)+q_F(x)>0\), \(q_N(x)=\Pr(D_1=0\mid Z_1=1,X=x)-q_F(x)\ge0\), and \(q_A(x)=\Pr(D_1=1\mid Z_1=0,X=x)-q_F(x)\ge0\).
\end{assumption}

\begin{assumption}[No direct assignment-memory effect in the untreated first-stage state]\label{ass:no-memory-direct}
Within \(X=x\), first-stage stratum \(s\), and first-stage treatment \(D_1=0\), the second-stage response law \(D_2^{s,0}(z_2)\) and potential outcomes \(Y(0,d_2)\) do not depend directly on whether the retained label was \(Z_1=0\) or \(Z_1=1\).
\end{assumption}

\begin{assumption}[Observational compatibility]\label{ass:compatible}
The observed law \(P\), adaptive assignment law \(e\), and defier budget \(\kappa\) are in the maintained model: \(\mathcal{L}_{\mathrm{bd}}(P,e,\kappa)\) is nonempty.  Consequently all endpoint functionals in the main results optimize over nonempty feasible sets.
\end{assumption}

\begin{assumption}[Cellwise covariate separability]\label{ass:cellwise}
The latent-response restrictions and bounded-defier budgets are imposed separately within each \(X=x\) cell, with no cross-\(x\) monotonicity, smoothness, rank, or shape restriction.
\end{assumption}

\begin{assumption}[Interior memory contrast]\label{ass:interior-memory}
For the strict-gain claim, at least one \(x\) has \(q_C(x)>0\), positive feasible never-taker mass \(q_N(x)>0\) for some feasible \(q_F(x)\), and distinct second-stage assignment probabilities \(e_2(1\mid x,0,0)\ne e_2(1\mid x,1,0)\).  The retained-memory and coarsened endpoint problems have finite optimal solutions in the relative interior of the maintained support face.
\end{assumption}

\section{Main results}
\begin{theorem}[Bounded-defier nesting and parent corner]\label{thm:corner-nesting}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:compatible}, if \(0\le\kappa_1(x)\le\kappa_2(x)\) for all \(x\), then
\[
\Theta_{\mathrm{bd}}(P,e,\kappa_1)\subseteq \Theta_{\mathrm{bd}}(P,e,\kappa_2).
\]
If \(\kappa(x)=0\) for all \(x\), then \(\mathcal{L}_{\mathrm{bd}}(P,e,0)\) is exactly the parent v2 one-sided first-stage memory polytope after deleting the zero-mass defier stratum, and
\[
\Theta_{\mathrm{bd}}(P,e,0)=\Theta_{\mathrm{mem}}^{\mathrm{parent}}(P,e).
\]
\end{theorem}
\paragraph{Why this is new and worth studying.}
The closest in-repo result is the parent \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v2}, whose sharp response-contribution formula assumes \(q_F=0\).  The theorem is routine feasible-set algebra, but it certifies that v3 is a genuine generalization rather than a pivot.  The concrete consumer is the v2 derivation itself: Stage 0 can use this theorem as the mandatory reduction showing that any bounded-defier formula has the accepted parent theorem as its zero-defier corner.

\begin{conjecture}[Defier-trimmed response-contribution prism]\label{conj:defier-prism}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:cellwise}, fix a target cell \(x\).  Let \(\mathcal{F}_x(P,\kappa)\) be the observable interval of feasible defier shares \(f=q_F(x)\) satisfying
\[
0\le f\le\kappa(x),\quad q_C(f)=\Delta_D(x)+f>0,\quad
q_N(f)=\Pr(D_1=0\mid Z_1=1,X=x)-f\ge0,\quad
q_A(f)=\Pr(D_1=1\mid Z_1=0,X=x)-f\ge0.
\]
For each \(f\in\mathcal{F}_x(P,\kappa)\), define the defier-trimmed prism
\[
\mathcal{P}_x(f)=
\left\{(c_0,c_\rho,c_\gamma):
\begin{array}{l}
M=q_C(f)(c_0,c_\rho,c_\gamma)+q_N(f)n,\\
H=q_N(f)n+f\,d,\\
n,d\in[0,1]^3,\ 0\le n_\gamma\le n_\rho\le1,\ 0\le d_\gamma\le d_\rho\le1,\\
0\le c_\gamma\le c_\rho\le1,\ 0\le c_0\le1
\end{array}
\right\}.
\]
Then the sharp cellwise retained-memory identified set for
\(\theta_{C,0}^{(2)}(x)\) is
\[
\bigcup_{f\in\mathcal{F}_x(P,\kappa)}
\left\{
c_\gamma+\delta-c_0:
(c_0,c_\rho,c_\gamma)\in\mathcal{P}_x(f),\
0\le \delta\le1-c_\rho
\right\}.
\]
Under Assumption~\ref{ass:cellwise}, the aggregate sharp set is obtained by optimizing the complier-weighted sum over the product of these cellwise prism projections, with weights \(w_C(x)\) evaluated at the same feasible defier shares.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
The closest published sensitivity paper is \citet{Noack2021}, which already derives sharp static bounds indexed by defier share, so the epsilon-gap must be narrower and more structural: the conjecture adds a retained dynamic assignment-memory equation whose branch contamination is governed by \(H=q_Nn+fd\), not by a single-period Wald decomposition.  \citet{DeChaisemartin2017} and \citet{DahlHuberMellace2023} relax monotonicity for static IV estimands, but their objects do not contain a retained dynamic assignment label whose branch changes from pure never-taker to never-taker/defier mixture.  Resolving this conjecture would give \citet{SojitraSyrgkanis2024}-style dynamic IV applications a nonparametric sensitivity interval when one-sided noncompliance is doubtful.

\begin{conjecture}[Generic defier-budget threshold for strict memory gain]\label{conj:phase-transition}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:interior-memory}, fix an endpoint \(b\in\{\inf,\sup\}\) and a finite retained-memory system whose active branch equations include the two-stage \((M,H)\) system above as a submodel.  There is an observable threshold \(\kappa^\dagger_b(P,e,x)>0\), equal to the smallest defier share for which the \(b\)-endpoint solution of the coarsened summed-equation relaxation can be lifted to a retained-memory feasible table satisfying \(H=q_Nn+fd\), the nonnegativity constraints for \(q_C,q_N,q_A,q_F\), and \(0\le d_\gamma\le d_\rho\le1\).  On a relatively open set of laws this threshold has the following property.  If \(\kappa(x)<\kappa^\dagger_b(P,e,x)\), then
\[
\Theta_{\mathrm{bd}}(P,e,\kappa)\subsetneq
\Theta_{\mathrm{bd,coarse}}(A P,e,\kappa)
\]
because the \(b\)-endpoint of the prism projection is pulled inward by the retained \(H\)-branch restriction.  If \(\kappa(x)\ge\kappa^\dagger_b(P,e,x)\), then the defier component can absorb that retained-branch restriction for endpoint \(b\), and the corresponding memory endpoint equals the coarsened endpoint.  In the two-stage submodel at \(\kappa=0\), this generic threshold statement reduces to the parent v2 strict memory-gain proposition.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
\citet{BugniGaoObradovicVelez2024} show that assignment probabilities enter static imperfect-compliance bounds under covariate-adaptive randomization, and \citet{DuarteFinkelsteinKnoxMummoloShpitser2024} can numerically search sharp bounds in discrete settings.  Neither paper identifies an observable sensitivity threshold at which remembered randomization changes from an active identifying restriction to an absorbable perturbation across a class of retained-memory LPs.  The concrete consumer is \citet{ArtmanBhattacharyaErtefaieLynchMcKayJohnson2024}: SMART analyses with partial compliance would be able to report how much defiance is needed to eliminate the memory gain.

\section{Sanity-check corollaries}
\begin{corollary}[Zero-defier reduction to parent]\label{cor:parent}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:compatible}, if \(\kappa(x)=0\) for all \(x\), then Conjecture~\ref{conj:defier-prism} collapses to the parent v2 response-contribution formula: \(f=0\), \(H=q_N n\), and
\[
(c_0,c_\rho,c_\gamma)=\frac{M-H}{q_C}.
\]
\end{corollary}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:compatible} plus \(\kappa=0\), the reduction is algebraic: the contaminated branch becomes pure never-taker, so the prism has a singleton never-taker subtraction coordinate and the only remaining freedom is the parent nonresponder outcome mass.

\begin{corollary}[No retained-memory difference, no strict gain]\label{cor:no-memory-diff}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:compatible}, if \(e_2(1\mid x,0,0)=e_2(1\mid x,1,0)\) and the retained \(Z_1\) label contributes no distinct \(D_1=0\) branch equations within every target cell, then the strict-gain mechanism in Conjecture~\ref{conj:phase-transition} cannot operate in that cell.
\end{corollary}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:compatible}, the reduction follows because the memory and coarsened observed-equation systems impose the same branch restrictions once the retained label carries no distinct assignment or moment equation.

\section{Proof-sketch route}
The verification route is finite-dimensional convex geometry.  First, write the retained-memory problem cellwise using unnormalized contribution variables, so the two key branch equations are \(M=q_C a_C+q_N a_N\) and \(H=q_N a_N+q_F a_F\), with \(q_A(f)\ge0\) carried as a first-stage feasibility constraint even though always-takers do not enter the \(D_1=0\) branch.  Theorem~\ref{thm:corner-nesting} follows by inclusion of feasible sets as \(\kappa\) expands and by deleting the zero-mass defier stratum at \(\kappa=0\).  For Conjecture~\ref{conj:defier-prism}, eliminate \(q_C,q_N,q_A\) as affine functions of \(f=q_F\), project the finite response-type polytope onto \((c_0,c_\rho,c_\gamma)\), and check that bounded \(a_F\) contributes exactly the displayed trim interval for \(q_Na_N\).  For Conjecture~\ref{conj:phase-transition}, treat the coarsened endpoint optimizer as a parametric LP and compute the minimal \(f\) for which a retained-memory lift satisfies the \(H\)-branch equations and all stratum-share inequalities; the two-stage binary-outcome witness should be the first boundary case, while the generic statement follows by LP basis stability on each active face.

\section{Honest scope flags}
Theorem~\ref{thm:corner-nesting} is expected to be routine.  Conjectures~\ref{conj:defier-prism} and \ref{conj:phase-transition} are not yet proved and are the flagship content.  The v1 draft omitted the always-taker nonnegativity constraint \(q_A(f)\ge0\); v2 adds it to the formal setup, Assumption~\ref{ass:bounded-defiers}, and Conjecture~\ref{conj:defier-prism}.  The main risk is that second-stage response-type compatibility adds facets to the prism beyond the coordinatewise inequalities displayed in Conjecture~\ref{conj:defier-prism}; if so, the correct result should replace the simple prism with a smaller projected polytope, not return to the parent one-sided formula.  The no-direct-memory assumption remains strong and is inherited from the parent as part of the estimand convention.  This upgrade deliberately does not revive the burned v1 Bellman/non-pasteability seed.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial flagship-upgrade draft generalizing the parent one-sided memory bound to bounded first-stage defiers; prior verdict: none.
\item v2 (revise) -- added the missing always-taker nonnegativity constraint, thickened the static defier-sensitivity comparison, and strengthened the strict-gain threshold into a generic retained-memory LP threshold conjecture; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Angrist, Imbens, and Rubin(1996)]{AngristImbensRubin1996}
Joshua D. Angrist, Guido W. Imbens, and Donald B. Rubin.
\newblock Identification of causal effects using instrumental variables.
\newblock \emph{Journal of the American Statistical Association}, 91(434):444--455, 1996.
\newblock \url{https://doi.org/10.1080/01621459.1996.10476902}.

\bibitem[Artman et~al.(2024)]{ArtmanBhattacharyaErtefaieLynchMcKayJohnson2024}
William J. Artman, Indrabati Bhattacharya, Ashkan Ertefaie, Kevin G. Lynch, James R. McKay, and Brent A. Johnson.
\newblock A marginal structural model for partial compliance in SMARTs.
\newblock \emph{Annals of Applied Statistics}, 18(2):905--921, 2024.
\newblock \url{https://doi.org/10.1214/21-AOAS1586}.

\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Alexander Balke and Judea Pearl.
\newblock Bounds on treatment effects from studies with imperfect compliance.
\newblock \emph{Journal of the American Statistical Association}, 92(439):1171--1176, 1997.
\newblock \url{https://doi.org/10.1080/01621459.1997.10474074}.

\bibitem[Bugni et~al.(2024)]{BugniGaoObradovicVelez2024}
Federico A. Bugni, Mengsi Gao, Filip Obradovic, and Amilcar Velez.
\newblock Identification and inference on treatment effects under covariate-adaptive randomization and imperfect compliance.
\newblock \emph{arXiv:2406.08419}, 2024.
\newblock \url{https://arxiv.org/abs/2406.08419}.

\bibitem[Dahl, Huber, and Mellace(2023)]{DahlHuberMellace2023}
Christian M. Dahl, Martin Huber, and Giovanni Mellace.
\newblock It is never too LATE: A new look at local average treatment effects with or without defiers.
\newblock \emph{The Econometrics Journal}, 26(3):378--404, 2023.
\newblock \url{https://doi.org/10.1093/ectj/utad013}.

\bibitem[de Chaisemartin(2017)]{DeChaisemartin2017}
Clement de Chaisemartin.
\newblock Tolerating defiance? Local average treatment effects without monotonicity.
\newblock \emph{Quantitative Economics}, 8(2):367--396, 2017.
\newblock \url{https://doi.org/10.3982/QE601}.

\bibitem[Duarte et~al.(2024)]{DuarteFinkelsteinKnoxMummoloShpitser2024}
Guilherme Duarte, Noam Finkelstein, Dean Knox, Jonathan Mummolo, and Ilya Shpitser.
\newblock An automated approach to causal inference in discrete settings.
\newblock \emph{Journal of the American Statistical Association}, 119(547):1778--1793, 2024.
\newblock \url{https://doi.org/10.1080/01621459.2023.2216909}.

\bibitem[Kitagawa(2015)]{Kitagawa2015}
Toru Kitagawa.
\newblock A test for instrument validity.
\newblock \emph{Econometrica}, 83(5):2043--2063, 2015.
\newblock \url{https://doi.org/10.3982/ECTA11974}.

\bibitem[Mourifie and Wan(2017)]{MourifieWan2017}
Ismael Mourifie and Yuanyuan Wan.
\newblock Testing local average treatment effect assumptions.
\newblock \emph{Review of Economics and Statistics}, 99(2):305--313, 2017.
\newblock \url{https://doi.org/10.1162/REST_a_00622}.

\bibitem[Noack(2021)]{Noack2021}
Claudia Noack.
\newblock Sensitivity of LATE estimates to violations of the monotonicity assumption.
\newblock \emph{arXiv:2106.06421}, 2021.
\newblock \url{https://arxiv.org/abs/2106.06421}.

\bibitem[Sojitra and Syrgkanis(2024)]{SojitraSyrgkanis2024}
Ravi B. Sojitra and Vasilis Syrgkanis.
\newblock Dynamic local average treatment effects.
\newblock \emph{arXiv:2405.01463}, 2024.
\newblock \url{https://arxiv.org/abs/2405.01463}.

\bibitem[Swanson et~al.(2018)]{SwansonHernanMillerRobinsRichardson2018}
Sonja A. Swanson, Miguel A. Hernan, Matthew Miller, James M. Robins, and Thomas S. Richardson.
\newblock Partial identification of the average treatment effect using instrumental variables: Review of methods for binary instruments, treatments, and outcomes.
\newblock \emph{Journal of the American Statistical Association}, 113(522):933--947, 2018.
\newblock \url{https://doi.org/10.1080/01621459.2018.1434530}.
\end{thebibliography}

\end{document}
