% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_continuous\_iv\_no\_monotonicity, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_continuous\_iv\_no\_monotonicity} / \texttt{v1}%
  \\ \large\textit{Continuous-IV derivative-feasibility certificates under bounded monotonicity violations}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form partial-identification anchor.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional}).
\]
Here \(\texttt{qid}=\texttt{pid\_continuous\_iv\_no\_monotonicity}\) and \(\texttt{specialization}=\texttt{v1}\).  \(P\) is the observable law of \((Y,D,Z)\), where \(Y\in[0,1]\), \(D\in\{0,1\}\), and \(Z\in[0,1]\) has a density bounded away from zero and infinity.  Write \(p(z)=\Pr(D=1\mid Z=z)\), \(g_y(z)=\E[\one\{Y\le y,D=1\}\mid Z=z]\), and \(h_y(z)=\E[\one\{Y\le y,D=0\}\mid Z=z]\), with weak derivatives \(p'\), \(g_y'\), and \(h_y'\).  The parameter \(\theta\) is the feasibility/refutability status of a calibrated continuous-IV monotonicity-violation model, represented by the indicator
\[
\theta(P,b)=\one\{(p',g',h')\in K_b^{\mathrm{proj}}\},
\]
where \(b\in L^1_+([0,1])\) is a known envelope on the negative first-stage response density and \(K_b^{\mathrm{proj}}\) is the projection of an explicit closed linear feasibility system \(H_b\).  An element of \(H_b\) consists of nonnegative finite Borel measures \(\mu^+_{dz,dy}\) and \(\mu^-_{dz,dy}\) on instrument--outcome pairs for up- and down-switchers, baseline subdistribution curves \(G_{d,z}(y)\), and response densities \(a,d\in L^1_+([0,1])\), subject to the endpoint, CDF-in-\(y\), level-recursion, and envelope constraints stated in Assumptions~\ref{ass:subcdf} and~\ref{ass:constructive}.  The projection map \(\Pi(H_b)\) returns the observable derivative process \(r(P)=(p',g',h')\), and \(K_b^{\mathrm{proj}}=\overline{\Pi(H_b)}\).  The ambient space is
\[
\mathbb X=\mathcal M([0,1])\times \mathcal M([0,1]_z\times[0,1]_y)^2
\]
with the bounded-Lipschitz norm \(\|\cdot\|_{\mathrm{BL}}\); its dual unit ball is the set of test triples \(\varphi=(\varphi_p,\varphi_g,\varphi_h)\) with \(\|\varphi\|_{\mathrm{BL}^\ast}\le1\).  The identifying restrictions are instrument independence, exclusion, bounded outcomes, differentiability of the conditional distribution processes, a signed Jordan decomposition \(dD(z)=dD_+(z)-dD_-(z)\) with \(dD_-\) dominated by \(b(z)\,dz\), the constructive constraints \(H_b\), and full level matching to \(P_{Y,D\mid Z=z}\).  The bounding functional is the support-function feasibility gap
\[
\Delta_b(P)=\sup_{\|\varphi\|_{\mathrm{BL}^\ast}\le1}\{\langle\varphi,(p',g',h')\rangle-\sigma_{K_b^{\mathrm{proj}}}(\varphi)\},
\]
where \(\sigma_{K_b^{\mathrm{proj}}}(\varphi)=\sup_{r\in K_b^{\mathrm{proj}}}\langle\varphi,r\rangle\); the model is feasible iff \(\Delta_b(P)\le0\).  The fixed-\(b\) object is not treated as a cone because the bound \(c_-\le b\) is not homogeneous under scaling.

\begin{abstract}
This proposal pivots from directly bounding the continuous-IV LATE to the prerequisite feasibility problem: which observable derivative processes can be generated by a scalar continuous instrument when local violations of monotonicity are bounded by a known envelope.  Discrete-IV work such as Kitagawa's monotonicity test produces finite conditional-distribution inequalities, while generalized-IV work such as Chesher--Rosen gives broad sharp-set machinery; a scalar continuous instrument with a fixed downward-response envelope creates a sharper function-space compatibility problem because one latent response path must generate all infinitesimal margins.  The flagship conjecture is that feasibility is equivalent to membership in the constructive projection \(K_b^{\mathrm{proj}}\) with a bounded-Lipschitz support-function separation certificate, and that this projection is strictly smaller than an internal locally pasted derivative-envelope relaxation on an open class of observables.  A zero-envelope theorem should recover the Heckman--Vytlacil monotone threshold-crossing derivative restrictions as the corner case.  If resolved, the result would give applied continuous-IV researchers a falsification and calibration diagnostic before reporting any bounded-violation LATE interval.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Continuous instruments are usually interpreted through a monotone threshold-crossing model: a marginal change in the instrument shifts some units into treatment and never shifts units out.  The topic here deliberately relaxes that restriction by allowing a known amount of local nonmonotone response mass.  Before one can claim sharp LATE bounds under such a relaxation, there is a more basic question: does the observed derivative process \((p',g',h')\) even come from one latent response path obeying the envelope?  Without a feasibility theorem, a proposed sharp set may optimize over locally plausible derivative cells that cannot be pasted into any full-data law.

\paragraph{The main finding (proposed).}
The flagship claim is Conjecture~\ref{conj:feasible}: the bounded-violation continuous-IV model is nonempty if and only if the observable derivative process belongs to \(K_b^{\mathrm{proj}}\), the closure of an explicit linear projection system over signed response-path subdistribution measures with negative variation dominated by \(b(z)\,dz\).  Theorem~\ref{thm:necessary} records the explicit all-cell local signed-measure equations that every feasible process must satisfy, and Theorem~\ref{thm:zero} checks that the feasible set collapses to the standard monotone Heckman--Vytlacil derivative restriction when \(b=0\).  Conjecture~\ref{conj:strict} is a secondary internal separation claim: the pointwise derivative-envelope relaxation \(\mathcal L_b\), obtained by optimizing adjacent cells independently, is not sharp because global response-path compatibility cuts away an open set of locally feasible observables and admits a support-function rejection certificate.

\paragraph{What is new.}
The novelty kernel is an observable derivative-process feasibility theorem, not another LATE formula.  \citet{Kitagawa2015} characterizes testable implications for discrete IV validity and monotonicity through finite inequalities, \citet{ChesherRosen2017} characterize generalized IV identified sets through conditional moment restrictions, and \citet{MogstadTorgovitskyWalters2021} and \citet{JiangSun2023PartialMonotonicityTest} develop partial-monotonicity checks for multi-instrument settings.  The epsilon-gap is that none of these papers delivers the finite-threshold support-function certificate for a scalar continuous instrument with a fixed function-valued bound \(b(z)\) on negative response density, where infinitesimal inequalities must integrate into one bounded-variation binary path.  The proposed strictness result is deliberately positioned as an internal CausalSmith comparison against \(\mathcal L_b\), not as a claim that Kennedy--Lorch--Small, Kilbertus--Kusner--Silva, or Gunsilius publish that exact local-pasting estimator.

\paragraph{How it positions in the literature.}
This is a partial-identification and specification-testing proposal for IV models with heterogeneous treatment effects.  It is adjacent to exact LATE/MTE identification in \citet{ImbensAngrist1994}, \citet{Vytlacil2002}, and \citet{HeckmanVytlacil2005}; to monotonicity-relaxation work in \citet{Klein2010}, \citet{DeChaisemartin2017}, and \citet{MogstadTorgovitskyWalters2021}; and to partial-ID/testability results in \citet{BalkePearl1997}, \citet{Kitagawa2015}, and \citet{MogstadSantosTorgovitsky2018}.  The proposal's distinctive object is a continuum-indexed derivative feasible set, which is closer to a sharp refutability theorem than to a plug-in sensitivity formula.

\paragraph{Implications for the community.}
The concrete downstream consumer is the continuous-instrument LIV workflow of \citet{KennedyLorchSmall2019}: before estimating or plotting a local-IV curve, researchers could report whether their observed derivative process is inside \(K_b^{\mathrm{proj}}\) for calibrated envelope values and use the support-function certificate to identify where the monotonicity-violation model fails.  The same feasibility diagnostic would be a front-end check for MTE policy bounds in \citet{MogstadSantosTorgovitsky2018}.

\paragraph{How research benefits from the conclusion.}
Researchers should check support-function feasibility of a calibrated monotonicity-violation model before treating continuous-IV derivative ratios or bounded-violation LATE intervals as causally interpretable.

\section{Related work}
\citet{ImbensAngrist1994} show that LATE is point identified for a binary instrument under independence, exclusion, and monotonicity; this proposal studies whether an observable continuous-IV process can satisfy a calibrated relaxation of that monotonicity restriction.  \citet{Vytlacil2002} proves that the LATE monotonicity condition is equivalent to a latent-index threshold-crossing model; the zero-envelope feasible set in Theorem~\ref{thm:zero} is designed to recover that threshold-crossing corner.  \citet{HeckmanVytlacil2005} develop the LIV/MTE derivative formula under threshold crossing; the present proposal supplies a feasibility screen for the derivative processes to which that formula is often applied.  \citet{Klein2010} shows that local departures from monotonicity contaminate monotonicity-based MTE, ATE, and LATE estimands; the current proposal asks when such departures are observationally feasible under a known envelope, not how a maintained formula is biased.  \citet{DeChaisemartin2017} obtains LATE-like interpretations without full monotonicity by adding restrictions linking compliers and defiers; here defier outcome heterogeneity is unrestricted, but the amount of negative response density is calibrated.  \citet{BalkePearl1997} gives sharp finite-IV bounds under imperfect compliance; its finite latent-type geometry motivates, but does not solve, the continuous response-path feasible set.  \citet{Kitagawa2015} derives finite conditional-distribution inequalities that test IV validity including monotonicity in discrete heterogeneous-effect models; it is the closest published comparator for Conjecture~\ref{conj:feasible}.  \citet{ChesherRosen2017} give generalized-IV sharp identified-set machinery for incomplete structural models; the epsilon-gap is that their abstract conditional-moment set does not expose the finite-threshold derivative certificate or the path-pasting obstruction created by a fixed \(b(z)\) envelope.  \citet{MachadoShaikhVytlacil2019} characterize sign identification under binary-IV restrictions; this proposal instead targets a continuous-IV feasibility/refutability object.  \citet{MogstadSantosTorgovitsky2018} formulate policy-relevant treatment-effect bounds through MTE restrictions; \(K_b^{\mathrm{proj}}\) would provide a calibrated first-stage admissibility condition for those exercises when monotonicity is suspect.  \citet{MogstadTorgovitskyWalters2021} give necessary and sufficient conditions for positive-weight 2SLS interpretation under partial monotonicity with multiple instruments; the epsilon-gap is scalar continuous-IV derivative-path compatibility.  \citet{Mountjoy2024} proposes vector monotonicity for multiple instruments and reinforces the point that useful relaxations should keep the causal-weighting question explicit.  \citet{JiangSun2023PartialMonotonicityTest} extends testing to partial instrument monotonicity for multidimensional instruments; Conjecture~\ref{conj:feasible} is the scalar continuous derivative-envelope analogue.  \citet{Yap2022} studies sensitivity of policy-relevant treatment parameters to monotonicity violations; the current proposal uses an observable derivative-process envelope rather than a scalar defier-to-complier outcome restriction.  \citet{KilbertusKusnerSilva2020} develop algorithms for causal bounds in general continuous IV models; they are close on the continuous-observable computational side, but do not impose or certify a scalar derivative-path monotonicity-violation envelope.  \citet{Gunsilius2019} develops path-sampling bounds for continuous IV models; that path-space perspective is adjacent to \(K_b^{\mathrm{proj}}\), but the paper does not give a fixed-\(b\) binary-treatment derivative-process feasibility certificate.

In-repo prior art is closest in four banked CausalSmith proposal families.  \texttt{pid\_late\_bounded\_defiers\_one\_sided\_compliance} left binary-IV bounded-defier sharpness open and a reviewer required all four observed cells; this proposal builds the all-cell requirement into the derivative process \((p',g',h')\).  \texttt{pid\_ordinal\_late\_partial\_defiers\_v1} left pairwise-versus-global adjacent-bound strictness as a witness problem; Conjecture~\ref{conj:strict} is the continuous analogue, but phrased as a support-function feasibility separation.  \texttt{pid\_dose\_response\_iv\_v1} flagged the same pasting theorem risk from adjacent-rank IV bounds; here the pasting theorem is the object being proposed.  \texttt{pid\_dynamic\_iv\_compliance\_v1} was downgraded because a generic finite latent-response LP gap was below field tier; the present angle ties the gap to Kitagawa-style testable implications and continuous-IV derivative paths.

\section{Formal setup}
Let \(Z\in[0,1]\), \(D\in\{0,1\}\), and \(Y\in[0,1]\).  For every \(z\), let \(D(z)\) denote the potential treatment status and let \(Y(1),Y(0)\) denote bounded potential outcomes; exclusion gives \(Y=Y(D(Z))\).  For each threshold \(y\in[0,1]\), define observable conditional processes
\[
p(z)=\Pr(D=1\mid Z=z),\qquad
g_y(z)=\E[\one\{Y\le y,D=1\}\mid Z=z],\qquad
h_y(z)=\E[\one\{Y\le y,D=0\}\mid Z=z].
\]
Assume these processes are absolutely continuous in \(z\), with weak derivatives \(p'\), \(g_y'\), and \(h_y'\).  A latent response path of bounded variation has a Jordan decomposition into positive and negative response measures \(dD_+(z)\) and \(dD_-(z)\).  In density form write \(c_+(z)\,dz=dD_+(z)\) and \(c_-(z)\,dz=dD_-(z)\), so \(p'(z)=c_+(z)-c_-(z)\).  The envelope restriction is \(0\le c_-(z)\le b(z)\) almost everywhere.

The full observable derivative process is \(r(P)=(p',g',h')\), where \(g'\) and \(h'\) mean the collections \(\{g_y':y\in[0,1]\}\) and \(\{h_y':y\in[0,1]\}\).  To make the support-function statement non-tautological, encode \(r(P)\) as an element of
\[
\mathbb X=\mathcal M([0,1])\times \mathcal M([0,1]_z\times[0,1]_y)^2
\]
by pairing \(p'\) with signed measures whose distribution functions in \(y\) are \(g_y'\) and \(h_y'\).  Equip \(\mathbb X\) with the bounded-Lipschitz norm \(\|\cdot\|_{\mathrm{BL}}\), and let \(\mathbb X^\ast_{\mathrm{BL},1}\) be its dual unit ball.  Let \(H_b\) be the closed linear feasibility system over variables \((a,d,\alpha^+_1,\alpha^+_0,\alpha^-_1,\alpha^-_0,G_{1,z},G_{0,z})\) satisfying Assumptions~\ref{ass:subcdf} and~\ref{ass:constructive}.  Define the constructive feasible set
\[
K_b^{\mathrm{proj}}=\overline{\{\Pi(a,d,\alpha,G):(a,d,\alpha,G)\in H_b\}}^{\|\cdot\|_{\mathrm{BL}}},
\]
where \(\Pi\) maps latent intensities to the observable equations in Theorem~\ref{thm:necessary}.  This set is convex but not homogeneous when \(b\) is fixed.  Let \(\mathcal L_b\) be the pointwise relaxation obtained by imposing all local derivative equations and inequalities at each \(z\) while dropping the requirement that the same response path and outcome distribution paste across different \(z\)'s.  For any bounded-Lipschitz linear functional \(\varphi\), define the support function \(\sigma_{K_b^{\mathrm{proj}}}(\varphi)=\sup_{r\in K_b^{\mathrm{proj}}}\langle\varphi,r\rangle\) and the support-function feasibility gap
\[
\Delta_b(P)=\sup_{\varphi\in\mathbb X^\ast_{\mathrm{BL},1}}\{\langle\varphi,r(P)\rangle-\sigma_{K_b^{\mathrm{proj}}}(\varphi)\}.
\]
The intended separation theorem is \(r(P)\in K_b^{\mathrm{proj}}\) if and only if \(\Delta_b(P)\le0\).

\begin{quote}
\begin{verbatim}
Locked parameters:
qid = pid_continuous_iv_no_monotonicity
specialization = v1
observable distribution P = law(Y,D,Z), Y in [0,1], D binary, Z in [0,1]
parameter theta(P,b) = 1{(p',g',h') in K_b^proj}
identifying restrictions = IV independence/exclusion, bounded outcomes,
  differentiable conditional distribution processes, one bounded-variation
  binary response path D(z), Jordan negative variation c_-(z) <= b(z),
  constructive system H_b, and full level matching to P_{Y,D|Z=z}
bounding functional = support-function feasibility gap Delta_b(P) for K_b^proj
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Continuous IV law]\label{ass:law}
\(Z\) has support \([0,1]\) with a density bounded away from zero and infinity, \(D\in\{0,1\}\), and \(Y\in[0,1]\).
\end{assumption}

\begin{assumption}[Instrument validity and exclusion]\label{ass:iv}
\(Z\) is independent of the full latent response path \(\{D(z):z\in[0,1]\}\) and the potential outcomes \((Y(1),Y(0))\), and \(Y=Y(D(Z))\).
\end{assumption}

\begin{assumption}[Derivative process regularity]\label{ass:regular}
The functions \(p(z)\), \(g_y(z)\), and \(h_y(z)\) are absolutely continuous in \(z\), uniformly over \(y\), and their weak derivatives define a finite signed vector measure \(r(P)=(p',g',h')\).
\end{assumption}

\begin{assumption}[Bounded-variation response path]\label{ass:bv}
The binary path \(z\mapsto D(z)\) is of bounded variation almost surely and has response measures \(dD_+\) and \(dD_-\) whose population densities are \(c_+\) and \(c_-\), with \(p'=c_+-c_-\).
\end{assumption}

\begin{assumption}[Calibrated negative-response envelope]\label{ass:envelope}
The known envelope \(b\in L^1_+([0,1])\) satisfies \(0\le c_-(z)\le b(z)\) almost everywhere.
\end{assumption}

\begin{assumption}[Full level matching]\label{ass:levels}
The same full-data law that generates \(r(P)\) also reproduces the full conditional distribution \(P_{Y,D\mid Z=z}\) for every \(z\), including \(p(z)\), \(g_y(z)\), and \(h_y(z)\), not only their derivatives.
\end{assumption}

\begin{assumption}[Subdistribution structure in the outcome threshold]\label{ass:subcdf}
For almost every \(z\), each map \(y\mapsto \alpha^+_{1y}(z)\), \(y\mapsto \alpha^+_{0y}(z)\), \(y\mapsto \alpha^-_{1y}(z)\), and \(y\mapsto \alpha^-_{0y}(z)\) is a right-continuous nondecreasing subdistribution function on \([0,1]\), has value \(0\) at \(y=0-\), and has endpoint masses \(\alpha^+_{1,1}(z)=\alpha^+_{0,1}(z)=a(z)\) and \(\alpha^-_{1,1}(z)=\alpha^-_{0,1}(z)=d(z)\).  The corresponding \(D=1\) and \(D=0\) level curves \(G_{1,z}(y)\) and \(G_{0,z}(y)\) are also right-continuous CDFs in \(y\).
\end{assumption}

\begin{assumption}[Constructive path-projection system]\label{ass:constructive}
The variables \((a,d,\alpha,G)\) satisfy the linear level-recursion constraints obtained by integrating the derivative equations in Theorem~\ref{thm:necessary} from a baseline \(z_0\): the integrated \(D=1\) and \(D=0\) subdistribution curves remain between \(0\) and \(1\), sum to one at \(y=1\), match the observed \(P_{Y,D\mid Z=z}\), and use one common pair of potential-outcome subdistributions for response segments that persist across adjacent instrument intervals.
\end{assumption}

\begin{assumption}[Interior nondegeneracy for strictness]\label{ass:interior}
For strict-separation statements, the observable process has positive first-stage derivative on two intervals of positive Lebesgue measure, \(b\) is positive on one of them, all local pointwise inequalities hold with slack, and the conditional outcome distributions place positive mass on at least two separated \(Y\)-regions.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: necessary all-cell local derivative equations]\label{thm:necessary}
Under Assumptions~\ref{ass:law}--\ref{ass:subcdf}, every feasible derivative process \(r(P)\in K_b^{\mathrm{proj}}\) admits nonnegative measurable response intensities \(a(z)\) and \(d(z)\), and for each \(y\) nonnegative switcher subdistribution intensities
\[
\alpha^+_{1y}(z),\ \alpha^+_{0y}(z),\ \alpha^-_{1y}(z),\ \alpha^-_{0y}(z),
\]
such that, almost everywhere,
\[
d(z)\le b(z),\qquad p'(z)=a(z)-d(z),\qquad
0\le \alpha^+_{1y}(z),\alpha^+_{0y}(z)\le a(z),\quad
0\le \alpha^-_{1y}(z),\alpha^-_{0y}(z)\le d(z),
\]
and, as functions of \(y\), the four \(\alpha\)-curves satisfy the right-continuity, monotonicity, zero-left-endpoint, and endpoint-mass restrictions in Assumption~\ref{ass:subcdf}.  The two observable subdistribution derivatives obey the all-cell balances
\[
g_y'(z)=\alpha^+_{1y}(z)-\alpha^-_{1y}(z),\qquad
h_y'(z)=-\alpha^+_{0y}(z)+\alpha^-_{0y}(z).
\]
The endpoint equations include all four observed cells:
\[
\alpha^+_{1,1}(z)=\alpha^+_{0,1}(z)=a(z),\qquad
\alpha^-_{1,1}(z)=\alpha^-_{0,1}(z)=d(z),
\]
so \(g_1'(z)=p'(z)\), \(h_1'(z)=-p'(z)\), and no \(D=1\) or \(D=0\) subdistribution margin is omitted.  Consequently \(r(P)\in\mathcal L_b\), the pointwise local envelope relaxation defined by these equations with no cross-\(z\) path-pasting restriction.
\end{theorem}
\paragraph{Why this is new and worth studying.}
The closest published comparator is \citet{Kitagawa2015}, whose discrete-IV inequalities use finite differences of conditional outcome-treatment distributions.  The epsilon-gap is that Theorem~\ref{thm:necessary} states the infinitesimal all-cell analogue under a known negative-response density envelope, including both \(D=1\) and \(D=0\) outcome subdistribution derivatives and the complement equations that prevent hiding missing cells.  The concrete consumer is Conjecture~\ref{conj:feasible}: the feasible-set theorem needs this local relaxation as the outer object it sharpens.

\begin{theorem}[Theorem 2: zero-envelope threshold-crossing corner]\label{thm:zero}
Under Assumptions~\ref{ass:law}--\ref{ass:constructive}, if \(b=0\) almost everywhere and \(p'(z)\ge0\) almost everywhere, then \(K_0^{\mathrm{proj}}\) equals the derivative-process set generated by monotone response paths.  If in addition \(p'(z)>0\) on an interval, the associated local positive-response outcome distribution is the Heckman--Vytlacil LIV/MTE derivative object on that interval.
\end{theorem}
\paragraph{Why this is new and worth studying.}
This is a sanity result rather than the flagship contribution.  The closest paper is \citet{HeckmanVytlacil2005}, which identifies MTEs through local derivatives under threshold crossing; the epsilon-gap is only that the proposed feasibility object has the right zero-violation boundary.  The concrete consumer is \citet{KennedyLorchSmall2019}, because their continuous-IV curve should be recovered exactly when the calibrated violation envelope is zero.

\begin{conjecture}[Conjecture 1: sharp derivative-feasible set and support certificates (NOT YET PROVED)]\label{conj:feasible}
Under Assumptions~\ref{ass:law}--\ref{ass:constructive}, the bounded-violation continuous-IV model is nonempty if and only if \(r(P)\in K_b^{\mathrm{proj}}\), where \(K_b^{\mathrm{proj}}\) is the bounded-Lipschitz closure of the projection of the explicit linear system \(H_b\) in the product space \(\mathbb X=\mathcal M([0,1])\times\mathcal M([0,1]^2)^2\).  Equivalently,
\[
r(P)\in K_b^{\mathrm{proj}}
\quad\Longleftrightarrow\quad
\langle\varphi,r(P)\rangle\le\sigma_{K_b^{\mathrm{proj}}}(\varphi)\ \text{ for every }\varphi\in\mathbb X^\ast_{\mathrm{BL},1}.
\]
Moreover, whenever \(r(P)\notin K_b^{\mathrm{proj}}\), there exists a finite-threshold support certificate \(\varphi^\star\in\mathbb X^\ast_{\mathrm{BL},1}\) involving only finitely many \(y\)-thresholds and finitely many \(z\)-intervals such that \(\langle\varphi^\star,r(P)\rangle>\sigma_{K_b^{\mathrm{proj}}}(\varphi^\star)\).  The certificate can be normalized to define the feasibility gap \(\Delta_b(P)>0\), and \(\Delta_b(P)\le0\) if and only if the calibrated envelope model is observationally feasible.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
The closest published results are \citet{Kitagawa2015}, \citet{ChesherRosen2017}, \citet{KilbertusKusnerSilva2020}, and \citet{Gunsilius2019}: Kitagawa gives finite conditional-distribution inequalities for discrete IV monotonicity, Chesher--Rosen gives generalized-IV sharp-set machinery through abstract conditional restrictions, Kilbertus--Kusner--Silva compute bounds in continuous IV models, and Gunsilius studies path-sampling bounds for continuous IV.  The flagship epsilon-gap is a necessary-and-sufficient scalar continuous-IV feasible set with a fixed function-valued violation envelope and a finite-threshold support certificate that is computable from derivative-process primitives.  Neither \citet{MogstadTorgovitskyWalters2021} nor \citet{JiangSun2023PartialMonotonicityTest} gives this object, because their partial-monotonicity tests concern multidimensional/discrete instrument directions rather than a scalar continuous response path with bounded downward variation.  The concrete consumer is monotonicity-violation sensitivity for LIV analyses: \citet{KennedyLorchSmall2019} users would get an observable diagnostic showing whether a proposed envelope \(b\) can rationalize the data before estimating a causal curve.

\begin{conjecture}[Conjecture 2: global path compatibility strictly tightens pointwise envelopes (NOT YET PROVED)]\label{conj:strict}
There is a nonempty open set of observable laws \(P\) and envelopes \(b\) satisfying Assumptions~\ref{ass:law}--\ref{ass:interior} such that
\[
r(P)\in\mathcal L_b\quad\text{but}\quad r(P)\notin K_b^{\mathrm{proj}} .
\]
For this open set, \(\Delta_b(P)\ge\varepsilon\) for some \(\varepsilon>0\) that is stable under small perturbations of \((p',g',h',b)\).  A minimal witness class uses three adjacent instrument regions: region one creates positive response mass with low \(Y(1)\), region two uses allowed negative response mass with high \(Y(0)\), and region three forces the binary response path to return to the original treatment level.  The pointwise inequalities in Theorem~\ref{thm:necessary} hold on each region, but no single bounded-variation binary response path with one pair of potential outcomes can realize all three derivative signs and subdistribution shifts.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
The closest published comparators are \citet{BalkePearl1997}, \citet{Kitagawa2015}, and \citet{Gunsilius2019}: finite latent-type or finite-inequality systems are sharp in the corresponding discrete problems, while path-space continuous-IV bounds emphasize that global compatibility matters.  The epsilon-gap is an open-neighborhood nonsharpness theorem for the internal CausalSmith relaxation \(\mathcal L_b\); it proves that derivative-cell feasibility is not enough once all cells must be generated by one response path.  The concrete consumer is the CausalSmith \texttt{pid\_ordinal\_late\_partial\_defiers\_v1} line: it identifies the exact obstruction that prevents independently optimized adjacent intervals from being reported as sharp.

\section{Sanity-check corollaries}
\begin{corollary}[Discrete Kitagawa corner]\label{cor:kitagawa}
If \(Z\) is restricted to a finite grid, \(b=0\), and Assumptions~\ref{ass:law}--\ref{ass:constructive} are replaced by their finite analogues, Conjecture~\ref{conj:feasible} reduces to finite conditional-distribution inequalities of the Kitagawa type.  The reduction is obtained by replacing weak derivatives with adjacent finite differences and setting all negative response cells to zero.
\end{corollary}

\begin{corollary}[Adjacent bounded-defier local algebra]\label{cor:binary}
On a two-point interval \([z,z+h]\), Theorem~\ref{thm:necessary} reduces to a binary-IV bounded-defier cell system with defier mass at most \(h\,b(z)+o(h)\) and with both \(D=1\) and \(D=0\) outcome subdistribution cells included.  This is the infinitesimal version of the all-four-observed-cell correction flagged in the failed \texttt{pid\_late\_bounded\_defiers} proposal.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is convex-analytic.  First derive Theorem~\ref{thm:necessary} by taking the Jordan decomposition of the bounded-variation binary response path and differentiating the conditional subdistribution processes for \((Y,D)\), checking the CDF-in-\(y\) restrictions in Assumption~\ref{ass:subcdf}.  The zero-envelope theorem follows by eliminating the negative variation and applying the Vytlacil threshold-crossing equivalence to the remaining monotone path.  For Conjecture~\ref{conj:feasible}, approximate \(Z\) by finite grids, write \(H_b\) as a latent-response-type linear feasibility problem with all outcome-threshold cells, use Farkas separation to obtain finite support-function certificates, and pass to the limit in \(\mathbb X\) through weak compactness of bounded-variation measures and closedness of the envelope constraint.  For Conjecture~\ref{conj:strict}, compute the three-region witness as a finite grid first; then show that the separating functional has slack, so the same certificate rejects an open bounded-Lipschitz neighborhood of derivative processes after mesh refinement.

\section{Honest scope flags}
Theorems~\ref{thm:necessary} and~\ref{thm:zero} are proposed as routine mathematical checks.  Conjecture~\ref{conj:feasible} is the main open kernel; its risk is that closedness or finite-threshold certificate extraction may require tighter regularity than Assumption~\ref{ass:regular} or a stronger compactness condition on \(H_b\).  Conjecture~\ref{conj:strict} is also open and is scoped as an internal relaxation-vs-projection separation, not a claim that a named published estimator uses \(\mathcal L_b\); it must use a nondegenerate observable law and an open neighborhood, not a single hand-tuned zero-outcome witness.  This proposal does not yet characterize the LATE interval endpoints under feasible \(P\); it supplies the feasibility/refutability layer that a later sharp-bound theorem must condition on.  Statistical inference for \(\Delta_b(P)\), estimation of derivatives, covariates, and data-driven calibration of \(b\) are out of scope.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- fresh derivative-feasibility proposal replacing the exhausted sharp-set angle; prior verdict: none.
\item v2 (revise) -- fixed the fixed-\(b\) convex object, specified all-cell local derivative equations, corrected Jiang--Sun metadata, and anchored strictness to a named continuous-IV workflow; prior verdict: REVISE.
\item v3 (revise) -- made \(K_b^{\mathrm{proj}}\) constructive in a bounded-Lipschitz product space, added subdistribution-in-\(y\) constraints, added Kilbertus--Kusner--Silva and Gunsilius comparators, and downgraded Conjecture~\ref{conj:strict} to an internal \(\mathcal L_b\) separation; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Balke, A. and J. Pearl (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association} 92(439), 1171--1176.
\url{https://doi.org/10.1080/01621459.1997.10474074}

\bibitem[Chesher and Rosen(2017)]{ChesherRosen2017}
Chesher, A. and A. M. Rosen (2017).
Generalized instrumental variable models.
\emph{Econometrica} 85(3), 959--989.
\url{https://doi.org/10.3982/ECTA11208}

\bibitem[de Chaisemartin(2017)]{DeChaisemartin2017}
de Chaisemartin, C. (2017).
Tolerating defiance? Local average treatment effects without monotonicity.
\emph{Quantitative Economics} 8(2), 367--396.
\url{https://doi.org/10.3982/QE601}

\bibitem[Heckman and Vytlacil(2005)]{HeckmanVytlacil2005}
Heckman, J. J. and E. Vytlacil (2005).
Structural equations, treatment effects, and econometric policy evaluation.
\emph{Econometrica} 73(3), 669--738.
\url{https://doi.org/10.1111/j.1468-0262.2005.00594.x}

\bibitem[Imbens and Angrist(1994)]{ImbensAngrist1994}
Imbens, G. W. and J. D. Angrist (1994).
Identification and estimation of local average treatment effects.
\emph{Econometrica} 62(2), 467--475.
\url{https://www.gsb.stanford.edu/faculty-research/publications/identification-estimation-local-average-treatment-effects}

\bibitem[Jiang and Sun(2023)]{JiangSun2023PartialMonotonicityTest}
Jiang, H. and Z. Sun (2023).
Testing partial instrument monotonicity.
\emph{Economics Letters} 233, 111400.
\url{https://doi.org/10.1016/j.econlet.2023.111400}

\bibitem[Kennedy, Lorch, and Small(2019)]{KennedyLorchSmall2019}
Kennedy, E. H., S. Lorch, and D. S. Small (2019).
Robust causal inference with continuous instruments using the local instrumental variable curve.
\emph{Journal of the Royal Statistical Society: Series B} 81(1), 121--143.
\url{https://doi.org/10.1111/rssb.12300}

\bibitem[Kilbertus, Kusner, and Silva(2020)]{KilbertusKusnerSilva2020}
Kilbertus, N., M. J. Kusner, and R. Silva (2020).
A class of algorithms for general instrumental variable models.
\emph{Advances in Neural Information Processing Systems} 33.
\url{https://proceedings.neurips.cc/paper/2020/hash/e8b1cbd05f6e6a358a81dee52493dd06-Abstract.html}

\bibitem[Kitagawa(2015)]{Kitagawa2015}
Kitagawa, T. (2015).
A test for instrument validity.
\emph{Econometrica} 83(5), 2043--2063.
\url{https://doi.org/10.3982/ECTA11974}

\bibitem[Klein(2010)]{Klein2010}
Klein, T. J. (2010).
Heterogeneous treatment effects: Instrumental variables without monotonicity?
\emph{Journal of Econometrics} 155(2), 99--116.
\url{https://www.sciencedirect.com/science/article/pii/S030440760900219X}

\bibitem[Gunsilius(2019)]{Gunsilius2019}
Gunsilius, F. F. (2019).
A path-sampling method to partially identify causal effects in instrumental variable models.
\emph{arXiv working paper}.
\url{https://arxiv.org/abs/1910.09502}

\bibitem[Machado, Shaikh, and Vytlacil(2019)]{MachadoShaikhVytlacil2019}
Machado, C., A. M. Shaikh, and E. J. Vytlacil (2019).
Instrumental variables and the sign of the average treatment effect.
\emph{Journal of Econometrics} 212(2), 522--555.
\url{https://doi.org/10.1016/j.jeconom.2018.04.007}

\bibitem[Mogstad, Santos, and Torgovitsky(2018)]{MogstadSantosTorgovitsky2018}
Mogstad, M., A. Santos, and A. Torgovitsky (2018).
Using instrumental variables for inference about policy relevant treatment parameters.
\emph{Econometrica} 86(5), 1589--1619.
\url{https://doi.org/10.3982/ECTA15463}

\bibitem[Mogstad, Torgovitsky, and Walters(2021)]{MogstadTorgovitskyWalters2021}
Mogstad, M., A. Torgovitsky, and C. R. Walters (2021).
The causal interpretation of two-stage least squares with multiple instrumental variables.
\emph{American Economic Review} 111(11), 3663--3698.
\url{https://doi.org/10.1257/aer.20190221}

\bibitem[Mountjoy(2024)]{Mountjoy2024}
Mountjoy, J. (2024).
A vector monotonicity assumption for multiple instruments.
\emph{Journal of Econometrics} 241(1), 105735.
\url{https://doi.org/10.1016/j.jeconom.2024.105735}

\bibitem[Vytlacil(2002)]{Vytlacil2002}
Vytlacil, E. (2002).
Independence, monotonicity, and latent index models: An equivalence result.
\emph{Econometrica} 70(1), 331--341.
\url{https://doi.org/10.1111/1468-0262.00277}

\bibitem[Yap(2022)]{Yap2022}
Yap, L. (2022).
Sensitivity of policy relevant treatment parameters to violations of monotonicity.
\emph{Princeton Industrial Relations Section Working Paper} 655.
\url{http://arks.princeton.edu/ark:/88435/dsp015d86p341p}
\end{thebibliography}

\end{document}
