\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_rdd\_flow\_manipulation} / \texttt{v1}%
  \\ \large\textit{Nested-window flow certificates for bounded-manipulation RD intervals}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal.
The locked tuple is
\[
  (\texttt{qid}, \texttt{specialization}, P, \theta, \text{identifying restrictions},
  \text{bounding functional}).
\]
The convention is as follows.
\(\texttt{qid}=\texttt{pid\_rdd\_flow\_manipulation}\) and
\(\texttt{specialization}=\texttt{v1}\).
The observable distribution \(P\) is a finite nested-neighborhood sharp-RD array
\[
  P=\bigl\{(p_{bwr},\pi_{j,-}(w),\mu^-_j(w),\bar\rho_j,\bar s_{jw},\omega_j):
  1\le b\le j\le J,\ 1\le w\le K,\ 1\le r\le R_{bw}\bigr\},
\]
where \(H_1\subset \cdots \subset H_J\) are prespecified right-side cutoff neighborhoods,
\(b\) indexes the shell \(H_b\setminus H_{b-1}\) with \(H_0=\varnothing\),
\(p_{bwr}\) is the observed right-side mass of atom \(r\) in shell \(b\), covariate cell \(w\),
and outcome value \(y_{bwr}\in[\underline y,\overline y]\),
\(\pi_{j,-}(w)\) and \(\mu^-_j(w)\) are the left-limit covariate law and left-limit outcome mean
in neighborhood \(j\),
\(\bar\rho_j\in[0,1)\) is the neighborhood-\(j\) manipulation envelope,
\(\bar s_{jw}\in[0,1)\) is the cell cap, and \(\omega_j\ge0\) with \(\sum_{j=1}^J\omega_j=1\)
are fixed pooling weights.
The parameter is the vector \(\theta=(\theta_1,\ldots,\theta_J)\) of neighborhood-specific
nonmanipulator sharp-RD effects,
\[
  \theta_j=\mu^+_{j,0}-\sum_{w=1}^K \pi_{j,-}(w)\mu^-_j(w),
\]
where \(\mu^+_{j,0}\) is the unobserved retained right-side nonmanipulator mean in neighborhood \(j\).
The identifying restrictions are: one-sided upward manipulation, sharp RD on the treated side,
finite predetermined-covariate cells, bounded outcomes, left-limit continuity for nonmanipulators,
global envelopes \(\bar\rho_j\), cell caps \(\bar s_{jw}\), and nested-window compatibility induced by
one common retained right-side plan on shell atoms.
The bounding functional is the pooled upper and lower endpoint pair
\[
  B_U^{\mathrm{flow}}(P,\omega)=\sup_{x\in\calA(P,\bar\rho,\bar s)}
  \sum_{j=1}^J \omega_j\!\left\{\frac{S_j(x)}{m_j(x)}-\bar\mu^-_j\right\},
  \qquad
  B_L^{\mathrm{flow}}(P,\omega)=\inf_{x\in\calA(P,\bar\rho,\bar s)}
  \sum_{j=1}^J \omega_j\!\left\{\frac{S_j(x)}{m_j(x)}-\bar\mu^-_j\right\},
\]
where \(x\) is a shell-atom retained-mass plan, \(m_j(x)\) is retained mass in neighborhood \(j\),
\(S_j(x)\) is retained right-side outcome mass in neighborhood \(j\), and
\(\bar\mu^-_j=\sum_w \pi_{j,-}(w)\mu^-_j(w)\).
When \(J=1\) and \(\omega_1=1\), these are the parent sharp-RD endpoints.

\begin{abstract}
The banked parent proposal \texttt{pid\_rdd\_manipulation\_bounded/v1} gives a sharp interval for one
cutoff neighborhood under bounded manipulation.  This upgrade asks for one computational object that
evaluates manipulation-robust bounds across a prespecified nested class of neighborhoods.  The fixed
retained-mass problem is the key step: once the admissible retained masses are pinned down, the pooled
upper endpoint becomes a finite transportation problem over shell atoms and neighborhood-cell demands.
The flagship open claim is that the outer optimization over retained masses can be absorbed into an
expanded min-cost-flow network with a totally unimodular constraint matrix and an explicit dual
certificate.  If correct, the parent scalar interval becomes the \(J=1\) face of a strongly-polynomial
algorithm for many-neighborhood RD sensitivity analysis.
\end{abstract}

\section{Introduction}
The question is computational.  The parent result identifies a sharp interval for one RD neighborhood under
one-sided manipulation, but empirical work often reports several windows around the same cutoff and then
pools them informally.  This draft asks for one sharp pooled endpoint across a prespecified nested class of
windows, with the same retained right-side plan governing every window.

The upgrade delta is against the parent and then against the literature.  The parent proof route says
endpoint evaluation reduces to ``linear programs indexed by a candidate ratio lambda.''  Gerard, Rokkanen,
and Rothe write in the abstract, at the article's opening page, that under manipulation ``one can derive
sharp bounds under a general model'' \citep[p.~839]{GerardRokkanenRothe2020}; Rosenman, Rajkumar, Gauriot,
and Slonim write in their abstract that their discrete-RD procedure ``relies on two stages'' and then
uses ``a sequential convex programming approach'' \citep[p.~1]{RosenmanRajkumarGauriotSlonim2019}.  The
gap here is narrower: nested-window sharp-RD bounds with external cell caps, one common retained plan, and
an explicit transport dual that reduces to the parent one-window interval.

The consumer is many-window RD practice.  \citet{Bertanha2020} shows that pooling across thresholds is part
of the estimand under point identification, while \citet{CattaneoJanssonMa2020} gives the density tool that
empirical work already uses to calibrate manipulation envelopes.  A reader would stop reporting an
unstructured stack of window-by-window sensitivity intervals and instead report one pooled
manipulation-robust envelope with a dual certificate showing which shells and covariate cells bind.

\begin{itemize}[leftmargin=*]
  \item Theorem 1: for any admissible retained-mass profile, the pooled upper endpoint is a finite
  transportation LP on shell atoms and neighborhood-cell demands. Gap: the parent gives a one-window
  scalar program; \citet{RosenmanRajkumarGauriotSlonim2019} gives sequential convex programming rather
  than an explicit transport LP. Consumer: pooled many-window RD summaries in \citet{Bertanha2020}.
  \item Conjecture 1: the outer optimization over retained masses is itself an expanded min-cost-flow
  problem with a totally unimodular matrix and a dual node-potential certificate. Gap:
  \citet{GerardRokkanenRothe2020} gives sharp one-window bounds, not a many-window flow certificate.
  Consumer: auditable computation of manipulation-robust pooled RD endpoints.
  \item Theorem 2: when \(J=1\), the flow formulation collapses to the parent sharp-RD interval. Gap:
  the parent proves the scalar interval but does not expose it as the one-window face of a many-window
  transport problem. Consumer: direct reuse of the banked parent as the corner case.
\end{itemize}

\section{Related work}
\citet{HahnToddVanDerKlaauw2001} is the classical sharp- and fuzzy-RD benchmark.  \citet{Lee2008} explains
the local-randomization interpretation behind continuity of predetermined covariates at the cutoff.
\citet{McCrary2008} develops the density-discontinuity diagnostic and writes in the abstract that the
continuity assumptions ``may not be plausible if agents can precisely manipulate the assignment variable''
\citep[p.~698]{McCrary2008}; that diagnostic is reused from the parent as the source of the envelope
\(\bar\rho_j\).  \citet{CattaneoJanssonMa2020} provide a boundary-adaptive density procedure and state in
their abstract that they ``develop a novel discontinuity in density testing procedure'' \citep[p.~1449]
{CattaneoJanssonMa2020}; this is also reused from the parent.

\citet{GerardRokkanenRothe2020} is the main identification anchor.  Their paper derives sharp manipulated-RD
bounds neighborhood by neighborhood and is the direct published comparator for the banked parent.  This
upgrade does not claim a new one-window identified set.  It claims a new computational representation for a
nested class of windows under one common retained plan.  \citet{RosenmanRajkumarGauriotSlonim2019} is the
new computation anchor: they obtain discrete manipulated-RD bounds with a sequential convex program, which
shows the computational frontier is active but does not furnish a many-window flow certificate.

\citet{Bertanha2020} studies RD with many thresholds under point-identification conditions and emphasizes
that the pooled estimand depends on the weighting scheme.  That is the natural consumer here: once each
window is only partially identified, the pooling map belongs inside the bound itself.  The proposal stays in
the PartialID theorem cluster and does not claim new SCM infrastructure.

In repository terms, \texttt{doc/API.md} \S3 still records no competing manipulated-RD PartialID entry
beyond the banked parent line of work.  The immediate in-repo comparator is
\texttt{doc/research/\_bank/candidates/pid\_rdd\_manipulation\_bounded\_v1/}
\texttt{pid\_rdd\_manipulation\_bounded\_v1\_proposal.tex}, especially its \S10 proof route and \S11 scope
flags.  No separate in-repo proposal already states a many-window transport or flow certificate for bounded
RDD manipulation.

\section{Formal setup}
Fix one cutoff and a prespecified nested right-side neighborhood class
\[
  H_1\subset H_2\subset\cdots\subset H_J,
  \qquad H_0=\varnothing.
\]
Write shell \(b\) for \(H_b\setminus H_{b-1}\).  The proposal works on the sharp-RD face, so treatment is
the cutoff assignment on the right and the target is the retained right-side outcome mean minus the observed
left-side outcome mean.  Let \(W\in\{1,\ldots,K\}\) be a finite predetermined-covariate cell and let
\(y_{bwr}\in[\underline y,\overline y]\) be the outcome value of atom \(r\) in shell \(b\) and cell \(w\),
with observed right-side mass \(p_{bwr}>0\).  For neighborhood \(j\), define cumulative observed masses
\[
  p_{j,+}=\sum_{b\le j}\sum_{w=1}^K\sum_{r=1}^{R_{bw}} p_{bwr},
  \qquad
  p_{j,w,+}=\sum_{b\le j}\sum_{r=1}^{R_{bw}} p_{bwr}.
\]
Let \(\pi_{j,-}(w)\) be the left-limit covariate law in neighborhood \(j\), let \(\mu^-_j(w)\) be the
left-limit outcome mean in cell \(w\), and let
\[
  \bar\mu^-_j=\sum_{w=1}^K \pi_{j,-}(w)\mu^-_j(w).
\]

A retained plan is a family \(x=(x_{bwr})\) with \(0\le x_{bwr}\le p_{bwr}\).  It induces cumulative
retained masses
\[
  m_j(x)=\sum_{b\le j}\sum_w\sum_r x_{bwr},
  \qquad
  m_{jw}(x)=\sum_{b\le j}\sum_r x_{bwr},
  \qquad
  S_j(x)=\sum_{b\le j}\sum_w\sum_r y_{bwr}x_{bwr}.
\]
The neighborhood-\(j\) sharp-RD value generated by \(x\) is
\[
  \theta_j(x)=\frac{S_j(x)}{m_j(x)}-\bar\mu^-_j.
\]
The pooled upper endpoint is
\[
  B_U^{\mathrm{flow}}(P,\omega)=
  \sup_{x\in\calA(P,\bar\rho,\bar s)}
  \sum_{j=1}^J \omega_j\theta_j(x),
\]
and \(B_L^{\mathrm{flow}}(P,\omega)\) is defined by replacing \(\sup\) with \(\inf\).
When \(J=1\), write \(B_U^{\mathrm{parent,sharp}}(P,\bar\rho,\bar s)\) and
\(B_L^{\mathrm{parent,sharp}}(P,\bar\rho,\bar s)\) for the corresponding sharp-RD endpoints from the
banked parent proposal.

The feasible set \(\calA(P,\bar\rho,\bar s)\) consists of retained plans satisfying, for every \(j\) and
\(w\),
\[
  m_j(x)\ge (1-\bar\rho_j)p_{j,+},
  \qquad
  m_{jw}(x)\ge (1-\bar s_{jw})p_{j,w,+},
  \qquad
  m_{jw}(x)=m_j(x)\pi_{j,-}(w).
\]
For a retained-mass profile \(m=(m_1,\ldots,m_J)\), define
\[
  q_{jw}(m)=m_j\pi_{j,-}(w)-m_{j-1}\pi_{j-1,-}(w),
  \qquad m_0=0,\quad \pi_{0,-}\equiv 0.
\]
The admissible profile set is
\[
  \calM(P,\bar\rho,\bar s)=
  \left\{
  m\in\R^J:
  0<m_1\le\cdots\le m_J,\,
  m_j\ge (1-\bar\rho_j)p_{j,+},\,
  m_j\pi_{j,-}(w)\ge (1-\bar s_{jw})p_{j,w,+},\,
  m_j\pi_{j,-}(w)\le p_{j,w,+},\,
  q_{jw}(m)\ge0
  \right\}.
\]
For fixed \(m\in\calM(P,\bar\rho,\bar s)\), let \(\calF(m)\) be the set of nonnegative flows
\(f_{bwr,j}\) defined on arcs \((b,w,r)\to(j,w)\) with \(b\le j\), satisfying
\[
  \sum_{j\ge b} f_{bwr,j}\le p_{bwr},
  \qquad
  \sum_{b\le j}\sum_r f_{bwr,j}=q_{jw}(m).
\]
The cumulative right-side outcome in neighborhood \(j\) is then
\[
  S_j(f)=\sum_{\ell\le j}\sum_{b\le \ell}\sum_w\sum_r y_{bwr}f_{bwr,\ell}.
\]
Write
\[
  c_j(m)=\sum_{\ell=j}^J \frac{\omega_\ell}{m_\ell}.
\]
Then the fixed-profile pooled value is
\[
  U_\omega(m)=
  \sup_{f\in\calF(m)}
  \left[
  \sum_{j=1}^J \omega_j\!\left\{\frac{S_j(f)}{m_j}-\bar\mu^-_j\right\}
  \right].
\]

\begin{verbatim}
Locked parameters.
qid = pid_rdd_flow_manipulation
specialization = v1
observable distribution P = finite nested-neighborhood sharp-RD shell array
parameter theta = vector of neighborhood-specific nonmanipulator sharp-RD effects
identifying restrictions = one-sided manipulation; sharp RD; bounded outcomes;
  finite covariate cells; left-limit continuity for nonmanipulators; global
  neighborhood envelopes rho_bar_j; cell caps s_bar_jw; one common retained
  shell plan across all nested neighborhoods
bounding functional = pooled endpoint pair
  (B_U^flow(P,omega), B_L^flow(P,omega))
  with one-window corner equal to the parent sharp-RD interval
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Nested finite neighborhood class]\label{ass:nested-class}
The neighborhood class \(\calH=\{H_1,\ldots,H_J\}\) is finite and nested, and the pooling weights satisfy
\(\omega_j\ge0\) and \(\sum_{j=1}^J \omega_j=1\).
\end{assumption}

\begin{assumption}[Finite shell support]\label{ass:finite-support}
For every shell \(b\) and covariate cell \(w\), the right-side outcome distribution has finite support
\(\{y_{bwr}:1\le r\le R_{bw}\}\subset[\underline y,\overline y]\).
\end{assumption}

\begin{assumption}[One-sided manipulation and sharp RD]\label{ass:sharp-rd}
Manipulation can only add mass to the treated-side law, and treatment receipt equals cutoff assignment on
the sharp-RD face analyzed here.
\end{assumption}

\begin{assumption}[Left-limit continuity for nonmanipulators]\label{ass:left-continuity}
After removing manipulators, the retained right-side covariate law in neighborhood \(j\) equals
\(\pi_{j,-}\), and the left-side means \(\mu^-_j(w)\) are the correct untreated comparison means.
\end{assumption}

\begin{assumption}[Envelope and cell-cap calibration]\label{ass:budgets}
The neighborhood-specific envelopes \(\bar\rho_j\) and cell caps \(\bar s_{jw}\) are fixed numbers in
\([0,1)\), and the feasible retained-plan set \(\calA(P,\bar\rho,\bar s)\) is nonempty.
\end{assumption}

\begin{assumption}[Admissible retained-mass profile]\label{ass:profile}
Whenever a result invokes a profile \(m\), that profile lies in \(\calM(P,\bar\rho,\bar s)\).
\end{assumption}

\begin{assumption}[Parent reduction face]\label{ass:parent-face}
For the one-window reduction result, \(J=1\), \(\omega_1=1\), and the right-side law is the parent
one-neighborhood sharp-RD specialization.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: explicit transportation LP for fixed retained masses]\label{thm:transport}
Under Assumptions~\ref{ass:nested-class}--\ref{ass:budgets} and Assumption~\ref{ass:profile}, the fixed
profile pooled upper endpoint satisfies
\[
  U_\omega(m)=
  \max_{f\in\calF(m)}
  \left[
  \sum_{b=1}^J\sum_{w=1}^K\sum_{r=1}^{R_{bw}}\sum_{j=b}^J
  c_j(m)\,y_{bwr}\,f_{bwr,j}
  -\sum_{j=1}^J \omega_j\bar\mu^-_j
  \right].
\]
Equivalently, for fixed \(m\), the pooled upper endpoint is a finite transportation LP with supply nodes
\((b,w,r)\), demand nodes \((j,w)\), capacities \(p_{bwr}\), demands \(q_{jw}(m)\), and arc payoffs
\(c_j(m)y_{bwr}\).
\end{theorem}

Proof sketch.  For fixed \(m\), each denominator \(m_j\) is constant, so the pooled objective is linear in
the shell masses assigned to each neighborhood increment.  Re-indexing retained shell masses by increment
\((j,w)\) produces the displayed transportation constraints.

\begin{conjecture}[Conjecture 1: totally unimodular flow certificate for the sharp envelope]\label{conj:flow}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:nested-class}--\ref{ass:budgets}, the sharp upper endpoint
\[
  B_U^{\mathrm{flow}}(P,\omega)=\sup_{m\in\calM(P,\bar\rho,\bar s)} U_\omega(m)
\]
and the analogous lower endpoint are the values of one expanded min-cost-flow problem whose arc set contains
the transportation arcs of Theorem~\ref{thm:transport} together with a mass-profile chain enforcing
\(m\in\calM(P,\bar\rho,\bar s)\).  The full constraint matrix is the node-arc incidence matrix of that
expanded network and is therefore totally unimodular.  Consequently a strongly polynomial min-cost-flow
algorithm returns the sharp endpoint together with dual node potentials
\((a_{bwr},b_{jw},u_j)\) certifying optimality.  When \(J=1\), the dual certificate collapses to the parent
one-neighborhood sharp-RD endpoint certificate.
\end{conjecture}

\begin{theorem}[Theorem 2: one-window parent reduction]\label{thm:parent}
Under Assumptions~\ref{ass:nested-class}--\ref{ass:budgets} and Assumption~\ref{ass:parent-face},
\[
  B_U^{\mathrm{flow}}(P,\omega)=B_U^{\mathrm{parent,sharp}}(P,\bar\rho,\bar s),
  \qquad
  B_L^{\mathrm{flow}}(P,\omega)=B_L^{\mathrm{parent,sharp}}(P,\bar\rho,\bar s),
\]
where \(B_U^{\mathrm{parent,sharp}}\) and \(B_L^{\mathrm{parent,sharp}}\) denote the parent sharp-RD
endpoints from \texttt{pid\_rdd\_manipulation\_bounded/v1}.
\end{theorem}

Proof sketch.  When \(J=1\), there is one demand node per covariate cell and
\(c_1(m)=1/m_1\), so Theorem~\ref{thm:transport} reduces to the parent one-neighborhood retained-mass
problem on the sharp-RD face.  The lower endpoint is the same reduction with outcomes negated.

\section{Sanity-check corollaries}
\begin{corollary}[No-manipulation corner]\label{cor:no-manip}
Under Assumptions~\ref{ass:nested-class}--\ref{ass:budgets}, if \(\bar\rho_j=0\),
\(\bar s_{jw}=0\), and \(p_{j,w,+}=p_{j,+}\pi_{j,-}(w)\) for every \((j,w)\), then the only feasible plan
retains all shell mass and
\[
  B_U^{\mathrm{flow}}(P,\omega)=B_L^{\mathrm{flow}}(P,\omega)=
  \sum_{j=1}^J \omega_j\left\{\frac{\sum_{b\le j}\sum_w\sum_r y_{bwr}p_{bwr}}{p_{j,+}}-\bar\mu^-_j\right\}.
\]
This reduces to the ordinary weighted sharp-RD contrast because every neighborhood retains its full
right-side distribution.
\end{corollary}

\begin{corollary}[Parent reduction corner]\label{cor:parent}
Under Assumptions~\ref{ass:nested-class}--\ref{ass:budgets} and Assumption~\ref{ass:parent-face},
Theorem~\ref{thm:parent} reduces the upgrade to the banked parent.  The reduction holds because the
increment demand system has one neighborhood only, so the nested transport graph has exactly the same
feasible retained masses as the parent sharp-RD retained-mass problem.
\end{corollary}

\paragraph{Exhibit 9.1.}
Take \(J=2\), \(K=1\), \(\omega_1=\omega_2=1/2\), and left means \(\bar\mu^-_1=\bar\mu^-_2=0\).  Let shell 1
contain one atom with \(y_{111}=1\) and supply \(p_{111}=1/2\), and let shell 2 contain one atom with
\(y_{211}=0\) and supply \(p_{211}=1/2\).  Fix the admissible retained-mass profile \(m_1=1/2\), \(m_2=1\).
Then \(q_{11}(m)=1/2\) and \(q_{21}(m)=1/2\), and the arc coefficients are
\[
  c_1(m)=\frac{\omega_1}{m_1}+\frac{\omega_2}{m_2}=1+\frac12=\frac32,
  \qquad
  c_2(m)=\frac{\omega_2}{m_2}=\frac12.
\]
The primal transport LP is
\[
  \max_{f\ge0}\ \frac32 f_{111,1}+\frac12 f_{111,2}
\]
subject to
\[
  f_{111,1}+f_{111,2}\le \frac12,\qquad
  f_{211,2}\le\frac12,\qquad
  f_{111,1}=\frac12,\qquad
  f_{111,2}+f_{211,2}=\frac12.
\]
Its unique optimizer is \(f_{111,1}=1/2\), \(f_{111,2}=0\), \(f_{211,2}=1/2\), which yields
\[
  U_\omega(m)=\frac32\cdot\frac12=\frac34.
\]
The dual is
\[
  \min_{a_1,a_2,b_1,b_2}
  \frac12 a_1+\frac12 a_2+\frac12 b_1+\frac12 b_2
\]
subject to
\[
  a_1+b_1\ge\frac32,\qquad
  a_1+b_2\ge\frac12,\qquad
  a_2+b_2\ge 0.
\]
One feasible optimal certificate is
\[
  a_1=\frac12,\qquad a_2=0,\qquad b_1=1,\qquad b_2=0,\qquad u_1=u_2=0,
\]
whose objective value is also \(3/4\).  The internal check is exact: shell 1 uses its full supply, shell 2
uses its full supply, all demands are met, the mass-profile chain is slack so \(u_1=u_2=0\), and
complementary slackness holds on the binding arcs.

\paragraph{Exhibit 9.2.}
Set \(J=1\), \(\omega_1=1\), and keep the shell-1 atom from Exhibit 9.1.  Then \(q_{11}(m)=m_1\pi_{1,-}(1)\),
the transport graph has one demand node, and Theorem~\ref{thm:transport} becomes the parent sharp-RD
retained-mass problem.  The dual node potentials reduce to one supply potential and one cell-balance
potential, which is the one-window certificate promised in Theorem~\ref{thm:parent}.

\section{Proof-sketch route}
The verification route is:
\[
  \text{pooled endpoint}
  \leftarrow
  \text{nested retained plan}
  \leftarrow
  \text{increment-demand decomposition}
  \leftarrow
  \text{transport LP for fixed }m
  \leftarrow
  \text{expanded flow over }m
  \leftarrow
  \text{network dual certificate}.
\]
The substantive steps are four.  First, rewrite one common retained shell plan as incremental demands
\(q_{jw}(m)\) for each neighborhood-cell pair.  Second, prove the identity in
Theorem~\ref{thm:transport} by summing each retained atom's contribution across all later neighborhoods.
Third, show the admissible mass-profile constraints can be represented by chain arcs and balance nodes so
that the expanded matrix is a node-arc incidence matrix.  Fourth, read the dual node potentials as the
global envelope, cell-balance, and shell-scarcity certificate, and check the \(J=1\) corner against the
parent interval.

\section{Honest scope flags}
Theorem~\ref{thm:transport} and Theorem~\ref{thm:parent} are intended as routine but nontrivial finite
dimensional reductions.  Conjecture~\ref{conj:flow} is the flagship open claim: the transport LP is
explicit, but total unimodularity and strong polynomiality for the outer mass-profile optimization are not
yet proved.  The draft works on the sharp-RD face only.  It does not solve the parent fuzzy-Wald coupling
problem, where outcome and treatment retention move together.  Continuous covariates are also outside scope;
the finite-cell convention is inherited from the parent.  The nested-window restriction is deliberate: a
general many-cutoff design with unrelated supports is a different computation problem.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
  \item v1 (pivot) --- initial draft of the support-function upgrade from the banked parent; prior verdict:
  none.
  \item v2 (revise) --- replaced the schematic support-function shell with an explicit nested-window
  transportation LP, added a worked primal-dual exhibit, removed the unsupported inference conjecture, and
  narrowed the flagship claim to a concrete TU/min-cost-flow conjecture; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}

\bibitem[Bertanha(2020)]{Bertanha2020}
Bertanha, Marinho.
2020.
Regression discontinuity design with many thresholds.
\emph{Journal of Econometrics} 218(1): 216--241.

\bibitem[Cattaneo, Jansson, and Ma(2020)]{CattaneoJanssonMa2020}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem[Gerard, Rokkanen, and Rothe(2020)]{GerardRokkanenRothe2020}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem[Hahn, Todd, and van der Klaauw(2001)]{HahnToddVanDerKlaauw2001}
Hahn, Jinyong, Petra Todd, and Wilbert van der Klaauw.
2001.
Identification and estimation of treatment effects with a regression-discontinuity design.
\emph{Econometrica} 69(1): 201--209.

\bibitem[Lee(2008)]{Lee2008}
Lee, David S.
2008.
Randomized experiments from non-random selection in U.S. House elections.
\emph{Journal of Econometrics} 142(2): 675--697.

\bibitem[McCrary(2008)]{McCrary2008}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem[Rosenman et~al.(2019)]{RosenmanRajkumarGauriotSlonim2019}
Rosenman, Evan, Karthik Rajkumar, Romain Gauriot, and Robert Slonim.
2019.
Optimized partial identification bounds for regression discontinuity designs with manipulation.
arXiv:1910.02170.

\end{thebibliography}

\end{document}
