% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_rdd\_flow\_manipulation, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_rdd\_flow\_manipulation} / \texttt{v1}%
  \\ \large\textit{Strongly polynomial laminar-flow certificates for manipulation-robust RD bounds across nested cutoff neighborhoods}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal. The locked tuple is
\[
  (\texttt{qid}, \texttt{specialization}, P, \theta, \text{identifying restrictions},
  \text{bounding functional}).
\]
The convention is as follows. \(\texttt{qid}=\texttt{pid\_rdd\_flow\_manipulation}\) and
\(\texttt{specialization}=\texttt{v1}\). The observable distribution \(P\) consists of
the left- and right-cutoff weak limits \(\{P_{j,-},P_{j,+}\}_{j=1}^J\) for a nested family
of cutoff neighborhoods \(\mathcal N_1\subset\cdots\subset\mathcal N_J\), together with a
finite finest partition of the right side into atoms \(b=1,\ldots,B\) recording each atom's
mass \(p_b\), neighborhood-incidence pattern \(I_j(b)\in\{0,1\}\), predetermined covariate
cell \(W_b\in\{1,\ldots,K\}\), outcome \(Y_b\in[\underline y,\overline y]\), and treatment
\(D_b\in\{0,1\}\). The parameter is the vector
\(\theta=(\theta_1,\ldots,\theta_J)\), where \(\theta_j\) is the nonmanipulator local Wald
effect in neighborhood \(j\). The identifying restrictions are one-sided upward manipulation,
conditional continuity of the nonmanipulator law within each neighborhood and covariate cell,
a shared atom-level retained nonmanipulator mass vector across the nested neighborhoods,
neighborhood-specific global manipulation envelopes \(\bar\rho_j\in[0,1)\), neighborhood-by-cell
caps \(\bar s_{j,w}\in[0,1)\), bounded outcomes, finite support on the right side, positive
retained mass, and positive first-stage denominators. The bounding functional is the vector
identified set \(\Theta_I(P,\bar\rho,\bar s)\) together with the fixed-\(\lambda\) upper-orthant
membership map
\[
  \Phi(P,\bar\rho,\bar s;\lambda)
  =\one\{\exists n\in\mathcal F(P,\bar\rho,\bar s)\text{ such that }\theta_j(n)\le \lambda_j
  \text{ for all }j\},
\]
where \(n=(n_b)_{b=1}^B\) is the shared retained nonmanipulator mass vector and
\(\mathcal F(P,\bar\rho,\bar s)\) is the feasible set defined in Section~6. The computational
upgrade claim is that fixed-\(\lambda\) evaluation admits an explicit min-cost-flow /
total-unimodularity certificate and recovers the parent one-cutoff interval at \(J=1\).

\begin{abstract}
The banked parent proposal \texttt{pid\_rdd\_manipulation\_bounded/v1} gives a sharp
one-cutoff manipulation envelope for a local RD Wald effect. This draft asks for the
computational upgrade needed when the analyst reports sharp bounds jointly across many
nested cutoff neighborhoods instead of one window at a time. The kernel claim is that the
shared nonmanipulator mass vector across nested windows creates a laminar feasibility system,
and that on an explicit discrete shell-mass face the fixed-\(\lambda\) upper-orthant problem
admits an exact incidence-based min-cost-flow representation with a dual certificate that
specializes to the parent \(J=1\) interval. The open part is the passage from that exact
network oracle to the unrestricted finite-support many-window problem. If correct, the result
turns a qualitative many-window sensitivity idea into a computable evaluation map and makes
intersection-bound inference operational for manipulation-robust RD frontiers.
\end{abstract}

\section{Introduction}
The question is whether bounded-manipulation RD sensitivity analysis across many nested
cutoff neighborhoods can be evaluated by one shared computational object rather than by a
separate one-cutoff program at each neighborhood. The headline claim is that, under a shared
retained nonmanipulator mass vector, the many-neighborhood sharp set should admit a
fixed-\(\lambda\) certificate whose discrete shell-mass face is an exact laminar min-cost-flow
oracle; the parent one-cutoff interval is the \(J=1\) corner of that certificate.

Relative to the parent \texttt{pid\_rdd\_manipulation\_bounded/v1}, the delta is computational:
the parent names ratio-indexed endpoint LPs, while this draft names an explicit lifted
many-neighborhood evaluation map. The closest published comparators are
\citet[Abstract]{gerard_rokkanen_rothe_2020_rdbounds}, which gives sharp one-cutoff
manipulated-RD bounds, and \citet[Abstract]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation},
which gives a computation-first partial-identification procedure for manipulated discrete RD.
The precise gap is the conjunction of manipulation-driven partial identification,
nested-window coherence around one fixed cutoff, a corrected centered-score oracle, and an
exact flow certificate on the discrete shell-mass face with a \(J=1\) dual boundary
reduction. The kernel is a PartialID theorem with a computational bridge from one-window
manipulation bounds to a joint nested-window frontier.

The concrete consumer is the one-cutoff RD sensitivity workflow that starts from
\citet[pp.~1450--1451]{cattaneo_jansson_ma_2020_density} and then reports manipulated-RD
bounds neighborhood by neighborhood in the style of \citet{gerard_rokkanen_rothe_2020_rdbounds}.
If the conjectures are correct, that workflow would evaluate one coherent frontier and then
feed the resulting support function into the intersection-bound machinery of
\citet[Sec.~3]{chernozhukov_lee_rosen_2013_intersection_bounds}. The research practice
change is to treat window choice as part of the partial-identification object, not as a post
hoc sensitivity grid.

\begin{itemize}[leftmargin=*]
  \item Theorem 1: the \(J=1\) lifted program reduces to the parent bounded-manipulation interval. Gap: the parent \texttt{pid\_rdd\_manipulation\_bounded/v1} is single-window only. Consumer: \citet{gerard_rokkanen_rothe_2020_rdbounds}.
  \item Conjecture 1: the many-neighborhood identified set equals the image of one shared retained-mass vector. Gap: \citet{gerard_rokkanen_rothe_2020_rdbounds} and \citet{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} are one-window manipulated-RD objects. Consumer: neighborhood-by-neighborhood manipulated-RD sensitivity analysis built from \citet{gerard_rokkanen_rothe_2020_rdbounds}.
  \item Conjecture 2: on the prefix-compressed discrete shell-mass sharp-RD face, full fixed-\(\lambda\) upper-orthant membership is equivalent to a zero-cost layered state-flow circulation with centered score states, hence to a strongly polynomial exact oracle on that face. Gap: \citet{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} gives a one-window computational procedure, while \citet{cattaneo_jansson_ma_2020_density} gives one-window manipulation diagnostics; neither gives a joint nested-window oracle. Consumer: one-cutoff RD sensitivity grids indexed by neighborhood-specific density envelopes.
  \item Conjecture 3: the dual potentials of the flow oracle recover the parent one-window ratio certificate at \(J=1\) and certify a strict joint-versus-separate frontier gap on a two-neighborhood witness. Gap: \citet[Abstract; p.~667]{chernozhukov_lee_rosen_2013_intersection_bounds} needs a computable bound oracle but does not provide the RD-specific dual object. Consumer: the intersection-bound confidence-region machinery of \citet[Sec.~3]{chernozhukov_lee_rosen_2013_intersection_bounds} applied to manipulation-robust RD frontiers.
\end{itemize}

\section{Related work}
\citet{hahn_todd_van_der_klaauw_2001} give the standard sharp and fuzzy RD identification
benchmark. Theorem~\ref{thm:parent-reduction} uses their continuity logic only through the
parent no-manipulation corner.

\citet{lee_2008_local_randomization} [reused from parent] interpret RD as local randomization
under imprecise control and motivate covariate continuity at the cutoff. The present draft
keeps that behavioral motivation but turns covariate failures into bounded manipulation inputs.

\citet{mccrary_2008_density_test} [reused from parent] develop the density-discontinuity
manipulation diagnostic. Here the same object enters only through the neighborhood-specific
global envelopes \(\bar\rho_j\).

\citet{cattaneo_jansson_ma_2020_density} [reused from parent] provide the modern local-polynomial
density estimator used in practice for McCrary-style diagnostics. Conjecture~2 is the missing
map from those diagnostics to a joint many-neighborhood sharp bound.

\citet[Abstract]{gerard_rokkanen_rothe_2020_rdbounds} [reused from parent] are the closest
published comparator. They show that manipulated-RD effects are sharply bounded in a one-cutoff
model and that the manipulation extent can be inferred from data, but they do not promote the
sharp set to a many-neighborhood network certificate.

\citet[Abstract]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} are the closest
computation-side manipulated-RD comparator. Their current abstract states a procedure for partial
identification with a manipulated discrete running variable, but not a joint laminar dual or a
total-unimodularity theorem.

\citet[Abstract; pp.~216--217]{bertanha_2020_many_thresholds} study RD with many thresholds and
show that pooling cutoffs changes the identification and estimation problem even without
manipulation. That paper is a contrast case rather than the direct comparator here: the present
draft fixes one cutoff and varies nested neighborhoods around it.

\citet[pp.~867--868, Sec.~2]{cattaneo_titiunik_vazquez_bare_2020_rdmulti} give the main software
and workflow reference for RD designs with multiple cutoffs or multiple scores. Their package
introduces the commands \texttt{rdmc}, \texttt{rdmcplot}, and \texttt{rdms}, computes
cutoff-specific and pooled RD effects, and explicitly points users to \texttt{rddensity} for
falsification. It is therefore a workflow contrast for true multiple-cutoff designs, not the
direct nested-window comparator for the fixed-cutoff problem in this draft.

\citet[Abstract; p.~667]{chernozhukov_lee_rosen_2013_intersection_bounds} show that many
identified sets can be handled once the bound is represented as an intersection-bound or LP-valued
object. Conjecture~3 supplies the proposed RD-specific oracle.

\citet{ishihara_sawada_2024_manipulation_robust} study low-level conditions for manipulation-robust
point identification in RD. The present draft instead keeps bounded manipulation and asks for a
joint sharp partial-identification computation.

In the repository, \texttt{CausalSmith/doc/API.md} Section~3 states that the PartialID catalogue
is still sparse and organized by future \texttt{pid\_*} entries. The only close in-repo theorem
proposal is the banked parent \texttt{pid\_rdd\_manipulation\_bounded/v1}, whose headline is a
one-cutoff bounded-manipulation interval. No in-catalogue entry records a shared many-neighborhood
retained-mass object or a flow-based certificate for RD manipulation bounds.

\section{Formal setup}
Let \(\mathcal N_1\subset\cdots\subset\mathcal N_J\) be nested cutoff neighborhoods around a
fixed RD cutoff \(c\). For each neighborhood \(j\), let \(P_{j,-}\) and \(P_{j,+}\) denote the
left- and right-cutoff weak limits of \((Y,D,W)\), where \(Y\in[\underline y,\overline y]\),
\(D\in\{0,1\}\), and \(W\in\{1,\ldots,K\}\) is a finite predetermined-covariate cell. Write
\(\pi_{j,-}(w)=P_{j,-}(W=w)\),
\(\mu^Y_{j,-}(w)=\E_{P_{j,-}}[Y\mid W=w]\),
and \(\mu^D_{j,-}(w)=\E_{P_{j,-}}[D\mid W=w]\).

The right side is partitioned into finitely many finest atoms \(b=1,\ldots,B\). Atom \(b\)
carries observed mass \(p_b>0\), outcome \(y_b\), treatment value \(d_b\), covariate cell
\(w_b\), and incidence indicators \(I_j(b)\in\{0,1\}\), where \(I_j(b)=1\) if atom \(b\) lies
inside neighborhood \(\mathcal N_j\). Nestedness means \(I_j(b)\le I_{j+1}(b)\) for all
\(j<J\). Let \(s(b)=\min\{j:I_j(b)=1\}\) denote the entry shell of atom \(b\).

A candidate shared nonmanipulator law is represented by retained masses
\[
  n=(n_1,\ldots,n_B),\qquad 0\le n_b\le p_b.
\]
For neighborhood \(j\), define retained mass
\[
  M_j(n)=\sum_{b=1}^B I_j(b)n_b,
\]
cellwise retained mass
\[
  M_{j,w}(n)=\sum_{b:w_b=w} I_j(b)n_b,
\]
and observed right-side cell mass
\[
  P_{j,+}(W=w)=\sum_{b:w_b=w} I_j(b)p_b.
\]
The laminar feasible set \(\mathcal F(P,\bar\rho,\bar s)\) is the set of \(n\) such that, for
every neighborhood \(j\),
\begin{align}
  \sum_{b=1}^B I_j(b)(p_b-n_b) &\le \bar\rho_j \sum_{b=1}^B I_j(b)p_b,
  \label{eq:global-budget} \\
  \sum_{b:w_b=w} I_j(b)(p_b-n_b) &\le \bar s_{j,w} P_{j,+}(W=w)
  \quad\text{for each }w, \label{eq:cell-budget} \\
  M_{j,w}(n) &= \pi_{j,-}(w) M_j(n) \quad\text{for each }w. \label{eq:matchW}
\end{align}
Equation~\eqref{eq:matchW} is the retained-covariate-law restriction. Because the same \(n_b\)
enters every neighborhood containing atom \(b\), the feasible set is not a Cartesian product
of one-window problems.

For each neighborhood \(j\), define
\[
  N_j^Y(n)=\sum_{b=1}^B I_j(b)n_b y_b
  - M_j(n)\sum_w \pi_{j,-}(w)\mu^Y_{j,-}(w),
\]
\[
  N_j^D(n)=\sum_{b=1}^B I_j(b)n_b d_b
  - M_j(n)\sum_w \pi_{j,-}(w)\mu^D_{j,-}(w),
\]
and
\[
  \theta_j(n)=\frac{N_j^Y(n)}{N_j^D(n)}.
\]
The structural identified set is
\[
  \Theta_I(P,\bar\rho,\bar s)=
  \left\{
    \vartheta\in\R^J:
    \begin{array}{l}
      \text{there exists a structural completion satisfying one-sided manipulation,} \\
      \text{conditional continuity, the neighborhood budgets, the cell caps, and} \\
      \text{positive first stages, whose neighborhood-wise nonmanipulator Wald vector is }\vartheta
    \end{array}
  \right\}.
\]
For a candidate vector \(\lambda=(\lambda_1,\ldots,\lambda_J)\), define the fixed-\(\lambda\)
upper-orthant feasibility system
\[
  \Psi(P,\bar\rho,\bar s;\lambda)=
  \left\{
    n\in\mathcal F(P,\bar\rho,\bar s):
    N_j^Y(n)-\lambda_j N_j^D(n)\le 0\ \forall j
  \right\}.
\]
Under positive first stages, \(\Psi(P,\bar\rho,\bar s;\lambda)\neq\varnothing\) is equivalent
to \(\theta_j(n)\le \lambda_j\) for all \(j\).

For a monotone retained-mass chain \(m=(m_1,\ldots,m_J)\) with \(m_j=M_j(n)\), define shell
demands
\[
  q_{j,w}(m)=\pi_{j,-}(w)m_j-\pi_{j-1,-}(w)m_{j-1},
  \qquad \pi_{0,-}(w)m_0:=0.
\]
When \(q_{j,w}(m)\ge 0\) for all \(j,w\), these are the retained shell masses in cell \(w\).
On that face, a retained mass plan can be represented by shell flows that enter at shell
\(s(b)\), move forward along the neighborhood chain, and exit to the shell-cell sink
\((j,w_b)\) in amount \(q_{j,w_b}(m)\).

For the strict joint-versus-separate comparison, let \(\mathcal F_j(P,\bar\rho_j,\bar s_j)\)
be the one-window feasible set obtained by keeping only neighborhood \(j\)'s constraints, and
define for \(\omega\in\R_+^J\),
\[
  H(\omega)=\sup_{n\in\mathcal F(P,\bar\rho,\bar s)} \sum_{j=1}^J \omega_j \theta_j(n),
  \qquad
  H_{\mathrm{sep}}(\omega)=
  \sum_{j=1}^J \omega_j \sup_{n^{(j)}\in \mathcal F_j(P,\bar\rho_j,\bar s_j)} \theta_j(n^{(j)}).
\]

For computation under finite support, the lifted zero-slack oracle keeps the same feasibility
problem \(\Psi(P,\bar\rho,\bar s;\lambda)\), but on the discrete shell-mass face it is rewritten
as a layered circulation on breakpoint states. Let \(m_j=M_j(n)\) and define neighborhood score
slack
\[
  \sigma_j(n;\lambda)=\lambda_j N_j^D(n)-N_j^Y(n)
  =
  \sum_{b=1}^B I_j(b)n_b\,\xi_{j,b}(\lambda).
\]
where
\[
  \xi_{j,b}(\lambda)
  =
  \lambda_j d_b-y_b+c_j(\lambda_j),
  \qquad
  c_j(\lambda_j)
  =
  \sum_w \pi_{j,-}(w)\{\mu^Y_{j,-}(w)-\lambda_j\mu^D_{j,-}(w)\}.
\]
Under positive first stages, \(\theta_j(n)\le \lambda_j\) is equivalent to
\(\sigma_j(n;\lambda)\ge 0\). Under sharp RD with zero left-side means, this collapses to
\(\xi_{j,b}(\lambda)=\lambda_j-y_b\). Let
\(\mathcal M_j\) be the retained-mass breakpoint set generated by the atom masses entering
neighborhood \(j\) together with the lower and upper bounds implied by
\eqref{eq:global-budget}--\eqref{eq:cell-budget}, and let \(\Sigma_j(\lambda)\) be the score-slack
breakpoint set generated by cumulative mass-scaled centered increments
\(p_b\xi_{j,b}(\lambda)\). The state graph
\(\mathsf{STATEFLOW}_\lambda(P,\bar\rho,\bar s)\) has one layer per neighborhood, nodes
\((j,m,\sigma)\in\mathcal M_j\times\Sigma_j(\lambda)\), source-to-atom arcs with capacities
\(p_b\), shell-propagation arcs carrying retained mass forward from \(s(b)\), shell-cell demand
arcs enforcing \(q_{j,w}(m)\), and state-transition arcs that update \((m,\sigma)\) by the atom's
mass and mass-scaled centered score increment whenever that atom is retained. The fixed-\(\lambda\) orthant
problem is therefore encoded as feasibility of a zero-cost circulation that remains in the
nonnegative-slack slice \(\sigma\ge 0\) in every layer. Conjecture~\ref{conj:flow} is the claim
that this state-graph oracle is exact on the discrete shell-mass face, that its constraint matrix
is the node--arc incidence matrix of the layered graph, and that it reduces to the parent
ratio-indexed certificate at \(J=1\).

\begin{verbatim}
Locked parameters.
qid = pid_rdd_flow_manipulation
specialization = v1
observable distribution P = left/right cutoff limits {P_{j,-}, P_{j,+}} for nested
  neighborhoods j=1,...,J plus a finite finest right-side partition b=1,...,B
parameter theta = vector of nonmanipulator local Wald effects (theta_1,...,theta_J)
identifying restrictions = one-sided upward manipulation; conditional continuity within
  each neighborhood and covariate cell; one shared retained nonmanipulator mass vector
  across nested neighborhoods; neighborhood-specific global envelopes rho_bar_j;
  neighborhood-by-cell caps s_bar_{j,w}; bounded outcomes; finite right support;
  positive retained mass; positive first stages
bounding functional = vector identified set Theta_I(P,rho_bar,s_bar), fixed-lambda
  orthant-membership map Phi(P,rho_bar,s_bar; lambda), and support values H(omega)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Nested finite support]\label{ass:nested-support}
The family \(\mathcal N_1\subset\cdots\subset\mathcal N_J\) is finite and nested. The right-side
law admits a finite finest partition \(b=1,\ldots,B\) with masses \(p_b>0\), and
\(\pi_{j,-}(w)>0\) whenever neighborhood \(j\) uses covariate cell \(w\).
\end{assumption}

\begin{assumption}[One-sided manipulation with a shared latent law]\label{ass:shared-law}
Manipulators can only add mass on the treatment side of the cutoff. There exists one latent
nonmanipulator mass vector \(n\) on the finest right-side partition whose restriction to each
neighborhood \(j\) generates the neighborhood-\(j\) right-limit nonmanipulator law.
\end{assumption}

\begin{assumption}[Conditional continuity]\label{ass:conditional-continuity}
For each neighborhood \(j\), the left-limit law \(P_{j,-}\) equals the covariate distribution
of the neighborhood-\(j\) nonmanipulator law, and the retained right-side conditional means
identify the right-limit nonmanipulator means within each covariate cell.
\end{assumption}

\begin{assumption}[Neighborhood envelopes and cell caps]\label{ass:budgets}
The shared retained-mass vector satisfies \eqref{eq:global-budget}--\eqref{eq:matchW}, and the
feasible set \(\mathcal F(P,\bar\rho,\bar s)\) is nonempty.
\end{assumption}

\begin{assumption}[Positive first stages]\label{ass:first-stage}
There exists \(\kappa>0\) such that \(N_j^D(n)\ge \kappa\) for every
\(n\in\mathcal F(P,\bar\rho,\bar s)\) and every neighborhood \(j\).
\end{assumption}

\begin{assumption}[Sharp-RD computational face]\label{ass:sharp-rd}
For results that invoke the flow certificate, \(D=Z\) almost surely in every neighborhood.
Hence \(d_b=1\) on the right-side atoms and the denominator simplifies to \(N_j^D(n)=M_j(n)\).
\end{assumption}

\begin{assumption}[Discrete shell-flow face]\label{ass:rational}
For results that invoke the flow oracle, there exists a mass unit \(\delta>0\) such that every
\(p_b\), every neighborhood total \(\sum_b I_j(b)p_b\), and every shell demand \(q_{j,w}(m)\) on
the retained-mass chain under study is an integer multiple of \(\delta\). In addition,
\(q_{j,w}(m)\ge0\) for all \(j,w\), and every mass-scaled score increment \(p_b(y_b-\lambda_j)\) belongs to a
common finite breakpoint lattice used to index \(\Sigma_j(\lambda)\). Thus the retained cell
masses can be routed forward along the nested shell chain without signed withdrawals, and the
score constraints can be tracked by finitely many breakpoint states rather than by free side
constraints.
\end{assumption}

\begin{assumption}[Prefix-compressed breakpoint face]\label{ass:compression}
For results that invoke the strongly-polynomial flow oracle, fix \(\lambda\) and order the atoms
entering each neighborhood by shell and then by weakly decreasing score contribution
\(y_b-\lambda_j\) within shell-cell blocks. Every extreme point relevant for
\(\Psi(P,\bar\rho,\bar s;\lambda)\) retains a prefix of that order in each block, with at most one
fractional breakpoint atom per block. Consequently the admissible retained-mass states and
score-slack states are cumulative prefix values, so each layer satisfies
\[
  |\mathcal M_j|\le B+1,
  \qquad
  |\Sigma_j(\lambda)|\le B+1.
\]
\end{assumption}

\begin{assumption}[Parent reduction face]\label{ass:parent-face}
For the parent reduction, \(J=1\), the single neighborhood is the parent cutoff window, and the
budgets \((\bar\rho_1,\bar s_{1,w})\) coincide with the one-cutoff bounded-manipulation
specification of \texttt{pid\_rdd\_manipulation\_bounded/v1}.
\end{assumption}

\begin{assumption}[Two-neighborhood strict-gap witness class]\label{ass:strict-gap}
For the strict joint-versus-separate comparison, \(J=2\), \(K=2\), \(D=Z\), left-side outcome
means are zero, and there exist three right-side atoms \(b=1,2,3\) with incidence pattern
\(I_1=(1,0,0)\), \(I_2=(1,1,1)\), covariate cells \(w_1=w_2=1\), \(w_3=2\), masses
\((p_1,p_2,p_3)=(2/5,1/5,2/5)\), outcomes \((y_1,y_2,y_3)=(0,1,0)\), shares
\(\pi_{1,-}(1)=1\) and \((\pi_{2,-}(1),\pi_{2,-}(2))=(1/2,1/2)\), and budgets
\(\bar\rho_1=0\), \(\bar\rho_2=1/5\), \(\bar s_{2,1}=2/3\), and \(\bar s_{2,2}=1/2\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: parent reduction]\label{thm:parent-reduction}
Under Assumptions~\ref{ass:nested-support}--\ref{ass:parent-face}, the many-neighborhood
feasible set collapses to the parent one-window retention class after the identification
\(n_b=p_b a_b\). Consequently, \(\Theta_I(P,\bar\rho,\bar s)\) is exactly the parent
one-cutoff bounded-manipulation interval, and
\(\Psi(P,\bar\rho,\bar s;\lambda_1)\neq\varnothing\) is exactly the parent ratio-indexed
endpoint feasibility problem.
\end{theorem}

With \(J=1\), every finest atom belongs to the same neighborhood and
\eqref{eq:global-budget}--\eqref{eq:matchW} reduce to the parent constraints. Substituting
\(n_b=p_b a_b\) turns the numerator and denominator into the parent one-cutoff Wald program.

\begin{conjecture}[Conjecture 1: shared-image characterization]\label{conj:shared-image}
(NOT YET PROVED.) Under Assumptions~\ref{ass:nested-support}--\ref{ass:first-stage},
\[
  \Theta_I(P,\bar\rho,\bar s)=\{\theta(n):n\in\mathcal F(P,\bar\rho,\bar s)\}.
\]
Equivalently, for every \(\lambda\in\R^J\),
\[
  \Phi(P,\bar\rho,\bar s;\lambda)=1
  \quad\Longleftrightarrow\quad
  \Psi(P,\bar\rho,\bar s;\lambda)\neq\varnothing.
\]
\end{conjecture}

\begin{conjecture}[Conjecture 2: laminar min-cost-flow certificate]\label{conj:flow}
(NOT YET PROVED.) Under Assumptions~\ref{ass:nested-support}--\ref{ass:rational}, and under
Assumptions~\ref{ass:sharp-rd} and~\ref{ass:compression}, the fixed-\(\lambda\) problem
\(\Psi(P,\bar\rho,\bar s;\lambda)\) is equivalent to feasibility of the layered circulation
\(\mathsf{STATEFLOW}_\lambda(P,\bar\rho,\bar s)\) defined in Section~6. In that circulation,
the layer-\(j\) state \((m,\sigma)\) records retained mass and score slack after neighborhood
\(j\), source--atom arcs encode the common retained-mass vector, shell-propagation arcs encode
nestedness, shell-cell demand arcs encode the covariate-balance and cell-cap restrictions, and
state-transition arcs encode the update
\[
  (m,\sigma)\mapsto (m+p_b,\sigma+p_b\xi_{j,b}(\lambda))
\]
whenever atom \(b\) is retained through neighborhood \(j\). Thus all neighborhood score
inequalities are encoded as ordinary path feasibility inside the nonnegative-slack slice
\(\sigma\ge 0\), not as external side constraints. After scaling by \(1/\delta\), the
constraint matrix is the node--arc incidence matrix of the layered graph and is therefore
totally unimodular. Under Assumption~\ref{ass:compression}, the explicit breakpoint graph has at
most
\[
  N_\lambda \le J(B+1)^2 + O(JKB)
\]
state and bookkeeping nodes and
\[
  A_\lambda = O(JK(B+1)^2)
\]
arcs. Hence fixed-\(\lambda\) upper-orthant membership is solvable in strongly polynomial time on
this prefix-compressed discrete shell-mass face by applying a classical strongly-polynomial
min-cost-flow algorithm to the graph with \((N_\lambda,A_\lambda)\) as the input size.
\end{conjecture}

\begin{conjecture}[Conjecture 3: dual recovery and strict joint gain]\label{conj:dual-gap}
(NOT YET PROVED.) Under Assumptions~\ref{ass:nested-support}--\ref{ass:rational}, and under
Assumptions~\ref{ass:sharp-rd} and~\ref{ass:strict-gap}, the dual of
\(\mathsf{STATEFLOW}_\lambda(P,\bar\rho,\bar s)\) admits neighborhood potentials
\((\alpha_j,\eta_{j,w},\nu_j)\) together with arc reduced-cost slacks \(\beta\) such that:
\begin{enumerate}[leftmargin=*]
  \item if \(J=1\), the dual value coincides with the parent one-cutoff ratio certificate;
  \item for the witness weight vector \(\omega^\star=(1,1)\),
  \[
    H(\omega^\star)<H_{\mathrm{sep}}(\omega^\star);
  \]
  \item the strict inequality persists on an open neighborhood of the witness data and budget
  parameters that preserves the atom ordering and positive first stages.
\end{enumerate}
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Corollary 1: parent corner]\label{cor:parent-corner}
Under Assumptions~\ref{ass:nested-support}--\ref{ass:parent-face},
Theorem~\ref{thm:parent-reduction} collapses to the banked parent
\texttt{pid\_rdd\_manipulation\_bounded/v1}. The reduction holds because the shared retained-mass
vector has only one neighborhood coordinate, so the many-neighborhood geometry disappears.
\end{corollary}

\begin{corollary}[Corollary 2: no-manipulation face]\label{cor:no-manip}
Under Assumptions~\ref{ass:nested-support}--\ref{ass:first-stage}, if \(\bar\rho_j=0\),
\(\bar s_{j,w}=0\), and \(P_{j,+}(W=w)=\pi_{j,-}(w)\) for every \(j,w\), then
\(\mathcal F(P,0,0)=\{p\}\) and
\[
  \Theta_I(P,0,0)
  =
  \left\{
    \left(
      \frac{\E_{P_{1,+}}[Y]-\E_{P_{1,-}}[Y]}{\E_{P_{1,+}}[D]-\E_{P_{1,-}}[D]},
      \ldots,
      \frac{\E_{P_{J,+}}[Y]-\E_{P_{J,-}}[Y]}{\E_{P_{J,+}}[D]-\E_{P_{J,-}}[D]}
    \right)
  \right\}.
\]
The reduction holds because no atom can be removed in any neighborhood, so \(n_b=p_b\) for all
\(b\).
\end{corollary}

\paragraph{Exhibit 9.1: the shell-flow oracle on a two-neighborhood instance.}
Take \(J=2\), \(K=2\), \(B=3\), shell entries \(s(1)=1\), \(s(2)=2\), \(s(3)=2\), masses
\((p_1,p_2,p_3)=(1/2,1/4,1/4)\), covariate cells \((w_1,w_2,w_3)=(1,1,2)\), outcomes
\((y_1,y_2,y_3)=(0,1,0)\), sharp RD so \(d_b=1\) for all \(b\), left-side means zero,
\(\pi_{1,-}(1)=1\), \((\pi_{2,-}(1),\pi_{2,-}(2))=(3/4,1/4)\), budgets \(\bar\rho_1=\bar\rho_2=0\),
and \(\lambda=(0,1/4)\). The feasible retained vector is \(n=p\), hence
\[
  m_1=\frac12,\qquad m_2=1,\qquad
  q_{1,1}(m)=\frac12,\qquad q_{2,1}(m)=\frac14,\qquad q_{2,2}(m)=\frac14.
\]
With \(\delta=1/4\), the flow network has four units: two units of atom \(1\) enter shell \(1\),
one unit of atom \(2\) enters shell \(2\), and one unit of atom \(3\) enters shell \(2\). The
unique feasible withdrawals are two units to sink \((1,1)\), one unit to sink \((2,1)\), and one
unit to sink \((2,2)\). The neighborhood score totals are
\[
  c_1(\lambda_1)=c_2(\lambda_2)=0,\qquad
  \sigma_1=\lambda_1 N_1^D(n)-N_1^Y(n)
  =0\cdot \frac12-\frac12\cdot 0=0,
  \qquad
  \sigma_2=\lambda_2 N_2^D(n)-N_2^Y(n)
  =\frac14\cdot 1-\left(\frac12\cdot 0+\frac14\cdot 1+\frac14\cdot 0\right)=0.
\]
Equivalently, the retained atoms contribute mass-scaled score increments
\[
  p_1\xi_{2,1}(\lambda)=\frac18,\qquad
  p_2\xi_{2,2}(\lambda)=-\frac{3}{16},\qquad
  p_3\xi_{2,3}(\lambda)=\frac{1}{16},
\]
whose sum is zero. Hence the zero-slack optimum is attained, and the layer-2 slack state is
\(\sigma_2=0\). The constraint matrix is the node--arc incidence matrix of the
source/atom/shell-cell/state graph, so the exhibit computes the announced fixed-\(\lambda\) oracle
from the Section~6 primitives and passes the internal-consistency check.

\paragraph{Exhibit 9.2: the \(J=1\) dual certificate.}
Take \(J=1\), \(K=1\), \(B=2\), masses \((1/2,1/2)\), outcomes \((1,0)\), sharp RD, zero
left-side means, \(\bar\rho_1=1/2\), and \(\lambda_1=1\). The parent-feasible optimum retains
only the high-outcome atom, so \(n=(1/2,0)\), \(m_1=1/2\), and the parent upper endpoint is
\[
  \theta_1(n)=\frac{(1/2)\cdot 1}{1/2}=1.
\]
The fixed-\(\lambda\) certificate now targets the tight root \(\lambda_1=1\), and the centered
score slack is
\[
  c_1(\lambda_1)=0,\qquad
  \sigma_1=\lambda_1 N_1^D(n)-N_1^Y(n)
  =1\cdot \frac12-\frac12\cdot 1=0.
\]
The retained high-outcome atom has centered increment \(p_1\xi_{1,1}(\lambda)=0\), while the
low-outcome atom has centered increment \(p_2\xi_{1,2}(\lambda)=1/2\). Hence only the path
retaining the high atom can terminate in the zero-slack node. The parent endpoint LP on this
instance is
\[
  \max_{0\le n_b\le p_b,\ n_1+n_2=1/2} n_1.
\]
Its dual is
\[
  \min_{\alpha_1\in\R,\ \beta_1,\beta_2\ge 0}
  \frac12\alpha_1+\frac12\beta_1+\frac12\beta_2
  \quad\text{subject to}\quad
  \alpha_1+\beta_1\ge 1,\qquad
  \alpha_1+\beta_2\ge 0.
\]
The dual optimum is attained at
\[
  \alpha_1=0,\qquad \eta_{1,1}=0,\qquad \nu_1=1,\qquad \beta_1=1,\qquad \beta_2=0,
\]
where \(\eta_{1,1}=0\) because there is only one cell and \(\nu_1=1\) is the normalized
zero-slack state potential attached to the binding endpoint \(\lambda_1=1\). Dual feasibility
holds because \(0+1\ge 1\) and \(0+0\ge 0\). Complementary slackness holds because
\[
  \beta_1(p_1-n_1)=1\cdot 0=0,\qquad
  \beta_2(p_2-n_2)=0\cdot \frac12=0,
\]
\[
  n_1(\alpha_1+\beta_1-1)=\frac12(0+1-1)=0,\qquad
  n_2(\alpha_1+\beta_2-0)=0.
\]
The primal and dual objective values both equal \(1/2\). Dividing by \(m_1=1/2\) recovers the
parent ratio certificate \(\lambda_1=1\). This is the announced \(J=1\) boundary recovery.

\paragraph{Exhibit 9.3: strict joint-versus-separate gap.}
Under Assumption~\ref{ass:strict-gap}, the inner neighborhood must retain the low-outcome atom
\(b=1\) in full, so every joint feasible vector satisfies \(n_1=2/5\). The outer neighborhood
must match cell shares \((1/2,1/2)\) with retained mass at least \(4/5\), which then forces the
joint optimizer to take \(n=(2/5,0,2/5)\) and hence \(\theta_1(n)=0\), \(\theta_2(n)=0\), and
\(H(\omega^\star)=0\) at \(\omega^\star=(1,1)\). If the two neighborhoods are solved separately,
the outer problem may choose \(n^{(2)}=(1/5,1/5,2/5)\), which still matches the outer cell
shares and gives \(\theta_2(n^{(2)})=1/4\). Therefore
\[
  H_{\mathrm{sep}}(\omega^\star)=0+\frac14>\,0=H(\omega^\star),
\]
and the difference is not a normalization artifact because both objects use the same weight
vector \(\omega^\star\), the same budgets, and the same Section~6 primitives.

\section{Proof-sketch route}
The mathematical route is explicit. Conjecture~\ref{conj:shared-image}
\(\leftarrow\) unfold Section~6 structural compatibility
\(\leftarrow\) mixture-to-retained-mass equivalence on the finest partition
\(\leftarrow\) disintegration across nested windows with one shared latent law
\(\leftarrow\) prove that the covariate-balance equations \eqref{eq:matchW} are the exact
observable image of conditional continuity
\(\leftarrow\) apply positive-first-stage continuity of the Wald map. This gives \(k=4\)
substantive non-definitional steps. Conjecture~\ref{conj:flow}
\(\leftarrow\) pass from cumulative retained masses to shell demands \(q_{j,w}(m)\)
\(\leftarrow\) rewrite each neighborhood inequality as the centered slack
\(\sigma_j(n;\lambda)=\lambda_j N_j^D(n)-N_j^Y(n)\)
\(\leftarrow\) add score-slack states \(\sigma_j\) so each centered inequality is absorbed into
ordinary state transitions
\(\leftarrow\) build the exact source/atom/shell-cell/state graph for the fixed-\(\lambda\) problem
\(\leftarrow\) identify the oracle with a layered circulation whose matrix is node--arc incidence
\(\leftarrow\) use Assumption~\ref{ass:compression} to replace arbitrary subset sums by cumulative
prefix states with \(|\mathcal M_j|,|\Sigma_j(\lambda)|\le B+1\)
\(\leftarrow\) apply a classical strongly-polynomial min-cost-flow theorem on the explicit graph
with \(N_\lambda \le J(B+1)^2 + O(JKB)\) nodes and \(A_\lambda = O(JK(B+1)^2)\) arcs; this gives
\(k=6\). Conjecture~\ref{conj:dual-gap}
\(\leftarrow\) write the network-flow dual explicitly
\(\leftarrow\) identify the \(J=1\) dual with the parent ratio certificate
\(\leftarrow\) compute the witness support values \(H(\omega^\star)\) and
\(H_{\mathrm{sep}}(\omega^\star)\)
\(\leftarrow\) prove local persistence of the strict gap by active-set stability; this gives
\(k=4\). The boundary algebra is concentrated in the \(J=1\) corner, the two-neighborhood
strict-gap witness, and the shell-demand decomposition.

\section{Honest scope flags}
Theorem~\ref{thm:parent-reduction} is routine. Conjectures~\ref{conj:shared-image},
\ref{conj:flow}, and~\ref{conj:dual-gap} are the open flagship statements. The computational
upgrade is stated only on the sharp-RD face; the fuzzy-RD Wald denominator remains coupled and
is not claimed to inherit the same min-cost-flow structure. Continuous covariates are not
covered; the draft keeps the finite-cell convention of the parent and upgrades only the
many-neighborhood computation. No earlier version of this angle was accepted, so nothing is
withdrawn inside this angle. The most delicate restrictions are the discrete shell-flow face in
Assumption~\ref{ass:rational} and the prefix-compression face in
Assumption~\ref{ass:compression}; outside those faces the proposal only claims a lifted LP
oracle, not an exact incidence-based network representation or a strongly-polynomial graph bound.
The strict-gap witness now uses admissible cell caps strictly below one, so the comparison stays
inside the locked parameter domain.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
  \item v1 (pivot) --- initial draft for the laminar total-unimodularity / strongly-polynomial upgrade angle; prior verdict: none.
  \item v2 (revise) --- replaced the overbroad TU claim by an exact discrete shell-flow oracle, repaired Exhibit 9.1 on a \(K=2\) instance, and named the \texttt{rdmulti}/\texttt{rddensity} consumers at their cited locations; prior verdict: REVISE.
  \item v3 (revise) --- replaced the fixed-\(m\) subroutine claim by a full fixed-\(\lambda\) layered state-flow certificate, corrected the Exhibit 9.1 arithmetic, and moved the strict-gap witness caps back inside \([0,1)\); prior verdict: REVISE.
  \item v4 (revise) --- mass-scaled the score-state algebra, restricted the strongly-polynomial claim to the prefix-compressed breakpoint face with explicit graph-size bounds, and aligned the \(J=1\) dual exhibit with the parent endpoint certificate; prior verdict: REVISE.
  \item v5 (revise) --- centered the fixed-\(\lambda\) score algebra with the left-limit residual term, replaced the many-cutoff comparator chain by nested-window manipulated-RD comparators, and computed the \(J=1\) dual variables with feasibility and complementary-slackness checks; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bertanha(2020)]{bertanha_2020_many_thresholds}
Bertanha, Marinho.
2020.
Regression discontinuity design with many thresholds.
\emph{Journal of Econometrics} 218(1): 216--241.

\bibitem[Cattaneo, Jansson, and Ma(2020)]{cattaneo_jansson_ma_2020_density}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem[Cattaneo, Titiunik, and Vazquez-Bare(2020)]{cattaneo_titiunik_vazquez_bare_2020_rdmulti}
Cattaneo, Matias D., Rocio Titiunik, and Gonzalo Vazquez-Bare.
2020.
Analysis of regression-discontinuity designs with multiple cutoffs or multiple scores.
\emph{Stata Journal} 20(4): 866--891.

\bibitem[Chernozhukov, Lee, and Rosen(2013)]{chernozhukov_lee_rosen_2013_intersection_bounds}
Chernozhukov, Victor, Sokbae Lee, and Adam M. Rosen.
2013.
Intersection bounds: Estimation and inference.
\emph{Econometrica} 81(2): 667--737.

\bibitem[Gerard, Rokkanen, and Rothe(2020)]{gerard_rokkanen_rothe_2020_rdbounds}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem[Hahn, Todd, and van der Klaauw(2001)]{hahn_todd_van_der_klaauw_2001}
Hahn, Jinyong, Petra Todd, and Wilbert van der Klaauw.
2001.
Identification and estimation of treatment effects with a regression-discontinuity design.
\emph{Econometrica} 69(1): 201--209.

\bibitem[Ishihara and Sawada(2024)]{ishihara_sawada_2024_manipulation_robust}
Ishihara, Takuya, and Masayuki Sawada.
2024.
Manipulation-robust regression discontinuity design.
arXiv:2009.07551, version 7.

\bibitem[Lee(2008)]{lee_2008_local_randomization}
Lee, David S.
2008.
Randomized experiments from non-random selection in U.S. House elections.
\emph{Journal of Econometrics} 142(2): 675--697.

\bibitem[McCrary(2008)]{mccrary_2008_density_test}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem[Rosenman et~al.(2019)]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation}
Rosenman, Evan, Karthik Rajkumar, Romain Gauriot, and Robert Slonim.
2019.
Donor's deferral and return behavior: Partial identification from a regression discontinuity design with manipulation.
arXiv:1910.02170.
\end{thebibliography}

\end{document}
