% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_rdd\_flow\_manipulation} / \texttt{v1}%
  \\ \large\textit{Laminar flow certificates for manipulation-robust RD bounds across nested cutoff neighborhoods}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal.  The locked tuple is
\[
  (\texttt{qid}, \texttt{specialization}, P, \theta, \text{identifying restrictions},
    \text{bounding functional})
\]
with the following convention.  \(\texttt{qid}=\texttt{pid\_rdd\_flow\_manipulation}\) and
\(\texttt{specialization}=\texttt{v1}\).  The observable distribution \(P\) consists of the
left- and right-cutoff weak limits \(\{P_{j,-},P_{j,+}\}_{j=1}^J\) for a nested family of
cutoff neighborhoods \(\calN_1\subset\cdots\subset\calN_J\), together with a finite finest
partition of the right side into atoms \(b=1,\ldots,B\) that records each atom's
neighborhood-incidence pattern, predetermined covariate cell \(W_b\in\{1,\ldots,K\}\),
outcome value \(Y_b\in[\underline y,\overline y]\), treatment value \(D_b\in\{0,1\}\), and
observed right-side mass \(p_b\).  The parameter is the vector
\(\theta=(\theta_1,\ldots,\theta_J)\), where
\[
  \theta_j=
  \frac{\sum_w \pi_{j,-}(w)\{\mu^Y_{j,+,0}(w)-\mu^Y_{j,-}(w)\}}
       {\sum_w \pi_{j,-}(w)\{\mu^D_{j,+,0}(w)-\mu^D_{j,-}(w)\}}
\]
is the nonmanipulator local Wald effect in neighborhood \(j\).  The identifying restrictions
are: one-sided upward manipulation, local continuity of the nonmanipulator law within each
neighborhood and covariate cell, a shared atom-level nonmanipulator mass vector across the
nested neighborhoods, neighborhood-specific global manipulation envelopes
\(\bar\rho_j\in[0,1)\), neighborhood-by-cell caps \(\bar s_{j,w}\in[0,1)\), bounded outcomes,
positive retained mass, and positive first-stage denominators.  The bounding functional is the
joint identified set of neighborhood-wise Wald vectors compatible with these restrictions.
For computation, the focal object is the orthant-membership map
\[
  \Phi(P,\bar\rho,\bar s;\lambda)
  =\one\{\exists n\in\calN(P,\bar\rho,\bar s)\text{ with }\theta_j(n)\le \lambda_j
  \text{ for all }j\},
\]
where \(n=(n_b)_{b=1}^B\) is the shared retained nonmanipulator mass on the finest partition,
\(\calN(P,\bar\rho,\bar s)\) is the laminar feasible set defined in Section~6, and
\(\theta(n)\) stacks the neighborhood-specific Wald ratios.  The upgrade claim is that
fixed-\(\lambda\) evaluation admits an explicit lifted min-cost-flow / total-unimodularity
certificate.

\begin{abstract}
The banked parent proposal \texttt{pid\_rdd\_manipulation\_bounded/v1} gives a sharp
one-cutoff manipulation envelope for a local RD Wald effect.  This draft asks for the
computational upgrade needed when the analyst reports bounds jointly across many nested cutoff
neighborhoods rather than at one window in isolation.  The kernel claim is that a shared
nonmanipulator mass vector across nested windows creates a laminar feasible set, and that the
fixed-\(\lambda\) orthant-membership problem for the resulting vector identified set reduces to
an explicit lifted linear program whose core is a laminar min-cost-flow network and whose full
constraint matrix is total unimodular under finite support and rational scaling.  The one-window
dual must collapse to the parent ratio-indexed interval as its \(J=1\) face.  If correct, the
result would turn a banked one-cutoff sharpness statement into a computable many-window
sensitivity frontier and make intersection-bound inference operational in manipulation-robust RD.
\end{abstract}

\section{Introduction}
Manipulation-robust RD analysis is usually reported one neighborhood at a time.  The parent
\texttt{pid\_rdd\_manipulation\_bounded/v1} already gives a sharp one-cutoff envelope.  The
question here is whether the same bounded-manipulation model admits a computationally explicit
joint bound when the analyst wants all nested cutoff neighborhoods to be valid at once.  The
headline claim is Conjecture~\ref{conj:flow-certificate}: under a shared nonmanipulator mass
vector across nested windows, the candidate vector \(\lambda\) belongs to the upper orthant of
the identified set if and only if a lifted laminar program has zero optimal slack.

The upgrade delta relative to the parent is computational, not conceptual.  The parent banked
entry reduces one-cutoff endpoints to linear programs indexed by a candidate ratio; this draft
replaces that scalar-family description with a shared many-window object whose fixed-\(\lambda\)
evaluation should be a strongly polynomial lifted flow problem.  The closest published
comparators are \citet[Abstract; pp.~216--217]{bertanha_2020_many_thresholds}, which studies
many-threshold RD under point-identifying assumptions rather than manipulation bounds, and
\citet[Abstract; p.~667]{chernozhukov_lee_rosen_2013_intersection_bounds}, which gives inference
for bounds defined by rich inequality systems but does not supply the RD-specific evaluation
map.  Relative to the parent \texttt{pid\_rdd\_manipulation\_bounded/v1}, the new object is the
lifted laminar feasibility certificate itself.  The kernel lives in partial identification, with
a computational bridge to the many-cutoff RD and intersection-bounds literatures.

The immediate downstream consumer is RD practice that reports manipulation diagnostics over a
grid of bandwidths or cutoff neighborhoods.  A verified flow certificate would let those
applications replace disconnected one-window envelopes with a joint feasible region that
respects the same latent nonmanipulator mass across windows, and it would give the
Chernozhukov--Lee--Rosen inference machinery a concrete support-function oracle.  A reader would
then compute a joint sensitivity frontier, not a list of unrelated interval endpoints.

\begin{itemize}[leftmargin=*]
  \item Theorem 1: The \(J=1\) laminar program reduces to the parent one-cutoff bounded-manipulation interval. Gap: parent \texttt{pid\_rdd\_manipulation\_bounded/v1} is single-window only; this pins the upgrade to the parent rather than a new model. Consumer: \citet{gerard_rokkanen_rothe_2020_rdbounds}.
  \item Conjecture 1: A compatible many-window Wald vector exists if and only if one shared retained-mass vector satisfies the nested-window structural constraints. Gap: \citet[Abstract]{gerard_rokkanen_rothe_2020_rdbounds} and \citet[Abstract]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} are one-window manipulated-RD objects. Consumer: multi-window RD sensitivity analysis.
  \item Conjecture 2: For finite support and sharp RD, fixed-\(\lambda\) orthant membership is equivalent to an explicit lifted LP with laminar network core, slack objective, total-unimodular matrix, and strongly polynomial evaluation. Gap: \citet[Abstract; pp.~216--217]{bertanha_2020_many_thresholds} gives many-threshold identification and estimation, not a manipulation-driven laminar flow certificate. Consumer: bandwidth-grid software built on \citet{cattaneo_jansson_ma_2020_density}.
  \item Conjecture 3: The dual potentials of the lifted LP recover the parent one-cutoff ratio certificate at \(J=1\) and, at \(\omega^\star=(1,1)\), certify a strict joint-vs-separate frontier gap on a two-neighborhood witness. Gap: \citet[Abstract; p.~667]{chernozhukov_lee_rosen_2013_intersection_bounds} provides generic inference for intersection bounds, not the RD dual object that certifies the bound. Consumer: uniform inference over joint RD sensitivity frontiers.
\end{itemize}

\section{Related work}
\citet{hahn_todd_van_der_klaauw_2001} identify the standard sharp and fuzzy RD estimands under
cutoff continuity.  Theorem~\ref{thm:parent-reduction} uses that benchmark only as the
no-manipulation corner inherited from the parent model.

\citet{lee_2008_local_randomization} [reused from parent] gives the local-randomization
interpretation of RD and explains why predetermined covariates should be continuous at the
cutoff.  The present draft keeps that covariate logic but treats failures as bounded
manipulation inputs rather than as a binary design verdict.

\citet{mccrary_2008_density_test} [reused from parent] turns density discontinuities into a
manipulation diagnostic.  Here the same object enters only through the neighborhood-specific
envelopes \(\bar\rho_j\).

\citet{cattaneo_jansson_ma_2020_density} [reused from parent] provide the local-polynomial
density estimators used in practice to construct McCrary-style diagnostics.  Conjecture~2 is
meant to supply the missing evaluation map from those diagnostics to a joint sensitivity
frontier.

\citet[Abstract]{gerard_rokkanen_rothe_2020_rdbounds} [reused from parent] are the closest
published anchor.  They derive sharp manipulated-RD bounds in the one-cutoff model and their
covariate conditioning and fuzzy-share arguments show that the relevant endpoint object is
already an optimization problem.  The gap here is narrower: the parent result and GRR are
single-window objects, whereas this draft imposes one shared nonmanipulator mass vector across
nested windows.

\citet[Abstract, arXiv v4]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} state
only that they ``propose a procedure for obtaining partial identification bounds where
manipulation is present.''  This makes the paper a computational comparator, but not a source
for a nested-window laminar flow / total-unimodularity certificate.

\citet[Abstract; pp.~216--217]{bertanha_2020_many_thresholds} study RD with many thresholds and
show that pooling cutoffs raises a distinct identification problem even without manipulation.
This is the main many-window comparator for Conjecture~2.

\citet[Abstract; p.~667]{chernozhukov_lee_rosen_2013_intersection_bounds} provide valid
inference for bounds defined by rich systems of inequalities.  Their methods are the natural
consumer of a computable joint RD manipulation bound once the evaluation map is explicit.

\citet{ishihara_sawada_2024_manipulation_robust} study low-level conditions for
manipulation-robust RD identification.  Their paper locates the point-identified frontier; the
current draft instead keeps bounded violations and asks for a joint partial-ID computation.

In the repository, the only close prior art is the banked parent
\texttt{pid\_rdd\_manipulation\_bounded/v1}, which proves a one-cutoff bounded-manipulation
interval.  No catalogue entry proposes a shared many-neighborhood retained-mass object or a
flow-based certificate for RD manipulation bounds.

\section{Formal setup}
Let \(\calN_1\subset\cdots\subset\calN_J\) be nested cutoff neighborhoods around a fixed RD
cutoff \(c\).  For each neighborhood \(j\), let
\[
  P_{j,-},P_{j,+}
\]
denote the left- and right-limit laws of \((Y,D,W)\) conditional on the running variable lying
in \(\calN_j\), where \(Y\in[\underline y,\overline y]\), \(D\in\{0,1\}\), and
\(W\in\{1,\ldots,K\}\) is a finite predetermined-covariate cell.  Write
\(\pi_{j,-}(w)=P_{j,-}(W=w)\), \(\mu_{j,-}^Y(w)=\E_{P_{j,-}}[Y\mid W=w]\), and
\(\mu_{j,-}^D(w)=\E_{P_{j,-}}[D\mid W=w]\).

The right side is partitioned into finitely many finest atoms \(b=1,\ldots,B\).  Each atom
records its observed mass \(p_b>0\), outcome \(y_b\), treatment value \(d_b\), covariate cell
\(w_b\), and incidence pattern \(I_j(b)\in\{0,1\}\), where \(I_j(b)=1\) if atom \(b\) lies in
neighborhood \(\calN_j\).  Nestedness means \(I_j(b)\le I_{j+1}(b)\) for all \(j<J\).

A candidate shared nonmanipulator law is represented by retained masses
\[
  n=(n_1,\ldots,n_B),\qquad 0\le n_b\le p_b.
\]
For neighborhood \(j\), define retained mass
\[
  M_j(n)=\sum_{b=1}^B I_j(b)n_b,
\]
cellwise retained mass
\[
  M_{j,w}(n)=\sum_{b:w_b=w} I_j(b)n_b,
\]
and observed right-side cell mass
\[
  P_{j,+}(W=w)=\sum_{b:w_b=w} I_j(b)p_b.
\]
The laminar feasible set \(\calN(P,\bar\rho,\bar s)\) is the set of \(n\) such that, for every
neighborhood \(j\),
\begin{align}
  \sum_{b=1}^B I_j(b)(p_b-n_b) &\le \bar\rho_j \sum_{b=1}^B I_j(b)p_b, \label{eq:global-budget}\\
  \sum_{b:w_b=w} I_j(b)(p_b-n_b) &\le \bar s_{j,w}\, P_{j,+}(W=w)
  \quad\text{for each }w, \label{eq:cell-budget}\\
  M_{j,w}(n) &= \pi_{j,-}(w)\, M_j(n) \quad\text{for each }w. \label{eq:matchW}
\end{align}
Equation~\eqref{eq:matchW} is the retained-covariate-law restriction.  Because the same \(n_b\)
enters every neighborhood containing atom \(b\), the constraints across \(j\) are not a product
of one-window feasible sets.

For each neighborhood \(j\), define the retained right-side Wald components
\[
  N_j^Y(n)=\sum_{b=1}^B I_j(b)n_b y_b - M_j(n)\sum_w \pi_{j,-}(w)\mu_{j,-}^Y(w),
\]
\[
  N_j^D(n)=\sum_{b=1}^B I_j(b)n_b d_b - M_j(n)\sum_w \pi_{j,-}(w)\mu_{j,-}^D(w),
\]
and the implied local Wald effect
\[
  \theta_j(n)=\frac{N_j^Y(n)}{N_j^D(n)}.
\]
The structural identified set is
\[
  \Theta_I(P,\bar\rho,\bar s)
  =
  \left\{
    \vartheta\in\R^J:
    \begin{array}{l}
      \text{there exists a structural completion satisfying one-sided manipulation,}\\
      \text{conditional continuity, the neighborhood budgets, the cell caps, and}\\
      \text{positive first stages, whose neighborhood-wise nonmanipulator Wald vector is }\vartheta
    \end{array}
  \right\}.
\]
For each feasible retained-mass vector \(n\), write
\[
  \theta(n)=(\theta_1(n),\ldots,\theta_J(n)).
\]
For a candidate vector \(\lambda=(\lambda_1,\ldots,\lambda_J)\), define the fixed-\(\lambda\)
orthant-feasibility system
\[
  \Psi(P,\bar\rho,\bar s;\lambda)=
  \left\{n\in\calN(P,\bar\rho,\bar s):
    N_j^Y(n)-\lambda_j N_j^D(n)\le 0\ \forall j
  \right\}.
\]
Under positive first stages, \(\Psi(P,\bar\rho,\bar s;\lambda)\neq\varnothing\) is equivalent to
\(\theta_j(n)\le\lambda_j\) for all \(j\).

For computation under finite support, define the lifted slack LP
\[
  \mathsf{LP}_\lambda(P,\bar\rho,\bar s):
  \qquad
  \min_{n,m,u,z}\ \sum_{j=1}^J z_j
\]
subject to
\begin{align}
  0\le n_b &\le p_b && \text{for each atom }b, \label{eq:atom-capacity}\\
  m_j &= \sum_{b=1}^B I_j(b)n_b && \text{for each }j, \label{eq:mj-def}\\
  u_{j,w} &= \sum_{b:w_b=w} I_j(b)n_b && \text{for each }j,w, \label{eq:ujw-def}\\
  u_{j,w} &= \pi_{j,-}(w)m_j && \text{for each }j,w, \label{eq:ujw-match}\\
  m_j &\ge (1-\bar\rho_j)\sum_{b=1}^B I_j(b)p_b && \text{for each }j, \label{eq:mj-budget}\\
  u_{j,w} &\ge (1-\bar s_{j,w})P_{j,+}(W=w) && \text{for each }j,w, \label{eq:ujw-budget}\\
  \sum_{b=1}^B I_j(b)n_b(y_b-\lambda_j d_b)
  &\le
  m_j\sum_w \pi_{j,-}(w)\bigl(\mu_{j,-}^Y(w)-\lambda_j\mu_{j,-}^D(w)\bigr)+z_j
  && \text{for each }j, \label{eq:score-slack}\\
  z_j &\ge 0 && \text{for each }j. \label{eq:score-slack-nonneg}
\end{align}
Then \(\Phi(P,\bar\rho,\bar s;\lambda)=1\) if and only if the optimum value of
\(\mathsf{LP}_\lambda(P,\bar\rho,\bar s)\) is zero.

\begin{verbatim}
Locked parameters.
qid = pid_rdd_flow_manipulation
specialization = v1
observable distribution P = left/right cutoff limits {P_{j,-}, P_{j,+}} for nested
  neighborhoods j=1,...,J plus a finite finest right-side partition b=1,...,B
parameter theta = vector of nonmanipulator local Wald effects (theta_1,...,theta_J)
identifying restrictions = one-sided upward manipulation; local continuity within each
  neighborhood and covariate cell; a shared retained nonmanipulator mass vector across
  nested neighborhoods; neighborhood-specific global envelopes rho_bar_j; neighborhood-
  by-cell caps s_bar_{j,w}; bounded outcomes; positive retained mass; positive first stages
bounding functional = joint identified set Theta_I(P,rho_bar,s_bar) and fixed-lambda
  orthant-membership map Phi(P,rho_bar,s_bar; lambda)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Nested finite-support neighborhoods]\label{ass:nested-support}
The family \(\calN_1\subset\cdots\subset\calN_J\) is finite and nested.  The right-side law is
represented on a finite finest partition \(b=1,\ldots,B\) with masses \(p_b>0\), and
\(\pi_{j,-}(w)>0\) whenever neighborhood \(j\) uses covariate cell \(w\).
\end{assumption}

\begin{assumption}[One-sided manipulation with a shared latent law]\label{ass:shared-law}
Manipulators can only add mass on the treatment side of the cutoff.  There exists one latent
nonmanipulator mass vector \(n\) on the finest right-side partition whose restriction to each
neighborhood \(j\) generates the neighborhood-\(j\) right-limit nonmanipulator law.
\end{assumption}

\begin{assumption}[Conditional continuity]\label{ass:conditional-continuity}
For each neighborhood \(j\), the left-limit law \(P_{j,-}\) equals the covariate distribution
of the neighborhood-\(j\) nonmanipulator law, and the retained right-side conditional means
identify the right-limit nonmanipulator means within each covariate cell.
\end{assumption}

\begin{assumption}[Neighborhood budgets and cell caps]\label{ass:budgets}
The shared retained-mass vector satisfies the neighborhood-specific global bounds
\eqref{eq:global-budget} and cellwise bounds \eqref{eq:cell-budget}, and the feasible set
\(\calN(P,\bar\rho,\bar s)\) is nonempty.
\end{assumption}

\begin{assumption}[Positive first stages]\label{ass:first-stage}
There exists \(\kappa>0\) such that \(N_j^D(n)\ge \kappa\) for every
\(n\in\calN(P,\bar\rho,\bar s)\) and every neighborhood \(j\).
\end{assumption}

\begin{assumption}[Sharp-RD computational face]\label{ass:sharp-rd}
For results that explicitly invoke the computational flow certificate, \(D=Z\) almost surely in
every neighborhood and hence \(d_b=1\) on the right-side atoms.  The left-side treatment mean
is zero, so \(N_j^D(n)=M_j(n)\).
\end{assumption}

\begin{assumption}[Rational benchmark masses for the lifted network]\label{ass:rational}
For results that explicitly invoke total unimodularity, the masses
\(\pi_{j,-}(w)\), \(p_b\), the budget right-hand sides, and the candidate vector \(\lambda\)
admit a common rational scaling.  After multiplying
\eqref{eq:mj-def}--\eqref{eq:score-slack} by that common denominator, the lifted LP is an
integer linear program.
\end{assumption}

\begin{assumption}[Parent reduction face]\label{ass:parent-face}
For the parent reduction, \(J=1\), the single neighborhood is the parent cutoff window, and the
budgets \((\bar\rho_1,\bar s_{1,w})\) coincide with the parent one-cutoff bounded-manipulation
specification.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: one-window reduction to the parent]\label{thm:parent-reduction}
Under Assumptions~\ref{ass:nested-support}--\ref{ass:parent-face}, the joint feasible set
\(\calN(P,\bar\rho,\bar s)\) coincides with the parent one-window retention set after the
identification \(n_b=p_b a_b\).  Consequently, \(\Theta_I(P,\bar\rho,\bar s)\) is exactly the
parent one-cutoff bounded-manipulation interval, and the fixed-\(\lambda\)
orthant-feasibility condition \(\Psi(P,\bar\rho,\bar s;\lambda_1)\neq\varnothing\) is exactly
the parent ratio-indexed endpoint feasibility problem.
\end{theorem}

The proof is a relabeling argument.  With \(J=1\), every finest atom lies in the same
neighborhood, so \(n_b=p_b a_b\) turns \eqref{eq:global-budget}--\eqref{eq:matchW} into the
parent constraints and the Wald components into the parent numerator and denominator.

\begin{conjecture}[Conjecture 1: shared-image characterization]\label{conj:shared-image}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:nested-support}--\ref{ass:first-stage}, the
many-neighborhood identified set is exactly
\[
  \Theta_I(P,\bar\rho,\bar s)=\{\theta(n):n\in\calN(P,\bar\rho,\bar s)\}.
\]
Equivalently, a candidate vector \(\lambda\in\R^J\) lies in the upper orthant of the
identified set if and only if \(\Psi(P,\bar\rho,\bar s;\lambda)\neq\varnothing\).
\end{conjecture}

\begin{conjecture}[Conjecture 2: laminar flow certificate]\label{conj:flow-certificate}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:nested-support}--\ref{ass:rational}, and under
the sharp-RD specialization of Assumption~\ref{ass:sharp-rd}, the fixed-\(\lambda\) feasibility
problem \(\Psi(P,\bar\rho,\bar s;\lambda)\) is equivalent to the zero-optimum event for the
lifted program \(\mathsf{LP}_\lambda(P,\bar\rho,\bar s)\).  After introducing shell variables
for the differences between consecutive neighborhoods and split positive/negative score-flow
arcs for the coefficients in \eqref{eq:score-slack}, the constraint matrix of
\(\mathsf{LP}_\lambda\) becomes a block matrix
\[
  A_\lambda=
  \begin{pmatrix}
    A_{\mathrm{tree}} & 0 & 0 \\
    A_{\mathrm{match}} & I & 0 \\
    A_{\mathrm{score}}(\lambda) & 0 & I
  \end{pmatrix},
\]
where \(A_{\mathrm{tree}}\) is the node-arc incidence matrix of a laminar tree, the columns of
\(A_{\mathrm{match}}\) and \(A_{\mathrm{score}}(\lambda)\) have consecutive nonzero blocks after
ordering rows by neighborhood depth, and the full matrix \(A_\lambda\) is total unimodular.
Hence orthant membership can be decided in strongly polynomial time in the size of the lifted
network.
\end{conjecture}

\begin{conjecture}[Conjecture 3: dual reduction and strict joint gap]\label{conj:dual-gap}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:nested-support}--\ref{ass:rational} and
Assumption~\ref{ass:sharp-rd}, the dual of the lifted program in
Conjecture~\ref{conj:flow-certificate} yields node potentials
\((\alpha_j,\beta_{j,w},\gamma_j)\) that certify orthant membership.  When \(J=1\), those
potentials collapse to the parent ratio-indexed dual certificate.  When \(J=2\) and the
neighborhoods have distinct left-side covariate shares, there is a named positive weight vector
\(\omega^\star=(1,1)\in\R_{++}^2\) and an open class of finite-support laws for which the joint
support function
\[
  h_{\Theta_I}(\omega)=\sup_{\theta\in\Theta_I(P,\bar\rho,\bar s)} \omega^\top \theta
\]
is strictly below the sum of the separately computed one-window envelopes at
\(\omega=\omega^\star\).
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Parent corner]\label{cor:parent-corner}
Under Assumptions~\ref{ass:nested-support}--\ref{ass:parent-face},
Theorem~\ref{thm:parent-reduction} reduces the upgrade to the banked parent result.  The
reduction is exact because the shared retained-mass vector has only one neighborhood
restriction, so the laminar system collapses to the parent one-cutoff retention program.
\end{corollary}

\begin{corollary}[No-manipulation corner]\label{cor:no-manipulation}
Under Assumptions~\ref{ass:nested-support}--\ref{ass:first-stage}, if \(\bar\rho_j=0\) and
\(\bar s_{j,w}=0\) for every \(j,w\), then \(n_b=p_b\) for all \(b\), so each
\(\theta_j(n)\) equals the usual neighborhood-\(j\) RD Wald estimand.  This follows because
\eqref{eq:global-budget} and \eqref{eq:cell-budget} force zero removal in every neighborhood.
\end{corollary}

\paragraph{Exhibit 9.1 (parent dual from primitives).}
Take \(J=1\), one covariate cell, and sharp RD.  Let the right-side atoms be
\((p_1,y_1)=(0.4,1)\) and \((p_2,y_2)=(0.6,0)\), let the left-side outcome mean be \(0\), and
let \(\bar\rho_1=0.5\).  For candidate \(\lambda\), the fixed-\(\lambda\) feasibility problem is
\[
  n_1+n_2\ge 0.5,\qquad
  n_1(1-\lambda)+n_2(0-\lambda)\le 0,\qquad
  0\le n_1\le 0.4,\ 0\le n_2\le 0.6.
\]
At \(\lambda=0.8\), the choice \((n_1,n_2)=(0.4,0.1)\) satisfies the system with equality in
both constraints, so the dual certificate is the parent ratio multiplier \(\lambda=0.8\) plus a
single retained-mass shadow price.  This is the \(J=1\) face demanded by
Conjecture~\ref{conj:dual-gap}.

\paragraph{Exhibit 9.2 (explicit lifted LP and TU witness).}
Take \(J=2\), one covariate cell, and sharp RD.  Let \(\calN_1\subset\calN_2\), with finest
atoms \(a,b,c\) such that \(a,b\in\calN_1\) and \(c\in\calN_2\setminus\calN_1\).  Let
\[
  (p_a,p_b,p_c)=(1,1,1),\qquad (y_a,y_b,y_c)=(1,0,1),\qquad
  (\bar\rho_1,\bar\rho_2)=\left(\frac12,\frac13\right).
\]
For \(\lambda_1=\lambda_2=\frac12\), write \(m_1=n_a+n_b\), \(m_2=m_1+n_c\), and let
\(z_1,z_2\) be orthant slacks.  The lifted LP is
\[
  \min z_1+z_2
\]
subject to
\[
  m_1=n_a+n_b,\qquad m_2=m_1+n_c,\qquad m_1\ge 1,\qquad m_2\ge 2,
\]
\[
  n_a-m_1/2\le z_1,\qquad n_a+n_c-m_2/2\le z_2,
\]
\[
  0\le n_a,n_b,n_c\le 1,\qquad z_1,z_2\ge 0.
\]
After substituting out \(m_1,m_2\), multiplying by \(2\), and ordering rows as
\((m_1,m_2,\mathrm{score}_1,\mathrm{score}_2)\), the coefficient matrix on
\((n_a,n_b,n_c,z_1,z_2)\) is
\[
  \begin{pmatrix}
    1 & 1 & 0 & 0 & 0\\
    1 & 1 & 1 & 0 & 0\\
    1 & -1 & 0 & -2 & 0\\
    1 & 1 & 1 & 0 & -2
  \end{pmatrix}.
\]
The shell-lifted version replaces the two score rows by arc balances into two slack sinks on a
laminar tree with root \(\calN_2\), child \(\calN_1\), outer-shell leaf \(c\), and inner leaves
\(a,b\).  The feasible point
\[
  (n_a,n_b,n_c,m_1,m_2,z_1,z_2)=(0.5,0.5,1,1,2,0,0)
\]
has zero objective, so \(\Phi(P,\bar\rho,\bar s;\lambda)=1\) on this witness.  This exhibit pins
down the lifted variables, the objective, the slack construction, and the matrix block that
Conjecture~\ref{conj:flow-certificate} asks to prove total unimodular in general.

\paragraph{Exhibit 9.3 (dual potentials and strict joint-vs-separate gap).}
Take sharp RD with two covariate cells \(A,B\), two nested neighborhoods, and left outcome mean
zero everywhere.  Let the finest atoms be
\[
  a=(p=0.4,w=A,y=1)\in\calN_1,\qquad
  b=(p=0.1,w=B,y=0)\in\calN_1,\qquad
  c=(p=0.5,w=B,y=1)\in\calN_2\setminus\calN_1.
\]
Let the left covariate shares be
\[
  \pi_{1,-}(A)=\pi_{1,-}(B)=0.5,\qquad
  \pi_{2,-}(A)=0.25,\ \pi_{2,-}(B)=0.75,
\]
and take loose budgets so only the matching equations bind.  Solving the two neighborhoods
separately gives the sharp-RD upper means
\[
  \theta_1^{\mathrm{sep}}=0.5,\qquad \theta_2^{\mathrm{sep}}=0.875,
\]
attained by \((n_a,n_b)=(0.1,0.1)\) for \(\calN_1\) and
\((n_a,n_b,n_c)=(0.2,0.1,0.5)\) for \(\calN_2\).  Those solutions are incompatible because the
shared inner atom \(a\) cannot simultaneously retain mass \(0.1\) and \(0.2\).  Under the
shared-mass restriction, the inner-window matching condition forces \(n_a=n_b\), and the outer
matching condition then implies \(n_c=2n_a\).  The best joint choice is
\[
  (n_a,n_b,n_c)=(0.1,0.1,0.2),
\]
which yields
\[
  \theta_1^{\mathrm{joint}}=0.5,\qquad \theta_2^{\mathrm{joint}}=0.75,
\]
so the support-function value at weight vector \(\omega=(1,1)\) drops from
\[
  h_{\mathrm{sep}}(\omega)=0.5+0.875=1.375
\]
to
\[
  h_{\mathrm{joint}}(\omega)=0.5+0.75=1.25.
\]
For the candidate orthant threshold \(\lambda=(0.5,0.75)\), one compatible zero-slack retained
vector is exactly the joint optimizer above.  A dual certificate is given by
\[
  \alpha_1=\alpha_2=1,\qquad
  \beta_{1,A}=0,\ \beta_{1,B}=1/2,\qquad
  \beta_{2,A}=0,\ \beta_{2,B}=1/4,\qquad
  \gamma_1=\gamma_2=0,
\]
where \(\alpha_j\) prices the neighborhood mass constraint, \(\beta_{j,w}\) prices the
retained-\(W\) equations, and \(\gamma_j\) prices the score slack.  These potentials make the
inner \(A\)-atom and outer \(B\)-atom tight, leave the incompatible separate optimum with
positive reduced cost, and normalize to the parent \(J=1\) multiplier in Exhibit~9.1.  This is
the concrete strict-gap witness required by Conjecture~\ref{conj:dual-gap}.

\section{Proof-sketch route}
The verification route has five substantive steps.  First, prove a mixture-retention lemma for a
shared atom-level nonmanipulator mass vector across nested windows, extending the parent's
one-window decomposition.  Second, map structural completions to the algebraic feasible set
\(\calN(P,\bar\rho,\bar s)\) and back, so that Conjecture~\ref{conj:shared-image} is not a
definition unfold.  Third, show that the orthant inequalities
\(N_j^Y(n)-\lambda_j N_j^D(n)\le 0\) characterize upper-orthant membership once
Assumption~\ref{ass:first-stage} makes each denominator positive.  Fourth, on finite support,
lift \(\mathsf{LP}_\lambda\) to shell variables and score-slack arcs on a laminar tree, then use
the consecutive-ones structure of nested neighborhoods to prove total unimodularity of
\(A_\lambda\).  Fifth, derive the dual node potentials and verify the boundary cases explicitly:
the parent \(J=1\) face, the one-cell lifted witness in Exhibit~9.2, and the two-cell strict gap
with \(\omega^\star=(1,1)\) in Exhibit~9.3.

\section{Honest scope flags}
Theorem~\ref{thm:parent-reduction} is the only statement asserted as routine.  Conjecture~1 is
the substantive identification claim: the parent sharpness argument must be extended from one
window to a shared nested-window latent law.  Conjecture~2 is the computation delta, and its
strongly polynomial claim is only for the lifted finite-support sharp-RD orthant problem with
rational scaling, not for continuous covariates or unrestricted fuzzy RD.  Conjecture~3 adds the
dual certificate and the strict joint-vs-separate phenomenon at the named positive weight vector
\(\omega^\star=(1,1)\); Exhibit~9.3 verifies one worked witness but not yet an open-class
theorem.  Relative to the prior draft, the separable neighborhood formulation has been
withdrawn: the windows now share atom variables by construction, because otherwise laminarity
does no mathematical work.  The Rosenman comparison has also been narrowed to the current arXiv
v4 abstract claim and no longer attributes a specific algorithm absent a location anchor.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft of the many-neighborhood flow upgrade; prior verdict: none.
\item v2 (revise) --- replaced separable window programs with a shared laminar retained-mass model, added Bertanha and Chernozhukov--Lee--Rosen location anchors, and computed Exhibits 9.1--9.3; prior verdict: REVISE.
\item v3 (revise) --- redefined the identified set structurally, made the lifted LP / TU object explicit, computed named dual potentials, and stabilized the Rosenman citation to arXiv v4; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}

\bibitem[Bertanha(2020)]{bertanha_2020_many_thresholds}
Bertanha, Marinho.
2020.
Regression discontinuity design with many thresholds.
\emph{Journal of Econometrics} 218(1): 216--241.

\bibitem[Cattaneo, Jansson, and Ma(2020)]{cattaneo_jansson_ma_2020_density}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem[Chernozhukov, Lee, and Rosen(2013)]{chernozhukov_lee_rosen_2013_intersection_bounds}
Chernozhukov, Victor, Sokbae Lee, and Adam M. Rosen.
2013.
Intersection bounds: Estimation and inference.
\emph{Econometrica} 81(2): 667--737.

\bibitem[Gerard, Rokkanen, and Rothe(2020)]{gerard_rokkanen_rothe_2020_rdbounds}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem[Hahn, Todd, and van der Klaauw(2001)]{hahn_todd_van_der_klaauw_2001}
Hahn, Jinyong, Petra Todd, and Wilbert van der Klaauw.
2001.
Identification and estimation of treatment effects with a regression-discontinuity design.
\emph{Econometrica} 69(1): 201--209.

\bibitem[Ishihara and Sawada(2024)]{ishihara_sawada_2024_manipulation_robust}
Ishihara, Takuya, and Masayuki Sawada.
2024.
Manipulation-robust regression discontinuity designs.
arXiv:2009.07551.

\bibitem[Lee(2008)]{lee_2008_local_randomization}
Lee, David S.
2008.
Randomized experiments from non-random selection in U.S. House elections.
\emph{Journal of Econometrics} 142(2): 675--697.

\bibitem[McCrary(2008)]{mccrary_2008_density_test}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem[Rosenman et~al.(2025)]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation}
Rosenman, Evan, Karthik Rajkumar, Romain Gauriot, and Robert Slonim.
2025.
Donor's Deferral and Return Behavior: Partial Identification from a Regression Discontinuity Design with Manipulation.
arXiv:1910.02170v4.

\end{thebibliography}

\end{document}
