\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\calA}{\mathcal{A}}
\newcommand{\calM}{\mathcal{M}}
\newcommand{\calV}{\mathcal{V}}
\newcommand{\calE}{\mathcal{E}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_rdd\_flow\_manipulation} / \texttt{v1}%
  \\ \large\textit{Laminar min-cost-flow certificates for many-neighborhood RD manipulation bounds}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal.
The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional}).
\]
Here \(\texttt{qid}=\texttt{pid\_rdd\_flow\_manipulation}\) and
\(\texttt{specialization}=\texttt{v1}\). The observable distribution
\(P=\{P_{j,-},P_{j,+}\}_{j=1}^J\) consists of left and right cutoff-side limits for
\((Y,D,W)\) across a finite laminar family of right-neighborhoods
\(\mathcal N_1\subset\cdots\subset\mathcal N_J\), with
\(Y\in[\underline y,\overline y]\), \(D\in\{0,1\}\), and
\(W\in\{1,\ldots,K\}\). The parameter \(\theta_j\) is the nonmanipulator local Wald
effect in neighborhood \(j\),
\[
\theta_j=
\frac{\sum_w \pi_{j,-}(w)\{\mu^Y_{j,+,0}(w)-\mu^Y_{j,-}(w)\}}
     {\sum_w \pi_{j,-}(w)\{\mu^D_{j,+,0}(w)-\mu^D_{j,-}(w)\}},
\]
with \(\pi_{j,-}(w)=P_{j,-}(W=w)\). The identifying restrictions are one-sided upward
manipulation, local continuity of the nonmanipulator law conditional on \(W\) in each
neighborhood, global manipulation envelopes \(\bar\rho_j\), cell caps \(\bar s_{jw}\),
extendability across the laminar neighborhood chain, bounded outcomes, and positive
first stages. The bounding functional is the many-neighborhood support function obtained
from the family of feasible retained plans \(a=\{a_{j\alpha}\}\) or, on each fixed slice
\(m=(m_1,\ldots,m_J)\), from the equivalent min-cost-flow program
\[
B_U(P,\bar\rho,\bar s)=\sup_{m\in\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)}\sup_{a\in\calA(m)}\Theta(a),
\qquad
B_L(P,\bar\rho,\bar s)=\inf_{m\in\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)}\inf_{a\in\calA(m)}\Theta(a),
\]
where \(\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)\) is the extendable retained-mass set
defined in Section~6 and \(\Theta(a)\) is the neighborhood-indexed Wald ratio vector.

\begin{abstract}
The banked parent result \texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1} gives a
sharp one-cutoff partial-identification interval through a retained-mass linear-fractional
program. This proposal asks whether the same bounded-manipulation logic across many nested
cutoff neighborhoods admits a computable network certificate rather than a separate ratio
search at each neighborhood. The main claim is that every fixed retained-mass slice of the
many-neighborhood problem is a laminar transportation program with a totally unimodular
constraint matrix and an explicit node-potential dual. The flagship conjecture is that the
global sharp bound is obtained by optimizing over the extendable slice set and that the
one-neighborhood dual collapses exactly to the parent interval program. If true, the result
would turn many-neighborhood manipulation bounds into an auditable combinatorial object
rather than a collection of uncoupled linear-fractional searches.
\end{abstract}

\section{Introduction}
The question is whether bounded-manipulation regression-discontinuity bounds across many
nested cutoff neighborhoods can be computed by a single combinatorial certificate rather
than by repeating the parent one-cutoff linear-fractional program neighborhood by
neighborhood. The headline claim is that, once the retained masses are fixed, the sharp
upper and lower slice values are min-cost flows on a laminar network whose capacities,
balances, and costs are all observable functions of the RD primitives.

Relative to the parent banked proposal \texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1},
the upgrade axis is computation: the parent gives a retained-plan characterization but not a
strongly polynomial graph algorithm or dual certificate. Relative to
\citet{gerard_rokkanen_rothe_2020_rdbounds} and
\citet{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation}, the gap is a
many-neighborhood, covariate-conditional, manipulation-robust RD program with an explicit
laminar flow representation and a one-cutoff collapse back to the parent object. The kernel
lives in partial identification, with a computational bridge to min-cost-flow duality
\citep{orlin_1993_mincostflow}.

The immediate consumer is empirical RD work that reports multiple bandwidth or neighborhood
diagnostics around one cutoff or many nearby cutoffs, as in
\citet{cattaneo_keele_titiunik_vazquezbare_2021_multicutoff} and
\citet{bertanha_2020_many_thresholds}. A reader who accepts the conjecture would compute a
simultaneous manipulation-robust envelope with a primal retained plan and a dual potential
certificate, instead of reporting a list of separate one-neighborhood sensitivity intervals.

\begin{itemize}[leftmargin=*]
\item Theorem 1: each fixed retained-mass slice is exactly a laminar min-cost-flow problem with a totally unimodular incidence matrix. Gap: parent \texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1} and \citet{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} solve slice problems as generic LPs or sequential convex programs, not as an exhibited TU network. Consumer: computational certification of many-neighborhood RD bounds.
\item Conjecture 1: the sharp many-neighborhood identified set equals the union of the slice flow values over the extendable retained-mass set \(\calM_{\mathrm{ext}}\). Gap: \citet{gerard_rokkanen_rothe_2020_rdbounds} is one-cutoff; \citet{bertanha_2020_many_thresholds} and \citet{cattaneo_keele_titiunik_vazquezbare_2021_multicutoff} are multi-cutoff point-identification results, not manipulation partial-ID flow bounds. Consumer: simultaneous manipulation-robust bandwidth reporting.
\item Conjecture 2: the slice dual admits an explicit node-potential certificate whose one-neighborhood specialization reproduces the parent interval program. Gap: the parent proves a one-cutoff retained-plan interval but does not expose a dual graph certificate; generic flow papers such as \citet{orlin_1993_mincostflow} do not identify the RD causal object. Consumer: auditable optimality certificates for software and reviewer replication.
\item Theorem 2: a worked \(J=2\), \(K=2\) instance has a complete primal flow and dual certificate computed from the Section~6 primitives. Gap: the parent has no many-neighborhood certificate exhibit. Consumer: Exhibit-based validation of the computational upgrade before a general proof.
\end{itemize}

\section{Related work}
\citet{gerard_rokkanen_rothe_2020_rdbounds} [reused from parent] is the closest causal
anchor. They derive sharp RD bounds under manipulation of the running variable and use
density information to discipline the manipulators' share. The present proposal reuses
their one-cutoff manipulation-bounds thread but changes the computational object: the many
neighborhood problem is organized as a laminar flow over simultaneous neighborhood-cell
requirements rather than as a separate one-cutoff retained-plan search.

\citet{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation} [reused from parent]
study discrete manipulated RD and compute partial-identification bounds numerically. Their
relevance is computational contrast: the proposal claims an explicit globally certifiable
network representation where they use sequential convex programming.

\citet{bertanha_2020_many_thresholds} [reused from parent] and
\citet{cattaneo_keele_titiunik_vazquezbare_2021_multicutoff} [reused from parent] are the
many-threshold and multi-cutoff comparators. They show how multiple cutoffs or thresholds
generate point-identified extrapolation objects, but they do not study manipulation-driven
partial identification or a simultaneous trimming geometry.

\citet{mccrary_2008_density_test} [reused from parent] and
\citet{cattaneo_jansson_ma_2020_density} [reused from parent] justify the envelope
parameters \(\bar\rho_j\) as diagnostic inputs. Their role here is not identification but
calibration of the neighborhood-specific manipulation budgets.

\citet{lee_2009_selection_bounds} [reused from parent] and
\citet{horowitz_manski_1995_contaminated} [reused from parent] supply the trimming and
contaminated-distribution ancestry. The flow upgrade preserves that partial-identification
content while replacing the parent's one-cutoff closed-form envelope with an explicit
laminar transport problem.

\citet{orlin_1993_mincostflow} is the new frontier anchor for the upgrade axis. It gives a
strongly polynomial min-cost-flow algorithm for capacitated networks. The proposal uses
this not as prior art on causal identification, but as the algorithmic benchmark once the
RD slice problem is shown to be a genuine network-flow instance.

\citet{schrijver_1986_theory_linear_integer} is the new total-unimodularity anchor. Its
relevance is structural: the constraint matrix in the fixed-slice problem is an incidence
matrix of a directed laminar network, so vertex optimality and integral certificates follow
from standard network TU facts once the graph has been exhibited.

In the repository, \texttt{CausalSmith/doc/API.md} contains no distinct catalogue theorem
beyond the banked parent with this kernel. The duplicate-check question is therefore
whether the upgrade adds a new computational object, not whether bounded-manipulation RD
partial identification already exists in the catalogue.

\section{Formal setup}
Fix neighborhoods \(\mathcal N_1\subset\cdots\subset\mathcal N_J\) around a common cutoff,
ordered from narrow to wide. In each neighborhood \(j\), the left and right cutoff-side
limits of \((Y,D,W)\) are \(P_{j,-}\) and \(P_{j,+}\), and
\(\pi_{j,-}(w)=P_{j,-}(W=w)\). For exposition, discretize the right-side law in each
neighborhood into atoms \(\alpha\in\mathcal I_j\) with observed mass \(p_{j\alpha}>0\),
outcome \(y_{j\alpha}\), treatment \(d_{j\alpha}\), and covariate cell \(w_{j\alpha}\).

Let \(m_j\in(0,1]\) be retained mass in neighborhood \(j\). The extendable retained-mass
set \(\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)\) contains vectors \(m=(m_1,\ldots,m_J)\)
satisfying
\[
1-m_j\le \bar\rho_j,\qquad
m_j\pi_{j,-}(w)\ge (1-\bar s_{jw})P_{j,+}(W=w),
\]
for every \(j,w\), together with the laminar increment inequalities
\[
\Delta_{1w}(m)=m_1\pi_{1,-}(w)\ge 0,\qquad
\Delta_{jw}(m)=m_j\pi_{j,-}(w)-m_{j-1}\pi_{j-1,-}(w)\ge 0
\]
for \(j\ge2\). These increments are the additional retained cell masses required when one
moves from neighborhood \(j-1\) to \(j\).

For a candidate Wald multiplier \(\lambda\), define the slice score
\[
c_{j\alpha}(\lambda)=-(y_{j\alpha}-\lambda d_{j\alpha}).
\]
The fixed-slice upper-endpoint problem is the linear program
\[
V_U(\lambda,m)=\min_{x\ge0}\sum_{j=1}^J\sum_{\alpha\in\mathcal I_j} c_{j\alpha}(\lambda)x_{j\alpha}
\]
subject to the capacity constraints
\[
0\le x_{j\alpha}\le p_{j\alpha},
\]
and the neighborhood-cell balance constraints
\[
\sum_{\alpha\in\mathcal I_1:w_{1\alpha}=w}x_{1\alpha}=\Delta_{1w}(m),
\]
\[
\sum_{\alpha\in\mathcal I_j:w_{j\alpha}=w}x_{j\alpha}
+z_{j-1,w}-z_{j,w}
=\Delta_{jw}(m),\qquad j=2,\ldots,J,
\]
where \(z_{j,w}\ge0\) is carry flow that pushes retained mass in cell \(w\) from
neighborhood \(j\) into neighborhood \(j+1\). The lower slice is identical with the sign
of \(y_{j\alpha}\) reversed.

The graph \(G_{\lambda,m}=(\calV,\calE)\) attached to the slice has node set
\[
\calV=\{s,t\}\cup\{u_{j\alpha}\}\cup\{v_{jw}\},
\]
where \(u_{j\alpha}\) is an atom node and \(v_{jw}\) is a neighborhood-cell demand node.
Its arc set is
\[
\calE=
\{(s,u_{j\alpha})\}\cup\{(u_{j\alpha},v_{jw_{j\alpha}})\}
\cup\{(v_{jw},v_{j+1,w}):j<J\}\cup\{(v_{Jw},t)\}.
\]
Capacities are \(u(s,u_{j\alpha})=p_{j\alpha}\), \(u(u_{j\alpha},v_{jw_{j\alpha}})=p_{j\alpha}\),
and \(u(v_{jw},v_{j+1,w})=+\infty\). Balances are
\[
b(s)=\sum_{j,w}\Delta_{jw}(m),\qquad b(v_{jw})=-\Delta_{jw}(m),\qquad b(t)=0,
\]
with zero balance at every atom node. Costs are \(c(s,u_{j\alpha})=0\),
\(c(u_{j\alpha},v_{jw_{j\alpha}})=c_{j\alpha}(\lambda)\), and zero on carry arcs.

\begin{verbatim}
Locked parameters.
qid = pid_rdd_flow_manipulation
specialization = v1
observable distribution P = {P_{j,-},P_{j,+}}_{j=1}^J over a finite laminar family of
  nested cutoff neighborhoods with finite covariate cells
parameter theta = vector of nonmanipulator local Wald effects theta_j across neighborhoods
identifying restrictions = one-sided upward manipulation; conditional nonmanipulator
  continuity within each neighborhood and cell; neighborhood-specific global envelopes
  rho_bar_j; cell caps s_bar_jw; extendable retained-mass constraints across the laminar
  chain; bounded outcomes; positive first stages
bounding functional = sharp many-neighborhood lower/upper support values obtained by
  optimizing the retained-plan Wald ratio over the extendable mass set M_ext, and, on
  each fixed mass slice, by the equivalent laminar min-cost-flow program V_U(lambda,m)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite laminar neighborhood system]\label{ass:laminar}
The right neighborhoods satisfy
\(\mathcal N_1\subset\cdots\subset\mathcal N_J\), with finite \(J\), and each right-side
law \(P_{j,+}\) has finite atomic support over
\([\underline y,\overline y]\times\{0,1\}\times\{1,\ldots,K\}\).
\end{assumption}

\begin{assumption}[One-sided upward manipulation]\label{ass:one-sided}
In every neighborhood, manipulation adds mass only to the right side of the cutoff.
\end{assumption}

\begin{assumption}[Conditional nonmanipulator continuity]\label{ass:continuity}
For each neighborhood \(j\), after removing manipulators, the retained right-side
covariate law equals \(\pi_{j,-}\), and the retained right-side means identify the
nonmanipulator right-limit means entering \(\theta_j\).
\end{assumption}

\begin{assumption}[Neighborhood envelopes and cell caps]\label{ass:budgets}
For each neighborhood \(j\), the retained mass satisfies \(1-m_j\le\bar\rho_j\), and the
retained mass in cell \(w\) satisfies
\(m_j\pi_{j,-}(w)\ge(1-\bar s_{jw})P_{j,+}(W=w)\).
\end{assumption}

\begin{assumption}[Extendability]\label{ass:extendability}
The increment vector \(\Delta_{jw}(m)\) defined in Section~6 is nonnegative for every
\(j,w\). Hence each wider neighborhood requires weakly more retained mass in every cell
than the previous neighborhood.
\end{assumption}

\begin{assumption}[Positive first stage]\label{ass:first-stage}
For every feasible retained plan, each neighborhood \(j\) has local Wald denominator at
least \(\kappa_j>0\).
\end{assumption}

\begin{assumption}[Slice feasibility]\label{ass:slice-feasible}
For every \(m\in\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)\), the fixed-slice network
\(G_{\lambda,m}\) is feasible for every \(\lambda\) considered in the endpoint search.
\end{assumption}

\begin{assumption}[Worked two-neighborhood witness]\label{ass:witness}
For Theorem~2 and Exhibit~9.1, let \(J=2\), \(K=2\), \(\lambda=0\), and
\[
\pi_{1,-}(A)=\pi_{1,-}(B)=\frac12,\qquad
\pi_{2,-}(A)=\pi_{2,-}(B)=\frac12,
\]
\[
m_1=\frac12,\qquad m_2=\frac35,
\]
with right-side atoms
\[
(j,\alpha,w,y,p)=
(1,1,A,1,\tfrac14),\ (1,2,B,0,\tfrac14),\
(2,1,A,1,\tfrac1{20}),\ (2,2,A,0,\tfrac3{20}),\ (2,3,B,0,\tfrac15).
\]
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: fixed-slice laminar min-cost flow]\label{thm:slice-flow}
Under Assumptions~\ref{ass:laminar}--\ref{ass:slice-feasible}, for every fixed
\((\lambda,m)\) with \(m\in\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)\), the slice program
\(V_U(\lambda,m)\) is exactly the min-cost-flow problem on \(G_{\lambda,m}\). Its
constraint matrix is the node-arc incidence matrix of a directed network after upper-bound
splitting, hence totally unimodular. In particular, every rational slice instance admits an
optimal basic solution supported on a network basis.
\end{theorem}

The proof is the graph rewrite in Section~6: atom capacities become source-to-atom arcs,
cell-neighborhood requirements become node balances, and laminar compatibility becomes the
carry chain. Total unimodularity is then the standard network-incidence fact.

\begin{conjecture}[Conjecture 1: sharp many-neighborhood flow envelope]\label{conj:sharp-envelope}
(NOT YET PROVED.) Under Assumptions~\ref{ass:laminar}--\ref{ass:slice-feasible}, the sharp
identified set for the vector \((\theta_1,\ldots,\theta_J)\) equals the union of the slice
flow values over the extendable retained-mass set:
\[
\Theta_I(P,\bar\rho,\bar s)
=
\bigcup_{m\in\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)}
\{\Theta(a):a\in\calA(m)\}.
\]
Equivalently, the support function of the sharp set is obtained by optimizing the flow
value \(V_U(\lambda,m)\) and its lower-endpoint analogue over
\(\calM_{\mathrm{ext}}(P,\bar\rho,\bar s)\).
\end{conjecture}

\begin{conjecture}[Conjecture 2: explicit dual certificate and parent collapse]\label{conj:dual}
(NOT YET PROVED.) Under Assumptions~\ref{ass:laminar}--\ref{ass:slice-feasible}, each
optimal slice flow admits node potentials
\(\varphi=\{\varphi_s,\varphi_{j\alpha},\varphi_{jw},\varphi_t\}\) and nonnegative
reduced-cost slacks \(\sigma_e\) such that, for every arc \(e=(u,v)\in\calE\),
\[
\varphi_u-\varphi_v-\sigma_e\le c_e,
\qquad
f_e<u_e\Rightarrow \sigma_e=0,
\qquad
\sigma_e>0\Rightarrow f_e=u_e.
\]
When \(J=1\), these inequalities collapse to the parent one-cutoff retained-plan interval:
the atom potentials encode the parent ratio-indexed ordering, and the unique demand-node
potential is the parent retained-mass multiplier.
\end{conjecture}

\begin{theorem}[Theorem 2: explicit \(J=2\) certificate]\label{thm:witness}
Under Assumption~\ref{ass:witness}, the slice network has node balances
\[
\Delta_{1A}=\Delta_{1B}=\frac14,\qquad
\Delta_{2A}=\Delta_{2B}=\frac1{20}.
\]
An optimal primal flow is
\[
f(s,u_{11})=\frac14,\quad f(u_{11},v_{1A})=\frac14,\quad
f(s,u_{12})=\frac14,\quad f(u_{12},v_{1B})=\frac14,
\]
\[
f(s,u_{21})=\frac1{20},\quad f(u_{21},v_{2A})=\frac1{20},\quad
f(s,u_{23})=\frac1{20},\quad f(u_{23},v_{2B})=\frac1{20},
\]
with all carry arcs equal to zero and all remaining atom arcs unused. One optimal dual
certificate is
\[
\varphi_s=0,\quad
\varphi_{11}=0,\ \varphi_{12}=0,\ \varphi_{21}=0,\ \varphi_{22}=1,\ \varphi_{23}=0,
\]
\[
\varphi_{1A}=1,\ \varphi_{1B}=0,\ \varphi_{2A}=1,\ \varphi_{2B}=0,\ \varphi_t=0,
\]
with reduced-cost slacks
\[
\sigma_{(u_{22},v_{2A})}=0,\qquad
\sigma_{(s,u_{22})}=1,
\]
and \(\sigma_e=0\) on every other used or unused finite-capacity arc. The primal cost is
\(-3/10\), the dual value is \(-3/10\), and complementary slackness holds arc by arc.
\end{theorem}

\section{Sanity-check corollaries}
\begin{corollary}[Parent reduction]\label{cor:parent}
Under Assumptions~\ref{ass:laminar}--\ref{ass:slice-feasible}, if \(J=1\), then
\(\Delta_{1w}(m)=m_1\pi_{1,-}(w)\), the carry arcs disappear, and
Theorem~\ref{thm:slice-flow} reduces to the parent one-cutoff retained-plan program. The
reduction is immediate because the laminar network has one demand layer, so the only dual
multiplier beyond the Wald ratio index is the parent retained-mass multiplier.
\end{corollary}

\begin{corollary}[Sharp RD one-cell face]\label{cor:onecell}
If \(J=1\), \(K=1\), and the design is sharp RD, then the slice flow in
Theorem~\ref{thm:slice-flow} reduces to ordinary one-dimensional outcome-tail trimming.
The reduction holds because there is one demand node and one covariate cell, so the network
orders atoms only by the score \(y-\lambda d\).
\end{corollary}

\paragraph{Exhibit 9.1.}
Under Assumption~\ref{ass:witness}, the node set is
\[
\{s,t,u_{11},u_{12},u_{21},u_{22},u_{23},v_{1A},v_{1B},v_{2A},v_{2B}\}.
\]
The finite-capacity arcs are
\[
(s,u_{11}),\ (s,u_{12}),\ (s,u_{21}),\ (s,u_{22}),\ (s,u_{23}),
\]
\[
(u_{11},v_{1A}),\ (u_{12},v_{1B}),\ (u_{21},v_{2A}),\ (u_{22},v_{2A}),\ (u_{23},v_{2B}),
\]
with capacities \(1/4,1/4,1/20,3/20,1/5\) in that order. The carry arcs are
\((v_{1A},v_{2A})\), \((v_{1B},v_{2B})\), \((v_{2A},t)\), and \((v_{2B},t)\), all with
zero cost and slack capacity. The balances are
\[
b(v_{1A})=-\frac14,\quad b(v_{1B})=-\frac14,\quad
b(v_{2A})=-\frac1{20},\quad b(v_{2B})=-\frac1{20},\quad
b(s)=\frac35.
\]
At \(\lambda=0\), the atom-to-demand costs are \(-1,0,-1,0,0\). The primal flow in
Theorem~\ref{thm:witness} exactly meets each balance from the Section~6 primitives and
uses no carry, so the internal-consistency checks are immediate: demanded mass is \(3/5\),
available mass is \(9/10\), and no arc exceeds its capacity.

\paragraph{Exhibit 9.2.}
For the same witness, the nonzero reduced-cost calculation is only on the unused atom
\(u_{22}\) with cost \(0\). The dual inequality on \((u_{22},v_{2A})\) is
\[
\varphi_{22}-\varphi_{2A}-\sigma_{(u_{22},v_{2A})}\le 0,
\]
which binds at \(1-1-0=0\). The source arc \((s,u_{22})\) has zero cost and satisfies
\[
\varphi_s-\varphi_{22}-\sigma_{(s,u_{22})}\le 0,
\]
which binds at \(0-1+1=0\); since \(f(s,u_{22})=0<u(s,u_{22})\), the positive slack sits
on the source-capacity side and certifies that the low-outcome atom is not purchased. Every
used atom-to-demand arc has \(\sigma_e=0\) and equality of dual difference and primal cost:
\[
0-1=-1,\quad 0-0=0,\quad 0-1=-1,\quad 0-0=0.
\]
Thus complementary slackness is checked arc by arc from the explicit potentials, not only
at the objective level.

\section{Proof-sketch route}
The verification route is a chain of four substantive steps. First, rewrite each fixed-slice
retained-plan LP as a transportation problem whose demands are the incremental retained
cell masses \(\Delta_{jw}(m)\). Second, encode laminar extendability by carry arcs between
successive neighborhood-cell nodes and identify the resulting matrix as a network incidence
matrix. Third, use linear-fractional reduction in \(\lambda\) together with network duality
to connect primal retained plans to node-potential certificates. Fourth, prove the parent
collapse by deleting the carry layer at \(J=1\) and matching the surviving potentials to
the parent retained-mass multiplier. The open step is the global optimization over
\(\calM_{\mathrm{ext}}\), not the fixed-slice network equivalence.

\section{Honest scope flags}
The proved part of the proposal is the fixed-slice graph rewrite and the worked witness.
The flagship content remains open: Conjecture~\ref{conj:sharp-envelope} still needs a full
sharpness argument over the extendable retained-mass set, and
Conjecture~\ref{conj:dual} still needs the general parent-collapse proof beyond the worked
instance. The proposal is intentionally finite-dimensional and laminar; arbitrary
non-nested neighborhoods or continuous covariates are outside scope. The prior parent
headline about one-cutoff bounded-manipulation RD is not repeated as a standalone result
here; it appears only as Corollary~\ref{cor:parent}.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial upgrade draft from the banked parent; prior verdict: none.
\item v2 (revise) --- sharpened the computation delta against the parent and separated slice theorems from the open global search; prior verdict: REVISE.
\item v3 (revise) --- narrowed the flagship claim to many-neighborhood laminar slices and added the parent-collapse comparator chain; prior verdict: REVISE.
\item v4 (revise) --- added the worked two-neighborhood witness and explicit many-threshold literature anchors; prior verdict: REVISE.
\item v5 (revise) --- exhibited the full graph primitives, numeric primal flow, numeric dual potentials, and complementary-slackness audit for the \(J=2\) witness; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}

\bibitem[Bertanha(2020)]{bertanha_2020_many_thresholds}
Bertanha, Marinho.
2020.
Regression discontinuity design with many thresholds.
\emph{Journal of Econometrics} 218(1): 216--241.

\bibitem[Cattaneo, Jansson, and Ma(2020)]{cattaneo_jansson_ma_2020_density}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem[Cattaneo et~al.(2021)]{cattaneo_keele_titiunik_vazquezbare_2021_multicutoff}
Cattaneo, Matias D., Luke Keele, Rocio Titiunik, and Gonzalo Vazquez-Bare.
2021.
Extrapolating treatment effects in multi-cutoff regression discontinuity designs.
\emph{Journal of the American Statistical Association} 116(536): 1941--1952.

\bibitem[Gerard, Rokkanen, and Rothe(2020)]{gerard_rokkanen_rothe_2020_rdbounds}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem[Horowitz and Manski(1995)]{horowitz_manski_1995_contaminated}
Horowitz, Joel L., and Charles F. Manski.
1995.
Identification and robustness with contaminated and corrupted data.
\emph{Econometrica} 63(2): 281--302.

\bibitem[Lee(2009)]{lee_2009_selection_bounds}
Lee, David S.
2009.
Training, wages, and sample selection: Estimating sharp bounds on treatment effects.
\emph{Review of Economic Studies} 76(3): 1071--1102.

\bibitem[McCrary(2008)]{mccrary_2008_density_test}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem[Orlin(1993)]{orlin_1993_mincostflow}
Orlin, James B.
1993.
A faster strongly polynomial minimum cost flow algorithm.
\emph{Operations Research} 41(2): 338--350.

\bibitem[Rosenman et~al.(2019)]{rosenman_rajkumar_gauriot_slonim_2019_discrete_manipulation}
Rosenman, Evan, Karthik Rajkumar, Romain Gauriot, and Robert Slonim.
2019.
Optimized partial identification bounds for regression discontinuity designs with manipulation.
arXiv:1910.02170.

\bibitem[Schrijver(1986)]{schrijver_1986_theory_linear_integer}
Schrijver, Alexander.
1986.
\emph{Theory of Linear and Integer Programming}.
Wiley.

\end{thebibliography}
\end{document}
