% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_rdd\_flow\_manipulation, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_rdd\_flow\_manipulation} / \texttt{v1}%
  \\ \large\textit{Sharp many-neighborhood RD manipulation bounds via a joint min-cost-flow dual}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal. The locked tuple is
\[
  (\texttt{qid}, \texttt{specialization}, P, \theta, \text{identifying restrictions},
  \text{bounding functional})
\]
with the following convention. \(\texttt{qid}=\texttt{pid\_rdd\_flow\_manipulation}\) and
\(\texttt{specialization}=\texttt{v1}\). The observable distribution \(P\) is a finite-support
many-neighborhood manipulated-RD input
\[
  P=\bigl\{P_{j,-},P_{j,+}: j=1,\ldots,J\bigr\},
\]
where \(j\) indexes cutoff neighborhoods, each \(P_{j,-}\) and \(P_{j,+}\) is the left and right
cutoff-side law of \((Y,D,W,U)\), \(Y\in[\underline y,\overline y]\), \(D\in\{0,1\}\),
\(W\in\{1,\ldots,K\}\) is a predetermined covariate cell, and \(U\) indexes finitely many
right-side atoms inside \((j,w)\). The parameter \(\theta\) is the pooled nonmanipulator local
Wald effect
\[
  \theta_\beta =
  \frac{\sum_{j=1}^J \beta_j
    \sum_w \pi_{j,-}(w)\{\mu^Y_{j,+,0}(w)-\mu^Y_{j,-}(w)\}}
       {\sum_{j=1}^J \beta_j
    \sum_w \pi_{j,-}(w)\{\mu^D_{j,+,0}(w)-\mu^D_{j,-}(w)\}},
\]
for fixed nonnegative weights \(\beta_j\) summing to one, where
\(\pi_{j,-}(w)=P_{j,-}(W=w)\), \(\mu^V_{j,-}(w)=\E_{P_{j,-}}[V\mid W=w]\), and
\(\mu^V_{j,+,0}(w)\) is the right-limit nonmanipulator mean of \(V\in\{Y,D\}\) in neighborhood
\(j\), cell \(w\). The identifying restrictions are: one-sided manipulation in each
neighborhood, local continuity of the nonmanipulator law conditional on \(W\), neighborhood
global envelopes \(\bar\rho_j\in[0,1)\), shared cross-neighborhood cell-removal budgets
\(\bar S_w\ge 0\), bounded outcomes, exact retained-\(W\) matching inside each neighborhood,
positive retained mass, positive pooled first stage, and a laminar neighborhood structure used
for the flow representation. The bounding functional is the sharp pooled interval
\[
  B_L^\beta(P,\bar\rho,\bar S)=\inf_{x\in\mathcal A(P,\bar\rho,\bar S)} \Theta_\beta(x),
  \qquad
  B_U^\beta(P,\bar\rho,\bar S)=\sup_{x\in\mathcal A(P,\bar\rho,\bar S)} \Theta_\beta(x),
\]
where \(x\) is a joint retention plan over right-side atoms, \(\mathcal A(P,\bar\rho,\bar S)\)
enforces neighborhood envelopes, shared cell budgets, and retained-\(W\) equalities, and
\(\Theta_\beta(x)\) is the pooled Wald ratio formed from retained right-side means and observed
left-side means. When \(J=1\) and \(\bar S_w=\bar s_w P_{1,+}(W=w)\), this convention reduces to
the banked parent \(\texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1}\).

\begin{abstract}
The banked parent \texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1} characterizes a
one-cutoff bounded-manipulation RD interval through a \(\lambda\)-indexed linear-fractional
endpoint program. This proposal asks whether the many-neighborhood analogue admits a sharp
network-flow representation when several cutoff neighborhoods share manipulation budgets across
predetermined covariate cells. The headline claim is that the pooled manipulation-robust RD
support function should equal a min-cost-flow problem on a laminar neighborhood graph, with a
total-unimodular dual certificate that recovers the parent interval when \(J=1\). A second
claim is that the joint certificate is not only computationally cleaner but substantively
sharper: a binding shared cell budget can force a larger retained mass in one neighborhood once
another neighborhood uses the same scarce cell. If resolved, the result would turn current
many-cutoff RD practice from cutoff-by-cutoff sensitivity reporting into a joint sharp partial-ID
computation with an auditable dual witness.
\end{abstract}

\section{Introduction}
The question is whether bounded-manipulation RD partial identification remains sharp and
computable once the analyst stacks many cutoff neighborhoods and allows the same covariate cell
budget to bind across them. The main claim is Conjecture~\ref{conj:flow-dual}: after a
\(\lambda\)-indexed support-function transform, the pooled endpoint problem should be equivalent
to a min-cost-flow program whose dual variables certify both the active shared cell budgets and
the parent one-cutoff interval.

Relative to the parent \texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1}, the upgrade axis is
computation: the parent leaves endpoint evaluation as linear programs indexed by a candidate
ratio, while this run seeks a network representation with a strongly polynomial oracle.
Relative to published work, \citet{GerardRokkanenRothe2020} derive sharp one-cutoff manipulated-RD
bounds and optimize over partially identified shares in fuzzy RD (Corollary 3, p.~22;
Corollary 4, p.~23; Corollary 9, p.~44), while \citet{Bertanha2020} studies many-threshold RD
under standard identification by pooling local effects across cutoffs (Introduction, pp.~216--218).
The missing statement is a joint partial-ID theorem combining many neighborhoods, shared cell
budgets, and an explicit computational dual. The kernel lives in partial identification with a
computational-combinatorial interface.

The concrete consumer is many-cutoff empirical RD practice, especially software and applications
that now report pooled or cutoff-specific effects neighborhood by neighborhood
\citep{CattaneoTitiunikVazquezBare2020,Bertanha2020}. If the joint certificate exists, an
applied researcher with several neighborhoods and one suspicious covariate cell no longer solves
separate sensitivity problems and averages them ex post; the researcher solves one joint sharp
program and reads off which shared cap binds.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the one-neighborhood corner of the joint program reduces exactly to the banked parent bounded-manipulation interval. Gap: parent \texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1} is one-cutoff only; this pins the upgrade boundary case. Consumer: \citet{GerardRokkanenRothe2020}.
\item Conjecture 1: the \(\lambda\)-transformed pooled endpoint equals a laminar min-cost-flow problem with a total-unimodular dual certificate, hence admits a strongly polynomial oracle. Gap: \citet{GerardRokkanenRothe2020} give one-cutoff sharp bounds, while \citet{Orlin1993} gives flow complexity abstractly; neither identifies this RD manipulation network. Consumer: multi-cutoff RD implementations.
\item Theorem 2: when shared cell budgets are slack or separable by neighborhood, the joint flow decomposes into independent parent subproblems. Gap: existing many-cutoff RD work does not isolate the exact boundary between joint and separate computation. Consumer: \citet{CattaneoTitiunikVazquezBare2020}.
\item Conjecture 2: on an open two-neighborhood class, the joint sharp upper endpoint is strictly below the weighted average of separate neighborhood bounds because one shared cell budget binds both neighborhoods. Gap: \citet{Bertanha2020} studies pooling without manipulation, and the parent only has a one-cutoff cap-separation witness. Consumer: manipulated multi-cutoff RD applications.
\end{itemize}

\section{Related work}
\citet{GerardRokkanenRothe2020} [reused from parent] is the direct econometric ancestor. The
paper derives sharp bounds for manipulated sharp and fuzzy RD, including covariate-conditioned
results and partially identified share optimization. The present proposal keeps that one-cutoff
identification logic but asks for a many-neighborhood joint support function with shared cell
budgets and an explicit dual certificate.

\citet{McCrary2008} [reused from parent] and \citet{CattaneoJanssonMa2020} [reused from parent]
anchor the manipulation-diagnostic side of the problem. The first turns density discontinuities
into evidence of sorting, and the second gives the boundary-adaptive density procedure used in
practice. The proposal consumes these objects as sources of neighborhood-wise envelope parameters
\(\bar\rho_j\), not as endpoint formulas.

\citet{Lee2009} [reused from parent] and \citet{HorowitzManski1995} [reused from parent]
provide the trimming and contaminated-data geometry behind the parent one-cutoff bound. Their
relevance here is structural: once the pooled Wald objective is converted to a support function,
the remaining difficulty is not the existence of trimming logic but the cross-neighborhood
coupling induced by shared cell budgets.

\citet{Bertanha2020} [new relative to parent proposal] and
\citet{CattaneoTitiunikVazquezBare2020} [reused from parent literature map] represent the
active many-cutoff RD frontier. Bertanha studies how to pool many thresholds under maintained
point-identification structure, and \texttt{rdmulti} operationalizes cutoff-specific and pooled
RD estimation. Neither paper studies manipulation-driven partial identification or a joint
optimization certificate across neighborhoods.

\citet{Orlin1993} is the new computational anchor. It gives a strongly polynomial algorithm for
minimum-cost flow. The upgrade claim is not that min-cost flow is new, but that the many-neighborhood
RD manipulation support function may have exactly that structure once the laminar retained-\(W\)
and shared-cap constraints are written as node-balance equations.

In repository prior art is thin by design. `CausalSmith/doc/API.md` Section 3 records that the
PartialID catalogue is effectively empty apart from study-specific wrappers, so there is no
non-parent catalogue entry duplicating this kernel. The only close in-repo theorem proposal is
the banked parent \(\texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1}\), whose headline
statement is a one-cutoff bounded-manipulation interval with a \(\lambda\)-indexed LP endpoint
route; the present proposal upgrades that route to a many-neighborhood flow dual.

\section{Formal setup}
Fix neighborhoods \(j\in\{1,\ldots,J\}\), covariate cells \(w\in\{1,\ldots,K\}\), and for each
\((j,w)\) a finite set of right-side atoms \(u\in\{1,\ldots,L_{jw}\}\). The observable input is
\[
  P=\{P_{j,-},P_{j,+}\}_{j=1}^J,
\]
where \(P_{j,-}\) and \(P_{j,+}\) are the left and right cutoff-side laws of \((Y,D,W,U)\) for
neighborhood \(j\). Write \(p_{jwu}=P_{j,+}(W=w,U=u)\), \(\pi_{j,-}(w)=P_{j,-}(W=w)\), and let
\((y_{jwu},d_{jwu})\) denote the outcome and treatment values on atom \((j,w,u)\). Let
\(\mu^V_{j,-}(w)=\E_{P_{j,-}}[V\mid W=w]\) for \(V\in\{Y,D\}\). The analyst fixes weights
\(\beta_j\ge 0\) with \(\sum_j \beta_j=1\), neighborhood manipulation envelopes
\(\bar\rho_j\in[0,1)\), and shared cross-neighborhood cell-removal budgets \(\bar S_w\ge 0\).

A joint retention plan is an array \(x=(x_{jwu})\) with \(0\le x_{jwu}\le p_{jwu}\). Let
\[
  m_j(x)=\sum_{w=1}^K \sum_{u=1}^{L_{jw}} x_{jwu}
\]
be retained mass in neighborhood \(j\), and define the retained law
\[
  Q_{j,x}(Y=y_{jwu},D=d_{jwu},W=w,U=u)=\frac{x_{jwu}}{m_j(x)}
  \qquad \text{when }m_j(x)>0.
\]
The feasible set \(\mathcal A(P,\bar\rho,\bar S)\) consists of retention plans satisfying
\[
  1-m_j(x)\le \bar\rho_j \qquad \text{for each }j,
\]
\[
  \sum_{u=1}^{L_{jw}} x_{jwu}=m_j(x)\pi_{j,-}(w)
  \qquad \text{for each }(j,w),
\]
and the shared cell-budget inequality
\[
  \sum_{j=1}^J \left(P_{j,+}(W=w)-\sum_{u=1}^{L_{jw}} x_{jwu}\right)\le \bar S_w
  \qquad \text{for each }w.
\]
The pooled Wald functional is
\[
  \Theta_\beta(x)=
  \frac{\sum_{j=1}^J \beta_j
    \sum_{w=1}^K \pi_{j,-}(w)\{\E_{Q_{j,x}}[Y\mid W=w]-\mu^Y_{j,-}(w)\}}
       {\sum_{j=1}^J \beta_j
    \sum_{w=1}^K \pi_{j,-}(w)\{\E_{Q_{j,x}}[D\mid W=w]-\mu^D_{j,-}(w)\}}.
\]
Equivalently,
\[
  \Theta_\beta(x)=
  \frac{\sum_{j=1}^J \beta_j \left(
    m_j(x)^{-1}\sum_{w,u} y_{jwu}x_{jwu}-\E_{P_{j,-}}[Y]\right)}
       {\sum_{j=1}^J \beta_j \left(
    m_j(x)^{-1}\sum_{w,u} d_{jwu}x_{jwu}-\E_{P_{j,-}}[D]\right)}.
\]
The identified set is
\[
  \Theta_I^\beta(P,\bar\rho,\bar S)
  =\{\Theta_\beta(x):x\in \mathcal A(P,\bar\rho,\bar S)\}.
\]
For \(\lambda\in\R\), define the transformed support-function objective
\[
  V_\lambda(P,\bar\rho,\bar S)
  =
  \sup_{x\in\mathcal A(P,\bar\rho,\bar S)}
  \sum_{j=1}^J \beta_j
  \left[
    \sum_{w=1}^K \pi_{j,-}(w)
    \{\E_{Q_{j,x}}[Y-\lambda D\mid W=w]
     -(\mu^Y_{j,-}(w)-\lambda\mu^D_{j,-}(w))\}
  \right].
\]
The upper endpoint is the smallest \(\lambda\) with \(V_\lambda\le 0\), and the lower endpoint
is the largest \(\lambda\) with the sign reversed.
Write \(V_{j,\lambda}(P_{j,-},P_{j,+},\bar\rho_j)\) for the same transformed objective in the
one-neighborhood problem obtained by fixing \(J=1\) and removing shared cross-neighborhood
budgets. Write \(B_{U,j,\mathrm{sep}}(P_{j,-},P_{j,+},\bar\rho_j)\) for the resulting separate
upper endpoint in neighborhood \(j\).

\begin{verbatim}
Locked parameters.
qid = pid_rdd_flow_manipulation
specialization = v1
observable distribution P = finite-support collection {P_{j,-}, P_{j,+}}_{j=1}^J of
  cutoff-neighborhood left/right laws of (Y,D,W,U)
parameter theta = pooled nonmanipulator local Wald effect theta_beta with user-fixed
  neighborhood weights beta_j
identifying restrictions = one-sided neighborhood-wise manipulation; conditional
  nonmanipulator continuity; neighborhood envelopes rho_bar_j; shared cross-neighborhood
  cell-removal budgets S_bar_w; retained-W matching inside each neighborhood; bounded
  outcomes; positive retained mass; positive pooled first stage; laminar neighborhood structure
bounding functional = sharp pooled interval
  [inf_{x in A(P,rho_bar,S_bar)} Theta_beta(x),
   sup_{x in A(P,rho_bar,S_bar)} Theta_beta(x)]
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite-support many-neighborhood input]\label{ass:finite-support}
For each neighborhood \(j\), the side limits \(P_{j,-}\) and \(P_{j,+}\) exist on
\([\underline y,\overline y]\times\{0,1\}\times\{1,\ldots,K\}\times\mathcal U_j\), with
\(-\infty<\underline y\le \overline y<\infty\), \(\pi_{j,-}(w)>0\) for every \((j,w)\), and
\(\mathcal U_j\) finite.
\end{assumption}

\begin{assumption}[One-sided manipulation and conditional continuity]\label{ass:continuity}
Within each neighborhood \(j\), the left-side limit is the nonmanipulator law, the right-side
limit is a mixture of nonmanipulators and upward manipulators, and the nonmanipulator right-side
covariate law equals \(\pi_{j,-}\). Hence a feasible retention plan recovers the right-limit
nonmanipulator means cell by cell.
\end{assumption}

\begin{assumption}[Neighborhood envelopes]\label{ass:envelopes}
For every feasible retention plan \(x\), retained mass satisfies \(1-m_j(x)\le \bar\rho_j\) in
each neighborhood \(j\).
\end{assumption}

\begin{assumption}[Shared cell budgets]\label{ass:shared-caps}
For every feasible retention plan \(x\), total removed mass from cell \(w\) across all
neighborhoods satisfies
\[
  \sum_{j=1}^J \left(P_{j,+}(W=w)-\sum_u x_{jwu}\right)\le \bar S_w .
\]
\end{assumption}

\begin{assumption}[Positive pooled first stage]\label{ass:first-stage}
There exists \(\kappa>0\) such that for every \(x\in\mathcal A(P,\bar\rho,\bar S)\),
\[
  \sum_{j=1}^J \beta_j
  \sum_{w=1}^K \pi_{j,-}(w)\{\E_{Q_{j,x}}[D\mid W=w]-\mu^D_{j,-}(w)\}\ge \kappa .
\]
\end{assumption}

\begin{assumption}[Laminar neighborhood family]\label{ass:laminar}
The neighborhoods can be ordered so that any two are either disjoint or nested, and the
retained-\(W\) equalities together with the shared cell budgets can be represented by flow
conservation on a directed acyclic graph built from neighborhood nodes, cell nodes, and right-side
atom nodes.
\end{assumption}

\begin{assumption}[Parent reduction corner]\label{ass:parent-corner}
For results invoking the parent reduction, \(J=1\), \(\beta_1=1\), and
\(\bar S_w=\bar s_w P_{1,+}(W=w)\) for some parent cell-share parameters \(\bar s_w\).
\end{assumption}

\begin{assumption}[Decoupled shared caps]\label{ass:decoupled}
For results invoking decomposition, each shared budget is either slack at every optimizer or
separable as \(\bar S_w=\sum_j \bar S_{jw}\) with no cross-neighborhood coupling in the active
constraints.
\end{assumption}

\begin{assumption}[Two-neighborhood separation witness]\label{ass:witness}
For results invoking strict joint tightening, \(J=2\), \(K=2\), \(D=Z\), both neighborhoods have
\(\pi_{j,-}(1)=\pi_{j,-}(2)=1/2\), \(P_{j,+}(W=1)=3/5\), \(P_{j,+}(W=2)=2/5\),
\(\bar\rho_1=\bar\rho_2=1/2\), and the shared budget is \(\bar S_1=1/2\) with \(\bar S_2\) slack.
In each neighborhood, cell \(1\) has a right-side outcome atom of mass \(3/10\) at \(Y=1\) and a
right-side outcome atom of mass \(3/10\) at \(Y=0\); cell \(2\) has all right-side mass at
\(Y=0\); left-side outcome means are zero.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: one-neighborhood reduction to the parent]\label{thm:parent-reduction}
Under Assumptions~\ref{ass:finite-support}--\ref{ass:first-stage} and
Assumption~\ref{ass:parent-corner}, the feasible set \(\mathcal A(P,\bar\rho,\bar S)\) is
identical to the parent one-cutoff feasible set after the identification
\(\bar S_w=\bar s_w P_{1,+}(W=w)\). Consequently,
\[
  \Theta_I^\beta(P,\bar\rho,\bar S)
  =\Theta_I(P_{1,-},P_{1,+},\bar\rho_1,\bar s)
\]
and
\[
  [B_L^\beta(P,\bar\rho,\bar S),B_U^\beta(P,\bar\rho,\bar S)]
  =
  [B_L(P_{1,-},P_{1,+},\bar\rho_1,\bar s),B_U(P_{1,-},P_{1,+},\bar\rho_1,\bar s)] .
\]
\end{theorem}

The proof is a relabeling argument. When \(J=1\), the shared cell-budget inequality becomes the
parent cell-cap inequality after dividing by \(P_{1,+}(W=w)\), and the pooled Wald ratio is the
parent Wald ratio because \(\beta_1=1\).

\begin{conjecture}[Conjecture 1: laminar flow dual for the pooled endpoint]\label{conj:flow-dual}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite-support}--\ref{ass:laminar}, for every
\(\lambda\in\R\) the transformed objective \(V_\lambda(P,\bar\rho,\bar S)\) is equal to the value
of a min-cost-flow problem on a directed acyclic graph \(G_\lambda(P)\) with node-arc incidence
matrix \(N_\lambda(P)\). The graph has atom-supply nodes, neighborhood-cell demand nodes, and
shared-cell budget nodes, and its arc costs are affine in \(y_{jwu}-\lambda d_{jwu}\). Moreover,
\(N_\lambda(P)\) is a network matrix and hence totally unimodular. Therefore the upper and lower
endpoints satisfy
\[
  B_U^\beta(P,\bar\rho,\bar S)=\inf\{\lambda:V_\lambda(P,\bar\rho,\bar S)\le 0\},
  \qquad
  B_L^\beta(P,\bar\rho,\bar S)=\sup\{\lambda:V_\lambda(P,\bar\rho,\bar S)\ge 0\},
\]
and can be computed by a strongly polynomial outer search over \(\lambda\) with a min-cost-flow
oracle. The dual multipliers on the shared-cell nodes recover the parent one-cutoff certificate
from Theorem~\ref{thm:parent-reduction} when \(J=1\).
\end{conjecture}

\begin{theorem}[Theorem 2: decomposition when shared caps are inactive]\label{thm:decompose}
Under Assumptions~\ref{ass:finite-support}--\ref{ass:first-stage} and
Assumption~\ref{ass:decoupled}, the transformed objective decomposes as
\[
  V_\lambda(P,\bar\rho,\bar S)
  =
  \sum_{j=1}^J \beta_j V_{j,\lambda}(P_{j,-},P_{j,+},\bar\rho_j),
\]
where each \(V_{j,\lambda}\) is the parent one-neighborhood transformed program. Hence the joint
endpoint equals the weighted combination of separate neighborhood endpoints whenever no shared
cell budget is active.
\end{theorem}

The proof separates the Lagrangian by neighborhood once every shared-cell multiplier is zero, or
equivalently once the shared-cap constraints split additively by neighborhood. The parent program
then reappears term by term.

\begin{conjecture}[Conjecture 2: strict joint tightening relative to separate solves]\label{conj:strict}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite-support}--\ref{ass:first-stage} and
Assumption~\ref{ass:witness}, the joint sharp upper endpoint satisfies
\[
  B_U^\beta(P,\bar\rho,\bar S)
  <
  \sum_{j=1}^2 \beta_j B_{U,j,\mathrm{sep}}(P_{j,-},P_{j,+},\bar\rho_j),
\]
where \(B_{U,j,\mathrm{sep}}\) is the upper endpoint obtained by solving neighborhood \(j\)
separately without the cross-neighborhood budget \(\bar S_1\). The strict inequality is locally
stable under perturbations of the atom probabilities and envelope parameters that preserve the
same binding shared cell.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Reduction to the parent under \(J=1\)]\label{cor:parent}
Under Assumptions~\ref{ass:finite-support}--\ref{ass:first-stage} and
Assumption~\ref{ass:parent-corner}, Theorem~\ref{thm:parent-reduction} recovers the banked parent
\(\texttt{pid\_rdd\_manipulation\_bounded}/\texttt{v1}\). The reduction holds because the shared
budget \(\bar S_w\) becomes the parent cellwise removal cap, and all cross-neighborhood indices
disappear.
\end{corollary}

\begin{corollary}[Separate-neighborhood practice is correct only off the shared-cap face]\label{cor:separate}
Under Assumptions~\ref{ass:finite-support}--\ref{ass:first-stage} and
Assumption~\ref{ass:decoupled}, solving neighborhoods separately and averaging the resulting
endpoints is exact. Under Conjecture~\ref{conj:strict}, that same procedure is strictly
anti-conservative once a shared cell budget binds.
\end{corollary}

\paragraph{Exhibit 9.1: one-neighborhood dual corner computed from primitives.}
Take \(J=1\), \(K=2\), \(\pi_{1,-}(1)=\pi_{1,-}(2)=1/2\), \(P_{1,+}(W=1)=3/5\),
\(P_{1,+}(W=2)=2/5\), \(\bar\rho_1=1/2\), and
\[
  \bar S_1=\frac14, \qquad \bar S_2=\frac15 .
\]
The retained-\(W\) equations require cell-\(w\) retained mass \(m\pi_{1,-}(w)\), so the removed
mass in cell \(w\) is \(P_{1,+}(W=w)-m/2\). The shared-cap inequalities therefore imply
\[
  \frac35-\frac m2\le \frac14, \qquad \frac25-\frac m2\le \frac15,
\]
which yields the minimum feasible retained mass \(m^\star=7/10\). A primal feasible flow keeps
\(x_{111}=x_{121}=7/20\) in the two cells, removes \(1/4\) from cell \(1\), and removes \(1/20\)
from cell \(2\). If the right-side outcome atoms are \(3/10\) at \(Y=1\) and \(3/10\) at \(Y=0\)
in cell \(1\), with all right-side mass at \(Y=0\) in cell \(2\), then the retained conditional
mean in cell \(1\) is \((3/10)/(7/20)=6/7\), the retained mean in cell \(2\) is \(0\), and the
sharp-RD upper endpoint is \(B_U=3/7\). This is exactly the parent witness value. Internal
consistency check: the retained masses sum to \(7/10\), no cell retains more than observed mass,
and the sharp-RD denominator is one.

\paragraph{Exhibit 9.2: strict joint tightening on a two-neighborhood instance.}
Under Assumption~\ref{ass:witness}, each neighborhood solved separately can remove
\(7/20\) from cell \(1\), attain retained mass \(m_j=1/2\), and achieve upper endpoint \(1/2\).
Jointly, the shared budget \(\bar S_1=1/2\) imposes
\[
  \left(\frac35-\frac{m_1}{2}\right)+\left(\frac35-\frac{m_2}{2}\right)\le \frac12,
\]
so every joint feasible plan satisfies \(m_1+m_2\ge 7/5\). The symmetric choice
\((m_1,m_2)=(7/10,7/10)\) is feasible and saturates the shared cap, and Exhibit 9.1 then gives
each neighborhood upper endpoint \(3/7\). Hence the joint weighted upper value is \(3/7\), while
the weighted average of separate upper values is \(1/2\). The difference is not a normalization
artifact: both calculations use the same pooled weights \((\beta_1,\beta_2)=(1/2,1/2)\), the
same left-side means, and the same atom masses; only the shared budget distinguishes them.

\section{Proof-sketch route}
For Conjecture~\ref{conj:flow-dual}, the reduction chain is
\[
  \text{headline}
  \leftarrow \text{support-function transform of }\Theta_\beta
  \leftarrow \text{atomized retained-mass representation}
  \leftarrow \text{retained-}W\text{ equalities written as node balances}
  \leftarrow \text{shared-cap inequalities written as budget arcs}
  \leftarrow \text{laminar node-splitting gives a network matrix}
  \leftarrow \text{network-flow duality and TU}.
\]
This has \(k=4\) substantive non-definitional steps: the support-function transform, the
atomization-to-flow rewrite, the laminar network-matrix lemma, and the duality/TU step. For
Conjecture~\ref{conj:strict}, the chain is
\[
  \text{strict joint gap}
  \leftarrow \text{shared-cap lower bound on }m_1+m_2
  \leftarrow \text{cell-1 upper-tail crossing at }r=1/2
  \leftarrow \text{monotonicity of the sharp-RD fixed-mass endpoint},
\]
with \(k=3\). The boundary cases needing explicit algebra are the parent \(J=1\) corner, the
decomposition face where all shared-cap multipliers vanish, and the two-neighborhood witness in
Exhibit 9.2.

\section{Honest scope flags}
Theorem~\ref{thm:parent-reduction} and Theorem~\ref{thm:decompose} are routine once the feasible
set is written correctly. Conjecture~\ref{conj:flow-dual} is the flagship delta and is not yet
proved: the load-bearing step is the claim that the laminar many-neighborhood constraint matrix is
a network matrix rather than a generic linear program. Conjecture~\ref{conj:strict} is also open:
the worked witness computes the geometry, but the open-set stability statement still needs a full
proof. No statements from the parent were withdrawn here; the upgrade preserves the parent kernel
and changes only the computational representation and the many-neighborhood coupling. I am least
certain about the exact regularity needed to justify a strongly polynomial outer search in
\(\lambda\) without adding a finite-support grid or piecewise-linearity lemma.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for the joint many-neighborhood flow-dual angle replacing the dead prior angle; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bertanha(2020)]{Bertanha2020}
Bertanha, Marinho.
2020.
Regression discontinuity design with many thresholds.
\emph{Journal of Econometrics} 218(1): 216--241.

\bibitem[Cattaneo, Jansson, and Ma(2020)]{CattaneoJanssonMa2020}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem[Cattaneo, Titiunik, and Vazquez-Bare(2020)]{CattaneoTitiunikVazquezBare2020}
Cattaneo, Matias D., Rocio Titiunik, and Gonzalo Vazquez-Bare.
2020.
Analysis of regression-discontinuity designs with multiple cutoffs or multiple scores.
\emph{Stata Journal} 20(4): 866--891.

\bibitem[Gerard, Rokkanen, and Rothe(2020)]{GerardRokkanenRothe2020}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem[Horowitz and Manski(1995)]{HorowitzManski1995}
Horowitz, Joel L., and Charles F. Manski.
1995.
Identification and robustness with contaminated and corrupted data.
\emph{Econometrica} 63(2): 281--302.

\bibitem[Lee(2009)]{Lee2009}
Lee, David S.
2009.
Training, wages, and sample selection: Estimating sharp bounds on treatment effects.
\emph{Review of Economic Studies} 76(3): 1071--1102.

\bibitem[McCrary(2008)]{McCrary2008}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem[Orlin(1993)]{Orlin1993}
Orlin, James B.
1993.
A faster strongly polynomial minimum cost flow algorithm.
\emph{Operations Research} 41(2): 338--350.
\end{thebibliography}

\end{document}
