\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\section*{exp\_njack\_inflation\_frontier (isoperimetry\_lecam\_matched\_converse)}

\paragraph{TL;DR.} The proposed all-rule frontier is false on the frozen parameter domain. The padded uniform update block at \(L_\star\asymp\sqrt{Mn}\) does satisfy a uniform \(1+O(\sqrt{M/n})\) inflation bound, but when \(c_0=C_0=1/4\) an admissible empty/full multiscale update law and schedule-uniform proxy attain inflation exactly \(1\), matching the universal Poincar\'e floor.

\section{Project justification}

\paragraph{Gap.} Existing recompute theory proves expected conservativeness for a fixed update rule and displays an oracle-proxy tradeoff, but it does not quantify the unavoidable price of conservativeness after optimizing over update laws and proxies.

\paragraph{Niche.} The constant-direct-effect class removes the ordinary Neyman heterogeneity floor, so the frontier isolates conservativeness created by recomputation under local interference.

\paragraph{Fill.} The derivation proves the padded-block upper bound and then gives a boundary-collapse counterexample showing that the requested all-rule converse cannot hold over the stated rule and schedule classes.

\section{Related work}

Park and Wager (2026) introduce the Neyman Jackknife, derive the fixed-block cycle construction, and identify the oracle-proxy tradeoff; their discussion explicitly treats choice of the block length as unresolved. Harshaw, Middleton, and S\u00e4vje (2026) characterize admissible quadratic conservative bounds under specified exposure mappings, but their Loewner frontier neither indexes local radius nor measures unavoidable inflation. Lin and Ding (2025) establish design-based normality and pointwise HAC conservativeness for time-series experiments, not minimax tuning or an all-rule converse. Gao and Ding (2025) construct conservative network-HAC adjustments without a sharp bandwidth lower bound. Polyanskiy and Wu (2026) develop the general dual Le Cam theory that motivates a nuisance-rich functional lower bound rather than a parametric two-point witness. K\u00fcnsch (1989) supplies the block-jackknife precedent for the contiguous-block half of the argument.

\section{Setup}

Target (estimand / structural parameter): \(\tau=Y_i(1,w_{-i})-Y_i(0,w_{-i})\).
Identifying functional / recovery map: \(R_n^\star(M)=\inf_{(\mu,g)\in\mathfrak R_n}\sup_{Y\in\mathcal Y_n(M;c_0,C_0)}\mathbb E_W[\widehat V_{\mu,g}]/\operatorname{Var}_W(\widehat\tau)\).
\begin{itemize}
  \item \(n\) --- \texttt{cycle\_size}; \(\mathbb N\); \texttt{asymptotic\_index} $:=$ \texttt{Number of fixed experimental units on the cycle.}
  \item \(M\) --- \texttt{interference\_radius}; \(\{0,\ldots,\lfloor n/4\rfloor\}\); \texttt{dependence\_index} $:=$ \texttt{Radius of the local-interference neighborhood.}
  \item \(\delta\) --- \texttt{growth\_slack}; \((0,1)\); \texttt{asymptotic\_constant} $:=$ \texttt{Fixed exponent delimiting the growing-radius regime.}
  \item \(\alpha\) --- \texttt{radius\_growth\_exponent}; \((0,1)\); \texttt{model\_example\_constant} $:=$ \texttt{Illustrative exponent for a sublinear interference radius.}
  \item \(C_0\) --- \texttt{outcome\_envelope\_constant}; \((0,\infty)\); \texttt{class\_constant} $:=$ \texttt{Fixed outcome envelope and upper arc-wise score-variance constant.}
  \item \(c_0\) --- \texttt{variance\_density\_constant}; \((0,\min\{C_0,4C_0^2\}]\); \texttt{class\_constant} $:=$ \texttt{Fixed lower bound on arc-wise score variance per vertex.}
  \item \(V_n\) --- \texttt{unit\_set}; \(\mathbb Z/n\mathbb Z\); \texttt{population\_index} $:=$ \texttt{Vertex set of the cycle with cyclic addition.}
  \item \(\mathsf C_n\) --- \texttt{cycle\_graph}; \(V_n\times V_n\); \texttt{interference\_graph} $:=$ Undirected cycle graph on \(V_n\).
  \item \(\mathcal N_i\) --- \texttt{exposure\_neighborhood}; \(2^{V_n}\); \texttt{interference\_support} $:=$ Neighborhood \(\mathcal N_i=\{j\in V_n:d_{\mathsf C_n}(i,j)\le M\}\).
  \item \(W\) --- \texttt{assignment\_vector}; \(\{0,1\}^{V_n}\); \texttt{only\_random\_object} $:=$ \texttt{Bernoulli treatment assignment vector.}
  \item \(w\) --- \texttt{assignment\_argument}; \(\{0,1\}^{V_n}\); \texttt{potential\_outcome\_argument} $:=$ \texttt{Generic deterministic assignment vector used to index potential outcomes.}
  \item \(w'\) --- \texttt{assignment\_argument}; \(\{0,1\}^{V_n}\); \texttt{potential\_outcome\_argument} $:=$ \texttt{Second generic deterministic assignment vector used to state local interference.}
  \item \(Y_i(w)\) --- \texttt{potential\_outcome}; \(\mathbb R\); \texttt{causal\_primitive} $:=$ Fixed potential outcome of unit \(i\) under assignment \(w\).
  \item \(Y\) --- \texttt{potential\_outcome\_schedule}; \(\mathbb R^{n2^n}\); \texttt{finite\_population} $:=$ Collection \(Y=\{Y_i(w):i\in V_n,w\in\{0,1\}^{V_n}\}\).
  \item \(\tau\) --- \texttt{constant\_direct\_effect}; \([-1/2,1/2]\); \texttt{target\_estimand} $:=$ \texttt{Direct-effect contrast held constant across units and neighbor assignments.}
  \item \(\psi_i\) --- \texttt{IPW\_score}; \(\mathbb R\); \texttt{estimation\_summand} $:=$ Direct-effect score \(\psi_i=2(2W_i-1)Y_i(W)\).
  \item \(\widehat\tau\) --- \texttt{IPW\_estimator}; \(\mathbb R\); \texttt{point\_estimator} $:=$ Estimator \(\widehat\tau=n^{-1}\sum_{i\in V_n}\psi_i\).
  \item \(\mathcal A_{n,M}\) --- \texttt{long\_arc\_collection}; \(2^{V_n}\); \texttt{variance\_regularization\_index} $:=$ Cyclic contiguous arcs \(I\subseteq V_n\) with \(|I|\ge 2M+1\).
  \item \(I\) --- \texttt{cycle\_arc}; \(\mathcal A_{n,M}\); \texttt{variance\_regularization\_argument} $:=$ \texttt{Generic cyclic arc over which the score-variance density is evaluated.}
  \item \(a\) --- \texttt{local\_response\_baseline}; \(\mathbb R\); \texttt{model\_example\_constant} $:=$ \texttt{Baseline coefficient in the explicit local-response family verifying the arc-variance condition.}
  \item \(\eta\) --- \texttt{neighbor\_response\_coefficient}; \(\mathbb R\); \texttt{model\_example\_constant} $:=$ \texttt{Nearest-neighbor coefficient in the explicit local-response family verifying the arc-variance condition.}
  \item \(S\) --- \texttt{update\_set}; \(2^{V_n}\); \texttt{recomputation\_choice} $:=$ \texttt{Random index set whose treatment coordinates are Gibbs-rerandomized.}
  \item \(\mu\) --- \texttt{update\_set\_law}; \(\mathcal P(2^{V_n})\); \texttt{recomputation\_choice} $:=$ Assignment-independent law of \(S\).
  \item \(D(S)\) --- \texttt{deleted\_outcome\_set}; \(2^{V_n}\); \texttt{proxy\_information\_loss} $:=$ Set \(D(S)=\{i\in V_n:\mathcal N_i\cap S\ne\varnothing\}\).
  \item \(g\) --- \texttt{observable\_proxy\_map}; \(\mathbb R\)-valued measurable maps; \texttt{recomputation\_choice} $:=$ One fixed measurable map of \(S\), \(W_{-S}\), and \(\{Y_i(W):i\notin D(S)\}\).
  \item \(\lambda_\mu\) --- \texttt{Gibbs\_spectral\_gap}; \((0,1]\); \texttt{Poincare\_normalizer} $:=$ Spectral gap of the Bernoulli Gibbs-rerandomization transition induced by \(\mu\).
  \item \(\mathcal G\) --- \texttt{proxy\_map\_space}; \(\{g:g\text{ is an observable measurable proxy map}\}\); \texttt{function\_space} $:=$ \texttt{Measurable-map space used in the recompute rule class.}
  \item \(\mathfrak R_n\) --- \texttt{recompute\_rule\_class}; \(\mathcal P(2^{V_n})\times\mathcal G\); \texttt{minimax\_action\_class} $:=$ \texttt{Class of assignment-independent positive-gap update laws paired with schedule-uniform observable proxies.}
  \item \(L_\star\) --- \texttt{block\_length}; \(\mathbb N\); \texttt{attaining\_tuning} $:=$ Canonical block scale \(L_\star=\lfloor\sqrt{Mn}\rfloor\).
  \item \(L\) --- \texttt{calibration\_block\_length}; \(\{1,\ldots,n-1\}\); \texttt{calibration\_index} $:=$ \texttt{Block length in the no-interference calibration.}
  \item \(\mu_L,g_L\) --- \texttt{sutva\_block\_rule}; \(\mathfrak R_n\); \texttt{calibration\_rule} $:=$ Uniform length-\(L\) block law and leave-block proxy in the no-interference calibration.
  \item \(\mu_{L_\star},g_{L_\star}\) --- \texttt{padded\_block\_rule}; \(\mathfrak R_n\); \texttt{attaining\_rule} $:=$ Update law and observable proxy induced by the padded uniform block at length \(L_\star\).
  \item \(\widehat V_{\mu,g}\) --- \texttt{Neyman\_Jackknife\_variance\_estimator}; \([0,\infty)\); \texttt{variance\_estimator} $:=$ Recompute variance estimator normalized by \(\lambda_\mu\).
  \item \(\mathcal Y_n(M;c_0,C_0)\) --- \texttt{finite\_population\_class}; \(\mathbb R^{n2^n}\); \texttt{minimax\_model\_class} $:=$ \texttt{Bounded constant-direct-effect local-interference schedules with nondegenerate arc variances.}
  \item \(R_n^\star(M)\) --- \texttt{minimax\_inflation\_frontier}; \([1,\infty]\); \texttt{focal\_object} $:=$ Smallest worst-case expected variance-inflation ratio over \(\mathfrak R_n\).
  \item \(C_{\mathrm{up}}\) --- \texttt{upper\_bound\_constant}; \((0,\infty)\); \texttt{theorem\_constant} $:=$ Finite constant in the padded-block upper bound, depending only on \(c_0,C_0,\delta\).
  \item \(c\) --- \texttt{lower\_bound\_constant}; \((0,\infty)\); \texttt{open\_problem\_constant} $:=$ \texttt{Putative positive constant in the all-rule lower-bound question.}
  \item \(\mathsf H_{n,M}\) --- \texttt{converse\_handle}; \(\text{lower-bound programs}\); \texttt{open\_problem\_handle} $:=$ \texttt{Joint geometry and missing-information lower-bound program for an arbitrary recompute rule.}
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:radius-local-interference]\label{ass:radius-local-interference}
\(Y_i(w)=Y_i(w')\) whenever \(w_{\mathcal N_i}=w'_{\mathcal N_i}\).
\par\smallskip\noindent\emph{Standard} (known local-interference exposure condition, \cite{AronowSamii2017}).
\end{assumption}

\begin{assumption}[ass:constant-direct-effect]\label{ass:constant-direct-effect}
\(Y_i(1,w_{-i})-Y_i(0,w_{-i})=\tau\) for every \(i\in V_n\) and every \(w_{-i}\in\{0,1\}^{V_n\setminus\{i\}}\).
\par\smallskip\noindent\emph{Novel.} This is a constant own-treatment-effect restriction that permits unrestricted radius-\(M\) spillovers through the neighbor assignment. It models interventions whose direct effect is operationally stable while ambient local congestion or peer exposure changes the outcome level; the explicit local schedules displayed in Assumption \(\textnormal{ass:arc-variance-density}\) satisfy it.
\end{assumption}

\begin{assumption}[ass:bounded-schedule]\label{ass:bounded-schedule}
\(\max_{i\in V_n,w\in\{0,1\}^{V_n}}|Y_i(w)|\le C_0\).
\par\smallskip\noindent\emph{Standard} (uniform bounded potential-outcomes condition, \cite{LinDing2025TimeSeries}).
\end{assumption}

\begin{assumption}[ass:arc-variance-density]\label{ass:arc-variance-density}
\(c_0|I|\le\operatorname{Var}_W(\sum_{i\in I}\psi_i)\le C_0|I|\) for every \(I\in\mathcal A_{n,M}\).
\par\smallskip\noindent\emph{Novel.} This finite-population stability condition retains experimental settings with persistent assignment variation on every spatial or temporal segment. For \(M\ge1\), the explicit local family \(Y_i(w)=a+\eta(2w_{i+1}-1)+\tau(w_i-1/2)\), with \(4(a^2+\eta^2)\in[c_0,C_0]\) and \(|a|+|\eta|+1/4\le C_0\), obeys the condition because \(\operatorname{Var}_W(\sum_{i\in I}\psi_i)=4(a^2+\eta^2)|I|\). For \(M=0\), take \(\eta=0\).
\end{assumption}

\begin{assumption}[ass:growing-radius-regime]\label{ass:growing-radius-regime}
\(1\le M\le n^{1-\delta}\).
\par\smallskip\noindent\emph{Novel.} This sublinear-radius asymptotic regime represents spatial or switchback deployments whose spillover window grows with deployment length but remains smaller than the experimental horizon; for example, \(M=\lfloor n^\alpha\rfloor\) with \(0<\alpha<1\).
\end{assumption}

\begin{assumption}[ass:outcome-blind-update]\label{ass:outcome-blind-update}
\(S\sim\mu\) is independent of \(W\) and of the fixed schedule \(Y\).
\par\smallskip\noindent\emph{Standard} (assignment-independent update-set condition, \cite{ParkWager2026NeymanJackknife}).
\end{assumption}

\begin{assumption}[ass:positive-gibbs-gap]\label{ass:positive-gibbs-gap}
\(\lambda_\mu>0\).
\par\smallskip\noindent\emph{Standard} (positive spectral-gap condition, \cite{ParkWager2026NeymanJackknife}).
\end{assumption}

\section{Definitions}

\begin{definition}[def:cycle-neighborhoods]\label{def:cycle-neighborhoods}
\texttt{Cycle neighborhoods} $:=$ \(V_n=\mathbb Z/n\mathbb Z,\quad \mathcal N_i=\{j\in V_n:d_{\mathsf C_n}(i,j)\le M\},\quad \mathcal A_{n,M}=\{I\subseteq V_n:I\text{ is a cyclic arc and }|I|\ge2M+1\}\). \quad (\text{inputs: } \textbackslash{}(n\textbackslash{}), \textbackslash{}(M\textbackslash{}))
\end{definition}

\begin{definition}[def:schedule-class]\label{def:schedule-class}
\texttt{Regular local-interference schedules} $:=$ \(\mathcal Y_n(M;c_0,C_0)=\{Y\in\mathbb R^{n2^n}:Y\text{ satisfies Assumptions }\textnormal{ass:radius-local-interference},\textnormal{ ass:constant-direct-effect},\textnormal{ ass:bounded-schedule},\textnormal{ and ass:arc-variance-density for this }n\}\). --- the class of all objects satisfying: ass:radius-local-interference; ass:constant-direct-effect; ass:bounded-schedule; ass:arc-variance-density.
\end{definition}

\begin{definition}[def:ipw-score]\label{def:ipw-score}
\texttt{Direct-effect IPW score and estimator} $:=$ \(\psi_i=2(2W_i-1)Y_i(W),\qquad\widehat\tau=n^{-1}\sum_{i\in V_n}\psi_i\). \quad (\text{inputs: } \textbackslash{}(W\textbackslash{}), \textbackslash{}(Y\_i(w)\textbackslash{}), \textbackslash{}(n\textbackslash{}), \textbackslash{}(V\_n\textbackslash{}))
\end{definition}

\begin{definition}[def:deletion-set]\label{def:deletion-set}
\texttt{Proxy deletion set} $:=$ \(D(S)=\{i\in V_n:\mathcal N_i\cap S\ne\varnothing\}\). \quad (\text{inputs: } \textbackslash{}(S\textbackslash{}), \textbackslash{}(\textbackslash{}mathcal N\_i\textbackslash{}), \textbackslash{}(V\_n\textbackslash{}))
\end{definition}

\begin{definition}[def:rule-class]\label{def:rule-class}
\texttt{Outcome-blind recompute class} $:=$ \(\mathfrak R_n=\{(\mu,g):\mu\text{ satisfies Assumptions }\textnormal{ass:outcome-blind-update}\text{ and ass:positive-gibbs-gap};\ g: (S,W_{-S},\{Y_i(W):i\notin D(S)\})\mapsto\mathbb R\text{ is one fixed measurable map for every }Y\in\mathcal Y_n(M;c_0,C_0)\}\). --- the class of all objects satisfying: ass:outcome-blind-update; ass:positive-gibbs-gap.
\end{definition}

\begin{definition}[def:variance-estimator]\label{def:variance-estimator}
\texttt{Neyman-Jackknife recompute variance estimator} $:=$ \(\widehat V_{\mu,g}=\lambda_\mu^{-1}\,\mathbb E_{S\sim\mu}[(\widehat\tau-g(S,W_{-S},\{Y_i(W):i\notin D(S)\}))^2\mid W]\). \quad (\text{inputs: } \textbackslash{}(\textbackslash{}mu\textbackslash{}), \textbackslash{}(g\textbackslash{}), \textbackslash{}(\textbackslash{}lambda\_\textbackslash{}mu\textbackslash{}), \textbackslash{}(\textbackslash{}widehat\textbackslash{}tau\textbackslash{}), \textbackslash{}(D(S)\textbackslash{}))
\end{definition}

\begin{definition}[def:inflation-frontier]\label{def:inflation-frontier}
\texttt{Minimax excess-inflation frontier} $:=$ \(R_n^\star(M)=\inf_{(\mu,g)\in\mathfrak R_n}\sup_{Y\in\mathcal Y_n(M;c_0,C_0)}\frac{\mathbb E_W[\widehat V_{\mu,g}]}{\operatorname{Var}_W(\widehat\tau)}\). \quad (\text{inputs: } \textbackslash{}(\textbackslash{}mathfrak R\_n\textbackslash{}), \textbackslash{}(\textbackslash{}mathcal Y\_n(M;c\_0,C\_0)\textbackslash{}), \textbackslash{}(\textbackslash{}widehat V\_\{\textbackslash{}mu,g\}\textbackslash{}), \textbackslash{}(\textbackslash{}widehat\textbackslash{}tau\textbackslash{}))
\end{definition}

\begin{definition}[def:sutva-block-rule]\label{def:sutva-block-rule}
\texttt{No-interference uniform-block rule} $:=$ \(M=0,\quad S=\{s,\ldots,s+L-1\}\text{ for }s\sim\operatorname{Unif}(V_n),\quad \mu_L=\mathcal L(S),\quad D(S)=S,\quad g_L=\frac{1}{n-L}\sum_{i\notin S}\psi_i,\quad\lambda_{\mu_L}=L/n\). \quad (\text{inputs: } \textbackslash{}(L\textbackslash{}), \textbackslash{}(V\_n\textbackslash{}), \textbackslash{}(\textbackslash{}psi\_i\textbackslash{}))
\end{definition}

\begin{definition}[def:balanced-block-rule]\label{def:balanced-block-rule}
\texttt{Padded uniform-block rule} $:=$ \(L_\star=\lfloor\sqrt{Mn}\rfloor,\quad S=\{s,\ldots,s+L_\star-1\}\text{ for }s\sim\operatorname{Unif}(V_n),\quad\mu_{L_\star}=\mathcal L(S),\quad D(S)=\{i:d_{\mathsf C_n}(i,S)\le M\},\quad g_{L_\star}=\frac{1}{n-|D(S)|}\sum_{i\notin D(S)}\psi_i,\quad\lambda_{\mu_{L_\star}}=L_\star/n\). \quad (\text{inputs: } \textbackslash{}(M\textbackslash{}), \textbackslash{}(n\textbackslash{}), \textbackslash{}(\textbackslash{}psi\_i\textbackslash{}), \textbackslash{}(\textbackslash{}mathsf C\_n\textbackslash{}))
\end{definition}

\begin{definition}[def:converse-handle]\label{def:converse-handle}
\texttt{All-rule converse handle} $:=$ \(\mathsf H_{n,M}\) is the joint lower-bound program that maps an arbitrary \(\mu\) to its cycle-neighborhood deletion geometry and maps the hidden outcomes in \(D(S)\) to a nuisance-rich Le Cam modulus for the observable sigma-field \(\sigma(S,W_{-S},\{Y_i(W):i\notin D(S)\})\). \quad (\text{inputs: } \textbackslash{}(\textbackslash{}mu\textbackslash{}), \textbackslash{}(S\textbackslash{}), \textbackslash{}(D(S)\textbackslash{}), \textbackslash{}(g\textbackslash{}))
\end{definition}

\section{Main results}

\begin{proposition}[prop:sutva-calibration]\label{prop:sutva-calibration}
For every \(Y\in\mathcal Y_n(0;c_0,C_0)\) and \(L\in\{1,\ldots,n-1\}\), the pair \((\mu_L,g_L)\) in \(\textnormal{def:sutva-block-rule}\) belongs to \(\mathfrak R_n\) and satisfies \[\frac{\mathbb E_W[\widehat V_{\mu_L,g_L}]}{\operatorname{Var}_W(\widehat\tau)}=\frac{n}{n-L}.\] In particular, \(L=1\) yields the classical leave-one-out inflation \(n/(n-1)\).
\end{proposition}
\begin{proof}
Fix \(Y\in\mathcal Y_n(0;c_0,C_0)\) and \(L\in\{1,\ldots,n-1\}\). Because \(M=0\), one has \(\mathcal N_i=\{i\}\). Assumption \(\textnormal{ass:radius-local-interference}\), incorporated in \(\textnormal{def:schedule-class}\), therefore implies that \(Y_i(W)\) is a function of \(W_i\) alone. Write its two values as \(y_i(0)\) and \(y_i(1)\). Assumption \(\textnormal{ass:constant-direct-effect}\) gives \(y_i(1)-y_i(0)=\tau\). Under the Bernoulli\((1/2)\) design,
\[
\mathbb E_W[\psi_i]=\frac12\,2y_i(1)+\frac12\,(-2y_i(0))=y_i(1)-y_i(0)=\tau.
\]
Set \(X_i=\psi_i-\tau\), \(v_i=\operatorname{Var}_W(\psi_i)=\mathbb E_W[X_i^2]\), and \(V=\sum_{i\in V_n}v_i\). Each \(X_i\) is a function only of \(W_i\), so the family \(\{X_i:i\in V_n\}\) is independent and centered. Taking \(I=V_n\) in Assumption \(\textnormal{ass:arc-variance-density}\) yields
\[
V=\operatorname{Var}_W\!\left(\sum_{i\in V_n}\psi_i\right)\ge c_0n>0.
\]
Thus the ratio in the proposition has a strictly positive denominator.

We first verify membership in \(\mathfrak R_n\). The block origin is sampled independently of \(W\) and of the fixed schedule, so \(\mu_L\) satisfies Assumption \(\textnormal{ass:outcome-blind-update}\). To verify the asserted spectral gap, let \(P_L\) be the Markov operator that samples a uniform cyclic block \(S\) of length \(L\) and refreshes the coordinates in \(S\) from their Bernoulli\((1/2)\) law. For \(A\subseteq V_n\), define the Walsh character
\[
\chi_A(w)=\prod_{i\in A}(2w_i-1).
\]
The Walsh characters form an orthonormal basis under the product Bernoulli law. Conditional refreshment kills \(\chi_A\) if \(S\cap A\ne\varnothing\) and leaves it unchanged otherwise; hence
\[
P_L\chi_A=\mathbb P_S(S\cap A=\varnothing)\chi_A.
\]
For every nonempty \(A\), choose \(i\in A\). Exactly \(L\) of the \(n\) cyclic blocks contain \(i\), and consequently
\[
1-\mathbb P_S(S\cap A=\varnothing)=\mathbb P_S(S\cap A\ne\varnothing)\ge\frac Ln.
\]
Equality holds when \(A=\{i\}\). Since the displayed diagonalization covers the full orthonormal basis, the largest nonconstant eigenvalue of \(P_L\) is \(1-L/n\), and its spectral gap is exactly \(\lambda_{\mu_L}=L/n>0\). Finally, \(D(S)=S\) when \(M=0\), and
\[
g_L=\frac{1}{n-L}\sum_{i\notin S}\psi_i
\]
is a single measurable function of \(S\), \(W_{-S}\), and the observed outcomes \(\{Y_i(W):i\notin S\}\); in particular, the formula does not depend on the unknown schedule except through its observable inputs. Hence \((\mu_L,g_L)\in\mathfrak R_n\).

It remains to compute the expectation of the variance estimator. For a fixed block \(S\), put \(A_S=\sum_{i\in S}X_i\) and \(B_S=\sum_{i\notin S}X_i\). The common means cancel, and direct algebra gives
\[
\widehat\tau-g_L=\frac1n A_S-\frac{L}{n(n-L)}B_S.
\]
The two sums are independent and centered, so
\[
\mathbb E_W[(\widehat\tau-g_L)^2\mid S]=\frac1{n^2}\left(\sum_{i\in S}v_i+\frac{L^2}{(n-L)^2}\sum_{i\notin S}v_i\right).
\]
Every vertex belongs to exactly \(L\) of the \(n\) possible cyclic blocks. Therefore
\[
\mathbb E_S\!\left[\sum_{i\in S}v_i\right]=\frac LnV,\qquad \mathbb E_S\!\left[\sum_{i\notin S}v_i\right]=\frac{n-L}{n}V.
\]
Using \(\lambda_{\mu_L}=L/n\), the definition of \(\widehat V_{\mu_L,g_L}\), and interchange of the two finite expectations, we obtain
\[
\mathbb E_W[\widehat V_{\mu_L,g_L}]=\frac nL\frac1{n^2}\left(\frac LnV+\frac{L^2}{(n-L)^2}\frac{n-L}{n}V\right)=\frac{V}{n(n-L)}.
\]
Independence of the scores also gives
\[
\operatorname{Var}_W(\widehat\tau)=\frac1{n^2}\operatorname{Var}_W\!\left(\sum_{i\in V_n}\psi_i\right)=\frac{V}{n^2}.
\]
Since \(V>0\), division yields
\[
\frac{\mathbb E_W[\widehat V_{\mu_L,g_L}]}{\operatorname{Var}_W(\widehat\tau)}=\frac{n}{n-L}.
\]
Substitution of \(L=1\) gives \(n/(n-1)\), as claimed.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The arc-variance condition makes the denominator positive, and the exact no-interference identity calibrates the proxy-loss term against the classical jackknife. \textit{Gap.} Kunsch1989BlockJackknife and ParkWager2026NeymanJackknife provide the block-jackknife and recomputation precedents; the displayed ratio is retained solely as the required exact reduction for this frontier. \textit{Consumer.} It fixes the \(L/n\) boundary term used to assess the local-interference frontier.

\begin{theorem}[thm:block-upper]\label{thm:block-upper}
There is a constant \(C_{\mathrm{up}}<\infty\), depending only on \(c_0,C_0,\delta\), such that, for all sufficiently large \(n\) in Assumption \(\textnormal{ass:growing-radius-regime}\), the padded uniform-block rule in \(\textnormal{def:balanced-block-rule}\) belongs to \(\mathfrak R_n\) and satisfies \[\sup_{Y\in\mathcal Y_n(M;c_0,C_0)}\frac{\mathbb E_W[\widehat V_{\mu_{L_\star},g_{L_\star}}]}{\operatorname{Var}_W(\widehat\tau)}\le 1+C_{\mathrm{up}}\sqrt{M/n}.\]
\end{theorem}
\begin{proof}
Fix \(Y\in\mathcal Y_n(M;c_0,C_0)\), and put \(L=L_\star\), \(d=L+2M\), and \(b=n-d\). We first record consequences that hold uniformly over this schedule class. For fixed \(i\) and \(w_{-i}\), define \[m_i(w_{-i})=\frac{Y_i(1,w_{-i})+Y_i(0,w_{-i})}{2}.\] Assumption \(\textnormal{ass:constant-direct-effect}\), incorporated in \(\textnormal{def:schedule-class}\), gives \[Y_i(W)=m_i(W_{-i})+\frac{\tau}{2}(2W_i-1),\qquad \psi_i=\tau+2(2W_i-1)m_i(W_{-i}).\] By Assumption \(\textnormal{ass:radius-local-interference}\), the function \(m_i\) depends only on \(W_{\mathcal N_i\setminus\{i\}}\). Since the Bernoulli design makes \(W_i\) independent of those coordinates, \(\mathbb E_W[\psi_i]=\tau\). Set \[X_i=\psi_i-\tau,\qquad T=\sum_{i\in V_n}X_i,\qquad V=\operatorname{Var}_W(T).\] The full cycle is an admissible arc, so Assumption \(\textnormal{ass:arc-variance-density}\) yields \[c_0n\le V\le C_0n.\tag{1}\] In particular, \(\operatorname{Var}_W(\widehat\tau)=V/n^2>0\). Moreover, \(X_i\) is measurable with respect to \(W_{\mathcal N_i}\). Hence product Bernoulli assignment and disjointness of the neighborhoods imply \[\operatorname{Cov}_W(X_i,X_j)=0\quad\text{whenever }d_{\mathsf C_n}(i,j)>2M.\tag{2}\] We next verify that the padded block rule is admissible. Its block origin is uniform and independent of \(W\) and of the fixed schedule, so Assumption \(\textnormal{ass:outcome-blind-update}\) holds. Let \(P_L\) denote the Markov operator that chooses a uniform cyclic block \(S\) of length \(L\) and refreshes the coordinates in \(S\) independently from their Bernoulli\((1/2)\) law. For \(A\subseteq V_n\), let \[\chi_A(w)=\prod_{i\in A}(2w_i-1).\] The Walsh characters form an orthonormal basis for the product Bernoulli law, and conditional refreshment of \(S\) kills \(\chi_A\) if \(S\cap A\ne\varnothing\) and preserves it otherwise. Consequently, \[P_L\chi_A=\mathbb P_S(S\cap A=\varnothing)\chi_A.\] For every nonempty \(A\), choosing any \(i\in A\) shows that \(\mathbb P_S(S\cap A\ne\varnothing)\ge L/n\), because exactly \(L\) of the \(n\) cyclic blocks contain \(i\). Equality holds for \(A=\{i\}\). Thus the spectral gap is exactly \(\lambda_{\mu_{L_\star}}=L/n>0\). For all sufficiently large \(n\) under Assumption \(\textnormal{ass:growing-radius-regime}\), one has \(L+4M+1\le n\). It follows that \(D(S)\) is an arc of size \(d=L+2M\), its complement has size \(b>0\), and \[g_{L_\star}=\frac1b\sum_{i\notin D(S)}\psi_i\] is a fixed measurable function of the allowed inputs: if \(i\notin D(S)\), then \(\mathcal N_i\cap S=\varnothing\), so \(W_i\) is contained in \(W_{-S}\) and \(Y_i(W)\) is one of the supplied outcomes. The same formula serves every schedule in the class. Therefore \((\mu_{L_\star},g_{L_\star})\in\mathfrak R_n\). It remains to bound its inflation. We establish an averaged arc-variance identity that does not require translation invariance of the schedule. Write \[c_{ij}=\operatorname{Cov}_W(X_i,X_j),\qquad \rho_{ij}=d_{\mathsf C_n}(i,j),\qquad \beta=\frac1n\sum_{i\ne j}\rho_{ij}c_{ij}.\] For a cyclic arc \(I_s(k)=\{s,\ldots,s+k-1\}\), define \[\overline V_k=\frac1n\sum_{s\in V_n}\operatorname{Var}_W\!\left(\sum_{i\in I_s(k)}X_i\right).\] Suppose \(2M+1\le k\le n-2M\). A fixed vertex belongs to exactly \(k\) of the \(n\) arcs. For a distinct pair with \(\rho_{ij}\le2M\), exactly \(k-\rho_{ij}\) such arcs contain both vertices; pairs at distance greater than \(2M\) have zero covariance by \((2)\). Summing the covariance expansion over the block origin therefore gives the exact identity \[\overline V_k=\frac{k}{n}V-\beta.\tag{3}\] Take \(k_0=2M+1\). For all sufficiently large \(n\), \(k_0\le n-2M\), so \((3)\) applies. Assumption \(\textnormal{ass:arc-variance-density}\), first for the full cycle and then for every length-\(k_0\) arc, implies \[\frac Vn\in[c_0,C_0],\qquad \frac{\overline V_{k_0}}{k_0}\in[c_0,C_0].\] Together with \((3)\), these inclusions give the uniform boundary estimate \[|\beta|=k_0\left|\frac Vn-\frac{\overline V_{k_0}}{k_0}\right|\le (C_0-c_0)(2M+1)\le3C_0M.\tag{4}\] This is the step that controls arbitrary nonstationarity of the fixed potential-outcome schedule. For a block origin \(s\), write \(D_s=D(S)\) and set \[A_s=\sum_{i\in D_s}X_i,\qquad B_s=\sum_{i\notin D_s}X_i.\] Since both the full estimator and the complement average have mean \(\tau\), direct algebra yields \[\widehat\tau-g_{L_\star}=\frac1n\left(A_s-\frac db B_s\right).\tag{5}\] The sets \(D_s\) and \(V_n\setminus D_s\) range uniformly over arcs of lengths \(d\) and \(b\), respectively. Also, \(A_s+B_s=T\), whence \[\mathbb E_s[\operatorname{Cov}_W(A_s,B_s)]=\frac12\left(V-\overline V_d-\overline V_b\right).\tag{6}\] Our choice of sufficiently large \(n\) ensures that both \(d\) and \(b\) lie in \([2M+1,n-2M]\). Expanding the variance in \((5)\), using \((6)\), and then applying \((3)\) twice gives \[\begin{aligned}\mathbb E_s\!\left[\operatorname{Var}_W\!\left(A_s-\frac dbB_s\right)\right]&=\left(1+\frac db\right)\overline V_d+\left(\frac{d^2}{b^2}+\frac db\right)\overline V_b-\frac dbV\\&=\frac nb\,\overline V_d+\frac{dn}{b^2}\,\overline V_b-\frac dbV\\&=\frac dbV-\frac{n^2}{b^2}\beta.\end{aligned}\tag{7}\] Using \(\lambda_{\mu_{L_\star}}=L/n\), finite Fubini, \((5)\), and \((7)\), we obtain the exact ratio \[\frac{\mathbb E_W[\widehat V_{\mu_{L_\star},g_{L_\star}}]}{\operatorname{Var}_W(\widehat\tau)}=\frac nL\left(\frac db-\frac{n^2\beta}{b^2V}\right).\tag{8}\] Finally, let \(\varepsilon=\sqrt{M/n}\). Assumption \(\textnormal{ass:growing-radius-regime}\) gives \(\varepsilon\le n^{-\delta/2}\), so \(\varepsilon\to0\) uniformly over the stated regime. Since \(L=\lfloor\sqrt{Mn}\rfloor\), for all sufficiently large \(n\), \[L\ge\frac12\sqrt{Mn},\qquad \frac ML\le2\varepsilon,\qquad \frac dn=\frac Ln+2\frac Mn\le3\varepsilon,\qquad b\ge\frac n2.\tag{9}\] The first term on the right-hand side of \((8)\) consequently satisfies \[\frac{nd}{Lb}-1=\frac{2M/L+d/n}{1-d/n}\le14\varepsilon.\tag{10}\] By \((1)\), \((4)\), and \((9)\), the absolute value of the second term is at most \[\frac{n^3|\beta|}{Lb^2V}\le\frac{4|\beta|}{c_0L}\le\frac{12C_0M}{c_0L}\le\frac{24C_0}{c_0}\varepsilon.\tag{11}\] Combining \((8)\)--\((11)\) proves, uniformly over \(Y\in\mathcal Y_n(M;c_0,C_0)\), \[\frac{\mathbb E_W[\widehat V_{\mu_{L_\star},g_{L_\star}}]}{\operatorname{Var}_W(\widehat\tau)}\le1+\left(14+\frac{24C_0}{c_0}\right)\sqrt{M/n}.\] Thus one may take \(C_{\mathrm{up}}=14+24C_0/c_0\). The threshold for \(n\) depends only on \(\delta\) (and the displayed constant depends only on \(c_0,C_0\)), as required.
\end{proof}
\par\smallskip\noindent \textit{Justification.} It turns the displayed oracle-versus-proxy tradeoff into a uniform finite-population upper bound at the balanced scale. \textit{Gap.} ParkWager2026NeymanJackknife derives the fixed-block estimator and its scaled Newey--West form, while its cycle evidence tunes \(L\) numerically and does not give a schedule-uniform \(\sqrt{M/n}\) inflation theorem. \textit{Consumer.} It supplies a non-oracle, exposure-free tuning rule for randomized spatial and switchback experiments with a known interference radius.

\begin{lemma}[lem:recompute-poincare-floor]\label{lem:recompute-poincare-floor}
For every \(Y\in\mathcal Y_n(M;c_0,C_0)\) and every \((\mu,g)\in\mathfrak R_n\),\[\mathbb E_W[\widehat V_{\mu,g}]\ge\operatorname{Var}_W(\widehat\tau).\]In particular, whenever \(\operatorname{Var}_W(\widehat\tau)>0\), the corresponding inflation ratio is at least \(1\).
\end{lemma}
\begin{proof}
Fix the schedule \(Y\) and write \(f(W)=\widehat\tau(W)\). For a realized update set \(S\), every reported outcome \(Y_i(W)\) with \(i\notin D(S)\) is a function of \(W_{-S}\): indeed, \(i\notin D(S)\) means \(\mathcal N_i\cap S=\varnothing\), and Assumption \(\textnormal{ass:radius-local-interference}\) makes \(Y_i(W)\) depend only on \(W_{\mathcal N_i}\). Therefore the random variable produced by the fixed proxy map is measurable with respect to \(\sigma(S,W_{-S})\) once \(Y\) is fixed.

Let \(W'\) be obtained by drawing \(S\sim\mu\) and replacing \(W_S\) by an independent Bernoulli half-assignment, leaving \(W_{-S}\) unchanged. The Dirichlet form of this heat-bath kernel is\[\mathcal E_\mu(f,f)=\frac12\mathbb E[(f(W)-f(W'))^2]=\mathbb E_{S\sim\mu}\mathbb E_W[\operatorname{Var}_W(f(W)\mid W_{-S})].\]Because \(\lambda_\mu\) is the spectral gap, its defining Poincare inequality is\[\mathcal E_\mu(f,f)\ge\lambda_\mu\operatorname{Var}_W(f).\]For each \(S\), conditional expectation is the least-squares projection onto the \(W_{-S}\)-measurable functions. Hence, writing \(g_S\) for the proxy evaluated at the allowed data, the elementary orthogonal decomposition gives\[\mathbb E_W[(f-g_S)^2]\ge\mathbb E_W[(f-\mathbb E_W[f\mid W_{-S}])^2]=\mathbb E_W[\operatorname{Var}_W(f\mid W_{-S})].\]Average over \(S\), divide by \(\lambda_\mu>0\), and use the definition of \(\widehat V_{\mu,g}\) to obtain\[\mathbb E_W[\widehat V_{\mu,g}]=\lambda_\mu^{-1}\mathbb E_{S,W}[(f-g_S)^2]\ge\lambda_\mu^{-1}\mathcal E_\mu(f,f)\ge\operatorname{Var}_W(f).\]This is the claimed floor.
\end{proof}

\begin{lemma}[lem:boundary-class-zero-direct-effect]\label{lem:boundary-class-zero-direct-effect}
Suppose \(c_0=C_0=1/4\) and \(1\le M\le\lfloor n/4\rfloor\). Then every \(Y\in\mathcal Y_n(M;1/4,1/4)\) has constant direct effect \(\tau=0\).
\end{lemma}
\begin{proof}
Put \(\epsilon_i=2W_i-1\). For each \(i\), define\[m_i(W_{-i})=\frac{Y_i(1,W_{-i})+Y_i(0,W_{-i})}{2}.\]Assumption \(\textnormal{ass:constant-direct-effect}\) gives\[Y_i(W)=m_i(W_{-i})+\frac{\tau}{2}\epsilon_i,\qquad \psi_i=2\epsilon_i m_i(W_{-i})+\tau.\]Since \(W_i\) is independent of \(W_{-i}\) and \(\mathbb E_W[\epsilon_i]=0\), it follows that \(\mathbb E_W[\psi_i]=\tau\). Assumption \(\textnormal{ass:bounded-schedule}\), with \(C_0=1/4\), also gives \(|\psi_i|=2|Y_i(W)|\le1/2\). Consequently,\[\operatorname{Var}_W(\psi_i)=\mathbb E_W[\psi_i^2]-\tau^2\le\frac14-\tau^2.\tag{1}\]

Let \(F=\sum_{i\in V_n}\psi_i\). Both \(V_n\) and \(V_n\setminus\{j\}\) are cyclic arcs. The latter has length \(n-1\ge2M+1\) because \(1\le M\le\lfloor n/4\rfloor\). When \(c_0=C_0=1/4\), the lower and upper sides of Assumption \(\textnormal{ass:arc-variance-density}\) coincide. Thus, for every \(j\in V_n\),\[\operatorname{Var}_W(F)=\frac n4,\qquad \operatorname{Var}_W(F-\psi_j)=\frac{n-1}{4}.\]Subtracting the two identities and summing over \(j\) yields\[\frac n4=\sum_{j\in V_n}\left\{2\operatorname{Cov}_W(F,\psi_j)-\operatorname{Var}_W(\psi_j)\right\}=2\operatorname{Var}_W(F)-\sum_{j\in V_n}\operatorname{Var}_W(\psi_j).\]Using \(\operatorname{Var}_W(F)=n/4\), we obtain\[\sum_{j\in V_n}\operatorname{Var}_W(\psi_j)=\frac n4.\tag{2}\]On the other hand, summing inequality \((1)\) gives\[\sum_{j\in V_n}\operatorname{Var}_W(\psi_j)\le\frac n4-n\tau^2.\tag{3}\]Equations \((2)\) and \((3)\) imply \(n\tau^2\le0\), and hence \(\tau=0\).
\end{proof}

\begin{theorem}[thm:boundary-collapse-of-all-rule-frontier]\label{thm:boundary-collapse-of-all-rule-frontier}
The answer to the all-rule converse question is negative under the frozen parameter domain. In the admissible boundary case \(c_0=C_0=1/4\), for every \(n\) and \(M\) satisfying \(1\le M\le\lfloor n/4\rfloor\), one has \[R_n^\star(M)=1.\] Consequently, for these class constants there is no \(c=c(c_0,C_0,\delta)>0\) such that \(R_n^\star(M)\ge 1+c\sqrt{M/n}\) throughout Assumption \(\textnormal{ass:growing-radius-regime}\).
\end{theorem}
\begin{proof}
Fix \(c_0=C_0=1/4\), \(1\le M\le\lfloor n/4\rfloor\), and choose any \(\varepsilon\in(0,1]\). Define the update law\[\mu_\varepsilon=(1-\varepsilon)\delta_{\varnothing}+\varepsilon\delta_{V_n}.\]It is independent of the assignment and the fixed schedule. Its Gibbs operator is\[K_{\mu_\varepsilon}f=(1-\varepsilon)f+\varepsilon\mathbb E_W[f].\]Thus every mean-zero function is an eigenfunction with eigenvalue \(1-\varepsilon\), and the Gibbs spectral gap is exactly \(\lambda_{\mu_\varepsilon}=\varepsilon>0\). Define one schedule-uniform measurable proxy by\[g_\varepsilon(S,W_{-S},\{Y_i(W):i\notin D(S)\})=\begin{cases}n^{-1}\sum_{i\in V_n}2(2W_i-1)Y_i(W),&S=\varnothing,\\0,&S\ne\varnothing.\end{cases}\]When \(S=\varnothing\), one has \(D(S)=\varnothing\), so all quantities in the first branch are among the allowed inputs. The second branch is constant. Hence \(g_\varepsilon\) is a single admissible map for the entire schedule class, and \((\mu_\varepsilon,g_\varepsilon)\in\mathfrak R_n\).

By Lemma \(\textnormal{lem:boundary-class-zero-direct-effect}\), every \(Y\in\mathcal Y_n(M;1/4,1/4)\) has \(\tau=0\). For the rule just constructed, conditional on \(W\),\[\mathbb E_{S\sim\mu_\varepsilon}[(\widehat\tau-g_\varepsilon)^2\mid W]=(1-\varepsilon)\cdot0+\varepsilon\widehat\tau^2.\]The definition of the recompute estimator and \(\lambda_{\mu_\varepsilon}=\varepsilon\) therefore give the pointwise identity \(\widehat V_{\mu_\varepsilon,g_\varepsilon}=\widehat\tau^2\). Moreover, \(\mathbb E_W[\widehat\tau]=\tau=0\), while the full-cycle arc condition gives\[\operatorname{Var}_W(\widehat\tau)=n^{-2}\operatorname{Var}_W\!\left(\sum_{i\in V_n}\psi_i\right)=\frac{1}{4n}>0.\]It follows that, for every schedule in the class,\[\frac{\mathbb E_W[\widehat V_{\mu_\varepsilon,g_\varepsilon}]}{\operatorname{Var}_W(\widehat\tau)}=\frac{\mathbb E_W[\widehat\tau^2]}{\operatorname{Var}_W(\widehat\tau)}=1.\]Thus the displayed rule yields \(R_n^\star(M)\le1\). Lemma \(\textnormal{lem:recompute-poincare-floor}\) gives the reverse inequality for every admissible rule, so \(R_n^\star(M)=1\). Since \(M\ge1\) makes \(\sqrt{M/n}>0\), no strictly positive constant \(c(1/4,1/4,\delta)\) can satisfy the proposed lower bound.
\end{proof}

\section*{Technical internal limitation (diagnostic only)}

The all-rule lower bound fails because the constant-effect and exact boundary-variance restrictions force \(\tau=0\), while an admissible empty/full multiscale update law separates spectral gap from deletion cost and lets a schedule-uniform proxy attain the Poincar\'e floor.

\section{Honest scope}

The sound subsidiary results are the exact \(M=0\) block calibration, the uniform \(1+O(\sqrt{M/n})\) padded-block upper bound, and the universal Poincar\'e floor. The boundary-collapse theorem refutes the proposed positive all-rule excess lower bound on an admissible part of the frozen domain, so the matched field-level kernel does not survive.

\begin{thebibliography}{99}

  \bibitem{ParkWager2026NeymanJackknife} Park, B. and Wager, S. (2026). Neyman Jackknife: Design-Based Variance Estimation for Causal Inference under Interference. arXiv:2604.24017.

  \bibitem{HarshawMiddletonSavje2026OptimizedVariance} Harshaw, C., Middleton, J. A., and S\textbackslash{}u00e4vje, F. (2026). Optimized Variance Estimation under Interference and Complex Experimental Designs. Journal of the American Statistical Association.

  \bibitem{LinDing2025TimeSeries} Lin, Z. and Ding, P. (2025). Unifying Regression-Based and Design-Based Causal Inference in Time-Series Experiments. arXiv:2510.22864.

  \bibitem{GaoDing2025NetworkRegression} Gao, M. and Ding, P. (2025). Causal Inference in Network Experiments: Regression-Based Analysis and Design-Based Properties. Journal of Econometrics 252, 106119.

  \bibitem{PolyanskiyWu2026DualLeCam} Polyanskiy, Y. and Wu, Y. (2026). Dualizing Le Cam's Method for Functional Estimation I: General Theory. Annals of Statistics.

  \bibitem{Kunsch1989BlockJackknife} K\textbackslash{}u00fcnsch, H. R. (1989). The Jackknife and the Bootstrap for General Stationary Observations. Annals of Statistics 17, 1217--1241.

  \bibitem{AronowSamii2017} Aronow, P. M. and Samii, C. (2017). Estimating Average Causal Effects under General Interference, with Application to a Social Network Experiment. Annals of Applied Statistics 11, 1912--1947.

\end{thebibliography}

\end{document}
