\begin{proof}[Proof of \cref{obj:thm:generic-arrow-recovery-and-fiber-obstruction}]
Fix \(m\ge 1\) and put \(K=2m+2\).

\begin{enumerate}
\item \cref{obj:thm:generic-apolar-arrow-recovery} gives loci
\(U^{\mathrm{right}}_m\) and \(U^{\mathrm{left}}_m\), each contained in the corresponding generic locus of \cref{obj:def:generic-parameter-loci}, and supplies their relative Zariski openness, relative Zariski density, and the asserted real-incidence open sets.  For each forward point it also supplies an empty opposite-arrow fiber, a support-annihilator kernel identity for the divided-power forms \(f_r\), and a nonzero univariate polynomial whose roots are exactly the multiset
\(\{\gamma,\rho_1,\ldots,\rho_m\}\) and whose value at \(0\) is nonzero.  The reverse statement is supplied with the same data after interchanging the two arrows.

\item Let \(\theta=(\gamma,\rho,c)\in U^{\mathrm{right}}_m\).  If
\(\theta'\in R^{\mathrm{right}}_{m,K}(\Phi^{\mathrm{right}}_{m,K}(\theta))\), then the definition of the fiber gives equality of all cumulant coordinates in the active range \(2\le r\le K\), \(a\le r\); outside this range both polynomial maps are zero by definition, so
\[
\Phi^{\mathrm{right}}_{m,K}(\theta')
=
\Phi^{\mathrm{right}}_{m,K}(\theta).
\]
The support-annihilator of the loading directions of \(\theta'\) lies in the same contraction kernel.  By the kernel identity furnished in Step 1, it is a nonzero scalar multiple of the support-annihilator of \(\theta\).  Dehomogenizing along the forward finite-slope chart therefore gives the same root multiset, hence
\[
\{\gamma',\rho'_1,\ldots,\rho'_m\}
=
\{\gamma,\rho_1,\ldots,\rho_m\}.
\]
Thus every forward point in the forward fiber has the same unordered loading-slope multiset as \(\theta\).

\item The opposite-arrow conclusion for this \(\theta\) is exactly the empty reverse-fiber conclusion supplied in Step 1:
\[
R^{\mathrm{left}}_{m,K}(\Phi^{\mathrm{right}}_{m,K}(\theta))=\varnothing .
\]
Moreover, because the polynomial from Step 1 has roots \(\{\gamma,\rho_1,\ldots,\rho_m\}\) and is nonzero at \(0\), none of the latent slopes \(\rho_i\) is zero.

\item Fix \(i\in\{1,\ldots,m\}\), and define \(\theta'\) by swapping the full direct-source pair \((\gamma,(c_{0r})_{r=2}^K)\) with the full \(i\)-th latent pair \((\rho_i,(c_{ir})_{r=2}^K)\), leaving every other coordinate fixed.  Since \(\theta\) is generic and \(\rho_i\ne0\), the swapped parameter remains in \(\Theta^{\mathrm{right},\circ}_{m,K}\).

\item This \(\theta'\) is, by construction, the forward direct-latent swap required in the statement.

\item The forward cumulant map is unchanged under this full-pair swap: the defining source sum is merely reindexed by the transposition of the direct source label and the \(i\)-th latent source label.  Hence
\[
\Phi^{\mathrm{right}}_{m,K}(\theta')
=
\Phi^{\mathrm{right}}_{m,K}(\theta).
\]


\item The swapped parameter is not in the admissible \(G_m\)-orbit of \(\theta\).  Indeed, admissible relabelings only permute the middle latent source labels and keep the direct coordinate fixed, whereas the constructed swap changes the direct coordinate from \(\gamma\) to \(\rho_i\); genericity gives \(\gamma\ne\rho_i\).

\item If \(m\ge2\), apply the same-arrow fiber dimension statement to the generic point \(\theta\), using the multiset recovery proved in Step 2.  Once the loading multiset is recovered, the fiber is controlled by fixed-loading weight fibers; their independent low-order kernels have total dimension
\[
\sum_{r=2}^{m}(m+1-r)=\frac{m(m-1)}2,
\]
and every irreducible chain in the full fiber is contained in one of these fixed-loading components.  Therefore the forward fiber has exact relative Zariski dimension \(\frac{m(m-1)}2\).

\item Now let \(\eta=(\delta,\sigma,d)\in U^{\mathrm{left}}_m\).  If
\(\eta'\in R^{\mathrm{left}}_{m,K}(\Phi^{\mathrm{left}}_{m,K}(\eta))\), the same fiber-coordinate bookkeeping gives
\[
\Phi^{\mathrm{left}}_{m,K}(\eta')
=
\Phi^{\mathrm{left}}_{m,K}(\eta).
\]
The reverse support-annihilator of \(\eta'\) is then in the common reverse contraction kernel, hence is a nonzero scalar multiple of the reverse support-annihilator of \(\eta\).  Dehomogenizing in the reverse finite-slope chart gives
\[
\{\delta',\sigma'_1,\ldots,\sigma'_m\}
=
\{\delta,\sigma_1,\ldots,\sigma_m\}.
\]


\item The opposite-arrow conclusion for this \(\eta\) is the empty forward-fiber conclusion supplied in Step 1:
\[
R^{\mathrm{right}}_{m,K}(\Phi^{\mathrm{left}}_{m,K}(\eta))=\varnothing .
\]
The same root-polynomial argument also gives \(\sigma_i\ne0\) for every latent index \(i\).

\item For each \(i\), define \(\eta'\) by swapping the full reverse direct-source pair
\((\delta,(d_{m+1,r})_{r=2}^K)\) with the full \(i\)-th latent pair
\((\sigma_i,(d_{ir})_{r=2}^K)\), leaving all other coordinates fixed.  Since \(\eta\) is generic and \(\sigma_i\ne0\), this swapped point remains in
\(\Theta^{\mathrm{left},\circ}_{m,K}\).

\item This \(\eta'\) is, by construction, the reverse direct-latent swap required in the statement.

\item The reverse cumulant map is unchanged by the swap, again because the source sum is only reindexed by the corresponding transposition.  Thus
\[
\Phi^{\mathrm{left}}_{m,K}(\eta')
=
\Phi^{\mathrm{left}}_{m,K}(\eta).
\]


\item The swapped reverse parameter is not in the admissible \(G_m\)-orbit of \(\eta\): admissible relabelings keep the reverse direct coordinate fixed, while the constructed swap changes it from \(\delta\) to \(\sigma_i\), and genericity gives \(\delta\ne\sigma_i\).

\item Finally, if \(m\ge2\), the reverse same-arrow fiber dimension statement applied with the recovered multiset from Step 9 gives exact relative Zariski dimension
\[
\frac{m(m-1)}2
\]
for
\(R^{\mathrm{left}}_{m,K}(\Phi^{\mathrm{left}}_{m,K}(\eta))\).
\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:exceptional-locus-codimension-one}]
Fix \(m\ge 1\) and set \(K=2m+2\).  Let
\[
D_m:=\frac{3(m+2)^2+(m+2)}{2}-5 .
\]
\begin{enumerate}
\item The geometric argument works in the affine space of the retained cumulants, those of orders \(2,\ldots,K\). In that space, the closure of the common-axis image is a proper irreducible component of \(\overline E_m\) and has dimension one less than each arrow image variety of \cref{obj:def:image-varieties}. The codimension claim follows from this dimension comparison and irreducibility. The preimage and low-dimensional claims then follow by unpacking \cref{obj:def:generic-full-fiber-compatibility}.

\item For the common-axis image, evaluate a \(D_m\times D_m\) Jacobian minor at an explicit common-axis parameter point. The matrix is block upper triangular: the ordinary-order block is Vandermonde-type, the top-order block is an augmented confluent block, and the lower-left block vanishes because cumulants of different orders have separate source-weight coordinates. Both diagonal determinants are nonzero. The Jacobian lower bound and the matching transcendence-degree upper bound therefore give dimension \(D_m\) for the common-axis image.

\item For the full forward arrow image, evaluate the analogous \((D_m+1)\times(D_m+1)\) Jacobian minor at an explicit forward parameter point. The same order separation makes the matrix block upper triangular, and both diagonal blocks have nonzero determinant. Hence the forward polynomial image has dimension at least \(D_m+1\); the coordinate-algebra upper bound gives equality.

\item Let \(C\) be the common-axis image closure in the retained cumulant coordinates, and let \(X^{\mathrm{right}}\) be the forward arrow image variety in the same coordinates. The inclusions \(C\subseteq \overline E_m\subseteq X^{\mathrm{right}}\) hold by construction. They are proper because a horizontal contraction polynomial vanishes on the reverse image but is nonzero at an explicit forward parameter point. Since \(X^{\mathrm{right}}\) is irreducible and the preceding dimensions are \(D_m\) and \(D_m+1\), no irreducible closed set can lie strictly between \(C\) and \(X^{\mathrm{right}}\). Exchanging the coordinates gives the same conclusion for the reverse image.

\item Projection to the retained cumulant coordinates is injective on the truncated objects under consideration, so the dimension comparison transfers to the ambient cumulant space. The forward and reverse arrow image varieties are irreducible polynomial-image closures, and \(\overline E_m\) is contained in both. On the common-axis component, the horizontal or vertical contraction polynomial defines a principal component and rules out an intermediate irreducible set between that component and the corresponding arrow variety. Thus \(\overline E_m\) has codimension exactly \(1\) in both \(C^{\mathrm{right}}_{m,K}\) and \(C^{\mathrm{left}}_{m,K}\).

\item If \(m\ge 2\), exact codimension \(1\) excludes exact codimension \(m\): a longer irreducible chain would contain an intermediate closed set between the common-axis component and the ambient arrow variety, contradicting the preceding conclusion.

\item For the forward preimage, \cref{obj:def:generic-full-fiber-compatibility} identifies \(H^{\mathrm{right}}_m\) with the parameters whose forward image lies in the generic full-fiber compatibility locus.  Unpacking this definition, and using \cref{obj:def:generic-parameter-loci} and \cref{obj:def:fiber-correspondences}, gives exactly
\[
\theta\in H^{\mathrm{right}}_m
\quad\Longleftrightarrow\quad
\theta\in\Theta^{\mathrm{right},\circ}_{m,K}
\ \text{and}\
R^{\mathrm{left}}_{m,K}\!\left(\Phi^{\mathrm{right}}_{m,K}(\theta)\right)\neq\varnothing .
\]
Coordinates outside orders \(2,\ldots,K\) vanish under the truncation convention.

\item The reverse preimage is identical with the two arrows interchanged.  Thus \cref{obj:def:generic-full-fiber-compatibility}, \cref{obj:def:generic-parameter-loci}, and \cref{obj:def:fiber-correspondences} give
\[
\eta\in H^{\mathrm{left}}_m
\quad\Longleftrightarrow\quad
\eta\in\Theta^{\mathrm{left},\circ}_{m,K}
\ \text{and}\
R^{\mathrm{right}}_{m,K}\!\left(\Phi^{\mathrm{left}}_{m,K}(\eta)\right)\neq\varnothing .
\]

\item Finally, for \(m=1\) and \(m=2\), the worked systems of \cref{obj:def:worked-compatibility-instances} are exactly the retained-coordinate incidence descriptions of the generic compatibility locus. A point of \(E_m\) supplies forward and reverse parameters with equal retained cumulants and hence a solution of \(A_m\). Conversely, a solution \(p=(p^{\mathrm{right}},p^{\mathrm{left}})\) supplies parameters in the two fibers with the required generic side. Coordinates beyond the truncation order vanish by convention. Taking \(m=1\) and \(m=2\) gives the displayed formulas with \(A_1\) and \(A_2\).
\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:improved-real-information-order}]
Fix \(m\ge 3\), and put \(L=2m+1\).

\begin{enumerate}
\item The separation input at this order is obtained by the lower-order apolar
calculation.  On the forward parameter space, let
\[
\Delta^{\mathrm{right}}_m
  =
  \Bigl(\prod_{i=1}^{m}\rho_i\Bigr)\cdot
  \bigl(\text{the forward lower-order contraction-rank determinant}\bigr),
\]
and on the reverse parameter space let
\[
\Delta^{\mathrm{left}}_m
  =
  \Bigl(\prod_{i=1}^{m}\sigma_i\Bigr)\cdot
  \bigl(\text{the reverse lower-order contraction-rank determinant}\bigr).
\]
Evaluation at explicit parameter points shows that both determinant factors are
nonzero polynomials; hence \(\Delta^{\mathrm{right}}_m\) and
\(\Delta^{\mathrm{left}}_m\) are nonzero real polynomials.  Define
\[
E^{\mathrm{right}}
  :=\{\theta:\Delta^{\mathrm{right}}_m(\theta)=0\},
\qquad
E^{\mathrm{left}}
  :=\{\eta:\Delta^{\mathrm{left}}_m(\eta)=0\}.
\]
Thus both sets are proper real algebraic subsets of their respective real
parameter spaces.  The truncated-moment interior fact at order \(L\), together
with these explicit nonvanishing evaluations, gives feasible real points outside each
zero locus:
\[
F^{\mathrm{right}}_{m,L}\setminus E^{\mathrm{right}}\ne\varnothing,
\qquad
F^{\mathrm{left}}_{m,L}\setminus E^{\mathrm{left}}\ne\varnothing .
\]


\item Let \(\theta\in F^{\mathrm{right}}_{m,L}\setminus E^{\mathrm{right}}\).
After viewing \(\theta\) as a complex parameter, the nonvanishing of
\(\Delta^{\mathrm{right}}_m(\theta)\) gives all \(\rho_i\ne0\) and
nonvanishing of the forward contraction-rank determinant.  Feasibility gives
\(\gamma\ne0\) and the required distinctness of the forward loading slopes, so
the forward loading directions used in the lower-order apolar blocks are
injectively indexed and, together with the nonzero \(\rho_i\)'s, have the needed
nonzero second coordinates.  The determinant condition gives injectivity of the
associated lower-order weighted contraction map.  Suppose, toward a
contradiction, that some \(\eta\in F^{\mathrm{left}}_{m,L}\) satisfies
\[
\Phi^{\mathrm{right}}_{m,L}(\theta)
 =
\Phi^{\mathrm{left}}_{m,L}(\eta).
\]
The equality remains true after complexification, since the cumulant maps of
\cref{obj:def:forward-cumulant-map} and
\cref{obj:def:reverse-cumulant-map} have real polynomial coordinates.


\item Let \(Q_{\mathrm{left}}\) be the degree-\(m+2\) support-annihilator
polynomial of the reverse loading directions, and let \(Q_{\mathrm{right}}\) be
the corresponding support-annihilator polynomial of the forward loading
directions, in the notation of \cref{obj:def:apolar-notation}.
The polynomial \(Q_{\mathrm{left}}\) annihilates the reverse divided-power
cumulant blocks in orders \(m+2,\ldots,2m+1\); by the assumed equality of
cumulants, it also annihilates the corresponding forward blocks.  The forward
lower-order apolar kernel identity, applied with the slope and rank conditions
from the previous step, therefore yields a scalar \(c\) such that
\[
Q_{\mathrm{left}}=c\,Q_{\mathrm{right}}.
\]
But every reverse support annihilator is divisible by the horizontal-axis
factor, whereas the forward support annihilator is not divisible by that factor
when \(\gamma\ne0\) and all \(\rho_i\ne0\).  If \(c=0\), then
\(Q_{\mathrm{left}}=0\), contradicting nonzero support annihilation.  If
\(c\ne0\), divisibility transfers from \(Q_{\mathrm{left}}\) to
\(Q_{\mathrm{right}}\), again a contradiction.  Hence no such reverse
\(\eta\) exists.


\item The reverse argument is identical with the roles interchanged.  For
\(\eta\in F^{\mathrm{left}}_{m,L}\setminus E^{\mathrm{left}}\), the
nonvanishing of \(\Delta^{\mathrm{left}}_m(\eta)\) gives all
\(\sigma_i\ne0\) and nonvanishing of the reverse contraction-rank determinant.
Feasibility gives \(\delta\ne0\) and injectivity of the relevant reverse loading
slopes; together with the nonzero \(\sigma_i\)'s this gives the needed nonzero
first coordinates.  The determinant condition gives injectivity of the reverse
lower-order weighted contraction map.  If
\[
\Phi^{\mathrm{left}}_{m,L}(\eta)
 =
\Phi^{\mathrm{right}}_{m,L}(\theta)
\]
for some \(\theta\in F^{\mathrm{right}}_{m,L}\), then the forward support
annihilator annihilates the reverse lower-order blocks and must be a scalar
multiple of the reverse support annihilator.  The forward support annihilator is
divisible by the vertical-axis factor, while the reverse one is not divisible by
that factor under \(\delta\ne0\) and all \(\sigma_i\ne0\).  The same scalar
case split gives a contradiction.  Thus no such forward \(\theta\) exists.


\item The preceding four steps prove generic real separation at order
\(L=2m+1\), with the theorem-local exceptional sets
\(E^{\mathrm{right}}\) and \(E^{\mathrm{left}}\).  Since \(m\ge3\), also
\(2\le 2m+1\).  Therefore \(2m+1\) is an admissible element in the set whose
infimum defines \(K^\star(m)\) in \cref{obj:def:information-order},
and hence
\[
K^\star(m)\le 2m+1 .
\]


\item Finally, if \(K^\star(m)=2m+2\), the just-proved inequality would give
\(2m+2\le 2m+1\) after comparing the corresponding finite elements of
\(\mathbb N_\infty\), which is impossible.  Hence
\[
K^\star(m)\ne 2m+2 .
\]

\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:generic-apolar-arrow-recovery}]
Put \(K=2m+2\) and \(n=m+2\).  We argue in nine steps.

\begin{enumerate}
\item The truncated Hamburger moment interior theorem gives, at order \(K\), a nonempty Euclidean open set of admissible centered non-Gaussian one-dimensional source cumulant vectors, realized by laws with finite \(K\)-th moment.  This is the real feasibility input used below to make prescribed nonvanishing polynomial conditions hold inside the feasible region of \cref{obj:def:real-feasible-regions}.%


\item On the forward side, choose a nonzero determinant polynomial \(M_{\mathrm r}\) whose nonvanishing makes the forward weighted contraction map injective; on the reverse side choose the analogous nonzero determinant polynomial \(M_{\mathrm l}\).  In each case the determinant is nonzero at an explicit parameter whose source-cumulant coordinates vanish outside the orders \(2,\ldots,K\), so the same determinant remains nonzero after restricting to the truncated coordinate chart.%


\item Let \(\Delta_{\mathrm{gen}}\) be the polynomial cutting out the complement of the generic locus of \cref{obj:def:generic-parameter-loci}: it is the product of the direct slope, all direct-versus-latent slope differences, all latent slope differences, and all retained source-cumulant coordinates.  Let
\[
\Delta_\rho=\prod_{i=1}^m \rho_i
\]
in the forward chart, and use the identical product in the reverse chart with the reverse finite slopes.  Define
\[
R_{\mathrm r}:=\Delta_{\mathrm{gen}}\Delta_\rho M_{\mathrm r},
\qquad
R_{\mathrm l}:=\Delta_{\mathrm{gen}}\Delta_\rho M_{\mathrm l}.
\]
The preceding step and the explicit nonzero factors show that both \(R_{\mathrm r}\) and \(R_{\mathrm l}\) are nonzero on the retained-coordinate parameter spaces.%


\item Define \(U_m^{\mathrm{right}}\) to be the truncated forward parameter space cut by \(R_{\mathrm r}\ne0\), and \(U_m^{\mathrm{left}}\) to be the truncated reverse parameter space cut by \(R_{\mathrm l}\ne0\).  A principal nonvanishing locus whose truncated restriction is not the zero polynomial is relatively Zariski open and relatively Zariski dense.  Since \(R_{\mathrm r}\) and \(R_{\mathrm l}\) contain \(\Delta_{\mathrm{gen}}\), these loci are contained in the corresponding generic parameter loci; since they contain \(\Delta_\rho\), all finite latent slopes are nonzero on them; and since they contain the determinant factors, the corresponding weighted contraction maps are injective.%


\item Set
\[
O^{\mathrm{right}}=\{\theta\in\Theta^{\mathrm{right}}_{m,K}(\mathbb R):
R_{\mathrm r}(\theta_{\mathbb C})\ne0\},
\qquad
O^{\mathrm{left}}=\{\eta\in\Theta^{\mathrm{left}}_{m,K}(\mathbb R):
R_{\mathrm l}(\eta_{\mathbb C})\ne0\}.
\]
These are Euclidean open by continuity.  Applying the moment-interior nonvanishing statement to \(R_{\mathrm r}\) and \(R_{\mathrm l}\) gives feasible real points in each open set.  If a feasible real parameter lies in the appropriate open set, then its coordinatewise complexification satisfies the truncated support equations and the same nonvanishing condition, hence belongs to the corresponding \(U\)-locus.%


\item Fix \(\theta\in U_m^{\mathrm{right}}\).  From the construction, \(\theta\) is generic, \(\gamma\ne0\), all \(\rho_i\ne0\), the finite forward loading slopes are pairwise distinct and nonzero, and the forward weighted contraction map is injective.  Suppose that a reverse parameter \(\eta\) had the same truncated cumulants.  Its reverse support-annihilator is homogeneous of degree \(n\), annihilates the reverse divided-power blocks, and therefore, by equality of cumulants, annihilates the forward blocks.  The forward apolar kernel identity then forces it to be a scalar multiple of the forward support-annihilator.  The scalar is nonzero because a support-annihilator of the loading directions is nonzero.  But the reverse support-annihilator is divisible by \(y\), whereas the forward support-annihilator is not divisible by \(y\), since \(\gamma\) and all \(\rho_i\) are nonzero.  This contradiction proves
\[
R^{\mathrm{left}}_{m,K}\!\left(\Phi^{\mathrm{right}}_{m,K}(\theta)\right)=\varnothing .
\]%


\item For the same \(\theta\), take
\[
Q(z)=\prod_{r\in\{\gamma,\rho_1,\ldots,\rho_m\}}(z-r),
\]
with the multiset interpretation of the product.  Genericity makes the entries \(\gamma,\rho_1,\ldots,\rho_m\) pairwise distinct, and the extra factor \(\Delta_\rho\) together with genericity excludes \(0\); hence \(Q\ne0\), \(Q\) is squarefree, \(Q(0)\ne0\), and its root multiset is exactly \(\{\gamma,\rho_1,\ldots,\rho_m\}\).  If another generic forward parameter \(\theta''\) has the same forward cumulants, its own support-annihilator lies in the same forward apolar kernel; the kernel identity makes it a nonzero scalar multiple of the support-annihilator of \(\theta\), and dehomogenizing in the \(x\)-chart gives the same root multiset.%


\item Let \(D\) be the forward loading-direction support and let \(Q_D\) be its homogeneous support-annihilator as in \cref{obj:def:apolar-notation}.  Each loading direction has at least one nonzero coordinate, so \(Q_D\ne0\).  The fixed vertical loading direction contributes the factor \(x\), while the nonzero finite slopes and \(\gamma\ne0\) exclude a factor \(y\).  Finally, the forward apolar kernel identity gives, for every homogeneous binary form \(q\) of degree \(n\),
\[
\bigl[q(\partial)f_{n+k}=0\ \text{for all }0\le k\le m\bigr]
\Longleftrightarrow
\exists c\in\mathbb C:\ q=cQ_D .
\]%


\item The reverse proof is the same argument with \(x\) and \(y\), and right and left, interchanged.  For \(\eta\in U_m^{\mathrm{left}}\), genericity and \(R_{\mathrm l}\ne0\) give \(\delta\ne0\), all \(\sigma_i\ne0\), distinct nonzero reverse finite loading coordinates, and injectivity of the reverse weighted contraction map.  A hypothetical forward parameter with the same cumulants would have a forward support-annihilator lying in the reverse apolar kernel; hence it would be a nonzero scalar multiple of the reverse support-annihilator.  This contradicts divisibility by \(x\), because the forward support-annihilator is divisible by \(x\) and the reverse one is not.  Thus the forward fiber is empty.  The univariate polynomial
\[
Q(z)=\prod_{r\in\{\delta,\sigma_1,\ldots,\sigma_m\}}(z-r)
\]
is nonzero, squarefree, nonzero at \(0\), and has the stated root multiset; the same dehomogenized-kernel argument shows that every generic reverse parameter with the same cumulants has that multiset.  For the reverse loading-direction support \(D\), the homogeneous \(Q_D\) is nonzero, is divisible by \(y\), is not divisible by \(x\), and its degree-\(n\) common apolar kernel is exactly the line \(\mathbb C Q_D\).%

\end{enumerate}
\end{proof}
