\begin{abstract}
We study a population identification question for a bivariate latent linear non-Gaussian model in which the number \(m\) of middle source slots and an axis normalization are maintained inputs. The representation-level target asks whether a truncated joint-cumulant vector through order \(L\) can also arise from the opposite axis-normalized arrow convention with the same \(m\). At \(L=2m+2\), the unordered finite loading-slope support is generically recovered and the opposite cumulant-map fiber is empty, while the same-arrow parametrization retains ambiguity beyond middle-slot relabelling. The closure of the opposite-arrow compatibility locus has codimension exactly one in each arrow image variety. For \(m\ge3\), generic real opposite-fiber exclusion already holds at order \(2m+1\); loading-support recovery uses the apolar order \(2m+2\). The real-incidence result applies to Euclidean-open parameter neighborhoods meeting the feasible region and sharpens the population geometry of the maintained representation class.
\end{abstract}

\section{Introduction}

Econometric models often become directionally informative only after the researcher imposes structure beyond covariance restrictions. In linear non-Gaussian models, higher-order cumulants encode the loading directions of independent shocks and can therefore restrict which recursive representation is compatible with the population distribution. This mechanism underlies LiNGAM and its latent-variable extensions \citep{ShimizuHyvarinenKanoHoyer2006,HoyerShimizuKerminenPalviainen2008,TashiroShimizuHyvarinenWashio2014,MaedaShimizu2020}, and is closely connected to independent component analysis and cumulant-based tensor decompositions \citep{Comon1994,HyvarinenOja2000,Cardoso1999,KoldaBader2009}.

This paper isolates a population question for a fixed number \(m\) of known or externally specified middle source slots and the two axis-normalized bivariate latent linear non-Gaussian representation classes in \cref{obj:def:forward-lvlingam-class} and~\cref{obj:def:reverse-lvlingam-class}. One convention tags the representation as \(X\to Y\), the other as \(Y\to X\). The observed object is the finite vector of joint cumulants \(T_L(P)\) in \cref{obj:def:truncated-cumulant}. The target is whether this vector has an opposite-arrow cumulant-map preimage with the same source count and normalization. It serves settings in which an institutional model, factor design, or separate model-selection analysis fixes the number of common shock slots and the researcher evaluates population compatibility of the maintained reverse representation.

\paragraph{Econometric target and decision.}
The maintained model class contains two competing structural representations with the same externally fixed \(m\). The population decision rejects a convention when the observed truncated cumulant vector has an empty fiber under its polynomial cumulant map. The resulting exclusion restriction is representation-level and comes with an exact description of the compatibility set and the residual ambiguity within the surviving convention. These questions matter before estimation: they establish the population target for a cumulant-based procedure and identify the algebraic surface near which such a procedure would be weak.

\paragraph{Contributions.}
The paper establishes three facts about this target. First, the apolar order \(2m+2\) generically recovers the loading-slope support and excludes the opposite fiber. Second, opposite-arrow compatibility has a codimension-one closure, substantially larger than a dimension count based on the \(m\) middle slots might suggest. Third, for \(m\ge3\), generic real opposite-fiber exclusion requires one less cumulant order than support recovery. A separate fiber result characterizes the remaining same-arrow parameter ambiguity.

The main result at the apolar order \(K=2m+2\) is \cref{obj:thm:generic-apolar-arrow-recovery}. On relatively Zariski-open dense parameter loci, and on Euclidean-open parameter neighborhoods that meet the real feasible region, the order-\(K\) cumulants recover the unordered finite loading-slope support through binary-form apolar equations and rule out a full representation in the opposite arrow convention. Its exact domain is the pair of polynomial cumulant maps and their parameter fibers.

The same-arrow corollary in \cref{obj:thm:generic-arrow-recovery-and-fiber-obstruction} adds the corresponding fiber behavior on the generic loci of the apolar theorem. The same cumulants preserve the unordered loading-slope multiset while leaving multiple same-arrow parametrizations beyond the admissible middle-source relabellings in \cref{obj:def:admissible-source-swaps}. In particular, a direct slot can be exchanged with a middle slot while preserving the cumulant vector and remaining outside the admissible label orbit. Thus generic arrow separation delivers more information than covariance equivalence while retaining precisely characterized structural-parameter ambiguity.

The third result, \cref{obj:thm:exceptional-locus-codimension-one}, describes the failure set at the same apolar order. The cumulant vectors that have a generic representation for one arrow and at least one full representation for the other form an exceptional compatibility locus whose closure has codimension exactly one inside each arrow image variety. For \(m\ge2\), a single algebraic dimension is therefore lost throughout this compatibility geometry. This codimension-one statement is important for interpretation: generic exclusion holds off the exceptional set, whose size makes proximity to compatibility surfaces empirically relevant.

The final identification result concerns the cumulant information needed for generic real opposite-arrow exclusion. \Cref{obj:thm:improved-real-information-order} shows that, for \(m\ge3\), order \(2m+1\) already suffices for generic separation over the real feasible regions of \cref{obj:def:real-feasible-regions}. This improves the real information-order bound relative to the apolar support-recovery order, which remains the relevant threshold when the target includes recovery of the loading support.

The paper is closest to the cumulant-based latent LiNGAM literature. \citet{ChenPengHuangEtAl2025Direction} develop a directional testing construction from a higher-cumulant rank deficiency at order \(2m+3\). \citet{SchkodaRobevaDrton2024} give recursive higher-cumulant rank conditions for unobserved confounding. \citet{TramontanoKivvaSalehkaleybarDrtonKiyavash2024,TramontanoKivvaSalehkaleybarDrtonKiyavash2025} target causal-effect identification from cumulants. Our one-order improvement pertains specifically to fixed-slot, axis-normalized population fiber exclusion; the comparison below aligns each result with its statistical or algebraic target.

The comparison with \citet{ChenPengHuangEtAl2025Direction} turns on distinct targets. In their result, \(m\) counts latent confounders in a real statistical testing problem, and the order-\(2m+3\) rank condition supports a causal-direction test. Here \(m\) counts externally fixed middle source slots, the axis normalization is maintained, and the conclusion is generic emptiness of an opposite polynomial-map fiber together with support-recovery and codimension-one geometry. The difference in order is therefore indexed to these respective targets and assumptions.

\begin{table}[ht]
\centering
\scriptsize
\caption{Auditable comparison with the closest cumulant-based approaches}
\begin{tabular}{p{0.17\linewidth}p{0.15\linewidth}p{0.17\linewidth}p{0.21\linewidth}p{0.20\linewidth}}
\hline
Work & Source-count and normalization & Population object & Scope of conclusion & Statistical output \\
\hline
Classical LiNGAM/ICA & model-specific dimension and mixing structure & observational distribution or mixing representation & ordering or mixing identification under the stated statistical model & estimators or algorithms are central \\
\citet{ChenPengHuangEtAl2025Direction} & \(m\) enters a latent-confounder testing construction & higher-cumulant rank condition & directional testing at order \(2m+3\) in a real statistical model & test construction \\
\citet{SchkodaRobevaDrton2024} & latent-confounding structure encoded by recursive rank restrictions & higher-cumulant tensors & rank conditions for unobserved confounding & identification conditions \\
\citet{TramontanoKivvaSalehkaleybarDrtonKiyavash2024,TramontanoKivvaSalehkaleybarDrtonKiyavash2025} & model-specific latent structure & cumulants relevant to causal effects & causal-effect identification & constructive identification methodology \\
This paper & externally fixed \(m\), fixed source slots, and axis normalization & truncated population cumulant vector & complex-generic opposite-fiber exclusion and support recovery at \(2m+2\); codimension-one compatibility; separate real-generic exclusion at \(2m+1\) for \(m\ge3\) & population fiber characterization \\
\hline
\end{tabular}
\end{table}

\paragraph{A one-middle-slot interpretation.}
When \(m=1\), the forward convention can be written
\[
X=S_0+S_1,\qquad
Y=\gamma S_0+\rho S_1+S_2.
\]
An econometrician may regard \(S_1\) as one externally maintained common-shock slot and \(S_0,S_2\) as the two axis-normalized innovation slots. If both loadings of \(S_1\) are nonzero, it has the usual latent-confounder interpretation; the theorem uses the more general source-slot representation. At order four, \cref{obj:thm:generic-apolar-arrow-recovery} says that, off its stated algebraic exceptional set, the resulting population cumulants have an empty reverse-convention fiber under the same one-slot specification. \Cref{obj:thm:exceptional-locus-codimension-one} then places vectors admitting both conventions on a codimension-one closure. This example illustrates the precise representation-level decision delivered by the theory.

The paper's scope is population identification from finite cumulants within a fixed axis-normalized latent-source representation class. It establishes representation compatibility and separation for a maintained \(m\), complementing finite-sample inference, model selection, and broader graphical identification analyses \citep{Pearl2009,SpirtesGlymourScheines2001,PetersJanzingScholkopf2017,RichardsonSpirtes2002}. This precise scope makes the causal interpretation conditional on the stated latent-source class.

The proofs use classical apolarity of binary forms and simultaneous decomposition ideas \citep{ComonMourrain1996,Landsberg2012}. Cumulants turn independent-source representations into sums of powers of loading directions; apolar equations then recover, or partially constrain, the support of those directions. The verification appendix records the Lean 4 declarations corresponding to the delivered mathematical objects.
