% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_honest\_did\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{panel\_honest\_did\_phase} / \texttt{v1}%
  \\ \large\textit{Active-face phase diagram for zero inclusion in Honest-DiD sensitivity analysis}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form panel / partial-identification proposal, not a Q1
pool-mode instance.  The locked tuple is:
\[
(\texttt{qid},\texttt{specialization},p,\texttt{assignment},\texttt{target},\texttt{regression})
=
(\texttt{panel\_honest\_did\_phase},\texttt{v1},(T_0,T_1),
\texttt{event-study normal limit},\ell^\transpose\tau_{\mathrm{post}},
\texttt{Honest-DiD polyhedral sensitivity}).
\]
Here \(T_0 \ge 2\) is the number of pre-treatment event-time coefficients and
\(T_1 \ge 1\) is the number of post-treatment coefficients.  The observable
input is
\[
\widehat\beta=(\widehat\beta_{\mathrm{pre}}^\transpose,
\widehat\beta_{\mathrm{post}}^\transpose)^\transpose
\in \mathbb{R}^{T_0+T_1}, \qquad
\widehat\Sigma \in \mathbb{S}^{T_0+T_1}_{++},
\]
with the usual event-study normal approximation for
\(\widehat\beta-\beta\).  The target is the scalar dynamic ATT
\(\theta=\ell^\transpose\tau_{\mathrm{post}}\) for a fixed
\(\ell\in\mathbb{R}^{T_1}\).  The sensitivity restriction is the
Rambachan--Roth smoothness class written as a parametric polyhedron
\(\Delta(M)=\{\delta: A\delta \le a+M b\}\), where \(A,a,b\) encode the
chosen second-difference or relative-magnitude restriction and \(M\ge 0\).
The proposed kernel concerns the zero-null decision
\[
0\in CI(M) \quad\Longleftrightarrow\quad
\text{the Honest-DiD test of }H_0:\theta=0\text{ does not reject at budget }M,
\]
using the same fixed-\(M\) conditional or hybrid confidence-set convention as
\citet{RambachanRoth2023}; the novelty is the facewise characterization as
\(M\) varies, not a change in the fixed-\(M\) procedure.

\begin{abstract}
Honest-DiD sensitivity analysis asks how much violation of parallel trends is
needed before an event-study conclusion changes, but current implementations
treat the sensitivity budget \(M\) as an external grid value.  This proposal
asks for a sharp pathwise inference principle for affine-budget linear
conditional-moment sensitivity problems, with Rambachan--Roth Honest-DiD as the
leading specialization.  The kernel conjecture is that the whole zero-null
decision path decomposes into finitely many observable certificate intervals,
each carrying the active sensitivity face, selected moment set, RR/ARP critical
value, and first-crossing equation; zero rejection, tangency, and zero
inclusion are separated by certificate-specific endpoint formulas.  Unlike a
generic parametric-linear-programming restatement, the proposed object includes
the data-dependent RR/ARP conditional critical value, the pretrend nuisance
equality, slack-moment selection, and the regular-conditional tie law needed
for coverage.  The flagship conjecture then uses that diagram to give local
and tie-robust inference for the random breakdown frontier itself.  Resolving
it would turn sensitivity plots into auditable face certificates for any
affine-budget conditional-moment sensitivity path, not only into a faster way
to compute one Honest-DiD grid crossing.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied Honest-DiD papers now report sensitivity curves and breakdown values,
but the substantive interpretation of a breakdown value depends on which
admissible trend-deviation face makes the zero null feasible.  Two studies can
have the same reported breakdown budget while one is overturned by a single
stable curvature pattern and the other only by a knife-edge tie among slack
moments.  The scientific question is therefore not only ``how large is \(M\)?''
but ``which counterfactual trend geometry makes the conclusion fail?''

\paragraph{The main finding (proposed).}
The headline result is Conjecture 1: for affine-budget linear
conditional-moment sensitivity paths with RR/ARP-style conditional critical
values, the zero-null decision admits a finite active-face certificate, and
Honest-DiD is the motivating specialization.  Each certificate cell is indexed
by a pair \((F,J)\), where \(F\) is a face of the sensitivity polyhedron and
\(J\) is the set of binding conditional moment inequalities, and the endpoints
are explicit roots of facewise equations whose deterministic support component
is obtained from a labelled KKT system and whose cutoff is the RR/ARP
conditional Gaussian critical value.  A companion conjecture gives the
tie-case boundary through a regular conditional Gaussian law on the affine tie
subspace, equivalently a vanishing-tube limit.  A final conjecture inverts this
local law under a transversality condition to form confidence sets for the
breakdown point \(M_\star\) itself.

\paragraph{What is new.}
\citet{RambachanRoth2023} provide uniformly valid confidence sets for each
fixed \(M\), and \citet{AndrewsRothPakes2023} provide the conditional
moment-inequality inference machinery underlying the fixed-\(M\) test.
Classical multiparametric programming already gives critical regions and
piecewise affine or quadratic value maps for parametric LP/QP problems, so
the labelled KKT partition is treated here as imported optimization
bookkeeping rather than a novelty claim.  The epsilon-gap is the econometric
object that those optimization results do not cover: a uniform-in-\(M\)
certificate for a moving-budget conditional-moment inference path whose
critical value, selected moments, and tie law are themselves part of the
statistical procedure.  Honest-DiD supplies the leading pretrend nuisance
equality and smoothness budget, but the proposed theorem is stated for the
broader affine-budget RR/ARP class.  The proposed kernel is the observable
face certificate and crossing-time law for the entire path
\(\{0\in CI(M):M\ge 0\}\), with the same fixed-\(M\) inference convention held
fixed.

\paragraph{How it positions in the literature.}
The anchor cluster is panel / linear-projection DiD with a partial-ID
sensitivity layer.  It sits downstream of staggered and event-study DiD
estimators, but its theorem is not an estimator-comparison theorem; it is a
pathwise geometry theorem for the Honest-DiD identified set and its robust
confidence set.  It uses the partial-identification language of breakdown
frontiers while staying inside the event-study normal limit used by
Rambachan--Roth.

\paragraph{Implications for the community.}
The concrete consumer is the applied Honest-DiD workflow implemented in the
HonestDiD and moderndid packages and used in sensitivity plots following
\citet{RambachanRoth2023}: instead of reporting only the first \(M\) on a
grid at which zero enters the interval, or only the one-sided confidence
interval for \(M_\star\) noted in their discussion of breakdown values, a
paper could report the controlling face, the slack moments, and whether the
crossing is regular or tied.

\paragraph{How research benefits from the conclusion.}
Researchers should report the active deviation pattern and tie status of an
Honest-DiD breakdown value, not only the scalar budget.

\section{Related work}
\citet{RambachanRoth2023} are the direct anchor: they define the Honest-DiD
sensitivity restrictions, show fixed-\(M\) uniform validity for robust
confidence sets, and present empirical breakdown plots, but they do not give a
pathwise active-face theorem in \(M\).  \citet{AndrewsRothPakes2023} provide
linear conditional moment-inequality tests with nuisance parameters and slack
moment robustness; this proposal asks how those binding moments change along
the Honest-DiD sensitivity path.  \citet{KaidoMolinariStoye2019} study
projection inference for partially identified parameters by optimizing over
moment-inequality regions, which is the closest general partial-ID inference
thread, but their target is calibrated projection intervals rather than an
Honest-DiD zero-crossing face diagram.  \citet{MastenPoirier2020} formalize
breakdown frontiers as targets, motivating the crossing value as an object in
its own right; the present proposal specializes this idea to the
Rambachan--Roth event-study geometry and adds active-face certificates.
\citet{Roth2022Pretrends} explains why binary pretrend tests distort
event-study inference, which motivates continuous sensitivity paths rather
than accept/reject pretesting.  \citet{RothSantAnnaBilinskiPoe2023} survey
recent DiD methods and identify violations of parallel trends as a central
frontier; this proposal contributes a pathwise diagnostic for that frontier.
\citet{SunAbraham2021} and \citet{CallawaySantAnna2021} are relevant because
modern event-study inputs to Honest-DiD often come from staggered-adoption
estimators; the proposal treats those inputs through their asymptotic
coefficient vector and covariance matrix.  \citet{ChernozhukovHongTamer2007}
are a foundational moment-inequality inference reference; they are included to
mark that the novelty is not generic inequality inference but the
Rambachan--Roth moving-budget face path.  \citet{GalNedoma1972} and
\citet{BemporadMorariDuaPistikopoulos2002} are the relevant
multiparametric-programming comparators: they show that parametric LP/QP
solutions admit critical regions and piecewise affine control/value maps, but
they do not contain the conditional moment-inequality critical values,
slack-moment conditioning, or breakdown-value coverage target of Honest-DiD.
\citet{FangSantos2019} give the closest generic nonsmooth-inference
comparison through the delta method for directionally differentiable
functionals; the proposed gap is that the Honest-DiD crossing functional has a
moving RR/ARP critical value and a data-dependent active-moment selection rule
that must be stated before the directional derivative is usable.
\citet{FirpoGalvaoParker2023} are a closer value-function comparator: they
develop uniform inference after marginal optimization, while this proposal
targets a moving-budget zero-crossing value with RR/ARP conditional critical
values and tied active moments.
\citet{AndrewsSoares2010} develop generalized moment selection for moment
inequality models; this proposal asks for the special selection path generated
by the Rambachan--Roth budget \(M\), including which selected moments survive
at a breakdown crossing.  \citet{KaidoMolinariStoye2022} is the closest
constraint-qualification comparison: it relates partial-identification
regularity assumptions to Mangasarian--Fromowitz type conditions, whereas this
proposal asks how RR/ARP critical values behave when the Honest-DiD path
crosses regular and tied faces.

In-catalogue ThmSmith prior art is nearby but distinct.  The API entry
``Q1\_SpectralThreshold -- stationary first-order Markov spectral-threshold
refutation'' records a panel FWL sign-lock refutation for Q1 Markov assignment,
not Honest-DiD sensitivity inference.  The banked
\texttt{q1\_spectral\_phase\_transition/p1\_markov} proposal identified a
three-regime phase-transition vocabulary, but its review notes left the
row-space/box affine-fiber lemma unresolved and it did not involve
Rambachan--Roth fixed-\(M\) confidence sets.  The banked
\texttt{pid\_did\_anticipation\_bounded/v1} proposal gives sharp intervals for
independent anticipation boxes and explicitly warns that coupled restrictions
make the displayed interval only an outer bound; this proposal studies the
coupled second-difference polyhedron used by Honest-DiD.

\section{Formal setup}
There are \(T_0\) pre-treatment event-time coefficients and \(T_1\)
post-treatment event-time coefficients.  Write
\[
\beta=(\beta_{\mathrm{pre}}^\transpose,\beta_{\mathrm{post}}^\transpose)^\transpose
=
(\delta_{\mathrm{pre}}^\transpose,
(\delta_{\mathrm{post}}+\tau_{\mathrm{post}})^\transpose)^\transpose,
\]
where \(\delta\in\mathbb{R}^{T_0+T_1}\) is the untreated differential trend
and \(\tau_{\mathrm{post}}\in\mathbb{R}^{T_1}\) is the dynamic ATT vector.
The observed estimator satisfies the finite-dimensional normal approximation
\[
\widehat\beta \sim N(\beta,\widehat\Sigma/n)
\]
with \(\widehat\Sigma\) treated as known for the normal-limit problem.

The target is \(\theta=\ell^\transpose\tau_{\mathrm{post}}\).  For
\(M\ge 0\), the sensitivity set is the polyhedron
\[
\Delta(M)=\{\delta\in\mathbb{R}^{T_0+T_1}: A\delta \le a+M b\}.
\]
The zero-null feasible set is
\[
\mathcal{N}_0(M)=\{(\delta,\tau_{\mathrm{post}}):
\delta\in\Delta(M),\ \ell^\transpose\tau_{\mathrm{post}}=0,\ 
\beta=(\delta_{\mathrm{pre}},
\delta_{\mathrm{post}}+\tau_{\mathrm{post}})\}.
\]
Let \(Y(M)\) denote the Rambachan--Roth linear-inequality statistic for the
null \(\theta=0\) after eliminating \((\delta,\tau_{\mathrm{post}})\), and
write it in canonical form as
\[
G(M)\eta \le h(M)+R\widehat\beta,\qquad
h(M)=h_0+M h_1,
\]
where \(\eta\in\mathbb{R}^d\) is the nuisance parameter left by the null,
\(G(M)\in\mathbb{R}^{q\times d}\), \(h_0,h_1\in\mathbb{R}^q\), and
\(R\in\mathbb{R}^{q\times(T_0+T_1)}\) is the observable coefficient-loading
matrix in the zero-null inequality system.  For each face pair \((F,J)\),
\(F\) indexes binding sensitivity inequalities and \(J\) indexes binding
conditional moment inequalities in the fixed-\(M\) test.
The fixed-\(M\) RR/ARP decision is represented by the studentized slack
statistic
\[
T_{\mathrm{RR}}(M)
=\inf_{\eta\in\mathbb{R}^d}
\left\| \left(G(M)\eta-h_0-Mh_1-R\widehat\beta\right)_{+}
\right\|_{\Omega(M)^{-1}},
\]
where \(\Omega(M)\) is the covariance matrix of the canonical inequalities
induced by \(\widehat\Sigma\).  Let \(\mathcal{C}(M)\) denote the conditioning
event or hybrid selection event used by the fixed-\(M\) Rambachan--Roth
procedure, let \(S(M)\subseteq\{1,\ldots,q\}\) be the selected non-slack
moment set, and let
\[
c_{1-\alpha}^{\mathrm{RR}}(M;S,\mathcal{C})
\]
be the corresponding conditional or hybrid critical value.  Thus
\[
\mathsf{Acc}(M)=1
\quad\Longleftrightarrow\quad
T_{\mathrm{RR}}(M)\le
c_{1-\alpha}^{\mathrm{RR}}(M;S(M),\mathcal{C}(M)).
\]
For tied active pairs
\(\mathcal{Q}=\{(F_1,J_1),\ldots,(F_s,J_s)\}\), let
\(L_r\subseteq\mathbb{R}^{q}\) be the tangent space of canonical inequality
scores that leaves the face pair \((F_r,J_r)\) first-order unchanged, and let
\[
L_{\mathcal{Q}}=\bigcap_{r=1}^s L_r,\qquad
H_{\mathcal{Q}}=\mathbb{R}^{q}/L_{\mathcal{Q}}.
\]
Let \(\Pi_{\mathcal{Q}}\) be the \(\Omega(M_0)\)-orthogonal projection onto a
chosen representative of the quotient space \(H_{\mathcal{Q}}\).  If
\(Z\sim N(0,\Omega(M_0))\), the adjacent face scores are
\[
\mathbb{G}_r=g_r^\transpose\Pi_{\mathcal{Q}}Z,\qquad r=1,\ldots,s,
\]
where \(g_r\) is the normalized outward support direction for face pair
\((F_r,J_r)\).  Let \(B_{\mathcal{Q}}\) be the \((s-1)\times q\) matrix whose
rows are \((g_r-g_1)^\transpose\Pi_{\mathcal{Q}}\), \(r=2,\ldots,s\).  Let
\(\Pr_{\mathcal{Q}}\) be the regular conditional Gaussian law of
\(\Pi_{\mathcal{Q}}Z\) given the affine tie subspace
\[
E_{\mathcal{Q}}=\{B_{\mathcal{Q}}Z=0\};
\]
equivalently, \(\Pr_{\mathcal{Q}}\) is the limit of the conditional laws given
\(\|B_{\mathcal{Q}}Z\|\le\varepsilon\) as \(\varepsilon\downarrow 0\), whenever
that tube limit exists.  Let \(\mathcal{A}(\mathcal{Q})\) be the finite set of
adjacent nonselected face pairs whose one-sided support scores are comparable
at \(M_0\), and write their scores as
\(\mathbb{G}_{r'}=g_{r'}^\transpose\Pi_{\mathcal{Q}}Z\).  The tied
conditioning event inside the tie law is
\[
K_{\mathcal{Q}}
=\{\mathbb{G}_1
\ge \mathbb{G}_{r'}\text{ for every }r'\in\mathcal{A}(\mathcal{Q})\},
\]
with nonadjacent slack inequalities conditioned on the same slack rule used in
the fixed-\(M\) RR/ARP procedure.  The tied quotient critical value is the
regular-conditional quantile
\[
c_{1-\alpha}^{\mathrm{RR}}(\mathcal{Q})
=\inf\{c:\Pr_{\mathcal{Q}}(\max_{r\le s}\mathbb{G}_r\le c\mid
K_{\mathcal{Q}})\ge 1-\alpha\}.
\]
The acceptance indicator is
\[
\mathsf{Acc}(M)=\one\{0\in CI(M)\}.
\]
The first crossing is
\[
M_\star=\inf\{M\ge 0:\mathsf{Acc}(M)=1\}.
\]
The plug-in crossing \(\widehat M_\star\) is the same functional with
\((\widehat\beta,\widehat\Sigma)\) substituted for the limiting inputs.
For inference on \(M_\star\), the observable Gaussian analogue draws
\(Z^\ast\sim N(0,\widehat\Omega(\widehat M_\star))\) conditional on the data,
forms \(\widehat{\mathbb{G}}_r^{\,\ast}
=\widehat g_r^\transpose\widehat\Pi_{\widehat{\mathcal{Q}}}Z^\ast\), and
computes the plug-in tied critical value
\(\widehat c_{1-\alpha}^{\mathrm{RR}}(\widehat{\mathcal{Q}})\) by the same
conditional-quantile rule on the estimated quotient event.

The locked parameters are reproduced verbatim:
\begin{quote}
\begin{verbatim}
(qid, specialization, p, assignment, target, regression)
= (panel_honest_did_phase, v1, (T0,T1),
   event-study normal limit, ell' tau_post,
   Honest-DiD polyhedral sensitivity).
Observable input: beta_hat in R^(T0+T1), Sigma_hat positive definite.
Sensitivity set: Delta(M) = {delta : A delta <= a + M b}, M >= 0.
Decision path: Acc(M) = 1{0 in CI(M)} under the fixed-M
Rambachan-Roth conditional or hybrid confidence-set convention.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Normal event-study limit]\label{ass:normal}
The event-study estimator obeys the fixed-dimensional normal approximation
\(\widehat\beta\sim N(\beta,\widehat\Sigma/n)\), with
\(\widehat\Sigma\in\mathbb{S}_{++}^{T_0+T_1}\) treated as known in the
normal-limit problem.
\end{assumption}

\begin{assumption}[Polyhedral Honest-DiD sensitivity]\label{ass:poly}
For every \(M\ge 0\), the admissible trend-deviation set is
\(\Delta(M)=\{\delta:A\delta\le a+Mb\}\), with fixed observable matrices
\((A,a,b)\).  The rows include the chosen second-difference or
relative-magnitude smoothness restriction and any sign restriction being held
fixed throughout the path.
\end{assumption}

\begin{assumption}[Fixed-\(M\) confidence-set convention]\label{ass:fixedM}
For every fixed \(M\), \(CI(M)\) is the Rambachan--Roth conditional or hybrid
confidence set for \(\theta=\ell^\transpose\tau_{\mathrm{post}}\) using the
linear conditional moment-inequality representation of the zero null.  The
proposal does not alter the fixed-\(M\) critical-value rule.
\end{assumption}

\begin{assumption}[Facewise critical-value specification]\label{ass:critical}
On every open phase interval, the selected non-slack set \(S(M)\), conditioning
event \(\mathcal{C}(M)\), covariance map \(\Omega(M)\), and critical value
\(c_{1-\alpha}^{\mathrm{RR}}(M;S(M),\mathcal{C}(M))\) are given by the
fixed-\(M\) RR/ARP conditional or hybrid rule applied to the same canonical
rows.  Conditional on a fixed active pair \((F,J)\), this critical value is
the \(1-\alpha\) quantile of the Gaussian statistic induced by
\(\Omega(M)\) and \(\mathcal{C}(M)\); it is continuous on the open phase
interval.  At a finite tie, the quotient space \(H_{\mathcal{Q}}\), tie
subspace \(E_{\mathcal{Q}}\), regular conditional law
\(\Pr_{\mathcal{Q}}\), tie event \(K_{\mathcal{Q}}\), and tied critical value
\(c_{1-\alpha}^{\mathrm{RR}}(\mathcal{Q})\) are those defined in the formal
setup; the regular conditional law is equivalently the vanishing-tube limit
around \(E_{\mathcal{Q}}\), \(K_{\mathcal{Q}}\) has positive
\(\Pr_{\mathcal{Q}}\)-probability, and the resulting tied critical value is
finite.
\end{assumption}

\begin{assumption}[Moving-budget RR/ARP moment-inequality path]\label{ass:moving_budget}
After imposing the scalar zero null, the fixed-\(M\) confidence-set decision
for the class under study can be written as a finite linear conditional
moment-inequality system
\[
G(M)\eta \le h_0+Mh_1+R\widehat\beta,
\]
with \(q\) canonical inequalities, nuisance parameter
\(\eta\in\mathbb{R}^d\), positive-definite covariance map \(\Omega(M)\), and
the RR/ARP conditional or hybrid critical-value rule applied to the canonical
rows.  The Honest-DiD system in the formal setup is the maintained
specialization, with \(G(M),h_0,h_1,R\) generated by the
Rambachan--Roth sensitivity restrictions.
\end{assumption}

\begin{assumption}[Nondegenerate target]\label{ass:target}
The target loading \(\ell\neq 0\), and the zero-null elimination map has full
row rank after quotienting out nuisance directions that are unidentified under
\(\ell^\transpose\tau_{\mathrm{post}}=0\).
\end{assumption}

\begin{assumption}[Face regularity on open phases]\label{ass:face_regular}
On each open phase interval, the binding sensitivity face \(F\) and binding
moment set \(J\) satisfy the linear independence constraint qualification of
the fixed-\(M\) moment-inequality problem, and all nonbinding inequalities are
slack by a positive margin.
\end{assumption}

\begin{assumption}[Finite tie set]\label{ass:finite_tie}
The observable path is generic except at finitely many values of \(M\): outside
that finite set there is a unique active pair \((F,J)\), and at each tie value
only finitely many adjacent active pairs bind.
\end{assumption}

\begin{assumption}[Consistent quotient-law estimation]\label{ass:quotient_est}
At every regular or tied breakdown crossing, the plug-in active-pair set
\(\widehat{\mathcal{Q}}\), projection
\(\widehat\Pi_{\widehat{\mathcal{Q}}}\), adjacent support directions
\(\widehat g_r\), one-sided slopes \(\widehat c_r\), and covariance
\(\widehat\Omega(\widehat M_\star)\) converge to their population analogues
uniformly over local sequences with the same adjacent active-pair set.  The
conditional Gaussian simulation or analytic calculation used to compute
\(\widehat c_{1-\alpha}^{\mathrm{RR}}(\widehat{\mathcal{Q}})\) consistently
estimates the tied quotient critical value.
\end{assumption}

\begin{assumption}[Breakdown transversality]\label{ass:transversal}
The first crossing \(M_\star\) is finite and isolated.  On a regular face,
the controlling function \(\chi_k(M)\) satisfies
\(\chi_k(M_\star)=0\) and has nonzero one-sided derivative
\(\dot\chi_k(M_\star)<0\), so the path moves from rejection
\((\chi_k>0)\) to nonrejection \((\chi_k\le 0)\) at a first-order rate.  At a
tied crossing with adjacent set \(\mathcal{Q}\), each active one-sided score
has a finite slope \(c_r\), at least one adjacent direction has inward slope
and at least one has outward slope after applying the RR/ARP critical-value
derivative, and no nonadjacent slack inequality becomes binding at the same
\(n^{-1/2}\) scale.
\end{assumption}

\section{Main results}
\paragraph{Known optimization input, not claimed as a novel theorem.}
Classical multiparametric programming and KKT normal-fan arguments imply that,
under Assumptions \ref{ass:normal}, \ref{ass:poly},
\ref{ass:moving_budget}, \ref{ass:target}, \ref{ass:face_regular}, and
\ref{ass:finite_tie}, the deterministic statistic
\[
D(M)=\inf_{\eta\in\mathbb{R}^d}
\left\| \left(G(M)\eta-h_0-Mh_1-R\widehat\beta\right)_{+}
\right\|_{\Omega(M)^{-1}}
\]
has a finite partition of the \(M\)-axis into open intervals and finitely many
tie points such that one active pair \((F_k,J_k)\) solves the KKT system on
each open interval.  On such an interval,
\[
D(M)=D_k(M;\widehat\beta,\widehat\Sigma,\ell,A,a,b),
\]
where \(D_k\) is obtained by solving the linear KKT equations for
\((F_k,J_k)\) and substituting the solution into the displayed norm.  The
endpoints of the interval are exactly the smallest nonnegative roots of the
face-feasibility, nonbinding-slack, or adjacent-face equality equations for
that labelled KKT solution.  This paragraph is included only to name the
imported deterministic support-function skeleton; the novelty claims below
begin where this generic active-region decomposition is combined with RR/ARP
critical values, moment selection, and breakdown-value inference.

\begin{conjecture}[Conjecture 1: uniform active-face certificate for
affine-budget sensitivity paths (NOT YET PROVED)]\label{conj:phase_diagram}
Under Assumptions \ref{ass:normal}--\ref{ass:finite_tie}, every
moving-budget RR/ARP moment-inequality path satisfying Assumption
\ref{ass:moving_budget} has a finite ordered certificate
\[
\Gamma=\{(m_{k-1},m_k,F_k,J_k,S_k,\mathcal{C}_k,\chi_k):k=1,\ldots,K\}
\]
with partition
\[
0=m_0<m_1<\cdots<m_{K-1}<m_K=\infty
\]
such that, for the Honest-DiD specialization and for any other member of the
same affine-budget RR/ARP class, on every open interval
\((m_{k-1},m_k)\):
\begin{enumerate}[label=(\roman*)]
\item the fixed-\(M\) zero-null test is controlled by the same sensitivity
face \(F_k\) and moment set \(J_k\);
\item the deterministic slack statistic is the facewise function
\[
D_k(M;\widehat\beta,\widehat\Sigma,\ell,A,a,b)
\]
from the labelled KKT skeleton above, while the stochastic cutoff is the
RR/ARP conditional or hybrid quantile
\[
c_k(M)=c_{1-\alpha}^{\mathrm{RR}}(M;S_k,\mathcal{C}_k)
\]
specified in Assumption \ref{ass:critical};
\item \(\mathsf{Acc}(M)=1\) if and only if
\[
\chi_k(M):=
D_k(M;\widehat\beta,\widehat\Sigma,\ell,A,a,b)-c_k(M)\le 0.
\]
\end{enumerate}
Consequently \(M_\star\) is the first nonnegative zero of the explicitly
defined facewise equation \(\chi_k(M)=0\), with the additional requirement
that the zero lies inside the interval on which \((F_k,J_k)\), \(S_k\), and
\(\mathcal{C}_k\) are feasible and slack-compatible.  Moreover, the certificate
is uniform in \(M\): checking the finitely many labelled equations and tie
rules in \(\Gamma\) is equivalent to checking the whole path
\(\{\mathsf{Acc}(M):M\ge 0\}\), so no grid search or post hoc active-set
selection is part of the target estimand.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{RambachanRoth2023} prove fixed-\(M\) validity and show empirical
breakdown values, while \citet{AndrewsRothPakes2023} classify conditional
tests by binding and slack moments at a fixed parameter value.
\citet{GalNedoma1972} and
\citet{BemporadMorariDuaPistikopoulos2002} give the closest generic
optimization analogue, namely critical regions for parametric LP/QP problems.
\citet{FirpoGalvaoParker2023} give the closest value-function inference
comparison after optimization.  The epsilon-gap is that the proposed
certificate is not merely an optimizer or value-function region: it is a
uniform-in-\(M\) zero-null inference certificate whose endpoint must include
the RR/ARP critical value, slack-moment selection, and nuisance conditioning
convention, with Honest-DiD as the leading specialization of a broader
affine-budget class.  \citet{AndrewsSoares2010} gives moment-selection critical
values, but not the ordered sensitivity-budget path generated by a
moving-budget restriction.  None of these papers states an observable
certificate for which sensitivity face and selected moment set controls the
first zero crossing of a conditional-moment sensitivity confidence set.
(b) Resolving this advances the applied HonestDiD workflow in
\citet{RambachanRoth2023}: sensitivity plots would gain a reproducible
face certificate and would distinguish regular crossings from crossings caused
by a slack-moment tie.

\begin{conjecture}[Conjecture 2: regular-conditional tie law and tangent regime
(NOT YET PROVED)]\label{conj:tie_law}
Under Assumptions \ref{ass:normal}--\ref{ass:finite_tie}, suppose
\(M_0=m_k\) is a boundary at which active pairs
\((F_1,J_1),\ldots,(F_s,J_s)\) tie.  In a local experiment
\(M=M_0+t/\sqrt{n}\), the zero-null acceptance boundary is governed by
\[
\max_{r\le s}\{\mathbb{G}_r+c_r t\}\le c_{1-\alpha}^{\mathrm{RR}}(F_1,J_1,
\ldots,F_s,J_s),
\]
where \((\mathbb{G}_1,\ldots,\mathbb{G}_s)\) is distributed under the regular
conditional Gaussian law \(\Pr_{\mathcal{Q}}\) on the quotient-space tie
subspace \(E_{\mathcal{Q}}\) defined in the setup, equivalently under the
vanishing-tube limit around that subspace,
\(c_r\) is the one-sided derivative of face \(r\)'s support score with
respect to \(M\), and
\[
c_{1-\alpha}^{\mathrm{RR}}(F_1,J_1,\ldots,F_s,J_s)
\]
is the Rambachan--Roth conditional or hybrid critical value for the tied
quotient problem defined in the setup.  The tangent phase is the set of local
\(t\)-values for which at least two adjacent facewise scores attain the
maximum with positive regular-conditional probability; outside it the crossing
is regular and inherits the single-face law.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest published comparisons are \citet{AndrewsRothPakes2023}, which
shows slack-moment-insensitive conditional inference for fixed linear
conditional moment inequalities, \citet{FangSantos2019}, which supplies
generic inference tools for directionally differentiable functionals,
\citet{FirpoGalvaoParker2023}, which develops uniform inference for optimized
value functions, and \citet{KaidoMolinariStoye2022}, which clarifies how
partial-identification regularity conditions relate to Mangasarian--Fromowitz
constraint qualification.  The epsilon-gap is the operational RR/ARP quotient
problem created when a moving sensitivity budget crosses a tie of active
faces: regular conditional Gaussian law on the tie hyperplane, common tangent
space, projected covariance, selected moment event, and tied critical value
must all be named before generic directional-delta or value-function bootstrap
theory applies.  (b) The concrete consumer is
breakdown-frontier inference in \citet{MastenPoirier2020}: this conjecture
supplies the Honest-DiD kink law needed before one can attach valid
uncertainty bands to an estimated breakdown value \(M_\star\).

\begin{conjecture}[Conjecture 3: valid local inference for affine-budget
breakdown frontiers (NOT YET PROVED)]\label{conj:mstar_inference}
Under Assumptions \ref{ass:normal}--\ref{ass:transversal}, let
\(\widehat M_\star\) be the plug-in first crossing of the fixed-\(M\)
RR/ARP decision path, with Honest-DiD as the leading specialization.  On a
regular face,
\(\sqrt{n}(\widehat M_\star-M_\star)\) has the one-dimensional delta-method
law obtained by differentiating the controlling \(\chi_k(M)\) at
\(M_\star\), with nonzero derivative as required by Assumption
\ref{ass:transversal}.  At a tied crossing satisfying the inward/outward
one-sided slope condition in Assumption \ref{ass:transversal}, define the
observable confidence set by
\[
\widehat{\mathcal{I}}_{1-\alpha}^{M_\star}
=\left\{m\ge 0:
\Pr^\ast\!\left[
\max_{r\le s}\{\widehat{\mathbb{G}}_r^{\,\ast}
+\widehat c_r\sqrt n(m-\widehat M_\star)\}
\le
\widehat c_{1-\alpha}^{\mathrm{RR}}(\widehat{\mathcal{Q}})
\right]\ge 1-\alpha
\right\},
\]
where \(\Pr^\ast\) is conditional probability over
\(Z^\ast\sim N(0,\widehat\Omega(\widehat M_\star))\), the scores
\(\widehat{\mathbb{G}}_r^{\,\ast}\), slopes \(\widehat c_r\), and critical
value \(\widehat c_{1-\alpha}^{\mathrm{RR}}(\widehat{\mathcal{Q}})\) are the
sample analogues defined in the setup and the probability is computed under
the plug-in regular conditional or vanishing-tube tie law.  The set
\(\widehat{\mathcal{I}}_{1-\alpha}^{M_\star}\) has asymptotic coverage at
least \(1-\alpha\), uniformly over local sequences with the same adjacent
active-pair set.  Thus the phase diagram yields inference for the breakdown
value itself, not only fixed-\(M\) inference for whether zero belongs to
\(CI(M)\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{RambachanRoth2023} give valid robust confidence sets at fixed
\(M\) and note a valid one-sided confidence interval for the breakdown value
under their fixed-\(M\) size control, \citet{MastenPoirier2020} develop
inference on breakdown frontiers in general sensitivity models,
\citet{FangSantos2019} covers directionally differentiable plug-in
functionals, \citet{FirpoGalvaoParker2023} covers uniform inference for value
functions after marginal optimization, and \citet{AndrewsSoares2010} covers
generalized moment selection.  The epsilon-gap is therefore not first
inference for a breakdown value; it is an observable two-sided/local
crossing-time law for an affine-budget RR/ARP sensitivity path under moving
conditional critical values, including tied active faces, estimated quotient
events, and an explicit transversality condition.  This is not supplied by
generic multiparametric LP/QP critical regions, static moment-selection theory,
or value-function bootstrap theory.  (b) The
concrete consumer is the empirical breakdown value reported in Honest-DiD
applications following \citet{RambachanRoth2023}: the conjecture would say
when that number can be accompanied by a local tie-robust uncertainty interval
and when a reported crossing is a nonregular kink.

\section{Sanity-check corollaries}
\begin{corollary}[Reduction to fixed-\(M\) Honest-DiD]\label{cor:fixedM}
Under Assumptions \ref{ass:normal}--\ref{ass:fixedM}, if \(M\) is held fixed
and the active pair \((F,J)\) is known, the canonical system used by the
labelled KKT skeleton in §8
collapses to the Rambachan--Roth fixed-\(M\) linear conditional
moment-inequality test with statistic \(T_{\mathrm{RR}}(M)\) and critical
value \(c_{1-\alpha}^{\mathrm{RR}}(M;S(M),\mathcal{C}(M))\).
\end{corollary}

The reduction is immediate because \(\Delta(M)\) is then a single fixed
polyhedron and the phase index carries no pathwise content.

\begin{corollary}[Parallel-trends corner]\label{cor:M0}
Under Assumptions \ref{ass:normal}--\ref{ass:target}, if \(M=0\) and the
chosen \(A,a,b\) encode exact linear extrapolation of the pretrend, then
\(\Delta(0)\) is the Rambachan--Roth baseline restriction and
\(\mathsf{Acc}(0)\) is exactly the zero-null decision of the baseline robust
confidence set.
\end{corollary}

The reduction checks that the phase diagram does not create a new estimand at
the Honest-DiD origin; it only organizes the movement away from that origin.

\begin{corollary}[Single post-period scalar sanity check]\label{cor:scalar}
Under Assumptions \ref{ass:normal}--\ref{ass:finite_tie}, if \(T_1=1\),
\(\ell=1\), and the zero-null system has a unique binding sensitivity
inequality on an open \(M\)-interval, then Conjecture
\ref{conj:phase_diagram} reduces to a one-dimensional affine crossing rule:
zero enters \(CI(M)\) at the first root of the unique facewise inequality plus
the fixed-\(M\) critical-value correction.
\end{corollary}

This is the corner in which an applied breakdown plot should be reproducible
by inspecting a single trend-deviation inequality.

\section{Proof-sketch route}
The route is finite-dimensional convex analysis.  First eliminate the
zero-null nuisance parameters by Fourier--Motzkin elimination or LP duality to
obtain a labelled conditional moment system with right-hand side affine in
\(M\), its covariance \(\Omega(M)\), and the associated RR/ARP critical-value
map.  Next apply the normal-fan decomposition of a polyhedron to partition
the \(M\)-axis by active sensitivity faces and binding moment sets; on each
open cell, the KKT system is linear after fixing \((F,J)\), so the
deterministic slack statistic is an explicit fixed-face function of the
observable coefficient vector and covariance matrix.  The RR/ARP cutoff is
then appended as the conditional Gaussian quantile for the same labelled rows,
not folded into the KKT algebra.  The boundary cases are exactly the failures
of unique active face or LICQ, so the remaining algebra is a local expansion
of adjacent KKT systems, a regular-conditional Gaussian calculation on the
affine tie subspace (or its vanishing-tube limit), and a plug-in inversion
step for \(\widehat M_\star\).  The transversality condition is then checked
by the one-sided derivatives of the selected facewise \(\chi_k\) functions.
The smallest nontrivial worked example should be \(T_0=2,T_1=1\), where all
faces can be enumerated and the regular crossing formula can be checked by
hand against the Rambachan--Roth fixed-\(M\) test.

\section{Honest scope flags}
The deterministic active-region skeleton is imported convex-analytic
bookkeeping from multiparametric programming, not a flagship novelty claim.
Conjectures \ref{conj:phase_diagram}, \ref{conj:tie_law}, and
\ref{conj:mstar_inference} are the open research kernel and are not yet
proved.  The proposal deliberately withdraws
the prior angle's singular-value formulas for global thresholds: the active
face, not a global singular direction, is now the primitive object.  The main
assumption requiring care is Assumption \ref{ass:finite_tie}; a non-generic
observable covariance or coefficient vector may produce continua of ties, in
which case the phase diagram should be stated after perturbation or as a
stratified semialgebraic result rather than a finite interval list.
The v3 revision also withdraws the earlier claim that the full
critical-value-adjusted endpoint is affine-quadratic; only the deterministic
support component has the fixed-face KKT closed form, while the RR/ARP cutoff
is an explicitly defined conditional Gaussian quantile.
The v4 revision withdraws the deterministic active-region decomposition as a
numbered theorem, acknowledges the Rambachan--Roth one-sided confidence
interval for \(M_\star\), and narrows the open inference claim to
two-sided/local/tie-robust moving-critical-value inference.
The v5 revision responds to the field-tier novelty concern by restating the
flagship kernel as a uniform-in-\(M\) active-face certificate for the broader
affine-budget RR/ARP sensitivity class, while keeping Honest-DiD as the lead
application.  It also replaces exact-probability-zero tie conditioning by a
regular conditional Gaussian or vanishing-tube law and adds the nonzero
crossing-rate / inward-outward transversality assumption needed for
\(M_\star\) inference.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 1, replacing the rejected
singular-value threshold kernel with an active-face phase diagram; prior
verdict: none.
\item v2 (revise) --- added multiparametric-programming and
constraint-qualification prior art, made the fixed-\(M\) RR/ARP test statistic
and critical-value convention explicit, fixed the terminal phase ray, defined
the tied quotient object, and added a breakdown-value inference conjecture;
prior verdict: REVISE.
\item v3 (revise) --- removed the already-known fixed-\(M\) reduction as a
main novelty claim, separated deterministic active-region geometry from the
RR/ARP stochastic critical-value path, added Fang--Santos and Andrews--Soares
comparators, operationalized the tied quotient, and replaced the infeasible
population-score \(M_\star\) interval with an observable plug-in Gaussian
construction; prior verdict: REVISE.
\item v4 (revise) --- withdrew the generic active-region decomposition as a
numbered theorem, fixed the tied-face \(s\)-versus-\(q\) notation, added
Firpo--Galvao--Parker as the value-function comparator, accounted for the
Rambachan--Roth one-sided \(M_\star\) interval, and strengthened the kernel to
a moving-budget RR/ARP class theorem with Honest-DiD as the specialization;
prior verdict: REVISE.
\item v5 (revise) --- lifted the novelty claim to a uniform-in-\(M\)
active-face certificate for affine-budget RR/ARP sensitivity paths, defined
ties through a regular conditional Gaussian / vanishing-tube law, and added
the transversality condition for regular and tied \(M_\star\) crossings; prior
verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Andrews, Roth, and Pakes(2023)]{AndrewsRothPakes2023}
Andrews, I., J. Roth, and A. Pakes (2023).
\newblock Inference for linear conditional moment inequalities.
\newblock \emph{Review of Economic Studies} 90(6), 2763--2791.

\bibitem[Andrews and Soares(2010)]{AndrewsSoares2010}
Andrews, D. W. K. and G. Soares (2010).
\newblock Inference for parameters defined by moment inequalities using
generalized moment selection.
\newblock \emph{Econometrica} 78(1), 119--157.

\bibitem[Bemporad, Morari, Dua, and Pistikopoulos(2002)]{BemporadMorariDuaPistikopoulos2002}
Bemporad, A., M. Morari, V. Dua, and E. N. Pistikopoulos (2002).
\newblock The explicit linear quadratic regulator for constrained systems.
\newblock \emph{Automatica} 38(1), 3--20.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and P. H. C. Sant'Anna (2021).
\newblock Difference-in-differences with multiple time periods.
\newblock \emph{Journal of Econometrics} 225(2), 200--230.

\bibitem[Chernozhukov, Hong, and Tamer(2007)]{ChernozhukovHongTamer2007}
Chernozhukov, V., H. Hong, and E. Tamer (2007).
\newblock Estimation and confidence regions for parameter sets in econometric
models.
\newblock \emph{Econometrica} 75(5), 1243--1284.

\bibitem[Gal and Nedoma(1972)]{GalNedoma1972}
Gal, T. and J. Nedoma (1972).
\newblock Multiparametric linear programming.
\newblock \emph{Management Science} 18(7), 406--422.

\bibitem[Fang and Santos(2019)]{FangSantos2019}
Fang, Z. and A. Santos (2019).
\newblock Inference on directionally differentiable functions.
\newblock \emph{Review of Economic Studies} 86(1), 377--412.

\bibitem[Firpo, Galvao, and Parker(2023)]{FirpoGalvaoParker2023}
Firpo, S., A. F. Galvao, and T. Parker (2023).
\newblock Uniform inference for value functions.
\newblock \emph{Journal of Econometrics} 235(2), 1680--1699.

\bibitem[Kaido, Molinari, and Stoye(2019)]{KaidoMolinariStoye2019}
Kaido, H., F. Molinari, and J. Stoye (2019).
\newblock Confidence intervals for projections of partially identified
parameters.
\newblock \emph{Econometrica} 87(4), 1397--1432.

\bibitem[Kaido, Molinari, and Stoye(2022)]{KaidoMolinariStoye2022}
Kaido, H., F. Molinari, and J. Stoye (2022).
\newblock Constraint qualifications in partial identification.
\newblock \emph{Econometric Theory} 38(3), 596--619.

\bibitem[Masten and Poirier(2020)]{MastenPoirier2020}
Masten, M. A. and A. Poirier (2020).
\newblock Inference on breakdown frontiers.
\newblock \emph{Quantitative Economics} 11(1), 41--111.

\bibitem[Rambachan and Roth(2023)]{RambachanRoth2023}
Rambachan, A. and J. Roth (2023).
\newblock A more credible approach to parallel trends.
\newblock \emph{Review of Economic Studies} 90(5), 2555--2591.

\bibitem[Roth(2022)]{Roth2022Pretrends}
Roth, J. (2022).
\newblock Pretest with caution: Event-study estimates after testing for
parallel trends.
\newblock \emph{American Economic Review: Insights} 4(3), 305--322.

\bibitem[Roth, Sant'Anna, Bilinski, and Poe(2023)]{RothSantAnnaBilinskiPoe2023}
Roth, J., P. H. C. Sant'Anna, A. Bilinski, and J. Poe (2023).
\newblock What's trending in difference-in-differences? A synthesis of the
recent econometrics literature.
\newblock \emph{Journal of Econometrics} 235(2), 2218--2244.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021}
Sun, L. and S. Abraham (2021).
\newblock Estimating dynamic treatment effects in event studies with
heterogeneous treatment effects.
\newblock \emph{Journal of Econometrics} 225(2), 175--199.
\end{thebibliography}

\end{document}
