% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_honest\_did\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section initially contains exactly one stage-1 placeholder.
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{panel\_honest\_did\_phase} / \texttt{v1}%
  \\ \large\textit{Singular-value phase transition for covariance-whitened Honest-DiD breakdown frontiers}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid = panel_honest_did_phase
specialization = v1
p = finite event-study memory with pre-period length T_pre >= 2 and post-period
  target dimension r >= 1; the smoothness operator uses second differences
  across the ordered pre/post event-time grid.
assignment = staggered or non-staggered DiD event-study input summarized by
  the asymptotically Gaussian coefficient vector beta_hat =
  (beta_hat_pre, beta_hat_post), covariance matrix Sigma, and a fixed
  post-period loading matrix L selecting the dynamic ATT vector theta =
  L tau_post.  Cohort aggregation is allowed through a known linear map A.
target = robust zero-exclusion threshold for theta under a quadratic
  Honest-DiD smoothness budget M: the smallest M at which the robust
  confidence set for theta contains 0, together with the lower and upper
  phase boundaries M_star_lo and M_star_hi for directional refutability.
regression = event-study or modern staggered-DiD coefficient estimator whose
  output is beta_hat and Sigma; the baseline decomposition is
  beta = tau + delta with tau_pre = 0, theta = L tau_post, and delta constrained
  by the pretrend-matching and second-difference budget below.  The proposed
  closed form is for the covariance-whitened ellipsoidal descendant of the
  Rambachan-Roth smoothness set, not for every polyhedral l_infty variant.
\end{verbatim}

\begin{abstract}
Rambachan and Roth's Honest-DiD procedure asks researchers to report how robust an event-study conclusion is as the smoothness budget \(M\) for violations of parallel trends grows.
This proposal asks for a theorem-level description of the first zero-crossing and the surrounding active-direction geometry, rather than a grid search over \(M\).
For the covariance-whitened quadratic descendant of the Honest-DiD second-difference restriction, the kernel conjecture is a sharp three-regime phase transition: below \(M_\star^{lo}\) zero is excluded for every admissible trend deviation, between \(M_\star^{lo}\) and \(M_\star^{hi}\) zero is excluded only for a calibrated subset of projection directions, and above \(M_\star^{hi}\) zero is robustly irrefutable.
The conjectured thresholds are singular-value functionals of an observable kernel matrix built from the event-study covariance, the post-period loading, the pretrend extrapolation operator, and the second-difference smoothness operator.
If resolved, the result would turn Honest-DiD breakdown plots into closed-form diagnostics for staggered event studies and would give applied researchers a reproducible way to report the exact amount and direction of pretrend deviation needed to overturn a null-effect conclusion.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Honest-DiD made sensitivity to violations of parallel trends operational, but the usual empirical object is still a curve or table: evaluate a robust confidence interval at several values of \(M\), then report the value at which the interval first contains zero.
That workflow hides the geometry of the breakdown point.
In particular, it does not say whether the conclusion fails because every admissible post-trend direction can mimic zero, because one narrow active direction can do so, or because staggered aggregation has made some directions invisible.

\paragraph{The main finding (proposed).}
The flagship claim is Conjecture~\ref{conj:svd-phase}: in the covariance-whitened quadratic Honest-DiD descendant, the robust zero-exclusion decision is governed by the ellipsoid
\[
  q - M K u,\qquad \|u\|_2\le 1,
\]
where \(q=V^{-1/2}\widehat\theta\), \(V=L\Sigma_{post}L^\transpose\), and \(K=V^{-1/2}L S\) is the observable bias-kernel induced by the second-difference smoothness operator.
The conjecture gives two sharp thresholds \(M_\star^{lo}\le M_\star^{hi}\) and an active-direction set \(\mathcal U(M)\).
For \(M<M_\star^{lo}\), zero is excluded for every admissible deviation in the smoothness ball; for \(M_\star^{lo}\le M<M_\star^{hi}\), zero is globally included but some projection directions still reject; for \(M\ge M_\star^{hi}\), zero is included by every regularized projection direction.

\paragraph{What is new.}
The closest published result is \citet{rambachan2023parallel}, which constructs valid robust confidence sets for fixed \(M\), discusses breakdown values in applications, and proves optimality properties for several procedures.
The epsilon-gap is that the paper does not classify the zero-crossing as a singular-value phase diagram of the whitened bias map; it computes or plots robust sets under a user-chosen restriction.
The proposal is also distinct from \citet{masten2020breakdown}: breakdown frontiers are the conceptual target, but the new object is the closed-form crossing geometry for an Honest-DiD event-study confidence set with covariance and smoothness operators visible in the formula.

\paragraph{How it positions in the literature.}
The anchor cluster is panel and partial identification: event-study DiD supplies the coefficient vector, while the uncertainty about \(\delta_{post}\) is a partial-identification problem.
\citet{andrews2023linear} is the nearest inference geometry comparator because Honest-DiD restrictions can be written as linear moment inequalities, but its contribution is valid inference at fixed nuisance configurations rather than an explicit active-face or singular-value breakdown formula.
Modern staggered-DiD papers such as \citet{callaway2021multiple}, \citet{sunabraham2021eventstudy}, and \citet{borusyak2024eventstudy} determine which event-study coefficients are meaningful; the proposed result starts after that estimator is chosen and asks how the robustness threshold depends on its covariance and aggregation map.

\paragraph{Implications for the community.}
The concrete downstream consumer is the HonestDiD empirical workflow used after Rambachan--Roth: a researcher who now reports a grid-based breakdown value for the Benzarti--Carloni or teen-employment style event study could instead report \(M_\star^{lo}\), \(M_\star^{hi}\), and the active projection direction that explains the crossing.

\paragraph{How research benefits from the conclusion.}
Researchers should report the singular direction of the pretrend violation that overturns the result, not only the scalar \(M\) at which a plotted interval first touches zero.

\section{Related work}
\citet{rambachan2023parallel} introduce robust inference for DiD and event studies under restrictions on violations of parallel trends; this is the primary anchor because the proposal studies the crossing geometry of their \(CI(M)\) path.
\citet{roth2022pretest} shows why binary pretrend testing has low power and can distort inference after pretesting; this motivates a continuous breakdown threshold rather than a pass/fail pretrend screen.
\citet{manski2018bounded} use bounded-variation restrictions to cope with ambiguity in panel policy evaluation; their role here is the bounded-deviation tradition that Honest-DiD makes inferential.
\citet{masten2020breakdown} define breakdown frontiers as boundaries between assumptions that preserve or overturn a conclusion; the proposal specializes that frontier idea to the Honest-DiD smoothness parameter and seeks a closed-form event-study frontier.
\citet{andrews2023linear} provide uniformly valid inference for linear conditional moment inequalities with nuisance parameters; the closest gap is that they do not derive symbolic active-face formulas for the Honest-DiD zero crossing.
\citet{kwon2024bayes} propose Bayes and empirical-Bayes approaches to parallel-trends deviations learned from pretrends; this creates a useful contrast between posterior calibration and the minimax singular direction proposed here.
\citet{callaway2021multiple} identify group-time ATT parameters in staggered DiD under conditional parallel trends; the proposed threshold can be applied after their event-study aggregation map is fixed.
\citet{sunabraham2021eventstudy} show that TWFE event-study coefficients can be contaminated by treatment effects from other relative periods; this proposal treats the resulting coefficient vector and covariance as inputs and studies robustness to trend deviations, not treatment-effect contamination itself.
\citet{borusyak2024eventstudy} develop imputation-based event-study estimation for staggered designs; their estimator is a natural source of \((\widehat\beta,\Sigma)\) for the proposed threshold.
\citet{rothsantanna2023efficient} derive efficient estimators for staggered rollout designs; the covariance-aware threshold here would quantify how efficiency changes the Honest-DiD breakdown frontier.
\citet{wing2024stacked} show that stacked DiD can impose different implicit weights on treatment and control trends; this is the aggregation warning behind Conjecture~\ref{conj:aggregation}.
\citet{liu2025cohort} argues that aggregated Rambachan--Roth robust inference can be misleading in staggered adoption because pre and post coefficients mix cohorts differently; the proposal gives an operator-level threshold diagnostic for that problem.

In-repository prior art is related but not duplicative.
\texttt{ThmSmith/doc/API.md} Section 1.1, Q1\_MinimalBasis, records a minimal decontaminating history-basis theorem for the \(p=1\) switch-on target.
\texttt{ThmSmith/doc/API.md} Section 1.2, Q1\_StaggeredMinimalBasis, records a staggered-adoption analogue with cohort-period switch-on and continued-treatment columns.
\texttt{ThmSmith/doc/API.md} Section 1.4, Q1\_SpectralThreshold, records a Markov spectral-threshold refutation about FWL weight signs, while the banked \texttt{q1\_spectral\_phase\_transition/p1\_markov} proposal attempted a row-space phase transition for dynamic ATT support.
The closest banked DiD partial-ID proposal, \texttt{pid\_did\_anticipation\_bounded/v1}, gives support-function intervals for bounded anticipation boxes.
The present proposal differs from all of these: its kernel is a covariance-whitened Honest-DiD breakdown frontier for a chosen event-study estimator, with the phase boundaries expressed through the smoothness-bias kernel rather than through history-cell contamination or anticipation boxes.

\section{Formal setup}
Let \(\widehat\beta=(\widehat\beta_{pre}^\transpose,\widehat\beta_{post}^\transpose)^\transpose\in\R^{T_{pre}+T_{post}}\) be an event-study coefficient vector with covariance matrix \(\Sigma\).
Partition \(\Sigma\) conformably and write \(\Sigma_{post}\) for the post-period block.
The population event-study coefficient decomposes as
\[
  \beta=\tau+\delta,\qquad \tau_{pre}=0,\qquad \theta=L\tau_{post}\in\R^r,
\]
where \(\delta\) is the untreated trend violation and \(L\in\R^{r\times T_{post}}\) is a known loading matrix for the dynamic ATT vector.
The null of interest is \(\theta=0\).
The observed post-period point estimate is \(\widehat\theta=L\widehat\beta_{post}\), and its covariance is \(V=L\Sigma_{post}L^\transpose\).

Let \(D_2\) be the second-difference operator on the ordered pre/post event-time grid.
Let \(R_{pre}\) select the pre-period restrictions and \(R_{post}\) select the post-period coordinates.
The quadratic Honest-DiD descendant used here fixes the observed pretrend deviation at \(\delta_{pre}=\widehat\beta_{pre}\), chooses the minimum-energy extrapolation \(\delta^0\) satisfying that pre-period match, and writes every admissible post-period deviation as
\[
  \delta_{post}=\delta^0_{post}+S u,\qquad \|u\|_2\le M.
\]
The matrix \(S\in\R^{T_{post}\times d}\) is the observable post-bias sensitivity matrix induced by the second-difference budget after eliminating the pre-period equality constraints.
The corresponding possible bias in the target is \(L\delta^0_{post}+M L S u\).
After subtracting the baseline extrapolated bias, define
\[
  \widetilde\theta=\widehat\theta-L\delta^0_{post},\qquad
  q=V^{-1/2}\widetilde\theta,\qquad
  K=V^{-1/2}L S.
\]
Let \(c_\alpha\) be the critical radius for the chosen \(1-\alpha\) Gaussian confidence ellipsoid for the \(r\)-dimensional target.
For a budget \(M\), the covariance-whitened robust confidence set contains zero exactly when
\[
  d(M):=\inf_{\|u\|_2\le1}\|q-MKu\|_2\le c_\alpha.
\]
For a unit projection direction \(v\in\R^r\), define the directional statistic
\[
  T_M(v)=\inf_{\|u\|_2\le1}|v^\transpose(q-MKu)|.
\]
The direction \(v\) rejects zero at budget \(M\) when \(T_M(v)>c_\alpha\).
The active rejecting-direction set is
\[
  \mathcal U(M)=\{v\in\R^r:\|v\|_2=1,\ T_M(v)>c_\alpha\}.
\]
Let \(\sigma_{\max}(K)\) be the largest singular value and \(\sigma_{\min}^+(K)\) the smallest positive singular value of \(K\), with \(\sigma_{\min}^+(K)=+\infty\) when \(K=0\).
For staggered aggregation, let \(A\) map cohort-period ATT components and cohort-period trend-deviation components into the reported event-study coefficient vector.
The staggered Honest-DiD kernel is \(K_A=V^{-1/2}L A S_A\), where \(S_A\) is the second-difference sensitivity matrix before aggregation.

\begin{verbatim}
qid = panel_honest_did_phase
specialization = v1
p = finite event-study memory with pre-period length T_pre >= 2 and post-period
  target dimension r >= 1; the smoothness operator uses second differences
  across the ordered pre/post event-time grid.
assignment = staggered or non-staggered DiD event-study input summarized by
  the asymptotically Gaussian coefficient vector beta_hat =
  (beta_hat_pre, beta_hat_post), covariance matrix Sigma, and a fixed
  post-period loading matrix L selecting the dynamic ATT vector theta =
  L tau_post.  Cohort aggregation is allowed through a known linear map A.
target = robust zero-exclusion threshold for theta under a quadratic
  Honest-DiD smoothness budget M: the smallest M at which the robust
  confidence set for theta contains 0, together with the lower and upper
  phase boundaries M_star_lo and M_star_hi for directional refutability.
regression = event-study or modern staggered-DiD coefficient estimator whose
  output is beta_hat and Sigma; the baseline decomposition is
  beta = tau + delta with tau_pre = 0, theta = L tau_post, and delta constrained
  by the pretrend-matching and second-difference budget below.  The proposed
  closed form is for the covariance-whitened ellipsoidal descendant of the
  Rambachan-Roth smoothness set, not for every polyhedral l_infty variant.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Gaussian event-study input]\label{ass:gaussian-input}
The estimator supplies \(\widehat\beta\) and a positive semidefinite covariance matrix \(\Sigma\), and the target covariance \(V=L\Sigma_{post}L^\transpose\) is positive definite on the reported target space \(\R^r\).
\end{assumption}

\begin{assumption}[Event-study causal decomposition]\label{ass:decomposition}
The population coefficient decomposes as \(\beta=\tau+\delta\), with \(\tau_{pre}=0\), \(\theta=L\tau_{post}\), and the null hypothesis \(\theta=0\).
\end{assumption}

\begin{assumption}[Pretrend match]\label{ass:pretrend-match}
For the sensitivity calculation, admissible trend deviations satisfy \(\delta_{pre}=\widehat\beta_{pre}\), so the only unknown violation component entering the target is \(\delta_{post}\).
\end{assumption}

\begin{assumption}[Quadratic second-difference budget]\label{ass:quadratic-budget}
After imposing the pretrend match, the admissible post-period deviations are exactly
\(\delta_{post}=\delta^0_{post}+S u\) with \(\|u\|_2\le M\), where \(\delta^0_{post}\) and \(S\) are the minimum-energy extrapolation and sensitivity matrix induced by the second-difference operator \(D_2\).
\end{assumption}

\begin{assumption}[Honest critical radius]\label{ass:critical-radius}
The robust \(1-\alpha\) confidence decision for the \(r\)-dimensional target uses the covariance-whitened Gaussian critical radius \(c_\alpha\), and zero is included in \(CI(M)\) if and only if \(d(M)\le c_\alpha\).
\end{assumption}

\begin{assumption}[Regular projection directions]\label{ass:regular-directions}
Directional statements range over unit vectors \(v\in\R^r\) with nonzero projected sensitivity \(\|K^\transpose v\|_2>0\), unless explicitly stated otherwise.
\end{assumption}

\begin{assumption}[Staggered aggregation map]\label{ass:aggregation-map}
For staggered event-study inputs, cohort-period treatment-effect and trend-deviation components enter the reported event-study coefficient through a known linear aggregation map \(A\), and the covariance matrix \(\Sigma\) is the covariance of the aggregated coefficient vector.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: deterministic ellipsoid zero-crossing dictionary]\label{thm:ellipsoid-dictionary}
Under Assumptions~\ref{ass:gaussian-input}--\ref{ass:critical-radius}, the covariance-whitened robust confidence set contains zero at budget \(M\) if and only if
\[
  d(M)=\inf_{\|u\|_2\le1}\|q-MKu\|_2\le c_\alpha.
\]
Moreover, for each unit direction \(v\), zero is directionally rejected at \(M\) if and only if
\[
  T_M(v)=\max\{|v^\transpose q|-M\|K^\transpose v\|_2,0\}>c_\alpha.
\]
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is routine convex duality, not the flagship novelty; the gap to \citet{rambachan2023parallel} and \citet{andrews2023linear} is only organizational, namely isolating the exact ellipsoid dictionary needed before proving a symbolic phase transition.
(b) It advances the HonestDiD workflow by giving the reviewer and Stage 0 a precise target: the empirical breakdown plot is the scalar function \(d(M)\), and the active directions are the vectors \(v\) with \(T_M(v)>c_\alpha\).

\begin{conjecture}[Conjecture 1: singular-value Honest-DiD phase transition (NOT YET PROVED)]\label{conj:svd-phase}
Under Assumptions~\ref{ass:gaussian-input}--\ref{ass:regular-directions}, suppose \(K\) has full row rank on the reported target space.
There exist observable thresholds \(M_\star^{lo}\le M_\star^{hi}\), expressible from \(q\) and the singular system of \(K\), such that:
\[
  M_\star^{lo}=
  \inf\{M\ge0:d(M)\le c_\alpha\},\qquad
  M_\star^{hi}=
  \sup_{\|v\|_2=1,\ \|K^\transpose v\|_2>0}
  \frac{(|v^\transpose q|-c_\alpha)_+}{\|K^\transpose v\|_2}.
\]
Equivalently, \(M_\star^{lo}\) is the first global zero-crossing of \(CI(M)\), while \(M_\star^{hi}\) is the last budget at which any regular projection direction can still reject zero.
The following sharp phase diagram holds:
\[
\begin{array}{ll}
M<M_\star^{lo}: & 0\notin CI(M)\ \text{for every admissible deviation, and}\ \mathcal U(M)\neq\varnothing;\\[2mm]
M_\star^{lo}\le M<M_\star^{hi}: & 0\in CI(M)\ \text{globally, but}\ \mathcal U(M)\ \text{is a nonempty proper spherical cap};\\[2mm]
M\ge M_\star^{hi}: & \mathcal U(M)=\varnothing,\ \text{so zero is robustly irrefutable in every regular direction.}
\end{array}
\]
In the special case where \(q\) is aligned with a right singular direction of \(K^\transpose\), the two boundaries reduce to the closed forms
\[
  M_\star^{lo}=\frac{(\|q\|_2-c_\alpha)_+}{\sigma_{\max}(K)},\qquad
  M_\star^{hi}=\frac{(\|q\|_2-c_\alpha)_+}{\sigma_{\min}^+(K)}
\]
with the convention that \(M_\star^{hi}=+\infty\) if the aligned direction lies outside the row space of \(K\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest paper is \citet{rambachan2023parallel}: it constructs valid robust sets and reports breakdown values, but it does not state a two-threshold singular-value phase diagram or identify the active spherical cap of trend-deviation directions.
\citet{masten2020breakdown} names the frontier object, but not the Honest-DiD covariance-whitened kernel or its active-direction singular values.
(b) Resolving this conjecture would give users of \texttt{HonestDiD} a closed-form diagnostic: which pretrend-deviation direction overturns the result, and whether the reported breakdown value is a knife-edge direction or a fully irrefutable null.

\begin{conjecture}[Conjecture 2: staggered aggregation sharpness threshold (NOT YET PROVED)]\label{conj:aggregation}
Under Assumptions~\ref{ass:gaussian-input}--\ref{ass:aggregation-map}, replace \(K\) in Conjecture~\ref{conj:svd-phase} by \(K_A=V^{-1/2}L A S_A\).
Then the same three-regime phase diagram is sharp for the aggregated staggered Honest-DiD coefficient if and only if \(K_A\) has the same row space as the unaggregated cohort-period bias kernel after applying \(L\).
If the row spaces differ, the aggregate threshold is conservative exactly in the quotient directions in
\[
  \operatorname{Row}(L S_A)\big/\operatorname{Row}(L A S_A),
\]
and the gap in \(M_\star^{lo}\) is bounded below by the smallest nonzero singular value lost by the aggregation map.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{callaway2021multiple}, \citet{sunabraham2021eventstudy}, and \citet{borusyak2024eventstudy} clarify which staggered event-study coefficients should be estimated, while \citet{liu2025cohort} warns that aggregated Rambachan--Roth robust inference can be misleading when cohort composition changes.
The epsilon-gap is an operator-level necessary-and-sufficient condition for when the aggregate Honest-DiD breakdown threshold is sharp rather than conservative.
(b) The concrete consumer is cohort-anchored robust inference for staggered adoption: Conjecture~\ref{conj:aggregation} would tell researchers when they must compute Honest-DiD thresholds at the cohort-period level instead of from aggregated event-study coefficients.

\section{Sanity-check corollaries}
\begin{corollary}[Zero budget recovers the linear-pretrend point estimate]\label{cor:zero-budget}
Under Assumptions~\ref{ass:gaussian-input}--\ref{ass:critical-radius}, when \(M=0\), zero is excluded exactly when \(\|q\|_2>c_\alpha\).
Thus the proposal recovers the Rambachan--Roth \(M=0\) linear-extrapolation corner for the covariance-whitened target.
\end{corollary}

\begin{corollary}[Scalar target collapses to a single threshold]\label{cor:scalar}
Under Assumptions~\ref{ass:gaussian-input}--\ref{ass:regular-directions}, if \(r=1\) and \(K\neq0\), then \(\sigma_{\max}(K)=\sigma_{\min}^+(K)=\|K\|_2\) and the intermediate cap regime degenerates to the usual single breakdown value \((|q|-c_\alpha)_+/\|K\|_2\).
\end{corollary}

\begin{corollary}[No aggregation loss]\label{cor:no-aggregation-loss}
Under Assumption~\ref{ass:aggregation-map}, if \(A\) is the identity on the cohort-period bias coordinates used by \(L\), then \(K_A=K\) and Conjecture~\ref{conj:aggregation} reduces to Conjecture~\ref{conj:svd-phase}.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is finite-dimensional convex geometry.
First, derive Theorem~\ref{thm:ellipsoid-dictionary} by applying the support function of the Euclidean ball to the affine bias set \(q-MK B_2\), then use the separating-hyperplane theorem to equate zero inclusion with \(d(M)\le c_\alpha\).
Second, diagonalize \(K=U\Sigma_K W^\transpose\) and reduce \(d(M)\) to the distance from \(U^\transpose q\) to the axis-aligned ellipsoid \(M\Sigma_K B_2\), with separate algebra for full row rank, rank-deficient, and aligned-direction cases.
Third, for staggered aggregation, compare the row spaces of \(L S_A\) and \(L A S_A\) through singular values of the quotient map; the smallest explicit check should be a two-cohort, one-pre, two-post design where \(A\) either preserves or averages away one cohort-specific pretrend-curvature direction.

\section{Honest scope flags}
Theorem~\ref{thm:ellipsoid-dictionary} is proposed as routine and should be provable by convex duality.
Conjecture~\ref{conj:svd-phase} is the main novel kernel and is not yet proved; the exact closed form for non-aligned \(q\) may require replacing the displayed simple aligned formulas by a secular equation for distance to an ellipsoid.
Conjecture~\ref{conj:aggregation} is also open; the row-space quotient statement may need an additional regularity condition excluding nearly singular covariance directions.
This v1 deliberately uses the covariance-whitened quadratic descendant of Honest-DiD, not the full Rambachan--Roth polyhedral \(\ell_\infty\) second-difference class.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft centered on the covariance-whitened Honest-DiD singular-value phase transition; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Andrews, Roth, and Pakes(2023)]{andrews2023linear}
Andrews, I., J. Roth, and A. Pakes (2023).
Inference for linear conditional moment inequalities.
\emph{Review of Economic Studies} 90(6), 2763--2791.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{borusyak2024eventstudy}
Borusyak, K., X. Jaravel, and J. Spiess (2024).
Revisiting event-study designs: Robust and efficient estimation.
\emph{Review of Economic Studies} 91(6), 3253--3285.

\bibitem[Callaway and Sant'Anna(2021)]{callaway2021multiple}
Callaway, B. and P. H. C. Sant'Anna (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics} 225(2), 200--230.

\bibitem[Kwon and Roth(2024)]{kwon2024bayes}
Kwon, S. and J. Roth (2024).
(Empirical) Bayes approaches to parallel trends.
\emph{AEA Papers and Proceedings} 114, 629--633.

\bibitem[Liu(2025)]{liu2025cohort}
Liu, Z. (2025).
Cohort-anchored robust inference for event-study with staggered adoption.
\emph{arXiv:2509.01829}.

\bibitem[Manski and Pepper(2018)]{manski2018bounded}
Manski, C. F. and J. V. Pepper (2018).
How do right-to-carry laws affect crime rates? Coping with ambiguity using bounded-variation assumptions.
\emph{Review of Economics and Statistics} 100(2), 232--244.

\bibitem[Masten and Poirier(2020)]{masten2020breakdown}
Masten, M. A. and A. Poirier (2020).
Inference on breakdown frontiers.
\emph{Quantitative Economics} 11(1), 41--111.

\bibitem[Rambachan and Roth(2023)]{rambachan2023parallel}
Rambachan, A. and J. Roth (2023).
A more credible approach to parallel trends.
\emph{Review of Economic Studies} 90(5), 2555--2591.

\bibitem[Roth(2022)]{roth2022pretest}
Roth, J. (2022).
Pretest with caution: Event-study estimates after testing for parallel trends.
\emph{American Economic Review: Insights} 4(3), 305--322.

\bibitem[Roth and Sant'Anna(2023)]{rothsantanna2023efficient}
Roth, J. and P. H. C. Sant'Anna (2023).
Efficient estimation for staggered rollout designs.
\emph{Journal of Political Economy Microeconomics} 1(4), 669--709.

\bibitem[Sun and Abraham(2021)]{sunabraham2021eventstudy}
Sun, L. and S. Abraham (2021).
Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\emph{Journal of Econometrics} 225(2), 175--199.

\bibitem[Wing, Freedman, and Hollingsworth(2024)]{wing2024stacked}
Wing, C., S. Freedman, and A. Hollingsworth (2024).
Stacked difference-in-differences.
\emph{NBER Working Paper No. 32054}.
\end{thebibliography}

\end{document}
