% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orth\_uniform, specialization=v2
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_dml\_orth\_uniform} / \texttt{v2}%
  \\ \large\textit{A sharp studentization-report frontier for DML, LRO, and ADML ATE inference}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Exact-identification anchor, free-form qid.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},\text{target estimand},\text{identifying assumptions})
\]
with the following meanings: \texttt{qid}=\texttt{eid\_dml\_orth\_uniform};
\texttt{specialization}=\texttt{v2}; graph/SWIG is the binary-treatment
unconfoundedness model \(Y(d)\perp D\mid X\), \(d\in\{0,1\}\), with observed
law of \(O=(Y,D,X)\); treatment is the binary exposure \(D\); target estimand
is the population ATE \(\theta_0=\E[Y(1)-Y(0)]\); identifying assumptions are
consistency, conditional unconfoundedness, square integrability, and local
overlap sequences allowing the ATE Riesz representer
\(\alpha_0(D,X)=D/e_0(X)-(1-D)/(1-e_0(X))\) to be stable or weakly unstable.
The objects compared are the exact published studentization reports attached
to the DML AIPW score of \citet{ChernozhukovEtAl2018ECTJ}, the
ATE-specialized locally robust GMM report of
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}, and the automatic
Riesz/debiased report of \citet{ChernozhukovNeweySingh2022ADML}.

\begin{abstract}
This proposal asks whether three leading DML-style ATE procedures that share
the canonical efficient influence function can nevertheless produce uniformly
different studentized Wald limits once their exact published variance reports
are compared under local nuisance and weak-overlap sequences.  The first
result is a guardrail rather than a novelty claim: any comparison that replaces
the three reports by the same population EIF variance map necessarily
collapses to first-order equivalence and cannot deliver a strict
DML--LRO--ADML ordering.  The flagship
conjecture is a positive report-level frontier: after deriving the three exact
binary-ATE variance-score summands, their pairwise report gaps are governed by
an observable, scale-invariant generalized spectral kernel whose weak-overlap
growth defines the sharp exponent \(\rho_\star\).  The conjectured boundary is
\(r_g+r_\alpha>\rho_\star\) for common studentized inference and
\(r_g+r_\alpha\le \rho_\star\) for strict report separation on an open class
of laws.  Resolving this would tell applied users whether DML, locally robust
GMM, and automatic debiasing are interchangeable for Wald inference, or only
for point estimation and canonical first-order influence functions.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
DML, locally robust semiparametric GMM, and automatic debiased machine learning
are now standard routes to ATE inference under unconfoundedness.  For the same
ATE law they are usually described through the same canonical AIPW influence
function, but practitioners use estimator-specific variance reports and
software-level studentization rules.  The methodological question is whether
``same EIF'' really means ``same Wald inference'' uniformly over weak
nuisance and weak-overlap designs.

\paragraph{The main finding (proposed).}
The proposal has a guardrail theorem and a flagship conjecture.  The guardrail
theorem records the already-known collapse: a strict first-order variance
ordering is impossible if the three procedures are compared only through the
common canonical EIF variance.
Conjecture 1, the novel kernel, says that a strict boundary reappears at the
studentization-report level: the exact DML empirical AIPW variance, LRO
first-step-adjusted sandwich variance, and ADML Riesz robust variance have a
common Wald limit if and only if \(r_g+r_\alpha>\rho_\star\), where
\(\rho_\star\) is computed from a normalized Rayleigh quotient comparing the
observable covariance kernel for outcome-regression/Riesz perturbations to the
chosen nuisance-direction norm.

\paragraph{What is new.}
\citet{ChernozhukovEtAl2018ECTJ} gives sufficient product-rate conditions for
orthogonal-score inference, \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
constructs locally robust moments and misspecification-robust standard errors,
and \citet{ChernozhukovNeweySingh2022ADML} automates debiasing and robust
standard errors through Riesz representations.  None of these papers supplies
a three-way necessary-and-sufficient comparison of the exact ATE variance
reports under one normalization.  The epsilon-gap is the report derivative:
the proposal targets pairwise matrices \(\Gamma_{\mathrm{DML},\mathrm{LRO}}\),
\(\Gamma_{\mathrm{DML},\mathrm{ADML}}\), and
\(\Gamma_{\mathrm{LRO},\mathrm{ADML}}\) that vanish for the population EIF
map but may be nonzero for the published studentization reports.

\paragraph{How it positions in the literature.}
This is an exact-identification ATE proposal, not a panel or partial-ID
proposal.  The identifying model is the standard binary-treatment
unconfoundedness model, while the frontier sits in semiparametric inference
for exact-ID targets.  It is closest to the active DML/Riesz/locally robust
thread opened by \citet{ChernozhukovEtAl2018ECTJ},
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO},
\citet{ChernozhukovNeweySingh2022ADML}, and
\citet{ChernozhukovNeweySingh2022RR}; it also uses the recent warnings from
\citet{DukesVansteelandtWhitney2024JMLR} and
\citet{VanDerLaanLuedtkeCarone2024CDML} that one-good-nuisance and
calibrated regimes are subtler than a single product-rate slogan.  For weak
overlap, it is adjacent to \citet{Rothe2017LimitedOverlapCI},
\citet{HongLeungLi2020LimitedOverlap}, \citet{HeilerKazak2021ExtremePS}, and
\citet{MaSantAnnaSasakiUra2026WeakOverlapDR}, but those papers study valid
inference, slow rates, stable laws, trimming, or bias correction rather than a
three-report DML--LRO--ADML equivalence frontier.

\paragraph{Implications for the community.}
The concrete downstream consumer is the weak-overlap ATE inference problem
studied by \citet{Dorn2025WeakOverlapDR}: if the conjecture is true, thresholded
or regularized doubly robust \(t\)-statistics should report which variance
rule they use, because point-estimate equivalence need not imply
studentized-law equivalence.

\paragraph{How research benefits from the conclusion.}
Researchers should check and report the variance-report normalization, not
only the orthogonal score, whenever overlap or Riesz instability makes
\(\rho_\star\) close to the product-rate exponent.

\section{Related work}
\citet{ChernozhukovEtAl2018ECTJ} is the baseline DML paper: it supplies the
cross-fit Neyman-orthogonal ATE score and product-rate sufficient conditions
whose sharp report-level frontier is studied here.  \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
is the LRO comparator: it gives the broad locally robust GMM construction and
the sandwich logic whose ATE specialization must be pinned down.  \citet{ChernozhukovNeweySingh2022ADML}
is the ADML comparator: it automates debiasing through Riesz representations
and gives robust standard errors, but not a closed-form three-way ATE
studentization comparison.  \citet{ChernozhukovNeweySingh2022RR} is the
regularized-Riesz bridge: it documents weak double-sparsity robustness and
Riesz instability, both of which motivate a spectral exponent rather than a
fixed-overlap product-rate boundary.  \citet{Newey1994Econometrica} provides
the semiparametric variance benchmark: for a regular estimator with the same
canonical gradient, first-order population variance equality is forced.
\citet{RobinsRotnitzkyZhao1994JASA} is the augmented-IPW ancestor for the
canonical ATE influence function and double robustness.  \citet{AtheyImbensWager2018JRSSB}
is relevant because approximate residual balancing highlights that weak
overlap makes ATE inference sensitive to weighting and extrapolation choices.
\citet{DukesVansteelandtWhitney2024JMLR} shows that doubly robust DML inference
can lose regularity when only one nuisance is consistently estimated, so a
sharp validity partition cannot be replaced by a slogan.  \citet{VanDerLaanLuedtkeCarone2024CDML}
proposes calibrated DML to recover doubly robust asymptotic linearity, making
calibration an adjacent route to one-good-nuisance inference rather than a
three-estimator report comparison.  \citet{Dorn2025WeakOverlapDR} is the
weak-overlap consumer whose thresholded doubly robust \(t\)-statistics would
benefit from knowing whether estimator-specific studentization rules separate.
\citet{Rothe2017LimitedOverlapCI} shows that limited overlap can make
traditional ATE confidence intervals unreliable because local effective sample
sizes, not only total sample size, drive coverage.  \citet{HongLeungLi2020LimitedOverlap}
models finite-population treatment-effect inference with propensities drifting
to zero or one and derives slower-rate asymptotics under common randomization
schemes.  \citet{HeilerKazak2021ExtremePS} studies irregular identification
with many extreme propensity scores and alpha-stable limits for IPW and
doubly robust estimators.  \citet{MaSantAnnaSasakiUra2026WeakOverlapDR}
constructs trim-and-bias-correct doubly robust estimators under weak overlap;
it is close in motivation but not a comparison of DML, LRO, and ADML
studentization reports under a common ATE law.
\citet{BrunsSmithDukesFellerOgburn2024ABW} and \citet{BrunsSmith2026RieszApproaches}
are adjacent Riesz-equivalence papers: they compare augmented balancing and
direct Riesz constructions, showing that exact equivalence can hold for some
regularized linear/RKHS cases and fail for other ML classes.

In-repo prior art is the downgraded \texttt{eid\_dml\_orth\_uniform}/v1 entry:
its banking note records that the population variance maps coincide at the
truth with identical Riesz-direction derivatives, and its reviewer requested
exact published variance summands before any renewed frontier claim.  The
\texttt{doc/API.md} ExactID catalogue is currently a seed catalogue for
\texttt{eid\_*} qids rather than a bank of completed DML/LRO/ADML theorems, so
there is no in-catalogue theorem that already gives the report-level spectral
boundary proposed here.

\section{Formal setup}
Let \(O=(Y,D,X)\sim P_n\), where \(D\in\{0,1\}\).  Write
\(e_n(x)=\Pr_n(D=1\mid X=x)\), \(\mu_{d,n}(x)=\E_n[Y\mid D=d,X=x]\), and
\[
\theta_n=\E_n[\mu_{1,n}(X)-\mu_{0,n}(X)]
\]
for the identified ATE under consistency and conditional unconfoundedness.
The ATE Riesz representer is
\[
\alpha_n(D,X)=\frac{D}{e_n(X)}-\frac{1-D}{1-e_n(X)},
\]
and the canonical efficient influence function is
\[
\phi_n(O)=\mu_{1,n}(X)-\mu_{0,n}(X)-\theta_n
          +\alpha_n(D,X)\{Y-\mu_{D,n}(X)\}.
\]
Let \(m\in\mathcal M=\{\mathrm{DML},\mathrm{LRO},\mathrm{ADML}\}\).  For a
candidate nuisance tuple \(\eta=(\mu_0,\mu_1,e)\), write
\(\alpha_e(D,X)=D/e(X)-(1-D)/(1-e(X))\) and set
\[
\psi(O;\theta,\eta)=\mu_1(X)-\mu_0(X)-\theta+\alpha_e(D,X)\{Y-\mu_D(X)\}.
\]
The DML report summand is
\[
s_{\mathrm{DML}}(O;\theta,\eta)
  =\{\psi(O;\theta,\eta)-P_n\psi(\cdot;\theta,\eta)\}^2.
\]
Fix a published-rule first-step score vector
\[
q^{\mathrm{pub}}_n(O;\eta)\in\R^{K_n},\qquad
\Omega_n=P_n[q^{\mathrm{pub}}_n q^{\mathrm{pub}\transpose}_n],
\]
whose coordinates are the finite-dimensional score equations used by the
published variance report to estimate the outcome-regression and
propensity/Riesz nuisances.  This proposal locks the following common
population normalization of the three reports.
\begin{itemize}[leftmargin=*]
\item DML source object: the cross-fit AIPW score and empirical variance in
\citet{ChernozhukovEtAl2018ECTJ}; locked population report:
\[
V_{\mathrm{DML},n}(\eta)=P_n\{\psi-P_n\psi\}^2.
\]
\item LRO source object: the scalar locally robust GMM sandwich in
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}; locked population
report:
\[
V_{\mathrm{LRO},A,n}(\eta)=P_n h_A(O;\theta_n,\eta)^2.
\]
\item ADML source object: the automatic Riesz/debiased robust variance in
\citet{ChernozhukovNeweySingh2022ADML}; locked population report:
\[
V_{\mathrm{ADML},n}(\eta)=P_n\{\psi-c_{\mathrm{AD},n}^{\transpose}
q^{\mathrm{pub}}_n\}^2.
\]
\end{itemize}
On finite support with cells \(x_1,\ldots,x_J\), the locked diagnostic choice is
\[
q^{\mathrm{pub}}_n(O;\eta)=
\bigl((1-D)\one\{X=x_j\}(Y-\mu_0(x_j)),
D\one\{X=x_j\}(Y-\mu_1(x_j)),
\one\{X=x_j\}(D-e(x_j))\bigr)_{j=1}^J,
\]
so the first-step score dimension is \(K_n=3J\); in a sieve version the same display is replaced by the chosen
basis coordinates.  A report is therefore exact in this proposal only after
the triple
\((q^{\mathrm{pub}}_n,L_{A,n},\Omega_n)\) is fixed; changing this triple is a
different report rule, not a proof of the same conjecture.

The LRO report is locked to scalar ATE-GMM moments
\[
h_A(O;\theta,\eta)=
\psi(O;\theta,\eta)-c_{L,A,n}^{\transpose}q^{\mathrm{pub}}_n(O;\eta),
\]
where \(A_n=(1,-c_{L,A,n}^{\transpose})\in\R^{1\times(1+K_n)}\) is the
published scalar ATE normalization and \(G_{A,n}=P_n[\partial_\theta
h_A(O;\theta_n,\eta_n)]=-1\).  The finite-dimensional LRO normalization is an
operator \(L_{A,n}\in\R^{d_A\times K_n}\) selecting the first-step score
directions used in the scalar sandwich.  Its coefficient space is
\[
\mathcal C_{L,A,n}=\operatorname{range}(L_{A,n}^{\transpose})\subseteq\R^{K_n}.
\]
The fixed published-rule LRO report audited in Conjecture
\ref{conj:spectral-frontier} is the scalar ATE locally robust sandwich
specialization obtained by applying the LRO first-step-adjusted GMM formula to
the AIPW ATE moment and the score vector \(q^{\mathrm{pub}}_n\) above, with
the first-step sensitivity selector locked, in the finite-support diagnostic,
to
\[
L_{A^{\mathrm{pub}},n}
=
\begin{bmatrix}
I_J&0&0\\
0&I_J&0
\end{bmatrix}
\in\R^{2J\times 3J}.
\]
Thus the audited LRO report adjusts the scalar ATE sandwich by the two
outcome-regression score blocks used in the locally robust moment
construction, while the ADML report below uses the full automatic
Riesz/debiasing normal equation over all \(3J\) score coordinates.  In a sieve
version the same convention is the coordinate projection onto the two
outcome-regression first-step score blocks.  If an implementation instead
uses \(L_{A,n}=I_{K_n}\), it belongs to the equivalence class in Conjecture
\ref{conj:lro-class} and is not the fixed LRO report audited for strict
separation.
The first-step-adjustment coefficient is the unique \(\Omega_n\)-projection of
the raw AIPW score onto this space:
\[
c_{L,A,n}
=\arg\min_{c\in\mathcal C_{L,A,n}}P_n\{\psi(O;\theta_n,\eta_n)-
c^{\transpose}q^{\mathrm{pub}}_n(O;\eta_n)\}^2
=L_{A,n}^{\transpose}(L_{A,n}\Omega_nL_{A,n}^{\transpose})^\dagger
L_{A,n}P_n[q^{\mathrm{pub}}_n\psi_n],
\]
where \(\psi_n=\psi(O;\theta_n,\eta_n)\) and \({}^\dagger\) denotes the
Moore--Penrose inverse after redundant score directions are dropped.  The report
summand is
\[
s_{\mathrm{LRO},A}(O;\theta,\eta)
  =G_{A,n}^{-2}h_A(O;\theta,\eta)^2
\]
and is read as a scalar sandwich report after projecting onto the ATE coordinate.
The ADML report summand is
\[
s_{\mathrm{ADML}}(O;\theta,\eta)
  =\{\psi(O;\theta,\eta)-c_{\mathrm{AD},n}^{\transpose}
       q^{\mathrm{pub}}_n(O;\eta)\}^2,
\]
where \(c_{\mathrm{AD},n}\in\R^{K_n}\) is the automatic Riesz/debiasing
coefficient obtained by the full normal equation
\[
c_{\mathrm{AD},n}
=\arg\min_{c\in\R^{K_n}}P_n\{\psi(O;\theta_n,\eta_n)-
c^{\transpose}q^{\mathrm{pub}}_n(O;\eta_n)\}^2
=\Omega_n^\dagger P_n[q^{\mathrm{pub}}_n\psi_n].
\]
Thus the ADML random-variable correction is fixed as
\(\kappa_{\mathrm{AD},n}(O;\eta)=-c_{\mathrm{AD},n}^{\transpose}
q^{\mathrm{pub}}_n(O;\eta)\).  The
coefficient notation below sets \(c_{\mathrm{DML},n}=0\),
\(c_{\mathrm{LRO},n}=c_{L,A^{\mathrm{pub}},n}\), and
\(c_{\mathrm{ADML},n}=c_{\mathrm{AD},n}\).
The population report maps are \(V_{m,n}(\eta)=P_n s_{m}(O;\theta_n,\eta)\), with
\(V_{\mathrm{LRO},n}\) meaning \(V_{\mathrm{LRO},A,n}\) for an \(A_n\) in the
locked LRO class below.  Local nuisance perturbations are
\(\delta\mu_{d,n}=n^{-r_g}u_{d,n}\) and the induced Riesz perturbation
\(\delta\alpha_{e,n}=n^{-r_\alpha}v_n\), with
\(u_n=(u_{0,n},u_{1,n})\).  The
report-difference expansion, when it exists, is written
\[
V_{m,n}(\eta_n+\delta\eta_n)-V_{\ell,n}(\eta_n+\delta\eta_n)
= n^{-(r_g+r_\alpha)}
  \langle z_n,\Gamma_{m\ell,n}z_n\rangle + o(n^{-(r_g+r_\alpha)}),
\]
where \(z_n=(u_n,v_n)\) and the symmetric matrix or compact operator
\(\Gamma_{m\ell,n}\) is obtained by the mixed Gateaux derivative of the
displayed summands with respect to \((u_n,v_n)\).  Specifically, with
\(\eta_{t,s}=(\mu_{0,n}+tu_{0,n},\mu_{1,n}+tu_{1,n},
\alpha_n+sv_n)\),
\[
\langle z_n,\Gamma_{m\ell,n}z_n\rangle
=\left.
\frac{\partial^2}{\partial t\,\partial s}
\{V_{m,n}(\eta_{t,s})-V_{\ell,n}(\eta_{t,s})\}
\right|_{t=s=0}.
\]
Let \(V^{\mathrm{EIF}}_n=P_n\phi_n^2\).  The object
\(\mathcal V_{m,n}(z)\) used below is the local report-ratio lower bound
\[
\mathcal V_{m,n}(z)
=\liminf_{n\to\infty}
\frac{V_{m,n}(\eta_n+\delta\eta_n(z))}{V^{\mathrm{EIF}}_n};
\]
it is a variance-report ratio for the Wald interval, not the variance of the
studentized statistic itself and not a new semiparametric efficiency bound.
The observable covariance kernel \(\mathsf K_n\) is the covariance matrix of the
finite-dimensional score vector formed by the outcome residual
\(\varepsilon_n=Y-\mu_{D,n}(X)\), the Riesz term \(\alpha_n(D,X)\), and the
chosen basis coordinates for \(u_n\) and \(v_n\).  The nuisance-direction
metric \(S_n\) is the block \(L^2(P_n)\) Gram matrix for the same coordinates.
Define the scale-invariant generalized weak-overlap index
\[
\chi_n=\inf_{z\ne 0}\frac{z^{\transpose}\mathsf K_nz}{z^{\transpose}S_nz},
\qquad
\omega_K=\limsup_{n\to\infty}\frac{-\log \chi_n}{\log n},
\qquad
\rho_\star=\frac{1+\omega_K}{2}.
\]
With fixed overlap and a nondegenerate finite support, \(\chi_n\) is bounded
away from zero, \(\omega_K=0\), and \(\rho_\star=1/2\), the usual
product-rate exponent.  With weak overlap, \(\chi_n\asymp n^{-\omega}\) gives
\(\rho_\star=(1+\omega)/2\), separating shrinking-overlap sequences from
fixed-overlap bounded-eigenvalue designs.

\begin{quote}
\begin{verbatim}
Locked parameters:
qid = eid_dml_orth_uniform
specialization = v2
graph/SWIG = binary-treatment unconfoundedness model Y(d) independent of D given X
treatment = binary D
target estimand = theta_0 = E[Y(1)-Y(0)]
identifying assumptions = consistency, conditional unconfoundedness,
  square integrability, and local overlap/Riesz stability or weak instability
compared reports = exact DML AIPW, LRO ATE-GMM sandwich, and ADML Riesz robust variance reports
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[ATE identification]\label{ass:ate-id}
For each \(n\), \(Y=DY(1)+(1-D)Y(0)\), \(Y(d)\perp D\mid X\) for
\(d\in\{0,1\}\), and the conditional means \(\mu_{d,n}\) are square
integrable.  The ATE is \(\theta_n=\E_n[Y(1)-Y(0)]\).
\end{assumption}

\begin{assumption}[Local overlap and Riesz scale]\label{ass:overlap}
The propensity satisfies \(0<e_n(X)<1\) almost surely.  The Riesz representer
\(\alpha_n\) is square integrable for every \(n\), but
\(\E_n[\alpha_n(D,X)^2]\) and the generalized index \(\chi_n\) may vary with
\(n\).  The metric matrix \(S_n\) is positive definite on the chosen
nuisance-direction sieve, and \(\Omega_n\) is positive definite on the chosen
first-step score coordinates after dropping redundant coordinates.
\end{assumption}

\begin{assumption}[Exact report definitions]\label{ass:reports}
The report maps \(V_{\mathrm{DML},n}\), \(V_{\mathrm{LRO},n}\), and
\(V_{\mathrm{ADML},n}\) are the population means of the summands
\(s_{\mathrm{DML}}\), \(s_{\mathrm{LRO},A}\), and \(s_{\mathrm{ADML}}\)
defined in Section 3.  The DML report is the centered empirical AIPW variance.
The LRO report is the scalar ATE coordinate of the first-step-adjusted
sandwich variance with \(A_n=(1,-c_{L,A,n}^{\transpose})\),
\(L_{A,n}\in\R^{d_A\times K_n}\), and
\[
c_{L,A,n}
=L_{A,n}^{\transpose}(L_{A,n}\Omega_nL_{A,n}^{\transpose})^\dagger
L_{A,n}P_n[q^{\mathrm{pub}}_n\psi_n].
\]
For the fixed LRO report used in Conjecture
\ref{conj:spectral-frontier}, the published-rule selector is
\[
L_{A^{\mathrm{pub}},n}=
\begin{bmatrix}
I_J&0&0\\
0&I_J&0
\end{bmatrix}
\]
under the finite-support ordering
\((q_{0,1:J},q_{1,1:J},q_{e,1:J})\), and is the analogous projection onto the
two outcome-regression first-step score blocks in a sieve implementation.
The ADML report is the Riesz-robust variance after the automatic correction
\(\kappa_{\mathrm{AD},n}=-c_{\mathrm{AD},n}^{\transpose}q^{\mathrm{pub}}_n\),
where
\[
c_{\mathrm{AD},n}=\Omega_n^\dagger P_n[q^{\mathrm{pub}}_n\psi_n].
\]
The dimensions are fixed by \(q^{\mathrm{pub}}_n\in\R^{K_n}\),
\(c_{L,A,n},c_{\mathrm{AD},n}\in\R^{K_n}\),
\(L_{A,n}\in\R^{d_A\times K_n}\), and
\(A_n\in\R^{1\times(1+K_n)}\).
\end{assumption}

\begin{assumption}[Locked LRO normalization class]\label{ass:lro-class}
The LRO normalization domain is
\[
\mathcal A_n=\{(A_n,L_{A,n}): A_n=(1,-c_{L,A,n}^{\transpose}),\
L_{A,n}\in\R^{d_A\times K_n},\
G_{A,n}=-1,\ P_n h_A(O;\theta_n,\eta_n)=0,\ 
h_A\text{ is Neyman-orthogonal at }\eta_n,\ 
c_{L,A,n}\text{ is given by Assumption \ref{ass:reports}}\}.
\]
Conjecture \ref{conj:spectral-frontier} uses one fixed published ATE
normalization \((A_n^{\mathrm{pub}},L_{A^{\mathrm{pub}},n})\in\mathcal A_n\).
For any \(A\), define the closed coefficient subspace
\[
\mathcal C_{L,A,n}=\operatorname{range}(L_{A,n}^{\transpose})
\]
with the inner product \(\langle a,b\rangle_{\Omega_n}=a^\transpose
\Omega_nb\).  Conjecture
\ref{conj:lro-class} quantifies over the whole class and defines the
subclass that is report-equivalent to ADML.
\end{assumption}

\begin{assumption}[Report-separating normalization for the frontier]\label{ass:lro-separated}
For the fixed \(A_n^{\mathrm{pub}}\) used in Conjecture
\ref{conj:spectral-frontier}, the automatic ADML coefficient is not contained
in the LRO coefficient space:
\[
c_{\mathrm{AD},n}\notin \mathcal C_{L,A^{\mathrm{pub}},n}.
\]
Equivalently, because \(c_{L,A^{\mathrm{pub}},n}\) is the
\(\Omega_n\)-orthogonal projection of \(c_{\mathrm{AD},n}\) onto
\(\mathcal C_{L,A^{\mathrm{pub}},n}\), the non-tautological separation premise
is \(c_{L,A^{\mathrm{pub}},n}\ne c_{\mathrm{AD},n}\).  This assumption is not
imposed in Conjecture
\ref{conj:lro-class}, whose purpose is to classify exactly when it fails.
\end{assumption}

\begin{assumption}[Common canonical EIF]\label{ass:eif}
At the true nuisance \(\eta_n=(\mu_{0,n},\mu_{1,n},e_n)\), all three
methods have influence function \(\phi_n\) for the target \(\theta_n\).
\end{assumption}

\begin{assumption}[Quadratic report expansion]\label{ass:quadratic}
For each pair \(m,\ell\in\mathcal M\), the difference between their report
maps has the expansion in Section 3 with a symmetric coefficient
\(\Gamma_{m\ell,n}\), uniformly over perturbation directions \(z_n=(u_n,v_n)\)
in the chosen finite-dimensional sieve with \(z_n^{\transpose}S_nz_n=1\).
\end{assumption}

\begin{assumption}[Observable spectral nondegeneracy]\label{ass:spectral}
The covariance kernel \(\mathsf K_n\) and metric \(S_n\) are consistently estimable
from the observed law, \(\chi_n>0\) for all large \(n\), and \(\omega_K\)
exists along the local sequence.  Pairwise report-gap signs are not assumed;
when a strict ordering is claimed below, it is derived from positive
generalized eigenvalue gaps of \((\Gamma_{m\ell,n},S_n)\) on the stated open
set of finite-support laws and perturbation directions.
\end{assumption}

\begin{assumption}[Finite-support audit design]\label{ass:finite-audit}
For the audit theorem only, \(X\) has finite support
\(\{x_1,\ldots,x_J\}\), \(q^{\mathrm{pub}}_n\) is the \(3J\)-coordinate cell
score vector from Section 3, and the perturbation sieve is cellwise constant
in the coordinates
\((u_{01},\ldots,u_{0J},u_{11},\ldots,u_{1J},v_1,\ldots,v_J)\).
\end{assumption}

\section{Main results}
\begin{proposition}[Guardrail: canonical-EIF equivalence]\label{prop:eif-no-go}
Under Assumptions \ref{ass:ate-id}, \ref{ass:overlap}, \ref{ass:reports},
\ref{ass:lro-class}, and \ref{ass:eif}, if
\[
V_{\mathrm{DML},n}(\eta_n)=V_{\mathrm{LRO},n}(\eta_n)
=V_{\mathrm{ADML},n}(\eta_n)=\E_n[\phi_n(O)^2]
\]
and the three studentizers are replaced by any uniformly consistent estimator
of \(\E_n[\phi_n(O)^2]\), then the studentized DML, LRO, and ADML Wald
statistics have the same first-order Gaussian limit whenever they are
asymptotically linear with influence function \(\phi_n\).  Consequently no
strict first-order variance ordering among the three named procedures can be
proved from the common population EIF variance map alone.
\end{proposition}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{Newey1994Econometrica},
\citet{ChernozhukovEtAl2018ECTJ}, and \citet{ChernozhukovNeweySingh2022ADML},
and the closest project artifact is the banked \texttt{eid\_dml\_orth\_uniform}/v1
note that population variance maps coincide at truth with identical
Riesz-direction derivatives.  This result is therefore not claimed as the
flagship novelty; it is an explicit guardrail documenting that the common-EIF
route is already exhausted.  (b) Recording this guardrail prevents the
\texttt{eid\_dml\_orth\_uniform}/v1 failure mode from recurring: the
downstream Stage 0 derivation must compare exact variance reports, not relabel
the canonical EIF variance.

\begin{conjecture}[Conjecture 1: spectral studentization-report frontier (NOT YET PROVED)]\label{conj:spectral-frontier}
Under Assumptions \ref{ass:ate-id}, \ref{ass:overlap}, \ref{ass:reports},
\ref{ass:lro-class}, \ref{ass:lro-separated}, \ref{ass:eif},
\ref{ass:quadratic}, and \ref{ass:spectral}, suppose the local
nuisance rates satisfy
\(\|\delta\mu_{0,n}\|_2+\|\delta\mu_{1,n}\|_2\asymp n^{-r_g}\) and
\(\|\delta\alpha_{e,n}\|_2\asymp n^{-r_\alpha}\).  Then the exact published DML,
the fixed published LRO normalization \(A_n^{\mathrm{pub}}\), and ADML
studentization reports are uniformly first-order equivalent if and only if
\[
r_g+r_\alpha>\rho_\star=\frac{1+\omega_K}{2}.
\]
If \(r_g+r_\alpha\le \rho_\star\), there is an open set of finite-support laws
and perturbation directions on which the generalized eigenvalue gaps of
\((\Gamma_{\mathrm{DML},\mathrm{LRO},n},S_n)\) and
\((\Gamma_{\mathrm{LRO},\mathrm{ADML},n},S_n)\) are positive and bounded away
from zero after the \(\chi_n\) normalization; on that open set the Wald
interval report-ratio lower bounds
\(\mathcal V_{m,n}(z)=\liminf V_{m,n}(\eta_n+\delta\eta_n(z))/V^{\mathrm{EIF}}_n\)
are strictly separated in the variance order
\[
\mathcal V_{\mathrm{ADML},n}
<\mathcal V_{\mathrm{LRO},n}
<\mathcal V_{\mathrm{DML},n},
\]
with the pairwise separation constants proportional to the nonzero spectral
gaps of
\(\Gamma_{\mathrm{DML},\mathrm{LRO},n}\) and
\(\Gamma_{\mathrm{LRO},\mathrm{ADML},n}\) in the generalized
\((\mathsf K_n,S_n)\)-geometry.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{ChernozhukovEtAl2018ECTJ} gives sufficient product-rate validity,
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} gives locally robust
GMM variance formulas, and \citet{ChernozhukovNeweySingh2022ADML} gives robust
Riesz standard errors, but none characterizes an iff exponent boundary for the
three exact reports under one binary-ATE normalization.  The epsilon-gap is
the scale-invariant threshold \(\rho_\star=(1+\omega_K)/2\): fixed-overlap
theory gives \(\rho_\star=1/2\), while weak-overlap/Riesz instability changes
it through the generalized eigenvalue decay \(\chi_n\).  The closest
weak-overlap comparators, \citet{Rothe2017LimitedOverlapCI},
\citet{HongLeungLi2020LimitedOverlap}, \citet{HeilerKazak2021ExtremePS}, and
\citet{MaSantAnnaSasakiUra2026WeakOverlapDR}, analyze robust intervals,
slow-rate randomization limits, stable-law inference, and trimmed DR
corrections, not an iff boundary among the three named report rules.  (b) The
consumer is \citet{Dorn2025WeakOverlapDR}: a true frontier would tell users of
weak-overlap doubly robust \(t\)-statistics when equal point-estimate behavior
still permits different studentized laws across named variance rules.

\begin{theorem}[Theorem 1: finite-support auditability of the report certificates]\label{thm:finite-audit}
Under Assumptions \ref{ass:ate-id}, \ref{ass:overlap}, \ref{ass:reports},
\ref{ass:lro-class}, \ref{ass:quadratic}, and \ref{ass:finite-audit}, with
\(\kappa_{\mathrm{AD},n}=-c_{\mathrm{AD},n}^{\transpose}
q^{\mathrm{pub}}_n\), each
coefficient \(\Gamma_{m\ell,n}\), the kernels \(\mathsf K_n,S_n\), and the exponent
\(\rho_\star\) reduce to explicit finite matrices as follows.  Let
\(\pi_j=P_n(X=x_j)\), \(p_j=e_n(x_j)\),
\(\sigma_{dj}^2=\operatorname{Var}_n(Y\mid D=d,X=x_j)\), and let the
cellwise direction vector be
\[
z=(u_{01},\ldots,u_{0J},u_{11},\ldots,u_{1J},v_1,\ldots,v_J)^\transpose.
\]
For \(a,b\) indexing these \(3J\) coordinates, the product-rate block of
\(\Gamma_{m\ell,n}\) has the following closed form.  Set
\(c_{\mathrm{DML},n}=0\),
\(c_{\mathrm{LRO},n}=c_{L,A^{\mathrm{pub}},n}\), and
\(c_{\mathrm{ADML},n}=c_{\mathrm{AD},n}\).  For a generic coefficient
\(c\in\R^{3J}\), write \(c_{0j},c_{1j},c_{ej}\) for its three cell blocks and
\[
r_c(O)=\psi_n(O)-c^\transpose q^{\mathrm{pub}}_n(O;\eta_n),
\]
\[
a^{c}_{0j}(O)=-\one\{X=x_j\}-\alpha_n(D,X)\one\{X=x_j,D=0\}
  +c_{0j}\one\{X=x_j,D=0\},
\]
\[
a^{c}_{1j}(O)=\one\{X=x_j\}-\alpha_n(D,X)\one\{X=x_j,D=1\}
  +c_{1j}\one\{X=x_j,D=1\},
\qquad
b^{c}_{k}(O)=\one\{X=x_k\}\varepsilon_n .
\]
Then, for \(d\in\{0,1\}\),
\[
(\Gamma_{m\ell,n})_{u_{dj},v_k}
=2P_n\!\left[
a^{c_m}_{dj}b^{c_m}_{k}-a^{c_\ell}_{dj}b^{c_\ell}_{k}
-\{r_{c_m}-r_{c_\ell}\}\one\{X=x_j,D=d\}\one\{j=k\}
\right],
\]
and \((\Gamma_{m\ell,n})_{v_k,u_{dj}}\) is the symmetric transpose block.
The outcome--outcome and Riesz--Riesz blocks do not contribute to the
\(n^{-(r_g+r_\alpha)}\) product-rate frontier and are zero in this certificate.
If the exact report summands chosen by an implementation create additional
same-type second-order blocks, those displayed blocks must be added before
the generalized-eigenvalue calculation.  In particular, the two pairwise
matrices needed for Conjecture \ref{conj:spectral-frontier} are obtained by
substituting
\((c_m,c_\ell)=(0,c_{L,A^{\mathrm{pub}},n})\) and
\((c_{L,A^{\mathrm{pub}},n},c_{\mathrm{AD},n})\) in this display.
The metric entries are
\[
(S_n)_{u_{dj},u_{d'k}}=\one\{d=d',j=k\}\pi_jP_n(D=d\mid X=x_j),\qquad
(S_n)_{v_j,v_k}=\one\{j=k\}\pi_j,\qquad
(S_n)_{u_{dj},v_k}=0.
\]
The covariance-kernel entries are \((\mathsf K_n)_{ab}=P_n[\ell_a(O)\ell_b(O)]\), where
\[
\ell_{u_{dj}}(O)=\one\{X=x_j,D=d\}\{\alpha_n(D,X)\varepsilon_n\},\qquad
\ell_{v_j}(O)=\one\{X=x_j\}\varepsilon_n,
\]
and \(\varepsilon_n=Y-\mu_{D,n}(X)\).  Hence
\(\chi_n=\lambda_{\min}(S_n^{-1/2}\mathsf K_nS_n^{-1/2})\) after restricting to the
nonredundant score span, and strict separation in Conjecture 1 can be audited
by checking generalized eigenvalues of the finite pairs
\((\Gamma_{m\ell,n},S_n)\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The nearest project artifact is the \texttt{eid\_dml\_orth\_uniform}/v1
banked note, which warned that certificate matrices were asserted rather than
derived from the published formulas; no published DML/LRO/ADML paper gives
this common finite-support audit table.  (b) The consumer is
\citet{Dorn2025WeakOverlapDR}'s weak-overlap \(t\)-statistic problem together
with the Stage 0 derivation for this qid: both need a concrete algebraic
diagnostic rather than a frontier hidden behind estimator labels.

\begin{conjecture}[Conjecture 2: LRO normalization equivalence class (NOT YET PROVED)]\label{conj:lro-class}
Under Assumptions \ref{ass:ate-id}, \ref{ass:overlap}, \ref{ass:reports},
\ref{ass:lro-class}, \ref{ass:eif}, and \ref{ass:quadratic}, for a sequence
\((A_n,L_{A,n})\in\mathcal A_n\), the ATE-specialized LRO
report shares the ADML report certificate if and only if the ADML coefficient
belongs to the LRO coefficient space, or equivalently if and only if the LRO
coefficient equals the ADML coefficient:
\[
c_{\mathrm{AD},n}\in\mathcal C_{L,A,n}
\quad\Longleftrightarrow\quad
c_{L,A,n}=c_{\mathrm{AD},n}.
\]
The projection identity always holds under Assumption \ref{ass:reports},
\[
c_{L,A,n}=\Pi_{\mathcal C_{L,A,n}}^{\Omega_n}c_{\mathrm{AD},n},
\]
so it is not the
equivalence condition.  Outside the non-tautological equivalence class
\(c_{\mathrm{AD},n}\in\mathcal C_{L,A,n}\), a two- or three-point
finite-support law and an open neighborhood of LRO normalizations exist for
which
\(\Gamma_{\mathrm{LRO},\mathrm{ADML},n}\ne 0\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} deliberately
allows broad locally robust moments, while
\citet{ChernozhukovNeweySingh2022ADML} constructs the Riesz correction from
the functional; neither paper classifies which ATE-specialized LRO choices are
report-equivalent to ADML.  (b) The consumer is the exact LRO specialization
requested by prior CausalSmith reviewers: before any strict DML--LRO--ADML
claim is reviewed, the LRO moment and Jacobian must be pinned to an
equivalence class.

\section{Sanity-check corollaries}
\begin{corollary}[Fixed-overlap product-rate reduction]\label{cor:fixed-overlap}
Under Assumptions \ref{ass:ate-id}, \ref{ass:overlap}, \ref{ass:reports},
\ref{ass:lro-class}, \ref{ass:lro-separated}, \ref{ass:eif},
\ref{ass:quadratic}, and \ref{ass:spectral}, if overlap is fixed
so that the generalized eigenvalues of \((\mathsf K_n,S_n)\) are bounded above and
below away from zero, then \(\omega_K=0\), \(\rho_\star=1/2\), and
Conjecture 1 reduces to the standard product-rate requirement
\(r_g+r_\alpha>1/2\) from
\citet{ChernozhukovEtAl2018ECTJ}.
\end{corollary}

\begin{corollary}[Common-report collapse]\label{cor:common-report}
Under Assumptions \ref{ass:ate-id}, \ref{ass:overlap}, \ref{ass:reports},
\ref{ass:lro-class}, and \ref{ass:eif}, if
\(V_{\mathrm{DML},n}=V_{\mathrm{LRO},n}=V_{\mathrm{ADML},n}\) as functionals
in a neighborhood of \(\eta_n\), then all \(\Gamma_{m\ell,n}=0\), the spectral
gap is zero, and Conjecture 1 has no strict-separation branch.
\end{corollary}

\section{Proof-sketch route}
The no-go proposition reduces to the classical semiparametric fact that
asymptotically linear estimators with the same influence function and
consistent studentizers have the same first-order studentized limit.  The
conjectured frontier requires writing the three published variance reports as
sample averages plus first-step adjustment terms, taking Gateaux derivatives
in \((\mu_0,\mu_1,\alpha_e)\), and identifying the pairwise bilinear forms
\(\Gamma_{m\ell,n}\).  On finite support, this becomes ordinary matrix
algebra: enumerate the \(J\) covariate cells, compute the residual/Riesz
covariance kernel \(\mathsf K_n\), compute the nuisance metric \(S_n\), diagonalize
the generalized pairwise report-gap matrices, and
check whether the local term
\(\sqrt n\,n^{-(r_g+r_\alpha)}\chi_n^{-1/2}\) vanishes, is tight, or diverges.
The main boundary cases are fixed overlap, a two-cell
weak-overlap sequence, and an LRO normalization whose coefficient space
contains the ADML automatic coefficient \(c_{\mathrm{AD},n}\).

\section{Honest scope flags}
The guardrail proposition is intended to be routine once the common canonical
EIF hypothesis is accepted.  Theorem 1 is an algebraic auditability claim, not a proof that
the pairwise certificate matrices are nonzero.  Conjectures 1 and 2 are the
open kernels: they require exact published DML, LRO, and ADML report summands
under one normalization and may fail if the audited LRO selector
\(L_{A^{\mathrm{pub}},n}\) is not the selector used by the target
implementation, or if all three reports collapse as functionals near the
truth.  The strict ordering in Conjecture 1 is conditional on the
computed generalized eigenvalues of the exact report-gap matrices; if those
matrices are indefinite, the result should be revised to an incomparability
frontier rather than a dominance frontier.  The withdrawn v1 claim was the
stronger assertion that population variance maps themselves separate; this
version treats that as refuted and moves the possible novelty to exact report
derivatives.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft reframing the topic as a canonical-EIF
no-go theorem plus a conjectured exact studentization-report spectral
frontier; prior verdict: none.
\item v2 (revise) -- downgraded Theorem 1 to a guardrail, added exact
report-summand conventions, replaced the scale-dependent eigenvalue by a
generalized Rayleigh quotient, parameterized the LRO normalization class, and
added weak-overlap comparators; prior verdict: REVISE.
\item v3 (revise) -- moved the common-EIF result out of the novelty-bearing
theorem list, replaced unnamed report-adjustment placeholders by explicit
published-rule score and correction coefficients, and narrowed the spectral
frontier to a fixed non-equivalent LRO normalization; prior verdict: REVISE.
\item v4 (revise) -- pinned the three report maps to explicit population
summands and normal equations, defined the LRO coefficient subspace as
\(\operatorname{range}(L_{A,n}^{\transpose})\), replaced undefined variance
objects by report-ratio lower bounds, and gave entrywise finite-support matrix
definitions; prior verdict: REVISE.
\item v5 (revise) -- replaced the tautological LRO projection premise by the
non-tautological condition \(c_{\mathrm{AD},n}\notin\mathcal C_{L,A^{\mathrm{pub}},n}\),
locked the audited LRO selector to an explicit outcome-score-block formula,
and expanded the finite-support audit theorem with closed-form
\((u_{dj},v_k)\) entries for the DML--LRO and LRO--ADML report-gap matrices;
prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018ECTJ}
Chernozhukov, V., Chetverikov, D., Demirer, M., Duflo, E., Hansen, C.,
Newey, W., and Robins, J. (2018).
\newblock Double/debiased machine learning for treatment and structural parameters.
\newblock \emph{The Econometrics Journal}, 21(1):C1--C68.
\newblock \url{https://doi.org/10.1111/ectj.12097}.

\bibitem[Chernozhukov et~al.(2022a)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
Chernozhukov, V., Escanciano, J. C., Ichimura, H., Newey, W. K., and
Robins, J. M. (2022).
\newblock Locally robust semiparametric estimation.
\newblock \emph{Econometrica}, 90(4):1501--1535.
\newblock \url{https://doi.org/10.3982/ECTA16294}.

\bibitem[Chernozhukov et~al.(2022b)]{ChernozhukovNeweySingh2022ADML}
Chernozhukov, V., Newey, W. K., and Singh, R. (2022).
\newblock Automatic debiased machine learning of causal and structural effects.
\newblock \emph{Econometrica}, 90(3):967--1027.
\newblock \url{https://doi.org/10.3982/ECTA18515}.

\bibitem[Chernozhukov et~al.(2022c)]{ChernozhukovNeweySingh2022RR}
Chernozhukov, V., Newey, W. K., and Singh, R. (2022).
\newblock Debiased machine learning of global and local parameters using
regularized Riesz representers.
\newblock \emph{The Econometrics Journal}, 25(3):576--601.
\newblock \url{https://doi.org/10.1093/ectj/utac002}.

\bibitem[Newey(1994)]{Newey1994Econometrica}
Newey, W. K. (1994).
\newblock The asymptotic variance of semiparametric estimators.
\newblock \emph{Econometrica}, 62(6):1349--1382.

\bibitem[Robins et~al.(1994)]{RobinsRotnitzkyZhao1994JASA}
Robins, J. M., Rotnitzky, A., and Zhao, L. P. (1994).
\newblock Estimation of regression coefficients when some regressors are not
always observed.
\newblock \emph{Journal of the American Statistical Association}, 89(427):846--866.

\bibitem[Athey et~al.(2018)]{AtheyImbensWager2018JRSSB}
Athey, S., Imbens, G. W., and Wager, S. (2018).
\newblock Approximate residual balancing: debiased inference of average
treatment effects in high dimensions.
\newblock \emph{Journal of the Royal Statistical Society: Series B},
80(4):597--623.
\newblock \url{https://doi.org/10.1111/rssb.12268}.

\bibitem[Dukes et~al.(2024)]{DukesVansteelandtWhitney2024JMLR}
Dukes, O., Vansteelandt, S., and Whitney, D. (2024).
\newblock On doubly robust inference for double machine learning in
semiparametric regression.
\newblock \emph{Journal of Machine Learning Research}, 25:1--46.
\newblock \url{https://jmlr.org/papers/v25/22-1233.html}.

\bibitem[van der Laan et~al.(2024)]{VanDerLaanLuedtkeCarone2024CDML}
van der Laan, L., Luedtke, A., and Carone, M. (2024).
\newblock Automatic doubly robust inference for linear functionals via
calibrated debiased machine learning.
\newblock \emph{arXiv:2411.02771}.
\newblock \url{https://doi.org/10.48550/arXiv.2411.02771}.

\bibitem[Dorn(2025)]{Dorn2025WeakOverlapDR}
Dorn, J. (2025).
\newblock Weak overlap and thresholded doubly robust inference for average
treatment effects.
\newblock Working paper.
\newblock \url{https://arxiv.org/abs/2504.13273}.

\bibitem[Rothe(2017)]{Rothe2017LimitedOverlapCI}
Rothe, C. (2017).
\newblock Robust confidence intervals for average treatment effects under
limited overlap.
\newblock \emph{Econometrica}, 85(2):645--660.

\bibitem[Hong et~al.(2020)]{HongLeungLi2020LimitedOverlap}
Hong, H., Leung, M. P., and Li, J. (2020).
\newblock Inference on finite-population treatment effects under limited
overlap.
\newblock \emph{The Econometrics Journal}, 23(1):32--47.
\newblock \url{https://doi.org/10.1093/ectj/utz017}.

\bibitem[Heiler and Kazak(2021)]{HeilerKazak2021ExtremePS}
Heiler, P. and Kazak, E. (2021).
\newblock Valid inference for treatment effect parameters under irregular
identification and many extreme propensity scores.
\newblock \emph{Journal of Econometrics}, 222(2):1083--1108.
\newblock \url{https://doi.org/10.1016/j.jeconom.2020.03.025}.

\bibitem[Ma et~al.(2026)]{MaSantAnnaSasakiUra2026WeakOverlapDR}
Ma, Y., Sant'Anna, P. H. C., Sasaki, Y., and Ura, T. (2026).
\newblock Doubly robust estimators with weak overlap.
\newblock Working paper.
\newblock \url{https://psantanna.com/files/MSSU2026.pdf}.

\bibitem[Bruns-Smith et~al.(2024)]{BrunsSmithDukesFellerOgburn2024ABW}
Bruns-Smith, D., Dukes, O., Feller, A., and Ogburn, E. L. (2024).
\newblock Augmented balancing weights as linear regression.
\newblock Working paper.
\newblock \url{https://doi.org/10.48550/arXiv.2304.14545}.

\bibitem[Bruns-Smith(2026)]{BrunsSmith2026RieszApproaches}
Bruns-Smith, D. (2026).
\newblock Two approaches to direct estimation of Riesz representers.
\newblock \emph{arXiv:2603.20936}.
\newblock \url{https://arxiv.org/abs/2603.20936}.
\end{thebibliography}

\end{document}
