% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orth\_uniform, specialization=v2
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_dml\_orth\_uniform} / \texttt{v2}%
  \\ \large\textit{ATE-specialized LRO reports are EIF-equivalent to DML/ADML iff their admissible weighted-GMM aggregation spans the residual-variance Riesz quotient}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid = eid_dml_orth_uniform
specialization = v2
graph / SWIG = binary-treatment unconfoundedness SWIG with observed
  O=(Y,D,X), D in {0,1}, potential outcomes (Y(1),Y(0)), consistency
  Y=D Y(1)+(1-D)Y(0), and no hidden common cause of D and (Y(1),Y(0))
  after conditioning on X.
treatment = D, a binary treatment with propensity p0(X)=Pr(D=1|X).
target estimand = theta0 = E[Y(1)-Y(0)].
identifying assumptions = consistency, conditional exchangeability
  (Y(1),Y(0)) independent of D given X, overlap epsilon <= p0(X) <= 1-epsilon,
  square-integrable outcomes, and finite-support diagnostic submodels for
  the normalization-frontier statements.
estimator reports compared = DML empirical AIPW report, ADML Riesz-score
  report, and the class of CEINR-admissible ATE-specialized LRO GMM reports
  indexed by a residual-loading/Jacobian/weight normalization J generated
  by a locally robust first-step influence-function moment dictionary.
equivalence notion = identical first-order influence function and identical
  first-order variance report under the same observable law P, where residual
  loadings are identified in the sigma^2-weighted L2 quotient generated by
  sigma_d^2(x)=Var(Y|D=d,X=x).
\end{verbatim}

\begin{abstract}
Double machine learning, locally robust semiparametric GMM, and automatic debiased machine learning all produce orthogonal ATE scores under unconfoundedness, so comparisons often collapse them into one efficient-influence-function baseline.  This proposal asks which Chernozhukov--Escanciano--Ichimura--Newey--Robins (CEINR)-admissible ATE-specialized LRO moment/Jacobian/sandwich normalizations are genuinely report-equivalent to the DML AIPW report and the ADML Riesz-score report, rather than merely adjacent to the same target parameter.  The flagship conjecture is an iff frontier for the published LRO GMM aggregation rule, with special attention to the optimal-weight overidentified LRO normalization inherited from the GMM efficiency literature: the report is first-order equivalent to DML/ADML exactly when its weighted Jacobian aggregation of the locally robust residual loading has zero residual-variance-weighted distance from the binary-ATE Riesz representer.  For the named optimal-weight normalization, the proposed primitive certificate is the observable scalar $\rho_{\mathrm{ow}}=K_{\mathrm{ow}}/Q_0$, where $K_{\mathrm{ow}}$ is the residual-variance Riesz projection error and $Q_0$ is the squared residual-variance norm of the ATE Riesz representer.  Outside the zero-certificate class, the influence-function gap is the residual Riesz direction and the variance-report gap is the exact signed quadratic expression $K_J-2C_J$, so strict studentized separation requires a visible noncancellation diagnostic rather than $K_J$ alone.  This is not a new ATE estimand and not a routine nuisance-rate weakening; it is an admissible-normalization classification for a named published estimator class whose generality otherwise hides non-equivalent reports.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
For the unconfounded ATE, the efficient influence function is unique, but estimator labels are not: DML, LRO, and ADML arrive at orthogonality through hand-coded AIPW scores, locally robust GMM corrections, and automatic Riesz debiasing.  If every ATE-specialized LRO normalization delivered the same report as DML and ADML, researchers could choose among them for convenience; if only a strict subclass does, then variance reports and Wald intervals can differ even though all three papers target the same population functional.

\paragraph{The main finding (proposed).}
The proposed headline result is Conjecture 1, an iff classification of CEINR-admissible ATE-specialized LRO reports.  Let $\alpha_0(D,X)=D/p_0(X)-(1-D)/(1-p_0(X))$ be the binary-ATE Riesz representer, and let $b_J(D,X)$, $A_J$, and $W_J$ be the residual loading vector, Jacobian, and positive-definite weight generated by an admissible first-step influence-function moment dictionary for the LRO semiparametric GMM report.  The conjecture says that DML, ADML, and the LRO report indexed by $J$ are first-order report-equivalent if and only if the published scalar GMM aggregation $\alpha_J=(A_J^\transpose W_JA_J)^{-1}A_J^\transpose W_Jb_J$ equals $\alpha_0$ in the residual-variance-weighted $L^2$ quotient, not necessarily pointwise on cells with zero residual variance.  For the named optimal-weight overidentified LRO normalization $J_{\mathrm{ow}}$, this becomes the explicit certificate
\[
  \rho_{\mathrm{ow}}={K_{\mathrm{ow}}\over Q_0},\qquad
  K_{\mathrm{ow}}=\E[(\alpha_0-\alpha_{\mathrm{ow}})^2e^2],\quad
  Q_0=\E[\alpha_0^2e^2],
\]
with $\alpha_{\mathrm{ow}}=(A_J^\transpose\Omega_J^{-1}A_J)^{-1}A_J^\transpose\Omega_J^{-1}b_J$ and $\Omega_J=\E[b_Jb_J^\transpose e^2]$: equivalence is the primitive boundary $\rho_{\mathrm{ow}}=0$, while $\rho_{\mathrm{ow}}>0$ gives influence-function separation and the signed variance gap is exactly $K_J-2C_J$, with strict variance separation on open finite-support neighborhoods where this diagnostic does not cancel.

\paragraph{What is new.}
The nearest published comparison points establish valid orthogonal scores or automatic Riesz debiasing, but they do not classify the admissible LRO normalization choices that are actually equivalent to the ATE efficient influence function.  \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} gives the locally robust GMM influence aggregation $(A^\transpose W A)^{-1}A^\transpose Wg$ for broad semiparametric moments; \citet{Hansen1982Econometrica} supplies the optimal-weight GMM benchmark; \citet{IchimuraNewey2022QE} characterizes influence functions for semiparametric estimators; \citet{ChernozhukovEtAl2018ECTJ} fixes the AIPW/DML score; and \citet{ChernozhukovNeweySingh2022ADML} constructs the Riesz score automatically.  The epsilon-gap is not ``another GMM row'': it is the proposed ATE-specialized iff statement for the exact LRO aggregation rule under first-step influence-function admissibility, including the optimal-weight scalar threshold $\rho_{\mathrm{ow}}$, plus the exact noncancellation variance identity that says when a residual Riesz direction becomes a strict report gap rather than an accidental equal-variance misspecification.

\paragraph{How it positions in the literature.}
This is an exact-identification proposal in the unconfoundedness/ATE branch, not a panel or partial-identification proposal.  It treats the ATE as identified by the usual back-door adjustment assumptions and studies the equality or separation of named first-order estimator reports inside that identified model.  The proposal also uses the semiparametric efficiency language of \citet{Newey1994Econometrica}, \citet{IchimuraNewey2022QE}, the optimal-GMM efficiency benchmark of \citet{Hansen1982Econometrica}, and the augmented-IPW lineage of \citet{RobinsRotnitzkyZhao1994JASA}, but the novel object is the LRO normalization frontier relative to DML and ADML.

\paragraph{Implications for the community.}
The concrete downstream consumer is the ADML and augmented-balancing-weight comparison program in \citet{BrunsSmithDukesFellerOgburn2025JRSSB}: a weighted-GMM Riesz-frontier theorem would say exactly when an automatically learned Riesz report, an augmented balancing report, and an LRO GMM report may share standard errors.  If a reader takes only the conclusion away, the practice change is to report the residual-Riesz diagnostic for the chosen LRO normalization before treating its Wald interval as interchangeable with DML or ADML.

\paragraph{How research benefits from the conclusion.}
Researchers should treat DML, ADML, and LRO ATE reports as interchangeable only after checking that the chosen admissible LRO normalization has $\rho_J=0$ in the residual-variance quotient; otherwise they should report the residual-Riesz certificate and avoid pooling the three Wald intervals.

\section{Related work}
\citet{ChernozhukovEtAl2018ECTJ} is the DML baseline: it fixes the cross-fitted Neyman-orthogonal ATE score and sufficient product-rate conditions under which the AIPW score yields valid inference.  \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} is the LRO anchor: it supplies locally robust semiparametric GMM moments whose scalar estimator report is obtained through the Jacobian-and-weight aggregation $(A^\transpose W A)^{-1}A^\transpose Wg$ after a first-step influence-function correction; this proposal specializes that published aggregation to CEINR-admissible binary-ATE moment dictionaries and asks which choices reproduce the ATE Riesz score in the residual-variance quotient.  \citet{Hansen1982Econometrica} is the overidentified-GMM efficiency anchor for the optimal weighting rule $W=\Omega^{-1}$; this proposal's optimal-weight LRO specialization asks whether that efficient GMM weighting also spans the ATE Riesz direction, as measured by the scalar certificate $\rho_{\mathrm{ow}}$.  \citet{IchimuraNewey2022QE} gives a modern influence-function representation for semiparametric estimators, which is the comparator that prevents the conjecture from being sold as a generic IF identity: the new step is the ATE/LRO admissible-normalization iff, not the existence of an influence function.  \citet{ChernozhukovNeweySingh2022ADML} is the ADML anchor: it derives automatic debiasing through Riesz representers for causal and structural effects, including treatment-effect reports.  \citet{ChernozhukovNeweySingh2022RR} develops regularized Riesz representers and highlights instability of Riesz-based inference in ATE-like settings, which motivates making the representer direction explicit in the normalization frontier.  \citet{Newey1994Econometrica} is the semiparametric variance benchmark: the proposal uses its canonical-gradient perspective to avoid attributing the efficient influence function to an estimator label.  \citet{RobinsRotnitzkyZhao1994JASA} is the augmented-IPW ancestor for the binary-treatment score.  \citet{Hahn1998Econometrica} and \citet{HiranoImbensRidder2003Econometrica} are the classical ATE efficiency anchors, so the common DML/ADML influence-function baseline is treated here as known calibration rather than a novel theorem.  \citet{BrunsSmithDukesFellerOgburn2025JRSSB} connects augmented balancing weights and AutoDML to linear-regression identities, making it a direct consumer of any theorem that classifies when ADML-style and alternative reports are numerically or first-order equivalent.  \citet{BrunsSmith2026RieszApproaches} compares two direct Riesz-estimation approaches and finds equivalence in ridge/RKHS settings but possible separation for lasso or general ML classes; this proposal asks the complementary question for LRO GMM normalizations rather than Riesz-estimation losses.

The in-repository prior art is the downgraded \texttt{eid\_dml\_orth\_uniform\_v1} proposal, whose reviewer found that the written population variance maps coincide at truth and requested exact variance summands and explicit LRO/ADML binary-ATE formulas before any separation claim.  The prior-proposal map also flags \texttt{eid\_bjs\_efficient\_event\_study\_v1} as a useful template for comparing named estimator influence functions to one true efficient influence function, and \texttt{pid\_offline\_policy\_joint\_misspec\_v1} as a warning that separate nuisance envelopes can hide compatibility constraints.  This v2 pivot therefore avoids a blanket DML--LRO--ADML variance ordering and instead proposes a precise LRO-equivalence classification against the single ATE efficient influence function.

\section{Formal setup}
The observed law $P$ is the distribution of $O=(Y,D,X)$, where $D\in\{0,1\}$, $Y\in\R$, and $X$ takes values in a measurable covariate space $\mathcal X$.  Potential outcomes $(Y(1),Y(0))$ obey consistency, $Y=DY(1)+(1-D)Y(0)$, and conditional exchangeability given $X$.  The target is
\[
  \theta_0=\E[Y(1)-Y(0)]
  =\E[m_1(X)-m_0(X)],
\]
where $m_d(x)=\E[Y\mid D=d,X=x]$ and $p_0(x)=\Pr(D=1\mid X=x)$.  The binary-ATE Riesz representer is
\[
  \alpha_0(D,X)=\frac{D}{p_0(X)}-\frac{1-D}{1-p_0(X)},
\]
and the canonical ATE influence function is
\[
  \varphi_0(O)=m_1(X)-m_0(X)-\theta_0+\alpha_0(D,X)\{Y-m_D(X)\}.
\]
Write $e=Y-m_D(X)$, $\sigma_d^2(x)=\operatorname{Var}(Y\mid D=d,X=x)$, and let $\nu$ be the residual-variance measure on $(D,X)$ defined by
\[
  \nu(B)=\E[\one\{(D,X)\in B\}e^2].
\]
Thus two residual loadings are equivalent for first-order reports when they agree in the quotient $L^2(\nu)$; differences on cells with $\sigma_d^2(x)=0$ are not identified by either the influence function or the variance report.

An ATE-specialized LRO report is indexed by an admissible normalization $J=(\mathcal H_J,b_J,A_J,W_J)$.  Here $\mathcal H_J$ is a finite first-step influence-function moment dictionary in the sense of the locally robust construction of \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}; its ATE specialization has a residual-loading vector $b_J(D,X)\in\R^{m_J}$, a population Jacobian $A_J\in\R^{m_J}$ with respect to the scalar ATE parameter, and a positive-definite GMM weight $W_J\in\R^{m_J\times m_J}$ used in the published LRO sandwich report.  The admissibility requirement rules out arbitrary algebraic loadings: $b_J$ and $A_J$ must be generated by a locally robust moment whose first-step Gateaux derivative is canceled by the associated first-step influence-function correction.  The scalar LRO aggregation row is
\[
  \kappa_J^\transpose=(A_J^\transpose W_JA_J)^{-1}A_J^\transpose W_J,
\]
and the residual weight actually used by the ATE-specialized LRO influence-function report is
\[
  \alpha_J(D,X)=\kappa_J^\transpose b_J(D,X).
\]
Two named normalizations will be tracked explicitly.  The just-identified Riesz normalization is $J_{\mathrm{EIF}}$, where $m_J=1$, $b_{J_{\mathrm{EIF}}}=\alpha_0$, $A_{J_{\mathrm{EIF}}}=1$, $W_{J_{\mathrm{EIF}}}=1$, and hence $\alpha_{J_{\mathrm{EIF}}}=\alpha_0$.  The optimal-weight overidentified LRO normalization is $J_{\mathrm{ow}}$, where
\[
  \Omega_J=\E\!\left[b_J(D,X)b_J(D,X)^\transpose\{Y-m_D(X)\}^2\right],\qquad
  W_J=\Omega_J^{-1},
\]
so its residual loading is
\[
  \alpha_{\mathrm{ow}}(D,X)
  =(A_J^\transpose\Omega_J^{-1}A_J)^{-1}A_J^\transpose\Omega_J^{-1}b_J(D,X).
\]
This is the specialization of the usual efficient GMM weighting rule to the residual-loading part of the ATE LRO report; the question is whether the resulting scalar loading equals the ATE Riesz representer.
The corresponding ATE-specialized LRO population moment, Jacobian, influence-function report, and sandwich variance report are
\[
  \psi_J(O;\theta)=m_1(X)-m_0(X)-\theta+\alpha_J(D,X)\{Y-m_D(X)\},
\]
\[
  \bar A_J=\E[\partial_\theta\psi_J(O;\theta_0)]=-1,\qquad
  \varphi_J(O)=-\bar A_J^{-1}\psi_J(O;\theta_0),\qquad
  V_J=\bar A_J^{-2}\E[\psi_J(O;\theta_0)^2].
\]
Let $\mu(X)=m_1(X)-m_0(X)-\theta_0$ and $V_{\mathrm{EIF}}=\E[\varphi_0^2]$.  Thus $J\mapsto(\varphi_J,V_J)$ is the report map to be compared with the DML AIPW report $(\varphi_0,V_{\mathrm{EIF}})$ and the ADML Riesz-score report.  Define the residual Riesz direction $r_J=\alpha_0-\alpha_J$ and the finite-support residual-Riesz diagnostics
\[
  K_J=\E\!\left[r_J(D,X)^2\{Y-m_D(X)\}^2\right],
\]
and
\[
  C_J=\E\!\left[\alpha_0(D,X)r_J(D,X)\{Y-m_D(X)\}^2\right],\qquad
  \Delta_J=\left|K_J-2C_J\right|,\qquad
  Q_0=\E\!\left[\alpha_0(D,X)^2\{Y-m_D(X)\}^2\right],
  \qquad
  \rho_J={K_J\over Q_0}.
\]
When $Q_0>0$, $\rho_J$ is the normalized residual-variance Riesz certificate.  For $J_{\mathrm{ow}}$ it is the proposed primitive observable threshold: $\rho_{\mathrm{ow}}=0$ is the equivalence boundary, and $\rho_{\mathrm{ow}}>0$ is the influence-function separation region before the signed variance noncancellation check.
For a finite support $\{(d_\ell,x_\ell)\}_{\ell=1}^L$, these quantities are cell sums with weights $P(d_\ell,x_\ell)\sigma_d^2(x_\ell)$, where $\sigma_d^2(x)=\operatorname{Var}(Y\mid D=d,X=x)$.  Direct expansion gives the signed variance identity
\[
  V_J-V_{\mathrm{EIF}}=K_J-2C_J.
\]
The LRO report indexed by $J$ is report-equivalent to the DML and ADML baselines when both its first-order influence function and variance report coincide with $\varphi_0$ and $V_{\mathrm{EIF}}$.  When strict variance separation is stated below, it is stated through $\Delta_J>0$; this is the required noncancellation condition and replaces the incorrect v2 shorthand that treated $K_J$ alone as the variance gap.

\begin{verbatim}
qid = eid_dml_orth_uniform
specialization = v2
graph / SWIG = binary-treatment unconfoundedness SWIG with observed
  O=(Y,D,X), D in {0,1}, potential outcomes (Y(1),Y(0)), consistency
  Y=D Y(1)+(1-D)Y(0), and no hidden common cause of D and (Y(1),Y(0))
  after conditioning on X.
treatment = D, a binary treatment with propensity p0(X)=Pr(D=1|X).
target estimand = theta0 = E[Y(1)-Y(0)].
identifying assumptions = consistency, conditional exchangeability
  (Y(1),Y(0)) independent of D given X, overlap epsilon <= p0(X) <= 1-epsilon,
  square-integrable outcomes, and finite-support diagnostic submodels for
  the normalization-frontier statements.
estimator reports compared = DML empirical AIPW report, ADML Riesz-score
  report, and the class of CEINR-admissible ATE-specialized LRO GMM reports
  indexed by a residual-loading/Jacobian/weight normalization J generated
  by a locally robust first-step influence-function moment dictionary.
equivalence notion = identical first-order influence function and identical
  first-order variance report under the same observable law P, where residual
  loadings are identified in the sigma^2-weighted L2 quotient generated by
  sigma_d^2(x)=Var(Y|D=d,X=x).
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Unconfounded binary ATE model]\label{ass:ate-model}
The observed law $P$ is generated by the SWIG setup in the locked parameters: consistency holds, $(Y(1),Y(0))\perp D\mid X$, $\E[Y^2]<\infty$, and the target is $\theta_0=\E[Y(1)-Y(0)]$.
\end{assumption}

\begin{assumption}[Overlap]\label{ass:overlap}
There exists $\epsilon>0$ such that $\epsilon\le p_0(X)\le 1-\epsilon$ almost surely.
\end{assumption}

\begin{assumption}[Exact population nuisances for report comparison]\label{ass:exact-nuisance}
The first-order report comparison is conducted at the population nuisance functions $m_0,m_1,p_0$ and the population Riesz representer $\alpha_0$; estimation error is reserved for later nuisance-rate refinements and is not part of the flagship equivalence relation.
\end{assumption}

\begin{assumption}[Nondegenerate residual-Riesz norm]\label{ass:nondegenerate-riesz}
The residual-variance norm of the ATE Riesz representer is positive and finite: $0<Q_0=\E[\alpha_0(D,X)^2e^2]<\infty$.
\end{assumption}

\begin{assumption}[CEINR-admissible ATE-specialized LRO report]\label{ass:lro-report}
The LRO normalization $J=(\mathcal H_J,b_J,A_J,W_J)$ is generated by a finite ATE-specialized first-step influence-function moment dictionary $\mathcal H_J$ satisfying the locally robust moment equations of \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}.  Its report is evaluated through the published GMM aggregation, influence-function report, and sandwich variance map displayed in the formal setup; $b_J$ is square-integrable, $A_J^\transpose W_JA_J$ is nonsingular, and $W_J$ is positive definite.  Algebraic loadings not generated by such a locally robust moment dictionary are outside the flagship Conjecture~\ref{conj:lro-iff}.
\end{assumption}

\begin{assumption}[Algebraic diagnostic report map]\label{ass:diagnostic-map}
For non-flagship diagnostic arithmetic only, the displayed report map may be evaluated at a square-integrable residual loading $b_J$, nonsingular scalar or vector Jacobian $A_J$, and positive-definite weight $W_J$ without asserting that the resulting triple is CEINR-admissible.
\end{assumption}

\begin{assumption}[Optimal-weight LRO normalization]\label{ass:optimal-lro}
When the named optimal-weight LRO specialization $J_{\mathrm{ow}}$ is invoked, $\Omega_J=\E[b_Jb_J^\transpose e^2]$ exists, is positive definite, and the LRO GMM weight is $W_J=\Omega_J^{-1}$.
\end{assumption}

\begin{assumption}[Finite-support diagnostic class]\label{ass:finite-support}
For strict separation and smallest-witness statements, $X$ has finite support, $\Pr(D=d,X=x)>0$ on every support cell, and $\operatorname{Var}(Y\mid D=d,X=x)>0$ on at least one cell where $r_J(d,x)\ne0$.
\end{assumption}

\begin{assumption}[Variance-gap noncancellation]\label{ass:noncancel}
For a strict variance-report separation statement, the finite-support law and LRO normalization satisfy $\Delta_J=|K_J-2C_J|>0$ with $K_J$ and $C_J$ as defined in the formal setup.
\end{assumption}

\section{Main results}
\begin{proposition}[Calibration 1: common EIF baseline, already known]\label{prop:common-eif}
Under Assumptions~\ref{ass:ate-model}, \ref{ass:overlap}, and \ref{ass:exact-nuisance}, the DML AIPW population report and the ADML population Riesz-score report have the same influence function $\varphi_0$ and the same first-order variance report $\E[\varphi_0^2]$.
\end{proposition}
\paragraph{Why this is new and worth studying.}
(a) This proposition is explicitly not the flagship novelty; it records the invariant baseline in \citet{Hahn1998Econometrica}, \citet{HiranoImbensRidder2003Econometrica}, \citet{ChernozhukovEtAl2018ECTJ}, and \citet{ChernozhukovNeweySingh2022ADML}.  The gap to those papers is only notational: the equality is written in the same binary-ATE notation needed for the LRO frontier.  (b) It advances the proposal by preventing the error flagged in the downgraded \texttt{eid\_dml\_orth\_uniform\_v1}: any non-equivalence claim must be a deviation from the unique EIF baseline, not an estimator-label comparison.

\begin{conjecture}[Conjecture 1: admissible LRO weighted-GMM Riesz frontier (NOT YET PROVED)]\label{conj:lro-iff}
Under Assumptions~\ref{ass:ate-model}--\ref{ass:lro-report}, a CEINR-admissible ATE-specialized LRO report indexed by $J=(\mathcal H_J,b_J,A_J,W_J)$ is first-order report-equivalent to the DML AIPW report and the ADML Riesz-score report if and only if
\[
  \alpha_J(D,X)=\kappa_J^\transpose b_J(D,X)=\alpha_0(D,X)\quad\text{in }L^2(\nu),
  \qquad
  \kappa_J^\transpose=(A_J^\transpose W_JA_J)^{-1}A_J^\transpose W_J.
\]
In particular, the just-identified Riesz normalization $J_{\mathrm{EIF}}$ is equivalent, while the named optimal-weight LRO normalization $J_{\mathrm{ow}}$ of Assumption~\ref{ass:optimal-lro} is equivalent if and only if
\[
  \rho_{\mathrm{ow}}={\E[(\alpha_0(D,X)-\alpha_{\mathrm{ow}}(D,X))^2e^2]\over \E[\alpha_0(D,X)^2e^2]}=0,
  \qquad
  (A_J^\transpose\Omega_J^{-1}A_J)^{-1}A_J^\transpose\Omega_J^{-1}b_J(D,X)
  =
  \frac{D}{p_0(X)}-\frac{1-D}{1-p_0(X)}
  \quad\text{in }L^2(\nu).
\]
Moreover, on the finite-support diagnostic class of Assumption~\ref{ass:finite-support}, if $\rho_J>0$ then the influence-function gap has squared $L^2(\nu)$ norm $K_J>0$ and the exact signed variance difference is
\[
  V_J - V_{\mathrm{EIF}} = K_J - 2C_J.
\]
If, in addition, Assumption~\ref{ass:noncancel} holds, then there is an open neighborhood of laws on which the named LRO sandwich report remains variance-separated from the DML/ADML report:
\[
  |V_J - V_{\mathrm{EIF}}|=\Delta_J>0,
\]
with local persistence by continuity of the finite-support cell-sum map.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest paper is \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}, which establishes the general locally robust GMM aggregation but does not state an ATE-specific iff classification of which CEINR-admissible Jacobian-and-weight normalizations aggregate their locally robust residual loading into the ATE Riesz representer in the residual-variance quotient.  \citet{Hansen1982Econometrica} and \citet{IchimuraNewey2022QE} make the generic GMM and influence-function rows familiar, so the epsilon-gap is deliberately narrower and sharper: for the actual ATE LRO report, including the optimal-weight specialization $W_J=\Omega_J^{-1}$, equivalence is the primitive scalar boundary $\rho_J=0$ rather than the tautological pointwise equation $\alpha_J=\alpha_0$, and strict variance separation additionally requires the signed noncancellation identity $V_J-V_{\mathrm{EIF}}=K_J-2C_J$.  (b) Resolving it gives \citet{BrunsSmithDukesFellerOgburn2025JRSSB} and applied AutoDML users a diagnostic for when an LRO GMM standard error can be substituted for an ADML or AIPW standard error.

\begin{proposition}[Diagnostic 1: two-cell non-Riesz aggregation sanity check]\label{prop:two-cell}
Under Assumptions~\ref{ass:ate-model}, \ref{ass:overlap}, \ref{ass:exact-nuisance}, \ref{ass:nondegenerate-riesz}, \ref{ass:diagnostic-map}, \ref{ass:finite-support}, and \ref{ass:noncancel}, there exists a pair $(P^\dagger,J^\dagger)$ such that $X\in\{0,1\}$, $\Pr(X=0)=\Pr(X=1)=1/2$, $p_0(0)=1/3$, $p_0(1)=2/3$, $m_0(x)=m_1(x)=0$, $\operatorname{Var}(Y\mid D=d,X=x)=1$ on all four cells, and $J^\dagger$ uses a one-dimensional intercept-only residual loading $b_{J^\dagger}(D,X)\equiv1$, scalar Jacobian $A_{J^\dagger}=1$, and scalar weight $W_{J^\dagger}=1$.  For this law-normalization pair, $\alpha_{J^\dagger}\equiv1$, $r_{J^\dagger}=\alpha_0-1$ is nonzero in $L^2(\nu)$, $K_{J^\dagger}>0$, $\Delta_{J^\dagger}>0$, the DML and ADML reports are equivalent by Proposition~\ref{prop:common-eif}, and the algebraic GMM aggregation indexed by $J^\dagger$ is first-order separated from them in the sense of the Conjecture~\ref{conj:lro-iff} diagnostic formulas.  This proposition does not assert that $J^\dagger$ is a CEINR-admissible LRO normalization.
\end{proposition}
\paragraph{Why this is new and worth studying.}
(a) This is no longer a novelty-bearing refutation of \citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}; the intercept-only loading is a diagnostic boundary case for the displayed GMM aggregation, not a claimed published recommendation.  The closest prior-art warning is the prior CausalSmith review excerpt requiring an explicit LRO Jacobian/projection matrix, and the value of this proposition is to make the algebraic noncancellation check auditable on the smallest support.  (b) Resolving it gives the \texttt{eid\_dml\_orth\_uniform} Stage 0 derivation a minimal worked example for testing the Conjecture~\ref{conj:lro-iff} formulas before applying them to named ATE-specialized LRO reports.

\section{Sanity-check corollaries}
\begin{corollary}[Canonical normalization collapses to the published AIPW score]\label{cor:canonical}
Under Assumptions~\ref{ass:ate-model}--\ref{ass:lro-report}, if the weighted LRO aggregation satisfies $\alpha_J=\kappa_J^\transpose b_J=\alpha_0$ in $L^2(\nu)$, then $r_J=0$ in the residual-variance quotient, $K_J=\rho_J=\Delta_J=0$, and Conjecture~\ref{conj:lro-iff} reduces to the standard DML/ADML AIPW influence function $\varphi_0$.
\end{corollary}

\begin{corollary}[Constant propensity removes one source of failed spanning]\label{cor:constant-propensity}
Under Assumptions~\ref{ass:ate-model}--\ref{ass:lro-report}, if $p_0(X)\equiv p$ and the weighted LRO aggregation equals the treatment contrast $D/p-(1-D)/(1-p)$ in $L^2(\nu)$, then $r_J=0$ in the residual-variance quotient and the proposed frontier predicts no LRO--ADML report separation.
\end{corollary}

\begin{corollary}[Two-cell arithmetic for Diagnostic 1]\label{cor:two-cell-arithmetic}
For the law and normalization in Proposition~\ref{prop:two-cell}, the four observed cells have probabilities $(1/6,1/3,1/3,1/6)$ for $(D,X)=(1,0),(0,0),(1,1),(0,1)$.  With $\alpha_{J^\dagger}\equiv1$,
\[
  r_{J^\dagger}=(2,-5/2,1/2,-4),
\]
and therefore
\[
  K_{J^\dagger}
  ={1\over6}4+{1\over3}{25\over4}+{1\over3}{1\over4}+{1\over6}16
  ={11\over2},
\]
\[
  C_{J^\dagger}
  ={1\over6}6+{1\over3}{15\over4}+{1\over3}{3\over4}+{1\over6}12
  ={9\over2},
  \qquad
  V_{J^\dagger}-V_{\mathrm{EIF}}=K_{J^\dagger}-2C_{J^\dagger}=-{7\over2},
  \qquad
  \Delta_{J^\dagger}={7\over2}.
\]
\end{corollary}

\section{Proof-sketch route}
The mathematical route is to derive all three reports as first-order von Mises expansions around the same identified ATE functional.  Proposition~\ref{prop:common-eif} is routine algebra: substitute the binary-ATE Riesz representer into the ADML score and compare with the AIPW/DML score.  For Conjecture~\ref{conj:lro-iff}, first verify the primitive admissibility step: the chosen CEINR first-step influence-function dictionary generates the displayed $b_J$, $A_J$, and $W_J$, and the published scalar GMM aggregation gives $\alpha_J=\kappa_J^\transpose b_J$.  Then work in the residual-variance Hilbert quotient $L^2(\nu)$, decompose $\alpha_0=\alpha_J+r_J$, and compute
\[
  \varphi_J-\varphi_0=-r_Je,\qquad
  V_J-V_{\mathrm{EIF}}=\E[(\alpha_J^2-\alpha_0^2)e^2]=K_J-2C_J.
\]
The optimal-weight threshold is then the same calculation normalized by $Q_0$: $\rho_{\mathrm{ow}}=0$ if and only if the optimal-weight aggregation has zero residual-variance distance from $\alpha_0$, while $\rho_{\mathrm{ow}}>0$ gives influence-function separation before the signed variance noncancellation check.  The finite-support part reduces to weighted cell sums: positivity of at least one residual-Riesz cell with positive outcome variance yields $K_J>0$, while $\Delta_J>0$ gives strict variance separation and continuity upgrades the witness to an open set.  Proposition~\ref{prop:two-cell} and Corollary~\ref{cor:two-cell-arithmetic} are checked by plugging the stated two-cell law and intercept-only diagnostic normalization into the scalar GMM aggregation, computing $\alpha_{J^\dagger}\equiv1$, and verifying the explicit values $K_{J^\dagger}=11/2$, $C_{J^\dagger}=9/2$, and $\Delta_{J^\dagger}=7/2$; that arithmetic is a diagnostic check on the formulas, not evidence that the intercept-only normalization is CEINR-admissible.

\section{Honest scope flags}
Proposition~\ref{prop:common-eif} is already-known calibration, not a flagship claim.  Conjecture~\ref{conj:lro-iff} is not yet proved; the open technical step is checking that the displayed ATE-specialized LRO report map is exactly the specialization of the published CEINR moment/Jacobian/sandwich formulas for the admissible first-step influence-function dictionaries, especially the optimal-weight overidentified normalization $J_{\mathrm{ow}}$.  Proposition~\ref{prop:two-cell} is a diagnostic sanity check for the algebra and is explicitly not a novelty-bearing claim against a named published LRO workflow.  Corollary~\ref{cor:two-cell-arithmetic} is included only to make the noncancellation arithmetic auditable.  The proposal deliberately withdraws the rejected v1-style claim that standard population variance maps produce a blanket DML $<$ LRO $<$ ADML ordering, and it also withdraws the v2 shorthand that $K_J$ alone controls variance separation or that pointwise $L^2(P_{D,X})$ equality is needed on residual-variance-zero cells.  It does not claim a nuisance-rate threshold, weak-overlap phase transition, or implementation-level software variance gap; those would require a separate exact variance-rule derivation.  The main uncertainty is whether every useful ATE-specialized LRO normalization can be represented by a finite-dimensional admissible dictionary $\mathcal H_J$ with residual loading $b_J$, Jacobian $A_J$, and weight $W_J$ above; if not, the classification should be restricted to the representable subclass.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
  \item v1 (pivot) --- initial draft for the LRO-normalization equivalence-class angle after the weak-overlap/spectral frontier angle was rejected; prior verdict: none.
  \item v2 (revise) --- added the required research-practice paragraph, demoted the common EIF baseline to already-known calibration, defined the LRO moment/Jacobian/sandwich report map, and pinned the two-cell witness quantifiers; prior verdict: REVISE.
  \item v3 (revise) --- replaced the projection shorthand by the published LRO weighted-GMM aggregation, added the exact $K_J-2C_J$ variance identity and noncancellation condition, and demoted the constant-score witness to a diagnostic sanity check; prior verdict: REVISE.
  \item v4 (revise) --- tied the flagship conjecture to the named optimal-weight LRO normalization, added Ichimura--Newey and overidentified-GMM comparators, and made the two-cell $K=11/2$, $C=9/2$, $\Delta=7/2$ arithmetic explicit; prior verdict: REVISE.
  \item v5 (revise) --- moved the iff condition to the residual-variance-weighted $L^2$ quotient, restricted the flagship class to CEINR-admissible LRO first-step influence-function dictionaries, and added the optimal-weight scalar threshold $\rho_{\mathrm{ow}}$; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018ECTJ}
Chernozhukov, V., Chetverikov, D., Demirer, M., Duflo, E., Hansen, C., Newey, W., and Robins, J. (2018).
\newblock Double/debiased machine learning for treatment and structural parameters.
\newblock \emph{The Econometrics Journal}, 21(1), C1--C68.

\bibitem[Chernozhukov et~al.(2022a)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
Chernozhukov, V., Escanciano, J.~C., Ichimura, H., Newey, W.~K., and Robins, J.~M. (2022).
\newblock Locally robust semiparametric estimation.
\newblock \emph{Econometrica}, 90(4), 1501--1535.

\bibitem[Hansen(1982)]{Hansen1982Econometrica}
Hansen, L.~P. (1982).
\newblock Large sample properties of generalized method of moments estimators.
\newblock \emph{Econometrica}, 50(4), 1029--1054.

\bibitem[Ichimura and Newey(2022)]{IchimuraNewey2022QE}
Ichimura, H., and Newey, W.~K. (2022).
\newblock The influence function of semiparametric estimators.
\newblock \emph{Quantitative Economics}, 13(1), 29--61.

\bibitem[Chernozhukov et~al.(2022b)]{ChernozhukovNeweySingh2022ADML}
Chernozhukov, V., Newey, W.~K., and Singh, R. (2022).
\newblock Automatic debiased machine learning of causal and structural effects.
\newblock \emph{Econometrica}, 90(3), 967--1027.

\bibitem[Chernozhukov et~al.(2022c)]{ChernozhukovNeweySingh2022RR}
Chernozhukov, V., Newey, W.~K., and Singh, R. (2022).
\newblock Debiased machine learning of global and local parameters using regularized Riesz representers.
\newblock \emph{The Econometrics Journal}, 25(3), 576--601.

\bibitem[Newey(1994)]{Newey1994Econometrica}
Newey, W.~K. (1994).
\newblock The asymptotic variance of semiparametric estimators.
\newblock \emph{Econometrica}, 62(6), 1349--1382.

\bibitem[Robins et~al.(1994)]{RobinsRotnitzkyZhao1994JASA}
Robins, J.~M., Rotnitzky, A., and Zhao, L.~P. (1994).
\newblock Estimation of regression coefficients when some regressors are not always observed.
\newblock \emph{Journal of the American Statistical Association}, 89(427), 846--866.

\bibitem[Hahn(1998)]{Hahn1998Econometrica}
Hahn, J. (1998).
\newblock On the role of the propensity score in efficient semiparametric estimation of average treatment effects.
\newblock \emph{Econometrica}, 66(2), 315--331.

\bibitem[Hirano et~al.(2003)]{HiranoImbensRidder2003Econometrica}
Hirano, K., Imbens, G.~W., and Ridder, G. (2003).
\newblock Efficient estimation of average treatment effects using the estimated propensity score.
\newblock \emph{Econometrica}, 71(4), 1161--1189.

\bibitem[Bruns-Smith et~al.(2025)]{BrunsSmithDukesFellerOgburn2025JRSSB}
Bruns-Smith, D., Dukes, O., Feller, A., and Ogburn, E.~L. (2025).
\newblock Augmented balancing weights as linear regression.
\newblock \emph{Journal of the Royal Statistical Society: Series B}.

\bibitem[Bruns-Smith(2026)]{BrunsSmith2026RieszApproaches}
Bruns-Smith, D. (2026).
\newblock Two approaches to direct estimation of Riesz representers.
\newblock \emph{arXiv preprint arXiv:2603.20936}.
\end{thebibliography}

\end{document}
