\begin{abstract}
This paper studies average treatment effect estimation with binary treatment and outcome when the covariate is a discrete variable with \(d\) categories and otherwise unrestricted marginal distribution. Under iid sampling and uniform overlap, the estimand is the covariate-adjusted ATE, written as a sum of homogeneous four-cell functionals. For each fixed overlap constant \(0<\epsilon<1/2\), there are constants \(\rho_\epsilon>0\) and \(N_\epsilon<\infty\) such that, for \(n\ge N_\epsilon\), \(d>0\), and \(d\le \rho_\epsilon n\log n\), we establish the minimax mean-squared-error rate
\[
\mathsf R_{n,d,\epsilon}
\asymp_\epsilon
\frac1n+\frac{d^2}{n^2(\log n)^2}.
\]
The upper bound is attained by a computable split-sample hybrid estimator: empirical ratios are used on pilot-certified heavy categories, while light categories are estimated by a Chebyshev-polynomial continuation implemented through factorial moments. The lower-bound scale is imported from the fixed-sample construction of \citet{ZengBalakrishnanHanKennedy2024}; the new contribution is the matching computable upper bound and the resulting sharp fixed-interior regimes. The result implies a parametric-rate window \(d=O(\sqrt n\log n)\), within the fixed-interior range, and a consistency threshold \(d=o(n\log n)\). For each fixed interior \(0<\epsilon<1/2\), under the same hybrid calibration range \(n\ge N_\epsilon\) and \(d\le \rho_\epsilon n\log n\), we also record an oracle-calibrated deterministic comparison envelope near exact randomization. This theoretical comparison uses the known constants \(\epsilon\) and \(C_\epsilon\). At the separate endpoint \(\epsilon=1/2\), the minimax risk is bracketed between constants times \(n^{-1}\), uniformly in \(d\).
\end{abstract}

\section{Introduction}

Covariate adjustment is central to observational causal inference. Under consistency, conditional exchangeability, and overlap, the average treatment effect can be identified by comparing treated and control outcomes within covariate strata and averaging over the covariate distribution \citep{Rubin1974,RosenbaumRubin1983,Hahn1998,HiranoImbensRidder2003}. Classical semiparametric theory describes this problem well when the adjustment dimension is fixed or when nuisance functions can be estimated with enough structure. This paper studies a finite-alphabet benchmark in which that structure is deliberately absent.

The model is simple. A single observation is \(O=(X,A,Y)\), where \(X\in\{1,\ldots,d\}\), \(A\in\{0,1\}\), and \(Y\in\{0,1\}\). The observations are iid as in \cref{obj:ass:iid-sampling}. The covariate marginal is unrestricted, and treatment assignment satisfies the categorywise overlap condition in \cref{obj:ass:overlap}. With the usual potential-outcome interpretation supplied by \cref{obj:ass:consistency} and \cref{obj:ass:conditional-exchangeability}, the ATE is the functional in \cref{obj:def:ate-functional}. The statistical object is the minimax mean-squared-error risk over the finite-alphabet overlap class in \cref{obj:def:experiment-class} and \cref{obj:def:minimax-risk}.

The main result is that, for each fixed \(0<\epsilon<1/2\), polynomial approximation improves the plug-in scale suggested by summing \(d\) ordinary cellwise errors. \Cref{obj:thm:sharp-minimax-fixed-interior} shows that there are constants depending on \(\epsilon\) such that, whenever \(n\) is large enough, \(d>0\), and \(d\le \rho_\epsilon n\log n\),
\[
\mathsf R_{n,d,\epsilon}
\asymp_\epsilon
\frac1n+\frac{d^2}{n^2(\log n)^2}.
\]
Within the same fixed-interior range, the theorem also gives a parametric-rate window when \(d\le K\sqrt n\log n\), and it gives the consistency threshold \(d=o(n\log n)\). These statements are uniform over unrestricted covariate marginals satisfying only the stated overlap restriction.

The upper bound is constructive. \Cref{obj:def:hybrid-estimator-handle} gives a split-sample estimator that first uses pilot counts to classify covariate categories as heavy or light. Heavy categories are estimated by empirical ratios on an independent split. Light categories are estimated by a polynomial approximation to the homogeneous cell functional in \cref{obj:def:cell-functional}, with factorial moments replacing unstable empirical denominators. \Cref{obj:thm:overlap-adaptive-universal-hybrid} records both the fixed-overlap risk envelope and the real-arithmetic computability bound for this estimator.

The logarithmic improvement comes from the same broad source as in large-alphabet nonsmooth functional estimation: polynomial approximation can outperform direct substitution when many cells are weakly sampled \citep{Paninski2003,JiaoVenkatHanWeissman2015,WuYang2016,HanJiaoWeissman2020}. Here the nonsmooth object is the four-cell ATE contribution
\[
p_k(\mu_{1k}-\mu_{0k}).
\]
\citet{ZengBalakrishnanHanKennedy2024} provide the fixed-sample lower-bound ingredient used here and analyze standard regression, weighting, and doubly robust estimators for this high-dimensional discrete ATE problem. This paper closes the corresponding upper-bound gap by constructing the ratio-polynomial hybrid estimator and deriving the sharp fixed-interior consistency and parametric-rate regimes. The lower-bound transfer itself is stated in \cref{obj:lem:ate-lower-bound-transfer}.

The result provides a complementary finite-alphabet minimax benchmark for semiparametric and doubly robust theory. In settings with smoothness, sparsity, or accurate nuisance regression and propensity estimates, inverse-probability, doubly robust, targeted, double-machine-learning, and higher-order approaches address different regimes \citep{RobinsRotnitzkyZhao1994,BangRobins2005,VanDerLaanRubin2006,BelloniChernozhukovHansen2014,Chernozhukov2018,Robins2008,Robins2009,Robins2017,Kennedy2024}. In the growing unrestricted-alphabet regime studied here, overlap is the sole regularity condition and many small categories create the nonregular term \(d^2/(n^2\log^2 n)\).

The endpoint \(\epsilon=1/2\) is different. At exact within-category randomization, \cref{obj:thm:overlap-adaptive-universal-hybrid} brackets the minimax risk between \(1/(100n)\) and \(1/n\), uniformly in \(d\). For each fixed interior \(0<\epsilon<1/2\), and only under the same calibration conditions \(n\ge N_\epsilon\) and \(d\le \rho_\epsilon n\log n\), the same theorem also gives an oracle-calibrated deterministic comparison envelope near randomization,
\[
\frac1n+
\min\left\{
\frac{d^2}{n^2(\log n)^2},(1/2-\epsilon)^2
\right\},
\]
up to constants. This comparison chooses between two already analyzed estimators using the known fixed-interior constants and supplies an oracle-calibrated upper envelope near the randomized endpoint.

The formal statements and derivations are supported by a Lean 4 development, with the precise verification boundary recorded in the verification appendix.
