% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_contdid\_acrt\_lipschitz, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_core.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_contdid\_acrt\_lipschitz} / \texttt{v1}%
  \\ \large\textit{Algebraic Lipschitz envelopes for continuous-treatment DiD causal responses}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Cluster: PartialID.  The locked tuple is
\[
  (\text{qid},\text{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional}).
\]
Here \(\text{qid}=\texttt{pid\_contdid\_acrt\_lipschitz}\) and
\(\text{specialization}=\texttt{v1}\).  \(P\) is the observable law of a
two-period continuous-treatment DiD array \(O=(Y_0,Y_1,D)\), with \(D\) taking
values on a fixed ordered finite grid
\(\mathcal D=\{d_0<d_1<\cdots<d_K\}\), where \(d_0=0\) denotes the untreated or
baseline dose.  The latent causal array is
\(\alpha_{j h}=\operatorname{ATT}(d_j\mid d_h)
=\E[Y_1(d_j)-Y_1(d_0)\mid D=d_h]\).  The diagonal entries
\(\alpha_{h h}\), the definitional baseline row \(\alpha_{0h}=0\), and the
Callaway--Goodman-Bacon--Sant'Anna observed level-change contrasts
\(\tau_h(P)=\E[Y_1-Y_0\mid D=d_h]-\E[Y_1-Y_0\mid D=d_0]\) are taken as the
identified inputs under generalized parallel trends.  The target is the
finite-grid average causal response on the
treated at dose \(d_h\),
\[
  \theta_h=\operatorname{ACRT}(d_h)
  =\sum_{j=0}^K q_{j h}\alpha_{j h},
\]
where \(q_{\cdot h}\) is a locked local finite-difference stencil satisfying
\(\sum_jq_{j h}=0\) and \(\sum_jq_{j h}(d_j-d_h)=1\).  The identifying
restrictions are consistency, no anticipation, generalized parallel trends for
the diagonal treated-type parameters, bounded outcomes
\(\alpha_{j h}\in[\underline y,\overline y]\), and either the row-wise
structural Lipschitz restriction
\(|\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\) for all \(j,h,h'\), or the
row-wise isotonic restriction in the conditioning group \(d_h\).  The bounding
functional is the algebraic finite-grid envelope
\([L_h(L;P),U_h(L;P)]\), the image of the joint feasible nuisance polytope under
the linear map \(\alpha\mapsto\theta_h\), together with the critical regularity
constant \(L_h^\star(P)=\inf\{L:0\in[L_h(L;P),U_h(L;P)]\}\).
Law sharpness of this algebraic envelope as a causal interval is the
separate completion claim in Conjecture~\ref{conj:law-sharp}.

\begin{abstract}
Continuous-treatment DiD identifies treated-type dose effects under generalized
parallel trends, but adjacent dose comparisons remain contaminated by
cross-dose selection terms.  This proposal asks whether structural regularity
of the full cross-dose array \(\operatorname{ATT}(l\mid d)\) can turn those
unidentified terms into an algebraic finite-grid envelope for
\(\operatorname{ACRT}(d)\).  The kernel claim is that the ACRT envelope is the
support-function image of one joint Lipschitz or isotonic nuisance polytope,
not a coordinatewise observed-contrast interval formed by bounding each
selection-bias term separately.  The proposal also singles out the critical
Lipschitz constant \(L_h^\star\) at which zero first enters the envelope and a
small witness where joint constraints strictly sharpen marginal local bounds.
A plug-in relaxed-LP estimator would make the algebraic envelope and the sign
frontier usable in empirical continuous-dose DiD applications, with causal
law sharpness left to a latent-completion conjecture.
\end{abstract}

\section{Introduction}
Many DiD applications have treatments that vary in amount.  A dose may be a
subsidy rate, an exposure intensity, a price change, or a policy dosage.  In
these settings the treated-type level effect at a dose and the causal response
to a local dose increase are different objects.  The question is how much can
be learned about the causal response for the group actually exposed to dose
\(d_h\) when comparisons across dose groups carry selection bias.

\citet[Sections 3--4]{CallawayGoodmanBaconSantAnna2021} show that
continuous-treatment DiD identifies treated-type parameters but that adjacent
dose comparisons are contaminated because parallel trends does not rule out
cross-dose selection bias.  \citet{ManskiPepper2000} show how monotone
restrictions can shrink nonparametric treatment-effect bounds, and
\citet{Voronin2025} shows how sharp partial-identification bounds can be
represented and estimated as LP values.  The gap is that no published result
turns the Callaway--Goodman-Bacon--Sant'Anna cross-dose ATT array into one
joint Lipschitz or isotonic nuisance set and then maps that set into an
algebraic ACRT envelope.  The kernel is a PartialID theorem: characterize
\([L_h(L;P),U_h(L;P)]\), \(L_h^\star(P)\), and the nonseparability of the joint
constraints, with law-level sharpness isolated as a completion question.

The concrete consumer is continuous-dose DiD reporting in the Medicare payment
application of \citet{CallawayGoodmanBaconSantAnna2021} and in no-stayer or
switcher designs such as
\citet{deChaisemartinDHaultfoeuillePasquierSowVazquezBare2022} and
\citet{deChaisemartinDHaultfoeuilleVazquezBare2024}.  A reader would report
the smallest cross-dose regularity needed to make the ACRT sign unidentified,
rather than interpreting a TWFE sign or a local contrast as if cross-dose
selection were absent.

\begin{itemize}[leftmargin=*]
  \item Theorem 1: the finite-grid Lipschitz or isotonic ACRT algebraic envelope is the support-function image of one joint cross-dose ATT polytope. Gap: \citet{CallawayGoodmanBaconSantAnna2021} leaves the cross-dose selection terms exposed; \citet{ManskiPepper2000} and \citet{Voronin2025} give shape and LP templates outside this ACRT array. Consumer: continuous-dose DiD applications in \citet{CallawayGoodmanBaconSantAnna2021}.
  \item Conjecture 1: the algebraic LP envelope is law-sharp for finite bounded potential outcomes, with a latent completion for every feasible ATT array. Gap: prior in-repo \texttt{pid\_dose\_response\_shape} warned that pointwise continuous-dose bounds may fail to paste across doses. Consumer: causal interpretation of the ACRT envelope.
  \item Conjecture 2: \(L_h^\star(P)\) is the value of an explicit parametric LP feasibility problem and is affine in \(b_{\mathrm{CGS}}(P)\) on fixed active bases. Gap: \citet{ChernozhukovLeeRosen2013} and \citet{Stoye2020} study optimized bounds and scalar interval inference, but not the inverse sign-sensitivity problem for continuous-treatment DiD. Consumer: sign-sensitivity reporting for ACRT.
  \item Conjecture 3: relaxed plug-in LPs give valid endpoint and \(L_h^\star\) inference under active-face switching and empty sample feasibility. Gap: \citet{KaidoMolinariStoye2019}, \citet{BelloniBugniChernozhukov2018}, and \citet{Voronin2025} provide adjacent inference machinery, but not for the joint ACRT Lipschitz envelope. Consumer: empirical confidence sets for the algebraic ACRT envelope.
\end{itemize}

\section{Related work}
\citet{CallawayGoodmanBaconSantAnna2021} is the anchor because it defines the
continuous-treatment DiD treated-type and ACRT objects and shows why
cross-dose comparisons require stronger assumptions than generalized parallel
trends.  \citet{deChaisemartinDHaultfoeuille2020} is the binary and
multi-period TWFE diagnostic benchmark; it motivates treating regression signs
as objects to be audited rather than as causal response estimates.
\citet{deChaisemartinDHaultfoeuillePasquierSowVazquezBare2022} gives an
adjacent continuous-treatment DiD design based on switchers, which is a natural
consumer for a shape-restricted ACRT algebraic envelope.
\citet{deChaisemartinDHaultfoeuilleVazquezBare2024} studies continuous
treatments without stayers, where replacing missing stayer information by
structural cross-dose regularity is especially relevant.
\citet{ManskiPepper2000} supplies the monotone instrumental-variable and
monotone treatment-response precedent for credible shape restrictions that
shrink nonparametric bounds.  \citet{ChernozhukovFernandezValHahnNewey2013}
shows why nonseparability in panel response surfaces can make linear fixed
effect estimands miss average causal effects, which is the panel-side warning
behind the present cross-dose nuisance array.  \citet{Ishihara2017} is an
adjacent nonseparable-model reference for using monotonicity and concavity to
obtain partial identification when point identification fails.
\citet{ChernozhukovLeeRosen2013} frames bounds as optimized infimum or
supremum objects and explains the inferential problem caused by plug-in
intersection-bound estimators.  \citet{KaidoMolinariStoye2019} gives
calibrated projection confidence intervals for functions of partially
identified parameters and is the closest projection-inference template for
relaxed ACRT LPs.  \citet{BelloniBugniChernozhukov2018} supplies uniform
many-moment-inequality subvector inference, relevant when the grid and
regularity constraints are large.  \citet{Stoye2020} gives a never-empty
confidence interval for scalar interval-identified parameters, directly
relevant to empty or reversed sample analog ACRT intervals.  \citet{Voronin2025}
is the closest LP-value estimation reference because it handles feasibility,
solution multiplicity, and root-\(n\) pointwise LP-value estimation.
\citet{ArmstrongKolesar2018} is adjacent because it develops optimal inference
for linear functionals over smoothness and shape classes, the continuous
analogue of the Lipschitz grid restriction used here.

The in-repository predecessor \texttt{pid\_dose\_response\_iv\_v1} gives a
finite LP envelope, rank-coupling sign certificate, and critical radius for a
continuous-IV dose-response target; this proposal uses the LP and critical
radius pattern but changes the estimand to CGS ACRT and changes the coupling
object to cross-dose ATT regularity.  The accepted
\texttt{pid\_did\_anticipation\_bounded\_v1} artifact gives support-function
intervals for bounded anticipation in DiD; it is prior art for shared-coordinate
aggregation but not for continuous-dose cross-dose selection.  The downgraded
\texttt{pid\_dose\_response\_shape\_v1} artifact warned that pointwise
continuous-dose sensitivity bounds may fail law-level pasting; this is why
Conjecture 1 is stated separately.  The \texttt{q\_lpdid\_bjs\_frontier\_v1}
proposal is prior art for DiD weight-frontier diagnostics, while this proposal
optimizes an algebraic partial-ID causal response envelope rather than an LP-DiD weight
equality.  The catalogue in \texttt{doc/API.md} records \texttt{CausalSmith/PartialID/}
as the staging area for partial-ID research theorems; no current catalogue
entry already contains a continuous-treatment DiD ACRT Lipschitz envelope.

\paragraph{Exemplars.}
The writing exemplar is \citet{CallawayGoodmanBaconSantAnna2021},
arXiv:2107.02637; the introduction mirrors its arc from continuous doses, to
treated-type identification, to the cross-dose ACRT selection-bias gap.
Theorem 1 adapts \citet{ManskiPepper2000} (identification, DOI
10.1111/1468-0262.00144) by replacing monotone response primitives with a
cross-dose ATT shape polytope, and adapts \citet{Voronin2025} (estimation and
LP values, arXiv:2503.14940) by writing the endpoint as an LP value.
Conjecture 1 adapts the observational-equivalence discipline recorded in
Molinari-style random-set sharpness and the in-repo \texttt{pid\_dose\_response\_shape}
warning; the carried-over move is to separate algebraic feasibility from
latent-law realization.  Conjecture 2 adapts the sensitivity-frontier grammar
of \citet{ChernozhukovLeeRosen2013} and \citet{Stoye2020} by inverting the
endpoint interval in \(L\).  Conjecture 3 adapts \citet{KaidoMolinariStoye2019}
(projection inference, arXiv:1601.00934), \citet{BelloniBugniChernozhukov2018}
(many inequalities, arXiv:1806.11466), and \citet{Voronin2025} (LP-value
estimation) for relaxed finite-grid ACRT endpoint inference.

\section{Formal setup}
Let \(O=(Y_0,Y_1,D)\sim P\), where \(D\in\mathcal D\) and
\(\Pr(D=d_h)>0\) for \(h=0,\ldots,K\).  The post-period potential outcome
under dose \(d_j\) is \(Y_1(d_j)\).  The level treatment effect for treatment
dose \(d_j\) in conditioning group \(d_h\) is
\[
  \alpha_{j h}=\operatorname{ATT}(d_j\mid d_h)
  =\E\{Y_1(d_j)-Y_1(d_0)\mid D=d_h\}.
\]
Write the observed mean change in group \(h\) as
\[
  m_h(P)=\E[Y_1-Y_0\mid D=d_h],
  \qquad
  \tau_h(P)=m_h(P)-m_0(P).
\]
Under the maintained generalized parallel-trends convention of
\citet[Sections 3--4]{CallawayGoodmanBaconSantAnna2021},
\(\tau_h(P)=\alpha_{h h}\).  The baseline-dose identities are
\(\alpha_{0h}=0\) for every conditioning group \(h\).  Define
\[
  b_{\mathrm{CGS}}(P)=
  \bigl((0)_{h=0}^K,(\tau_h(P))_{h=0}^K\bigr),
\]
and let \(A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P)\) denote exactly the
linear rows
\[
  \alpha_{0h}=0\quad(h=0,\ldots,K),
  \qquad
  \alpha_{hh}=\tau_h(P)\quad(h=0,\ldots,K).
\]
For a fixed target group \(h\), let \(q_h=(q_{0h},\ldots,q_{Kh})\) be a local
finite-difference stencil with \(\sum_jq_{jh}=0\) and
\(\sum_jq_{jh}(d_j-d_h)=1\).  The CGS observable local contrast for this
stencil is the derived functional
\[
  r_h(P)=\sum_{j=0}^K q_{jh}\tau_j(P)
       =\theta_h(\alpha)+\sum_{j=0}^K q_{jh}\{\alpha_{jj}-\alpha_{jh}\},
\]
which is the target response plus the cross-dose selection-bias functional.
The finite-grid ACRT target is
\[
  \theta_h(\alpha)=\sum_{j=0}^Kq_{j h}\alpha_{j h}.
\]
For a Lipschitz constant \(L\ge0\), define the feasible nuisance set
\[
\mathcal A_L(P)=
\left\{\alpha\in[\underline y,\overline y]^{(K+1)^2}:
 A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\
 |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|
 \ \forall j,h,h'\right\}.
\]
The isotonic variant \(\mathcal A_{\mathrm{iso}}(P)\) replaces the Lipschitz
inequalities by \(\alpha_{j0}\le\alpha_{j1}\le\cdots\le\alpha_{jK}\), or by
the reversed order if the locked application specifies decreasing selection in
the conditioning dose.  The algebraic envelope is
\[
  L_h(L;P)=\inf_{\alpha\in\mathcal A_L(P)}\theta_h(\alpha),\qquad
  U_h(L;P)=\sup_{\alpha\in\mathcal A_L(P)}\theta_h(\alpha),
\]
with the analogous isotonic endpoints.  The critical Lipschitz constant is
\[
  L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\},
\]
with \(L_h^\star(P)=+\infty\) if zero never enters on the locked domain.

\begin{quote}
\begin{verbatim}
Cluster: PartialID.
qid=pid_contdid_acrt_lipschitz; specialization=v1.
Observable law P is the law of O=(Y0,Y1,D), with D on a fixed finite
ordered dose grid D={d0<...<dK}.  The latent array is
alpha[j,h]=ATT(d_j | d_h).  The target is
theta_h=sum_j q[j,h] alpha[j,h], where q[.,h] is a fixed local
finite-difference stencil for ACRT(d_h).  Restrictions are consistency,
no anticipation, generalized parallel trends identifying the CGS diagonal
level-change vector, bounded outcomes, and row-wise Lipschitz or isotonic
regularity of alpha[j,h] in the conditioning group h.  The bounding
functional is the algebraic envelope [L_h(L;P),U_h(L;P)] from the joint
feasible alpha-polytope, and L_h^*(P)=inf{L:0 in [L_h(L;P),U_h(L;P)]}.
Law sharpness requires the latent-completion claim in Conjecture 1.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite dose grid and bounded outcomes]\label{ass:grid-bounds}
The dose grid \(\mathcal D=\{d_0<\cdots<d_K\}\) is fixed, each dose group has
positive probability, and every level treatment effect satisfies
\(\alpha_{j h}\in[\underline y,\overline y]\).  This is the finite-outcome
and finite-support convention used in classical nonparametric bounds such as
\citet{ManskiPepper2000}.
\end{assumption}

\begin{assumption}[Consistency and no anticipation]\label{ass:consistency-noanticip}
Observed outcomes satisfy \(Y_1=Y_1(D)\), and the pre-period outcome is not
affected by the later dose.  This is the continuous-treatment DiD convention
used by \citet{CallawayGoodmanBaconSantAnna2021}.
\end{assumption}

\begin{assumption}[CGS generalized parallel trends inputs]\label{ass:cgs-inputs}
The generalized parallel-trends assumptions of
\citet{CallawayGoodmanBaconSantAnna2021} identify
\(\tau_h(P)=\E[Y_1-Y_0\mid D=d_h]-\E[Y_1-Y_0\mid D=d_0]\) and hence the
diagonal treated-type effects \(\alpha_{hh}=\tau_h(P)\).  Together with the
definitional baseline rows \(\alpha_{0h}=0\), these are exactly the rows in
\(A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P)\).  This assumption imports the
CGS identified inputs but does not impose strong parallel trends or set
cross-dose selection bias to zero.
\end{assumption}

\begin{assumption}[Structural cross-dose regularity]\label{ass:regularity}
For the Lipschitz version, a finite \(L\in[0,\bar L]\) is fixed and each
treatment row \(h\mapsto\alpha_{j h}\) obeys
\(|\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\).  For the isotonic version,
each row is monotone in the conditioning group.  These are structural
cross-dose variants of the monotone and smoothness restrictions used in
\citet{ManskiPepper2000} and \citet{ArmstrongKolesar2018}.
\end{assumption}

\begin{assumption}[Finite latent support]\label{ass:completion}
The latent potential-outcome law may place mass on a finite product support
for \((Y_1(d_0),\ldots,Y_1(d_K),D)\), with each coordinate bounded in
\([\underline y,\overline y]\), while preserving the observed \(P\), consistency,
no anticipation, and the CGS baseline and diagonal level-change vector.  This is the usual
finite observational-equivalence convention for checking sharpness; it does
not assert that every feasible mean array is realizable.
\end{assumption}

\begin{assumption}[Sampling and LP regularity]\label{ass:sampling-lp}
The sample is iid across units; the empirical CGS input vector
\(\widehat b_{\mathrm{CGS}}\) is asymptotically linear and root-\(n\)
normal; the population LPs are feasible and finite; and on each regular
active region the endpoint value has a nonempty compact dual solution set.
This is the finite-dimensional LP setup used in \citet{Voronin2025} and the
projection-inference setup of \citet{KaidoMolinariStoye2019}.
\end{assumption}

\begin{assumption}[Critical-frontier contact]\label{ass:frontier-contact}
For inference on \(L_h^\star(P)\), the zero-contact set is either a singleton
with nonzero one-sided slope in \(L\), a finite tie set with separated
candidate slopes, or a compact flat face for which the support-function
directional derivative exists.  This is the standard nonsmooth-contact
taxonomy used for frontier and interval inversion.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: joint polytope support envelope]\label{thm:joint-envelope}
Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, if
\(\mathcal A_L(P)\) is nonempty, then the finite-grid ACRT algebraic envelope
under the cross-dose restrictions is
\[
  \Theta_h^{\mathrm{alg}}(L;P)=
  [L_h(L;P),U_h(L;P)]
  =
  \{\theta_h(\alpha):\alpha\in\mathcal A_L(P)\}.
\]
The endpoints are attained by finite linear programs.  Equivalently,
\[
  U_h(L;P)=\sigma_{\mathcal A_L(P)}(q_h\otimes e_h),
  \qquad
  L_h(L;P)=-\sigma_{\mathcal A_L(P)}(-q_h\otimes e_h),
\]
where \(\sigma_C(v)=\sup_{x\in C}v^\transpose x\) is the support function.
The same statement holds for the isotonic set
\(\mathcal A_{\mathrm{iso}}(P)\).
\end{theorem}
The proof is finite-dimensional convex analysis: the CGS equalities, box
bounds, and Lipschitz or isotonic inequalities define a compact polytope, and
\(\theta_h\) is linear.

\begin{conjecture}[Conjecture 1: law-sharp ACRT envelope (NOT YET PROVED)]\label{conj:law-sharp}
Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, the algebraic
envelope in Theorem~\ref{thm:joint-envelope} is law-sharp:
\[
  [L_h(L;P),U_h(L;P)]
  =
  \{\operatorname{ACRT}(d_h;Q):Q \text{ is a finite bounded latent law
  preserving } P \text{ and Assumptions } \ref{ass:consistency-noanticip}
  \text{--}\ref{ass:regularity}\}.
\]
In particular, no endpoint is an outer-bound artifact caused by an
unrealizable cross-dose ATT array.
\end{conjecture}

\begin{conjecture}[Conjecture 2: critical Lipschitz frontier (NOT YET PROVED)]\label{conj:critical-l}
Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, the endpoint
functions \(L\mapsto L_h(L;P)\) and \(L\mapsto U_h(L;P)\) are monotone
piecewise linear on every finite grid.  The critical constant
\[
  L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}
\]
is equivalently the optimum of a finite parametric LP feasibility problem in
\((\alpha,L)\):
\[
 \min_{\alpha,L}\ L
 \quad\text{subject to}\quad
 A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ 
 \theta_h(\alpha)=0,\ 
 \underline y\le\alpha_{jh}\le\overline y,\ 
 |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|,\ 
 0\le L\le\bar L .
\]
For each nonsingular active basis of this LP, \(L_h^\star(P)\) is an affine
function of \(b_{\mathrm{CGS}}(P)\) on the region where that basis remains
optimal; globally it is the lower envelope of these basis-specific affine
pieces.
\end{conjecture}

\begin{conjecture}[Conjecture 3: relaxed-LP endpoint and threshold inference (NOT YET PROVED)]\label{conj:plugin-inference}
Under Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact}, define
\(\widehat L_h(L)\), \(\widehat U_h(L)\), and
\(\widehat L_h^\star\) by replacing \(b_{\mathrm{CGS}}(P)\) with an
asymptotically linear estimate and relaxing equality and inequality
constraints by calibrated Gaussian or bootstrap critical values.  Then the
resulting confidence set covers the algebraic envelope endpoints
\([L_h(L;P),U_h(L;P)]\) and the critical constant \(L_h^\star(P)\) pointwise,
and remains nonempty with probability approaching one even when the unrelaxed
sample LP is infeasible.  If Conjecture~\ref{conj:law-sharp} holds, the same
endpoint confidence set covers the law-sharp ACRT interval.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Strong-parallel-trends collapse]\label{cor:spt-collapse}
If strong parallel trends holds in the CGS sense, then
\(\alpha_{j h}=\alpha_{j j}\) for all \(j,h\).  Hence
\[
  L_h(L;P)=U_h(L;P)=\sum_jq_{j h}\alpha_{j j},
\]
for every \(L\ge0\), and the proposal collapses to the point-identified CGS
ACRT stencil.
\end{corollary}

\begin{corollary}[Unrestricted regularity collapse]\label{cor:unrestricted-collapse}
If \(L\ge(\overline y-\underline y)/\min_{h\ne h'}|d_h-d_{h'}|\), the
Lipschitz inequalities are implied by the outcome box.  The algebraic envelope in
Theorem~\ref{thm:joint-envelope} then reduces to the CGS algebraic outer set
with only the baseline identities, diagonal level-change equations, and
bounded outcomes.
\end{corollary}

\begin{example}[Three-dose isotonic strict-sharpening audit]\label{ex:isotone-audit}
Let \(\mathcal D=\{0,1,2\}\), \([\underline y,\overline y]=[-2,2]\), and
suppose the CGS diagonal inputs are
\(\alpha_{00}=0\), \(\alpha_{11}=0\), and \(\alpha_{22}=0\).  Consider the
right-response target at group \(d_1\), \(\theta_1=\alpha_{21}-\alpha_{11}\).
A coordinatewise local box with radius one allows
\(\alpha_{21}\in[-1,1]\), so the local interval for \(\theta_1\) is
\([-1,1]\).  If treatment rows are isotone increasing in the conditioning
group, row \(j=2\) obeys \(\alpha_{20}\le\alpha_{21}\le\alpha_{22}=0\), so the
joint isotonic envelope gives \(U_1=0\).  The strict positive part of the
coordinatewise interval is therefore infeasible under the joint structural
restriction, and the difference is not a normalization artifact because both
calculations use the same target \(\theta_1\) and the same diagonal inputs.
\end{example}

\section{Proof-sketch route}
The proof first imports the CGS baseline identities and diagonal level-change
inputs and
rewrites the ACRT stencil as a linear functional of the finite array
\(\alpha\).  The endpoint theorem then follows from the separating hyperplane
and support-function representation of a compact polytope; the only boundary
algebra is checking that isotonic and Lipschitz inequalities remain closed
under the CGS equality restrictions.  The law-sharpness conjecture requires a
finite latent-completion construction: assign potential-outcome increments on
a product support so that each conditioning group has the prescribed row means
and the observed \((Y_0,Y_1,D)\) margin is preserved.  The \(L_h^\star\) result
uses parametric LP sensitivity: add \(L\) as a scalar variable, homogenize the
absolute-value inequalities, and derive primal feasibility and dual
certificates for zero containment.  The inference result follows the relaxed
projection method of \citet{KaidoMolinariStoye2019} for feasibility, the
many-inequality Gaussian approximation of \citet{BelloniBugniChernozhukov2018}
for large grids, and the LP-value estimator logic of \citet{Voronin2025} for
active-face multiplicity.

\section{Honest scope flags}
Theorem~\ref{thm:joint-envelope} is the algebraic partial-ID statement once
the CGS baseline identities and diagonal level-change vector are fixed.  Conjecture~\ref{conj:law-sharp} is the
sharpness risk: some feasible ATT arrays may fail to paste into one
potential-outcome panel law.  Conjecture~\ref{conj:critical-l}
is mathematically plausible for finite grids but still needs active-set
bookkeeping.  Conjecture~\ref{conj:plugin-inference} is intentionally stated as
pointwise, not uniformly over all laws; uniform coverage would require a
separate compactness and minimum-singular-value condition.  The proposal does
not claim that the Lipschitz-only envelope always strictly improves the
coordinatewise local interval for a one-sided two-dose stencil; the
nonseparability audit is stated for the isotonic variant and more complex CGS
contrast systems.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
  \item v1 (cold-start) -- initial field-tier draft centered on the joint Lipschitz/isotonic ACRT envelope, critical \(L^\star\), nonseparability audit, and relaxed-LP inference; prior verdict: none.
  \item v2 (revise) -- fixed the baseline-dose rows, made the CGS input matrix explicit, and restated the critical Lipschitz frontier as a basis-wise affine LP value; prior verdict: REVISE.
  \item v3 (revise) -- restated Theorem 1 and all headline language as an algebraic envelope unless conditioned on the latent-completion conjecture; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Armstrong and Kolesar(2018)]{ArmstrongKolesar2018}
Armstrong, T. B. and Kolesar, M. (2018).
Optimal inference in a class of regression models.
\textit{Econometrica}, 86, 655--683.

\bibitem[Belloni, Bugni, and Chernozhukov(2018)]{BelloniBugniChernozhukov2018}
Belloni, A., Bugni, F., and Chernozhukov, V. (2018).
Subvector inference in partially identified models with many moment
inequalities.
arXiv:1806.11466.

\bibitem[Callaway, Goodman-Bacon, and Sant'Anna(2021)]{CallawayGoodmanBaconSantAnna2021}
Callaway, B., Goodman-Bacon, A., and Sant'Anna, P. H. C. (2021).
Difference-in-differences with a continuous treatment.
arXiv:2107.02637.

\bibitem[Chernozhukov, Fernandez-Val, Hahn, and Newey(2013)]{ChernozhukovFernandezValHahnNewey2013}
Chernozhukov, V., Fernandez-Val, I., Hahn, J., and Newey, W. (2013).
Average and quantile effects in nonseparable panel models.
\textit{Econometrica}, 81, 535--580.

\bibitem[Chernozhukov, Lee, and Rosen(2013)]{ChernozhukovLeeRosen2013}
Chernozhukov, V., Lee, S., and Rosen, A. M. (2013).
Intersection bounds: estimation and inference.
\textit{Econometrica}, 81, 667--737.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{deChaisemartinDHaultfoeuille2020}
de Chaisemartin, C. and D'Haultfoeuille, X. (2020).
Two-way fixed effects estimators with heterogeneous treatment effects.
\textit{American Economic Review}, 110, 2964--2996.

\bibitem[de Chaisemartin et al.(2022)]{deChaisemartinDHaultfoeuillePasquierSowVazquezBare2022}
de Chaisemartin, C., D'Haultfoeuille, X., Pasquier, F., Sow, D., and
Vazquez-Bare, G. (2022).
Difference-in-differences estimators for treatments continuously distributed at
every period.
arXiv:2201.06898.

\bibitem[de Chaisemartin, D'Haultfoeuille, and Vazquez-Bare(2024)]{deChaisemartinDHaultfoeuilleVazquezBare2024}
de Chaisemartin, C., D'Haultfoeuille, X., and Vazquez-Bare, G. (2024).
Two-way fixed effects and differences-in-differences with continuous
treatments and no stayers.
arXiv:2402.05432.

\bibitem[Ishihara(2017)]{Ishihara2017}
Ishihara, T. (2017).
Partial identification of treatment effects in nonseparable models under
monotonicity and concavity.
arXiv:1707.04405.

\bibitem[Kaido, Molinari, and Stoye(2019)]{KaidoMolinariStoye2019}
Kaido, H., Molinari, F., and Stoye, J. (2019).
Confidence intervals for projections of partially identified parameters.
\textit{Econometrica}, 87, 1397--1432.

\bibitem[Manski and Pepper(2000)]{ManskiPepper2000}
Manski, C. F. and Pepper, J. V. (2000).
Monotone instrumental variables: with an application to the returns to
schooling.
\textit{Econometrica}, 68, 997--1010.

\bibitem[Stoye(2020)]{Stoye2020}
Stoye, J. (2020).
A simple, short, but never-empty confidence interval for partially identified
parameters.
arXiv:2010.10484.

\bibitem[Voronin(2025)]{Voronin2025}
Voronin, A. (2025).
Linear programming approach to partially identified econometric models.
arXiv:2503.14940.
\end{thebibliography}

\end{document}
