\paragraph{\S9-fragment-statement: Mended result for the labelled solve target \texttt{law-sharp}.}\label{prop:law-sharp-mended}
\textbf{Motivating claim restated.} Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, the algebraic
envelope in Theorem~\ref{thm:joint-envelope} is law-sharp:
\[
  [L_h(L;P),U_h(L;P)]
  =
  \{\operatorname{ACRT}(d_h;Q):Q \text{ is a finite bounded latent law
  preserving } P \text{ and Assumptions } \ref{ass:consistency-noanticip}
  \text{--}\ref{ass:regularity}\}.
\]
In particular, no endpoint is an outer-bound artifact caused by an
unrealizable cross-dose ATT array.

\textbf{Original claim and object correction.} The displayed claim is false for
the loose algebraic ATT-array envelope \(\mathcal A_L(P)\): an array can
satisfy the baseline row, diagonal CGS inputs, bounded ATT entries, and
row-wise Lipschitz inequalities while failing to be the mean array of any
latent potential-outcome completion.  The correction is to use the actual
finite-dimensional projection of completions satisfying Assumption~\ref{ass:completion}.

For each conditioning dose define the identified on-arm post mean and implied
baseline mean
\[
  \mu_{1h}(P)=\E_P[Y_1\mid D=d_h],
  \qquad
  \beta_h(P)=\mu_{1h}(P)-\tau_h(P).
\]
The corrected completion polytope is
\[
  \mathcal A_L^{\mathrm{mc}}(P)
  =
  \Bigl\{\alpha\in\mathcal A_L(P):
    \underline y\le \beta_h(P)+\alpha_{j h}\le \overline y
    \text{ for every }h\text{ and every }j\ne h
  \Bigr\}.
\]
Let
\[
  L_h^{\mathrm{mc}}(L;P)
  =
  \min_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha),
  \qquad
  U_h^{\mathrm{mc}}(L;P)
  =
  \max_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha).
\]

\textbf{Headline statement.} Confirmed after object correction: write \(\mu_{1h}(P)=\E_P[Y_1\mid D=d_h]\) and \(\beta_h(P)=\mu_{1h}(P)-\tau_h(P)\), define \(\mathcal A_L^{\mathrm{mc}}(P)=\{\alpha\in\mathcal A_L(P):\underline y\le \beta_h(P)+\alpha_{jh}\le\overline y\ \forall h,\ \forall j\ne h\}\), and set \(L_h^{\mathrm{mc}}(L;P)=\min_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha)\), \(U_h^{\mathrm{mc}}(L;P)=\max_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha)\). Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, with the algebraic object replaced by this mean-completion polytope, \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\) is law-sharp for the finite-grid ACRT over latent completions preserving \(P\) whose off-arm potential outcomes are assigned by finite \([\underline y,\overline y]\)-supported product kernels conditional on the observed data: every such completion maps into \(\mathcal A_L^{\mathrm{mc}}(P)\), and every \(\alpha\in\mathcal A_L^{\mathrm{mc}}(P)\) is realized by such a completion.

This is an object correction, not a new identifying restriction on the law
class.  It keeps the original finite-grid continuous-treatment DiD ACRT target,
but removes arrays whose implied off-arm potential-outcome means cannot be
generated under the maintained bounded off-arm support.

\paragraph{\S10-mend-classification and guard record.}
\textbf{Classification.} Type A, object bug.  The witness lives on a boundary
support face.  In the \(D=d_1\) stratum, consistency gives
\(Y_1(d_1)=Y_1=1\), so
\(\mu_{1,1}(P)=1\).  The diagonal input \(\alpha_{11}=\tau_1(P)=0\) then
forces
\[
  \E_Q[Y_1(d_0)\mid D=d_1]
  =
  \mu_{1,1}(P)-\tau_1(P)
  =
  1.
\]
With support \([0,1]\), this mean places \(Y_1(d_0)\) on the upper boundary
almost surely.  The algebraic vertex with \(\alpha_{21}=1\) asks for
\[
  \E_Q[Y_1(d_2)\mid D=d_1]
  =
  \mu_{1,1}(P)-\tau_1(P)+\alpha_{21}
  =
  2,
\]
outside the maintained off-arm support \([0,1]\).  The kernel LP,
support-function, and critical-\(L\) mechanisms are not false; the array object
omitted the coordinate mean-completion inequalities that any bounded off-arm
completion must satisfy.

\textbf{Naturalness.} The correction follows the standard
observational-equivalence convention for sharp identified sets: characterize
exactly the parameter values generated by latent random variables consistent
with the data and maintained assumptions.  Molinari's survey organizes partial
identification around random variables consistent with the available data and
credible maintained assumptions \cite{Molinari2020}.  The inequalities above
are that convention written for the finite-grid ATT means.  They are not
witness-tailored: without them, the object is not the projection of the
bounded off-arm potential-outcome completion class in
Assumption~\ref{ass:completion}.

\textbf{Vacuity and substance.} The mended class is nonempty.  In the witness
observable law, the completion
\[
\begin{array}{c|ccc}
  D & Y_1(d_0) & Y_1(d_1) & Y_1(d_2)\\ \hline
  d_0 & 0&0&1\\
  d_1 & 1&1&1\\
  d_2 & 0&0&1
\end{array}
\]
preserves \(P\), is \(1\)-Lipschitz at the ATT-array level, and induces
\[
  \alpha=
  \begin{pmatrix}
    0&0&0\\
    0&0&0\\
    1&0&1
  \end{pmatrix}
  \in\mathcal A_1^{\mathrm{mc}}(P).
\]
The motivating regime also survives: finite ordered dose grids, CGS diagonal
inputs, bounded off-arm post-period potential outcomes, and row-wise cross-dose
Lipschitz or isotonic restrictions remain exactly the maintained regime.  The
repair only removes arrays whose implied off-arm potential-outcome means leave
the support interval.

\paragraph{\S11-primitive derivation of the corrected law-sharpness claim.}
\textbf{Necessity.} Let \(Q\) be any latent completion preserving \(P\) and
satisfying Assumptions~\ref{ass:consistency-noanticip}--\ref{ass:completion}.
Thus \(Q\) preserves the observed conditional law of \((Y_0,Y_1)\) given
\(D=d_h\), sets \(Y_1(d_h)=Y_1\) on that cell, and assigns the off-arm
coordinates through finite product kernels supported on
\([\underline y,\overline y]\).  Define
\[
  \alpha_{j h}(Q)
  =
  \E_Q[Y_1(d_j)-Y_1(d_0)\mid D=d_h].
\]
The baseline row, diagonal entries, ATT bounds, and row-wise regularity put
\(\alpha(Q)\) in \(\mathcal A_L(P)\).  Moreover, consistency and preservation
of \(P\) give
\[
  \E_Q[Y_1(d_h)\mid D=d_h]
  =
  \E_P[Y_1\mid D=d_h]
  =
  \mu_{1h}(P).
\]
The CGS diagonal input gives \(\alpha_{hh}(Q)=\tau_h(P)\).  Therefore, for
\(h>0\),
\[
  \E_Q[Y_1(d_0)\mid D=d_h]
  =
  \E_Q[Y_1(d_h)\mid D=d_h]-\alpha_{hh}(Q)
  =
  \mu_{1h}(P)-\tau_h(P)
  =
  \beta_h(P).
\]
For \(h=0\), the baseline coordinate is on-arm, \(\tau_0(P)=0\), and the same
identity reads
\[
  \E_Q[Y_1(d_0)\mid D=d_0]=\mu_{10}(P)=\beta_0(P).
\]
Consequently, for every off-arm coordinate \(j\ne h\),
\[
  \E_Q[Y_1(d_j)\mid D=d_h]
  =
  \E_Q[Y_1(d_0)\mid D=d_h]
  +
  \E_Q[Y_1(d_j)-Y_1(d_0)\mid D=d_h]
  =
  \beta_h(P)+\alpha_{j h}(Q).
\]
Assumption~\ref{ass:completion} supports each off-arm \(Y_1(d_j)\) in
\([\underline y,\overline y]\), so its conditional mean lies in that interval.
Hence \(\alpha(Q)\in\mathcal A_L^{\mathrm{mc}}(P)\), and every law-level ACRT
value belongs to the corrected algebraic image.

\textbf{Sufficiency.} Conversely fix
\(\alpha\in\mathcal A_L^{\mathrm{mc}}(P)\).  Work separately in each observed
dose stratum \(D=d_h\), and preserve the conditional observable law of
\((Y_0,Y_1)\) given \(D=d_h\).  Set the on-arm potential outcome
\[
  Y_1(d_h)=Y_1
\]
so consistency is automatic and no finite-support condition is imposed on the
observed on-arm coordinate.  For every off-arm index \(j\ne h\), choose a
finite-support variable \(Z_{jh}\in[\underline y,\overline y]\) with mean
\[
  \E[Z_{jh}\mid D=d_h]=\beta_h(P)+\alpha_{jh}.
\]
Such variables exist because the corrected inequalities put each desired mean
in the support interval: if \(\underline y<\overline y\), use the two-point
law assigning \(\overline y\) with probability
\((\mu-\underline y)/(\overline y-\underline y)\) and \(\underline y\)
otherwise; if \(\underline y=\overline y\), use the degenerate law.  Conditional
on \((Y_0,Y_1,D=d_h)\), assign the off-arm vector
\((Y_1(d_j))_{j\ne h}\) as the product of these finite kernels.

This construction preserves \(P\) because it does not alter
\((Y_0,Y_1,D)\), sets \(Y_1(d_h)=Y_1\) on each observed cell, and uses only
finite off-arm product kernels as required by Assumption~\ref{ass:completion}.
It is intentionally not a finite-support law for the observed variables unless
the observable law \(P\) already has finite support.  Thus the completion is
well typed for the general observable law allowed by the setup.

For \(h>0\), the off-arm baseline coordinate has mean
\[
  \E[Y_1(d_0)\mid D=d_h]=\beta_h(P)+\alpha_{0h}=\beta_h(P),
\]
because the baseline row has \(\alpha_{0h}=0\).  For \(h=0\), the same baseline
mean is on-arm and equals \(\mu_{10}(P)=\beta_0(P)\).  Therefore, for any
off-arm \(j\ne h\),
\[
  \E[Y_1(d_j)-Y_1(d_0)\mid D=d_h]
  =
  (\beta_h(P)+\alpha_{jh})-\beta_h(P)
  =
  \alpha_{jh}.
\]
For the diagonal coordinate \(j=h\),
\[
  \E[Y_1(d_h)-Y_1(d_0)\mid D=d_h]
  =
  \mu_{1h}(P)-\beta_h(P)
  =
  \tau_h(P)
  =
  \alpha_{hh},
\]
where the last equality is the CGS diagonal constraint in \(\mathcal A_L(P)\).
The row-wise Lipschitz or isotonic restriction is inherited from \(\alpha\),
since the maintained regularity is a restriction on the ATT mean array.  Thus
every corrected algebraic point is law-realized.

The set \(\mathcal A_L^{\mathrm{mc}}(P)\) is obtained from
\(\mathcal A_L(P)\) by adding finitely many closed linear inequalities.  The
same compact-polytope and support-function argument as
Theorem~\ref{thm:joint-envelope} applies after adding these rows.  Consequently
\(\mathcal A_L^{\mathrm{mc}}(P)\) is a compact convex polytope whenever
nonempty, and the linear image
\(\theta_h(\mathcal A_L^{\mathrm{mc}}(P))\) is the compact interval whose
endpoints are the finite LP values
\(L_h^{\mathrm{mc}}(L;P)\) and \(U_h^{\mathrm{mc}}(L;P)\).  Combining the
necessity and sufficiency directions proves the corrected law-sharpness
equality.

\paragraph{\S12-sanity check and anchor compatibility.}
As a corner case, take the degenerate one-dose grid \(K=0\).  There are no
off-arm coordinates, \(\tau_0(P)=0\), \(\beta_0(P)=\mu_{10}(P)\), and the only
ATT entry is the definitional baseline entry \(\alpha_{00}=0\).  Hence
\(\mathcal A_L^{\mathrm{mc}}(P)=\mathcal A_L(P)=\{0\}\), and both endpoints
satisfy
\[
  L_0^{\mathrm{mc}}(L;P)=U_0^{\mathrm{mc}}(L;P)=\theta_0(0)=0.
\]
The law-level ACRT is also zero because \(Y_1(d_0)-Y_1(d_0)=0\).  The corrected
statement therefore reduces to the tautological no-off-arm special case.

The confirmed sibling \texttt{critical-l} remains the right structural anchor.
Replacing \(\mathcal A_L(P)\) by \(\mathcal A_L^{\mathrm{mc}}(P)\) only adds
finite linear inequalities independent of \(L\).  The endpoint maps are still
finite LP values, hence monotone piecewise linear in \(L\), and the zero-contact
constant is still a finite parametric LP in \((\alpha,L)\) after inserting the
same mean-completion rows.  The confirmed sibling \texttt{plugin-inference}
also keeps its structure: relaxed-LP inference covers the corrected endpoints
by relaxing the same finite equality and inequality system, now including the
observable mean-completion constraints.

\paragraph{\S13-original witness after the mend.}
The refutation primitive is vertex enumeration on the smallest nontrivial
binary boundary support: three doses, binary post outcomes, and deterministic
observed cells.  In the refuting three-dose law, take \(Y_0=0\) in every dose
cell and \(Y_1=0,1,1\) in the \(D=d_0,d_1,d_2\) cells respectively.  Then
\[
  (\mu_{10},\mu_{11},\mu_{12})=(0,1,1),
  \qquad
  (m_0,m_1,m_2)=(0,1,1),
  \qquad
  (\tau_0,\tau_1,\tau_2)=(0,0,1),
  \qquad
  (\beta_0,\beta_1,\beta_2)=(0,1,0).
\]
The old algebraic maximizer had \(\alpha^\dagger_{21}=1\).  The corrected
constraint for \((j,h)=(2,1)\) requires
\[
  \underline y
  \le
  \beta_1(P)+\alpha_{21}
  \le
  \overline y,
  \qquad\text{that is}\qquad
  0\le 1+\alpha_{21}\le 1.
\]
Thus \(\alpha^\dagger_{21}=1\) is excluded because it implies the impossible
off-arm mean \(2\).  In fact the corrected constraint gives
\(\alpha_{21}\le0\), while the original nonnegativity and
Lipschitz/diagonal restrictions give \(\alpha_{21}\ge0\).  Hence the corrected
law-sharp interval for this witness collapses to the law-realized value
\[
  \operatorname{ACRT}(d_1)=\alpha_{21}-\alpha_{11}=0.
\]
The original counterexample no longer refutes the mended statement; it
identifies the missing coordinate of the correct law-level LP.
