% file-plan: reuse-pattern/bypass-justified: substrate survey found reusable PartialID, PO, and Manski population-bound primitives, but no direct continuous-treatment DiD ACRT relaxed-LP inference primitive; this fragment stays at the paper-level finite LP abstraction, reuses Theorem~\ref{thm:joint-envelope}, and cites no implementation files.

\paragraph{\S9-fragment-statement.}
\paragraph{Conjecture restated verbatim.}
Under Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact}, define
\(\widehat L_h(L)\), \(\widehat U_h(L)\), and
\(\widehat L_h^\star\) by replacing \(b_{\mathrm{CGS}}(P)\) with an
asymptotically linear estimate and relaxing equality and inequality
constraints by calibrated Gaussian or bootstrap critical values.  Then the
resulting confidence set covers the algebraic envelope endpoints
\([L_h(L;P),U_h(L;P)]\) and the critical constant \(L_h^\star(P)\) pointwise,
and remains nonempty with probability approaching one even when the unrelaxed
sample LP is infeasible.  If Conjecture~\ref{conj:law-sharp} holds, the same
endpoint confidence set covers the corrected law-sharp ACRT interval through
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\subseteq[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)]\), or after replacing the sample LP by the analogous relaxed mean-completion program.

\begin{theorem}[Relaxed-LP endpoint and frontier confidence set]\label{thm:plugin-inference}
\paragraph{Verdict headline.}
Confirmed conservative relaxed-LP inference. Let \(\Delta Y_i=Y_{1i}-Y_{0i}\), \(\widehat\mu_g=\sum_i\one\{D_i=d_g\}\Delta Y_i/\sum_i\one\{D_i=d_g\}\), \(\widehat\tau_g=\widehat\mu_g-\widehat\mu_0\), and \(\widehat z=(\widehat\tau_1,\ldots,\widehat\tau_K)\). Let \(\widehat c_{n,\alpha}\) be the conditional \((1-\alpha)\)-quantile of the Gaussian or multiplier-bootstrap statistic \(\max_{1\le g\le K}|\widehat G_g^\ast|/\widehat s_g\), and set \(r_{g,n}=(\widehat c_{n,\alpha}\widehat s_g+\rho_n)/\sqrt n\) with \(\rho_n\to\infty\) and \(\rho_n/\sqrt n\to0\), for example \(\rho_n=\log n\). If \(A_0\alpha=0\) denotes the baseline-row equations, \(A_\tau\alpha=z(P)\) the diagonal CGS equations, \(B_L\alpha\le d_L\) the box and Lipschitz (or isotonic) inequalities, and \(a_h^\transpose\alpha=\sum_j q_{jh}\alpha_{jh}\), define
\[
  \widehat{\mathcal A}_{L,n}
  =
  \{\alpha:A_0\alpha=0,\ |(A_\tau\alpha)_g-\widehat z_g|\le r_{g,n}\ (g=1,\ldots,K),\ B_L\alpha\le d_L+\rho_n n^{-1/2}\one\},
\]
\[
  \widehat L_h(L)=\min_{\alpha\in\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha,
  \qquad
  \widehat U_h(L)=\max_{\alpha\in\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha,
\]
and
\[
  \widehat C_{h,n}^\star=\{\ell\in[0,\bar L]:\widehat L_h(\ell)\le0\le\widehat U_h(\ell)\},
  \qquad
  \widehat L_h^\star=\inf \widehat C_{h,n}^\star .
\]
Under Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact}, for each fixed \(L\) with \(\mathcal A_L(P)\ne\emptyset\),
\[
  \Pr\{[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)]\}\to1,
  \qquad
  \Pr\{\widehat{\mathcal A}_{L,n}\ne\emptyset\}\to1,
\]
and, whenever \(L_h^\star(P)\in[0,\bar L]\),
\[
  \Pr\{L_h^\star(P)\in\widehat C_{h,n}^\star\}\to1 .
\]
If Conjecture~\ref{conj:law-sharp} holds, the same interval
\([\widehat L_h(L),\widehat U_h(L)]\) covers the corrected law-sharp
mean-completion ACRT interval
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\), because
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\subseteq[L_h(L;P),U_h(L;P)]\).  The coverage is deliberately conservative: the diverging but vanishing padding \(\rho_n/\sqrt n\) is what turns calibrated projection relaxation into a never-empty LP relaxation at boundary laws.
\paragraph{Verdict headline (machine-readable).}
Confirmed conservative relaxed-LP inference. Define \(\widehat\tau_g=\widehat\mu_g-\widehat\mu_0\) with \(\widehat\mu_g=\sum_i\one\{D_i=d_g\}(Y_{1i}-Y_{0i})/\sum_i\one\{D_i=d_g\}\), set \(r_{g,n}=(\widehat c_{n,\alpha}\widehat s_g+\rho_n)/\sqrt n\), \(\rho_n=\log n\), and \(\widehat{\mathcal A}_{L,n}=\{\alpha:A_0\alpha=0,\ |(A_\tau\alpha)_g-\widehat\tau_g|\le r_{g,n}\ (g=1,\ldots,K),\ B_L\alpha\le d_L+\rho_n n^{-1/2}\one\}\), where \(\widehat c_{n,\alpha}\) is the Gaussian or multiplier-bootstrap \((1-\alpha)\)-critical value for the studentized CGS input vector. With \(a_h^\transpose\alpha=\sum_jq_{jh}\alpha_{jh}\), \(\widehat L_h(L)=\min_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat U_h(L)=\max_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat C_{h,n}^\star=\{\ell\in[0,\bar L]:\widehat L_h(\ell)\le0\le\widehat U_h(\ell)\}\), and \(\widehat L_h^\star=\inf\widehat C_{h,n}^\star\), Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact} imply \(\Pr\{[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)],\ \widehat{\mathcal A}_{L,n}\ne\emptyset\}\to1\) for each fixed feasible \(L\), and \(\Pr\{L_h^\star(P)\in\widehat C_{h,n}^\star\}\to1\); if Conjecture~\ref{conj:law-sharp} holds, the same endpoint interval covers the corrected law-sharp mean-completion ACRT interval \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\) through \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\subseteq[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)]\).
\end{theorem}

\paragraph{\S13-refutation-attempt.}
The partial-identification refutation primitive is a finite response-type LP
with the smallest nontrivial dose grid.  Take \(K=1\), keep the baseline row
\(\alpha_{01}=0\), and write the only stochastic diagonal input as
\(\alpha_{11}=\tau_1(P)\).  The population feasible set is the interval
cut out by the box, baseline, diagonal, and one Lipschitz face; its vertices
are therefore the usual lower-bound, upper-bound, and diagonal-contact
points.  At every such vertex the relaxed sample constraints contain the
population vertex on the event
\[
  \sqrt n\,|\widehat\tau_1-\tau_1(P)|
  \le \widehat c_{n,\alpha}\widehat s_1+\rho_n,
\]
and Assumption~\ref{ass:sampling-lp} makes the left side \(O_p(1)\) while
\(\rho_n\to\infty\).  Hence the two-response-type LP cannot produce a
population endpoint outside the relaxed sample interval.

The next candidate witness is sample infeasibility at a boundary law.  Let the
population diagonal input satisfy \(\tau_1(P)=\overline y\), so the exact
population feasible point lies on the upper box face.  The unrelaxed sample
LP with \(A_\tau\alpha=\widehat\tau_1\) and \(\alpha\le\overline y\) is
infeasible whenever \(\widehat\tau_1>\overline y\), an event with nonvanishing
probability under a centered nondegenerate root-\(n\) limit.  This does not
refute the conjecture because the proposed relaxed LP also widens the
inequality face by \(\rho_n/\sqrt n\).  The population vertex
\(\alpha_{11}=\overline y\) is feasible for the relaxed sample LP whenever
\(\sqrt n(\widehat\tau_1-\overline y)\le \widehat c_{n,\alpha}\widehat s_1+\rho_n\),
which occurs with probability tending to one.  Thus the refutation search
finds exactly the obstruction the conjecture was designed to remove, not a
violation of the relaxed construction.

The final candidate is the critical frontier.  At \(L=L_h^\star(P)\), the
support-envelope theorem gives an array \(\alpha^\star\in\mathcal A_{L_h^\star(P)}(P)\)
with \(a_h^\transpose\alpha^\star=0\), provided the zero-contact set is closed.
Assumption~\ref{ass:frontier-contact} is precisely the contact condition that
rules out a missing boundary contact.  The same containment event puts
\(\alpha^\star\) in \(\widehat{\mathcal A}_{L_h^\star(P),n}\), so
\(0\in[\widehat L_h(L_h^\star(P)),\widehat U_h(L_h^\star(P))]\).  No finite
vertex or frontier-contact witness violates the advertised coverage claim.

\paragraph{\S10 Interpretation.}
The theorem is an inference result for the computable algebraic envelope, not
a new point-identification result for \(\operatorname{ACRT}(d_h)\).  The
population object remains the LP image
\([L_h(L;P),U_h(L;P)]\) from Theorem~\ref{thm:joint-envelope}.  The sample
object replaces the identified CGS inputs by their cell-mean estimates and
then solves the same endpoint LP after widening the stochastic diagonal
equations and the deterministic inequality faces by a root-\(n\) amount.

This is the calibrated-projection construction of
\cite{KaidoMolinariStoye2019} specialized to a finite linear program: the
reported endpoint is obtained by optimizing the projection
\(a_h^\transpose\alpha\) over sample analog constraints relaxed by Gaussian or
bootstrap critical values.  The extra \(\rho_n/\sqrt n\) padding is the
smallest asymptotic device needed for the conjecture's never-empty clause.
It vanishes at the population scale, so it does not change the limiting
identified object, but it dominates \(O_p(n^{-1/2})\) sampling error at
binding faces and therefore prevents boundary laws from producing empty
sample LPs.

The confidence set for \(L_h^\star(P)\) is an inversion of zero-containment:
it reports every regularity radius \(\ell\) whose relaxed endpoint interval
contains zero.  If Conjecture~\ref{conj:law-sharp} holds, the causal ACRT
identified interval is the corrected mean-completion interval
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\), not the larger algebraic
interval.  The relaxed algebraic interval still covers it because the
mean-completion feasible set is nested inside the algebraic feasible set.
Without that separate law-sharpness result, the theorem covers the algebraic
envelope only.

\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:plugin-inference}]
Let
\[
  z(P)=(\tau_1(P),\ldots,\tau_K(P))
\]
be the stochastic part of \(b_{\mathrm{CGS}}(P)\); the baseline row
\(\alpha_{0g}=0\) is kept as the exact equation \(A_0\alpha=0\).  By
Assumption~\ref{ass:sampling-lp}, the cell-mean vector
\(\widehat z=(\widehat\tau_1,\ldots,\widehat\tau_K)\) is asymptotically
linear and root-\(n\) normal.  Equivalently,
\[
  \sqrt n\{\widehat z-z(P)\}=O_p(1).
\]
The Gaussian or multiplier-bootstrap statistic used to form
\(\widehat c_{n,\alpha}\) is the finite-dimensional calibrated-projection
critical value in the sense of \cite{KaidoMolinariStoye2019}.  For the
containment argument below, only tightness of the studentized statistic is
needed; the diverging sequence \(\rho_n\) provides the never-empty padding.
Thus
\[
  E_n=
  \left\{
    |\,\widehat z_g-z_g(P)\,|
    \le
    \frac{\widehat c_{n,\alpha}\widehat s_g+\rho_n}{\sqrt n}
    \quad\text{for all }g=1,\ldots,K
  \right\}
\]
satisfies \(\Pr(E_n)\to1\), because \(\sqrt n(\widehat z-z(P))=O_p(1)\) and
\(\rho_n\to\infty\).

Fix \(L\in[0,\bar L]\) with \(\mathcal A_L(P)\ne\emptyset\), and take any
\(\alpha\in\mathcal A_L(P)\).  By the definition of the population feasible
set in Section~7,
\[
  A_0\alpha=0,\qquad A_\tau\alpha=z(P),\qquad B_L\alpha\le d_L .
\]
On \(E_n\), the diagonal equation gives
\[
  |(A_\tau\alpha)_g-\widehat z_g|
  =
  |z_g(P)-\widehat z_g|
  \le r_{g,n}
  \quad(g=1,\ldots,K),
\]
and the deterministic inequalities give
\[
  B_L\alpha\le d_L\le d_L+\rho_n n^{-1/2}\one .
\]
Therefore
\[
  \mathcal A_L(P)\subseteq \widehat{\mathcal A}_{L,n}
  \quad\text{on }E_n .
\]
Since \(\mathcal A_L(P)\) is nonempty, the relaxed sample set is nonempty on
the same event.  Hence
\[
  \Pr\{\widehat{\mathcal A}_{L,n}\ne\emptyset\}\ge \Pr(E_n)\to1 .
\]
This remains true regardless of whether the unrelaxed sample system
\(A_\tau\alpha=\widehat z,\ B_L\alpha\le d_L\) is feasible.

The endpoint containment is now a deterministic LP monotonicity calculation.
On \(E_n\), minimizing a linear functional over the larger set
\(\widehat{\mathcal A}_{L,n}\) can only weakly decrease the value, and
maximizing over the larger set can only weakly increase it:
\[
  \widehat L_h(L)
  =
  \min_{\alpha\in\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha
  \le
  \min_{\alpha\in\mathcal A_L(P)}a_h^\transpose\alpha
  =
  L_h(L;P),
\]
\[
  \widehat U_h(L)
  =
  \max_{\alpha\in\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha
  \ge
  \max_{\alpha\in\mathcal A_L(P)}a_h^\transpose\alpha
  =
  U_h(L;P).
\]
Thus
\[
  [L_h(L;P),U_h(L;P)]
  \subseteq
  [\widehat L_h(L),\widehat U_h(L)]
  \quad\text{on }E_n,
\]
and the advertised pointwise endpoint coverage follows from
\(\Pr(E_n)\to1\).  The proof uses the support-envelope conclusion of
Theorem~\ref{thm:joint-envelope} only to interpret the two LP endpoint values
as the full algebraic envelope.

It remains to prove coverage of \(L_h^\star(P)\).  Suppose
\[
  L_h^\star(P)=\inf\{\ell\in[0,\bar L]:L_h(\ell;P)\le0\le U_h(\ell;P)\}
\]
belongs to \([0,\bar L]\).  Assumption~\ref{ass:frontier-contact} gives a
closed zero-contact set of one of the three listed types: a single
transversal contact, a finite separated tie, or a compact flat face.  Hence
\[
  0\in[L_h(L_h^\star(P);P),U_h(L_h^\star(P);P)] .
\]
By Theorem~\ref{thm:joint-envelope}, the interval is exactly the image of
\(\mathcal A_{L_h^\star(P)}(P)\) under \(a_h^\transpose\alpha\), so there is
an array \(\alpha^\star\in\mathcal A_{L_h^\star(P)}(P)\) such that
\[
  a_h^\transpose\alpha^\star=0 .
\]
The containment argument already proved implies
\[
  \alpha^\star\in\widehat{\mathcal A}_{L_h^\star(P),n}
  \quad\text{on }E_n .
\]
Consequently, on \(E_n\),
\[
  \widehat L_h(L_h^\star(P))
  \le
  a_h^\transpose\alpha^\star
  =
  0
  \le
  \widehat U_h(L_h^\star(P)),
\]
so \(L_h^\star(P)\in\widehat C_{h,n}^\star\).  Therefore
\[
  \Pr\{L_h^\star(P)\in\widehat C_{h,n}^\star\}\ge \Pr(E_n)\to1 .
\]

Finally assume Conjecture~\ref{conj:law-sharp}.  Then the law-level ACRT
identified interval equals the corrected mean-completion interval
\[
  \Theta_I(P)
  =
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)] .
\]
By the definition of the completion-compatible feasible set in Section~7,
\(\mathcal A_L^{\mathrm{mc}}(P)\subseteq\mathcal A_L(P)\).  Applying the
same linear objective \(a_h^\transpose\alpha\) to a smaller feasible set gives
the deterministic nesting
\[
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
  \subseteq
  [L_h(L;P),U_h(L;P)] .
\]
Combining this nesting with the endpoint containment already established,
on \(E_n\) one has
\[
  \Theta_I(P)
  =
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
  \subseteq
  [L_h(L;P),U_h(L;P)]
  \subseteq
  [\widehat L_h(L),\widehat U_h(L)] .
\]
Since \(\Pr(E_n)\to1\), this proves the conditional coverage statement for
the corrected law-sharp ACRT interval.
\end{proof}

\paragraph{\S12 Sanity check.}
Take the two-dose corner \(K=1\), \(d_0=0\), \(d_1>0\), and use the canonical
forward-difference stencil \(q_{11}=1/d_1\), \(q_{01}=-1/d_1\).  Because the
baseline row is \(\alpha_{01}=0\) and the diagonal CGS input is
\(\alpha_{11}=\tau_1(P)\), the algebraic envelope collapses to the point
\[
  L_1(L;P)=U_1(L;P)=\frac{\tau_1(P)}{d_1}
\]
whenever the box and regularity inequalities do not rule out the diagonal
input.  The relaxed sample set is
\[
  |\,\alpha_{11}-\widehat\tau_1\,|\le r_{1,n}
\]
intersected with the relaxed deterministic faces, so the endpoint interval is
\[
  [\widehat L_1(L),\widehat U_1(L)]
  =
  \left[
    \frac{\widehat\tau_1-r_{1,n}}{d_1},
    \frac{\widehat\tau_1+r_{1,n}}{d_1}
  \right]
\]
up to the irrelevant relaxed box truncation.  Since
\(\sqrt n(\widehat\tau_1-\tau_1(P))=O_p(1)\) and
\(\rho_n\to\infty\),
\[
  \Pr\left\{
    \frac{\tau_1(P)}{d_1}
    \in
    \left[
      \frac{\widehat\tau_1-r_{1,n}}{d_1},
      \frac{\widehat\tau_1+r_{1,n}}{d_1}
    \right]
  \right\}\to1 .
\]
Thus the general relaxed LP reduces to the ordinary cell-mean Wald interval
with an additional vanishing feasibility padding in the point-identified
two-dose case.

\paragraph{\S13 Counterexample or minimality check.}
The padding and the relaxation of deterministic faces are necessary for the
conjecture's nonemptiness clause.  Use the same \(K=1\) corner, set
\(\tau_1(P)=\overline y\), and suppose the root-\(n\) limit of
\(\widehat\tau_1-\tau_1(P)\) is nondegenerate and centered.  The population
LP is feasible at the boundary point \(\alpha_{11}=\overline y\).  The
unrelaxed sample LP imposes both \(\alpha_{11}=\widehat\tau_1\) and
\(\alpha_{11}\le\overline y\), so it is infeasible whenever
\(\widehat\tau_1>\overline y\).  That event has limiting probability
\(1/2\) in the symmetric normal case and, more generally, need not vanish.

If one relaxes only the stochastic equality but not the deterministic upper
box face, the same boundary problem persists unless the equality relaxation
is wide enough to reach back to \(\overline y\).  With a fixed Gaussian
critical value and no diverging padding, the feasibility probability at this
boundary is only the corresponding fixed normal tail probability, not one.
The sequence \(\rho_n\to\infty\), \(\rho_n/\sqrt n\to0\), fixes exactly this:
it is asymptotically invisible for the population envelope but large enough
on the root-\(n\) scale to include the boundary population feasible point
with probability tending to one.  Dropping this device would refute the
"remains nonempty with probability approaching one" part of the conjecture.
