% =====================================================================
%  thmsmith Stage 0 derivation skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_contdid\_acrt\_lipschitz, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
%  - Immutability is SCOPED to section headers, macro names, and the
%    preamble. The PLACEMENT of theorem/proposition/lemma/assumption
%    environments is YOUR responsibility: a `theorem` env may be freely
%    moved into whichever fixed-header section fits (e.g. promote the
%    field-level result from \S11 into \S9). Relocating a block between
%    fixed headers is NOT a skeleton violation.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{pid\_contdid\_acrt\_lipschitz} / \texttt{v1}%
  \\ \large\textit{Finite-grid algebraic envelopes for continuous-treatment DiD ACRT under cross-dose regularity}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
For a fixed target dose \(d_h\), this note studies the finite-grid average
causal response on the treated,
\(\theta_h=\operatorname{ACRT}(d_h)\), in a two-period continuous-treatment
DiD design where generalized parallel trends identify only the diagonal
treated-type effects and leave cross-dose comparisons contaminated by
selection terms.  The estimand-defining functionals are the algebraic
envelope \(\Theta_h^{\mathrm{alg}}(L;P)=[L_h(L;P),U_h(L;P)]\), obtained by
optimizing the linear ACRT stencil over the joint feasible array of cross-dose
ATT coordinates that matches the observed
Callaway--Goodman-Bacon--Sant'Anna inputs and satisfies boundedness together
with either row-wise Lipschitz or isotonic regularity, and the stricter
mean-completion envelope
\(\Theta_h^{\mathrm{mc}}(L;P)=[L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\),
which additionally imposes
\(\underline y\le \beta_h(P)+\alpha_{jh}\le\overline y\) for every off-arm
coordinate, where \(\beta_h(P)=\mu_{1h}(P)-\tau_h(P)\).  Both are computable
maps of the observable law \(P\) because their endpoints are finite LP values
on explicitly described polytopes.  The target causal estimand itself remains
the law-level response \(\operatorname{ACRT}(d_h)\), not an envelope endpoint.
The supporting theorem concerns \(\Theta_h^{\mathrm{alg}}(L;P)\) as an outer
algebraic bound, while the conjecture sub-stages will verify or refute three
further claims: law-level sharpness for \(\Theta_h^{\mathrm{mc}}(L;P)\), a
parametric-LP characterization of the critical Lipschitz constant
\(L_h^\star(P)\), and relaxed plug-in inference for the endpoint interval and
the critical frontier.
\end{abstract}

\section{Introduction}
Many DiD applications assign treatment in amounts rather than in a binary
on/off format.  A policy may change a reimbursement rate, a tax schedule, a
subsidy intensity, or an exposure dosage.  In those settings a researcher
often wants the causal response to a local dose increase for units observed at
a particular treatment level \(d_h\), not only the level effect of moving from
zero treatment to \(d_h\).  The difficulty is that cross-dose comparisons are
not identified by generalized parallel trends alone, so the sign and magnitude
of \(\operatorname{ACRT}(d_h)\) depend on how one constrains the latent array
\(\operatorname{ATT}(d_j\mid d_h)\) across conditioning doses.

Callaway, Goodman-Bacon, and Sant'Anna \cite{CallawayGoodmanBaconSantAnna2021}
show that continuous-treatment DiD identifies treated-type parameters on the
diagonal but that differences across treatment doses inherit selection bias.
That paper is the writing exemplar for this note, and the present introduction
keeps the same register: continuous doses are economically common; the
identified treated-type building blocks are useful but not sufficient for
cross-dose causal-response claims; and stronger structure is needed before a
local response can be interpreted causally.  The closest external templates
for that extra structure are shape-restricted partial-identification results,
such as Manski and Pepper \cite{ManskiPepper2000}, and LP-value
characterizations of sharp bounds, such as Voronin \cite{Voronin2025}.

The contribution targeted here is narrower and more explicit than a generic
shape-restriction slogan.  Fix a finite dose grid and a local finite-difference
stencil \(q_{\cdot h}\) for \(\operatorname{ACRT}(d_h)\).  The note studies one
joint feasible set for the entire cross-dose ATT array, formed by the observed
Callaway--Goodman-Bacon--Sant'Anna diagonal inputs, the definitional baseline
row, bounded outcomes, and either row-wise Lipschitz or isotonic regularity in
the conditioning dose.  If the supporting theorem is correct, the algebraic
ACRT envelope is the image of that single feasible polytope under the linear
map \(\alpha\mapsto \theta_h(\alpha)\).  If the remaining conjectures are
confirmed, the same setup also yields a law-level sharpness statement for the
mean-completion sub-envelope obtained by intersecting that polytope with the
off-arm bounded-mean inequalities
\(\underline y\le \beta_h(P)+\alpha_{jh}\le\overline y\), an explicit
critical-regularity frontier \(L_h^\star(P)\), and a usable relaxed-LP
inference procedure.

The payoff is practical.  In continuous-dose DiD applications, including the
Medicare setting emphasized by
\cite{CallawayGoodmanBaconSantAnna2021} and the adjacent switcher or no-stayer
designs of \cite{deChaisemartinDHaultfoeuillePasquierSowVazquezBare2022} and
\cite{deChaisemartinDHaultfoeuilleVazquezBare2024}, the relevant empirical
question is often not whether a single local contrast is positive under no
selection bias, but how much cross-dose regularity is needed before the sign
of the local causal response becomes ambiguous.  The finite-grid envelope and
its critical constant are intended as that reporting object.

\paragraph{Motivating conjecture(s).}
\textbf{Conjecture 1 (law-sharp).} Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, write
\(\beta_h(P)=\mu_{1h}(P)-\tau_h(P)\) and define
\[
  \mathcal A_L^{\mathrm{mc}}(P)=
  \{\alpha\in\mathcal A_L(P):
    \underline y\le \beta_h(P)+\alpha_{jh}\le \overline y
    \ \forall h,\ \forall j\neq h\}.
\]
Then the mean-completion envelope
\[
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
  =
  \{\theta_h(\alpha):\alpha\in\mathcal A_L^{\mathrm{mc}}(P)\}
  =
  \Theta_h^{\mathrm{mc}}(L;P)
\]
is law-sharp:
\[
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
  =
  \{\operatorname{ACRT}(d_h;Q):Q \text{ is a finite bounded latent law
  preserving } P \text{ and Assumptions } \ref{ass:consistency-noanticip}
  \text{--}\ref{ass:regularity}\}.
\]
In particular, \([L_h(L;P),U_h(L;P)]\) remains an outer algebraic bound, while
no endpoint of the corrected mean-completion interval is an outer-bound
artifact caused by an unrealizable cross-dose ATT array.

\textbf{Conjecture 2 (critical-l).} Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, the endpoint
functions \(L\mapsto L_h(L;P)\) and \(L\mapsto U_h(L;P)\) are monotone
piecewise linear on every finite grid.  The critical constant
\[
  L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}
\]
is equivalently the optimum of a finite parametric LP feasibility problem in
\((\alpha,L)\):
\[
 \min_{\alpha,L}\ L
 \quad\text{subject to}\quad
 A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ 
 \theta_h(\alpha)=0,\ 
 \underline y\le\alpha_{jh}\le\overline y,\ 
 |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|,\ 
 0\le L\le\bar L .
\]
For each nonsingular active basis of this LP, \(L_h^\star(P)\) is an affine
function of \(b_{\mathrm{CGS}}(P)\) on the region where that basis remains
optimal; globally it is the lower envelope of these basis-specific affine
pieces.

\textbf{Conjecture 3 (plugin-inference).} Under Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact}, define
\(\widehat L_h(L)\), \(\widehat U_h(L)\), and
\(\widehat L_h^\star\) by replacing \(b_{\mathrm{CGS}}(P)\) with an
asymptotically linear estimate and relaxing equality and inequality
constraints by calibrated Gaussian or bootstrap critical values.  Then the
resulting confidence set covers the algebraic envelope endpoints
\([L_h(L;P),U_h(L;P)]\) and the critical constant \(L_h^\star(P)\) pointwise,
and remains nonempty with probability approaching one even when the unrelaxed
sample LP is infeasible.  If Conjecture~\ref{conj:law-sharp} holds, the same
endpoint confidence set covers the corrected law-sharp ACRT interval through
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
\subseteq [L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)]\), or
after replacing the sample LP by the analogous relaxed mean-completion
program.

\section{Related work and positioning}
Callaway, Goodman-Bacon, and Sant'Anna \cite{CallawayGoodmanBaconSantAnna2021}
are the anchor because they define the continuous-treatment DiD treated-type
and ACRT objects and isolate the cross-dose selection-bias problem that this
note takes as primitive.  De Chaisemartin, D'Haultfoeuille, Pasquier, Sow, and
Vazquez-Bare \cite{deChaisemartinDHaultfoeuillePasquierSowVazquezBare2022}
provide an adjacent switcher-based continuous-treatment DiD design, so they are
a natural consumer once an ACRT envelope is available.  De Chaisemartin,
D'Haultfoeuille, and Vazquez-Bare
\cite{deChaisemartinDHaultfoeuilleVazquezBare2024} study the no-stayer case,
which sharpens the motivation for replacing missing comparison groups by
cross-dose regularity.

Manski and Pepper \cite{ManskiPepper2000} supply the closest identification
template: credible shape restrictions can tighten a treatment-effect set
without forcing point identification.  Ishihara \cite{Ishihara2017} is the
closest nonseparable-treatment-effect precedent for shape restrictions that
coordinate otherwise separate latent objects.  Armstrong and Kolesar
\cite{ArmstrongKolesar2018} are not a DiD paper, but their convex-smoothness
view clarifies why a Lipschitz restriction belongs in the same family of
evaluable linear-functional problems.  Relative to these papers, the present
note is more specialized: the feasible object is not a generic response
surface, but the cross-dose ATT array indexed by treatment dose and
conditioning dose in the Callaway--Goodman-Bacon--Sant'Anna decomposition.
Molinari \cite{Molinari2020} provides the closest sharpness discipline: the
identified set should be the image of latent laws consistent with the observed
distribution and the maintained assumptions, which is why this note separates
the algebraic envelope \(\Theta_h^{\mathrm{alg}}(L;P)\) from the
completion-compatible interval \(\Theta_h^{\mathrm{mc}}(L;P)\).

Chernozhukov, Lee, and Rosen \cite{ChernozhukovLeeRosen2013} frame partially
identified parameters as optimized extrema and explain the nonregularity of
plug-in bound estimators; that is the closest positioning for the critical
frontier \(L_h^\star(P)\).  Kaido, Molinari, and Stoye
\cite{KaidoMolinariStoye2019}, Belloni, Bugni, and Chernozhukov
\cite{BelloniBugniChernozhukov2018}, and Stoye \cite{Stoye2020} provide the
projection, many-inequality, and never-empty interval inference templates that
motivate Conjecture 3.  Voronin \cite{Voronin2025} is the closest LP-specific
reference because the endpoint functional here is literally an LP value once
the finite grid and regularity inequalities are fixed.  None of these papers,
however, derives the continuous-treatment DiD ACRT envelope from one joint
cross-dose ATT polytope or treats law-level sharpness as a separate latent
completion question.

The in-repository predecessors sharpen the same distinction.  The candidate
\texttt{pid\_dose\_response\_iv\_v1} already uses a finite LP envelope and a
critical-radius pattern, but for a continuous-IV dose-response target rather
than a continuous-treatment DiD ACRT target.  The accepted
\texttt{pid\_did\_anticipation\_bounded\_v1} already uses support-function
interval logic in DiD, but not with cross-dose ATT coordinates.  The
downgraded \texttt{pid\_dose\_response\_shape\_v1} is especially relevant
because it records the law-level pasting risk that motivates keeping algebraic
feasibility separate from causal sharpness here.  The current note therefore
positions Theorem~\ref{thm:joint-envelope} as an algebraic PartialID envelope,
not yet as a complete causal identified-set theorem.

\section{Formal setup}
Fix a target dose index \(h\in\{1,\ldots,K\}\).  The observable law is
\(P=\mathcal L(O)\) for the two-period array \(O=(Y_0,Y_1,D)\), where
\(D\in\mathcal D=\{d_0<d_1<\cdots<d_K\}\) is observed on a fixed finite ordered
grid and \(d_0=0\) is the untreated baseline dose.  For each dose \(d_j\), let
\(Y_1(d_j)\) denote the post-period potential outcome under that dose.  The
latent mean array is
\[
  \alpha_{jh}=\operatorname{ATT}(d_j\mid d_h)
  =\E[Y_1(d_j)-Y_1(d_0)\mid D=d_h],
\]
so rows index treatment doses and columns index conditioning doses.

Write the observed level-change contrast in conditioning group \(h\) as
\[
  \mu_{1h}(P)=\E[Y_1\mid D=d_h], \qquad
  m_h(P)=\E[Y_1-Y_0\mid D=d_h], \qquad
  \tau_h(P)=m_h(P)-m_0(P), \qquad
  \beta_h(P)=\mu_{1h}(P)-\tau_h(P).
\]
Under the maintained generalized parallel-trends convention, the diagonal
treated-type effects are identified by \(\alpha_{hh}=\tau_h(P)\).  The
definitional baseline row is \(\alpha_{0h}=0\) for every \(h\).  Let
\[
  b_{\mathrm{CGS}}(P)=\bigl((0)_{h=0}^K,(\tau_h(P))_{h=0}^K\bigr),
\]
and write \(A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P)\) for the linear system
consisting exactly of those baseline and diagonal equations.

Whenever a latent law \(Q\) preserves \(P\), satisfies consistency, and obeys
the diagonal restriction \(\alpha_{hh}(Q)=\tau_h(P)\), the baseline
post-period mean in conditioning group \(h\) is pinned down by
\[
  \E_Q[Y_1(d_0)\mid D=d_h]=\beta_h(P),
\]
because \(Y_1(d_h)=Y_1\) almost surely on \(\{D=d_h\}\).  Consequently every
off-arm post-period coordinate must satisfy
\[
  \E_Q[Y_1(d_j)\mid D=d_h]
  =
  \beta_h(P)+\alpha_{jh}(Q),
  \qquad j\neq h.
\]

For the fixed target group \(h\), let \(q_h=(q_{0h},\ldots,q_{Kh})\) be a
locked local finite-difference stencil satisfying
\(\sum_{j=0}^K q_{jh}=0\) and \(\sum_{j=0}^K q_{jh}(d_j-d_h)=1\).  The target
response associated with a latent law \(Q\) is
\[
  \theta_h(Q)=\operatorname{ACRT}(d_h;Q)
  =\sum_{j=0}^K q_{jh}\alpha_{jh}(Q),
\]
where \(\alpha_{jh}(Q)\) is the ATT entry induced by \(Q\).  The identified set
at the law level is therefore
\[
  \Theta_I(P)=
  \{\theta_h(Q): Q \text{ is a latent law for }
    (Y_0,Y_1,Y_1(d_0),\ldots,Y_1(d_K),D)
    \text{ consistent with } P \text{ and the maintained restrictions}\}.
\]
Stage 0.0 does not assume that every algebraically feasible array \(\alpha\) is
realizable by such a law; instead it defines an explicit algebraic outer set
and a stricter completion-compatible set whose image is the candidate
law-sharp interval.  Equality with \(\Theta_I(P)\) is deferred to
Conjecture~\ref{conj:law-sharp}.

\paragraph{Locked parameters.}
\begin{itemize}
  \item qid: \texttt{pid\_contdid\_acrt\_lipschitz}
  \item specialization: \texttt{v1}
  \item observable distribution: \(P\) is the observable law of a two-period continuous-treatment DiD array \(O=(Y_0,Y_1,D)\), with \(D\) taking values on a fixed ordered finite grid \(\mathcal D=\{d_0<d_1<\cdots<d_K\}\), where \(d_0=0\) denotes the untreated or baseline dose.
  \item parameter \(\theta\): The latent causal array is \(\alpha_{j h}=\operatorname{ATT}(d_j\mid d_h)=\E[Y_1(d_j)-Y_1(d_0)\mid D=d_h]\).  The diagonal entries \(\alpha_{h h}\), the definitional baseline row \(\alpha_{0h}=0\), and the Callaway--Goodman-Bacon--Sant'Anna observed level-change contrasts \(\tau_h(P)=\E[Y_1-Y_0\mid D=d_h]-\E[Y_1-Y_0\mid D=d_0]\) are taken as the identified inputs under generalized parallel trends.  The target is the finite-grid average causal response on the treated at dose \(d_h\),
  \[
    \theta_h=\operatorname{ACRT}(d_h)
    =\sum_{j=0}^K q_{j h}\alpha_{j h},
  \]
  where \(q_{\cdot h}\) is a locked local finite-difference stencil satisfying \(\sum_jq_{j h}=0\) and \(\sum_jq_{j h}(d_j-d_h)=1\).
  \item identifying restrictions: consistency, no anticipation, generalized parallel trends for the diagonal treated-type parameters, bounded outcomes \(\alpha_{j h}\in[\underline y,\overline y]\), and either the row-wise structural Lipschitz restriction \(|\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\) for all \(j,h,h'\), or the row-wise isotonic restriction in the conditioning group \(d_h\).
  \item bounding functional: The algebraic finite-grid envelope \([L_h(L;P),U_h(L;P)]\), the image of the joint feasible nuisance polytope under the linear map \(\alpha\mapsto\theta_h\), together with the critical regularity constant \(L_h^\star(P)=\inf\{L:0\in[L_h(L;P),U_h(L;P)]\}\).  Law sharpness of this algebraic envelope as a causal interval is the separate completion claim in Conjecture~\ref{conj:law-sharp}.
\end{itemize}

\section{Assumptions}
\begin{assumption}[Finite dose grid and bounded outcomes]\label{ass:grid-bounds}
The dose grid \(\mathcal D=\{d_0<\cdots<d_K\}\) is fixed, each dose group has
positive probability, and every level treatment effect satisfies
\(\alpha_{j h}\in[\underline y,\overline y]\).  The same compact interval is
also used as the support bound for the off-arm completion kernels introduced
in Assumption~\ref{ass:completion}.  This keeps both the algebraic polytope and
the completion-compatible mean restrictions finite-dimensional.
\end{assumption}

\begin{assumption}[Consistency and no anticipation]\label{ass:consistency-noanticip}
Observed outcomes satisfy \(Y_1=Y_1(D)\), and the pre-period outcome is not
affected by the later dose.  This is the continuous-treatment DiD convention
used by \cite{CallawayGoodmanBaconSantAnna2021}.
\end{assumption}

\begin{assumption}[CGS generalized parallel trends inputs]\label{ass:cgs-inputs}
The generalized parallel-trends assumptions of
\cite{CallawayGoodmanBaconSantAnna2021} identify
\(\tau_h(P)=\E[Y_1-Y_0\mid D=d_h]-\E[Y_1-Y_0\mid D=d_0]\) and hence the
diagonal treated-type effects \(\alpha_{hh}=\tau_h(P)\).  Together with the
definitional baseline rows \(\alpha_{0h}=0\), these are exactly the rows in
\(A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P)\).  This assumption imports the
identified CGS inputs but does not impose strong parallel trends or set
cross-dose selection bias to zero.
\end{assumption}

\begin{assumption}[Structural cross-dose regularity]\label{ass:regularity}
For the Lipschitz version, a finite \(L\in[0,\bar L]\) is fixed and each
treatment row \(h\mapsto\alpha_{j h}\) obeys
\(|\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\).  For the isotonic version,
each row is monotone in the conditioning group.  These are structural
cross-dose variants of the monotone and smoothness restrictions used in
\cite{ManskiPepper2000} and \cite{ArmstrongKolesar2018}.
\end{assumption}

\begin{assumption}[Conditional finite off-arm completion]\label{ass:completion}
For the sharpness question, a latent law \(Q\) preserves the full observed law
\(P\), satisfies consistency and no anticipation, and sets
\(Y_1(d_h)=Y_1\) almost surely on each observed cell \(\{D=d_h\}\).  Conditional
on \((Y_0,Y_1,D=d_h)\), the off-arm vector \((Y_1(d_j))_{j\neq h}\) may be
assigned by a finite product kernel supported on
\([\underline y,\overline y]^K\).  Thus the completion argument discretizes
only the unobserved off-arm coordinates and does not impose finite support on
the observed on-arm outcome \(Y_1\).  Consequently every realizable array obeys
\(\underline y\le \beta_h(P)+\alpha_{jh}(Q)\le\overline y\) for all
\(h\) and all \(j\neq h\).
\end{assumption}

\begin{assumption}[Sampling and LP regularity]\label{ass:sampling-lp}
The sample is iid across units; the empirical CGS input vector
\(\widehat b_{\mathrm{CGS}}\) is asymptotically linear and root-\(n\) normal;
the population LPs are feasible and finite; and on each regular active region
the endpoint value has a nonempty compact dual solution set.  This is the
finite-dimensional LP setup used in \cite{Voronin2025} and the
projection-inference setup of \cite{KaidoMolinariStoye2019}.
\end{assumption}

\begin{assumption}[Critical-frontier contact]\label{ass:frontier-contact}
For inference on \(L_h^\star(P)\), the zero-contact set is either a singleton
with nonzero one-sided slope in \(L\), a finite tie set with separated
candidate slopes, or a compact flat face for which the support-function
directional derivative exists.  This is the standard nonsmooth-contact
taxonomy used for frontier and interval inversion.
\end{assumption}

\section{Estimand-defining functional}
The observable input is the vector \(b_{\mathrm{CGS}}(P)\) of baseline and
diagonal treated-type restrictions.  For each fixed \(L\in[0,\bar L]\), define
the feasible cross-dose array
\[
  \mathcal A_L(P)=
  \left\{\alpha\in[\underline y,\overline y]^{(K+1)^2}:
    A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\
    |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|
    \ \forall j,h,h'
  \right\}.
\]
The isotonic alternative replaces the Lipschitz inequalities by
\[
  \mathcal A_{\mathrm{iso}}(P)=
  \left\{\alpha\in[\underline y,\overline y]^{(K+1)^2}:
    A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\
    \alpha_{j0}\le\alpha_{j1}\le\cdots\le\alpha_{jK}
    \ \forall j
  \right\},
\]
or the reversed order if the application locks decreasing selection in dose.
The ACRT linear functional is
\[
  \theta_h(\alpha)=\sum_{j=0}^K q_{jh}\alpha_{jh}.
\]
The completion-compatible subset of the Lipschitz feasible set is
\[
  \mathcal A_L^{\mathrm{mc}}(P)=
  \left\{\alpha\in\mathcal A_L(P):
    \underline y\le \beta_h(P)+\alpha_{jh}\le \overline y
    \ \forall h,\ \forall j\neq h
  \right\},
\]
and \(\mathcal A_{\mathrm{iso}}^{\mathrm{mc}}(P)\) is defined analogously with
\(\mathcal A_{\mathrm{iso}}(P)\) in place of \(\mathcal A_L(P)\).  These are
exactly the arrays whose implied off-arm conditional means are compatible with
the bounded completion class from Assumption~\ref{ass:completion}.
The algebraic endpoints are the explicit functionals
\[
  L_h(L;P)=\inf_{\alpha\in\mathcal A_L(P)} \theta_h(\alpha), \qquad
  U_h(L;P)=\sup_{\alpha\in\mathcal A_L(P)} \theta_h(\alpha),
\]
with the same definitions over \(\mathcal A_{\mathrm{iso}}(P)\) in the isotonic
case.  The associated algebraic envelope is
\[
  \Theta_h^{\mathrm{alg}}(L;P)=[L_h(L;P),U_h(L;P)].
\]
The mean-completion endpoints are
\[
  L_h^{\mathrm{mc}}(L;P)=\inf_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}
  \theta_h(\alpha), \qquad
  U_h^{\mathrm{mc}}(L;P)=\sup_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}
  \theta_h(\alpha),
\]
with the analogous isotonic definitions over
\(\mathcal A_{\mathrm{iso}}^{\mathrm{mc}}(P)\).  The associated
completion-compatible envelope is
\[
  \Theta_h^{\mathrm{mc}}(L;P)=
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)].
\]
By construction,
\(\Theta_h^{\mathrm{mc}}(L;P)\subseteq\Theta_h^{\mathrm{alg}}(L;P)\), so
\(\Theta_h^{\mathrm{alg}}(L;P)\) is an outer bound for the law-level
identified set \(\Theta_I(P)\).  The corrected law-sharpness question is
whether \(\Theta_I(P)=\Theta_h^{\mathrm{mc}}(L;P)\).

\section{Target causal estimand}
The target causal estimand is the finite-grid average causal response on the
treated at the locked dose \(d_h\),
\[
  \theta_h=\operatorname{ACRT}(d_h)
  =\sum_{j=0}^K q_{jh}\operatorname{ATT}(d_j\mid d_h)
  =\sum_{j=0}^K q_{jh}\E[Y_1(d_j)-Y_1(d_0)\mid D=d_h].
\]
This is a scalar feature of the latent causal law, not a feature of the
observable law \(P\) alone.  The role of Section~7 is therefore not to redefine
\(\theta_h\), but to provide a computable observable functional whose values
bound the set of admissible \(\theta_h\) under the maintained restrictions.
When strong cross-dose assumptions collapse the feasible array to a singleton,
\(\Theta_I(P)\) becomes a point and \(\theta_h\) is identified; otherwise the
conclusion is an interval containment statement rather than an equality.  Under
the bounded completion class from Assumption~\ref{ass:completion}, the
candidate sharp interval is \(\Theta_h^{\mathrm{mc}}(L;P)\), while
\(\Theta_h^{\mathrm{alg}}(L;P)\) remains the larger algebraic outer bound.

\section{Main theorems}
\begin{theorem}[Theorem 1: Mean-completion law-sharpness]\label{prop:law-sharp-mended}\label{conj:law-sharp}
Confirmed after object correction: write \(\mu_{1h}(P)=\E_P[Y_1\mid D=d_h]\) and \(\beta_h(P)=\mu_{1h}(P)-\tau_h(P)\), define \(\mathcal A_L^{\mathrm{mc}}(P)=\{\alpha\in\mathcal A_L(P):\underline y\le \beta_h(P)+\alpha_{jh}\le\overline y\ \forall h,\ \forall j\ne h\}\), and set \(L_h^{\mathrm{mc}}(L;P)=\min_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha)\), \(U_h^{\mathrm{mc}}(L;P)=\max_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha)\). Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, with the algebraic object replaced by this mean-completion polytope, \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\) is law-sharp for the finite-grid ACRT over latent completions preserving \(P\) whose off-arm potential outcomes are assigned by finite \([\underline y,\overline y]\)-supported product kernels conditional on the observed data: every such completion maps into \(\mathcal A_L^{\mathrm{mc}}(P)\), and every \(\alpha\in\mathcal A_L^{\mathrm{mc}}(P)\) is realized by such a completion.
\end{theorem}

This is an object correction, not a new identifying restriction on the law class.  It keeps the original finite-grid continuous-treatment DiD ACRT target, but removes arrays whose implied off-arm potential-outcome means cannot be generated under the maintained bounded off-arm support.

\begin{theorem}[Theorem 2: Critical Lipschitz frontier]\label{thm:critical-l}\label{conj:critical-l}
Confirmed critical-L result. Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, define \(\mathcal F_0(P)=\{(\alpha,L):A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ \theta_h(\alpha)=0,\ \underline y\le\alpha_{jh}\le\overline y,\ |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\ \forall j,h,h',\ 0\le L\le\bar L\}\). The endpoint maps \(L\mapsto L_h(L;P)\) and \(L\mapsto U_h(L;P)\) are respectively nonincreasing and nondecreasing finite piecewise-linear functions on \([0,\bar L]\). The critical constant \(L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}\), with value \(+\infty\) if the zero-contact set is empty, is exactly \(\min\{L:(\alpha,L)\in\mathcal F_0(P)\}\), with the same \(+\infty\) convention for LP infeasibility. If \(B\) ranges over the finite nonsingular active bases of this LP, each basis has an affine candidate value \(L_B^\star(P)=a_B^\transpose b_{\mathrm{CGS}}(P)+c_B\) on the polyhedral region where that basis is feasible and optimal, and globally \(L_h^\star(P)=\min_B L_B^\star(P)\) over feasible optimal basis pieces, i.e. the lower envelope of the basis-specific affine pieces.
\end{theorem}

The theorem turns the regularity radius \(L\) into a computable sensitivity frontier.  For each fixed \(L\), Theorem~\ref{thm:joint-envelope} says that the algebraic ACRT envelope is the image of a finite feasible polytope under the linear stencil \(\alpha\mapsto\theta_h(\alpha)\).  Increasing \(L\) relaxes only the cross-dose Lipschitz inequalities, so the lower endpoint can only move down and the upper endpoint can only move up.

\begin{theorem}[Theorem 3: Relaxed-LP endpoint and frontier confidence set]\label{thm:plugin-inference}\label{conj:plugin-inference}
Confirmed conservative relaxed-LP inference. Define \(\widehat\tau_g=\widehat\mu_g-\widehat\mu_0\) with \(\widehat\mu_g=\sum_i\one\{D_i=d_g\}(Y_{1i}-Y_{0i})/\sum_i\one\{D_i=d_g\}\), set \(r_{g,n}=(\widehat c_{n,\alpha}\widehat s_g+\rho_n)/\sqrt n\), \(\rho_n=\log n\), and \(\widehat{\mathcal A}_{L,n}=\{\alpha:A_0\alpha=0,\ |(A_\tau\alpha)_g-\widehat\tau_g|\le r_{g,n}\ (g=1,\ldots,K),\ B_L\alpha\le d_L+\rho_n n^{-1/2}\one\}\), where \(\widehat c_{n,\alpha}\) is the Gaussian or multiplier-bootstrap \((1-\alpha)\)-critical value for the studentized CGS input vector. With \(a_h^\transpose\alpha=\sum_jq_{jh}\alpha_{jh}\), \(\widehat L_h(L)=\min_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat U_h(L)=\max_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat C_{h,n}^\star=\{\ell\in[0,\bar L]:\widehat L_h(\ell)\le0\le\widehat U_h(\ell)\}\), and \(\widehat L_h^\star=\inf\widehat C_{h,n}^\star\), Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact} imply \(\Pr\{[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)],\ \widehat{\mathcal A}_{L,n}\ne\emptyset\}\to1\) for each fixed feasible \(L\), and \(\Pr\{L_h^\star(P)\in\widehat C_{h,n}^\star\}\to1\); if Conjecture~\ref{conj:law-sharp} holds, the same endpoint interval covers the corrected law-sharp mean-completion ACRT interval \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\) through \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\subseteq[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)]\).
\end{theorem}

The theorem is an inference result for the computable algebraic envelope, not a new point-identification result for \(\operatorname{ACRT}(d_h)\).  The population object remains the LP image \([L_h(L;P),U_h(L;P)]\) from Theorem~\ref{thm:joint-envelope}.  The sample object replaces the identified CGS inputs by their cell-mean estimates and then solves the same endpoint LP after widening the stochastic diagonal equations and the deterministic inequality faces by a root-\(n\) amount.  This is the calibrated-projection construction of \cite{KaidoMolinariStoye2019} specialized to a finite linear program.

\section{Interpretation}
\subsubsection*{Conjecture 1 (law-sharp)}
\textbf{Classification.} Type A, object bug.  The witness lives on a boundary
support face.  In the \(D=d_1\) stratum, consistency gives
\(Y_1(d_1)=Y_1=1\), so
\(\mu_{1,1}(P)=1\).  The diagonal input \(\alpha_{11}=\tau_1(P)=0\) then
forces
\[
  \E_Q[Y_1(d_0)\mid D=d_1]
  =
  \mu_{1,1}(P)-\tau_1(P)
  =
  1.
\]
With support \([0,1]\), this mean places \(Y_1(d_0)\) on the upper boundary
almost surely.  The algebraic vertex with \(\alpha_{21}=1\) asks for
\[
  \E_Q[Y_1(d_2)\mid D=d_1]
  =
  \mu_{1,1}(P)-\tau_1(P)+\alpha_{21}
  =
  2,
\]
outside the maintained off-arm support \([0,1]\).  The kernel LP,
support-function, and critical-\(L\) mechanisms are not false; the array object
omitted the coordinate mean-completion inequalities that any bounded off-arm
completion must satisfy.

\textbf{Naturalness.} The correction follows the standard
observational-equivalence convention for sharp identified sets: characterize
exactly the parameter values generated by latent random variables consistent
with the data and maintained assumptions.  Molinari's survey organizes partial
identification around random variables consistent with the available data and
credible maintained assumptions \cite{Molinari2020}.  The inequalities above
are that convention written for the finite-grid ATT means.  They are not
witness-tailored: without them, the object is not the projection of the
bounded off-arm potential-outcome completion class in
Assumption~\ref{ass:completion}.

\textbf{Vacuity and substance.} The mended class is nonempty.  In the witness
observable law, the completion
\[
\begin{array}{c|ccc}
  D & Y_1(d_0) & Y_1(d_1) & Y_1(d_2)\\ \hline
  d_0 & 0&0&1\\
  d_1 & 1&1&1\\
  d_2 & 0&0&1
\end{array}
\]
preserves \(P\), is \(1\)-Lipschitz at the ATT-array level, and induces
\[
  \alpha=
  \begin{pmatrix}
    0&0&0\\
    0&0&0\\
    1&0&1
  \end{pmatrix}
  \in\mathcal A_1^{\mathrm{mc}}(P).
\]
The motivating regime also survives: finite ordered dose grids, CGS diagonal
inputs, bounded off-arm post-period potential outcomes, and row-wise cross-dose
Lipschitz or isotonic restrictions remain exactly the maintained regime.  The
repair only removes arrays whose implied off-arm potential-outcome means leave
the support interval.

\subsubsection*{Conjecture 2 (critical-l)}
The theorem turns the regularity radius \(L\) into a computable sensitivity
frontier.  For each fixed \(L\), Theorem~\ref{thm:joint-envelope} says that
the algebraic ACRT envelope is the image of a finite feasible polytope under
the linear stencil \(\alpha\mapsto\theta_h(\alpha)\).  Increasing \(L\) relaxes
only the cross-dose Lipschitz inequalities, so the lower endpoint can only move
down and the upper endpoint can only move up.  Consequently, once zero enters
the algebraic interval, it remains in the interval for all larger admissible
regularity radii.

The critical value \(L_h^\star(P)\) is therefore the first amount of
cross-dose roughness at which the observed CGS inputs and the maintained
bounds no longer sign the local causal response algebraically.  If
\(L<L_h^\star(P)\) and the interval is strictly on one side of zero, the sign
of the algebraic ACRT envelope is robust to that degree of cross-dose
regularity.  If \(L\ge L_h^\star(P)\), the same observable inputs admit a
feasible cross-dose ATT array with \(\theta_h=0\), so the sign conclusion has
reached its sensitivity frontier.  This is an algebraic PartialID statement;
law-level causal sharpness still depends on the separate completion claim in
Conjecture~\ref{conj:law-sharp}.

\subsubsection*{Conjecture 3 (plugin-inference)}
The theorem is an inference result for the computable algebraic envelope, not
a new point-identification result for \(\operatorname{ACRT}(d_h)\).  The
population object remains the LP image
\([L_h(L;P),U_h(L;P)]\) from Theorem~\ref{thm:joint-envelope}.  The sample
object replaces the identified CGS inputs by their cell-mean estimates and
then solves the same endpoint LP after widening the stochastic diagonal
equations and the deterministic inequality faces by a root-\(n\) amount.

This is the calibrated-projection construction of
\cite{KaidoMolinariStoye2019} specialized to a finite linear program: the
reported endpoint is obtained by optimizing the projection
\(a_h^\transpose\alpha\) over sample analog constraints relaxed by Gaussian or
bootstrap critical values.  The extra \(\rho_n/\sqrt n\) padding is the
smallest asymptotic device needed for the conjecture's never-empty clause.
It vanishes at the population scale, so it does not change the limiting
identified object, but it dominates \(O_p(n^{-1/2})\) sampling error at
binding faces and therefore prevents boundary laws from producing empty
sample LPs.

The confidence set for \(L_h^\star(P)\) is an inversion of zero-containment:
it reports every regularity radius \(\ell\) whose relaxed endpoint interval
contains zero.  If Conjecture~\ref{conj:law-sharp} holds, the causal ACRT
identified interval is the corrected mean-completion interval
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\), not the larger algebraic
interval.  The relaxed algebraic interval still covers it because the
mean-completion feasible set is nested inside the algebraic feasible set.
Without that separate law-sharpness result, the theorem covers the algebraic
envelope only.

The corrected completion polytope keeps the original finite-grid
continuous-treatment DiD ACRT target, but removes arrays whose implied off-arm
potential-outcome means cannot be generated under the maintained bounded off-arm
support.  The theorem turns the regularity radius \(L\) into a computable
sensitivity frontier.  The sample object replaces the identified CGS inputs by
their cell-mean estimates and then solves the same endpoint LP after widening
the stochastic diagonal equations and the deterministic inequality faces by a
root-\(n\) amount.  If Conjecture~\ref{conj:law-sharp} holds, the causal ACRT
identified interval is the corrected mean-completion interval
\([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\), not the larger algebraic
interval.  The relaxed algebraic interval still covers it because the
mean-completion feasible set is nested inside the algebraic feasible set.

\section{Step-by-step proof}
\subsection*{Supporting lemmas}
\begin{theorem}[Theorem 1: joint polytope support envelope]\label{thm:joint-envelope}
Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, if \(\mathcal A_L(P)\) is nonempty, then the finite-grid ACRT algebraic envelope under the cross-dose restrictions is
\[
  \Theta_h^{\mathrm{alg}}(L;P)=
  [L_h(L;P),U_h(L;P)]
  =
  \{\theta_h(\alpha):\alpha\in\mathcal A_L(P)\}.
\]
The endpoints are attained by finite linear programs.  Equivalently,
\[
  U_h(L;P)=\sigma_{\mathcal A_L(P)}(q_h\otimes e_h),
  \qquad
  L_h(L;P)=-\sigma_{\mathcal A_L(P)}(-q_h\otimes e_h),
\]
where \(\sigma_C(v)=\sup_{x\in C}v^\transpose x\) is the support function.
The same statement holds for the isotonic set
\(\mathcal A_{\mathrm{iso}}(P)\).
\end{theorem}
\begin{proof}
Work in \(\R^{(K+1)^2}\) after stacking \(\alpha\) by conditioning-dose blocks, so the block indexed by \(h\) is \((\alpha_{0h},\ldots,\alpha_{Kh})\).  Under Assumption~\ref{ass:grid-bounds}, the box restriction \([\underline y,\overline y]^{(K+1)^2}\) is compact.  The equations \(A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P)\) are affine, and the Lipschitz inequalities \(|\alpha_{jh}-\alpha_{jh'}|\le L|d_h-d_{h'}|\) can be written as the finite family of linear inequalities \(\alpha_{jh}-\alpha_{jh'}\le L|d_h-d_{h'}|\) and \(\alpha_{jh'}-\alpha_{jh}\le L|d_h-d_{h'}|\).  Hence \(\mathcal A_L(P)\) is the intersection of a compact box with finitely many closed half-spaces and an affine subspace.  If it is nonempty, then it is a nonempty compact convex polytope.

The map \(\theta_h(\alpha)=\sum_{j=0}^K q_{jh}\alpha_{jh}\) is linear and therefore continuous.  By compactness, the extrema
\[
  L_h(L;P)=\min_{\alpha\in\mathcal A_L(P)}\theta_h(\alpha),
  \qquad
  U_h(L;P)=\max_{\alpha\in\mathcal A_L(P)}\theta_h(\alpha)
\]
are attained.  Because both the objective and the feasible set are finite-dimensional and polyhedral, each endpoint is the value of a finite linear program.

It remains to identify the image of \(\mathcal A_L(P)\) under \(\theta_h\).  Since \(\mathcal A_L(P)\) is convex and \(\theta_h\) is linear, the image \(\theta_h(\mathcal A_L(P))\subset\R\) is convex.  Every convex subset of \(\R\) is an interval, and compactness makes it a compact interval.  Its lower and upper endpoints are exactly the attained minimum and maximum above.  Therefore
\[
  \theta_h(\mathcal A_L(P))=[L_h(L;P),U_h(L;P)],
\]
which is the desired set equality.

For the support-function representation, let \(e_h\) be the \((K+1)\)-vector selecting the block indexed by \(h\).  Under the chosen stacking convention, the coefficient vector for \(\theta_h\) is \(q_h\otimes e_h\), so for every feasible \(\alpha\),
\[
  \theta_h(\alpha)=(q_h\otimes e_h)^\transpose \alpha.
\]
Hence
\[
  U_h(L;P)=\sup_{\alpha\in\mathcal A_L(P)}(q_h\otimes e_h)^\transpose\alpha
  =\sigma_{\mathcal A_L(P)}(q_h\otimes e_h).
\]
Applying the same identity to the linear functional \(-\theta_h\) gives
\[
  -L_h(L;P)=\sup_{\alpha\in\mathcal A_L(P)}-(q_h\otimes e_h)^\transpose\alpha
  =\sigma_{\mathcal A_L(P)}(-q_h\otimes e_h),
\]
which rearranges to
\[
  L_h(L;P)=-\sigma_{\mathcal A_L(P)}(-q_h\otimes e_h).
\]
For the isotonic alternative, one replaces the Lipschitz inequalities by the finite linear order restrictions \(\alpha_{j0}\le\alpha_{j1}\le\cdots\le\alpha_{jK}\) (or their reversed counterparts).  The feasible set \(\mathcal A_{\mathrm{iso}}(P)\) is again a nonempty compact convex polytope, and the same compactness, convexity, LP-attainment, and support-function arguments apply verbatim.
\end{proof}

\subsubsection*{Proof of Theorem 1}
\begin{proof}
\textbf{Necessity.} Let \(Q\) be any latent completion preserving \(P\) and
satisfying Assumptions~\ref{ass:consistency-noanticip}--\ref{ass:completion}.
Thus \(Q\) preserves the observed conditional law of \((Y_0,Y_1)\) given
\(D=d_h\), sets \(Y_1(d_h)=Y_1\) on that cell, and assigns the off-arm
coordinates through finite product kernels supported on
\([\underline y,\overline y]\).  Define
\[
  \alpha_{j h}(Q)
  =
  \E_Q[Y_1(d_j)-Y_1(d_0)\mid D=d_h].
\]
The baseline row, diagonal entries, ATT bounds, and row-wise regularity put
\(\alpha(Q)\) in \(\mathcal A_L(P)\).  Moreover, consistency gives
\[
  \E_Q[Y_1(d_h)\mid D=d_h]
  =
  \E_P[Y_1\mid D=d_h]
  =
  \mu_{1h}(P).
\]
The CGS diagonal input gives \(\alpha_{hh}(Q)=\tau_h(P)\).  Therefore, for
\(h>0\),
\[
  \E_Q[Y_1(d_0)\mid D=d_h]
  =
  \E_Q[Y_1(d_h)\mid D=d_h]-\alpha_{hh}(Q)
  =
  \mu_{1h}(P)-\tau_h(P)
  =
  \beta_h(P).
\]
For \(h=0\), the baseline coordinate is on-arm, \(\tau_0(P)=0\), and the same
identity reads
\[
  \E_Q[Y_1(d_0)\mid D=d_0]=\mu_{10}(P)=\beta_0(P).
\]
Consequently, for every off-arm coordinate \(j\ne h\),
\[
  \E_Q[Y_1(d_j)\mid D=d_h]
  =
  \beta_h(P)+\alpha_{j h}(Q).
\]
Assumption~\ref{ass:completion} supports each off-arm \(Y_1(d_j)\) in
\([\underline y,\overline y]\), so its conditional mean lies in that interval.
Hence \(\alpha(Q)\in\mathcal A_L^{\mathrm{mc}}(P)\), and every law-level ACRT
value belongs to the corrected algebraic image.

\textbf{Sufficiency.} Conversely fix
\(\alpha\in\mathcal A_L^{\mathrm{mc}}(P)\).  Work separately in each observed
dose stratum \(D=d_h\), and preserve the conditional observable law of
\((Y_0,Y_1)\) given \(D=d_h\).  Set the on-arm potential outcome
\[
  Y_1(d_h)=Y_1
\]
so consistency is automatic and no finite-support condition is imposed on the
observed on-arm coordinate.  For every off-arm index \(j\ne h\), choose a
finite-support variable \(Z_{jh}\in[\underline y,\overline y]\) with mean
\[
  \E[Z_{jh}\mid D=d_h]=\beta_h(P)+\alpha_{jh}.
\]
Such variables exist because the corrected inequalities put each desired mean
in the support interval: if \(\underline y<\overline y\), use the two-point
law assigning \(\overline y\) with probability
\((\mu-\underline y)/(\overline y-\underline y)\) and \(\underline y\)
otherwise; if \(\underline y=\overline y\), use the degenerate law.  Conditional
on \((Y_0,Y_1,D=d_h)\), assign the off-arm vector
\((Y_1(d_j))_{j\ne h}\) as the product of these finite kernels.

This construction preserves \(P\) because it does not alter
\((Y_0,Y_1,D)\), sets \(Y_1(d_h)=Y_1\) on each observed cell, and uses only
finite off-arm product kernels as required by Assumption~\ref{ass:completion}.
It is intentionally not a finite-support law for the observed variables unless
the observable law \(P\) already has finite support.  Thus the completion is
well typed for the general observable law allowed by the setup.

For \(h>0\), the off-arm baseline coordinate has mean
\[
  \E[Y_1(d_0)\mid D=d_h]=\beta_h(P)+\alpha_{0h}=\beta_h(P),
\]
because the baseline row has \(\alpha_{0h}=0\).  For \(h=0\), the same baseline
mean is on-arm and equals \(\mu_{10}(P)=\beta_0(P)\).  Therefore, for any
off-arm \(j\ne h\),
\[
  \E[Y_1(d_j)-Y_1(d_0)\mid D=d_h]
  =
  (\beta_h(P)+\alpha_{jh})-\beta_h(P)
  =
  \alpha_{jh}.
\]
For the diagonal coordinate \(j=h\),
\[
  \E[Y_1(d_h)-Y_1(d_0)\mid D=d_h]
  =
  \mu_{1h}(P)-\beta_h(P)
  =
  \tau_h(P)
  =
  \alpha_{hh},
\]
where the last equality is the CGS diagonal constraint in \(\mathcal A_L(P)\).
The row-wise Lipschitz or isotonic restriction is inherited from \(\alpha\),
since the maintained regularity is a restriction on the ATT mean array.  Thus
every corrected algebraic point is law-realized.

The set \(\mathcal A_L^{\mathrm{mc}}(P)\) is obtained from
\(\mathcal A_L(P)\) by adding finitely many closed linear inequalities.
The same compact-polytope and support-function argument as
Theorem~\ref{thm:joint-envelope} applies after adding these rows.  Consequently
\(\mathcal A_L^{\mathrm{mc}}(P)\) is a compact convex polytope whenever
nonempty, and the linear image
\(\theta_h(\mathcal A_L^{\mathrm{mc}}(P))\) is the compact interval whose
endpoints are the finite LP values
\(L_h^{\mathrm{mc}}(L;P)\) and \(U_h^{\mathrm{mc}}(L;P)\).  Combining the
necessity and sufficiency directions proves the corrected law-sharpness
equality.
\end{proof}

\subsubsection*{Proof of Theorem 2}
\begin{proof}[Proof of Theorem~\ref{thm:critical-l}]
Stack the array \(\alpha\) in \(\R^{(K+1)^2}\), and let \(c_h\) be the vector
such that \(\theta_h(\alpha)=c_h^\transpose\alpha\).  Assumption
\ref{ass:grid-bounds} gives a fixed finite ordered grid and a compact box
\([\underline y,\overline y]^{(K+1)^2}\).  Assumption~\ref{ass:cgs-inputs}
gives the affine equalities
\[
  A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),
\]
consisting of the baseline row and diagonal CGS input equations.  The constant
row construction
\[
  \alpha_{j h'}=\alpha_{j j}=\tau_j(P)\quad(j\ge1),\qquad
  \alpha_{0 h'}=0
\]
is feasible at \(L=0\) whenever the identified diagonal inputs obey the box,
which is part of Assumption~\ref{ass:grid-bounds}.  Hence
\(\mathcal A_L(P)\) is nonempty for every \(L\in[0,\bar L]\).  It is also a
compact polytope because it is the intersection of the compact box, the CGS
affine subspace, and finitely many closed Lipschitz half-spaces.

For \(0\le L_1\le L_2\le\bar L\), every \(\alpha\in\mathcal A_{L_1}(P)\)
satisfies
\[
  |\alpha_{j h}-\alpha_{j h'}|
  \le L_1|d_h-d_{h'}|
  \le L_2|d_h-d_{h'}|
\]
for every \(j,h,h'\).  The other constraints do not depend on \(L\).  Thus
\[
  \mathcal A_{L_1}(P)\subseteq\mathcal A_{L_2}(P).
\]
Taking the infimum of the same linear functional over a larger set can only
weakly decrease its value, while taking the supremum can only weakly increase
its value.  Therefore
\[
  L_h(L_2;P)\le L_h(L_1;P),
  \qquad
  U_h(L_2;P)\ge U_h(L_1;P).
\]
This proves the asserted monotonicity directions.

It remains to prove piecewise linearity.  Write the Lipschitz inequalities in
the two linear forms
\[
  \alpha_{j h}-\alpha_{j h'}\le L\Delta_{hh'},
  \qquad
  \alpha_{j h'}-\alpha_{j h}\le L\Delta_{hh'},
  \qquad
  \Delta_{hh'}=|d_h-d_{h'}|.
\]
Together with the box inequalities and the CGS equalities, this is a finite
parametric LP with right-hand side affine in \(L\).  Fix any nonsingular active
basis \(B\) for the endpoint LP.  Solving the active equalities gives a basic
candidate
\[
  \alpha_B(L;P)=r_B+s_B L+T_B b_{\mathrm{CGS}}(P),
\]
where \(r_B,s_B,T_B\) depend only on the grid, the stencil, the selected active
constraints, and the outcome bounds.  The corresponding endpoint candidate is
\[
  c_h^\transpose\alpha_B(L;P)
  =c_h^\transpose r_B+L\,c_h^\transpose s_B
   +c_h^\transpose T_B b_{\mathrm{CGS}}(P),
\]
which is affine in \(L\) for fixed \(P\).  The set of \(L\)'s for which this
candidate satisfies all inactive primal inequalities and the relevant dual
optimality inequalities is an interval, because those checks are linear
inequalities in \(L\).  There are only finitely many possible active bases.
Consequently \(U_h(L;P)\) and \(L_h(L;P)\), being selected from finitely many
affine candidate values on finitely many intervals, are finite piecewise-linear
functions of \(L\).  This is the same optimized-bound basis logic used for
LP-valued partial-identification functionals in \cite{ChernozhukovLeeRosen2013}
and \cite{Voronin2025}.

Now consider the critical frontier.  By Theorem~\ref{thm:joint-envelope},
\[
  0\in[L_h(L;P),U_h(L;P)]
\]
if and only if there exists \(\alpha\in\mathcal A_L(P)\) such that
\(\theta_h(\alpha)=0\).  Indeed, the theorem identifies
\([L_h(L;P),U_h(L;P)]\) with the full image
\(\{\theta_h(\alpha):\alpha\in\mathcal A_L(P)\}\), and the image is an
interval because \(\mathcal A_L(P)\) is convex and \(\theta_h\) is linear.
Therefore
\[
  \{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}
  =
  \{L\in[0,\bar L]:\exists\alpha\in\mathcal A_L(P),\
    \theta_h(\alpha)=0\}.
\]
Expanding the definition of \(\mathcal A_L(P)\) gives exactly
\[
 \min_{\alpha,L}\ L
 \quad\text{subject to}\quad
 A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ 
 \theta_h(\alpha)=0,\ 
 \underline y\le\alpha_{jh}\le\overline y,\ 
 |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|,\ 
 0\le L\le\bar L .
\]
Thus the critical constant equals the finite LP value.  If no feasible
zero-contact pair \((\alpha,L)\) exists, the set in the infimum is empty and
the LP is infeasible; both sides have the standard extended value \(+\infty\).
If the set is nonempty, compactness of the box and the closed interval
\([0,\bar L]\) imply that the LP feasible region is compact, so the minimum is
attained.

Finally fix a nonsingular active basis \(B\) of the critical LP, now in the
variables \(x=(\alpha,L)\).  The active equations consist of the CGS equations,
the zero-contact equation \(c_h^\transpose\alpha=0\), selected box faces,
selected signed Lipschitz faces, and possibly one of the bounds \(L=0\) or
\(L=\bar L\).  Because the active matrix is nonsingular, solving it yields
\[
  x_B(P)=r_B+T_B b_{\mathrm{CGS}}(P).
\]
Taking the \(L\)-coordinate gives
\[
  L_B^\star(P)=e_L^\transpose x_B(P)
  =e_L^\transpose r_B+e_L^\transpose T_B b_{\mathrm{CGS}}(P),
\]
an affine function of \(b_{\mathrm{CGS}}(P)\).  The region on which this basis
remains feasible and optimal is carved out by the inactive primal inequalities
and the dual optimality inequalities, all linear in \(b_{\mathrm{CGS}}(P)\);
therefore it is polyhedral.  Since the LP has finitely many bases, the global
value is obtained by selecting the smallest feasible optimal basis value:
\[
  L_h^\star(P)=\min_{B} L_B^\star(P),
\]
with the minimum taken over basis pieces whose feasibility and optimality
conditions hold at \(b_{\mathrm{CGS}}(P)\).  This is precisely the lower
envelope of the basis-specific affine pieces.
\end{proof}

\subsubsection*{Proof of Theorem 3}
\begin{proof}[Proof of Theorem~\ref{thm:plugin-inference}]
Let
\[
  z(P)=(\tau_1(P),\ldots,\tau_K(P))
\]
be the stochastic part of \(b_{\mathrm{CGS}}(P)\); the baseline row
\(\alpha_{0g}=0\) is kept as the exact equation \(A_0\alpha=0\).  By
Assumption~\ref{ass:sampling-lp}, the cell-mean vector
\(\widehat z=(\widehat\tau_1,\ldots,\widehat\tau_K)\) is asymptotically
linear and root-\(n\) normal.  Equivalently,
\[
  \sqrt n\{\widehat z-z(P)\}=O_p(1).
\]
The Gaussian or multiplier-bootstrap statistic used to form
\(\widehat c_{n,\alpha}\) is the finite-dimensional calibrated-projection
critical value in the sense of \cite{KaidoMolinariStoye2019}.  For the
containment argument below, only tightness of the studentized statistic is
needed; the diverging sequence \(\rho_n\) provides the never-empty padding.
Thus
\[
  E_n=
  \left\{
    |\,\widehat z_g-z_g(P)\,|
    \le
    \frac{\widehat c_{n,\alpha}\widehat s_g+\rho_n}{\sqrt n}
    \quad\text{for all }g=1,\ldots,K
  \right\}
\]
satisfies \(\Pr(E_n)\to1\), because \(\sqrt n(\widehat z-z(P))=O_p(1)\) and
\(\rho_n\to\infty\).

Fix \(L\in[0,\bar L]\) with \(\mathcal A_L(P)\ne\emptyset\), and take any
\(\alpha\in\mathcal A_L(P)\).  By the definition of the population feasible
set in Section~7,
\[
  A_0\alpha=0,\qquad A_\tau\alpha=z(P),\qquad B_L\alpha\le d_L .
\]
On \(E_n\), the diagonal equation gives
\[
  |(A_\tau\alpha)_g-\widehat z_g|
  =
  |z_g(P)-\widehat z_g|
  \le r_{g,n}
  \quad(g=1,\ldots,K),
\]
and the deterministic inequalities give
\[
  B_L\alpha\le d_L\le d_L+\rho_n n^{-1/2}\one .
\]
Therefore
\[
  \mathcal A_L(P)\subseteq \widehat{\mathcal A}_{L,n}
  \quad\text{on }E_n .
\]
Since \(\mathcal A_L(P)\) is nonempty, the relaxed sample set is nonempty on
the same event.  Hence
\[
  \Pr\{\widehat{\mathcal A}_{L,n}\ne\emptyset\}\ge \Pr(E_n)\to1 .
\]
This remains true regardless of whether the unrelaxed sample system
\(A_\tau\alpha=\widehat z,\ B_L\alpha\le d_L\) is feasible.

The endpoint containment is now a deterministic LP monotonicity calculation.
On \(E_n\), minimizing a linear functional over the larger set
\(\widehat{\mathcal A}_{L,n}\) can only weakly decrease the value, and
maximizing over the larger set can only weakly increase it:
\[
  \widehat L_h(L)
  =
  \min_{\alpha\in\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha
  \le
  \min_{\alpha\in\mathcal A_L(P)}a_h^\transpose\alpha
  =
  L_h(L;P),
\]
\[
  \widehat U_h(L)
  =
  \max_{\alpha\in\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha
  \ge
  \max_{\alpha\in\mathcal A_L(P)}a_h^\transpose\alpha
  =
  U_h(L;P).
\]
Thus
\[
  [L_h(L;P),U_h(L;P)]
  \subseteq
  [\widehat L_h(L),\widehat U_h(L)]
  \quad\text{on }E_n,
\]
and the advertised pointwise endpoint coverage follows from
\(\Pr(E_n)\to1\).  The proof uses the support-envelope conclusion of
Theorem~\ref{thm:joint-envelope} only to interpret the two LP endpoint values
as the full algebraic envelope.

It remains to prove coverage of \(L_h^\star(P)\).  Suppose
\[
  L_h^\star(P)=\inf\{\ell\in[0,\bar L]:L_h(\ell;P)\le0\le U_h(\ell;P)\}
\]
belongs to \([0,\bar L]\).  Assumption~\ref{ass:frontier-contact} gives a
closed zero-contact set of one of the three listed types: a single
transversal contact, a finite separated tie, or a compact flat face.  Hence
\[
  0\in[L_h(L_h^\star(P);P),U_h(L_h^\star(P);P)] .
\]
By Theorem~\ref{thm:joint-envelope}, the interval is exactly the image of
\(\mathcal A_{L_h^\star(P)}(P)\) under \(a_h^\transpose\alpha\), so there is
an array \(\alpha^\star\in\mathcal A_{L_h^\star(P)}(P)\) such that
\[
  a_h^\transpose\alpha^\star=0 .
\]
The containment argument already proved implies
\[
  \alpha^\star\in\widehat{\mathcal A}_{L_h^\star(P),n}
  \quad\text{on }E_n .
\]
Consequently, on \(E_n\),
\[
  \widehat L_h(L_h^\star(P))
  \le
  a_h^\transpose\alpha^\star
  =
  0
  \le
  \widehat U_h(L_h^\star(P)),
\]
so \(L_h^\star(P)\in\widehat C_{h,n}^\star\).  Therefore
\[
  \Pr\{L_h^\star(P)\in\widehat C_{h,n}^\star\}\ge \Pr(E_n)\to1 .
\]

Finally assume Conjecture~\ref{conj:law-sharp}.  Then the law-level ACRT
identified interval equals the corrected mean-completion interval
\[
  \Theta_I(P)
  =
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)] .
\]
By the definition of the completion-compatible feasible set in Section~7,
\(\mathcal A_L^{\mathrm{mc}}(P)\subseteq\mathcal A_L(P)\).  Applying the
same linear objective \(a_h^\transpose\alpha\) to a smaller feasible set gives
the deterministic nesting
\[
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
  \subseteq
  [L_h(L;P),U_h(L;P)] .
\]
Combining this nesting with the endpoint containment already established,
on \(E_n\) one has
\[
  \Theta_I(P)
  =
  [L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]
  \subseteq
  [L_h(L;P),U_h(L;P)]
  \subseteq
  [\widehat L_h(L),\widehat U_h(L)] .
\]
Since \(\Pr(E_n)\to1\), this proves the conditional coverage statement for
the corrected law-sharp ACRT interval.
\end{proof}

\section{Sanity checks}
\subsubsection*{Conjecture 1 (law-sharp)}
As a corner case, take the degenerate one-dose grid \(K=0\).  There are no
off-arm coordinates, \(\tau_0(P)=0\), \(\beta_0(P)=\mu_{10}(P)\), and the only
ATT entry is the definitional baseline entry \(\alpha_{00}=0\).  Hence
\(\mathcal A_L^{\mathrm{mc}}(P)=\mathcal A_L(P)=\{0\}\), and both endpoints
satisfy
\[
  L_0^{\mathrm{mc}}(L;P)=U_0^{\mathrm{mc}}(L;P)=\theta_0(0)=0.
\]
The law-level ACRT is also zero because \(Y_1(d_0)-Y_1(d_0)=0\).  The corrected
statement therefore reduces to the tautological no-off-arm special case.

The confirmed sibling \texttt{critical-l} remains the right structural anchor.
Replacing \(\mathcal A_L(P)\) by \(\mathcal A_L^{\mathrm{mc}}(P)\) only adds
finite linear inequalities independent of \(L\).  The endpoint maps are still
finite LP values, hence monotone piecewise linear in \(L\), and the zero-contact
constant is still a finite parametric LP in \((\alpha,L)\) after inserting the
same mean-completion rows.  The confirmed sibling \texttt{plugin-inference}
also keeps its structure: relaxed-LP inference covers the corrected endpoints
by relaxing the same finite equality and inequality system, now including the
observable mean-completion constraints.

\subsubsection*{Conjecture 2 (critical-l)}
At the zero-roughness corner \(L=0\), the Lipschitz restrictions force every
treatment row to be constant across conditioning groups:
\[
  \alpha_{j0}=\alpha_{j1}=\cdots=\alpha_{jK}.
\]
Combining this with the diagonal CGS input \(\alpha_{jj}=\tau_j(P)\) gives
\[
  \alpha_{j h}=\tau_j(P)\qquad\text{for every }j,h.
\]
The baseline row gives \(\tau_0(P)=0\).  Hence the ACRT stencil collapses to
the observable CGS finite-difference contrast
\[
  \theta_h(\alpha)
  =
  \sum_{j=0}^K q_{jh}\tau_j(P).
\]
Therefore
\[
  L_h(0;P)=U_h(0;P)=\sum_{j=0}^K q_{jh}\tau_j(P).
\]
If this CGS local slope is zero, then \(L_h^\star(P)=0\).  If it is nonzero,
zero is not in the interval at \(L=0\), and the critical value is the first
larger Lipschitz radius at which cross-dose selection terms can move the
linear ACRT stencil to zero.  This is exactly the intended reduction: with no
cross-dose roughness, the algebraic envelope degenerates to the observed
continuous-treatment DiD local contrast; with more roughness, it widens
monotonically.

\subsubsection*{Conjecture 3 (plugin-inference)}
Take the two-dose corner \(K=1\), \(d_0=0\), \(d_1>0\), and use the canonical
forward-difference stencil \(q_{11}=1/d_1\), \(q_{01}=-1/d_1\).  Because the
baseline row is \(\alpha_{01}=0\) and the diagonal CGS input is
\(\alpha_{11}=\tau_1(P)\), the algebraic envelope collapses to the point
\[
  L_1(L;P)=U_1(L;P)=\frac{\tau_1(P)}{d_1}
\]
whenever the box and regularity inequalities do not rule out the diagonal
input.  The relaxed sample set is
\[
  |\,\alpha_{11}-\widehat\tau_1\,|\le r_{1,n}
\]
intersected with the relaxed deterministic faces, so the endpoint interval is
\[
  [\widehat L_1(L),\widehat U_1(L)]
  =
  \left[
    \frac{\widehat\tau_1-r_{1,n}}{d_1},
    \frac{\widehat\tau_1+r_{1,n}}{d_1}
  \right]
\]
up to the irrelevant relaxed box truncation.  Since
\(\sqrt n(\widehat\tau_1-\tau_1(P))=O_p(1)\) and
\(\rho_n\to\infty\),
\[
  \Pr\left\{
    \frac{\tau_1(P)}{d_1}
    \in
    \left[
      \frac{\widehat\tau_1-r_{1,n}}{d_1},
      \frac{\widehat\tau_1+r_{1,n}}{d_1}
    \right]
  \right\}\to1 .
\]
Thus the general relaxed LP reduces to the ordinary cell-mean Wald interval
with an additional vanishing feasibility padding in the point-identified
two-dose case.

\section{Counterexample or minimality check}
\subsubsection*{Conjecture 1 (law-sharp)}
The refutation primitive is vertex enumeration on the smallest nontrivial
binary boundary support: three doses, binary post outcomes, and deterministic
observed cells.  In the refuting three-dose law, take \(Y_0=0\) in every dose
cell and \(Y_1=0,1,1\) in the \(D=d_0,d_1,d_2\) cells respectively.  Then
\[
  (\mu_{10},\mu_{11},\mu_{12})=(0,1,1),
  \qquad
  (m_0,m_1,m_2)=(0,1,1),
  \qquad
  (\tau_0,\tau_1,\tau_2)=(0,0,1),
  \qquad
  (\beta_0,\beta_1,\beta_2)=(0,1,0).
\]
The old algebraic maximizer had \(\alpha^\dagger_{21}=1\).  The corrected
constraint for \((j,h)=(2,1)\) requires
\[
  \underline y
  \le
  \beta_1(P)+\alpha_{21}
  \le
  \overline y,
  \qquad\text{that is}\qquad
  0\le 1+\alpha_{21}\le 1.
\]
Thus \(\alpha^\dagger_{21}=1\) is excluded because it implies the impossible
off-arm mean \(2\).  In fact the corrected constraint gives
\(\alpha_{21}\le0\), while the original nonnegativity and
Lipschitz/diagonal restrictions give \(\alpha_{21}\ge0\).  Hence the corrected
law-sharp interval for this witness collapses to the law-realized value
\[
  \operatorname{ACRT}(d_1)=\alpha_{21}-\alpha_{11}=0.
\]
The original counterexample no longer refutes the mended statement; it
identifies the missing coordinate of the correct law-level LP.

\subsubsection*{Conjecture 2 (critical-l)}
The finite-grid condition is essential for the finite active-basis conclusion.
If the conditioning-dose support were a continuum rather than the locked grid
\(\{d_0,\ldots,d_K\}\), the Lipschitz restriction would be an infinite family
of inequalities and the endpoint would be a semi-infinite optimization
problem.  The endpoint could still be an optimized support functional, but it
would no longer be represented by a finite list of active bases, and the
``lower envelope of finitely many affine pieces'' conclusion would fail as a
finite LP statement.

The zero-contact equality is also essential for the frontier interpretation.
If one minimized \(L\) over \(\mathcal A_L(P)\) without imposing
\(\theta_h(\alpha)=0\), the constant-row construction in the proof would make
\(L=0\) feasible for every admissible \(P\), so the resulting minimum would
always be zero and would contain no information about sign robustness.  The
rank condition in the last paragraph is exactly the nonsingular active-basis
condition stated in the conjecture: it is needed only to say that a particular
basis-specific piece is affine on its region.  Degenerate ties are handled by
taking the lower envelope over all feasible optimal basis pieces.

\subsubsection*{Conjecture 3 (plugin-inference)}
The padding and the relaxation of deterministic faces are necessary for the
conjecture's nonemptiness clause.  Use the same \(K=1\) corner, set
\(\tau_1(P)=\overline y\), and suppose the root-\(n\) limit of
\(\widehat\tau_1-\tau_1(P)\) is nondegenerate and centered.  The population
LP is feasible at the boundary point \(\alpha_{11}=\overline y\).  The
unrelaxed sample LP imposes both \(\alpha_{11}=\widehat\tau_1\) and
\(\alpha_{11}\le\overline y\), so it is infeasible whenever
\(\widehat\tau_1>\overline y\).  That event has limiting probability
\(1/2\) in the symmetric normal case and, more generally, need not vanish.

If one relaxes only the stochastic equality but not the deterministic upper
box face, the same boundary problem persists unless the equality relaxation
is wide enough to reach back to \(\overline y\).  With a fixed Gaussian
critical value and no diverging padding, the feasibility probability at this
boundary is only the corresponding fixed normal tail probability, not one.
The sequence \(\rho_n\to\infty\), \(\rho_n/\sqrt n\to0\), fixes exactly this:
it is asymptotically invisible for the population envelope but large enough
on the root-\(n\) scale to include the boundary population feasible point
with probability tending to one.  Dropping this device would refute the
``remains nonempty with probability approaching one'' part of the conjecture.

\section{Formalization checklist}
% file-plan: bypass-justified: POManskiIVSystem -- no matching local declaration surfaced from the current project root, and the object is a generic PO/Manski system rather than the finite-grid cross-dose ACRT LP used here; manski_bounds_ATE -- reusable only at the generic population-bound level, while this note needs the ACRT-specific stencil and frontier LP geometry; PartialID.Basic -- generic infrastructure rather than the theorem-specific mean-completion, zero-contact, and relaxed-LP objects assembled in this stitch.
\begin{itemize}[leftmargin=*]
  \item \textbf{Dose grid and observable law.} \(\mathcal D=\{d_0<\cdots<d_K\}\) with \(d_0=0\), \(P=\mathcal L(Y_0,Y_1,D)\), \(D\in\mathcal D\).  Role: base observable objects for all bounds and completions.  Dependencies: Assumptions~\ref{ass:grid-bounds}, \ref{ass:consistency-noanticip}.
  \item \textbf{Potential-outcome coordinates.} \(Y_1(d_j)\in[\underline y,\overline y]\) for \(j=0,\ldots,K\).  Role: latent variables used in the law-sharpness completion argument.  Dependencies: Assumptions~\ref{ass:grid-bounds}, \ref{ass:completion}.
  \item \textbf{ATT mean array.} \(\alpha_{jh}=\E[Y_1(d_j)-Y_1(d_0)\mid D=d_h]\in\R\).  Role: central nuisance array over which the LPs optimize.  Dependencies: Formal setup, Assumptions~\ref{ass:cgs-inputs}, \ref{ass:regularity}.
  \item \textbf{CGS inputs.} \(m_h(P)=\E[Y_1-Y_0\mid D=d_h]\), \(\tau_h(P)=m_h(P)-m_0(P)\), \(b_{\mathrm{CGS}}(P)\in\R^{2(K+1)}\).  Role: observable restriction vector identifying the baseline row and diagonal entries.  Dependencies: Assumption~\ref{ass:cgs-inputs}.
  \item \textbf{On-arm and baseline completion means.} \(\mu_{1h}(P)=\E_P[Y_1\mid D=d_h]\) and \(\beta_h(P)=\mu_{1h}(P)-\tau_h(P)\).  Role: convert ATT means into implied coordinate means in the corrected law-sharpness polytope.  Dependencies: consistency, diagonal CGS input identity.
  \item \textbf{ACRT stencil and linear functional.} \(q_h=(q_{0h},\ldots,q_{Kh})\in\R^{K+1}\) with \(\sum_j q_{jh}=0\) and \(\sum_j q_{jh}(d_j-d_h)=1\); \(\theta_h(\alpha)=\sum_j q_{jh}\alpha_{jh}\).  Role: target causal contrast and LP objective.  Dependencies: locked parameters, target estimand section.
  \item \textbf{Feasible algebraic polytopes.} \(\mathcal A_L(P)\subseteq[\underline y,\overline y]^{(K+1)^2}\), \(\mathcal A_{\mathrm{iso}}(P)\subseteq[\underline y,\overline y]^{(K+1)^2}\).  Role: algebraic envelopes under Lipschitz or isotonic restrictions.  Dependencies: Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}.
  \item \textbf{Corrected completion polytope.} \(\mathcal A_L^{\mathrm{mc}}(P)=\{\alpha\in\mathcal A_L(P):\underline y\le \beta_h(P)+\alpha_{jh}\le\overline y\ \forall h,\ \forall j\ne h\}\).  Role: law-sharp identified-set object after object correction.  Dependencies: Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}.
  \item \textbf{Endpoint maps.} \(L_h(L;P)=\min_{\alpha\in\mathcal A_L(P)}\theta_h(\alpha)\), \(U_h(L;P)=\max_{\alpha\in\mathcal A_L(P)}\theta_h(\alpha)\), and \(L_h^{\mathrm{mc}}(L;P)\), \(U_h^{\mathrm{mc}}(L;P)\) defined analogously on \(\mathcal A_L^{\mathrm{mc}}(P)\).  Role: computable identified-interval endpoints.  Dependencies: feasible polytopes, ACRT stencil.
  \item \textbf{Support-function representation.} \(\sigma_C(v)=\sup_{x\in C}v^\transpose x\), \(U_h(L;P)=\sigma_{\mathcal A_L(P)}(q_h\otimes e_h)\), \(L_h(L;P)=-\sigma_{\mathcal A_L(P)}(-q_h\otimes e_h)\).  Role: converts the envelope into an evaluable convex-analytic object.  Dependencies: Theorem~\ref{thm:joint-envelope}, block selector \(e_h\).
  \item \textbf{Zero-contact feasibility system.} \(\mathcal F_0(P)=\{(\alpha,L):A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\theta_h(\alpha)=0,\underline y\le\alpha_{jh}\le\overline y,|\alpha_{jh}-\alpha_{jh'}|\le L|d_h-d_{h'}|,0\le L\le\bar L\}\).  Role: parametric LP whose minimum is \(L_h^\star(P)\).  Dependencies: Theorem~\ref{thm:critical-l}.
  \item \textbf{Critical regularity constant.} \(L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}\in[0,\bar L]\cup\{+\infty\}\).  Role: sign-sensitivity frontier for the algebraic envelope.  Dependencies: endpoint maps, zero-contact feasibility system.
  \item \textbf{Sample estimators and relaxations.} \(\Delta Y_i=Y_{1i}-Y_{0i}\), \(\widehat\mu_g=\sum_i\one\{D_i=d_g\}\Delta Y_i/\sum_i\one\{D_i=d_g\}\), \(\widehat\tau_g=\widehat\mu_g-\widehat\mu_0\), \(r_{g,n}=(\widehat c_{n,\alpha}\widehat s_g+\rho_n)/\sqrt n\).  Role: stochastic inputs for relaxed-LP inference.  Dependencies: Assumption~\ref{ass:sampling-lp}.
  \item \textbf{Relaxed sample feasible set and sample endpoints.} \(\widehat{\mathcal A}_{L,n}=\{\alpha:A_0\alpha=0,\ |(A_\tau\alpha)_g-\widehat\tau_g|\le r_{g,n},\ B_L\alpha\le d_L+\rho_n n^{-1/2}\one\}\), \(\widehat L_h(L)=\min_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat U_h(L)=\max_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\).  Role: conservative sample analogues of the population LP bounds.  Dependencies: \(a_h^\transpose\alpha=\sum_j q_{jh}\alpha_{jh}\), bootstrap/Gaussian critical value, \(\rho_n\).
  \item \textbf{Frontier confidence set.} \(\widehat C_{h,n}^\star=\{\ell\in[0,\bar L]:\widehat L_h(\ell)\le0\le\widehat U_h(\ell)\}\), \(\widehat L_h^\star=\inf\widehat C_{h,n}^\star\).  Role: inverted relaxed-LP confidence set for the critical frontier.  Dependencies: sample endpoints, Assumption~\ref{ass:frontier-contact}.
  \item \textbf{Containment event.} \(E_n=\{|\,\widehat z_g-z_g(P)\,|\le(\widehat c_{n,\alpha}\widehat s_g+\rho_n)/\sqrt n,\ g=1,\ldots,K\}\).  Role: high-probability event on which the population feasible set is contained in the relaxed sample feasible set.  Dependencies: Assumption~\ref{ass:sampling-lp}.
  \item \textbf{Deterministic identities used in proof.} \(\mathcal A_{L_1}(P)\subseteq\mathcal A_{L_2}(P)\) for \(L_1\le L_2\); \(0\in[L_h(L;P),U_h(L;P)]\) iff \(\exists \alpha\in\mathcal A_L(P)\) with \(\theta_h(\alpha)=0\); \(\E[Y_1(d_j)\mid D=d_h]=\beta_h(P)+\alpha_{jh}\).  Role: trace the monotonicity, frontier equivalence, and mean-completion arguments.  Dependencies: linearity, bounded support, Theorem~\ref{thm:joint-envelope}.
\end{itemize}

\section{Conclusion and references}
Theorem 1 (law-sharp) is confirmed; Confirmed after object correction: write \(\mu_{1h}(P)=\E_P[Y_1\mid D=d_h]\) and \(\beta_h(P)=\mu_{1h}(P)-\tau_h(P)\), define \(\mathcal A_L^{\mathrm{mc}}(P)=\{\alpha\in\mathcal A_L(P):\underline y\le \beta_h(P)+\alpha_{jh}\le\overline y\ \forall h,\ \forall j\ne h\}\), and set \(L_h^{\mathrm{mc}}(L;P)=\min_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha)\), \(U_h^{\mathrm{mc}}(L;P)=\max_{\alpha\in\mathcal A_L^{\mathrm{mc}}(P)}\theta_h(\alpha)\). Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, with the algebraic object replaced by this mean-completion polytope, \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\) is law-sharp for the finite-grid ACRT over latent completions preserving \(P\) whose off-arm potential outcomes are assigned by finite \([\underline y,\overline y]\)-supported product kernels conditional on the observed data: every such completion maps into \(\mathcal A_L^{\mathrm{mc}}(P)\), and every \(\alpha\in\mathcal A_L^{\mathrm{mc}}(P)\) is realized by such a completion.

Theorem 2 (critical-l) is confirmed; Confirmed critical-L result. Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, define \(\mathcal F_0(P)=\{(\alpha,L):A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ \theta_h(\alpha)=0,\ \underline y\le\alpha_{jh}\le\overline y,\ |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\ \forall j,h,h',\ 0\le L\le\bar L\}\). The endpoint maps \(L\mapsto L_h(L;P)\) and \(L\mapsto U_h(L;P)\) are respectively nonincreasing and nondecreasing finite piecewise-linear functions on \([0,\bar L]\). The critical constant \(L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}\), with value \(+\infty\) if the zero-contact set is empty, is exactly \(\min\{L:(\alpha,L)\in\mathcal F_0(P)\}\), with the same \(+\infty\) convention for LP infeasibility. If \(B\) ranges over the finite nonsingular active bases of this LP, each basis has an affine candidate value \(L_B^\star(P)=a_B^\transpose b_{\mathrm{CGS}}(P)+c_B\) on the polyhedral region where that basis is feasible and optimal, and globally \(L_h^\star(P)=\min_B L_B^\star(P)\) over feasible optimal basis pieces, i.e. the lower envelope of the basis-specific affine pieces.

Theorem 3 (plugin-inference) is confirmed; Confirmed conservative relaxed-LP inference. Define \(\widehat\tau_g=\widehat\mu_g-\widehat\mu_0\) with \(\widehat\mu_g=\sum_i\one\{D_i=d_g\}(Y_{1i}-Y_{0i})/\sum_i\one\{D_i=d_g\}\), set \(r_{g,n}=(\widehat c_{n,\alpha}\widehat s_g+\rho_n)/\sqrt n\), \(\rho_n=\log n\), and \(\widehat{\mathcal A}_{L,n}=\{\alpha:A_0\alpha=0,\ |(A_\tau\alpha)_g-\widehat\tau_g|\le r_{g,n}\ (g=1,\ldots,K),\ B_L\alpha\le d_L+\rho_n n^{-1/2}\one\}\), where \(\widehat c_{n,\alpha}\) is the Gaussian or multiplier-bootstrap \((1-\alpha)\)-critical value for the studentized CGS input vector. With \(a_h^\transpose\alpha=\sum_jq_{jh}\alpha_{jh}\), \(\widehat L_h(L)=\min_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat U_h(L)=\max_{\widehat{\mathcal A}_{L,n}}a_h^\transpose\alpha\), \(\widehat C_{h,n}^\star=\{\ell\in[0,\bar L]:\widehat L_h(\ell)\le0\le\widehat U_h(\ell)\}\), and \(\widehat L_h^\star=\inf\widehat C_{h,n}^\star\), Assumptions~\ref{ass:sampling-lp}--\ref{ass:frontier-contact} imply \(\Pr\{[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)],\ \widehat{\mathcal A}_{L,n}\ne\emptyset\}\to1\) for each fixed feasible \(L\), and \(\Pr\{L_h^\star(P)\in\widehat C_{h,n}^\star\}\to1\); if Conjecture~\ref{conj:law-sharp} holds, the same endpoint interval covers the corrected law-sharp mean-completion ACRT interval \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\) through \([L_h^{\mathrm{mc}}(L;P),U_h^{\mathrm{mc}}(L;P)]\subseteq[L_h(L;P),U_h(L;P)]\subseteq[\widehat L_h(L),\widehat U_h(L)]\).

\subsection*{References}
\begin{thebibliography}{99}

\bibitem[Armstrong and Kolesar(2018)]{ArmstrongKolesar2018}
Armstrong, T. B. and Kolesar, M. (2018).
Optimal inference in a class of regression models.
\textit{Econometrica}, 86, 655--683.

\bibitem[Belloni, Bugni, and Chernozhukov(2018)]{BelloniBugniChernozhukov2018}
Belloni, A., Bugni, F., and Chernozhukov, V. (2018).
Subvector inference in partially identified models with many moment
inequalities.
arXiv:1806.11466.

\bibitem[Callaway, Goodman-Bacon, and Sant'Anna(2021)]{CallawayGoodmanBaconSantAnna2021}
Callaway, B., Goodman-Bacon, A., and Sant'Anna, P. H. C. (2021).
Difference-in-differences with a continuous treatment.
arXiv:2107.02637.

\bibitem[Chernozhukov, Lee, and Rosen(2013)]{ChernozhukovLeeRosen2013}
Chernozhukov, V., Lee, S., and Rosen, A. M. (2013).
Intersection bounds: estimation and inference.
\textit{Econometrica}, 81, 667--737.

\bibitem[de Chaisemartin et al.(2022)]{deChaisemartinDHaultfoeuillePasquierSowVazquezBare2022}
de Chaisemartin, C., D'Haultfoeuille, X., Pasquier, F., Sow, D., and
Vazquez-Bare, G. (2022).
Difference-in-differences estimators for treatments continuously distributed at
every period.
arXiv:2201.06898.

\bibitem[de Chaisemartin, D'Haultfoeuille, and Vazquez-Bare(2024)]{deChaisemartinDHaultfoeuilleVazquezBare2024}
de Chaisemartin, C., D'Haultfoeuille, X., and Vazquez-Bare, G. (2024).
Two-way fixed effects and differences-in-differences with continuous
treatments and no stayers.
arXiv:2402.05432.

\bibitem[Ishihara(2017)]{Ishihara2017}
Ishihara, T. (2017).
Partial identification of treatment effects in nonseparable models under
monotonicity and concavity.
arXiv:1707.04405.

\bibitem[Kaido, Molinari, and Stoye(2019)]{KaidoMolinariStoye2019}
Kaido, H., Molinari, F., and Stoye, J. (2019).
Confidence intervals for projections of partially identified parameters.
\textit{Econometrica}, 87, 1397--1432.

\bibitem[Manski and Pepper(2000)]{ManskiPepper2000}
Manski, C. F. and Pepper, J. V. (2000).
Monotone instrumental variables: with an application to the returns to
schooling.
\textit{Econometrica}, 68, 997--1010.

\bibitem[Molinari(2020)]{Molinari2020}
Molinari, F. (2020).
Microeconometrics with partial identification.
arXiv:2004.11751.

\bibitem[Stoye(2020)]{Stoye2020}
Stoye, J. (2020).
A simple, short, but never-empty confidence interval for partially identified
parameters.
arXiv:2010.10484.

\bibitem[Voronin(2025)]{Voronin2025}
Voronin, A. (2025).
Linear programming approach to partially identified econometric models.
arXiv:2503.14940.

\end{thebibliography}

\end{document}
