% file-plan: bypass-justified: the substrate survey found reusable generic PartialID Manski-style, Lee-trim, proxy-condition, and PO-system primitives, but this solve target is finite-grid parametric LP geometry for the cross-dose ACRT array; the proof therefore stays at the algebraic observable-law LP layer.

\paragraph{\S9-fragment-statement for the labelled solve target \texttt{critical-l}.}
\paragraph{Conjecture restated verbatim (Conjecture~\ref{conj:critical-l}).}
Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, the endpoint
functions \(L\mapsto L_h(L;P)\) and \(L\mapsto U_h(L;P)\) are monotone
piecewise linear on every finite grid.  The critical constant
\[
  L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}
\]
is equivalently the optimum of a finite parametric LP feasibility problem in
\((\alpha,L)\):
\[
 \min_{\alpha,L}\ L
 \quad\text{subject to}\quad
 A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ 
 \theta_h(\alpha)=0,\ 
 \underline y\le\alpha_{jh}\le\overline y,\ 
 |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|,\ 
 0\le L\le\bar L .
\]
For each nonsingular active basis of this LP, \(L_h^\star(P)\) is an affine
function of \(b_{\mathrm{CGS}}(P)\) on the region where that basis remains
optimal; globally it is the lower envelope of these basis-specific affine
pieces.

\begin{theorem}[Critical Lipschitz frontier as a parametric LP]\label{thm:critical-l}
\paragraph{Verdict headline.}
Confirmed critical-L result. Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:regularity}, define \(\mathcal F_0(P)=\{(\alpha,L):A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ \theta_h(\alpha)=0,\ \underline y\le\alpha_{jh}\le\overline y,\ |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|\ \forall j,h,h',\ 0\le L\le\bar L\}\). The endpoint maps \(L\mapsto L_h(L;P)\) and \(L\mapsto U_h(L;P)\) are respectively nonincreasing and nondecreasing finite piecewise-linear functions on \([0,\bar L]\). The critical constant \(L_h^\star(P)=\inf\{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}\), with value \(+\infty\) if the zero-contact set is empty, is exactly \(\min\{L:(\alpha,L)\in\mathcal F_0(P)\}\), with the same \(+\infty\) convention for LP infeasibility. If \(B\) ranges over the finite nonsingular active bases of this LP, each basis has an affine candidate value \(L_B^\star(P)=a_B^\transpose b_{\mathrm{CGS}}(P)+c_B\) on the polyhedral region where that basis is feasible and optimal, and globally \(L_h^\star(P)=\min_B L_B^\star(P)\) over feasible optimal basis pieces, i.e. the lower envelope of the basis-specific affine pieces.
\end{theorem}

\paragraph{\S13-refutation-attempt.}
The refutation-first primitive is vertex enumeration for the smallest
nontrivial finite grids, followed by the general active-basis enumeration.
This is the finite-grid analogue of the optimized-bound inversion perspective
used by \cite{ChernozhukovLeeRosen2013}: the endpoint interval is an optimized
object, and the frontier is obtained by imposing zero contact and optimizing
over the regularity radius.

Start with the two-dose grid \(\mathcal D=\{d_0,d_1\}\) and target \(h=1\).
The stencil restrictions imply, after normalizing
\(\Delta=d_1-d_0>0\),
\[
  q_{01}=-\Delta^{-1},\qquad q_{11}=\Delta^{-1}.
\]
The baseline row and diagonal equations give
\[
  \alpha_{01}=0,\qquad \alpha_{11}=\tau_1(P),
\]
so every vertex of every \(\mathcal A_L(P)\) has
\[
  \theta_1(\alpha)=\Delta^{-1}\tau_1(P).
\]
Thus
\[
  L_1(L;P)=U_1(L;P)=\Delta^{-1}\tau_1(P)
\]
for all \(L\in[0,\bar L]\).  This smallest-grid search cannot violate
monotonicity or piecewise linearity.  If \(\tau_1(P)=0\), the zero-contact LP
is feasible and \(L_1^\star(P)=0\).  If \(\tau_1(P)\ne0\), the zero-contact
set is empty and both the defining infimum and the LP minimum have the
standard extended value \(+\infty\).  Hence the smallest grid forces the
extended-value convention but does not refute the equivalence.

For a general finite grid, enumerate vertices by taking the fixed affine
constraints \(A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P)\), adding enough
active box and Lipschitz inequalities to reach full rank, and solving the
resulting square linear system.  A candidate vertex at \(L_1\) remains feasible
for every \(L_2\ge L_1\) because each Lipschitz inequality has the form
\[
  \alpha_{j h}-\alpha_{j h'}\le L|d_h-d_{h'}|,
  \qquad
  \alpha_{j h'}-\alpha_{j h}\le L|d_h-d_{h'}|,
\]
and the right-hand side weakly expands with \(L\).  Therefore no vertex can
produce \(L_h(L_2;P)>L_h(L_1;P)\) for the lower endpoint or
\(U_h(L_2;P)<U_h(L_1;P)\) for the upper endpoint.  The equality face
\(\theta_h(\alpha)=0\) used in the frontier LP is also linear, so every
zero-contact candidate is one of the same finite active-basis solutions with
the extra equality included.  A candidate outside its inactive inequalities is
not feasible; a feasible candidate is an LP vertex; and the objective chooses
the smallest \(L\) among those vertices.  The bounded vertex search therefore
finds no admissible witness outside the claimed interval, no boundary vertex
that contradicts weak monotonicity, and no zero-contact basis whose value is
not one of the affine pieces used in the lower envelope.

The proof below verifies the positive statement.

\paragraph{\S10 Interpretation.}
The theorem turns the regularity radius \(L\) into a computable sensitivity
frontier.  For each fixed \(L\), Theorem~\ref{thm:joint-envelope} says that
the algebraic ACRT envelope is the image of a finite feasible polytope under
the linear stencil \(\alpha\mapsto\theta_h(\alpha)\).  Increasing \(L\) relaxes
only the cross-dose Lipschitz inequalities, so the lower endpoint can only move
down and the upper endpoint can only move up.  Consequently, once zero enters
the algebraic interval, it remains in the interval for all larger admissible
regularity radii.

The critical value \(L_h^\star(P)\) is therefore the first amount of
cross-dose roughness at which the observed CGS inputs and the maintained
bounds no longer sign the local causal response algebraically.  If
\(L<L_h^\star(P)\) and the interval is strictly on one side of zero, the sign
of the algebraic ACRT envelope is robust to that degree of cross-dose
regularity.  If \(L\ge L_h^\star(P)\), the same observable inputs admit a
feasible cross-dose ATT array with \(\theta_h=0\), so the sign conclusion has
reached its sensitivity frontier.  This is an algebraic PartialID statement;
law-level causal sharpness still depends on the separate completion claim in
Conjecture~\ref{conj:law-sharp}.

\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:critical-l}]
Stack the array \(\alpha\) in \(\R^{(K+1)^2}\), and let \(c_h\) be the vector
such that \(\theta_h(\alpha)=c_h^\transpose\alpha\).  Assumption
\ref{ass:grid-bounds} gives a fixed finite ordered grid and a compact box
\([\underline y,\overline y]^{(K+1)^2}\).  Assumption~\ref{ass:cgs-inputs}
gives the affine equalities
\[
  A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),
\]
consisting of the baseline row and diagonal CGS input equations.  The constant
row construction
\[
  \alpha_{j h'}=\alpha_{j j}=\tau_j(P)\quad(j\ge1),\qquad
  \alpha_{0 h'}=0
\]
is feasible at \(L=0\) whenever the identified diagonal inputs obey the box,
which is part of Assumption~\ref{ass:grid-bounds}.  Hence
\(\mathcal A_L(P)\) is nonempty for every \(L\in[0,\bar L]\).  It is also a
compact polytope because it is the intersection of the compact box, the CGS
affine subspace, and finitely many closed Lipschitz half-spaces.

For \(0\le L_1\le L_2\le\bar L\), every \(\alpha\in\mathcal A_{L_1}(P)\)
satisfies
\[
  |\alpha_{j h}-\alpha_{j h'}|
  \le L_1|d_h-d_{h'}|
  \le L_2|d_h-d_{h'}|
\]
for every \(j,h,h'\).  The other constraints do not depend on \(L\).  Thus
\[
  \mathcal A_{L_1}(P)\subseteq\mathcal A_{L_2}(P).
\]
Taking the infimum of the same linear functional over a larger set can only
weakly decrease its value, while taking the supremum can only weakly increase
its value.  Therefore
\[
  L_h(L_2;P)\le L_h(L_1;P),
  \qquad
  U_h(L_2;P)\ge U_h(L_1;P).
\]
This proves the asserted monotonicity directions.

It remains to prove piecewise linearity.  Write the Lipschitz inequalities in
the two linear forms
\[
  \alpha_{j h}-\alpha_{j h'}\le L\Delta_{hh'},
  \qquad
  \alpha_{j h'}-\alpha_{j h}\le L\Delta_{hh'},
  \qquad
  \Delta_{hh'}=|d_h-d_{h'}|.
\]
Together with the box inequalities and the CGS equalities, this is a finite
parametric LP with right-hand side affine in \(L\).  Fix any nonsingular active
basis \(B\) for the endpoint LP.  Solving the active equalities gives a basic
candidate
\[
  \alpha_B(L;P)=r_B+s_B L+T_B b_{\mathrm{CGS}}(P),
\]
where \(r_B,s_B,T_B\) depend only on the grid, the stencil, the selected active
constraints, and the outcome bounds.  The corresponding endpoint candidate is
\[
  c_h^\transpose\alpha_B(L;P)
  =c_h^\transpose r_B+L\,c_h^\transpose s_B
   +c_h^\transpose T_B b_{\mathrm{CGS}}(P),
\]
which is affine in \(L\) for fixed \(P\).  The set of \(L\)'s for which this
candidate satisfies all inactive primal inequalities and the relevant dual
optimality inequalities is an interval, because those checks are linear
inequalities in \(L\).  There are only finitely many possible active bases.
Consequently \(U_h(L;P)\) and \(L_h(L;P)\), being selected from finitely many
affine candidate values on finitely many intervals, are finite piecewise-linear
functions of \(L\).  This is the same optimized-bound basis logic used for
LP-valued partial-identification functionals in \cite{ChernozhukovLeeRosen2013}
and \cite{Voronin2025}.

Now consider the critical frontier.  By Theorem~\ref{thm:joint-envelope},
\[
  0\in[L_h(L;P),U_h(L;P)]
\]
if and only if there exists \(\alpha\in\mathcal A_L(P)\) such that
\(\theta_h(\alpha)=0\).  Indeed, the theorem identifies
\([L_h(L;P),U_h(L;P)]\) with the full image
\(\{\theta_h(\alpha):\alpha\in\mathcal A_L(P)\}\), and the image is an
interval because \(\mathcal A_L(P)\) is convex and \(\theta_h\) is linear.
Therefore
\[
  \{L\in[0,\bar L]:L_h(L;P)\le0\le U_h(L;P)\}
  =
  \{L\in[0,\bar L]:\exists\alpha\in\mathcal A_L(P),\
    \theta_h(\alpha)=0\}.
\]
Expanding the definition of \(\mathcal A_L(P)\) gives exactly
\[
 \min_{\alpha,L}\ L
 \quad\text{subject to}\quad
 A_{\mathrm{CGS}}\alpha=b_{\mathrm{CGS}}(P),\ 
 \theta_h(\alpha)=0,\ 
 \underline y\le\alpha_{jh}\le\overline y,\ 
 |\alpha_{j h}-\alpha_{j h'}|\le L|d_h-d_{h'}|,\ 
 0\le L\le\bar L .
\]
Thus the critical constant equals the finite LP value.  If no feasible
zero-contact pair \((\alpha,L)\) exists, the set in the infimum is empty and
the LP is infeasible; both sides have the standard extended value \(+\infty\).
If the set is nonempty, compactness of the box and the closed interval
\([0,\bar L]\) imply that the LP feasible region is compact, so the minimum is
attained.

Finally fix a nonsingular active basis \(B\) of the critical LP, now in the
variables \(x=(\alpha,L)\).  The active equations consist of the CGS equations,
the zero-contact equation \(c_h^\transpose\alpha=0\), selected box faces,
selected signed Lipschitz faces, and possibly one of the bounds \(L=0\) or
\(L=\bar L\).  Because the active matrix is nonsingular, solving it yields
\[
  x_B(P)=r_B+T_B b_{\mathrm{CGS}}(P).
\]
Taking the \(L\)-coordinate gives
\[
  L_B^\star(P)=e_L^\transpose x_B(P)
  =e_L^\transpose r_B+e_L^\transpose T_B b_{\mathrm{CGS}}(P),
\]
an affine function of \(b_{\mathrm{CGS}}(P)\).  The region on which this basis
remains feasible and optimal is carved out by the inactive primal inequalities
and the dual optimality inequalities, all linear in \(b_{\mathrm{CGS}}(P)\);
therefore it is polyhedral.  Since the LP has finitely many bases, the global
value is obtained by selecting the smallest feasible optimal basis value:
\[
  L_h^\star(P)=\min_{B} L_B^\star(P),
\]
with the minimum taken over basis pieces whose feasibility and optimality
conditions hold at \(b_{\mathrm{CGS}}(P)\).  This is precisely the lower
envelope of the basis-specific affine pieces.
\end{proof}

\paragraph{\S12 Sanity check.}
At the zero-roughness corner \(L=0\), the Lipschitz restrictions force every
treatment row to be constant across conditioning groups:
\[
  \alpha_{j0}=\alpha_{j1}=\cdots=\alpha_{jK}.
\]
Combining this with the diagonal CGS input \(\alpha_{jj}=\tau_j(P)\) gives
\[
  \alpha_{j h}=\tau_j(P)\qquad\text{for every }j,h.
\]
The baseline row gives \(\tau_0(P)=0\).  Hence the ACRT stencil collapses to
the observable CGS finite-difference contrast
\[
  \theta_h(\alpha)
  =
  \sum_{j=0}^K q_{jh}\tau_j(P).
\]
Therefore
\[
  L_h(0;P)=U_h(0;P)=\sum_{j=0}^K q_{jh}\tau_j(P).
\]
If this CGS local slope is zero, then \(L_h^\star(P)=0\).  If it is nonzero,
zero is not in the interval at \(L=0\), and the critical value is the first
larger Lipschitz radius at which cross-dose selection terms can move the
linear ACRT stencil to zero.  This is exactly the intended reduction: with no
cross-dose roughness, the algebraic envelope degenerates to the observed
continuous-treatment DiD local contrast; with more roughness, it widens
monotonically.

\paragraph{\S13 Counterexample/minimality check.}
The finite-grid condition is essential for the finite active-basis conclusion.
If the conditioning-dose support were a continuum rather than the locked grid
\(\{d_0,\ldots,d_K\}\), the Lipschitz restriction would be an infinite family
of inequalities and the endpoint would be a semi-infinite optimization
problem.  The endpoint could still be an optimized support functional, but it
would no longer be represented by a finite list of active bases, and the
``lower envelope of finitely many affine pieces'' conclusion would fail as a
finite LP statement.

The zero-contact equality is also essential for the frontier interpretation.
If one minimized \(L\) over \(\mathcal A_L(P)\) without imposing
\(\theta_h(\alpha)=0\), the constant-row construction in the proof would make
\(L=0\) feasible for every admissible \(P\), so the resulting minimum would
always be zero and would contain no information about sign robustness.  The
rank condition in the last paragraph is exactly the nonsingular active-basis
condition stated in the conjecture: it is needed only to say that a particular
basis-specific piece is affine on its region.  Degenerate ties are handled by
taking the lower envelope over all feasible optimal basis pieces.
