% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_rdd\_manipulation\_bounded, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_rdd\_manipulation\_bounded} / \texttt{v1}%
  \\ \large\textit{Sharp RD manipulation bounds from a McCrary envelope and covariate-share caps}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal, not a Q1--Q6 panel pool-mode instance.
The locked tuple is
\[
  (\texttt{qid}, \texttt{specialization}, P, \theta, \text{identifying restrictions},
    \text{bounding functional})
\]
with the following convention.  \(\texttt{qid}=\texttt{pid\_rdd\_manipulation\_bounded}\) and
\(\texttt{specialization}=\texttt{v1}\).  The observable distribution \(P\) consists of the two
cutoff-side weak limits \(P_-\) and \(P_+\) of \((Y,D,W)\) given the running variable
approaches the cutoff from below and above, where \(Y\in[\underline y,\overline y]\),
\(D\in\{0,1\}\), and \(W\in\{1,\ldots,K\}\) is a finite predetermined-covariate cell.
The parameter \(\theta\) is the local Wald effect for the nonmanipulating cutoff population,
\[
  \theta =
  \frac{\sum_w \pi_-(w)\{\mu^Y_{+,0}(w)-\mu^Y_-(w)\}}
       {\sum_w \pi_-(w)\{\mu^D_{+,0}(w)-\mu^D_-(w)\}},
\]
where \(\pi_-(w)=P_-(W=w)\), \(\mu^-_V(w)=\E_{P_-}[V\mid W=w]\), and
\(\mu^V_{+,0}(w)\) denotes the right-limit nonmanipulator mean of \(V\in\{Y,D\}\)
in covariate cell \(w\).  The identifying restrictions are: one-sided upward manipulation
at the cutoff, local continuity of the nonmanipulator potential-outcome and compliance
law conditional on \(W\), a McCrary-style global manipulation-share envelope
\(\bar\rho\in[0,1)\), covariate-cell manipulation-share caps \(\bar s_w\in[0,1)\),
bounded outcomes, positive retained mass, and a positive nonmanipulator first-stage
denominator.  The bounding functional is the sharp fractional trimming program over
retention weights \(a(y,d,w)\in[0,1]\):
\[
  B_L(P,\bar\rho,\bar s)=\inf_{a\in\mathcal A(P,\bar\rho,\bar s)} \Theta(a),
  \qquad
  B_U(P,\bar\rho,\bar s)=\sup_{a\in\mathcal A(P,\bar\rho,\bar s)} \Theta(a),
\]
where \(\mathcal A(P,\bar\rho,\bar s)\) enforces the global and cellwise removal budgets
and the retained right-side covariate distribution \(\pi_-\), and \(\Theta(a)\) is the Wald
ratio formed from the retained right-side means and the observed left-side means.

\begin{abstract}
Regression discontinuity analyses often treat a McCrary density jump as a binary diagnostic:
either the design is kept as a point-identified Lee-style RD or discarded as manipulated.
Gerard, Rokkanen, and Rothe give sharp bounds when one-sided manipulation identifies an
exact manipulator share, while covariate-adjusted Lee-bound work shows that conditional
trimming can be much sharper than unconditional trimming.  This proposal asks for the sharp
identified interval for the RD local Wald effect when the density jump is used only as an
upper envelope on total manipulation and predetermined covariates impose cellwise upper
bounds on the manipulator share.  The proposed kernel is that the tight interval is a
budgeted conditional trimming problem whose endpoint allocation couples outcome tails,
first-stage tails, and covariate cells; it is not obtained by plugging the largest allowed
share into the cell-cap-free exact-share formula.  Resolving this would turn manipulation
tests into a sensitivity-analysis object with a sharp no-manipulation face that recovers
the Lee RD point estimand.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
RD validity checks have become routine, but the empirical decision rule remains coarse:
researchers report a density-continuity or covariate-balance diagnostic, and then either
proceed with point identification or abandon the design.  In many applied settings, such as
school admissions, benefit thresholds, ratings cutoffs, and elections, a small density or
covariate discontinuity is more naturally evidence about the possible magnitude and location
of manipulation than proof that all RD information is unusable.  A sharp partial-identification
formula would let applied researchers report the local effect compatible with a stated
manipulation envelope rather than choosing between exact RD and no RD.

\paragraph{The main finding (proposed).}
The flagship statement is Conjecture~\ref{conj:sharp-budgeted-trim}: under one-sided
manipulation and local continuity for nonmanipulators, the sharp identified set for the RD
local Wald effect is the image of a finite-dimensional retention-weight program.  The
program removes at most \(\bar\rho\) total right-side mass and at most \(\bar s_w\) mass in
each covariate cell, forces the retained right-side covariate law to equal the left-side
law, and forms the Wald ratio using the retained right-side outcome and treatment means.

\paragraph{What is new.}
The novelty kernel is the sharp \emph{envelope} version of covariate-conditional RD
manipulation bounds.  Gerard, Rokkanen, and Rothe already optimize over partially identified
shares in fuzzy RD and give covariate-conditioned sharp bounds; this proposal does not claim
that share optimization or covariate trimming is absent from their paper.  The gap is more
specific: their feasible share sets come from the exact one-sided manipulation model and
conditional density ratios, whereas the proposed object intersects a McCrary-style upper
confidence envelope with external covariate-cell caps and the retained-covariate-law
restriction.  That intersection creates a coupled set of fixed-share faces: one cell cap
can force extra right-side retention in every cell through the retained-\(W\) equation, so
the endpoint can be strictly narrower than the cell-cap-free GRR envelope and can kink at a
cell-cap boundary.  Semenova generalizes Lee bounds using covariates in
sample-selection problems, but not in RD with this global-plus-cell manipulation envelope.

\paragraph{How it positions in the literature.}
This is a partial-identification proposal in the RD manipulation and Lee-bounds cluster.
It consumes the exact RD identification benchmark of Hahn, Todd, and van der Klaauw and
Lee, the density-discontinuity diagnostic of McCrary and Cattaneo--Jansson--Ma, the
manipulated-running-variable bounds of Gerard--Rokkanen--Rothe, and the covariate-sharpened
Lee-bound logic of Semenova.  It is not a panel or linear-projection theorem, and it does
not add new SCM or do-calculus infrastructure.

\paragraph{Implications for the community.}
The concrete downstream consumer is applied RD work that reports the McCrary density test
implemented through \citet{CattaneoJanssonMa2020} and then faces a small but nonzero density
or covariate discontinuity.  A verified version would give those studies a sharp sensitivity
interval indexed by \((\bar\rho,\bar s)\), rather than a binary ``pass/fail'' diagnostic.

\paragraph{How research benefits from the conclusion.}
Researchers should report a manipulation-envelope curve for the RD local effect, and should
check which covariate cell binds, instead of treating a density discontinuity as an automatic
design failure.

\section{Related work}
\citet{HahnToddVanDerKlaauw2001} give the classical continuity-based identification result
for RD treatment effects and fuzzy RD Wald estimands; Theorem~\ref{thm:no-manipulation-face}
uses this as the point-identification face.  \citet{Lee2008} supplies the behavioral
``imprecise control'' interpretation under which treatment status is locally as good as
randomized and baseline covariates should be continuous at the cutoff; this is the sharp
RD benchmark recovered when the manipulation envelope is zero.  \citet{ImbensLemieux2008}
and \citet{LeeLemieux2010} are the standard RD practice references explaining why density
and predetermined-covariate checks are central validity diagnostics.  \citet{CattaneoTitiunik2022}
survey the modern RD literature and motivate treating validation and falsification as
first-order parts of the design rather than auxiliary reporting.

\citet{McCrary2008} develops the density-discontinuity test for manipulation of the running
variable; the proposed \(\bar\rho\) parameter interprets such a discontinuity as an upper
envelope rather than a binary rejection.  \citet{CattaneoJanssonMa2020} provide modern
local-polynomial density estimators that underlie common implementations of McCrary-style
tests, making them the practical source of the global manipulation envelope.  \citet{BugniCanay2021}
develop an alternative density-continuity testing approach, reinforcing that density
diagnostics are testing objects rather than sharp causal estimands by themselves.
\citet{CanayKamat2018} formalize covariate-distribution continuity tests implied by Lee's
local-randomization condition; the proposed covariate-share caps convert such failures into
cellwise sensitivity parameters.

\citet{GerardRokkanenRothe2020} are the closest prior art: they derive sharp RD treatment-effect
bounds with a manipulated running variable, use the density jump to infer the extent of
one-sided manipulation, give covariate-conditioned sharp bounds in their Corollary~3, and
optimize over partially identified fuzzy-RD share functions in their Corollary~4 and
appendix Corollary~9.  This proposal does not claim covariate trimming or share-set
optimization itself is new.  It differs by replacing the exact density-ratio share set with
a sensitivity envelope: the analyst supplies a global density-discontinuity upper bound
and covariate-cell manipulation-share caps, while the retained right-side covariate law must
still equal the left-side law.  These three restrictions produce a coupled feasible set
that is generally a proper subset of the cell-cap-free GRR fixed-share envelope because a
binding cap in one cell changes the admissible retained mass for all cells.  \citet{Lee2009}
and \citet{HorowitzManski1995} provide the trimming and contaminated-distribution logic that
the proof route should reduce to in one-covariate-cell or exact-share faces.  \citet{Semenova2025}
generalizes Lee bounds with covariate-conditional monotonicity; this proposal borrows the
lesson that covariate conditioning can sharpen trimming bounds but places it inside an RD
manipulation model with a density budget.  \citet{ChoiLee2023} argue that density continuity
is neither necessary nor sufficient for RD validity and call for more attention to how units
react around the threshold; the proposed sensitivity curve is a formal response to that
critique.  \citet{IshiharaSawada2024} give low-level conditions for manipulation-robust RD
identification; their point-identification focus is adjacent but does not characterize the
sharp bounded-manipulation interval.  \citet{AraiHsuKitagawaMourifieWan2022} and
\citet{HsuShiuWan2024} test fuzzy RD identifying assumptions, which motivates keeping the
first-stage denominator explicit in the local Wald target.

In-repository, \texttt{ThmSmith/doc/API.md} \S3 states that the ThmSmith PartialID catalogue
is empty at seed time and will be populated by \texttt{pid\_*} qids for Manski-family,
Balke--Pearl, IV-bound, sensitivity, shape-restriction, and missing-data results.  Thus
there is no in-catalogue RDD manipulation-bounds proposal whose kernel coincides with this
one.  The reusable banked dynamic-IV PartialID proposals are finite latent-type sharpness
comparators, but their kernels concern dynamic compliance histories rather than RD
manipulation envelopes or covariate-conditional trimming.

\section{Formal setup}
Let \(R\) be the running variable with cutoff \(c\), \(Z=\one\{R\ge c\}\) the threshold
assignment indicator, \(D\in\{0,1\}\) the received treatment, \(Y\in[\underline y,\overline y]\)
the observed outcome, and \(W\in\mathcal W=\{1,\ldots,K\}\) a finite predetermined-covariate
cell.  Write \(\mathcal Y=[\underline y,\overline y]\).  The observable input is the pair of local weak limits
\[
  P_-=\lim_{r\uparrow c}\mathcal L(Y,D,W\mid R=r), \qquad
  P_+=\lim_{r\downarrow c}\mathcal L(Y,D,W\mid R=r),
\]
plus two sensitivity parameters: a global manipulation-share bound \(\bar\rho\in[0,1)\)
and covariate-cell bounds \(\bar s_w\in[0,1)\).  Write \(\pi_-(w)=P_-(W=w)\) and
\(\mu^-_V(w)=\E_{P_-}[V\mid W=w]\) for \(V\in\{Y,D\}\).  When the running-variable
density has cutoff-side limits, write them as \(f_-(c)\) and \(f_+(c)\).

A candidate right-side nonmanipulator distribution is represented by a measurable retention
weight \(a:\mathcal Y\times\{0,1\}\times\mathcal W\to[0,1]\) applied to \(P_+\).  Let
\[
  M_a=\E_{P_+}[a(Y,D,W)],\qquad
  Q_a(B,w)=M_a^{-1}\E_{P_+}[a(Y,D,W)\one\{(Y,D)\in B,W=w\}].
\]
The feasible set \(\mathcal A(P,\bar\rho,\bar s)\) contains those \(a\) satisfying
\[
  1-M_a\le \bar\rho,\qquad
  1-\E_{P_+}[a(Y,D,W)\mid W=w]\le \bar s_w \ \text{for every }w,
  \qquad
  Q_a(W=w)=\pi_-(w).
\]
For a retained mass \(m\in(0,1]\), write
\[
  \mathcal A_m(P,\bar s)=
  \{a:0\le a\le1,\ M_a=m,\ Q_a(W=w)=\pi_-(w),\
    1-\E_{P_+}[a(Y,D,W)\mid W=w]\le\bar s_w\ \forall w\},
  \qquad
  \mathcal A_m^0(P)=
  \{a:0\le a\le1,\ M_a=m,\ Q_a(W=w)=\pi_-(w)\},
\]
and
\[
  I(P,\bar\rho,\bar s)=\{m:\mathcal A_m(P,\bar s)\neq\varnothing,\ 1-m\le\bar\rho\}.
\]
For an exact-share sensitivity face with removed share \(\tau\), define the equality-budget
feasible set
\[
  \mathcal A^{=}_\tau(P,\bar s)=
  \{a:0\le a\le1,\ M_a=1-\tau,\ Q_a(W=w)=\pi_-(w),\
    1-\E_{P_+}[a(Y,D,W)\mid W=w]\le\bar s_w\ \forall w\}.
\]
This face is compatible with the global upper envelope only when \(\tau\le\bar\rho\).
When \(K=1\) and \(\bar s_1\ge\tau\), it is exactly the ordinary class of right-side
subdistributions obtained by trimming the fraction \(\tau\) of the right-side law.
The cell-removal fraction forced by retaining mass \(m\) and matching the left-side
covariate law is
\[
  \phi_w(m)=1-\frac{m\,\pi_-(w)}{P_+(W=w)}
\]
whenever \(P_+(W=w)>0\).  Thus cell caps require \(\phi_w(m)\le\bar s_w\).
For \(a\in\mathcal A(P,\bar\rho,\bar s)\), define
\[
  \Theta(a)=
  \frac{\sum_w \pi_-(w)\{\E_{Q_a}[Y\mid W=w]-\mu^-_Y(w)\}}
       {\sum_w \pi_-(w)\{\E_{Q_a}[D\mid W=w]-\mu^-_D(w)\}}.
\]
Define the capped fixed-mass upper endpoint
\(U(m)=\sup\{\Theta(a):a\in\mathcal A_m(P,\bar s)\}\), the uncapped fixed-mass upper
endpoint \(U^0(m)=\sup\{\Theta(a):a\in\mathcal A_m^0(P)\}\), and the uncapped envelope
endpoint \(U^0_{\mathrm{env}}(\bar\rho)=\sup\{U^0(m):1-m\le\bar\rho\}\).
The identified set \(\Theta_I(P,\bar\rho,\bar s)\) is the set of values of the nonmanipulator
local Wald parameter compatible with \(P\), one-sided manipulation, local continuity for the
nonmanipulator law conditional on \(W\), and the two manipulation budgets.

\begin{verbatim}
Locked parameters.
qid = pid_rdd_manipulation_bounded
specialization = v1
observable distribution P = cutoff-side limits P_- and P_+ of (Y,D,W)
parameter theta = nonmanipulator local Wald effect at the RD cutoff
identifying restrictions = one-sided upward manipulation; local continuity of the
  nonmanipulator potential-outcome/compliance law conditional on finite W; global
  McCrary-style bound rho_bar; covariate-cell manipulation-share caps s_bar_w;
  bounded outcomes; positive retained mass; positive nonmanipulator first stage
bounding functional = sharp fractional trimming interval
  [inf_{a in A(P,rho_bar,s_bar)} Theta(a),
   sup_{a in A(P,rho_bar,s_bar)} Theta(a)]
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Cutoff limits and finite covariate cells]\label{ass:cutoff-limits}
The side limits \(P_-\) and \(P_+\) exist as probability laws on
\([\underline y,\overline y]\times\{0,1\}\times\{1,\ldots,K\}\), and
\(P_-(W=w)>0\) for every \(w\).
\end{assumption}

\begin{assumption}[One-sided upward manipulation]\label{ass:one-sided}
Near the cutoff, manipulators can only add mass to the right side \(R\ge c\).
The left-side limit \(P_-\) is the nonmanipulator limit, while \(P_+\) is a mixture of
nonmanipulators and right-side manipulators.
\end{assumption}

\begin{assumption}[Conditional nonmanipulator continuity]\label{ass:conditional-continuity}
For nonmanipulators, the conditional law of the potential outcomes and treatment-receipt
types relevant for the local Wald numerator and denominator is continuous at \(c\) within
each covariate cell \(W=w\).  Equivalently for this proposal, after removing right-side
manipulators, the retained right-side covariate law equals the left-side law \(\pi_-\), and
the retained right-side observed means identify the right-limit nonmanipulator means.
\end{assumption}

\begin{assumption}[McCrary-style global manipulation envelope]\label{ass:global-envelope}
The total removed right-side mass is bounded by \(\bar\rho\in[0,1)\):
\[
  1-\E_{P_+}[a(Y,D,W)] \le \bar\rho .
\]
The number \(\bar\rho\) may be set from a density-discontinuity confidence envelope rather
than treated as an exactly identified manipulator share.
\end{assumption}

\begin{assumption}[Covariate-cell manipulation-share caps]\label{ass:cell-caps}
For each covariate cell \(w\), the right-side fraction removed inside that cell is bounded
by \(\bar s_w\in[0,1)\):
\[
  1-\E_{P_+}[a(Y,D,W)\mid W=w]\le \bar s_w .
\]
\end{assumption}

\begin{assumption}[Positive retained mass]\label{ass:positive-retained}
Every feasible retention rule has \(M_a=\E_{P_+}[a(Y,D,W)]>0\), and the feasible set
\(\mathcal A(P,\bar\rho,\bar s)\) is nonempty.
\end{assumption}

\begin{assumption}[Positive nonmanipulator first stage]\label{ass:positive-first-stage}
There exists \(\kappa>0\) such that for every feasible \(a\in\mathcal A(P,\bar\rho,\bar s)\),
\[
  \sum_w \pi_-(w)\{\E_{Q_a}[D\mid W=w]-\mu^-_D(w)\}\ge \kappa .
\]
In a sharp RD specialization \(D=Z\), this denominator is equal to one.
\end{assumption}

\begin{assumption}[Sharp RD specialization]\label{ass:sharp-rd-specialization}
For results that explicitly invoke the sharp RD face, \(D=Z\) almost surely in the
left- and right-cutoff limits, so treatment receipt is the threshold assignment indicator.
\end{assumption}

\begin{assumption}[Finite-support endpoint geometry]\label{ass:finite-support-geometry}
For results that explicitly invoke endpoint geometry, \(Y\) has finite support in each
covariate cell \(W=w\).
\end{assumption}

\begin{assumption}[Exact-share one-cell face]\label{ass:exact-share-one-cell}
For results that explicitly invoke the one-cell exact-share face, \(K=1\), the removed share
is fixed at \(\tau\in[0,1)\), \(\tau\le\bar\rho\), the endpoint is evaluated on the
restricted equality-budget set \(\mathcal A^{=}_\tau(P,\bar s)\) rather than on the full
upper-envelope set \(\mathcal A(P,\bar\rho,\bar s)\), and the cell cap is inactive or
satisfies \(\bar s_1\ge\tau\).
\end{assumption}

\begin{assumption}[Two-cell cap-separation design]\label{ass:cap-separation}
For results that explicitly invoke cap-envelope separation, \(K=2\), \(P_+(W=w)>0\) for
both cells, \(Y\) has finite support in each cell, \(D=Z\), and the fixed-mass upper endpoint
\(U(m)\) is finite and locally single-valued on a nonempty interval of retained masses.
There is an uncapped maximizer \(m^0=1-\bar\rho\) for \(U^0_{\mathrm{env}}(\bar\rho)\), a unique capped
minimum feasible mass
\[
  m^c=\max\left\{1-\bar\rho,\,
    \frac{(1-\bar s_1)P_+(W=1)}{\pi_-(1)},\,
    \frac{(1-\bar s_2)P_+(W=2)}{\pi_-(2)}
  \right\},
\]
with \(m^c>m^0\), and \(U(m)\) is strictly decreasing on a neighborhood of
\([m^0,m^c]\).  The binding cell at \(m^c\) is unique.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: no-manipulation face]\label{thm:no-manipulation-face}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage}, if
\(\bar\rho=0\), \(\bar s_w=0\) for every \(w\), and \(P_+(W=w)=P_-(W=w)\) for every \(w\),
then \(\mathcal A(P,0,0)=\{a\equiv1\}\) and
\[
  \Theta_I(P,0,0)=
  \left\{
  \frac{\E_{P_+}[Y]-\E_{P_-}[Y]}{\E_{P_+}[D]-\E_{P_-}[D]}
  \right\}.
\]
For sharp RD with \(D=Z\), this singleton is \(\E_{P_+}[Y]-\E_{P_-}[Y]\).
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This theorem is not the novelty claim; it records the exact face where the proposal
reduces to \citet{HahnToddVanDerKlaauw2001} and \citet{Lee2008}.  The gap is that those
papers do not define the surrounding bounded-manipulation sensitivity set.  (b) The
consumer is the applied RD workflow in \citet{CattaneoIdroboTitiunik2020}: the sensitivity
curve must pass through the conventional RD point estimate when the manipulation budget is
set to zero.

\begin{conjecture}[Conjecture 1: sharp budgeted conditional trimming]\label{conj:sharp-budgeted-trim}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage},
the sharp identified set for the nonmanipulator local Wald parameter is exactly
\[
  \Theta_I(P,\bar\rho,\bar s)
  =
  \{\Theta(a):a\in\mathcal A(P,\bar\rho,\bar s)\}.
\]
Equivalently, the tightest sharp interval is
\[
  [B_L(P,\bar\rho,\bar s),B_U(P,\bar\rho,\bar s)]
  =
  \left[
  \inf_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a),
  \sup_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a)
  \right].
\]
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{GerardRokkanenRothe2020} give sharp RD manipulation bounds when the relevant
manipulation share is inferred from the density ratio, including covariate-conditioned
tightening based on identified covariate distributions, and their fuzzy-RD results optimize
over partially identified share values.  The precise gap is therefore not ``GRR has no
optimization.''  It is that this conjecture treats the density jump as an upper envelope
and adds external cell caps while still forcing \(Q_a(W)=\pi_-\).  The feasible set is the
intersection of fixed-share GRR faces indexed by \(m\in I(P,\bar\rho,\bar s)\), with the
admissible index set itself changed by the external cell caps and retained-\(W\) equation
rather than by the exact conditional density-ratio face alone.  \citet{Semenova2025} gives covariate Lee bounds
in sample-selection settings, but not the RD density-envelope restriction
\(1-M_a\le\bar\rho\) or the retained-covariate-law condition \(Q_a(W)=\pi_-\).  (b) The
consumer is RD studies with small density discontinuities, such as the manipulation-sensitive
applications discussed by \citet{ChoiLee2023}; they would get a sharp interval instead of
a binary validity decision.

\begin{conjecture}[Conjecture 2: active-budget endpoint geometry]\label{conj:endpoint-geometry}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage}
and Assumption~\ref{ass:finite-support-geometry}, the endpoint functions
\((\bar\rho,\bar s)\mapsto B_L(P,\bar\rho,\bar s)\) and
\((\bar\rho,\bar s)\mapsto B_U(P,\bar\rho,\bar s)\) are attained by threshold-retention
rules that order observations by an affine score
\[
  y-\lambda d+\eta_w+\nu
\]
for a scalar fractional-program multiplier \(\lambda\), cell multipliers \(\eta_w\), and
a global density-budget multiplier \(\nu\).  Consequently the endpoints are continuous
and piecewise rational in \((\bar\rho,\bar s)\), with kinks when the binding constraint
switches between the McCrary envelope and one or more covariate-share caps.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest known formulas are Lee-style trimming quantiles in \citet{Lee2009} and the
exact-share RD trimming in \citet{GerardRokkanenRothe2020}; neither has a two-level budget
whose active constraint changes across covariate cells.  (b) The concrete consumer is
software based on \citet{CattaneoJanssonMa2020}: a verified endpoint geometry would let
implementations report which covariate cell or global density envelope determines the
manipulation-robust RD interval.

\begin{conjecture}[Conjecture 3: positive cap-envelope separation]\label{conj:cap-separation}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage}
and Assumption~\ref{ass:cap-separation}, the capped upper endpoint is
\[
  B_U(P,\bar\rho,\bar s)=U(m^c)<U^0(m^0)=U^0_{\mathrm{env}}(\bar\rho).
\]
Moreover this strict inequality is locally stable under small perturbations of \(P\),
\(\bar\rho\), and \(\bar s\) that preserve the unique binding cell.  Thus the external
cell-cap restriction changes the sharp upper envelope on an open class of observable laws:
the endpoint is not merely a different maximizer within the cell-cap-free GRR exact-share
family, but a strictly smaller value forced by the retained-\(W\) equality
\(\phi_w(m)=1-m\pi_-(w)/P_+(W=w)\) and the binding cap.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{GerardRokkanenRothe2020} already cover exact-share and partially identified
share optimization; this conjecture isolates the additional field-level claim needed here:
cell caps plus the retained-\(W\) equation can remove the GRR worst-case fixed-share face
from the feasible set on an open class of observable laws.  The gap is a positive sharpness
separation between the proposed global-plus-cell envelope and the cell-cap-free GRR
fixed-share envelope, not a refutation of any named estimator or software implementation.
(b) The consumer is the empirical RD validation workflow in
\citet{CattaneoIdroboTitiunik2020}: a practitioner who observes one problematic covariate
cell would know that the correct sensitivity interval may be driven by that cell cap rather
than by the largest density-discontinuity share.

\begin{theorem}[Theorem 2: sharp-RD exact-share one-cell reduction]\label{thm:exact-share-face}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage},
\ref{ass:sharp-rd-specialization}, and~\ref{ass:exact-share-one-cell}, the restricted
equality-budget face
\[
  \{\Theta(a):a\in\mathcal A^{=}_\tau(P,\bar s)\}
\]
reduces to the ordinary Lee outcome-tail trimming bounds for the right-side distribution.
This is the sharp-design exact-share face of \citet{GerardRokkanenRothe2020}.  The theorem
does not assert that the full upper-envelope bounds in
Conjecture~\ref{conj:sharp-budgeted-trim} equal exact-share Lee trimming unless the
upper-envelope feasible set is explicitly replaced by this equality-budget face.  No
ordinary-outcome-trimming reduction is asserted here for fuzzy RD, where the Wald endpoint
couples outcome and treatment-retention margins.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This theorem is a required sanity face rather than the new kernel: in sharp RD it
matches \citet{Lee2009} and the sharp-design specialization of
\citet{GerardRokkanenRothe2020} when the proposed upper-envelope uncertainty is replaced
by the equality-budget constraint \(1-M_a=\tau\).  The compatibility condition
\(\tau\le\bar\rho\) and the cap condition \(\bar s_1\ge\tau\), or explicit deactivation of
the one cell cap, are needed because otherwise the exact-share restricted feasible set is
outside the upper envelope or empty.
The fuzzy exact-share face is intentionally left to the full Wald program because GRR's
fuzzy bounds optimize over treatment-status-specific manipulator shares rather than a
single ordinary outcome tail.  (b) The consumer is \citet{GerardRokkanenRothe2020} itself:
the proposed envelope result must contain their sharp-design exact-share formula as a clean
corollary before the bounded-share extension is credible.

\section{Sanity-check corollaries}
\begin{corollary}[Sharp RD point-identification corner]\label{cor:sharp-rd-corner}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage} and
Assumption~\ref{ass:sharp-rd-specialization}, if \(\bar\rho=0\), \(\bar s_w=0\) for every
\(w\), and \(P_+(W)=P_-(W)\), then
Theorem~\ref{thm:no-manipulation-face} collapses to the Lee sharp RD estimand
\(\E[Y\mid R=c+]-\E[Y\mid R=c-]\).  The reduction is immediate because no right-side mass
can be removed and the sharp RD first stage is one.
\end{corollary}

\begin{corollary}[Sharp-RD exact density-ratio corner]\label{cor:grr-corner}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage},
\ref{ass:sharp-rd-specialization}, and~\ref{ass:exact-share-one-cell}, if the
density jump point-identifies \(\tau=1-f_-(c)/f_+(c)\), then the restricted exact-share version of
Theorem~\ref{thm:exact-share-face} gives the Gerard--Rokkanen--Rothe sharp-design
manipulation bounds.  The reduction holds because
\(\mathcal A^{=}_\tau(P,\bar s)\) is nonempty, \(\tau\le\bar\rho\) makes it compatible
with the global envelope, and \(K=1\) with \(\bar s_1\ge\tau\) makes the cell cap inactive;
therefore the feasible set is the class of subdistributions obtained by trimming exactly
the fraction \(\tau\) from the right-side outcome law, and the first-stage denominator is
fixed at one.
\end{corollary}

\begin{corollary}[Vacuous upper-envelope corner]\label{cor:manski-corner}
If the global and cellwise envelopes allow removing all but an arbitrarily small retained
right-side mass in every covariate cell while preserving Assumption~\ref{ass:positive-first-stage},
then the endpoint problem approaches the bounded-outcome Manski/Horowitz--Manski fill-in
face for the right-side nonmanipulator means.  This checks that the proposal becomes
conservative when the manipulation envelope carries essentially no information.
\end{corollary}

\section{Proof-sketch route}
The verification route is finite-dimensional after discretizing \(W\) and, for the endpoint
geometry theorem, taking \(Y\) to have finite support.  Sharpness should follow from the
standard contaminated-distribution construction: any feasible retention rule decomposes the
observed right-side law into retained nonmanipulator mass plus removed manipulator mass, and
conversely any structural model satisfying one-sided manipulation and the budgets induces
such a retention rule.  The fractional Wald objective can be handled by a Charnes--Cooper
or support-function transform, reducing endpoint evaluation to linear programs indexed by
a candidate ratio \(\lambda\).  The boundary checks are the zero-budget singleton, the
sharp-RD one-cell equality-budget Lee trimming formula with \(\tau\le\bar\rho\) and
\(\bar s_1\ge\tau\), and a two-cell example where the global density budget and one
covariate cap alternately bind.  The
separation conjecture should reduce to computing the fixed-mass tail derivative \(U'(m)\)
on that two-cell example and checking that excluding the uncapped minimum-mass optimizer \(m^0\) forces
the endpoint to the capped boundary \(m^c\).

\section{Honest scope flags}
Theorem~\ref{thm:no-manipulation-face} is intended as a routine reduction, and
Theorem~\ref{thm:exact-share-face} is only the sharp-RD equality-budget exact-share sanity
face, not a claim about the full upper-envelope program.  The fuzzy
exact-share reduction is not claimed to be ordinary Lee trimming; it remains part of the
full Wald endpoint program because outcome and treatment retention are coupled.
Conjectures~\ref{conj:sharp-budgeted-trim}
and~\ref{conj:endpoint-geometry} and the separation
Conjecture~\ref{conj:cap-separation} are the novel kernels and are not yet proved.  The finite
covariate-cell convention is deliberate; continuous covariates would require an additional
measurability and regularization layer and are outside this proposal.  The proposal assumes
one-sided upward manipulation; two-sided manipulation can mask density jumps and would need
a different sensitivity parameter.  The first-stage positivity assumption is strong but
keeps the target a well-posed local Wald effect rather than a weak-instrument RD problem.
No v1 flagship conjecture has been withdrawn; the v1 exact-share reduction was narrowed to
the sharp-RD face and no longer claims ordinary outcome-tail trimming for fuzzy RD.  The
v3 draft concedes that GRR already has partially identified share optimization and therefore
promotes the cell-cap/nonrectangular-feasible-set separation to an explicit conjecture.  The
v4 draft reframes this separation as a positive open-set sharpness claim rather than a
shortcut refutation, and restricts Theorem~\ref{thm:exact-share-face} to the equality-budget
face \(\mathcal A^{=}_\tau(P,\bar s)\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft of the bounded RD manipulation-envelope proposal;
prior verdict: none.
\item v2 (revise) --- sharpened the GRR comparison around upper-envelope and cell-cap
uncertainty, renamed the generic mean index to avoid collision with threshold assignment,
and narrowed the exact-share sanity reduction to sharp RD; prior verdict: REVISE.
\item v3 (revise) --- corrected the GRR comparison, added a nonrectangular cap-envelope
separation conjecture, and required \(\bar s_1\ge\tau\) for the exact-share one-cell sanity
face; prior verdict: REVISE.
\item v4 (revise) --- reframed Conjecture~\ref{conj:cap-separation} as a positive
open-set separation from the cell-cap-free GRR envelope and defined the equality-budget
face used by Theorem~\ref{thm:exact-share-face}; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Arai et~al.(2022)]{AraiHsuKitagawaMourifieWan2022}
Arai, Yoichi, Yu-Chin Hsu, Toru Kitagawa, Ismael Mourifie, and Yuanyuan Wan.
2022.
Testing identifying assumptions in fuzzy regression discontinuity designs.
\emph{Quantitative Economics} 13(1): 1--28.

\bibitem[Bugni and Canay(2021)]{BugniCanay2021}
Bugni, Federico A., and Ivan A. Canay.
2021.
Testing continuity of a density via \(g\)-order statistics in the regression discontinuity design.
\emph{Journal of Econometrics} 221(1): 138--159.

\bibitem[Canay and Kamat(2018)]{CanayKamat2018}
Canay, Ivan A., and Vishal Kamat.
2018.
Approximate permutation tests and induced order statistics in the regression discontinuity design.
\emph{Review of Economic Studies} 85(3): 1577--1608.

\bibitem[Cattaneo, Idrobo, and Titiunik(2020)]{CattaneoIdroboTitiunik2020}
Cattaneo, Matias D., Nicolas Idrobo, and Rocio Titiunik.
2020.
\emph{A Practical Introduction to Regression Discontinuity Designs: Foundations}.
Cambridge University Press.

\bibitem[Cattaneo, Jansson, and Ma(2020)]{CattaneoJanssonMa2020}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem[Cattaneo and Titiunik(2022)]{CattaneoTitiunik2022}
Cattaneo, Matias D., and Rocio Titiunik.
2022.
Regression discontinuity designs.
\emph{Annual Review of Economics} 14: 821--851.

\bibitem[Choi and Lee(2023)]{ChoiLee2023}
Choi, Jin-young, and Myoung-jae Lee.
2023.
Score manipulation, density continuity and intent-to-treat effect for regression discontinuity.
\emph{Pacific Economic Review} 28(4): 552--569.

\bibitem[Gerard, Rokkanen, and Rothe(2020)]{GerardRokkanenRothe2020}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem[Hahn, Todd, and van der Klaauw(2001)]{HahnToddVanDerKlaauw2001}
Hahn, Jinyong, Petra Todd, and Wilbert van der Klaauw.
2001.
Identification and estimation of treatment effects with a regression-discontinuity design.
\emph{Econometrica} 69(1): 201--209.

\bibitem[Horowitz and Manski(1995)]{HorowitzManski1995}
Horowitz, Joel L., and Charles F. Manski.
1995.
Identification and robustness with contaminated and corrupted data.
\emph{Econometrica} 63(2): 281--302.

\bibitem[Hsu, Shiu, and Wan(2024)]{HsuShiuWan2024}
Hsu, Yu-Chin, Ji-Liang Shiu, and Yuanyuan Wan.
2024.
Testing identification conditions of LATE in fuzzy regression discontinuity designs.
\emph{Journal of Econometrics} 241(1).

\bibitem[Imbens and Lemieux(2008)]{ImbensLemieux2008}
Imbens, Guido W., and Thomas Lemieux.
2008.
Regression discontinuity designs: A guide to practice.
\emph{Journal of Econometrics} 142(2): 615--635.

\bibitem[Ishihara and Sawada(2024)]{IshiharaSawada2024}
Ishihara, Takuya, and Masayuki Sawada.
2024.
Manipulation-robust regression discontinuity designs.
arXiv:2009.07551, version 7.

\bibitem[Lee(2008)]{Lee2008}
Lee, David S.
2008.
Randomized experiments from non-random selection in U.S. House elections.
\emph{Journal of Econometrics} 142(2): 675--697.

\bibitem[Lee(2009)]{Lee2009}
Lee, David S.
2009.
Training, wages, and sample selection: Estimating sharp bounds on treatment effects.
\emph{Review of Economic Studies} 76(3): 1071--1102.

\bibitem[Lee and Lemieux(2010)]{LeeLemieux2010}
Lee, David S., and Thomas Lemieux.
2010.
Regression discontinuity designs in economics.
\emph{Journal of Economic Literature} 48(2): 281--355.

\bibitem[McCrary(2008)]{McCrary2008}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem[Semenova(2025)]{Semenova2025}
Semenova, Vira.
2025.
Generalized Lee bounds.
\emph{Journal of Econometrics} 251: 106055.
\end{thebibliography}

\end{document}
