% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_rdd\_manipulation\_bounded, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_rdd\_manipulation\_bounded} / \texttt{v1}%
  \\ \large\textit{Sharp budgeted RD manipulation bounds from covariate-capped trimming}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies a regression-discontinuity design in which the right-limit law at the
cutoff may contain one-sided manipulators, but the total manipulated share is bounded by a
McCrary-style envelope and each predetermined-covariate cell has its own manipulation cap.
The target causal estimand is the local Wald effect for the nonmanipulating cutoff
population, formed from the nonmanipulator right-limit outcome and treatment means and the
observed left-limit means.  The estimand-defining object is the fractional trimming
functional
\[
  \bigl(B_L(P,\bar\rho,\bar s),B_U(P,\bar\rho,\bar s)\bigr)
  =
  \left(\inf_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a),
  \sup_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a)\right),
\]
where \(a\) is a right-side retention weight satisfying the global budget, cell caps, and
the retained-covariate-law equation.  The first theorem gives the sharp trimming
characterization: the identified set is exactly the image of this feasible retention class,
and hence is contained in the displayed interval with sharp endpoints.  The novelty-bearing
result is cap-envelope separation: on an explicit two-cell finite-support open set, a
binding external cell cap forces a larger retained mass than the McCrary envelope alone
and strictly lowers the sharp upper endpoint relative to the cell-cap-free envelope.
Finite-support endpoint geometry is obtained as a compact linear-fractional program with
score-threshold retention rules and piecewise-rational formulas only on feasible
active-basis regions with denominator bounded away from zero.
\end{abstract}

\section{Introduction}
Regression discontinuity designs are valuable because they turn local movement across a
cutoff into a source of quasi-experimental variation.  Manipulation of the running
variable threatens that interpretation: the right-limit population may contain units that
selected into the treatment side, so the usual right-minus-left contrast need not compare
the same local population.  Density and covariate-balance diagnostics often reveal this
threat, but a diagnostic rejection by itself does not say how large the local effect could
still be under a controlled amount of manipulation.

The classical RD result identifies a local effect under continuity of potential-outcome and
compliance laws at the cutoff.  The manipulated-running-variable literature gives sharp
bounds when one-sided manipulation identifies or restricts the manipulator share, and
Lee-style trimming results show how bounded contamination can be converted into extremal
subpopulation means.  This note uses the same contaminated-distribution logic, but treats
the density discontinuity as an upper envelope and intersects it with finite
covariate-cell caps.

The first object is a sharp fractional trimming interval.  A feasible retention rule
removes some right-side mass, subject to the total and cellwise budgets, and forces the
retained right-side covariate distribution to match the left-side distribution.  The
retained right-side law then supplies the possible nonmanipulator right-limit means; the
local Wald ratio over all such retained laws is the identified set.  The additional
separation result proves that the cell caps are not merely a reparameterization of the
cell-cap-free envelope: on a nondegenerate open class, the cap removes the uncapped
worst-case fixed-share face and strictly tightens the upper bound.  Together these results
turn a pass/fail manipulation diagnostic into a sensitivity curve and identify which global
or cellwise restriction tightens the interval.

\paragraph{Motivating conjecture(s).}
\begin{conjecture}[Conjecture 1: sharp budgeted conditional trimming]\label{conj:sharp-budgeted-trim}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage},
the sharp identified set for the nonmanipulator local Wald parameter is exactly
\[
  \Theta_I(P,\bar\rho,\bar s)
  =
  \{\Theta(a):a\in\mathcal A(P,\bar\rho,\bar s)\}.
\]
Equivalently, the tightest sharp interval is
\[
  [B_L(P,\bar\rho,\bar s),B_U(P,\bar\rho,\bar s)]
  =
  \left[
  \inf_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a),
  \sup_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a)
  \right].
\]
\end{conjecture}

\begin{conjecture}[Conjecture 2: active-budget endpoint geometry]\label{conj:endpoint-geometry}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage}
and Assumption~\ref{ass:finite-support-geometry}, the endpoint functions
\((\bar\rho,\bar s)\mapsto B_L(P,\bar\rho,\bar s)\) and
\((\bar\rho,\bar s)\mapsto B_U(P,\bar\rho,\bar s)\) are attained by threshold-retention
rules that order observations by an affine score
\[
  y-\lambda d+\eta_w+\nu
\]
for a scalar fractional-program multiplier \(\lambda\), cell multipliers \(\eta_w\), and
a global density-budget multiplier \(\nu\).  Consequently the endpoints are continuous
and piecewise rational in \((\bar\rho,\bar s)\), with kinks when the binding constraint
switches between the McCrary envelope and one or more covariate-share caps.
\end{conjecture}

\begin{conjecture}[Conjecture 3: positive cap-envelope separation]\label{conj:cap-separation}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage}
and Assumption~\ref{ass:cap-separation}, the capped upper endpoint is
\[
  B_U(P,\bar\rho,\bar s)=U(m^c)<U^0(m^0)=U^0_{\mathrm{env}}(\bar\rho).
\]
Moreover this strict inequality is locally stable under small perturbations of \(P\),
\(\bar\rho\), and \(\bar s\) that preserve the unique binding cell.  Thus the external
cell-cap restriction changes the sharp upper envelope on an open class of observable laws:
the endpoint is not merely a different maximizer within the cell-cap-free GRR exact-share
family, but a strictly smaller value forced by the retained-\(W\) equality
\(\phi_w(m)=1-m\pi_-(w)/P_+(W=w)\) and the binding cap.
\end{conjecture}

\section{Related work and positioning}
Hahn, Todd, and van der Klaauw \cite{HahnToddVanDerKlaauw2001} give the continuity-based
identification argument for sharp and fuzzy RD estimands; the zero-manipulation face below
reduces to their local Wald formula.  Lee \cite{Lee2008} gives the local-randomization
interpretation of close elections and motivates the idea that predetermined covariates
should be continuous at a valid cutoff.  Imbens and Lemieux \cite{ImbensLemieux2008} and
Lee and Lemieux \cite{LeeLemieux2010} explain the applied RD workflow in which density and
covariate checks are routine design diagnostics.

McCrary \cite{McCrary2008} introduced the density-discontinuity test used to detect sorting
around the cutoff.  Cattaneo, Jansson, and Ma \cite{CattaneoJanssonMa2020} provide modern
local-polynomial density estimators, which are a natural source for the envelope
\(\bar\rho\).  Canay and Kamat \cite{CanayKamat2018} develop covariate-distribution tests
in RD, motivating sensitivity parameters that restrict manipulation cell by cell.

Gerard, Rokkanen, and Rothe \cite{GerardRokkanenRothe2020} are the closest prior result:
they derive sharp RD bounds under one-sided manipulation when density ratios discipline
the manipulated share, develop covariate-conditioned bounds, and handle fuzzy designs by
optimizing over partially identified share functions.  The present note does not claim
that covariate conditioning or share optimization is absent from their analysis.  The
difference is the feasible set.  GRR's covariate-conditioned and fuzzy/share-optimization
classes are generated by the exact one-sided manipulation model and the observable
density/covariate restrictions available inside that model.  Here the analyst instead
supplies an external McCrary upper envelope \(1-M_a\le\bar\rho\), external cell caps
\(1-\E[a\mid W=w]\le\bar s_w\), and the retained-covariate-law equation
\(Q_a(W)=\pi_-\).  The intersection of these three restrictions can delete the
cell-cap-free worst fixed-share face even when that face is allowed by the global envelope;
Theorem~\ref{thm:cap-separation} proves this strict deletion on an open two-cell class.
Lee \cite{Lee2009} and Horowitz and Manski \cite{HorowitzManski1995} supply the trimming
and contaminated-distribution arguments used in the proof.  Semenova \cite{Semenova2025}
shows how covariates sharpen Lee-style selection bounds; here the same conditioning logic
is embedded in an RD manipulation model with an external density envelope.  Arai et al.
\cite{AraiHsuKitagawaMourifieWan2022} and Hsu, Shiu, and Wan \cite{HsuShiuWan2024} study
testing assumptions in fuzzy RD, which is why the first-stage denominator remains explicit
rather than being suppressed.

No in-repository theorem is used as an input to this derivation.  The note is positioned
as a self-contained partial-identification result: its closest mathematical relatives are
Manski contaminated-distribution bounds, Lee trimming bounds, and the manipulated-RD
bounds of Gerard, Rokkanen, and Rothe, but the novelty-bearing comparison is the strict
separation between the cell-cap-free upper-envelope retention class and the proposed
global-plus-cell budgeted retention class.

\section{Formal setup}
Let \(R\) be the running variable with cutoff \(c\), let \(Z=\one\{R\ge c\}\) be the
cutoff-side indicator, let \(D\in\{0,1\}\) be treatment receipt, let
\(Y\in[\underline y,\overline y]\) be the observed outcome, and let
\(W\in\mathcal W=\{1,\ldots,K\}\) be a finite predetermined-covariate cell.  The observable
distribution is
\[
  P=(P_-,P_+),\qquad
  P_-=\lim_{r\uparrow c}\mathcal L(Y,D,W\mid R=r),\qquad
  P_+=\lim_{r\downarrow c}\mathcal L(Y,D,W\mid R=r).
\]
Write \(\pi_-(w)=P_-(W=w)\), \(p_+(w)=P_+(W=w)\), and
\(\mu^-_V(w)=\E_{P_-}[V\mid W=w]\) for \(V\in\{Y,D\}\).  The analyst also fixes
\(\bar\rho\in[0,1)\) and \(\bar s_w\in[0,1)\), interpreted respectively as a total
right-side manipulation envelope and cellwise manipulation-share caps.

A candidate nonmanipulator right-limit law is represented by a measurable retention weight
\[
  a:[\underline y,\overline y]\times\{0,1\}\times\mathcal W\to[0,1].
\]
Let
\[
  M_a=\E_{P_+}[a(Y,D,W)]
\]
be retained right-side mass.  If \(M_a>0\), define the retained law
\[
  Q_a(B)=M_a^{-1}\E_{P_+}\!\left[a(Y,D,W)\one\{(Y,D,W)\in B\}\right].
\]
The feasible retention class is
\[
\begin{split}
  \mathcal A(P,\bar\rho,\bar s)=
  \bigl\{a:\;&0\le a\le1,\ M_a>0,\ 1-M_a\le\bar\rho,\\
  &1-\E_{P_+}[a(Y,D,W)\mid W=w]\le \bar s_w\ \forall w\text{ with }p_+(w)>0,\\
  &Q_a(W=w)=\pi_-(w)\ \forall w\bigr\}.
\end{split}
\]
If \(p_+(w)=0\) and \(\pi_-(w)>0\), the last equality is impossible, so the feasible set is
empty; nonemptiness is stated as an assumption below.  For \(a\in\mathcal A(P,\bar\rho,\bar s)\),
define
\[
  \Theta(a)=
  \frac{\sum_w \pi_-(w)\{\E_{Q_a}[Y\mid W=w]-\mu^-_Y(w)\}}
       {\sum_w \pi_-(w)\{\E_{Q_a}[D\mid W=w]-\mu^-_D(w)\}}.
\]
Equivalently, because \(Q_a(W=w)=\pi_-(w)\),
\[
  \Theta(a)=
  \frac{M_a^{-1}\E_{P_+}[aY]-\E_{P_-}[Y]}
       {M_a^{-1}\E_{P_+}[aD]-\E_{P_-}[D]}.
\]
The identified set \(\Theta_I(P,\bar\rho,\bar s)\) is the set of nonmanipulator local Wald
values compatible with \(P\), one-sided upward manipulation, conditional nonmanipulator
continuity, bounded outcomes, positive retained mass, the positive first-stage condition,
and the two manipulation budgets.

For endpoint geometry, it is useful to fix retained mass \(m\) and write
\[
\begin{split}
  \mathcal A_m(P,\bar s)=
  \bigl\{a:\;&0\le a\le1,\ M_a=m,\ Q_a(W=w)=\pi_-(w)\ \forall w,\\
  &1-\E_{P_+}[a(Y,D,W)\mid W=w]\le\bar s_w\ \forall w\text{ with }p_+(w)>0\bigr\},
\end{split}
\]
\[
  \mathcal A_m^0(P)=
  \{a:0\le a\le1,\ M_a=m,\ Q_a(W=w)=\pi_-(w)\ \forall w\},
\]
and
\[
  I(P,\bar\rho,\bar s)=
  \{m\in(0,1]:\mathcal A_m(P,\bar s)\neq\varnothing,\ 1-m\le\bar\rho\}.
\]
Define \(U(m)=\sup\{\Theta(a):a\in\mathcal A_m(P,\bar s)\}\) on the capped feasible
domain, \(U^0(m)=\sup\{\Theta(a):a\in\mathcal A_m^0(P)\}\), and
\[
  U^0_{\mathrm{env}}(\bar\rho)=\sup\{U^0(m):1-m\le\bar\rho\}.
\]
For an exact-share face with removed share \(\tau\), define
\[
  \mathcal A^{=}_\tau(P,\bar s)
  =
  \{a\in\mathcal A(P,\bar\rho,\bar s):M_a=1-\tau\}.
\]
The cell-removal fraction forced by retained mass \(m\) and the retained-\(W\) equation is
\[
  \phi_w(m)=1-\frac{m\pi_-(w)}{p_+(w)}
\]
whenever \(p_+(w)>0\).  Equivalently the retained fraction in cell \(w\) is
\[
  r_w(m)=\frac{m\pi_-(w)}{p_+(w)}.
\]
Thus fixed-mass feasibility requires both
\[
  r_w(m)\le1
  \quad\Longleftrightarrow\quad
  m\le \frac{p_+(w)}{\pi_-(w)}
\]
from the constraint \(a\le1\), and
\[
  r_w(m)\ge1-\bar s_w
  \quad\Longleftrightarrow\quad
  m\ge \frac{(1-\bar s_w)p_+(w)}{\pi_-(w)}
\]
from the cell cap.  Both inequalities are part of the fixed-mass cell-feasibility algebra.

For sharp RD finite-support separation arguments, define the upper-tail retained mean in
cell \(w\) by
\[
  \Gamma_w(r)
  =
  \sup\left\{
    \frac{\E_{P_+}[b(Y,D,W)Y\mid W=w]}{r}:
    0\le b\le1,\ \E_{P_+}[b(Y,D,W)\mid W=w]=r
  \right\},
  \qquad r\in(0,1].
\]
In finite support this supremum is attained by retaining the largest \(Y\)-atoms in that
cell, with possible fractional retention at the cutoff atom.  The function
\(\Gamma_w\) is weakly decreasing in \(r\), and it is strictly decreasing on intervals
where the required retained fraction crosses a positive-mass lower outcome atom after all
higher atoms are already fully retained.

\paragraph{Locked parameters.}
\begin{itemize}
  \item \(\texttt{qid}\): \(\texttt{pid\_rdd\_manipulation\_bounded}\).
  \item \(\texttt{specialization}\): \(\texttt{v1}\).
  \item observable distribution \(P\): the two cutoff-side weak limits \(P_-\) and \(P_+\) of
  \((Y,D,W)\) given the running variable approaches the cutoff from below and above, where
  \(Y\in[\underline y,\overline y]\), \(D\in\{0,1\}\), and
  \(W\in\{1,\ldots,K\}\) is a finite predetermined-covariate cell.
  \item parameter \(\theta\): the local Wald effect for the nonmanipulating cutoff population,
  \[
    \theta =
    \frac{\sum_w \pi_-(w)\{\mu^Y_{+,0}(w)-\mu^Y_-(w)\}}
         {\sum_w \pi_-(w)\{\mu^D_{+,0}(w)-\mu^D_-(w)\}},
  \]
  where \(\pi_-(w)=P_-(W=w)\), \(\mu^-_V(w)=\E_{P_-}[V\mid W=w]\), and
  \(\mu^V_{+,0}(w)\) denotes the right-limit nonmanipulator mean of \(V\in\{Y,D\}\)
  in covariate cell \(w\).
  \item identifying restrictions: one-sided upward manipulation at the cutoff, local continuity
  of the nonmanipulator potential-outcome and compliance law conditional on \(W\), a
  McCrary-style global manipulation-share envelope \(\bar\rho\in[0,1)\),
  covariate-cell manipulation-share caps \(\bar s_w\in[0,1)\), bounded outcomes,
  positive retained mass, and a positive nonmanipulator first-stage denominator.
  \item bounding functional: the sharp fractional trimming program over retention weights
  \(a(y,d,w)\in[0,1]\):
  \[
    B_L(P,\bar\rho,\bar s)=\inf_{a\in\mathcal A(P,\bar\rho,\bar s)} \Theta(a),
    \qquad
    B_U(P,\bar\rho,\bar s)=\sup_{a\in\mathcal A(P,\bar\rho,\bar s)} \Theta(a),
  \]
  where \(\mathcal A(P,\bar\rho,\bar s)\) enforces the global and cellwise removal
  budgets and the retained right-side covariate distribution \(\pi_-\), and
  \(\Theta(a)\) is the Wald ratio formed from the retained right-side means and the
  observed left-side means.  The sharpness verdict proved below is sharp for the
  maintained bounded-manipulation model.
\end{itemize}

\section{Assumptions}
\begin{assumption}[Cutoff limits and finite covariate cells]\label{ass:cutoff-limits}
The side limits \(P_-\) and \(P_+\) exist as probability laws on
\([\underline y,\overline y]\times\{0,1\}\times\{1,\ldots,K\}\).  The outcome endpoints
satisfy \(-\infty<\underline y\le\overline y<\infty\), and
\(\pi_-(w)=P_-(W=w)>0\) for every \(w\).
\end{assumption}

\begin{assumption}[One-sided upward manipulation]\label{ass:one-sided}
Near the cutoff, manipulators can only add mass to the right side \(R\ge c\).  Thus
\(P_-\) is the nonmanipulator left-limit law, while \(P_+\) is a mixture of a
right-limit nonmanipulator law and a right-side manipulator law.
\end{assumption}

\begin{assumption}[Conditional nonmanipulator continuity]\label{ass:conditional-continuity}
For nonmanipulators, the conditional law of the potential outcomes and treatment-receipt
types relevant for the local Wald numerator and denominator is continuous at \(c\) within
each covariate cell \(W=w\).  Consequently the retained right-side covariate law for
nonmanipulators must equal \(\pi_-\), and retained right-side observed means equal the
right-limit nonmanipulator means \(\mu^V_{+,0}(w)\), \(V\in\{Y,D\}\).
\end{assumption}

\begin{assumption}[McCrary-style global manipulation envelope]\label{ass:global-envelope}
For every admissible structural completion, the total removed right-side mass is bounded
by \(\bar\rho\in[0,1)\).  In retention-weight notation this is
\[
  1-\E_{P_+}[a(Y,D,W)]\le\bar\rho .
\]
\end{assumption}

\begin{assumption}[Covariate-cell manipulation-share caps]\label{ass:cell-caps}
For every admissible structural completion and every \(w\) with \(p_+(w)>0\), the
right-side fraction removed inside cell \(w\) is bounded by \(\bar s_w\in[0,1)\):
\[
  1-\E_{P_+}[a(Y,D,W)\mid W=w]\le\bar s_w .
\]
If \(p_+(w)=0\), feasibility requires \(\pi_-(w)=0\), which is ruled out by
Assumption~\ref{ass:cutoff-limits}; hence nonemptiness below implies \(p_+(w)>0\) for
all \(w\).
\end{assumption}

\begin{assumption}[Positive retained mass]\label{ass:positive-retained}
The feasible set \(\mathcal A(P,\bar\rho,\bar s)\) is nonempty, and every feasible
retention rule has \(M_a>0\).
\end{assumption}

\begin{assumption}[Positive nonmanipulator first stage]\label{ass:positive-first-stage}
There exists \(\kappa>0\) such that for every feasible
\(a\in\mathcal A(P,\bar\rho,\bar s)\),
\[
  \sum_w \pi_-(w)\{\E_{Q_a}[D\mid W=w]-\mu^-_D(w)\}\ge \kappa .
\]
This support condition makes the local Wald ratio well defined and rules out a weak or
zero first-stage denominator over the entire feasible set.
\end{assumption}

\begin{assumption}[Sharp RD specialization]\label{ass:sharp-rd-specialization}
For results that invoke the sharp RD face, \(D=Z\) almost surely in the left- and
right-cutoff limits, so treatment receipt is the threshold assignment indicator.
\end{assumption}

\begin{assumption}[Finite-support endpoint geometry]\label{ass:finite-support-geometry}
For results that invoke endpoint geometry, \(Y\) has finite support in each covariate cell
\(W=w\).  Since \(D\) and \(W\) are already finite, this makes the feasible retention
region a finite-dimensional polytope.  Endpoint claims below are made only for nonempty
compact feasible regions, feasible active bases, and denominator values bounded below by
Assumption~\ref{ass:positive-first-stage}.
\end{assumption}

\begin{assumption}[Exact-share one-cell face]\label{ass:exact-share-one-cell}
For results that invoke the one-cell exact-share face, \(K=1\), the removed share is fixed
at \(\tau\in[0,1)\), \(\tau\le\bar\rho\), the endpoint is evaluated on the restricted
equality-budget set \(\mathcal A^{=}_\tau(P,\bar s)\), and the cell cap is inactive or
satisfies \(\bar s_1\ge\tau\).
\end{assumption}

\begin{assumption}[Two-cell cap-separation design]\label{ass:cap-separation}
For results that invoke cap-envelope separation, \(K=2\), \(p_+(w)>0\) for both cells,
\(Y\) has finite support in each cell, and \(D=Z\).  Let
\[
  \ell_w=\frac{(1-\bar s_w)p_+(w)}{\pi_-(w)},
  \qquad
  u_w=\frac{p_+(w)}{\pi_-(w)},
  \qquad
  m^0=1-\bar\rho .
\]
The cap-forced minimum retained mass is
\[
  m^c=\max\left\{1-\bar\rho,\,
    \ell_1,\ell_2
  \right\},
\]
and it is feasible in the fixed-mass sense:
\[
  m^c\le \min\{1,u_1,u_2\}.
\]
There is a unique binding cell \(b\in\{1,2\}\) such that
\[
  \ell_b=m^c>\max\{m^0,\ell_{3-b}\}.
\]
Finally, the binding cell has a nondegenerate upper tail between the uncapped and capped
retained fractions:
\[
  \Gamma_b\!\left(\frac{m^c\pi_-(b)}{p_+(b)}\right)
  <
  \Gamma_b\!\left(\frac{m^0\pi_-(b)}{p_+(b)}\right).
\]
No strict inequality comparing \(U(m^c)\) with \(U^0(m^0)\) is assumed here; it is proved
from these primitive cap-feasibility and tail-shape conditions.
\end{assumption}

\section{Estimand-defining functional}
The bounding functional is
\[
  \theta_L(P;\bar\rho,\bar s)=B_L(P,\bar\rho,\bar s)
  =\inf_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a),
\]
\[
  \theta_U(P;\bar\rho,\bar s)=B_U(P,\bar\rho,\bar s)
  =\sup_{a\in\mathcal A(P,\bar\rho,\bar s)}\Theta(a).
\]
This is an observable functional of \(P=(P_-,P_+)\) and the sensitivity parameters because
\(\mathcal A(P,\bar\rho,\bar s)\) and \(\Theta(a)\) are defined only through integrals
under \(P_-\) and \(P_+\), the fixed bounds \((\bar\rho,\bar s)\), and the known outcome
support.

The intended result is sharp, not merely an outer bound.  The outer-bound statement is
\[
  \Theta_I(P,\bar\rho,\bar s)\subseteq
  [\theta_L(P;\bar\rho,\bar s),\theta_U(P;\bar\rho,\bar s)].
\]
Sharpness means that every value in the image
\(\{\Theta(a):a\in\mathcal A(P,\bar\rho,\bar s)\}\) is generated by some structural
completion satisfying the maintained restrictions, and the interval endpoints are the
tight lower and upper envelope of that image.  Because the feasible set is convex and the
positive first-stage assumption makes \(\Theta\) continuous, the image is an interval; in
finite-support cases the infimum and supremum are attained.

\section{Target causal estimand}
The causal target is the scalar nonmanipulator local Wald effect at the cutoff,
\[
  \theta =
  \frac{\sum_w \pi_-(w)\{\mu^Y_{+,0}(w)-\mu^Y_-(w)\}}
       {\sum_w \pi_-(w)\{\mu^D_{+,0}(w)-\mu^D_-(w)\}}.
\]
Here \(\mu^V_{+,0}(w)\) is the right-limit mean of \(V\in\{Y,D\}\) for the
nonmanipulating cutoff population in covariate cell \(w\), and
\(\mu^-_V(w)=\E_{P_-}[V\mid W=w]\) is observed on the left because upward manipulation
does not contaminate the left side.  The denominator is the local first stage for
nonmanipulators and is bounded below by Assumption~\ref{ass:positive-first-stage}.

The target is not defined to be the trimming functional.  Rather, the maintained
restrictions imply that the unobserved nonmanipulator right-limit law must equal \(Q_a\)
for some feasible \(a\), and therefore the target must equal \(\Theta(a)\) for that
completion.  Partial identification arises because \(P_+\) need not reveal which
right-side units are nonmanipulators.

\section{Main theorems}
\begin{theorem}[Sharp budgeted conditional trimming]\label{thm:sharp-budgeted-trimming}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage},
\[
  \Theta_I(P,\bar\rho,\bar s)
  =
  \{\Theta(a):a\in\mathcal A(P,\bar\rho,\bar s)\}.
\]
Consequently
\[
  \Theta_I(P,\bar\rho,\bar s)\subseteq
  [B_L(P,\bar\rho,\bar s),B_U(P,\bar\rho,\bar s)],
\]
and this interval is sharp: no uniformly smaller interval contains all values compatible
with the maintained restrictions.  Verdict on Conjecture~\ref{conj:sharp-budgeted-trim}:
confirmed.
\end{theorem}

This theorem is the sharpness backbone for the maintained model.  By itself it is a
contaminated-law representation: it converts structural completions into retention weights
and back again.  The novelty-bearing claim below is that the externally supplied cell caps
can remove the cell-cap-free worst fixed-share face, so the proposed feasible set is not
just a relabeling of the upper-envelope version of ordinary trimming.

\begin{proposition}[Finite-support endpoint geometry]\label{prop:endpoint-geometry}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage} and
\ref{ass:finite-support-geometry}, each upper or lower endpoint over a nonempty compact
finite-support feasible region is attained by an extreme point of a finite-dimensional
linear-fractional program.  At any feasible active basis whose denominator is bounded away
from zero, and at any endpoint value \(\lambda\), an optimizer can be chosen as a
threshold-retention rule: it retains all atoms with favorable affine score, drops all atoms
with unfavorable affine score, and may fractionally retain only atoms tied at the
threshold.  For the upper endpoint the relevant score has the form
\[
  y-\lambda d+\eta_w+\nu,
\]
with \(\eta_w\) absorbing the retained-\(W\) and cell-cap multipliers and \(\nu\)
absorbing the retained-mass/global-budget multiplier; the lower endpoint uses the
corresponding sign reversal.  On any region of \((\bar\rho,\bar s)\)-space where the
feasible active basis remains valid, no denominator approaches zero, and the same endpoint
basis is optimal, the endpoint is a rational function of
\((\bar\rho,\bar s)\), and kinks occur when the active basis changes.  Verdict on
Conjecture~\ref{conj:endpoint-geometry}: partial.  The score-threshold and local
piecewise-rational claims are confirmed; an unrestricted global piecewise-rational
statement needs the usual qualification by feasible active-set regions.
\end{proposition}

This proposition is useful for computation and diagnostics rather than for defining the
identified set.  It explains why endpoint software can search over finitely many active
sets in finite-support approximations and why reported sensitivity curves kink when a
cell cap replaces the global density envelope as the binding constraint.

\begin{proposition}[Zero-budget and exact-share faces]\label{prop:faces}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage}, if
\(\bar\rho=0\), \(\bar s_w=0\) for all \(w\), and \(P_+(W=w)=P_-(W=w)\) for all \(w\),
then \(\mathcal A(P,0,0)=\{a\equiv1\}\) and
\[
  \Theta_I(P,0,0)=
  \left\{
  \frac{\E_{P_+}[Y]-\E_{P_-}[Y]}{\E_{P_+}[D]-\E_{P_-}[D]}
  \right\}.
\]
If, in addition, Assumptions~\ref{ass:sharp-rd-specialization} and
\ref{ass:exact-share-one-cell} hold on an exact-share face
\(\mathcal A^{=}_\tau(P,\bar s)\), then the endpoint problem reduces to ordinary
Lee outcome-tail trimming of the right-side outcome distribution, with denominator equal
to one.
\end{proposition}

This proposition records the main sanity faces.  The first face is the Hahn--Todd--van der
Klaauw local Wald estimand; the second is the sharp-design exact-share trimming formula
that appears in Lee-style and manipulated-RD bounds.

\begin{theorem}[Primitive cap-envelope separation]\label{thm:cap-separation}
Under Assumptions~\ref{ass:cutoff-limits}--\ref{ass:positive-first-stage},
\ref{ass:sharp-rd-specialization}, and \ref{ass:cap-separation}, the capped upper endpoint
satisfies
\[
  B_U(P,\bar\rho,\bar s)=U(m^c)<U^0(m^0)=U^0_{\mathrm{env}}(\bar\rho).
\]
The strict inequality is locally stable under sufficiently small perturbations of the
finite-support atom probabilities and sensitivity parameters that preserve
\(m^c<\min\{1,u_1,u_2\}\), the positive first-stage condition, the unique binding cell,
and the strict upper-tail crossing in Assumption~\ref{ass:cap-separation}.  Moreover, the
assumption is nonempty: it contains the explicit witness
\[
  \pi_-(1)=\pi_-(2)=\frac12,\quad
  p_+(1)=\frac35,\quad p_+(2)=\frac25,\quad
  \bar\rho=\frac12,\quad
  \bar s_1=\frac5{12},\quad \bar s_2=\frac12,
\]
with \(Y=1\) on a right-side atom of mass \(3/10\) in cell \(1\), \(Y=0\) on a right-side
atom of mass \(3/10\) in cell \(1\), \(Y=0\) on all right-side mass in cell \(2\), and
left-side outcome mean zero in both cells.  For this witness,
\[
  m^0=\frac12,\qquad m^c=\frac7{10},\qquad
  U^0(m^0)=\frac12,\qquad U(m^c)=\frac37.
\]
Verdict on Conjecture~\ref{conj:cap-separation}: confirmed after replacing the circular
strict-gap assumption by primitive fixed-mass feasibility and upper-tail crossing
conditions.
\end{theorem}

The separation theorem identifies the role of covariate caps.  A binding cap can rule out
the uncapped worst-case retained mass, so the sharp upper endpoint is driven by the
smallest retained mass that both matches the left covariate law, respects the cap, and
does not require retaining more than all of any right-side cell.  Relative to the
cell-cap-free GRR-style envelope, the result proves a strict feasible-set deletion rather
than a different parametrization of the same share-optimization problem.

\section{Interpretation}
Theorem~\ref{thm:sharp-budgeted-trimming} says that all uncertainty about manipulation can
be represented as uncertainty about which portion of the observed right-limit law is
retained as the nonmanipulator law.  The left side is fixed by one-sided upward
manipulation, while the right side is partially latent.  The global envelope limits total
removed mass; the cell caps limit removal inside each covariate cell; the retained-\(W\)
equation forces the candidate nonmanipulator population to have the same covariate law as
the uncontaminated left side.

The bound collapses to point identification when no mass may be removed and the observed
right and left covariate laws already match.  In that case \(a\equiv1\), the retained law
is just \(P_+\), and the usual local Wald contrast is recovered.  In sharp RD, the
denominator is one, so the result becomes the ordinary right-minus-left jump in the outcome.

The bound widens toward the Manski contaminated-data face when the budgets allow nearly all
right-side mass to be reassigned as manipulation while still satisfying the first-stage
condition.  Then the retained right-side means can be pushed toward extreme feasible
outcome values, and the interval is driven mostly by bounded outcome support rather than
by density or covariate information.  The main tightening work is done jointly by
Assumptions~\ref{ass:global-envelope} and \ref{ass:cell-caps}; the former limits total
trimming, and the latter can prevent all trimming from being concentrated in the cell that
would make the Wald ratio most extreme.

Theorem~\ref{thm:cap-separation} gives the noncircular tightening mechanism.  The retained
mass \(m\) must be large enough to keep each cell's removed fraction below its cap, but it
also must be small enough that the retained-\(W\) equality does not require more than the
entire observed right-side cell mass.  In the two-cell witness, the global envelope alone
would allow \(m^0=1/2\), while the cap in cell \(1\) forces \(m^c=7/10\); crossing the
upper-tail atom in that cell lowers the attainable retained outcome mean.

Proposition~\ref{prop:endpoint-geometry} explains the computational shape of the bounds.
Endpoint rules sort atoms by a score that combines outcome desirability, treatment
first-stage leverage, cell scarcity, and global retained-mass scarcity.  This is why fuzzy
RD endpoints are not generally ordinary outcome-tail trims: retaining an atom changes both
the numerator and the denominator of the Wald ratio.

\section{Step-by-step proof}
\begin{lemma}[Mixture-retention equivalence]\label{lem:mixture-retention}
Under Assumptions~\ref{ass:one-sided}--\ref{ass:cell-caps}, a structural completion is
admissible if and only if its right-limit nonmanipulator law can be written as \(Q_a\) for
some \(a\in\mathcal A(P,\bar\rho,\bar s)\).
\end{lemma}

\begin{proof}
First take an admissible structural completion.  By one-sided manipulation,
\[
  P_+ = m Q_0 + (1-m)G
\]
for some retained nonmanipulator mass \(m\in(0,1]\), right-limit nonmanipulator law
\(Q_0\), and right-side manipulator law \(G\), with \(P_-=Q_-\) equal to the left-limit
nonmanipulator law.  The mixture identity implies \(mQ_0(B)\le P_+(B)\) for every
measurable set \(B\), so \(mQ_0\) is absolutely continuous with respect to \(P_+\).  Let
\[
  a=\frac{d(mQ_0)}{dP_+}.
\]
Then \(0\le a\le1\), \(M_a=\E_{P_+}[a]=m\), and \(Q_a=Q_0\).  The global envelope and
cell caps are exactly Assumptions~\ref{ass:global-envelope} and \ref{ass:cell-caps}, so
\(a\) satisfies the budget inequalities.  Conditional nonmanipulator continuity gives
\[
  Q_a(W=w)=Q_0(W=w)=P_-(W=w)=\pi_-(w),
\]
so \(a\in\mathcal A(P,\bar\rho,\bar s)\).

Conversely, take \(a\in\mathcal A(P,\bar\rho,\bar s)\) and write \(m=M_a\).  Define the
candidate nonmanipulator law \(Q_0=Q_a\).  If \(m<1\), define the manipulator law
\[
  G_a(B)=\frac{1}{1-m}\E_{P_+}[(1-a(Y,D,W))\one\{(Y,D,W)\in B\}],
\]
and if \(m=1\) choose any probability law \(G_a\), which receives zero mixture weight.
Then
\[
  P_+(B)=mQ_a(B)+(1-m)G_a(B)
\]
for all \(B\) by construction.  The inequalities in the definition of
\(\mathcal A(P,\bar\rho,\bar s)\) give the global and cellwise manipulation budgets, and
the equality \(Q_a(W)=\pi_-\) supplies the conditional continuity restriction at the level
needed for the local Wald numerator and denominator.  Thus \(a\) generates an admissible
structural completion.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:sharp-budgeted-trimming}]
Let \(\theta\in\Theta_I(P,\bar\rho,\bar s)\).  By definition of the identified set, there
is an admissible structural completion satisfying the maintained restrictions and producing
the target value \(\theta\).  Lemma~\ref{lem:mixture-retention} gives
\(a\in\mathcal A(P,\bar\rho,\bar s)\) such that the right-limit nonmanipulator law is
\(Q_a\).  By Assumption~\ref{ass:conditional-continuity},
\(\mu^V_{+,0}(w)=\E_{Q_a}[V\mid W=w]\) for \(V\in\{Y,D\}\).  Substituting these equalities
into the target definition gives
\[
  \theta
  =
  \frac{\sum_w \pi_-(w)\{\E_{Q_a}[Y\mid W=w]-\mu^-_Y(w)\}}
       {\sum_w \pi_-(w)\{\E_{Q_a}[D\mid W=w]-\mu^-_D(w)\}}
  =
  \Theta(a).
\]
The denominator is positive by Assumption~\ref{ass:positive-first-stage}.  Therefore
\[
  \Theta_I(P,\bar\rho,\bar s)\subseteq
  \{\Theta(a):a\in\mathcal A(P,\bar\rho,\bar s)\}.
\]

For the reverse inclusion, take \(a\in\mathcal A(P,\bar\rho,\bar s)\).  The converse part
of Lemma~\ref{lem:mixture-retention} constructs an admissible structural completion whose
right-limit nonmanipulator law is \(Q_a\).  Under Assumption~\ref{ass:conditional-continuity},
that completion has target value \(\Theta(a)\).  Hence
\[
  \{\Theta(a):a\in\mathcal A(P,\bar\rho,\bar s)\}
  \subseteq \Theta_I(P,\bar\rho,\bar s).
\]
The two inclusions prove equality.  Taking the infimum and supremum over the common set
gives the sharp interval.  Since every feasible retention rule is attainable by a
completion, lowering the upper endpoint or raising the lower endpoint would exclude an
admissible target value.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:endpoint-geometry}]
Under Assumption~\ref{ass:finite-support-geometry}, index each atom of
\((Y,D,W)\) under \(P_+\) by \(j\), with atom values \((y_j,d_j,w_j)\), probability
\(p_j\), and decision variable \(a_j\in[0,1]\).  The constraints defining
\(\mathcal A(P,\bar\rho,\bar s)\) are linear in \(a=(a_j)\): retained mass is
\(\sum_j p_ja_j\), the retained-\(W\) equations are
\(\sum_{j:w_j=w}p_ja_j=\pi_-(w)\sum_jp_ja_j\), and the cell caps are
\(\sum_{j:w_j=w}p_j(1-a_j)\le \bar s_w p_+(w)\).  The numerator and denominator of
\(\Theta(a)\) are affine in \(a\) after multiplying by \(M_a\):
\[
  N(a)=\E_{P_+}[aY]-M_a\E_{P_-}[Y],\qquad
  F(a)=\E_{P_+}[aD]-M_a\E_{P_-}[D].
\]
Assumption~\ref{ass:positive-first-stage} gives \(F(a)\ge \kappa M_a>0\) on the feasible
set, and the global budget gives \(M_a\ge1-\bar\rho>0\).  Therefore the denominator is
bounded away from zero on any feasible region covered by the statement.  With
\(0\le a_j\le1\) and closed linear constraints, maximizing \(\Theta(a)=N(a)/F(a)\) is a
linear-fractional program on a compact polytope whenever the feasible region is nonempty.

Fix a candidate endpoint value \(\lambda\).  The Dinkelbach or Charnes--Cooper
transformation says that the inequality \(\Theta(a)\le\lambda\) over the feasible set is
equivalent to
\[
  N(a)-\lambda F(a)\le0
\]
over the same set, because \(F(a)>0\).  The transformed objective is linear in \(a\).
The Lagrangian coefficient on an atom \((y_j,d_j,w_j)\), after collecting constants and
multipliers for retained mass, retained-\(W\), the global budget, and the cell caps, has
the form
\[
  y_j-\lambda d_j+\eta_{w_j}+\nu
\]
up to a positive atom-probability multiplier and sign conventions.  Linear programming
optimality therefore retains atoms with positive reduced cost, drops atoms with negative
reduced cost, and allows fractional retention only on zero-reduced-cost ties.  This proves
the threshold-retention claim.  For a fixed active basis, the basic variables are affine
functions of the right-hand sides \((1-\bar\rho,\bar s)\), so the ratio \(N(a)/F(a)\) is
rational in those parameters.  Basis changes are exactly the kink points described in the
statement.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:faces}]
If \(\bar\rho=0\), the global budget gives \(M_a=1\).  Since \(0\le a\le1\) and
\(\E_{P_+}[a]=1\), we have \(a=1\) \(P_+\)-almost surely.  The retained-\(W\) equation is
then \(P_+(W=w)=\pi_-(w)\), which holds by the proposition's premise.  Thus
\(\mathcal A(P,0,0)=\{1\}\).  Substituting \(a=1\) into \(\Theta(a)\) gives the displayed
local Wald contrast.  Under the sharp RD specialization, \(D=0\) on the left and \(D=1\)
on the right at the cutoff, so the denominator is one.

For the one-cell exact-share face, \(K=1\) makes the retained-\(W\) equation vacuous, and
Assumption~\ref{ass:exact-share-one-cell} fixes \(M_a=1-\tau\) with no active cell cap.
Under sharp RD, the denominator of \(\Theta(a)\) is one, so maximizing or minimizing
\(\Theta(a)\) is the same as maximizing or minimizing the retained right-side outcome
mean.  The standard Lee trimming argument applies: to maximize the retained mean, retain
the upper \(1-\tau\) fraction of the right-side outcome distribution, fractionally retaining
only at the cutoff quantile if needed; to minimize it, retain the lower \(1-\tau\) fraction.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:cap-separation}]
Under \(D=Z\), the first-stage denominator is one, so the upper endpoint at fixed retained
mass \(m\) is the largest retained right-side outcome mean minus the fixed left-side mean.
The retained-\(W\) equation requires cell \(w\) to contribute retained mass
\(m\pi_-(w)\), so the required retained fraction in that cell is
\[
  r_w(m)=\frac{m\pi_-(w)}{p_+(w)}.
\]
The constraint \(0\le a\le1\) requires
\[
  r_w(m)\le1,
  \qquad\text{or}\qquad
  m\le u_w=\frac{p_+(w)}{\pi_-(w)}.
\]
The cell cap \(\bar s_w\) is equivalent to
\[
  1-r_w(m)\le\bar s_w,
  \qquad\text{or}\qquad
  m\ge\ell_w=\frac{(1-\bar s_w)p_+(w)}{\pi_-(w)}.
\]
Combining these inequalities with the global budget \(m\ge m^0=1-\bar\rho\) shows that
the capped fixed-mass domain is
\[
  m\in
  \left[
    \max\{m^0,\ell_1,\ell_2\},
    \min\{1,u_1,u_2\}
  \right]
\]
whenever this interval is nonempty.  Assumption~\ref{ass:cap-separation} makes the lower
endpoint equal to \(m^c\), makes it feasible, and gives a unique binding cell \(b\) with
\(m^c=\ell_b>m^0\).  Thus the cap itself, together with retained-\(W\), forces
\(m^c>m^0\); this is not an assumed endpoint inequality.

For sharp RD with finite support, the fixed-mass upper endpoint in each cell is obtained
by retaining the largest outcomes in that cell.  Hence
\[
  U^0(m)
  =
  \sum_w \pi_-(w)\Gamma_w(r_w(m))-\E_{P_-}[Y].
\]
Each \(\Gamma_w\) is weakly decreasing in its retained fraction and \(r_w(m)\) is
increasing in \(m\).  Therefore \(U^0(m)\) is weakly decreasing in \(m\), so the
cell-cap-free upper envelope over the global budget is attained at \(m^0\):
\[
  U^0_{\mathrm{env}}(\bar\rho)=U^0(m^0).
\]
On the capped domain, the same monotonicity implies that the upper envelope is attained at
the smallest capped feasible mass \(m^c\).  At a fixed feasible mass the cell caps impose
only the already-satisfied total retained fraction constraints, so \(U(m^c)=U^0(m^c)\).
Thus
\[
  B_U(P,\bar\rho,\bar s)=U(m^c).
\]
The strict upper-tail crossing in Assumption~\ref{ass:cap-separation} gives
\[
  \Gamma_b(r_b(m^c))<\Gamma_b(r_b(m^0)).
\]
For the other cell \(w\ne b\), weak monotonicity gives
\(\Gamma_w(r_w(m^c))\le\Gamma_w(r_w(m^0))\).  Since \(\pi_-(b)>0\), summing across cells
therefore yields
\[
  U(m^c)=U^0(m^c)<U^0(m^0)=U^0_{\mathrm{env}}(\bar\rho),
\]
which proves the strict endpoint drop.

For the displayed witness, \(\ell_1=7/10\), \(\ell_2=2/5\),
\(u_1=6/5\), and \(u_2=4/5\).  Hence \(m^0=1/2\), \(m^c=7/10\), and \(m^c<\min\{1,u_1,u_2\}\).
The conditional high-outcome share in cell \(1\) is \(1/2\).  Thus
\[
  r_1(m^0)=\frac{5}{12}<\frac12<\frac{7}{12}=r_1(m^c),
\]
so \(\Gamma_1(r_1(m^0))=1\) and
\(\Gamma_1(r_1(m^c))=(1/2)/(7/12)=6/7\).  Cell \(2\) has only outcome zero, so
\(\Gamma_2(r)=0\) for all feasible \(r\).  With left-side mean zero,
\[
  U^0(m^0)=\frac12\cdot1+\frac12\cdot0=\frac12,\qquad
  U(m^c)=\frac12\cdot\frac67+\frac12\cdot0=\frac37.
\]
This verifies the nondegenerate strict gap in the witness.

The open-set claim follows because all inequalities defining the active configuration are
strict except the deliberately binding cell cap, the crossing
\(r_b(m^0)<\) upper-tail mass \(<r_b(m^c)\) is strict, and the finite-support endpoint
values are continuous rational functions of atom probabilities and budget parameters as
long as the same active basis and positive denominator persist.  Therefore a sufficiently
small perturbation preserving the listed primitive inequalities preserves the same
endpoint ordering.
\end{proof}

\section{Sanity checks}
\begin{enumerate}[leftmargin=*]
  \item \emph{Zero-width point-identification corner.}  If \(\bar\rho=0\),
  \(\bar s_w=0\) for every \(w\), and \(P_+(W)=P_-(W)\), Proposition~\ref{prop:faces}
  gives the usual local Wald estimand.  In sharp RD this is
  \(\E_{P_+}[Y]-\E_{P_-}[Y]\).

  \item \emph{One-cell exact-share Lee corner.}  If \(K=1\), \(D=Z\), and the removed
  share is fixed at \(\tau\le\bar\rho\) with an inactive cell cap, the endpoint problem is
  ordinary Lee trimming: the upper bound retains the upper \(1-\tau\) outcome tail and the
  lower bound retains the lower \(1-\tau\) outcome tail.  This is the sharp-design
  exact-share face of Gerard, Rokkanen, and Rothe \cite{GerardRokkanenRothe2020}.

  \item \emph{Vacuous contaminated-data corner.}  If \(\bar\rho\) and the cell caps allow
  arbitrarily small retained mass in every cell while preserving the positive first-stage
  condition, the right-side nonmanipulator means can approach their bounded-support
  extremes.  The interval then approaches the Horowitz--Manski contaminated-data bound
  induced by \(Y\in[\underline y,\overline y]\) and \(D\in\{0,1\}\).

  \item \emph{No ordinary outcome trimming in fuzzy RD.}  When \(D\) is not equal to \(Z\),
  the endpoint score contains both \(y\) and \(-\lambda d\).  Thus the optimal retained
  set is ordered by Wald-ratio leverage, not by the outcome alone.  This sanity check
  prevents importing the sharp-RD Lee-tail formula into the fuzzy design without the
  needed denominator argument.

  \item \emph{Cell-cap tightening.}  If \(p_+(w)\) is large relative to \(\pi_-(w)\), the
  retained-\(W\) equation requires removing a large share from cell \(w\) at small retained
  masses.  The cap \(\bar s_w\) imposes the lower bound
  \(m\ge (1-\bar s_w)p_+(w)/\pi_-(w)\), while the retention constraint \(a\le1\) imposes
  the upper bound \(m\le p_+(w)/\pi_-(w)\).  Thus a single cell can force a larger retained
  mass and narrow the interval only when the resulting \(m\) is still fixed-mass feasible.
\end{enumerate}

\section{Counterexample or minimality check}
The retained-\(W\) equation is not cosmetic.  Consider a sharp RD design with
\(\underline y=0\), \(\overline y=1\), \(K=2\), \(\pi_-(1)=\pi_-(2)=1/2\),
\(P_+(W=1)=P_+(W=2)=1/2\), and left-side outcome mean zero in both cells.  On the right,
let \(Y=1\) in cell \(1\) and \(Y=0\) in cell \(2\).  Let \(\bar\rho=1/2\) and take loose
cell caps.  If the retained-\(W\) equality is dropped, the upper endpoint can retain only
cell \(1\) with \(M_a=1/2\), giving right-side retained outcome mean \(1\).  With
\(Q_a(W)=\pi_-\), any retained law with \(M_a=1/2\) must retain mass \(1/4\) from each
cell, so the right-side retained outcome mean is \(1/2\).  Thus removing the covariate-law
restriction strictly enlarges the bound and breaks the intended nonmanipulator continuity
interpretation.

The positive first-stage condition is also minimal for a Wald target.  If a feasible
retention rule has
\[
  \sum_w \pi_-(w)\{\E_{Q_a}[D\mid W=w]-\mu^-_D(w)\}=0,
\]
then \(\Theta(a)\) is undefined; if denominators can approach zero while numerators remain
away from zero, the interval can become unbounded even though \(Y\) is bounded.  The
restriction is therefore a support condition, not a normalization.

The fixed-mass feasibility upper bound is also necessary.  If one kept only the lower
bound \(m\ge(1-\bar s_w)p_+(w)/\pi_-(w)\) and ignored
\(m\le p_+(w)/\pi_-(w)\), the retained-\(W\) equation could demand more retained mass from
a cell than the observed right-side law contains.  For example, if
\(\pi_-(1)=1/2\), \(p_+(1)=1/10\), and \(m=1/2\), then cell \(1\) would have to retain
mass \(1/4\) from only \(1/10\) observed mass, contradicting \(a\le1\).  This is why
Theorem~\ref{thm:cap-separation} conditions endpoint attainment and separation on
\(m^c\le\min\{1,u_1,u_2\}\), not just on the cap lower bounds.

\section{Formalization checklist}
\paragraph{Probability objects.}
\begin{itemize}[leftmargin=*]
  \item Observable laws: \(P_-\) and \(P_+\), probability measures on
  \([\underline y,\overline y]\times\{0,1\}\times\{1,\ldots,K\}\).
  Dependencies: cutoff-side weak limits.  Role: all functionals are computed from these
  two laws.
  \item Cell probabilities: \(\pi_-(w)=P_-(W=w)\), \(p_+(w)=P_+(W=w)\).
  Dependencies: finite \(W\), positive left cell support.  Role: retained-\(W\) matching
  and cell-cap feasibility.
  \item Left means: \(\mu^-_V(w)=\E_{P_-}[V\mid W=w]\) for \(V\in\{Y,D\}\).
  Dependencies: \(\pi_-(w)>0\), bounded \(Y\), binary \(D\).  Role: fixed left side of the
  local Wald target.
  \item Retention weight: measurable \(a(y,d,w)\in[0,1]\).  Dependencies: right-side
  support.  Role: Radon--Nikodym derivative of retained nonmanipulator mass with respect
  to \(P_+\).
  \item Retained mass and law: \(M_a=\E_{P_+}[a]\) and
  \(Q_a(B)=M_a^{-1}\E_{P_+}[a\one_B]\).  Dependencies: \(M_a>0\).  Role: candidate
  right-limit nonmanipulator distribution.
\end{itemize}

\paragraph{Assumptions as mathematical predicates.}
\begin{itemize}[leftmargin=*]
  \item Cutoff limits and bounded support: existence of \(P_-,P_+\), finite \(W\), bounded
  \(Y\), and \(\pi_-(w)>0\).
  \item One-sided mixture: existence of \(m,Q_0,G\) with \(P_+=mQ_0+(1-m)G\) and \(P_-\)
  equal to the left nonmanipulator law.
  \item Conditional continuity: \(Q_0(W=w)=\pi_-(w)\) and
  \(\mu^V_{+,0}(w)=\E_{Q_0}[V\mid W=w]\).
  \item Budget predicates: \(1-M_a\le\bar\rho\) and
  \(1-\E_{P_+}[a\mid W=w]\le\bar s_w\), together with \(a\le1\), which imposes
  fixed-mass upper feasibility \(m\pi_-(w)/p_+(w)\le1\).
  \item First-stage support: denominator of \(\Theta(a)\) bounded below by \(\kappa>0\)
  for all feasible \(a\).
\end{itemize}

\paragraph{Deterministic identities and lemmas.}
\begin{itemize}[leftmargin=*]
  \item Mixture-to-retention identity:
  if \(P_+=mQ_0+(1-m)G\), then \(a=d(mQ_0)/dP_+\) satisfies \(0\le a\le1\),
  \(M_a=m\), and \(Q_a=Q_0\).
  \item Retention-to-mixture identity:
  if \(0\le a\le1\) and \(M_a=m\), then
  \(P_+=mQ_a+(1-m)G_a\) with
  \(G_a(B)=(1-m)^{-1}\E_{P_+}[(1-a)\one_B]\) when \(m<1\).
  \item Wald simplification under retained-\(W\):
  \(\sum_w\pi_-(w)\E_{Q_a}[V\mid W=w]=\E_{Q_a}[V]=M_a^{-1}\E_{P_+}[aV]\).
  \item Fixed-mass cell-cap inequality:
  \(Q_a(W=w)=\pi_-(w)\) and \(M_a=m\) imply retained cell mass
  \(m\pi_-(w)\), so the retained fraction is
  \(r_w(m)=m\pi_-(w)/p_+(w)\).  Fixed-mass feasibility requires
  \(r_w(m)\le1\), equivalently \(m\le p_+(w)/\pi_-(w)\), and the cell cap is
  equivalent to \(r_w(m)\ge1-\bar s_w\), equivalently
  \(m\ge(1-\bar s_w)p_+(w)/\pi_-(w)\), when \(p_+(w)>0\).
  \item Upper-tail mean function:
  \(\Gamma_w(r)\) is the maximum retained conditional \(Y\)-mean in cell \(w\) after
  retaining fraction \(r\).  Dependencies: finite support and \(r\in(0,1]\).  Role:
  proves \(U^0(m)\) is weakly decreasing in \(m\) and proves strict cap-envelope
  separation when the binding cell crosses a positive-mass upper-tail threshold.
  \item Linear-fractional endpoint identity:
  for positive denominator \(F(a)\), \(\sup_a N(a)/F(a)\le\lambda\) if and only if
  \(\sup_a\{N(a)-\lambda F(a)\}\le0\).
  \item Finite-support extreme-point fact:
  a linear objective over a nonempty compact retention polytope has an optimizer at an
  extreme point, with at most tie atoms fractionally retained after reduced costs are
  ordered.  Piecewise-rational endpoint formulas require a feasible active basis and a
  first-stage denominator bounded away from zero on the active-basis region.
\end{itemize}

\section{Conclusion and references}
The sharpness theorem equates the identified set for the nonmanipulator RD local Wald
effect with the image of the budgeted conditional trimming program.  The novelty-bearing
theorem proves a stricter fact: external covariate-cell caps, combined with the
retained-\(W\) equality, can force a larger retained mass than the McCrary envelope alone
and strictly lower the upper endpoint on an open two-cell finite-support class.  The bound
becomes point-identifying at the no-manipulation face and approaches a Manski-style
contaminated-data bound when the budgets permit nearly arbitrary right-side removal.  In
fuzzy RD, endpoint rules sort by Wald-ratio score rather than by outcome tails alone, so
the ordinary Lee trimming formula is valid only on the sharp-RD exact-share face.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AraiHsuKitagawaMourifieWan2022}
Arai, Yoichi, Yu-Chin Hsu, Toru Kitagawa, Ismael Mourifie, and Yuanyuan Wan.
2022.
Testing identifying assumptions in fuzzy regression discontinuity designs.
\emph{Quantitative Economics} 13(1): 1--28.

\bibitem{CanayKamat2018}
Canay, Ivan A., and Vishal Kamat.
2018.
Approximate permutation tests and induced order statistics in the regression discontinuity design.
\emph{Review of Economic Studies} 85(3): 1577--1608.

\bibitem{CattaneoJanssonMa2020}
Cattaneo, Matias D., Michael Jansson, and Xinwei Ma.
2020.
Simple local polynomial density estimators.
\emph{Journal of the American Statistical Association} 115(531): 1449--1455.

\bibitem{GerardRokkanenRothe2020}
Gerard, Francois, Miikka Rokkanen, and Christoph Rothe.
2020.
Bounds on treatment effects in regression discontinuity designs with a manipulated running variable.
\emph{Quantitative Economics} 11(3): 839--870.

\bibitem{HahnToddVanDerKlaauw2001}
Hahn, Jinyong, Petra Todd, and Wilbert van der Klaauw.
2001.
Identification and estimation of treatment effects with a regression-discontinuity design.
\emph{Econometrica} 69(1): 201--209.

\bibitem{HorowitzManski1995}
Horowitz, Joel L., and Charles F. Manski.
1995.
Identification and robustness with contaminated and corrupted data.
\emph{Econometrica} 63(2): 281--302.

\bibitem{HsuShiuWan2024}
Hsu, Yu-Chin, Ji-Liang Shiu, and Yuanyuan Wan.
2024.
Testing identification conditions of LATE in fuzzy regression discontinuity designs.
\emph{Journal of Econometrics} 241(1): 105655.

\bibitem{ImbensLemieux2008}
Imbens, Guido W., and Thomas Lemieux.
2008.
Regression discontinuity designs: A guide to practice.
\emph{Journal of Econometrics} 142(2): 615--635.

\bibitem{Lee2008}
Lee, David S.
2008.
Randomized experiments from non-random selection in U.S. House elections.
\emph{Journal of Econometrics} 142(2): 675--697.

\bibitem{Lee2009}
Lee, David S.
2009.
Training, wages, and sample selection: Estimating sharp bounds on treatment effects.
\emph{Review of Economic Studies} 76(3): 1071--1102.

\bibitem{LeeLemieux2010}
Lee, David S., and Thomas Lemieux.
2010.
Regression discontinuity designs in economics.
\emph{Journal of Economic Literature} 48(2): 281--355.

\bibitem{McCrary2008}
McCrary, Justin.
2008.
Manipulation of the running variable in the regression discontinuity design: A density test.
\emph{Journal of Econometrics} 142(2): 698--714.

\bibitem{Semenova2025}
Semenova, Vira.
2025.
Generalized Lee bounds.
\emph{Journal of Econometrics} 251: 106055.
\end{thebibliography}

\end{document}
