% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=eid\_frontdoor\_multi\_mediator, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{eid\_frontdoor\_multi\_mediator} / \texttt{v1}%
  \\ \large\textit{Sharp finite bounds for a two-mediator natural direct effect with a shared proxy envelope}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
The locked parameters define a partial-identification problem, so the fixed
section heading ``Regression estimator'' below is interpreted as the
estimand-defining bounding functional rather than as a regression coefficient.
The observable functional is the projection of a finite linear polytope in the
unknown no-treatment mediator coupling \(q_0\) and the weighted response
coordinates \(v_{am}=\pi^0_m\E\{Y(a,m)\mid M(0)=m\}\).  The causal target is
the pure natural direct effect
\(\theta_{\mathrm{PNDE}}=\E\{Y(1,M_1(0),M_2(0))-Y(0,M_1(0),M_2(0))\}\).
The routine LP projection is stated only as an outer-bound proposition, with
global sharpness conditional on a separate finite-realization assumption.  The
main theorem is instead a realized one-parameter binary family: a shared proxy
face forces the sharp lower endpoint to occur at an interior mediator coupling,
and an explicit finite potential-outcome/proxy construction verifies
realization rather than assuming it.
\end{abstract}

\section{Introduction}
Natural direct effects ask how much the outcome would change under treatment
while holding the mediator process at its no-treatment counterfactual value.
With two binary mediators, the target depends on the joint law of
\((M_1(0),M_2(0))\), not merely on the two marginal mediator laws.  This is a
common empirical limitation: separate data systems or reports may identify
\(\Pr(M_j(a)=m)\) while leaving the within-unit mediator dependence only within
a reported band.

Negative-control proxies can add information about mediator--outcome
confounding, but the proxy restrictions need not separate across mediator
cells.  Classical mediation identification, proximal mediation identification,
and sharp finite-table bounds each explain part of the problem.  What is not
settled by those results is whether one may first bound the mediator copula,
then separately bound the proxy-confounding problem, and finally combine the
two sets coordinate by coordinate.

This note gives the finite polytope for the locked two-mediator PNDE problem
and proves that its linear projection is an outer identified interval.  That
LP bookkeeping is not presented as the novelty: global sharpness of an
arbitrary proxy-envelope summary remains conditional unless finite
realizability is separately verified.  The nonroutine contribution is a
one-parameter rational binary family for which realizability is constructed
directly.  In that family, shared proxy equations can make the optimizing
mediator coupling interior even though the dependence-band endpoints are
feasible, and a coordinatewise rectangular relaxation is strictly too wide.
The result is useful because it identifies the precise algebraic obstruction
to combining mediator-copula bounds and proxy-confounding bounds separately.

\section{Related work and positioning}
\cite{RobinsGreenland1992} and \cite{Pearl2001} introduced the direct and
indirect effect language that supplies the PNDE target used here.  \cite{ImaiKeeleYamamoto2010}
developed single-mediator identification and sensitivity analysis under
sequential ignorability, which is the baseline contrast for the present
mediator--outcome confounding problem.  \cite{TchetgenShpitser2012} gave
semiparametric theory for marginal natural effects once identification is
available, whereas this note studies the finite partial-identification step
before estimation.

\cite{VanderWeeleVansteelandt2014} and \cite{DanielDeStavolaCousensVansteelandt2015}
show why multiple mediators require joint mediator information rather than a
cell-by-cell single-mediator reduction.  \cite{VansteelandtDaniel2017}
introduced interventional effects for multiple mediators, a related strategy
that avoids some cross-world natural-effect requirements by changing the
target.  \cite{XiaChan2022} use copula-compatible nuisance modeling for
multiple natural mediation effects; here the copula coordinate is not modeled
pointwise but is part of a finite partial-identification problem.

\cite{DingVanderWeele2016} and \cite{MilesKankiMeloniTchetgen2017} are close
partial-identification references for mediation under missing or weakened
cross-world information.  \cite{DukesShpitserTchetgen2023} and
\cite{GhassamiYangShpitserTchetgen2025} give proximal mediation and hidden
mediator identification results under stronger bridge/completeness regimes.
\cite{GhassamiShpitserTchetgen2023} is the closest proxy-bound comparator:
it studies proxy-based partial identification without completeness, but not
the geometry created by an unobserved two-mediator coupling.  \cite{Manski1990}
and \cite{BalkePearl1997} supply the finite worst-case and latent-table
perspective behind the outer LP proposition; that proposition is standard
finite partial-identification machinery.  \cite{GabrielSachsSjolander2023}
derive sharp nonparametric bounds for decomposition effects with two binary
mediators; the present theorem differs by leaving the joint no-treatment
mediator law partly unidentified, adding shared negative-control
bridge-envelope equations, and constructing a finite realized family in which
the shared face changes the optimum.

Within the repository documentation, the closest ingredients are the exact
front-door identification catalogue, the proxy partial-identification
catalogue, and the finite latent-table bounds catalogue.  Those artifacts are
relevant as substrate examples, but none states a multi-mediator PNDE
non-rectangularity result with an explicit finite realization of the
proxy-envelope summaries.  This note therefore positions the theorem as a
partial-identification result, despite the \texttt{eid} prefix in the qid, and
does not claim a general new sharp-bounds theorem for all proxy systems.

\section{Formal setup}
Let \(A\in\{0,1\}\) be treatment, \(M=(M_1,M_2)\in\{0,1\}^2\) the two
mediators, \(Y\in[0,1]\) the outcome, and \(W,Z\) negative-control proxies
whose observed implications are summarized by linear bridge-envelope
constraints.  Potential mediators are denoted by \(M_j(a)\), and
potential outcomes by \(Y(a,m)\) for \(a\in\{0,1\}\) and
\(m=(m_1,m_2)\in\mathcal M=\{0,1\}^2\).  All expectations are finite because
the state spaces are finite and \(Y\) is bounded.

The observable distribution \(P_{\mathrm{obs}}\) contains the treatment law,
the observed outcome/proxy law, the mediator marginals
\[
  p_{ja}(m)=\Pr(M_j=m\mid A=a),\qquad j\in\{1,2\},\ a,m\in\{0,1\},
\]
and a reported dependence band
\(\mathcal Q_a=[\underline q_a,\overline q_a]\) for
\(q_a=\Pr(M_1(a)=1,M_2(a)=1)\).  The PNDE depends only on
\(\mathcal Q_0\), but \(\mathcal Q_1\) remains part of the locked observable
record.  Write
\[
  p_1=p_{10}(1),\qquad p_2=p_{20}(1).
\]
For any \(q\in\mathcal Q_0\), the no-treatment mediator law induced by the
observed marginals and \(q\) is
\[
  \pi_{11}(q)=q,\qquad
  \pi_{10}(q)=p_1-q,\qquad
  \pi_{01}(q)=p_2-q,\qquad
  \pi_{00}(q)=1-p_1-p_2+q.
\]
The boundary convention is that a cell with \(\pi_m(q)=0\) contributes zero
to every weighted mean.  Conditional response means \(r_{am}\) on such null
cells may be chosen arbitrarily in \([0,1]\); all identified-set and LP
statements use the weighted coordinates
\[
  v_{am}=\pi_m(q)\,r_{am},\qquad
  r_{am}=\E\{Y(a,m)\mid M(0)=m\}
\]
only through \(v_{am}\).

For each treatment arm \(a\), the proxy-envelope summary consists of an
observable matrix \(G_a(P_{\mathrm{obs}})\), an observable vector
\(b_a(P_{\mathrm{obs}})\), and observable cell envelopes
\(\ell_{am}(P_{\mathrm{obs}}),u_{am}(P_{\mathrm{obs}})\) with
\(0\le \ell_{am}\le u_{am}\le1\).  The finite feasible polytope is
\[
\begin{aligned}
  \mathcal P(P_{\mathrm{obs}})
  =\{&(q,\pi,v_0,v_1):
      q\in\mathcal Q_0,\ 
      \pi=\pi(q),\\
    & G_a v_a=b_a\ \text{for }a=0,1,\quad
      \ell_{am}\pi_m\le v_{am}\le u_{am}\pi_m
      \ \text{for all }a,m\}.
\end{aligned}
\]
If this set is empty, the maintained restrictions reject
\(P_{\mathrm{obs}}\); all bounds below are stated for the nonempty case.  The
identified set \(\Theta_I(P_{\mathrm{obs}})\) is the set of all values of the
PNDE over finite potential-outcome laws that match \(P_{\mathrm{obs}}\) and
satisfy the maintained restrictions.

\paragraph{Locked parameters.}
\begin{quote}
\textbf{Partial identification tuple.}
\texttt{qid = eid\_frontdoor\_multi\_mediator};
\texttt{specialization = v1};
observable distribution \(P_{\mathrm{obs}}\) consists of the treatment law
\(\Pr(A=a)\), the outcome/proxy law \(\Pr(A,Y,W,Z)\), the two marginal
mediator laws \(p_{ja}(m)=\Pr(M_j=m\mid A=a)\) for \(j=1,2\) and
\(a\in\{0,1\}\), and a reported dependence band
\(\mathcal Q_a=[\underline q_a,\overline q_a]\) for
\(q_a=\Pr(M_1(a)=1,M_2(a)=1)\);
the parameter \(\theta\) is the pure natural direct effect
\[
  \theta_{\mathrm{PNDE}}
  = \E\{Y(1,M_1(0),M_2(0))-Y(0,M_1(0),M_2(0))\};
\]
identifying restrictions are finite binary treatment and mediators, bounded
outcome \(Y\in[0,1]\), randomized treatment with consistency, marginal
mediator consistency, the dependence-band restriction \(q_a\in\mathcal Q_a\),
and negative-control proxy restrictions summarized by the shared linear
bridge-envelope system in Assumption~\ref{ass:proxy-envelope};
the bounding functional is the projection of the finite mediator--response
polytope
\[
  B(P_{\mathrm{obs}})
  = \{\sum_m(v_{1m}-v_{0m}) :
       (q_0,\pi^0,v_0,v_1)\in\mathcal P(P_{\mathrm{obs}})\},
\]
where \(\pi^0\) is the no-treatment joint mediator law induced by
\((p_{10},p_{20},q_0)\), and \(v_{am}=\pi^0_m\E\{Y(a,m)\mid M(0)=m\}\).
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite bounded mediation system]\label{ass:finite-bounded}
\(A,M_1,M_2\) are binary, \(Y\in[0,1]\), and the mediator index set is
\(\mathcal M=\{0,1\}^2\).  All sums over mediator cells are finite sums over
\(\mathcal M\).
\end{assumption}

\begin{assumption}[Randomization and consistency]\label{ass:randomization-consistency}
Treatment is randomized relative to the mediator and outcome potential
outcomes, and the treatment law has support \(\Pr(A=a)>0\) for
\(a\in\{0,1\}\).  Observed variables equal their corresponding potential
variables on the factual history: \(M_j=M_j(A)\) and \(Y=Y(A,M_1,M_2)\).
\end{assumption}

\begin{assumption}[Marginal mediator observation]\label{ass:marginal-mediators}
The observable law identifies the mediator marginals
\(p_{ja}(m)=\Pr(M_j(a)=m)\) for \(j\in\{1,2\}\), \(a\in\{0,1\}\), and
\(m\in\{0,1\}\).  It does not identify the joint no-treatment mediator law
\(\pi^0\) beyond the dependence band for \(q_0\).
\end{assumption}

\begin{assumption}[Dependence-band feasibility]\label{ass:dependence-band}
\(\mathcal Q_0=[\underline q_0,\overline q_0]\) is a nonempty subinterval of
the Frechet interval
\[
  \max\{0,p_1+p_2-1\}\le q_0\le \min\{p_1,p_2\}.
\]
For every \(q_0\in\mathcal Q_0\), the vector \(\pi(q_0)\) defined in the
Formal setup is nonnegative and sums to one.
\end{assumption}

\begin{assumption}[Shared proxy bridge-envelope system]\label{ass:proxy-envelope}
For each treatment arm \(a\), the negative-control proxies \(W,Z\) imply the
observable linear restrictions \(G_a v_a=b_a\) and cell envelopes
\[
  \ell_{am}\pi_m(q_0)\le v_{am}\le u_{am}\pi_m(q_0),
  \qquad 0\le \ell_{am}\le u_{am}\le1 .
\]
The same vector \(v_a\) must satisfy all rows of \(G_a v_a=b_a\), so the proxy
information is shared across mediator cells rather than imposed as four
independent cellwise sensitivity intervals.
\end{assumption}

\begin{assumption}[Optional canonical finite sharpness]\label{ass:canonical-sharpness}
Every finite array \((q_0,\pi^0,v_0,v_1)\in\mathcal P(P_{\mathrm{obs}})\)
can be realized by a finite potential-outcome/proxy-summary model with the
same observable \(P_{\mathrm{obs}}\), mediator marginals, dependence band, and
proxy-envelope summaries.  This is not derived from Assumptions
\ref{ass:finite-bounded}--\ref{ass:proxy-envelope}; it is an optional
realizability condition used only when converting a generic LP envelope into a
generic sharp identified set.  The realized family in
Theorem~\ref{thm:interior-witness} verifies the corresponding finite
realization directly, so its sharpness claim does not rest on this assumption
as an unexplained axiom.
\end{assumption}

\begin{assumption}[No mediator interaction]\label{ass:no-interaction}
For each treatment arm \(a\), the response table can be written
\[
  r_{am}=\alpha_a+\beta_{a1}m_1+\beta_{a2}m_2
\]
for coefficients compatible with \(0\le r_{am}\le1\) and with the proxy
bridge-envelope system.  Equivalently,
\(v_{am}=\pi_m(q_0)(\alpha_a+\beta_{a1}m_1+\beta_{a2}m_2)\).
\end{assumption}

\section{Regression estimator}
There is no regression estimator in the locked partial-identification tuple.
The estimand-defining functional is the LP projection
\[
  B_{\mathrm{LP}}(P_{\mathrm{obs}})
  =
  \left\{\sum_{m\in\mathcal M}(v_{1m}-v_{0m}):
     (q_0,\pi^0,v_0,v_1)\in\mathcal P(P_{\mathrm{obs}})
  \right\}.
\]
When \(\mathcal P(P_{\mathrm{obs}})\neq\emptyset\), define the lower and upper
LP endpoints by
\[
  \theta_L(P_{\mathrm{obs}})
   =\min_{\mathcal P(P_{\mathrm{obs}})}
      \sum_{m\in\mathcal M}(v_{1m}-v_{0m}),\qquad
  \theta_U(P_{\mathrm{obs}})
   =\max_{\mathcal P(P_{\mathrm{obs}})}
      \sum_{m\in\mathcal M}(v_{1m}-v_{0m}).
\]
The outer-bound statement is
\(\Theta_I(P_{\mathrm{obs}})\subseteq
[\theta_L(P_{\mathrm{obs}}),\theta_U(P_{\mathrm{obs}})]\).  The bound is
sharp only after adding Assumption~\ref{ass:canonical-sharpness}; without that
assumption the LP is an envelope implied by the recorded summaries, not a
claim that every feasible point is generated by a full causal model.

For comparison with the Stage -1 conjecture, define the fixed-coupling response
set, for positive mediator cells, by
\[
  R_a(q)=
  \{r_a\in[0,1]^4:
      G_a(\pi(q)\odot r_a)=b_a,\ 
      \ell_{am}\le r_{am}\le u_{am}\text{ for all }m\},
\]
with null cells handled by the zero-weight convention of the Formal setup.
The coordinatewise rectangular relaxation first forms
\[
  [\underline r^{\mathrm{sep}}_{am},\overline r^{\mathrm{sep}}_{am}]
  =
  \operatorname{conv}\left(
    \bigcup_{q\in\mathcal Q_0}
      \{r_{am}:r_a\in R_a(q)\}
  \right),
\]
and then allows those four coordinates to vary independently across cells:
\[
  B_{\mathrm{sep}}(P_{\mathrm{obs}})
  =
  \left\{
  \sum_{m\in\mathcal M}\pi_m(q)(r_{1m}-r_{0m}):
  q\in\mathcal Q_0,\ 
  r_{am}\in
  [\underline r^{\mathrm{sep}}_{am},\overline r^{\mathrm{sep}}_{am}]
  \right\}.
\]
This relaxation is always at least as permissive as the joint LP projection
when the fixed-\(q\) sets are nonempty, but it need not be sharp.

\section{Target causal estimand}
The causal target is the pure natural direct effect
\[
  \theta_{\mathrm{PNDE}}
  =
  \E\{Y(1,M_1(0),M_2(0))-Y(0,M_1(0),M_2(0))\}.
\]
This target is a property of the joint counterfactual distribution of
\((Y(1,m),Y(0,m),M(0))\).  It is not defined to be an LP endpoint or an
observable functional.  By the law of total expectation over \(M(0)\),
whenever the relevant conditional means exist,
\[
\begin{aligned}
  \theta_{\mathrm{PNDE}}
  &=
  \sum_{m\in\mathcal M}
    \Pr(M(0)=m)
      \left[
        \E\{Y(1,m)\mid M(0)=m\}
        -\E\{Y(0,m)\mid M(0)=m\}
      \right]\\
  &=
  \sum_{m\in\mathcal M}(v_{1m}-v_{0m}).
\end{aligned}
\]
The proof below shows that the LP endpoints bound the possible values of this
causal target.  Sharpness is asserted only in settings where finite
realization is either assumed explicitly or constructed directly.

\section{Main theorems}
\begin{proposition}[Finite LP envelope; conditional sharpness]\label{prop:lp-envelope}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:proxy-envelope}, for every
nonempty \(\mathcal P(P_{\mathrm{obs}})\),
\[
  \Theta_I(P_{\mathrm{obs}})
  \subseteq
  [\theta_L(P_{\mathrm{obs}}),\theta_U(P_{\mathrm{obs}})].
\]
If Assumption~\ref{ass:canonical-sharpness} also holds, then the containment is
equality and the interval is the sharp identified set for
\(\theta_{\mathrm{PNDE}}\).
\end{proposition}

The proposition is the bookkeeping formula for the locked target.  It is close
in spirit to Manski worst-case bounds and Balke--Pearl finite latent-table
bounds.  Its sharpness clause is deliberately conditional; it should not be
read as proving canonical finite realization from proxy or causal primitives.

\begin{theorem}[Realized shared-face non-rectangularity family; Conjecture 1 confirmed]\label{thm:interior-witness}
Fix any rational \(\lambda\in(0,1/7]\).  There is a rational binary instance
with \(p_{10}(1)=p_{20}(1)=3/5\) and
\(\mathcal Q_0=[1/4,11/20]\) such that both dependence-band endpoints are
feasible, every feasible point of the displayed proxy-envelope polytope has a
finite potential-outcome/proxy-summary realization with the same observable
record, and the sharp lower PNDE endpoint is attained only at the interior
coupling \(q_0^\star=2/5\).  In this family,
\[
  \theta_L(P_{\mathrm{obs}})=\frac{3\lambda}{5},\qquad
  \theta_U(P_{\mathrm{obs}})=\frac35,
\]
whereas the coordinatewise rectangular relaxation contains the lower value
\[
  \frac{9\lambda}{20}<\frac{3\lambda}{5}.
\]
Thus the Stage -1 coupling--proxy incompatibility conjecture is confirmed in
a realized finite class, not merely in a formal LP with sharpness assumed by
Assumption~\ref{ass:canonical-sharpness}.
\end{theorem}

This theorem is the non-rectangularity contribution.  It shows that the proxy
and mediator-dependence restrictions cannot in general be combined by first
taking coordinatewise proxy response ranges and then optimizing over the
mediator copula.  Unlike a single numerical counterexample, the parameter
\(\lambda\) gives a family of binary shared-face systems and the proof
constructs the finite causal/proxy realizations that make the endpoint sharp.

\begin{proposition}[No-interaction marginal reduction]\label{prop:additive-reduction}
Under Assumptions~\ref{ass:finite-bounded}--\ref{ass:dependence-band} and
Assumption~\ref{ass:no-interaction}, the PNDE value associated with fixed
additive coefficients is independent of \(q_0\):
\[
  \theta_{\mathrm{PNDE}}
  =
  (\alpha_1-\alpha_0)
  +(\beta_{11}-\beta_{01})p_{10}(1)
  +(\beta_{12}-\beta_{02})p_{20}(1).
\]
\end{proposition}

This proposition is a sanity-corner result rather than the flagship theorem.
It isolates the source of the interior-coupling phenomenon: the unknown
mediator copula matters for the PNDE only through mediator interaction or
through proxy restrictions that force non-additive shared response geometry.

\section{Interpretation}
The LP envelope says that the estimand-defining object is a joint feasibility
problem.  The analyst must choose one mediator coupling \(q_0\), the induced
four mediator weights \(\pi(q_0)\), and response vectors \(v_0,v_1\) that
satisfy the same proxy equations.  The bound is clean and sharp when the
finite sharpness assumption is credible: every feasible weighted table can be
implemented by a causal model matching the recorded summaries.  Without that
assumption, the interval remains an outer bound but not a sharp identified
set.

The shared-face theorem explains what goes wrong with rectangularization.
Each cellwise response value may be attainable for some mediator coupling, yet
the same coupling need not attain all the desired cellwise values
simultaneously.  In the realized family, the shared proxy equations paste
three weighted arm-one response coordinates together.  The lower endpoint is
obtained by minimizing the largest of the three relevant mediator masses,
which occurs at the interior coupling \(q_0=2/5\), not at either endpoint of
the dependence band.  The finite construction keeps the observed outcome and
proxy law fixed across feasible points by putting the factual treated mediator
state on the fourth cell and using only cross-mediator arm-one responses for
the varying PNDE component.

The only treatment positivity required for the target interpretation is the
randomized treatment support needed to learn the recorded mediator marginals
and proxy summaries from the observed arms.  Mediator-cell positivity is not a
global assumption: null cells have zero weighted contribution.  However, the
response-ratio notation \(r_{am}=v_{am}/\pi_m\) should be used only on positive
cells, and the explicit witness keeps all four mediator cells positive over
its reported band.  Misspecifying the proxy equations, replacing the joint LP
by independent cellwise ranges, or treating an outer bound as sharp without
Assumption~\ref{ass:canonical-sharpness} breaks the conclusion.

\section{Step-by-step proof}
\begin{lemma}[Weighted PNDE identity]\label{lem:weighted-pnde}
Under Assumptions~\ref{ass:finite-bounded} and
\ref{ass:randomization-consistency}, any admissible model with
\(\pi_m=\Pr(M(0)=m)\) and
\(v_{am}=\pi_m\E\{Y(a,m)\mid M(0)=m\}\) satisfies
\[
  \theta_{\mathrm{PNDE}}=\sum_{m\in\mathcal M}(v_{1m}-v_{0m}).
\]
\end{lemma}

\begin{proof}
Because \(M(0)\) has the finite support \(\mathcal M\),
the law of total expectation gives
\[
  \E\{Y(a,M(0))\}
  =
  \sum_{m\in\mathcal M}
    \Pr(M(0)=m)\E\{Y(a,m)\mid M(0)=m\}.
\]
Subtracting the expression with \(a=0\) from the expression with \(a=1\)
gives the claimed identity.  Boundedness of \(Y\) in
Assumption~\ref{ass:finite-bounded} ensures all conditional expectations lie
in \([0,1]\), and the zero-cell convention makes the weighted terms well
defined when \(\pi_m=0\).
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:lp-envelope}]
Take any finite potential-outcome model counted by
\(\Theta_I(P_{\mathrm{obs}})\).  By Assumption~\ref{ass:marginal-mediators},
its no-treatment mediator marginals equal \(p_1\) and \(p_2\).  By
Assumption~\ref{ass:dependence-band}, its joint mass
\(q_0=\Pr(M_1(0)=1,M_2(0)=1)\) lies in \(\mathcal Q_0\), so the four cell
masses equal \(\pi(q_0)\) by the algebra of a binary \(2\times2\) table:
\[
  \pi_{11}=q_0,\quad
  \pi_{10}=p_1-q_0,\quad
  \pi_{01}=p_2-q_0,\quad
  \pi_{00}=1-p_1-p_2+q_0.
\]
By Assumption~\ref{ass:proxy-envelope}, the weighted response vectors
\(v_a\) satisfy \(G_a v_a=b_a\) and
\(\ell_{am}\pi_m\le v_{am}\le u_{am}\pi_m\).  Therefore
\((q_0,\pi,v_0,v_1)\in\mathcal P(P_{\mathrm{obs}})\).
Lemma~\ref{lem:weighted-pnde} then yields
\[
  \theta_{\mathrm{PNDE}}
  =\sum_m(v_{1m}-v_{0m})
  \in
  [\theta_L(P_{\mathrm{obs}}),\theta_U(P_{\mathrm{obs}})].
\]
Since the model was arbitrary, this proves the outer containment.

Now add Assumption~\ref{ass:canonical-sharpness}.  Every point of
\(\mathcal P(P_{\mathrm{obs}})\) is realized by some finite causal model
matching the observable summaries, and Lemma~\ref{lem:weighted-pnde} maps that
point to the linear value \(\sum_m(v_{1m}-v_{0m})\).  The polytope is convex
and compact, and the linear image of a convex compact set in \(\R\) is the
closed interval between its minimum and maximum.  Hence every value in
\([\theta_L,\theta_U]\) is attainable and the LP interval is sharp.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:interior-witness}]
Order mediator cells as \(00,10,01,11\), and write
\(S=\{00,10,01\}\).  Fix a rational \(\lambda\in(0,1/7]\).  Let
\[
  p_1=p_2=\frac35,\qquad
  \mathcal Q_0=\left[\frac14,\frac{11}{20}\right].
\]
This band is contained in the Frechet interval
\([1/5,3/5]\), so Assumption~\ref{ass:dependence-band} holds.  The induced
cell masses are
\[
  \pi_{00}(q)=q-\frac15,\quad
  \pi_{10}(q)=\frac35-q,\quad
  \pi_{01}(q)=\frac35-q,\quad
  \pi_{11}(q)=q,
\]
which are strictly positive for all \(q\in[1/4,11/20]\).

Define the arm-zero envelope by \(\ell_{0m}=u_{0m}=0\) for all \(m\); hence
\(v_{0m}=0\).  For arm one, set
\[
  \ell_{1m}=\lambda,\quad u_{1m}=1\quad(m\in S),
  \qquad
  \ell_{1,11}=u_{1,11}=0.
\]
Let the shared arm-one proxy equations be
\[
  v_{1,00}-v_{1,10}=0,\qquad
  v_{1,00}-v_{1,01}=0,
\]
and take \(b_1=0\).  No arm-zero equation is needed beyond the zero envelope.
These are rational linear restrictions of the form allowed by
Assumption~\ref{ass:proxy-envelope}.

The two shared equations imply
\[
  v_{1,00}=v_{1,10}=v_{1,01}=t
\]
for some \(t\ge0\).  The box constraints are exactly
\[
  \lambda\left(q-\frac15\right)\le t\le q-\frac15,\qquad
  \lambda\left(\frac35-q\right)\le t\le \frac35-q,
\]
with the second inequality applying to both \(10\) and \(01\).  Thus, for
fixed \(q\),
\[
  \lambda M(q)\le t\le m(q),
  \qquad
  M(q)=\max\left\{q-\frac15,\frac35-q\right\},
  \quad
  m(q)=\min\left\{q-\frac15,\frac35-q\right\}.
\]
The ratio \(m(q)/M(q)\) is minimized at the two band endpoints and equals
\((1/20)/(7/20)=1/7\).  Since \(\lambda\le1/7\), this interval for \(t\) is
nonempty for every \(q\in\mathcal Q_0\), including both endpoints.

The PNDE linear functional is
\[
  \sum_m(v_{1m}-v_{0m})=3t.
\]
For fixed \(q\), the smallest value is therefore \(3\lambda M(q)\).  The two
arguments of \(M(q)\) are respectively increasing and decreasing affine
functions of \(q\), and they are equal only at \(q^\star=2/5\).  Hence
\[
  M(q)\ge M(2/5)=\frac15,
\]
with equality only at \(q=2/5\).  Consequently
\[
  \theta_L(P_{\mathrm{obs}})=3\lambda\cdot\frac15=\frac{3\lambda}{5},
\]
and the lower endpoint is attained only at the interior coupling
\(q^\star=2/5\).  The upper endpoint is obtained by maximizing
\(3m(q)\), and \(m(q)\) is uniquely maximized at the same interior coupling,
where \(m(2/5)=1/5\).  Thus
\[
  \theta_U(P_{\mathrm{obs}})=\frac35.
\]

We now construct the promised finite realization.  Fix any feasible
\((q,t)\).  Let \(A\) be Bernoulli with probabilities in \((0,1)\),
independent of all potential variables.  Let \(M(0)\) have law \(\pi(q)\), and
let \(M(1)=(1,1)\) almost surely; the treatment-one mediator marginals are
therefore \(p_{11}(1)=p_{21}(1)=1\), and take the reported band
\(\mathcal Q_1=\{1\}\).  Set \(Y(0,m)=0\) for all \(m\) and
set \(Y(1,11)=0\).  Conditional on \(M(0)=s\in S\), set
\[
  \Pr\{Y(1,s)=1\mid M(0)=s\}=\frac{t}{\pi_s(q)},
\]
and set the remaining cross-cell potential outcomes arbitrarily in
\(\{0,1\}\), for instance equal to zero.  The feasibility inequalities above
ensure \(0\le t/\pi_s(q)\le1\).  Then
\[
  \pi_s(q)\E\{Y(1,s)\mid M(0)=s\}=t,\quad s\in S,
  \qquad
  \pi_{11}(q)\E\{Y(1,11)\mid M(0)=11\}=0,
\]
and \(v_{0m}=0\) for all \(m\).  By consistency, if \(A=0\) the observed
outcome is \(Y(0,M(0))=0\), and if \(A=1\) the factual mediator is \(11\) and
the observed outcome is \(Y(1,11)=0\).  Thus the observable
\(\Pr(A,Y,W,Z)\) can be held fixed across all feasible \((q,t)\): take finite
proxies \(W,Z\) with a fixed distribution and let their reported
negative-control calibration summary be the rational system
\((G_a,b_a,\ell_{am},u_{am})\) displayed above.  The locked abstraction uses
this bridge-envelope summary, not a completeness theorem, as the proxy
restriction.  The displayed weighted table satisfies the summary exactly, so
every feasible point of this polytope is realized by a finite
potential-outcome/proxy-summary model with the same observable outcome/proxy
law, mediator marginals, dependence bands, and proxy-envelope summaries.  This
verifies the finite sharpness needed for this family directly.

It remains to compare the rectangular relaxation.  At \(q^\star=2/5\), the
three cells in \(S\) all have mass \(1/5\), and choosing
\(t=\lambda/5\) gives \(r_{1s}=\lambda\) for \(s\in S\).  More specifically,
the cell \(00\) has separated lower response value \(\lambda\) at the upper
band endpoint \(q=11/20\), while cells \(10\) and \(01\) have separated lower
response value \(\lambda\) at the lower band endpoint \(q=1/4\).  The
rectangular relaxation may combine these three coordinatewise lower responses
at \(q=11/20\), giving
\[
  \lambda\{\pi_{00}(11/20)+\pi_{10}(11/20)+\pi_{01}(11/20)\}
  =
  \lambda\left(\frac7{20}+\frac1{20}+\frac1{20}\right)
  =
  \frac{9\lambda}{20}.
\]
Since \(9\lambda/20<3\lambda/5\), the rectangular lower endpoint is strictly
below the realized sharp lower endpoint.  This confirms the conjectured
coupling--proxy incompatibility.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:additive-reduction}]
Let
\[
  \Delta\alpha=\alpha_1-\alpha_0,\quad
  \Delta\beta_1=\beta_{11}-\beta_{01},\quad
  \Delta\beta_2=\beta_{12}-\beta_{02}.
\]
Under Assumption~\ref{ass:no-interaction},
\[
  r_{1m}-r_{0m}
  =
  \Delta\alpha+\Delta\beta_1 m_1+\Delta\beta_2 m_2.
\]
Substituting this into the weighted PNDE identity gives
\[
\begin{aligned}
  \theta_{\mathrm{PNDE}}
  &=
  \sum_m\pi_m(q_0)
    \{\Delta\alpha+\Delta\beta_1 m_1+\Delta\beta_2 m_2\}\\
  &=
  \Delta\alpha\sum_m\pi_m(q_0)
  +\Delta\beta_1\sum_m m_1\pi_m(q_0)
  +\Delta\beta_2\sum_m m_2\pi_m(q_0).
\end{aligned}
\]
The first sum is \(1\), the second is \(p_{10}(1)\), and the third is
\(p_{20}(1)\) by the mediator marginal definitions.  The claimed formula
follows, and no term involving \(q_0\) remains.
\end{proof}

\section{Sanity checks}
\begin{enumerate}[leftmargin=*]
\item \textbf{No proxy information.}  If the proxy-envelope system is replaced
by the trivial restrictions \(0\le v_{am}\le\pi_m(q)\) and no equations, then
the LP endpoints are \(-1\) and \(1\).  The lower endpoint takes
\(v_{0m}=\pi_m(q)\) and \(v_{1m}=0\); the upper endpoint takes
\(v_{1m}=\pi_m(q)\) and \(v_{0m}=0\).  This is the natural Manski-style
bounded-outcome range for a contrast of two \([0,1]\)-valued counterfactual
means.

\item \textbf{Observed joint mediator law.}  If
\(\mathcal Q_0=\{q^\dagger\}\), then \(\pi(q^\dagger)\) is fixed and the LP
reduces to a proxy-envelope problem over \(v_0,v_1\) only.  There is no
mediator-copula uncertainty, so the interior-coupling issue cannot arise.

\item \textbf{Point-identification corner.}  If the proxy equations and cell
envelopes force a unique pair \((v_0,v_1)\) for the admissible mediator law,
then \(\theta_L=\theta_U\) and the bound collapses to point identification.
Under canonical sharpness, or under a direct finite realization of that
singleton, it equals \(\Theta_I(P_{\mathrm{obs}})\).

\item \textbf{No mediator interaction.}  Proposition~\ref{prop:additive-reduction}
shows that if the response table is additive in \(m_1\) and \(m_2\), the PNDE
depends only on the observed mediator marginals.  This recovers the expected
multiple-mediator additivity specialization.

\item \textbf{Null direct effect.}  If the maintained restrictions imply
\(v_{1m}=v_{0m}\) for every mediator cell and every feasible point, then both
LP endpoints equal \(0\).  This agrees with the causal null
\(\E\{Y(1,M(0))\}=\E\{Y(0,M(0))\}\).
\end{enumerate}

\section{Counterexample or minimality check}
Theorem~\ref{thm:interior-witness} is also the minimality check for the shared
proxy restriction.  In the realized family, the true sharp lower endpoint is
\(3\lambda/5\), but the formula obtained by replacing the shared equations
with coordinatewise separated response ranges admits \(9\lambda/20\).  Thus a
weaker cellwise relaxation fails even though each cellwise response value used
by the relaxation is attainable at some admissible fixed coupling.

Dropping the proxy-envelope system altogether gives the vacuous
\([-1,1]\) check in the previous section, so the proxy restrictions are doing
the narrowing work.  For a generic proxy-envelope problem, dropping
Assumption~\ref{ass:canonical-sharpness} does not invalidate the LP as an
outer bound, but it does invalidate a generic sharpness claim.  Theorem
\ref{thm:interior-witness} avoids that gap for its family by explicitly
realizing every feasible weighted table.  The nearby correct formula is
therefore not the rectangular relaxation; it is the joint projection
\(\mathcal P(P_{\mathrm{obs}})\mapsto\sum_m(v_{1m}-v_{0m})\), together with a
realization proof when sharpness is asserted.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
\item \textbf{Finite mediator index.}  Object:
\(\mathcal M=\{0,1\}^2\) with ordered cells \(00,10,01,11\).  Role:
indexes all finite sums and vector coordinates.

\item \textbf{Observable summary.}  Object:
\(P_{\mathrm{obs}}\) with treatment law, outcome/proxy law, mediator
marginals \(p_{ja}(m)\), dependence bands \(\mathcal Q_a\), proxy matrices
\(G_a\), vectors \(b_a\), and envelopes \(\ell_{am},u_{am}\).  Role:
parameterizes the feasible polytope.

\item \textbf{Binary table map.}  Deterministic definition:
\(\pi_{11}(q)=q\), \(\pi_{10}(q)=p_1-q\),
\(\pi_{01}(q)=p_2-q\), and
\(\pi_{00}(q)=1-p_1-p_2+q\).  Dependencies:
Assumption~\ref{ass:marginal-mediators} and the Frechet support condition in
Assumption~\ref{ass:dependence-band}.

\item \textbf{Weighted response coordinates.}  Definition:
\(v_{am}=\pi_m(q)r_{am}\) with \(r_{am}\in[0,1]\).  Role:
avoids division by zero on null mediator cells and makes the target linear.

\item \textbf{Probabilistic assumptions.}  Items:
finite bounded variables, treatment randomization and consistency, marginal
mediator observation, dependence-band feasibility, shared proxy
bridge-envelope validity, and optional canonical finite sharpness.  Role:
connects counterfactual models to the LP summaries; canonical sharpness is a
separate realization condition, not a deterministic LP identity.

\item \textbf{Polytope.}  Definition:
\(\mathcal P(P_{\mathrm{obs}})\subseteq
\R\times\R^4\times\R^4\times\R^4\) cut out by the band constraints, the
binary table equations, \(G_a v_a=b_a\), and
\(\ell_{am}\pi_m\le v_{am}\le u_{am}\pi_m\).  Role:
domain of the bounding functional.

\item \textbf{Linear functional.}  Definition:
 \(L(v_0,v_1)=\sum_m(v_{1m}-v_{0m})\).  Role:
maps feasible weighted tables to PNDE values.

\item \textbf{Identified set and endpoints.}  Definitions:
\(\Theta_I(P_{\mathrm{obs}})\), \(\theta_L=\min_{\mathcal P}L\), and
\(\theta_U=\max_{\mathcal P}L\).  Role:
states outer containment and, with finite realization, sharpness.

\item \textbf{Core deterministic identities.}  Lemmas:
law-of-total-expectation decomposition of the PNDE; compact convex linear
image is an interval; finite LP extrema exist on nonempty compact polytopes;
the additive cancellation
\(\sum_m m_j\pi_m(q)=p_{j0}(1)\).

\item \textbf{Realized family arithmetic.}  Constants:
\(p_1=p_2=3/5\), \(\mathcal Q_0=[1/4,11/20]\),
\(\lambda\in(0,1/7]\), \(q^\star=2/5\),
\(M(q)=\max\{q-1/5,3/5-q\}\), and
\(m(q)=\min\{q-1/5,3/5-q\}\).  Role:
proves unique interior minimization, endpoint feasibility, and strict
rectangular relaxation.

\item \textbf{Finite realization map.}  Construction:
\(A\) randomized, \(M(0)\sim\pi(q)\), \(M(1)=11\) almost surely,
\(Y(0,m)=0\), \(Y(1,11)=0\), and
\(\Pr\{Y(1,s)=1\mid M(0)=s\}=t/\pi_s(q)\) for
\(s\in\{00,10,01\}\).  Role:
verifies the sharpness of the non-rectangularity family without appealing to
Assumption~\ref{ass:canonical-sharpness} as an unexplained axiom.
\end{itemize}

\section{Conclusion and references}
The contribution is a realized non-rectangularity theorem for the locked
two-mediator PNDE problem.  The observable functional is the joint LP
projection over mediator dependence and proxy-constrained weighted response
tables; as a generic statement it is an outer bound, and it becomes sharp only
under canonical finite realization or under a direct construction such as the
one given here.  The clean cases are point identification by the proxy system,
an observed singleton mediator coupling, or a no-interaction response table
where the copula cancels.  The main source of nonsharpness in the tempting
alternative formula is rectangular contamination: cellwise proxy ranges that
are each attainable at some coupling are combined as if they were jointly
attainable at one coupling.

\subsection*{References}
\begin{thebibliography}{99}

\bibitem[Balke and Pearl(1997)]{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
\newblock Bounds on treatment effects from studies with imperfect compliance.
\newblock \emph{Journal of the American Statistical Association} 92(439),
1171--1176.

\bibitem[Daniel et~al.(2015)]{DanielDeStavolaCousensVansteelandt2015}
Daniel, R.~M., De Stavola, B.~L., Cousens, S.~N., and Vansteelandt, S. (2015).
\newblock Causal mediation analysis with multiple mediators.
\newblock \emph{Biometrics} 71(1), 1--14.

\bibitem[Ding and VanderWeele(2016)]{DingVanderWeele2016}
Ding, P. and VanderWeele, T.~J. (2016).
\newblock Sharp sensitivity bounds for mediation under unmeasured
mediator--outcome confounding.
\newblock \emph{Biometrika} 103(2), 483--490.

\bibitem[Dukes et~al.(2023)]{DukesShpitserTchetgen2023}
Dukes, O., Shpitser, I., and Tchetgen Tchetgen, E.~J. (2023).
\newblock Proximal mediation analysis.
\newblock \emph{Biometrika} 110(4), 939--955.

\bibitem[Gabriel et~al.(2023)]{GabrielSachsSjolander2023}
Gabriel, E.~E., Sachs, M.~C., and Sjolander, A. (2023).
\newblock Sharp nonparametric bounds for decomposition effects with two binary
mediators.
\newblock \emph{Journal of the American Statistical Association} 118(544),
2446--2453.

\bibitem[Ghassami et~al.(2023)]{GhassamiShpitserTchetgen2023}
Ghassami, A., Shpitser, I., and Tchetgen Tchetgen, E.~J. (2023).
\newblock Partial identification of causal effects using proxy variables.
\newblock arXiv:2304.04374.

\bibitem[Ghassami et~al.(2025)]{GhassamiYangShpitserTchetgen2025}
Ghassami, A., Yang, A., Shpitser, I., and Tchetgen Tchetgen, E.~J. (2025).
\newblock Causal inference with hidden mediators.
\newblock \emph{Biometrika} 112(1), asae037.

\bibitem[Imai et~al.(2010)]{ImaiKeeleYamamoto2010}
Imai, K., Keele, L., and Yamamoto, T. (2010).
\newblock Identification, inference and sensitivity analysis for causal
mediation effects.
\newblock \emph{Statistical Science} 25(1), 51--71.

\bibitem[Manski(1990)]{Manski1990}
Manski, C.~F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{The American Economic Review} 80(2), 319--323.

\bibitem[Miles et~al.(2017)]{MilesKankiMeloniTchetgen2017}
Miles, C.~H., Kanki, P., Meloni, S., and Tchetgen Tchetgen, E.~J. (2017).
\newblock On partial identification of the natural indirect effect.
\newblock \emph{Journal of Causal Inference} 5(2).

\bibitem[Pearl(2001)]{Pearl2001}
Pearl, J. (2001).
\newblock Direct and indirect effects.
\newblock In \emph{Proceedings of the Seventeenth Conference on Uncertainty in
Artificial Intelligence}, 411--420.

\bibitem[Robins and Greenland(1992)]{RobinsGreenland1992}
Robins, J.~M. and Greenland, S. (1992).
\newblock Identifiability and exchangeability for direct and indirect effects.
\newblock \emph{Epidemiology} 3(2), 143--155.

\bibitem[Tchetgen Tchetgen and Shpitser(2012)]{TchetgenShpitser2012}
Tchetgen Tchetgen, E.~J. and Shpitser, I. (2012).
\newblock Semiparametric theory for causal mediation analysis: efficiency
bounds, multiple robustness and sensitivity analysis.
\newblock \emph{Annals of Statistics} 40(3), 1816--1845.

\bibitem[VanderWeele and Vansteelandt(2014)]{VanderWeeleVansteelandt2014}
VanderWeele, T.~J. and Vansteelandt, S. (2014).
\newblock Mediation analysis with multiple mediators.
\newblock \emph{Epidemiologic Methods} 2(1), 95--115.

\bibitem[Vansteelandt and Daniel(2017)]{VansteelandtDaniel2017}
Vansteelandt, S. and Daniel, R.~M. (2017).
\newblock Interventional effects for mediation analysis with multiple
mediators.
\newblock \emph{Epidemiology} 28(2), 258--265.

\bibitem[Xia and Chan(2022)]{XiaChan2022}
Xia, F. and Chan, K.~C.~G. (2022).
\newblock Decomposition, identification and multiply robust estimation of
natural mediation effects with multiple mediators.
\newblock \emph{Biometrika} 109(4), 1085--1100.

\end{thebibliography}

\end{document}
