% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_surrogate\_paradox\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_surrogate\_paradox\_phase} / \texttt{v1}%
  \\ \large\textit{A binary principal-stratum sign frontier for the surrogate paradox}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
cluster=partial identification
qid=pid_surrogate_paradox_phase
specialization=v1
observable distribution P=the two randomized-arm binary tables
  P_z(s,y)=Pr(S=s,Y=y | Z=z), z,s,y in {0,1}, with treatment
  assignment Z randomized and 0<Pr(Z=1)<1
parameter theta=theta_R=E[Y(1)-Y(0) | G=R], where
  G=(S(0),S(1)) and R=(0,1) is the binary responder principal stratum
identifying restrictions=consistency; random assignment of Z; binary
  potential outcomes S(0),S(1),Y(0),Y(1); monotone surrogate response
  S(1)>=S(0); positive responder share r=Pr(G=R)>0; positive observed
  surrogate movement Delta_S=Pr(S=1|Z=1)-Pr(S=1|Z=0)>0; positive
  observed surrogate-outcome concordance c_z=E[Y|Z=z,S=1]-E[Y|Z=z,S=0]>0
  for z=0,1 when the conditional means exist
bounding functional=the responder active-face certificate
  A_R(P)=(T_R(P),F_R(P),W_R(P)), where T_R(P)=U_{0R}(P)-L_{1R}(P),
  F_R(P) records the active lower face for E[Y(1)|G=R] and active upper
  face for E[Y(0)|G=R], and W_R(P) is the finite endpoint-attaining
  binary witness table; the flagship question is whether A_R(P) gives a
  strict non-equivalence frontier between observed-data exclusion criteria
  for the average surrogate paradox and responder-stratum CEP sign failure
\end{verbatim}

\begin{abstract}
Binary surrogate endpoints can look favorable in the observed trial while the responder principal stratum has a harmful outcome effect. The object studied here is the responder active-face certificate \(A_R(P)\), a finite table certificate computed from the two observed \((S,Y)\) arms. The main conjecture states that \(A_R(P)\) gives a strict non-equivalence frontier: observed-data criteria that exclude the average surrogate paradox can hold while the responder causal-effect-predictiveness cell admits an endpoint-attaining negative effect. This is not the lower endpoint of a Manski interval restated as an if and only if; the certificate must identify the active faces, paste them into one binary principal-strata law, and preserve the observed positive concordance inequalities. Resolving the conjecture would make the hidden principal-cell failure mode visible in a hand-checkable binary table.
\end{abstract}

\section{Introduction}
Clinical surrogate validation often asks whether a positive treatment effect on a binary surrogate can certify the sign of a later endpoint. The claim studied here is sharper: a table may satisfy observed-data exclusion logic for the average surrogate paradox while a responder principal-stratum cell has a negative endpoint effect certified by \(A_R(P)\).

\citet[Sec.~2]{FrangakisRubin2002} make principal effects the causal comparison within post-treatment response strata, while \citet[p.~920, Summary]{ChenGengJia2007} define the surrogate paradox through endpoint sign unpredictability. \citet[Sec.~3, Theorems~1--2]{YinLiuGengLuo2019} give observed-data criteria with optimality claims for excluding the average paradox, and \citet[Sec.~3]{VanderWeele2013} characterizes conditions sufficient to avoid it. The gap is a strict binary non-equivalence result for the responder CEP cell; it lives in partial identification with principal strata.

The immediate consumer is the principal surrogate endpoint program of \citet{GilbertHudgens2008}. A reader who accepts the frontier would check \(T_R(P)\) before treating a favorable observed surrogate table as evidence about the responder stratum.

\begin{itemize}[leftmargin=*]
\item Theorem 1: monotone binary principal strata reduce the responder means to two sharp mixture-deconvolution intervals. Gap: \citet{FrangakisRubin2002} defines the strata but does not give this sign frontier. Consumer: \citet{GilbertHudgens2008}.
\item Conjecture 1: the active-face certificate \(A_R(P)\) gives a strict non-equivalence frontier between average observed-data exclusion criteria and responder CEP sign failure. Gap: \citet[p.~920]{ChenGengJia2007}, \citet[Sec.~3]{VanderWeele2013}, and \citet[Sec.~3, Theorems~1--2]{YinLiuGengLuo2019} do not characterize a principal-cell witness that survives their average-level logic. Consumer: binary clinical surrogate trials.
\item Conjecture 2: the concordance-preserving witness polytope \(\mathcal W_R(P)\) has a computable active-face certificate \(F_R(P)\) and nonempty relative interior on the strict frontier region. Gap: \citet[Sec.~3]{Kuroki2013} gives sharp endpoint bounds, but not the active-face principal-stratum certificate. Consumer: finite-support sensitivity analyses for principal surrogates.
\end{itemize}

\section{Related work}
\citet{FrangakisRubin2002} introduce principal stratification and justify causal effects within strata defined by \((S(0),S(1))\); this is the latent population on which \(\theta_R\) is defined.
\citet[p.~920, Summary]{ChenGengJia2007} define the surrogate paradox as endpoint sign unpredictability despite favorable surrogate relations; their criterion is stated at the endpoint sign level rather than as a responder-stratum phase frontier.
\citet{GilbertHudgens2008} introduce the causal effect predictiveness surface for principal surrogate endpoints; the proposed \(T_R(P)\) is a binary sign diagram for one cell of that surface.
\citet[Sec.~3]{VanderWeele2013} shows that favorable surrogate associations need stronger conditions to rule out the surrogate paradox; this proposal asks when a principal-cell inverse witness remains feasible.
\citet[Sec.~3]{Kuroki2013} derives sharp bounds using a surrogate endpoint; the present proposal replaces a generic bound with a named responder active-face certificate and endpoint witnesses.
\citet{JuGeng2010} develop distributional surrogate criteria; their target is sign preservation for distributional effects, not a binary principal-cell witness frontier.
\citet[Sec.~3, Theorems~1--2]{YinLiuGengLuo2019} provide observed-data criteria to exclude surrogate paradoxes with optimality claims; the proposed frontier is a strict principal-stratum non-equivalence statement rather than another average exclusion rule.
\citet{MaYinLiuGeng2021} show that individual surrogate paradoxes can survive average criteria; this motivates a worst-principal-cell rather than average endpoint target.
\citet{DingLu2017} study monotonicity and principal scores in principal stratification; monotone binary surrogate response is the convention that makes \(R=(0,1)\) observable in prevalence but not in outcomes.
The in-repo catalogue in \texttt{doc/API.md} records only seed-level ExactID and PartialID catalogue placeholders for this cluster, with no accepted surrogate-paradox phase theorem.
The closest banked CausalSmith prior is \texttt{pid\_long\_term\_surrogate}, whose rejected phase diagram was a prevalence-interval dilation for a long-term proxy endpoint; it did not define a Frangakis--Rubin responder stratum or a positive-concordance sign frontier.
The accepted adjacent proposal \texttt{pid\_ordinal\_principal\_strata} studies ordinal \(K\ge3\) compatibility facets with supplied principal scores; it is not a binary surrogate-paradox threshold.
The downgraded \texttt{pid\_collider\_bias\_sharp} proposal supplies finite binary principal-strata threshold machinery for selected outcomes, not for surrogate endpoint response strata.

\section{Formal setup}
Let \(Z\in\{0,1\}\) be randomized, \(S\in\{0,1\}\) the observed surrogate, and \(Y\in\{0,1\}\) the endpoint. Potential variables are \(S(z)\) and \(Y(z)\). Consistency gives \(S=S(Z)\) and \(Y=Y(Z)\), and random assignment gives the two observed tables
\[
  P_z(s,y)=\Pr(S(z)=s,Y(z)=y),\qquad z,s,y\in\{0,1\}.
\]
Write \(p_z=\Pr(S=1\mid Z=z)\), \(q_{zs}=\Pr(Y=1\mid Z=z,S=s)\), and \(c_z=q_{z1}-q_{z0}\).

Under monotone surrogate response \(S(1)\ge S(0)\), the principal strata are \(N=(0,0)\), \(R=(0,1)\), and \(A=(1,1)\), with masses
\[
  n=1-p_1,\qquad r=p_1-p_0,\qquad a=p_0 .
\]
The target is the responder effect
\[
  \theta_R=\mu_{1R}-\mu_{0R},\qquad
  \mu_{zR}=\E[Y(z)\mid G=R].
\]
The two mixtures involving \(R\) are
\[
  q_{11}=\lambda\,\mu_{1R}+(1-\lambda)\mu_{1A},
  \qquad
  q_{00}=\eta\,\mu_{0R}+(1-\eta)\mu_{0N},
\]
where \(\lambda=r/(r+a)=r/p_1\) and \(\eta=r/(r+n)=r/(1-p_0)\). Define
\[
  L_{1R}=\max\{0,(q_{11}-(1-\lambda))/\lambda\},\quad
  U_{1R}=\min\{1,q_{11}/\lambda\},
\]
\[
  L_{0R}=\max\{0,(q_{00}-(1-\eta))/\eta\},\quad
  U_{0R}=\min\{1,q_{00}/\eta\}.
\]
The identified set and frontier are
\[
  \Theta_R(P)=\{\mu_{1R}-\mu_{0R}: \text{a binary monotone principal-strata law induces }P\},
  \qquad
  T_R(P)=U_{0R}-L_{1R}.
\]
Let \(\mathcal W_R(P)\) be the finite polytope of binary monotone principal-strata laws inducing \(P\), satisfying \(c_0>0\), \(c_1>0\), and attaining either endpoint of \(\Theta_R(P)\). Let \(F_R(P)=(f_{1R},f_{0R})\) record which of the two active faces defines \(L_{1R}\) and \(U_{0R}\): \(f_{1R}\in\{\text{zero face},\text{one face}\}\) and \(f_{0R}\in\{\text{zero face},\text{one face}\}\). The active-face certificate is
\[
  A_R(P)=(T_R(P),F_R(P),\mathcal W_R(P)).
\]
Write \(\mathcal E_{\mathrm{avg}}\) for the observed-data exclusion region for the average surrogate paradox in the sense of \citet[Sec.~3, Theorems~1--2]{YinLiuGengLuo2019}. The strict non-equivalence target is the set difference
\[
  \mathcal E_{\mathrm{avg}}\cap\{P:\mathcal W_R(P)\ne\varnothing,\ \inf_{\omega\in\mathcal W_R(P)}\theta_R(\omega)<0\}.
\]

\begin{verbatim}
cluster=partial identification
qid=pid_surrogate_paradox_phase
specialization=v1
observable distribution P=the two randomized-arm binary tables
  P_z(s,y)=Pr(S=s,Y=y | Z=z), z,s,y in {0,1}, with treatment
  assignment Z randomized and 0<Pr(Z=1)<1
parameter theta=theta_R=E[Y(1)-Y(0) | G=R], where
  G=(S(0),S(1)) and R=(0,1) is the binary responder principal stratum
identifying restrictions=consistency; random assignment of Z; binary
  potential outcomes S(0),S(1),Y(0),Y(1); monotone surrogate response
  S(1)>=S(0); positive responder share r=Pr(G=R)>0; positive observed
  surrogate movement Delta_S=Pr(S=1|Z=1)-Pr(S=1|Z=0)>0; positive
  observed surrogate-outcome concordance c_z=E[Y|Z=z,S=1]-E[Y|Z=z,S=0]>0
  for z=0,1 when the conditional means exist
bounding functional=the responder active-face certificate
  A_R(P)=(T_R(P),F_R(P),W_R(P)), where T_R(P)=U_{0R}(P)-L_{1R}(P),
  F_R(P) records the active lower face for E[Y(1)|G=R] and active upper
  face for E[Y(0)|G=R], and W_R(P) is the finite endpoint-attaining
  binary witness table; the flagship question is whether A_R(P) gives a
  strict non-equivalence frontier between observed-data exclusion criteria
  for the average surrogate paradox and responder-stratum CEP sign failure
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Randomization and consistency]\label{ass:randomization}
\(0<\Pr(Z=1)<1\), \(Z\perp (S(0),S(1),Y(0),Y(1))\), and \(S=S(Z)\), \(Y=Y(Z)\).
\end{assumption}

\begin{assumption}[Binary support]\label{ass:binary-support}
\(S(0),S(1),Y(0),Y(1)\in\{0,1\}\) almost surely.
\end{assumption}

\begin{assumption}[Monotone surrogate response]\label{ass:monotone-surrogate}
\(S(1)\ge S(0)\) almost surely and \(r=\Pr\{S(0)=0,S(1)=1\}>0\).
\end{assumption}

\begin{assumption}[Observable favorable surrogate table]\label{ass:favorable-observed}
\(\Delta_S=p_1-p_0>0\), \(0<p_0<p_1<1\), and \(c_z=q_{z1}-q_{z0}>0\) for \(z=0,1\).
\end{assumption}

\begin{assumption}[Interior phase region]\label{ass:interior-phase}
All displayed conditional probabilities in Section 6 lie in \((0,1)\), and the inequalities used to classify \(T_R(P)\) are strict.
\end{assumption}

\begin{assumption}[Average exclusion region]\label{ass:average-exclusion}
The observed law \(P\) lies in \(\mathcal E_{\mathrm{avg}}\), the observed-data region satisfying the average surrogate-paradox exclusion criteria of \citet[Sec.~3, Theorems~1--2]{YinLiuGengLuo2019}.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: responder mixture intervals]\label{thm:mixture-intervals}
Under Assumptions~\ref{ass:randomization}--\ref{ass:monotone-surrogate}, the sharp feasible sets for the two responder endpoint means are
\[
  \mu_{1R}\in [L_{1R},U_{1R}],\qquad
  \mu_{0R}\in [L_{0R},U_{0R}].
\]
Consequently,
\[
  \Theta_R(P)=[L_{1R}-U_{0R},\, U_{1R}-L_{0R}]
\]
whenever the two responder components can be pasted into one joint binary potential-outcome law.
\end{theorem}
The proof solves the two displayed two-component mixture equations over \([0,1]\). Sharpness follows by assigning the residual mixture mass to \(A\) and \(N\), then coupling \(Y(0)\) and \(Y(1)\) inside \(R\) arbitrarily.

\begin{conjecture}[Conjecture 1: strict average-versus-responder non-equivalence frontier (NOT YET PROVED)]\label{conj:phase-frontier}
Under Assumptions~\ref{ass:randomization}--\ref{ass:average-exclusion}, the set
\[
  \mathcal E_{\mathrm{avg}}\cap\{P:T_R(P)>0,\ \mathcal W_R(P)\ne\varnothing\}
\]
contains a relatively open subset of the binary-table simplex. For every \(P\) in that subset, \(A_R(P)\) certifies a binary monotone principal-strata law inducing \(P\) such that
\[
  \Delta_S>0,\qquad c_0>0,\qquad c_1>0,\qquad \theta_R<0,
\]
although \(P\) satisfies the observed-data criteria that exclude the average surrogate paradox. The frontier is strict: the same construction gives a path \(P_t\in\mathcal E_{\mathrm{avg}}\) for which \(T_R(P_t)\) crosses zero at one interior value, while the average exclusion status does not change.
\end{conjecture}

\begin{conjecture}[Conjecture 2: concordance-preserving witness polytope (NOT YET PROVED)]\label{conj:open-witness}
Under Assumptions~\ref{ass:randomization}--\ref{ass:interior-phase}, the set of observed laws satisfying \(T_R(P)>0\), \(\Delta_S>0\), \(c_0>0\), and \(c_1>0\) contains a relatively open subset of the binary-table simplex. On that subset, both endpoints \(L_{1R}-U_{0R}\) and \(U_{1R}-L_{0R}\) are attained by nondegenerate laws with \(0<\Pr(G=g,Y(0)=u,Y(1)=v)<1\) for at least two endpoint-potential cells in the responder stratum.
Equivalently, \(\mathcal W_R(P)\) has nonempty relative interior and an active-face certificate \(F_R(P)\) that is locally constant throughout each strict phase cell.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[No respondent ambiguity]\label{cor:no-ambiguity}
Under Assumptions~\ref{ass:randomization}--\ref{ass:monotone-surrogate}, if \(\lambda=\eta=1\), then \(L_{1R}=U_{1R}=q_{11}\), \(L_{0R}=U_{0R}=q_{00}\), and \(\Theta_R(P)=\{q_{11}-q_{00}\}\).
\end{corollary}
This is the pure-responder corner: the observed \(Z=1,S=1\) and \(Z=0,S=0\) cells contain only \(R\), so the frontier collapses by substitution.

\begin{corollary}[Homogeneous endpoint effects]\label{cor:homogeneous}
If \(\mu_{1N}-\mu_{0N}=\mu_{1R}-\mu_{0R}=\mu_{1A}-\mu_{0A}=\tau\), then \(\theta_R=\tau\) and \(T_R(P)>0\) can only reflect unmodeled heterogeneity allowed by the partial-identification problem.
\end{corollary}
Under a homogeneous effect restriction, the proposed paradox phase must disappear because all principal strata share the same endpoint contrast.

\paragraph{Exhibit 9.1: a worked frontier.}
Let \((n,r,a)=(0.30,0.40,0.30)\). Set
\[
  \mu_{1R}=0.20,\quad \mu_{1A}=1.00,\quad \mu_{0R}=0.60,\quad \mu_{0N}=0.00,\quad
  \mu_{1N}=0.10,\quad \mu_{0A}=0.40 .
\]
Then \(p_0=0.30\), \(p_1=0.70\), \(\lambda=4/7\), and \(\eta=4/7\). The observed means are
\[
  q_{11}=(4/7)0.20+(3/7)1.00=19/35,\quad
  q_{00}=(4/7)0.60+(3/7)0.00=12/35.
\]
The frontier is
\[
  L_{1R}=0.20,\quad U_{1R}=0.95,\quad
  L_{0R}=0,\quad U_{0R}=0.60,\quad
  T_R(P)=0.40>0.
\]
The average endpoint effect is
\[
  \Delta_Y=0.30(0.10-0)+0.40(0.20-0.60)+0.30(1.00-0.40)=0.05>0.
\]
Thus this table is in the observable no-average-paradox sign region used by the Yin--Liu--Geng--Luo exclusion criteria: \(\Delta_S=0.40>0\), \(\Delta_Y>0\), \(c_1=q_{11}-q_{10}=19/35-0.10=31/70>0\), and \(c_0=q_{01}-q_{00}=0.40-12/35=2/35>0\). It nevertheless has responder harm \(\theta_R=0.20-0.60=-0.40\).

\paragraph{Exhibit 9.2: the responder witness polytope.}
For Exhibit 9.1 write \(x_{uv}=\Pr(G=R,Y(1)=u,Y(0)=v)\). The responder constraints are
\[
  x_{11}+x_{10}+x_{01}+x_{00}=0.40,\quad
  x_{11}+x_{10}=0.08,\quad
  x_{11}+x_{01}=0.24,\quad x_{uv}\ge0.
\]
Hence
\[
  x_{11}=t,\quad x_{10}=0.08-t,\quad x_{01}=0.24-t,\quad x_{00}=0.08+t,
  \qquad 0\le t\le 0.08 .
\]
The point \(t=0.04\) is a relative-interior point with masses \((0.04,0.04,0.20,0.12)\). The two endpoint-attaining faces are \(t=0\) and \(t=0.08\), and both preserve the same values of \(\mu_{1R}=0.20\), \(\mu_{0R}=0.60\), and \(\theta_R=-0.40\); they vary only the latent association between \(Y(1)\) and \(Y(0)\) inside \(R\). The active certificate is \(F_R(P)=(\text{one face for }L_{1R},\text{zero face for }U_{0R})\), since \(L_{1R}=(q_{11}-(1-\lambda))/\lambda\) and \(U_{0R}=q_{00}/\eta\). The \(N\) cells put masses \(0.03,0.27\) on \(Y(1)=1,0\) and \(Y(0)=0\); the \(A\) cells put masses \(0.12,0.18\) on \(Y(0)=1,0\) and \(Y(1)=1\). All denominators are positive, all principal strata have positive mass, and no displayed equality overdetermines the four \(x_{uv}\) variables.

\section{Proof-sketch route}
Conjecture~\ref{conj:phase-frontier} follows the chain
\[
\text{strict non-equivalence frontier}
\leftarrow \text{unfold Section 6 definitions}
\leftarrow \text{substitute Assumptions 1--5}
\leftarrow \text{derive monotone stratum masses from the two surrogate margins}
\leftarrow \text{solve the two responder mixture inversions}
\leftarrow \text{map the active faces into the Yin--Liu--Geng--Luo average exclusion coordinates}
\leftarrow \text{paste endpoint-attaining responder means into one joint finite law}
\leftarrow \text{verify positive-concordance inequalities after pasting}
\leftarrow \text{finite-dimensional sharpness of binary mixture models}.
\]
The substantive steps are the two inverse-mixture endpoint derivations, the coordinate comparison with the observed-data exclusion inequalities, the common-law pasting argument, and the strict-inequality preservation check for the observed concordances, so \(k=4\) before the final finite-mixture sharpness theorem. Conjecture~\ref{conj:open-witness} adds an active-face stability step: perturb the six endpoint means and the three stratum masses inside the strict region, then show the same active formulas for \(L_{1R}\), \(U_{0R}\), and \(F_R(P)\) continue to define the witness polytope.

\section{Honest scope flags}
Theorem~\ref{thm:mixture-intervals} is routine mixture algebra and is included to make the target well posed. Conjectures~\ref{conj:phase-frontier} and \ref{conj:open-witness} are the novelty claims and are not yet proved. Version 2 withdraws the v1 claim that \(T_R(P)>0\) alone is the flagship if-and-only-if result; the revised object is the active-face certificate \(A_R(P)\) and its strict non-equivalence with average observed-data exclusion logic. The main uncertainty is whether the positive observed concordance constraints always preserve the same active face, or whether they introduce an additional compatibility facet beyond \(A_R(P)\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft of the binary responder-stratum phase frontier; prior verdict: none.
\item v2 (revise) -- added location-level comparator anchors, replaced the definitional interval-sign headline with a strict average-versus-responder non-equivalence frontier, and named the concordance-preserving witness polytope; prior verdict: REVISE.
\item v3 (revise) -- corrected the Kuroki citation, replaced the negative-average-effect witness with a positive-average-effect sign-region witness, and computed the responder witness polytope with an interior point and endpoint faces; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chen, Geng, and Jia(2007)]{ChenGengJia2007}
Chen, H., Geng, Z., and Jia, J. (2007).
Criteria for surrogate end points.
\emph{Journal of the Royal Statistical Society: Series B}, 69(5), 919--932.

\bibitem[Ding and Lu(2017)]{DingLu2017}
Ding, P. and Lu, J. (2017).
Principal stratification analysis using principal scores.
\emph{Journal of the Royal Statistical Society: Series B}, 79(3), 757--777.

\bibitem[Frangakis and Rubin(2002)]{FrangakisRubin2002}
Frangakis, C. E. and Rubin, D. B. (2002).
Principal stratification in causal inference.
\emph{Biometrics}, 58(1), 21--29.

\bibitem[Gilbert and Hudgens(2008)]{GilbertHudgens2008}
Gilbert, P. B. and Hudgens, M. G. (2008).
Evaluating candidate principal surrogate endpoints.
\emph{Biometrics}, 64(4), 1146--1154.

\bibitem[Ju and Geng(2010)]{JuGeng2010}
Ju, C. and Geng, Z. (2010).
Criteria for surrogate end points based on causal distributions.
\emph{Journal of the Royal Statistical Society: Series B}, 72(1), 129--142.

\bibitem[Kuroki(2013)]{Kuroki2013}
Kuroki, M. (2013).
Sharp bounds on causal effects using a surrogate endpoint.
\emph{Statistics in Medicine}, 32(25), 4338--4347.

\bibitem[Ma et al.(2021)]{MaYinLiuGeng2021}
Ma, L., Yin, G., Liu, L., and Geng, Z. (2021).
On the individual surrogate paradox.
\emph{Biostatistics}, 22(3), 545--560.

\bibitem[VanderWeele(2013)]{VanderWeele2013}
VanderWeele, T. J. (2013).
Surrogate measures and consistent surrogates.
\emph{Biometrics}, 69(3), 561--569.

\bibitem[Yin et al.(2019)]{YinLiuGengLuo2019}
Yin, G., Liu, L., Geng, Z., and Luo, P. (2019).
Novel criteria to exclude the surrogate paradox and their optimalities.
\emph{Scandinavian Journal of Statistics}, 46(1), 166--184.
\end{thebibliography}

\end{document}
