% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_surrogate\_paradox\_phase, specialization=v1
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_surrogate\_paradox\_phase} / \texttt{v1}%
  \\ \large\textit{Average-sufficiency vacuity threshold for binary principal surrogates}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid=pid_surrogate_paradox_phase
specialization=v1
anchor_cluster=Partial identification
observable distribution P=the randomized binary law of (Z,S,Y), where
  Z in {0,1}, S=S(Z) in {0,1} is the observed surrogate, and
  Y=Y(Z) in {0,1} is the endpoint observed in the assigned arm; treatment
  probabilities e_z=P(Z=z) are known and positive
parameter theta=theta_R=E[Y(1)-Y(0) | S(0)=0,S(1)=1], the endpoint effect
  in the binary responder principal stratum R=(0,1)
identifying restrictions=random assignment, consistency, binary potential
  surrogates and endpoints, surrogate monotonicity S(1)>=S(0), positive
  responder mass r=P(S(0)=0,S(1)=1)>0, positive observed surrogate contrast,
  and an average endpoint-sufficiency margin Delta_Y=E[Y(1)-Y(0)]>=eta
bounding functional=the worst-responder lower support
  W(P,eta)=inf theta_R over all finite binary principal-strata endpoint laws
  matching the observed (S,Y) arm tables and satisfying Delta_Y>=eta; the
  phase threshold tau*(P,eta) is the largest responder mass-normalized
  endpoint deficit for which W(P,eta)<0
\end{verbatim}

\begin{abstract}
Average surrogate criteria do not by themselves say what happens inside the Frangakis--Rubin responder stratum.
This draft asks whether a positive average endpoint margin, together with a positive treatment effect on a binary surrogate, gives any nonvacuous lower bound on the responder-stratum endpoint effect.
The main conjecture states that it does not: unless an explicit mass-balance threshold is crossed, an endpoint-attaining binary principal-strata witness can keep the average endpoint effect positive while making the responder effect negative.
The threshold is a finite-table phase boundary, not a Manski interval restatement.
If correct, the result gives a sharp warning label for uses of average causal sufficiency as a principal-surrogate sign guarantee.
\end{abstract}

\section{Introduction}
A binary surrogate may move in the right direction on average while the endpoint effect inside the responder principal stratum moves in the wrong direction.  The question is whether adding a positive average endpoint-sufficiency margin rules out that principal-stratum sign failure.  The main conjecture says that, in the finite binary monotone model, average sufficiency has a vacuous worst-responder lower bound below an explicit mass-balance threshold.

The closest published comparators are \citet[Sec.~2]{ChenGengJia2007}, which formulate causal necessity and sufficiency for surrogate endpoints at an average level, and \citet[p.~21]{FrangakisRubin2002}, which make the responder stratum a causal comparison unit.  \citet[Sec.~2]{MaYinLiuGeng2021} show that individual surrogate paradoxes can survive average criteria, but they do not give the finite principal-strata threshold that determines when a responder-cell sign flip remains compatible with a positive average endpoint margin.  The kernel is a partial-identification statement for a binary principal-strata law.

The concrete consumer is the surrogate-paradox exclusion literature represented by \citet{YinLiuGengLuo2019}.  If the conjecture is right, average endpoint sufficiency must be supplemented by a responder-mass balance check before it is used as a sign-preservation condition.  A reader would report the phase slack rather than treating positive average endpoint movement as evidence against a harmful responder effect.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the average endpoint margin decomposes into responder, never-responder, and always-surrogate endpoint components with weights \((r,\nu,a)\). Gap: \citet{FrangakisRubin2002} define principal strata but do not state this sufficiency-to-worst-cell reduction. Consumer: principal-strata sensitivity analysis.
\item Conjecture 1: the sharp worst-responder lower support under an average endpoint-sufficiency margin is \(W(P,\eta)=\max\{-1,(\eta-\nu-a)/r,L_R^{obs}(P)\}\), with endpoint-attaining binary witnesses. Gap: \citet{ChenGengJia2007} average sufficiency does not control the minimum responder effect. Consumer: \citet{YinLiuGengLuo2019}.
\item Conjecture 2: the sign phase threshold is \(\tau^*(P,\eta)=(\eta-\nu-a)/r\); negative responder effects are compatible exactly when \(\tau^*(P,\eta)<0\) and observed responder-cell feasibility is nonempty. Gap: \citet{MaYinLiuGeng2021} identifies individual sign failures but not the finite-table average-sufficiency threshold. Consumer: binary surrogate-endpoint trial design.
\end{itemize}

\section{Related work}
\citet{FrangakisRubin2002} introduce principal stratification, which supplies the binary responder stratum \(R=(0,1)\).  \citet{ChenGengJia2007} define surrogate paradoxes and causal necessity/sufficiency criteria; their average criteria motivate the margin \(\Delta_Y\ge\eta\) but do not bound the worst responder-cell effect.  \citet{GilbertHudgens2008} study causal effect predictiveness for principal surrogate endpoints; their CEP surface is adjacent because it evaluates endpoints within principal strata.  \citet{VanderWeele2013} shows that positive surrogate and endpoint associations are insufficient to exclude harmful treatment effects; the present proposal asks for the finite principal-strata threshold behind that warning.  \citet{KurokiCai2013} derive sharp bounds using surrogate endpoints; this draft differs by isolating a named phase threshold for the responder effect rather than a generic surrogate-bound interval.  \citet{YinLiuGengLuo2019} give optimal observed-data criteria to exclude surrogate paradoxes, making them the main consumer of a constructive inclusion threshold.  \citet{MaYinLiuGeng2021} show that average criteria may miss individual or stratum-level paradoxes; the proposed threshold gives a binary principal-strata mechanism for that gap.  The \texttt{doc/API.md} PartialID catalogue records Manski nonparametric bound wrappers only, with no binary principal-surrogate phase theorem.  The failed in-repo \texttt{pid\_long\_term\_surrogate\_v1} proposal studied noisy long-term proxies and was rejected as prevalence-interval algebra; the present draft removes proxy bridges and fixes the target as a responder-stratum sign frontier.

\section{Formal setup}
Let \(Z\in\{0,1\}\) be randomized with \(0<\Pr(Z=z)<1\).  Let \(S(z)\in\{0,1\}\) and \(Y(z)\in\{0,1\}\).  The observed data are \((Z,S,Y)=(Z,S(Z),Y(Z))\).  Under monotone surrogate response, define the principal strata
\[
  N=(0,0),\qquad R=(0,1),\qquad A=(1,1),
\]
with masses \(\nu,r,a\).  The observed surrogate margins identify \(a=\Pr(S=1\mid Z=0)\), \(r=\Pr(S=1\mid Z=1)-\Pr(S=1\mid Z=0)\), and \(\nu=1-a-r\).

For \(g\in\{N,R,A\}\) and \(z\in\{0,1\}\), write \(m_{zg}=\Pr(Y(z)=1\mid G=g)\) and \(\theta_g=m_{1g}-m_{0g}\).  The target is the responder effect \(\theta_R\).  The average endpoint margin is
\[
  \Delta_Y=\E[Y(1)-Y(0)]=\nu\theta_N+r\theta_R+a\theta_A.
\]
For an average-sufficiency margin \(\eta\in[0,1]\), let
\[
  W(P,\eta)=\inf\{\theta_R:\text{a finite binary latent law matches }P
    \text{ and }\Delta_Y\ge\eta\}.
\]
The observable feasibility term \(L_R^{obs}(P)\) denotes the lower support for \(\theta_R\) imposed by the two arm-specific \((S,Y)\) mixture equations alone.

\begin{verbatim}
qid=pid_surrogate_paradox_phase
specialization=v1
anchor_cluster=Partial identification
observable distribution P=the randomized binary law of (Z,S,Y), where
  Z in {0,1}, S=S(Z) in {0,1} is the observed surrogate, and
  Y=Y(Z) in {0,1} is the endpoint observed in the assigned arm; treatment
  probabilities e_z=P(Z=z) are known and positive
parameter theta=theta_R=E[Y(1)-Y(0) | S(0)=0,S(1)=1], the endpoint effect
  in the binary responder principal stratum R=(0,1)
identifying restrictions=random assignment, consistency, binary potential
  surrogates and endpoints, surrogate monotonicity S(1)>=S(0), positive
  responder mass r=P(S(0)=0,S(1)=1)>0, positive observed surrogate contrast,
  and an average endpoint-sufficiency margin Delta_Y=E[Y(1)-Y(0)]>=eta
bounding functional=the worst-responder lower support
  W(P,eta)=inf theta_R over all finite binary principal-strata endpoint laws
  matching the observed (S,Y) arm tables and satisfying Delta_Y>=eta; the
  phase threshold tau*(P,eta) is the largest responder mass-normalized
  endpoint deficit for which W(P,eta)<0
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Randomization and consistency]\label{ass:random-consistency}
\(Z\perp(S(0),S(1),Y(0),Y(1))\), \(0<\Pr(Z=z)<1\), and \(S=S(Z)\), \(Y=Y(Z)\).
\end{assumption}

\begin{assumption}[Binary support]\label{ass:binary-support}
\(S(z),Y(z)\in\{0,1\}\) for \(z=0,1\).
\end{assumption}

\begin{assumption}[Monotone positive responder stratum]\label{ass:monotone-responder}
\(S(1)\ge S(0)\) almost surely and \(r=\Pr(S(0)=0,S(1)=1)>0\).
\end{assumption}

\begin{assumption}[Average endpoint sufficiency margin]\label{ass:average-sufficiency}
For a fixed \(\eta\in[0,1]\), admissible latent laws satisfy \(\Delta_Y=\E[Y(1)-Y(0)]\ge\eta\).
\end{assumption}

\begin{assumption}[Observed responder feasibility]\label{ass:observed-feasibility}
The observed \((S,Y)\) arm tables admit at least one monotone binary principal-strata completion, and \(L_R^{obs}(P)\) is finite.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: average margin decomposition]\label{thm:decomposition}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:monotone-responder},
\[
  \Delta_Y=\nu\theta_N+r\theta_R+a\theta_A.
\]
Hence any admissible law satisfying Assumption~\ref{ass:average-sufficiency} obeys
\[
  \theta_R\ge \frac{\eta-\nu\theta_N-a\theta_A}{r}.
\]
\end{theorem}
The proof is the law of total expectation over the three monotone principal strata.

\begin{conjecture}[Conjecture 1: vacuous worst-responder lower bound (NOT YET PROVED)]\label{conj:vacuity}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:observed-feasibility}, the sharp worst-responder support is
\[
  W(P,\eta)=
  \max\left\{
    -1,\,
    L_R^{obs}(P),\,
    \frac{\eta-\nu-a}{r}
  \right\}.
\]
Moreover, each active endpoint is attained by a finite binary principal-strata law with \(m_{z g}\in[0,1]\).  Thus average endpoint sufficiency gives no nonvacuous lower bound on \(\theta_R\) whenever \((\eta-\nu-a)/r<0\) and the observed arm tables do not bind first.
\end{conjecture}

\begin{conjecture}[Conjecture 2: explicit sign phase threshold (NOT YET PROVED)]\label{conj:threshold}
Under the same assumptions, define
\[
  \tau^*(P,\eta)=
  \max\left\{
    L_R^{obs}(P),\,
    \frac{\eta-\nu-a}{r}
  \right\}.
\]
There exists a negative responder-effect witness if and only if \(\tau^*(P,\eta)<0\).  In the one-parameter family with fixed \((\nu,r,a)\), fixed observed feasibility slack, and \(\eta(t)=\nu+a+rt\), the phase transition occurs exactly at \(t=0\).
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Homogeneous endpoint effects]\label{cor:homogeneous}
If \(\theta_N=\theta_R=\theta_A\), then Assumption~\ref{ass:average-sufficiency} implies \(\theta_R=\Delta_Y\ge\eta\).  The vacuity result is therefore driven by principal-stratum heterogeneity, not by the definition of the average margin.
\end{corollary}

\begin{corollary}[No responder mass]\label{cor:no-responder}
If \(r=0\), the target \(\theta_R\) is undefined and the threshold formula is not invoked.  The phase statement is only for positive observed surrogate movement.
\end{corollary}

\paragraph{Exhibit 9.1: computed threshold witness.}
Take \((\nu,r,a)=(0.30,0.20,0.50)\) and \(\eta=0.60\).  Then
\[
  \frac{\eta-\nu-a}{r}=\frac{0.60-0.30-0.50}{0.20}=-1.
\]
Set \(\theta_R=-1\), \(\theta_N=1\), and \(\theta_A=1\), with \(m_{0R}=1,m_{1R}=0,m_{0N}=0,m_{1N}=1,m_{0A}=0,m_{1A}=1\).  The average margin is \(0.30(1)+0.20(-1)+0.50(1)=0.60=\eta\), so average sufficiency and a maximally harmful responder effect coexist.  All endpoint risks are in \([0,1]\), the three principal-strata masses sum to one, and the denominator \(r=0.20\) is nonzero.

\section{Proof-sketch route}
For Conjecture~\ref{conj:vacuity}, the reduction chain is: headline \(\leftarrow\) unfold \(W(P,\eta)\), \(\Delta_Y\), and \(\Theta_I(P)\) \(\leftarrow\) substitute Assumptions~\ref{ass:random-consistency}--\ref{ass:observed-feasibility} \(\leftarrow\) decompose the average margin by principal strata \(\leftarrow\) solve the one-dimensional lower-support problem for \(\theta_R\) after setting the nonresponder and always-surrogate effects to their endpoint-attaining upper values \(\leftarrow\) intersect this support with the observed responder feasibility interval \(\leftarrow\) construct endpoint tables for each active face.  The substantive non-definitional steps are support reduction, endpoint saturation, interval intersection, and witness construction, so \(k=4\).  For Conjecture~\ref{conj:threshold}, substitute \(\eta(t)=\nu+a+rt\), verify the sign of the maximum term, check observed feasibility slack, and reuse the endpoint construction; here \(k=3\).

\section{Honest scope flags}
Theorem~\ref{thm:decomposition} is routine.  Conjectures~\ref{conj:vacuity} and \ref{conj:threshold} are open as sharpness claims once the observed \((S,Y)\) arm tables are imposed; the displayed formula may need a more detailed expression for \(L_R^{obs}(P)\).  The draft does not claim to characterize nonmonotone surrogate defiers, noisy proxy bridges, or causal necessity restrictions stronger than the average endpoint margin.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the average-sufficiency vacuity angle; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chen, Geng, and Jia(2007)]{ChenGengJia2007}
Chen, H., Z. Geng, and J. Jia (2007). Criteria for surrogate end points. \emph{Journal of the Royal Statistical Society: Series B} 69(5), 919--932.

\bibitem[Frangakis and Rubin(2002)]{FrangakisRubin2002}
Frangakis, C. E. and D. B. Rubin (2002). Principal stratification in causal inference. \emph{Biometrics} 58(1), 21--29.

\bibitem[Gilbert and Hudgens(2008)]{GilbertHudgens2008}
Gilbert, P. B. and M. G. Hudgens (2008). Evaluating candidate principal surrogate endpoints. \emph{Biometrics} 64(4), 1146--1154.

\bibitem[Kuroki and Cai(2013)]{KurokiCai2013}
Kuroki, M. and Z. Cai (2013). On recovering a population mean from incomplete data with surrogate outcomes. \emph{Biometrics} 69(4), 951--960.

\bibitem[Ma, Yin, Liu, and Geng(2021)]{MaYinLiuGeng2021}
Ma, Y., G. Yin, Y. Liu, and Z. Geng (2021). Identifying individual surrogate paradoxes. \emph{Biostatistics} 22(2), 312--327.

\bibitem[VanderWeele(2013)]{VanderWeele2013}
VanderWeele, T. J. (2013). Surrogate measures and consistent surrogates. \emph{Biometrics} 69(3), 561--565.

\bibitem[Yin, Liu, Geng, and Luo(2019)]{YinLiuGengLuo2019}
Yin, G., Y. Liu, Z. Geng, and X. Luo (2019). Optimal criteria to exclude the surrogate paradox and their applications. \emph{Scandinavian Journal of Statistics} 46(3), 771--787.
\end{thebibliography}

\end{document}
