% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_surrogate\_paradox\_phase, specialization=v1
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_surrogate\_paradox\_phase} / \texttt{v1}%
  \\ \large\textit{Average surrogate sufficiency has a sharp worst-responder phase threshold}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Partial-identification anchor.  The locked tuple is
\[
(qid, specialization, observable\ distribution\ P, parameter\ \theta, identifying\ restrictions, bounding\ functional).
\]
\begin{quote}\small\ttfamily
qid=pid\_surrogate\_paradox\_phase; specialization=v1; observable distribution P is the randomized binary law of (Z,S,Y) with Z,S,Y in \{0,1\}; latent principal strata are G=(S(0),S(1)) in \{00,01,11\} under monotone surrogate response; parameter theta is theta\_R=E[Y(1)-Y(0) | G=01], the responder principal-stratum outcome effect; identifying restrictions are random assignment, consistency, binary bounded outcomes, monotone S(1)>=S(0), known or identified responder share pi\_R=P(S=1|Z=1)-P(S=1|Z=0)>0, an aggregate average-sufficiency margin gamma, and primitive endpoint rank/slack inequalities for the arm-specific (S,Y) mixture equations; bounding functional is L\_R(gamma,pi\_R)=max\{-1,(gamma-(1-pi\_R))/pi\_R\}, with phase threshold gamma\_star=1-pi\_R for sign preservation of theta\_R.
\end{quote}

\begin{abstract}
A binary surrogate may satisfy positive average surrogate criteria while the responder principal stratum has a harmful endpoint effect.  This proposal asks whether average causal sufficiency supplies any nonvacuous lower bound on the worst responder effect once the Frangakis--Rubin principal strata are made explicit.  The kernel is a sharp phase frontier: the worst-responder lower bound equals \(L_R(\gamma,\pi_R)=\max\{-1,(\gamma-(1-\pi_R))/\pi_R\}\), so sign preservation requires the aggregate sufficiency margin to exceed \(\gamma_\star=1-\pi_R\).  The flagship conjecture is that this frontier is endpoint-attaining inside a finite binary principal-strata witness class compatible with positive observed treatment effects on the surrogate.  Resolving it would turn average surrogate-paradox criteria into a checkable warning about the responder stratum rather than another generic principal-strata bound.
\end{abstract}

\section{Introduction}
Positive treatment effects on a surrogate are often used as evidence that the clinical endpoint should move in the same direction.  The question here is whether an average surrogate-sufficiency margin controls the endpoint effect for the responder principal stratum \(G=01\).  The proposed answer is a phase threshold: unless the margin exceeds \(1-\pi_R\), the responder effect can be negative, and below that threshold the lower endpoint is attained by finite binary tables.

The closest conceptual comparators are \citet[p.~24, Definition 1]{FrangakisRubin2002}, where principal strata are defined by joint potential values of a post-treatment variable, and \citet[p.~919, Summary]{ChenGengJia2007}, where the surrogate paradox is defined at the level of average endpoint signs.  The strict-delta claim is not that \citet{YinLiuGengLuo2020} is tightened as an exclusion theorem; it is that failed exclusion can be refined into a responder-stratum inclusion diagnostic with endpoint tables and an explicit phase frontier.  This proposal lives in partial identification with a finite exact-identification corner for the responder share.

The downstream consumer is the principal-surrogate endpoint workflow of \citet{GilbertHudgens2008} and binary surrogate-paradox exclusion work such as \citet{YinLiuGengLuo2020}.  A reader can separate an average criterion that protects the overall endpoint from a threshold that protects the responder stratum.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the aggregate-margin lower envelope for \(\theta_R\) is \(L_R(\gamma,\pi_R)\). Gap: \citet{ChenGengJia2007} gives average surrogate-paradox criteria, not the responder lower envelope. Consumer: \citet{GilbertHudgens2008} principal-surrogate analyses.
\item Conjecture 1: primitive rank/slack conditions give an endpoint-attaining exposed face and interior sign-reversal witnesses for the responder frontier. Gap: \citet[p.~24, Definition 1]{FrangakisRubin2002} supplies the strata, \citet[p.~97, abstract; p.~99, Section 2]{MaYinLiuGeng2021} motivates individual failures beyond average criteria, and \citet[pp.~84--85, Introduction; p.~88, Theorem 1]{YinLiuGengLuo2020} gives optimal exclusion criteria, but none gives a responder-stratum inclusion frontier with finite endpoint tables. Consumer: \citet{YinLiuGengLuo2020} exclusion diagnostics.
\item Corollary 1: sign preservation of the responder effect is guaranteed if and only if \(\gamma\ge 1-\pi_R\). Gap: \citet{VanderWeele2013} gives sufficient qualitative consistency conditions, while this statement gives the scalar phase threshold. Consumer: binary surrogate validation designs.
\end{itemize}

\section{Related work}
\citet[p.~24, Definition 1]{FrangakisRubin2002} introduce principal stratification; the present proposal uses their binary response types as the latent cells whose worst effect is being bounded.  \citet[p.~919, Summary]{ChenGengJia2007} define the surrogate paradox and causal necessity/sufficiency criteria; the present proposal treats their average-sign framing as the comparator that may fail to protect \(G=01\).  \citet{GilbertHudgens2008} define causal effect predictiveness surfaces for principal surrogate endpoints; the proposed frontier gives a binary lower-envelope diagnostic for the responder slice.  \citet[p.~561, abstract; p.~562, Definition 1]{VanderWeele2013} shows that positive treatment-surrogate and surrogate-outcome relations do not by themselves remove the surrogate paradox; the frontier below quantifies one finite-strata version of that warning.  \citet[p.~4338, abstract; pp.~4339--4340, Section 2]{Kuroki2013} derives closed-form sharp bounds using surrogate endpoints, making the binary surrogate problem a partial-identification problem rather than an observed sign comparison.  \citet[pp.~84--85, Introduction; p.~88, Theorem 1]{YinLiuGengLuo2020} give optimal observed-data criteria to exclude surrogate paradoxes; the present proposal does not dispute their exclusion optimality and instead studies the inclusion-side responder-stratum witness when those criteria do not exclude a paradox.  \citet[p.~97, abstract; p.~99, Section 2]{MaYinLiuGeng2021} show that individual surrogate paradoxes can survive average criteria; the present proposal replaces individual heterogeneity by an explicit worst-principal-stratum lower bound.  \citet{DingLu2017} study monotonicity and principal scores in principal stratification; the responder share \(\pi_R\) is the minimal monotone principal-score object used here.

The in-catalogue summary from \texttt{doc/API.md} is that \texttt{CausalSmith/PartialID/} is seeded for \texttt{pid\_*} questions but has no recorded surrogate-paradox theorem matching this kernel.  The failed \texttt{pid\_long\_term\_surrogate} angle studied noisy proxy and bridge-law sign ambiguity; reviewers asked for explicit finite constructions rather than prevalence-interval algebra.  The candidate \texttt{pid\_ordinal\_principal\_strata} uses compatibility facets for ordinal principal strata, and downgraded \texttt{pid\_collider\_bias\_sharp} uses finite binary threshold machinery in a selection problem.  None states an average-sufficiency-to-worst-responder phase threshold for the binary Frangakis--Rubin surrogate strata.

\section{Formal setup}
Let \(Z\in\{0,1\}\) be randomized treatment, \(S(z)\in\{0,1\}\) the surrogate potential value, and \(Y(z)\in\{0,1\}\) the endpoint potential value.  The observed data are \((Z,S,Y)=(Z,S(Z),Y(Z))\) with law \(P\).  Surrogate monotonicity restricts the principal stratum \(G=(S(0),S(1))\) to \(00,01,11\).  Write \(\pi_g=\Pr(G=g)\), \(\pi_R=\pi_{01}\), \(\theta_g=\E[Y(1)-Y(0)\mid G=g]\), and \(\theta_R=\theta_{01}\).  The aggregate sufficiency margin is
\[
  \Gamma_Y = \sum_{g\in\{00,01,11\}} \pi_g\theta_g.
\]
For a fixed reported margin \(\gamma\in[-1,1]\), define the feasible class \(\mathcal M(P,\gamma)\) as all joint laws \(M\) of \((S(0),S(1),Y(0),Y(1))\) satisfying the assumptions below, matching the full observed law \(P(S,Y\mid Z=z)\) for both arms, and obeying \(\Gamma_Y(M)\ge\gamma\).  A latent law \(M\) is endpoint-compatible with \(P\) when the displayed principal-stratum risks \(\mu_{gz}=\Pr_M\{Y(z)=1\mid G=g\}\) solve the two arm-specific mixture systems
\[
  P(S=s,Y=y\mid Z=z)=
  \sum_{g:g_z=s}\pi_g \Pr\{Y(z)=y\mid G=g\},
  \qquad z,s,y\in\{0,1\}.
\]
Let \(\mathcal C_{\mathrm{rank}}(P,\gamma)\subseteq\mathcal M(P,\gamma)\) denote the primitive rank/slack class in which the mixture map from \((\pi_g,\mu_{gz})\) to the two observed endpoint tables has locally constant rank, all observed \((S,Y)\) cells have positive mass, and every inequality not forced by the exposed binary face has positive slack.  The identified lower envelope for the responder effect is
\[
  \underline\theta_R(P;\gamma)=\inf_{M\in\mathcal M(P,\gamma)} \E_M[Y(1)-Y(0)\mid G=01].
\]
The proposed phase threshold is \(\gamma_\star(P)=1-\pi_R(P)\).

The locked parameters are reproduced as:
\begin{quote}\small\ttfamily
qid=pid\_surrogate\_paradox\_phase; specialization=v1; observable distribution P is the randomized binary law of (Z,S,Y); theta=theta\_R; restrictions=randomization, consistency, bounded binary outcomes, monotone S(1)>=S(0), pi\_R>0, aggregate margin Gamma\_Y>=gamma, primitive endpoint rank/slack class C\_rank(P,gamma); bounding functional L\_R(gamma,pi\_R)=max\{-1,(gamma-(1-pi\_R))/pi\_R\}.
\end{quote}

\section{Assumptions}
\begin{assumption}[Randomization and consistency]\label{ass:rand-cons}
\(Z\perp (S(0),S(1),Y(0),Y(1))\), \(0<\Pr(Z=1)<1\), and the observed variables satisfy \(S=S(Z)\) and \(Y=Y(Z)\).
\end{assumption}

\begin{assumption}[Binary monotone principal surrogate]\label{ass:mono}
\(S(0),S(1)\in\{0,1\}\), \(S(1)\ge S(0)\) almost surely, and \(\pi_R=\Pr\{S(0)=0,S(1)=1\}>0\).
\end{assumption}

\begin{assumption}[Bounded binary endpoint]\label{ass:binary-y}
\(Y(0),Y(1)\in\{0,1\}\).  Hence every principal-stratum endpoint effect \(\theta_g\) lies in \([-1,1]\).
\end{assumption}

\begin{assumption}[Aggregate sufficiency margin]\label{ass:margin}
The nonparametric joint law satisfies \(\Gamma_Y=\sum_g\pi_g\theta_g\ge\gamma\) for a fixed \(\gamma\in[-1,1]\).  This assumption records the average surrogate-sufficiency information available to the analyst and does not impose \(\theta_R\ge0\).
\end{assumption}

\begin{assumption}[Nondegenerate phase regime]\label{ass:nondeg}
For the sharpness conjecture, \(0<\pi_R<1\), \(-1<\gamma<1\), and the target phase is below sign preservation, \(\gamma<1-\pi_R\).  The displayed principal-stratum masses satisfy \(\pi_{00},\pi_{01},\pi_{11}>0\).
\end{assumption}

\begin{assumption}[Primitive endpoint rank and slack]\label{ass:endpoint-compatible}
For the sharpness conjecture, the arm-specific mixture equations in \S6 admit at least one monotone principal-strata solution \(M_0\) matching \(P\) such that the Jacobian of the active equality map in \((\pi_g,\mu_{gz})\) has the same rank in a neighborhood of \(M_0\), every observed \((S,Y)\) cell has probability at least \(\eta>0\), and every inactive binary-risk inequality has slack at least \(\eta\).  The exposed face used for exact endpoint attainment is obtained only by setting the nonresponder outcome effects to their binary maximum and the responder effect to \(L_R(\gamma,\pi_R)\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: average-margin lower envelope]\label{thm:lower-envelope}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:margin}, every feasible law satisfies
\[
  \theta_R\ge L_R(\gamma,\pi_R):=\max\left\{-1,\frac{\gamma-(1-\pi_R)}{\pi_R}\right\}.
\]
The inequality is the best possible algebraic consequence of the aggregate margin and binary bounded outcomes before compatibility with the observed endpoint table is imposed.
\end{theorem}
The proof writes \(\Gamma_Y=\pi_R\theta_R+\sum_{g\ne 01}\pi_g\theta_g\) and bounds the second term by \(1-\pi_R\).  The lower endpoint \(-1\) is the binary outcome bound.

\begin{conjecture}[Conjecture 1: responder-stratum inclusion frontier beyond exclusion criteria (NOT YET PROVED)]\label{conj:sharp-frontier}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:endpoint-compatible}, for every \((\pi_R,\gamma)\) in the nondegenerate phase regime and every observed law \(P\) with positive surrogate contrast \(\Pr(S=1\mid Z=1)-\Pr(S=1\mid Z=0)=\pi_R\), the primitive rank/slack class contains an exposed finite binary face matching the full observed arm-specific endpoint table \(P(S,Y\mid Z=z)\) such that
\[
  \underline\theta_R(P;\gamma)=L_R(\gamma,\pi_R).
\]
Moreover, for every sufficiently small \(\varepsilon>0\) there is a fully interior finite binary witness matching a nearby observed law \(P_\varepsilon\) with all eight arm-specific \((S,Y)\) cells positive and \(\theta_R\le L_R(\gamma,\pi_R)+\varepsilon<0\).  This is a responder-stratum refinement, not a contradiction of \citet{YinLiuGengLuo2020}: when observed-data exclusion criteria fail, the conjecture gives the inclusion-side finite principal-stratum witnesses and their phase frontier.
\end{conjecture}

\begin{corollary}[Corollary 1: sign-preservation phase threshold]\label{cor:threshold}
Under the sharpness conclusion of Conjecture~\ref{conj:sharp-frontier}, the aggregate margin guarantees \(\theta_R\ge0\) for all compatible binary principal-strata laws if and only if
\[
  \gamma\ge \gamma_\star(P):=1-\pi_R(P).
\]
If \(\gamma<\gamma_\star(P)\), a compatible endpoint-attaining witness has negative responder effect.
\end{corollary}

\section{Sanity-check corollaries}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:margin}, if \(\pi_R=1\), then \(L_R(\gamma,1)=\gamma\), so the aggregate margin is exactly the responder effect bound.  If \(\gamma=1\), then \(L_R(1,\pi_R)=1\), so all positive-mass strata must have \(Y(1)-Y(0)=1\) almost surely.

\paragraph{Exhibit 9.1: interior finite binary sign-reversal witness.}
Take \(\pi_{01}=1/4\), \(\pi_{00}=\pi_{11}=3/8\), and \(\delta=0.01\).  Let \((\mu_{00,0},\mu_{00,1})=(\delta,1-\delta)\), \((\mu_{11,0},\mu_{11,1})=(\delta,1-\delta)\), and \((\mu_{01,0},\mu_{01,1})=(1-\delta,\delta)\).  Then \(\theta_{00}=\theta_{11}=0.98\), \(\theta_{01}=-0.98\), \(\Gamma_Y=0.49\), and \(\gamma_\star=1-\pi_R=0.75\).  For \(\gamma=0.49\), \(L_R(\gamma,\pi_R)=\max\{-1,(0.49-0.75)/0.25\}=-1\), so the interior table is within \(0.02\) of the exposed lower face and already has a negative responder effect.
The induced observed endpoint tables are \(P(0,0\mid0)=0.37375\), \(P(0,1\mid0)=0.25125\), \(P(1,0\mid0)=0.37125\), \(P(1,1\mid0)=0.00375\), \(P(0,0\mid1)=0.00375\), \(P(0,1\mid1)=0.37125\), \(P(1,0\mid1)=0.25125\), and \(P(1,1\mid1)=0.37375\), where \(P(s,y\mid z)\) abbreviates \(P(S=s,Y=y\mid Z=z)\).  All eight cells are positive, the three principal-stratum masses sum to one, all conditional endpoint risks lie in \((0,1)\), and the surrogate contrast is \(P(S=1\mid Z=1)-P(S=1\mid Z=0)=1/4\).  Sending \(\delta\downarrow0\) gives the exposed endpoint-attaining face \(\theta_{01}=-1\), \(\theta_{00}=\theta_{11}=1\), with the same \(\pi_R\) and a limiting observed law; thus the exhibit computes the focal threshold from \S6 primitives and separates the interior sign-reversal witness from the boundary sharpness limit.

\section{Proof-sketch route}
The reduction chain for Conjecture~\ref{conj:sharp-frontier} is: headline \(\leftarrow\) unfold \S6 definitions of \(\underline\theta_R\), \(\Gamma_Y\), \(L_R\), and \(\mathcal C_{\mathrm{rank}}(P,\gamma)\) \(\leftarrow\) substitute Assumptions~\ref{ass:rand-cons}--\ref{ass:endpoint-compatible} \(\leftarrow\) step 1, decompose the average margin by the three monotone principal strata and isolate the responder coefficient \(\pi_R\) \(\leftarrow\) step 2, solve the two observed arm-specific endpoint mixture equations for a finite-support table and compute the Jacobian rank of the active equality map \(\leftarrow\) step 3, move nonresponder strata to the favorable binary face and the responder stratum to the adverse face while checking that the inactive endpoint inequalities remain slack until the exposed limit \(\leftarrow\) step 4, use the rank-stable implicit-function argument to thicken the boundary face into the interior positive-cell witnesses of Exhibit 9.1 \(\leftarrow\) step 5, compare the resulting inclusion-side frontier to the failure region of the observed-data exclusion criteria without claiming to improve their exclusion theorem \(\leftarrow\) finite-dimensional convexity of binary mixtures.  Thus \(k=5\) substantive steps beyond definitions and direct assumption substitution.  Boundary cases needing explicit algebra are \(\pi_R\downarrow0\), \(\pi_R=1\), \(\gamma=1-\pi_R\), and observed endpoint tables outside \(\mathcal C_{\mathrm{rank}}(P,\gamma)\), where an additional lower-bound term may appear.

\section{Honest scope flags}
Theorem~\ref{thm:lower-envelope} is routine algebra and is included to locate the phase frontier.  Conjecture~\ref{conj:sharp-frontier} is not yet proved; the open part is the endpoint-compatible open-class sharpness statement, not the displayed average-margin inequality.  Corollary~\ref{cor:threshold} is only a sanity consequence of Conjecture~\ref{conj:sharp-frontier}; it does not carry flagship novelty on its own.  This pivot withdraws the previous exhausted threshold, observed-table, and monotonicity-classification angles and focuses on whether average causal sufficiency is vacuous for worst-responder sign preservation below \(1-\pi_R\).  The most delicate assumption is the aggregate margin \(\Gamma_Y\ge\gamma\), because different surrogate-paradox papers formalize average sufficiency with different conditioning events.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 3, replacing the exhausted phase-threshold angles with the average-sufficiency-to-worst-responder frontier; prior verdict: none.
\item v2 (revise) --- fixed bibliography metadata, added location-level comparator anchors, restricted Conjecture~\ref{conj:sharp-frontier} to the endpoint-compatible open class, and demoted Corollary~\ref{cor:threshold} to a sanity consequence; prior verdict: REVISE.
\item v3 (revise) --- reframed the Yin--Liu--Geng--Luo comparison as an inclusion-side responder diagnostic, replaced endpoint-compatible sharpness-by-assumption with primitive rank/slack conditions, and added an interior finite witness with all observed cells positive; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chen et~al.(2007)]{ChenGengJia2007} Chen, H., Geng, Z., and Jia, J. (2007). Criteria for surrogate end points. \emph{Journal of the Royal Statistical Society: Series B} 69(5), 919--932.
\bibitem[Ding and Lu(2017)]{DingLu2017} Ding, P. and Lu, J. (2017). Principal stratification analysis using principal scores. \emph{Journal of the Royal Statistical Society: Series B} 79(3), 757--777.
\bibitem[Frangakis and Rubin(2002)]{FrangakisRubin2002} Frangakis, C. E. and Rubin, D. B. (2002). Principal stratification in causal inference. \emph{Biometrics} 58(1), 21--29.
\bibitem[Gilbert and Hudgens(2008)]{GilbertHudgens2008} Gilbert, P. B. and Hudgens, M. G. (2008). Evaluating candidate principal surrogate endpoints. \emph{Biometrics} 64(4), 1146--1154.
\bibitem[Kuroki(2013)]{Kuroki2013} Kuroki, M. (2013). Sharp bounds on causal effects using a surrogate endpoint. \emph{Statistics in Medicine} 32(25), 4338--4347.
\bibitem[Ma et~al.(2021)]{MaYinLiuGeng2021} Ma, L., Yin, Y., Liu, L., and Geng, Z. (2021). On the individual surrogate paradox. \emph{Biostatistics} 22(1), 97--113.
\bibitem[VanderWeele(2013)]{VanderWeele2013} VanderWeele, T. J. (2013). Surrogate measures and consistent surrogates. \emph{Biometrics} 69(3), 561--565.
\bibitem[Yin et~al.(2020)]{YinLiuGengLuo2020} Yin, Y., Liu, L., Geng, Z., and Luo, P. (2020). Novel criteria to exclude the surrogate paradox and their optimalities. \emph{Scandinavian Journal of Statistics} 47(1), 84--103.
\end{thebibliography}

\end{document}
