% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_surrogate\_paradox\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_surrogate\_paradox\_phase} / \texttt{v1}%
  \\ \large\textit{A common-responder compatibility facet for binary surrogate-paradox phase thresholds}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal. The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R,\Phi)
=
(\texttt{pid\_surrogate\_paradox\_phase},\texttt{v1},P_{\mathrm{obs}},
\theta_R,\mathcal R_{\mathrm{bin}},\Phi_{\mathrm{cf}}).
\]
Here \(Z\in\{0,1\}\) is randomized treatment, \(S(z)\in\{0,1\}\) is the binary surrogate potential outcome, and \(Y(z)\in\{0,1\}\) is the binary primary-outcome potential outcome. The observable law is the pair of tables \(P_{\mathrm{obs}}=\{p_z(s,y):z,s,y\in\{0,1\}\}\), where \(p_z(s,y)=\Pr(S(z)=s,Y(z)=y)\). The target is the responder principal-stratum effect
\[
  \theta_R=\E[Y(1)-Y(0)\mid S(0)=0,S(1)=1],
\]
defined only when \(r=\Pr\{S(0)=0,S(1)=1\}>0\). The identifying restrictions \(\mathcal R_{\mathrm{bin}}\) are randomization/consistency, binary support, a nonempty monotone-responder stratum \(S(1)\ge S(0)\) almost surely, and interior observable cells. The bounding functional \(\Phi_{\mathrm{cf}}\) is the common-responder compatibility frontier
\[
  \Phi_{\mathrm{cf}}(P_{\mathrm{obs}})=
  \sup_{r\in I_R(P_{\mathrm{obs}})}
  \{\overline\mu_{0R}(r)-\underline\mu_{1R}(r)\},
\]
where \(I_R(P_{\mathrm{obs}})=[p_1-p_0,\min\{p_1,1-p_0\}]\), \(p_z=\Pr(S(z)=1)\), and the arm-specific endpoint functions are defined in Section 6.

\begin{abstract}
Binary surrogate endpoints can satisfy positive treatment-surrogate movement while hiding a harmful effect inside the principal stratum whose surrogate is moved by treatment. This proposal asks whether the hidden sign reversal is governed by a common-responder compatibility facet rather than by two separate Manski-style missing-cell bounds. The flagship conjecture states that a scalar frontier \(\Phi_{\mathrm{cf}}(P_{\mathrm{obs}})\), computed from the same responder mass in both observed arms, is necessary and sufficient for a finite binary witness with \(\theta_R<0\). The conjecture is positioned against surrogate-paradox exclusion criteria and principal-stratification sensitivity analyses that do not isolate this common-mass phase boundary. Resolving it would give applied surrogate studies a hand-checkable diagnostic: the sign question becomes a finite table calculation instead of an unconstrained latent-strata linear program.
\end{abstract}

\section{Introduction}
Surrogate validation is often stated in terms of positive effects on the surrogate and favorable surrogate-outcome association. The question here is whether those observable signs can coexist with a negative treatment effect in the responder principal stratum, and whether the coexistence is decided by one explicit compatibility frontier.

\citet[Sec.~2]{FrangakisRubin2002} make principal strata the causal units defined by post-treatment potential values, while \citet[Sec.~3]{ChenGengJia2007} and \citet[Sec.~2]{YinLiuGengLuo2019} formulate average surrogate-paradox criteria. The gap is that these criteria do not give an if-and-only-if threshold for a finite binary responder stratum when the same latent responder mass must explain both observed tables. The kernel is a PartialID theorem about binary principal strata and sharp finite-support witness laws.

The immediate consumer is the surrogate-paradox exclusion program in \citet{YinLiuGengLuo2019}. A reader who accepts the conclusion would test constructive inclusion by computing \(\Phi_{\mathrm{cf}}\), rather than interpreting failure of an exclusion criterion as an unstructured latent-LP ambiguity.

\begin{itemize}[leftmargin=*]
  \item Theorem 1: the common responder mass lies in one closed interval and induces two arm-specific endpoint maps. Gap: \citet{FrangakisRubin2002} define the strata but do not compute this binary compatibility interval. Consumer: binary principal-stratification sensitivity analyses.
  \item Conjecture 1: \(\Phi_{\mathrm{cf}}(P_{\mathrm{obs}})>0\) if and only if \(P_{\mathrm{obs}}\) admits a nondegenerate binary principal-surrogate witness with \(\theta_R<0\). Gap: \citet{YinLiuGengLuo2019} give optimal exclusion criteria for average surrogate paradoxes, while this is a constructive inclusion frontier for a named principal stratum. Consumer: surrogate-paradox risk diagnostics.
  \item Conjecture 2: the common-responder frontier is strictly sharper than the pairwise armwise bound on an open set of binary tables. Gap: \citet{KurokiCai2013} and \citet{VanderWeele2013} motivate binary surrogate partial identification, but do not isolate the common-stratum compatibility facet. Consumer: studies using binary clinical surrogates under principal stratification.
\end{itemize}

\section{Related work}
\citet{FrangakisRubin2002} introduce principal stratification, which legitimizes conditioning on the latent response type \(G=(S(0),S(1))\). \citet{ChenGengJia2007} define the surrogate paradox and causal necessity/sufficiency criteria at an average endpoint level. \citet{GilbertHudgens2008} study causal effect predictiveness for principal surrogate endpoints, but their surface is not a binary sign-reversal phase diagram. \citet{VanderWeele2013} gives sufficient conditions for consistent surrogates and emphasizes that positive surrogate relationships alone do not rule out harmful treatment effects on the outcome. \citet{KurokiCai2013} frames surrogate-endpoint use as a sharp-bound problem, which is the closest published partial-identification ancestor for this proposal. \citet{YinLiuGengLuo2019} give optimal observed-data criteria to exclude the surrogate paradox; the present question is the constructive complement inside one named principal stratum. \citet{MaYinLiuGeng2021} show that individual or stratum-level paradoxes can survive average surrogate criteria, motivating the responder-stratum target. \citet{DingLu2017} review identification and sensitivity analysis in principal stratification, including monotonicity and principal-score restrictions that calibrate the assumptions here.

Within CausalSmith, `doc/API.md' records only a general ExactID/PartialID catalogue slot and a Manski nonparametric-bounds entry, so the current qid is not a duplicate of a registered surrogate theorem. The failed `pid_long_term_surrogate_v1' angle studied noisy long-term surrogate sign ambiguity and was rejected when its phase diagram collapsed to prevalence-interval algebra. The rejected angle0 file for this qid derived responder mixture intervals and then conjectured an average-versus-responder frontier. The accepted candidate `pid_ordinal_principal_strata_v1' is adjacent because it uses shared principal-stratum coordinates to create compatibility facets, but it is ordinal \(K\ge3\) and principal-score based rather than a binary surrogate-paradox frontier. The downgraded `pid_collider_bias_sharp_v1' shows how finite principal-strata endpoint tables can carry thresholds, but its target is collider/selection bias rather than surrogate validation.

\section{Formal setup}
Let \(Z\in\{0,1\}\) be randomized. Potential outcomes are \(S(0),S(1),Y(0),Y(1)\in\{0,1\}\), and the observed table in arm \(z\) is
\[
  p_z(s,y)=\Pr(S(z)=s,Y(z)=y).
\]
Write \(p_z=\Pr(S(z)=1)\), \(a=\Pr(S(0)=0,Y(0)=1)\), and \(b=\Pr(S(1)=1,Y(1)=1)\). Under monotonicity \(S(1)\ge S(0)\), the principal strata are \(N=(0,0)\), \(R=(0,1)\), and \(A=(1,1)\). Their masses satisfy
\[
  r=\Pr(G=R)\in I_R(P_{\mathrm{obs}}):=[p_1-p_0,\min\{p_1,1-p_0\}],
  \quad n=1-p_0-r,\quad a_G=p_1-r .
\]
For a fixed admissible \(r>0\), the feasible responder means are
\[
  \mu_{0R}\in[\underline\mu_{0R}(r),\overline\mu_{0R}(r)]
  =
  \left[
  \max\left\{0,\frac{a-n}{r}\right\},
  \min\left\{1,\frac{a}{r}\right\}
  \right],
\]
and
\[
  \mu_{1R}\in[\underline\mu_{1R}(r),\overline\mu_{1R}(r)]
  =
  \left[
  \max\left\{0,\frac{b-a_G}{r}\right\},
  \min\left\{1,\frac{b}{r}\right\}
  \right].
\]
The identified set for the responder effect is
\[
  \Theta_R(P_{\mathrm{obs}})
  =
  \bigcup_{r\in I_R(P_{\mathrm{obs}})}
  [\underline\mu_{1R}(r)-\overline\mu_{0R}(r),
   \overline\mu_{1R}(r)-\underline\mu_{0R}(r)].
\]
The common-responder compatibility frontier is
\[
  \Phi_{\mathrm{cf}}(P_{\mathrm{obs}})
  =
  \sup_{r\in I_R(P_{\mathrm{obs}})}
  \{\overline\mu_{0R}(r)-\underline\mu_{1R}(r)\}.
\]
The pairwise benchmark \(\Phi_{\mathrm{pair}}\) replaces the same \(r\) in the two endpoint maps by separately chosen \(r_0,r_1\in I_R(P_{\mathrm{obs}})\).

\begin{verbatim}
Locked parameters:
(qid, specialization, P, theta, R, Phi)
=(pid_surrogate_paradox_phase, v1, P_obs, theta_R, R_bin, Phi_cf).
P_obs={p_z(s,y): z,s,y in {0,1}}.
theta_R=E[Y(1)-Y(0) | S(0)=0,S(1)=1].
R_bin=randomization/consistency, binary support, S(1)>=S(0), interior cells.
Phi_cf(P_obs)=sup_{r in I_R(P_obs)} {overline_mu_0R(r)-underline_mu_1R(r)}.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Randomization and consistency]\label{ass:rand-cons}
The assignment \(Z\) is independent of \((S(0),S(1),Y(0),Y(1))\), and the observed variables satisfy \(S=S(Z)\) and \(Y=Y(Z)\).
\end{assumption}

\begin{assumption}[Binary support]\label{ass:binary}
The variables \(Z,S(0),S(1),Y(0),Y(1)\) take values in \(\{0,1\}\).
\end{assumption}

\begin{assumption}[Monotone surrogate response]\label{ass:monotone}
\(\Pr\{S(1)\ge S(0)\}=1\), and the responder mass \(r=\Pr\{S(0)=0,S(1)=1\}\) is positive.
\end{assumption}

\begin{assumption}[Interior observed cells]\label{ass:interior}
The observable law has \(0<p_0<p_1<1\), \(0<a<1-p_0\), and \(0<b<p_1\). The interval \(I_R(P_{\mathrm{obs}})\) has positive length.
\end{assumption}

\begin{assumption}[Observable surrogate concordance]\label{ass:concordance}
The observed surrogate contrast is positive, \(p_1-p_0>0\). When armwise surrogate-outcome concordance is invoked, it means \(\E[Y\mid Z=z,S=1]>\E[Y\mid Z=z,S=0]\) for \(z=0,1\).
\end{assumption}

\begin{assumption}[Open-cell strictness]\label{ass:open-cell}
There is an \(r^\star\) in the relative interior of \(I_R(P_{\mathrm{obs}})\) such that all four mixture components used to attain \(\overline\mu_{0R}(r^\star)\) and \(\underline\mu_{1R}(r^\star)\) lie strictly between zero and their stratum masses.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: common responder compatibility interval]\label{thm:compat-interval}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:monotone}, the responder mass \(r\) is feasible if and only if
\[
  r\in I_R(P_{\mathrm{obs}})=[p_1-p_0,\min\{p_1,1-p_0\}].
\]
For every such \(r\), the displayed intervals in Section 6 are the sharp feasible sets for \(\mu_{0R}\) and \(\mu_{1R}\), conditional on that same \(r\).
\end{theorem}
The proof solves the two binary mixture equations in the \(S(0)=0\) and \(S(1)=1\) observed cells. Sharpness follows by assigning the residual outcome-one mass to \(N\) and \(A\), respectively, and then coupling \(Y(0)\) and \(Y(1)\) within \(R\) arbitrarily.

\begin{conjecture}[Conjecture 1: common-facet phase frontier (NOT YET PROVED)]\label{conj:phase-frontier}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:interior}, the following are equivalent:
\[
  \Phi_{\mathrm{cf}}(P_{\mathrm{obs}})>0
  \quad\Longleftrightarrow\quad
  \exists\ \text{a finite binary principal-strata law inducing }P_{\mathrm{obs}}
  \text{ with }\theta_R<0 .
\]
Moreover, if Assumption~\ref{ass:concordance} holds, the equivalence remains valid after restricting to laws with positive observed surrogate contrast and positive armwise surrogate-outcome concordance.
\end{conjecture}

\begin{conjecture}[Conjecture 2: strict separation from pairwise bounds (NOT YET PROVED)]\label{conj:pairwise-strict}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:open-cell}, there is a relatively open set of binary observable tables for which
\[
  \Phi_{\mathrm{cf}}(P_{\mathrm{obs}})<\Phi_{\mathrm{pair}}(P_{\mathrm{obs}}).
\]
On this set, the pairwise benchmark admits a negative-responder sign certificate that no single common responder mass \(r\) can paste into a joint principal-strata law.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[No hidden paradox when the common frontier is nonpositive]\label{cor:no-paradox}
Under Assumptions~\ref{ass:rand-cons}--\ref{ass:interior}, Conjecture~\ref{conj:phase-frontier} implies that \(\Phi_{\mathrm{cf}}(P_{\mathrm{obs}})\le0\) rules out \(\theta_R<0\) for every binary monotone principal-strata law inducing \(P_{\mathrm{obs}}\). This collapses to the finite-cell Frangakis--Rubin responder comparison because the union in \(\Theta_R(P_{\mathrm{obs}})\) contains no interval with a negative endpoint.
\end{corollary}

\begin{example}[Exhibit 9.1: computed common-facet witness]\label{ex:computed-witness}
Let \(p_0=0.40\), \(p_1=0.70\), \(a=\Pr(S(0)=0,Y(0)=1)=0.30\), and \(b=\Pr(S(1)=1,Y(1)=1)=0.25\). Then
\[
  I_R=[0.30,0.60].
\]
At the common responder mass \(r=0.50\), the residual masses are \(n=0.10\) and \(a_G=0.20\). The endpoint maps give
\[
  \overline\mu_{0R}(0.50)=\min\{1,0.30/0.50\}=0.60,
  \qquad
  \underline\mu_{1R}(0.50)=\max\{0,(0.25-0.20)/0.50\}=0.10.
\]
Thus \(\Phi_{\mathrm{cf}}(P_{\mathrm{obs}})\ge0.50\), and the endpoint law has \(\theta_R=0.10-0.60=-0.50\). One valid set of observed tables is
\[
\begin{array}{c|cccc}
z & p_z(0,0)&p_z(0,1)&p_z(1,0)&p_z(1,1)\\
\hline
0&0.30&0.30&0.20&0.20\\
1&0.20&0.10&0.45&0.25
\end{array}
\]
with \(\E[Y\mid Z=0,S=1]=0.50>\E[Y\mid Z=0,S=0]=0.50\) replaced by the nearby perturbation \(p_0(1,1)=0.21,p_0(1,0)=0.19,p_0(0,1)=0.29,p_0(0,0)=0.31\) to satisfy strict concordance without changing the sign of \(\Phi_{\mathrm{cf}}\). The construction uses three principal strata \(N,R,A\), positive masses \(0.10,0.50,0.20\) plus an unused \(S\)-defier mass zero under monotonicity, and no denominator is zero.
\end{example}

\begin{example}[Exhibit 9.2: pairwise overstatement target]\label{ex:pairwise}
Keep \(p_0=0.40\) and \(p_1=0.70\), but choose \(a=0.18\) and \(b=0.38\). Pairwise calculations can use \(r_0=0.30\) to make \(\overline\mu_{0R}(r_0)=0.60\) and \(r_1=0.60\) to make \(\underline\mu_{1R}(r_1)=0\). The common calculation cannot use both values of \(r\) in one principal-strata law; Conjecture~\ref{conj:pairwise-strict} asks for the exact open-cell inequalities under which this mismatch is a strict compatibility facet rather than a normalization artifact.
\end{example}

\section{Proof-sketch route}
For Theorem~\ref{thm:compat-interval}, the route is finite mixture algebra: \(P(S(0)=1)=p_0\) and \(P(S(1)=1)=p_1\) give \(r\in I_R\); the two observed outcome-one equations are split across \((N,R)\) and \((R,A)\); Frechet bounds give the endpoint formulas. For Conjecture~\ref{conj:phase-frontier}, the chain is
\[
\text{headline}
\leftarrow \text{unfold Section 6 definitions}
\leftarrow \text{substitute Assumptions 1--4}
\leftarrow \text{Step 1: eliminate }(n,a_G)\text{ using the common }r
\leftarrow \text{Step 2: prove endpoint attainability by a joint }(Y(0),Y(1))\text{ coupling in }R
\leftarrow \text{Step 3: show strict positivity of }\Phi_{\mathrm{cf}}\text{ is equivalent to a negative endpoint of }\Theta_R
\leftarrow \text{Step 4: verify concordance-preserving perturbations keep the active face}
\leftarrow \text{finite-dimensional polytope projection}.
\]
For Conjecture~\ref{conj:pairwise-strict}, the chain is
\[
\text{headline}
\leftarrow \text{unfold }\Phi_{\mathrm{pair}}\text{ and }\Phi_{\mathrm{cf}}
\leftarrow \text{substitute Assumption 6}
\leftarrow \text{Step 1: identify active pairwise endpoints with }r_0\ne r_1
\leftarrow \text{Step 2: derive the common-}r\text{ facet from the shared stratum mass}
\leftarrow \text{Step 3: prove the strict gap survives an open perturbation}
\leftarrow \text{Step 4: construct endpoint-attaining binary tables}
\leftarrow \text{polyhedral stability of exposed faces}.
\]
The substantive step count is \(k=4\) for each conjecture.

\section{Honest scope flags}
Theorem~\ref{thm:compat-interval} is routine binary mixture algebra and is included only to lock the convention. Conjecture~\ref{conj:phase-frontier} is the main open statement; the proof must still verify the if-and-only-if direction with concordance-preserving perturbations. Conjecture~\ref{conj:pairwise-strict} is also open; Exhibit~\ref{ex:pairwise} gives the intended separation mechanism but not the final closed-form open-cell inequalities. The prior angle's average-exclusion frontier is withdrawn for this pivot and is not used as a comparator claim.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
  \item v1 (pivot) -- initial draft for a common-responder compatibility-facet angle; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chen, Geng, and Jia(2007)]{ChenGengJia2007}
Chen, H., Geng, Z., and Jia, J. (2007).
Criteria for surrogate end points.
\emph{Journal of the Royal Statistical Society: Series B}, 69, 919--932.

\bibitem[Ding and Lu(2017)]{DingLu2017}
Ding, P. and Lu, J. (2017).
Principal stratification analysis using principal scores.
\emph{Journal of the Royal Statistical Society: Series B}, 79, 757--777.

\bibitem[Frangakis and Rubin(2002)]{FrangakisRubin2002}
Frangakis, C. E. and Rubin, D. B. (2002).
Principal stratification in causal inference.
\emph{Biometrics}, 58, 21--29.

\bibitem[Gilbert and Hudgens(2008)]{GilbertHudgens2008}
Gilbert, P. B. and Hudgens, M. G. (2008).
Evaluating candidate principal surrogate endpoints.
\emph{Biometrics}, 64, 1146--1154.

\bibitem[Kuroki and Cai(2013)]{KurokiCai2013}
Kuroki, M. and Cai, Z. (2013).
Sharp bounds on causal effects using a surrogate endpoint.
\emph{Statistics in Medicine}, 32, 4338--4347.

\bibitem[Ma et~al.(2021)]{MaYinLiuGeng2021}
Ma, C., Yin, Y., Liu, L., and Geng, Z. (2021).
On the individual surrogate paradox.
\emph{Biostatistics}, 22, 97--114.

\bibitem[VanderWeele(2013)]{VanderWeele2013}
VanderWeele, T. J. (2013).
Surrogate measures and consistent surrogates.
\emph{Biometrics}, 69, 561--569.

\bibitem[Yin et~al.(2019)]{YinLiuGengLuo2019}
Yin, Y., Liu, L., Geng, Z., and Luo, P. (2019).
Novel criteria to exclude the surrogate paradox and their optimalities.
\emph{Scandinavian Journal of Statistics}, 46, 778--799.
\end{thebibliography}

\end{document}
