% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_overlap\_tail\_phase, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_overlap\_tail\_phase} / \texttt{v1}%
  \\ \large\textit{Two-tail overlap profiles and endpoint certificates for sharp partial-ID width}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\texttt{(qid, specialization, observable distribution P, parameter theta, identifying restrictions, bounding functional)}
is locked as follows. The qid is \texttt{pid\_overlap\_tail\_phase} and the specialization is
\texttt{v1}. The observable law \(P\) is the joint law of \(O=(Y,D,X)\), where
\(D\in\{0,1\}\), \(X\in[0,1]\), \(e(x)=P(D=1\mid X=x)\), and \(Y=D Y(1)+(1-D)Y(0)\).
The parameter is the weak-overlap full-population contribution
\[
\theta_\varepsilon(P)=E[(Y(1)-Y(0))\mathbf 1\{X\in T_\varepsilon\}],\qquad
T_\varepsilon=\{x:e(x)\leq \varepsilon\}\cup\{x:1-e(x)\leq \varepsilon\},
\]
with CATT and ATT obtained by replacing \(P_X\) by the treated covariate law and using
the one-sided untreated tail \(T_\varepsilon^1\). The identifying restrictions are consistency, conditional
unconfoundedness on overlap cells, bounded potential outcomes \(Y(d)\in[-B,B]\), and no
restriction on the missing potential-outcome regression on cells whose treatment arm is
absent at the \(\varepsilon\)-profile. The bounding functional is the sharp interval
\(\Theta_\varepsilon(P)\) induced by all full-data laws compatible with \(P\) and these
restrictions, its width \(W_\varepsilon(P)=\operatorname{diam}\Theta_\varepsilon(P)\), and
the normalized overlap-tail amplification
\[
A_\varepsilon(P)=W_\varepsilon(P)/\varepsilon .
\]
The focal object is the two-tail exponent profile
\(\alpha(P)=(\alpha_0(P),\alpha_1(P))\), where
\(P\{e(X)\leq t\}\asymp t^{\alpha_0(P)}\) and
\(P\{1-e(X)\leq t\}\asymp t^{\alpha_1(P)}\) as \(t\downarrow0\).

\begin{abstract}
Limited overlap is usually handled by changing the estimand, trimming the sample, or
reporting worst-case bounds on non-overlap cells. This note asks whether two laws with the
same nominal overlap support and the same coarse non-overlap input can have different
sharp partial-identification profiles because their propensity-score tails have different
polynomial exponents. The central conjecture states that the normalized sharp width
\(A_\varepsilon(P)\) admits an exact exponent frontier and that this frontier is not
recoverable from the mass-only inputs used by non-overlap bounds. The witness is a
two-tail family with bounded outcomes whose endpoint-attaining completions produce
finite, polynomial, and vacuous first-order regimes. If correct, the result separates
tail-profile partial identification from estimator-rate limited-overlap theory and from
partial-ID bounds that depend only on a reported non-overlap mass.
\end{abstract}

\section{Introduction}
Overlap failure can occur without a visible support gap: the propensity score can be
positive on the same support while one arm vanishes polynomially fast in a tail. The main
claim is that the sharp width of the weak-overlap contribution is governed by a tail
exponent, not only by the presence or absence of common support.

\citet[p.~2021]{KhanTamer2010IrregularIdentification} connect inverse-weight estimability
to tail conditions, and \citet[Abstract, pp.~1--2]{LeeWeidner2026LimitedPoolingBounds}
give ATE/ATT bounds under violated overlap by limiting pooling. \citet[Sec.~2]{SusmannMcCleanDiaz2025NonOverlapATEBounds}
write bounded-outcome non-overlap bounds as an overlap estimand plus worst-case
non-overlap mass. The gap here is an exponent-indexed sharp-width frontier that separates
laws with the same comparator-level support and mass summaries. The theorem lives in
partial identification with bounded outcomes.

The direct consumers are bounded-outcome non-overlap ATE reporting in
\citet{SusmannMcCleanDiaz2025NonOverlapATEBounds} and limited-pooling sensitivity
analysis in \citet{LeeWeidner2026LimitedPoolingBounds}. A reader would report the
overlap-tail exponent together with the mass bound, because the mass bound alone can hide
different first-order identification costs as the reporting threshold changes.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the sharp weak-overlap contribution width is \(2B\{P(T_\varepsilon^0)+P(T_\varepsilon^1)\}\), with the intersection counted twice. Gap: \citet{Manski1990NonparametricBounds} gives the no-assumption benchmark but not the propensity-tail profile. Consumer: \citet{SusmannMcCleanDiaz2025NonOverlapATEBounds}.
\item Conjecture 1: the overlap-tail profile \(\alpha(P)\) is a strict comparator frontier: two laws can share nominal support and a coarse non-overlap mass report while \(A_\varepsilon(P)\) lies in different finite, polynomial, and vacuous regimes. Gap: \citet{LeeWeidner2026LimitedPoolingBounds} and \citet{SusmannMcCleanDiaz2025NonOverlapATEBounds} use pooling or mass summaries, not an exponent certificate. Consumer: non-overlap ATE reporting in \citet{SusmannMcCleanDiaz2025NonOverlapATEBounds}.
\item Conjecture 2: CATT/ATT use only the untreated treated-population tail, while ATE uses the sum of the two full-population tails. Gap: \citet{HongLeungLi2020FinitePopulationLimitedOverlap} and \citet{Rothe2017LimitedOverlapCI} tie overlap to effective sample size and inference, not one-sided sharp widths. Consumer: limited-overlap ATT sensitivity in \citet{LeeWeidner2026LimitedPoolingBounds}.
\end{itemize}

\section{Related work}
\citet[pp.~319--320]{Manski1990NonparametricBounds} is the bounded-outcome benchmark:
missing potential outcomes contribute worst-case intervals when no identifying restriction
links the missing cell to observed outcomes. \citet{ImbensManski2004ConfidenceIntervals} gives inference for
interval-identified parameters and fixes the interpretation of an identified interval as
the target object. \citet[p.~2021 and Sec.~2]{KhanTamer2010IrregularIdentification} is the closest tail
anchor because arbitrarily large inverse weights make point-identified parameters
irregular and tail-dependent. \citet[Sec.~2]{Rothe2017LimitedOverlapCI} develops robust
confidence intervals when overlap is limited; the present object is the identified set,
not sampling uncertainty around a point estimand. \citet[Sec.~2]{HongLeungLi2020FinitePopulationLimitedOverlap}
formalize degenerating finite-population overlap through propensity scores approaching
zero or one; the profile here is superpopulation partial identification. \citet[Sec.~3]{HeilerKazak2021ExtremePropensity}
derive non-Gaussian limits for IPW and doubly robust estimators with many extreme
propensity scores; the present conjecture separates those estimator limits from the
sharp-width exponent. \citet{CrumpHotzImbensMitnik2009Trimming} and
\citet{LiMorganZaslavsky2018OverlapWeights} are the main estimand-change responses to
limited overlap, which this note treats as comparators rather than solutions.
\citet[Abstract and Sec.~2]{LeeWeidner2026LimitedPoolingBounds} construct ATE/ATT bounds by limiting pooling
across observations under overlap violation; the proposed certificate varies tail
exponents while keeping nominal support fixed. \citet[Sec.~2]{SusmannMcCleanDiaz2025NonOverlapATEBounds}
give bounded-outcome ATE bounds whose width is driven by non-overlap mass; the proposed
profile distinguishes laws with the same support description but different polynomial tail
mass. In the CausalSmith catalogue, `doc/API.md` Section 3.1
`ManskiNonparametricBounds_Study` records bounded-outcome Manski-style treatment-effect
bounds; it has no overlap-tail exponent, endpoint sequence, or one-sided CATT/ATT phase
statement. The prior CausalSmith bank entry `pid_critical_overlap_exponent/v1` failed
before mathematical review and left no theorem or witness; the rejected
`pid_heavy_tail_cate_bounds/v1` warns that endpoint claims must exhibit a concrete
non-corner law and must not confuse finite truncation with an infinite endpoint.

\section{Formal setup}
Let \(O=(Y,D,X)\sim P\), with \(D\in\{0,1\}\), \(X\in[0,1]\), and
\(Y=D Y(1)+(1-D)Y(0)\). Write \(e(x)=P(D=1\mid X=x)\),
\(m_d(x)=E[Y\mid D=d,X=x]\) on cells where \(P(D=d\mid X=x)>0\), and
\(q_\varepsilon^0=P\{X\in T_\varepsilon^0\}\),
\(q_\varepsilon^1=P\{X\in T_\varepsilon^1\}\), where
\[
T_\varepsilon^0=\{x:e(x)\leq\varepsilon\},\qquad
T_\varepsilon^1=\{x:1-e(x)\leq\varepsilon\},\qquad
T_\varepsilon=T_\varepsilon^0\cup T_\varepsilon^1 .
\]
The full-data completion class \(\mathcal F_\varepsilon(P)\) contains all laws of
\((Y(0),Y(1),D,X)\) that reproduce \(P\), satisfy the assumptions in Section 7, and allow
the counterfactual regression for arm \(d\) to vary freely on \(T_\varepsilon^d\) within
\([-B,B]\). The weak-overlap profile identified set is
\[
\Theta_\varepsilon(P)=\{\theta_\varepsilon(F):F\in\mathcal F_\varepsilon(P)\},
\quad
W_\varepsilon(P)=\sup\Theta_\varepsilon(P)-\inf\Theta_\varepsilon(P),
\quad
A_\varepsilon(P)=W_\varepsilon(P)/\varepsilon .
\]
The coarse comparator report is
\[
C_{\varepsilon_0}(P)=\bigl(\operatorname{supp}(X),P(T_{\varepsilon_0}^0),
P(T_{\varepsilon_0}^1),B\bigr)
\]
at a fixed reporting threshold \(\varepsilon_0\in(0,1/2)\). It records the support and
the two weak-overlap masses at the reporting threshold but not how these masses change
as the threshold moves toward zero.
For CATT/ATT, replace \(P_X\) in all tail masses by \(P_{X\mid D=1}\) and use the
one-sided target \(E[(Y(1)-Y(0))\mathbf 1\{X\in T_\varepsilon^1\}\mid D=1]\). For ATE,
use both tails under \(P_X\).

\begin{quote}\small
\texttt{(qid, specialization, observable distribution P, parameter theta, identifying restrictions, bounding functional)}
is locked as follows. The qid is \texttt{pid\_overlap\_tail\_phase} and the specialization is
\texttt{v1}. The observable law \(P\) is the joint law of \(O=(Y,D,X)\), where
\(D\in\{0,1\}\), \(X\in[0,1]\), \(e(x)=P(D=1\mid X=x)\), and \(Y=D Y(1)+(1-D)Y(0)\).
The parameter is the weak-overlap full-population contribution
\[
\theta_\varepsilon(P)=E[(Y(1)-Y(0))\mathbf 1\{X\in T_\varepsilon\}],\qquad
T_\varepsilon=\{x:e(x)\leq \varepsilon\}\cup\{x:1-e(x)\leq \varepsilon\},
\]
with CATT and ATT obtained by replacing \(P_X\) by the treated covariate law and using
the one-sided untreated tail \(T_\varepsilon^1\). The identifying restrictions are consistency, conditional
unconfoundedness on overlap cells, bounded potential outcomes \(Y(d)\in[-B,B]\), and no
restriction on the missing potential-outcome regression on cells whose treatment arm is
absent at the \(\varepsilon\)-profile. The bounding functional is the sharp interval
\(\Theta_\varepsilon(P)\) induced by all full-data laws compatible with \(P\) and these
restrictions, its width \(W_\varepsilon(P)=\operatorname{diam}\Theta_\varepsilon(P)\), and
the normalized overlap-tail amplification
\[
A_\varepsilon(P)=W_\varepsilon(P)/\varepsilon .
\]
The focal object is the two-tail exponent profile
\(\alpha(P)=(\alpha_0(P),\alpha_1(P))\), where
\(P\{e(X)\leq t\}\asymp t^{\alpha_0(P)}\) and
\(P\{1-e(X)\leq t\}\asymp t^{\alpha_1(P)}\) as \(t\downarrow0\).
\end{quote}

\section{Assumptions}
\begin{assumption}[Consistency]\label{ass:consistency}
\(Y=D Y(1)+(1-D)Y(0)\) almost surely.
\end{assumption}

\begin{assumption}[Overlap-cell unconfoundedness]\label{ass:unconf}
For every \(x\) with \(0<e(x)<1\), \((Y(0),Y(1))\perp D\mid X=x\).
\end{assumption}

\begin{assumption}[Bounded outcomes]\label{ass:bounded}
There is a known \(B<\infty\) such that \(Y(0),Y(1)\in[-B,B]\) almost surely.
\end{assumption}

\begin{assumption}[Profile completion]\label{ass:completion}
For each \(\varepsilon>0\), the unobserved arm-\(d\) regression on
\(T_\varepsilon^d\) is restricted only by Assumption \ref{ass:bounded}; outside
\(T_\varepsilon^d\), it agrees with the observed overlap-cell regression \(m_d(x)\).
\end{assumption}

\begin{assumption}[Regular two-tail variation]\label{ass:regularvariation}
There are constants \(c_0,c_1\in(0,\infty)\) and exponents
\(\alpha_0,\alpha_1\in(0,\infty]\) such that, as \(t\downarrow0\),
\[
P\{e(X)\leq t\}=c_0 t^{\alpha_0}+o(t^{\alpha_0}),\qquad
P\{1-e(X)\leq t\}=c_1 t^{\alpha_1}+o(t^{\alpha_1}),
\]
with the convention \(t^\infty=0\) for a tail that is eventually empty.
\end{assumption}

\begin{assumption}[Non-corner witness admissibility]\label{ass:witness}
The witness family has \(P(0<e(X)<1)=1\), positive mass in both treatment arms for
every open subinterval of \((0,1)\), and \(B>0\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: profile sharp-width formula]\label{thm:profile-width}
Under Assumptions \ref{ass:consistency}--\ref{ass:completion}, the ATE contribution width is
\[
W_\varepsilon^{ATE}(P)=2B\{P(T_\varepsilon^0)+P(T_\varepsilon^1)\}
  =2B\,P(T_\varepsilon^0\triangle T_\varepsilon^1)
    +4B\,P(T_\varepsilon^0\cap T_\varepsilon^1).
\]
For the CATT/ATT contribution,
\[
W_\varepsilon^{ATT}(P)=2B\,P(X\in T_\varepsilon^1\mid D=1).
\]
\end{theorem}
The proof is the standard bounded-outcome completion argument: set each missing arm mean
equal to \(B\) for the upper endpoint and \(-B\) for the lower endpoint on its profile
cell, then integrate the endpoint gap. On \(T_\varepsilon^0\cap T_\varepsilon^1\), both
potential-outcome regressions are free, so the treatment-effect range has width \(4B\).

\begin{conjecture}[Conjecture 1: strict overlap-tail frontier (NOT YET PROVED)]\label{conj:two-tail-phase}
Under Assumptions \ref{ass:consistency}--\ref{ass:witness}, let
\(\bar\alpha(P)=\min\{\alpha_0(P),\alpha_1(P)\}\). For each
\(\varepsilon_0\in(0,1/2)\) and each pair
\((a,b)\neq(a',b')\) with \(\min(a,b)\neq\min(a',b')\), there are endpoint-attaining
two-tail laws \(P_{a,b}\) and \(P_{a',b'}\) with
\[
C_{\varepsilon_0}(P_{a,b})=C_{\varepsilon_0}(P_{a',b'})
\quad\text{and}\quad
P_{a,b}\{0<e(X)<1\}=P_{a',b'}\{0<e(X)<1\}=1,
\]
but
\[
A_\varepsilon^{ATE}(P)\asymp \varepsilon^{\bar\alpha(P)-1}.
\]
Thus \(A_\varepsilon^{ATE}(P)\to0\) when \(\bar\alpha(P)>1\), remains finite and nonzero
when \(\bar\alpha(P)=1\), and diverges polynomially when \(\bar\alpha(P)<1\). The
endpoint sequence with missing-arm means \(\pm B\) attains the sharp lower and upper
limits in each regime, so \(\alpha(P)\) is not recoverable from the mass-only comparator
report \(C_{\varepsilon_0}(P)\).
\end{conjecture}

\begin{conjecture}[Conjecture 2: one-tail CATT/ATT separation (NOT YET PROVED)]\label{conj:one-tail-separation}
Under Assumptions \ref{ass:consistency}--\ref{ass:witness}, the treated-population
weak-overlap contribution satisfies
\[
W_\varepsilon^{ATT}(P)\asymp \varepsilon^{\alpha_1(P)}
\quad\text{and}\quad
W_\varepsilon^{ATT}(P)/\varepsilon\asymp
\varepsilon^{\alpha_1(P)-1}.
\]
The untreated tail exponent \(\alpha_0(P)\) affects the ATE profile but not this CATT/ATT
contribution except through normalization by the treated population. Hence a one-tail
ATT report can be finite while the two-tail ATE profile is polynomially divergent.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Manski corner]\label{cor:manski-corner}
Under Assumptions \ref{ass:consistency}--\ref{ass:completion}, if
\(T_\varepsilon^0=T_\varepsilon^1=[0,1]\), then the ATE contribution interval has width \(4B\). This collapses
to the bounded-outcome no-information benchmark because every counterfactual regression
can be moved independently over \([-B,B]\), so \(Y(1)-Y(0)\in[-2B,2B]\).
\end{corollary}

\begin{corollary}[Disjoint-tail corner]\label{cor:disjoint-tail}
Under Assumptions \ref{ass:consistency}--\ref{ass:completion}, if
\(\varepsilon<1/2\), then \(T_\varepsilon^0\cap T_\varepsilon^1=\varnothing\) and
\(W_\varepsilon^{ATE}(P)=2B\,P(T_\varepsilon^0\cup T_\varepsilon^1)\). This is the
formula used by mass-only non-overlap summaries when the two missing arms cannot occur
in the same covariate cell.
\end{corollary}

\paragraph{Exhibit 9.1: two-tail exponent witness.}
Fix \(\varepsilon_0\in(0,1/2)\), \(r_0,s_0\in(0,1/4)\), let
\(X\sim \mathrm{Unif}(0,1)\), \(B=1\), and for \(a,b>0\) define
\[
e_{a,b}(x)=
\begin{cases}
\varepsilon_0(x/r_0)^{1/a}, & 0\leq x\leq r_0,\\
1/2, & r_0<x<1-s_0,\\
1-\varepsilon_0((1-x)/s_0)^{1/b}, & 1-s_0\leq x\leq 1.
\end{cases}
\]
Then \(P\{e_{a,b}(X)\leq t\}=r_0(t/\varepsilon_0)^a\) and
\(P\{1-e_{a,b}(X)\leq t\}=s_0(t/\varepsilon_0)^b\) for
\(0<t\leq\varepsilon_0\), while \(P\{e_{a,b}(X)\leq\varepsilon_0\}=r_0\),
\(P\{1-e_{a,b}(X)\leq\varepsilon_0\}=s_0\), and \(0<e_{a,b}(X)<1\) almost surely for
every \(a,b\). Thus all pairs \((a,b)\) share the same comparator report
\(C_{\varepsilon_0}(P)=( [0,1],r_0,s_0,1)\). The endpoint completion sets the
missing \(Y(1)\) mean on \(T_\varepsilon^0\) to \(1\) or \(-1\), and the missing \(Y(0)\)
mean on \(T_\varepsilon^1\) to \(-1\) or \(1\); the two endpoints differ by
\[
W_\varepsilon^{ATE}(P_{a,b})
=2\{r_0(\varepsilon/\varepsilon_0)^a+s_0(\varepsilon/\varepsilon_0)^b\}
\]
for the full-population tail contribution when \(0<\varepsilon\leq\varepsilon_0\). Hence
\(W_\varepsilon^{ATE}(P_{a,b})/\varepsilon
\asymp \varepsilon^{\min(a,b)-1}\). The system is not over-determined: the two missing
arm regressions are distinct functions, both remain in \([-1,1]\), and all denominators
are positive for \(\varepsilon>0\).

\section{Proof-sketch route}
The proof route for Conjecture 1 is:
headline \(\leftarrow\) unfold Section 6 definitions \(\leftarrow\) substitute
Assumptions \ref{ass:bounded}--\ref{ass:regularvariation} \(\leftarrow\)
derive the sharp missing-arm support function over \(T_\varepsilon^0\) and
\(T_\varepsilon^1\) \(\leftarrow\) prove that the two-tail completion is endpoint
attaining and not only endpoint approaching \(\leftarrow\) construct the rescaled
two-tail family that fixes \(C_{\varepsilon_0}(P)\) while varying \((a,b)\)
\(\leftarrow\) compute the two endpoint support functions on that family
\(\leftarrow\) compare two distinct pairs \((a,b)\) and \((a',b')\) with the same
comparator report \(\leftarrow\) derive the finite, polynomial, and vacuous regimes from
the strict ordering of \(\min(a,b)\). The substantive step count is \(k=5\):
two-arm support-function sharpness, endpoint compatibility, comparator-preserving
rescaling, pairwise non-representability by \(C_{\varepsilon_0}\), and phase
classification. The proof route for Conjecture 2 changes the base measure to
\(P_{X\mid D=1}\), computes
\(P(X\in T_\varepsilon^1\mid D=1)=E[e(X)\mathbf 1\{1-e(X)\leq\varepsilon\}]/P(D=1)\),
uses the same endpoint support function only on the missing \(Y(0)\) arm, and then
constructs a pair of laws with equal \(C_{\varepsilon_0}\) but different treated-tail
exponents; this has \(k=4\).

\section{Honest scope flags}
Theorem 1 is a bounded-outcome sharpness calculation and should be treated as routine.
Conjectures 1 and 2 are the novel claims and are not yet proved. The proposal deliberately
uses the full-population contribution \(W_\varepsilon\) for the phase statement; the
conditional tail target has bounded width \(2B\), so claiming polynomial blow-up for that
unnormalized conditional width would be false. The endpoint certificate may need to
be weakened from endpoint-attaining to endpoint-approaching if the profile completion
class is later required to impose continuity of the full-data regression at the tail
boundary.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the two-tail endpoint-certificate angle; prior verdict: none.
\item v2 (revise) -- corrected the ATE intersection width and Manski corner, added location-level literature anchors, and reframed Conjecture 1 as a strict comparator-frontier witness with fixed \(C_{\varepsilon_0}\); prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Crump et~al.(2009)]{CrumpHotzImbensMitnik2009Trimming}
Crump, R.~K., Hotz, V.~J., Imbens, G.~W., and Mitnik, O.~A. (2009).
Dealing with limited overlap in estimation of average treatment effects.
\emph{Biometrika}, 96(1), 187--199.

\bibitem[Heiler and Kazak(2021)]{HeilerKazak2021ExtremePropensity}
Heiler, P. and Kazak, E. (2021).
Valid inference for treatment effect parameters under irregular identification and many
extreme propensity scores.
\emph{Journal of Econometrics}, 222(2), 1083--1108.

\bibitem[Hong et~al.(2020)]{HongLeungLi2020FinitePopulationLimitedOverlap}
Hong, H., Leung, M.~P., and Li, J. (2020).
Inference on finite-population treatment effects under limited overlap.
\emph{The Econometrics Journal}, 23(1), 32--47.

\bibitem[Imbens and Manski(2004)]{ImbensManski2004ConfidenceIntervals}
Imbens, G.~W. and Manski, C.~F. (2004).
Confidence intervals for partially identified parameters.
\emph{Econometrica}, 72(6), 1845--1857.

\bibitem[Khan and Tamer(2010)]{KhanTamer2010IrregularIdentification}
Khan, S. and Tamer, E. (2010).
Irregular identification, support conditions, and inverse weight estimation.
\emph{Econometrica}, 78(6), 2021--2042.

\bibitem[Lee and Weidner(2026)]{LeeWeidner2026LimitedPoolingBounds}
Lee, S. and Weidner, M. (2026).
Bounding treatment effects by pooling limited information across observations.
\emph{Journal of Econometrics}, 106254.

\bibitem[Li et~al.(2018)]{LiMorganZaslavsky2018OverlapWeights}
Li, F., Morgan, K.~L., and Zaslavsky, A.~M. (2018).
Balancing covariates via propensity score weighting.
\emph{Journal of the American Statistical Association}, 113(521), 390--400.

\bibitem[Manski(1990)]{Manski1990NonparametricBounds}
Manski, C.~F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review}, 80(2), 319--323.

\bibitem[Rothe(2017)]{Rothe2017LimitedOverlapCI}
Rothe, C. (2017).
Robust confidence intervals for average treatment effects under limited overlap.
\emph{Econometrica}, 85(2), 645--660.

\bibitem[Susmann et~al.(2025)]{SusmannMcCleanDiaz2025NonOverlapATEBounds}
Susmann, H., McClean, A., and Diaz, I. (2025).
Non-overlap average treatment effect bounds.
\emph{arXiv:2509.20206}.
\end{thebibliography}

\end{document}
