\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{pid\_cvar\_welfare\_msm\_v1} / \texttt{robust\_cvar\_policy}%
  \\ \large\textit{MSM-CVaR bounds for confounding-robust policy welfare}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This note studies partial identification of the fixed-policy tail-risk target
\(\theta(Q)=\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}\) under a marginal
sensitivity model with sensitivity parameter \(\Gamma\).  The locked
restrictions impose consistency, overlap, and an odds-ratio bound on the latent
treatment rule, but they do not impose support restrictions on nonfactual
potential outcomes and do not impose conditional exchangeability of treatment
with the potential-outcome vector.  Consequently the locked full class has no
finite upper endpoint when nonfactual potential outcomes are allowed to be
arbitrarily large: \(\sup\Theta_I(P)=+\infty\).  If an explicit
all-potential-outcome support restriction \(Y(a)\in[y_L,y_U]\) is added, the
sharp endpoint is the Manski-style support completion that keeps factual
outcomes fixed and places nonfactual policy-relevant outcomes at the relevant
support endpoint.  The joint-compatible kernel program is the sharp endpoint for
the conditionally exchangeable marginal-sensitivity subclass.  The nested
actionwise functional
\[
\inf_{\eta\in[y_L,y_U]}
\left\{
\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,X\}
\right]\right\}
\]
is a computable conservative upper bound for that conditionally exchangeable
subclass, but it is not a valid finite upper endpoint for the locked full class
and is not proved sharp for general multi-action policies because actionwise
least-favorable tilts must be jointly realizable by one latent treatment rule.
A pointwise-band comparator is conservative relative to this separated bound
once its thresholdwise envelopes are defined term-by-term.  For inference on the
separated bound, the valid one-step score requires a canonical differentiable
dual threshold for the bounded-weight linear program, the derivative of the MSM
operator with respect to the nominal propensity score, and global localization
of the data-selected CVaR threshold.
\end{abstract}

\section{Introduction}
Policy learning from observational data matters in settings where randomized
experimentation is infeasible or unethical, including clinical treatment
assignment, education, and public policy.  The difficulty is that a policy
learned under unconfoundedness can look attractive only because treatment choice
reacted to unrecorded risk.  A useful robust policy criterion therefore must
account for hidden confounding, and it must do so for the welfare object the
decision maker actually cares about.  In this note that welfare object is not
the mean policy value but the conditional value-at-risk of the policy-induced
outcome, which isolates the worst \(\tau\)-tail of the distribution.

Recent work has clarified the mean-value analogue.  Hess, Frauen, Melnychuk, and
Feuerriegel (2025) derive a sharp closed-form marginal-sensitivity bound for a
fixed policy's mean value and a semiparametrically efficient estimator.  Jin,
Xu, Zheng, and Zhou (2025) likewise study robust and efficient policy learning
under hidden confounding for mean or worst-case mean welfare.  On the
distributional side, Rockafellar and Uryasev (2000) give the variational formula
for \(\operatorname{CVaR}\), while Dorn and Guo (2021), Frauen, Melnychuk, and
Feuerriegel (2023), and Masten, Poirier, and Ren (2025) show how
marginal-sensitivity restrictions generate sharp pointwise mean, quantile, and
distributional envelopes.

The first mathematical point is that the locked marginal-sensitivity restriction
does not, by itself, connect treatment assignment to the potential-outcome vector
through the latent variable.  For any full-data law,
\[
\E_Q[\one\{A=a\}b\{Y(a)\}\mid X=x]
=
\E_Q[p_a(X,U)b\{Y(a)\}\mid X=x]
+
\E_Q[(\one\{A=a\}-p_a(X,U))b\{Y(a)\}\mid X=x],
\]
where \(p_a(X,U)=Q(A=a\mid X,U)\).  The final residual term is zero only under a
conditional-exchangeability restriction.  Without that restriction, even
\(\Gamma=1\) leaves nonfactual potential outcomes partially unidentified.
Moreover, the observed support condition \(Y\in[y_L,y_U]\) controls only the
factual outcome \(Y=Y(A)\).  It does not bound \(Y(a)\) on units with \(A\ne a\).
Thus a finite support-completion endpoint is a theorem about a support-restricted
subclass, not about the locked full class.

The second mathematical point is that, after conditional exchangeability is
imposed, a multi-action policy tail functional is still not generally sharp
merely because every actionwise generated-loss mean is sharp.  For one covariate
value \(x\), the full-data law must contain a single latent treatment-probability
vector \(p(\cdot\mid x,U)\) satisfying \(\sum_a p_a(x,U)=1\).  Equivalently, the
selected actionwise density ratios \(r_a\) cannot be chosen independently; at
the latent-unit level they must obey
\[
\sum_{a\in\mathcal A}\frac{e_a(x)}{r_a}=1.
\]

\paragraph{Motivating conjecture(s).}
\textbf{Conjecture 1: Sharp nested MSM-CVaR endpoint.} (NOT YET PROVED.)  Under
Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail}, for every fixed policy
\(\pi\),
\[
\sup_{Q\in\mathcal M_\Gamma(P)}
\operatorname{CVaR}_\tau\{Y_Q(\pi)\}
=
\inf_{\eta\in\mathcal I}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,X\}
\right]\right\}.
\]
The equality is sharp: every value above the right-hand side is valid, and no
smaller endpoint is valid over \(\mathcal M_\Gamma(P)\).

\textbf{Conjecture 2: Non-commutation gap.} (NOT YET PROVED.)  Under
Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail},
\[
\Delta_{\mathrm{nc}}(\pi;P)=
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
-\underline W_{\tau,\Gamma}(\pi;P)\geq 0.
\]
Moreover, there is a two-action, three-outcome, one-covariate-cell class
satisfying strict overlap and \(1<\Gamma<\infty\) on which
\(\Delta_{\mathrm{nc}}(\pi;P)>0\).  Equality holds when the same monotone
least-favorable MSM tilt is simultaneously optimal for all \(\eta\) in the
active subgradient set of \(\mathcal C_\eta(P,\pi)\).

\textbf{Conjecture 3: One-step limit law.} (NOT YET PROVED.)  Under
Assumptions~\ref{ass:iid-overlap}--\ref{ass:nuisance}, the estimator in
Definition~\ref{def:onestep} is asymptotically linear:
\[
\sqrt n\{\hat W_{\tau,\Gamma}(\pi)-\underline W_{\tau,\Gamma}(\pi;P)\}
=
\frac{1}{\sqrt n}\sum_{i=1}^n
\varphi_{\tau,\Gamma,\pi}(O_i)+o_p(1),
\qquad
\E[\varphi_{\tau,\Gamma,\pi}(O)]=0.
\]
The variance of \(\varphi_{\tau,\Gamma,\pi}\) is consistently estimated by the
fold-stacked empirical variance of
\(\hat\eta+\tau^{-1}\hat\phi_{\hat\eta,\pi}-\hat W_{\tau,\Gamma}(\pi)\).

\section{Related work and positioning}
The closest published comparator is Hess, Frauen, Melnychuk, and Feuerriegel
(2025), which derives sharp and efficient marginal-sensitivity bounds for the
mean value of a fixed policy; this note keeps the same observational-policy
learning arc but replaces the linear welfare functional by the nonlinear tail
functional \(\operatorname{CVaR}_{\tau}\).  Jin, Xu, Zheng, and Zhou (2025) is
another close comparator because it studies robust and efficient policy learning
under hidden confounding, but its welfare targets remain mean or worst-case mean
objects rather than a partially identified fixed-policy CVaR.  Kallus and Zhou
(2018, 2021) motivate confounding-robust policy learning through worst-case mean
regret and propensity-weight uncertainty; that line does not provide the joint
CVaR endpoint targeted here.

On the partial-identification side, Rockafellar and Uryasev (2000) supply the
one-dimensional variational representation of \(\operatorname{CVaR}\), which is
the outer layer of the present functional.  Manski (1990) is the source for the
support-completion logic used by the explicitly support-restricted endpoint.
Dorn and Guo (2021) show that direct quantile-balancing sensitivity analysis can
be sharp while indirect band-based procedures can be conservative; this logic is
the published comparator for the pointwise-band calculation.  Frauen,
Melnychuk, and Feuerriegel (2023) generalize sharp causal sensitivity analysis
beyond simple binary-treatment settings and therefore justify using actionwise
sharp MSM operators.  Masten, Poirier, and Ren (2025) derive sharp
distributional and quantile bounds under relaxations that include
marginal-sensitivity restrictions, but they do not address the joint
compatibility required by a multi-action rank-dependent policy functional.

For estimation and inference, Dorn, Guo, and Kallus (2021) provide the closest
orthogonal-score template because they construct doubly-sharp scores for sharp
MSM endpoints.  The present score differs in two necessary ways: the
least-favorable generated-loss transform must be the canonical dual
pseudo-outcome of the bounded-weight linear program, and the score must include
the derivative of that program with respect to the nominal propensity score.
Imbens and Manski (2004) give the interval-identified scalar confidence-interval
template that can consume endpoint limit laws once those laws are established.

\section{Formal setup}
\begin{definition}[Observed law, latent law, and identified sets]
Let \(O=(Y,A,X)\sim P\), where the observed factual outcome
\(Y\in[y_L,y_U]\subset\R\), the action \(A\in\mathcal A\) is finite, and
\(X\in\mathcal X\) is an observed covariate vector.  A fixed stochastic
evaluation policy is a measurable map
\(\pi:\mathcal A\times\mathcal X\to[0,1]\) satisfying
\(\sum_{a\in\mathcal A}\pi(a\mid x)=1\) for each \(x\).  Potential outcomes are
\(Y_{\mathcal A}=\{Y(a):a\in\mathcal A\}\).  Unless explicitly restricted,
nonfactual potential outcomes are real-valued and are not assumed to lie in the
observed factual support.  The policy draw \(A^\pi\sim\pi(\cdot\mid X)\) is
drawn conditionally on \(X\) independently of \((A,U,Y_{\mathcal A})\), and
\(Y(\pi)=Y(A^\pi)\).

Fix a sensitivity parameter \(\Gamma\geq 1\) and a tail level \(\tau\in(0,1)\).
Let \(\mathcal M_\Gamma(P)\) denote the locked full class of full-data laws
\(Q\) on \((Y_{\mathcal A},A,X,U)\) such that:
\begin{enumerate}[label=(\roman*),leftmargin=2em]
\item the observed margin of \((Y,A,X)\), with \(Y=Y(A)\), equals \(P\);
\item consistency \(Y=Y(A)\) holds \(Q\)-almost surely;
\item the treatment assignment under \(Q\) satisfies the marginal sensitivity
  restriction in Assumption~\ref{ass:msm}; and
\item \(\operatorname{CVaR}_\tau\{Y_Q(\pi)\}\) is finite for the law under
  consideration.
\end{enumerate}
This class does not impose conditional exchangeability and does not impose
\(Y(a)\in[y_L,y_U]\) for \(a\ne A\).  For each \(Q\in\mathcal M_\Gamma(P)\),
define
\[
\theta(Q)=\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}.
\]
The locked identified set is
\[
\Theta_I(P)=\{\theta(Q):Q\in\mathcal M_\Gamma(P)\}.
\]

Let \(\mathcal M_\Gamma^{\mathrm{bd}}(P)\subseteq\mathcal M_\Gamma(P)\) denote
the support-restricted subclass satisfying
\[
Q\{Y(a)\in[y_L,y_U]\text{ for every }a\in\mathcal A\}=1.
\]
Its identified set is
\[
\Theta_I^{\mathrm{bd}}(P)
=
\{\theta(Q):Q\in\mathcal M_\Gamma^{\mathrm{bd}}(P)\}.
\]

Let \(\mathcal M_\Gamma^{\mathrm{ce}}(P)\subseteq\mathcal M_\Gamma(P)\) denote
the conditionally exchangeable subclass satisfying
\[
Q(A=a\mid X,U,Y_{\mathcal A})=Q(A=a\mid X,U)
\quad\text{for every }a\in\mathcal A.
\]
Its identified set is
\[
\Theta_I^{\mathrm{ce}}(P)
=
\{\theta(Q):Q\in\mathcal M_\Gamma^{\mathrm{ce}}(P)\}.
\]
\end{definition}

The note follows the convention that lower values of \(Y\) are better.  Under
that convention a robust planner evaluates a fixed policy \(\pi\) through the
upper endpoint of the tail-risk target because large values correspond to poor
upper-tail outcomes.

\paragraph{Locked parameters.}
\begin{itemize}
  \item qid: \texttt{pid\_cvar\_welfare\_msm\_v1}
  \item specialization: \texttt{robust\_cvar\_policy}
  \item observable distribution: \(P\) over \((Y,A,X)\), with
    \(A\in\mathcal A\) finite and factual \(Y\in[y_L,y_U]\)
  \item parameter \(\theta\): the scalar causal target
    \(\theta(Q)=\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}\), equivalently the
    MSM-CVaR lower welfare endpoint under the lower-is-better convention
  \item identifying restrictions in the locked full class:
    consistency, overlap on the support of \(\pi\), and the odds-ratio marginal
    sensitivity bound indexed by \(\Gamma\); no nonfactual support restriction
    and no conditional exchangeability restriction are included in this locked
    list
  \item support-restricted comparison class:
    \(\mathcal M_\Gamma^{\mathrm{bd}}(P)\), obtained by adding the explicit
    all-potential-outcome support restriction
    \(Y(a)\in[y_L,y_U]\) for every \(a\)
  \item conditionally exchangeable comparison class:
    \(\mathcal M_\Gamma^{\mathrm{ce}}(P)\), obtained by adding
    \(A\perp Y_{\mathcal A}\mid (X,U)\)
  \item inference-only regularity:
    canonical differentiability of the bounded-weight LP threshold, global
    threshold localization, local quadratic expansion, and second-order
    nuisance rates, stated in Assumptions~\ref{ass:lp-diff}--\ref{ass:nuisance}
  \item bounding functionals:
    the locked full-class upper endpoint is infinite under unbounded
    nonfactual support; the support-restricted finite endpoints
    \((\theta_L^{\mathrm{bd}}(P),\theta_U^{\mathrm{bd}}(P))\) are defined in
    Definition~\ref{def:bd-endpoints}; the conditionally exchangeable
    joint-compatible endpoints
    \((\theta_L^{\mathrm{jnt}}(P),\theta_U^{\mathrm{jnt}}(P))\) are defined in
    Definition~\ref{def:joint-kernels}; and the computable separated subclass
    outer endpoints
    \((\overline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P),
      \underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P))\) are defined in
    Section~\ref{sec:functional}
\end{itemize}
Policy \(\pi\), sensitivity \(\Gamma\), and tail fraction \(\tau\) are fixed
throughout.

\section{Assumptions}
\begin{assumption}[Observed sampling and population overlap]\label{ass:iid-overlap}
The nominal propensity score
\(e_a(X)=P(A=a\mid X)\) satisfies
\(0<\epsilon\leq e_a(X)\leq 1-\epsilon\) almost surely for every
\(a\in\mathcal A\), and \(\pi(a\mid X)>0\) implies \(e_a(X)>0\) almost surely.
For estimation statements, the observations \(O_1,\ldots,O_n\) are iid from
\(P\).  Identification statements use only the population-overlap part of this
assumption.
\end{assumption}

\begin{assumption}[Consistency and policy support]\label{ass:consistency}
For every action \(a\in\mathcal A\), the factual outcome satisfies \(Y=Y(A)\)
almost surely, and the policy draw \(A^\pi\) used to define \(Y(\pi)\) is drawn
from \(\pi(\cdot\mid X)\) independently of the factual treatment assignment and
potential outcomes conditional on \(X\).
\end{assumption}

\begin{assumption}[Marginal sensitivity model]\label{ass:msm}
There exists a latent variable \(U\) such that, for every \(a\in\mathcal A\) and
every \((x,u)\) in the support of \((X,U)\),
\[
\Gamma^{-1}\leq
\frac{P(A=a\mid X=x)/(1-P(A=a\mid X=x))}
{P(A=a\mid X=x,U=u)/(1-P(A=a\mid X=x,U=u))}
\leq \Gamma.
\]
\end{assumption}

\begin{assumption}[Observed tail support]\label{ass:tail}
The observed conditional law of \(Y\mid A=a,X=x\) is supported on the common
compact interval \([y_L,y_U]\) for every \((a,x)\).  For each
\(\eta\in[y_L,y_U]\), the generated factual loss \((Y-\eta)_+\) has finite
conditional mean in every \((a,x)\) cell.  This assumption is only about the
observed factual outcome; it does not impose \(Y(a)\in[y_L,y_U]\) for
nonfactual potential outcomes in the locked full class.
\end{assumption}

\begin{assumption}[Canonical differentiability of the cellwise LP]\label{ass:lp-diff}
For every action \(a\), for \(P_X\)-almost every \(x\), and uniformly for
\(\eta\) in a neighborhood of the separated minimizer \(\eta_*\) in
Assumption~\ref{ass:unique-eta}, the upper bounded-weight program for
\(g_\eta(Y)=(Y-\eta)_+\) has a unique canonical dual threshold
\(\lambda_{\eta,a}(x)\).  When \(\Gamma>1\), this means the equation
\[
\Pr\{g_\eta(Y)>\lambda_{\eta,a}(x)\mid A=a,X=x\}
=
\frac{1-\ell_a(x)}{u_a(x)-\ell_a(x)}
\]
has a unique solution with no threshold interval in a support gap and with no
atom at \(g_\eta(Y)=\lambda_{\eta,a}(x)\).  The map from the conditional law of
\(Y\mid A=a,X=x\) and the propensity \(e_a(x)\) to
\((\lambda_{\eta,a},h_{\eta,a},T_{\eta,a},\dot T_{\eta,a,e})\) in
Lemma~\ref{lem:lp-envelope} is locally Hadamard differentiable along the
first-stage paths used by the estimator.  When \(\Gamma=1\), the program is
degenerate with \(r^*\equiv1\), \(h_{\eta,a}=g_\eta\), and
\(\dot T_{\eta,a,e}=0\).
\end{assumption}

\begin{assumption}[Differentiable interior robust optimizer]\label{ass:unique-eta}
The separated criterion
\(\eta\mapsto \mathcal C_\eta^{+,\mathrm{sep}}(P,\pi)\) defined in
Section~\ref{sec:functional} has a unique minimizer
\(\eta_*=\eta_{\tau,\Gamma}(P,\pi)\) in the interior of
\([y_L,y_U]\).  In a neighborhood of \(\eta_*\), the criterion is twice
continuously differentiable, satisfies
\[
\partial_\eta \mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)=0,
\qquad
\partial_{\eta\eta}^2 \mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)>0,
\]
and the classes of canonical pseudo-outcomes and propensity-derivative terms in
Definition~\ref{def:onestep} are uniformly Lipschitz in \(\eta\) in
\(L_2(P)\).
\end{assumption}

\begin{assumption}[Global localization of the selected threshold]\label{ass:global-eta}
The population criterion \(\eta\mapsto
\mathcal C_\eta^{+,\mathrm{sep}}(P,\pi)\) is continuous on
\(\mathcal I=[y_L,y_U]\) and is globally separated at its unique minimizer:
for every \(\delta>0\),
\[
\kappa_\delta
:=
\inf_{\eta\in\mathcal I:\ |\eta-\eta_*|\ge\delta}
\left\{
\mathcal C_\eta^{+,\mathrm{sep}}(P,\pi)
-
\mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)
\right\}
>0.
\]
For the cross-fitted criterion in Definition~\ref{def:onestep},
\[
\sup_{\eta\in\mathcal I}
\left|
\widehat{\mathcal C}_\eta^{\mathrm{sep}}
-
\mathcal C_\eta^{+,\mathrm{sep}}(P,\pi)
\right|
=o_p(1).
\]
Moreover, on some fixed neighborhood of \(\eta_*\), the local criterion obeys
the quadratic expansion
\[
\widehat{\mathcal C}_\eta^{\mathrm{sep}}
-
\widehat{\mathcal C}_{\eta_*}^{\mathrm{sep}}
=
\frac12
\partial_{\eta\eta}^2
\mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)(\eta-\eta_*)^2
+
(\eta-\eta_*)Z_n
+
R_n(\eta),
\]
where \(Z_n=O_p(n^{-1/2})\) and
\[
\sup_{|\eta-\eta_*|\le\rho}
\frac{|R_n(\eta)|}{(\eta-\eta_*)^2+n^{-1}}
=o_p(1)
\]
for a radius \(\rho>0\).
\end{assumption}

\begin{assumption}[Nuisance-rate regime for the corrected one-step score]\label{ass:nuisance}
The first-stage estimators used in Definition~\ref{def:onestep} are trained on
auxiliary folds.  Uniformly for \(\eta\) in a neighborhood of \(\eta_*\), they
estimate \(e_a\), the active dual thresholds \(\lambda_{\eta,a}\), the canonical
pseudo-outcomes \(h_{\eta,a}\), the cell functionals \(T_{\eta,a}\), and the
propensity derivatives \(\dot T_{\eta,a,e}\).  The estimators are \(L_2(P)\)
consistent, bounded with probability tending to one, and satisfy the second
order expansion
\[
P\{\widehat\chi_{\eta_*,\pi}-\chi_{\eta_*,\pi}\}
=
O_p\!\left(
\sum_{a\in\mathcal A}
\|\widehat e_a-e_a\|_2\|\widehat h_{\eta_*,a}-h_{\eta_*,a}\|_2
+\|\widehat e_a-e_a\|_2^2
+\|\widehat F_{\eta_*,a}-F_{\eta_*,a}\|_2^2
\right)
=o_p(n^{-1/2}),
\]
where \(\chi_{\eta,\pi}\) is the corrected score in Definition~\ref{def:onestep}
and \(\widehat F_{\eta,a}\) denotes the fitted conditional distribution object
from which \(\widehat\lambda_{\eta,a}\), \(\widehat h_{\eta,a}\), and
\(\widehat T_{\eta,a}\) are computed.
\end{assumption}

\section{Estimand-defining functional}
\label{sec:functional}
For \(e\in(0,1)\), define
\[
\ell(e)=e+\frac{1-e}{\Gamma},
\qquad
u(e)=e+\Gamma(1-e).
\]
For a cell \((a,x)\), write
\[
\ell_a(x)=\ell(e_a(x)),
\qquad
u_a(x)=u(e_a(x)).
\]
For \(\eta\in\mathcal I=[y_L,y_U]\), put
\[
m_{\eta,a}(x)=\E_P[(Y-\eta)_+\mid A=a,X=x].
\]

\begin{definition}[Support-restricted Manski completion endpoints]\label{def:bd-endpoints}
The support-restricted upper and lower CVaR criteria are
\[
\mathcal C_\eta^{+,\mathrm{bd}}(P,\pi)
=
\eta+\tau^{-1}
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\left\{
e_a(X)m_{\eta,a}(X)
+
(1-e_a(X))(y_U-\eta)_+
\right\}
\right],
\]
and
\[
\mathcal C_\eta^{-,\mathrm{bd}}(P,\pi)
=
\eta+\tau^{-1}
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\left\{
e_a(X)m_{\eta,a}(X)
+
(1-e_a(X))(y_L-\eta)_+
\right\}
\right].
\]
Because the infimum over \(\eta\) is restricted to
\(\mathcal I=[y_L,y_U]\), the final term in
\(\mathcal C_\eta^{-,\mathrm{bd}}\) is identically zero, but it is kept to
display the symmetric support-endpoint completion.  Define
\[
\theta_U^{\mathrm{bd}}(P)
=
\inf_{\eta\in\mathcal I}
\mathcal C_\eta^{+,\mathrm{bd}}(P,\pi),
\qquad
\theta_L^{\mathrm{bd}}(P)
=
\inf_{\eta\in\mathcal I}
\mathcal C_\eta^{-,\mathrm{bd}}(P,\pi).
\]
These are finite functionals of the observed law \(P\) and the explicit
additional support restriction \(Y(a)\in[y_L,y_U]\) for every action.
\end{definition}

\begin{definition}[Actionwise bounded-weight operators]
For a nonnegative measurable loss \(Z=Z(Y)\), define
\[
\mathfrak T_{\Gamma}^{+}(Z\mid a,x)
=
\sup_{\ell_a(x)\le r\le u_a(x),\ \E_P[r(Y)\mid A=a,X=x]=1}
\E_P[r(Y)Z(Y)\mid A=a,X=x],
\]
and
\[
\mathfrak T_{\Gamma}^{-}(Z\mid a,x)
=
\inf_{\ell_a(x)\le r\le u_a(x),\ \E_P[r(Y)\mid A=a,X=x]=1}
\E_P[r(Y)Z(Y)\mid A=a,X=x].
\]
The upper optimizer places weight \(u_a(x)\) on the largest values of \(Z\),
weight \(\ell_a(x)\) on the smallest values of \(Z\), and splits only at the
canonical threshold needed to enforce \(\E r=1\).  This is the
Hardy--Littlewood rearrangement form of the sharp marginal-sensitivity
bounded-weight calculation used by Tan (2006), Dorn and Guo (2021), and Frauen,
Melnychuk, and Feuerriegel (2023).
\end{definition}

For \(\eta\in\mathcal I=[y_L,y_U]\), define
\[
\Psi_\eta^{+,\mathrm{sep}}(P,\pi)=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)\,
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,X\}
\right],
\]
\[
\Psi_\eta^{-,\mathrm{sep}}(P,\pi)=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)\,
\mathfrak T_{\Gamma}^{-}\{(Y-\eta)_+\mid a,X\}
\right].
\]
The corresponding Rockafellar--Uryasev criteria are
\[
\mathcal C_\eta^{+,\mathrm{sep}}(P,\pi)
=
\eta+\tau^{-1}\Psi_\eta^{+,\mathrm{sep}}(P,\pi),
\qquad
\mathcal C_\eta^{-,\mathrm{sep}}(P,\pi)
=
\eta+\tau^{-1}\Psi_\eta^{-,\mathrm{sep}}(P,\pi).
\]
The separated outer endpoints are
\[
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)
:=
\inf_{\eta\in\mathcal I}\mathcal C_\eta^{+,\mathrm{sep}}(P,\pi),
\qquad
\overline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)
:=
\inf_{\eta\in\mathcal I}\mathcal C_\eta^{-,\mathrm{sep}}(P,\pi).
\]
The upper endpoint is conservative for the lower-is-better welfare convention.

\begin{definition}[Conditional-exchangeable joint-compatible endpoint program]\label{def:joint-kernels}
For each \(x\), let \(\Delta_{\mathcal A}\) be the probability simplex on
\(\mathcal A\).  Let \(\calH_\Gamma(P)\) be the class of regular conditional
kernels
\[
H_x(dy_{\mathcal A},dp)
\quad\text{on}\quad
[y_L,y_U]^{|\mathcal A|}\times \Delta_{\mathcal A},
\]
where \(y_{\mathcal A}=(y_a:a\in\mathcal A)\) and
\(p=(p_a:a\in\mathcal A)\), satisfying the following constraints for
\(P_X\)-almost every \(x\):
\begin{enumerate}[label=(\roman*),leftmargin=2em]
\item \(p_a\in(0,1)\) and \(\sum_a p_a=1\), \(H_x\)-almost surely;
\item for every \(a\),
\[
\Gamma^{-1}\leq
\frac{e_a(x)/(1-e_a(x))}{p_a/(1-p_a)}
\leq \Gamma,
\qquad H_x\text{-almost surely};
\]
\item for every \(a\),
\[
\int p_a\,dH_x=e_a(x);
\]
\item for every bounded measurable \(b:[y_L,y_U]\to\R\) and every \(a\),
\[
\int p_a\,b(y_a)\,dH_x
=
e_a(x)\,\E_P[b(Y)\mid A=a,X=x].
\]
\end{enumerate}
For \(H\in\calH_\Gamma(P)\), define the conditionally exchangeable induced
policy law by
\[
\E_H[b\{Y(\pi)\}]
=
\E_{P_X}\int
\sum_{a\in\mathcal A}\pi(a\mid X)b(y_a)\,dH_X(y_{\mathcal A},p)
\]
for bounded measurable \(b\).  The sharp conditionally exchangeable
joint-compatible upper and lower endpoints are
\[
\theta_U^{\mathrm{jnt}}(P)
=
\sup_{H\in\calH_\Gamma(P)}
\inf_{\eta\in[y_L,y_U]}
\left\{
\eta+\tau^{-1}
\E_{P_X}\int
\sum_{a\in\mathcal A}\pi(a\mid X)(y_a-\eta)_+\,dH_X
\right\},
\]
\[
\theta_L^{\mathrm{jnt}}(P)
=
\inf_{H\in\calH_\Gamma(P)}
\inf_{\eta\in[y_L,y_U]}
\left\{
\eta+\tau^{-1}
\E_{P_X}\int
\sum_{a\in\mathcal A}\pi(a\mid X)(y_a-\eta)_+\,dH_X
\right\}.
\]
\end{definition}

The joint program is explicit for the conditionally exchangeable subclass: its
decision variable is the conditional kernel \(H_x\); its constraints are the
simplex, odds-ratio, observed propensity, and observed selected-outcome moment
equations above.  On finite outcome and covariate support it becomes a finite
nonlinear program with variables equal to the masses assigned to
\((y_{\mathcal A},p)\); if the admissible \(p\)-support is discretized or known
to attain finitely many odds-ratio faces, it becomes a finite-dimensional
constrained program over those support points.

\begin{definition}[Pointwise CDF envelopes and band comparator]\label{def:band}
For \(y\in[y_L,y_U]\), define the actionwise lower and upper CDF envelopes
\[
\mathfrak F_{\Gamma}^{-}(y\mid a,x)
=
\inf_{\ell_a(x)\le r\le u_a(x),\ \E_P[r(Y)\mid A=a,X=x]=1}
\E_P[r(Y)\one\{Y\le y\}\mid A=a,X=x],
\]
\[
\mathfrak F_{\Gamma}^{+}(y\mid a,x)
=
\sup_{\ell_a(x)\le r\le u_a(x),\ \E_P[r(Y)\mid A=a,X=x]=1}
\E_P[r(Y)\one\{Y\le y\}\mid A=a,X=x].
\]
The policy-level pointwise envelopes are
\[
\underline F_{\Gamma}(y\mid P,\pi)
=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak F_{\Gamma}^{-}(y\mid a,X)
\right],
\]
and
\[
\overline F_{\Gamma}(y\mid P,\pi)
=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak F_{\Gamma}^{+}(y\mid a,X)
\right].
\]
Let \(\calF_{\Gamma}^{\mathrm{pt}}(P,\pi)\) be the set of distribution
functions \(F\) on \([y_L,y_U]\) that are cadlag, nondecreasing, satisfy
\(F(y_L-)=0\), \(F(y_U)=1\), and obey
\[
\underline F_{\Gamma}(y\mid P,\pi)\le F(y)\le
\overline F_{\Gamma}(y\mid P,\pi)
\quad\text{for every }y\in[y_L,y_U].
\]
Define
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
:=
\inf_{\eta\in\mathcal I}
\left\{
\eta+\tau^{-1}\sup_{F\in\calF_{\Gamma}^{\mathrm{pt}}(P,\pi)}
\int_{[y_L,y_U]} (y-\eta)_+\,dF(y)
\right\}.
\]
The separated non-commutation gap is
\[
\Delta_{\mathrm{nc}}^{\mathrm{sep}}(\pi;P)
=
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
-
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P).
\]
\end{definition}

\section{Target causal estimand}
\begin{definition}[Policy CVaR target]
For each latent law \(Q\in\mathcal M_\Gamma(P)\) with integrable positive part,
the target causal estimand is
\[
\theta(Q)=\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}
=
\inf_{\eta\in\R}
\left\{
\eta+\tau^{-1}\E_Q[(Y_Q(\pi)-\eta)_+]
\right\}.
\]
For \(Q\in\mathcal M_\Gamma^{\mathrm{bd}}(P)\) or
\(Q\in\mathcal M_\Gamma^{\mathrm{ce}}(P)\), the policy outcome is supported on
\([y_L,y_U]\), so the infimum may be restricted to \([y_L,y_U]\).  For the
locked full class \(\mathcal M_\Gamma(P)\), no such restriction is available
unless a nonfactual support condition is added.
\end{definition}

\section{Main theorems}
\begin{theorem}[Locked full class, support completion, joint subclass, and separated bound]\label{thm:joint-sharp-and-sep-bound}
Assume the population-overlap component of Assumption~\ref{ass:iid-overlap} and
Assumptions~\ref{ass:consistency}--\ref{ass:tail}.  Let
\[
q_\pi(P)
=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)\{1-e_a(X)\}
\right].
\]
Under Assumption~\ref{ass:iid-overlap}, \(q_\pi(P)\ge\epsilon>0\).  If the
locked full class \(\mathcal M_\Gamma(P)\) imposes no finite upper support
restriction on nonfactual potential outcomes, then
\[
\sup\Theta_I(P)=+\infty.
\]
More explicitly, for every \(M>y_U\) there exists
\(Q_M\in\mathcal M_\Gamma(P)\) such that \(Y_{Q_M}(\pi)=M\) with probability
\(q_\pi(P)\), and
\[
\operatorname{CVaR}_{\tau}\{Y_{Q_M}(\pi)\}\to+\infty
\qquad\text{as }M\to\infty.
\]
Thus the locked full class has no finite sharp upper endpoint.

For the support-restricted subclass,
\[
\Theta_I^{\mathrm{bd}}(P)
=
\left[\theta_L^{\mathrm{bd}}(P),\theta_U^{\mathrm{bd}}(P)\right],
\qquad
\sup\Theta_I^{\mathrm{bd}}(P)=\theta_U^{\mathrm{bd}}(P),
\qquad
\inf\Theta_I^{\mathrm{bd}}(P)=\theta_L^{\mathrm{bd}}(P),
\]
with \(\theta_U^{\mathrm{bd}}\) and \(\theta_L^{\mathrm{bd}}\) defined in
Definition~\ref{def:bd-endpoints}.

For the conditionally exchangeable subclass,
\[
\sup\Theta_I^{\mathrm{ce}}(P)=\theta_U^{\mathrm{jnt}}(P),
\qquad
\inf\Theta_I^{\mathrm{ce}}(P)=\theta_L^{\mathrm{jnt}}(P),
\]
with \(\theta_U^{\mathrm{jnt}}\) and \(\theta_L^{\mathrm{jnt}}\) defined in
Definition~\ref{def:joint-kernels}.  Moreover,
\[
\theta_U^{\mathrm{jnt}}(P)
\le
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P),
\qquad
\theta_L^{\mathrm{jnt}}(P)
\ge
\overline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P).
\]
Thus
\[
\Theta_I^{\mathrm{ce}}(P)\subseteq
\left[
\overline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P),
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)
\right].
\]
The separated upper functional in Conjecture~1 is therefore not a valid finite
full-class endpoint under the locked restrictions.  It is a valid computable
outer endpoint for the conditionally exchangeable subclass, and it is sharp for
that subclass whenever a maximizing joint kernel can realize the actionwise
least-favorable tilts at an active minimizer \(\eta_*\).  This joint
realizability condition holds in the conditionally exchangeable
\(\Gamma=1\) corner and in degenerate single-action policies, but is not implied
by the multi-action MSM restrictions alone.
\end{theorem}

\begin{theorem}[Pointwise-band comparison]\label{thm:band}
Under the population-overlap component of Assumption~\ref{ass:iid-overlap} and
the observed-support component of Assumption~\ref{ass:tail},
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
\ge
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P).
\]
If, in addition, the conditionally exchangeable joint program
\(\calH_\Gamma(P)\) represents a nonempty subclass as in
Theorem~\ref{thm:joint-sharp-and-sep-bound}, then
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
\ge
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)
\ge
\theta_U^{\mathrm{jnt}}(P).
\]
The comparison is a statement about the conditionally exchangeable
actionwise-bounding workflow; it need not bound the larger locked full class,
whose upper endpoint is infinite when nonfactual potential outcomes are
unbounded above.

In the two-action, three-outcome, one-covariate-cell strict-overlap class with
\(1<\Gamma<\infty\), the same monotone upper-tail bounded-weight vertex is
optimal for every generated loss \((Y-\eta)_+\).  Consequently
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
=
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P),
\qquad
\Delta_{\mathrm{nc}}^{\mathrm{sep}}(\pi;P)=0
\]
throughout that class.
\end{theorem}

\begin{lemma}[Envelope derivative of the cellwise MSM operator]\label{lem:lp-envelope}
Fix \((\eta,a,x)\), put \(g_\eta(y)=(y-\eta)_+\), and suppose the cell satisfies
the canonical differentiability condition in Assumption~\ref{ass:lp-diff}.  If
\(\Gamma=1\), set \(r_{\eta,a}^*\equiv1\),
\(h_{\eta,a}(y,x)=g_\eta(y)\), \(T_{\eta,a}(x)=\E_P[g_\eta(Y)\mid A=a,X=x]\),
and \(\dot T_{\eta,a,e}(x)=0\).  If \(\Gamma>1\), let
\[
r_{\eta,a}^*(y,x)
=
u_a(x)\one\{g_\eta(y)>\lambda_{\eta,a}(x)\}
+
\ell_a(x)\one\{g_\eta(y)<\lambda_{\eta,a}(x)\},
\]
where \(\lambda_{\eta,a}(x)\) is the unique canonical threshold satisfying
\[
\E_P[r_{\eta,a}^*(Y,x)\mid A=a,X=x]=1.
\]
Define the canonical dual pseudo-outcome
\[
h_{\eta,a}(y,x)
=
\lambda_{\eta,a}(x)
+
r_{\eta,a}^*(y,x)\{g_\eta(y)-\lambda_{\eta,a}(x)\},
\]
and
\[
T_{\eta,a}(x)
=
\mathfrak T_{\Gamma}^{+}\{g_\eta(Y)\mid a,x\}
=
\E_P[h_{\eta,a}(Y,x)\mid A=a,X=x].
\]
Then the pathwise derivative of \(T_{\eta,a}(x)\) with respect to the
conditional law of \(Y\mid A=a,X=x\) is represented by
\(h_{\eta,a}(Y,x)-T_{\eta,a}(x)\).  For \(\Gamma>1\), the derivative with
respect to the nominal propensity \(e_a(x)\), holding the conditional law fixed,
is
\[
\dot T_{\eta,a,e}(x)
=
u_a'(x)\,
\E_P[(g_\eta(Y)-\lambda_{\eta,a}(x))_+\mid A=a,X=x]
-
\ell_a'(x)\,
\E_P[(g_\eta(Y)-\lambda_{\eta,a}(x))_-\mid A=a,X=x],
\]
where
\[
u_a'(x)=1-\Gamma,
\qquad
\ell_a'(x)=1-\Gamma^{-1},
\qquad
t_-=\max\{-t,0\}.
\]
\end{lemma}

\begin{theorem}[Corrected one-step limit law for the separated endpoint]\label{thm:onestep-limit}\label{prop:onestep-limit}\label{conj:onestep-limit}
Let \(\widehat W_{\tau,\Gamma}^{\mathrm{sep}}(\pi)\) be the estimator in
Definition~\ref{def:onestep}.  As a statistical statement about the observed-law
functional \(\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)\), assume
Assumptions~\ref{ass:iid-overlap}, \ref{ass:tail}, and
\ref{ass:lp-diff}--\ref{ass:nuisance}.  Then
\[
\sqrt n\{
\widehat W_{\tau,\Gamma}^{\mathrm{sep}}(\pi)
-
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)
\}
=
\frac{1}{\sqrt n}\sum_{i=1}^n
\varphi_{\tau,\Gamma,\pi}^{\mathrm{sep}}(O_i)+o_p(1),
\]
where
\[
\varphi_{\tau,\Gamma,\pi}^{\mathrm{sep}}(O)
=
\tau^{-1}
\left\{
\chi_{\eta_*,\pi}(O)
-
\Psi_{\eta_*}^{+,\mathrm{sep}}(P,\pi)
\right\},
\qquad
\E[\varphi_{\tau,\Gamma,\pi}^{\mathrm{sep}}(O)]=0.
\]
The fold-stacked sample variance in Definition~\ref{def:onestep} converges in
probability to
\[
\operatorname{Var}\{\varphi_{\tau,\Gamma,\pi}^{\mathrm{sep}}(O)\}.
\]
This limit law is for the separated outer endpoint.  It does not require
consistency or the causal MSM restriction except for interpreting the separated
functional as a causal sensitivity bound.  A limit law for the exact
joint-compatible endpoint \(\theta_U^{\mathrm{jnt}}(P)\) requires
differentiability of the joint program in Definition~\ref{def:joint-kernels}.
\end{theorem}

\paragraph{Verdicts for the motivating conjectures.}
Conjecture~1 is refuted for the locked full class
\(\mathcal M_\Gamma(P)\): without a nonfactual upper-support restriction,
\(\sup\Theta_I(P)=+\infty\).  The support-completion endpoint is sharp only for
the explicitly support-restricted subclass
\(\mathcal M_\Gamma^{\mathrm{bd}}(P)\), while the nested actionwise MSM-CVaR
functional is only a conditionally exchangeable subclass outer bound.
Conjecture~2 is confirmed only as the weak comparison
\(W_{\tau,\Gamma}^{\mathrm{band}}\ge
\underline W_{\tau,\Gamma}^{\mathrm{sep}}\ge\theta_U^{\mathrm{jnt}}\), and the
proposed finite class gives equality rather than a strict gap.  Conjecture~3 is
confirmed for the separated endpoint under the corrected score and the explicit
LP differentiability, global localization, local smoothness, and nuisance-rate
conditions stated above; it is open for the exact joint-compatible endpoint.

\section{Interpretation}
Theorem~\ref{thm:joint-sharp-and-sep-bound} separates four objects that are
often conflated.  The locked full class has no finite upper endpoint if
nonfactual potential outcomes are allowed to be arbitrarily large.  The
support-completion bound is exact only after adding the all-potential-outcome
support restriction \(Y(a)\in[y_L,y_U]\).  The joint-compatible kernel program
is exact for the conditionally exchangeable subclass; in that subclass,
conditional exchangeability and the finite odds-ratio bounds force the
unselected potential-outcome margins to be absolutely continuous with respect to
the observed selected margins.  The separated nested functional is simpler and
computable from the observed conditional laws, but it optimizes each action's
density ratio as if the actionwise ratios could be selected independently.  In a
multi-action conditionally exchangeable MSM that independence is not automatic
because the ratios must come from one latent treatment-probability vector.

Theorem~\ref{thm:band} compares two conservative workflows inside the
conditionally exchangeable actionwise-bounding analysis.  The pointwise-band
workflow builds explicit thresholdwise CDF envelopes and then applies the CVaR
formula.  The separated nested workflow applies the sharp bounded-weight mean
operator to the generated loss \((Y-\eta)_+\) and then minimizes over \(\eta\).
The band is no smaller than the separated nested bound.  In the finite
response-type class specified in the theorem, there is a common upper-tail
vertex, so the two workflows agree and the separated non-commutation gap is
zero.

Theorem~\ref{thm:onestep-limit} identifies the score needed to estimate the
separated endpoint.  A transformed loss with the correct conditional mean is not
enough.  The first-order derivative of the bounded-weight operator is represented
by the dual pseudo-outcome \(h_{\eta,a}\), and the dependence of the MSM bounds
\(\ell_a,u_a\) on \(e_a\) contributes the additional term
\(\dot T_{\eta,a,e}(X)\{\one(A=a)-e_a(X)\}\).  This derivative is justified only
under a canonical differentiable threshold condition for the cellwise linear
program.  The minimization over \(\eta\) is first-order silent only after the
global localization and local quadratic conditions in
Assumptions~\ref{ass:unique-eta} and~\ref{ass:global-eta} force the
data-selected minimizer into the differentiable neighborhood.

\section{Step-by-step proof}
\begin{proof}[Proof of Theorem~\ref{thm:joint-sharp-and-sep-bound}]
First prove that the locked full class has no finite upper endpoint.  For
\(M>y_U\), construct a full-data law \(Q_M\) as follows.  Draw
\((X,A,Y)\sim P\), set \(Y(A)=Y\), set \(Y(a)=M\) for every \(a\ne A\), and take
\(U\) to be constant.  Then the observed margin is exactly \(P\), consistency
holds, and
\[
Q_M(A=a\mid X,U)=P(A=a\mid X)=e_a(X),
\]
so the odds-ratio in Assumption~\ref{ass:msm} equals one and is feasible for
every \(\Gamma\ge1\).  The construction therefore belongs to the locked class
\(\mathcal M_\Gamma(P)\).

Let \(B=\one\{A^\pi\ne A\}\), where the policy action is drawn conditionally on
\(X\).  Then
\[
\Pr_{Q_M}(B=1)
=
\E_P\left[\sum_{a\in\mathcal A}\pi(a\mid X)\{1-e_a(X)\}\right]
=
q_\pi(P).
\]
By Assumption~\ref{ass:iid-overlap}, \(e_a(X)\le1-\epsilon\) for every action,
so \(q_\pi(P)\ge\epsilon\sum_a\pi(a\mid X)=\epsilon\) after averaging.  On the
event \(B=1\), \(Y_{Q_M}(\pi)=M\); on \(B=0\), the policy outcome is factual and
lies in \([y_L,y_U]\).  Hence \(Y_{Q_M}(\pi)\) stochastically dominates
\(V_M=M B+y_L(1-B)\).  By monotonicity of upper-tail CVaR,
\[
\operatorname{CVaR}_\tau\{Y_{Q_M}(\pi)\}
\ge
\operatorname{CVaR}_\tau(V_M).
\]
If \(q_\pi(P)\ge\tau\), the right side equals \(M\).  If
\(q_\pi(P)<\tau\), the Rockafellar--Uryasev formula gives
\[
\operatorname{CVaR}_\tau(V_M)
=
\frac{q_\pi(P)M+\{\tau-q_\pi(P)\}y_L}{\tau}.
\]
In either case the lower bound diverges to \(+\infty\) as \(M\to\infty\).
Thus \(\sup\Theta_I(P)=+\infty\).

Next prove the finite support-restricted endpoint.  Fix
\(Q\in\mathcal M_\Gamma^{\mathrm{bd}}(P)\) and
\(\eta\in[y_L,y_U]\).  With \(g_\eta(y)=(y-\eta)_+\), consistency and the
observed margin give, for \(P_X\)-almost every \(x\),
\[
\E_Q[g_\eta\{Y(a)\}\mid X=x]
=
e_a(x)\E_P[g_\eta(Y)\mid A=a,X=x]
+
(1-e_a(x))\E_Q[g_\eta\{Y(a)\}\mid A\ne a,X=x].
\]
The support restriction \(Y(a)\in[y_L,y_U]\) implies
\[
(y_L-\eta)_+\le
\E_Q[g_\eta\{Y(a)\}\mid A\ne a,X=x]
\le
(y_U-\eta)_+.
\]
Multiplying by \(\pi(a\mid x)\), summing over \(a\), and integrating over
\(P_X\) yields
\[
\eta+\tau^{-1}\E_Q[(Y_Q(\pi)-\eta)_+]
\le
\mathcal C_\eta^{+,\mathrm{bd}}(P,\pi)
\]
and
\[
\eta+\tau^{-1}\E_Q[(Y_Q(\pi)-\eta)_+]
\ge
\mathcal C_\eta^{-,\mathrm{bd}}(P,\pi)
\]
for every \(\eta\).  Taking the Rockafellar--Uryasev infimum over \(\eta\)
gives \(\theta(Q)\le\theta_U^{\mathrm{bd}}(P)\) and
\(\theta(Q)\ge\theta_L^{\mathrm{bd}}(P)\).

The two support-restricted bounds are sharp.  For the upper endpoint, draw
\((X,A,Y)\sim P\), set \(Y(A)=Y\), set \(Y(a)=y_U\) for every \(a\ne A\), and
take \(U\) to be constant.  This law belongs to
\(\mathcal M_\Gamma^{\mathrm{bd}}(P)\) and turns the upper display into an
equality for every \(\eta\).  Hence it attains
\(\theta_U^{\mathrm{bd}}(P)\).  The lower endpoint is attained by the same
construction with \(Y(a)=y_L\) for every \(a\ne A\).  To see that the whole
interval is sharp, mix the lower and upper completion laws with an independent
Bernoulli selector \(B_t\sim\operatorname{Bernoulli}(t)\), leaving the observed
\((Y,A,X)\) margin unchanged and using the upper completion when \(B_t=1\).  The
resulting law belongs to \(\mathcal M_\Gamma^{\mathrm{bd}}(P)\) for every
\(t\in[0,1]\).  Because all policy outcome laws in this subclass are supported
on the common compact interval \([y_L,y_U]\), the map
\[
t\mapsto \operatorname{CVaR}_\tau\{Y_{Q_t}(\pi)\}
\]
is continuous under this mixture.  At \(t=0\) it equals
\(\theta_L^{\mathrm{bd}}(P)\), and at \(t=1\) it equals
\(\theta_U^{\mathrm{bd}}(P)\).  Therefore every value between the two endpoints
is attainable.

Now prove the conditionally exchangeable joint-kernel representation.  Given
any \(Q\in\mathcal M_\Gamma^{\mathrm{ce}}(P)\), take \(H_x\) to be the
conditional law under \(Q\) of
\[
\bigl((Y(a):a\in\mathcal A),(Q(A=a\mid X=x,U):a\in\mathcal A)\bigr)
\]
given \(X=x\).  The simplex constraint is immediate.  The odds-ratio constraint
is Assumption~\ref{ass:msm}.  The identity
\(\int p_a\,dH_x=e_a(x)\) follows from iterated expectation.  Because the
odds-ratio bound and population overlap imply \(p_a>0\) almost surely, observed
support also implies support of each \(Y(a)\) inside \([y_L,y_U]\) in the
conditionally exchangeable subclass: for any Borel set
\(B\subseteq\R\setminus[y_L,y_U]\),
\[
0
=
\E_Q[\one\{A=a\}\one\{Y(a)\in B\}\mid X=x]
=
\E_Q[p_a(X,U)\one\{Y(a)\in B\}\mid X=x],
\]
and the positivity of \(p_a\) forces
\(\Pr_Q\{Y(a)\in B\mid X=x\}=0\).

For every bounded \(b:[y_L,y_U]\to\R\),
\[
\int p_a b(y_a)\,dH_x
=
\E_Q[p_a(X,U)b\{Y(a)\}\mid X=x]
=
\E_Q[\one(A=a)b\{Y(a)\}\mid X=x],
\]
where the second equality is exactly conditional exchangeability.  Consistency
and the observed margin then give
\[
\E_Q[\one(A=a)b\{Y(a)\}\mid X=x]
=
e_a(x)\E_P[b(Y)\mid A=a,X=x].
\]
Hence \(H\in\calH_\Gamma(P)\).

Conversely, given \(H\in\calH_\Gamma(P)\), construct a law by drawing
\(X\sim P_X\), drawing \((Y_{\mathcal A},p)\sim H_X\), drawing
\(A\) from the categorical distribution \(p\) conditionally on
\((X,Y_{\mathcal A},p)\), and setting \(Y=Y_A\).  With \(U=p\), the constructed
law satisfies conditional exchangeability because
\(Q(A=a\mid X,U,Y_{\mathcal A})=p_a=Q(A=a\mid X,U)\).  The moment constraints in
Definition~\ref{def:joint-kernels} imply
\[
\Pr(A=a\mid X=x)=e_a(x)
\]
and
\[
\Pr(Y\in B\mid A=a,X=x)=P(Y\in B\mid A=a,X=x)
\]
for every measurable \(B\subseteq[y_L,y_U]\).  Thus the observed margin is
\(P\), consistency holds by construction, and the odds-ratio constraint gives
\(Q\in\mathcal M_\Gamma^{\mathrm{ce}}(P)\).  The two constructions preserve the
law of \(Y(\pi)\).  Therefore optimizing
\(\operatorname{CVaR}_{\tau}\{Y(\pi)\}\) over
\(\mathcal M_\Gamma^{\mathrm{ce}}(P)\) is equivalent to optimizing the displayed
Rockafellar--Uryasev criterion over \(\calH_\Gamma(P)\), proving the sharp
subclass endpoint equalities.

It remains to prove the separated outer inequalities for the conditionally
exchangeable subclass.  Fix \(H\in\calH_\Gamma(P)\), \(a\), and \(x\).  The
marginal law of \(Y_a\) under \(H_x\) is absolutely continuous with respect to
the observed selected law \(P(Y\in\cdot\mid A=a,X=x)\).  Its Radon--Nikodym
derivative can be written as
\[
r_{H,a,x}(y)
=
\frac{e_a(x)}
{\E_H[p_a\mid Y_a=y,X=x]}.
\]
The odds-ratio bound on \(p_a\) implies
\[
\ell_a(x)\le r_{H,a,x}(y)\le u_a(x),
\qquad
\E_P[r_{H,a,x}(Y)\mid A=a,X=x]=1.
\]
For \(Z_\eta(y)=(y-\eta)_+\),
\[
\int Z_\eta(y_a)\,dH_x
=
\E_P[r_{H,a,x}(Y)Z_\eta(Y)\mid A=a,X=x]
\le
\mathfrak T_\Gamma^+(Z_\eta\mid a,x).
\]
Multiplying by \(\pi(a\mid x)\), summing over \(a\), and integrating over
\(P_X\) gives
\[
\E_H[(Y(\pi)-\eta)_+]
\le
\Psi_\eta^{+,\mathrm{sep}}(P,\pi)
\quad\text{for every }\eta.
\]
By the Rockafellar--Uryasev identity,
\[
\operatorname{CVaR}_{\tau}\{Y_H(\pi)\}
=
\inf_{\eta\in[y_L,y_U]}
\{\eta+\tau^{-1}\E_H[(Y(\pi)-\eta)_+]\}
\le
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P).
\]
Taking the supremum over \(H\) proves
\(\theta_U^{\mathrm{jnt}}(P)\le
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)\).

The lower inequality is analogous.  The same induced density ratio is feasible
for the lower bounded-weight program, so
\[
\E_H[(Y(\pi)-\eta)_+]\ge
\Psi_\eta^{-,\mathrm{sep}}(P,\pi)
\quad\text{for every }\eta.
\]
Taking the Rockafellar--Uryasev infimum over \(\eta\) and then the infimum over
\(H\) gives
\[
\theta_L^{\mathrm{jnt}}(P)
\ge
\overline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P).
\]

The subclass equality condition follows from the preceding proof.  Equality in
the separated upper bound requires a joint kernel \(H\) whose induced ratios
\(r_{H,a,x}\) attain the actionwise upper linear programs at an active minimizer
\(\eta_*\).  Equivalently the ratios must obey the latent compatibility equation
\[
\sum_{a\in\mathcal A}\frac{e_a(x)}{r_{H,a,x}(y_{\mathcal A})}=1
\]
for \(H_x\)-almost every latent unit while also matching the observed selected
laws.  This compatibility is automatic in the conditionally exchangeable
\(\Gamma=1\) corner, since all ratios equal one, and for degenerate
single-action policies, since only one actionwise ratio enters the policy value.
It is not a consequence of the separate box and normalization constraints
defining \(\mathfrak T_\Gamma^+\) when multiple actions receive positive policy
weight.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:band}]
The band comparison is an observed-law calculation.  Fix \(a,x\).  Among all
weights \(r\) satisfying
\(\ell_a(x)\le r\le u_a(x)\) and
\(\E[r(Y)\mid A=a,X=x]=1\), the monotone upper-tail rearrangement places
weight \(u_a(x)\) on the largest outcomes, \(\ell_a(x)\) on the smallest
outcomes, and splits at the normalization threshold if necessary.  This single
upper-tail rearrangement minimizes
\(\E[r(Y)\one\{Y\le y\}\mid A=a,X=x]\) for every threshold \(y\), and it
maximizes \(\E[r(Y)(Y-\eta)_+\mid A=a,X=x]\) for every
\(\eta\in[y_L,y_U]\).  This is the Hardy--Littlewood exchange argument:
if a feasible vector puts extra weight on a smaller outcome while a larger
outcome is not at its cap, shifting that weight upward preserves normalization
and box constraints, weakly decreases every lower CDF value, and weakly
increases every increasing objective.

Let \(F_\eta^\uparrow\) be the policy mixture distribution induced by these
actionwise upper-tail rearrangements.  Because the rearrangement attains the
term-by-term lower CDF envelope in Definition~\ref{def:band},
\(F_\eta^\uparrow\in\calF_\Gamma^{\mathrm{pt}}(P,\pi)\), and for every
\(\eta\),
\[
\int (y-\eta)_+\,dF_\eta^\uparrow(y)
=
\Psi_\eta^{+,\mathrm{sep}}(P,\pi).
\]
Therefore
\[
\sup_{F\in\calF_\Gamma^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)
\ge
\Psi_\eta^{+,\mathrm{sep}}(P,\pi).
\]
Adding \(\eta\), multiplying by \(\tau^{-1}\), and taking the infimum over
\(\eta\) gives
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
\ge
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P).
\]
The comparison with \(\theta_U^{\mathrm{jnt}}(P)\) is the separated outer
inequality in Theorem~\ref{thm:joint-sharp-and-sep-bound}.

For the finite-class statement, take \(X=x_0\) almost surely,
\(\mathcal A=\{0,1\}\), and \(Y\in\{0,1,2\}\).  Write
\[
p_{aj}=P(Y=j\mid A=a,X=x_0),
\qquad
q_{aj}=p_{aj}r_{aj}.
\]
The actionwise bounded-weight constraints are
\[
\ell_a\le r_{aj}\le u_a,
\qquad
\sum_{j=0}^2 p_{aj}r_{aj}=1.
\]
Starting from the lower face \(q_{aj}=\ell_a p_{aj}\), allocate the remaining
mass to the largest outcomes first, respecting the caps
\((u_a-\ell_a)p_{aj}\).  The upper-tail vertex is
\[
q^\star_{a2}=\min\{u_ap_{a2},\,1-\ell_a(p_{a0}+p_{a1})\},
\]
\[
q^\star_{a1}=\min\{u_ap_{a1},\,1-q^\star_{a2}-\ell_ap_{a0}\},
\qquad
q^\star_{a0}=1-q^\star_{a1}-q^\star_{a2}.
\]
The exchange argument above shows that \(q_a^\star\) simultaneously minimizes
all lower CDF thresholds and maximizes
\(\sum_{j=0}^2 q_{aj}(j-\eta)_+\) for every \(\eta\in[0,2]\).

Mix the vertices using the policy:
\[
q^{\pi,\star}_j=\sum_{a\in\{0,1\}}\pi_a q^\star_{aj}.
\]
For every \(\eta\),
\[
\sup_{F\in\calF_\Gamma^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)
=
\sum_{j=0}^2 q^{\pi,\star}_j(j-\eta)_+
=
\Psi_\eta^{+,\mathrm{sep}}(P,\pi).
\]
The band and separated criteria are equal pointwise in \(\eta\), and their
infima are equal.
\end{proof}

\begin{proof}[Proof of Lemma~\ref{lem:lp-envelope}]
The case \(\Gamma=1\) is immediate because the only feasible weight is
\(r\equiv1\).  Consider \(\Gamma>1\).  Conditional on \((A=a,X=x)\), suppress
\((a,x)\) from the notation and write \(\ell=\ell_a(x)\), \(u=u_a(x)\), and
\(g=g_\eta\).  The upper operator is
\[
T=\sup_{\ell\le r\le u,\ \E r=1}\E[rg].
\]
Introduce a Lagrange multiplier \(\lambda\) for the normalization.  For fixed
\(\lambda\), the pointwise maximizer of
\(\E[r\{g-\lambda\}]+\lambda\) sets \(r=u\) when \(g>\lambda\) and \(r=\ell\)
when \(g<\lambda\).  Assumption~\ref{ass:lp-diff} supplies a unique canonical
threshold and rules out a first-order contribution from an atom or a
selection-dependent threshold interval.  The multiplier is chosen so that the
resulting \(r^*\) satisfies \(\E r^*=1\).  Hence
\[
T
=
\lambda+\E[r^*(g-\lambda)]
=
\E[\lambda+r^*(g-\lambda)]
=
\E[h].
\]

For a regular perturbation of the conditional law, the envelope theorem for a
linear program with a unique canonical active threshold gives the derivative
obtained by holding the optimizer fixed.  The mean-zero derivative is therefore
\(h(Y)-T\).  For a perturbation of \(e\), the conditional law is held fixed and
only the bounds move.  Since
\[
T
=
\lambda+
\E\{u(e)(g-\lambda)_+-\ell(e)(g-\lambda)_-\},
\]
the derivative with respect to \(e\) is
\[
u'(e)\E[(g-\lambda)_+]-\ell'(e)\E[(g-\lambda)_-].
\]
The identities \(u'(e)=1-\Gamma\) and \(\ell'(e)=1-\Gamma^{-1}\) follow by
differentiating \(u(e)=e+\Gamma(1-e)\) and
\(\ell(e)=e+(1-e)/\Gamma\).
\end{proof}

\begin{definition}[Corrected cross-fitted one-step endpoint estimator]\label{def:onestep}
Let \(g_\eta(y)=(y-\eta)_+\).  For each \((\eta,a,x)\), let
\(\lambda_{\eta,a}(x)\), \(h_{\eta,a}(y,x)\), \(T_{\eta,a}(x)\), and
\(\dot T_{\eta,a,e}(x)\) be the objects in Lemma~\ref{lem:lp-envelope}.  Define
\[
\chi_{\eta,\pi}(O)
=
\sum_{a\in\mathcal A}\pi(a\mid X)
\left[
T_{\eta,a}(X)
+
\frac{\one\{A=a\}}{e_a(X)}
\{h_{\eta,a}(Y,X)-T_{\eta,a}(X)\}
+
\dot T_{\eta,a,e}(X)\{\one\{A=a\}-e_a(X)\}
\right].
\]
Split the sample into fixed folds \(F_1,\ldots,F_K\).  On the training sample
outside fold \(F_k\), estimate
\[
\widehat\nu_\eta^{(-k)}
=
(\widehat e_a^{(-k)},\widehat\lambda_{\eta,a}^{(-k)},
 \widehat h_{\eta,a}^{(-k)},\widehat T_{\eta,a}^{(-k)},
 \widehat{\dot T}_{\eta,a,e}^{(-k)})_{a\in\mathcal A}
\]
and form \(\widehat\chi_{\eta,\pi}^{(-k)}\) by replacing each nuisance in
\(\chi_{\eta,\pi}\) by its fold-specific estimate.  Put
\[
\widehat{\mathcal C}_\eta^{\mathrm{sep}}
=
\eta+\tau^{-1}\frac1n
\sum_{k=1}^K\sum_{i\in F_k}
\widehat\chi_{\eta,\pi}^{(-k)}(O_i),
\]
\[
\widehat\eta
\in
\operatorname*{arg\,min}_{\eta\in[y_L,y_U]}
\widehat{\mathcal C}_\eta^{\mathrm{sep}},
\qquad
\widehat W_{\tau,\Gamma}^{\mathrm{sep}}(\pi)
=
\widehat{\mathcal C}_{\widehat\eta}^{\mathrm{sep}}.
\]
The fold-stacked variance estimator is
\[
\widehat\sigma_{\tau,\Gamma,\pi}^{2,\mathrm{sep}}
=
\frac1{n-1}\sum_{k=1}^K\sum_{i\in F_k}
\left\{
\widehat\eta+
\tau^{-1}\widehat\chi_{\widehat\eta,\pi}^{(-k)}(O_i)
-
\widehat W_{\tau,\Gamma}^{\mathrm{sep}}(\pi)
\right\}^2 .
\]
\end{definition}

\begin{proof}[Proof of Theorem~\ref{thm:onestep-limit}]
Let \(\eta_*=\eta_{\tau,\Gamma}(P,\pi)\) and
\(\Psi_*=\Psi_{\eta_*}^{+,\mathrm{sep}}(P,\pi)\).  First,
Lemma~\ref{lem:lp-envelope} and iterated expectation give
\[
\E[\chi_{\eta,\pi}(O)]
=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)T_{\eta,a}(X)
\right]
=
\Psi_\eta^{+,\mathrm{sep}}(P,\pi).
\]
The inverse-propensity term has conditional mean zero given \(X\), and the
propensity-derivative term has conditional mean zero because
\(\E[\one\{A=a\}-e_a(X)\mid X]=0\).

For fixed \(\eta_*\), cross-fitting makes the validation observations
independent of the nuisance estimates.  Assumption~\ref{ass:nuisance}, together
with the derivative representation in Lemma~\ref{lem:lp-envelope}, gives
\[
\frac1n\sum_{k=1}^K\sum_{i\in F_k}
\widehat\chi_{\eta_*,\pi}^{(-k)}(O_i)
=
\frac1n\sum_{i=1}^n
\chi_{\eta_*,\pi}(O_i)
+
o_p(n^{-1/2}).
\]
The key point is the cancellation of first-order drift.  The derivative with
respect to the conditional outcome law is represented by \(h_{\eta,a}\), and the
derivative with respect to \(e_a\) is represented by
\(\dot T_{\eta,a,e}\{\one(A=a)-e_a(X)\}\).  After these two linear terms are
included, the conditional mean remainder is bounded by the second-order
quantity stated in Assumption~\ref{ass:nuisance}; the conditional empirical
process remainder is \(o_p(n^{-1/2})\) by \(L_2(P)\) consistency, boundedness,
and the fixed number of folds.

Next consider the data-selected threshold.  The minimization in
Definition~\ref{def:onestep} is over all of \(\mathcal I\), so a local
expansion alone is not enough.  Assumption~\ref{ass:global-eta} supplies the
global step.  Fix \(\delta>0\).  On the event
\[
\sup_{\eta\in\mathcal I}
\left|
\widehat{\mathcal C}_{\eta}^{\mathrm{sep}}
-
\mathcal C_{\eta}^{+,\mathrm{sep}}(P,\pi)
\right|
<
\kappa_\delta/2,
\]
every \(\eta\) with \(|\eta-\eta_*|\ge\delta\) has
\[
\widehat{\mathcal C}_{\eta}^{\mathrm{sep}}
\ge
\mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)+\kappa_\delta/2
>
\widehat{\mathcal C}_{\eta_*}^{\mathrm{sep}}.
\]
Thus any global minimizer satisfies
\(\widehat\eta\to_p\eta_*\).

Once \(\widehat\eta\) is in the local neighborhood, the quadratic expansion in
Assumption~\ref{ass:global-eta} applies.  Write
\(d_n=\widehat\eta-\eta_*\) and
\(\ddot C_*=\partial_{\eta\eta}^2
\mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)>0\).  Since
\(\widehat\eta\) minimizes the sample criterion,
\[
0
\ge
\widehat{\mathcal C}_{\widehat\eta}^{\mathrm{sep}}
-
\widehat{\mathcal C}_{\eta_*}^{\mathrm{sep}}
=
\frac12\ddot C_* d_n^2+d_nZ_n+R_n(\widehat\eta).
\]
The bound on \(R_n\) and \(Z_n=O_p(n^{-1/2})\) imply
\(d_n=O_p(n^{-1/2})\).  Consequently,
\[
\mathcal C_{\widehat\eta}^{+,\mathrm{sep}}(P,\pi)
-
\mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)
=O_p(n^{-1})=o_p(n^{-1/2}),
\]
and the sample-process difference
\[
\left[
\widehat{\mathcal C}_{\widehat\eta}^{\mathrm{sep}}
-\mathcal C_{\widehat\eta}^{+,\mathrm{sep}}(P,\pi)
\right]
-
\left[
\widehat{\mathcal C}_{\eta_*}^{\mathrm{sep}}
-\mathcal C_{\eta_*}^{+,\mathrm{sep}}(P,\pi)
\right]
\]
equals \(d_nZ_n+R_n(\widehat\eta)=O_p(n^{-1})+o_p(n^{-1})\).  Therefore
threshold selection contributes no first-order term.

Combining the fixed-\(\eta_*\) expansion with the threshold step,
\[
\widehat W_{\tau,\Gamma}^{\mathrm{sep}}(\pi)
-
\underline W_{\tau,\Gamma}^{\mathrm{sep}}(\pi;P)
=
\tau^{-1}
\left[
\frac1n\sum_{i=1}^n
\chi_{\eta_*,\pi}(O_i)
-
\Psi_*
\right]
+
o_p(n^{-1/2}).
\]
Multiplication by \(\sqrt n\) gives the displayed asymptotic linear expansion.

For the variance estimator, define the ideal summand
\[
S_i=\eta_*+\tau^{-1}\chi_{\eta_*,\pi}(O_i).
\]
The preceding \(L_2(P)\) convergence and threshold consistency imply
\[
\frac1n\sum_{k=1}^K\sum_{i\in F_k}
\left[
\widehat\eta+
\tau^{-1}\widehat\chi_{\widehat\eta,\pi}^{(-k)}(O_i)
-
S_i
\right]^2
=o_p(1).
\]
The variables \(S_i\) are iid and bounded under
Assumptions~\ref{ass:iid-overlap}, \ref{ass:tail}, and \ref{ass:lp-diff}.  The
sample variance of \(S_i\) therefore converges to
\(\operatorname{Var}\{\varphi_{\tau,\Gamma,\pi}^{\mathrm{sep}}(O)\}\), and
replacing \(S_i\) by the fold-stacked estimated summands changes the variance by
\(o_p(1)\).
\end{proof}

\section{Sanity checks}
\subsubsection*{No finite locked full-class upper endpoint at \(\Gamma=1\)}
When \(\Gamma=1\), the latent odds-ratio restriction forces
\(Q(A=a\mid X,U)=e_a(X)\), but it still does not force
\(A\perp Y_{\mathcal A}\mid X\).  The construction in
Theorem~\ref{thm:joint-sharp-and-sep-bound} has constant \(U\), satisfies
\(\Gamma=1\), and sets all nonfactual policy-relevant outcomes to \(M\).  Hence
the locked full-class upper endpoint remains infinite whenever nonfactual
potential outcomes have no finite upper support restriction.

Inside the conditionally exchangeable subclass, by contrast,
\(\ell_a(x)=u_a(x)=1\) for every action and covariate value.  The only feasible
density ratio is \(r\equiv1\), and the joint-compatible subclass endpoint, the
separated endpoint, and the pointwise-band endpoint all collapse to
\[
\inf_{\eta\in[y_L,y_U]}
\left\{
\eta+\tau^{-1}
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\E_P[(Y-\eta)_+\mid A=a,X]
\right]\right\}.
\]
Thus \(\Gamma=1\) point-identifies the policy CVaR only after imposing the
conditional-exchangeability link.

\subsubsection*{Potential-outcome support is not an observed-support consequence}
Observed support says \(Y(A)\in[y_L,y_U]\).  In the locked full class it places
no restriction on \(Y(a)\) when \(A\ne a\).  Therefore the support-completion
criterion in Definition~\ref{def:bd-endpoints} is not a full-class endpoint; it
is the sharp endpoint after adding
\(Y(a)\in[y_L,y_U]\) for all actions.  In the conditionally exchangeable
subclass, finite odds-ratio overlap and the moment equation
\[
\E[p_a\one\{Y(a)\in B\}\mid X]
=
\E[\one\{A=a\}\one\{Y\in B\}\mid X]
\]
do imply support of \(Y(a)\) from support of the observed selected outcome,
because \(p_a>0\) almost surely.

\subsubsection*{Joint-compatibility check}
For two or more actions, a collection of actionwise ratios
\((r_a:a\in\mathcal A)\) can be feasible for the separated programs while
failing to come from one latent treatment rule.  The latent rule would require
\(p_a=e_a/r_a\) and hence
\[
\sum_{a\in\mathcal A}\frac{e_a}{r_a}=1.
\]
The separated program imposes only the actionwise box constraints and
normalizations.  This check explains why
Theorem~\ref{thm:joint-sharp-and-sep-bound} states the separated functional as a
conditionally exchangeable subclass outer bound unless joint realizability is
verified.

\subsubsection*{Finite band class}
Take \(X=x_0\) almost surely, \(e_0=e_1=1/2\), \(\Gamma=2\),
\(\pi_0=\pi_1=1/2\), and
\[
P(Y=0\mid A=a)=P(Y=1\mid A=a)=P(Y=2\mid A=a)=1/3,\qquad a=0,1.
\]
Then \(\ell_a=3/4\), \(u_a=3/2\), and the common upper-tail vertex is
\[
q_a^\star=(1/4,1/4,1/2),\qquad a=0,1.
\]
At \(\tau=1/2\), both the band comparator and the separated endpoint equal
\[
\inf_{\eta\in[0,2]}
\left\{\eta+2\sum_{j=0}^2q^{\pi,\star}_j(j-\eta)_+\right\}
=2,
\]
so \(\Delta_{\mathrm{nc}}^{\mathrm{sep}}(\pi;P)=0\).

\subsubsection*{Score check}
When \(\Gamma=1\), the dual threshold term is inactive, \(r^*\equiv1\), and
\(\dot T_{\eta,a,e}\equiv0\).  The canonical pseudo-outcome becomes
\(h_{\eta,a}(Y,X)=g_\eta(Y)\), so the corrected score reduces to the standard
policy AIPW generated-loss score
\[
\sum_{a\in\mathcal A}\pi(a\mid X)
\left[
m_{\eta,a}(X)
+
\frac{\one\{A=a\}}{e_a(X)}
\{g_\eta(Y)-m_{\eta,a}(X)\}
\right],
\]
where \(m_{\eta,a}(X)=\E[g_\eta(Y)\mid A=a,X]\).

\section{Counterexample or minimality check}
\subsubsection*{Finite full-class upper bounds require nonfactual support}
Fix any observed law satisfying the population-overlap condition.  For each
\(M>y_U\), the law \(Q_M\) constructed in
Theorem~\ref{thm:joint-sharp-and-sep-bound} has the same observed margin,
satisfies consistency, and satisfies the marginal sensitivity model with
constant \(U\).  It also gives positive policy probability to nonfactual
outcomes equal to \(M\).  Therefore any claimed finite upper bound written only
as a functional of the observed law \(P\), consistency, overlap, and the
odds-ratio MSM restriction is violated by taking \(M\) large enough.

\subsubsection*{Sensitivity is necessary for nonvacuous subclass actionwise bounds}
If Assumption~\ref{ass:msm} is dropped, the weight interval becomes unbounded
apart from nonnegativity and normalization in the conditionally exchangeable
actionwise analysis.  In a one-cell binary example with \(Y\in\{0,1\}\),
\(P(Y=1\mid A=a)=p>0\), and \(\pi(a)=1\), the largest compatible bad-outcome
mass under no sensitivity restriction is one: place all reweighting mass on
\(Y=1\).  The corresponding subclass robust CVaR endpoint is then
\[
\operatorname{CVaR}_{\tau}\{\mathrm{Bernoulli}(1)\}=1.
\]
Under finite \(\Gamma\), the corresponding bad-outcome mass is bounded by
\[
q_U=\min\{p\,u_a,\ 1-(1-p)\ell_a\},
\]
and the endpoint is \(\min\{1,q_U/\tau\}\), which is strictly below one whenever
\(q_U<\tau\).  Thus the odds-ratio marginal sensitivity bound is the condition
that prevents the no-restriction subclass upper endpoint from being vacuous.
For the larger locked full class, the no-finite-upper-endpoint result is
operative unless nonfactual support or conditional exchangeability is added.

\subsubsection*{Strict separated non-commutation is not witnessed by the finite class}
The two-action, three-outcome, one-covariate-cell class with monotone
upper-tail vertices does not witness a strict separated non-commutation gap.
The common vertex \(q_a^\star\) maximizes every generated loss
\((Y-\eta)_+\) and attains the pointwise lower CDF envelope at every threshold.
Therefore the band and separated nested criteria agree for every \(\eta\).
A strict gap, if present in a richer regime lacking a common least-favorable
tilt, requires a different witness.

\subsubsection*{Canonical LP differentiability is necessary for the one-step law}
The no-atom condition alone cannot replace Assumption~\ref{ass:lp-diff}.  If the
conditional support of \(g_\eta(Y)\) has a gap containing all thresholds that
solve the normalization equation, then the optimizing density ratio is the same
for every threshold in the gap but the dual pseudo-outcome
\(\lambda+r^*(g_\eta-\lambda)\) changes with the selected \(\lambda\).  The
cell functional remains directionally differentiable, but the displayed
influence function becomes selection-dependent.  The one-step theorem therefore
requires a canonical differentiable threshold selection rather than only the
absence of an atom at one selected threshold.

\subsubsection*{Local smoothness is necessary for the threshold-selected one-step law}
The differentiable interior optimizer and global localization clauses cannot be
dropped.  Take the point-identified special case \(\Gamma=1\), one action, no
covariates, \(Y\in\{0,1\}\), and \(\Pr(Y=1)=\tau=1/2\).  Then, for every
\(\eta\in[0,1]\),
\[
\eta+\tau^{-1}\E[(Y-\eta)_+]
=
\eta+2\cdot \frac12(1-\eta)=1.
\]
The whole interval \([0,1]\) minimizes the criterion.  The sample endpoint has a
kinked form,
\[
\widehat W=
\begin{cases}
2\bar Y_n, & \bar Y_n<1/2,\\
1, & \bar Y_n\ge 1/2,
\end{cases}
\]
up to tie conventions, so
\[
\sqrt n(\widehat W-1)
=
\min\{2\sqrt n(\bar Y_n-1/2),0\}+o_p(1).
\]
The limit is not a mean-zero Gaussian linear expansion with a fixed influence
function.

\section{Formalization checklist}
\subsection*{Probabilistic objects and assumptions}
\begin{description}[leftmargin=4.1cm,style=sameline]
\item[\(P\)] Observable law on \(O=(Y,A,X)\).  Role: source of all evaluable
population functionals.
\item[\(\mathcal M_\Gamma(P)\)] Locked full-data law class on
\((\{Y(a)\},A,X,U)\) without conditional exchangeability and without
nonfactual support.  Role: defines the target identified set; its upper endpoint
is infinite under unbounded nonfactual support.
\item[\(\mathcal M_\Gamma^{\mathrm{bd}}(P)\)] Support-restricted full-data law
class with \(Y(a)\in[y_L,y_U]\) for every action.  Role: class for the sharp
Manski support-completion endpoint.
\item[\(\mathcal M_\Gamma^{\mathrm{ce}}(P)\)] Conditionally exchangeable
subclass of \(\mathcal M_\Gamma(P)\).  Role: class represented by the joint
kernel program.
\item[\(\calH_\Gamma(P)\)] Conditional-kernel representation of
\(\mathcal M_\Gamma^{\mathrm{ce}}(P)\).  Role: exact sharp subclass endpoint
program with joint treatment-probability compatibility.
\item[\(e_a(x)\)] Propensity score.  Role: overlap, odds-ratio bounds, and
propensity derivative in the score.
\item[\(\ell_a(x),u_a(x)\)] Bounded-weight limits
\(e_a(x)+(1-e_a(x))/\Gamma\) and \(e_a(x)+\Gamma(1-e_a(x))\).  Role: cellwise
MSM optimization.
\item[\(q_\pi(P)\)] Policy probability of selecting a nonfactual action,
\(\E\sum_a\pi(a\mid X)\{1-e_a(X)\}\).  Role: witness mass for the locked
full-class unboundedness construction.
\item[\(\Theta_I(P)\)] Set
\(\{\operatorname{CVaR}_{\tau}(Y_Q(\pi)):Q\in\mathcal M_\Gamma(P)\}\).  Role:
locked partial-identification target.
\item[\(\Theta_I^{\mathrm{bd}}(P)\)] Set
\(\{\operatorname{CVaR}_{\tau}(Y_Q(\pi)):Q\in
\mathcal M_\Gamma^{\mathrm{bd}}(P)\}\).  Role: support-restricted target.
\item[\(\Theta_I^{\mathrm{ce}}(P)\)] Set
\(\{\operatorname{CVaR}_{\tau}(Y_Q(\pi)):Q\in
\mathcal M_\Gamma^{\mathrm{ce}}(P)\}\).  Role: subclass target for the joint
kernel and separated-bounding results.
\end{description}

\subsection*{Deterministic functionals}
\begin{description}[leftmargin=4.1cm,style=sameline]
\item[\(\mathfrak T_\Gamma^{+}\)] Actionwise upper bounded-weight operator.
Role: computable cellwise upper mean for generated losses.
\item[\(\mathfrak T_\Gamma^{-}\)] Actionwise lower bounded-weight operator.
Role: computable cellwise lower mean for generated losses.
\item[\(\theta_U^{\mathrm{bd}}\)] Sharp support-restricted upper endpoint.
Role: worst-case policy CVaR only after all potential outcomes are restricted
to \([y_L,y_U]\).
\item[\(\theta_L^{\mathrm{bd}}\)] Sharp support-restricted lower endpoint.
Role: best-case policy CVaR under the same explicit support restriction.
\item[\(\Psi_\eta^{+,\mathrm{sep}}\)] Separated worst-case expected excess loss
at threshold \(\eta\).  Role: outer upper CVaR criterion.
\item[\(\underline W_{\tau,\Gamma}^{\mathrm{sep}}\)] Separated nested upper
bound.  Role: conservative endpoint and inference target in
Theorem~\ref{thm:onestep-limit}.
\item[\(\theta_U^{\mathrm{jnt}}\)] Exact joint-compatible upper endpoint.  Role:
sharp upper endpoint of \(\Theta_I^{\mathrm{ce}}(P)\).
\item[\(\mathfrak F_\Gamma^{-},\mathfrak F_\Gamma^{+}\)] Actionwise CDF
envelopes.  Role: term-by-term definition of the pointwise band.
\item[\(W_{\tau,\Gamma}^{\mathrm{band}}\)] Pointwise-CDF-band CVaR comparator.
Role: benchmark in Theorem~\ref{thm:band}.
\end{description}

\subsection*{Estimator and derivative objects}
\begin{description}[leftmargin=4.1cm,style=sameline]
\item[\(\lambda_{\eta,a}(x)\)] Canonical dual threshold of the cellwise
bounded-weight linear program.  Role: determines the active least-favorable
tilt; uniqueness and differentiable selection are inference assumptions.
\item[\(r_{\eta,a}^*(y,x)\)] Least-favorable density ratio.  Role: optimizer of
\(\mathfrak T_\Gamma^+\) for \(g_\eta\).
\item[\(h_{\eta,a}(y,x)\)] Canonical dual pseudo-outcome
\(\lambda+r^*(g_\eta-\lambda)\).  Role: derivative with respect to the
conditional outcome law.
\item[\(\dot T_{\eta,a,e}(x)\)] Derivative of the MSM operator with respect to
\(e_a(x)\).  Role: propensity contribution in the corrected score.
\item[\(\chi_{\eta,\pi}(O)\)] Corrected observed-data score for
\(\Psi_\eta^{+,\mathrm{sep}}\).  Role: first-order summand in the one-step
expansion.
\item[\(\widehat W_{\tau,\Gamma}^{\mathrm{sep}}(\pi)\)] Cross-fitted one-step
endpoint estimator.  Role: estimator map from the observed sample.
\item[\(\varphi_{\tau,\Gamma,\pi}^{\mathrm{sep}}\)] Mean-zero influence
function.  Role: limit law and variance target.
\end{description}

\section{Conclusion and references}
Under the locked restrictions, the full-class MSM-CVaR upper endpoint is not the
nested actionwise MSM functional and is not the finite support-completion
functional.  Without a support restriction on nonfactual potential outcomes, the
locked full-class upper endpoint is infinite.  If the explicit support
restriction \(Y(a)\in[y_L,y_U]\) is added, the sharp finite endpoint is the
Manski support-completion functional \(\theta_U^{\mathrm{bd}}(P)\).  The
joint-compatible program \(\theta_U^{\mathrm{jnt}}(P)\) is sharp for the
conditionally exchangeable subclass, and the separated nested MSM-CVaR
functional is a valid and evaluable outer bound for that subclass.  Its
universal sharpness still requires a joint-realizability condition not supplied
by the actionwise bounded-weight constraints.  The pointwise-band comparator is
conservative relative to the separated bound once its CDF envelopes are defined
term-by-term, and it equals the separated bound in the finite monotone-tilt
class.  The corrected one-step estimator for the separated bound uses the
canonical LP pseudo-outcome, includes the propensity derivative of the MSM
operator, and has the stated asymptotic linear expansion under explicit
canonical LP differentiability, global localization, local smoothness, and
second-order nuisance rates.

\subsection*{References}
\begin{thebibliography}{99}

\bibitem[Dorn and Guo(2021)]{DornGuo2021QuantileBalancing}
Dorn, J. and Guo, K. (2021).
\newblock Sharp sensitivity analysis for inverse propensity weighting via
quantile balancing.
\newblock \emph{Journal of the American Statistical Association},
arXiv:2102.04543.

\bibitem[Dorn, Guo, and Kallus(2021)]{DornGuoKallus2021DoublySharp}
Dorn, J., Guo, K., and Kallus, N. (2021).
\newblock Doubly-valid/doubly-sharp sensitivity analysis for causal inference
with unmeasured confounding.
\newblock arXiv:2112.11449.

\bibitem[Fan, Qi, and Xu(2025)]{FanQiXu2025AlphaExpectedWelfare}
Fan, Y., Qi, Y., and Xu, G. (2025).
\newblock Policy learning with alpha-expected welfare.
\newblock arXiv:2505.00256.

\bibitem[Frauen, Melnychuk, and Feuerriegel(2023)]{FrauenMelnychukFeuerriegel2023SharpCSA}
Frauen, D., Melnychuk, V., and Feuerriegel, S. (2023).
\newblock Sharp bounds for generalized causal sensitivity analysis.
\newblock arXiv:2305.16988.

\bibitem[Hess et al.(2025)]{HessFrauenMelnychukFeuerriegel2025SharpOPE}
Hess, K., Frauen, D., Melnychuk, V., and Feuerriegel, S. (2025).
\newblock Efficient and sharp off-policy learning under unobserved confounding.
\newblock arXiv:2502.13022.

\bibitem[Imbens and Manski(2004)]{ImbensManski2004PartialIDCI}
Imbens, G. W. and Manski, C. F. (2004).
\newblock Confidence intervals for partially identified parameters.
\newblock \emph{Econometrica}, 72(6):1845--1857.

\bibitem[Jin et al.(2025)]{JinXuZhengZhou2025RobustEfficientPolicy}
Jin, Z., Xu, G., Zheng, X., and Zhou, Y. (2025).
\newblock Robust and efficient policy learning under the marginal sensitivity
model.
\newblock arXiv:2507.20550.

\bibitem[Kallus and Zhou(2018)]{KallusZhou2018ConfoundingRobustPolicy}
Kallus, N. and Zhou, A. (2018).
\newblock Confounding-robust policy improvement.
\newblock \emph{NeurIPS}, arXiv:1805.08593.

\bibitem[Kallus and Zhou(2021)]{KallusZhou2021}
Kallus, N. and Zhou, A. (2021).
\newblock Minimax-optimal policy learning under unobserved confounding.
\newblock \emph{Management Science}, 67(5):2870--2890.

\bibitem[Manski(1990)]{Manski1990NonparametricBounds}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review}, 80(2):319--323.

\bibitem[Masten, Poirier, and Ren(2025)]{MastenPoirierRen2025RelaxingUnconfoundedness}
Masten, M. A., Poirier, A., and Ren, M. (2025).
\newblock A general approach to relaxing unconfoundedness.
\newblock arXiv:2501.15400.

\bibitem[Rockafellar and Uryasev(2000)]{RockafellarUryasev2000CVaR}
Rockafellar, R. T. and Uryasev, S. (2000).
\newblock Optimization of conditional value-at-risk.
\newblock \emph{Journal of Risk}, 2(3):21--41.

\bibitem[Tan(2006)]{Tan2006MSM}
Tan, Z. (2006).
\newblock A distributional approach for causal inference using propensity
scores.
\newblock \emph{Journal of the American Statistical Association},
101(476):1619--1637.

\end{thebibliography}

\end{document}
