% file-plan: bypass-justified: the substrate survey found no direct fixed-policy MSM-CVaR primitive; this fragment works at the paper-level observable-law, marginal-sensitivity, and minimax-functional layer and cites no implementation files.

\paragraph{\S9-fragment-statement for the labelled solve target \texttt{nested-endpoint}.}
\paragraph{Conjecture restated verbatim.}\label{conj:nested-endpoint}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail}, for every fixed policy \(\pi\),
\[
\sup_{Q\in\mathcal M_\Gamma(P)}
\mathrm{CVaR}_\tau\{Y_Q(\pi)\}
=
\inf_{\eta\in\mathcal I}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,X\}
\right]\right\}.
\]
The equality is sharp: every value above the right-hand side is valid, and no smaller endpoint is valid over \(\mathcal M_\Gamma(P)\).

\begin{theorem}[Sharp nested MSM-CVaR upper endpoint]\label{thm:nested-endpoint}
\paragraph{Verdict headline.}
Confirmed nested endpoint. Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail}, for every fixed policy \(\pi\), \(\sup_{Q\in\mathcal M_\Gamma(P)}\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}\) equals the computable nested functional
\[
\underline W_{\tau,\Gamma}(\pi;P)=
\inf_{\eta\in[y_L,y_U]}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,X\}
\right]\right\}.
\]
Equivalently, if \(e_a(x)=P(A=a\mid X=x)\), \(\ell_a(x)=e_a(x)+(1-e_a(x))/\Gamma\), and \(u_a(x)=e_a(x)+\Gamma(1-e_a(x))\), then for each nonnegative generated cell loss \(Z=(Y-\eta)_+\),
\[
\mathfrak T_{\Gamma}^{+}(Z\mid a,x)=
\sup_{\ell_a(x)\le r\le u_a(x),\, \E_P[r(Y)\mid A=a,X=x]=1}
\E_P[r(Y)Z\mid A=a,X=x],
\]
and the supremum is attained by the monotone least-favorable tilt that assigns weight \(u_a(x)\) to the largest values of \(Z\), weight \(\ell_a(x)\) to the smallest values of \(Z\), and only splits mass at the single threshold needed to make the conditional mean of \(r\) equal one. Thus \(\underline W_{\tau,\Gamma}(\pi;P)\) is the sharp upper endpoint of \(\Theta_I(P)\): every \(c\ge \underline W_{\tau,\Gamma}(\pi;P)\) is a valid upper bound for \(\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}\) over \(Q\in\mathcal M_\Gamma(P)\), and every \(c<\underline W_{\tau,\Gamma}(\pi;P)\) is violated by some compatible law.
\end{theorem}

\paragraph{\S13-refutation-attempt.}
The partial-identification refutation primitive is the two-strata response-type LP.  First collapse
\(X\) to a point and take a single active action \(a\) with \(\pi(a)=1\).  Let \(Y\in\{0,1\}\) and
\(p=P(Y=1\mid A=a)\).  Any MSM completion of this one cell is represented by two weights
\[
r_0=r(0),\qquad r_1=r(1),
\]
subject to
\[
\ell\le r_0,r_1\le u,\qquad (1-p)r_0+pr_1=1,
\]
where \(\ell=e_a+(1-e_a)/\Gamma\) and \(u=e_a+\Gamma(1-e_a)\).  The feasible response-type
probability of a bad policy outcome is
\[
q=Q\{Y(a)=1\}=pr_1
\]
with LP interval
\[
q\in
\left[
\max\{p\ell,\,1-(1-p)u\},
\min\{pu,\,1-(1-p)\ell\}
\right].
\]
For a fixed \(\eta\in[0,1]\),
\[
\sup_Q\E_Q[(Y(a)-\eta)_+]
=q_U(1-\eta),
\qquad
q_U=\min\{pu,\,1-(1-p)\ell\},
\]
and the nested endpoint searched by the conjecture is
\[
\inf_{\eta\in[0,1]}
\left\{\eta+\tau^{-1}q_U(1-\eta)\right\}
=\min\{1,q_U/\tau\}.
\]
The actual left-hand side of the conjecture is also
\[
\sup_{q\le q_U}\operatorname{CVaR}_{\tau}\{\mathrm{Bernoulli}(q)\}
=\min\{1,q_U/\tau\}.
\]
Thus the binary response-type LP finds no witness outside the conjectured interval.

The same LP check with two active actions and binary potential outcomes also fails to refute the
claim.  With fixed \(x\), each action contributes a feasible Bernoulli bad-outcome mass \(q_a\), and
the policy-induced binary outcome has bad mass \(q_\pi=\sum_a\pi(a\mid x)q_a\).  The LP objective
for each generated loss \((Y-\eta)_+\) and the Bernoulli CVaR are both monotone in the same scalar
\(q_\pi\).  Hence every vertex that maximizes the nested \(\eta\)-indexed loss also maximizes the
policy bad-outcome probability within the searched binary response-type space.  The primitive
therefore does not produce a refuting law; it instead points to the positive proof route: characterize
the MSM ambiguity set by bounded cell weights, apply the sharp actionwise tilt to each generated
loss, and interchange the outer supremum with the Rockafellar--Uryasev minimization.

\paragraph{\S10 Interpretation.}
The theorem says that the robust tail-risk endpoint is not obtained by first building a loose
pointwise distributional band for \(Y(\pi)\) and then applying a CVaR formula to that band.  For
each candidate tail threshold \(\eta\), the generated loss \((Y-\eta)_+\) is an ordinary nonnegative
outcome.  The marginal sensitivity restriction then has a sharp, actionwise, least-favorable
conditional mean for that generated loss.  Averaging those sharp cell means under the fixed policy
\(\pi\) gives the largest compatible expected excess loss above \(\eta\).  The CVaR endpoint is the
minimum, over \(\eta\), of threshold plus scaled worst-case excess loss.

The tightening restriction is Assumption~\ref{ass:msm}.  When \(\Gamma=1\), the weight interval
collapses to \(r\equiv1\), so the formula reduces to the ordinary identified policy CVaR under
consistency and overlap.  As \(\Gamma\) grows, the interval \([\ell_a(x),u_a(x)]\) widens, allowing
more mass to be shifted toward high values of \((Y-\eta)_+\), and the endpoint increases toward the
natural no-restriction tail bound.  Bounded support and tail regularity in Assumption~\ref{ass:tail}
make the one-dimensional minimization well defined and ensure that the monotone tilt is evaluable
from the observed conditional laws.

\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:nested-endpoint}]
Fix the policy \(\pi\).  The proof uses three ingredients: the odds-ratio-to-weight
reparameterization of the marginal sensitivity model of \cite{Tan2006MSM}, the sharp cellwise
policy-value construction adapted from \cite{HessFrauenMelnychukFeuerriegel2025SharpOPE}, and the
Rockafellar--Uryasev variational formula for CVaR \cite{RockafellarUryasev2000CVaR}.

First fix an action \(a\) and a covariate value \(x\) with \(e_a(x)>0\).  For any compatible law
\(Q\in\mathcal M_\Gamma(P)\), consistency in Assumption~\ref{ass:consistency} makes the observed
cell law \(P(Y\in\cdot\mid A=a,X=x)\) the factual selected law of \(Y(a)\).  If
\[
r_{Q,a,x}(Y)=
\frac{dQ\{Y(a)\in\cdot\mid X=x\}}
     {dP\{Y\in\cdot\mid A=a,X=x\}}(Y),
\]
then Bayes' rule gives \(r_{Q,a,x}=e_a(x)/Q(A=a\mid X=x,U)\) after representing the latent
heterogeneity by \(U\).  Assumption~\ref{ass:msm} is equivalent to
\[
\ell_a(x)\le r_{Q,a,x}(Y)\le u_a(x),
\qquad
\E_P[r_{Q,a,x}(Y)\mid A=a,X=x]=1,
\]
where
\[
\ell_a(x)=e_a(x)+\frac{1-e_a(x)}{\Gamma},
\qquad
u_a(x)=e_a(x)+\Gamma\{1-e_a(x)\}.
\]
The lower bound is at most one and the upper bound is at least one because \(\Gamma\ge1\); overlap in
Assumption~\ref{ass:iid-overlap} rules out division by zero on the support used by \(\pi\).

Therefore, for every nonnegative measurable cell loss \(Z=Z(Y)\),
\[
\E_Q[Z(Y(a))\mid X=x]
=
\E_P[r_{Q,a,x}(Y)Z(Y)\mid A=a,X=x]
\le
\mathfrak T_\Gamma^+(Z\mid a,x).
\]
Taking \(Z_\eta(Y)=(Y-\eta)_+\), multiplying by \(\pi(a\mid x)\), summing over the finite action set,
and integrating over \(P_X\) gives, for each fixed \(\eta\in[y_L,y_U]\),
\[
\E_Q[(Y_Q(\pi)-\eta)_+]
\le
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right].
\]
Combining this inequality with the Rockafellar--Uryasev identity
\[
\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}
=
\inf_{\eta\in[y_L,y_U]}
\left\{\eta+\tau^{-1}\E_Q[(Y_Q(\pi)-\eta)_+]\right\}
\]
yields the upper-bound half
\[
\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}
\le
\inf_{\eta\in[y_L,y_U]}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right]\right\}.
\]
Since this holds for every \(Q\in\mathcal M_\Gamma(P)\), the displayed nested functional is a valid
upper endpoint.

It remains to prove that no smaller endpoint is valid.  Let
\[
\mathcal R_\Gamma(P)
\]
be the set of all measurable selections of cell weights
\(\{r_{a,x}:a\in\mathcal A,x\in\mathcal X\}\) satisfying
\(\ell_a(x)\le r_{a,x}\le u_a(x)\) and
\(\E_P[r_{a,x}(Y)\mid A=a,X=x]=1\).  This set is convex because the constraints are linear in the
weights, and it is compact for the present bounded-loss optimization in the weak topology induced by
bounded measurable losses.  Assumption~\ref{ass:tail} supplies boundedness of \(Z_\eta\) and
restricts \(\eta\) to the compact interval \([y_L,y_U]\).  For \(r\in\mathcal R_\Gamma(P)\), define
\[
G(r,\eta)
=
\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\E_P\{r_{a,X}(Y)(Y-\eta)_+\mid A=a,X\}
\right],
\]
where the outer expectation is over \(X\) and the inner expectation is over the observed cell law
\(P(Y\mid A=a,X)\).  For
fixed \(r\), \(G(r,\eta)\) is continuous and convex in \(\eta\); for fixed \(\eta\), it is affine in
\(r\).  Sion's minimax theorem therefore gives
\[
\sup_{r\in\mathcal R_\Gamma(P)}\inf_{\eta\in[y_L,y_U]}G(r,\eta)
=
\inf_{\eta\in[y_L,y_U]}\sup_{r\in\mathcal R_\Gamma(P)}G(r,\eta).
\]
The right-hand side is exactly the nested functional because the supremum over \(r\) separates by
\((a,x)\) and is, by definition, \(\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,x\}\).

For the left-hand side, the sharp MSM construction used for the mean policy-value endpoint in
\cite{HessFrauenMelnychukFeuerriegel2025SharpOPE} realizes every extremal measurable weight
selection, up to arbitrary \(\varepsilon>0\), by a full-data law in \(\mathcal M_\Gamma(P)\) with the
same observed margin \(P\).  The construction introduces latent heterogeneity carrying the selected
cell ranks and then assigns treatment probabilities whose one-vs-rest odds ratios saturate the
MSM faces; consistency keeps the factual cell law equal to \(P(Y\mid A=a,X=x)\).  Consequently
\[
\sup_{r\in\mathcal R_\Gamma(P)}\inf_{\eta\in[y_L,y_U]}G(r,\eta)
=
\sup_{Q\in\mathcal M_\Gamma(P)}
\inf_{\eta\in[y_L,y_U]}
\left\{\eta+\tau^{-1}\E_Q[(Y_Q(\pi)-\eta)_+]\right\}.
\]
The inner infimum is \(\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}\) by the same
Rockafellar--Uryasev identity.  Hence
\[
\sup_{Q\in\mathcal M_\Gamma(P)}
\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}
=
\inf_{\eta\in[y_L,y_U]}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right]\right\}.
\]

Finally, the formula for \(\mathfrak T_\Gamma^+\) is computable.  Conditional on \((A=a,X=x)\), the
optimization
\[
\sup_{\ell_a(x)\le r\le u_a(x),\ \E r=1}\E[rZ]
\]
is a linear program over bounded densities.  Its extreme points place the upper weight \(u_a(x)\)
on the largest values of \(Z\), the lower weight \(\ell_a(x)\) on the smallest values, and, only if
the relevant conditional distribution has an atom at the cutoff, split that atom to enforce
\(\E r=1\).  This is the rearrangement/Hardy--Littlewood form of the sharp marginal-sensitivity
tilt used by \cite{DornGuo2021QuantileBalancing} and \cite{FrauenMelnychukFeuerriegel2023SharpCSA}.
Assumption~\ref{ass:tail} excludes degeneracy at the active thresholds, so no ambiguous split is
needed at the minimizer.  Thus the endpoint is a one-dimensional minimization of observable
conditional quantile and truncated-moment functionals.

Sharpness follows immediately from the equality.  If \(c\ge\underline W_{\tau,\Gamma}(\pi;P)\),
then the upper-bound half shows \(c\) bounds every feasible \(\operatorname{CVaR}_{\tau}\).  If
\(c<\underline W_{\tau,\Gamma}(\pi;P)\), the equality and the epsilon-attainability of the MSM
extreme-point construction give a compatible law \(Q_c\in\mathcal M_\Gamma(P)\) with
\(\operatorname{CVaR}_{\tau}\{Y_{Q_c}(\pi)\}>c\).  Thus no smaller upper endpoint is valid.
\end{proof}

\paragraph{\S12 Sanity check.}
Take the point-identification corner \(\Gamma=1\).  Then
\[
\ell_a(x)=u_a(x)=1
\]
for every action and covariate value.  The only feasible cell weight is \(r\equiv1\), so
\[
\mathfrak T_{\Gamma=1}^{+}\{(Y-\eta)_+\mid a,x\}
=
\E_P[(Y-\eta)_+\mid A=a,X=x].
\]
The theorem reduces to
\[
\sup_{Q\in\mathcal M_1(P)}
\operatorname{CVaR}_{\tau}\{Y_Q(\pi)\}
=
\inf_{\eta\in[y_L,y_U]}
\left\{\eta+\tau^{-1}
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\E_P[(Y-\eta)_+\mid A=a,X]
\right]\right\}.
\]
By consistency and overlap, the inner expectation is exactly
\(\E_P[(Y(\pi)-\eta)_+]\) under the identified policy law.  Hence the display is the ordinary
Rockafellar--Uryasev formula for the identified policy CVaR.  This is the expected collapse of the
partial-identification interval to a point when the marginal sensitivity parameter rules out hidden
confounding.

\paragraph{\S13 Counterexample/minimality check.}
The sensitivity restriction is the minimal tightening condition.  If Assumption~\ref{ass:msm} is
dropped, the weight interval becomes unbounded apart from nonnegativity and normalization.  In a
one-cell binary example with \(Y\in\{0,1\}\), \(P(Y=1\mid A=a)=p\), and \(\pi(a)=1\), the largest
compatible bad-outcome mass under no sensitivity restriction is one whenever the observed cell has
any bad-outcome support \(p>0\): place all reweighting mass on \(Y=1\).  The robust CVaR endpoint is
then
\[
\operatorname{CVaR}_{\tau}\{\mathrm{Bernoulli}(1)\}=1.
\]
Under a finite \(\Gamma\), the same endpoint is
\[
\min\left\{1,\frac{q_U}{\tau}\right\},
\qquad
q_U=\min\{p\,u_a,\ 1-(1-p)\ell_a\},
\]
which is strictly below one whenever \(q_U<\tau\).  Thus the odds-ratio marginal sensitivity bound
is exactly the condition that prevents the natural Manski no-restriction upper endpoint from being
vacuous.  Overlap in Assumption~\ref{ass:iid-overlap} is also minimal for the displayed map: if
\(\pi(a\mid x)>0\) but \(e_a(x)=0\), the observed conditional law
\(P(Y\mid A=a,X=x)\) and hence \(\mathfrak T_\Gamma^+(\cdot\mid a,x)\) are not evaluable from \(P\).
