% file-plan: bypass-justified: the substrate survey found no direct fixed-policy MSM-CVaR primitive; this fragment works at the paper-level observable-law, pointwise-band, marginal-sensitivity, and finite response-type LP layer and cites no implementation files.

\paragraph{\S9-fragment-statement for the labelled solve target \texttt{noncommutation}.}
\paragraph{Original conjecture restated verbatim.}\label{conj:noncommutation}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail},
\[
\Delta_{\mathrm{nc}}(\pi;P)=
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
-\underline W_{\tau,\Gamma}(\pi;P)\geq 0.
\]
Moreover, there is a two-action, three-outcome, one-covariate-cell class satisfying strict overlap
and \(1<\Gamma<\infty\) on which \(\Delta_{\mathrm{nc}}(\pi;P)>0\).  Equality holds when the same
monotone least-favorable MSM tilt is simultaneously optimal for all \(\eta\) in the active
subgradient set of \(\mathcal C_\eta(P,\pi)\).

\begin{theorem}[Rate-corrected pointwise-band noncommutation]\label{thm:noncommutation-zero-finite-class}
\paragraph{Verdict headline.}
Confirmed after rate/value correction.  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail},
the pointwise-band comparator is conservative relative to the sharp nested MSM-CVaR endpoint:
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
\ge
\underline W_{\tau,\Gamma}(\pi;P).
\]
In the proposed two-action, three-outcome, one-covariate-cell strict-overlap MSM response-type
class with \(1<\Gamma<\infty\), the common monotone upper-tail tilt is simultaneously optimal for
every generated loss \((Y-\eta)_+\).  Therefore
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
=
\underline W_{\tau,\Gamma}(\pi;P),
\qquad
\Delta_{\mathrm{nc}}(\pi;P)=0
\]
throughout that class.  The refuted strict-existence clause is corrected from a positive gap to the
witness-implied zero gap; no new hypothesis is added.
\end{theorem}

\paragraph{\S10-assumptions and mend.}
The mend is a rate/value correction, not an added regularity condition.  The law-level assumptions
remain Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail}.  The finite-class equality clause
specializes these assumptions to
\[
X=x_0\ \text{a.s.},\qquad
\mathcal A=\{0,1\},\qquad
Y\in\{0,1,2\},\qquad
0<e_a=P(A=a\mid X=x_0)<1,
\]
with a fixed \(1<\Gamma<\infty\) and fixed policy weights
\(\pi_a=\pi(a\mid x_0)\).  The repair replaces only the false finite-class claim
\(\Delta_{\mathrm{nc}}>0\) by the exact value \(\Delta_{\mathrm{nc}}=0\) proved by the response-type
LP.  This is the standard sharp marginal-sensitivity bounded-weight/rearrangement calculation used
in quantile balancing for Tan's marginal sensitivity model
\cite{DornGuo2021QuantileBalancing}.

\paragraph{\S11-proof.}
\begin{proof}[Proof of Theorem~\ref{thm:noncommutation-zero-finite-class}]
First prove the retained nonnegativity inequality.  For any compatible full-data law
\(Q\in\mathcal M_\Gamma(P)\), let \(F_Q\) be the distribution function of \(Y_Q(\pi)\).  Since
\(\underline F_\Gamma(\cdot\mid P,\pi)\) and \(\overline F_\Gamma(\cdot\mid P,\pi)\) are the
pointwise sharp threshold envelopes, \(F_Q\in\mathcal F_\Gamma^{\mathrm{pt}}(P,\pi)\).  Hence, for
every \(\eta\in[y_L,y_U]\),
\[
\sup_{F\in\mathcal F_\Gamma^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)
\ge
\sup_{Q\in\mathcal M_\Gamma(P)}
\E_Q[(Y_Q(\pi)-\eta)_+].
\]
The fixed-\(\eta\) part of the sharp nested-endpoint theorem identifies the right-hand side with
\[
\Psi_\eta^+(P,\pi)
=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right].
\]
Adding \(\eta\), multiplying the excess-loss term by \(\tau^{-1}\), and taking the infimum over
\(\eta\in[y_L,y_U]\) gives
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
\ge
\inf_{\eta\in[y_L,y_U]}
\{\eta+\tau^{-1}\Psi_\eta^+(P,\pi)\}
=
\underline W_{\tau,\Gamma}(\pi;P),
\]
where the last equality is the confirmed nested endpoint.

It remains to compute the value in the proposed finite class.  Fix one covariate cell
\(X=x_0\), actions \(a\in\{0,1\}\), and outcomes \(j\in\{0,1,2\}\).  Write
\[
p_{aj}=P(Y=j\mid A=a,X=x_0),\qquad
q_{aj}=p_{aj}r_{aj}.
\]
The marginal sensitivity model is the actionwise bounded-weight LP
\[
\ell_a\le r_{aj}\le u_a,\qquad
\sum_{j=0}^2 p_{aj}r_{aj}=1,
\]
where
\[
\ell_a=e_a+\frac{1-e_a}{\Gamma},
\qquad
u_a=e_a+\Gamma(1-e_a).
\]
Strict overlap and \(1<\Gamma<\infty\) give \(0<\ell_a\le1\le u_a<\infty\).

For each action \(a\), start from the lower face \(q_{aj}=\ell_a p_{aj}\) and allocate the remaining
mass \(1-\ell_a\) to the largest outcomes first, respecting the caps
\((u_a-\ell_a)p_{aj}\).  The resulting upper-tail vertex is
\[
q^\star_{a2}=\min\{u_ap_{a2},\,1-\ell_a(p_{a0}+p_{a1})\},
\]
\[
q^\star_{a1}=\min\{u_ap_{a1},\,1-q^\star_{a2}-\ell_ap_{a0}\},
\qquad
q^\star_{a0}=1-q^\star_{a1}-q^\star_{a2}.
\]
This vertex is feasible.  It is also simultaneously optimal for every lower CDF threshold and every
generated loss.  Indeed, if a feasible vector \(q_a\) puts an extra \(\varepsilon\)-unit above the
lower face on a smaller outcome while a larger outcome is not at its cap, shifting that
\(\varepsilon\)-unit upward preserves normalization and all box constraints, weakly decreases every
lower CDF value \(\sum_{j\le k}q_{aj}\), and weakly increases every increasing objective.  Repeating
the exchange until no such pair remains terminates at \(q_a^\star\).  Therefore \(q_a^\star\)
simultaneously minimizes \(q_{a0}\) and \(q_{a0}+q_{a1}\), and simultaneously maximizes
\[
\sum_{j=0}^2 q_{aj}(j-\eta)_+
\]
for every \(\eta\in[0,2]\).

Mix the actionwise vertices with the fixed policy:
\[
q^{\pi,\star}_j=\sum_{a\in\{0,1\}}\pi_a q^\star_{aj}.
\]
The associated CDF \(F_\pi^\star\) is first-order-stochastically maximal among the policy CDFs in
the pointwise band, because it attains the sharp lower CDF envelope at each threshold.  Since
\((y-\eta)_+\) is increasing in \(y\),
\[
\sup_{F\in\mathcal F_\Gamma^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)
=
\sum_{j=0}^2 q^{\pi,\star}_j(j-\eta)_+.
\]
The nested MSM generated-loss endpoint gives the same expression:
\[
\E_P\left[
\sum_{a\in\{0,1\}}\pi_a
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right]
=
\sum_{j=0}^2 q^{\pi,\star}_j(j-\eta)_+.
\]
Thus the band and nested criteria are equal for every \(\eta\in[0,2]\).  Taking the same
Rockafellar--Uryasev infimum over \(\eta\) on both sides yields
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
=
\underline W_{\tau,\Gamma}(\pi;P),
\qquad
\Delta_{\mathrm{nc}}(\pi;P)=0
\]
throughout the proposed finite class.
\end{proof}

\paragraph{\S12-guard checks.}
\textbf{Vacuity.}  The mended class is nonempty.  For example, take \(X=x_0\) a.s.,
\(e_0=e_1=1/2\), \(\Gamma=2\), \(\pi_0=\pi_1=1/2\), and
\[
P(Y=0\mid A=a)=P(Y=1\mid A=a)=P(Y=2\mid A=a)=1/3,\qquad a=0,1.
\]
Then \(\ell_a=3/4\), \(u_a=3/2\), and the common upper-tail vertex is
\[
q_a^\star=(1/4,1/4,1/2),\qquad a=0,1.
\]

\textbf{Substance.}  The motivating regime is retained: fixed-policy robust MSM-CVaR welfare under
strict overlap, \(1<\Gamma<\infty\), and the same pointwise-CDF band comparator.  The repair does not
exclude the two-action, three-outcome, one-covariate-cell class; it computes the correct gap in that
class.

\textbf{Naturalness.}  No new hypothesis is introduced.  The calculation is the usual bounded
density-ratio LP and monotone rearrangement argument for Tan-style marginal sensitivity, as used in
sharp quantile-balancing partial identification \cite{DornGuo2021QuantileBalancing}.  The mend is
therefore a correction of the asserted value, not monster-barring.

\paragraph{\S13-original-witness after the mend.}
The original refutation witness no longer applies as a counterexample, because the mended theorem
asserts exactly what the witness proves.  In the concrete member
\[
e_0=e_1=1/2,\qquad \Gamma=2,\qquad \pi_0=\pi_1=1/2,\qquad
P(Y=j\mid A=a)=1/3,
\]
the upper-tail vertex \(q_a^\star=(1/4,1/4,1/2)\) is common to every \(\eta\).  At
\(\tau=1/2\), both the band comparator and the nested endpoint equal
\[
\inf_{\eta\in[0,2]}
\left\{\eta+2\sum_{j=0}^2q^{\pi,\star}_j(j-\eta)_+\right\}
=2,
\]
so \(\Delta_{\mathrm{nc}}(\pi;P)=0\).  The old strict-existence clause is therefore not salvaged;
it is replaced by the positive equality certificate supplied by the same finite LP.  A strict gap,
if one exists in a richer regime lacking a common least-favorable tilt, is a separate open target
and is not asserted here.
