% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_cvar\_welfare\_msm\_v1, specialization=robust\_cvar\_policy
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_core.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_cvar\_welfare\_msm\_v1} / \texttt{robust\_cvar\_policy}%
  \\ \large\textit{Sharp nested MSM bounds and one-step inference for CVaR policy welfare}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification proposal with tuple
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R,\mathsf B)
=
(\texttt{pid\_cvar\_welfare\_msm\_v1},
\texttt{robust\_cvar\_policy},P,\underline W_{\tau,\Gamma}(\pi;P),
\mathcal R_{\mathrm{MSM}},\mathsf B_{\mathrm{CVaR}}).
\]
Here \(P\) is the observed law of \(O=(Y,A,X)\), where \(A\in\mathcal A\) is a finite action, \(X\in\mathcal X\) is a covariate vector, and lower \(Y\) is better.  A fixed stochastic policy is \(\pi(a\mid x)\), the sensitivity parameter is \(\Gamma\geq 1\), and the tail fraction is \(\tau\in(0,1)\).  The target \(\theta=\underline W_{\tau,\Gamma}(\pi;P)\) is the sharp lower welfare endpoint, equivalently the upper tail-risk endpoint for the cost \(Y(\pi)\), under the marginal sensitivity model \(\mathcal R_{\mathrm{MSM}}\).  The bounding functional \(\mathsf B_{\mathrm{CVaR}}\) is the nested Rockafellar--Uryasev functional
\[
\mathsf B_{\mathrm{CVaR}}(P,\pi,\Gamma,\tau)
 =
\inf_{\eta\in\mathcal I}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid A=a,X\}
\right]\right\},
\]
where \(\mathfrak T_{\Gamma}^{+}\) is the sharp upper MSM tilted conditional-mean operator from the observed conditional law of \(Y\mid A=a,X=x\), and \(\mathcal I\) is the compact interval containing the relevant robust \(\tau\)-quantile.  No regression target is locked; estimation, when stated, uses the cross-fitted one-step map in Definition~\ref{def:onestep}.

\begin{abstract}
Confounding-robust off-policy learning under the marginal sensitivity model has sharp and efficient theory for the mean policy value.  Many policy decisions instead turn on tail welfare: the policy should control the worst \(\tau\)-fraction of the policy-induced outcome distribution.  The proposed kernel replaces the linear mean value by a CVaR functional and conjectures that the sharp endpoint is a nested one-dimensional variational object, with the MSM tilt applied to the eta-indexed truncated loss before the outer CVaR minimization.  The second claim isolates a non-commutation gap showing why applying CVaR after pointwise mean or distributional bands is generally conservative.  A final inference conjecture adapts doubly-sharp MSM endpoint scores to the generated truncated-loss family and supplies the endpoint limit law needed for an Imbens--Manski interval for the partially identified CVaR.
\end{abstract}

\section{Introduction}
Policy learning from observational data is attractive when randomized experiments are unavailable.  It is also fragile.  A policy learned under unconfoundedness can select actions that look good only because treatment choice was driven by unrecorded risk.  Marginal sensitivity models address this problem by bounding how much an unobserved variable can change the treatment odds, and recent work uses this model to obtain sharp and efficient bounds for the mean value of a stochastic policy.

The closest mean-policy result is \citet[Secs.~3--4]{HessFrauenMelnychukFeuerriegel2025SharpOPE}, which derives a closed-form sharp MSM bound for \(V(\pi)=\E[\sum_a\pi(a\mid X)Y(a)]\) and a semiparametrically efficient estimator.  \citet{JinXuZhengZhou2025RobustEfficientPolicy} also studies robust and efficient MSM policy learning, but its welfare target remains mean or worst-case mean welfare rather than fixed-policy CVaR partial identification.  The closest tail-welfare result is \citet{FanQiXu2025AlphaExpectedWelfare}, which studies worst-off-\(\alpha\) policy welfare under conventional identification.  None of these results gives the partial-identification endpoint for \(\mathrm{CVaR}_{\tau}\{Y(\pi)\}\) under unobserved confounding.  The kernel is a PartialID theorem: does the sharp MSM endpoint equal a nested CVaR problem in which the least-favorable tilt is recomputed for every \(\eta\)?

The immediate consumer is confounding-robust policy learning in high-stakes settings such as clinical treatment assignment, where \citet{KallusZhou2018ConfoundingRobustPolicy} already motivate robust improvement but use mean regret.  A reader who accepts the endpoint no longer evaluates a tail-risk policy by plugging pointwise bands into CVaR.  They solve a one-dimensional convex program in \(\eta\), with a sharp tilted truncated mean at each step.

\begin{itemize}[leftmargin=2em]
\item Conjecture 1: The sharp MSM-CVaR lower welfare endpoint equals the nested variational functional \(\inf_\eta\{\eta+\tau^{-1}\Psi_\eta(P,\pi)\}\). Gap: \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE} and \citet{JinXuZhengZhou2025RobustEfficientPolicy} solve mean-welfare MSM policy targets, not the eta-indexed truncated-loss family. Consumer: confounding-robust clinical policy learning.
\item Conjecture 2: The non-commutation gap \(\Delta_{\mathrm{nc}}(\pi)\) is strictly positive on a nondegenerate finite-support class and has a common-tilt equality case. Gap: \citet{DornGuo2021QuantileBalancing} and \citet{MastenPoirierRen2025RelaxingUnconfoundedness} give sharp pointwise bounds, not a rank-dependent policy functional. Consumer: audits of coordinatewise QTE/CDF sensitivity envelopes.
\item Conjecture 3: The cross-fitted one-step estimator in Definition~\ref{def:onestep} using the truncated-loss MSM score is asymptotically linear at the unique robust quantile. Gap: \citet{DornGuoKallus2021DoublySharp} gives the sharp mean-bound score, not the CVaR envelope score. Consumer: Imbens--Manski confidence intervals for robust CVaR policy intervals.
\end{itemize}

\section{Related work}
\citet{HessFrauenMelnychukFeuerriegel2025SharpOPE} is the direct writing and notation exemplar: it frames observational policy learning, relaxes unconfoundedness with the MSM, derives a sharp closed-form mean-value bound, and constructs an efficient one-step estimator.  \citet{JinXuZhengZhou2025RobustEfficientPolicy} is the closest recent MSM policy-learning comparator because it develops robust and efficient policy learning for mean or worst-case mean welfare, while the present endpoint is a fixed-policy CVaR partial-identification target.  \citet{KallusZhou2018ConfoundingRobustPolicy} is the policy-learning comparator because it optimizes worst-case mean regret under unobserved confounding using propensity-weight uncertainty rather than a sharp CVaR endpoint.  \citet{DornGuo2021QuantileBalancing} shows that indirect MSM/IPW sensitivity intervals can be too wide and supplies the quantile-balancing sharpness logic that the non-commutation theorem adapts.  \citet{DornGuoKallus2021DoublySharp} is the estimation-inference method exemplar because its doubly-sharp score estimates sharp MSM ATE endpoints and provides the orthogonal-score template for generated truncated losses.  \citet{FanQiXu2025AlphaExpectedWelfare} is the tail-welfare comparator because it targets the worst-off \(\alpha\)-fraction of policy outcomes and develops debiased policy learning, but it assumes conventional identification rather than MSM partial identification.  \citet{RockafellarUryasev2000CVaR} supplies the variational representation of CVaR as a minimization over \(\eta\), which is the outer layer of the proposed endpoint.  \citet{MastenPoirierRen2025RelaxingUnconfoundedness} gives sharp QTE and DTE bounds under relaxation classes that include the MSM; the proposed claim is different because a rank-dependent policy functional cannot generally be recovered by switching among pointwise distributional envelopes.  \citet{FrauenMelnychukFeuerriegel2023GeneralizedCSA} develops generalized sharp sensitivity bounds for multiple treatments and distributional effects; it informs the multi-action setup but does not solve randomized-policy CVaR.  \citet{ImbensManski2004PartialIDCI} gives the canonical interval-identified scalar confidence interval used after the two CVaR endpoints have asymptotic linear representations.

The closest in-repo prior is \texttt{pid\_qte\_marginal\_sensitivity\_v1}, which studies coordinatewise QTE envelopes and finite rank certificates under marginal sensitivity.  The present object is the process-level CVaR endpoint, not another pointwise quantile envelope.  The \texttt{pid\_bound\_intersection\_inference\_v1} family records generic max-map and contact-set inference templates; the inference result here is tied to a new eta-indexed MSM endpoint rather than to a generic interval intersection.  The \texttt{pid\_offline\_policy\_joint\_misspec\_v1} family records rectangular policy relaxations with strict-witness diagnostics; Conjecture~2 instead names the coordinatewise-band CVaR workflow and the scalar non-commutation gap.  The local theorem catalogue in \texttt{doc/API.md} places this proposal in the \texttt{CausalSmith/PartialID} and \texttt{CausalSmith/Stat} staging families, with no existing PartialID or Stat theorem for MSM-CVaR policy welfare.

\paragraph{Exemplars.}
Writing exemplar: \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE}, arXiv:2502.13022; the introduction arc mirrored here is observational policy learning \(\to\) hidden confounding \(\to\) sharp MSM mean-value bounds \(\to\) unresolved tail welfare.  Conjecture~1: \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE} (identification, arXiv:2502.13022) and \citet{RockafellarUryasev2000CVaR} (identification, DOI:10.21314/JOR.2000.038) -- least-favorable MSM tilting is nested inside the CVaR variational formula.  Conjecture~2: \citet{DornGuo2021QuantileBalancing} (identification, arXiv:2102.04543) and \citet{MastenPoirierRen2025RelaxingUnconfoundedness} (identification, arXiv:2501.15400) -- direct sharpness is compared with a pointwise-envelope construction.  Conjecture~3: \citet{DornGuoKallus2021DoublySharp} (estimation/inference, arXiv:2112.11449) and \citet{ImbensManski2004PartialIDCI} (estimation/inference, DOI:10.1111/j.1468-0262.2004.00555.x) -- orthogonal endpoint scores are converted into interval-identified CVaR coverage.

\section{Formal setup}
Let \(O=(Y,A,X)\sim P\) be iid.  The action set \(\mathcal A\) is finite, \(e_a(x)=P(A=a\mid X=x)\), and \(\pi(a\mid x)\) is a known stochastic evaluation policy with \(\sum_a\pi(a\mid x)=1\).  Potential outcomes are \(\{Y(a):a\in\mathcal A\}\), and the policy-induced potential outcome is \(Y(\pi)\), generated by drawing \(A^\pi\sim\pi(\cdot\mid X)\) independently of the factual action conditional on \(X\) and setting \(Y(\pi)=Y(A^\pi)\).  Lower values of \(Y\) are preferred, so the relevant welfare lower endpoint is the upper endpoint for the tail-risk cost \(Y(\pi)\).

Let \(\mathcal M_\Gamma(P)\) be the set of full-data laws \(Q\) for \(\{Y(a):a\in\mathcal A\},A,X,U\) with observed margin \(P\) satisfying the MSM in Assumption~\ref{ass:msm}.  Write \(Y_Q(\pi)\) for the policy-induced potential outcome under \(Q\).

For a measurable nonnegative loss \(Z=g(Y)\), define \(\mathfrak T_\Gamma^+(Z\mid a,x)\) as the sharp upper conditional mean over all latent laws satisfying the marginal sensitivity model at \((a,x)\).  Equivalently,
\[
\mathfrak T_\Gamma^+(Z\mid a,x)
=
\sup_{\omega\in\Omega_{\Gamma,e_a(x)}} \E[\omega(Y)Z\mid A=a,X=x],
\]
where \(\Omega_{\Gamma,e}\) is the Dorn--Guo quantile-balancing weight class implied by the odds-ratio MSM, normalized so that \(\E[\omega(Y)\mid A=a,X=x]=1\).  Under a continuous conditional law this supremum is attained by a monotone two-level weight that places the high weight on the upper \(\alpha_{\Gamma,e}\)-tail of \(Z\), with a boundary mass split at the conditional quantile when needed.  For \(\eta\in\mathcal I\), set
\[
\Psi_\eta(P,\pi)
=
\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)\,
\mathfrak T_\Gamma^+\{(Y-\eta)_+\mid a,X\}
\right],
\qquad
\mathcal C_\eta(P,\pi)
=
\eta+\tau^{-1}\Psi_\eta(P,\pi).
\]
The proposed sharp endpoint is
\[
\underline W_{\tau,\Gamma}(\pi;P)
=
\inf_{\eta\in\mathcal I}\mathcal C_\eta(P,\pi).
\]

The comparator endpoint is the monotone coordinatewise-band CVaR functional.  Let \(\underline F_{\Gamma}(y\mid P,\pi)\) and \(\overline F_{\Gamma}(y\mid P,\pi)\) denote the pointwise sharp lower and upper MSM envelopes for \(P\{Y(\pi)\leq y\}\).  Let \(\mathcal F_{\Gamma}^{\mathrm{pt}}(P,\pi)\) be the set of cadlag nondecreasing distribution functions \(F\) on \([y_L,y_U]\) satisfying
\[
\underline F_{\Gamma}(y\mid P,\pi)\leq F(y)\leq
\overline F_{\Gamma}(y\mid P,\pi)
\quad\text{for every }y\in[y_L,y_U].
\]
This comparator is a distributional band relaxation: it enforces monotonicity and right-continuity, but it does not require one latent MSM law to attain all selected thresholds.  Define
\[
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
=
\inf_{\eta\in\mathcal I}
\left\{\eta+\tau^{-1}\sup_{F\in\mathcal F_{\Gamma}^{\mathrm{pt}}(P,\pi)}
\int (y-\eta)_+\,dF(y)\right\},
\qquad
\Delta_{\mathrm{nc}}(\pi;P)=W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
-\underline W_{\tau,\Gamma}(\pi;P).
\]
The full-data identified set for the CVaR welfare is the interval obtained by pairing the upper tail-risk endpoint above with the analogous lower endpoint that replaces \(\mathfrak T_\Gamma^+\) by \(\mathfrak T_\Gamma^-\).  This proposal focuses on the upper tail-risk endpoint because it is the conservative endpoint used when lower \(Y\) is better.

\begin{quote}
\small\ttfamily
Locked tuple: (qid, specialization, P, theta, R, B) =\\
(pid\_cvar\_welfare\_msm\_v1, robust\_cvar\_policy, observed law of (Y,A,X),\\
sharp MSM-CVaR lower welfare endpoint underline W\_\{tau,Gamma\}(pi;P),\\
MSM latent-confounding restrictions R\_\{MSM\}, nested CVaR bounding functional B\_\{CVaR\}).\\
Policy pi, sensitivity Gamma, and tail fraction tau are fixed throughout.
\end{quote}

\section{Assumptions}
\begin{assumption}[Observed sampling and overlap]\label{ass:iid-overlap}
The observations \(O_i=(Y_i,A_i,X_i)\) are iid from \(P\).  For each \(a\in\mathcal A\), \(0<\epsilon\leq e_a(X)\leq 1-\epsilon\) almost surely.  This is the policy-learning overlap condition used by \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE} and \citet{AtheyWager2021PolicyLearning}, specialized to finite actions.
\end{assumption}

\begin{assumption}[Consistency and policy support]\label{ass:consistency}
The factual outcome satisfies \(Y=Y(A)\), and \(\pi(a\mid X)>0\) only when \(e_a(X)>0\).  This is the standard potential-outcome consistency and support convention used in off-policy learning, as in \citet{KallusZhou2018ConfoundingRobustPolicy}.
\end{assumption}

\begin{assumption}[Marginal sensitivity model]\label{ass:msm}
There exists a latent \(U\) such that, for every \(a,x,u\),
\[
\Gamma^{-1}\leq
\frac{e_a(x)/(1-e_a(x))}
{P(A=a\mid X=x,U=u)/(1-P(A=a\mid X=x,U=u))}
\leq \Gamma .
\]
This is Tan's marginal sensitivity model as used by \citet{DornGuo2021QuantileBalancing}, \citet{DornGuoKallus2021DoublySharp}, and \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE}.
\end{assumption}

\begin{assumption}[Tail regularity]\label{ass:tail}
For every \(a,x\), \(Y\mid A=a,X=x\) has support in a common compact interval \([y_L,y_U]\), and the conditional distribution has a density bounded above and bounded away from zero in a neighborhood of the active quantiles of \((Y-\eta)_+\).  This adapts the bounded-outcome and positive-density quantile conditions used by \citet{DornGuo2021QuantileBalancing} and \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE}.
\end{assumption}

\begin{assumption}[Unique robust CVaR optimizer]\label{ass:unique-eta}
The map \(\eta\mapsto \mathcal C_\eta(P,\pi)\) has a unique minimizer \(\eta_{\tau,\Gamma}(P,\pi)\) in the interior of \(\mathcal I\), and its one-sided derivatives cross zero there.  This is the Rockafellar--Uryasev CVaR uniqueness condition, adapted from \citet{RockafellarUryasev2000CVaR} to the MSM-tilted truncated-loss criterion.
\end{assumption}

\begin{assumption}[Nuisance rates for one-step inference]\label{ass:nuisance}
The estimators of \(e_a(x)\), the active conditional quantiles, and the tilted truncated-loss regressions are estimated on auxiliary folds and converge in \(L_2(P)\) fast enough that products of first-stage errors are \(o_p(n^{-1/2})\).  This is the cross-fitting and product-rate condition used by \citet{DornGuoKallus2021DoublySharp} and by debiased policy learning work such as \citet{FanQiXu2025AlphaExpectedWelfare}.
\end{assumption}

\section{Main results}
\begin{conjecture}[Conjecture 1: Sharp nested MSM-CVaR endpoint]\label{conj:nested-endpoint}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail}, for every fixed policy \(\pi\),
\[
\sup_{Q\in\mathcal M_\Gamma(P)}
\mathrm{CVaR}_\tau\{Y_Q(\pi)\}
=
\inf_{\eta\in\mathcal I}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_{a\in\mathcal A}\pi(a\mid X)
\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,X\}
\right]\right\}.
\]
The equality is sharp: every value above the right-hand side is valid, and no smaller endpoint is valid over \(\mathcal M_\Gamma(P)\).
\end{conjecture}

\begin{conjecture}[Conjecture 2: Non-commutation gap]\label{conj:noncommutation}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:tail},
\[
\Delta_{\mathrm{nc}}(\pi;P)=
W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)
-\underline W_{\tau,\Gamma}(\pi;P)\geq 0.
\]
Moreover, there is a two-action, three-outcome, one-covariate-cell class satisfying strict overlap and \(1<\Gamma<\infty\) on which \(\Delta_{\mathrm{nc}}(\pi;P)>0\).  Equality holds when the same monotone least-favorable MSM tilt is simultaneously optimal for all \(\eta\) in the active subgradient set of \(\mathcal C_\eta(P,\pi)\).
\end{conjecture}

\begin{definition}[Cross-fitted one-step estimator]\label{def:onestep}
Let \(\hat\eta\) minimize the sample version of \(\mathcal C_\eta\) on a grid or by line search.  On each evaluation fold define
\[
\hat\phi_{\hat\eta,\pi}(O_i)
=
\sum_{a\in\mathcal A}\pi(a\mid X_i)\hat m_{\hat\eta,a}^{+}(X_i)
+
\frac{\pi(A_i\mid X_i)}{\hat e_{A_i}(X_i)}
\left[
\hat\omega_{\hat\eta,A_i,X_i}^{+}(Y_i)(Y_i-\hat\eta)_+
-\hat m_{\hat\eta,A_i}^{+}(X_i)
\right],
\]
where \(\hat\omega^+\) is the estimated MSM least-favorable weight for the generated loss and \(\hat m_{\eta,a}^{+}(x)=\mathfrak T_{\Gamma}^{+}\{(Y-\eta)_+\mid a,x\}\).  The one-step endpoint estimator is
\[
\hat W_{\tau,\Gamma}(\pi)
=
\hat\eta+\tau^{-1}\mathbb P_n\hat\phi_{\hat\eta,\pi}.
\]
\end{definition}

\begin{conjecture}[Conjecture 3: One-step limit law]\label{conj:onestep-limit}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:nuisance}, the estimator in Definition~\ref{def:onestep} is asymptotically linear:
\[
\sqrt n\{\hat W_{\tau,\Gamma}(\pi)-\underline W_{\tau,\Gamma}(\pi;P)\}
=
\frac{1}{\sqrt n}\sum_{i=1}^n
\varphi_{\tau,\Gamma,\pi}(O_i)+o_p(1),
\qquad
\E[\varphi_{\tau,\Gamma,\pi}(O)]=0.
\]
The variance of \(\varphi_{\tau,\Gamma,\pi}\) is consistently estimated by the fold-stacked empirical variance of \(\hat\eta+\tau^{-1}\hat\phi_{\hat\eta,\pi}-\hat W_{\tau,\Gamma}(\pi)\).
\end{conjecture}

\section{Sanity-check corollaries}
\paragraph{No hidden confounding.}
Under Assumptions~\ref{ass:iid-overlap}--\ref{ass:unique-eta} and \(\Gamma=1\), the MSM feasible weight set is the singleton \(\{\omega\equiv1\}\).  Hence \(\mathfrak T_1^+(Z\mid a,x)=\E[Z\mid A=a,X=x]\) and Conjecture~\ref{conj:nested-endpoint} reduces to
\[
\underline W_{\tau,1}(\pi;P)
=
\inf_{\eta\in\mathcal I}
\left\{\eta+\tau^{-1}\E_P\left[
\sum_a\pi(a\mid X)\E\{(Y-\eta)_+\mid A=a,X\}
\right]\right\},
\]
which is the Rockafellar--Uryasev CVaR representation for the identified policy-induced outcome distribution by consistency and overlap.

\paragraph{Mean-welfare corner.}
If \(\tau=1\) and \(\mathcal I\) contains the lower endpoint of the outcome support, then \(\inf_\eta\{\eta+\E[(Y-\eta)_+]\}=\E[Y]\).  The nested endpoint therefore reduces to the sharp mean-policy bound of \citet{HessFrauenMelnychukFeuerriegel2025SharpOPE}, with the same actionwise MSM tilted conditional means.

\paragraph{Common-tilt equality case.}
If, for all \(\eta\) in the active subgradient set, the ordering of \((Y-\eta)_+\) induces the same least-favorable upper-tail set within every \((a,x)\) cell, then \(W_{\tau,\Gamma}^{\mathrm{band}}(\pi;P)=\underline W_{\tau,\Gamma}(\pi;P)\).  This checks that the non-commutation gap is not forced by notation; it appears only when the CVaR optimizer changes which latent tilt is least favorable.

\paragraph{Interval calibration.}
If Conjecture~\ref{conj:onestep-limit} holds for both lower and upper MSM-CVaR endpoints, then the \citet{ImbensManski2004PartialIDCI} critical value applied to the endpoint standard errors gives asymptotic coverage for the partially identified scalar \(\mathrm{CVaR}_{\tau}\{Y(\pi)\}\).  The reduction uses the endpoint CLTs as inputs and does not add a separate smoothness condition beyond Assumptions~\ref{ass:unique-eta}--\ref{ass:nuisance}.

\section{Proof-sketch route}
The identification proof starts from the Rockafellar--Uryasev representation and applies the Dorn--Guo/Frauen sharp MSM conditional-mean operator to the generated loss \(Z_\eta=(Y-\eta)_+\).  The nontrivial step is sharpness uniformly over \(\eta\): the proof must paste the eta-indexed least-favorable conditional laws into one full-data law or prove a minimax argument that justifies the nested endpoint without illicitly switching laws after \(\eta\) is chosen.  The non-commutation proof should use a finite one-cell support, compute the tilted truncated means for three candidate \(\eta\)'s, and show that the pointwise CDF-band optimizer switches latent tilts while the nested endpoint cannot.  The inference proof adapts the \citet{DornGuoKallus2021DoublySharp} orthogonal score to \(Z_\eta\), uses the envelope theorem at the unique robust quantile to remove first-order estimation of \(\eta\), and then applies the \citet{ImbensManski2004PartialIDCI} interval construction to the lower and upper endpoint CLTs.

\section{Honest scope flags}
Conjectures~\ref{conj:nested-endpoint}, \ref{conj:noncommutation}, and \ref{conj:onestep-limit} are not proved in this proposal.  The most delicate point is whether sharpness for each fixed \(\eta\) can be promoted to sharpness of the outer CVaR endpoint without assuming the answer through a common latent law.  The one-step estimator is stated only under a unique robust quantile and positive density near active cutoffs; mass points at the robust quantile should be handled later by directional differentiability or subsampling rather than by the smooth CLT in Conjecture~\ref{conj:onestep-limit}.  Multi-action latent compatibility beyond the actionwise MSM operator is outside the locked kernel; it is a follow-up if Conjecture~\ref{conj:noncommutation} exposes a strict coupled-action gap.

\section{Iteration trail}
\begin{itemize}[leftmargin=2em]
\item v1 (cold-start) -- initial draft with nested MSM-CVaR endpoint, non-commutation scalar, and cross-fitted one-step inference rung; prior verdict: none.
\item v2 (revise) -- constrained the pointwise-band comparator to cadlag monotone CDFs and recentered the one-step tilted-loss pseudo-outcome at \(m_{\eta,a}^+\); prior verdict: REVISE.
\item v3 (revise) -- added the Jin--Xu--Zheng--Zhou MSM policy-learning comparator and moved the \(\Gamma=1\) CVaR identity from §8 into the sanity reductions; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Athey and Wager(2021)]{AtheyWager2021PolicyLearning}
Athey, S. and Wager, S. (2021).
\newblock Policy learning with observational data.
\newblock \emph{Econometrica}, 89(1):133--161.

\bibitem[Dorn and Guo(2021)]{DornGuo2021QuantileBalancing}
Dorn, J. and Guo, K. (2021).
\newblock Sharp sensitivity analysis for inverse propensity weighting via quantile balancing.
\newblock \emph{Journal of the American Statistical Association}, arXiv:2102.04543.

\bibitem[Dorn, Guo, and Kallus(2021)]{DornGuoKallus2021DoublySharp}
Dorn, J., Guo, K., and Kallus, N. (2021).
\newblock Doubly-valid/doubly-sharp sensitivity analysis for causal inference with unmeasured confounding.
\newblock arXiv:2112.11449.

\bibitem[Fan, Qi, and Xu(2025)]{FanQiXu2025AlphaExpectedWelfare}
Fan, Y., Qi, Y., and Xu, G. (2025).
\newblock Policy learning with alpha-expected welfare.
\newblock arXiv:2505.00256.

\bibitem[Frauen, Melnychuk, and Feuerriegel(2023)]{FrauenMelnychukFeuerriegel2023GeneralizedCSA}
Frauen, D., Melnychuk, V., and Feuerriegel, S. (2023).
\newblock Sharp bounds for generalized causal sensitivity analysis.
\newblock arXiv:2305.16988.

\bibitem[Hess et al.(2025)]{HessFrauenMelnychukFeuerriegel2025SharpOPE}
Hess, K., Frauen, D., Melnychuk, V., and Feuerriegel, S. (2025).
\newblock Efficient and sharp off-policy learning under unobserved confounding.
\newblock arXiv:2502.13022.

\bibitem[Imbens and Manski(2004)]{ImbensManski2004PartialIDCI}
Imbens, G. W. and Manski, C. F. (2004).
\newblock Confidence intervals for partially identified parameters.
\newblock \emph{Econometrica}, 72(6):1845--1857.

\bibitem[Jin et al.(2025)]{JinXuZhengZhou2025RobustEfficientPolicy}
Jin, Z., Xu, G., Zheng, X., and Zhou, Y. (2025).
\newblock Robust and efficient policy learning under the marginal sensitivity model.
\newblock arXiv:2507.20550.

\bibitem[Kallus and Zhou(2018)]{KallusZhou2018ConfoundingRobustPolicy}
Kallus, N. and Zhou, A. (2018).
\newblock Confounding-robust policy improvement.
\newblock \emph{NeurIPS}, arXiv:1805.08593.

\bibitem[Masten, Poirier, and Ren(2025)]{MastenPoirierRen2025RelaxingUnconfoundedness}
Masten, M. A., Poirier, A., and Ren, M. (2025).
\newblock A general approach to relaxing unconfoundedness.
\newblock arXiv:2501.15400.

\bibitem[Rockafellar and Uryasev(2000)]{RockafellarUryasev2000CVaR}
Rockafellar, R. T. and Uryasev, S. (2000).
\newblock Optimization of conditional value-at-risk.
\newblock \emph{Journal of Risk}, 2(3):21--41.
\end{thebibliography}

\end{document}
