\section{Setup and assumptions}

\subsection{The algebraic theorem domain}

The main theorems concern two polynomial maps defined on fixed-source-count parameter spaces. Fix \(m\) and a truncation order \(L\). The right-arrow parameter records the finite slopes \(\gamma,\rho_1,\ldots,\rho_m\) and order-specific source weights \(c_{jr}\); the left-arrow parameter records \(\delta,\sigma_1,\ldots,\sigma_m\) and \(d_{jr}\). For each \(2\le r\le L\), the two maps send these coordinates to the mixed-cumulant block
\[
t_{r,a}
=\sum_{j=0}^{m+1}c_{jr}(u_{j1})^{r-a}(u_{j2})^a
\quad\text{or}\quad
t_{r,a}
=\sum_{j=0}^{m+1}d_{jr}(v_{j1})^{r-a}(v_{j2})^a,
\qquad 0\le a\le r.
\]
The loading vectors \(u_j\) and \(v_j\) encode the two axis conventions. The theorem domain is the resulting pair of complex affine parameter spaces and polynomial cumulant maps, stated formally in \cref{obj:def:truncated-cumulant}--\cref{obj:def:reverse-cumulant-map}. ``Generic'' in the complex results means outside a proper algebraic subset of these parameter spaces. The conclusion establishes emptiness of one map fiber within this domain.

\subsection{Probabilistic interpretation}

The probabilistic assumptions now attach an econometric interpretation to real points of the algebraic maps. Each representation has \(m+2\) source slots: two are tied to the coordinate-axis normalization and the remaining \(m\) middle source slots have finite slopes. Centered mutually independent sources make cumulants additive across slots, finite moments make the retained cumulants well-defined, and non-Gaussianity provides higher-order information. These assumptions define the real feasible regions below, while the complex-polynomial interpretation of the maps applies on the full affine parameter spaces. A middle source slot receives the latent-confounder interpretation when both coordinate loadings are nonzero, so ``middle source slot'' is the default term.

The source dimension is indexed by \leanref{sym:m}{$m$}, with \leanref{sym:n}{$n$} later denoting \(m+2\) loading directions. The working truncation order \leanref{sym:K}{$K$} is finite, and \leanref{sym:S_j}{$S_j$} denotes the \(j\)th centered latent source.

\begin{assumptionv}{ass:independent-sources}[Independent latent sources]
The latent source variables \(S_0,\ldots,S_{m+1}\) are mutually independent with respect to \(\mu\):
\[
S_0\perp\cdots\perp S_{m+1}.
\]
\end{assumptionv}

\cref{obj:ass:independent-sources} is the standard independent-component source condition in latent-variable LiNGAM; it is what makes joint cumulants additive across source slots \citep{ChenPengHuangEtAl2025Direction}.

\begin{assumptionv}{ass:finite-cumulants}
For every \(j=0,\ldots,m+1\), the latent source variable \(S_j\) has finite \(K\)-th absolute moment:
\[
\mathbb E |S_j|^K<\infty .
\]
\end{assumptionv}

\cref{obj:ass:finite-cumulants} is the standard finite-order cumulant existence condition, tailored to the truncation order used by the paper \citep{ChenPengHuangEtAl2025Direction}.

\begin{assumptionv}{ass:source-nongaussianity}
For every \(j=0,\ldots,m+1\), the latent source variable \(S_j\) is non-Gaussian.
\end{assumptionv}

\cref{obj:ass:source-nongaussianity} is the usual non-Gaussian disturbance condition in LiNGAM-type identification; higher-order non-Gaussian structure supplies the cumulant information beyond covariance restrictions \citep{ChenPengHuangEtAl2025Direction}.

The two axis-normalized parametrizations give the real structural interpretation of the arrow tags used by the polynomial maps. In the right-arrow convention, \leanref{sym:X}{$X$} is the first coordinate and \leanref{sym:Y}{$Y$} is the second coordinate, the direct loading has slope \leanref{sym:gamma}{$\gamma$}, the middle finite slopes are \leanref{sym:rho_i}{$\rho_i$}, and the forward loading vectors are \leanref{sym:u_j}{$u_j$}. In the left-arrow convention, the analogous direct and middle slopes are \leanref{sym:delta}{$\delta$} and \leanref{sym:sigma_i}{$\sigma_i$}, with reverse loading vectors \leanref{sym:v_j}{$v_j$}.

\begin{assumptionv}{ass:forward-axis-model}
With forward loading vectors \(u_0=(1,\gamma)\), \(u_j=(1,\rho_j)\) for \(1\le j\le m\), and \(u_{m+1}=(0,1)\), the bivariate observed outcome vector admits the forward latent linear representation
\[
(X,Y)^\top=\sum_{j=0}^{m+1} u_j S_j .
\]
\end{assumptionv}

\cref{obj:ass:forward-axis-model} is a bivariate linear acyclic representation with latent source slots in the \(X\to Y\) orientation \citep{ChenPengHuangEtAl2025Direction}. The axis normalization fixes one horizontal-axis and one vertical-axis slot, so only the middle source slots carry free finite slopes.

\begin{assumptionv}{ass:reverse-axis-model}
With reverse loading vectors \(v_0=(1,0)\), \(v_j=(\sigma_j,1)\) for \(1\le j\le m\), and \(v_{m+1}=(\delta,1)\), the bivariate observed outcome vector admits the reverse latent linear representation
\[
(X,Y)^\top=\sum_{j=0}^{m+1} v_j S_j .
\]
\end{assumptionv}

\cref{obj:ass:reverse-axis-model} is the corresponding reversed bivariate linear acyclic parametrization for the \(Y\to X\) orientation \citep{ChenPengHuangEtAl2025Direction}. Its symmetric normalization permits a direct comparison of the two representation fibers.

Genericity enters through distinct finite loading directions and nonzero direct edges. These restrictions remove lower-dimensional coincidences in the loading support while permitting middle source slots with a zero coordinate loading.

\begin{assumptionv}{ass:forward-noncollinearity}
The direct and latent finite slopes in the forward parametrization are pairwise distinct:
\[
\bigl|\{\gamma,\rho_i:1\le i\le m\}\bigr|=m+1 .
\]
\end{assumptionv}

\cref{obj:ass:forward-noncollinearity} is the standard generic distinct-loading-directions condition for the forward parametrization \citep{SchkodaRobevaDrton2024}. It excludes merged finite slopes while permitting zero-valued middle slopes.

\begin{assumptionv}{ass:reverse-noncollinearity}
The reverse slopes are pairwise distinct:
\[
\left|\{\delta,\sigma_i:1\le i\le m\}\right|=m+1.
\]
\end{assumptionv}

\cref{obj:ass:reverse-noncollinearity} imposes the same generic distinct-loading-directions condition on the reverse parametrization \citep{SchkodaRobevaDrton2024}. The symmetry is useful because later separation statements compare full opposite-arrow fibers.

\begin{assumptionv}{ass:forward-nonzero-edge}
The forward direct slope is nonzero:
\[
\gamma\ne 0.
\]
\end{assumptionv}

\cref{obj:ass:forward-nonzero-edge} is the standard nonzero direct-edge genericity restriction in the forward direction \citep{ChenPengHuangEtAl2025Direction}. It excludes the degenerate case in which the distinguished direct slot lies on the horizontal axis.

\begin{assumptionv}{ass:reverse-nonzero-edge}
The reverse direct slope is nonzero:
\[
\delta\ne 0.
\]
\end{assumptionv}

\cref{obj:ass:reverse-nonzero-edge} is the analogous nonzero direct-edge genericity restriction for the reverse direction \citep{ChenPengHuangEtAl2025Direction}. Together, the two nonzero-edge restrictions keep the two arrow conventions from sharing their distinguished direct-axis slot.

We now define the two law classes. The notation \(\operatorname{Laws}(\mathbb R^2)\) denotes the ambient class of Borel probability laws on \(\mathbb R^2\), and \leanref{S-1}{the observational law setup} is the data-generating world in which these law classes live.

\begin{definitionv}{def:forward-lvlingam-class}[Forward class \(\mathcal P^{\mathrm{right}}_{m,K}\)]
Write \(\operatorname{Laws}(\mathbb R^2)\) for the Borel probability laws on \(\mathbb R^2\). Let \(\mathcal P^{\mathrm{right}}_{m,2m+2}\) be the set of all probability laws \(P\in \operatorname{Laws}(\mathbb R^2)\) for which there exist a measurable space \((\Omega,\mathcal A)\), a probability measure \(\mu\) on \(\Omega\), source functions
\[
S_0,\ldots,S_{m+1}:\Omega\to\mathbb R,
\]
observed variables \(X,Y:\Omega\to\mathbb R\), a direct forward slope \(\gamma\in\mathbb R\), and latent forward slopes \(\rho_1,\ldots,\rho_m\in\mathbb R\) such that:
\begin{itemize}
\item \textbf{(Source independence.)} The sources \(S_0,\ldots,S_{m+1}\) are mutually independent under \(\mu\).
\item \textbf{(Finite cumulant order.)} Each source has finite moments through order \(2m+2\).
\item \textbf{(Source non-Gaussianity.)} Each source has non-Gaussian law under \(\mu\).
\item \textbf{(Centering.)} Each source is centered: \(\int S_j\,d\mu=0\) for every \(j=0,\ldots,m+1\).
\item \textbf{(Forward representation.)} For every \(\omega\in\Omega\), the bivariate observed outcome vector \((X(\omega),Y(\omega))^\top\) admits the forward \(X\to Y\) latent linear non-Gaussian representation with loading vectors \(u_j\).
\item \textbf{(Forward noncollinearity.)} The forward direct and latent finite slopes \(\gamma,\rho_1,\ldots,\rho_m\) are pairwise distinct.
\item \textbf{(Nonzero forward edge.)} The forward direct slope satisfies \(\gamma\ne 0\).
\item \textbf{(Observed law.)} The law \(P\) is the pushforward \(\mu\)-law of \((X,Y)\), i.e. \(P=\mu\circ (X,Y)^{-1}\).
\end{itemize}
\end{definitionv}

\cref{obj:def:forward-lvlingam-class} is a representation-level class: membership means that the law has at least one centered non-Gaussian source representation satisfying the right-arrow axis convention.

\begin{definitionv}{def:reverse-lvlingam-class}[Reverse class \(\mathcal P^{\mathrm{left}}_{m,K}\)]
Using the ambient law class \(\operatorname{Laws}(\mathbb R^2)\) defined in \cref{obj:def:forward-lvlingam-class}, let \(\mathcal P^{\mathrm{left}}_{m,2m+2}\) be the set of all probability laws \(P\in \operatorname{Laws}(\mathbb R^2)\) for which there exist a probability space \((\Omega,\mathcal A,\mu)\), latent source variables
\[
S_0,\ldots,S_{m+1}:\Omega\to\mathbb R,
\]
observed variables \(X,Y:\Omega\to\mathbb R\), a reverse direct slope \(\delta\in\mathbb R\), and reverse latent slopes \(\sigma_1,\ldots,\sigma_m\in\mathbb R\), such that:
\begin{itemize}
\item \textbf{(Source independence.)} The sources \(S_0,\ldots,S_{m+1}\) are mutually independent under \(\mu\).
\item \textbf{(Finite cumulant order.)} Each source belongs to \(L^{2m+2}(\mu)\).
\item \textbf{(Source non-Gaussianity.)} Each source law \(\mu\circ S_j^{-1}\) is non-Gaussian.
\item \textbf{(Centering.)} Each source is centered: \(\int_\Omega S_j\,d\mu=0\) for all \(j=0,\ldots,m+1\).
\item \textbf{(Reverse representation.)} The bivariate observed outcome vector \((X,Y)^\top\) admits the reverse \(Y\to X\) latent linear non-Gaussian representation with loading vectors \(v_j\), pointwise on \(\Omega\).
\item \textbf{(Reverse noncollinearity.)} The reverse direct and latent finite slopes \(\delta,\sigma_1,\ldots,\sigma_m\) are pairwise distinct.
\item \textbf{(Nonzero reverse edge.)} The reverse direct slope satisfies \(\delta\ne 0\).
\item \textbf{(Observed law.)} The law \(P\) is the pushforward of \(\mu\) by \(\omega\mapsto (X(\omega),Y(\omega))\).
\end{itemize}
\end{definitionv}

\cref{obj:def:reverse-lvlingam-class} gives the opposite representation class under the same source-count convention. The paper's separation statements characterize when cumulants from one parametrization have an empty fiber under the other cumulant map.

The identifying information is expressed through joint cumulants. For a law \(P\), \(\operatorname{Cum}\) denotes the joint cumulant functional, \leanref{sym:kappa_{r,a}(P)}{$\kappa_{r,a}(P)$} is the coordinate with \(r-a\) copies of \(X\) and \(a\) copies of \(Y\), and \leanref{sym:T_L(P)}{$T_L(P)$} collects all cumulants from orders \(2\) through \leanref{sym:L}{$L$}. The dimension of this vector is \leanref{sym:q_L}{$q_L$}. Classical references for cumulant notation and higher-order moment methods include \citet{Brillinger1969} and \citet{McCullagh1987}.

\begin{definitionv}{def:truncated-cumulant}[Truncated cumulant vector \(T_L(P)\)]
For the ambient law class of \cref{obj:def:forward-lvlingam-class}, write \(\operatorname{Cum}_P(Z_1,\ldots,Z_r)\) for the joint cumulant under \(P\), and define \(\operatorname{Cum}_r(Z)\) to be the joint cumulant of \(r\) copies of \(Z\). For \(P\in \operatorname{Laws}(\mathbb R^2)\), define
\[
T_L(P)=\bigl(\kappa_{r,a}(P):2\le r\le L,\ 0\le a\le r\bigr),
\]
where
\[
\kappa_{r,a}(P)
=
\operatorname{Cum}_P(\underbrace{X,\ldots,X}_{r-a\ \mathrm{copies}},
\underbrace{Y,\ldots,Y}_{a\ \mathrm{copies}}).
\]
The coordinate dimension is
\[
q_L=\frac{L(L+3)}{2}-2.
\]

For later cumulant maps, define the complex parameter spaces
\[
\Theta^{\mathrm{right}}_{m,L}
=\mathbb C^{,m+1+(m+2)(L-1)}
\]
with coordinates \((\gamma,\rho_1,\ldots,\rho_m,(c_{jr})_{0\le j\le m+1,,2\le r\le L})\), and
\[
\Theta^{\mathrm{left}}_{m,L}
=\mathbb C^{,m+1+(m+2)(L-1)}
\]
with coordinates \((\delta,\sigma_1,\ldots,\sigma_m,(d_{jr})_{0\le j\le m+1,,2\le r\le L})\).
\end{definitionv}

\cref{obj:def:truncated-cumulant} also introduces the complex affine parameter spaces \leanref{sym:Theta^right_{m,L}}{$\Theta^{\mathrm{right}}_{m,L}$} and \leanref{sym:Theta^left_{m,L}}{$\Theta^{\mathrm{left}}_{m,L}$}. These complexified coordinates, summarized by \leanref{S-2}{the complexified structural-parameter and cumulant-coordinate world}, are algebraic devices for studying polynomial images; real feasibility is imposed separately below.

By independence and multilinearity of cumulants, each source contributes its order-\(r\) cumulant weight times the appropriate monomial in its loading vector. We write \leanref{sym:c_{jr}}{$c_{jr}$} and \leanref{sym:d_{jr}}{$d_{jr}$} for these source-cumulant weights, and use the polynomial maps \leanref{sym:Phi^right_{m,L}}{$\Phi^{\mathrm{right}}_{m,L}$} and \leanref{sym:Phi^left_{m,L}}{$\Phi^{\mathrm{left}}_{m,L}$} to encode the resulting cumulant vectors.

\begin{definitionv}{def:forward-cumulant-map}[Forward cumulant map \(\Phi^{\mathrm{right}}_{m,L}\)]
Using the complex parameter space of \cref{obj:def:truncated-cumulant}, The forward cumulant map \(\Phi^{\mathrm{right}}_{m,L}:\Theta^{\mathrm{right}}_{m,L}\to\mathbb C^{q_L}\) is defined coordinatewise by
\[
\bigl[\Phi^{\mathrm{right}}_{m,L}(\gamma,\rho,c)\bigr]_{r,a}
=
\sum_{j=0}^{m+1}
c_{jr}\,(u_{j1})^{r-a}(u_{j2})^a,
\qquad
2\le r\le L,\quad 0\le a\le r,
\]
where
\[
u_0=(1,\gamma),\qquad
u_j=(1,\rho_j)\ \text{for }1\le j\le m,\qquad
u_{m+1}=(0,1).
\]
\end{definitionv}

The map in \cref{obj:def:forward-cumulant-map} is the cumulant analogue of a finite simultaneous binary-form decomposition. At this stage its source weights are free algebraic coordinates, with real-random-variable realizability imposed later through the feasible regions.

\begin{definitionv}{def:reverse-cumulant-map}[Reverse cumulant map \(\Phi^{\mathrm{left}}_{m,L}\)]
Using the complex parameter space of \cref{obj:def:truncated-cumulant}, The reverse cumulant map \(\Phi^{\mathrm{left}}_{m,L}:\Theta^{\mathrm{left}}_{m,L}\to\mathbb C^{q_L}\) is defined coordinatewise by
\[
\bigl[\Phi^{\mathrm{left}}_{m,L}(\delta,\sigma,d)\bigr]_{r,a}
=
\sum_{j=0}^{m+1}
d_{jr}\,(v_{j1})^{r-a}(v_{j2})^a,
\qquad
2\le r\le L,\quad 0\le a\le r,
\]
where
\[
v_0=(1,0),\qquad
v_j=(\sigma_j,1)\ \text{for }1\le j\le m,\qquad
v_{m+1}=(\delta,1).
\]
\end{definitionv}

\cref{obj:def:reverse-cumulant-map} mirrors \cref{obj:def:forward-cumulant-map} after exchanging the axis convention. This symmetry lets the paper characterize possible simultaneous membership in both parametrized images.

The algebraic images are taken after Zariski closure in the ambient complex affine cumulant space. We write \(\operatorname{ZariskiClosure}\) for this closure operation, and denote the two closed image varieties by \leanref{sym:C^right_{m,L}}{$C^{\mathrm{right}}_{m,L}$} and \leanref{sym:C^left_{m,L}}{$C^{\mathrm{left}}_{m,L}$}.

\begin{definitionv}{def:image-varieties}[Image varieties \(C^{\mathrm{right}}_{m,L}\) and \(C^{\mathrm{left}}_{m,L}\)]
For a subset of the ambient complex affine space, write \(\operatorname{ZariskiClosure}\) for its Zariski closure. Using the parameter spaces and maps of \cref{obj:def:forward-cumulant-map} and~\cref{obj:def:reverse-cumulant-map}, the forward and reverse image varieties are
\[
C^{\mathrm{right}}_{m,L}
=
\operatorname{ZariskiClosure}
\bigl(\Phi^{\mathrm{right}}_{m,L}(\Theta^{\mathrm{right}}_{m,L})\bigr),
\qquad
C^{\mathrm{left}}_{m,L}
=
\operatorname{ZariskiClosure}
\bigl(\Phi^{\mathrm{left}}_{m,L}(\Theta^{\mathrm{left}}_{m,L})\bigr),
\]
as subvarieties of \(\mathbb C^{q_L}\).
\end{definitionv}

These varieties record the algebraic restrictions imposed by a fixed number of source slots and a fixed arrow convention. Their use is standard in algebraic treatments of tensor and binary-form decompositions, where generic conclusions are naturally stated off proper algebraic subsets \citep{ComonMourrain1996,Landsberg2012}.

The next definition isolates the open parameter loci on which slopes are distinct, direct slopes are nonzero, and all retained source cumulant weights are nonzero. We denote these loci by \leanref{sym:Theta^{right,circ}_{m,L}}{$\Theta^{\mathrm{right},\circ}_{m,L}$} and \leanref{sym:Theta^{left,circ}_{m,L}}{$\Theta^{\mathrm{left},\circ}_{m,L}$}.

\begin{definitionv}{def:generic-parameter-loci}[Generic loci \(\Theta^{\mathrm{right},\circ}_{m,L}\) and \(\Theta^{\mathrm{left},\circ}_{m,L}\)]
For every \(L\ge2\), using the parameter spaces of \cref{obj:def:forward-cumulant-map} and~\cref{obj:def:reverse-cumulant-map}, the forward generic parameter locus is
\[
\Theta^{\mathrm{right},\circ}_{m,L}
=
\left\{
(\gamma,\rho,c)\in \Theta^{\mathrm{right}}_{m,L}:
\gamma
\prod_{i=1}^m(\gamma-\rho_i)
\prod_{1\le i<\ell\le m}(\rho_i-\rho_\ell)
\prod_{j=0}^{m+1}\prod_{r=2}^L c_{jr}
\ne 0
\right\}.
\]
The reverse generic parameter locus is
\[
\Theta^{\mathrm{left},\circ}_{m,L}
=
\left\{
(\delta,\sigma,d)\in \Theta^{\mathrm{left}}_{m,L}:
\delta
\prod_{i=1}^m(\delta-\sigma_i)
\prod_{1\le i<\ell\le m}(\sigma_i-\sigma_\ell)
\prod_{j=0}^{m+1}\prod_{r=2}^L d_{jr}
\ne 0
\right\}.
\]
\end{definitionv}

\cref{obj:def:generic-parameter-loci} strengthens the assumption-level genericity by also requiring nonzero retained source cumulants. This representation-level restriction selects the finite cumulant coordinates used by the generic theorem.

For a cumulant coordinate vector \leanref{sym:t}{$t$}, the relevant inverse images are the parameter fibers under the two polynomial maps. We use \leanref{sym:R^right_{m,L}(t)}{$R^{\mathrm{right}}_{m,L}(t)$} and \leanref{sym:R^left_{m,L}(t)}{$R^{\mathrm{left}}_{m,L}(t)$} for these fibers.

\begin{definitionv}{def:fiber-correspondences}
For a cumulant vector \(t\), the forward and reverse fibers are
\[
R^{\mathrm{right}}_{m,L}(t)
=
\left\{
\theta\in \Theta^{\mathrm{right}}_{m,L}:
\Phi^{\mathrm{right}}_{m,L}(\theta)=t
\right\},
\qquad
R^{\mathrm{left}}_{m,L}(t)
=
\left\{
\eta\in \Theta^{\mathrm{left}}_{m,L}:
\Phi^{\mathrm{left}}_{m,L}(\eta)=t
\right\}.
\]
\end{definitionv}

\cref{obj:def:fiber-correspondences} separates two questions: whether a cumulant vector lies in an arrow image, and how many parameter points produce it. The same-arrow fiber facts in the next section therefore have a different status from opposite-arrow exclusion.

Source labels in the middle block are exchangeable. The admissible relabelling group \leanref{sym:G_m}{$G_m$} acts by a permutation \leanref{sym:pi}{$\pi$} of the middle labels while fixing the two axis slots.

\begin{definitionv}{def:admissible-source-swaps}
Let \(G_m\) be the permutation group of the middle source labels \(\{1,\ldots,m\}\), acting while fixing labels \(0\) and \(m+1\). For \(\pi\in G_m\), the forward action on parameters is
\[
\pi\cdot(\gamma,(\rho_i)_{i=1}^m,(c_{jr})_{j,r})
=
(\gamma,(\rho_{\pi(i)})_{i=1}^m,(c'_{jr})_{j,r}),
\]
where
\[
c'_{ir}=c_{\pi(i),r}\quad(1\le i\le m),\qquad
c'_{0r}=c_{0r},\qquad
c'_{m+1,r}=c_{m+1,r}.
\]
The left action is the analogous action with \(\gamma,\rho,c\) replaced by \(\delta,\sigma,d\). Thus the source labels \(0\) and \(m+1\) are fixed, while the labels \(1,\ldots,m\) are permuted.
\end{definitionv}

\cref{obj:def:admissible-source-swaps} specifies the label symmetry quotiented in the paper. It fixes the direct-axis and fixed-axis source slots and permits permutations among the middle latent-source slots.

\subsection{The real-feasibility bridge}

The algebraic parameter spaces allow arbitrary complex source-cumulant weights. For econometric interpretation, we also need real parameter points whose source cumulants are realized by centered non-Gaussian real random variables through the retained order. These real feasible regions are denoted \leanref{sym:F^right_{m,L}}{$F^{\mathrm{right}}_{m,L}$} and \leanref{sym:F^left_{m,L}}{$F^{\mathrm{left}}_{m,L}$}. They bridge the complex theorem layer to real source models and retain the theorem's parameter-space interpretation.

\begin{definitionv}{def:real-feasible-regions}[Real feasible regions \(F^{\mathrm{right}}_{m,L}\) and \(F^{\mathrm{left}}_{m,L}\)]
Using the cumulant convention of \cref{obj:def:truncated-cumulant}, the forward real feasible region \(F^{\mathrm{right}}_{m,L}\) is the set of all real tuples \((\gamma,\rho,c)\in \mathbb R^{m+1}\times \mathbb R^{(m+2)(L-1)}\) such that \(\gamma\neq 0\), the slopes \(\rho_1,\ldots,\rho_m,\gamma\) are pairwise distinct, and, for every \(0\leq j\leq m+1\), there exists a centered non-Gaussian real random variable \(S_j\) with \(\mathbb E|S_j|^L<\infty\) satisfying
\[
\operatorname{Cum}_r(S_j)=c_{jr},
\qquad 2\leq r\leq L.
\]
The reverse real feasible region \(F^{\mathrm{left}}_{m,L}\) is defined analogously, with \((\delta,\sigma,d)\) in place of \((\gamma,\rho,c)\) and with \(\delta\neq 0\).
\end{definitionv}

\cref{obj:def:real-feasible-regions} identifies the finite real cumulant coordinates realized by actual centered non-Gaussian source laws.

We summarize the amount of cumulant information needed for generic real arrow separation by the information order \leanref{sym:K^star(m)}{$K^\star(m)$}. The arrow index \leanref{sym:b}{$b$} ranges over the two conventions, and \(\operatorname{opposite}(b)\) denotes the opposite-arrow involution.

\begin{definitionv}{def:information-order}[Information order \(K^\star(m)\)]
For \(b\in\{\mathrm{right},\mathrm{left}\}\), use the branch convention \(\Phi^b_{m,L}=\Phi^{\mathrm{right}}_{m,L}\) and \(F^b_{m,L}=F^{\mathrm{right}}_{m,L}\) when \(b=\mathrm{right}\), and \(\Phi^b_{m,L}=\Phi^{\mathrm{left}}_{m,L}\) and \(F^b_{m,L}=F^{\mathrm{left}}_{m,L}\) when \(b=\mathrm{left}\), using \cref{obj:def:forward-cumulant-map},~\cref{obj:def:reverse-cumulant-map}, and~\cref{obj:def:real-feasible-regions}. Define \(\operatorname{opposite}(\mathrm{right})=\mathrm{left}\) and \(\operatorname{opposite}(\mathrm{left})=\mathrm{right}\). Define \(K^\star(m)\) to be the minimum integer \(L\geq 2\), if such an integer exists, such that for each \(b\in\{\mathrm{right},\mathrm{left}\}\), outside a proper real algebraic subset of \(F^b_{m,L}\), the cumulant vector
\[
\Phi^b_{m,L}(\theta)
\]
has no representation in
\[
F^{\operatorname{opposite}(b)}_{m,L}.
\]
If no such \(L\) exists, set \(K^\star(m)=\infty\).
\end{definitionv}

\cref{obj:def:information-order} introduces notation for the generic separation threshold. The value \(K^\star(m)=2m+2\) serves as a conjectural benchmark, and the later information-order theorem establishes the sharper value in the relevant range.

Finally, the main theorem uses the classical apolar language for binary forms. For a finite projective support \(D\), the polynomial \(Q_D\) annihilates that support, and \(q(\partial)\) denotes the associated constant-coefficient differential operator. This notation is standard in binary-form decomposition and Waring-rank geometry \citep{ComonMourrain1996,Landsberg2012}.

\begin{definitionv}{def:apolar-notation}[Apolar operators \(Q_D\) and \(q(\partial)\)]
For a finite projective loading-direction support \(D\), define \(Q_D\) to be its squarefree homogeneous support-annihilator polynomial, with the normalization used by the cumulant-map coordinates. For a homogeneous binary form \(q(x,y)\), define \(q(\partial)\) to be the constant-coefficient differential operator obtained by substituting \(\partial_x,\partial_y\) for \(x,y\). For a real parameter set \(A\), define \(A_{\mathbb C}\) to be its coordinatewise complexification.
\end{definitionv}

\cref{obj:def:apolar-notation} supplies the notation used to recover unordered loading directions from truncated higher-order population cumulants.
