\section{Discussion and extensions}

\subsection{Interpretation}

The results in the preceding section identify a representation-level exclusion restriction in bivariate latent linear non-Gaussian models. \Cref{obj:thm:generic-apolar-arrow-recovery} excludes the opposite axis-normalized cumulant-map fiber. Thus, if a structural model \leanref{sym:M}{$M$} induces observational law \leanref{sym:P_M}{$P_M$}, the theorems characterize the truncated cumulants of \(P_M\) under the fixed source-count and axis-normalization conventions of \cref{obj:def:forward-lvlingam-class} and~\cref{obj:def:reverse-lvlingam-class}.

This distinction matters for econometric interpretation. In a conventional nonparametric identification problem, one asks whether the observational law determines a structural object over a specified model class. Here the maintained class is more structured: independent non-Gaussian source slots, a fixed and externally specified number of slots, and two axis-normalized loading conventions. A natural user is therefore a researcher whose institutional or factor model fixes these inputs and who wants to know whether the competing recursive specification is compatible with the population cumulants. Within that class, higher-order cumulants impose restrictions beyond covariance information and can generically exclude the opposite truncated-cumulant fiber. Related recent work on algebraic and semialgebraic identification likewise distinguishes generic algebraic separation from full distributional identification \citep{MestersZwiernik2022,Virolainen2024}.

The codimension-one exceptional locus in \cref{obj:thm:exceptional-locus-codimension-one} is a compatibility set for truncated cumulant vectors. Generic separation holds off this Zariski-closed set, and the theorem gives it exactly codimension one inside each arrow image variety at the apolar order. Econometrically, opposite-arrow compatibility is therefore a genuine lower-dimensional restriction governed by a single algebraic dimension even when \(m\ge2\). The size of this set motivates explicit reporting in applications where the data-generating process may be close to a compatibility surface.

The same-arrow fiber statements in \cref{obj:thm:generic-arrow-recovery-and-fiber-obstruction} sharpen the interpretation of the information recovered. The unordered loading-slope support is recovered on the stated generic loci, while the chosen arrow retains parametrization ambiguity beyond the admissible middle-source relabellings of \cref{obj:def:admissible-source-swaps}. In particular, exchanging a direct slot with a middle slot can preserve the cumulant vector while falling outside the admissible \(G_m\)-orbit. Opposite-fiber exclusion is therefore compatible with substantial within-convention nonidentification.

The information-order result has a separate role. The apolar theorem uses order \(2m+2\) to recover the unordered loading support through the binary-form annihilator equations. \Cref{obj:thm:improved-real-information-order} shows that, for \(m\ge3\), generic real exclusion of the opposite arrow can already occur at order \(2m+1\). The two thresholds therefore align with distinct targets: generic real arrow separation at \(2m+1\) and loading-support recovery at \(2m+2\).

\subsection{Limitations and future work}

These qualifications also delimit the connection to empirical practice. The paper provides population-level algebraic identification statements for truncated cumulants. Its immediate user is a theorist or model-class analyst who treats \(m\) and the axis normalization as maintained inputs and needs to know whether the population cumulant map separates the two representations. It does not supply a finite-sample estimator, a sampling distribution, a model-selection criterion, or a numerical decision rule. Any applied implementation would have to confront cumulant estimation error, weak higher-order signal, near-exceptional parameter values, and uncertainty about the number of source slots. Recent work on latent non-Gaussian identification and causal discovery develops complementary estimation and testing perspectives, but those problems are not solved by the generic separation theorem alone \citep{XieHuangChenEtAl2023,MorinishiShimizu2025,ChenGuPengEtAl2025}.

The main contribution is algebraic econometric identification for a fixed, axis-normalized latent-source representation class. Higher-order cumulants generically contain enough information to exclude the opposite convention's cumulant-map fiber inside that class, the exceptional compatibility set is exactly codimension one at the apolar order, and lower real truncation can suffice for generic opposite-fiber exclusion when \(m\ge3\). These statements establish the population information available before estimation and provide a foundation for future finite-sample procedures.
