\section{Appendix: verification and reproducibility scope}

\begin{definitionv}{def:global-feasible-fiber-decision}[Order-\(2m+2\) feasible-fiber predicate \(\operatorname{FeasFiber}^{b}_{m,2m+2}(t)\)]
Set \(K=2m+2\). For \(b\in\{\mathrm{right},\mathrm{left}\}\), with the branch convention of \cref{obj:def:information-order}, define the order-\(K\) predicate \(\operatorname{FeasFiber}^{b}_{m,2m+2}(t)\) to be the atomic-certificate predicate asserting that there exist real \(b\)-loading and source-cumulant coordinates \(\lambda\), and, for each \(0\leq j\leq m+1\), witnesses
\[
(w_{jh},z_{jh})_{h=1}^{m+2},
\]
such that
\[
\Phi^b_{m,K}(\lambda)=t,
\]
the direct slope for \(b\) is nonzero, all finite loading slopes for \(b\) are pairwise distinct, and the following moment conditions hold. Write \(k_{jr}\) for the source cumulants contained in \(\lambda\), let \(B_r\) denote the complete exponential Bell polynomial (the cumulant-to-moment polynomial), and set
\[
\mu_{jr}=B_r(0,k_{j2},\ldots,k_{jr}).
\]
Then
\[
\sum_{h=1}^{m+2} w_{jh}=1,\qquad
w_{jh}\geq 0,\qquad
\sum_{h=1}^{m+2} w_{jh}z_{jh}^r=\mu_{jr}\quad(1\leq r\leq K),
\qquad
\mu_{j2}>0.
\]
Separately, the formal object records an unproved proposition asserting the existence of a sign-invariant cylindrical algebraic decomposition procedure, in variable order \(t\), then \(\lambda\), then the witnesses, that decides this displayed predicate for the fixed axis \(b\). The predicate definition itself does not assert equivalence with nonemptiness of the corresponding real-source feasible fiber.
\end{definitionv}

\begin{definitionv}{def:direction-selector}[Direction selector \(S_m\)]
Using the order-\(2m+2\) feasible-fiber predicates of \cref{obj:def:global-feasible-fiber-decision}, define the partial direction selector
\[
S_m(t)=
\begin{cases}
X\to Y,&\operatorname{FeasFiber}^{\mathrm{right}}_{m,2m+2}(t)\text{ holds and }\operatorname{FeasFiber}^{\mathrm{left}}_{m,2m+2}(t)\text{ does not},\\
Y\to X,&\operatorname{FeasFiber}^{\mathrm{left}}_{m,2m+2}(t)\text{ holds and }\operatorname{FeasFiber}^{\mathrm{right}}_{m,2m+2}(t)\text{ does not},\\
\text{undefined},&\text{otherwise}.
\end{cases}
\]
Separately, the formal object records the unproved proposition that a globally finite semialgebraic function on \(\mathbb R^{q_{2m+2}}\) agrees with \(S_m\) wherever exactly one feasibility predicate holds, together with Boolean decision functions for the forward and reverse maps. This definition supplies neither a proof of that proposition nor an evaluable decision procedure.
\end{definitionv}

\begin{definitionv}{def:separated-model-domain}[Separated model domain \(M^{\mathrm{sep}}_{m,K}\)]
For a structural model \(M\), write \(P_M\) for its induced observational law and \(D(M)\in\{X\to Y,Y\to X\}\) for its arrow. Define \(M^{\mathrm{sep}}_{m,K}\) to be the class of structural models \(M\) such that either \(M\) has a forward representation with parameter \(\theta\in F^{\mathrm{right}}_{m,K}\) and
\[
R^{\mathrm{left}}_{m,K}\bigl(T_K(P_M)\bigr)\cap F^{\mathrm{left}}_{m,K}=\varnothing,
\]
or \(M\) has a reverse representation with parameter \(\eta\in F^{\mathrm{left}}_{m,K}\) and
\[
R^{\mathrm{right}}_{m,K}\bigl(T_K(P_M)\bigr)\cap F^{\mathrm{right}}_{m,K}=\varnothing.
\]
\end{definitionv}

\begin{remarkv}{thm:exact-real-exceptional-atlas}[Exact Real Exceptional Atlas]
One worthwhile direction for future research is to determine whether \emph{For every fixed m, there is a finite computable semialgebraic cylindrical atlas of the real exceptional closure such that, on each base cell, the complete feasible forward and reverse fibers are finite unions of recursively cylindrical section and sector cells and their nonemptiness labels are constant. The atlas includes singular and nongeneric boundary branches and decides exactly when both real arrows are feasible.}. Doing so requires the remaining paper-specific exact-atlas constructor would require substantial CAD/elimination substrate, while the node is secondary and has no delivered theorem consumer, which lies beyond the present development.
\end{remarkv}

The formal claim in this paper is reproducible at the source revision used to build the manuscript. The repository is \url{https://github.com/Jiyuan-Tan/CausalForge}; the pinned revision is
\[
\texttt{2c9214dff2d737c1d131f6056916aad82bdc7e4b},
\]
and the CausalSmith project uses Lean \texttt{v4.29.0-rc3}. The matching
machine-readable contract is
\path{CausalSmith/doc/presentation/eid_lingam_direction_min_order_v1_truncated_cumulant_minimality/verification_contract.json};
the declaration table below refers to that same revision. From the repository
root, the checked project is built with
\[
\texttt{lake -d CausalSmith build}.
\]
The repository's \texttt{CausalSmith/lean-toolchain}, \texttt{CausalSmith/lakefile.toml}, and dependency manifests fix the toolchain and local Causalean dependency used by that build.

\begin{table}[ht]
\centering
\scriptsize
\caption{Main paper results and checked Lean declarations}
\begin{tabular}{p{0.30\linewidth}p{0.62\linewidth}}
\hline
Paper result & Lean declaration \\
\hline
Generic apolar arrow recovery &
\texttt{CausalSmith.ExactID.EID\_LingamDirectionMinOrderV1.generic\_apolar\_arrow\_recovery} \\
Same-arrow fiber consequences &
\texttt{CausalSmith.ExactID.EID\_LingamDirectionMinOrderV1.genericArrowRecoveryAndFiberObstruction} \\
Exceptional locus of codimension one &
\texttt{CausalSmith.ExactID.EID\_LingamDirectionMinOrderV1.exceptionalLocusCodimensionOne} \\
Improved real information order &
\texttt{CausalSmith.ExactID.EID\_LingamDirectionMinOrderV1.improvedRealInformationOrder} \\
Admissible-swap invariance &
\texttt{CausalSmith.ExactID.EID\_LingamDirectionMinOrderV1.admissibleSwaps\_preserve\_direction} \\
\hline
\end{tabular}
\end{table}

The generated \texttt{verification\_contract.json} in the paper bundle gives the full declaration-to-paper mapping, source file, statement match, and sorry-free status for every displayed formal object. The checked scope covers the frozen definitions and theorems used for the cumulant maps, generic separation, same-arrow fiber behavior, exceptional-locus dimension, and information-order result. Classical library facts and explicitly stated external algebraic inputs remain dependencies, while the prose supplies the surrounding interpretation.

\paragraph{Limitations.}
The formalization does not certify an estimator, sampling theory, selection of \(m\), or an exact decision procedure for all real feasible fibers, including singular and nongeneric boundary cases. Those tasks are outside the delivered contribution.
