% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_text\_treatment\_distortion, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_text\_treatment\_distortion} / \texttt{v1}%
  \\ \large\textit{Selector-indexed distortion frontiers for text/image treatment representations}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
  (\texttt{qid},\texttt{specialization},P,\Theta_\epsilon,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_text\_treatment\_distortion},\texttt{v1},
  P_{Z,Y},\ \Theta_{\epsilon}(r_1,r_0),\
  \mathcal R_{\epsilon,\mathrm{dist+suff}},\
  B_\epsilon(P;r_1,r_0)).
\end{gathered}
\]
Here \(Z\in\mathcal Z\subset\mathbb R^d\) is the learned observed representation of a randomized high-dimensional text/image treatment object, \(Y\in[0,1]\) is the outcome, \(P_{Z,Y}\) is the observable law, and \(\mu\) is the \(P_Z\)-a.s. equivalence class of observed-representation regressions \(\E_P[Y\mid Z=z]\).  The latent oracle representation is \(R^\star\in\mathcal Z\) and is known only to satisfy \(\|R^\star-Z\|_\infty\le\epsilon\) almost surely.  The target object is not a single unqualified number \(m(r_1)-m(r_0)\): an intervention fixing \(R^\star=r_j\) must also specify a stochastic learned-preimage selector \(\kappa_j\) on the feasible fiber \(B_\infty(r_j,\epsilon)\cap\operatorname{supp}(Z)\).  For selectors \(\kappa_1,\kappa_0\), the selector-indexed oracle contrast is \(\theta_{\kappa}(r_1,r_0)=\int\mu(z)\,d\kappa_1(z)-\int\mu(z)\,d\kappa_0(z)\), and \(\Theta_{\epsilon}(r_1,r_0)\) ranges this contrast over all admissible selectors.  The identifying restrictions \(\mathcal R_{\epsilon,\mathrm{dist+suff}}\) are randomized object assignment, consistency, bounded outcomes, selector-stable observed-response sufficiency, positive-mass local distortion fibers, target inverse-reachability of \(r_1,r_0\) through admissible stochastic selectors, and distortion-only calibration: any measurable oracle calibration inside the \(\epsilon\)-balls that preserves \(P_{Z,Y}\) and satisfies the selector equations is admissible.  The bounding functional is the essential distortion envelope
\[
B_\epsilon(P;r_1,r_0)=
\left[
  \operatorname*{ess\,inf}_{u\in B_\infty(r_1,\epsilon)\cap\operatorname{supp}(Z)}\mu(u)
  -
  \operatorname*{ess\,sup}_{v\in B_\infty(r_0,\epsilon)\cap\operatorname{supp}(Z)}\mu(v),\
  \operatorname*{ess\,sup}_{u\in B_\infty(r_1,\epsilon)\cap\operatorname{supp}(Z)}\mu(u)
  -
  \operatorname*{ess\,inf}_{v\in B_\infty(r_0,\epsilon)\cap\operatorname{supp}(Z)}\mu(v)
\right].
\]

\begin{abstract}
Many current designs for causal inference with text or images replace the object treatment by a learned representation and then report one regression endpoint.  This proposal asks what remains identified when that learned representation is only known to be within an \(\ell_\infty\) distortion budget \(\epsilon\) of an oracle causal representation.  The flagship conjecture is that the sharp selector-indexed ATE set is the essential ballwise observed-regression envelope \(B_\epsilon(P;r_1,r_0)\), once the intervention fixing an oracle representation is required to name the learned-preimage distribution it induces.  The flagship impossibility result is estimator-specific: for the single learned-representation endpoint used by GenAI text-treatment workflows, bounded distortion plus randomized assignment is generically insufficient unless the named structural assumption of \(\epsilon\)-fiber invariance holds on the target fibers; otherwise an open class of observable laws admits multiple selector-indexed oracle contrasts, with sign reversal under a local crossing.  The exact-recovery corner \(\epsilon=0\) is retained as an atomic sanity boundary for \(B_0\), with continuous point-evaluation recovery treated separately as a different target functional.  If resolved, the result would give text-as-treatment and image-as-treatment studies a finite sensitivity frontier and an empirically checkable calibration condition rather than a silent plug-in endpoint.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
High-dimensional object treatments are now common in political science, social science, marketing, medicine, and vision applications: the treatment is a text, image, video, graph, or generated object rather than a scalar dose.  The methodological promise is that a learned representation can reduce the object to a tractable causal treatment coordinate.  The identification risk is that a representation can be nearly correct in a predictive or geometric sense while still moving the causal endpoint, because causal contrasts use values of an oracle representation that are not directly observed.

\paragraph{The main finding (proposed).}
The proposed main finding is Conjecture~\ref{conj:sharp-envelope}: under randomized object assignment, selector-stable observed-response sufficiency, and only an \(\epsilon\)-sup-norm distortion restriction between the learned and oracle representations, the sharp identified set for the selector-indexed oracle contrast \(\theta_{\kappa}(r_1,r_0)\) is exactly the essential-envelope functional \(B_\epsilon(P;r_1,r_0)\).  Theorem~\ref{thm:finite-support-lp} gives the finite-support version as an explicit selector linear program, making the law-preservation equations visible rather than hiding them in random-set notation.  Conjecture~\ref{conj:single-endpoint-impossibility} then states the flagship impossibility for the published learned-representation endpoint: if \(\mu\) is not \(\epsilon\)-fiber invariant on the target balls, the plug-in contrast that treats the learned representation as the oracle representation cannot be a uniformly valid ATE estimand on the full distortion-only model; in an open class of laws with a local crossing, admissible selectors give opposite signs.

\paragraph{What is new.}
The novelty kernel is not that learned representations may be biased, and not another estimator for text treatments.  The closest text-causal papers either use observed text as a confounder proxy through causally sufficient embeddings \citep{VeitchSridharBlei2020}, propose GenAI internal representations as exact treatment features and report fitted representation-surface contrasts \citep{ImaiNakamura2024TextTreatments,ImaiNakamura2025GPI}, or warn that latent text treatments require extra assumptions \citep{FongGrimmer2023}.  The flagship epsilon-gap here is a sharp selector-indexed partial-identification statement for oracle target values that are inverse-reachable through learned-representation support, plus an estimator-specific obstruction for the published single-representation endpoint: approximate sufficiency is converted into an explicit intervention-kernel frontier, and the paper-level object is the necessary-and-sufficient \(\epsilon\)-fiber-invariance certificate for when the published endpoint can collapse that frontier to one number.  This is stronger than a domain-specific random-set envelope because the finite-support LP exposes the exact selector variables and the Borel conjecture predicts a uniform, empirically checkable singleton boundary from the observable regression on target balls.

\paragraph{How it positions in the literature.}
This sits in the partial-identification and sensitivity-analysis cluster.  Manski-style bounded variation over latent quantities, random-set identification, and corrupted-data or measurement-error bounds supply the mathematical grammar; text and structured-treatment causal inference supply the active frontier where the issue matters.  The proposal deliberately avoids panel and structural-SCM axiomatics: the object is a sharp identified set for an ATE under representation distortion.

\paragraph{Implications for the community.}
The concrete community implication is for the texts-as-treatments and GenAI internal-representation workflow of \citet{ImaiNakamura2024TextTreatments}: when an analyst can only validate a learned representation up to a representation error radius, the reported endpoint should be replaced by \(B_\epsilon(P;r_1,r_0)\) or accompanied by a defense of \(\epsilon\)-fiber invariance as the additional structural assumption that chooses a unique selector-indexed contrast.

\paragraph{How research benefits from the conclusion.}
If a reader takes only the conclusion away, their research practice changes from reporting one text- or image-representation regression contrast to reporting a distortion envelope and checking whether the observed regression is constant on the target distortion fibers.

\section{Related work}
\citet{VeitchSridharBlei2020} is a text-adjustment anchor: it develops causally sufficient embeddings for estimating causal effects from observational text used as covariate information, whereas this proposal concerns text or images as structured treatments and asks what sharp identified set remains when a treatment representation is only approximately recovered.  \citet{EgamiFongGrimmerRobertsStewart2022} show that text-based causal inferences depend on latent representations and that estimating those representations can create identification problems or overfitting; this proposal treats representation error as an observational-equivalence restriction rather than a sample-splitting problem.  \citet{FongGrimmer2023} show that randomized texts do not by themselves identify latent-treatment effects when unmeasured latent text features move together; the present proposal turns that qualitative insufficiency into a quantitative distortion frontier.

\citet{ImaiNakamura2024TextTreatments} propose using generative-model internal representations for causal inference with texts as treatments and motivate the oracle-representation language used here; the estimator-specific contrast in Conjecture~\ref{conj:single-endpoint-impossibility} targets the resulting fitted representation-surface endpoint when the internal representation is only approximately recovered.  \citet{ImaiNakamura2025GPI} generalize GenAI-powered inference to unstructured data including text and images, making the learned-representation endpoint a current methodological object rather than a textbook example.  \citet{ImaiNakamura2026Dynamic} extend this agenda to dynamic unstructured treatments; the contrast here is that even the static one-object endpoint has a nontrivial partial-ID frontier when representation recovery is approximate.

\citet{KaddourZhuLiuKusnerSilva2021} develop structured-treatment CATE estimation using a generalized Robinson decomposition; their estimator assumes the structured treatment representation is the object entering the causal estimand, while this proposal asks when such a single representation endpoint is identified under oracle distortion.  \citet{CorcollAndreuVlontzosORiordanGilliganLee2026} show that contrastive representations for structured treatments can support unbiased causal estimation under causal-latent separation assumptions; the present proposal supplies the complementary warning that a distortion ball around the learned representation remains interval-valued unless the observed regression is fiber invariant.  This is not a claim that those papers assert validity under bounded representation distortion alone; rather, their exact representation or separation assumptions are the named structural assumptions replaced here by a selector-indexed sensitivity frontier.  \citet{MozerMiratrixKaufmanAnastasopoulos2020} study representation and distance choices for matching with text data, illustrating why geometric closeness of documents is an empirical design object; this proposal asks for the causal identified set induced by a formal closeness budget.

\citet{Manski1990} and \citet{Manski2003} are the bounded-outcome and partial-identification anchors: they justify ranging causal parameters over all latent completions compatible with data and restrictions.  \citet{ManskiTamer2002} is the closest interval-data comparator because it studies regressions when a regressor or outcome is only known to lie in an interval; the present proposal differs by treating the interval as a high-dimensional representation fiber for a causal intervention target and by asking for the sharp ATE set, not a semiparametric regression parameter set.  \citet{HorowitzManski1995} give the classic corrupted-data robustness analysis; the present proposal is not another contamination-rate interval, because the admissible ambiguity is geometric inverse-calibration of target representation values through \(\ell_\infty\) fibers.  \citet{BeresteanuMolchanovMolinari2012} provide the random-set language for latent feasible sets; here the random set is the \(\epsilon\)-ball of learned representations that can serve as observed preimages of an oracle target.  \citet{BeresteanuMolchanovMolinari2011} show how sharp identification regions can be represented through Aumann expectations of random sets, which is the closest general econometric comparator to the ballwise envelope.  \citet{Ura2018} gives sharp finite bounds for treatment effects with mismeasured binary endogenous treatment; this proposal differs because high-dimensional representation distortion produces target-fiber regression extrema and a fiber-invariance singleton condition rather than a scalar treatment-error bound.

The in-catalogue ThmSmith prior art does not already contain this kernel.  \texttt{doc/API.md} Section 3 records ExactID/PartialID as seed catalogues for Manski-family bounds, IV bounds, sensitivity analysis, shape restrictions, and missing-data bounds, but it has no representation-distortion theorem.  The closest banked proposal is \texttt{pid\_network\_exposure} (``Sharp ADE bounds from shared local-network completions under misspecified exposure maps''), which is also a partial-ID problem over hidden completions, but its kernel is graph-completion compatibility rather than learned-representation distortion.  The banked \texttt{pid\_dose\_response\_shape} proposal studies shape-restricted dose-response sensitivity, and \texttt{pid\_long\_term\_surrogate} studies surrogate drift; neither contains the \(\epsilon\)-fiber-invariance boundary for text or image treatment representations.

\section{Formal setup}
Let \(T\) be a randomized high-dimensional treatment object, such as a text or image, and let \(Z=\phi(T)\in\mathcal Z\subset\mathbb R^d\) be the learned representation observed by the analyst.  Let \(R^\star=\rho(T)\in\mathcal Z\) be the latent oracle representation, but suppose \(\rho\) is not observed.  The observable law is \(P=P_{Z,Y}\), the observed regression \(\mu\) is the \(P_Z\)-a.s. equivalence class of conditional means \(\E_P[Y\mid Z=z]\), and outcomes are bounded in \([0,1]\).  The published single-representation endpoint targeted by this proposal is the plug-in contrast
\[
\Delta_{\mathrm{plug}}(P;r_1,r_0)=\mu^\dagger(r_1)-\mu^\dagger(r_0),
\]
where \(\mu^\dagger\) is a chosen fitted or identified version of the outcome surface on the learned-representation coordinate, as in workflows that treat the learned internal representation as the causal treatment feature.  For target oracle representation values \(r_1,r_0\in\mathcal Z\), an intervention fixing \(R^\star=r_j\) is incomplete until it specifies the distribution of learned preimages \(Z\) among objects compatible with that oracle value.  Let \(\mathcal K_\epsilon(r)\) be the class of probability selectors \(\kappa_r\) supported on the distortion fiber \(\mathcal F_\epsilon(r)\) and absolutely continuous with respect to \(P_Z\) restricted to that fiber, together with limits of such selectors along positive-mass sets used to attain essential extrema; in the finite-support specialization, \(\mathcal K_\epsilon(r)\) is the simplex over atoms in the fiber.  The selector-indexed parameter is
\[
\theta_{\kappa}(r_1,r_0)
=
\int_{\mathcal F_\epsilon(r_1)}\mu(z)\,d\kappa_1(z)
-
\int_{\mathcal F_\epsilon(r_0)}\mu(z)\,d\kappa_0(z),
\]
and the unidentified object \(\Theta_\epsilon(P;r_1,r_0)\) is the closed set of all such values over admissible selector pairs \(\kappa=(\kappa_1,\kappa_0)\in\mathcal K_\epsilon(r_1)\times\mathcal K_\epsilon(r_0)\).  If a substantive intervention supplies a particular kernel \(\kappa\), the target is \(\theta_\kappa\); if it only says ``set the oracle representation to \(r_j\),'' the identified object is the selector frontier \(\Theta_\epsilon\).

For \(\epsilon\ge0\), define the closed distortion fiber
\[
\mathcal F_\epsilon(r)=B_\infty(r,\epsilon)\cap\operatorname{supp}(Z)
=\{z\in\operatorname{supp}(Z):\|z-r\|_\infty\le\epsilon\}.
\]
Whenever \(P_Z(\mathcal F_\epsilon(r))>0\), write
\[
\underline\mu_\epsilon(r)=\operatorname*{ess\,inf}_{z\in\mathcal F_\epsilon(r)}\mu(z),
\qquad
\overline\mu_\epsilon(r)=\operatorname*{ess\,sup}_{z\in\mathcal F_\epsilon(r)}\mu(z),
\]
with essential extrema taken under the conditional \(P_Z\)-law restricted to \(\mathcal F_\epsilon(r)\).  These are observable-law functionals of the regression equivalence class, unlike pointwise values of a chosen conditional-mean version on non-atomic support points.  The proposal may be read first under finite \(Z\)-support, where the essential extrema are ordinary minimum and maximum over atoms; the Borel-support statement uses the essential-extrema notation throughout.
The fiber oscillation is \(\operatorname{osc}_\epsilon(r)=\overline\mu_\epsilon(r)-\underline\mu_\epsilon(r)\), and the diameter of a closed interval \(I=[a,b]\) is \(\operatorname{diam}(I)=b-a\).
The identified set \(\Theta_\epsilon(P;r_1,r_0)\) is the set of all values of \(\theta_\kappa(r_1,r_0)\) generated by full-data laws for \((T,Z,R^\star,Y(\cdot))\) whose \((Z,Y)\) marginal is \(P\), whose oracle representation is within \(\epsilon\) of the learned representation almost surely, and whose intervention kernels satisfy the selector equations above.  The proposed bounding functional is \(B_\epsilon(P;r_1,r_0)\), as locked above.
At the exact-recovery boundary, the essential-envelope functional \(B_0\) is defined only when the singleton target fibers have positive \(P_Z\)-mass.  For continuous support with a pre-specified identified version \(\mu^\dagger\), the separate point-evaluation functional is
\[
B^{\mathrm{eval}}_0(P;r_1,r_0)=\{\mu^\dagger(r_1)-\mu^\dagger(r_0)\},
\]
which records exact-representation recovery of the plug-in endpoint but is not the positive-mass essential-envelope \(B_0\).
An admissible calibration is a pair \((c,\kappa)\), where \(c:\operatorname{supp}(Z)\to\mathcal Z\) is a measurable possible oracle map \(R^\star=c(Z)\) satisfying \(\|c(z)-z\|_\infty\le\epsilon\), and \(\kappa=(\kappa_1,\kappa_0)\) are target-intervention kernels supported on the corresponding target fibers.  A target value \(r\) is inverse-reachable if at least one admissible selector \(\kappa_r\) assigns positive probability only to learned preimages in \(\mathcal F_\epsilon(r)\); under the distortion restriction every such preimage must lie in \(\mathcal F_\epsilon(r)\).  The estimand in this proposal is restricted to target values \(r_1,r_0\) that are inverse-reachable under the admissible selectors used to generate \(\Theta_\epsilon(P;r_1,r_0)\).  For a compact class of target pairs \(\mathcal T\subseteq\mathcal Z^2\) with positive-mass target fibers, the uniform sensitivity frontier is the set-valued map \((r_1,r_0)\mapsto B_\epsilon(P;r_1,r_0)\) over \(\mathcal T\).
An open neighborhood of observable laws means a weak neighborhood of the \(Z\)-marginal together with a uniform neighborhood of the regression function \(\mu\) on the compact target fibers.  An overlapping-support neighborhood of a target value \(r\) means a set of target values \(r'\) whose fibers \(\mathcal F_\epsilon(r')\) intersect a common nonempty relative-open subset of \(\operatorname{supp}(Z)\).

\begin{verbatim}
(qid, specialization, P, Theta_epsilon, identifying restrictions, bounding functional)
=
(pid_text_treatment_distortion, v1,
  P_{Z,Y}, Theta_epsilon(r_1,r_0),
  R_{epsilon,dist+suff},
  B_epsilon(P;r_1,r_0)).
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Randomized object assignment and consistency]\label{ass:randomized-consistency}
The treatment object \(T\) is assigned independently of potential outcomes, and the observed outcome satisfies consistency for the realized object and representation pair.  The target values \(r_1,r_0\) and any substantive selector kernels \(\kappa_1,\kappa_0\) are fixed before seeing outcomes.
\end{assumption}

\begin{assumption}[Bounded outcome and regular observed regression]\label{ass:bounded-regular}
The outcome satisfies \(Y\in[0,1]\).  The observed regression \(\mu\) exists as a \(P_Z\)-a.s. equivalence class, is represented by a bounded measurable version when notation requires a function, and has finite essential infimum and essential supremum on each positive-mass target fiber \(\mathcal F_\epsilon(r_j)\), \(j\in\{0,1\}\).  If \(\epsilon=0\) and a pointwise value at a non-atomic target is used, it is denoted \(\mu^\dagger(r_j)\) and belongs to the separate point-evaluation functional \(B^{\mathrm{eval}}_0\), not to the positive-mass essential-envelope functional \(B_0\).
\end{assumption}

\begin{assumption}[Selector-stable observed-response sufficiency]\label{ass:selector-sufficiency}
For any target value \(r\) and learned-preimage selector \(\kappa_r\) supported on \(\mathcal F_\epsilon(r)\), the mean outcome under the intervention that fixes \(R^\star=r\) and samples the learned preimage from \(\kappa_r\) is \(\int\mu(z)\,d\kappa_r(z)\).  Thus the intervention target explicitly includes the residual distribution over learned object types inside the oracle fiber; without this selector, the phrase ``fix \(R^\star=r\)'' is not a well-defined mean outcome when multiple learned preimages are compatible with \(r\).
\end{assumption}

\begin{assumption}[Sup-norm representation distortion]\label{ass:distortion}
The latent oracle representation and observed learned representation satisfy
\[
\|R^\star-Z\|_\infty\le\epsilon
\]
almost surely, for a known distortion budget \(\epsilon\ge0\).
\end{assumption}

\begin{assumption}[Distortion-only calibration sharpness]\label{ass:distortion-sharpness}
Subject to Assumption~\ref{ass:target-reachability} for the two target values, every measurable oracle calibration \(c:\operatorname{supp}(Z)\to\mathcal Z\) with \(\|c(z)-z\|_\infty\le\epsilon\) and every pair of selector kernels \(\kappa_j\) supported on \(\mathcal F_\epsilon(r_j)\) are admissible, provided the induced \((Z,Y)\) law is \(P\) and the selector-indexed means are computed as in Assumption~\ref{ass:selector-sufficiency}.  No smoothness, Lipschitz, monotonicity, model-training, semantic-alignment, or parametric restriction links two points inside the same distortion fiber unless explicitly stated.
\end{assumption}

\begin{assumption}[Positive-mass target fibers]\label{ass:nonempty-fibers}
For the target values \(r_1,r_0\), the sets \(\mathcal F_\epsilon(r_1)\) and \(\mathcal F_\epsilon(r_0)\) have strictly positive \(P_Z\)-probability.  At the exact-recovery boundary \(\epsilon=0\), this means the target points are positive-mass atoms for statements about \(B_0\); continuous point-evaluation exact recovery is handled only by \(B^{\mathrm{eval}}_0\).
\end{assumption}

\begin{assumption}[Target inverse-reachability]\label{ass:target-reachability}
Every admissible full-data law contributing to \(\Theta_\epsilon(P;r_1,r_0)\) includes selector kernels \(\kappa_j\in\mathcal K_\epsilon(r_j)\), \(j\in\{0,1\}\), whose supports are contained in \(\mathcal F_\epsilon(r_j)\) and whose supports have positive \(P_Z\)-mass in every neighborhood used for essential-extrema approximation.  Conversely, for sharpness, every probability kernel absolutely continuous with respect to \(P_Z\) restricted to \(\mathcal F_\epsilon(r_j)\), every limit of such kernels along positive-mass sets approaching an essential extremum, and every finite-support probability vector on atoms in that fiber, is permitted as a target preimage selector, subject only to the other stated assumptions and preservation of \(P_{Z,Y}\).
\end{assumption}

\begin{assumption}[Finite-support specialization]\label{ass:finite-support}
For finite-support results, \(\operatorname{supp}(Z)\) is a finite set and \(P_Z(z)>0\) for every \(z\in\operatorname{supp}(Z)\).  Selector kernels are then probability vectors over the atoms in the relevant target fiber.
\end{assumption}

\begin{assumption}[\(\epsilon\)-fiber invariance]\label{ass:fiber-invariance}
The observed regression is \(\epsilon\)-fiber invariant on the target pair if \(\mu\) is \(P_Z\)-a.s. constant on \(\mathcal F_\epsilon(r_1)\) and \(P_Z\)-a.s. constant on \(\mathcal F_\epsilon(r_0)\).  The two constants may differ across the two target fibers.
\end{assumption}

\begin{assumption}[Local crossing for sign reversal]\label{ass:local-crossing}
The target pair has a local crossing at budget \(\epsilon\) if
\[
\underline\mu_\epsilon(r_1)
<
\overline\mu_\epsilon(r_0)
\quad\text{and}\quad
\overline\mu_\epsilon(r_1)
>
\underline\mu_\epsilon(r_0).
\]
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite-support selector LP]\label{thm:finite-support-lp}
Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability} and Assumption~\ref{ass:finite-support}, let \(S_j=\{z:\|z-r_j\|_\infty\le\epsilon,\ P_Z(z)>0\}\).  The finite-support selector identified set is
\[
\left\{
\sum_{z\in S_1}w_{1z}\mu(z)-\sum_{z\in S_0}w_{0z}\mu(z):
w_{jz}\ge0,\ \sum_{z\in S_j}w_{jz}=1,\ j\in\{0,1\}
\right\}
=
B_\epsilon(P;r_1,r_0),
\]
where the right-hand side uses ordinary minima and maxima over \(S_1,S_0\).  The law-preservation equations are only the observed restrictions \(\Pr(Z=z,Y\in A)=P_{Z,Y}(z,A)\); the selector weights \(w_{jz}\) index counterfactual intervention kernels for the target oracle values and therefore do not alter the observed marginal.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{ManskiTamer2002} on interval regressors/outcomes, \citet{BeresteanuMolchanovMolinari2011,BeresteanuMolchanovMolinari2012} on random-set sharp regions, and \citet{Ura2018} on treatment measurement error.  The epsilon-gap is the explicit selector LP for high-dimensional learned-representation treatment interventions: the latent ambiguity is not an interval covariate or a contaminated subpopulation, but the distribution of learned preimages that an intervention fixing \(R^\star=r_j\) must carry inside an \(\ell_\infty\) distortion fiber.  This finite-support theorem is included to rule out the ambiguous ``preimage average'' reading: it states the exact variables and law-preservation constraints a reviewer can audit.  (b) The concrete consumer is \citet{ImaiNakamura2024TextTreatments}: finite empirical support is the natural first audit of whether a GenAI representation endpoint survives bounded representation error or must be reported as a selector frontier.

\begin{conjecture}[Conjecture 1: Borel sharp distortion envelope for selector-indexed oracle ATEs]\label{conj:sharp-envelope}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability}, for every \(\epsilon\ge0\),
\[
\Theta_\epsilon(P;r_1,r_0)=B_\epsilon(P;r_1,r_0).
\]
Equivalently, every value between the essential ballwise lower and upper endpoints can be generated by admissible target-intervention selectors without changing the observed law \(P_{Z,Y}\), and no value outside those endpoints is compatible with the distortion restriction and selector-stable response restriction.  Uniformly over any compact target-pair class \(\mathcal T\) satisfying Assumptions~\ref{ass:nonempty-fibers}--\ref{ass:target-reachability}, the same formula defines the representation-distortion sensitivity frontier \((r_1,r_0)\mapsto B_\epsilon(P;r_1,r_0)\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{ManskiTamer2002} on interval regressors/outcomes, \citet{HorowitzManski1995} on corrupted data, \citet{BeresteanuMolchanovMolinari2012} on random-set partial identification, \citet{Ura2018} on sharp bounds with treatment measurement error, and \citet{FongGrimmer2023} on insufficiency of randomized text for latent-treatment effects.  The flagship epsilon-gap is geometric and representation-specific: none of these papers characterizes the sharp selector-indexed ATE set for inverse-reachable high-dimensional oracle target values when the only misspecification is a sup-norm distortion budget around a learned representation, yielding essential-extrema endpoints of the observed-representation regression over target-intervention fibers and a uniform sensitivity frontier over a class of text/image treatment contrasts.  The proposed Borel statement is not just a relabelled random-set envelope because the selector intervention semantics make explicit which residual preimage distribution is part of the causal target, and the finite-support theorem above is the algebraic specialization it must extend.  (b) Resolving the conjecture would give users of the texts-as-treatments workflow in \citet{ImaiNakamura2024TextTreatments} a named sensitivity target: replace a single GenAI-representation endpoint by \(B_\epsilon(P;r_1,r_0)\) whenever exact representation recovery is not defensible.

\begin{conjecture}[Conjecture 2: GenAI representation endpoint obstruction]\label{conj:single-endpoint-impossibility}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability}, suppose \(\epsilon>0\).  Consider the learned-representation plug-in endpoint \(\Delta_{\mathrm{plug}}(P;r_1,r_0)=\mu^\dagger(r_1)-\mu^\dagger(r_0)\) used by workflows that treat the internal learned representation as the causal treatment feature.  If Assumption~\ref{ass:fiber-invariance} fails on at least one target fiber, then there is an open neighborhood of observable laws around \(P\) on which \(\Delta_{\mathrm{plug}}\) cannot equal \(\theta_\kappa(r_1,r_0)\) for all admissible selector kernels \(\kappa\) in the distortion-only model.  Quantitatively, \(\operatorname{diam}(\Theta_\epsilon(P;r_1,r_0))\) is at least \(\operatorname{osc}_\epsilon(r_j)\) for a non-invariant target fiber \(r_j\) after holding the other selector fixed.  If, in addition, Assumption~\ref{ass:local-crossing} holds, admissible selectors can be chosen so that one gives \(\theta_\kappa(r_1,r_0)>0\) and another gives \(\theta_\kappa(r_1,r_0)<0\), while \(\Delta_{\mathrm{plug}}\) reports only one sign.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) This is not a strawman claim that \citet{ImaiNakamura2024TextTreatments} or \citet{CorcollAndreuVlontzosORiordanGilliganLee2026} assert validity under bounded distortion alone; those papers impose true internal representations or causal-latent separation conditions.  The flagship epsilon-gap is the complementary nonparametric impossibility boundary for the specific fitted representation-surface endpoint used in the GenAI text-treatment workflow: \(\epsilon\)-fiber invariance is the named structural condition required to collapse a selector-indexed representation frontier to that published endpoint, and failure of that condition produces an open-class obstruction rather than a hand-tuned two-calibration example.  \citet{EgamiFongGrimmerRobertsStewart2022} and \citet{FongGrimmer2023} warn that learned or latent text representations may create identification problems, but they do not give this necessary singleton condition or the sign-reversal frontier for inverse-reachable oracle targets.  (b) The concrete consumer is the GenAI representation-as-treatment program of \citet{ImaiNakamura2024TextTreatments}: the conjecture says the analyst must either report the distortion envelope or defend \(\epsilon\)-fiber invariance before interpreting the fitted representation-surface contrast as an ATE.

\begin{theorem}[Theorem 2: fiber invariance is the singleton certificate for the proposed envelope]\label{thm:fiber-singleton}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, \(B_\epsilon(P;r_1,r_0)\) is a singleton if Assumption~\ref{ass:fiber-invariance} holds on the target pair.  Conversely, if \(B_\epsilon(P;r_1,r_0)\) is a singleton for every choice of the other target point in an overlapping-support neighborhood, then \(\mu\) is \(\epsilon\)-fiber invariant on the corresponding target fiber.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is routine interval algebra for the proposed bounding functional, but it names the structural assumption hidden behind any single learned-representation endpoint.  It is closest to the structured-treatment representation assumptions in \citet{ImaiNakamura2024TextTreatments} and \citet{CorcollAndreuVlontzosORiordanGilliganLee2026}; neither states \(\epsilon\)-fiber invariance as the singleton certificate under bounded representation distortion.  (b) The consumer is the GenAI-powered inference program of \citet{ImaiNakamura2025GPI}: the theorem gives a diagnostic for when a low-dimensional representation endpoint can be reported without an additional distortion interval.

\section{Sanity-check corollaries}
\begin{corollary}[Exact-recovery reduction]\label{cor:exact}
Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability}, if \(\epsilon=0\) and \(P_Z(\{r_1\})>0\), \(P_Z(\{r_0\})>0\), then \(B_0(P;r_1,r_0)=\{\mu(r_1)-\mu(r_0)\}\), matching the exact-representation plug-in endpoint on atoms.  If instead \(r_1,r_0\) are non-atomic points with a pre-specified identified continuous version \(\mu^\dagger\), the exact-recovery target is the separate point-evaluation functional \(B^{\mathrm{eval}}_0(P;r_1,r_0)=\{\mu^\dagger(r_1)-\mu^\dagger(r_0)\}\), not the essential-envelope \(B_0\).
\end{corollary}
The reduction is concrete: under Assumption~\ref{ass:distortion}, zero distortion forces \(R^\star=Z\), so each positive-mass target fiber is an atom; Assumption~\ref{ass:bounded-regular} then makes the essential lower and upper endpoint values equal the identified atom value \(\mu(r_j)\).  The continuous-version branch is checked separately by the displayed definition of \(B^{\mathrm{eval}}_0\), avoiding pointwise evaluation inside an essential-extrema functional.

\begin{corollary}[Flat-regression reduction]\label{cor:flat}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, if \(\mu(z)=c\) \(P_Z\)-a.s. on \(\mathcal F_\epsilon(r_1)\cup\mathcal F_\epsilon(r_0)\), then \(B_\epsilon(P;r_1,r_0)=\{0\}\).
\end{corollary}
The reduction is concrete: under Assumption~\ref{ass:fiber-invariance} with equal constants on both target fibers, all four endpoint extrema equal \(c\), so the lower and upper ATE bounds are both zero.

\begin{corollary}[Separated-fiber sign decision]\label{cor:separated}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, if
\[
\underline\mu_\epsilon(r_1)>
\overline\mu_\epsilon(r_0),
\]
then every value in \(B_\epsilon(P;r_1,r_0)\) is positive.
\end{corollary}
The reduction is concrete: the lower endpoint of the envelope is positive by the displayed strict separation, so even the most adverse admissible oracle calibration preserves the sign.

\section{Proof-sketch route}
The mathematical route begins with the finite-support selector LP: write one simplex of weights over the atoms in each target distortion fiber, use Assumption~\ref{ass:selector-sufficiency} to identify each selector mean as a weighted average of \(\mu(z)\), and observe that the difference of two simplex averages is exactly the interval between the worst and best endpoint choices.  The Borel conjecture should then follow by replacing atomwise minima and maxima with essential extrema and approximating them by selector kernels supported on positive-mass neighborhoods inside each fiber; the only non-routine step is a measurable-selection or kernel-approximation lemma that preserves the target-fiber support conditions.  Outer containment is endpoint algebra because every selector integral over a fiber lies between the essential infimum and supremum of \(\mu\) on that fiber.  The estimator-specific impossibility follows by holding the published plug-in endpoint \(\Delta_{\mathrm{plug}}\) fixed as a functional of the learned-representation surface and comparing two admissible selectors concentrated near distinct values of \(\mu\) on a non-invariant fiber; the sign-reversal clause follows by choosing selectors on opposite sides of zero under Assumption~\ref{ass:local-crossing}.

\section{Honest scope flags}
The exact-recovery statement is only a sanity-check boundary, not a theorem-level novelty claim.  For \(B_0\) it requires atomic target support; continuous exact-representation recovery is tracked by the separate \(B^{\mathrm{eval}}_0\) functional and should not be conflated with positive-mass essential extrema.  Theorem~\ref{thm:finite-support-lp} is finite-support algebra; it is included to make the selector semantics and law-preservation equations auditable before the Borel case.  Conjecture~\ref{conj:sharp-envelope} is the flagship kernel and is not yet proved; the main technical uncertainty is whether the essential-envelope sharpness argument for arbitrary Borel supports needs a measurable-selection lemma or a restriction to regular conditional selector kernels.  Conjecture~\ref{conj:single-endpoint-impossibility} is also open and should be read as a nonparametric sensitivity boundary for the fitted representation-surface endpoint used in GenAI text-treatment workflows, not as a claim that exact-representation or causal-latent-separation papers are invalid.  Theorem~\ref{thm:fiber-singleton} is only envelope algebra; it becomes an identified-set singleton statement only if Conjecture~\ref{conj:sharp-envelope} is proved.  This v5 revision ties the no-single-endpoint obstruction to the published GenAI representation endpoint and separates atomic \(B_0\) exact recovery from continuous point evaluation.  This proposal deliberately does not re-propose the burned dynamic-IV compliance seed and does not rely on panel or structural-SCM infrastructure.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial pivot draft proposing sharp representation-distortion ATE envelopes and a sign-reversal impossibility boundary for approximate causal sufficiency; prior verdict: none.
\item v2 (revise) -- added target inverse-reachability, split the introduction into the required six subparagraphs, and sharpened the flagship novelty comparison away from generic corrupted-data bounds and toward representation-specific calibration geometry; prior verdict: REVISE.
\item v3 (revise) -- replaced pointwise regression extrema by essential extrema on positive-mass distortion fibers, added the \citet{ManskiTamer2002} interval-data comparator, demoted exact recovery to a sanity boundary, and reframed sign reversal as a fiber-invariance sensitivity frontier; prior verdict: REVISE.
\item v4 (revise) -- added selector-indexed intervention semantics, made finite-support law-preservation equations explicit, and replaced the strawman sign-reversal framing by a no-selector-free-endpoint conjecture under failure of \(\epsilon\)-fiber invariance; prior verdict: REVISE.
\item v5 (revise) -- tied the flagship obstruction to the GenAI learned-representation plug-in endpoint and patched the \(\epsilon=0\) sanity boundary by separating atomic \(B_0\) from continuous point-evaluation \(B^{\mathrm{eval}}_0\); prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Beresteanu, Molchanov, and Molinari(2011)]{BeresteanuMolchanovMolinari2011}
Beresteanu, A., Molchanov, I., and Molinari, F. (2011).
\newblock Sharp identification regions in models with convex moment predictions.
\newblock \emph{Econometrica}, 79(6):1785--1821.
\newblock \url{https://www.econometricsociety.org/publications/econometrica/2011/11/01/sharp-identification-regions-models-convex-moment-predictions}.

\bibitem[Beresteanu, Molchanov, and Molinari(2012)]{BeresteanuMolchanovMolinari2012}
Beresteanu, A., Molchanov, I., and Molinari, F. (2012).
\newblock Partial identification using random set theory.
\newblock \emph{Journal of Econometrics}, 166(1):17--32.
\newblock \url{https://www.sciencedirect.com/science/article/pii/S0304407611001163}.

\bibitem[Corcoll-Andreu et~al.(2026)]{CorcollAndreuVlontzosORiordanGilliganLee2026}
Corcoll-Andreu, V., Vlontzos, A., O'Riordan, L., Gilligan-Lee, C., and collaborators (2026).
\newblock Contrastive representations of structured treatments.
\newblock \emph{npj Artificial Intelligence}.
\newblock \url{https://www.nature.com/articles/s44387-026-00105-2}.

\bibitem[Egami et~al.(2022)]{EgamiFongGrimmerRobertsStewart2022}
Egami, N., Fong, C. J., Grimmer, J., Roberts, M. E., and Stewart, B. M. (2022).
\newblock How to make causal inferences using texts.
\newblock \emph{Science Advances}, 8(42):eabg2652.
\newblock \url{https://doi.org/10.1126/sciadv.abg2652}.

\bibitem[Fong and Grimmer(2023)]{FongGrimmer2023}
Fong, C. and Grimmer, J. (2023).
\newblock Causal inference with latent treatments.
\newblock \emph{American Journal of Political Science}, 67(2):374--389.
\newblock \url{https://doi.org/10.1111/ajps.12649}.

\bibitem[Horowitz and Manski(1995)]{HorowitzManski1995}
Horowitz, J. L. and Manski, C. F. (1995).
\newblock Identification and robustness with contaminated and corrupted data.
\newblock \emph{Econometrica}, 63(2):281--302.

\bibitem[Imai and Nakamura(2024)]{ImaiNakamura2024TextTreatments}
Imai, K. and Nakamura, K. (2024).
\newblock Causal representation learning with generative artificial intelligence: Application to texts as treatments.
\newblock arXiv:2410.00903.
\newblock \url{https://arxiv.org/abs/2410.00903}.

\bibitem[Imai and Nakamura(2025)]{ImaiNakamura2025GPI}
Imai, K. and Nakamura, K. (2025).
\newblock GenAI-powered inference.
\newblock arXiv:2507.03897.
\newblock \url{https://arxiv.org/abs/2507.03897}.

\bibitem[Nakamura and Imai(2026)]{ImaiNakamura2026Dynamic}
Nakamura, K. and Imai, K. (2026).
\newblock GenAI powered dynamic causal inference with unstructured data.
\newblock arXiv:2605.07834.
\newblock \url{https://arxiv.org/abs/2605.07834}.

\bibitem[Kaddour et~al.(2021)]{KaddourZhuLiuKusnerSilva2021}
Kaddour, J., Zhu, Y., Liu, Q., Kusner, M. J., and Silva, R. (2021).
\newblock Causal effect inference for structured treatments.
\newblock \emph{Advances in Neural Information Processing Systems}, 34:24841--24854.
\newblock \url{https://proceedings.neurips.cc/paper/2021/hash/d02e9bdc27a894e882fa0c9055c99722-Abstract.html}.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review Papers and Proceedings}, 80(2):319--323.

\bibitem[Manski(2003)]{Manski2003}
Manski, C. F. (2003).
\newblock \emph{Partial Identification of Probability Distributions}.
\newblock Springer.

\bibitem[Manski and Tamer(2002)]{ManskiTamer2002}
Manski, C. F. and Tamer, E. (2002).
\newblock Inference on regressions with interval data on a regressor or outcome.
\newblock \emph{Econometrica}, 70(2):519--546.
\newblock \url{https://www.econometricsociety.org/publications/econometrica/2002/03/01/inference-regressions-interval-data-regressor-or-outcome}.

\bibitem[Mozer et~al.(2020)]{MozerMiratrixKaufmanAnastasopoulos2020}
Mozer, R., Miratrix, L., Kaufman, A. R., and Anastasopoulos, L. J. (2020).
\newblock Matching with text data: An experimental evaluation of methods for matching documents and of measuring match quality.
\newblock \emph{Political Analysis}, 28(4):445--468.
\newblock \url{https://doi.org/10.1017/pan.2020.1}.

\bibitem[Ura(2018)]{Ura2018}
Ura, T. (2018).
\newblock Heterogeneous treatment effects with mismeasured endogenous treatment.
\newblock \emph{Quantitative Economics}, 9(3):1335--1370.
\newblock \url{https://qeconomics.org/ojs/forth/886/886-2.pdf}.

\bibitem[Veitch, Sridhar, and Blei(2020)]{VeitchSridharBlei2020}
Veitch, V., Sridhar, D., and Blei, D. M. (2020).
\newblock Adapting text embeddings for causal inference.
\newblock In \emph{Proceedings of the 36th Conference on Uncertainty in Artificial Intelligence}, PMLR 124:919--928.
\newblock \url{https://proceedings.mlr.press/v124/veitch20a.html}.
\end{thebibliography}

\end{document}
