% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_text\_treatment\_distortion, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_text\_treatment\_distortion} / \texttt{v1}%
  \\ \large\textit{Certified distortion audits for text/image treatment representation endpoints}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
  (\texttt{qid},\texttt{specialization},P,\Theta_\epsilon,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_text\_treatment\_distortion},\texttt{v1},
  P_{Z,Y},\ \Theta_{\epsilon}(r_1,r_0),\
  \mathcal R_{\epsilon,\mathrm{dist+suff}},\
  B_\epsilon(P;r_1,r_0)).
\end{gathered}
\]
Here \(Z\in\mathcal Z\subset\mathbb R^d\) is the learned observed representation of a randomized high-dimensional text/image treatment object, \(Y\in[0,1]\) is the outcome, \(P_{Z,Y}\) is the observable law, and \(\mu\) is the \(P_Z\)-a.s. equivalence class of observed-representation regressions \(\E_P[Y\mid Z=z]\).  The latent oracle representation is \(R^\star\in\mathcal Z\) and is known only to satisfy \(\|R^\star-Z\|_\infty\le\epsilon\) almost surely.  The target object is not a single unqualified number \(m(r_1)-m(r_0)\): an intervention fixing \(R^\star=r_j\) must also specify a stochastic learned-preimage selector \(\kappa_j\) on the feasible fiber \(B_\infty(r_j,\epsilon)\cap\operatorname{supp}(Z)\).  For selectors \(\kappa_1,\kappa_0\), the selector-indexed oracle contrast is \(\theta_{\kappa}(r_1,r_0)=\int\mu(z)\,d\kappa_1(z)-\int\mu(z)\,d\kappa_0(z)\), and \(\Theta_{\epsilon}(r_1,r_0)\) ranges this contrast over all admissible selectors.  The identifying restrictions \(\mathcal R_{\epsilon,\mathrm{dist+suff}}\) are randomized object assignment, consistency, bounded outcomes, selector-stable observed-response sufficiency, positive-mass local distortion fibers, target inverse-reachability of \(r_1,r_0\) through admissible stochastic selectors, and distortion-only calibration: any measurable oracle calibration inside the \(\epsilon\)-balls that preserves \(P_{Z,Y}\) and satisfies the selector equations is admissible.  The bounding functional is the essential distortion envelope
\[
B_\epsilon(P;r_1,r_0)=
\left[
  \operatorname*{ess\,inf}_{u\in B_\infty(r_1,\epsilon)\cap\operatorname{supp}(Z)}\mu(u)
  -
  \operatorname*{ess\,sup}_{v\in B_\infty(r_0,\epsilon)\cap\operatorname{supp}(Z)}\mu(v),\
  \operatorname*{ess\,sup}_{u\in B_\infty(r_1,\epsilon)\cap\operatorname{supp}(Z)}\mu(u)
  -
  \operatorname*{ess\,inf}_{v\in B_\infty(r_0,\epsilon)\cap\operatorname{supp}(Z)}\mu(v)
\right].
\]

\begin{abstract}
Many current designs for causal inference with text or images replace the object treatment by a learned representation and then report one regression endpoint.  This proposal asks what remains identified when that learned representation is only known to be within an \(\ell_\infty\) distortion budget \(\epsilon\) of an oracle causal representation.  The baseline sharp-set conjecture is that the selector-indexed ATE set is the essential ballwise observed-regression envelope \(B_\epsilon(P;r_1,r_0)\), once the intervention fixing an oracle representation is required to name the learned-preimage distribution it induces.  The flagship conjecture is representation-learning-specific: every selector-free scalar endpoint has worst-case error at least one half of the sharp distortion-frontier diameter, and the literal plug-in contrast is uniformly valid only under the observable \(\epsilon\)-fiber-invariance plus endpoint-calibration audit.  When the audit fails through positive fiber oscillation, the same observed law and the same fitted endpoint support a nondegenerate two-fiber open class of admissible oracle calibrations with separated, and under local crossing oppositely signed, selector-indexed ATEs.  The conjecture also proposes a finite-sample audit reporting rule: replace a GenAI plug-in sign claim by simultaneous confidence bands for the two distortion-envelope endpoints and report the plug-in endpoint only when the audit certificate collapses the band.  If resolved, the result would give text-as-treatment and image-as-treatment studies a finite sensitivity frontier, an exact robust sign-decision threshold, and a falsifiable representation audit rather than a silent plug-in endpoint.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
High-dimensional object treatments are now common in political science, social science, marketing, medicine, and vision applications: the treatment is a text, image, video, graph, or generated object rather than a scalar dose.  The methodological promise is that a learned representation can reduce the object to a tractable causal treatment coordinate.  The identification risk is that a representation can be nearly correct in a predictive or geometric sense while still moving the causal endpoint, because causal contrasts use values of an oracle representation that are not directly observed.

\paragraph{The main finding (proposed).}
The proposed main finding is Conjecture~\ref{conj:audit-impossibility}: on a compact class of target text/image representation contrasts, every selector-free scalar endpoint has a nonzero minimax error whenever the distortion frontier has positive diameter, and a literal learned-representation regression endpoint is uniformly valid only when the two-part observable audit passes.  The generic part is an envelope obstruction: if the target fiber has positive regression oscillation, the same observed law supports multiple admissible selector-indexed oracle ATEs, so no scalar endpoint can equal them all and the best possible endpoint still has error at least one half of the frontier diameter.  The representation-learning part strengthens this into an auditable failure class for GenAI plug-in workflows: two positive-mass distortion fibers with fixed fitted endpoint and positive local oscillation generate an open neighborhood of observationally equivalent oracle calibrations, so a sign decision based only on \(\mu^\dagger(r_1)-\mu^\dagger(r_0)\) is not uniformly valid.  The finite-sample part turns the obstruction into a reporting rule using simultaneous confidence bands for the envelope endpoints.  Conjecture~\ref{conj:sharp-envelope} supplies the underlying sharp frontier \(B_\epsilon(P;r_1,r_0)\), and Theorem~\ref{thm:finite-support-lp} gives the finite-support selector LP that exposes the law-preservation equations.

\paragraph{What is new.}
The novelty kernel is not that learned representations may be biased, and not another estimator for text treatments.  The closest text-causal papers either use observed text as a confounder proxy through causally sufficient embeddings \citep{VeitchSridharBlei2020}, propose GenAI internal representations as exact treatment features and report fitted representation-surface contrasts \citep{ImaiNakamura2024TextTreatments,ImaiNakamura2025GPI}, or warn that latent text treatments require extra assumptions \citep{FongGrimmer2023}.  The closest partial-identification papers provide interval-data, corrupted-data, random-set, and corrupted-treatment NPIV machinery \citep{HorowitzManski1995,ManskiTamer2002,BeresteanuMolchanovMolinari2012,ZhuGultchinGrettonKusnerSilva2022}, but they do not state a distortion audit for learned treatment representations.  The flagship epsilon-gap is workflow-specific: bounded representation distortion converts any positive target-fiber oscillation into a calculable lower bound on the worst-case error of the GenAI single-surface endpoint in \citet{ImaiNakamura2024TextTreatments}, while the literal GenAI regression endpoint is valid exactly when fiber invariance and endpoint calibration both hold.  Relative to generic partial-ID set inference \citep{ImbensManski2004,Stoye2009}, the proposed advance is the representation audit that tells the analyst which set to cover: the two endpoint extrema induced by certified \(\ell_\infty\) distortion fibers, not an abstract interval parameter.  The sharp envelope remains essential because it supplies the exact diameter and robust sign-decision threshold, but the central contribution is the certified endpoint-validity boundary, the two-positive-mass-fiber failure class, and the finite-sample reporting rule for learned text/image treatment endpoints rather than generic random-set algebra.

\paragraph{How it positions in the literature.}
This sits in the partial-identification and sensitivity-analysis cluster.  Manski-style bounded variation over latent quantities, random-set identification, and corrupted-data or measurement-error bounds supply the mathematical grammar; text and structured-treatment causal inference supply the active frontier where the issue matters.  The proposal deliberately avoids panel and structural-SCM axiomatics: the object is a sharp identified set for an ATE under representation distortion.

\paragraph{Implications for the community.}
The concrete community implication is for the texts-as-treatments and GenAI internal-representation workflow of \citet{ImaiNakamura2024TextTreatments}: when an analyst can only validate a learned representation up to a representation error radius, the reported endpoint should be replaced by \(B_\epsilon(P;r_1,r_0)\), by a minimax-error statement based on \(\operatorname{diam}(B_\epsilon)\), or by a simultaneous confidence-band audit showing that the robust sign decision and the fitted endpoint survive \(\epsilon\)-fiber invariance and endpoint calibration on the target contrast class.

\paragraph{How research benefits from the conclusion.}
If a reader takes only the conclusion away, their research practice changes from reporting one text- or image-representation regression contrast to reporting a distortion envelope, its half-diameter endpoint-error floor, and whether the observed regression is constant on the target distortion fibers.

\section{Related work}
\citet{VeitchSridharBlei2020} is a text-adjustment anchor: it develops causally sufficient embeddings for estimating causal effects from observational text used as covariate information, whereas this proposal concerns text or images as structured treatments and asks what sharp identified set remains when a treatment representation is only approximately recovered.  \citet{EgamiFongGrimmerRobertsStewart2022} show that text-based causal inferences depend on latent representations and that estimating those representations can create identification problems or overfitting; this proposal treats representation error as an observational-equivalence restriction rather than a sample-splitting problem.  \citet{FongGrimmer2023} show that randomized texts do not by themselves identify latent-treatment effects when unmeasured latent text features move together; the present proposal turns that qualitative insufficiency into a quantitative distortion frontier.

\citet{ImaiNakamura2024TextTreatments} propose using generative-model internal representations for causal inference with texts as treatments and motivate the oracle-representation language used here; Conjecture~\ref{conj:audit-impossibility} targets the resulting fitted representation-surface endpoint when the internal representation is only approximately recovered and separates two claims: a generic scalar endpoint cannot beat the selector frontier, and the literal fitted-surface contrast needs endpoint calibration in addition to frontier singletonness.  \citet{ImaiNakamura2025GPI} generalize GenAI-powered inference to unstructured data including text and images, making the learned-representation endpoint a current methodological object rather than a textbook example.  \citet{ImaiNakamura2026Dynamic} extend this agenda to dynamic unstructured treatments; the contrast here is that even the static one-object endpoint has a nontrivial partial-ID frontier and an auditability boundary when representation recovery is approximate.

\citet{KaddourZhuLiuKusnerSilva2021} develop structured-treatment CATE estimation using a generalized Robinson decomposition; their estimator assumes the structured treatment representation is the object entering the causal estimand, while this proposal asks when such a single representation endpoint is identified under oracle distortion.  \citet{CorcollAndreuVlontzosORiordanGilliganLee2026} show that contrastive representations for structured treatments can support unbiased causal estimation under causal-latent separation assumptions; the present proposal supplies the complementary audit: a distortion ball around the learned representation remains interval-valued unless the observed regression is fiber invariant, and a literal published plug-in endpoint additionally needs endpoint calibration to the fiber constants.  This is not a claim that those papers assert validity under bounded representation distortion alone; rather, their exact representation or separation assumptions are the named structural assumptions replaced here by a selector-indexed sensitivity frontier, a minimax error lower bound, and an observable certificate for when that frontier collapses.  \citet{MozerMiratrixKaufmanAnastasopoulos2020} study representation and distance choices for matching with text data, illustrating why geometric closeness of documents is an empirical design object; this proposal asks for the causal identified set and endpoint-validity audit induced by a formal closeness budget.

\citet{Manski1990} and \citet{Manski2003} are the bounded-outcome and partial-identification anchors: they justify ranging causal parameters over all latent completions compatible with data and restrictions.  \citet{ManskiTamer2002} is the closest interval-data comparator because it studies regressions when a regressor or outcome is only known to lie in an interval; the present proposal differs by treating the interval as a high-dimensional representation fiber for a causal intervention target and by asking for the sharp ATE set, not a semiparametric regression parameter set.  \citet{HorowitzManski1995} give the classic corrupted-data robustness analysis; the present proposal is not another contamination-rate interval, because the admissible ambiguity is geometric inverse-calibration of target representation values through \(\ell_\infty\) fibers.  \citet{BeresteanuMolchanovMolinari2012} provide the random-set language for latent feasible sets; here the random set is the \(\epsilon\)-ball of learned representations that can serve as observed preimages of an oracle target.  \citet{BeresteanuMolchanovMolinari2011} show how sharp identification regions can be represented through Aumann expectations of random sets, which is the closest general econometric comparator to the ballwise envelope.  \citet{Ura2018} gives sharp finite bounds for treatment effects with mismeasured binary endogenous treatment; this proposal differs because high-dimensional representation distortion produces target-fiber regression extrema and a fiber-invariance singleton condition rather than a scalar treatment-error bound.  \citet{ZhuGultchinGrettonKusnerSilva2022} propose MEKIV, a kernel nonparametric IV estimator for causal effects when a continuous treatment measurement is corrupted by error and confounding may remain; it is a close measurement-error comparator, but it targets recovery of a structural response using instruments, not a sharp selector-indexed partial-ID frontier for oracle text/image representation targets under a certified sup-norm distortion budget.
\citet{ImbensManski2004} and \citet{Stoye2009} are the closest finite-sample inference comparators for partially identified parameters; the proposed audit uses their confidence-set logic, but the novel object is the representation-distortion endpoint band whose lower and upper endpoints are the two fiber-extrema functionals generated by a learned text/image representation certificate.

The in-catalogue ThmSmith prior art does not already contain this kernel.  \texttt{doc/API.md} Section 3 records ExactID/PartialID as seed catalogues for Manski-family bounds, IV bounds, sensitivity analysis, shape restrictions, and missing-data bounds, but it has no representation-distortion theorem.  The closest banked proposal is \texttt{pid\_network\_exposure} (``Sharp ADE bounds from shared local-network completions under misspecified exposure maps''), which is also a partial-ID problem over hidden completions, but its kernel is graph-completion compatibility rather than learned-representation distortion.  The banked \texttt{pid\_dose\_response\_shape} proposal studies shape-restricted dose-response sensitivity, and \texttt{pid\_long\_term\_surrogate} studies surrogate drift; neither contains the \(\epsilon\)-fiber-invariance boundary for text or image treatment representations.

\section{Formal setup}
Let \(T\) be a randomized high-dimensional treatment object, such as a text or image, and let \(Z=\phi(T)\in\mathcal Z\subset\mathbb R^d\) be the learned representation observed by the analyst.  Let \(R^\star=\rho(T)\in\mathcal Z\) be the latent oracle representation, but suppose \(\rho\) is not observed.  The observable law is \(P=P_{Z,Y}\), the observed regression \(\mu\) is the \(P_Z\)-a.s. equivalence class of conditional means \(\E_P[Y\mid Z=z]\), and outcomes are bounded in \([0,1]\).  The published single-representation endpoint targeted by this proposal is the plug-in contrast
\[
\Delta_{\mathrm{plug}}(P;r_1,r_0)=\mu^\dagger(r_1)-\mu^\dagger(r_0),
\]
where \(\mu^\dagger\) is a chosen fitted or identified version of the outcome surface on the learned-representation coordinate, as in workflows that treat the learned internal representation as the causal treatment feature.  For target oracle representation values \(r_1,r_0\in\mathcal Z\), an intervention fixing \(R^\star=r_j\) is incomplete until it specifies the distribution of learned preimages \(Z\) among objects compatible with that oracle value.  Let \(\mathcal K_\epsilon(r)\) be the class of probability selectors \(\kappa_r\) supported on the distortion fiber \(\mathcal F_\epsilon(r)\) and absolutely continuous with respect to \(P_Z\) restricted to that fiber, together with limits of such selectors along positive-mass sets used to attain essential extrema; in the finite-support specialization, \(\mathcal K_\epsilon(r)\) is the simplex over atoms in the fiber.  The selector-indexed parameter is
\[
\theta_{\kappa}(r_1,r_0)
=
\int_{\mathcal F_\epsilon(r_1)}\mu(z)\,d\kappa_1(z)
-
\int_{\mathcal F_\epsilon(r_0)}\mu(z)\,d\kappa_0(z),
\]
and the unidentified object \(\Theta_\epsilon(P;r_1,r_0)\) is the closed set of all such values over admissible selector pairs \(\kappa=(\kappa_1,\kappa_0)\in\mathcal K_\epsilon(r_1)\times\mathcal K_\epsilon(r_0)\).  If a substantive intervention supplies a particular kernel \(\kappa\), the target is \(\theta_\kappa\); if it only says ``set the oracle representation to \(r_j\),'' the identified object is the selector frontier \(\Theta_\epsilon\).

For \(\epsilon\ge0\), define the closed distortion fiber
\[
\mathcal F_\epsilon(r)=B_\infty(r,\epsilon)\cap\operatorname{supp}(Z)
=\{z\in\operatorname{supp}(Z):\|z-r\|_\infty\le\epsilon\}.
\]
Whenever \(P_Z(\mathcal F_\epsilon(r))>0\), write
\[
\underline\mu_\epsilon(r)=\operatorname*{ess\,inf}_{z\in\mathcal F_\epsilon(r)}\mu(z),
\qquad
\overline\mu_\epsilon(r)=\operatorname*{ess\,sup}_{z\in\mathcal F_\epsilon(r)}\mu(z),
\]
with essential extrema taken under the conditional \(P_Z\)-law restricted to \(\mathcal F_\epsilon(r)\).  These are observable-law functionals of the regression equivalence class, unlike pointwise values of a chosen conditional-mean version on non-atomic support points.  The proposal may be read first under finite \(Z\)-support, where the essential extrema are ordinary minimum and maximum over atoms; the Borel-support statement uses the essential-extrema notation throughout.
The fiber oscillation is \(\operatorname{osc}_\epsilon(r)=\overline\mu_\epsilon(r)-\underline\mu_\epsilon(r)\), and the diameter of a closed interval \(I=[a,b]\) is \(\operatorname{diam}(I)=b-a\).
The identified set \(\Theta_\epsilon(P;r_1,r_0)\) is the set of all values of \(\theta_\kappa(r_1,r_0)\) generated by full-data laws for \((T,Z,R^\star,Y(\cdot))\) whose \((Z,Y)\) marginal is \(P\), whose oracle representation is within \(\epsilon\) of the learned representation almost surely, and whose intervention kernels satisfy the selector equations above.  The proposed bounding functional is \(B_\epsilon(P;r_1,r_0)\), as locked above.  Endpoint calibration for the learned-representation plug-in endpoint is separate from singletonness of the envelope: when a fiber is invariant with constant \(c_j\), the endpoint is calibrated on that fiber only if \(\mu^\dagger(r_j)=c_j\).  Thus \(B_\epsilon(P;r_1,r_0)\) may be a singleton without \(\Delta_{\mathrm{plug}}\) equaling that singleton if the fitted representation surface is evaluated at an off-fiber or misspecified endpoint value.
More generally, a selector-free scalar endpoint rule is a map
\[
E^\dagger(P,\mu^\dagger;r_1,r_0)
\]
whose value is determined by the observable law \(P_{Z,Y}\), the fitted learned-representation surface \(\mu^\dagger\), and the two oracle target coordinates, but not by a learned-preimage selector \(\kappa\) or by a particular oracle calibration \(c\).  The plug-in contrast \(\Delta_{\mathrm{plug}}\) is the leading example, but the definition also covers any deterministic smoothing, interpolation, or post-processing of a single learned representation surface before evaluating the target coordinates.  The observable audit certificate for a target value \(r\) passes when \(\operatorname{osc}_\epsilon(r)=0\) and, writing \(c_r\) for the common value of \(\mu\) on \(\mathcal F_\epsilon(r)\), the endpoint surface is calibrated, \(\mu^\dagger(r)=c_r\).  For a target-pair class \(\mathcal T\), the audit passes on \(\mathcal T\) when it passes for every coordinate appearing in a pair in \(\mathcal T\) and \(E^\dagger(P,\mu^\dagger;r_1,r_0)=c_{r_1}-c_{r_0}\) for every \((r_1,r_0)\in\mathcal T\).
The generic selector-free validity audit for such a scalar rule is envelope calibration:
\[
E^\dagger(P,\mu^\dagger;r_1,r_0)\in\Theta_\epsilon(P;r_1,r_0)
\quad\text{and}\quad
\Theta_\epsilon(P;r_1,r_0)\text{ is a singleton}.
\]
For a literal learned-representation regression endpoint, the rule is specifically
\[
\Delta_{\mathrm{plug}}(P;r_1,r_0)=\mu^\dagger(r_1)-\mu^\dagger(r_0),
\]
so envelope calibration decomposes into two observable clauses: \(\epsilon\)-fiber invariance and endpoint calibration of \(\mu^\dagger\) to the fiber constants.  Thus endpoint calibration is not asserted to be necessary for an arbitrary selector-free rule that post-processes \(P\) into the singleton value; it is necessary for the literal regression-endpoint workflow that evaluates one fitted learned-representation surface at the oracle target coordinates.  For any scalar rule \(E^\dagger\), define the selector worst-case error on a target pair by
\[
\mathcal E_\epsilon(E^\dagger;r_1,r_0)
=
\sup_{\theta\in\Theta_\epsilon(P;r_1,r_0)}
\left|E^\dagger(P,\mu^\dagger;r_1,r_0)-\theta\right|.
\]
For finite-sample audit statements, let \((Z_i,Y_i)_{i=1}^n\) be the observed sample, and let
\[
\widehat B_{\epsilon,\alpha}(r_1,r_0)
=
[\widehat L_{\epsilon,\alpha}(r_1,r_0),\widehat U_{\epsilon,\alpha}(r_1,r_0)]
\]
be a data-dependent simultaneous \((1-\alpha)\)-confidence band for the lower and upper endpoints of \(B_\epsilon(P;r_1,r_0)\) over a compact target-pair class \(\mathcal T\).  The finite-sample robust-sign audit reports positive only when \(\widehat L_{\epsilon,\alpha}(r_1,r_0)>0\), negative only when \(\widehat U_{\epsilon,\alpha}(r_1,r_0)<0\), point endpoint valid only when the band diameter is zero up to the announced tolerance and the endpoint-calibration audit passes, and otherwise reports sign unresolved.  This proposal does not require a particular estimator of \(\mu\); the statistical input is the existence of simultaneous valid bands for the two observable fiber-extrema functionals.
At the exact-recovery boundary, the essential-envelope functional \(B_0\) is defined only when the singleton target fibers have positive \(P_Z\)-mass.  For continuous support with a pre-specified identified version \(\mu^\dagger\), the separate point-evaluation functional is
\[
B^{\mathrm{eval}}_0(P;r_1,r_0)=\{\mu^\dagger(r_1)-\mu^\dagger(r_0)\},
\]
which records exact-representation recovery of the plug-in endpoint but is not the positive-mass essential-envelope \(B_0\).
An admissible calibration is a pair \((c,\kappa)\), where \(c:\operatorname{supp}(Z)\to\mathcal Z\) is a measurable possible oracle map \(R^\star=c(Z)\) satisfying \(\|c(z)-z\|_\infty\le\epsilon\), and \(\kappa=(\kappa_1,\kappa_0)\) are target-intervention kernels supported on the corresponding target fibers.  A target value \(r\) is inverse-reachable if at least one admissible selector \(\kappa_r\) assigns positive probability only to learned preimages in \(\mathcal F_\epsilon(r)\); under the distortion restriction every such preimage must lie in \(\mathcal F_\epsilon(r)\).  The estimand in this proposal is restricted to target values \(r_1,r_0\) that are inverse-reachable under the admissible selectors used to generate \(\Theta_\epsilon(P;r_1,r_0)\).  For a compact class of target pairs \(\mathcal T\subseteq\mathcal Z^2\) with positive-mass target fibers, the uniform sensitivity frontier is the set-valued map \((r_1,r_0)\mapsto B_\epsilon(P;r_1,r_0)\) over \(\mathcal T\).
An open neighborhood of observable laws means a weak neighborhood of the \(Z\)-marginal together with a uniform neighborhood of the regression function \(\mu\) on the compact target fibers.  An overlapping-support neighborhood of a target value \(r\) means a set of target values \(r'\) whose fibers \(\mathcal F_\epsilon(r')\) intersect a common nonempty relative-open subset of \(\operatorname{supp}(Z)\).

\begin{verbatim}
(qid, specialization, P, Theta_epsilon, identifying restrictions, bounding functional)
=
(pid_text_treatment_distortion, v1,
  P_{Z,Y}, Theta_epsilon(r_1,r_0),
  R_{epsilon,dist+suff},
  B_epsilon(P;r_1,r_0)).
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Randomized object assignment and consistency]\label{ass:randomized-consistency}
The treatment object \(T\) is assigned independently of potential outcomes, and the observed outcome satisfies consistency for the realized object and representation pair.  The target values \(r_1,r_0\) and any substantive selector kernels \(\kappa_1,\kappa_0\) are fixed before seeing outcomes.
\end{assumption}

\begin{assumption}[Bounded outcome and regular observed regression]\label{ass:bounded-regular}
The outcome satisfies \(Y\in[0,1]\).  The observed regression \(\mu\) exists as a \(P_Z\)-a.s. equivalence class, is represented by a bounded measurable version when notation requires a function, and has finite essential infimum and essential supremum on each positive-mass target fiber \(\mathcal F_\epsilon(r_j)\), \(j\in\{0,1\}\).  If \(\epsilon=0\) and a pointwise value at a non-atomic target is used, it is denoted \(\mu^\dagger(r_j)\) and belongs to the separate point-evaluation functional \(B^{\mathrm{eval}}_0\), not to the positive-mass essential-envelope functional \(B_0\).
\end{assumption}

\begin{assumption}[Selector-stable observed-response sufficiency]\label{ass:selector-sufficiency}
For any target value \(r\) and learned-preimage selector \(\kappa_r\) supported on \(\mathcal F_\epsilon(r)\), the mean outcome under the intervention that fixes \(R^\star=r\) and samples the learned preimage from \(\kappa_r\) is \(\int\mu(z)\,d\kappa_r(z)\).  Thus the intervention target explicitly includes the residual distribution over learned object types inside the oracle fiber; without this selector, the phrase ``fix \(R^\star=r\)'' is not a well-defined mean outcome when multiple learned preimages are compatible with \(r\).
\end{assumption}

\begin{assumption}[Sup-norm representation distortion]\label{ass:distortion}
The latent oracle representation and observed learned representation satisfy
\[
\|R^\star-Z\|_\infty\le\epsilon
\]
almost surely, for a known distortion budget \(\epsilon\ge0\).
\end{assumption}

\begin{assumption}[Distortion-only calibration sharpness]\label{ass:distortion-sharpness}
Subject to Assumption~\ref{ass:target-reachability} for the two target values, every measurable oracle calibration \(c:\operatorname{supp}(Z)\to\mathcal Z\) with \(\|c(z)-z\|_\infty\le\epsilon\) and every pair of selector kernels \(\kappa_j\) supported on \(\mathcal F_\epsilon(r_j)\) are admissible, provided the induced \((Z,Y)\) law is \(P\) and the selector-indexed means are computed as in Assumption~\ref{ass:selector-sufficiency}.  No smoothness, Lipschitz, monotonicity, model-training, semantic-alignment, or parametric restriction links two points inside the same distortion fiber unless explicitly stated.
\end{assumption}

\begin{assumption}[Positive-mass target fibers]\label{ass:nonempty-fibers}
For the target values \(r_1,r_0\), the sets \(\mathcal F_\epsilon(r_1)\) and \(\mathcal F_\epsilon(r_0)\) have strictly positive \(P_Z\)-probability.  At the exact-recovery boundary \(\epsilon=0\), this means the target points are positive-mass atoms for statements about \(B_0\); continuous point-evaluation exact recovery is handled only by \(B^{\mathrm{eval}}_0\).
\end{assumption}

\begin{assumption}[Target inverse-reachability]\label{ass:target-reachability}
Every admissible full-data law contributing to \(\Theta_\epsilon(P;r_1,r_0)\) includes selector kernels \(\kappa_j\in\mathcal K_\epsilon(r_j)\), \(j\in\{0,1\}\), whose supports are contained in \(\mathcal F_\epsilon(r_j)\) and whose supports have positive \(P_Z\)-mass in every neighborhood used for essential-extrema approximation.  Conversely, for sharpness, every probability kernel absolutely continuous with respect to \(P_Z\) restricted to \(\mathcal F_\epsilon(r_j)\), every limit of such kernels along positive-mass sets approaching an essential extremum, and every finite-support probability vector on atoms in that fiber, is permitted as a target preimage selector, subject only to the other stated assumptions and preservation of \(P_{Z,Y}\).
\end{assumption}

\begin{assumption}[Finite-support specialization]\label{ass:finite-support}
For finite-support results, \(\operatorname{supp}(Z)\) is a finite set and \(P_Z(z)>0\) for every \(z\in\operatorname{supp}(Z)\).  Selector kernels are then probability vectors over the atoms in the relevant target fiber.
\end{assumption}

\begin{assumption}[\(\epsilon\)-fiber invariance]\label{ass:fiber-invariance}
The observed regression is \(\epsilon\)-fiber invariant on the target pair if \(\mu\) is \(P_Z\)-a.s. constant on \(\mathcal F_\epsilon(r_1)\) and \(P_Z\)-a.s. constant on \(\mathcal F_\epsilon(r_0)\).  The two constants may differ across the two target fibers.
\end{assumption}

\begin{assumption}[Endpoint calibration]\label{ass:endpoint-calibration}
When Assumption~\ref{ass:fiber-invariance} holds with constants \(c_1\) and \(c_0\) on \(\mathcal F_\epsilon(r_1)\) and \(\mathcal F_\epsilon(r_0)\), respectively, the fitted or identified learned-representation surface used in \(\Delta_{\mathrm{plug}}\) is endpoint-calibrated if \(\mu^\dagger(r_1)=c_1\) and \(\mu^\dagger(r_0)=c_0\).  This assumption is not implied by singletonness of \(B_\epsilon(P;r_1,r_0)\); it is the extra condition that connects the singleton selector frontier to the particular published plug-in endpoint.
\end{assumption}

\begin{assumption}[Local crossing for sign reversal]\label{ass:local-crossing}
The target pair has a local crossing at budget \(\epsilon\) if
\[
\underline\mu_\epsilon(r_1)
<
\overline\mu_\epsilon(r_0)
\quad\text{and}\quad
\overline\mu_\epsilon(r_1)
>
\underline\mu_\epsilon(r_0).
\]
\end{assumption}

\begin{assumption}[Nondegenerate two-fiber audit class]\label{ass:two-fiber-open}
There exist target values \(r_1,r_0\), positive-mass relative-open subsets \(A_j^-,A_j^+\subseteq\mathcal F_\epsilon(r_j)\), and constants \(0<\eta<\delta<1\) such that \(P_Z(A_j^-)>0\), \(P_Z(A_j^+)>0\), \(\mu\le c_j-\delta\) on \(A_j^-\), \(\mu\ge c_j+\delta\) on \(A_j^+\), and the fitted endpoint surface satisfies \(|\mu^\dagger(r_j)-c_j|\le\eta\), for \(j\in\{0,1\}\).  The sets remain inside their target distortion fibers under small weak perturbations of \(P_Z\) and small uniform perturbations of \(\mu\) on the four sets.  This is the nondegenerate open-class witness used for the GenAI plug-in endpoint obstruction; it excludes zero-mass, collapsed-arm, or hand-tuned single-point examples.
\end{assumption}

\begin{assumption}[Simultaneous finite-sample envelope bands]\label{ass:simul-bands}
For the sample \((Z_i,Y_i)_{i=1}^n\), the reported functions \(\widehat L_{\epsilon,\alpha}\) and \(\widehat U_{\epsilon,\alpha}\) satisfy
\[
\Pr\!\left(
  \widehat L_{\epsilon,\alpha}(r_1,r_0)
  \le
  \inf B_\epsilon(P;r_1,r_0)
  \le
  \sup B_\epsilon(P;r_1,r_0)
  \le
  \widehat U_{\epsilon,\alpha}(r_1,r_0)
  \ \text{for every }(r_1,r_0)\in\mathcal T
\right)\ge 1-\alpha .
\]
The event is simultaneous over the compact target-pair audit class \(\mathcal T\).
\end{assumption}

\begin{assumption}[Sharp frontier on the audit class]\label{ass:sharp-frontier}
For every target pair in the audit class \(\mathcal T\), the selector-indexed identified set equals the distortion envelope, \(\Theta_\epsilon(P;r_1,r_0)=B_\epsilon(P;r_1,r_0)\).  This assumption is already delivered by Theorem~\ref{thm:finite-support-lp} in the finite-support specialization and is the Borel sharpness claim of Conjecture~\ref{conj:sharp-envelope} otherwise.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite-support selector LP]\label{thm:finite-support-lp}
Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability} and Assumption~\ref{ass:finite-support}, let \(S_j=\{z:\|z-r_j\|_\infty\le\epsilon,\ P_Z(z)>0\}\).  The finite-support selector identified set is
\[
\left\{
\sum_{z\in S_1}w_{1z}\mu(z)-\sum_{z\in S_0}w_{0z}\mu(z):
w_{jz}\ge0,\ \sum_{z\in S_j}w_{jz}=1,\ j\in\{0,1\}
\right\}
=
B_\epsilon(P;r_1,r_0),
\]
where the right-hand side uses ordinary minima and maxima over \(S_1,S_0\).  The law-preservation equations are only the observed restrictions \(\Pr(Z=z,Y\in A)=P_{Z,Y}(z,A)\); the selector weights \(w_{jz}\) index counterfactual intervention kernels for the target oracle values and therefore do not alter the observed marginal.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{ManskiTamer2002} on interval regressors/outcomes, \citet{BeresteanuMolchanovMolinari2011,BeresteanuMolchanovMolinari2012} on random-set sharp regions, and \citet{Ura2018} on treatment measurement error.  The epsilon-gap is the explicit selector LP for high-dimensional learned-representation treatment interventions: the latent ambiguity is not an interval covariate or a contaminated subpopulation, but the distribution of learned preimages that an intervention fixing \(R^\star=r_j\) must carry inside an \(\ell_\infty\) distortion fiber.  This finite-support theorem is included to rule out the ambiguous ``preimage average'' reading: it states the exact variables and law-preservation constraints a reviewer can audit.  (b) The concrete consumer is \citet{ImaiNakamura2024TextTreatments}: finite empirical support is the natural first audit of whether a GenAI representation endpoint survives bounded representation error or must be reported as a selector frontier.

\begin{conjecture}[Conjecture 1: Borel sharp distortion envelope for selector-indexed oracle ATEs]\label{conj:sharp-envelope}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability}, for every \(\epsilon\ge0\),
\[
\Theta_\epsilon(P;r_1,r_0)=B_\epsilon(P;r_1,r_0).
\]
Equivalently, every value between the essential ballwise lower and upper endpoints can be generated by admissible target-intervention selectors without changing the observed law \(P_{Z,Y}\), and no value outside those endpoints is compatible with the distortion restriction and selector-stable response restriction.  Uniformly over any compact target-pair class \(\mathcal T\) satisfying Assumptions~\ref{ass:nonempty-fibers}--\ref{ass:target-reachability}, the same formula defines the representation-distortion sensitivity frontier \((r_1,r_0)\mapsto B_\epsilon(P;r_1,r_0)\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet{ManskiTamer2002} on interval regressors/outcomes, \citet{HorowitzManski1995} on corrupted data, \citet{BeresteanuMolchanovMolinari2012} on random-set partial identification, \citet{Ura2018} on sharp bounds with treatment measurement error, and \citet{FongGrimmer2023} on insufficiency of randomized text for latent-treatment effects.  The flagship epsilon-gap is geometric and representation-specific: none of these papers characterizes the sharp selector-indexed ATE set for inverse-reachable high-dimensional oracle target values when the only misspecification is a sup-norm distortion budget around a learned representation, yielding essential-extrema endpoints of the observed-representation regression over target-intervention fibers and a uniform sensitivity frontier over a class of text/image treatment contrasts.  The proposed Borel statement is not just a relabelled random-set envelope because the selector intervention semantics make explicit which residual preimage distribution is part of the causal target, and the finite-support theorem above is the algebraic specialization it must extend.  (b) Resolving the conjecture would give users of the texts-as-treatments workflow in \citet{ImaiNakamura2024TextTreatments} a named sensitivity target: replace a single GenAI-representation endpoint by \(B_\epsilon(P;r_1,r_0)\) whenever exact representation recovery is not defensible.

\begin{conjecture}[Conjecture 2: certified audit obstruction for GenAI representation endpoints]\label{conj:audit-impossibility}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability} and Assumption~\ref{ass:sharp-frontier}, suppose \(\epsilon>0\), let \(\mathcal T\subseteq\mathcal Z^2\) be a compact target-pair class satisfying Assumption~\ref{ass:nonempty-fibers} for every target pair, and let \(E^\dagger(P,\mu^\dagger;r_1,r_0)\) be any selector-free scalar endpoint rule as defined in the formal setup.  For every \((r_1,r_0)\in\mathcal T\),
\[
\mathcal E_\epsilon(E^\dagger;r_1,r_0)
\ge
\frac{1}{2}\operatorname{diam}\!\left(B_\epsilon(P;r_1,r_0)\right),
\]
with equality attainable only by a midpoint rule when the sharp frontier is exactly \(B_\epsilon(P;r_1,r_0)\).  Consequently, a selector-free scalar endpoint can be uniformly valid for every admissible selector on \(\mathcal T\) only when \(B_\epsilon(P;r_1,r_0)\) is a singleton for every target pair and the reported scalar equals that singleton.

For the literal GenAI plug-in endpoint \(\Delta_{\mathrm{plug}}(P;r_1,r_0)=\mu^\dagger(r_1)-\mu^\dagger(r_0)\), Assumption~\ref{ass:two-fiber-open} generates a nondegenerate open failure class: there is an open neighborhood of observable laws, in the setup topology defined above, on which two admissible oracle calibrations and selector kernels preserve the same \(P_{Z,Y}\), the same certified distortion budget, the same fitted learned-representation surface \(\mu^\dagger\), and therefore the same published plug-in endpoint value, while generating selector-indexed oracle contrasts separated by at least \(2(\delta-\eta)\) and by the diameter of \(B_\epsilon(P;r_1,r_0)\) up to arbitrarily small essential-extrema approximation error.  Under Assumption~\ref{ass:local-crossing}, the two contrasts can be chosen with opposite signs, so no sign decision based only on \(\Delta_{\mathrm{plug}}\) is uniformly valid on that open class.

If Assumption~\ref{ass:simul-bands} also holds, the finite-sample robust-sign audit based on \(\widehat B_{\epsilon,\alpha}\) has simultaneous coverage \(1-\alpha\) for the selector-indexed oracle ATE frontier over \(\mathcal T\): with probability at least \(1-\alpha\), every positive or negative sign report made by the audit is correct for all admissible selectors, and every point-endpoint report is correct only when the finite-sample band collapse and endpoint-calibration certificate hold.  Thus the workflow-specific failure of the \citet{ImaiNakamura2024TextTreatments} endpoint is not merely interval midpoint algebra: it yields a certified reporting replacement for learned text/image treatment studies.  For the literal plug-in endpoint, uniform validity on \(\mathcal T\) is equivalent to the observable two-part audit: \(\epsilon\)-fiber invariance on every target fiber and endpoint calibration of \(\mu^\dagger\) to the corresponding fiber constants.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) This is not a strawman claim that \citet{ImaiNakamura2024TextTreatments} or \citet{CorcollAndreuVlontzosORiordanGilliganLee2026} assert validity under bounded distortion alone; those papers impose true internal representations or causal-latent separation conditions.  The flagship epsilon-gap is the complementary nonparametric audit theorem for the learned-representation endpoint workflow itself: positive \(\epsilon\)-fiber oscillation gives a quantitative lower bound on the worst-case error of the GenAI fitted-surface endpoint and of any other selector-free scalar rule, while endpoint calibration is required only for the literal fitted-surface contrast after the selector frontier collapses.  Relative to \citet{ManskiTamer2002} and \citet{BeresteanuMolchanovMolinari2012}, the conjecture adds the two-positive-mass-fiber representation failure class and a finite-sample robust-sign audit for the fiber-extrema endpoints.  Relative to \citet{ImbensManski2004} and \citet{Stoye2009}, it does not merely request a confidence interval for an already specified partially identified parameter; it identifies the learned-representation distortion parameter and the endpoint-calibration certificate that decide whether a GenAI plug-in endpoint may be interpreted at all.  \citet{ZhuGultchinGrettonKusnerSilva2022} address corrupted continuous treatment measurements through an NPIV estimator, but their target is estimator recovery under instrumental restrictions rather than a selector-free endpoint impossibility under observationally equivalent oracle-representation calibrations.  \citet{EgamiFongGrimmerRobertsStewart2022} and \citet{FongGrimmer2023} warn that learned or latent text representations may create identification problems, but they do not give a nondegenerate open-class sign-reversal frontier, a regression-endpoint calibration audit, or a confidence-band reporting rule for inverse-reachable oracle targets.  (b) The concrete consumer is the GenAI representation-as-treatment program of \citet{ImaiNakamura2024TextTreatments}: the conjecture says the analyst must either report the distortion envelope and its half-diameter endpoint-error floor with simultaneous endpoint bands, or publish the fiber-invariance and endpoint-calibration audit before interpreting a fitted representation-surface contrast as an ATE.

\begin{theorem}[Theorem 2: singleton envelope versus plug-in endpoint calibration]\label{thm:fiber-singleton}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, \(B_\epsilon(P;r_1,r_0)\) is a singleton if Assumption~\ref{ass:fiber-invariance} holds on the target pair.  Conversely, if \(B_\epsilon(P;r_1,r_0)\) is a singleton for every choice of the other target point in an overlapping-support neighborhood, then \(\mu\) is \(\epsilon\)-fiber invariant on the corresponding target fiber.  Moreover, when \(B_\epsilon(P;r_1,r_0)=\{c_1-c_0\}\), the published plug-in endpoint \(\Delta_{\mathrm{plug}}(P;r_1,r_0)\) equals that singleton if and only if Assumption~\ref{ass:endpoint-calibration} holds for the two fiber constants \(c_1,c_0\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is routine interval algebra for the proposed bounding functional, but it names the two structural assumptions hidden behind any single learned-representation endpoint.  It is closest to the structured-treatment representation assumptions in \citet{ImaiNakamura2024TextTreatments} and \citet{CorcollAndreuVlontzosORiordanGilliganLee2026}; neither separates \(\epsilon\)-fiber invariance from endpoint calibration under bounded representation distortion.  (b) The consumer is the GenAI-powered inference program of \citet{ImaiNakamura2025GPI}: the theorem gives a diagnostic for when a low-dimensional representation endpoint can be reported without an additional distortion interval and when a singleton envelope still does not justify the fitted endpoint value.

\section{Sanity-check corollaries}
\begin{corollary}[Exact-recovery reduction]\label{cor:exact}
Under Assumptions~\ref{ass:randomized-consistency}--\ref{ass:target-reachability}, if \(\epsilon=0\) and \(P_Z(\{r_1\})>0\), \(P_Z(\{r_0\})>0\), then \(B_0(P;r_1,r_0)=\{\mu(r_1)-\mu(r_0)\}\), matching the exact-representation plug-in endpoint on atoms.  If instead \(r_1,r_0\) are non-atomic points with a pre-specified identified continuous version \(\mu^\dagger\), the exact-recovery target is the separate point-evaluation functional \(B^{\mathrm{eval}}_0(P;r_1,r_0)=\{\mu^\dagger(r_1)-\mu^\dagger(r_0)\}\), not the essential-envelope \(B_0\).
\end{corollary}
The reduction is concrete: under Assumption~\ref{ass:distortion}, zero distortion forces \(R^\star=Z\), so each positive-mass target fiber is an atom; Assumption~\ref{ass:bounded-regular} then makes the essential lower and upper endpoint values equal the identified atom value \(\mu(r_j)\).  The continuous-version branch is checked separately by the displayed definition of \(B^{\mathrm{eval}}_0\), avoiding pointwise evaluation inside an essential-extrema functional.

\begin{corollary}[Flat-regression reduction]\label{cor:flat}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, if \(\mu(z)=c\) \(P_Z\)-a.s. on \(\mathcal F_\epsilon(r_1)\cup\mathcal F_\epsilon(r_0)\), then \(B_\epsilon(P;r_1,r_0)=\{0\}\).
\end{corollary}
The reduction is concrete: under Assumption~\ref{ass:fiber-invariance} with equal constants on both target fibers, all four endpoint extrema equal \(c\), so the lower and upper ATE bounds are both zero.

\begin{corollary}[Separated-fiber sign decision]\label{cor:separated}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, if
\[
\underline\mu_\epsilon(r_1)>
\overline\mu_\epsilon(r_0),
\]
then every value in \(B_\epsilon(P;r_1,r_0)\) is positive.
\end{corollary}
The reduction is concrete: the lower endpoint of the envelope is positive by the displayed strict separation, so even the most adverse admissible oracle calibration preserves the sign.

\begin{corollary}[Exact envelope diameter and robust sign threshold]\label{cor:diameter-sign}
Under Assumptions~\ref{ass:bounded-regular} and \ref{ass:nonempty-fibers}, the proposed envelope has
\[
\operatorname{diam}(B_\epsilon(P;r_1,r_0))
=
\operatorname{osc}_\epsilon(r_1)+\operatorname{osc}_\epsilon(r_0).
\]
Under Conjecture~\ref{conj:sharp-envelope}, the selector-indexed oracle ATE is uniformly positive if and only if \(\underline\mu_\epsilon(r_1)>\overline\mu_\epsilon(r_0)\), uniformly negative if and only if \(\overline\mu_\epsilon(r_1)<\underline\mu_\epsilon(r_0)\), and sign-ambiguous if \(0\in B_\epsilon(P;r_1,r_0)\).
\end{corollary}
The reduction is concrete: subtracting the displayed lower endpoint of \(B_\epsilon\) from the displayed upper endpoint cancels the cross terms and leaves exactly the two fiber oscillations.  The sign thresholds are the three possible locations of zero relative to a closed interval, so the corollary is only using Conjecture~\ref{conj:sharp-envelope} to interpret the algebraic envelope as the sharp identified set.

\begin{corollary}[Finite-sample audit collapses to exact endpoint under valid singleton bands]\label{cor:band-collapse}
Under Assumptions~\ref{ass:simul-bands}, \ref{ass:fiber-invariance}, and \ref{ass:endpoint-calibration}, if \(\widehat L_{\epsilon,\alpha}(r_1,r_0)=\widehat U_{\epsilon,\alpha}(r_1,r_0)=\Delta_{\mathrm{plug}}(P;r_1,r_0)\) on the simultaneous coverage event, then the finite-sample audit reports the same sign and endpoint as the exact-representation plug-in rule on that target pair.
\end{corollary}
The reduction is concrete: Assumption~\ref{ass:fiber-invariance} collapses \(B_\epsilon(P;r_1,r_0)\) to \(c_1-c_0\), Assumption~\ref{ass:endpoint-calibration} identifies \(c_1-c_0\) with \(\Delta_{\mathrm{plug}}\), and Assumption~\ref{ass:simul-bands} makes the reported band contain that singleton on the stated coverage event.

\section{Proof-sketch route}
The mathematical route begins with the finite-support selector LP: write one simplex of weights over the atoms in each target distortion fiber, use Assumption~\ref{ass:selector-sufficiency} to identify each selector mean as a weighted average of \(\mu(z)\), and observe that the difference of two simplex averages is exactly the interval between the worst and best endpoint choices.  The Borel conjecture should then follow by replacing atomwise minima and maxima with essential extrema and approximating them by selector kernels supported on positive-mass neighborhoods inside each fiber; the only non-routine step is a measurable-selection or kernel-approximation lemma that preserves the target-fiber support conditions.  Outer containment is endpoint algebra because every selector integral over a fiber lies between the essential infimum and supremum of \(\mu\) on that fiber.  The audit-impossibility conjecture then adds a representation-learning step: condition on the same \(P\), \(\mu^\dagger\), and certified distortion fibers used by a GenAI plug-in endpoint, vary only the admissible oracle calibration and selector kernels, and use the elementary fact that every scalar approximation to an interval has worst-case absolute error at least half the interval diameter.  The two-fiber open-class clause should be verified by constructing selectors on the four positive-mass sets \(A_j^-,A_j^+\), perturbing \(\mu\) uniformly by less than \(\delta-\eta\), and checking that the plug-in endpoint remains fixed while the selector-indexed oracle contrast moves across the displayed separation.  The finite-sample audit clause is a coverage transfer: on the simultaneous coverage event for \(\widehat B_{\epsilon,\alpha}\), the robust-sign decision is simply the sign of a covered interval endpoint, and point-endpoint reporting reduces to the band-collapse plus endpoint-calibration certificate.  The sign-reversal clause follows by choosing selectors on opposite sides of zero under Assumption~\ref{ass:local-crossing}; when the interval collapses, literal plug-in validity reduces to comparing \(\mu^\dagger(r_j)\) with the common fiber constants.

\section{Honest scope flags}
The exact-recovery statement is only a sanity-check boundary, not a theorem-level novelty claim.  For \(B_0\) it requires atomic target support; continuous exact-representation recovery is tracked by the separate \(B^{\mathrm{eval}}_0\) functional and should not be conflated with positive-mass essential extrema.  Theorem~\ref{thm:finite-support-lp} is finite-support algebra; it is included to make the selector semantics and law-preservation equations auditable before the Borel case.  Conjecture~\ref{conj:sharp-envelope} is open; the main technical uncertainty is whether the essential-envelope sharpness argument for arbitrary Borel supports needs a measurable-selection lemma or a restriction to regular conditional selector kernels.  Conjecture~\ref{conj:audit-impossibility} is the flagship open kernel and should be read as a quantitative nonparametric obstruction for the GenAI representation-endpoint workflow plus a finite-sample robust-sign reporting rule; it is not claiming that endpoint calibration is necessary for an arbitrary rule that computes the singleton value directly from \(P\).  Theorem~\ref{thm:fiber-singleton} is only envelope and endpoint-calibration algebra; it becomes an identified-set singleton statement only if Conjecture~\ref{conj:sharp-envelope} is proved.  This v5 revision addresses the prior \texttt{N-thin-survey} concern by adding a nondegenerate two-fiber open failure class, finite-sample simultaneous-band audit language, and the \citet{ImbensManski2004}/\citet{Stoye2009} inference comparators.  This proposal deliberately does not re-propose the burned dynamic-IV compliance seed and does not rely on panel or structural-SCM infrastructure.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial pivot draft proposing sharp representation-distortion ATE envelopes and a sign-reversal impossibility boundary for approximate causal sufficiency; prior verdict: none.
\item v2 (revise) -- addressed \texttt{N-thin-survey} by making the flagship kernel a certified audit impossibility for any selector-free single learned-representation endpoint, separating it from generic BMM/Manski envelope algebra; prior verdict: REVISE.
\item v3 (revise) -- narrowed endpoint-calibration necessity to literal learned-regression endpoints and strengthened the flagship obstruction to a half-diameter lower bound for every selector-free scalar endpoint on open target classes; prior verdict: REVISE.
\item v4 (revise) -- addressed \texttt{N-thin-survey} by tying Conjecture~\ref{conj:audit-impossibility} to the GenAI plug-in endpoint workflow and adding the Zhu--Gultchin--Gretton--Kusner--Silva corrupted-treatment NPIV comparator; prior verdict: REVISE.
\item v5 (revise) -- addressed \texttt{N-thin-survey} by upgrading Conjecture~\ref{conj:audit-impossibility} with a nondegenerate two-fiber open failure class and a finite-sample simultaneous-band audit/reporting rule; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Beresteanu, Molchanov, and Molinari(2011)]{BeresteanuMolchanovMolinari2011}
Beresteanu, A., Molchanov, I., and Molinari, F. (2011).
\newblock Sharp identification regions in models with convex moment predictions.
\newblock \emph{Econometrica}, 79(6):1785--1821.
\newblock \url{https://www.econometricsociety.org/publications/econometrica/2011/11/01/sharp-identification-regions-models-convex-moment-predictions}.

\bibitem[Beresteanu, Molchanov, and Molinari(2012)]{BeresteanuMolchanovMolinari2012}
Beresteanu, A., Molchanov, I., and Molinari, F. (2012).
\newblock Partial identification using random set theory.
\newblock \emph{Journal of Econometrics}, 166(1):17--32.
\newblock \url{https://www.sciencedirect.com/science/article/pii/S0304407611001163}.

\bibitem[Corcoll-Andreu et~al.(2026)]{CorcollAndreuVlontzosORiordanGilliganLee2026}
Corcoll-Andreu, V., Vlontzos, A., O'Riordan, L., Gilligan-Lee, C., and collaborators (2026).
\newblock Contrastive representations of structured treatments.
\newblock \emph{npj Artificial Intelligence}.
\newblock \url{https://www.nature.com/articles/s44387-026-00105-2}.

\bibitem[Egami et~al.(2022)]{EgamiFongGrimmerRobertsStewart2022}
Egami, N., Fong, C. J., Grimmer, J., Roberts, M. E., and Stewart, B. M. (2022).
\newblock How to make causal inferences using texts.
\newblock \emph{Science Advances}, 8(42):eabg2652.
\newblock \url{https://doi.org/10.1126/sciadv.abg2652}.

\bibitem[Fong and Grimmer(2023)]{FongGrimmer2023}
Fong, C. and Grimmer, J. (2023).
\newblock Causal inference with latent treatments.
\newblock \emph{American Journal of Political Science}, 67(2):374--389.
\newblock \url{https://doi.org/10.1111/ajps.12649}.

\bibitem[Horowitz and Manski(1995)]{HorowitzManski1995}
Horowitz, J. L. and Manski, C. F. (1995).
\newblock Identification and robustness with contaminated and corrupted data.
\newblock \emph{Econometrica}, 63(2):281--302.

\bibitem[Imai and Nakamura(2024)]{ImaiNakamura2024TextTreatments}
Imai, K. and Nakamura, K. (2024).
\newblock Causal representation learning with generative artificial intelligence: Application to texts as treatments.
\newblock arXiv:2410.00903.
\newblock \url{https://arxiv.org/abs/2410.00903}.

\bibitem[Imai and Nakamura(2025)]{ImaiNakamura2025GPI}
Imai, K. and Nakamura, K. (2025).
\newblock GenAI-powered inference.
\newblock arXiv:2507.03897.
\newblock \url{https://arxiv.org/abs/2507.03897}.

\bibitem[Imbens and Manski(2004)]{ImbensManski2004}
Imbens, G. W. and Manski, C. F. (2004).
\newblock Confidence intervals for partially identified parameters.
\newblock \emph{Econometrica}, 72(6):1845--1857.
\newblock \url{https://doi.org/10.1111/j.1468-0262.2004.00555.x}.

\bibitem[Nakamura and Imai(2026)]{ImaiNakamura2026Dynamic}
Nakamura, K. and Imai, K. (2026).
\newblock GenAI powered dynamic causal inference with unstructured data.
\newblock arXiv:2605.07834.
\newblock \url{https://arxiv.org/abs/2605.07834}.

\bibitem[Kaddour et~al.(2021)]{KaddourZhuLiuKusnerSilva2021}
Kaddour, J., Zhu, Y., Liu, Q., Kusner, M. J., and Silva, R. (2021).
\newblock Causal effect inference for structured treatments.
\newblock \emph{Advances in Neural Information Processing Systems}, 34:24841--24854.
\newblock \url{https://proceedings.neurips.cc/paper/2021/hash/d02e9bdc27a894e882fa0c9055c99722-Abstract.html}.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review Papers and Proceedings}, 80(2):319--323.

\bibitem[Manski(2003)]{Manski2003}
Manski, C. F. (2003).
\newblock \emph{Partial Identification of Probability Distributions}.
\newblock Springer.

\bibitem[Manski and Tamer(2002)]{ManskiTamer2002}
Manski, C. F. and Tamer, E. (2002).
\newblock Inference on regressions with interval data on a regressor or outcome.
\newblock \emph{Econometrica}, 70(2):519--546.
\newblock \url{https://www.econometricsociety.org/publications/econometrica/2002/03/01/inference-regressions-interval-data-regressor-or-outcome}.

\bibitem[Mozer et~al.(2020)]{MozerMiratrixKaufmanAnastasopoulos2020}
Mozer, R., Miratrix, L., Kaufman, A. R., and Anastasopoulos, L. J. (2020).
\newblock Matching with text data: An experimental evaluation of methods for matching documents and of measuring match quality.
\newblock \emph{Political Analysis}, 28(4):445--468.
\newblock \url{https://doi.org/10.1017/pan.2020.1}.

\bibitem[Stoye(2009)]{Stoye2009}
Stoye, J. (2009).
\newblock More on confidence intervals for partially identified parameters.
\newblock \emph{Econometrica}, 77(4):1299--1315.
\newblock \url{https://doi.org/10.3982/ECTA7173}.

\bibitem[Ura(2018)]{Ura2018}
Ura, T. (2018).
\newblock Heterogeneous treatment effects with mismeasured endogenous treatment.
\newblock \emph{Quantitative Economics}, 9(3):1335--1370.
\newblock \url{https://qeconomics.org/ojs/forth/886/886-2.pdf}.

\bibitem[Veitch, Sridhar, and Blei(2020)]{VeitchSridharBlei2020}
Veitch, V., Sridhar, D., and Blei, D. M. (2020).
\newblock Adapting text embeddings for causal inference.
\newblock In \emph{Proceedings of the 36th Conference on Uncertainty in Artificial Intelligence}, PMLR 124:919--928.
\newblock \url{https://proceedings.mlr.press/v124/veitch20a.html}.

\bibitem[Zhu et~al.(2022)]{ZhuGultchinGrettonKusnerSilva2022}
Zhu, Y., Gultchin, L., Gretton, A., Kusner, M. J., and Silva, R. (2022).
\newblock Causal inference with treatment measurement error: A nonparametric instrumental variable approach.
\newblock In \emph{Proceedings of the Thirty-Eighth Conference on Uncertainty in Artificial Intelligence}, PMLR 180:2414--2424.
\newblock \url{https://proceedings.mlr.press/v180/zhu22a.html}.
\end{thebibliography}

\end{document}
