\begin{proof}[Proof of \cref{obj:thm:hetero-clt}]
Write \(p_n=p_n^*(G_n)\).  The optimality condition identifies this sequence; the argument uses its stated feasibility and regularity properties.

\begin{enumerate}
\item[(1)] Outcome indexing gives \(|O_n|=n\) eventually.  Hence \(|O_n|\to\infty\), and, on this tail, \(\sqrt{|O_n|}=\sqrt n\) and \(|O_n|^{-1/2}=n^{-1/2}\).
% lean: hetero_clt

\item[(2)] Let \(K(\epsilon,\bar d)\) be the denominator-kernel bound.  Uniform positivity gives \(\epsilon_0>0\) with \(\epsilon_0\le\epsilon_n\) eventually.  Thus \(K(\epsilon_n,\bar d)\) is eventually bounded by \(K(\epsilon_0,\bar d)\), and therefore
\[
\frac{K(\epsilon_n,\bar d)}{|O_n|}\longrightarrow0.
\]
% lean: denominatorKernelBound_div_card_tendsto_zero

\item[(3)] Define
\[
R_{1n}=|O_n|^{-1/2}\{\text{treated numerator}\},\qquad
R_{0n}=|O_n|^{-1/2}\{\text{control numerator}\},
\]
and
\[
Q_{1n}=|O_n|^{-1}D_1(p_n,Z)-1,\qquad
Q_{0n}=|O_n|^{-1}D_0(p_n,Z)-1.
\]
The local numerator bounds give boundedness in probability of \(R_{1n}\) and \(R_{0n}\).  The rate in (2), together with \cref{obj:ass:bounded-outcome-degree} and~\cref{obj:ass:bounded-overlap-dependency}, gives
\[
Q_{1n}\xrightarrow{\Pr}0,\qquad Q_{0n}\xrightarrow{\Pr}0.
\]
Consequently,
\[
2|R_{1n}||Q_{1n}|+2|R_{0n}||Q_{0n}|
\xrightarrow{\Pr}0.
\]

For all sufficiently large \(n\), split according as
\[
D_1(p_n,Z)\ge\frac{|O_n|}{2}
\quad\text{and}\quad
D_0(p_n,Z)\ge\frac{|O_n|}{2}.
\]
When both inequalities hold, the capped Hájek remainder bound yields
\[
\left|
\sqrt{|O_n|}\{\widehat\tau_H(p_n)-\tau_n\}
-|O_n|^{-1/2}\sum_{i\in O_n}\eta_i(p_n,Z)
\right|
\le
2|R_{1n}||Q_{1n}|+2|R_{0n}||Q_{0n}|.
\]
If either inequality fails, then respectively
\[
|Q_{1n}|\ge\frac12
\quad\text{or}\quad
|Q_{0n}|\ge\frac12.
\]
Thus, for every \(\delta>0\), the probability that the absolute remainder exceeds \(\delta\) is bounded by the probability of this denominator-ratio bad event plus
\[
\Pr_{D_n}\!\left(
2|R_{1n}||Q_{1n}|+2|R_{0n}||Q_{0n}|\ge\delta
\right),
\]
and both terms converge to zero.
% lean: remainder_tendstoInProb_zero

\item[(4)] Taking the absolute remainder itself as the dominating product tail, the preceding convergence and the rate in (2) give the denominator-tightness condition.  The resulting squeeze therefore gives
\[
\sqrt{|O_n|}\{\widehat\tau_H(p_n)-\tau_n\}
-|O_n|^{-1/2}\sum_{i\in O_n}\eta_i(p_n,Z)
\xrightarrow{\Pr}0.
\]
% lean: heteroDenominatorTightness_discharged
% lean: hetero_linearization_of_denominator_tightness

\item[(5)] Set \(X_{n,i}=\eta_i(p_n,Z)\) for \(i\in O_n\), and use the outcome-overlap graph as a dependency graph.  These summands have mean zero; its neighborhoods have cardinality at most \(\lceil\bar D\rceil+1\); and \cref{obj:ass:bounded-outcomes} and~\cref{obj:ass:bounded-outcome-degree}, together with the eventual positivity floor, give the eventual bound
\[
|X_{n,i}|\le 4\{K(\epsilon_0,\bar d)+2\}.
\]
Moreover, with
\[
v_n=\mathbb E_{D_n}\!\left[\left(\sum_{i\in O_n}X_{n,i}\right)^2\right],
\]
the score-moment identity gives
\[
v_n=|O_n|\,\sigma^2_{G_n,p_n}(Y).
\]
\cref{obj:ass:variance-nondegenerate} consequently supplies \(c>0\) such that \(v_n\ge c|O_n|\) eventually.  On the tail from (1), \cref{obj:lem:bounded-degree-dependency-clt} applies and yields, for every \(s\in\mathbb R\),
\[
\Pr_{D_n}\!\left(
\frac{|O_n|^{-1/2}\sum_{i\in O_n}\eta_i(p_n,Z)}
{\sqrt{\sigma^2_{G_n,p_n}(Y)}}\le s
\right)
\longrightarrow
\Pr\{N(0,1)\le s\}.
\]
% lean: hetero_linscore_clt_of_depgraph

\item[(6)] Define
\[
S_n=
\frac{\sqrt{|O_n|}\{\widehat\tau_H(p_n)-\tau_n\}}
{\sqrt{\sigma^2_{G_n,p_n}(Y)}},
\qquad
T_n=
\frac{|O_n|^{-1/2}\sum_{i\in O_n}\eta_i(p_n,Z)}
{\sqrt{\sigma^2_{G_n,p_n}(Y)}}.
\]
For every \(\eta>0\), the variance lower bound implies eventually
\[
\Pr_{D_n}(|S_n-T_n|\ge\eta)
\le
\Pr_{D_n}\!\left(
\left|
\sqrt{|O_n|}\{\widehat\tau_H(p_n)-\tau_n\}
-|O_n|^{-1/2}\sum_{i\in O_n}\eta_i(p_n,Z)
\right|
\ge\eta\sqrt c
\right),
\]
which tends to zero by (4).  Since \(T_n\) has the standard-normal CDF limit by (5), continuity of that CDF and the converging-together argument yield
\[
\Pr_{D_n}(S_n\le s)\longrightarrow\Pr\{N(0,1)\le s\}
\]
for every \(s\in\mathbb R\).  Replacing \(|O_n|\) by \(n\) on the eventual tail from (1) proves both conclusions.
% lean: hetero_studentized_slutsky
\end{enumerate}
\end{proof}
