\begin{proof}[Proof of \cref{obj:thm:heterogeneity-separation}]
\begin{enumerate}
\item Suppose that the homogeneous-point gradient scores are not all equal.  First, \(p^{\mathrm{hom}}\in\mathcal P_{n,B_n,\epsilon}\): each coordinate equals \(\rho\in(\epsilon,1-\epsilon)\), and
\[
\sum_{k\in I_n}p^{\mathrm{hom}}_k=m_n\rho=B_n.
\]

For later use, fix arbitrary \(a,b\in I_n\), write
\[
d=e_b-e_a,\qquad
T=\min\{\rho-\epsilon,\,1-\epsilon-\rho\},
\]
and set
\[
\gamma(s)=\frac14V_{\mathrm{env}}(G_n,p^{\mathrm{hom}}+sd).
\]
The segment \(p^{\mathrm{hom}}+sd\) is feasible for \(s\in[-T,T]\).  For \(s\geq0\), this follows directly from the bounds defining \(T\); for \(s<0\), it follows by applying the same argument with \(a\) and \(b\) exchanged.  Moreover, \(|d_k|\leq1\) for every \(k\), and, on \(0\leq s\leq T\), both coordinates \(p^{\mathrm{hom}}_k+sd_k\) and their complements are at least \(\epsilon/2\).

Consequently, \(\gamma\) is twice continuously differentiable on \([0,T]\), differentiable at \(0\), and
\[
\gamma'(0)=g_b(G_n,p^{\mathrm{hom}})-g_a(G_n,p^{\mathrm{hom}}).
\]
Writing \(L_{ab}\) for the directional modulus along \(d\), convexity of the envelope from \cref{obj:thm:convex-design}, together with the directional curvature representation, gives
\[
0\leq L_{ab},
\qquad
\gamma''(s)\leq L_{ab}\quad(0\leq s\leq T).
\]

We next show that \(p^{\mathrm{hom}}\) is not a minimizer.  Otherwise, \cref{obj:thm:convex-design} supplies a budget multiplier \(\lambda_n\) and nonnegative upper- and lower-box multipliers \(\nu^+_{k,n}\) and \(\nu^-_{k,n}\) satisfying
\[
g_k(G_n,p^{\mathrm{hom}})
=\lambda_n-\nu^+_{k,n}+\nu^-_{k,n},
\]
together with the complementary-slackness identities
\[
\nu^+_{k,n}\bigl(p^{\mathrm{hom}}_k-(1-\epsilon)\bigr)=0,
\qquad
\nu^-_{k,n}\bigl(\epsilon-p^{\mathrm{hom}}_k\bigr)=0.
\]
Since every homogeneous coordinate is strictly interior, both factors multiplying the respective multipliers are nonzero.  Thus \(\nu^+_{k,n}=\nu^-_{k,n}=0\) for every \(k\), so all gradient scores equal \(\lambda_n\), a contradiction.

Choose \(a\) attaining the maximum and \(b\) attaining the minimum of
\(k\mapsto g_k(G_n,p^{\mathrm{hom}})\).  If these extrema were equal, all scores would be equal, contrary to hypothesis.  Hence
\[
\Delta_g
=g_a(G_n,p^{\mathrm{hom}})-g_b(G_n,p^{\mathrm{hom}})
>0.
\]
For the above line function associated with these extremal indices,
\[
\gamma'(0)=-\Delta_g.
\]
Define
\[
s_*=
\begin{cases}
T, & L_{ab}=0,\\
\min\{T,\Delta_g/L_{ab}\}, & L_{ab}\ne0.
\end{cases}
\]
The one-dimensional second-order descent estimate yields \(s_*\in[0,T]\) and
\[
\gamma(0)-\gamma(s_*)\geq \frac{\Delta_g}{2}s_*.
\]
The design \(q=p^{\mathrm{hom}}+s_*d\) is feasible.  Therefore, for every
\(p_n^*(G_n)\in\operatorname{argmin}_{p\in\mathcal P_{n,B_n,\epsilon}}
V_{\mathrm{env}}(G_n,p)\),
\[
V_{\mathrm{env}}(G_n,p_n^*(G_n))
\leq V_{\mathrm{env}}(G_n,q).
\]
Multiplying the preceding descent inequality by \(4\) gives
\[
V_{\mathrm{env}}(G_n,p^{\mathrm{hom}})
-
V_{\mathrm{env}}(G_n,p_n^*(G_n))
\geq 2\Delta_gs_*,
\]
which is the asserted bound after substituting \(T\) and \(s_*\).

Finally, \(p_n^*(G_n)\neq p^{\mathrm{hom}}\), since otherwise
\(p^{\mathrm{hom}}\) would be a minimizer.  Optimality gives the corresponding weak inequality in envelope values; equality would again make \(p^{\mathrm{hom}}\) a minimizer.  Thus
\[
V_{\mathrm{env}}(G_n,p_n^*(G_n))
<
V_{\mathrm{env}}(G_n,p^{\mathrm{hom}}).
\]
% lean: CausalSmith.Experimentation.BipartiteMinimaxDesign.envelope_segment_descent_gap

\item Now suppose that \(|N_i(G_n)|=1\) for every \(i\in O_n\), and fix \(k\in I_n\).  If \(k\in S_{ij}(G_n)\), then \(S_{ij}(G_n)\) is a nonempty subset of \(N_i(G_n)\), and hence has cardinality one.  Therefore every nonzero summand in the homogeneous-point gradient formula equals
\[
(1-\rho)^{-2}-\rho^{-2}.
\]
The number of ordered pairs \((i,j)\) such that \(k\in S_{ij}(G_n)\) is \(s_k^2\).  Substitution into the gradient formula gives
\[
g_k(G_n,p^{\mathrm{hom}})
=
n^{-1}s_k^2\left((1-\rho)^{-2}-\rho^{-2}\right).
\]
% lean: CausalSmith.Experimentation.BipartiteMinimaxDesign.singleton_envelopeGrad_eq_sdeg_sq

\item Retain the singleton-neighborhood condition and suppose that
\(s_a^2\neq s_b^2\) for some \(a,b\in I_n\).  Put
\[
C=(1-\rho)^{-2}-\rho^{-2}.
\]
This scalar is nonzero.  Indeed, if \(C=0\), then
\((1-\rho)^2=\rho^2\); thus either \(1-\rho=\rho\), contradicting
\(\rho\neq1/2\), or \(1-\rho=-\rho\), which would imply \(1=0\).

Also \(n>0\).  Otherwise \(O_n\) would be empty, every intervention-side degree quantity would vanish, and \(s_a^2\neq s_b^2\) would be impossible.  Hence \(n^{-1}C\neq0\).  The formula from the preceding step then implies
\[
g_a(G_n,p^{\mathrm{hom}})\neq g_b(G_n,p^{\mathrm{hom}}).
\]
The conclusions of the first step therefore apply.
% lean: CausalSmith.Experimentation.BipartiteMinimaxDesign.singleton_degree_spread_to_gradient_spread
\end{enumerate}
% lean: CausalSmith.Experimentation.BipartiteMinimaxDesign.heterogeneity_separation
\end{proof}
