% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_network\_exposure, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_network\_exposure} / \texttt{v1}%
  \\ \large\textit{Sharp joint-completion bounds for network-exposure ADEs}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This partial-identification instance has no regression coefficient; the inherited
``Regression estimator'' slot is filled by the finite optimization formula
\[
\underline\theta_{\mathrm{joint}}(P)
=\min_{G,\mu}\theta_{\mathrm{ADE}}(s;G,\mu),
\qquad
\overline\theta_{\mathrm{joint}}(P)
=\max_{G,\mu}\theta_{\mathrm{ADE}}(s;G,\mu),
\]
where \(G\) ranges over one shared hidden-edge completion and \(\mu_i(a,s,r)\)
ranges over bounded mean potential outcomes satisfying the observed mean
equations.  The causal target is the finite-population average direct effect
\(\theta_{\mathrm{ADE}}(s)\), comparing \(A_i=1\) with \(A_i=0\) while holding
the local exposure \(S_i=s\) fixed and averaging over the hidden-neighbor state
induced by the same graph completion.  The main result is that the exact
mean-identified set is the finite union of these graph-specific LP projections,
so the displayed endpoints give the sharp endpoint interval
\(\Theta_I(P)\subseteq
[\underline\theta_{\mathrm{joint}}(P),\overline\theta_{\mathrm{joint}}(P)]\).
The proposal's cellwise nonsharpness conjecture is confirmed by an explicit
open three-unit design: independent unitwise hidden-exposure kernels can attain
an upper endpoint that no single degree-capped graph completion can realize.
The certificate conjecture is confirmed in the finite-polyhedral sense: every
failed endpoint demand is separated by a valid inequality of the projected
capacitated incidence polytope, although no polynomial-size universal list of
named inequalities is claimed.
\end{abstract}

\section{Introduction}
Network-interference analyses often replace the full assignment vector by a
low-dimensional exposure mapping.  This is attractive because it makes direct
and spillover effects estimable, but it is also fragile: if the analyst observes
only a local graph, a hidden edge changes the exposure labels of both endpoints.
The econometric question in this note is therefore not whether an exposure
mapping is useful, but how much of an average direct effect is identified when
hidden exposure errors must be generated by one shared graph completion.

The usual bounded-outcome logic says that unobserved potential outcomes produce
intervals rather than point estimates.  Existing network-interference work also
shows how to define exposure-specific effects under a known mapping and how to
study sensitivity to misspecified exposure maps or networks.  What is not
captured by a product of unitwise sensitivity sets is the cross-unit
compatibility restriction: one hidden edge consumes degree capacity at both
endpoints and fixes exposure labels jointly across units and assignments.

This note makes that compatibility restriction explicit.  It writes the sharp
finite mean-identified set as a union of linear-programming projections indexed
by feasible graph completions, proves that the cellwise exposure-propensity
relaxation is an outer bound, and gives a concrete open design where that outer
bound is strictly too wide.  The result is useful for formula design because it
separates two sources of uncertainty: bounded missing potential outcomes and
hidden-network feasibility.  A valid sensitivity formula for locally measured
networks should keep both, rather than replacing the hidden graph by independent
unitwise nuisance kernels.

\section{Related work and positioning}
The partial-identification anchor is \cite{Manski1990}, which shows how bounded
unobserved potential outcomes imply sharp worst-case bounds rather than point
identification.  The interference terminology follows \cite{HudgensHalloran2008},
where direct and indirect effects are defined in settings where one unit's
outcome can depend on other units' treatments.  The exposure-mapping framework
of \cite{AronowSamii2017} is the known-network benchmark: when the exposure
mapping is correct and the relevant cells have positive design probability,
randomization identifies exposure-specific average potential outcomes.

\cite{Savje2024} emphasizes that an exposure mapping can be either a definition
of the estimand or a structural restriction on potential outcomes; this note
uses the mapping as part of the structural restriction and then relaxes it by a
finite graph-completion class.  \cite{SavjeAronowHudgens2021} studies average
treatment effects under unknown limited interference, which is a useful
contrast because the local direct effect here deliberately depends on the
unobserved local exposure state.  \cite{Leung2022} develops asymptotic inference
under approximate neighborhood interference, whereas this note is finite and
partial-identification based.

The closest exposure-misspecification comparator is
\cite{SchroderOprescuFeuerriegelKallus2026}, which derives partial-identification
bounds using exposure-propensity sensitivity restrictions.  The present theorem
differs because its hidden exposure propensities must be induced by one shared
degree-capped graph completion, not by independent unitwise kernels.
\cite{WeinsteinNevo2026} studies bias and robust estimation under candidate
network misspecification; the object here is instead the exact finite
mean-identified set for a direct-effect target.  \cite{Egami2020},
\cite{BhattacharyaMalinskyShpitser2020}, and \cite{LiSussmanKolaczyk2021} are
network-uncertainty comparators, but they do not characterize the polyhedral
compatibility gap between a shared hidden graph and a product relaxation.
\cite{ZhangMohanPearl2023} gives bounds under uncertain interaction patterns in
linear graphical causal models, while the present note works with bounded
finite-population potential-outcome means under a local graph-completion class.

The certificate part is positioned against classical integer-programming
geometry.  \cite{Edmonds1965} is the canonical matching-polytope reference
showing that local degree constraints alone can miss global compatibility
inequalities, and \cite{Wolsey1975} is a standard source for cover and lifting
inequalities in \(0\)-\(1\) programs.  The causal contribution is not a new
polyhedral theorem; it is the reduction from a cellwise ADE endpoint to a
finite signed exposure-demand system whose infeasibility explains why a
sensitivity endpoint is not generated by any locally feasible network.  The
in-repository PartialID catalogue currently records this area as a seed family
for Manski, Balke--Pearl, IV, sensitivity, shape-restriction, and missing-data
bounds; it does not contain a prior network-exposure theorem of this form.

\section{Formal setup}
There are \(n<\infty\) units, indexed by \(i\in N=\{1,\ldots,n\}\).  The
assignment vector \(A=(A_1,\ldots,A_n)\in\{0,1\}^n\) is drawn from a known
randomized design \(\pi\) with finite support
\(\Omega_\pi=\{a:\pi(a)>0\}\).  The observed local graph is an undirected graph
\(\mathcal L\), and the analyst also specifies a finite candidate hidden-edge
set \(\mathcal C\subseteq\{\{i,j\}:i<j\}\) disjoint from \(\mathcal L\).  A
completion is an undirected graph
\[
G=\mathcal L\cup\{e\in\mathcal C:x_e=1\},
\qquad x_e\in\{0,1\},
\]
subject to degree caps
\[
\sum_{e\in\mathcal C}B_{ie}x_e\le K_i,\qquad
B_{ie}=\one\{i\in e\}.
\]
The finite completion class is denoted by \(\mathfrak G(\mathcal L,\mathcal C,K)\).

For assignment \(a\), the researcher-specified local exposure is
\[
S_i=s_i(a,\mathcal L)\in\mathcal S.
\]
For a completion \(G\), the hidden-neighbor exposure is
\[
R_i(G,a)=
\one\{\exists j:\{i,j\}\in G\setminus\mathcal L,\ a_j=1\}\in\{0,1\}.
\]
The structural exposure state is \(H_i(G,a)=(S_i,R_i(G,a))\).  The mean
potential-outcome surface is
\(\mu_i(a_i,s,r)=\E\{Y_i(a_i,s,r)\}\in[0,1]\).  The note works with the
mean-relevant observable law
\[
P=P_{I,A,S,Y;\,\pi,\mathcal L},
\]
where \(I\) is uniformly sampled from \(N\), \(A\sim\pi\), \(S_I=s_I(A,\mathcal L)\),
and \(Y_I\in[0,1]\) is observed.  The only features of \(P\) used by the
bounding functional are the known design and the conditional means
\[
m_{i,a,s}(P)=\E_P(Y_I\mid I=i,A_i=a,S_i=s),
\]
for cells with \(p_{i,a,s}=\Pr_\pi(A_i=a,S_i=s)>0\).

For a fixed completion \(G\), define
\[
w^G_{i,a,s,r}
=\Pr_\pi(R_i(G,A)=r\mid A_i=a,S_i=s),
\]
whenever \(p_{i,a,s}>0\).  A pair \((G,\mu)\) is mean-compatible with \(P\) if
\(G\in\mathfrak G(\mathcal L,\mathcal C,K)\), \(0\le \mu_i(a,s,r)\le1\), and
\[
\sum_{r\in\{0,1\}}w^G_{i,a,s,r}\mu_i(a,s,r)=m_{i,a,s}(P)
\]
for every observed cell with positive design probability.  The identified set
\(\Theta_I(P)\) is the set of all values of the target
\(\theta_{\mathrm{ADE}}(s;G,\mu)\) generated by mean-compatible pairs satisfying
the maintained restrictions below.

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_network\_exposure},\texttt{v1},
  P_{I,A,S,Y;\,\pi,\mathcal L},\ \theta_{\mathrm{ADE}}(s),\
  \mathcal{R}_{\mathrm{local\ graph+hidden\ completion}},\
  [\underline\theta_{\mathrm{joint}}(P),\overline\theta_{\mathrm{joint}}(P)]) .
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population,
\(A=(A_1,\ldots,A_n)\in\{0,1\}^n\) is assigned by a known randomized design
\(\pi\), \(\mathcal L\) is the locally observed undirected graph,
\(S_i=s_i(A,\mathcal L)\) is the researcher-specified local exposure, and
\(Y_i\in[0,1]\) is the observed outcome.  The target
\(\theta_{\mathrm{ADE}}(s)\) is the average direct treatment effect comparing
\(A_i=1\) to \(A_i=0\) while holding the local exposure value \(S_i=s\) fixed
and averaging over the latent hidden-exposure state induced by the true graph
completion.  The restrictions
\(\mathcal{R}_{\mathrm{local\ graph+hidden\ completion}}\) are finite support,
consistency, bounded outcomes, randomized assignment, local exposure positivity,
a completion class \(\mathfrak G(\mathcal L,\mathcal C,K)\) of undirected true
graphs that extend \(\mathcal L\) by hidden candidate edges \(\mathcal C\)
subject to degree caps \(K_i\), and exposure sufficiency for the pair
\((S_i,R_i(G,A))\), where \(R_i(G,A)\) is the hidden-neighbor exposure generated
by the same graph completion \(G\) for all units.  The bounding functional is
the sharp finite linear-programming projection over one shared graph completion
and bounded potential outcomes, not the product of independent unitwise
exposure-propensity sensitivity sets.

\section{Assumptions}
\begin{assumption}[Finite randomized local-network experiment]\label{ass:finite-randomized}
The population \(N\), assignment support \(\Omega_\pi\), design probabilities
\(\pi(a)\), local graph \(\mathcal L\), candidate hidden-edge set
\(\mathcal C\), degree caps \(K_i\), and local exposure maps \(s_i\) are finite
and known.  Conditioning is used only on cells with positive probability under
\(\pi\).
\end{assumption}

\begin{assumption}[Bounded potential-outcome means]\label{ass:bounded}
For every unit \(i\), treatment \(a\in\{0,1\}\), local exposure
\(s\in\mathcal S\), and hidden exposure \(r\in\{0,1\}\),
\[
0\le \mu_i(a,s,r)\le1.
\]
\end{assumption}

\begin{assumption}[Shared hidden graph completion]\label{ass:shared-completion}
There exists one graph \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\) that
determines \(R_i(G,A)\) for all units and all assignments.  Hidden edge choices
are not unit-specific nuisance variables and cannot vary across target units or
observed cells.
\end{assumption}

\begin{assumption}[Exposure sufficiency and consistency]\label{ass:exposure-consistency}
For the true completion \(G\), if \(A_i=a\), \(S_i=s\), and \(R_i(G,A)=r\), then
the observed mean outcome for unit \(i\) is generated by the mean potential
outcome \(\mu_i(a,s,r)\).  Other units' assignments affect \(i\)'s mean outcome
only through \((S_i,R_i(G,A))\).
\end{assumption}

\begin{assumption}[Local exposure positivity]\label{ass:positivity}
For the target exposure value \(s\), the target set
\[
T_s=\{i:\Pr_\pi(A_i=0,S_i=s)>0\text{ and }\Pr_\pi(A_i=1,S_i=s)>0\}
\]
is nonempty.  Every conditional probability \(w^G_{i,a,s,r}\) and every
observable mean \(m_{i,a,s}(P)\) used in the LP is formed only for cells with
\(p_{i,a,s}>0\).
\end{assumption}

\begin{assumption}[Observed conditional-mean matching]\label{ass:law-matching}
A feasible pair \((G,\mu)\) must reproduce the observed conditional-mean vector
\(m(P)=\{m_{i,a,s}(P):p_{i,a,s}>0\}\) through the linear equations
\[
\sum_{r\in\{0,1\}}w^G_{i,a,s,r}\mu_i(a,s,r)=m_{i,a,s}(P).
\]
The note makes no additional restriction on higher moments or full conditional
outcome distributions beyond boundedness and these means.
\end{assumption}

\begin{assumption}[Cellwise relaxation comparator]\label{ass:cellwise-comparator}
The cellwise comparator replaces the shared \(G\) by unit-specific kernels
\(Q_i(r\mid a,s)\) on \(\{0,1\}\).  For each \(i\), the support and marginal
range of \(Q_i\) must be attainable by some feasible completion when unit \(i\)
is considered in isolation, but the kernels for different units need not be
generated by the same edge vector \(x\).  Cellwise mean compatibility is imposed
by
\[
\sum_{r\in\{0,1\}}Q_i(r\mid a,s)\nu_i(a,s,r)=m_{i,a,s}(P),
\qquad 0\le\nu_i(a,s,r)\le1.
\]
\end{assumption}

\begin{assumption}[No hidden-effect restriction]\label{ass:no-hidden-effect}
For the joint model, \(\mu_i(a,s,0)=\mu_i(a,s,1)\) for every \(i,a,s\).  For the
corresponding no-hidden-effect cellwise comparator,
\(\nu_i(a,s,0)=\nu_i(a,s,1)\) for every \(i,a,s\).  This restriction is used
only as a sanity-check specialization, not in the main nonsharpness theorem.
\end{assumption}

\section{Regression estimator}
This section title is inherited from a common skeleton.  In the present
partial-identification problem, the estimand-defining functional is not a
regression estimator but a finite bounding program.

For a fixed completion \(G\), let \(\mathcal M(G;P)\) be the polytope of all
bounded mean surfaces \(\mu\) satisfying Assumptions~\ref{ass:bounded} and
\ref{ass:law-matching}.  For \(i\in T_s\), define the control-arm hidden-exposure
weights
\[
q^G_{i,s,r}=\Pr_\pi(R_i(G,A)=r\mid A_i=0,S_i=s).
\]
The graph-specific target value is
\[
\theta_{\mathrm{ADE}}(s;G,\mu)
=\frac{1}{|T_s|}
\sum_{i\in T_s}\sum_{r\in\{0,1\}}
q^G_{i,s,r}\{\mu_i(1,s,r)-\mu_i(0,s,r)\}.
\]
The exact mean-identified set is
\[
\Theta_I(P)=
\bigcup_{G\in\mathfrak G(\mathcal L,\mathcal C,K)}
\{\theta_{\mathrm{ADE}}(s;G,\mu):\mu\in\mathcal M(G;P)\}.
\]
The endpoint functionals are
\[
\underline\theta_{\mathrm{joint}}(P)
=\min_{G\in\mathfrak G(\mathcal L,\mathcal C,K)}
\min_{\mu\in\mathcal M(G;P)}\theta_{\mathrm{ADE}}(s;G,\mu),
\qquad
\overline\theta_{\mathrm{joint}}(P)
=\max_{G\in\mathfrak G(\mathcal L,\mathcal C,K)}
\max_{\mu\in\mathcal M(G;P)}\theta_{\mathrm{ADE}}(s;G,\mu).
\]
The minima and maxima exist because the completion class is finite and each
\(\mathcal M(G;P)\) is a compact polytope.  The interval
\([\underline\theta_{\mathrm{joint}}(P),\overline\theta_{\mathrm{joint}}(P)]\)
is the sharp endpoint interval: both endpoints are attainable whenever the
corresponding feasible set is nonempty.  The exact set \(\Theta_I(P)\) is the
finite union displayed above and need not be a connected interval.

The cellwise relaxation is
\[
\Theta_{\mathrm{cell}}(P)=
\left\{
\frac{1}{|T_s|}\sum_{i\in T_s}\sum_{r\in\{0,1\}}
Q_i(r\mid0,s)\{\nu_i(1,s,r)-\nu_i(0,s,r)\}:
(Q,\nu)\text{ satisfies Assumption~\ref{ass:cellwise-comparator}}
\right\}.
\]
It is an outer comparator, not the target identifying functional.  The main
question is when this product relaxation strictly exceeds the shared-completion
projection.

\section{Target causal estimand}
The causal target is a finite-population average direct effect at the local
exposure value \(s\).  If the true hidden completion is \(G_0\) and the true
mean potential-outcome surface is \(\mu^0\), then
\[
\theta_{\mathrm{ADE}}(s)
=\theta_{\mathrm{ADE}}(s;G_0,\mu^0)
=\frac{1}{|T_s|}
\sum_{i\in T_s}\sum_{r\in\{0,1\}}
q^{G_0}_{i,s,r}\{\mu^0_i(1,s,r)-\mu^0_i(0,s,r)\}.
\]
This is not defined to be an observed contrast.  It is the causal contrast that
would be obtained by changing \(A_i\) from \(0\) to \(1\), holding
\(S_i=s\), and averaging over the hidden-neighbor exposure distribution induced
by the true graph under the control-arm reference event \((A_i=0,S_i=s)\).  The
LP in Section~7 is an identifying and bounding device for this target, using
the observable conditional means and the graph-completion restrictions.

\section{Main theorems}
\begin{theorem}[Sharp finite joint-completion projection]\label{thm:joint-lp-sharp}
Under Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching}, the
exact mean-identified set is
\[
\Theta_I(P)=
\bigcup_{G\in\mathfrak G(\mathcal L,\mathcal C,K)}
\{\theta_{\mathrm{ADE}}(s;G,\mu):\mu\in\mathcal M(G;P)\}.
\]
Consequently,
\[
\Theta_I(P)\subseteq
[\underline\theta_{\mathrm{joint}}(P),\overline\theta_{\mathrm{joint}}(P)],
\]
and the two endpoints are sharp: each endpoint is attained by some
mean-compatible shared completion whenever the identified set is nonempty.
The interval is the sharp endpoint envelope; the exact identified set itself is
the displayed finite union and may be nonconvex.
\end{theorem}

Theorem~\ref{thm:joint-lp-sharp} confirms the Stage -1 routine LP-sharpness
claim, with the important precision that the sharp object is the finite
projection and the interval is the minimal endpoint envelope.  This differs
from known-exposure mapping results such as \cite{AronowSamii2017} because the
weights \(q^G_{i,s,r}\) and the observed mean equations both depend on an
unknown but shared graph completion.

\begin{theorem}[Cellwise nonsharpness and finite certificates]\label{thm:cellwise-gap}
Assume Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching} and
define \(\Theta_{\mathrm{cell}}(P)\) by Assumption~\ref{ass:cellwise-comparator}.
Then \(\Theta_I(P)\subseteq\Theta_{\mathrm{cell}}(P)\).  Moreover, Conjecture 1
from the Stage -1 proposal is confirmed: there is an open set of finite
experiments for which the containment is strict.

For every cellwise endpoint demand, graph realizability is equivalent to
feasibility of a finite binary capacitated-incidence system in the hidden-edge
variables \(x_e\).  Thus Conjecture 2 is confirmed in the finite-polyhedral
sense: if a cellwise endpoint is not generated by any shared completion, then a
valid inequality of the projected capacitated incidence polytope separates its
exposure-demand vector from all realizable vectors.  The statement does not
claim that odd-set and lifted-cover inequalities by themselves form a universal
small certificate list; all facets of the finite projected polytope are allowed.
\end{theorem}

Theorem~\ref{thm:cellwise-gap} is the nontrivial contribution.  It shows that
the product relaxation used in exposure-propensity sensitivity analysis can be
conservative for a reason that is invisible unit by unit: different unitwise
kernels may each be locally plausible but jointly incompatible with one
degree-capped hidden graph.  Compared with \cite{SchroderOprescuFeuerriegelKallus2026},
the theorem isolates the additional identifying content of local network
knowledge; compared with \cite{WeinsteinNevo2026}, it gives a population
partial-identification statement rather than a bias or robustness calculation.

\section{Interpretation}
Theorem~\ref{thm:joint-lp-sharp} says that there are two layers of missing
information.  First, for a fixed graph completion, the hidden exposure \(r\)
creates missing potential-outcome means, handled by a bounded linear program in
the style of Manski bounds.  Second, the graph itself is unknown, so the exact
identified set is the union over feasible completions.  The endpoint interval is
sharp as a bound because its lower and upper endpoints are achieved by actual
mean-compatible completions.

There is no clean regression coefficient in this partial-ID instance.  The
analog of a clean point estimate arises only in special cases: the hidden graph
is known, hidden exposure has no effect on the response surface, or the design
makes the hidden-exposure distribution the same in the observed treated cells
and the target reference distribution.  Otherwise the target is contaminated by
unobserved hidden-exposure states, and bounded potential outcomes leave a
genuine interval.

Theorem~\ref{thm:cellwise-gap} says that the shared-completion restriction can
tighten the interval beyond cellwise sensitivity bounds.  If no graph
restriction is imposed, the bound widens to the natural Manski range allowed by
\([0,1]\)-valued missing potential outcomes.  If the graph is known or the
hidden state is irrelevant, the bound can collapse to the known-exposure direct
effect.  Between these extremes, the tightening work is done by the incidence
constraints \(Bx\le K\) and by the fact that a single edge vector must serve all
units and all assignments.

\section{Step-by-step proof}
\begin{lemma}[Fixed-completion mean equations]\label{lem:fixed-completion}
Fix \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\).  Under
Assumptions~\ref{ass:finite-randomized}, \ref{ass:exposure-consistency}, and
\ref{ass:law-matching}, a bounded mean surface \(\mu\) is compatible with
\(P\) for this \(G\) if and only if, for every observed cell
\((i,a,s)\),
\[
\sum_{r\in\{0,1\}}w^G_{i,a,s,r}\mu_i(a,s,r)=m_{i,a,s}(P).
\]
\end{lemma}

\begin{proof}
Condition on the event \((I=i,A_i=a,S_i=s)\), whose probability is positive by
Assumption~\ref{ass:positivity} whenever it is used.  By
Assumption~\ref{ass:shared-completion}, the same \(G\) determines
\(R_i(G,A)\) for every assignment.  By
Assumption~\ref{ass:exposure-consistency}, the conditional mean outcome is
\(\mu_i(a,s,R_i(G,A))\).  Taking the conditional expectation over the remaining
random assignment coordinates under the known design \(\pi\) gives
\[
\E_P(Y_I\mid I=i,A_i=a,S_i=s)
=\sum_{r\in\{0,1\}}
\Pr_\pi(R_i(G,A)=r\mid A_i=a,S_i=s)\mu_i(a,s,r),
\]
which is the displayed equation by the definitions of \(m_{i,a,s}(P)\) and
\(w^G_{i,a,s,r}\).  The converse is definitional for mean compatibility:
bounded \(\mu\) satisfying these equations reproduces every observed conditional
mean used by the problem.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:joint-lp-sharp}]
The proof is a finite LP projection argument.  Let \((G_0,\mu^0)\) be any
mean-compatible data-generating structure satisfying
Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching}.  Lemma
\ref{lem:fixed-completion} implies \(\mu^0\in\mathcal M(G_0;P)\), so its target
value belongs to the displayed union.  This proves
\(\Theta_I(P)\subseteq\bigcup_G\{\theta_{\mathrm{ADE}}(s;G,\mu):\mu\in
\mathcal M(G;P)\}\).

Conversely, take any \(G\) and any \(\mu\in\mathcal M(G;P)\).  Since
\(\mathcal M(G;P)\) includes exactly the boundedness and observed mean-matching
constraints, the pair \((G,\mu)\) is a maintained mean-compatible structure.
The value \(\theta_{\mathrm{ADE}}(s;G,\mu)\) is therefore an element of
\(\Theta_I(P)\).  This proves equality with the finite union.

For each fixed \(G\), \(\mathcal M(G;P)\) is an intersection of finitely many
closed half-spaces, affine equalities, and the box \(0\le\mu\le1\), hence a
compact polytope.  The map \(\mu\mapsto\theta_{\mathrm{ADE}}(s;G,\mu)\) is
linear, so its minimum and maximum over \(\mathcal M(G;P)\) are attained at
extreme points.  Since the set of feasible completions is finite by
Assumption~\ref{ass:finite-randomized}, taking the minimum lower endpoint and
maximum upper endpoint over \(G\) gives attained values
\(\underline\theta_{\mathrm{joint}}(P)\) and
\(\overline\theta_{\mathrm{joint}}(P)\).  Every element of the exact union lies
between these endpoints by the definition of minimum and maximum, proving the
containment in the endpoint interval.  The endpoint sharpness follows from
attainment.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:cellwise-gap}]
First prove the outer-bound containment.  Any shared completion \(G\) induces
unitwise kernels \(Q_i^G(r\mid a,s)=w^G_{i,a,s,r}\).  These kernels satisfy the
unitwise isolation condition in Assumption~\ref{ass:cellwise-comparator}
because they are generated by a feasible completion, namely \(G\) itself.  With
\(\nu=\mu\), the cellwise mean equations are the same equations as in Lemma
\ref{lem:fixed-completion}.  Therefore every value in \(\Theta_I(P)\) also lies
in \(\Theta_{\mathrm{cell}}(P)\).

It remains to show strictness on an open set.  Consider \(n=3\), empty local
graph \(\mathcal L=\emptyset\), constant local exposure \(S_i=s\), hidden
candidates
\[
\mathcal C=\{\{1,3\},\{2,3\}\},
\]
and degree caps \(K_1=K_2=K_3=1\).  Let \(\pi\) be uniform over assignments with
exactly one treated unit.  Then every unit is in \(T_s\).  The feasible
completions are the empty hidden graph, the graph with edge \(\{1,3\}\), and
the graph with edge \(\{2,3\}\).

Let \(m_{i0}=m_{i,0,s}(P)\) and \(m_{i1}=m_{i,1,s}(P)\), and suppose
\[
0<m_{i0}<1,\qquad 0<m_{i1}<1,\qquad i=1,2,3.
\]
These inequalities define an open set of observable mean vectors.  If unit
\(i\) has no incident hidden edge in \(G\), then \(R_i(G,A)=0\) always, so the
largest contribution of unit \(i\) to the ADE is
\[
b_i=m_{i1}-m_{i0}.
\]
If unit \(i\) has one incident hidden edge, then under the exactly-one-treated
design
\[
\Pr_\pi(R_i=1\mid A_i=0,S_i=s)=\frac12,\qquad
\Pr_\pi(R_i=1\mid A_i=1,S_i=s)=0.
\]
The treated observed mean equation gives \(\mu_i(1,s,0)=m_{i1}\), while the
control equation gives
\[
\frac12\mu_i(0,s,0)+\frac12\mu_i(0,s,1)=m_{i0}.
\]
Maximizing the unit's target contribution subject to \(0\le\mu\le1\) sets
\(\mu_i(1,s,1)=1\), and the sum
\(\mu_i(0,s,0)+\mu_i(0,s,1)=2m_{i0}\) is fixed.  Hence the largest contribution
for an incident unit is
\[
u_i=\frac12\{m_{i1}+1-2m_{i0}\}
=b_i+d_i,
\qquad
d_i=\frac{1-m_{i1}}{2}>0.
\]
The shared graph can give incident hidden edges either to units \(1\) and \(3\)
or to units \(2\) and \(3\), but not to all three units.  Therefore the joint
upper endpoint in this design is
\[
\overline\theta_{\mathrm{joint}}(P)
=\frac13\left\{\sum_{i=1}^3 b_i+d_3+\max(d_1,d_2)\right\}.
\]
The cellwise relaxation can select, for each unit separately, a kernel generated
by some feasible one-edge completion in isolation.  It can therefore add all
three gains \(d_1,d_2,d_3\), giving
\[
\overline\theta_{\mathrm{cell}}(P)
=\frac13\left\{\sum_{i=1}^3 b_i+d_1+d_2+d_3\right\}.
\]
The gap is
\[
\overline\theta_{\mathrm{cell}}(P)
-\overline\theta_{\mathrm{joint}}(P)
=\frac{\min(d_1,d_2)}{3}>0.
\]
Thus the cellwise upper endpoint is not attainable by any shared completion, and
\(\Theta_I(P)\subsetneq\Theta_{\mathrm{cell}}(P)\) on this open set.  This
confirms Conjecture 1.

For the certificate claim, fix any finite list of endpoint exposure demands.
Let \(\mathcal D^+\) be the demanded events \((i,a)\) requiring
\(R_i(G,a)=1\), and let \(\mathcal D^0\) be the demanded events requiring
\(R_i(G,a)=0\).  Graph realizability is exactly feasibility of
\[
x_e\in\{0,1\},\qquad
\sum_{e\in\mathcal C}B_{ie}x_e\le K_i,
\]
\[
\sum_{e=\{i,j\}\in\mathcal C}a_jx_e\ge1
\quad ((i,a)\in\mathcal D^+),
\qquad
\sum_{e=\{i,j\}\in\mathcal C}a_jx_e=0
\quad ((i,a)\in\mathcal D^0).
\]
Let \(\mathcal V\subseteq\{0,1\}^M\) be the finite set of all demand-label
vectors generated by feasible edge vectors \(x\), where \(M=|\mathcal D^+|+
|\mathcal D^0|\), and let \(\mathcal P_{\mathrm{dem}}=\operatorname{conv}
(\mathcal V)\).  A binary demand vector belongs to \(\mathcal V\) if and only if
it belongs to \(\mathcal P_{\mathrm{dem}}\): a convex combination of binary
vectors can equal a binary vector only when every vector with positive weight
agrees in every coordinate.  Hence any nonrealizable binary demand vector is
outside the projected capacitated incidence polytope.  By finite-dimensional
separation, there is a valid inequality \(\alpha^\transpose z\le\beta\) for
\(\mathcal P_{\mathrm{dem}}\) such that \(\alpha^\transpose z^\star>\beta\) at
the cellwise demand \(z^\star\).  This is the promised finite certificate.  The
observed mean equations add only finitely many bounded linear constraints in the
potential-outcome means, so the same separation argument applies after adjoining
the LP variables.  This confirms Conjecture 2 in the finite-polyhedral sense
stated in the theorem.
\end{proof}

\section{Sanity checks}
\begin{enumerate}[leftmargin=*]
\item \textbf{Known-network collapse.}  If \(\mathcal C=\emptyset\) or all
hidden degree caps are zero, then \(\mathfrak G(\mathcal L,\mathcal C,K)\) has
one element and \(R_i(G,A)=0\) for every \(i,A\).  The observed mean equations
reduce to \(\mu_i(a,s,0)=m_{i,a,s}(P)\), so
\[
\theta_{\mathrm{ADE}}(s)
=\frac1{|T_s|}\sum_{i\in T_s}
\{m_{i,1,s}(P)-m_{i,0,s}(P)\},
\]
the standard known-exposure randomized direct-effect contrast.

\item \textbf{Natural Manski bound.}  If the graph-completion and
mean-matching restrictions are removed and only \(0\le\mu\le1\) remains, each
unit-level direct-effect contrast lies in \([-1,1]\).  Therefore the endpoint
interval widens to the vacuous bounded-outcome range \([-1,1]\), matching the
logic of \cite{Manski1990}.

\item \textbf{No-hidden-effect point identification.}  Under
Assumption~\ref{ass:no-hidden-effect}, write
\(\mu_i(a,s,0)=\mu_i(a,s,1)=\bar\mu_i(a,s)\).  The mean equation becomes
\(\bar\mu_i(a,s)=m_{i,a,s}(P)\), regardless of \(G\).  The joint and cellwise
sets both collapse to the known-exposure contrast in the first check.

\item \textbf{Balanced hidden exposure across treatment arms.}  If, for every
feasible \(G\) and target unit \(i\),
\[
\Pr_\pi(R_i(G,A)=r\mid A_i=1,S_i=s)
=
\Pr_\pi(R_i(G,A)=r\mid A_i=0,S_i=s),
\]
then the target weights equal the observed treated-cell mixture weights.  The
hidden state cancels from the arm contrast, and the ADE is again the average of
observed conditional mean differences.

\item \textbf{Monotone-treatment-response specialization.}  Adding the shape
restriction \(\mu_i(1,s,r)\ge\mu_i(0,s,r)\) for all \(i,s,r\) simply intersects
each graph-specific LP with linear inequalities.  The same projection proof
goes through, but the lower endpoint can only increase and the upper endpoint
can only decrease.  This is the direct analogue of adding shape restrictions to
Manski-style bounds.
\end{enumerate}

\section{Counterexample or minimality check}
The three-unit construction in the proof of Theorem~\ref{thm:cellwise-gap} is
also the minimality check for Assumption~\ref{ass:shared-completion}.  Dropping
the shared-completion restriction and retaining only unitwise feasible hidden
exposure propensities lets the endpoint add \(d_1+d_2+d_3\).  The degree cap at
unit \(3\) allows at most one hidden edge, so any true completion can add only
\(d_3+\max(d_1,d_2)\).  The weaker product basis therefore gives a strictly
larger upper bound even though each unitwise kernel is plausible in isolation.

The nearby formula that fixes the problem is to keep the binary edge variables
\(x_e\) and the incidence constraints in the endpoint program.  Equivalently,
one may start from the cellwise relaxation but add the finite realizability
certificate system
\[
\sum_{e\in\mathcal C}B_{ie}x_e\le K_i,\qquad
\sum_{e=\{i,j\}\in\mathcal C}a_jx_e\ge1,\qquad
\sum_{e=\{i,j\}\in\mathcal C}a_jx_e=0
\]
for the positive and zero exposure demands used by the endpoint.  Without local
positivity, the conditional weights \(w^G_{i,a,s,r}\) and \(q^G_{i,s,r}\) need
not be defined; without bounded outcomes, the LP endpoints may be infinite.
These are the support and boundary conditions that cannot be weakened in this
finite bounded-outcome formulation.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
\item \textbf{Finite sets.}  \(N=\{1,\ldots,n\}\), assignment support
\(\Omega_\pi\subseteq\{0,1\}^n\), local exposure range \(\mathcal S\), hidden
edge set \(\mathcal C\), and hidden state set \(\{0,1\}\).

\item \textbf{Graph-completion object.}  Binary vector
\(x=(x_e)_{e\in\mathcal C}\in\{0,1\}^{|\mathcal C|}\) with incidence matrix
\(B_{ie}\) and caps \(Bx\le K\); associated graph
\(G(x)=\mathcal L\cup\{e:x_e=1\}\).

\item \textbf{Exposure maps.}  Deterministic maps
\(s_i:\Omega_\pi\times\{\mathcal L\}\to\mathcal S\) and
\(R_i:\mathfrak G(\mathcal L,\mathcal C,K)\times\Omega_\pi\to\{0,1\}\).

\item \textbf{Observable mean vector.}  For positive cells,
\(m_{i,a,s}(P)=\E_P(Y_I\mid I=i,A_i=a,S_i=s)\), with
\(0\le m_{i,a,s}(P)\le1\).

\item \textbf{Probability weights.}  Conditional design weights
\(w^G_{i,a,s,r}=\Pr_\pi(R_i(G,A)=r\mid A_i=a,S_i=s)\) and target reference
weights \(q^G_{i,s,r}=\Pr_\pi(R_i(G,A)=r\mid A_i=0,S_i=s)\).  Dependencies:
finite support and local positivity.

\item \textbf{Potential-outcome mean surface.}  Array
\(\mu_i(a,s,r)\in[0,1]\).  Role: LP variables for missing bounded mean
potential outcomes.

\item \textbf{Graph-specific feasible polytope.}  \(\mathcal M(G;P)\) is the
box \(0\le\mu\le1\) intersected with the affine equations
\(\sum_r w^G_{i,a,s,r}\mu_i(a,s,r)=m_{i,a,s}(P)\).

\item \textbf{Linear target functional.}  Map
\((G,\mu)\mapsto\theta_{\mathrm{ADE}}(s;G,\mu)\), linear in \(\mu\) for fixed
\(G\).

\item \textbf{Exact identified set and endpoint interval.}  Finite union
\(\Theta_I(P)=\bigcup_G\theta_{\mathrm{ADE}}(s;G,\mathcal M(G;P))\) and
endpoint functionals \(\underline\theta_{\mathrm{joint}}(P)\),
\(\overline\theta_{\mathrm{joint}}(P)\).

\item \textbf{Probabilistic assumptions.}  Known randomized design, positive
conditioning cells, consistency/exposure sufficiency, and observed
conditional-mean matching.

\item \textbf{Deterministic identities.}  Incidence degree constraints,
definition of \(R_i(G,a)\), fixed-completion mean equation, compact-polytope
attainment of a linear functional, and finite-union endpoint identities.

\item \textbf{Strict-gap arithmetic.}  In the three-unit example, prove the
weights \(q=1/2\) for incident units under exactly-one-treated randomization,
derive \(u_i=b_i+d_i\) and \(d_i=(1-m_{i1})/2\), and compare
\(d_3+\max(d_1,d_2)\) with \(d_1+d_2+d_3\).

\item \textbf{Certificate object.}  Demand sets \(\mathcal D^+\) and
\(\mathcal D^0\), binary demand vector \(z\), feasible demand set
\(\mathcal V\), projected polytope \(\mathcal P_{\mathrm{dem}}=\operatorname{conv}
(\mathcal V)\), and separating inequality \(\alpha^\transpose z\le\beta\).
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a sharp finite partial-identification
description for a network-exposure average direct effect when hidden local edges
must arise from one shared graph completion.  The exact mean-identified set is a
finite union of graph-specific LP projections, and the reported interval is the
sharp endpoint envelope.  The clean point-identified cases are the known graph,
no hidden effect, or balanced hidden-exposure designs; otherwise the unobserved
hidden state creates Manski-style missing-potential-outcome ambiguity.  The main
source of extra tightening relative to cellwise sensitivity analysis is not a
new outcome restriction but the cross-unit incidence compatibility of hidden
edges.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AronowSamii2017}
Aronow, P. M. and Samii, C. (2017).
Estimating average causal effects under general interference, with application
to a social network experiment.
\emph{The Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem{BhattacharyaMalinskyShpitser2020}
Bhattacharya, R., Malinsky, D., and Shpitser, I. (2020).
Causal inference under interference and network uncertainty.
\emph{Proceedings of the 35th Conference on Uncertainty in Artificial
Intelligence}, PMLR 115, 1028--1038.

\bibitem{Edmonds1965}
Edmonds, J. (1965).
Maximum matching and a polyhedron with 0,1-vertices.
\emph{Journal of Research of the National Bureau of Standards, Section B}
69B(1--2), 125--130.

\bibitem{Egami2020}
Egami, N. (2020).
Spillover effects in the presence of unobserved networks.
\emph{Political Analysis} 29(3), 287--316.

\bibitem{HudgensHalloran2008}
Hudgens, M. G. and Halloran, M. E. (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.

\bibitem{Leung2022}
Leung, M. P. (2022).
Causal inference under approximate neighborhood interference.
\emph{Econometrica} 90(1), 267--293.

\bibitem{LiSussmanKolaczyk2021}
Li, W., Sussman, D. L., and Kolaczyk, E. D. (2021).
Causal inference under network interference with noise.
arXiv:2105.04518.

\bibitem{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem{Savje2024}
Savje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions
and assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem{SavjeAronowHudgens2021}
Savje, F., Aronow, P. M., and Hudgens, M. G. (2021).
Average treatment effects in the presence of unknown interference.
\emph{The Annals of Statistics} 49(2), 673--701.

\bibitem{SchroderOprescuFeuerriegelKallus2026}
Schroder, M., Oprescu, M., Feuerriegel, S., and Kallus, N. (2026).
Causal inference on networks under misspecified exposure mappings: A partial
identification framework.
arXiv:2602.03459.

\bibitem{WeinsteinNevo2026}
Weinstein, B. and Nevo, D. (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.

\bibitem{Wolsey1975}
Wolsey, L. A. (1975).
Faces for a linear inequality in 0--1 variables.
\emph{Mathematical Programming} 8, 165--178.

\bibitem{ZhangMohanPearl2023}
Zhang, C., Mohan, K., and Pearl, J. (2023).
Causal inference under interference and model uncertainty.
\emph{Proceedings of the Second Conference on Causal Learning and Reasoning},
PMLR 213, 371--385.
\end{thebibliography}

\end{document}
