% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_network\_exposure, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_network\_exposure} / \texttt{v1}%
  \\ \large\textit{Sharp ADE bounds from shared local-network completions under misspecified exposure maps}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_network\_exposure},\texttt{v1},
  P_{I,A,S,Y;\,\pi,\mathcal L},\ \theta_{\mathrm{ADE}}(s),\
  \mathcal{R}_{\mathrm{local\ graph+hidden\ completion}},\
  [\underline\theta_{\mathrm{joint}}(P),\overline\theta_{\mathrm{joint}}(P)]) .
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population, \(A=(A_1,\ldots,A_n)\in\{0,1\}^n\) is assigned by a known randomized design \(\pi\), \(\mathcal L\) is the locally observed undirected graph, \(S_i=s_i(A,\mathcal L)\) is the researcher-specified local exposure, and \(Y_i\in[0,1]\) is the observed outcome.  The target \(\theta_{\mathrm{ADE}}(s)\) is the average direct treatment effect comparing \(A_i=1\) to \(A_i=0\) while holding the local exposure value \(S_i=s\) fixed and averaging over the latent hidden-exposure state induced by the true graph completion.  The restrictions \(\mathcal{R}_{\mathrm{local\ graph+hidden\ completion}}\) are finite support, consistency, bounded outcomes, randomized assignment, local exposure positivity, a completion class \(\mathfrak G(\mathcal L,\mathcal C,K)\) of undirected true graphs that extend \(\mathcal L\) by hidden candidate edges \(\mathcal C\) subject to degree caps \(K_i\), and exposure sufficiency for the pair \((S_i,R_i(G,A))\), where \(R_i(G,A)\) is the hidden-neighbor exposure generated by the same graph completion \(G\) for all units.  The bounding functional is the sharp finite linear-programming projection over one shared graph completion and bounded potential outcomes, not the product of independent unitwise exposure-propensity sensitivity sets.

\begin{abstract}
Network-interference analyses often specify a low-dimensional exposure mapping, but in many applications only the local neighborhood of each unit is known.  Recent work gives sharp bounds for misspecified exposure mappings by bounding unitwise exposure propensities, and separate work studies bias or robust estimation when candidate networks are misspecified.  This proposal asks whether sharp partial identification of an average direct treatment effect changes when hidden exposure errors must arise from one shared graph completion rather than from independent unitwise sensitivity perturbations.  The routine theorem is a finite sharpness statement: the identified set is the projection of a graph-completion linear program.  The flagship conjecture is that the usual cellwise propensity-ratio relaxation can be strictly nonsharp because one hidden edge simultaneously constrains the exposure labels of both endpoints.  Resolving the conjecture would turn ``local network knowledge'' into testable compatibility inequalities for network exposure sensitivity analysis.
\end{abstract}

\section{Introduction}
Causal effects under interference depend on how treatments assigned to other units enter each unit's potential outcome.  Exposure mappings make this problem tractable by compressing a high-dimensional assignment vector into a local summary, but the mapping is rarely known.  The problem is sharper when the analyst knows only local network ties: a hidden tie is not merely a nuisance for one unit's exposure label, because the same edge also constrains the exposure label of the other endpoint.

The main proposed finding is a partial-identification result for average direct effects under locally known interference structure.  Theorem~\ref{thm:joint-lp-sharp} states the finite sharp identified set as a linear-programming projection over graph completions and bounded potential outcomes.  Conjecture~\ref{conj:cellwise-nonsharp} states the novelty kernel: the standard cellwise exposure-sensitivity relaxation is generally too wide because it lets each unit choose an exposure-error law that no single hidden graph can realize jointly.

What is new is the shared-completion constraint.  \citet{ZhangMohanPearl2023} derive bounds for average causal effects under uncertain interaction patterns in linear graphical causal models, \citet{Egami2020} treats spillover effects when the relevant network is unobserved, \citet{SchroderOprescuFeuerriegelKallus2026} bound direct and spillover effects under misspecified exposure mappings through exposure-propensity ratio bounds, and \citet{WeinsteinNevo2026} study bias and robust estimation under candidate network misspecification.  None isolates the finite partial-identification phenomenon that hidden local edges create cross-unit compatibility inequalities.  This proposal is not another estimator and not a weaker version of known-exposure mapping theory; it asks for the sharp gap between a joint graph-completion identified set and the product relaxation obtained by forgetting that hidden exposures share edges.

The proposal sits in the partial-identification and sensitivity-analysis cluster.  Its closest ancestors are Manski-style bounded-outcome identification, exposure-mapping interference estimands, and recent sensitivity analyses for misspecified exposure maps or misspecified networks.  It deliberately avoids the panel / linear-projection cluster: the target is a finite-population average direct effect under interference, and the object to be characterized is a sharp identified interval over feasible graph completions.

\section{Related work}
\citet{Manski1990} is the bounded-outcome partial-identification anchor: the present proposal uses the same logic that unobserved potential outcomes define intervals rather than point estimates.  \citet{HudgensHalloran2008} define direct and indirect effects under interference in the partial-interference setting, fixing the terminology for direct effects.  \citet{AronowSamii2017} introduce the exposure-mapping framework for general interference and show how randomized designs identify exposure-specific potential-outcome means when the mapping is correct.  \citet{ForastiereAiroldiMealli2021} extend network direct and interference effects to observational network studies with generalized propensity scores, illustrating how local exposures become estimands in applied network data.

\citet{SavjeAronowHudgens2021} show that a marginalized expected average treatment effect can be estimated under unknown limited interference, which is a useful contrast because this proposal targets a local-exposure direct effect that generally still needs network information.  \citet{Leung2022} replaces exact neighborhood interference by approximate neighborhood interference and establishes asymptotic inference for exposure effects; the present proposal instead keeps a finite partial-identification target and asks which graph completions are jointly feasible.  \citet{Savje2024} separates exposure mappings as definitions from exposure mappings as structural restrictions, motivating sensitivity analyses when the mapping is not fully correct.  The discussion by \citet{Leung2024Discussion} emphasizes that once exposure mappings no longer impose the full structure, alternative restrictions are needed for inference; the shared graph-completion class is one such finite restriction.

\citet{ZhangMohanPearl2023} is a close model-uncertainty bounds comparator: it models uncertain interaction patterns using linear graphical causal models, quantifies bias from incorrectly assuming IID data, and derives bounds for average causal effects, but it does not study a finite exposure-mapping ADE whose latent exposure labels must be induced by one shared local graph completion.  \citet{Egami2020} is the closest unobserved-network sensitivity comparator: it estimates network-specific spillover effects when one relevant network is unobserved, but it does not characterize sharp ADE bounds over a shared local graph-completion class.  \citet{BhattacharyaMalinskyShpitser2020} combines structure-learning and interference ideas for causal inference when network dependence is uncertain, whereas this proposal fixes a local completion class and asks for its finite identified set.  \citet{LiSussmanKolaczyk2021} studies how noisy network measurements affect bias and variance of network-interference estimators under a four-level exposure model; it does not give partial-identification bounds or shared-completion compatibility certificates.  \citet{SchroderOprescuFeuerriegelKallus2026} is the closest published partial-identification comparator: it gives sharp bounds for direct and spillover effects under exposure mapping misspecification through propensity-ratio sensitivity bounds, but it assumes a fully known network and does not impose shared hidden-edge compatibility.  \citet{WeinsteinNevo2026} is the closest network-misspecification comparator: it bounds bias from using a wrong network and constructs an estimator robust to a list of candidate networks, but it does not derive sharp average-direct-effect bounds over a local graph-completion class.  \citet{YuAiroldiBorgsChayes2022} studies total treatment effects with unknown network structure, showing that some global targets can be handled without network measurement; the local direct-effect target here is precisely a case where that escape route is unavailable.  \citet{BelloniFangVolfovsky2022} adaptively estimates unknown interference radius on a known network, whereas this proposal treats hidden graph completion as the partial-identification object.  \citet{GaoHarshawSavjeWang2026} proves that broad specification tests for exposure mapping models are impossible without additional restrictions, strengthening the case for reporting sharp bounds under explicit local-knowledge restrictions.

The certificate conjecture also touches classical polyhedral combinatorics rather than inventing new certificate mechanics.  \citet{Edmonds1965} gives the matching-polytope template in which degree constraints alone miss odd-set compatibility inequalities.  \citet{Wolsey1975} is a canonical source for cover and lifting inequalities in \(0\)-\(1\) programs, which is the relevant prior art for the proposed infeasible-demand certificates.  The causal contribution is not the existence of such inequalities in integer programming; it is the claim that the exposed-neighbor demands produced by a cellwise ADE endpoint reduce to a signed graph-completion feasibility system whose violated inequalities explain exactly why the causal bound is nonsharp.

The in-repository catalogue does not already contain this kernel.  The relevant entry in \texttt{doc/API.md} is the ExactID / PartialID catalogue note, which records that the PartialID catalogue is a seed area for Manski-family bounds, IV bounds, sensitivity analysis, shape restrictions, and missing-data bounds rather than a populated network-exposure theorem.  The closest banked partial-ID proposal is \texttt{pid\_dynamic\_iv\_compliance\_v2}: assignment-memory mixture splitting for dynamic IV bounds under imperfect compliance.  That proposal also uses finite latent-response sharpness, but its kernel is compliance-history memory, not shared graph-completion compatibility.  The failed \texttt{pid\_late\_bounded\_defiers} proposal concerns bounded-defier complier-LATE envelopes and is likewise outside network interference.

\section{Formal setup}
There are \(n<\infty\) units.  The assignment vector is \(A\in\{0,1\}^n\), drawn from a known design \(\pi(a)>0\) on its support.  The analyst observes a local undirected graph \(\mathcal L\) and a candidate hidden-edge set \(\mathcal C\subseteq\{\{i,j\}:i<j\}\) disjoint from \(\mathcal L\).  A feasible true graph \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\) contains all edges in \(\mathcal L\), may contain hidden edges from \(\mathcal C\), and satisfies \(\sum_{j:\{i,j\}\in G\setminus\mathcal L}1\le K_i\) for each unit \(i\).

For \(e=\{i,j\}\in\mathcal C\), let \(x_e(G)=\one\{e\in G\}\), and let \(B_{ie}=\one\{i\in e\}\) be the hidden-edge endpoint incidence matrix.  Degree-cap feasibility is equivalently the capacitated incidence system
\[
x_e\in\{0,1\},\qquad \sum_{e\in\mathcal C} B_{ie}x_e\le K_i\quad\text{for every }i.
\]
For any assignment \(a\), the hidden-exposure requirement that unit \(i\) has at least one treated hidden neighbor is
\[
\sum_{e=\{i,j\}\in\mathcal C} x_e a_j \ge z_i(a),
\]
where \(z_i(a)\in\{0,1\}\) is the exposure-event variable used in the certificate formulation.  If an endpoint construction demands \(z_i(a)=0\), graph realizability also requires the upper/no-treated-neighbor constraint
\[
\sum_{e=\{i,j\}\in\mathcal C} x_e a_j =0 .
\]
A strict cellwise endpoint is graph-realizable only if one binary vector \(x\) satisfies all endpoint-incidence, degree-cap, positive-exposure, and zero-exposure requirements that the endpoint construction demands.

The researcher-specified local exposure is \(S_i=s_i(A,\mathcal L)\in\mathcal S\).  For a graph completion \(G\), the hidden exposure is
\[
R_i(G,A)=\one\{\exists j:\{i,j\}\in G\setminus\mathcal L,\ A_j=1\}\in\{0,1\}.
\]
The structural exposure state is \(H_i(G,A)=(S_i,R_i(G,A))\).  Potential outcomes are \(Y_i(a_i,s,r)\in[0,1]\), and consistency requires \(Y_i=Y_i(A_i,S_i,R_i(G,A))\) for the true completion \(G\).  The observable distribution is the finite-population law \(P_{I,A,S,Y;\pi,\mathcal L}\) generated by a uniformly sampled unit \(I\), the known assignment law \(\pi\), the observed local exposure \(S_I\), and the outcome \(Y_I\).  The proposal's finite LP matches the observed conditional-mean vector
\[
m_{i,a,s}(P)=\E_P(Y_I\mid I=i,A_i=a,S_i=s)
\]
for every observed cell with positive probability; it does not attempt to match unmodelled latent outcome distributions beyond these bounded means.

For a local exposure value \(s\) with positive design probability, define
\[
q_{i,s,r}(G)=\Pr_\pi(R_i(G,A)=r\mid S_i=s,A_i=0)
\]
and the average direct effect
\[
\theta_{\mathrm{ADE}}(s;G,Y(\cdot))
=\frac{1}{n_s(G)}\sum_{i:\Pr_\pi(S_i=s,A_i=0)>0}
\sum_{r\in\{0,1\}}q_{i,s,r}(G)
\{Y_i(1,s,r)-Y_i(0,s,r)\},
\]
where \(n_s(G)\) is the number of units in the displayed sum.  The identified set \(\Theta_I(P)\) is the set of all values of \(\theta_{\mathrm{ADE}}(s;G,Y(\cdot))\) over feasible graph completions and bounded potential outcomes satisfying consistency and matching the observed conditional-mean vector \(m(P)\).  The bounding functionals are \(\underline\theta_{\mathrm{joint}}(P)=\inf\Theta_I(P)\) and \(\overline\theta_{\mathrm{joint}}(P)=\sup\Theta_I(P)\).

For the cellwise comparator, a tuple \(Q=(Q_i)_{i=1}^n\) assigns independent latent hidden-exposure kernels \(Q_i(z\mid a_i,s)\) on \(z\in\{0,1\}\).  The reference weights in the cellwise target use the same control-arm convention as the joint target:
\[
q^{\mathrm{cell}}_{i,s,z}(Q)=Q_i(z\mid 0,s).
\]
For bounded cellwise potential outcomes \(U_i(a,s,z)\in[0,1]\), define the target projection
\[
\theta_{\mathrm{cell}}(s;Q,U)
=\frac{1}{n_s}\sum_{i:\Pr_\pi(S_i=s,A_i=0)>0}
\sum_{z\in\{0,1\}}q^{\mathrm{cell}}_{i,s,z}(Q)
\{U_i(1,s,z)-U_i(0,s,z)\},
\]
where \(n_s\) is the same count of target-eligible units used in \(\theta_{\mathrm{ADE}}(s)\).  The relaxed set \(\Theta_{\mathrm{cell}}(P)\) is the set of all such \(\theta_{\mathrm{cell}}(s;Q,U)\) satisfying the support, propensity-range, boundedness, and observed conditional-mean equations in Assumption~\ref{ass:cellwise-comparator}.

\begin{quote}\small
This is a partial-identification anchor, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_network\_exposure},\texttt{v1},
  P_{I,A,S,Y;\,\pi,\mathcal L},\ \theta_{\mathrm{ADE}}(s),\
  \mathcal{R}_{\mathrm{local\ graph+hidden\ completion}},\
  [\underline\theta_{\mathrm{joint}}(P),\overline\theta_{\mathrm{joint}}(P)]) .
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population, \(A=(A_1,\ldots,A_n)\in\{0,1\}^n\) is assigned by a known randomized design \(\pi\), \(\mathcal L\) is the locally observed undirected graph, \(S_i=s_i(A,\mathcal L)\) is the researcher-specified local exposure, and \(Y_i\in[0,1]\) is the observed outcome.  The target \(\theta_{\mathrm{ADE}}(s)\) is the average direct treatment effect comparing \(A_i=1\) to \(A_i=0\) while holding the local exposure value \(S_i=s\) fixed and averaging over the latent hidden-exposure state induced by the true graph completion.  The restrictions \(\mathcal{R}_{\mathrm{local\ graph+hidden\ completion}}\) are finite support, consistency, bounded outcomes, randomized assignment, local exposure positivity, a completion class \(\mathfrak G(\mathcal L,\mathcal C,K)\) of undirected true graphs that extend \(\mathcal L\) by hidden candidate edges \(\mathcal C\) subject to degree caps \(K_i\), and exposure sufficiency for the pair \((S_i,R_i(G,A))\), where \(R_i(G,A)\) is the hidden-neighbor exposure generated by the same graph completion \(G\) for all units.  The bounding functional is the sharp finite linear-programming projection over one shared graph completion and bounded potential outcomes, not the product of independent unitwise exposure-propensity sensitivity sets.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite randomized local-network experiment]\label{ass:finite-randomized}
The population has \(n<\infty\) units, \(A\in\{0,1\}^n\) is drawn from a known design \(\pi\), the local graph \(\mathcal L\), candidate hidden-edge set \(\mathcal C\), degree caps \(K_i\), local exposure functions \(s_i\), and outcome \(Y_i\) are observed as in Section~6.
\end{assumption}

\begin{assumption}[Bounded potential outcomes]\label{ass:bounded}
For every unit \(i\), treatment \(a\in\{0,1\}\), local exposure \(s\in\mathcal S\), and hidden exposure \(r\in\{0,1\}\), \(0\le Y_i(a,s,r)\le1\).
\end{assumption}

\begin{assumption}[Shared hidden graph completion]\label{ass:shared-completion}
There exists one undirected graph \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\) that determines \(R_i(G,A)\) for all units and all assignments.  Hidden edge choices are not unit-specific nuisance variables.
\end{assumption}

\begin{assumption}[Exposure sufficiency and consistency]\label{ass:exposure-consistency}
For the true graph completion \(G\), if \(A_i=a\), \(S_i=s\), and \(R_i(G,A)=r\), then the observed outcome satisfies \(Y_i=Y_i(a,s,r)\).  Potential outcomes depend on other units' assignments only through \((S_i,R_i(G,A))\).
\end{assumption}

\begin{assumption}[Local positivity]\label{ass:positivity}
For the target exposure value \(s\), every unit included in \(\theta_{\mathrm{ADE}}(s)\) has positive design probability for \(A_i=0,S_i=s\) and \(A_i=1,S_i=s\).  Every observed cell used to match \(P\) has positive probability under \(\pi\).
\end{assumption}

\begin{assumption}[Observed conditional-mean matching]\label{ass:law-matching}
A feasible pair \((G,Y(\cdot))\) must reproduce the observed conditional-mean vector \(m(P)=\{m_{i,a,s}(P)\}\) from Section~6.  Equivalently, for each observed cell with positive probability, the average outcome induced by \((G,Y(\cdot))\) under the known assignment law and local graph equals \(m_{i,a,s}(P)\).
\end{assumption}

\begin{assumption}[Cellwise relaxation comparator]\label{ass:cellwise-comparator}
The cellwise comparator \(\Theta_{\mathrm{cell}}(P)\) is the projection onto the explicitly defined functional \(\theta_{\mathrm{cell}}(s;Q,U)\) from Section~6.  It keeps Assumptions~\ref{ass:finite-randomized}, \ref{ass:bounded}, and \ref{ass:positivity}, but replaces the shared completion \(G\) and the graph-based consistency equation in Assumptions~\ref{ass:shared-completion}--\ref{ass:exposure-consistency} by independent latent exposure variables \(Z_i(a)\in\{0,1\}\) with kernels \(Q_i(z\mid a_i,s_i(a,\mathcal L))\).  These kernels must have the same unitwise support and marginal exposure-propensity-ratio ranges that some feasible completion in \(\mathfrak G(\mathcal L,\mathcal C,K)\) could generate for unit \(i\) in isolation.  Observed conditional-mean matching is imposed directly through the mixture equations
\[
\E_{Z_i\sim Q_i(\cdot\mid A_i,S_i)}
  \{U_i(A_i,S_i,Z_i)\mid I=i,A_i,S_i\}
=
\E_P(Y_I\mid I=i,A_i,S_i),
\]
with \(0\le U_i(a,s,z)\le1\).  No true graph \(G\), no shared edge vector \(x\), and no equation involving \(R_i(G,A)\) is assumed inside \(\Theta_{\mathrm{cell}}(P)\).
\end{assumption}

\begin{assumption}[No hidden-effect restriction]\label{ass:no-hidden-effect}
For the joint model, \(Y_i(a,s,0)=Y_i(a,s,1)\) for every \(i,a,s\).  For the corresponding no-hidden-effect cellwise comparator, the response surface is also restricted so that \(U_i(a,s,0)=U_i(a,s,1)\) for every \(i,a,s\).  This restriction is used only in Corollary~\ref{cor:no-hidden-effect}; it is not imposed in Conjectures~\ref{conj:cellwise-nonsharp}--\ref{conj:cut-certificate}.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite joint-completion LP sharpness]\label{thm:joint-lp-sharp}
Under Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching}, the sharp identified set for \(\theta_{\mathrm{ADE}}(s)\) is
\[
\Theta_I(P)
=
\left\{
\theta_{\mathrm{ADE}}(s;G,Y(\cdot)):
G\in\mathfrak G(\mathcal L,\mathcal C,K),\
0\le Y_i(a,s,r)\le1,\
(G,Y(\cdot))\text{ matches }m(P)
\right\}.
\]
Because \(\mathfrak G(\mathcal L,\mathcal C,K)\) is finite, the endpoints
\(\underline\theta_{\mathrm{joint}}(P)\) and \(\overline\theta_{\mathrm{joint}}(P)\) are obtained by solving a finite collection of linear programs, one for each graph completion, and taking the minimum lower endpoint and maximum upper endpoint.
\end{theorem}
\paragraph{Why this is new and worth studying.}
The closest papers are \citet{SchroderOprescuFeuerriegelKallus2026} and \citet{WeinsteinNevo2026}.  The former gives exposure-propensity sensitivity bounds without hidden graph-completion compatibility, while the latter studies bias and robust estimation across candidate networks rather than the sharp partial-identification projection for a direct effect.  This theorem is routine finite-dimensional sharpness, but it fixes the correct object for the genuinely new compatibility conjecture and gives Stage~0 a precise bounding functional.

\begin{conjecture}[Conjecture 1: shared-edge compatibility makes cellwise bounds nonsharp]\label{conj:cellwise-nonsharp}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching}, and with \(\Theta_{\mathrm{cell}}(P)\) defined by Assumption~\ref{ass:cellwise-comparator}, there exists an open set of finite experiments with at least one hidden candidate edge \(\{i,j\}\in\mathcal C\) such that
\[
\Theta_I(P)\subsetneq \Theta_{\mathrm{cell}}(P).
\]
The strict containment can occur even when every unit-level hidden-exposure propensity allowed by the cellwise relaxation is generated by some feasible graph completion for that unit in isolation.  The obstruction is joint: the same hidden edge must simultaneously determine \(R_i(G,A)\) and \(R_j(G,A)\), so endpoint assignments permitted by independent unitwise kernels need not be realizable by any single \(G\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
The closest published results are the model-uncertainty bounds of \citet{ZhangMohanPearl2023} and the sharp propensity-ratio framework of \citet{SchroderOprescuFeuerriegelKallus2026}; the epsilon-gap is that neither identifies the loss from replacing one shared local graph completion by the product projection \(\theta_{\mathrm{cell}}(s;Q,U)\).  \citet{Egami2020}, \citet{BhattacharyaMalinskyShpitser2020}, and \citet{LiSussmanKolaczyk2021} are closer on network uncertainty, but they target estimation, discovery, or bias correction rather than finite sharp ADE bounds under one shared completion.  \citet{WeinsteinNevo2026} recognizes that the correctly specified network may not be unique, but it does not characterize the finite compatibility facets that distinguish a joint hidden graph from a product of unitwise errors.  Proving or refuting the conjecture would tell practitioners when exposure-mapping sensitivity intervals are conservative because they forgot edge sharing, and it would supply concrete compatibility checks for locally measured networks.

\begin{conjecture}[Conjecture 2: capacitated-incidence certificate characterization]\label{conj:cut-certificate}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching}, and with \(\Theta_{\mathrm{cell}}(P)\) defined by Assumption~\ref{ass:cellwise-comparator}, every strict gap between \(\Theta_I(P)\) and \(\Theta_{\mathrm{cell}}(P)\) has a finite certificate supported on the capacitated incidence system linking hidden candidate edges to signed unit-assignment exposure events.  After fixing an endpoint value in \(\Theta_{\mathrm{cell}}(P)\), let \(\mathcal D^+\) be the finite set of demanded exposure events \((i,a)\) for which the endpoint construction requires \(z_i(a)=1\), and let \(\mathcal D^0\) be the finite set of demanded zero-exposure events \((i,a)\) for which it requires \(z_i(a)=0\).  Graph-realizability requires binary hidden-edge variables \(x_e\) satisfying
\[
\sum_{e\in\mathcal C}B_{ie}x_e\le K_i\quad\text{for all }i,
\qquad
\sum_{e=\{i,j\}\in\mathcal C}x_ea_j\ge 1\quad\text{for all }(i,a)\in\mathcal D^+,
\qquad
\sum_{e=\{i,j\}\in\mathcal C}x_ea_j=0\quad\text{for all }(i,a)\in\mathcal D^0.
\]
The conjecture is that failure of this system, together with the observed conditional-mean equalities, is always witnessed by a violated finite certificate from the associated capacitated b-matching / set-covering polytope, including endpoint-incidence degree consumption and any odd-set or lifted cover inequalities needed for binary graph feasibility.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
No cited network-interference paper gives this finite compatibility certificate.  \citet{BelloniFangVolfovsky2022} search adaptively over local patterns on a known network, \citet{Egami2020} develops sensitivity analysis for unobserved networks, and \citet{YuAiroldiBorgsChayes2022} avoid local-network measurement for a total-effect target; none supplies a capacitated graph-completion certificate for a local direct-effect bound.  Classical results such as \citet{Edmonds1965} and \citet{Wolsey1975} are prior art for matching, cover, and lifting inequalities, so the novelty is not the certificate vocabulary by itself.  The proposed causal gap is the signed-demand reduction from a cellwise ADE endpoint to positive and zero hidden-exposure constraints, plus the interpretation of a violated polyhedral inequality as the exact reason a sensitivity endpoint is not generated by any locally feasible network completion.

\section{Sanity-check corollaries}
\begin{corollary}[Known-network collapse]\label{cor:known-network}
Under Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching}, if \(\mathcal C=\emptyset\) or \(K_i=0\) for all \(i\), then \(\mathfrak G(\mathcal L,\mathcal C,K)=\{\mathcal L\}\), \(R_i(G,A)=0\), and Theorem~\ref{thm:joint-lp-sharp} reduces to the usual exposure-mapping finite-population direct-effect calculation under a known graph.
\end{corollary}
Under Assumptions~\ref{ass:shared-completion} and \ref{ass:exposure-consistency}, the hidden exposure has only the value \(r=0\), so the target collapses to the known-exposure contrast because the sum over \(r\) has one term.

\begin{corollary}[No hidden-effect collapse]\label{cor:no-hidden-effect}
If Assumptions~\ref{ass:finite-randomized}--\ref{ass:law-matching} and Assumption~\ref{ass:no-hidden-effect} hold, then every feasible graph completion gives the same \(\theta_{\mathrm{ADE}}(s)\).  The joint no-hidden-effect identified set and the corresponding no-hidden-effect cellwise comparator coincide.
\end{corollary}
Under Assumption~\ref{ass:no-hidden-effect}, both \(R_i(G,A)\) and \(Z_i\) drop out of their respective response surfaces, so changing \(G\) or \(Q_i\) only relabels a nuisance state that has no effect on the direct-effect contrast; both models reduce to matching the same observed conditional-mean vector \(m(P)\).

\section{Proof-sketch route}
Theorem~\ref{thm:joint-lp-sharp} reduces to finite support and the classical sharpness argument for bounded missing potential outcomes: condition on a graph completion, write each observed conditional mean as a linear equality in the bounded latent outcomes \(Y_i(a,s,r)\), optimize the linear functional defining \(\theta_{\mathrm{ADE}}(s)\), and take the union over finitely many completions.  Conjecture~\ref{conj:cellwise-nonsharp} should be attacked first by a four-unit boundary example with hidden candidates \(\{1,3\}\) and \(\{2,3\}\), degree cap \(K_3=1\), and assignments where units 1 and 2 both demand a treated hidden neighbor through unit 3.  The cellwise endpoint can assign \(Q_1(1\mid 0,s)=Q_2(1\mid 0,s)=1\) in isolation, while no single binary edge vector can include both hidden edges under \(K_3=1\); enumerating the four candidate edge vectors then compares the resulting joint endpoint with \(\theta_{\mathrm{cell}}(s;Q,U)\).  Conjecture~\ref{conj:cut-certificate} is a finite integer/linear-programming duality question: project the capacitated incidence constraints \(Bx\le K\), the assignment-specific positive covering constraints, and the zero-exposure equalities onto exposure-event requirements, then identify the b-matching, cover, or odd-set inequalities that separate infeasible cellwise endpoints.  The two sanity corollaries are direct substitutions into the target formula and should be checked before any larger witness is trusted.

\section{Honest scope flags}
The LP sharpness theorem is labelled as a theorem because it is routine finite partial-identification algebra, not because it has been proved in this proposal.  The strict nonsharpness and cut-certificate statements are conjectures and are the real novelty kernel.  The proposal does not claim statistical inference, asymptotic coverage, or an efficient estimator; it is only about the population identified set.  The exact minimal number of units needed for strict containment is intentionally left open.  The most delicate modelling choice is the target's use of \(q_{i,s,r}(G)\) conditional on \(A_i=0\); Stage~0 may instead prefer a symmetric reference distribution over \(R_i\) conditional only on \(S_i=s\), but the shared-completion phenomenon should survive that convention.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft proposing shared hidden-edge graph-completion bounds for locally known network exposures; prior verdict: none.
\item v2 (revise) -- added missing unobserved-network comparators, separated the cellwise relaxation from true-graph consistency, and replaced the cut display with a capacitated-incidence certificate statement; prior verdict: REVISE.
\item v3 (revise) -- defined the cellwise target projection and control-arm reference weights, added Zhang--Mohan--Pearl model-uncertainty bounds as a close comparator, and anchored the strict-containment route with a four-unit capacity witness; prior verdict: REVISE.
\item v4 (revise) -- locked observable matching to the observed conditional-mean vector, restricted the no-hidden-effect cellwise comparator in the sanity corollary, and added zero-exposure certificate constraints plus classical matching / cover-inequality prior art; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Aronow and Samii(2017)]{AronowSamii2017}
Aronow, P. M. and Samii, C. (2017).
Estimating average causal effects under general interference, with application to a social network experiment.
\emph{The Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem[Belloni, Fang, and Volfovsky(2022)]{BelloniFangVolfovsky2022}
Belloni, A., Fang, F., and Volfovsky, A. (2022).
Neighborhood adaptive estimators for causal inference under network interference.
arXiv:2212.03683.

\bibitem[Bhattacharya, Malinsky, and Shpitser(2020)]{BhattacharyaMalinskyShpitser2020}
Bhattacharya, R., Malinsky, D., and Shpitser, I. (2020).
Causal inference under interference and network uncertainty.
\emph{Proceedings of the 35th Conference on Uncertainty in Artificial Intelligence}, PMLR 115, 1028--1038.

\bibitem[Egami(2020)]{Egami2020}
Egami, N. (2020).
Spillover effects in the presence of unobserved networks.
\emph{Political Analysis} 29(3), 287--316.

\bibitem[Edmonds(1965)]{Edmonds1965}
Edmonds, J. (1965).
Maximum matching and a polyhedron with 0,1-vertices.
\emph{Journal of Research of the National Bureau of Standards, Section B} 69B(1--2), 125--130.

\bibitem[Forastiere, Airoldi, and Mealli(2021)]{ForastiereAiroldiMealli2021}
Forastiere, L., Airoldi, E. M., and Mealli, F. (2021).
Identification and estimation of treatment and interference effects in observational studies on networks.
\emph{Journal of the American Statistical Association} 116(534), 901--918.

\bibitem[Gao, Harshaw, Sävje, and Wang(2026)]{GaoHarshawSavjeWang2026}
Gao, C., Harshaw, C., Sävje, F., and Wang, Y. (2026).
On the impossibility of specification testing of interference models based on exposure mappings.
arXiv:2605.09726.

\bibitem[Hudgens and Halloran(2008)]{HudgensHalloran2008}
Hudgens, M. G. and Halloran, M. E. (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.

\bibitem[Leung(2022)]{Leung2022}
Leung, M. P. (2022).
Causal inference under approximate neighborhood interference.
\emph{Econometrica} 90(1), 267--293.

\bibitem[Leung(2024)]{Leung2024Discussion}
Leung, M. P. (2024).
Discussion of ``Causal inference with misspecified exposure mappings: separating definitions and assumptions''.
\emph{Biometrika} 111(1), 17--20.

\bibitem[Li, Sussman, and Kolaczyk(2021)]{LiSussmanKolaczyk2021}
Li, W., Sussman, D. L., and Kolaczyk, E. D. (2021).
Causal inference under network interference with noise.
arXiv:2105.04518.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Sävje(2024)]{Savje2024}
Sävje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions and assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem[Sävje, Aronow, and Hudgens(2021)]{SavjeAronowHudgens2021}
Sävje, F., Aronow, P. M., and Hudgens, M. G. (2021).
Average treatment effects in the presence of unknown interference.
\emph{The Annals of Statistics} 49(2), 673--701.

\bibitem[Schröder, Oprescu, Feuerriegel, and Kallus(2026)]{SchroderOprescuFeuerriegelKallus2026}
Schröder, M., Oprescu, M., Feuerriegel, S., and Kallus, N. (2026).
Causal inference on networks under misspecified exposure mappings: A partial identification framework.
arXiv:2602.03459.

\bibitem[Weinstein and Nevo(2026)]{WeinsteinNevo2026}
Weinstein, B. and Nevo, D. (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.

\bibitem[Wolsey(1975)]{Wolsey1975}
Wolsey, L. A. (1975).
Faces for a linear inequality in 0--1 variables.
\emph{Mathematical Programming} 8, 165--178.

\bibitem[Yu, Airoldi, Borgs, and Chayes(2022)]{YuAiroldiBorgsChayes2022}
Yu, C. L., Airoldi, E. M., Borgs, C., and Chayes, J. T. (2022).
Estimating the total treatment effect in randomized experiments with unknown network structure.
\emph{Proceedings of the National Academy of Sciences} 119(44), e2208975119.

\bibitem[Zhang, Mohan, and Pearl(2023)]{ZhangMohanPearl2023}
Zhang, C., Mohan, K., and Pearl, J. (2023).
Causal inference under interference and model uncertainty.
\emph{Proceedings of the Second Conference on Causal Learning and Reasoning}, PMLR 213, 371--385.
\end{thebibliography}

\end{document}
