Fix \(K,m,u,\gamma,\alpha\) as in the statement. Put \(r=K-\gamma\), \(B=Z_\alpha\), \(C=C_\alpha\), \(n=m^\gamma\), and \(c=m^r\). Thus \(B\) has \(n\) cells, \(C\) has \(c\) cells, and \(nc=m^K\). The argument is invariant under relabeling the proxy coordinates, so it applies to every \(\alpha\in\mathcal A_\gamma\).

We first prove necessity. If \(\Delta_{K,m,u}(\gamma)<0\), Theorem \(\mathrm{thm:universal-rank-barrier}\) gives \(\operatorname{rank}M_\gamma(P,\alpha)<Q_{K,m,u}(\gamma)\) for every full-cell law \(P\), including every such law in \(\mathcal P_{\gamma,\alpha}\). Hence existence of a row-rank-attaining compatible law implies \(\Delta_{K,m,u}(\gamma)\ge0\).

For sufficiency, suppose \(\Delta_{K,m,u}(\gamma)\ge0\), equivalently \(D_{K,m}(\gamma)\ge2uc\). We construct the law of \((U,A,Z)\). Give \((A,B,C)\) the uniform law
\[P(A=a,B=b,C=x)=\frac{1}{2nc}.\]
Under the weighted-array bijection of Theorem \(\mathrm{thm:weighted-dimension}\), the orthogonal complement of the image of \(\mathcal H_\gamma(P)\), for the ordinary Euclidean pairing of arrays, is
\[\langle\mathbf 1_A\rangle\otimes\mathcal L_r,\qquad \mathcal L_r=\bigoplus_{\substack{S\subseteq[K]\\ |S|\le r}}\left(\bigotimes_{i\in S}E_i^0\right)\otimes\left(\bigotimes_{i\notin S}\langle\mathbf 1_i\rangle\right).\]
Indeed, the theorem puts all treatment-contrast tensors and all treatment-constant proxy interactions of order greater than \(r\) in the image, leaving exactly the displayed treatment-constant interactions of order at most \(r\). Define
\[\mathcal N=\left\{\rho\in\mathcal L_r:\sum_b\rho(b,x)=0\text{ for every cell }x\text{ of }C\right\}.\]
Every function of \(C\) belongs to \(\mathcal L_r\), because it is a sum of interactions supported on the \(r\) complement coordinates. The map \(\rho\mapsto n^{-1}\sum_b\rho(b,\cdot)\) therefore maps \(\mathcal L_r\) onto the \(c\)-dimensional space of functions of \(C\), and its kernel is \(\mathcal N\). Since the full \((A,Z)\)-array space has dimension \(2nc\), Theorem \(\mathrm{thm:weighted-dimension}\) gives
\[\dim\mathcal L_r=2nc-h_{K,m}(\gamma),\qquad \dim\mathcal N=2nc-h_{K,m}(\gamma)-c=2nc-D_{K,m}(\gamma).\]
For each cell \(x\) of \(C\), set
\[V_x=\left\{v\in\mathbb R^n:\sum_bv_b=0\right\}.\]
Then \(\mathcal N\subseteq\bigoplus_xV_x\), with \(\dim V_x=n-1\). Permuting the \(m\) levels separately in the \(r\) coordinates of \(C\) preserves interaction order and \(\mathcal N\), acts through block isomorphisms, and is transitive on the \(c\) cells of \(C\).

Because \(\dim\mathcal L_r\ge c\),
\[D_{K,m}(\gamma)=2nc-\dim\mathcal L_r+c\le2nc.\]
Together with \(D_{K,m}(\gamma)\ge2uc\), this implies \(u\le n\). Let
\[e=\max\{0,2u-n-1\},\qquad d=n-1.\]
Then \(0\le e\le d\). If \(e=0\), the inclusion \(\mathcal N\subseteq\bigoplus_xV_x\) yields \(\dim\mathcal N\le cd=c(d-e)\). If \(e>0\), then \(e=2u-n-1\), and the slack inequality yields
\[\dim\mathcal N=2nc-D_{K,m}(\gamma)\le2c(n-u)=c(n-1-e)=c(d-e).\]
Lemma \(\mathrm{lem:transitive-block-avoidance}\) consequently supplies subspaces \(E_x\subseteq V_x\), each of dimension \(e\), such that
\[\mathcal N\cap\bigoplus_xE_x=\{0\}.\]

For each \(x\), put
\[J_x=\langle\mathbf 1_B\rangle\oplus E_x,\qquad j=\dim J_x=e+1=\max\{1,2u-n\}.\]
The inequalities \(1\le j\le u\le n\) hold. There are \(u\)-dimensional subspaces \(L_{0x},L_{1x}\subseteq\mathbb R^n\) containing \(\mathbf 1_B\) and satisfying \(L_{0x}\cap L_{1x}=J_x\). To construct them, choose in \(\mathbb R^n/J_x\) two subspaces of dimension \(u-j\) having zero intersection, then lift and adjoin \(J_x\). Such a pair exists because
\[2(u-j)\le n-j.\]
When \(2u\le n+1\), this is \(2(u-1)\le n-1\); when \(2u>n+1\), equality holds because \(j=2u-n\). By Lemma \(\mathrm{lem:positive-stochastic-subspace-realization}\), for every \(a\in\{0,1\}\) and \(x\) there is a strictly positive row-stochastic \(n\)-by-\(u\) matrix \(\Pi_{a,x}\) of column rank \(u\) with \(\operatorname{col}(\Pi_{a,x})=L_{ax}\). Define
\[P(U=v\mid A=a,B=b,C=x)=\Pi_{a,x}(b,v).\]
Every cell of \((U,A,Z)\) now has positive probability, so Assumption \(\mathrm{ass:full-cell-support}\) holds.

We next prove injectivity. Let \(g\in\mathcal G_\alpha(P)\) satisfy \(\mathsf T_{P,\alpha}g=0\), and define
\[R_g(a,b,x)=\mathbb E_P\{g(U,A,C)\mid A=a,B=b,C=x\}=\sum_v\Pi_{a,x}(b,v)g(v,a,x).\]
For every \(s\in\mathcal H_\gamma(P)\), the weighted-array identity gives
\[0=\mathbb E_P\{s(A,Z)g(U,A,C)\}=\sum_{a,b,x}q_s(a,b,x)R_g(a,b,x).\]
Thus \(R_g\) belongs to the orthogonal complement displayed above. Consequently there is \(\rho\in\mathcal L_r\) such that \(R_g(a,b,x)=\rho(b,x)\), independently of \(a\). The pairing also vanishes against every \(s=f(C)\in L_P^2(C)\). By the uniform law and iterated expectation,
\[0=\mathbb E_P\{f(C)g(U,A,C)\}=\frac1c\sum_x f(x)\left\{\frac1n\sum_b\rho(b,x)\right\}\]
for every \(f\). Hence \(\rho\in\mathcal N\). For every \(a,x\), the slice \(R_g(a,\cdot,x)\) lies in \(\operatorname{col}(\Pi_{a,x})=L_{ax}\). The two treatment-arm slices both equal \(\rho(\cdot,x)\), so
\[\rho(\cdot,x)\in L_{0x}\cap L_{1x}=\langle\mathbf1_B\rangle\oplus E_x.\]
Because \(\rho\in\mathcal N\), this slice has coordinate sum zero; hence \(\rho(\cdot,x)\in E_x\). It follows that \(\rho\in\mathcal N\cap\bigoplus_xE_x=\{0\}\), and therefore \(R_g=0\). Since each \(\Pi_{a,x}\) has column rank \(u\), \(\Pi_{a,x}g(\cdot,a,x)=0\) implies \(g(\cdot,a,x)=0\) for every \(a,x\). Thus \(g=0\), and \(\mathsf T_{P,\alpha}\) is injective. Theorem \(\mathrm{thm:weighted-dimension}\) gives \(\dim\mathcal G_\alpha(P)=Q_{K,m,u}(\gamma)\), so equivalently
\[\operatorname{rank}M_\gamma(P,\alpha)=Q_{K,m,u}(\gamma).\]

It remains to complete the full-data law and establish genericity. Take \(Y(0)\), \(Y(1)\), and \(W\) to be mutually independent nondegenerate Bernoulli variables, independent of \((U,A,Z)\), and set \(Y=Y(A)\). Consistency holds by construction. The independence of the completion gives \(Y(a)\perp A\mid(U,C)\), \(Y\perp Z_\alpha\mid(A,U,C)\), and \(W\perp(A,Z_\alpha)\mid(U,C)\). Hence the completed law lies in \(\mathcal P_{\gamma,\alpha}\).

Fix cell-indicator bases of \(\mathcal G_\alpha(P)\) and \(L_P^2(C)\), and fix a basis \((q_j)_j\) of the law-independent weighted-array image of \(\mathcal H_\gamma(P)\) in Theorem \(\mathrm{thm:weighted-dimension}\). On the positive table parameter space use \(s_j=q_j/p_{AZ}\) for the corresponding basis of \(\mathcal H_\gamma(P)\). The entries of the resulting pairing matrix are rational functions of the conditional-table coordinates, with denominators that are products of positive cell probabilities. After clearing these denominators, every \(Q_{K,m,u}(\gamma)\)-minor has a polynomial numerator. At the law just constructed at least one maximal minor is nonzero. Therefore the common zero set of all maximal-minor numerators is a proper real algebraic subset of the compatible factor-table parameter space in Definition \(\mathrm{def:compatible-minor-handle}\). The minors depend only on the law of \((U,A,Z)\), while the independent completion above witnesses compatibility. The complement of the failure set is consequently nonempty and relative Zariski open. A proper real algebraic subset has empty Euclidean interior and Lebesgue measure zero in the free factor-table coordinates, so this complement is Euclidean dense and has full Lebesgue measure in the positive compatible parameter space. This proves sufficiency, genericity, and, together with the necessity argument, the asserted equivalence.