Fix \(K,m,u,\gamma,\alpha\) as in the statement. Put \(r=K-\gamma\), \(B=Z_\alpha\), \(C=C_\alpha\), \(n=m^\gamma\), and \(c=m^r\). Thus \(B\) has \(n\) cells, \(C\) has \(c\) cells, and \(nc=m^K\). The argument below is invariant under relabeling proxy coordinates and therefore applies to every \(\alpha\in\mathcal A_\gamma\).

We first prove necessity. If \(\Delta_{K,m,u}(\gamma)<0\), Theorem \(\mathrm{thm:universal-rank-barrier}\) gives \(\operatorname{rank}M_\gamma(P,\alpha)<Q_{K,m,u}(\gamma)\) for every full-cell law \(P\), including every such law in \(\mathcal P_{\gamma,\alpha}\). Hence existence of a row-rank-attaining compatible law implies \(\Delta_{K,m,u}(\gamma)\ge0\).

For sufficiency, assume \(\Delta_{K,m,u}(\gamma)\ge0\), equivalently \(D_{K,m}(\gamma)\ge2uc\). We first construct the law of \((U,A,Z)\). Give \((A,B,C)\) the uniform law
\[P(A=a,B=b,C=x)=\frac{1}{2nc}.\]
Let \(\mathcal H_0\) denote the law-independent weighted-array image of \(\mathcal H_\gamma(P)\) supplied by Theorem \(\mathrm{thm:weighted-dimension}\). Under the uniform law, the weighted-array image of \(L_P^2(C)\) is, up to the common positive scalar \((2nc)^{-1}\), the subspace
\[\mathcal R=\{q:q(a,b,x)=f(x)\text{ for some function }f\}.\]
Theorem \(\mathrm{thm:weighted-dimension}\) also gives \(\mathcal H_0\cap\mathcal R=\{0\}\). Define the Euclidean orthogonal complement
\[\mathcal N=(\mathcal H_0\oplus\mathcal R)^\perp\]
in the \((A,B,C)\)-array space. Since that ambient space has dimension \(2nc\), the same theorem yields
\[\dim\mathcal N=2nc-D_{K,m}(\gamma).\]
Moreover, the tensor decomposition in that theorem shows that
\[\mathcal H_0^\perp=\langle\mathbf1_A\rangle\otimes\mathcal L_r,\qquad \mathcal L_r=\bigoplus_{\substack{S\subseteq[K]\\|S|\le r}}\left(\bigotimes_{i\in S}E_i^0\right)\otimes\left(\bigotimes_{i\notin S}\langle\mathbf1_i\rangle\right).\]
Consequently, every \(q\in\mathcal N\) has the form \(q(a,b,x)=\rho(b,x)\), independently of \(a\). Orthogonality to \(\mathcal R\) says for every cell \(x\) that
\[0=\sum_{a,b}q(a,b,x)=2\sum_b\rho(b,x).\]
For each block \(y=(a,x)\in\{0,1\}\times\operatorname{supp}(C)\), set
\[V_y=\left\{v\in\mathbb R^n:\sum_bv_b=0\right\}.\]
Then \(\dim V_y=n-1\) and \(\mathcal N\subseteq\bigoplus_yV_y\). The group generated by swapping the two treatment levels and by independently permuting the \(m\) levels in each coordinate of \(C\) preserves both \(\mathcal H_0\) and \(\mathcal R\), hence preserves \(\mathcal N\), and acts transitively on the \(2c\) blocks through block isomorphisms.

The supply space is a subspace of the \(2nc\)-dimensional ambient array space, so Theorem \(\mathrm{thm:weighted-dimension}\) gives \(D_{K,m}(\gamma)\le2nc\). Combining this with \(D_{K,m}(\gamma)\ge2uc\) gives \(u\le n\). Put \(d=n-1\) and \(e=u-1\), so \(0\le e\le d\). The slack inequality also gives
\[\dim\mathcal N=2nc-D_{K,m}(\gamma)\le2c(n-u)=2c(d-e).\]
Lemma \(\mathrm{lem:transitive-block-avoidance}\), applied to the \(2c\) blocks \((V_y)_y\), therefore supplies subspaces \(F_y\subseteq V_y\), each of dimension \(u-1\), such that
\[\mathcal N\cap\bigoplus_yF_y=\{0\}.\]
For every \(y=(a,x)\), define
\[L_y=\langle\mathbf1_B\rangle\oplus F_y.\]
This is a \(u\)-dimensional subspace of \(\mathbb R^n\) containing the all-ones vector. Lemma \(\mathrm{lem:positive-stochastic-subspace-realization}\) gives a strictly positive row-stochastic \(n\)-by-\(u\) matrix \(\Pi_y\) of column rank \(u\) with \(\operatorname{col}(\Pi_y)=L_y\). Define
\[P(U=v\mid A=a,B=b,C=x)=\Pi_{(a,x)}(b,v).\]
Uniform positivity of \((A,B,C)\) and strict positivity of every \(\Pi_y\) imply \(P(U=v,A=a,Z=z)>0\) at every cell, so Assumption \(\mathrm{ass:full-cell-support}\) holds.

We now verify injectivity of the pairing. Let \(g\in\mathcal G_\alpha(P)\) satisfy \(\mathsf T_{P,\alpha}g=0\), and define
\[R_g(a,b,x)=\mathbb E_P\{g(U,A,C)\mid A=a,B=b,C=x\}=\sum_v\Pi_{(a,x)}(b,v)g(v,a,x).\]
For any \(s\in\mathcal S_{\gamma,\alpha}(P)\), the weighted-array identity and the definition of the uniform conditional tables give
\[0=\mathbb E_P\{s(A,Z)g(U,A,C)\}=\sum_{a,b,x}q_s(a,b,x)R_g(a,b,x).\]
As \(s\) ranges over \(\mathcal H_\gamma(P)+L_P^2(C)\), its weighted arrays range over \(\mathcal H_0\oplus\mathcal R\). Hence \(R_g\in\mathcal N\). On the other hand, for every block \(y=(a,x)\),
\[R_g(a,\cdot,x)=\Pi_y g(\cdot,a,x)\in L_y.\]
Membership in \(\mathcal N\) makes this slice coordinate-sum zero, while \(L_y=\langle\mathbf1_B\rangle\oplus F_y\) and \(F_y\subseteq V_y\); therefore \(R_g(a,\cdot,x)\in F_y\). It follows that
\[R_g\in\mathcal N\cap\bigoplus_yF_y=\{0\}.\]
Because every \(\Pi_y\) has column rank \(u\), the equality \(\Pi_y g(\cdot,a,x)=0\) implies \(g(\cdot,a,x)=0\) for every \(a,x\). Thus \(g=0\), so \(\mathsf T_{P,\alpha}\) is injective. Theorem \(\mathrm{thm:weighted-dimension}\) gives \(\dim\mathcal G_\alpha(P)=Q_{K,m,u}(\gamma)\), and hence
\[\operatorname{rank}M_\gamma(P,\alpha)=Q_{K,m,u}(\gamma).\]

It remains to complete the full-data law and prove genericity. Take \(Y(0)\), \(Y(1)\), and \(W\) to be mutually independent nondegenerate Bernoulli variables, independent of \((U,A,Z)\), and set \(Y=Y(A)\). Assumption \(\mathrm{ass:consistency}\) holds by construction. Independence gives \(Y(a)\perp A\mid(U,C)\), \(Y\perp Z_\alpha\mid(A,U,C)\), and \(W\perp(A,Z_\alpha)\mid(U,C)\). Thus Assumptions \(\mathrm{ass:selected-latent-ignorability}\), \(\mathrm{ass:selected-treatment-proxy-exclusion}\), and \(\mathrm{ass:selected-outcome-proxy-exclusion}\) hold, so the completed law belongs to \(\mathcal P_{\gamma,\alpha}\).

For genericity, fix cell-indicator bases of \(\mathcal G_\alpha(P)\) and \(L_P^2(C)\), and fix a basis \((q_j)_j\) of the law-independent weighted-array space \(\mathcal H_0\). At an arbitrary positive table let \(s_j=q_j/p_{AZ}\); these functions form the corresponding basis of \(\mathcal H_\gamma(P)\). In the free positive factor-table coordinates of Definition \(\mathrm{def:compatible-minor-handle}\), entries of the resulting pairing matrix are rational functions whose denominators are products of positive cell probabilities. After those denominators are cleared, every \(Q_{K,m,u}(\gamma)\)-minor has a polynomial numerator. At the compatible law just constructed, row rank is \(Q_{K,m,u}(\gamma)\), so at least one such numerator is nonzero there and is therefore not the zero polynomial. The common zero set of all maximal-minor numerators is consequently a proper real algebraic subset of the compatible parameter space, and its complement is nonempty and relative Zariski open. To verify the measure and density claims directly, a nonzero polynomial on \(\mathbb R^d\) has a Lebesgue-null zero set: induct on \(d\), write the polynomial as a polynomial in the last coordinate, use the induction hypothesis for the set on which all coefficient polynomials vanish, and use finiteness of the remaining one-dimensional root fibers together with Fubini's theorem. Its zero set therefore cannot contain a nonempty Euclidean open set. Since the rank-failure locus is contained in the zero set of the one maximal-minor numerator that is not identically zero, it has Lebesgue measure zero and empty relative interior in the free positive factor-table coordinates. Thus the row-rank-attaining locus is Euclidean dense and has full Lebesgue measure in the positive compatible parameter space. Together with the necessity argument, this proves the equivalence and every genericity assertion.