Fix \(\alpha\in\mathcal A_\gamma\). We first prove the general sufficient assertion. Put \(r=m^\gamma\) and \(n=m^{K-\gamma}\). Since \(h_{K,m}(\gamma)\ge m^K=rn\), the condition \(2u\le r+1\) gives
\[D_{K,m}(\gamma)=h_{K,m}(\gamma)+n\ge n(r+1)\ge2un=Q_{K,m,u}(\gamma).\]
Therefore \(\Delta_{K,m,u}(\gamma)\ge0\).

We construct a compatible law attaining equality in the row-rank requirement. Give \((A,Z)\) the uniform distribution on its \(2m^K\) cells. Identify the function space on the \(r\) values of \(Z_\alpha\) with \(\mathbb R^r\), write \(\mathbf 1\) for the constant vector, and set \(F=\mathbf 1^\perp\). The inequality \(2u\le r+1\) is equivalent to \(2(u-1)\le r-1=\dim F\). Hence there are subspaces \(V_0,V_1\subseteq F\), each of dimension \(u-1\), with \(V_0\cap V_1=\{0\}\). For \(a\in\{0,1\}\), define
\[L_a=\langle\mathbf 1\rangle\oplus V_a.\]
Then \(\dim L_a=u\) and \(L_0\cap L_1=\langle\mathbf 1\rangle\).

Suppose first that \(u>1\), and choose a basis \(f_{a,1},\ldots,f_{a,u-1}\) of \(V_a\) for each treatment arm. Uniformly in \(c\in\operatorname{supp}(C_\alpha)\), define
\[\begin{aligned}P(U=v\mid A=a,Z_\alpha=x,C_\alpha=c)&=u^{-1}+\varepsilon f_{a,v}(x),&&1\le v<u,\\P(U=u\mid A=a,Z_\alpha=x,C_\alpha=c)&=u^{-1}-\varepsilon\sum_{v=1}^{u-1}f_{a,v}(x).\end{aligned}\]
Because only finitely many entries occur, all entries are strictly positive for sufficiently small \(\varepsilon>0\); the displayed entries sum to one at every \((a,x,c)\). If \(u=1\), use the unique conditional probability one. For each \((a,c)\), the \(u\) column vectors
\[x\longmapsto P(U=v\mid A=a,Z_\alpha=x,C_\alpha=c),\qquad v\in\mathcal U,\]
are linearly independent and span \(L_a\): their sum is \(\mathbf 1\), and their deviations from their common constant part span \(V_a\). Together with the uniform \((A,Z)\) marginal, these conditional tables define a joint law having positive probability at every \((v,a,z)\) cell.

For \(g\in\mathcal G_\alpha(P)=L_P^2(U,A,C_\alpha)\), define
\[R_g(a,x,c)=\mathbb E_P\{g(U,A,C_\alpha)\mid A=a,Z_\alpha=x,C_\alpha=c\}.\]
For fixed \((a,c)\), the linear map from \((g(v,a,c))_{v\in\mathcal U}\) to \((R_g(a,x,c))_x\) has precisely the preceding \(u\) conditional-probability columns. It is therefore injective, with range \(L_a\).

Assume \(\mathsf T_{P,\alpha}g=0\). By Theorem \(\mathrm{thm:weighted-dimension}\), the weighted arrays corresponding to \(\mathcal H_\gamma(P)\) contain \(E_A^0\otimes\mathbb R^{\mathcal Z}\). Since the \((A,Z)\) marginal is uniform, the supply consequently contains every treatment contrast with an arbitrary proxy-coordinate function. Orthogonality of \(g\) to these contrasts, followed by conditioning on \((A,Z)\), yields
\[R_g(0,x,c)=R_g(1,x,c)\qquad\text{for every }(x,c).\]
For each fixed \(c\), this common vector lies in \(L_0\cap L_1=\langle\mathbf 1\rangle\). Thus there is a scalar \(b(c)\) such that \(R_g(a,x,c)=b(c)\) for every \((a,x)\). The supply also contains \(L_P^2(C_\alpha)\). Consequently, for every \(f\in L_P^2(C_\alpha)\),
\[0=\mathbb E_P\{f(C_\alpha)g(U,A,C_\alpha)\}=\mathbb E_P\{f(C_\alpha)R_g(A,Z_\alpha,C_\alpha)\}=\mathbb E_P\{f(C_\alpha)b(C_\alpha)\}.\]
Taking \(f=b\) gives \(b=0\) almost surely. Full support of \(C_\alpha\) makes this a cellwise conclusion. Hence \(R_g=0\), and the blockwise injectivity just proved implies \(g=0\). Therefore \(\mathsf T_{P,\alpha}\) is injective and
\[\operatorname{rank}M_\gamma(P,\alpha)=\dim\mathcal G_\alpha(P)=Q_{K,m,u}(\gamma).\]

We next prove the exact endpoint assertion. If \(\gamma=K\), then \(\alpha=[K]\), \(C_\alpha\) is constant, and the only conditional-mean restriction in the definition of \(\mathcal H_K(P)\) is \(\mathbb E_P d=0\). Therefore
\[\mathcal S_{K,[K]}(P)=\mathcal H_K(P)+L_P^2(C_{[K]})=L_P^2(A,Z).\]
For any \(g\in L_P^2(U,A)\), vanishing of \(\mathsf T_{P,[K]}g\) is now equivalent to
\[\mathbb E_P\{g(U,A)\mid A=a,Z=z\}=0\qquad\text{for every }(a,z),\]
because the supply contains every cell-indicator function of \((A,Z)\) and all cells have positive probability. For each arm \(a\), let \(\Pi_a\) be the \(m^K\)-by-\(u\) matrix
\[\Pi_a(z,v)=P(U=v\mid A=a,Z=z).\]
Writing \(g_a=(g(v,a))_{v\in\mathcal U}\), the preceding conditional means form the vector \(\Pi_a g_a\). It follows that the pairing is injective if and only if both \(\Pi_0\) and \(\Pi_1\) have column rank \(u\). Necessarily \(u\le m^K\).

Conversely, suppose \(u\le m^K\), put \(N=m^K\), and identify functions of \(z\) with \(\mathbb R^N\). For each arm separately, choose linearly independent vectors \(f_{a,1},\ldots,f_{a,u-1}\in\mathbf 1^\perp\); this is possible because \(u-1\le N-1\). Use the same positive perturbation construction as above, now with \(x=z\), to define a strictly positive row-stochastic matrix \(\Pi_a\) whose columns span
\[\langle\mathbf 1\rangle\oplus\operatorname{span}\{f_{a,1},\ldots,f_{a,u-1}\}.\]
Each \(\Pi_a\) has column rank \(u\), so the blockwise criterion proves injectivity. Thus compatible attainment holds exactly when \(u\le m^K\). Moreover, the binomial identity gives
\[\begin{aligned}h_{K,m}(K)&=m^K+\sum_{j=1}^K\binom Kj(m-1)^j=2m^K-1,\\D_{K,m}(K)&=2m^K,\qquad Q_{K,m,u}(K)=2u,\\\Delta_{K,m,u}(K)&=2(m^K-u).\end{aligned}\]
Hence \(u\le m^K\) is equivalent to \(\Delta_{K,m,u}(K)\ge0\). The general sufficient condition at this endpoint is only \(2u\le m^K+1\), so the exact endpoint argument adds every integer \(u\) with \((m^K+1)/2<u\le m^K\).

Both constructions so far specify only the positive law of \((U,A,Z)\). Complete either construction by taking \(Y(0)=Y(1)=Y=W=0\) almost surely. Assumption \(\mathrm{ass:consistency}\) holds, and Assumptions \(\mathrm{ass:selected-latent-ignorability}\), \(\mathrm{ass:selected-treatment-proxy-exclusion}\), and \(\mathrm{ass:selected-outcome-proxy-exclusion}\) hold because the variables on the left sides of their conditional-independence assertions are constant. Thus each constructed law belongs to \(\mathcal P_{\gamma,\alpha}\). The same constant completion is available for every strictly positive \((U,A,Z)\) table and does not alter the pairing matrix.

It remains to prove genericity. Fix the weighted-array basis displayed in Theorem \(\mathrm{thm:weighted-dimension}\), append a fixed cell-indicator basis for \(L_P^2(C_\alpha)\), and use the cell-indicator basis of \(L_P^2(U,A,C_\alpha)\). A weighted-array basis element \(q\) corresponds to the supply function \(q(a,z)/p_{AZ}(a,z)\). Hence every entry of the resulting pairing matrix is a rational function of the positive joint-cell probabilities, and its denominators are products of positive marginal cells \(p_{AZ}(a,z)\). After clearing these denominators, every maximal minor has a polynomial numerator. At any one of the constructed laws, some maximal minor is nonzero, so the corresponding numerator polynomial is not identically zero on the affine simplex. Every rank-deficient table lies in the zero set of that polynomial. The zero set of a nonzero real polynomial has empty relative Euclidean interior: this follows by induction on the number of affine coordinates, since a univariate polynomial vanishing on an interval is identically zero and the coefficients in the last coordinate are polynomials in the remaining coordinates. Therefore the complement of the chosen zero set is relative Zariski open and Euclidean dense. It is contained in the full-row-rank locus; the latter is itself relative Zariski open because it is the union of the nonvanishing sets of all maximal-minor numerators. Thus the full-row-rank locus is nonempty, relative Zariski open, and Euclidean dense. The constant completion establishes the same conclusion on the compatible completion parameter space. This proves every assertion.