Fix \(\alpha\in\mathcal A_\gamma\), and write \(r=m^\gamma\) and \(n=m^{K-\gamma}\). Since \(h_{K,m}(\gamma)\ge m^K=rn\),
\[D_{K,m}(\gamma)=h_{K,m}(\gamma)+n\ge n(r+1)\ge2un=Q_{K,m,u}(\gamma),\]
where the second inequality is the assumed condition \(2u\le r+1\). Thus \(\Delta_{K,m,u}(\gamma)\ge0\).

We now construct a full-rank compatible law. Give \((A,Z)\) the uniform distribution on its \(2m^K\) cells. Identify the real function space on the \(r\) values of \(Z_\alpha\) with \(\mathbb R^r\), let \(\mathbf 1\) be its constant vector, and let \(F=\mathbf 1^\perp\), so \(\dim F=r-1\). The inequality \(2u\le r+1\) is equivalent to \(2(u-1)\le r-1\). We may therefore choose subspaces \(V_0,V_1\subseteq F\), each of dimension \(u-1\), such that \(V_0\cap V_1=\{0\}\). Put
\[L_a=\langle\mathbf 1\rangle\oplus V_a,\qquad a\in\{0,1\}.\]
Then \(\dim L_a=u\) and \(L_0\cap L_1=\langle\mathbf 1\rangle\).

For each \(a\), choose a basis \(f_{a,1},\ldots,f_{a,u-1}\) of \(V_a\). When \(u>1\), define conditional probabilities, uniformly over values \(c\) of \(C_\alpha\), by
\[\begin{aligned}P(U=v\mid A=a,Z_\alpha=x,C_\alpha=c)&=u^{-1}+\varepsilon f_{a,v}(x),&&1\le v<u,\\P(U=u\mid A=a,Z_\alpha=x,C_\alpha=c)&=u^{-1}-\varepsilon\sum_{v=1}^{u-1}f_{a,v}(x).\end{aligned}\]
For sufficiently small \(\varepsilon>0\), all these finitely many probabilities are strictly positive and they sum to one. When \(u=1\), take the unique conditional probability to be one. For each \((a,c)\), the \(u\) column vectors \(x\mapsto P(U=v\mid a,x,c)\) are linearly independent and span \(L_a\): their sum is \(\mathbf 1\), while their deviations from the constant vector span \(V_a\). Together with the uniform \((A,Z)\) marginal, these conditional probabilities define a joint law with positive mass on every \((u,a,z)\) cell.

For \(g\in L_P^2(U,A,C_\alpha)\), set
\[R_g(a,x,c)=\mathbb E_P\{g(U,A,C_\alpha)\mid A=a,Z_\alpha=x,C_\alpha=c\}.\]
On each block \((a,c)\), the map from the \(u\) values \(g(v,a,c)\) to the vector \(R_g(a,\cdot,c)\) has the preceding independent conditional-probability columns. It is therefore injective and has range \(L_a\).

Suppose \(\mathsf T_{P,\alpha}g=0\). Because \(p_{AZ}\) is constant, the weighted-array decomposition in the weighted-dimension theorem shows that \(\mathcal H_\gamma(P)\), and hence the supply space, contains every function whose treatment coordinate lies in \(E_A^0\) and whose proxy coordinate is arbitrary. Orthogonality of \(g\) to all those supply functions is, after conditioning on \((A,Z)\), equivalent to
\[R_g(0,x,c)=R_g(1,x,c)\qquad\text{for every }(x,c).\]
For fixed \(c\), this common vector belongs to \(L_0\cap L_1=\langle\mathbf 1\rangle\); hence it equals a scalar \(b(c)\) independent of \(a\) and \(x\). The supply space also contains all functions of \(C_\alpha\). Orthogonality to those functions gives
\[0=\mathbb E_P\{f(C_\alpha)R_g(A,Z_\alpha,C_\alpha)\}=\mathbb E_P\{f(C_\alpha)b(C_\alpha)\}\]
for every \(f\in L_P^2(C_\alpha)\). Taking \(f=b\) yields \(b=0\). Thus \(R_g=0\), and blockwise injectivity implies \(g=0\). The pairing map is injective, so its matrix has row rank \(Q_{K,m,u}(\gamma)\).

Complete this positive joint law to a full-data law by taking \(Y(0)=Y(1)=Y=W=0\) almost surely. Consistency holds, and the latent-ignorability and both proxy-exclusion conditions hold because the variables on the left sides of those conditions are constant. Hence the completed law belongs to \(\mathcal P_{\gamma,\alpha}\).

Finally, fix bases of the weighted array space displayed in the weighted-dimension theorem and of \(L_P^2(C_\alpha)\). The corresponding supply functions are obtained by dividing the fixed weighted arrays by the positive marginal cells \(p_{AZ}(a,z)\). Entries of the pairing matrix are consequently rational functions of the positive joint-cell probabilities, with products of marginal cells as denominators. Every maximal minor has a polynomial numerator after clearing those denominators. At the constructed positive law, at least one such minor is nonzero, so its numerator polynomial is not identically zero. Every rank-deficient positive table lies in its zero set. A nonzero real polynomial has zero set with empty Euclidean interior, so the complement is nonempty, relatively Zariski open, and Euclidean dense in the positive table simplex. The constant completion above is available for every positive \((U,A,Z)\) table and does not change the pairing matrix, which proves the final claim.