For \(S\subseteq I\), let \(\pi_S\) be block projection and put \(\rho(S)=\dim\pi_S(N)\). The function \(\rho\) is a normalized, monotone, submodular rank function. The fractional-cover inequality for such a projection-rank function states that if a finite family \((S_\ell)_\ell\) covers every block exactly \(k\) times, then
\[
\sum_\ell\rho(S_\ell)\ge k\rho(I).
\]
For completeness, order the blocks and write each projection rank as a sum of successive dimension increments. Submodularity says that conditioning an increment on more preceding blocks can only decrease it. Assign each occurrence of a block in the cover its corresponding increment; because every block occurs \(k\) times, comparison with the increments along the full ordering gives the displayed inequality after summation.

Apply this inequality to the orbit of a fixed \(S\) under the finite permutation group induced on \(I\). Transitivity implies that every block occurs in exactly \(|G||S|/c\) orbit members, counted with multiplicity, while invariance of \(N\) gives \(\rho(gS)=\rho(S)\). Hence
\[
\rho(S)\ge\frac{|S|}{c}\dim N.
\]
For \(J\subseteq I\), let \(N_J=N\cap\bigoplus_{x\in J}V_x\). Since \(N_J\) is the kernel of \(\pi_{I\setminus J}|_N\),
\[
\dim N_J=\dim N-\rho(I\setminus J)\le\frac{|J|}{c}\dim N\le |J|(d-e).
\]

Consider the product Grassmannian \(\mathfrak G=\prod_{x\in I}\operatorname{Gr}(e,V_x)\), of dimension \(ce(d-e)\). For each nonempty \(J\subseteq I\), stratify the projective vectors \([v]\in\mathbb P(N_J)\) by requiring their block support to be exactly \(J\). This stratum has dimension at most \(\dim N_J-1\). For a fixed such \([v]\), the requirement \(v_x\in E_x\) has codimension \(d-e\) in \(\operatorname{Gr}(e,V_x)\) for every \(x\in J\), because the subspaces containing a fixed line form \(\operatorname{Gr}(e-1,d-1)\). Thus the corresponding incidence stratum has dimension at most
\[
\dim\mathfrak G+\dim N_J-1-|J|(d-e)\le\dim\mathfrak G-1.
\]
There are only finitely many \(J\). The full incidence variety is projective over \(\mathfrak G\), so its image, the set of tuples having a nonzero intersection with \(N\), is Zariski closed. The preceding dimension bound makes that image proper. Any tuple in its complement has the asserted trivial intersection. The cases \(N=\{0\}\) or \(e=0\) are immediate and agree with the same conclusion.