% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=eid\_lp\_svar\_nonequiv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{eid\_lp\_svar\_nonequiv} / \texttt{v1}%
  \\ \large\textit{LP/Sign versus Non-Gaussian SVAR Support-Function Boundary}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies a partial-identification problem for structural impulse
responses when the observable population input consists of finite-order
LP/VAR response rows, the reduced-form innovation covariance, and the
reduced-form fourth cumulant tensor.  The target is the horizon vector
\(\theta=\psi_j(B)=(e_y^\transpose\Gamma_h b_j)_{h=0}^H\) for a labelled
structural shock \(j\).  The estimand-defining functional is the pair of
directional support functions \(h_{\mathrm{LP}}(w;P)\) and
\(h_{\mathrm{SVAR}}(w;P)\), computed by explicit finite polynomial programs
over rotations and, on the SVAR side, admissible fourth cumulants.  The main
result is conditional: under the user-approved quantitative margin assumption
\textup{A-quant-margin}, the LP support bound is a strict outer bound for the
non-Gaussian SVAR/sign support in every admissible report direction.  The
primitive claim that this strict margin follows generically from fourth
cumulant geometry is not proved here and is recorded as an open conjecture.
A two-shock planar specialization gives a closed-form witness: the gap is at
least \(\rho_w(1-\cos d_w)\) when the LP sign optimizer is not one of the
cumulant-diagonalizing angles.
\end{abstract}

\section{Introduction}
Local projections and VARs both report population impulse-response rows, and
the equivalence result of Plagborg-M{\o}ller and Wolf \cite{PlagborgMollerWolf2021}
justifies moving many second-moment identifying restrictions between the two
languages.  Non-Gaussian SVAR identification changes the object being
transported: the shock label is not only a response-sign convention, but a
property of one joint reduced-form innovation law whose fourth cumulant tensor
must be diagonalized by the same impact rotation.  The econometric question is
therefore whether an LP implementation that keeps only sign and zero response
restrictions remains sharp for the same non-Gaussian structural shock.

Before this note, the closest pieces were known separately.  LP/VAR
equivalence gives a common reduced-form impulse-response object under common
identifying restrictions.  Sign-restricted SVAR geometry gives rotation
inequalities for impact matrices.  Non-Gaussian SVAR identification uses higher
unconditional moments to choose, or at least restrict, the structural mixing
matrix.  What was missing is a population-level comparison between the LP/sign
relaxation and the non-Gaussian SVAR/sign set when the LP object does not impose
the common fourth-cumulant diagonalization restriction.

The new contribution is a support-function boundary, not a refutation of a
named published LP or SVAR estimator.  For every report
direction \(w\), the note writes \(h_{\mathrm{LP}}(w;P)\) and
\(h_{\mathrm{SVAR}}(w;P)\) as computable maps of the observed population
objects \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u)\).  It then proves
\(\mathcal R_{\mathrm{SVAR}}(P)\subseteq \mathcal R_{\mathrm{LP}}(P)\),
identifies exactly when the directional support gap is zero, and proves a
closed-form two-shock witness with a strictly positive gap.  This is useful for
formula design because it says when LP sign restrictions are a valid sharp
report for the same structural shock and when they are only a conservative
outer relaxation of the non-Gaussian SVAR object.

\paragraph{Motivating conjecture(s).}
\begin{conjecture}[Conjecture 1: primitive generic strict non-equivalence under fourth cumulants (NOT YET PROVED)]\label{conj:primitive-strict-gap}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:bounded-gap} and \ref{ass:generic-report}, suppose Assumption~\ref{ass:cumulant-matching} is not imposed on the LP/sign side and Assumption~\ref{ass:sign-zero} leaves a positive-dimensional feasible rotation component.  There exists a nonempty open semi-algebraic class \(\mathcal O_{\mathrm{prim}}\) of observable objects \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\), with nonempty \(\mathcal Q_{\mathrm{SVAR}}(P)\), such that for every \((P,w)\in\mathcal O_{\mathrm{prim}}\)
\[
\Delta_w(P)=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)>0.
\]
Moreover, the strict gap is generated by primitive separation between the LP support maximizers and the cumulant-diagonalizing locus:
\[
\inf_{Q\in\arg\max_{\mathcal Q_{\mathrm{LP}}(P)} w^\transpose\psi_j(Q)}
m_{\delta_4}(Q;P)>0,
\]
with the response-flat exceptional set removed by Assumption~\ref{ass:generic-report}.  Equivalently, Conjecture~1 asks to prove Assumption~\ref{ass:quant-margin} from the primitive fourth-cumulant geometry on an open class, not to assume it.
\end{conjecture}

\begin{conjecture}[Conjecture 2: closed-form two-shock witness (NOT YET PROVED)]\label{conj:two-shock-witness}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:bounded-gap}, \ref{ass:generic-report}, and \ref{ass:two-shock}, let \(Q(\varphi)\) be the planar impact rotation and let the LP/sign restrictions define an interval \(I_{\mathrm{LP}}\subset S^1\).  The non-Gaussian SVAR/sign set reduces to the nonempty finite subset \(I_{\mathrm{SVAR}}=I_{\mathrm{LP}}\cap\{\varphi_\star,\varphi_\star+\pi/2,\varphi_\star+\pi,\varphi_\star+3\pi/2\}\), where \(\varphi_\star\) diagonalizes \(K_u\).  Write the report objective as \(w^\transpose\psi_j(Q(\varphi))=a_w\cos\varphi+b_w\sin\varphi=\rho_w\cos(\varphi-\varphi_w)\), with response-row amplitude \(\rho_w=(a_w^2+b_w^2)^{1/2}>0\), and let \(d_w=\operatorname{dist}_{S^1}(\varphi_w,I_{\mathrm{SVAR}})\).  For a nonempty open set of \((\Gamma_0,\ldots,\Gamma_H,K_u,A,Z,w)\) in which \(\varphi_w\) is an interior LP/sign optimizer and \(\varphi_w\notin I_{\mathrm{SVAR}}\),
\[
\max_{\varphi\in I_{\mathrm{LP}}}w^\transpose\psi_j(Q(\varphi))
>
\max_{\varphi\in I_{\mathrm{SVAR}}}w^\transpose\psi_j(Q(\varphi)),
\]
with the auditable lower bound
\[
\max_{\varphi\in I_{\mathrm{LP}}}w^\transpose\psi_j(Q(\varphi))
-
\max_{\varphi\in I_{\mathrm{SVAR}}}w^\transpose\psi_j(Q(\varphi))
\ge \rho_w(1-\cos d_w)>0.
\]
\end{conjecture}

\section{Related work and positioning}
Jorda \cite{Jorda2005} introduced local projections as direct regressions for
impulse responses, which is why the observable rows \(\Gamma_h\) are treated
here as population objects.  Plagborg-M{\o}ller and Wolf
\cite{PlagborgMollerWolf2021} show that LPs and VARs estimate the same
population impulse responses when the same identifying restrictions are
imposed; the present note differs by comparing a sign-only LP relaxation with
an SVAR restriction that also uses fourth cumulants.  Montiel Olea and
Plagborg-M{\o}ller \cite{MontielOleaPlagborgMoller2021} and Montiel Olea,
Plagborg-M{\o}ller, Qian, and Wolf
\cite{MontielOleaPlagborgMollerQianWolf2024} study robust LP inference and
local VAR misspecification, motivating LP rows as useful empirical summaries
but not changing the population identified set.  Li, Plagborg-M{\o}ller, and
Wolf \cite{LiPlagborgMollerWolf2024} compare LP and VAR estimators across many
DGPs; their contrast is statistical rather than a fourth-cumulant
identified-set separation.

Rubio-Ramirez, Waggoner, and Zha \cite{RubioRamirezWaggonerZha2010} and Arias,
Rubio-Ramirez, and Waggoner \cite{AriasRubioRamirezWaggoner2018} give the
standard rotation geometry for sign and zero restrictions in SVARs.  Baumeister
and Hamilton \cite{BaumeisterHamilton2015} emphasize the sensitivity of
underidentified sign-restricted SVAR conclusions, which is one reason a
support-function boundary is the right population object.  Read
\cite{Read2022} supplies algorithms for sign and zero restrictions; this note
uses the same finite rotation-constraint language but adds a cumulant tensor
constraint.

Gourieroux, Monfort, and Renne \cite{GourierouxMonfortRenne2017} and Lanne,
Meitz, and Saikkonen \cite{LanneMeitzSaikkonen2017} identify non-Gaussian SVAR
mixing matrices using independent components.  Guay \cite{Guay2021} gives
rank-style identification conditions from higher unconditional moments, which
is the closest moment-identification ingredient to the tensor diagonalization
used below.  Lanne and Luoto \cite{LanneLuoto2021} study GMM estimation of
non-Gaussian SVARs, relevant as an estimation counterpart but not as a
population LP/SVAR equivalence result.  Drautzburg and Wright
\cite{DrautzburgWright2023} are closest in partial-identification spirit:
independence refines sign-restricted VAR sets, while the present note asks
when a sign-restricted LP set can be pasted into that same independence-based
shock law.  The comparison is deliberately one-sided.  No cited paper is
attributed the claim that a sign-only LP set is already the sharp set for a
labelled non-Gaussian SVAR shock; the theorem is framed instead as a positive
population bound and diagnostic for any workflow that wants to use LP sign
restrictions as a robustness report for such a shock.  Lanne, Liu, and Luoto
\cite{LanneLiuLuoto2026} relax independence
toward dependent non-Gaussian shocks, underscoring that the common shock-law
restriction is substantive rather than cosmetic.

The Stage -1 proposal for this qid posed the comparison as two conjectures:
a primitive open-class support-function gap and a two-shock witness.  This
note does not prove the primitive open-class claim in
Conjecture~\ref{conj:primitive-strict-gap}; it proves the conditional
support-gap theorem obtained by adding the user-approved quantitative margin
assumption, and it proves the two-shock witness in closed form.  Accordingly,
the theorem-level novelty claimed here is the conditional sharp-bound
comparison and the special-case certificate, not an unconditional generic
negative-result theorem.  No repository theorem is used as a premise; the
contribution is the standalone algebraic comparison between two population
response sets plus the explicit conditional margin bookkeeping.

\section{Formal setup}
The locked parameters define a partial-identification problem for structural
impulse-response sets.  Let \(Y_t\in\R^n\) be covariance stationary with
reduced-form innovation \(u_t\), innovation covariance
\(\Sigma_u=\E[u_tu_t^\transpose]\succ0\), and finite fourth cumulant tensor
\(K_u=\operatorname{cum}_4(u_t)\).  The observed population law \(P\) is
summarized, for this theorem, by
\[
(\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u),\qquad
\Gamma_h=\E[Y_{t+h}u_t^\transpose]\Sigma_u^{-1},\quad h=0,\ldots,H.
\]

A structural completion writes
\[
u_t=B\varepsilon_t,\qquad \E[\varepsilon_t\varepsilon_t^\transpose]=I_n,
\qquad BB^\transpose=\Sigma_u.
\]
Fix the symmetric square root \(\Sigma_u^{1/2}\).  Every such \(B\) can be
written as \(B(Q)=\Sigma_u^{1/2}Q\) for a rotation or reflection
\(Q\in O(n)=\{Q\in\R^{n\times n}:Q^\transpose Q=I_n\}\).  For a labelled shock
index \(j\), set \(b_j(Q)=B(Q)e_j\) and define
\[
\psi_j(Q)=\bigl(e_y^\transpose\Gamma_h b_j(Q)\bigr)_{h=0}^H
        \in\R^{H+1}.
\]
The maintained sign and zero restrictions are \(A\psi_j(Q)\ge0\) and
\(Z\psi_j(Q)=0\), where inequalities are componentwise.

The non-Gaussian SVAR restriction says that the same rotation also diagonalizes
the observed fourth cumulant tensor:
\[
K_u=\sum_{k=1}^n \kappa_k\, b_k(Q)^{\otimes4},
\qquad b_k(Q)=\Sigma_u^{1/2}Qe_k,
\]
for an admissible cumulant vector \(\kappa=(\kappa_1,\ldots,\kappa_n)\) with
the target component separated by \(\delta_4>0\):
\[
\mathcal K_{\delta_4}(j)=
\{\kappa\in\R^n: |\kappa_j|\ge\delta_4,\ 
|\kappa_\ell-\kappa_j|\ge\delta_4\ \text{for every }\ell\ne j\}.
\]
The LP/sign response set and the non-Gaussian SVAR/sign response set are
\[
\mathcal R_{\mathrm{LP}}(P)=
\{\psi_j(Q):Q\in O(n),\ A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0\},
\]
\[
\mathcal R_{\mathrm{SVAR}}(P)=
\{\psi_j(Q):Q\in O(n),\ A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0,\ 
K_u=\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4}
\text{ for some }\kappa\in\mathcal K_{\delta_4}(j)\}.
\]
The vector identified set for the structural response is
\(\Theta_I(P)=\mathcal R_{\mathrm{SVAR}}(P)\).  The LP/sign set is an outer
relaxation, not the causal or structural target itself.
It is useful to name the corresponding feasible rotation sets:
\[
\mathcal Q_{\mathrm{LP}}(P)=
\{Q\in O(n):A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0\},
\]
\[
\mathcal Q_{\mathrm{SVAR}}(P)=
\{Q\in\mathcal Q_{\mathrm{LP}}(P):
K_u=\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4}
\text{ for some }\kappa\in\mathcal K_{\delta_4}(j)\}.
\]

\paragraph{Locked parameters.}
\begin{verbatim}
qid = eid_lp_svar_nonequiv
specialization = v1
anchor_cluster = partial identification / linear-projection IRF methods
observable distribution P = the population law of a covariance-stationary
  finite-order VAR(p) process Y_t, summarized by reduced-form LP/VAR response
  rows Gamma_h = E[Y_{t+h} u_t'] Sigma_u^{-1} for h=0,...,H, innovation
  covariance Sigma_u, and fourth cumulant tensor K_u = cum4(u_t)
parameter theta = the H+1 horizon structural impulse-response vector
  psi_j(B) = (e_y' Gamma_h b_j)_{h=0}^H for a labelled structural shock j,
  with u_t = B epsilon_t, E[epsilon_t epsilon_t'] = I, and b_j = B e_j
identifying restrictions = (i) finite-order linear VAR/LP population rows,
  (ii) unit-variance structural shocks, (iii) a partial sign/zero pattern
  A psi_j(B) >= 0 and Z psi_j(B) = 0, (iv) observed fourth cumulant tensor
  K_u generated by independent non-Gaussian shocks with an admissible
  cumulant vector kappa in K_delta4(j), where |kappa_j| >= delta_4 and
  |kappa_l-kappa_j| >= delta_4 for every l != j after the target label is
  fixed, and (v) an optional common cumulant-matching restriction requiring
  the same rotation to satisfy the LP sign rows and diagonalize K_u
bounding functional = for any report direction w in R^{H+1}, compare support
  functions h_LP(w;P) over the LP/sign relaxation and h_SVAR(w;P) over the
  non-Gaussian SVAR/sign feasible set; the non-equivalence gap is
  Delta_w(P)=h_LP(w;P)-h_SVAR(w;P)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite-order linear projection environment]\label{ass:finite-var}
The population law \(P\) is covariance stationary and generated by a finite
order VAR(p) with innovation \(u_t\), positive definite innovation covariance
\(\Sigma_u\succ0\), and finite fourth moments.  For each reported horizon
\(h=0,\ldots,H\), the row \(\Gamma_h=\E[Y_{t+h}u_t^\transpose]\Sigma_u^{-1}\)
exists and equals the corresponding unrestricted population VAR response row.
\end{assumption}

\begin{assumption}[Rotation normalization and labelled target shock]\label{ass:normalization}
Structural shocks have identity covariance and every impact matrix is
parameterized as \(B(Q)=\Sigma_u^{1/2}Q\) with \(Q\in O(n)\).  The target shock
index \(j\) is fixed after the usual sign and permutation normalization; all
sets below are for this fixed label.
\end{assumption}

\begin{assumption}[Partial sign and zero restrictions]\label{ass:sign-zero}
Known matrices \(A\in\R^{m_A\times(H+1)}\) and
\(Z\in\R^{m_Z\times(H+1)}\) encode the maintained restrictions
\(A\psi_j(Q)\ge0\) and \(Z\psi_j(Q)=0\).  The LP/sign feasible rotation set is
nonempty.  In strict-gap statements, the restrictions leave a
positive-dimensional feasible component rather than pinning the labelled shock
direction to a finite signed-permutation orbit.
\end{assumption}

\begin{assumption}[Observed fourth-cumulant tensor]\label{ass:cumulant-tensor}
The fourth cumulant tensor \(K_u=\operatorname{cum}_4(u_t)\) is finite and
observed at the population level.  A non-Gaussian SVAR completion requires
\[
K_u=\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4},
\qquad b_k(Q)=\Sigma_u^{1/2}Qe_k,
\]
where \(\kappa_k\) is the fourth cumulant of the \(k\)-th independent
unit-variance structural shock.  Admissible cumulant vectors are understood to
be moment-realizable by such univariate shocks.
\end{assumption}

\begin{assumption}[Bounded target fourth-cumulant gap]\label{ass:bounded-gap}
For the labelled target component, the admissible structural fourth-cumulant
vector belongs to
\[
\mathcal K_{\delta_4}(j)=
\{\kappa\in\R^n:|\kappa_j|\ge\delta_4,\ 
|\kappa_\ell-\kappa_j|\ge\delta_4\ \text{for every }\ell\ne j\}
\]
for a fixed \(\delta_4>0\).  Gaussian shocks and equal-target-kurtosis
boundaries are therefore outside the strict-gap specialization.
\end{assumption}

\begin{assumption}[Nonempty non-Gaussian SVAR feasible set]\label{ass:svar-nonempty}
There exists at least one \(Q\in O(n)\) and at least one
\(\kappa\in\mathcal K_{\delta_4}(j)\) satisfying the sign/zero restrictions
and the fourth-cumulant diagonalization equation.  This assumption is used for
finite-valued support-function comparisons; if it fails, the SVAR support is
\(-\infty\) by convention.
\end{assumption}

\begin{assumption}[Common cumulant-matching restriction]\label{ass:cumulant-matching}
The same rotation \(Q\) that generates a reported LP response vector
\(\psi_j(Q)\) is required to diagonalize \(K_u\) as in
Assumption~\ref{ass:cumulant-tensor}.  Equivalently, the LP/sign candidate is
restricted to the non-Gaussian SVAR feasible rotation set.
\end{assumption}

\begin{assumption}[Generic report direction]\label{ass:generic-report}
The report direction \(w\in\R^{H+1}\) is such that
\(w^\transpose\psi_j(Q)\) is not constant on any positive-dimensional
connected component of the LP/sign feasible set that contains a
non-cumulant-matching rotation.
\end{assumption}

\begin{assumption}[A-quant-margin: user-approved quantitative margin]\label{ass:A-quant-margin}\label{ass:quant-margin}
\begin{verbatim}
(Quantitative margin, §7.) For every observable law P in the open class O and every admissible direction w, the cumulant-envelope support loss chi_w(P) := h_{R_LP(P)}(w) - sup_{Sigma in R_LP(P) cap C_eps(P)} <w, Sigma> is strictly positive, i.e. chi_w(P) > 0.
\end{verbatim}
This is a locked-parameter addition approved for this correction round.  It is
invoked only as a hypothesis; the proof below does not derive this strict
margin from primitive fourth-cumulant geometry.  The symbols
\(\mathcal O\), \(\mathcal C_\varepsilon(P)\), and \(\chi_w(P)\) are the
open class, cumulant-envelope set, and support loss formalized in the next
section.
\end{assumption}

\begin{assumption}[Minimal two-shock witness design]\label{ass:two-shock}
For the finite witness, \(n=2\), \(p=1\), \(H\ge1\), the relevant component of
\(O(2)\) is parameterized by a planar angle \(Q(\varphi)\), and the sign
restrictions leave a nondegenerate interval \(I_{\mathrm{LP}}\subset S^1\).
The fourth cumulant tensor has two distinct structural excess kurtoses with
gap at least \(\delta_4\), and at least one fourth-cumulant diagonalizing angle
lies in the LP/sign interval.
\end{assumption}

\section{Estimand-defining functional}
For \(h=0,\ldots,H\), set
\[
g_h(P)=e_y^\transpose\Gamma_h\Sigma_u^{1/2}\in\R^{1\times n},
\qquad
\Psi_j(Q)=\bigl(g_0(P)Qe_j,\ldots,g_H(P)Qe_j\bigr).
\]
Then \(\Psi_j(Q)=\psi_j(Q)\).  For a report direction
\(w=(w_0,\ldots,w_H)^\transpose\), define
\[
g_w(P)=\sum_{h=0}^H w_h g_h(P),\qquad
w^\transpose\Psi_j(Q)=g_w(P)Qe_j.
\]

The LP/sign support functional is the value of the following finite polynomial
program in the \(n^2\) real entries of \(Q\):
\[
h_{\mathrm{LP}}(w;P)=
\max_Q\ g_w(P)Qe_j
\]
subject to
\[
Q^\transpose Q=I_n,\qquad A\Psi_j(Q)\ge0,\qquad Z\Psi_j(Q)=0.
\]
There are \(n(n+1)/2\) orthogonality equations, \(m_A\) linear inequalities in
\(\Psi_j(Q)\), and \(m_Z\) linear equations in \(\Psi_j(Q)\).  The feasible set
is closed inside the compact group \(O(n)\), so the maximum exists whenever the
LP/sign set is nonempty.

The SVAR/sign support functional is computed by adding \(n\) cumulant variables
\(\kappa=(\kappa_1,\ldots,\kappa_n)\) and the fourth-cumulant equations.  A
redundant population bound makes the optimization compact:
\[
\kappa_{\max}(P)=\|K_u\|_F\,\|\Sigma_u^{-1/2}\|_{\mathrm{op}}^4.
\]
For every exact cumulant decomposition,
\(|\kappa_k|\le\kappa_{\max}(P)\) because \(\kappa_k\) is the contraction of
\(K_u\) with the \(k\)-th dual impact vector four times.  The SVAR support is
the maximum over the finite union of sign cases \(s=(s_0,s_\ell:\ell\ne j)\in
\{-1,1\}^{n}\) of the polynomial program
\[
h_{\mathrm{SVAR}}(w;P)=\max_{Q,\kappa}\ g_w(P)Qe_j
\]
subject to
\[
Q^\transpose Q=I_n,\qquad A\Psi_j(Q)\ge0,\qquad Z\Psi_j(Q)=0,
\]
\[
K_u=\sum_{k=1}^n\kappa_k(\Sigma_u^{1/2}Qe_k)^{\otimes4},
\qquad -\kappa_{\max}(P)\le\kappa_k\le\kappa_{\max}(P)\quad(k=1,\ldots,n),
\]
\[
s_0\kappa_j\ge\delta_4,\qquad
s_\ell(\kappa_\ell-\kappa_j)\ge\delta_4\quad(\ell\ne j).
\]
The tensor equation is a finite list of \(n^4\) scalar polynomial equations
(or the equivalent reduced symmetric list).  Thus \(h_{\mathrm{SVAR}}\) is a
computable map from \(P\): evaluate \(2^n\) compact semialgebraic global
optimization problems with \(n^2+n\) real decision variables and take the
largest value.  Equivalently, exact evaluation can be reduced to real
quantifier elimination over this displayed constraint list.

The cumulant-envelope objects used by
Assumption~\ref{ass:A-quant-margin} are also computable from \(P\).  Define
\[
m_{\delta_4}(Q;P)=
\inf_{\kappa\in\mathcal K_{\delta_4}(j)}
\left\|K_u-\sum_{k=1}^n\kappa_k(\Sigma_u^{1/2}Qe_k)^{\otimes4}\right\|_F
\]
and, for the envelope tolerance \(\varepsilon\ge0\) fixed by the open-class
certificate in Assumption~\ref{ass:A-quant-margin},
\[
\mathcal C_\varepsilon(P)=
\{\Psi_j(Q):Q\in\mathcal Q_{\mathrm{LP}}(P),\
m_{\delta_4}(Q;P)\le\varepsilon\}.
\]
The support loss named in the approved assumption is therefore
\[
\chi_w(P)=
h_{\mathcal R_{\mathrm{LP}}(P)}(w)
-
\sup_{\Sigma\in\mathcal R_{\mathrm{LP}}(P)\cap\mathcal C_\varepsilon(P)}
\langle w,\Sigma\rangle,
\]
where \(h_{\mathcal R_{\mathrm{LP}}(P)}(w)=h_{\mathrm{LP}}(w;P)\).  This
quantity is an assumed strict margin, not a derived primitive genericity
claim.

For scalar reports \(\theta_w=w^\transpose\theta\), define the sharp SVAR
directional endpoint functionals
\[
\theta_U^{\mathrm{SVAR}}(w;P)=h_{\mathrm{SVAR}}(w;P),\qquad
\theta_L^{\mathrm{SVAR}}(w;P)=-h_{\mathrm{SVAR}}(-w;P).
\]
The LP/sign outer endpoints are defined analogously by replacing
\(h_{\mathrm{SVAR}}\) with \(h_{\mathrm{LP}}\).  The interval
\([\theta_L^{\mathrm{SVAR}},\theta_U^{\mathrm{SVAR}}]\) gives sharp extrema
for the scalar report, although the interior of the interval need not be sharp
when the feasible response set is disconnected.  The Stage -1 conjecture
verdict is: Conjecture~\ref{conj:primitive-strict-gap} remains open as a
primitive generic-class statement; Theorem~\ref{thm:conditional-margin} below
proves the conditional strict support gap only after invoking
Assumption~\ref{ass:A-quant-margin}.  Conjecture~\ref{conj:two-shock-witness}
is confirmed by the planar calculation in Proposition~\ref{prop:two-shock},
which is a special-case certificate and not a substitute for the open generic
obstruction in Conjecture~\ref{conj:primitive-strict-gap}.

\section{Target causal estimand}
The structural target is not defined as a support function.  It is the
response vector generated by the true labelled structural shock:
\[
\theta=\psi_j(B_0)=
\bigl(e_y^\transpose\Gamma_h b_{0j}\bigr)_{h=0}^H,
\qquad b_{0j}=B_0e_j,
\]
where \(B_0=\Sigma_u^{1/2}Q_0\) for the true rotation \(Q_0\).  Under the
maintained non-Gaussian SVAR restrictions, \(Q_0\) satisfies the sign/zero
restrictions and the fourth-cumulant diagonalization equation for some
\(\kappa_0\in\mathcal K_{\delta_4}(j)\).  Hence the vector identified set is
\[
\Theta_I(P)=\mathcal R_{\mathrm{SVAR}}(P),
\]
and, for any report direction \(w\), the scalar target is
\(\theta_w=w^\transpose\theta\).  The conclusion below is a containment and
sharp-extrema statement for \(\theta_w\), plus a comparison to the larger
LP/sign relaxation; it is not a point-identification claim unless the SVAR
response set is a singleton or the two directional endpoints coincide.

\section{Main theorems}
\begin{theorem}[Theorem 1: conditional support gap under A-quant-margin]\label{thm:conditional-margin}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:svar-nonempty},
\ref{ass:generic-report}, and \ref{ass:A-quant-margin}, for every observable
law \(P\in\mathcal O\) and every admissible report direction
\(w\in\R^{H+1}\),
\[
\Theta_I(P)=\mathcal R_{\mathrm{SVAR}}(P)
\subseteq \mathcal R_{\mathrm{LP}}(P),
\]
and the scalar report satisfies
\[
\theta_w\in
\bigl[-h_{\mathrm{SVAR}}(-w;P),\,h_{\mathrm{SVAR}}(w;P)\bigr]
\subseteq
\bigl[-h_{\mathrm{LP}}(-w;P),\,h_{\mathrm{LP}}(w;P)\bigr].
\]
The displayed SVAR endpoints are sharp extrema over the maintained
second-and-fourth-moment structural restrictions; the LP endpoints are outer
endpoints and are sharp only for the relaxation that drops common cumulant
matching.  Moreover,
\[
\Delta_w(P)=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)\ge0,
\]
and the approved cumulant-envelope margin gives the strict lower bound
\[
\Delta_w(P)\ge \chi_w(P)>0.
\]
\end{theorem}

Theorem~\ref{thm:conditional-margin} is the main result of this corrected
note.  It is intentionally conditional on
Assumption~\ref{ass:A-quant-margin}; it does not confirm
Conjecture~\ref{conj:primitive-strict-gap}.  Its value is that, once the
approved cumulant-envelope support loss is part of the locked-parameter
environment, the reported LP/sign support function is a computable strict
outer bound for the non-Gaussian SVAR/sign structural support.  The theorem
does not assert that any cited estimator or workflow made the omitted-cumulant
shortcut; it supplies the population diagnostic needed before such a shortcut
could be used.

\begin{proposition}[Computable support bounds and equality boundary]\label{prop:support-boundary}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:svar-nonempty}, for every
report direction \(w\in\R^{H+1}\),
\[
\Theta_I(P)=\mathcal R_{\mathrm{SVAR}}(P)
\subseteq \mathcal R_{\mathrm{LP}}(P),
\]
and the scalar report satisfies
\[
\theta_w\in
\bigl[-h_{\mathrm{SVAR}}(-w;P),\,h_{\mathrm{SVAR}}(w;P)\bigr]
\subseteq
\bigl[-h_{\mathrm{LP}}(-w;P),\,h_{\mathrm{LP}}(w;P)\bigr].
\]
The displayed SVAR endpoints are sharp extrema over the maintained
second-and-fourth-moment structural restrictions; the LP endpoints are outer
endpoints and are sharp only for the relaxation that drops common cumulant
matching.  Moreover,
\[
\Delta_w(P)=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)\ge0,
\]
with equality if and only if at least one LP/sign maximizer of
\(Q\mapsto w^\transpose\psi_j(Q)\) also satisfies the non-Gaussian cumulant
diagonalization restriction.  If Assumption~\ref{ass:cumulant-matching} is
imposed on the LP/sign side, then \(\mathcal R_{\mathrm{LP}}(P)\) is replaced
by \(\mathcal R_{\mathrm{SVAR}}(P)\) and all support functions agree.
\end{proposition}

This proposition is the deterministic support-function boundary underneath
Theorem~\ref{thm:conditional-margin}.  Compared with Plagborg-M{\o}ller and Wolf
\cite{PlagborgMollerWolf2021}, the difference is not LPs versus VARs as
estimators; it is the omitted fourth-cumulant identifying restriction.  Compared
with non-Gaussian SVAR identification results such as
\cite{GourierouxMonfortRenne2017,LanneMeitzSaikkonen2017,Guay2021}, the new
object is the explicit gap between a sign-only LP relaxation and the
cumulant-matching structural set.

\begin{proposition}[Closed-form two-shock witness]\label{prop:two-shock}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:bounded-gap},
\ref{ass:generic-report}, and \ref{ass:two-shock}, restrict attention to the
connected planar component \(Q(\varphi)\).  Suppose the LP/sign restrictions
define a nondegenerate interval \(I_{\mathrm{LP}}\subset S^1\), the
non-Gaussian SVAR angles are
\[
I_{\mathrm{SVAR}}=
I_{\mathrm{LP}}\cap
\{\varphi_\star,\varphi_\star+\pi/2,\varphi_\star+\pi,
\varphi_\star+3\pi/2\},
\]
and \(I_{\mathrm{SVAR}}\ne\emptyset\).  If
\[
w^\transpose\psi_j(Q(\varphi))
=a_w\cos\varphi+b_w\sin\varphi
=\rho_w\cos(\varphi-\varphi_w),\qquad \rho_w>0,
\]
with \(\varphi_w\) an interior point of \(I_{\mathrm{LP}}\) and
\(\varphi_w\notin I_{\mathrm{SVAR}}\), then
\[
h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)
\ge \rho_w(1-\cos d_w)>0,
\qquad d_w=\operatorname{dist}_{S^1}(\varphi_w,I_{\mathrm{SVAR}}).
\]
For the open class in which the nearest SVAR angle is the SVAR maximizer, the
inequality is an equality.
\end{proposition}

This proposition confirms Conjecture~\ref{conj:two-shock-witness}.  Its value
is that the support separation is visible in the smallest nontrivial rotation
geometry: a sign interval can contain both a valid non-Gaussian structural
angle and a different LP-sign angle with a larger reported response.  It is
only a planar witness, not a proof of the generic open-class obstruction in
Conjecture~\ref{conj:primitive-strict-gap}.  The closest sign/SVAR algorithms
enumerate feasible rotations, while the formula above gives the gap itself.

\section{Interpretation}
The LP/sign set answers the question, ``which response paths can be produced by
some orthogonal impact rotation satisfying the reported response signs and
zeros?''  The non-Gaussian SVAR/sign set answers the stricter question, ``which
of those paths can be produced by the same rotation that diagonalizes the
observed fourth cumulant tensor with a separated labelled shock?''  The only
tightening restriction in Proposition~\ref{prop:support-boundary} is this
common cumulant-matching requirement.

The bound collapses to point identification for a report direction \(w\) when
\(h_{\mathrm{SVAR}}(w;P)=-h_{\mathrm{SVAR}}(-w;P)\).  At the vector level this
requires \(\mathcal R_{\mathrm{SVAR}}(P)\) to be a singleton in the reported
coordinates.  The LP and SVAR bounds coincide in direction \(w\) exactly when a
support-exposed LP optimizer is also cumulant matching.  They differ when the
best LP-sign response is generated by a rotation that cannot be part of any
independent non-Gaussian shock law producing the observed \(K_u\).

If the cumulant restriction is removed, or if \(K_u\) carries no usable label
information, the comparison widens back to the familiar sign-restricted
LP/VAR object.  If the sign and zero restrictions already pin down the same
signed-permutation orbit selected by the fourth cumulants, there is no room for
a gap.  The conditional strict-gap theorem applies in the genuinely
partial-sign region only after Assumption~\ref{ass:A-quant-margin} supplies a
positive support loss.  Proving that this positive support loss holds
generically from the primitive fourth-cumulant geometry is exactly the open
content of Conjecture~\ref{conj:primitive-strict-gap}.

\section{Step-by-step proof}
\begin{lemma}[Rotation parameterization]\label{lem:rotation}
Under Assumptions~\ref{ass:finite-var} and \ref{ass:normalization}, the set of
impact matrices with identity structural covariance and reduced-form
covariance \(\Sigma_u\) is exactly
\(\{\Sigma_u^{1/2}Q:Q\in O(n)\}\).
\end{lemma}

\begin{proof}
If \(B=\Sigma_u^{1/2}Q\) and \(Q^\transpose Q=I_n\), then
\(BB^\transpose=\Sigma_u^{1/2}QQ^\transpose\Sigma_u^{1/2}=\Sigma_u\).  Conversely,
if \(BB^\transpose=\Sigma_u\), set \(Q=\Sigma_u^{-1/2}B\).  Then
\[
QQ^\transpose=\Sigma_u^{-1/2}BB^\transpose\Sigma_u^{-1/2}=I_n.
\]
Since \(Q\) is square, \(QQ^\transpose=I_n\) implies \(Q^\transpose Q=I_n\).
Thus \(B=\Sigma_u^{1/2}Q\) with \(Q\in O(n)\).
\end{proof}

\begin{lemma}[SVAR feasibility is LP feasibility plus cumulant matching]\label{lem:constraint-inclusion}
Under Assumptions~\ref{ass:sign-zero}--\ref{ass:bounded-gap}, every
non-Gaussian SVAR/sign feasible rotation is LP/sign feasible.
\end{lemma}

\begin{proof}
An SVAR/sign feasible pair \((Q,\kappa)\) must satisfy
\(Q\in O(n)\), \(A\psi_j(Q)\ge0\), and \(Z\psi_j(Q)=0\) by the definition of
the SVAR/sign set.  These are exactly the LP/sign feasibility constraints.
The additional equations
\[
K_u=\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4},
\qquad \kappa\in\mathcal K_{\delta_4}(j),
\]
are extra restrictions and remove rotations; they add no LP-feasible rotations.
\end{proof}

\begin{lemma}[Cumulant-filtered envelope]\label{lem:envelope}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:svar-nonempty}, let
\[
h_\varepsilon(w;P)=
\sup\{w^\transpose\psi_j(Q):Q\in\mathcal Q_{\mathrm{LP}}(P),
m_{\delta_4}(Q;P)\le\varepsilon\}.
\]
Then \(h_\varepsilon(w;P)\downarrow h_{\mathrm{SVAR}}(w;P)\) as
\(\varepsilon\downarrow0\).
\end{lemma}

\begin{proof}
The LP feasible rotation set is closed in \(O(n)\), hence compact.  The
function \(Q\mapsto w^\transpose\psi_j(Q)\) is continuous because it is linear
in \(Q\).  The mismatch function \(m_{\delta_4}(Q;P)\) is continuous.  To see
this, write the tensor map as
\(L_Q\kappa=\sum_k\kappa_kb_k(Q)^{\otimes4}\).  For each \(Q\), the tensors
\(\{b_k(Q)^{\otimes4}\}_{k=1}^n\) are linearly independent because
\(\{b_k(Q)\}_{k=1}^n\) is a basis; by compactness of \(O(n)\), the smallest
singular value of \(L_Q\) is bounded away from zero uniformly in \(Q\).  Hence
the distance from \(K_u\) to the closed set \(L_Q\mathcal K_{\delta_4}(j)\)
can be computed over a compact \(\kappa\)-ball depending only on \(P\), and
a standard compact-minimum argument gives continuity.  The sets
\(\mathcal Q_\varepsilon(P)\) are nested closed subsets of a compact set and
their intersection is exactly the cumulant-matching rotation set
\(\mathcal Q_0(P)\).  Since \(\mathcal Q_0(P)\) is nonempty by
Assumption~\ref{ass:svar-nonempty}, compactness gives maximizers
\(Q_\varepsilon\) along any sequence \(\varepsilon\downarrow0\).  Every
convergent subsequence has a limit in \(\mathcal Q_0(P)\), so every limit point
of \(h_\varepsilon(w;P)\) is at most \(h_{\mathrm{SVAR}}(w;P)\).  The reverse
inequality holds because \(\mathcal Q_0(P)\subseteq\mathcal Q_\varepsilon(P)\)
for all \(\varepsilon>0\).  Hence the decreasing limit equals
\(h_{\mathrm{SVAR}}(w;P)\).
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:support-boundary}]
By Lemma~\ref{lem:rotation}, all admissible structural impact matrices are
indexed by rotations \(Q\).  By Lemma~\ref{lem:constraint-inclusion}, every
rotation satisfying the SVAR/sign restrictions also satisfies the LP/sign
restrictions.  Applying the response map \(\psi_j\) to both feasible rotation
sets gives
\[
\mathcal R_{\mathrm{SVAR}}(P)\subseteq \mathcal R_{\mathrm{LP}}(P).
\]
The true target \(\theta\) belongs to \(\mathcal R_{\mathrm{SVAR}}(P)\) by the
maintained structural restrictions in Assumptions~\ref{ass:normalization},
\ref{ass:sign-zero}, \ref{ass:cumulant-tensor}, and \ref{ass:bounded-gap}.
Therefore, for every \(w\),
\[
w^\transpose\theta
\le \sup_{r\in\mathcal R_{\mathrm{SVAR}}(P)}w^\transpose r
=h_{\mathrm{SVAR}}(w;P),
\]
and applying the same inequality to \(-w\) gives
\[
w^\transpose\theta\ge -h_{\mathrm{SVAR}}(-w;P).
\]
Set inclusion gives the LP outer interval because the supremum of a linear
functional cannot decrease when the feasible set is enlarged.

The nonnegativity of \(\Delta_w(P)\) is the same support-function monotonicity:
\[
h_{\mathrm{SVAR}}(w;P)
=\sup_{r\in\mathcal R_{\mathrm{SVAR}}(P)}w^\transpose r
\le
\sup_{r\in\mathcal R_{\mathrm{LP}}(P)}w^\transpose r
=h_{\mathrm{LP}}(w;P).
\]
Equality holds if an LP/sign maximizer is cumulant matching, because that
maximizer is also SVAR feasible and attains both support values.  Conversely,
if the two support values are equal, compactness of the LP/sign feasible set
gives an LP maximizer \(Q^\star\).  The equal value must also be attained by
some SVAR feasible rotation \(Q^0\); \(Q^0\) is therefore an LP maximizer that
satisfies cumulant matching.  This proves the argmax-intersection boundary.

If Assumption~\ref{ass:cumulant-matching} is imposed on the LP/sign side, the
LP feasible rotations are, by definition, restricted to the SVAR feasible
rotations; hence the two response sets and all support functions coincide.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:conditional-margin}]
The containment and scalar endpoint statements are exactly the first part of
Proposition~\ref{prop:support-boundary}.  It remains to prove the strict
lower bound.  Every SVAR/sign feasible response is generated by a rotation
with \(m_{\delta_4}(Q;P)=0\).  Since \(0\le\varepsilon\), this response belongs
to the cumulant-envelope set \(\mathcal C_\varepsilon(P)\) used in
Assumption~\ref{ass:A-quant-margin}.  Hence
\[
\mathcal R_{\mathrm{SVAR}}(P)
\subseteq
\mathcal R_{\mathrm{LP}}(P)\cap\mathcal C_\varepsilon(P),
\]
and support monotonicity gives
\[
h_{\mathrm{SVAR}}(w;P)
\le
\sup_{\Sigma\in\mathcal R_{\mathrm{LP}}(P)\cap\mathcal C_\varepsilon(P)}
\langle w,\Sigma\rangle.
\]
Subtracting this inequality from \(h_{\mathrm{LP}}(w;P)\) yields
\[
\Delta_w(P)
=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)
\ge
h_{\mathcal R_{\mathrm{LP}}(P)}(w)
-
\sup_{\Sigma\in\mathcal R_{\mathrm{LP}}(P)\cap\mathcal C_\varepsilon(P)}
\langle w,\Sigma\rangle
=\chi_w(P).
\]
Assumption~\ref{ass:A-quant-margin} states \(\chi_w(P)>0\) for every
observable law \(P\in\mathcal O\) and every admissible direction \(w\).  Thus
\(\Delta_w(P)\ge\chi_w(P)>0\).  This is a conditional implication from the
approved margin assumption, not a proof of
Conjecture~\ref{conj:primitive-strict-gap}.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:two-shock}]
On the relevant component of \(O(2)\), write the labelled shock direction as
\((\cos\varphi,\sin\varphi)^\transpose\).  Since \(w^\transpose\psi_j(Q)\) is
linear in this direction, there exist \(a_w,b_w\) such that
\[
w^\transpose\psi_j(Q(\varphi))=a_w\cos\varphi+b_w\sin\varphi.
\]
With \(\rho_w=(a_w^2+b_w^2)^{1/2}>0\), choose \(\varphi_w\) satisfying
\((a_w,b_w)=\rho_w(\cos\varphi_w,\sin\varphi_w)\).  Then the objective is
\(\rho_w\cos(\varphi-\varphi_w)\).

Assumption~\ref{ass:two-shock} and the distinct fourth cumulants imply that
the fourth-cumulant tensor has exactly the signed and permuted diagonalizing
directions
\[
\{\varphi_\star,\varphi_\star+\pi/2,\varphi_\star+\pi,
\varphi_\star+3\pi/2\}
\]
on the circle for the labelled column convention.  Intersecting this finite
set with \(I_{\mathrm{LP}}\) gives \(I_{\mathrm{SVAR}}\).  Since \(\varphi_w\)
is an interior point of \(I_{\mathrm{LP}}\), the LP maximum is
\[
\max_{\varphi\in I_{\mathrm{LP}}}\rho_w\cos(\varphi-\varphi_w)=\rho_w.
\]
For any \(\varphi\in I_{\mathrm{SVAR}}\),
\[
\rho_w\cos(\varphi-\varphi_w)\le
\rho_w\cos d_w,
\qquad d_w=\operatorname{dist}_{S^1}(\varphi_w,I_{\mathrm{SVAR}}),
\]
because cosine decreases with angular distance on the nearest-arc range
selected by the finite maximizer.  Therefore
\[
h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)
\ge \rho_w-\rho_w\cos d_w
=\rho_w(1-\cos d_w).
\]
The condition \(\varphi_w\notin I_{\mathrm{SVAR}}\) gives \(d_w>0\), hence the
gap is strictly positive.  When the nearest SVAR angle attains the SVAR maximum
over the finite set, the displayed inequality is equality.  The strict
inequalities defining interiority, nonzero amplitude, distinct cumulants, and
nonmembership in the finite SVAR set are stable under small perturbations, so
the witness describes a nonempty open class.
\end{proof}

\section{Sanity checks}
\begin{enumerate}[leftmargin=*]
\item \textbf{Common restrictions recover LP/VAR equivalence.}  If the
fourth-cumulant restriction is removed from the SVAR side, both feasible sets
are the same sign/zero-restricted rotation set.  Thus
\(h_{\mathrm{LP}}(w;P)=h_{\mathrm{SVAR}}(w;P)\), matching the common-restriction
population equivalence in \cite{PlagborgMollerWolf2021}.

\item \textbf{Gaussian or equal-kurtosis boundary.}  If \(K_u=0\), or if the
target cumulant is not separated from another structural cumulant, then
Assumption~\ref{ass:bounded-gap} fails.  The conditional strict-gap theorem
therefore makes no claim there unless a separate approved margin assumption is
supplied; the non-Gaussian label has disappeared or become ambiguous.

\item \textbf{Full sign/zero labeling.}  If \(A\psi_j(Q)\ge0\) and
\(Z\psi_j(Q)=0\) already restrict the labelled column \(Qe_j\) to the same
finite signed-permutation orbit selected by \(K_u\), every LP support maximizer
is cumulant matching.  Proposition~\ref{prop:support-boundary} then gives
\(\Delta_w(P)=0\) for all \(w\).

\item \textbf{Point-identification special case.}  If the cumulant tensor and
sign normalization select a unique reported response vector \(r^\star\), then
\(\mathcal R_{\mathrm{SVAR}}(P)=\{r^\star\}\).  For every \(w\),
\(-h_{\mathrm{SVAR}}(-w;P)=h_{\mathrm{SVAR}}(w;P)=w^\transpose r^\star\).

\item \textbf{No-restriction LP outer envelope.}  If \(A\) and \(Z\) are empty,
the LP support reduces to
\[
h_{\mathrm{LP}}(w;P)=\max_{\|q\|=1} g_w(P)q=\|g_w(P)\|_2,
\]
because the labelled column \(q=Qe_j\) can be any unit vector.  The SVAR
support is no larger and can be strictly smaller when the cumulant tensor
admits only a finite diagonalizing set.
\end{enumerate}

\section{Counterexample or minimality check}
The common cumulant-matching condition is minimal for sharpness of the
non-Gaussian structural interpretation.  Consider \(n=2\), \(\Sigma_u=I_2\),
and a reduced-form cumulant tensor generated by independent components in the
standard basis with distinct fourth cumulants
\(\kappa_1\ne\kappa_2\), both satisfying the \(\delta_4\) separation.  Then the
cumulant-diagonalizing target angles are \(0,\pi/2,\pi,3\pi/2\).

Let the LP/sign restrictions on the labelled direction
\((\cos\varphi,\sin\varphi)\) define the interval
\[
I_{\mathrm{LP}}=[0,\pi/3]
\]
through the two linear inequalities
\(\sin\varphi\ge0\) and
\((\sqrt3/2)\cos\varphi-(1/2)\sin\varphi\ge0\).  The SVAR/sign target set is
nonempty because \(0\in I_{\mathrm{LP}}\), and within this interval the only
cumulant-diagonalizing target angle is \(0\).  Choose response rows and report
direction such that
\[
w^\transpose\psi_j(Q(\varphi))
=\cos(\varphi-\pi/4).
\]
Then the LP/sign support is attained at the interior nonmatching angle
\(\varphi=\pi/4\), with value \(1\), while the SVAR/sign support is attained at
\(\varphi=0\), with value \(\cos(\pi/4)=\sqrt2/2\).  Thus
\[
\Delta_w(P)=1-\sqrt2/2>0.
\]
Dropping cumulant matching would report the infeasible angle \(\pi/4\) as if
it were a valid non-Gaussian structural shock.  The nearest correct repair is
exactly the restriction in Assumption~\ref{ass:cumulant-matching}: filter LP
rotations through the fourth-cumulant diagonalization equation before
interpreting the response as a labelled non-Gaussian SVAR impulse response.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
\item \textbf{Observed population objects.}  Natural numbers \(n,H\); matrices
\(\Gamma_h\in\R^{n\times n}\), \(\Sigma_u\in\R^{n\times n}\) with
\(\Sigma_u\succ0\), fourth cumulant tensor \(K_u\in(\R^n)^{\otimes4}\), and
restriction matrices \(A\in\R^{m_A\times(H+1)}\),
\(Z\in\R^{m_Z\times(H+1)}\).

\item \textbf{Deterministic maps.}  Orthogonal group
\(O(n)=\{Q:Q^\transpose Q=I_n\}\); impact map \(B(Q)=\Sigma_u^{1/2}Q\);
column map \(b_k(Q)=B(Q)e_k\); response map
\(\psi_j(Q)=(e_y^\transpose\Gamma_h b_j(Q))_{h=0}^H\); report objective
\(Q\mapsto w^\transpose\psi_j(Q)\).

\item \textbf{Probabilistic restrictions.}  Finite VAR/LP response rows;
identity covariance structural shocks; independent non-Gaussian shocks whose
fourth cumulants form \(\kappa\in\mathcal K_{\delta_4}(j)\); tensor equation
\(K_u=\sum_k\kappa_kb_k(Q)^{\otimes4}\); nonempty SVAR feasible set.

\item \textbf{Feasible sets.}  LP rotation set defined by orthogonality,
\(A\psi_j(Q)\ge0\), and \(Z\psi_j(Q)=0\).  SVAR rotation set defined by the
same constraints plus existential \(\kappa\) satisfying the tensor equation
and the separated-cumulant inequalities.

\item \textbf{Optimization functionals.}  \(h_{\mathrm{LP}}(w;P)\) as a compact
polynomial optimization in \(n^2\) variables.  \(h_{\mathrm{SVAR}}(w;P)\) as
the maximum over \(2^n\) compact semialgebraic programs in \(n^2+n\) variables
with explicit orthogonality, sign/zero, tensor, box, and gap constraints.
The cumulant-envelope set \(\mathcal C_\varepsilon(P)\) and support loss
\(\chi_w(P)\) used by Assumption~\ref{ass:A-quant-margin}.

\item \textbf{Deterministic identities.}  Polar/rotation identity
\(\{B:BB^\transpose=\Sigma_u\}=\{\Sigma_u^{1/2}Q:Q\in O(n)\}\).  Set inclusion
identity: adding cumulant equations to LP constraints yields a subset.
Support monotonicity: \(S_1\subseteq S_2\Rightarrow h_{S_1}(w)\le h_{S_2}(w)\).
Envelope inclusion for the conditional theorem:
\(\mathcal R_{\mathrm{SVAR}}(P)\subseteq
\mathcal R_{\mathrm{LP}}(P)\cap\mathcal C_\varepsilon(P)\).  Envelope
convergence for nested compact level sets of a continuous mismatch function,
used only as a deterministic continuity fact and not as a source of the
positive margin.

\item \textbf{Two-shock trigonometry.}  Parameterization
\(q(\varphi)=(\cos\varphi,\sin\varphi)\); linear report objective
\(a_w\cos\varphi+b_w\sin\varphi=\rho_w\cos(\varphi-\varphi_w)\); distinct
fourth cumulants imply a finite diagonalizing orbit; angular-distance gap
\(\rho_w(1-\cos d_w)\).
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a computable partial-identification boundary
between two population response objects.  The LP/sign support function is an
outer relaxation; the non-Gaussian SVAR/sign support function is obtained by
requiring the same impact rotation to diagonalize the observed fourth cumulant
tensor with a separated labelled shock.  This common cumulant-matching
restriction is exactly what tightens the bound.  The gap is zero when a
support-exposed LP optimizer is cumulant matching and becomes strictly positive
under the approved A-quant-margin hypothesis.  The two-shock witness supplies a
separate closed-form positive-gap certificate, but it is not a generic-class
obstruction.  The note is therefore a conditional bound and diagnostic rather
than a negative refutation of a specific published estimator.  The primitive
generic claim that the A-quant-margin condition follows from fourth-cumulant
geometry remains open as Conjecture~\ref{conj:primitive-strict-gap}; no
unconditional strict-gap theorem is claimed here.

\subsection*{References}
\begin{thebibliography}{99}

\bibitem{AriasRubioRamirezWaggoner2018}
Arias, J.~E., J.~F. Rubio-Ramirez, and D.~F. Waggoner (2018).
Inference based on structural vector autoregressions identified with sign and
zero restrictions: Theory and applications.
\emph{Econometrica} 86(2), 685--720.

\bibitem{BaumeisterHamilton2015}
Baumeister, C. and J.~D. Hamilton (2015).
Sign restrictions, structural vector autoregressions, and useful prior
information.
\emph{Econometrica} 83(5), 1963--1999.

\bibitem{DrautzburgWright2023}
Drautzburg, T. and J.~H. Wright (2023).
Refining set-identification in VARs through independence.
\emph{Journal of Econometrics} 235(2), 1827--1847.

\bibitem{GourierouxMonfortRenne2017}
Gourieroux, C., A. Monfort, and J.-P. Renne (2017).
Statistical inference for independent component analysis: Application to
structural VAR models.
\emph{Journal of Econometrics} 196(1), 111--126.

\bibitem{Guay2021}
Guay, A. (2021).
Identification of structural vector autoregressions through higher
unconditional moments.
\emph{Journal of Econometrics} 225(1), 27--46.

\bibitem{Jorda2005}
Jorda, O. (2005).
Estimation and inference of impulse responses by local projections.
\emph{American Economic Review} 95(1), 161--182.

\bibitem{LanneLuoto2021}
Lanne, M. and J. Luoto (2021).
GMM estimation of non-Gaussian structural vector autoregression.
\emph{Journal of Business \& Economic Statistics} 39(1), 69--81.

\bibitem{LanneLiuLuoto2026}
Lanne, M., K. Liu, and J. Luoto (2026).
Identifying structural vector autoregressions via non-Gaussianity of
potentially dependent shocks.
\emph{The Econometrics Journal}, utag002.

\bibitem{LanneMeitzSaikkonen2017}
Lanne, M., M. Meitz, and P. Saikkonen (2017).
Identification and estimation of non-Gaussian structural vector
autoregressions.
\emph{Journal of Econometrics} 196(2), 288--304.

\bibitem{LiPlagborgMollerWolf2024}
Li, D., M. Plagborg-M{\o}ller, and C.~K. Wolf (2024).
Local projections vs. VARs: Lessons from thousands of DGPs.
\emph{Journal of Econometrics} 244, 105722.

\bibitem{MontielOleaPlagborgMoller2021}
Montiel Olea, J.~L. and M. Plagborg-M{\o}ller (2021).
Local projection inference is simpler and more robust than you think.
\emph{Econometrica} 89(4), 1789--1823.

\bibitem{MontielOleaPlagborgMollerQianWolf2024}
Montiel Olea, J.~L., M. Plagborg-M{\o}ller, E. Qian, and C.~K. Wolf (2024).
Double robustness of local projections and some unpleasant VARithmetic.
NBER Working Paper 32495; \emph{Econometrica}, forthcoming.

\bibitem{PlagborgMollerWolf2021}
Plagborg-M{\o}ller, M. and C.~K. Wolf (2021).
Local projections and VARs estimate the same impulse responses.
\emph{Econometrica} 89(2), 955--980.

\bibitem{Read2022}
Read, M. (2022).
Algorithms for inference in SVARs identified with sign and zero restrictions.
\emph{The Econometrics Journal} 25(3), 699--718.

\bibitem{RubioRamirezWaggonerZha2010}
Rubio-Ramirez, J.~F., D.~F. Waggoner, and T. Zha (2010).
Structural vector autoregressions: Theory of identification and algorithms for
inference.
\emph{Review of Economic Studies} 77(2), 665--696.

\end{thebibliography}

\end{document}
