% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_lp\_svar\_nonequiv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{eid\_lp\_svar\_nonequiv} / \texttt{v1}%
  \\ \large\textit{A cumulant-matching boundary for LP/sign and non-Gaussian SVAR impulse-response sets}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid = eid_lp_svar_nonequiv
specialization = v1
anchor_cluster = partial identification / linear-projection IRF methods
observable distribution P = the population law of a covariance-stationary
  finite-order VAR(p) process Y_t, summarized by reduced-form LP/VAR response
  rows Gamma_h = E[Y_{t+h} u_t'] Sigma_u^{-1} for h=0,...,H, innovation
  covariance Sigma_u, and fourth cumulant tensor K_u = cum4(u_t)
parameter theta = the H+1 horizon structural impulse-response vector
  psi_j(B) = (e_y' Gamma_h b_j)_{h=0}^H for a labelled structural shock j,
  with u_t = B epsilon_t, E[epsilon_t epsilon_t'] = I, and b_j = B e_j
identifying restrictions = (i) finite-order linear VAR/LP population rows,
  (ii) unit-variance structural shocks, (iii) a partial sign/zero pattern
  A psi_j(B) >= 0 and Z psi_j(B) = 0, (iv) observed fourth cumulant tensor
  K_u generated by independent non-Gaussian shocks with an admissible
  cumulant vector kappa in K_delta4(j), where |kappa_j| >= delta_4 and
  |kappa_l-kappa_j| >= delta_4 for every l != j after the target label is
  fixed, and (v) an optional common cumulant-matching restriction requiring
  the same rotation to satisfy the LP sign rows and diagonalize K_u
bounding functional = for any report direction w in R^{H+1}, compare support
  functions h_LP(w;P) over the LP/sign relaxation and h_SVAR(w;P) over the
  non-Gaussian SVAR/sign feasible set; the non-equivalence gap is
  Delta_w(P)=h_LP(w;P)-h_SVAR(w;P)
\end{verbatim}

\begin{abstract}
This proposal asks where the Plagborg-Moller--Wolf LP/VAR equivalence stops once the structural label is supplied by non-Gaussian fourth cumulants rather than by second-moment sign restrictions alone.  The kernel is a sharp partial-identification boundary: the LP/sign relaxation and the non-Gaussian SVAR/sign identified set agree exactly when the LP-admissible response rows admit one common rotation that also diagonalizes the reduced-form fourth cumulant tensor.  Away from that cumulant-matching face, the proposal conjectures a computable support-function gap bounded below by a fourth-cumulant mismatch margin, so horizonwise LP-sign responses can satisfy the same signs while failing to come from any independent-component structural shock law.  The Gaussian limit is a sanity case, not a contradiction: when the fourth cumulant tensor carries no label information, the proposal collapses back to the usual sign-restricted LP/VAR equivalence.  If resolved, the theorem would give applied SVAR users a reportable diagnostic for when LP sign restrictions are only an outer relaxation of the non-Gaussian structural impulse-response set.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Empirical macroeconomists increasingly combine local projections, sign or zero restrictions, external instruments, and non-Gaussian shock information when reporting structural impulse responses.  \citet{PlagborgMollerWolf2021} made a powerful equivalence claim for LPs and VARs, but that claim is deliberately about a common population impulse-response object under the same identifying restrictions.  Non-Gaussian SVAR identification is different in kind: the structural shock label is a property of one joint innovation law and one fourth-cumulant tensor, not a collection of horizon-by-horizon response inequalities.  The methodological question is whether an LP implementation that keeps only the sign/zero response restrictions is still structurally sharp once the SVAR side uses higher moments to label shocks.

\paragraph{The main finding (proposed).}
The proposed flagship result is Conjecture~\ref{conj:primitive-strict-gap}: primitive non-Gaussian fourth-cumulant and partial sign/zero conditions generically force a positive LP/sign versus SVAR/sign support-function gap, rather than merely allowing one to assume such a gap.  Theorem~\ref{thm:inclusion-boundary} records the routine algebraic inclusion and equality boundary, and Theorem~\ref{thm:conditional-margin} records the conditional consequence of the quantitative margin assumption.  Conjecture~\ref{conj:two-shock-witness} asks for a minimal two-shock, one-lag witness with closed-form trigonometric inequalities, making the non-equivalence check finite and auditable.

\paragraph{What is new.}
The novelty kernel is not ``LPs versus VARs have different finite-sample behavior'' and not ``higher moments refine sign-restricted VARs.''  The precise gap is that \citet{PlagborgMollerWolf2021} transport sign restrictions between LPs and VARs when the identifying restrictions define the same reduced-form IRF object, while \citet{LanneMeitzSaikkonen2017} and \citet{GourierouxMonfortRenne2017} identify a single mixing matrix from one non-Gaussian innovation system.  This proposal asks for the primitive algebraic boundary between those objects: when do response rows satisfying the LP sign pattern paste into one fourth-cumulant diagonalizing rotation, and when can strict separation be derived from the geometry of the cumulant tensor and partial sign cone rather than inserted as a margin assumption?

\paragraph{How it positions in the literature.}
The anchor cluster is partial identification for structural impulse-response sets, sitting at the intersection of LP/VAR equivalence and sign-restricted non-Gaussian SVARs.  It uses the linear-projection language of \citet{Jorda2005}, \citet{PlagborgMollerWolf2021}, \citet{MontielOleaPlagborgMoller2021}, and \citet{MontielOleaPlagborgMollerQianWolf2024}, but the target is a support-function comparison between two identified sets.  It uses the non-Gaussian SVAR identification thread of \citet{GourierouxMonfortRenne2017}, \citet{LanneMeitzSaikkonen2017}, \citet{Guay2021}, \citet{LanneLuoto2021}, and \citet{DrautzburgWright2023}, but it does not assume away the LP relaxation by putting the same independence restriction into the LP object from the start.

\paragraph{Implications for the community.}
The direct downstream consumer is \citet{DrautzburgWright2023}: their independence-refined sign-restricted VAR confidence sets need a population comparison object when applied researchers present LP responses as a robustness check.  A cumulant-matching theorem would say exactly when the LP robustness check is valid for the same non-Gaussian shock label and when it is only a conservative outer set.

\paragraph{How research benefits from the conclusion.}
Researchers should report a cumulant-matching or tensor-diagonalization diagnostic before interpreting LP sign-restricted responses as robustness evidence for a non-Gaussian SVAR shock.

\section{Related work}
\citet{Jorda2005} introduced local projections as a direct regression-based way to estimate impulse responses, making horizonwise response rows a standard empirical object.  \citet{PlagborgMollerWolf2021} prove that LPs and VARs estimate the same population impulse responses under unrestricted lag structures and that VAR identification schemes, including sign restrictions, can be implemented with LPs when the same identifying restrictions are imposed.  \citet{MontielOleaPlagborgMoller2021} and \citet{MontielOleaPlagborgMollerQianWolf2024} sharpen the LP side by showing robust inference properties under persistence, long horizons, and local VAR lag misspecification; these papers motivate treating LP rows as attractive empirical objects but do not add non-Gaussian shock-label restrictions.  \citet{LiPlagborgMollerWolf2024} document that LP and VAR estimators can behave differently across many macroeconomic DGPs, but their comparison is statistical rather than a population identified-set separation.

\citet{RubioRamirezWaggonerZha2010} and \citet{AriasRubioRamirezWaggoner2018} provide the standard sign/zero-restricted SVAR geometry in terms of admissible rotations.  \citet{BaumeisterHamilton2015} emphasize that sign-restricted SVAR conclusions can be sensitive to underidentification and prior choices, which is one reason a sharp support-function boundary matters.  \citet{Read2022} develops algorithms for exact sign and zero restrictions, supplying the finite rotation-inequality language used here.

\citet{GourierouxMonfortRenne2017} and \citet{LanneMeitzSaikkonen2017} show that independent non-Gaussian structural shocks can identify the SVAR impact matrix up to scale, sign, and permutation; this is the closest exact-identification thread.  \citet{Guay2021} gives local statistical identification conditions for non-Gaussian SVARs from third and fourth unconditional moments, which is relevant because the proposed equality boundary can be read as a rank/cumulant matching condition after LP projection.  \citet{LanneLuoto2021} develops GMM estimation for non-Gaussian SVARs, supplying the intended GMM comparator without confusing it with Guay's Journal of Econometrics identification paper.  \citet{DrautzburgWright2023} are the closest partial-identification paper: they refine sign-restricted VAR sets through independence, allow weak higher-moment information, and note non-convex IRF sets, but they do not prove a primitive open-class theorem separating an LP-sign support function from the single-law non-Gaussian SVAR support function.  \citet{LanneLiuLuoto2026} relax independence toward potentially dependent non-Gaussian shocks, underscoring that the common-shock-law condition is an active frontier rather than a textbook assumption.

The in-catalogue ThmSmith prior art is adjacent rather than duplicate.  The `doc/API.md' ExactID and PartialID catalogues are empty at seed time for `eid_*' and `pid_*' entries, so there is no existing LP/SVAR or non-Gaussian impulse-response theorem.  The closest proposal family `q1_spectral_phase_transition' studies row-space and singular-subspace boundaries in panel event-study regressions, but its kernel is Markov support for TWFE rows rather than fourth-cumulant diagonalization for structural shocks.  The closest partial-ID templates, `pid_network_exposure' and `pid_dose_response_iv', concern shared-completion and common-latent pasting failures; they motivate the common-law discipline here but contain no time-series SVAR, LP, or fourth-cumulant result.

\section{Formal setup}
Let \(Y_t\in\R^n\) be covariance stationary with reduced-form VAR innovation \(u_t\), covariance \(\Sigma_u\succ0\), and population LP/VAR response rows
\[
\Gamma_h=\E[Y_{t+h}u_t^\transpose]\Sigma_u^{-1},\qquad h=0,\ldots,H.
\]
A structural representation writes \(u_t=B\varepsilon_t\), \(\E[\varepsilon_t\varepsilon_t^\transpose]=I_n\), so \(BB^\transpose=\Sigma_u\).  Equivalently, fixing the symmetric square root \(\Sigma_u^{1/2}\), every admissible impact matrix is \(B(Q)=\Sigma_u^{1/2}Q\) for some \(Q\in O(n)\).  The horizon-\(h\) response of outcome coordinate \(e_y\) to labelled shock \(j\) is
\[
\psi_{h,j}(Q)=e_y^\transpose\Gamma_h\Sigma_u^{1/2}Qe_j,\qquad
\psi_j(Q)=(\psi_{0,j}(Q),\ldots,\psi_{H,j}(Q))\in\R^{H+1}.
\]
The observable fourth cumulant tensor of reduced-form innovations is \(K_u=\operatorname{cum}_4(u_t)\).  If the structural shocks are independent with fourth cumulants \(\kappa_1,\ldots,\kappa_n\), then
\[
K_u=\sum_{k=1}^n \kappa_k\, b_k(Q)^{\otimes4},
\qquad b_k(Q)=\Sigma_u^{1/2}Qe_k.
\]
For a fixed label \(j\) and gap \(\delta_4>0\), define the admissible target-cumulant set
\[
\mathcal K_{\delta_4}(j)=
\{\kappa\in\R^n:\ |\kappa_j|\ge\delta_4\ \text{and}
|\kappa_\ell-\kappa_j|\ge\delta_4\ \text{for every }\ell\ne j\}.
\]
Let \(A\psi_j(Q)\ge0\) and \(Z\psi_j(Q)=0\) encode the partial sign and zero restrictions across the reported horizons.  The LP/sign identified response set is
\[
\mathcal R_{\mathrm{LP}}(P)=
\{\psi_j(Q):Q\in O(n),\ A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0\}.
\]
The non-Gaussian SVAR/sign identified response set is
\[
\mathcal R_{\mathrm{SVAR}}(P)=
\{\psi_j(Q):Q\in O(n),\ A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0,
K_u=\sum_{k=1}^n \kappa_k b_k(Q)^{\otimes4}\text{ for some }\kappa\in\mathcal K_{\delta_4}(j)\}.
\]
Let \(\mathcal Q_{\mathrm{LP}}(P)\) denote the set of rotations \(Q\) satisfying the LP sign/zero restrictions, and let \(\mathcal Q_{\mathrm{SVAR}}(P)\subseteq\mathcal Q_{\mathrm{LP}}(P)\) denote the rotations that also satisfy the fourth-cumulant diagonalization restriction for some \(\kappa\in\mathcal K_{\delta_4}(j)\).  Define the cumulant-mismatch diagnostic
\[
m_{\delta_4}(Q;P)=
\inf_{\kappa\in\mathcal K_{\delta_4}(j)}
\left\|K_u-\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4}\right\|_F.
\]
For \(\varepsilon\ge0\), let \(\mathcal Q_\varepsilon(P)=\{Q\in\mathcal Q_{\mathrm{LP}}(P):m_{\delta_4}(Q;P)\le\varepsilon\}\) and
\[
h_\varepsilon(w;P)=\sup_{Q\in\mathcal Q_\varepsilon(P)}w^\transpose\psi_j(Q).
\]
Thus \(h_0(w;P)=h_{\mathrm{SVAR}}(w;P)\) whenever the SVAR feasible set is nonempty.  For any report direction \(w\in\R^{H+1}\), define support functions \(h_{\mathrm{LP}}(w;P)=\sup_{r\in\mathcal R_{\mathrm{LP}}(P)}w^\transpose r\), \(h_{\mathrm{SVAR}}(w;P)=\sup_{r\in\mathcal R_{\mathrm{SVAR}}(P)}w^\transpose r\), and \(\Delta_w(P)=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)\).  If a displayed support set is empty, the convention is \(\sup\emptyset=-\infty\); all finite-gap statements below explicitly assume the SVAR feasible set is nonempty.

\begin{verbatim}
qid = eid_lp_svar_nonequiv
specialization = v1
anchor_cluster = partial identification / linear-projection IRF methods
observable distribution P = the population law of a covariance-stationary
  finite-order VAR(p) process Y_t, summarized by reduced-form LP/VAR response
  rows Gamma_h = E[Y_{t+h} u_t'] Sigma_u^{-1} for h=0,...,H, innovation
  covariance Sigma_u, and fourth cumulant tensor K_u = cum4(u_t)
parameter theta = the H+1 horizon structural impulse-response vector
  psi_j(B) = (e_y' Gamma_h b_j)_{h=0}^H for a labelled structural shock j,
  with u_t = B epsilon_t, E[epsilon_t epsilon_t'] = I, and b_j = B e_j
identifying restrictions = (i) finite-order linear VAR/LP population rows,
  (ii) unit-variance structural shocks, (iii) a partial sign/zero pattern
  A psi_j(B) >= 0 and Z psi_j(B) = 0, (iv) observed fourth cumulant tensor
  K_u generated by independent non-Gaussian shocks with an admissible
  cumulant vector kappa in K_delta4(j), where |kappa_j| >= delta_4 and
  |kappa_l-kappa_j| >= delta_4 for every l != j after the target label is
  fixed, and (v) an optional common cumulant-matching restriction requiring
  the same rotation to satisfy the LP sign rows and diagonalize K_u
bounding functional = for any report direction w in R^{H+1}, compare support
  functions h_LP(w;P) over the LP/sign relaxation and h_SVAR(w;P) over the
  non-Gaussian SVAR/sign feasible set; the non-equivalence gap is
  Delta_w(P)=h_LP(w;P)-h_SVAR(w;P)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite-order linear projection environment]\label{ass:finite-var}
The population law \(P\) is generated by a covariance-stationary finite-order VAR(p) with innovation \(u_t\), \(\Sigma_u\succ0\), and finite fourth moments.  The LP rows \(\Gamma_h\) for \(h=0,\ldots,H\) equal the corresponding unrestricted population VAR response rows.
\end{assumption}

\begin{assumption}[Rotation normalization and labelled target shock]\label{ass:normalization}
Structural shocks have identity covariance and the impact matrix is parameterized as \(B(Q)=\Sigma_u^{1/2}Q\), \(Q\in O(n)\).  A target shock index \(j\) is fixed after the usual sign and permutation normalization.
\end{assumption}

\begin{assumption}[Partial sign and zero restrictions]\label{ass:sign-zero}
Known matrices \(A\) and \(Z\) encode the maintained economic restrictions \(A\psi_j(Q)\ge0\) and \(Z\psi_j(Q)=0\).  The feasible LP/sign set is nonempty and the restrictions do not by themselves reduce \(Qe_j\) to a finite signed-permutation set.
\end{assumption}

\begin{assumption}[Observed fourth-cumulant tensor]\label{ass:cumulant-tensor}
The fourth cumulant tensor \(K_u=\operatorname{cum}_4(u_t)\) is part of the population object and is finite.  A non-Gaussian SVAR completion requires \(K_u=\sum_{k=1}^n\kappa_k b_k(Q)^{\otimes4}\) for structural columns \(b_k(Q)=\Sigma_u^{1/2}Qe_k\).
\end{assumption}

\begin{assumption}[Nonempty non-Gaussian SVAR feasible set]\label{ass:svar-nonempty}
The non-Gaussian SVAR/sign feasible set is nonempty for the population law under comparison: there exists \(Q\in O(n)\) and \(\kappa\in\mathcal K_{\delta_4}(j)\) satisfying the sign/zero restrictions and the fourth-cumulant diagonalization equation in Assumption~\ref{ass:cumulant-tensor}.  This assumption is used for finite-valued support-function comparisons; without it, \(h_{\mathrm{SVAR}}(w;P)=-\infty\) by convention.
\end{assumption}

\begin{assumption}[Bounded target fourth-cumulant gap]\label{ass:bounded-gap}
For the labelled target component, the admissible structural fourth-cumulant vector belongs to \(\mathcal K_{\delta_4}(j)\): \(|\kappa_j|\ge\delta_4>0\) and \(|\kappa_\ell-\kappa_j|\ge\delta_4\) for every \(\ell\ne j\) after the target label \(j\) has been fixed by the sign and permutation normalization.  The Gaussian limit and equal-target-kurtosis boundary are excluded from this assumption and must be treated as separate specializations.
\end{assumption}

\begin{assumption}[Common cumulant-matching restriction]\label{ass:cumulant-matching}
The same rotation \(Q\) that generates the reported LP response vector \(\psi_j(Q)\) also diagonalizes the observed fourth-cumulant tensor as in Assumption~\ref{ass:cumulant-tensor}.  Equivalently, the LP-sign candidate is required to belong to the SVAR non-Gaussian feasible rotation set.
\end{assumption}

\begin{assumption}[Generic report direction]\label{ass:generic-report}
The report direction \(w\in\R^{H+1}\) is such that \(w^\transpose\psi_j(Q)\) is not constant on any positive-dimensional connected component of the LP/sign feasible set that contains a non-cumulant-matching rotation.
\end{assumption}

\begin{assumption}[Quantitative cumulant-separation margin]\label{ass:quant-margin}
For the population law \(P\) and report direction \(w\), the polynomial program \(h_{\mathrm{LP}}(w;P)\) has at least one maximizer and the cumulant-filtered envelope \(h_\varepsilon(w;P)\) has a one-sided limit as \(\varepsilon\downarrow0\).  The diagnostic support margin
\[
\chi_w(P)=h_{\mathrm{LP}}(w;P)-\lim_{\varepsilon\downarrow0}h_\varepsilon(w;P)
\]
is strictly positive on the open class used by Theorem~\ref{thm:conditional-margin}.  This is a conditional margin assumption, not a proof of the primitive generic strict-gap claim in Conjecture~\ref{conj:primitive-strict-gap}.
\end{assumption}

\begin{assumption}[Minimal two-shock witness design]\label{ass:two-shock}
For the finite witness, \(n=2\), \(p=1\), \(H\ge1\), \(Q(\varphi)\) is a planar rotation, the sign restrictions leave a nondegenerate interval of angles, the fourth cumulant tensor has two distinct structural excess kurtoses with gap at least \(\delta_4\), and at least one fourth-cumulant diagonalizing angle lies in the LP/sign interval.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: inclusion and equality boundary]\label{thm:inclusion-boundary}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:cumulant-tensor} and \ref{ass:svar-nonempty}, the non-Gaussian SVAR/sign response set is contained in the LP/sign response set:
\[
\mathcal R_{\mathrm{SVAR}}(P)\subseteq\mathcal R_{\mathrm{LP}}(P),
\qquad
\Delta_w(P)\ge0\quad\text{for every }w\in\R^{H+1}.
\]
If Assumption~\ref{ass:cumulant-matching} is imposed on the LP/sign side, then the two support functions are equal for every report direction \(w\).  Conversely, if the LP/sign set contains a response \(\psi_j(Q_0)\) that violates Assumption~\ref{ass:cumulant-matching}\) and \(w^\transpose\psi_j(Q_0)>h_{\mathrm{SVAR}}(w;P)\), then \(\Delta_w(P)>0\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest published result is \citet{PlagborgMollerWolf2021}, whose epsilon-gap is that LP/VAR portability is stated for the same identifying restrictions; this theorem isolates the extra common cumulant-matching restriction needed when \citet{LanneMeitzSaikkonen2017}-style non-Gaussian labeling is added.  (b) The concrete consumer is \citet{DrautzburgWright2023}: their independence-refined sign-restricted confidence sets need this population inclusion to determine whether an LP-sign comparison is sharp or only conservative.

\begin{conjecture}[Conjecture 1: primitive generic strict non-equivalence under fourth cumulants (NOT YET PROVED)]\label{conj:primitive-strict-gap}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:bounded-gap} and \ref{ass:generic-report}, suppose Assumption~\ref{ass:cumulant-matching} is not imposed on the LP/sign side and Assumption~\ref{ass:sign-zero} leaves a positive-dimensional feasible rotation component.  There exists a nonempty open semi-algebraic class \(\mathcal O_{\mathrm{prim}}\) of observable objects \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\), with nonempty \(\mathcal Q_{\mathrm{SVAR}}(P)\), such that for every \((P,w)\in\mathcal O_{\mathrm{prim}}\)
\[
\Delta_w(P)=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)>0.
\]
Moreover, the strict gap is generated by primitive separation between the LP support maximizers and the cumulant-diagonalizing locus:
\[
\inf_{Q\in\arg\max_{\mathcal Q_{\mathrm{LP}}(P)} w^\transpose\psi_j(Q)}
m_{\delta_4}(Q;P)>0,
\]
with the response-flat exceptional set removed by Assumption~\ref{ass:generic-report}.  Equivalently, Conjecture~1 asks to prove Assumption~\ref{ass:quant-margin} from the primitive fourth-cumulant geometry on an open class, not to assume it.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest papers are \citet{LanneMeitzSaikkonen2017}, \citet{GourierouxMonfortRenne2017}, \citet{Guay2021}, and \citet{DrautzburgWright2023}.  They identify or refine SVAR rotations using non-Gaussianity, but they do not derive a primitive open-class support-function separation between an LP/sign relaxation and a single-law non-Gaussian SVAR feasible set.  The epsilon-gap is the derivation of \(\Delta_w(P)>0\) from fourth-cumulant tensor geometry and partial sign inequalities, not the set-theoretic fact that adding a constraint can shrink a feasible set.  (b) Resolving the conjecture gives applied users of \citet{DrautzburgWright2023} a diagnostic warning: a sign-restricted LP robustness band can include response paths that no independent-component SVAR shock could generate.

\begin{theorem}[Theorem 2: conditional quantitative margin theorem]\label{thm:conditional-margin}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:bounded-gap}, \ref{ass:svar-nonempty}, \ref{ass:generic-report}, and \ref{ass:quant-margin}, suppose Assumption~\ref{ass:cumulant-matching} is not imposed on the LP/sign side.  Then
\[
\Delta_w(P)=h_{\mathrm{LP}}(w;P)-h_{\mathrm{SVAR}}(w;P)\ge \chi_w(P)>0.
\]
Here \(\chi_w(P)\) is computable from the finite polynomial optimization problem defined by the LP/sign inequalities, the tensor-mismatch diagnostic \(m_{\delta_4}\), and the limit \(\varepsilon\downarrow0\).  The boundary \(\Delta_w(P)=0\) is contained in the union of the common cumulant-matching face \(\chi_w(P)=0\) and the response-flat exceptional set where \(w^\transpose\psi_j(Q)\) is constant along every LP/sign direction that fails to diagonalize \(K_u\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest papers are again \citet{PlagborgMollerWolf2021}, \citet{LanneMeitzSaikkonen2017}, and \citet{DrautzburgWright2023}.  This theorem is deliberately conditional: its epsilon-gap is only the bookkeeping identity that converts an assumed positive cumulant-filtered support loss into a positive LP/SVAR support-function gap.  (b) The concrete consumer is \citet{DrautzburgWright2023}: their independence-refined sign-restricted VAR workflow can use the theorem as a conditional conservative-outer-set certificate while Conjecture~\ref{conj:primitive-strict-gap} remains the flagship primitive gap.

\begin{conjecture}[Conjecture 2: closed-form two-shock witness (NOT YET PROVED)]\label{conj:two-shock-witness}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:bounded-gap}, \ref{ass:generic-report}, and \ref{ass:two-shock}, let \(Q(\varphi)\) be the planar impact rotation and let the LP/sign restrictions define an interval \(I_{\mathrm{LP}}\subset S^1\).  The non-Gaussian SVAR/sign set reduces to the nonempty finite subset \(I_{\mathrm{SVAR}}=I_{\mathrm{LP}}\cap\{\varphi_\star,\varphi_\star+\pi/2,\varphi_\star+\pi,\varphi_\star+3\pi/2\}\), where \(\varphi_\star\) diagonalizes \(K_u\).  Write the report objective as \(w^\transpose\psi_j(Q(\varphi))=a_w\cos\varphi+b_w\sin\varphi=\rho_w\cos(\varphi-\varphi_w)\), with response-row amplitude \(\rho_w=(a_w^2+b_w^2)^{1/2}>0\), and let \(d_w=\operatorname{dist}_{S^1}(\varphi_w,I_{\mathrm{SVAR}})\).  For a nonempty open set of \((\Gamma_0,\ldots,\Gamma_H,K_u,A,Z,w)\) in which \(\varphi_w\) is an interior LP/sign optimizer and \(\varphi_w\notin I_{\mathrm{SVAR}}\),
\[
\max_{\varphi\in I_{\mathrm{LP}}}w^\transpose\psi_j(Q(\varphi))
>
\max_{\varphi\in I_{\mathrm{SVAR}}}w^\transpose\psi_j(Q(\varphi)),
\]
with the auditable lower bound
\[
\max_{\varphi\in I_{\mathrm{LP}}}w^\transpose\psi_j(Q(\varphi))
-
\max_{\varphi\in I_{\mathrm{SVAR}}}w^\transpose\psi_j(Q(\varphi))
\ge \rho_w(1-\cos d_w)>0.
\]
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet{Guay2021} gives higher-moment rank conditions, \citet{LanneLuoto2021} gives GMM estimation, and \citet{Read2022} gives sign/zero rotation algorithms, but none supplies a minimal LP/SVAR witness where the sign optimizer is a non-diagonalizing rotation.  The epsilon-gap is the finite closed-form certificate, which would make the flagship non-equivalence auditable rather than a high-dimensional existence claim.  (b) The concrete consumer is \citet{PlagborgMollerWolf2021}: the witness would mark the smallest setting in which their sign-restriction portability remains true for common restrictions but fails for a non-Gaussian SVAR restriction omitted from the LP relaxation.

\section{Sanity-check corollaries}
\begin{corollary}[Gaussian or no-higher-moment specialization]\label{cor:gaussian}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:sign-zero}, if \(K_u=0\) and the non-Gaussian cumulant restriction is removed, then both \(\mathcal R_{\mathrm{LP}}(P)\) and \(\mathcal R_{\mathrm{SVAR}}(P)\) reduce to the same sign/zero-restricted rotation set.  The support functions therefore agree, recovering the \citet{PlagborgMollerWolf2021} equivalence for common sign restrictions.
\end{corollary}

\begin{corollary}[Full sign/zero labeling removes the gap]\label{cor:full-label}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:cumulant-tensor}, if the sign/zero restrictions in Assumption~\ref{ass:sign-zero} already pin \(Qe_j\) to the same finite signed-permutation orbit selected by \(K_u\), then \(\mathcal R_{\mathrm{LP}}(P)=\mathcal R_{\mathrm{SVAR}}(P)\) for the labelled shock \(j\).  The non-equivalence requires both a nontrivial cumulant label and a genuinely partial sign/zero pattern.
\end{corollary}

\begin{corollary}[Equal target cumulants are outside the strict-gap specialization]\label{cor:equal-kurtosis-boundary}
Under Assumptions~\ref{ass:finite-var}--\ref{ass:cumulant-tensor}, if a structural completion has \(\kappa_\ell=\kappa_j\) for some \(\ell\ne j\), then Assumption~\ref{ass:bounded-gap} fails for every \(\delta_4>0\).  Consequently Conjectures~\ref{conj:primitive-strict-gap} and \ref{conj:two-shock-witness} make no strict-gap claim at this equal-target-kurtosis boundary; that boundary requires a separate identified-set analysis without the target-separation clause.
\end{corollary}

\section{Proof-sketch route}
Theorem~\ref{thm:inclusion-boundary} is set algebra: write every impact matrix as \(\Sigma_u^{1/2}Q\), observe that cumulant diagonalization is an additional constraint on the same rotation, and compare support functions under constraint inclusion.  Conjecture~\ref{conj:primitive-strict-gap} should reduce to a semi-algebraic optimization argument on the orthogonal group: the fourth-cumulant mismatch \(m_{\delta_4}(Q;P)\) defines a polynomial diagnostic, the diagonalizing locus is a proper algebraic subset of the LP/sign feasible manifold on an open primitive class, and a generic response objective places its LP optimizer a positive diagnostic distance from that locus.  Theorem~\ref{thm:conditional-margin} is the conditional envelope step: once that positive diagnostic support margin is assumed, nested compact filtered sets imply the displayed support-function gap.  Conjecture~\ref{conj:two-shock-witness} is the boundary calculation: parameterize \(O(2)\), including the reflected \(O(2)\) component, by angles, express signs and zeros as sine/cosine inequalities, express fourth-cumulant diagonalization by the vanishing mixed fourth cumulant, and compute the support-function gap from the angular distance between the LP optimum and the finite diagonalizing set.  The main boundary cases to check explicitly are \(K_u=0\), empty SVAR feasibility, equal structural kurtoses, a sign cone that already pins the shock direction, and a report direction orthogonal to the non-diagonalizing tangent.

\section{Honest scope flags}
Theorem~\ref{thm:inclusion-boundary} is routine algebra and should be treated as a setup theorem, not as the flagship novelty claim.  Theorem~\ref{thm:conditional-margin} is also conditional on Assumption~\ref{ass:quant-margin}; it must not be read as a proof that the quantitative margin holds generically.  Conjectures~\ref{conj:primitive-strict-gap} and \ref{conj:two-shock-witness} are not yet proved; the strongest open point is the primitive open-class separation showing that the diagnostic margin \(\chi_w(P)\) follows from fourth-cumulant geometry and partial sign restrictions rather than from assumption.  The proposal deliberately avoids claiming that standard LP estimators estimate fourth cumulants; the LP object here is the population sign/zero response relaxation built from LP/VAR response rows.  The fourth-cumulant gap is stated as a population identification condition, not an inference condition.  The v4 revision responds to the Stage 0.5 rewind by demoting the unconditional strict-gap claim to Conjecture~\ref{conj:primitive-strict-gap} and isolating the margin-based statement as Theorem~\ref{thm:conditional-margin}.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 2, selecting the Lanne--Meitz--Saikkonen anchored strict LP/sign versus non-Gaussian SVAR cumulant-matching boundary; prior verdict: none.
\item v2 (revise) --- patched the admissible cumulant set, replaced the contradictory bounded-gap wording, and made the two-shock lower-bound formula explicit; prior verdict: REVISE.
\item v3 (revise) --- corrected the Guay and Lanne--Liu--Luoto bibliographic record, added finite support-function feasibility assumptions, and sharpened the flagship strict-gap conjecture to a computable cumulant-mismatch margin; prior verdict: REVISE.
\item v4 (revise) --- split the Stage 0.5-rejected strict-gap kernel into an open primitive generic-gap conjecture and a conditional theorem using the quantitative margin assumption; prior verdict: REJECT.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Arias, Rubio-Ramirez, and Waggoner(2018)]{AriasRubioRamirezWaggoner2018}
Arias, J.~E., J.~F. Rubio-Ramirez, and D.~F. Waggoner (2018).
Inference based on structural vector autoregressions identified with sign and zero restrictions: Theory and applications.
\emph{Econometrica} 86(2), 685--720.

\bibitem[Baumeister and Hamilton(2015)]{BaumeisterHamilton2015}
Baumeister, C. and J.~D. Hamilton (2015).
Sign restrictions, structural vector autoregressions, and useful prior information.
\emph{Econometrica} 83(5), 1963--1999.

\bibitem[Drautzburg and Wright(2023)]{DrautzburgWright2023}
Drautzburg, T. and J.~H. Wright (2023).
Refining set-identification in VARs through independence.
\emph{Journal of Econometrics} 235(2), 1827--1847.

\bibitem[Gourieroux, Monfort, and Renne(2017)]{GourierouxMonfortRenne2017}
Gourieroux, C., A. Monfort, and J.-P. Renne (2017).
Statistical inference for independent component analysis: Application to structural VAR models.
\emph{Journal of Econometrics} 196(1), 111--126.

\bibitem[Guay(2021)]{Guay2021}
Guay, A. (2021).
Identification of structural vector autoregressions through higher unconditional moments.
\emph{Journal of Econometrics} 225(1), 27--46.

\bibitem[Jorda(2005)]{Jorda2005}
Jorda, O. (2005).
Estimation and inference of impulse responses by local projections.
\emph{American Economic Review} 95(1), 161--182.

\bibitem[Lanne and Luoto(2021)]{LanneLuoto2021}
Lanne, M. and J. Luoto (2021).
GMM estimation of non-Gaussian structural vector autoregression.
\emph{Journal of Business \& Economic Statistics} 39(1), 69--81.

\bibitem[Lanne, Liu, and Luoto(2026)]{LanneLiuLuoto2026}
Lanne, M., K. Liu, and J. Luoto (2026).
Identifying structural vector autoregressions via non-Gaussianity of potentially dependent shocks.
\emph{The Econometrics Journal}, utag002.

\bibitem[Lanne, Meitz, and Saikkonen(2017)]{LanneMeitzSaikkonen2017}
Lanne, M., M. Meitz, and P. Saikkonen (2017).
Identification and estimation of non-Gaussian structural vector autoregressions.
\emph{Journal of Econometrics} 196(2), 288--304.

\bibitem[Li, Plagborg-Moller, and Wolf(2024)]{LiPlagborgMollerWolf2024}
Li, D., M. Plagborg-Moller, and C.~K. Wolf (2024).
Local projections vs. VARs: Lessons from thousands of DGPs.
\emph{Journal of Econometrics} 244, 105722.

\bibitem[Montiel Olea and Plagborg-Moller(2021)]{MontielOleaPlagborgMoller2021}
Montiel Olea, J.~L. and M. Plagborg-Moller (2021).
Local projection inference is simpler and more robust than you think.
\emph{Econometrica} 89(4), 1789--1823.

\bibitem[Montiel Olea, Plagborg-Moller, Qian, and Wolf(2024)]{MontielOleaPlagborgMollerQianWolf2024}
Montiel Olea, J.~L., M. Plagborg-Moller, E. Qian, and C.~K. Wolf (2024).
Double robustness of local projections and some unpleasant VARithmetic.
NBER Working Paper 32495; \emph{Econometrica}, forthcoming.

\bibitem[Plagborg-Moller and Wolf(2021)]{PlagborgMollerWolf2021}
Plagborg-Moller, M. and C.~K. Wolf (2021).
Local projections and VARs estimate the same impulse responses.
\emph{Econometrica} 89(2), 955--980.

\bibitem[Read(2022)]{Read2022}
Read, M. (2022).
Algorithms for inference in SVARs identified with sign and zero restrictions.
\emph{The Econometrics Journal} 25(3), 699--718.

\bibitem[Rubio-Ramirez, Waggoner, and Zha(2010)]{RubioRamirezWaggonerZha2010}
Rubio-Ramirez, J.~F., D.~F. Waggoner, and T. Zha (2010).
Structural vector autoregressions: Theory of identification and algorithms for inference.
\emph{Review of Economic Studies} 77(2), 665--696.
\end{thebibliography}

\end{document}
