% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_bound\_intersection\_inference, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section originally contained a stage placeholder.
%    Replace each placeholder with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_bound\_intersection\_inference} / \texttt{v1}%
  \\ \large\textit{Contact-cone inference for covariate-level partial-identification bound intersections}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form PartialID anchor.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R,\mathcal B)
=
(\texttt{pid\_bound\_intersection\_inference},\texttt{v1},P,\theta,\mathcal R,\mathcal B).
\]
Here \(P\) is the observable law of \(O=(Y,D,X)\), with \(Y\in[\underline y,\overline y]\), \(D\in\{0,1\}\), and \(X\in\mathcal X\), where \(\mathcal X\) is a compact metric space.  The scalar parameter \(\theta\) is a common treatment-effect or structural-index value constrained by covariate-level partial-identification intervals \([\ell_P(x),u_P(x)]\).  The identifying restrictions \(\mathcal R\) are bounded outcomes, consistency for the observed treatment arm, overlap \(0<\Pr(D=1\mid X=x)<1\) on the effective support, continuity of the bound maps in \(x\), and the maintained common-\(\theta\) restriction \(\theta\in[\ell_P(x),u_P(x)]\) for every \(x\in\mathcal X\).  The bounding functional is the intersection endpoint pair
\[
  \mathcal B(P)=[L(P),U(P)],
  \qquad
  L(P)=\sup_{x\in\mathcal X}\ell_P(x),\quad
  U(P)=\inf_{x\in\mathcal X}u_P(x).
\]
The flagship object is the contact-cone derivative of \(L(P)\), with the upper endpoint obtained by replacing \(\ell\), \(\sup\), and upper contact sets by \(u\), \(\inf\), and lower contact sets.

\begin{abstract}
Many partial-identification problems deliver a scalar interval only after intersecting covariate-level bounds over a rich support.  The lower endpoint \(L(P)=\sup_x \ell_P(x)\) is a nonregular functional when the active covariate set changes with the law.  The central conjecture is a contact-cone phase calculus for \(L(P)\): singleton contact gives an ordinary linear limit, finite ties give a maximum of finitely many Gaussian scores, and continuum contact gives a Gaussian support functional over the flat face.  A second conjecture gives a two-point witness where the centered naive bootstrap has the wrong conditional law at a tie.  If resolved, the result would turn intersection-bound inference from a generic moment-inequality exercise into an endpoint-specific diagnostic based on the geometry of the active level set.
\end{abstract}

\section{Introduction}
Partial-identification intervals often arise by intersecting many covariate-level restrictions.  The statistical question is how to conduct inference on the endpoint when the maximizer of the lower bound is not fixed by the law.

The main claim is that the endpoint has a three-phase contact calculus.  Under smooth first-stage bound maps, the directional derivative of \(L(P)=\sup_x\ell_P(x)\) is the support functional of the tangent scores restricted to the contact set; its limit law changes discretely between singleton, finite-tie, and continuum-flat regimes.

The closest published comparator is \citet[pp. 667--737]{ChernozhukovLeeRosen2013}, whose intersection-bound method treats suprema of estimated functions and adaptive inequality selection, and \citet[Section 3]{FangSantos2019}, whose bootstrap theorem explains why ordinary resampling can fail for directionally but not fully differentiable maps.  The gap is that neither paper isolates the covariate-contact geometry of a partial-identification endpoint or gives a phase threshold that says when the endpoint reduces to a finite-dimensional face and when it remains a continuum Gaussian supremum.  The kernel is a PartialID inference theorem, not a new sharpness theorem for Manski bounds.

The consumer is empirical work that uses covariate-indexed missing-data, monotone-IV, or selection bounds and then reports the intersection interval as the object of inference, as in the quantile-selection and interval-outcome examples discussed by \citet{AndrewsShi2013}.  A reader would report the active contact regime and choose inference by contact geometry, rather than treating every rich-support bound intersection as a generic conditional-moment-inequality problem.

\begin{itemize}[leftmargin=*]
  \item Conjecture 1: the lower endpoint has the contact-cone derivative \(\dot L_P(h)=\sup_{x\in C_L(P)}\dot\ell_P[h](x)\). Gap: \citet{ChernozhukovLeeRosen2013} supplies intersection-bound inference, but not a phase calculus for moving covariate contact sets. Consumer: covariate-level partial-ID bound applications using \citet{Manski1990} or \citet{ManskiPepper2000}.
  \item Conjecture 2: singleton, finite-tie, and continuum-flat contact sets imply three different local laws. Gap: \citet{FangSantos2019} gives the general nonsmooth delta method, but not the endpoint-specific finite-versus-continuum reduction criterion. Consumer: conditional-moment and functional-inequality procedures such as \citet{AndrewsShi2013}, \citet{Armstrong2014}, and \citet{LeeSongWhang2018}.
  \item Theorem 1: the two-point tie model gives a hand-computed bootstrap-failure witness for the centered naive bootstrap. Gap: \citet{ImbensManski2004} treats scalar interval nonuniformity and \citet{FangSantos2019} gives a general failure condition, but neither computes this bound-intersection witness. Consumer: bootstrap implementations for intersection bounds, including the workflow described by \citet{ChernozhukovKimLeeRosen2015}.
\end{itemize}

\section{Related work}
\citet{Manski1990} provides the baseline bounded-outcome partial-identification logic behind the pointwise covariate bounds \(\ell_P(x)\) and \(u_P(x)\).  \citet{ManskiPepper2000} shows how monotone instrumental-variable restrictions sharpen such bounds through covariate-indexed inequalities.  \citet{ImbensManski2004} develops confidence intervals for a scalar partially identified interval and documents nonuniformity when the interval width approaches zero.  \citet{ChernozhukovHongTamer2007} studies confidence regions for parameter sets defined by moment inequalities and equalities, which is the broad set-inference comparator rather than the endpoint-specific object here.  \citet{BeresteanuMolinari2008} develops support-function inference for random-set identification regions, a finite-dimensional face comparator for the continuum contact-set issue.  \citet{AndrewsShi2013} gives uniformly valid conditional-moment-inequality inference and includes intersection-bound examples, but the procedure is not organized around the endpoint contact set.  \citet{ChernozhukovLeeRosen2013} is the closest direct paper because it studies inference on suprema and infima of estimated bound functions with adaptive inequality selection.  \citet{Armstrong2014} shows that conditional-moment-inequality inference can have rate and critical-value changes under weighted Kolmogorov-Smirnov statistics.  \citet{LeeSongWhang2018} uses estimated contact sets for nonparametric functional-inequality tests, which is adjacent to but not the same as inference on an identified-set endpoint.  \citet{KaidoMolinariStoye2019} gives calibrated projection intervals for finite-dimensional moment-inequality models, making clear what is lost when the active face is a covariate contact set rather than a finite constraint face.  \citet{FangSantos2019} supplies the directional-differentiability and bootstrap-failure framework used to phrase the endpoint law.

The in-catalogue PartialID closest entry is `doc/API.md` Section 3.1, especially `t3_thm`, which records a level-set restriction theorem intersecting pointwise Manski intervals across covariate sets.  The closest banked proposal is `pid_rdd_manipulation_bounded_v1`, whose scope flags state that continuous covariates need an additional measurability and regularization layer.  The failed `pid_text_treatment_distortion_v1` proposal is relevant only as a warning that rich Borel-support extrema need simultaneous bands and measurable-selection care.

\section{Formal setup}
Let \(O=(Y,D,X)\sim P\), where \(Y\in[\underline y,\overline y]\), \(D\in\{0,1\}\), and \(X\in\mathcal X\).  The support \(\mathcal X\) is compact.  For each \(x\), the maintained partial-identification restrictions \(\mathcal R\) generate an interval \([\ell_P(x),u_P(x)]\) for a common scalar \(\theta\).  A concrete bounded-outcome example is
\[
  \ell_P(x)=e_P(x)m_{1P}(x)+(1-e_P(x))\underline y-m_{0P}(x),\qquad
  u_P(x)=e_P(x)m_{1P}(x)+(1-e_P(x))\overline y-m_{0P}(x),
\]
where \(e_P(x)=\Pr_P(D=1\mid X=x)\), \(m_{1P}(x)=\E_P[Y\mid D=1,X=x]\), and \(m_{0P}(x)=\E_P[Y\mid D=0,X=x]\).  The proposal allows other pointwise bound maps as long as their first-order perturbations are defined by the same smooth-map condition below.

The identified set for the common scalar is
\[
  \Theta_I(P)=\bigcap_{x\in\mathcal X}[\ell_P(x),u_P(x)]
  =[L(P),U(P)],
  \qquad
  L(P)=\sup_{x\in\mathcal X}\ell_P(x),\quad
  U(P)=\inf_{x\in\mathcal X}u_P(x),
\]
when \(L(P)\le U(P)\).  The upper contact set for the lower endpoint is
\[
  C_L(P)=\{x\in\mathcal X:\ell_P(x)=L(P)\}.
\]
For a regular parametric submodel \(P_t\) with score direction \(h\), write \(\dot\ell_P[h](x)\) for the first-order perturbation of \(\ell_{P_t}(x)\) at \(t=0\).  The contact-phase map is
\[
  \Phi_P(h)=\sup_{x\in C_L(P)}\dot\ell_P[h](x).
\]
For an estimator \(\widehat P_n\), let \(G_\ell\) be the tight Gaussian limit of \(x\mapsto\sqrt n\{\ell_{\widehat P_n}(x)-\ell_P(x)\}\) in \(\ell^\infty(\mathcal X)\).  Define the deterministic contact gap
\[
  \Delta_P(A)=L(P)-\sup_{x\in A}\ell_P(x)
\]
for closed \(A\subseteq\mathcal X\), and the local contact radius \(r_n(P)=\inf\{\Delta_P(\mathcal X\setminus N):N\supset C_L(P)\}/n^{-1/2}\) for a chosen shrinking neighborhood \(N\).

\begin{verbatim}
Locked parameters.
qid = pid_bound_intersection_inference
specialization = v1
observable distribution P = law of O=(Y,D,X), with bounded Y, binary D, and
  compact covariate support X in mathcal X
parameter theta = common scalar constrained by all covariate-level partial-ID
  intervals [ell_P(x), u_P(x)]
identifying restrictions = bounded outcomes; consistency for the observed arm;
  overlap on the effective support; continuous pointwise bound maps; common-theta
  intersection restriction theta in [ell_P(x), u_P(x)] for every x
bounding functional = [L(P), U(P)] where L(P)=sup_x ell_P(x) and
  U(P)=inf_x u_P(x)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Bound maps and compact support]\label{ass:compact-continuous}
\(\mathcal X\) is compact, and \(x\mapsto\ell_P(x)\) and \(x\mapsto u_P(x)\) are continuous.  The intersection is nonempty: \(L(P)\le U(P)\).
\end{assumption}

\begin{assumption}[First-stage process]\label{ass:first-stage-process}
The estimator \(\widehat P_n\) satisfies
\[
  \sqrt n\{\ell_{\widehat P_n}-\ell_P\}\rightsquigarrow G_\ell
  \quad\text{in }\ell^\infty(\mathcal X),
\]
where \(G_\ell\) has a.s. bounded, uniformly continuous sample paths on \(\mathcal X\).  Along regular submodels, \(\ell_{P_t}(x)=\ell_P(x)+t\dot\ell_P[h](x)+o(t)\) uniformly in \(x\).
\end{assumption}

\begin{assumption}[Contact regularity]\label{ass:contact-regularity}
The contact set \(C_L(P)\) is nonempty and compact.  For every sequence \(x_n\) with \(\ell_P(x_n)\to L(P)\), every cluster point lies in \(C_L(P)\).
\end{assumption}

\begin{assumption}[Phase alternatives]\label{ass:phase-alternatives}
One of the following regimes holds: (i) \(C_L(P)=\{x_0\}\); (ii) \(C_L(P)=\{x_1,\ldots,x_K\}\) with \(2\le K<\infty\); or (iii) \(C_L(P)\) contains a compact continuum \(C\) on which \(\ell_P(x)=L(P)\) and the restriction of \(G_\ell\) to \(C\) is non-degenerate.
\end{assumption}

\begin{assumption}[Two-point tie witness]\label{ass:two-point-witness}
For the bootstrap witness, \(\mathcal X=\{a,b\}\), \(\ell_P(a)=\ell_P(b)=0\), \(L(P)=0\), and
\[
  \sqrt n(\ell_{\widehat P_n}(a),\ell_{\widehat P_n}(b))
  \rightsquigarrow (Z_a,Z_b),
  \qquad
  (Z_a,Z_b)\sim N(0,I_2).
\]
The naive centered bootstrap conditionally satisfies
\[
  \sqrt n(\ell_{\widehat P_n^*}(a)-\ell_{\widehat P_n}(a),
           \ell_{\widehat P_n^*}(b)-\ell_{\widehat P_n}(b))
  \rightsquigarrow_{\Pr} (Z_a^*,Z_b^*),
\]
with \(N(0,I_2)\) limit independent of the original sample.
\end{assumption}

\section{Main results}
\begin{conjecture}[Conjecture 1: contact-cone derivative]\label{conj:contact-cone}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:compact-continuous}--\ref{ass:contact-regularity}, the lower endpoint \(L(P)=\sup_x\ell_P(x)\) is Hadamard directionally differentiable tangentially to the first-stage tangent set, with derivative
\[
  \dot L_P(h)=\Phi_P(h)=\sup_{x\in C_L(P)}\dot\ell_P[h](x).
\]
Consequently, under Assumption~\ref{ass:first-stage-process},
\[
  \sqrt n\{L(\widehat P_n)-L(P)\}\rightsquigarrow
  \sup_{x\in C_L(P)}G_\ell(x).
\]
\end{conjecture}

\begin{conjecture}[Conjecture 2: contact-phase threshold]\label{conj:phase-threshold}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:compact-continuous}--\ref{ass:phase-alternatives}, the limiting law in Conjecture~\ref{conj:contact-cone} has three regimes:
\[
  \begin{array}{ll}
  C_L(P)=\{x_0\}: & G_\ell(x_0),\\[2mm]
  C_L(P)=\{x_1,\ldots,x_K\}: & \max_{1\le k\le K}G_\ell(x_k),\\[2mm]
  C_L(P)\supset C\text{ continuum}: & \sup_{x\in C}G_\ell(x).
  \end{array}
\]
Moreover, a local sequence with \(n^{1/2}\{L(P_n)-\sup_{x\notin C_L(P)}\ell_{P_n}(x)\}\to\infty\) has the same active-contact law, while finite limits enter the support functional through a deterministic drift penalty.
\end{conjecture}

\begin{theorem}[Theorem 1: centered-bootstrap failure at a two-point tie]\label{thm:bootstrap-failure}
Under Assumption~\ref{ass:two-point-witness},
\[
  \sqrt n\{L(\widehat P_n)-L(P)\}\rightsquigarrow \max\{Z_a,Z_b\}.
\]
The centered naive bootstrap statistic
\[
  T_n^*=\sqrt n\{L(\widehat P_n^*)-L(\widehat P_n)\}
\]
has conditional weak limits of the form
\[
  \max\{Z_a+Z_a^*,Z_b+Z_b^*\}-\max\{Z_a,Z_b\}
\]
along subsequences where the realized original score converges to \((Z_a,Z_b)\), and this random conditional law is not the fixed law of \(\max\{Z_a,Z_b\}\).
The first display is the continuous mapping theorem for the maximum map.  The second follows by conditioning on the first-stage tie gap and observing that the centering term selects a random face.
\end{theorem}

\section{Sanity-check corollaries}
\begin{corollary}[Unique-contact reduction]\label{cor:unique-contact}
Under Assumptions~\ref{ass:compact-continuous}--\ref{ass:phase-alternatives}, if \(C_L(P)=\{x_0\}\), then the endpoint limit reduces to the ordinary first-stage limit \(G_\ell(x_0)\).  This collapses to scalar endpoint inference because the supremum map is locally linear at a strict maximizer.
\end{corollary}

\begin{corollary}[Finite-cell Manski reduction]\label{cor:finite-cell}
If \(\mathcal X=\{x_1,\ldots,x_K\}\), the proposal reduces to inference on the maximum of \(K\) estimated pointwise lower bounds.  Under Assumption~\ref{ass:two-point-witness} with \(K=2\), Corollary~\ref{cor:finite-cell} is exactly the nonregular maximum law in Theorem~\ref{thm:bootstrap-failure}.
\end{corollary}

\paragraph{Exhibit 9.1: computing the contact-cone object.}
Let \(\mathcal X=\{a,b\}\), \(\ell_P(a)=\ell_P(b)=0\), and \(u_P(a)=u_P(b)=1\).  Then \(L(P)=0\), \(U(P)=1\), \(C_L(P)=\{a,b\}\), and for a perturbation \(h\) with \(\dot\ell_P[h](a)=s_a\), \(\dot\ell_P[h](b)=s_b\),
\[
  \Phi_P(h)=\max\{s_a,s_b\}.
\]
No denominator appears, the two contact labels represent exactly two observable covariate atoms, and the displayed derivative is computed from the Section 6 primitives \((\ell_P(a),\ell_P(b),\dot\ell_P[h](a),\dot\ell_P[h](b))\).

\paragraph{Exhibit 9.2: bootstrap witness.}
In the same two-point design, take realized original scores \((z_a,z_b)=(1,-1)\).  The population limit law is \(\max\{Z_a,Z_b\}\), whereas the conditional centered bootstrap face is
\[
  \max\{1+Z_a^*,-1+Z_b^*\}-1.
\]
This differs from \(\max\{Z_a,Z_b\}\) because the first coordinate is selected with a two-unit deterministic drift, not by a normalization of the same Gaussian maximum.

\section{Proof-sketch route}
For Conjecture~\ref{conj:contact-cone}, the route is: headline \(<-\) unfold \(L(P)=\sup_x\ell_P(x)\) and \(C_L(P)\) \(<-\) substitute the uniform first-stage expansion \(<-\) prove epi-localization to \(C_L(P)\) using the contact-gap condition \(<-\) apply the directional derivative formula for the supremum norm functional \(<-\) transfer the result from deterministic paths to the empirical process by stochastic equicontinuity \(<-\) verify measurability of the contact support functional.  This gives \(k=4\) substantive steps: localization, supremum derivative, empirical-process transfer, and measurability.  For Conjecture~\ref{conj:phase-threshold}, the route is: headline \(<-\) unfold the derivative \(<-\) classify \(C_L(P)\) by Assumption~\ref{ass:phase-alternatives} \(<-\) show singleton evaluation is linear \(<-\) show finite contact is a maximum over a finite Gaussian vector \(<-\) show continuum contact is a support functional on \(\ell^\infty(C)\) \(<-\) add local drift penalties through the contact-gap expansion; here \(k=4\).  Theorem~\ref{thm:bootstrap-failure} is a direct two-coordinate calculation using the continuous mapping theorem and conditional weak convergence for the bootstrap scores.

\section{Honest scope flags}
Conjectures~\ref{conj:contact-cone} and \ref{conj:phase-threshold} are not yet proved.  The proposal assumes a tight first-stage process for the bound map rather than proving kernel or series conditions for a specific estimator.  The continuum-contact case may require an outer-probability formulation if the contact set is not separable under the covariance metric.  The upper endpoint \(U(P)\) is omitted from the main statements only to avoid duplication; it should follow by applying the same argument to \(-u_P\).  No claim is made that generic conditional-moment-inequality confidence sets are invalid; the claim is that they do not identify the endpoint-specific phase law.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
  \item v1 (cold-start) -- initial draft centered on the contact-cone derivative, three-phase active-set law, and two-point bootstrap-failure witness; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Andrews and Shi(2013)]{AndrewsShi2013}
Andrews, D. W. K. and X. Shi (2013).
\newblock Inference based on conditional moment inequalities.
\newblock \emph{Econometrica} 81(2), 609--666.
\newblock \url{https://doi.org/10.3982/ECTA9370}.

\bibitem[Armstrong(2014)]{Armstrong2014}
Armstrong, T. B. (2014).
\newblock Weighted KS statistics for inference on conditional moment inequalities.
\newblock \emph{Journal of Econometrics} 181(2), 92--116.
\newblock \url{https://doi.org/10.1016/j.jeconom.2014.04.021}.

\bibitem[Beresteanu and Molinari(2008)]{BeresteanuMolinari2008}
Beresteanu, A. and F. Molinari (2008).
\newblock Asymptotic properties for a class of partially identified models.
\newblock \emph{Econometrica} 76(4), 763--814.
\newblock \url{https://doi.org/10.1111/j.1468-0262.2008.00859.x}.

\bibitem[Chernozhukov, Hong, and Tamer(2007)]{ChernozhukovHongTamer2007}
Chernozhukov, V., H. Hong, and E. Tamer (2007).
\newblock Estimation and confidence regions for parameter sets in econometric models.
\newblock \emph{Econometrica} 75(5), 1243--1284.
\newblock \url{https://doi.org/10.1111/j.1468-0262.2007.00794.x}.

\bibitem[Chernozhukov, Kim, Lee, and Rosen(2015)]{ChernozhukovKimLeeRosen2015}
Chernozhukov, V., W. Kim, S. Lee, and A. M. Rosen (2015).
\newblock Implementing intersection bounds in Stata.
\newblock \emph{Stata Journal} 15(1), 21--44.
\newblock \url{https://doi.org/10.1177/1536867X1501500103}.

\bibitem[Chernozhukov, Lee, and Rosen(2013)]{ChernozhukovLeeRosen2013}
Chernozhukov, V., S. Lee, and A. M. Rosen (2013).
\newblock Intersection bounds: Estimation and inference.
\newblock \emph{Econometrica} 81(2), 667--737.
\newblock \url{https://doi.org/10.3982/ECTA8718}.

\bibitem[Fang and Santos(2019)]{FangSantos2019}
Fang, Z. and A. Santos (2019).
\newblock Inference on directionally differentiable functions.
\newblock \emph{Review of Economic Studies} 86(1), 377--412.
\newblock \url{https://doi.org/10.1093/restud/rdy049}.

\bibitem[Imbens and Manski(2004)]{ImbensManski2004}
Imbens, G. W. and C. F. Manski (2004).
\newblock Confidence intervals for partially identified parameters.
\newblock \emph{Econometrica} 72(6), 1845--1857.
\newblock \url{https://doi.org/10.1111/j.1468-0262.2004.00555.x}.

\bibitem[Kaido, Molinari, and Stoye(2019)]{KaidoMolinariStoye2019}
Kaido, H., F. Molinari, and J. Stoye (2019).
\newblock Confidence intervals for projections of partially identified parameters.
\newblock \emph{Econometrica} 87(4), 1397--1432.
\newblock \url{https://doi.org/10.3982/ECTA14075}.

\bibitem[Lee, Song, and Whang(2018)]{LeeSongWhang2018}
Lee, S., K. Song, and Y.-J. Whang (2018).
\newblock Testing for a general class of functional inequalities.
\newblock \emph{Econometric Theory} 34(5), 1018--1064.
\newblock \url{https://doi.org/10.1017/S0266466617000329}.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review} 80(2), 319--323.

\bibitem[Manski and Pepper(2000)]{ManskiPepper2000}
Manski, C. F. and J. V. Pepper (2000).
\newblock Monotone instrumental variables: With an application to the returns to schooling.
\newblock \emph{Econometrica} 68(4), 997--1010.
\newblock \url{https://doi.org/10.1111/1468-0262.00144}.
\end{thebibliography}

\end{document}
