\begin{proof}[Proof of \cref{obj:lem:unit-fe-collapse}]
The horizon assumption gives \(T>0\), and the cohort-support assumption gives \(\top\in\mathcal C\), so \(\mathcal C\) is nonempty.  The deterministic support assumption gives \(G_i\in\mathcal C\) for every array \(N\) and every unit \(i\).  Fix \(N\ge |\mathcal C|\).  The share-limit assumption supplies \(N>0\) and strictly positive finite cohort counts for every \(g\in\mathcal C\).  With these positive counts and the collapsed rank condition, the finite collapsed PPML criterion has a unique maximizer.  Lift any collapsed parameter to unit fixed effects by choosing unit levels whose linear index equals the collapsed cohort-time index plus
\[
\log\{b_{iN}/\bar b_{G_iN}\},
\]
while keeping the same time levels and treatment coefficient.  At this lifted parameter, each unit residual is exactly this baseline ratio times the residual in its cohort-period cell.  Summing within a supported cohort uses
\[
\sum_{i\in I_{gN}} b_{iN}/\bar b_{gN}=n_{gN}.
\]
Consequently, in every unit-FE direction the lifted unit score equals the collapsed score in the corresponding baseline-ratio-aggregated direction.  Since the collapsed maximizer has zero score in every collapsed direction, its lift has zero score in every unit-FE direction and therefore maximizes the unit-FE criterion.  Together with \(T>0\) and \(\top\in\mathcal C\), the same deterministic support, positive supported counts, and collapsed rank condition give full column rank for the unit design, so this unit maximizer is unique.  Its treatment coordinate is the treatment coordinate of the finite collapsed maximizer.
This proves, for every \(N\ge|\mathcal C|\), the asserted uniqueness of the finite unit-FE and finite collapsed maximizers and the equality between \(\beta_N^\star(\delta)\) and the finite collapsed treatment coordinate.
Next, the finite cell masses \(n_{gN}/(NT)\) converge to \(q_{gt}=\pi_g/T\), and the finite observed cohort means converge to \(m_{gt}(\delta)\), because the within-cohort baseline averages converge to \(\bar b_g\) and the factors \(\exp(\gamma_{t0})\exp\{D_{gt}\delta_{gt}\}\) are fixed.  The selected finite collapsed maximizers therefore converge to the limiting collapsed maximizer by the finite Poisson argmax-continuity theorem, using the same collapsed rank condition and the uniqueness supplied by \cref{obj:lem:pseudo-true-ppml-projection}.
Taking the treatment-coordinate projection gives convergence of the finite collapsed treatment coordinates to \(\beta^\star(\delta)\); since those coordinates equal \(\beta_N^\star(\delta)\) for all sufficiently large \(N\), it follows that \(\beta_N^\star(\delta)\to\beta^\star(\delta)\).
Finally fix \(N\ge|\mathcal C|\) and an alternative positive baseline array \(b'_{iN}\) with the same within-cohort averages as \(b_{iN}\) for every \(g\in\mathcal C\).  The finite untreated cohort mean is \(\bar b_{gN}\exp(\gamma_{t0})\), and the finite observed cohort mean only multiplies this by \(\exp\{D_{gt}\delta_{gt}\}\); hence all finite observed cohort means are unchanged under \(b'\).  The entire finite collapsed criterion is therefore unchanged, so its selected maximizer is unchanged.
Applying the exact finite unit-FE/collapsed treatment-coordinate equality once for \(b'\) and once for \(b\) gives
\[
\beta_N^\star(\delta;b')=\beta_N^\star(\delta;b).
\]

\end{proof}
