\begin{proof}[Proof of Four-Cohort Sign Reversal]
\begin{enumerate}
\item The defining conditions of the region in \cref{obj:def:global-sign-reversal-region} are checked directly for the displayed primitive.  The horizon condition is \(4\le 4\).  The support contains the never-treated cohort and the finite cohorts \(2,3,4\), all dated after period \(1\), and these four cohorts give the required four-cohort frontier scope.  The shares sum to
\[
\sum_{g\in\mathcal C}\pi_g=4\cdot \frac14=1,
\]
and, since \(\bar b_g=1\) and \(\gamma_{t0}=0\), the untreated mean representation is \(1=1\cdot \exp(0)\) in every supported cell.

For rank, let \(a\) be a collapsed parameter whose weighted quadratic design norm is zero.  Each summand is nonnegative and each supported cell mass is nonzero, so every collapsed index \(r_{gt}'a\) is zero.  Evaluating these zero equations first at the never-treated cohort in period \(1\) gives the intercept equal to zero; evaluating finite cohorts in period \(1\) gives all cohort dummy coordinates equal to zero; evaluating the never-treated cohort across periods gives all time dummy coordinates equal to zero; and evaluating the cohort \(2\), period \(2\), treated cell then gives the treatment coordinate equal to zero.  Hence \(a=0\), proving the collapsed design rank condition.

The sign condition is obtained from the primitive sign index \(\Phi\) in \cref{obj:def:frontier-elimination-handle}.  In the multiplier subfamily with common treated multiplier \(x\) off cell \((2,4)\) and multiplier \(y\) at \((2,4)\),
\[
\Phi=\frac{5x^2+12x-2y-15}{16}.
\]
Substituting \(x=101/100\) and \(y=4\) gives
\[
\Phi=-\frac{11559}{32000}<0.
\]
The sign characterization of the frontier index gives \(\beta^\star(\delta)<0\), and the restricted primitive has the same primitive treatment coordinate.  Together with the strict positivity of the treated effects verified in the next step, all clauses of \cref{obj:def:global-sign-reversal-region} hold.

\item If \(D_{gt}=1\), then the specified effect is either \(\log 4\) or \(\log(101/100)\).  Both are strictly positive because \(4>1\) and \(101/100>1\).

\item For the designated cell \((2,4)\), treatment is on and the effect is \(\delta_{2,4}=\log 4\).  For every other treated supported cell, the effect is \(\log(101/100)\).  Since \(101/100<4\) and the logarithm is strictly increasing on positive numbers,
\[
\log(101/100)<\log 4=\delta_{2,4}.
\]


\item At the zero-effect vector, the fitted mean is \(1\) in every supported cell by \cref{obj:prop:homogeneous-effect-reduction}.  Hence the mean weights in \cref{obj:def:weighted-fwl-residual} are all \(1/16\).  The displayed candidate residual table has row sums and column sums all equal to zero.  Moreover, treatment minus this table equals
\[
-\frac38+c_g+s_t,
\]
with
\[
(c_2,c_3,c_4,c_\infty)=\Bigl(\frac34,\frac12,\frac14,0\Bigr),
\qquad
(s_1,s_2,s_3,s_4)=\Bigl(0,\frac14,\frac12,\frac34\Bigr),
\]
so treatment minus the table lies in the nuisance fixed-effect space.  The zero row and column sums make the table orthogonal, under the constant weights \(1/16\), to every nuisance regressor and therefore to the whole nuisance space.  Thus the weighted projection of treatment onto the nuisance space is treatment minus the table, and the residual is the table.  This gives exactly
\[
\widetilde W_{gt}
=
\frac{1}{8}
\begin{pmatrix}
-3 & 3 & 1 & -1\\
-1 & -3 & 3 & 1\\
1 & -1 & -3 & 3\\
3 & 1 & -1 & -3
\end{pmatrix}_{gt}.
\]


\item Evaluating the residual table at the designated cell gives
\[
\widetilde W_{2,4}(0)=-\frac18.
\]


\item The residual energy at zero effects is
\[
\sum_{g,t} q_{gt}\,\mu^\star_{gt}(0)\,\widetilde W_{gt}(0)^2
=
\frac1{16}\sum_{g,t}\widetilde W_{gt}(0)^2
=
\frac1{16}\cdot\frac{80}{64}
=
\frac5{64}.
\]
\cref{obj:thm:sharp-ppml-forbidden-sign}, applied to the treated cell \((2,4)\), gives
\[
\left.\frac{d}{dx}\beta^\star(\delta_{2,4}=x,\delta_{gt}=0\text{ otherwise})\right|_{x=0}
=
\frac{q_{2,4}\,B_{2,4}\,\exp(0)\,\widetilde W_{2,4}(0)}
{5/64}.
\]
Here \(q_{2,4}=1/16\), \(B_{2,4}=1\), and \(\widetilde W_{2,4}(0)=-1/8\).  Therefore the derivative is
\[
\frac{(1/16)\cdot 1\cdot 1\cdot(-1/8)}{5/64}
=
-\frac{1}{10}.
\]


\item By continuity of the weighted FWL residual in the effect vector, \(\widetilde W_{2,4}(\delta)\) is continuous at the zero-effect vector.  Since \(\widetilde W_{2,4}(0)=-1/8<0\), the inverse image of \(( -\infty,0)\) is a neighborhood of zero.  Choose a finite coordinate neighborhood contained in that inverse image, choose a positive radius for each coordinate neighborhood, and let \(\varepsilon\) be the minimum of those radii, or \(1\) if the finite coordinate set is empty.

Now take any \(\delta'\) such that \(|\delta'_{gt}|<\varepsilon\) on every supported cell and \(\delta'_{gt}>0\) on every treated supported cell.  Define the supported truncation \(\delta^s\) by \(\delta^s_{gt}=\delta'_{gt}\) on \(g\in\mathcal C\) and \(\delta^s_{gt}=0\) outside the support.  The choice of \(\varepsilon\) puts \(\delta^s\) in the coordinate neighborhood, hence \(\widetilde W_{2,4}(\delta^s)<0\).  Changing effects outside supported cohorts leaves the limiting criterion, fitted means, and weighted FWL residuals unchanged, so \(\widetilde W_{2,4}(\delta')=\widetilde W_{2,4}(\delta^s)<0\).  Applying \cref{obj:thm:sharp-ppml-forbidden-sign} again at the treated cell \((2,4)\), the derivative of \(x\mapsto\beta^\star\) with the \((2,4)\) coordinate of \(\delta'\) replaced by \(x\), evaluated at \(x=\delta'_{2,4}\), has the same sign as \(\widetilde W_{2,4}(\delta')\), because the denominator and multiplicative prefactor are strictly positive.  Thus this derivative is strictly negative for every such strictly positive \(\delta'\).

\item The seven conclusions above are assembled in the order stated: region membership, positivity of treated effects, uniqueness of the largest treated effect at \((2,4)\), the full weighted FWL residual table, the late-cell residual \(-1/8\), the exact late-cell derivative at zero, and the local negative derivative statement under strict positivity of treated supported effects.
\end{enumerate}
\end{proof}
