\begin{proof}[Proof of \cref{obj:prop:homogeneous-effect-reduction}]
\begin{enumerate}
\item Let \(\infty\) denote the never-treated reference cohort, and define the candidate collapsed parameter
\(\theta^0=(a^0,\delta_0)\) as follows: the intercept coordinate is
\(\log \bar b_\infty\); the cohort-dummy coordinate for a supported finite cohort
\(c\) is
\[
\log \bar b_c-\log \bar b_\infty;
\]
and the non-base-period time-dummy coordinate for period \(u\) is
\(\gamma_{u0}\). \Cref{obj:ass:unit-untreated-exponential-mean} gives the normalization \(\gamma_{10}=0\). Hence the time-dummy contribution equals \(\gamma_{t0}\): if \(t\) is the base period all time dummies vanish and \(\gamma_{t0}=0\), while if \(t\) is not the base period exactly its own dummy contributes. Likewise, the cohort-dummy contribution is \(0\) for \(g=\infty\), and is \(\log\bar b_g-\log\bar b_\infty\) for \(g\neq\infty\).

\item Therefore, for every supported cohort \(g\in\mathcal C\) and every period \(t\), the collapsed linear index at \(\theta^0\) is
\[
\eta_{gt}(\theta^0)
=
\log \bar b_g+\gamma_{t0}+D_{gt}\delta_0 .
\]
This is checked by the two cohort cases \(g=\infty\) and \(g\neq\infty\), using the preceding dummy-sum identities.

\item The homogeneous-effect hypothesis implies
\[
D_{gt}\delta_{gt}=D_{gt}\delta_0
\]
for every \(g\in\mathcal C\) and \(t\). Indeed, if \(D_{gt}=1\), the common treated-cell effect assumption gives \(\delta_{gt}=\delta_0\); if \(D_{gt}=0\), both products are zero.

\item Combining the previous two displays with \(B_{gt}=\bar b_g\exp(\gamma_{t0})\), the observed collapsed mean satisfies
\[
m_{gt}(\delta)
=
B_{gt}\exp(D_{gt}\delta_{gt})
=
\exp\{\eta_{gt}(\theta^0)\}.
\]
In particular \(m_{gt}(\delta)>0\), and
\[
\log m_{gt}(\delta)=\eta_{gt}(\theta^0).
\]


\item For any \(m>0\) and any real \(\eta\),
\[
m\eta-\exp(\eta)
\le
m\log m-\exp(\log m),
\]
with strict inequality when \(\eta\neq\log m\). This follows from \(1+x\le \exp(x)\), and from its strict form when \(x\neq0\), applied to \(x=\eta-\log m\) and then rearranged after multiplying by \(m>0\).

\item The cell masses are strictly positive. The rank condition in \cref{obj:ass:collapsed-design-rank} first rules out \(T=0\): the direction with zero nuisance coordinates and treatment coordinate one would otherwise have zero weighted squared index, contradicting collapsed full rank. Thus \(T>0\), and since \(\pi_g\in(0,1)\),
\[
q_{gt}=\frac{\pi_g}{T}>0 .
\]


\item For any collapsed parameter \(\theta\), write
\[
L(\theta;\delta)
=
\sum_{g\in\mathcal C}\sum_t
q_{gt}\{m_{gt}(\delta)\eta_{gt}(\theta)-\exp(\eta_{gt}(\theta))\}.
\]
Using \(\log m_{gt}(\delta)=\eta_{gt}(\theta^0)\) cell by cell and the weak scalar inequality above gives
\[
L(\theta;\delta)\le L(\theta^0;\delta).
\]
Thus \(\theta^0\) is a global maximizer of the limiting collapsed criterion.

\item This maximizer is unique. Suppose \(L(\theta;\delta)=L(\theta^0;\delta)\). If \(\theta\neq\theta^0\), then \(\theta-\theta^0\neq0\), so \cref{obj:ass:collapsed-design-rank} gives a positive weighted sum of squared index differences. Hence some supported cell \((g_0,t_0)\) must have
\[
\eta_{g_0t_0}(\theta)\neq \eta_{g_0t_0}(\theta^0);
\]
otherwise linearity of the index under subtraction would make every squared term zero. At this cell the strict scalar inequality applies, while all other cells satisfy the weak inequality. Since \(q_{g_0t_0}>0\), summing yields
\[
L(\theta;\delta)<L(\theta^0;\delta),
\]
contradicting the assumed equality. Therefore \(\theta=\theta^0\).

\item Consequently, the selected limiting collapsed projection in \cref{obj:def:collapsed-population-projection} is exactly
\[
\theta^\star(\delta)=\theta^0,
\]
because \(\theta^0\) exists as the unique global maximizer.

\item The treatment coordinate of \(\theta^0\) is \(\delta_0\), so
\[
\beta^\star(\delta)=\delta_0.
\]
For every \(g\in\mathcal C\) and every \(t\),
\[
\mu^\star_{gt}(\delta)
=
\exp\{\eta_{gt}(\theta^\star(\delta))\}
=
\exp\{\log\bar b_g+\gamma_{t0}+D_{gt}\delta_0\}
=
B_{gt}\exp(D_{gt}\delta_0).
\]

\end{enumerate}
\end{proof}
