\begin{proof}[Proof of \cref{obj:thm:primitive-global-frontier}]
Write \(q_{gt}=\pi_g/T\), and write
\[
Z=\sum_{(g,t)\in H}q_{gt}B^{obs}_{gt}.
\]
The proof proceeds by the same reductions used in the collapsed frontier calculation.

\begin{enumerate}
\item Since \(T\ge 4\), in particular \(T>0\). The frontier sign calculation applies because the never-treated cohort is in \(\mathcal C\) and the collapsed rank condition holds. At the frontier fit with treatment coefficient set to zero, the nuisance scores vanish and the treatment score is
\[
\frac{\Phi}{T M}.
\]
The denominator is strictly positive: \(T>0\) and \(M\) is a sum of strictly positive primitive cell masses. Therefore the sign, zero, and positive sign of \(\beta^\star(\delta)\) agree exactly with those of \(\Phi\). This gives
\[
\beta^\star(\delta)<0\iff \Phi<0,\qquad
\beta^\star(\delta)=0\iff \Phi=0,\qquad
0<\beta^\star(\delta)\iff 0<\Phi .
\]

\item For every supported cohort \(g\), the first-period treatment indicator is zero. If \(g=\infty\), this is the never-treated path. If \(g\) is finite, support excludes adoption in the first period; hence treatment in the first period would force the adoption date to be the first period, a contradiction. Also \(D_{\infty t}=0\) for every \(t\), and \cref{obj:ass:unit-untreated-exponential-mean} gives the first-period normalization \(\gamma_{10}=0\). Thus, for every \(g\in\mathcal C\) and every \(t\),
\[
B^{obs}_{gt}
=
\frac{m_{g1}m_{\infty t}}{m_{\infty 1}}
=
\frac{\bar b_g e^{\gamma_{10}}\bar b_\infty e^{\gamma_{t0}}}
{\bar b_\infty e^{\gamma_{10}}}
=
\bar b_g e^{\gamma_{t0}}
=
B_{gt}.
\]

\item \cref{obj:ass:multicohort-frontier-scope} supplies a supported finite cohort adopting in the second paper period; in that period its treatment indicator equals one. Hence \(H\) is nonempty. For every \((g,t)\in H\), both \(q_{gt}\) and \(B^{obs}_{gt}=B_{gt}\) are positive. Consequently every summand in \(Z\) is nonnegative and at least one is strictly positive, so
\[
Z>0.
\]

\item We next identify membership in \(\mathcal R_T\). If the induced primitive tuple belongs to \(\mathcal R_T\), then \cref{obj:def:global-sign-reversal-region} includes negativity of the primitive treatment coefficient. The restricted primitive coefficient is exactly \(\beta^\star(\delta)\), so Step 1 gives \(\Phi<0\).

Conversely suppose \(\Phi<0\). The horizon, support, and frontier-scope clauses are the assumptions of the theorem. The share simplex clause follows from the cohort-share limit and array support, which imply \(\sum_{g\in\mathcal C}\pi_g=1\). The baseline clause is witnessed by \(g\mapsto \bar b_g\), since the primitive untreated coordinate is \(\bar b_g e^{\gamma_{t0}}\). The positive-effect clause is \cref{obj:ass:strict-positive-effects}. The rank clause is \cref{obj:ass:collapsed-design-rank}, after rewriting the supported-cell sum as the corresponding sum over \(g\in\mathcal C\) and \(t\). Finally Step 1 gives \(\beta^\star(\delta)<0\), and the restricted primitive coefficient equals \(\beta^\star(\delta)\). Thus the induced primitive tuple is in \(\mathcal R_T\).

\item In the four-period support \(\{2,3,4,\infty\}\), expand \cref{obj:def:frontier-elimination-handle} with equal shares, unit limiting baselines, zero untreated time effects, multiplier \(x\) on every treated cell except \((2,4)\), and multiplier \(y\) at \((2,4)\). Since \(x>1\) and \(y>1\), \(\exp(\log x)=x\) and \(\exp(\log y)=y\). Direct summation of the four row margins, four column margins, treated total, and grand total gives
\[
\Phi=\frac{5x^2+12x-2y-15}{16}.
\]

\item The displayed numerical identity is then ordinary rational arithmetic:
\[
\frac{5(101/100)^2+12(101/100)-15}{2}
=\frac{4441}{4000}.
\]

\item For the witness \(W_4\) of \cref{obj:def:four-cohort-witness}, the effect vector is the preceding four-period family with \(x=101/100\) and \(y=4\). Substituting these values in Step 5 gives
\[
\Phi
=
\frac{5(101/100)^2+12(101/100)-2\cdot 4-15}{16}
=
-\frac{11559}{32000}.
\]

\item Let \((g,t)\in H\). Then \(D_{gt}=1\). Step 2 gives \(B^{obs}_{gt}=B_{gt}\). Moreover
\[
\tau_{gt}
=
\frac{m_{gt}}{B^{obs}_{gt}}-1
=
\frac{B_{gt}\exp(\delta_{gt})}{B_{gt}}-1
=
\exp(\delta_{gt})-1,
\]
using \(B_{gt}>0\). Also
\[
\omega_{gt}=\frac{q_{gt}B^{obs}_{gt}}{Z}>0
\]
because \(q_{gt}>0\), \(B^{obs}_{gt}>0\), and \(Z>0\).

\item The weights sum to one by the definition of \(Z\):
\[
\sum_{(g,t)\in H}\omega_{gt}
=
\sum_{(g,t)\in H}\frac{q_{gt}B^{obs}_{gt}}{Z}
=
\frac{Z}{Z}
=
1,
\]
again using \(Z>0\).

\item Expanding the definition of the counterfactual-share target and using \(B^{obs}_{gt}>0\),
\[
PTT
=
\sum_{(g,t)\in H}\frac{q_{gt}B^{obs}_{gt}}{Z}
\left(\frac{m_{gt}}{B^{obs}_{gt}}-1\right)
=
\frac{\sum_{(g,t)\in H}q_{gt}m_{gt}}{Z}
-\frac{\sum_{(g,t)\in H}q_{gt}B^{obs}_{gt}}{Z}.
\]
The second fraction is \(1\), so
\[
PTT
=
\frac{\sum_{(g,t)\in H}q_{gt}m_{gt}}
{\sum_{(g,t)\in H}q_{gt}B^{obs}_{gt}}
-1.
\]

\item Finally suppose \(\Phi<0\). Step 1 gives \(\beta^\star(\delta)<0\). For \(PTT\), every treated cell has \(\omega_{gt}>0\), and \cref{obj:ass:strict-positive-effects} gives \(\delta_{gt}>0\), hence \(\exp(\delta_{gt})>1\) and \(\tau_{gt}>0\). Since \(H\) is nonempty, the finite sum defining \(PTT\) contains at least one strictly positive term and no negative terms. Therefore \(PTT>0\). Hence
\[
\Phi<0\quad\Longrightarrow\quad \beta^\star(\delta)<0<PTT .
\]
\end{enumerate}
\end{proof}
