\begin{proof}[Proof of \cref{obj:thm:sharp-ppml-forbidden-sign}]
Write \(W_{gt}=\widetilde W_{gt}(\delta)\) and
\[
\mathcal E=\sum_{g\in\mathcal C}\sum_{t=1}^T
q_{gt}\mu^\star_{gt}(\delta)W_{gt}^2 .
\]
\begin{enumerate}
\item First, \(\mathcal E>0\). Each summand is nonnegative, since \(q_{gt}>0\), \(\mu^\star_{gt}(\delta)>0\), and \(W_{gt}^2\ge0\). If \(\mathcal E\) were not positive, then \(\mathcal E=0\), and every summand would have to vanish. Positivity of \(q_{gt}\mu^\star_{gt}(\delta)\) then gives \(W_{gt}=0\) for every supported cohort-period cell. Let \(\rho^\star(\delta)\) be the weighted nuisance projection coefficient used to define the FWL residual, and set the collapsed parameter
\[
a=(-\rho^\star(\delta),1).
\]
Its treatment coordinate is one, so \(a\ne0\). The coefficient form of the FWL residual gives, for every supported cell,
\[
r_{gt}'a
=
D_{gt}-\sum_j X_{gt,j}\rho^\star_j(\delta)
=
W_{gt}
=
0.
\]
Hence
\[
\sum_{g\in\mathcal C}\sum_{t=1}^T q_{gt}(r_{gt}'a)^2=0,
\]
contradicting the full-rank condition in \cref{obj:ass:collapsed-design-rank}. Thus \(\mathcal E>0\).

\item The scalar multiplying \(W_{ks}\) in the displayed derivative is strictly positive:
\[
c
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})}{\mathcal E}
>0.
\]
Indeed \(q_{ks}>0\), \(B_{ks}>0\), \(\exp(\delta_{ks})>0\), and the previous step gives \(\mathcal E>0\).

\item Consider the path that replaces only \(\delta_{ks}\) by \(x\). Since \(D_{ks}=1\), this changes the collapsed observed mean only in cell \((k,s)\), where it is \(B_{ks}\exp(x)\), and leaves all other collapsed means unchanged. The collapsed criterion is rewritten as a finite Poisson objective on the supported cohort-period table, with positive masses, positive means, and design map \(\theta\mapsto(r_{gt}'\theta)_{g,t}\). The rank condition makes this design map injective: if two parameters have the same fitted index in every supported cell, their difference violates \cref{obj:ass:collapsed-design-rank} unless it is zero.

\item The derivative of the selected treatment coordinate is identified from the corresponding linearized score. For any solution \(v\) of that linearized score, let \(v_\beta\) be its treatment coordinate. Normalize the weights \(q_{gt}\mu^\star_{gt}(\delta)\) by their positive total \(Z\), let \(Y\) be the one-cell source divided by \(\mu^\star\), and let the nuisance part of \(v\) lie in the fixed-effect nuisance span. The linearized score gives orthogonality of \(Y-v_\beta D-\alpha\) both to \(D\) and to every nuisance direction. Since \(\langle W,W\rangle>0\), the scalar FWL identity yields
\[
v_\beta
=
\frac{\langle W,Y\rangle}{\langle W,W\rangle}.
\]
The one-cell source gives
\[
\langle W,Y\rangle
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})W_{ks}}{Z},
\qquad
\langle W,W\rangle
=
\frac{\mathcal E}{Z},
\]
so
\[
v_\beta
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})W_{ks}}{\mathcal E}.
\]


\item The one-cell finite-Poisson derivative calculation therefore gives
\[
\frac{d}{dx}\,
\beta^\star\!\bigl(\delta \text{ with } \delta_{ks}\text{ replaced by }x\bigr)
\Big|_{x=\delta_{ks}}
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})W_{ks}}{\mathcal E}.
\]
This proves differentiability at \(x=\delta_{ks}\) and the displayed derivative formula.

\item Since the derivative is \(cW_{ks}\) with \(c>0\),
\[
cW_{ks}<0 \iff W_{ks}<0.
\]
The forward implication follows because \(W_{ks}\ge0\) would imply \(cW_{ks}\ge0\); the reverse implication is multiplication by a positive scalar.

\item Again using \(c>0\), hence \(c\ne0\),
\[
cW_{ks}=0 \iff W_{ks}=0.
\]


\item Finally, multiplication by the same positive scalar gives
\[
0<cW_{ks} \iff 0<W_{ks}.
\]
Substituting \(W_{ks}=\widetilde W_{ks}(\delta)\) gives the three asserted sign equivalences.
\end{enumerate}
\end{proof}
