% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_data\_fusion\_k\_source, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_data\_fusion\_k\_source} / \texttt{v1}%
  \\ \large\textit{A k-source overlap-hedge criterion for observational data fusion under selection diagrams}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is an exact-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},\text{graph/selection diagram},
\text{treatment},\text{target estimand},\text{identifying assumptions}).
\]
Here \(\texttt{qid}=\texttt{eid\_data\_fusion\_k\_source}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph is a finite acyclic
semi-Markovian target diagram \(G^\star=(V,E,U)\) augmented by \(k\) source
selection nodes \(S_1,\ldots,S_k\), source-observation sets
\(O_j\subseteq V\), and a typed factor-local constraint set
\(\mathcal C=\mathcal C^{\mathrm{obs}}\cup\mathcal C^{\mathrm{fix}}\).
An ordinary clause \(c=(\mathrm{obs},j,A,B)\in\mathcal C^{\mathrm{obs}}\)
asserts that the target conditional kernel \(P^\star(A\mid B)\) equals the
selected-source conditional read from \(P_j(O_j\mid S_j=1)\) whenever
\(A\cup B\subseteq O_j\).  A nested clause
\(c=(\mathrm{fix},j,H,D,R)\in\mathcal C^{\mathrm{fix}}\) asserts that, at
ID-recursion CADMG \(H\), the requested target district/fixing kernel
\(q^\star_H(D\mid R)\) equals the nested Markov kernel extracted from the
selected source law by fixing \(O_j\setminus(D\cup R)\) in the source
projection, with \(D\cup R\subseteq O_j\).  Source \(j\) contributes only the observational law
\(P_j(O_j\mid S_j=1)\), with no experimental source law.  The treatment is a
fixed intervention \(X=x\), with \(X\subset V\), and the target estimand is
the interventional law \(P^\star_x(Y)\) for \(Y\subseteq V\setminus X\).
The identifying assumptions are: consistency and acyclicity of the target
SCM; the target nested Markov property for \(G^\star\); source-selection
invariance only through the typed clauses in \(\mathcal C\);
observed-source compatibility on overlaps; source-specific positivity for
every ordinary conditional or nested/fixing kernel used by the fusion
formula; and the overlap-ancestral restriction that each observed set
\(O_j\) is ancestral, after deleting intervention arrows into \(X\), for the
typed district factors it is used to supply.  The proposed decision object is the
source-cover certificate \(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\)
defined in Section~6; failure of this certificate is conjectured to be
equivalent to a finite multisource overlap-hedge witness.

\begin{abstract}
This proposal asks when an interventional law in a target population is
identified from \(k\) heterogeneous, partially overlapping, observational
source distributions connected by a selection-diagram constraint set.  The
kernel claim is a conjectured iff frontier: a recursive source-cover
certificate identifies \(P^\star_x(Y)\), and if the certificate fails then a
finite overlap-hedge pair of SCMs agrees on all \(k\) observed source laws and
all stated invariance constraints while disagreeing on \(P^\star_x(Y)\).  The
statement is deliberately restricted to observational-only,
factor-local, overlap-ancestral source collections, so it is not a claim about
arbitrary do-calculus search inputs or source experiments.  Relative to the
general systematic-selection data-fusion algorithm of
\citet{LeeGhassamiShpitser2024DataFusionSelection}, the proposed epsilon-gap is
a source-cover specialization with a graph-readable certificate and a
canonical finite overlap-hedge pair for the observational factor-local
subclass, aimed specifically at the systematic-selection failure case whose
published nonidentification proof is not yet closed by the existing
hedge/thicket analysis.  The payoff for applied transportability and
generalizability work is a sharp diagnostic distinguishing ``add another
source can identify the effect'' from ``the same source margins can still hide
two target effects.''
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Modern causal data fusion rarely supplies one clean target-population
observational law.  Instead, analysts combine registries, trials, surveys, and
administrative extracts whose variable sets overlap only partially and whose
selection mechanisms differ.  Graphical transportability and selection-bias
theory give powerful results for single-source or experiment-aided settings,
but an applied analyst still needs to know whether the particular collection of
observational source laws pins down the same target intervention in every
compatible causal model.

\paragraph{The main finding (proposed).}
The headline claim is Conjecture~\ref{conj:overlap-hedge-completeness}: in the
locked overlap-ancestral observational class, source-cover success is
necessary and sufficient for identifying \(P^\star_x(Y)\).  The constructive
side is Theorem~\ref{thm:source-cover-soundness}: a valid cover yields an
explicit functional assembled from source conditionals.  The novel side is
the proposed converse: source-cover failure should generate a multisource
overlap hedge, namely two finite SCMs with identical \(P_j(O_j\mid S_j=1)\)
for all \(j\) and identical \(\mathcal C\)-invariant kernels, but different
target interventional laws.

\paragraph{What is new.}
The epsilon-gap to \citet{BareinboimPearl2014MZTransport} and
\citet{BareinboimPearl2016DataFusion} is not the word ``multiple sources.''
Those papers treat transportability and data fusion with heterogeneous
regimes, populations, and sampling processes, including experimental or
limited-experimental information.  The closest published comparator is now
\citet{LeeGhassamiShpitser2024DataFusionSelection}, which gives a general
identification algorithm for interventional distributions from data sources
under systematic selection and states hedge/thicket-style nonidentification
witnesses for its failure branches, with one failure case left outside the
proved nonidentification theorem.  This proposal does not claim to be outside
that general framework.  Its proposed flagship refinement is narrower and more
structural: for observational-only, factor-local, overlap-ancestral inputs
falling inside the remaining witness gap, decide identification by a
polynomial source-cover certificate and, on failure, output a canonical finite
overlap-hedge pair that preserves every selected source distribution and every
cross-source invariance clause.  The new mathematical object is the overlap
hedge, which records source coverage and factor-local invariance in the
obstruction itself, so the conjecture is evaluated against the Lee--Ghassami--
Shpitser failure layer rather than against a straw generic search failure.

\paragraph{How it positions in the literature.}
The proposal sits in the exact-identification cluster, at the intersection of
ordinary ID completeness, transportability, and selection-bias recovery.  It
does not propose new do-calculus rules or SCM semantics.  Instead, it asks for
a theorem-level identification criterion over a restricted but empirically
common input class: \(k\) observational source distributions, heterogeneous
selection nodes, and partially overlapping measured variable sets.  The active
frontier comparator is \citet{LeeGhassamiShpitser2024DataFusionSelection};
\citet{TikkaHyttinenKarvanen2021DoSearch} is the adjacent arbitrary-input
do-search tool.  The proposed contribution is a closed-form source-cover
specialization and a canonical nonidentification witness for a named
observational selection-diagram class, not a replacement for the general
search algorithms.

\paragraph{Implications for the community.}
The immediate downstream consumer is the practical generalizability and
trial/observational-combination workflow surveyed by
\citet{DegtiarRose2023Generalizability} and \citet{ColnetEtAl2024RCTObservationalReview}:
before estimating a transported effect, an analyst could check whether the
available source collection actually identifies the target intervention, and
if not, read off a witness explaining which source overlap is insufficient.

\paragraph{How research benefits from the conclusion.}
Researchers should report the source-cover certificate, or the overlap hedge
that blocks it, before treating a multi-dataset observational fusion estimand
as identified.

\section{Related work}
\citet{ShpitserPearl2006ID} give the ordinary interventional-ID algorithm and
hedge-style completeness witnesses; this proposal asks for the analogous
witness after every source overlap and selection law must be preserved.
\citet{ShpitserPearl2008CompleteID} provide the complete identification
program for recursive semi-Markovian models; the present source-cover
criterion should reduce to that result when one complete target observational
law is available.  \citet{BareinboimPearl2012TransportCompleteness} establish
transportability completeness with selection diagrams; the gap here is the
observational k-source setting with partially observed source laws rather than
transporting experimental information from a source domain.  \citet{BareinboimPearl2014MZTransport}
prove completeness for transportability from multiple environments with
limited experiments; the proposed overlap-hedge obstruction removes source
experiments and makes partial observational overlap part of the witness.
\citet{BareinboimPearl2016DataFusion} frame data fusion as combining
heterogeneous populations, regimes, and sampling processes; this proposal
turns one observational fragment of that program into a proposed iff theorem.
\citet{LeeHonavar2013MTransport} study transportability from multiple
environments, supplying a multi-environment ancestor but not the selected
observational overlap criterion proposed here.

\citet{BareinboimTianPearl2014Selection} give complete graphical and
algorithmic conditions for recovering conditional probabilities from
selection-biased data, including some external unbiased-data cases; the
present problem has several selected sources and no single unbiased external
law.  \citet{BareinboimTian2015RecoveringEffects} characterize recoverable
effects with selection and confounding in Markovian models and give sufficient
semi-Markovian conditions; the proposal asks whether source overlap restores
completeness in a k-source observational fragment.
\citet{CorreaTianBareinboim2019SelectionEffects} prove completeness for
causal-effect identification in the presence of selection bias and extend the
setting to one additional unbiased external data source; the proposed
overlap-hedge conjecture differs by requiring one witness pair to preserve
several selected, partially overlapping observational source laws rather than
a biased law plus a single unbiased external law.  \citet{CorreaTianBareinboim2018Adjustment}
derive generalized adjustment under confounding and selection; their
adjustment fragment is a sanity corner rather than the full recursive
source-cover problem.  \citet{TikkaHyttinenKarvanen2021DoSearch} develop
do-search for multiple incomplete observational and experimental source
distributions; their work is the closest published tool, while this proposal
targets a closed-form polynomial criterion and explicit nonidentification
certificate for a narrower input class.  \citet{LeeGhassamiShpitser2024DataFusionSelection}
is closer still: it gives a general graphical identification algorithm for
interventional distributions from multiple data sources under systematic
selection, allowing arbitrary unobserved confounding and arbitrary selection
processes into experimental regimes.  The present proposal is best read as a
restricted specialization and strengthening of the certificate layer for the
observational, factor-local, partial-overlap fragment: the desired output is a
source-cover certificate or a source-minimal overlap-hedge pair, not only a
successful symbolic identification expression or a general failure trace.
\citet{LeeBareinboim2020PartialObservability} study causal-effect
identification when available distributions measure different subsets of the
modeled variables, establish a sufficient graphical criterion, and state
NP-completeness for the partial-observability decision problem conditional on
their completeness conjecture; the present conjecture must therefore be
separated from their GID-PO setting by its selected-source laws, typed
factor-local invariance clauses, and claimed source-minimal nonidentification
witness rather than by partial variable overlap alone.
\citet{LeeCorreaBareinboim2020GID} introduce g-identifiability from arbitrary
collections of observational and experimental distributions and prove
non-gID using thickets and hedgelets; their inputs are full interventional
kernels for named variable sets, whereas the current proposal forces every
available object to be a selected observational law on a partially observed
source set with either an ordinary conditional or a nested/fixing extraction
map.  \citet{KivvaMokhtarianEtesamiKiyavash2022RevisitGID} revisit gID
under explicit positivity, show the earlier positivity omission matters, and
give a sound-and-complete positive gID algorithm by reducing to classical ID
subproblems; the source-cover conjecture therefore includes source-specific
positivity in the locked parameters and must not be sold as a generic gID
completeness theorem.  The witness-layer comparison is:
\[
\begin{array}{lll}
\text{ordinary ID} & \text{hedge} &
  \text{one complete observational law;}\\
\text{gID} & \text{thicket/hedgelet} &
  \text{full observational or interventional kernels;}\\
\text{SS-ID} & \text{hedge/thicket-style failure certificates} &
  \text{systematic-selection data-fusion inputs, with one failure case open;}\\
\text{partial observability} & \text{GID-PO criterion} &
  \text{subset-measured distributions, sufficient criterion, conditional NP-completeness;}\\
\text{this proposal} & \text{source-minimal overlap hedge} &
  \text{selected observational margins plus typed factor-local invariance clauses.}
\end{array}
\]
The conjecture is meant to close the last line only for the observational
factor-local overlap-ancestral subclass, and specifically as a candidate
resolution of the open SS-ID failure branch when that branch is entered by
source-overlap rather than by unavailable experiments.

\citet{CrumpHotzImbensMitnik2006Overlap} show why limited support can force
an estimand change even when formulas look algebraically valid; this motivates
the source-positivity clauses in the locked parameters.  \citet{DegtiarRose2023Generalizability}
review generalizability and transportability methods in which overlap
conditions are central; the proposed criterion would state the graphical
identification counterpart of those practical assumptions.  \citet{ColnetEtAl2024RCTObservationalReview}
review randomized-trial and observational-study combination methods; the
proposal addresses the nonparametric identification question that precedes
their estimation workflows.

In-catalogue CausalSmith prior art is thin for this exact-ID kernel.
\texttt{doc/API.md} Section~3 reports empty active ExactID and PartialID
catalogues at seed time, aside from a paper-scoped Manski bounds study in
PartialID.  The banked proposal \texttt{eid\_proximal\_phase} studies
nonunique proximal bridges and native estimator-selection frontiers, not
selection-diagram source fusion.  The banked proposal
\texttt{eid\_frontdoor\_multi\_mediator} studies a finite mediator/proxy
partial-ID polytope, not k-source observational exact identification.
The closest data-fusion banked proposal is \texttt{pid\_long\_term\_surrogate},
whose rejected angle concerns sharp long-term surrogate bounds; it is a
partial-identification problem rather than the exact-ID overlap-hedge
criterion proposed here.

\paragraph{Theorem-mapped literature checklist for review.}
\citet{LeeGhassamiShpitser2024DataFusionSelection} is relevant to
Theorem~\ref{thm:source-cover-soundness} and
Conjecture~\ref{conj:overlap-hedge-completeness} because it is the closest
general systematic-selection data-fusion algorithm and supplies the failure
branch that this proposal narrows to a source-cover overlap hedge.
\citet{TikkaHyttinenKarvanen2021DoSearch} is relevant to
Theorem~\ref{thm:source-cover-soundness} because it searches arbitrary
observational and experimental inputs, whereas the source-cover theorem claims
a polynomial closed-form certificate for a restricted observational class.
\citet{LeeBareinboim2020PartialObservability} is relevant to
Conjecture~\ref{conj:overlap-hedge-completeness} because it is the closest
partial-variable-observation analogue, but its NP-completeness claim is
conditional on its completeness conjecture and it does not encode selected
source laws plus typed factor-local equality clauses.  \citet{LeeCorreaBareinboim2020GID}
is relevant to Conjecture~\ref{conj:overlap-hedge-completeness} because
thickets and hedgelets are the nearest existing non-gID witnesses, but they do
not preserve \(k\) selected observational margins.  \citet{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}
is relevant to Conjecture~\ref{conj:overlap-hedge-completeness} because it
shows positivity-sensitive gID completeness by reduction to ID, making the
proposal's source-specific positivity and overlap-preservation requirements
part of the epsilon-gap rather than incidental notation.  \citet{CorreaTianBareinboim2019SelectionEffects}
is relevant to Theorem~\ref{thm:reductions} and
Conjecture~\ref{conj:overlap-hedge-completeness} because it gives selection
effect completeness with one external unbiased source, while this proposal
requires simultaneous preservation of several selected overlapping source
laws.  \citet{CorreaTianBareinboim2018Adjustment} is relevant to
Theorem~\ref{thm:reductions} because the adjustment reduction should collapse
to their selection-adjustment corner under the source-valid adjustment
assumption.

\section{Formal setup}
Let \(V\) be a finite set of observed target variables, \(U\) a finite set of
latent variables, and \(G^\star\) the target acyclic directed mixed graph
induced by a recursive semi-Markovian SCM.  For disjoint \(X,Y\subseteq V\),
the target query is
\[
  \theta(G^\star,X,Y,x)=P^\star_x(Y),
\]
the postintervention distribution of \(Y\) after setting \(X=x\) in the
target population.  Source \(j\in\{1,\ldots,k\}\) has a selection node \(S_j\),
an observed variable set \(O_j\subseteq V\), and contributes the law
\(P_j(O_j\mid S_j=1)\).  No source contributes \(P_j(\cdot\mid do(z))\).

The constraint set \(\mathcal C\) is typed and factor-local:
\[
  \mathcal C=\mathcal C^{\mathrm{obs}}\cup\mathcal C^{\mathrm{fix}}.
\]
An ordinary clause \(c=(\mathrm{obs},j,A,B)\in\mathcal C^{\mathrm{obs}}\),
with \(A,B\subseteq O_j\), asserts that \(P^\star(A\mid B)\) equals the
ordinary selected-source conditional
\[
  E_j(c;P_j)=P_j(A\mid B,S_j=1)
\]
on the positive support of \(B\).  A nested clause
\(c=(\mathrm{fix},j,H,D,R)\in\mathcal C^{\mathrm{fix}}\), with
\(D\cup R\subseteq O_j\), is tied to a particular CADMG \(H\) encountered by
the ID recursion and asserts that the target district/fixing kernel
\(q^\star_H(D\mid R)\) equals
\[
  E_j(c;P_j)=\phi^{j}_{O_j\setminus(D\cup R)}
    \{P_j(O_j\mid S_j=1)\}(D\mid R),
\]
the nested Markov kernel obtained by fixing the nonrequested variables in the
selected-source projection whenever that fixing operation is valid.  The map
\(E_j\) is part of the input convention: ordinary clauses never discharge
nested/fixing requests, and nested clauses discharge only the named
\((H,D,R)\) request.  Let \(\mathcal K_j(\mathcal C)=\{E_j(c;P_j):
c\in\mathcal C,\ c\text{ has source }j\}\).  A district/fixing request
\(\rho=(H,D,R,\tau)\), with \(\tau\in\{\mathrm{obs},\mathrm{fix}\}\), is
\emph{source-coverable} if there is a source \(j\) and a clause \(c\in
\mathcal C\) of the same type \(\tau\) whose requested kernel is exactly
\(q^\star_H(D\mid R)\), whose extraction \(E_j(c;P_j)\) is defined, and whose
source positivity condition for \(R\) holds.

The recursive source-cover certificate
\(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\) is obtained by running
the ordinary ID district recursion on the target graph, except that every
ordinary conditional or nested/fixing c-factor request is first typed as
\(\rho=(H,D,R,\tau)\) and then discharged by a source-coverable factor from
some \(\mathcal K_j(\mathcal C)\).  When all
requests are discharged, the algorithm returns a functional
\[
  \Phi_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)
\]
formed by multiplying, summing, and conditioning the selected source kernels.
When a request is not source-coverable, the failed request consists of a
district \(D\), its required parents \(R\), the remaining graph at that
recursion node, and the set of sources whose observed sets intersect
\(D\cup R\).
The input size is
\[
  n_{\mathrm{in}}=|V|+|E|+k+\sum_{j=1}^k |O_j|+|\mathcal C|,
\]
with finite variable alphabets treated as fixed for the graph-theoretic
decision problem.  A \emph{two-source observational fusion fragment} means a
case in which a published Bareinboim--Pearl fusion formula uses two typed
target kernels \(Q_1^\star(A_1\mid B_1)\) and \(Q_2^\star(A_2\mid B_2)\),
source 1 supplies \(Q_1^\star\) through a matching typed clause in
\(\mathcal C\), source 2 supplies \(Q_2^\star\) through a matching typed
clause in \(\mathcal C\), and the final estimand is obtained by summing over
the shared variables.

The proposal's relation to systematic-selection data fusion is fixed as
follows.  A \emph{source-cover input} is a special case of the data-fusion
input class in which every available distribution is observational, every
source reports only \(O_j\) after selection, and every cross-source equality is
listed as a typed factor-local clause in \(\mathcal C\).  The source-cover algorithm
does not attempt arbitrary symbolic search over all data-fusion inputs; it
checks this subclass in time polynomial in \(n_{\mathrm{in}}\) by testing
district-factor coverability.  A \emph{canonical overlap hedge} is the failed
district request together with two finite SCMs \(M_0,M_1\) that agree on each
selected source law, agree on every \(\mathcal C\)-listed kernel, disagree on
\(P^\star_x(Y)\), and are source-minimal in the sense that deleting any source
not mentioned at the failed recursion node does not affect the disagreement.

\begin{quote}
This is an exact-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},\text{graph/selection diagram},
\text{treatment},\text{target estimand},\text{identifying assumptions}).
\]
Here \(\texttt{qid}=\texttt{eid\_data\_fusion\_k\_source}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph is a finite acyclic
semi-Markovian target diagram \(G^\star=(V,E,U)\) augmented by \(k\) source
selection nodes \(S_1,\ldots,S_k\), source-observation sets
\(O_j\subseteq V\), and a typed factor-local constraint set
\(\mathcal C=\mathcal C^{\mathrm{obs}}\cup\mathcal C^{\mathrm{fix}}\).
An ordinary clause \(c=(\mathrm{obs},j,A,B)\in\mathcal C^{\mathrm{obs}}\)
asserts that the target conditional kernel \(P^\star(A\mid B)\) equals the
selected-source conditional read from \(P_j(O_j\mid S_j=1)\) whenever
\(A\cup B\subseteq O_j\).  A nested clause
\(c=(\mathrm{fix},j,H,D,R)\in\mathcal C^{\mathrm{fix}}\) asserts that, at
ID-recursion CADMG \(H\), the requested target district/fixing kernel
\(q^\star_H(D\mid R)\) equals the nested Markov kernel extracted from the
selected source law by fixing \(O_j\setminus(D\cup R)\) in the source
projection, with \(D\cup R\subseteq O_j\).  Source \(j\) contributes only the observational law
\(P_j(O_j\mid S_j=1)\), with no experimental source law.  The treatment is a
fixed intervention \(X=x\), with \(X\subset V\), and the target estimand is
the interventional law \(P^\star_x(Y)\) for \(Y\subseteq V\setminus X\).
The identifying assumptions are: consistency and acyclicity of the target
SCM; the target nested Markov property for \(G^\star\); source-selection
invariance only through the typed clauses in \(\mathcal C\);
observed-source compatibility on overlaps; source-specific positivity for
every ordinary conditional or nested/fixing kernel used by the fusion
formula; and the overlap-ancestral restriction that each observed set
\(O_j\) is ancestral, after deleting intervention arrows into \(X\), for the
typed district factors it is used to supply.  The proposed decision object is the
source-cover certificate \(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\)
defined in Section~6; failure of this certificate is conjectured to be
equivalent to a finite multisource overlap-hedge witness.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite semi-Markovian target]\label{ass:finite-sm}
The target population is generated by a recursive semi-Markovian SCM over
finite observed variables \(V\) and finite latent variables \(U\), inducing
the acyclic directed mixed graph \(G^\star\).  Consistency holds for the
intervention \(X=x\), and \(P^\star_x(Y)\) is the standard truncated-factor
interventional law in this SCM class.  The observed target margin obeys the
nested Markov/fixing factorization used to define CADMG district kernels
\(q^\star_H(D\mid R)\) at ID-recursion states.
\end{assumption}

\begin{assumption}[Observational k-source inputs]\label{ass:k-source-inputs}
For each \(j=1,\ldots,k\), the only available source datum is the selected
observational distribution \(P_j(O_j\mid S_j=1)\) on a finite observed subset
\(O_j\subseteq V\).  No source provides an experimental, randomized, or
postintervention law.
\end{assumption}

\begin{assumption}[Factor-local selection constraints]\label{ass:factor-local-C}
The constraint set \(\mathcal C\) consists only of source-indexed typed
invariance clauses.  Ordinary clauses
\((\mathrm{obs},j,A,B)\in\mathcal C^{\mathrm{obs}}\) equate
\(P^\star(A\mid B)\) with \(E_j(c;P_j)=P_j(A\mid B,S_j=1)\).  Nested clauses
\((\mathrm{fix},j,H,D,R)\in\mathcal C^{\mathrm{fix}}\) equate the requested
target district/fixing kernel \(q^\star_H(D\mid R)\) with the source
extraction \(E_j(c;P_j)=\phi^j_{O_j\setminus(D\cup R)}
\{P_j(O_j\mid S_j=1)\}(D\mid R)\), whenever the fixing operation is valid in
the source projection.  The proposal does not assume unlisted cross-source,
cross-factor, or cross-type equalities.
\end{assumption}

\begin{assumption}[Overlap compatibility]\label{ass:overlap-compat}
Whenever two source laws report the same \(\mathcal C\)-invariant target
kernel on an overlap, the observed kernels agree on their common positive
support.  The observed collection is therefore not internally contradictory.
\end{assumption}

\begin{assumption}[Source positivity]\label{ass:source-positivity}
Every ordinary conditional or nested/fixing kernel used in
\(\Phi_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)\) has strictly positive conditioning
event under the source law from which it is read.  Positivity is source
specific: a denominator or fixing normalizer required from source \(j\) must
be positive in \(P_j(O_j\mid S_j=1)\), not merely in another source.
\end{assumption}

\begin{assumption}[Overlap-ancestral source coverage]\label{ass:overlap-ancestral}
At every recursive source-cover step, if source \(j\) is used to supply a
request \(\rho=(H,D,R,\tau)\), then \(D\cup R\subseteq O_j\), the set
\(O_j\) is ancestral for the supplied factor in the graph at that recursion
node after deleting intervention arrows into \(X\), and \(\mathcal C\)
contains a matching typed clause: \((\mathrm{obs},j,D,R)\) for an ordinary
conditional request or \((\mathrm{fix},j,H,D,R)\) for a nested/fixing request.
\end{assumption}

\begin{assumption}[Binary finite witness class]\label{ass:binary-witness}
For nonidentification witnesses, it is enough to search over finite binary
observed variables and finite binary latent variables preserving the same
ADMG adjacencies, source observation sets, and \(\mathcal C\)-clauses.  This
is a witness-class restriction for Conjecture~\ref{conj:overlap-hedge-completeness},
not a restriction on the positive identification formula in
Theorem~\ref{thm:source-cover-soundness}.
\end{assumption}

\begin{assumption}[Adjustment-corner notation]\label{ass:adjustment-corner}
A set \(Z\subseteq V\setminus (X\cup Y)\) is called a valid adjustment set for
\((X,Y)\) when it satisfies the standard graphical adjustment criterion in
the target graph and the target adjustment functional
\(\sum_z P^\star(Y\mid X=x,Z=z)P^\star(Z=z)\) equals \(P^\star_x(Y)\).
\end{assumption}

\begin{assumption}[Complete target-source supply]\label{ass:complete-source}
For the complete-source corner, there is a source \(j^\star\) with
\(O_{j^\star}=V\), typed clauses in \(\mathcal C\) identifying every
ordinary or nested/fixing district kernel requested by ordinary ID with its
selected-source extraction, and
\(P_{j^\star}(V\mid S_{j^\star}=1)=P^\star(V)\) on the support needed by the
ordinary ID functional.
\end{assumption}

\begin{assumption}[Source-valid adjustment supply]\label{ass:source-valid-adjustment}
For a source-valid adjustment corner, there is a source \(j\) and a valid
target adjustment set \(Z\) such that \(X\cup Y\cup Z\subseteq O_j\),
\((\mathrm{obs},j,Y,X\cup Z)\in\mathcal C^{\mathrm{obs}}\), and
\((\mathrm{obs},j,Z,\varnothing)\in\mathcal C^{\mathrm{obs}}\).  For
every \(z\) contributing to the adjustment sum, \(P_j(Z=z\mid S_j=1)>0\) and
\(P_j(X=x,Z=z\mid S_j=1)>0\), so both
\[
  P_j(Z=z\mid S_j=1)
  \quad\text{and}\quad
  P_j(Y\mid X=x,Z=z,S_j=1)
\]
are defined from the same selected source law.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: source-cover soundness]\label{thm:source-cover-soundness}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:overlap-ancestral}, if
\(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\) succeeds, then
\[
  P^\star_x(Y)=\Phi_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)
\]
for every finite semi-Markovian SCM compatible with
\((G^\star,\{S_j,O_j,P_j\}_{j=1}^k,\mathcal C)\).  The returned functional is
a finite expression using only source kernels whose conditioning events
satisfy Assumption~\ref{ass:source-positivity}.  The certificate can be
checked in time polynomial in \(n_{\mathrm{in}}\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) The closest positive results are
\citet{BareinboimPearl2012TransportCompleteness},
\citet{BareinboimPearl2014MZTransport}, and
\citet{BareinboimTianPearl2014Selection}; the closest modern algorithmic
comparator is \citet{LeeGhassamiShpitser2024DataFusionSelection}.  The theorem
is not the flagship novelty: it is the soundness half of a source-aware ID
recursion.  The epsilon-gap is that every ordinary conditional or nested/fixing
c-factor request is tied to a named source law, a source-observation set, a
typed extraction map, and a local invariance clause
rather than to a complete target law or to source experiments, yielding a
transparent source-cover certificate for the observational partial-overlap
fragment of the larger systematic-selection problem.  (b) The concrete consumer is
the multi-dataset generalizability workflow in
\citet{ColnetEtAl2024RCTObservationalReview}: a successful certificate gives
the exact nonparametric estimand to plug into a later estimator.

\begin{conjecture}[Conjecture 1: overlap-hedge completeness (NOT YET PROVED)]\label{conj:overlap-hedge-completeness}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:binary-witness},
\(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\) succeeds if and only if
\(P^\star_x(Y)\) is identified from the collection
\(\{P_j(O_j\mid S_j=1)\}_{j=1}^k\) and the constraint set \(\mathcal C\).
Equivalently, if the source-cover recursion fails, then there exist two
finite binary semi-Markovian SCMs \(M_0,M_1\) on the same
\((G^\star,\{S_j,O_j\}_{j=1}^k,\mathcal C)\) such that
\[
  P^{M_0}_j(O_j\mid S_j=1)=P^{M_1}_j(O_j\mid S_j=1)
  \quad\text{for all }j=1,\ldots,k,
\]
all \(\mathcal C\)-invariant kernels agree in \(M_0\) and \(M_1\), but
\[
  P^{M_0}_x(Y)\ne P^{M_1}_x(Y).
\]
The failed recursion node determines a multisource overlap hedge: a pair of
districts together with the list of sources that observe each boundary
variable, the invariant kernels that must be held fixed, and a source-minimal
finite witness pair in the sense defined in Section~6.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published comparators are \citet{ShpitserPearl2006ID} for
ordinary hedge witnesses, \citet{BareinboimPearl2012TransportCompleteness}
for transportability obstructions,
\citet{CorreaTianBareinboim2019SelectionEffects} for complete effect
identification with selection bias and one external unbiased data source, and
\citet{TikkaHyttinenKarvanen2021DoSearch} for arbitrary-input do-calculus
search.  A separate close comparator is
\citet{LeeBareinboim2020PartialObservability}, whose GID-PO algorithm handles
different measured variable sets and whose NP-completeness comparison is
conditional on their completeness conjecture; its criterion is not a
selected-source overlap hedge because it does not require the witness to hold
fixed source selection laws and typed factor-local invariance clauses.  The
closest systematic-selection paper is \citet{LeeGhassamiShpitser2024DataFusionSelection},
which supplies a general identification algorithm for data fusion under
systematic selection and whose failure analysis already returns hedge or
thicket-style witnesses for the handled failure cases, proving
nonidentification in all but one branch.  The proposal's flagship epsilon-gap
is not a broader algorithm and not the claim that Lee--Ghassami--Shpitser lack
failure certificates.  It is the following narrower open branch: in the
observational, factor-local, overlap-ancestral source-cover subclass, the
remaining SS-ID witness gap should collapse to a source-minimal overlap hedge.
This witness must preserve all \(k\) selected source laws and all typed
\(\mathcal C\)-equalities, ordinary and nested/fixing, while changing the
target intervention.  Relative
to the gID thicket lineage in \citet{LeeCorreaBareinboim2020GID} and the
positivity-corrected gID reduction in
\citet{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}, the extra invariant is
not merely a named c-component obstruction; it is simultaneous preservation of
partially observed selected margins and overlap equality clauses.  (b) The
concrete consumer is the open data-fusion problem posed by
\citet{BareinboimPearl2016DataFusion}: the conjecture would tell a
data-fusion analyst exactly when another observational source closes the
identification gap and when it cannot.

\begin{theorem}[Theorem 2: single-complete-source and adjustment reductions]\label{thm:reductions}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:source-positivity} and
Assumption~\ref{ass:adjustment-corner}, the following reductions hold.
First, if Assumption~\ref{ass:complete-source} holds, then
\(\mathsf{Cover}_{\mathcal C}\) reduces to ordinary ID for
\((G^\star,X,Y)\).  Second, if
Assumption~\ref{ass:source-valid-adjustment} holds for a source \(j\) and
valid adjustment set \(Z\), then \(\mathsf{Cover}_{\mathcal C}\) returns the
standard adjustment functional
\[
  \sum_z P_j(Y\mid X=x,Z=z,S_j=1) P_j(Z=z\mid S_j=1)
\]
where \(X\cup Y\cup Z\subseteq O_j\), the denominator
\(P_j(X=x,Z=z\mid S_j=1)\) is positive whenever the conditional outcome
kernel is used, and the equalities
\[
  P_j(Y\mid X=x,Z=z,S_j=1)=P^\star(Y\mid X=x,Z=z),
  \qquad
  P_j(Z=z\mid S_j=1)=P^\star(Z=z)
\]
are justified by the \(\mathcal C\)-clauses
\((\mathrm{obs},j,Y,X\cup Z)\) and
\((\mathrm{obs},j,Z,\varnothing)\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is a sanity theorem rather than a flagship novelty.  The closest
published references are \citet{ShpitserPearl2008CompleteID} for the ordinary
ID reduction and \citet{CorreaTianBareinboim2018Adjustment} for adjustment
under selection.  The epsilon-gap is bookkeeping: the proposed certificate
must collapse to those known formulas when the k-source problem degenerates
to one complete law or one source-valid adjustment set.  (b) The concrete
consumer is the support-overlap diagnostic emphasized by
\citet{DegtiarRose2023Generalizability}: the theorem identifies the exact
corner in which familiar adjustment practice is still valid.

\section{Sanity-check corollaries}
\begin{corollary}[No-fusion corner]\label{cor:no-fusion}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:source-positivity}, if
\(k=1\), \(O_1=V\), the typed clauses in \(\mathcal C\) identify every
ordinary ID district request with its extraction from
\(P_1(V\mid S_1=1)\), and \(S_1\) has no active selection effect on \(V\), then
\(\mathsf{Cover}_{\mathcal C}\) succeeds exactly when ordinary ID succeeds,
and its formula is the ordinary ID formula.
\end{corollary}

\begin{corollary}[Two-source Bareinboim--Pearl observational fragment]\label{cor:bp-two-source}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:overlap-ancestral}, if
\(k=2\) and the query is a two-source observational fusion fragment with
target kernels \(Q_1^\star(A_1\mid B_1)\) and
\(Q_2^\star(A_2\mid B_2)\), then Theorem~\ref{thm:source-cover-soundness}
returns the functional obtained by replacing \(Q_1^\star\) and
\(Q_2^\star\) with their source-1 and source-2 typed source extractions and
summing over the shared variables.  Under the same specialization,
Conjecture~\ref{conj:overlap-hedge-completeness} predicts that failure of the
two-source factor cover is witnessed by a two-source overlap hedge.
\end{corollary}

\begin{example}[Three-source boundary witness template]\label{ex:three-source-template}
The smallest nontrivial template to test the conjectured witness is a binary
three-variable target \(V=\{X,Z,Y\}\) with three observational sources:
source 1 observes \((X,Z)\), source 2 observes \((Z,Y)\), and source 3 observes
a selected \((X,Y)\) margin.  The source-cover recursion fails when the target
district request needs the joint factor on \((X,Z,Y)\) but
\(\mathcal C\) supplies only the three pairwise typed source extractions.  At
the response-function level, the candidate linear system has nonnegative type
weights \(\pi_r\), equations \(A_{\mathrm{src}}\pi=m\) for the three selected
pairwise margins, equations \(A_{\mathcal C}\pi=c\) for the listed typed
invariance clauses, and target contrast \(b_{xY}^{\transpose}\pi=P_x(Y=1)\).
The algebraic certificate sought in this template is a nonzero direction
\(h\) with \(A_{\mathrm{src}}h=0\), \(A_{\mathcal C}h=0\), and
\(b_{xY}^{\transpose}h\ne 0\), while \(\pi\pm\varepsilon h\) remain in the
response-type simplex for small \(\varepsilon>0\).  Pairwise binary margins
alone admit the familiar three-way-interaction null direction, but the
conjecture requires verifying that an analogous direction survives the typed
\(\mathcal C\)-constraints and corresponds to two SCMs in the same ADMG.  This
example is not asserted as a proved counterexample; it is the explicit
boundary algebra that a proof of
Conjecture~\ref{conj:overlap-hedge-completeness} must either instantiate or
show cannot occur under the overlap-ancestral restriction.
\end{example}

\section{Proof-sketch route}
The soundness theorem should follow by induction on the ordinary ID district
recursion: each time ID requests a target ordinary conditional or nested/fixing
c-factor, the source-cover certificate supplies a matching typed source
extraction \(E_j(c;P_j)\), and the overlap-compatibility and positivity
assumptions justify the same summation and conditioning identities.
The completeness conjecture should start from the ordinary hedge
counterexample and refine the response-function construction so that boundary
variables observed in several sources are pasted through common latent
response coordinates, while source-private variables are copied independently
inside each source margin.  The proof obligation is to show that, for the
observational factor-local overlap-ancestral subclass, the SS-ID failure
branch not already covered by the published hedge/thicket proof can always be
converted into that pasted source-margin construction.  The first boundary
computation is
Example~\ref{ex:three-source-template}: write the three pairwise selected
source margins as linear constraints on binary response-function types, then
check whether the failed district leaves one free direction
\(h\in\ker(A_{\mathrm{src}})\cap\ker(A_{\mathcal C})\) with
\(b_{xY}^{\transpose}h\ne 0\).  If that linear system has
no such response-type direction under overlap-ancestrality, the conjecture must be narrowed
to the corresponding support or ancestry subclass before any flagship claim is
made.  The reduction theorem is checked by
collapsing the source index and verifying that the source-cover recursion is
syntactically identical to ordinary ID, with the adjustment corner obtained by
one application of conditional exchangeability and the law of total
probability.

\section{Honest scope flags}
Theorem~\ref{thm:source-cover-soundness} and
Theorem~\ref{thm:reductions} are proposed as routine algebraic results once
the source-cover recursion is fixed.  Conjecture~\ref{conj:overlap-hedge-completeness}
is the novel kernel and is not yet proved.  The proposal does not claim
completeness for arbitrary do-search inputs, arbitrary systematic-selection
inputs in \citet{LeeGhassamiShpitser2024DataFusionSelection}, source
experiments, non-factor-local invariance constraints, or non-ancestral
observed source sets.  It also does not claim priority over gID thickets,
hedgelets, or positivity-corrected gID algorithms in
\citet{LeeCorreaBareinboim2020GID} and
\citet{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}; the conjectural novelty
is only the source-cover closure of the observational partial-overlap branch
not already discharged by those witness systems or by the handled SS-ID
failure cases.  The most uncertain assumption is
Assumption~\ref{ass:binary-witness}:
ordinary ID admits finite binary witnesses, but the multisource overlap
constraints may require a larger finite alphabet unless the response-function
pasting argument is sharpened.  No iteration has yet withdrawn a result.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial exact-ID draft centered on a k-source
observational source-cover criterion and overlap-hedge completeness
conjecture; prior verdict: none.
\item v2 (revise) -- added the 2019 selection-bias completeness comparator
and tightened the adjustment reduction with source observation, positivity,
and \(\mathcal C\)-clause requirements; prior verdict: REVISE.
\item v3 (revise) -- added the Lee--Ghassami--Shpitser 2024 systematic-selection
data-fusion comparator, sharpened the flagship epsilon-gap to a source-cover
specialization with canonical overlap-hedge witnesses, and added the
three-source boundary witness template; prior verdict: REVISE.
\item v4 (revise) -- corrected the Lee--Ghassami--Shpitser comparison to
acknowledge its hedge/thicket-style failure witnesses, added the gID and
positivity-corrected gID witness lineage, and narrowed Conjecture~1 to the
remaining observational source-overlap witness branch; prior verdict: REVISE.
\item v5 (revise) -- added the Lee--Bareinboim 2020 partial-observability
comparator, typed \(\mathcal C\)-clauses as ordinary versus nested/fixing
source extractions, and made the three-source boundary algebra explicit;
prior verdict: REVISE.
\item v6 (revise) -- added the theorem-mapped literature checklist required
for reviewer auditability and corrected the GID-PO comparison to state
conditional NP-completeness; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bareinboim and Pearl(2012)]{BareinboimPearl2012TransportCompleteness}
Bareinboim, E. and Pearl, J. (2012).
Transportability of causal effects: Completeness results.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 26(1).

\bibitem[Bareinboim and Pearl(2014)]{BareinboimPearl2014MZTransport}
Bareinboim, E. and Pearl, J. (2014).
Transportability from multiple environments with limited experiments:
Completeness results.
\emph{Advances in Neural Information Processing Systems}, 27.

\bibitem[Bareinboim and Pearl(2016)]{BareinboimPearl2016DataFusion}
Bareinboim, E. and Pearl, J. (2016).
Causal inference and the data-fusion problem.
\emph{Proceedings of the National Academy of Sciences}, 113(27):7345--7352.

\bibitem[Bareinboim, Tian, and Pearl(2014)]{BareinboimTianPearl2014Selection}
Bareinboim, E., Tian, J., and Pearl, J. (2014).
Recovering from selection bias in causal and statistical inference.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 28(1).

\bibitem[Bareinboim and Tian(2015)]{BareinboimTian2015RecoveringEffects}
Bareinboim, E. and Tian, J. (2015).
Recovering causal effects from selection bias.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 29(1).

\bibitem[Colnet et al.(2024)]{ColnetEtAl2024RCTObservationalReview}
Colnet, B., Mayer, I., Chen, G., Dieng, A., Li, R., Varoquaux, G.,
Vert, J.-P., Josse, J., and Yang, S. (2024).
Causal inference methods for combining randomized trials and observational
studies: A review.
\emph{Statistical Science}, 39(1):165--191.

\bibitem[Correa, Tian, and Bareinboim(2018)]{CorreaTianBareinboim2018Adjustment}
Correa, J. D., Tian, J., and Bareinboim, E. (2018).
Generalized adjustment under confounding and selection biases.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 32(1).

\bibitem[Correa, Tian, and Bareinboim(2019)]{CorreaTianBareinboim2019SelectionEffects}
Correa, J. D., Tian, J., and Bareinboim, E. (2019).
Identification of causal effects in the presence of selection bias.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence},
33(1):2744--2751.

\bibitem[Crump et al.(2006)]{CrumpHotzImbensMitnik2006Overlap}
Crump, R. K., Hotz, V. J., Imbens, G. W., and Mitnik, O. A. (2006).
Moving the goalposts: Addressing limited overlap in the estimation of average
treatment effects by changing the estimand.
\emph{NBER Technical Working Paper} 330.

\bibitem[Degtiar and Rose(2023)]{DegtiarRose2023Generalizability}
Degtiar, I. and Rose, S. (2023).
A review of generalizability and transportability.
\emph{Annual Review of Statistics and Its Application}, 10:501--524.

\bibitem[Lee and Honavar(2013)]{LeeHonavar2013MTransport}
Lee, S. and Honavar, V. (2013).
m-transportability: Transportability of a causal effect from multiple
environments.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 27(1).

\bibitem[Lee and Bareinboim(2020)]{LeeBareinboim2020PartialObservability}
Lee, S. and Bareinboim, E. (2020).
Causal effect identifiability under partial-observability.
\emph{Proceedings of the 37th International Conference on Machine Learning},
PMLR 119:5692--5701.

\bibitem[Lee, Correa, and Bareinboim(2020)]{LeeCorreaBareinboim2020GID}
Lee, S., Correa, J. D., and Bareinboim, E. (2020).
Identifiability from a combination of observations and experiments.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence},
34(09):13677--13680.

\bibitem[Lee, Ghassami, and Shpitser(2024)]{LeeGhassamiShpitser2024DataFusionSelection}
Lee, J. J. R., Ghassami, A., and Shpitser, I. (2024).
A general identification algorithm for data fusion problems under systematic
selection.
\emph{Proceedings of the Fortieth Conference on Uncertainty in Artificial
Intelligence}, PMLR 244:2188--2204.

\bibitem[Kivva et al.(2022)]{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}
Kivva, Y., Mokhtarian, E., Etesami, J., and Kiyavash, N. (2022).
Revisiting the general identifiability problem.
\emph{Proceedings of the Thirty-Eighth Conference on Uncertainty in
Artificial Intelligence}, PMLR 180:1022--1030.

\bibitem[Shpitser and Pearl(2006)]{ShpitserPearl2006ID}
Shpitser, I. and Pearl, J. (2006).
Identification of joint interventional distributions in recursive
semi-Markovian causal models.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 21(1).

\bibitem[Shpitser and Pearl(2008)]{ShpitserPearl2008CompleteID}
Shpitser, I. and Pearl, J. (2008).
Complete identification methods for the causal hierarchy.
\emph{Journal of Machine Learning Research}, 9:1941--1979.

\bibitem[Tikka, Hyttinen, and Karvanen(2021)]{TikkaHyttinenKarvanen2021DoSearch}
Tikka, S., Hyttinen, A., and Karvanen, J. (2021).
Causal effect identification from multiple incomplete data sources: A general
search-based approach.
\emph{Journal of Statistical Software}, 99(5):1--40.
\end{thebibliography}

\end{document}
