% =====================================================================
%  thmsmith Stage 0 derivation skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=eid\_data\_fusion\_k\_source, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{eid\_data\_fusion\_k\_source} / \texttt{v1}%
  \\ \large\textit{Chain-refined source-cover for observational data fusion}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
The exact-identification target is the target-population interventional law
\(P^\star_x(Y)\) in a finite semi-Markovian selection-diagram model with
\(k\) observational source laws \(P_j(O_j\mid S_j=1)\) and typed
factor-local invariance clauses \(\mathcal C\).  The estimand-defining
functional is the chain-refined source-cover functional
\(\Phi^{\mathrm{cr}}_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)\), obtained by running
ordinary ID and discharging each requested kernel either by an exact typed
source extraction or, for ordinary multi-variable requests, by a finite
chain-rule product of smaller source-supplied ordinary conditionals.  The main
positive theorem proves that this functional is a computable finite
sum-product map and equals \(P^\star_x(Y)\) whenever the chain-refined
certificate succeeds and the stated source-specific positivity conditions
hold.  A second theorem proves relative completeness for the finite
chain-product certificate language and, under an explicit randomized-root
treatment restriction, shows a strict infinite-family extension over exact
source-cover: postintervention district chains are identified from
source-supplied sequential conditionals even when no source covers the exact
joint district request.  The claim is deliberately modest: its algebra is the
ordinary finite chain rule plus assumed singleton source invariances, so this
note does not establish a flagship-level separation from published
systematic-selection, DoSearch, or gID frameworks.  Thus the Stage--1
overlap-hedge conjecture is refuted only as an exact-cover necessity claim;
the repaired theorem-level statement is a positive chain-refinement closure
criterion for a typed observational factor-local subclass.
\end{abstract}

\section{Introduction}
Modern causal data fusion often supplies several selected observational
sources rather than one complete target-population law.  One source may
measure treatment and a mediator, another may measure mediator and outcome,
and selection mechanisms may differ across sources.  The mathematical
question is whether these heterogeneous margins, together with explicit
factor-local invariance clauses, determine the same target intervention
\(P^\star_x(Y)\) in every compatible causal model.

Ordinary ID gives a complete graphical criterion when the full target
observational law is available.  Transportability, selection-bias recovery,
general identifiability, and systematic-selection data fusion extend that
program to richer collections of source distributions and regimes.  The
source-cover proposal considered here is narrower: all sources are
observational, every available equality is a typed local clause in
\(\mathcal C\), and every requested source extraction must be read from a
finite selected source law.

This note keeps the Stage--1 target and assumptions fixed but changes the
mathematical load-bearing statement.  Exact source-cover soundness is true,
yet by itself it is only a substitution lemma: ordinary ID requests a target
kernel and a typed clause replaces that kernel by a selected-source
extraction.  The incremental contribution is a computable closure operation
that permits ordinary multi-variable requests to be refined by the finite chain
rule before source substitution.  The resulting certificate,
\(\mathsf{CRCover}_{\mathcal C}\), remains an explicit source-law functional,
is complete for a finite chain-product expression language, and strictly
extends exact source-cover on an infinite family of randomized-root
postintervention district chain problems.

The result is useful because it identifies a concrete algebraic failure mode
in the original source-cover frontier and repairs it without invoking an
unbounded symbolic search.  If a district request \(q^\star(D\mid R)\) is not
covered as an atom, the certificate checks whether the same kernel is
recoverable as
\[
  \prod_{\ell=1}^{|D|}
  P^\star(W_{\pi(\ell)}\mid R,W_{\pi(<\ell)})
\]
with every factor supplied by a typed source clause.  This is still a
transparent observational fusion formula: the analyst can list the source
law, conditioning variables, and positivity requirement for each factor.  The
Stage--1 overlap-hedge converse is therefore not accepted as stated, but the
nearest correct statement is not merely a counterexample; it is a positive
chain-refined source-cover criterion with a randomized-root strict-extension
class.  The note does not prove that this class is outside, sharper than, or
an open subcase of the closest published general data-fusion algorithms.

\paragraph{Motivating conjecture(s).}
\begin{conjecture}[Conjecture 1: overlap-hedge completeness (NOT YET PROVED)]\label{conj:overlap-hedge-completeness}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:binary-witness},
\(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\) succeeds if and only if
\(P^\star_x(Y)\) is identified from the collection
\(\{P_j(O_j\mid S_j=1)\}_{j=1}^k\) and the constraint set \(\mathcal C\).
Equivalently, if the source-cover recursion fails, then there exist two
finite binary semi-Markovian SCMs \(M_0,M_1\) on the same
\((G^\star,\{S_j,O_j\}_{j=1}^k,\mathcal C)\) such that
\[
  P^{M_0}_j(O_j\mid S_j=1)=P^{M_1}_j(O_j\mid S_j=1)
  \quad\text{for all }j=1,\ldots,k,
\]
all \(\mathcal C\)-invariant kernels agree in \(M_0\) and \(M_1\), but
\[
  P^{M_0}_x(Y)\ne P^{M_1}_x(Y).
\]
The failed recursion node determines a multisource overlap hedge: a pair of
districts together with the list of sources that observe each boundary
variable, the invariant kernels that must be held fixed, and a source-minimal
finite witness pair in the sense defined in Section~6.
\end{conjecture}

\section{Related work and positioning}
\cite{ShpitserPearl2006ID} introduced the ordinary ID algorithm and hedge
nonidentification witnesses for recursive semi-Markovian models; the positive
part of this note substitutes source-supplied kernels into that ID recursion.
\cite{ShpitserPearl2008CompleteID} developed the complete identification
program for the causal hierarchy; the complete-source sanity check below
reduces to that setting when one selected source is invariant for the whole
target law.  \cite{BareinboimPearl2012TransportCompleteness} proved
transportability completeness with selection diagrams, and
\cite{BareinboimPearl2014MZTransport} extended transportability to multiple
environments with limited experiments; the present setting is more restricted
because all available source laws are observational and partially overlapping.
\cite{BareinboimPearl2016DataFusion} framed the general data-fusion problem;
this note studies one observational, factor-local fragment of that program.

\cite{BareinboimTianPearl2014Selection} and
\cite{CorreaTianBareinboim2019SelectionEffects} identify causal and
statistical functionals under selection bias; they are relevant because each
source law here is conditioned on a source-specific selection event.
\cite{CorreaTianBareinboim2018Adjustment} studies generalized adjustment
under confounding and selection, which is the closest adjustment-corner
comparison for a single source that supplies \(P^\star(Y\mid X,Z)\) and
\(P^\star(Z)\).  \cite{TikkaHyttinenKarvanen2021DoSearch} gives a
search-based approach for multiple incomplete data sources, while
\cite{LeeCorreaBareinboim2020GID} and
\cite{KivvaMokhtarianEtesamiKiyavash2022RevisitGID} analyze
g-identifiability from combinations of observational and experimental
distributions; those frameworks allow richer inputs than the typed
observational clauses considered here.

\cite{LeeBareinboim2020PartialObservability} studies identifiability when
different distributions measure different subsets of variables; this is close
in spirit but does not impose selected source laws plus typed source-selection
invariance clauses.  \cite{LeeGhassamiShpitser2024DataFusionSelection}
provides the closest systematic-selection comparator, a general identification
algorithm for data-fusion problems under systematic selection.  The present
theorem is not a refutation of that algorithm, not a claim of general
systematic-selection completeness, and not a theorem-level separation from
DoSearch or gID.  It targets a named bookkeeping subproblem inside those
broader published input classes: observational-only, factor-local, partially
overlapping source laws for which the ordinary ID output is known but its
requested ordinary kernels may be assembled from selected-source
conditionals.  The technical content is a closed chain-product certificate
language with a soundness proof, a finite dynamic-programming completeness
proof for that language, and an infinite randomized-root family on which this
certificate succeeds while exact source-cover fails.

No stronger literature claim is made.  This note does not prove that the
chain-product class lies outside the algorithm of
\cite{LeeGhassamiShpitser2024DataFusionSelection}, is sharper than the
search space of \cite{TikkaHyttinenKarvanen2021DoSearch}, or resolves an open
gID subcase relative to \cite{LeeCorreaBareinboim2020GID} and
\cite{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}.  A flagship-level
comparison would require a theorem mapping the chain-product certificate
class against one of those published frameworks; the result here is a useful
source-cover closure built from the finite chain rule and listed singleton
source invariances.

The Stage--1 proposal for this qid introduced an exact
source-cover/overlap-hedge frontier.  The review-relevant correction made
here is that the exact-cover converse is not the right frontier: the
chain-refined closure strictly expands the identified regime before any
nonidentification witness should be sought.  \cite{DegtiarRose2023Generalizability}
and \cite{ColnetEtAl2024RCTObservationalReview} survey applied
generalizability and trial-observational combination workflows; their
estimation questions presuppose the nonparametric identification question
answered or diagnosed by this note.

\section{Formal setup}
Let \(V\) be a finite set of observed target variables and \(U\) a finite set
of latent variables.  The target population is represented by a recursive
semi-Markovian SCM whose acyclic directed mixed graph is denoted
\(G^\star=(V,E,U)\).  For disjoint \(X,Y\subseteq V\) and a fixed treatment
value \(x\), \(P^\star_x(Y)\) denotes the target-population postintervention
law of \(Y\) after replacing the structural equations for \(X\) by the
constant \(x\).  All variables have finite support, all sums below are over
finite support points, and every conditional probability used in a formula is
only evaluated on a positive conditioning event.

There are \(k\) observational sources.  Source \(j\) has a selection node
\(S_j\), observes only \(O_j\subseteq V\), and contributes the selected
observational law \(P_j(O_j\mid S_j=1)\).  No source contributes an
experimental or postintervention distribution.  The only cross-population
invariance information is the typed factor-local constraint set
\[
  \mathcal C=\mathcal C^{\mathrm{obs}}\cup\mathcal C^{\mathrm{fix}}.
\]
An ordinary clause \(c=(\mathrm{obs},j,A,B)\) with \(A\cup B\subseteq O_j\)
asserts
\[
  P^\star(A\mid B)=E_j(c;P_j):=P_j(A\mid B,S_j=1)
\]
on the relevant positive support.  A nested clause
\(c=(\mathrm{fix},j,H,D,R)\) with \(D\cup R\subseteq O_j\) asserts that the
target district/fixing kernel requested at CADMG \(H\) equals
\[
  q^\star_H(D\mid R)=E_j(c;P_j)
  :=\phi^j_{O_j\setminus(D\cup R)}
        \{P_j(O_j\mid S_j=1)\}(D\mid R),
\]
where the fixing operation is assumed valid in the source projection.  The
type is part of the input: an ordinary clause does not automatically discharge
a nested/fixing request, and a nested clause discharges only the named
\((H,D,R)\) request.  Compatibility of the source collection means that two
clauses naming the same target kernel give the same numerical kernel on their
common positive support.

A district/fixing request is a tuple
\(\rho=(H,D,R,\tau)\), where \(H\) is the current CADMG in the ID recursion,
\(D\) is the requested random district, \(R\) is its fixed/parent set, and
\(\tau\in\{\mathrm{obs},\mathrm{fix}\}\) records whether the request is an
ordinary target conditional or a nested/fixing kernel.  It is
\(\mathcal C\)-coverable if some source \(j\) has \(D\cup R\subseteq O_j\), a
matching clause of the same type in \(\mathcal C\), a valid extraction
\(E_j(c;P_j)\), the source-specific positivity needed to evaluate that
extraction, and the overlap-ancestral condition stated in
Assumption~\ref{ass:overlap-ancestral}.

\paragraph{Locked parameters.}
This is an exact-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},\text{graph/selection diagram},
\text{treatment},\text{target estimand},\text{identifying assumptions}).
\]
Here \(\texttt{qid}=\texttt{eid\_data\_fusion\_k\_source}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph is a finite acyclic
semi-Markovian target diagram \(G^\star=(V,E,U)\) augmented by \(k\) source
selection nodes \(S_1,\ldots,S_k\), source-observation sets
\(O_j\subseteq V\), and a typed factor-local constraint set
\(\mathcal C=\mathcal C^{\mathrm{obs}}\cup\mathcal C^{\mathrm{fix}}\).
An ordinary clause \(c=(\mathrm{obs},j,A,B)\in\mathcal C^{\mathrm{obs}}\)
asserts that the target conditional kernel \(P^\star(A\mid B)\) equals the
selected-source conditional read from \(P_j(O_j\mid S_j=1)\) whenever
\(A\cup B\subseteq O_j\).  A nested clause
\(c=(\mathrm{fix},j,H,D,R)\in\mathcal C^{\mathrm{fix}}\) asserts that, at
ID-recursion CADMG \(H\), the requested target district/fixing kernel
\(q^\star_H(D\mid R)\) equals the nested Markov kernel extracted from the
selected source law by fixing \(O_j\setminus(D\cup R)\) in the source
projection, with \(D\cup R\subseteq O_j\).  Source \(j\) contributes only the observational law
\(P_j(O_j\mid S_j=1)\), with no experimental source law.  The treatment is a
fixed intervention \(X=x\), with \(X\subset V\), and the target estimand is
the interventional law \(P^\star_x(Y)\) for \(Y\subseteq V\setminus X\).
The identifying assumptions are: consistency and acyclicity of the target
SCM; the target nested Markov property for \(G^\star\); source-selection
invariance only through the typed clauses in \(\mathcal C\);
observed-source compatibility on overlaps; source-specific positivity for
every ordinary conditional or nested/fixing kernel used by the fusion
formula; and the overlap-ancestral restriction that each observed set
\(O_j\) is ancestral, after deleting intervention arrows into \(X\), for the
typed district factors it is used to supply.  The proposed decision object is the
source-cover certificate \(\mathsf{Cover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\)
defined in Section~6; failure of this certificate is conjectured to be
equivalent to a finite multisource overlap-hedge witness.

\section{Assumptions}
\begin{assumption}[Finite semi-Markovian target]\label{ass:finite-sm}
The target population is generated by a recursive semi-Markovian SCM over
finite observed variables \(V\) and finite latent variables \(U\), inducing
the acyclic directed mixed graph \(G^\star\).  Consistency holds for the
intervention \(X=x\): if \(X=x\) is observed, then the observed variables
agree with their \(x\)-intervention counterfactuals wherever both are defined.
The target law obeys the nested Markov/fixing factorization for
\(G^\star\), so each ID-recursion CADMG \(H\) has well-defined district
kernels \(q^\star_H(D\mid R)\).
\end{assumption}

\begin{assumption}[Observational \(k\)-source inputs]\label{ass:k-source-inputs}
For each source \(j=1,\ldots,k\), the only available population object is the
selected observational distribution \(P_j(O_j\mid S_j=1)\) on a finite
observed set \(O_j\subseteq V\).  No source contributes an experimental,
randomized, interventional, or regime-specific law.
\end{assumption}

\begin{assumption}[Typed factor-local invariance]\label{ass:factor-local-C}
All source-selection invariance information is contained in
\(\mathcal C=\mathcal C^{\mathrm{obs}}\cup\mathcal C^{\mathrm{fix}}\).
Ordinary clauses equate one target ordinary conditional with one selected
source conditional, and nested clauses equate one target district/fixing
kernel with one selected source fixing extraction.  No unlisted
cross-source, cross-factor, or cross-type equality is assumed.
\end{assumption}

\begin{assumption}[Observed-source compatibility]\label{ass:overlap-compat}
If two clauses in \(\mathcal C\) name the same target kernel and their source
conditioning events have positive probability, then the two selected-source
extractions agree on the common positive support.  Thus the listed source
constraints are mutually consistent.
\end{assumption}

\begin{assumption}[Source-specific positivity]\label{ass:source-positivity}
Every ordinary conditional or nested/fixing kernel used by a displayed
identifying formula has a positive denominator or fixing normalizer in the
same source law from which that kernel is extracted.  Positivity is not
borrowed across sources: if a formula reads a kernel from source \(j\), then
the required support condition must hold under \(P_j(O_j\mid S_j=1)\).
\end{assumption}

\begin{assumption}[Overlap-ancestral source coverage]\label{ass:overlap-ancestral}
Whenever source \(j\) is used to supply a request
\(\rho=(H,D,R,\tau)\), \(D\cup R\subseteq O_j\), \(O_j\) is ancestral for the
supplied factor in the graph at that recursion node after deleting arrows
into the intervened variables \(X\), and \(\mathcal C\) contains a matching
typed clause: \((\mathrm{obs},j,D,R)\) for an ordinary request or
\((\mathrm{fix},j,H,D,R)\) for a nested/fixing request.
\end{assumption}

\begin{assumption}[Binary finite witness class]\label{ass:binary-witness}
For the proposed nonidentification converse only, the witness class is
restricted to finite binary observed variables and finite binary latent
variables preserving the same ADMG adjacencies, source observation sets, and
\(\mathcal C\)-clauses.  The positive soundness theorem does not require this
binary restriction.
\end{assumption}

\section{Estimand-defining functional}
The exact source-cover functional is the Stage--1 map: run the ordinary ID
district recursion for \((G^\star,X,Y)\), and whenever the recursion requests
\(\rho=(H,D,R,\tau)\), scan \(\mathcal C\) for an exact same-type source
clause satisfying Assumptions~\ref{ass:factor-local-C},
\ref{ass:source-positivity}, and \ref{ass:overlap-ancestral}.  If every
request is discharged, the returned functional is the ordinary ID expression
with each target kernel \(q^\star_H(D\mid R)\) replaced by its selected-source
extraction \(E_j(c;P_j)\).  This exact functional is denoted
\(\Phi_{\mathcal C}\).

The repaired functional used in this note is the \emph{chain-refined
source-cover} functional \(\Phi^{\mathrm{cr}}_{\mathcal C}\).  It uses the
same ordinary ID recursion and the same exact matching rule, but it adds one
closure operation for ordinary requests.  Suppose ID requests an ordinary
kernel \(\rho=(H,D,R,\mathrm{obs})\) with finite
\(D=\{W_1,\ldots,W_r\}\).  A chain certificate for \(\rho\) is an ordering
\(\pi\) of \(D\) and ordinary clauses
\[
  c_\ell=
  \bigl(\mathrm{obs},j_\ell,\{W_{\pi(\ell)}\},
        R\cup\{W_{\pi(1)},\ldots,W_{\pi(\ell-1)}\}\bigr),
  \qquad \ell=1,\ldots,r,
\]
with each conditioning event positive in its own source law.  The certified
source kernel is
\[
  K^{\mathrm{cr}}_\rho(d\mid r)
  =
  \prod_{\ell=1}^{r}
  E_{j_\ell}(c_\ell;P_{j_\ell})
  \{w_{\pi(\ell)}\mid r,w_{\pi(1)},\ldots,w_{\pi(\ell-1)}\}.
\]
For nested/fixing requests, this note keeps the Stage--1 exact matching rule;
no chain refinement for nested kernels is part of the theorem.

The algorithm \(\mathsf{CRCover}_{\mathcal C}\) is:
\begin{enumerate}[leftmargin=*]
\item Run ordinary ID and record its finite list \(\mathcal R\) of requested
target kernels in the returned sum-product expression.  If ordinary ID fails,
return failure.
\item For each \(\rho\in\mathcal R\), first try exact source-cover.  If exact
cover succeeds, store that extraction.
\item If exact cover fails and \(\rho\) is an ordinary request with
\(|D|>1\), run a subset dynamic program.  A state is
\(A\subseteq D\).  There is an edge \(A\to A\cup\{W\}\) when
\(\mathcal C\) contains an ordinary clause for
\((W,R\cup A)\) whose source observes all variables in \(R\cup A\cup\{W\}\)
and whose source-specific positivity condition holds.  A path from
\(\varnothing\) to \(D\) gives a chain certificate and its product kernel.
\item If neither exact cover nor the chain dynamic program succeeds for a
request, return failure.  Otherwise substitute all stored kernels into the
ordinary ID expression.
\end{enumerate}
The returned expression is
\[
  \Phi^{\mathrm{cr}}_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)
  =
  \sum_{v\in\mathcal V_{\mathrm{sum}}}
    \prod_{\rho\in\mathcal R}
      K^{\mathrm{cr}}_\rho
      \{d_\rho(v,y,x)\mid r_\rho(v,y,x)\},
\]
where exact-covered requests use their exact selected-source extraction and
chain-covered requests use the product kernel above.  The map is computable:
for a request with \(|D|=r\), the chain search has \(2^r\) states and at most
\(r2^r|\mathcal C|\) typed-clause checks; checking a displayed certificate is
linear in \(r|\mathcal C|\).  Thus the procedure is fixed-parameter
tractable in the maximum ordinary request size and polynomial for bounded
district size.

The finite expression language \(\mathfrak G_{\mathrm{chain}}\) consists of
all ordinary ID sum-product expressions whose target requests are replaced
request-by-request by either exact typed source extractions or singleton
chain products of the form just displayed.  Theorem~\ref{thm:cr-soundness}
proves that every successful \(\mathsf{CRCover}_{\mathcal C}\) expression
equals the causal target, and Theorem~\ref{thm:chain-completeness} proves that
the subset dynamic program is complete for \(\mathfrak G_{\mathrm{chain}}\).
The verdict on Conjecture~\ref{conj:overlap-hedge-completeness} is therefore
split: exact source-cover success is sound, exact source-cover failure is not
a nonidentification certificate, and the nearest correct positive replacement
is chain-refined source-cover within the finite chain-product language.  This
replacement is an identification closure, not a general nonidentification
frontier for systematic-selection data fusion.

\section{Target causal estimand}
The target causal estimand is the target-population interventional law
\[
  \theta^\star(y;x)=P^\star_x(Y=y),
  \qquad y\in\mathrm{supp}(Y),
\]
for a fixed intervention \(X=x\) and \(Y\subseteq V\setminus X\).  This is a
causal object defined by the target SCM after intervention; it is not defined
to be any source functional.  The identification statements below prove
equality between this causal law and computable expressions in the selected
source distributions.

\begin{definition}[Randomized-root district-chain family]\label{def:chain-family}
For the strict-extension theorem, use the following theorem-local subclass.
For any integer \(r\ge 2\), let
\[
  V_r=\{X,W_1,\ldots,W_r\},\qquad Y=W_r,
\]
with \(X\) a directed root, no bidirected edge incident to \(X\), directed
arrows from \(X\) to each \(W_\ell\), optional directed arrows from earlier
\(W\)'s to later \(W\)'s respecting the order, and bidirected edges among
\(W_1,\ldots,W_r\) connecting them into a single post-\(X\) district.  The
``no bidirected edge incident to \(X\)'' condition is part of this
strict-extension family; root status alone would not exclude latent
confounding between treatment and post-treatment variables.  The target
stratum \(X=x\) is on the positive support needed for the displayed
conditionals, so the subclass satisfies randomized-treatment exchangeability
\[
  (W_1(x),\ldots,W_r(x))\perp X.
\]
The target estimand is still
\(\theta^\star(y;x)=P^\star_x(W_r=y)\).  The chain-refined functional for
this family is
\[
  \Psi_r(y;x)
  =
  \sum_{w_1,\ldots,w_{r-1}}
  \prod_{\ell=1}^{r}
  P_{j_\ell}\!\left(
    W_\ell=w_\ell
    \mid X=x,W_1=w_1,\ldots,W_{\ell-1}=w_{\ell-1},S_{j_\ell}=1
  \right),
\]
with \(w_r=y\), where \(\mathcal C\) contains the corresponding ordinary
clauses and the required source-specific positivity holds.  This is a causal
target first and an observable functional second; the theorem proves their
equality.
\end{definition}

\section{Main theorems}
\begin{theorem}[Chain-refined source-cover soundness]\label{thm:cr-soundness}
Under Assumptions~\ref{ass:finite-sm}--\ref{ass:overlap-ancestral}, if
\(\mathsf{CRCover}_{\mathcal C}(G^\star,X,Y,\{O_j\})\) succeeds and returns
\(\Phi^{\mathrm{cr}}_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)\), then for every
target SCM and source collection compatible with \(G^\star\), the selected
source laws, and the typed constraint set \(\mathcal C\),
\[
  P^\star_x(Y)=
  \Phi^{\mathrm{cr}}_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k).
\]
The right-hand side is a finite computable expression in the observed source
laws: it consists only of selected-source conditioning, valid source fixing
extractions, finite chain-rule products, and finite sums over explicitly
stated support sets.  Exact source-cover is the special case in which every
request is discharged by an exact typed source extraction, so the
Stage--1 soundness direction is confirmed and strengthened.
\end{theorem}

\begin{theorem}[Relative completeness and strict extension of exact source-cover]\label{thm:chain-completeness}
Fix the ordinary ID output for \((G^\star,X,Y)\).  Within the finite
expression language \(\mathfrak G_{\mathrm{chain}}\), the subset dynamic
program defined in the estimand-functional section is complete: if every ID
request can be replaced by an exact typed source extraction, or, when the
request is ordinary, by a singleton chain-product of typed source
conditionals, then
\(\mathsf{CRCover}_{\mathcal C}\) returns such an expression.  Consequently,
Theorem~\ref{thm:cr-soundness} identifies every query in this source-typed
chain-product class.

The inclusion over exact source-cover is strict.  For every \(r\ge 2\), in
the randomized-root district-chain family of Definition~\ref{def:chain-family},
suppose the
source
collection contains sources \(j_1,\ldots,j_r\) with
\[
  \{X,W_1,\ldots,W_\ell\}\subseteq O_{j_\ell},
  \qquad \ell=1,\ldots,r,
\]
and ordinary clauses
\[
  (\mathrm{obs},j_\ell,\{W_\ell\},
    \{X,W_1,\ldots,W_{\ell-1}\}),
  \qquad \ell=1,\ldots,r,
\]
with source-specific positivity for every displayed conditional.  Suppose
also that \(\mathcal C\) contains no exact ordinary or nested/fixing clause
for the joint district request
\[
  q^\star(W_1,\ldots,W_r\mid X).
\]
Then exact source-cover fails at that district request, but
\(\mathsf{CRCover}_{\mathcal C}\) succeeds and returns
\[
  P^\star_x(W_r=y)
  =
  \sum_{w_1,\ldots,w_{r-1}}
  \prod_{\ell=1}^{r}
  P_{j_\ell}\!\left(
    W_\ell=w_\ell
    \mid X=x,W_1=w_1,\ldots,W_{\ell-1}=w_{\ell-1},S_{j_\ell}=1
  \right),
\]
where \(w_r=y\).  Thus Conjecture~\ref{conj:overlap-hedge-completeness} is
refuted as an exact source-cover necessity claim on this randomized-root
subclass, while the positive replacement is a chain-refinement closure rather
than a general overlap-hedge completeness theorem.
\end{theorem}

Theorem~\ref{thm:cr-soundness} is more than ordinary soundness-by-substitution
because the substituted object may be a source-assembled chain product that
no single source covers as a district factor.  Theorem~\ref{thm:chain-completeness}
is the main technical claim of this note: it gives a computable certificate
language, proves that the dynamic program finds every formula in that
language, and exhibits an infinite randomized-root family on which the new
certificate succeeds and exact source-cover fails.  Its novelty tier is
modest.  The proof uses the ordinary finite chain rule plus the singleton
source invariances already assumed in \(\mathcal C\); it does not prove that
the class is outside, sharper than, or an open subcase of
\cite{LeeGhassamiShpitser2024DataFusionSelection},
\cite{TikkaHyttinenKarvanen2021DoSearch},
\cite{LeeCorreaBareinboim2020GID}, or
\cite{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}.

\begin{proposition}[Known-corner reductions]\label{prop:reductions}
If some source \(j^\star\) observes \(O_{j^\star}=V\) and \(\mathcal C\)
contains every ordinary or nested/fixing target kernel requested by ordinary
ID, with \(P_{j^\star}(V\mid S_{j^\star}=1)=P^\star(V)\) on the needed
support, then \(\Phi_{\mathcal C}\) is the ordinary ID functional.  If a
source \(j\) supplies a valid adjustment set \(Z\) through ordinary clauses
\((\mathrm{obs},j,Y,\{X,Z\})\) and \((\mathrm{obs},j,Z,\varnothing)\), then
\[
  P^\star_x(Y)
  =
  \sum_z P_j(Y\mid X=x,Z=z,S_j=1)P_j(Z=z\mid S_j=1).
\]
\end{proposition}

This proposition is a sanity result, not the novel contribution.  It records
that the source-cover formula collapses to ordinary ID or ordinary adjustment
when the multisource problem degenerates to a complete target source or to a
single source-valid adjustment formula.

\section{Interpretation}
The positive theorem says that a chain-refined source-cover certificate is a
valid identifying formula, not just a graph label.  The assumptions doing the
work are the factor-local invariance clauses and source-specific positivity.
Factor-local invariance licenses replacing a target conditional or district
kernel by a selected-source extraction.  Positivity makes the required
conditionals and fixing normalizers defined in the same source where they are
used.  Overlap compatibility prevents two listed sources from giving
contradictory values for the same target kernel.

The refinement changes what counts as a genuine source-overlap obstruction.
Exact source-cover treats a requested district kernel as atomic.  But
probability kernels can sometimes be reconstructed from smaller target
conditionals by deterministic identities such as
\[
  P^\star(M,Y\mid X)=P^\star(Y\mid M,X)P^\star(M\mid X).
\]
If those smaller conditionals are separately invariant across sources, the
effect may be identified even though no source supplies the exact district
request.  Thus exact source-cover failure is not, by itself, an
identification failure.  What Theorem~\ref{thm:chain-completeness} adds is a
bounded repair: before looking for an overlap hedge, close ordinary requests
under a specified chain-product language and check that every factor is
explicitly supplied by \(\mathcal C\).

In applied terms, the result sharpens the diagnostic promised by the proposal.
A successful chain-refined certificate remains decisive: it gives a valid
estimand.  A failed exact certificate is only a failure of that particular
atomic decomposition.  A failed chain-refined certificate has a narrower
meaning: no expression in \(\mathfrak G_{\mathrm{chain}}\) was found.  It is
still not a general nonidentification theorem for the full
systematic-selection problem.  A mis-specified formula would arise if one
silently used an unlisted source conditional, ignored a zero denominator, or
treated a source's full selected law as target-invariant when \(\mathcal C\)
declares only selected factor-local kernels invariant.  In the
strict-extension family, another mis-specification would be to use
\(P^\star_x(W)=P^\star(W\mid X=x)\) from root status alone; the equality is
licensed only after the no-bidirected-edge/randomized-treatment condition in
Definition~\ref{def:chain-family}.

\section{Step-by-step proof}
\begin{proof}[Proof of Theorem~\ref{thm:cr-soundness}]
By Assumption~\ref{ass:finite-sm}, the ordinary ID recursion supplies a
target-kernel expression \(F_{\mathrm{ID}}\) for the target semi-Markovian
graph.  The rule used here is the recursive c-factor identification theorem
of \cite{ShpitserPearl2006ID}: after the intervention \(X=x\) is represented
by the truncated graph, district factorization/fixing gives the relevant
c-kernels, irrelevant variables are marginalized, and the returned finite
sum-product expression equals \(P^\star_x(Y)\).  No source law is used in
this first step; it is ordinary target-population ID soundness.

Consider any request \(\rho=(H,D,R,\tau)\) appearing in that returned ID
expression.  If \(\mathsf{CRCover}_{\mathcal C}\) exact-covers the request,
there is a source \(j\) and a matching typed clause \(c\in\mathcal C\).  The
rule used at this step is typed source-kernel substitution: a listed
\(\mathcal C\)-clause is an exchangeability/invariance assertion equating one
named target kernel with one named selected-source extraction.  If
\(\tau=\mathrm{obs}\), Assumption~\ref{ass:factor-local-C} gives
\[
  q^\star_H(D\mid R)=P^\star(D\mid R)
  =E_j(c;P_j)=P_j(D\mid R,S_j=1)
\]
on the positive support used in the formula.  If
\(\tau=\mathrm{fix}\), the same typed source-substitution rule and the named
nested clause give
\[
  q^\star_H(D\mid R)
  =
  E_j(c;P_j)
  =
  \phi^j_{O_j\setminus(D\cup R)}
        \{P_j(O_j\mid S_j=1)\}(D\mid R).
\]
Assumption~\ref{ass:overlap-ancestral} ensures that the requested variables
are present in the selected source and that the extraction has the same
ancestral target meaning as the ID request.  Assumption~\ref{ass:source-positivity}
ensures each displayed conditional or fixing normalizer is defined.

If exact cover fails but the request is chain-covered, then
\(\tau=\mathrm{obs}\), \(D=\{W_1,\ldots,W_r\}\), and the certificate supplies
an order \(\pi\) plus clauses
\[
  c_\ell=
  \bigl(\mathrm{obs},j_\ell,\{W_{\pi(\ell)}\},
        R\cup\{W_{\pi(1)},\ldots,W_{\pi(\ell-1)}\}\bigr).
\]
The finite chain rule for the target ordinary conditional gives
\[
  P^\star(D=d\mid R=r_0)
  =
  \prod_{\ell=1}^{|D|}
  P^\star\{W_{\pi(\ell)}=w_{\pi(\ell)}
    \mid R=r_0,W_{\pi(1)}=w_{\pi(1)},\ldots,
          W_{\pi(\ell-1)}=w_{\pi(\ell-1)}\},
\]
with zero-probability predecessor strata contributing zero to the enclosing
ID sum by the usual finite-kernel convention.  For every positive stratum
used by the product, the typed source-substitution rule from
Assumption~\ref{ass:factor-local-C} and the listed ordinary clause
\(c_\ell\) give
\[
  P^\star\{W_{\pi(\ell)}\mid R,W_{\pi(<\ell)}\}
  =
  E_{j_\ell}(c_\ell;P_{j_\ell})
  \{W_{\pi(\ell)}\mid R,W_{\pi(<\ell)}\}.
\]
Source-specific positivity ensures that every source conditional in the
product is defined, and Assumption~\ref{ass:overlap-ancestral} ensures that
each source observation set is valid for the factor it supplies.  Multiplying
these equalities yields
\[
  q^\star_H(D\mid R)=K^{\mathrm{cr}}_\rho(D\mid R)
\]
for the chain-refined kernel stored by the algorithm.

Substitute the exact or chain equalities request by request into the ordinary
ID expression.  Products and finite sums preserve equality.  If two matching
clauses could have been chosen for the same target factor, Assumption~\ref{ass:overlap-compat}
guarantees that the selected numerical kernel is invariant to that choice on
the support used by the formula.  The resulting expression is precisely
\(\Phi^{\mathrm{cr}}_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k)\), so
\[
  P^\star_x(Y)=
  \Phi^{\mathrm{cr}}_{\mathcal C}(Y,x;\{P_j\}_{j=1}^k).
\]
Every operation in the right-hand side is a finite source-law operation, so
the functional is computable.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:chain-completeness}]
First fix the finite language \(\mathfrak G_{\mathrm{chain}}\).  For an
ordinary request \((H,D,R,\mathrm{obs})\), a singleton chain-product
derivation is exactly an ordering \(W_{\pi(1)},\ldots,W_{\pi(r)}\) such that,
for every prefix \(A_{\ell-1}=\{W_{\pi(1)},\ldots,W_{\pi(\ell-1)}\}\),
\(\mathcal C\) contains an ordinary source clause for
\((W_{\pi(\ell)},R\cup A_{\ell-1})\) with the required observation and
positivity conditions.  The subset dynamic program has precisely these
prefix sets as states and precisely these admissible clauses as edges.
Therefore a derivation in \(\mathfrak G_{\mathrm{chain}}\) gives a path from
\(\varnothing\) to \(D\), and any path from \(\varnothing\) to \(D\) gives the
corresponding derivation.  Exact source extractions are checked before the
dynamic program.  Thus, request by request, the algorithm succeeds exactly
when a replacement allowed by \(\mathfrak G_{\mathrm{chain}}\) exists.  Since
ordinary ID produces finitely many requests, the algorithm is complete for
the whole finite expression language.

Now consider the randomized-root district-chain family of
Definition~\ref{def:chain-family}.  The theorem-local randomized-root
condition licenses action-observation exchange:
\(X\) is a directed root and no bidirected edge is incident to \(X\), so the
SWIG/counterfactual separation statement is
\((W_1(x),\ldots,W_r(x))\perp X\).  By consistency and Rule 2 of
do-calculus, the action-observation exchange rule of
\cite{Pearl1995CausalDiagrams}, on the positive stratum \(X=x\), we obtain
\[
  P^\star_x(W_1=w_1,\ldots,W_r=w_r)
  =
  P^\star(W_1=w_1,\ldots,W_r=w_r\mid X=x).
\]
The explicit no-bidirected-edge condition is essential here; directed-root
status alone would not exclude latent confounding between \(X\) and the
post-\(X\) variables.
The post-\(X\) variables form one district, so ordinary ID requests the joint
district kernel \(q^\star(W_1,\ldots,W_r\mid X=x)\).  By construction,
\(\mathcal C\) has no exact ordinary clause and no nested/fixing clause for
that joint request; exact source-cover therefore fails.

The finite chain rule gives
\[
  P^\star(W_1=w_1,\ldots,W_r=w_r\mid X=x)
  =
  \prod_{\ell=1}^{r}
  P^\star(W_\ell=w_\ell
    \mid X=x,W_1=w_1,\ldots,W_{\ell-1}=w_{\ell-1})
\]
on positive predecessor strata, with zero-mass strata contributing zero to
the marginal sum.  The ordinary clauses in the theorem and
Assumption~\ref{ass:factor-local-C} replace each target factor by the
corresponding selected-source conditional by typed source-kernel
substitution.  Summing over
\(w_1,\ldots,w_{r-1}\) and setting \(w_r=y\) yields the displayed
\(\Psi_r(y;x)\).  Hence \(\mathsf{CRCover}_{\mathcal C}\) succeeds while
exact source-cover fails for every \(r\ge 2\).  The \(r=2\) case is the
minimal three-variable chain \(X,M,Y\); the theorem supplies the whole
randomized-root class.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:reductions}]
For the complete-source case, every target kernel requested by ordinary ID is
matched by a typed clause from source \(j^\star\), and the selected source law
equals the target observational law on the support used by ID.  The
source-cover substitution in Theorem~\ref{thm:cr-soundness} is
therefore the identity substitution into the ordinary ID expression.

For the adjustment case, the graphical adjustment criterion gives the
standard target equality by the back-door adjustment theorem of
\cite{Pearl1995CausalDiagrams}: conditional
exchangeability of \(Y(x)\) and \(X\) given \(Z\) licenses the
action-observation replacement, consistency evaluates \(Y(x)\) among units
with \(X=x\), and the law of total probability marginalizes over \(Z\):
\[
  P^\star_x(Y)=\sum_z P^\star(Y\mid X=x,Z=z)P^\star(Z=z).
\]
The two ordinary clauses in the proposition replace the first target kernel
by \(P_j(Y\mid X=x,Z=z,S_j=1)\) and the second by
\(P_j(Z=z\mid S_j=1)\).  Source-specific positivity makes the conditionals
well-defined for all terms with positive mass.  Substitution gives the
displayed source adjustment formula.
\end{proof}

\section{Sanity checks}
\begin{itemize}[leftmargin=*]
\item If \(X=\varnothing\), the target is the observational marginal
\(P^\star(Y)\).  Source-cover succeeds exactly when \(\mathcal C\) supplies
the target marginal or an ID-valid decomposition of it; the formula reduces
to finite marginalization of the supplied source kernels.
\item If \(X\) is randomized in the target graph and a source supplies
\((\mathrm{obs},j,Y,X)\) with positivity at \(X=x\), then the formula reduces
to \(P^\star_x(Y)=P_j(Y\mid X=x,S_j=1)\).  For a binary treatment and scalar
mean outcome, the ATE corner is
\[
  \E[Y(1)-Y(0)]
  =
  \E_j[Y\mid X=1,S_j=1]-\E_j[Y\mid X=0,S_j=1].
\]
\item If the null-effect condition \(P^\star_x(Y)=P^\star_{x'}(Y)\) holds for
two treatment values, then any two valid source-cover formulas for \(x\) and
\(x'\) evaluate to the same target law.  The equality follows from the causal
null condition, not from source overlap alone.
\item In the complete-source corner of Proposition~\ref{prop:reductions},
the formula is ordinary ID.  Thus the note agrees with the standard ID
special case when one selected source is invariant for all target kernels
needed by ID.
\item In the \(r=2\) strict-extension family with \(W_1=M\) and \(W_2=Y\),
the formula reduces to
\[
  P^\star_x(Y=y)
  =
  \sum_m
    P_2(Y=y\mid X=x,M=m,S_2=1)
    P_1(M=m\mid X=x,S_1=1).
\]
Adding the single extra clause \((\mathrm{obs},2,\{M,Y\},X)\) or a matching
nested/fixing clause makes exact source-cover succeed, and the exact-cover
functional equals the chain-refined functional by the ordinary chain rule.
\end{itemize}

\section{Counterexample or minimality check}
The minimal strict-extension witness is the \(r=2\) member of
Theorem~\ref{thm:chain-completeness}.  Take binary
\(V=\{X,M,Y\}\), graph \(X\to M\), \(X\to Y\), \(M\to Y\),
\(M\leftrightarrow Y\), no bidirected edge incident to \(X\), sources
\(O_1=\{X,M\}\) and
\(O_2=\{X,M,Y\}\), and clauses \((\mathrm{obs},1,M,X)\) and
\((\mathrm{obs},2,Y,\{X,M\})\).  Exact source-cover fails because the joint
district request \(q^\star(M,Y\mid X)\) is not listed as a typed source
clause, but chain-refined source-cover succeeds through
\[
  P^\star(M,Y\mid X)=P^\star(Y\mid X,M)P^\star(M\mid X).
\]
This witness is included only to show strictness and minimality; the headline
novelty is the generic chain-product closure theorem, not the isolated
negative example.

The nearest repair to Conjecture~\ref{conj:overlap-hedge-completeness} is
therefore not to assert an overlap hedge after every exact-cover failure.  A
correct first diagnostic is: run exact source-cover, then close ordinary
requests under the chain-product dynamic program in the estimand-functional
section, and only then
interpret failure as failure of the explicit chain-product language.  A
nonidentification theorem after this stronger failure would require an
additional overlap-hedge construction and is not claimed here.

The source-specific assumptions are also minimal in the ordinary exact-ID
sense.  If \(c_1\) is removed, two compatible target models can have the same
source 2 conditional \(Y\mid X,M\) but different target \(M\mid X=x\), changing
\(P^\star_x(Y)\).  If \(c_2\) is removed, two compatible target models can
have the same source 1 conditional \(M\mid X\) but different target
\(Y\mid X,M\), again changing the effect.  If source positivity fails for an
\(m\) with positive \(P_1(M=m\mid X=x,S_1=1)\), the displayed formula asks for
a source 2 conditional that is not defined on a stratum used by the target
sum.

\section{Formalization checklist}
\paragraph{Probabilistic objects.}
\begin{itemize}[leftmargin=*]
\item Finite target SCM: variables \(V\), latent variables \(U\), target graph
\(G^\star\), observational law \(P^\star(V)\), and interventional law
\(P^\star_x(Y)\).
\item Selected source law: for each \(j\), a finite probability distribution
\(P_j(O_j\mid S_j=1)\) with support predicates for all denominators used.
\item Ordinary typed clause:
\((\mathrm{obs},j,A,B)\mapsto P^\star(A\mid B)=P_j(A\mid B,S_j=1)\) on
positive support.
\item Nested/fixing typed clause:
\((\mathrm{fix},j,H,D,R)\mapsto q^\star_H(D\mid R)=
\phi^j_{O_j\setminus(D\cup R)}\{P_j(O_j\mid S_j=1)\}(D\mid R)\).
\item Compatibility predicate: if two clauses name the same target kernel,
their extracted source kernels agree on common positive support.
\item Strict-extension graph family: finite variables
\(\{X,W_1,\ldots,W_r\}\), randomized root treatment \(X\) with no bidirected
edge incident to \(X\), ordered post-\(X\) variables forming one bidirected
district, and target \(Y=W_r\).  The \(r=2\) member is the binary
\(\{X,M,Y\}\) minimality witness.
\end{itemize}

\paragraph{Deterministic identities and lemmas.}
\begin{itemize}[leftmargin=*]
\item Ordinary ID soundness: the returned target-kernel expression equals
\(P^\star_x(Y)\) under the finite semi-Markovian model assumptions.
\item Exact source substitution lemma: if a request \(\rho\) is matched by a
typed clause, replacing \(q^\star_H(D\mid R)\) by the selected source
extraction preserves the value of the ID expression.
\item Chain-refinement lemma: for an ordinary request \(P^\star(D\mid R)\)
and an ordering of \(D\), the finite chain rule expresses the request as the
product of singleton target conditionals given \(R\) and earlier variables;
typed ordinary clauses may then replace each singleton conditional by its
selected-source extraction.
\item Subset dynamic-programming completeness: states are subsets of \(D\);
an edge adds \(W\) when \(\mathcal C\) supplies the ordinary clause for
\(W\mid R,A\); paths from \(\varnothing\) to \(D\) are exactly singleton
chain-product certificates.
\item Finite sum-product congruence: equality of each kernel factor implies
equality of the full finite expression after multiplication and summation.
\item Root-intervention identity for the strict-extension family:
under Definition~\ref{def:chain-family}, consistency plus
do-calculus Rule 2/action-observation exchange gives
\(P^\star_x(W_1,\ldots,W_r)=P^\star(W_1,\ldots,W_r\mid X=x)\) on the
positive stratum \(X=x\).  Root status without the no-bidirected-edge
condition is not enough.
\item Chain rule for finite conditionals:
\(P^\star(M,Y\mid X)=P^\star(Y\mid X,M)P^\star(M\mid X)\) on positive
support, and its ordered \(r\)-variable analogue, with zero-mass strata
contributing zero to the marginal sum.
\item Exact-cover failure predicate: a request fails when no same-type
\(\mathcal C\) clause names the exact requested kernel and source support.
\item bypass-justified: declaration-level substrate survey found no direct
abstraction for this paper's typed \(k\)-source selected-law clauses; the
available exact-ID primitives are at the level of standard identification
and adjustment rather than source-indexed factor-local invariance.
\item bypass-justified: conditional-probability primitives remain useful for
downstream finite-kernel formalization, but the mathematical note needs a
source-cover recursion, subset dynamic program, and chain-refined finite
probability-kernel theorem rather than a single pre-existing identification
theorem.
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a positive refinement of the Stage--1
source-cover idea.  Chain-refined source-cover is a sound
exact-identification certificate for observational \(k\)-source data fusion
under typed factor-local selection invariance, source-specific positivity,
compatibility on overlaps, and the overlap-ancestral coverage condition.  The
subset dynamic program is complete for the finite chain-product certificate
language, and the randomized-root district-chain family shows a strict
extension over exact source-cover.  This is a useful source-cover closure, not
a flagship-level frontier theorem relative to systematic-selection,
DoSearch, or gID.  The identifying assumptions carrying the result are
precisely the listed typed invariances, the support conditions needed to
evaluate them, and, for the strict-extension family only, randomized-treatment
exchangeability for \(X\).  Identification breaks if an unlisted source
equality is used, if a required denominator is zero, if \(X\) is latently
confounded with post-\(X\) variables in the chain family, or if
chain-refined failure is mistaken for nonidentification in the full
systematic-selection problem.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{BareinboimPearl2012TransportCompleteness}
Bareinboim, E. and Pearl, J. (2012).
Transportability of causal effects: Completeness results.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 26(1).

\bibitem{BareinboimPearl2014MZTransport}
Bareinboim, E. and Pearl, J. (2014).
Transportability from multiple environments with limited experiments:
Completeness results.
\emph{Advances in Neural Information Processing Systems}, 27.

\bibitem{BareinboimPearl2016DataFusion}
Bareinboim, E. and Pearl, J. (2016).
Causal inference and the data-fusion problem.
\emph{Proceedings of the National Academy of Sciences}, 113(27):7345--7352.

\bibitem{BareinboimTianPearl2014Selection}
Bareinboim, E., Tian, J., and Pearl, J. (2014).
Recovering from selection bias in causal and statistical inference.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 28(1).

\bibitem{ColnetEtAl2024RCTObservationalReview}
Colnet, B., Mayer, I., Chen, G., Dieng, A., Li, R., Varoquaux, G.,
Vert, J.-P., Josse, J., and Yang, S. (2024).
Causal inference methods for combining randomized trials and observational
studies: A review.
\emph{Statistical Science}, 39(1):165--191.

\bibitem{CorreaTianBareinboim2018Adjustment}
Correa, J. D., Tian, J., and Bareinboim, E. (2018).
Generalized adjustment under confounding and selection biases.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 32(1).

\bibitem{CorreaTianBareinboim2019SelectionEffects}
Correa, J. D., Tian, J., and Bareinboim, E. (2019).
Identification of causal effects in the presence of selection bias.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence},
33(1):2744--2751.

\bibitem{DegtiarRose2023Generalizability}
Degtiar, I. and Rose, S. (2023).
A review of generalizability and transportability.
\emph{Annual Review of Statistics and Its Application}, 10:501--524.

\bibitem{KivvaMokhtarianEtesamiKiyavash2022RevisitGID}
Kivva, Y., Mokhtarian, E., Etesami, J., and Kiyavash, N. (2022).
Revisiting the general identifiability problem.
\emph{Proceedings of the Thirty-Eighth Conference on Uncertainty in
Artificial Intelligence}, PMLR 180:1022--1030.

\bibitem{LeeBareinboim2020PartialObservability}
Lee, S. and Bareinboim, E. (2020).
Causal effect identifiability under partial-observability.
\emph{Proceedings of the 37th International Conference on Machine Learning},
PMLR 119:5692--5701.

\bibitem{LeeCorreaBareinboim2020GID}
Lee, S., Correa, J. D., and Bareinboim, E. (2020).
Identifiability from a combination of observations and experiments.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence},
34(09):13677--13680.

\bibitem{LeeGhassamiShpitser2024DataFusionSelection}
Lee, J. J. R., Ghassami, A., and Shpitser, I. (2024).
A general identification algorithm for data fusion problems under systematic
selection.
\emph{Proceedings of the Fortieth Conference on Uncertainty in Artificial
Intelligence}, PMLR 244:2188--2204.

\bibitem{Pearl1995CausalDiagrams}
Pearl, J. (1995).
Causal diagrams for empirical research.
\emph{Biometrika}, 82(4):669--688.

\bibitem{ShpitserPearl2006ID}
Shpitser, I. and Pearl, J. (2006).
Identification of joint interventional distributions in recursive
semi-Markovian causal models.
\emph{Proceedings of the AAAI Conference on Artificial Intelligence}, 21(1).

\bibitem{ShpitserPearl2008CompleteID}
Shpitser, I. and Pearl, J. (2008).
Complete identification methods for the causal hierarchy.
\emph{Journal of Machine Learning Research}, 9:1941--1979.

\bibitem{TikkaHyttinenKarvanen2021DoSearch}
Tikka, S., Hyttinen, A., and Karvanen, J. (2021).
Causal effect identification from multiple incomplete data sources: A general
search-based approach.
\emph{Journal of Statistical Software}, 99(5):1--40.
\end{thebibliography}

\end{document}
