\section{Related Literature}

This paper is closest to four strands of work: econometric treatment choice, semiparametric and doubly robust estimation, margin-based excess-risk theory, and empirical learning under weak or limited overlap.  The \leanref{S-1}{observed-law policy-learning experiment} studied here keeps the target at the level of welfare regret for deterministic treatment rules, while allowing the information available for learning the sign of the conditional treatment contrast to deteriorate near either propensity boundary; the lower-bound witness specializes this mechanism to one boundary.

The treatment-choice literature frames policy learning as a welfare maximization problem under sampling uncertainty.  \citet{Manski2004,Manski2009} and \citet{Stoye2009} formulate finite-sample and minimax perspectives on treatment choice, while \citet{Kitagawa2018} develop empirical welfare maximization over policy classes and connect regret to classification-type complexity.  The modern policy-learning literature extends these ideas using doubly robust and orthogonal scores, sample splitting, and high-dimensional nuisance estimation \citep{Athey2021,Chernozhukov2018,Chernozhukov2022}.  The present paper places one-sided overlap decay directly in the lower-bound calibration and quantifies its interaction with margin complexity.

The semiparametric literature provides the estimation architecture behind the feasible rule considered later.  Efficient influence-function calculations and doubly robust estimating equations originate in the general semiparametric theory of \citet{Bickel1993} and \citet{Newey1994}, and in the causal-inference developments of \citet{Robins1994}, \citet{Hahn1998}, \citet{Hirano2003}, and \citet{VanDerLaan2011}.  Cross-fitting and Neyman-orthogonal score construction make these ideas compatible with flexible first-stage estimation \citep{Chernozhukov2018,Chernozhukov2022}.  Our conditional upper bound applies this orthogonal-score logic to a clipped AIPW empirical welfare rule under explicit nuisance-rate and empirical-process side conditions.

A second point of contact is individualized treatment-rule estimation.  Outcome-weighted learning and related classification reductions appear in \citet{Qian2011}, \citet{Zhao2012}, and \citet{Zhang2012}; off-policy and contextual-bandit work studies related inverse-propensity and doubly robust objectives \citep{Dudik2011,Swaminathan2015,Kallus2017}.  More recent work studies causal forests, R-learning, and robust policy learning under flexible nuisance estimation \citep{Nie2021,Sasaki2020,Sun2021,Kitagawa2022}.  These papers emphasize feasible algorithms and statistical guarantees under their respective overlap and nuisance assumptions.  The present contribution instead separates an observed-law minimax lower bound from a conditional clipped-AIPW achievability statement, so the feasible analysis should be read as one procedure-specific upper bound under stated side conditions.

The exponent calculations are also related to margin-based excess-risk theory.  The role played here by small conditional treatment contrasts is analogous to the low-noise or margin conditions in binary classification \citep{Audibert2007,Massart2006,Tsybakov2009}.  Under strict overlap, margin structure yields the familiar improvement from a square-root empirical-process rate toward faster regret rates.  With one-sided overlap decay, however, observations near the relevant treatment-propensity boundary become less informative precisely where the treatment contrast is small.  This changes the testing difficulty in the local alternatives used for the lower bound and makes the exponent depend jointly on the margin and overlap-decay parameters.

Limited-overlap and weak-overlap problems have been studied extensively in causal inference and off-policy evaluation.  Diagnostics, trimming, weighting instability, and design sensitivity are discussed by \citet{Li2016}, \citet{DAmour2017}, \citet{BenMichael2022}, \citet{Hill2024}, and \citet{Susmann2025}.  Recent work develops weak-overlap guarantees and clipping-based procedures for treatment-effect or policy-value estimation \citep{Zhan2021,Chen2020,Zhao2023,Sakaguchi2024,Girard2025,Liu2026}.  This paper couples overlap decay to the margin region for welfare regret, concentrating the difficulty where small treatment contrasts and weak treatment-arm information coincide.

\Cref{tab:related-comparison} summarizes the closest comparisons at the level of target, overlap condition, and conclusion.  The table is intentionally limited to high-level rate structure; constants, logarithmic factors, and side-condition domains differ across papers.

\begin{table}[t]
\centering
\caption{Closest comparisons in the related literature}
\label{tab:related-comparison}
\begin{tabular}{p{0.18\linewidth}p{0.20\linewidth}p{0.22\linewidth}p{0.28\linewidth}}
\hline
Reference & Target & Overlap treatment & Relation to this paper \\
\hline
\citet{Kitagawa2018} & Welfare regret for empirical welfare maximization & Standard overlap conditions for observational welfare learning & Establishes the empirical-welfare framework; the present paper changes the local testing calibration under one-sided overlap decay. \\
\citet{Luedtke2017} & Optimal treatment-rule regret under margin structure & Strict-overlap setting & Provides the strict-overlap benchmark in which the rate is driven by the margin exponent; here the lower-bound exponent also includes an overlap-decay component. \\
\citet{Chernozhukov2018,Chernozhukov2022} & Orthogonal and cross-fitted semiparametric estimation & Overlap enters through score regularity and nuisance control & Supplies the orthogonal-score methodology used by the feasible clipped-AIPW rule; the present paper adds the one-sided overlap-decay minimax lower bound. \\
\citet{Liu2026} & Clipping and weak-overlap upper bounds for policy learning or related causal targets & Allows weak-overlap behavior controlled through clipping and nuisance conditions & Closest to the feasible upper-bound side: this paper adds a separate observed-law lower-bound exponent and keeps the clipped-AIPW achievability statement conditional. \\
\hline
\end{tabular}
\end{table}

Finally, the lower-bound argument follows the classical testing tradition of \citet{LeCam1986} and its use in nonparametric and classification lower bounds \citep{Tsybakov2009}.  The least favorable alternatives are calibrated so that regret separation and product divergence balance after accounting for the mass of the margin region and the information loss from one-sided overlap decay.  The paper thereby gives a lower-bound exponent for the law class and a separate conditional upper exponent for one clipped cross-fitted AIPW rule, including its nuisance-limited regime under the stated side conditions.
