\section{Discussion, Limitations, and Open Question}

The preceding sections separate two complementary objects.  \Cref{obj:thm:minimax-lower} gives an observed-law minimax lower bound over the class \(\mathcal P_{\alpha,\gamma}\) in \cref{obj:def:law-class}.  \Cref{obj:oeq:feasible-upper} gives a conditional upper bound for the clipped cross-fitted AIPW empirical welfare rule over the side-condition domain in \cref{obj:def:upper-risk}.  Thus the exponent \(r_\star(\alpha,\gamma)\) is a converse benchmark for the law class, whereas \(r_{\mathrm{up}}\) is the exponent delivered by one feasible procedure under explicit nuisance-rate, cross-fitting, boundedness, and localized empirical-process conditions.

This distinction matters in regimes where the nuisance and clipping balance binds.  In the nonbinding branch of \cref{obj:def:feasible-rate}, the optimized nuisance exponent is at least the lower-bound exponent, so the conditional upper bound has the same polynomial exponent as the observed-law lower bound, up to logarithmic factors.  In the strict-gap branch, the feasible exponent is smaller because one of the nuisance-dependent terms in the master bound of \cref{obj:lem:crude-localized-master-bound} controls the rate.  The two conclusions are consistent: the lower bound ranges over all measurable policy estimators, while the upper bound analyzes a particular clipped AIPW ERM with estimated cross-fitted nuisance functions.

The statistical source of the gap is the same weak-overlap mechanism emphasized in the limited-overlap literature \citep{Li2016,DAmour2017,BenMichael2022,Hill2024,Susmann2025}.  The lower-bound alternatives make the informative treatment arm rare precisely on the small-contrast block that determines regret.  A fully informed oracle procedure is limited by the testing difficulty encoded in \(r_\star(\alpha,\gamma)\).  A feasible clipped-score procedure must also estimate the nuisance functions and choose a clipping level that controls inverse-propensity variability.  When nuisance learning is slow in the weak arm, the product remainder and localized drift terms can dominate the purely testing-driven benchmark.  This connects to recent weak-overlap and clipping analyses of how overlap, nuisance estimation, and localization interact \citep{Zhao2023,Liu2026}.

\begin{definitionv}{oeq:feasible-tight}[Feasible Tightness Question]
In the strict-gap branch of the conditional feasible achievability bound for the regime-indexed risk \(U_n\), it is open whether a genuinely feasible estimator using estimated cross-fitted nuisance functions can attain the converse exponent \(r_\star(\alpha,\gamma)\), or whether weak-arm nuisance learning imposes the slower conditional exponent derived by the feasible upper bound.
\end{definitionv}

\cref{obj:oeq:feasible-tight} is intentionally stated as an open question.  It asks whether the gap in the strict-gap branch is an artifact of the plain clipped AIPW ERM and its analysis, or whether it reflects an intrinsic cost of learning the nuisance functions in the same weak-overlap region that drives the lower-bound construction.  Resolving this would require either a feasible procedure whose risk reaches \(r_\star(\alpha,\gamma)\) under comparable nuisance-side conditions, or a converse argument that incorporates nuisance learning into the lower-bound experiment.

\Cref{obj:oeq:feasible-upper} controls \(U_n(\alpha,\gamma,a,c;\widehat\eta)\) for the specified clipped cross-fitted rule and the stated side-condition domain.  The broader feasible minimax problem also includes other estimators, adaptive clipping schemes, and procedures that exploit additional structure in the nuisance functions.  \Cref{obj:thm:minimax-lower} supplies the observed-law converse free of nuisance-estimation restrictions.  The strict-gap branch therefore poses a genuine feasible minimax question beyond the completed observed-law lower-bound calculation.

