% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_qte\_marginal\_sensitivity, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_qte\_marginal\_sensitivity} / \texttt{v1}%
  \\ \large\textit{Finite-support CQTE process compatibility under covariate-wise marginal sensitivity}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form partial-identification proposal with locked tuple
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},\text{bounding functional}).
\]
\begin{verbatim}
qid = pid_qte_marginal_sensitivity
specialization = v1
observable distribution P = law of (Y,A,X), with A in {0,1},
    X a covariate value in a standard measurable space, and Y real-valued
    with known conditional support interval [L_x,U_x].
parameter theta = conditional quantile treatment effect curve
    Delta_x(tau) = Q_{Y(1)|X=x}(tau) - Q_{Y(0)|X=x}(tau),
    tau in (0,1), for P_X-a.e. x.
identifying restrictions = consistency, conditional positivity,
    covariate-wise marginal Rosenbaum sensitivity:
    for each arm a and covariate value x, the odds ratio
    odds P(A=a | Y(a)=y, X=x) / odds P(A=a | X=x)
    lies in [1/Gamma_a(x), Gamma_a(x)] for all y, plus an optional
    Manski-Pepper endpoint shape restriction S_MP stated explicitly in
    Assumption MP-shape.
bounding functional = the finite-grid CQTE process identified set:
    all vectors (Delta_x(tau_1),...,Delta_x(tau_m)) generated by a
    common pair of armwise likelihood-ratio weights satisfying the
    covariate-wise marginal sensitivity bounds.  The pointwise CDF and
    quantile envelopes F^L/F^U and Q^L/Q^U are retained as published
    background primitives, not as the novelty claim.
\end{verbatim}

\begin{abstract}
This proposal asks for sharp partial identification of a conditional quantile treatment effect process under a covariate-wise marginal Rosenbaum sensitivity model.  The revised kernel is not the now-published pointwise QTE envelope; it is a finite-support necessary-and-sufficient compatibility criterion for when a whole CQTE vector at several quantile indices is jointly attainable by one pair of latent arm laws.  Pointwise clipping and inversion enter only as background lemmas used to form the candidate hull.  The main conjecture predicts an exact polyhedral witness for process-level failure of the pointwise hull, even when every individual quantile endpoint is sharp.  If resolved, the result would tell applied sensitivity analyses when plotted CQTE bands are merely pointwise summaries and when they correspond to an actual latent distributional process.
\end{abstract}

\section{Introduction}
Observational sensitivity analysis is often reported for average effects even when the scientific question is distributional: who is helped, who is harmed, and where in the conditional outcome distribution hidden confounding could overturn a conclusion.  Recent work has substantially closed the gap for pointwise distributional and QTE bounds under marginal sensitivity.  The remaining methodological risk is process-level: a curve drawn by stacking sharp pointwise intervals may not itself correspond to any single latent law.

The main proposed finding is Conjecture~\ref{conj:process-compatibility}: on finite conditional supports, a finite CQTE vector is jointly attainable if and only if a stated pair of armwise bounded-weight polytopes intersects the quantile-cell constraints induced by that vector.  The conjecture also predicts a smallest certificate of noncompatibility: two or three quantile indices can already force a pointwise-attainable CQTE selection to fail as a process.

What is new is the compatibility boundary, not the pointwise envelope.  \citet{MastenPoirierRen2025} is treated as covering, at least in substance, sharp pointwise QTE and DTE bounds under broad relaxations including marginal sensitivity, and \citet{DornGuo2023} gives closely related sharp marginal-sensitivity logic for IPW functionals.  This proposal therefore asks for the residual theorem those papers do not spell out: exactly when a collection of pointwise CQTE choices can be pasted into one process under covariate-wise, arm-specific odds-ratio constraints.

The proposal lives in the partial-identification cluster: it connects Rosenbaum-style sensitivity analysis, marginal sensitivity models, Manski--Pepper bounds, and sharp bounds for distributional or quantile treatment effects.  It does not ask for a new do-calculus rule or a structural-graph axiom; the graph or potential-outcome machinery is background, while the theorem-level object is an identified set for a conditional quantile curve.

\section{Related work}
\citet{Rosenbaum1995} is the classical reference for hidden-bias sensitivity through bounded treatment-assignment odds ratios; it motivates the odds-ratio scale used here.  \citet{Tan2006} develops a distributional sensitivity analysis based on propensity-score departures from ignorability, and is the closest older source for moving beyond mean-only sensitivity.  \citet{DAmourFranksFeller2019} use Tukey factorization to separate observed and unidentified components and include QTE examples, but their Bayesian sensitivity analysis does not give the finite-support process-compatibility criterion proposed here.  \citet{ZhaoSmallBhattacharya2019} and \citet{KallusMaoZhou2019} study marginal sensitivity models and sharp intervals for heterogeneous mean-effect targets; their focus is CATE-style mean functionals rather than CQTE processes.  \citet{YadlowskyNamkoongBasuDuchiTian2022} give sharp ATE bounds under marginal sensitivity and influence-function inference, providing the nearest sharp mean-effect analogue.  \citet{DornGuo2023} sharpen and estimate marginal-sensitivity bounds with practical algorithms; their envelope logic is important prior art for the bounded-weight representation used below.  \citet{MastenPoirierRen2025} is the closest published threat because it studies sensitivity for broad treatment-effect functionals including QTE and DTE; this proposal treats pointwise QTE bounds as covered by that line and positions novelty only in finite-grid process compatibility.  \citet{ManskiPepper2000} supplies the monotone shape-restriction endpoint logic used only as a sanity check.  \citet{Firpo2007} gives point-identified QTE under unconfoundedness; it is the \(\Gamma=1\) reduction target.  \citet{FanPark2010} develops partial-identification bounds for distributions and quantiles under limited information, framing the quantile inversion problem independently of marginal sensitivity.  \citet{FirpoRidder2019} warn that function-valued distributional parameters need process-level care; this motivates the distinction between pointwise quantile sharpness and curve-level CQTE compatibility.

Within this repository, \texttt{ThmSmith/doc/API.md} Section~3 records that the ThmSmith PartialID catalogue is empty at seed time, so there is no existing ThmSmith \texttt{pid\_*} proposal with this kernel.  AutoID's \texttt{doc/API.md} Section~9j records promoted Manski-family ATE bounds under discrete-IV and monotone restrictions; those are mean-effect and shape-restriction bounds, not conditional QTE sensitivity envelopes.  AutoID's \texttt{doc/API.md} Section~9j2 records abstract partial-identification infrastructure, Section~9j3 records Balke--Pearl sharp binary-IV ATE bounds, and Section~9j5 records Lee bounds with the quantile form explicitly deferred; these are useful in-repo prior art but do not contain the proposed marginal-sensitivity CQTE formula.

\section{Formal setup}
Let \(P\) denote the observable law of \(O=(Y,A,X)\), where \(A\in\{0,1\}\), \(Y\in\mathbb{R}\), and \(X\in\mathcal{X}\).  For \(a\in\{0,1\}\), write \(e_a(x)=P(A=a\mid X=x)\) and \(F^{\mathrm{obs}}_{a,x}(y)=P(Y\le y\mid A=a,X=x)\).  The unobserved objects are the conditional potential-outcome CDFs \(F_{a,x}(y)=P(Y(a)\le y\mid X=x)\), their generalized inverses \(Q_{a,x}(\tau)=\inf\{y:F_{a,x}(y)\ge \tau\}\), and the CQTE curve \(\Delta_x(\tau)=Q_{1,x}(\tau)-Q_{0,x}(\tau)\).

For a sensitivity value \(\Gamma_a(x)\in[1,\infty]\), with the value \(\infty\) interpreted by the usual limiting convention, define
\[
\ell_a(x)=e_a(x)+\frac{1-e_a(x)}{\Gamma_a(x)},\qquad
u_a(x)=e_a(x)+(1-e_a(x))\Gamma_a(x).
\]
For \(F=F^{\mathrm{obs}}_{a,x}(y)\), define the candidate armwise CDF envelopes
\[
F^L_{a,x,\Gamma}(y)=\max\{\ell_a(x)F,\ 1-u_a(x)(1-F)\},
\qquad
F^U_{a,x,\Gamma}(y)=\min\{u_a(x)F,\ 1-\ell_a(x)(1-F)\}.
\]
The corresponding generalized-inverse envelopes are
\[
Q^L_{a,x,\Gamma}(\tau)=\inf\{y:F^U_{a,x,\Gamma}(y)\ge \tau\},\qquad
Q^U_{a,x,\Gamma}(\tau)=\inf\{y:F^L_{a,x,\Gamma}(y)\ge \tau\}.
\]
The identified set \(\Theta_I(P)\) is the set of all functions \(\Delta_x(\cdot)\) generated by latent laws for \((Y(0),Y(1),A,X)\) that reproduce \(P\) and satisfy the assumptions below.  For a finite grid \(\mathcal{T}=(\tau_1,\ldots,\tau_M)\), write
\[
\mathcal{D}_x(\mathcal{T})=\{(\Delta_x(\tau_1),\ldots,\Delta_x(\tau_M)):\Delta_x(\cdot)\in\Theta_I(P)\}
\]
for the process identified set on that grid, and write \(\mathcal{H}_x(\mathcal{T})\) for the Cartesian product of the pointwise CQTE intervals formed from \(Q^L_{a,x,\Gamma}\) and \(Q^U_{a,x,\Gamma}\).

When the conditional observed arm distribution is finite, let its support be \(y_{a1}<\cdots<y_{aJ_a}\) with masses \(p_{aj}=P(Y=y_{aj}\mid A=a,X=x)\).  Define the armwise bounded-weight polytope
\[
\mathcal{W}_{a,x}=\left\{w\in\mathbb{R}^{J_a}:
\ell_a(x)\le w_j\le u_a(x),\quad \sum_{j=1}^{J_a}p_{aj}w_j=1\right\},
\]
with \(u_a(x)=\infty\) interpreted as the absence of an upper cap.  For \(w\in\mathcal{W}_{a,x}\), define \(F^w_{a,x}(y)=\sum_{j:y_{aj}\le y}p_{aj}w_j\), \(F^w_{a,x}(y^-)=\sum_{j:y_{aj}<y}p_{aj}w_j\), and \(Q^w_{a,x}(\tau)=\inf\{y:F^w_{a,x}(y)\ge\tau\}\).

The locked parameters are reproduced here for downstream quoting:
\begin{verbatim}
qid = pid_qte_marginal_sensitivity
specialization = v1
observable distribution P = law of (Y,A,X), with A in {0,1},
    X a covariate value in a standard measurable space, and Y real-valued
    with known conditional support interval [L_x,U_x].
parameter theta = conditional quantile treatment effect curve
    Delta_x(tau) = Q_{Y(1)|X=x}(tau) - Q_{Y(0)|X=x}(tau),
    tau in (0,1), for P_X-a.e. x.
identifying restrictions = consistency, conditional positivity,
    covariate-wise marginal Rosenbaum sensitivity:
    for each arm a and covariate value x, the odds ratio
    odds P(A=a | Y(a)=y, X=x) / odds P(A=a | X=x)
    lies in [1/Gamma_a(x), Gamma_a(x)] for all y, plus an optional
    Manski-Pepper endpoint shape restriction S_MP stated explicitly in
    Assumption MP-shape.
bounding functional = the finite-grid CQTE process identified set:
    all vectors (Delta_x(tau_1),...,Delta_x(tau_m)) generated by a
    common pair of armwise likelihood-ratio weights satisfying the
    covariate-wise marginal sensitivity bounds.  The pointwise CDF and
    quantile envelopes F^L/F^U and Q^L/Q^U are retained as published
    background primitives, not as the novelty claim.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Consistency and conditional observability]\label{ass:consistency}
For \(a\in\{0,1\}\), \(Y=Y(a)\) almost surely on \(\{A=a\}\), and the conditional law \(P(Y,A\mid X=x)\) is defined for \(P_X\)-almost every \(x\).
\end{assumption}

\begin{assumption}[Conditional positivity]\label{ass:positivity}
For \(P_X\)-almost every \(x\), \(0<e_a(x)<1\) for \(a=0,1\).
\end{assumption}

\begin{assumption}[Known conditional support]\label{ass:support}
For \(P_X\)-almost every \(x\), \(Y(a)\in[L_x,U_x]\) almost surely for both arms, and \(F^{\mathrm{obs}}_{a,x}\) is supported on the same interval after adding possible endpoint mass.
\end{assumption}

\begin{assumption}[Covariate-wise marginal Rosenbaum sensitivity]\label{ass:msm}
For \(P_X\)-almost every \(x\), each arm \(a\), and all potential-outcome values \(y\) in the support,
\[
\Gamma_a(x)^{-1}
\le
\frac{\Pr(A=a\mid Y(a)=y,X=x)/(1-\Pr(A=a\mid Y(a)=y,X=x))}
     {e_a(x)/(1-e_a(x))}
\le
\Gamma_a(x).
\]
When \(\Gamma_a(x)=\infty\), this means only the limiting nonnegativity and probability constraints remain.
\end{assumption}

\begin{assumption}[Endpoint Manski--Pepper shape restriction]\label{ass:mp}
When the endpoint reduction is invoked, write \(X=(Z,W)\) with \(Z\) in a totally ordered support and with the order oriented so larger \(Z\) weakly raises potential outcomes.  The shape restriction \(S_{\mathrm{MP}}\) consists exactly of: (i) monotone treatment response \(Y(1)\ge Y(0)\) almost surely, equivalently \(F_{1,(z,w)}(y)\le F_{0,(z,w)}(y)\) for all \(y,z,w\); and (ii) monotone-IV CDF restrictions \(F_{a,(z',w)}(y)\le F_{a,(z,w)}(y)\) for every arm \(a\), threshold \(y\), and ordered pair \(z\le z'\).  When \(S_{\mathrm{MP}}\) is not invoked, no shape restriction beyond Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, and \ref{ass:msm} is imposed.
\end{assumption}

\begin{assumption}[Quantile regularity for closed-form inversion]\label{ass:quantile}
The generalized inverse convention is left-continuous, endpoint masses at \(L_x\) and \(U_x\) are allowed, and all statements are interpreted for quantile indices \(\tau\in(0,1)\) at which the relevant inverse is finite.
\end{assumption}

\begin{assumption}[Finite conditional support for the process theorem]\label{ass:finite}
For the process-compatibility theorem, conditional on the fixed covariate value \(x\), each observed arm distribution \(P(Y\mid A=a,X=x)\) has finite support \(y_{a1}<\cdots<y_{aJ_a}\) with strictly positive masses \(p_{aj}\).  The quantile grid \(\mathcal{T}=(\tau_1,\ldots,\tau_M)\) is finite and lies in \((0,1)^M\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: background pointwise armwise CDF envelope]\label{thm:cdf-envelope}
Under Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, and \ref{ass:msm}, for every arm \(a\), \(P_X\)-almost every \(x\), and every threshold \(y\), the sharp identified interval for \(F_{a,x}(y)\) is
\[
F^L_{a,x,\Gamma}(y)\le F_{a,x}(y)\le F^U_{a,x,\Gamma}(y).
\]
The lower and upper endpoints are attainable by a latent treatment-assignment odds rule that saturates the odds-ratio bound on the event \(\{Y\le y\}\) and on its complement.
\end{theorem}
\paragraph{Why this is new and worth studying.}
This theorem is included as a background lemma rather than as a novelty claim; \citet{DornGuo2023} and \citet{MastenPoirierRen2025} are the closest published sources for the same pointwise marginal-sensitivity logic.  Its role here is to supply the bounded-weight polytope whose joint quantile-cell feasibility is the new process-level question.

\begin{conjecture}[Conjecture 1: finite-support CQTE process compatibility (NOT YET PROVED)]\label{conj:process-compatibility}
Under Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, \ref{ass:msm}, \ref{ass:quantile}, and \ref{ass:finite}, a vector \(d=(d_1,\ldots,d_M)\) belongs to \(\mathcal{D}_x(\mathcal{T})\) if and only if there exist weights \(w_a\in\mathcal{W}_{a,x}\) and support values \(q_{ak}\in\{y_{a1},\ldots,y_{aJ_a}\}\) such that, for every grid index \(k\) and arm \(a\),
\[
F^{w_a}_{a,x}(q_{ak}^-)<\tau_k\le F^{w_a}_{a,x}(q_{ak}),
\qquad
d_k=q_{1k}-q_{0k}.
\]
Equivalently, \(\mathcal{D}_x(\mathcal{T})\) is the union, over finitely many support-cell assignments \((q_{ak})\), of the feasible projections of two normalized bounded-weight polytopes cut by linear quantile-cell inequalities.  Therefore the pointwise hull \(\mathcal{H}_x(\mathcal{T})\) is process-sharp exactly when every vector in that Cartesian hull satisfies this finite compatibility condition.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
\citet{MastenPoirierRen2025} is the closest threat because it covers QTE and DTE in a broad sensitivity framework, while \citet{FirpoRidder2019} explains why process-valued distributional functionals require more than pointwise bounds.  The gap is an explicit necessary-and-sufficient finite-support compatibility theorem for the CQTE process under covariate-wise marginal sensitivity; resolving it would tell researchers when a sensitivity band is jointly interpretable and would give a checkable certificate when it is only pointwise.

\begin{conjecture}[Conjecture 2: minimal pointwise-versus-process gap (NOT YET PROVED)]\label{conj:minimal-gap}
Under Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, \ref{ass:msm}, \ref{ass:quantile}, and \ref{ass:finite}, there is no compatibility gap for a one-point grid \(\mathcal{T}=(\tau)\): \(\mathcal{D}_x(\mathcal{T})=\mathcal{H}_x(\mathcal{T})\).  There exists, however, a finite-support design with \(J_0,J_1\le 3\), finite \(\Gamma_0(x),\Gamma_1(x)>1\), and a two-point grid \(\mathcal{T}=(\tau_1,\tau_2)\) for which \(\mathcal{D}_x(\mathcal{T})\subsetneq\mathcal{H}_x(\mathcal{T})\).  The strict inclusion can be witnessed by incompatible quantile-cell inequalities for one arm's single weight vector.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
\citet{FanPark2010} and \citet{FirpoRidder2019} make the general warning that pointwise distributional bounds need not describe a process, but they do not identify the smallest marginal-sensitivity CQTE design where the failure appears.  A minimal finite-support witness would separate this proposal from published pointwise QTE bounds and give Stage~0 a concrete algebraic target rather than a vague process-level concern.

\section{Sanity-check corollaries}
\begin{corollary}[Unconfoundedness collapse]\label{cor:unconfounded}
Under Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, \ref{ass:msm}, \ref{ass:quantile}, and \ref{ass:finite} with \(\Gamma_a(x)=1\), the process set \(\mathcal{D}_x(\mathcal{T})\) is the singleton vector \((Q^{\mathrm{obs}}_{1,x}(\tau_k)-Q^{\mathrm{obs}}_{0,x}(\tau_k))_{k=1}^M\).  The reduction is immediate because \(\ell_a(x)=u_a(x)=1\), so \(\mathcal{W}_{a,x}\) contains only the all-ones weight vector and each arm CDF equals \(F^{\mathrm{obs}}_{a,x}\) before inversion.
\end{corollary}

\begin{corollary}[Manski endpoint collapse]\label{cor:manski}
Under Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, \ref{ass:msm}, and \ref{ass:quantile} with \(\Gamma_a(x)=\infty\) and without Assumption~\ref{ass:mp}, the armwise lower CDF envelope is \(e_a(x)F^{\mathrm{obs}}_{a,x}(y)\) up to endpoint filling and the upper envelope is \(e_a(x)F^{\mathrm{obs}}_{a,x}(y)+1-e_a(x)\).  This is the conditional Manski mixture bound because the unobserved off-arm potential outcomes can be placed at the lower or upper support endpoint.
\end{corollary}

\begin{corollary}[Manski--Pepper shaped endpoint]\label{cor:mp-shaped}
Under Assumptions~\ref{ass:consistency}, \ref{ass:positivity}, \ref{ass:support}, \ref{ass:msm}, \ref{ass:quantile}, and \ref{ass:mp} with \(\Gamma_a(x)=\infty\), the endpoint fillers used in Corollary~\ref{cor:manski} must also satisfy \(Y(1)\ge Y(0)\) and the ordered-\(Z\) CDF inequalities in Assumption~\ref{ass:mp}.  The reduction is the conditional Manski--Pepper endpoint because the unrestricted missing-potential-outcome fillers are intersected exactly with those monotone response and monotone-IV inequalities.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is to rewrite the marginal odds-ratio restriction as a bounded likelihood-ratio restriction \(dP(Y(a)\mid X=x)/dP(Y\mid A=a,X=x)\in[\ell_a(x),u_a(x)]\) with unit mean.  The pointwise CDF bound is the elementary two-cell extremum for a bounded weight over the event \(\{Y\le y\}\).  On finite supports, each quantile statement becomes a pair of strict/weak linear inequalities in a single arm's weight vector, so the CQTE process problem reduces to enumerating finitely many support-cell assignments and checking the resulting bounded-weight feasibility systems.  The main algebraic tasks are to prove the iff direction for the union-of-polytopes representation and to construct or refute the claimed \(J_0,J_1\le3\), two-quantile gap witness.

\section{Honest scope flags}
Theorem~\ref{thm:cdf-envelope} is retained as background and should not be sold as a novel published contribution after \citet{MastenPoirierRen2025}.  Conjecture~\ref{conj:process-compatibility} and Conjecture~\ref{conj:minimal-gap} are the revised novelty-bearing claims and are deliberately marked not yet proved.  The Manski--Pepper material is now only an endpoint sanity check with \(S_{\mathrm{MP}}\) explicitly defined in Assumption~\ref{ass:mp}.  The v1 claim that closed-form clipping-and-inversion was the flagship novelty has been withdrawn in response to the v1 review.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft of the covariate-wise marginal-sensitivity CQTE envelope proposal; prior verdict: none.
\item v2 (revise) --- moved the novelty kernel to finite-support CQTE process compatibility, removed unverifiable citations, demoted endpoint reductions to sanity checks, and made \(S_{\mathrm{MP}}\) explicit; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[D'Amour et~al.(2019)]{DAmourFranksFeller2019}
D'Amour, A., Franks, A., and Feller, A. (2019).
Flexible sensitivity analysis for observational studies without observable implications.
\emph{Journal of the American Statistical Association}.

\bibitem[Dorn and Guo(2023)]{DornGuo2023}
Dorn, J. and Guo, K. (2023).
Sharp sensitivity analysis for inverse propensity weighting via quantile balancing.
\emph{Journal of the American Statistical Association}.

\bibitem[Fan and Park(2010)]{FanPark2010}
Fan, Y. and Park, S.~S. (2010).
Sharp bounds on the distribution of treatment effects and their statistical inference.
\emph{Econometric Theory}.

\bibitem[Firpo(2007)]{Firpo2007}
Firpo, S. (2007).
Efficient semiparametric estimation of quantile treatment effects.
\emph{Econometrica}.

\bibitem[Firpo and Ridder(2019)]{FirpoRidder2019}
Firpo, S. and Ridder, G. (2019).
Partial identification of the treatment effect distribution and its functionals.
\emph{Journal of Econometrics}.

\bibitem[Kallus et~al.(2019)]{KallusMaoZhou2019}
Kallus, N., Mao, X., and Zhou, A. (2019).
Interval estimation of individual-level causal effects under unobserved confounding.
\emph{Proceedings of the Twenty-Second International Conference on Artificial Intelligence and Statistics}.

\bibitem[Manski and Pepper(2000)]{ManskiPepper2000}
Manski, C.~F. and Pepper, J.~V. (2000).
Monotone instrumental variables: with an application to the returns to schooling.
\emph{Econometrica}.

\bibitem[Masten et~al.(2025)]{MastenPoirierRen2025}
Masten, M.~A., Poirier, A., and Ren, H. (2025).
Sensitivity analysis for treatment effects.
\emph{Working paper}.

\bibitem[Rosenbaum(1995)]{Rosenbaum1995}
Rosenbaum, P.~R. (1995).
Observational studies.
\emph{Springer}.

\bibitem[Tan(2006)]{Tan2006}
Tan, Z. (2006).
A distributional approach for causal inference using propensity scores.
\emph{Journal of the American Statistical Association}.

\bibitem[Yadlowsky et~al.(2022)]{YadlowskyNamkoongBasuDuchiTian2022}
Yadlowsky, S., Namkoong, H., Basu, S., Duchi, J., and Tian, L. (2022).
Bounds on the conditional and average treatment effect with unobserved confounding factors.
\emph{Annals of Statistics}.

\bibitem[Zhao et~al.(2019)]{ZhaoSmallBhattacharya2019}
Zhao, Q., Small, D.~S., and Bhattacharya, B.~B. (2019).
Sensitivity analysis for inverse probability weighting estimators via the percentile bootstrap.
\emph{Journal of the Royal Statistical Society: Series B}.
\end{thebibliography}

\end{document}
