% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_ordinal\_principal\_strata, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_ordinal\_principal\_strata} / \texttt{v1}%
  \\ \large\textit{Sharp adjacent-chain bounds for ordinal principal-stratum effects}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies a finite-support partial-identification problem for principal
stratum effects when the post-treatment intermediate is ordinal.  The causal
target is
\[
  \theta_g=\mu_{1g}-\mu_{0g},\qquad
  \mu_{zg}=\E\{Y(z)\mid G=g\},
\]
for a fixed principal stratum \(g=(S(0),S(1))\).  The estimand-defining
functional is the calibrated adjacent-chain linear program
\[
  L_g(P,\pi,\Gamma)
  =
  \min_{q\in\mathcal Q(P,\pi,\Gamma)}
  \{\mu_{1g}(q)-\mu_{0g}(q)\},\qquad
  U_g(P,\pi,\Gamma)
  =
  \max_{q\in\mathcal Q(P,\pi,\Gamma)}
  \{\mu_{1g}(q)-\mu_{0g}(q)\},
\]
where \(q\) is a latent principal-stratum posterior satisfying simplex,
principal-score calibration, and adjacent odds-ratio divergence constraints.
The main conclusion is sharpness:
\[
  \Theta_I(P,\pi,\Gamma;g)
  =
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)].
\]
The note confirms the Stage -1 chain-polytope conjecture in its finite-support
form: \(\Gamma=1\) collapses to the usual principal-score formula, \(K=2\)
reduces to the one-pair binary sensitivity problem, and for \(K\ge3\) the
shared middle ordinal stratum creates nonrectangular compatibility constraints
that can make an edgewise binary relaxation strictly too wide.
\end{abstract}

\section{Introduction}
Principal stratification defines causal effects inside subpopulations indexed
by the joint potential values of an intermediate variable.  In applications
such as intercurrent-event analysis, adherence, disease severity, and
post-treatment educational attainment, that intermediate is often ordinal
rather than binary.  A principal-stratum estimand is therefore scientifically
natural, but the stratum \(G=(S(0),S(1))\) is latent and the usual
principal-ignorability formula can be too strong.

The known principal-score approach identifies \(\theta_g\) when, conditional
on covariates and the observed intermediate cell, the latent principal stratum
is unrelated to the observed outcome.  Sensitivity analyses relax that
condition by allowing the posterior stratum weights to tilt with \(Y\).  The
question here is whether an ordinal relaxation can keep the ordered structure
of \(S\) rather than replacing it by unrelated adjacent binary problems.

This note proves that the appropriate finite-support object is a calibrated
adjacent-chain linear program.  The variables are posterior weights
\[
  q_{z,h}(x,y)
  =
  \Pr\{G=h\mid Z=z,S=h_z,X=x,Y=y\},
\]
and the restrictions say that these weights average back to the supplied
principal-score vector and that adjacent strata in the unobserved ordinal
coordinate have posterior odds ratios bounded by \(\Gamma\).  The resulting
interval is not merely an outer bound: it is the sharp identified set for the
principal-stratum effect under the maintained restrictions.

The result is useful because it separates three objects that are often
conflated.  The causal target is \(\theta_g\).  The identifying information is
the observable law \(P\), the supplied principal scores \(\pi\), and the
sensitivity parameter \(\Gamma\).  The computable object is the value interval
of a finite linear program.  That separation makes clear when the analysis
collapses to principal ignorability, when it is only a binary sensitivity
problem, and when a genuinely ordinal compatibility constraint is doing work.

\paragraph{Motivating conjecture(s).}
\paragraph{Conjecture 1: sharp ordinal chain polytope with nonrectangular compatibility (NOT YET PROVED).}
Under Assumptions~\ref{ass:randomization}--\ref{ass:nondegenerate-chain}, the following hold.

First, the sharp identified set for \(\theta_g\) is exactly the interval
\[
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)]
  =
  \left[
  \min_{q\in\mathcal Q(P,\pi,\Gamma)}\{\mu_{1g}(q)-\mu_{0g}(q)\},
  \max_{q\in\mathcal Q(P,\pi,\Gamma)}\{\mu_{1g}(q)-\mu_{0g}(q)\}
  \right].
\]
Second, for at least one three-vertex chain \(a\sim_z b\sim_z c\) in an observed cell, the projection of \(\mathcal Q(P,\pi,\Gamma)\) onto the two incident edge coordinates is generically nonrectangular: it is a proper subset of the product of the two separately feasible full-cell-scale edge projections because the same posterior coordinate \(q_{z,b}(x,y)\) must satisfy both adjacent inequalities and one calibration equation.  Equivalently, the shared middle stratum creates compatibility facets that are absent from any product of adjacent two-stratum sensitivity problems.

Third, as a scale-comparable diagnostic rather than a refutation of a named ordinal estimator, there exists an open set of observable laws \(P\) and principal-score vectors \(\pi\) for which the full-cell-scale edgewise binary-collapse interval strictly contains the ordinal sharp interval:
\[
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)]
  \subsetneq
  \mathcal B_{\mathrm{bin}}(P,\pi,\Gamma;g).
\]
The strictness mechanism is that separate edge problems choose incompatible full-cell-scale posterior tilts for the shared middle ordinal stratum, whereas \(\mathcal Q(P,\pi,\Gamma)\) requires one posterior vector to satisfy all adjacent inequalities at once.

\section{Related work and positioning}
Principal stratification was introduced by \cite{FrangakisRubin2002} to define
effects inside subpopulations indexed by joint potential values of
post-treatment variables; this note keeps that causal target and changes the
identifying restriction.  \cite{VanderWeele2011} reviews the use and limits of
principal stratification and emphasizes the practical pressure to dichotomize
non-binary intermediates; the present theorem shows what is lost when an
ordinal chain is replaced by edgewise binary relaxations.

\cite{DingLu2017} and \cite{JiangYangDing2022} develop principal-score
identification and estimation under principal ignorability.  In this note, the
\(\Gamma=1\) boundary of the LP reproduces that point-identification formula,
while \(\Gamma>1\) gives a sensitivity interval.  \cite{ForastiereMatteiDing2018}
connect principal ignorability to mediation analysis; their relevance here is
that the same principal-score logic is used, but it is embedded in a
partial-identification model rather than taken as an exact identifying
assumption.

\cite{NguyenStuartScharfsteinOgburn2024} study sensitivity to principal
ignorability violations in a one-sided noncompliance setting, and
\cite{WangZhangMealliBornkamp2023} give a binary clinical-trial workflow for
principal-ignorability sensitivity analysis.  Those papers motivate the
posterior-tilting viewpoint, but their binary or low-dimensional latent
geometry does not contain the three-vertex chain compatibility issue addressed
here.  \cite{WuAntonelli2024} show that violations of principal ignorability
lead to partial identification even when principal-strata distributions are
known; the present result gives a sharp finite-support LP for one specific
ordinal divergence restriction.  \cite{TongKahanHarhayLi2025} use an
odds-ratio sensitivity parameter in semiparametric principal stratification;
the difference is that this note focuses on the nonparametric finite ordinal
posterior polytope and its edge-compatibility facets.

Nonbinary principal-stratification work is also close, but it does not already
isolate the object studied here.  \cite{MatteiMealli2011} use augmented
designs to sharpen principal-strata direct effects; the additional design
information differs from the known-\(\pi\), bounded-posterior-divergence
restriction used below.  \cite{LeeDanielsSargent2010} analyze quality-of-life
outcomes with death/progression principal strata and sensitivity parameters,
showing the applied need for richer principal-strata models without deriving
the adjacent ordinal posterior polytope.  \cite{LuJiangDing2024} study
continuous post-treatment variables under principal-score style conditions;
their nonbinary intermediate is handled through continuous-stratum
identification and estimation, whereas this note uses the finite ordinal graph
to obtain a nonparametric sharp sensitivity LP.  Thus the claim here is not
that ordinal principal stratification is new; it is that the adjacent
principal-score posterior-divergence chain yields a sharp finite
partial-identification interval and a strict compatibility gap relative to
edgewise binary relaxations.

The proof method is in the partial-identification tradition of worst-case
completion and finite-dimensional optimization.  \cite{Manski1990} provides the
canonical bounded-outcome partial-identification viewpoint, while
\cite{BalkePearl1997} illustrates how causal restrictions with latent response
types can be converted into sharp linear programs.  Modern sharp sensitivity
analyses such as \cite{DornGuoKallus2022} and
\cite{FrauenMelnychukFeuerriegel2023} are close in optimization spirit, but
their sensitivity models concern unmeasured treatment confounding rather than
latent ordinal principal-stratum posteriors.

The closest in-repository analogue is the ordinal late partial-defier proposal,
which also observes that a shared ordinal middle object can make adjacent
binary bounds too wide.  The object is different here: the current theorem
couples posterior principal-stratum weights inside observed
\((Z,S,X,Y)\) cells, not instrumental-variable response paths.  Thus the
shared compatibility mechanism is similar, but the estimand, feasible set, and
sharp LP are specific to ordinal principal stratification.

\section{Formal setup}
\begin{definition}[Observed law and potential variables]\label{def:observed-law}
The observable law \(P\) is the law of \((Z,S,Y,X)\) on the finite support
\[
  \{0,1\}\times\{0,\ldots,K-1\}\times\mathcal Y\times\mathcal X,
  \qquad \mathcal Y\subset[0,1].
\]
Treatment \(Z\) is binary, \(S\) is an ordinal post-treatment intermediate,
\(Y\) is the bounded outcome, and \(X\) is a finite-support covariate.  Write
\[
  e_z=\Pr_P(Z=z),\qquad
  p_X(x)=\Pr_P(X=x),
\]
and let \(P_{zky\mid x}\) denote
\(\Pr_P(S=k,Y=y\mid Z=z,X=x)\).
\end{definition}

Potential intermediate values are \(S(0)\) and \(S(1)\).  The principal stratum
is
\[
  G=(S(0),S(1))\in\mathcal G_K:=\{0,\ldots,K-1\}^2.
\]
For \(g=(g_0,g_1)\), write \(g_z\) for the \(z\)-arm component.  The supplied
principal-score vector is
\[
  \pi_g(x)=\Pr(G=g\mid X=x),\qquad g\in\mathcal G_K.
\]
The population share of stratum \(g\) is
\[
  p_g=\sum_{x\in\mathcal X}p_X(x)\pi_g(x).
\]

\begin{definition}[Compatible strata and baseline cell weights]\label{def:cell-weights}
For an observed arm-level cell \((z,k,x)\), the compatible principal strata are
\[
  A_z(k)=\{h\in\mathcal G_K:h_z=k\}.
\]
Whenever \(\sum_{h\in A_z(k)}\pi_h(x)>0\), define the principal-score cell
weights
\[
  w^z_h(x)=
  \frac{\pi_h(x)}{\sum_{\ell\in A_z(k)}\pi_\ell(x)},
  \qquad h\in A_z(k).
\]
If the denominator is zero, the observed cell has zero probability under the
compatibility assumption below and no posterior weight is used there.
\end{definition}

\begin{definition}[Posterior-weight system]\label{def:posterior-system}
A posterior-weight system is a finite array
\[
  q=\{q_{z,h}(x,y): z\in\{0,1\},\ x\in\mathcal X,\ y\in\mathcal Y,\ h\in A_z(h_z)\}.
\]
The intended interpretation is
\[
  q_{z,h}(x,y)
  =
  \Pr(G=h\mid Z=z,S=h_z,X=x,Y=y).
\]
The maintained restrictions in Section~\ref{sec:assumptions} define the
feasible set \(\mathcal Q(P,\pi,\Gamma)\).
\end{definition}

\begin{definition}[Identified set]\label{def:identified-set}
For a fixed target stratum \(g\), the partial-identification object is
\[
  \Theta_I(P,\pi,\Gamma;g)
  =
  \{\theta_g(\mathbb M): \mathbb M
    \text{ is a latent law consistent with }P,\pi,\Gamma\},
\]
where \(\theta_g(\mathbb M)=\E_{\mathbb M}\{Y(1)\mid G=g\}
-\E_{\mathbb M}\{Y(0)\mid G=g\}\).  Consistency with \(P,\pi,\Gamma\) means
that the latent law has observable margin \(P\), has
\(\Pr(G=h\mid X=x)=\pi_h(x)\), satisfies randomization and consistency, and
satisfies the adjacent divergence restriction stated below.
\end{definition}

\paragraph{Locked parameters.}
\begin{itemize}
  \item qid: \texttt{pid\_ordinal\_principal\_strata}
  \item specialization: \texttt{v1}
  \item anchor\_cluster: Partial identification
  \item observable\_distribution\_P: law of \((Z,S,Y,X)\), where \(Z\) in
  \(\{0,1\}\) is randomized, \(S\) in \(\{0,\ldots,K-1\}\) is the observed
  ordinal post-treatment intermediate, \(Y\) in finite support Ygrid subset
  \([0,1]\), \(X\) in finite support Xgrid, \(K\ge3\) unless a theorem
  explicitly specializes to \(K=2\)
  \item parameter\_theta: \(\theta_g = \mu_{1g} - \mu_{0g}\) for a fixed
  principal stratum \(g=(s0,s1)\), with
  \(\mu_{zg}=\E[Y(z)\mid G=g]\) and \(G=(S(0),S(1))\)
  \item identifying\_restrictions: randomization, consistency, positivity,
  known covariate-conditional ordinal principal scores
  \(\pi_g(x)=\Pr(G=g\mid X=x)\), and Gamma-adjacent covariate-conditional
  principal-score divergence for latent posterior stratum weights inside each
  observed \((Z=z,S=k,X=x,Y=y)\) cell
  \item bounding\_functional: \(L_g(P,\pi,\Gamma)\), \(U_g(P,\pi,\Gamma)\), the
  sharp lower and upper values of \(\theta_g\) obtained by optimizing
  \(\mu_{1g}(q)-\mu_{0g}(q)\) over posterior weights \(q_{z,g}(x,y)\) satisfying
  principal-score calibration to the supplied pi, simplex constraints, and all
  adjacent odds-ratio divergence inequalities
\end{itemize}

\section{Assumptions}
\label{sec:assumptions}
\begin{assumption}[Randomization and consistency]\label{ass:randomization}
The potential variables satisfy
\[
  (Y(0),Y(1),S(0),S(1),X)\perp Z,
\]
and the observed variables obey
\[
  S=S(Z),\qquad Y=Y(Z).
\]
\end{assumption}

\begin{assumption}[Finite support, bounded outcome, and positivity]\label{ass:positivity}
The sets \(\mathcal X\), \(\mathcal Y\), and \(\mathcal G_K\) are finite,
\(\mathcal Y\subset[0,1]\), and \(0<e_z<1\) for \(z=0,1\).  If the target
stratum is \(g\), then
\[
  p_g=\sum_x p_X(x)\pi_g(x)>0.
\]
Every conditional probability and ratio used below is evaluated only on
observed cells \((z,k,x,y)\) with positive \(P\)-probability.  If an observed
cell has zero probability, its posterior weights are irrelevant to all
functionals.
\end{assumption}

\begin{assumption}[Known ordinal principal scores]\label{ass:principal-scores}
For every \(x\in\mathcal X\), the vector
\(\pi(x)=\{\pi_h(x):h\in\mathcal G_K\}\) is known or supplied by external
design information, satisfies
\[
  \pi_h(x)\ge0,\qquad \sum_{h\in\mathcal G_K}\pi_h(x)=1,
\]
and is compatible with the observed ordinal margins:
\[
  \Pr_P(S=k\mid Z=z,X=x)
  =
  \sum_{h\in A_z(k)}\pi_h(x)
\]
whenever \(\Pr_P(Z=z,X=x)>0\).
\end{assumption}

\begin{assumption}[Ordinal adjacency graph]\label{ass:adjacency}
Within an observed arm-level cell \(A_z(k)\), two strata \(h,\ell\in A_z(k)\)
are adjacent, written \(h\sim_z \ell\), when they agree in the observed
coordinate and differ by one ordinal step in the unobserved coordinate:
\[
  h_z=\ell_z=k,\qquad |h_{1-z}-\ell_{1-z}|=1.
\]
\end{assumption}

\begin{assumption}[Cellwise connected positive principal-score support]\label{ass:connected-support}
For every \(z,k,x\) with \(\Pr_P(Z=z,S=k,X=x)>0\), the subgraph of \(A_z(k)\)
induced by the vertices with \(w^z_h(x)>0\) is connected under
Assumption~\ref{ass:adjacency}.  If \(w^z_h(x)=0\), feasible posterior systems
set \(q_{z,h}(x,y)=0\) for every \(y\) in the support of
\((Y\mid Z=z,S=k,X=x)\).
\end{assumption}

\begin{assumption}[\(\Gamma\)-adjacent principal-score divergence]\label{ass:divergence}
Fix \(\Gamma\in[1,\infty]\).  A posterior-weight system belongs to
\(\mathcal Q(P,\pi,\Gamma)\) when, for every positive-probability observed cell
\((z,k,x,y)\), the following conditions hold.

First, the posterior weights are a simplex over the compatible strata:
\[
  q_{z,h}(x,y)\ge0,\qquad
  \sum_{h\in A_z(k)}q_{z,h}(x,y)=1.
\]
Second, they calibrate to the supplied principal-score cell weights:
\[
  \sum_{y\in\mathcal Y}
  q_{z,h}(x,y)
  \Pr_P(Y=y\mid Z=z,S=k,X=x)
  =
  w^z_h(x),
  \qquad h\in A_z(k).
\]
Third, for every adjacent pair \(h\sim_z\ell\) with positive
\(w^z_h(x)\) and \(w^z_\ell(x)\),
\[
  \Gamma^{-1} q_{z,\ell}(x,y)w^z_h(x)
  \le
  q_{z,h}(x,y)w^z_\ell(x)
  \le
  \Gamma q_{z,\ell}(x,y)w^z_h(x).
\]
When \(\Gamma=\infty\), the adjacent ratio inequalities are omitted while the
simplex and calibration constraints remain.
\end{assumption}

\begin{assumption}[Nondegenerate ordinal chain for the flagship comparison]\label{ass:nondegenerate-chain}
For statements about a strict ordinal-versus-binary gap, \(K\ge3\),
\(1<\Gamma<\infty\), and the target stratum \(g\) has at least one observed
arm cell containing three adjacent ordinal strata with positive principal
scores.
\end{assumption}

\section{Estimand-defining functional}
For \(q\in\mathcal Q(P,\pi,\Gamma)\), define the induced arm-specific
principal-stratum mean by
\[
  \mu_{zg}(q)
  =
  \frac{
    \E_P\!\left[
      \one\{Z=z,S=g_z\}q_{z,g}(X,Y)Y/e_z
    \right]
  }{p_g}.
\]
Equivalently, expanding over the finite support,
\[
  \mu_{zg}(q)
  =
  \frac{1}{p_g}
  \sum_{x\in\mathcal X} p_X(x)
  \Pr_P(S=g_z\mid Z=z,X=x)
  \sum_{y\in\mathcal Y}
  q_{z,g}(x,y)y
  \Pr_P(Y=y\mid Z=z,S=g_z,X=x).
\]

The bounding functional is
\[
  L_g(P,\pi,\Gamma)
  =
  \min_{q\in\mathcal Q(P,\pi,\Gamma)}
  \{\mu_{1g}(q)-\mu_{0g}(q)\},
\]
\[
  U_g(P,\pi,\Gamma)
  =
  \max_{q\in\mathcal Q(P,\pi,\Gamma)}
  \{\mu_{1g}(q)-\mu_{0g}(q)\}.
\]
The feasible set is nonempty because the constant posterior
\[
  q_{z,h}(x,y)=w^z_h(x)
\]
satisfies simplex, calibration, and the adjacent inequalities for every
\(\Gamma\ge1\).  Since all constraints are linear after multiplying by the
fixed positive principal-score weights, the bounds are finite-dimensional
linear-program values.  Theorem~\ref{thm:sharp-chain} proves that this
functional is sharp, not merely an outer bound.

\begin{definition}[Edgewise binary relaxation]\label{def:binary-relaxation}
For a diagnostic comparison, replace the single cell-level vector
\(\{q_{z,h}(x,y):h\in A_z(k)\}\) by separate full-cell-scale pair weights
\[
  r^e_{z,h}(x,y),\qquad e=\{a,b\},\quad a\sim_z b.
\]
For each edge \(e=\{a,b\}\), the pair weights satisfy nonnegativity,
\[
  r^e_{z,a}(x,y)+r^e_{z,b}(x,y)\le1,
\]
the same calibration equations for \(a\) and \(b\), and the same adjacent
odds-ratio inequalities on that edge.  Copies of a shared middle stratum across
two incident edges are not required to agree.  Let
\(\mathcal Q^e_{\mathrm{bin}}(P,\pi,\Gamma)\) be this edgewise feasible set.
For an edge \(e\) incident to \(g\), write
\[
  \mu^e_{zg}(r^e)
  =
  \frac{
    \E_P[
      \one\{Z=z,S=g_z\}r^e_{z,g}(X,Y)Y/e_z
    ]
  }{p_g}.
\]
The edgewise arm envelopes are
\[
  \ell^{\mathrm{bin}}_{zg}
  =
  \min_{e\in E_z(g)}
  \inf_{r^e\in\mathcal Q^e_{\mathrm{bin}}(P,\pi,\Gamma)}
  \mu^e_{zg}(r^e),
  \qquad
  u^{\mathrm{bin}}_{zg}
  =
  \max_{e\in E_z(g)}
  \sup_{r^e\in\mathcal Q^e_{\mathrm{bin}}(P,\pi,\Gamma)}
  \mu^e_{zg}(r^e),
\]
where \(E_z(g)\) is the set of adjacent edges in \(A_z(g_z)\) incident to
\(g\).  The binary-collapse diagnostic interval is
\[
  \mathcal B_{\mathrm{bin}}(P,\pi,\Gamma;g)
  =
  [\ell^{\mathrm{bin}}_{1g}-u^{\mathrm{bin}}_{0g},
   u^{\mathrm{bin}}_{1g}-\ell^{\mathrm{bin}}_{0g}].
\]
\end{definition}

\section{Target causal estimand}
The causal target is the scalar principal-stratum average causal effect
\[
  \theta_g=\mu_{1g}-\mu_{0g},
  \qquad
  \mu_{zg}=\E\{Y(z)\mid G=g\}.
\]
The conditioning event \(G=g\) refers to the joint potential intermediate
values, not to the observed intermediate \(S\).  Thus the target is not
identified by conditioning on observed \(S=g_z\); the observed cell generally
contains all strata in \(A_z(g_z)\).  The role of the posterior weights
\(q_{z,g}(x,y)\) is to complete the latent composition of each observed
\((Z=z,S=g_z,X=x,Y=y)\) cell subject to the maintained restrictions.  The
result below is therefore a containment and sharpness statement for
\(\theta_g\), not a definition of \(\theta_g\) as the LP value.

\section{Main theorems}
\begin{theorem}[Sharp calibrated adjacent-chain bounds]\label{thm:sharp-chain}
Under Assumptions~\ref{ass:randomization}--\ref{ass:divergence}, for every
target stratum \(g\) with \(p_g>0\),
\[
  \Theta_I(P,\pi,\Gamma;g)
  =
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)].
\]
Equivalently, every latent law satisfying the maintained restrictions yields a
value of \(\theta_g\) inside the LP interval, and every value in the LP interval
is attained by at least one latent law satisfying those restrictions.
\end{theorem}

This theorem confirms the first clause of Conjecture 1.
The new content relative to principal-score identification is that the
posterior-tilting sensitivity model remains sharp for \(K\ge3\) when all
adjacent ordinal restrictions are imposed simultaneously.  Compared with the
Balke--Pearl style LP tradition, the response type here is not a treatment or
instrument response; it is the posterior principal-stratum composition inside
an observed ordinal cell.

\begin{proposition}[Principal-ignorability collapse]\label{prop:pi-collapse}
Under Assumptions~\ref{ass:randomization}--\ref{ass:divergence} with
\(\Gamma=1\), including the connected-support condition in
Assumption~\ref{ass:connected-support}, the feasible set contains exactly the
principal-score posterior
\[
  q_{z,h}(x,y)=w^z_h(x)
\]
on every positive-support observed cell.  Hence the sharp interval is the
singleton
\[
  L_g(P,\pi,1)=U_g(P,\pi,1)
  =
  \frac{\E_P[\one\{Z=1,S=g_1\}w^1_g(X)Y/e_1]}{p_g}
  -
  \frac{\E_P[\one\{Z=0,S=g_0\}w^0_g(X)Y/e_0]}{p_g}.
\]
\end{proposition}

\begin{proposition}[Binary one-pair reduction]\label{prop:binary-reduction}
Under Assumptions~\ref{ass:randomization}--\ref{ass:divergence} with \(K=2\),
every nontrivial observed cell \(A_z(k)\) has at most one adjacent latent pair.
Consequently \(\mathcal Q(P,\pi,\Gamma)\) factors across observed cells into
calibrated binary odds-ratio sensitivity sets, and the sharp interval is the
one obtained by optimizing the two binary arm-specific posterior-tilting
problems and differencing their endpoints.
\end{proposition}

Propositions~\ref{prop:pi-collapse} and \ref{prop:binary-reduction} confirm the
principal-ignorability and binary sanity checks in the Stage -1 proposal.  They
are calibration results rather than the main novelty: they show that the LP
has the right boundaries before one uses it for ordinal sensitivity analysis.

\begin{theorem}[Nonrectangular ordinal compatibility and strict edgewise gap]\label{thm:nonrectangular}
Under Assumptions~\ref{ass:randomization}--\ref{ass:nondegenerate-chain}, the
projection of the full ordinal feasible set onto two incident adjacent-edge
coordinates is a subset of the product of the separately feasible edge
projections.  Whenever the two edge projections assign different
full-cell-scale posterior functions to their shared middle stratum, that
containment is proper.  For every \(P,\pi,\Gamma\), the sharp ordinal interval
is contained in the full-cell-scale edgewise binary interval,
\[
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)]
  \subseteq
  \mathcal B_{\mathrm{bin}}(P,\pi,\Gamma;g).
\]
Moreover, for every finite \(\Gamma>1\) there is a nonempty relative-open set
of finite-support laws \(P\) and compatible principal-score vectors \(\pi\),
within the margin-compatible simplex with \(p_g>0\) and a positive three-chain
target-arm cell, for which
\[
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)]
  \subsetneq
  \mathcal B_{\mathrm{bin}}(P,\pi,\Gamma;g).
\]
\end{theorem}

This theorem confirms the remaining clauses of Conjecture 1, with the word
``generically'' made precise as strictness on a nonempty relative-open set of
problem instances satisfying the stated compatibility and positivity
hypotheses.  The
result is important because it says that solving adjacent two-stratum
sensitivity problems independently can be conservative in a way that is not
forced by the causal target.  The difference from binary principal-stratum
sensitivity analyses is exactly the shared middle ordinal coordinate.

\section{Interpretation}
Theorem~\ref{thm:sharp-chain} says that the LP is the identified set, not a
computational approximation.  The analyst may therefore report
\([L_g,U_g]\) as the exact set of principal-stratum effects compatible with the
observed law, the supplied principal scores, and the adjacent divergence
restriction.  The causal estimand remains \(\theta_g\); the LP is the
observable-and-sensitivity functional that brackets it.

When \(\Gamma=1\), adjacent posterior odds must equal adjacent principal-score
odds at every outcome value.  Connected positive support then propagates this
equality through the ordinal chain, so the posterior composition is
outcome-invariant and the bound collapses to the usual principal-score formula.
This is the point-identification boundary corresponding to principal
ignorability.

As \(\Gamma\) grows, the adjacent restrictions allow more outcome-dependent
posterior tilting.  At \(\Gamma=\infty\), the odds-ratio constraints disappear;
the remaining information is only the simplex constraint, principal-score
calibration, and the bounded finite support of \(Y\).  This is a calibrated
Manski-style completion problem.  If the principal-score calibration were also
removed, the natural bounded-outcome effect range would be the vacuous interval
\([-1,1]\).

For \(K=2\), there is no middle stratum shared by two adjacent edges.  The
ordinal LP therefore reduces to a binary posterior-tilting problem in each
relevant observed cell.  For \(K\ge3\), an observed cell contains chains such as
\[
  a\sim_z b\sim_z c.
\]
The same posterior coordinate \(q_{z,b}(x,y)\) must satisfy both the
\((a,b)\) and \((b,c)\) inequalities and a single calibration equation.  The
tightening work is done by this shared-coordinate compatibility condition.
An edgewise binary analysis drops exactly that condition by allowing one copy
of the middle stratum on the left edge and another copy on the right edge.

\section{Step-by-step proof}
\begin{lemma}[Bayes disintegration of feasible posteriors]\label{lem:disintegration}
Under Assumptions~\ref{ass:randomization}--\ref{ass:divergence}, feasible
posterior systems \(q\in\mathcal Q(P,\pi,\Gamma)\) are in one-to-one
correspondence, up to irrelevant couplings of \((Y(0),Y(1))\), with latent laws
that reproduce \(P\), have principal scores \(\pi\), and satisfy the adjacent
divergence restriction.
\end{lemma}

\begin{proof}
First take a latent law satisfying the maintained restrictions.  On every
positive observed cell define
\[
  q_{z,h}(x,y)
  =
  \Pr(G=h\mid Z=z,S=k,X=x,Y=y),
  \qquad h\in A_z(k).
\]
The simplex constraints follow from the definition of a conditional
probability.  By randomization and consistency,
\[
  \Pr(G=h\mid Z=z,S=k,X=x)
  =
  \Pr(G=h\mid S(z)=k,X=x)
  =
  w^z_h(x),
\]
where the last equality is Assumption~\ref{ass:principal-scores} and Bayes'
rule on the finite set \(A_z(k)\).  Taking conditional expectation of
\(q_{z,h}(x,Y)\) given \((Z=z,S=k,X=x)\) gives the calibration equation in
Assumption~\ref{ass:divergence}.  The adjacent odds-ratio inequalities are
exactly the maintained sensitivity restriction.  Thus every admissible latent
law yields a feasible \(q\).

Conversely, fix \(q\in\mathcal Q(P,\pi,\Gamma)\).  Construct a latent law as
follows.  Draw \(X\) from its \(P\)-margin, draw \(G\) conditional on \(X=x\)
with probabilities \(\pi_h(x)\), set \(S(0)=G_0\) and \(S(1)=G_1\), and draw
\(Z\) independently of all potential variables with \(\Pr(Z=z)=e_z\).  For
each arm \(z\), stratum \(h\), and covariate \(x\) with \(w^z_h(x)>0\), define
the conditional marginal law of \(Y(z)\) by
\[
  m_{z,h,x}(y)
  =
  \frac{
    q_{z,h}(x,y)\Pr_P(Y=y\mid Z=z,S=h_z,X=x)
  }{w^z_h(x)}.
\]
The calibration equation implies
\[
  \sum_y m_{z,h,x}(y)=1.
\]
If \(w^z_h(x)=0\), Assumption~\ref{ass:connected-support} sets the corresponding
posterior weights to zero and the conditional law can be chosen arbitrarily
because the event \(\{G=h,X=x\}\) has zero probability.  Couple \(Y(0)\) and
\(Y(1)\) arbitrarily conditional on \((G,X)\) with these two marginals, for
example independently.

It remains to check that the observable margin is \(P\).  For \(h\in A_z(k)\),
\[
  \pi_h(x)m_{z,h,x}(y)
  =
  \pi_h(x)
  \frac{q_{z,h}(x,y)\Pr_P(Y=y\mid Z=z,S=k,X=x)}{w^z_h(x)}.
\]
Since
\[
  w^z_h(x)=\frac{\pi_h(x)}{\sum_{\ell\in A_z(k)}\pi_\ell(x)},
\]
the sum over \(h\in A_z(k)\) equals
\[
  \left\{\sum_{\ell\in A_z(k)}\pi_\ell(x)\right\}
  \Pr_P(Y=y\mid Z=z,S=k,X=x)
  \sum_{h\in A_z(k)}q_{z,h}(x,y).
\]
By the simplex constraint, the last sum is one.  By
Assumption~\ref{ass:principal-scores}, the prefactor is
\(\Pr_P(S=k\mid Z=z,X=x)\).  Thus the constructed law gives
\[
  \Pr(Y=y,S=k\mid Z=z,X=x)
  =
  \Pr_P(S=k\mid Z=z,X=x)
  \Pr_P(Y=y\mid Z=z,S=k,X=x),
\]
which is the \(P\)-conditional law.  Multiplying by the \(P\)-margins of
\((Z,X)\) gives the full observable law \(P\).  The constructed posterior of
\(G\) given \((Z=z,S=k,X=x,Y=y)\) is \(q\) by the same Bayes calculation, so the
adjacent divergence inequalities hold.  This proves the correspondence.
\end{proof}

\begin{lemma}[LP interval image]\label{lem:lp-interval}
The set \(\mathcal Q(P,\pi,\Gamma)\) is a nonempty compact convex polytope, and
the map \(q\mapsto\mu_{1g}(q)-\mu_{0g}(q)\) is linear.  Its image is therefore a
closed interval whose endpoints are attained by extreme points of
\(\mathcal Q(P,\pi,\Gamma)\).
\end{lemma}

\begin{proof}
Nonemptiness follows from the constant posterior \(q_{z,h}(x,y)=w^z_h(x)\).
The simplex and calibration restrictions are linear equalities and
inequalities.  The adjacent odds-ratio restrictions are linear inequalities
after multiplying by the fixed nonnegative weights \(w^z_h(x)\) and
\(w^z_\ell(x)\), with zero-weight vertices handled by
Assumption~\ref{ass:connected-support}.  Boundedness follows from
\(0\le q_{z,h}(x,y)\le1\).  Hence \(\mathcal Q(P,\pi,\Gamma)\) is compact and
convex.  The denominator \(p_g\) is positive by Assumption~\ref{ass:positivity},
so \(\mu_{zg}(q)\) is a fixed linear combination of the coordinates of \(q\).
The continuous image of a compact convex set under a linear map into
\(\mathbb R\) is a compact interval, and linear programming attains its extrema
at extreme points.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:sharp-chain}]
Let \(\mathbb M\) be any latent law consistent with
Assumptions~\ref{ass:randomization}--\ref{ass:divergence}.  By
Lemma~\ref{lem:disintegration}, it induces a feasible
\(q\in\mathcal Q(P,\pi,\Gamma)\).  Consistency gives
\[
  \E_{\mathbb M}\{Y(z)\mid G=g\}
  =
  \frac{
    \E_{\mathbb M}[\one\{G=g\}Y(z)]
  }{p_g}.
\]
By randomization and consistency,
\[
  \E_{\mathbb M}[\one\{G=g\}Y(z)]
  =
  \E_{\mathbb M}[\one\{Z=z,S=g_z,G=g\}Y/e_z].
\]
Conditioning on \((Z=z,S=g_z,X,Y)\) and using the definition of \(q\),
\[
  \E_{\mathbb M}[\one\{Z=z,S=g_z,G=g\}Y/e_z]
  =
  \E_P[\one\{Z=z,S=g_z\}q_{z,g}(X,Y)Y/e_z].
\]
Therefore \(\theta_g(\mathbb M)=\mu_{1g}(q)-\mu_{0g}(q)\), so every admissible
latent value lies in \([L_g,U_g]\).

For the reverse inclusion, take any \(q\in\mathcal Q(P,\pi,\Gamma)\).
Lemma~\ref{lem:disintegration} constructs a latent law consistent with all
maintained restrictions whose induced arm means are exactly
\(\mu_{zg}(q)\).  Hence every value of the linear image of
\(\mathcal Q(P,\pi,\Gamma)\) is attainable.  Lemma~\ref{lem:lp-interval} says
that this image is precisely the closed interval between its minimum and
maximum.  Thus
\[
  \Theta_I(P,\pi,\Gamma;g)
  =
  [L_g(P,\pi,\Gamma),U_g(P,\pi,\Gamma)].
\]
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:pi-collapse}]
Set \(\Gamma=1\).  For every adjacent positive-weight pair \(h\sim_z\ell\), the
divergence inequality becomes the equality
\[
  q_{z,\ell}(x,y)w^z_h(x)=q_{z,h}(x,y)w^z_\ell(x).
\]
Thus
\[
  \frac{q_{z,h}(x,y)}{w^z_h(x)}
  =
  \frac{q_{z,\ell}(x,y)}{w^z_\ell(x)}
\]
on every adjacent edge with positive weights.  By the connected-positive-support
condition, this ratio is a common constant \(c_{z,k,x,y}\) across the whole
positive-support component of \(A_z(k)\).  Summing over \(h\in A_z(k)\) gives
\[
  1=\sum_h q_{z,h}(x,y)
  =
  c_{z,k,x,y}\sum_h w^z_h(x)
  =
  c_{z,k,x,y}.
\]
Zero-weight vertices carry zero posterior mass by
Assumption~\ref{ass:connected-support}.  Hence \(q_{z,h}(x,y)=w^z_h(x)\) for
all relevant coordinates.  Substituting this unique feasible posterior into
the definition of \(\mu_{zg}(q)\) gives the displayed singleton formula.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:binary-reduction}]
If \(K=2\), then within any observed cell \(A_z(k)\) the unobserved coordinate
can take only the two values \(0\) and \(1\).  Therefore the ordinal adjacency
graph has either no positive edge or exactly one positive edge.  There is no
third vertex and no shared middle coordinate.  The constraints defining
\(\mathcal Q(P,\pi,\Gamma)\) in that cell are exactly the two-stratum simplex,
the two calibration equations, and one odds-ratio bound.  The objective is a
sum of the arm-specific cell objectives, so optimizing \(\mu_{1g}-\mu_{0g}\)
amounts to optimizing the \(Z=1,S=g_1\) binary problem and the
\(Z=0,S=g_0\) binary problem in opposite directions and differencing the
endpoints.  This is the one-pair posterior-tilting bound.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:nonrectangular}]
Let \(a\sim_z b\sim_z c\) be a three-vertex chain in a positive observed cell.
Any ordinal feasible vector \(q\) induces edge coordinates
\((q_{z,a},q_{z,b})\) on edge \(\{a,b\}\) and \((q_{z,b},q_{z,c})\) on edge
\(\{b,c\}\).  Each edge coordinate satisfies the corresponding full-cell-scale
binary constraints, so the projection of \(\mathcal Q(P,\pi,\Gamma)\) is a
subset of the product of the two separately feasible edge projections.

The inclusion is proper whenever the product contains two edge solutions with
different middle coordinates.  Indeed, an element of the product may have
middle copies \(r^{ab}_{z,b}(x,y)\) and \(r^{bc}_{z,b}(x,y)\).  If these
functions differ for some \((x,y)\), no single ordinal posterior coordinate
\(q_{z,b}(x,y)\) can project to both edges.  Hence the product point has no
preimage in \(\mathcal Q(P,\pi,\Gamma)\), proving nonrectangularity.

The same projection gives the general outer containment.  For any
\(q\in\mathcal Q(P,\pi,\Gamma)\) and any edge \(e\in E_z(g)\), set
\[
  r^e_{z,h}(x,y)=q_{z,h}(x,y),\qquad h\in e.
\]
The simplex constraint for the whole ordinal cell implies the pair inequality
\(r^e_{z,a}+r^e_{z,b}\le1\); calibration and the adjacent ratio inequality are
inherited coordinatewise.  Thus \(r^e\in\mathcal Q^e_{\mathrm{bin}}\), and
\[
  \mu_{zg}(q)=\mu^e_{zg}(r^e)
\]
for each incident edge.  Consequently
\[
  \ell^{\mathrm{bin}}_{zg}\le \mu_{zg}(q)\le u^{\mathrm{bin}}_{zg},
  \qquad z=0,1.
\]
Every ordinal feasible effect therefore lies in
\[
  [\ell^{\mathrm{bin}}_{1g}-u^{\mathrm{bin}}_{0g},
   u^{\mathrm{bin}}_{1g}-\ell^{\mathrm{bin}}_{0g}],
\]
which proves
\([L_g,U_g]\subseteq\mathcal B_{\mathrm{bin}}(P,\pi,\Gamma;g)\).

It remains to show that the containment can be strict for a complete
finite-support problem.  Fix \(K=3\), \(\mathcal X=\{x_0\}\),
\(\mathcal Y=\{0,1\}\), \(e_0=e_1=1/2\), and target
\[
  g=b=(1,1).
\]
In the treated target cell \(Z=1,S=1\), let
\[
  a=(0,1),\qquad b=(1,1),\qquad c=(2,1).
\]
Choose \(0<\varepsilon<1/6\) and set
\[
  \pi_a(x_0)=\pi_b(x_0)=\pi_c(x_0)=\frac{1-6\varepsilon}{3},
  \qquad
  \pi_h(x_0)=\varepsilon
  \quad
  \text{for }h\in\mathcal G_3\setminus\{a,b,c\}.
\]
Define the observable intermediate margins by the required compatibility
equations
\[
  \Pr_P(S=k\mid Z=z,X=x_0)=\sum_{h\in A_z(k)}\pi_h(x_0).
\]
Set
\[
  \Pr_P(Y=1\mid Z=1,S=1,X=x_0)=\frac12,
  \qquad
  \Pr_P(Y=1\mid Z=0,S=1,X=x_0)=0,
\]
and assign any fixed probabilities in \((0,1)\), for instance \(1/2\), to the
remaining observed cells.  This specifies a full finite-support law \(P\)
compatible with the displayed \(\pi\), with \(p_b=(1-6\varepsilon)/3>0\).
Inside the treated target cell,
\[
  w_a=w_b=w_c=\frac13,\qquad
  \Pr(Y=1\mid Z=1,S=1,X=x_0)=\frac12.
\]
Write \(t=q_{1,b}(x_0,1)\).  In the coherent ordinal problem, calibration gives
\(q_h^0+q_h^1=2/3\) for each \(h\), and the \(Y=0\) simplex equation plus the
two inequalities \(q_a^0\le\Gamma q_b^0\) and
\(q_c^0\le\Gamma q_b^0\) imply
\[
  1=q_a^0+q_b^0+q_c^0
  \le
  (2\Gamma+1)q_b^0
  =
  (2\Gamma+1)\left(\frac23-t\right).
\]
Hence
\[
  t\le
  \frac{4\Gamma-1}{3(2\Gamma+1)}.
\]
The bound is attained by
\[
  q_b^0=\frac{1}{2\Gamma+1},\quad
  q_a^0=q_c^0=\frac{\Gamma}{2\Gamma+1},\quad
  q_b^1=\frac{4\Gamma-1}{3(2\Gamma+1)},\quad
  q_a^1=q_c^1=\frac{\Gamma+2}{3(2\Gamma+1)}.
\]
On the single edge \(\{a,b\}\), the full-cell-scale binary relaxation has only
one companion for \(b\).  Pair calibration, the \(Y=1\) pair simplex
\(r_a^1+r_b^1\le1\), and the \(Y=0\) ratio inequality
\(r_a^0\le\Gamma r_b^0\) give
\[
  r_b^1-\frac13\le \Gamma\left(\frac23-r_b^1\right),
\]
so
\[
  r_b^1\le
  \frac{2\Gamma+1}{3(\Gamma+1)}.
\]
This is attained by
\[
  r_b^1=\frac{2\Gamma+1}{3(\Gamma+1)},\quad
  r_a^1=\frac{\Gamma+2}{3(\Gamma+1)},\quad
  r_b^0=\frac{1}{3(\Gamma+1)},\quad
  r_a^0=\frac{\Gamma}{3(\Gamma+1)}.
\]
The binary upper value exceeds the ordinal upper value by
\[
  \frac{2\Gamma+1}{3(\Gamma+1)}
  -
  \frac{4\Gamma-1}{3(2\Gamma+1)}
  =
  \frac{\Gamma+2}{3(\Gamma+1)(2\Gamma+1)}
  >0.
\]
Because
\[
  \frac{\Pr_P(S=1\mid Z=1,X=x_0)}{p_b}=\frac{1-6\varepsilon}{(1-6\varepsilon)/3}
  =3,
\]
the treated arm mean multiplies these posterior coordinates by \(1/2\cdot3\).
Thus the binary upper treated-arm envelope exceeds the ordinal treated-arm
upper value by
\[
  \frac{\Gamma+2}{2(\Gamma+1)(2\Gamma+1)}.
\]
In the opposite target arm \(Z=0,S=1\), \(Y=0\) almost surely, so both the
ordinal and edgewise programs have lower and upper arm mean equal to zero.
Therefore the upper endpoint of
\(\mathcal B_{\mathrm{bin}}(P,\pi,\Gamma;g)\) is strictly larger than
\(U_g(P,\pi,\Gamma)\), while the outer containment already proved gives
strict interval containment.

Finally, the strict gap is not an isolated equality artifact.  The feasible
sets are compact finite-dimensional polyhedra, the objectives and calibration
right-hand sides vary continuously with \((P,\pi)\) whenever margin
compatibility, positive denominators, and \(p_b>0\) are preserved, and the
constant posterior remains feasible.  Hence the relevant LP value functions
are continuous on a neighborhood in the margin-compatible parameter space.
Replacing the zero probability in the opposite arm by a sufficiently small
\(\rho>0\), and then allowing sufficiently small compatible perturbations of
both \(P\) and \(\pi\), preserves the active positive gap above.  The strict
containment therefore holds on a nonempty relative-open set with positive
three-chain margins and \(p_g>0\).
\end{proof}

\section{Sanity checks}
\paragraph{Principal ignorability.}
When \(\Gamma=1\), Proposition~\ref{prop:pi-collapse} gives
\[
  L_g(P,\pi,1)=U_g(P,\pi,1),
\]
and the common value is the standard principal-score reweighting formula.  This
is the zero-width, point-identification check.

\paragraph{No adjacent divergence restriction.}
When \(\Gamma=\infty\), the ratio inequalities are absent.  The arm-specific
problem becomes a calibrated finite-support worst-case completion: the target
stratum's posterior mass must average to \(w^z_g(x)\), but it may be assigned
to high or low outcome values subject only to the simplex constraints.  This is
the relevant Manski-style bound when principal scores remain known.  If one
also removed the principal-score calibration, boundedness of \(Y\in[0,1]\)
would leave only the natural effect range \([-1,1]\).

\paragraph{Binary ordinal scale.}
For \(K=2\), Proposition~\ref{prop:binary-reduction} removes the ordinal
compatibility issue.  Each observed cell contains at most one adjacent pair, so
the sharp set is exactly the binary posterior-odds sensitivity interval.

\paragraph{Degenerate outcome cell.}
If \(Y\) is constant within every relevant observed cell, then posterior tilting
cannot change the conditional mean in that cell.  The LP still has latent
posterior uncertainty, but the target mean contribution is fixed because every
feasible posterior is multiplied by the same outcome value.

\paragraph{No maintained MTR restriction.}
There is no monotone-treatment-response restriction in the locked parameter
block.  An MTR specialization would be an additional shape restriction on
\((Y(0),Y(1))\), not a consequence of the adjacent principal-score divergence
model studied here.

\section{Counterexample or minimality check}
\label{sec:counterexample-minimality}
The positive result does not survive replacing the ordinal feasible set by the
product of its adjacent binary edge relaxations.  The smallest useful example
embeds the local three-stratum calculation in a complete finite-support law.
Let \(K=3\), \(\mathcal X=\{x_0\}\), \(\mathcal Y=\{0,1\}\), \(e_0=e_1=1/2\),
and target \(g=b=(1,1)\).  In the treated target cell \(Z=1,S=1\), define
\[
  a=(0,1),\qquad b=(1,1),\qquad c=(2,1),
\]
so \(a\sim_1 b\sim_1 c\).  Choose any \(0<\varepsilon<1/6\), set
\(\pi_a=\pi_b=\pi_c=(1-6\varepsilon)/3\) and set every other principal score
equal to \(\varepsilon\).  Let \(P\) have the compatible intermediate margins
\[
  \Pr_P(S=k\mid Z=z,X=x_0)=\sum_{h\in A_z(k)}\pi_h,
\]
put
\[
  \Pr_P(Y=1\mid Z=1,S=1,X=x_0)=\frac12,
  \qquad
  \Pr_P(Y=1\mid Z=0,S=1,X=x_0)=0,
\]
and assign any fixed probabilities to the remaining observed cells.  Then the
treated target cell has equal principal-score cell weights
\[
  w_a=w_b=w_c=\frac13,
\]
and
\[
  \Pr(Y=1\mid Z=1,S=1,X=x_0)
  =
  \Pr(Y=0\mid Z=1,S=1,X=x_0)
  =
  \frac12.
\]
Set \(\Gamma=2\).  Write
\[
  q_h^1=q_{1,h}(x_0,1),\qquad q_h^0=q_{1,h}(x_0,0).
\]
Calibration gives
\[
  q_h^0+q_h^1=\frac23,\qquad h=a,b,c,
\]
and the two simplex equations give
\[
  q_a^1+q_b^1+q_c^1=1,\qquad
  q_a^0+q_b^0+q_c^0=1.
\]
Maximizing the middle posterior \(q_b^1\) subject to both adjacent odds-ratio
constraints has solution
\[
  (q_a^0,q_b^0,q_c^0,q_a^1,q_b^1,q_c^1)
  =
  \left(\frac25,\frac15,\frac25,\frac4{15},\frac7{15},\frac4{15}\right).
\]
Thus the coherent ordinal cell has \(\sup q_b^1=7/15\).

For the full-cell-scale binary relaxation on the edge \(\{a,b\}\), the
corresponding optimization ignores the \(b\sim_z c\) constraint and has feasible
solution
\[
  (r_a^0,r_b^0,r_a^1,r_b^1)
  =
  \left(\frac29,\frac19,\frac49,\frac59\right),
\]
which satisfies pair calibration, the pair simplex inequalities, and the
\(\Gamma=2\) odds-ratio bounds.  Hence the edgewise relaxation allows
\(r_b^1=5/9>7/15\).  Since \(Y=0\) in the opposite target arm, both programs
give the same zero value for \(\mu_{0b}\).  Therefore, for the shared middle
target stratum \(b=(1,1)\), the upper endpoint of
\(\mathcal B_{\mathrm{bin}}\) is strictly larger than the sharp ordinal upper
endpoint.

This example is also the minimality check for the shared-coordinate condition.
If the requirement that the same \(q_{z,b}(x,y)\) serve both incident edges is
dropped, the two adjacent binary problems can choose incompatible middle
posterior tilts.  The nearest correct replacement is not an equality with the
binary relaxation; it is the sharp ordinal LP of Theorem~\ref{thm:sharp-chain},
with the binary interval retained only as an outer diagnostic.

\section{Formalization checklist}
\paragraph{Finite probabilistic objects.}
\begin{itemize}
  \item Observable law:
  \(P\) on
  \(\{0,1\}\times\{0,\ldots,K-1\}\times\mathcal Y\times\mathcal X\),
  with \(\mathcal X\) and \(\mathcal Y\) finite and \(\mathcal Y\subset[0,1]\).
  \item Principal strata:
  \(\mathcal G_K=\{0,\ldots,K-1\}^2\), with coordinate projection
  \(g\mapsto g_z\).
  \item Principal scores:
  \(\pi:\mathcal X\to\Delta(\mathcal G_K)\), satisfying the observed-margin
  compatibility equations.
  \item Compatible-cell set:
  \(A_z(k)=\{h:h_z=k\}\).
  \item Cell weights:
  \(w^z_h(x)=\pi_h(x)/\sum_{\ell\in A_z(k)}\pi_\ell(x)\) on positive
  denominator cells.
  \item Posterior system:
  \(q_{z,h}(x,y)\) indexed by arm, compatible stratum, covariate, and outcome.
\end{itemize}

\paragraph{Probabilistic assumptions.}
\begin{itemize}
  \item Randomization:
  \((Y(0),Y(1),S(0),S(1),X)\perp Z\).
  \item Consistency:
  \(S=S(Z)\) and \(Y=Y(Z)\).
  \item Positivity:
  \(0<e_z<1\), \(p_g>0\), and all conditioning events used in ratios have
  positive probability.
  \item Known principal-score compatibility:
  \(\Pr(S=k\mid Z=z,X=x)=\sum_{h\in A_z(k)}\pi_h(x)\).
  \item Adjacent divergence:
  linearized odds-ratio inequalities for every adjacent pair in the ordinal
  graph.
\end{itemize}

\paragraph{Deterministic identities and lemmas.}
\begin{itemize}
  \item Bayes cell identity:
  \(\Pr(G=h\mid S(z)=k,X=x)=w^z_h(x)\) for \(h\in A_z(k)\).
  \item Calibration identity:
  \(\sum_y q_{z,h}(x,y)\Pr(Y=y\mid Z=z,S=k,X=x)=w^z_h(x)\).
  \item Latent-law construction:
  \(m_{z,h,x}(y)=q_{z,h}(x,y)\Pr(Y=y\mid Z=z,S=h_z,X=x)/w^z_h(x)\).
  \item Observable-margin reconstruction:
  \(\sum_{h\in A_z(k)}\pi_h(x)m_{z,h,x}(y)
  =
  \Pr(S=k\mid Z=z,X=x)\Pr(Y=y\mid Z=z,S=k,X=x)\).
  \item LP structure:
  simplex, calibration, and adjacent divergence constraints define a compact
  convex polytope; the target map is linear.
  \item Connected-chain propagation:
  at \(\Gamma=1\), equality of adjacent posterior-to-prior ratios on a
  connected graph implies \(q=w\).
  \item Binary reduction:
  when \(K=2\), each observed cell has at most one edge and no shared middle
  coordinate.
  \item Nonrectangularity:
  product edge projections may assign two different functions to the shared
  middle coordinate; a coherent ordinal posterior cannot.
  \item Edgewise outer-containment map:
  from any ordinal feasible \(q\), restrict coordinates to each incident edge
  to obtain a full-cell-scale binary feasible \(r^e\), giving
  \(\ell^{\mathrm{bin}}_{zg}\le\mu_{zg}(q)\le u^{\mathrm{bin}}_{zg}\).
  \item Strict-gap witness:
  the \(K=3\), \(\mathcal Y=\{0,1\}\), equal-treated-cell-weight construction
  with target \(g=(1,1)\), and the continuity argument on the
  margin-compatible parameter space with \(p_g>0\).
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a sharp partial-identification result for
ordinal principal-stratum effects under known principal scores and
\(\Gamma\)-adjacent posterior odds-ratio divergence.  The bound is tightened by
the requirement that one posterior vector satisfy all adjacent ordinal
constraints and principal-score calibration simultaneously.  It becomes
point-identifying at \(\Gamma=1\), reduces to the usual binary sensitivity
problem when \(K=2\), and widens to a calibrated Manski-style completion when
\(\Gamma=\infty\).  For \(K\ge3\), the shared middle stratum creates
nonrectangular compatibility facets, so an edgewise binary relaxation is only
an outer diagnostic and can be strictly too wide.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association} 92, 1171--1176.

\bibitem{DingLu2017}
Ding, P. and Lu, J. (2017).
Principal stratification analysis using principal scores.
\emph{Journal of the Royal Statistical Society: Series B} 79, 757--777.

\bibitem{DornGuoKallus2022}
Dorn, J., Guo, K., and Kallus, N. (2022).
Doubly-valid/doubly-sharp sensitivity analysis for causal inference with
unmeasured confounding.
\emph{arXiv:2112.11449}.

\bibitem{ForastiereMatteiDing2018}
Forastiere, L., Mattei, A., and Ding, P. (2018).
Principal ignorability in mediation analysis: through and beyond sequential
ignorability.
\emph{Biometrika} 105, 979--986.

\bibitem{FrangakisRubin2002}
Frangakis, C. E. and Rubin, D. B. (2002).
Principal stratification in causal inference.
\emph{Biometrics} 58, 21--29.

\bibitem{FrauenMelnychukFeuerriegel2023}
Frauen, D., Melnychuk, V., and Feuerriegel, S. (2023).
Sharp bounds for generalized causal sensitivity analysis.
\emph{Advances in Neural Information Processing Systems} 36.

\bibitem{JiangYangDing2022}
Jiang, Z., Yang, S., and Ding, P. (2022).
Multiply robust estimation of causal effects under principal ignorability.
\emph{Journal of the Royal Statistical Society: Series B} 84, 1423--1445.

\bibitem{LeeDanielsSargent2010}
Lee, K., Daniels, M. J., and Sargent, D. J. (2010).
Causal effects of treatments for informative missing data due to
progression/death.
\emph{Journal of the American Statistical Association} 105, 912--929.

\bibitem{LuJiangDing2024}
Lu, S., Jiang, Z., and Ding, P. (2024).
Principal stratification with continuous post-treatment variables:
nonparametric identification and semiparametric estimation.
\emph{arXiv:2309.12425}.

\bibitem{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{The American Economic Review} 80, 319--323.

\bibitem{MatteiMealli2011}
Mattei, A. and Mealli, F. (2011).
Augmented designs to assess principal strata direct effects.
\emph{Journal of the Royal Statistical Society: Series B} 73, 729--752.

\bibitem{NguyenStuartScharfsteinOgburn2024}
Nguyen, T. Q., Stuart, E. A., Scharfstein, D. O., and Ogburn, E. L. (2024).
Sensitivity analysis for principal ignorability violation in estimating
complier and noncomplier average causal effects.
\emph{arXiv:2303.05032}.

\bibitem{TongKahanHarhayLi2025}
Tong, J., Kahan, B., Harhay, M. O., and Li, F. (2025).
Semiparametric principal stratification analysis beyond monotonicity.
\emph{arXiv:2501.17514}.

\bibitem{VanderWeele2011}
VanderWeele, T. J. (2011).
Principal stratification--uses and limitations.
\emph{International Journal of Biostatistics} 7, Article 28.

\bibitem{WangZhangMealliBornkamp2023}
Wang, C., Zhang, Y., Mealli, F., and Bornkamp, B. (2023).
Sensitivity analyses for the principal ignorability assumption using multiple
imputation.
\emph{Pharmaceutical Statistics} 22, 64--78.

\bibitem{WuAntonelli2024}
Wu, M. and Antonelli, J. (2024).
Partial identification of principal causal effects under violations of
principal ignorability.
\emph{arXiv:2412.06628}.
\end{thebibliography}

\end{document}
