% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_offline\_policy\_joint\_misspec, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_offline\_policy\_joint\_misspec} / \texttt{v1}%
  \\ \large\textit{Sharp joint sensitivity intervals for offline policy value}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\newcounter{stagezeroconjecture}

\begin{abstract}
This note studies the partial-identification problem for the target-policy value
$\theta=V(\pi)=\E_X\sum_{a\in\mathcal A}\pi(a\mid X)\E[Y(a)\mid X]$
from an offline contextual-bandit law of $(X,A,Y)$.  The estimand-defining
functional is the program pair $(B_L(P),B_U(P))$ obtained by optimizing
$V(\pi)$ over full-data laws for $(X,(Y(a))_{a\in\mathcal A},A)$ that match the
full observed reward-cell law of $(A,Y)$ given $X$, obey bounded outcomes,
satisfy a pointwise $f$-divergence ball around the nominal logging kernel
$e_0$, and keep each arm mean within $\eta$ of the nominal regression $m_0$.
The main representation theorem proves that this
program pair equals the lower and upper extrema of the identified set, rather
than defining those extrema by notation.  The field-level kernel is a strict
non-rectangularity obstruction to separable rectangular support-function
formulas for joint causal sensitivity: on an open binary-action class, the
joint endpoint is smaller than the envelope formed by solving a propensity-only
sensitivity problem and then adding an independent outcome-regression error
allowance.  The two calibration faces are the expected ones: the zero-budget
calibrated face collapses to the usual doubly robust point value, while vacuous
general bounded-outcome budgets recover the Manski fill-in interval and the
finite-grid face replaces the support endpoints by the minimum and maximum grid
points when needed.
\end{abstract}

\section{Introduction}
Offline policy evaluation asks what value a target policy would have if deployed
using only data collected under an existing logging policy.  In the ideal
contextual-bandit model the logging propensity is known, the logged action is
as-good-as randomized conditional on $X$, and doubly robust formulas identify
the policy value.  In many applications the recorded propensity and the fitted
reward regression are both nominal objects: unmeasured factors may affect
assignment, and the regression can drift away from the true arm means.  The
causal question is therefore not only how to estimate a point value, but which
policy values remain compatible with the log after both nuisance models are
allowed to be wrong by explicit budgets.

This note gives the population identification object for that question.  The
observable input is the law of $(X,A,Y)$ together with a target policy
$\pi$, a nominal logging kernel $e_0$, a nominal regression $m_0$, a divergence
budget $\rho$, and an outcome-regression budget $\eta$.  The unobserved object
is a full response table $(Y(a))_{a\in\mathcal A}$ and a latent logging kernel
that may depend on that response table.  The key mathematical point is that the
same latent response table must satisfy both restrictions; the propensity tilt
and the outcome-regression perturbation cannot be optimized independently.

The result is useful because it separates a sharp identified interval from
conservative rectangular ambiguity envelopes.  The interval reduces to standard
doubly robust policy value when both budgets are zero and calibrated, and it
reduces to Manski's bounded-outcome fill-in logic when the budgets are vacuous
on the general bounded-outcome face, with the finite-grid support endpoints
used if that restriction is kept.
Away from those faces, the theorem supplies a conditional convex program that
can be used as the population formula before any statistical estimation or
policy-learning layer is added.  The strict-gap theorem is a model-class
no-go result for separable rectangular support functions: if the upper endpoint
is obtained by first solving the propensity-only sensitivity problem and then
adding an independent outcome-regression allowance, the resulting formula is
not uniformly sharp for the joint causal model.  This elevates the contribution
beyond a finite latent-type representation.  The joint model opens a genuinely
non-separable sensitivity regime because the same latent response table must
satisfy both restrictions while matching every factual reward cell.

\paragraph{Motivating conjecture(s).}
\refstepcounter{stagezeroconjecture}\label{conj:sharp-interval}
\paragraph{Conjecture \thestagezeroconjecture: sharp joint-misspecification variational interval (NOT YET PROVED).}
Under Assumptions \ref{ass:bounded}--\ref{ass:finite-support}, whenever $\mathcal Q(P;\rho,\eta)$ is nonempty, the endpoints $L(P;\rho,\eta)$ and $U(P;\rho,\eta)$ equal the integral over $X$ of the conditional optimum of a finite-dimensional convex program. At each $x$, the program ranges over a conditional distribution on response vectors $y_{\mathcal A}\in\mathcal G^{|\mathcal A|}$ and a stochastic logging kernel $e^\star(\cdot\mid x,y_{\mathcal A})$; it imposes every observed factual reward-cell probability,
\[
  \sum_{y_{\mathcal A}:y_a=c}
    H_x(y_{\mathcal A})e^\star(a\mid x,y_{\mathcal A})
  =q_a(c\mid x),
  \qquad a\in\mathcal A,\ c\in\mathcal G,
\]
which are equivalent to matching the full finite conditional law of $(A,Y)$ given $X=x$. It also imposes the pointwise divergence budget in Assumption \ref{ass:f-budget} and the arm-mean band
$|\int y_a\,dH_x(y_{\mathcal A})-m_0(a,x)|\le\eta$. The conditional objective is
$\sum_a\pi(a\mid x)\int y_a\,dH_x(y_{\mathcal A})$ for the upper endpoint and its negative for the lower endpoint.

\refstepcounter{stagezeroconjecture}\label{conj:nonrect}
\paragraph{Conjecture \thestagezeroconjecture: non-rectangular phase transition (NOT YET PROVED).}
Assume \ref{ass:bounded}--\ref{ass:finite-support} and \ref{ass:binary-nondegenerate}. There is an open set of observable conditional laws $P(\cdot\mid X=x)$ on a two-action, three-reward grid $\mathcal A=\{0,1\}$ and $\mathcal G=\{g_L,g_M,g_H\}$ with $\ell\le g_L<g_M<g_H\le u$, and budgets $(\rho,\eta)$ with $\rho>0$, $0<\eta<u-\ell$, and $\mathcal Q(P;\rho,\eta)\ne\varnothing$, such that the sharp upper endpoint in Conjecture \ref{conj:sharp-interval} is strictly below the rectangular diagnostic envelope:
\[
  U(P;\rho,\eta) < U_{\mathrm{rect}}(P;\rho,\eta).
\]
The witness template has positive observed mass in at least two reward cells for each action, target mass on action $1$, and an $m_0(1,x)+\eta$ cap lying strictly between the pure propensity-sensitivity optimum and the rectangular envelope. The strict gap occurs when the propensity tilt that increases the pure sensitivity endpoint would require response-vector mass assignments that violate either the full factual reward-cell constraints or the $\eta$-tube around $m_0$, so the two worst-case mechanisms compete for the same response types. In the theorem below this conjecture is strengthened into a generic no-go theorem for separable rectangular endpoint formulas, rather than being used as an estimator-specific complaint.

Theorem~\ref{thm:nonrect} confirms this conjecture through a stronger
generic-class obstruction: separable rectangular support-function formulas are
conservative on an open set for this joint causal sensitivity target.

\section{Related work and positioning}
The nearest point-identification baseline is doubly robust contextual-bandit
evaluation and learning.  Dudik, Langford, and Li \cite{DudikLangfordLi2011}
introduced the doubly robust policy-value score that this note recovers on the
calibrated zero-budget face.  Wang, Agarwal, and Dudik
\cite{WangAgarwalDudik2017} analyze minimax and adaptive offline policy
evaluation, motivating why outcome-regression errors matter even before
sensitivity analysis is introduced.

The nearest sensitivity-analysis baseline is the marginal-sensitivity and
confounding-robust policy literature.  Tan \cite{Tan2006} is the classical
propensity-score sensitivity ancestor for bounded deviations from a nominal
assignment law.  Kallus and Zhou \cite{KallusZhou2018,KallusZhou2020,KallusZhou2021}
study confounding-robust policy improvement, policy evaluation, and minimax
policy learning under unobserved confounding; their uncertainty sets do not
also impose a sup-norm tube around a nominal arm-mean regression.  Dorn and Guo
\cite{DornGuo2023} and Dorn, Guo, and Kallus \cite{DornGuoKallus2025}
establish sharp sensitivity bounds in treatment-effect settings; the present
result instead targets a fixed contextual-bandit policy value with multiple
actions and a paired outcome-regression budget.  Hess, Frauen, Melnychuk, and
Feuerriegel \cite{HessFrauenMelnychukFeuerriegel2026} study sharp off-policy
learning bounds under unobserved confounding, but without the same nominal
regression tube.  Zhang, Xu, and Tan \cite{ZhangXuTan2025} is the closest
simultaneous-constraint comparator because it combines treatment-probability
and outcome-distribution sensitivity constraints; the second restriction here
is different, since it is an analyst-supplied sup-norm restriction on the
contextual arm means.  Ishikawa and He \cite{IshikawaHe2023} study confounding
robust inference for contextual bandits using conditional moment constraints
and $f$-divergence ideas, but not the paired nominal arm-mean tube with full
factual reward-cell matching.  Jin, Xu, Zheng, and Zhou
\cite{JinXuZhengZhou2025} study robust policy learning under unobserved
confounding; their welfare criteria are natural downstream consumers of the
sharp fixed-policy interval derived here.

Si, Zhang, Zhou, and Blanchet \cite{SiZhangZhouBlanchet2020} and Kallus, Mao,
Wang, and Zhou \cite{KallusMaoWangZhou2022} are relevant distributionally robust
offline-policy comparators because they combine offline policy evaluation with
ambiguity sets and doubly robust ideas.  They also illustrate a standard
separable support-function workflow: specify an uncertainty source, optimize
the value over that source, and report the resulting worst-case value.  The
present paper abstracts from those examples to a causal identified-set question
and proves that the corresponding separable endpoint formula fails for the
joint propensity-plus-regression sensitivity model.  Theorem~\ref{thm:nonrect}
therefore targets the mathematical workflow class itself: optimize the
propensity/confounding sensitivity source and then add an independent
regression-error allowance.  The open-set gap shows that this class is not a
valid sharp formula for the model, because after full reward-cell matching the
two worst-case mechanisms must be carried by the same latent response table.

The limiting partial-identification faces connect to classical bounded-outcome
and finite latent-response methods.  Manski \cite{Manski1990} supplies the
fill-in argument recovered when both misspecification restrictions are vacuous,
and Manski and Pepper \cite{ManskiPepper2000} show how additional shape
restrictions can tighten bounded-outcome intervals.  Balke and Pearl
\cite{BalkePearl1997} give the canonical finite latent-type linear-programming
template for sharp bounds, although their binary-IV target differs from the
offline policy value studied here.  The current theorem differs from these
known result classes by imposing two simultaneous restrictions on the same
latent response table while matching the full factual reward-cell law.

\section{Formal setup}
Let $\mathcal A$ be a finite action set and let $P$ denote the observable input:
the law of $(X,A,Y)$, the target policy $\pi(a\mid x)$, the nominal logging
kernel $e_0(a\mid x)$, and the nominal regression $m_0(a,x)$.  The outcome is
bounded in the known interval $[\ell,u]$ with $\ell<u$.  In the finite-grid
version locked by the proposal, there is a finite reward grid
$\mathcal G=\{g_1,\ldots,g_M\}\subset[\ell,u]$ such that the observed reward and
every admissible potential reward take values in $\mathcal G$.  Write
$g_{\min}=\min\mathcal G$ and $g_{\max}=\max\mathcal G$.  The grid endpoints
need not equal $\ell$ and $u$ unless this is stated explicitly; this distinction
matters only for the vacuous finite-grid face in Proposition~\ref{prop:manski}.
For $P_X$-almost every $x$, define the observed conditional reward-cell law,
action mass, and factual first moment by
\[
  q_a(c\mid x)=P(A=a,Y=c\mid X=x),\qquad
  p_a(x)=\sum_{c\in\mathcal G}q_a(c\mid x),\qquad
  r_a(x)=\sum_{c\in\mathcal G}c\,q_a(c\mid x).
\]
Equivalently,
\[
  p_a(x)=P(A=a\mid X=x), \qquad
  r_a(x)=\E_P[Y\one\{A=a\}\mid X=x].
\]
If $p_a(x)>0$, then $\bar y_a(x)=r_a(x)/p_a(x)$ is the observed conditional
mean in the factual action cell; all endpoint formulas below are written using
$r_a(x)$ so that zero-cell means need not be defined.

A compatible full-data law $Q$ augments the observed law by the response table
$Y_{\mathcal A}=(Y(a))_{a\in\mathcal A}$ and by a latent logging kernel
\[
  e_Q^\star(a\mid x,y_{\mathcal A})
  =Q(A=a\mid X=x,Y_{\mathcal A}=y_{\mathcal A}).
\]
The conditional law of $Y_{\mathcal A}$ given $X=x$ is denoted by $H_x^Q$.
Observational compatibility means that the marginal law of $(X,A,Y(A))$ under
$Q$ equals the observed law $P$.  On the finite reward grid this is the full
reward-cell matching condition
\[
  \int \one\{y_a=c\}e_Q^\star(a\mid x,y_{\mathcal A})\,
      dH_x^Q(y_{\mathcal A})
  =q_a(c\mid x),
  \qquad a\in\mathcal A,\ c\in\mathcal G,
\]
for almost every $x$.  Summing this display over $c$ gives the action mass
$p_a(x)$, and multiplying by $c$ before summing over $c$ gives the factual
moment $r_a(x)$.

The unobserved parameter is the scalar policy value
\[
  \theta=V_Q(\pi)
  =\E_Q\!\left[\sum_{a\in\mathcal A}\pi(a\mid X)Y(a)\right]
  =\E_{P_X}\sum_{a\in\mathcal A}\pi(a\mid X)\mu_a^Q(X),
  \qquad
  \mu_a^Q(x)=\int y_a\,dH_x^Q(y_{\mathcal A}).
\]
Let $\mathcal Q(P;\rho,\eta)$ be the set of compatible full-data laws satisfying
the assumptions in Section~\ref{sec-assumptions}.  The identified set is
\[
  \Theta_I(P;\rho,\eta)
  =\{V_Q(\pi):Q\in\mathcal Q(P;\rho,\eta)\}.
\]
If $\mathcal Q(P;\rho,\eta)=\varnothing$ then $\Theta_I(P;\rho,\eta)=\varnothing$;
the endpoint theorems are stated on nonempty faces.  Otherwise define the
identified-set extrema semantically by
\[
  \underline{\theta}_I(P;\rho,\eta)=\inf \Theta_I(P;\rho,\eta),\qquad
  \overline{\theta}_I(P;\rho,\eta)=\sup \Theta_I(P;\rho,\eta).
\]
Section~7 defines the computable program endpoints
$B_L(P;\rho,\eta)$ and $B_U(P;\rho,\eta)$ separately; the main theorem proves
$\underline{\theta}_I=B_L$ and $\overline{\theta}_I=B_U$.
The support convention is absolute continuity with respect to the nominal
kernel: if $e_0(a\mid x)=0$, then every admissible latent kernel assigns zero
probability to action $a$ at $(x,y_{\mathcal A})$.  Hence an observed cell with
$p_a(x)>0$ but $e_0(a\mid x)=0$ makes the compatible class empty.

\paragraph{Locked parameters.}
\begin{quote}\small
\begin{verbatim}
(qid, specialization) =
  (pid_offline_policy_joint_misspec, v1)
anchor cluster = PartialID
observable distribution P =
  law of (X,A,Y) with finite action set Acal, bounded outcome Y in [lo,hi],
  nominal logging propensity e0(a|x), nominal outcome regression m0(a,x),
  and target policy pi(a|x)
parameter theta =
  V(pi) = E_X sum_a pi(a|X) E[Y(a)|X]
identifying restrictions =
  consistency Y=Y(A); bounded potential outcomes lo <= Y(a) <= hi;
  overlap e0(a|x)>0 on pi(a|x)>0; f-divergence support convention
  e_star(.|x,y_vec) << e0(.|x), with zero e0 cells carrying zero latent
  logging mass and with f(t)>=0 uniquely minimized at t=1; under any
  compatible full-data law Q, the latent logging kernel
  e_star^Q(a|x,y_vec)=Q(A=a|X=x,Y_vec=y_vec) satisfies
  D_f(e_star(.|x,y_vec) || e0(.|x)) <= rho pointwise; and
  |E[Y(a)|X=x]-m0(a,x)| <= eta for every action a
bounding functional =
  lower/upper sharp values obtained by optimizing V(pi) over all full-data
  laws of (X,(Y(a))_a,A) satisfying the observable law P and the restrictions
  above; rho=0, eta=0 is the doubly robust point-ID corner, and vacuous
  rho/eta gives Manski fill-in bounds for unobserved action outcomes
\end{verbatim}
\end{quote}

\section{Assumptions}\label{sec-assumptions}
\begin{assumption}[Finite actions, standard measurability, and bounded outcomes]\label{ass:bounded}
The action set $\mathcal A$ is finite.  The covariate space is a standard
Borel space, regular conditional laws given $X=x$ exist, and the kernels
$q_a(c\mid x)$, $e_0(a\mid x)$, $\pi(a\mid x)$, and $m_0(a,x)$ are measurable.
There are known constants $\ell<u$ such that $\ell\le Y(a)\le u$ almost surely
for every action $a$ under every compatible full-data law.
\end{assumption}

\begin{assumption}[Consistency and observational compatibility]\label{ass:compat}
The observed outcome equals the potential outcome under the logged action:
$Y=Y(A)$.  Every admissible full-data law $Q$ has observed marginal law $P$ for
$(X,A,Y(A))$.
\end{assumption}

\begin{assumption}[Nominal overlap and zero-cell support]\label{ass:overlap}
For $P_X$-almost every $x$, $e_0(\cdot\mid x)$ and $\pi(\cdot\mid x)$ are
probability mass functions on $\mathcal A$, and $e_0(a\mid x)>0$ whenever
$\pi(a\mid x)>0$.  If $e_0(a\mid x)=0$, then admissible latent kernels satisfy
$e_Q^\star(a\mid x,y_{\mathcal A})=0$ for almost every response vector.
\end{assumption}

\begin{assumption}[Pointwise finite-valued $f$-divergence logging budget]\label{ass:f-budget}
The generator $f:[0,\infty)\to[0,\infty)$ is convex, lower semicontinuous,
satisfies $f(1)=0$, and has unique zero at $1$.  For probability mass functions
$q$ and $e_0(\cdot\mid x)$ on the finite action set, define
\[
  D_f(q\Vert e_0(\cdot\mid x))
  =\sum_{a:e_0(a\mid x)>0} e_0(a\mid x)
      f\!\left(\frac{q(a)}{e_0(a\mid x)}\right),
\]
with the support convention in Assumption~\ref{ass:overlap}.  For every
admissible full-data law $Q$ and almost every $(x,y_{\mathcal A})$,
\[
  D_f(e_Q^\star(\cdot\mid x,y_{\mathcal A})\Vert e_0(\cdot\mid x))\le \rho.
\]
When $\rho=0$, the unique-zero condition forces
$e_Q^\star(\cdot\mid x,y_{\mathcal A})=e_0(\cdot\mid x)$ almost surely.
\end{assumption}

\begin{assumption}[Sup-norm outcome-regression budget]\label{ass:outcome-gap}
For every admissible full-data law $Q$, every action $a$, and $P_X$-almost
every $x$,
\[
  |\mu_a^Q(x)-m_0(a,x)|\le \eta.
\]
\end{assumption}

\begin{assumption}[Finite observed reward grid]\label{ass:finite-support}
There is a fixed finite grid $\mathcal G=\{g_1,\ldots,g_M\}\subset[\ell,u]$
such that $P(Y\in\mathcal G\mid X,A)=1$, and every admissible full-data law has
$Y(a)\in\mathcal G$ almost surely for every action $a$.  The theorem is a
finite-grid statement; no limiting claim for general bounded outcomes is part
of this specialization.
\end{assumption}

\begin{assumption}[Calibrated zero-budget face]\label{ass:zero-calibrated}
For $P_X$-almost every $x$ and every action $a$,
$p_a(x)=e_0(a\mid x)$ and $r_a(x)=e_0(a\mid x)m_0(a,x)$.  The class
$\mathcal Q(P;0,0)$ is nonempty.
\end{assumption}

\begin{assumption}[Vacuous-budget face]\label{ass:vacuous}
The phrase ``vacuous $\rho$ and $\eta$'' means that the logging budget allows
every stochastic kernel on the finite action set and the outcome-regression
budget allows every arm mean in $[\ell,u]$.
\end{assumption}

\begin{assumption}[Binary non-degenerate phase-transition specialization]\label{ass:binary-nondegenerate}
For the non-rectangularity theorem, $\mathcal A=\{0,1\}$ on a non-null
covariate stratum and the reward grid contains three ordered points
$g_L<g_M<g_H$.  The nominal logging probabilities
$e_0(0\mid x)$ and $e_0(1\mid x)$ are both strictly positive, the target policy
puts positive weight on action $1$, and each action has positive observed mass
in at least two reward cells on the relevant stratum.
\end{assumption}

\section{Estimand-defining functional}
For a fixed $x$, write
\[
  \mathcal C_\rho(x)
  =\{q\in\Delta(\mathcal A):q(a)=0\text{ if }e_0(a\mid x)=0,
       D_f(q\Vert e_0(\cdot\mid x))\le \rho\}.
\]
Enumerate the finite response-vector grid
$\mathcal G^{|\mathcal A|}=\{y^1,\ldots,y^J\}$, where
$y^j=(y^j_a)_{a\in\mathcal A}$.  Define the conditional feasible set
$\mathcal K_x(P;\rho,\eta)$ to consist of nonnegative arrays
$z_{ja}$, $j=1,\ldots,J$, $a\in\mathcal A$, with
$h_j=\sum_b z_{jb}$, satisfying the full factual reward-cell constraints
\[
  \sum_{j:y^j_a=c} z_{ja}=q_a(c\mid x),
  \qquad a\in\mathcal A,\ c\in\mathcal G,
\]
the support convention $z_{ja}=0$ whenever $e_0(a\mid x)=0$, the arm-mean bands
\[
  \sum_j h_j y^j_a \in [m_0(a,x)-\eta,\ m_0(a,x)+\eta]\cap[\ell,u],
  \qquad a\in\mathcal A,
\]
and, for every $j$ with $h_j>0$,
\[
  \left(\frac{z_{ja}}{h_j}\right)_{a\in\mathcal A}\in\mathcal C_\rho(x).
\]
If $h_j=0$, then $z_{ja}=0$ for all $a$ and the divergence constraint is void.
The cell constraints imply $\sum_{j,a}z_{ja}=1$ and
$\sum_j z_{ja}=p_a(x)$.  They also imply
$\sum_j y^j_a z_{ja}=r_a(x)$, but the stronger cell-by-cell equalities are the
locked functional.  This is a finite-dimensional convex representation: the
cell constraints and mean bands are linear in $z$, and the divergence constraint
is the perspective inequality
\[
  h_j\!\left[
  D_f\!\left(\left(\frac{z_{ja}}{h_j}\right)_a
          \middle\Vert e_0(\cdot\mid x)\right)-\rho\right]\le 0,
\]
with the usual closed extension at $h_j=0$.

For $z\in\mathcal K_x(P;\rho,\eta)$ define
\[
  v_x(z)=\sum_{a\in\mathcal A}\pi(a\mid x)
       \sum_{j=1}^J h_j y^j_a.
\]
The conditional program values are
\[
  \ell_x(P;\rho,\eta)=\inf_{z\in\mathcal K_x(P;\rho,\eta)}v_x(z),
  \qquad
  u_x(P;\rho,\eta)=\sup_{z\in\mathcal K_x(P;\rho,\eta)}v_x(z),
\]
with the convention that the endpoints are undefined if
$\mathcal K_x(P;\rho,\eta)$ is empty on a set of positive $P_X$ mass.  The
population program functional is
\[
  B_L(P;\rho,\eta)=\E_{P_X}[\ell_X(P;\rho,\eta)],\qquad
  B_U(P;\rho,\eta)=\E_{P_X}[u_X(P;\rho,\eta)].
\]
These are only program values at this point in the note.  Theorem~\ref{thm:sharp}
proves that they are equal to the identified-set extrema
$\underline{\theta}_I$ and $\overline{\theta}_I$, at which point they are the sharp
bounding functionals customarily denoted by $\theta_L$ and $\theta_U$.  The
diagnostic rectangular upper envelope used only for comparison is
\[
  U_{\mathrm{rect}}(P;\rho,\eta)
  =\min\left\{
       U_{\mathrm{prop}}(P;\rho)
       +\eta\,\E_{P_X}\sum_a\pi(a\mid X),\
       u\,\E_{P_X}\sum_a\pi(a\mid X)
     \right\},
\]
where $U_{\mathrm{prop}}(P;\rho)$ is the upper endpoint of the same program with
the outcome-regression budget removed.  A rectangular post-processing workflow
for the present problem is any workflow that reports this envelope after first
solving the one-source propensity or confounding sensitivity problem.  This is
the separable product-ambiguity support function for the two sensitivity
sources: one source is optimized to a worst-case value, and the other is added
as an independent arm-mean allowance.  The envelope is always an outer
relaxation because it adds the regression-error allowance after solving the
propensity-sensitivity problem, without requiring a single latent response table
to realize both worst cases.

\section{Target causal estimand}
The causal target is the scalar value of the target policy under the full-data
law:
\[
  \theta=V_Q(\pi)=\E_Q\left[\sum_{a\in\mathcal A}\pi(a\mid X)Y(a)\right].
\]
This is not defined as an observable functional of $P$.  Different compatible
full-data laws can agree on the same observed law and nominal nuisance inputs
while assigning different values to the unobserved response table.  The
identified set is therefore
\[
  \Theta_I(P;\rho,\eta)
  =\{V_Q(\pi):Q\in\mathcal Q(P;\rho,\eta)\},
\]
and the theorem-level conclusion is the sharp containment, in fact equality,
\[
  \Theta_I(P;\rho,\eta)=[B_L(P;\rho,\eta),B_U(P;\rho,\eta)]
\]
on nonempty faces, equivalently
$\underline{\theta}_I(P;\rho,\eta)=B_L(P;\rho,\eta)$ and
$\overline{\theta}_I(P;\rho,\eta)=B_U(P;\rho,\eta)$.  Point identification occurs
only when these two endpoints coincide.

\section{Main theorems}
\begin{theorem}[Sharp joint variational interval]\label{thm:sharp}
Under Assumptions~\ref{ass:bounded}--\ref{ass:finite-support}, if
$\mathcal Q(P;\rho,\eta)$ is nonempty, then
\[
  \underline{\theta}_I(P;\rho,\eta)=B_L(P;\rho,\eta),\qquad
  \overline{\theta}_I(P;\rho,\eta)=B_U(P;\rho,\eta),
\]
and consequently
\[
  \Theta_I(P;\rho,\eta)=[B_L(P;\rho,\eta),B_U(P;\rho,\eta)].
\]
Equivalently, the lower and upper identified-set extrema are obtained by
integrating the conditional finite-dimensional convex programs in Section~7.
Therefore Conjecture~\ref{conj:sharp-interval} is confirmed, with the endpoint
notation made explicit and with convexity understood through the closed
measure-variable perspective parametrization $z_{ja}$.
\end{theorem}

The new ingredient is the shared latent-response compatibility program.  Manski
\cite{Manski1990} fixes only observed factual contributions and fills the
unobserved parts of the response table at endpoints, while Balke and Pearl
\cite{BalkePearl1997} optimize over finite latent types for binary-IV bounds.
Here the same conditional response types must also carry a pointwise
$f$-divergence-constrained logging kernel and arm-mean bands around $m_0$.
As a representation theorem, Theorem~\ref{thm:sharp} is best viewed as a
Balke--Pearl/Manski finite latent-type optimization with additional convex
feasibility constraints.  The field-level contribution is the
non-rectangularity theorem below, which shows that this paired sensitivity model
does not reduce to a product or Minkowski sum of its one-source faces.

\begin{theorem}[Non-rectangular upper endpoint]\label{thm:nonrect}
Under Assumptions~\ref{ass:bounded}--\ref{ass:finite-support} and the binary
specialization in Assumption~\ref{ass:binary-nondegenerate}, there is an open
set of conditional
observable inputs and budgets with $\rho>0$,
$0<\eta<u-\ell$, and $\mathcal Q(P;\rho,\eta)\ne\varnothing$ such that
\[
  B_U(P;\rho,\eta)<U_{\mathrm{rect}}(P;\rho,\eta).
\]
Thus Conjecture~\ref{conj:nonrect} is confirmed in a stronger generic-class
form: the separable rectangular support-function formula
$U_{\mathrm{rect}}$ is conservative on this open class and therefore cannot be
a sharp identified-set formula for the joint propensity-plus-regression
sensitivity model.
\end{theorem}

This theorem matters because it rules out a whole separable formula class in
this setting: solve a sharp propensity-sensitivity problem and then add a
separate regression-error band.  That shortcut is only an outer envelope for
the present causal model.  When the reward types that raise the propensity-only
endpoint would also move the arm mean outside the $\eta$-tube around $m_0$, the
joint endpoint is strictly lower.

\begin{proposition}[Calibrated zero-budget point face]\label{prop:dr-corner}
Under Assumptions~\ref{ass:bounded}--\ref{ass:outcome-gap} and
\ref{ass:zero-calibrated}, if $\rho=0$ and $\eta=0$, then
\[
  \Theta_I(P;0,0)
  =\left\{\E_{P_X}\sum_{a\in\mathcal A}\pi(a\mid X)m_0(a,X)\right\}.
\]
The same value is the population doubly robust score
\[
  \E_P\left[
    \sum_a\pi(a\mid X)m_0(a,X)
    +\frac{\pi(A\mid X)}{e_0(A\mid X)}\{Y-m_0(A,X)\}
  \right].
\]
The ratio is evaluated on positive-$e_0$ cells; under
Assumptions~\ref{ass:overlap} and \ref{ass:zero-calibrated}, any remaining
zero-$e_0$ cell has both zero target mass and zero observed probability.
\end{proposition}

\begin{proposition}[Vacuous-budget Manski fill-in faces]\label{prop:manski}
Under Assumptions~\ref{ass:bounded}, \ref{ass:compat}, and \ref{ass:vacuous},
without imposing the finite-grid restriction in Assumption~\ref{ass:finite-support},
the sharp general bounded-outcome identified interval is
\[
  \left[
  \E_{P_X}\sum_a\pi(a\mid X)\{r_a(X)+(1-p_a(X))\ell\},
  \E_{P_X}\sum_a\pi(a\mid X)\{r_a(X)+(1-p_a(X))u\}
  \right].
\]
If Assumption~\ref{ass:finite-support} is also imposed and the grid endpoints
are arbitrary, the sharp finite-grid vacuous interval is instead
\[
  \left[
  \E_{P_X}\sum_a\pi(a\mid X)\{r_a(X)+(1-p_a(X))g_{\min}\},
  \E_{P_X}\sum_a\pi(a\mid X)\{r_a(X)+(1-p_a(X))g_{\max}\}
  \right].
\]
The two displays coincide when the finite-grid specialization includes
$\ell,u\in\mathcal G$ as its minimum and maximum grid points.
\end{proposition}

\section{Interpretation}
Theorem~\ref{thm:sharp} says that the right population object is a joint
conditional program.  The factual law pins down, for each action and reward
cell, the conditional probability $q_a(c\mid x)$; the masses $p_a(x)$ and
moments $r_a(x)$ are only summaries of these stronger constraints.  The
unobserved response-table distribution may still vary, but each candidate table
must be paired with a latent logging kernel that remains inside the
$f$-divergence ball and whose resulting arm means remain inside the
$\eta$-tube around $m_0$.

The interval collapses to point identification when the conditional feasible set
forces the target-weighted arm mean to be unique.  The most important such face
is Proposition~\ref{prop:dr-corner}: $\rho=0$ makes the latent logging kernel
equal to $e_0$ for every response type, and $\eta=0$ fixes each arm mean at
$m_0$.  If the observed law is calibrated to those two equalities, the residual
part of the doubly robust score integrates to zero and the policy value is
unique.

The interval widens to the natural Manski no-restriction bound when both
misspecification budgets are vacuous.  Then the only fixed contribution to
$\mu_a(x)$ is the factual part $r_a(x)$ among units actually assigned action
$a$; the unobserved contribution among the remaining mass $1-p_a(x)$ can be
filled with $\ell$ or $u$ in the general bounded-outcome face.  If the
finite-grid restriction is kept and $\ell,u$ are not grid points, the same
logic fills with $g_{\min}$ or $g_{\max}$ instead.  Between these faces, the
$f$-divergence restriction tightens the bound by limiting how much high-reward
response types can be hidden behind low logging probabilities, while the
outcome-regression budget tightens the bound by capping the marginal arm means
directly.

The non-rectangularity theorem explains why a rectangular post-processing
workflow should not report the two restrictions as independent robustness
adjustments for this joint causal target.  The same latent mass that would raise
the propensity-only endpoint also raises the arm mean, so the
outcome-regression tube can bind exactly where the propensity tilt is most
valuable.

\section{Step-by-step proof}
\begin{lemma}[Conditional compatibility equals the finite program]\label{lem:conditional-program}
Fix $x$ outside a $P_X$-null set and suppose Assumptions~\ref{ass:bounded}--
\ref{ass:finite-support} hold.  A conditional full-data law
$H_x(dy_{\mathcal A})e^\star(da\mid x,y_{\mathcal A})$ is compatible with the
observed conditional law and the two budgets if and only if its finite-grid
weights $z_{ja}=H_x(\{y^j\})e^\star(a\mid x,y^j)$ lie in
$\mathcal K_x(P;\rho,\eta)$.
\end{lemma}

\begin{proof}
Given a conditional full-data law, set $h_j=H_x(\{y^j\})$ and
$z_{ja}=h_j e^\star(a\mid x,y^j)$.  Nonnegativity and
$\sum_{j,a}z_{ja}=1$ follow because $H_x$ is a probability law and
$e^\star(\cdot\mid x,y^j)$ is a stochastic kernel.  Observational compatibility
and consistency in Assumption~\ref{ass:compat} give, for every action $a$ and
reward cell $c$,
\[
  \sum_{j:y^j_a=c}z_{ja}
  =\sum_{j:y^j_a=c}H_x(\{y^j\})e^\star(a\mid x,y^j)
  =q_a(c\mid x).
\]
Assumption~\ref{ass:overlap} gives the zero-$e_0$ support convention.
Assumption~\ref{ass:f-budget} gives
$(z_{ja}/h_j)_a\in\mathcal C_\rho(x)$ whenever $h_j>0$, and
Assumption~\ref{ass:outcome-gap} gives the arm-mean bands because
$\mu_a(x)=\sum_j h_jy^j_a$.

Conversely, given $z\in\mathcal K_x(P;\rho,\eta)$, set
$H_x(\{y^j\})=h_j=\sum_b z_{jb}$.  If $h_j>0$, set
$e^\star(a\mid x,y^j)=z_{ja}/h_j$; if $h_j=0$, choose any kernel in
$\mathcal C_\rho(x)$, which exists because $e_0(\cdot\mid x)\in\mathcal C_\rho(x)$.
The constraints defining $\mathcal K_x(P;\rho,\eta)$ then give the conditional
observed reward-cell probabilities, divergence budget, support convention,
bounded outcomes, and arm-mean bands.  Summing the reward-cell equalities gives
the observed action probabilities and factual moments.  This proves the
equivalence.
\end{proof}

\begin{lemma}[Pasting conditional laws]\label{lem:pasting}
Under Assumptions~\ref{ass:bounded}--\ref{ass:finite-support}, measurable
conditional selections
$z_x\in\mathcal K_x(P;\rho,\eta)$ paste together to an admissible
full-data law $Q$ whose policy value is
$\E_{P_X}v_X(z_X)$.
\end{lemma}

\begin{proof}
For each $x$, Lemma~\ref{lem:conditional-program} turns $z_x$ into a
conditional response-table law and latent logging kernel.  Define the full law
by
\[
  Q(dx,dy_{\mathcal A},da)
  =P_X(dx)H_x(dy_{\mathcal A})e^\star(da\mid x,y_{\mathcal A}),
\]
and set the observed outcome to $Y=Y(A)$.  The two compatibility equalities in
Lemma~\ref{lem:conditional-program} imply that every conditional cell
probability $P(A=a,Y(A)=c\mid X=x)$ matches $q_a(c\mid x)$, so the marginal law
of $(X,A,Y)$ is $P$.  The support, divergence, outcome-band, and boundedness
restrictions hold conditionally and therefore hold under $Q$.  Finally,
\[
  V_Q(\pi)=\E_{P_X}\sum_a\pi(a\mid X)\sum_j h_j(X)y^j_a
          =\E_{P_X}v_X(z_X),
\]
which is the desired value identity.
\end{proof}

\begin{lemma}[Convex posterior-mixture closure]\label{lem:mixture-closure}
Under Assumptions~\ref{ass:bounded}--\ref{ass:finite-support}, if
$Q^0,Q^1\in\mathcal Q(P;\rho,\eta)$ and $t\in[0,1]$, then there is an
admissible law $Q^t\in\mathcal Q(P;\rho,\eta)$ with
\[
  V_{Q^t}(\pi)=tV_{Q^1}(\pi)+(1-t)V_{Q^0}(\pi).
\]
\end{lemma}

\begin{proof}
The common grid is already $\mathcal G^{|\mathcal A|}$.  Let $z^k_{ja}$ be the
conditional program array associated with $Q^k$, $k=0,1$, and set
\[
  z^t_{ja}=tz^1_{ja}+(1-t)z^0_{ja},\qquad
  h_j^t=\sum_a z^t_{ja}.
\]
The reward-cell constraints are affine, so $z^t$ matches the same
$q_a(c\mid x)$ as $P$.  The arm means also mix linearly, hence remain inside
the convex intervals
$[m_0(a,x)-\eta,m_0(a,x)+\eta]$.

It remains to check the response-type logging constraints.  If $h_j^t=0$, the
closed perspective convention makes the constraint void.  If $h_j^t>0$, write
\[
  q_j^t(a)=\frac{z^t_{ja}}{h_j^t}
  =\alpha_j q_j^1(a)+(1-\alpha_j)q_j^0(a),
  \qquad
  \alpha_j=\frac{t h_j^1}{t h_j^1+(1-t)h_j^0},
\]
with the obvious convention when one denominator term is zero.  Each
$q_j^k$ lies in $\mathcal C_\rho(x)$, and $\mathcal C_\rho(x)$ is convex because
the finite-action $f$-divergence is convex in its first argument and the support
restriction is linear.  Thus $q_j^t\in\mathcal C_\rho(x)$.  Lemma~\ref{lem:pasting}
turns the measurable family $z^t_X$ into a full-data law $Q^t$, and the
objective identity follows from the linearity of $v_x$.
\end{proof}

\begin{lemma}[Compact measurable conditional programs]\label{lem:measurable-program}
Under Assumptions~\ref{ass:bounded}--\ref{ass:finite-support}, for almost every
$x$ such that $\mathcal K_x(P;\rho,\eta)$ is nonempty, the set
$\mathcal K_x(P;\rho,\eta)$ is compact and convex, the conditional values
$\ell_x(P;\rho,\eta)$ and $u_x(P;\rho,\eta)$ are measurable in $x$, and there
exist measurable minimizer and maximizer selections.
\end{lemma}

\begin{proof}
The variables $z_{ja}$ live in a finite-dimensional simplex because
$\mathcal A$ and $\mathcal G^{|\mathcal A|}$ are finite.  The reward-cell
constraints, support constraints, and mean bands are closed affine constraints.
For each response type $j$, the divergence condition is the closed perspective
extension of a convex lower-semicontinuous function, so the feasible set is
closed; it is therefore compact.  Convexity follows from the same affine
constraints and from convexity of the perspective divergence sublevel set.  The
data entering the constraints, namely $q_a(c\mid x)$, $e_0(a\mid x)$,
$m_0(a,x)$, and $\pi(a\mid x)$, are measurable kernels or functions by the setup
and Assumption~\ref{ass:bounded}.  The finite-dimensional measurable maximum
theorem then gives measurable value functions and measurable selections of the
argmin and argmax correspondences on the nonempty face.
\end{proof}

\begin{lemma}[Finite strict-gap stability]\label{lem:strict-gap-stability}
Fix a finite binary conditional program with reward grid contained in $[0,1]$,
target policy $\pi(1)=1$, and $e_0(0),e_0(1)>0$.  Suppose that at a parameter
point $(q,e_0,m_0,\rho,\eta)$ with $\rho>0$ and $\eta>0$: there is a jointly
feasible array with strict slack in the divergence inequalities and in the
outcome-regression bands; there is a propensity-only feasible array matching
the same reward-cell probabilities $q_a(c)$ with strict divergence slack and
value $w$; and for some
$\delta>0$,
\[
  w+\eta \le 1-\delta,\qquad
  w+\eta \ge m_0(1)+\eta+2\delta .
\]
Then the compatible class remains nonempty and the strict inequality
$B_U(P;\rho,\eta)<U_{\mathrm{rect}}(P;\rho,\eta)$ persists on a sufficiently
small open neighborhood of that parameter point.
\end{lemma}

\begin{proof}
The finite feasible sets are compact subsets of a Euclidean simplex cut out by
linear equalities, closed perspective divergence inequalities, and closed
mean-band inequalities.  The displayed strict feasible arrays give lower
hemicontinuity and nonemptiness under small perturbations of the right-hand
sides and budgets; the closed graph of the constraints gives upper
hemicontinuity.  Berge's maximum theorem for compact-valued finite-dimensional
correspondences then gives continuity of the joint value $B_U$ and of the
propensity-only value $U_{\mathrm{prop}}$ at the strict point.  The upper bound
$B_U(P;\rho,\eta)\le m_0(1)+\eta$ is continuous in $(m_0(1),\eta)$, while the
rectangular envelope is the minimum of continuous functions near the point
because $w+\eta\le1-\delta$ keeps the outcome-support cap inactive.  The margin
$2\delta$ therefore shrinks to a positive margin on a small enough
neighborhood, and the strict gap persists.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:sharp}]
First take any admissible $Q\in\mathcal Q(P;\rho,\eta)$.  By
Lemma~\ref{lem:conditional-program}, its conditional weights
$z_X^Q$ lie in $\mathcal K_X(P;\rho,\eta)$ almost surely.  Therefore
\[
  \ell_X(P;\rho,\eta)\le v_X(z_X^Q)\le u_X(P;\rho,\eta)
  \quad\text{almost surely}.
\]
Integrating this conditional sandwich gives
\[
  B_L(P;\rho,\eta)\le V_Q(\pi)\le B_U(P;\rho,\eta).
\]
Thus $\Theta_I(P;\rho,\eta)\subseteq[B_L,B_U]$, and consequently
$\underline{\theta}_I\ge B_L$ and $\overline{\theta}_I\le B_U$.

For the reverse inclusion, Lemma~\ref{lem:measurable-program} gives measurable
minimizer and maximizer selections of the compact correspondence
$\mathcal K_x(P;\rho,\eta)$.  Lemma~\ref{lem:pasting} pastes these selections
into full-data laws $Q^L,Q^U\in\mathcal Q(P;\rho,\eta)$ with
\[
  V_{Q^L}(\pi)=B_L(P;\rho,\eta),\qquad
  V_{Q^U}(\pi)=B_U(P;\rho,\eta).
\]
Therefore $\underline{\theta}_I\le B_L$ and $\overline{\theta}_I\ge B_U$, so the
identified-set extrema equal the program endpoints.  Finally,
Lemma~\ref{lem:mixture-closure} applies to $Q^L$ and $Q^U$: every convex
combination of their policy values is realized by a posterior-mixture
full-data law that preserves the same observed law $P$, the same support
restriction, the same $f$-divergence budget, and the same mean bands.  Hence
the identified set is the full interval $[B_L,B_U]$.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:nonrect}]
It is enough to give one strict binary construction and then apply
Lemma~\ref{lem:strict-gap-stability}.  Let $X$ be degenerate,
$\mathcal A=\{0,1\}$, $\ell=0$, $u=1$, and
$\mathcal G=\{0,1/2,1\}$.  Set
$e_0(1)=e_0(0)=1/2$ and let the target policy put all mass on action $1$.
Fix a small $\gamma\in(0,1/2)$ and choose the observed reward-cell law
\[
  q_1(1)=q_1(0)=q_0(1)=q_0(0)=\frac{1-\gamma}{4},
  \qquad q_1(1/2)=q_0(1/2)=\frac{\gamma}{2}.
\]
Thus each action has positive observed mass in all three reward cells.  Set
$m_0(1)=m_0(0)=1/2$ and choose $0<\eta<1/4$.  The independent response law with
$Y(1)$ and $Y(0)$ each having marginal mass $(1-\gamma)/2$ at $0$, mass
$\gamma$ at $1/2$, and mass $(1-\gamma)/2$ at $1$, and with
$e^\star=e_0$ matches these six observed cells, has
$\mu_1=\mu_0=1/2$, and therefore is strictly inside the outcome bands and has
zero divergence.  Hence the joint class is nonempty with strict slack whenever
$\rho>0$.

Because $f$ is finite-valued and convex, it is continuous near $1$.  Choose
$\varepsilon>0$ small enough that
\[
  0<\varepsilon<\min\{1/4,\ 1/2-\eta\}
\]
and that $(1-\gamma)\varepsilon+\eta<1/2$, and that the logging probabilities
below have divergence strictly below $\rho$.  Construct a propensity-only
feasible law on the four endpoint response types and the middle type
$(1/2,1/2)$.  Let the middle type have mass $\gamma$ and action-one logging
probability $1/2$.  On the endpoint types, let
\[
  h_{11}=(1-\gamma)\alpha,\quad
  h_{10}=(1-\gamma)(1/2+\varepsilon-\alpha),\quad
  h_{01}=(1-\gamma)\beta,\quad
  h_{00}=(1-\gamma)(1/2-\varepsilon-\beta),
\]
where the first subscript is $Y(1)$ and the second is $Y(0)$.  Choose $\beta>0$
small enough that $\beta<1/2-\varepsilon$ and, after defining
\[
  q_H=\frac{1/4}{1/2+\varepsilon},\qquad
  q_L=\frac{1/4}{1/2-\varepsilon},\qquad
  \alpha=\frac{1/4-\beta(1-q_L)}{1-q_H},
\]
we have $0<\alpha<1/2+\varepsilon$.  Such a $\beta$ exists because the value at
$\beta=0$ is strictly between $0$ and $1/2+\varepsilon$.  On response types with
$Y(1)=1$ set the action-one logging probability to $q_H$, and on response types
with $Y(1)=0$ set it to $q_L$; the remaining logging mass goes to action $0$.
The action-one observed cells
are matched because
\[
  (1-\gamma)(1/2+\varepsilon)q_H=(1-\gamma)/4,\qquad
  (1-\gamma)(1/2-\varepsilon)q_L=(1-\gamma)/4,
\]
and the middle type contributes $\gamma/2$ to $q_1(1/2)$.
The action-zero observed cells are matched because
\[
  \alpha(1-q_H)+\beta(1-q_L)=1/4,\qquad
  (1/2+\varepsilon-\alpha)(1-q_H)
    +(1/2-\varepsilon-\beta)(1-q_L)=1/4,
\]
where the first equality is exactly the definition of $\alpha$ and the second
follows by subtracting the first from the endpoint-type action-zero mass
$1/2$.  Multiplying these two equalities by $1-\gamma$ gives the observed
endpoint cells $q_0(1)$ and $q_0(0)$, and the middle type contributes
$\gamma/2$ to $q_0(1/2)$.  For
$\varepsilon$ small, $q_H$ and $q_L$ are close to $1/2$, so the pointwise
$f$-divergences from $e_0$ are strictly below $\rho$.  This response law has
$\mu_1=1/2+(1-\gamma)\varepsilon$; therefore the propensity-only upper endpoint
satisfies
$U_{\mathrm{prop}}(P;\rho)\ge w:=1/2+(1-\gamma)\varepsilon$.

In the joint problem, Assumption~\ref{ass:outcome-gap} implies
$\mu_1\le m_0(1)+\eta=1/2+\eta$, hence
$B_U(P;\rho,\eta)\le1/2+\eta$.  The rectangular envelope satisfies
\[
  U_{\mathrm{rect}}(P;\rho,\eta)
  \ge 1/2+(1-\gamma)\varepsilon+\eta
  > 1/2+\eta
  \ge B_U(P;\rho,\eta).
\]
Moreover $1/2+(1-\gamma)\varepsilon+\eta<1$, so the outcome-support cap in
$U_{\mathrm{rect}}$ is inactive with slack.  Taking
$\delta<(1-\gamma)\varepsilon/2$ and also smaller than the support-cap slack
verifies the strict inequalities required by
Lemma~\ref{lem:strict-gap-stability}.  Hence the compatible class remains
nonempty and the strict gap persists on an open neighborhood of the displayed
conditional law and budget pair.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:dr-corner}]
When $\rho=0$, Assumption~\ref{ass:f-budget} and the unique-zero property of
$f$ force $e_Q^\star(\cdot\mid x,y_{\mathcal A})=e_0(\cdot\mid x)$ for almost
every response table.  When $\eta=0$, Assumption~\ref{ass:outcome-gap} forces
$\mu_a^Q(x)=m_0(a,x)$ for every arm.  Hence every compatible full-data law has
the same value
$\E_{P_X}\sum_a\pi(a\mid X)m_0(a,X)$.  For the doubly robust score, expand the
residual term conditionally on $X=x$:
\[
  \E_P\!\left[
    \frac{\pi(A\mid X)}{e_0(A\mid X)}\{Y-m_0(A,X)\}\middle|X=x
  \right]
  =\sum_{a:e_0(a\mid x)>0} \frac{\pi(a\mid x)}{e_0(a\mid x)}
        \{r_a(x)-e_0(a\mid x)m_0(a,x)\}=0,
\]
where the last equality is Assumption~\ref{ass:zero-calibrated}.  The point
value and the population doubly robust score coincide.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:manski}]
For the general bounded-outcome face, under vacuous budgets no restriction
remains on the unobserved potential outcomes except $\ell\le Y(a)\le u$ and
consistency.  For each arm and context,
\[
  \mu_a^Q(x)
  =\E_Q[Y(a)\one\{A=a\}\mid X=x]
   +\E_Q[Y(a)\one\{A\ne a\}\mid X=x].
\]
The first term equals $r_a(x)$ by consistency and observational compatibility.
The second term lies between $(1-p_a(x))\ell$ and $(1-p_a(x))u$ by
Assumption~\ref{ass:bounded}.  Multiplying by $\pi(a\mid x)$, summing over
actions, and integrating gives the displayed interval.  Sharpness follows by
Manski worst-case completion: set the unobserved $Y(a)$ on the off-arm stratum
$\{A\ne a\}$ equal to $\ell$ for the lower endpoint and $u$ for the upper
endpoint, leaving the factual outcomes unchanged.

If Assumption~\ref{ass:finite-support} is also imposed, the same argument runs
inside the finite set $\mathcal G$.  The second term then lies between
$(1-p_a(x))g_{\min}$ and $(1-p_a(x))g_{\max}$, and sharpness is obtained by
assigning the off-arm potential outcomes to $g_{\min}$ or $g_{\max}$.  These
finite-grid endpoints equal the general $\ell,u$ endpoints exactly when
$g_{\min}=\ell$ and $g_{\max}=u$.
\end{proof}

\section{Sanity checks}
\begin{enumerate}[leftmargin=*]
\item \textbf{Vacuous restrictions.}  If both budgets are vacuous, the sharp
program drops the divergence and mean-tube constraints.  Proposition~\ref{prop:manski}
then gives exactly the general bounded-outcome fill-in interval
$r_a(x)+(1-p_a(x))[\ell,u]$ for each arm and context, the contextual-policy
analogue of Manski \cite{Manski1990}.  If the finite-grid restriction remains
active and $\ell,u$ are not grid endpoints, this sanity check becomes
$r_a(x)+(1-p_a(x))[g_{\min},g_{\max}]$.

\item \textbf{Zero-width point face.}  If $\rho=0$, $\eta=0$, and the observed
law is calibrated to $e_0$ and $m_0$, Proposition~\ref{prop:dr-corner} gives a
singleton interval equal to the standard doubly robust policy-value functional.

\item \textbf{Random logging special case.}  If $\rho=0$ but $\eta$ is not zero,
the latent logging kernel is independent of the response table and equal to
$e_0$.  Compatibility fixes $\mu_a(x)=r_a(x)/e_0(a\mid x)$ on positive-$e_0$
cells; the outcome-regression tube only checks whether this already-identified
arm mean is admissible.  Thus the interval is either empty or point identified,
as it should be under known randomized logging.

\item \textbf{Single-action target policy.}  If $\pi(a_0\mid x)=1$ for one arm,
the conditional objective is just $\mu_{a_0}(x)$.  The program reduces to the
partial-identification interval for one mean potential outcome under the same
joint sensitivity budgets, and under vacuous budgets it becomes
$r_{a_0}(x)+(1-p_{a_0}(x))[\ell,u]$.

\item \textbf{Balke--Pearl-style finite latent table.}  With finite $X$, finite
outcome grid, binary action, and additional IV restrictions replacing the
present sensitivity restrictions, the proof technique becomes the finite
latent-table linear program of Balke and Pearl \cite{BalkePearl1997}.  The
current theorem differs by using a logging-kernel divergence ball and
arm-mean bands instead of IV exclusion and independence.
\end{enumerate}

\section{Counterexample or minimality check}
The binary construction in the proof of Theorem~\ref{thm:nonrect} is also the
minimality check.  If the outcome-regression budget is dropped, the same
observed reward-cell law admits response tables with
$\mu_1=1/2+(1-\gamma)\varepsilon$ while keeping the six factual cells on
$\mathcal G=\{0,1/2,1\}$ fixed through a small response-dependent logging
tilt.  If one then adds an independent
$+\eta$ allowance after solving that propensity-only problem, the value
$1/2+(1-\gamma)\varepsilon+\eta$ is counted by the rectangular envelope.

That value is not generated by any single full-data law satisfying the joint
restrictions when $m_0(1)=1/2$ and the outcome tube is active, because every
jointly admissible law must obey $\mu_1\le1/2+\eta$.  The nearest correct
formula is therefore not the rectangular envelope but the joint conditional
program in Section~7.  The support condition is also minimal: if
$e_0(a\mid x)=0$ while $p_a(x)>0$, absolute continuity of the latent logging
kernel makes the feasible set empty; if $e_0(a\mid x)=0$ while
$\pi(a\mid x)>0$, the target policy asks for an action outside the nominal
support and the sensitivity model supplies no logging-kernel mass with which to
identify or bound that arm beyond the stated empty/support convention.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
\item \textbf{Observable input.}  A finite action type $\mathcal A$; a standard
Borel covariate space; a probability law $P$ for $(X,A,Y)$; bounded support
$Y\in[\ell,u]$; optional finite grid $\mathcal G\subset[\ell,u]$ with
$g_{\min}$ and $g_{\max}$; kernels
$e_0,\pi:\mathcal X\to\Delta(\mathcal A)$; regression
$m_0:\mathcal A\times\mathcal X\to[\ell,u]$; budgets $\rho,\eta\ge0$.

\item \textbf{Full-data object.}  A law $Q$ for
$(X,Y_{\mathcal A},A)$ with conditional response-table law $H_x$ and latent
logging kernel $e^\star(\cdot\mid x,y_{\mathcal A})$.

\item \textbf{Probabilistic assumptions.}  Consistency $Y=Y(A)$; observed
compatibility constraints for $p_a(x)$ and $r_a(x)$; bounded potential outcomes;
absolute continuity of $e^\star$ with respect to $e_0$; pointwise
$f$-divergence budget; arm-mean tube around $m_0$; nonemptiness of the
compatible class on the faces where endpoints are asserted.

\item \textbf{Deterministic convex objects.}  The finite conditional feasible
set $\mathcal K_x(P;\rho,\eta)$; variables $z_{ja}\ge0$;
$h_j=\sum_a z_{ja}$; the perspective form of the $f$-divergence constraint;
linear observed reward-cell constraints
$\sum_{j:y^j_a=c}z_{ja}=q_a(c\mid x)$; linear mean-band constraints; linear
objective $v_x(z)$.

\item \textbf{Identified-set definitions.}  Policy value
$V_Q(\pi)$; compatible class $\mathcal Q(P;\rho,\eta)$; identified set
$\Theta_I(P;\rho,\eta)$; semantic extrema
$\underline{\theta}_I(P;\rho,\eta)$ and $\overline{\theta}_I(P;\rho,\eta)$; program
endpoints $B_L(P;\rho,\eta)$ and $B_U(P;\rho,\eta)$; theorem identity
$\underline{\theta}_I=B_L$ and $\overline{\theta}_I=B_U$; diagnostic outer envelope
$U_{\mathrm{rect}}(P;\rho,\eta)$.

\item \textbf{Lemmas.}  Conditional full reward-cell compatibility is
equivalent to membership in $\mathcal K_x$; compact measurable conditional
programs have optimizer selections; conditional optimizer selections paste into
full-data laws; posterior mixtures of compatible full-data laws remain
compatible because $q_j^t=\alpha_jq_j^1+(1-\alpha_j)q_j^0$ and
$\mathcal C_\rho(x)$ is convex; Manski worst-case completion fills off-arm
potential outcomes at $\ell,u$ in the general bounded-outcome face and at
$g_{\min},g_{\max}$ in the finite-grid face; zero divergence implies equality
of finite kernels because $f$ has unique minimum at $1$.

\item \textbf{Continuity and open-set step.}  The finite strict-gap stability
lemma uses compact closed feasible correspondences, strict divergence slack,
strict outcome-band slack for nonemptiness, an inactive support cap in
$U_{\mathrm{rect}}$, and Berge continuity of the joint and propensity-only
value functions.  This turns the binary strict-gap construction into an open
set of conditional observable laws and budgets.
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a sharp partial-identification formula for an
offline target-policy value under joint propensity and outcome-regression
misspecification.  The tightening work is done by two restrictions imposed on
the same latent response table: the pointwise $f$-divergence budget limits
response-dependent logging distortions, and the sup-norm regression budget
limits the arm means.  The bound is point-identifying on the calibrated
zero-budget face and becomes the Manski fill-in interval when both budgets are
vacuous, with $\ell,u$ used in the general bounded-outcome face and
$g_{\min},g_{\max}$ used when the finite grid excludes the support endpoints.
The non-rectangularity result shows that a separable rectangular support
function is generally conservative for this joint causal sensitivity problem:
it allows two worst-case mechanisms that no single compatible full-data law can
realize simultaneously.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association}, 92(439):1171--1176.

\bibitem{DornGuo2023}
Dorn, J. and Guo, K. (2023).
Sharp sensitivity analysis for inverse propensity weighting via quantile balancing.
\emph{Journal of the American Statistical Association}, 118(544):2645--2657.

\bibitem{DornGuoKallus2025}
Dorn, J., Guo, K., and Kallus, N. (2025).
Doubly-valid/doubly-sharp sensitivity analysis for causal inference with unmeasured confounding.
\emph{Journal of the American Statistical Association}, 120(549):331--342.

\bibitem{DudikLangfordLi2011}
Dudik, M., Langford, J., and Li, L. (2011).
Doubly robust policy evaluation and learning.
\emph{Proceedings of the 28th International Conference on Machine Learning}.

\bibitem{HessFrauenMelnychukFeuerriegel2026}
Hess, K., Frauen, D., Melnychuk, V., and Feuerriegel, S. (2026).
Efficient and sharp off-policy learning under unobserved confounding.
\emph{International Conference on Learning Representations}.

\bibitem{IshikawaHe2023}
Ishikawa, K. and He, N. (2023).
Kernel conditional moment constraints for confounding robust inference.
\emph{Proceedings of The 26th International Conference on Artificial
Intelligence and Statistics}, PMLR 206:650--674.

\bibitem{JinXuZhengZhou2025}
Jin, Z., Xu, G., Zheng, X., and Zhou, Y. (2025).
Policy learning under unobserved confounding: A robust and efficient approach.
\emph{arXiv:2507.20550}.

\bibitem{KallusZhou2018}
Kallus, N. and Zhou, A. (2018).
Confounding-robust policy improvement.
\emph{Advances in Neural Information Processing Systems 31}, 9289--9299.

\bibitem{KallusZhou2020}
Kallus, N. and Zhou, A. (2020).
Confounding-robust policy evaluation in infinite-horizon reinforcement learning.
\emph{Advances in Neural Information Processing Systems 33}.

\bibitem{KallusZhou2021}
Kallus, N. and Zhou, A. (2021).
Minimax-optimal policy learning under unobserved confounding.
\emph{Management Science}, 67(5):2870--2890.

\bibitem{KallusMaoWangZhou2022}
Kallus, N., Mao, X., Wang, K., and Zhou, Z. (2022).
Doubly robust distributionally robust off-policy evaluation and learning.
\emph{Proceedings of the 39th International Conference on Machine Learning},
PMLR 162:10598--10632.

\bibitem{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review}, 80(2):319--323.

\bibitem{ManskiPepper2000}
Manski, C. F. and Pepper, J. V. (2000).
Monotone instrumental variables: With an application to the returns to schooling.
\emph{Econometrica}, 68(4):997--1010.

\bibitem{Tan2006}
Tan, Z. (2006).
A distributional approach for causal inference using propensity scores.
\emph{Journal of the American Statistical Association}, 101(476):1619--1637.

\bibitem{SiZhangZhouBlanchet2020}
Si, N., Zhang, F., Zhou, Z., and Blanchet, J. (2020).
Distributionally robust policy evaluation and learning in offline contextual
bandits.
\emph{Proceedings of the 37th International Conference on Machine Learning},
PMLR 119:8884--8894.

\bibitem{WangAgarwalDudik2017}
Wang, Y.-X., Agarwal, A., and Dudik, M. (2017).
Optimal and adaptive off-policy evaluation in contextual bandits.
\emph{Proceedings of the 34th International Conference on Machine Learning}, PMLR 70:3589--3597.

\bibitem{ZhangXuTan2025}
Zhang, Y., Xu, R., and Tan, Z. (2025).
Distributionally enhanced marginal sensitivity model: Simultaneous sensitivity constraints on treatment probability and outcome distribution.
\emph{arXiv preprint}.
\end{thebibliography}

\end{document}
