% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_did\_anticipation\_bounded, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_did\_anticipation\_bounded} / \texttt{v1}%
  \\ \large\textit{Sharp Staggered-DID ATT Bounds under Covariate-Conditional Bounded Anticipation}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note derives the bounding functional for a fixed staggered-adoption group-time
\(ATT(g,t)\), and for finite weighted aggregates of such effects, when
anticipatory outcome distortions are not ruled out but are bounded
covariate-conditionally.  The functional starts from the observable conditional
DID contrast and adds the support function of the finite box of treated-cohort and
comparison-cohort anticipation distortions.  The causal target is
\(\theta_{g,t}=\E[Y_t(g)-Y_t(\infty)\mid G=g]\), with aggregate targets obtained by
finite known weights over post-adoption cohort-period cells.  Under finite
support, consistency, conditional baseline parallel trends, overlap, normalized
comparison weights, bounded anticipation, and variation-independent anticipation
boxes, the identified set is exactly the proposed interval.  Thus the Stage -1
sharp-support conjecture is confirmed; without the variation-independent box
condition the same formula remains a valid outer bound but need not be sharp.
\end{abstract}

\section{Introduction}
Staggered DID designs often involve policies that are announced before the legal
or administrative adoption date.  Firms may reorganize before a subsidy starts,
students may respond before a school reform is implemented, and local governments
may alter behavior before a regulation binds.  A strict no-anticipation
assumption turns these pre-adoption responses into violations; excluding all
near-adoption cells restores a clean design only when the exclusion horizon is
credible and enough comparison support remains.

The question here is partial identification rather than point identification.
Suppose the researcher is willing to bound, but not eliminate, the conditional
mean anticipatory distortion for each cohort, period, and covariate cell.  The
standard group-time DID contrast is then not equal to \(ATT(g,t)\).  It equals the
target minus a finite signed linear functional of latent anticipation
distortions.  The useful object is therefore the support interval of that signed
functional, computed after the observable DID contrast has been fixed by \(P\).

The note establishes that this interval is sharp under the proposal's
variation-independent anticipation-box condition.  The result keeps the
Callaway--Sant'Anna style group-time target and risk-set comparison structure, but
it replaces the binary choice between clean exclusion and no causal statement with
a finite support-function calculation.  It also records the aggregate rule: when a
single latent anticipation coordinate enters several cohort-period contrasts, its
signed coefficients must be pooled before taking absolute values.

The result is useful for formula design because it separates three ingredients
that are often conflated: the causal target \(ATT(g,t)\), the observed DID
contrast, and the latent anticipation support correction.  Once the comparison
risk set, base period, and bound radii \(M_{h,s}(x)\) are specified, the width of
the identified set is a deterministic diagnostic of which treated and
not-yet-treated cells are doing the sensitivity work.

\paragraph{Motivating conjecture(s).}
Conjecture 1: sharp support interval for bounded anticipation (NOT YET PROVED).
Under Assumptions~\ref{ass:finite-overlap}--\ref{ass:fixed-weights}, the interval in Theorem~\ref{thm:linear-contamination} is the sharp identified set for \(ATT(g,t)\).  More generally, for any finite aggregate \(\Theta(w)=\sum_{(g,t)}w_{g,t}ATT(g,t)\), the sharp identified set is
\[
  \left[
    \sum_{(g,t)} w_{g,t}\E[\Delta_{g,t,b}(X)\mid G=g]
      - \sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x),
    \sum_{(g,t)} w_{g,t}\E[\Delta_{g,t,b}(X)\mid G=g]
      + \sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x)
  \right],
\]
where \(c^{(w)}_{h,s}(x)\) is the total signed coefficient on \(a_{h,s}(x)\) after expanding the weighted sum of \(\Lambda_{g,t,b}\) functionals.  Thus, when the same anticipation coordinate enters multiple cohort-period contrasts, the aggregate width is computed by summing signed coefficients before taking absolute values.

\section{Related work and positioning}
Callaway and Sant'Anna \cite{CallawaySantAnna2021} identify group-time ATT
parameters in staggered DID under conditional parallel trends and a known limited
anticipation convention; their result is the point-identification benchmark that
is recovered when all relevant anticipation bounds are zero.  de Chaisemartin and
D'Haultfoeuille \cite{DCDH2020} show how heterogeneous effects interact with DID
weights and motivate explicit accounting for the cells that enter a comparison;
the present note keeps known comparison weights but bounds anticipation bias
rather than decomposing a TWFE coefficient.  Goodman-Bacon
\cite{GoodmanBacon2021} decomposes timing-variation DID into weighted two-by-two
comparisons, which is relevant because later-treated controls may be untreated but
already anticipatory.  Sun and Abraham \cite{SunAbraham2021} show that staggered
event-study leads and lags can mix effects from other relative periods; here the
near-adoption preperiod object is a bounded latent causal distortion entering the
ATT contrast.

Borusyak, Jaravel, and Spiess \cite{BorusyakJaravelSpiess2024} develop imputation
estimators for staggered event studies under no anticipation; the present theorem
asks what remains identified when an imputation or base cell can itself contain a
bounded anticipatory component.  Rambachan and Roth \cite{RambachanRoth2023}
provide a modern sensitivity-analysis and support-function perspective for DID
violations; this note specializes the support-function logic to a staggered
adoption anticipation operator with shared latent coordinates across aggregates.
Manski \cite{Manski1990,Manski2003} and Manski and Pepper
\cite{ManskiPepper2018} supply the partial-identification tradition of replacing
exact assumptions by transparent bounds; the difference here is that adoption
timing fixes exactly which latent coordinates enter each DID contrast.  Roth,
Sant'Anna, Bilinski, and Poe \cite{RothSantAnnaBilinskiPoe2023} emphasize
sensitivity analysis in modern DID practice; the current result gives a concrete
sensitivity target for anticipation rather than for parallel-trends drift.
Piccininni, Tchetgen Tchetgen, and Stensrud
\cite{PiccininniTchetgenStensrud2025} stress that no anticipation must be tied to
a precise intervention and timing convention; the locked adoption-cohort
notation here makes that convention explicit.  Augustin, Gutknecht, and Liu
\cite{AugustinGutknechtLiu2025} study staggered adoption with anticipation and
timing misclassification; their work motivates the bias concern, while the
present note gives a nonparametric sharp interval under covariate-conditional
magnitude bounds.

In-repository prior work is adjacent but not duplicative.  The staggered
minimal-basis panel catalogue studies point formulas and coefficient
decompositions under exact history conventions.  The earlier
\texttt{q1\_partial\_did\_unobserved\_trends} proposal studies latent trend
summary sufficiency and nonsharpness.  The theorem below differs from both:
it is a partial-identification result whose identified set is a finite linear
image of a bounded anticipation box.

\section{Formal setup}
Let the observable distribution \(P\) be the law of
\((Y_0,\ldots,Y_T,G,X)\), where \(T<\infty\),
\(G\in\{1,\ldots,T,\infty\}\), and \(X\) takes values in a finite set
\(\mathcal{X}\).  The observed adoption path is absorbing:
\[
  D_s=\one\{G\le s\},\qquad s=0,\ldots,T.
\]
For a finite adoption cohort \(h\), \(Y_s(h)\) denotes the potential outcome at
period \(s\) under first adoption at \(h\).  The symbol \(Y_s(\infty)\) denotes
the never-adopt potential outcome.  The never-adopt cohort has no anticipation
coordinate.

For \(s<h<\infty\), define the conditional anticipation distortion
\[
  a_{h,s}(x)
  =
  \E[Y_s(h)-Y_s(\infty)\mid G=h,X=x],
  \qquad x\in\mathcal{X}.
\]
Set \(a_{\infty,s}(x)=0\).  Coordinates outside the anticipation horizon have
radius zero.  Thus the finite anticipation box is
\[
  \mathcal{A}(M)
  =
  \prod_{\substack{x\in\mathcal{X}\\ h<\infty,\ s<h}}
  [-M_{h,s}(x),M_{h,s}(x)],
  \qquad
  M_{h,s}(x)=0\ \text{if }h-s>k.
\]

Fix a finite target collection \(\mathcal{J}\).  Each
\(j\in\mathcal{J}\) consists of a post-adoption cell
\((g_j,t_j)\) with \(t_j\ge g_j\), a base period \(b_j<g_j\), a comparison risk
set \(R_j\subseteq\{h:h>t_j\}\cup\{\infty\}\), and known comparison weights
\(\omega_{h\mid j}(x)\) for \(h\in R_j\).  The singleton target is obtained by
taking \(\mathcal{J}=\{j\}\) and weight \(w_j=1\).  A finite aggregate uses known
nonnegative weights \(w_j\) with \(\sum_{j\in\mathcal{J}}w_j=1\).

Write
\[
  \pi_j(x)=\Pr(X=x\mid G=g_j).
\]
The target value induced by a compatible full potential-outcome law is
\[
  \theta_w
  =
  \sum_{j\in\mathcal{J}}w_j
  \E[Y_{t_j}(g_j)-Y_{t_j}(\infty)\mid G=g_j].
\]
The identified set is the set of all such values across full laws that preserve
the observable distribution \(P\) and satisfy the maintained restrictions:
\[
  \Theta_I^w(P)
  =
  \left\{\theta_w:
  \text{there is a compatible potential-outcome law satisfying
  Assumptions~\ref{ass:finite-overlap}--\ref{ass:fixed-weights}}\right\}.
\]

\paragraph{Locked parameters.}
\begin{itemize}[leftmargin=*]
  \item qid: \texttt{pid\_did\_anticipation\_bounded}
  \item specialization: \texttt{v1}
  \item observable distribution: \(P=\) law of \((Y_t,G,X)\) for finite periods \(t=0,\ldots,T\), adoption cohort \(G\in\{1,\ldots,T,\infty\}\), and finite covariate support \(X\).
  \item parameter \(\theta\): \(ATT(g,t)=\E[Y_t(g)-Y_t(\infty)\mid G=g]\) for a fixed treated cohort \(g\) and post-adoption period \(t\ge g\), plus finite weighted aggregates of such cohort-period ATTs.
  \item identifying restrictions: absorbing staggered adoption; conditional baseline parallel trends for \(Y(\infty)\) between cohort \(g\) and the chosen comparison risk set; consistency; overlap; bounded anticipation horizon \(k\); for every cohort \(h\) and pre-adoption period \(s\) with \(0<h-s\le k\), the conditional anticipation distortion \(a_{h,s}(x)=\E[Y_s(h)-Y_s(\infty)\mid G=h,X=x]\) lies in the known interval \([-M_{h,s}(x),M_{h,s}(x)]\), and \(a_{h,s}(x)=0\) outside that horizon; comparison weights are defined only on positive-overlap risk-set cells and satisfy \(\sum_h\omega_{h\mid g,t,b}(x)=1\) for every target cell and \(x\).
  \item bounding functional: the support-function interval obtained by adding to the observed conditional DID contrast the sharp box support of all treated-cohort and comparison-cohort anticipation distortions that enter the contrast.
\end{itemize}

\section{Assumptions}
\begin{assumption}[Finite support, finite means, and overlap]\label{ass:finite-overlap}
The period set, treated-cohort set, target collection \(\mathcal{J}\), comparison
risk sets, and covariate support \(\mathcal{X}\) are finite.  All conditional
means appearing in the displayed formulas exist as finite real numbers.  For
every \(j\in\mathcal{J}\), \(x\) with \(\pi_j(x)>0\), and comparison cohort
\(h\in R_j\) with \(\omega_{h\mid j}(x)\ne0\), the conditional cell probability
\(\Pr(G=h,X=x)\) is positive.
\end{assumption}

\begin{assumption}[Consistency and absorbing adoption]\label{ass:consistency}
Observed treatment is \(D_s=\one\{G\le s\}\).  Observed outcomes satisfy
\[
  Y_s=Y_s(G)\ \text{when }G<\infty,
  \qquad
  Y_s=Y_s(\infty)\ \text{when }G=\infty.
\]
\end{assumption}

\begin{assumption}[Conditional baseline parallel trends]\label{ass:baseline-pt}
For every \(j\in\mathcal{J}\), comparison cohort \(h\in R_j\), and covariate
value \(x\) used by the contrast,
\[
  \E[Y_{t_j}(\infty)-Y_{b_j}(\infty)\mid G=g_j,X=x]
  =
  \E[Y_{t_j}(\infty)-Y_{b_j}(\infty)\mid G=h,X=x].
\]
\end{assumption}

\begin{assumption}[Bounded anticipation horizon]\label{ass:bounded-anticipation}
There is a fixed integer \(k\ge0\) and known finite radii \(M_{h,s}(x)\ge0\) such
that, for every finite cohort \(h\), pre-adoption period \(s<h\), and
\(x\in\mathcal{X}\),
\[
  a_{h,s}(x)=0\quad\text{if }h-s>k,
  \qquad
  -M_{h,s}(x)\le a_{h,s}(x)\le M_{h,s}(x)
  \quad\text{if }0<h-s\le k.
\]
For the never-adopt cohort, \(a_{\infty,s}(x)=0\).
\end{assumption}

\begin{assumption}[Variation-independent anticipation boxes]\label{ass:box-independence}
Every finite array \(a\in\mathcal{A}(M)\) is compatible with at least one joint
potential-outcome law that preserves the observable distribution \(P\),
Assumptions~\ref{ass:consistency}--\ref{ass:baseline-pt}, and the post-treatment
ATT values induced by the decomposition in Lemma~\ref{lem:conditional-decomp}.
\end{assumption}

\begin{assumption}[Fixed normalized comparison weights]\label{ass:fixed-weights}
The weights \(\omega_{h\mid j}(x)\) and aggregate weights \(w_j\) are known
functions of the observable law and the chosen comparison convention; they are not
functions of unobserved anticipation distortions.  For every \(j\in\mathcal{J}\)
and \(x\in\mathcal{X}\) with \(\pi_j(x)>0\), comparison weights are defined only
on positive-overlap cells and satisfy
\[
  \sum_{h\in R_j}\omega_{h\mid j}(x)=1.
\]
\end{assumption}

\section{Estimand-defining functional}
For \(j=(g_j,t_j,b_j,R_j,\omega_j)\), define the observable conditional DID
contrast
\[
  \Delta_j(x)
  =
  \E[Y_{t_j}-Y_{b_j}\mid G=g_j,X=x]
  -
  \sum_{h\in R_j}\omega_{h\mid j}(x)
  \E[Y_{t_j}-Y_{b_j}\mid G=h,X=x].
\]
Define the latent anticipation-bias functional
\[
  \Lambda_j(a)(x)
  =
  a_{g_j,b_j}(x)
  +
  \sum_{h\in R_j}\omega_{h\mid j}(x)
    \{a_{h,t_j}(x)-a_{h,b_j}(x)\},
\]
where \(a_{\infty,s}(x)=0\) and every coordinate outside the anticipation horizon
has radius zero.

The observable aggregate contrast is
\[
  \delta_w(P)=\sum_{j\in\mathcal{J}}w_j
  \sum_{x\in\mathcal{X}}\pi_j(x)\Delta_j(x).
\]
For each anticipation coordinate \((h,s,x)\), define the pooled signed
coefficient
\[
  c^{(w)}_{h,s}(x)
  =
  \sum_{j\in\mathcal{J}}w_j\pi_j(x)
  \left[
    \one\{h=g_j,\ s=b_j\}
    +
    \one\{h\in R_j,\ s=t_j\}\omega_{h\mid j}(x)
    -
    \one\{h\in R_j,\ s=b_j\}\omega_{h\mid j}(x)
  \right].
\]
The candidate bounding functional is the interval
\[
  [\theta_L^w(P),\theta_U^w(P)]
  =
  \left[
    \delta_w(P)-\sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x),
    \delta_w(P)+\sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x)
  \right],
\]
where the sums are finite and \(M_{h,s}(x)=0\) for impossible, never-adopt, and
outside-horizon coordinates.  The singleton \(ATT(g,t)\) interval is obtained by
using one \(j\) and \(w_j=1\).  Without
Assumption~\ref{ass:box-independence}, the interval is an outer bound; with that
assumption, Theorem~\ref{thm:sharp-box-stage0} proves that it is sharp.

\section{Target causal estimand}
For a fixed treated cohort \(g<\infty\) and post-adoption period \(t\ge g\), the
causal target is
\[
  \theta_{g,t}=ATT(g,t)
  =
  \E[Y_t(g)-Y_t(\infty)\mid G=g].
\]
The conditional target is
\[
  ATT(g,t\mid x)
  =
  \E[Y_t(g)-Y_t(\infty)\mid G=g,X=x].
\]
For a finite target collection \(\mathcal{J}\), the aggregate causal target is
\[
  \theta_w
  =
  \sum_{j\in\mathcal{J}}w_j ATT(g_j,t_j).
\]
The object in Section~7 is not the target by definition.  It is an observable
contrast plus a support correction for the latent anticipation coordinates.  The
main result is the partial-identification statement
\(\Theta_I^w(P)=[\theta_L^w(P),\theta_U^w(P)]\), not a point equality except in
zero-width cases.

\section{Main theorems}
\begin{theorem}[Linear anticipation contamination]\label{thm:linear-contamination}
Under Assumptions~\ref{ass:finite-overlap}--\ref{ass:fixed-weights}, for every
\(j\in\mathcal{J}\) and covariate value \(x\) used by the contrast,
\[
  ATT(g_j,t_j\mid x)=\Delta_j(x)+\Lambda_j(a)(x).
\]
Consequently, for any compatible law,
\[
  \theta_w
  =
  \delta_w(P)+
  \sum_{h,s,x}c^{(w)}_{h,s}(x)a_{h,s}(x).
\]
For a singleton target \(j=(g,t,b,R,\omega)\), this implies the outer interval
\[
  ATT(g,t)\in
  \left[
  \E[\Delta_j(X)\mid G=g]-W_j(M),
  \E[\Delta_j(X)\mid G=g]+W_j(M)
  \right],
\]
where
\[
  W_j(M)
  =
  \E\!\left[
    M_{g,b}(X)+
    \sum_{h\in R}|\omega_{h\mid j}(X)|
      \{M_{h,t}(X)+M_{h,b}(X)\}
    \,\middle|\,G=g
  \right].
\]
\end{theorem}

This theorem is the algebraic decomposition behind the result.  It is useful
because it identifies the exact treated-cohort and comparison-cohort
anticipation cells that contaminate a group-time DID contrast.  It differs from
the usual point-ID DID formulas by retaining, rather than ruling out, those
latent terms.

\begin{theorem}[Sharp bounded-anticipation identified set]\label{thm:sharp-box-stage0}
Under Assumptions~\ref{ass:finite-overlap}--\ref{ass:fixed-weights}, the
identified set for the finite aggregate \(\theta_w\) is exactly
\[
  \Theta_I^w(P)=[\theta_L^w(P),\theta_U^w(P)].
\]
For a singleton target this gives the sharp identified set for \(ATT(g,t)\).  The
verdict on Conjecture 1 is therefore: confirmed under the proposal's
variation-independent anticipation-box assumption; without that assumption the
same displayed interval is only an outer bound.
\end{theorem}

The theorem is the contribution of the note.  It turns a bounded-anticipation
restriction into a sharp finite-dimensional support-function interval and shows
that aggregates require coefficient pooling before taking absolute values.  This
is more specific than the general sensitivity logic of Rambachan and Roth
\cite{RambachanRoth2023} and more permissive than point-ID limited-anticipation
DID formulas because it allows contaminated comparison cohorts to remain in the
risk set.

\begin{proposition}[Zero-bound recovery]\label{prop:zero-bound-recovery}
If \(M_{h,s}(x)=0\) for every coordinate with
\(|c^{(w)}_{h,s}(x)|>0\), then
\[
  \Theta_I^w(P)=\{\delta_w(P)\}.
\]
For a singleton target with a clean base period \(b<g-k\) and comparison cohorts
satisfying \(h-t>k\), this singleton is the usual conditional group-time DID
functional.  With any normalized heterogeneity-robust comparison convention whose
weights satisfy Assumption~\ref{ass:fixed-weights}, the corresponding aggregate
also collapses to its no-anticipation point estimand.
\end{proposition}

This recovery result is not the new partial-identification kernel; it is the
sanity link to Callaway and Sant'Anna \cite{CallawaySantAnna2021} and to
heterogeneity-robust staggered DID weighting ideas such as de Chaisemartin and
D'Haultfoeuille \cite{DCDH2020}.  It confirms that the interval extends standard
workflows instead of changing the target at the clean corner.

\section{Interpretation}
The interval is centered at an observable DID contrast.  Its half-width is not a
generic penalty; it is the support value of the exact signed anticipation
operator induced by the selected base period, risk set, covariate distribution,
and aggregate weights.  A treated cohort contributes through its base-period
anticipation \(a_{g,b}(x)\).  A not-yet-treated comparison cohort contributes
through \(a_{h,t}(x)-a_{h,b}(x)\), so controls can be contaminated even though
they are untreated at period \(t\).

The bound collapses to point identification precisely when every anticipation
coordinate with a nonzero pooled coefficient has zero radius.  This includes the
usual clean-horizon design in which \(b<g-k\) and every comparison cohort is more
than \(k\) periods away from adoption at \(t\).  It also includes less obvious
aggregate cancellations: if the same latent coordinate enters two targets with
opposite signed pooled coefficients, the aggregate interval can be narrower than
the sum of singleton half-widths.

The bound widens as the radii \(M_{h,s}(x)\) grow or as risk-set weights place
mass on cohorts close to adoption.  If the bounded-anticipation restriction is
removed and no alternative outcome-support bound is imposed, the relevant latent
coordinates are unrestricted and the partial-ID interval becomes uninformative.
If only a global bounded-outcome restriction is imposed, the result reduces to a
Manski-style worst-case completion for the missing counterfactual components.

The tightening work is done by Assumption~\ref{ass:bounded-anticipation}; the
sharpness work is done by Assumption~\ref{ass:box-independence}.  Conditional
baseline parallel trends and normalized weights move the untreated trend out of
the contrast.  The anticipation boxes then say how far the remaining latent bias
can move the target.

\section{Step-by-step proof}
\begin{lemma}[Conditional DID decomposition]\label{lem:conditional-decomp}
Under Assumptions~\ref{ass:finite-overlap}, \ref{ass:consistency},
\ref{ass:baseline-pt}, and \ref{ass:fixed-weights},
\[
  ATT(g_j,t_j\mid x)=\Delta_j(x)+\Lambda_j(a)(x)
\]
for every used cell \((j,x)\).
\end{lemma}

\begin{proof}
Fix \(j\) and \(x\).  By consistency and the definition of \(ATT(g_j,t_j\mid x)\),
\[
\begin{aligned}
  \E[Y_{t_j}-Y_{b_j}\mid G=g_j,X=x]
  &=
  \E[Y_{t_j}(g_j)-Y_{b_j}(g_j)\mid G=g_j,X=x] \\
  &=
  ATT(g_j,t_j\mid x)
  +\E[Y_{t_j}(\infty)-Y_{b_j}(\infty)\mid G=g_j,X=x]
  -a_{g_j,b_j}(x).
\end{aligned}
\]
For each \(h\in R_j\), the restriction \(h>t_j\) or \(h=\infty\) means the
comparison cohort is not yet adopted at both \(b_j\) and \(t_j\).  By consistency,
\[
\begin{aligned}
  \E[Y_{t_j}-Y_{b_j}\mid G=h,X=x]
  &=
  \E[Y_{t_j}(h)-Y_{b_j}(h)\mid G=h,X=x] \\
  &=
  \E[Y_{t_j}(\infty)-Y_{b_j}(\infty)\mid G=h,X=x]
  +a_{h,t_j}(x)-a_{h,b_j}(x),
\end{aligned}
\]
with both anticipation terms equal to zero when \(h=\infty\).  Substituting these
two displays into the definition of \(\Delta_j(x)\) gives
\[
\begin{aligned}
  \Delta_j(x)
  &=
  ATT(g_j,t_j\mid x)-a_{g_j,b_j}(x) \\
  &\quad
  +\E[Y_{t_j}(\infty)-Y_{b_j}(\infty)\mid G=g_j,X=x] \\
  &\quad
  -\sum_{h\in R_j}\omega_{h\mid j}(x)
    \E[Y_{t_j}(\infty)-Y_{b_j}(\infty)\mid G=h,X=x] \\
  &\quad
  -\sum_{h\in R_j}\omega_{h\mid j}(x)
    \{a_{h,t_j}(x)-a_{h,b_j}(x)\}.
\end{aligned}
\]
Assumption~\ref{ass:baseline-pt} makes every comparison untreated trend in the
sum equal to the treated-cohort untreated trend at the same \(x\).  The
normalization in Assumption~\ref{ass:fixed-weights} then cancels the entire
untreated-trend line.  Rearranging the remaining terms yields
\[
  ATT(g_j,t_j\mid x)
  =
  \Delta_j(x)
  +a_{g_j,b_j}(x)
  +\sum_{h\in R_j}\omega_{h\mid j}(x)
    \{a_{h,t_j}(x)-a_{h,b_j}(x)\},
\]
which is the claimed identity.
\end{proof}

\begin{lemma}[Support function of a finite symmetric box]\label{lem:box-support}
Let \(I\) be finite, \(M_i\ge0\), and
\(\mathcal{B}=\prod_{i\in I}[-M_i,M_i]\).  For any real coefficients \(c_i\),
\[
  \left\{\sum_{i\in I}c_i u_i:u\in\mathcal{B}\right\}
  =
  \left[-\sum_{i\in I}|c_i|M_i,\ \sum_{i\in I}|c_i|M_i\right].
\]
\end{lemma}

\begin{proof}
For any \(u\in\mathcal{B}\),
\[
  \sum_{i\in I}c_i u_i
  \le
  \sum_{i\in I}|c_i||u_i|
  \le
  \sum_{i\in I}|c_i|M_i,
\]
and applying the same argument to \(-u\) gives the lower bound.  The upper bound
is attained by taking \(u_i=M_i\) when \(c_i\ge0\) and \(u_i=-M_i\) when
\(c_i<0\); the lower bound is attained by the opposite choice.  Since
\(\mathcal{B}\) is convex and the displayed map is linear, every point between
the two endpoint values is attained by convexly mixing the two endpoint arrays.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:linear-contamination}]
The first display is Lemma~\ref{lem:conditional-decomp}.  Multiply that identity
by \(w_j\pi_j(x)\), sum over \(j\in\mathcal{J}\) and \(x\in\mathcal{X}\), and
use the law of iterated expectation over the finite support of \(X\mid G=g_j\).
The terms involving \(\Delta_j(x)\) sum to \(\delta_w(P)\).  Collecting equal
anticipation coordinates gives exactly the coefficient definition
\(c^{(w)}_{h,s}(x)\), hence
\[
  \theta_w
  =
  \delta_w(P)+\sum_{h,s,x}c^{(w)}_{h,s}(x)a_{h,s}(x).
\]
For a singleton target, Assumption~\ref{ass:bounded-anticipation} bounds
\(a_{g,b}(X)\), \(a_{h,t}(X)\), and \(a_{h,b}(X)\) by their corresponding radii.
The triangle inequality applied inside the finite conditional expectation gives
the displayed outer interval with half-width \(W_j(M)\).
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:sharp-box-stage0}]
First prove containment.  For any element of \(\Theta_I^w(P)\), the compatible
law satisfies Assumption~\ref{ass:bounded-anticipation}, so its anticipation
array lies in \(\mathcal{A}(M)\).  Theorem~\ref{thm:linear-contamination}
expresses the target as \(\delta_w(P)\) plus a finite linear functional of that
array.  Lemma~\ref{lem:box-support} therefore implies
\[
  \theta_L^w(P)\le \theta_w\le \theta_U^w(P),
\]
so \(\Theta_I^w(P)\subseteq[\theta_L^w(P),\theta_U^w(P)]\).

Now prove sharpness.  Lemma~\ref{lem:box-support} says that for every
\(r\) between
\(-\sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x)\) and
\(\sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x)\), there is an anticipation array
\(a^r\in\mathcal{A}(M)\) such that
\[
  \sum_{h,s,x}c^{(w)}_{h,s}(x)a^r_{h,s}(x)=r.
\]
By Assumption~\ref{ass:box-independence}, this array is compatible with some
full potential-outcome law preserving \(P\) and the maintained restrictions.
For that law, Theorem~\ref{thm:linear-contamination} gives
\(\theta_w=\delta_w(P)+r\).  Since \(r\) ranges over the whole support interval,
every point in \([\theta_L^w(P),\theta_U^w(P)]\) is in
\(\Theta_I^w(P)\).  Combining this reverse containment with the first one proves
equality and confirms Conjecture 1.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:zero-bound-recovery}]
If \(M_{h,s}(x)=0\) for every coordinate with nonzero pooled coefficient, then
\(\sum_{h,s,x}|c^{(w)}_{h,s}(x)|M_{h,s}(x)=0\).  The endpoints in Section~7 are
both \(\delta_w(P)\), and Theorem~\ref{thm:sharp-box-stage0} gives
\(\Theta_I^w(P)=\{\delta_w(P)\}\).  In the clean-horizon singleton case,
\(b<g-k\) sets \(M_{g,b}(x)=0\), and \(h-t>k\) plus \(h-b>k\) sets the comparison
anticipation radii to zero.  The remaining identity is the standard conditional
DID point formula under conditional baseline parallel trends.
\end{proof}

\section{Sanity checks}
\begin{itemize}[leftmargin=*]
  \item \textbf{No anticipation.}  If \(k=0\), or if all nonzero-coefficient
  coordinates have \(M_{h,s}(x)=0\), the interval has zero width and
  \(\theta_w=\delta_w(P)\).  This is Proposition~\ref{prop:zero-bound-recovery}.

  \item \textbf{Clean never-treated controls.}  If the singleton target uses
  \(R_j=\{\infty\}\) and \(b_j<g_j-k\), then \(a_{g_j,b_j}(x)=0\) and the
  never-treated comparison has no anticipation coordinate.  The formula reduces
  to the usual two-period conditional DID expression.

  \item \textbf{One contaminated treated base period.}  If \(R_j=\{\infty\}\) but
  \(g_j-k\le b_j<g_j\), then the only latent coordinate is \(a_{g_j,b_j}(x)\).
  The singleton interval is
  \[
    \E[\Delta_j(X)\mid G=g_j]
    \pm
    \E[M_{g_j,b_j}(X)\mid G=g_j].
  \]

  \item \textbf{Anticipatory not-yet-treated controls.}  If \(X\) is degenerate,
  \(R_j=\{h\}\), \(h>t_j\), \(h-t_j\le k\), \(h-b_j>k\), and \(g_j-b_j>k\), then
  \[
    ATT(g_j,t_j)=\Delta_j+a_{h,t_j},
  \]
  and the singleton interval is \([\Delta_j-M_{h,t_j},\Delta_j+M_{h,t_j}]\).
  This is the smallest case showing why untreated controls need not be
  unanticipated controls.

  \item \textbf{Aggregate coefficient pooling.}  Suppose two singleton targets
  share one anticipation coordinate with coefficients \(+1\) and \(-1\) and have
  equal aggregate weights.  The pooled coefficient is zero, so that coordinate
  does not widen the aggregate interval even though it widens each singleton
  interval.  This verifies the absolute-value-after-pooling rule.

  \item \textbf{Vacuous no-restriction corner.}  If the bounded-anticipation
  restriction is removed and no outcome-support restriction replaces it, the
  affected latent coordinates are unrestricted and the interval is all of
  \(\mathbb{R}\).  If instead one imposes only a bounded outcome support
  \(Y_s(h)\in[\underline y,\overline y]\), the same proof becomes the standard
  Manski worst-case completion, replacing each missing latent mean by its support
  endpoints.
\end{itemize}

\section{Counterexample or minimality check}
\begin{example}[Normalization is necessary]\label{ex:normalization}
Let \(X\) be degenerate, let there be no anticipation, and let the true target be
\(ATT(g,t)=0\).  Suppose two comparison cohorts have the same untreated trend as
the treated cohort, equal to \(1\), so conditional baseline parallel trends holds.
If a researcher used weights \(1\) and \(1\), whose sum is \(2\), then
\[
  \Delta=(0+1)-2\cdot 1=-1.
\]
The DID contrast would not equal the target even though no anticipation is
present.  The failure is exactly the missing normalization
\(\sum_h\omega_h=1\) in Assumption~\ref{ass:fixed-weights}.
\end{example}

\begin{example}[Variation independence is necessary for sharpness]\label{ex:box-independence}
Let the observable contrast be \(\delta_w(P)=0\) and let two latent anticipation
coordinates have coefficients \(+1\) and \(-1\), each with radius \(M>0\).  The
box-support formula gives the outer interval \([-2M,2M]\).  If a substantive
restriction not included in the proposal forced the two coordinates to be equal,
then the latent functional would be \(a_1-a_2=0\) for every compatible law, and
the true identified set would be the singleton \(\{0\}\).  Thus
Assumption~\ref{ass:box-independence} is the minimal condition turning the outer
box support into a sharp identified set.
\end{example}

These examples also describe the nearest correct weakenings.  Without normalized
weights, one must either renormalize the comparison contrast or add an explicit
baseline-trend remainder.  Without variation-independent boxes, the formula in
Section~7 remains a valid outer bound, but sharpness must be recomputed using the
smaller feasible set of anticipation arrays.

\section{Formalization checklist}
\paragraph{Probabilistic objects and assumptions.}
\begin{itemize}[leftmargin=*]
  \item Finite period set \(\{0,\ldots,T\}\), finite covariate support
  \(\mathcal{X}\), cohort set \(\{1,\ldots,T,\infty\}\), and finite target index
  set \(\mathcal{J}\).
  \item Observable law \(P\) of \((Y_0,\ldots,Y_T,G,X)\), with conditional cell
  probabilities \(\Pr(G=h,X=x)\) and \(\pi_j(x)=\Pr(X=x\mid G=g_j)\).
  \item Potential outcomes \(Y_s(h)\) for finite \(h\) and \(Y_s(\infty)\), with
  consistency and absorbing adoption.
  \item Conditional target \(ATT(g,t\mid x)\), marginal target \(ATT(g,t)\), and
  aggregate target \(\theta_w\).
  \item Anticipation coordinates \(a_{h,s}(x)\), radii \(M_{h,s}(x)\), and the
  product box \(\mathcal{A}(M)\).
  \item Conditional baseline parallel trends for \(Y(\infty)\), positive overlap
  on all used cells, fixed normalized comparison weights, and
  variation-independent compatibility of every array in \(\mathcal{A}(M)\).
\end{itemize}

\paragraph{Deterministic definitions and identities.}
\begin{itemize}[leftmargin=*]
  \item Observable DID contrast \(\Delta_j(x)\) and latent anticipation
  functional \(\Lambda_j(a)(x)\).
  \item Algebraic identity
  \(ATT(g_j,t_j\mid x)=\Delta_j(x)+\Lambda_j(a)(x)\), depending on consistency,
  baseline parallel trends, and normalized weights.
  \item Aggregate observable center \(\delta_w(P)\) and pooled coefficient
  \(c^{(w)}_{h,s}(x)\), obtained by collecting equal anticipation coordinates
  after summing over \(j\) and \(x\).
  \item Finite symmetric-box support identity:
  \(\{\sum_i c_i u_i:u_i\in[-M_i,M_i]\}
    =[-\sum_i|c_i|M_i,\sum_i|c_i|M_i]\).
  \item Containment proof:
  \(\Theta_I^w(P)\subseteq[\theta_L^w(P),\theta_U^w(P)]\) from the box support
  inequality.
  \item Sharpness proof: endpoint attainment and convex interpolation in the
  finite box, combined with variation-independent compatibility, gives the
  reverse containment.
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a sharp identified-set formula for staggered
DID group-time ATT targets under covariate-conditional bounded anticipation.  The
observable DID contrast is corrected by the support function of exactly those
anticipation coordinates that enter through the treated base period and the
not-yet-treated comparison cohorts.  Bounded anticipation tightens the interval;
variation-independent boxes make the support interval sharp.  The interval is
point-identifying when every nonzero pooled coordinate has zero radius, and it is
vacuous when the relevant latent coordinates are left unrestricted with no
alternative outcome-support bound.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AugustinGutknechtLiu2025}
Augustin, C., D. Gutknecht, and C. Liu (2025).
\newblock Staggered adoption DID designs with misclassification and anticipation.
\newblock arXiv preprint arXiv:2507.20415.

\bibitem{BorusyakJaravelSpiess2024}
Borusyak, K., X. Jaravel, and J. Spiess (2024).
\newblock Revisiting event-study designs: Robust and efficient estimation.
\newblock \emph{Review of Economic Studies} 91(6), 3253--3285.

\bibitem{CallawaySantAnna2021}
Callaway, B. and P. H. C. Sant'Anna (2021).
\newblock Difference-in-differences with multiple time periods.
\newblock \emph{Journal of Econometrics} 225(2), 200--230.

\bibitem{DCDH2020}
de Chaisemartin, C. and X. D'Haultfoeuille (2020).
\newblock Two-way fixed effects estimators with heterogeneous treatment effects.
\newblock \emph{American Economic Review} 110(9), 2964--2996.

\bibitem{GoodmanBacon2021}
Goodman-Bacon, A. (2021).
\newblock Difference-in-differences with variation in treatment timing.
\newblock \emph{Journal of Econometrics} 225(2), 254--277.

\bibitem{Manski1990}
Manski, C. F. (1990).
\newblock Nonparametric bounds on treatment effects.
\newblock \emph{American Economic Review, Papers and Proceedings} 80(2), 319--323.

\bibitem{Manski2003}
Manski, C. F. (2003).
\newblock \emph{Partial Identification of Probability Distributions}.
\newblock Springer.

\bibitem{ManskiPepper2018}
Manski, C. F. and J. V. Pepper (2018).
\newblock How do right-to-carry laws affect crime rates? Coping with ambiguity using bounded-variation assumptions.
\newblock \emph{Review of Economics and Statistics} 100(2), 232--244.

\bibitem{PiccininniTchetgenStensrud2025}
Piccininni, M., E. J. Tchetgen Tchetgen, and M. J. Stensrud (2025).
\newblock Refining the notion of no anticipation in difference-in-differences studies.
\newblock arXiv preprint arXiv:2507.12891.

\bibitem{RambachanRoth2023}
Rambachan, A. and J. Roth (2023).
\newblock A more credible approach to parallel trends.
\newblock \emph{Review of Economic Studies} 90(5), 2555--2591.

\bibitem{RothSantAnnaBilinskiPoe2023}
Roth, J., P. H. C. Sant'Anna, A. Bilinski, and J. Poe (2023).
\newblock What's trending in difference-in-differences? A synthesis of the recent econometrics literature.
\newblock \emph{Journal of Econometrics} 235(2), 2218--2244.

\bibitem{SunAbraham2021}
Sun, L. and S. Abraham (2021).
\newblock Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\newblock \emph{Journal of Econometrics} 225(2), 175--199.
\end{thebibliography}

\end{document}
