\documentclass{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{mathrsfs,bm,bbm}
\usepackage{graphicx,booktabs,array,multirow,tabularx,longtable}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm,algpseudocode}
\usepackage{subcaption,tikz}
\usepackage{siunitx,cancel,accents}
\usepackage{microtype}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{cleveref}
\setlength{\emergencystretch}{2em}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\sloppy

\section*{stat\_\allowbreak{}optimal\_\allowbreak{}value\_\allowbreak{}honest\_\allowbreak{}adaptation}

\noindent\textit{Specialization:} binary\_\allowbreak{}optimal\_\allowbreak{}value\_\allowbreak{}sparse\_\allowbreak{}neartie\_\allowbreak{}adaptation\par

\paragraph{TL;DR.} The proposal fixes a two-stratum randomized causal union before sampling: an exact-tie Hölder stratum and a rougher margin-constrained near-tie stratum. The ordinary tie-only oracle has root-\(n\) interval length. The focal theorem target constructs a sparse randomized-sign full-data near-tie mixture in the second stratum whose product chi-square distance from an exact-tie law remains bounded while its optimal-value separation is \(n^{-\xi}\). When \(3s_1\alpha<d\), this yields a strictly slower expected-length lower bound at an exact-tie law. At equality the displayed family has root-\(n\) order, and above it the family is nonbinding. Ponomarev--Semenova's one-sided non-uniqueness-robust bands and Liu--Liu--Sasaki--Wan's Gaussian inference under distinct representative-policy assumptions do not supply this two-sided sparse-mixture lower bound. Cai--Low's testing reduction is supporting machinery; a matching connected union interval and any stronger obstruction remain open.

\section{Project justification}

\paragraph{Gap.} Existing work provides smoothing, subagging, exceptional-law methods, one-sided bands robust to non-uniqueness, or Gaussian inference under distinct representative-policy assumptions, but not the displayed sparse causal mixture and its two-sided union-honest expected-length cost. Cai--Low supply the general testing reduction, not this causal construction. Armstrong--Kolesar show why an honest upper construction must explicitly pay worst-case bias.

\paragraph{Niche.} The kernel isolates an ordered pair for which the oracle exact-tie problem is root-\(n\) and, in the explicit regime \(3s_1\alpha<d\), a union-honest interval faces a slower, parameterized sparse-near-tie lower bound.

\paragraph{Fill.} It supplies dominated full-data laws, verifies their observed images and product testing distance, and states the lower bound as the focal theorem target; a multiscale union-calibrated upper construction is retained only as an open handle.

\section{Related work}

Luedtke and van der Laan \cite{LuedtkeVanderLaan2016} characterize exceptional-law nonregularity and develop optimal-value inference under sufficient conditions. Wu and Wang \cite{WuWang2021} give smoothed robust and resampling-based optimal-regime inference. Shi, Lu, and Song \cite{ShiLuSong2020} develop nominal-coverage subagging intervals and compare average lengths. Xu and Guo \cite{XuGuo2026} study adaptive smoothing and a variance bound within a restricted robust asymptotically linear unbiased class. Whitehouse, Chen, Austern, and Syrgkanis \cite{WhitehouseAusternSyrgkanis2025} develop constant-fit softmax inference for optimal-policy values. Ponomarev and Semenova \cite{PonomarevSemenova2024} provide one-sided lower confidence bands robust to non-unique policies through moment-inequality tests, not a connected two-sided interval uniformly asymptotically honest over the displayed ordered union or its sparse-mixture expected-length penalty. Liu, Liu, Sasaki, and Wan \cite{LiuLiuSasakiWan2025} give Gaussian optimal-policy-value inference using a strictly convex surrogate under distinct representative-policy assumptions, not the exact-tie ordered union or its two-sided union-honest expected-length lower bound. Cai and Low \cite{CaiLow2004} provide the standard testing-to-interval-length reduction used here as supporting machinery, while the causal sparse mixture is the proposed contribution. Armstrong and Kolesar \cite{ArmstrongKolesar2020} construct bias-aware honest intervals under predeclared smoothness restrictions and explain why data-driven adaptation needs explicit bias protection; the present finite two-stratum union neither evades that warning nor claims an upper interval before it is proved. Audibert and Tsybakov \cite{AudibertTsybakov2007} provide margin and Hölder geometry for the sparse family. Liu, Zhang, Nie, and Soon \cite{LiuZhangNieSoon2017} provide the rilpivirine-versus-efavirenz optimized-regime consumer setting. None of these sources establishes one connected interval uniformly asymptotically honest over this displayed ordered causal union together with its sparse-mixture expected-length penalty.

\section{Setup}

Target (estimand / structural parameter): \(V(P)=E_P[\max\{m_{P,0}(X),m_{P,1}(X)\}]\).
Primary functional / estimator / diagnostic: \(\delta_n=a_nN_nh_n^d\int_{[0,1]^d}\psi(z)dz/2\asymp n^{-2s_1(\alpha+1)/(d+s_1\alpha+4s_1)}\).
\begin{itemize}
  \item \texttt{n} --- \texttt{sample\_\allowbreak{}size}; \(\mathbb N\); \texttt{index}
  \par\smallskip\noindent\emph{Definition.} \texttt{Sample size.}
  \item \texttt{d} --- \texttt{covariate\_\allowbreak{}dimension}; \(\mathbb N\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Covariate dimension.}
  \item \texttt{B} --- \texttt{outcome\_\allowbreak{}bound}; \((0,\infty)\); \texttt{constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Known outcome bound.}
  \item \texttt{v\_\allowbreak{}0} --- \texttt{variance\_\allowbreak{}floor}; \((0,B^2)\); \texttt{constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Known conditional-\allowbreak{}variance floor.}
  \item \texttt{\textbackslash{}\allowbreak{}bar B} --- \texttt{mean\_\allowbreak{}envelope}; \((0,B)\); \texttt{derived\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \(\bar B=\sqrt{B^2-v_0}\).
  \item \texttt{\textbackslash{}\allowbreak{}mathcal X} --- \texttt{covariate\_\allowbreak{}space}; \([0,1]^d\); \texttt{sample\_\allowbreak{}space}
  \par\smallskip\noindent\emph{Definition.} \texttt{Covariate support.}
  \item \texttt{\textbackslash{}\allowbreak{}lambda\_\allowbreak{}d} --- \texttt{Lebesgue\_\allowbreak{}measure}; \(\mathcal X\); \texttt{measure}
  \par\smallskip\noindent\emph{Definition.} Lebesgue measure restricted to \(\mathcal X\).
  \item \texttt{\textbackslash{}\allowbreak{}kappa\_\allowbreak{}B} --- \texttt{outcome\_\allowbreak{}measure}; \([-B,B]\); \texttt{measure}
  \par\smallskip\noindent\emph{Definition.} \(\kappa_B=\lambda_{[-B,B]}+\delta_{-B}+\delta_B\).
  \item \texttt{X} --- \texttt{covariate}; \(\mathcal X\); \texttt{causal\_\allowbreak{}primitive}
  \par\smallskip\noindent\emph{Definition.} \texttt{Baseline covariate.}
  \item \texttt{A} --- \texttt{treatment}; \(\{0,1\}\); \texttt{causal\_\allowbreak{}primitive}
  \par\smallskip\noindent\emph{Definition.} \texttt{Binary treatment.}
  \item \texttt{Y(a)} --- \texttt{potential\_\allowbreak{}outcome}; \([-B,B]\); \texttt{causal\_\allowbreak{}primitive}
  \par\smallskip\noindent\emph{Definition.} Potential outcome under \(a\in\{0,1\}\).
  \item \texttt{Y} --- \texttt{observed\_\allowbreak{}outcome}; \([-B,B]\); \texttt{data\_\allowbreak{}component}
  \par\smallskip\noindent\emph{Definition.} Observed outcome \(Y=Y(A)\).
  \item \texttt{W} --- \texttt{full\_\allowbreak{}data\_\allowbreak{}unit}; \(\mathcal X\times\{0,1\}\times[-B,B]^2\); \texttt{data\_\allowbreak{}unit}
  \par\smallskip\noindent\emph{Definition.} \(W=(X,A,Y(0),Y(1))\).
  \item \texttt{F} --- \texttt{full\_\allowbreak{}data\_\allowbreak{}law}; \(\mathcal P(\mathcal X\times\{0,1\}\times[-B,B]^2)\); \texttt{causal\_\allowbreak{}model}
  \par\smallskip\noindent\emph{Definition.} Law of \(W\).
  \item \texttt{\textbackslash{}\allowbreak{}nu} --- \texttt{full\_\allowbreak{}data\_\allowbreak{}dominating\_\allowbreak{}measure}; \(\lambda_d\otimes\#_{\{0,1\}}\otimes\kappa_B\otimes\kappa_B\); \texttt{measure}
  \par\smallskip\noindent\emph{Definition.} \texttt{Common dominating measure for the full-\allowbreak{}data classes.}
  \item \texttt{T} --- \texttt{observation\_\allowbreak{}map}; \(T(x,a,y_0,y_1)=(x,a,y_a)\); \texttt{observation\_\allowbreak{}map}
  \par\smallskip\noindent\emph{Definition.} \texttt{Measurable observation map.}
  \item \texttt{O} --- \texttt{observed\_\allowbreak{}data\_\allowbreak{}unit}; \(\mathcal O=\mathcal X\times\{0,1\}\times[-B,B]\); \texttt{data\_\allowbreak{}unit}
  \par\smallskip\noindent\emph{Definition.} \(O=T(W)=(X,A,Y(A))\).
  \item \texttt{O\_\allowbreak{}i} --- \texttt{sample\_\allowbreak{}element}; \(\mathcal O\); \texttt{data}
  \par\smallskip\noindent\emph{Definition.} Observed unit \(i\), with treatment and outcome components \(A_i\) and \(Y_i\).
  \item \texttt{\textbackslash{}\allowbreak{}mu} --- \texttt{observed\_\allowbreak{}data\_\allowbreak{}dominating\_\allowbreak{}measure}; \(\lambda_d\otimes\#_{\{0,1\}}\otimes\kappa_B\); \texttt{measure}
  \par\smallskip\noindent\emph{Definition.} \texttt{Common dominating measure for observed-\allowbreak{}data laws.}
  \item \texttt{P} --- \texttt{observed\_\allowbreak{}data\_\allowbreak{}law}; \(\mathcal P(\mathcal O)\); \texttt{model}
  \par\smallskip\noindent\emph{Definition.} \(P=T_\#F\).
  \item \texttt{P\_\allowbreak{}X} --- \texttt{covariate\_\allowbreak{}marginal}; \(\mathcal P(\mathcal X)\); \texttt{nuisance\_\allowbreak{}law}
  \par\smallskip\noindent\emph{Definition.} Covariate marginal of \(P\).
  \item \texttt{g\_\allowbreak{}P} --- \texttt{design\_\allowbreak{}density}; \(\mathcal X\to[0,\infty)\); \texttt{nuisance}
  \par\smallskip\noindent\emph{Definition.} A fixed Borel version of \(dP_X/d\lambda_d\).
  \item \texttt{e\_\allowbreak{}P} --- \texttt{propensity\_\allowbreak{}score}; \(\mathcal X\to[0,1]\); \texttt{nuisance}
  \par\smallskip\noindent\emph{Definition.} A fixed Borel version of \(P(A=1\mid X=\cdot)\).
  \item \texttt{m\_\allowbreak{}\{P,\allowbreak{}a\}\allowbreak{}} --- \texttt{outcome\_\allowbreak{}regression}; \(\mathcal X\to[-\bar B,\bar B]\); \texttt{nuisance}
  \par\smallskip\noindent\emph{Definition.} A fixed Borel version of \(E_P[Y\mid A=a,X=\cdot]\), for \(a\in\{0,1\}\).
  \item \texttt{\textbackslash{}\allowbreak{}Delta\_\allowbreak{}P} --- \texttt{blip\_\allowbreak{}function}; \(\Delta_P=m_{P,1}-m_{P,0}\); \texttt{boundary\_\allowbreak{}geometry}
  \par\smallskip\noindent\emph{Definition.} \texttt{Treatment contrast.}
  \item \texttt{V(P)} --- \texttt{causal\_\allowbreak{}estimand}; \(\mathbb R\); \texttt{target\_\allowbreak{}estimand}
  \par\smallskip\noindent\emph{Definition.} \(V(P)=E_P[\max\{m_{P,0}(X),m_{P,1}(X)\}]\).
  \item \texttt{s\_\allowbreak{}0} --- \texttt{tie\_\allowbreak{}smoothness}; \((0,\infty)\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Hölder smoothness of the exact-\allowbreak{}tie stratum.}
  \item \texttt{L\_\allowbreak{}0} --- \texttt{tie\_\allowbreak{}radius}; \((0,\infty)\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Hölder radius of the exact-\allowbreak{}tie stratum.}
  \item \texttt{s\_\allowbreak{}1} --- \texttt{near\_\allowbreak{}tie\_\allowbreak{}smoothness}; \((0,\infty)\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Hölder smoothness of the near-\allowbreak{}tie stratum.}
  \item \texttt{L\_\allowbreak{}1} --- \texttt{near\_\allowbreak{}tie\_\allowbreak{}radius}; \((0,\infty)\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Hölder radius of the near-\allowbreak{}tie stratum.}
  \item \texttt{\textbackslash{}\allowbreak{}alpha} --- \texttt{margin\_\allowbreak{}exponent}; \((0,\infty)\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Margin exponent of the near-\allowbreak{}tie stratum.}
  \item \texttt{C} --- \texttt{margin\_\allowbreak{}constant}; \((0,\infty)\); \texttt{regularity\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Margin constant of the near-\allowbreak{}tie stratum.}
  \item \texttt{\textbackslash{}\allowbreak{}beta} --- \texttt{bump\_\allowbreak{}boundary\_\allowbreak{}power}; \((s_1,1/\alpha)\); \texttt{construction\_\allowbreak{}parameter}
  \par\smallskip\noindent\emph{Definition.} \texttt{Fixed boundary power used in the sparse near-\allowbreak{}tie bump.}
  \item \texttt{\textbackslash{}\allowbreak{}mathcal F\_\allowbreak{}0} --- \texttt{exact\_\allowbreak{}tie\_\allowbreak{}full\_\allowbreak{}data\_\allowbreak{}class}; \(\mathcal P(\mathcal X\times\{0,1\}\times[-B,B]^2)\); \texttt{model\_\allowbreak{}class}
  \par\smallskip\noindent\emph{Definition.} \texttt{Full-\allowbreak{}data exact-\allowbreak{}tie stratum.}
  \item \texttt{\textbackslash{}\allowbreak{}mathcal F\_\allowbreak{}1} --- \texttt{near\_\allowbreak{}tie\_\allowbreak{}full\_\allowbreak{}data\_\allowbreak{}class}; \(\mathcal P(\mathcal X\times\{0,1\}\times[-B,B]^2)\); \texttt{model\_\allowbreak{}class}
  \par\smallskip\noindent\emph{Definition.} \texttt{Full-\allowbreak{}data margin stratum.}
  \item \texttt{\textbackslash{}\allowbreak{}mathcal P\_\allowbreak{}0} --- \texttt{exact\_\allowbreak{}tie\_\allowbreak{}observed\_\allowbreak{}class}; \(\mathcal P(\mathcal O)\); \texttt{model\_\allowbreak{}class}
  \par\smallskip\noindent\emph{Definition.} \(\mathcal P_0=\{T_\#F:F\in\mathcal F_0\}\).
  \item \texttt{\textbackslash{}\allowbreak{}mathcal P\_\allowbreak{}1} --- \texttt{near\_\allowbreak{}tie\_\allowbreak{}observed\_\allowbreak{}class}; \(\mathcal P(\mathcal O)\); \texttt{model\_\allowbreak{}class}
  \par\smallskip\noindent\emph{Definition.} \(\mathcal P_1=\{T_\#F:F\in\mathcal F_1\}\).
  \item \texttt{\textbackslash{}\allowbreak{}mathcal U} --- \texttt{union\_\allowbreak{}model}; \(\mathcal P(\mathcal O)\); \texttt{adaptation\_\allowbreak{}domain}
  \par\smallskip\noindent\emph{Definition.} \(\mathcal U=\mathcal P_0\cup\mathcal P_1\).
  \item \texttt{\textbackslash{}\allowbreak{}gamma} --- \texttt{miscoverage\_\allowbreak{}level}; \((0,1/4)\); \texttt{inference\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Target miscoverage probability.}
  \item \texttt{C\_\allowbreak{}n} --- \texttt{generic\_\allowbreak{}interval}; \(2^{\mathbb R}\); \texttt{decision\_\allowbreak{}rule}
  \par\smallskip\noindent\emph{Definition.} A sample-measurable, almost surely finite connected closed interval \(C_n=[L_n,U_n]\) with \(L_n\le U_n\).
  \item \texttt{\textbackslash{}\allowbreak{}mathfrak C\textasciicircum{}\{\textbackslash{}\allowbreak{}mathrm\{asy\}\allowbreak{}\}\allowbreak{}(\textbackslash{}\allowbreak{}mathcal U,\allowbreak{}\textbackslash{}\allowbreak{}gamma)} --- \texttt{honest\_\allowbreak{}interval\_\allowbreak{}sequences}; \(2^{\{(C_n)_n\}}\); \texttt{decision\_\allowbreak{}class}
  \par\smallskip\noindent\emph{Definition.} Sequences satisfying \(\liminf_{n\to\infty}\inf_{P\in\mathcal U}P^n\{V(P)\in C_n\}\ge1-\gamma\).
  \item \texttt{a} --- \texttt{benchmark\_\allowbreak{}sequence}; \((0,\infty)^{\mathbb N}\); \texttt{frontier\_\allowbreak{}scale}
  \par\smallskip\noindent\emph{Definition.} Deterministic positive benchmark sequence \(a=(a_n)_n\).
  \item \texttt{\textbackslash{}\allowbreak{}mathfrak R\textasciicircum{}\{\textbackslash{}\allowbreak{}mathrm\{asy\}\allowbreak{}\}\allowbreak{}\_\allowbreak{}j(a)} --- \texttt{sequence\_\allowbreak{}minimax\_\allowbreak{}coefficient}; \([0,\infty]\); \texttt{frontier\_\allowbreak{}object}
  \par\smallskip\noindent\emph{Definition.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \mathfrak R^{\mathrm{asy}}_j(a)=\inf_{(C_n)_n\in\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)}\limsup_{n\to\infty}\sup_{P\in\mathcal P_j}E_{P^n}[\operatorname{length}(C_n)]/a_n\)}}\par\noindent, for \(j\in\{0,1\}\).
  \item \texttt{\textbackslash{}\allowbreak{}psi} --- \texttt{reference\_\allowbreak{}bump}; \(\psi(z)=\prod_{r=1}^d[4z_r(1-z_r)]^{\beta}\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}object}
  \par\smallskip\noindent\emph{Definition.} Boundary-vanishing reference bump on \( [0,1]^d\), extended by zero outside that cube.
  \item \texttt{D} --- \texttt{sparse\_\allowbreak{}mixture\_\allowbreak{}denominator}; \((0,\infty)\); \texttt{derived\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \(D=d+s_1\alpha+4s_1\).
  \item \texttt{c\_\allowbreak{}h} --- \texttt{cell\_\allowbreak{}width\_\allowbreak{}constant}; \((0,\infty)\); \texttt{calibration\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Fixed cell-\allowbreak{}width calibration constant.}
  \item \texttt{c\_\allowbreak{}a} --- \texttt{amplitude\_\allowbreak{}constant}; \((0,\infty)\); \texttt{calibration\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Fixed bump-\allowbreak{}amplitude calibration constant.}
  \item \texttt{c\_\allowbreak{}N} --- \texttt{cell\_\allowbreak{}count\_\allowbreak{}constant}; \((0,\infty)\); \texttt{calibration\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Fixed cell-\allowbreak{}count calibration constant.}
  \item \texttt{h\_\allowbreak{}n} --- \texttt{cell\_\allowbreak{}width}; \((0,1)\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}sequence}
  \par\smallskip\noindent\emph{Definition.} \(h_n=c_h n^{-2/D}\), where \(c_h>0\) is a fixed sufficiently small constant.
  \item \texttt{a\_\allowbreak{}n} --- \texttt{bump\_\allowbreak{}amplitude}; \((0,\infty)\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}sequence}
  \par\smallskip\noindent\emph{Definition.} \(a_n=c_a h_n^{s_1}\), where \(c_a>0\) is fixed.
  \item \texttt{N\_\allowbreak{}n} --- \texttt{number\_\allowbreak{}of\_\allowbreak{}cells}; \(\mathbb N\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}sequence}
  \par\smallskip\noindent\emph{Definition.} \(N_n=\lfloor c_N h_n^{s_1\alpha-d}\rfloor\), where \(c_N>0\) is fixed.
  \item \texttt{\textbackslash{}\allowbreak{}mathcal C\_\allowbreak{}n} --- \texttt{cell\_\allowbreak{}collection}; \(2^{\mathcal X}\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}object}
  \par\smallskip\noindent\emph{Definition.} The lexicographically first \(N_n\) pairwise disjoint cubes of side \(h_n\) lying in \( [1/4,3/4]^d\).
  \item \texttt{c\_\allowbreak{}\{\textbackslash{}\allowbreak{}ell,\allowbreak{}n\}\allowbreak{}} --- \texttt{cell\_\allowbreak{}corner}; \(\mathcal X\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}object}
  \par\smallskip\noindent\emph{Definition.} Lower-left corner of the \(\ell\)-th cube in \(\mathcal C_n\).
  \item \texttt{\textbackslash{}\allowbreak{}theta} --- \texttt{sign\_\allowbreak{}vector}; \(\{-1,1\}^{N_n}\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}index}
  \par\smallskip\noindent\emph{Definition.} \texttt{Rademacher sign vector indexing a sparse near-\allowbreak{}tie law.}
  \item \texttt{\textbackslash{}\allowbreak{}Delta\_\allowbreak{}\{\textbackslash{}\allowbreak{}theta,\allowbreak{}n\}\allowbreak{}} --- \texttt{sparse\_\allowbreak{}blip}; \(\Delta_{\theta,n}(x)=a_n\sum_{\ell=1}^{N_n}\theta_\ell\psi((x-c_{\ell,n})/h_n)\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}object}
  \par\smallskip\noindent\emph{Definition.} Sparse signed contrast on the cubes \(\mathcal C_n\).
  \item \texttt{F\_\allowbreak{}\{\textbackslash{}\allowbreak{}theta,\allowbreak{}n\}\allowbreak{}} --- \texttt{least\_\allowbreak{}favorable\_\allowbreak{}full\_\allowbreak{}data\_\allowbreak{}law}; \(\mathcal F_1\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}submodel}
  \par\smallskip\noindent\emph{Definition.} Full-data law constructed from \(\Delta_{\theta,n}\) in \(\mathrm{def:sparse-near-tie-family}\).
  \item \texttt{P\_\allowbreak{}\{\textbackslash{}\allowbreak{}theta,\allowbreak{}n\}\allowbreak{}} --- \texttt{least\_\allowbreak{}favorable\_\allowbreak{}observed\_\allowbreak{}law}; \(\mathcal P_1\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}submodel}
  \par\smallskip\noindent\emph{Definition.} \(P_{\theta,n}=T_\#F_{\theta,n}\).
  \item \texttt{P\_\allowbreak{}0\textasciicircum{}\textbackslash{}\allowbreak{}circ} --- \texttt{tie\_\allowbreak{}base\_\allowbreak{}law}; \(\mathcal P_0\); \texttt{least\_\allowbreak{}favorable\_\allowbreak{}submodel}
  \par\smallskip\noindent\emph{Definition.} Observed image of the zero-mean randomized Rademacher full-data law in \(\mathrm{def:base-law}\).
  \item \texttt{\textbackslash{}\allowbreak{}overline Q\_\allowbreak{}n} --- \texttt{fuzzy\_\allowbreak{}product\_\allowbreak{}alternative}; \(\mathcal P(\mathcal O^n)\); \texttt{testing\_\allowbreak{}object}
  \par\smallskip\noindent\emph{Definition.} \(\overline Q_n=2^{-N_n}\sum_{\theta\in\{-1,1\}^{N_n}}P_{\theta,n}^n\).
  \item \texttt{\textbackslash{}\allowbreak{}delta\_\allowbreak{}n} --- \texttt{mixture\_\allowbreak{}value\_\allowbreak{}separation}; \((0,\infty)\); \texttt{frontier\_\allowbreak{}scale}
  \par\smallskip\noindent\emph{Definition.} \(\delta_n=a_nN_nh_n^d\int_{[0,1]^d}\psi(z)dz/2\).
  \item \texttt{\textbackslash{}\allowbreak{}xi} --- \texttt{adaptation\_\allowbreak{}exponent}; \((0,\infty)\); \texttt{derived\_\allowbreak{}rate}
  \par\smallskip\noindent\emph{Definition.} \(\xi=2s_1(\alpha+1)/(d+s_1\alpha+4s_1)\).
  \item \texttt{\textbackslash{}\allowbreak{}varepsilon} --- \texttt{testing\_\allowbreak{}tolerance}; \((0,1-2\gamma)\); \texttt{calibration\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Fixed testing tolerance.}
  \item \texttt{K} --- \texttt{chi\_\allowbreak{}square\_\allowbreak{}constant}; \((0,\infty)\); \texttt{claim\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} \texttt{Finite constant in the sparse-\allowbreak{}mixture chi-\allowbreak{}square bound.}
  \item \texttt{c\_\allowbreak{}\{\textbackslash{}\allowbreak{}gamma,\allowbreak{}\textbackslash{}\allowbreak{}varepsilon\}\allowbreak{}} --- \texttt{length\_\allowbreak{}lower\_\allowbreak{}bound\_\allowbreak{}constant}; \((0,\infty)\); \texttt{claim\_\allowbreak{}constant}
  \par\smallskip\noindent\emph{Definition.} Positive constant depending only on \(\gamma\) and \(\varepsilon\).
  \item \texttt{\textbackslash{}\allowbreak{}widehat V\_\allowbreak{}\{0,\allowbreak{}n\}\allowbreak{}} --- \texttt{oracle\_\allowbreak{}tie\_\allowbreak{}estimator}; \(\mathbb R\); \texttt{estimator}
  \par\smallskip\noindent\emph{Definition.} \(\widehat V_{0,n}=2n^{-1}\sum_{i=1}^n1\{A_i=0\}Y_i\).
  \item \texttt{C\_\allowbreak{}\{0,\allowbreak{}n\}\allowbreak{}\textasciicircum{}\{\textbackslash{}\allowbreak{}mathrm\{or\}\allowbreak{}\}\allowbreak{}} --- \texttt{oracle\_\allowbreak{}tie\_\allowbreak{}interval}; \(2^{\mathbb R}\); \texttt{decision\_\allowbreak{}rule}
  \par\smallskip\noindent\emph{Definition.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle C_{0,n}^{\mathrm{or}}=[\widehat V_{0,n}-B\sqrt{8\log(2/\gamma)/n},\widehat V_{0,n}+B\sqrt{8\log(2/\gamma)/n}]\)}}\par\noindent.
  \item \texttt{C\_\allowbreak{}n\textasciicircum{}\textbackslash{}\allowbreak{}dagger} --- \texttt{candidate\_\allowbreak{}union\_\allowbreak{}interval}; \(2^{\mathbb R}\); \texttt{decision\_\allowbreak{}rule}
  \par\smallskip\noindent\emph{Definition.} \texttt{Connected interval sequence associated with the union-\allowbreak{}calibrated route.}
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:iid-sampling]\label{ass:iid-sampling}
\(O_1,\ldots,O_n\sim P^n\).
\par\smallskip\noindent\emph{Standard} (iid observed-data sampling, \cite{LuedtkeVanderLaan2016}).
\end{assumption}

\begin{assumption}[ass:consistency]\label{ass:consistency}
\(Y=Y(A)\) under \(F\).
\par\smallskip\noindent\emph{Standard} (consistency, \cite{LuedtkeVanderLaan2016}).
\end{assumption}

\begin{assumption}[ass:exchangeability]\label{ass:exchangeability}
\((Y(0),Y(1))\perp A\mid X\quad[F]\).
\par\smallskip\noindent\emph{Standard} (conditional exchangeability, \cite{LuedtkeVanderLaan2016}).
\end{assumption}

\begin{assumption}[ass:randomization]\label{ass:randomization}
\(e_P(x)=1/2\quad\lambda_d\text{-a.e.}\).
\par\smallskip\noindent\emph{Standard} (known randomized propensity, \cite{LuedtkeVanderLaan2016}).
\end{assumption}

\begin{assumption}[ass:bounded-outcomes]\label{ass:bounded-outcomes}
\(|Y(a)|\le B\quad F\text{-a.s.},\ a\in\{0,1\}\).
\par\smallskip\noindent\emph{Standard} (bounded potential outcomes, \cite{LuedtkeVanderLaan2016}).
\end{assumption}

\begin{assumption}[ass:variance-floor]\label{ass:variance-floor}
\(\operatorname{Var}_F(Y(a)\mid X)\ge v_0\quad F\text{-a.s.},\ a\in\{0,1\}\).
\par\smallskip\noindent\emph{Standard} (nondegenerate conditional variance, \cite{LuedtkeVanderLaan2016}).
\end{assumption}

\begin{assumption}[ass:bounded-density]\label{ass:bounded-density}
\(1/2\le g_P(x)\le3/2\quad\lambda_d\text{-a.e.}\).
\par\smallskip\noindent\emph{Standard} (strong density condition, \cite{AudibertTsybakov2007}).
\end{assumption}

\begin{assumption}[ass:holder-tie]\label{ass:holder-tie}
\(\max_{a\in\{0,1\}}\lVert m_{P,a}\rVert_{C^{s_0}(\mathcal X)}\le L_0\).
\par\smallskip\noindent\emph{Standard} (Hölder regression smoothness, \cite{AudibertTsybakov2007}).
\end{assumption}

\begin{assumption}[ass:holder-near-tie]\label{ass:holder-near-tie}
\(\max_{a\in\{0,1\}}\lVert m_{P,a}\rVert_{C^{s_1}(\mathcal X)}\le L_1\).
\par\smallskip\noindent\emph{Standard} (Hölder regression smoothness, \cite{AudibertTsybakov2007}).
\end{assumption}

\begin{assumption}[ass:exact-tie]\label{ass:exact-tie}
\(P_X\{\Delta_P(X)=0\}=1\).
\par\smallskip\noindent\emph{Novel.} An exact-treatment-response tie stratum describes settings in which either treatment has the same conditional mean for every baseline profile; it is a law-level benchmark for the exceptional boundary.
\end{assumption}

\begin{assumption}[ass:margin-near-tie]\label{ass:margin-near-tie}
\(P_X\{0<|\Delta_P(X)|\le u\}\le Cu^{\alpha}\quad\forall u\in(0,2\bar B]\).
\par\smallskip\noindent\emph{Standard} (Tsybakov margin condition with an allowed tie atom, \cite{AudibertTsybakov2007}).
\end{assumption}

\section{Definitions}

\begin{definition}[def:admissible-pair]\label{def:admissible-pair}
\par\smallskip\noindent\emph{Defined object.} \texttt{admissible ordered pair}
\par\smallskip\noindent\emph{Construction.} Write \(s=r+\tau\) with \(r=\lfloor s\rfloor\) and \(\tau\in[0,1)\); \(C^s(\mathcal X)\) has bounded continuous derivatives through order \(r\), with order-\(r\) derivatives \(\tau\)-Hölder when \(\tau>0\). Fix \(0<s_1<s_0\), \(L_0,L_1>0\), and \(\alpha,C>0\) satisfying \(s_1\alpha<1\), and choose \(\beta\in(s_1,1/\alpha)\).
\par\smallskip\noindent\emph{Inputs.} \texttt{s\_\allowbreak{}0}; \texttt{s\_\allowbreak{}1}; \texttt{L\_\allowbreak{}0}; \texttt{L\_\allowbreak{}1}; \texttt{\textbackslash{}\allowbreak{}alpha}; \texttt{C}; \texttt{d}; \texttt{\textbackslash{}\allowbreak{}beta}.
\end{definition}

\begin{definition}[def:exact-tie-stratum]\label{def:exact-tie-stratum}
\par\smallskip\noindent\emph{Defined object.} \(\mathcal F_0\)
\par\smallskip\noindent\emph{Construction.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \mathcal F_0=\{F\ll\nu:F\text{ satisfies }\mathrm{ass:consistency},\mathrm{ass:exchangeability},\mathrm{ass:randomization},\mathrm{ass:bounded-outcomes},\mathrm{ass:variance-floor},\mathrm{ass:bounded-density},\mathrm{ass:holder-tie},\mathrm{ass:exact-tie}\}\)}}\par\noindent.
\par\smallskip\noindent\emph{Member properties.} \texttt{ass:\allowbreak{}consistency}; \texttt{ass:\allowbreak{}exchangeability}; \texttt{ass:\allowbreak{}randomization}; \texttt{ass:\allowbreak{}bounded-\allowbreak{}outcomes}; \texttt{ass:\allowbreak{}variance-\allowbreak{}floor}; \texttt{ass:\allowbreak{}bounded-\allowbreak{}density}; \texttt{ass:\allowbreak{}holder-\allowbreak{}tie}; \texttt{ass:\allowbreak{}exact-\allowbreak{}tie}.
\end{definition}

\begin{definition}[def:near-tie-stratum]\label{def:near-tie-stratum}
\par\smallskip\noindent\emph{Defined object.} \(\mathcal F_1\)
\par\smallskip\noindent\emph{Construction.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \mathcal F_1=\{F\ll\nu:F\text{ satisfies }\mathrm{ass:consistency},\mathrm{ass:exchangeability},\mathrm{ass:randomization},\mathrm{ass:bounded-outcomes},\mathrm{ass:variance-floor},\mathrm{ass:bounded-density},\mathrm{ass:holder-near-tie},\mathrm{ass:margin-near-tie}\}\)}}\par\noindent.
\par\smallskip\noindent\emph{Member properties.} \texttt{ass:\allowbreak{}consistency}; \texttt{ass:\allowbreak{}exchangeability}; \texttt{ass:\allowbreak{}randomization}; \texttt{ass:\allowbreak{}bounded-\allowbreak{}outcomes}; \texttt{ass:\allowbreak{}variance-\allowbreak{}floor}; \texttt{ass:\allowbreak{}bounded-\allowbreak{}density}; \texttt{ass:\allowbreak{}holder-\allowbreak{}near-\allowbreak{}tie}; \texttt{ass:\allowbreak{}margin-\allowbreak{}near-\allowbreak{}tie}.
\end{definition}

\begin{definition}[def:observed-strata]\label{def:observed-strata}
\par\smallskip\noindent\emph{Defined object.} \(\mathcal P_0,\mathcal P_1\)
\par\smallskip\noindent\emph{Construction.} \(\mathcal P_0=\{T_\#F:F\in\mathcal F_0\}\) and \(\mathcal P_1=\{T_\#F:F\in\mathcal F_1\}\).
\par\smallskip\noindent\emph{Inputs.} \texttt{T}; \texttt{\textbackslash{}\allowbreak{}mathcal F\_\allowbreak{}0}; \texttt{\textbackslash{}\allowbreak{}mathcal F\_\allowbreak{}1}.
\end{definition}

\begin{definition}[def:union-class]\label{def:union-class}
\par\smallskip\noindent\emph{Defined object.} \(\mathcal U\)
\par\smallskip\noindent\emph{Construction.} \(\mathcal U=\mathcal P_0\cup\mathcal P_1\).
\par\smallskip\noindent\emph{Inputs.} \texttt{\textbackslash{}\allowbreak{}mathcal P\_\allowbreak{}0}; \texttt{\textbackslash{}\allowbreak{}mathcal P\_\allowbreak{}1}.
\end{definition}

\begin{definition}[def:base-law]\label{def:base-law}
\par\smallskip\noindent\emph{Defined object.} \texttt{exact-\allowbreak{}tie base law}
\par\smallskip\noindent\emph{Construction.} Let \(X\sim\operatorname{Unif}(\mathcal X)\), let \(A\sim\operatorname{Bernoulli}(1/2)\) independently, and conditionally independently draw \(Y(0),Y(1)\in\{-B,B\}\) with conditional means zero.  Let \(P_0^\circ\) be its observed image.
\par\smallskip\noindent\emph{Inputs.} \texttt{X}; \texttt{A}; \texttt{Y(a)}; \texttt{B}; \texttt{T}; \texttt{P\_\allowbreak{}0\textasciicircum{}\textbackslash{}\allowbreak{}circ}.
\end{definition}

\begin{definition}[def:sparse-near-tie-family]\label{def:sparse-near-tie-family}
\par\smallskip\noindent\emph{Defined object.} \texttt{sparse randomized-\allowbreak{}sign near-\allowbreak{}tie family}
\par\smallskip\noindent\emph{Construction.} For each sufficiently large \(n\), use \(\mathcal C_n\) and \(\Delta_{\theta,n}\). Let \(X\sim\operatorname{Unif}(\mathcal X)\), let \(A\sim\operatorname{Bernoulli}(1/2)\) independently, set \(E_F[Y(1)\mid X=x]=\Delta_{\theta,n}(x)/2\) and \(E_F[Y(0)\mid X=x]=-\Delta_{\theta,n}(x)/2\), and conditionally independently draw \(Y(a)\in\{-B,B\}\) with the corresponding Rademacher probabilities.  The constants \(c_h,c_a,c_N\) are fixed small enough that every displayed mean lies in \([-\bar B,\bar B]\), every conditional variance is at least \(v_0\), and the Hölder and margin bounds hold.
\par\smallskip\noindent\emph{Inputs.} \texttt{\textbackslash{}\allowbreak{}mathcal C\_\allowbreak{}n}; \texttt{\textbackslash{}\allowbreak{}Delta\_\allowbreak{}\{\textbackslash{}\allowbreak{}theta,\allowbreak{}n\}\allowbreak{}}; \texttt{B}; \texttt{\textbackslash{}\allowbreak{}bar B}; \texttt{v\_\allowbreak{}0}; \texttt{L\_\allowbreak{}1}; \texttt{C}; \texttt{F\_\allowbreak{}\{\textbackslash{}\allowbreak{}theta,\allowbreak{}n\}\allowbreak{}}.
\end{definition}

\begin{definition}[def:sequence-frontier]\label{def:sequence-frontier}
\par\smallskip\noindent\emph{Defined object.} \texttt{sequence-\allowbreak{}level honest adaptation criterion}
\par\smallskip\noindent\emph{Construction.} For every positive deterministic \(a=(a_n)_n\), use \(\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\) and \(\mathfrak R^{\mathrm{asy}}_j(a)\) exactly as defined in the symbol table; honesty is a property of the entire interval sequence.
\par\smallskip\noindent\emph{Inputs.} \texttt{a}; \texttt{\textbackslash{}\allowbreak{}mathfrak C\textasciicircum{}\{\textbackslash{}\allowbreak{}mathrm\{asy\}\allowbreak{}\}\allowbreak{}(\textbackslash{}\allowbreak{}mathcal U,\allowbreak{}\textbackslash{}\allowbreak{}gamma)}; \texttt{\textbackslash{}\allowbreak{}mathfrak R\textasciicircum{}\{\textbackslash{}\allowbreak{}mathrm\{asy\}\allowbreak{}\}\allowbreak{}\_\allowbreak{}j(a)}.
\end{definition}

\begin{definition}[def:union-upper-route]\label{def:union-upper-route}
\par\smallskip\noindent\emph{Defined object.} \texttt{union-\allowbreak{}calibrated upper-\allowbreak{}construction handle}
\par\smallskip\noindent\emph{Construction.} Construct a connected interval by fitting multiscale contrast estimates on training folds, using independent holdout folds to form simultaneous confidence bounds for their dyadic block coefficients, and calibrating the final interval to the maximum smoothing and nuisance bias over both \(\mathcal F_0\) and \(\mathcal F_1\).
\par\smallskip\noindent\emph{Inputs.} \texttt{\textbackslash{}\allowbreak{}mathcal F\_\allowbreak{}0}; \texttt{\textbackslash{}\allowbreak{}mathcal F\_\allowbreak{}1}; \texttt{\textbackslash{}\allowbreak{}mathcal U}; \texttt{C\_\allowbreak{}n}.
\end{definition}

\section{Main results}

\begin{lemma}[lem:mean-envelope]\label{lem:mean-envelope}
Under \(\mathrm{ass:consistency}\), \(\mathrm{ass:exchangeability}\), \(\mathrm{ass:randomization}\), \(\mathrm{ass:bounded-outcomes}\), and \(\mathrm{ass:variance-floor}\), consistency, conditional exchangeability, and positivity from known randomization identify \(m_{P,a}(x)=E_F[Y(a)\mid X=x]\) for \(P_X\)-almost every \(x\) and each \(a\in\{0,1\}\); consequently \(|m_{P,a}(x)|\le\bar B=\sqrt{B^2-v_0}\) for \(P_X\)-almost every \(x\).
\end{lemma}
\begin{proof}
Fix \(a\in\{0,1\}\).  By consistency, on \(\{A=a\}\) one has \(Y=Y(a)\).  Conditional exchangeability and the positivity \(P(A=a\mid X)=1/2\) supplied by known randomization therefore give, for \(P_X\)-almost every \(x\),
\[
 m_{P,a}(x)=E_P[Y\mid A=a,X=x]
 =E_F[Y(a)\mid A=a,X=x]
 =E_F[Y(a)\mid X=x].
\]
This proves the asserted identification without defining the causal quantity to be the observed regression.

By bounded outcomes, \(E_F[Y(a)^2\mid X=x]\le B^2\).  The conditional variance identity and \(\mathrm{ass:variance-floor}\) now imply
\[
 v_0\le \operatorname{Var}_F(Y(a)\mid X=x)
 =E_F[Y(a)^2\mid X=x]-E_F[Y(a)\mid X=x]^2
 \le B^2-m_{P,a}(x)^2.
\]
Consequently \(m_{P,a}(x)^2\le B^2-v_0=\bar B^2\), and hence \(|m_{P,a}(x)|\le\bar B\), for \(P_X\)-almost every \(x\).
\end{proof}
\par\smallskip\noindent \textit{Justification.} Identification precedes the conditional second-moment calculation that yields the envelope. \textit{Gap.} Both identification and the envelope are standard supporting facts, not contributions. \textit{Consumer.} It supplies the outcome slack used by the sparse family.

\begin{lemma}[lem:nonempty-strata]\label{lem:nonempty-strata}
The base law in \(\mathrm{def:base-law}\) belongs to \(\mathcal F_0\).  For every admissible pair, the zero-contrast law also belongs to \(\mathcal F_1\); hence both observed-data strata and \(\mathcal U\) are nonempty.
\end{lemma}
\begin{proof}
Let \(F^\circ\) denote the full-data law specified in \(\mathrm{def:base-law}\). Because \(X\) is uniform on \(\mathcal X=[0,1]^d\), \(A\) has mass \(1/2\) at each point of \(\{0,1\}\), and each potential outcome is supported on the two atoms \(\{-B,B\}\), the product construction gives \(F^\circ\ll\nu\). Indeed, relative to the factors of \(\nu=\lambda_d\otimes\#_{\{0,1\}}\otimes\kappa_B\otimes\kappa_B\), the corresponding factor densities are respectively \(1\), \(1/2\), and, for each potential outcome, \(1/2\) on each of the atoms \(-B\) and \(B\) and zero elsewhere.

The observation map gives \(Y=Y(A)\), so consistency holds. The conditional mean-zero requirement and the support \(\{-B,B\}\) force
\[
F^\circ\{Y(a)=B\mid X,A\}=F^\circ\{Y(a)=-B\mid X,A\}=\frac12,
\qquad a\in\{0,1\}.
\]
Thus the conditional law of \((Y(0),Y(1))\) given \((X,A)\) does not depend on \(A\), which proves \((Y(0),Y(1))\perp A\mid X\). Independence of \(A\) and \(X\) gives \(e_{P_0^\circ}(x)=1/2\), while uniformity of \(X\) gives \(g_{P_0^\circ}(x)=1\), in each case for \(\lambda_d\)-almost every \(x\). Moreover, \(|Y(a)|=B\) almost surely and
\[
\operatorname{Var}_{F^\circ}(Y(a)\mid X)=B^2\ge v_0,
\]
where the last inequality follows from \(v_0\in(0,B^2)\).

For each \(a\in\{0,1\}\), consistency and the preceding conditional distribution yield
\[
m_{P_0^\circ,a}(x)=E_{P_0^\circ}[Y\mid A=a,X=x]=0
\]
for \(P_X\)-almost every \(x\). Hence \(\lVert m_{P_0^\circ,a}\rVert_{C^{s_0}(\mathcal X)}=0\le L_0\), and \(\Delta_{P_0^\circ}=0\) almost everywhere. All defining conditions in \(\mathrm{def:exact-tie-stratum}\) therefore hold, so \(F^\circ\in\mathcal F_0\).

Now fix any admissible pair from \(\mathrm{def:admissible-pair}\) and regard the same \(F^\circ\) as the zero-contrast law. The domination, consistency, exchangeability, randomization, boundedness, variance, and density calculations above are unchanged. Since the zero function belongs to every Hölder class with norm zero,
\[
\max_{a\in\{0,1\}}\lVert m_{P_0^\circ,a}\rVert_{C^{s_1}(\mathcal X)}=0\le L_1.
\]
For every \(u\in(0,2\bar B]\), the event \(\{0<|\Delta_{P_0^\circ}(X)|\le u\}\) is empty, and consequently
\[
P_X\{0<|\Delta_{P_0^\circ}(X)|\le u\}=0\le Cu^\alpha.
\]
Thus every defining condition in \(\mathrm{def:near-tie-stratum}\) holds and \(F^\circ\in\mathcal F_1\).

Finally, by \(\mathrm{def:observed-strata}\), the observed image \(P_0^\circ=T_\#F^\circ\) belongs to both \(\mathcal P_0\) and \(\mathcal P_1\). Hence both observed-data strata are nonempty, and therefore their union \(\mathcal U=\mathcal P_0\cup\mathcal P_1\) is nonempty.
\end{proof}
\par\smallskip\noindent \textit{Justification.} A union-honesty problem is meaningful only for compatible dominated full-data classes. \textit{Gap.} This is a model audit rather than a claimed advance over optimal-value procedures. \textit{Consumer.} It validates the ordered pair used in the lower-bound calculation.

\begin{proposition}[prop:oracle-tie-rootn]\label{prop:oracle-tie-rootn}
For every \(P\in\mathcal P_0\), \(E_P[\widehat V_{0,n}]=V(P)\), and \(P^n\{V(P)\in C_{0,n}^{\mathrm{or}}\}\ge1-\gamma\).  Consequently \(\sup_{P\in\mathcal P_0}E_{P^n}[\operatorname{length}(C_{0,n}^{\mathrm{or}})]=O(n^{-1/2})\).
\end{proposition}
\begin{proof}
Fix \(P\in\mathcal P_0\).  The exact-tie condition gives \(m_{P,1}(X)=m_{P,0}(X)\) almost surely, and thus
\[
 V(P)=E_P[\max\{m_{P,0}(X),m_{P,1}(X)\}]=E_P[m_{P,0}(X)].
\]
Randomization and iterated expectation yield
\[
 E_P[2\,1\{A=0\}Y\mid X]
 =2P(A=0\mid X)E_P[Y\mid A=0,X]
 =m_{P,0}(X).
\]
Averaging over \(X\) proves \(E_P[\widehat V_{0,n}]=V(P)\).

Set \(Z_i=2\,1\{A_i=0\}Y_i\).  Under iid sampling, \(Z_1,\ldots,Z_n\) are independent, have common mean \(V(P)\), and lie in \([-2B,2B]\).  Hoeffding's inequality, in its bounded-range form,
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle P^n\!\left\{\left|n^{-1}\sum_{i=1}^n Z_i-E_PZ_i\right|\ge t\right\}
 \le 2\exp\!\left\{-\frac{2n t^2}{(4B)^2}\right\}
 =2\exp\!\left\{-\frac{nt^2}{8B^2}\right\},\)}}
\]
with \(t=B\sqrt{8\log(2/\gamma)/n}\), gives
\[
 P^n\{V(P)\in C_{0,n}^{\mathrm{or}}\}\ge1-\gamma.
\]
Finally, the interval length is nonrandom and equals
\[
 2B\sqrt{8\log(2/\gamma)/n}.
\]
Taking the supremum over \(P\in\mathcal P_0\) proves the claimed \(O(n^{-1/2})\) bound.
\end{proof}
\par\smallskip\noindent \textit{Justification.} When the contrast is identically zero, the value is an ordinary randomized-arm mean. \textit{Gap.} This is the oracle benchmark, not a novelty claim; Luedtke--van der Laan already motivate regular versus exceptional optimal-value inference. \textit{Consumer.} It defines the root-\(n\) precision that union honesty may fail to retain at the exact-tie stratum.

\begin{lemma}[lem:sparse-family-membership]\label{lem:sparse-family-membership}
For all sufficiently large \(n\) and every \(\theta\in\{-1,1\}^{N_n}\), \(F_{\theta,n}\in\mathcal F_1\), \(P_{\theta,n}\in\mathcal P_1\), and \(V(P_{\theta,n})-V(P_0^\circ)=\delta_n\).  Moreover \(\delta_n\asymp n^{-\xi}\).
\end{lemma}
\begin{proof}
Write \(s=s_1\), let
\[
 J_1=\int_{[0,1]^d}\psi(z)\,dz>0,
 \qquad
 J_2=\int_{[0,1]^d}\psi(z)^2\,dz>0,
\]
and extend \(\psi\) by zero as in the symbol declaration.  Since \(\beta>s\), every derivative required by the definition of \(C^s\) vanishes continuously at the boundary of the cube, and the order-\(\lfloor s\rfloor\) derivatives have the required Hölder modulus.  Consequently there is a finite constant \(M_\psi\), depending only on \((d,s,\beta)\), such that for every \(h\in(0,1)\), every collection of disjoint cubes \(Q_\ell=c_\ell+h[0,1]^d\), and every signs \(\vartheta_\ell\in\{-1,1\}\),
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \left\|h^s\sum_\ell \vartheta_\ell
 \psi\!\left(\frac{\cdot-c_\ell}{h}\right)\right\|_{C^s(\mathcal X)}
 \le M_\psi.\)}}
\]
Indeed, scaling gives this bound within one cube.  Between two cubes, the boundary vanishing of all derivatives through order \(\lfloor s\rfloor\) bounds the cross-cube Hölder quotient by the same constant.  Disjointness ensures that no point receives two nonzero summands.

We next verify the margin inequality rather than treating it as part of the construction.  For \(z\in[0,1]\), put \(r(z)=2\min\{z,1-z\}\).  Then \(4z(1-z)\ge r(z)\), and \(r(Z)\) is uniform on \([0,1]\) when \(Z\) is uniform.  Iterated integration gives, for independent uniform \(R_1,\ldots,R_d\) and \(q\in(0,1]\),
\[
 \Pr\!\left\{\prod_{j=1}^dR_j\le q\right\}
 =q\sum_{k=0}^{d-1}\frac{\{\log(1/q)\}^k}{k!}.
\]
Because \(\alpha\beta<1\), the right-hand side at \(q=t^{1/\beta}\) is at most \(M_{\alpha,\beta,d}t^\alpha\), uniformly over \(t\in(0,1]\).  The same bound, after increasing the constant, is trivial for \(t\ge1\).  Hence
\[
 \lambda_d\{z\in(0,1)^d:0<\psi(z)\le t\}
 \le M_{\alpha,\beta,d}t^\alpha,
 \qquad t>0.
\]
Since the cubes are disjoint and \(X\) is uniform under the construction,
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \begin{aligned}
 P_X\{0<|\Delta_{\theta,n}(X)|\le u\}
 &=N_nh_n^d\lambda_d\{0<\psi\le u/a_n\}\\
 &\le M_{\alpha,\beta,d}N_nh_n^d(u/a_n)^\alpha\\
 &\le M_{\alpha,\beta,d}c_Nc_a^{-\alpha}u^\alpha.
 \end{aligned}\)}}
\]
Thus choosing the fixed calibration so that \(M_{\alpha,\beta,d}c_Nc_a^{-\alpha}\le C\) proves \(\mathrm{ass:margin-near-tie}\).

Now consider the full-data law in \(\mathrm{def:sparse-near-tie-family}\).  Uniform \(X\), randomized \(A\), and endpoint-supported potential outcomes give domination by \(\nu\), consistency under the observation map, and conditional exchangeability because \(A\) is independent of \((X,Y(0),Y(1))\).  They also give \(g_P=1\), \(e_P=1/2\), and bounded outcomes.  The observed regressions are
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle m_{P_{\theta,n},1}(x)=\frac{\Delta_{\theta,n}(x)}2,
 \qquad
 m_{P_{\theta,n},0}(x)=-\frac{\Delta_{\theta,n}(x)}2.\)}}
\]
The scaling bound above gives
\[
 \max_{a\in\{0,1\}}\|m_{P_{\theta,n},a}\|_{C^s(\mathcal X)}
 \le \frac{M_\psi c_a}{2}.
\]
Choose \(c_a\le2L_1/M_\psi\).  Also \(\|\Delta_{\theta,n}\|_\infty\le a_n\to0\), so eventually \(|\Delta_{\theta,n}|/2\le\bar B\).  For the endpoint Rademacher outcome with mean \((2a-1)\Delta_{\theta,n}(x)/2\),
\[
 \operatorname{Var}_F(Y(a)\mid X=x)
 =B^2-\frac{\Delta_{\theta,n}(x)^2}{4}
 \ge B^2-\bar B^2=v_0.
\]
All conditions defining \(\mathcal F_1\) now hold, so \(F_{\theta,n}\in\mathcal F_1\), and its observed image belongs to \(\mathcal P_1\).

The base law has both regressions equal to zero, hence \(V(P_0^\circ)=0\).  Under an alternative,
\[
 \max\{m_{P_{\theta,n},0}(x),m_{P_{\theta,n},1}(x)\}
 =\frac{|\Delta_{\theta,n}(x)|}{2}.
\]
The signs disappear after taking the absolute value, and a change of variables on every cube gives
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle V(P_{\theta,n})-V(P_0^\circ)
 =\frac12\int_{\mathcal X}|\Delta_{\theta,n}(x)|\,dx
 =\frac{a_nN_nh_n^dJ_1}{2}
 =\delta_n.\)}}
\]
Finally, \(s\alpha<1\le d\), so \(h_n^{s\alpha-d}\to\infty\) and
\[
 N_n\sim c_Nh_n^{s\alpha-d}.
\]
Therefore
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \delta_n\asymp h_n^s h_n^{s\alpha-d}h_n^d
 =h_n^{s(\alpha+1)}
 \asymp n^{-2s(\alpha+1)/(d+s\alpha+4s)}
 =n^{-\xi}.\)}}
\]
\end{proof}
\par\smallskip\noindent \textit{Justification.} The signed construction keeps the causal max functional positive while the signs conceal the alternatives from product testing. \textit{Gap.} Audibert--Tsybakov give classification-margin constructions, but not this full-data randomized causal max-functional family with an exact-tie oracle stratum. \textit{Consumer.} It supplies the explicit cross-stratum alternatives for the adaptation lower bound.

\begin{theorem}[thm:sparse-near-tie-adaptation-lower-bound]\label{thm:sparse-near-tie-adaptation-lower-bound}
For every admissible pair satisfying \(3s_1\alpha<d\), there are fixed admissible choices of \(c_h,c_a,c_N\) and \(\varepsilon\in(0,1-2\gamma)\) such that \(\chi^2(\overline Q_n,(P_0^\circ)^n)\le\exp\{K n^2N_na_n^4h_n^{2d}\}-1\le\varepsilon^2\) eventually.  Hence every \((C_n)_n\in\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\) obeys \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \liminf_{n\to\infty}E_{(P_0^\circ)^n}[\operatorname{length}(C_n)]/\delta_n\ge c_{\gamma,\varepsilon}>0\)}}\par\noindent.  Since \(3s_1\alpha<d\) gives \(\xi<1/2\), union honesty forces a strictly slower-than-root-\(n\) expected length at an exact-tie law even though \(\mathcal P_0\) alone admits \(O(n^{-1/2})\) length.
\end{theorem}
\begin{proof}
Let \(R_n=(P_0^\circ)^n\), and write \(L_{\theta,n}=dP_{\theta,n}/dP_0^\circ\) for the one-observation likelihood ratio.  Under the base law, conditional on \((X,A)\), the observed outcome is uniform on \(\{-B,B\}\).  Under \(P_{\theta,n}\), its conditional mean is \((2A-1)\Delta_{\theta,n}(X)/2\).  Hence
\[
 L_{\theta,n}(O)
 =1+\frac{(2A-1)Y\Delta_{\theta,n}(X)}{2B^2}.
\]
For two sign vectors \(\theta,\theta'\), independence and symmetry under the base law give
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle E_{P_0^\circ}[L_{\theta,n}L_{\theta',n}]
 =1+\frac1{4B^2}\int_{\mathcal X}
 \Delta_{\theta,n}(x)\Delta_{\theta',n}(x)\,dx
 =1+q_n\sum_{\ell=1}^{N_n}\theta_\ell\theta'_\ell,\)}}
\]
where
\[
 q_n=\frac{a_n^2h_n^dJ_2}{4B^2},
 \qquad
 J_2=\int_{[0,1]^d}\psi(z)^2\,dz.
\]
The cube supports are disjoint, which is exactly what removes all cross-cell integrals.

Squaring the mixture likelihood and using product sampling yields
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle 1+\chi^2(\overline Q_n,R_n)
 =2^{-2N_n}\sum_{\theta,\theta'}
 \left(1+q_n\sum_{\ell=1}^{N_n}\theta_\ell\theta'_\ell\right)^n.\)}}
\]
If \(R_1,\ldots,R_{N_n}\) are independent Rademacher variables, the right-hand side equals
\[
 E\left(1+q_n\sum_{\ell=1}^{N_n}R_\ell\right)^n.
\]
The inner factor is positive because it is an integral of a product of nonnegative likelihoods.  Using \(1+x\le e^x\) and \(\cosh t\le e^{t^2/2}\),
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \begin{aligned}
 1+\chi^2(\overline Q_n,R_n)
 &\le E\exp\!\left(nq_n\sum_{\ell=1}^{N_n}R_\ell\right)\\
 &=\{\cosh(nq_n)\}^{N_n}\\
 &\le\exp\!\left(\frac{N_nn^2q_n^2}{2}\right)\\
 &=\exp\!\left\{K n^2N_na_n^4h_n^{2d}\right\},
 \end{aligned}\)}}
\]
with \(K=J_2^2/(32B^4)\).  This proves the first displayed inequality in the theorem.

The calibration constraints used in the membership proof are compatible with the testing constraint.  Indeed,
\[
 n^2N_na_n^4h_n^{2d}
 \le c_Nc_a^4n^2h_n^{d+s_1\alpha+4s_1}
 =c_Nc_a^4c_h^{D}.
\]
Choose, for example, any fixed \(\varepsilon\in(0,1-2\gamma)\), then choose positive \(c_a,c_N,c_h\) small enough to satisfy the Hölder, margin, support, and variance calibrations in \(\mathrm{def:sparse-near-tie-family}\) and
\[
 Kc_Nc_a^4c_h^D\le\log(1+\varepsilon^2).
\]
The collection of \(N_n\) cubes exists eventually because \(N_nh_n^d\asymp h_n^{s_1\alpha}\to0\), whereas \([1/4,3/4]^d\) has fixed positive volume.  It follows that \(\chi^2(\overline Q_n,R_n)\le\varepsilon^2\) eventually.

It remains to transfer testing indistinguishability to interval length.  The base law satisfies the exact-tie conditions directly: its regressions vanish, its design density is one, its propensity is one half, and its conditional outcome variances equal \(B^2\).  Thus \(P_0^\circ\in\mathcal P_0\subset\mathcal U\).  By \(\mathrm{lem:sparse-family-membership}\), every alternative in the mixture belongs to \(\mathcal P_1\subset\mathcal U\), has value \(\delta_n\), and the base value is zero.

Fix any \((C_n)_n\in\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\).  Uniform asymptotic honesty gives a deterministic sequence \(r_n\downarrow0\) such that, eventually,
\[
 R_n\{0\in C_n\}\ge1-\gamma-r_n,
 \qquad
 \overline Q_n\{\delta_n\in C_n\}\ge1-\gamma-r_n.
\]
Cauchy--Schwarz gives the total-variation bound
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \sup_E|\overline Q_n(E)-R_n(E)|
 \le\frac12\left\{\chi^2(\overline Q_n,R_n)\right\}^{1/2}
 \le\frac\varepsilon2.\)}}
\]
Consequently
\[
 R_n\{0\in C_n,\ \delta_n\in C_n\}
 \ge1-2\gamma-2r_n-\frac\varepsilon2.
\]
Because \(C_n\) is connected, the event on the left forces \(\operatorname{length}(C_n)\ge\delta_n\).  Therefore
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \liminf_{n\to\infty}
 \frac{E_{R_n}[\operatorname{length}(C_n)]}{\delta_n}
 \ge1-2\gamma-\frac\varepsilon2
 =:c_{\gamma,\varepsilon}>0.\)}}
\]
Finally,
\[
 \xi-\frac12
 =\frac{3s_1\alpha-d}{2(d+s_1\alpha+4s_1)}.
\]
Thus \(3s_1\alpha<d\) implies \(\xi<1/2\) and
\[
 \frac{\delta_n}{n^{-1/2}}\asymp n^{1/2-\xi}\longrightarrow\infty.
\]
The lower bound is therefore strictly slower than root-\(n\) at \(P_0^\circ\), whereas \(\mathrm{prop:oracle-tie-rootn}\) supplies a root-\(n\) interval when only the exact-tie stratum must be covered.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This is the focal causal least-favorable calculation: a sparse randomized-sign mixture, not the routine Cai--Low two-point transfer, creates the strict adaptation penalty. \textit{Gap.} Cai--Low provide the standard expected-length testing reduction for Gaussian linear functionals; the new target is the explicit causal sparse near-tie mixture, its product chi-square calculation, and its strict cross-stratum penalty. Luedtke--van der Laan, Wu--Wang, Shi--Lu--Song, Xu--Guo, Whitehouse--Chen--Austern--Syrgkanis, Ponomarev--Semenova, and Liu--Liu--Sasaki--Wan do not give the displayed two-sided union-honest expected-length lower bound from this explicit dominated causal sparse randomized-sign mixture. \textit{Consumer.} It determines when a single interval for optimized rilpivirine-versus-efavirenz value must be wider at an exact biomarker-response tie than an oracle tie-only analysis.

\begin{lemma}[lem:local-polynomial-policy-regret]\label{lem:local-polynomial-policy-regret}
There is an explicit cellwise local-polynomial estimator, based on \(m\) iid training observations and smoothness \(s_1\), whose induced rule \(\widehat d_m(x)=1\{\widehat m_1(x)\ge\widehat m_0(x)\}\) satisfies
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \sup_{P\in\mathcal P_1}E_{P^m}\!\left[V(P)-E_P\{m_{P,\widehat d_m(X)}(X)\mid\widehat d_m\}\right]
 \le K m^{-s_1(\alpha+1)/(2s_1+d)}.\)}}
\]
The constant \(K\) depends only on the frozen class parameters.  For every \(P\in\mathcal P_0\), the regret inside the expectation is identically zero for every training realization.
\end{lemma}
\begin{proof}
Put \(s=s_1\), \(q=\lceil s\rceil-1\), and let \(\phi(u)=(u^k:|k|\le q)\) be the finite vector of tensor monomials on \([0,1]^d\).  Let
\[
 k_m=\left\lceil m^{1/(2s+d)}\right\rceil,
 \qquad h_m=k_m^{-1},
\]
and partition \(\mathcal X\) into the \(k_m^d\) cubes of side \(h_m\).  If \(Q\) has lower corner \(c_Q\), write \(\phi_Q(x)=\phi((x-c_Q)/h_m)\) on \(Q\).  For \(a\in\{0,1\}\), define
\[
 G_{a,Q}=\frac2m\sum_{i=1}^m1\{A_i=a,X_i\in Q\}\phi_Q(X_i)\phi_Q(X_i)^\top,
\]
\[
 H_{a,Q}=\frac2m\sum_{i=1}^m1\{A_i=a,X_i\in Q\}Y_i\phi_Q(X_i).
\]
Let \(M_\phi=\int_{[0,1]^d}\phi(u)\phi(u)^\top du\) and \(\lambda_\star=\lambda_{\min}(M_\phi)/4>0\).  If \(\lambda_{\min}(G_{a,Q})\ge\lambda_\star h_m^d\), set \(\widehat b_{a,Q}=G_{a,Q}^{-1}H_{a,Q}\); otherwise set \(\widehat b_{a,Q}=0\).  For \(x\in Q\), define \(\widehat m_a(x)\) by truncating \(\phi_Q(x)^\top\widehat b_{a,Q}\) to \([-\bar B,\bar B]\).  This is a completely sample-measurable estimator.

We first establish its pointwise tail bound uniformly over \(P\in\mathcal P_1\).  Randomization gives
\[
 E_PG_{a,Q}=\int_Qg_P(x)\phi_Q(x)\phi_Q(x)^\top dx.
\]
The density lower bound implies
\[
 \lambda_{\min}(E_PG_{a,Q})
 \ge\frac12h_m^d\lambda_{\min}(M_\phi)
 =2\lambda_\star h_m^d.
\]
For every \(m_{P,a}\in C^s(\mathcal X)\), Taylor's formula on a cube gives a polynomial \(p_{a,Q}\) of degree at most \(q\) satisfying
\[
 \sup_{x\in Q}|m_{P,a}(x)-p_{a,Q}(x)|\le K_1h_m^s.
\]
For integer \(s\), this is the degree-\((s-1)\) Taylor bound using the bounded order-\(s\) derivatives; for noninteger \(s\), it is the degree-\(\lfloor s\rfloor\) Taylor bound using the stated Hölder modulus.  The constants are uniform because the Hölder radius is \(L_1\).

Let \(b^*_{a,Q}\) be the population weighted least-squares coefficient.  The preceding approximation, the density bounds, and the population Gram lower bound imply
\[
 \sup_{x\in Q}|m_{P,a}(x)-\phi_Q(x)^\top b^*_{a,Q}|\le K_2h_m^s,
 \qquad \|b^*_{a,Q}\|\le K_2.
\]
For independent bounded variables, scalar Bernstein's inequality reads
\[
 \Pr\{|m^{-1}\textstyle\sum_{i=1}^m(Z_i-EZ_i)|>t\}
 \le2\exp\!\left\{-\frac{mt^2}{2(\sigma^2+Mt/3)}\right\}
\]
when \(|Z_i-EZ_i|\le M\) and \(\operatorname{Var}(Z_i)\le\sigma^2\).  Apply this inequality to the finitely many entries of \(G_{a,Q}\) and to the coordinates of
\[
 \frac2m\sum_{i=1}^m1\{A_i=a,X_i\in Q\}
 \phi_Q(X_i)\{Y_i-\phi_Q(X_i)^\top b^*_{a,Q}\}.
\]
Each summand is bounded by a class-dependent constant and has variance at most a constant times \(h_m^d\).  A finite-dimensional union bound, the population eigenvalue bound, and the inverse perturbation identity therefore give constants \(K_3,k_3>0\) such that, for every fixed \(x\in Q\),
\[
 P^m\{|\widehat m_a(x)-m_{P,a}(x)|>K_3(h_m^s+u)\}
 \le K_3\exp(-k_3mh_m^du^2)+K_3\exp(-k_3mh_m^d)
\]
for \(0<u\le1\).  Truncation cannot increase the error because the true regression lies in \([-\bar B,\bar B]\).

Set
\[
 r_m=h_m^s+(mh_m^d)^{-1/2}\asymp m^{-s/(2s+d)}.
\]
The last display and a union bound over the two arms imply, uniformly in \(x\), a sub-Gaussian bound for \(|\widehat\Delta(x)-\Delta_P(x)|/r_m\) on its bounded range.  If \(\widehat d_m(x)\) chooses the wrong sign and \(\Delta_P(x)\ne0\), then
\[
 |\widehat\Delta(x)-\Delta_P(x)|\ge|\Delta_P(x)|.
\]
Split the nonzero contrast range into \(0<|\Delta_P|\le K_4r_m\) and the dyadic shells
\[
 2^jK_4r_m<|\Delta_P|\le2^{j+1}K_4r_m,
 \qquad j\ge0.
\]
The first region contributes at most \(K r_m^{\alpha+1}\) by the margin condition.  On shell \(j\), the pointwise tail bound and the margin condition give a contribution at most
\[
 K r_m^{\alpha+1}2^{j(\alpha+1)}e^{-k4^j}.
\]
The series over \(j\) is finite; the exponentially small Gram-failure term is smaller than every fixed power of \(r_m\).  Fubini's theorem consequently yields
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \sup_{P\in\mathcal P_1}E_{P^m}
 E_{P_X}\!\left[|\Delta_P(X)|1\{\widehat d_m(X)\ne1\{\Delta_P(X)\ge0\}\}\mid\widehat d_m\right]
 \le K r_m^{\alpha+1}.\)}}
\]
The inner expectation is exactly the policy-value regret, with zero contribution from the tie set.  Since \(r_m^{\alpha+1}\asymp m^{-s(\alpha+1)/(2s+d)}\), the claimed near-tie bound follows.  On \(\mathcal P_0\), \(m_{P,0}=m_{P,1}\) almost surely, so every rule has the same value and the regret is identically zero.
\end{proof}

\begin{lemma}[lem:parametric-tie-length-lower-bound]\label{lem:parametric-tie-length-lower-bound}
There is a constant \(c_\gamma>0\) such that every \((C_n)_n\in\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\) satisfies
\[
 \liminf_{n\to\infty}n^{1/2}E_{(P_0^\circ)^n}[\operatorname{length}(C_n)]\ge c_\gamma.
\]
The base law \(P_0^\circ\) belongs to both \(\mathcal P_0\) and \(\mathcal P_1\), so this lower bound applies to both stratum-wise frontier criteria.
\end{lemma}
\begin{proof}
Choose a fixed \(t>0\), to be made small below, and put \(\mu_n=t/\sqrt n\).  Define a full-data law \(F_{t,n}\) exactly as in the base construction except that, conditionally independently for \(a\in\{0,1\}\), the endpoint-supported potential outcome has mean \(E[Y(a)\mid X]=\mu_n\).  Thus
\[
 F_{t,n}\{Y(a)=B\mid X\}=\frac{1+\mu_n/B}{2},
 \qquad
 F_{t,n}\{Y(a)=-B\mid X\}=\frac{1-\mu_n/B}{2}.
\]
For all sufficiently large \(n\), these laws are dominated by \(\nu\), have uniform design density and propensity one half, satisfy consistency and exchangeability, have constant regressions \(m_0=m_1=\mu_n\), and obey
\[
 \operatorname{Var}(Y(a)\mid X)=B^2-\mu_n^2\ge v_0.
\]
Their constant regression norms are eventually below both \(L_0\) and \(L_1\), and the margin event \(\{0<|\Delta|\le u\}\) is empty.  Hence their observed images \(P_{t,n}\) belong to both \(\mathcal P_0\) and \(\mathcal P_1\), while
\[
 V(P_{t,n})-V(P_0^\circ)=\mu_n.
\]

Under \(P_0^\circ\), the one-observation likelihood ratio is
\[
 \frac{dP_{t,n}}{dP_0^\circ}(O)=1+\frac{\mu_nY}{B^2}.
\]
Therefore
\[
 1+\chi^2(P_{t,n}^n,(P_0^\circ)^n)
 =\left(1+\frac{\mu_n^2}{B^2}\right)^n
 \le\exp(t^2/B^2).
\]
Choose \(t>0\) so small that
\[
 \rho_t:=\frac12\sqrt{e^{t^2/B^2}-1}<1-2\gamma.
\]
Then the total variation distance between the two product laws is at most \(\rho_t\).

For any union-honest interval sequence, uniform honesty applied to the base and the triangular sequence \(P_{t,n}\) gives coverage at least \(1-\gamma-r_n\) for some \(r_n\downarrow0\).  Transferring the alternative coverage event to the base law and intersecting it with base coverage yields
\[
 (P_0^\circ)^n\{0\in C_n,\ \mu_n\in C_n\}
 \ge1-2\gamma-2r_n-\rho_t.
\]
Connectedness forces length at least \(\mu_n\) on this event.  Consequently
\[
 \liminf_n n^{1/2}E_{(P_0^\circ)^n}[\operatorname{length}(C_n)]
 \ge t(1-2\gamma-\rho_t)=:c_\gamma>0.
\]
The final stratum-wise assertion follows from \(\mathrm{lem:nonempty-strata}\), which places \(P_0^\circ\) in both observed strata.
\end{proof}

\begin{theorem}[thm:split-sample-union-upper-bracket]\label{thm:split-sample-union-upper-bracket}
Let \(\eta=s_1(\alpha+1)/(2s_1+d)\).  There is an explicit split-sample local-polynomial interval sequence \((C_n^\dagger)_n\in\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\) such that
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \sup_{P\in\mathcal P_j}E_{P^n}[\operatorname{length}(C_n^\dagger)]
 \le K_\gamma\{n^{-1/2}+n^{-\eta}\},
 \qquad j\in\{0,1\}.\)}}
\]
The same interval is uniformly honest on the near-tie stratum.  For every admissible pair, \(s_1\alpha<d\) and hence \(\eta<\xi\); consequently this proved generic upper bound does not attain the sparse lower scale \(\delta_n\asymp n^{-\xi}\).
\end{theorem}
\begin{proof}
Use a deterministic split \(I_{\mathrm{tr}}\cup I_{\mathrm{ev}}=\{1,\ldots,n\}\), with both sizes asymptotic to \(n/2\).  On the training sample, form the explicit cellwise local-polynomial regressions \(\widehat m_0,\widehat m_1\) from \(\mathrm{lem:local-polynomial-policy-regret}\), and set
\[
 \widehat d(x)=1\{\widehat m_1(x)\ge\widehat m_0(x)\}.
\]
For a rule \(d\), write
\[
 V_P(d)=E_P[m_{P,d(X)}(X)],
 \qquad
 R_P(d)=V(P)-V_P(d)\ge0.
\]
The lemma gives a constant \(K_0\), uniform over \(P\in\mathcal P_1\), such that
\[
 E_{P^{|I_{\mathrm{tr}}|}}R_P(\widehat d)
 \le K_0|I_{\mathrm{tr}}|^{-\eta}.
\]
For \(P\in\mathcal P_0\), the exact tie gives \(R_P(d)=0\) for every measurable rule \(d\), so the same inequality is valid there.

On the independent evaluation sample define
\[
 \widehat V_n
 =\frac1{|I_{\mathrm{ev}}|}
 \sum_{i\in I_{\mathrm{ev}}}2\,1\{A_i=\widehat d(X_i)\}Y_i.
\]
Conditional on the training sample, randomization gives
\[
 E_P[\widehat V_n\mid I_{\mathrm{tr}}]=V_P(\widehat d).
\]
Each summand lies in \([-2B,2B]\).  Hence, with
\[
 t_n=B\sqrt{\frac{8\log(4/\gamma)}{|I_{\mathrm{ev}}|}},
\]
Hoeffding's inequality gives
\[
 P^n\{|\widehat V_n-V_P(\widehat d)|>t_n\mid I_{\mathrm{tr}}\}\le\frac\gamma2.
\]
Markov's inequality and the regret bound, with
\[
 b_n=\frac{2K_0}{\gamma}|I_{\mathrm{tr}}|^{-\eta},
\]
give \(P^n\{R_P(\widehat d)>b_n\}\le\gamma/2\), uniformly over \(P\in\mathcal U\).  Define the connected interval
\[
 C_n^\dagger=[\widehat V_n-t_n,\ \widehat V_n+t_n+b_n].
\]
On the intersection of the two preceding events,
\[
 \widehat V_n-t_n
 \le V_P(\widehat d)
 \le V(P)=V_P(\widehat d)+R_P(\widehat d)
 \le\widehat V_n+t_n+b_n.
\]
Therefore \(\inf_{P\in\mathcal U}P^n\{V(P)\in C_n^\dagger\}\ge1-\gamma\) for all sufficiently large \(n\), and the interval sequence belongs to \(\mathfrak C^{\mathrm{asy}}(\mathcal U,\gamma)\).  Its length is deterministic:
\[
 \operatorname{length}(C_n^\dagger)=2t_n+b_n
 \le K_\gamma\{n^{-1/2}+n^{-\eta}\}.
\]
This proves both displayed stratum-wise bounds.

Finally,
\[
 \xi-\eta
 =\frac{s_1(\alpha+1)(d-s_1\alpha)}
 {(d+s_1\alpha+4s_1)(2s_1+d)}.
\]
Admissibility gives \(s_1\alpha<1\le d\), so the numerator is positive.  Thus \(\eta<\xi\), which is the stated honest loose upper bracket rather than a matching \(O(\delta_n)\) conclusion.
\end{proof}

\begin{theorem}[thm:honest-adaptation-phase-bracket]\label{thm:honest-adaptation-phase-bracket}
Let \(\eta=s_1(\alpha+1)/(2s_1+d)\).  For both \(j\in\{0,1\}\), the honest expected-length frontier has the following proved phase diagram.  If \(3s_1\alpha<d\), then
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle 0<\mathfrak R_j^{\mathrm{asy}}((n^{-\xi})_n)
 \quad\text{and}\quad
 \mathfrak R_j^{\mathrm{asy}}((n^{-\eta})_n)<\infty.\)}}
\]
If \(3s_1\alpha\ge d\), then
\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle 0<\mathfrak R_j^{\mathrm{asy}}((n^{-1/2})_n)
 \quad\text{and}\quad
 \mathfrak R_j^{\mathrm{asy}}((n^{-\min\{1/2,\eta\}})_n)<\infty.\)}}
\]
In particular, when \(2s_1\alpha\ge d\), a root-\(n\) union-honest connected interval is attainable and the root-\(n\) order is minimax.  In the regimes \(3s_1\alpha<d\) and \(d/3\le s_1\alpha<d/2\), respectively, the proved lower and upper exponents do not coincide, so no matching-frontier conclusion follows from these bounds.
\end{theorem}
\begin{proof}
The upper theorem supplies one interval sequence honest over \(\mathcal U\) with expected length bounded, on both strata, by
\[
 K_\gamma\{n^{-1/2}+n^{-\eta}\}
 =O(n^{-\min\{1/2,\eta\}}).
\]
This gives every asserted finiteness conclusion.  In the low-margin regime \(3s_1\alpha<d\), one has \(\xi<1/2\) and \(\eta<\xi\), so the same upper bound is in particular \(O(n^{-\eta})\).

For the lower conclusions, \(\mathrm{lem:nonempty-strata}\) places \(P_0^\circ\) in both \(\mathcal P_0\) and \(\mathcal P_1\).  When \(3s_1\alpha<d\), \(\mathrm{thm:sparse-near-tie-adaptation-lower-bound}\) gives, for every honest interval sequence,
\[
 \liminf_n
 \frac{E_{(P_0^\circ)^n}[\operatorname{length}(C_n)]}{n^{-\xi}}>0.
\]
Since the supremum defining either stratum-wise criterion includes \(P_0^\circ\), taking first the stratum supremum and then the infimum over honest sequences proves
\[
 \mathfrak R_j^{\mathrm{asy}}((n^{-\xi})_n)>0,
 \qquad j\in\{0,1\}.
\]
For every admissible pair, \(\mathrm{lem:parametric-tie-length-lower-bound}\) similarly gives
\[
 \mathfrak R_j^{\mathrm{asy}}((n^{-1/2})_n)>0.
\]
This is the relevant lower bound when \(3s_1\alpha\ge d\), because the displayed sparse separation is then no larger than root-\(n\).

It remains only to identify when the upper exponent is root-\(n\).  Direct algebra gives
\[
 \eta-\frac12
 =\frac{2s_1\alpha-d}{2(2s_1+d)}.
\]
Thus \(2s_1\alpha\ge d\) is equivalent to \(\eta\ge1/2\).  In that regime the split-sample interval has \(O(n^{-1/2})\) length and the parametric lower bound proves minimax optimality.  If \(3s_1\alpha<d\), the available exponents satisfy \(\eta<\xi<1/2\).  If \(d/3\le s_1\alpha<d/2\), they satisfy \(\eta<1/2\) while the binding proved lower scale is only root-\(n\).  These strict inequalities establish the two stated nonmatching brackets without asserting that either gap is sharp.
\end{proof}

\section*{Technical internal limitation (diagnostic only)}

The proposed multiscale upper route has no established cross-stratum bias bound, so it is not a theorem-level construction. The lower bound uses a deliberately specified two-stratum subproblem: it is binding only when \(3s_1\alpha<d\), and it does not itself characterize every tie-mass, margin, and smoothness union.

\section{Honest scope}

The theorem target is the sparse causal mixture and its strict ordered-pair lower bound under \(3s_1\alpha<d\). At \(3s_1\alpha=d\), the displayed sparse separation has root-\(n\) order; above it, that separation is \(o(n^{-1/2})\) and is nonbinding against the tie-only oracle. The two-point expected-length reduction is standard Cai--Low machinery rather than a novelty claim. Attainment by a connected union-honest interval, a stronger obstruction in the nonbinding regimes, extension to arbitrary tie-mass bands, and the global adaptation diagram remain open. The two strata, their radii, the margin parameters, randomization, outcome bounds, and \(\gamma\) are fixed before sampling; unknown continuum smoothness adaptation and monotone coarsening are outside this core.

\begin{thebibliography}{99}

  \bibitem{LuedtkeVanderLaan2016} A. R. Luedtke and M. J. van der Laan (2016). Statistical inference for the mean outcome under a possibly non-unique optimal treatment strategy. \textit{Annals of Statistics} 44, 713--742. doi:10.1214/15-AOS1384.

  \bibitem{WuWang2021} P. Wu and L. Wang (2021). Inference for optimal treatment regimes. \textit{Biometrics} 77, 465--476. doi:10.1111/biom.13337.

  \bibitem{ShiLuSong2020} C. Shi, W. Lu, and R. Song (2020). Breaking the curse of nonregularity with subagging: Inference of the mean outcome under optimal treatment regimes. \textit{Journal of Machine Learning Research} 21(176), 1--67.

  \bibitem{XuGuo2026} S. Xu and X. Guo (2026). Optimal inference of the mean outcome under optimal treatment regime. \textit{arXiv:2509.09773}.

  \bibitem{WhitehouseAusternSyrgkanis2025} J. Whitehouse, Q. Chen, M. Austern, and V. Syrgkanis (2025). Inference on optimal policy values and other irregular functionals via softmax smoothing. \textit{arXiv:2507.11780}.

  \bibitem{PonomarevSemenova2024} K. Ponomarev and V. Semenova (2024). Inference on optimal welfare. \textit{arXiv:2410.07443}, revised September 2025.

  \bibitem{LiuLiuSasakiWan2025} R. Liu, Z. Liu, Y. Sasaki, and Y. Wan (2025). Nonparametric classification and policy value inference. \textit{arXiv:2511.14700}.

  \bibitem{CaiLow2004} T. T. Cai and M. G. Low (2004). An adaptation theory for nonparametric confidence intervals. \textit{Annals of Statistics} 32, 1805--1840. doi:10.1214/009053604000000049.

  \bibitem{ArmstrongKolesar2020} T. B. Armstrong and M. Kolesar (2020). Simple and honest confidence intervals in nonparametric regression. \textit{Quantitative Economics} 11, 1--39. doi:10.3982/QE1199.

  \bibitem{AudibertTsybakov2007} J.-Y. Audibert and A. B. Tsybakov (2007). Fast learning rates for plug-in classifiers. \textit{Annals of Statistics} 35, 608--633. doi:10.1214/009053606000001217.

  \bibitem{LiuZhangNieSoon2017} W. Liu, Z. Zhang, L. Nie, and G. Soon (2017). A case study in personalized medicine: Rilpivirine versus efavirenz for treatment-naive HIV patients. \textit{Journal of the American Statistical Association} 112, 1381--1392. doi:10.1080/01621459.2017.1280404.

\end{thebibliography}

\end{document}