% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=panel\_calendar\_snf\_alias, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{panel\_calendar\_snf\_alias} / \texttt{v1}%
  \\ \large\textit{A Smith-normal-form certificate for calendar-residue aliasing in event-study panels}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\texttt{qid} is \texttt{panel\_calendar\_snf\_alias}. \texttt{specialization} is \texttt{v1}. The anchor cluster is Panel. The panel has units $i=1,\ldots,n$, periods $t=0,\ldots,T-1$, and first-treatment dates $G_i\in\{0,\ldots,T-1,\infty\}$. The residue modulus is $m=4$ in the worked certificate and $m\geq 2$ in the family statement; $R_i=G_i\bmod m$ for treated units. The event window is $K=\{-1,0,1,2\}$ in the worked certificate and a finite set $K\subset\mathbb{Z}$ in the family statement, with event columns $X_{it,k}=\one\{t-G_i=k\}$. The assignment support is the set $\calR\subseteq\mathbb{Z}_m$ of adoption residues with positive limiting frequency and at least one observation in every listed event bin. The target is not an average treatment effect. The target is the design-level estimability of the alternating event-time contrast $a_K$ with entries $a_k=(-1)^k$, against the period-two calendar component $c(t)=(-1)^t$. The regression design contains unit fixed effects, calendar fixed effects after the chosen normalization, the event columns in $K\setminus\{-1\}$ when $-1$ is omitted, and the finite residue-event incidence matrix $B_{m,K,\calR}$ defined in Section 6. The focal object is the primitive integer alias certificate $\zeta_{m,K,\calR}\in\ker_{\mathbb{Z}} B_{m,K,\calR}$, equivalently the zero-invariant block in the Smith normal form of $B_{m,K,\calR}$ whose event projection is proportional to $a_K$ and whose calendar projection is proportional to $c$ on the observed cells.

\begin{abstract}
Event-study regressions separate event time from calendar time only through a finite incidence map induced by the adoption calendar. This proposal asks when a period-two calendar component is indistinguishable from an alternating event-time contrast before any outcome model is estimated. The main conjecture is a necessary and sufficient Smith-normal-form certificate for this alias: the alternating contrast is estimable if and only if no primitive integer kernel vector links the event projection to the period-two calendar projection. The worked four-residue table gives the certificate explicitly and shows why the obstruction is not a Goodman-Bacon weight, a Sun-Abraham contamination term, or a BJS imputation residual. If resolved, the result would turn calendar/event-time collinearity into a finite diagnostic that is invariant to omitted-bin normalization.
\end{abstract}

\section{Introduction}
Staggered event studies use calendar variation to estimate dynamic treatment effects, yet the same calendar can contain periodic shocks that mimic event-time movement. The headline claim is that this mimicry has an exact finite certificate: in residue-balanced panels, a primitive Smith-normal-form kernel vector decides whether the alternating event-time contrast is a real design contrast or a calendar alias.

The closest published comparators are \citet[Section 3]{SunAbraham2021EventStudies}, who decompose cross-relative-period contamination, and \citet[Sections 2--3]{BorusyakJaravelSpiess2024Revisiting}, who make event-study imputation robust to forbidden comparisons and calendar collinearity. The gap is that neither paper gives an integer invariant for the event-calendar incidence map; the proposed object is a normalization-invariant alias certificate rather than a weighting decomposition or an imputation formula. The kernel lives in panel and linear-projection methods, with the theorem stated entirely as a finite-design estimability claim.

The downstream consumer is applied event-study work with seasonally or politically periodic adoption, such as labor-market, school-calendar, and election-cycle designs. A reader who takes the conclusion away checks the design matrix for an integer alias certificate before interpreting an alternating lead-lag contrast as treatment dynamics.

\begin{itemize}[leftmargin=*]
\item Theorem 1: in the four-residue, four-bin hand design, the period-two calendar component and the residue-weighted alternating event contrast have the same incidence image, and the primitive alias vector has Smith invariant zero. Gap: \citet{SunAbraham2021EventStudies} and \citet{BorusyakJaravelSpiess2024Revisiting} diagnose contamination and collinearity but do not exhibit an integer residue certificate. Consumer: applied event-study designs with calendar-period adoption cycles.
\item Conjecture 1: for finite residue panels, the alternating event contrast is estimable modulo calendar normalization if and only if $B_{m,K,\calR}$ has no primitive kernel vector whose event projection is $a_K$ and whose calendar projection is period two. Gap: \citet{GoodmanBacon2021Timing} and \citet{DeChaisemartinDHaultfoeuille2020TWFE} characterize weighted comparisons, not necessary-and-sufficient integer aliasing. Consumer: normalization-invariant design audits for dynamic DiD.
\item Conjecture 2: the computable SNF diagnostic yields an estimator by projecting event-study coefficients onto the orthogonal complement of the certified alias module, with root-$n$ asymptotic normality for non-aliased contrasts and non-identification for certified aliases. Gap: \citet{CallawaySantAnna2021MultiplePeriods} and \citet{SchmidheinySiegloch2023EventStudies} give aggregation and binning frameworks but not an alias-module estimator. Consumer: empirical event-study workflows that must decide which contrasts survive calendar adjustment.
\end{itemize}

\section{Related work}
\citet{GoodmanBacon2021Timing} decomposes staggered TWFE DiD into two-by-two comparisons and explains negative timing weights; the present object is not a weight but an integer kernel of the event-calendar incidence map. \citet{SunAbraham2021EventStudies} shows that event-study leads and lags can be contaminated by effects from other relative periods; the present object asks when a calendar character itself equals an event-time contrast after incidence. \citet{BorusyakJaravelSpiess2024Revisiting} develops an imputation estimator for event studies and treats collinearity as a design problem; the present claim supplies a finite certificate for one named collinearity class. \citet{DeChaisemartinDHaultfoeuille2020TWFE} shows TWFE can be a nonconvex average under heterogeneous effects; this proposal concerns estimability under a periodic calendar component even before heterogeneous effects enter. \citet{CallawaySantAnna2021MultiplePeriods} identifies group-time treatment effects and aggregation schemes; the alias certificate is a pre-aggregation diagnostic for whether an alternating contrast is a design artifact. \citet{SchmidheinySiegloch2023EventStudies} relates binned event-study designs to distributed-lag specifications; the proposed family frontier asks which bins and residues create an invariant alias. \citet{FreyaldenhovenHansenShapiro2019PreEvent} uses pre-event behavior to address confounding by policy timing; the present diagnostic is design-level and does not use proxy outcomes. \citet{RothSantAnnaBilinskiPoe2023WhatsTrending} surveys modern DiD threats around timing, pre-trends, and inference; the integer alias module is a narrower algebraic threat in the same event-study frontier.

The in-catalogue closest prior work is \texttt{q1\_spectral\_phase\_transition/p1\_markov}, whose headline object is a spectral support threshold for Markov treatment paths, not a finite integer residue certificate. The banked \texttt{panel\_jackknife\_signflip\_phase/v1} attempt is a deletion and sign-flip frontier for event-study estimators, not a normalization-invariant alias module. The banked \texttt{eid\_bjs\_efficient\_event\_study/v1} reviewer requested a fully observable active-rank object; this proposal answers that request with a Smith-normal-form object on the design matrix. The banked \texttt{eid\_switchback\_debruijn\_carryover/v1} and \texttt{pid\_network\_exposure\_aliasing\_graphpair/v1} warn that a single alias witness is too weak; Conjectures 1 and 2 therefore state a family certificate and an estimator-facing diagnostic.

\section{Formal setup}
For treated unit $i$, write the adoption residue as $R_i=G_i\bmod m$. Let $\calR$ be the observed set of residues and let $K$ be the event window. The finite incidence cells are $(r,k)$ with $r\in\calR$, $k\in K$, and observed calendar residue $j=r+k\bmod m$. Let $s_m(r)=(-1)^r$ be the observable adoption-residue character when $m$ is even. The integer incidence matrix $B_{m,K,\calR}$ has one row for each observed cell $(r,k)$ and columns for the residue-character-weighted event coefficients $\beta_k$, period-two calendar coefficients $\gamma_j$, and residue normalizations $\rho_r$:
\[
  (B_{m,K,\calR} x)_{r,k}
  = s_m(r)\beta_k+\gamma_{r+k\bmod m}+\rho_r .
\]
The event contrast vector is $a_K=( (-1)^k )_{k\in K}$, and the period-two calendar vector is $c_m=( (-1)^j )_{j\in\mathbb{Z}_m}$ when $m$ is even. A primitive integer alias certificate is a vector
\[
  \zeta=(u,v,w)\in\mathbb{Z}^{K}\times\mathbb{Z}^{m}\times\mathbb{Z}^{\calR}
\]
with $\gcd(\zeta)=1$, $B_{m,K,\calR}\zeta=0$, $u$ proportional to $a_K$, and $v$ proportional to $-c_m$ on the observed calendar residues. The Smith normal form of $B_{m,K,\calR}$ is $U B_{m,K,\calR} V=\operatorname{diag}(d_1,\ldots,d_s,0,\ldots,0)$ with unimodular $U,V$ and $d_j\mid d_{j+1}$; the certificate lives in the integer kernel block of $V$.

\begin{quote}
\texttt{qid} is \texttt{panel\_calendar\_snf\_alias}. \texttt{specialization} is \texttt{v1}. The anchor cluster is Panel. The panel has units $i=1,\ldots,n$, periods $t=0,\ldots,T-1$, and first-treatment dates $G_i\in\{0,\ldots,T-1,\infty\}$. The residue modulus is $m=4$ in the worked certificate and $m\geq 2$ in the family statement; $R_i=G_i\bmod m$ for treated units. The event window is $K=\{-1,0,1,2\}$ in the worked certificate and a finite set $K\subset\mathbb{Z}$ in the family statement, with event columns $X_{it,k}=\one\{t-G_i=k\}$. The assignment support is the set $\calR\subseteq\mathbb{Z}_m$ of adoption residues with positive limiting frequency and at least one observation in every listed event bin. The target is not an average treatment effect. The target is the design-level estimability of the alternating event-time contrast $a_K$ with entries $a_k=(-1)^k$, against the period-two calendar component $c(t)=(-1)^t$. The regression design contains unit fixed effects, calendar fixed effects after the chosen normalization, the event columns in $K\setminus\{-1\}$ when $-1$ is omitted, and the finite residue-event incidence matrix $B_{m,K,\calR}$ defined in Section 6. The focal object is the primitive integer alias certificate $\zeta_{m,K,\calR}\in\ker_{\mathbb{Z}} B_{m,K,\calR}$, equivalently the zero-invariant block in the Smith normal form of $B_{m,K,\calR}$ whose event projection is proportional to $a_K$ and whose calendar projection is proportional to $c$ on the observed cells.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite residue support]\label{ass:finite-residue}
The event window $K$ is finite, the residue modulus $m$ is finite, and every cell $(r,k)$ with $r\in\calR$ and $k\in K$ has positive limiting frequency.
\end{assumption}

\begin{assumption}[Even calendar character]\label{ass:period-two}
The modulus $m$ is even, and the calendar component of interest is the period-two character $c_m(j)=(-1)^j$.
\end{assumption}

\begin{assumption}[Normalization invariance]\label{ass:normalization}
Two designs are equivalent if they differ only by adding constants to the omitted event bin, calendar fixed-effect normalization, or residue normalization; estimability is decided on the quotient by these normalizations.
\end{assumption}

\begin{assumption}[Sampling regularity for estimator statement]\label{ass:sampling}
Units are independent, residue-cell frequencies converge to positive limits on the support in Assumption~\ref{ass:finite-residue}, and cell-level outcome variances are finite and bounded away from infinity.
\end{assumption}

\section{Main results}
\begin{theorem}[The four-residue alias certificate]\label{thm:four-residue}
Under Assumptions~\ref{ass:finite-residue}--\ref{ass:normalization} with $m=4$, $\calR=\{0,1,2,3\}$, and $K=\{-1,0,1,2\}$, the array
\[
  H[r,k]=(-1)^{r+k}
\]
has rows $[-,+,-,+]$ and $[+,-,+,-]$ alternating by residue, and it equals both the period-two calendar component evaluated at $t\equiv r+k\pmod 4$ and the residue-weighted alternating event contrast $(-1)^r a_k$. Hence the integer vector $\zeta_{4,K,\calR}$ with event projection $a_K$, calendar projection $-c_4$, and residue adjustment $((-1)^r)_{r\in\calR}$ lies in the integer kernel of $B_{4,K,\calR}$ and is primitive.
\end{theorem}
The proof is direct substitution into the incidence equation, followed by division by the common gcd of the integer entries.

\begin{conjecture}[SNF iff certificate for finite calendar aliasing]\label{conj:snf-iff}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite-residue}--\ref{ass:normalization}, the alternating event contrast is estimable modulo period-two calendar shocks if and only if the Smith-normal-form kernel block of $B_{m,K,\calR}$ contains no primitive vector whose event projection is proportional to $a_K$ and whose calendar projection is proportional to $-c_m$ on observed cells.
\end{conjecture}

\begin{conjecture}[Alias-module projection estimator]\label{conj:estimator}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite-residue}--\ref{ass:sampling}, let $\Pi_{\mathrm{alias}}$ be the rational projection onto the event-coordinate image of the SNF alias module of $B_{m,K,\calR}$. For any contrast $\ell$ with $\Pi_{\mathrm{alias}}\ell=0$, the event-study coefficient estimator projected onto $\ell$ is root-$n$ asymptotically normal after the usual cell-frequency scaling; for any $\ell$ with $\Pi_{\mathrm{alias}}\ell\neq 0$, there exist two outcome processes with the same observed design incidence and different values of $\ell^\transpose\beta$ after adding a period-two calendar component.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[No period-two calendar variation]\label{cor:no-calendar}
Under Assumptions~\ref{ass:finite-residue} and \ref{ass:normalization}, if the calendar component is restricted to be constant on parity classes or the calendar fixed effects are fully unrestricted before the alternating event contrast is formed, the certificate in Theorem~\ref{thm:four-residue} is absorbed by calendar normalization and the alternating contrast is not interpreted as treatment dynamics.
\end{corollary}
This collapses to the standard event-study warning that a collinear calendar direction cannot identify a dynamic coefficient because the incidence equation has no unique event-coordinate solution.

\paragraph{Exhibit 9.1: four-residue SNF alias transcript.}
Focal object: $\zeta_{4,K,\calR}$, the primitive integer alias certificate.
Defining equation (copy from Section 6): $(B_{m,K,\calR}x)_{r,k}=s_m(r)\beta_k+\gamma_{r+k\bmod m}+\rho_r$ and a certificate has $B_{m,K,\calR}\zeta=0$, event projection proportional to $a_K$, and calendar projection proportional to $-c_m$.
RHS symbol provenance:
\begin{itemize}[leftmargin=*]
\item $m=4$; source: Section 6 primitive.
\item $K=\{-1,0,1,2\}$; source: Section 6 primitive.
\item $\calR=\{0,1,2,3\}$; source: Section 6 primitive.
\item $a_K=(-1,1,-1,1)$ in the order $(-1,0,1,2)$; source: derived from Section 6 definition $a_k=(-1)^k$.
\item $c_4=(-1,1,-1,1)$ in the order $(0,1,2,3)$; source: derived from Section 6 definition $c_m(j)=(-1)^j$.
\item $\rho_r=0$ for every residue; source: derived value in the worked certificate.
\end{itemize}
Substituted equation: for each $(r,k)$, set $\beta_k=(-1)^k$, $\gamma_{r+k}=-(-1)^{r+k}$, and $\rho_r=0$; the cell image is $(-1)^r(-1)^k-(-1)^{r+k}+0=0$.
Computed value: the residue-event table is
\[
\begin{array}{c|rrrr}
r\backslash k & -1 & 0 & 1 & 2\\
\hline
0&-1&1&-1&1\\
1&1&-1&1&-1\\
2&-1&1&-1&1\\
3&1&-1&1&-1
\end{array}
\]
and the primitive certificate has event coordinates $(-1,1,-1,1)$ and calendar coordinates $(1,-1,1,-1)$, with gcd equal to $1$.
Invariant check 1: support cardinality. LHS $|\calR||K|=16$; RHS table cells $=16$; result = OK.
Invariant check 2: primitive gcd. LHS $\gcd(|\zeta_j|)=1$; RHS $1$; result = OK.
Invariant check 3: normalization quotient. LHS omitted-bin shifts add a constant event vector; RHS $a_K$ has nonzero alternating component orthogonal to constants; result = OK.
Assumption-substitution screen: no RHS symbol is sourced from Section 7 as a load-bearing flagship object. The positive-support and even-modulus assumptions determine the admissible design class, not the value of the certificate.

\section{Proof-sketch route}
Theorem~\ref{thm:four-residue} follows by evaluating the incidence homomorphism on the four-by-four residue-event table and computing the primitive integer kernel vector. Conjecture~\ref{conj:snf-iff} should reduce to a quotient-module statement: headline $<- $ unfold Section 6 definitions of $B_{m,K,\calR}$ and $\zeta$ $<- $ apply Assumptions~\ref{ass:finite-residue}--\ref{ass:normalization} $<- $ Step 1, identify event-calendar estimability with equality in the quotient abelian group of integer design columns $<- $ Step 2, use Smith normal form to characterize all primitive integer relations in that quotient $<- $ Step 3, prove that the Fourier character $(-1)^t$ factors through the incidence relation exactly when the kernel vector has event projection $a_K$ and calendar projection $-c_m$ $<- $ classical result: the structure theorem for finitely generated abelian groups. Conjecture~\ref{conj:estimator} then uses the rational SNF projection to separate estimable and aliased contrasts, followed by a finite-dimensional central limit theorem for non-aliased cell means and a two-law construction along the certified alias direction for non-identification.

\section{Honest scope flags}
The four-residue certificate is stated as a theorem because it is a finite computation. The family iff statement and the estimator statement are conjectures. The family statement may need a stronger quotient definition when $K$ has gaps or when adoption residues are unbalanced. No claim is made about negative TWFE weights, leave-one-cohort-out sign flips, or the efficiency of BJS imputation estimators.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft centered on a finite SNF/Fourier alias certificate; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Goodman-Bacon(2021)]{GoodmanBacon2021Timing}
Goodman-Bacon, A. (2021).
Difference-in-differences with variation in treatment timing.
\emph{Journal of Econometrics}, 225(2), 254--277.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021EventStudies}
Sun, L. and Abraham, S. (2021).
Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\emph{Journal of Econometrics}, 225(2), 175--199.

\bibitem[Borusyak, Jaravel, and Spiess(2024)]{BorusyakJaravelSpiess2024Revisiting}
Borusyak, K., Jaravel, X., and Spiess, J. (2024).
Revisiting event-study designs: robust and efficient estimation.
\emph{Review of Economic Studies}, 91(6), 3253--3285.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{DeChaisemartinDHaultfoeuille2020TWFE}
de Chaisemartin, C. and D'Haultfoeuille, X. (2020).
Two-way fixed effects estimators with heterogeneous treatment effects.
\emph{American Economic Review}, 110(9), 2964--2996.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021MultiplePeriods}
Callaway, B. and Sant'Anna, P. H. C. (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics}, 225(2), 200--230.

\bibitem[Schmidheiny and Siegloch(2023)]{SchmidheinySiegloch2023EventStudies}
Schmidheiny, K. and Siegloch, S. (2023).
On event studies and distributed-lags in two-way fixed effects models: identification, equivalence, and generalization.
\emph{Journal of Applied Econometrics}, 38(5), 695--713.

\bibitem[Freyaldenhoven, Hansen, and Shapiro(2019)]{FreyaldenhovenHansenShapiro2019PreEvent}
Freyaldenhoven, S., Hansen, C., and Shapiro, J. M. (2019).
Pre-event trends in the panel event-study design.
\emph{American Economic Review}, 109(9), 3307--3338.

\bibitem[Roth et al.(2023)]{RothSantAnnaBilinskiPoe2023WhatsTrending}
Roth, J., Sant'Anna, P. H. C., Bilinski, A., and Poe, J. (2023).
What's trending in difference-in-differences? A synthesis of the recent econometrics literature.
\emph{Journal of Econometrics}, 235(2), 2218--2244.
\end{thebibliography}

\end{document}
