\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\section*{scm\_cs\_hedge\_completeness (v1)}

\paragraph{TL;DR.} The completeness program is reversed. The exact \(\mathsf{SS\text{-}ID}\) target is the context-setting intervention \(p(X_Y(a,S=\emptyset))\), and the input is the full observed joint law \(p(X_{V^\circ},S)\). A support-pooling family reaches the final bare return of Algorithm 2 even though every positive selector stratum implements \(A=a\), so the target is identified by the observed marginal \(p(X_Y)\). Thus the final return is not a universal nonidentification certificate: the published algorithm remains sound but is not complete. The two-arm parity calculation is retained only as a supporting cancellation and normalization check.

\section{Project justification}

\paragraph{Gap.} Algorithm 2 searches for one supported selector context that simultaneously passes a context-specific independence test and a fixing-reachability test. It does not pool selector strata that all implement the same intervention. Consequently its final return can occur at an identified query.

\paragraph{Niche.} The graph-native contribution is a support-pooling identification certificate at the exact uncovered Algorithm 2 line-9 trace, not a new nonidentification hedge. Its smallest member has an unlabelled \(S\leftrightarrow Y\) edge causing every eligible one-context independence test to fail, while all supported contexts set the treatment cutset to the same target value.

\paragraph{Fill.} If all positive selector states seriously assign \(A=a\), do not seriously assign target ancestors downstream of \(A\), and \(A\) cuts every directed path from \(S\) to those ancestors, then \(X_Y(a,S=\emptyset)=X_Y\) almost surely and the identifying functional is \(p(X_Y)\). A four-vertex LS-ADMMG satisfies these conditions and reaches the final Algorithm 2 failure, refuting the completeness conjecture and motivating a support-pooling precheck.

\section{Related work}

The soundness theorem of \cite{LeeGhassamiShpitser2024Systematic} remains intact, as does their nonidentification theorem for Algorithm 1 lines 4 and 14 and Algorithm 2 line 3. Their final Algorithm 2 return is outside that theorem, and the support-pooling family shows that this omission cannot be filled by assigning a nonidentification certificate to every final return. Ordinary Shpitser--Pearl hedges preserve one observational law and certify nonidentification; they cannot represent an identified algorithmic failure. Hedgelets and thickets of \cite{LeeCorreaBareinboim2020General} preserve collections of surrogate experimental laws, whereas the present obstruction is that selector strata implement the target experiment only after pooling their coherent joint law. The selector-aware parity cancellation is not claimed as the headline because the supplementary construction of \cite{LeeGhassamiShpitser2024Systematic} already uses the same serious-assignment uniformization mechanism in greater generality.

\section{Setup}

Target (estimand / structural parameter): \(Q(x_Y)=p(X_Y(a)=x_Y,S=\emptyset)\).
Identifying functional / recovery map: \(Q_\kappa(x_Y)=\pi(\emptyset)p_{M_\kappa}(X_Y=x_Y\mid\operatorname{do}(A=a),S=\emptyset)\).
\begin{itemize}
  \item \(V\) --- \texttt{finite set}; \texttt{vertex set} $:=$ \texttt{Observed vertices.}
  \item \(S\) --- element of \(V\); \texttt{selector} $:=$ \texttt{Selector vertex.}
  \item \(V^\circ\) --- \texttt{finite set}; \texttt{nonselector vertices} $:=$ \(V^\circ=V\setminus\{S\}\).
  \item \(\mathcal L\) --- \texttt{finite set}; \texttt{label alphabet} $:=$ \texttt{Atomic selector labels.}
  \item \(\ell'\) --- element of \(\mathcal L\); \texttt{label index} $:=$ \texttt{A second atomic selector label used in label-coherence conditions.}
  \item \(W_\ell\) --- element of \(V^\circ\) indexed by \(\ell\in\mathcal L\); \texttt{label target} $:=$ Child vertex seriously assigned by label \(\ell\).
  \item \(W_{\ell'}\) --- element of \(V^\circ\) indexed by \(\ell'\in\mathcal L\); \texttt{label target} $:=$ Child vertex seriously assigned by the second label \(\ell'\).
  \item \(z_\ell\) --- element of \(\{0,1\}\) indexed by \(\ell\in\mathcal L\); \texttt{assignment value} $:=$ Value imposed by label \(\ell\).
  \item \(z_{\ell'}\) --- element of \(\{0,1\}\) indexed by \(\ell'\in\mathcal L\); \texttt{assignment value} $:=$ Value imposed by the second label \(\ell'\).
  \item \(\mathcal S\) --- \texttt{finite set}; \texttt{coherent selector state space} $:=$ \(\mathcal S=\{s\subseteq\mathcal L:\ell,\ell'\in s,\ W_\ell=W_{\ell'}\Rightarrow z_\ell=z_{\ell'}\}\).
  \item \(\emptyset\) --- element of \(\mathcal S\); \texttt{target context} $:=$ \texttt{The target selector state with no serious assignment.}
  \item \(\pi\) --- probability mass function on \(\mathcal S\); \texttt{selector law} $:=$ Law of the selector \(S\).
  \item \(\mathcal U\) --- finite subset of \(\mathcal S\); \texttt{positive selector support} $:=$ \(\mathcal U=\operatorname{supp}(\pi)\).
  \item \(u\) --- element of \(\mathcal U\); \texttt{context index} $:=$ \texttt{One supplied selector state.}
  \item \(J(u)\) --- subset of \(V^\circ\); \texttt{seriously assigned vertices} $:=$ \(J(u)=\{W_\ell:\ell\in u\}\).
  \item \(z_v(u)\) --- element of \(\{0,1\}\) for \(v\in J(u)\); \texttt{serious assigned value} $:=$ \(z_v(u)=z_\ell\) for any \(\ell\in u\) with \(W_\ell=v\).
  \item \(E^{\to}\) --- \texttt{finite set}; \texttt{labelled directed edges} $:=$ Directed edge copies on \(V\), including edges incident to \(S\); each copy may carry a finite child-label set.
  \item \(E^{\leftrightarrow}\) --- \texttt{finite set}; \texttt{labelled bidirected edges} $:=$ Bidirected edge copies on \(V\), including selector-incident copies; each copy may carry a finite child-label set.
  \item \(\bar G\) --- \texttt{labelled selection acyclic directed mixed multigraph}; \texttt{systematic-selection latent-projection graph} $:=$ \(\bar G\) has vertex set \(V\), directed and bidirected edge copies \(E^{\to}\) and \(E^{\leftrightarrow}\), and child-label sets on edge copies; \(\bar G^{[s]}\) deletes every edge copy whose label names a vertex in \(J(s)\).
  \item \(A\) --- subset of \(V^\circ\); \texttt{treatment set} $:=$ \texttt{Treatment vertices fixed in the target intervention.}
  \item \(a\) --- element of \(\{0,1\}^{A}\); \texttt{treatment level} $:=$ \texttt{Target treatment value.}
  \item \(Y\) --- subset of \(V^\circ\setminus A\); \texttt{outcome set} $:=$ \texttt{Outcome vertices in the target law.}
  \item \(d\) --- element of \(A\); \texttt{gated treatment} $:=$ \texttt{Treatment vertex used as the parity gate.}
  \item \(y\) --- element of \(Y\); \texttt{exposed outcome} $:=$ \texttt{Outcome vertex at which the two arms meet.}
  \item \(b_L,b_R\) --- distinct elements of \(V^\circ\setminus(A\cup Y)\); \texttt{arm sources} $:=$ \texttt{Initial vertices of the left and right parity arms.}
  \item \(P_L,P_R\) --- \texttt{directed simple paths}; \texttt{parity arms} $:=$ Directed paths from \(b_L\) and \(b_R\), respectively, to \(y\).
  \item \(T_L,T_R\) --- subsets of \(V^\circ\); \texttt{whole-arm assignment sets} $:=$ \(T_j=\operatorname{v}(P_j)\setminus\{y\}\) for \(j\in\{L,R\}\).
  \item \(e_\star\) --- element of \(E^{\leftrightarrow}\); \texttt{distinguished coupling edge} $:=$ The distinguished bidirected edge copy whose edge-local exogenous law is perturbed; in the two-arm parity construction its endpoints are \(b_L\) and \(b_R\).
  \item \(\mathfrak H\) --- \texttt{finite response-null certificate tuple}; \texttt{context-specific nonidentification certificate} $:=$ \(\mathfrak H=(e_\star,\Omega_\star,\lambda_0,h,\mathbf f,\rho)\) specifies one graph-compatible finite canonical CS-SCM response skeleton and one observed-null but target-nonnull perturbation of an edge-local exogenous law.
  \item \(\mathcal H_{\mathrm{CS}}\) --- \texttt{finite-dimensional semialgebraic set}; \texttt{graph-readable paired-model certificate set} $:=$ The set of context-specific response-null certificate tuples for \(\bar G,A,a,Y,\mathcal U\).
  \item \(B_L,B_R\) --- \texttt{binary random variables}; \texttt{coupled latent coordinates} $:=$ Two coordinates of the edge-local exogenous variable \(U_\star\).
  \item \(U_\star\) --- \texttt{finite exogenous random variable}; \texttt{distinguished edge-local source} $:=$ The exogenous source associated with \(e_\star\), parent only of the endpoints of that edge copy; in the parity specialization \(U_\star=(B_L,B_R)\).
  \item \(\kappa\) --- real number in \((-1,1)\); \texttt{latent coupling} $:=$ \(\kappa=\mathbb E[(-1)^{B_L+B_R}]\).
  \item \(X_v\) --- binary random variable indexed by \(v\in V^\circ\); \texttt{endogenous response} $:=$ Observed response at nonselector vertex \(v\).
  \item \(X_Y\) --- \texttt{binary random vector}; \texttt{outcome vector} $:=$ \(X_Y=(X_v)_{v\in Y}\).
  \item \(M_\kappa\) --- \texttt{finite CS-SCM}; \texttt{countermodel} $:=$ The explicit selector-aware parity CS-SCM indexed by \(\kappa\).
  \item \(P_{u,\kappa}\) --- \texttt{probability law}; \texttt{supplied context law} $:=$ \(P_{u,\kappa}=p_{M_\kappa}(X_{V^\circ}\mid S=u)\).
  \item \(Q_\kappa\) --- probability law on \(\{0,1\}^{Y}\); \texttt{context-setting interventional target law} $:=$ \(Q_\kappa(x_Y)=p_{M_\kappa}(X_Y(a,S=\emptyset)=x_Y)\).
  \item \(\mathcal I\) --- \texttt{finite SS-ID input}; \texttt{algorithm input} $:=$ A finite LS-ADMMG \(\bar G\), the full observed joint law \(p(X_{V^\circ},S)\), a treatment value \(a\), and an outcome query \(Y\) supplied to \(\mathsf{SS\text{-}ID}\).
  \item \(\mathsf{SS\text{-}ID}\) --- \texttt{algorithm}; \texttt{identification algorithm} $:=$ \texttt{The systematic-selection identification algorithm of Lee, Ghassami, and Shpitser.}
  \item \(\mathcal C_{\mathrm{cs2}}\) --- \texttt{class}; \texttt{uncovered terminal failure class} $:=$ \texttt{Finite inputs whose Algorithm 2 candidate loop is exhausted and whose execution reaches the final bare failure return at line 9.}
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:finite-binary-domain]\label{ass:finite-binary-domain}
\(|V|<\infty\), \(|\mathcal L|<\infty\), and \(X_v\in\{0,1\}\) for every \(v\in V^\circ\).
\par\smallskip\noindent\emph{Novel.} Binary encouragements, treatments, and outcomes are common in the data-fusion settings motivating CS-SCMs. This is an explicitly delimited countermodel domain, not a claim about the general CS-SCM semantics.
\end{assumption}

\begin{assumption}[ass:recursive-directed-part]\label{ass:recursive-directed-part}
The directed part of \(\bar G\) on \(V\), including selector-incident edges, is acyclic.
\par\smallskip\noindent\emph{Standard} (recursive semi-Markovian acyclicity, \cite{ShpitserPearl2006Joint}).
\end{assumption}

\begin{assumption}[ass:label-value-coherence]\label{ass:label-value-coherence}
For every \(s\in\mathcal S\) and every \(\ell,\ell'\in s\), \(W_\ell=W_{\ell'}\Rightarrow z_\ell=z_{\ell'}\).
\par\smallskip\noindent\emph{Novel.} This is the coherent-subset encoding of the child-specific intervention-indicator and intervention-value selector in a binary CS-SCM. It permits different contexts to assign different values to the same child, while forbidding contradictory assignments within one context.
\end{assumption}

\begin{assumption}[ass:supplied-context-mass]\label{ass:supplied-context-mass}
\(\mathcal U=\operatorname{supp}(\pi)=\{s\in\mathcal S:\pi(s)>0\}\).
\par\smallskip\noindent\emph{Standard} (exhaustive positive selector support, \cite{LeeGhassamiShpitser2024Systematic}).
\end{assumption}

\begin{assumption}[ass:target-context-mass]\label{ass:target-context-mass}
\(\emptyset\in\mathcal S\).
\par\smallskip\noindent\emph{Standard} (admissible laidback intervention value, \cite{LeeGhassamiShpitser2024Systematic}).
\end{assumption}

\section{Definitions}

\begin{definition}[def:serious-assignment]\label{def:serious-assignment}
\texttt{Serious selector assignment} $:=$ For every selector state \(s\in\mathcal S\), define \(J(s)=\{W_\ell:\ell\in s\}\) and, for \(v\in J(s)\), define \(z_v(s)=z_\ell\) for any \(\ell\in s\) satisfying \(W_\ell=v\). Statewise label-value coherence makes \(z_v(s)\) single valued, and \(J(\emptyset)=\emptyset\). \quad (\text{inputs: } \textbackslash{}(\textbackslash{}mathcal S\textbackslash{}), \textbackslash{}(W\_\textbackslash{}ell\textbackslash{}), \textbackslash{}(z\_\textbackslash{}ell\textbackslash{}))
\end{definition}

\begin{definition}[def:cs-hedge]\label{def:cs-hedge}
\texttt{Context-specific response-null certificate} $:=$ For a finite binary LS-ADMMG \(\bar G\), let \(\mathcal H_{\mathrm{CS}}(\bar G,A,a,Y,\mathcal U)\) be the set of tuples \(\mathfrak H=(e_\star,\Omega_\star,\lambda_0,h,\mathbf f,\rho)\) with the following properties. The tuple \((\mathbf f,\rho)\) specifies a finite canonical CS-SCM skeleton compatible with \(\bar G\): there is one mutually independent exogenous source for each bidirected edge copy, parent only of that copy's endpoints, one mutually independent finite local source for each observed vertex, deterministic structural maps of the directed parents, and the serious-selector override at every child of \(S\). Every source state space is the graph-determined finite set of deterministic response types of its children. The distinguished source \(U_\star\) belongs to edge copy \(e_\star\), its graph-determined state space is \(\Omega_\star\), and all other source probabilities are collected in \(\rho\). The vector \(\lambda_0\) is a probability mass function on \(\Omega_\star\), \(\sum_{t\in\Omega_\star}h(t)=0\), and \(\lambda_0(t)>|h(t)|\) for every \(t\). Holding \((\mathbf f,\rho)\) fixed, define \(K_{\mathrm{obs}}(x,s\mid t)=\Pr_{\mathbf f,\rho}(X_{V^\circ}=x,S=s\mid U_\star=t)\) and \(K_Q(x_Y\mid t)=\Pr_{\mathbf f,\rho}(X_Y(a,S=\emptyset)=x_Y\mid U_\star=t)\) by summing the finite product law of all other sources. Finally require \(\sum_t h(t)K_{\mathrm{obs}}(x,s\mid t)=0\) for every \((x,s)\), and require \(\sum_t h(t)K_Q(x_Y\mid t)\ne0\) for at least one \(x_Y\). \quad (\text{inputs: } \textbackslash{}(\textbackslash{}bar G\textbackslash{}), \textbackslash{}(A\textbackslash{}), \textbackslash{}(a\textbackslash{}), \textbackslash{}(Y\textbackslash{}), \textbackslash{}(\textbackslash{}mathcal U\textbackslash{}))
\end{definition}

\begin{definition}[def:parity-cs-scm]\label{def:parity-cs-scm}
\texttt{Two-arm selector-aware parity CS-SCM} $:=$ The domain of \(M_\kappa=\operatorname{CSParity}(\bar G,d,y,b_L,b_R,P_L,P_R,e_\star,\pi,\kappa)\) consists of tuples for which \(d\in A\), \(a_d=1\), \(y\in Y\), \(b_L\) and \(b_R\) are distinct vertices outside \(A\cup Y\), \(P_L\) and \(P_R\) are directed simple paths from \(b_L\) and \(b_R\) to \(y\) with \(\operatorname{v}(P_L)\cap\operatorname{v}(P_R)=\{y\}\), \(e_\star=(b_L\leftrightarrow b_R)\in E^{\leftrightarrow}\), \(d\to y\in E^{\to}\), \(T_j=\operatorname{v}(P_j)\setminus\{y\}\) for \(j\in\{L,R\}\), \((T_L\cup T_R)\cap A=\emptyset\), and \(T_L\subseteq J(u)\) or \(T_R\subseteq J(u)\) for every \(u\in\operatorname{supp}(\pi)\). For every \(s\in\mathcal S\), first evaluate the laidback equations \(X_{b_L}=B_L\), \(X_{b_R}=B_R\), copying along \(P_L\) and \(P_R\), \(X_d=1\), \(X_y=X_d(X_{p_L}\oplus X_{p_R})\), and \(X_v=0\) at remaining vertices; then replace the equation at every \(v\in J(s)\) by \(X_v=z_v(s)\). Here \(S\sim\pi\), \(U_\star=(B_L,B_R)\perp S\), \(\Pr_\kappa(B_L=i,B_R=j)=\tfrac14[1+\kappa(-1)^{i+j}]\), and all other exogenous sources are mutually independent and degenerate. \quad (\text{inputs: } \textbackslash{}(\textbackslash{}bar G\textbackslash{}), \textbackslash{}(d\textbackslash{}), \textbackslash{}(y\textbackslash{}), \textbackslash{}(b\_L,b\_R\textbackslash{}), \textbackslash{}(P\_L,P\_R\textbackslash{}), \textbackslash{}(e\_\textbackslash{}star\textbackslash{}), \textbackslash{}(\textbackslash{}pi\textbackslash{}), \textbackslash{}(\textbackslash{}kappa\textbackslash{}), \textbackslash{}(J(u)\textbackslash{}), \textbackslash{}(z\_v(u)\textbackslash{}))
\end{definition}

\begin{definition}[def:target-law]\label{def:target-law}
\texttt{Context-setting interventional target law} $:=$ For every compatible CS-SCM \(M\), define \(Q_M(x_Y)=p_M(X_Y(a,S=\emptyset)=x_Y)=p_M(X_Y=x_Y\mid\operatorname{do}(A=a,S=\emptyset))\). For the parity model, write \(Q_\kappa=Q_{M_\kappa}\). \quad (\text{inputs: } \textbackslash{}(M\_\textbackslash{}kappa\textbackslash{}), \textbackslash{}(X\_Y\textbackslash{}), \textbackslash{}(a\textbackslash{}), \textbackslash{}(\textbackslash{}emptyset\textbackslash{}))
\end{definition}

\begin{definition}[def:cs-fail-2-class]\label{def:cs-fail-2-class}
\texttt{Uncovered SS-ID final failure class} $:=$ \(\mathcal C_{\mathrm{cs2}}\) is the class of finite SS-ID inputs for which Algorithm 1 calls Algorithm 2 on a district \(D^\ast\) with \(S\in C=\operatorname{cl}(D^\ast)\) and \(\operatorname{ch}^\ast(S)=\operatorname{ch}(S)\cap(C\setminus D^\ast)\ne\emptyset\), and for which every supported selector state \(s\) that is laidback for \(D^\ast\), serious for a subset of \(\operatorname{ch}^\ast(S)\), and consistent with \(a_{\operatorname{spa}(D^\ast)}\) fails at least one of Algorithm 2 line 7's graphical independence and reachability conditions. Equivalently, the loop exhausts all candidates and reaches the final bare failure return at line 9. --- the class of all objects satisfying: ass:finite-binary-domain; ass:supplied-context-mass.
\end{definition}

\begin{definition}[def:cs-hedge-extraction-handle]\label{def:cs-hedge-extraction-handle}
\texttt{Response-null and support-pooling checks} $:=$ First enumerate the finite canonical binary response maps compatible with \(\bar G\), one finite independent exogenous source for every bidirected edge copy, and one finite independent local source for every observed vertex. For each distinguished edge source \(U_\star\), form \(K_{\mathrm{obs}}(x,s\mid t)\) and \(K_Q(x_Y\mid t)\), and solve the explicit semialgebraic feasibility system in \(\lambda_0\), \(h\), and the remaining source probabilities given in the response-null certificate definition. Independently compute \(R=\operatorname{an}_{\bar G^{[\emptyset]}_{V^\circ\setminus A}}(Y)\) and accept a support-pooling identification certificate when, for every \(s\in\operatorname{supp}(\pi)\), \(A\subseteq J(s)\), \((z_v(s))_{v\in A}=a\), and \(J(s)\cap R=\emptyset\), and when \(S\notin\operatorname{an}_{\bar G^{[\emptyset]}_{V\setminus A}}(R)\). \quad (\text{inputs: } \textbackslash{}(\textbackslash{}bar G\textbackslash{}), \textbackslash{}(\textbackslash{}pi\textbackslash{}), \textbackslash{}(J(u)\textbackslash{}), \textbackslash{}(A\textbackslash{}), \textbackslash{}(a\textbackslash{}), \textbackslash{}(Y\textbackslash{}))
\end{definition}

\section{Main results}

\begin{lemma}[lem:parity-cs-scm-validity]\label{lem:parity-cs-scm-validity}
For every two-arm parity-severing configuration in the domain of \(M_\kappa=\operatorname{CSParity}(\bar G,d,y,b_L,b_R,P_L,P_R,e_\star,\pi,\kappa)\) and every \(\kappa\in(-1,1)\), \(M_\kappa\) is a finite binary CS-SCM compatible with \(\bar G\). The selector, the edge-local source \(U_\star=(B_L,B_R)\), and all remaining degenerate exogenous sources are mutually independent, and \(U_\star\) is a parent only of the endpoints of \(e_\star\). The structural equations are defined for every \(s\in\mathcal S\), and \(P_{u,\kappa}=p_{M_\kappa}(X_{V^\circ}\mid S=u)\) is well defined for every \(u\in\mathcal U=\operatorname{supp}(\pi)\).
\end{lemma}
\begin{proof}
Fix a configuration in the domain of \(M_\kappa\) and fix \(\kappa\in(-1,1)\). For \(i,j\in\{0,1\}\), put \(\lambda_\kappa(i,j)=\tfrac14\{1+\kappa(-1)^{i+j}\}\). Since \(|\kappa|<1\), every \(\lambda_\kappa(i,j)\) is strictly positive, and
\[
\sum_{i,j=0}^1\lambda_\kappa(i,j)=\frac14\left\{4+\kappa\left(\sum_{i=0}^1(-1)^i\right)\left(\sum_{j=0}^1(-1)^j\right)\right\}=1.
\]
Thus the displayed law in \(\texttt{def:parity-cs-scm}\) is a probability mass function on the finite state space \(\{0,1\}^2\). The selector has the probability mass function \(\pi\), and the definition takes \(S\), \(U_\star=(B_L,B_R)\), and every remaining degenerate source to be mutually independent. In particular, \(U_\star\) is an edge-local source attached only to \(b_L\) and \(b_R\), the endpoints of \(e_\star\).

We next check the structural maps. The two paths are directed and simple, meet only at \(y\), and the directed part of \(\bar G\) is acyclic by \(\texttt{ass:recursive-directed-part}\). Hence the laidback equations can be evaluated in a topological order: first the arm sources, then the internal arm vertices, and finally the parity gate at \(y\). All other vertices receive the constant zero equation, except for \(d\), whose laidback equation is the constant one. Every nonconstant endogenous dependence used by these equations follows a directed edge declared in the domain of the construction. The only nondegenerate shared source is \(U_\star\), and its two children are joined by the declared bidirected edge copy \(e_\star\). Extra directed parents and extra edge-local sources allowed by \(\bar G\) may be ignored or taken degenerate, so the resulting structural maps are compatible with \(\bar G\).

It remains to check selector overrides. For any \(s\in\mathcal S\), \(\texttt{ass:label-value-coherence}\) and \(\texttt{def:serious-assignment}\) make \(z_v(s)\) single valued for each \(v\in J(s)\). Replacing the laidback equation at precisely those vertices by the constant \(z_v(s)\) therefore defines a binary equation at every vertex for every \(s\in\mathcal S\). Finiteness follows from \(\texttt{ass:finite-binary-domain}\). Consequently \(M_\kappa\) is a finite binary CS-SCM compatible with \(\bar G\). Finally, if \(u\in\mathcal U=\operatorname{supp}(\pi)\), then \(\pi(u)>0\) by \(\texttt{ass:supplied-context-mass}\), so conditioning on \(S=u\) is legitimate and \(P_{u,\kappa}\) is well defined.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This lemma verifies that the totalized two-arm construction is a legitimate finite binary CS-SCM. \textit{Gap.} It does not extract a witness from an arbitrary Algorithm 2 terminal trace. \textit{Consumer.} It licenses the supporting parity and normalization calculations.

\begin{theorem}[thm:context-marginal-sufficiency]\label{thm:context-marginal-sufficiency}
For every two-arm parity-severing configuration in the domain of \(M_\kappa\), every \(u\in\mathcal U=\operatorname{supp}(\pi)\), and every \(\kappa\in(-1,1)\), \(P_{u,\kappa}=P_{u,0}\). If \(T_L\subseteq J(u)\), then the full response vector is a function of \(B_R\) and selector-fixed constants only, and
\[\Pr_\kappa(B_R=j\mid S=u)=\sum_{i=0}^1\frac14\{1+\kappa(-1)^{i+j}\}=\frac12.\]
The symmetric identity holds if \(T_R\subseteq J(u)\). Since the domain requires one of these two inclusions at every supported selector state, the full observed joint laws agree:
\[p_{M_\kappa}(X_{V^\circ}=x,S=s)=p_{M_0}(X_{V^\circ}=x,S=s)\quad\text{for every }(x,s).\]
Under \(\operatorname{do}(A=a,S=\emptyset)\), the parity-gate coordinate satisfies \(X_y=B_L\oplus B_R\), and therefore
\[Q_\kappa(X_y=0)=\Pr_\kappa(B_L\oplus B_R=0)=\frac{1+\kappa}{2}.\]
Consequently \(M_{1/2}\) and \(M_{-1/2}\) agree on the full observed SS-ID input but disagree on the context-setting target.
\end{theorem}
\begin{proof}
Fix a configuration, a supported state \(u\), and \(\kappa\in(-1,1)\). The preceding lemma licenses all structural evaluations below. Suppose first that \(T_L\subseteq J(u)\). Every vertex of the left arm other than \(y\), including \(b_L\) and the final left parent \(p_L\) of \(y\), is then replaced by a selector-fixed constant. Conditional on \(S=u\), the right arm is obtained from \(B_R\) by copies and possibly by further selector-fixed overrides. The coordinate \(d\), every remaining coordinate, and \(y\) itself are likewise either fixed constants or functions of the final right-arm value. Hence the entire vector \(X_{V^\circ}\) is a deterministic function, say \(g_u(B_R)\), of \(B_R\) and constants determined by \(u\).

Because \(U_\star\perp S\), for each \(j\in\{0,1\}\),
\[
\begin{aligned}
\Pr_\kappa(B_R=j\mid S=u)
&=\Pr_\kappa(B_R=j)\\
&=\sum_{i=0}^1\frac14\{1+\kappa(-1)^{i+j}\}\\
&=\frac12+\frac{\kappa(-1)^j}{4}\sum_{i=0}^1(-1)^i=\frac12.
\end{aligned}
\]
Therefore, for every \(x\in\{0,1\}^{V^\circ}\),
\[
P_{u,\kappa}(x)=\sum_{j=0}^1\frac12\,\mathbf 1\{g_u(j)=x\}=P_{u,0}(x).
\]
If instead \(T_R\subseteq J(u)\), the same argument with left and right interchanged writes the full vector as a function of \(B_L\), whose marginal is also Bernoulli \(1/2\). The domain of \(M_\kappa\) requires at least one of these alternatives for every \(u\in\operatorname{supp}(\pi)\), so \(P_{u,\kappa}=P_{u,0}\) for every supported state.

Now fix any \((x,s)\). If \(\pi(s)=0\), both joint probabilities are zero. If \(\pi(s)>0\), then \(s\in\mathcal U\), and the conditional equality just proved gives
\[
p_{M_\kappa}(X_{V^\circ}=x,S=s)=\pi(s)P_{s,\kappa}(x)=\pi(s)P_{s,0}(x)=p_{M_0}(X_{V^\circ}=x,S=s).
\]
This proves equality of the full observed joint laws, including the selector masses.

Finally apply \(\operatorname{do}(A=a,S=\emptyset)\). The state \(\emptyset\) is admissible by \(\texttt{ass:target-context-mass}\), and \(J(\emptyset)=\emptyset\), so no serious override occurs. The arm equations copy \(B_L\) and \(B_R\) to \(p_L\) and \(p_R\). Since \(d\in A\) and \(a_d=1\), the intervention fixes \(X_d=1\), whence
\[
X_y=X_d(X_{p_L}\oplus X_{p_R})=B_L\oplus B_R.
\]
Using \(\texttt{def:target-law}\),
\[
Q_\kappa(X_y=0)=\sum_{i=0}^1\Pr_\kappa(B_L=i,B_R=i)=2\cdot\frac{1+\kappa}{4}=\frac{1+\kappa}{2}.
\]
Both \(1/2\) and \(-1/2\) belong to \((-1,1)\). Thus \(M_{1/2}\) and \(M_{-1/2}\) have the same full observed law, while their target probabilities of \(X_y=0\) are \(3/4\) and \(1/4\), respectively.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The theorem proves exact equality of every supported context law and of the full observed joint law while the context-setting target changes with \(\kappa\). \textit{Gap.} Its whole-arm premise is not implied by the terminal trace, so it is supporting rather than headline content. \textit{Consumer.} It supplies the finite normalization proposition and a reusable correlation-hiding example.

\begin{proposition}[prop:normalization-sanity-reduction]\label{prop:normalization-sanity-reduction}
In the smallest two-arm parity-severing configuration with \(P_L=(b_L\to y)\), \(P_R=(b_R\to y)\), \(e_\star=(b_L\leftrightarrow b_R)\), and \(d\to y\), let \(u\in\operatorname{supp}(\pi)\) satisfy \(T_L=\{b_L\}\subseteq J(u)\), \(d\notin J(u)\), and \(b_R\notin J(u)\). Put \(c=z_{b_L}(u)\) and define \(h_u(r)=z_y(u)\) if \(y\in J(u)\), while \(h_u(r)=c\oplus r\) if \(y\notin J(u)\). Then
\[p_{M_\kappa}(X_{b_L}=x_L,X_{b_R}=x_R,X_y=x_y\mid S=u)=\frac12\mathbf 1\{x_L=c\}\mathbf 1\{x_y=h_u(x_R)\},\]
independently of \(\kappa\). Under the context-setting intervention \(\operatorname{do}(d=1,S=\emptyset)\),
\[p_{M_\kappa}(X_y=0\mid\operatorname{do}(d=1,S=\emptyset))=\frac{1+\kappa}{2}.\]
\end{proposition}
\begin{proof}
Condition on \(S=u\). Since \(b_L\in J(u)\), the serious override gives \(X_{b_L}=c\). Since \(b_R\notin J(u)\), the laidback source equation gives \(X_{b_R}=B_R\). The condition \(d\notin J(u)\) gives \(X_d=1\). If \(y\in J(u)\), then \(X_y=z_y(u)=h_u(B_R)\); if \(y\notin J(u)\), then
\[
X_y=X_d(X_{b_L}\oplus X_{b_R})=c\oplus B_R=h_u(B_R).
\]
By the marginal calculation in \(\texttt{thm:context-marginal-sufficiency}\), \(B_R\mid(S=u)\) is Bernoulli \(1/2\), independently of \(\kappa\). Therefore, for every \((x_L,x_R,x_y)\in\{0,1\}^3\),
\[
\begin{aligned}
& p_{M_\kappa}(X_{b_L}=x_L,X_{b_R}=x_R,X_y=x_y\mid S=u)\\
&\qquad=\sum_{r=0}^1\frac12\,\mathbf 1\{x_L=c\}\mathbf 1\{x_R=r\}\mathbf 1\{x_y=h_u(r)\}\\
&\qquad=\frac12\mathbf 1\{x_L=c\}\mathbf 1\{x_y=h_u(x_R)\}.
\end{aligned}
\]
Under \(\operatorname{do}(d=1,S=\emptyset)\), no selector override is active, so \(X_{b_L}=B_L\), \(X_{b_R}=B_R\), and \(X_y=B_L\oplus B_R\). Hence
\[
p_{M_\kappa}(X_y=0\mid\operatorname{do}(d=1,S=\emptyset))=\sum_{i=0}^1\frac14\{1+\kappa(-1)^{2i}\}=\frac{1+\kappa}{2}.
\]
\end{proof}
\par\smallskip\noindent \textit{Justification.} The proposition audits the smallest supplied-context law and the intervention \(\operatorname{do}(S=\emptyset)\) without a selector-mass factor. \textit{Gap.} It is a special three-coordinate calculation, not an algorithmic completeness result. \textit{Consumer.} It prevents recurrence of the natural-event normalization error.

\begin{theorem}[thm:ss-id-completeness-frontier]\label{thm:ss-id-completeness-frontier}
On finite binary CS-SCM inputs, \(\mathsf{SS\text{-}ID}\) is sound but not complete. There is a four-vertex LS-ADMMG on \(\{S,A_0,Y_0,W_0\}\), with directed edges \(S\to A_0\to Y_0\) and \(S\to W_0\), an unlabelled edge \(S\leftrightarrow Y_0\), an \(A_0\)-labelled edge copy \(A_0\leftrightarrow Y_0\), and positive selector support on two states that both seriously assign \(A_0=a_0\) and differ only in whether \(W_0\) is seriously assigned, for which the algorithm reaches the final bare failure return of Algorithm 2, while
\[p(X_{Y_0}(a_0,S=\emptyset)=y_0)=p(X_{Y_0}=y_0)\]
for every compatible CS-SCM and every \(y_0\in\{0,1\}\). Thus failure at that return does not imply nonidentification. The published nonidentification conclusions for Algorithm 1 lines 4 and 14 and Algorithm 2 line 3 are unaffected.
\end{theorem}
\begin{proof}
After replacing the open-ended question by \(\texttt{thm:identified-final-return-without-certificate}\), that theorem supplies an explicit finite binary input \(\mathcal I_0\) for which \(\mathsf{SS\text{-}ID}\) reaches Algorithm 2 line 9 although the target is identified by the observed marginal \(p(X_{Y_0})\). Existence of one identified query on which the algorithm fails is exactly failure of completeness. The same replacement theorem records the published soundness result, so the algorithm is sound but not complete. It also isolates the counterexample at Algorithm 2 line 9; the published nonidentification theorem for Algorithm 1 lines 4 and 14 and Algorithm 2 line 3 is a separate cited result and is therefore unchanged. This proves every clause of the statement.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The theorem states the corrected frontier: published soundness survives, but one identified line-9 input disproves completeness. \textit{Gap.} A complete augmented identification algorithm remains to be developed. \textit{Consumer.} It separates the uncovered final return from the three published nonidentification returns.

\begin{lemma}[lem:support-pooling-identification]\label{lem:support-pooling-identification}
Let \(M\) be a finite recursive CS-SCM compatible with \(\bar G\), and put
\[R=\operatorname{an}_{\bar G^{[\emptyset]}_{V^\circ\setminus A}}(Y).\]
Suppose that, for every \(s\in\operatorname{supp}(\pi)\), \(A\subseteq J(s)\), \((z_v(s))_{v\in A}=a\), and \(J(s)\cap R=\emptyset\), and suppose that \(S\notin\operatorname{an}_{\bar G^{[\emptyset]}_{V\setminus A}}(R)\). Then the context-setting target is identified by the observed marginal:
\[p_M(X_Y(a,S=\emptyset)=x_Y)=p_M(X_Y=x_Y)\quad\text{for every }x_Y.\]
\end{lemma}
\begin{proof}
Couple the natural and interventional worlds by using the same realization of every exogenous source. Let the naturally realized selector state be \(s\). By exhaustive support, \(s\in\operatorname{supp}(\pi)\) almost surely. The serious-selector equations therefore set every coordinate of \(A\) to \(a\) in the natural world. They set no coordinate in \(R\), because \(J(s)\cap R=\emptyset\).

Order the vertices of \(R\) topologically, which is possible by recursive acyclicity. We prove by induction along this order that each natural response in \(R\) equals its response under \(\operatorname{do}(A=a,S=\emptyset)\). Consider a vertex \(r\in R\). Every non-treatment directed parent of \(r\), and recursively every non-treatment directed ancestor capable of changing \(r\), belongs to \(R\) by the definition of \(R\). The selector is not such an ancestor by the displayed ancestry condition. A vertex outside \(A\cup R\) cannot be a directed parent or ancestor of \(r\), for otherwise it would belong to \(R\). Thus all endogenous arguments of the laidback equation for \(r\) agree in the two worlds by the induction hypothesis, while every treatment argument agrees because its natural serious value and its interventional value are both \(a\). The edge-local and local exogenous arguments also agree under the coupling: interventions change structural equations but not exogenous laws, including laws associated with bidirected edges incident to \(S\). Since \(r\notin J(s)\), the natural world uses the same laidback structural map as the \(S=\emptyset\) world. Hence the two responses at \(r\) agree.

Induction proves \(X_R=X_R(a,S=\emptyset)\) almost surely under the coupling. Since \(Y\subseteq R\),
\[
X_Y=X_Y(a,S=\emptyset)\quad\text{almost surely}.
\]
Taking probabilities gives the claimed equality. The right-hand side is obtained by marginalizing the observed joint law, so it is a computable identifying functional.
\end{proof}

\begin{lemma}[lem:four-vertex-line-nine-trace]\label{lem:four-vertex-line-nine-trace}
Let \(\bar G_0\) have vertices \(\{S,A_0,Y_0,W_0\}\), directed edges \(S\to A_0\to Y_0\) and \(S\to W_0\), an unlabelled edge \(S\leftrightarrow Y_0\), and an \(A_0\)-labelled edge copy \(A_0\leftrightarrow Y_0\). Let the positive selector support be \(\{s_0,s_1\}\), where both states seriously assign \(A_0=a_0\), neither seriously assigns \(Y_0\), and only \(s_1\) seriously assigns \(W_0\). For the query \(A=\{A_0\}\), \(a=a_0\), and \(Y=\{Y_0\}\), Algorithm 1 invokes Algorithm 2 with \(D^\ast=\{Y_0\}\), \(C=\operatorname{cl}(D^\ast)=\{S,A_0,Y_0\}\), and \(\operatorname{ch}^\ast(S)=\{A_0\}\). Every supported candidate fails Algorithm 2 line 7, so the input reaches the final return at line 9 and belongs to \(\mathcal C_{\mathrm{cs2}}\).
\end{lemma}
\begin{proof}
In the graph for \(\operatorname{do}(A_0=a_0,S=\emptyset)\), neither \(A_0\), \(S\), nor \(W_0\) is a random ancestor of \(Y_0\). Thus \(Y^\ast=\{Y_0\}\), and its only district is \(D^\ast=\{Y_0\}\). We compute its reachable closure in the laidback graph. The vertex \(W_0\) is fixable because its district is the singleton \(\{W_0\}\). After fixing \(W_0\), the vertices \(S,A_0,Y_0\) remain in one district through \(S\leftrightarrow Y_0\) and the labelled copy \(A_0\leftrightarrow Y_0\). The vertex \(A_0\) is not fixable while \(Y_0\) remains, because \(Y_0\in\operatorname{dis}(A_0)\cap\operatorname{de}(A_0)\); likewise \(S\) is not fixable because \(A_0\in\operatorname{dis}(S)\cap\operatorname{de}(S)\). Therefore the smallest reachable superset of \(D^\ast\) is
\[
C=\operatorname{cl}(D^\ast)=\{S,A_0,Y_0\}.
\]
Consequently \(S\in C\), \(C\ne D^\ast\), and
\[
\operatorname{ch}^\ast(S)=\operatorname{ch}(S)\cap(C\setminus D^\ast)=\{A_0\}.
\]
Both supported states are laidback for \(D^\ast\), so Algorithm 1 does not take line 4 and invokes Algorithm 2; its line-3 condition also fails because \(\operatorname{ch}^\ast(S)\ne\emptyset\).

Every supported state eligible for the Algorithm 2 loop seriously assigns \(A_0\) at the query-consistent value \(a_0\) and is laidback for \(Y_0\); the extra assignment to \(W_0\) in \(s_1\) lies outside \(C\) and does not change the restricted graph on the call. In either eligible context, restriction deletes the \(A_0\)-labelled copy \(A_0\leftrightarrow Y_0\) and retains the unlabelled edge \(S\leftrightarrow Y_0\). Hence the district containing \(D^\ast\) is
\[
D'=\{S,Y_0\}.
\]
The coordinate \(Y_0\) is a descendant of \(S\) in the call graph through \(S\to A_0\to Y_0\). Thus the line-7 independence conjunct requires the descendant response containing \(Y_0(s)\) to be graphically separated from \(S\), conditional on the stated non-descendant responses and strict parents. This separation is impossible: the length-one path \(S\leftrightarrow Y_0\) has no internal vertex, neither endpoint is conditioned upon, and it remains in every eligible context. The independence conjunct therefore fails independently of reachability. All eligible positive-support states fail line 7, so the loop reaches line 9. By \(\texttt{def:cs-fail-2-class}\), the input belongs to \(\mathcal C_{\mathrm{cs2}}\).
\end{proof}

\begin{lemma}[lem:response-null-certificate-soundness]\label{lem:response-null-certificate-soundness}
If \(\mathcal H_{\mathrm{CS}}(\bar G,A,a,Y,\mathcal U)\ne\emptyset\), then the target law is not identified from the full observed joint law over finite CS-SCMs compatible with \(\bar G\). More precisely, every \(\mathfrak H=(e_\star,\Omega_\star,\lambda_0,h,\mathbf f,\rho)\) in this set yields two compatible models with distinguished-source laws \(\lambda_+=\lambda_0+h\) and \(\lambda_-=\lambda_0-h\), identical observed laws, and different target laws.
\end{lemma}
\begin{proof}
Fix \(\mathfrak H\in\mathcal H_{\mathrm{CS}}\). For each \(t\in\Omega_\star\), define \(\lambda_\pm(t)=\lambda_0(t)\pm h(t)\). The inequalities \(\lambda_0(t)>|h(t)|\) make both masses strictly positive. Since \(\lambda_0\) is a probability mass function and \(\sum_t h(t)=0\),
\[
\sum_t\lambda_\pm(t)=1.
\]
Thus \(\lambda_+\) and \(\lambda_-\) are probability mass functions on the graph-determined state space of \(U_\star\). Keep \((\mathbf f,\rho)\) fixed and replace only the law of \(U_\star\) by \(\lambda_+\) or \(\lambda_-\), obtaining models \(M_+\) and \(M_-\). Both remain compatible with \(\bar G\), because the response maps, source incidence, and mutual independence structure are unchanged.

For every observed cell \((x,s)\), the kernel definition and the observed-null equations give
\[
\begin{aligned}
p_{M_+}(x,s)-p_{M_-}(x,s)
&=\sum_{t\in\Omega_\star}\{\lambda_+(t)-\lambda_-(t)\}K_{\mathrm{obs}}(x,s\mid t)\\
&=2\sum_{t\in\Omega_\star}h(t)K_{\mathrm{obs}}(x,s\mid t)=0.
\end{aligned}
\]
For the target cell \(x_Y\) required by the certificate definition, however,
\[
Q_{M_+}(x_Y)-Q_{M_-}(x_Y)=2\sum_{t\in\Omega_\star}h(t)K_Q(x_Y\mid t)\ne0.
\]
The two models therefore agree on the entire observed input and disagree on the causal target, which is exactly nonidentification.
\end{proof}

\begin{lemma}[lem:ss-id-published-soundness]\label{lem:ss-id-published-soundness}
For a hidden-variable CS-SCM represented by an LS-ADMMG, whenever Algorithm 1, \(\mathsf{SS\text{-}ID}\), returns a functional for \(p(X_Y(a,S=\emptyset))\), that functional equals the context-setting interventional target in every compatible model.
\end{lemma}

\begin{lemma}[lem:ss-id-published-covered-failures]\label{lem:ss-id-published-covered-failures}
If \(\mathsf{SS\text{-}ID}\) fails at Algorithm 1 line 4, Algorithm 1 line 14, or Algorithm 2 line 3, then the context-setting causal effect is not identified.
\end{lemma}

\begin{theorem}[thm:identified-final-return-without-certificate]\label{thm:identified-final-return-without-certificate}
The answer is no. Let \(\bar G_0\) be the LS-ADMMG on \(\{S,A_0,Y_0,W_0\}\) with directed edges \(S\to A_0\to Y_0\) and \(S\to W_0\), an unlabelled bidirected edge \(S\leftrightarrow Y_0\), and an \(A_0\)-labelled bidirected edge copy \(A_0\leftrightarrow Y_0\). Let \(A=\{A_0\}\), \(Y=\{Y_0\}\), and let the positive selector support be \(\{s_0,s_1\}\), where both states seriously assign \(A_0=a_0\), neither seriously assigns \(Y_0\), and only \(s_1\) seriously assigns \(W_0\). Then the associated input \(\mathcal I_0\) belongs to \(\mathcal C_{\mathrm{cs2}}\), but for every compatible finite binary CS-SCM \(M\),
\[p_M(X_{Y_0}(a_0,S=\emptyset)=y_0)=p_M(X_{Y_0}=y_0),\qquad y_0\in\{0,1\}.\]
Thus the target is identified by the observed marginal \(p_M(X_{Y_0})\), and \(\mathcal H_{\mathrm{CS}}(\bar G_0,\{A_0\},a_0,\{Y_0\},\{s_0,s_1\})=\emptyset\). Consequently the universal context-specific response-null certificate assertion is false, and the publishedly sound \(\mathsf{SS\text{-}ID}\) algorithm is not complete. This counterexample concerns only the final Algorithm 2 return and does not alter the published nonidentification results for Algorithm 1 lines 4 and 14 or Algorithm 2 line 3.
\end{theorem}
\begin{proof}
Choose coherent labels \(\ell_A\) and \(\ell_W\) with \(W_{\ell_A}=A_0\), \(z_{\ell_A}=a_0\), \(W_{\ell_W}=W_0\), and \(z_{\ell_W}=w_0\), and put \(s_0=\{\ell_A\}\) and \(s_1=\{\ell_A,\ell_W\}\). Let \(C\) and \(D\) be independent Bernoulli \(1/2\) variables. Set \(S=s_C\); use the laidback equations \(X_{A_0}=D\), \(X_{W_0}=0\), and \(X_{Y_0}=X_{A_0}\oplus C\oplus D\); and apply the prescribed serious overrides in states \(s_0\) and \(s_1\). Then \(C\) is a common cause of \(S\) and \(Y_0\), while \(D\) is a common cause of \(A_0\) and \(Y_0\). The latter latent path is disabled when \(A_0\) is seriously assigned, so its latent-projection copy carries the label \(A_0\). Thus this is a concrete finite binary CS-SCM compatible with exactly the displayed selector-incident and labelled edges, and \(\Pr(S=s_0)=\Pr(S=s_1)=1/2\). By \(\texttt{lem:four-vertex-line-nine-trace}\), the associated input \(\mathcal I_0\) reaches Algorithm 2 line 9 and belongs to \(\mathcal C_{\mathrm{cs2}}\).

For identification, compute the support-pooling ancestor set after removing \(A_0\):
\[
R=\operatorname{an}_{(\bar G_0^{[\emptyset]})_{V^\circ\setminus\{A_0\}}}(Y_0)=\{Y_0\}.
\]
After \(A_0\) is removed, the only directed edge out of \(S\) is \(S\to W_0\), and no directed path from \(S\) or \(W_0\) reaches \(Y_0\). Both supported states seriously assign \(A_0\) to \(a_0\), neither assigns \(Y_0\), and \(S\notin\operatorname{an}_{(\bar G_0^{[\emptyset]})_{V\setminus\{A_0\}}}(Y_0)\). Hence \(\texttt{lem:support-pooling-identification}\) gives, for every compatible \(M\),
\[
p_M(X_{Y_0}(a_0,S=\emptyset)=y_0)=p_M(X_{Y_0}=y_0),\qquad y_0\in\{0,1\}.
\]
The right side is obtained by marginalizing the observed joint law. The unlabelled edge \(S\leftrightarrow Y_0\) does not invalidate the equality: the two coupled worlds retain the same edge-local exogenous variable, and after fixing \(A_0\) there is no directed causal path from \(S\) to \(Y_0\).

Suppose that \(\mathfrak H\in\mathcal H_{\mathrm{CS}}(\bar G_0,\{A_0\},a_0,\{Y_0\},\{s_0,s_1\})\). The skeleton in this certificate has selector support \(\mathcal U=\{s_0,s_1\}\) by \(\texttt{ass:supplied-context-mass}\). By \(\texttt{lem:response-null-certificate-soundness}\), it yields two compatible models with the same full observed joint law and different target laws. Applying the displayed identifying formula to each model instead makes both targets equal to the same observed marginal, a contradiction. Therefore the certificate set is empty and the universal assertion in the open-ended question is false.

Finally, \(\texttt{lem:ss-id-published-soundness}\) supplies soundness of the published algorithm. Because \(\mathcal I_0\) is identified but the algorithm fails on it, the algorithm is not complete. The distinct result \(\texttt{lem:ss-id-published-covered-failures}\) concerns Algorithm 1 lines 4 and 14 and Algorithm 2 line 3, whereas \(\mathcal I_0\) reaches Algorithm 2 line 9. Those published nonidentification conclusions are therefore unaffected.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This theorem gives the explicit four-vertex line-9 trace, the computable identifying functional \(p(X_{Y_0})\), and the resulting emptiness of the response-null certificate set. \textit{Gap.} It is a counterexample to completeness, not a characterization of every final-return input. \textit{Consumer.} It resolves the open-ended question negatively and supplies the frontier theorem.

\section{Interpretation}

When every observed selector state forces \(A=a\), the observed population has already undergone the target treatment intervention, even if the selector is arbitrarily confounded with the outcome. If fixing \(A\) removes every directed route from \(S\) to \(Y\), setting \(S=\emptyset\) changes no outcome mechanism. Marginalizing the observed joint law over \(S\) therefore gives the target directly. Algorithm 2 misses this because it demands a valid single-context bridge rather than recognizing the support-wide experiment.

\section*{Technical internal limitation (diagnostic only)}

The result refutes completeness but does not characterize all identifiable final-return inputs or furnish a complete replacement algorithm. The support-pooling certificate is sufficient, finite, and graph readable. The explicit counterexample is binary and restricts support to contexts assigning one treatment value; mixtures of treatment values require additional transport or fixing arguments.

\section{Honest scope}

No universal CS-hedge or terminal nonidentification theorem is claimed. Positive mass at the laidback target context is neither assumed nor needed. The parity model proves only a restricted conditional-law cancellation and a finite normalization check. The substantive conclusion is negative for the published conjecture: on the displayed finite binary input, \(\mathsf{SS\text{-}ID}\) reaches its uncovered final return although the causal target has the explicit functional \(p(X_Y)\).

\begin{thebibliography}{99}

  \bibitem{LeeGhassamiShpitser2024Systematic} J. J. R. Lee, A. Ghassami, and I. Shpitser. A General Identification Algorithm for Data Fusion Problems under Systematic Selection. UAI, 2024, PMLR 244:2188--2204.

  \bibitem{ShpitserPearl2006Joint} I. Shpitser and J. Pearl. Identification of Joint Interventional Distributions in Recursive Semi-Markovian Causal Models. AAAI, 2006, pp. 1219--1226.

  \bibitem{LeeCorreaBareinboim2020General} S. Lee, J. D. Correa, and E. Bareinboim. General Identifiability with Arbitrary Surrogate Experiments. UAI, 2020, PMLR 115:389--398.

  \bibitem{KivvaEtAl2022Revisiting} Y. Kivva, E. Mokhtarian, J. Etesami, and N. Kiyavash. Revisiting the General Identifiability Problem. UAI, 2022, PMLR 180:1022--1030.

\end{thebibliography}

\end{document}