% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_ordinal\_late\_partial\_defiers, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_ordinal\_late\_partial\_defiers} / \texttt{v1}%
  \\ \large\textit{Sharp ordinal-IV LATE bounds with bounded adjacent defiers}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies a partial-identification analogue of the adjacent-rung
ordinal-IV Wald formula when Imbens--Angrist monotonicity is relaxed by known
per-rung down-defier caps.  The estimand-defining formula is not a regression
coefficient but the sharp linear-fractional response-path program whose
endpoints are denoted
\([\underline\theta_\omega(P,\eta),\overline\theta_\omega(P,\eta)]\).  The
target causal estimand is the weighted positive-rung LATE
\(\theta^+_\omega\), the average treatment effect over adjacent up-complier
events \(U_j=\{D(j)=0,D(j+1)=1\}\) with known positive weights \(\omega_j\).
The main result is sharpness:
\(\Theta_I(P,\eta)=[\underline\theta_\omega(P,\eta),
\overline\theta_\omega(P,\eta)]\), where the endpoints are attained by a
finite latent response-path program over \(r\in\{0,1\}^{J+1}\).  When all caps
are zero, the interval collapses to the usual adjacent-rung weighted Wald
estimand.  With three instrument levels, the global ordinal response-path
program can be strictly tighter than independently pasted adjacent binary-IV
bounded-defier bounds; a rational witness has global upper endpoint \(1/9\)
while the pairwise relaxation attains \(1/5\).
\end{abstract}

\section{Introduction}
Ordinal instruments arise when encouragement, eligibility, or exposure
intensity has several ordered levels.  Under the standard no-defiers
monotonicity condition, adjacent reduced-form contrasts identify weighted
averages of local treatment effects.  The full no-defiers restriction is often
substantive rather than mechanical, so a useful sensitivity analysis should
allow a calibrated amount of defiance while preserving the fact that a unit has
one whole treatment response path across all instrument levels.

For a binary instrument, bounded defier shares lead naturally to a finite
latent-type partial-identification problem.  With an ordinal instrument, the
same adjacent binary calculation can be run pair by pair, but that calculation
forgets cross-rung compatibility.  A path such as \(010\) is an up-complier for
the \(0\to1\) rung and a down-defier for the \(1\to2\) rung, so the same
potential-outcome contrast must serve both roles.  Pairwise binary programs can
assign incompatible values to those two appearances.

This note gives the exact finite response-path bounding functional for the
locked target \(\theta^+_\omega\).  It proves that the response-path projection
is sharp, proves the monotone zero-cap reduction to the adjacent weighted Wald
estimand, and confirms the Stage -1 zig-zag compatibility conjecture by an
explicit rational witness.  It also records the correct parametric-LP statement
behind the proposed kink claim: endpoint functions along a cap ray are
piecewise linear-fractional, but the stronger ``first kink is ordinal''
existence claim requires an additional active-basis certificate and is left as
partial rather than asserted.

The result is useful for formula design because it separates three objects:
the causal target, the sharp global bounding functional, and the looser
pairwise-pasting comparator.  That separation identifies exactly when a local
binary-IV sensitivity analysis is conservative for an ordinal design and when
it coincides with the sharp global response-path analysis.

\section{Related work and positioning}
\cite{ImbensAngrist1994} establish binary-instrument LATE identification under
independence, exclusion, relevance, and monotonicity; the present note keeps
the IV structure but replaces no-defiers by per-rung defier caps.
\cite{AngristImbens1995} study IV with variable treatment intensity and give
the ordered-monotonicity weighted-average interpretation; the zero-cap result
below is the adjacent-rung version of that benchmark.  \cite{AngristImbensRubin1996}
develop the principal-strata language used here to name up-compliers and
down-defiers.  \cite{Vytlacil2002} links monotonicity and latent-index
selection; the zig-zag paths \(010\) and \(101\) are precisely the ordinal
patterns that violate a scalar monotone threshold picture.

\cite{BalkePearl1997} derive sharp IV bounds by optimizing over latent
response types.  The finite response-path program in this note follows that
sharpness logic, but its latent type is the full ordinal treatment path
\((D(0),\ldots,D(J))\), not an independent binary type for each adjacent pair.
\cite{deChaisemartin2017} shows that IV estimands can retain a LATE
interpretation with defiers under additional compliers-defiers restrictions;
the present model imposes only quantitative adjacent defier caps and therefore
delivers an interval.  \cite{HuberMellace2012} and
\cite{DahlHuberMellace2023} study local monotonicity and defier/complier
identification in binary-IV settings, whereas the new feature here is
cross-rung compatibility in a single ordinal response path.  \cite{Noack2021}
studies sensitivity of LATE estimates to monotonicity violations for binary
instruments; the strictness witness below shows what binary sensitivity misses
when adjacent rungs share latent paths.  \cite{MogstadTorgovitskyWalters2021}
analyze when multiple-IV 2SLS has a positive-weight LATE interpretation; this
note instead treats one ordered instrument and a partial-ID target.  \cite{Kitagawa2015}
and \cite{HuberMellace2015} provide inequality tests of IV/LATE restrictions;
the present result uses inequalities as calibrated bounds rather than as a
validity test.  \cite{SunWuthrich2025} is the closest pairwise comparator
because it works with researcher-selected valid instrument pairs, but it does
not impose one global response path across all pairs.

The in-repository positioning is as follows.  The ThmSmith catalogue reserves
\texttt{ThmSmith/PartialID/} for Manski-family bounds, Balke--Pearl bounds, IV
bounds, sensitivity analysis, and shape restrictions.  The existing
Manski-family infrastructure is relevant because it uses bounded outcomes and
worst-case completion, while the Balke--Pearl infrastructure is relevant
because it optimizes over latent response tables.  The closest banked proposal
is \texttt{pid\_late\_bounded\_defiers}/\texttt{one\_sided\_compliance}, a
binary-instrument bounded-defier envelope; it cannot contain the ordinal
zig-zag compatibility phenomenon because it has only one adjacent rung.

\section{Formal setup}
Let \(Z\in\{0,\ldots,J\}\) be an ordinal instrument with \(J\ge1\), let
\(D\in\{0,1\}\) be the treatment, and let \(Y\in[0,1]\) be the observed
outcome.  The observable object is the first-moment array
\[
P=P^{(1)}=\{p_z,d_z,m_z:z=0,\ldots,J\},
\quad
p_z=\Pr(Z=z)>0,\quad
d_z=\E[D\mid Z=z],\quad
m_z=\E[Y\mid Z=z].
\]
The full-data object consists of the potential treatment path
\[
R=(D(0),\ldots,D(J))\in\{0,1\}^{J+1}
\]
and potential outcomes \(Y(0),Y(1)\in[0,1]\).  For a response path
\(r\in\{0,1\}^{J+1}\), write \(\pi_r=\Pr(R=r)\) and
\(\mu_{dr}=\pi_r y_d(r)\), where \(y_d(r)=\E[Y(d)\mid R=r]\in[0,1]\) when
\(\pi_r>0\) and any value in \([0,1]\) when \(\pi_r=0\).  Thus
\[
0\le \mu_{dr}\le \pi_r,\qquad
\sum_r\pi_r=1,\qquad
\pi_r\ge0.
\]
The response-path representation matches the observable moments when, for
every instrument value \(z\),
\[
\sum_r \pi_r r_z=d_z,\qquad
\sum_r\{r_z\mu_{1r}+(1-r_z)\mu_{0r}\}=m_z.
\]

For each adjacent rung \(j=0,\ldots,J-1\), define
\[
U_j=\{R_j=0,R_{j+1}=1\},\qquad
V_j=\{R_j=1,R_{j+1}=0\},
\]
with masses \(q_j^+=\Pr(U_j)\) and \(q_j^-=\Pr(V_j)\).  The maintained
restriction \(q_j^-\le\eta_j\) is imposed by
\[
\sum_{r:r_j=1,r_{j+1}=0}\pi_r\le\eta_j.
\]
Let \(\mathcal C(P,\eta)\) denote the finite set of all arrays
\((\pi_r,\mu_{0r},\mu_{1r})_{r\in\{0,1\}^{J+1}}\) satisfying the preceding
linear constraints, boundedness, and the defier caps.  The identified set is
\[
\Theta_I(P,\eta)
=\{\theta^+_\omega(\pi,\mu):(\pi,\mu)\in\mathcal C(P,\eta),
\ \sum_j\omega_j q_j^+>0\}.
\]
The positivity condition on the denominator is a boundary condition for the
ratio target; without it the positive-rung LATE is not defined.

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode.  The locked
tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_ordinal\_late\_partial\_defiers},\texttt{v1},
  P^{(1)},\theta^+_\omega,\mathcal R_{\eta}^{\mathrm{ordIV}},
  [\underline\theta_\omega(P,\eta),\overline\theta_\omega(P,\eta)]) .
\end{gathered}
\]
Here \(P^{(1)}=\{p_z,d_z,m_z:z=0,\ldots,J\}\) is the observable first-moment
array with \(p_z=\Pr(Z=z)>0\), \(d_z=\E[D\mid Z=z]\), and
\(m_z=\E[Y\mid Z=z]\).  The outcome is bounded, \(Y\in[0,1]\),
\(Z\in\{0,\ldots,J\}\) is an ordinal instrument with \(J\ge 1\),
\(D\in\{0,1\}\), and the full-data response path is
\(R=(D(0),\ldots,D(J))\in\{0,1\}^{J+1}\).  For adjacent rung \(j\), let
\[
U_j=\{D(j)=0,D(j+1)=1\},\qquad V_j=\{D(j)=1,D(j+1)=0\}
\]
be the up-complier and down-defier events, with masses \(q^+_j=\Pr(U_j)\) and
\(q^-_j=\Pr(V_j)\).  The target is the weighted positive-rung LATE
\[
\theta^+_\omega
=\frac{\sum_{j=0}^{J-1}\omega_j\,\E[(Y(1)-Y(0))\one\{U_j\}]}
        {\sum_{j=0}^{J-1}\omega_j q^+_j},
\]
where the known weights satisfy \(\omega_j>0\).  The restrictions
\(\mathcal R_{\eta}^{\mathrm{ordIV}}\) are ordinal-IV random assignment,
exclusion, consistency, bounded outcomes, positive instrument cells,
\(q^-_j\le \eta_j\) for known per-rung defier caps \(\eta_j\), and the
observable feasibility inequalities
\(\max\{0,d_j-d_{j+1}\}\le\eta_j\).  The bounding functional is the sharp
projection of the finite response-path latent-type polytope matching
\(P^{(1)}\), with the pairwise-pasting relaxation defined in
Assumption~\ref{ass:pairwise}.

\section{Assumptions}
\begin{assumption}[Ordinal finite IV setup]\label{ass:finite-ordinal}
\(Z\in\{0,\ldots,J\}\) with \(J\ge1\), \(D\in\{0,1\}\), \(Y\in[0,1]\), and
the known target weights satisfy \(\omega_j>0\) for every adjacent rung
\(j=0,\ldots,J-1\).
\end{assumption}

\begin{assumption}[Ordinal IV validity]\label{ass:ord-iv}
\((D(0),\ldots,D(J),Y(0),Y(1))\) is independent of \(Z\).  Exclusion and
consistency hold: \(D=D(Z)\) and \(Y=Y(D)\) almost surely.
\end{assumption}

\begin{assumption}[Positive cells and positive target mass]\label{ass:positive}
\(\Pr(Z=z)>0\) for every \(z\in\{0,\ldots,J\}\).  For each full-data law whose
target is evaluated,
\[
\sum_{j=0}^{J-1}\omega_j q_j^+>0.
\]
\end{assumption}

\begin{assumption}[Known per-rung defier caps]\label{ass:defier-caps}
For known constants \(\eta_j\in[0,1]\), the adjacent down-defier masses satisfy
\(q_j^-=\Pr(V_j)\le\eta_j\).  The observable first-stage feasibility condition
\[
\max\{0,d_j-d_{j+1}\}\le\eta_j
\]
holds for every \(j=0,\ldots,J-1\).
\end{assumption}

\begin{assumption}[Finite response-path sharpness class]\label{ass:finite-types}
Sharpness is evaluated over all response paths \(r\in\{0,1\}^{J+1}\).  Let
\(\pi_r\) be the path mass and let \(\mu_{0r},\mu_{1r}\) be outcome-mass
variables, where \(\mu_{dr}=\pi_r y_d(r)\) for some path-specific
potential-outcome mean \(y_d(r)\in[0,1]\).  Equivalently, the endpoint program
uses the linear constraints
\[
0\le\mu_{dr}\le\pi_r,\qquad
\sum_r\pi_r=1,\qquad
\pi_r\ge0.
\]
The induced moments must equal \(P\): for every \(z\),
\[
\sum_r \pi_r r_z=d_z,\qquad
\sum_r \{r_z\mu_{1r}+(1-r_z)\mu_{0r}\}=m_z.
\]
The class must also satisfy Assumptions~\ref{ass:finite-ordinal}--\ref{ass:defier-caps};
in particular, each cap is
\[
\sum_{r:r_j=1,r_{j+1}=0}\pi_r\le\eta_j.
\]
\end{assumption}

\begin{assumption}[Pairwise-pasting comparator]\label{ass:pairwise}
For each adjacent pair \(j\), let \(\mathcal F_j(P,\eta_j)\) be the binary-IV
bounded-defier feasible set for the two cells \((Z=j,Z=j+1)\), matching
\((d_j,m_j,d_{j+1},m_{j+1})\) and satisfying \(q_j^-\le\eta_j\).  Each element
of \(\mathcal F_j\) supplies an adjacent up-complier numerator
\[
a_j=\E[(Y(1)-Y(0))\one\{U_j\}]
\]
and denominator \(b_j=q_j^+\).  The pairwise-pasting interval is
\[
B_{\mathrm{pair}}(P,\eta)=
\left[
\inf_{(a_j,b_j)\in\mathcal F_j\ \forall j}
\frac{\sum_j\omega_j a_j}{\sum_j\omega_j b_j},
\;
\sup_{(a_j,b_j)\in\mathcal F_j\ \forall j}
\frac{\sum_j\omega_j a_j}{\sum_j\omega_j b_j}
\right],
\]
where the product relaxation optimizes the adjacent binary problems
independently before forming the aggregate ratio, and the denominator is
restricted to be positive.
\end{assumption}

\begin{assumption}[Three-rung zig-zag witness class]\label{ass:zigzag-class}
For the zig-zag and kink claims, take \(J=2\), \(\omega_0=\omega_1=1\),
positive first stages \(\Delta^D_0,\Delta^D_1>0\), and caps satisfying
\(0<\eta_0,\eta_1<1\).  The response paths \(010\) and \(101\) have positive
admissible mass under the response-path polytope.  For cap sensitivity,
evaluate only along a fixed positive ray \(\eta(s)=s v\), where
\(v=(v_0,v_1)\in(0,\infty)^2\) is fixed and \(s\ge0\).
\end{assumption}

\section{Regression estimator}
This partial-identification instance has no regression estimator.  The
estimand-defining functional is the sharp response-path bounding functional.
For \((\pi,\mu)\in\mathcal C(P,\eta)\), define
\[
N_\omega(\pi,\mu)
=\sum_{j=0}^{J-1}\omega_j
  \sum_{r:r_j=0,r_{j+1}=1}(\mu_{1r}-\mu_{0r}),
\qquad
B_\omega(\pi)
=\sum_{j=0}^{J-1}\omega_j
  \sum_{r:r_j=0,r_{j+1}=1}\pi_r.
\]
The pointwise response-path value is
\[
\psi_\omega(\pi,\mu)=\frac{N_\omega(\pi,\mu)}{B_\omega(\pi)}
\]
on the domain \(B_\omega(\pi)>0\).  The sharp endpoint functionals are
\[
\underline\theta_\omega(P,\eta)
=\inf\{\psi_\omega(\pi,\mu):(\pi,\mu)\in\mathcal C(P,\eta),
B_\omega(\pi)>0\},
\]
\[
\overline\theta_\omega(P,\eta)
=\sup\{\psi_\omega(\pi,\mu):(\pi,\mu)\in\mathcal C(P,\eta),
B_\omega(\pi)>0\}.
\]
They are sharp bounds, not merely outer bounds, once
\(\mathcal C(P,\eta)\) is interpreted as the full finite response-path class
of Assumption~\ref{ass:finite-types}.  The pairwise-pasting interval
\(B_{\mathrm{pair}}(P,\eta)\) in Assumption~\ref{ass:pairwise} is only a
comparator: it is an outer relaxation of the global ordinal program and need
not be sharp for the ordinal model.

\section{Target causal estimand}
The target is the weighted positive-rung local average treatment effect
\[
\theta^+_\omega
=
\frac{\sum_{j=0}^{J-1}\omega_j
\E[(Y(1)-Y(0))\one\{U_j\}]}
{\sum_{j=0}^{J-1}\omega_j q_j^+},
\qquad
U_j=\{D(j)=0,D(j+1)=1\}.
\]
The numerator averages treatment effects only over adjacent up-complier
events.  Down-defier events \(V_j=\{D(j)=1,D(j+1)=0\}\) affect the observed
reduced forms but are not part of the target numerator or target denominator.
Thus the causal target is not defined as an observable contrast.  The
observable object \(P\) and restrictions \(\mathcal R_\eta^{\mathrm{ordIV}}\)
instead determine an identified set \(\Theta_I(P,\eta)\) of target values.
The theorem below proves containment and sharpness of that set.

\section{Main theorems}
\begin{proposition}[Monotone ordinal-IV reduction]\label{prop:monotone-reduction}
Under Assumptions~\ref{ass:finite-ordinal}--\ref{ass:defier-caps}, if
\(\eta_j=0\) for every \(j\), then every feasible full-data law has
\[
\theta^+_\omega
=
\frac{\sum_{j=0}^{J-1}\omega_j\Delta^Y_j}
     {\sum_{j=0}^{J-1}\omega_j\Delta^D_j},
\quad
\Delta^D_j=d_{j+1}-d_j,\quad
\Delta^Y_j=m_{j+1}-m_j,
\]
whenever the denominator is positive.  Equivalently, the sharp identified set
is a singleton equal to the adjacent-rung weighted Wald estimand.
\end{proposition}

This proposition confirms the Stage -1 monotone benchmark.  Its role is not
novelty relative to \cite{ImbensAngrist1994} and \cite{AngristImbens1995};
it verifies that the bounded-defier construction reduces to the familiar
ordered-monotonicity formula when the caps are zero.

\begin{proposition}[Sharp finite response-path bounds]\label{prop:finite-polytope}
Under Assumptions~\ref{ass:finite-ordinal}--\ref{ass:finite-types}, for every
nonempty feasible array \(P\) with positive target denominator,
\[
\Theta_I(P,\eta)
=
[\underline\theta_\omega(P,\eta),\overline\theta_\omega(P,\eta)].
\]
The lower and upper endpoints are attained by finite linear-fractional
programs over \((\pi_r,\mu_{0r},\mu_{1r})_{r\in\{0,1\}^{J+1}}\) satisfying the
constraints in Assumption~\ref{ass:finite-types}.  Because
\(B_\omega(\pi)>0\), each endpoint program is equivalent to a finite linear
program by Charnes--Cooper rescaling.
\end{proposition}

This proposition confirms the Stage -1 finite-polytope theorem.  It is the
sharpness analogue of the Balke--Pearl latent-table argument, with the
important difference that the latent type is one full ordinal treatment path.
That difference is the source of the strict pairwise gap in the next
proposition.

\begin{proposition}[Zig-zag compatibility strictly tightens pairwise bounds]\label{prop:zigzag-strict}
The pairwise-pasting interval is an outer relaxation:
\[
\Theta_I(P,\eta)\subseteq B_{\mathrm{pair}}(P,\eta)
\]
whenever Assumptions~\ref{ass:finite-ordinal}--\ref{ass:pairwise} hold and
the target denominator is positive.  The inclusion can be strict.  In the
three-rung witness class with \(J=2\), \(\omega_0=\omega_1=1\), take
\[
d=(1/5,2/5,4/5),\qquad
m=(3/5,1/5,2/5),\qquad
\eta=(3/5,2/5),
\]
and any strictly positive instrument cell probabilities \(p_z\).  Then the
global response-path upper endpoint is \(1/9\), whereas the pairwise-pasting
relaxation attains \(1/5\).  Hence
\[
[\underline\theta_\omega(P,\eta),\overline\theta_\omega(P,\eta)]
\subsetneq B_{\mathrm{pair}}(P,\eta).
\]
\end{proposition}

This proposition confirms Stage -1 Conjecture 1.  The mechanism is genuinely
ordinal: a path \(010\) is an up-complier on the first rung and a down-defier
on the second, while \(101\) has the opposite sign pattern.  Adjacent binary
programs can paste together effect assignments that no single ordinal
response-path law can realize.

\begin{proposition}[Cap-ray endpoint regularity; partial verdict on the kink claim]\label{prop:kink-partial}
Fix \(P\), \(J=2\), a positive ray \(v\in(0,\infty)^2\), and
\(\eta(s)=s v\).  On any interval of \(s\)-values for which the feasible
polytope is nonempty and \(B_\omega(\pi)>0\) for the evaluated target, the
endpoint functions
\[
s\mapsto \underline\theta_\omega(P,\eta(s)),
\qquad
s\mapsto \overline\theta_\omega(P,\eta(s))
\]
are piecewise linear-fractional.  Breakpoints occur only when the active basis
of the finite response-path endpoint program changes.  The stronger Stage -1
claim that there exist \(P\) and \(v\) whose first positive breakpoint is an
ordinal zig-zag compatibility facet is therefore reduced to a finite
active-basis certificate; this note does not prove that stronger existence
claim.
\end{proposition}

This is the verdict on Stage -1 Conjecture 2: partial.  The parametric
linear-fractional regularity is proved, but the proposed first-breakpoint
existence statement is not asserted without a separate rational active-basis
certificate.

\section{Interpretation}
The monotone reduction says that, when all adjacent down-defier masses are
ruled out, the observed reduced form on each rung equals the target numerator
contribution on that rung and the observed first stage equals the target
denominator contribution.  The adjacent weighted Wald ratio is then clean.

With positive defier caps, the same observed contrasts decompose as
\[
\Delta^D_j=q_j^+-q_j^-,
\qquad
\Delta^Y_j
=\E[(Y(1)-Y(0))\one\{U_j\}]
-\E[(Y(1)-Y(0))\one\{V_j\}].
\]
The target contains the up-complier terms but not the down-defier terms.
Thus a Wald-style ratio is contaminated by defier effect contributions unless
the caps, outcomes, or additional restrictions force those terms to vanish or
to be known.

The finite response-path bound is the exact way to account for this
contamination under the locked restrictions.  It allows every bounded
potential-outcome completion consistent with \(P\), but it requires all
adjacent appearances to come from one response path.  The pairwise relaxation
forgets that requirement, so it is always conservative and can be strictly
conservative.  The rational witness demonstrates that the tightening can be
substantive even with only first moments and only three instrument levels.

The bound collapses to point identification in the zero-cap monotone case.  It
widens toward the natural bounded-outcome IV envelope as the defier caps become
large, because the restrictions then place less control on the contaminating
terms.  The tightening work is done by the per-rung cap inequalities together
with the global path compatibility constraints, not by any regression
orthogonality or panel structure.

\section{Step-by-step proof}
\begin{lemma}[Adjacent first-stage and reduced-form identities]\label{lem:adjacent-identities}
Under Assumptions~\ref{ass:finite-ordinal} and~\ref{ass:ord-iv}, for each
adjacent rung \(j\),
\[
\Delta^D_j=q_j^+-q_j^-,
\]
and
\[
\Delta^Y_j
=\E[(Y(1)-Y(0))\one\{U_j\}]
-\E[(Y(1)-Y(0))\one\{V_j\}].
\]
\end{lemma}

\begin{proof}
By ordinal IV validity, the distribution of the full-data vector is the same
in every instrument cell.  Consistency gives
\[
d_z=\E[D\mid Z=z]=\E[D(z)].
\]
Therefore
\[
\Delta^D_j=\E[D(j+1)-D(j)].
\]
Since \(D(j+1)-D(j)\) equals \(1\) on \(U_j\), equals \(-1\) on \(V_j\), and
equals \(0\) otherwise, \(\Delta^D_j=q_j^+-q_j^-\).

Similarly, exclusion and consistency imply
\[
m_z=\E[Y\mid Z=z]=\E[Y(D(z))].
\]
Thus
\[
\Delta^Y_j
=\E[Y(D(j+1))-Y(D(j))].
\]
If the treatment does not change between \(j\) and \(j+1\), the integrand is
zero.  On \(U_j\) it is \(Y(1)-Y(0)\); on \(V_j\) it is
\(Y(0)-Y(1)\).  Taking expectations gives the displayed identity.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:monotone-reduction}]
Assumption~\ref{ass:defier-caps} and \(\eta_j=0\) imply \(q_j^-=0\) for every
\(j\).  Lemma~\ref{lem:adjacent-identities} then gives
\[
\Delta^D_j=q_j^+,\qquad
\Delta^Y_j=\E[(Y(1)-Y(0))\one\{U_j\}].
\]
Multiplying by \(\omega_j\), summing over \(j\), and using the positive
denominator condition in Assumption~\ref{ass:positive} gives the ratio in the
statement.  Because every feasible full-data law has the same ratio, the
identified set is the singleton containing that ratio.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:finite-polytope}]
The proof is a finite extreme-point and worst-case-completion argument in the
style of Balke--Pearl.

First prove necessity.  Take any full-data law satisfying
Assumptions~\ref{ass:finite-ordinal}--\ref{ass:finite-types}.  Define
\(\pi_r=\Pr(R=r)\) and
\(\mu_{dr}=\E[Y(d)\one\{R=r\}]\).  Bounded outcomes give
\(0\le\mu_{dr}\le\pi_r\).  Independence, exclusion, and consistency give the
moment equations in Assumption~\ref{ass:finite-types}.  The defier caps give
the cap inequalities.  Therefore the law induces a point of
\(\mathcal C(P,\eta)\), and its target value is
\(\psi_\omega(\pi,\mu)\).  This proves
\[
\Theta_I(P,\eta)
\subseteq
[\underline\theta_\omega(P,\eta),\overline\theta_\omega(P,\eta)].
\]

Now prove sufficiency.  Take any point \((\pi,\mu)\in\mathcal C(P,\eta)\).
Construct a canonical full-data law as follows.  Draw \(Z\) independently of
\((R,Y(0),Y(1))\) with \(\Pr(Z=z)=p_z\).  Draw \(R=r\) with probability
\(\pi_r\).  Conditional on \(R=r\), set \(Y(d)\) to be a Bernoulli random
variable with mean \(y_d(r)=\mu_{dr}/\pi_r\) if \(\pi_r>0\), and choose any
mean in \([0,1]\) if \(\pi_r=0\).  Set \(D=D(Z)\) and \(Y=Y(D)\).  The
constructed law satisfies ordinal IV validity, bounded outcomes, the positive
cell condition, and the defier caps.  Its observable first moments are exactly
the constraints defining \(\mathcal C(P,\eta)\), and its target value is
\(\psi_\omega(\pi,\mu)\).  Hence every feasible program value is attainable,
so the displayed containment is equality.

Finally, \(\mathcal C(P,\eta)\) is a closed and bounded finite-dimensional
polytope.  On the positive-denominator domain, the endpoint values are
attained by standard compactness after restricting to the feasible component
where \(B_\omega(\pi)>0\).  Charnes--Cooper rescaling sets
\[
T=\frac{1}{B_\omega(\pi)},\qquad
X_r=T\pi_r,\qquad
M_{dr}=T\mu_{dr},
\]
and adds the normalization
\[
\sum_j\omega_j\sum_{r:r_j=0,r_{j+1}=1}X_r=1.
\]
All constraints become linear in \((X,M,T)\), and the objective becomes the
linear form
\[
\sum_j\omega_j\sum_{r:r_j=0,r_{j+1}=1}(M_{1r}-M_{0r}).
\]
Thus each endpoint is the value of a finite linear program.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:zigzag-strict}]
The outer-bound part follows by marginalization.  Given any globally feasible
ordinal response-path law, restrict the path \(R\) to the adjacent pair
\((R_j,R_{j+1})\).  The resulting four-type binary table matches
\((d_j,m_j,d_{j+1},m_{j+1})\), preserves the same adjacent numerator
\(a_j\), denominator \(b_j\), and defier cap \(q_j^-\le\eta_j\).  Doing this
for every \(j\) maps a global feasible law into the product relaxation
\(\prod_j\mathcal F_j(P,\eta_j)\).  Therefore every global target value lies
in \(B_{\mathrm{pair}}(P,\eta)\).

It remains to prove strictness for the rational witness.  The first stages are
positive:
\[
\Delta^D_0=1/5,\qquad \Delta^D_1=2/5.
\]
The following global response-path table is feasible for \(P\) and \(\eta\):
\[
\begin{array}{c|ccccc}
r & 000 & 001 & 010 & 011 & 101\\ \hline
\pi_r & 1/10 & 3/10 & 1/10 & 3/10 & 1/5\\
y_0(r) & 1 & 0 & 0 & 1 & 0\\
y_1(r) & 0 & 1/3 & 1 & 0 & 1
\end{array}
\]
all omitted paths having mass zero.  It matches
\[
d=(1/5,2/5,4/5),\qquad m=(3/5,1/5,2/5),
\]
has \(q^-_0=1/5\le3/5\) and \(q^-_1=1/10\le2/5\), and gives
\[
B_\omega=9/10,\qquad N_\omega=1/10,\qquad \psi_\omega=1/9.
\]
To certify that no global feasible law has value above \(1/9\), apply
Charnes--Cooper normalization \(B_\omega=1\) and minimize \(-N_\omega\).  Use
the equality constraints in the order
\[
\sum X=T,\ d_0,\ d_1,\ d_2,\ m_0,\ m_1,\ m_2,\ B_\omega=1.
\]
The equality dual multipliers
\[
\left(0,-\frac{13}{9},-\frac49,\frac19,\frac{13}{9},-\frac49,-1,-\frac19\right)
\]
together with the following nonzero multipliers on constraints
\(M_{dr}\le X_r\),
\[
\begin{array}{c|cccccc}
(d,r) &(0,011)&(0,110)&(1,010)&(1,100)&(1,101)&(1,110)\\ \hline
\lambda_{d,r}&-4/9&-8/9&-5/9&-13/9&-13/9&-1
\end{array}
\]
and zero multipliers on all other upper-bound and cap inequalities form a
dual-feasible certificate for the minimization problem.  The nonzero reduced
costs on the nonnegative variables are
\[
\begin{array}{c|cccccc}
\text{variable}&X_{111}&M_{0,010}&M_{0,100}&M_{0,101}&M_{0,110}&M_{1,011}\\
\hline
\text{reduced cost}&16/9&5/9&13/9&13/9&17/9&4/9,
\end{array}
\]
with all omitted reduced costs equal to zero.  The dual objective is
\(-1/9\), so weak duality gives \(-N_\omega\ge-1/9\), or
\(N_\omega\le1/9\), for every globally feasible normalized solution.  The
displayed primal table attains \(1/9\), so the global upper endpoint is
\(1/9\).

By contrast, the pairwise relaxation attains \(1/5\).  For rung \(0\), use the
binary table
\[
\begin{array}{c|ccc}
(D(j),D(j+1))&00&01&10\\ \hline
\pi&2/5&2/5&1/5\\
y_0&1/2&1/2&0\\
y_1&0&0&1
\end{array}
\]
which matches \((d_0,m_0,d_1,m_1)\), has \(q^-_0=1/5\), and gives
\(a_0=-1/5\), \(b_0=2/5\).  For rung \(1\), use
\[
\begin{array}{c|ccc}
(D(j),D(j+1))&01&10&11\\ \hline
\pi&3/5&1/5&1/5\\
y_0&0&0&0\\
y_1&2/3&1&0
\end{array}
\]
which matches \((d_1,m_1,d_2,m_2)\), has \(q^-_1=1/5\), and gives
\(a_1=2/5\), \(b_1=3/5\).  Hence the pasted pairwise value is
\[
\frac{a_0+a_1}{b_0+b_1}
=\frac{-1/5+2/5}{2/5+3/5}
=\frac15.
\]
Since \(1/5>1/9\), the pairwise relaxation contains values excluded by the
sharp global ordinal response-path program.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{prop:kink-partial}]
Work in the original variables \((\pi,\mu)\), before Charnes--Cooper
rescaling.  For a fixed active set of equality constraints and binding
inequalities, the constraint matrix is constant and the right-hand side is
affine in the cap vector \(\eta(s)=s v\), because the only cap-dependent
constraints are
\[
\sum_{r:r_j=1,r_{j+1}=0}\pi_r\le s v_j.
\]
Therefore each basic feasible solution is affine in \(s\) on the interval
where that basis remains feasible.  At such a basis, both
\(N_\omega(\pi,\mu)\) and \(B_\omega(\pi)\) are affine functions of \(s\), and
the endpoint value is their ratio.  Because there are finitely many bases, the
lower and upper endpoints are piecewise linear-fractional, and breakpoints can
occur only when the active basis changes.  This proves the regularity claim.
It does not identify which basis changes first from \(s=0\); that requires an
additional certificate for a particular \(P\) and ray \(v\).
\end{proof}

\section{Sanity checks}
\paragraph{Binary-instrument reduction.}
If \(J=1\), there is only one adjacent rung.  The global response path has the
four binary principal strata \(00,01,10,11\), and the product relaxation has
only one factor.  Hence the pairwise-pasting comparator equals the global
sharp bound.  No zig-zag path can appear because there is no second rung on
which a type can switch back.

\paragraph{Full-monotonicity reduction.}
If \(\eta_j=0\) for all \(j\), Assumption~\ref{ass:defier-caps} gives
\(q_j^-=0\) for all \(j\).  Proposition~\ref{prop:monotone-reduction} then
recovers the ordered adjacent Wald estimand.  This is the zero-width,
point-identification special case.

\paragraph{Natural bounded-outcome envelope.}
If the defier caps are set to their vacuous values and no ordinal monotonicity
shape is imposed, the only remaining outcome restriction is \(Y(d)\in[0,1]\).
The response-path program then reduces to a Manski-style worst-case completion
over the unobserved potential-outcome means \(y_0(r),y_1(r)\), subject only to
matching the observed first moments.  The interval can be wide because the
contaminating defier terms in Lemma~\ref{lem:adjacent-identities} are no
longer controlled.

\paragraph{MTR specialization.}
If one additionally imposed monotone treatment response,
\(Y(1)\ge Y(0)\) pathwise, the endpoint program would add the linear
constraints \(\mu_{1r}\ge\mu_{0r}\) for all \(r\).  Those constraints are not
part of the locked tuple, but the specialization shows how a standard shape
restriction would tighten the same response-path polytope without changing the
observable array \(P\).

\paragraph{Balke--Pearl special case.}
For \(J=1\), the response-path sharpness argument is the binary-IV latent-type
argument of \cite{BalkePearl1997} with first moments rather than full outcome
cell probabilities.  The difference for \(J=2\) is not the LP technique; it is
the single shared ordinal path across adjacent binary margins.

\section{Counterexample or minimality check}
The strictness witness in Proposition~\ref{prop:zigzag-strict} is also the
minimality check for replacing the global response-path basis by adjacent
binary bases.  The pairwise construction reaches \(1/5\), but the global
ordinal program has upper endpoint \(1/9\).  Thus a formula that pastes
adjacent binary bounded-defier intervals is not sharp for the locked ordinal
target, even though each adjacent binary table is internally feasible and
matches its two observed cells.

The positive-cell condition is also necessary for the conditioning notation in
\(P^{(1)}\).  If some \(p_z=0\), the conditional means \(d_z\) and \(m_z\) are
not identified from the observable law without a separate convention for null
instrument cells.  The positive-denominator condition is necessary for the
target itself: if \(q_j^+=0\) for every rung with positive weight, then
\(\theta^+_\omega\) divides by zero and no LATE ratio exists.

For Stage -1 Conjecture 2, the nearest correct statement is
Proposition~\ref{prop:kink-partial}.  The locked assumptions imply finite
piecewise linear-fractional endpoint paths along a cap ray, but they do not by
themselves specify a rational \(P\) and ray \(v\) whose first positive
breakpoint is an ordinal zig-zag facet.  Establishing that stronger statement
requires a separate active-basis certificate analogous to the dual/primal
certificate used for Proposition~\ref{prop:zigzag-strict}.

\section{Formalization checklist}
\paragraph{Probabilistic objects and assumptions.}
\begin{itemize}[leftmargin=*]
\item Finite ordinal instrument: a finite set \(\{0,\ldots,J\}\) with
positive cell probabilities \(p_z>0\).
\item Binary treatment and bounded outcome: \(D\in\{0,1\}\) and
\(Y(0),Y(1)\in[0,1]\).
\item Full response path: \(R=(D(0),\ldots,D(J))\in\{0,1\}^{J+1}\), with path
mass function \(\pi_r\).
\item Ordinal IV validity: \(Z\) independent of \((R,Y(0),Y(1))\), plus
exclusion and consistency \(D=D(Z)\), \(Y=Y(D)\).
\item Adjacent events: \(U_j=\{R_j=0,R_{j+1}=1\}\) and
\(V_j=\{R_j=1,R_{j+1}=0\}\), with masses \(q_j^+\) and \(q_j^-\).
\item Defier caps: linear inequalities \(q_j^-\le\eta_j\).
\item Positive target denominator:
\(\sum_j\omega_j q_j^+>0\).
\end{itemize}

\paragraph{Deterministic finite-dimensional objects.}
\begin{itemize}[leftmargin=*]
\item Observable first-moment array:
\(P^{(1)}=\{p_z,d_z,m_z:z=0,\ldots,J\}\).
\item Outcome-mass variables:
\(\mu_{dr}=\pi_r y_d(r)\), constrained by \(0\le\mu_{dr}\le\pi_r\).
\item Moment equations:
\(\sum_r\pi_r r_z=d_z\) and
\(\sum_r\{r_z\mu_{1r}+(1-r_z)\mu_{0r}\}=m_z\).
\item Feasible polytope \(\mathcal C(P,\eta)\): all finite arrays satisfying
nonnegativity, moment equations, boundedness, and cap inequalities.
\item Target numerator and denominator:
\[
N_\omega=\sum_j\omega_j\sum_{r:r_j=0,r_{j+1}=1}(\mu_{1r}-\mu_{0r}),\quad
B_\omega=\sum_j\omega_j\sum_{r:r_j=0,r_{j+1}=1}\pi_r.
\]
\item Sharp endpoint functionals:
\(\inf N_\omega/B_\omega\) and \(\sup N_\omega/B_\omega\) over
\(\mathcal C(P,\eta)\) with \(B_\omega>0\).
\item Charnes--Cooper transformation:
\((\pi,\mu)\mapsto (X,M,T)=(\pi/B_\omega,\mu/B_\omega,1/B_\omega)\), turning
the endpoint problem into a linear program.
\end{itemize}

\paragraph{Lemmas and identities.}
\begin{itemize}[leftmargin=*]
\item Adjacent first-stage identity:
\(\Delta^D_j=q_j^+-q_j^-\), derived by case analysis on
\((D(j),D(j+1))\).
\item Adjacent reduced-form identity:
\(\Delta^Y_j=\E[(Y(1)-Y(0))\one\{U_j\}]
-\E[(Y(1)-Y(0))\one\{V_j\}]\), derived by consistency and case analysis.
\item Canonical sharpness construction: any feasible \((\pi,\mu)\) is realized
by drawing \(Z\) independently, drawing \(R\sim\pi\), and choosing bounded
potential outcomes with means \(\mu_{dr}/\pi_r\).
\item Pairwise outer-bound map: global ordinal feasible point
\(\mapsto\) adjacent binary feasible point by marginalizing
\((R_j,R_{j+1})\).
\item Strictness certificate: rational witness with global upper dual value
\(1/9\) and pairwise attainable value \(1/5\).
\item Parametric endpoint regularity: fixed active bases give affine
\((\pi,\mu)\) in the cap parameter and hence linear-fractional endpoint values.
\end{itemize}

\section{Conclusion and references}
The theorem-level contribution is a sharp finite response-path bound for the
weighted positive-rung ordinal-IV LATE under known adjacent down-defier caps.
The clean point-identification condition is exactly the zero-cap monotone
case, where every down-defier mass vanishes and the target equals the adjacent
weighted Wald ratio.  With positive caps, reduced forms contain contaminating
down-defier effect terms, and the sharp way to bound the target is to optimize
over one global ordinal response-path polytope.  The pairwise binary-IV
relaxation is always an outer bound and can be strictly too wide; the rational
three-rung witness proves the Stage -1 zig-zag compatibility claim.  The cap-ray
kink claim is partially resolved: endpoint paths are piecewise
linear-fractional, but a first-zig-zag-breakpoint theorem needs a separate
active-basis witness.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AngristImbens1995}
Angrist, J. D. and G. W. Imbens (1995).
\newblock Two-stage least squares estimation of average causal effects in
models with variable treatment intensity.
\newblock \emph{Journal of the American Statistical Association} 90(430),
431--442.
\newblock \url{https://doi.org/10.1080/01621459.1995.10476535}.

\bibitem{AngristImbensRubin1996}
Angrist, J. D., G. W. Imbens, and D. B. Rubin (1996).
\newblock Identification of causal effects using instrumental variables.
\newblock \emph{Journal of the American Statistical Association} 91(434),
444--455.
\newblock \url{https://doi.org/10.1080/01621459.1996.10476902}.

\bibitem{BalkePearl1997}
Balke, A. and J. Pearl (1997).
\newblock Bounds on treatment effects from studies with imperfect compliance.
\newblock \emph{Journal of the American Statistical Association} 92(439),
1171--1176.
\newblock \url{https://doi.org/10.1080/01621459.1997.10474074}.

\bibitem{DahlHuberMellace2023}
Dahl, C. M., M. Huber, and G. Mellace (2023).
\newblock It is never too LATE: a new look at local average treatment effects
with or without defiers.
\newblock \emph{The Econometrics Journal} 26(3), 378--404.
\newblock \url{https://doi.org/10.1093/ectj/utad013}.

\bibitem{deChaisemartin2017}
de Chaisemartin, C. (2017).
\newblock Tolerating defiance? Local average treatment effects without
monotonicity.
\newblock \emph{Quantitative Economics} 8(2), 367--396.
\newblock \url{https://doi.org/10.3982/QE601}.

\bibitem{HuberMellace2012}
Huber, M. and G. Mellace (2012).
\newblock Relaxing monotonicity in the identification of local average
treatment effects.
\newblock Economics Working Paper Series 1212, University of St. Gallen.
\newblock \url{https://ux-tauri.unisg.ch/RePEc/usg/econwp/EWP-1212.pdf}.

\bibitem{HuberMellace2015}
Huber, M. and G. Mellace (2015).
\newblock Testing instrument validity for LATE identification based on
inequality moment constraints.
\newblock \emph{Review of Economics and Statistics} 97(2), 398--411.
\newblock \url{https://doi.org/10.1162/REST_a_00450}.

\bibitem{ImbensAngrist1994}
Imbens, G. W. and J. D. Angrist (1994).
\newblock Identification and estimation of local average treatment effects.
\newblock \emph{Econometrica} 62(2), 467--475.
\newblock \url{https://www.nber.org/papers/t0118}.

\bibitem{Kitagawa2015}
Kitagawa, T. (2015).
\newblock A test for instrument validity.
\newblock \emph{Econometrica} 83(5), 2043--2063.
\newblock \url{https://doi.org/10.3982/ECTA11974}.

\bibitem{MogstadTorgovitskyWalters2021}
Mogstad, M., A. Torgovitsky, and C. R. Walters (2021).
\newblock The causal interpretation of two-stage least squares with multiple
instrumental variables.
\newblock \emph{American Economic Review} 111(11), 3663--3698.
\newblock \url{https://doi.org/10.1257/aer.20190221}.

\bibitem{Noack2021}
Noack, C. (2021).
\newblock Sensitivity of LATE estimates to violations of the monotonicity
assumption.
\newblock arXiv:2106.06421.
\newblock \url{https://arxiv.org/abs/2106.06421}.

\bibitem{SunWuthrich2025}
Sun, Z. and K. W\"uthrich (2025).
\newblock Pairwise valid instruments.
\newblock \emph{Journal of Econometrics} 250, 106009.
\newblock \url{https://doi.org/10.1016/j.jeconom.2025.106009}.

\bibitem{Vytlacil2002}
Vytlacil, E. (2002).
\newblock Independence, monotonicity, and latent index models: An equivalence
result.
\newblock \emph{Econometrica} 70(1), 331--341.
\newblock \url{https://doi.org/10.1111/1468-0262.00282}.
\end{thebibliography}

\end{document}
