% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_fold\_spectrum\_phase, specialization=v1
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{Fold-spectrum phase threshold for cross-fitted DML causal estimators}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{quote}\small
\begin{verbatim}
(qid, specialization) = (eid_dml_fold_spectrum_phase, v1)
anchor cluster = ExactID / causal-ML inference
graph / SWIG = observed O=(Y,D,X) with binary treatment D, potential
  outcomes (Y(1),Y(0)), observed outcome Y=D Y(1)+(1-D)Y(0), and
  covariates X satisfying consistency and conditional exchangeability
treatment = binary D in {0,1}
target estimand = theta_0 = E[Y(1)-Y(0)] = E[mu_1(X)-mu_0(X)]
  for mu_d(x)=E[Y | D=d,X=x]
identifying assumptions = consistency, conditional exchangeability,
  overlap e_min <= e_0(X) <= 1-e_min, finite fourth moments, and
  Neyman-orthogonal AIPW/DML scores
fold geometry = deterministic triangular-array partitions
  I_{1,n},...,I_{K_n,n} of {1,...,n}; c_{k,n}=|I_{k,n}|/n;
  c_n^min=min_k c_{k,n}; rho_n=sum_k c_{k,n}^2; nuisance learners
  eta_hat_{-k} are trained off I_{k,n}
estimator = DML2/AIPW root solving the fold-weighted score average
  n^{-1} sum_k sum_{i in I_{k,n}} psi(O_i;theta,eta_hat_{-k})=0
phase functional = the fold-spectrum certificate
  Gamma_n = max{ max_k c_{k,n}^{-1/2} R_{k,n},
                 sqrt(n) sum_k c_{k,n} R_{k,n}^2,
                 1/(n c_n^min) }
  with R_{k,n} the fold-specific nuisance L2 error envelope.
\end{verbatim}
\end{quote}

\begin{abstract}
Cross-fitted DML theory treats fold choice as asymptotically harmless under fixed, equal folds. This proposal asks whether that conclusion survives deterministic triangular arrays in which the evaluation-fold masses \(c_{k,n}\) are unequal, vanish, or approach leave-one-out geometry. The main conjecture is a phase theorem: a computable fold-spectrum certificate separates ordinary \(\sqrt n\) asymptotic linearity, inflated or slower small-fold regimes, and a no-splitting endpoint that requires leave-one-out stability. A calibration theorem records the equal-fold corner of \citet{ChernozhukovEtAl2018DML}. If the conjecture is correct, software that exposes custom folds can report a fold-geometry diagnostic before applying the usual DML standard error.
\end{abstract}

\section{Introduction}
Cross-fitting removes overfitting bias by training nuisance functions away from the observations used in the estimating score. The question is whether the standard DML first-order law is still the right law when the evaluation folds have a non-degenerate mass spectrum rather than equal mass.

\citet[Section~3.1]{ChernozhukovEtAl2018DML} defines DML through a \(K\)-fold partition with equal fold sizes, and \citet[Sections~5.2.1--5.2.3]{AhrensHansenSchafferWiemann2024DDML} exposes custom folds and repeated folds in software practice. \citet[abstract]{Velez2024DMLGrowingK} shows that changing the asymptotic fold regime can separate DML1 and DML2, but it does not characterize unequal evaluation-fold masses as the theorem object. The kernel lives in exact identification and causal-ML inference: the estimand is the ATE identified by the standard AIPW score, while the new object is the fold geometry of the estimating equation.

The direct consumer is applied DML practice using DoubleML or ddml when folds are clustered, deterministic, custom, or repeated. A reader who accepts the phase theorem would no longer treat \(K\) and the fold labels as bookkeeping; the fold-mass certificate becomes part of the inferential report.

\begin{itemize}[leftmargin=*]
\item Theorem 1: equal positive fold masses recover the usual DML asymptotic linear representation. Gap: \citet{ChernozhukovEtAl2018DML} proves this under equal folds; this theorem fixes the calibration corner for the fold-spectrum notation. Consumer: DML implementations following \citet{BachEtAl2024DoubleMLR}.
\item Conjecture 1: the fold-spectrum certificate \(\Gamma_n\) gives a three-phase frontier for root-\(n\) DML, small-fold slower limits, and leave-one-out endpoints. Gap: \citet{Velez2024DMLGrowingK} changes \(K\), and \citet{ChenSyrgkanisAustern2022NoSplitDML} changes the dependence condition; neither gives an unequal-fold mass threshold. Consumer: custom-fold and repeated-fold inference in \citet{AhrensHansenSchafferWiemann2024DDML}.
\item Conjecture 2: a two-fold triangular-array witness has the same target and nuisance rates as the equal-fold design but invalidates the usual score-variance report when \(c_{2,n}\to0\) and \(n c_{2,n}\) stays bounded. Gap: \citet{ChernozhukovEtAl2018DML} treats split randomness as finite-sample relevant, not as an asymptotic variance component. Consumer: variance reporting for custom folds in \citet{AhrensHansenSchafferWiemann2024DDML}.
\end{itemize}

\section{Related work}
\citet[Sections~3.1 and~3.4]{ChernozhukovEtAl2018DML} is the baseline reference because it defines DML1/DML2 with equal \(K\)-fold partitions and proves asymptotic linearity under product-rate and orthogonality conditions. Its finite-sample repeated-splitting discussion motivates, but does not solve, an asymptotic fold-geometry variance theorem.

\citet{ChernozhukovEtAl2017DMLAPP} gives the earlier treatment-effect DML presentation and fixes the AIPW score used here. It is cited only to identify the causal estimand, not as a fold-spectrum result.

\citet{BachEtAl2024DoubleMLR} is the software and implementation comparator because DoubleML reports score-based inference after \(K\)-fold sample splitting. The proposed certificate is meant to be evaluated before that report is trusted under unbalanced folds.

\citet[Sections~5.2.1--5.2.3]{AhrensHansenSchafferWiemann2024DDML} is the practice-facing comparator because ddml exposes \texttt{kfolds}, \texttt{foldvar}, repetitions, and fold-frequency tables. That interface creates exactly the deterministic custom-fold regimes studied here.

\citet[abstract]{Velez2024DMLGrowingK} is the closest asymptotic-regime comparator because it separates DML1 and DML2 when the fold count grows. The present proposal instead keeps the AIPW/DML2 score fixed and asks how the mass vector \((c_{k,n})\) changes the first-order law.

\citet[abstract]{ChenSyrgkanisAustern2022NoSplitDML} is the no-splitting endpoint comparator because it replaces cross-fitting by leave-one-out stability. Conjecture~\ref{conj:phase} treats that result as the limiting boundary, not as an ordinary cross-fitting theorem.

\citet{NeweyRobins2018CrossFittingFastRemainders} is relevant because different cross-fit constructions can change semiparametric remainder rates. The fold-spectrum certificate makes that dependence explicit through fold-specific remainder envelopes.

\citet{McGrathMukherjee2022NuisanceTuningSplitting} is adjacent because nuisance tuning and splitting choices jointly affect rates for doubly robust functionals. The present proposal freezes the target score and makes the allocation mass itself the focal object.

\citet{ChernozhukovNeweySingh2023FiniteSampleDML} translates nuisance rates into finite-sample DML inference conditions. It is a comparator for the rate-conversion pieces of \(\Gamma_n\), but it does not state a fold-allocation phase diagram.

\citet{ChiangKatoMaSasaki2022MultiwayDML} shows that changing the DML sampling geometry can require a new cross-fitting algorithm and variance formula. That paper supports the premise that fold geometry can be inferential, even though its geometry is multiway clustering rather than unequal evaluation folds.

The closest in-repo artifacts are the downgraded \texttt{eid\_dml\_orth\_uniform}/v1 and failed \texttt{eid\_dml\_orth\_uniform}/v2 proposals, which studied weak-overlap and DML/LRO/ADML studentization frontiers rather than fold-mass spectra. The downgraded \texttt{eid\_dml\_orthogonality\_frontier}/v1 proposal studied local Riesz critical radii for shrinking HTE reports; it is adjacent on DML rate frontiers but does not vary the cross-fitting partition.

\section{Formal setup}
Let \(O=(Y,D,X)\sim P_0\), with \(D\in\{0,1\}\), consistency, conditional exchangeability \((Y(1),Y(0))\perp D\mid X\), and overlap. Write \(e_0(x)=\Pr(D=1\mid X=x)\), \(\mu_d(x)=\E[Y\mid D=d,X=x]\), and
\[
  \theta_0=\E[\mu_1(X)-\mu_0(X)].
\]
For \(\eta=(\mu_0,\mu_1,e)\), define the orthogonal AIPW score
\[
  \psi(O;\theta,\eta)=\mu_1(X)-\mu_0(X)-\theta+
  \left\{\frac{D}{e(X)}-\frac{1-D}{1-e(X)}\right\}\{Y-\mu_D(X)\}.
\]
The true score is \(\psi_0(O)=\psi(O;\theta_0,\eta_0)\), and \(V_0=\E[\psi_0(O)^2]\in(0,\infty)\).

For each \(n\), let \(I_{1,n},\ldots,I_{K_n,n}\) be a deterministic partition of \(\{1,\ldots,n\}\), with \(m_{k,n}=|I_{k,n}|\), \(c_{k,n}=m_{k,n}/n\), \(c_n^{\min}=\min_k c_{k,n}\), and \(\rho_n=\sum_{k=1}^{K_n}c_{k,n}^2\). Let \(\hat\eta_{-k}\) be learned on the complement of \(I_{k,n}\). The estimator \(\hat\theta_n\) solves
\[
  \Psi_n(\theta)=\frac{1}{n}\sum_{k=1}^{K_n}\sum_{i\in I_{k,n}}
  \psi(O_i;\theta,\hat\eta_{-k})=0.
\]
Let
\[
  R_{k,n}=\|\hat\mu_{1,-k}-\mu_1\|_{2,I_k}+\|\hat\mu_{0,-k}-\mu_0\|_{2,I_k}+\|
  \hat e_{-k}-e_0\|_{2,I_k},
\]
where \(\|f\|_{2,I_k}^2=m_{k,n}^{-1}\sum_{i\in I_{k,n}}\E[f(O_i)^2]\). The focal fold-spectrum certificate is
\[
  \Gamma_n=\max\left\{
  \max_{k\le K_n}c_{k,n}^{-1/2}R_{k,n},\quad
  \sqrt n\sum_{k=1}^{K_n}c_{k,n}R_{k,n}^2,
  \quad \frac{1}{n c_n^{\min}}
  \right\}.
\]
The first component controls foldwise stochastic equicontinuity, the second controls the orthogonal second-order remainder, and the third records whether the smallest evaluation fold has a genuine empirical-process limit.

\paragraph{Locked parameters reproduced.}
\begin{quote}\small
\begin{verbatim}
(qid, specialization) = (eid_dml_fold_spectrum_phase, v1)
anchor cluster = ExactID / causal-ML inference
graph / SWIG = observed O=(Y,D,X) with binary treatment D, potential
  outcomes (Y(1),Y(0)), observed outcome Y=D Y(1)+(1-D)Y(0), and
  covariates X satisfying consistency and conditional exchangeability
treatment = binary D in {0,1}
target estimand = theta_0 = E[Y(1)-Y(0)] = E[mu_1(X)-mu_0(X)]
  for mu_d(x)=E[Y | D=d,X=x]
identifying assumptions = consistency, conditional exchangeability,
  overlap e_min <= e_0(X) <= 1-e_min, finite fourth moments, and
  Neyman-orthogonal AIPW/DML scores
fold geometry = deterministic triangular-array partitions
  I_{1,n},...,I_{K_n,n} of {1,...,n}; c_{k,n}=|I_{k,n}|/n;
  c_n^min=min_k c_{k,n}; rho_n=sum_k c_{k,n}^2; nuisance learners
  eta_hat_{-k} are trained off I_{k,n}
estimator = DML2/AIPW root solving the fold-weighted score average
  n^{-1} sum_k sum_{i in I_{k,n}} psi(O_i;theta,eta_hat_{-k})=0
phase functional = the fold-spectrum certificate
  Gamma_n = max{ max_k c_{k,n}^{-1/2} R_{k,n},
                 sqrt(n) sum_k c_{k,n} R_{k,n}^2,
                 1/(n c_n^min) }
  with R_{k,n} the fold-specific nuisance L2 error envelope.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[ATE identification and overlap]\label{ass:id}
The observed law satisfies consistency, conditional exchangeability \((Y(1),Y(0))\perp D\mid X\), and overlap \(e_{\min}\le e_0(X)\le1-e_{\min}\) almost surely for a constant \(e_{\min}>0\). The outcome has finite fourth moment.
\end{assumption}

\begin{assumption}[Orthogonal score regularity]\label{ass:orth}
The map \(\eta\mapsto \E[\psi(O;\theta_0,\eta)]\) is Neyman orthogonal at \(\eta_0\), the derivative in \(\theta\) equals \(-1\), and the second-order expansion is bounded by a constant times the product of outcome and propensity errors on each evaluation fold.
\end{assumption}

\begin{assumption}[Foldwise independence]\label{ass:split}
For each fold \(I_{k,n}\), \(\hat\eta_{-k}\) is measurable with respect to observations outside \(I_{k,n}\). Conditional on those training observations, the score summands indexed by \(I_{k,n}\) are independent with conditional variance converging to \(V_0\).
\end{assumption}

\begin{assumption}[Fold-spectrum regularity]\label{ass:spectrum}
The deterministic masses satisfy \(\sum_{k=1}^{K_n}c_{k,n}=1\), \(m_{k,n}\ge1\), and either \(c_n^{\min}\) is bounded away from zero, or the triangular-array limits of \(n c_n^{\min}\), \(\rho_n\), and \(\Gamma_n\) exist along a subsequence.
\end{assumption}

\begin{assumption}[Equal-fold calibration]\label{ass:equal}
For Theorem~\ref{thm:equal}, \(K\) is fixed, \(c_{k,n}=1/K+o(1)\) for every \(k\), \(\max_k R_{k,n}=o_p(1)\), and \(\sqrt n\max_k R_{k,n}^2=o_p(1)\).
\end{assumption}

\begin{assumption}[Open witness class]\label{ass:witness}
For Conjecture~\ref{conj:witness}, there is a two-fold design with \(c_{1,n}=1-a_n\), \(c_{2,n}=a_n\), \(a_n\downarrow0\), and \(n a_n\to\lambda\in(0,\infty)\). The nuisance learner on the large training set has fold-two prediction error whose conditional mean is zero and conditional variance has a nonzero limit on an open neighborhood of laws satisfying Assumption~\ref{ass:id}.
\end{assumption}

\begin{assumption}[Leave-one-out stability endpoint]\label{ass:loo}
When \(n c_n^{\min}\) is bounded, the no-splitting endpoint is admitted only if replacing one training observation changes each nuisance prediction by \(o_p(n^{-1/2})\) uniformly over the evaluation observations.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: equal-fold calibration]\label{thm:equal}
Under Assumptions~\ref{ass:id}--\ref{ass:equal},
\[
  \sqrt n(\hat\theta_n-\theta_0)=\frac{1}{\sqrt n}\sum_{i=1}^n\psi_0(O_i)+o_p(1),
  \qquad
  \sqrt n(\hat\theta_n-\theta_0)\rightsquigarrow N(0,V_0).
\]
The empirical score variance computed over all evaluation observations is consistent for \(V_0\).
\end{theorem}
The proof is the standard cross-fit DML expansion: conditional independence removes first-order overfitting terms, orthogonality bounds the foldwise remainder by \(\sum_k c_{k,n}R_{k,n}^2\), and the fixed equal-fold CLT applies to the oracle score average.

\begin{conjecture}[Conjecture 1: fold-spectrum phase theorem (NOT YET PROVED)]\label{conj:phase}
Under Assumptions~\ref{ass:id}--\ref{ass:spectrum}, the following trichotomy is sharp for the DML2/AIPW estimator.
\begin{enumerate}[label=(\roman*),leftmargin=*]
\item If \(\Gamma_n=o_p(1)\) and \(n c_n^{\min}\to\infty\), then the equal-fold representation in Theorem~\ref{thm:equal} remains valid, possibly with a design effect in the consistent variance estimator when folds are random and repeated.
\item If \(\max_k c_{k,n}^{-1/2}R_{k,n}\not\to0\) or \(\sqrt n\sum_k c_{k,n}R_{k,n}^2\not\to0\) while \(n c_n^{\min}\to\infty\), then \(\hat\theta_n\) has a slower or inflated first-order limit governed by the active fold components of \(\Gamma_n\).
\item If \(n c_n^{\min}\) is bounded, ordinary cross-fitting ceases to be the relevant asymptotic approximation; root-\(n\) DML can hold only under the leave-one-out stability endpoint in Assumption~\ref{ass:loo}.
\end{enumerate}
Moreover, each boundary is witnessed by an open class of triangular-array laws with the same identified ATE and the same pointwise nuisance-rate exponents.
\end{conjecture}

\begin{conjecture}[Conjecture 2: two-fold report-separation witness (NOT YET PROVED)]\label{conj:witness}
Under Assumptions~\ref{ass:id}, \ref{ass:orth}, \ref{ass:split}, and \ref{ass:witness}, there is an open class of two-fold triangular arrays for which
\[
  \sqrt n(\hat\theta_n-\theta_0)-\frac{1}{\sqrt n}\sum_{i=1}^n\psi_0(O_i)
  \rightsquigarrow Z_{\lambda},
\]
where \(Z_{\lambda}\) is non-degenerate and generated by the vanishing evaluation fold. On the same class, the usual empirical score variance over \(n\) observations converges to \(V_0\), but the variance of the centered estimator is \(V_0+\operatorname{Var}(Z_{\lambda})\).
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Balanced-fold reduction]\label{cor:balanced}
Under Assumptions~\ref{ass:id}--\ref{ass:equal}, Conjecture~\ref{conj:phase} reduces to Theorem~\ref{thm:equal} because \(c_n^{\min}\to1/K\), \(1/(n c_n^{\min})\to0\), and the certificate satisfies \(\Gamma_n=o_p(1)\) whenever the standard DML product-rate condition holds.
\end{corollary}

\begin{corollary}[No-splitting endpoint is not a cross-fitting corollary]\label{cor:loo}
If \(K_n=n\), then \(c_n^{\min}=1/n\) and the third component of \(\Gamma_n\) equals one. Thus Conjecture~\ref{conj:phase} cannot recover root-\(n\) inference from fold averaging alone; it must invoke the stability condition used by \citet{ChenSyrgkanisAustern2022NoSplitDML}.
\end{corollary}

\paragraph{Exhibit 9.1: fold-spectrum certificate on a two-fold instance.}
Let \(I_{1,n}\) have mass \(1-a_n\) and \(I_{2,n}\) have mass \(a_n\), with fold errors \(R_{1,n}=n^{-1/4}\) and \(R_{2,n}=b_n\). Then
\[
  \Gamma_n=\max\left\{(1-a_n)^{-1/2}n^{-1/4},\ a_n^{-1/2}b_n,
  \sqrt n\{(1-a_n)n^{-1/2}+a_nb_n^2\},\ (n a_n)^{-1}\right\}.
\]
For \(a_n=n^{-1/2}\) and \(b_n=n^{-1/4}\), \(\Gamma_n\ge a_n^{-1/2}b_n=1\), although the equal-fold product-rate expression \(\sqrt n b_n^2\) is constant and hides the fold mass. The denominators are positive for \(0<a_n<1\), and the two fold labels encode exactly two distinct evaluation distributions.

\paragraph{Exhibit 9.2: report separation is not a normalization artifact.}
In the witness of Assumption~\ref{ass:witness}, set \(n a_n\to\lambda\) and let the fold-two nuisance prediction perturbation contribute conditional variance \(\omega^2>0\) to the score average. The usual score report estimates \(V_0\), while the centered estimator has limit variance \(V_0+\omega^2\); multiplying both reports by the same \(\sqrt n\) scale leaves the additive \(\omega^2\) gap unchanged.

\section{Proof-sketch route}
For Theorem~\ref{thm:equal}: headline \(\leftarrow\) unfold \(\hat\theta_n\) and \(\psi\) definitions \(\leftarrow\) substitute Assumptions~\ref{ass:id}--\ref{ass:equal} \(\leftarrow\) Taylor expansion of the orthogonal score \(\leftarrow\) foldwise conditional mean-zero empirical-process bound \(\leftarrow\) Lindeberg CLT for the oracle score average. For Conjecture~\ref{conj:phase}: headline \(\leftarrow\) unfold \(\Gamma_n\) \(\leftarrow\) substitute Assumptions~\ref{ass:id}--\ref{ass:spectrum} \(\leftarrow\) prove a foldwise maximal inequality with mass-dependent constants \(\leftarrow\) derive the orthogonal second-order remainder with fold weights \(\leftarrow\) classify triangular-array CLT regimes by \(n c_n^{\min}\) \(\leftarrow\) construct boundary alternatives with equal pointwise nuisance exponents. For Conjecture~\ref{conj:witness}: headline \(\leftarrow\) unfold the two-fold design \(\leftarrow\) substitute Assumption~\ref{ass:witness} \(\leftarrow\) compute the conditional law of the small-fold score average \(\leftarrow\) show the empirical score variance omits the training-induced component \(\leftarrow\) verify openness by perturbing the cell probabilities and error variance.

\section{Honest scope flags}
Theorem~\ref{thm:equal} is a calibration theorem, not the novelty claim. Conjectures~\ref{conj:phase} and~\ref{conj:witness} are open and may need stronger empirical-process assumptions on the nuisance learner class. The proposal deliberately does not claim that all growing-\(K\) DML results fail; it claims that unequal evaluation-fold mass is a distinct theorem object. No v1 statement has been withdrawn.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft around the fold-spectrum certificate, phase theorem, and two-fold witness; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bach et~al.(2024)]{BachEtAl2024DoubleMLR}
Bach, P., V. Chernozhukov, M. S. Kurz, M. Spindler, and S. Klaassen (2024).
\newblock DoubleML: An object-oriented implementation of double machine learning in R.
\newblock \emph{Journal of Statistical Software} 108(3), 1--56.

\bibitem[Chernozhukov et~al.(2017)]{ChernozhukovEtAl2017DMLAPP}
Chernozhukov, V., D. Chetverikov, M. Demirer, E. Duflo, C. Hansen, and W. Newey (2017).
\newblock Double/debiased/neyman machine learning of treatment effects.
\newblock \emph{American Economic Review Papers and Proceedings} 107(5), 261--265.

\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., D. Chetverikov, M. Demirer, E. Duflo, C. Hansen, W. Newey, and J. Robins (2018).
\newblock Double/debiased machine learning for treatment and structural parameters.
\newblock \emph{The Econometrics Journal} 21(1), C1--C68.

\bibitem[Chernozhukov, Newey, and Singh(2023)]{ChernozhukovNeweySingh2023FiniteSampleDML}
Chernozhukov, V., W. Newey, and R. Singh (2023).
\newblock A simple and general debiased machine learning theorem with finite-sample guarantees.
\newblock \emph{Biometrika} 110(1), 257--264.

\bibitem[Chen, Syrgkanis, and Austern(2022)]{ChenSyrgkanisAustern2022NoSplitDML}
Chen, Q., V. Syrgkanis, and M. Austern (2022).
\newblock Debiased machine learning without sample-splitting for stable estimators.
\newblock \emph{NeurIPS}.

\bibitem[Chiang et~al.(2022)]{ChiangKatoMaSasaki2022MultiwayDML}
Chiang, H. D., K. Kato, Y. Ma, and Y. Sasaki (2022).
\newblock Multiway cluster robust double/debiased machine learning.
\newblock \emph{Journal of Business \& Economic Statistics} 40(3), 1046--1056.

\bibitem[McGrath and Mukherjee(2022)]{McGrathMukherjee2022NuisanceTuningSplitting}
McGrath, S. and R. Mukherjee (2022).
\newblock Nuisance tuning and sample splitting for doubly robust functionals.
\newblock arXiv:2212.14857.

\bibitem[Newey and Robins(2018)]{NeweyRobins2018CrossFittingFastRemainders}
Newey, W. K. and J. M. Robins (2018).
\newblock Cross-fitting and fast remainder rates for semiparametric estimation.
\newblock arXiv:1801.09138.

\bibitem[Velez(2024)]{Velez2024DMLGrowingK}
Velez, A. (2024).
\newblock On the asymptotic properties of debiased machine learning estimators.
\newblock arXiv:2411.01864.

\bibitem[Ahrens et~al.(2024)]{AhrensHansenSchafferWiemann2024DDML}
Ahrens, A., C. B. Hansen, M. E. Schaffer, and T. Wiemann (2024).
\newblock ddml: Double/debiased machine learning in Stata.
\newblock \emph{The Stata Journal} 24(1), 3--45.
\end{thebibliography}

\end{document}
