\begin{proof}[Proof of \cref{obj:thm:tv-envelope-design}]
Let
\[
c:=\frac{\sigma_0^2}{n}.
\]
The envelope-scale assumption gives \(c\ge 0\). We use this nonnegativity twice below, when pulling the scalar \(c\) through an infimum. % lean: div_nonneg

\begin{enumerate}
\item
First, \(W_\beta(p)\) is nonempty. Indeed, the order hypothesis gives \(\beta\ge 1\), the theorem assumes \(k\ge \beta\), and \(p\in S_{k,q}\). Hence \cref{obj:lem:unbiased-weight-set-nonempty} applies and gives a weight vector \(w\in W_\beta(p)\). % lean: unbiased_weight_set_nonempty

\item
Fix now any \(w\in W_\beta(p)\). By linearity of design expectation and by the defining mean-curve restriction in \(\mathcal P_\beta\),
\[
\mathbb E_\pi\!\left[\sum_{j=0}^k w_j\bar Y_j\right]
=
\sum_{j=0}^k w_j\,m_P(p_j).
\]
Since \(p\in S_{k,q}\), every node \(p_j\) lies in \([0,1]\), so the degree-\(\beta\) polynomial condition in \(\mathcal P_\beta\) gives
\[
m_P(p_j)=\sum_{\ell=0}^{\beta} a_{P,\ell}p_j^\ell .
\]
Substituting and interchanging the two finite sums,
\[
\sum_{j=0}^k w_jm_P(p_j)
=
\sum_{\ell=0}^{\beta}
a_{P,\ell}\sum_{j=0}^k w_jp_j^\ell .
\]
The moment equations defining \(W_\beta(p)\) give
\[
\sum_{j=0}^k w_jp_j^0=0,
\qquad
\sum_{j=0}^k w_jp_j^\ell=1
\quad(1\le \ell\le \beta).
\]
Thus the last display equals \(\sum_{\ell=1}^{\beta}a_{P,\ell}\). By \cref{obj:prop:rollout-polynomial-identity}, this is \(m_P(1)-m_P(0)\), proving the unbiasedness identity. % lean: rollout_polynomial_identity

\item
For the variance statement, apply \cref{obj:lem:variance-envelope-sharpness} with \(X_j=\bar Y_j\). Its hypotheses are exactly the nonnegative-scale assumption and the round-mean variance-envelope component of \(\mathcal P_\beta\). Therefore
\[
\operatorname{Var}_\pi\!\left(\sum_{j=0}^k w_j\bar Y_j\right)
\le
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2,
\]
and the same lemma supplies a positive semidefinite matrix \(\Gamma\) with
\[
\Gamma_{jj}\le \frac{\sigma_0^2}{n}
\quad\text{for all }j,
\qquad
\sum_{i=0}^k\sum_{j=0}^k w_i\Gamma_{ij}w_j
=
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2 .
\] % lean: variance_envelope_sharpness

\item
For the fixed schedule \(p\), the defining set on the left-hand side of the first envelope identity is
\[
\left\{c\,u:\ 
u=\left(\sum_{j=0}^k |w_j|\right)^2
\text{ for some }w\in W_\beta(p)
\right\}.
\]
Since \(c\ge0\), the infimum of this scalar multiple is \(c\) times the infimum of the unscaled set. By the definition of \(A_\beta(p)\) in \cref{obj:def:amplification-criterion}, this gives
\[
\inf\left\{
v:\ \exists w\in W_\beta(p),\
v=\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2
\right\}
=
\frac{\sigma_0^2}{n}A_\beta(p).
\] % lean: Real.sInf_smul_of_nonneg

\item
The same scalar-infimum argument applies after also varying the schedule. Namely,
\[
\left\{
v:\ \exists p'\in S_{k,q},\
v=c\,A_\beta(p')
\right\}
=
c\left\{
u:\ \exists p'\in S_{k,q},\
u=A_\beta(p')
\right\}.
\]
Using \(c\ge0\) and the definition of \(M_{\beta,k,q}\) in \cref{obj:def:amplification-criterion}, we obtain
\[
\inf\left\{
v:\ \exists p'\in S_{k,q},\
v=\frac{\sigma_0^2}{n}A_\beta(p')
\right\}
=
\frac{\sigma_0^2}{n}M_{\beta,k,q}.
\] % lean: Real.sInf_smul_of_nonneg

\item
Finally, suppose \(p^\star\in S_{k,q}\) and
\[
A_\beta(p^\star)=M_{\beta,k,q}.
\]
For any \(p'\in S_{k,q}\), the definition of \(M_{\beta,k,q}\) as the infimum over budgeted schedules gives
\[
M_{\beta,k,q}\le A_\beta(p').
\]
Hence \(A_\beta(p^\star)\le A_\beta(p')\). Multiplying by the nonnegative scalar \(c=\sigma_0^2/n\) yields
\[
\frac{\sigma_0^2}{n}A_\beta(p^\star)
\le
\frac{\sigma_0^2}{n}A_\beta(p'),
\]
as required. % lean: minimaxAmplification_le_of_budgeted
\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:chebyshev-minimax}]
\begin{enumerate}
\item By \cref{obj:lem:continuous-chebyshev-endpoint-bound}, choose constants
\(C_{\mathrm{ep}}(q_{\max})>0\) and \(c_{\mathrm{ep}}(q_{\max})>0\) such that, for
\(x_q=2/q-1\) and
\[
\lambda(q)=x_q+\sqrt{x_q^2-1},
\]
both the continuous endpoint upper bound and the Chebyshev endpoint lower bound hold uniformly
for \(0<q\le q_{\max}\). Set
\[
C_-(q_{\max})=c_{\mathrm{ep}}(q_{\max})^2 .
\]
Now fix \(c>1\). By \cref{obj:lem:oversampled-chebyshev-lobatto-norming}, choose
\(K(c)>0\), and set
\[
C_+(c,q_{\max})=\bigl(K(c)C_{\mathrm{ep}}(q_{\max})\bigr)^2 .
\]
% lean: chebyshev_minimax

\item Fix \(\beta,k,q\) satisfying the hypotheses. The low-budget cap gives
\(q\le q_{\max}<1\), hence \(q\le 1\). Since \(k\ge c\beta\), \(c>1\), and
\(\beta\ge1\), we have \(\beta\le k\), and in particular \(k\ge1\). Therefore
\cref{obj:lem:chebyshev-schedule-admissible} gives
\[
p^{\mathrm{Ch}}(k,q)\in S_{k,q}.
\]
Also,
\[
\lambda(q)=\frac{(1+\sqrt{1-q})^2}{q},
\]
by the elementary algebraic identity for the exterior Chebyshev parameter.
% lean: chebyshev_lambda_eq_rho_div_q

\item We first prove the lower bound for an arbitrary \(p\in S_{k,q}\). Since
\(\beta\le k\), \(\beta\ge1\), and \(p\in S_{k,q}\), \cref{obj:lem:unbiased-weight-set-nonempty}
makes \(W_\beta(p)\) nonempty; the strict ordering in \(S_{k,q}\) gives distinct nodes.
Thus \cref{obj:lem:amplification-dual-norm} applies.

Consider
\[
r(u)=T_\beta\!\left(\frac{2u}{q}-1\right).
\]
This polynomial has degree at most \(\beta\). For every rollout node \(p_j\), admissibility gives
\(0\le p_j\le q\), hence \(2p_j/q-1\in[-1,1]\), so \(|r(p_j)|\le1\). Therefore \(r\) is an
admissible dual test polynomial. The endpoint lower bound from
\cref{obj:lem:continuous-chebyshev-endpoint-bound} gives
\[
T_\beta(x_q)-1\ge c_{\mathrm{ep}}(q_{\max})\lambda(q)^\beta .
\]
Since \(x_q>1\), \(T_\beta(x_q)\ge0\), and \(|T_\beta(-1)|\le1\), the reverse triangle
inequality yields
\[
T_\beta(x_q)-1
\le |T_\beta(x_q)-T_\beta(-1)|
=|r(1)-r(0)|.
\]
Hence the dual supremum is at least \(c_{\mathrm{ep}}(q_{\max})\lambda(q)^\beta\), and after
squaring,
\[
A_\beta(p)\ge c_{\mathrm{ep}}(q_{\max})^2\lambda(q)^{2\beta}
=
C_-(q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}.
\]
% lean: chebyshev_amplification_lower

\item For the Chebyshev--Lobatto schedule, apply the same dual characterization. Let \(r\) be
any degree-at-most-\(\beta\) dual polynomial with
\(\max_j |r(p^{\mathrm{Ch}}_j(k,q))|\le1\), and put
\[
R(x)=r\!\left(\frac q2(x+1)\right).
\]
Then \(\deg(R)\le\beta\), and the Lobatto nodes
\(-\cos(\pi j/k)\) are mapped exactly to \(p^{\mathrm{Ch}}_j(k,q)\). Hence the discrete
Lobatto maximum of \(|R|\) is at most \(1\). The oversampled norming inequality gives
\[
|R(x)|\le K(c)\qquad (x\in[-1,1]).
\]
Thus \(K(c)^{-1}R\) is bounded by \(1\) on \([-1,1]\). Applying the endpoint upper bound from
\cref{obj:lem:continuous-chebyshev-endpoint-bound} gives
\[
K(c)^{-1}|r(1)-r(0)|
\le C_{\mathrm{ep}}(q_{\max})\lambda(q)^\beta,
\]
because \(x_q\) maps to \(1\) and \(-1\) maps to \(0\). Taking the supremum over all such \(r\)
and squaring,
\[
A_\beta\!\left(p^{\mathrm{Ch}}(k,q)\right)
\le
\bigl(K(c)C_{\mathrm{ep}}(q_{\max})\bigr)^2\lambda(q)^{2\beta}
=
C_+(c,q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}.
\]
% lean: chebyshev_amplification_upper

\item The first two displayed inequalities are exactly the bounds just proved. For the minimax
lower bound, the lower estimate holds for every \(p\in S_{k,q}\), and the schedule class is
nonempty because \(p^{\mathrm{Ch}}(k,q)\in S_{k,q}\). Taking the infimum over \(S_{k,q}\) gives
\[
M_{\beta,k,q}
\ge
C_-(q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}.
\]
For the minimax upper bound, use the admissible schedule \(p^{\mathrm{Ch}}(k,q)\) in the
infimum and then apply the Chebyshev upper bound:
\[
M_{\beta,k,q}
\le
A_\beta\!\left(p^{\mathrm{Ch}}(k,q)\right)
\le
C_+(c,q_{\max})
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta}.
\]
This proves the claimed two-sided minimax estimate.
% lean: minimaxAmplification_lower_of_forall
\end{enumerate}
\end{proof}
