\begin{abstract}
This paper studies how to place measurement rounds in a finite-population rollout experiment when the target is the full-adoption contrast but the rollout budget stops at a treated fraction \(q<1\). Under static rollout consistency, a degree-\(\beta\) polynomial restriction on the rollout mean curve, and a common round-mean variance envelope, unbiased linear estimation reduces to a polynomial extrapolation problem from \([0,q]\) to \(1\). For a fixed schedule, the sharp envelope variance is the variance scale times the squared \(\ell^1\) norm of the polynomial-exact weights. The resulting amplification criterion is minimized, up to constants, by shifted Chebyshev-Lobatto measurement fractions when \(q\le q_{\max}<1\) and the number of rollout intervals satisfies \(k\ge c\beta\) for some \(c>1\). The minimax amplification rate is
\[
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta},
\]
with constants depending only on \(q_{\max}\) and the oversampling ratio. For the exact nested rollout covariance problem, the same Chebyshev schedule is rate-feasible through the envelope bound, and exact optimality under the true rollout covariance structure is posed as a separate covariance-specific design question.
\end{abstract}

\section{Introduction}
Rollout experiments often measure outcomes before full adoption. A platform may expose a small treated fraction before scaling a feature, a policy maker may expand access in stages, or a researcher may observe several rollout fractions strictly below the endpoint at which everyone is treated. Under interference, the treated-fraction mean response follows a rollout curve that can extend beyond the convex-combination structure of two no-interference potential outcomes. The full-adoption contrast must then be inferred from the response curve traced out by the rollout.

This paper studies the design problem of where to place the rollout measurement fractions. The estimand is the endpoint contrast \(m_P(1)-m_P(0)\), while the experiment observes round means on the truncated interval \([0,q]\), with \(q\le q_{\max}<1\). The design variable is the ordered schedule of treated fractions between the untreated baseline and the budget endpoint. The analysis is finite-population and design-based. \Cref{obj:ass:static-rollout-consistency} gives a static rollout potential-outcome interpretation indexed by contemporaneous assignments; \cref{obj:ass:beta-order-polynomial} restricts the rollout mean curve to be a polynomial of degree at most \(\beta\); and \cref{obj:ass:round-mean-variance-envelope} bounds each round mean variance by a common scale \(\sigma_0^2/n\).

Under these conditions, the statistical problem becomes a polynomial extrapolation problem. \Cref{obj:prop:rollout-polynomial-identity} identifies the endpoint contrast with the sum of the nonconstant coefficients of the rollout mean curve. \Cref{obj:def:unbiased-weight-set} then characterizes linear weights that are unbiased for every degree-\(\beta\) rollout mean curve by exactness on the monomials \(1,u,\ldots,u^\beta\). \Cref{obj:thm:tv-envelope-design} shows that, when cross-round covariances are left unrestricted except for positive semidefiniteness and the diagonal variance envelope, the sharp worst-case variance bound for a linear unbiased estimator is
\[
\frac{\sigma_0^2}{n}\left(\sum_{j=0}^k |w_j|\right)^2.
\]
Thus the schedule affects the envelope risk only through the smallest squared \(\ell^1\) norm of polynomial-exact weights, the amplification criterion \(A_\beta(p)\) in \cref{obj:def:amplification-criterion}.

The main design result is \cref{obj:thm:chebyshev-minimax}. For any fixed low-budget cap \(q_{\max}\in(0,1)\), any oversampling ratio \(c>1\), and any \(k\ge c\beta\), every admissible schedule has amplification at least a constant times
\[
\left(\frac{(1+\sqrt{1-q})^2}{q}\right)^{2\beta},
\]
uniformly over \(0<q\le q_{\max}\). The shifted Chebyshev-Lobatto schedule in \cref{obj:def:chebyshev-schedule} attains the same rate up to a constant depending only on \(c\) and \(q_{\max}\). The result is therefore a rate-minimax statement for the envelope criterion: low-budget extrapolation carries an exponential cost in the polynomial order, and endpoint-clustered Chebyshev-Lobatto placement controls the exponent that is unavoidable under the stated envelope.

The full-budget boundary clarifies what drives this cost. \Cref{obj:prop:no-extrapolation-boundary} shows that when \(q=1\), the endpoint contrast can be estimated by the difference between the final and baseline round means with amplification at most \(4\), independent of \(\beta\). The exponential factor in \cref{obj:thm:chebyshev-minimax} is therefore specifically the price of estimating an endpoint outside the observed rollout interval.

The exact nested covariance problem is kept separate. \Cref{obj:def:exact-nested-risk} leaves inside the minimax problem the covariance matrix generated by the monotone Bernoulli rollout law, and \cref{obj:oeq:exact-nested-minimax} poses exact optimality for that narrower problem. The proved result is the one-sided comparison in \cref{obj:lem:exact-risk-envelope-upper}: at every admissible schedule, the exact finite-population risk is bounded above by the envelope amplification criterion. Consequently, \cref{obj:lem:exact-chebyshev-rate-feasible} establishes the displayed low-budget exponential upper bound for the exact rollout risk attained by the Chebyshev-Lobatto schedule.

The paper contributes to the design-based interference literature by making the treated-fraction schedule itself the object of minimax analysis. Classical potential-outcome formulations treat no-interference experiments as the baseline case \citep{cox1958,rubin1974,imbens2015}, while social-interaction and interference settings make spillovers part of the estimand rather than only a nuisance dependence structure \citep{manski1993,manski2013}. Modern work has developed exposure mappings, randomization-based estimators, graph cluster designs, and randomization tests under interference \citep{aronow2017,savje2017,eckles2017,ugander2013,athey2018,basse2019,puelz2019}. The closest line of work is the low-order network-interference and rollout literature, where polynomial structure permits identification of global treatment effects from partial exposure or staged adoption \citep{cortez2022,cortezrodriguez2022,cortezrodriguez2024,eichhorn2024}. The present analysis keeps that polynomial-extrapolation structure but asks a different design question: conditional on a rollout budget, where should the measurement fractions be placed?

The answer uses classical ideas from optimal design and approximation theory. Polynomial-regression design and equivalence theory provide the language for optimizing measurement locations \citep{smith1918,kiefer1959,kiefer1974,pukelsheim1993}, and Chebyshev systems explain why endpoint-spread nodes control polynomial extrapolation \citep{karlin1966}. Here those approximation facts enter through the dual representation in \cref{obj:lem:amplification-dual-norm}: minimizing the \(\ell^1\) norm of unbiased weights is equivalent to controlling the largest endpoint contrast among degree-\(\beta\) polynomials bounded at the schedule nodes. The formal statements and proofs are machine-checked in Lean 4 to the extent recorded in the verification note in the appendix.
