\section{Appendix: verification note}

This appendix records the verification scope for the formal statements used in the paper. The observed-data experiment, causal overlay, Hölder dose class, target functional, minimax risk, published benchmark sequence, auxiliary testing statements, algebraic rate comparisons, and lower-bound consequences are represented by the numbered assumptions, definitions, lemmas, propositions, theorems, and remarks displayed in the paper. The corresponding theorem statements and their derivations are machine-checked in Lean~4.

The machine-checked part covers the consequences of the stated assumptions and auxiliary lemmas as they are formulated here. In particular, \cref{obj:ass:iid-sampling}--\cref{obj:ass:baseline-submodel-slack} define the statistical and causal restrictions used by the displayed results; \cref{obj:def:theta-functional}, \cref{obj:def:holder-dose-class}, \cref{obj:def:minimax-risk}, and~\cref{obj:def:published-hoif-rate} fix the target, model class, risk, and comparison sequence; and the auxiliary appendix lemmas supply the testing and algebraic inputs used to derive \cref{obj:thm:sharp-pointwise-lower-bound}, \cref{obj:thm:sharp-minimax-smooth-covariate}, and~\cref{obj:thm:frontier-bracket-deficient} together with \cref{obj:prop:oracle-regime-reduction}. The verification establishes the same-class lower-bound and rate-comparison statements, with the upper frontier identified as a separate research question.

Several ingredients enter as mathematical assumptions or cited comparators. The causal identification primitives in \cref{obj:ass:consistency} and~\cref{obj:ass:no-unmeasured-confounding} are imposed conditions on the observed-data law with its potential-outcome interpretation. The formal argument uses the classical Le Cam minimax reduction at the level of the auxiliary testing lemma stated in the appendix and verifies its consequences for the present model and rates. The Bonvini--Kennedy result in \cref{obj:lem:published-upper-bound-cited}, imported from \citet{bonvini2022}, motivates the benchmark sequence \(\rho_n\) on its localized-regularity class; \cref{obj:def:holder-dose-class} specifies the distinct same-class lower-bound model studied here.

The Lean-oriented labels are therefore confined to cross-references and this reproducibility note. In the main text they serve only to identify the precise assumptions and statements being invoked. The econometric content of the paper is the lower bound over \cref{obj:def:holder-dose-class}, the algebraic comparison with \cref{obj:def:published-hoif-rate}, and the explicit separation between those same-class lower results and the external higher-order influence-function comparator.
