% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orthogonality\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_dml\_orthogonality\_frontier} / \texttt{v1}%
  \\ \large\textit{CEINR-admissible LRO normalizations are DML/ADML-equivalent exactly at a primitive full-report Gram frontier}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This proposal uses the ExactID/free-form convention
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
The locked tuple is
\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_dml\_orthogonality\_frontier},\qquad
\texttt{specialization}=\texttt{v1},\\
\text{graph/SWIG}=X\to D\to Y,\; X\to Y,\quad
\text{treatment }D\in\{0,1\},\\
\text{target estimand }\theta_0=\E[Y(1)-Y(0)],\\
\text{identifying assumptions}=\text{consistency, conditional exchangeability }
(Y(1),Y(0))\perp D\mid X,\\
\text{overlap }\epsilon\le p_0(X)\le 1-\epsilon,\text{ square-integrability, and}\\
\text{the CEINR-admissible LRO report restrictions in
Assumptions \ref{ass:ate-model}--\ref{ass:finite-support}.}
\end{gathered}
\]
The estimator reports compared are the DML AIPW report, the ADML Riesz-score
report, and ATE-specialized locally robust semiparametric GMM reports generated
by Chernozhukov--Escanciano--Ichimura--Newey--Robins style first-step
influence-function dictionaries.  The focal mathematical object is the
\emph{CEINR full-report Gram certificate}
\[
\Xi_J(P)=\big(U_J(P),S_J(P),T_J(P)\big),
\]
where \(U_J\) is the nonresidual plug-in defect, \(S_J\) is the
residual-variance span defect of the LRO dictionary for the ATE Riesz
representer, and \(T_J\) is the residual-variance normal-equation defect of the
published GMM aggregation row.  Report equivalence means identical first-order
influence function and identical first-order variance report, not only
identical residual loading.

\begin{abstract}
Double machine learning, locally robust semiparametric GMM, and automatic DML
can all target the unconfounded binary ATE, but this common target does not make
every locally robust GMM normalization first-order report-equivalent to the DML
AIPW or ADML Riesz score.  This pivot asks for a primitive characterization of
which CEINR-admissible LRO dictionaries, Jacobians, and GMM weights reproduce
the ATE Riesz representer before collapsing the comparison to the already-known
canonical-gradient uniqueness theorem.  The flagship conjecture states that an
ATE-specialized LRO report is DML/ADML-equivalent exactly when its full-report
Gram certificate \(\Xi_J(P)=(U_J,S_J,T_J)\) vanishes: the aggregated
nonresidual component must equal \(m_1(X)-m_0(X)-\theta_0\), the dictionary must
span the ATE Riesz direction in \(L^2(\nu_P)\), and the published
\((A_J^\transpose W_JA_J)^{-1}A_J^\transpose W_J\) aggregation row must select a
Riesz coefficient vector.  A second conjecture asks for a relatively open
CEINR-admissible overidentified finite-support class, with an explicit two-cell
witness, where the plug-in and span checks hold but alignment fails, producing
an auditable influence-function and variance-report separation.  Resolving the proposal
would tell applied users when LRO, DML, and
ADML standard errors are interchangeable and when the chosen LRO normalization
must be reported as a different first-order object.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
The unconfounded ATE has a unique efficient influence function in the
nonparametric model, but modern estimators arrive at that object through
different constructions.  DML writes the AIPW score directly, ADML learns the
Riesz representer, and LRO starts from a broad locally robust GMM moment
dictionary and then aggregates moments through a Jacobian and weight matrix.
Without a primitive normalization test, it is too easy to say that all three
reports are equivalent simply because the ATE efficient influence function is
unique, or to claim non-equivalence from arbitrary loadings that no published
LRO construction would generate.

\paragraph{The main finding (proposed).}
Theorem \ref{thm:baseline} records the known ExactID calibration: under
unconfoundedness the DML AIPW and ADML Riesz population reports share the
canonical ATE influence function.  Conjecture \ref{conj:gram-frontier} is the
flagship kernel.  It defines the dictionary Gram matrix \(G_J\), the Riesz
cross-moment \(c_J\), and the GMM aggregation row
\(\kappa_J=W_JA_J(A_J^\transpose W_JA_J)^{-1}\), and conjectures that a
CEINR-admissible LRO report is first-order report-equivalent to DML/ADML if
and only if
\[
U_J=0,\qquad S_J=q_0-c_J^\transpose G_J^+c_J=0,\qquad
T_J=(G_J\kappa_J-c_J)^\transpose G_J^+(G_J\kappa_J-c_J)=0.
\]
Conjecture \ref{conj:witness} then promotes the two-covariate-cell witness to a
relative-open separation class \(\mathcal O_{\mathrm{sep}}\) of
CEINR-admissible overidentified dictionaries with cell probabilities,
nonresidual rows, residual loadings, \(A_J\), and \(W_J\) for which the algebra
gives \(U_J=S_J=0<T_J\) and \(\Delta_J>0\).  This shows that dictionary richness
and correct plug-in normalization together do not force the LRO GMM report to
select the Riesz direction.

\paragraph{What is new.}
\citet[\S2, eqs.\ (2.2)--(2.3), and \S2, eq.\ (2.8)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} give a
general locally robust semiparametric GMM construction and its variance-report
map, while their \S2.3 equations (2.10)--(2.11) anchor the automatic
first-step influence-function/Riesz estimation problem rather than the GMM
report row itself.  In parallel,
\citet[\S3]{ChernozhukovEtAl2018DML} and
\citet[\S2--\S3]{ChernozhukovNeweySingh2022AutoDML} give DML and ADML routes to
orthogonal ATE scores.  \citet{Newey1994Econometrica},
\citet{Hahn1998Econometrica}, and \citet{HiranoImbensRidder2003Econometrica}
make the canonical ATE efficient influence function a settled baseline.  The
epsilon-gap is therefore deliberately narrow but not tautological: the proposal
does not rediscover the ATE EIF and does not define a frontier as
\(\alpha_J=\alpha_0\); it asks for the primitive three-part certificate
\(\Xi_J=(U_J,S_J,T_J)\) on CEINR-admissible dictionaries, Jacobians, and weights
that decides whether the published LRO aggregation row lands on the full
ADML/DML influence function.  Relative to the general projection and
influence-function comparators in \citet[\S3--\S4]{Newey1994Econometrica} and
\citet[\S2--\S4]{IchimuraNewey2022QE}, the added object is the CEINR
normalization frontier: it separates residual span from the row selected by
the published GMM weight/Jacobian map and gives an empirical diagnostic target.
This targets the exact strengthening path left by the failed
prior CausalSmith \texttt{eid\_dml\_orth\_uniform/v2} angle: replace a residual
\(L^2\) restatement with necessary-and-sufficient conditions on admissible
dictionaries, Jacobians, and weights.

\paragraph{How it positions in the literature.}
The anchor cluster is ExactID.  The causal estimand is point-identified by the
standard back-door/unconfoundedness formula; the proposal studies first-order
inference reports after identification rather than a new adjustment criterion.
Methodologically it sits at the intersection of DML, semiparametric efficiency,
locally robust GMM, and automatic Riesz debiasing.

\paragraph{Implications for the community.}
The concrete downstream consumer is the ATE implementation workflow in
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}: the conjecture would
tell users exactly which ATE-specialized LRO moment dictionaries and weights
may share a DML/ADML standard error, and which require a distinct report.

\paragraph{How research benefits from the conclusion.}
Researchers should check \(\Xi_J(P)\), or an empirical analogue of it, before
treating an overidentified LRO ATE report as interchangeable with DML or ADML.

\section{Related work}
\citet[\S2, eqs.\ (2.2)--(2.3), and \S2, eq.\ (2.8)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO} is the primary
published anchor: it constructs locally robust semiparametric GMM moments and
standard-error reports from first-step influence-function adjustments.  Its
\S2.3 equations (2.10)--(2.11) are used here only for the automatic
alpha/Riesz first-step estimation problem, not as the source of the GMM
aggregation row; the missing classification is which ATE-specialized
dictionaries and GMM normalizations reproduce the ATE Riesz report.
\citet{ChernozhukovEtAl2018DML} is the DML baseline: it
specifies orthogonal AIPW-type scores and cross-fitting for treatment effects
under sufficient nuisance-rate conditions.  \citet{ChernozhukovNeweySingh2022AutoDML}
is the ADML baseline: it obtains debiased machine learning scores by estimating
Riesz representers for causal and structural functionals.  \citet{ChernozhukovNeweySingh2022Riesz}
develops regularized Riesz regression for global and local linear functionals,
which motivates treating the Riesz direction as the object that LRO must match.
\citet[\S3--\S4]{Hansen1982Econometrica} supplies the overidentified GMM
aggregation, asymptotic distribution, and over-identifying-restriction
benchmark; this proposal asks when that aggregation selects the ATE Riesz
coefficient vector.  \citet{BrunsSmithDukesFellerOgburn2025ABW} characterizes
augmented balancing weights and AutoDML as linear regression when outcome and
weighting models are linear in a basis; it is the closest Riesz/AutoDML
equivalence comparator, but it does not study CEINR locally robust GMM
dictionaries or the \(A_J,W_J\) aggregation row.  \citet{Newey1994Econometrica} gives the
pathwise-differentiability and semiparametric efficiency framework that makes
the canonical gradient a property of the model and parameter, not of an
estimator label.  \citet{IchimuraNewey2022QE} gives a modern influence-function
representation for semiparametric estimators with nonparametric first steps,
which is the closest general influence-function comparator.  \citet{Hahn1998Econometrica}
derives efficiency bounds for ATE/ATT under propensity-score selection on
observables; this is part of the settled efficient-influence-function baseline.
\citet{HiranoImbensRidder2003Econometrica} shows that estimating the propensity
score can improve ATE efficiency, reinforcing why the exact first-order report
matters.  \citet{RobinsRotnitzkyZhao1994JASA} is the augmented-IPW ancestor for
semiparametric regression with missingness/nonresponse, and it supplies the
historical AIPW lineage behind the binary-treatment score.

In-repo prior art is nonduplicative.  The \texttt{doc/API.md} ExactID catalogue
section records that \texttt{CausalSmith/ExactID/} is empty at seed time, so
there is no banked ExactID theorem classifying DML/LRO/ADML ATE reports.  The
closest prior CausalSmith signal is the failed
\texttt{eid\_dml\_orth\_uniform/v2} angle whose Stage -0.5 reviewer requested
``primitive necessary-and-sufficient conditions on CEINR admissible
dictionaries, Jacobians, and weights'' rather than the residual
\(\rho=0\) restatement.  This proposal is exactly that pivot: its focal object
is the primitive full-report Gram certificate \(\Xi_J=(U_J,S_J,T_J)\), not a new ATE
estimand and not an assumed DML/LRO/ADML variance ordering.

\section{Formal setup}
Let \(O=(Y,D,X)\sim P\), where \(D\in\{0,1\}\), \(Y\in\R\), and \(X\) lies in
a measurable covariate space \(\mathcal X\).  Potential outcomes
\((Y(1),Y(0))\) obey consistency and conditional exchangeability.  Write
\[
m_d(x)=\E[Y\mid D=d,X=x],\qquad p_0(x)=\Pr(D=1\mid X=x),
\qquad \theta_0=\E[m_1(X)-m_0(X)].
\]
The binary-ATE Riesz representer and canonical ATE influence function are
\[
\alpha_0(D,X)=\frac{D}{p_0(X)}-\frac{1-D}{1-p_0(X)},
\]
\[
\varphi_0(O)=m_1(X)-m_0(X)-\theta_0+\alpha_0(D,X)\{Y-m_D(X)\}.
\]
Write
\[
\mu_0(X)=m_1(X)-m_0(X)-\theta_0
\]
for the nonresidual plug-in component of the canonical influence function.
Let \(e=Y-m_D(X)\), and define the residual-variance measure \(\nu_P\) on
\((D,X)\) by
\[
\nu_P(B)=\E[\one\{(D,X)\in B\}e^2].
\]
Thus equality of residual loadings is understood in the quotient \(L^2(\nu_P)\).

An ATE-specialized LRO report is indexed by
\[
J=(\mathcal H_J,a_J,b_J,A_J,W_J),
\]
where \(\mathcal H_J\) is a finite CEINR first-step influence-function moment
dictionary, \(a_J(X)\in\R^{m_J}\) is its centered nonresidual row vector,
\(b_J(D,X)\in\R^{m_J}\) is its residual-loading vector, \(A_J\in\R^{m_J}\) is
the scalar-parameter Jacobian vector, and \(W_J\) is a positive-definite GMM
weight.  The published scalar GMM aggregation column,
whose transpose is the report row, is
\[
\kappa_J=W_JA_J(A_J^\transpose W_JA_J)^{-1}\in\R^{m_J},
\]
and the residual loading selected by the LRO report is
\[
\alpha_J(D,X)=b_J(D,X)^\transpose\kappa_J.
\]
The full first-order LRO report represented by the row is
\[
\varphi_J(O)=a_J(X)^\transpose\kappa_J+\alpha_J(D,X)e.
\]
Define the dictionary Gram matrix, Riesz cross-moment, and Riesz norm by
\[
G_J=\E_\nu[b_Jb_J^\transpose]=\E[b_J(D,X)b_J(D,X)^\transpose e^2],
\]
\[
c_J=\E_\nu[b_J\alpha_0]=\E[b_J(D,X)\alpha_0(D,X)e^2],
\qquad
q_0=\E_\nu[\alpha_0^2]=\E[\alpha_0(D,X)^2e^2].
\]
Let \(G_J^+\) be the Moore--Penrose inverse.  The three primitive defects are
\[
U_J=\E\left[\{a_J(X)^\transpose\kappa_J-\mu_0(X)\}^2\right],
\]
\[
S_J=q_0-c_J^\transpose G_J^+c_J,\qquad
T_J=(G_J\kappa_J-c_J)^\transpose G_J^+(G_J\kappa_J-c_J),
\]
and the focal certificate is \(\Xi_J(P)=(U_J,S_J,T_J)\).  The residual Riesz
direction is \(r_J=\alpha_0-\alpha_J\), and the report-gap scalars are
\[
K_J=\E[r_J(D,X)^2e^2],\qquad
C_J=\E[\alpha_0(D,X)r_J(D,X)e^2],\qquad
\Delta_J=|K_J-2C_J|.
\]

The non-corner finite-support witness class used in Conjecture
\ref{conj:witness} has two covariate cells \(x_a,x_b\), four treatment cells
with probability \(1/4\) each, propensity \(p_0(x_a)=p_0(x_b)=1/2\), and
\(\operatorname{Var}(Y\mid D=d,X=x)=1\) on each cell.  On this class
\(\alpha_0=2\) when \(D=1\) and \(\alpha_0=-2\) when \(D=0\).  The candidate
overidentified tuple is
\[
a_{J^\dagger}(X)=
\begin{pmatrix}
\mu_0(X)\\0
\end{pmatrix},\qquad
b_{J^\dagger}(D,X)=
\begin{pmatrix}
\alpha_0(D,X)\\ h(X)
\end{pmatrix},\qquad
h(x_a)=1,\quad h(x_b)=-1,\qquad
A_{J^\dagger}=\begin{pmatrix}1/2\\1/2\end{pmatrix},\qquad
W_{J^\dagger}=I_2.
\]
For this concrete tuple,
\[
G_{J^\dagger}=\begin{pmatrix}4&0\\0&1\end{pmatrix},\quad
c_{J^\dagger}=\begin{pmatrix}4\\0\end{pmatrix},\quad
\kappa_{J^\dagger}=\begin{pmatrix}1\\1\end{pmatrix}.
\]
Thus \(S_{J^\dagger}=0\), \(T_{J^\dagger}=1\), \(K_{J^\dagger}=1\),
\(C_{J^\dagger}=0\), \(U_{J^\dagger}=0\), and \(\Delta_{J^\dagger}=1\) whenever
the two rows are CEINR-generated by primitive first-step influence-function
equations.

More generally, the relative-open separation class
\(\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\) consists of two-cell
finite-support CEINR tuples satisfying, for fixed constants
\(0<\eta_-<\eta_+<\infty\),
\[
a_J(X)=\begin{pmatrix}\mu_0(X)\\0\end{pmatrix},\qquad
b_J(D,X)=\begin{pmatrix}\alpha_0(D,X)\\h(X)\end{pmatrix},\qquad
\E_\nu[\alpha_0 h]=0,\qquad
\eta_-\le \E_\nu[h^2]\le \eta_+,
\]
and whose published GMM row is
\[
\kappa_J=\begin{pmatrix}1\\t\end{pmatrix},\qquad |t|\ge \eta_-.
\]
The topology is relative to the plug-in-correct and span-correct CEINR
manifold defined by \(a_J^\transpose\kappa_J=\mu_0\) and
\(\alpha_0\in\operatorname{span}_{L^2(\nu_P)}(b_J)\).  On this class,
\[
U_J=0,\qquad S_J=0,\qquad
T_J=t^2\E_\nu[h^2]\ge \eta_-^3,\qquad
\Delta_J=t^2\E_\nu[h^2].
\]
The displayed \(J^\dagger\) is the normalized element with
\(\eta_-<1<\eta_+\) and \(t=1\).

\begin{verbatim}
qid = eid_dml_orthogonality_frontier
specialization = v1
graph / SWIG = binary-treatment unconfoundedness SWIG with observed
  O=(Y,D,X), D in {0,1}, potential outcomes (Y(1),Y(0)), consistency
  Y=D Y(1)+(1-D)Y(0), and no hidden common cause of D and (Y(1),Y(0))
  after conditioning on X.
treatment = D, a binary treatment with propensity p0(X)=Pr(D=1|X).
target estimand = theta0 = E[Y(1)-Y(0)].
identifying assumptions = consistency, conditional exchangeability
  (Y(1),Y(0)) independent of D given X, overlap epsilon <= p0(X) <= 1-epsilon,
  square-integrability, and finite CEINR-admissible LRO report dictionaries.
estimator reports compared = DML AIPW report, ADML Riesz-score report, and
  CEINR-admissible ATE-specialized LRO GMM reports indexed by
  (H_J,a_J,b_J,A_J,W_J).
equivalence notion = identical first-order influence function and identical
  first-order variance report.
focal object = Xi_J(P)=(U_J(P),S_J(P),T_J(P)), the nonresidual plug-in, span,
  and GMM-row alignment defects.
separation class = O_sep(eta_-,eta_+), the relative-open class of two-cell
  CEINR dictionaries with U_J=S_J=0 and T_J bounded below by eta_-^3.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Unconfounded binary ATE model]\label{ass:ate-model}
The observed law is generated by the SWIG in the locked parameters:
consistency holds, \((Y(1),Y(0))\perp D\mid X\), \(\E[Y^2]<\infty\), and
\(\theta_0=\E[Y(1)-Y(0)]\).
\end{assumption}

\begin{assumption}[Overlap]\label{ass:overlap}
There exists \(\epsilon>0\) such that
\(\epsilon\le p_0(X)\le1-\epsilon\) almost surely.
\end{assumption}

\begin{assumption}[Population report comparison]\label{ass:population-report}
The DML, ADML, and LRO reports are compared at the population nuisances
\((m_0,m_1,p_0)\) and at the population Riesz representer \(\alpha_0\).  Nuisance
estimation rates are outside this pivot and are not used to create the
equivalence frontier.
\end{assumption}

\begin{assumption}[Nondegenerate residual-variance geometry]\label{ass:nondegenerate}
The residual-variance Riesz norm is finite and nonzero:
\[
0<q_0=\E[\alpha_0(D,X)^2e^2]<\infty.
\]
All entries of \(G_J\), \(c_J\), \(U_J\), \(S_J\), \(T_J\), \(K_J\), \(C_J\), and
\(\Delta_J\) are finite for the LRO dictionary under consideration.
\end{assumption}

\begin{assumption}[CEINR-admissible ATE-specialized LRO dictionary]\label{ass:ceinr}
The tuple \(J=(\mathcal H_J,a_J,b_J,A_J,W_J)\) is generated by a finite
ATE-specialized locally robust semiparametric GMM moment dictionary through the
following primitive equations.  For each row \(j\le m_J\) there is an
identifying moment \(g_j(O;\gamma,\theta)\), with
\(\gamma=(m_0,m_1,p_0)\), and an FSIF row
\(\phi_j(O;\gamma,b_j)=b_j(D,X)\{Y-\gamma_D(X)\}\) such that the row's
population first-order contribution decomposes as
\[
\zeta_j(O)=a_j(X)+b_j(D,X)e,\qquad \E[a_j(X)]=0,
\]
and
\[
\E[g_j(O;\gamma_0,\theta_0)]=0,\qquad
A_{J,j}=-\partial_\theta \E[g_j(O;\gamma_0,\theta)]|_{\theta=\theta_0},
\]
and for every square-integrable perturbation
\(\delta=(\delta_0,\delta_1)\) of the outcome-regression first step,
\[
\left.\frac{d}{dt}\E[g_j(O;\gamma_0+t\delta,\theta_0)]\right|_{t=0}
=\E[b_j(D,X)\delta_D(X)].
\]
Consequently
\(\psi_j(O;\gamma,\theta,b_j)=g_j(O;\gamma,\theta)+\phi_j(O;\gamma,b_j)\)
has zero first-order derivative in the outcome-regression direction at
\((\gamma_0,\theta_0)\).  The dictionary also satisfies
\(a_J\in L^2(P_X)^{m_J}\), \(b_J\in L^2(\nu_P)^{m_J}\),
\(A_J\in\R^{m_J}\), \(W_J\) symmetric positive definite, and
\(A_J^\transpose W_JA_J>0\).
\end{assumption}

\begin{assumption}[Optimal-weight specialization]\label{ass:optimal-weight}
When the optimal-weight LRO specialization is named,
\[
\Omega_J=\E[b_J(D,X)b_J(D,X)^\transpose e^2]
\]
is positive definite and \(W_J=\Omega_J^{-1}\).  This is a specialization of
Assumption \ref{ass:ceinr}, not an additional route to equivalence.
\end{assumption}

\begin{assumption}[Finite-support witness class]\label{ass:finite-support}
For the concrete witness conjecture, \(X\) has finite support,
\(\Pr(D=d,X=x)>0\) on every listed cell, \(\operatorname{Var}(Y\mid D=d,X=x)>0\)
on every listed cell, and the candidate overidentified dictionary has
\(m_J\ge2\).  For the relative-open separation class
\(\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\), the constants
\(0<\eta_-<\eta_+<\infty\) are fixed before the dictionary is chosen and bound
the second-row residual norm and non-Riesz row coefficient as in Section 6.
No nonresidual, span, alignment, \(U_J\), \(S_J\), \(T_J\), or \(\Delta_J\)
condition is assumed outside the displayed definition of
\(\mathcal O_{\mathrm{sep}}\); those quantities must be computed from
\(a_J,G_J,c_J,A_J,W_J\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: common ATE report baseline]\label{thm:baseline}
Under Assumptions \ref{ass:ate-model}--\ref{ass:population-report}, the DML AIPW
population report and the ADML population Riesz-score report have the same
first-order influence function \(\varphi_0\) and the same variance report
\(\E[\varphi_0^2]\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is not claimed as novel; it is the calibration supplied by
\citet{Hahn1998Econometrica}, \citet{HiranoImbensRidder2003Econometrica},
\citet{ChernozhukovEtAl2018DML}, and \citet{ChernozhukovNeweySingh2022AutoDML}.
(b) The concrete consumer is Conjecture \ref{conj:gram-frontier}: it fixes the
single canonical report that LRO normalizations must match, avoiding the
failed prior-proposal mistake of attributing the EIF to estimator labels.

\begin{conjecture}[Conjecture 1: CEINR full-report Gram frontier (NOT YET PROVED)]\label{conj:gram-frontier}
Under Assumptions \ref{ass:ate-model}--\ref{ass:ceinr}, an
ATE-specialized CEINR-admissible LRO report indexed by
\(J=(\mathcal H_J,a_J,b_J,A_J,W_J)\) is first-order report-equivalent to the DML AIPW
and ADML Riesz reports if and only if its full-report Gram certificate vanishes:
\[
\Xi_J(P)=(U_J(P),S_J(P),T_J(P))=(0,0,0).
\]
Equivalently, the LRO aggregation row must select the canonical nonresidual
component \(a_J^\transpose\kappa_J=\mu_0\) in \(L^2(P_X)\), the LRO dictionary
must span the ATE Riesz representer in \(L^2(\nu_P)\), and the published GMM
aggregation row
\(\kappa_J^\transpose=(A_J^\transpose W_JA_J)^{-1}A_J^\transpose W_J\) must
satisfy the primitive normal equation \(G_J\kappa_J=c_J\).  Under Assumption
\ref{ass:optimal-weight}, the same statement specializes to \(W_J=G_J^{-1}\),
so the optimal-weight LRO report is DML/ADML-equivalent exactly when
\[
U_J=0,\qquad
G_JG_J^{-1}A_J(A_J^\transpose G_J^{-1}A_J)^{-1}=c_J
\quad\text{and}\quad S_J=0.
\]
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published result is
\citet[\S2, eqs.\ (2.2)--(2.3), and \S2, eq.\ (2.8)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}, which gives
the locally robust GMM construction, FSIF cancellation, and variance-report
aggregation map.  Its \S2.3 equations (2.10)--(2.11) supply the adjacent
automatic alpha/Riesz first-step equations, not the report aggregation formula.
The paper does not give the ATE-specific equivalence classification against
the DML/ADML Riesz score.  \citet[\S3--\S4]{Newey1994Econometrica} and
\citet[\S2--\S4]{IchimuraNewey2022QE} give the general semiparametric
projection and influence-function maps that make coefficient-space projection
routine, but they do not identify the ATE-specialized CEINR defect triple
\((U_J,S_J,T_J)\) or classify when the published LRO row
\((A_J^\transpose W_JA_J)^{-1}A_J^\transpose W_J\) selects the Riesz report.
The closest AutoDML equivalence comparator,
\citet[\S2--\S3]{BrunsSmithDukesFellerOgburn2025ABW}, collapses augmented
balancing weights to linear regression under linear outcome and weighting
models; it does not classify CEINR GMM dictionaries by the Jacobian/weight row
\(A_J,W_J\).  The closest prior CausalSmith proposal reduced equivalence to the
residual distance \(\|\alpha_J-\alpha_0\|_{L^2(\nu_P)}=0\); this conjecture
replaces that tautological check with the primitive nonresidual, dictionary-span
and GMM-row alignment defects \(U_J,S_J,T_J\), computable from
\(a_J,G_J,c_J,A_J,W_J\) before naming \(\varphi_J=\varphi_0\).  (b) The
concrete consumer is the LRO
implementation class of
\citet{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}: resolving the
conjecture would give an auditable normalization diagnostic for deciding when
LRO standard errors may be reused as DML/ADML standard errors, a classification
not stated in the CEINR construction formulas or in the general
Newey--Ichimura influence-function representation.

\begin{conjecture}[Conjecture 2: relative-open overidentified separation class (NOT YET PROVED)]\label{conj:witness}
There exists a nonempty relative-open class
\(\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\) of CEINR-admissible two-cell
finite-support ATE moment dictionaries satisfying Assumptions
\ref{ass:ate-model}--\ref{ass:finite-support} and containing the displayed
tuple \(J^\dagger\).  For every
\(J\in\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\),
\[
U_J(P)=0,\qquad S_J(P)=0,\qquad T_J(P)\ge \eta_-^3>0,\qquad
\Delta_J(P)\ge \eta_-^3.
\]
The normalized witness \(J^\dagger\) has
\[
U_{J^\dagger}(P)=0,\qquad S_{J^\dagger}(P)=0,\qquad T_{J^\dagger}(P)=1,\qquad
\Delta_{J^\dagger}(P)=1.
\]
Thus there is a generic CEINR-admissible region, not only a hand-tuned tuple,
where the dictionary has the correct nonresidual ATE component and enough
first-step influence-function information to span the ATE Riesz direction, but
the published LRO Jacobian/weight aggregation selects a different residual
loading and yields a strictly different first-order report.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[\S3--\S4]{Hansen1982Econometrica} justifies overidentified GMM
aggregation and tests of over-identifying restrictions, while
\citet[\S2, eqs.\ (2.2)--(2.3), and \S2, eq.\ (2.8)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
supplies the locally robust GMM moment construction and variance-report
aggregation map, with \S2.3 equations (2.10)--(2.11) used only as the automatic
alpha/Riesz first-step anchor.  Neither supplies a
relative-open ATE class where plug-in correctness and Riesz span hold but
GMM-row alignment fails.  The prior
\texttt{eid\_dml\_orth\_uniform/v2} reviewer specifically asked for a named
nontrivial CEINR-admissible overidentified dictionary class where fixed LRO
weighting fails or succeeds; this is that open separation region.  (b) The concrete
consumer is any empirical ATE analysis using overidentified LRO moments: the
class would show that adding valid locally robust rows can change the
first-order report unless \(\Xi_J=0\) is checked, and that the failure is stable
to perturbations within the plug-in/span-correct CEINR manifold.

\section{Sanity-check corollaries}
\begin{corollary}[Just-identified Riesz reduction]\label{cor:riesz-reduction}
Under Assumptions \ref{ass:ate-model}--\ref{ass:nondegenerate}, take the
just-identified Riesz normalization \(m_J=1\),
\(a_J(X)=\mu_0(X)\), \(b_J(D,X)=\alpha_0(D,X)\), \(A_J=1\), and \(W_J=1\).
Then \(G_J=q_0\), \(c_J=q_0\), \(\kappa_J=1\), and hence
\(U_J=S_J=T_J=0\).  Conjecture \ref{conj:gram-frontier} therefore reduces to
the known DML/ADML EIF baseline in Theorem \ref{thm:baseline}.
\end{corollary}

\begin{corollary}[Span is not enough]\label{cor:span-not-enough}
Under Assumptions \ref{ass:ate-model}--\ref{ass:finite-support}, the concrete
two-cell tuple in Section 6 has
\[
G_{J^\dagger}=\begin{pmatrix}4&0\\0&1\end{pmatrix},\quad
c_{J^\dagger}=\begin{pmatrix}4\\0\end{pmatrix},\quad
\kappa_{J^\dagger}=\begin{pmatrix}1\\1\end{pmatrix}.
\]
Therefore \(S_{J^\dagger}=0\) but
\(G_{J^\dagger}\kappa_{J^\dagger}\ne c_{J^\dagger}\), so span alone is not the
same as the LRO aggregation row selecting the Riesz representer.  Since
\(a_{J^\dagger}^\transpose\kappa_{J^\dagger}=\mu_0\), this is not a hidden
nonresidual-normalization failure.  The remaining open part of Conjecture
\ref{conj:witness} is CEINR generation, not this linear-algebra calculation.
\end{corollary}

\begin{corollary}[Relative-open separation algebra]\label{cor:open-separation}
Under Assumptions \ref{ass:ate-model}--\ref{ass:finite-support}, any tuple in
\(\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\) has
\[
U_J=S_J=0,\qquad T_J=t^2\E_\nu[h^2]\ge \eta_-^3,\qquad
\Delta_J=t^2\E_\nu[h^2]\ge \eta_-^3.
\]
Thus the open-class claim in Conjecture \ref{conj:witness} reduces to the
CEINR-admissibility construction for \(\mathcal O_{\mathrm{sep}}\), not to an
unverified continuity assertion.
\end{corollary}

\begin{lemma}[Singular-Gram certificate algebra]\label{lem:singular-gram}
Under Assumptions \ref{ass:ate-model}--\ref{ass:nondegenerate} and
\ref{ass:ceinr}, suppose \(S_J=0\).  Then \(c_J\in\operatorname{Range}(G_J)\),
and for every published LRO row \(\kappa_J\),
\[
T_J=(G_J\kappa_J-c_J)^\transpose G_J^+(G_J\kappa_J-c_J)=0
\quad\Longleftrightarrow\quad
G_J\kappa_J=c_J,
\]
even when \(G_J\) is singular.  Consequently
\[
U_J=S_J=T_J=0
\quad\Longleftrightarrow\quad
\varphi_J=\varphi_0\text{ in }L^2(P)
\]
provided the CEINR row \(a_J^\transpose\kappa_J\) and residual loading
\(b_J^\transpose\kappa_J\) generate the report in Section 6.
\end{lemma}
\paragraph{Reduction check.}
The key algebra is independent of nonsingularity: \(G_J\) is positive
semidefinite, \(G_J\kappa_J\in\operatorname{Range}(G_J)\), and
\(S_J=0\) is the projection identity placing \(c_J\) in the same range.  The
quadratic form \(v^\transpose G_J^+v\) is positive definite on
\(\operatorname{Range}(G_J)\), so \(T_J=0\) forces
\(v=G_J\kappa_J-c_J=0\).  Combining this row-alignment identity with
\(U_J=0\) and \(S_J=0\) gives equality of the nonresidual part and the
residual \(L^2(\nu_P)\) loading, hence equality of first-order reports.

\section{Proof-sketch route}
The mathematical route is finite-dimensional Hilbert-space and
semiparametric-GMM algebra.  First, use the standard back-door/AIPW identity to
calibrate the DML and ADML reports to \(\varphi_0\).  Second, view the residual
part of any finite LRO dictionary as a linear map
\(\gamma\mapsto b_J^\transpose\gamma\) from \(\R^{m_J}\) into \(L^2(\nu_P)\).
The identity \(U_J=0\) is the nonresidual check that the same row selects
\(\mu_0(X)\); \(S_J=0\) is the projection residual formula for whether
\(\alpha_0\) lies in the closed span of the residual dictionary; and \(T_J=0\)
is the normal-equation check that the published GMM row
\(\kappa_J^\transpose\) chooses a Riesz coefficient vector; Lemma
\ref{lem:singular-gram} is the explicit singular-Gram step showing why
\(S_J=0\) and \(T_J=0\) imply \(G_J\kappa_J=c_J\) without assuming \(G_J\) is
invertible.  For Conjecture
\ref{conj:witness}, plug the four cell probabilities, \(a_{J^\dagger}\),
\(b_{J^\dagger}\), \(A_{J^\dagger}\), and
\(W_{J^\dagger}\) from Section 6 into the definitions to get
\(G=\operatorname{diag}(4,1)\), \(c=(4,0)^\transpose\), \(\kappa=(1,1)^\transpose\),
\(U=0\), \(S=0\), \(T=1\), and \(\Delta=1\).  For the relative-open class
\(\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\), the same computation gives
\(U=S=0\) and \(T=\Delta=t^2\E_\nu[h^2]\ge\eta_-^3\) because the first
dictionary row is exactly \(\alpha_0\) and the second row is \(\nu_P\)-orthogonal
to it.  The only non-algebraic step is to construct
identifying moments \(g_1,g_2\) whose Gateaux derivatives satisfy the primitive
CEINR equations in Assumption \ref{ass:ceinr}; one route is to take row one as
the usual ATE moment and row two as a centered covariate-contrast linear
functional with \(\E[g_2(O;\gamma_0,\theta_0)]=0\),
\(-\partial_\theta\E[g_2(O;\gamma_0,\theta)]|_{\theta_0}=1/2\), and
Gateaux derivative
\(\left.d\E[g_2(O;\gamma_0+t\delta,\theta_0)]/dt\right|_{0}
=\E[h(X)\delta_D(X)]\).  Its FSIF is then \(h(X)\{Y-m_D(X)\}\), and the
displayed derivative equality can be checked cell by cell.

\section{Honest scope flags}
Theorem \ref{thm:baseline} is a calibration theorem from standard
semiparametric ATE theory.  Conjectures \ref{conj:gram-frontier} and
\ref{conj:witness} are not proved.  The open technical step is the CEINR
admissibility half: it must be shown that the dictionary/Jacobian/weight tuples
covered by \(\Xi_J\) are exactly those generated by the primitive
first-step influence-function equations in Assumption \ref{ass:ceinr}, including
the nonresidual row \(a_J\), and that the displayed relative-open
\(\mathcal O_{\mathrm{sep}}\) rows are generated by actual identifying moments
rather than arbitrary residual loadings.
This v5 revision corrects the LRO location-level anchors: CEINR equations
(2.10)--(2.11) are treated as automatic alpha/Riesz first-step equations, while
the locally robust moment construction and variance-report aggregation are
anchored to the paper's earlier GMM equations.  It also adds Lemma
\ref{lem:singular-gram} so the Gram-certificate implication
\(S_J=T_J=0\Rightarrow G_J\kappa_J=c_J\) is explicit even when \(G_J\) is
singular.
This v4 revision strengthens the witness from one tuple to a relative-open
plug-in/span-correct separation class and adds the Newey--Ichimura
projection/influence-function comparator chain to make clear why \(\Xi_J\) is
more than routine projection algebra.  No high-level Holder/entropy DML
frontier assumptions are retained as theorem premises in this angle; the
earlier smoothness-frontier kernel is withdrawn rather than demoted to a
conditional theorem.
This v3 revision patches the prior full-influence-function gap by adding the
nonresidual defect \(U_J\); the residual Gram defects \(S_J,T_J\) alone are no
longer claimed to decide full report equivalence.  This v2 revision withdraws the
circular finite-support assumption \(S_J=0<T_J\) and replaces it with explicit
cell probabilities, loadings, \(A_J\), \(W_J\), and computed
\((S_J,T_J,\Delta_J)\).  This pivot deliberately withdraws the earlier
DML/LRO/ADML spectral studentization frontier and the earlier residual-\(\rho=0\)
equivalence statement as flagship kernels; those are treated as prior failed
angles.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial angle-2 draft around the CEINR Gram-alignment
certificate \(\Xi_J=(S_J,T_J)\) and a finite-support overidentified witness;
prior verdict: none.
\item v2 (revise) -- pinned CEINR admissibility to primitive FSIF derivative
equations, added Bruns-Smith--Dukes--Feller--Ogburn as the closest
Riesz/AutoDML equivalence comparator, corrected the AutoDML bibliography, and
replaced the circular witness assumption with an explicit two-cell table and
computed \(S_J,T_J,\Delta_J\); prior verdict: REVISE.
\item v3 (revise) -- added the nonresidual defect \(U_J\) to the certificate so
\(\Xi_J\) decides full influence-function equivalence, gave the two-cell
witness \(U_J=0\), made the \(g_2\) CEINR route explicit, and corrected the
Bruns-Smith--Dukes--Feller--Ogburn JRSSB metadata; prior verdict: REVISE.
\item v4 (revise) -- added location-level Newey--Ichimura comparator
positioning, promoted the witness to the relative-open
\(\mathcal O_{\mathrm{sep}}(\eta_-,\eta_+)\) separation class, and recorded that
the earlier Holder/entropy frontier was withdrawn rather than assumed; prior
verdict: REVISE.
\item v5 (revise) -- corrected the LRO comparator anchors by separating
CEINR's locally robust GMM moment/report equations from its automatic
alpha/Riesz equations, and added the singular-Gram certificate lemma; prior
verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Bruns-Smith et~al.(2025)]{BrunsSmithDukesFellerOgburn2025ABW}
Bruns-Smith, D., O. Dukes, A. Feller, and E. L. Ogburn (2025).
\newblock Augmented balancing weights as linear regression.
\newblock \emph{Journal of the Royal Statistical Society: Series B}.
\newblock Published 24 April 2025, doi:10.1093/jrsssb/qkaf019;
arXiv:2304.14545.

\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., D. Chetverikov, M. Demirer, E. Duflo, C. Hansen,
W. Newey, and J. Robins (2018).
\newblock Double/debiased machine learning for treatment and structural
parameters.
\newblock \emph{The Econometrics Journal} 21(1), C1--C68.

\bibitem[Chernozhukov et~al.(2022a)]{ChernozhukovEscancianoIchimuraNeweyRobins2022LRO}
Chernozhukov, V., J. C. Escanciano, H. Ichimura, W. K. Newey, and J. M. Robins
(2022).
\newblock Locally robust semiparametric estimation.
\newblock \emph{Econometrica} 90(4), 1501--1535.

\bibitem[Chernozhukov et~al.(2022b)]{ChernozhukovNeweySingh2022AutoDML}
Chernozhukov, V., W. K. Newey, and R. Singh (2022).
\newblock Automatic debiased machine learning of causal and structural effects.
\newblock \emph{Econometrica} 90(3), 967--1027.

\bibitem[Chernozhukov et~al.(2022c)]{ChernozhukovNeweySingh2022Riesz}
Chernozhukov, V., W. K. Newey, and R. Singh (2022).
\newblock Debiased machine learning of global and local parameters using
regularized Riesz representers.
\newblock \emph{The Econometrics Journal} 25(3), 576--601.

\bibitem[Hahn(1998)]{Hahn1998Econometrica}
Hahn, J. (1998).
\newblock On the role of the propensity score in efficient semiparametric
estimation of average treatment effects.
\newblock \emph{Econometrica} 66(2), 315--331.

\bibitem[Hansen(1982)]{Hansen1982Econometrica}
Hansen, L. P. (1982).
\newblock Large sample properties of generalized method of moments estimators.
\newblock \emph{Econometrica} 50(4), 1029--1054.

\bibitem[Hirano et~al.(2003)]{HiranoImbensRidder2003Econometrica}
Hirano, K., G. W. Imbens, and G. Ridder (2003).
\newblock Efficient estimation of average treatment effects using the estimated
propensity score.
\newblock \emph{Econometrica} 71(4), 1161--1189.

\bibitem[Ichimura and Newey(2022)]{IchimuraNewey2022QE}
Ichimura, H. and W. K. Newey (2022).
\newblock The influence function of semiparametric estimators.
\newblock \emph{Quantitative Economics} 13(1), 29--61.

\bibitem[Newey(1994)]{Newey1994Econometrica}
Newey, W. K. (1994).
\newblock The asymptotic variance of semiparametric estimators.
\newblock \emph{Econometrica} 62(6), 1349--1382.

\bibitem[Robins et~al.(1994)]{RobinsRotnitzkyZhao1994JASA}
Robins, J. M., A. Rotnitzky, and L. P. Zhao (1994).
\newblock Estimation of regression coefficients when some regressors are not
always observed.
\newblock \emph{Journal of the American Statistical Association} 89(427),
846--866.
\end{thebibliography}

\end{document}
