% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orthogonality\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_dml\_orthogonality\_frontier} / \texttt{v1}%
  \\ \large\textit{Orthogonality-order index for CATE DML below the nuisance-smoothness elbow}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This proposal uses the ExactID/free-form convention
\[
(\texttt{qid},\texttt{specialization},\text{SWIG/DAG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
The locked tuple is
\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_dml\_orthogonality\_frontier},\qquad
\texttt{specialization}=\texttt{v1},\\
\text{SWIG/DAG}=X\to D\to Y,\; X\to Y,\quad
\text{treatment }D\in\{0,1\},\\
\text{target estimand}=\tau_0(x_0)=\E[Y(1)-Y(0)\mid X=x_0]
\text{ and local CATE reports } \theta_0(\ell_h),\\
\text{identifying assumptions}=\text{consistency, conditional unconfoundedness }
(Y(1),Y(0))\perp D\mid X,\\
\text{overlap } \underline e\le p_0(X)\le 1-\underline e,\text{ and the Holder experiment in
Assumptions \ref{ass:causal}--\ref{ass:higher-order-class}.}
\end{gathered}
\]
Here \(p_0(x)=\Pr(D=1\mid X=x)\), \(m_{d,0}(x)=\E[Y\mid D=d,X=x]\),
\(\tau_0(x)=m_{1,0}(x)-m_{0,0}(x)\), and \(x_0\) is an interior point of
the covariate support.  The focal mathematical object is the
\emph{primitive orthogonality-order index}.  Let
\(\mathsf B_K\subset(0,\infty)^3\times\{1,2,\ldots\}\) denote the
Kennedy--Balakrishnan--Robins--Wasserman below-elbow region: the open set of
Holder parameters, indexed by their average nuisance smoothness
\(s=(\alpha+\beta)/2\) together with \(\gamma\) and \(d\), for which their
published minimax lower bound for CATE estimation is strictly slower than the
oracle nonparametric-regression rate \(n^{-\gamma/(2\gamma+d)}\).  This
proposal treats \(\mathsf B_K\) as a published calibration, not as a new
frontier.  Define first the product/projection candidate
\[
q^\dagger(\alpha,\beta,\gamma,d)=
\begin{cases}
1,& r_m+r_p>r_\tau,\\
\min\{q\ge2:\;q(r_m+r_p)>r_\tau\text{ and }\mathcal K_q\ne\varnothing\},
& r_m+r_p\le r_\tau\text{ and the displayed set is nonempty},\\
\infty,& r_m+r_p\le r_\tau\text{ and the displayed set is empty}.
\end{cases}
\]
The locked frontier object is
\[
q_\star(\alpha,\beta,\gamma,d)=
\begin{cases}
\infty,&(\alpha,\beta,\gamma,d)\in\mathsf B_K,\\
q^\dagger(\alpha,\beta,\gamma,d),&\text{otherwise}.
\end{cases}
\]
where \(\alpha,\beta\) are the Holder smoothness exponents of the outcome and
propensity nuisances, \(\gamma\) is the Holder smoothness exponent of the CATE
surface, \(d\) is the covariate dimension,
\(r_m=\alpha/(2\alpha+d)\), \(r_p=\beta/(2\beta+d)\), and
\(r_\tau=\gamma/(2\gamma+d)\).  The projection-feasibility set is
\[
\mathcal K_q=\left\{\kappa\in(0,1):
{\kappa\min\{\alpha,\beta\}\over d}>r_\tau
\text{ and }q(1-\kappa)>1\right\}.
\]
First-order DML corresponds to \(q=1\); \(q>1\) denotes a localized
HOIF/U-statistic correction with projection dimension \(J_n=n^\kappa\).  The
set \(\mathcal K_q\) is independent of the success event: it records the
primitive approximation and stochastic projection inequalities that a concrete
localized higher-order correction must satisfy.

\begin{abstract}
This proposal asks where first-order Neyman-orthogonal DML stops being enough
for local CATE inference in the primitive Holder experiment studied by modern
minimax HTE theory.  The routine theorem records the exact first-order AIPW
drift for local CATE reports under an explicit localized nuisance-rate
condition: after cross-fitting, the population bias is a localized product of
outcome-regression and propensity errors.  The novel kernel is Conjecture
\ref{conj:order-frontier}: outside the published
Kennedy--Balakrishnan--Robins--Wasserman below-elbow region \(\mathsf B_K\),
the independently defined index \(q_\star(\alpha,\beta,\gamma,d)\), including
primitive projection feasibility through \(\mathcal K_q\), is the necessary
and sufficient orthogonalization order for oracle-rate Gaussian local CATE
inference.  Inside \(\mathsf B_K\), the proposal sets \(q_\star=\infty\),
reflecting the published full-class lower bound rather than a new
impossibility claim.  Thus the first-order impossibility itself is treated as
a published minimax calibration, not as the flagship novelty.  The new
question is whether this Kennedy-calibrated integer frontier, including the
\(q_\star=\infty\) case, is the minimal order at which localized HOIF
corrections recover oracle Gaussian local CATE inference whenever the
published lower bound leaves oracle inference possible.  Resolving the
conjecture would tell HTE researchers when to use ordinary DML, when to
construct a concrete localized HOIF correction, and when a claimed CATE
confidence interval is attempting a nonregular problem with a first-order
tool.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Heterogeneous-treatment-effect DML often starts from a first-order
orthogonal pseudo-outcome and then smooths or projects it to estimate CATE
features.  The usual first-order message is that nuisance products are
second-order for a root-\(n\) scalar target.  Local CATE reports are different:
their oracle stochastic scale is \(n^{-\gamma/(2\gamma+d)}\), not
\(n^{-1/2}\), so the same nuisance product can be first-order relative to the
target's own minimax scale.

\paragraph{The main finding (proposed).}
Theorem \ref{thm:first-order-drift} gives the algebraic starting point: for
the local AIPW report \(\theta_0(\ell_h)\), cross-fitted first-order DML has a
localized product drift controlled by
\(\delta_{m,h,n}\delta_{p,h,n}\).  Under the local sup-norm rates in
Assumption \ref{ass:nuisance-rates}, this product has exponent
\(r_m+r_p\); under only global \(L^2\) rates an additional localization
amplification factor would be present.  Theorem
\ref{thm:kennedy-calibration} separates two frontiers that the v3 draft had
conflated.  The Kennedy--Balakrishnan--Robins--Wasserman below-elbow region
\(\mathsf B_K\) is a full-class minimax obstruction stated in their average
nuisance smoothness \(s=(\alpha+\beta)/2\), whereas
\(\Delta_1=r_m+r_p-r_\tau\) is only the first-order AIPW product-drift index.
Conjecture \ref{conj:order-frontier} is the flagship kernel:
\(q_\star(\alpha,\beta,\gamma,d)\), with \(q_\star=\infty\) on
\(\mathsf B_K\), is exactly the minimal orthogonalization order needed for
oracle-rate Gaussian local CATE inference when the correction is a localized
projection HOIF/U-statistic with \(J_n=n^\kappa\) and
\(\kappa\in\mathcal K_q\).

\paragraph{What is new.}
\citet[\S3]{ChernozhukovEtAl2018DML} give sufficient first-order DML product
rate conditions for low-dimensional treatment and structural parameters, but
not a local CATE impossibility theorem.  \citet[\S2--\S4]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
derive minimax CATE rates and an elbow in nuisance smoothness, but their
headline target is CATE estimation rate optimality, not a minimal
orthogonalization-order index for oracle Gaussian local CATE inference after
the elbow is crossed.  \citet[\S2.1, \S3.1, Corollary 4]{MackeySyrgkanisZadik2018OML} show that \(k\)-th
order orthogonality can relax nuisance-rate requirements in orthogonal machine
learning, while \citet{RobinsLiTchetgenVanDerVaart2008HOIF} develop the
higher-order influence-function machinery behind many nonparametric
improvements and \citet{LiTchetgenVanDerVaartRobins2011HOIFTreatment}
specialize higher-order U-statistic inference to a low-regularity treatment
effect interval problem.  The Kennedy estimator uses localized higher-order
local-polynomial/R-learner structure to attain minimax CATE rates; the present
proposal asks for the integer order at which such localized higher-order
corrections become necessary and sufficient for oracle Gaussian local reports.
\citet[\S2--\S3]{ChernozhukovNeweySingh2022Riesz} analyze
regularized Riesz representers for global and local linear functionals, but
their local-nonregularity discussion does not give a Holder-indexed minimal
orthogonalization order.  The epsilon-gap is the named scalar
\(q_\star(\alpha,\beta,\gamma,d)\), calibrated to the Kennedy below-elbow set
\(\mathsf B_K\) and refined outside that set by the projection-feasibility set
\(\mathcal K_q\): the proposal claims an iff frontier tying first-order DML,
regularized Riesz local inference, minimax CATE elbows, and concrete
higher-order orthogonal scores in one primitive Holder experiment, with
\(q_\star=\infty\) marking either the published Kennedy oracle-impossibility
region or the projection-infeasible regime rather than an undefined minimum.

\paragraph{How it positions in the literature.}
The anchor cluster is ExactID.  The identifying formula is the usual
unconfoundedness/back-door formula for \(m_{1,0}(x)-m_{0,0}(x)\); the proposal
does not add a new causal estimand.  The methodological question is
semiparametric inference after exact identification: which order of
orthogonalization makes the identified local CATE functional regular enough
for oracle Gaussian inference over Holder nuisance classes.

\paragraph{Implications for the community.}
The concrete downstream consumer is the simultaneous CATE and structural
function procedure of \citet{SemenovaChernozhukov2021DMLCATE}: the conjecture
would say when its first-order orthogonal-signal workflow can be pushed from
linear or group summaries to truly local CATE reports, and when a
higher-order signal is mathematically required.

\paragraph{How research benefits from the conclusion.}
If the conclusion resolves favorably, empirical HTE papers should report
\(q_\star(\alpha,\beta,\gamma,d)\) or a conservative lower bound on it before
using first-order DML pseudo-outcomes for local CATE confidence intervals.

\section{Related work}
\citet[\S3]{ChernozhukovEtAl2018DML} is the first-order DML anchor: it gives
orthogonal scores and cross-fitting under sufficient product-rate conditions,
but it does not prove a necessary CATE smoothness frontier.  \citet{SemenovaChernozhukov2021DMLCATE}
develop DML estimation and simultaneous inference for CATE best linear
predictors and group averages; this proposal asks when the same first-order
signal can be sharpened to local CATE inference.  \citet[\S2--\S4 and Theorems 1--2]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
derive minimax rates for Holder-smooth CATE and identify an elbow in average
nuisance smoothness \(s=(\alpha+\beta)/2\) where the oracle
nonparametric-regression rate is unattainable; this is the closest published
elbow result and is recorded here as \(\mathsf B_K\).
\citet{RobinsLiTchetgenVanDerVaart2008HOIF}
develop higher-order influence functions for minimax estimation of nonlinear
functionals and supply the mathematical technology the conjecture would
specialize.  \citet[\S2.1, \S3.1, Corollary 4]{MackeySyrgkanisZadik2018OML} show that higher-order
orthogonality relaxes first-stage rate requirements in orthogonal machine
learning, including a limitation result for second-order orthogonality in a
partially linear setting; this is the closest order-comparison comparator.
\citet{LiTchetgenVanDerVaartRobins2011HOIFTreatment} is the closest published
treatment-effect interval precedent: it builds higher-order U-statistic point
and interval estimators under low regularity by reducing the problem to
expected conditional covariance estimation, whereas this proposal targets a
local CATE order frontier indexed by \((\alpha,\beta,\gamma,d)\) and calibrated
against the Kennedy minimax CATE elbow.
\citet{ChernozhukovNeweySingh2022AutoDML} gives automatic debiasing through
Riesz representers for causal and structural effects, motivating the need to
distinguish first-order automatic bias correction from genuinely higher-order
orthogonalization.  \citet[\S2--\S3]{ChernozhukovNeweySingh2022Riesz} develops DML for
global and local linear functionals using regularized Riesz representers,
including nonregular local objects; this is the closest Riesz-locality
comparator and motivates the local regular-to-nonregular boundary in the
present conjecture.  \citet{FosterSyrgkanis2023OSL} provides orthogonal
statistical-learning excess-risk bounds under metric entropy, which motivates
but does not settle Gaussian local CATE inference.  \citet{ArmstrongKolesar2021FiniteSampleATE}
prove finite-sample honest ATE inference and minimum smoothness conditions
under unconfoundedness, making them a necessity precedent for smoothness-based
causal inference frontiers.

The in-repository prior-art map supplied by Stage -1.1 says that
\texttt{eid\_dml\_orthogonality\_frontier}/v1 previously pursued a
two-channel first-order HTE-DML frontier and failed after Stage 0.5 because
the claimed iff boundary was encoded in high-level assumptions.  The failed
banked \texttt{eid\_dml\_orth\_uniform}/v2 proposal targeted DML/LRO/ADML
variance-report equivalence, not the Holder CATE orthogonalization-order
frontier.  The \texttt{doc/API.md} catalogue is panel-heavy in the relevant
index and records no existing ExactID proposal for a CATE
\(q_\star(\alpha,\beta,\gamma,d)\) order frontier.

\section{Formal setup}
The observed data are i.i.d. draws \(O_i=(Y_i,D_i,X_i)\), where
\(D_i\in\{0,1\}\), \(X_i\in[0,1]^d\), and \(Y_i\in\mathbb R\).  Potential
outcomes \(Y(1),Y(0)\) obey consistency and conditional unconfoundedness.
Let \(p_0(x)=\Pr(D=1\mid X=x)\), \(m_{d,0}(x)=\E[Y\mid D=d,X=x]\), and
\(\tau_0(x)=m_{1,0}(x)-m_{0,0}(x)\).  For an interior point \(x_0\) and
bandwidth \(h\), let \(K_h(x)=h^{-d}K((x-x_0)/h)\) with a bounded compactly
supported order-\(\lfloor\gamma\rfloor\) kernel, and define
\[
\theta_0(\ell_h)=\E[\ell_h(X)\tau_0(X)],\qquad
\ell_h(x)={K_h(x)\over \E[K_h(X)]}.
\]
The oracle local CATE rate is
\[
r_\tau={\gamma\over 2\gamma+d},\qquad
a_n=n^{-r_\tau},
\]
obtained by the usual bias-variance balance \(h_n\asymp n^{-1/(2\gamma+d)}\).
The nuisance rates are
\[
r_m={\alpha\over 2\alpha+d},\qquad r_p={\beta\over 2\beta+d},\qquad
\delta_{m,n}\asymp n^{-r_m},\quad \delta_{p,n}\asymp n^{-r_p}.
\]
The localized nuisance scales are
\[
\delta_{m,h,n}=\max_{d\in\{0,1\}}
\sup_{x\in\operatorname{supp}(K_h)}|\hat m_d(x)-m_{d,0}(x)|,\qquad
\delta_{p,h,n}=\sup_{x\in\operatorname{supp}(K_h)}|\hat p(x)-p_0(x)|.
\]
Let \(s=(\alpha+\beta)/2\), and let
\(\mathsf B_K\subset(0,\infty)^3\times\{1,2,\ldots\}\) be the published
Kennedy--Balakrishnan--Robins--Wasserman below-elbow region: the open set of
parameters for which their minimax lower bound for Holder CATE estimation is
strictly slower than the oracle rate \(a_n\).  The definition is deliberately
keyed to their average nuisance smoothness \(s\), not to the first-order AIPW
product exponent below.  Define the first-order deficit,
projection-feasibility set, product/projection candidate, and primitive
orthogonalization-order index by
\[
\Delta_1(\alpha,\beta,\gamma,d)=r_m+r_p-r_\tau,
\qquad
\mathcal K_q=\left\{\kappa\in(0,1):
{\kappa\min\{\alpha,\beta\}\over d}>r_\tau,\;q(1-\kappa)>1\right\},
\]
\[
q^\dagger(\alpha,\beta,\gamma,d)=
\begin{cases}
1,& r_m+r_p>r_\tau,\\
\min\{q\ge2:\;q(r_m+r_p)>r_\tau\text{ and }\mathcal K_q\ne\varnothing\},
& r_m+r_p\le r_\tau\text{ and the displayed set is nonempty},\\
\infty,& r_m+r_p\le r_\tau\text{ and the displayed set is empty}.
\end{cases}
\]
\[
q_\star(\alpha,\beta,\gamma,d)=
\begin{cases}
\infty,&(\alpha,\beta,\gamma,d)\in\mathsf B_K,\\
q^\dagger(\alpha,\beta,\gamma,d),&\text{otherwise}.
\end{cases}
\]
These are defined from the published Kennedy elbow, Holder localization, and
projection exponents alone; they are not defined as the first order for which
inference succeeds.
The oracle variance \(V_{\mathrm{or}}(x_0)\) is the pointwise variance of the
localized oracle empirical process obtained by replacing \(Y(1)-Y(0)\) with
the known regression contrast and using bandwidth \(h_n\).  A two-point lower
bound has bounded testing distance when the Hellinger distance between the two
localized laws is bounded away from both \(0\) and infinity while their CATE
separation is of order \(a_n\).

For nuisances \(\eta=(m_0,m_1,p)\), the first-order AIPW signal is
\[
\phi(O;\eta)=m_1(X)-m_0(X)
 + {D\{Y-m_1(X)\}\over p(X)}
 - {(1-D)\{Y-m_0(X)\}\over 1-p(X)}.
\]
The local first-order DML estimator is
\[
\hat\theta_1(\ell_h)=n^{-1}\sum_{i=1}^n \ell_h(X_i)\phi(O_i;\hat\eta_{-i}),
\]
where \(\hat\eta_{-i}\) denotes cross-fitted nuisances trained without
observation \(i\).  Let \(\mathcal A_1\) denote the class of first-order
cross-fitted estimators obtained from this AIPW signal with nuisance learners
satisfying Assumption \ref{ass:nuisance-rates}.  For \(q\ge2\), a localized
projection HOIF estimator
\(\hat\theta_{q,J}(\ell_h)\) adds to \(\hat\theta_1(\ell_h)\) an explicit sum
of degenerate U-statistics of orders \(2,\ldots,q\), built from a localized
basis \(b_J(X)\in\mathbb R^J\) supported on the \(h_n\)-neighborhood of
\(x_0\).  The conjectured remainder is decomposed as
\[
R_{q,J,n}=R^{\mathrm{prod}}_{q,n}+R^{\mathrm{proj}}_{J,n}
 +R^{\mathrm{ustat}}_{q,J,n},
\]
where the three terms are respectively the uncanceled product drift,
projection approximation error, and degenerate-U-statistic stochastic error.

\begin{verbatim}
qid = eid_dml_orthogonality_frontier
specialization = v1
graph / SWIG = binary-treatment unconfoundedness SWIG with observed
  O=(Y,D,X), D in {0,1}, potential outcomes (Y(1),Y(0)), consistency
  Y=D Y(1)+(1-D)Y(0), and no hidden common cause of D and (Y(1),Y(0))
  after conditioning on X.
treatment = D, a binary treatment with propensity p0(X)=Pr(D=1|X).
target estimand = tau0(x0)=E[Y(1)-Y(0)|X=x0] and local CATE
  reports theta0(ell_h)=E[ell_h(X){Y(1)-Y(0)}].
identifying assumptions = consistency, conditional exchangeability,
  overlap, Holder(alpha) outcome regressions, Holder(beta) propensity,
  Holder(gamma) CATE surface, compact interior localization, localized
  nuisance rates, and the primitive localized HOIF construction class in
  Assumption 5.
focal object = q_star(alpha,beta,gamma,d), the Kennedy-calibrated minimal
  orthogonalization order. It is infinity on the published Kennedy--
  Balakrishnan--Robins--Wasserman below-elbow region B_K indexed by average
  nuisance smoothness s=(alpha+beta)/2; outside B_K it equals the smallest
  product/projection order whose Holder exponent q(r_m+r_p) beats the oracle
  CATE exponent r_tau=gamma/(2 gamma+d) and whose projection exponent kappa
  satisfies the primitive approximation/stochastic inequalities in K_q.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[ExactID causal model and overlap]\label{ass:causal}
The observations are i.i.d.; consistency holds; \((Y(1),Y(0))\perp D\mid X\);
and for a fixed \(\underline e\in(0,1/2)\),
\(\underline e\le p_0(X)\le 1-\underline e\) almost surely.
\end{assumption}

\begin{assumption}[Holder nuisance and target classes]\label{ass:holder}
The outcome regressions \(m_{0,0},m_{1,0}\) belong to Holder balls
\(\mathcal H^\alpha(L_m)\), the propensity \(p_0\) belongs to
\(\mathcal H^\beta(L_p)\) and obeys Assumption \ref{ass:causal}, and the CATE
surface \(\tau_0\) belongs to \(\mathcal H^\gamma(L_\tau)\) on \([0,1]^d\).
The exponents \(\alpha,\beta,\gamma,d\) are fixed constants with
\(\alpha,\beta,\gamma>0\) and \(d\ge1\).
\end{assumption}

\begin{assumption}[Interior local report]\label{ass:local-report}
The point \(x_0\) lies in the interior of \([0,1]^d\), the density of \(X\) is
bounded above and below in a neighborhood of \(x_0\), and
\(\ell_h(x)=K_h(x)/\E[K_h(X)]\) uses a bounded compactly supported kernel of
order at least \(\lfloor\gamma\rfloor\) with
\(h_n\asymp n^{-1/(2\gamma+d)}\).
\end{assumption}

\begin{assumption}[Localized rate-attaining nuisance learners]\label{ass:nuisance-rates}
There exist cross-fitted learners \(\hat m_d\) and \(\hat p\) such that, on
the support of \(K_{h_n}\),
\[
\delta_{m,h,n}=O_{\Pr}(n^{-r_m}\log^c n),\qquad
\delta_{p,h,n}=O_{\Pr}(n^{-r_p}\log^c n)
\]
for a fixed \(c<\infty\), where \(r_m=\alpha/(2\alpha+d)\) and
\(r_p=\beta/(2\beta+d)\).  This is a local sup-norm condition; it is stronger
than a global \(L^2(P_X)\) rate and is included to prevent a hidden
\(h_n^{-d/2}\) localization amplification from being mistaken for the
Holder product exponent.
\end{assumption}

\begin{assumption}[Primitive localized HOIF construction class]\label{ass:higher-order-class}
For \(q\ge2\), the candidate estimator class \(\mathcal A_q^{\mathrm{loc}}\)
is restricted to cross-fitted estimators \(\hat\theta_{q,J}(\ell_{h_n})\)
formed by adding degenerate U-statistics of orders \(2,\ldots,q\) to the
first-order AIPW report.  The U-statistics use a localized basis
\(b_J(X)\in\mathbb R^J\) with entropy \(\log N(\varepsilon,\{b_J\},L^2)
\le C J\log(1/\varepsilon)\), projection dimension \(J_n=n^\kappa\), and
\(\kappa\in(0,1)\).  Membership in \(\mathcal A_q^{\mathrm{loc}}\) requires
only the structural cancellation of Gateaux derivatives through order \(q-1\)
and finite oracle-scale variance; it does not assume that
\((\delta_{m,h,n}\delta_{p,h,n})^q=o(a_n)\) or that Gaussian inference
already holds.
\end{assumption}

\begin{assumption}[Aligned first-order witness perturbations]\label{ass:aligned-witness}
For the first-order subclass claim in Theorem \ref{thm:kennedy-calibration},
there is a sequence of laws in the wavelet witness class of Assumption
\ref{ass:witness} and a sequence of cross-fitted nuisance estimates such that,
with probability tending to one,
\[
\left|\E\!\left[\ell_{h_n}(X)(\hat p(X)-p_0(X))
\left\{ {\hat m_1(X)-m_{1,0}(X)\over \hat p(X)}
       +{\hat m_0(X)-m_{0,0}(X)\over 1-\hat p(X)}\right\}
\middle|\,\hat\eta\right]\right|
\ge c_{\mathrm{align}} n^{-(r_m+r_p)}\log^{-c_{\mathrm{align}}'}n
\]
for fixed constants \(c_{\mathrm{align}},c_{\mathrm{align}}'>0\).  This is a
conditional aligned-error witness, not a minimax lower bound for every
first-order learner in \(\mathcal A_1\).
\end{assumption}

\begin{assumption}[Concrete non-corner witness class]\label{ass:witness}
The lower-bound witness class contains laws with \(X\) uniform on \([0,1]^d\),
propensities \(p_0(x)=1/2+b_p\psi_j(x)\), outcome regressions
\(m_{d,0}(x)=b_{d,j}\psi_j(x)\), and CATE perturbations
\(\tau_0(x)=b_{\tau,j}\psi_j(x)\), where \(\psi_j\) is an \(L^2\)-normalized
compactly supported wavelet bump at resolution \(j\), localized in the
\(h_n\)-neighborhood of \(x_0\).  The raw coefficients scale as
\[
|b_p|=c_p2^{-j(\beta+d/2)},\qquad
|b_{d,j}|=c_{m,d}2^{-j(\alpha+d/2)},\qquad
|b_{\tau,j}|=c_\tau2^{-j(\gamma+d/2)},
\]
with normalized constants \(c_p,c_{m,d},c_\tau\in[\underline c,\bar c]\) for
fixed \(0<\underline c<\bar c<\infty\), chosen so that
\(|p_0(x)-1/2|\le1/4\) and all functions remain inside the Holder balls of
Assumption \ref{ass:holder}.  Thus ``restricted away from zero'' refers to
the normalized constants, not to the shrinking resolution-level coefficients.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: first-order local AIPW drift]\label{thm:first-order-drift}
Under Assumptions \ref{ass:causal}--\ref{ass:nuisance-rates}, for any
cross-fitted nuisances \(\hat\eta=(\hat m_0,\hat m_1,\hat p)\) satisfying the
overlap bound, the conditional expectation of the local first-order DML report
obeys
\[
\E[\ell_h(X)\phi(O;\hat\eta)\mid \hat\eta]-\theta_0(\ell_h)
=\E\!\left[
\ell_h(X)(\hat p(X)-p_0(X))
\left\{ {\hat m_1(X)-m_{1,0}(X)\over \hat p(X)}
       +{\hat m_0(X)-m_{0,0}(X)\over 1-\hat p(X)}\right\}
\middle|\,\hat\eta\right].
\]
Consequently the deterministic first-order drift is bounded by a constant
times the localized product
\(\delta_{p,h,n}\delta_{m,h,n}\).  Under Assumption
\ref{ass:nuisance-rates} its exponent is \(r_m+r_p\) up to logarithms; under
only global \(L^2(P_X)\) nuisance control this conclusion is not asserted,
because the kernel weight can introduce an \(h_n\)-dependent amplification.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is not the novelty claim; it is the exact algebraic bridge
from the DML score of \citet[\S3]{ChernozhukovEtAl2018DML} to the local CATE
frontier.  Its gap is that the published DML theorem states sufficient
high-level remainders, while this display isolates the product term whose
scale is compared with \citet[\S2--\S4]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}.
(b) The concrete consumer is \citet{SemenovaChernozhukov2021DMLCATE}: the
identity tells when their first-order pseudo-outcome has a local report drift
large enough to obstruct CATE band inference.

\begin{theorem}[Theorem 2: Kennedy calibration and conditional first-order drift witness]\label{thm:kennedy-calibration}
Under Assumptions \ref{ass:causal}--\ref{ass:witness}, the published
Kennedy--Balakrishnan--Robins--Wasserman below-elbow region \(\mathsf B_K\)
and the first-order AIPW product-drift condition
\(\Delta_1(\alpha,\beta,\gamma,d)=r_m+r_p-r_\tau\le0\) are distinct objects.
If \((\alpha,\beta,\gamma,d)\in\mathsf B_K\), then by
\citet[\S2--\S4 and Theorems 1--2]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
uniform oracle-rate local CATE estimation is impossible over the full Holder
class, and the calibrated index in Conjecture \ref{conj:order-frontier} must
equal \(q_\star=\infty\).  Separately, if
\(\Delta_1(\alpha,\beta,\gamma,d)\le0\) and the aligned-error witness in
Assumption \ref{ass:aligned-witness} holds for a first-order AIPW report, then
the first-order drift in Theorem \ref{thm:first-order-drift} is not
\(o_{\Pr}(a_n)\) on that witness sequence.  Therefore that specified
first-order report cannot have the oracle Gaussian local CATE expansion
\[
a_n^{-1}\{\hat\theta_1(\ell_{h_n})-\theta_0(\ell_{h_n})\}
\rightsquigarrow N(0,V_{\mathrm{or}}(x_0))
\]
over the Holder experiment, where \(a_n=n^{-r_\tau}\) and
\(V_{\mathrm{or}}(x_0)\) is the oracle variance obtained when
\((m_{0,0},m_{1,0},p_0)\) are known.  The theorem makes no claim that
\(\Delta_1\le0\) is the Kennedy elbow, a full-class minimax impossibility, or
a lower bound for every nuisance learner in \(\mathcal A_1\); that uniform
necessity claim is part of Conjecture \ref{conj:order-frontier}.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This result is not claimed as a new publication-level contribution after
the v2 novelty review: it is a named calibration to the lower-bound elbow of
\citet[\S2--\S4 and Theorems 1--2]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}.
Its role is to keep their average-smoothness elbow \(\mathsf B_K\) separate
from the AIPW product index \(\Delta_1\) and to make the first-order failure
conditional on an explicit aligned-error witness rather than on an unstated
minimax lower bound.  (b) The concrete consumer is the local CATE
confidence-interval problem in
\citet[\S2--\S4]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}: the theorem
marks the region where the proposed \(q_\star\) frontier must declare
oracle-rate inference impossible, and the separate region where only
specified first-order AIPW reports with aligned nuisance errors are ruled out.

\begin{conjecture}[Conjecture 1: orthogonality-order frontier (NOT YET PROVED)]\label{conj:order-frontier}
Under Assumptions \ref{ass:causal}--\ref{ass:witness}, consider the primitive
localized HOIF classes \(\mathcal A_q^{\mathrm{loc}}\) in Assumption
\ref{ass:higher-order-class}.  For every fixed
\((\alpha,\beta,\gamma,d)\), the minimal order \(q\) for which there exists
\(\kappa\in\mathcal K_q\), \(J_n=n^\kappa\), and an estimator
\(\hat\theta_{q,J}\in\mathcal A_q^{\mathrm{loc}}\) with uniformly oracle
Gaussian local CATE inference is
\[
q_\star(\alpha,\beta,\gamma,d)=
\begin{cases}
\infty,&(\alpha,\beta,\gamma,d)\in\mathsf B_K,\\
q^\dagger(\alpha,\beta,\gamma,d),&\text{otherwise}.
\end{cases}
\]
For finite \(q_\star\), every \(q<q_\star\) fails to give uniform oracle
Gaussian inference on an open neighborhood of the wavelet witness laws.  If
\(q_\star=\infty\), no finite-order estimator in
\(\bigcup_{q<\infty}\mathcal A_q^{\mathrm{loc}}\) achieves that oracle
Gaussian limit: on \(\mathsf B_K\) this is exactly the published full-class
lower bound, and outside \(\mathsf B_K\) it is the primitive
projection-infeasibility claim.  If \(q_\star=1\), first-order DML already
attains the oracle local CATE Gaussian limit under the localized-rate
condition.  For any finite
\(q\ge\max\{2,q_\star\}\), the localized HOIF estimator
admits the explicit leading decomposition
\[
R_{q,J,n}=O_{\Pr}\{(\delta_{m,h,n}\delta_{p,h,n})^q\}
 +O_{\Pr}\{J_n^{-\min\{\alpha,\beta\}/d}\}
 +O_{\Pr}\{J_n^{q/2}n^{-q/2}h_n^{-d/2}\},
\]
and each displayed term is \(o_{\Pr}(a_n)\) for some
\(\kappa\in\mathcal K_q\), yielding the oracle local CATE Gaussian limit up to
logarithmic factors.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest comparator chain is
\citet[\S3, especially the orthogonal-score product-rate condition]{ChernozhukovEtAl2018DML}
\(\to\)
\citet[\S2.1, \S3.1, Corollary 4]{MackeySyrgkanisZadik2018OML} \(\to\)
\citet[\S2--\S3 on regularized Riesz local functionals]{ChernozhukovNeweySingh2022Riesz}
\(\to\)
\citet[\S2--\S4 and Theorems 1--2]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
\(\to\)
\citet{LiTchetgenVanDerVaartRobins2011HOIFTreatment}:
respectively first-order sufficient DML, higher-order orthogonality rate
relief, regularized Riesz local inference, minimax CATE elbows with localized
higher-order local-polynomial/R-learner upper constructions, and treatment-
effect higher-order U-statistic intervals under low regularity.  None names
the Kennedy-calibrated integer frontier
\(q_\star(\alpha,\beta,\gamma,d)\) together with the projection-feasibility
set \(\mathcal K_q\) as a necessary-and-sufficient order for local CATE
Gaussian inference outside the published below-elbow impossibility region.
(b) The concrete consumer is
automatic debiasing as in \citet{ChernozhukovNeweySingh2022AutoDML}: if
\(q_\star>1\), first-order learned Riesz corrections are not enough for local
CATE inference, and the debiasing target must be upgraded to a higher-order
correction or the report must be weakened.

\section{Sanity-check corollaries}
\begin{corollary}[Root-\(n\) scalar ATE corner]\label{cor:ate-corner}
If the report is replaced by a bounded global ATE weight \(\ell\equiv1\) so
that the oracle exponent becomes \(r_\tau=1/2\) and the Kennedy CATE
below-elbow set \(\mathsf B_K\) is not invoked, the first-order condition in
Conjecture \ref{conj:order-frontier} reduces to the usual DML product-rate
requirement \(r_m+r_p>1/2\); the localized projection set \(\mathcal K_q\) is
irrelevant in this nonlocal scalar corner.
\end{corollary}

\begin{corollary}[Oracle CATE corner]\label{cor:oracle-corner}
If the nuisances are known, then \(\delta_{m,n}=\delta_{p,n}=0\), all
orthogonality orders have zero nuisance drift, and the local CATE rate reduces
to the oracle nonparametric-regression rate \(n^{-\gamma/(2\gamma+d)}\).
\end{corollary}

\begin{example}[Concrete non-corner witness]\label{ex:wavelet-witness}
In the one-dimensional case with \(X\sim \mathrm{Unif}[0,1]\), interior
\(x_0=1/2\), and Haar-smooth wavelet perturbations satisfying Assumption
\ref{ass:witness}, the product-rate part of the boundary condition is
\[
q\left({\alpha\over 2\alpha+1}+{\beta\over 2\beta+1}\right)
>{\gamma\over 2\gamma+1}.
\]
For \(q\ge2\), the same witness also requires a projection exponent
\(\kappa\) satisfying \(\kappa\min\{\alpha,\beta\}>\gamma/(2\gamma+1)\) and
\(q(1-\kappa)>1\).  This witness is not the Gaussian oracle corner: both the
propensity and the outcome regression are perturbed away from constants while
overlap remains strict.
\end{example}

\section{Proof-sketch route}
Theorem \ref{thm:first-order-drift} follows by conditioning on the
cross-fitted nuisance estimates and expanding the AIPW identity under
unconfoundedness and then applying the local sup-norm rates from Assumption
\ref{ass:nuisance-rates}.  Theorem \ref{thm:kennedy-calibration} has two
checks.  The Kennedy-calibration clause is the implication ``oracle Gaussian
expansion implies oracle-rate estimation'' followed by the published
Kennedy--Balakrishnan--Robins--Wasserman lower bound on \(\mathsf B_K\),
whose definition is based on their average nuisance smoothness
\(s=(\alpha+\beta)/2\).  The conditional first-order-witness clause combines
the explicit AIPW product display from Theorem \ref{thm:first-order-drift}
with Assumption \ref{ass:aligned-witness}; no claim is made here that every
first-order learner must realize that aligned product drift.  The sufficiency
half of Conjecture
\ref{conj:order-frontier} would construct the localized HOIF correction
explicitly: fix \(q\), choose \(J_n=n^\kappa\), project the nuisance tangent
directions onto the localized basis \(b_{J_n}\), and verify the three-term
decomposition
\[
R_{q,J,n}=R^{\mathrm{prod}}_{q,n}+R^{\mathrm{proj}}_{J,n}
 +R^{\mathrm{ustat}}_{q,J,n}
\]
with the rates displayed in Conjecture \ref{conj:order-frontier}.  The
necessity half would first import the published lower bound on
\(\mathsf B_K\); outside \(\mathsf B_K\), it would use a two-point or packing
lower bound over the wavelet witness class: choose paired perturbations whose
local CATE shift is of order \(a_n\), whose likelihood ratio remains bounded,
and whose lower-order nuisance derivatives are canceled only through order
\(q-1\).  The boundary cases needing explicit algebra are the edge of
\(\mathsf B_K\), \(\Delta_1=0\), where logarithmic factors decide the
first-order product edge, and the transition from \(q_\star=1\) to
\(q_\star=2\), where \(\mathcal K_2\) can be empty even when the product-rate
inequality alone holds.

\section{Honest scope flags}
Theorem \ref{thm:first-order-drift} is routine algebra from the AIPW score and
is included only to lock the object.  Theorem \ref{thm:kennedy-calibration}
is a calibration to the published Kennedy--Balakrishnan--Robins--Wasserman
minimax elbow plus a conditional aligned-error first-order witness, not a new
full-class lower-bound claim.  Conjecture
\ref{conj:order-frontier} is not yet proved; the primitive localized HOIF
construction outside \(\mathsf B_K\), the \(q_\star=\infty\)
projection-infeasible case outside the published Kennedy lower-bound region,
and the matching wavelet or minimax lower bound for all lower-order
orthogonal reports are the genuine open work.
The proposal deliberately withdraws the failed angle-0 claim that a
two-channel empirical-process frontier had already been derived from
high-level frontier assumptions.  The v2 revision also withdraws the stronger
claim that an abstract class \(\mathcal A_q\) with assumed
\((\delta_m\delta_p)^q\) drift proves the frontier; Conjecture
\ref{conj:order-frontier} now asks for the primitive localized HOIF
construction and the matching wavelet lower bound.  The uncertain point is
whether the scalar product exponent \(q(r_m+r_p)\), plus \(\mathcal K_q\), is
exactly right for all \(\alpha,\beta\), or whether asymmetric
outcome/propensity smoothness creates mixed higher-order terms; if the latter
occurs, \(q_\star\) should be replaced by the corresponding multi-index order
frontier rather than forcing the scalar index.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 1, replacing the rejected
two-channel first-order frontier with a structurally different
orthogonality-order-index conjecture anchored to CATE minimax elbows; prior
verdict: none.
\item v2 (revise) -- added the local Riesz comparator, replaced global
\(L^2\) nuisance-rate language with localized rates, and reframed Conjecture
\ref{conj:order-frontier} around a primitive localized HOIF/U-statistic
remainder decomposition instead of an assumed abstract frontier; prior
verdict: REVISE.
\item v3 (revise) -- demoted the first-order below-elbow impossibility to a
Kennedy--Balakrishnan--Robins--Wasserman calibration theorem, made
\(q_\star\) total with an \(\infty\) projection-infeasible case, added
location-level anchors for the flagship comparator chain, and normalized the
wavelet witness coefficients by resolution; prior verdict: REVISE.
\item v4 (revise) -- separated the Kennedy average-smoothness elbow
\(\mathsf B_K\) from the first-order AIPW product index \(\Delta_1\), set
\(q_\star=\infty\) on the published Kennedy below-elbow region, and reframed
Conjecture \ref{conj:order-frontier} as the primitive localized-HOIF minimal
order outside that region; prior verdict: REVISE.
\item v5 (revise) -- narrowed Theorem \ref{thm:kennedy-calibration} to a
conditional aligned-error first-order witness, made the missing minimax
necessity an explicit part of Conjecture \ref{conj:order-frontier}, and added
Kennedy-estimator plus Li--Tchetgen--van der Vaart--Robins HOIF interval
comparators; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., Chetverikov, D., Demirer, M., Duflo, E., Hansen, C.,
Newey, W., and Robins, J. (2018).
Double/debiased machine learning for treatment and structural parameters.
\emph{The Econometrics Journal}, 21(1):C1--C68.
\url{https://doi.org/10.1111/ectj.12097}.

\bibitem[Semenova and Chernozhukov(2021)]{SemenovaChernozhukov2021DMLCATE}
Semenova, V. and Chernozhukov, V. (2021).
Debiased machine learning of conditional average treatment effects and other
causal functions.
\emph{The Econometrics Journal}, 24(2):264--289.
\url{https://doi.org/10.1093/ectj/utaa027}.

\bibitem[Kennedy et~al.(2024)]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
Kennedy, E. H., Balakrishnan, S., Robins, J. M., and Wasserman, L. (2024).
Minimax rates for heterogeneous causal effect estimation.
\emph{The Annals of Statistics}, 52(2):793--816.
\url{https://doi.org/10.1214/24-AOS2369}.

\bibitem[Robins et~al.(2008)]{RobinsLiTchetgenVanDerVaart2008HOIF}
Robins, J., Li, L., Tchetgen Tchetgen, E., and van der Vaart, A. W. (2008).
Higher order influence functions and minimax estimation of nonlinear
functionals.
In \emph{Probability and Statistics: Essays in Honor of David A. Freedman},
IMS Collections, volume 2, pages 335--421.
\url{https://arxiv.org/abs/0805.3040}.

\bibitem[Li et~al.(2011)]{LiTchetgenVanDerVaartRobins2011HOIFTreatment}
Li, L., Tchetgen Tchetgen, E., van der Vaart, A. W., and Robins, J. M. (2011).
Higher order inference on a treatment effect under low regularity conditions.
\emph{Statistics \& Probability Letters}, 81(7):821--828.
\url{https://doi.org/10.1016/j.spl.2011.02.030}.

\bibitem[Mackey et~al.(2018)]{MackeySyrgkanisZadik2018OML}
Mackey, L., Syrgkanis, V., and Zadik, I. (2018).
Orthogonal machine learning: power and limitations.
In \emph{Proceedings of the 35th International Conference on Machine
Learning}, PMLR 80:3375--3383.
\url{https://proceedings.mlr.press/v80/mackey18a.html}.

\bibitem[Chernozhukov et~al.(2022)]{ChernozhukovNeweySingh2022AutoDML}
Chernozhukov, V., Newey, W. K., and Singh, R. (2022).
Automatic debiased machine learning of causal and structural effects.
\emph{Econometrica}, 90(3):967--1027.
\url{https://doi.org/10.3982/ECTA18515}.

\bibitem[Chernozhukov et~al.(2022)]{ChernozhukovNeweySingh2022Riesz}
Chernozhukov, V., Newey, W. K., and Singh, R. (2022).
Debiased machine learning of global and local parameters using regularized
Riesz representers.
\emph{The Econometrics Journal}, 25(3):576--601.
\url{https://doi.org/10.1093/ectj/utac002}.

\bibitem[Foster and Syrgkanis(2023)]{FosterSyrgkanis2023OSL}
Foster, D. J. and Syrgkanis, V. (2023).
Orthogonal statistical learning.
\emph{The Annals of Statistics}, 51(3).
\url{https://doi.org/10.1214/23-AOS2258}.

\bibitem[Armstrong and Kolesar(2021)]{ArmstrongKolesar2021FiniteSampleATE}
Armstrong, T. B. and Kolesar, M. (2021).
Finite-sample optimal estimation and inference on average treatment effects
under unconfoundedness.
\emph{Econometrica}, 89(3):1141--1177.
\url{https://doi.org/10.3982/ECTA16907}.
\end{thebibliography}

\end{document}
