\begin{theorem}[Conjecture 1 frontier]\label{thm:frontier}
Under Assumptions \ref{ass:unconfounded}--\ref{ass:curvature}, first-order
orthogonal DML is uniformly asymptotically linear and Gaussian for the
\(\mathcal{L}_n\)-indexed HTE report process if and only if
\[
\sup_{P\in\mathcal{P}_n}\mathfrak{F}_n(P)
=\sup_{P\in\mathcal{P}_n}\max\{\sqrt n\,\delta_{g,n}(P)\delta_{p,n}(P),
\{\delta_{g,n}(P)+\delta_{p,n}(P)\}\mathcal{E}_n\}
\longrightarrow0 .
\]
The necessity half is interpreted in the minimax/adversarial first-order
experiment of Assumption \ref{ass:curvature}: if
\(\limsup_n\sup_{P\in\mathcal{P}_n}\mathfrak{F}_n(P)>0\) and either the active
curvature constant \(c_R\) or the empirical leakage constant \(c_{\mathrm{ep}}\)
is bounded below, then there exist an active sequence \(P_n\), an open subset
of the locked Holder nuisance class, and cross-fit nuisance estimates attaining
the active tangent directions for which
\[
\sup_{\ell\in\mathcal{L}_n}
\left|\sqrt n\{\hat\theta_n(\ell)-\theta_0(\ell)\}-\mathbb{G}_n(\ell)\right|
\]
has a liminf bounded away from zero in probability.  Thus the usual
oracle-centered first-order Gaussian studentization is not uniformly valid in
the minimax first-order experiment.  If \(\mathfrak{D}_n\) is the active
channel the failure is a deterministic translation by \(R_P\); if
\(\mathfrak{S}_n\) is the active channel the failure is non-negligible nuisance
empirical-process leakage.  Faster oracle learners outside the active error
class are not claimed to fail.

Equivalently, under Assumptions \ref{ass:unconfounded}--\ref{ass:curvature}, first-order orthogonal DML is uniformly asymptotically linear and Gaussian for the \(\mathcal{L}_n\)-indexed HTE report process if and only if \(\sup_{P\in\mathcal{P}_n}\mathfrak{F}_n(P)\to0\), with necessity interpreted in the minimax/adversarial first-order experiment of Assumption \ref{ass:curvature}.
\end{theorem}

\paragraph{Refutation attempt before proof.}
The required ExactID refutation primitive was the smallest finite SWIG/DAG
witness \(X\to D\to Y\) and \(X\to Y\).  I searched the two-point case
\(X\in\{0,1\}\) with \(0<\Pr(X=1)<1\), overlap
\(\underline e\le p_0(x)\le1-\underline e\), bounded potential outcomes
\(Y(d)\), and report classes containing either \(\ell\equiv1\) or the two cell
indicators.  This search cannot falsify the causal exact-ID part: by
Assumption \ref{ass:unconfounded}, for every admissible finite law,
\[
\E[\ell(X)\Gamma(W;\eta_0)\mid X]
=\ell(X)\{g_{1,0}(X)-g_{0,0}(X)\}
=\ell(X)\E[Y(1)-Y(0)\mid X],
\]
so the observable AIPW functional equals the target report cell by cell.  I
also checked the one-cell randomized subcase \(X=\emptyset\), \(p_0\in
[\underline e,1-\underline e]\).  With oracle nuisances, \(\delta_{g,n}=
\delta_{p,n}=0\), hence \(\mathfrak{F}_n(P)=0\) and Theorem
\ref{thm:score-remainder} reduces the estimator to the oracle empirical
process, exactly as the conjecture predicts.  With adversarial nonzero nuisance
errors \(u=\hat g-g_0\) and \(v=\hat p-p_0\), the same one-cell law gives the
deterministic drift
\[
R_P(1;u,v)
=v\left\{\frac{u_1}{p_0}+\frac{u_0}{1-p_0}\right\},
\]
so if \(\sqrt n|uv|\) is bounded away from zero, the oracle-centered estimator
has a first-order translation rather than a counterexample to the theorem.  The
finite-support overlap-violation candidate with \(p_0(x)=0\) in one stratum is
outside Assumption \ref{ass:unconfounded}.  Thus the primitive search found no
admissible witness against the conjecture; it instead reproduces the two
channels named in the statement.

\paragraph{Interpretation.}
The theorem says that exact identification by the AIPW signal is not the
limiting step.  Under consistency, conditional unconfoundedness, and fixed
overlap, \(\Psi_P(\ell)=\theta_0(\ell)\) is computable from the observed law.
The frontier is the extra first-order inference requirement for a whole
\(\mathcal{L}_n\)-indexed report process.  The term
\(\mathfrak{D}_n(P)=\sqrt n\,\delta_{g,n}(P)\delta_{p,n}(P)\) is the usual
orthogonal second-order drift, uniformly over report weights.  The term
\(\mathfrak{S}_n(P)=\{\delta_{g,n}(P)+\delta_{p,n}(P)\}\mathcal{E}_n\) is the
price of estimating nuisances inside a growing empirical process.  Both must
vanish for oracle-centered first-order Gaussian studentization to be uniformly
valid.  If either active channel remains visible in the minimax first-order
experiment of Assumption \ref{ass:curvature}, the failure is structural rather
than a proof artifact.

\begin{proof}[Proof of Theorem~\ref{thm:frontier}]
All statements below are uniform over \(\ell\in\mathcal{L}_n\) and
\(P\in\mathcal{P}_n\).  Let \(u=\hat g-g_0\) denote the pair
\((\hat g_1-g_{1,0},\hat g_0-g_{0,0})\) and \(v=\hat p-p_0\).  The exact-ID
identity and plug-in expansion are supplied by Theorem
\ref{thm:score-remainder}.  After multiplying that expansion by \(\sqrt n\)
and using the denominator replacement in Assumption \ref{ass:denominator}, we
obtain
\[
\sqrt n\{\hat\theta_n(\ell)-\theta_0(\ell)\}-\mathbb{G}_n(\ell)
=\sqrt n\,R_P(\ell;u,v)
+\sqrt n\,\Delta^{\mathrm{ep}}_n(\ell)+r_n(\ell),
\]
where \(\sup_{\ell\in\mathcal{L}_n}|r_n(\ell)|=o_P(1)\).  The divisions in
\(R_P\) and in \(\Gamma(W;\eta_0)\) are justified by the fixed overlap part of
Assumption \ref{ass:unconfounded} and the estimated-denominator event in
Assumption \ref{ass:denominator}.

First prove sufficiency.  The bilinear functional defined in Section 7 obeys,
by Cauchy--Schwarz, bounded reports, and fixed overlap,
\[
\sup_{\ell\in\mathcal{L}_n}|R_P(\ell;u,v)|
\le L_\ell\underline e^{-1}
\{\|u_1\|_{2,P}+\|u_0\|_{2,P}\}\|v\|_{2,P}
\le C\,\delta_{g,n}(P)\delta_{p,n}(P),
\]
for a constant \(C\) independent of \(n\), \(P\), and \(\ell\).  Therefore
\[
\sqrt n\sup_{\ell\in\mathcal{L}_n}|R_P(\ell;u,v)|
\le C\,\mathfrak{D}_n(P).
\]
Assumption \ref{ass:crossfit} gives
\[
\sqrt n\sup_{\ell\in\mathcal{L}_n}
|\Delta^{\mathrm{ep}}_n(\ell)|=O_P(\mathfrak{S}_n(P)).
\]
If \(\sup_{P\in\mathcal{P}_n}\mathfrak{F}_n(P)\to0\), then both
\(\sup_P\mathfrak{D}_n(P)\to0\) and \(\sup_P\mathfrak{S}_n(P)\to0\).  The last
three displays imply
\[
\sup_{\ell\in\mathcal{L}_n}
\left|\sqrt n\{\hat\theta_n(\ell)-\theta_0(\ell)\}
-\mathbb{G}_n(\ell)\right|=o_P(1)
\]
uniformly in \(P\).  This is the uniform asymptotic linear representation.  By
the oracle Gaussian approximation clause of Assumption \ref{ass:crossfit},
\(\mathbb{G}_n\) has a tight Gaussian multiplier approximation on
\(\mathcal{L}_n\) whenever \(\mathfrak{F}_n(P)\to0\).  The preceding
\(\ell^\infty(\mathcal{L}_n)\) remainder bound and Slutsky's theorem for
bounded stochastic processes transfer that Gaussian approximation from the
oracle process to the cross-fitted DML report process.  This proves the
upper-bound half.

Now prove the minimax/adversarial necessity statement in the precise sense
specified by Assumption \ref{ass:curvature}.  Suppose
\[
\limsup_{n\to\infty}\sup_{P\in\mathcal{P}_n}\mathfrak{F}_n(P)>0.
\]
Then for some \(\varepsilon>0\), a subsequence \(n_j\), and laws
\(P_j\in\mathcal{P}_{n_j}\), either
\(\mathfrak{D}_{n_j}(P_j)\ge\varepsilon\) along a further subsequence or
\(\mathfrak{S}_{n_j}(P_j)\ge\varepsilon\) along a further subsequence.

If the active channel is \(\mathfrak{D}_n\), Assumption
\ref{ass:curvature} supplies tangent errors \(u_j\in\mathcal{T}_{g,n_j}\) and
\(v_j\in\mathcal{T}_{p,n_j}\), with norms bounded by the locked learner radii,
and report weights \(\ell_j\in\mathcal{L}_{n_j}\) such that
\[
|R_{P_j}(\ell_j;u_j,v_j)|
\ge c_R(P_j)\delta_{g,n_j}(P_j)\delta_{p,n_j}(P_j).
\]
On the active subsequence \(c_R(P_j)\ge c_0>0\), hence
\[
\sqrt{n_j}|R_{P_j}(\ell_j;u_j,v_j)|
\ge c_0\,\mathfrak{D}_{n_j}(P_j)
\ge c_0\varepsilon .
\]
Choosing cross-fit learners in the open Holder neighborhood that attain these
tangent directions gives, by Theorem \ref{thm:score-remainder}, an
oracle-centered process with a deterministic first-order translation of size at
least \(c_0\varepsilon+o(1)\) in the active direction.  Such a translated
process cannot be uniformly centered Gaussian under the usual
oracle-centered studentization.

If the active channel is \(\mathfrak{S}_n\), Assumption
\ref{ass:curvature} instead supplies cross-fit nuisance estimates in the
active tangent class for which
\[
\sqrt{n_j}\sup_{\ell\in\mathcal{L}_{n_j}}
|\Delta^{\mathrm{ep}}_{n_j}(\ell)|
\ge c_{\mathrm{ep}}(P_j)
\{\delta_{g,n_j}(P_j)+\delta_{p,n_j}(P_j)\}\mathcal{E}_{n_j}
\]
with probability bounded away from zero.  On the active subsequence
\(c_{\mathrm{ep}}(P_j)\ge c_0>0\), so the right side is at least
\(c_0\varepsilon\) with probability bounded away from zero.  The expansion from
Theorem \ref{thm:score-remainder} then leaves a non-negligible nuisance
empirical-process component in
\[
\sup_{\ell\in\mathcal{L}_{n_j}}
\left|\sqrt{n_j}\{\hat\theta_{n_j}(\ell)-\theta_{0,j}(\ell)\}
-\mathbb{G}_{n_j}(\ell)\right|.
\]
Consequently the oracle-centered first-order Gaussian approximation is not
uniformly valid in the minimax first-order experiment.  The theorem makes no
claim about faster oracle learners outside this active error class, so this is
exactly the promised necessity statement.
\end{proof}

\paragraph{Sanity check.}
Take the randomized special case \(X=\emptyset\), \(\mathcal{L}_n=\{1\}\), and
\(p_0=\Pr(D=1)\in[\underline e,1-\underline e]\).  The target is the ATE
\(\theta_0= \E[Y(1)-Y(0)]\), and the AIPW functional collapses to
\[
\Psi_P(1)=g_{1,0}-g_{0,0}
+\E\!\left[\frac{D}{p_0}(Y-g_{1,0})\right]
-\E\!\left[\frac{1-D}{1-p_0}(Y-g_{0,0})\right]
=g_{1,0}-g_{0,0}.
\]
Because treatment is randomized, \(g_{d,0}=\E[Y(d)]\), so
\(\Psi_P(1)=\theta_0\).  The report entropy is constant, so
\(\mathcal{E}_n\asymp1\), and the theorem reduces to the familiar scalar DML
condition
\(\sqrt n\,\delta_{g,n}\delta_{p,n}\to0\) together with
\(\delta_{g,n}+\delta_{p,n}\to0\) for the nuisance empirical-process term.
With oracle nuisances both channels are zero and the estimator is the usual
centered empirical mean of the efficient ATE signal.

\paragraph{Minimality check.}
Fixed overlap is a genuine support condition.  In the two-stratum finite law
with \(X\in\{0,1\}\), \(\Pr(X=x)>0\), and \(p_0(1)=0\), the target contribution
\(\Pr(X=1)\ell(1)\E[Y(1)-Y(0)\mid X=1]\) is part of
\(\theta_0(\ell)\), but the treated conditional mean \(g_{1,0}(1)=\E[Y\mid
D=1,X=1]\) is not identified from the observed law.  The AIPW signal also
contains the undefined factor \(D/p_0(1)\).  Thus dropping positivity on a
stratum used by \(\ell\) breaks the computable identifying functional before
any DML frontier question arises.  Separately, keeping overlap but dropping
the active-curvature lower bound removes the minimax necessity conclusion:
there may be no admissible nuisance tangent direction that realizes a
first-order \(R_P\) translation or empirical-process leakage even when a
high-level error envelope is numerically large.
