% --- \S9-fragment-statement ---
\paragraph{\S9-fragment-statement.}
\begin{theorem}[Conjecture 2: Holder-rate frontier]\label{thm:holder-frontier}
\paragraph{Motivating claim, restated verbatim.}
In the canonical Holder-rate specialization of Assumption \ref{ass:holder} with
\(\mathcal{E}_n\asymp n^\zeta\), the frontier in Conjecture
\ref{conj:frontier} is equivalent, up to logarithmic factors, to
\[
\frac{\alpha_g}{2\alpha_g+d}+\frac{\alpha_p}{2\alpha_p+d}
>\frac12,\qquad
\min\left\{\frac{\alpha_g}{2\alpha_g+d},\frac{\alpha_p}{2\alpha_p+d}\right\}
>\zeta.
\]
Below this boundary, first-order DML cannot be uniformly Gaussian over the
locked Holder/entropy class; above it, first-order DML is uniformly Gaussian
provided the oracle Gaussian approximation in Assumption \ref{ass:crossfit}
holds.

\paragraph{Headline.}
Conjecture~\ref{conj:holder} is confirmed: in the canonical Holder-rate specialization with \(r_g=\alpha_g/(2\alpha_g+d)\), \(r_p=\alpha_p/(2\alpha_p+d)\), and \(\mathcal{E}_n\asymp n^\zeta\), the two-channel frontier satisfies
\[
\mathfrak F_n(P)\asymp
\max\{n^{1/2-r_g-r_p},\,n^{\zeta-\min(r_g,r_p)}\}
\]
up to logarithmic factors, so \(\mathfrak F_n(P)\to0\) if and only if \(r_g+r_p>1/2\) and \(\min(r_g,r_p)>\zeta\); above this boundary the oracle-centered first-order DML report process is uniformly Gaussian under Assumption~\ref{ass:crossfit}, while below it uniform Gaussianity fails in the active-channel experiment of Assumption~\ref{ass:curvature}.
\end{theorem}

% --- \S13-refutation-attempt ---
\paragraph{\S13-refutation-attempt.}
The required refutation-first check was run inside the exact-identification
regime locked by the setup: \(X\to D\to Y\), \(X\to Y\), binary \(D\),
consistency, conditional unconfoundedness, fixed overlap, Holder nuisance
classes, and the two-channel first-order experiment in Assumptions
\ref{ass:unconfounded}--\ref{ass:curvature}.

First, consider the three-node SWIG/back-door primitive with a finite law on
\((X,D,Y)\).  For any candidate satisfying
\((Y(1),Y(0))\perp D\mid X\), consistency, and
\(\underline e\le p_0(X)\le1-\underline e\), Theorem
\ref{thm:score-remainder} gives the exact observable identity
\[
\theta_0(\ell)=\E[\ell(X)\Gamma(W;\eta_0)]
\]
for every report weight \(\ell\).  Thus no three-node exact-ID witness can
make the target report differ from the AIPW functional.  Such a witness would
have to break the rate frontier, not the identifying formula.

Second, try the finite-support overlap-violation primitive.  On a two-point
support, setting \(p_0(x_0)=0\) or \(p_0(x_0)=1\) would indeed obstruct the
terms \(D\{Y-g_{1,0}(X)\}/p_0(X)\) or
\((1-D)\{Y-g_{0,0}(X)\}/\{1-p_0(X)\}\).  This is not an admissible
counterexample, because Assumption \ref{ass:unconfounded} imposes the fixed
overlap bound on every stratum actually used by \(\ell\).  Keeping fixed
overlap leaves the AIPW map well defined and does not change the two exponents
\(\sqrt n\,\delta_{g,n}\delta_{p,n}\) and
\((\delta_{g,n}+\delta_{p,n})\mathcal{E}_n\).

Third, trace the do-calculus/adjustment step.  The only conditional
independence required for the exact-ID part is the back-door independence
\((Y(1),Y(0))\perp D\mid X\), already named in Assumption
\ref{ass:unconfounded}.  Once that adjustment is in place, the conjecture
reduces to the deterministic exponent comparison
\[
\sqrt n\,\delta_{g,n}\delta_{p,n}
\quad\hbox{and}\quad
(\delta_{g,n}+\delta_{p,n})\mathcal{E}_n.
\]
The boundary cases do not refute the conjecture: if \(r_g+r_p=1/2\), the
drift channel is order one, and if \(\min(r_g,r_p)=\zeta\), the
empirical-process leakage channel is order one.  Assumption
\ref{ass:curvature} supplies active tangent directions for those channels, so
these boundary candidates support the strict inequalities rather than
contradicting them.  The bounded search therefore finds no admissible witness,
and the proof below verifies the claim.

% --- \S10 Interpretation ---
\paragraph{\S10 Interpretation.}
The theorem says that the abstract frontier has two independent rate
requirements in the canonical Holder specialization.  The deterministic
orthogonal-score drift is controlled by the product of the outcome-regression
and propensity rates, so it disappears at first order exactly when
\(\sqrt n\,n^{-r_g}n^{-r_p}\to0\), or \(r_g+r_p>1/2\).  The growing HTE report
class creates a separate nuisance empirical-process channel.  Since
\(\delta_{g,n}+\delta_{p,n}\) is governed by the slower of the two nuisance
rates, that channel disappears exactly when
\(n^{-\min(r_g,r_p)}n^\zeta\to0\), or \(\min(r_g,r_p)>\zeta\).

This connects the motivating frontier to the usual DML product-rate message.
When \(\mathcal L_n\) is effectively fixed, \(\zeta=0\), the entropy channel
does not bind for positive Holder smoothness and the product-rate condition is
the familiar one.  As the report class grows, the entropy inequality becomes a
second and genuinely distinct requirement: even if the product remainder is
small, first-order Gaussian inference can fail because nuisance error leaks
through the indexed empirical process.

% --- \S11 Proof ---
\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:holder-frontier}]
Set
\[
r_g=\frac{\alpha_g}{2\alpha_g+d},
\qquad
r_p=\frac{\alpha_p}{2\alpha_p+d}.
\]
In the canonical Holder-rate specialization of Assumption \ref{ass:holder},
the uniform nuisance envelopes satisfy
\[
\delta_{g,n}(P)\asymp n^{-r_g},
\qquad
\delta_{p,n}(P)\asymp n^{-r_p},
\]
up to the logarithmic factors suppressed in the statement.  Assumption
\ref{ass:entropy} and the conjecture's specialization give
\(\mathcal{E}_n\asymp n^\zeta\), again up to logarithmic factors.  Therefore
the deterministic drift channel is
\[
\mathfrak D_n(P)
=\sqrt n\,\delta_{g,n}(P)\delta_{p,n}(P)
\asymp
n^{1/2-r_g-r_p}.
\]
Similarly,
\[
\mathfrak S_n(P)
=\{\delta_{g,n}(P)+\delta_{p,n}(P)\}\mathcal{E}_n
\asymp
\{n^{-r_g}+n^{-r_p}\}n^\zeta
\asymp
n^{\zeta-\min(r_g,r_p)}.
\]
The last equivalence is the elementary identity that the larger of
\(n^{-r_g}\) and \(n^{-r_p}\) is \(n^{-\min(r_g,r_p)}\).  Since
\(\mathfrak F_n(P)=\max\{\mathfrak D_n(P),\mathfrak S_n(P)\}\), this proves
\[
\mathfrak F_n(P)\asymp
\max\{n^{1/2-r_g-r_p},\,n^{\zeta-\min(r_g,r_p)}\}
\]
with the same logarithmic convention.

A power \(n^a\) tends to zero if and only if \(a<0\).  Hence
\(\mathfrak D_n(P)\to0\) if and only if
\[
1/2-r_g-r_p<0,
\quad\hbox{that is}\quad
r_g+r_p>1/2,
\]
and \(\mathfrak S_n(P)\to0\) if and only if
\[
\zeta-\min(r_g,r_p)<0,
\quad\hbox{that is}\quad
\min(r_g,r_p)>\zeta.
\]
Because the maximum of two nonnegative sequences tends to zero exactly when
both sequences tend to zero, the two displayed inequalities are equivalent to
\(\mathfrak F_n(P)\to0\).  Substituting the definitions of \(r_g\) and \(r_p\)
gives the two inequalities displayed in the motivating claim.

Now suppose the two inequalities hold uniformly over the locked
Holder/entropy class.  Theorem \ref{thm:score-remainder} gives the uniform
expansion
\[
\sqrt n\{\hat\theta_n(\ell)-\theta_0(\ell)\}
=\mathbb G_n(\ell)
+\sqrt n\,\widetilde R_P(\ell;\hat g-g_0,\hat p-p_0,\hat p)
+\sqrt n\,\Delta_n^{\mathrm{ep}}(\ell)+o_P(1)
\]
uniformly in \(\ell\in\mathcal L_n\).  Assumption \ref{ass:denominator} lets
us replace \(\widetilde R_P\) by \(R_P\) at \(o_P(1)\) first-order scale.  The
boundedness and fixed-overlap calculation in the setup gives
\[
\sqrt n\sup_{\ell\in\mathcal L_n}|R_P(\ell;\hat g-g_0,\hat p-p_0)|
\lesssim
\sqrt n\,\delta_{g,n}(P)\delta_{p,n}(P)
=\mathfrak D_n(P)=o(1).
\]
Assumption \ref{ass:crossfit} gives
\[
\sqrt n\sup_{\ell\in\mathcal L_n}|\Delta_n^{\mathrm{ep}}(\ell)|
=O_P(\mathfrak S_n(P))=o_P(1).
\]
Thus
\[
\sup_{\ell\in\mathcal L_n}
\left|
\sqrt n\{\hat\theta_n(\ell)-\theta_0(\ell)\}-\mathbb G_n(\ell)
\right|
\to_P0.
\]
The oracle process \(\mathbb G_n\) admits the tight Gaussian multiplier
approximation by Assumption \ref{ass:crossfit} whenever
\(\mathfrak F_n(P)\to0\).  Combining this approximation with the displayed
uniform \(o_P(1)\) difference proves the upper-bound claim: first-order DML is
uniformly Gaussian above the Holder boundary.

Conversely, suppose the product inequality fails, so \(r_g+r_p\le1/2\).  Then
\(\mathfrak D_n(P)\) does not tend to zero.  In the active drift channel,
Assumption \ref{ass:curvature} supplies a nondegenerate Holder tangent cone
and a constant bounded away from zero along an admissible sequence such that
\[
\sup_{\ell\in\mathcal L_n}|R_P(\ell;u_n,v_n)|
\ge c_R(P)\delta_{g,n}(P)\delta_{p,n}(P).
\]
Multiplying by \(\sqrt n\) gives a first-order deterministic translation whose
liminf is bounded away from zero along the active sequence.  The oracle-centered
process therefore cannot be uniformly approximated by \(\mathbb G_n\) over the
locked first-order experiment.

If instead the entropy inequality fails, so \(\min(r_g,r_p)\le\zeta\), then
\(\mathfrak S_n(P)\) does not tend to zero.  In the active empirical-process
channel, Assumption \ref{ass:curvature} supplies cross-fit nuisance errors for
which
\[
\sqrt n\sup_{\ell\in\mathcal L_n}|\Delta_n^{\mathrm{ep}}(\ell)|
\ge
c_{\mathrm{ep}}(P)\{\delta_{g,n}(P)+\delta_{p,n}(P)\}\mathcal{E}_n
\]
with probability bounded away from zero.  Thus the nuisance empirical-process
leakage remains visible at first order, again preventing a uniform
oracle-centered Gaussian approximation.  These two cases cover the complement
of the strict Holder boundary and prove the claimed failure below it in the
active-channel experiment of Assumption \ref{ass:curvature}.
\end{proof}

% --- \S12 Sanity check ---
\paragraph{\S12 Sanity check.}
Take the fixed-report corner \(\mathcal{E}_n\asymp1\), so \(\zeta=0\).  Because
\(\alpha_g,\alpha_p>0\), both \(r_g\) and \(r_p\) are positive, and the entropy
condition
\[
\min(r_g,r_p)>\zeta
\]
is automatic.  The theorem reduces to the familiar first-order DML
product-rate condition
\[
r_g+r_p>1/2.
\]
For a symmetric nuisance class with \(\alpha_g=\alpha_p=\alpha\), this becomes
\[
2\frac{\alpha}{2\alpha+d}>\frac12,
\]
or equivalently \(\alpha>d/2\).  Thus the fixed-report special case recovers
the usual product-rate elbow: each nuisance may be slower than \(n^{-1/4}\)
only if the other is faster enough that the product remains \(o(n^{-1/2})\),
and in the symmetric case both must beat the \(n^{-1/4}\) rate.

% --- \S13 Counterexample or minimality check ---
\paragraph{\S13 Counterexample or minimality check.}
The strict inequalities are minimal.  At the deterministic-drift boundary,
choose an active Holder sequence from Assumption \ref{ass:curvature} with
\(r_g+r_p=1/2\) and \(\min(r_g,r_p)>\zeta\).  Then
\[
\mathfrak D_n(P)\asymp n^{1/2-r_g-r_p}\asymp1,
\qquad
\mathfrak S_n(P)=o(1).
\]
Theorem \ref{thm:score-remainder} and the active \(R_P\) lower bound imply
that
\[
\sup_{\ell\in\mathcal L_n}
\left|
\sqrt n\{\hat\theta_n(\ell)-\theta_0(\ell)\}-\mathbb G_n(\ell)
\right|
\]
has a deterministic translation bounded away from zero along the active
sequence.  Replacing \(r_g+r_p>1/2\) by \(r_g+r_p\ge1/2\) would therefore be
false.

At the entropy boundary, choose an active report-class sequence from
Assumption \ref{ass:curvature} with \(\min(r_g,r_p)=\zeta\) and
\(r_g+r_p>1/2\).  Then
\[
\mathfrak D_n(P)=o(1),
\qquad
\mathfrak S_n(P)\asymp1.
\]
The empirical-process lower bound in Assumption \ref{ass:curvature} gives
non-negligible \(\sqrt n\,\Delta_n^{\mathrm{ep}}\) with probability bounded
away from zero.  Replacing \(\min(r_g,r_p)>\zeta\) by
\(\min(r_g,r_p)\ge\zeta\) would therefore also be false.  Fixed overlap in
Assumption \ref{ass:unconfounded}, the denominator condition in Assumption
\ref{ass:denominator}, and the active-channel lower bounds in Assumption
\ref{ass:curvature} are the support and rank conditions that make these
minimality witnesses valid.

\paragraph{Substrate audit record.}
\texttt{bypass-justified}: declaration-level searches for the requested
ExactID primitives did not surface a reusable project-level object matching
this semiparametric Holder/entropy HTE-DML frontier.  The fragment therefore
uses the shared mathematical setup and Theorem \ref{thm:score-remainder}
rather than introducing a substrate-specific object.
