% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orthogonality\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_dml\_orthogonality\_frontier} / \texttt{v1}%
  \\ \large\textit{Orthogonal excess risk does not buy Gaussian HTE bands: an entropy--remainder counterfrontier}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form ExactID proposal.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
Here \(\texttt{qid}=\texttt{eid\_dml\_orthogonality\_frontier}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph/SWIG has observed
\((X,D,Y)\), binary treatment \(D\in\{0,1\}\), potential outcomes
\((Y(1),Y(0))\), and observed outcome \(Y=DY(1)+(1-D)Y(0)\).  The treatment is
the binary intervention \(D\leftarrow d\).  The target estimands are the
heterogeneous-treatment-effect reports
\[
\theta_h(P)=\E_P[h(X)\tau_0(X)],\qquad
\tau_0(x)=\E_P[Y(1)-Y(0)\mid X=x],\qquad h\in\calH_n,
\]
with simultaneous inference over an entropy-indexed report class \(\calH_n\).
The identifying assumptions are consistency, conditional unconfoundedness
\((Y(1),Y(0))\perp D\mid X\), overlap \(\varepsilon\leq e_0(X)\leq 1-\varepsilon\),
and finite second moments.  The proposed estimator is the cross-fitted
first-order AIPW/DML report process based on nuisances
\(\eta=(m_1,m_0,e)\), where \(m_d(x)=\E[Y\mid D=d,X=x]\) and
\(e(x)=\Pr(D=1\mid X=x)\).

\begin{abstract}
Orthogonal statistical learning shows that Neyman-orthogonal losses can retain
second-order excess-risk behavior even when nuisance functions are learned by
complex methods.  This proposal asks whether those excess-risk guarantees are
enough to justify simultaneous Gaussian confidence bands for heterogeneous
treatment-effect DML reports over growing report classes.  The proposed kernel
is a counterfrontier: the named Gaussian-band gap index
\(\Lambda_n\), combining report entropy and second-order nuisance drift, is
conjectured to be the sharp obstruction separating excess-risk-valid
orthogonal learning from honest Gaussian bands.  The flagship conjecture is not
that first-order DML always fails; it is that \citet{FosterSyrgkanis2023OSL}'s
excess-risk conclusion can hold while \citet{SemenovaChernozhukov2021DMLCATE}
style multiplier bands undercover whenever \(\Lambda_n\) stays bounded away
from zero.  Resolving this would tell empirical HTE users when an orthogonal
learner must report a report-class entropy diagnostic before using simultaneous
bands.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Modern HTE work often estimates rich CATE objects and then displays many
subgroup, basis, or function-valued reports with simultaneous bands.  Neyman
orthogonality makes this plausible by killing first-order nuisance bias, but
orthogonal excess-risk control is a prediction guarantee, not automatically a
Gaussian approximation for a supremum of many debiased reports.  The scientific
question is whether a learner that is good enough for orthogonal risk is also
good enough for honest simultaneous causal inference.

\paragraph{The main finding (proposed).}
The headline result is Conjecture~\ref{conj:gap-counterfrontier}: for a
finite-packing Holder witness class and its open perturbations, there are
orthogonal HTE learners satisfying the excess-risk conclusion of
\citet{FosterSyrgkanis2023OSL} but whose DML multiplier bands have non-vanishing
undercoverage when the Gaussian-band gap index
\(\Lambda_n=\sqrt{2\log M_n}\,|b_n|/\sigma_n\) has a positive limit.  The same
conjecture includes the positive edge: when \(\Lambda_n\to0\) and the usual
high-dimensional Gaussian approximation remainder is negligible, the same
first-order reports recover valid simultaneous bands.  Theorem~\ref{thm:id}
records the standard ExactID AIPW identity so the proposed frontier is about
inference, not identification.

\paragraph{What is new.}
The novelty kernel is the \emph{Gaussian-band gap index}
\(\Lambda_n\), a focal scalar whose factors are independently meaningful:
\(\sqrt{2\log M_n}\) is the extreme-value inflation of a report-class packing,
\(b_n\) is the common second-order orthogonal nuisance drift left invisible to
excess-risk control, and \(\sigma_n\) is the report standard deviation.  The
proposal is informed by the sufficient product-rate conditions in
\citet{ChernozhukovEtAl2018DML}, but the delivered comparator promise is
against the BLP/group-average simultaneous inference conditions in
\citet{SemenovaChernozhukov2021DMLCATE} and the orthogonal excess-risk theorem
of \citet{FosterSyrgkanis2023OSL}.  It targets a strict
non-implication: second-order orthogonal excess risk may hold while Gaussian
HTE bands fail by a quantifiable entropy-amplified mean shift.

\paragraph{How it positions in the literature.}
This is an ExactID / causal-ML proposal.  The identification object is the
standard unconfoundedness AIPW functional for weighted CATE reports.  The
frontier itself sits between DML inference, high-dimensional Gaussian
approximation, and orthogonal statistical learning: \citet{ChernozhukovEtAl2018DML}
give orthogonal scores and cross-fitting, \citet{ChernozhukovChetverikovKato2017EmpiricalBootstrap}
give Gaussian and multiplier bootstrap tools for growing empirical processes,
\citet{SemenovaChernozhukov2021DMLCATE} use such tools for CATE reports, and
\citet{FosterSyrgkanis2023OSL} prove entropy-aware orthogonal excess-risk
oracle inequalities.  The proposal asks for the missing bridge theorem, and a
matching counterexample, between the last two claims.

\paragraph{Implications for the community.}
The concrete downstream consumer is simultaneous HTE reporting in
\citet{SemenovaChernozhukov2021DMLCATE}: if the conjecture resolves favorably,
those reports gain a necessary entropy--remainder diagnostic rather than only a
list of sufficient nuisance-rate assumptions.

\paragraph{How research benefits from the conclusion.}
Researchers using orthogonal HTE learners should check or estimate a
report-class entropy times nuisance-drift diagnostic before treating an
orthogonal excess-risk guarantee as permission to draw simultaneous Gaussian
bands.

\section{Related work}
\citet{ChernozhukovEtAl2018DML} is the canonical DML anchor: it introduces
orthogonal scores and cross-fitting and states sufficient nuisance product-rate
conditions for asymptotically linear treatment-effect estimators.  The present
proposal keeps the same first-order AIPW score but asks for a necessary
entropy-amplified obstruction to simultaneous HTE bands.

\citet{SemenovaChernozhukov2021DMLCATE} develops debiased ML for CATE and
other causal functions, including simultaneous inference for best linear
predictors and group averages using Gaussian bootstrap.  The proposed
counterfrontier is directly relevant to their simultaneous-inference consumer:
it identifies a drift regime where orthogonal reports can be risk-valid but
band-invalid.

\citet{FosterSyrgkanis2023OSL} gives nonasymptotic orthogonal statistical
learning bounds under metric entropy, with nuisance error entering at second
order.  This paper is the main comparator: Conjecture~\ref{conj:gap-counterfrontier}
is a non-representability result showing that those excess-risk guarantees do
not, by themselves, imply Gaussian HTE bands.

\citet{ChernozhukovChetverikovKato2017HDCLT} and
\citet{ChernozhukovChetverikovKato2017EmpiricalBootstrap} provide
high-dimensional Gaussian approximation and multiplier-bootstrap theory for
maxima and suprema of empirical processes.  The proposal uses their
anti-concentration logic to explain why a coordinatewise second-order drift can
be magnified by \(\sqrt{\log M_n}\) in a simultaneous band.

\citet{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE} derives minimax CATE
rates and nuisance-smoothness elbows using higher-order ideas.  Their result is
adjacent because it shows that first-order orthogonality has smoothness
boundaries, while this proposal isolates a distinct simultaneous-inference
boundary driven by entropy-amplified second-order drift.

\citet{ChernozhukovNeweySingh2022Riesz} study debiased ML for global and local
linear functionals using regularized Riesz representers, including nonregular
local objects.  Their local-functional instability motivates the present
proposal's focus on report classes whose effective dimension grows.

\citet{ArmstrongKolesar2021FiniteSampleATE} show that honest ATE inference
under unconfoundedness depends sharply on smoothness, shape, and overlap
restrictions.  Their finite-sample necessity perspective supports the proposal
strategy: inferential validity should be characterized by necessity frontiers,
not only sufficient DML rate conditions.

In-repository prior art does not contain this kernel.  The \texttt{doc/API.md}
ExactID / PartialID catalogue reports that new \texttt{eid\_*} qids are seeded
through CausalSmith and that the current ExactID catalogue has no documented
Holder/entropy DML theorem.  The failed bank entry
\texttt{eid\_dml\_orth\_uniform/v2} targeted a two-channel DML/LRO/ADML
studentization frontier, but Stage~0.5 rejected it because the advertised
frontier was encoded in high-level assumptions; the present pivot instead
targets the structurally different Foster--Syrgkanis excess-risk-to-band
non-implication and names the concrete scalar \(\Lambda_n\) as the focal object.

\section{Formal setup}
Let \(O=(X,D,Y)\sim P\), \(D\in\{0,1\}\), and \(Y=DY(1)+(1-D)Y(0)\).  Write
\[
m_d(x)=\E_P[Y\mid D=d,X=x],\qquad e(x)=\Pr_P(D=1\mid X=x),
\qquad \tau_0(x)=m_1(x)-m_0(x).
\]
For a report function \(h\in\calH_n\), the target is
\(\theta_h(P)=\E_P[h(X)\tau_0(X)]\).  The AIPW signal is
\[
\psi_h(O;\eta)=h(X)\left[
m_1(X)-m_0(X)+\frac{D\{Y-m_1(X)\}}{e(X)}
-\frac{(1-D)\{Y-m_0(X)\}}{1-e(X)}
\right],
\]
where \(\eta=(m_1,m_0,e)\).  The cross-fitted DML report is
\(\widehat\theta_h=n^{-1}\sum_{i=1}^n \psi_h(O_i;\widehat\eta_{-k(i)})\).
Let
\[
Z_{n,h}=\frac{\sqrt n(\widehat\theta_h-\theta_h(P))}{\sigma_h(P)},\qquad
\sigma_h^2(P)=\operatorname{Var}_P(\psi_h(O;\eta_0)).
\]

The proposal studies a finite-packing subclass
\(\calH_n^\circ=\{h_1,\ldots,h_{M_n}\}\subseteq\calH_n\).  Let \(b_{n,j}(P)\)
denote the second-order mean drift
\[
b_{n,j}(P)=\E_P[\psi_{h_j}(O;\widehat\eta)-\psi_{h_j}(O;\eta_0)
+\theta_{h_j}(P)-\theta_{h_j}(P_{\widehat\eta})],
\]
with \(b_n=\max_{1\leq j\leq M_n}|b_{n,j}(P)|\) and
\(\sigma_n=\min_{1\leq j\leq M_n}\sigma_{h_j}(P)\).  The named focal object is
the \emph{Gaussian-band gap index}
\[
\Lambda_n(P,\widehat\eta,\calH_n^\circ)
=\sqrt{2\log M_n}\,\frac{b_n}{\sigma_n}.
\]
The companion high-dimensional Gaussian approximation remainder is
\[
G_n(P,\calH_n^\circ)=
\sup_t\left|\Pr\left(\max_{j\leq M_n} Z^0_{n,h_j}\leq t\right)
-\Pr\left(\max_{j\leq M_n} G_{n,j}\leq t\right)\right|,
\]
where \(Z^0_{n,h_j}\) is the oracle centered score process and
\((G_{n,1},\ldots,G_{n,M_n})\) is a centered Gaussian vector with the same
covariance.

\begin{center}
\fbox{\begin{minipage}{0.92\linewidth}
This proposal uses the ExactID/free-form convention
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
The entries are
\(\texttt{qid}=\texttt{eid\_dml\_orthogonality\_frontier}\),
\(\texttt{specialization}=\texttt{v1}\), graph/SWIG
\((X,D,Y(1),Y(0),Y)\) with \(Y=DY(1)+(1-D)Y(0)\), treatment \(D\leftarrow d\),
target \(\{\theta_h(P):h\in\calH_n\}\), and assumptions consistency,
conditional unconfoundedness, overlap, finite second moments, and the
report-class / nuisance-class restrictions listed in Section~\ref{sec:assumptions}.
\end{minipage}}
\end{center}

\section{Assumptions}\label{sec:assumptions}
\begin{assumption}[ExactID sampling and overlap]\label{ass:exactid}
The observations \(O_i=(X_i,D_i,Y_i)\) are i.i.d.; consistency holds; \((Y(1),Y(0))\perp D\mid X\); \(\varepsilon\leq e(X)\leq 1-\varepsilon\) almost surely for a fixed \(\varepsilon>0\); and \(\E[Y(d)^2]<\infty\) for \(d\in\{0,1\}\).
\end{assumption}

\begin{assumption}[Report entropy and variance]\label{ass:entropy}
For each \(n\), \(\calH_n\) has envelope \(B_{h,n}<\infty\), contains a finite
\(L_2(P)\)-separated packing
\(\calH_n^\circ=\{h_1,\ldots,h_{M_n}\}\), and
\(0<\underline\sigma\leq\sigma_{h_j}(P)\leq\overline\sigma<\infty\) for all
\(j\leq M_n\).  The entropy scale is \(H_n=\log M_n\).
\end{assumption}

\begin{assumption}[Cross-fitted first-order orthogonal reports]\label{ass:dml}
The estimator \(\widehat\theta_h\) is the sample average of the AIPW signal
\(\psi_h(O;\widehat\eta_{-k(i)})\) with folds independent of their nuisance
training samples.  The nuisance errors satisfy
\(\|\widehat m_d-m_d\|_{2,P}\leq a_{d,n}\) and
\(\|\widehat e-e\|_{2,P}\leq c_n\), and the second-order drift vector
\((b_{n,1},\ldots,b_{n,M_n})\) is well-defined.
\end{assumption}

\begin{assumption}[Orthogonal excess-risk benchmark]\label{ass:osl}
The learner also satisfies an orthogonal statistical learning excess-risk
bound of the Foster--Syrgkanis type:
\[
\mathcal E_{\mathrm{OSL},n}
\leq C_{\mathrm{OSL}}\{r_{\theta,n}^2+a_{1,n}^2+a_{0,n}^2+c_n^2\}
\]
up to logarithmic factors, where \(r_{\theta,n}\) is the target-class
approximation radius.  This is a benchmark condition, not a Gaussian-band
validity assumption.
\end{assumption}

\begin{assumption}[Finite-packing Holder witness]\label{ass:witness}
There is a sequence of DGPs with \(X\in[0,1]^d\), \(M_n\) disjoint cubes
\((B_{n,j})_{j\leq M_n}\) of side length \(\ell_n\), report functions
\[
h_j(x)=\Pr(X\in B_{n,j})^{-1/2}\one\{x\in B_{n,j}\},
\]
and Holder-smooth nuisance perturbations supported on the same cubes with
amplitudes \(\alpha_n\) and \(\gamma_n\).  These primitives imply
\(b_{n,j}=b_n=\kappa_0\alpha_n\gamma_n\Pr(X\in B_{n,j})^{1/2}\) for all
\(j\leq M_n\), with \(0<\kappa_0<\infty\), while preserving
Assumptions~\ref{ass:exactid}--\ref{ass:osl}.
\end{assumption}

\begin{assumption}[Gaussian approximation edge]\label{ass:gaussianedge}
The oracle centered score process over \(\calH_n^\circ\) has
\(G_n(P,\calH_n^\circ)\to0\), and the multiplier bootstrap consistently
estimates the oracle Gaussian quantile when the drift vector is removed.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: ExactID AIPW report identity]\label{thm:id}
Under Assumption~\ref{ass:exactid}, for every bounded report
\(h\in\calH_n\),
\[
\E_P[\psi_h(O;\eta_0)]=\theta_h(P).
\]
Moreover, the Gateaux derivative of
\(\eta\mapsto \E_P[\psi_h(O;\eta)]\) at \(\eta_0=(m_1,m_0,e)\) is zero in each
nuisance direction with finite \(L_2(P)\) norm.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This statement is not the novelty claim; it records the standard
\citet{ChernozhukovEtAl2018DML} AIPW orthogonality identity in the report
notation used by the proposal.  (b) It is worth including because it pins the
ExactID estimand consumed by \citet{SemenovaChernozhukov2021DMLCATE}; the new
question is whether the resulting report process has honest simultaneous
bands.

\begin{conjecture}[Conjecture 1: Gaussian-band gap counterfrontier (NOT YET PROVED)]\label{conj:gap-counterfrontier}
Under Assumptions~\ref{ass:exactid}--\ref{ass:gaussianedge}, the Gaussian-band
gap index \(\Lambda_n=\sqrt{2\log M_n}\,b_n/\sigma_n\) is the sharp
counterfrontier for converting orthogonal excess-risk control into
simultaneous HTE bands over the finite packing \(\calH_n^\circ\):
\begin{enumerate}[label=(\roman*)]
\item If \(\Lambda_n\to0\) and \(G_n(P,\calH_n^\circ)\to0\), the centered
first-order DML process and its multiplier bootstrap band have asymptotically
correct simultaneous coverage over \(\calH_n^\circ\).
\item If \(\liminf_n \Lambda_n>\lambda>0\), then there are DGPs and nuisance
learners satisfying Assumption~\ref{ass:osl} for which the nominal
\((1-\alpha)\) multiplier band undercovers by at least
\(\Phi(\lambda/2)-1/2-o(1)\) along a subsequence.
\end{enumerate}
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest comparator is \citet[\S3]{FosterSyrgkanis2023OSL}, which gives
second-order orthogonal excess-risk bounds under entropy restrictions but does
not claim a necessary and sufficient Gaussian-band frontier.  The
\(\varepsilon\)-gap is the entropy-amplified drift
\(\sqrt{2\log M_n}b_n/\sigma_n\): it can be \(O(1)\) while the second-order
excess-risk term in Assumption~\ref{ass:osl} still vanishes.  The second
comparator is \citet[\S3]{SemenovaChernozhukov2021DMLCATE}, whose simultaneous
inference theory supplies sufficient high-level conditions but not a lower
bound showing that orthogonal excess-risk control alone is insufficient.  (b)
Resolving this conjecture gives Semenova--Chernozhukov style CATE reports a
concrete diagnostic: report \(\Lambda_n\), or a conservative upper bound for it,
before using a simultaneous Gaussian band.

\begin{theorem}[Theorem 2: Max-shift coverage loss calculation]\label{thm:maxshift}
Assume Assumptions~\ref{ass:entropy} and \ref{ass:gaussianedge}.  If the
centered oracle process over \(\calH_n^\circ\) is approximated by independent
standard Gaussian coordinates \(G_1,\ldots,G_{M_n}\), and the feasible DML
process adds a common nonnegative mean shift \(b_n/\sigma_n\), then any
bootstrap band calibrated to the centered oracle quantile has coverage loss at
least \(\Phi(\Lambda_n/2)-1/2-o(1)\) when
\(\Lambda_n=\sqrt{2\log M_n}b_n/\sigma_n\) has a positive limit.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is a routine extreme-value calculation rather than the flagship
conjecture; its purpose is to make the obstruction in
Conjecture~\ref{conj:gap-counterfrontier} non-tautological.  The closest
published tools are \citet{ChernozhukovChetverikovKato2017HDCLT} and
\citet{ChernozhukovChetverikovKato2017EmpiricalBootstrap}, which justify
centered Gaussian approximations but do not analyze the nuisance-drift
counterexample.  (b) The consumer is again simultaneous CATE inference: the
calculation shows exactly why a small coordinatewise second-order bias can be
large at the band maximum.

\begin{conjecture}[Conjecture 2: Open-class Holder witness (NOT YET PROVED)]\label{conj:holder-witness}
The finite-packing construction in Assumption~\ref{ass:witness} can be promoted
to an open \(L_2(P)\)-neighborhood of Holder-smooth nuisance pairs and report
classes: for every sufficiently small perturbation preserving cube separation,
overlap, and variance lower bounds, Assumptions~\ref{ass:exactid}--\ref{ass:gaussianedge}
continue to hold and the lower-bound half of
Conjecture~\ref{conj:gap-counterfrontier} remains valid with constants reduced
by at most a fixed factor.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE} give smoothness
elbows for CATE rates, and \citet{ArmstrongKolesar2021FiniteSampleATE} give
finite-sample necessity logic for ATE inference, but neither paper supplies an
open-class lower bound for simultaneous HTE bands under orthogonal excess-risk
control.  The \(\varepsilon\)-gap is genericity: the obstruction is not a
single hand-tuned distribution but a neighborhood of Holder nuisance systems.
(b) This would unblock a clean negative result for Foster--Syrgkanis style
orthogonal learning: a user can satisfy their excess-risk benchmark on an open
class and still fail Semenova--Chernozhukov simultaneous bands.

\section{Sanity-check corollaries}
\begin{corollary}[No entropy amplification]\label{cor:no-entropy}
Under Assumptions~\ref{ass:exactid}--\ref{ass:gaussianedge}, if \(M_n\) is
bounded and \(b_n\to0\), then \(\Lambda_n\to0\), so
Conjecture~\ref{conj:gap-counterfrontier}(i) reduces to ordinary pointwise or
fixed-dimensional DML Gaussian inference.
\end{corollary}

\begin{corollary}[Oracle nuisance corner]\label{cor:oracle}
Under Assumptions~\ref{ass:exactid}, \ref{ass:entropy}, and
\ref{ass:gaussianedge}, if \(\widehat\eta=\eta_0\), then \(b_n=0\),
\(\Lambda_n=0\), and the proposal collapses to the centered high-dimensional
Gaussian approximation problem studied by
\citet{ChernozhukovChetverikovKato2017HDCLT}.
\end{corollary}

\begin{example}[Concrete non-corner witness]\label{ex:concrete-witness}
Take \(X\sim\operatorname{Unif}([0,1]^d)\), let \(B_{n,j}\) be \(M_n\) disjoint
cubes of side length \(\ell_n\), set \(e_0(x)=1/2\), and let the nuisance
learners have independent cross-fit perturbations
\(\widehat m_1-m_1=\alpha_n\sum_j q_j(x)\) and
\(\widehat e-e_0=\gamma_n\sum_j q_j(x)\), where each \(q_j\) is a smooth bump
supported in \(B_{n,j}\).  Choosing
\(\alpha_n\gamma_n\ell_n^{d/2}\sqrt{2\log M_n}\to\lambda>0\) gives
\(\Lambda_n\to\lambda/\sigma\) while the coordinatewise drift is \(o(1)\);
this is the explicit witness Conjecture~\ref{conj:holder-witness} must verify,
not a Gaussian or oracle corner.
\end{example}

\section{Proof-sketch route}
Theorem~\ref{thm:id} follows by conditioning on \(X\), substituting
consistency and unconfoundedness, and differentiating the AIPW expectation in
the \(m_1\), \(m_0\), and \(e\) directions.  Theorem~\ref{thm:maxshift} reduces
to the extreme-value expansion for \(\max_{j\leq M_n}G_j\): a common mean shift
of size \(b_n/\sigma_n\) moves the maximum by the product
\(\sqrt{2\log M_n}b_n/\sigma_n\), and Gaussian anti-concentration converts that
movement into coverage loss.  Conjecture~\ref{conj:gap-counterfrontier} then
requires two non-routine mathematical steps: construct cross-fitted nuisance
learners on the bump class whose orthogonal excess-risk bound remains
second-order while their AIPW report drift equals the displayed \(b_n\), and
couple the drifted report process to the centered Gaussian maximum uniformly
over the open Holder neighborhood.  Conjecture~\ref{conj:holder-witness} should
be attacked by explicit bump algebra, small-cube packing estimates, and
stability of Holder norms, overlap, and covariance eigenvalues under small
\(L_2\) perturbations.

\section{Honest scope flags}
The exact-identification identity and max-shift calculation are labelled
Theorem because they are standard conditioning and Gaussian-maximum algebra.
The counterfrontier and open-class witness are Conjectures: the difficult
construction of nuisance learners satisfying orthogonal excess-risk control
while producing aligned report drift is not proved here.  This pivot
intentionally withdraws the previously rejected two-channel ``necessary and
sufficient DML frontier'' framing; the new proposal is a narrower
non-implication / counterfrontier against the excess-risk-to-band inference
shortcut.  The uncertain technical point is whether the open-neighborhood
promotion in Conjecture~\ref{conj:holder-witness} can preserve the common-drift
geometry without imposing an artificial alignment condition that would weaken
the novelty claim.

\section{Iteration trail}
\begin{itemize}
\item v1 (pivot) -- initial draft for angle 3 after exhausting the prior DML
frontier, higher-order CATE elbow, and LRO/ADML report-equivalence angles;
prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Armstrong and Kolesar(2021)]{ArmstrongKolesar2021FiniteSampleATE}
Armstrong, T. B. and M. Kolesar (2021).
\newblock Finite-sample optimal estimation and inference on average treatment effects under unconfoundedness.
\newblock \emph{Econometrica} 89(3), 1141--1177.

\bibitem[Chernozhukov, Chetverikov, and Kato(2017)]{ChernozhukovChetverikovKato2017HDCLT}
Chernozhukov, V., D. Chetverikov, and K. Kato (2017).
\newblock Central limit theorems and bootstrap in high dimensions.
\newblock \emph{Annals of Probability} 45(4), 2309--2352.

\bibitem[Chernozhukov, Chetverikov, and Kato(2017)]{ChernozhukovChetverikovKato2017EmpiricalBootstrap}
Chernozhukov, V., D. Chetverikov, and K. Kato (2017).
\newblock Empirical and multiplier bootstraps for suprema of empirical processes of increasing complexity, and related Gaussian couplings.
\newblock \emph{Stochastic Processes and their Applications} 126(12), 3632--3651.

\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., D. Chetverikov, M. Demirer, E. Duflo, C. Hansen, W. Newey, and J. Robins (2018).
\newblock Double/debiased machine learning for treatment and structural parameters.
\newblock \emph{The Econometrics Journal} 21(1), C1--C68.

\bibitem[Chernozhukov, Newey, and Singh(2022)]{ChernozhukovNeweySingh2022Riesz}
Chernozhukov, V., W. K. Newey, and R. Singh (2022).
\newblock Debiased machine learning of global and local parameters using regularized Riesz representers.
\newblock \emph{The Econometrics Journal} 25(3), 576--601.

\bibitem[Foster and Syrgkanis(2023)]{FosterSyrgkanis2023OSL}
Foster, D. J. and V. Syrgkanis (2023).
\newblock Orthogonal statistical learning.
\newblock \emph{Annals of Statistics} 51(3), 879--908.

\bibitem[Kennedy et~al.(2024)]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
Kennedy, E. H., S. Balakrishnan, J. M. Robins, and L. Wasserman (2024).
\newblock Minimax rates for heterogeneous causal effect estimation.
\newblock \emph{Annals of Statistics} 52(2), 793--817.

\bibitem[Semenova and Chernozhukov(2021)]{SemenovaChernozhukov2021DMLCATE}
Semenova, V. and V. Chernozhukov (2021).
\newblock Debiased machine learning of conditional average treatment effects and other causal functions.
\newblock \emph{The Econometrics Journal} 24(2), 264--289.
\end{thebibliography}

\end{document}
