% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_dml\_orthogonality\_frontier, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section originally contained a stage-1 placeholder. Replace each
%    placeholder with the content described in
%    `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_dml\_orthogonality\_frontier} / \texttt{v1}%
  \\ \large\textit{Riesz-localization critical radius for shrinking HTE DML reports}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form ExactID proposal.  The locked tuple is
\[
(\texttt{qid},\texttt{specialization},\text{graph/SWIG},\text{treatment},
\text{target estimand},\text{identifying assumptions}).
\]
Here \(\texttt{qid}=\texttt{eid\_dml\_orthogonality\_frontier}\) and
\(\texttt{specialization}=\texttt{v1}\).  The graph/SWIG has observed
\((X,D,Y)\), binary treatment \(D\in\{0,1\}\), potential outcomes
\((Y(1),Y(0))\), and observed outcome \(Y=DY(1)+(1-D)Y(0)\).  The treatment is
the binary intervention \(D\leftarrow d\).  Write \(X=(Z,W)\), where \(Z\in
\R^{d_z}\) is the localization coordinate and \(W\) contains the remaining
covariates.  For a center \(z_0\), bandwidth \(r_n>0\), kernel \(K\), and
report modifier \(h\in\calH_n\), the target estimand is the shrinking local
HTE report
\[
\theta_{r_n,h}(P)=
\frac{\E_P[K((Z-z_0)/r_n)h(W)\tau_0(X)]}
{\E_P[K((Z-z_0)/r_n)h(W)]},\qquad
\tau_0(x)=\E_P[Y(1)-Y(0)\mid X=x].
\]
The identifying assumptions are consistency, conditional unconfoundedness
\((Y(1),Y(0))\perp D\mid X\), overlap
\(\varepsilon\le e_0(X)\le 1-\varepsilon\), and finite fourth moments.  The
proposed estimator is the cross-fitted first-order AIPW/DML report process
based on nuisances \(\eta=(m_1,m_0,e)\), where
\(m_d(x)=\E[Y\mid D=d,X=x]\) and \(e(x)=\Pr(D=1\mid X=x)\).

\begin{abstract}
Debiased ML with learned Riesz representers handles many global and local
linear functionals, but the literature has not isolated a sharp primitive
transition from root-\(n\) regularity to slower local Gaussian inference and
then to nonregularity for shrinking HTE reports.  This proposal introduces the
\emph{Riesz-localization critical radius}
\(\mathfrak C_n(P)=\max\{A_n/\sqrt n,\sqrt n\,\Delta_{m,n}\Delta_{e,n}/A_n,
J_nA_n/\sqrt n\}\), where \(A_n\) is the local AIPW Riesz norm, the
\(\Delta\)'s are local nuisance radii, and \(J_n\) is the report-class entropy
integral.  The Stage~0.5 rewind is handled by splitting the kernel: a
conditional theorem records what follows if the upper empirical-process and
lower minimax channels are assumed active, while the flagship Conjecture asks
for primitive Holder/entropy arguments that prove those channels instead of
assuming them.  If resolved, the conjecture would classify when local HTE DML
is root-\(n\), when it is only slower-rate Gaussian, and when first-order
orthogonality is insufficient.  A resolution would give users of AutoDML and
local CATE reports a concrete diagnostic for when shrinking subgroup inference
is a regular DML problem and when it is not.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Empirical HTE papers routinely move from global ATE or CATE summaries to local
subgroups: treatment effects for a neighborhood of an age, income, risk score,
geography, or learned policy margin.  In these problems the Riesz representer
for the target grows as the subgroup mass shrinks.  Orthogonality still removes
first-order nuisance bias, but it does not by itself say whether the localized
parameter is root-\(n\) regular, slower-rate Gaussian, or nonregular.

\paragraph{The main finding (proposed).}
The proposed headline is Conjecture~\ref{conj:primitive-critical-radius}: over
Holder nuisance classes with entropy-indexed report modifiers, primitive
maximal-inequality and local-minimax arguments should make the named scalar
\(\mathfrak C_n(P)\) the sharp uniform frontier for first-order DML inference
on shrinking local HTE reports.  Theorem~\ref{thm:conditional-frontier} is
kept as a conditional split theorem only: it records the deterministic
classification if the frontier-active empirical-process and lower-bound
channels are granted as assumptions.  The novelty claim is not that
Theorem~\ref{thm:conditional-frontier} is hard; it is that
Conjecture~\ref{conj:primitive-critical-radius} should replace those
high-level frontier assumptions with primitive Holder smoothness, metric
entropy, overlap, and tangent-cone calculations.

\paragraph{What is new.}
The new focal object is the Riesz-localization critical radius
\[
\mathfrak C_n(P)=
\max\left\{\frac{A_n(P)}{\sqrt n},
\frac{\sqrt n\,\Delta_{m,n}(P)\Delta_{e,n}(P)}{A_n(P)},
\frac{J_nA_n(P)}{\sqrt n}\right\}.
\]
It is not defined as the value at which inference succeeds.  Its three terms
come from independent primitives: effective local sample size, orthogonal
second-order nuisance drift after local standardization, and entropy of the
localized report process.  The closest published comparators are
\citet[Section~2]{ChernozhukovNeweySingh2022Riesz}, which defines global,
local, and perfectly localized linear functionals and orthogonal
representations, and \citet[Sections~2--3]{ChernozhukovNeweySingh2022AutoDML},
which gives the AutoDML Riesz-normal-equation route to bias correction.  The
epsilon-gap is that those papers give regularized Riesz inference conditions,
not a primitive necessary-and-sufficient frontier in which each channel of
\(\mathfrak C_n\) is also shown necessary by an open Holder witness class.
The Holder witness also connects to
\citet[Theorem~1, Section~3.3, and Theorem~2]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
and \citet[abstract and Sections~2--3]{ArmstrongKolesar2021FiniteSampleATE}:
their smoothness and necessity messages motivate, but do not deliver, the
local bandwidth exponent frontier or the growing-report-class entropy channel in
Conjecture~\ref{conj:holder-exponent}.

\paragraph{How it positions in the literature.}
This is an ExactID / causal-ML proposal.  Identification is the standard
unconfoundedness AIPW identity for a weighted CATE functional.  The research
frontier is semiparametric inference with learned nuisance functions and Riesz
representers: \citet{ChernozhukovEtAl2018DML} gives first-order orthogonal DML
conditions, \citet{ChernozhukovNeweySingh2022AutoDML} automates the Riesz
correction, \citet{ChernozhukovNeweySingh2022Riesz} treats local functionals
whose Riesz norms can diverge, \citet{SemenovaChernozhukov2021DMLCATE}
motivates simultaneous HTE reports, and
\citet{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE} shows that CATE
smoothness elbows can force nonstandard rates.  The proposal narrows the
frontier to a first-order DML question where the localization-induced Riesz
norm is the central mathematical object.

\paragraph{Implications for the community.}
The concrete downstream consumer is AutoDML analysis of local linear
functionals in \citet{ChernozhukovNeweySingh2022AutoDML}: a resolved
primitive frontier would tell analysts when their learned Riesz correction
licenses root-\(n\) inference, when it only licenses slower local Gaussian
inference, and when a higher-order or minimax-local method is required.

\paragraph{How research benefits from the conclusion.}
Researchers should report the Riesz norm and \(\mathfrak C_n\) channels for
shrinking subgroup HTE analysis rather than treating all orthogonal local
reports as ordinary root-\(n\) DML targets.

\section{Related work}
\citet{ChernozhukovEtAl2018DML} is the baseline DML reference: it introduces
orthogonal scores and cross-fitting and gives sufficient product-rate
conditions for asymptotically linear treatment-effect estimators.  The present
proposal keeps the same first-order orthogonal logic but asks where localized
Riesz norms destroy ordinary root-\(n\) inference.

\citet{SemenovaChernozhukov2021DMLCATE} gives DML estimation and simultaneous
inference for CATE summaries such as best linear predictors and group average
effects.  This proposal targets a different object, shrinking local reports,
where subgroup mass is allowed to vanish and the Riesz norm can diverge.

\citet[Sections~2--3]{ChernozhukovNeweySingh2022AutoDML} develops automatic
debiasing through learned Riesz representers and supplies primitive inference
conditions for causal and structural effects.  The proposed gap is a sharp
primitive transition theorem for the local Riesz norm rather than another
sufficient AutoDML condition.

\citet[Section~2]{ChernozhukovNeweySingh2022Riesz} studies debiased ML for
global, local, and perfectly localized linear functionals using regularized
Riesz representers, including nonregular local objects.  This is the closest
comparator: it motivates diverging Riesz norms but does not isolate the
three-channel critical radius \(\mathfrak C_n\) for shrinking HTE DML, nor a
matching lower-bound witness for each failure channel.

\citet[Theorem~1 and Section~3.3]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
derives the CATE minimax lower-bound rate and explains the nuisance-smoothness
elbow where the oracle nonparametric regression rate becomes unattainable;
\citet[Theorem~2 and Section~4.1]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
then gives a local-polynomial R-learner upper bound matching that rate.  It is
relevant because it proves a Holder elbow for pointwise CATE estimation, but
it does not characterize shrinking-neighborhood Riesz norms, first-order DML
Gaussian reports, or a growing report-class entropy obstruction.

\citet[abstract and Sections~2--3]{ArmstrongKolesar2021FiniteSampleATE} shows
that honest treatment-effect inference can depend sharply on smoothness,
shape, and overlap restrictions, including cases where ordinary
\(\sqrt n\)-inference is not available.  That necessity perspective motivates
the lower-bound side of the proposed frontier; the present proposal is informed
by it rather than claiming to extend its finite-sample optimality theorem.

\citet{FosterSyrgkanis2023OSL} proves orthogonal statistical learning
excess-risk guarantees under entropy conditions.  It supplies the entropy
language for \(J_n\), while this proposal asks for Gaussian inference rather
than prediction-risk control.

\citet{KallusMaoUehara2024LDML} develops localized debiased machine learning
for low-dimensional parameters such as local quantile treatment effects whose
nuisances depend on the target value.  It is adjacent in terminology, but the
present proposal concerns shrinking covariate-neighborhood HTE reports and a
Riesz-norm regular-to-nonregular frontier.

The in-repo prior-art slice is thin for this topic.  The Stage -1.1 prior
proposal map reports no accepted CausalSmith theorem for Holder-smoothness or
metric-entropy DML nuisance frontiers.  The closest banked artifact is the
failed \texttt{eid\_dml\_orth\_uniform/v2} proposal, whose reviewer asked for
explicit DML/LRO/ADML report summands and primitive frontier arguments; this
proposal deliberately pivots away from studentization reports to a narrower
local Riesz-norm trichotomy.  \texttt{doc/API.md} records active Panel and
PartialID catalogue entries, but no accepted ExactID proposal duplicating a
Riesz-localization critical radius for HTE DML.

\section{Formal setup}
Let \(O=(Y,D,X)\), \(X=(Z,W)\), \(D\in\{0,1\}\), and let
\((Y(1),Y(0))\) be potential outcomes.  The CATE is
\(\tau_0(x)=m_1(x)-m_0(x)\), with \(m_d(x)=\E[Y\mid D=d,X=x]\), and the
propensity score is \(e_0(x)=\Pr(D=1\mid X=x)\).  For a bounded nonnegative
kernel \(K\) supported on the unit ball and a bandwidth \(r_n\), write
\[
q_{r_n,h}(x)=K((z-z_0)/r_n)h(w),\qquad
\mu_{r_n,h}(P)=\E_P[q_{r_n,h}(X)].
\]
The target is
\[
\theta_{r_n,h}(P)=\E_P[q_{r_n,h}(X)\tau_0(X)]/\mu_{r_n,h}(P).
\]
The AIPW score is
\[
\psi_{r_n,h}(O;\eta,\theta)=
\frac{q_{r_n,h}(X)}{\mu_{r_n,h}}
\left[
m_1(X)-m_0(X)
+\,
\frac{D(Y-m_1(X))}{e(X)}
-\frac{(1-D)(Y-m_0(X))}{1-e(X)}
-\theta
\right].
\]
The local AIPW Riesz representer for the weighted CATE functional is
\[
\alpha_{r_n,h}(O;P)=
\frac{q_{r_n,h}(X)}{\mu_{r_n,h}(P)}
\left(\frac{D}{e_0(X)}-\frac{1-D}{1-e_0(X)}\right),
\]
and the Riesz norm envelope is
\[
A_n(P)=\sup_{h\in\calH_n}\|\alpha_{r_n,h}(\cdot;P)\|_{L_2(P)}.
\]
Equivalently,
\[
\|\alpha_{r_n,h}\|_2^2=
\E_P\left[
\frac{q_{r_n,h}(X)^2}{\mu_{r_n,h}(P)^2}
\left\{\frac{1}{e_0(X)}+\frac{1}{1-e_0(X)}\right\}
\right].
\]
Let \(J_n\) denote a fixed entropy integral for the standardized report class
\(\{\alpha_{r_n,h}/\|\alpha_{r_n,h}\|_2:h\in\calH_n\}\), and let
\(\Delta_{m,n}(P)\), \(\Delta_{e,n}(P)\) be local \(L_2(P)\) nuisance error
radii for cross-fitted estimates of \(m=(m_1,m_0)\) and \(e\).  The focal
critical radius is
\[
\mathfrak C_n(P)=
\max\left\{
\frac{A_n(P)}{\sqrt n},\,
\frac{\sqrt n\,\Delta_{m,n}(P)\Delta_{e,n}(P)}{A_n(P)},\,
\frac{J_nA_n(P)}{\sqrt n}
\right\}.
\]
For the Holder witness, let \(d_x=\dim(X)\) and define the local-polynomial
nuisance exponent
\[
\beta_H(s_m,s_e,d_x)=\frac{s_m}{2s_m+d_x}+\frac{s_e}{2s_e+d_x},
\]
the product exponent delivered by standard local nonparametric regression
rates when both nuisance functions are learned on the local effective sample.

\begin{quote}
\begin{verbatim}
Locked parameters:
qid = eid_dml_orthogonality_frontier
specialization = v1
graph/SWIG = observed (X,D,Y), potential outcomes (Y(1),Y(0)),
  Y = D Y(1) + (1-D)Y(0), X=(Z,W)
treatment = binary intervention D <- d
target estimand = theta_{r_n,h}(P) for shrinking local HTE reports
identifying assumptions = consistency, conditional unconfoundedness,
  overlap, finite fourth moments, and local Holder/entropy regularity
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[ExactID causal model]\label{ass:exactid}
Consistency holds, \((Y(1),Y(0))\perp D\mid X\), and
\(\varepsilon\le e_0(X)\le 1-\varepsilon\) almost surely for some fixed
\(\varepsilon>0\).  The fourth moments of \(Y(d)\) are uniformly bounded over
the DGP class.
\end{assumption}

\begin{assumption}[Local Holder geometry]\label{ass:holder}
The density of \(Z\) given \(W\) is bounded above and below in a neighborhood
of \(z_0\), and \(m_0,m_1,e_0\) belong to Holder balls with smoothness
\((s_m,s_e)\) and radii bounded by constants independent of \(n\).  The kernel
\(K\) is bounded, compactly supported, and has positive integral.
\end{assumption}

\begin{assumption}[Report entropy]\label{ass:entropy}
The modifier class \(\calH_n\) is uniformly bounded, nonnegative, and has
standardized entropy integral \(J_n<\infty\) for the local Riesz class
\(\{\alpha_{r_n,h}/\|\alpha_{r_n,h}\|_2:h\in\calH_n\}\).  The denominator
\(\mu_{r_n,h}(P)\) is positive for every \(h\in\calH_n\).  There are constants
\(0<c_h<C_h<\infty\) such that, uniformly in \(h\) and \(P\),
\[
c_h\mu_{r_n,h}(P)\le \E_P[q_{r_n,h}(X)^2]\le C_h\mu_{r_n,h}(P).
\]
This comparability condition is the report-modifier regularity needed to turn
the exact \(L_2\) Riesz identity into the simpler local-mass envelope.
\end{assumption}

\begin{assumption}[Cross-fitted nuisance radii]\label{ass:nuisance}
Cross-fitted nuisance estimates satisfy local \(L_2(P)\) bounds
\(\|\widehat m-m_0\|_{r_n}\le \Delta_{m,n}(P)\) and
\(\|\widehat e-e_0\|_{r_n}\le \Delta_{e,n}(P)\) with probability tending to
one, where the local norm is weighted by \(q_{r_n,h}/\mu_{r_n,h}\) uniformly
over \(h\in\calH_n\).  The product
\(\Delta_{m,n}(P)\Delta_{e,n}(P)\) is bounded above by the named structural
quantity \(A_n(P)^2/\sqrt n\), so the second channel of \(\mathfrak C_n\) is
not a free epsilon parameter.
\end{assumption}

\begin{assumption}[Holder-rate nuisance learners]\label{ass:holder-learners}
For the bandwidth witness, the nuisance learners are local-polynomial or
series estimators over the local effective sample \(nr_n^{d_z}\) and satisfy
\[
\Delta_{m,n}\Delta_{e,n}\asymp
(nr_n^{d_z})^{-\beta_H(s_m,s_e,d_x)}
\]
with \(\beta_H(s_m,s_e,d_x)\) defined in Section~6.
\end{assumption}

\begin{assumption}[Open witness class]\label{ass:witness}
The DGP class contains an open Holder neighborhood of the concrete witness in
Section~\ref{sec:witness}: \(Z\) has a density bounded away from zero near
\(z_0\), \(e_0\in[\varepsilon,1-\varepsilon]\), the conditional outcome
variance is positive, and local perturbations of \(m\) and \(e\) can attain
the nuisance product direction at the order
\(\Delta_{m,n}(P)\Delta_{e,n}(P)\).
\end{assumption}

\begin{assumption}[Frontier-active conditional split]\label{ass:frontier-active}
There exist cross-fitted nuisance estimators and a tangent-cone collection
such that the following three high-level channels are active at the scale
\(\mathfrak C_n(P)\): (i) the localized empirical-process remainder of the
AIPW score is bounded above by \(J_nA_n(P)/\sqrt n\) up to logarithmic
factors, (ii) the oracle Gaussian and multiplier approximations hold whenever
\(\mathfrak C_n(P)\to0\), and (iii) for each nonvanishing term of
\(\mathfrak C_n(P)\), there are local alternatives in the witness class with
constants \(c_R,c_{\mathrm{ep}}>0\) that realize the corresponding lower-bound
failure.  This assumption is used only in
Theorem~\ref{thm:conditional-frontier}; the flagship conjecture is precisely
to replace it with primitive Holder/entropy/minimax arguments.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: exact local AIPW representation and Riesz norm identity]\label{thm:id}
Under Assumption~\ref{ass:exactid}, for every \(r_n\) and
\(h\in\calH_n\) with \(\mu_{r_n,h}(P)>0\), the local HTE report
\(\theta_{r_n,h}(P)\) is identified by the AIPW moment
\(\E_P[\psi_{r_n,h}(O;\eta_0,\theta_{r_n,h})]=0\).  Its first-order
representer is \(\alpha_{r_n,h}\), with exact norm
\[
\|\alpha_{r_n,h}\|_2^2=
\E_P\left[
\frac{q_{r_n,h}(X)^2}{\mu_{r_n,h}(P)^2}
\left\{\frac{1}{e_0(X)}+\frac{1}{1-e_0(X)}\right\}
\right].
\]
Under Assumptions~\ref{ass:holder} and \ref{ass:entropy}, the report-modifier
comparability condition implies the envelope simplification
\[
A_n(P)^2\asymp
\sup_{h\in\calH_n}\mu_{r_n,h}(P)^{-1}.
\]
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is not the novelty claim; it is the ExactID bookkeeping
needed to keep the proposal anchored in the standard AIPW functional of
\citet{ChernozhukovEtAl2018DML}.  The only local addition is the explicit
Riesz norm envelope \(A_n\) for shrinking weighted reports, with the
comparability condition made explicit rather than hidden.  (b) The consumer
is Conjecture~\ref{conj:primitive-critical-radius}: without this
representation, the critical-radius channels would not be tied to a causal
estimand.

\begin{theorem}[Theorem 2: conditional frontier under active channels]\label{thm:conditional-frontier}
Under Assumptions~\ref{ass:exactid}--\ref{ass:frontier-active}, the following
conditional trichotomy holds for the cross-fitted first-order DML process
indexed by \(h\in\calH_n\).
\begin{enumerate}[label=(\roman*)]
\item If \(A_n(P)\) is bounded and \(\mathfrak C_n(P)\to0\), then the reports
are uniformly root-\(n\) regular and admit centered Gaussian and multiplier
bootstrap approximation at the usual \(\sqrt n\) scale.
\item If \(A_n(P)\to\infty\), \(A_n(P)/\sqrt n\to0\), and
\(\mathfrak C_n(P)\to0\), then the reports are not root-\(n\) regular but are
uniformly Gaussian after local standardization at rate \(\sqrt n/A_n(P)\).
\item If any term in \(\mathfrak C_n(P)\) has a positive limsup, then no
centered first-order DML Gaussian approximation is uniformly valid over the
open witness class: the failure is respectively local-sample nonregularity,
second-order nuisance drift, or report-entropy leakage.
\end{enumerate}
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is deliberately conditional and is not the flagship novelty
claim.  It is included to obey the Stage~0.5 split directive: the high-level
frontier-active content is quarantined in Assumption~\ref{ass:frontier-active}
rather than advertised as a proved primitive theorem.  (b) The consumer is the
AutoDML local-functional analysis of
\citet{ChernozhukovNeweySingh2022AutoDML}: it can use the conditional
classification as a diagnostic while keeping the primitive empirical-process
and lower-bound steps visibly open in
Conjecture~\ref{conj:primitive-critical-radius}.

\begin{conjecture}[Conjecture 1: primitive Riesz-localization frontier (NOT YET PROVED)]\label{conj:primitive-critical-radius}
Under Assumptions~\ref{ass:exactid}, \ref{ass:holder}, \ref{ass:entropy},
\ref{ass:nuisance}, and \ref{ass:witness}, but without
Assumption~\ref{ass:frontier-active}, primitive Holder smoothness, overlap,
metric-entropy, and local tangent-cone arguments imply the same trichotomy as
Theorem~\ref{thm:conditional-frontier}.  Equivalently, the three independent
terms of \(\mathfrak C_n(P)\) are both sufficient and necessary for uniform
centered Gaussian first-order DML inference for shrinking local HTE reports:
local-sample size controls the oracle term, the standardized product
\(\sqrt n\,\Delta_{m,n}\Delta_{e,n}/A_n\) controls orthogonal drift, and
\(J_nA_n/\sqrt n\) controls report-process approximation.  This is a strict
extension of the local-functional Riesz condition in
\citet[Section~2]{ChernozhukovNeweySingh2022Riesz}: instead of taking a
diverging local Riesz norm as a sufficient-rate input, it asserts an iff
frontier in which \(A_n/\sqrt n\), the localized DML product remainder, and
the report entropy integral are each necessary on an open Holder witness
class.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest comparator is
\citet[Section~2]{ChernozhukovNeweySingh2022Riesz}, whose local and perfectly
localized functionals expose slower-than-\(n^{-1/2}\) rates through diverging
Riesz norms, and
\citet[Sections~2--3]{ChernozhukovNeweySingh2022AutoDML}, whose Riesz normal
equations deliver debiasing under sufficient conditions.  The epsilon-gap is
the primitive necessity frontier: those papers do not prove that each channel
of the independently defined \(\mathfrak C_n\) is a necessary obstruction over
an open Holder witness class for shrinking HTE reports, including the
non-corner report-packing witness of Example~\ref{ex:report-packing}.  (b)
Resolving this directly benefits AutoDML local-functional practice in
\citet{ChernozhukovNeweySingh2022AutoDML}, because it turns a diverging learned
Riesz norm from a caveat into a diagnostic regime classifier.

\begin{conjecture}[Conjecture 2: Holder bandwidth exponent witness (NOT YET PROVED)]\label{conj:holder-exponent}
Under Assumptions~\ref{ass:exactid}, \ref{ass:holder}, \ref{ass:entropy},
\ref{ass:nuisance}, \ref{ass:holder-learners}, and \ref{ass:witness},
specialize to the concrete witness class of Example~\ref{ex:witness} with
\(r_n=n^{-a}\), \(Z\in\R^{d_z}\), and bounded report entropy \(J_n=O(1)\), so
that
\[
\Delta_{m,n}\Delta_{e,n}
\asymp (nr_n^{d_z})^{-\beta_H(s_m,s_e,d_x)}.
\]
Then \(A_n(P)\asymp r_n^{-d_z/2}\), and first-order local HTE DML is uniformly
locally Gaussian if and only if
\[
0<a d_z<1
\quad\text{and}\quad
\beta_H(s_m,s_e,d_x)>1/2.
\]
If \(a d_z=0\) the regime collapses to root-\(n\) DML, if
\(0<a d_z<1\) it is slower Gaussian at rate \(n^{(1-a d_z)/2}\), and if
\(a d_z\ge1\) it is nonregular for first-order DML.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Theorem~1, Section~3.3, and Theorem~2]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
gives the lower-bound and matching upper-bound Holder CATE elbow, and
\citet[abstract and Sections~2--3]{ArmstrongKolesar2021FiniteSampleATE}
emphasizes smoothness and overlap necessity, but neither converts a shrinking
local Riesz norm into this DML bandwidth exponent trichotomy.  The gap is the
explicit boundary \(a d_z=1\) paired with the first-order orthogonal product
smoothness condition \(\beta_H(s_m,s_e,d_x)>1/2\), rather than a free
rate exponent.  (b) The concrete consumer is local subgroup CATE reporting in
\citet{SemenovaChernozhukov2021DMLCATE}: it would specify when a shrinking
group average can be accompanied by Gaussian bands and when it should be
reported as nonregular.

\section{Sanity-check corollaries}
\label{sec:witness}
\begin{corollary}[Fixed subgroup reduction]\label{cor:fixed}
Under Assumptions~\ref{ass:exactid}--\ref{ass:nuisance}, if \(r_n\equiv r_0>0\)
and \(\inf_h\mu_{r_0,h}(P)>0\), then \(A_n(P)=O(1)\) and
Conjecture~\ref{conj:primitive-critical-radius} reduces to the usual
first-order DML product-rate requirement
\(\sqrt n\,\Delta_{m,n}\Delta_{e,n}\to0\), plus the standard report-entropy
condition \(J_n/\sqrt n\to0\).  Under
Assumption~\ref{ass:frontier-active}, Theorem~\ref{thm:conditional-frontier}
has the same fixed-subgroup reduction by direct substitution into
\(\mathfrak C_n\).
\end{corollary}

\begin{example}[Concrete non-corner witness]\label{ex:witness}
Let \(Z\sim\mathrm{Unif}([0,1]^{d_z})\), \(W=(U,V)\) with
\(U,V\sim\mathrm{Unif}([0,1])\) independent of \(Z\), \(e_0(X)=1/2\),
\(Y(d)=d\,\tau_0(Z,W)+\varepsilon\), \(\varepsilon\sim N(0,1)\), and
\(\tau_0(z,u,v)=1+z_1+u+v\).  Take \(z_0\) in the
interior, \(K(u)=\one\{\|u\|\le1\}\), \(h\equiv1\), and \(r_n=n^{-a}\).  Then
\(\mu_{r_n,1}(P)\asymp r_n^{d_z}\), \(A_n(P)\asymp r_n^{-d_z/2}\), and the
proof route for Conjecture~\ref{conj:holder-exponent} reduces to checking the
three terms in \(\mathfrak C_n\) explicitly.  This is not the fixed-\(r\)
corner and is stable under small Holder perturbations of \(e_0,m_0,m_1\).
\end{example}

\begin{example}[Concrete report-packing entropy witness]\label{ex:report-packing}
Keep the distributional primitives of Example~\ref{ex:witness}, set
\(r_n=n^{-a}\) with \(0<a d_z<1\), and write \(W=(U,V)\) where
\(U,V\sim\mathrm{Unif}([0,1])\) are independent of \(Z\).  Fix
\(0<\rho<1/4\) and \(0<\zeta<(1-a d_z)/2\).  For
\(M_n=\lceil\exp(n^{2\zeta})\rceil\), let
\[
h_j(U,V)=1+\rho\,\mathrm{sign}\{\sin(2^j\pi U)\},\qquad
j=1,\ldots,M_n,
\]
and \(\calH_n=\{h_1,\ldots,h_{M_n}\}\).  The modifiers are bounded between
\(1-\rho\) and \(1+\rho\), so
\(\mu_{r_n,h_j}(P)\asymp r_n^{d_z}\) and
\(A_n(P)\asymp r_n^{-d_z/2}\) uniformly in \(j\).  The standardized Riesz
class contains \(M_n\) pairwise separated localized reports, giving the
finite-class entropy integral \(J_n\asymp\sqrt{\log M_n}\asymp n^\zeta\).
Therefore
\[
\frac{J_nA_n(P)}{\sqrt n}\asymp n^{\zeta-(1-a d_z)/2}.
\]
This witness is non-corner: \(r_n\to0\), the report class grows, and the
entropy channel can be made critical by taking
\(\zeta\uparrow(1-a d_z)/2\), while the same construction remains inside the
open Holder causal model because the oscillation is only in the report
modifier, not in \(m_0,m_1,e_0\).
\end{example}

\section{Proof-sketch route}
Theorem~\ref{thm:id} follows by the standard AIPW identity under
unconfoundedness and by computing the \(L_2(P)\) norm of the localized Riesz
representer; the simplification \(A_n^2\asymp\sup_h\mu_{r_n,h}^{-1}\) uses
the explicit \(L_2/L_1\) report-modifier comparability in
Assumption~\ref{ass:entropy}.  Theorem~\ref{thm:conditional-frontier} is the
formal theorem-split: expand the three clauses of
Assumption~\ref{ass:frontier-active} and map each to the corresponding term of
\(\mathfrak C_n\).  The sufficiency side of
Conjecture~\ref{conj:primitive-critical-radius} should replace that assumption
with cross-fitting, a second-order von Mises expansion, maximal inequalities
for the standardized localized report class, and high-dimensional Gaussian
approximation for the resulting empirical process.  The necessity side should
build three separate local alternatives inside Assumption~\ref{ass:witness}:
one with \(n/A_n^2\) bounded, one with a nuisance product perturbation
producing standardized drift \(\sqrt n\,\Delta_m\Delta_e/A_n\), and one with a
report packing like Example~\ref{ex:report-packing}, where
\(\log|\calH_n|\asymp n^{2\zeta}\) and
\(J_nA_n/\sqrt n\asymp n^{\zeta-(1-a d_z)/2}\), whose entropy term prevents a
uniform multiplier approximation at the boundary.
Conjecture~\ref{conj:holder-exponent} then becomes an exponent calculation
using \(\mu_{r_n}\asymp r_n^{d_z}\), \(A_n\asymp r_n^{-d_z/2}\), and the
Holder local-polynomial product exponent \(\beta_H(s_m,s_e,d_x)\).
Boundary cases needing explicit algebra are \(a d_z=1\), vanishing conditional
variance, kernels with boundary bias, and report classes whose entropy grows
at the same order as \(n/A_n^2\).

\section{Honest scope flags}
Theorem~\ref{thm:id} is a routine identification and norm calculation, now
stated with the exact \(L_2\) expression needed for well-posedness.
Theorem~\ref{thm:conditional-frontier} is only a conditional theorem under
Assumption~\ref{ass:frontier-active}; it is not the flagship novelty claim.
Conjectures~\ref{conj:primitive-critical-radius} and
\ref{conj:holder-exponent} are not proved.  The main open work is replacing
Assumption~\ref{ass:frontier-active} with a primitive lower-bound construction
for the three failure channels and an empirical-process upper bound for
localized report classes; Example~\ref{ex:report-packing} is a concrete target
for the entropy-channel part of that construction, not a completed proof.  The
proposal does not claim that
\citet{ChernozhukovNeweySingh2022Riesz} or
\citet{ChernozhukovNeweySingh2022AutoDML} are wrong; it claims that their
local Riesz discussion leaves a sharper regime classifier open.  The exact
form of \(J_nA_n/\sqrt n\) may need a logarithmic or anti-concentration factor
after a full Gaussian-approximation proof, but the focal object should remain
an independently defined entropy-localization channel.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 4, replacing the rejected
orthogonal excess-risk bridge with a Riesz-localization critical-radius
trichotomy; prior verdict: none.
\item v2 (revise) -- added location-level anchors, repaired the Riesz norm
comparability condition, and split the frontier into a conditional theorem
plus a primitive flagship conjecture after the Stage~0.5 rewind; prior
verdict: REVISE / Stage~0.5 reject.
\item v3 (revise) -- added a growing-\(\calH_n\) report-packing witness for
the entropy channel, replaced the Kennedy comparison with theorem/section
anchors, and stated Conjecture~1 as a strict local-Riesz extension; prior
verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Chernozhukov et~al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., Chetverikov, D., Demirer, M., Duflo, E., Hansen, C.,
Newey, W., and Robins, J. (2018).
Double/debiased machine learning for treatment and structural parameters.
\emph{The Econometrics Journal}, 21(1), C1--C68.

\bibitem[Semenova and Chernozhukov(2021)]{SemenovaChernozhukov2021DMLCATE}
Semenova, V. and Chernozhukov, V. (2021).
Debiased machine learning of conditional average treatment effects and other
causal functions.
\emph{The Econometrics Journal}, 24(2), 264--289.

\bibitem[Chernozhukov, Newey, and Singh(2022a)]{ChernozhukovNeweySingh2022AutoDML}
Chernozhukov, V., Newey, W., and Singh, R. (2022).
Automatic debiased machine learning of causal and structural effects.
\emph{Econometrica}, 90(3), 967--1027.

\bibitem[Chernozhukov, Newey, and Singh(2022b)]{ChernozhukovNeweySingh2022Riesz}
Chernozhukov, V., Newey, W., and Singh, R. (2022).
Debiased machine learning of global and local parameters using regularized
Riesz representers.
\emph{The Econometrics Journal}, 25(3), 576--601.

\bibitem[Kennedy et~al.(2024)]{KennedyBalakrishnanRobinsWasserman2024MinimaxCATE}
Kennedy, E. H., Balakrishnan, S., Robins, J. M., and Wasserman, L. (2024).
Minimax rates for heterogeneous treatment effect estimation.
\emph{The Annals of Statistics}, 52(2), 793--816.

\bibitem[Armstrong and Kolesar(2021)]{ArmstrongKolesar2021FiniteSampleATE}
Armstrong, T. B. and Kolesar, M. (2021).
Finite-sample optimal estimation and inference on average treatment effects
under unconfoundedness.
\emph{Econometrica}, 89(3), 1141--1177.

\bibitem[Foster and Syrgkanis(2023)]{FosterSyrgkanis2023OSL}
Foster, D. J. and Syrgkanis, V. (2023).
Orthogonal statistical learning.
\emph{The Annals of Statistics}, 51(3), 879--908.

\bibitem[Kallus, Mao, and Uehara(2024)]{KallusMaoUehara2024LDML}
Kallus, N., Mao, X., and Uehara, M. (2024).
Localized debiased machine learning: efficient inference on quantile treatment
effects and beyond.
\emph{Journal of Machine Learning Research}, 25(16), 1--59.
\end{thebibliography}

\end{document}
