\section{Discussion and extensions}

The fixed-interior result extends the usual semiparametric picture. For fixed \(d\), or more generally throughout the parametric window in \cref{obj:thm:sharp-minimax-fixed-interior}, the minimax risk is of order \(n^{-1}\), in line with the classical efficiency theory for the average treatment effect under overlap \citep{Hahn1998,HiranoImbensRidder2003}. Allowing the alphabet to grow freely adds the challenge of estimating many small, poorly sampled conditional contrasts to the variance of an efficient influence-function average.

This distinction explains the hybrid estimator's improvement over direct plug-in and weighting estimators in the unrestricted discrete model. A plug-in estimator based on empirical conditional means treats each category as if its arm-specific denominators were reliable. In light categories, those denominators are often zero or very small, and trimming or stabilization introduces bias whose worst-case size depends on the number of categories. Inverse-probability weighting faces the same local denominator problem from the other side: bounded population overlap in \cref{obj:ass:overlap} coexists with unstable empirical treatment-cell counts when category mass is small. The hybrid estimator in \cref{obj:def:hybrid-estimator-handle} uses ratios on pilot-certified heavy categories and a polynomial continuation on the light categories. The sharp logarithmic factor in \cref{obj:thm:sharp-minimax-fixed-interior} confirms that this distinction is essential to the rate.

Doubly robust and targeted estimators are designed to protect first-order inference against nuisance estimation error, and they are central in modern observational causal inference \citep{RobinsRotnitzkyZhao1994,BangRobins2005,VanDerLaanRubin2006}. Their usual guarantees are most naturally expressed through convergence conditions on nuisance regressions or propensities. The warning of \citet{RobinsRitov1997} that unrestricted high-dimensional adjustment can obstruct uniform model-free inference is therefore especially relevant here. The experiment class in \cref{obj:def:experiment-class} ranges freely over smoothness, sparsity, margin, and category ordering, precluding uniform nuisance rates based on those structures. The minimax statement isolates that difficulty in a finite-alphabet benchmark: even with exact overlap and binary outcomes, unrestricted covariate heterogeneity creates a nonregular term \(d^2/(n^2(\log n)^2)\).

Higher-order influence-function methods are also closely related in motivation, since they seek to reduce bias from estimating high-dimensional nuisance components \citep{Robins2008,Robins2009,Robins2017,LiuMukherjeeNeweyRobins2017,Kennedy2024}. The present construction is complementary: it replaces unstable light-cell ratios directly by a polynomial approximation to the cell functional in \cref{obj:def:cell-functional}. The rate in \cref{obj:thm:sharp-minimax-fixed-interior} indicates that, in this unrestricted discrete benchmark, the relevant bias-variance tradeoff is the degree of the polynomial approximation against factorial-moment variance.

This result is related to recent discussions of limited overlap and high-dimensional adjustment \citep{DAmour2021,Balakrishnan2023,JinSyrgkanis2025}. \Cref{obj:thm:sharp-minimax-fixed-interior} fixes \(0<\epsilon<1/2\) and shows that many covariate categories with small marginal mass remain difficult under bounded overlap. \Cref{obj:thm:overlap-adaptive-universal-hybrid} separately characterizes the exact-randomization endpoint \(\epsilon=1/2\), where the minimax risk is bracketed between constants times \(n^{-1}\), uniformly in \(d\).

\subsection{Limitations and future work}

The selected-envelope part of \cref{obj:thm:overlap-adaptive-universal-hybrid} connects these two regimes without claiming a full transition theory or an adaptive implementation. For each fixed interior \(0<\epsilon<1/2\), and under the theorem's hybrid calibration range \(n\ge N_\epsilon\) and \(d\le \rho_\epsilon n\log n\), it compares the fixed-overlap hybrid estimator with the centered estimator using the known theoretical constants and gives an upper bound involving
\[
\frac1n+
\min\left\{
\frac{d^2}{n^2(\log n)^2},(1/2-\epsilon)^2
\right\}.
\]
This is useful as a theoretical envelope when the assignment mechanism is close to randomized, because the centered estimator improves as \(\epsilon\) approaches \(1/2\). The selector depends on \(\epsilon\) and \(C_\epsilon\), so it should not be read as a data-driven procedure when those quantities are unknown. Moreover, the theorem does not assert that this combined upper envelope is minimax sharp for triangular arrays with \(\epsilon=\epsilon_n\). The fixed-interior lower bound applies for each fixed \(0<\epsilon<1/2\), and the endpoint bracket applies at \(\epsilon=1/2\); together they leave open the possibility that the exact minimax transition depends on the joint rates at which \(d\), \(n\), and \(1/2-\epsilon_n\) vary.
