\section{Appendix: verification note}

This appendix documents the scope and boundary of the machine-checked component of the paper.

The checked development includes the finite-alphabet observed-data model used in \cref{obj:ass:iid-sampling} and \cref{obj:def:experiment-class}. In particular, the single-observation law \(P\), the iid product law \(P^{\otimes n}\), and the finite four-cell representation by category are represented directly. The same layer also includes the bridge from finite products to the infinite-product notation used for sequences of observations, so that the sample-level risk statements are connected to repeated iid sampling rather than to an informal limiting construction.

The local observational model is checked at the level needed for the overlap and ATE objects. The overlap cone in \cref{obj:def:overlap-cone}, the homogeneous cell functional in \cref{obj:def:cell-functional}, and the ATE functional in \cref{obj:def:ate-functional} are represented as finite-alphabet objects with arbitrary category masses. Thus the verification covers the unrestricted discrete-confounding geometry used throughout the paper, including categories with small marginal probability, subject only to the stated overlap restrictions.

The estimator objects are also included in the checked scope. This covers the deterministic split, the split cell counts, the heavy and light pilot sets, the ratio contribution on pilot-certified heavy categories, the Chebyshev-polynomial continuation on light categories, the factorial-moment estimator, and the final truncation in \cref{obj:def:hybrid-estimator-handle}. The minimax risk in \cref{obj:def:minimax-risk} is checked as a worst-case mean-squared-error criterion over the experiment class, with the infimum taken over measurable estimators as stated there.

Lean declaration names and low-level convention checks are retained in the formal crosswalk and verification artifacts. The statistical proof prose focuses on the heavy/light decomposition, approximation bias, variance control, minimax reduction, and endpoint comparison.

For results whose theorem-local verification footnotes cite an external mathematical input, the cited input is part of the paper's stated dependency boundary. The machine check covers the formal statement that imports that input, the compatibility of its hypotheses with the objects defined in the paper, and the remaining derivation from that point. Results without such a footnote are checked internally against the definitions and assumptions stated in the paper.

All theorem statements and formal derivations in this paper are machine-checked in Lean 4, subject to the theorem-local external inputs explicitly identified in the formalization-scope footnotes.
