% Sec. 9 fragment statement
\paragraph{Conjecture under test, restated verbatim.}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:exposed-endpoints}, fix an endpoint direction \(\ell\in\{-,+\}\).  Let \(b_\ell(P;\Gamma,\kappa)\) be the corresponding support value of the \((\Gamma,\kappa)\) frontier in Conjecture~\ref{conj:lee-gamma-frontier}.  Then \(b_\ell(P;\Gamma,\kappa)=v_\ell^{\mathrm{SGJR}}(P;\Gamma)\) for the finite-binary \citet{ShepherdGilbertJemiaiRotnitzky2006} / \citet{JemiaiRotnitzkyShepherdGilbert2007}-induced beta/psi endpoint problem if and only if \(\Delta_\ell^{\mathrm{SGJR}}(P;\Gamma,\kappa)=0\).  If \(\Delta_\ell^{\mathrm{SGJR}}(P;\Gamma,\kappa)>0\), then \(b_\ell(P;\Gamma,\kappa)\) is strictly inside that SGJR/JR-induced armwise beta/psi benchmark.  Separately, \(b_\ell(P;\Gamma,\kappa)=v_\ell^{\mathrm{HH}}(P;\Gamma)\) for the proposal-defined binary no-exclusion support benchmark inspired by \citet{HonoreHu2020Selection} only if \(\Delta_\ell^{\mathrm{HH}}(P;\Gamma,\kappa)=0\); under local uniqueness and strict exposure, \(\Delta_\ell^{\mathrm{HH}}(P;\Gamma,\kappa)>0\) implies strict separation from the no-exclusion endpoint.

\paragraph{Headline.}
Conjecture 3 is confirmed: zero compatibility gap is necessary and sufficient for equality with the SGJR/JR armwise beta/psi endpoint, and is necessary (indeed sufficient in this binary specialization) for equality with the proposal-defined Honore--Hu-style no-exclusion endpoint; positive gap gives strict separation in the appropriate endpoint direction.

\begin{theorem}[Theorem 3: Compatibility-gap characterization]\label{thm:coupling-iff-confirmed}
Work under Assumptions~\ref{ass:random-consistency}--\ref{ass:exposed-endpoints}.  Interpret \(\ell=-\) as the lower support problem and \(\ell=+\) as the upper support problem.  Use the Section~7 definitions
\[
  b_-(P;\Gamma,\kappa)=\theta_L(P;\Gamma,\kappa),\qquad
  b_+(P;\Gamma,\kappa)=\theta_U(P;\Gamma,\kappa),
\]
\[
  v_-^{\mathrm{SGJR}}(P;\Gamma)=\psi_L(P;\Gamma,\varepsilon),\qquad
  v_+^{\mathrm{SGJR}}(P;\Gamma)=\psi_U(P;\Gamma,\varepsilon),
\]
and
\[
  v_-^{\mathrm{HH}}(P;\Gamma)=\eta_L(P;\Gamma,\varepsilon),\qquad
  v_+^{\mathrm{HH}}(P;\Gamma)=\eta_U(P;\Gamma,\varepsilon),
\]
with the compact benchmark rectangle \(\mathcal R_\varepsilon\) fixed as in Section~7 and with the \(\varepsilon\)-dependence suppressed in the shorthand \(v_\ell\).  Then
\[
  b_\ell(P;\Gamma,\kappa)=v_\ell^{\mathrm{SGJR}}(P;\Gamma)
  \quad\Longleftrightarrow\quad
  \Delta_\ell^{\mathrm{SGJR}}(P;\Gamma,\kappa)=0.
\]
Consequently, if \(\Delta_-^{\mathrm{SGJR}}(P;\Gamma,\kappa)>0\), then
\[
  v_-^{\mathrm{SGJR}}(P;\Gamma)<b_-(P;\Gamma,\kappa),
\]
and if \(\Delta_+^{\mathrm{SGJR}}(P;\Gamma,\kappa)>0\), then
\[
  b_+(P;\Gamma,\kappa)<v_+^{\mathrm{SGJR}}(P;\Gamma).
\]
For the proposal-defined binary Honore--Hu-style no-exclusion benchmark,
\[
  b_\ell(P;\Gamma,\kappa)=v_\ell^{\mathrm{HH}}(P;\Gamma)
  \quad\Longrightarrow\quad
  \Delta_\ell^{\mathrm{HH}}(P;\Gamma,\kappa)=0.
\]
In the binary finite-table specialization of Section~7 the HH feasible support set is the same compact armwise rectangle as the SGJR/JR benchmark, so the converse also holds.  In particular, under local uniqueness and strict exposure, \(\Delta_-^{\mathrm{HH}}>0\) implies
\[
  v_-^{\mathrm{HH}}(P;\Gamma)<b_-(P;\Gamma,\kappa),
\]
and \(\Delta_+^{\mathrm{HH}}>0\) implies
\[
  b_+(P;\Gamma,\kappa)<v_+^{\mathrm{HH}}(P;\Gamma).
\]
\end{theorem}

% Sec. 13 refutation attempt
\paragraph{Refutation attempt before proof.}
The cluster-appropriate finite-binary refutation primitive is endpoint or vertex enumeration of the two selected-arm support problem.  After Theorem~\ref{thm:arm-quadratic}, every armwise candidate endpoint is represented by a selected-arm \(2\times2\) table with margins \((q_d,m_d)\) and an active Frechet or odds-ratio face.  Thus a counterexample to the conjecture can only occur through the two-dimensional endpoint optimizer set in the benchmark rectangle and its relation to the common-\(\alpha\) curve \(\mathcal C_\kappa(P)\).

The search considered the three possible witness types.  Type I is a zero-gap witness with unequal values: an endpoint optimizer \(q^\star\) of the SGJR/JR rectangle, or of the HH rectangle, satisfies \(q^\star\in\mathcal C_\kappa(P)\) but the restricted Lee--Gamma support value differs from the benchmark support value.  This candidate cannot work, because the same table \(q^\star\) is feasible for the restricted support problem and has exactly the benchmark endpoint value.  Type II is an equal-value witness with positive gap: the restricted support value equals the benchmark value even though every benchmark optimizer lies a positive Euclidean distance from \(\mathcal C_\kappa(P)\).  This candidate cannot work, because compactness of \(\mathcal C_\kappa(P)\) gives a restricted optimizer \(\tilde q\), and equality of the values makes \(\tilde q\) an unrestricted benchmark optimizer on the curve.  Type III is a positive-gap witness without strict separation.  Since the restricted feasible set is a subset of the benchmark rectangle, failure of strict separation is exactly equality of the support values, reducing Type III to Type II.

Thus vertex enumeration of the finite binary endpoint geometry produces no witness under the stated assumptions.  The attempted counterexample search fails for a structural reason: benchmark endpoint equality is equivalent to intersection of the benchmark optimizer set with the common-\(\alpha\) compatibility curve.

% Sec. 10 interpretation
\paragraph{Interpretation.}
The theorem says that the comparison with the SGJR/JR-inspired beta/psi benchmark is not about whether a selected-arm log-odds parameter exists.  Such a parameter exists arm by arm by construction.  The issue is whether the two armwise endpoint tables can be coupled into one principal-strata law with a single always-selected share \(\alpha\) and the harmed-budget restriction \(p_0-\alpha\le\kappa p_0\).  The observable gap \(\Delta_\ell^{\mathrm{SGJR}}\) measures exactly that coupling failure at the endpoint optimizer set.  A zero gap means an armwise beta/psi endpoint is already a valid Lee--Gamma endpoint; a positive gap means the armwise endpoint sits outside the one-dimensional common-\(\alpha\) frontier, so the Lee--Gamma endpoint is strictly inside the larger armwise benchmark.

The same logic applies to the proposal-defined binary Honore--Hu-style no-exclusion support benchmark because Section~7 defines it through the same finite armwise tables and the same compact margin rectangle.  The theorem therefore records a set-restriction fact: adding the common-\(\alpha\) and harmed-budget compatibility equations can only shrink the support interval, and it shrinks it strictly whenever the exposed benchmark endpoint set misses the compatibility curve.

% Sec. 11 proof
\begin{proof}
Write
\[
  C=\mathcal C_\kappa(P)
\]
for the common-\(\alpha\) compatibility curve and write \(R=\mathcal R_\varepsilon\) for the compact SGJR/JR margin rectangle from Section~7.  By the definition of \(R\), \(C\subset R\).  By Assumption~\ref{ass:interior}, \(\mathcal A_\kappa^+(P)\) is compact and \(r_d(\alpha)\in(0,1)\) on the profile.  By Theorem~\ref{thm:arm-quadratic} and the explicit Section~7 formula for \(\ell_\Gamma\) and \(u_\Gamma\), the endpoint maps are continuous on the compact rectangle used by the comparison theorem.  Hence all benchmark and restricted support extrema below are attained.

For the upper endpoint define
\[
  F_+(q_1,q_0)=u_\Gamma(q_1,m_1)-\ell_\Gamma(q_0,m_0),
\]
and for the lower endpoint define
\[
  F_-(q_1,q_0)=\ell_\Gamma(q_1,m_1)-u_\Gamma(q_0,m_0).
\]
The Section~7 definitions give
\[
  v_+^{\mathrm{SGJR}}=\max_{q\in R}F_+(q),\qquad
  b_+=\max_{q\in C}F_+(q),
\]
and
\[
  v_-^{\mathrm{SGJR}}=\min_{q\in R}F_-(q),\qquad
  b_-=\min_{q\in C}F_-(q).
\]
Let \(R_+^\star=\arg\max_{q\in R}F_+(q)\) and \(R_-^\star=\arg\min_{q\in R}F_-(q)\).  These sets are nonempty compact sets by Assumption~\ref{ass:exposed-endpoints} and continuity.  The compatibility gaps are
\[
  \Delta_+^{\mathrm{SGJR}}=\inf_{q\in R_+^\star}\operatorname{dist}(q,C),
  \qquad
  \Delta_-^{\mathrm{SGJR}}=\inf_{q\in R_-^\star}\operatorname{dist}(q,C).
\]
Because \(R_\ell^\star\) and \(C\) are compact, \(\Delta_\ell^{\mathrm{SGJR}}=0\) if and only if \(R_\ell^\star\cap C\ne\varnothing\).

Consider \(\ell=+\).  Since \(C\subset R\),
\[
  b_+=\max_C F_+\le \max_R F_+=v_+^{\mathrm{SGJR}}.
\]
If \(\Delta_+^{\mathrm{SGJR}}=0\), choose \(q^\star\in R_+^\star\cap C\).  Then
\[
  b_+\ge F_+(q^\star)=v_+^{\mathrm{SGJR}},
\]
so \(b_+=v_+^{\mathrm{SGJR}}\).  Conversely, if \(b_+=v_+^{\mathrm{SGJR}}\), choose a restricted maximizer \(\tilde q\in C\).  Then
\[
  F_+(\tilde q)=b_+=v_+^{\mathrm{SGJR}},
\]
so \(\tilde q\in R_+^\star\cap C\), and therefore \(\Delta_+^{\mathrm{SGJR}}=0\).  The strict statement follows by contraposition: if \(\Delta_+^{\mathrm{SGJR}}>0\), equality is impossible, and the subset inequality above sharpens to
\[
  b_+<v_+^{\mathrm{SGJR}}.
\]

The lower endpoint is the same argument with the order reversed.  Because \(C\subset R\),
\[
  v_-^{\mathrm{SGJR}}=\min_R F_-\le \min_C F_-=b_-.
\]
If \(\Delta_-^{\mathrm{SGJR}}=0\), choose \(q^\star\in R_-^\star\cap C\), giving
\[
  b_-\le F_-(q^\star)=v_-^{\mathrm{SGJR}}.
\]
Together with \(v_-^{\mathrm{SGJR}}\le b_-\), this gives equality.  Conversely, if \(b_-=v_-^{\mathrm{SGJR}}\), a restricted minimizer \(\tilde q\in C\) also minimizes \(F_-\) over \(R\), so \(R_-^\star\cap C\ne\varnothing\) and \(\Delta_-^{\mathrm{SGJR}}=0\).  If \(\Delta_-^{\mathrm{SGJR}}>0\), equality is impossible and hence
\[
  v_-^{\mathrm{SGJR}}<b_-.
\]

For the Honore--Hu-style benchmark, let \(H_+^\star\) and \(H_-^\star\) be the corresponding Section~7 endpoint optimizer sets.  In the binary no-covariate specialization defined in Section~7, the HH feasible support set uses the same compact armwise rectangle \(R\) and the same objective functions \(F_+\) and \(F_-\), with a different interpretation of the armwise tables.  Therefore the same subset and optimizer-intersection proof gives the only-if implication claimed in the conjecture, and in this binary specialization also gives the converse.  Under local uniqueness and strict exposure, \(H_\ell^\star\) is locally stable as an exposed endpoint face.  If \(\Delta_\ell^{\mathrm{HH}}>0\), the endpoint optimizer set misses \(C\); the equality argument above cannot occur, so the restricted support value is strictly inside the HH benchmark in the lower or upper direction as displayed in the theorem.
\end{proof}

% Sec. 12 sanity check
\paragraph{Sanity check: selected-mixture independence boundary.}
At the boundary \(\Gamma=1\), the selected-mixture odds-ratio restriction forces \(OR_d=1\) in each selected arm.  The armwise quadratic endpoint in Theorem~\ref{thm:arm-quadratic} collapses to the independent table \(t_d=q_dm_d\), so
\[
  \ell_1(q_d,m_d)=u_1(q_d,m_d)=m_d.
\]
Therefore
\[
  F_+(q_1,q_0)=F_-(q_1,q_0)=m_1-m_0
\]
for every benchmark margin pair \(q\) and for every \(q\in\mathcal C_\kappa(P)\).  Hence
\[
  b_-(P;1,\kappa)=b_+(P;1,\kappa)=v_-^{\mathrm{SGJR}}(P;1)=v_+^{\mathrm{SGJR}}(P;1)=m_1-m_0,
\]
and the same equality holds for the HH-style benchmark.  The entire benchmark rectangle is an optimizer set, so it intersects \(\mathcal C_\kappa(P)\) whenever the alpha profile is nonempty, giving \(\Delta_\ell^{\mathrm{SGJR}}=\Delta_\ell^{\mathrm{HH}}=0\).  This recovers the known selected-mixture independence corner: armwise and coupled support calculations all reduce to the observed selected mean contrast.

% Sec. 13 counterexample or minimality check
\paragraph{Minimality check: dropping common-\(\alpha\) compatibility.}
The common-\(\alpha\) condition is necessary for the comparison to be meaningful.  If it is dropped, the benchmark may choose an exposed armwise endpoint \(q^\star=(q_1^\star,q_0^\star)\) with
\[
  p_1q_1^\star\ne p_0q_0^\star.
\]
Such a pair can satisfy both armwise odds-ratio quadratic restrictions, because those restrictions are checked separately in the two selected arms, but it cannot be generated by any single binary principal-strata law with always-selected mass \(\alpha\).  Under Assumption~\ref{ass:exposed-endpoints}, if this off-curve \(q^\star\) is the locally unique benchmark endpoint, then
\[
  \operatorname{dist}(q^\star,\mathcal C_\kappa(P))>0
\]
and the theorem gives strict separation.  Thus the weaker armwise beta/psi or no-exclusion restriction without common-\(\alpha\) coupling is not enough to recover the Lee--Gamma support value.
