% =====================================================================
%  thmsmith Stage 0 derivation skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_collider\_bias\_sharp, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{pid\_collider\_bias\_sharp} / \texttt{v1}%
  \\ \large\textit{Sharp alpha-profile Lee--Gamma bounds for always-selected effects}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\providecommand{\citet}[1]{\cite{#1}}

\begin{abstract}
This setup note defines the finite-table bounding functional
\(B_{\Gamma,\kappa}(P)=[\theta_L(P;\Gamma,\kappa),\theta_U(P;\Gamma,\kappa)]\)
for the Lee always-selected effect when monotone selection is replaced by a
finite harmed-stratum budget \(\kappa\) and an arm-specific selected-mixture
odds-ratio bound \(\Gamma\).  The observed input is the randomized law of
\((D,S,SY)\), summarized by selected shares \(p_d=P(S=1\mid D=d)\) and selected
binary means \(m_d=P(Y=1\mid D=d,S=1)\).  The target is
\(\theta=\E[Y(1)-Y(0)\mid S(1)=S(0)=1]\), which is not point identified because
the always-selected principal stratum is latent.  The functional profiles over the common
always-selected share \(\alpha\), solves two closed-form selected-arm
odds-ratio quadratics, and then takes the support function of the resulting
armwise mean intervals restricted to the common-\(\alpha\) compatibility curve.
The per-conjecture stages will verify whether this computable
\(\alpha\)-profile is sharp, whether finite \(\Gamma\) strictly tightens the
unrestricted bidirectional principal-strata interval, and whether equality with
the proposal-defined armwise beta/psi and no-exclusion support benchmarks is
exactly governed by the common-\(\alpha\), harmed-budget compatibility gap.
\end{abstract}

\section{Introduction}
Treatment-induced sample selection is central in program evaluation when wages,
health outcomes, test scores, or institutional records are only observed after a
post-treatment event such as employment, survival, response, or participation.
Lee's monotone-selection analysis converts the problem into a sharp trimming
bound, but the monotonicity requirement rules out units who would be selected
under control and not under treatment.  In many applications, treatment may help
some units enter the selected sample and harm others, so a useful robustness
analysis should allow both one-sided principal strata while still controlling
how much selected-sample sorting can be attributed to the latent always-selected
type.

This note studies that robustness problem in the simplest finite setting:
binary treatment, binary selection, and binary selected outcomes.  The maintained
restrictions are randomized assignment and consistency, the four principal
selection strata \(A=(1,1)\), \(G=(0,1)\), \(H=(1,0)\), and \(N=(0,0)\), a finite
budget \(h\le \kappa p_0\) on the harmed stratum \(H\), and a selected-arm
odds-ratio bound \(\Gamma\) linking membership in the always-selected stratum
to the selected outcome.  The targeted result is a sharp one-dimensional
\(\alpha\)-profile: once \(\alpha=P(A)\) is fixed, each arm would be a \(2\times2\)
selected-mixture table with known margins, so the feasible always-selected mean
is obtained by solving two odds-ratio saturation quadratics.

The contribution sought by the conjectures is not another tail-trimming formula and not the observation
that a log-odds sensitivity parameter can reproduce a single selected-arm table.
Indeed, every interior selected-arm endpoint has the armwise representation
\(\beta_d=\log OR_d\).  If confirmed, the contribution is the coupled sharp set generated by
one common principal share \(\alpha\), the harmed-stratum budget, and two
selected-mixture odds-ratio faces.  This gives applied Lee-bounds workflows a
direct diagnostic for whether monotone selection is doing substantive work:
compare the Lee trimming interval, the unrestricted bidirectional
principal-strata interval, and the finite \((\Gamma,\kappa)\) profile interval.

The paper-level novelty target is the explicit sharp finite-table functional, not the
scalar sensitivity parameter and not a claim that a published open-regime
problem is being closed.  Lee's monotone-selection trimming theorem
is the boundary benchmark: the present functional contains its binary case as a
face and then studies an adjacent bidirectional sensitivity model where both
one-sided principal strata may be positive.  Section~7 also defines
proposal-level binary armwise support benchmarks motivated by the
Shepherd--Gilbert--Jemiai--Rotnitzky /
Jemiai--Rotnitzky--Shepherd--Gilbert beta/psi workflow and by no-exclusion
selection bounds.  The proposed main comparison theorem would prove only a
set-restriction frontier if the conjectures are confirmed: the alpha-profile
equals those larger armwise benchmarks exactly when
an exposed optimizer lies on the one-dimensional curve
\(p_1q_1=p_0q_0=\alpha\) with \(p_0-\alpha\le\kappa p_0\).  A nonzero
derivative normal to that curve is a computable open-set separating certificate
for these proposal-defined benchmarks; it is not asserted to be an equivalence
or non-equivalence theorem between named published estimators.

\paragraph{Motivating conjecture(s).}
\paragraph{Conjecture 1.}
\phantomsection\label{conj:lee-gamma-frontier}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:interior}, the sharp identified set for the always-selected effect is
\[
  \Theta_I(P;\Gamma,\kappa)=
  \left[
    \inf_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\underline a_1(\alpha)-\overline a_0(\alpha)\},
    \sup_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\overline a_1(\alpha)-\underline a_0(\alpha)\}
  \right],
\]
where \(\underline a_d(\alpha)\) and \(\overline a_d(\alpha)\) are the armwise quadratic endpoints from Theorem~\ref{thm:arm-quadratic}.  Moreover, each global endpoint is attained by an explicit four-stratum law \((A,G,H,N)\) whose two selected-arm \(2\times2\) tables saturate the appropriate odds-ratio boundary, and the optimizing \(\alpha\) is either an endpoint of \(\mathcal A_\kappa^+(P)\) or a root of the derivative of a quadratic-radical profile induced by the active odds-ratio equations.
For an open set of observable laws satisfying the comparison regime in Assumption~\ref{ass:exposed-endpoints}, this frontier is conjectured not to be representable as either the \citet{HuberMellace2015SharpSelection} monotonicity/stochastic-dominance sharp-bound geometry, a \citet{LaffersNedela2017Sensitivity} Lee sensitivity program with only monotonicity/exogeneity relaxation parameters, a \citet{Semenova2025GeneralizedLee} conditional-monotonicity Lee bound, the stochastic-monotonicity-plus-symmetry geometry of \citet{Okamoto2025RobustifyLee}, or a margin-free application of the \citet{ShepherdGilbertJemiaiRotnitzky2006}, \citet{JemiaiRotnitzkyShepherdGilbert2007}, \citet{ShepherdRedmanAnkerst2008}, and \citet{ShepherdGilbertDupont2011} beta/psi principal-stratum sensitivity family.  The statement explicitly concedes that beta \(=\log OR_d(t_d;r_d(\alpha),m_d)\) reproduces each armwise selected table; the conjectured non-equivalence is the sharper claim that without adding the same \(\alpha\)-coupling and \(H\le \kappa p_0\) restriction, those armwise beta tables do not define the same global sharp ATE endpoint.  The distinguishing certificate is an interior active odds-ratio equality \(OR_d(t_d;r_d(\alpha),m_d)\in\{\Gamma^{-1},\Gamma\}\) plus the cross-arm equalities \(p_1r_1(\alpha)=p_0r_0(\alpha)=\alpha\), with no tail-trimming quantile cutoff, stochastic-dominance ordering, stochastic monotonicity/symmetry condition, covariate sign partition, or right-censoring survival model that pins the same coupled selected-cell endpoint.  A concrete open-cell witness target is \(p_1=0.6\), \(p_0=0.5\), \(m_1=0.5\), \(m_0=0.4\), \(\Gamma=4\), \(\kappa=0.5\), and \(\alpha=0.3\): both \(G=0.3\) and \(H=0.2\) are positive.  At this witness the local upper ATE endpoint uses \(t_1=1/3\) and \(t_0=(-1+\sqrt{3.88})/6\), while the local lower ATE endpoint uses \(t_1=1/6\) and \(t_0=(4-\sqrt{4.48})/6\); the corresponding armwise beta values are \(\pm\log 4\), so the certificate is not the absence of a log-odds parametrization but the extra \((\alpha,\kappa)\) compatibility restriction:
\[
\begin{array}{c|cc|c|c}
\text{arm/endpoint} & P(A,Y=1\mid S(d)=1) & P(A,Y=0\mid S(d)=1) &
P(A^c,Y=1\mid S(d)=1) & P(A^c,Y=0\mid S(d)=1)\\
\hline
d=1,\ \text{upper} & 0.333 & 0.167 & 0.167 & 0.333\\
d=1,\ \text{lower} & 0.167 & 0.333 & 0.333 & 0.167\\
d=0,\ \text{upper for }a_0 & 0.314 & 0.286 & 0.086 & 0.314\\
d=0,\ \text{lower for }a_0 & 0.162 & 0.438 & 0.238 & 0.162
\end{array}
\]
Thus the displayed witness gives local ATE values approximately \([-0.190,0.397]\) at \(\alpha=0.3\), with all active cells interior rather than tail-trimming faces.

\paragraph{Conjecture 2.}
\phantomsection\label{conj:strict-tightening}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:exposed-endpoints}, if \(\Gamma<\infty\) and every unrestricted \(\Gamma=\infty\) optimizer for the lower or upper ATE endpoint uses at least one selected-arm cell on a nondegenerate Fréchet equality face \(t_d=L_d(\alpha)\) or \(t_d=U_d(\alpha)\) with \(0<L_d(\alpha)<U_d(\alpha)<1\), then the interval in Conjecture~\ref{conj:lee-gamma-frontier} is a strict subset of the unrestricted bidirectional-principal-strata interval obtained by setting \(\Gamma=\infty\).  Within the interior assumptions, equality is possible only through profile-level compensation: a different positive \(\alpha\) must reproduce the unrestricted ATE endpoint while all active arm cells satisfy the finite-\(\Gamma\) odds-ratio inequalities.  Outside the interior assumptions, equality can also occur when an optimizing \(\alpha\) forces a degenerate principal mixture \(r_d(\alpha)\in\{0,1\}\), an observed selected outcome margin has \(m_d\in\{0,1\}\), or the reverse-selection budget collapses to Lee monotonicity and the unrestricted endpoint is already compatible with the finite-\(\Gamma\) odds-ratio face.

\paragraph{Conjecture 3.}
\phantomsection\label{conj:coupling-iff}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:exposed-endpoints}, fix an endpoint direction \(\ell\in\{-,+\}\).  Let \(b_\ell(P;\Gamma,\kappa)\) be the corresponding support value of the \((\Gamma,\kappa)\) frontier in Conjecture~\ref{conj:lee-gamma-frontier}.  Then \(b_\ell(P;\Gamma,\kappa)=v_\ell^{\mathrm{SGJR}}(P;\Gamma)\) for the finite-binary \citet{ShepherdGilbertJemiaiRotnitzky2006} / \citet{JemiaiRotnitzkyShepherdGilbert2007}-induced beta/psi endpoint problem if and only if \(\Delta_\ell^{\mathrm{SGJR}}(P;\Gamma,\kappa)=0\).  If \(\Delta_\ell^{\mathrm{SGJR}}(P;\Gamma,\kappa)>0\), then \(b_\ell(P;\Gamma,\kappa)\) is strictly inside that SGJR/JR-induced armwise beta/psi benchmark.  Separately, \(b_\ell(P;\Gamma,\kappa)=v_\ell^{\mathrm{HH}}(P;\Gamma)\) for the proposal-defined binary no-exclusion support benchmark inspired by \citet{HonoreHu2020Selection} only if \(\Delta_\ell^{\mathrm{HH}}(P;\Gamma,\kappa)=0\); under local uniqueness and strict exposure, \(\Delta_\ell^{\mathrm{HH}}(P;\Gamma,\kappa)>0\) implies strict separation from the no-exclusion endpoint.

\section{Related work and positioning}
Lee \cite{Lee2009SampleSelection} is the primary boundary benchmark.  Lee's
theorem gives sharp trimming bounds for the always-selected effect under
monotone selection; in the binary no-covariate notation here, that is the
boundary face \(\kappa=0\), \(\Gamma=\infty\), \(\alpha=p_0\), and \(H=0\) when
\(p_1\ge p_0\).  The conjectured \(\alpha\)-profile is positioned as a
computable finite-table sensitivity model for regimes with \(G>0\), \(H>0\),
finite \(\Gamma\), and \(p_0-\alpha\le\kappa p_0\).  This is a field-level
sharp-bound target: the note does not cite a published open-problem statement asserting that the
finite bidirectional \((\Gamma,\kappa)\) regime was unresolved, and it therefore
does not present the result as a priority claim about Lee.  Manski
\cite{Manski1990} and Horowitz and Manski \cite{HorowitzManski1995} provide the
bounded-outcome and mixture-completion logic that appears here when the
selected-mixture odds-ratio bound is removed.  Balke and Pearl
\cite{BalkePearl1997} establish the finite response-type endpoint-attainment
perspective used in the constructive sharpness proof.

Principal stratification, as formulated by Frangakis and Rubin
\cite{FrangakisRubin2002} and used for truncation-by-death problems by Zhang and
Rubin \cite{ZhangRubin2003}, motivates the target
\(\E[Y(1)-Y(0)\mid S(1)=S(0)=1]\).  Shepherd, Gilbert, Jemiai, and Rotnitzky
\cite{ShepherdGilbertJemiaiRotnitzky2006}, Jemiai, Rotnitzky, Shepherd, and
Gilbert \cite{JemiaiRotnitzkyShepherdGilbert2007}, Shepherd, Redman, and
Ankerst \cite{ShepherdRedmanAnkerst2008}, and Shepherd, Gilbert, and Dupont
\cite{ShepherdGilbertDupont2011} develop principal-stratum sensitivity analyses
with log-odds-style sensitivity parameters.  The comparison in
the third conjecture is deliberately narrower: Section~7 defines a
proposal-level binary no-covariate armwise support benchmark motivated by that
beta/psi workflow.  In each selected arm it uses \(\beta_d=\log OR_d\) to index
the association between always-selected membership and \(Y(d)\), while treating
the selected-arm always share as an arm-specific sensitivity margin.  The
target statement is an exact set-restriction criterion for this benchmark, not an
iff frontier between named published estimators or identification strategies:
armwise beta values reproduce each selected table, but the resulting support
function should equal the sharp Lee--Gamma support function only if an endpoint
optimizer also satisfies
\[
  p_1q_1=p_0q_0=\alpha,\qquad \alpha\in\mathcal A_\kappa^+(P).
\]
Thus the difference is not qualitative rhetoric about hidden strata; it is a
checkable equality condition for joint attainability by one principal-strata
law within the proposal-defined rectangle, with a normal derivative as the
computable separating object.

Honore and Hu \cite{HonoreHu2020Selection} is the no-exclusion selection
comparator.  This setup does not claim that their paper states, estimates, or
identifies the finite binary support functional used here; rather, it defines a
Honore--Hu-style no-exclusion support benchmark by retaining the observed
selected margins and finite armwise odds-ratio faces while dropping the
common-\(\alpha\) and harmed-budget restrictions.  In this binary
specialization the benchmark is intentionally identical to the same larger
armwise rectangle used for the SGJR--Jemiai comparison.  Equality with the
Lee--Gamma endpoint would therefore record a set-inclusion fact: an exposed
no-exclusion endpoint table must have implied selected-arm shares satisfying
the same principal-share compatibility equations.

Huber and Mellace \cite{HuberMellace2015SharpSelection} derive sharp bounds for sample
selection under monotonicity and stochastic dominance, and Laffers and Nedela
\cite{LaffersNedela2017Sensitivity} formulate Lee sensitivity analysis as an optimization
problem.  Semenova \cite{Semenova2025GeneralizedLee} generalizes Lee bounds when covariates
identify the sign of the selection effect, while Okamoto \cite{Okamoto2025RobustifyLee}
replaces deterministic monotonicity by stochastic monotonicity and a symmetry
shape restriction.  The present finite-table target differs because it allows
latent bidirectional selection within the same covariate cell and controls
selected-mixture collider dependence through odds-ratio faces rather than
through sign, dominance, stochastic monotonicity, or symmetry conditions.  In
particular, the proposed open-set certificate has
both \(G\) and \(H\) positive, an interior odds-ratio face, and a nonzero normal
derivative away from the common-\(\alpha\) curve; these are exactly the objects
that tail trimming, stochastic-dominance ordering, conditional sign partitions,
and stochastic-monotonicity/symmetry frontiers do not compute.

Scharfstein, Manski, and Anthony \cite{ScharfsteinManskiAnthony2004} and Smith
and VanderWeele \cite{SmithVanderWeele2019} are useful missing-outcome and
selection-bias comparators; their bounds are armwise or robustness-factor tools,
not sharp always-selected principal-strata endpoint constructions.  Kroft,
Mourifie, and Vayalinkal \cite{KroftMourifieVayalinkal2024} document how
multilayered selection can stress applied Lee-bounds workflows, which is the
empirical use case for reporting the \((\Gamma,\kappa)\)-profile interval.  The
in-repository CausalSmith API catalogue records Manski-style partial-ID
comparators and adjacent budgeted-selection envelopes; this setup is at a
different abstraction because it uses a finite principal-strata table with a
common alpha profile and selected-arm odds-ratio quadratics.

\section{Formal setup}
Let \(D\in\{0,1\}\) be randomized treatment, let \(S(d)\in\{0,1\}\) be the
potential post-treatment selection or collider state, and let
\(Y(d)\in\{0,1\}\) be the potential selected outcome on the scale of interest.
The observed law \(P\) is the joint law of \(D\), \(S=S(D)\), and \(SY\), where
\(Y=Y(D)\) is observed only when \(S=1\).  The observable inputs used by the
functional are
\[
  p_d=P(S=1\mid D=d),\qquad
  m_d=P(Y=1\mid D=d,S=1),\qquad d\in\{0,1\}.
\]
Randomization makes these equal to \(P(S(d)=1)\) and
\(P(Y(d)=1\mid S(d)=1)\), respectively, under the consistency assumption below.

There are four binary principal selection strata:
\[
  A=(1,1),\qquad G=(0,1),\qquad H=(1,0),\qquad N=(0,0),
\]
where \(A\) is always selected, \(G\) is treatment-helped, \(H\) is
treatment-harmed, and \(N\) is never selected.  Write their masses as
\(\alpha,g,h,n\).  Compatibility with the selected shares gives
\[
  g=p_1-\alpha,\qquad h=p_0-\alpha,\qquad
  n=1-p_0-p_1+\alpha.
\]
Thus the observable and harmed-budget restrictions imply
\[
  \mathcal A_\kappa(P)
  =
  \bigl[
    \max\{0,p_0+p_1-1,p_0(1-\kappa)\},\ \min\{p_0,p_1\}
  \bigr].
\]
Because the target conditions on the always-selected stratum, the profile uses
only positive always-selected shares,
\[
  \mathcal A_\kappa^+(P)=\mathcal A_\kappa(P)\cap (0,\min\{p_0,p_1\}].
\]
The main sharpness theorem is stated under the nondegenerate case in which this
positive set is a compact interval with a positive lower endpoint.

For a candidate \(\alpha\in\mathcal A_\kappa^+(P)\), define the selected-arm
share of always-selected units by
\[
  r_d(\alpha)=\frac{\alpha}{p_d},\qquad d\in\{0,1\}.
\]
Let
\[
  t_d=P(A,Y(d)=1\mid S(d)=1)
\]
inside the selected arm.  Then the always-selected mean in arm \(d\) is
\[
  a_d(\alpha,t_d)=\E[Y(d)\mid A]=\frac{t_d}{r_d(\alpha)}.
\]
The selected-arm \(2\times2\) table with row \(A\) and column \(Y(d)=1\) has
margins \(r_d(\alpha)\) and \(m_d\).  Its Frechet interval is
\[
  L_d(\alpha)=\max\{0,r_d(\alpha)+m_d-1\},\qquad
  U_d(\alpha)=\min\{r_d(\alpha),m_d\}.
\]
For \(t\in[L_d(\alpha),U_d(\alpha)]\), define the selected-mixture odds ratio
with the usual boundary conventions by
\[
  OR_d(t;\alpha)
  =
  \frac{t(1-r_d(\alpha)-m_d+t)}
       {(r_d(\alpha)-t)(m_d-t)}.
\]
Interior zero denominators correspond to \(OR_d=+\infty\), and interior zero
numerators correspond to \(OR_d=0\).  The maintained collider-dependence
restriction is \(OR_d(t;\alpha)\in[\Gamma^{-1},\Gamma]\).

The identified set is the set of target values generated by all finite laws on
\((S(0),S(1),Y(0),Y(1))\) satisfying the restrictions and inducing the observed
law \(P\):
\[
  \Theta_I(P;\Gamma,\kappa)
  =
  \left\{
    \E[Y(1)-Y(0)\mid A]:
    \text{a compatible law satisfying Assumptions~\ref{ass:random-consistency}--\ref{ass:interior}
    exists}
  \right\}.
\]

For literature-comparison statements, write \(q_d\) for an armwise
always-selected share used by the SGJR--Jemiai beta/psi principal-stratum
sensitivity workflow in its binary no-covariate specialization.  The two
armwise shares are jointly attainable by one binary
principal-strata law with the observed selected shares and harmed-stratum budget
if and only if
\[
  (q_1,q_0)\in\mathcal C_\kappa(P)
  :=
  \left\{
    (q_1,q_0)\in(0,1)^2:
    p_1q_1=p_0q_0=\alpha\in\mathcal A_\kappa^+(P)
  \right\}.
\]
This curve is the common-\(\alpha\) frontier.  The named armwise beta/psi
specialization may choose \(q_1\) and \(q_0\) separately; the sharp Lee--Gamma
problem is the restriction of that two-dimensional margin space to
\(\mathcal C_\kappa(P)\).

\paragraph{Locked parameters.}
\begin{verbatim}
qid = pid_collider_bias_sharp.
specialization = v1_lee_gamma_selection.
observable distribution P = the randomized binary-treatment law of
    (D,S,SY), where D in {0,1}, S is the realized post-treatment
    selection/collider indicator, and Y in {0,1} is observed only when S=1.
parameter theta = E[Y(1)-Y(0) | S(1)=S(0)=1], the Lee always-selected
    average treatment effect for the outcome scale on which Y is defined.
identifying restrictions = random assignment and consistency; binary
    principal selection strata A=(1,1), G=(0,1), H=(1,0), N=(0,0);
    a finite reverse-selection budget kappa limiting the harmed stratum H;
    and an arm-specific collider odds-ratio bound Gamma on the association,
    inside each selected arm, between the always-selected stratum A and the
    selected outcome Y(d).
bounding functional = the alpha-profile quadratic selected-mixture
    envelope B_{Gamma,kappa}(P), obtained by varying the always-selected
    share alpha=P(A)>0 over its positive observable/reverse-budget interval
    and solving
    the two arm-specific odds-ratio saturation quadratics for the feasible
    always-selected means.
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Random assignment and consistency]\label{ass:random-consistency}
Treatment \(D\) is independent of \((S(0),S(1),Y(0),Y(1))\), both treatment
arms have positive probability, and observed variables satisfy \(S=S(D)\) and
\(Y=Y(D)\) whenever \(S=1\).
\end{assumption}

\begin{assumption}[Binary selected-outcome support]\label{ass:binary-support}
For each \(d\in\{0,1\}\), \(S(d)\in\{0,1\}\) and \(Y(d)\in\{0,1\}\).  The
observed selected rates and selected means satisfy
\[
  p_d\in(0,1),\qquad m_d\in(0,1),\qquad d\in\{0,1\}.
\]
\end{assumption}

\begin{assumption}[Finite reverse-selection budget]\label{ass:reverse-budget}
For a fixed \(\kappa\in[0,\infty]\), the harmed principal stratum mass
\(h=P(S(0)=1,S(1)=0)\) satisfies \(h\le \kappa p_0\).  Equivalently, admissible
always-selected shares must lie in \(\mathcal A_\kappa(P)\) as defined above,
and the target profile is restricted to \(\mathcal A_\kappa^+(P)\).
\end{assumption}

\begin{assumption}[Finite selected-mixture collider dependence]\label{ass:gamma-mixture}
For a fixed \(\Gamma\in[1,\infty]\), each selected arm \(d\in\{0,1\}\) obeys
\[
  OR_d(t_d;\alpha)\in[\Gamma^{-1},\Gamma]
\]
for its selected-arm \(2\times2\) table with margins \(r_d(\alpha)\) and
\(m_d\).  When \(\Gamma=\infty\), this restriction is interpreted as the
vacuous Frechet restriction \(t_d\in[L_d(\alpha),U_d(\alpha)]\).
\end{assumption}

\begin{assumption}[Nondegenerate interior case]\label{ass:interior}
The selected mixture is in the finite interior regime \(\Gamma\in(1,\infty)\).
The positive alpha profile is a nonempty compact interval
\[
  \mathcal A_\kappa^+(P)=[\alpha_-,\alpha_+]
\]
with \(0<\alpha_-\le \alpha_+\le \min\{p_0,p_1\}\).  For every
\(\alpha\in[\alpha_-,\alpha_+]\) and arm \(d\), the selected-arm feasible set
under Assumption~\ref{ass:gamma-mixture} is nonempty, and
\(r_d(\alpha)\in(0,1)\) for both arms and every
\(\alpha\in\mathcal A_\kappa^+(P)\).  Boundary cases with \(r_d\in\{0,1\}\) or
\(m_d\in\{0,1\}\) are handled separately as degeneracies rather than by the
strict-tightening theorem.
\end{assumption}

\begin{assumption}[Exposed endpoint faces for comparison]\label{ass:exposed-endpoints}
For each endpoint direction \(\ell\in\{-,+\}\) used in the comparison theorem,
the SGJR/JR-induced beta/psi comparator optimizer set and the
Honore--Hu-style no-exclusion endpoint set defined in Section~7 are nonempty.
The comparison regime has \(p_0\ne p_1\), nondegenerate selected mixtures
\(r_d(\alpha)\in(0,1)\) for all \(\alpha\in\mathcal A_\kappa^+(P)\), and
positive one-sided principal strata \(G=p_1-\alpha>0\) and
\(H=p_0-\alpha>0\) at the \((\Gamma,\kappa)\) optimizer.  Whenever a strict
separation conclusion is claimed, the relevant endpoint is locally unique and
is exposed by the stated Frechet or interior odds-ratio face.
\end{assumption}

\section{Estimand-defining functional}
This section gives the computable map from \(P\) to the bound
\(B_{\Gamma,\kappa}(P)\).  For \(r,m\in(0,1)\) and an odds-ratio level
\(\lambda>0\), define
\[
  Q_\lambda(t;r,m)
  =
  t(1-r-m+t)-\lambda(r-t)(m-t).
\]
The unique root of \(Q_\lambda(\cdot;r,m)\) in the Frechet interval
\([\max\{0,r+m-1\},\min\{r,m\}]\) is
\[
  \rho_\lambda(r,m)
  =
  \begin{cases}
    rm, & \lambda=1,\\[0.5em]
    \displaystyle
    \frac{-b_\lambda(r,m)+
      \sqrt{b_\lambda(r,m)^2+4\lambda(1-\lambda)rm}}
      {2(1-\lambda)}, & \lambda\ne 1,
  \end{cases}
\]
where
\[
  b_\lambda(r,m)=1-r-m+\lambda(r+m).
\]
This is an explicit quadratic formula; no latent optimization is hidden in the
definition.  For \(\Gamma<\infty\), monotonicity of the odds ratio in \(t\)
implies
\[
  T_\Gamma(r,m)=
  [\,\rho_{\Gamma^{-1}}(r,m),\rho_{\Gamma}(r,m)\,].
\]
For \(\Gamma=\infty\), set
\[
  T_\infty(r,m)=
  [\,\max\{0,r+m-1\},\min\{r,m\}\,].
\]
If \(r=1\), the selected arm consists only of always-selected units and
\(T_\Gamma(1,m)=\{m\}\) for every \(\Gamma\).

For \(\alpha\in\mathcal A_\kappa^+(P)\), define the armwise feasible
always-selected mean endpoints by
\[
  \underline a_d(\alpha;P,\Gamma)
  =
  \frac{\inf T_\Gamma(r_d(\alpha),m_d)}{r_d(\alpha)},
  \qquad
  \overline a_d(\alpha;P,\Gamma)
  =
  \frac{\sup T_\Gamma(r_d(\alpha),m_d)}{r_d(\alpha)}.
\]
The bounding functional is
\[
  \theta_L(P;\Gamma,\kappa)
  =
  \min_{\alpha\in\mathcal A_\kappa^+(P)}
  \{\underline a_1(\alpha;P,\Gamma)-\overline a_0(\alpha;P,\Gamma)\},
\]
\[
  \theta_U(P;\Gamma,\kappa)
  =
  \max_{\alpha\in\mathcal A_\kappa^+(P)}
  \{\overline a_1(\alpha;P,\Gamma)-\underline a_0(\alpha;P,\Gamma)\}.
\]
Under Assumption~\ref{ass:interior}, the extrema exist by continuity on
a compact interval.  Computationally, this is a one-dimensional explicit
optimization: the decision variable is \(\alpha\in[\alpha_-,\alpha_+]\), the
constraints are the interval endpoints defining \(\mathcal A_\kappa^+(P)\), and
the objective is a closed-form expression made of rational functions and square
roots.  In the finite nondegenerate case, candidate global extrema are
endpoints \(\alpha_-,\alpha_+\) and interior roots of the derivative of the
corresponding quadratic-radical profile; equivalently, they can be obtained by
standard one-dimensional semialgebraic global optimization after squaring the
radicals with the displayed sign constraints.

The same closed-form pieces define the proposal-level armwise comparator used
by Conjecture~\ref{conj:coupling-iff}.  It is motivated by the binary
no-covariate specialization of the Shepherd--Gilbert--Jemiai--Rotnitzky /
Jemiai--Rotnitzky--Shepherd--Gilbert beta/psi principal-stratum sensitivity
workflow, but is defined here as a finite support benchmark: in arm \(d\), the
log-odds sensitivity parameter is
\(\beta_d=\log OR_d\), and the armwise always-selected share
\(q_d=P(A\mid S(d)=1)\) is treated as an arm-specific sensitivity margin unless
a joint principal-strata law is imposed.  For \(q\in(0,1)\) and selected mean
\(m\), write
\[
  \ell_\Gamma(q,m)=\frac{\inf T_\Gamma(q,m)}{q},\qquad
  u_\Gamma(q,m)=\frac{\sup T_\Gamma(q,m)}{q}.
\]
Fix any compact margin rectangle
\(\mathcal R_\varepsilon=[\varepsilon,1-\varepsilon]^2\) that contains
\(\mathcal C_\kappa(P)\) for some \(\varepsilon>0\).  The named
SGJR--Jemiai armwise beta/psi envelope in this binary specialization is the
computable two-dimensional support interval
\[
  \psi_L(P;\Gamma,\varepsilon)
  =
  \min_{(q_1,q_0)\in\mathcal R_\varepsilon}
  \{\ell_\Gamma(q_1,m_1)-u_\Gamma(q_0,m_0)\},
\]
\[
  \psi_U(P;\Gamma,\varepsilon)
  =
  \max_{(q_1,q_0)\in\mathcal R_\varepsilon}
  \{u_\Gamma(q_1,m_1)-\ell_\Gamma(q_0,m_0)\}.
\]
Its variables are the two armwise principal shares \(q_1,q_0\); its constraints
are only the rectangle and the armwise odds-ratio quadratics corresponding to
\(|\beta_d|\le \log\Gamma\).  The proposal-defined binary
Honore--Hu-style no-exclusion support benchmark uses the same finite-table
variables and armwise constraints, but interprets them as no-exclusion marginal
selection tables rather than as a beta/psi principal-stratum sensitivity
workflow.  Its endpoints are
\[
  \eta_L(P;\Gamma,\varepsilon)
  =
  \min_{(q_1,q_0)\in\mathcal R_\varepsilon}
  \{\ell_\Gamma(q_1,m_1)-u_\Gamma(q_0,m_0)\},
\]
\[
  \eta_U(P;\Gamma,\varepsilon)
  =
  \max_{(q_1,q_0)\in\mathcal R_\varepsilon}
  \{u_\Gamma(q_1,m_1)-\ell_\Gamma(q_0,m_0)\}.
\]
Thus \(\eta_L=\psi_L\) and \(\eta_U=\psi_U\) in this binary specialization,
but the labels record two different interpretations of the same larger
no-common-\(\alpha\) support set.  The sharp Lee--Gamma functional
is the same support calculation restricted to the one-dimensional compatibility
curve:
\[
  \theta_L(P;\Gamma,\kappa)
  =
  \min_{(q_1,q_0)\in\mathcal C_\kappa(P)}
  \{\ell_\Gamma(q_1,m_1)-u_\Gamma(q_0,m_0)\},
\]
\[
  \theta_U(P;\Gamma,\kappa)
  =
  \max_{(q_1,q_0)\in\mathcal C_\kappa(P)}
  \{u_\Gamma(q_1,m_1)-\ell_\Gamma(q_0,m_0)\}.
\]
Thus \(\mathcal C_\kappa(P)\), not \(\beta_d=\log OR_d\) by itself, is the
extra object that turns two proposal-defined armwise sensitivity tables into
one sharp always-selected ATE frontier.

For endpoint direction \(U\), let \(\mathcal R_U^*\) and \(\mathcal H_U^*\) be
the nonempty argmax sets of \(\phi_U(q)=u_\Gamma(q_1,m_1)-\ell_\Gamma(q_0,m_0)\)
over the SGJR--Jemiai and Honore--Hu-style rectangles.  For endpoint direction
\(L\), let \(\mathcal R_L^*\) and \(\mathcal H_L^*\) be the argmin sets of
\(\phi_L(q)=\ell_\Gamma(q_1,m_1)-u_\Gamma(q_0,m_0)\).  Define the observable
compatibility gaps by
\[
  \Delta_s^{\mathrm{SGJR}}(P;\Gamma,\kappa)
  =
  \inf_{q\in\mathcal R_s^*}\operatorname{dist}(q,\mathcal C_\kappa(P)),
  \qquad
  \Delta_s^{\mathrm{HH}}(P;\Gamma,\kappa)
  =
  \inf_{q\in\mathcal H_s^*}\operatorname{dist}(q,\mathcal C_\kappa(P)),
\]
for \(s\in\{L,U\}\), using Euclidean distance in the two-dimensional margin
space.  These are computable because the optimizer sets are closed subsets of a
compact rectangle and the objective functions are explicit quadratic-root
maps.

These definitions are the shared inputs for the per-conjecture proof stages.
Conjecture~\ref{conj:lee-gamma-frontier} will test whether
\(B_{\Gamma,\kappa}(P)\) is sharp for the latent always-selected target.
Conjecture~\ref{conj:strict-tightening} will test whether finite \(\Gamma\)
strictly excludes unrestricted Frechet-face endpoint laws except through the
listed compensation or degeneracy cases.  Conjecture~\ref{conj:coupling-iff}
will test whether the compatibility gaps
\(\Delta_s^{\mathrm{SGJR}}\) and \(\Delta_s^{\mathrm{HH}}\) exactly diagnose
equality with the proposal-defined armwise support benchmarks.

\section{Target causal estimand}
The target causal estimand is the always-selected average treatment effect
\[
  \theta
  =
  \E[Y(1)-Y(0)\mid S(1)=S(0)=1]
  =
  \E[Y(1)\mid A]-\E[Y(0)\mid A].
\]
It is a scalar causal parameter of the latent principal stratum \(A\), not an
observed selected-sample contrast.  The selected means \(m_1-m_0\) equal
\(\theta\) only in special cases, such as selected-mixture independence
\(\Gamma=1\).  The proposed partial-identification target is to evaluate where
the identified set lies relative to the computable interval:
\[
  \Theta_I(P;\Gamma,\kappa)
  \quad\text{and}\quad
  [\theta_L(P;\Gamma,\kappa),\theta_U(P;\Gamma,\kappa)],
\]
without treating this display as a point-identification equality unless later
proof stages show that the lower and upper endpoints coincide.

\section{Main theorems}
\begin{proposition}[Partial resolution of Conjecture~\ref{conj:lee-gamma-frontier}]\label{prop:lee-gamma-frontier-partial}
Partial verdict: Assumptions~\ref{ass:random-consistency}--\ref{ass:interior} imply the sharp common-\(\alpha\) frontier displayed in Conjecture~\ref{conj:lee-gamma-frontier}; the additional open-set non-representability assertions relative to external comparator geometries are not confirmed by the finite-table assumptions alone.
\end{proposition}

The confirmed content is the sharp common-\(\alpha\) frontier, endpoint
attainment by a four-stratum law, and the endpoint optimizer
characterization.  The proof does not define the cited external procedures as
mathematical support functions on the same input space, so it does not
establish an open-set non-representability theorem against them.

\begin{theorem}[Strict finite-\(\Gamma\) tightening for exposed Frechet endpoints]\label{thm:strict-tightening}
Conjecture~\ref{conj:strict-tightening} is confirmed as a directional strict-tightening statement: for any endpoint direction whose unrestricted optimizer set is supported only on nondegenerate Frechet equality faces, the finite-\(\Gamma\) endpoint is strictly inside the corresponding unrestricted endpoint, and endpoint equality can occur only through a finite-\(\Gamma\)-compatible unrestricted optimizer profile.
\end{theorem}

The unrestricted bidirectional principal-strata bound is the same
alpha-profile calculation with the armwise selected-mixture odds-ratio
constraint removed.  The new comparison is pointwise nesting plus strict
exclusion of exposed nondegenerate Frechet faces by any finite collider
odds-ratio budget.

\begin{theorem}[Compatibility-gap characterization]\label{thm:coupling-iff-confirmed}
Conjecture 3 is confirmed: zero compatibility gap is necessary and sufficient for equality with the SGJR/JR armwise beta/psi endpoint, and is necessary (indeed sufficient in this binary specialization) for equality with the proposal-defined Honore--Hu-style no-exclusion endpoint; positive gap gives strict separation in the appropriate endpoint direction.
\end{theorem}

The theorem records a set-restriction fact: adding the common-\(\alpha\) and
harmed-budget compatibility equations can only shrink the proposal-defined
armwise support interval, and it shrinks it strictly whenever the exposed
benchmark endpoint set misses the compatibility curve.

\section{Interpretation}
\paragraph{Conjecture 1.}
The confirmed content is a sharp bound for the causal target
\(\theta=\E[Y(1)-Y(0)\mid A]\), not a point-identification statement.  The
observable law \(P\) identifies \(p_d\) and \(m_d\), but not the latent
always-selected share \(\alpha\) nor the always-selected means.  The theorem
reduces the latent problem to a one-dimensional computable profile.  For each
candidate \(\alpha\), the two selected arms are ordinary \(2\times2\) tables
with known margins.  The odds-ratio sensitivity bound cuts out a closed
interval of feasible always-selected means in each arm, and the common
\(\alpha\) and harmed-budget restrictions say which two armwise tables can be
glued into one four-stratum principal-strata law.

\paragraph{Conjecture 2.}
The unrestricted bidirectional principal-strata bound is the same alpha-profile
calculation with the armwise selected-mixture odds-ratio constraint removed.
Removing that constraint lets an endpoint place the always-selected type and
the selected outcome on a Frechet equality face inside at least one selected
arm.  Such a face is an extreme selected-arm table with perfect positive or
negative association between always-selected membership and the selected
outcome.  A finite collider odds-ratio budget excludes that perfect association
whenever the margins are nondegenerate.  Therefore the finite-\(\Gamma\)
interval cannot keep an unrestricted endpoint whose every optimizing profile
depends on such a face.

The qualification about profile-level compensation is not a new assumption.  It
is the only algebraic route by which endpoint equality can survive: the
common-alpha curve may contain another unrestricted optimizer whose
selected-arm active cells are not on the forbidden Frechet face and already
obey the finite odds-ratio budget.  Degenerate selected mixtures, degenerate
outcome margins, and Lee-monotonicity boundary cases are listed separately
because the odds ratio ceases to exclude the Frechet face in the same way.

\paragraph{Conjecture 3.}
The theorem says that the comparison with the SGJR/JR-inspired beta/psi
benchmark is not about whether a selected-arm log-odds parameter exists.  Such
a parameter exists arm by arm by construction.  The issue is whether the two
armwise endpoint tables can be coupled into one principal-strata law with a
single always-selected share \(\alpha\) and the harmed-budget restriction
\(p_0-\alpha\le\kappa p_0\).  The observable gap
\(\Delta_\ell^{\mathrm{SGJR}}\) measures exactly that coupling failure at the
endpoint optimizer set.  A zero gap means an armwise beta/psi endpoint is
already a valid Lee--Gamma endpoint; a positive gap means the armwise endpoint
sits outside the one-dimensional common-\(\alpha\) frontier, so the Lee--Gamma
endpoint is strictly inside the larger armwise benchmark.

The same logic applies to the proposal-defined binary Honore--Hu-style
no-exclusion support benchmark because Section~7 defines it through the same
finite armwise tables and the same compact margin rectangle.  The theorem
therefore records a set-restriction fact: adding the common-\(\alpha\) and
harmed-budget compatibility equations can only shrink the support interval, and
it shrinks it strictly whenever the exposed benchmark endpoint set misses the
compatibility curve.

\paragraph{Synthesis.}
Together, these interpretations return to the motivating conjectures: the
alpha-profile is a one-dimensional computable profile; finite \(\Gamma\)
excludes perfect selected-arm association whenever the margins are
nondegenerate; and the issue in armwise comparator geometries is whether the
two armwise endpoint tables can be coupled into one principal-strata law with a
single always-selected share \(\alpha\).

\section{Step-by-step proof}
\subsection*{Supporting lemmas}
\begin{theorem}[Theorem 1: Armwise quadratic selected-mixture envelope]\label{thm:arm-quadratic}
Under Assumptions~\ref{ass:random-consistency}, \ref{ass:binary-support}, and \ref{ass:gamma-mixture}, fix an arm \(d\) and an admissible \(\alpha\) with \(r=r_d(\alpha)\in(0,1)\) and \(m=m_d\in(0,1)\).  The feasible values of \(t=P(A,Y(d)=1\mid S(d)=1)\) form a closed interval obtained by intersecting the Frechet interval with the two odds-ratio quadratic inequalities
\[
  t(1-r-m+t)\le \Gamma(r-t)(m-t),
  \qquad
  \Gamma t(1-r-m+t)\ge (r-t)(m-t).
\]
Equivalently, the two possible active endpoint equations are quadratic polynomials in \(t\).  The feasible always-selected mean in arm \(d\) is the corresponding interval \(a_d=t/r\).
\end{theorem}
\begin{proof}
By randomization and consistency, the selected-arm margins \(r=r_d(\alpha)=P(A\mid S(d)=1)\) and \(m=m_d=P(Y(d)=1\mid S(d)=1)\) are the margins of the selected-arm binary table with row variable \(A\) and column variable \(Y(d)=1\).  If \(t=P(A,Y(d)=1\mid S(d)=1)\), the four cell probabilities are
\[
  t,\qquad r-t,\qquad m-t,\qquad 1-r-m+t.
\]
Nonnegativity of these four cells is equivalent to the Frechet interval
\[
  \max\{0,r+m-1\}\le t\le \min\{r,m\}.
\]
This interval is closed.  On its interior, the selected-mixture odds ratio is
\[
  OR(t;r,m)=\frac{t(1-r-m+t)}{(r-t)(m-t)}.
\]
Because all cells are nonnegative on the Frechet interval, the bound \(OR(t;r,m)\le \Gamma\) is equivalent to
\[
  t(1-r-m+t)\le \Gamma(r-t)(m-t),
\]
and the bound \(OR(t;r,m)\ge \Gamma^{-1}\) is equivalent to
\[
  \Gamma t(1-r-m+t)\ge (r-t)(m-t).
\]
The same inequalities give the correct closed boundary convention when a numerator or denominator cell is zero.  Each displayed boundary equality is a quadratic polynomial in \(t\), since both sides are products of affine functions of \(t\).  The feasible \(t\)-set is therefore the intersection of one closed Frechet interval and two closed quadratic sublevel/superlevel sets, hence is closed.  It is an interval because, on the open Frechet interval, the derivative of the log odds ratio is
\[
  \frac{1}{t}+\frac{1}{1-r-m+t}+\frac{1}{r-t}+\frac{1}{m-t}>0,
\]
so \(OR(t;r,m)\) is strictly increasing from the lower Frechet boundary to the upper Frechet boundary.  Intersecting an interval with \([\Gamma^{-1},\Gamma]\) under a monotone continuous map gives a closed interval, possibly a singleton.  Finally, because \(r\in(0,1)\), division by \(r\) is order-preserving, and the feasible always-selected mean is exactly the image interval \(a_d=t/r\).
\end{proof}

\subsubsection*{Proof of Conjecture 1}
We prove the sharp-frontier and endpoint-attainment parts of
Proposition~\ref{prop:lee-gamma-frontier-partial}.  By
Assumption~\ref{ass:random-consistency}, the observed selected share and
selected mean in arm \(d\) equal \(p_d=P(S(d)=1)\) and
\(m_d=P(Y(d)=1\mid S(d)=1)\).  By Assumption~\ref{ass:binary-support}, these
quantities lie in \((0,1)\).

First take any compatible full law.  Let
\(\alpha=P(A)=P(S(0)=1,S(1)=1)\).  The identities
\[
  P(G)=p_1-\alpha,\qquad P(H)=p_0-\alpha,\qquad P(N)=1-p_0-p_1+\alpha
\]
follow from the four principal strata and the definitions of \(p_0,p_1\).
Nonnegativity of these masses and Assumption~\ref{ass:reverse-budget} imply
\(\alpha\in\mathcal A_\kappa^+(P)\).  Since \(S(d)=1\) consists of the
always-selected stratum plus the one-sided stratum selected in arm \(d\),
\[
  P(A\mid S(d)=1)=r_d(\alpha)=\alpha/p_d .
\]
Let \(t_d=P(A,Y(d)=1\mid S(d)=1)\).  Assumption~\ref{ass:gamma-mixture} and
Theorem~\ref{thm:arm-quadratic} imply
\[
  \underline a_d(\alpha)\le
  \E[Y(d)\mid A]=\frac{t_d}{r_d(\alpha)}
  \le \overline a_d(\alpha).
\]
Therefore every compatible law satisfies, for its own \(\alpha\),
\[
  \underline a_1(\alpha)-\overline a_0(\alpha)
  \le
  \theta
  \le
  \overline a_1(\alpha)-\underline a_0(\alpha).
\]
Taking the infimum and supremum over
\(\alpha\in\mathcal A_\kappa^+(P)\) gives the outer inclusion
\[
  \Theta_I(P;\Gamma,\kappa)
  \subseteq
  \left[
    \inf_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\underline a_1(\alpha)-\overline a_0(\alpha)\},
    \sup_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\overline a_1(\alpha)-\underline a_0(\alpha)\}
  \right].
\]

We next prove attainability.  Fix \(\alpha\in\mathcal A_\kappa^+(P)\).  Set
\[
  g=p_1-\alpha,\qquad h=p_0-\alpha,\qquad n=1-p_0-p_1+\alpha .
\]
These are nonnegative by the definition of \(\mathcal A_\kappa^+(P)\), and
\(h\le \kappa p_0\) by Assumption~\ref{ass:reverse-budget}.  Choose any
\[
  t_d\in
  [r_d(\alpha)\underline a_d(\alpha),
   r_d(\alpha)\overline a_d(\alpha)]
\]
for \(d=0,1\).  By Theorem~\ref{thm:arm-quadratic}, the four selected-arm cell
probabilities are nonnegative and obey the odds-ratio bound.  Put
\[
  a_d=t_d/r_d(\alpha).
\]
On the always-selected stratum \(A\), assign any binary joint distribution for
\((Y(0),Y(1))\) with marginal means \(a_0\) and \(a_1\); such a joint
distribution exists because every pair of Bernoulli marginals has a Frechet
coupling.  On \(G\), choose \(Y(1)\) to have mean
\[
  \frac{m_1-t_1}{1-r_1(\alpha)},
\]
and choose \(Y(0)\) arbitrarily.  On \(H\), choose \(Y(0)\) to have mean
\[
  \frac{m_0-t_0}{1-r_0(\alpha)},
\]
and choose \(Y(1)\) arbitrarily.  On \(N\), choose both potential outcomes
arbitrarily.  The displayed means for \(G\) and \(H\) lie in \([0,1]\) because
the selected-arm Frechet inequalities hold.  Assumption~\ref{ass:interior}
ensures \(r_d(\alpha)\in(0,1)\), so the divisions by
\(1-r_d(\alpha)\) are legitimate.

The constructed law has principal-stratum masses \((\alpha,g,h,n)\), hence it
reproduces \(p_0,p_1\).  Its selected-arm means are
\[
  r_d(\alpha)a_d+\{1-r_d(\alpha)\}
  \frac{m_d-t_d}{1-r_d(\alpha)}
  =
  t_d+(m_d-t_d)
  =
  m_d,
\]
so it reproduces the observable law \(P\) on \((D,S,SY)\).  Its odds-ratio
restriction is exactly the selected-arm restriction used to choose \(t_d\), and
its target value is \(a_1-a_0\).

For this fixed \(\alpha\), the set of attainable target values is therefore
\[
  [\underline a_1(\alpha),\overline a_1(\alpha)]
  -
  [\underline a_0(\alpha),\overline a_0(\alpha)]
  =
  [\underline a_1(\alpha)-\overline a_0(\alpha),
   \overline a_1(\alpha)-\underline a_0(\alpha)].
\]
The union of these intervals over \(\alpha\in\mathcal A_\kappa^+(P)\) is itself
an interval.  To see this, suppose a real number \(y\) is missed by the union.
Then for each \(\alpha\), either the local upper endpoint is below \(y\) or the
local lower endpoint is above \(y\).  The two alternatives define disjoint open
sets in the connected compact interval \(\mathcal A_\kappa^+(P)\).  Continuity
of the quadratic-root endpoints rules out a separation between any two
attained values on opposite sides of \(y\).  Hence the union is exactly the
global interval whose endpoints are the displayed infimum and supremum.

Under Assumption~\ref{ass:interior}, the endpoint functions are continuous
quadratic-root functions of \(\alpha\) on a compact interval, so the infimum
and supremum are attained.  In the finite interior case \(\Gamma\in(1,\infty)\),
Theorem~\ref{thm:arm-quadratic} places each armwise endpoint on one of the two
active odds-ratio equalities \(OR_d=\Gamma^{-1}\) or \(OR_d=\Gamma\), rather
than on a degenerate Frechet face.  Therefore each global endpoint is attained
by the four-stratum construction above with the appropriate selected-arm
tables saturating the relevant odds-ratio boundary.  If the optimizing
\(\alpha\) is not \(\alpha_-\) or \(\alpha_+\), Fermat's rule applies to the
active quadratic-radical profile and the derivative of that profile is zero.
This proves the sharp common-\(\alpha\) frontier and the endpoint
characterization.

The remaining literature non-representability clause is not proved by this
argument.  The proof has only used the finite response-type law, the
common-\(\alpha\) curve, the harmed-budget inequality, and the selected-arm
odds-ratio faces.  It does not define the cited external procedures as
mathematical support functions on the same input space, so it cannot establish
an open-set non-representability theorem against them.

\subsubsection*{Proof of Conjecture 2}
\begin{proof}
All extrema below are over the compact set \(\mathcal A_\kappa^+(P)\) from
Assumption~\ref{ass:interior}.  By Theorem~\ref{thm:arm-quadratic}, for each
arm \(d\) and each admissible \(\alpha\), the finite-\(\Gamma\) feasible
selected-cell interval is
\[
  T_\Gamma(r_d(\alpha),m_d)
  =
  [\,\rho_{\Gamma^{-1}}(r_d(\alpha),m_d),\rho_\Gamma(r_d(\alpha),m_d)\,],
\]
while the unrestricted interval is
\[
  T_\infty(r_d(\alpha),m_d)
  =
  [\,L_d(\alpha),U_d(\alpha)\,].
\]
Assumption~\ref{ass:gamma-mixture} with finite \(\Gamma\) imposes the
additional restriction \(OR_d(t;\alpha)\in[\Gamma^{-1},\Gamma]\).  Hence
\[
  T_\Gamma(r_d(\alpha),m_d)\subseteq T_\infty(r_d(\alpha),m_d).
\]
Since \(r_d(\alpha)\in(0,1)\) by Assumption~\ref{ass:interior}, division by
\(r_d(\alpha)\) is order-preserving.  Therefore, for each \(\alpha\),
\[
  \underline a_d(\alpha;P,\infty)
  \le
  \underline a_d(\alpha;P,\Gamma)
  \le
  \overline a_d(\alpha;P,\Gamma)
  \le
  \overline a_d(\alpha;P,\infty).
\]
Combining these armwise inequalities gives the pointwise lower-endpoint
inequality
\[
  F_L^\infty(\alpha)
  =
  \underline a_1(\alpha;P,\infty)-\overline a_0(\alpha;P,\infty)
  \le
  \underline a_1(\alpha;P,\Gamma)-\overline a_0(\alpha;P,\Gamma)
  =
  F_L^\Gamma(\alpha),
\]
and the pointwise upper-endpoint inequality
\[
  F_U^\Gamma(\alpha)
  =
  \overline a_1(\alpha;P,\Gamma)-\underline a_0(\alpha;P,\Gamma)
  \le
  \overline a_1(\alpha;P,\infty)-\underline a_0(\alpha;P,\infty)
  =
  F_U^\infty(\alpha).
\]
Taking the minimum of the first display and the maximum of the second display
over \(\mathcal A_\kappa^+(P)\) yields
\[
  \theta_L^\infty\le \theta_L^\Gamma,
  \qquad
  \theta_U^\Gamma\le \theta_U^\infty.
\]
By the definitions of the finite-\(\Gamma\) alpha-profile interval and its
unrestricted \(\Gamma=\infty\) analogue, this gives
\[
  [\theta_L^\Gamma,\theta_U^\Gamma]\subseteq[\theta_L^\infty,\theta_U^\infty].
\]

It remains to prove strictness.  Consider the lower endpoint.  Let
\(\alpha^\star\in\arg\min F_L^\infty\).  The unrestricted lower endpoint uses
\(t_1=L_1(\alpha^\star)\) in arm \(1\) and \(t_0=U_0(\alpha^\star)\) in arm
\(0\).  If \(t_1=L_1(\alpha^\star)\) is on a nondegenerate Frechet face with
\(0<L_1(\alpha^\star)<U_1(\alpha^\star)<1\), then the selected-arm table has
\(x_{00}=1-r_1-m_1+L_1=0\) and the other three active cells are nonnegative
with the denominator cells positive.  Thus \(OR_1=0<\Gamma^{-1}\), so
\(L_1(\alpha^\star)\notin T_\Gamma(r_1(\alpha^\star),m_1)\).  Monotonicity of
the odds ratio in Theorem~\ref{thm:arm-quadratic} implies
\[
  \underline a_1(\alpha^\star;P,\Gamma)
  >
  \underline a_1(\alpha^\star;P,\infty).
\]
If instead \(t_0=U_0(\alpha^\star)\) is on a nondegenerate Frechet face, then
one denominator cell in the arm \(0\) table is zero, so
\(OR_0=+\infty>\Gamma\), and
\[
  \overline a_0(\alpha^\star;P,\Gamma)
  <
  \overline a_0(\alpha^\star;P,\infty).
\]
Either active nondegenerate face therefore gives
\[
  F_L^\Gamma(\alpha^\star)>F_L^\infty(\alpha^\star)=\theta_L^\infty.
\]

Suppose, toward contradiction, that \(\theta_L^\Gamma=\theta_L^\infty\).  By
compactness and continuity, choose \(\tilde\alpha\in\arg\min F_L^\Gamma\).
Then
\[
  \theta_L^\infty
  =
  F_L^\Gamma(\tilde\alpha)
  \ge
  F_L^\infty(\tilde\alpha)
  \ge
  \theta_L^\infty.
\]
Both inequalities must be equalities.  Hence
\(\tilde\alpha\in\arg\min F_L^\infty\) and
\(F_L^\Gamma(\tilde\alpha)=F_L^\infty(\tilde\alpha)\), contradicting the
strict inequality just proved for every unrestricted lower-endpoint optimizer
under the stated hypothesis.  Therefore \(\theta_L^\infty<\theta_L^\Gamma\).

The upper endpoint is identical with the inequalities reversed.  Let
\(\alpha^\star\in\arg\max F_U^\infty\).  The unrestricted upper endpoint uses
\(t_1=U_1(\alpha^\star)\) in arm \(1\) and \(t_0=L_0(\alpha^\star)\) in arm
\(0\).  A nondegenerate upper face in arm \(1\) has \(OR_1=+\infty\) and forces
\[
  \overline a_1(\alpha^\star;P,\Gamma)
  <
  \overline a_1(\alpha^\star;P,\infty),
\]
whereas a nondegenerate lower face in arm \(0\) has \(OR_0=0\) and forces
\[
  \underline a_0(\alpha^\star;P,\Gamma)
  >
  \underline a_0(\alpha^\star;P,\infty).
\]
In either case \(F_U^\Gamma(\alpha^\star)<F_U^\infty(\alpha^\star)=\theta_U^\infty\).
If \(\theta_U^\Gamma=\theta_U^\infty\), an optimizer
\(\tilde\alpha\in\arg\max F_U^\Gamma\) would satisfy
\[
  \theta_U^\infty
  =
  F_U^\Gamma(\tilde\alpha)
  \le
  F_U^\infty(\tilde\alpha)
  \le
  \theta_U^\infty,
\]
so \(\tilde\alpha\in\arg\max F_U^\infty\) and
\(F_U^\Gamma(\tilde\alpha)=F_U^\infty(\tilde\alpha)\), again contradicting
strict exclusion of the nondegenerate Frechet face at every unrestricted
upper-endpoint optimizer.  Therefore \(\theta_U^\Gamma<\theta_U^\infty\).

The profile-compensation clause follows from the same contradiction argument.
If an endpoint equality holds in the interior regime, the finite-\(\Gamma\)
optimizer \(\tilde\alpha\) must also be an unrestricted optimizer and must
satisfy equality in the pointwise nesting inequality.  Equality in that nesting
means the active selected-arm cells used by the endpoint all belong to
\(T_\Gamma(r_d(\tilde\alpha),m_d)\), equivalently they obey the
finite-\(\Gamma\) odds-ratio inequalities.  Thus any equality not explained by
reusing the original exposed Frechet-face optimizer must be explained by a
different positive alpha profile that reproduces the unrestricted endpoint
while remaining finite-\(\Gamma\)-compatible.
\end{proof}

\subsubsection*{Proof of Conjecture 3}
\begin{proof}
Write
\[
  C=\mathcal C_\kappa(P)
\]
for the common-\(\alpha\) compatibility curve and write \(R=\mathcal R_\varepsilon\)
for the compact SGJR/JR margin rectangle from Section~7.  By the definition of
\(R\), \(C\subset R\).  By Assumption~\ref{ass:interior},
\(\mathcal A_\kappa^+(P)\) is compact and \(r_d(\alpha)\in(0,1)\) on the
profile.  By Theorem~\ref{thm:arm-quadratic} and the explicit Section~7 formula
for \(\ell_\Gamma\) and \(u_\Gamma\), the endpoint maps are continuous on the
compact rectangle used by the comparison theorem.  Hence all benchmark and
restricted support extrema below are attained.

For the upper endpoint define
\[
  F_+(q_1,q_0)=u_\Gamma(q_1,m_1)-\ell_\Gamma(q_0,m_0),
\]
and for the lower endpoint define
\[
  F_-(q_1,q_0)=\ell_\Gamma(q_1,m_1)-u_\Gamma(q_0,m_0).
\]
The Section~7 definitions give
\[
  v_+^{\mathrm{SGJR}}=\max_{q\in R}F_+(q),\qquad
  b_+=\max_{q\in C}F_+(q),
\]
and
\[
  v_-^{\mathrm{SGJR}}=\min_{q\in R}F_-(q),\qquad
  b_-=\min_{q\in C}F_-(q).
\]
Let \(R_+^\star=\arg\max_{q\in R}F_+(q)\) and
\(R_-^\star=\arg\min_{q\in R}F_-(q)\).  These sets are nonempty compact sets by
Assumption~\ref{ass:exposed-endpoints} and continuity.  The compatibility gaps
are
\[
  \Delta_+^{\mathrm{SGJR}}=\inf_{q\in R_+^\star}\operatorname{dist}(q,C),
  \qquad
  \Delta_-^{\mathrm{SGJR}}=\inf_{q\in R_-^\star}\operatorname{dist}(q,C).
\]
Because \(R_\ell^\star\) and \(C\) are compact,
\(\Delta_\ell^{\mathrm{SGJR}}=0\) if and only if
\(R_\ell^\star\cap C\ne\varnothing\).

Consider \(\ell=+\).  Since \(C\subset R\),
\[
  b_+=\max_C F_+\le \max_R F_+=v_+^{\mathrm{SGJR}}.
\]
If \(\Delta_+^{\mathrm{SGJR}}=0\), choose \(q^\star\in R_+^\star\cap C\).
Then
\[
  b_+\ge F_+(q^\star)=v_+^{\mathrm{SGJR}},
\]
so \(b_+=v_+^{\mathrm{SGJR}}\).  Conversely, if
\(b_+=v_+^{\mathrm{SGJR}}\), choose a restricted maximizer \(\tilde q\in C\).
Then
\[
  F_+(\tilde q)=b_+=v_+^{\mathrm{SGJR}},
\]
so \(\tilde q\in R_+^\star\cap C\), and therefore
\(\Delta_+^{\mathrm{SGJR}}=0\).  The strict statement follows by
contraposition: if \(\Delta_+^{\mathrm{SGJR}}>0\), equality is impossible, and
the subset inequality above sharpens to
\[
  b_+<v_+^{\mathrm{SGJR}}.
\]

The lower endpoint is the same argument with the order reversed.  Because
\(C\subset R\),
\[
  v_-^{\mathrm{SGJR}}=\min_R F_-\le \min_C F_-=b_-.
\]
If \(\Delta_-^{\mathrm{SGJR}}=0\), choose \(q^\star\in R_-^\star\cap C\),
giving
\[
  b_-\le F_-(q^\star)=v_-^{\mathrm{SGJR}}.
\]
Together with \(v_-^{\mathrm{SGJR}}\le b_-\), this gives equality.
Conversely, if \(b_-=v_-^{\mathrm{SGJR}}\), a restricted minimizer
\(\tilde q\in C\) also minimizes \(F_-\) over \(R\), so
\(R_-^\star\cap C\ne\varnothing\) and \(\Delta_-^{\mathrm{SGJR}}=0\).  If
\(\Delta_-^{\mathrm{SGJR}}>0\), equality is impossible and hence
\[
  v_-^{\mathrm{SGJR}}<b_-.
\]

For the Honore--Hu-style benchmark, let \(H_+^\star\) and \(H_-^\star\) be the
corresponding Section~7 endpoint optimizer sets.  In the binary no-covariate
specialization defined in Section~7, the HH feasible support set uses the same
compact armwise rectangle \(R\) and the same objective functions \(F_+\) and
\(F_-\), with a different interpretation of the armwise tables.  Therefore the
same subset and optimizer-intersection proof gives the only-if implication
claimed in the conjecture, and in this binary specialization also gives the
converse.  Under local uniqueness and strict exposure, \(H_\ell^\star\) is
locally stable as an exposed endpoint face.  If \(\Delta_\ell^{\mathrm{HH}}>0\),
the endpoint optimizer set misses \(C\); the equality argument above cannot
occur, so the restricted support value is strictly inside the HH benchmark in
the lower or upper direction as displayed in the theorem.
\end{proof}

\section{Sanity checks}
\paragraph{Conjecture 1 witness.}
At the witness in the conjecture, \(p_1=0.6\), \(p_0=0.5\), and
\(\alpha=0.3\).  Hence \(g=0.3\), \(h=0.2\), and
\(n=1-0.6-0.5+0.3=0.2\), all nonnegative, and the harmed budget is saturated:
\[
  h=0.2=\kappa p_0=0.5\cdot 0.5 .
\]
The selected-arm always shares are \(r_1=0.3/0.6=0.5\) and
\(r_0=0.3/0.5=0.6\).  With \(m_1=0.5\), the two active odds-ratio roots are
\(\underline t_1=1/6\) and \(\overline t_1=1/3\).  With \(m_0=0.4\), the
corresponding roots are
\[
  \underline t_0=(-1+\sqrt{3.88})/6,\qquad
  \overline t_0=(4-\sqrt{4.48})/6 .
\]
Thus the local lower and upper ATE endpoints are
\[
  \frac{1/6}{0.5}-\frac{(4-\sqrt{4.48})/6}{0.6}
  \approx -0.190,
  \qquad
  \frac{1/3}{0.5}-\frac{(-1+\sqrt{3.88})/6}{0.6}
  \approx 0.397 .
\]
This matches the proposal's local interval and confirms that the active cells
are interior odds-ratio faces rather than Lee tail-trimming faces.

\paragraph{Conjecture 2: no finite odds-ratio restriction.}
When \(\Gamma=\infty\), Assumption~\ref{ass:gamma-mixture} reduces to the
Frechet restriction \(T_\infty(r,m)=[L(r,m),U(r,m)]\).  The pointwise nesting
inequalities become equalities for every \(\alpha\), so
\[
  F_L^\infty(\alpha)=F_L^\Gamma(\alpha),
  \qquad
  F_U^\infty(\alpha)=F_U^\Gamma(\alpha)
\]
after interpreting \(\Gamma=\infty\).  Hence the finite-\(\Gamma\) strictness
conclusion disappears exactly when the odds-ratio budget is removed, as it
should.

\paragraph{Conjecture 2: Lee monotonicity boundary.}
If the reverse-selection budget collapses to the Lee monotonicity face \(H=0\),
then the alpha profile can be forced to \(\alpha=p_0\) in the usual case
\(p_1\ge p_0\).  If the selected-arm active table at that profile is already
compatible with \(OR_d\in[\Gamma^{-1},\Gamma]\), the finite-\(\Gamma\) and
unrestricted endpoint values coincide at that boundary.  This is not a
contradiction of the theorem because the strict theorem assumes the interior
nondegenerate regime and excludes equality only when every unrestricted
endpoint optimizer depends on a nondegenerate Frechet equality face that finite
\(\Gamma\) rules out.

\paragraph{Conjecture 3: selected-mixture independence boundary.}
At the boundary \(\Gamma=1\), the selected-mixture odds-ratio restriction
forces \(OR_d=1\) in each selected arm.  The armwise quadratic endpoint in
Theorem~\ref{thm:arm-quadratic} collapses to the independent table
\(t_d=q_dm_d\), so
\[
  \ell_1(q_d,m_d)=u_1(q_d,m_d)=m_d.
\]
Therefore
\[
  F_+(q_1,q_0)=F_-(q_1,q_0)=m_1-m_0
\]
for every benchmark margin pair \(q\) and for every
\(q\in\mathcal C_\kappa(P)\).  Hence
\[
  b_-(P;1,\kappa)=b_+(P;1,\kappa)=v_-^{\mathrm{SGJR}}(P;1)=v_+^{\mathrm{SGJR}}(P;1)=m_1-m_0,
\]
and the same equality holds for the HH-style benchmark.  The entire benchmark
rectangle is an optimizer set, so it intersects \(\mathcal C_\kappa(P)\)
whenever the alpha profile is nonempty, giving
\(\Delta_\ell^{\mathrm{SGJR}}=\Delta_\ell^{\mathrm{HH}}=0\).  This recovers
the known selected-mixture independence corner: armwise and coupled support
calculations all reduce to the observed selected mean contrast.

\section{Counterexample or minimality check}\label{sec:counterexample}
\subsubsection*{Conjecture 1}
\paragraph{Refutation attempt before positive proof.}
The required refutation primitive is the finite binary response-type LP.  Fix
an admissible \(\alpha\in\mathcal A_\kappa^+(P)\).  The principal-stratum
masses are forced by the observed selected shares:
\[
  P(A)=\alpha,\qquad P(G)=p_1-\alpha,\qquad P(H)=p_0-\alpha,\qquad P(N)=1-p_0-p_1+\alpha .
\]
Assumptions~\ref{ass:random-consistency}, \ref{ass:binary-support}, and
\ref{ass:reverse-budget} make these masses nonnegative and impose
\(p_0-\alpha\le \kappa p_0\).  Conditional on \(S(d)=1\), the selected-arm LP
has the four cells
\[
  t_d,\qquad r_d(\alpha)-t_d,\qquad m_d-t_d,\qquad
  1-r_d(\alpha)-m_d+t_d ,
\]
and Assumption~\ref{ass:gamma-mixture} adds the two quadratic inequalities in
Theorem~\ref{thm:arm-quadratic}.  Thus the LP feasible set at fixed \(\alpha\)
is exactly
\[
  t_1\in[\underline t_1(\alpha),\overline t_1(\alpha)],
  \qquad
  t_0\in[\underline t_0(\alpha),\overline t_0(\alpha)],
\]
where \(\underline t_d(\alpha)=r_d(\alpha)\underline a_d(\alpha)\) and
\(\overline t_d(\alpha)=r_d(\alpha)\overline a_d(\alpha)\).  The objective is
\[
  \theta(t_1,t_0;\alpha)
  =
  \frac{t_1}{r_1(\alpha)}-\frac{t_0}{r_0(\alpha)} .
\]
The vertex enumeration is therefore exhaustive: the minimum is attained at
\((\underline t_1(\alpha),\overline t_0(\alpha))\) and the maximum is attained
at \((\overline t_1(\alpha),\underline t_0(\alpha))\).  No fixed-\(\alpha\)
response-type vertex lies outside the conjectured local interval.

At the concrete witness stated in the conjecture,
\[
  r_1(0.3)=0.5,\qquad r_0(0.3)=0.6.
\]
The active roots are
\[
  \underline t_1=1/6,\quad \overline t_1=1/3,\quad
  \underline t_0=(-1+\sqrt{3.88})/6\approx 0.161629,\quad
  \overline t_0=(4-\sqrt{4.48})/6\approx 0.313900 .
\]
The four objective values at the fixed-\(\alpha\) vertices are approximately
\[
  -0.189833,\qquad 0.063952,\qquad 0.143500,\qquad 0.397286 .
\]
Hence the displayed witness does not refute the sharp common-\(\alpha\)
frontier; it realizes the local interval claimed in the conjecture, with both
one-sided strata positive.  The primitive also does not prove the final
open-set non-representability sentence, because the named comparator geometries
are not encoded in the finite-table LP as explicit feasible sets or support
functions.  The honest outcome is therefore a partial verdict: the sharp
frontier is proved below, while the external-comparator non-equivalence claim
remains a definition-level gap rather than a counterexample.

\paragraph{Minimality check after proof.}
The common-\(\alpha\) restriction is necessary for sharpness of the stated
frontier.  If it is dropped, one can choose armwise always-selected shares
\(q_1\) and \(q_0\) independently.  At the witness, the sharp law uses
\(q_1=r_1=0.5\) and \(q_0=r_0=0.6\), which satisfy the compatibility equality
\[
  p_1q_1=0.6\cdot 0.5=0.3
  =
  0.5\cdot 0.6=p_0q_0 .
\]
If instead a comparator selects \(q_1=0.5\) and \(q_0=0.5\), both armwise
selected tables can still be parameterized by log odds ratios, but
\[
  p_1q_1=0.30\ne 0.25=p_0q_0 .
\]
No single principal-strata law can have two different masses for the same
always-selected stratum \(A\).  This is the minimal obstruction behind the
common-\(\alpha\) frontier: armwise beta tables are not enough; the selected-arm
shares must glue through one latent mass \(\alpha\) and must also obey
\(p_0-\alpha\le \kappa p_0\).

\subsubsection*{Conjecture 2}
\paragraph{Refutation attempt before proof.}
I used the two-strata selected-arm response-type enumeration required for the
partial-identification refutation primitive.  Fix an admissible profile
\(\alpha\), an arm \(d\), and write \(r=r_d(\alpha)\), \(m=m_d\).  The latent
selected-arm table has four cells
\[
  x_{11}=t,\qquad x_{10}=r-t,\qquad x_{01}=m-t,\qquad x_{00}=1-r-m+t,
\]
with \(t\in[L_d(\alpha),U_d(\alpha)]\).  The unrestricted \(\Gamma=\infty\)
vertices are \(t=L_d(\alpha)\) and \(t=U_d(\alpha)\).  On a nondegenerate face
\(0<L_d(\alpha)<U_d(\alpha)<1\), the lower vertex satisfies \(x_{00}=0\) and
therefore \(OR_d=0\), while the upper vertex sets one denominator cell to zero
and therefore \(OR_d=+\infty\).  Both violate
\(OR_d\in[\Gamma^{-1},\Gamma]\) for every finite \(\Gamma\in(1,\infty)\).

The only remaining way for this enumeration to refute the conjecture would be
a profile \(\tilde\alpha\) whose finite-\(\Gamma\) active table has the same
global lower or upper ATE value as the unrestricted endpoint even though the
Frechet-face optimizer is excluded.  The pointwise inequalities proved below
rule this out unless \(\tilde\alpha\) is itself an unrestricted optimizer and
its active cells already satisfy the finite-\(\Gamma\) odds-ratio inequalities.
Under the conjecture's stated hypothesis that every unrestricted optimizer for
the endpoint touches a nondegenerate Frechet equality face in the active
direction, no such finite-table witness exists.  Thus the refutation search
fails in the smallest nontrivial binary selected-arm polytope and the positive
proof below applies.

\paragraph{Minimality check.}
The nondegeneracy condition \(0<L_d(\alpha)<U_d(\alpha)<1\) is needed.  If
\(r_d(\alpha)=1\), the selected arm contains only always-selected units,
\(t_d=m_d\), and the odds ratio is not a meaningful finite-table separator of
the Frechet endpoint; the finite and unrestricted armwise means both equal
\(m_d\).  If \(m_d\in\{0,1\}\), the selected outcome is deterministic in the
arm, so the always-selected mean is pinned at the same boundary value
regardless of the odds-ratio budget.  Finally, if the reverse-selection budget
fixes the Lee monotonicity profile and the active table at that profile is
already finite-\(\Gamma\)-compatible, then equality is caused by the collapsed
profile rather than by a failure of the strict-exclusion argument.  These cases
explain why the theorem is stated for exposed nondegenerate Frechet faces
inside Assumption~\ref{ass:interior} and why the conjecture lists the boundary
equality cases separately.

\subsubsection*{Conjecture 3}
\paragraph{Refutation attempt before proof.}
The cluster-appropriate finite-binary refutation primitive is endpoint or
vertex enumeration of the two selected-arm support problem.  After
Theorem~\ref{thm:arm-quadratic}, every armwise candidate endpoint is
represented by a selected-arm \(2\times2\) table with margins \((q_d,m_d)\) and
an active Frechet or odds-ratio face.  Thus a counterexample to the conjecture
can only occur through the two-dimensional endpoint optimizer set in the
benchmark rectangle and its relation to the common-\(\alpha\) curve
\(\mathcal C_\kappa(P)\).

The search considered the three possible witness types.  Type I is a zero-gap
witness with unequal values: an endpoint optimizer \(q^\star\) of the SGJR/JR
rectangle, or of the HH rectangle, satisfies \(q^\star\in\mathcal C_\kappa(P)\)
but the restricted Lee--Gamma support value differs from the benchmark support
value.  This candidate cannot work, because the same table \(q^\star\) is
feasible for the restricted support problem and has exactly the benchmark
endpoint value.  Type II is an equal-value witness with positive gap: the
restricted support value equals the benchmark value even though every benchmark
optimizer lies a positive Euclidean distance from \(\mathcal C_\kappa(P)\).
This candidate cannot work, because compactness of \(\mathcal C_\kappa(P)\)
gives a restricted optimizer \(\tilde q\), and equality of the values makes
\(\tilde q\) an unrestricted benchmark optimizer on the curve.  Type III is a
positive-gap witness without strict separation.  Since the restricted feasible
set is a subset of the benchmark rectangle, failure of strict separation is
exactly equality of the support values, reducing Type III to Type II.

Thus vertex enumeration of the finite binary endpoint geometry produces no
witness under the stated assumptions.  The attempted counterexample search
fails for a structural reason: benchmark endpoint equality is equivalent to
intersection of the benchmark optimizer set with the common-\(\alpha\)
compatibility curve.

\paragraph{Minimality check: dropping common-\(\alpha\) compatibility.}
The common-\(\alpha\) condition is necessary for the comparison to be
meaningful.  If it is dropped, the benchmark may choose an exposed armwise
endpoint \(q^\star=(q_1^\star,q_0^\star)\) with
\[
  p_1q_1^\star\ne p_0q_0^\star.
\]
Such a pair can satisfy both armwise odds-ratio quadratic restrictions, because
those restrictions are checked separately in the two selected arms, but it
cannot be generated by any single binary principal-strata law with
always-selected mass \(\alpha\).  Under Assumption~\ref{ass:exposed-endpoints},
if this off-curve \(q^\star\) is the locally unique benchmark endpoint, then
\[
  \operatorname{dist}(q^\star,\mathcal C_\kappa(P))>0
\]
and the theorem gives strict separation.  Thus the weaker armwise beta/psi or
no-exclusion restriction without common-\(\alpha\) coupling is not enough to
recover the Lee--Gamma support value.

\section{Formalization checklist}
\paragraph{Substrate survey record.}
\texttt{bypass-justified}: local name audit for
\texttt{POManskiIVSystem}, \texttt{manski\_bounds\_ATE}, and
\texttt{PartialID.Basic} did not expose a direct finite common-\(\alpha\)
selected-mixture quadratic primitive at this artifact's abstraction level.  The
note is therefore written as a finite algebraic table argument; Stage~1 can
still map the objects below to available repository structures where
appropriate.

\begin{center}
\begin{tabular}{p{0.22\linewidth}p{0.27\linewidth}p{0.25\linewidth}p{0.16\linewidth}}
\hline
Object & Typed signature & Role in proof & Dependencies \\
\hline
Observed law \(P\) & probability law of \((D,S,SY)\) with \(D,S,Y\in\{0,1\}\) & supplies \(p_d,m_d\) & Assumptions~\ref{ass:random-consistency}, \ref{ass:binary-support} \\
Principal masses & \((\alpha,g,h,n)\in[0,1]^4\), sum \(1\) & glues selected arms into one law & selected shares, reverse budget \\
\(\mathcal A_\kappa^+(P)\) & compact interval in \((0,\min\{p_0,p_1\}]\) & one-dimensional profile domain & \(p_0,p_1,\kappa\) \\
\(r_d(\alpha)\) & map \(\mathcal A_\kappa^+(P)\to(0,1)\) & selected-arm always share & \(\alpha,p_d\) \\
\(T_\Gamma(r,m)\) & closed interval of \(t\)-values & feasible selected-arm cell set & Frechet margins, odds-ratio bound \\
\(\rho_\lambda(r,m)\) & quadratic-root map \((0,1)^2\to\mathbb R\) & computes finite-\(\Gamma\) endpoints & \(Q_\lambda(t;r,m)=0\) \\
\(\underline a_d,\overline a_d\) & maps \(\mathcal A_\kappa^+(P)\to[0,1]\) & armwise always-selected mean bounds & \(T_\Gamma,r_d\) \\
\(\theta_L,\theta_U\) & real-valued extrema over \(\mathcal A_\kappa^+(P)\) & sharp Lee--Gamma interval endpoints & armwise endpoints \\
\(F_L^\Gamma,F_U^\Gamma\) & continuous real profiles on \(\mathcal A_\kappa^+(P)\) & strict-tightening comparison & finite and unrestricted \(T\)-sets \\
\(\mathcal C_\kappa(P)\) & compact curve in \((0,1)^2\) & common-\(\alpha\) coupling set & \(p_1q_1=p_0q_0=\alpha\) \\
\(\mathcal R_\varepsilon\) & compact rectangle in \((0,1)^2\) & armwise comparator feasible set & chosen \(\varepsilon\), contains \(\mathcal C_\kappa(P)\) \\
\(\ell_\Gamma,u_\Gamma\) & maps \((q,m)\mapsto[0,1]\) endpoints & comparator support objectives & \(T_\Gamma(q,m)\) \\
\(\Delta_\ell^{\mathrm{SGJR}},\Delta_\ell^{\mathrm{HH}}\) & nonnegative distances from optimizer sets to \(\mathcal C_\kappa(P)\) & equality and strict-separation certificate & compactness and exposed endpoint sets \\
\hline
\end{tabular}
\end{center}

\section{Conclusion and references}
Conjecture 1 (lee-gamma-frontier) is partial; Partial verdict: Assumptions~\ref{ass:random-consistency}--\ref{ass:interior} imply the sharp common-\(\alpha\) frontier displayed in Conjecture~\ref{conj:lee-gamma-frontier}; the additional open-set non-representability assertions relative to external comparator geometries are not confirmed by the finite-table assumptions alone.
Conjecture 2 (strict-tightening) is confirmed; Conjecture~\ref{conj:strict-tightening} is confirmed as a directional strict-tightening statement: for any endpoint direction whose unrestricted optimizer set is supported only on nondegenerate Frechet equality faces, the finite-\(\Gamma\) endpoint is strictly inside the corresponding unrestricted endpoint, and endpoint equality can occur only through a finite-\(\Gamma\)-compatible unrestricted optimizer profile.
Conjecture 3 (coupling-iff) is confirmed; Conjecture 3 is confirmed: zero compatibility gap is necessary and sufficient for equality with the SGJR/JR armwise beta/psi endpoint, and is necessary (indeed sufficient in this binary specialization) for equality with the proposal-defined Honore--Hu-style no-exclusion endpoint; positive gap gives strict separation in the appropriate endpoint direction.

\begin{thebibliography}{99}
\bibitem{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association}, 92(439), 1171--1176.

\bibitem{FrangakisRubin2002}
Frangakis, C. E. and Rubin, D. B. (2002).
Principal stratification in causal inference.
\emph{Biometrics}, 58(1), 21--29.

\bibitem{HonoreHu2020Selection}
Honore, B. E. and Hu, L. (2020).
Selection without exclusion.
\emph{Econometrica}, 88(3), 1007--1029.

\bibitem{HorowitzManski1995}
Horowitz, J. L. and Manski, C. F. (1995).
Identification and robustness with contaminated and corrupted data.
\emph{Econometrica}, 63(2), 281--302.

\bibitem{HuberMellace2015SharpSelection}
Huber, M. and Mellace, G. (2015).
Sharp bounds on causal effects under sample selection.
\emph{Oxford Bulletin of Economics and Statistics}, 77(1), 129--151.

\bibitem{JemiaiRotnitzkyShepherdGilbert2007}
Jemiai, Y., Rotnitzky, A., Shepherd, B. E., and Gilbert, P. B. (2007).
Semiparametric estimation of treatment effects given base-line covariates on
an outcome measured after a post-randomization event occurs.
\emph{Journal of the Royal Statistical Society: Series B}, 69(5), 879--901.

\bibitem{KroftMourifieVayalinkal2024}
Kroft, K., Mourifie, I., and Vayalinkal, A. (2024).
Horowitz--Manski--Lee bounds with multilayered sample selection.
NBER Working Paper No. 32952.

\bibitem{LaffersNedela2017Sensitivity}
Laffers, L. and Nedela, R. (2017).
Sensitivity of the bounds on the average treatment effect in the presence of
sample selection.
\emph{Economics Letters}, 160, 105--108.

\bibitem{Lee2009SampleSelection}
Lee, D. S. (2009).
Training, wages, and sample selection: estimating sharp bounds on treatment
effects.
\emph{Review of Economic Studies}, 76(3), 1071--1102.

\bibitem{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review}, 80(2), 319--323.

\bibitem{Okamoto2025RobustifyLee}
Okamoto, Y. (2025).
Robustify and tighten the Lee bounds: a sample selection model under stochastic
monotonicity and symmetry assumptions.
\emph{The Econometrics Journal}, 28(3), 482--501.

\bibitem{ScharfsteinManskiAnthony2004}
Scharfstein, D. O., Manski, C. F., and Anthony, J. C. (2004).
On the construction of bounds in prospective studies with missing ordinal
outcomes: application to the Good Behavior Game Trial.
\emph{Biometrics}, 60(1), 154--164.

\bibitem{Semenova2025GeneralizedLee}
Semenova, V. (2025).
Generalized Lee bounds.
\emph{Journal of Econometrics}, 247, 106033.

\bibitem{ShepherdGilbertDupont2011}
Shepherd, B. E., Gilbert, P. B., and Dupont, C. T. (2011).
Sensitivity analyses comparing time-to-event outcomes only existing in a
subset selected postrandomization and relaxing monotonicity.
\emph{Biometrics}, 67(3), 1100--1110.

\bibitem{ShepherdGilbertJemiaiRotnitzky2006}
Shepherd, B. E., Gilbert, P. B., Jemiai, Y., and Rotnitzky, A. (2006).
Sensitivity analyses comparing outcomes only existing in a subset selected
post-randomization, conditional on covariates, with application to HIV vaccine
trials.
\emph{Biometrics}, 62(2), 332--342.

\bibitem{ShepherdRedmanAnkerst2008}
Shepherd, B. E., Redman, M. W., and Ankerst, D. P. (2008).
Does finasteride affect the severity of prostate cancer? A causal sensitivity
analysis.
\emph{Journal of the American Statistical Association}, 103(484), 1392--1404.

\bibitem{SmithVanderWeele2019}
Smith, L. H. and VanderWeele, T. J. (2019).
Bounding bias due to selection.
\emph{Epidemiology}, 30(4), 509--516.

\bibitem{ZhangRubin2003}
Zhang, J. L. and Rubin, D. B. (2003).
Estimation of causal effects via principal stratification when some outcomes
are truncated by death.
\emph{Journal of Educational and Behavioral Statistics}, 28(4), 353--368.
\end{thebibliography}

\end{document}
