% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_collider\_bias\_sharp, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_collider\_bias\_sharp} / \texttt{v1}%
  \\ \large\textit{A common-error compatibility frontier beyond rectangular collider-bias bounds}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{quote}
\begin{verbatim}
(qid, specialization, observable distribution P, parameter theta,
 identifying restrictions, bounding functional)
qid = pid_collider_bias_sharp.
specialization = v1.
P = the law of (D,C,YC) generated by a binary randomized treatment D,
    a binary post-treatment collider/selection indicator C, and a
    binary outcome Y observed only on C=1; P supplies
    s_d = P(C=1 | D=d) and m_d = E[Y | D=d,C=1] for d in {0,1}.
theta = E[Y(1)-Y(0)] in the target population before conditioning on C.
identifying restrictions = consistency, random assignment of D, bounded
    binary outcomes, finite collider-bias parameter Gamma in [1,infty]
    bounding arm-specific odds ratios OR(Y(d),C(d)), and a common
    structural-error model with one latent outcome rank U and one latent
    collider rank V, both with uniform [0,1] marginals, treatment-specific
    outcome thresholds rho_d, and treatment-specific selection threshold
    maps kappa_{d0}, kappa_{d1}.
bounding functional = the Gamma-indexed common-error ATE identified set:
    the Scharfstein-Manski-Anthony rectangular armwise interval intersected
    with the conjectured quadratic compatibility inequality Q_Gamma(P,theta)<=0;
    endpoint laws must use the same joint law of (U,V) and may not paste
    independent armwise missing-outcome completions.
\end{verbatim}
\end{quote}

\begin{abstract}
Conditioning on a post-treatment collider, mediator, or selection indicator is a familiar source of bias, but the sharp-set object relevant for target-population ATEs is not the rectangular one-arm missing-outcome bound alone.  \citet{ScharfsteinManskiAnthony2004Bounds} already gives the armwise class-based benchmark under bounded selection-bias log odds ratios.  This revised proposal asks whether a stronger common structural-error model, in which both treatment arms are generated from the same latent outcome rank and collider rank with treatment-specific threshold maps, creates a nonrectangular sharp ATE frontier inside that rectangular benchmark.  The flagship kernel is Conjecture~\ref{conj:common-frontier}: a computable quadratic compatibility inequality \(Q_\Gamma(P,\theta)\le 0\) whose roots give the sharp ATE endpoints and whose strict interior cut separates this proposal from the Scharfstein--Manski--Anthony armwise construction on an open set of observed laws.  Resolving it would turn qualitative collider-bias warnings into a sensitivity curve that reports both the published rectangular benchmark and the additional price of requiring a single latent collider mechanism across treatment arms.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Many applied analyses intentionally restrict to a selected sample or control for a post-treatment variable because the selected data are the only usable data.  In causal diagrams this is the canonical collider problem: conditioning on \(C\) can create dependence between treatment-side and outcome-side errors even if treatment was randomized before selection.  Existing sensitivity analyses can bound the missing outcome distribution arm by arm, but an analyst who interprets selection as one biological, behavioral, or institutional collider mechanism needs to know whether those separately sharp completions can be pasted into a single latent-error law.

\paragraph{The main finding (proposed).}
The proposed flagship result is Conjecture~\ref{conj:common-frontier}.  Let
\[
  R_\Gamma(P)=[\,\ell_1^{\rm SMA}(\Gamma)-u_0^{\rm SMA}(\Gamma),\
  u_1^{\rm SMA}(\Gamma)-\ell_0^{\rm SMA}(\Gamma)\,]
\]
be the rectangular benchmark obtained from \citet{ScharfsteinManskiAnthony2004Bounds}.  The conjecture is that imposing one shared latent structural-error pair \((U,V)\), rather than two independently completed armwise tables, cuts \(R_\Gamma(P)\) by a quadratic compatibility inequality \(Q_\Gamma(P,\theta)\le 0\); the sharp set is the resulting root interval, with endpoint laws that saturate the upper and lower envelopes of the same joint law of \((U,V)\).

\paragraph{What is new.}
The closest published result is now \citet{ScharfsteinManskiAnthony2004Bounds}, not the earlier qualitative collider-bias papers.  The precise epsilon-gap is that their class-based construction allows the missing ordinal or binary outcome distribution to be bounded separately within each intervention arm; it does not impose that the treatment-0 and treatment-1 collider tables arise from the same latent outcome rank \(U\), the same latent collider rank \(V\), and treatment-specific threshold maps.  The novelty claim is therefore not the armwise odds-ratio formula.  It is the nonrectangular compatibility frontier that appears when separately sharp Scharfstein--Manski--Anthony endpoint tables must be jointly realized by one open class of common structural-error laws.

\paragraph{How it positions in the literature.}
This is a partial-identification proposal.  It uses Manski-style bounded-outcome logic as the no-assumption baseline, \citet{ScharfsteinManskiAnthony2004Bounds} as the sharp rectangular missing-outcome benchmark, Balke--Pearl-style endpoint realization as the sharpness standard, and modern sensitivity-analysis practice as the parameter-indexed reporting target.  It is adjacent to sample-selection bounds such as \citet{Lee2009SampleSelection}, but it replaces monotone selection and trimming with a finite collider-dependence budget plus a common latent-error compatibility requirement.

\paragraph{Implications for the community.}
The concrete downstream consumer is the prospective-trial missing-outcome workflow of \citet{ScharfsteinManskiAnthony2004Bounds}: if Conjecture~\ref{conj:common-frontier} is true, analysts can report when the published rectangular class-based interval is too wide because it pastes armwise endpoint laws that cannot share one collider mechanism.  A second consumer is the selection-bias sensitivity workflow of \citet{SmithVanderWeele2019Selection}, which would gain an endpoint-attaining additive ATE curve with an explicit common-mechanism warning.

\paragraph{How research benefits from the conclusion.}
A reader should report both the Scharfstein--Manski--Anthony rectangular interval and the common-error compatibility interval, and should treat a discrepancy between them as evidence that separate armwise sensitivity bounds are mechanically over-permissive for the causal story being invoked.

\section{Related work}
\citet{ScharfsteinManskiAnthony2004Bounds} is the primary comparator: it constructs bounds in prospective studies with missing ordinal outcomes using class-based restrictions, including bounded selection-bias log odds ratios, and in the binary no-baseline case it supplies the rectangular armwise benchmark used here.  \citet{Greenland2003ColliderBias} is the central quantitative collider-stratification anchor: it shows that conditioning on variables affected by exposure and disease can induce biases comparable to classical confounding, but it does not characterize a sharp ATE identified set.  \citet{HernanHernandezDiazRobins2004Selection} frames selection bias structurally as conditioning on a common effect, which is the causal environment encoded here by \(C(d)\).  \citet{VanderWeeleRobins2009MonotonicEffects} develops signed-edge and monotonic-effect tools for qualitative conclusions on DAGs; this proposal asks for the numerical sharp frontier behind those qualitative warnings.  \citet{SmithVanderWeele2019Selection} gives practical selection-bias bounding factors, including additive-scale supplements, but those factors are robustness outer bounds rather than endpoint-attaining common-error identified sets.

\citet{Manski1990NonparametricBounds} supplies the no-assumption bounded-outcome interval that the finite-\(\Gamma\) rectangular curve approaches as \(\Gamma\to\infty\).  \citet{BalkePearl1997Bounds} proves that finite causal systems can have sharp closed-form treatment-effect bounds via response-type programs; the present proposal imports that endpoint-realization standard to a post-treatment collider restriction whose common-error feasible set is not the same compliance polytope.  \citet{Lee2009SampleSelection} derives sharp trimming bounds for treatment-induced sample selection under monotone selection; the current proposal keeps the target as the full-population ATE but replaces monotonicity with a finite symmetric dependence budget and common latent collider ranks.  \citet{MastenPoirierZhang2024Sensitivity} estimates ATE and ATT bounds under scalar relaxations of unconfoundedness; this proposal is the collider-conditioning analogue, with \(\Gamma\) indexing movement from no collider dependence toward Manski and with an additional common-mechanism compatibility check.

\citet{FrangakisRubin2002PrincipalStratification} addresses post-treatment variables by changing the estimand to principal-stratum effects; here the estimand remains the marginal ATE and post-treatment conditioning is treated as a source of partial identification.  \citet{CaiKurokiPearlTian2008DirectEffects} derives tight controlled-direct-effect bounds with an unmeasured intermediate-outcome confounder, which is adjacent because it uses closed-form bounds for a post-treatment intermediate, but it does not bound total ATE distortion from conditioning on that intermediate.  \citet{DingMiratrix2015MBias} gives linear-structural formulae for M-bias; this proposal asks for a nonparametric binary-outcome sharp set rather than a linear coefficient comparison.  \citet{Huber2020DirectIndirectSelection} treats mediation with sample selection under identifying assumptions and motivates the harder mediator-plus-selection frontier that a collider-bias sharp set would feed.

The in-repo prior-art map has no direct accepted \texttt{pid\_collider\_bias\_sharp} proposal.  The closest project artefact is \texttt{pid\_mediation\_proxy\_v1}, whose Stage 0.5 reviews rejected generic Manski/Balke--Pearl LP sharpness and asked for explicit endpoint-table constructions for a mean-kernel polytope.  The \texttt{q\_did\_drdid\_ipwdid\_frontier\_v1} bad-control frontier reviews asked for primitive structural conditions and a finite-support quadratic program rather than a bridge conditional probability table treated as primitive.  The accepted \texttt{pid\_ordinal\_principal\_strata\_v1} bank entry supplies an adjacent sharp LP for ordinal post-treatment intermediates and warns about nonrectangular compatibility, while \texttt{pid\_rdd\_manipulation\_bounded\_v1} supplies a successful global-plus-cell selection-budget template.  The \texttt{CausalSmith/doc/API.md} PartialID catalogue records \texttt{ManskiNonparametricBounds\_Study} as the no-assumption bounded-outcome comparator.  The novelty axis here is a new common-error sharp bounding functional inside the Scharfstein--Manski--Anthony rectangular benchmark, not a new SCM or graph calculus rule.

\section{Formal setup}
Let \(D\in\{0,1\}\) be a randomized treatment assigned before a post-treatment collider or selection indicator \(C\in\{0,1\}\).  Let \(Y(d)\in\{0,1\}\) be the potential outcome under treatment \(d\), and let \(C(d)\in\{0,1\}\) be the potential collider/selection state under treatment \(d\).  The target parameter is
\[
  \theta = E[Y(1)-Y(0)].
\]
The observable distribution \(P\) consists of treatment probabilities, the selection rates
\[
  s_d=P(C=1\mid D=d),
\]
and the selected-sample outcome means
\[
  m_d=E[Y\mid D=d,C=1], \qquad d\in\{0,1\}.
\]
Write the observed selected cells
\[
  a_d=s_dm_d,\qquad b_d=s_d(1-m_d),\qquad n_d=1-s_d.
\]
For each arm \(d\), the missing scalar is
\[
  x_d=P(Y(d)=1,C(d)=0),
\]
and the full-population arm mean is
\[
  \mu_d(P,x_d)=a_d+x_d.
\]
The arm-specific collider odds ratio is
\[
  OR_d(x_d)=
  \frac{a_d(n_d-x_d)}{b_dx_d},
\]
with the standard limiting conventions when \(a_d=0\), \(b_d=0\), or \(x_d\in\{0,n_d\}\).  A finite collider-bias parameter \(\Gamma\in[1,\infty]\) restricts \(OR_d(x_d)\in[\Gamma^{-1},\Gamma]\).  The Scharfstein--Manski--Anthony rectangular benchmark is
\[
  R_\Gamma(P)=
  \{\mu_1(P,x_1)-\mu_0(P,x_0): x_d\in[0,n_d],\
  OR_d(x_d)\in[\Gamma^{-1},\Gamma]\ \text{for }d=0,1\}.
\]

The proposed common-error model refines \(R_\Gamma(P)\).  A feasible law consists of one joint distribution \(H\) of \((U,V)\in[0,1]^2\) with both one-dimensional marginals uniform on \([0,1]\), two treatment-specific outcome thresholds \(\rho_d\in[0,1]\), and four treatment-specific selection thresholds \(\kappa_{dy}\in[0,1]\), with
\[
  Y(d)=\one\{U\le \rho_d\},\qquad
  C(d)=\one\{V\le \kappa_{d,Y(d)}\}.
\]
Different observed selection rates \(s_0\) and \(s_1\) are allowed because the maps \(\kappa_{0y}\) and \(\kappa_{1y}\) may differ by treatment arm and outcome state.  The common-error identified set is
\[
  \Theta_I^{\rm CE}(P;\Gamma)=
  \{\theta(H,\rho,\kappa): H,\rho,\kappa\ \text{generate }P
  \text{ and satisfy } OR_d\in[\Gamma^{-1},\Gamma]\ \text{for }d=0,1\}.
\]
Here \(OR_d\) is computed from the generated two-by-two table of \((Y(d),C(d))\), so \(\Theta_I^{\rm CE}(P;\Gamma)\subseteq R_\Gamma(P)\) by construction.

For a single arm, if a latent binary outcome error \(E_d\) and collider error \(V_d\) have margins \(r_d,c_d\), the odds-ratio saturation equation for the joint cell \(t=P(E_d=1,V_d=1)\) is the quadratic
\[
  (\Gamma-1)t^2-\{1+(\Gamma-1)(r_d+c_d)\}t+\Gamma r_dc_d=0,
\]
with the reciprocal equation for the lower envelope.  The new object is the two-arm compatibility polynomial \(Q_\Gamma(P,\theta)\), conjectured to be the elimination of the shared \(H,\rho,\kappa\) variables from these two armwise quadratic frontiers.

\begin{quote}
\begin{verbatim}
(qid, specialization, observable distribution P, parameter theta,
 identifying restrictions, bounding functional)
qid = pid_collider_bias_sharp.
specialization = v1.
P = the law of (D,C,YC) generated by a binary randomized treatment D,
    a binary post-treatment collider/selection indicator C, and a
    binary outcome Y observed only on C=1; P supplies
    s_d = P(C=1 | D=d) and m_d = E[Y | D=d,C=1] for d in {0,1}.
theta = E[Y(1)-Y(0)] in the target population before conditioning on C.
identifying restrictions = consistency, random assignment of D, bounded
    binary outcomes, finite collider-bias parameter Gamma in [1,infty]
    bounding arm-specific odds ratios OR(Y(d),C(d)), and a common
    structural-error model with one latent outcome rank U and one latent
    collider rank V, both with uniform [0,1] marginals, treatment-specific
    outcome thresholds rho_d, and treatment-specific selection threshold
    maps kappa_{d0}, kappa_{d1}.
bounding functional = the Gamma-indexed common-error ATE identified set:
    the Scharfstein-Manski-Anthony rectangular armwise interval intersected
    with the conjectured quadratic compatibility inequality Q_Gamma(P,theta)<=0;
    endpoint laws must use the same joint law of (U,V) and may not paste
    independent armwise missing-outcome completions.
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Random assignment and consistency]\label{ass:random-consistency}
\(D\) is randomized before \(C\): \((Y(0),Y(1),C(0),C(1),U,V)\perp D\).  The observed variables satisfy \(C=C(D)\) and, on \(C=1\), \(Y=Y(D)\).
\end{assumption}

\begin{assumption}[Binary outcome and observed selected law]\label{ass:bounded-observed}
\(Y(d)\in\{0,1\}\) for \(d\in\{0,1\}\).  The observable law \(P\) identifies \(s_d=P(C=1\mid D=d)\) and \(m_d=E[Y\mid D=d,C=1]\), with \(a_d=s_dm_d\), \(b_d=s_d(1-m_d)\), and \(n_d=1-s_d\).
\end{assumption}

\begin{assumption}[Finite collider odds-ratio budget]\label{ass:gamma-or}
For a fixed \(\Gamma\in[1,\infty]\), each arm-specific completion \(x_d=P(Y(d)=1,C(d)=0)\) must satisfy the collider-dependence restriction
\[
  OR_d(x_d)=\frac{a_d(n_d-x_d)}{b_dx_d}\in[\Gamma^{-1},\Gamma],
\]
with limiting conventions for boundary cells.  \(\Gamma=1\) encodes no outcome-collider dependence within arm \(d\), and \(\Gamma=\infty\) imposes no collider-dependence restriction.
\end{assumption}

\begin{assumption}[Nondegenerate arm]\label{ass:nondegenerate}
When strict tightening is claimed for arm \(d\), \(s_d\in(0,1)\), \(m_d\in(0,1)\), and \(\Gamma<\infty\).
\end{assumption}

\begin{assumption}[Common structural-error threshold model]\label{ass:common-error}
There exists one joint law \(H\) for latent ranks \((U,V)\in[0,1]^2\), with both one-dimensional marginals uniform on \([0,1]\), treatment-specific outcome thresholds \(\rho_0,\rho_1\in[0,1]\), and treatment-specific selection thresholds \(\kappa_{dy}\in[0,1]\) for \(d,y\in\{0,1\}\), such that
\[
  Y(d)=\one\{U\le \rho_d\},\qquad
  C(d)=\one\{V\le \kappa_{d,Y(d)}\}.
\]
The generated \((Y(d),C(d))\) table must equal the completed arm \(d\) table.  The maps \(\kappa_{0y}\) and \(\kappa_{1y}\) may differ, so the model permits \(s_0\ne s_1\).
\end{assumption}

\begin{assumption}[Open interior compatibility regime]\label{ass:open-interior}
The observed law is in the nonboundary region \(s_d\in(0,1)\), \(m_d\in(0,1)\), \(\Gamma\in(1,\infty)\), and the Scharfstein--Manski--Anthony rectangular benchmark \(R_\Gamma(P)\) has nonempty interior.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: Scharfstein--Manski--Anthony binary reduction]\label{thm:sma-reduction}
Under Assumptions~\ref{ass:random-consistency}, \ref{ass:bounded-observed}, and \ref{ass:gamma-or}, and without imposing Assumption~\ref{ass:common-error}, the class-based armwise odds-ratio benchmark of \citet{ScharfsteinManskiAnthony2004Bounds} reduces in the binary no-baseline case to
\[
  \mu_d\in[\ell_d^{\rm SMA}(\Gamma),u_d^{\rm SMA}(\Gamma)],
\]
where, for nonboundary cells,
\[
  \ell_d^{\rm SMA}(\Gamma)=a_d+\frac{a_dn_d}{a_d+\Gamma b_d},
  \qquad
  u_d^{\rm SMA}(\Gamma)=a_d+\frac{\Gamma a_dn_d}{b_d+\Gamma a_d}.
\]
Consequently the published rectangular ATE benchmark is
\[
  R_\Gamma(P)=
  [\,\ell_1^{\rm SMA}(\Gamma)-u_0^{\rm SMA}(\Gamma),\
  u_1^{\rm SMA}(\Gamma)-\ell_0^{\rm SMA}(\Gamma)\,].
\]
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This theorem is not claimed as the flagship novelty: it is the required published-prior-art reduction that fixes the v1 mistake of presenting the armwise odds-ratio completion as new.  The epsilon-gap starts only after this rectangular benchmark is imposed, because \citet{ScharfsteinManskiAnthony2004Bounds} does not require a single latent collider mechanism to realize both treatment-arm endpoint tables.  (b) The concrete consumer is the prospective-trial missing-outcome workflow of \citet{ScharfsteinManskiAnthony2004Bounds}: all common-error claims must be measured against \(R_\Gamma(P)\), not against Manski or Greenland-style qualitative bounds.

\begin{conjecture}[Conjecture 1: common-error quadratic compatibility frontier (NOT YET PROVED)]\label{conj:common-frontier}
Under Assumptions~\ref{ass:random-consistency}, \ref{ass:bounded-observed}, \ref{ass:gamma-or}, \ref{ass:common-error}, and \ref{ass:open-interior}, there exists a computable quadratic polynomial
\[
  Q_\Gamma(P,\theta)=A_\Gamma(P)\theta^2+B_\Gamma(P)\theta+C_\Gamma(P)
\]
obtained by eliminating \((H,\rho,\kappa)\) from the two armwise odds-ratio saturation equations and the shared-threshold constraints in Assumption~\ref{ass:common-error}, such that
\[
  \Theta_I^{\rm CE}(P;\Gamma)
  =\{\theta\in R_\Gamma(P): Q_\Gamma(P,\theta)\le 0\}.
\]
On a nonempty open subset of observed laws \(P\), this set is a strict subset of \(R_\Gamma(P)\).  At the two endpoints, the attaining laws use the same joint law \(H\) of \((U,V)\); one endpoint saturates the upper Scharfstein--Manski--Anthony envelope in the treatment arm and the lower envelope in the control arm subject to the compatibility equation, and the other endpoint reverses the saturation pattern.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The epsilon-gap to \citet{ScharfsteinManskiAnthony2004Bounds} is open-class nonrectangularity: their binary specialization gives \(R_\Gamma(P)\), while this conjecture says the true set under one common latent collider mechanism is \(R_\Gamma(P)\) cut by a quadratic compatibility inequality.  The gap to \citet{Greenland2003ColliderBias}, \citet{VanderWeeleRobins2009MonotonicEffects}, and \citet{SmithVanderWeele2019Selection} is sharpness with endpoint laws, not qualitative sign or outer-factor control.  (b) Resolving the conjecture would tell users of \citet{ScharfsteinManskiAnthony2004Bounds} exactly when class-based armwise bounds are conservative for a common-mechanism causal story, and would answer the prior \texttt{q\_did\_drdid\_ipwdid\_frontier\_v1} request for a primitive finite-support quadratic frontier.

\section{Sanity-check corollaries}
\begin{corollary}[Manski limit]\label{cor:manski-limit}
Under Assumptions~\ref{ass:bounded-observed} and \ref{ass:gamma-or}, as \(\Gamma\to\infty\),
\[
  \ell_d^{\rm SMA}(\Gamma)\downarrow a_d,\qquad u_d^{\rm SMA}(\Gamma)\uparrow a_d+n_d.
\]
Thus the rectangular benchmark \(R_\Gamma(P)\) reduces to the Manski no-assumption ATE interval whenever the collider-bias budget is infinite.  Under Assumption~\ref{ass:common-error}, Conjecture~\ref{conj:common-frontier} must either reduce to the same interval or identify the residual common-error compatibility cut that remains after the odds-ratio budget is removed.
\end{corollary}

\begin{corollary}[No collider dependence]\label{cor:no-dependence}
Under Assumptions~\ref{ass:bounded-observed} and \ref{ass:gamma-or} with \(\Gamma=1\), the arm mean collapses to
\[
  \ell_d^{\rm SMA}(1)=u_d^{\rm SMA}(1)=a_d+\frac{a_dn_d}{a_d+b_d}=m_d.
\]
Hence, if Conjecture~\ref{conj:common-frontier} holds and \(\Gamma=1\) in both arms, \(\Theta_I^{\rm CE}(P;1)=\{m_1-m_0\}\), the selected-sample contrast.
\end{corollary}

\begin{corollary}[Known finite-\(\Gamma\) tightening relative to Manski]\label{cor:sma-tightening}
Under Assumptions~\ref{ass:bounded-observed}, \ref{ass:gamma-or}, and \ref{ass:nondegenerate}, the published Scharfstein--Manski--Anthony arm interval is strictly contained in the Manski arm interval:
\[
  a_d < \ell_d^{\rm SMA}(\Gamma) \le u_d^{\rm SMA}(\Gamma) < a_d+n_d.
\]
This is the known rectangular benchmark; Conjecture~\ref{conj:common-frontier} must be judged by whether it further tightens \(R_\Gamma(P)\) on an open set.
\end{corollary}

\section{Proof-sketch route}
The calibration theorem reduces to the Scharfstein--Manski--Anthony one-arm odds-ratio completion: solve two fractional inequalities for \(x_d\) and check the boundary conventions when \(a_d=0\), \(b_d=0\), or \(s_d\in\{0,1\}\).  The mathematical work for Conjecture~\ref{conj:common-frontier} is an elimination problem.  Introduce finite variables for the masses of the regions cut out by the four thresholds \(\rho_0,\rho_1,\kappa_{00},\kappa_{01},\kappa_{10},\kappa_{11}\) in the common \((U,V)\) plane, impose the observed-cell equations and the two armwise odds-ratio inequalities, project onto \(\theta=\rho_1-\rho_0\) using the uniform marginal of \(U\), and eliminate the nuisance masses.  The expected proof route is that the two active odds-ratio constraints reduce the projection to one quadratic inequality \(Q_\Gamma(P,\theta)\le 0\); the smallest nontrivial boundary case is the binary nondegenerate interior with opposite Scharfstein endpoint saturations.

\section{Honest scope flags}
The Scharfstein--Manski--Anthony reduction and finite-\(\Gamma\) tightening relative to Manski are now treated as known calibration facts, not as the flagship contribution.  The flagship contribution is deliberately labelled as Conjecture~\ref{conj:common-frontier}: the common structural-error compatibility cut may be empty for some laws, may be weaker than conjectured in boundary cells, or may require several inequalities rather than one quadratic inequality.  The v1 bounded-outcome extension has been withdrawn; this version is binary-outcome only.  The proposal does not claim point identification for \(\Gamma=1\) is substantively credible; it is a sanity-check corner case of the sensitivity model.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft proposing a finite-\(\Gamma\) collider odds-ratio sharp ATE interval with explicit extremal arm tables and a common-error sharpness conjecture; prior verdict: none.
\item v2 (revise) -- added \citet{ScharfsteinManskiAnthony2004Bounds} as the primary comparator, withdrew the bounded-\([0,1]\) outcome extension, replaced the single common \(V\) with a shared \((U,V)\) threshold model allowing \(s_0\ne s_1\), and shifted the flagship kernel to the common-error quadratic compatibility frontier beyond the rectangular benchmark; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Balke and Pearl(1997)]{BalkePearl1997Bounds}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association} 92(439), 1171--1176.
\url{https://doi.org/10.1080/01621459.1997.10474074}.

\bibitem[Cai et~al.(2008)]{CaiKurokiPearlTian2008DirectEffects}
Cai, Z., Kuroki, M., Pearl, J., and Tian, J. (2008).
Bounds on direct effects in the presence of confounded intermediate variables.
\emph{Biometrics} 64(3), 695--701.
\url{https://doi.org/10.1111/j.1541-0420.2007.00874.x}.

\bibitem[Ding and Miratrix(2015)]{DingMiratrix2015MBias}
Ding, P. and Miratrix, L. W. (2015).
To adjust or not to adjust? Sensitivity analysis of M-bias and butterfly-bias.
\emph{Journal of Causal Inference} 3(1), 41--57.
\url{https://doi.org/10.1515/jci-2013-0021}.

\bibitem[Frangakis and Rubin(2002)]{FrangakisRubin2002PrincipalStratification}
Frangakis, C. E. and Rubin, D. B. (2002).
Principal stratification in causal inference.
\emph{Biometrics} 58(1), 21--29.
\url{https://doi.org/10.1111/j.0006-341X.2002.00021.x}.

\bibitem[Greenland(2003)]{Greenland2003ColliderBias}
Greenland, S. (2003).
Quantifying biases in causal models: classical confounding vs collider-stratification bias.
\emph{Epidemiology} 14(3), 300--306.
\url{https://doi.org/10.1097/01.EDE.0000042804.12056.6C}.

\bibitem[Hernan et~al.(2004)]{HernanHernandezDiazRobins2004Selection}
Hernan, M. A., Hernandez-Diaz, S., and Robins, J. M. (2004).
A structural approach to selection bias.
\emph{Epidemiology} 15(5), 615--625.
\url{https://doi.org/10.1097/01.ede.0000135174.63482.43}.

\bibitem[Huber(2020)]{Huber2020DirectIndirectSelection}
Huber, M. (2020).
Direct and indirect effects of treatment with sample selection.
\emph{Econometrics} 8(4), 44.
\url{https://doi.org/10.3390/econometrics8040044}.

\bibitem[Lee(2009)]{Lee2009SampleSelection}
Lee, D. S. (2009).
Training, wages, and sample selection: estimating sharp bounds on treatment effects.
\emph{Review of Economic Studies} 76(3), 1071--1102.
\url{https://doi.org/10.1111/j.1467-937X.2009.00536.x}.

\bibitem[Manski(1990)]{Manski1990NonparametricBounds}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Masten et~al.(2024)]{MastenPoirierZhang2024Sensitivity}
Masten, M. A., Poirier, A., and Zhang, L. (2024).
Assessing sensitivity to unconfoundedness: estimation and inference.
\emph{Journal of Business \& Economic Statistics} 42(1), 1--13.
\url{https://doi.org/10.1080/07350015.2023.2183212}.

\bibitem[Scharfstein et~al.(2004)]{ScharfsteinManskiAnthony2004Bounds}
Scharfstein, D. O., Manski, C. F., and Anthony, J. C. (2004).
On the construction of bounds in prospective studies with missing ordinal outcomes: application to the Good Behavior Game trial.
\emph{Biometrics} 60(1), 154--164.
\url{https://doi.org/10.1111/j.0006-341X.2004.00158.x}.

\bibitem[Smith and VanderWeele(2019)]{SmithVanderWeele2019Selection}
Smith, L. H. and VanderWeele, T. J. (2019).
Bounding bias due to selection.
\emph{Epidemiology} 30(4), 509--516.
\url{https://doi.org/10.1097/EDE.0000000000001032}.

\bibitem[VanderWeele and Robins(2009)]{VanderWeeleRobins2009MonotonicEffects}
VanderWeele, T. J. and Robins, J. M. (2009).
Properties of monotonic effects on directed acyclic graphs.
\emph{Journal of Machine Learning Research} 10, 699--718.
\url{https://www.jmlr.org/papers/v10/vanderweele09a.html}.
\end{thebibliography}

\end{document}
