% §9-fragment-statement
\begin{theorem}[Strict finite-\(\Gamma\) tightening for exposed Frechet endpoints]\label{thm:strict-tightening}
\paragraph{Motivating conjecture restated verbatim.}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:exposed-endpoints}, if \(\Gamma<\infty\) and every unrestricted \(\Gamma=\infty\) optimizer for the lower or upper ATE endpoint uses at least one selected-arm cell on a nondegenerate Frechet equality face \(t_d=L_d(\alpha)\) or \(t_d=U_d(\alpha)\) with \(0<L_d(\alpha)<U_d(\alpha)<1\), then the interval in Conjecture~\ref{conj:lee-gamma-frontier} is a strict subset of the unrestricted bidirectional-principal-strata interval obtained by setting \(\Gamma=\infty\).  Within the interior assumptions, equality is possible only through profile-level compensation: a different positive \(\alpha\) must reproduce the unrestricted ATE endpoint while all active arm cells satisfy the finite-\(\Gamma\) odds-ratio inequalities.  Outside the interior assumptions, equality can also occur when an optimizing \(\alpha\) forces a degenerate principal mixture \(r_d(\alpha)\in\{0,1\}\), an observed selected outcome margin has \(m_d\in\{0,1\}\), or the reverse-selection budget collapses to Lee monotonicity and the unrestricted endpoint is already compatible with the finite-\(\Gamma\) odds-ratio face.

\paragraph{Confirmed statement.}
Conjecture~\ref{conj:strict-tightening} is confirmed as a directional strict-tightening statement: for any endpoint direction whose unrestricted optimizer set is supported only on nondegenerate Frechet equality faces, the finite-\(\Gamma\) endpoint is strictly inside the corresponding unrestricted endpoint, and endpoint equality can occur only through a finite-\(\Gamma\)-compatible unrestricted optimizer profile.
More explicitly, write
\[
  F_L^\Gamma(\alpha)=\underline a_1(\alpha;P,\Gamma)-\overline a_0(\alpha;P,\Gamma),
  \qquad
  F_U^\Gamma(\alpha)=\overline a_1(\alpha;P,\Gamma)-\underline a_0(\alpha;P,\Gamma),
\]
and define \(F_L^\infty,F_U^\infty\) by replacing \(T_\Gamma\) with the Frechet interval \(T_\infty\).  Let
\[
  \theta_L^\Gamma=\min_{\alpha\in\mathcal A_\kappa^+(P)}F_L^\Gamma(\alpha),
  \qquad
  \theta_U^\Gamma=\max_{\alpha\in\mathcal A_\kappa^+(P)}F_U^\Gamma(\alpha),
\]
and analogously let \(\theta_L^\infty,\theta_U^\infty\) be the unrestricted endpoints.  Then
\[
  \theta_L^\infty\le \theta_L^\Gamma\le \theta_U^\Gamma\le \theta_U^\infty.
\]
If every \(\alpha\in\arg\min F_L^\infty\) has either the arm \(1\) active value \(t_1=L_1(\alpha)\) or the arm \(0\) active value \(t_0=U_0(\alpha)\) on a nondegenerate Frechet face, then \(\theta_L^\infty<\theta_L^\Gamma\).  If every \(\alpha\in\arg\max F_U^\infty\) has either the arm \(1\) active value \(t_1=U_1(\alpha)\) or the arm \(0\) active value \(t_0=L_0(\alpha)\) on a nondegenerate Frechet face, then \(\theta_U^\Gamma<\theta_U^\infty\).  Hence the finite-\(\Gamma\) interval is a strict subset of the unrestricted interval whenever this condition holds for at least one endpoint, and it is strictly inside on both sides when it holds for both endpoints.
\end{theorem}

% §13-refutation-attempt
\paragraph{Refutation attempt before proof.}
I used the two-strata selected-arm response-type enumeration required for the partial-identification refutation primitive.  Fix an admissible profile \(\alpha\), an arm \(d\), and write \(r=r_d(\alpha)\), \(m=m_d\).  The latent selected-arm table has four cells
\[
  x_{11}=t,\qquad x_{10}=r-t,\qquad x_{01}=m-t,\qquad x_{00}=1-r-m+t,
\]
with \(t\in[L_d(\alpha),U_d(\alpha)]\).  The unrestricted \(\Gamma=\infty\) vertices are \(t=L_d(\alpha)\) and \(t=U_d(\alpha)\).  On a nondegenerate face \(0<L_d(\alpha)<U_d(\alpha)<1\), the lower vertex satisfies \(x_{00}=0\) and therefore \(OR_d=0\), while the upper vertex sets one denominator cell to zero and therefore \(OR_d=+\infty\).  Both violate \(OR_d\in[\Gamma^{-1},\Gamma]\) for every finite \(\Gamma\in(1,\infty)\).

The only remaining way for this enumeration to refute the conjecture would be a profile \(\tilde\alpha\) whose finite-\(\Gamma\) active table has the same global lower or upper ATE value as the unrestricted endpoint even though the Frechet-face optimizer is excluded.  The pointwise inequalities proved below rule this out unless \(\tilde\alpha\) is itself an unrestricted optimizer and its active cells already satisfy the finite-\(\Gamma\) odds-ratio inequalities.  Under the conjecture's stated hypothesis that every unrestricted optimizer for the endpoint touches a nondegenerate Frechet equality face in the active direction, no such finite-table witness exists.  Thus the refutation search fails in the smallest nontrivial binary selected-arm polytope and the positive proof below applies.

% §10 Interpretation
\paragraph{Interpretation.}
The unrestricted bidirectional principal-strata bound is the same alpha-profile calculation with the armwise selected-mixture odds-ratio constraint removed.  Removing that constraint lets an endpoint place the always-selected type and the selected outcome on a Frechet equality face inside at least one selected arm.  Such a face is an extreme selected-arm table with perfect positive or negative association between always-selected membership and the selected outcome.  A finite collider odds-ratio budget excludes that perfect association whenever the margins are nondegenerate.  Therefore the finite-\(\Gamma\) interval cannot keep an unrestricted endpoint whose every optimizing profile depends on such a face.

The qualification about profile-level compensation is not a new assumption.  It is the only algebraic route by which endpoint equality can survive: the common-alpha curve may contain another unrestricted optimizer whose selected-arm active cells are not on the forbidden Frechet face and already obey the finite odds-ratio budget.  Degenerate selected mixtures, degenerate outcome margins, and Lee-monotonicity boundary cases are listed separately because the odds ratio ceases to exclude the Frechet face in the same way.

% §11 Proof
\begin{proof}
All extrema below are over the compact set \(\mathcal A_\kappa^+(P)\) from Assumption~\ref{ass:interior}.  By Theorem~\ref{thm:arm-quadratic}, for each arm \(d\) and each admissible \(\alpha\), the finite-\(\Gamma\) feasible selected-cell interval is
\[
  T_\Gamma(r_d(\alpha),m_d)
  =
  [\,\rho_{\Gamma^{-1}}(r_d(\alpha),m_d),\rho_\Gamma(r_d(\alpha),m_d)\,],
\]
while the unrestricted interval is
\[
  T_\infty(r_d(\alpha),m_d)
  =
  [\,L_d(\alpha),U_d(\alpha)\,].
\]
Assumption~\ref{ass:gamma-mixture} with finite \(\Gamma\) imposes the additional restriction \(OR_d(t;\alpha)\in[\Gamma^{-1},\Gamma]\).  Hence
\[
  T_\Gamma(r_d(\alpha),m_d)\subseteq T_\infty(r_d(\alpha),m_d).
\]
Since \(r_d(\alpha)\in(0,1)\) by Assumption~\ref{ass:interior}, division by \(r_d(\alpha)\) is order-preserving.  Therefore, for each \(\alpha\),
\[
  \underline a_d(\alpha;P,\infty)
  \le
  \underline a_d(\alpha;P,\Gamma)
  \le
  \overline a_d(\alpha;P,\Gamma)
  \le
  \overline a_d(\alpha;P,\infty).
\]
Combining these armwise inequalities gives the pointwise lower-endpoint inequality
\[
  F_L^\infty(\alpha)
  =
  \underline a_1(\alpha;P,\infty)-\overline a_0(\alpha;P,\infty)
  \le
  \underline a_1(\alpha;P,\Gamma)-\overline a_0(\alpha;P,\Gamma)
  =
  F_L^\Gamma(\alpha),
\]
and the pointwise upper-endpoint inequality
\[
  F_U^\Gamma(\alpha)
  =
  \overline a_1(\alpha;P,\Gamma)-\underline a_0(\alpha;P,\Gamma)
  \le
  \overline a_1(\alpha;P,\infty)-\underline a_0(\alpha;P,\infty)
  =
  F_U^\infty(\alpha).
\]
Taking the minimum of the first display and the maximum of the second display over \(\mathcal A_\kappa^+(P)\) yields
\[
  \theta_L^\infty\le \theta_L^\Gamma,
  \qquad
  \theta_U^\Gamma\le \theta_U^\infty.
\]
By the definitions of the finite-\(\Gamma\) alpha-profile interval and its unrestricted \(\Gamma=\infty\) analogue, this gives
\[
  [\theta_L^\Gamma,\theta_U^\Gamma]\subseteq[\theta_L^\infty,\theta_U^\infty].
\]

It remains to prove strictness.  Consider the lower endpoint.  Let \(\alpha^\star\in\arg\min F_L^\infty\).  The unrestricted lower endpoint uses \(t_1=L_1(\alpha^\star)\) in arm \(1\) and \(t_0=U_0(\alpha^\star)\) in arm \(0\).  If \(t_1=L_1(\alpha^\star)\) is on a nondegenerate Frechet face with \(0<L_1(\alpha^\star)<U_1(\alpha^\star)<1\), then the selected-arm table has \(x_{00}=1-r_1-m_1+L_1=0\) and the other three active cells are nonnegative with the denominator cells positive.  Thus \(OR_1=0<\Gamma^{-1}\), so \(L_1(\alpha^\star)\notin T_\Gamma(r_1(\alpha^\star),m_1)\).  Monotonicity of the odds ratio in Theorem~\ref{thm:arm-quadratic} implies
\[
  \underline a_1(\alpha^\star;P,\Gamma)
  >
  \underline a_1(\alpha^\star;P,\infty).
\]
If instead \(t_0=U_0(\alpha^\star)\) is on a nondegenerate Frechet face, then one denominator cell in the arm \(0\) table is zero, so \(OR_0=+\infty>\Gamma\), and
\[
  \overline a_0(\alpha^\star;P,\Gamma)
  <
  \overline a_0(\alpha^\star;P,\infty).
\]
Either active nondegenerate face therefore gives
\[
  F_L^\Gamma(\alpha^\star)>F_L^\infty(\alpha^\star)=\theta_L^\infty.
\]

Suppose, toward contradiction, that \(\theta_L^\Gamma=\theta_L^\infty\).  By compactness and continuity, choose \(\tilde\alpha\in\arg\min F_L^\Gamma\).  Then
\[
  \theta_L^\infty
  =
  F_L^\Gamma(\tilde\alpha)
  \ge
  F_L^\infty(\tilde\alpha)
  \ge
  \theta_L^\infty.
\]
Both inequalities must be equalities.  Hence \(\tilde\alpha\in\arg\min F_L^\infty\) and \(F_L^\Gamma(\tilde\alpha)=F_L^\infty(\tilde\alpha)\), contradicting the strict inequality just proved for every unrestricted lower-endpoint optimizer under the stated hypothesis.  Therefore \(\theta_L^\infty<\theta_L^\Gamma\).

The upper endpoint is identical with the inequalities reversed.  Let \(\alpha^\star\in\arg\max F_U^\infty\).  The unrestricted upper endpoint uses \(t_1=U_1(\alpha^\star)\) in arm \(1\) and \(t_0=L_0(\alpha^\star)\) in arm \(0\).  A nondegenerate upper face in arm \(1\) has \(OR_1=+\infty\) and forces
\[
  \overline a_1(\alpha^\star;P,\Gamma)
  <
  \overline a_1(\alpha^\star;P,\infty),
\]
whereas a nondegenerate lower face in arm \(0\) has \(OR_0=0\) and forces
\[
  \underline a_0(\alpha^\star;P,\Gamma)
  >
  \underline a_0(\alpha^\star;P,\infty).
\]
In either case \(F_U^\Gamma(\alpha^\star)<F_U^\infty(\alpha^\star)=\theta_U^\infty\).  If \(\theta_U^\Gamma=\theta_U^\infty\), an optimizer \(\tilde\alpha\in\arg\max F_U^\Gamma\) would satisfy
\[
  \theta_U^\infty
  =
  F_U^\Gamma(\tilde\alpha)
  \le
  F_U^\infty(\tilde\alpha)
  \le
  \theta_U^\infty,
\]
so \(\tilde\alpha\in\arg\max F_U^\infty\) and \(F_U^\Gamma(\tilde\alpha)=F_U^\infty(\tilde\alpha)\), again contradicting strict exclusion of the nondegenerate Frechet face at every unrestricted upper-endpoint optimizer.  Therefore \(\theta_U^\Gamma<\theta_U^\infty\).

The profile-compensation clause follows from the same contradiction argument.  If an endpoint equality holds in the interior regime, the finite-\(\Gamma\) optimizer \(\tilde\alpha\) must also be an unrestricted optimizer and must satisfy equality in the pointwise nesting inequality.  Equality in that nesting means the active selected-arm cells used by the endpoint all belong to \(T_\Gamma(r_d(\tilde\alpha),m_d)\), equivalently they obey the finite-\(\Gamma\) odds-ratio inequalities.  Thus any equality not explained by reusing the original exposed Frechet-face optimizer must be explained by a different positive alpha profile that reproduces the unrestricted endpoint while remaining finite-\(\Gamma\)-compatible.
\end{proof}

% §12 Sanity check
\paragraph{Sanity check: no finite odds-ratio restriction.}
When \(\Gamma=\infty\), Assumption~\ref{ass:gamma-mixture} reduces to the Frechet restriction \(T_\infty(r,m)=[L(r,m),U(r,m)]\).  The pointwise nesting inequalities become equalities for every \(\alpha\), so
\[
  F_L^\infty(\alpha)=F_L^\Gamma(\alpha),
  \qquad
  F_U^\infty(\alpha)=F_U^\Gamma(\alpha)
\]
after interpreting \(\Gamma=\infty\).  Hence the finite-\(\Gamma\) strictness conclusion disappears exactly when the odds-ratio budget is removed, as it should.

\paragraph{Sanity check: Lee monotonicity boundary.}
If the reverse-selection budget collapses to the Lee monotonicity face \(H=0\), then the alpha profile can be forced to \(\alpha=p_0\) in the usual case \(p_1\ge p_0\).  If the selected-arm active table at that profile is already compatible with \(OR_d\in[\Gamma^{-1},\Gamma]\), the finite-\(\Gamma\) and unrestricted endpoint values coincide at that boundary.  This is not a contradiction of the theorem because the strict theorem assumes the interior nondegenerate regime and excludes equality only when every unrestricted endpoint optimizer depends on a nondegenerate Frechet equality face that finite \(\Gamma\) rules out.

% §13 Counterexample or minimality check
\paragraph{Minimality check.}
The nondegeneracy condition \(0<L_d(\alpha)<U_d(\alpha)<1\) is needed.  If \(r_d(\alpha)=1\), the selected arm contains only always-selected units, \(t_d=m_d\), and the odds ratio is not a meaningful finite-table separator of the Frechet endpoint; the finite and unrestricted armwise means both equal \(m_d\).  If \(m_d\in\{0,1\}\), the selected outcome is deterministic in the arm, so the always-selected mean is pinned at the same boundary value regardless of the odds-ratio budget.  Finally, if the reverse-selection budget fixes the Lee monotonicity profile and the active table at that profile is already finite-\(\Gamma\)-compatible, then equality is caused by the collapsed profile rather than by a failure of the strict-exclusion argument.  These cases explain why the theorem is stated for exposed nondegenerate Frechet faces inside Assumption~\ref{ass:interior} and why the conjecture lists the boundary equality cases separately.
