\begin{proposition}[Partial resolution of Conjecture~\ref{conj:lee-gamma-frontier}]\label{prop:lee-gamma-frontier-partial}
The claim under test is the following verbatim statement from the proposal.

\begin{quote}
Under Assumptions~\ref{ass:random-consistency}--\ref{ass:interior}, the sharp identified set for the always-selected effect is
\[
  \Theta_I(P;\Gamma,\kappa)=
  \left[
    \inf_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\underline a_1(\alpha)-\overline a_0(\alpha)\},
    \sup_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\overline a_1(\alpha)-\underline a_0(\alpha)\}
  \right],
\]
where \(\underline a_d(\alpha)\) and \(\overline a_d(\alpha)\) are the armwise quadratic endpoints from Theorem~\ref{thm:arm-quadratic}.  Moreover, each global endpoint is attained by an explicit four-stratum law \((A,G,H,N)\) whose two selected-arm \(2\times2\) tables saturate the appropriate odds-ratio boundary, and the optimizing \(\alpha\) is either an endpoint of \(\mathcal A_\kappa^+(P)\) or a root of the derivative of a quadratic-radical profile induced by the active odds-ratio equations.
For an open set of observable laws satisfying the comparison regime in Assumption~\ref{ass:exposed-endpoints}, this frontier is conjectured not to be representable as either the \citet{HuberMellace2015SharpSelection} monotonicity/stochastic-dominance sharp-bound geometry, a \citet{LaffersNedela2017Sensitivity} Lee sensitivity program with only monotonicity/exogeneity relaxation parameters, a \citet{Semenova2025GeneralizedLee} conditional-monotonicity Lee bound, the stochastic-monotonicity-plus-symmetry geometry of \citet{Okamoto2025RobustifyLee}, or a margin-free application of the \citet{ShepherdGilbertJemiaiRotnitzky2006}, \citet{JemiaiRotnitzkyShepherdGilbert2007}, \citet{ShepherdRedmanAnkerst2008}, and \citet{ShepherdGilbertDupont2011} beta/psi principal-stratum sensitivity family.  The statement explicitly concedes that beta \(=\log OR_d(t_d;r_d(\alpha),m_d)\) reproduces each armwise selected table; the conjectured non-equivalence is the sharper claim that without adding the same \(\alpha\)-coupling and \(H\le \kappa p_0\) restriction, those armwise beta tables do not define the same global sharp ATE endpoint.  The distinguishing certificate is an interior active odds-ratio equality \(OR_d(t_d;r_d(\alpha),m_d)\in\{\Gamma^{-1},\Gamma\}\) plus the cross-arm equalities \(p_1r_1(\alpha)=p_0r_0(\alpha)=\alpha\), with no tail-trimming quantile cutoff, stochastic-dominance ordering, stochastic monotonicity/symmetry condition, covariate sign partition, or right-censoring survival model that pins the same coupled selected-cell endpoint.  A concrete open-cell witness target is \(p_1=0.6\), \(p_0=0.5\), \(m_1=0.5\), \(m_0=0.4\), \(\Gamma=4\), \(\kappa=0.5\), and \(\alpha=0.3\): both \(G=0.3\) and \(H=0.2\) are positive.  At this witness the local upper ATE endpoint uses \(t_1=1/3\) and \(t_0=(-1+\sqrt{3.88})/6\), while the local lower ATE endpoint uses \(t_1=1/6\) and \(t_0=(4-\sqrt{4.48})/6\); the corresponding armwise beta values are \(\pm\log 4\), so the certificate is not the absence of a log-odds parametrization but the extra \((\alpha,\kappa)\) compatibility restriction:
\[
\begin{array}{c|cc|c|c}
\text{arm/endpoint} & P(A,Y=1\mid S(d)=1) & P(A,Y=0\mid S(d)=1) &
P(A^c,Y=1\mid S(d)=1) & P(A^c,Y=0\mid S(d)=1)\\
\hline
d=1,\ \text{upper} & 0.333 & 0.167 & 0.167 & 0.333\\
d=1,\ \text{lower} & 0.167 & 0.333 & 0.333 & 0.167\\
d=0,\ \text{upper for }a_0 & 0.314 & 0.286 & 0.086 & 0.314\\
d=0,\ \text{lower for }a_0 & 0.162 & 0.438 & 0.238 & 0.162
\end{array}
\]
Thus the displayed witness gives local ATE values approximately \([-0.190,0.397]\) at \(\alpha=0.3\), with all active cells interior rather than tail-trimming faces.
\end{quote}

Partial verdict: Assumptions~\ref{ass:random-consistency}--\ref{ass:interior} imply the sharp common-\(\alpha\) frontier displayed in Conjecture~\ref{conj:lee-gamma-frontier}; the additional open-set non-representability assertions relative to external comparator geometries are not confirmed by the finite-table assumptions alone.
\end{proposition}

\paragraph{Section 13 refutation attempt before positive proof.}
The required refutation primitive is the finite binary response-type LP.  Fix an admissible \(\alpha\in\mathcal A_\kappa^+(P)\).  The principal-stratum masses are forced by the observed selected shares:
\[
  P(A)=\alpha,\qquad P(G)=p_1-\alpha,\qquad
  P(H)=p_0-\alpha,\qquad P(N)=1-p_0-p_1+\alpha .
\]
Assumptions~\ref{ass:random-consistency}, \ref{ass:binary-support}, and \ref{ass:reverse-budget} make these masses nonnegative and impose \(p_0-\alpha\le \kappa p_0\).  Conditional on \(S(d)=1\), the selected-arm LP has the four cells
\[
  t_d,\qquad r_d(\alpha)-t_d,\qquad m_d-t_d,\qquad
  1-r_d(\alpha)-m_d+t_d ,
\]
and Assumption~\ref{ass:gamma-mixture} adds the two quadratic inequalities in
Theorem~\ref{thm:arm-quadratic}.  Thus the LP feasible set at fixed \(\alpha\)
is exactly
\[
  t_1\in[\underline t_1(\alpha),\overline t_1(\alpha)],
  \qquad
  t_0\in[\underline t_0(\alpha),\overline t_0(\alpha)],
\]
where \(\underline t_d(\alpha)=r_d(\alpha)\underline a_d(\alpha)\) and
\(\overline t_d(\alpha)=r_d(\alpha)\overline a_d(\alpha)\).  The objective is
\[
  \theta(t_1,t_0;\alpha)
  =
  \frac{t_1}{r_1(\alpha)}-\frac{t_0}{r_0(\alpha)} .
\]
The vertex enumeration is therefore exhaustive: the minimum is attained at
\((\underline t_1(\alpha),\overline t_0(\alpha))\) and the maximum is attained
at \((\overline t_1(\alpha),\underline t_0(\alpha))\).  No fixed-\(\alpha\)
response-type vertex lies outside the conjectured local interval.

At the concrete witness stated in the conjecture,
\[
  r_1(0.3)=0.5,\qquad r_0(0.3)=0.6.
\]
The active roots are
\[
  \underline t_1=1/6,\quad \overline t_1=1/3,\quad
  \underline t_0=(-1+\sqrt{3.88})/6\approx 0.161629,\quad
  \overline t_0=(4-\sqrt{4.48})/6\approx 0.313900 .
\]
The four objective values at the fixed-\(\alpha\) vertices are approximately
\[
  -0.189833,\qquad 0.063952,\qquad 0.143500,\qquad 0.397286 .
\]
Hence the displayed witness does not refute the sharp common-\(\alpha\)
frontier; it realizes the local interval claimed in the conjecture, with both
one-sided strata positive.  The primitive also does not prove the final
open-set non-representability sentence, because the named comparator
geometries are not encoded in the finite-table LP as explicit feasible sets or
support functions.  The honest outcome is therefore a partial verdict: the
sharp frontier is proved below, while the external-comparator non-equivalence
claim remains a definition-level gap rather than a counterexample.

\paragraph{Section 10 interpretation.}
The confirmed content is a sharp bound for the causal target
\(\theta=\E[Y(1)-Y(0)\mid A]\), not a point-identification statement.  The
observable law \(P\) identifies \(p_d\) and \(m_d\), but not the latent
always-selected share \(\alpha\) nor the always-selected means.  The theorem
reduces the latent problem to a one-dimensional computable profile.  For each
candidate \(\alpha\), the two selected arms are ordinary \(2\times2\) tables
with known margins.  The odds-ratio sensitivity bound cuts out a closed
interval of feasible always-selected means in each arm, and the common
\(\alpha\) and harmed-budget restrictions say which two armwise tables can be
glued into one four-stratum principal-strata law.

\paragraph{Section 11 proof of the confirmed sharp-frontier component.}
We prove the sharp-frontier and endpoint-attainment parts of
Proposition~\ref{prop:lee-gamma-frontier-partial}.  By
Assumption~\ref{ass:random-consistency}, the observed selected share and
selected mean in arm \(d\) equal \(p_d=P(S(d)=1)\) and
\(m_d=P(Y(d)=1\mid S(d)=1)\).  By Assumption~\ref{ass:binary-support}, these
quantities lie in \((0,1)\).

First take any compatible full law.  Let
\(\alpha=P(A)=P(S(0)=1,S(1)=1)\).  The identities
\[
  P(G)=p_1-\alpha,\qquad P(H)=p_0-\alpha,\qquad
  P(N)=1-p_0-p_1+\alpha
\]
follow from the four principal strata and the definitions of \(p_0,p_1\).
Nonnegativity of these masses and Assumption~\ref{ass:reverse-budget} imply
\(\alpha\in\mathcal A_\kappa^+(P)\).  Since \(S(d)=1\) consists of the
always-selected stratum plus the one-sided stratum selected in arm \(d\),
\[
  P(A\mid S(d)=1)=r_d(\alpha)=\alpha/p_d .
\]
Let \(t_d=P(A,Y(d)=1\mid S(d)=1)\).  Assumption~\ref{ass:gamma-mixture} and
Theorem~\ref{thm:arm-quadratic} imply
\[
  \underline a_d(\alpha)\le
  \E[Y(d)\mid A]=\frac{t_d}{r_d(\alpha)}
  \le \overline a_d(\alpha).
\]
Therefore every compatible law satisfies, for its own \(\alpha\),
\[
  \underline a_1(\alpha)-\overline a_0(\alpha)
  \le
  \theta
  \le
  \overline a_1(\alpha)-\underline a_0(\alpha).
\]
Taking the infimum and supremum over
\(\alpha\in\mathcal A_\kappa^+(P)\) gives the outer inclusion
\[
  \Theta_I(P;\Gamma,\kappa)
  \subseteq
  \left[
    \inf_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\underline a_1(\alpha)-\overline a_0(\alpha)\},
    \sup_{\alpha\in\mathcal A_\kappa^+(P)}
      \{\overline a_1(\alpha)-\underline a_0(\alpha)\}
  \right].
\]

We next prove attainability.  Fix \(\alpha\in\mathcal A_\kappa^+(P)\).  Set
\[
  g=p_1-\alpha,\qquad h=p_0-\alpha,\qquad n=1-p_0-p_1+\alpha .
\]
These are nonnegative by the definition of \(\mathcal A_\kappa^+(P)\), and
\(h\le \kappa p_0\) by Assumption~\ref{ass:reverse-budget}.  Choose any
\[
  t_d\in
  [r_d(\alpha)\underline a_d(\alpha),
   r_d(\alpha)\overline a_d(\alpha)]
\]
for \(d=0,1\).  By Theorem~\ref{thm:arm-quadratic}, the four selected-arm cell
probabilities are nonnegative and obey the odds-ratio bound.  Put
\[
  a_d=t_d/r_d(\alpha).
\]
On the always-selected stratum \(A\), assign any binary joint distribution for
\((Y(0),Y(1))\) with marginal means \(a_0\) and \(a_1\); such a joint
distribution exists because every pair of Bernoulli marginals has a Frechet
coupling.  On \(G\), choose \(Y(1)\) to have mean
\[
  \frac{m_1-t_1}{1-r_1(\alpha)},
\]
and choose \(Y(0)\) arbitrarily.  On \(H\), choose \(Y(0)\) to have mean
\[
  \frac{m_0-t_0}{1-r_0(\alpha)},
\]
and choose \(Y(1)\) arbitrarily.  On \(N\), choose both potential outcomes
arbitrarily.  The displayed means for \(G\) and \(H\) lie in \([0,1]\) because
the selected-arm Frechet inequalities hold.  Assumption~\ref{ass:interior}
ensures \(r_d(\alpha)\in(0,1)\), so the divisions by
\(1-r_d(\alpha)\) are legitimate.

The constructed law has principal-stratum masses \((\alpha,g,h,n)\), hence it
reproduces \(p_0,p_1\).  Its selected-arm means are
\[
  r_d(\alpha)a_d+\{1-r_d(\alpha)\}
  \frac{m_d-t_d}{1-r_d(\alpha)}
  =
  t_d+(m_d-t_d)
  =
  m_d,
\]
so it reproduces the observable law \(P\) on \((D,S,SY)\).  Its odds-ratio
restriction is exactly the selected-arm restriction used to choose \(t_d\), and
its target value is \(a_1-a_0\).

For this fixed \(\alpha\), the set of attainable target values is therefore
\[
  [\underline a_1(\alpha),\overline a_1(\alpha)]
  -
  [\underline a_0(\alpha),\overline a_0(\alpha)]
  =
  [\underline a_1(\alpha)-\overline a_0(\alpha),
   \overline a_1(\alpha)-\underline a_0(\alpha)].
\]
The union of these intervals over \(\alpha\in\mathcal A_\kappa^+(P)\) is itself
an interval.  To see this, suppose a real number \(y\) is missed by the union.
Then for each \(\alpha\), either the local upper endpoint is below \(y\) or the
local lower endpoint is above \(y\).  The two alternatives define disjoint open
sets in the connected compact interval \(\mathcal A_\kappa^+(P)\).  Continuity
of the quadratic-root endpoints rules out a separation between any two
attained values on opposite sides of \(y\).  Hence the union is exactly the
global interval whose endpoints are the displayed infimum and supremum.

Under Assumption~\ref{ass:interior}, the endpoint functions are continuous
quadratic-root functions of \(\alpha\) on a compact interval, so the infimum
and supremum are attained.  In the finite interior case \(\Gamma\in(1,\infty)\),
Theorem~\ref{thm:arm-quadratic} places each armwise endpoint on one of the two
active odds-ratio equalities \(OR_d=\Gamma^{-1}\) or \(OR_d=\Gamma\), rather
than on a degenerate Frechet face.  Therefore each global endpoint is attained
by the four-stratum construction above with the appropriate selected-arm
tables saturating the relevant odds-ratio boundary.  If the optimizing
\(\alpha\) is not \(\alpha_-\) or \(\alpha_+\), Fermat's rule applies to the
active quadratic-radical profile and the derivative of that profile is zero.
This proves the sharp common-\(\alpha\) frontier and the endpoint
characterization.

The remaining literature non-representability clause is not proved by this
argument.  The proof has only used the finite response-type law, the
common-\(\alpha\) curve, the harmed-budget inequality, and the selected-arm
odds-ratio faces.  It does not define the cited external procedures as
mathematical support functions on the same input space, so it cannot establish
an open-set non-representability theorem against them.

\paragraph{Section 12 sanity check.}
At the witness in the conjecture, \(p_1=0.6\), \(p_0=0.5\), and
\(\alpha=0.3\).  Hence \(g=0.3\), \(h=0.2\), and
\(n=1-0.6-0.5+0.3=0.2\), all nonnegative, and the harmed budget is saturated:
\[
  h=0.2=\kappa p_0=0.5\cdot 0.5 .
\]
The selected-arm always shares are \(r_1=0.3/0.6=0.5\) and
\(r_0=0.3/0.5=0.6\).  With \(m_1=0.5\), the two active odds-ratio roots are
\(\underline t_1=1/6\) and \(\overline t_1=1/3\).  With \(m_0=0.4\), the
corresponding roots are
\[
  \underline t_0=(-1+\sqrt{3.88})/6,\qquad
  \overline t_0=(4-\sqrt{4.48})/6 .
\]
Thus the local lower and upper ATE endpoints are
\[
  \frac{1/6}{0.5}-\frac{(4-\sqrt{4.48})/6}{0.6}
  \approx -0.190,
  \qquad
  \frac{1/3}{0.5}-\frac{(-1+\sqrt{3.88})/6}{0.6}
  \approx 0.397 .
\]
This matches the proposal's local interval and confirms that the active cells
are interior odds-ratio faces rather than Lee tail-trimming faces.

\paragraph{Section 13 counterexample or minimality check after proof.}
The common-\(\alpha\) restriction is necessary for sharpness of the stated
frontier.  If it is dropped, one can choose armwise always-selected shares
\(q_1\) and \(q_0\) independently.  At the witness, the sharp law uses
\(q_1=r_1=0.5\) and \(q_0=r_0=0.6\), which satisfy the compatibility equality
\[
  p_1q_1=0.6\cdot 0.5=0.3
  =
  0.5\cdot 0.6=p_0q_0 .
\]
If instead a comparator selects \(q_1=0.5\) and \(q_0=0.5\), both armwise
selected tables can still be parameterized by log odds ratios, but
\[
  p_1q_1=0.30\ne 0.25=p_0q_0 .
\]
No single principal-strata law can have two different masses for the same
always-selected stratum \(A\).  This is the minimal obstruction behind the
common-\(\alpha\) frontier: armwise beta tables are not enough; the selected-arm
shares must glue through one latent mass \(\alpha\) and must also obey
\(p_0-\alpha\le \kappa p_0\).
