% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_mte\_multi\_iv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_mte\_multi\_iv} / \texttt{v1}%
  \\ \large\textit{A pre-saturated face-rank certificate for when multi-IV MST all-split bounds beat coordinate shortcuts}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Partial-identification anchor with locked tuple
\[
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
\text{bounding functional})
\]
as follows.  \texttt{qid}=\texttt{pid\_mte\_multi\_iv} and
\texttt{specialization}=\texttt{v1}.  The observable distribution \(P\) is the
joint law of \((Y,D,Z)\), where \(D\in\{0,1\}\), \(Z\in{\cal Z}\subseteq
\{0,1\}^K\) with \(K\ge 2\), every \(z\in{\cal Z}\) has positive probability,
and \(p_z=\Pr_P(D=1\mid Z=z)\) is known from \(P\).  The target parameter is
\(\theta(q)=q^\transpose\beta\), the Bernstein-basis projection of a
policy-relevant treatment-effect weight \(q=\int_0^1\omega_{\rm prte}(u)
B_J(u)\,du\) against an unknown MTE coefficient vector \(\beta\in\R^{J+1}\).
The identifying restrictions are instrument exogeneity and exclusion,
latent-index selection \(D_z=\one\{U\le p_z\}\) with \(U\sim{\rm Unif}[0,1]\),
the Bernstein MTE representation \(m(u)=B_J(u)^\transpose\beta\), and the
shape restrictions \(L\beta\le r\).  The bounding functional is the saturated
all-IV-like MST/Han--Yang linear program over all nonzero propensity-score
contrasts among cells in \({\cal Z}\), compared endpoint-by-endpoint with the
best retained-coordinate shortcut whose coarsened Wald row is computed from
the conditional
selection-probability contrast \(u\mapsto
\Pr(p_Z\ge u\mid Z_j=1)-\Pr(p_Z\ge u\mid Z_j=0)\).  The proposed
adequacy diagnostic is the endpoint-specific face-rank residual certificate
\(\tau_{e,j}\) defined in Section 6 from the tied coordinate-optimal face and
the saturated all-split moment rows, before solving the saturated endpoint.

\begin{abstract}
This proposal asks for an endpoint-level adequacy certificate for a common
multi-instrument shortcut: using the best retained binary coordinate instead
of the saturated all-IV-like MTE/PRTE bound already permitted by
\citet{MogstadSantosTorgovitsky2018} and sharpened computationally by
\citet{HanYang2024}.  The finite-dimensional LP itself is published
machinery, not the novelty claim.  The novel kernel is the conjectured
frontier theorem: before solving the saturated endpoint, one can solve only
the tied coordinate endpoint LPs and then apply a rank/projection test to the
residual all-split moment rows on their optimal faces.  Strict improvement
occurs exactly when every tied coordinate-optimal face fails this residual
moment test, and the resulting endpoint gain is represented by a residual
face-restricted dual program rather than by a generic restatement of nested LP
endpoints.  Resolving this would turn MST's split-instrument examples and the
recent binary-IV LP literature into a checkable diagnostic for when a multi-IV
design adds policy-relevant information beyond coordinate-wise single-IV
reporting.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Policy-relevant treatment effects usually require extrapolating away from the
local population moved by a particular instrument.  When an application has
several binary instruments, applied researchers often hope that the instruments
jointly cover more of the latent resistance distribution than any one
instrument does.  \citet{MogstadSantosTorgovitsky2018} already allow
IV-like estimands generated from discrete or split instruments, and
\citet{HanYang2024} give sharp binary-IV computational bounds, but neither
paper gives an endpoint-level test for when a retained-coordinate shortcut is
lossless relative to the saturated all-split procedure.

\paragraph{The main finding (proposed).}
The proposed headline result is Conjecture 1: under the locked latent-index and
Bernstein-shape convention, the saturated all-IV-like PRTE interval uses the
published MST/Han--Yang row system, while the adequacy of the best
retained-coordinate shortcut is decided by a pre-saturated face-rank
certificate.  For each tied coordinate endpoint, the researcher solves the
coordinate LP only, records the exposed optimal face, residualizes the
saturated all-split rows against the coordinate row and active shape rows, and
checks whether the residual joint moments lie in the projected affine hull of
that face.  The finite LP and the single-instrument limit are treated as
benchmark normalizations rather than flagship contributions.

\paragraph{What is new.}
The closest published paper is \citet{MogstadSantosTorgovitsky2018}, which
shows how arbitrary IV-like estimands, including estimands generated by
splitting a discrete instrument, restrict MTE/MTR functions.  Recent multi-IV
work by \citet{MogstadTorgovitskyWalters2024} shows that multiple instruments
can be aggregated more informatively under partial monotonicity and mutual
consistency, while \citet{HanYang2024} gives sharp computational bounds for
policy-relevant weighted MTE averages with binary instruments.  The novelty
kernel here is not a new LP and not the claim that splitting can tighten
bounds; it is the algebraic frontier between two named procedures, the
retained-coordinate shortcut and the saturated all-IV-like MST/Han--Yang
system.  The epsilon gap is an if-and-only-if pre-saturated threshold:
coordinate-wise reporting is endpoint-adequate exactly when at least one tied
coordinate-optimal face passes a residual all-split rank/projection test,
where the test uses only the coordinate endpoint solution, the active
Bernstein-shape face, and the joint propensity-contrast row geometry.  This is
not the support-function endpoint drop itself; it is a diagnostic that says,
before solving the saturated endpoint, whether the saturated endpoint can
possibly equal the best coordinate endpoint.

\paragraph{How it positions in the literature.}
The anchor cluster is partial identification for IV/MTE policy parameters:
\citet{HeckmanVytlacil2005} and \citet{Vytlacil2002} supply the latent-index
MTE framework, \citet{BrinchMogstadWiswall2017} is the close
discrete-instrument comparator for identifying richer MTE structure from
finite propensity support, \citet{ManskiPepper2000} supplies the
shape-restricted partial-ID tradition, and
\citet{MogstadSantosTorgovitsky2018} gives the IV-like Bernstein LP
benchmark, including split-instrument comparisons.  The multi-IV frontier is represented by
\citet{MogstadTorgovitskyWalters2021}, \citet{MogstadTorgovitskyWalters2024},
\citet{Goff2024}, and \citet{HanYang2024}; this proposal sits at the point
where their multiple-instrument support logic meets MST-style PRTE
extrapolation.  The flagship gap relative to
\citet{MogstadSantosTorgovitsky2018} and \citet{HanYang2024} is
endpoint-specific: those papers give the procedures whose LP endpoints can be
computed, while this proposal asks when the lower-dimensional
coordinate-wise report is already adequate and when the saturated endpoint
must be reported instead.

\paragraph{Implications for the community.}
If Conjecture 1 is true, empirical users of the MST framework in
labor-market and education-return designs with several eligibility, distance,
or encouragement instruments can report a reproducible diagnostic for each
endpoint: the face-rank residual certificate showing whether the saturated all-split
MST/Han--Yang analysis tightens the PRTE interval beyond the best
coordinate-wise analysis; the residual dual value is then reported only when
the certificate predicts a gain.

\paragraph{How research benefits from the conclusion.}
Researchers should report the saturated all-split PRTE endpoint whenever the
face-rank residual certificate is positive in the policy-weight direction;
otherwise the best retained-coordinate interval is an adequate summary for
that endpoint.

\section{Related work}
\citet{Vytlacil2002} proves the equivalence between latent-index selection
models and the LATE framework, which justifies using propensity-score
intervals as MTE weights.  \citet{HeckmanVytlacil2005} develops the MTE policy
evaluation framework and explains why local IV estimands need not answer the
policy question of interest.  \citet{ManskiPepper2000} is the shape-restricted
partial-identification ancestor for the \(L\beta\le r\) restrictions used
below.  \citet{BrinchMogstadWiswall2017} shows that a discrete instrument can
identify richer MTE specifications under functional structure; it is a close
comparator because it uses finite propensity support for MTE identification,
but it does not supply a PRTE endpoint adequacy frontier between a coordinate
shortcut and a saturated all-split IV-like system.  \citet{MogstadSantosTorgovitsky2018}
is the closest benchmark: it expresses IV-like estimands and policy
parameters as weighted averages of MTE/MTR functions, computes
Bernstein-polynomial LP bounds, and shows that splitting discrete instrument
variation can tighten bounds.  The proposal therefore treats the MST all-split
LP as published machinery and asks for the missing necessary-and-sufficient
endpoint diagnostic.
\citet{MogstadTorgovitsky2018Review} reviews why PRTE analysis usually
requires extrapolation from instrument-affected individuals to policy-affected
individuals.

\citet{MogstadTorgovitskyWalters2021} shows that full monotonicity with
multiple IVs is so restrictive that choice behavior is effectively
homogeneous, motivating weaker multi-IV monotonicity concepts.  \citet{Goff2024}
gives a vector-monotonicity theory for binary multiple instruments and
identifies LATE-type parameters, but it does not characterize Bernstein-basis
PRTE support gaps.  \citet{MogstadTorgovitskyWalters2024} is the closest
multi-IV MTE paper because it aggregates information from multiple instruments
through partial monotonicity and mutual consistency; the present proposal asks
for a sharper endpoint comparison between the best coordinate shortcut and the
saturated all-split MST/Han--Yang interval.
\citet{HanYang2024}
provides sharp LP bounds for policy-relevant weighted averages of the MTE with
binary instruments, making it an important prior-art candidate for the
saturated primal LP but not for the coordinate-adequacy frontier.  \citet{Marx2024}
derives analytic sharp bounds for latent-index MTE functionals using full
marginal-distribution content; it is adjacent because it clarifies what is
lost when the design supplies only finite binary-IV moments.
Standard convex-analysis and linear-programming results, as in
\citet{Rockafellar1970}, already imply support-function monotonicity and
duality for nested polyhedra.  Those generic facts are deliberately not the
claimed contribution; the proposed novelty is the econometric specialization
that converts the multiple-binary-IV propensity geometry into a
pre-saturated face-rank adequacy certificate for MST/Han--Yang PRTE endpoints.

In-repo prior art from the Stage -1.1 scout reports no existing
\texttt{pid\_mte\_multi\_iv} proposal or review under
\texttt{doc/research}.  The closest accepted or banked
CausalSmith artifacts are \texttt{pid\_dose\_response\_iv\_v1} and
\texttt{pid\_ordinal\_late\_partial\_defiers\_v1}, both IV partial-ID LP
proposals that are not MTE/PRTE multi-instrument Bernstein kernels, and
\texttt{pid\_dynamic\_iv\_compliance\_v1}, whose bank note warns that generic
finite latent-type LP sharpness and generic LP duality are not enough for a
novel proposal.  The relevant \texttt{doc/API.md} family is PartialID rather
than Panel or ExactID.

\section{Formal setup}
Let \(Z\in{\cal Z}\subseteq\{0,1\}^K\), \(K\ge2\), have cell probabilities
\(\pi_z=\Pr(Z=z)>0\), and let \(p_z=\Pr(D=1\mid Z=z)\).  Potential outcomes
\((Y_0,Y_1)\) and the latent resistance \(U\sim{\rm Unif}[0,1]\) satisfy
\(D_z=\one\{U\le p_z\}\) and \(Y=DY_1+(1-D)Y_0\).  The MTE curve is
\[
m(u)=\E[Y_1-Y_0\mid U=u]=B_J(u)^\transpose\beta,\qquad
B_J(u)_\ell={J\choose \ell}u^\ell(1-u)^{J-\ell},\quad \ell=0,\ldots,J .
\]
For every ordered contrast \(a=(z,z')\) with \(p_z>p_{z'}\), define
\[
w_a=\frac{1}{p_z-p_{z'}}\int_{p_{z'}}^{p_z}B_J(u)\,du,\qquad
\gamma_a=\frac{\E[Y\mid Z=z]-\E[Y\mid Z=z']}{p_z-p_{z'}}.
\]
The joint matrix \(M_{\rm joint}\) stacks all rows \(w_a^\transpose\), and
\(\gamma_{\rm joint}\) stacks the corresponding \(\gamma_a\).  In this
proposal \(M_{\rm joint}\) is interpreted as the saturated all-split
MST/Han--Yang benchmark row system, not as a new identification procedure.
For each coordinate \(j\), write \(\pi_{j,b}=\Pr(Z_j=b)\),
\(\bar p_{j,b}=\E[p_Z\mid Z_j=b]\), and
\(\bar y_{j,b}=\E[Y\mid Z_j=b]\).  If
\(d_j=\bar p_{j,1}-\bar p_{j,0}\ne0\), the retained-coordinate MST-style row is
\[
w_j=\frac{1}{d_j}\int_0^1
\{\Pr(p_Z\ge u\mid Z_j=1)-\Pr(p_Z\ge u\mid Z_j=0)\}B_J(u)\,du,\qquad
\gamma_j=\frac{\bar y_{j,1}-\bar y_{j,0}}{d_j}.
\]
Thus \(M_j\) is the one-row matrix \(w_j^\transpose\).  This row reduces to
the usual single-IV interval row
\((\bar p_{j,1}-\bar p_{j,0})^{-1}\int_{\bar p_{j,0}}^{\bar p_{j,1}}B_J(u)\,du\)
only when \(p_Z\) is conditionally degenerate within each retained value of
\(Z_j\), up to orientation.  Shape restrictions are \(L\beta\le r\), where
\(L\) may encode bounded outcomes, monotonicity, convexity, or Bernstein
coefficient restrictions.  The identified interval for a row vector \(q\) is
\[
\Theta_I(P;q,M,\gamma)=
\{q^\transpose\beta: M\beta=\gamma,\ L\beta\le r\}.
\]
Its lower and upper endpoints are denoted \(L(M,\gamma;q)\) and
\(U(M,\gamma;q)\).  The endpoint-specific best retained-coordinate benchmarks are
\[
L_{\rm sing}=\max_j L(M_j,\gamma_j;q),\qquad
U_{\rm sing}=\min_j U(M_j,\gamma_j;q).
\]
Let \({\cal J}_L=\arg\max_j L(M_j,\gamma_j;q)\) and
\({\cal J}_U=\arg\min_j U(M_j,\gamma_j;q)\).  Strict-gain claims are indexed
over every optimizer in the relevant argmax/argmin set; no tie-breaking rule
is used in the proposed frontier statistic.

For \(e\in\{U,L\}\), set \(s_U=q\), \(s_L=-q\), and define
\({\cal J}_e={\cal J}_U\) for \(e=U\) and \({\cal J}_e={\cal J}_L\) for
\(e=L\).  For each \(j\in{\cal J}_e\), let
\[
F_{e,j}=\{\beta:M_j\beta=\gamma_j,\ L\beta\le r\},\qquad
{\cal O}_{e,j}=\arg\max_{\beta\in F_{e,j}}s_e^\transpose\beta ,
\]
and let
\[
{\cal A}_{\rm joint}=\{\beta:M_{\rm joint}\beta=\gamma_{\rm joint}\}.
\]
The tied-face residual support width is
\[
W_{e,j}(P;q,L,r)=
h_{F_{e,j}}(s_e)-h_{F_{e,j}\cap{\cal A}_{\rm joint}}(s_e),
\qquad
h_A(s)=\sup_{\beta\in A}s^\transpose\beta ,
\]
and the endpoint width is \(W_e(P;q,L,r)=\min_{j\in{\cal J}_e}W_{e,j}(P;q,L,r)\).
To make the face-separation statistic invariant to the arbitrary scaling or
basis used to write residual moment rows, define the Bernstein Gram matrix
\[
G_J=\int_0^1B_J(u)B_J(u)^\transpose\,du
\]
and the induced function-space distance
\[
\operatorname{dist}_J(\beta,A)=
\inf_{\tilde\beta\in A}\{(\beta-\tilde\beta)^\transpose
G_J(\beta-\tilde\beta)\}^{1/2}.
\]
The optimizer-indexed endpoint-frontier statistic is
\[
\kappa_{e,j}(P;q,L,r)=
\inf_{\beta\in{\cal O}_{e,j}}
\operatorname{dist}_J(\beta,F_{e,j}\cap{\cal A}_{\rm joint}).
\]
Both \(W_{e,j}\) and \(\kappa_{e,j}\) depend on the outcome moments
\(\gamma\) and on the shape system \(L\beta\le r\), not only on the
propensity support; the propensity distribution determines the row maps
\(M_{\rm joint}\) and \(M_j\), while \(\operatorname{dist}_J\) is tied to the
locked Bernstein basis rather than to a residual-row representation.

The flagship adequacy object is a pre-saturated face-rank certificate, not the
endpoint drop \(W_{e,j}\).  For each tied coordinate optimum define
\({\cal B}_{e,j}\) as the set of rows of \(L\) that are tight for every
\(\beta\in{\cal O}_{e,j}\).  Let \(L_{{\cal B}_{e,j}}\) and
\(r_{{\cal B}_{e,j}}\) collect those rows and right-hand sides.  Set
\[
H_{e,j}=\begin{bmatrix}M_j\\ L_{{\cal B}_{e,j}}\\ s_e^\transpose\end{bmatrix},
\qquad
b_{e,j}=\begin{bmatrix}\gamma_j\\ r_{{\cal B}_{e,j}}\\
h_{F_{e,j}}(s_e)\end{bmatrix}.
\]
Choose any \(\beta^0_{e,j}\) satisfying \(H_{e,j}\beta=b_{e,j}\), and let
\({\cal N}_{e,j}=\{v:H_{e,j}v=0\}\).  The residual all-split consistency
distance is
\[
\tau_{e,j}(P;q,L,r,\gamma)=
\operatorname{dist}\bigl(\gamma_{\rm joint}-M_{\rm joint}\beta^0_{e,j},
M_{\rm joint}{\cal N}_{e,j}\bigr),
\]
where the distance is Euclidean in the finite vector space of saturated
contrast moments.  This number is independent of the representative
\(\beta^0_{e,j}\), equals zero exactly when the coordinate-optimal face
contains a coefficient vector satisfying all saturated rows, and can be
computed by the rank test
\[
\operatorname{rank}\begin{bmatrix}H_{e,j}\\ M_{\rm joint}\end{bmatrix}
=
\operatorname{rank}\begin{bmatrix}H_{e,j}&b_{e,j}\\
M_{\rm joint}&\gamma_{\rm joint}\end{bmatrix}.
\]
Thus \(\tau_{e,j}\) is available after solving the coordinate endpoint LP and
before solving the saturated all-split endpoint LP.

\begin{verbatim}
Locked tuple:
qid = pid_mte_multi_iv
specialization = v1
P = joint observable law of (Y,D,Z), Z in {0,1}^K, K >= 2
theta = q^T beta, a PRTE Bernstein-basis functional of the MTE curve
identifying restrictions = IV exogeneity/exclusion, latent-index selection,
  Bernstein MTE m(u)=B_J(u)^T beta, and shape restrictions L beta <= r
bounding functional = saturated all-split MST/Han-Yang LP using all nonzero
  propensity contrasts, compared endpoint-by-endpoint with the best
  retained-coordinate shortcut,
  whose coarsened Wald row is E[1{p_Z >= u}|Z_j=1]-E[1{p_Z >= u}|Z_j=0]
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Observed support and overlap]\label{ass:support}
\({\cal Z}\subseteq\{0,1\}^K\) is finite with \(K\ge2\), \(\pi_z>0\) for all
\(z\in{\cal Z}\), and at least two cells have distinct propensities \(p_z\).
Every contrast used in \(M_{\rm joint}\) has nonzero cell-level propensity
difference, and every retained coordinate considered for the coordinate
benchmark has \(d_j=\bar p_{j,1}-\bar p_{j,0}\ne0\).
\end{assumption}

\begin{assumption}[Latent-index IV validity]\label{ass:latent}
\((Y_0,Y_1,U)\perp Z\), \(Y=DY_1+(1-D)Y_0\), and
\(D_z=\one\{U\le p_z\}\) with \(U\sim{\rm Unif}[0,1]\).  The propensity values
\(\{p_z:z\in{\cal Z}\}\) are the observable conditional treatment
probabilities.
\end{assumption}

\begin{assumption}[Bernstein MTE sieve]\label{ass:bernstein}
For a fixed degree \(J\), the MTE curve satisfies
\(m(u)=B_J(u)^\transpose\beta\) for some \(\beta\in\R^{J+1}\), where \(B_J\) is
the Bernstein basis defined in Section 6.
\end{assumption}

\begin{assumption}[Shape restrictions]\label{ass:shape}
The coefficient vector obeys known linear restrictions \(L\beta\le r\).  The
polyhedron \(\{\beta:L\beta\le r\}\) is nonempty and bounded in the target
direction \(q\).
\end{assumption}

\begin{assumption}[Policy weight]\label{ass:policy}
The target PRTE weight has a known Bernstein projection
\(q=\int_0^1\omega_{\rm prte}(u)B_J(u)\,du\), so the finite-sieve target is
\(\theta(q)=q^\transpose\beta\).
\end{assumption}

\begin{assumption}[Endpoint benchmark regularity]\label{ass:nonredundant}
For each endpoint \(e\in\{U,L\}\) and each optimizer \(j\in{\cal J}_e\) of
the relevant single-coordinate benchmark, the fiber \(F_{e,j}\) is nonempty
and bounded in direction \(s_e\), the intersection
\(F_{e,j}\cap{\cal A}_{\rm joint}\) is nonempty, and the optimal face
\({\cal O}_{e,j}\) is nonempty.  Strict gain is not assumed; it is the
condition characterized by
\(\min_{j\in{\cal J}_e}\tau_{e,j}(P;q,L,r,\gamma)>0\) in Conjecture
\ref{conj:width}.
\end{assumption}

\section{Main results}
\paragraph{Benchmark normalization, not a novelty claim.}
Under Assumptions \ref{ass:support}--\ref{ass:policy}, the saturated
all-split MST/Han--Yang finite-sieve endpoint is the already-published LP
\[
U(M_{\rm joint},\gamma_{\rm joint};q)=
\max_{\beta\in\R^{J+1}}\{q^\transpose\beta:
M_{\rm joint}\beta=\gamma_{\rm joint},\ L\beta\le r\},
\]
with lower endpoint \(-U(M_{\rm joint},\gamma_{\rm joint};-q)\) and the usual
dual
\[
\min_{\eta\in\R^{m_{\rm joint}},\lambda\ge0}
\{\gamma_{\rm joint}^\transpose\eta+r^\transpose\lambda:
M_{\rm joint}^\transpose\eta+L^\transpose\lambda=q\}.
\]
Here \(m_{\rm joint}\) is the number of saturated all-split contrast rows.
This paragraph is included only to pin the comparator used by Conjecture
\ref{conj:width}; it is routine LP machinery from
\citet{MogstadSantosTorgovitsky2018} and \citet{HanYang2024}, so it is not
counted as a flagship theorem.

\begin{conjecture}[Conjecture 1: pre-saturated coordinate-shortcut adequacy certificate (NOT YET PROVED)]\label{conj:width}
Under Assumptions \ref{ass:support}--\ref{ass:nonredundant}, define the
upper- and lower-bound gains
\[
\Delta_U(P;q)=U_{\rm sing}(P;q)-U(M_{\rm joint},\gamma_{\rm joint};q),
\qquad
\Delta_L(P;q)=L(M_{\rm joint},\gamma_{\rm joint};q)-L_{\rm sing}(P;q).
\]
Then the retained-coordinate shortcut is endpoint-adequate before solving the
saturated endpoint if and only if at least one tied coordinate-optimal face
passes the residual all-split consistency test:
\[
\Delta_e(P;q)=0
\quad\Longleftrightarrow\quad
\min_{j\in{\cal J}_e}\tau_{e,j}(P;q,L,r,\gamma)=0,\qquad e\in\{U,L\}.
\]
Equivalently, the saturated all-split MST/Han--Yang interval is strictly
tighter than the best retained-coordinate shortcut exactly when
\[
\min_{j\in{\cal J}_e}\tau_{e,j}(P;q,L,r,\gamma)>0.
\]
On this strict-gain region, the endpoint drop has the residual
face-restricted representation
\[
\Delta_e(P;q)=
\min_{j\in{\cal J}_e}
\inf_{\beta\in F_{e,j}\cap{\cal A}_{\rm joint}}
\{h_{F_{e,j}}(s_e)-s_e^\transpose\beta\},
\]
with the usual finite-dimensional dual obtained by adding the saturated
moment rows to the coordinate-optimal face equations.  Thus \(\tau_{e,j}\) is
the pre-saturated diagnostic and the displayed residual program is used only
to quantify the gain after the diagnostic has predicted strict improvement.
The strictness is locally stable: whenever the displayed minimum of
\(\tau_{e,j}\) is positive and the active single-coordinate argmax/argmin set
and exposed coordinate faces are unchanged, there is a relative open
neighborhood of the observable outcome moments and shape right-hand side in
which the saturated endpoint remains strictly tighter.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{MogstadSantosTorgovitsky2018} already provide the all-IV-like
MTE/PRTE LP and show that split IV-like estimands can tighten bounds;
\citet{HanYang2024} provide sharp binary-IV LP bounds; and
\citet{MogstadTorgovitskyWalters2024} show that multiple instruments can be
aggregated more informatively than separate single-IV analyses.  The epsilon
gap is not another LP endpoint and not the generic identity that intersecting
a polyhedron can lower its support function.  It is the tied-face
rank/projection certificate \(\min_{j\in{\cal J}_e}\tau_{e,j}\): prior work
computes or motivates the two procedures, while this conjecture gives a
necessary-and-sufficient pre-saturated test, expressed in the econometric row
geometry generated by the joint binary-instrument propensity distribution, for
when the retained-coordinate shortcut is inadequate.  (b) The concrete
consumer is an applied MST-style PRTE analysis with several eligibility or
encouragement instruments, where the researcher can decide whether a
coordinate-wise report is lossless before spending the main analysis on a
saturated all-split endpoint.

\begin{example}[Smallest nontrivial face-rank diagnostic]\label{ex:k2j2}
For \(K=2\), \(J=2\), and four equally likely cells with
\[
p_{00}=1/5,\qquad p_{10}=2/5,\qquad p_{01}=3/5,\qquad p_{11}=4/5,
\]
the \(Z_1\)-coordinate row is
\[
w_1=(22/75,\ 31/75,\ 22/75),
\]
whereas the saturated all-split row comparing \(00\) to \(11\) is
\[
w_{00,11}=(7/25,\ 11/25,\ 7/25).
\]
The \(Z_2\)-coordinate row is
\[
w_2=(41/150,\ 34/75,\ 41/150).
\]
Thus the saturated design contains rows that are not identical to either
coordinate row even in the smallest binary multi-IV design.  If, for example,
the tied upper endpoint is exposed by \(Z_1\) and by one active Bernstein
shape face, the proposed diagnostic forms
\[
H_{U,1}=\begin{bmatrix}w_1\\ L_{{\cal B}_{U,1}}\\ q^\transpose\end{bmatrix}
\]
and tests whether the saturated moment vector
\(\gamma_{\rm joint}\) is consistent with
\(\begin{bmatrix}H_{U,1}\\ M_{\rm joint}\end{bmatrix}\beta
=\begin{bmatrix}b_{U,1}\\ \gamma_{\rm joint}\end{bmatrix}\).  Generic
outcome moments fail this augmented-rank equality whenever the residual
all-split row has a nonzero projection off the \(Z_1\)-optimal face; the
proposal asks to prove that this pre-saturated failure is exactly the
strict-tightening event for the upper PRTE endpoint.
\end{example}

\section{Sanity-check corollaries}
\begin{corollary}[No-gain under redundant support]\label{cor:no-gain}
Under Assumptions \ref{ass:support}--\ref{ass:policy}, if every joint
propensity-contrast row is affinely implied by every tied endpoint-specific
retained-coordinate system with the same right-hand-side moment, equivalently
\(F_{e,j}\cap{\cal A}_{\rm joint}=F_{e,j}\) for every \(e\in\{U,L\}\) and
\(j\in{\cal J}_e\), then \(W_{e,j}=0\) for all tied endpoints and
\(\Delta_U(P;q)=\Delta_L(P;q)=0\).
\end{corollary}

\begin{corollary}[Homogeneous-effect collapse]\label{cor:homogeneous}
If Assumptions \ref{ass:support}--\ref{ass:policy} hold and the shape system
adds \(m(u)\equiv\tau\), equivalently \(\beta_0=\cdots=\beta_J=\tau\), then
all valid contrast rows imply the same value \(\tau\) and every joint or
single-IV PRTE interval collapses to the point \(\theta(q)=\tau\int_0^1
\omega_{\rm prte}(u)\,du\).
\end{corollary}

\begin{corollary}[External single-IV boundary]\label{cor:k1-boundary}
Outside the locked \(K\ge2\) tuple, if \(K=1\) and \(Z\) is binary with
nonzero first-stage contrast, the retained-coordinate row is the saturated
row system.  The benchmark normalization therefore coincides exactly with the
finite Bernstein LP of \citet{MogstadSantosTorgovitsky2018} for the same
basis, target weight, and shape restrictions.
\end{corollary}

\section{Proof-sketch route}
The benchmark LP normalization reduces to the latent-index identity that a
cell-level Wald contrast between two propensity values averages the MTE over
the interval between them, while the retained-coordinate row follows by
integrating the conditional selection-probability contrast
\(\Pr(p_Z\ge u\mid Z_j=1)-\Pr(p_Z\ge u\mid Z_j=0)\).  Finite-dimensional
linear programming duality then gives the primal and dual endpoints.
Conjecture 1 should be attacked endpoint by endpoint and tied optimizer by
tied optimizer by first solving the coordinate endpoint LP, extracting the
exposed face equations \(H_{e,j}\beta=b_{e,j}\), and applying the finite
linear-system consistency theorem to the augmented saturated system
\((H_{e,j},M_{\rm joint})\beta=(b_{e,j},\gamma_{\rm joint})\).  The key
non-generic step is to prove that, in the MST/Han--Yang MTE row geometry,
failure of this augmented-rank test on every tied coordinate-optimal face is
equivalent to a positive PRTE endpoint drop.  Once strictness is established,
standard LP duality can quantify the drop through the residual
face-restricted program.  The local open-set strictness clause should follow
from stability of LP optimal faces under fixed active sets.  The boundary
algebra to check first is the worked \(K=2\), \(J=2\), four-cell example in
Example \ref{ex:k2j2}, where all coarsened rows, saturated rows, active-face
rank tests, and dual certificates can be listed explicitly.

\section{Honest scope flags}
The saturated LP normalization and the external \(K=1\) boundary are routine
published machinery, not flagship results.  Conjecture 1 is the novel kernel
and is not yet proved; in particular, the endpoint-frontier equivalence may
need a closure or facial-exposure condition when the coordinate shortcut has
multiple optimal faces within a tied retained coordinate.  Ties across
retained coordinates are handled explicitly by the minimum over
\(j\in{\cal J}_e\).  The pre-saturated certificate is not claimed to be a
design-only functional: its row geometry is determined by the joint propensity
distribution, but the augmented-rank right-hand side depends on
\((\gamma,L,r)\).  The proposal deliberately does not claim
robustness to violations of latent-index monotonicity, partial monotonicity
failures, or estimated-propensity inference.  In v2 the design-only width
claim was withdrawn and replaced by the endpoint-specific residual support
width \(W_e(P;q,L,r)\).  In v3 the residual-row-basis norm \(\kappa_e\) was
withdrawn and replaced by the Bernstein Gram-distance statistics
\(\kappa_{e,j}\) over every tied single-coordinate optimizer.  In v5 the
support-drop statistic was demoted to a magnitude descriptor and the flagship
claim was recast as the face-rank certificate \(\tau_{e,j}\) computed before
the saturated endpoint is solved.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft centered on the projected
moment-cone width comparison between the joint multi-IV Bernstein LP and the
best single-IV MST benchmark; prior verdict: none.
\item v2 (revise) --- replaced the design-only width with endpoint-specific
residual support widths \(W_U,W_L\), defined coarsened retained-coordinate
Wald rows, and separated lower/upper single-IV optimizers; prior verdict:
REVISE.
\item v3 (revise) --- added the Brinch-Mogstad-Wiswall discrete-instrument
MTE comparator, replaced the basis-dependent residual norm by tied-face
Bernstein Gram-distance statistics \(\kappa_{e,j}\), and sharpened Conjecture
1 into a named MST/Han-Yang endpoint-frontier comparison; prior verdict:
REVISE.
\item v4 (revise) --- demoted the saturated primal-dual LP and the \(K=1\)
MST limit to benchmark normalizations, re-anchored the flagship novelty
against MST's all-IV-like split-instrument benchmark and Han-Yang's binary-IV
LP, and separated the external \(K=1\) boundary from the locked \(K\ge2\)
tuple; prior verdict: REVISE.
\item v5 (revise) --- replaced the endpoint-drop-as-frontier phrasing with a
pre-saturated face-rank certificate \(\tau_{e,j}\), added a \(K=2,J=2\)
worked diagnostic, and clarified that generic LP support-function duality is
not the novelty claim; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Vytlacil(2002)]{Vytlacil2002}
Vytlacil, Edward. 2002. ``Independence, Monotonicity, and Latent Index
Models: An Equivalence Result.'' \emph{Econometrica} 70(1):331--341.

\bibitem[Heckman and Vytlacil(2005)]{HeckmanVytlacil2005}
Heckman, James J., and Edward Vytlacil. 2005. ``Structural Equations,
Treatment Effects, and Econometric Policy Evaluation.'' \emph{Econometrica}
73(3):669--738.

\bibitem[Brinch, Mogstad, and Wiswall(2017)]{BrinchMogstadWiswall2017}
Brinch, Christian N., Magne Mogstad, and Matthew Wiswall. 2017. ``Beyond LATE
with a Discrete Instrument.'' \emph{Journal of Political Economy}
125(4):985--1039.

\bibitem[Manski and Pepper(2000)]{ManskiPepper2000}
Manski, Charles F., and John V. Pepper. 2000. ``Monotone Instrumental
Variables: With an Application to the Returns to Schooling.'' \emph{Econometrica}
68(4):997--1010.

\bibitem[Mogstad, Santos, and Torgovitsky(2018)]{MogstadSantosTorgovitsky2018}
Mogstad, Magne, Andres Santos, and Alexander Torgovitsky. 2018. ``Using
Instrumental Variables for Inference about Policy Relevant Treatment
Parameters.'' \emph{Econometrica} 86(5):1589--1619.

\bibitem[Mogstad and Torgovitsky(2018)]{MogstadTorgovitsky2018Review}
Mogstad, Magne, and Alexander Torgovitsky. 2018. ``Identification and
Extrapolation of Causal Effects with Instrumental Variables.'' \emph{Annual
Review of Economics} 10:577--613.

\bibitem[Mogstad, Torgovitsky, and Walters(2021)]{MogstadTorgovitskyWalters2021}
Mogstad, Magne, Alexander Torgovitsky, and Christopher R. Walters. 2021.
``The Causal Interpretation of Two-Stage Least Squares with Multiple
Instrumental Variables.'' \emph{American Economic Review} 111(11):3663--3698.

\bibitem[Mogstad, Torgovitsky, and Walters(2024)]{MogstadTorgovitskyWalters2024}
Mogstad, Magne, Alexander Torgovitsky, and Christopher R. Walters. 2024.
``Policy Evaluation with Multiple Instrumental Variables.'' \emph{Journal of
Econometrics} 243(1--2):105718.

\bibitem[Goff(2024)]{Goff2024}
Goff, Leonard. 2024. ``A Vector Monotonicity Assumption for Multiple
Instruments.'' \emph{Journal of Econometrics} 241:105735.

\bibitem[Han and Yang(2024)]{HanYang2024}
Han, Sukjin, and Shenshen Yang. 2024. ``A Computational Approach to
Identification of Treatment Effects for Policy Evaluation.'' \emph{Journal of
Econometrics} 240:105680.

\bibitem[Marx(2024)]{Marx2024}
Marx, Philip. 2024. ``Sharp Bounds in the Latent Index Selection Model.''
\emph{Journal of Econometrics} 238:105561.

\bibitem[Rockafellar(1970)]{Rockafellar1970}
Rockafellar, R. Tyrrell. 1970. \emph{Convex Analysis}. Princeton University
Press.
\end{thebibliography}

\end{document}
