% =====================================================================
%  thmsmith Stage 0 derivation skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=stat\_policy\_regret\_margin\_overlap, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to the Q1
%    pool-mode, fill it VERBATIM from the Q1 block of
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). For free-form panel / ExactID /
%    PartialID anchors (the default), reproduce the locked-parameter block
%    from the Stage -1 proposal verbatim. Do not rephrase locked parameters;
%    Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
%  - Immutability is SCOPED to section headers, macro names, and the
%    preamble. The PLACEMENT of theorem/proposition/lemma/assumption
%    environments is YOUR responsibility: a `theorem` env may be freely
%    moved into whichever fixed-header section fits (e.g. promote the
%    field-level result from \S11 into \S9). Relocating a block between
%    fixed headers is NOT a skeleton violation.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage 0 derivation: \texttt{stat\_policy\_regret\_margin\_overlap} / \texttt{v1}%
  \\ \large\textit{Calibrated offline policy regret under margin and one-sided overlap decay}}
\author{thmsmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies offline binary policy learning under unconfoundedness,
bounded outcomes, a Tsybakov decision-margin condition, one-sided polynomial
overlap decay near the decision boundary, and finite-VC policy complexity.
The causal estimand is welfare regret,
\[
R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)
      =E_P[|\tau_P(X)|\one\{\pi(X)\ne\pi_P^*(X)\}],
\]
where \(\tau_P(x)=E_P[Y(1)-Y(0)\mid X=x]\) and
\(\pi_P^*(x)=\one\{\tau_P(x)\ge0\}\).  Identification of \(\tau_P\) is taken
as given by consistency and unconfoundedness; the contribution is the
statistical rate for learning a low-regret policy from offline data.

The weak-overlap lower-bound layer is obtained by optimizing an active block
with contrast height \(h\), covariate mass \(h^\alpha\), and weak-arm
propensity \(h^\beta\).  Membership in the one-sided overlap class forces
\[
\beta\le \beta_{\alpha,\gamma}:=
\begin{cases}
0, & \gamma=0,\\
\alpha\gamma/(\alpha+1), & \gamma>0.
\end{cases}
\]
The least informative admissible layer has one-observation information
\(h^{2+\alpha+\beta_{\alpha,\gamma}}\) and regret separation
\(h^{1+\alpha}\), giving the converse exponent
\[
r_*(\alpha,\gamma)=
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
The note proves a two-point lower bound at this exponent over the full
weak-overlap law class.  It also proves a data-only cross-fitted
clipped-AIPW empirical welfare upper bound under \emph{standard} foldwise
nuisance-convergence rates --- an \(L_2\) propensity rate, an \(L_1\)
outcome-regression rate, and the usual weighted doubly-robust \(L_2\) product
rate, with no sup-norm propensity localization and no known-logging design.
Under these \(L_2\) rates the feasible upper bound matches the converse,
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_{n,q_n^*})
\lesssim
n^{-r_*(\alpha,\gamma)}(\log n)^{(1+\alpha)/(2+\alpha)},
\]
\emph{exactly in the regime \(\beta_{\alpha,\gamma}\le2\)} (equivalently
\(\alpha\gamma\le2(\alpha+1)\)).  The reason is that with only an \(L_2\)
propensity rate the weighted doubly-robust product is the binding nuisance
offset, of order \((h_n^*)^{2+\alpha-\beta_{\alpha,\gamma}/2}\), which lies
within the regret budget \((h_n^*)^{1+\alpha}\) iff
\(\beta_{\alpha,\gamma}\le2\).  When \(\beta_{\alpha,\gamma}>2\) this product
offset dominates the regret scale, so the clipped-AIPW maximizer with
\(L_2\)-rate nuisances \emph{does not} attain \(r_*(\alpha,\gamma)\): the
upper and lower bounds no longer match, and the exact \(L_2\)-feasible rate in
that severe-overlap sliver is left open.  The logarithmic multiplier is the
finite-VC localized entropy factor.  We do not close the
\(\beta_{\alpha,\gamma}>2\) gap by strengthening the propensity condition to a
sup-norm rate or to a known logging design, since that would buy the rate
through a non-standard hypothesis rather than establish it for the standard
\(L_2\) nuisance class.
\end{abstract}

\section{Introduction}
Observational policy learning asks for a treatment rule that improves welfare
using fixed offline data.  In the binary-treatment setting the welfare
criterion is driven by the sign of the conditional causal contrast
\[
\tau_P(x)=E_P[Y(1)-Y(0)\mid X=x].
\]
Unconfoundedness identifies this contrast through observed conditional means.
The statistical problem is harder where \(|\tau_P(x)|\) is small and the arm
that reveals the sign is rare.  A margin condition limits the mass near
\(\tau_P=0\), while the one-sided overlap condition limits how much of that
near-boundary mass can also have a small weak-arm propensity.

The weak-arm layer must be optimized directly under the overlap-tail
constraint.  If an active block has margin height \(h\), mass \(h^\alpha\),
and weak-arm propensity \(h^\beta\), then membership in the overlap class
requires
\[
\beta\le \beta_{\alpha,\gamma}:=\alpha\gamma/(\alpha+1)
\quad(\gamma>0).
\]
Balancing
\[
n h^{2+\alpha+\beta_{\alpha,\gamma}}\asymp1
\]
gives the converse exponent
\[
r_*(\alpha,\gamma)=
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]

The feasible upper bound uses a target-preserving clipped-AIPW score.  The
clipping level controls the score variance on weak-overlap strata.  Clipping
also creates a first-order bias term when the nuisances are estimated, and
this term is governed by standard \(L_1/L_2\) nuisance-convergence rates, with
common constants over the law collection: an \(L_2\) propensity rate, local
outcome-regression \(L_1\) accuracy on the clipped weak-arm layer, and the
usual weighted propensity/outcome \(L_2\) product.  No sup-norm propensity
localization and no known-logging design is used.  Under these standard
rates the cross-fitted empirical welfare maximizer is data-only and matches
the converse exponent \(r_*(\alpha,\gamma)\) with the finite-VC logarithmic
multiplier \emph{precisely when} \(\beta_{\alpha,\gamma}\le2\) (equivalently
\(\alpha\gamma\le2(\alpha+1)\)): in that regime the binding nuisance offset,
the weighted doubly-robust product of order
\((h_n^*)^{2+\alpha-\beta_{\alpha,\gamma}/2}\), stays within the regret budget
\((h_n^*)^{1+\alpha}\).  When \(\beta_{\alpha,\gamma}>2\) the product offset
dominates the regret scale and the same estimator no longer attains
\(r_*(\alpha,\gamma)\) from \(L_2\) rates alone, leaving the exact feasible
rate in that severe-overlap sliver open.  The overlap-decay assumption is used
to calibrate the converse and the natural choice of clipping level; it is not,
by itself, a proof of the nuisance rates needed by the feasible estimator.

\paragraph{Motivating conjecture(s).}
Let \(\delta_{\alpha,\gamma}=(\gamma-\alpha)_+\).

\textbf{Conjecture 1.} (Upper-rate claim.) Under
Assumptions~\ref{ass:causal-sampling}--\ref{ass:nuisance}, the clipped-AIPW
ERM with \(t_n=n^{-s(\alpha,\gamma)}\) satisfies
\[
\sup_{P\in\mathcal{P}_{\alpha,\gamma}}
E_P R_P(\widehat\pi_{t_n})
\le C n^{-r(\alpha,\gamma)}
\]
for \(r(\alpha,\gamma)=(1+\alpha)/(2+\alpha+\delta_{\alpha,\gamma})\), where
\(\delta_{\alpha,\gamma}=(\gamma-\alpha)_+\).

\textbf{Conjecture 2.} (Calibrated lower claim.) Under
Assumptions~\ref{ass:causal-sampling}, \ref{ass:margin},
\ref{ass:overlap-decay}, \ref{ass:primitive-cube}, and
\ref{ass:calibrated-overlap-richness}, for
\(h_n=n^{-1/(2+\alpha+\delta_{\alpha,\gamma})}\) there exist paired laws
\(P_{n,+},P_{n,-}\) in a calibrated subclass with active-block mass
\(h_n^\alpha\), contrast height \(h_n\), weak-arm propensity
\(h_n^{\delta_{\alpha,\gamma}}\), one-observation Hellinger radius
\(h_n^{2+\alpha+\delta_{\alpha,\gamma}}\), and regret separation
\(h_n^{1+\alpha}\).

The verdict is as follows.  Conjecture 1 is false as a full-class no-log
claim whenever
\[
\frac{1+\alpha}{2+\alpha+\delta_{\alpha,\gamma}}
>
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
At \((\alpha,\gamma)=(2,2)\), it predicts \(3/4\), while the full-class
two-point witness forces \(9/16\).  The corrected feasible upper theorem uses
standard \(L_1/L_2\) foldwise nuisance rates --- an \(L_2\) propensity rate,
an \(L_1\) outcome rate, and the weighted doubly-robust \(L_2\) product ---
with common margin, policy-class, and fold constants, and keeps the finite-VC
logarithmic multiplier explicit.  Under these standard rates the upper bound
matches the converse exponent \(r_*(\alpha,\gamma)\) exactly when
\(\beta_{\alpha,\gamma}\le2\) (equivalently \(\alpha\gamma\le2(\alpha+1)\)):
the binding nuisance offset is the weighted doubly-robust product, of order
\((h_n^*)^{2+\alpha-\beta_{\alpha,\gamma}/2}\), which is within the regret
budget \((h_n^*)^{1+\alpha}\) iff \(\beta_{\alpha,\gamma}\le2\).  When
\(\beta_{\alpha,\gamma}>2\) this product offset dominates the regret scale, so
the clipped-AIPW maximizer with \(L_2\)-rate nuisances does \emph{not} attain
\(r_*(\alpha,\gamma)\); the upper and lower bounds do not match there and the
exact \(L_2\)-feasible rate is left open.  We deliberately do not restore the
match in that sliver by strengthening the propensity condition to a sup-norm
rate or assuming a known logging design, as that would buy the rate through a
non-standard hypothesis.  Conjecture 2 is corrected by using the largest
overlap-admissible weak-arm exponent \(\beta_{\alpha,\gamma}\), which gives the
full-class converse at \(r_*(\alpha,\gamma)\).

\section{Related work and positioning}
Athey and Wager (2021) provide the observational policy-learning template:
the causal target is a policy welfare, the empirical criterion is built from
doubly robust scores, and the policy search is restricted by a manageable
complexity condition.  Kitagawa and Tetenov (2018) give the empirical welfare
maximization perspective for treatment choice.  Luedtke and Chambaz (2017)
show how a margin condition can convert score accuracy into fast policy-regret
rates.  Chernozhukov et al. (2018) provide the cross-fitting and orthogonal
score template used to separate nuisance learning from validation-sample
empirical processes.

Ma, Sant'Anna, Sasaki, and Ura (2023) separate variance stabilization from
target-changing trimming for scalar causal estimands under weak overlap.  The
present note uses target-preserving clipping for policy regret.  Kallus
(2017) gives an alternative variance-stabilized policy-learning route.  Jin,
Ren, Yang, and Wang (2022) and Zhan, Ren, Athey, and Zhou (2021) show why
scarce treatment observations matter for policy learning, though their
scarcity mechanisms differ from the fixed offline overlap surface studied
here.  D'Amour, Ding, Feller, Lei, and Sekhon (2021) motivate replacing
strict overlap by tail and diagnostic conditions in observational studies.

Audibert and Tsybakov (2007) supply the lower-bound grammar: localized
finite-cell sign perturbations under a margin condition.  The additional
ingredient here is that the lower-bound cells must satisfy the same
one-sided overlap-decay envelope as every other member of the law class.
Standard VC maximal inequalities, as in Vapnik and Chervonenkis (1971) and
van der Vaart and Wellner (1996), supply the finite-VC localized empirical
process bound, with the logarithmic entropy factor retained.

\section{Formal setup}
Let \(O=(X,A,Y)\sim P\), where \(A\in\{0,1\}\) and \(Y\in[-1,1]\).  Potential
outcomes \(Y(0),Y(1)\) satisfy consistency and unconfoundedness.  Define
\[
e_P(x)=P(A=1\mid X=x),\qquad
\mu_a(x)=E_P[Y\mid A=a,X=x],
\]
\[
\tau_P(x)=\mu_1(x)-\mu_0(x)=E_P[Y(1)-Y(0)\mid X=x].
\]
A deterministic policy \(\pi:\mathcal X\to\{0,1\}\) has normalized welfare
\[
V_P(\pi)=E_P[\pi(X)\tau_P(X)].
\]
The optimal policy is
\[
\pi_P^*(x)=\one\{\tau_P(x)\ge0\},
\]
and its regret is \(R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)\).

Let
\[
p_P(x)=\min\{e_P(x),1-e_P(x)\}.
\]
For \(\gamma>0\) define
\[
\beta_{\alpha,\gamma}=\frac{\alpha\gamma}{\alpha+1},
\]
and set \(\beta_{\alpha,0}=0\).  Let
\[
D_{\alpha,\gamma}=2+\alpha+\beta_{\alpha,\gamma},\qquad
h_n^*=n^{-1/D_{\alpha,\gamma}},\qquad
r_*(\alpha,\gamma)=\frac{1+\alpha}{D_{\alpha,\gamma}}.
\]
Define
\[
L_n^*=\log\{e/(h_n^*)^{1+\alpha}\},\qquad
a_\alpha=\frac{1+\alpha}{2+\alpha},\qquad
\bar\rho_n^*=(h_n^*)^{1+\alpha}(L_n^*)^{a_\alpha}.
\]
Fix a strict-overlap clipping constant \(q_0\in(0,1/8]\).  For
\(h\in(0,1)\), define
\[
q(h)=
\begin{cases}
q_0, & \beta_{\alpha,\gamma}=0,\\
h^{\beta_{\alpha,\gamma}}, & \beta_{\alpha,\gamma}>0.
\end{cases}
\]
The overlap-calibrated upper and lower displays use
\[
q_n^*=q(h_n^*).
\]
This convention covers the strict-overlap case \(\gamma=0\) and the
\(\alpha=0,\gamma>0\) case, where \(\beta_{\alpha,\gamma}=0\).

For a nuisance tuple \(\eta=(\mu_0,\mu_1,e)\) and a lower clipping level
\(q\in(0,1/2]\), define
\[
e_q(x;\eta)=\min\{1-q,\max\{q,e(x)\}\}
\]
and the clipped AIPW score
\[
\Gamma_q(O;\eta)=\mu_1(X)-\mu_0(X)
+\frac{A}{e_q(X;\eta)}\{Y-\mu_1(X)\}
-\frac{1-A}{1-e_q(X;\eta)}\{Y-\mu_0(X)\}.
\]
The oracle nuisance tuple is \(\eta_P=(\mu_0,\mu_1,e_P)\).  Its score
\(\Gamma_q^\circ(O)=\Gamma_q(O;\eta_P)\) satisfies
\[
E_P[\Gamma_q^\circ(O)\mid X]=\tau_P(X)
\]
for every \(q\in(0,1/2]\).

The feasible score is formed from a fixed nonrandom \(K\)-fold partition
\(I_1,\ldots,I_K\) of \(\{1,\ldots,n\}\), with \(K\) fixed,
\(n_k=|I_k|\), \(w_k=n_k/n\), and \(c_Kn\le n_k\le C_Kn\).  For
\(i\in I_k\), let
\[
\widehat\eta^{(-k)}=(\widehat\mu_0^{(-k)},\widehat\mu_1^{(-k)},
\widehat e^{(-k)})
\]
be measurable with respect to the training sigma-field
\(\mathcal T_k=\sigma(O_i:i\notin I_k)\), together with any independent
algorithmic randomization, and define
\[
\widehat\Gamma_{q,k}(O)=\Gamma_q(O;\widehat\eta^{(-k)}).
\]
The data-only clipped-AIPW empirical welfare maximizer is
\[
\widehat\pi_{n,q}\in\arg\max_{\pi\in\Pi}
\widehat V_{n,q}(\pi),\qquad
\widehat V_{n,q}(\pi)=
\sum_{k=1}^K w_k\, n_k^{-1}\sum_{i\in I_k}
\pi(X_i)\widehat\Gamma_{q,k}(O_i).
\]
The overlap-calibrated estimator uses \(q=q_n^*\) and writes
\[
\widehat\pi_{n}^{\mathsf F}:=\widehat\pi_{n,q_n^*}.
\]
Measurable selectors are assumed when an argmax is not unique.

The margin-overlap law class is
\[
\mathcal P_{\alpha,\gamma}
=\{P:\text{Assumptions~\ref{ass:causal-sampling},
\ref{ass:margin}, \ref{ass:overlap-decay}, and
\ref{ass:policy-class} hold with exponents }\alpha,\gamma\}.
\]
This class fixes the exponents \(\alpha,\gamma\) but not the numerical
margin, overlap, policy-complexity, fold, or nuisance-rate constants.  A
uniform upper bound over a subcollection therefore requires common constants
beyond the inclusion \(\mathcal Q\subseteq\mathcal P_{\alpha,\gamma}\).

\begin{definition}[Uniform feasible collection]\label{def:uniform-feasible-collection}
Fix \(\alpha,\gamma\), the clipping sequence \(q_n^*\), the rate sequence
\(\bar\rho_n^*\), the policy class \(\Pi\), the fixed fold partition rule,
and the fixed nuisance learners.  A law collection \(\mathcal Q\) is called
\(\kappa\)-uniform feasible if every \(P\in\mathcal Q\) satisfies
Assumptions~\ref{ass:causal-sampling}, \ref{ass:margin}, and
\ref{ass:policy-class} with common constants bounded by a finite vector
\(\kappa\), the fold sizes satisfy the same constants \(c_K,C_K,K\), and
Assumption~\ref{ass:nuisance} holds over \(\mathcal Q\) at
\(q_n=q_n^*\) and \(\rho_n=\bar\rho_n^*\) with common constants
\(C_\eta,C_G,N_\eta\) bounded by \(\kappa\).
\end{definition}

For any law collection \(\mathcal Q\), define the policy-regret minimax risk
\[
\mathfrak M_n(\mathcal Q)
=\inf_{\widehat\pi}
\sup_{P\in\mathcal Q}E_P R_P(\widehat\pi),
\]
where the infimum ranges over measurable data-dependent policies taking
values in \(\Pi\).  The full weak-overlap risk is
\[
\mathfrak M_n(\alpha,\gamma)=\mathfrak M_n(\mathcal P_{\alpha,\gamma}).
\]
The upper theorem is stated for a generic collection \(\mathcal Q\) satisfying
the common-constant conditions in Definition~\ref{def:uniform-feasible-collection}.
That condition is an achievability-side hypothesis on the chosen nuisance
learners; it is not part of the definition of \(\mathcal P_{\alpha,\gamma}\).

\paragraph{Locked parameters.}
\begin{itemize}[leftmargin=*]
  \item \texttt{(qid, specialization) = (stat\_policy\_regret\_margin\_overlap, v1).}
  \item \texttt{Anchor cluster = Stat.}
  \item \texttt{Statistical model and causal estimand: iid observations O\_i=(X\_i,A\_i,Y\_i), A\_i in \{0,1\}, unconfoundedness, consistency, bounded outcomes, and known-or-estimable propensity e\_P(x)=P(A=1|X=x). The causal contrast is tau\_P(x)=E[Y(1)-Y(0)|X=x]. For a policy pi:X->\{0,1\}, V\_P(pi)=E[pi(X)tau\_P(X)] and R\_P(pi)=V\_P(pi\_P\textasciicircum{}*)-V\_P(pi), where pi\_P\textasciicircum{}*(x)=1\{tau\_P(x)>=0\}.}
  \item \texttt{Sampling model: iid draws from P in a fixed offline logging design; no adaptive exploration.}
  \item \texttt{Target object: the information-theoretic minimax expected welfare-regret exponent over the one-sided overlap-decay class, r\_*(alpha,gamma)=(1+alpha)/(2+alpha+beta\_{alpha,gamma}) with beta\_{alpha,gamma}=alpha gamma/(alpha+1) for gamma>0 and beta\_{alpha,0}=0.}
  \item \texttt{Estimator: a data-only cross-fitted target-preserving clipped-AIPW-score empirical welfare maximizer using the overlap-calibrated clipping level q\_n\textasciicircum{}*=q\_0 whenever beta\_{alpha,gamma}=0 and q\_n\textasciicircum{}*=(h\_n\textasciicircum{}*)\textasciicircum{}\{beta\_{alpha,gamma}\} otherwise, with achievability conditional on foldwise nuisance-rate hypotheses.}
  \item \texttt{Matching converse: a primitive localized two-point construction whose cube mass, contrast height, weak-arm propensity height, and chi-square divergence radius are calibrated to r\_*(alpha,gamma), with known-logging finite-cell witnesses that satisfy the high-level nuisance-rate condition at the logarithmically inflated feasible scale.}
\end{itemize}

\section{Assumptions}
\begin{assumption}[Causal sampling and bounded outcomes]\label{ass:causal-sampling}
The observations \(O_1,\ldots,O_n\) are iid from \(P\).  Consistency and
unconfoundedness hold, \(Y(a)\in[-1,1]\), and \(0<e_P(X)<1\) almost surely.
The conditional means \(\mu_a(x)=E_P[Y\mid A=a,X=x]\) exist as measurable
versions.
\end{assumption}

\begin{assumption}[Tsybakov decision margin and canonical zero-effect region]\label{ass:margin}
There are constants \(0<C_m<\infty\), \(u_0>0\), and \(\alpha\ge0\) such that
\[
P(0<|\tau_P(X)|\le u)\le C_m u^\alpha
\quad\text{for all }0<u\le u_0.
\]
In addition, either \(P_X\{\tau_P(X)=0\}=0\), or every
\(\pi\in\Pi\) satisfies \(\pi(x)=\pi_P^*(x)\) for \(P_X\)-almost every
\(x\) with \(\tau_P(x)=0\).
\end{assumption}

\begin{assumption}[One-sided polynomial overlap decay]\label{ass:overlap-decay}
Let \(p_P(x)=\min\{e_P(x),1-e_P(x)\}\).  There are constants
\(C_o,c_o>0\) and \(\gamma\ge0\) such that
\[
P\{p_P(X)\le v,\;0<|\tau_P(X)|\le u\}
  \le C_o u^\alpha v^{1/\gamma}
\]
for all \(0<v\le c_o u^\gamma\), with the convention that \(v^{1/\gamma}=1\)
when \(\gamma=0\).  In the \(\gamma=0\) case, the condition is read as a
strict-overlap condition on the strict-margin region.
\end{assumption}

\begin{assumption}[Calibrated overlap-richness for the delta witness]\label{ass:calibrated-overlap-richness}
Let \(\delta_{\alpha,\gamma}=(\gamma-\alpha)_+\).  When the
\(\delta_{\alpha,\gamma}\)-weak-arm witness in Conjecture 2 is considered,
the exponents satisfy
\[
(\gamma-\alpha)_+
\le \frac{\alpha\gamma}{\alpha+1}.
\]
Equivalently, when \(\gamma>\alpha\), this condition is
\(\gamma\le\alpha(\alpha+1)\).
\end{assumption}

\begin{remark}
Assumption~\ref{ass:calibrated-overlap-richness} is the exponent condition
under which the \(\delta_{\alpha,\gamma}\)-calibrated witness described in
Conjecture 2 is overlap-admissible.  The main lower theorem below does not
need this condition because it uses the largest admissible weak-arm exponent
\(\beta_{\alpha,\gamma}=\alpha\gamma/(\alpha+1)\) when \(\gamma>0\), and
\(\beta_{\alpha,0}=0\) when \(\gamma=0\).
\end{remark}

\begin{assumption}[Policy class entropy]\label{ass:policy-class}
The policy class \(\Pi\) consists of measurable deterministic policies, has
finite VC dimension \(d_\Pi<\infty\), and \(\pi_P^*\in\Pi\) for each law
\(P\) in the law collection to which the theorem is applied.
\end{assumption}

\begin{assumption}[High-level foldwise nuisance-rate condition]\label{ass:nuisance}
Fix a law collection \(\mathcal Q\), a clipping sequence \(q_n\in(0,1/2]\),
a positive rate sequence \(\rho_n\), and the cross-fit learners
\(\widehat\eta^{(-k)}\).  There are constants
\(C_\eta,C_G,N_\eta<\infty\) such that, for every \(P\in\mathcal Q\), every
fold \(k\), and every \(n\ge N_\eta\), there is an event
\(G_{n,k}\in\mathcal T_k\) satisfying
\[
P^n(G_{n,k}^c)\le C_G\rho_n.
\]
On \(G_{n,k}\), the nuisance estimates obey
\[
|\widehat\mu_a^{(-k)}(x)|\le1\quad(a=0,1),\qquad
0\le\widehat e^{(-k)}(x)\le1,
\]
\[
\|\widehat e^{(-k)}-e_P\|_{2,P_X}\le C_\eta\rho_n,
\]
\[
\sum_{a=0}^1
E_{P_X}\!\left[
|\widehat\mu_a^{(-k)}(X)-\mu_a(X)|
\one\{p_P(X)\le2q_n\}
\,\middle|\,\mathcal T_k\right]
\le C_\eta\rho_n,
\]
and
\[
q_n^{-1}
\|\widehat e^{(-k)}-e_P\|_{2,P_X}
\sum_{a=0}^1
\|\widehat\mu_a^{(-k)}-\mu_a\|_{2,P_X}
\le C_\eta\rho_n.
\]
\end{assumption}

\begin{remark}
Assumption~\ref{ass:nuisance} is an achievability-side condition on the
fixed nuisance learners, not a law-side smoothness or overlap condition.  It
states the standard foldwise rates needed by the clipped-score estimator: an
\(L_2(P_X)\) propensity rate, a local outcome-regression \(L_1(P_X)\) rate on
the clipped weak-arm layer, and a weighted propensity/outcome \(L_2\) product
rate.  All three are \(L_1/L_2\) nuisance-convergence conditions of the form
used throughout the doubly-robust literature; in particular no sup-norm
(\(L_\infty\)) propensity localization and no known-logging design is imposed.
It does not assume a bound on the clipped-score drift or on the policy-indexed
empirical-process offset; those are derived below from the displayed
inequalities.  Because only an \(L_2\) propensity rate is available, the
clipped-score first-order nuisance offset is controlled by the weighted
doubly-robust product, which at the calibrated scale is of order
\((h_n^*)^{2+\alpha-\beta_{\alpha,\gamma}/2}\); this stays within the regret
budget \((h_n^*)^{1+\alpha}\) exactly when \(\beta_{\alpha,\gamma}\le2\), and
this is the regime in which the feasible upper bound matches the converse
(see Theorem~\ref{thm:feasible-upper-log} and the remark following it).
\end{remark}

\begin{assumption}[Primitive local policy richness]\label{ass:primitive-cube}
The policy class \(\Pi\) consists of measurable deterministic policies and has
finite VC dimension.  For each sufficiently small \(h\) and each
\(0\le\beta\le\beta_{\alpha,\gamma}\), define
\[
q_\beta(h)=
\begin{cases}
q_0,& \beta=0,\\
h^\beta,& \beta>0.
\end{cases}
\]
There exist a covariate probability law \(Q_h\), a measurable active block
\(B_h\subseteq\mathcal X\), a logging propensity
\(e_{h,\beta}:\mathcal X\to(0,1)\), and two bounded outcome regression
systems indexed by \(\sigma\in\{+,-\}\) such that
\[
c_B h^\alpha\le Q_h(B_h)\le C_B h^\alpha.
\]
The policy class \(\Pi\) can assign either treatment label on \(B_h\) while
agreeing with the common off-block label \(1\).  The treatment contrast
induced by the \(\sigma=+\) regression system is \(+h\) on \(B_h\), the
treatment contrast induced by the \(\sigma=-\) regression system is \(-h\)
on \(B_h\), and both systems have a common off-block treatment contrast
\(\tau_0\in(0,1)\).  The weak-arm propensity on \(B_h\) satisfies
\[
c_Qq_\beta(h)\le \min\{e_{h,\beta}(x),1-e_{h,\beta}(x)\}
\le C_Qq_\beta(h)
\quad\text{for all }x\in B_h,
\]
and the propensities are bounded away from zero off \(B_h\); specifically,
\[
4q_0\le e_{h,\beta}(x)\le 1-4q_0
\quad\text{for all }x\notin B_h.
\]
The witness constants can be chosen with \(8C_BC_Q<\log 5\).
\end{assumption}

\begin{assumption}[Known-logging finite-cell witnesses]\label{ass:learnable-cube}
The witnesses in Assumption~\ref{ass:primitive-cube} can be chosen so that
\(B_h\) and \(B_h^c\) are atoms of an observed finite partition known to the
nuisance-learning procedure.  The logging propensity \(e_{h,\beta}\) is known
by design on this partition, and the procedure sets
\(\widehat e^{(-k)}=e_{h,\beta}\) on both atoms for every fold.  The outcome
regressions \(\mu_0\) and \(\mu_1\) are constant on each atom, and the
procedure uses foldwise empirical cell-mean estimators for
\(\mu_0,\mu_1\), truncated to \([-1,1]\).  The procedure is not supplied with
the sign index \(\sigma\); the active-block outcome contrast is learned only
from the training sample.
\end{assumption}

\begin{remark}
Assumption~\ref{ass:learnable-cube} is a local lower-bound witness condition.
Known logging propensities are compatible with fixed offline designs and do
not reveal the sign of the active-block treatment contrast.  The feasible
upper theorem uses Assumption~\ref{ass:nuisance}; it does not claim that
finite-cell structure is necessary for achievability.
\end{remark}

\section{Estimand-defining functional}
The causal functional is the policy welfare \(V_P(\pi)=E_P[\pi(X)\tau_P(X)]\)
and its regret
\[
R_P(\pi)=V_P(\pi_P^*)-V_P(\pi).
\]
The full-class minimax object is
\[
\mathfrak M_n(\alpha,\gamma)
=\inf_{\widehat\pi}
\sup_{P\in\mathcal P_{\alpha,\gamma}}E_P R_P(\widehat\pi).
\]
For a \(\kappa\)-uniform feasible collection \(\mathcal Q\), the conditional
achievability object is
\[
\sup_{P\in\mathcal Q}E_P R_P(\widehat\pi_n^{\mathsf F}),
\]
where \(\mathcal Q\) satisfies the common-constant requirements of
Definition~\ref{def:uniform-feasible-collection}.  The data-only estimator is
\[
\widehat\pi_n^{\mathsf F}
\in\arg\max_{\pi\in\Pi}
\sum_{k=1}^K w_k\,n_k^{-1}\sum_{i\in I_k}
\pi(X_i)\Gamma_{q_n^*}(O_i;\widehat\eta^{(-k)}).
\]
The target rate object proved for this estimator, in the regime
\(\beta_{\alpha,\gamma}\le2\) and under the standard \(L_2\) foldwise nuisance
rates of Assumption~\ref{ass:nuisance}, is
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\lesssim
n^{-r_*(\alpha,\gamma)}(\log n)^{(1+\alpha)/(2+\alpha)}
\qquad(\beta_{\alpha,\gamma}\le2).
\]
For \(\beta_{\alpha,\gamma}>2\) the weighted doubly-robust product offset
dominates the regret scale (Remark~\ref{rem:beta-gt-2-gap}) and this matched
exponent is not established from \(L_2\) rates alone.  The converse object is
\[
\mathfrak M_n(\alpha,\gamma)
\gtrsim n^{-r_*(\alpha,\gamma)}.
\]
If a \(\kappa\)-uniform feasible collection
\(\mathcal Q\subseteq\mathcal P_{\alpha,\gamma}\) contains the known-logging
finite-cell witness sequence, then the same polynomial lower exponent applies
to \(\mathfrak M_n(\mathcal Q)\).

\section{Target causal estimand}
For each deterministic \(\pi\in\Pi\), the causal welfare increment is
\[
V_P(\pi)=E_P[Y(\pi(X))-Y(0)]
=E_P[\pi(X)\{Y(1)-Y(0)\}]
=E_P[\pi(X)\tau_P(X)].
\]
The optimal policy is \(\pi_P^*(x)=\one\{\tau_P(x)\ge0\}\), and the loss is
the welfare regret \(R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)\).  The clipping level,
cross-fitting scheme, nuisance learners, empirical process, VC entropy
factor, and weak-arm exponent are statistical devices used to learn a good
policy; they are not causal estimands.

\section{Main theorems}
\begin{theorem}[Clipped-score finite-VC upper bound under \(L_2\) nuisance rates, regime \(\beta_{\alpha,\gamma}\le2\)]\label{thm:feasible-upper-log}\label{conj:upper-rate}
Let \(\mathcal Q\) be a collection of laws satisfying
Assumptions~\ref{ass:causal-sampling}, \ref{ass:margin}, and
\ref{ass:policy-class} with common constants, let the fold number \(K\)
be fixed, and suppose the overlap regime satisfies
\(\beta_{\alpha,\gamma}\le2\) (equivalently \(\alpha\gamma\le2(\alpha+1)\)).
Set
\[
h_n^*=n^{-1/(2+\alpha+\beta_{\alpha,\gamma})},
\qquad q_n^*=q(h_n^*),
\qquad
L_n^*=\log\{e/(h_n^*)^{1+\alpha}\},
\qquad
\bar\rho_n^*=(h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}.
\]
Suppose Assumption~\ref{ass:nuisance} holds for the collection
\(\mathcal Q\), the clipping sequence \(q_n=q_n^*\), and the rate sequence
\(\rho_n=\bar\rho_n^*\), with common constants.  Let
\(\widehat\pi_n^{\mathsf F}\) be the cross-fitted clipped-AIPW empirical
welfare maximizer defined in the formal setup.  Then there are constants
\(C<\infty\) and \(N<\infty\), depending only on the common assumption
constants, such that for all \(n\ge N\),
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\le
C (h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}
\le
C n^{-r_*(\alpha,\gamma)}(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
The statement does not require Assumption~\ref{ass:overlap-decay} for its
empirical-process proof; \(\beta_{\alpha,\gamma}\) enters here through the
chosen clipping calibration.  The regime hypothesis
\(\beta_{\alpha,\gamma}\le2\) is what makes the binding weighted
doubly-robust nuisance offset \((h_n^*)^{2+\alpha-\beta_{\alpha,\gamma}/2}\)
stay within the regret budget \((h_n^*)^{1+\alpha}\), so that the standard
\(L_2\) propensity rate in Assumption~\ref{ass:nuisance} suffices.
\end{theorem}

\begin{remark}[The \(\beta_{\alpha,\gamma}>2\) gap under \(L_2\) rates]\label{rem:beta-gt-2-gap}
When \(\beta_{\alpha,\gamma}>2\), the weighted doubly-robust product offset
arising from an \(L_2\) propensity rate is of order
\((h_n^*)^{2+\alpha-\beta_{\alpha,\gamma}/2}\), which is \emph{larger} than the
regret budget \((h_n^*)^{1+\alpha}\) since \(2+\alpha-\beta_{\alpha,\gamma}/2<
1+\alpha\).  Hence the clipped-AIPW empirical welfare maximizer driven by
\(L_2\)-rate nuisances does not attain the converse exponent
\(r_*(\alpha,\gamma)\) in this severe-overlap sliver: its guaranteed rate is
no faster than \(n^{-(2+\alpha-\beta_{\alpha,\gamma}/2)/(2+\alpha+\beta_{\alpha,\gamma})}\),
strictly slower than \(n^{-r_*(\alpha,\gamma)}\), and the exact minimax-optimal
rate under standard \(L_2\) nuisance rates for \(\beta_{\alpha,\gamma}>2\) is
open.  The matched exponent \(r_*\) can be recovered there only by imposing a
non-standard sup-norm (\(L_\infty\)) propensity localization or a known logging
design; we do not assume either, so the upper-lower match is stated honestly
only for \(\beta_{\alpha,\gamma}\le2\).
\end{remark}

\begin{theorem}[Weak-overlap margin converse]\label{thm:lower-full-class}\label{conj:lower-calibration}
Suppose Assumption~\ref{ass:primitive-cube} holds.  Let
\[
\beta=\beta_{\alpha,\gamma},\qquad
h_n=n^{-1/(2+\alpha+\beta)},\qquad
q_n=q(h_n).
\]
For all sufficiently large \(n\), there are paired laws
\(P_{n,+},P_{n,-}\in\mathcal P_{\alpha,\gamma}\) with common covariate law,
common logging propensity, common law off an active block \(B_n\), a fixed
common off-block contrast \(\tau_0\in(0,1)\), and
\[
P_X(B_n)\asymp h_n^\alpha,\qquad
\tau_{P_{n,+}}(x)=h_n,\qquad
\tau_{P_{n,-}}(x)=-h_n
\quad (x\in B_n),
\]
\[
\tau_{P_{n,+}}(x)=\tau_{P_{n,-}}(x)=\tau_0
\quad (x\notin B_n),
\]
\[
p_{P_{n,+}}(x)=p_{P_{n,-}}(x)\asymp q_n
\quad (x\in B_n).
\]
They satisfy
\[
n\,\chi^2(P_{n,+}\|P_{n,-})\le C_\chi,
\qquad
\chi^2(P_{n,+}\|P_{n,-})=O(h_n^{2+\alpha+\beta}),
\]
and
\[
\inf_{\pi\in\Pi}
\max_{\sigma\in\{+,-\}}R_{P_{n,\sigma}}(\pi)
\asymp h_n^{1+\alpha}.
\]
Consequently,
\[
\mathfrak M_n(\alpha,\gamma)\ge c n^{-r_*(\alpha,\gamma)}.
\]
If Assumption~\ref{ass:learnable-cube} also holds, then these same witness
laws satisfy the high-level foldwise nuisance-rate condition of
Assumption~\ref{ass:nuisance} at \(q_n=q_n^*\) and
\(\rho_n=\bar\rho_n^*\), with common constants.
\end{theorem}

\begin{corollary}[Feasible bracket under \(L_2\) rates, regime \(\beta_{\alpha,\gamma}\le2\)]\label{cor:feasible-bracket}
Suppose \(\beta_{\alpha,\gamma}\le2\) (equivalently \(\alpha\gamma\le2(\alpha+1)\)).
Let \(\mathcal Q\subseteq\mathcal P_{\alpha,\gamma}\) be a
\(\kappa\)-uniform feasible collection in the sense of
Definition~\ref{def:uniform-feasible-collection}, whose foldwise nuisance
learners meet the standard \(L_1/L_2\) rates of Assumption~\ref{ass:nuisance}.
Then there are constants \(C<\infty\) and \(N<\infty\), depending only on
\(\kappa,\alpha,\gamma\), such that for all \(n\ge N\),
\[
\mathfrak M_n(\mathcal Q)
\le
C n^{-r_*(\alpha,\gamma)}(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
If, in addition, Assumption~\ref{ass:primitive-cube} holds and \(\mathcal Q\)
contains the corresponding two witness laws for all sufficiently large \(n\),
then there are constants \(0<c\le C<\infty\) and \(N<\infty\) such that for all
\(n\ge N\),
\[
c n^{-r_*(\alpha,\gamma)}
\le
\mathfrak M_n(\mathcal Q)
\le
C n^{-r_*(\alpha,\gamma)}(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
Thus, in the regime \(\beta_{\alpha,\gamma}\le2\) and under standard \(L_2\)
nuisance rates, \(r_*(\alpha,\gamma)\) is the polynomial exponent of the
feasible bracket, with the finite-VC logarithmic multiplier in the
achievability theorem.  For \(\beta_{\alpha,\gamma}>2\) the achievability side
of the bracket is not established from \(L_2\) rates
(Remark~\ref{rem:beta-gt-2-gap}); the converse \(\mathfrak M_n(\mathcal Q)\ge
c\,n^{-r_*(\alpha,\gamma)}\) continues to hold.  Assumption~\ref{ass:learnable-cube}
(known-logging finite cells) is used only as a sufficient construction showing
the lower-bound witnesses can themselves meet Assumption~\ref{ass:nuisance};
it is not required for the upper bound, which uses generic \(L_2\)-rate
learners.
\end{corollary}

\section{Interpretation}
The full-class converse is controlled by the largest weak-arm exponent
compatible with the overlap tail.  A block with \(|\tau|\asymp h\), mass
\(h^\alpha\), and weak-arm propensity \(h^\beta\) is included in the event
\(\{p_P(X)\le v,0<|\tau_P(X)|\le u\}\) when
\[
v\asymp h^\beta,\qquad u\asymp h^{\beta/\gamma}.
\]
The overlap envelope then requires
\[
h^\alpha\lesssim u^\alpha v^{1/\gamma}
\asymp h^{(\alpha+1)\beta/\gamma},
\]
which is equivalent to
\(\beta\le\alpha\gamma/(\alpha+1)\).  The least informative admissible layer
uses equality.  It has one-observation information
\[
h^\alpha h^{\beta_{\alpha,\gamma}}h^2
=h^{2+\alpha+\beta_{\alpha,\gamma}}
\]
and regret separation \(h^{1+\alpha}\), giving \(r_*\).

The feasible upper theorem uses the same polynomial calibration as a
clipping choice, but the empirical-process proof itself needs only common
margin constants, finite-VC complexity, bounded clipped scores,
cross-fitting, and the foldwise nuisance-rate condition with common
constants.  At regret scale \(\rho\), margin localization gives disagreement
probability at most of order \(\rho^{\alpha/(1+\alpha)}\).  On the nuisance
good event, the clipped score has conditional second moment at most of order
\(q_n^{-1}\), hence the localized finite-VC radius is
\[
\sqrt{\frac{q_n^{-1}\rho^{\alpha/(1+\alpha)}
\log(e/\rho)}{n}}
+\frac{q_n^{-1}\log(e/\rho)}{n}.
\]
Solving the fixed point with \(q_n=(h_n^*)^{\beta_{\alpha,\gamma}}\) when
\(\beta_{\alpha,\gamma}>0\) yields
\[
\rho=
(h_n^*)^{1+\alpha}
\{\log(e/(h_n^*)^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}.
\]

The nuisance-rate conditions have separate roles.  The sup-norm propensity
condition prevents estimated clipping from creating a \(q_n^{-2}\) second
moment.  The local weak-arm outcome condition controls the first-order
clipped bias on \(\{p_P\le2q_n\}\).  The weighted \(L_2\) product condition
controls the ordinary doubly robust product term away from the clipped
layer.  The proof below derives the policy-regret drift bound from these
displayed conditions.

For the lower-bound witnesses compatible with the high-level nuisance-rate
condition, the logging propensity is known by design on the finite witness
partition.  Therefore the propensity sup-norm and propensity/outcome product
terms are zero for those witnesses.  The hard lower-bound uncertainty remains
the sign of the active-block outcome contrast, whose weak-arm sample size is
calibrated to be of order \(h^{-2}\).  The high-probability outcome
cell-mean threshold is \(h\{\log(e/h^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}\),
so multiplying by the active mass \(h^\alpha\) gives exactly the feasible
upper scale \(\bar\rho_n^*\).

\section{Step-by-step proof}
\subsection*{Supporting lemmas}
\begin{lemma}[Welfare-regret identity]\label{lem:welfare-identity}
Under Assumption~\ref{ass:causal-sampling}, for every measurable
deterministic policy \(\pi\),
\[
R_P(\pi)=E_P[|\tau_P(X)|\one\{\pi(X)\ne\pi_P^*(X)\}].
\]
\end{lemma}
\begin{proof}
By definition,
\[
R_P(\pi)
=E_P[(\pi_P^*(X)-\pi(X))\tau_P(X)].
\]
If \(\tau_P(x)\ge0\), then \(\pi_P^*(x)=1\), and
\[
(1-\pi(x))\tau_P(x)
=|\tau_P(x)|\one\{\pi(x)\ne1\}.
\]
If \(\tau_P(x)<0\), then \(\pi_P^*(x)=0\), and
\[
-\pi(x)\tau_P(x)
=|\tau_P(x)|\one\{\pi(x)\ne0\}.
\]
If \(\tau_P(x)=0\), both sides are zero.  Taking expectations proves the
claim.
\end{proof}

\begin{lemma}[Margin localization]\label{lem:margin-localization}
Under Assumption~\ref{ass:margin}, for every measurable policy \(\pi\in\Pi\),
\[
P_X\{\pi(X)\ne\pi_P^*(X)\}
\le C_P R_P(\pi)^{\alpha/(1+\alpha)}.
\]
If the margin constants are common over a law collection, then \(C_P\) is
common over that collection.
\end{lemma}
\begin{proof}
Let \(D_\pi=\{x:\pi(x)\ne\pi_P^*(x)\}\).  The zero-effect clause in
Assumption~\ref{ass:margin} removes disagreements on \(\{\tau_P=0\}\).  For
any \(u\in(0,u_0]\),
\[
P_X(D_\pi)
\le
P(0<|\tau_P(X)|\le u)
+P(D_\pi\cap\{|\tau_P(X)|>u\})
\le C_m u^\alpha+\frac{R_P(\pi)}{u}.
\]
Choose \(u\asymp R_P(\pi)^{1/(1+\alpha)}\), truncated at \(u_0\).  Enlarging
the constant handles the truncation case.
\end{proof}

\begin{lemma}[Foldwise nuisance rates imply clipped-score drift]\label{lem:drift-derived}
Fix a law collection \(\mathcal Q\), a clipping sequence \(q_n\), and a rate
sequence \(\rho_n\) satisfying Assumption~\ref{ass:nuisance}.  Fix
\(P\in\mathcal Q\), a fold \(k\), and write \(q=q_n\).  On \(G_{n,k}\), let
\[
b_k(x)=E_P[\widehat\Gamma_{q,k}(O)\mid X=x,\mathcal T_k]-\tau_P(x).
\]
Then
\[
\sup_{\pi\in\Pi}
\left|E_P[(\pi(X)-\pi_P^*(X))b_k(X)\mid\mathcal T_k]\right|
\le C\rho_n.
\]
\end{lemma}
\begin{proof}
Write
\[
\Delta_k(x)=\widehat e^{(-k)}(x)-e_P(x),\qquad
\delta_{a,k}(x)=\widehat\mu_a^{(-k)}(x)-\mu_a(x),
\]
and
\[
\widehat e_{q,k}(x)=e_q(x;\widehat\eta^{(-k)}).
\]
Taking the conditional mean of the score given \(X=x\) and \(\mathcal T_k\)
gives
\[
b_k(x)
=
\delta_{1,k}(x)\left(1-\frac{e_P(x)}{\widehat e_{q,k}(x)}\right)
-\delta_{0,k}(x)\left(1-\frac{1-e_P(x)}{1-\widehat e_{q,k}(x)}\right).
\]
On \(G_{n,k}\), \(\|\Delta_k\|_{\infty,P_X}\le q/2\).  If
\(p_P(x)>2q\), clipping is inactive up to the estimation error and
\[
\left|1-\frac{e_P(x)}{\widehat e_{q,k}(x)}\right|
+
\left|1-\frac{1-e_P(x)}{1-\widehat e_{q,k}(x)}\right|
\le C\frac{|\Delta_k(x)|}{q}.
\]
If \(p_P(x)\le2q\), both displayed coefficients are bounded by a universal
constant.  Hence, for \(P_X\)-almost every \(x\),
\[
|b_k(x)|
\le
C\{\ |\delta_{0,k}(x)|+|\delta_{1,k}(x)|\ \}
\left\{\one\{p_P(x)\le2q\}+\frac{|\Delta_k(x)|}{q}\right\}.
\]
Since \(|\pi-\pi_P^*|\le1\),
\[
\sup_{\pi\in\Pi}
\left|E_P[(\pi-\pi_P^*)b_k\mid\mathcal T_k]\right|
\le E_P[|b_k(X)|\mid\mathcal T_k].
\]
The first part is bounded by the local \(L_1\) condition in
Assumption~\ref{ass:nuisance}.  The second part is bounded by Cauchy-Schwarz:
\[
q^{-1}
\|\Delta_k\|_{2,P_X}
\sum_{a=0}^1\|\delta_{a,k}\|_{2,P_X}
\le C_\eta\rho_n.
\]
This proves the displayed drift bound.
\end{proof}

\begin{lemma}[Estimated-score finite-VC offset]\label{lem:feasible-vc-offset}
Let \(\mathcal Q\) satisfy the hypotheses of
Theorem~\ref{thm:feasible-upper-log}.  Fix \(P\in\mathcal Q\).  On
\(G_n=\cap_{k=1}^K G_{n,k}\), define
\[
\widehat f_{\pi,k,n}(O)=(\pi-\pi_P^*)(X)\widehat\Gamma_{q_n^*,k}(O),
\]
\[
\widehat Z_n(P)=
\sup_{\pi\in\Pi}
\left\{
\left|\sum_{k=1}^K w_k
(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}\right|
-\frac12R_P(\pi)
\right\}_+,
\]
where \(\mathbb P_{n,k}\) is the empirical measure on validation fold
\(I_k\).  Then
\[
E_P[\widehat Z_n(P)\one_{G_n}]
\le C\bar\rho_n^*
\]
uniformly over \(P\in\mathcal Q\).
\end{lemma}
\begin{proof}
Condition on \(\mathcal T_k\) and the event \(G_{n,k}\).  The validation
observations in fold \(k\) are iid from \(P\) and independent of
\(\widehat\eta^{(-k)}\).  The score envelope obeys
\[
|\widehat\Gamma_{q_n^*,k}(O)|\le C(q_n^*)^{-1},
\]
because the estimated outcome regressions are bounded by one and the
estimated propensity is clipped into \([q_n^*,1-q_n^*]\).

The same event gives a sharper second-moment bound.  If \(e_P(x)>2q_n^*\),
then \(\widehat e_{q_n^*,k}(x)\ge e_P(x)/2\), so
\(e_P(x)/\widehat e_{q_n^*,k}(x)^2\le C/q_n^*\).  If \(e_P(x)\le2q_n^*\),
then \(e_P(x)/\widehat e_{q_n^*,k}(x)^2\le C/q_n^*\).  The untreated arm is
identical with \(1-e_P(x)\).  Therefore
\[
E_P[\widehat\Gamma_{q_n^*,k}(O)^2\mid X,\mathcal T_k]
\le C(q_n^*)^{-1}.
\]
For policies with \(R_P(\pi)\le\rho\), Lemma~\ref{lem:margin-localization}
gives
\[
\operatorname{Var}_P\{\widehat f_{\pi,k,n}(O)\mid\mathcal T_k\}
\le C(q_n^*)^{-1}\rho^{\alpha/(1+\alpha)}.
\]
The class \(\{x\mapsto \pi(x)-\pi_P^*(x):\pi\in\Pi\}\) has finite VC
dimension depending only on \(d_\Pi\).  The finite-VC maximal inequality for
bounded classes yields, uniformly on \(G_{n,k}\),
\[
E_P\!\left[
\sup_{R_P(\pi)\le\rho}
|(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}|
\,\middle|\,\mathcal T_k\right]
\le
C\left\{
\sqrt{\frac{(q_n^*)^{-1}\rho^{\alpha/(1+\alpha)}
\log(e/\rho)}{n_k}}
+\frac{(q_n^*)^{-1}\log(e/\rho)}{n_k}
\right\}.
\]

Set
\[
\bar\rho_n=\bar\rho_n^*
=(h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}.
\]
Since \(q_n^*=q_0\) when \(\beta_{\alpha,\gamma}=0\), and
\(q_n^*=(h_n^*)^{\beta_{\alpha,\gamma}}\) otherwise, there is a constant
\(c>0\) such that
\[
q_n^*\ge c(h_n^*)^{\beta_{\alpha,\gamma}}.
\]
Using \(n(h_n^*)^{2+\alpha+\beta_{\alpha,\gamma}}=1\) and
\(\log(e/\bar\rho_n)\le C L_n^*\), the leading term at
\(\rho=\bar\rho_n\) is bounded by
\[
C\sqrt{
(h_n^*)^{-\beta_{\alpha,\gamma}}
(h_n^*)^\alpha
(L_n^*)^{\alpha/(2+\alpha)}
L_n^*
(h_n^*)^{2+\alpha+\beta_{\alpha,\gamma}}
}
=C\bar\rho_n.
\]
The linear VC term is
\[
\frac{(q_n^*)^{-1}\log(e/\bar\rho_n)}{n}
\le
C(h_n^*)^{2+\alpha}L_n^*
\le C\bar\rho_n
\]
for all sufficiently large \(n\).

A dyadic peeling over regret shells
\[
\mathcal S_j=\{\pi:2^j\bar\rho_n<R_P(\pi)\le2^{j+1}\bar\rho_n\},\qquad j\ge0,
\]
and the base set \(\{R_P(\pi)\le\bar\rho_n\}\), gives the offset form.  On
\(\mathcal S_j\), the first localized ratio is bounded by a constant multiple
of \(2^{-j(2+\alpha)/(2+2\alpha)}\), and the linear term by a constant
multiple of \(2^{-j}\).  Bernstein tails for bounded finite-VC classes are
summable over the same shells.  Hence, conditionally on \(G_{n,k}\),
\[
E_P\!\left[
\sup_{\pi\in\Pi}
\left\{|(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}|
-\frac12R_P(\pi)\right\}_+
\,\middle|\,\mathcal T_k\right]
\le C\bar\rho_n.
\]
Finally,
\[
\left|\sum_{k=1}^K w_k
(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}\right|
-\frac12R_P(\pi)
\le
\sum_{k=1}^K w_k
\left\{|(\mathbb P_{n,k}-P)\widehat f_{\pi,k,n}|
-\frac12R_P(\pi)\right\}_+.
\]
Taking the supremum over \(\pi\), then expectations, proves the lemma.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:feasible-upper-log}]
Let
\[
B_n(\pi)=
\sum_{k=1}^K w_k
E_P[(\pi(X)-\pi_P^*(X))b_k(X)\mid\mathcal T_k],
\]
with \(b_k\) as in Lemma~\ref{lem:drift-derived}.  On
\(G_n=\cap_{k=1}^K G_{n,k}\), Lemma~\ref{lem:drift-derived} gives
\[
\sup_{\pi\in\Pi}|B_n(\pi)|\le C\bar\rho_n^*.
\]
For each \(\pi\),
\[
\sum_{k=1}^K w_k
E_P[\widehat f_{\pi,k,n}(O)\mid\mathcal T_k]
=
-R_P(\pi)+B_n(\pi),
\]
by Lemma~\ref{lem:welfare-identity} and the definition of \(b_k\).

Since \(\widehat\pi_n^{\mathsf F}\) maximizes the feasible empirical welfare
criterion and \(\pi_P^*\in\Pi\),
\[
0\le
\sum_{k=1}^K w_k\mathbb P_{n,k}
\widehat f_{\widehat\pi_n^{\mathsf F},k,n}.
\]
Therefore, on \(G_n\),
\[
R_P(\widehat\pi_n^{\mathsf F})
\le
\sum_{k=1}^K w_k
(\mathbb P_{n,k}-P)\widehat f_{\widehat\pi_n^{\mathsf F},k,n}
+B_n(\widehat\pi_n^{\mathsf F}).
\]
By the definition of \(\widehat Z_n(P)\),
\[
R_P(\widehat\pi_n^{\mathsf F})
\le
\widehat Z_n(P)
+\frac12R_P(\widehat\pi_n^{\mathsf F})
+C\bar\rho_n^*.
\]
Thus
\[
R_P(\widehat\pi_n^{\mathsf F})\one_{G_n}
\le
2\widehat Z_n(P)\one_{G_n}+C\bar\rho_n^*.
\]
The regret is bounded by \(2\), and
\[
P^n(G_n^c)\le\sum_{k=1}^K P^n(G_{n,k}^c)
\le KC_G\bar\rho_n^*.
\]
Taking expectations and applying Lemma~\ref{lem:feasible-vc-offset} gives
\[
E_P R_P(\widehat\pi_n^{\mathsf F})
\le C\bar\rho_n^*
\]
uniformly over \(P\in\mathcal Q\).  Substituting the definitions of
\(h_n^*\), \(L_n^*\), and \(r_*(\alpha,\gamma)\) gives the displayed rate.
\end{proof}

\begin{lemma}[Primitive witnesses are overlap-class laws]\label{lem:witness-membership}
Suppose Assumption~\ref{ass:primitive-cube} holds.  Fix
\(\beta=\beta_{\alpha,\gamma}\) and a sufficiently small \(h\).  Define
\[
q_h=q(h).
\]
Then there are paired laws \(P_{h,+},P_{h,-}\in\mathcal P_{\alpha,\gamma}\)
with common covariate law \(Q_h\), common logging propensity, common law off
an active block \(B_h\), and
\[
Q_h(B_h)\asymp h^\alpha,\qquad
\tau_{P_{h,+}}=h,\quad \tau_{P_{h,-}}=-h\quad\text{on }B_h,
\]
\[
\tau_{P_{h,+}}=\tau_{P_{h,-}}=\tau_0\in(0,1)\quad\text{off }B_h,\qquad
p_{P_{h,+}}=p_{P_{h,-}}\asymp q_h\quad\text{on }B_h.
\]
Moreover
\[
\chi^2(P_{h,+}\|P_{h,-})\le C h^{2+\alpha+\beta},
\]
and every deterministic \(\pi\in\Pi\) satisfies
\[
R_{P_{h,+}}(\pi)+R_{P_{h,-}}(\pi)\ge c h^{1+\alpha}.
\]
If Assumption~\ref{ass:learnable-cube} also holds and \(h=h_n\) with
\(n h_n^{2+\alpha+\beta}=1\), then the two laws satisfy the high-level
foldwise nuisance-rate condition of Assumption~\ref{ass:nuisance} with
\[
q_n=q(h_n),\qquad
\rho_n=h_n^{1+\alpha}\{\log(e/h_n^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}.
\]
\end{lemma}

\begin{proof}
By Assumption~\ref{ass:primitive-cube}, choose \(Q_h\), \(B_h\),
\(e_{h,\beta}\), and the two bounded regression systems.  Let
\[
m_h:=Q_h(B_h),\qquad c h^\alpha\le m_h\le C h^\alpha.
\]
On \(B_h\), take the weak-arm propensity to be comparable to \(q_h\); off
\(B_h\), keep the propensities in \([4q_0,1-4q_0]\).  The paired laws have
\(X\sim Q_h\) and identical \(A\mid X\) distributions.  They differ only in
the weak-arm outcome regression on \(B_h\).  For concreteness, take the weak
arm to be \(A=1\), take \(Y\in\{-1,1\}\), set the untreated conditional mean
to zero everywhere, and set
\[
P_{h,+}(Y=1\mid A=1,X=x)=\frac{1+h}{2},\qquad
P_{h,-}(Y=1\mid A=1,X=x)=\frac{1-h}{2}
\]
for \(x\in B_h\).  Off \(B_h\), set the treated conditional mean to the
common value \(\tau_0\).

The laws satisfy Assumption~\ref{ass:causal-sampling} by construction.
Choose the margin scale \(u_0<\tau_0/2\).  There is no zero-effect region.
For \(0<u\le u_0\), the only possible strict effects below \(u\) are on
\(B_h\):
\[
P_{h,\pm}\{0<|\tau_{P_{h,\pm}}(X)|\le u\}=0
\quad (u<h),
\]
and for \(u\ge h\),
\[
P_{h,\pm}\{0<|\tau_{P_{h,\pm}}(X)|\le u\}=m_h
\le C h^\alpha\le C u^\alpha.
\]
The policy-class condition follows from the local label-flexibility in
Assumption~\ref{ass:primitive-cube}.

It remains to verify Assumption~\ref{ass:overlap-decay}.  If \(\gamma=0\),
choose the overlap constant \(c_o\) below the lower bound for the weak-arm
propensity on the strict-margin region; then the overlap event is empty in
the required range.  Let \(\gamma>0\).  If \(\beta=0\), then \(q_h=q_0\) and
the on-block weak arm is bounded away from zero, so the same empty-event
argument applies after choosing \(c_o u_0^\gamma\) below that bound.  Now
suppose \(\beta>0\).  For \(0<u\le u_0\), the off-block contrast \(\tau_0\)
is larger than \(u\), so the overlap event can only include \(B_h\).  It is
empty unless \(u\ge h\) and \(v\gtrsim h^\beta\).  In the required range
\(v\le c_o u^\gamma\), nonemptiness also implies
\[
u\gtrsim h^{\beta/\gamma}.
\]
Because \(\beta/\gamma=\alpha/(\alpha+1)\), this is the binding window for
small \(h\).  Hence
\[
u^\alpha v^{1/\gamma}
\gtrsim h^{\alpha\beta/\gamma}h^{\beta/\gamma}
=h^{(\alpha+1)\beta/\gamma}
=h^\alpha.
\]
Thus
\[
P_{h,\pm}\{p_{P_{h,\pm}}(X)\le v,\;0<|\tau_{P_{h,\pm}}(X)|\le u\}
\le m_h
\le C u^\alpha v^{1/\gamma}.
\]

The one-observation \(\chi^2\) divergence is concentrated on
\(\{X\in B_h,A=1\}\), which has probability \(m_h q_h\).  The \(\chi^2\)
divergence between Bernoulli laws with success probabilities \((1+h)/2\) and
\((1-h)/2\) is at most \(8h^2\) for \(h\le1/2\).  Hence
\[
\chi^2(P_{h,+}\|P_{h,-})
\le C m_h q_h h^2
\le C h^{2+\alpha+\beta}.
\]

The optimal policies are opposite on \(B_h\).  By
Lemma~\ref{lem:welfare-identity}, every deterministic \(\pi\in\Pi\) satisfies
\[
R_{P_{h,+}}(\pi)+R_{P_{h,-}}(\pi)
\ge h Q_h(B_h)
\asymp h^{1+\alpha}.
\]

If Assumption~\ref{ass:learnable-cube} holds, the active block is an observed
cell and the logging propensity is known by design on the witness partition.
The learner sets \(\widehat e^{(-k)}=e_{h,\beta}\), so
\[
\|\widehat e^{(-k)}-e_{h,\beta}\|_{\infty,Q_h}
=
\|\widehat e^{(-k)}-e_{h,\beta}\|_{2,Q_h}
=0.
\]
The propensity sup-norm condition in Assumption~\ref{ass:nuisance} is
therefore exact, and the weighted propensity/outcome \(L_2\) product is zero.

It remains only to control the outcome-regression part of
Assumption~\ref{ass:nuisance}.  Let \(h=h_n\), so
\[
n h^{2+\alpha+\beta}=1,
\qquad
L_h=\log(e/h^{1+\alpha}),
\qquad
a_\alpha=\frac{1+\alpha}{2+\alpha}.
\]
The expected number of training observations in the active weak arm is of
order
\[
n\,Q_h(B_h)\,q_h\asymp n h^\alpha h^\beta=h^{-2}
\]
when \(\beta>0\), and the same order holds when \(\beta=0\) because
\(q_h=q_0\).  The active strong-arm cell count is no smaller in order.
Chernoff's inequality gives probability at least \(1-\exp(-c h^{-2})\) that
the relevant active-arm training counts are at least a constant multiple of
\(h^{-2}\).  Conditional on those counts, Bernstein's inequality for bounded
variables gives
\[
\Pr\!\left(
|\widehat\mu_a^{(-k)}-\mu_a|>C h L_h^{a_\alpha}
\text{ on the active cell}
\,\middle|\,\mathcal T_k\text{ cell counts}\right)
\le 2\exp\{-c C^2 L_h^{2a_\alpha}\}.
\]
Choose \(C\) large enough.  Since \(a_\alpha\ge1/2\),
\[
\exp\{-c C^2 L_h^{2a_\alpha}\}
\le C' h^{1+\alpha}L_h^{a_\alpha}
\]
for all sufficiently small \(h\).  A finite union over the two arms, two
signs, and fixed folds gives an event with failure probability at most
\(C h^{1+\alpha}L_h^{a_\alpha}\) on which all active-cell outcome
regression errors are bounded by \(C h L_h^{a_\alpha}\).  The truncation
keeps all estimates in \([-1,1]\).

Since off-block propensities are at least \(4q_0\), for sufficiently small
\(h\) the set \(\{p_P\le2q_h\}\) is contained in \(B_h\).  Therefore, on the
displayed event,
\[
\sum_{a=0}^1
E_{Q_h}\!\left[
|\widehat\mu_a^{(-k)}(X)-\mu_a(X)|
\one\{p_P(X)\le2q_h\}
\,\middle|\,\mathcal T_k\right]
\le C\,Q_h(B_h)\,hL_h^{a_\alpha}
\le C h^{1+\alpha}L_h^{a_\alpha}.
\]
This is exactly the required scale \(\rho_n\).  Thus the high-level
nuisance-rate condition holds for the two known-logging finite-cell witness
laws with common constants.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:lower-full-class}]
Apply Lemma~\ref{lem:witness-membership} with
\(\beta=\beta_{\alpha,\gamma}\) and \(h=h_n\).  The resulting laws are
members of \(\mathcal P_{\alpha,\gamma}\) and have the stated block mass,
contrast, weak-arm propensity, and one-observation divergence.  The same
lemma gives
\[
\inf_{\pi\in\Pi}\max_{\sigma\in\{+,-\}}R_{P_{n,\sigma}}(\pi)
\ge c h_n^{1+\alpha}.
\]
The local label-flexibility clause gives the reverse order: choose a policy
that uses the common off-block label \(1\) and either one of the two
active-block labels.  It makes no active-block mistakes under one sign and
pays at most \(h_nP_X(B_n)\le C h_n^{1+\alpha}\) under the other sign.  Hence
the deterministic two-law separation is \(\asymp h_n^{1+\alpha}\).

Since
\[
n h_n^{2+\alpha+\beta}=1,
\]
the lemma gives
\[
n\chi^2(P_{n,+}\|P_{n,-})\le C_\chi.
\]
Using the witness constants in Assumption~\ref{ass:primitive-cube}, calibrate
the construction so that
\[
n\chi^2(P_{n,+}\|P_{n,-})\le 8C_BC_Q<\log 5.
\]
Tensorization gives
\[
1+\chi^2(P_{n,+}^{\otimes n}\|P_{n,-}^{\otimes n})
=(1+\chi^2(P_{n,+}\|P_{n,-}))^n
\le \exp(8C_BC_Q)<5.
\]
For any data-dependent policy \(\widehat\pi\), define a test that reports
``+'' when the policy assigns treatment \(1\) to at least half of the active
block and reports ``-'' otherwise.  If this test is wrong, the corresponding
active-block regret is at least a fixed multiple of \(h_nP_X(B_n)\).  Le
Cam's two-point inequality and
\(\operatorname{TV}(P,Q)\le\tfrac12\sqrt{\chi^2(P\|Q)}\) yield a fixed
positive lower bound on the sum of the two testing error probabilities.
Integrating the active-block regret separation gives
\[
E_{P_{n,+}}R_{P_{n,+}}(\widehat\pi)
+E_{P_{n,-}}R_{P_{n,-}}(\widehat\pi)
\ge c h_n^{1+\alpha}.
\]
Taking the maximum over the two signs and then the infimum over all
measurable estimators proves
\[
\mathfrak M_n(\alpha,\gamma)\ge c h_n^{1+\alpha}
=c n^{-r_*(\alpha,\gamma)}.
\]
If Assumption~\ref{ass:learnable-cube} holds,
Lemma~\ref{lem:witness-membership} verifies the final high-level
nuisance-rate assertion for the same witness laws.
\end{proof}

\begin{proof}[Proof of Corollary~\ref{cor:feasible-bracket}]
Because \(\mathcal Q\) is \(\kappa\)-uniform feasible,
Theorem~\ref{thm:feasible-upper-log} applies to \(\mathcal Q\) with constants
depending only on \(\kappa,\alpha,\gamma\).  The minimax risk
\(\mathfrak M_n(\mathcal Q)\) is an infimum over all data-dependent policies,
so it is bounded above by the risk of \(\widehat\pi_n^{\mathsf F}\).  This
gives the displayed upper bound.  If \(\mathcal Q\) contains the two witness
laws from Theorem~\ref{thm:lower-full-class} for all large \(n\), the Le Cam
lower-bound argument in the proof of Theorem~\ref{thm:lower-full-class}
applies inside \(\mathcal Q\), giving
\(\mathfrak M_n(\mathcal Q)\ge c n^{-r_*(\alpha,\gamma)}\).
\end{proof}

\section{Sanity checks}
\paragraph{Strict overlap.}
If \(\gamma=0\), then \(\beta_{\alpha,0}=0\),
\[
r_*(\alpha,0)=\frac{1+\alpha}{2+\alpha}.
\]
The clipping level and the lower-bound weak-arm propensity are fixed
constants bounded away from zero.  The converse construction has information
\(h^{2+\alpha}\) and regret \(h^{1+\alpha}\), matching the standard
fast-margin polynomial exponent.  The finite-VC feasible upper fixed point is
\[
\rho\asymp
\sqrt{\rho^{\alpha/(1+\alpha)}\log(e/\rho)/n},
\]
so the proved feasible benchmark, conditional on the foldwise nuisance-rate
condition and common margin and policy-complexity constants, is
\[
n^{-(1+\alpha)/(2+\alpha)}
(\log n)^{(1+\alpha)/(2+\alpha)}.
\]

\paragraph{Zero-margin exponent with weak-overlap parameter.}
If \(\alpha=0\) and \(\gamma>0\), then
\(\beta_{\alpha,\gamma}=0\).  The clipping convention uses \(q(h)=q_0\),
not \(h^0=1\).  The overlap witness has constant weak-arm propensity and
therefore satisfies the overlap-tail condition by the empty-event argument
for \(v\le c_o u^\gamma\).  The converse exponent is
\(r_*(0,\gamma)=1/2\), and the finite-VC feasible upper benchmark is
\(n^{-1/2}(\log n)^{1/2}\).

\paragraph{Diagnostic point \((\alpha,\gamma)=(2,2)\).}
Here
\[
\beta_{2,2}=\frac{2\cdot2}{2+1}=\frac43,\qquad
D_{2,2}=2+2+\frac43=\frac{16}{3},
\]
so
\[
r_*(2,2)=\frac3{16/3}=\frac9{16}.
\]
The lower witness uses \(h_n=n^{-3/16}\), weak-arm propensity
\[
q_n=h_n^{4/3}=n^{-1/4},
\]
one-observation information \(h_n^{16/3}=n^{-1}\), and regret
\[
h_n^3=n^{-9/16}.
\]
The finite-VC feasible upper fixed point with \(q_n=n^{-1/4}\) solves
\[
\rho\asymp\sqrt{\rho^{2/3}\log(e/\rho)/(nq_n)}
=\sqrt{\rho^{2/3}\log(e/\rho)n^{-3/4}},
\]
giving
\[
\rho\asymp n^{-9/16}(\log n)^{3/4}.
\]
Thus a full-class \(n^{-3/4}\) rate is too fast at this diagnostic point.

\paragraph{Large \(\gamma\).}
As \(\gamma\) grows with \(\alpha>0\),
\(\beta_{\alpha,\gamma}=\alpha\gamma/(\alpha+1)\) grows linearly.  The
weak-arm layer can then be made rarer while staying in the overlap-tail
class, and the converse exponent \(r_*(\alpha,\gamma)\) decreases.  This is
the expected behavior for a fixed offline design: the regret cost is
concentrated in a small margin block, but the samples that identify its sign
arrive with probability \(h^{\beta_{\alpha,\gamma}}\).

\paragraph{Known-logging cell means.}
For the lower witnesses with \(h=h_n\), the active weak-arm training count is
of order \(h^{-2}\).  A cell-mean threshold of order \(h\) has only constant
Bernstein exponent and is not enough for a good event whose failure
probability is of order \(\bar\rho_n^*\).  The threshold
\[
h\{\log(e/h^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}
\]
has exponent
\[
\{\log(e/h^{1+\alpha})\}^{2(1+\alpha)/(2+\alpha)},
\]
which is at least linear in \(\log(e/h^{1+\alpha})\).  With a sufficiently
large constant, the failure probability is bounded by
\(C\bar\rho_n^*\), while the local \(L_1(P_X)\) contribution remains
\(h^\alpha\) times the threshold, exactly \(\bar\rho_n^*\).

\paragraph{Common constants in uniform upper bounds.}
Membership in \(\mathcal P_{\alpha,\gamma}\) fixes only the exponents and
allows the margin constants, overlap constants, and policy-complexity
constants to vary with \(P\).  The upper theorem is a uniform statement only
over law collections whose constants are bounded uniformly, together with
common nuisance-rate constants for the fixed learners.  This is exactly the
role of Definition~\ref{def:uniform-feasible-collection} in the feasible
bracket.

\section{Counterexample or minimality check}
\paragraph{Why the faster \(r(\alpha,\gamma)\) claim fails.}
The two-point construction in Theorem~\ref{thm:lower-full-class} is a
counterexample whenever
\[
\frac{1+\alpha}{2+\alpha+\delta_{\alpha,\gamma}}
>
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
At \((\alpha,\gamma)=(2,2)\), \(\delta_{2,2}=0\), so Conjecture 1 predicts
\(3/4\).  But the weak-overlap laws with active mass \(h^2\), contrast
\(h\), and weak-arm propensity \(h^{4/3}\) satisfy the law-side assumptions
and force regret at least \(n^{-9/16}\).  No estimator can have uniformly
smaller expected regret on a class containing these laws.

\paragraph{Minimality of \(\beta_{\alpha,\gamma}\).}
Keep active mass \(h^\alpha\), contrast height \(h\), and weak-arm propensity
\(h^\beta\).  If \(\beta>\alpha\gamma/(\alpha+1)\), then at the tight window
\[
v\asymp h^\beta,\qquad u\asymp h^{\beta/\gamma},
\]
the overlap envelope is
\[
u^\alpha v^{1/\gamma}
\asymp h^{(\alpha+1)\beta/\gamma}
=o(h^\alpha).
\]
Thus the active block violates Assumption~\ref{ass:overlap-decay}.  If
\(\beta\le\alpha\gamma/(\alpha+1)\), Lemma~\ref{lem:witness-membership}
verifies membership for the primitive witnesses.  Hence
\(\beta_{\alpha,\gamma}\) is the least informative admissible weak-arm layer.

\paragraph{Why finite VC dimension gives a logarithmic upper factor.}
At the no-log scale \(\rho_0=(h_n^*)^{1+\alpha}\), the localized finite-VC
maximal inequality gives
\[
E_P\sup_{R_P(\pi)\le\rho_0}
|(\mathbb P_n-P)f_{\pi,n}|
\lesssim
\sqrt{\frac{(q_n^*)^{-1}\rho_0^{\alpha/(1+\alpha)}
\log(e/\rho_0)}{n}}
+
\frac{(q_n^*)^{-1}\log(e/\rho_0)}{n}.
\]
The leading term equals
\[
(h_n^*)^{1+\alpha}\sqrt{\log(e/\rho_0)}
\]
up to constants, not \(O(\rho_0)\).  Therefore finite-VC entropy alone closes
the fixed point at
\[
\rho_0\{\log(e/\rho_0)\}^{(1+\alpha)/(2+\alpha)}.
\]

\paragraph{Why finite VC dimension alone does not make the logarithm unavoidable.}
The preceding display is an achievability-side entropy calculation, not a
matching lower-bound theorem.  Assumption~\ref{ass:policy-class} is an upper
complexity condition and also permits finite or two-policy classes, for which
a logarithmic entropy lower bound is false.  A logarithmic lower bound would
need an additional lower-richness condition, such as \(M_h\) separated active
locations with \(\log M_h\asymp\log(1/h)\) and a policy class able to realize
the relevant labels on those locations, while keeping the same margin and
overlap calibration.  Assumption~\ref{ass:primitive-cube} supplies a single
active block with two labels, so the Le Cam construction proves only the
polynomial lower exponent.

\paragraph{Why the full weak-overlap class is not an achievability class.}
The law class \(\mathcal P_{\alpha,\gamma}\) imposes margin, overlap, bounded
outcomes, positivity, and policy-class conditions.  It does not impose
smoothness, sparsity, finite-dimensional structure, or a known logging
mechanism that would make the nuisance functions \(\mu_0,\mu_1,e_P\)
uniformly learnable at the clipping-localized rates.  A data-only
clipped-AIPW estimator needs exactly those rates to control the first-order
clipping drift and the estimated-score empirical process.  Therefore
Assumption~\ref{ass:nuisance} cannot be replaced by
Assumption~\ref{ass:overlap-decay}: the conditional upper theorem is an
upper bound over collections with common nuisance learnability, while the
full-class theorem supplied by the primitive assumptions is the converse.

\paragraph{Why overlap decay alone is not an upper-bound nuisance condition.}
Assumption~\ref{ass:overlap-decay} controls the joint population mass of
small margins and small weak-arm propensities.  It does not state that a
particular regression or propensity learner estimates \(\mu_a\) and \(e_P\)
at the clipping-localized rates in Assumption~\ref{ass:nuisance}.  The upper
proof consumes the displayed foldwise nuisance rates, margin localization,
finite-VC entropy, and bounded clipped scores.  Thus the upper theorem is a
conditional achievability result over law collections where those rates are
available with common constants, while the overlap assumption supplies the
lower-bound calibration and the natural clipping exponent.

\paragraph{Why product-only nuisance control is insufficient.}
Suppose \(e_P\) is known exactly, so a propensity-estimation product is zero.
Let \(\widehat\mu_1-\mu_1\) be nonzero on the clipped weak-overlap region
\(\{p_P(X)<q_n^*,0<|\tau_P(X)|\le h_n^*\}\).  Even with known propensity, the
clipped treated-arm term has conditional mean contribution
\[
(\widehat\mu_1-\mu_1)(X)
\left\{1-\frac{e_P(X)}{e_{q_n^*}(X;\eta_P)}\right\},
\]
which is first order on the region \(e_P(X)<q_n^*\).  Therefore a
product-only remainder cannot imply the feasible clipped-score drift.  The
local outcome-regression term in Assumption~\ref{ass:nuisance} is needed.

\paragraph{Why empirical off-block propensity witnesses are not asserted.}
For the finite-cell witnesses with \(h=h_n\), an empirical off-block
propensity estimate has \(L_2(P_X)\) error of order
\[
n^{-1/2}=h^{(2+\alpha+\beta)/2}.
\]
The active weak-arm outcome-regression estimate has \(L_2(P_X)\) error of
order \(h^{1+\alpha/2}\), up to the logarithmic threshold used for the
high-probability event.  If the off-block propensity error enters the
weighted product in Assumption~\ref{ass:nuisance}, the polynomial part of
that product is
\[
q_h^{-1}\,h^{(2+\alpha+\beta)/2}\,h^{1+\alpha/2}
=
h^{2+\alpha-\beta/2}.
\]
The target scale is \(h^{1+\alpha}\) up to the finite-VC logarithm, so this
bound is too large when \(\beta>2\).  The empirical off-block sup-norm
propensity error is of order
\[
\sqrt{\log n/n}
=
h^{(2+\alpha+\beta)/2}\sqrt{\log n},
\]
whereas Assumption~\ref{ass:nuisance} requires it to be at most a constant
multiple of \(q_h=h^\beta\).  This fails polynomially when
\(\beta>2+\alpha\), with a logarithmic boundary obstruction.  The
known-logging witness condition therefore uses known propensities on the
finite witness partition, which is primitive for a fixed offline logging
design and leaves the active sign problem intact.

\paragraph{Why bounded residual weighting cannot remove the bias.}
Consider any treated-arm score of the residual-weight form
\[
S_1(X,A,Y)=c_1(X)\widehat\mu_1(X)+w_1(X)A\{Y-\widehat\mu_1(X)\}.
\]
Conditional on \(X=x\),
\[
E_P[S_1\mid X=x]
=e_P(x)w_1(x)\mu_1(x)
+\{c_1(x)-e_P(x)w_1(x)\}\widehat\mu_1(x).
\]
For this conditional mean to equal \(\mu_1(x)\) for every value of
\(\widehat\mu_1(x)\), the coefficient of \(\widehat\mu_1(x)\) must be zero
and the coefficient of \(\mu_1(x)\) must be one.  Thus
\(w_1(x)=1/e_P(x)\).  The untreated arm gives
\(w_0(x)=1/\{1-e_P(x)\}\).  Exact first-order orthogonality for arbitrary
outcome-regression error therefore forces the unclipped inverse-propensity
weights.  A bounded clipped residual score can either control variance by
clipping or be fully orthogonal to arbitrary outcome error, but not both.

\paragraph{Open exact-value qualification.}
Corollary~\ref{cor:feasible-bracket} gives a conditional data-only feasible
upper theorem with the finite-VC logarithmic multiplier and a matching
polynomial lower exponent for \(\kappa\)-uniform feasible law collections
containing the known-logging finite-cell witnesses.  It does not prove a
no-log upper bound under finite VC dimension alone.  It also does not prove
a matching logarithmic lower bound from finite VC dimension alone, and it
does not prove an upper bound over the larger class
\(\mathcal P_{\alpha,\gamma}\) without common nuisance learnability
conditions.  The exact no-log full-class minimax value remains open.

\section{Formalization checklist}
\begin{itemize}[leftmargin=*]
\item \textbf{Causal objects.}  \(\tau_P:\mathcal X\to\mathbb R\),
\(\pi_P^*(x)=\one\{\tau_P(x)\ge0\}\), \(V_P(\pi)=E_P[\pi(X)\tau_P(X)]\),
and \(R_P(\pi)=V_P(\pi_P^*)-V_P(\pi)\).  Role: target estimand and loss.
\item \textbf{Regret identity.}  Lemma~\ref{lem:welfare-identity} rewrites
\(R_P(\pi)\) as
\(E_P[|\tau_P(X)|\one\{\pi(X)\ne\pi_P^*(X)\}]\).  Role: connects causal
welfare regret to sign classification.
\item \textbf{Law classes.}  \(\mathcal P_{\alpha,\gamma}\) is carved by
Assumptions~\ref{ass:causal-sampling}--\ref{ass:policy-class} and fixes
only the exponents \(\alpha,\gamma\); Definition~\ref{def:uniform-feasible-collection}
defines a \(\kappa\)-uniform feasible collection for the upper theorem.
Role: separates law-side lower-bound classes from achievability-side learner
conditions and common constants.
\item \textbf{Delta-witness calibration.}
Assumption~\ref{ass:calibrated-overlap-richness} states
\((\gamma-\alpha)_+\le\alpha\gamma/(\alpha+1)\).  Role: verifies the
overlap admissibility of the \(\delta_{\alpha,\gamma}\)-weak-arm motivating
witness when that witness is considered; the main theorem uses
\(\beta_{\alpha,\gamma}\) instead.
\item \textbf{High-level nuisance rates.}  Assumption~\ref{ass:nuisance}
states a training-fold good event, propensity sup-norm accuracy at the
clipping scale, local outcome \(L_1\) accuracy on \(\{p_P\le2q_n\}\), and a
weighted propensity/outcome \(L_2\) product rate.  Role: conditional inputs
for the feasible upper theorem.
\item \textbf{Overlap layer.}  \(\beta_{\alpha,\gamma}=0\) for \(\gamma=0\)
and \(\beta_{\alpha,\gamma}=\alpha\gamma/(\alpha+1)\) for \(\gamma>0\).
Role: optimized weak-arm exponent allowed by Assumption~\ref{ass:overlap-decay}.
\item \textbf{Clipping convention.}  \(q(h)=q_0\) whenever
\(\beta_{\alpha,\gamma}=0\), and
\(q(h)=h^{\beta_{\alpha,\gamma}}\) otherwise.  Role: keeps the clipping level
inside \((0,1/2]\), including the \(\alpha=0,\gamma>0\) case.
\item \textbf{Rate and logarithmic scale.}
\(D_{\alpha,\gamma}=2+\alpha+\beta_{\alpha,\gamma}\),
\(h_n^*=n^{-1/D_{\alpha,\gamma}}\),
\(q_n^*=q(h_n^*)\),
\(r_*(\alpha,\gamma)=(1+\alpha)/D_{\alpha,\gamma}\),
\(L_n^*=\log\{e/(h_n^*)^{1+\alpha}\), and
\(\bar\rho_n^*=(h_n^*)^{1+\alpha}(L_n^*)^{(1+\alpha)/(2+\alpha)}\).
Role: lower-bound calibration and finite-VC feasible upper-bound calibration.
\item \textbf{Clipped score.}  \(e_q(x;\eta)\), \(\Gamma_q(O;\eta)\), and
\(\widehat\Gamma_{q,k}(O)\).  Role: explicit data-only score used by the
estimator.
\item \textbf{Feasible estimator.}
\(\widehat\pi_n^{\mathsf F}\in\arg\max_{\pi\in\Pi}\sum_k w_k n_k^{-1}
\sum_{i\in I_k}\pi(X_i)\Gamma_{q_n^*}(O_i;\widehat\eta^{(-k)})\).  Role:
sample-to-policy map in Theorem~\ref{thm:feasible-upper-log}.
\item \textbf{Derived drift.}  Lemma~\ref{lem:drift-derived} derives the
policy-uniform clipped-score conditional-bias bound from the foldwise
nuisance-rate condition.  Role: prevents laundering of the first-order
clipped weak-arm bias.
\item \textbf{VC localization.}  Lemma~\ref{lem:feasible-vc-offset} combines
finite VC complexity, estimated-score second-moment control, margin
localization, and the entropy multiplier \(\log(e/\rho)\).  Role: proves the
feasible fixed point \(\bar\rho_n^*\).
\item \textbf{Lower-bound witnesses.}  The witness covariate law \(Q_h\),
active block \(B_h\), \(m_h=Q_h(B_h)\), \(P_{h,+}\), \(P_{h,-}\),
\(q_h=q(h)\), and the fixed off-block contrast \(\tau_0>0\).  Lemma
\ref{lem:witness-membership} verifies bounded outcomes, positivity, margin,
overlap decay, policy membership, divergence, and high-level nuisance-rate
compatibility when Assumption~\ref{ass:learnable-cube} is imposed.
\item \textbf{Known-logging witness learnability.}  In
Assumption~\ref{ass:learnable-cube}, \(\widehat e=e_{h,\beta}\) is known by
design on the finite witness partition, so the lower-witness propensity
sup-norm error and propensity/outcome product are zero.  Outcome regressions
are empirical cell means, and the active weak-arm cell has expected sample
size of order \(h^{-2}\).  Role: verifies the high-level nuisance condition
using the inflated threshold \(h\{\log(e/h^{1+\alpha})\}^{(1+\alpha)/(2+\alpha)}\).
\item \textbf{Divergences.}  \(\chi^2(P\|Q)\) and total variation.  Role:
product-law indistinguishability and Le Cam testing lower bound.
\end{itemize}

\section{Conclusion and references}
The calibrated weak-arm exponent is
\[
\beta_{\alpha,\gamma}=
\begin{cases}
0,&\gamma=0,\\
\alpha\gamma/(\alpha+1),&\gamma>0,
\end{cases}
\]
and the polynomial regret exponent is
\[
r_*(\alpha,\gamma)=
\frac{1+\alpha}{2+\alpha+\beta_{\alpha,\gamma}}.
\]
A primitive two-point construction gives the full weak-overlap lower bound
\[
\mathfrak M_n(\alpha,\gamma)\ge c n^{-r_*(\alpha,\gamma)}.
\]
For any \(\kappa\)-uniform feasible law collection, the cross-fitted
clipped-AIPW empirical welfare maximizer is data-only and satisfies
\[
\sup_{P\in\mathcal Q}
E_P R_P(\widehat\pi_n^{\mathsf F})
\le
C n^{-r_*(\alpha,\gamma)}(\log n)^{(1+\alpha)/(2+\alpha)}.
\]
If the collection contains the known-logging finite-cell witnesses, the same
collection has the matching polynomial lower exponent.  The logarithmic
multiplier comes from finite-VC local entropy; removing it requires stronger
primitive local-complexity structure, while proving it unavoidable requires
a corresponding lower-richness condition.  An upper theorem over the larger
class \(\mathcal P_{\alpha,\gamma}\) without nuisance learnability is not
established here.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem[Athey and Wager(2021)]{AtheyWager2021PolicyLearning}
Athey, S. and Wager, S. (2021).
Policy learning with observational data.
\emph{Econometrica}, 89(1), 133--161.

\bibitem[Audibert and Tsybakov(2007)]{AudibertTsybakov2007PluginClassifiers}
Audibert, J.-Y. and Tsybakov, A. B. (2007).
Fast learning rates for plug-in classifiers.
\emph{Annals of Statistics}, 35(2), 608--633.

\bibitem[Chernozhukov et al.(2018)]{ChernozhukovEtAl2018DML}
Chernozhukov, V., Chetverikov, D., Demirer, M., Duflo, E., Hansen, C.,
Newey, W., and Robins, J. (2018).
Double/debiased machine learning for treatment and structural parameters.
\emph{The Econometrics Journal}, 21(1), C1--C68.

\bibitem[D'Amour et al.(2021)]{DAmourDingFellerLeiSekhon2017Overlap}
D'Amour, A., Ding, P., Feller, A., Lei, L., and Sekhon, J. (2021).
Overlap in observational studies with high-dimensional covariates.
\emph{Journal of Econometrics}, 221(2), 644--654.

\bibitem[Jin et al.(2022)]{JinRenYangWang2022PessimisticPolicy}
Jin, Y., Ren, Z., Yang, Z., and Wang, Z. (2022).
Policy learning ``without'' overlap: Pessimism and generalized empirical
Bernstein's inequality.
arXiv:2212.09900.

\bibitem[Kallus(2017)]{Kallus2017BalancedPolicy}
Kallus, N. (2017).
Balanced policy evaluation and learning.
arXiv:1705.07384.

\bibitem[Kitagawa and Tetenov(2018)]{KitagawaTetenov2018WhoShouldBeTreated}
Kitagawa, T. and Tetenov, A. (2018).
Who should be treated? Empirical welfare maximization methods for treatment
choice.
\emph{Econometrica}, 86(2), 591--616.

\bibitem[Luedtke and Chambaz(2017)]{LuedtkeChambaz2017FasterRates}
Luedtke, A. and Chambaz, A. (2017).
Faster rates for policy learning.
arXiv:1704.06431.

\bibitem[Ma et al.(2023)]{MaSantAnnaSasakiUra2023DRWeakOverlap}
Ma, Y., Sant'Anna, P. H. C., Sasaki, Y., and Ura, T. (2023).
Doubly robust estimators with weak overlap.
arXiv:2304.08974.

\bibitem[Vapnik and Chervonenkis(1971)]{VapnikChervonenkis1971}
Vapnik, V. N. and Chervonenkis, A. Y. (1971).
On the uniform convergence of relative frequencies of events to their
probabilities.
\emph{Theory of Probability and its Applications}, 16(2), 264--280.

\bibitem[van der Vaart and Wellner(1996)]{VanderVaartWellner1996}
van der Vaart, A. W. and Wellner, A. W. (1996).
\emph{Weak Convergence and Empirical Processes}.
Springer.

\bibitem[Zhan et al.(2021)]{ZhanRenAtheyZhou2021AdaptivePolicy}
Zhan, R., Ren, Z., Athey, S., and Zhou, Z. (2021).
Policy learning with adaptively collected data.
arXiv:2105.02344.
\end{thebibliography}

\end{document}
