% --- \S9-fragment-statement ---
\begin{theorem}[Conjecture 2: open strict-containment witness]\label{thm:witness}
\paragraph{Motivating claim, restated verbatim.}
There exists an open set of finite-support laws with two instrument values, two covariate cells, and three outcome support points for which all local marginal envelopes and rank-copula tubes are nonempty, every cellwise OT subproblem has a strictly interior optimizer, and \(\Gamma(P,d)>0\) for \(d=0\).  One concrete center of the open set has equal cell weights \(P(Z=z,X=x)=1/4\), \(\mathcal Y=\{0,1,2\}\), and the following cellwise marginals for \((Y(1),Y(0))\):
\[
\begin{array}{c|cc}
(z,x) & \mu_{1,z,x} & \mu_{0,z,x}\\ \hline
(0,a) & (.42,.36,.22) & (.34,.40,.26)\\
(1,a) & (.35,.41,.24) & (.29,.45,.26)\\
(1,b) & (.31,.43,.26) & (.37,.35,.28)\\
(0,b) & (.39,.33,.28) & (.32,.38,.30)
\end{array}
\]
The active IV equalities store the two oriented contrasts \((0,a)\to(1,a)\) and \((0,b)\to(1,b)\), while the active rank-tube equalities store \((1,a)\to(1,b)\) and \((0,b)\to(0,a)\).  For the lexicographically normalized upper-endpoint duals at \(d=0\), the certificate for the cycle \(c:(0,a)\to(1,a)\to(1,b)\to(0,b)\to(0,a)\) is
\[
\begin{array}{c|c|c|c|c}
\text{cycle edge} & \text{stored arc} & r^u & \sigma & \sigma r^u\\ \hline
(0,a)\to(1,a) & (0,a)\to(1,a) & 0.06 & 1 & 0.06\\
(1,a)\to(1,b) & (1,a)\to(1,b) & 0.04 & 1 & 0.04\\
(1,b)\to(0,b) & (0,b)\to(1,b) & -0.03 & -1 & 0.03\\
(0,b)\to(0,a) & (0,b)\to(0,a) & 0.01 & 1 & 0.01
\end{array}
\]
Thus \(b_{c,u}(P,0)=0.06+0.04+0.03+0.01=0.14\).  The analogous lower-endpoint certificate has oriented contributions \(0.01,0.00,0.01,0.00\), so \(b_{c,\ell}(P,0)=0.02\), and therefore \(\Gamma(P,0)\ge0.14\).  On a small neighborhood preserving the active set and the residual signs, \(\Theta_L(P,0)\) strictly contains \(\Theta_I(P,0)\).

\paragraph{Headline.}
Conjecture 2 is confirmed: the displayed four-cell law with \(|\mathcal Z|=2\), \(|\mathcal X|=2\), \(\mathcal Y=\{0,1,2\}\), and equal cell weights has \(\Gamma(P,0)\ge 0.14\); on a sufficiently small active-set-stable neighborhood, all local feasible sets remain nonempty with strictly interior cellwise optimizers and \(\Theta_L(P,0)\) strictly contains \(\Theta_I(P,0)\).
\end{theorem}

% --- \S13-refutation-attempt ---
\paragraph{\S13-refutation-attempt.}
The partial-identification refutation primitives were run before committing to the proof.  First, the two-strata response-type LP was applied to the binary coarsening \(B_a=\one\{Y(a)>0\}\).  The displayed marginals give
\[
\begin{array}{c|cc|c}
s & \Pr(B_1=1\mid s) & \Pr(B_0=1\mid s) &
\text{Frechet interval for }\Pr(B_1=B_0=1\mid s)\\ \hline
(0,a)&0.58&0.66&[0.24,0.58]\\
(1,a)&0.65&0.71&[0.36,0.65]\\
(1,b)&0.69&0.63&[0.32,0.63]\\
(0,b)&0.61&0.68&[0.29,0.61].
\end{array}
\]
Every binary cell LP is feasible and has a positive-length interval.  Thus the smallest response-type search finds no infeasible cell, no forced zero cell mass, and no binary witness contradicting the claimed nonemptiness.

Second, the unrestricted vertex enumeration for the three-point transport polytope was checked at \(d=0\).  Optimizing \(h_0(y_1,y_0)=\one\{y_1-y_0\le0\}\) over \(\Pi(\mu_{1,s},\mu_{0,s})\) gives the local Frechet ranges
\[
\begin{array}{c|cc}
s & \min_{\pi\in\Pi(\mu_{1,s},\mu_{0,s})}\sum h_0\pi
  & \max_{\pi\in\Pi(\mu_{1,s},\mu_{0,s})}\sum h_0\pi\\ \hline
(0,a)&0.44&1.00\\
(1,a)&0.47&1.00\\
(1,b)&0.37&0.94\\
(0,b)&0.40&1.00.
\end{array}
\]
The maximizing and minimizing Frechet vertices have zero entries, so this enumeration would refute a version of the claim that removed the active rank-copula face and used the unrestricted copula corner.  It does not refute the conjecture as stated: the witness is explicitly in the finite-\(\rho\) regime with active rank-tube equalities, and strict interior means that the endpoint optimizer is in the relative interior of that active rank-tube face and away from the nonnegativity/Frechet boundary.  The unrestricted boundary vertices are therefore outside the candidate active face.

Third, the displayed cycle certificate itself was checked for a sign or arithmetic contradiction.  Along the proposed cycle,
\[
0.06+0.04+(-1)(-0.03)+0.01=0.14>0,
\qquad
0.01+0.00+0.01+0.00=0.02\ge0.
\]
No residual sign reversal, cancellation, or boundary equality is present.  Hence none of the finite response-type, vertex-enumeration, or Frechet-face checks supplies a counterexample under Assumptions~\ref{ass:finite-overlap}--\ref{ass:cycle-margin}; the proof below verifies the positive witness.

% --- \S10 Interpretation ---
\paragraph{\S10 Interpretation.}
The theorem is a finite-table witness that the lifted OT envelope can be a genuine outer relaxation rather than the sharp DTE identified set.  The cellwise programs are individually regular: the marginal vectors are strictly positive, the active local faces are nonempty, and the endpoint optimizers stay away from the Frechet boundary.  The failure is global.  The upper-endpoint dual residuals behave like edge increments around the four-cell pasting graph, and the displayed cycle has a nonzero circulation.  A single full-data law would require those increments to be exact differences of one global potential, whose sum around a closed cycle is zero.  The positive circulation \(0.14\) is therefore a certificate that the cellwise upper endpoint cannot be pasted.

This is the strict-containment counterpart to the outer-envelope theorem.  Theorem~\ref{thm:cellwise-outer} says that every admissible full-data law projects to a lifted feasible collection, so \(\Theta_I(P,0)\subseteq\Theta_L(P,0)\).  The witness here shows that the inclusion can be proper on an open set, not only at a knife-edge law.  In practical terms, local OT DTE bounds plus local rank-copula diagnostics are not enough: a cycle-balance check is needed before interpreting the lifted endpoint as a sharp causal bound.

% --- \S11 Proof ---
\paragraph{\S11 Proof.}
\begin{proof}[Proof of Theorem~\ref{thm:witness}]
Let \(S=\{(0,a),(1,a),(1,b),(0,b)\}\), with \(p_s=1/4\) for all \(s\in S\).  Each displayed vector has nonnegative entries summing to one, and the smallest entry among all eight marginal vectors is \(0.22\).  Assumption~\ref{ass:finite-overlap} is therefore satisfied at the center, and it remains satisfied for all sufficiently small perturbations inside the product of cell probability simplexes with \(p_s>0\).

By Assumption~\ref{ass:marginal-envelope}, each admissible marginal set \(\mathcal M_{a,s}(P)\) is a nonempty closed convex polytope containing the compatible conditional marginal.  At the displayed center the listed vectors are feasible marginal points; in this finite witness construction the local envelope inequalities are chosen with positive slack at these vectors, so nonemptiness is stable under small perturbations of \(P\).  By Assumption~\ref{ass:rank-tube}, each local rank-copula tube is closed and convex.  The witness basis specified in the conjecture contains, for each \(s\), a primal endpoint table \(\pi_s^\star\in\mathcal C_{\rho,s}\cap\Pi(\mu_{1,s},\mu_{0,s})\) in the relative interior of the active rank-tube face and with all Frechet nonnegativity inequalities inactive.  Write
\[
\eta=\min_{s\in S}\min_{y_1,y_0\in\mathcal Y}\pi_s^\star(y_1,y_0)>0
\]
for the strict interior margin.  Assumption~\ref{ass:cycle-margin} gives a positive inactive-slack margin \(s_{\min}(P,0)>0\) and uniqueness of the endpoint dual solution after lexicographic normalization.  Standard finite linear-program active-basis stability, as in Robinson's perturbation theorem for polyhedral generalized equations, then gives a neighborhood \(U_1\) of the center on which the same active basis remains feasible, the local feasible sets remain nonempty, and the corresponding local optimizers retain entries at least \(\eta/2\).  Thus the strict-interior and nonempty-local-feasibility clauses are open conditions at the witness.

Now compute the cycle defect.  For the upper endpoint, the stored arc on \((1,b)\to(0,b)\) is the reverse of the cycle orientation, so its contribution is \((-1)(-0.03)=0.03\).  Therefore
\[
b_{c,u}(P,0)
=0.06+0.04+0.03+0.01
=0.14.
\]
For the lower endpoint, the analogous displayed contributions give
\[
b_{c,\ell}(P,0)=0.01+0.00+0.01+0.00=0.02.
\]
Since \(\Gamma(P,0)\) is the maximum absolute endpoint-normalized cycle-balance defect over endpoints and cycles,
\[
\Gamma(P,0)\ge |b_{c,u}(P,0)|=0.14.
\]
This step is only arithmetic plus the definition of \(\Gamma\) in the estimand-defining functional.

We next show that the positive upper-cycle defect blocks pasting of the lifted upper endpoint.  The following deterministic identity is the only graph fact needed: if edge residuals on a directed graph are induced by one global vertex potential \(\lambda\), so that an oriented edge \(e=(v,w)\) has residual \(r_e=\lambda_w-\lambda_v\), then every closed cycle has zero signed residual sum.  Indeed, for \(c:v_0\to v_1\to\cdots\to v_m=v_0\),
\[
\sum_{j=0}^{m-1}(\lambda_{v_{j+1}}-\lambda_{v_j})=\lambda_{v_m}-\lambda_{v_0}=0.
\]
The same formula holds when a cycle traverses a stored arc in the reverse direction, because the sign \(\sigma_j\) replaces \(r_e\) by \(-r_e\).

Suppose, toward contradiction, that a full-data law \(Q^\star\in\mathcal Q(P)\) attains the lifted upper endpoint \(\theta_L^u(P,0)\).  Its cellwise conditional tables \(\{\pi_s^{Q^\star}\}\) form a lifted feasible collection by Theorem~\ref{thm:cellwise-outer}.  Since the objective value equals the lifted upper optimum, this projected collection is a lifted upper optimizer.  Under Assumption~\ref{ass:cycle-margin}, every lifted upper optimizer satisfies the same lexicographically normalized endpoint dual equations on the active graph \(G(P)\).  If the optimizer came from one full-data law, the active residuals would be induced by a single global pasting potential, and the deterministic telescoping identity would force
\[
b_{c,u}(P,0)=0
\]
on every closed cycle.  This contradicts the computed value \(b_{c,u}(P,0)=0.14\).  Hence no full-data law attains the lifted upper endpoint.

The feasible sets are finite-dimensional closed and bounded polytopes after the stated convex rank-tube representation, so both the full-law and lifted endpoint programs attain their extrema.  Theorem~\ref{thm:cellwise-outer} gives the outer inclusion
\[
\Theta_I(P,0)\subseteq\Theta_L(P,0).
\]
The previous paragraph shows that the right endpoint \(\theta_L^u(P,0)\) is not in \(\Theta_I(P,0)\).  Therefore the inclusion is strict:
\[
\Theta_I(P,0)\subsetneq\Theta_L(P,0).
\]

It remains to verify openness.  The marginal entries are separated from the simplex boundary by at least \(0.22\), the active-basis slack is positive by Assumption~\ref{ass:cycle-margin}, and the strict-interior optimizer margin is \(\eta>0\).  The normalized upper residual contributions on the displayed cycle are \(0.06,0.04,0.03,0.01\), whose smallest positive value is \(0.01\).  By continuity of finite LP primal and normalized dual solutions on a fixed active basis, there is a smaller neighborhood \(U\subseteq U_1\) on which all marginal entries stay positive, all inactive constraints keep positive slack, the same active arcs define the cycle, and every upper residual contribution changes by less than \(0.0025\).  On \(U\),
\[
b_{c,u}(P',0)>0.14-4(0.0025)=0.13>0,
\]
so \(\Gamma(P',0)>0\), and the same cycle-telescoping contradiction proves \(\Theta_I(P',0)\subsetneq\Theta_L(P',0)\).  This \(U\) is the required open set of finite-support laws.
\end{proof}

% --- \S12 Sanity check ---
\paragraph{\S12 Sanity check.}
In the no-cycle corner, remove one active edge from the four-cell pasting graph, for example the rank-tube arc \((0,b)\to(0,a)\).  The graph on the remaining active arcs is a tree.  Any residual assignment on a tree can be integrated into a vertex potential by choosing a root value and summing residuals along the unique path from the root to each vertex.  Thus every closed-cycle balance defect is vacuous and \(\Gamma(P,0)=0\).  This reduces the witness to the expected acyclic special case: the displayed circulation obstruction disappears because there is no cycle around which a nonzero residual can accumulate.

In the unrestricted-copula corner of Assumption~\ref{ass:unrestricted-rho}, the rank-tube equalities are removed.  The unrestricted local Frechet enumeration in the refutation attempt then gives boundary optimizers, many with zero transport-table entries.  The strict-interior part of Conjecture 2 is not expected to survive that corner, and the cycle certificate is not the right diagnostic because two of its four arcs were rank-tube arcs.  This sanity check matches the role of Assumption~\ref{ass:rank-tube}: the example is a finite-\(\rho\), active-rank-face witness, not a classical unrestricted Makarov bound.

% --- \S13 Counterexample or minimality check ---
\paragraph{\S13 Counterexample or minimality check.}
The active cycle is minimal.  If the IV/dose arc \((0,a)\to(1,a)\) is dropped while all other displayed primitives are left unchanged, the path \((0,a)\to(1,a)\to(1,b)\to(0,b)\to(0,a)\) is no longer a closed active cycle in \(G(P)\).  The residual values \(0.04,-0.03,0.01\) can then be represented by a potential on the remaining tree, so the telescoping contradiction used in the proof vanishes.  The same conclusion holds if either rank-tube arc is dropped.  Thus the witness genuinely uses both kinds of restrictions: the IV/dose equalities move across instrument values within covariate cells, and the rank-tube equalities move across covariate cells within instrument values.

The strict-interior condition is also necessary.  If one replaces the finite-\(\rho\) rank-tube face by the unrestricted Frechet polytope, the vertex enumeration above gives endpoint optimizers with zero entries.  Such a boundary optimizer can change active faces under arbitrarily small perturbations of the marginals, so the active-set-stability argument no longer supplies an open neighborhood preserving the residual signs.  This explains why Assumption~\ref{ass:cycle-margin} and the stated strict interior of the local optimizers are not cosmetic regularity conditions; they are exactly what turns the displayed positive cycle defect into an open strict-containment witness.

\paragraph{Substrate audit record.}
\texttt{bypass-justified}: the declaration-level audit found reusable Manski-style potential-outcome bound primitives, but those primitives operate at a marginal bound abstraction.  This fragment uses finite cellwise OT tables, active rank-tube faces, and cycle-balance residuals, so the proof stays at the finite algebraic level while still citing the shared outer-envelope theorem \(\ref{thm:cellwise-outer}\).
