% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_ot\_dte\_marginal, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_ot\_dte\_marginal} / \texttt{v1}%
  \\ \large\textit{A finite LP/OT incompatibility diagnostic for overlap-constrained DTE reporting}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal, not a Q1 panel pool-mode instance.
The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\Pi^\eta,\mathcal B^\eta)
=
(\texttt{pid\_ot\_dte\_marginal},\texttt{v1},P,\theta_D,
\text{finite marginal-overlap restrictions},\text{LP/OT path diagnostic}).
\]
The observable distribution \(P\) consists of a finite covariate law
\(\Pr\{X=x_j\}=w_j>0\), \(j=1,\ldots,J\), and finite outcome grids
\(\mathcal Y_1=\{a_1,\ldots,a_M\}\), \(\mathcal Y_0=\{b_1,\ldots,b_N\}\).  For
each arm \(t\in\{0,1\}\), cell \(j\), and support point, \(P\) supplies lower and
upper marginal-overlap envelopes
\(\ell_{tjm}\le \mu_{tjm}\le u_{tjm}\) (using \(m=1,\ldots,M\) for \(t=1\) and
\(m=1,\ldots,N\) for \(t=0\)), with each admissible marginal vector summing to
one.  The target parameter is the finite-grid DTE path
\[
\theta_D=(F_\Delta(d_1),\ldots,F_\Delta(d_K)),\qquad
\Delta=Y(1)-Y(0),\quad D=\{d_1<\cdots<d_K\}.
\]
The restriction class \(\Pi^\eta(P)\) is the set of nonnegative
cell-specific coupling tables \(\pi_{jmn}\) whose row and column sums lie inside
the stated overlap envelopes.  The bounding functional \(\mathcal B^\eta(P;D)\)
is the sharp feasible set for \(\theta_D\) generated by these tables, and the
proposal's named object is the canonical finite LP/OT incompatibility scalar
\(G^\eta_P(D)\) defined in Section~\ref{sec:setup}.

\begin{abstract}
Pointwise Makarov bounds for the distribution of treatment effects can be sharp at
each threshold while still failing to describe any single feasible distribution of
\(Y(1)-Y(0)\) on a finite grid.  This proposal asks for an operational finite
LP/OT diagnostic, \(G^\eta_P(D)\), that tells a practitioner when a stacked
pointwise DTE band under marginal-overlap restrictions is incompatible with one
joint coupling of potential outcomes.  The routine finite-support endpoint LP is
treated as setup, because Russell--Ober-Reynolds style machinery already covers
that layer.  The flagship conjecture is instead an endpoint-face certificate
algorithm, \(\mathfrak F^\eta_P(D)\), that decides when the stacked endpoint
workflow is exactly pathwise sharp without defining the answer through
\(G^\eta_P(D)\).  If resolved, the result would turn the prior reviewer request
for an ``LP/Frechet--Makarov diagnostic'' into a computable overlap-envelope
frontier that is not just another endpoint LP.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Distributional treatment-effect reporting is attractive because it addresses harm,
benefit, and heterogeneity questions that are invisible in the ATE.  The hard
identification issue is that observed data usually identify, or partially identify,
the marginal laws of \(Y(1)\) and \(Y(0)\), but not their joint law.  In empirical
work, this often leads to a graph of pointwise lower and upper DTE bounds.  Such a
graph can be misleading: the lower endpoint at \(d_1\), the upper endpoint at
\(d_2\), and the visually interpolated band may be supported by mutually
incompatible latent couplings.

\paragraph{The main finding (proposed).}
The proposed flagship object is the \emph{endpoint-face certificate complex}
\(\mathfrak F^\eta_P(D)\).  For each canonical vertex of the stacked pointwise
DTE report, it records the finite system of active endpoint faces that one
coupling would have to satisfy simultaneously.  Conjecture~\ref{conj:diagnostic}
states that this certificate complex gives an independent zero-gap
characterization: the stacked endpoint report is pathwise sharp exactly when
every canonical endpoint-face system is feasible.  Conjectures~\ref{conj:open}
and \ref{conj:witness} then ask for a strict overlap-envelope extension beyond
Firpo--Ridder's fixed-marginal finite-vector phenomenon.

\paragraph{What is new.}
The closest published results give either DTE bounds or general computational
machinery, but not an endpoint-face compatibility frontier for marginal-overlap
envelopes.  \citet[Section 2 and Lemma 2.3]{FanPark2010} derive sharp pointwise
DTE bounds from identified marginals.  \citet[Section 2]{FirpoRidder2019} show
that pointwise Makarov bounds are not uniformly sharp for finite CDF vectors and
functionals.  \citet[Supplementary Appendix 3, especially the
finite-dimensional implementation discussion]{Russell2021} shows how sharp
bounds for continuous functionals of the joint potential-outcome distribution can
be implemented as linear programs, while \citet[Sections 2--3, where endpoint
bounds are OT values]{OberReynolds2023} gives OT endpoint values for moment-type
functionals.  The epsilon-gap is the explicit overlap-envelope layer:
\(\mathfrak F^\eta_P(D)\) works with nonsingleton marginal envelopes and asks
whether the endpoint faces selected across thresholds can be pasted into one
coupling, a question not answered by fixed-marginal finite-vector Makarov
nonuniformity or by generic single-functional endpoint LPs.

\paragraph{How it positions in the literature.}
This is a PartialID proposal in the DTE, Frechet--Makarov, and optimal-transport
coupling cluster.  It uses finite-dimensional LP geometry as the mathematical
language, but the estimand remains the distribution of \(Y(1)-Y(0)\).  It is not
a panel theorem and not an ExactID result.  The proposal is closest to the
computational partial-identification work of \citet{Russell2021} and
\citet{OberReynolds2023}, with the DTE-specific nonuniform-sharpness issue of
\citet{FirpoRidder2019} as the econometric comparator.  Its claim against those
papers is deliberately phrased as non-representability of stacked endpoint
reports under nonsingleton marginal envelopes, not as a strict tightening of
their endpoint theorems.

\paragraph{Implications for the community.}
The direct downstream consumer is the DTE reporting workflow in
\citet{FanPark2010} and the prior CausalSmith
\texttt{eid\_dist\_synth\_control}/\texttt{v1} reviewer request for a finite
LP/OT diagnostic: the diagnostic would tell analysts when a displayed DTE band is
a valid one-coupling partial-identification statement and when it is only a stack
of incompatible pointwise extrema.

\paragraph{How research benefits from the conclusion.}
Researchers should report \(G^\eta_P(D)\) next to finite-grid DTE bands whenever
counterfactual marginals are overlap-restricted, and should avoid interpreting
bands with \(G^\eta_P(D)>0\) as feasible treatment-effect distributions.

\section{Related work}
\citet{Makarov1981} and \citet{Rueschendorf1982} are the probability anchors for
extremal couplings with fixed marginals; the proposed LP is the finite
transport-table analogue with marginal envelopes.  \citet{HeckmanSmithClements1997}
motivate DTEs in program evaluation by showing why mean impacts do not settle
questions about individual gains and losses.  \citet[Section 2 and Lemma
2.3]{FanPark2010} give sharp pointwise DTE bounds and inference when the
potential-outcome marginals are identified; this proposal keeps their target but
asks whether stacked pointwise reports are jointly feasible.  \citet[Section
2]{FirpoRidder2019} prove that Makarov bounds at finitely many DTE CDF points can
be improved because pointwise sharpness is not uniform sharpness; this is the
closest published DTE comparator for Conjecture~\ref{conj:diagnostic}.
\citet[Sections 2--3]{FanWu2010} derive DTE partial-identification bounds in
switching-regime models; this proposal instead uses finite overlap envelopes and
one-coupling LP geometry.  \citet[Sections 2--3]{FanGuerreZhu2017} bound general
functionals of the joint potential-outcome distribution and study when covariates
shrink identified sets; the present proposal isolates a DTE CDF path and the
diagnostic gap between pointwise and pathwise reports.  \citet{FrandsenLefgren2021}
use mutually stochastic increasing potential outcomes to tighten DTE bounds and
obtain testable implications; their DTE applications are natural consumers of a
pathwise feasibility diagnostic.  \citet[Supplementary Appendix 3]{Russell2021}
develops computational sharp bounds for continuous functionals of the joint
potential-outcome distribution and explicitly discusses LP implementation; the
current proposal differs by making the finite DTE path overstatement itself the
estimand, a diagnostic object not reported by the single-functional endpoint
programs.  \citet[Sections 2--3]{OberReynolds2023} characterizes endpoint bounds
for moment-type functionals by OT values and studies estimation; here the object
is a vector CDF path and a diagnostic scalar for simultaneous representability.
\citet[Sections 2--3]{Lee2024}
studies conditional DTE distributions using Makarov bounds and uniformly valid
inference; the proposed diagnostic targets the finite-grid coupling compatibility
problem that remains after conditional bounds are stacked.

The Stage -1.1 in-repository scan reports that \texttt{doc/API.md} has no
accepted CausalSmith DTE coupling or OT diagnostic theorem; the closest PartialID
catalogue entry is only a Manski selected-cell mean-bound wrapper.  The closest
banked prior proposal is
\texttt{eid\_dist\_synth\_control}/\texttt{v1}, whose reviewer specifically asked
for a computable finite-support LP/OT diagnostic with explicit variables,
constraints, dimension, and width for \(\Pr\{\Delta\le d\}\).  This draft answers
that reviewer signal as a PartialID DTE proposal, not as an ExactID synthetic
control proposal.  The archived angle-0 draft for this qid pursued a broad
Choquet--OT path envelope; the present pivot narrows to the operational scalar
\(G^\eta_P(D)\) and its finite certificate.

\section{Formal setup}
\label{sec:setup}
There are \(J\) covariate cells with probabilities \(w_j>0\), \(\sum_j w_j=1\).
Treatment potential outcomes satisfy \(Y(1)\in\mathcal Y_1=\{a_1,\ldots,a_M\}\)
and \(Y(0)\in\mathcal Y_0=\{b_1,\ldots,b_N\}\).  For each cell \(j\), a feasible
full-data law is represented by a nonnegative table
\(\pi_j=(\pi_{jmn})_{m\le M,n\le N}\), where
\(\pi_{jmn}=\Pr\{Y(1)=a_m,Y(0)=b_n\mid X=x_j\}\).  Its implied DTE path is
\[
z_k(\pi)=\sum_{j=1}^J w_j\sum_{m=1}^M\sum_{n=1}^N
\pi_{jmn}\one\{a_m-b_n\le d_k\},\qquad k=1,\ldots,K.
\]
The one-coupling path polytope is
\[
\mathcal C^\eta(P;D)=\{z(\pi)\in\mathbb R^K:\pi\in\Pi^\eta(P)\},
\]
where \(\Pi^\eta(P)\) is the set of tables obeying the marginal-overlap
constraints in Assumption~\ref{ass:overlap-envelope}.  For direction
\(v\in\mathbb R^K\), define the LP/OT support value
\[
h^\eta_P(v;D)=
\max_{\pi\in\Pi^\eta(P)}
\sum_{k=1}^K v_k z_k(\pi).
\]
Here \(e_k\) denotes the \(k\)th standard basis vector in \(\mathbb R^K\).
For each threshold \(d_k\), let \(L^\eta_k=h^\eta_P(-e_k;D)(-1)\) and
\(U^\eta_k=h^\eta_P(e_k;D)\), and define the stacked pointwise report
\[
\mathcal S^\eta(P;D)=
\{r\in\mathbb R^K:L^\eta_k\le r_k\le U^\eta_k,\ r_1\le\cdots\le r_K\}.
\]
The proposed diagnostic is the canonical directed support gap
\[
G^\eta_P(D)=
\sup_{\|v\|_1\le 1}
\{h_{\mathcal S^\eta(P;D)}(v)-h^\eta_P(v;D)\}_+,
\]
where \(h_{\mathcal S}(v)=\max_{s\in\mathcal S}v^\transpose s\).  This equals
the \(\ell_\infty\)-directed Hausdorff distance from the stacked pointwise report
\(\mathcal S^\eta(P;D)\) to the one-coupling path set
\(\mathcal C^\eta(P;D)\) whenever both sets are nonempty compact convex
polytopes.  Thus \(G^\eta_P(D)\) is measured in DTE-CDF units and is independent
of any arbitrary exposing-direction choice.

The finite-support endpoint LP itself is not claimed as novel.  It has \(JMN\)
nonnegative coupling variables, at most \(2J(M+N)\) lower/upper marginal-envelope
inequalities, \(2J\) marginal-total equalities, and \(J\) redundant
coupling-total checks.  The lower and upper pointwise DTE bounds are the values
of this LP at directions \(-e_k\) and \(e_k\).

Let \(V(\mathcal S^\eta)\) be the set of vertices of the monotone box
\(\mathcal S^\eta(P;D)\).  For \(r\in V(\mathcal S^\eta)\), define the
endpoint-face system \(A^\eta(r)\) as the linear feasibility problem over
\(\Pi^\eta(P)\) obtained by adding the equalities \(z_k(\pi)=r_k\) for every
coordinate \(k\) at which \(r_k\) is one of its pointwise endpoints
\(L^\eta_k\) or \(U^\eta_k\), plus the monotone-block equalities implied when a
vertex uses \(r_k=r_{k+1}\).  The endpoint-face certificate complex is
\[
\mathfrak F^\eta_P(D)=\{A^\eta(r):r\in V(\mathcal S^\eta)\}.
\]
It is computable from endpoint LP optima and vertex enumeration of a monotone box,
without first computing the support-function gap \(G^\eta_P(D)\).

\begin{verbatim}
Locked parameters.
(qid, specialization, observable distribution P, parameter theta,
 identifying restrictions, bounding functional)
= (pid_ot_dte_marginal, v1, finite covariate/outcome law with
   marginal-overlap envelopes, theta_D=(F_Delta(d_k))_{k=1}^K,
   finite overlap-constrained coupling tables Pi^eta(P),
   LP/OT path diagnostic G^eta_P(D)).
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite support and positive cell mass]\label{ass:finite}
The covariate support has \(J<\infty\) cells with \(w_j>0\), and the potential
outcome supports \(\mathcal Y_1,\mathcal Y_0\) are finite and known.
\end{assumption}

\begin{assumption}[Marginal-overlap envelopes]\label{ass:overlap-envelope}
For every \(j\), the admissible conditional marginals satisfy
\[
\ell_{1jm}\le \sum_{n=1}^N\pi_{jmn}\le u_{1jm},\qquad
\ell_{0jn}\le \sum_{m=1}^M\pi_{jmn}\le u_{0jn},
\]
with nonnegative lower and upper bounds, and the row and column sums each total
one.  The envelope is feasible with nonempty relative interior.
\end{assumption}

\begin{assumption}[Fixed DTE grid]\label{ass:grid}
The reporting grid \(D=\{d_1<\cdots<d_K\}\) is finite, \(K\ge 2\), and all DTE
paths are evaluated only on this grid.
\end{assumption}

\begin{assumption}[Canonical dual diagnostic]\label{ass:dual-diagnostic}
The diagnostic \(G^\eta_P(D)\) is evaluated over the full compact dual unit ball
\(\{v\in\mathbb R^K:\|v\|_1\le 1\}\), not over an analyst-selected subset of
directions.
\end{assumption}

\begin{assumption}[Endpoint-face conflict margin]\label{ass:face-conflict}
There is a structural constant \(c_{\mathrm{fc}}(P,D,\eta)>0\), defined as the
minimum Hoffman distance from an infeasible endpoint-face system in
\(\mathfrak F^\eta_P(D)\) to feasibility after normalizing all row and column
constraints to unit \(\ell_\infty\) coefficient norm.  At least one system
\(A^\eta(r)\in\mathfrak F^\eta_P(D)\) is infeasible and has certificate distance
at least \(c_{\mathrm{fc}}(P,D,\eta)\).  Any claimed strict gap \(\varepsilon\) is
restricted to \(0<\varepsilon\le c_{\mathrm{fc}}(P,D,\eta)\).
\end{assumption}

\begin{assumption}[Open envelope cell]\label{ass:open-envelope}
For the finite witness class, each marginal-overlap bound may be perturbed by a
vector \(\rho\) with \(\|\rho\|_\infty\le
c_{\mathrm{fc}}(P,D,\eta)/16\), after renormalizing each cell's lower and upper
marginal bounds so the row and column totals remain feasible.  The perturbed
envelope keeps nonempty relative interior and the same finite supports.
\end{assumption}

\section{Main results}
\begin{conjecture}[Endpoint-face certificate algorithm (NOT YET PROVED)]\label{conj:diagnostic}
Under Assumptions~\ref{ass:finite}--\ref{ass:dual-diagnostic}, the following
finite algorithm is sound and complete for zero support gap.  Enumerate the
vertices \(r\in V(\mathcal S^\eta)\), build each endpoint-face system
\(A^\eta(r)\), and solve those linear feasibility problems over
\(\Pi^\eta(P)\).  Then
\[
G^\eta_P(D)=0
\quad\Longleftrightarrow\quad
A^\eta(r)\text{ is feasible for every }r\in V(\mathcal S^\eta).
\]
The algorithm uses at most \(2^K\) endpoint-face feasibility checks, each with
\(JMN\) coupling variables and the marginal-envelope constraints stated in
Section~\ref{sec:setup}.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Section 2 and Lemma 2.3]{FanPark2010} certify pointwise sharpness,
while \citet[Section 2]{FirpoRidder2019} shows finite-vector Makarov regions can
be improved; neither paper gives a vertex-level endpoint-face test for when a
stacked DTE endpoint report is exactly one-coupling sharp under nonsingleton
marginal-overlap envelopes.  \citet[Supplementary Appendix 3]{Russell2021} and
\citet[Sections 2--3]{OberReynolds2023} compute endpoint values for functionals,
but do not ask whether the endpoint-optimal faces across a CDF grid are jointly
pasteable.  The epsilon-gap is that the conjecture replaces the tautological
support-function equality \(G=0\) with the independently computable complex
\(\mathfrak F^\eta_P(D)\).  (b) Resolving the conjecture would give the DTE
reporting workflow in \citet{FanPark2010} and \citet{Lee2024} a sharp warning
label: an infeasible \(A^\eta(r)\) identifies the exact displayed vertex that
cannot be read as a feasible treatment-effect distribution.

\begin{conjecture}[Open overlap-envelope separation (NOT YET PROVED)]\label{conj:open}
Under Assumptions~\ref{ass:finite}--\ref{ass:open-envelope}, if
\(\mathfrak F^\eta_P(D)\) contains an infeasible endpoint-face system with
certificate distance \(c_{\mathrm{fc}}(P,D,\eta)\), then every perturbed envelope
in the open cell defined by Assumption~\ref{ass:open-envelope} has
\[
G^\eta_{P_\rho}(D)\ge c_{\mathrm{fc}}(P,D,\eta)/4>0.
\]
Thus the non-representability of stacked endpoint reports holds on a nonsingleton
open class of marginal-overlap laws, not only at a fixed-marginal Makarov
instance.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Section 2]{FirpoRidder2019} establish finite-vector nonuniform
sharpness for fixed or identified marginal laws.  This conjecture is the strict
overlap-envelope extension: the conflict survives a full open cell of marginal
envelopes whose counterfactual marginals are themselves partially identified.
\citet[Supplementary Appendix 3]{Russell2021} and
\citet[Sections 2--3]{OberReynolds2023} provide endpoint LP/OT values inside
such cells, but not an open-class pasting failure for DTE CDF paths.  (b) The
consumer is the prior \texttt{eid\_dist\_synth\_control}/\texttt{v1} reviewer
request: the open-cell result tells when a marginal DTE report must be replaced
by a genuine LP/Frechet--Makarov envelope rather than repaired by small changes
to the estimated marginal curves.

\begin{conjecture}[Concrete nonzero witness (NOT YET PROVED)]\label{conj:witness}
There exists a three-point DTE grid \(D=\{d_1,d_2,d_3\}\), two covariate cells,
and binary-by-ternary potential-outcome supports satisfying
Assumptions~\ref{ass:finite}--\ref{ass:face-conflict} for which at least one
endpoint-face system in \(\mathfrak F^\eta_P(D)\) is infeasible and
\(G^\eta_P(D)\ge 0.05\).  The witness is nondegenerate: both covariate cells have
positive mass, each marginal envelope has at least two feasible interior
marginals, and no treatment arm is constant almost surely.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Section 2]{FirpoRidder2019} gives numerical finite-vector
improvements, but the proposed witness isolates an overlap-envelope face conflict
with nonsingleton marginals and reports both the infeasible
\(\mathfrak F^\eta_P(D)\) certificate and the scalar \(G^\eta_P(D)\).  (b) A
concrete witness would make the diagnostic usable for
\citet{FrandsenLefgren2021}-style DTE applications where analysts need to know
whether a finite displayed DTE band is a coherent partial-identification object.

\section{Sanity-check corollaries}
\begin{corollary}[Pointwise Fan--Park reduction]\label{cor:pointwise}
If \(K=1\) and every marginal envelope is a singleton, then
\(\mathcal C^\eta(P;\{d\})=\mathcal S^\eta(P;\{d\})\) and
\(G^\eta_P(\{d\})=0\).  The finite endpoint LP in Section~\ref{sec:setup}
reduces to the finite-support Makarov/Fan--Park sharp bound for \(F_\Delta(d)\).
\end{corollary}

\begin{corollary}[Rank-invariant point identification]\label{cor:rank}
If every marginal envelope is a singleton and the restriction class
\(\Pi^\eta(P)\) is augmented before computing both
\(\mathcal C^\eta(P;D)\) and \(\mathcal S^\eta(P;D)\) by a known deterministic
rank-invariant coupling in every covariate cell, then both sets equal the same
singleton DTE path and \(G^\eta_P(D)=0\).  If instead
\(\mathcal S^\eta(P;D)\) is computed from marginal information alone, its support
gap to that externally fixed singleton is a different marginal-only diagnostic,
not the \(G^\eta_P(D)\) locked in this proposal.
\end{corollary}

\begin{example}[Concrete finite witness candidate]\label{ex:witness-candidate}
For Conjecture~\ref{conj:witness}, the intended non-corner witness has
\(J=2\), \(w_1=w_2=1/2\), \(\mathcal Y_1=\{0,1\}\),
\(\mathcal Y_0=\{0,1,2\}\), and \(D=\{-1,0,1\}\).  In cell \(1\), the
admissible \(Y(1)\) marginal is \((p,1-p)\) with \(p\in[0.35,0.55]\), and the
admissible \(Y(0)\) marginal \((q_0,q_1,q_2)\) satisfies
\[
q_0\in[0.10,0.30],\quad q_1\in[0.45,0.65],\quad q_2\in[0.15,0.35].
\]
In cell \(2\), the admissible \(Y(1)\) marginal has \(p\in[0.55,0.75]\), and
the \(Y(0)\) marginal satisfies
\[
q_0\in[0.25,0.45],\quad q_1\in[0.15,0.35],\quad q_2\in[0.30,0.50].
\]
All intervals have interior feasible points.  The concrete verification route is
to enumerate the twelve coupling variables, solve the six pointwise endpoint
LPs, construct the stacked report \(\mathcal S^\eta(P;D)\), enumerate the
candidate endpoint-face systems \(A^\eta(r)\), and then evaluate the canonical
support gap
\(\sup_{\|v\|_1\le1}\{h_{\mathcal S^\eta(P;D)}(v)-h^\eta_P(v;D)\}_+\) only after
an infeasible endpoint-face certificate has been found.
\end{example}

\section{Proof-sketch route}
The routine endpoint LP reduces to finite-dimensional transportation polytope
algebra: write the DTE CDF ordinates as linear maps of the coupling tables,
append lower and upper row/column-sum envelope inequalities, and apply
linear-program strong duality.  For Conjecture~\ref{conj:diagnostic}, the planned
route is to exploit the fact that \(\mathcal C^\eta(P;D)\subseteq
\mathcal S^\eta(P;D)\) and that a polytope contains a monotone box exactly when
it contains the box vertices; the nontrivial step is proving that the
endpoint-face system \(A^\eta(r)\) is the correct reduced feasibility problem for
each canonical vertex, including tied monotone blocks.  For
Conjecture~\ref{conj:open}, use Hoffman perturbation bounds for finite linear
systems to show that an infeasible endpoint-face certificate with margin
\(c_{\mathrm{fc}}\) remains infeasible under the open envelope perturbations in
Assumption~\ref{ass:open-envelope}.  The concrete witness is then a small-support
enumeration: solve the six endpoint LPs, list the finitely many vertex systems,
and exhibit one dual Farkas certificate whose normalized violation exceeds
0.05.

\section{Honest scope flags}
The finite endpoint LP is routine and is no longer presented as the novelty
carrier.  Conjectures~\ref{conj:diagnostic}, \ref{conj:open}, and
\ref{conj:witness} are the novel kernel and are not yet proved.  The proposed
diagnostic is finite-support and finite-grid; it does not claim a continuum CDF
process, asymptotic inference, or mixed-support formula.  The old v2 zero-gap
support-function iff has been withdrawn because it was essentially standard
support separation after \(G^\eta_P(D)\) was defined.  The remaining flagship
risk is whether the endpoint-face certificate and open-envelope witness are
viewed as sufficiently more than finite LP bookkeeping.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial finite LP/OT diagnostic draft centered on
\(G^\eta_P(D)\), after archived angle 0 pursued the broader Choquet--OT path
envelope; prior verdict: none.
\item v2 (revise) -- canonicalized \(G^\eta_P(D)\) as a full dual-unit-ball
support gap, separated \(\Pi^\eta\), \(\mathcal C^\eta\), and
\(\mathcal S^\eta\) notation, reframed the comparator promise as
non-representability rather than strict endpoint tightening, added
section-level Russell/Ober-Reynolds anchors, and repaired the rank-invariance
sanity check; prior verdict: REVISE.
\item v3 (revise) -- withdrew the tautological \(G=0\) support-function iff as
the flagship claim, demoted the finite endpoint LP to setup, introduced the
independent endpoint-face certificate complex \(\mathfrak F^\eta_P(D)\), added an
open overlap-envelope separation conjecture, and tied strict gaps to a Hoffman
certificate margin; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Fan and Park(2010)]{FanPark2010}
Fan, Y. and S. S. Park (2010).
Sharp bounds on the distribution of treatment effects and their statistical inference.
\emph{Econometric Theory} 26(3), 931--951.

\bibitem[Fan and Wu(2010)]{FanWu2010}
Fan, Y. and J. Wu (2010).
Partial identification of the distribution of treatment effects in switching regime models and its confidence sets.
\emph{Review of Economic Studies} 77(3), 1002--1041.

\bibitem[Fan, Guerre, and Zhu(2017)]{FanGuerreZhu2017}
Fan, Y., E. Guerre, and D. Zhu (2017).
Partial identification of functionals of the joint distribution of ``potential outcomes''.
\emph{Journal of Econometrics} 197(1), 42--59.

\bibitem[Firpo and Ridder(2019)]{FirpoRidder2019}
Firpo, S. and G. Ridder (2019).
Partial identification of the treatment effect distribution and its functionals.
\emph{Journal of Econometrics} 213(1), 210--234.

\bibitem[Frandsen and Lefgren(2021)]{FrandsenLefgren2021}
Frandsen, B. R. and L. J. Lefgren (2021).
Partial identification of the distribution of treatment effects with an application to the Knowledge Is Power Program (KIPP).
\emph{Quantitative Economics} 12(1), 143--171.

\bibitem[Heckman, Smith, and Clements(1997)]{HeckmanSmithClements1997}
Heckman, J. J., J. Smith, and N. Clements (1997).
Making the most out of programme evaluations and social experiments: accounting for heterogeneity in programme impacts.
\emph{Review of Economic Studies} 64(4), 487--535.

\bibitem[Lee(2024)]{Lee2024}
Lee, S. (2024).
Partial identification and inference for conditional distributions of treatment effects.
\emph{Journal of Applied Econometrics}.

\bibitem[Makarov(1981)]{Makarov1981}
Makarov, G. D. (1981).
Estimates for the distribution function of a sum of two random variables when the marginal distributions are fixed.
\emph{Theory of Probability and its Applications} 26(4), 803--806.

\bibitem[Ober-Reynolds(2023)]{OberReynolds2023}
Ober-Reynolds, D. (2023).
Estimating functionals of the joint distribution of potential outcomes with optimal transport.
\emph{arXiv:2311.09435}.

\bibitem[Rueschendorf(1982)]{Rueschendorf1982}
Rueschendorf, L. (1982).
Random variables with maximum sums.
\emph{Advances in Applied Probability} 14(3), 623--632.

\bibitem[Russell(2021)]{Russell2021}
Russell, T. M. (2021).
Sharp bounds on functionals of the joint distribution in the analysis of treatment effects.
\emph{Journal of Business \& Economic Statistics} 39(2), 532--546.
\end{thebibliography}

\end{document}
