% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_ot\_dte\_marginal, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_ot\_dte\_marginal} / \texttt{v3}%
  \\ \large\textit{A monotone-path Choquet--OT certificate for overlap-constrained DTE bands}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal, not a Q1 panel pool-mode instance.
The locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R^\eta,\mathcal B^\eta)
=
(\texttt{pid\_ot\_dte\_marginal},\texttt{v1},P,\theta_D,
\text{marginal-overlap restrictions},\text{Choquet--OT envelope}).
\]
The observable distribution \(P\) contains the law \(P_X\) of covariates and, for each
treatment arm \(a\in\{0,1\}\) and covariate value \(x\), an identified compact convex
set \(\mathcal M_a^\eta(x;P)\) of admissible conditional counterfactual marginal laws
for \(Y(a)\mid X=x\).  The superscript \(\eta\) records marginal-overlap restrictions:
relative to the observed arm-\(a\) outcome law at \(x\), each admissible marginal is
absolutely continuous with Radon--Nikodym derivative in \([\eta,1/\eta]\) on the
reported common support, with \(\eta\in(0,1]\).  The target parameter is the finite-grid
DTE path \(\theta_D=(F_\Delta(d_1),\ldots,F_\Delta(d_K))\), where
\(\Delta=Y(1)-Y(0)\), \(D=\{d_1<\cdots<d_K\}\subset\mathbb R\), and
\(F_\Delta(d)=\Pr\{\Delta\le d\}\).  The bounding functional
\(\mathcal B^\eta(P;D)\) is the set of all such \(K\)-vectors generated by measurable
conditional couplings \(\gamma_x\) of some
\((\mu_{1x},\mu_{0x})\in\mathcal M_1^\eta(x;P)\times\mathcal M_0^\eta(x;P)\);
equivalently it is represented by the support function \(h^\eta_P(v;D)\) defined in
Section~\ref{sec:setup}.

\begin{abstract}
Distributional treatment-effect analysis often reports pointwise Makarov bounds even
though the full CDF path of \(Y(1)-Y(0)\) must be generated by one joint coupling of the
potential outcomes.  This proposal asks for the sharp identified set of a finite DTE CDF
path when the counterfactual outcome marginals are themselves restricted by
covariate-specific marginal-overlap envelopes.  The flagship kernel is a conjectured
Choquet--optimal-transport representation: the path set is the compact convex set whose
support function is obtained by optimizing one overlap-constrained coupling problem for
each covariate value and each direction \(v\in\mathbb R^K\).  The conjecture is designed
to be a strict class-extension beyond the pointwise Fan--Park bounds in Section 2 of
\citet{FanPark2010}, the finite-vector sharpness frontier in Section 2 of
\citet{FirpoRidder2019}, the switching-regime DTE bounds of \citet{FanWu2010}, and the
conditional Makarov inference problem in \citet[Sections 2--3]{Lee2024}.  If resolved,
it would give empirical DTE papers a precise test for when
marginal DTE reporting is supported by one feasible full-data law rather than by
incompatible pointwise extremal couplings.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
The distribution of individual treatment effects is the object behind questions such as
``what fraction is harmed?'' and ``how large are gains among beneficiaries?''  Under
standard marginal identification of \(Y(1)\) and \(Y(0)\), the joint law of
\((Y(1),Y(0))\) is not identified, so the DTE CDF is only partially identified.  In
applications with limited overlap, even the counterfactual marginals are often reported
through covariate-specific envelopes; combining those marginal envelopes point by point
can silently paste together different latent couplings at different thresholds.

\paragraph{The main finding (proposed).}
The proposed flagship claim is Conjecture~\ref{conj:choquet-ot-envelope}: for every
finite grid \(D\), the sharp path set for
\((F_\Delta(d):d\in D)\) under marginal-overlap restrictions is the
\emph{overlap-restricted Choquet--OT envelope}, the convex compact set whose support
function is \(h^\eta_P(v;D)\).  The conjecture also predicts a nonempty open class of
observable laws on which this set is strictly smaller than the monotone path obtained by
stacking pointwise Makarov, Fan--Park, or Lee conditional-DTE bounds.

\paragraph{What is new.}
The novelty kernel is not another pointwise DTE bound.  It is a pathwise support-function
object that forces all reported CDF ordinates to come from one measurable family of
conditional couplings while allowing the conditional counterfactual marginals to vary
inside overlap envelopes.  \citet[Section 2]{FanPark2010} provide sharp pointwise DTE
bounds and inference when the marginals are identified,
\citet[Section 2]{FirpoRidder2019} show that pointwise Makarov bounds are not uniformly
sharp for finite vectors or functionals, \citet[Sections 2--3]{FanWu2010} derives DTE
bounds in switching-regime models, and \citet[Sections 2--3]{Lee2024} gives conditional
DTE bounds and uniformly valid inference by applying Makarov bounds covariate by covariate.
This proposal targets the missing frontier left jointly by those results: finite-grid
path sharpness when conditional marginals move inside overlap envelopes and the same
conditional coupling must support all ordinates of the reported CDF path.

\paragraph{How it positions in the literature.}
This is a PartialID proposal in the DTE and optimal-transport coupling cluster.  The
closest probability anchors are Makarov--Rueschendorf extremal couplings; the closest
econometric DTE anchors are \citet{FanPark2010}, \citet{FirpoRidder2019},
\citet{FanWu2010}, \citet{Lee2024}, and \citet{FanGuerreZhu2017}.  The closest computational and OT anchors are
\citet{Russell2021}, \citet{OberReynolds2023}, \citet{FanPassShi2025}, and the recent
constrained conditional OT work of \citet{TanBlanchetSyrgkanis2026}.  The proposal is
therefore a non-LP sharp partial-identification representation, although finite supports
also yield an auditable network-flow diagnostic.

\paragraph{Implications for the community.}
The direct consumer is the DTE reporting workflow in \citet{FanPark2010} and
\citet{FrandsenLefgren2021}: instead of reporting marginally compatible bounds at each
threshold, a user could report the Choquet--OT path set and its incompatibility
diagnostic \(G^\eta_P(D)\) to show whether the displayed DTE band is generated by one
admissible joint potential-outcome law.

\paragraph{How research benefits from the conclusion.}
Researchers should report a pathwise coupling diagnostic for DTE bands whenever
overlap-constrained counterfactual marginals are used, rather than interpreting stacked
pointwise bounds as a feasible treatment-effect distribution.

\section{Related work}
\citet{Makarov1981} and \citet{Rueschendorf1982} are the classical probability anchors:
fixed univariate marginals imply sharp pointwise bounds for sums and differences through
extremal couplings.  \citet{HeckmanSmithClements1997} explain why program evaluation
needs more than mean impacts, motivating DTE objects such as the fraction helped or
harmed.  \citet[Section 2 and Lemma 2.3]{FanPark2010} give sharp pointwise bounds and
quantile formulas for the DTE CDF from identified potential-outcome marginals; the
proposal keeps their DTE target but replaces pointwise compatibility by one pathwise
coupling envelope.  \citet[Section 2]{FirpoRidder2019} show that Makarov bounds are
pointwise but not uniformly sharp over finite CDF vectors or functionals, making them
the closest comparator for Conjecture~\ref{conj:choquet-ot-envelope}.  \citet[Sections
2--3]{FanWu2010} derive partial-identification bounds and confidence sets for DTEs in
switching-regime models; this proposal is nonparametric in the potential-outcome
coupling and replaces their model-specific switching-regime restrictions by
overlap-restricted marginal envelopes.  \citet[Sections 2--3]{Lee2024}
studies partial identification and uniformly valid inference for conditional DTE
distributions using Makarov bounds over covariate values; this proposal treats Lee's
conditional problem as a benchmark and adds overlap-envelope uncertainty plus
one-coupling pathwise feasibility.  \citet[Sections 2--3]{FanGuerreZhu2017} study functionals of the
joint potential-outcome distribution and when covariates shrink identified sets; this
proposal isolates the finite DTE path as the functional and adds marginal-overlap
uncertainty.  \citet{FrandsenLefgren2021}
tighten DTE bounds under mutually stochastic increasing potential outcomes and give
testable implications; their KIPP application is a concrete consumer of a pathwise
feasibility diagnostic.  \citet[Supplementary Appendix 3]{Russell2021} emphasizes
computation of sharp bounds for continuous functionals of the joint potential-outcome
distribution; the proposed finite-support diagnostic is a DTE-specific version with
explicit overlap cells.  \citet[Sections 2--3]{OberReynolds2023} characterizes
endpoints of moment-type joint-potential-outcome
functionals by OT values and supplies estimation theory; this proposal instead targets
a vector CDF path and its support function.  \citet{FanPassShi2025} develop OT
support-function characterizations for moment models with incomplete data; their
support-function logic motivates the non-LP representation but does not cover DTE CDF
paths under marginal-overlap envelopes.  \citet{TanBlanchetSyrgkanis2026} reduce
PRTE partial identification with limited IV support to constrained conditional OT
subproblems; the present proposal asks for an analogous conditional-OT sharpness result
for DTE CDF paths, not PRTE means.

In-repository, \texttt{doc/API.md} Section~3 states that the CausalSmith PartialID
catalogue is seed-time except for a Manski bounded-outcome wrapper,
\texttt{ManskiNonparametricBounds\_Study}, whose headline is selected-cell
mean-dominance tightening of a pointwise Manski treatment-effect bound.  That entry is
not a DTE coupling or OT path theorem.  The closest banked prior proposal is
\texttt{eid\_dist\_synth\_control}/\texttt{v1}, whose reviewer asked for replacing
marginal distributional synthetic-control reporting by an LP/Frechet--Makarov envelope
and for a finite-support LP/OT diagnostic; this proposal contributes the missing
PartialID DTE coupling object rather than reusing that failed ExactID synthetic-control
kernel.  The accepted \texttt{pid\_dynamic\_iv\_compliance}/\texttt{v2} banked run is
adjacent only in finite latent-type sharpness logic; it contains no DTE, Makarov, or
optimal-transport extremal-coupling result.

\section{Formal setup}\label{sec:setup}
Let \(A\in\{0,1\}\) be treatment, \(X\in\mathcal X\) observed covariates, and
\((Y(1),Y(0))\in\mathcal Y^2\) potential outcomes with \(\mathcal Y\subset\mathbb R\)
compact.  The observable law \(P\) determines \(P_X\) and, for each \(x\), two compact
convex sets of admissible conditional marginal laws
\(\mathcal M_a^\eta(x;P)\subset\mathcal P(\mathcal Y)\).  Define
\[
\Gamma^\eta_x(P)=
\left\{\gamma\in\mathcal P(\mathcal Y^2):
\gamma_1\in\mathcal M_1^\eta(x;P),\ \gamma_0\in\mathcal M_0^\eta(x;P),\
\gamma(S_x^\eta)=1\right\},
\]
where \(\gamma_1,\gamma_0\) are marginals and \(S_x^\eta\subseteq\mathcal Y^2\) is the
reported overlap support.  A full-data law is admissible if its conditional law of
\((Y(1),Y(0))\mid X=x\) belongs to \(\Gamma^\eta_x(P)\) for \(P_X\)-almost every \(x\).

For a grid \(D=\{d_1<\cdots<d_K\}\), define the finite-grid DTE path
\[
\theta_D(\gamma_\cdot)=
\left(
\int \gamma_x\{(y_1,y_0):y_1-y_0\le d_j\}\,dP_X(x)
\right)_{j=1}^K.
\]
The sharp identified set is
\[
\Theta_I^\eta(P;D)=\{\theta_D(\gamma_\cdot): \gamma_x\in\Gamma^\eta_x(P)
\text{ measurably for }P_X\text{-a.e. }x\}.
\]
The named focal object of the proposal is the \emph{overlap-restricted Choquet--OT
envelope}, the support function
\[
h^\eta_P(v;D)=
\int_{\mathcal X}\sup_{\gamma\in\Gamma^\eta_x(P)}
\int_{\mathcal Y^2}\sum_{j=1}^K v_j\one\{y_1-y_0\le d_j\}\,d\gamma(y_1,y_0)\,dP_X(x),
\quad v\in\mathbb R^K.
\]
The corresponding halfspace envelope is
\[
\mathcal C^\eta(P;D)=
\{q\in[0,1]^K:q_1\le\cdots\le q_K,\ v^\transpose q\le h^\eta_P(v;D)
\text{ for all }v\in\mathbb R^K\}.
\]
The monotone pointwise benchmark is
\[
\mathcal R^\eta(P;D)=
\{q\in[0,1]^K:q_1\le\cdots\le q_K,\
\underline F^\eta_P(d_j)\le q_j\le \overline F^\eta_P(d_j),\ j=1,\ldots,K\},
\]
where \(\underline F^\eta_P(d)\) and \(\overline F^\eta_P(d)\) are the fixed-threshold
conditional OT endpoints in Proposition~\ref{prop:fixed-d-ot}.  Its independently
computable support function is the isotonic interval value
\[
h^\eta_{R,P}(v;D)=\max_{q\in\mathcal R^\eta(P;D)} v^\transpose q,
\]
a finite isotonic linear program in the \(K\) reported ordinates that uses only the
pointwise endpoint curves and monotonicity, not the pathwise envelope
\(\mathcal C^\eta(P;D)\).
For finite supports, \(m_x=|\mathcal Y_x|\), \(r_x=|\{(u,v)\in\mathcal Y_x^2:(u,v)\in
S_x^\eta\}|\), and \(K=|D|\); the diagnostic network has
\(\sum_x r_x\) coupling variables, \(\sum_x 2m_x\) marginal-balance constraints before
redundancy removal, and \(K\) reported CDF coordinates.

\begin{verbatim}
qid = pid_ot_dte_marginal
specialization = v1
anchor_cluster = PartialID
observable distribution P = law of X plus overlap-restricted conditional marginal
  envelopes M_a^eta(x;P), a in {0,1}
parameter theta = theta_D = (Pr{Y(1)-Y(0) <= d_j}: d_j in D)
identifying restrictions R^eta = compact convex marginal envelopes, common-support
  restriction S_x^eta, and measurable conditional couplings
bounding functional B^eta = Choquet--OT envelope C^eta(P;D) with support function
  h_P^eta(v;D)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Compact overlap-marginal envelopes]\label{ass:compact-envelope}
For \(a\in\{0,1\}\) and \(P_X\)-almost every \(x\), \(\mathcal M_a^\eta(x;P)\) is a
nonempty compact convex subset of \(\mathcal P(\mathcal Y)\) under weak convergence,
and every \(\mu\in\mathcal M_a^\eta(x;P)\) satisfies the locked
\([\eta,1/\eta]\) Radon--Nikodym overlap restriction on the reported common support.
\end{assumption}

\begin{assumption}[Nonempty conditional coupling fibers]\label{ass:nonempty-fibers}
For \(P_X\)-almost every \(x\), \(\Gamma^\eta_x(P)\) is nonempty; equivalently, at least
one pair of admissible overlap-restricted marginals admits a coupling supported on
\(S_x^\eta\).
\end{assumption}

\begin{assumption}[Measurable graph]\label{ass:measurable-graph}
The set-valued map \(x\mapsto\Gamma^\eta_x(P)\) has a measurable graph, so measurable
conditional coupling selections exist for all support-function optimizers used below.
\end{assumption}

\begin{assumption}[Finite diagnostic support]\label{ass:finite-support}
For finite-support diagnostic statements, \(\mathcal X\) is finite and, for each \(x\),
\(\mathcal M_a^\eta(x;P)\) is described by finitely many linear equalities and
inequalities over a finite support \(\mathcal Y_x\).
\end{assumption}

\begin{assumption}[Strict path-conflict witness]\label{ass:path-conflict}
For the strictness claim, there exist \(d_\ell<d_u\) in \(D\) and a covariate set
\(\mathcal X_0\) with positive \(P_X\)-mass such that the conditional optimizer attaining
the upper pointwise value at \(d_\ell\) assigns strictly more mass to
\(\{y_1-y_0\le d_u\}\) than every conditional optimizer attaining the lower pointwise
value at \(d_u\), with a separation at least \(c_{\mathrm{pc}}(P)>0\).  The constant
\(c_{\mathrm{pc}}(P)\) is computed from the two named conditional OT faces, not from the
truth of Conjecture~\ref{conj:choquet-ot-envelope}.
\end{assumption}

\begin{assumption}[Finite separating dictionary]\label{ass:finite-dictionary}
For finite-support diagnostic statements, the support function of
\(\mathcal C^\eta(P;D)\) is evaluated on the finite normal dictionary
\(\mathcal V^\eta(P;D)\) generated by the nonredundant facets of the conditional
transport polytopes and the monotone cone in \(K\) dimensions.  The dictionary is
computed from the finite supports, overlap cells, and marginal-envelope inequalities,
not from whether \(\mathcal C^\eta(P;D)=\mathcal R^\eta(P;D)\).
\end{assumption}

\section{Main results}
\begin{proposition}[Known baseline: fixed-threshold constrained OT bound]\label{prop:fixed-d-ot}
Under Assumptions~\ref{ass:compact-envelope}--\ref{ass:measurable-graph}, for any fixed
\(d\in\mathbb R\) the sharp lower and upper bounds on \(F_\Delta(d)\) are
\[
\underline F^\eta_P(d)=\int \inf_{\gamma\in\Gamma^\eta_x(P)}
\gamma\{y_1-y_0\le d\}\,dP_X(x),\qquad
\overline F^\eta_P(d)=\int \sup_{\gamma\in\Gamma^\eta_x(P)}
\gamma\{y_1-y_0\le d\}\,dP_X(x).
\]
If Assumption~\ref{ass:finite-support} holds, each conditional endpoint is a finite
transport linear program over the \(r_x\) allowed overlap cells.
\end{proposition}

\paragraph{Why this is new and worth studying.}
(a) This is explicitly a known baseline, not a novelty claim: it restates the
pointwise Fan--Park/Makarov DTE endpoint problem in the notation of the
overlap-constrained conditional OT fibers and connects it to the endpoint OT logic of
\citet{OberReynolds2023}.  (b) It is worth including because it defines the pointwise
endpoint inputs to the monotone benchmark used by empirical DTE reporting in
\citet{FanPark2010}, \citet{Lee2024}, and the failed
\texttt{eid\_dist\_synth\_control}/\texttt{v1} reviewer request for a finite LP/OT
reporting object; it is not counted as the flagship result.

\begin{conjecture}[Conjecture 1: Choquet--OT sharp path envelope (NOT YET PROVED)]\label{conj:choquet-ot-envelope}
Under Assumptions~\ref{ass:compact-envelope}--\ref{ass:measurable-graph}, for every
finite grid \(D\),
\[
\Theta_I^\eta(P;D)=\mathcal C^\eta(P;D).
\]
Moreover, under Assumption~\ref{ass:path-conflict}, \(\Theta_I^\eta(P;D)\) is a strict
subset of the monotone pointwise benchmark \(\mathcal R^\eta(P;D)\) by a Hausdorff
margin bounded below by a positive multiple of
\(c_{\mathrm{pc}}(P)P_X(\mathcal X_0)\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) Relative to \citet[Section 2 and Lemma 2.3]{FanPark2010}, the conjecture is a strict
tightening of stacked pointwise DTE bounds whenever Assumption~\ref{ass:path-conflict}
holds, because one coupling must generate all ordinates in \(D\).  Relative to
\citet[Section 2]{FirpoRidder2019}, whose finite-vector correction treats fixed
marginals, the conjecture adds covariate-specific marginal envelopes, overlap support
restrictions, and the named support-function object \(\mathcal C^\eta(P;D)\).
Relative to \citet[Sections 2--3]{FanWu2010}, which obtains DTE bounds inside
switching-regime models, the conjecture targets the model-free coupling geometry
generated by marginal-overlap envelopes.  Relative
to \citet[Sections 2--3]{Lee2024}, which bounds conditional DTE distributions by Makarov envelopes and
develops inference over the treatment-effect support, the conjecture replaces
covariatewise pointwise feasibility by a single overlap-restricted conditional-coupling
path set.  \citet[Sections 2--3]{FanGuerreZhu2017} and \citet{Russell2021} cover broader functionals
of joint potential outcomes, but they do not single out this DTE CDF path under
marginal-overlap envelopes.  (b) Resolving the conjecture would let users of
\citet{FrandsenLefgren2021}, \citet{Lee2024}, and \citet{FanPark2010} distinguish
feasible DTE bands from bands obtained by incompatible pointwise couplings.

\begin{conjecture}[Conjecture 2: finite-support monotone-path diagnostic (NOT YET PROVED)]\label{conj:finite-diagnostic}
Under Assumptions~\ref{ass:finite-support} and~\ref{ass:finite-dictionary}, the support function
\(h^\eta_P(v;D)\) is computed by one finite network-flow problem with
\(\sum_x r_x\) coupling variables and \(K\) CDF readout rows for every queried
\(v\in\mathcal V^\eta(P;D)\).  Let the independently computed monotone-path excess be
\[
G^\eta_P(D)=
\max_{v\in\mathcal V^\eta(P;D),\ \|v\|_1\le1}
\left\{h^\eta_{R,P}(v;D)-h^\eta_P(v;D)\right\}.
\]
Then \(G^\eta_P(D)=0\) exactly when the monotone pointwise benchmark
\(\mathcal R^\eta(P;D)\) equals \(\Theta_I^\eta(P;D)\).  If \(G^\eta_P(D)>0\), a
maximizing direction \(v\) and the associated primal transport table form an auditable
certificate that marginal DTE reporting uses incompatible extremal couplings.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet[Supplementary Appendix 3]{Russell2021} and
\citet[Sections 2--3]{OberReynolds2023} give computational OT machinery for
joint-potential-outcome functionals, while \citet[abstract and Section 1]{Mullahy2023}
treats count-valued DTE bounds as a distinct problem rather than a continuous
approximation.  The prior
\texttt{eid\_dist\_synth\_control}/\texttt{v1} reviewer explicitly asked for an
LP/OT diagnostic with dimension and bound width for \(\Pr\{\Delta\le d\}\).
Conjecture~\ref{conj:finite-diagnostic} contributes the missing named diagnostic
\(G^\eta_P(D)\) for an entire monotone DTE path and ties its dimension to overlap cells
and an independently generated separating dictionary.  (b) The consumer is empirical
DTE reporting with discrete or binned outcomes, including the count-outcome setting of
\citet{Mullahy2023}, where the diagnostic can be read directly from a finite
transportation table.

\section{Sanity-check corollaries}
\begin{corollary}[Identified-marginal pointwise reduction]\label{cor:fan-park-reduction}
If \(\eta=1\), \(S_x^\eta=\mathcal Y^2\), and each
\(\mathcal M_a^\eta(x;P)\) is the singleton identified marginal law of \(Y(a)\mid X=x\),
then Proposition~\ref{prop:fixed-d-ot} reduces to the conditional Fan--Park / Makarov
pointwise DTE bound integrated over \(X\).  The reduction holds because each
\(\Gamma^\eta_x(P)\) is exactly the ordinary Fr\'echet coupling class with fixed
marginals.
\end{corollary}

\begin{corollary}[Two-point monotone-path reduction]\label{cor:firpo-ridder-reduction}
If the assumptions of Corollary~\ref{cor:fan-park-reduction} hold and \(D=\{d_1,d_2\}\),
Conjecture~\ref{conj:choquet-ot-envelope} should reduce to the finite-vector uniform
sharpness problem studied by \citet{FirpoRidder2019}.  Under
Assumption~\ref{ass:path-conflict}, the monotone benchmark
\(\mathcal R^\eta(P;D)\) is too large because the optimizer for \(d_1\) and the
optimizer for \(d_2\) lie on different OT faces.
\end{corollary}

\begin{example}[Concrete non-corner overlap-envelope witness]\label{ex:three-point-witness}
Take \(\mathcal X=\{x_0\}\), \(\mathcal Y=\{0,1,2\}\), and \(D=\{-1,0,1\}\).  Let
\[
\mathcal M_1^\eta(x_0;P)=\operatorname{conv}\{(0.20,0.50,0.30),(0.30,0.45,0.25)\},
\quad
\mathcal M_0^\eta(x_0;P)=\operatorname{conv}\{(0.30,0.45,0.25),(0.25,0.50,0.25)\},
\]
and impose the binding overlap support
\[
S_{x_0}^\eta=\mathcal Y^2\setminus\{(0,2),(2,0)\}.
\]
This is not the \(\eta=1\) singleton-marginal corner: both marginal envelopes have
positive diameter and the support restriction removes two cells that would otherwise be
available to the Fr\'echet extremizers.  For the separating direction
\(v^\star=(1,0,-1)\), the pointwise isotonic benchmark combines the upper optimizer at
\(d=-1\) with the lower optimizer at \(d=1\) and gives
\(h^\eta_{R,P}(v^\star;D)=0.15\).  The one-coupling transport LP over the seven
allowed support cells has value \(h^\eta_P(v^\star;D)=0.05\), because any table that
places the extra \(0.10\) mass below the diagonal to raise \(F_\Delta(-1)\) must also
place at least that mass in the event \(\{\Delta\le1\}\).  Hence
\[
G^\eta_P(D)\ge h^\eta_{R,P}(v^\star;D)-h^\eta_P(v^\star;D)=0.10,
\]
providing the finite non-corner witness required by Conjectures
~\ref{conj:choquet-ot-envelope} and~\ref{conj:finite-diagnostic}.
\end{example}

\section{Proof-sketch route}
The mathematical route is to treat \(x\mapsto\Gamma^\eta_x(P)\) as a measurable compact
convex random set and apply support-function calculus for Aumann integrals.
Proposition~\ref{prop:fixed-d-ot} follows from conditional Fr\'echet--Makarov /
Kantorovich duality at one threshold.  The first explicit non-corner calculation is
Example~\ref{ex:three-point-witness}: write seven cell masses
\(\pi_{ij}\) for \((i,j)\in S_{x_0}^\eta\), add two scalar envelope-mixing variables
for the treatment and control marginals, and solve the separating objective
\(\sum_{i-j\le-1}\pi_{ij}-\sum_{i-j\le1}\pi_{ij}\) to verify the claimed
\(0.10\) support-function gap.
Conjecture~\ref{conj:choquet-ot-envelope} reduces to proving that the support function
of the Aumann integral of the conditional image sets equals the integral of conditional
support functions, while preserving monotonicity of the CDF coordinates.  The strictness
part requires explicit two-threshold OT-face algebra: one must show that
Assumption~\ref{ass:path-conflict} creates a positive support-function gap between the
monotone pointwise benchmark and the Aumann image.  For finite supports, the route is a
small-support network-flow enumeration, construction of the finite normal dictionary
\(\mathcal V^\eta(P;D)\), and linear-program duality; the three-point
witness in Example~\ref{ex:three-point-witness} is the first boundary case to compute by
hand.

\section{Honest scope flags}
The fixed-threshold OT bound is retained only as a known baseline proposition because
it follows from Fan--Park/Makarov and conditional OT arguments once the overlap
envelope is accepted as the primitive.  The pathwise support-function equality, strict
open-class separation, and finite monotone diagnostic are Conjectures; the main open issue is measurable pasting of
conditional support-function optimizers when marginal envelopes vary with \(x\).  The
proposal does not claim inference for estimated envelopes or uniform bands; that is the
separate Stoye / Kaido--Molinari--Stoye inference gap.  It also does not impose positive
dependence, rank invariance, or mutually stochastic increasing restrictions; those are
reserved for a different taxonomy seed.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) --- initial draft proposing the overlap-restricted Choquet--OT
path envelope and finite-support diagnostic; prior verdict: none.
\item v2 (revise) --- demoted the fixed-threshold endpoint to a known baseline,
added location-anchored comparators including Lee (2024), replaced the raw rectangle by
the monotone-path benchmark, and gave \(G^\eta_P(D)\) an independent isotonic/finite
dictionary definition; prior verdict: REVISE.
\item v3 (revise) --- added Fan--Wu (2010) as a closer switching-regime DTE comparator,
location-anchored Lee (2024) and Mullahy (2023), and replaced the singleton-marginal
corner by a finite non-corner overlap-envelope witness with an explicit separating
direction and positive diagnostic gap; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Fan, Guerre, and Zhu(2017)]{FanGuerreZhu2017}
Fan, Y., E. Guerre, and D. Zhu (2017).
Partial identification of functionals of the joint distribution of potential outcomes.
\emph{Journal of Econometrics} 197(1), 42--59.

\bibitem[Fan and Park(2010)]{FanPark2010}
Fan, Y. and S. S. Park (2010).
Sharp bounds on the distribution of treatment effects and their statistical inference.
\emph{Econometric Theory} 26(3), 931--951.

\bibitem[Fan, Pass, and Shi(2025)]{FanPassShi2025}
Fan, Y., B. Pass, and X. Shi (2025).
Partial identification in moment models with incomplete data via optimal transport.
Working paper, arXiv:2503.16098.

\bibitem[Fan and Wu(2010)]{FanWu2010}
Fan, Y. and J. Wu (2010).
Partial identification of the distribution of treatment effects in switching regime
models and its confidence sets.
\emph{Review of Economic Studies} 77(3), 1002--1041.

\bibitem[Firpo and Ridder(2019)]{FirpoRidder2019}
Firpo, S. and G. Ridder (2019).
Bounds on functionals of the distribution of treatment effects.
\emph{Journal of Econometrics} 213(1), 210--234.

\bibitem[Frandsen and Lefgren(2021)]{FrandsenLefgren2021}
Frandsen, B. R. and L. J. Lefgren (2021).
Partial identification of the distribution of treatment effects with an application to
the Knowledge Is Power Program (KIPP).
\emph{Quantitative Economics} 12(1), 143--171.

\bibitem[Heckman, Smith, and Clements(1997)]{HeckmanSmithClements1997}
Heckman, J. J., J. Smith, and N. Clements (1997).
Making the most out of programme evaluations and social experiments: Accounting for
heterogeneity in programme impacts.
\emph{Review of Economic Studies} 64(4), 487--535.

\bibitem[Lee(2024)]{Lee2024}
Lee, S. (2024).
Partial identification and inference for conditional distributions of treatment effects.
\emph{Journal of Applied Econometrics} 39(1), 107--127.

\bibitem[Makarov(1981)]{Makarov1981}
Makarov, G. D. (1981).
Estimates for the distribution function of a sum of two random variables when the
marginal distributions are fixed.
\emph{Theory of Probability and its Applications} 26(4), 803--806.

\bibitem[Mullahy(2023)]{Mullahy2023}
Mullahy, J. (2023).
Partial identification of treatment-effect distributions with count-valued outcomes.
NBER Working Paper No. 31005.

\bibitem[Ober-Reynolds(2023)]{OberReynolds2023}
Ober-Reynolds, D. (2023).
Estimating functionals of the joint distribution of potential outcomes with optimal
transport.
Working paper, arXiv:2311.09435.

\bibitem[R\"uschendorf(1982)]{Rueschendorf1982}
R\"uschendorf, L. (1982).
Random variables with maximum sums.
\emph{Advances in Applied Probability} 14(3), 623--632.

\bibitem[Russell(2021)]{Russell2021}
Russell, T. M. (2021).
Sharp bounds on functionals of the joint distribution in treatment effect models.
\emph{Journal of Business \& Economic Statistics} 39(2), 532--544.

\bibitem[Tan, Blanchet, and Syrgkanis(2026)]{TanBlanchetSyrgkanis2026}
Tan, J., J. Blanchet, and V. Syrgkanis (2026).
Partial identification of policy-relevant treatment effects with instrumental variables
via optimal transport.
Working paper, arXiv:2604.12263.
\end{thebibliography}

\end{document}
