% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_ot\_dte\_marginal, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_ot\_dte\_marginal} / \texttt{v1}%
  \\ \large\textit{A lifted-OT cycle certificate for pasting local DTE relaxations into one full-data law}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form PartialID proposal, not a Q1 panel pool-mode instance.  The
locked tuple is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R,\mathcal B)
=
(\texttt{pid\_ot\_dte\_marginal},\texttt{v1},P,\theta_D,
\text{lifted marginal-overlap, IV/dose, and rank-tube restrictions},
\text{cycle-pasted OT bound}).
\]
The observable distribution \(P\) contains a finite covariate-dose-IV law over
cells \(c\in\mathcal C\), potential-outcome support points
\(\mathcal Y_1=\{a_1,\ldots,a_M\}\) and
\(\mathcal Y_0=\{b_1,\ldots,b_N\}\), and cell weights \(w_c>0\).
The parameter is the finite-grid DTE path
\[
\theta_D=(F_\Delta(d_1),\ldots,F_\Delta(d_K)),\qquad
\Delta=Y(1)-Y(0),\quad D=\{d_1<\cdots<d_K\}.
\]
The restriction class \(\mathcal R(P)\) consists of nonnegative local transport
tables \(\pi_c(m,n)\) satisfying: (i) marginal-overlap row and column envelope
constraints \(\ell^1_{cm}\le\sum_n\pi_c(m,n)\le u^1_{cm}\) and
\(\ell^0_{cn}\le\sum_m\pi_c(m,n)\le u^0_{cn}\); (ii) linear IV/dose balancing
constraints \(A\pi=b(P)\); and (iii) local rank-copula tube constraints
\(|\pi_c(R)-\bar\pi_c(R)|\le\rho_c(R)\) on a named finite rectangle family
\(\mathcal R_c^{\mathrm{rank}}\).  The bounding functional
\(\mathcal B(P;D)\) is the set of DTE paths generated by a single full-data law
whose cellwise margins are the \(\pi_c\)'s.  The named focal object is the
\emph{lifted-OT cycle certificate} \(\mathfrak C_P(D)\), defined in
Section~\ref{sec:setup}, whose vanishing is conjectured to be the exact frontier
between a sharp lifted relaxation and a merely valid outer envelope.

\begin{abstract}
Recent optimal-transport partial-identification results often reduce constrained
problems to local one-dimensional or conditional OT subproblems.  For
distributional treatment effects, however, a local table that is feasible in
each covariate-dose-IV cell need not be pasteable into one full-data law once
marginal-overlap envelopes, IV/dose restrictions, and rank-copula tubes are
imposed simultaneously.  This proposal asks for the sharp pasting frontier.  The
flagship conjecture is that a finite lifted-OT relaxation is sharp exactly when
the equality-expanded lifted-OT cycle certificate \(\mathfrak C_P(D)\) vanishes,
where \(\mathfrak C_P(D)\) is computed from the incidence matrix obtained after
turning every overlap-envelope and rank-tube inequality into an equality with a
named slack variable.  If resolved, the result
would tell users of constrained conditional OT when local DTE bounds are genuine
sharp partial-identification statements and when they are only outer bounds that
cannot be supported by any single latent potential-outcome law.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Distributional treatment-effect bounds are often constructed by solving local
transport problems after conditioning on covariates, instrument values, or dose
cells.  Local decomposition is attractive because each subproblem is small and
interpretable.  The scientific target, however, is a single joint law of all
relevant potential outcomes and latent ranks.  If separately feasible local OT
tables cannot be pasted into one law, the reported DTE bound can be numerically
tight but substantively false as a sharp identification statement.

\paragraph{The main finding (proposed).}
The proposed kernel is Conjecture~\ref{conj:cycle-frontier}: the lifted OT
relaxation that optimizes the DTE path over cellwise transport tables is sharp if
and only if every cycle in a finite compatibility hypergraph has zero imbalance.
The compatibility hypergraph is built from the row and column marginal envelopes,
the IV/dose balancing equations, and the local rank-copula tube rectangles.  The
cycle certificate \(\mathfrak C_P(D)\) is not defined as the distance to the true
sharp set; it is a computable algebraic obstruction obtained from signed sums of
shared marginal constraints.

\paragraph{What is new.}
\citet[Sections 2--3]{FanWu2010} study DTE bounds in switching-regime models,
while \citet[Sections 2--3]{TanBlanchetSyrgkanis2026} formulate PRTE partial
identification under limited IV support as constrained conditional OT and reduce
their mean problem to sharp one-dimensional OT subproblems.  \citet[Section
2]{GaoGeQian2025} casts causal partial identification with multiple potential
outcomes as exact multi-marginal OT.  The epsilon-gap is not the existence of an
MOT formulation; it is the full-data pasting layer for decomposed DTE reports:
local conditional OT sharpness does not by itself characterize whether one
shared latent-type law can realize all local tables after rank-tube and IV/dose
restrictions are added.  \citet[Section 2]{FirpoRidder2019} supplies the
finite-vector DTE motivation, but the proposed Conjecture~\ref{conj:firpo-frontier}
phrases a strict non-representability frontier against local pointwise Makarov
aggregation rather than merely citing that nonuniformity as background.

\paragraph{How it positions in the literature.}
This is a PartialID proposal in the DTE and constrained optimal-transport
cluster.  It is structurally different from a pointwise Makarov refinement or a
finite endpoint LP diagnostic: the target is a pasting theorem for full-data
realizability of local OT tables.  The proposal bridges DTE partial
identification, constrained conditional OT, and finite marginal-problem
compatibility.  It consumes IV/dose and rank-copula restrictions only as linear
constraints on potential-outcome tables; it is not a causal-discovery or
do-calculus proposal.

\paragraph{Implications for the community.}
The direct consumer is the constrained conditional OT workflow in
\citet{TanBlanchetSyrgkanis2026} and the rejected
\texttt{pid\_dose\_response\_iv}/\texttt{v1} CausalSmith angle that asked for a
pasting theorem: a researcher could compute \(\mathfrak C_P(D)\) before treating
local DTE relaxations as sharp.

\paragraph{How research benefits from the conclusion.}
Researchers should check the cycle-pasting certificate before reporting
lifted-OT DTE bounds that combine overlap, IV/dose, and rank-copula restrictions.

\section{Related work}
\citet{Makarov1981} and \citet{Rueschendorf1982} are the probability anchors for
extremal couplings with fixed marginals; this proposal studies when many such
local couplings can be globally pasted.  \citet{HeckmanSmithClements1997}
motivates DTE analysis in program evaluation by showing why mean effects miss
individual-level gains and losses.  \citet[Section 2 and Lemma 2.3]{FanPark2010}
gives sharp pointwise DTE bounds from identified potential-outcome marginals; the
present proposal asks whether local bounds with additional restrictions are
globally realizable.  \citet[Section 2]{FirpoRidder2019} shows that pointwise
Makarov bounds are not uniformly sharp for finite DTE vectors and functionals,
which motivates a pathwise rather than pointwise sharpness criterion.
\citet[Sections 2--3]{FanWu2010} derives DTE bounds and confidence sets in
switching-regime models; this proposal keeps the switching/dose motivation but
replaces model-specific restrictions by finite lifted OT compatibility.
\citet[Sections 2--3]{FanGuerreZhu2017} studies functionals of the joint
potential-outcome distribution and when covariates shrink identified sets; this
proposal isolates the pasting obstruction that appears when multiple conditional
joint-distribution restrictions are optimized separately.  \citet{FrandsenLefgren2021}
tightens DTE bounds under mutually stochastic increasing potential outcomes and
gives testable implications; their dependence restrictions are one source of the
rank-copula tube constraints used here.  \citet[Supplementary Appendix 3]{Russell2021}
emphasizes computation of sharp bounds for joint-potential-outcome functionals;
the proposed certificate is a diagnostic for when a decomposed computation is
actually sharp.  \citet[Sections 2--3]{OberReynolds2023} characterizes endpoints
of moment-type joint-potential-outcome functionals as OT values; this proposal
targets vector DTE paths and global feasibility of many local OT values.
\citet[Sections 2--3]{TanBlanchetSyrgkanis2026} is the closest modern comparator:
it reduces a limited-IV PRTE problem to constrained conditional OT subproblems,
whereas Conjecture~\ref{conj:cycle-frontier} asks for the finite cycle condition
that makes such local subproblem solutions pasteable for DTE paths.
\citet[Section 2]{GaoGeQian2025} is the closest MOT comparator because it
formulates causal partial identification with multiple potential outcomes as an
exact multi-marginal OT problem; the present proposal differs by diagnosing when
a cheaper decomposed conditional/lifted relaxation is equal to that global MOT
problem.  \citet[Section 2]{Vorobev1962} and \citet[Chapter 3]{Kellerer1984}
are the classical marginal-compatibility anchors; the proposed object is a
DTE-facing specialization of their extension obstruction with overlap, IV/dose,
and rank-tube slack variables made operational.

In-repository, the Stage -1.1 scan reports that \texttt{doc/API.md} has no
accepted CausalSmith DTE coupling or OT pasting theorem.  Its PartialID catalogue
contains only a Manski selected-cell mean-bound wrapper, not a DTE full-data
coupling result.  The closest banked prior proposal is
\texttt{pid\_dose\_response\_iv}/\texttt{v1}, whose rejected angle explicitly
asked for a lifted optimal-transport relaxation and a pasting theorem showing
when the envelope is sharp for one full-data law.  This proposal narrows that
request to a finite DTE setting with a named cycle certificate.

\section{Formal setup}
\label{sec:setup}
Let \(\mathcal C=\{1,\ldots,C\}\) be finite cells formed by covariates,
instrument values, and dose states, with weights \(w_c>0\).  Let
\(\mathcal Y_1=\{a_1,\ldots,a_M\}\) and
\(\mathcal Y_0=\{b_1,\ldots,b_N\}\).  A local coupling table is
\(\pi_c\in\R_+^{M\times N}\).  It generates the local DTE ordinate
\[
T_{ck}(\pi_c)=\sum_{m,n}\one\{a_m-b_n\le d_k\}\pi_c(m,n),
\]
and the population path is
\(\theta_D(\pi)=\bigl(\sum_c w_cT_{c1}(\pi_c),\ldots,\sum_cw_cT_{cK}(\pi_c)\bigr)\).

The lifted relaxation \(\mathcal L(P)\) is the polytope of all local tables
\((\pi_c)_c\) satisfying the row and column overlap envelopes, the global
linear IV/dose equations \(A\pi=b(P)\), and the rank-tube rectangle inequalities
indexed by \(\mathcal R_c^{\mathrm{rank}}\).  The full-data feasible set
\(\mathcal G(P)\subseteq\mathcal L(P)\) is the subset induced by one joint law of
all latent potential outcomes, doses, instruments, and ranks whose conditional
two-dimensional margins equal the \(\pi_c\)'s.  The sharp DTE set is
\(\Theta_I(P;D)=\{\theta_D(\pi):\pi\in\mathcal G(P)\}\), while the lifted outer
set is \(\Theta_L(P;D)=\{\theta_D(\pi):\pi\in\mathcal L(P)\}\).

Every inequality in \(\mathcal L(P)\) is converted to an equality with an
explicit nonnegative slack.  For example,
\(\sum_n\pi_c(m,n)\le u^1_{cm}\) becomes
\(\sum_n\pi_c(m,n)+s^{1,+}_{cm}=u^1_{cm}\), and
\(\ell^1_{cm}\le\sum_n\pi_c(m,n)\) becomes
\(\sum_n\pi_c(m,n)-s^{1,-}_{cm}=\ell^1_{cm}\); column envelopes and both sides
of each rank-tube inequality are expanded analogously.  Let
\[
x=(\pi,s^{1,+},s^{1,-},s^{0,+},s^{0,-},s^{R,+},s^{R,-})
\quad\text{and}\quad
E_Px=h_P
\]
be the resulting equality system after adding the IV/dose equations
\(A\pi=b(P)\).  The matrix \(E_P\) is the signed incidence matrix of all local
mass variables and equality-expanded slack variables, and \(h_P\) stacks
\((u^1,\ell^1,u^0,\ell^0,\bar\pi+\rho,\bar\pi-\rho,b(P))\).
For any DTE direction \(v\), let \(\mathcal A_v(P)\) be the active-facet list:
all equality rows for IV/dose restrictions, plus those overlap and rank-tube
facets whose corresponding slack is fixed at zero at a \(v^\transpose\theta_D\)
optimizer of \(\mathcal L(P)\).  Let \(E_P^{\mathcal A}\) denote the row
submatrix on \(\mathcal A_v(P)\) after deleting the columns of slacks fixed at
zero and retaining the columns for nonactive slacks, and let
\(h_P^{\mathcal A}\) be the corresponding subvector of \(h_P\).  The global
active list for the DTE path is
\(\mathcal A_D(P)=\bigcup_{v\in\{-1,0,1\}^K}\mathcal A_v(P)\).

The full-data set is defined by a single latent-type distribution
\(\mu\in\Delta(\Omega)\), where
\[
\Omega=\prod_{c\in\mathcal C}
(\mathcal Y_1\times\mathcal Y_0\times\mathcal U_c^{\mathrm{rank}})
\times\mathcal Z^{\mathrm{dose/IV}}.
\]
There is a fixed linear margin map \(R\) such that
\(\pi_{cmn}=(R\mu)_{cmn}\).  Thus \(\mathcal G(P)=\{\pi:\exists \mu\ge0,
\mathbf 1^\transpose\mu=1,\ R\mu=\pi,\ E_Px=h_P\text{ for some }s\ge0\}\).
The local relaxation \(\mathcal L(P)\) permits the \(\pi_c\)'s to be chosen
directly in \(E_Px=h_P\), while \(\mathcal G(P)\) requires the same \(\mu\) to
generate every cell margin.  This is the precise shared-latent-variable
distinction: local rebuilds use unrelated cellwise couplings, whereas full-data
feasibility uses one common type law.

Let \(\mathsf Z_D(E_P^{\mathcal A})\) be the integer left-null cycle space
generated by primitive signed vectors \(q\) with
\(q^\transpose E_P^{\mathcal A}=0\) and whose support
contains at least one equality involving a DTE face mass
\(\sum_{a_m-b_n\le d_k}\pi_c(m,n)\).  The imbalance of such a cycle is
\[
B_P(q)=q^\transpose h_P^{\mathcal A} .
\]
The lifted-OT cycle certificate is
\[
\mathfrak C_P(D)=\max_{q\in\mathcal Q_D}|q^\transpose h_P^{\mathcal A}|,
\]
where \(\mathcal Q_D\) is the Hilbert-basis subset of primitive cycles in
\(\mathsf Z_D(E_P^{\mathcal A})\), with \(\mathcal A=\mathcal A_D(P)\).
This definition is independent of
\(\Theta_I(P;D)\): it uses only the observable right-hand side vector \(h_P\)
and the equality-expanded active incidence matrix \(E_P^{\mathcal A}\), not the
sharp set whose equality it is meant to characterize.

\begin{quote}
\textbf{Locked tuple reproduced.}
\((\texttt{qid},\texttt{specialization},P,\theta,\mathcal R,\mathcal B)
=
(\texttt{pid\_ot\_dte\_marginal},\texttt{v1},P,\theta_D,
\text{lifted marginal-overlap, IV/dose, and rank-tube restrictions},
\text{cycle-pasted OT bound})\).
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite lifted support]\label{ass:finite}
\(\mathcal C\), \(\mathcal Y_1\), \(\mathcal Y_0\), \(D\), and
\(\mathcal R_c^{\mathrm{rank}}\) are finite, and \(w_c>0\) for every cell.
\end{assumption}

\begin{assumption}[Nonempty local relaxation]\label{ass:local}
The lifted polytope \(\mathcal L(P)\) is nonempty and every local table in it has
row and column sums in the stated marginal-overlap envelopes.
\end{assumption}

\begin{assumption}[Shared-margin incidence]\label{ass:incidence}
The full-data constraints connecting local tables are exactly the shared row,
column, IV/dose, and rank-tube margins represented by the equality-expanded
active incidence matrix \(E_P^{\mathcal A}\) and the common latent-type margin
map \(R\).
\end{assumption}

\begin{assumption}[Primitive DTE cycles]\label{ass:cycles}
\(\mathcal Q_D\) is the Hilbert-basis set of primitive signed cycles in the
integer left-null space of the equality-expanded active matrix
\(E_P^{\mathcal A}\), restricted to cycles whose support intersects at least
one DTE indicator face for the grid \(D\).
\end{assumption}

\begin{assumption}[Nondegenerate witness class]\label{ass:witness}
There is an open finite-support class \(\mathcal O_{\mathrm{cycle}}\) in which
all support atoms have positive probability, each inequality slack appearing in
\(x\) is strictly positive except the witness equalities listed in
Corollary~\ref{cor:witness}, and at least one primitive DTE cycle has nonzero
observable imbalance \(q^\transpose h_P^{\mathcal A}\).
\end{assumption}

\section{Main results}
\begin{theorem}[Lifted relaxation is a valid outer DTE envelope]\label{thm:outer}
Under Assumptions~\ref{ass:finite}--\ref{ass:local},
\(\Theta_I(P;D)\subseteq\Theta_L(P;D)\).  Consequently every linear lower or
upper bound on \(v^\transpose\theta_D\) obtained by optimizing over
\(\mathcal L(P)\) is a valid, though not necessarily sharp, partial-identification
bound.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is the routine validity layer behind the rejected
\texttt{pid\_dose\_response\_iv}/\texttt{v1} request and the constrained OT
thread of \citet{TanBlanchetSyrgkanis2026}; it is included to separate validity
from sharpness.  (b) It gives users of \citet{Russell2021} and
\citet{OberReynolds2023} a safe outer envelope while the pasting frontier is
being resolved.

\begin{conjecture}[Cycle-pasting frontier for sharp lifted OT]\label{conj:cycle-frontier}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:cycles},
\[
\Theta_I(P;D)=\Theta_L(P;D)
\quad\text{if and only if}\quad
\mathfrak C_P(D)=0.
\]
When \(\mathfrak C_P(D)>0\), at least one lifted-OT optimizer for a DTE direction
\(v\in\{-1,0,1\}^K\) is not induced by any single full-data law, so the lifted
relaxation is a strict outer envelope for the DTE path.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) The closest published comparators are \citet[Section 2]{GaoGeQian2025},
which gives an exact global MOT formulation for causal partial identification,
and \citet[Sections 2--3]{TanBlanchetSyrgkanis2026}, which obtains sharp
conditional OT subproblems for PRTE means.  The epsilon-gap is a computable
necessary-and-sufficient certificate for when the decomposed lifted relaxation
equals the global full-data MOT problem for DTE paths with rank-tube and IV/dose
restrictions.  \citet[Section 2]{Vorobev1962} and
\citet[Chapter 3]{Kellerer1984} explain why marginal compatibility can fail in
abstract, but not the DTE-face, slack-expanded certificate above.  (b)
Resolving this would directly unblock the
\texttt{pid\_dose\_response\_iv}/\texttt{v1} pasting request and would tell
applied DTE users whether local constrained-OT bounds are sharp.

\begin{conjecture}[Strict frontier against finite-vector Makarov aggregation]\label{conj:firpo-frontier}
(NOT YET PROVED.)  Under Assumption~\ref{ass:witness}, there is a nonempty open
set of observable laws \(P\in\mathcal O_{\mathrm{cycle}}\) for which
\(\mathfrak C_P(D)>0\) and \(\Theta_I(P;D)\subsetneq\Theta_L(P;D)\).  The
strictness is witnessed by the \(C=3\), \(M=N=2\), \(K=2\) law in
Corollary~\ref{cor:witness}.  Hence the finite-vector local Makarov aggregation
motivated by \citet[Section 2, equations (2.1)--(2.4)]{FirpoRidder2019} is not
representable as a sharp DTE identified set once the same rank-tube and
IV/dose restrictions must be pasted through one full-data law.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet[Section 2, equations (2.1)--(2.4)]{FirpoRidder2019} show why
pointwise Makarov bounds do not automatically deliver finite-vector sharpness.
This conjecture makes the comparison a strict frontier: even if every local
DTE ordinate is Makarov-sharp, the path can be non-representable because shared
rank-tube and IV/dose restrictions create a nonzero equality-expanded cycle
imbalance.  (b) The concrete consumer is the DTE reporting workflow in
\citet{FrandsenLefgren2021}:
rank-type restrictions can tighten bounds only after checking that the local
rank restrictions paste globally.

\section{Sanity-check corollaries}
\begin{corollary}[Single-cell reduction]\label{cor:single}
Under Assumptions~\ref{ass:finite}--\ref{ass:cycles}, if \(C=1\) and there are
no IV/dose or rank-tube shared margins, then \(\mathfrak C_P(D)=0\) and
Conjecture~\ref{conj:cycle-frontier} reduces to the usual finite
Frechet--Makarov transport problem for the DTE path.
\end{corollary}

\begin{corollary}[No shared cycle reduction]\label{cor:forest}
Under Assumptions~\ref{ass:finite}--\ref{ass:cycles}, if the active incidence
matrix \(E_P^{\mathcal A}\) has no primitive DTE-touching left-null cycle, then
\(\mathcal Q_D=\varnothing\),
\(\mathfrak C_P(D)=0\), and the proposed frontier predicts no extra pasting
obstruction beyond local feasibility.
\end{corollary}

\begin{corollary}[Concrete three-cell witness template]\label{cor:witness}
Consider \(C=3\), \(M=N=2\), \(D=\{0,1\}\), \(a=(0,2)\), \(b=(0,1)\), and
\(w_c=1/3\).  In each cell impose row and column sums \((1/2,1/2)\), so every
cell has a one-dimensional diagonal-mass parameter
\(r_c=\pi_c(1,1)+\pi_c(2,2)\).  The cellwise lifted relaxation admits local
tables with
\[
r_1=3/5,\qquad r_2=3/5,\qquad r_3=1/2,
\]
and all four atoms in every \(2\times2\) table strictly positive.  The
full-data rank-sharing map \(R\), however, implies the active equality-expanded
cyclic facets
\[
r_1-r_2+s_{12}=0,\qquad
r_2-r_3+s_{23}=0,\qquad
r_3-r_1+s_{31}=1/10,
\]
with the witness slacks \(s_{12}=s_{23}=s_{31}=0\), so these slack columns are
deleted in \(E_P^{\mathcal A}\).  The primitive cycle
\(q=(1,1,1)\) therefore has \(q^\transpose E_P^{\mathcal A}=0\) and
\(B_P(q)=q^\transpose h_P^{\mathcal A}=1/10\).  Perturbing the six off-diagonal masses by
less than \(1/40\) preserves positivity and the nonzero imbalance, so this is a
non-corner witness class rather than a single degenerate table.
\end{corollary}

\section{Proof-sketch route}
The mathematical route is finite-dimensional.  First, write the full-data law as
a nonnegative tensor whose two-dimensional margins are the local tables
\(\pi_c\), and project that tensor polytope onto the local-table coordinates.
Second, compare this projection with the lifted relaxation \(\mathcal L(P)\) by
the integer cycle space of the equality-expanded incidence matrix; the expected
tools are Farkas separation, Vorob'ev--Kellerer marginal-extension
compatibility for cyclic systems, network-matrix total unimodularity in the
acyclic case, and Hilbert-basis generation for primitive cycles.  Third, show that any
separating functional between \(\Theta_I(P;D)\) and \(\Theta_L(P;D)\) can be
chosen to touch a DTE indicator face, which is why \(\mathcal Q_D\) rather than
the full cycle space should suffice.  The boundary case needing explicit algebra
is the \(C=3\), \(M=N=2\), \(K=2\) witness in
Corollary~\ref{cor:witness}: enumerate the local tables, write the
equality-expanded rank-tube equations, and compute the nonzero signed cycle
imbalance \(1/10\).

\section{Honest scope flags}
Theorem~\ref{thm:outer} is routine once the restriction classes are accepted.
Conjectures~\ref{conj:cycle-frontier} and \ref{conj:firpo-frontier} are the novel
claims and are not yet proved.  The most delicate point is Assumption~\ref{ass:incidence}:
it rules out hidden higher-order restrictions beyond the named shared margins.
If that assumption is too strong, the conjecture should be narrowed to the
explicit tensor-margin model rather than claimed for all lifted OT relaxations.
This pivot intentionally withdraws the earlier angle-0 Choquet path-envelope
claim and the angle-1 endpoint-face diagnostic claim.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for angle 2, replacing the rejected
Choquet-envelope and LP-diagnostic kernels with a lifted-OT cycle-pasting
frontier; prior verdict: none.
\item v2 (revise) -- added the equality-expanded incidence matrix, explicit
shared latent-type law, Gao--Ge--Qian and Vorob'ev--Kellerer comparators, a
Firpo--Ridder strict-frontier statement, and a concrete three-cell witness;
prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Fan and Park(2010)]{FanPark2010}
Fan, Y. and S. Park (2010).
Sharp bounds on the distribution of treatment effects and their statistical
inference.
\emph{Econometric Theory} 26(3), 931--951.

\bibitem[Fan and Wu(2010)]{FanWu2010}
Fan, Y. and J. Wu (2010).
Partial identification of the distribution of treatment effects in switching
regime models and its confidence sets.
\emph{Review of Economic Studies} 77(3), 1002--1041.

\bibitem[Fan, Guerre, and Zhu(2017)]{FanGuerreZhu2017}
Fan, Y., E. Guerre, and D. Zhu (2017).
Partial identification of functionals of the joint distribution of potential
outcomes.
\emph{Journal of Econometrics} 197(1), 42--59.

\bibitem[Firpo and Ridder(2019)]{FirpoRidder2019}
Firpo, S. and G. Ridder (2019).
Partial identification of the treatment effect distribution and its functionals.
\emph{Journal of Econometrics} 213(1), 210--234.

\bibitem[Frandsen and Lefgren(2021)]{FrandsenLefgren2021}
Frandsen, B. R. and L. J. Lefgren (2021).
Partial identification of the distribution of treatment effects with an
application to the Knowledge Is Power Program.
\emph{Quantitative Economics} 12(1), 143--171.

\bibitem[Gao, Ge, and Qian(2025)]{GaoGeQian2025}
Gao, Z., S. Ge, and J. Qian (2025).
Bridging multiple worlds: Multi-marginal optimal transport for causal
partial-identification problem.
\emph{Proceedings of The 28th International Conference on Artificial
Intelligence and Statistics}, PMLR 258, 721--729.  Earlier version:
arXiv:2406.07868.

\bibitem[Heckman, Smith, and Clements(1997)]{HeckmanSmithClements1997}
Heckman, J. J., J. Smith, and N. Clements (1997).
Making the most out of programme evaluations and social experiments: Accounting
for heterogeneity in programme impacts.
\emph{Review of Economic Studies} 64(4), 487--535.

\bibitem[Kellerer(1984)]{Kellerer1984}
Kellerer, H. G. (1984).
Duality theorems for marginal problems.
In G. Kallianpur, P. R. Krishnaiah, and J. K. Ghosh (eds.),
\emph{Probability Measures on Groups}, Lecture Notes in Mathematics 1064,
211--251. Springer.

\bibitem[Makarov(1981)]{Makarov1981}
Makarov, G. D. (1981).
Estimates for the distribution function of a sum of two random variables when
the marginal distributions are fixed.
\emph{Theory of Probability and its Applications} 26(4), 803--806.

\bibitem[Ober-Reynolds(2023)]{OberReynolds2023}
Ober-Reynolds, D. (2023).
Partial identification of functionals of the joint distribution of potential
outcomes via optimal transport.
\emph{arXiv:2311.09435}.

\bibitem[Rueschendorf(1982)]{Rueschendorf1982}
Rueschendorf, L. (1982).
Random variables with maximum sums.
\emph{Advances in Applied Probability} 14(3), 623--632.

\bibitem[Russell(2021)]{Russell2021}
Russell, T. M. (2021).
Sharp bounds on functionals of the joint distribution in the analysis of
treatment effects.
\emph{Journal of Business \& Economic Statistics} 39(2), 532--546.

\bibitem[Tan, Blanchet, and Syrgkanis(2026)]{TanBlanchetSyrgkanis2026}
Tan, Z., J. Blanchet, and V. Syrgkanis (2026).
Policy-relevant treatment effect partial identification under limited
instrumental-variable support via constrained conditional optimal transport.
\emph{arXiv:2604.12263}.

\bibitem[Vorob'ev(1962)]{Vorobev1962}
Vorob'ev, N. N. (1962).
Consistent families of measures and their extensions.
\emph{Theory of Probability and Its Applications} 7(2), 147--163.
\end{thebibliography}

\end{document}
