\paragraph{Refutation note.}
Motivating conjecture restated verbatim:
Under Assumptions~\ref{ass:finite-overlap}--\ref{ass:cycle-margin}, the lifted OT relaxation is sharp for the DTE tail probability at \(d\),
\[
\Theta_I(P,d)=\Theta_L(P,d),
\]
if and only if the endpoint-normalized cycle-balance defect satisfies \(\Gamma(P,d)=0\).  Moreover, if \(\Gamma(P,d)>0\), then at least one endpoint of \(\Theta_L(P,d)\) differs from the corresponding sharp endpoint of \(\Theta_I(P,d)\) by at least \(\kappa_*(P,d)\Gamma(P,d)\).

Conjecture 1 is refuted: in the one-cell binary-outcome response-type LP below, \(\Gamma(P,0)=0\) but \(\Theta_I(P,0)=[4/5,1]\) and \(\Theta_L(P,0)=[2/5,1]\).
The failure is not a cycle-pasting failure.  It is a factual-compatibility failure: the lifted program optimizes over potential-outcome marginal envelopes and a cellwise coupling, while the sharp full-law program must also decompose that coupling across the treated and untreated factual strata so that \(Y=DY(1)+(1-D)Y(0)\) reproduces the observed law \(P\).

\paragraph{Section 13 refutation attempt and counterexample.}
The required refutation primitive is the response-type LP on the smallest nontrivial support.  Take a single observed cell \(Z=0\), \(X=x\), binary outcome support \(\mathcal Y=\{0,1\}\), and threshold \(d=0\).  Let the observed law be
\[
\begin{array}{c|cc}
 & Y=0 & Y=1\\ \hline
D=1 & 4/10 & 1/10\\
D=0 & 1/10 & 4/10
\end{array}
\]
so \(P(Z=0,X=x)=1\).  There are no IV or dose links across cells.  The local copula tube is unrestricted, \(\mathcal C_{\rho,x}=\Pi(\mu_{1,x},\mu_{0,x})\), and the only marginal envelopes are the no-shape factual envelopes
\[
\mu_{1,x}(1)\in[1/10,6/10],
\qquad
\mu_{0,x}(0)\in[1/10,6/10].
\]
These are nonempty closed convex polytopes and they contain every potential-outcome marginal compatible with the displayed observed law.  Add, if a positive inactive-slack table is desired for Assumption~\ref{ass:cycle-margin}, the redundant inequalities
\[
\mu_{1,x}(1)\le 7/10,\qquad \mu_{0,x}(0)\le 7/10,
\]
which do not change either feasible set and have slack at least \(1/10\) at every feasible marginal-envelope vertex used below.  Because there is only one observed cell and no shared cross-cell equality or active inequality, the pasting graph has no simple cycle.  Hence the endpoint-normalized cycle-balance defect is the maximum over an empty cycle set:
\[
\Gamma(P,0)=0.
\]

Now enumerate the four binary response types \((Y(1),Y(0))\in\{0,1\}^2\) separately in the treated and untreated factual strata.  Write
\[
q^d_{ij}=Q\{Y(1)=i,Y(0)=j,D=d,Z=0,X=x\},
\qquad i,j,d\in\{0,1\}.
\]
The observed law and consistency impose exactly
\[
\begin{aligned}
q^1_{10}+q^1_{11}&=1/10, &
q^1_{00}+q^1_{01}&=4/10,\\
q^0_{00}+q^0_{10}&=1/10, &
q^0_{01}+q^0_{11}&=4/10,
\end{aligned}
\]
with all \(q^d_{ij}\ge0\).  For \(d=0\), the DTE tail event is false only for response type \((Y(1),Y(0))=(1,0)\).  Therefore
\[
Q\{Y(1)-Y(0)\le0\}=1-q^1_{10}-q^0_{10}.
\]
The two observed equations that can contain type \((1,0)\) give
\[
q^1_{10}\le 1/10,
\qquad
q^0_{10}\le 1/10,
\]
so every admissible full-data law satisfies
\[
Q\{Y(1)-Y(0)\le0\}\ge 1-1/10-1/10=4/5.
\]
This lower endpoint is attained by setting \(q^1_{10}=q^0_{10}=1/10\), \(q^1_{01}=4/10\), and \(q^0_{01}=4/10\).  The upper endpoint is attained by setting \(q^1_{11}=1/10\), \(q^1_{00}=4/10\), \(q^0_{00}=1/10\), and \(q^0_{01}=4/10\), which makes \(q^1_{10}=q^0_{10}=0\).  Thus the sharp full-law identified interval is
\[
\Theta_I(P,0)=[4/5,1].
\]

The lifted relaxation drops the treated/untreated decomposition variables \(q^d_{ij}\).  Its lower endpoint chooses the marginal-envelope vertex
\[
\mu_{1,x}(1)=6/10,\qquad \mu_{0,x}(0)=6/10,
\]
and then puts as much coupling mass as possible on the sole tail-failing cell \((1,0)\):
\[
\pi_x(1,0)=6/10,\qquad \pi_x(0,1)=4/10,
\]
with all other entries zero.  This is a feasible element of \(\mathcal L(P)\), so
\[
\theta_L^\ell(P,0)\le 1-6/10=2/5.
\]
Conversely, no lifted coupling can put more than
\[
\min\{\mu_{1,x}(1),\mu_{0,x}(0)\}\le 6/10
\]
on \((1,0)\), by the coupling marginal equations.  Hence \(\theta_L^\ell(P,0)=2/5\).  The lifted upper endpoint equals one: choose \(\mu_{1,x}(1)=1/10\), \(\mu_{0,x}(0)=1/10\), and a coupling with \(\pi_x(1,0)=0\), for instance
\[
\pi_x(0,0)=1/10,\qquad \pi_x(0,1)=8/10,\qquad \pi_x(1,1)=1/10.
\]
Therefore
\[
\Theta_L(P,0)=[2/5,1].
\]

The candidate witness search thus produces a strict violation of the conjectured ``if and only if'' direction:
\[
\Gamma(P,0)=0
\quad\text{but}\quad
\Theta_I(P,0)=[4/5,1]\ne[2/5,1]=\Theta_L(P,0).
\]
The nearest correct statement would need an additional factual-compatibility restriction saying that every lifted marginal-and-coupling collection admits a nonnegative response-type decomposition \(q^d_{ij}\) matching the observed \((Y,D,Z,X)\) law.  That condition is regime-defining rather than a slack caveat: it is exactly the missing global full-law compatibility that separates the sharp program \(\Theta_I\) from the lifted relaxation \(\Theta_L\) in this witness.
