\section{Positive loss and sharp computation}

The preceding section identifies two implementable covariances that can solve the relaxed problem exactly. We now study relaxed points in \(\mathcal E_m^{\mathrm{blk}}\) lying beyond the covariances attainable by balanced \(\{\pm1\}\) assignment laws. This is the same basic tension that appears in correlation and semidefinite relaxations more broadly: the convex benchmark can contain exposed points beyond the original discrete objects \citep{goemans1995,deza1997,boyd2004}. In the present two-block design problem, the obstruction is finite and arithmetical. When \(m\) is odd, each realized block sum has odd parity, imposing a positive-mass restriction away from the pure within-block spectral direction.

The next result gives a parameter region in which this obstruction is binding. It uses the low-scale condition from \cref{obj:ass:low-scale-two-block} and the odd-block condition from \cref{obj:ass:odd-community-size}. The relevant relaxed covariance is the spread covariance \(X_{\mathrm{spread}}\), the vertex with spectral coordinates \((m/(m-1),0,0)\). In a nonempty interval of pseudoinverse weights, this point is uniquely relaxed-optimal and lies outside the implementable covariance class.

\begin{theoremv}{thm:gap-window}[Positive-Gap Window]
Suppose \cref{obj:ass:two-block-homophily} and \cref{obj:ass:low-scale-two-block} hold for the two-block model with block size \(m\) and weights \(a,b\). Let
\[
q=2(m-1),\qquad
\kappa_{\mathrm{gap}}(m,a,b)
=
\frac{(2m-a-3b)(a-b)\sqrt q}{a+b},
\]
and
\[
r_{\mathrm{cut,gap}}(m,a,b,\kappa)
=
\max\left\{0,\;2b(a+b)\left(1-\frac{\kappa}{a-b}\right)\right\}.
\]
Define
\[
R_x^-(m,a,b,\kappa)
=
2b(a+b)\left(1+\frac{\kappa}{(a-b)\sqrt q}\right),
\qquad
R_x^+(m,a,b,\kappa)
=
(a+b)\left(2m-a-b-\frac{\kappa}{\sqrt q}\right),
\]
and
\[
r_{\mathrm{gap}}^-(m,a,b,\kappa)
=
\frac{R_x^-(m,a,b,\kappa)+R_x^+(m,a,b,\kappa)}{2},
\qquad
r_{\mathrm{gap}}^+(m,a,b,\kappa)
=
R_x^+(m,a,b,\kappa).
\]

Then the following two statements hold.
\begin{itemize}
\item \textbf{(Odd block size.)} If \cref{obj:ass:odd-community-size} holds, then for every \(\kappa\) satisfying
\[
0\le \kappa < \kappa_{\mathrm{gap}}(m,a,b),
\]
one has
\[
r_{\mathrm{cut,gap}}(m,a,b,\kappa)
<
r_{\mathrm{gap}}^-(m,a,b,\kappa)
<
r_{\mathrm{gap}}^+(m,a,b,\kappa).
\]
Moreover, for every
\[
r_{\mathrm{gap}}^-(m,a,b,\kappa)
<
r
<
r_{\mathrm{gap}}^+(m,a,b,\kappa),
\]
the spread covariance \(X_{\mathrm{spread}}\) belongs to \(\mathcal E_m^{\mathrm{blk}}\), and it is the unique strict minimizer of the design objective \(F_{r,\kappa}\) from \cref{obj:def:design-objective} over \(\mathcal E_m^{\mathrm{blk}}\): for every \(X\in \mathcal E_m^{\mathrm{blk}}\) with \(X\ne X_{\mathrm{spread}}\),
\[
F_{r,\kappa}(X_{\mathrm{spread}})<F_{r,\kappa}(X).
\]
At the same time,
\[
X_{\mathrm{spread}}\notin \mathcal C_m^{\pm},
\]
where \(\mathcal C_m^{\pm}\) is the implementable covariance class of \cref{obj:def:implementable-covariance-class}, and the implementability loss of \cref{obj:def:implementability-gap} satisfies
\[
\Delta_m^{\pm}(r,\kappa)>0.
\]

\item \textbf{(Even block size.)} If \(m\) is even, then every covariance in the block elliptope is implementable:
\[
\mathcal E_m^{\mathrm{blk}}\subseteq \mathcal C_m^{\pm}.
\]
\end{itemize}
\end{theoremv}

\cref{obj:thm:gap-window} is the paper's positive-loss statement. For odd \(m\), the upper bound \(\kappa_{\mathrm{gap}}(m,a,b)\) defines a robustness range in which the interval \((r_{\mathrm{gap}}^-,r_{\mathrm{gap}}^+)\) is nonempty and lies strictly beyond the cut-side comparison threshold \(r_{\mathrm{cut,gap}}\). Inside that interval, the spread covariance is the unique strict minimizer over \(\mathcal E_m^{\mathrm{blk}}\) and lies outside \(\mathcal C_m^{\pm}\). Imposing implementability therefore raises the objective value, giving \(\Delta_m^{\pm}(r,\kappa)>0\).

The even-\(m\) clause marks the opposite parity case. When each block can have zero sign sum, every relaxed covariance in the block elliptope slice is generated by some block-exchangeable sign law. Thus \cref{obj:thm:gap-window} ties positive loss specifically to the odd-block parity restriction.

The interval result identifies an interpretable open region where the spread covariance is the relaxed optimum and the loss is strictly positive. For arbitrary \(r\) and \(\kappa\), the sharp finite active-set formula below supplies the global computation. The formula works in the reduced spectral simplex \(T_m\), with objective \(\phi_{r,\kappa}\), and with a parity truncation \(d_m\) that is zero for even block sizes and \(2/m\) for odd block sizes.

\begin{theoremv}{thm:sharp-rho-star}[Sharp Rounding Loss]
Under \cref{obj:ass:two-block-homophily}, fix $r,\kappa\in[0,\infty)$.  Let
\[
q=2(m-1),\qquad
c_x=q\Bigl((a+b)+\frac{r}{a+b}\Bigr),\qquad
c_y=2b+\frac{r}{2b},\qquad
c_z=2m,
\]
let
\[
T_m=\{(x,y,z_{\mathrm{sp}}):x,y,z_{\mathrm{sp}}\ge0,\ qx+y+z_{\mathrm{sp}}=2m\},
\]
let
\[
\phi_{r,\kappa}(x,y,z_{\mathrm{sp}})
=c_xx+c_yy+c_zz_{\mathrm{sp}}
+\kappa\sqrt{qx^2+y^2+z_{\mathrm{sp}}^2},
\]
and let $d_m=0$ if $m$ is even and $d_m=2/m$ if $m$ is odd.  Then:
\begin{itemize}
\item \textbf{(Sharp equality and range.)}
\[
\rho_\star(m,a,b,r,\kappa)=\Delta_m^{\pm}(r,\kappa),
\qquad
\rho_\star(m,a,b,r,\kappa)\ge0,
\qquad
\Delta_m^{\pm}(r,\kappa)\ge0,
\]
where $\Delta_m^{\pm}$ is the implementability gap of \cref{obj:def:implementability-gap}.

\item \textbf{(Zero loss.)}
\[
\rho_\star(m,a,b,r,\kappa)=0
\]
if and only if there exists $(x,y,z_{\mathrm{sp}})\in T_m$ such that
\[
\phi_{r,\kappa}(x,y,z_{\mathrm{sp}})
\le
\phi_{r,\kappa}(x',y',z'_{\mathrm{sp}})
\quad\text{for every }(x',y',z'_{\mathrm{sp}})\in T_m,
\]
and
\[
d_m\le y+z_{\mathrm{sp}}.
\]

\item \textbf{(Strict robustness.)}
If $\kappa>0$, then there is a unique relaxed minimizer of $\phi_{r,\kappa}$ over $T_m$.  Moreover,
\[
\rho_\star(m,a,b,r,\kappa)=0
\]
if and only if every relaxed minimizer $(x,y,z_{\mathrm{sp}})\in T_m$ satisfies
\[
d_m\le y+z_{\mathrm{sp}}.
\]

\item \textbf{(Linear case.)}
If $\kappa=0$, then for every $(x,y,z_{\mathrm{sp}})\in T_m$, the point $(x,y,z_{\mathrm{sp}})$ minimizes $\phi_{r,0}$ over $T_m$ if and only if
\[
x\ne0\Rightarrow \frac{c_x}{q}\le c_y\ \text{and}\ \frac{c_x}{q}\le c_z,
\]
\[
y\ne0\Rightarrow c_y\le \frac{c_x}{q}\ \text{and}\ c_y\le c_z,
\]
and
\[
z_{\mathrm{sp}}\ne0\Rightarrow c_z\le \frac{c_x}{q}\ \text{and}\ c_z\le c_y.
\]

\item \textbf{(Active-set formula.)}
If $\kappa>0$, then there exist an active support $S\subseteq\{x,y,z_{\mathrm{sp}}\}$ and a multiplier $\lambda\in\mathbb R$ such that $S$ and $\lambda$ are admissible for
\[
\alpha^\sharp=\Bigl(\frac{c_x}{q},c_y,c_z\Bigr),
\qquad
\beta^\sharp=\Bigl(\frac1q,1,1\Bigr),
\qquad
\kappa.
\]
Writing $t^{S,\lambda}=(t_x^{S,\lambda},t_y^{S,\lambda},t_z^{S,\lambda})$ for the associated active-set point on the simplex of mass $2m$, the reduced point
\[
\Bigl(\frac{t_x^{S,\lambda}}{q},t_y^{S,\lambda},t_z^{S,\lambda}\Bigr)
\]
belongs to $T_m$, minimizes $\phi_{r,\kappa}$ over $T_m$, and the relaxed reduced value is
\[
2m\,\lambda.
\]

\item \textbf{(Truncation correction.)}
If no relaxed minimizer $(x,y,z_{\mathrm{sp}})\in T_m$ satisfies $d_m\le y+z_{\mathrm{sp}}$, then the implementable reduced value equals the weighted-simplex objective with coefficients $\alpha^\sharp$, weights $\beta^\sharp$, and robustness weight $\kappa$, evaluated at the point on the truncation segment
\[
H_{d_m}=\{(2m-d_m,s,d_m-s):0\le s\le d_m\}
\]
selected by $\operatorname{truncSelector}(2m,d_m,\alpha^\sharp,\beta^\sharp,\kappa)$:
\[
\operatorname{val}_{\mathrm{impl}}(m,a,b,r,\kappa)
=
\Phi_{\alpha^\sharp,\beta^\sharp,\kappa}
\!\left(
2m-d_m,\,
s_\star,\,
d_m-s_\star
\right),
\]
where
\[
s_\star=\operatorname{truncSelector}(2m,d_m,\alpha^\sharp,\beta^\sharp,\kappa).
\]

\item \textbf{(Even block size.)}
If $m$ is even, then
\[
\rho_\star(m,a,b,r,\kappa)=0.
\]
\end{itemize}
\end{theoremv}

\cref{obj:thm:sharp-rho-star} turns the implementability question into a finite exact calculation: the sharp loss $\rho_\star(m,a,b,r,\kappa)$ equals \(\Delta_m^{\pm}(r,\kappa)\). Zero loss occurs precisely when at least one relaxed minimizer satisfies the parity-induced lower bound \(d_m\le y+z_{\mathrm{sp}}\). When \(\kappa>0\), strict convexity of the norm term gives a unique relaxed minimizer, and the zero-loss condition can be checked at that point alone.

The active-set part supplies the promised finite case split. The coefficients \(\alpha^\sharp=(c_x/q,c_y,c_z)\) and weights \(\beta^\sharp=(1/q,1,1)\) convert the reduced objective into a weighted simplex problem over total mass \(2m\). For positive robustness, an admissible support \(S\) and multiplier \(\lambda\) identify the relaxed minimizer and its value. If that minimizer violates the implementability truncation, the remaining optimization is one-dimensional: the implementable value is obtained on the segment \(H_{d_m}\) by the selector appearing in \cref{obj:thm:sharp-rho-star}. The theorem thereby gives a complete finite procedure for computing \(\Delta_m^{\pm}(r,\kappa)\) for any admissible \(m,a,b,r,\kappa\).

The two main results in this section therefore play complementary roles. \Cref{obj:thm:gap-window} provides an interpretable open region in which the relaxation has a strictly unattainable optimum for odd block sizes. \Cref{obj:thm:sharp-rho-star} gives the exact loss everywhere under \cref{obj:ass:two-block-homophily}, including the linear case \(\kappa=0\), the unique-minimizer case \(\kappa>0\), and the even-block case where the loss vanishes. For interference-aware randomized design, the practical implication is a two-step calculation: solve the covariance relaxation, then check its optimizer against the finite sign-assignment restrictions and apply the exact active-set adjustment when needed.
