\section{Appendix B. Verification note}

This appendix records the verification boundary for the mathematical claims used in the paper. The formal statements take the assignment law, its induced second moments, the two-block weighted graph, the block elliptope relaxation, and the finite comparison between relaxed and implementable covariance optima as their load-bearing objects. The design-based finite-population potential-outcome framework supplies the surrounding motivation.

The verified mathematical layer consists of the assumptions, definitions, lemmas, and theorems stated in the paper. In particular, it includes the two-block homophily, sign-symmetry, low-scale, and odd-block conditions in \cref{obj:ass:two-block-homophily}--\cref{obj:ass:odd-community-size}; the graph, design-class, covariance, objective, loss, and block-sum definitions in \cref{obj:def:two-block-graph}--\cref{obj:def:block-sum-handle}; the symmetry reduction in \cref{obj:prop:symmetry-reduction}; the exactness results in \cref{obj:thm:cut-corner-exactness} and~\cref{obj:thm:robust-corner-exactness}; and the positive-loss and sharp-computation results in \cref{obj:thm:gap-window} and~\cref{obj:thm:sharp-rho-star}. The auxiliary reductions collected in Appendix~A are part of the same mathematical layer.

The econometric motivation, related-work positioning, and interpretation are prose surrounding that layer. The displayed assumptions in the paper give exactly the conditions used to derive the formal conclusions, which are finite-dimensional and design based.

For reproducibility, the theorem statements and proofs are machine-checked in Lean~4. The assumed inputs to the checked arguments are the explicitly stated mathematical hypotheses, including the two-block homophily, sign-symmetry, low-scale, odd-block, and nonnegativity conditions where they appear; standard finite-dimensional real matrix primitives for traces, positive semidefiniteness, the Moore--Penrose pseudoinverse, and the Schatten--2 norm; and the usual classical real-analysis and finite-set principles available in the underlying library. The Lean verification discharges the algebraic, convex-geometric, spectral, parity, and active-set claims stated in the formal environments, while the historical, empirical, and interpretive material remains prose.
