% Fragment for Conjecture 2 (label=escape).  This file intentionally has
% no preamble and no document environment.

\begin{proposition}[Partial result for Conjecture 2: explicit augmented-affine escape]\label{prop:escape-partial}
\emph{Motivating conjecture restated verbatim.}
Under Assumptions~\ref{ass:consistency}, \ref{ass:monotone}, \ref{ass:qif}, \ref{ass:topology}, \ref{ass:rank}, \ref{ass:exactfit}, \ref{ass:convexfit}, and \ref{ass:affineinterior}, there is a nonempty relatively \(d_\infty\)-open set of observable donor/pre-period/post-donor quantile panels \(P\) for which the post-period donor quantile vector \(z(u)\notin\operatorname{rowspan}\bar X(u)\) on a positive-measure set of ranks.  Equivalently, there is an affine null direction \(h(u)\) with \(\one^\transpose h(u)=0\), \(X(u)h(u)=0\), and \(z(u)^\transpose h(u)\ne0\).  On this relative open set, two convex-compatible donor-weight systems that admit global rank-invariant quantile-factor representations agree on \(P\) but imply different monotone \(Q^0_{0s}\), so point identification fails even when a convex distributional synthetic-control weight vector fits all pre-period quantiles.

\emph{Partial headline.}
Partial verdict for Conjecture 2: the finite-dimensional augmented-affine escape is witnessed by an explicit \(J=3,T_0=1,R=2\) quantile panel with two convex-compatible global rank-invariant representations, but the full relatively \(d_\infty\)-open global monotone-selection claim is not proved under the stated assumptions.
\end{proposition}

\paragraph{Refutation attempt before proof.}
The refutation primitive used here is the smallest finite-support analogue of the three-node search: one treated unit, three donors, one pre-period, and one post-period.  The search space fixes \(J=3\), \(T_0=1\), \(R=2\), and a bounded strictly increasing base quantile \(H(u)=u\).  The candidate observable panel has
\[
X(u)=\begin{pmatrix}H(u)&H(u)+1&H(u)+2\end{pmatrix},\qquad
x_0(u)=H(u)+1,\qquad
z(u)=\begin{pmatrix}H(u)&H(u)&H(u)+1\end{pmatrix}^\transpose .
\]
The affine null direction \(h=(1,-2,1)^\transpose\) gives
\[
\one^\transpose h=0,\qquad X(u)h=H(u)-2\{H(u)+1\}+\{H(u)+2\}=0,\qquad z(u)^\transpose h=1.
\]
Thus the primitive does not produce a counterexample to the conjecture's finite-dimensional escape claim; it produces the advertised escape.  The finite-support overlap violation primitive is not the right obstruction in this deterministic quantile-panel setup because the relevant positivity analogue is \(\mathcal{W}_C(P,u)\ne\emptyset\) with relative interior, and this candidate has a nondegenerate convex feasible segment at every rank.  The graphical rule trace is also vacuous here: the identifying question is not a back-door, front-door, or instrument adjustment step, but whether the observed quantile panel fixes the missing post-period loading functional.  The attempted refutation therefore fails at the algebraic level.  The remaining issue is not a finite witness against row-span escape; it is the stronger global claim that an entire relatively \(d_\infty\)-open neighborhood has two monotone-admissible common-loading completions.

\paragraph{Interpretation.}
The calculation isolates the mechanism behind the conjecture.  Exact convex pre-period distributional fit says that the treated pre-period quantile can be written as a convex donor combination at each rank.  It does not by itself say that the donor post-period linear functional \(z(u)^\transpose w\) is constant on the same feasible set.  If a null direction \(h\) preserves the affine pre-period constraints but changes \(z(u)^\transpose w\), then two observationally equivalent donor-weight systems can agree on every observed donor cell and on every treated pre-period cell while assigning different untreated post-period quantiles to the treated unit.

The explicit witness below verifies that this failure is not a boundary artifact of the donor simplex.  Both weights used in the construction are strictly inside the feasible convex segment, and both induced post-period curves are valid quantile functions.  What remains only partial is the conjecture's openness claim after imposing the full global common-loading and monotone-selection restrictions.  Assumption~\ref{ass:exactfit} gives at least one global compatible system, Assumption~\ref{ass:convexfit} gives rank-wise convex feasibility, and Assumption~\ref{ass:affineinterior} gives rank-wise perturbation room.  None of those assumptions, as written, states that the perturbation can be selected across ranks as two finite, left-continuous, nondecreasing post-period quantile functions while also preserving common unit loadings.

\begin{proof}[Proof of the partial result]
Let \(H(u)=u\) on \((0,1)\).  Define donor loadings
\[
b_1=(0,0)^\transpose,\qquad b_2=(1,0)^\transpose,\qquad b_3=(2,1)^\transpose,
\]
and period-rank factors
\[
m_1(u)=m_s(u)=H(u),\qquad \ell_1(u)=(1,0)^\transpose,\qquad \ell_s(u)=(0,1)^\transpose .
\]
For donor \(j\), the rank-invariant quantile-factor equations give
\[
Q^0_{j1}(u)=H(u)+\ell_1(u)^\transpose b_j,\qquad
Q^0_{js}(u)=H(u)+\ell_s(u)^\transpose b_j.
\]
Hence the observed donor pre-period vector and donor post-period vector are exactly
\[
X(u)=\begin{pmatrix}H(u)&H(u)+1&H(u)+2\end{pmatrix},\qquad
z(u)=\begin{pmatrix}H(u)&H(u)&H(u)+1\end{pmatrix}^\transpose .
\]

For each \(r\in[0,1/2]\), set
\[
w(r)=\begin{pmatrix}r\\ 1-2r\\ r\end{pmatrix},\qquad b_0(r)=\sum_{j=1}^3 w_j(r)b_j=(1,r)^\transpose .
\]
The weights are convex because their coordinates are nonnegative and sum to one.  The treated pre-period quantile generated by \(b_0(r)\) is
\[
m_1(u)+\ell_1(u)^\transpose b_0(r)=H(u)+1,
\]
which is independent of \(r\).  Thus the same observed treated pre-period quantile \(x_0(u)=H(u)+1\) is matched by every \(w(r)\).  The corresponding untreated treated post-period quantile is
\[
q_r(u)=m_s(u)+\ell_s(u)^\transpose b_0(r)=H(u)+r=z(u)^\transpose w(r).
\]
Each \(q_r\) is finite, continuous, and nondecreasing, so it is admissible under Assumption~\ref{ass:monotone}.

Choose \(r_- =1/8\) and \(r_+=3/8\).  Then
\[
w^-=\begin{pmatrix}1/8\\3/4\\1/8\end{pmatrix},\qquad
w^+=\begin{pmatrix}3/8\\1/4\\3/8\end{pmatrix}
\]
are both in the relative interior of the convex feasible segment
\[
\mathcal{W}_C(P,u)=\{w(r):0\le r\le 1/2\}
\]
for every \(u\).  They produce the two monotone post-period quantile curves
\[
q_-(u)=H(u)+1/8,\qquad q_+(u)=H(u)+3/8,
\]
which differ by \(1/4\) at every rank.  The two systems have the same donor loadings, the same period-rank factors, the same observed donor quantile panel, and the same treated pre-period quantile panel.  They differ only in the unobserved treated post-period loading coordinate.  By Theorem~\ref{thm:sharp-set}, both \(q_-\) and \(q_+\) are attainable untreated post-period quantile functions for data-generating processes matching the same observed law \(P\).  Therefore \(Q^0_{0s}\) is not point identified at this panel.

The row-span certificate is the displayed null-vector calculation.  Equivalently,
\[
\det\begin{pmatrix}
1&1&1\\
H(u)&H(u)+1&H(u)+2\\
H(u)&H(u)&H(u)+1
\end{pmatrix}
=z(u)^\transpose h=1
\]
for every \(u\in(0,1)\).  Since the determinant is a continuous polynomial in the three donor pre-period coordinates and the three donor post-period coordinates, there is an \(\varepsilon>0\) such that every admissible panel \(P'\) within \(d_\infty\)-distance \(\varepsilon\) of this panel and with the same \(J=3,T_0=1\) coordinate layout satisfies
\[
\operatorname*{ess\,inf}_{u\in(0,1)}
\left|
\det\begin{pmatrix}
1&1&1\\
X'_1(u)&X'_2(u)&X'_3(u)\\
z'_1(u)&z'_2(u)&z'_3(u)
\end{pmatrix}
\right|>0.
\]
On that relatively open neighborhood, \(z'(u)\notin\operatorname{rowspan}\bar X'(u)\) for a.e. \(u\), and hence an affine null direction \(h'(u)\) with \(z'(u)^\transpose h'(u)\ne0\) exists rank by rank.

This proves the finite-dimensional and determinant-stable part of the conjecture.  It does not prove the final sentence of the conjecture for the whole neighborhood.  The proof above uses a fixed loading direction that is invisible to the single pre-period factor and visible to the post-period factor.  A general \(d_\infty\)-small perturbation inside the admissible observable-panel subspace may preserve rank-wise row-span failure while changing the global common-loading equations or the cross-rank monotonicity of separated selections.  The stated assumptions do not contain a separate stability condition that rules out that possibility.  The honest verdict is therefore partial, not confirmed.
\end{proof}

\paragraph{Sanity check.}
In the common-shape mean corner, if the same convex loading represents the treated unit in every compatible factorization as in Theorem~\ref{thm:convex-sufficient}, the escape disappears.  Algebraically, the post-period donor vector is then affine in the same loading coordinate used by the pre-period fit, so every \(h\) with \(\one^\transpose h=0\) and \(X(u)h=0\) also satisfies \(z(u)^\transpose h=0\).  In the explicit witness, the opposite happens: the post-period factor uses a second loading coordinate that the pre-period factor does not see.  Integrating the two valid quantile curves gives
\[
\int_0^1 q_+(u)\,du-\int_0^1 q_-(u)\,du
=\int_0^1\{H(u)+3/8-H(u)-1/8\}\,du
=1/4,
\]
so the distributional nonidentification also produces mean nonidentification in this deliberately non-stable-loading corner.

\paragraph{Counterexample and minimality check.}
The affine null dimension is necessary.  If \(J=2\) and \(T_0=1\) with noncollapsed donor pre-period quantiles, then
\[
\bar X(u)=\begin{pmatrix}1&1\\ X_1(u)&X_2(u)\end{pmatrix}
\]
has full column rank for a.e. \(u\).  Its row span is all of \(\R^2\), so every donor post vector \(z(u)\in\R^2\) lies in \(\operatorname{rowspan}\bar X(u)\), the affine feasible set is a singleton, and there is no nonzero \(h\) with \(\bar X(u)h=0\).  Thus exact convex pre-period fit alone cannot generate the escape; one needs an affine feasible face with a post-period functional that is nonconstant on that face.

The row-span failure is also necessary for the donor-weight obstruction.  If \(z(u)=\bar X(u)^\transpose a(u)\) for some \(a(u)\), then every feasible \(w\) obeys
\[
z(u)^\transpose w=a(u)^\transpose\bar X(u)w=a(u)^\transpose\bar x_0(u),
\]
so changing weights within \(\mathcal{W}_C(P,u)\) cannot change the post-period donor-weight value.  This is exactly the condition that fails in the explicit witness.  The unresolved minimality issue is global rather than rank-wise: an additional theorem would be needed to show that rank-wise separated convex weights can always be lifted, on a relatively open set, to two monotone-admissible global common-loading systems.
