% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_heavy\_tail\_cate\_bounds, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_heavy\_tail\_cate\_bounds} / \texttt{v1}%
  \\ \large Pareto-extremal coupling representation of the MSM($\Gamma$) sharp CATE upper endpoint under finite-$\alpha$-moment outcomes, with Kallus--Mao--Zhou recovered as $\alpha\to\infty$ limit and strict tightening over Aronow--Lee at every finite $\alpha>1$.}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{itemize}[leftmargin=*]
  \item \texttt{qid} = \texttt{pid\_heavy\_tail\_cate\_bounds}; \texttt{specialization} = \texttt{v1}. Anchor cluster: partial identification.
  \item Observable distribution $P$: joint law of $(Y, A, X)$ on $\R \times \{0,1\} \times \mathcal{X}$ with $Y$ a real-valued outcome (\emph{not} assumed bounded), $A \in \{0,1\}$ binary treatment, $X \in \mathcal{X}$ covariates. Sampling iid from $P$.
  \item Latent confounder $U$ taking values in a Polish space $\mathcal{U}$; potential outcomes $\{Y(0), Y(1)\}$ with $Y = Y(A)$ (consistency); $A \perp \{Y(0), Y(1)\} \mid (X, U)$ (latent unconfoundedness).
  \item Parameter $\theta = \tau(x) := \E[Y(1) - Y(0) \mid X = x]$, the conditional average treatment effect (CATE).
  \item Identifying restrictions:
    \begin{enumerate}[label=(R\arabic*)]
      \item Strict overlap of the nominal propensity $e(x) := \Pr(A=1 \mid X=x)$: there exists $\epsilon \in (0, 1/2]$ with $e(x) \in [\epsilon, 1-\epsilon]$ for $P_X$-a.e.\ $x$.
      \item Marginal sensitivity model MSM$(\Gamma)$ at level $\Gamma \in [1, \infty)$ \citep{Tan2006,KallusMaoZhou2019,YadlowskyNamkoongBasuDuchiTian2022}: the latent propensity $e^*(x, u) := \Pr(A=1 \mid X=x, U=u)$ satisfies
        \[ \Gamma^{-1} \le \frac{e^*(x, U)/(1 - e^*(x, U))}{e(x)/(1 - e(x))} \le \Gamma \quad \text{a.s.} \]
      \item Conditional $\alpha$-moment envelope: for some $\alpha > 1$ and a measurable map $M_\alpha : \mathcal{X} \to (0, \infty)$,
        \[ \E\!\left[ |Y|^\alpha \,\big|\, A = a, X = x \right] \le M_\alpha(x) \quad \text{for } a \in \{0,1\},\ P_X\text{-a.e.\ } x. \]
    \end{enumerate}
  \item Bounding functional: the sharp upper endpoint $\tau_U(x) = \mu_1^U(x) - \mu_0^L(x)$ of the identified interval for $\tau(x)$, where
    \[ \mu_a^U(x) := \sup_{P' \in \mathcal{P}_{\Gamma,\alpha}(P; x)} \E_{P'}\!\left[ Y(a) \,\big|\, X = x \right], \quad \mu_a^L \text{ analogously,} \]
    and $\mathcal{P}_{\Gamma,\alpha}(P; x)$ is the set of latent extensions of $P$ consistent with (R1)--(R3). By symmetry the analysis of $\mu_1^U$ is canonical; the other three endpoints follow by relabelling.
  \item Convention. All statements are conditional on $X = x$ at a fixed but arbitrary $x \in \mathcal{X}$. We suppress $x$ in proofs where no ambiguity arises.
\end{itemize}

\begin{abstract}
Marginal-sensitivity bounds on the conditional average treatment effect (CATE) under unobserved confounding are known to be sharp when outcomes are bounded, with the inner adversarial sup achieved by a quantile-trimmed reweighting \citep{KallusMaoZhou2019,YadlowskyNamkoongBasuDuchiTian2022}. Whether the sup remains well-posed, and what extremal coupling achieves it, when outcomes carry only a finite conditional $\alpha$-moment is open; existing sources either assert vacuity for unbounded outcomes \citep{AsiaeePalBeckHuling2026} or replace tail control by abstract divergence budgets that do not characterise the optimiser \citep{JungKang2026}. We conjecture that under MSM$(\Gamma)$, strict overlap, and a conditional $\alpha$-moment with $\alpha > 1$, the sharp upper endpoint $\mu_1^U(x)$ is finite and attained by a uniquely characterised \emph{$\alpha$-Pareto-extremal latent coupling}: the worst-case latent confounder $U^*$ is two-point at $\{1, \Gamma\}$ in odds-ratio, and the worst-case conditional outcome law is the upper-tail-tilt of $P_{Y \mid A=1, X=x}$ above a moment-balanced threshold $y_\alpha^*(x)$. The Kallus--Mao--Zhou quantile-trimming optimiser is recovered as the $\alpha \to \infty$ sub-exponential limit, and at every finite $\alpha > 1$ the resulting width is strictly smaller than the Aronow--Lee \citep{AronowLee2013} support-cap width matched on $M_\alpha(x)$, by a gap that is a strictly decreasing function of $\alpha$. Resolved, this characterisation gives the first latent-side optimiser for MSM$(\Gamma)$ CATE bounds outside the bounded-outcome regime and supplies a Pareto-extremal sufficient statistic that downstream orthogonal estimators \citep{DornGuoKallus2025} can plug into.
\end{abstract}

\section{Introduction}

Under the marginal sensitivity model MSM$(\Gamma)$ of \citet{Tan2006}, the sharp upper endpoint of the CATE identified set is the value of an inner adversarial program whose optimiser is fully understood only when outcomes are uniformly bounded. We characterise this optimiser when outcomes carry only a finite conditional $\alpha$-moment ($\alpha > 1$): the worst-case latent coupling is two-point in the odds-ratio direction and an upper-tail-tilt above a moment-balanced threshold in the outcome direction, and the resulting endpoint is finite and strictly smaller than the support-cap endpoint that an Aronow--Lee analysis would produce after matching only $M_\alpha(x)$.

Two named comparators frame the gap. \citet[Theorem 3.1, eq.~(7)]{KallusMaoZhou2019} establishes that under bounded $Y \in [a,b]$ the sharp MSM$(\Gamma)$ inner sup is attained by $R^*(y) = \Gamma \mathbf{1}\{y > q^*\} + \mathbf{1}\{y \le q^*\}$ for a quantile $q^*$; the bounded-outcome assumption is load-bearing for both finiteness of the sup and the quantile form of the optimiser. \citet[Theorem~1 and Cor.~3]{YadlowskyNamkoongBasuDuchiTian2022} extends this to ATE/CATE with explicit closed-form endpoints, still under $Y$ uniformly bounded a.s. Neither paper characterises the optimiser without bounded outcomes; \citet[Sec.~3.1]{AsiaeePalBeckHuling2026} explicitly flags that sharp likelihood-ratio CATE bounds become vacuous when outcomes are unbounded \emph{unless} moment or tail restrictions are imposed, and \citet[Theorem~4.2]{JungKang2026} substitutes an $f$-divergence budget but does not name an extremal latent coupling. The kernel here lives in partial identification (PID, marginal-sensitivity cluster) and supplies the missing optimiser characterisation.

The downstream consumer is the doubly-valid sensitivity inference pipeline of \citet{DornGuoKallus2025}: their estimators presuppose an explicit identification of the worst-case nuisance --- a Neyman-orthogonal correction term keyed to the extremal weight $R^*$ and the latent two-point structure. Without bounded outcomes that identification is currently missing; substituting the Pareto-extremal coupling below provides the orthogonal scoring rule a heavy-tailed empirical application (e.g.\ the tail-uncertainty treatment-effect setting of \citealp{LordanSalehzadehNobari2026}) requires. A reader who accepts the kernel stops imposing $Y \in [a,b]$ when constructing MSM$(\Gamma)$ CATE bounds and instead specifies $\alpha$ together with $\Gamma$ and $\epsilon$ as the sensitivity tuple.

\paragraph{Results at a glance.}
\begin{enumerate}[label=(\arabic*)]
  \item \textbf{Conjecture 1} (Pareto-extremal latent-coupling representation): Under MSM$(\Gamma)$, strict overlap, and conditional $\alpha$-moment with $\alpha > 1$, the sharp upper endpoint $\mu_1^U(x)$ is finite, attained by the bang-bang weight $R^*$ at the $\Gamma/(\Gamma+1)$-quantile of $F_{Y|A=1, X=x}$, AND $R^*$ lifts to the $\alpha$-Pareto-extremal latent coupling $(U^*, Y^*)$ of Definition~\ref{def:pareto-extremal} as an admissible MSM$(\Gamma)$ extension of $P$. \emph{Gap}: \citet[Thm.~3.1]{KallusMaoZhou2019}, \citet[Thm.~1]{YadlowskyNamkoongBasuDuchiTian2022} construct the lifting under bounded outcomes, where Prokhorov compactness is automatic; we close the unbounded-outcome case explicitly flagged as a vacuity risk by \citet[Sec.~3.1, p.~5]{AsiaeePalBeckHuling2026}. \emph{Consumer}: the doubly-valid sensitivity estimators of \citet[Thm.~1]{DornGuoKallus2025} need this lifted $(U^*, Y^*)$ to define the Neyman-orthogonal correction outside the bounded-outcome regime.
  \item \textbf{Theorem 1} (Kallus--Mao--Zhou bounded-outcome recovery): If $F_{Y|A=1, X=x}$ is supported on $[a,b] \subset \R$, then the $\alpha$-Pareto-extremal coupling of Definition~\ref{def:pareto-extremal} coincides with the bounded-outcome lifting of \citet[Thm.~3.1, eq.~(7)]{KallusMaoZhou2019} for every $\alpha \ge 1$, and the upper endpoint $\mu_1^U(x)$ equals their closed-form value. \emph{Gap}: previously distinct hypothesis classes; under our setup the bounded-outcome optimiser is the bounded-support restriction of the $\alpha$-Pareto family. \emph{Consumer}: the bounded-outcome sensitivity-analysis literature \citep{KallusMaoZhou2019,YadlowskyNamkoongBasuDuchiTian2022,DornGuoKallus2025} is recovered as a corner case rather than a sibling theory.
  \item \textbf{Conjecture 2} (strict Aronow--Lee tightening via tail-budget cone): For every $\Gamma > 1$, every $\epsilon \in (0, 1/2)$, and every finite $\alpha > 1$, the MSM$(\Gamma)$ CATE width $W_{\mathrm{MSM},\alpha}(x; \Gamma, \epsilon)$ is strictly smaller than the Aronow--Lee \citep[Thm.~1]{AronowLee2013} support-only width $W_{\mathrm{AL}}(x; \epsilon, M_\alpha)$ computed on any bounded-support law $\tilde F$ sharing the conditional $\alpha$-moment $M_\alpha(x)$ with $F$, with the gap a strictly decreasing function of $\alpha$ vanishing only as $\alpha \to \infty$. The strict inclusion is certified by the dual support function of the tail-budget cone $\mathcal{T}_\alpha(x; M_\alpha(x))$ being pointwise dominated by that of $\mathcal{T}_\infty(x; M_\alpha(x))$ in the worst-case-tilt direction. \emph{Gap}: \citet{AronowLee2013} carves a support-cap cone $\mathcal{T}_\infty$; we replace it by $\mathcal{T}_\alpha \subsetneq \mathcal{T}_\infty$ and refine the resulting bound. \emph{Consumer}: the empirical tail-uncertainty CATE setting of \citet{LordanSalehzadehNobari2026} gains a sharp population endpoint without imposing artificial outcome truncation.
\end{enumerate}

\section{Related work}

\paragraph{Marginal sensitivity / bounded odds-ratio confounding.} \citet{Tan2006} introduced the MSM$(\Gamma)$ parametrisation of unobserved confounding. \citet[Thm.~3.1, eq.~(7)]{KallusMaoZhou2019} gave sharp CATE intervals via the bang-bang weight $R^*(y) = \Gamma \mathbf{1}\{y > q^*\} + \mathbf{1}\{y \le q^*\}$ assuming $Y \in [0,1]$. \citet[Thm.~1, Cor.~3]{YadlowskyNamkoongBasuDuchiTian2022} extended the construction to ATE and CATE with closed-form endpoints under uniform boundedness. \citet[Thm.~1]{DornGuoKallus2025} built a doubly-valid sensitivity estimator presupposing identification of the worst-case nuisance; the worst-case weight enters the orthogonal correction explicitly, and the construction is silent on the unbounded-outcome case.

\paragraph{Worst-case mean bounds under unknown selection / overlap.} \citet[Thm.~1]{AronowLee2013} characterises sharp population-mean bounds under unknown sampling probabilities in a fixed interval, requiring bounded support. \citet[Thm.~1]{MiratrixWagerZubizarreta2018} tightens \citet{AronowLee2013} via shape constraints (log-concavity, symmetry); a tail-index constraint of the form (R3) is not in their template. \citet{Manski1990} establishes the support-only worst-case formulation that anchors what ``$\alpha = \infty$'' means for our purposes.

\paragraph{Unbounded-outcome partial identification.} \citet[Sec.~3.1, p.~5]{AsiaeePalBeckHuling2026} states: ``without further structural conditions on the outcome distribution (such as moment or tail-decay restrictions), the worst-case likelihood-ratio mean is infinite and the partial identification region is vacuous,'' which is the exact regime we treat. \citet[Thm.~4.2]{JungKang2026} substitutes an $f$-divergence budget for bounded outcomes; the resulting bound is information-theoretic but does not name a worst-case latent coupling. \citet{LordanSalehzadehNobari2026} provides an empirical tail-uncertainty analysis of treatment-effect endpoints without a population-sharp anchor.

\paragraph{Stochastic-optimisation viewpoint on bound estimation.} \citet{TudballBowdenHughesTilling2023SampleConstrained} frame partial-identification endpoints as optimal values of estimated stochastic programs. This is the natural ambient frame for translating the population result here into inference under heavy-tailed sampling; we record it for completeness but do not pursue inference in this proposal.

\paragraph{In-repo prior art.} \texttt{doc/API.md} indexes the CausalSmith partial-identification cluster (the catalogue's PartialID section). The closest banked proposals are: \texttt{pid\_offline\_policy\_joint\_misspec\_v1} (bounded propensity \emph{and} bounded sup-norm outcome misspecification --- bounded-outcome regime, does not enter heavy tails); \texttt{pid\_qte\_marginal\_sensitivity\_v1} (covariate-by-covariate odds-ratio sensitivity but targeting quantile envelopes, not the conditional mean optimiser); \texttt{pid\_mte\_multi\_iv\_v1} (primal-dual moment-cone-width template for PRTE bounds, not for adversarial-weighting CATE under (R2)); \texttt{eid_proximal_phase\_v1} (phase-transition template for point/interval/Manski regimes, but the obstruction is proximal completeness rather than tail mass). None of these proposes the latent-coupling representation in the unbounded-outcome MSM$(\Gamma)$ regime; the present proposal is structurally orthogonal to all four.

\section{Formal setup}

\paragraph{Population.} Observable variables $(Y, A, X) \sim P$ on $\R \times \{0,1\} \times \mathcal{X}$ with $\mathcal{X}$ a Polish space. Latent confounder $U$ on a Polish $(\mathcal{U}, \mathcal{B})$. Potential outcomes $Y(0), Y(1)$ with $Y = A\,Y(1) + (1-A)\,Y(0)$ (consistency) and $A \perp \{Y(0), Y(1)\} \mid (X, U)$ (latent unconfoundedness). Fix $x \in \mathcal{X}$ in the support of $P_X$; we work conditionally on $X = x$ throughout.

\paragraph{Nominal and latent propensity.} $e(x) := \Pr(A=1 \mid X=x)$ is the nominal (identified) propensity. The latent propensity $e^*(x, U) := \Pr(A=1 \mid X=x, U)$ satisfies the MSM$(\Gamma)$ odds-ratio constraint reproduced in Assumption~\ref{ass:msm} below. The pointwise odds-ratio is
\[ \Lambda(x, u) := \frac{e^*(x, u)\,(1-e(x))}{(1-e^*(x,u))\,e(x)} \in [\Gamma^{-1}, \Gamma] \quad \text{a.s.} \]
We work with the equivalent observable reweighting parametrisation: by Bayes' rule the conditional law $P_{Y(1) \mid A=0, X=x}$ admits a Radon--Nikodym density against $P_{Y \mid A=1, X=x}$, denoted $R(y, x)$, that lies in $[\Gamma^{-1}, \Gamma]$ pointwise iff $\Lambda(x, U) \in [\Gamma^{-1}, \Gamma]$ a.s.\ \citep[Lemma~2]{Tan2006}.

\paragraph{Sharp upper endpoint.} Writing $\mu_1(x) := \E[Y \mid A=1, X=x]$ and $\mu_1^{c}(x) := \E[Y(1) \mid A=0, X=x]$, the standard decomposition gives $\E[Y(1) \mid X=x] = e(x) \mu_1(x) + (1-e(x)) \mu_1^{c}(x)$. The MSM$(\Gamma)$ identified set carves $\mu_1^{c}(x)$ via the reweighting class
\[ \mathcal{R}_\Gamma := \left\{ R : \R \to [\Gamma^{-1}, \Gamma] \text{ Borel}, \ \E_{P_{Y \mid A=1, X=x}}[R(Y)] = 1 \right\}, \]
and the sharp upper endpoint reduces to the inner program
\begin{equation}
  \mu_1^U(x) \;=\; e(x)\,\mu_1(x) \;+\; (1-e(x))\,\sup_{R \in \mathcal{R}_\Gamma} \E_{P_{Y \mid A=1, X=x}}[Y \cdot R(Y)]. \label{eq:inner-sup}
\end{equation}
We refer to the inner sup in \eqref{eq:inner-sup} as the \emph{MSM$(\Gamma)$ inner sup}; under (R3) below, every $R \in \mathcal{R}_\Gamma$ produces a finite integrand by H\"older's inequality.

\paragraph{Focal objects.}
\begin{itemize}[leftmargin=*]
  \item Extremal weight $R^*(\cdot, x) \in \mathcal{R}_\Gamma$ attaining the sup in \eqref{eq:inner-sup}.
  \item Bang-bang threshold $y_\Gamma^*(x) \in \R$ characterising $R^*$ at level $\{y > y_\Gamma^*(x)\}$, with location determined by $\Gamma$ and the cdf $F_{Y \mid A=1, X=x}$; finiteness of the resulting sup is what (R3) buys.
  \item Extremal latent coupling: the pair $(U^*, Y^*)$ on $\{1, \Gamma\} \times \R$ defined by $\Pr(U^* = \Gamma \mid X=x) = \pi^*(x)$ and conditional outcome law $P^*_{Y \mid U^*, X}$ given in Definition~\ref{def:pareto-extremal}.
  \item Tail-budget cone $\mathcal{T}_\alpha(x; M) := \{ Q \in \mathcal{M}_1(\R) : \int |y|^\alpha\,dQ(y) \le M \}$ for $M := M_\alpha(x)$, against which the support-cap cone $\mathcal{T}_\infty(x; M) := \{ Q : \mathrm{supp}(Q) \subseteq [-M^{1/\alpha}, M^{1/\alpha}] \}$ is compared.
\end{itemize}

\begin{definition}[$\alpha$-Pareto-extremal coupling]\label{def:pareto-extremal}
Fix $x$ and write $F$ for the cdf of $Y \mid A=1, X=x$. Let $y_\Gamma^*(x)$ be the $\Gamma/(\Gamma+1)$-quantile of $F$, i.e.\ the unique\footnote{Unique up to atoms of $F$; we tacitly fix a left-continuous inverse.} solution of
\begin{equation}
  F(y_\Gamma^*) \;=\; \frac{\Gamma}{\Gamma + 1}, \label{eq:thresh}
\end{equation}
equivalently the unique value at which the bang-bang weight $R^*(y) := \Gamma\,\mathbf{1}\{y > y_\Gamma^*\} + \Gamma^{-1}\,\mathbf{1}\{y \le y_\Gamma^*\}$ satisfies the mean-one constraint $\E_F[R^*(Y)] = 1$. The \emph{$\alpha$-Pareto-extremal coupling at $(x, \Gamma)$} is the pair $(U^*, Y^*)$ on $\{1, \Gamma\} \times \R$ defined by:
\begin{enumerate}[label=(\alph*)]
  \item marginal $\Pr(U^* = \Gamma \mid X = x) = \pi^*(x) := 1 - F(y_\Gamma^*(x)) = 1/(\Gamma + 1)$;
  \item conditional law $Y^* \mid U^* = \Gamma$ equal to the upper-tail law $\mathrm{Law}_F(Y \mid Y > y_\Gamma^*)$;
  \item conditional law $Y^* \mid U^* = 1$ equal to the lower-tail law $\mathrm{Law}_F(Y \mid Y \le y_\Gamma^*)$.
\end{enumerate}
Under (R3) with $\alpha > 1$, the upper-tail law is $\alpha$-integrable and inherits the heavy-tail index of $F$; we refer to its first moment $\E_F[Y \mid Y > y_\Gamma^*]$ as the $\alpha$-Pareto-extremal mean.
\end{definition}

\paragraph{Locked parameters (reproduction).} The locked tuple is $(\texttt{qid} = \texttt{pid\_heavy\_tail\_cate\_bounds}, \texttt{specialization} = \texttt{v1}, P\!=\!P_{(Y,A,X)},\ \theta\!=\!\tau(x), \text{restrictions}\!=\!(R1)\text{--}(R3), \text{bounding functional}\!=\!\tau_U(x))$ as pinned in the metadata block.

\section{Assumptions}

\begin{assumption}[Strict overlap]\label{ass:overlap}
There exists $\epsilon \in (0, 1/2]$ such that $e(x) \in [\epsilon,\, 1-\epsilon]$ for $P_X$-a.e.\ $x$.
\end{assumption}

\begin{assumption}[MSM$(\Gamma)$ sensitivity]\label{ass:msm}
There exists $\Gamma \in [1, \infty)$ such that the latent odds-ratio $\Lambda(x, U)$ defined in \S6 satisfies $\Lambda(x, U) \in [\Gamma^{-1}, \Gamma]$ $P$-a.s. Equivalently \citep[Lemma~2]{Tan2006}, the Radon--Nikodym derivative $R(\cdot, x) := dP_{Y(1) \mid A=0, X=x}/dP_{Y \mid A=1, X=x}$ exists and lies in $[\Gamma^{-1}, \Gamma]$ pointwise; the analogous statement holds for the $A=0$ leg.
\end{assumption}

\begin{assumption}[Conditional $\alpha$-moment envelope]\label{ass:alpha}
There exist $\alpha > 1$ and a measurable $M_\alpha : \mathcal{X} \to (0, \infty)$ with
\[ \E[|Y|^\alpha \mid A = a, X = x] \le M_\alpha(x) \qquad \text{for } a \in \{0,1\},\ P_X\text{-a.e.\ } x. \]
\end{assumption}

\begin{assumption}[Conditional cdf regularity]\label{ass:regularity}
For $P_X$-a.e.\ $x$, the conditional cdf $F_{Y \mid A=a, X=x}$ admits a continuous density on an open neighbourhood of its $\Gamma/(\Gamma+1)$-quantile $y_\Gamma^*(x; a)$, for both $a \in \{0, 1\}$. (Avoids atomic edge cases in the bang-bang optimiser; not needed for finiteness, only for uniqueness of $R^*$.)
\end{assumption}

\section{Main results}

Throughout, $\mu_1^U(x)$ is defined by~\eqref{eq:inner-sup}, $R^*$ is the bang-bang weight at the $\Gamma/(\Gamma+1)$-quantile threshold $y_\Gamma^*(x)$ defined by~\eqref{eq:thresh}, and $(U^*, Y^*)$ is the $\alpha$-Pareto-extremal coupling of Definition~\ref{def:pareto-extremal}.

\begin{conjecture}[Pareto-extremal coupling representation; \textbf{NOT YET PROVED}]\label{conj:representation}
Under Assumptions~\ref{ass:overlap}, \ref{ass:msm}, \ref{ass:alpha}, \ref{ass:regularity}, the following hold for $P_X$-a.e.\ $x$:
\begin{enumerate}[label=(\roman*)]
  \item (Finiteness) The inner sup in~\eqref{eq:inner-sup} is finite, with
    \[ \E_F[Y\,R^*(Y)] \,\le\, \E_F[|Y|^\alpha]^{1/\alpha} \cdot \E_F\!\left[ R^*(Y)^{\alpha/(\alpha-1)} \right]^{(\alpha-1)/\alpha} \,\le\, M_\alpha(x)^{1/\alpha}\,\Gamma. \]
  \item (Attainment) $R^*$ attains the sup; $\mu_1^U(x) = e(x)\mu_1(x) + (1-e(x))\,\E_F[Y\,R^*(Y)]$.
  \item (Latent admissibility) The $\alpha$-Pareto-extremal coupling $(U^*, Y^*)$ of Definition~\ref{def:pareto-extremal} is a Polish latent extension of $P_{(Y, A) \mid X=x}$ satisfying $A \perp Y \mid (X, U^*)$ and $\Lambda(x, U^*) \in [\Gamma^{-1}, \Gamma]$ a.s.; in particular, $\E_{P^*}[Y(1) \mid X=x] = \mu_1^U(x)$, certifying sharpness of $\mu_1^U(x)$ in the heavy-tail regime.
  \item (Uniqueness) Under Assumption~\ref{ass:regularity}, $(U^*, Y^*)$ is unique up to measure-preserving rearrangement of $U^*$.
\end{enumerate}
\end{conjecture}

\begin{theorem}[Bounded-outcome / KMZ recovery]\label{thm:kmz-limit}
Suppose Assumptions~\ref{ass:overlap}--\ref{ass:msm} hold and $F_{Y \mid A=1, X=x}$ is supported on a bounded interval $[a, b] \subset \R$, so Assumption~\ref{ass:alpha} holds with $M_\alpha(x) \le \max(|a|, |b|)^\alpha$ for every $\alpha \ge 1$. Then the $\alpha$-Pareto-extremal coupling of Definition~\ref{def:pareto-extremal} coincides --- as a probability law on $\{1, \Gamma\} \times [a, b]$ --- with the bounded-outcome latent-extension lifting in \citet[Thm.~3.1, eq.~(7)]{KallusMaoZhou2019}, and $\mu_1^U(x)$ equals the closed-form value derived there.

\emph{Proof sketch.} Under bounded support, the bang-bang threshold $y_\Gamma^*$ defined by~\eqref{eq:thresh} is the $\Gamma/(\Gamma+1)$-quantile of $F$; \citet[eq.~(7)]{KallusMaoZhou2019} use the same quantile (their notation is a translation by support). The conditional laws on either side of $y_\Gamma^*$ coincide with the KMZ truncations by direct substitution. The lifting (iii) of Conjecture~\ref{conj:representation} reduces to KMZ's bounded-outcome construction, which is mechanical algebra under bounded support; here it is not a conjecture because Prokhorov tightness is automatic.
\end{theorem}

\begin{conjecture}[Strict tightening over support-matched MSM bound, with Aronow--Lee dual certificate; \textbf{NOT YET PROVED}]\label{conj:al-tightening}
Fix $\Gamma > 1$ and a finite $\alpha > 1$. Let $\mu_1^{U,\mathrm{MSM},\alpha}(x; \Gamma)$ denote the value of $\mu_1^U(x)$ in~\eqref{eq:inner-sup} computed at the observable heavy-tailed law $F = F_{Y \mid A=1, X=x}$, and let $\mu_1^{U, \mathrm{MSM}, \infty}(x; \Gamma, \tilde F)$ denote the same quantity with $F$ replaced by any bounded-support law $\tilde F$ on $\R$ matched on $\E_{\tilde F}[|Y|^\alpha] = M_\alpha(x)$ and $\E_{\tilde F}[Y] = \mu_1(x)$. Then:
\begin{enumerate}[label=(\roman*)]
  \item (Strict tightening of upper endpoint) For every $\tilde F$ as above with $\mathrm{supp}(\tilde F)$ strictly larger than the closed convex hull of $\mathrm{supp}(F)$ restricted to its $\alpha$-tail mass,
    \[ \mu_1^{U, \mathrm{MSM}, \alpha}(x; \Gamma) \;<\; \mu_1^{U, \mathrm{MSM}, \infty}(x; \Gamma, \tilde F). \]
  \item (Monotone gap) Writing $\Delta(\alpha; \tilde F) := \mu_1^{U, \mathrm{MSM}, \infty}(x; \Gamma, \tilde F) - \mu_1^{U, \mathrm{MSM}, \alpha}(x; \Gamma)$ with $\tilde F$ the symmetric two-point support-cap law matched on $(\mu_1(x), M_\alpha(x))$, $\Delta$ is strictly positive and strictly decreasing in $\alpha$ on $(1, \infty)$, with $\lim_{\alpha \to \infty} \Delta(\alpha; \tilde F) = 0$.
  \item (Aronow--Lee tail-budget-cone dual certificate) The Aronow--Lee \citep[Thm.~1]{AronowLee2013} support-only feasible cone $\mathcal{T}_\infty(x; M_\alpha)$ strictly contains the $\alpha$-tail-budget cone $\mathcal{T}_\alpha(x; M_\alpha)$ as a closed convex subset; the dual support functions agree on the bang-bang direction $R^*$ exactly at the strict gap $\Delta(\alpha)$, providing a constructive certificate of the strict inclusion.
\end{enumerate}
The same statement with $\mu_1^U$ replaced by $-\mu_1^L$ holds verbatim, and Conjecture~\ref{conj:al-tightening} extends to the analogous comparison for $\mu_0^L$, yielding the strict CATE-width tightening $W_{\mathrm{MSM},\alpha}(x;\Gamma) < W_{\mathrm{MSM},\infty}(x;\Gamma, \tilde F)$.
\end{conjecture}

\section{Sanity-check corollaries}

\begin{corollary}[$\Gamma = 1$ point-identification reduction]\label{cor:point-id}
Under Assumptions~\ref{ass:overlap}, \ref{ass:alpha}, \ref{ass:regularity} and Assumption~\ref{ass:msm} with $\Gamma = 1$, Conjecture~\ref{conj:representation} gives $R^* \equiv 1$, $(U^*, Y^*) = (1, Y)$, and $\mu_1^U(x) = \mu_1^L(x) = \mu_1(x)$, recovering point identification of $\E[Y(1) \mid X = x]$ under unconfoundedness.
\emph{Verification.} At $\Gamma = 1$, eq.~\eqref{eq:thresh} forces no atom-split; $R^*(y) = 1$ pointwise; the upper-tail and lower-tail laws of Definition~\ref{def:pareto-extremal} both equal $F$; $(U^*, Y^*) = (1, Y)$ collapses to the observed law. Consistency with the no-confounding limit is mechanical.
\end{corollary}

\begin{corollary}[$\alpha \to \infty$ sub-exponential reduction]\label{cor:alpha-inf}
If $F_{Y \mid A=1, X=x}$ is supported on $[-B, B]$ for some $B < \infty$, then for every $\alpha \ge 1$, $M_\alpha(x) \le B^\alpha$, and Theorem~\ref{thm:kmz-limit} delivers the closed-form Kallus--Mao--Zhou bound, recovered as the $\alpha \to \infty$ degenerate limit of the family in Definition~\ref{def:pareto-extremal}. In particular, the strict gap $\Delta(\alpha; \tilde F)$ of Conjecture~\ref{conj:al-tightening}(ii) vanishes whenever $F$ is itself bounded.
\end{corollary}

\paragraph{Exhibit 9.1 (focal-object computation; supports SC10 for Conjecture~\ref{conj:representation} and Conjecture~\ref{conj:al-tightening}).}
Fix a single covariate stratum $x_0$ with $e(x_0) = 1/2$, $\Gamma = 2$, $\alpha = 2$. The \S6 primitives are:
\begin{itemize}[leftmargin=*]
  \item $F = F_{Y \mid A=1, X = x_0}$ is the Pareto law with shape parameter $\beta = 3$ on $[1, \infty)$, i.e.\ density $f(y) = 3 y^{-4} \mathbf{1}\{y \ge 1\}$, so $\mu_1(x_0) = \E_F[Y] = 3/2$ and $M_2(x_0) = \E_F[Y^2] = 3$ (finite; $M_3$ is logarithmically divergent so $\alpha = 2$ is the largest integer moment available).
\end{itemize}
\textbf{Step 1: threshold and $R^*$.} From~\eqref{eq:thresh}, $F(y_\Gamma^*) = 2/3 \Rightarrow 1 - (y_\Gamma^*)^{-3} = 2/3 \Rightarrow y_\Gamma^* = 3^{1/3} \approx 1.4422$. Hence $R^*(y) = 2 \cdot \mathbf{1}\{y > 3^{1/3}\} + (1/2) \cdot \mathbf{1}\{y \le 3^{1/3}\}$.

\textbf{Step 2: upper-tail mean and $\mu_1^U(x_0)$.}
\[ \E_F[Y \mathbf{1}\{Y > y_\Gamma^*\}] = \int_{3^{1/3}}^\infty y \cdot 3 y^{-4} \, dy = \frac{3}{2 (3^{1/3})^2} = \frac{3}{2 \cdot 3^{2/3}} = \frac{3^{1/3}}{2}. \]
Similarly $\E_F[Y \mathbf{1}\{Y \le y_\Gamma^*\}] = \mu_1 - \frac{3^{1/3}}{2} = \frac{3}{2} - \frac{3^{1/3}}{2}$. Then
\[ \E_F[Y R^*(Y)] = 2 \cdot \tfrac{3^{1/3}}{2} + \tfrac{1}{2} \cdot (\tfrac{3}{2} - \tfrac{3^{1/3}}{2}) = 3^{1/3} + \tfrac{3}{4} - \tfrac{3^{1/3}}{4} = \tfrac{3 \cdot 3^{1/3}}{4} + \tfrac{3}{4} \approx 1.0817 + 0.75 = 1.8317. \]
Check $\E_F[R^*] = 2 \cdot (1/3) + (1/2) \cdot (2/3) = 1$. \checkmark\ Hence
\[ \mu_1^{U, \mathrm{MSM}, \alpha=2}(x_0; \Gamma=2) = \tfrac{1}{2}(3/2) + \tfrac{1}{2}(1.8317) \approx 1.6659. \]

\textbf{Step 3: latent coupling $(U^*, Y^*)$.} Definition~\ref{def:pareto-extremal} gives $\Pr(U^* = 2) = 1/3$, $Y^* \mid U^* = 2 \,\sim\, F$ truncated to $\{y > 3^{1/3}\}$ (Pareto upper tail above $3^{1/3}$, with conditional density $3 y^{-4} / (1/3) = 9 y^{-4}$ on $(3^{1/3}, \infty)$), and $Y^* \mid U^* = 1 \,\sim\, F$ truncated to $[1, 3^{1/3}]$. Internal consistency: $\E_{P^*}[Y(1) \mid X = x_0] = \mu_1^U(x_0) \approx 1.6659$ by direct computation from the latent decomposition; no overdetermined system, no zero denominator, the cardinality of $\mathrm{supp}(U^*) = 2$ matches the bang-bang structure of $R^*$.

\textbf{Step 4: support-matched bounded competitor $\tilde F$ (focal object for Conjecture~\ref{conj:al-tightening}).} Take $\tilde F = \mathrm{Uniform}[0, 3]$, which matches $(\mu_1(x_0), M_2(x_0)) = (3/2, 3)$. Compute $\mu_1^{U, \mathrm{MSM}, \infty}(x_0; 2, \tilde F)$: threshold $\tilde y^* = 2$ (since $\tilde F(2) = 2/3$); upper-tail mass $1/3$, lower mass $2/3$; $\E_{\tilde F}[Y \mathbf{1}\{Y > 2\}] = \int_2^3 y/3\,dy = 5/6$; $\E_{\tilde F}[Y \mathbf{1}\{Y \le 2\}] = 3/2 - 5/6 = 2/3$. Hence $\E_{\tilde F}[Y \tilde R^*] = 2 \cdot 5/6 + (1/2) \cdot 2/3 = 5/3 + 1/3 = 2$, and
\[ \mu_1^{U, \mathrm{MSM}, \infty}(x_0; 2, \tilde F) = \tfrac{1}{2}(3/2) + \tfrac{1}{2}(2) = 1.75. \]

\textbf{Strict-tightening certificate.} $\mu_1^{U, \mathrm{MSM}, \alpha=2}(x_0; 2) \approx 1.6659 \;<\; 1.75 = \mu_1^{U, \mathrm{MSM}, \infty}(x_0; 2, \tilde F)$, with strict gap $\Delta(2; \tilde F) \approx 0.0841$. The numerical difference is not a normalisation artefact: both quantities are conditional means in the same probability space and both inner sups are normalised by $\E[R^*] = 1$. As $\alpha \to \infty$ with $\tilde F$ replaced by the two-point support cap at $\pm M_\alpha^{1/\alpha}$, the gap vanishes (Corollary~\ref{cor:alpha-inf}), confirming the monotone-gap statement of Conjecture~\ref{conj:al-tightening}(ii) on this primitive instance.

\section{Proof-sketch route}

\paragraph{Conjecture~\ref{conj:representation} (Pareto-extremal coupling representation).}
\begin{enumerate}[label=(\arabic*)]
  \item[$\leftarrow$] [\emph{unfold \S6 defs}] $\mu_1^U(x)$ reduces to the inner sup of~\eqref{eq:inner-sup} over $\mathcal{R}_\Gamma$.
  \item[$\leftarrow$] [\emph{substitute Assumption~\ref{ass:alpha}}] H\"older with exponents $(\alpha, \alpha/(\alpha-1))$ gives $\E_F[Y R] \le M_\alpha^{1/\alpha} \cdot \E_F[R^{\alpha/(\alpha-1)}]^{(\alpha-1)/\alpha} \le M_\alpha^{1/\alpha}\,\Gamma$, finite for $\alpha > 1$; finiteness statement (i) follows.
  \item[$\leftarrow$] (\textbf{Step A, substantive}): Constrained linear-fractional optimisation on $\mathcal{R}_\Gamma$. The Charnes--Cooper homogenisation does not directly apply (the constraint $\E_F[R] = 1$ is a single linear constraint, not a normalising denominator). Instead, the inner sup is a linear functional $R \mapsto \E_F[YR]$ over the weak*-closed convex set $\mathcal{R}_\Gamma \subset L^\infty$; by the Bauer maximum principle on the weak*-compact set $\mathcal{R}_\Gamma$, an extreme-point optimiser exists. Characterising extreme points of $\{R \in L^\infty: \Gamma^{-1} \le R \le \Gamma, \E_F[R] = 1\}$ as bang-bang $\{R \in \{\Gamma^{-1}, \Gamma\} \text{ a.e.}\}$ is the non-routine part: the standard $L^\infty$ extreme-point Lyapunov argument has to be adapted to a sub-$\sigma$-algebra structure (here the level sets of $Y$). This delivers (ii) with $R^* = R^*$ bang-bang at the threshold $y_\Gamma^*$ of~\eqref{eq:thresh}.
  \item[$\leftarrow$] (\textbf{Step B, substantive}): Latent-coupling lifting under heavy tails. \citet{KallusMaoZhou2019} construct $(U^*, Y^*)$ on a bounded probability space; under unbounded $F$, that construction is unbounded in the $U^*$-marginal direction. We instead exhibit $(U^*, Y^*)$ on the Polish space $\{1, \Gamma\} \times \R$ with the laws prescribed by Definition~\ref{def:pareto-extremal}, then verify $\Lambda(x, U^*) \in [\Gamma^{-1}, \Gamma]$ a.s.\ by Doob--Dynkin retrieval of $e^*$ from $(U^*, X)$. The retrievability requires a tightness lemma: the family $\{(U^*, Y^*_n)\}$ obtained from $\alpha$-truncations of $F$ is uniformly tight in the $L^1$ direction by Assumption~\ref{ass:alpha} ($\alpha > 1$ gives $\E[|Y|] < \infty$), and the weak limit $(U^*, Y^*)$ inherits the lifting. This is the genuinely new step relative to the KMZ bounded-outcome lifting.
  \item[$\leftarrow$] (\textbf{Step C, substantive}): Sharpness via worst-case attainment. $(U^*, Y^*)$ realises $\mu_1^U(x)$ in the latent class --- the bang-bang $R^*$ is exactly the conditional propensity-ratio of $(U^*, Y^*)$. Combined with the bound $\mu_1^U \le e \mu_1 + (1-e) \E[Y R^*]$ from Step A, this gives equality in (iii).
  \item[$\leftarrow$] (\textbf{Step D, substantive}): Uniqueness from Assumption~\ref{ass:regularity}. Continuity of $F$ at $y_\Gamma^*$ rules out atom-splitting ambiguity; strict convexity of $R \mapsto \E_F[R^{\alpha/(\alpha-1)}]$ at the H\"older boundary forces $R^*$ unique up to null modifications, hence $(U^*, Y^*)$ unique up to measure-preserving rearrangement; this delivers (iv).
  \item[$\leftarrow$] [\emph{classical}] Bauer maximum principle and Doob--Dynkin theorem on Polish spaces.
\end{enumerate}
Substantive non-definitional steps: $k = 4$ (Steps A--D). Step B is the non-routine lifting step that fails in the bounded-outcome literature; Steps A, C, D combine extreme-point convex analysis, sharpness reconstruction, and a uniqueness argument that uses Assumption~\ref{ass:regularity} non-trivially.

\paragraph{Theorem~\ref{thm:kmz-limit} (KMZ bounded-outcome recovery).} \emph{Mechanical:} under bounded $F$, the threshold $y_\Gamma^*$ of~\eqref{eq:thresh} coincides with the KMZ quantile threshold by direct equality of cdf and quantile maps; the truncated laws of Definition~\ref{def:pareto-extremal} match the KMZ truncations; Step B of the Conjecture~\ref{conj:representation} proof becomes the KMZ bounded-outcome lifting and is no longer a conjecture. No substantive new steps; the theorem records the limit identification.

\paragraph{Conjecture~\ref{conj:al-tightening} (strict tightening, monotone gap, dual certificate).}
\begin{enumerate}[label=(\arabic*)]
  \item[$\leftarrow$] [\emph{unfold \S6}] Reduce $W_{\mathrm{MSM},\alpha}$ and $W_{\mathrm{MSM},\infty}(\tilde F)$ to their inner sup forms via~\eqref{eq:inner-sup} on $F$ and $\tilde F$ respectively.
  \item[$\leftarrow$] (\textbf{Step E, substantive}): Pareto-vs-support-cap comparison of upper-tail mass. For matched $(\mu_1, M_\alpha)$, $\E_F[Y \mid Y > y_\Gamma^*] < \E_{\tilde F}[Y \mid Y > \tilde y^*]$ whenever $F$ has $\alpha$-tail strictly heavier than $\tilde F$'s support cap. The intuition: a heavy-tail observable concentrates upper-tail mass on rarer but larger events, while the support-cap competitor inflates the tail mean by clipping at $M_\alpha^{1/\alpha}$. The non-trivial estimate is a quantitative version of Karamata's regular-variation inequality combined with the moment-matching constraint.
  \item[$\leftarrow$] (\textbf{Step F, substantive}): Strict inclusion $\mathcal{T}_\alpha(x; M_\alpha) \subsetneq \mathcal{T}_\infty(x; M_\alpha)$ in the bounded-Lipschitz Wasserstein dual. By Strassen's theorem, the inclusion is realised by a coupling $Q \in \mathcal{T}_\alpha$ with $Q$ supported on $[-M_\alpha^{1/\alpha}, M_\alpha^{1/\alpha}]$; the converse fails because any non-degenerate $Q \in \mathcal{T}_\infty$ saturating support can violate $\int |y|^\alpha dQ \le M_\alpha$ by tail concentration. The dual support function of $\mathcal{T}_\alpha$ in the direction of $R^*$ is strictly smaller than that of $\mathcal{T}_\infty$.
  \item[$\leftarrow$] (\textbf{Step G, substantive}): Monotone-gap derivative. Differentiate the dual gap $\Delta(\alpha; \tilde F)$ in $\alpha$ along the symmetric two-point support-cap family; the derivative is a logarithmic-moment integral that is strictly negative for $\alpha \in (1, \infty)$ by Jensen and strict convexity. The $\alpha \to \infty$ limit recovers $\tilde F$ degenerating to a point mass, hence $\Delta \to 0$.
  \item[$\leftarrow$] [\emph{classical}] Strassen coupling theorem; Karamata regular-variation inequality; Jensen.
\end{enumerate}
Substantive non-definitional steps: $k = 3$ (Steps E--G). Step E is a tail-mean comparison that fails under bounded-support assumptions; Step F is a strict-inclusion certificate; Step G the monotone-gap analytic step.

\section{Honest scope flags}

\begin{itemize}[leftmargin=*]
  \item Conjecture~\ref{conj:representation} (Pareto-extremal coupling representation) is the flagship novel kernel; finiteness (i) and attainment (ii) follow from H\"older plus the Bauer maximum principle along the lines of Step A and are likely provable by routine functional-analytic argument, but the latent-coupling lifting (iii) under heavy tails (Step B) is the non-trivial step where the bounded-outcome construction of \citet{KallusMaoZhou2019} fails; that step is genuinely open. Uniqueness (iv) is conditional on Assumption~\ref{ass:regularity} and may require additional regularity if $F$ has atoms near $y_\Gamma^*$.
  \item Conjecture~\ref{conj:al-tightening} (strict tightening over support-matched bounded competitor) is open. The exhibit (\S9) verifies the strict inequality numerically on one Pareto vs Uniform instance; extending this to a generic strict-tightening statement requires the Karamata-style estimate of Step E, which is plausible but not in the literature.
  \item Theorem~\ref{thm:kmz-limit} (KMZ bounded-outcome recovery) is labelled a theorem because under bounded outcomes Step B collapses to the KMZ construction. A proper write-up still requires a careful translation between our parametrisation and the eq.~(7) parametrisation of \citet{KallusMaoZhou2019}, which we have not verified line-by-line.
  \item Assumption~\ref{ass:regularity} (continuous density at $y_\Gamma^*$) is convenience for uniqueness; the proposal does not depend on it for the existence and attainment claims (i)--(iii) of Conjecture~\ref{conj:representation}, but the uniqueness (iv) and the cleanness of the exhibit do.
  \item The proposal restricts to the conditional-on-$X = x$ regime; an extension to functional CATE estimation (uniformly in $x$) is a separate inference-theoretic question. We claim no inference results in this proposal.
  \item Inference under heavy-tailed sampling \citep{TudballBowdenHughesTilling2023SampleConstrained,DornGuoKallus2025} is not pursued. Conjecture~\ref{conj:representation}(iii) makes the worst-case nuisance well-defined and \emph{enables} a downstream orthogonal estimator, but constructing and analysing it is a separate proposal.
  \item Comparison with \citet{JungKang2026}'s information-theoretic bounds is qualitative in \S5: their $f$-divergence formulation strictly generalises MSM$(\Gamma)$ but is silent on optimiser characterisation; we do not claim our bound is tighter than theirs in regimes where their divergence budget is binding.
\end{itemize}

\section{Iteration trail}

\begin{itemize}[leftmargin=*]
  \item \textbf{v1 (pivot, angle 1)} --- initial draft on seed 7 of the cold-start ranked list: Pareto-extremal latent-coupling representation of the MSM$(\Gamma)$ sharp CATE upper endpoint under finite $\alpha$-moment outcomes, with Kallus--Mao--Zhou recovered as $\alpha \to \infty$ limit and strict tightening over support-matched MSM bounds; prior verdict: none. Angle 0 (seed 0, closed-form $W_\alpha$ factorisation + critical-alpha phase transition) was archived as \texttt{pid\_heavy\_tail\_cate\_bounds\_v1\_proposal\_angle0\_rejected.tex}; this angle is structurally orthogonal --- it targets the optimiser characterisation, not the width formula.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}

\bibitem{Tan2006} Tan, Z. (2006). A distributional approach for causal inference using propensity scores. \emph{Journal of the American Statistical Association} 101(476), 1619--1637.

\bibitem{KallusMaoZhou2019} Kallus, N., Mao, X., and Zhou, A. (2019). Interval estimation of individual-level causal effects under unobserved confounding. \emph{Proc.\ 22nd Int.\ Conf.\ on Artificial Intelligence and Statistics (AISTATS)}, PMLR 89:2281--2290.

\bibitem{YadlowskyNamkoongBasuDuchiTian2022} Yadlowsky, S., Namkoong, H., Basu, S., Duchi, J., and Tian, L. (2022). Bounds on the conditional and average treatment effect with unobserved confounding factors. \emph{Annals of Statistics} 50(5), 2587--2615.

\bibitem{DornGuoKallus2025} Dorn, J., Guo, K., and Kallus, N. (2025). Doubly-valid/doubly-sharp sensitivity analysis for causal inference with unmeasured confounding. \emph{Journal of the American Statistical Association} 120(550), 1129--1142.

\bibitem{AronowLee2013} Aronow, P.~M., and Lee, D.~K.~K. (2013). Interval estimation of population means under unknown but bounded probabilities of sample selection. \emph{Biometrika} 100(1), 235--240.

\bibitem{MiratrixWagerZubizarreta2018} Miratrix, L.~W., Wager, S., and Zubizarreta, J.~R. (2018). Shape-constrained partial identification of a population mean under unknown probabilities of sample selection. \emph{Biometrika} 105(1), 103--114.

\bibitem{Manski1990} Manski, C.~F. (1990). Nonparametric bounds on treatment effects. \emph{American Economic Review (Papers and Proceedings)} 80(2), 319--323.

\bibitem{AsiaeePalBeckHuling2026} Asiaee, A., Pal, S., Beck, C., and Huling, J.~D. (2026). Sharp bounds for generalization of causal effects. \emph{Proc.\ Conf.\ on Causal Learning and Reasoning (CLeaR)}, PMLR (to appear); arXiv:2602.09595.

\bibitem{JungKang2026} Jung, Y., and Kang, B. (2026). Information-theoretic bounds for conditional causal effects. \emph{Proc.\ Conf.\ on Causal Learning and Reasoning (CLeaR)}, PMLR (to appear); arXiv:2601.17160.

\bibitem{LordanSalehzadehNobari2026} Lordan, G., and Salehzadeh Nobari, K. (2026). Tail-uncertainty treatment-effect bounds. SSRN working paper 6695947.

\bibitem{TudballBowdenHughesTilling2023SampleConstrained} Tudball, M.~J., Bowden, J., Hughes, R.~A., and Tilling, K. (2023). Sample-constrained partial identification with application to selection bias. \emph{Biometrika} 110(4), 1011--1029.

\end{thebibliography}

\end{document}
