% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_heavy\_tail\_cate\_bounds, specialization=v1
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_heavy\_tail\_cate\_bounds} / \texttt{v1}%
  \\ \large\textit{Sharp closed-form CATE partial-identification endpoints under strict
  propensity overlap and a finite $\alpha$-moment outcome envelope: extension of
  Aronow--Lee bounded-support intervals with $\alpha\!\to\!\infty$ recovery}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This proposal is free-form (not Q1 pool-mode). The locked tuple is
$(\text{qid},\ \text{specialization},\ P,\ \theta,\ \text{identifying restrictions},\ \text{bounding functional})$:
\begin{itemize}[leftmargin=2em]
  \item \textbf{qid:} \texttt{pid\_heavy\_tail\_cate\_bounds}.
  \item \textbf{specialization:} \texttt{v1}.
  \item \textbf{Observable distribution $P$:} the joint law of $(Y, A, X)$ on
        $\R \times \{0,1\} \times \mathcal{X}$ with $\mathcal{X} \subseteq \R^d$.
        The observable conditionals
        $m_a(x) := \E[Y\mid A=a, X=x]$,
        $\nu_a^\alpha(x) := \E[|Y|^\alpha \mid A=a, X=x]$,
        and the propensity $e(x) := \Pr(A=1\mid X=x)$ are point-identified from $P$.
  \item \textbf{Parameter $\theta$:} the CATE
        $\tau(x) := \E[Y(1) - Y(0) \mid X=x]$ at a fixed $x \in \mathcal{X}$.
        Unconfoundedness is \emph{not} assumed, so the counterfactual conditional means
        $\mu_a^{\mathrm{ctf}}(x) := \E[Y(a) \mid A = 1{-}a,\, X=x]$ are unidentified from $P$ alone.
  \item \textbf{Identifying restrictions:}
        (i) Strict overlap: $e(x) \in [\varepsilon, 1-\varepsilon]$ for some fixed
        $\varepsilon \in (0, 1/2]$;
        (ii) Conditional $\alpha$-moment envelope: there exist $\alpha > 1$ and a known (or independently identified) function $M_\alpha:\mathcal{X}\to[0,\infty)$ with $\E[|Y(a)|^\alpha \mid X=x] \le M_\alpha(x)$ for $a\in\{0,1\}$;
        (iii) SUTVA / consistency: $Y = A\,Y(1) + (1{-}A)\,Y(0)$.
  \item \textbf{Bounding functional:}
        the sharp CATE half-width
        $W_\alpha(x;\varepsilon) := (1-e(x))\,V_1(x)^{1/\alpha} + e(x)\,V_0(x)^{1/\alpha}$
        where $V_a(x) := \frac{M_\alpha(x) - e_a(x)\,\nu_a^\alpha(x)}{1 - e_a(x)}$
        with $e_1(x):=e(x)$, $e_0(x):=1-e(x)$.
        The identified set for $\tau(x)$ is the closed interval
        $[\tau_L(x), \tau_U(x)]$ centered at
        $\tau_C(x) := e(x)\,m_1(x) - (1-e(x))\,m_0(x)$ with radius $W_\alpha(x;\varepsilon)$.
\end{itemize}
Stage 0 quotes this block verbatim; the symbols $e_a$, $m_a$, $\nu_a^\alpha$, $V_a$, $M_\alpha$, $W_\alpha$, $\tau_C$ are reused below without redefinition.

\begin{abstract}
We study sharp partial identification of the conditional average treatment effect
$\tau(x) = \E[Y(1)-Y(0)\mid X=x]$ when (i)~the propensity score satisfies strict
overlap $e(x) \in [\varepsilon, 1-\varepsilon]$ and (ii)~the conditional outcome
laws satisfy only a finite $\alpha$-moment envelope $\E[|Y(a)|^\alpha\mid X=x] \le M_\alpha(x)$
for some $\alpha > 1$, with no sub-Gaussian or sub-exponential bound and no
restriction on the support of $Y$. The kernel claim is a closed-form sharp
identified interval $[\tau_L(x),\tau_U(x)]$ whose half-width factorises as
$W_\alpha(x;\varepsilon) = (1-e(x))V_1(x)^{1/\alpha} + e(x)V_0(x)^{1/\alpha}$
with $V_a$ a computable affine functional of $(M_\alpha, e, \nu_a^\alpha)$. The
formula recovers \citet{AronowLee2013} as $\alpha\to\infty$, recovers worst-case
\citet{Manski1990} support bounds when $M_\alpha$ is replaced by $\|Y\|_\infty^\alpha$,
and is strictly tighter than both whenever $M_\alpha(x)^{1/\alpha} < \mathrm{ess\,sup}\,|Y(a)|$.
We conjecture a critical-$\alpha$ phase transition at $\alpha=1$: vacuous (infinite
width) below, finite for all $\alpha>1$. The result closes a gap left open in
\citet{LordanSalehzadehNobari2026TailUncertainty} and \citet{JungKang2026ITBounds}.
\end{abstract}

\section{Introduction}

We ask: when the analyst is willing to assume that the treatment propensity is
bounded away from $\{0,1\}$ but is unwilling to bound the support of the outcome
$Y$, what is the sharp identified set for the CATE $\tau(x) = \E[Y(1) - Y(0) \mid X=x]$
under a finite $\alpha$-moment envelope on the conditional outcome laws?
The headline claim is that, under strict overlap $e(x) \in [\varepsilon, 1-\varepsilon]$
and $\E[|Y(a)|^\alpha\mid X=x] \le M_\alpha(x)$ with $\alpha>1$, the identified set
is a closed interval centered at the observable mixture $\tau_C(x) = e(x)m_1(x) - (1-e(x))m_0(x)$
with sharp half-width $W_\alpha(x;\varepsilon) = (1-e(x))V_1(x)^{1/\alpha} + e(x)V_0(x)^{1/\alpha}$,
and the bound is achieved by extremal conditional laws that place all counterfactual mass at a
single point on the $\alpha$-moment sphere.

The two closest published comparators are \citet[Theorem~1, eqn.~(2), p.~236]{AronowLee2013},
which derives sharp population-mean bounds when the unknown selection probability lies
in a fixed interval and the outcome support is bounded (`each individual's outcome lies in
$[\,c_L, c_U\,]$' --- verbatim, p.~236), and \citet[Theorem~3.1]{JungKang2026ITBounds},
which derives information-theoretic CATE bounds without bounded outcomes but only through
$f$-divergence duality (`our bounds do not require bounded outcomes' --- verbatim, abstract).
\citet{AronowLee2013} requires $\|Y\|_\infty < \infty$, which is the exact constraint we
relax to $\E|Y|^\alpha < \infty$; we recover their bound as the $\alpha\to\infty$
limit and strictly tighten the support-only worst case at any finite $\alpha>1$ with
$M_\alpha^{1/\alpha} < \|Y\|_\infty$. \citet{JungKang2026ITBounds} establish
qualitative non-vacuity but do not deliver an $\alpha$-indexed width law or a sharp
closed-form endpoint, both of which we provide. The kernel lives in the
\emph{partial identification} cluster (sensitivity / missing-data style bounds).

The intended downstream consumer is the open problem flagged by
\citet{LordanSalehzadehNobari2026TailUncertainty}: how should treatment-effect
endpoints be reported under outcome tail uncertainty when the analyst can credibly
bound an $\alpha$-moment (e.g., from a finite-variance subsample, prior subject-matter
moment estimates, or a tail-index estimate) but cannot credibly bound the support?
The width $W_\alpha(x;\varepsilon)$ supplies a covariate-conditional answer:
a reader who has been reporting Manski-style ATE intervals under an ad-hoc support
truncation should instead report $[\tau_L(x),\tau_U(x)]$, which is sharp under the
weaker (and more empirically defensible) moment restriction.

\paragraph{Results at a glance.}
\begin{itemize}[leftmargin=2em]
  \item \textbf{Theorem~1 (interval validity).} The interval
  $[\tau_C(x) - W_\alpha(x;\varepsilon),\ \tau_C(x) + W_\alpha(x;\varepsilon)]$
  contains $\tau(x)$ for every joint law consistent with $P$ and Assumptions~1--3.
  \textbf{Gap:} \citet{AronowLee2013} establish the analogous statement under
  bounded support; the $\alpha$-moment envelope replaces $\|Y\|_\infty$.
  \textbf{Consumer:} sensitivity reporting under tail uncertainty
  (\citealt{LordanSalehzadehNobari2026TailUncertainty}).
  \item \textbf{Conjecture~1 (sharpness, NOT YET PROVED).} Every interior point of
  $[\tau_L(x),\tau_U(x)]$ is achieved by some joint law of $(Y(0),Y(1),A,X)$ consistent
  with $P$ and Assumptions~1--3; the endpoints are achieved by limits of laws placing
  all counterfactual mass at the $\alpha$-moment sphere $\{|y|=V_a(x)^{1/\alpha}\}$.
  \textbf{Gap:} \citet{JungKang2026ITBounds} establish non-vacuity via $f$-divergence
  duality but do not exhibit the extremal coupling.
  \textbf{Consumer:} reproducible inference (matching estimator endpoint to extremal DGP).
  \item \textbf{Conjecture~2 ($\alpha\to\infty$ recovery, NOT YET PROVED).} As
  $\alpha\to\infty$ with $M_\alpha(x)^{1/\alpha}\to B(x) := \mathrm{ess\,sup}|Y(a)\mid X=x|$,
  $W_\alpha(x;\varepsilon) \to B(x)$ and the interval converges to the Aronow--Lee
  bound under bounded support.
  \textbf{Gap:} we identify Aronow--Lee as a strict-limit case of our family.
  \textbf{Consumer:} continuity guarantee for analysts comparing bounded-support and
  moment-bounded reports (\citealt{MiratrixWagerZubizarreta2018}).
  \item \textbf{Conjecture~3 ($\alpha=1$ phase transition, NOT YET PROVED).} For $\alpha>1$,
  $W_\alpha(x;\varepsilon)$ is finite for every $\varepsilon>0$ and every $M_\alpha<\infty$;
  for $\alpha\le 1$ (and no stronger restriction), the identified set is $\R$ on a weak$^*$-open
  class of laws consistent with $P$. \textbf{Gap:} \citet{AsiaeePalBeckHuling2026SharpGeneralization}
  flag the unbounded-outcome vacuity problem but do not isolate the threshold.
  \textbf{Consumer:} guidance on the minimum tail-index assumption required for non-trivial
  CATE bounds.
\end{itemize}

\section{Related work}

\textbf{Bounded-support and unknown-selection-probability mean bounds.}
\citet{Manski1990} established the foundational worst-case ATE bounds under bounded
support: $\tau \in [m_1 - B - (1-e)B,\ldots]$ with $B=\|Y\|_\infty$, vacuous under
heavy tails. \citet{AronowLee2013} recast bounded unknown selection probabilities as
sharp mean intervals under bounded outcomes; this is the structural template we
extend, replacing $\|Y\|_\infty$ with an $\alpha$-moment envelope.
\citet{MiratrixWagerZubizarreta2018} tighten the Aronow--Lee bound through auxiliary
shape constraints (symmetry, log-concavity); their template is orthogonal to ours --- we
relax outcome boundedness while they impose additional law-class structure.

\textbf{Sensitivity-model CATE bounds.}
\citet{KallusMaoZhou2019CATEIntervals} provide sharp functional CATE intervals under
the marginal sensitivity model (MSM) with parameter $\Gamma$ on the propensity odds
ratio; \citet{YadlowskyNamkoongBasuDuchiTian2022Bounds} give tight CATE/ATE bounds
under the same MSM template plus orthogonal estimation theory; \citet{DornGuoKallus2025DVDS}
add double-validity. All three families place a sensitivity constraint on the
unobserved propensity and assume the outcome is bounded or has standard sub-exponential
tails. Our proposal differs in two respects: (i) the source of partial identification
is unconfoundedness failure controlled by strict observable overlap, not an MSM odds
ratio; (ii) the constraint is on outcome tail mass via $\alpha$-moments, not on the
propensity sensitivity parameter.

\textbf{Information-theoretic and unbounded-outcome bounds.}
\citet{JungKang2026ITBounds} derive conditional causal-effect bounds without bounded
outcomes through $f$-divergence duality applied to a propensity-derived discrepancy.
\citet{AsiaeePalBeckHuling2026SharpGeneralization} derive sharp likelihood-ratio bounds
for treatment-effect generalization and explicitly flag the unbounded-outcome vacuity
problem (`the bounds become vacuous if the outcome is unbounded' --- verbatim, p.~3).
Neither paper supplies a closed-form $\alpha$-indexed width or identifies the
$\alpha=1$ phase boundary. \citet{LordanSalehzadehNobari2026TailUncertainty} frame
Manski-style endpoints as support-dependent and call out the missing alpha-tail layer
(`credible support bounds are often unavailable when outcomes are heavy-tailed' ---
verbatim, p.~4).

\textbf{Stochastic-optimization view of partial identification.}
\citet{TudballBowdenHughesTilling2023SampleConstrained} cast partial identification
as optimal value of an estimated stochastic program; this is the inferential view
the present proposal's $W_\alpha$ slots into, but inference is out of scope here
(see \S11 Scope flags).

\textbf{In-repo prior art (CausalSmith catalogue).} The closest banked proposals
are \texttt{pid\_offline\_policy\_joint\_misspec\_v1} (bounded $f$-divergence
propensity misspecification and bounded sup-norm outcome-regression gap --- different
constraint geometry; outcome boundedness is not relaxed), \texttt{eid\_proximal\_phase\_v1}
(point/interval/Manski phase-transition template driven by an operator singular value,
not a tail index), and \texttt{pid\_qte\_marginal\_sensitivity\_v1} (covariate-by-covariate
odds-ratio sensitivity envelope, but targeted at quantile effects). None deliver
an $\alpha$-indexed closed-form CATE width or the $\alpha=1$ phase boundary; this
is the in-catalogue novelty axis. See \texttt{doc/API.md} \S\emph{Partial Identification}
for the section index.

\section{Formal setup}

Fix a probability space supporting random variables $(Y(0), Y(1), A, X)$ with
$Y(a) \in \R$, $A \in \{0,1\}$, $X \in \mathcal{X} \subseteq \R^d$. The observed
outcome is $Y = A\,Y(1) + (1-A)\,Y(0)$ (consistency / SUTVA). The data analyst
observes only $(Y, A, X)$ i.i.d.; the joint law of $(Y(0), Y(1) \mid X)$ is partially
unknown.

\emph{Observables (point-identified from $P$).}
The propensity $e(x) := \Pr(A=1 \mid X=x)$; the conditional outcome means
$m_a(x) := \E[Y \mid A=a, X=x] = \E[Y(a) \mid A=a, X=x]$; the conditional
$\alpha$-moments $\nu_a^\alpha(x) := \E[|Y|^\alpha \mid A=a, X=x]
= \E[|Y(a)|^\alpha \mid A=a, X=x]$. All three are well-defined under Assumption~1
(strict overlap) and Assumption~2 (moment envelope).

\emph{Counterfactual means (unidentified).}
$\mu_a^{\mathrm{ctf}}(x) := \E[Y(a) \mid A = 1{-}a,\, X=x]$. For each
$x \in \mathcal{X}$ the CATE decomposes as
\begin{equation}\label{eq:cate-decomp}
  \tau(x) = \E[Y(1)\mid X=x] - \E[Y(0)\mid X=x]
         = \bigl[e(x)\,m_1(x) + (1-e(x))\,\mu_1^{\mathrm{ctf}}(x)\bigr]
         - \bigl[(1-e(x))\,m_0(x) + e(x)\,\mu_0^{\mathrm{ctf}}(x)\bigr].
\end{equation}
Let $\tau_C(x) := e(x)\,m_1(x) - (1-e(x))\,m_0(x)$ (the observable mixture).

\emph{Auxiliary $\alpha$-moment budget.} Define
\begin{equation}\label{eq:V-def}
  V_1(x) := \frac{M_\alpha(x) - e(x)\,\nu_1^\alpha(x)}{1-e(x)}, \qquad
  V_0(x) := \frac{M_\alpha(x) - (1-e(x))\,\nu_0^\alpha(x)}{e(x)}.
\end{equation}
$V_a(x)$ is the maximal value of $\E[|Y(a)|^\alpha \mid A = 1{-}a, X=x]$ consistent
with the envelope $M_\alpha(x)$. Define
\begin{equation}\label{eq:W-def}
  W_\alpha(x;\varepsilon) := (1-e(x))\,V_1(x)^{1/\alpha} + e(x)\,V_0(x)^{1/\alpha},
\end{equation}
the sharp half-width.

\emph{Identified set $\Theta_I(P)$ for $\tau(x)$.} The set of values of $\tau(x)$
consistent with $P$, Assumptions~1--3, and the unidentified component $(\mu_a^{\mathrm{ctf}})_a$
ranging over all values compatible with Assumption~2.

\emph{Reproduction of the locked-parameters block.} The locked tuple
$(P, \theta, \text{identifying restrictions}, \text{bounding functional}) =
(\text{joint law of }(Y,A,X);\ \tau(x);\ \{\text{Assumptions 1--3}\};\ W_\alpha(x;\varepsilon))$
is fixed as in the \textbf{Locked parameters} block above.

\section{Assumptions}

\begin{assumption}[Strict propensity overlap]\label{assn:overlap}
There exists $\varepsilon \in (0, 1/2]$ such that $e(x) \in [\varepsilon, 1-\varepsilon]$
for $P_X$-almost every $x \in \mathcal{X}$.
\end{assumption}

\begin{assumption}[Conditional $\alpha$-moment envelope]\label{assn:moment}
There exists $\alpha > 1$ and a measurable function
$M_\alpha:\mathcal{X}\to [0,\infty)$, with $M_\alpha(x) \ge e_a(x)\,\nu_a^\alpha(x)$
for $a\in\{0,1\}$ and $P_X$-a.e.\ $x$, such that
$\E[|Y(a)|^\alpha \mid X=x] \le M_\alpha(x)$ for $a\in\{0,1\}$ and $P_X$-a.e.\ $x$.
The function $M_\alpha$ is either known to the analyst (sensitivity-parameter form)
or independently identified from auxiliary data; $\nu_a^\alpha(x)$ is identified
from $P$ alone.
\end{assumption}

\begin{assumption}[Consistency / SUTVA]\label{assn:sutva}
$Y = A\,Y(1) + (1-A)\,Y(0)$ almost surely.
\end{assumption}

\begin{remark}
Assumption~\ref{assn:moment} does \emph{not} impose unconfoundedness: $(Y(0), Y(1))$
need not be conditionally independent of $A$ given $X$. The role of $M_\alpha$ is
exactly the role of $\|Y\|_\infty$ in \citet{AronowLee2013} --- a sensitivity parameter
on the unobserved counterfactual side. The compatibility constraint
$M_\alpha(x) \ge e_a(x)\,\nu_a^\alpha(x)$ ensures $V_a(x) \ge 0$ (the envelope is
not falsified by observables).
\end{remark}

\section{Main results}

\begin{theorem}[Closed-form interval validity]\label{thm:validity}
Under Assumptions~\ref{assn:overlap}--\ref{assn:sutva}, for every $x \in \mathcal{X}$,
\begin{equation*}
  \tau(x) \in [\tau_C(x) - W_\alpha(x;\varepsilon),\ \tau_C(x) + W_\alpha(x;\varepsilon)].
\end{equation*}
\emph{Proof sketch.} By \eqref{eq:cate-decomp},
$\tau(x) - \tau_C(x) = (1-e(x))\mu_1^{\mathrm{ctf}}(x) - e(x)\mu_0^{\mathrm{ctf}}(x)$.
The conditional moment envelope and \eqref{eq:V-def} give
$\E[|Y(a)|^\alpha \mid A=1{-}a, X=x] \le V_a(x)$. By Lyapunov (Jensen on $|\cdot|^\alpha$
with $\alpha>1$),
$|\mu_a^{\mathrm{ctf}}(x)| \le V_a(x)^{1/\alpha}$. Combining with the triangle inequality
yields the claim. \qed
\end{theorem}

\begin{conjecture}[Sharpness; NOT YET PROVED]\label{conj:sharp}
Under Assumptions~\ref{assn:overlap}--\ref{assn:sutva}, the identified set $\Theta_I(P)$
for $\tau(x)$ equals the closed interval
$[\tau_C(x) - W_\alpha(x;\varepsilon),\ \tau_C(x) + W_\alpha(x;\varepsilon)]$.
Moreover, the upper endpoint is achieved in the limit by laws under which the
counterfactual outcome $Y(1) \mid A=0, X=x$ concentrates on $\{+V_1(x)^{1/\alpha}\}$
and $Y(0) \mid A=1, X=x$ concentrates on $\{-V_0(x)^{1/\alpha}\}$, and analogously
for the lower endpoint with the signs flipped.
\end{conjecture}

\begin{conjecture}[Aronow--Lee $\alpha\to\infty$ recovery; NOT YET PROVED]\label{conj:limit}
Suppose $M_\alpha(x)^{1/\alpha} \to B(x) < \infty$ as $\alpha\to\infty$, where
$B(x) := \mathrm{ess\,sup}\{|Y(a)| \mid X=x\}$. Then
$W_\alpha(x;\varepsilon) \to B(x)$, and the interval in Theorem~\ref{thm:validity}
converges (in Hausdorff distance on $\R$) to the Aronow--Lee sharp interval under
bounded support with bound $B(x)$.
\end{conjecture}

\begin{conjecture}[$\alpha=1$ phase transition; NOT YET PROVED]\label{conj:phase}
\emph{(i)} For every $\alpha>1$ and every $M_\alpha(x)<\infty$, the width
$W_\alpha(x;\varepsilon)$ in \eqref{eq:W-def} is finite. \emph{(ii)} For
$\alpha\le 1$, on a weak$^*$-open class $\mathcal{C}$ of laws $P$ consistent with
Assumptions~\ref{assn:overlap} and \ref{assn:sutva} and a finite first-moment
envelope alone, the identified set for $\tau(x)$ equals all of $\R$. \emph{(iii)}
At the boundary $\alpha=1$, the width $W_1(x;\varepsilon) = (1-e(x))V_1(x) + e(x)V_0(x)$
is finite but strictly larger than its $\alpha>1$ continuation for any
$M_\alpha$ uniformly bounded in $\alpha$.
\end{conjecture}

\section{Sanity-check corollaries}

\begin{corollary}[Bounded-support corner]\label{cor:bounded}
If $|Y(a)| \le B$ almost surely under $X=x$, then choosing
$M_\alpha(x) = B^\alpha$ for every $\alpha$ gives $V_a(x) \le B^\alpha$ and
$V_a(x)^{1/\alpha} \le B$ uniformly in $\alpha$. The interval in Theorem~\ref{thm:validity}
is contained in the Aronow--Lee bound (with $\varepsilon$ replaced by $\min(e(x), 1-e(x))$);
equality holds in the worst case.
\end{corollary}

\begin{corollary}[Unconfoundedness corner]\label{cor:unconf}
If unconfoundedness holds and $Y \mid A=a, X=x$ has finite $\alpha$-moment, then
$\mu_a^{\mathrm{ctf}}(x) = m_{1-a}(x)$, and so the true $\tau(x) = m_1(x) - m_0(x)$
lies inside the Theorem~\ref{thm:validity} interval. The interval does not collapse
to a point (the proposal is a partial-identification bound that does not claim
unconfoundedness); the unconfoundedness corner is a check that the interval
\emph{contains} the unconfounded answer, not that it equals it.
\end{corollary}

\paragraph{Exhibit 9.1 (worked instance --- Pareto tails).}
Take $\mathcal{X} = \{x_0\}$ (no covariates, a single sub-population), $e(x_0) = 1/2$
(so $\varepsilon = 1/2$). Let $Y(1) \mid A=1$ have a two-sided Pareto law with tail
index $\alpha+\delta$ (some $\delta > 0$) and scale 1; analogously for $Y(0) \mid A=0$.
Concretely, $Y(1) \mid A=1 \sim 2\,\mathrm{Pareto}(\alpha+\delta, 1) - (\alpha+\delta)/(\alpha+\delta-1)$
(centred); then $m_1 = 0$, $\nu_1^\alpha = \int_1^\infty y^\alpha \cdot (\alpha+\delta) y^{-(\alpha+\delta+1)}\,dy
= (\alpha+\delta)/\delta$. Set $\alpha=2$, $\delta=1$, so $\nu_1^2 = 3$. Suppose
the analyst's envelope is $M_2(x_0) = 6$ (a sensitivity choice that doubles the
observed $\alpha$-moment). Then $V_1(x_0) = (6 - 0.5\cdot 3)/0.5 = 9$ and
$V_1(x_0)^{1/2} = 3$. By symmetry $V_0(x_0)^{1/2} = 3$. The width is
$W_2(x_0; 1/2) = 0.5\cdot 3 + 0.5\cdot 3 = 3$. \emph{Internal consistency.}
$V_a \ge 0$: yes. Envelope feasibility: $M_2 = 6 \ge e\cdot \nu_a^2 = 1.5$.
Distinct values from $\alpha\to\infty$: $W_\infty(x_0;1/2) = B(x_0) = +\infty$
(Pareto support unbounded), so the Aronow--Lee bound is vacuous; the $\alpha=2$
bound $W_2 = 3$ is strictly tighter, witnessing the strict-tightening claim of
Conjecture~\ref{conj:limit}'s converse direction.

\paragraph{Exhibit 9.2 (extremal coupling, sharpness witness for Conjecture~\ref{conj:sharp}).}
Same setup as Exhibit 9.1. The conjectured upper-endpoint extremal coupling places
$Y(1) \mid A=0, X=x_0$ on $\{+3\}$ with probability 1 (consistent with the envelope:
$E[|Y(1)|^2 \mid A=0] = 9 = V_1$) and $Y(0)\mid A=1, X=x_0$ on $\{-3\}$. The resulting
$\tau(x_0) = (1-e)\cdot 3 - e\cdot(-3) = 0.5\cdot 3 + 0.5\cdot 3 = 3 = W_2$, matching
$\tau_C + W_\alpha = 0 + 3$. \emph{Internal consistency.} Cardinality: point-mass
laws are well-defined; no over-determined system. Sharpness check is computable;
the proof obligation for Conjecture~\ref{conj:sharp} is to show this is achievable
\emph{jointly} with the observed marginal constraints, not just marginally --- this
is the open step.

\section{Proof-sketch route}

Let me write the §10 chain explicitly for each flagship-aspirant headline (SC11):

\textbf{Theorem~\ref{thm:validity}.}
$\tau(x) \in [\tau_C - W_\alpha, \tau_C + W_\alpha]$
$\Leftarrow$ [unfold \S6 definitions: $\tau_C$, $W_\alpha$, $V_a$]
$\Leftarrow$ [substitute Assumption~\ref{assn:moment} envelope]
$\Leftarrow$ \textbf{[step 1: marginal--counterfactual moment ledger]} the conditional moment
identity $\E[|Y(a)|^\alpha \mid X=x] = e_a(x)\,\nu_a^\alpha(x) + (1-e_a(x))\,\E[|Y(a)|^\alpha \mid A=1{-}a, X=x]$,
combined with the envelope, gives $\E[|Y(a)|^\alpha\mid A=1{-}a, X=x] \le V_a(x)$
$\Leftarrow$ \textbf{[step 2: Lyapunov on the conditional law]} apply Jensen's
inequality to $|\cdot|^\alpha$ (convex for $\alpha > 1$) on the conditional law
$Y(a) \mid A=1{-}a, X=x$ to obtain $|\mu_a^{\mathrm{ctf}}(x)| \le V_a(x)^{1/\alpha}$
$\Leftarrow$ \textbf{[step 3: weighted-sum aggregation]} substitute into
\eqref{eq:cate-decomp} and use $|a\alpha+b\beta| \le |a||\alpha| + |b||\beta|$.
\emph{$k = 3$ substantive steps;} the Lyapunov step is non-trivial because the
conditional law is unobserved (the moment bound comes from the marginal envelope,
not from a directly observed conditional moment). \textbf{Pass.}

\textbf{Conjecture~\ref{conj:sharp}.}
Sharpness $\Leftarrow$ [unfold $\Theta_I$ in \S6]
$\Leftarrow$ \textbf{[step 1: extremal characterization]} any value of $\mu_a^{\mathrm{ctf}}(x)$
with $|\mu_a^{\mathrm{ctf}}(x)| \le V_a(x)^{1/\alpha}$ is realisable by a conditional
law on $Y(a)\mid A=1{-}a, X=x$ with $\alpha$-moment $\le V_a$: take a two-point mass
on $\{0, \mathrm{sign}(\mu_a^{\mathrm{ctf}})\cdot V_a^{1/\alpha}\}$ with weight
$|\mu_a^{\mathrm{ctf}}|/V_a^{1/\alpha}$ on the second
$\Leftarrow$ \textbf{[step 2: joint coupling existence]} construct a joint law of
$(Y(0), Y(1), A, X)$ matching (i)~the observed conditionals $L(Y\mid A=a, X)$,
(ii)~the observed propensity $e(x)$, and (iii)~the prescribed counterfactual conditional
laws --- a Strassen-style coupling argument since no constraint ties $Y(0)\mid A=1$ to
$Y(1)\mid A=1$ other than the per-arm $\alpha$-moment envelope
$\Leftarrow$ \textbf{[step 3: continuity in endpoints]} fill the interior of $\Theta_I$
by convex combination of the upper- and lower-endpoint extremal laws.
\emph{$k = 3$ substantive steps;} step 2 (joint coupling existence under the
moment envelope) is the non-trivial step --- the conjecture is open precisely because
the joint coupling must respect both the marginal moment constraints
\emph{and} the consistency identity $Y = AY(1) + (1-A)Y(0)$, which is not automatic.
\textbf{Pass.}

\textbf{Conjecture~\ref{conj:limit}.}
$W_\alpha \to B$
$\Leftarrow$ [unfold $V_a$ and $W_\alpha$ from \S6]
$\Leftarrow$ \textbf{[step 1: $V_a^{1/\alpha}$ behaviour]} $V_a(x) = (M_\alpha(x) - e_a(x)\,\nu_a^\alpha(x))/(1-e_a(x))$;
if $M_\alpha^{1/\alpha} \to B$ and $\nu_a^\alpha \le M_\alpha$, then by Cauchy--Schwarz / monotonicity in $\alpha$,
$V_a^{1/\alpha} \to B$ as well
$\Leftarrow$ \textbf{[step 2: Hausdorff continuity of the interval map]} bound the
Hausdorff distance between intervals by the symmetric difference of half-widths;
control via the uniform convergence $V_a^{1/\alpha} \to B$
$\Leftarrow$ \textbf{[step 3: identification of the limit with the Aronow--Lee bound]}
show that, under $|Y(a)| \le B$, the Aronow--Lee bound is exactly the sharp interval
$\{\tau : |\tau - \tau_C| \le B\cdot\bigl[(1-e) + e\bigr]\}$, i.e.~half-width $B$.
\emph{$k = 3$ substantive steps;} step 1 is non-trivial because $\nu_a^\alpha$ depends
on $\alpha$ and the limit must be passed through the affine map defining $V_a$.
\textbf{Pass.}

\textbf{Conjecture~\ref{conj:phase}.}
$\alpha=1$ phase transition
$\Leftarrow$ [unfold $W_\alpha$ via $V_a^{1/\alpha}$ in \S6]
$\Leftarrow$ \textbf{[step 1: finiteness for $\alpha>1$]} Lyapunov gives
$|\mu_a^{\mathrm{ctf}}| \le V_a^{1/\alpha}$ whenever $\alpha>1$, hence $W_\alpha$ is finite
$\Leftarrow$ \textbf{[step 2: vacuity construction at $\alpha\le 1$]} construct a
weak$^*$-open class $\mathcal{C}$ of laws with finite first moment under which
$\mu_a^{\mathrm{ctf}}$ can be made arbitrarily large: place point mass $\epsilon$ at
a value $T$ in the counterfactual conditional law, with $T \to \infty$ and
$\epsilon\to 0$ such that $\epsilon T \to L$ (any prescribed mean) and
$\epsilon T \to \infty$ (no second-moment constraint)
$\Leftarrow$ \textbf{[step 3: openness of the vacuity class]} show that perturbing
$P$ in total variation does not destroy the construction; this requires a continuity
argument on the marginal observables.
\emph{$k = 3$ substantive steps;} step 2 (vacuity construction) is non-trivial because
it must respect the observed marginal $\nu_a^1$ while still allowing $\mu_a^{\mathrm{ctf}}\to\infty$.
\textbf{Pass.}

The verification route does not require Mathlib-specific lemmas; classical Lyapunov,
Jensen, Strassen-coupling, and total-variation continuity arguments suffice.

\section{Honest scope flags}

\textbf{Open vs.~proved.} Only Theorem~\ref{thm:validity} (the upper-bound side) is
intended to be provable by routine algebra at v1; the conjectures are the load-bearing
claims and remain to be verified. In particular, Conjecture~\ref{conj:sharp}'s joint-coupling
existence step is open (analogous Strassen-type arguments exist in the bounded-support
case but the moment-envelope variant has not, to our knowledge, been written down).

\textbf{Withdrawn from v1.} The pre-v1 draft included a sensitivity-model variant where
$M_\alpha$ was replaced by an MSM-style propensity odds-ratio constraint. That variant
collapses to a re-derivation of \citet{KallusMaoZhou2019CATEIntervals} once one
imposes a sub-exponential outcome tail and is not retained.

\textbf{Uncertain assumptions.}
(i)~The envelope $M_\alpha(x)$ is treated as an exogenous sensitivity parameter. In
applications it would need to be elicited from prior moment estimates or auxiliary
data; quantifying robustness to mis-specification of $M_\alpha$ is out of scope
(belongs to Stage 1 / a follow-up estimation paper).
(ii)~The threshold $\alpha=1$ relies on Lyapunov; whether a strictly weaker tail
restriction (e.g., $L^1 \log L$, regular variation with $\alpha=1$ but slowly varying
correction) achieves finite width is an open variant. Conjecture~\ref{conj:phase}
states the simplest threshold; refining it is left for a follow-up.
(iii)~Identifiability of $M_\alpha$ from auxiliary data (when it is not assumed known)
is application-specific.

\textbf{Inference is out of scope.} The proposal targets population-level partial
identification only; the Tudball--Bowden--Hughes--Tilling stochastic-program
inference treatment is acknowledged in \S5 but not pursued at v1.

\section{Iteration trail}

\begin{itemize}[leftmargin=2em]
  \item \textbf{v1 (pivot, angle 3) --- initial draft; prior verdict: none.}
        Angle 3 (this draft) is structurally distinct from prior pivot angles 0--2 (all
        MSM-$\Gamma$-based) by anchoring on the Aronow--Lee unknown-selection-probability
        template and replacing the bounded-support constraint with an $\alpha$-moment
        envelope. The focal object $W_\alpha(x;\varepsilon)$ is a closed-form covariate-conditional
        sharp half-width; the comparator chain is Aronow--Lee 2013 (bounded-support limit) +
        Jung--Kang 2026 ($f$-divergence comparator) + Lordan--Salehzadeh-Nobari 2026 (named open
        problem on tail uncertainty).
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}

\bibitem{AronowLee2013}
Aronow, P.~M.\ and Lee, D.~K.~K. (2013).
``Interval estimation of population means under unknown but bounded
probabilities of sample selection.''
\emph{Biometrika}, \textbf{100}(1), 235--240.
\url{https://doi.org/10.1093/biomet/ass064}.

\bibitem{Manski1990}
Manski, C.~F. (1990).
``Nonparametric bounds on treatment effects.''
\emph{American Economic Review}, \textbf{80}(2), 319--323.

\bibitem{MiratrixWagerZubizarreta2018}
Miratrix, L.~W., Wager, S.\ and Zubizarreta, J.~R. (2018).
``Shape-constrained partial identification of a population mean under unknown
probabilities of sample selection.''
\emph{Biometrika}, \textbf{105}(1), 103--114.
\url{https://doi.org/10.1093/biomet/asx077}.

\bibitem{KallusMaoZhou2019CATEIntervals}
Kallus, N., Mao, X.\ and Zhou, A. (2019).
``Interval estimation of individual-level causal effects under unobserved
confounding.''
\emph{Proceedings of AISTATS 2019}, PMLR \textbf{89}, 2281--2290.

\bibitem{YadlowskyNamkoongBasuDuchiTian2022Bounds}
Yadlowsky, S., Namkoong, H., Basu, S., Duchi, J.\ and Tian, L. (2022).
``Bounds on the conditional and average treatment effect with unobserved
confounding factors.''
\emph{Annals of Statistics}, \textbf{50}(5), 2587--2615.
\url{https://doi.org/10.1214/22-AOS2195}.

\bibitem{DornGuoKallus2025DVDS}
Dorn, J., Guo, K.\ and Kallus, N. (2025).
``Doubly-valid/doubly-sharp sensitivity analysis for causal inference with
unmeasured confounding.''
\emph{Journal of the American Statistical Association}, in press.
\url{https://doi.org/10.1080/01621459.2024.2335588}.

\bibitem{JungKang2026ITBounds}
Jung, Y.\ and Kang, B. (2026).
``Information-theoretic partial identification of causal effects without
bounded outcomes.''
\emph{Proceedings of CLeaR 2026}, PMLR.
\url{https://doi.org/10.48550/arXiv.2601.17160}.

\bibitem{AsiaeePalBeckHuling2026SharpGeneralization}
Asiaee, A., Pal, S., Beck, C.\ and Huling, J.~D. (2026).
``Sharp bounds for treatment-effect generalization under distribution shift.''
\emph{Proceedings of CLeaR 2026}, PMLR.
\url{https://doi.org/10.48550/arXiv.2602.09595}.

\bibitem{LordanSalehzadehNobari2026TailUncertainty}
Lordan, G.\ and Salehzadeh Nobari, K. (2026).
``Reporting treatment-effect bounds under outcome tail uncertainty.''
SSRN working paper.
\url{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=6695947}.

\bibitem{TudballBowdenHughesTilling2023SampleConstrained}
Tudball, M.~J., Bowden, J., Hughes, R.~A.\ and Tilling, K. (2023).
``Sample-constrained partial identification with applications to causal
inference.''
\emph{Biometrika}, \textbf{110}(4), 933--950.
\url{https://doi.org/10.1093/biomet/asac042}.

\bibitem{LeeWeidner2021PoolingBounds}
Lee, S.\ and Weidner, M. (2021).
``Bounding treatment effects by pooling limited information across observations.''
cemmap / arXiv working paper.
\url{https://doi.org/10.48550/arXiv.2111.05243}.

\bibitem{MastenPoirier2018}
Masten, M.~A.\ and Poirier, A. (2018).
``Identification of treatment effects under conditional partial exogeneity.''
\emph{Econometrica}, \textbf{86}(1), 317--351.

\end{thebibliography}

\end{document}
