\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\section*{panel_ppml_forbidden_comparison (v1)}

\paragraph{TL;DR.} The project characterizes the actual naive unit-and-time-fixed-effect PPML coefficient in staggered-adoption panels with heterogeneous proportional effects and within-cohort baseline heterogeneity. The unit-FE objective collapses exactly to a cohort-time Poisson projection, and enlarging a cell's true log proportional effect lowers the pooled coefficient exactly when that cell has a negative pseudo-true mean-weighted FWL residual. The global sign is also primitive and explicit: with h_gt=pi_g B_gt exp(D_gt delta_gt), row sums R_g, column sums C_t, total M, and treated total A, sign(beta_star)=sign(Phi) for Phi=M A-sum_{g,t}D_gt R_g C_t. Thus the zero frontier is Phi=0 and the all-positive-effect reversal region is Phi<0. In the equal-share T=4 family, reversal occurs exactly when y>(5*x^2+12*x-15)/2; at x=101/100 the sharp cutoff is 4441/4000, while W4 uses y=4. Operationally, Phi diagnoses when the pooled coefficient is an unsafe causal summary; the identified granular proportional effects and their positive counterfactual-share PTT are a distinct causal target, not a correction of beta_star. No fixed-T sampling or inference theorem is claimed.

\section{Project justification}

\paragraph{Gap.} Moreau-Kastler's two-individual, three-period PPML calculation exposes a wrong-comparison phenomenon but does not give either the general unit-FE derivative identity or a finite multicohort primitive sign frontier. Linear Goodman-Bacon and de Chaisemartin-D'Haultfoeuille decompositions cannot supply that frontier because PPML fitted-mean weights depend on the heterogeneous effect vector.

\paragraph{Niche.} Starting from the individual unit-and-time-FE population objective, the analysis allows unit baseline masses to vary within cohorts, collapses them only through cohort averages, and then eliminates the pseudo-true nuisance multipliers by the fitted row and column margins. This produces both a fitted-mean local diagnostic and a design-level primitive sign certificate in timing shares, untreated baseline masses, and the full effect vector.

\paragraph{Fill.} The proved results are the unit-FE collapse, the effect-dependent mean-weighted-FWL derivative rule, a non-vacuous four-cohort reversal, and the exact finite primitive theorem sign(beta_star)=sign(Phi). The T=4 subfamily has the sharp threshold y=(5*x^2+12*x-15)/2, equal to 4441/4000 at x=101/100. When Phi<0 under positive effects, the pooled PPML coefficient is diagnosed as an unsafe summary; researchers may instead report identified granular proportional effects and their counterfactual-share PTT, understood as a different causal estimand rather than a repaired beta_star.

\section{Related work}

MoreauKastler2025PTT is the direct conceptual anchor: Section 3.1, including equation (3.6), gives a two-individual, three-period individual-and-time-FE PPML wrong-comparison illustration and explains why proportional effects lack a linear aggregation identity. The present results extend that diagnosis to a general mean-weighted-FWL derivative identity and, after eliminating the endogenous Poisson margins, to the finite primitive certificate sign(beta_star)=sign(Phi). GoodmanBacon2021 supplies the canonical linear staggered-adoption comparison decomposition, and deChaisemartinDHaultfoeuille2020TWFE establishes negative treatment-cell weights for linear TWFE; both are benchmarks rather than PPML frontier results. NagengastYotov2025 estimates granular cohort-time PPML effects and aggregates them, which supports the diagnose-then-granular-effects strategy but does not reinterpret the misspecified pooled coefficient. Wooldridge2023NonlinearDiD supplies the multiplicative-parallel-trends causal structure, while White1982MisspecifiedML supplies generic pseudo-true-QMLE geometry. None of these references gives the exact Phi frontier or the T=4 threshold proved here.

\section{Setup}

Target (estimand / structural parameter): beta_star(delta), the limiting pseudo-true coefficient of naive unit-and-time-fixed-effect PPML under cohort-time proportional effects delta_gt.
Identifying functional / recovery map: sum_{g in C}sum_{t=1}^Tq_gt r_gt[m_gt(delta)-exp(r_gt'theta_star(delta))]=0, with beta_star(delta) the last coordinate of theta_star(delta).
\begin{itemize}
  \item $T$ --- integer; {4,5,...}; panel horizon $:= number of calendar periods$
  \item $C$ --- finite set; finite subsets of {2,...,T,infinity} containing infinity; timing support $:= adoption-cohort support$
  \item $g$ --- index; C; index $:= adoption-cohort index$
  \item $k$ --- index; C; index $:= cohort index of an effect perturbation$
  \item $t$ --- index; {1,...,T}; index $:= calendar-period index$
  \item $s$ --- index; {1,...,T}; index $:= calendar-period index of an effect perturbation$
  \item $u$ --- index; {1,...,T}; index $:= time-dummy index$
  \item $N$ --- integer; {N in Z: N>=|C|}; array size $:= number of units in the Nth panel$
  \item $i$ --- index; {1,...,N}; index $:= unit index$
  \item $j$ --- index; {2,...,N}; index $:= unit-dummy index$
  \item $n_gN$ --- integer; {1,...,N}; primitive timing-cell count $:= number of Nth-array units with cohort label g$
  \item $pi_gN$ --- scalar; (0,1]; Nth-array cohort share $:= n_gN/N$
  \item $pi_g$ --- positive scalar; (0,1); limiting cohort share $:= lim_{N->infinity} pi_gN$
  \item $q_gtN$ --- positive scalar; (0,1); finite-array cohort-time mass $:= n_gN/(NT)$
  \item $q_gt$ --- positive scalar; (0,1); limiting cohort-time mass $:= pi_g/T$
  \item $G_i$ --- fixed label; C; adoption date $:= adoption cohort of unit i, with exactly n_gN labels equal to g$
  \item $I_gN$ --- set; subsets of {1,...,N}; cohort index set $:= {i in {1,...,N}: G_i=g}$
  \item $D_gt$ --- binary scalar; {0,1}; cohort-time treatment indicator $:= 1{g<=t}, where 1{infinity<=t}=0$
  \item $D_it$ --- binary scalar; {0,1}; unit-time treatment indicator $:= D_{G_i,t}$
  \item $Y_it(d)$ --- potential outcome; R_+; potential outcome $:= period-t outcome of unit i under treatment state d$
  \item $Y_it$ --- random variable; R_+; observed outcome $:= D_it Y_it(1)+(1-D_it)Y_it(0)$
  \item $Pcal_N$ --- probability law; laws on potential-outcome arrays conditional on (G_i)_{i=1}^N; array sampling law $:= sampling law of {(Y_it(0),Y_it(1))_{t=1}^T:i=1,...,N}$
  \item $E_Pcal_N$ --- expectation operator; sampling expectation $:= expectation under Pcal_N$
  \item $b_iN$ --- positive scalar; (0,infinity); unit fixed-effect baseline $:= unit i untreated baseline mass in array N$
  \item $bar_b_gN$ --- positive scalar; (0,infinity); within-cohort average baseline mass $:= n_gN^(-1) sum_{i in I_gN} b_iN$
  \item $bar_b_g$ --- positive scalar; (0,infinity); limiting cohort baseline mass $:= lim_{N->infinity} bar_b_gN$
  \item $gamma_t0$ --- real scalar; R; untreated time effect $:= untreated time component, normalized by gamma_10=0$
  \item $delta_gt$ --- real scalar; R; heterogeneous causal effect $:= log proportional treatment effect in cohort-time cell (g,t)$
  \item $B_gtN$ --- positive scalar; (0,infinity); finite-array untreated cohort mean $:= bar_b_gN exp(gamma_t0)$
  \item $B_gt$ --- positive scalar; (0,infinity); limiting untreated cohort mean $:= bar_b_g exp(gamma_t0)$
  \item $m_itN(delta)$ --- positive scalar; (0,infinity); unit-time observed mean $:= b_iN exp(gamma_t0+D_it delta_{G_i,t})$
  \item $m_gtN(delta)$ --- positive scalar; (0,infinity); finite-array observed cohort mean $:= B_gtN exp(D_gt delta_gt)$
  \item $m_gt(delta)$ --- positive scalar; (0,infinity); limiting observed cohort mean $:= B_gt exp(D_gt delta_gt)$
  \item $v_itN$ --- vector; R^(N+T); intercept, unit-FE, time-FE, and treatment regressor $:= (1,(1{i=j})_{j=2}^N,(1{t=u})_{u=2}^T,D_it)'$
  \item $r_gt$ --- vector; R^(|C|+T); collapsed intercept, cohort-FE, time-FE, and treatment regressor $:= (1,(1{g=c})_{c in C minus {infinity}},(1{t=u})_{u=2}^T,D_gt)'$
  \item $theta_N$ --- vector; R^(N+T); unit-and-time-FE PPML argument $:= coefficient vector on v_itN whose last coordinate is beta$
  \item $theta$ --- vector; R^(|C|+T); collapsed PPML argument $:= coefficient vector on r_gt whose last coordinate is beta$
  \item $L_N(theta_N;delta)$ --- real functional; R^(N+T) x R^(|C|T) -> R; unit-FE population Poisson criterion $:= (NT)^(-1) sum_{i=1}^N sum_{t=1}^T[m_itN(delta)v_itN'theta_N-exp(v_itN'theta_N)]$
  \item $L_Nc(theta;delta)$ --- real functional; R^(|C|+T) x R^(|C|T) -> R; collapsed finite-array Poisson criterion $:= sum_{g in C}sum_{t=1}^T q_gtN[m_gtN(delta)r_gt'theta-exp(r_gt'theta)]$
  \item $L(theta;delta)$ --- real functional; R^(|C|+T) x R^(|C|T) -> R; limiting collapsed Poisson criterion $:= sum_{g in C}sum_{t=1}^T q_gt[m_gt(delta)r_gt'theta-exp(r_gt'theta)]$
  \item $beta_Nstar(delta)$ --- real scalar; R; unit-FE pseudo-true coefficient $:= last coordinate of the unique maximizer of L_N(theta_N;delta)$
  \item $theta_star(delta)$ --- vector-valued map; R^(|C|+T); limiting collapsed pseudo-true parameter $:= unique maximizer of L(theta;delta)$
  \item $beta_star(delta)$ --- real scalar; R; limiting naive unit-and-time-FE PPML coefficient $:= last coordinate of theta_star(delta)$
  \item $mu_star_gt(delta)$ --- positive scalar; (0,infinity); limiting fitted cohort-time mean $:= exp(r_gt'theta_star(delta))$
  \item $X_gt$ --- vector; R^(|C|+T-1); intercept, cohort-FE, and time-FE regressor $:= r_gt with its last treatment coordinate removed$
  \item $rho_star(delta)$ --- vector; R^(|C|+T-1); mean-weighted FE projection coefficient $:= argmin_rho sum_{g in C}sum_{t=1}^T q_gt mu_star_gt(delta)[D_gt-X_gt'rho]^2$
  \item $Wtilde_gt(delta)$ --- real scalar; R; pseudo-true mean-weighted-FWL treatment residual $:= D_gt-X_gt'rho_star(delta)$
  \item $hat_beta_N$ --- real random variable; R; reported sample coefficient $:= extended-MLE unit-and-time-FE PPML treatment coefficient with the finite-coordinate convention in def:sample-unit-fe-ppml$
  \item $R_T$ --- set; subsets of (simplex shares, baseline masses, effects); global sign frontier object $:= all-positive-effect unit-FE PPML sign-reversal region indexed by (pi_g,B_gt,delta_gt)$
  \item $W4$ --- constructed configuration; four-cohort, four-period limiting panels; non-vacuity witness $:= the equal-share unit-baseline configuration in def:four-cohort-witness$
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:cohort-share-limit]\label{ass:cohort-share-limit}
For every N>=|C| and every g in C, n_gN is positive and n_gN/N converges to pi_g in (0,1).
\par\smallskip\noindent\emph{Standard} (positive limiting cohort shares, \cite{deChaisemartinDHaultfoeuille2020TWFE}).
\end{assumption}

\begin{assumption}[ass:unit-untreated-exponential-mean]\label{ass:unit-untreated-exponential-mean}
E_Pcal_N[Y_it(0)]=b_iN exp(gamma_t0) for every i and t, with gamma_10=0.
\par\smallskip\noindent\emph{Standard} (unit-fixed-effect multiplicative parallel trends in an exponential mean, \cite{Wooldridge2023NonlinearDiD}).
\end{assumption}

\begin{assumption}[ass:within-cohort-baseline-limit]\label{ass:within-cohort-baseline-limit}
For every g in C, the deterministic triangular-array average bar_b_gN=n_gN^(-1)sum_{i in I_gN}b_iN converges to bar_b_g in (0,infinity).
\par\smallskip\noindent\emph{Novel.} This deterministic regularity is met, for example, when the empirical distribution of fixed unit baseline masses within each rollout cohort stabilizes as the cohort grows. It transparently supplies the cohort baseline limit without asserting an unmodeled sampling or mixing law for the fixed array.
\end{assumption}

\begin{assumption}[ass:proportional-effects]\label{ass:proportional-effects}
E_Pcal_N[Y_it(1)]=E_Pcal_N[Y_it(0)] exp(delta_{G_i,t}) for every i and t with D_it=1.
\par\smallskip\noindent\emph{Standard} (cohort-time proportional treatment effects, \cite{MoreauKastler2025PTT}).
\end{assumption}

\begin{assumption}[ass:collapsed-design-rank]\label{ass:collapsed-design-rank}
sum_{g in C}sum_{t=1}^T q_gt r_gt r_gt' is positive definite.
\par\smallskip\noindent\emph{Standard} (full-rank Poisson fixed-effect design, \cite{White1982MisspecifiedML}).
\end{assumption}

\begin{assumption}[ass:multicohort-frontier-scope]\label{ass:multicohort-frontier-scope}
C contains {2,3,4,infinity}.
\par\smallskip\noindent\emph{Novel.} Three adoption waves and a never-treated cohort occur in policy panels with several rollout dates and are the smallest scope in which a T>=4 primitive frontier is distinct from the published 2x3 illustration.
\end{assumption}

\begin{assumption}[ass:strict-positive-effects]\label{ass:strict-positive-effects}
delta_gt>0 for every (g,t) with D_gt=1.
\par\smallskip\noindent\emph{Novel.} Uniformly beneficial proportional effects are empirically meaningful for interventions whose outcome is a nonnegative count or flow; this restriction defines the sign-reversal region rather than an estimation class.
\end{assumption}

\section{Definitions}

\begin{definition}[def:unit-fe-population-projection]\label{def:unit-fe-population-projection}
$Unit-and-time-FE population PPML projection := beta_Nstar(delta) is the last coordinate of argmax_{theta_N in R^(N+T)} L_N(theta_N;delta), where L_N(theta_N;delta)=(NT)^(-1)sum_{i=1}^Nsum_{t=1}^T[m_itN(delta)v_itN'theta_N-exp(v_itN'theta_N)].$ \quad (\text{inputs: } N, T, m_itN(delta), v_itN, theta_N)
\end{definition}

\begin{definition}[def:collapsed-population-projection]\label{def:collapsed-population-projection}
$Collapsed cohort-time population PPML projection := theta_star(delta)=argmax_{theta in R^(|C|+T)}L(theta;delta), L(theta;delta)=sum_{g in C}sum_{t=1}^Tq_gt[m_gt(delta)r_gt'theta-exp(r_gt'theta)], beta_star(delta)=the last coordinate of theta_star(delta), and mu_star_gt(delta)=exp(r_gt'theta_star(delta)).$ \quad (\text{inputs: } C, T, q_gt, m_gt(delta), r_gt, theta)
\end{definition}

\begin{definition}[def:sample-unit-fe-ppml]\label{def:sample-unit-fe-ppml}
$Total extended-MLE unit-and-time-FE PPML coefficient := Let A_N be the argmax of sum_{i=1}^Nsum_{t=1}^T[Y_it v_itN'theta_N-exp(v_itN'theta_N)] over unit-effect coordinates in R union {-infinity}, time-effect coordinates in R with the period-1 normalization, and beta in R, using exp(-infinity)=0. If A_N contains a point with finite beta, hat_beta_N is its beta coordinate after choosing the finite (time-effect,beta) coordinates of smallest Euclidean norm; otherwise hat_beta_N=0.$ \quad (\text{inputs: } N, T, Y_it, v_itN, hat_beta_N)
\end{definition}

\begin{definition}[def:weighted-fwl-residual]\label{def:weighted-fwl-residual}
$Pseudo-true weighted-FWL residual := rho_star(delta)=argmin_{rho in R^(|C|+T-1)}sum_{g in C}sum_{t=1}^Tq_gt mu_star_gt(delta)[D_gt-X_gt'rho]^2 and Wtilde_gt(delta)=D_gt-X_gt'rho_star(delta).$ \quad (\text{inputs: } C, T, q_gt, mu_star_gt(delta), D_gt, X_gt)
\end{definition}

\begin{definition}[def:global-sign-reversal-region]\label{def:global-sign-reversal-region}
$All-positive-effect unit-FE PPML sign-reversal region := R_T={((pi_g)_{g in C},(B_gt)_{g in C,1<=t<=T},(delta_gt)_{(g,t):D_gt=1}): C contains {2,3,4,infinity}; B_gt=bar_b_g exp(gamma_t0); delta_gt>0 whenever D_gt=1; sum_{g,t}q_gt r_gt r_gt' is positive definite; and beta_star(delta)<0}.$ \quad (\text{inputs: } C, T, pi_g, B_gt, bar_b_g, gamma_t0, delta_gt, D_gt, q_gt, r_gt, beta_star(delta))
\end{definition}

\begin{definition}[def:four-cohort-witness]\label{def:four-cohort-witness}
$Explicit four-cohort sign-reversal witness := W4 is the cofinal triangular subsequence indexed by N=4m, m=1,2,..., with T=4, C={2,3,4,infinity}, n_2N=n_3N=n_4N=n_infinityN=m, b_iN=1 for every i, gamma_t0=0 for every t, delta_gt=log(101/100) for every treated cell except delta_2,4=log(4).$ \quad (\text{inputs: } T, C, n_gN, N, b_iN, gamma_t0, delta_gt, D_gt)
\end{definition}

\begin{definition}[def:frontier-elimination-handle]\label{def:frontier-elimination-handle}
$Primitive-frontier elimination handle := Starting from the limiting collapsed score equations sum_{g,t}q_gt X_gt[m_gt(delta)-mu_star_gt(delta)]=0 and sum_{g,t}q_gt D_gt[m_gt(delta)-mu_star_gt(delta)]=0, eliminate the intercept, cohort, and time multipliers by their fitted row and column margins, then characterize the beta_star(delta)=0 zero-level set in pi_g=lim_N n_gN/N, B_gt, and delta_gt.$ \quad (\text{inputs: } q_gt, X_gt, m_gt(delta), mu_star_gt(delta), D_gt, n_gN, pi_g, B_gt, delta_gt, beta_star(delta))
\end{definition}

\section{Main results}

\begin{lemma}[lem:unit-fe-collapse]\label{lem:unit-fe-collapse}
For every N, the unit-and-time-FE population projection in def:unit-fe-population-projection has a unique beta_Nstar(delta). Its beta_Nstar(delta) equals the beta coordinate of the unique maximizer of L_Nc(theta;delta). Consequently, beta_Nstar(delta) converges to beta_star(delta). Thus within-cohort baseline heterogeneity (b_iN) enters the limiting unit-FE coefficient only through B_gtN=n_gN^(-1)sum_{i in I_gN}b_iN exp(gamma_t0).
\end{lemma}
\begin{proof}
Proof. Put c_{gt}=exp(gamma_{t0}+D_{gt}delta_{gt}). From the definition of the observed outcome, ass:unit-untreated-exponential-mean, ass:proportional-effects, E[Y_{it}]=b_{iN}c_{G_i,t}=m_{itN}(delta). Hence units in the same cohort have proportional mean paths.

Write the normalized unit-and-time fixed-effect index as A_i+lambda_t+beta D_{gt}, with lambda_1=0, and the collapsed index as A_g+lambda_t+beta D_{gt}. These are nonsingular reparameterizations of v_{itN}'theta_N and r_{gt}'theta. Fix (lambda,beta), put z_{gt}=lambda_t+beta D_{gt}, C_g=sum_t c_{gt}>0, and H_g(lambda,beta)=sum_t exp(z_{gt})>0. For i in I_{gN}, the part of the unscaled unit criterion depending on A_i has first two derivatives

  d ell_i/dA_i=b_{iN}C_g-exp(A_i)H_g,
  d^2 ell_i/dA_i^2=-exp(A_i)H_g<0.

Its unique maximizer is A_i(lambda,beta)=log b_{iN}+log(C_g/H_g). Thus A_i-log b_{iN} is common within g at every profiled optimum.

Let h_{iN}=b_{iN}/bar b_{gN} for i in I_{gN}. Positivity makes this well-defined and sum_{i in I_{gN}}h_{iN}=n_{gN}. Given collapsed effects A_g, set A_i=A_g+log h_{iN}. With eta_{gt}=A_g+lambda_t+beta D_{gt}, one has m_{itN}=h_{iN}m_{gtN} and exp(A_i+lambda_t+beta D_{gt})=h_{iN}exp(eta_{gt}). Direct summation gives

  L_N((A_i),lambda,beta;delta)=L_Nc((A_g),lambda,beta;delta)+K_N(delta),

where

  K_N(delta)=(NT)^{-1}sum_{g,t}sum_{i in I_{gN}}h_{iN}m_{gtN}(delta)log h_{iN}

is independent of (A_g,lambda,beta). Indeed, the parameter-dependent terms in cell (g,t) equal

  (NT)^{-1}sum_{i in I_{gN}}h_{iN}{m_{gtN}eta_{gt}-exp(eta_{gt})}
  =q_{gtN}{m_{gtN}eta_{gt}-exp(eta_{gt})}.

Conversely, the preceding one-dimensional first-order condition shows that every unit-effect profile maximizer has this lifted form: the collapsed maximizer over A_g at fixed (lambda,beta) is A_g=log bar b_{gN}+log(C_g/H_g), so A_i=A_g+log h_{iN}. The two criteria therefore have identical profiled objectives in (lambda,beta), up to K_N, and their beta maximizers coincide.

Both maxima exist and are unique. The Hessian of L_N is

  -(NT)^{-1}sum_{i,t}exp(v_{itN}'theta_N)v_{itN}v_{itN}',

which is negative definite. Indeed, if a'v_{itN}=0 for every (i,t), then comparing two units in the same nonempty cohort at a fixed t shows that their unit-dummy coefficients agree. These common within-cohort coefficients define a collapsed linear relation a_c'r_{gt}=0 for every (g,t); ass:collapsed-design-rank makes a_c=0, and hence a=0. Thus the unit rows span and the Hessian is negative definite. The criterion is coercive. To see this, for any sequence with ||theta_l|| tending to infinity, pass to a subsequence u_l=theta_l/||theta_l|| tending to u. The design rows span, so some v_{itN}'u is nonzero. If one limiting inner product is positive, its negative exponential dominates the O(||theta_l||) linear part. If all are nonpositive, at least one is strictly negative, and the positive-mean linear part has a strictly negative order-||theta_l|| limit; the rows with zero limiting slope contribute only o(||theta_l||) to its positive part, while all exponential terms are nonpositive. Thus L_N(theta_l) tends to minus infinity. The same argument applies to L_Nc: ass:collapsed-design-rank says the fixed set {r_{gt}} spans, and every q_{gtN},m_{gtN} is positive. Strict concavity and coercivity give one maximizer for each criterion, proving the exact finite-N equality of beta coordinates.

For convergence, ass:cohort-share-limit and ass:within-cohort-baseline-limit give q_{gtN}->q_{gt} and m_{gtN}(delta)->m_{gt}(delta) cell by cell. Hence L_Nc converges to L uniformly on compact sets. Its maximizers theta_N^c are bounded. Otherwise normalize an unbounded subsequence as above. Because the finite collection of q_{gtN} and m_{gtN} is eventually bounded above and bounded away from zero, the same two-case argument forces L_Nc(theta_N^c)->-infinity, contradicting L_Nc(theta_N^c)>=L_Nc(0)=-1. Every convergent subsequence therefore has a limit theta_bar. Optimality and compact-uniform convergence imply L(theta_bar)>=L(theta) for every fixed theta. The limiting criterion is strictly concave and coercive under ass:collapsed-design-rank, so theta_bar=theta_star(delta). Thus theta_N^c->theta_star(delta) and beta_Nstar(delta)->beta_star(delta). The exact identity also shows that all within-cohort variation in b_{iN} occurs only in the parameter-free K_N; the optimizer depends on it only through bar b_{gN}, equivalently B_{gtN}=bar b_{gN}exp(gamma_{t0}). QED.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This anchors the nonlinear geometry to the requested individual-unit and time fixed-effect PPML target while retaining primitive within-cohort baseline heterogeneity. \textit{Gap.} MoreauKastler2025PTT §3.1 specifies individual and time effects, but does not derive the cohort summary of that unit-FE population projection under heterogeneous unit baseline masses. \textit{Consumer.} It makes the limiting cohort-time score a faithful representation of the naive unit-and-time-FE PPML estimand rather than a relabelled cohort-FE regression.

\begin{lemma}[lem:pseudo-true-ppml-projection]\label{lem:pseudo-true-ppml-projection}
The limiting projection theta_star(delta) is unique and satisfies sum_{g in C}sum_{t=1}^Tq_gt r_gt[m_gt(delta)-mu_star_gt(delta)]=0.
\end{lemma}
\begin{proof}
Proof. For every theta,

  nabla L(theta;delta)=sum_{g,t}q_{gt}r_{gt}[m_{gt}(delta)-exp(r_{gt}'theta)],
  nabla^2 L(theta;delta)=-sum_{g,t}q_{gt}exp(r_{gt}'theta)r_{gt}r_{gt}'.

For nonzero a,

  -a'nabla^2L(theta;delta)a=sum_{g,t}q_{gt}exp(r_{gt}'theta)(r_{gt}'a)^2>0,

because all weights and fitted means are positive and ass:collapsed-design-rank says the r_{gt}'s span the parameter space. Thus L is strictly concave.

It also attains its maximum. If ||theta_l|| tends to infinity, pass to a subsequence u_l=theta_l/||theta_l|| tending to u. Spanning gives some r_{gt}'u nonzero. If max_{g,t}r_{gt}'u>0, one negative exponential term tends to minus infinity exponentially and dominates the finite O(||theta_l||) sum of linear terms. If all r_{gt}'u<=0, at least one is strictly negative; the positive-weight, positive-m_{gt} linear part has a strictly negative order-||theta_l|| limit, rows with zero limiting slope contribute only o(||theta_l||) to its positive part, and all negative exponential terms are nonpositive. Hence L(theta_l;delta)->-infinity. Therefore L is coercive and continuous, so it has a maximizer; strict concavity makes it unique, namely theta_star(delta). Interiority in Euclidean space gives

  0=nabla L(theta_star;delta)
   =sum_{g in C}sum_{t=1}^Tq_{gt}r_{gt}[m_{gt}(delta)-mu_star_{gt}(delta)].

This is the claimed score system. QED.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The score characterizes the actual limit established by the unit-FE collapse and supplies the nonlinear geometry used below. \textit{Gap.} White1982MisspecifiedML supplies generic finite-dimensional pseudo-true-QMLE geometry; this lemma records its Poisson specialization after the unit-FE-to-cohort collapse. \textit{Consumer.} It supplies the score system differentiated in the forbidden-comparison theorem.

\begin{theorem}[thm:sharp-ppml-forbidden-sign]\label{thm:sharp-ppml-forbidden-sign}
For the limiting coefficient beta_star(delta) of the unit-and-time-FE Poisson projection, at every delta satisfying the assumptions and for every treated cell (k,s), beta_star(delta) is differentiable in delta_ks and d beta_star(delta)/d delta_ks=q_ks B_ks exp(delta_ks) Wtilde_ks(delta)/[sum_{g in C}sum_{t=1}^Tq_gt mu_star_gt(delta)Wtilde_gt(delta)^2]. The denominator is strictly positive. Hence sign{d beta_star(delta)/d delta_ks}=sign{Wtilde_ks(delta)}, and a treated cell is a forbidden comparison cell if and only if Wtilde_ks(delta)<0. Both Wtilde and its sign depend on delta through mu_star.
\end{theorem}
\begin{proof}
Proof. By lem:unit-fe-collapse, beta_star is the limit of the actual unit-and-time-fixed-effect population PPML coefficient. Define

  F(theta,delta)=sum_{g,t}q_{gt}r_{gt}[m_{gt}(delta)-exp(r_{gt}'theta)].

At theta_star this score is zero by lem:pseudo-true-ppml-projection. Let

  H=sum_{g,t}q_{gt}mu_star_{gt}r_{gt}r_{gt}'.

For nonzero a, a'Ha=sum q_{gt}mu_star_{gt}(a'r_{gt})^2>0 because all weights are positive and ass:collapsed-design-rank makes the r_{gt}'s span. Thus H is positive definite. The implicit-function theorem applies because partial F/partial theta=-H, so theta_star is continuously differentiable in every effect coordinate. For a treated cell (k,s),

  partial m_{gt}/partial delta_{ks}=1{(g,t)=(k,s)}B_{ks}exp(delta_{ks}).

Differentiating F(theta_star(delta),delta)=0 yields

  partial theta_star/partial delta_{ks}=H^{-1}q_{ks}r_{ks}B_{ks}exp(delta_{ks}).

Partition r_{gt}=(X_{gt}',D_{gt})' and write

  H=[A b; b' c],
  A=sum q mu XX',  b=sum q mu XD,  c=sum q mu D^2,

where every sum is over (g,t) and mu=mu_star(delta). The principal block A is positive definite. The projection in def:weighted-fwl-residual therefore has rho_star=A^{-1}b and Wtilde_{gt}=D_{gt}-X_{gt}'A^{-1}b. Its weighted residual sum of squares is the Schur complement

  S=c-b'A^{-1}b=sum_{g,t}q_{gt}mu_star_{gt}Wtilde_{gt}^2.

Positive definiteness of H gives S>0. Equivalently, S=0 would make D equal X'rho_star on every positive-weight cell, contradicting full column rank of r. The last row of H^{-1} is S^{-1}(-b'A^{-1},1), and hence

  e_beta'H^{-1}r_{ks}=S^{-1}[D_{ks}-b'A^{-1}X_{ks}]=Wtilde_{ks}/S.

Taking the last coordinate of the differentiated score gives

  d beta_star/d delta_{ks}
  =q_{ks}B_{ks}exp(delta_{ks})Wtilde_{ks}(delta)
   /{sum_{g,t}q_{gt}mu_star_{gt}(delta)Wtilde_{gt}(delta)^2}.

The denominator and every factor outside Wtilde_{ks} are strictly positive. The derivative therefore has the sign of Wtilde_{ks}; it is negative exactly when Wtilde_{ks}<0, which is precisely the forbidden-comparison condition. Finally, the projection weights are q_{gt}mu_star_{gt}(delta), so Wtilde, and potentially its sign, depend on the full effect vector through the pseudo-true fitted means. QED.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This theorem gives the exact local rule: a true proportional effect moves the naive pooled unit-and-time-FE PPML coefficient in the opposite direction if and only if its pseudo-true mean-weighted FWL residual is negative. \textit{Gap.} MoreauKastler2025PTT provides a 2x3 wrong-comparison calculation, while linear TWFE results use fixed linear weights; neither provides the general effect-dependent PPML derivative identity. \textit{Consumer.} Applied users can compute the fitted-mean residuals to identify forbidden cohort-time cells, then use the primitive Phi theorem to determine the pooled coefficient's global sign.

\begin{proposition}[prop:four-cohort-sign-reversal]\label{prop:four-cohort-sign-reversal}
The explicitly constructed W4 belongs to R_4. In particular, every treated cell has a strictly positive proportional effect, the exceptional cell (2,4) has the largest effect, and beta_star(delta)<0. At b_iN=1 and delta_gt=0 for all treated cells, Wtilde_gt equals the matrix with rows g=2,3,4,infinity and columns t=1,2,3,4: [(-3,3,1,-1),(-1,-3,3,1),(1,-1,-3,3),(3,1,-1,-3)]/8. Thus Wtilde_2,4=-1/8 and d beta_star(delta)/d delta_2,4<0 at the homogeneous no-effect point; continuity gives an open positive-effect neighborhood in which increasing the late effect of the earliest cohort strictly lowers beta_star.
\end{proposition}
\begin{proof}
Proof. The limiting primitive tuple induced by W4 has pi_g=1/4, bar b_g=1, and B_{gt}=1. Every treated effect is positive, and log 4>log(101/100), so (2,4) is uniquely largest. The normalized row and column dummy design is full rank. Moreover, the two-way residual table calculated below is nonzero, so D is not in the nuisance span; hence the full collapsed design has rank.

A sharper calculation places W4 relative to the exact operational frontier. Consider the equal-share, unit-baseline family with common treated multiplier x>1 except multiplier y>1 in cell (2,4). In row order (2,3,4,infinity) and column order (1,2,3,4),

  m=[[1,x,x,y],[1,1,x,x],[1,1,1,x],[1,1,1,1]].

Let R_g=sum_t m_{gt}, C_t=sum_g m_{gt}, and M=sum_g R_g. At beta=0, the nuisance score equations uniquely fit mu^0_{gt}=R_gC_t/M, because this positive row-column multiplicative array matches every observed row and column margin. Here

  R=(1+2x+y,2+2x,3+x,4),
  C=(4,3+x,2+2x,1+2x+y),
  M=10+5x+y.

The observed treated total is 5x+y, whereas the numerator of the fitted treated total is

  F=R_2(C_2+C_3+C_4)+R_3(C_3+C_4)+R_4C_4
   =20x^2+10xy+38x+y^2+12y+15.

Since q_{gt}=1/16, the treatment score at this beta-zero conditional fit is

  s_0=(1/16){5x+y-F/M}
     ={5x^2+12x-2y-15}/{16M}.

The criterion is strictly concave by the just-verified full rank. If theta^0 is the conditional optimizer at beta=0 and theta_star is the full optimizer, strict monotonicity of its gradient gives, whenever s_0 is nonzero,

  0>(theta_star-theta^0)'[nabla L(theta_star)-nabla L(theta^0)]
   =-beta_star s_0.

Thus sign(beta_star)=sign(s_0); if s_0=0, theta^0 is stationary in every coordinate and is the unique maximizer. Therefore the exact zero frontier is

  y=(5x^2+12x-15)/2,

and beta_star<0 exactly above it. At x=101/100 the cutoff is 4441/4000, whereas W4 sets y=4. In fact its denominator-cleared frontier value is (5x^2+12x-2y-15)/16=-11559/32000<0. This both proves beta_star<0 and shows that y=4 is a valid but deliberately nonminimal witness. All restrictions defining R_4 are satisfied, so the limiting tuple induced by W4 belongs to R_4.

For the diagnostic calculation, use the auxiliary no-effect vector delta^0 with every treated coordinate zero. Then m_{gt}=mu_star_{gt}=1 and beta_star=0. Equal q mu weights make Wtilde the ordinary two-way residual of D. The row means of D are (3/4,1/2,1/4,0), its column means are (0,1/4,1/2,3/4), and its grand mean is 3/8. Hence

  Wtilde(delta^0)=(1/8)[[-3,3,1,-1],[-1,-3,3,1],[1,-1,-3,3],[3,1,-1,-3]].

In particular Wtilde_{2,4}=-1/8. Also sum qWtilde^2=5/64 and q_{2,4}Wtilde_{2,4}=-1/128, so thm:sharp-ppml-forbidden-sign gives

  (partial beta_star/partial delta_{2,4})|_{delta^0}=-1/10<0.

The implicit-function argument in that theorem makes this derivative continuous. Thus it remains negative on a ball around zero. If K is the number of treated cells, choose a vector bar delta=(epsilon,...,epsilon) in that ball with epsilon>0 and then a sufficiently small ball around bar delta contained both in the strict positive orthant and in the original ball. This is a genuine open all-positive-effect neighborhood on which increasing the late effect of the earliest cohort strictly lowers beta_star. QED.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The explicit T=4 construction proves that the negative-residual derivative rule and an all-positive-effect negative pooled coefficient are both non-vacuous for the actual unit-FE PPML target. \textit{Gap.} The prior 2x3 illustration does not provide a four-cohort unit-FE witness or locate it relative to a sharp multicohort frontier. \textit{Consumer.} The witness is a regression-test fixture, and the exact comparison with the 4441/4000 cutoff shows that y=4 is valid but deliberately nonminimal.

\begin{proposition}[prop:homogeneous-effect-reduction]\label{prop:homogeneous-effect-reduction}
If delta_gt=delta_0 for every treated cell, then beta_star(delta)=delta_0 and mu_star_gt(delta)=B_gt exp(D_gt delta_0).
\end{proposition}
\begin{proof}
Proof. Suppose delta_{gt}=delta_0 in every treated cell. Since D_{gt} is binary,

  m_{gt}(delta)=B_{gt}exp(D_{gt}delta_0)
              =exp{log bar b_g+gamma_{t0}+D_{gt}delta_0}.

This log mean lies exactly in the collapsed design. Choose the normalized parameter theta_0 with intercept log bar b_infinity, cohort-g coefficient log bar b_g-log bar b_infinity for g not equal to infinity, time-t coefficient gamma_{t0} for t>=2, and treatment coefficient delta_0. Then r_{gt}'theta_0=log m_{gt}(delta) in every cell.

For fixed m>0, f_m(eta)=m eta-exp(eta) is strictly concave and uniquely maximized at eta=log m. Therefore, cell by cell,

  L(theta;delta)<=sum_{g,t}q_{gt}[m_{gt}log m_{gt}-m_{gt}]=L(theta_0;delta),

with equality only if r_{gt}'theta=log m_{gt} for every cell. By ass:collapsed-design-rank the r_{gt}'s span, so equality implies theta=theta_0. Hence theta_star=theta_0, beta_star(delta)=delta_0, and

  mu_star_{gt}(delta)=exp(r_{gt}'theta_0)=B_{gt}exp(D_{gt}delta_0).

By lem:unit-fe-collapse this is also the limiting individual-unit-and-time-FE projection. QED.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This is the required sanity reduction: a correctly specified unit-and-time-FE PPML coefficient equals the common log proportional effect. \textit{Gap.} MoreauKastler2025PTT equation (3.5) gives the homogeneous-effect benchmark; it is retained solely as a specification check for the heterogeneous sign theorem. \textit{Consumer.} It separates heterogeneity-driven forbidden comparisons from normalization or implementation errors.

\begin{theorem}[thm:primitive-global-frontier]\label{thm:primitive-global-frontier}
For h_gt=pi_g B_gt exp(D_gt delta_gt), define R_g=sum_{t=1}^T h_gt, C_t=sum_{g in C}h_gt, M=sum_{g in C}sum_{t=1}^T h_gt, A=sum_{g in C}sum_{t=1}^T D_gt h_gt, and Phi=M A-sum_{g in C}sum_{t=1}^T D_gt R_g C_t. Then sign{beta_star(delta)}=sign(Phi). In particular beta_star(delta)=0 if and only if Phi=0, so the requested zero-level set is the finite primitive system Phi>=0 and -Phi>=0, with no pseudo-true intercept, cohort, or time multiplier retained; subject to the defining positive-effect, baseline, share, and rank restrictions, R_T is exactly Phi<0. In the T=4, C={2,3,4,infinity}, equal-share, unit-baseline subfamily having treated multiplier x>1 outside (2,4) and multiplier y>1 at (2,4), Phi=(5x^2+12x-2y-15)/16, so beta_star<0 if and only if y>(5x^2+12x-15)/2; at x=101/100 the sharp cutoff is 4441/4000, and W4 has y=4. Operationally, let H={(g,t):D_gt=1}, Bobs_gt=m_g1 m_infinity,t/m_infinity,1, Z=sum_H q_gt Bobs_gt, omega_gt=q_gt Bobs_gt/Z, tau_gt=m_gt/Bobs_gt-1, and PTT=sum_H omega_gt tau_gt. Under the multiplicative-parallel-trends and proportional-effect assumptions, Bobs_gt=B_gt, tau_gt=exp(delta_gt)-1, every omega_gt is positive and the weights sum to one, and PTT=(sum_H q_gt m_gt)/(sum_H q_gt Bobs_gt)-1. Thus with positive effects, Phi<0 implies beta_star<0<PTT: Phi diagnoses the pooled PPML coefficient as an unsafe causal summary, while granular tau_gt and their counterfactual-share PTT form a distinct identified causal target, not a correction or reinterpretation of beta_star. This population result makes no fixed-T sampling or inference claim for hat_beta_N.
\end{theorem}
\begin{proof}
Proof. Part I: exact primitive frontier. All h_{gt}, R_g, C_t, and M are strictly positive. Since q_{gt}=pi_g/T and m_{gt}=h_{gt}/pi_g, constrain beta to zero and define

  mu^0_{gt}=R_g C_t/(pi_g M).

This array is representable by intercept, cohort, and time effects because

  log mu^0_{gt}=log(R_g/pi_g)+log C_t-log M.

It matches every nuisance margin. Indeed, using sum_t C_t=M and sum_g R_g=M,

  sum_t pi_g mu^0_{gt}=R_g=sum_t pi_g m_{gt},
  sum_g pi_g mu^0_{gt}=C_t=sum_g pi_g m_{gt}.

After division by T these are exactly all cohort, time, and intercept score equations. The nuisance block is full rank as a principal block of the full collapsed Gram matrix, so this conditional fit is unique. Let theta^0=(eta^0,0) denote its normalized coefficient. Its only possibly nonzero score is the treatment coordinate

  s_0=sum_{g,t}q_{gt}D_{gt}(m_{gt}-mu^0_{gt})
     =(1/T){A-(1/M)sum_{g,t}D_{gt}R_gC_t}
     =Phi/(TM).

No pseudo-true nuisance multiplier remains in this expression. The Hessian of L is

  nabla^2 L(theta)=-sum_{g,t}q_{gt}exp(r_{gt}'theta)r_{gt}r_{gt}',

which is negative definite under ass:collapsed-design-rank. Hence L is strictly concave and its gradient is strictly monotone: for distinct theta_1 and theta_0,

  (theta_1-theta_0)'[nabla L(theta_1)-nabla L(theta_0)]<0.

If s_0=0, theta^0 is stationary in every coordinate and strict concavity makes it theta_star, so beta_star=0. If s_0 is nonzero, theta_star differs from theta^0 and

  0>(theta_star-theta^0)'[nabla L(theta_star)-nabla L(theta^0)]
   =-beta_star s_0,

because nabla L(theta_star)=0 and the nuisance coordinates of nabla L(theta^0) vanish. Thus beta_star s_0>0. Conversely, beta_star=0 with s_0 nonzero would contradict the same strict inequality. Since TM>0,

  sign{beta_star(delta)}=sign(s_0)=sign(Phi).

Phi is a finite explicit expression in pi_g, B_{gt}, and exp(D_gt delta_gt). Equality Phi=0 is equivalent to the two weak inequalities Phi>=0 and -Phi>=0. Intersecting Phi<0 with the primitive restrictions in def:global-sign-reversal-region gives exactly R_T. By lem:unit-fe-collapse this is a frontier for the limiting naive individual-unit-and-time-FE PPML coefficient, not merely for a relabelled cohort regression.

Part II: operational T=4 threshold. In the equal-share, unit-baseline family from the statement, the observed mean matrix, in row order (2,3,4,infinity) and column order (1,2,3,4), is

  [[1,x,x,y],[1,1,x,x],[1,1,1,x],[1,1,1,1]].

Its unweighted row margins are (1+2x+y,2+2x,3+x,4), its unweighted column margins are (4,3+x,2+2x,1+2x+y), its total is 10+5x+y, and its treated total is 5x+y. Direct expansion gives

  sum_{g,t}D_{gt}R_gC_t
   =20x^2+10xy+38x+y^2+12y+15

after removal of the common share factors. Because pi_g=1/4, every product in Phi carries the common factor 1/16. Therefore

  Phi=[(10+5x+y)(5x+y)
       -(20x^2+10xy+38x+y^2+12y+15)]/16
      =(5x^2+12x-2y-15)/16.

Part I yields beta_star<0 exactly when

  y>(5x^2+12x-15)/2,

and equality is the exact zero frontier. At x=101/100 this cutoff is 4441/4000. Moreover

  (5x^2+12x-15)/2-x=(5/2)(x-1)(x+3)>0

for x>1, so reversal forces the exceptional multiplier to be uniquely largest. W4 takes x=101/100 and y=4, for which Phi=-11559/32000<0; thus its witness is valid but nonminimal.

Part III: diagnose, then target causal PTT. Let H={(g,t):D_{gt}=1}. Since every adoption cohort belongs to {2,...,T,infinity}, D_{g1}=0. The period-one normalization and the limiting untreated mean give

  m_{g1}=B_{g1}=bar b_g.

The never-treated cohort obeys D_{infinity,t}=0 for all t, so

  m_{infinity,t}=bar b_infinity exp(gamma_{t0}),
  m_{infinity,1}=bar b_infinity>0.

Consequently the observed-population counterfactual baseline

  Bobs_{gt}=m_{g1}m_{infinity,t}/m_{infinity,1}

equals bar b_g exp(gamma_{t0})=B_{gt}. In a treated cell, proportional effects give m_{gt}=B_{gt}exp(delta_{gt}); hence

  tau_{gt}=m_{gt}/Bobs_{gt}-1=exp(delta_{gt})-1.

Positive cohort shares and baselines imply Z=sum_H q_{gt}Bobs_{gt}>0, omega_{gt}=q_{gt}Bobs_{gt}/Z>0, and sum_H omega_{gt}=1. Therefore

  PTT=sum_H omega_{gt}tau_{gt}
     ={sum_H q_{gt}B_{gt}exp(delta_{gt})}/{sum_H q_{gt}B_{gt}}-1
     ={sum_H q_{gt}m_{gt}}/{sum_H q_{gt}Bobs_{gt}}-1.

This is a computable positive-counterfactual-share aggregation of the identified granular proportional effects. If every delta_{gt}>0 on H, then every tau_{gt}>0 and PTT>0. Part I says Phi<0 exactly when beta_star<0. Hence Phi<0 diagnoses the pooled PPML coefficient as an unsafe causal summary: the recommended granular effects and PTT target a distinct causal estimand and do not algebraically correct or reinterpret beta_star. Everything here is an observed-population statement; no fixed-T sampling limit, influence function, variance formula, or coverage result for hat_beta_N is asserted. QED.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The theorem closes the primitive-frontier question by proving sign(beta_star)=sign(Phi), eliminating all pseudo-true intercept, cohort, and time multipliers, and deriving the exact T=4 threshold and the qualified diagnose-then-causal-PTT rule. \textit{Gap.} Published nonlinear DiD and PPML work does not give a finite necessary-and-sufficient primitive sign system for the misspecified pooled unit-and-time-FE PPML coefficient in a general fixed-T multicohort panel. \textit{Consumer.} Design-stage users can evaluate Phi directly from cohort shares, baseline masses, and effects; if Phi<0, they should treat beta_star as an unsafe summary and report granular proportional effects or their distinct counterfactual-share PTT instead.

\section{Honest scope}

The contribution is at the observed-population identification and projection level. It proves the unit-FE collapse, the local forbidden-cell derivative rule, the exact primitive global sign frontier Phi=0, and the T=4 reversal threshold, and it identifies a separate positive counterfactual-share PTT from granular proportional effects. Phi is a diagnostic for beta_star, and PTT is a distinct causal estimand; PTT neither corrects nor reinterprets beta_star. The extended sample PPML coefficient is defined on all realizations, but no fixed-T consistency, influence-function, analytical-variance, limit-law, or coverage result is claimed here.

\begin{thebibliography}{99}

  \bibitem{MoreauKastler2025PTT} Ninon Moreau-Kastler (2025), Proportional Treatment Effects in Staggered Settings: An Approach for Poisson Pseudo-Maximum Likelihood, EU Tax Observatory Working Paper No. 31, https://doi.org/10.2139/ssrn.5247936.

  \bibitem{Wooldridge2023NonlinearDiD} Jeffrey M. Wooldridge (2023), Simple Approaches to Nonlinear Difference-in-Differences with Panel Data, The Econometrics Journal 26(3), C31-C66, https://doi.org/10.1093/ectj/utad016.

  \bibitem{GoodmanBacon2021} Andrew Goodman-Bacon (2021), Difference-in-Differences with Variation in Treatment Timing, Journal of Econometrics 225(2), 254-277, https://doi.org/10.1016/j.jeconom.2021.03.014.

  \bibitem{deChaisemartinDHaultfoeuille2020TWFE} Clement de Chaisemartin and Xavier D'Haultfoeuille (2020), Two-Way Fixed Effects Estimators with Heterogeneous Treatment Effects, American Economic Review 110(9), 2964-2996, https://doi.org/10.1257/aer.20181169.

  \bibitem{White1982MisspecifiedML} Halbert White (1982), Maximum Likelihood Estimation of Misspecified Models, Econometrica 50(1), 1-25, https://doi.org/10.2307/1912526.

  \bibitem{Andrews1988LLN} Donald W. K. Andrews (1988), Laws of Large Numbers for Dependent Non-Identically Distributed Random Variables, Econometric Theory 4(3), 458-467, https://doi.org/10.1017/S0266466600013396.

  \bibitem{NagengastYotov2025} Arne J. Nagengast and Yoto V. Yotov (2025), Staggered Difference-in-Differences in Gravity Settings: Revisiting the Effects of Trade Agreements, American Economic Journal: Applied Economics 17(1), 271-296, https://doi.org/10.1257/app.20230089.

\end{thebibliography}

\end{document}