% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_lp\_svar\_nonequiv, specialization=upgrade
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_lp\_svar\_nonequiv} / \texttt{upgrade}%
  \\ \large\textit{Mechanism decomposition of LP/sign versus non-Gaussian SVAR non-equivalence}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
\begin{verbatim}
qid = eid_lp_svar_nonequiv
specialization = upgrade
anchor_cluster = partial identification / structural impulse-response
  support functions with non-Gaussian shock-law restrictions
observable distribution P = the population law of a covariance-stationary
  finite-order VAR(p) process Y_t, summarized by reduced-form LP/VAR response
  rows Gamma_h = E[Y_{t+h} u_t'] Sigma_u^{-1} for h=0,...,H, innovation
  covariance Sigma_u, and fourth cumulant tensor K_u = cum4(u_t)
parameter theta = the horizon-H structural impulse-response vector
  psi_j(Q)=(e_y' Gamma_h Sigma_u^{1/2} Q e_j)_{h=0}^H for a labelled
  structural shock j, and scalar reports w' psi_j(Q)
identifying restrictions = covariance stationarity, finite fourth moments,
  unit-variance structural shocks, partial sign/zero restrictions on reported
  responses, a population fourth-cumulant tensor K_u, and a non-Gaussian
  shock-law restriction requiring one common orthogonal Q and admissible
  cumulants kappa to satisfy K_u=sum_k kappa_k b_k(Q)^{otimes 4}
bounding functional = compare three support functions for direction w:
  h_HLP over horizonwise LP/sign response rows, h_CLP over rows that paste
  to one common impact direction q=Qe_j, and h_SVAR over rows that paste to
  one full cumulant-diagonalizing non-Gaussian shock law
mechanism diagnostic = the augmented gap Delta_w^H(P)=h_HLP(w;P)-h_SVAR(w;P)
  is decomposed into E_w^{sign}(P), Pi_w^{paste}(P), and Lambda_w^{cum}(P):
  respectively sign-cone exposure of horizonwise LP rows, the loss from
  forcing those rows to paste to one common impact direction, and the
  fourth-cumulant label residual among common-impact exposed rotations
\end{verbatim}

\begin{abstract}
This proposal upgrades \texttt{eid\_lp\_svar\_nonequiv}/\texttt{v1} along the mechanism axis while retaining the parent's partial-identification support-function anchor.  The parent bundled strict LP/sign versus non-Gaussian SVAR separation into one quantitative margin \(\chi_w(P)\); this upgrade conjectures a three-channel factorization that isolates horizonwise sign exposure, common-impact pasting loss, and fourth-cumulant label residual.  The headline claim is that the augmented horizonwise-LP/SVAR support gap is bounded below by a closed diagnostic \(\tau_w^{\mathrm{mech}}(P)\), and that the parent common-rotation gap is recovered when the horizonwise pasting channel is normalized away.  The decomposition recovers Plagborg-Moller--Wolf equivalence when the extra non-Gaussian restriction is imposed equally on both sides.  If resolved, the result would tell applied users whether a sign-restricted LP robustness response fails because of ordinary sign masquerading, because horizonwise rows do not paste into one impact direction, or because the non-Gaussian label chooses another structural law.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
LP/VAR equivalence is most useful when the identifying restriction is transparently the same object in both languages.  Non-Gaussian SVAR identification is less transparent: the shock label is a property of one innovation law and one higher-moment tensor, while LP sign restrictions are usually imposed horizon by horizon on response rows.  The parent proposal asked for a support-function non-equivalence theorem, but its derivation collapsed to assuming one positive margin.  A flagship upgrade should explain why the margin is positive, and which economic or statistical mechanism is responsible.

\paragraph{The main finding (proposed).}
Conjecture~\ref{conj:mechanism-factorization} is the upgrade delta.  It conjectures that the horizonwise-LP/SVAR support gap admits a mechanism lower bound
\[
\Delta_w^H(P)\ge \tau_w^{\mathrm{mech}}(P)
=c_w(P)E_w^{\mathrm{sign}}(P)\Pi_w^{\mathrm{paste}}(P)\Lambda_w^{\mathrm{cum}}(P),
\]
with equality on a named exposed-face class.  Theorem~\ref{thm:mechanism-objects} records the routine construction of the three diagnostics.  Conjecture~\ref{conj:iff-frontier} states the sharp frontier: outside response-flat degeneracies, strict LP/SVAR non-equivalence holds if and only if the three mechanism channels are jointly positive.

\paragraph{What is new.}
Relative to the parent \texttt{eid\_lp\_svar\_nonequiv}/\texttt{v1}, the new content is not another statement that adding cumulant matching shrinks a feasible set.  The parent had a single black-box margin \(\chi_w(P)\).  This proposal decomposes that margin into a sign-exposure channel motivated by \citet[Section~2]{Wolf2022}, a genuine common-impact pasting channel between horizonwise LP rows and one impact direction, and a cumulant-label channel motivated by \citet[Sections~2--3]{GourierouxMonfortRenne2017}, \citet[Sections~2--3]{LanneMeitzSaikkonen2017}, and \citet[Sections~2--3]{Guay2021}.  Relative to published work, the gap is a mechanism-level algebraic frontier connecting the \citet[Sections~2--3]{PlagborgMollerWolf2021} common-restriction theorem to the non-Gaussian SVAR literature and the blended-identification frontier in \citet[Sections~2--3]{CarrieroMarcellinoTornese2024}; none of these papers separates these three channels or proves which one drives the support gap.

\paragraph{How it positions in the literature.}
The anchor cluster is partial identification for structural impulse-response support functions.  \citet{PlagborgMollerWolf2021} and \citet{MontielOleaPlagborgMollerQianWolf2024} explain why LP and VAR rows can share an estimand under common restrictions.  \citet{AriasRubioRamirezWaggoner2018}, \citet{Read2022}, \citet{Wolf2022}, and \citet{CarrieroMarcellinoTornese2024} explain why sign, narrative, instrument, or statistical restrictions can admit masquerading or blended shock labels.  \citet{GourierouxMonfortRenne2017}, \citet{LanneMeitzSaikkonen2017}, \citet{Guay2021}, \citet{DrautzburgWright2023}, and \citet{LanneLiuLuoto2026} explain why higher moments or independence refine the shock law.  The proposal is the support-function boundary between these restriction types.

\paragraph{Implications for the community.}
The concrete downstream consumer is \citet{DrautzburgWright2023}: their independence-refined sign-restricted VAR sets would gain a diagnostic that says whether an LP robustness response is excluded by shock masquerading, by fourth-cumulant label failure, or by failure of one common structural innovation law.

\paragraph{How research benefits from the conclusion.}
Researchers should report the three mechanism diagnostics before interpreting an LP sign-restricted response as evidence about the same non-Gaussian SVAR shock.

\section{Related work}
\citet{Jorda2005} introduced local projections as direct impulse-response regressions, making horizonwise LP response rows a standard empirical object.  \citet{PlagborgMollerWolf2021} [reused from parent] prove that LPs and VARs estimate the same population impulse responses under unrestricted lag structures and common identifying restrictions, including sign restrictions; this is the comparator whose common-restriction premise is stressed here.  \citet{MontielOleaPlagborgMoller2021} [reused from parent] establishes robust LP inference under persistence and long horizons, motivating LP rows as reports without adding higher-moment shock labels.  \citet{MontielOleaPlagborgMollerQianWolf2024} [reused from parent] extends the LP-versus-VAR frontier under local lag misspecification; the present proposal differs by changing the identifying restriction, not the lag approximation.

\citet{AriasRubioRamirezWaggoner2018} [reused from parent] gives the rotation geometry for sign and zero restricted SVARs, which supplies the feasible sign cone used in \(E_w^{\mathrm{sign}}\).  \citet{Read2022} [reused from parent] gives algorithms for exact sign and zero restrictions, which is the computational comparator for testing sign-cone exposure.  \citet{Wolf2022} is the new mechanism anchor: it identifies shock masquerading as a limitation of sign restrictions, and this proposal asks when such masquerading survives LP rows but is killed by the non-Gaussian shock-law label.

\citet{CarrieroMarcellinoTornese2024} is a new frontier anchor beyond the parent map: their blended-identification framework combines statistical identification with sign, narrative, or instrument restrictions and explicitly motivates ruling out masquerading shocks.  This proposal targets a different object, a population LP/SVAR support-function boundary under fourth-cumulant shock-law restrictions, but their blended-identification setting is the closest published comparator for combining weak sign information with a statistical shock label.

\citet{GourierouxMonfortRenne2017} [reused from parent] and \citet{LanneMeitzSaikkonen2017} [reused from parent] show that independent non-Gaussian shocks can identify the SVAR impact matrix up to the usual sign and permutation ambiguities; this is the source of the cumulant-label channel.  \citet{Guay2021} [reused from parent] gives higher-unconditional-moment rank conditions and tests, including cases of partial local identification; the proposed \(\Lambda_w^{\mathrm{cum}}\) is a population diagnostic rather than an estimator.  \citet{DrautzburgWright2023} [reused from parent] refine sign-restricted VAR identified sets through independence and emphasize nonconvexity and weak higher-moment information; their workflow is the main consumer of a channel-by-channel LP/SVAR comparison.  \citet{LanneLiuLuoto2026} [reused from parent] allows potentially dependent non-Gaussian shocks, highlighting boundary regimes where cumulants label only a block rather than one shock.

The in-catalogue prior art is adjacent but not duplicate.  The \texttt{doc/API.md} ExactID and PartialID catalogues contain no accepted \texttt{eid\_*} LP/SVAR or non-Gaussian shock-law theorem.  The closest banked parent, \texttt{eid\_lp\_svar\_nonequiv}/\texttt{v1}, proposed a cumulant-matching support gap but was downgraded because the derivation assumed rather than decomposed the positive margin.  The closest panel family, \texttt{q1\_spectral\_phase\_transition}, concerns panel row-space boundaries rather than structural innovation cumulants.  The closest partial-ID motifs, \texttt{pid\_network\_exposure} and \texttt{pid\_dose\_response\_iv}, share common-latent pasting logic but contain no time-series SVAR or fourth-cumulant result.

\section{Formal setup}
Let \(Y_t\in\R^n\) be covariance stationary with reduced-form innovation \(u_t\), covariance \(\Sigma_u\succ0\), finite fourth cumulant tensor \(K_u=\operatorname{cum}_4(u_t)\), and population response rows
\[
\Gamma_h=\E[Y_{t+h}u_t^\transpose]\Sigma_u^{-1},\qquad h=0,\ldots,H.
\]
A structural completion writes \(u_t=B(Q)\varepsilon_t\), where \(B(Q)=\Sigma_u^{1/2}Q\), \(Q\in O(n)\), and \(\E[\varepsilon_t\varepsilon_t^\transpose]=I_n\).  For labelled shock \(j\), define
\[
\psi_j(Q)=(e_y^\transpose\Gamma_h\Sigma_u^{1/2}Qe_j)_{h=0}^H\in\R^{H+1},
\qquad \ell_w(Q;P)=w^\transpose\psi_j(Q).
\]
Known matrices \(A\in\R^{m_A\times(H+1)}\) and \(Z\in\R^{m_Z\times(H+1)}\) encode sign and zero restrictions.  The horizonwise LP/sign relaxation allows each reported horizon to choose its own unit impact direction \(q_h\in S^{n-1}\):
\[
\mathcal R_{\mathrm{HLP}}(P)=
\left\{r\in\R^{H+1}:r_h=e_y^\transpose\Gamma_h\Sigma_u^{1/2}q_h,\ 
\|q_h\|_2=1,\ Ar\ge0,\ Zr=0\right\}.
\]
The common-impact LP/sign set forces the horizonwise directions to paste into one labelled impact direction \(q=Qe_j\):
\[
\mathcal Q_{\mathrm{CLP}}(P)=\{Q\in O(n):A\psi_j(Q)\ge0,\ Z\psi_j(Q)=0\},
\qquad
\mathcal R_{\mathrm{CLP}}(P)=\{\psi_j(Q):Q\in\mathcal Q_{\mathrm{CLP}}(P)\}.
\]
For \(\delta_4>0\), let
\[
\mathcal K_{\delta_4}(j)=\{\kappa\in\R^n: |\kappa_j|\ge\delta_4,\ |\kappa_\ell-\kappa_j|\ge\delta_4\ \forall \ell\ne j\}.
\]
Let \(\kappa_{\max}(P)<\infty\) be a maintained population envelope for admissible structural fourth cumulants, and write
\[
\mathcal K_{\delta_4}^{\max}(j;P)=\mathcal K_{\delta_4}(j)\cap[-\kappa_{\max}(P),\kappa_{\max}(P)]^n.
\]
The common non-Gaussian shock-law rotations are
\[
\mathcal Q_{\mathrm{SVAR}}(P)=\left\{Q\in\mathcal Q_{\mathrm{CLP}}(P):
K_u=\sum_{k=1}^n\kappa_k(\Sigma_u^{1/2}Qe_k)^{\otimes4}
\text{ for some }\kappa\in\mathcal K_{\delta_4}^{\max}(j;P)\right\}.
\]
where \(\mathcal Q_{\mathrm{LP}}(P)\) is retained only as an alias for \(\mathcal Q_{\mathrm{CLP}}(P)\) when comparing to the parent proposal.  Let \(\mathcal R_{\mathrm{SVAR}}(P)=\{\psi_j(Q):Q\in\mathcal Q_{\mathrm{SVAR}}(P)\}\).  Define
\[
h_{\mathrm{HLP}}(w;P)=\sup_{r\in\mathcal R_{\mathrm{HLP}}(P)}w^\transpose r,\quad
h_{\mathrm{CLP}}(w;P)=\sup_{r\in\mathcal R_{\mathrm{CLP}}(P)}w^\transpose r,\quad
h_{\mathrm{SVAR}}(w;P)=\sup_{r\in\mathcal R_{\mathrm{SVAR}}(P)}w^\transpose r.
\]
The upgraded support gap is \(\Delta_w^H(P)=h_{\mathrm{HLP}}(w;P)-h_{\mathrm{SVAR}}(w;P)\).  The parent common-rotation gap is \(\Delta_w(P)=h_{\mathrm{CLP}}(w;P)-h_{\mathrm{SVAR}}(w;P)\), assuming \(\mathcal Q_{\mathrm{SVAR}}(P)\ne\emptyset\).

The upgrade names three mechanism objects.  Let \(\mathcal M_w^H(P)=\arg\max_{r\in\mathcal R_{\mathrm{HLP}}(P)}w^\transpose r\) and \(\mathcal M_w^C(P)=\arg\max_{Q\in\mathcal Q_{\mathrm{CLP}}(P)}\ell_w(Q;P)\).  Let \(\mathcal D(P)=\{Q\in O(n):Q\text{ satisfies the fourth-cumulant equation for some }\kappa\in\mathcal K_{\delta_4}^{\max}(j;P)\}\).  Define the cumulant-label residual
\[
r_{\mathrm{cum}}(Q;P)=\inf_{R\in\mathcal D(P)}\|Qe_j-Re_j\|_2.
\]
Let
\[
\mathcal R_{\mathrm{paste}}(P)=\mathcal R_{\mathrm{CLP}}(P)
\]
be the response set that can be pasted to one common impact direction before any fourth-cumulant restriction is imposed.  This makes the pasting channel distinct from the cumulant/SVAR channel: \(\mathcal R_{\mathrm{HLP}}\supseteq\mathcal R_{\mathrm{paste}}\supseteq\mathcal R_{\mathrm{SVAR}}\).  Define
\[
\mathcal A_w^+(P)=\{a:(Ar)_a>0\text{ for every }r\in\mathcal M_w^H(P)\}.
\]
The sign-exposure diagnostic uses only sign rows that are uniformly slack on the exposed horizonwise face:
\[
E_w^{\mathrm{sign}}(P)=
\begin{cases}
1, & \mathcal A_w^+(P)=\emptyset,\\
\inf_{r\in\mathcal M_w^H(P)}\min_{a\in\mathcal A_w^+(P)}(Ar)_a, & \mathcal A_w^+(P)\ne\emptyset.
\end{cases}
\]
The value \(1\) in the empty case is a normalization saying that no exposed sign-slack row is available to attenuate the other two channels; it avoids treating absent sign information as an undefined minimum.  The pasting and cumulant diagnostics are
\[
\Pi_w^{\mathrm{paste}}(P)=\inf_{r\in\mathcal M_w^H(P)}\operatorname{dist}(r,\mathcal R_{\mathrm{paste}}(P)),
\qquad
\Lambda_w^{\mathrm{cum}}(P)=\inf_{Q\in\mathcal M_w^C(P)}r_{\mathrm{cum}}(Q;P),
\]
where response-space distances are Euclidean and rotation distances are Frobenius distances on \(O(n)\).  Finally set
\[
\tau_w^{\mathrm{mech}}(P)=c_w(P)E_w^{\mathrm{sign}}(P)\Pi_w^{\mathrm{paste}}(P)\Lambda_w^{\mathrm{cum}}(P),
\]
where \(c_w(P)>0\) is the local exposure-curvature constant for \(\ell_w\) on the exposed LP face, defined in Assumption~\ref{ass:curvature}.
For the zero-channel frontier in Conjecture~\ref{conj:iff-frontier}, also define the setwise channel widths
\[
\overline\Pi_w^{\mathrm{paste}}(P)=\sup_{r\in\mathcal M_w^H(P)}\operatorname{dist}(r,\mathcal R_{\mathrm{paste}}(P)),
\qquad
\overline\Lambda_w^{\mathrm{cum}}(P)=\sup_{Q\in\mathcal M_w^C(P)}r_{\mathrm{cum}}(Q;P).
\]
Thus \(\Pi_w^{\mathrm{paste}}=0\) or \(\Lambda_w^{\mathrm{cum}}=0\) is an existence statement about at least one exposed optimizer, while \(\overline\Pi_w^{\mathrm{paste}}=0\) or \(\overline\Lambda_w^{\mathrm{cum}}=0\) is the setwise statement that all exposed optimizers satisfy the corresponding restriction.

\begin{verbatim}
qid = eid_lp_svar_nonequiv
specialization = upgrade
anchor_cluster = partial identification / structural impulse-response
  support functions with non-Gaussian shock-law restrictions
observable distribution P = the population law of a covariance-stationary
  finite-order VAR(p) process Y_t, summarized by reduced-form LP/VAR response
  rows Gamma_h = E[Y_{t+h} u_t'] Sigma_u^{-1} for h=0,...,H, innovation
  covariance Sigma_u, and fourth cumulant tensor K_u = cum4(u_t)
parameter theta = the horizon-H structural impulse-response vector
  psi_j(Q)=(e_y' Gamma_h Sigma_u^{1/2} Q e_j)_{h=0}^H for a labelled
  structural shock j, and scalar reports w' psi_j(Q)
identifying restrictions = covariance stationarity, finite fourth moments,
  unit-variance structural shocks, partial sign/zero restrictions on reported
  responses, a population fourth-cumulant tensor K_u, and a non-Gaussian
  shock-law restriction requiring one common orthogonal Q and admissible
  cumulants kappa to satisfy K_u=sum_k kappa_k b_k(Q)^{otimes 4}
bounding functional = compare three support functions for direction w:
  h_HLP over horizonwise LP/sign response rows, h_CLP over rows that paste
  to one common impact direction q=Qe_j, and h_SVAR over rows that paste to
  one full cumulant-diagonalizing non-Gaussian shock law
mechanism diagnostic = the augmented gap Delta_w^H(P)=h_HLP(w;P)-h_SVAR(w;P)
  is decomposed into E_w^{sign}(P), Pi_w^{paste}(P), and Lambda_w^{cum}(P):
  respectively sign-cone exposure of horizonwise LP rows, the loss from
  forcing those rows to paste to one common impact direction, and the
  fourth-cumulant label residual among common-impact exposed rotations
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite-order response environment]\label{ass:finite-response}
The population law \(P\) is covariance stationary, has finite fourth moments, has \(\Sigma_u\succ0\), and admits response rows \(\Gamma_h\) for \(h=0,\ldots,H\).  These rows are the common population LP/VAR response rows under the unrestricted lag convention.
\end{assumption}

\begin{assumption}[Rotation normalization and labelled shock]\label{ass:rotation-label}
Every structural impact matrix is written as \(B(Q)=\Sigma_u^{1/2}Q\) for \(Q\in O(n)\).  The target index \(j\) and report direction \(w\in\R^{H+1}\) are fixed before optimization.
\end{assumption}

\begin{assumption}[Partial sign and zero cone]\label{ass:sign-cone}
The matrices \(A\) and \(Z\) define nonempty horizonwise and common-impact sign/zero feasible sets \(\mathcal R_{\mathrm{HLP}}(P)\) and \(\mathcal Q_{\mathrm{CLP}}(P)\).  The uniformly exposed sign-row set \(\mathcal A_w^+(P)\) is allowed to be empty; if it is nonempty, every row \(a\in\mathcal A_w^+(P)\) has a strictly positive minimum slack on the whole exposed horizonwise face \(\mathcal M_w^H(P)\).
\end{assumption}

\begin{assumption}[Fourth-cumulant shock-law label]\label{ass:cumulant-label}
The fourth cumulant tensor \(K_u\) is finite, and admissible structural cumulant vectors lie in the compact set \(\mathcal K_{\delta_4}^{\max}(j;P)\) for a finite population envelope \(\kappa_{\max}(P)\).  A non-Gaussian SVAR completion must satisfy
\[
K_u=\sum_{k=1}^n\kappa_k(\Sigma_u^{1/2}Qe_k)^{\otimes4}
\]
for some \(\kappa\in\mathcal K_{\delta_4}^{\max}(j;P)\), with \(\delta_4>0\).
\end{assumption}

\begin{assumption}[Nonempty common shock-law completion]\label{ass:nonempty-svar}
The set \(\mathcal Q_{\mathrm{SVAR}}(P)\) is nonempty.  This keeps \(h_{\mathrm{SVAR}}(w;P)\) finite and focuses the proposal on LP/SVAR non-equivalence rather than inconsistency of the non-Gaussian SVAR model.
\end{assumption}

\begin{assumption}[Exposed-face regularity]\label{ass:exposed-face}
The horizonwise support argmax set \(\mathcal M_w^H(P)\) is a compact exposed face of \(\mathcal R_{\mathrm{HLP}}(P)\), and the common-impact support argmax set \(\mathcal M_w^C(P)\) is compact.  Neighborhoods of these faces admit semi-algebraic descriptions for the sign cone, the common-impact pasting set, and the cumulant-diagonalizing locus, with well-defined local distances.
\end{assumption}

\begin{assumption}[Local exposure curvature]\label{ass:curvature}
There exists a constant \(c_w(P)>0\) such that, for every horizonwise exposed response \(r\in\mathcal M_w^H(P)\), every common-impact exposed rotation \(Q\in\mathcal M_w^C(P)\), and every \(R\in\mathcal Q_{\mathrm{SVAR}}(P)\) in the local comparison neighborhood,
\[
w^\transpose r-\ell_w(R;P)\ge c_w(P)\operatorname{dist}(r,\mathcal R_{\mathrm{paste}}(P))\,r_{\mathrm{cum}}(Q;P)
\]
whenever the comparison leaves the exposed LP face through the pasting and cumulant-label channels with positive sign exposure.  This is a local transversality hypothesis, not the flagship theorem.
\end{assumption}

\begin{assumption}[No response-flat degeneracy]\label{ass:no-flat}
The function \(\ell_w(Q;P)\) is not constant on any connected component of \(\mathcal Q_{\mathrm{CLP}}(P)\) that contains both a support-exposed masquerading rotation and a common-impact cumulant-diagonalizing rotation.
\end{assumption}

\begin{assumption}[Parent-collapse specialization]\label{ass:parent-collapse}
The parent margin \(\chi_w(P)\) is defined by the cumulant-envelope support loss from \texttt{eid\_lp\_svar\_nonequiv}/\texttt{v1}.  In the parent-collapse specialization, horizonwise LP rows are restricted ex ante to one common impact direction so \(h_{\mathrm{HLP}}=h_{\mathrm{CLP}}\), the sign and pasting channels are normalized as \(E_w^{\mathrm{sign}}(P)=1\) and \(\Pi_w^{\mathrm{paste}}(P)=1\), and the collapsed cumulant channel is defined as \(\Lambda_w^{\mathrm{cum}}(P)=\chi_w(P)/c_w(P)\).  Hence \(c_w(P)E_w^{\mathrm{sign}}(P)\Pi_w^{\mathrm{paste}}(P)\Lambda_w^{\mathrm{cum}}(P)=\chi_w(P)\) by definition.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: mechanism objects are well-defined]\label{thm:mechanism-objects}
Under Assumptions~\ref{ass:finite-response}--\ref{ass:exposed-face}, the sets \(\mathcal R_{\mathrm{HLP}}(P)\), \(\mathcal Q_{\mathrm{CLP}}(P)\), \(\mathcal Q_{\mathrm{SVAR}}(P)\), \(\mathcal M_w^H(P)\), \(\mathcal M_w^C(P)\), \(\mathcal D(P)\), and \(\mathcal R_{\mathrm{paste}}(P)\) are compact semi-algebraic sets.  The three diagnostics \(E_w^{\mathrm{sign}}(P)\), \(\Pi_w^{\mathrm{paste}}(P)\), and \(\Lambda_w^{\mathrm{cum}}(P)\) are finite, nonnegative, and computable by finite semi-algebraic optimization from \((\Gamma_0,\ldots,\Gamma_H,\Sigma_u,K_u,A,Z,w)\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) \citet{Read2022} gives sign/zero feasibility algorithms and \citet{Guay2021} gives higher-moment rank checks, but neither defines one diagnostic tuple that separates sign exposure, common-impact pasting, and cumulant labeling.  \citet[Sections~2--3]{CarrieroMarcellinoTornese2024} blends sign-type information with statistical identification, but does not give this support-function diagnostic.  (b) This object-level theorem gives \citet{DrautzburgWright2023} a computable population checklist before comparing independence-refined SVAR responses with LP sign responses.

\begin{conjecture}[Conjecture 1: three-channel mechanism factorization (NOT YET PROVED)]\label{conj:mechanism-factorization}
Under Assumptions~\ref{ass:finite-response}--\ref{ass:curvature}, there is a nonempty open semi-algebraic class \(\mathcal O_{\mathrm{mech}}\) of observable laws and report directions such that, for every \((P,w)\in\mathcal O_{\mathrm{mech}}\),
\[
\Delta_w^H(P)\ge \tau_w^{\mathrm{mech}}(P)
=c_w(P)E_w^{\mathrm{sign}}(P)\Pi_w^{\mathrm{paste}}(P)\Lambda_w^{\mathrm{cum}}(P).
\]
On the exposed-face subclass where the nearest SVAR rotation is reached by the same local normal direction that leaves the LP support face, the inequality is sharp up to a second-order remainder:
\[
\Delta_w^H(P)=\tau_w^{\mathrm{mech}}(P)+o\!\left(E_w^{\mathrm{sign}}\Pi_w^{\mathrm{paste}}\Lambda_w^{\mathrm{cum}}\right).
\]
The strict positive gap is therefore mechanism-generated, not an assumed parent margin.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest comparator is the parent \texttt{eid\_lp\_svar\_nonequiv}/\texttt{v1}, whose epsilon-gap is exactly that it assumed \(\chi_w(P)>0\) instead of isolating the mechanisms that make it positive.  The closest published comparators are \citet[Sections~2--3]{PlagborgMollerWolf2021}, \citet[Section~2]{Wolf2022}, \citet[Sections~2--3]{LanneMeitzSaikkonen2017}, \citet[Sections~2--3]{DrautzburgWright2023}, and \citet[Sections~2--3]{CarrieroMarcellinoTornese2024}; none gives a multiplicative mechanism lower bound for horizonwise LP/sign versus non-Gaussian SVAR support.  (b) Resolving it gives applied users of \citet{DrautzburgWright2023} a way to diagnose whether rejected LP robustness paths are sign masquerades, common-impact pasting failures, or cumulant-label failures.

\begin{conjecture}[Conjecture 2: iff frontier for strict non-equivalence (NOT YET PROVED)]\label{conj:iff-frontier}
Under Assumptions~\ref{ass:finite-response}--\ref{ass:no-flat}, restrict attention to the open class where \(c_w(P)>0\).  Then
\[
\Delta_w^H(P)>0
\quad\Longleftrightarrow\quad
E_w^{\mathrm{sign}}(P)>0,
\ \Lambda_w^{\mathrm{cum}}(P)>0,
\ \Pi_w^{\mathrm{paste}}(P)>0,
\]
except on the response-flat exceptional set ruled out by Assumption~\ref{ass:no-flat}.
The zero-channel conclusion is setwise, not inferred from the infimum diagnostics alone: \(\Delta_w^H(P)=0\) follows when the absent channel is certified by \(\mathcal A_w^+(P)=\emptyset\) together with common restrictions, by \(\overline\Pi_w^{\mathrm{paste}}(P)=0\), or by \(\overline\Lambda_w^{\mathrm{cum}}(P)=0\).  In contrast, \(\Pi_w^{\mathrm{paste}}(P)=0\) or \(\Lambda_w^{\mathrm{cum}}(P)=0\) by itself only says that at least one exposed optimizer has a representative in the smaller set, and is not claimed to make every optimizer representative.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Sections~2--3]{PlagborgMollerWolf2021} supplies the zero-gap common-restriction endpoint, while \citet[Section~2]{Wolf2022} supplies a sign-masquerading warning and \citet[Sections~2--3]{GourierouxMonfortRenne2017} supplies the non-Gaussian label endpoint.  The epsilon-gap is the iff frontier between these endpoints, with \citet[Sections~2--3]{CarrieroMarcellinoTornese2024} as the blended-identification comparator.  (b) The consumer is \citet{PlagborgMollerWolf2021}: the conjecture states exactly which missing channel prevents their common-restriction equivalence from applying to a non-Gaussian SVAR label.

\begin{theorem}[Theorem 2: reduction to the parent margin]\label{thm:parent-reduction}
Under Assumptions~\ref{ass:finite-response}--\ref{ass:nonempty-svar} and \ref{ass:parent-collapse}, the mechanism diagnostic reduces to the parent cumulant-envelope loss:
\[
\tau_w^{\mathrm{mech}}(P)=\chi_w(P)
\]
by the definition of Assumption~\ref{ass:parent-collapse}.  Consequently, Conjecture~\ref{conj:mechanism-factorization} strictly refines the parent \texttt{v1} margin claim rather than replacing it with an unrelated theorem.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This theorem is a bookkeeping reduction to the parent, not the flagship novelty.  Its gap to the parent is interpretive: it records exactly how the old one-margin statement appears as a collapsed special case of the mechanism proposal.  (b) The concrete consumer is the thmsmith banked parent \texttt{eid\_lp\_svar\_nonequiv}/\texttt{v1}: downstream derivations can reuse the parent conditional theorem when the mechanism conjecture is not yet proved.

\section{Sanity-check corollaries}
\begin{corollary}[Common restrictions recover LP/VAR equivalence]\label{cor:pmw}
Under Assumptions~\ref{ass:finite-response}--\ref{ass:sign-cone}, define the common-restriction LP object \(\mathcal R_{\mathrm{HLP}}^{\mathrm{common}}(P)=\mathcal R_{\mathrm{CLP}}(P)\) by imposing the same common-impact restriction on the LP side before taking supports.  If the fourth-cumulant label is removed from both sides, or imposed equally on both sides, then the compared feasible response sets are identical, \(\overline\Pi_w^{\mathrm{paste}}(P)=0\), \(\overline\Lambda_w^{\mathrm{cum}}(P)=0\), and \(h_{\mathrm{HLP}}^{\mathrm{common}}(w;P)-h_{\mathrm{SVAR}}(w;P)=0\).  This is the literal common-restriction specialization of \citet{PlagborgMollerWolf2021}; it is not a claim that the original horizonwise relaxation \(\mathcal R_{\mathrm{HLP}}(P)\) equals the common-impact set without imposing the common restriction.
\end{corollary}

\begin{corollary}[Reduction to parent under parent collapse]\label{cor:parent}
Under Assumption~\ref{ass:parent-collapse}, the mechanism proposal collapses to the parent \texttt{v1} statement because the sign-cone exposure and pasting channels are normalized away, leaving exactly the cumulant-envelope support loss \(\chi_w(P)\).
\end{corollary}

\begin{corollary}[Pure sign masquerading is not enough]\label{cor:sign-not-enough}
Under Assumptions~\ref{ass:finite-response}--\ref{ass:no-flat}, if \(E_w^{\mathrm{sign}}(P)>0\) but \(\overline\Lambda_w^{\mathrm{cum}}(P)=0\) or \(\overline\Pi_w^{\mathrm{paste}}(P)=0\), then the proposal predicts no strict horizonwise-LP/SVAR gap from non-Gaussian labeling alone.  The sign-masquerading channel identified by \citet{Wolf2022} must be paired with a positive setwise common-impact pasting and cumulant-label channel.
\end{corollary}

\section{Proof-sketch route}
Theorem~\ref{thm:mechanism-objects} should follow from compactness of \(S^{n-1}\) and \(O(n)\), continuity of \(Q\mapsto\psi_j(Q)\), and the Tarski-Seidenberg closure of semi-algebraic sets under projection over the horizonwise directions \(q_h\) and cumulant vector \(\kappa\).  Conjecture~\ref{conj:mechanism-factorization} should be attacked by local variational analysis on nested semi-algebraic sets: stratify the horizonwise sign cone, the common-impact pasting set, and the cumulant-diagonalizing locus, then prove an error-bound inequality relating support loss to the product of the three named distances on exposed LP faces.  Conjecture~\ref{conj:iff-frontier} requires checking both directions: positivity of all three infimum channels should imply a normal-cone separation of horizonwise LP support maximizers from \(\mathcal R_{\mathrm{SVAR}}\), while a setwise zero channel \(\overline\Pi_w^{\mathrm{paste}}=0\) or \(\overline\Lambda_w^{\mathrm{cum}}=0\) should construct common-restriction representatives for all exposed optimizers.  Theorem~\ref{thm:parent-reduction} is algebraic substitution of the collapsed channel definitions, where \(\Lambda_w^{\mathrm{cum}}=\chi_w/c_w\) is imposed rather than inferred.  The boundary cases needing explicit algebra are Gaussian or equal-kurtosis labels, sign cones that already pin the labelled column, disconnected non-Gaussian rotation sets, and report directions flat on an exposed face.

\section{Honest scope flags}
Theorem~\ref{thm:mechanism-objects} and Theorem~\ref{thm:parent-reduction} are setup and reduction results.  The flagship mathematical work is open in Conjectures~\ref{conj:mechanism-factorization} and \ref{conj:iff-frontier}.  The multiplicative form of \(\tau_w^{\mathrm{mech}}\) may need to become a minimum or infimal-convolution bound after the local error-bound analysis; if so, the mechanism interpretation should survive but the exact scalar formula would change.  The proposal does not claim that standard LP estimators estimate fourth cumulants.  It is a population identification proposal for comparing a sign-only LP relaxation with a non-Gaussian structural shock-law restriction.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial mechanism-axis upgrade draft; prior verdict: none.
\item v2 (revise) --- relocked the proposal to the parent partial-ID support-function cluster, made pasting a horizonwise-to-common-impact channel distinct from cumulant matching, added Carriero--Marcellino--Tornese 2024 and location-level comparator anchors, and repaired the parent-collapse identity by defining \(\Lambda_w^{\mathrm{cum}}=\chi_w/c_w\); prior verdict: REVISE.
\item v3 (revise) --- patched the sign-exposure diagnostic to avoid empty-row minima, made Conjecture~2's zero-channel clause setwise rather than infimum-based, and made the PMW sanity reduction compare a common-restriction LP object to the SVAR object; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Arias, Rubio-Ramirez, and Waggoner(2018)]{AriasRubioRamirezWaggoner2018}
Arias, J.~E., J.~F. Rubio-Ramirez, and D.~F. Waggoner (2018).
Inference based on structural vector autoregressions identified with sign and zero restrictions: Theory and applications.
\emph{Econometrica} 86(2), 685--720.

\bibitem[Carriero, Marcellino, and Tornese(2024)]{CarrieroMarcellinoTornese2024}
Carriero, A., M. Marcellino, and T. Tornese (2024).
Blended identification in structural VARs.
\emph{Journal of Monetary Economics} 146, 103581.

\bibitem[Drautzburg and Wright(2023)]{DrautzburgWright2023}
Drautzburg, T. and J.~H. Wright (2023).
Refining set-identification in VARs through independence.
\emph{Journal of Econometrics} 235(2), 1827--1847.

\bibitem[Gourieroux, Monfort, and Renne(2017)]{GourierouxMonfortRenne2017}
Gourieroux, C., A. Monfort, and J.-P. Renne (2017).
Statistical inference for independent component analysis: Application to structural VAR models.
\emph{Journal of Econometrics} 196(1), 111--126.

\bibitem[Guay(2021)]{Guay2021}
Guay, A. (2021).
Identification of structural vector autoregressions through higher unconditional moments.
\emph{Journal of Econometrics} 225(1), 27--46.

\bibitem[Jorda(2005)]{Jorda2005}
Jorda, O. (2005).
Estimation and inference of impulse responses by local projections.
\emph{American Economic Review} 95(1), 161--182.

\bibitem[Lanne, Liu, and Luoto(2026)]{LanneLiuLuoto2026}
Lanne, M., K. Liu, and J. Luoto (2026).
Identifying structural vector autoregressions via non-Gaussianity of potentially dependent shocks.
\emph{The Econometrics Journal}, utag002.

\bibitem[Lanne, Meitz, and Saikkonen(2017)]{LanneMeitzSaikkonen2017}
Lanne, M., M. Meitz, and P. Saikkonen (2017).
Identification and estimation of non-Gaussian structural vector autoregressions.
\emph{Journal of Econometrics} 196(2), 288--304.

\bibitem[Montiel Olea and Plagborg-Moller(2021)]{MontielOleaPlagborgMoller2021}
Montiel Olea, J.~L. and M. Plagborg-Moller (2021).
Local projection inference is simpler and more robust than you think.
\emph{Econometrica} 89(4), 1789--1823.

\bibitem[Montiel Olea, Plagborg-Moller, Qian, and Wolf(2024)]{MontielOleaPlagborgMollerQianWolf2024}
Montiel Olea, J.~L., M. Plagborg-Moller, E. Qian, and C.~K. Wolf (2024).
Double robustness of local projections and some unpleasant VARithmetic.
NBER Working Paper 32495; \emph{Econometrica}, forthcoming.

\bibitem[Plagborg-Moller and Wolf(2021)]{PlagborgMollerWolf2021}
Plagborg-Moller, M. and C.~K. Wolf (2021).
Local projections and VARs estimate the same impulse responses.
\emph{Econometrica} 89(2), 955--980.

\bibitem[Read(2022)]{Read2022}
Read, M. (2022).
Algorithms for inference in SVARs identified with sign and zero restrictions.
\emph{The Econometrics Journal} 25(3), 699--718.

\bibitem[Wolf(2022)]{Wolf2022}
Wolf, C.~K. (2022).
What can we learn from sign-restricted VARs?
\emph{AEA Papers and Proceedings} 112, 471--475.
\end{thebibliography}

\end{document}
