\begin{abstract}
We study independent, heterogeneous Bernoulli assignment in bipartite experiments, where intervention units are assigned treatment and outcome units may depend on assignments in known intervention neighborhoods. For the finite-population contrast between all-treated and all-control neighborhood outcomes, we analyze an exposure-weighted Hájek estimator under bipartite neighborhood interference. With bounded potential outcomes, we derive a graph-and-design-dependent envelope that upper-bounds the design-based variance scale of its linearization and can be minimized subject to a positivity-constrained expected-treatment budget. Under the full assumptions of \cref{obj:thm:hetero-clt} and~\cref{obj:thm:postdesign-wald}, the envelope-optimal design supports asymptotic normality and a graph-only Wald scale yields asymptotically conservative coverage. We also give conditions under which heterogeneous probabilities strictly improve the envelope relative to homogeneous assignment and, under an admissible budget and bounded outcome degree, certify a separable overlap-based surrogate. A complementary unbounded-degree construction establishes the necessity of richer overlap control for this approximation. Together, the results provide an outcome-model-free design criterion with convex, inferential, separation, and approximation guarantees.
\end{abstract}

\section{Introduction}

Interference often separates the units receiving assignments from the units whose outcomes are measured. In bipartite experiments, treatments are assigned to one set of units, while outcomes are recorded for another set whose members may each depend on several assigned interventions. This structure arises in settings involving suppliers and customers, advertisers and users, providers and patients, or policies and exposed populations. It also creates a design problem: even when assignments are independent, overlapping intervention neighborhoods induce dependence among outcome-level exposure terms.

This paper considers a finite-population bipartite experiment with known graph structure and independent Bernoulli assignment probabilities that may differ across intervention units. The estimand is the average contrast between each outcome unit's all-treated and all-control neighborhood potential outcomes. Under the bipartite interference restriction in \cref{obj:ass:bipartite-interference}, the exposure-weighted Hájek estimator in \cref{obj:def:hetero-hajek-estimator} uses realized all-treated and all-control neighborhood exposures. The design question is how to allocate a fixed expected number of treated intervention units when potential outcomes are unavailable at the design stage.

The answer studied here is a conservative design criterion. \Cref{obj:thm:hetero-envelope} gives a graph-only envelope for the design-based variance scale of the estimator's linearization under independent heterogeneous Bernoulli assignment and bounded potential outcomes. The envelope depends on shared intervention neighborhoods and assignment probabilities and is outcome-model independent. We minimize this upper bound over the feasible class in \cref{obj:def:feasible-designs}, which imposes both a positivity floor and a fixed expected-treatment budget. This yields a graph-adaptive allocation with an auditable robustness interpretation when outcomes are unavailable at design time.

The criterion targets an analytically convenient uniform variance upper bound over the bounded-outcome class. Its value is that the objective is observable before randomization, permits an exact convex formulation, and comes with formal separation, inference, and approximation certificates. It provides a robust graph-only benchmark for subsequent numerical comparisons with homogeneous, clustered, and outcome-informed alternatives.

The paper's closest literatures differ in either the assignment law, the information used to choose a design, or the target of optimization.

\begin{table}[t]
\centering
\small
\begin{tabular}{p{0.22\linewidth}p{0.18\linewidth}p{0.18\linewidth}p{0.30\linewidth}}
\hline
Approach & Assignment law & Outcome information in design & Objective and deliverable \\
\hline
Homogeneous bipartite Bernoulli analysis \citep{LuShiFangZhangDing2025BipartiteDesign}
& Common Bernoulli probability
& None
& Design-based estimation, asymptotic inference, and conservative variance analysis under homogeneous assignment. \\
Graph-cluster and bipartite-cluster designs \citep{UganderYin2020RandomizedGCR,BrennanMirrokniPougetAbadie2022ClusterBipartite}
& Correlated assignment induced by clusters
& Depends on the design objective and model restrictions
& Cluster construction to alter exposure probabilities, spillovers, bias, power, or minimax performance. \\
Exposure-reweighted or model-based bipartite methods \citep{HarshawSavjeEisenstatMirrokniPougetAbadie2021BipartiteERL,DoudchenkoEtAl2020BipartiteDesign}
& Varies by method
& Typically exposure or response-model structure
& Estimation or design criteria tailored to specified exposure-response structure. \\
This paper
& Independent heterogeneous Bernoulli probabilities
& None beyond the observed bipartite graph
& Convex minimization of an analytically convenient bounded-outcome variance upper bound, a strict objective-separation diagnostic, and a bounded-degree surrogate certificate. \\
\hline
\end{tabular}
\caption{Scope of the graph-only heterogeneous-probability criterion relative to related approaches.}
\end{table}

The first contribution is a covariance representation that separates graph-and-design loads from unknown centered potential outcomes. \Cref{obj:prop:homogeneous-reduction} recovers the homogeneous Bernoulli case, in which same-exposure loads depend on the size of shared neighborhoods. \Cref{obj:thm:hetero-envelope} extends this representation to heterogeneous independent probabilities and establishes the corresponding envelope under bounded potential outcomes. This extension captures an intervention's full role in outcome-pair overlap beyond its intervention-side incidence.

The second contribution concerns the allocation problem induced by that envelope. Under an admissible positivity floor and budget, \cref{obj:thm:convex-design} establishes existence of an envelope minimizer and characterizes it with first-order conditions. The associated gradient score aggregates the overlap contribution of an intervention across outcome pairs. \Cref{obj:thm:heterogeneity-separation} shows that, when homogeneous-point scores differ and the homogeneous rate is strictly interior and unequal to one half, a heterogeneous direction strictly improves the envelope and admits a quantitative lower bound. In the special case of singleton outcome neighborhoods, unequal intervention-side incidences are sufficient for this score heterogeneity.

The third contribution is a computational simplification with an exact certificate. The envelope couples probabilities within shared neighborhoods, while \cref{obj:thm:surrogate-certificate} gives a uniform approximation ratio for a separable surrogate under an admissible positivity-constrained budget and bounded outcome degree. \Cref{obj:thm:dispersion-certificate-unbounded} complements this guarantee with an unbounded-degree construction in which the approximation ratio diverges despite dispersed intervention-side degrees and comparable surrogate weights. Together, the results identify outcome-neighborhood and overlap diagnostics as the decisive inputs for surrogate reliability.

The inferential results remain design based throughout: potential outcomes are fixed, and assignment is the source of randomness. Under independent heterogeneous Bernoulli assignment, bipartite interference, bounded potential outcomes, bounded outcome degree, bounded overlap dependency, uniform positivity, and a nondegenerate variance scale, \cref{obj:thm:hetero-clt} establishes a Hájek central limit theorem for the envelope-optimal design. Under the same substantive regularity conditions, \cref{obj:thm:postdesign-wald} gives asymptotically conservative coverage for an interval using the deterministic graph-only scale in \cref{obj:def:conservative-variance-estimator}. The stated bounded-degree regime provides the local-dependence control supporting both guarantees.

The paper is related to design-based causal inference under interference \citep{HudgensHalloran2008,AronowSamii2017GeneralInterference,SavjeAronowHudgens2021}, to approximate or structured neighborhood restrictions \citep{Leung2019ApproxNeighborhoodInterference}, and to bipartite causal designs \citep{ZiglerPapadogeorgou2018,ChattopadhyayImaiZubizarreta2023GeneralizedNetwork}. Relative to homogeneous Bernoulli bipartite analysis \citep{LuShiFangZhangDing2025BipartiteDesign}, the contribution is the graph-dependent heterogeneous-probability envelope and the associated optimization and approximation results. Relative to clustered designs, the assignment law remains independent across intervention units; whether that operational distinction is preferable is application dependent.

The formal statements and associated proofs have Lean~4 verification support; the verification appendix describes its precise scope. The remainder of the paper sets out the experiment, estimator, and feasible design class; develops the envelope, inference, separation, and surrogate results; and discusses the resulting scope and limitations.
