% S9-fragment-statement
\begin{theorem}[Finite endpoint certificates for sparse random-set rejection]\label{thm:certificate}
\paragraph{Motivating conjecture.}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:audit}, for every finite direction \(u\in\mathcal U_K\) and endpoint \(t>h_K(u;P)\), endpoint rejection admits a finite certificate of exactly one of the following two types.  If \(t\notin\mathcal E_{\mathrm{cell}}(u,P)\), then \(t\) is separated by a violated bounded-response, observed-law, or Aumann-support inequality for the cellwise random set of feasible contrast selections.  If \(t\in\mathcal E_{\mathrm{cell}}(u,P)\), then the rejection has a sparse-network incompatibility certificate for the \(K\)-label exposure assignments, expressed through hidden-edge incidence, degree-cap, and label-support constraints.  In the special case \(K=2\) with binary ``unexposed/exposed'' labels and cellwise-feasible demanded exposure events, the network part reduces to a capacitated set-cover / b-matching feasibility certificate.

Confirmed: every endpoint \(t>h_K(u;P)\) admits the stated finite cellwise-or-network certificate, with \(K=2\) reducing to capacitated set-cover / b-matching feasibility.
\end{theorem}

% S13-refutation-attempt
\paragraph{Refutation attempt before proof.}
The cluster-level refutation primitive is vertex enumeration of the smallest non-trivial finite response-type problem.  Specialize to \(K=2\), binary outcomes, binary labels \(0=\) unexposed and \(1=\) exposed, and finitely many assignment cells.  A potential refuting witness would have to satisfy three properties simultaneously:
\[
t>h_K(u;P),\qquad t\in\mathcal E_{\mathrm{cell}}(u,P),\qquad
\text{and no finite network certificate for the demanded labels.}
\]
The enumeration has two layers.  First enumerate the vertices of the cellwise bounded-response polytope after adding the equality \(u^\transpose\theta_{\mathrm{DI}}=t\).  If the augmented polytope is empty, the candidate is not a refutation: finite-dimensional Farkas separation gives a violated cellwise inequality.  If a cellwise vertex exists, record its demanded exposure table \(z^\star\).  Second enumerate all hidden-edge incidence vectors \(b\in\{0,1\}^{\mathcal C}\) satisfying \(b_e=1\) on observed edges, \(b_e=0\) off \(\mathcal L\cup\mathcal C\), and \(\sum_{e\ni i,\ e\in\mathcal C}b_e\le\bar d_i\), and all binary label maps that are measurable with respect to the selected neighbors and have image size at most two.

The candidate branches considered by this enumeration are exhaustive.  A branch that generates \(z^\star\) together with the same bounded response selection would be an element of \(\mathcal F_K(P)\) by Assumptions~\ref{ass:sparse}--\ref{ass:matching}, so it would imply \(h_K(u;P)\ge t\), contradicting \(t>h_K(u;P)\).  Every remaining branch stops at a violated hidden-edge incidence row, degree-cap row, label-measurability row, support-size row, or demanded-label row.  Thus the searched space contains no counterexample to the dichotomy; the positive proof below abstracts exactly this finite alternative.

% S10 Interpretation
\paragraph{Interpretation.}
The theorem says that an endpoint failure for the sparse support program is auditable without guessing why the endpoint failed.  If the endpoint is not even attainable by the cellwise random-set relaxation, the obstruction is already a random-set or bounded-response obstruction: the demanded contrast is outside the Aumann expectation envelope generated by bounded potential outcomes and the observed law.  If the endpoint is attainable cellwise, then the remaining failure is not a response-bounds failure.  It is a shared-map failure: the demanded exposure cells cannot be generated by one hidden graph obeying the caps and one \(K\)-support exposure-label system.  This is the promised operational distinction between the cellwise frontier and the sparse shared-network frontier.

% S11 Proof
\begin{proof}
Fix \(u\in\mathcal U_K\) and \(t>h_K(u;P)\).  By Assumption~\ref{ass:finite}, there are finitely many units, assignment cells, candidate hidden edges, and exposure labels.  By Assumptions~\ref{ass:consistency} and~\ref{ass:matching}, the response variables used by the support programs are bounded in \([0,1]\) and satisfy finitely many observed-law matching equalities.  Hence both the sparse and cellwise endpoint-audit problems are finite systems of algebraic constraints.

Let \(\mathcal P_{\mathrm{cell}}(u,t;P)\) be the augmented cellwise feasibility system obtained from \(\mathcal F_{\mathrm{cell},K}(P)\) by adding the linear equality
\[
u^\transpose\theta_{\mathrm{DI}}=t.
\]
The variables are the cellwise feasible contrast selections and bounded response coordinates appearing in Section~\ref{sec:functional}.  The rows of this finite system are exactly the bounded-response inequalities, the observed-law matching equalities, the local positivity and support-size rows from Assumptions~\ref{ass:cellwise} and~\ref{ass:positivity}, and the displayed endpoint equality.

First suppose \(t\notin\mathcal E_{\mathrm{cell}}(u,P)\).  By the definition of \(\mathcal E_{\mathrm{cell}}(u,P)\), the augmented system \(\mathcal P_{\mathrm{cell}}(u,t;P)\) is infeasible.  The finite-dimensional Farkas alternative therefore provides multipliers on the inequality and equality rows whose nonnegative linear combination yields a strict contradiction.  Written in the random-set language of \cite{BeresteanuMolchanovMolinari2011}, this is precisely a violated support inequality for the Aumann expectation of the cellwise feasible contrast random set; in coordinate form the same certificate is a finite list of violated bounded-response, observed-law, local-positivity, or support rows.  This proves the first certificate type.

Now suppose \(t\in\mathcal E_{\mathrm{cell}}(u,P)\).  Choose a cellwise feasible selection \(w^\star\in\mathcal F_{\mathrm{cell},K}(P)\) with \(u^\transpose\theta_{\mathrm{DI}}(w^\star)=t\), and let \(z^\star\) denote its demanded table of exposure labels by unit and assignment cell.  Consider the finite sparse-network realization system \(\mathcal N(z^\star)\).  Its binary hidden-edge variables \(b_e\) satisfy the incidence restrictions from Assumption~\ref{ass:sparse}:
\[
b_e\in\{0,1\},\qquad
\sum_{e\ni i,\ e\in\mathcal C} b_e\le \bar d_i
\quad\text{for every unit }i.
\]
Its label variables \(r_{i\alpha k}\in\{0,1\}\), indexed by unit \(i\), assignment cell \(\alpha\in\{0,1\}^{n-1}\), and label \(k\in\{0,\ldots,K-1\}\), satisfy
\[
\sum_{k=0}^{K-1}r_{i\alpha k}=1,\qquad
\#\{k:\exists\alpha\ r_{i\alpha k}=1\}\le K,
\]
and the neighborhood-measurability rows required by Assumption~\ref{ass:k-support}: if two assignment cells \(\alpha,\alpha'\) agree on all selected neighbors of \(i\), then \(r_{i\alpha k}=r_{i\alpha'k}\) for every \(k\).  Equivalently, after writing \(g_{ij}\) for the observed-or-hidden edge indicator, these equalities are enforced by the finite linear implications
\[
|r_{i\alpha k}-r_{i\alpha'k}|
\le
\sum_{j:\alpha_j\ne\alpha'_j} g_{ij}.
\]
Finally \(\mathcal N(z^\star)\) imposes the demanded-label rows \(r_{i\alpha k}=z^\star_{i\alpha k}\) on all design-positive cells represented in \(w^\star\), together with the deterministic normalization rows from Assumption~\ref{ass:labels}.

If \(\mathcal N(z^\star)\) had a solution, then the solved hidden graph and exposure maps, combined with the bounded response selection already present in \(w^\star\), would satisfy Assumptions~\ref{ass:sparse}--\ref{ass:matching}.  Assumption~\ref{ass:positivity} supplies the active-label denominators used in the totalized direct and indirect coordinates, and Assumption~\ref{ass:audit} ensures that the finite direction \(u\) is one of the audited directions.  Therefore the same selection would be an element of \(\mathcal F_K(P)\) attaining \(u^\transpose\theta_{\mathrm{DI}}=t\), contradicting \(t>h_K(u;P)\).  Hence \(\mathcal N(z^\star)\) is infeasible.

Because \(\mathcal N(z^\star)\) is a finite \(0\)-\(1\) incidence system, infeasibility has a finite certificate: enumerate all incidence vectors satisfying the hidden-edge and degree-cap rows, and for each surviving incidence vector enumerate the finitely many \(K\)-label maps.  Each leaf fails one of the displayed incidence, degree-cap, label-measurability, label-support, normalization, or demanded-label rows.  This finite failed-branch list is the sparse-network incompatibility certificate.  The two cases \(t\notin\mathcal E_{\mathrm{cell}}(u,P)\) and \(t\in\mathcal E_{\mathrm{cell}}(u,P)\) are mutually exclusive and exhaustive, so the audit rule assigns exactly one certificate type to every endpoint \(t>h_K(u;P)\).

It remains to identify the \(K=2\) reduction.  With binary labels interpreted as unexposed/exposed and demanded exposure events fixed cellwise, introduce one edge-choice variable \(b_{ij}\) for each hidden candidate edge.  For a demanded exposed event of unit \(i\) under assignment \(\alpha\), the constraint is a covering row
\[
\sum_{j:\alpha_j=1,\ \{i,j\}\in\mathcal L}1
+
\sum_{j:\alpha_j=1,\ \{i,j\}\in\mathcal C} b_{ij}\ge1.
\]
For a demanded unexposed event, every treated observed neighbor is forbidden and every treated candidate neighbor must have \(b_{ij}=0\).  Together with
\[
\sum_{j:\{i,j\}\in\mathcal C}b_{ij}\le\bar d_i,
\]
these rows are exactly a capacitated set-cover feasibility problem with b-matching-style degree capacities on the selected hidden-edge incidence vector; infeasibility of this finite system is the advertised network certificate.  This proves the theorem.
\end{proof}

% S12 Sanity check
\paragraph{Sanity check.}
If the cellwise relaxation is replaced by the sparse feasible class itself, then \(\mathcal E_{\mathrm{cell}}(u,P)\) becomes the sparse attainable endpoint set.  For \(t>h_K(u;P)\), no sparse endpoint equality \(u^\transpose\theta_{\mathrm{DI}}=t\) is attainable, so the first branch gives the ordinary finite support-function separation of a compact feasible set.  In the no-hidden-edge corner \(\mathcal C=\emptyset\), the network branch has no hidden variables: every demanded exposed event must already be covered by an observed treated neighbor, every demanded unexposed event must have no observed treated neighbor, and the certificate collapses to direct inspection of the fixed observed network.  For \(K=2\), these rows are the displayed capacitated cover constraints with all capacities equal to zero, matching the known fixed-exposure audit.

% S13 Counterexample or minimality check
\paragraph{Minimality check.}
The sparse-network branch genuinely needs the shared-map restriction in Assumptions~\ref{ass:sparse} and~\ref{ass:k-support}.  If the cellwise demanded labels are allowed to vary independently by unit and assignment cell, then any \(t\in\mathcal E_{\mathrm{cell}}(u,P)\) already has a feasible cellwise selection and there is no remaining hidden-edge incidence system to refute.  In that weakened regime the second certificate type is vacuous, and endpoints between \(h_K(u;P)\) and \(h_{\mathrm{cell},K}(u;P)\) cannot be diagnosed as sparse-network failures.  The minimality role is therefore played by the finite shared hidden-edge incidence vector and the requirement that one \(K\)-support exposure map generate all demanded label cells.
