\paragraph{Refutation note for Conjecture 2 (joint-nonrectangular).}
\textbf{Conjecture restated verbatim.}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:audit}, there is an open set \(\mathcal O_K\) of finite observed laws \(P\) satisfying Assumption~\ref{ass:nondegenerate} such that
\[
\Delta_K(P)>0.
\]
For every \(P\in\mathcal O_K\),
\[
\Theta_I(P)\subsetneq
\prod_j [\inf_{\theta\in\Theta_I(P)}\theta_j,\ \sup_{\theta\in\Theta_I(P)}\theta_j],
\]
and there exists a direction \(u\in\mathcal U_K\) for which the componentwise rectangle overstates the sharp support value by exactly the direct-indirect coupling defect:
\[
h_{\mathrm{rect},K}(u;P)-h_K(u;P)=\Delta_K(P).
\]
For the concrete witness law \(P^\star\) in Corollary~\ref{cor:witness}, the conjectured certificate direction is \(u^\star=D_1-I_{01}\) and the conjectured margin is \(\Delta_2(P^\star)\ge1/40\).

\textbf{Verdict.}
Conjecture 2 is refuted because the advertised witness law \(P^\star\) has no \(K=2\) sparse exposure completion: unit 2's four neighbor-assignment means are all distinct, so no two-label exposure map can satisfy observed-law matching.

\paragraph{Refutation attempt and counterexample.}
The required refutation primitive is the two-strata response-type enumeration for the smallest nontrivial support.  I apply it directly to the advertised \(K=2,n=4\) witness law \(P^\star\) from Corollary~\ref{cor:witness}.  The search space for a unit with two possible path neighbors is the set of all binary maps
\[
q:\{0,1\}^2\to\{0,1\},
\]
which is the same as enumerating all two-label partitions of the four neighbor-assignment states.  This enumeration is stronger than a graph-subset search: if no such arbitrary binary partition works, then no map measurable with respect to any allowed neighbor subset can work.

Consider unit \(2\), whose left and right path-neighbor treatment indicators are \(z_L=A_1\) and \(z_R=A_3\).  Under \(P^\star\), its conditional mean table is
\[
m_{2a}(z_L,z_R)
=0.33+0.16a+0.11z_L+0.07z_R+0.05a\max\{z_L,z_R\}.
\]
Thus
\[
\begin{array}{c|cccc}
& (0,0)&(1,0)&(0,1)&(1,1)\\ \hline
a=0&0.33&0.44&0.40&0.51\\
a=1&0.49&0.65&0.61&0.72
\end{array}
\]
All four entries in the \(a=0\) row are distinct, and all four entries in the \(a=1\) row are distinct.  By Assumption~\ref{ass:k-support}, a \(K=2\) exposure map for unit \(2\) has at most two labels on these four neighbor states.  By the pigeonhole principle, any such map assigns the same label to at least two distinct states.  By Assumption~\ref{ass:consistency}, those two states must share the same potential-outcome value \(Y_2(a,k)\) for each own-treatment arm \(a\); by Assumption~\ref{ass:matching}, that common value must reproduce the observed conditional mean in both states.  The displayed table makes this impossible already in the \(a=0\) row.

Equivalently, the finite vertex enumeration over the \(2^4\) binary label assignments produces no feasible partition for unit \(2\).  The same obstruction also appears for unit \(3\):
\[
\begin{array}{c|cccc}
& (0,0)&(1,0)&(0,1)&(1,1)\\ \hline
a=0&0.35&0.46&0.42&0.53\\
a=1&0.51&0.67&0.63&0.74 .
\end{array}
\]
Hence the concrete law \(P^\star\) has \(\mathcal F_2(P^\star)=\emptyset\) under Assumptions~\ref{ass:finite}--\ref{ass:audit}.  Consequently \(\Theta_I(P^\star)\), the coordinate endpoints in the componentwise rectangle, \(h_2(u^\star;P^\star)\), and \(\Delta_2(P^\star)\) are not evaluable as finite sharp-support objects for this witness law.  This contradicts the conjecture's concrete claim that \(u^\star=D_1-I_{01}\) certifies \(\Delta_2(P^\star)\ge1/40\).  The nearest repair is not a proof of Conjecture 2 as stated: one would need either a different noncorner witness law whose conditional means are compatible with some two-label sparse exposure system, or a revised regime with \(K\ge4\) for the two-neighbor units.
