% --- S9-fragment-statement ---
\paragraph{Refutation note.}
\textbf{Conjecture 1 (verbatim).}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:nondegenerate} and Assumption~\ref{ass:cellwise}, there is a nonempty open set \(\mathcal O_{\Gamma,K}\) of nondegenerate finite observed laws and a finite direction family \(\mathcal V_K\subset\mathbb R^{K+K(K-1)}\) such that, for every \(P\in\mathcal O_{\Gamma,K}\), some \(u\in\mathcal V_K\) satisfies
\[
\Gamma_K(u;P)=h_{\mathrm{cell},K}(u;P)-h_K(u;P)>0.
\]
For the \(K=2,n=4\) witness law \(P^\star\) in Corollary~\ref{cor:witness}, the conjectured lower bound is
\[
\max_{u\in\mathcal V_2}\Gamma_2(u;P^\star)\ge \frac{1}{40}.
\]
The focal mathematical object is the shared-map compatibility gap \(\Gamma_K\), which compares two independently defined support programs: the sparse graph-compatible program \(h_K\) and the cellwise relaxation \(h_{\mathrm{cell},K}\).

\medskip
\noindent Refuted-with-counterexample: the stated \(K=2,n=4\) witness law \(P^\star\) has \(\mathcal F_2(P^\star)=\varnothing\), so the advertised finite compatibility gap \(\Gamma_2(u;P^\star)\) is not a well-defined sparse-versus-cellwise support-program comparison.

% --- S13-refutation-attempt ---
\paragraph{Refutation attempt and counterexample.}
The required refutation primitive is the two-strata response-type enumeration for the smallest nontrivial support, with \(K=2\), binary treatment, and the eight hidden-edge subsets of
\[
\mathcal C=\{\{1,2\},\{2,3\},\{3,4\}\}.
\]
For a fixed graph \(G\), the primitive enumerates every binary exposure partition \(e_i\) measurable with respect to the treatments of unit \(i\)'s neighbors in \(G\).  Observed-law matching under Assumption~\ref{ass:matching} implies the following deterministic cell restriction: for each own-treatment value \(a\), all assignments \(A_{-i}\) assigned to the same label \(e_i(A_{-i})=k\) must have the same observed conditional mean, because Assumption~\ref{ass:consistency} represents every such cell by one bounded response value \(Y_i(a,k)\).

Apply this enumeration to the proposed \(P^\star\) from Corollary~\ref{cor:witness}.  For unit \(2\), the observed mean is
\[
\mu_2(a,z_L,z_R)=0.33+0.16a+0.11z_L+0.07z_R+0.05a\max\{z_L,z_R\},
\]
where \(z_L=A_1\) and \(z_R=A_3\).  If the edge \(\{1,2\}\) is absent from \(G\), then \(e_2\) cannot depend on \(A_1\).  Holding \(A_3=0\) fixed gives
\[
\mu_2(a,1,0)-\mu_2(a,0,0)=0.11+0.05a>0,
\]
so two assignments with the same allowed exposure information would require different values of \(Y_2(a,k)\).  This violates Assumptions~\ref{ass:k-support}, \ref{ass:consistency}, and \ref{ass:matching}.  If instead the edge \(\{2,3\}\) is absent, holding \(A_1=0\) fixed gives
\[
\mu_2(a,0,1)-\mu_2(a,0,0)=0.07+0.05a>0,
\]
which gives the same contradiction.  Hence any feasible \(G\) would have to include both edges incident to unit \(2\).

When both incident edges are present, \(e_2\) may depend on the full pair \((A_1,A_3)\), but \(K=2\) leaves only two labels for four neighbor patterns.  At \(a=0\), the four means are
\[
\mu_2(0,0,0)=0.33,\quad
\mu_2(0,1,0)=0.44,\quad
\mu_2(0,0,1)=0.40,\quad
\mu_2(0,1,1)=0.51.
\]
They are all distinct.  By the pigeonhole principle, every binary partition of the four neighbor patterns puts two distinct means in one label cell, contradicting observed-law matching.  Thus unit \(2\) has no feasible binary exposure map for any candidate hidden-edge subset.

The same calculation holds for unit \(3\).  Its mean function is
\[
\mu_3(a,z_L,z_R)=0.35+0.16a+0.11z_L+0.07z_R+0.05a\max\{z_L,z_R\},
\]
with \(z_L=A_2\) and \(z_R=A_4\).  Missing either incident edge creates a positive omitted-neighbor contrast, while including both incident edges leaves the four \(a=0\) means
\[
0.35,\quad 0.46,\quad 0.42,\quad 0.53,
\]
again all distinct and therefore impossible to represent with two labels.

Consequently every one of the eight graph vertices in the sparse program fails feasibility for at least one of units \(2\) or \(3\).  The sparse feasible class is empty:
\[
\mathcal F_2(P^\star)=\varnothing.
\]
The advertised \(1/40\) witness is therefore not a finite shared-map compatibility calculation.  It is outside the stated \(K=2\) sparse-exposure regime rather than an example with
\(\Gamma_2(u^\star;P^\star)=h_{\mathrm{cell},2}(u^\star;P^\star)-h_2(u^\star;P^\star)\) bounded below by a verified finite slack.  This refutes Conjecture 1 as stated.  A nearest repair would replace \(P^\star\) by a law whose conditional means are constant on some two-label sparse exposure partition, or raise the support bound for the stated law to at least four labels for the two interior units; either change is a new theorem statement, not a proof of the original witness clause.
