% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_network\_random\_set, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_network\_random\_set} / \texttt{v1}%
  \\ \large\textit{A sparse exposure-collision frontier for when misspecified exposure maps become testable}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form partial-identification anchor with a specification-testing frontier, not a panel pool-mode.  The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_network\_random\_set},\texttt{v1},
P_{I,A,Y;\pi,\mathcal L,\mathcal C,\bar d,K,\mathcal E_0},\
\theta_{\mathrm{DI}},\
\mathcal R_{\mathrm{sparse}\ K\mathrm{-support,test}},\
\Lambda_K(P;\mathcal E_0)).
\end{gathered}
\]
Here \(I\) is a uniformly sampled unit from a finite population of size \(n\), \(A\in\{0,1\}^n\) is assigned by a known randomized design \(\pi\), \(Y_I\in\{0,1\}\) is the observed Bernoulli outcome, \(\mathcal L\) is the observed network, \(\mathcal C\) is a finite set of candidate unobserved edges, \(\bar d=(\bar d_1,\ldots,\bar d_n)\) are hidden-degree caps, \(K\ge2\) bounds the cardinality of latent exposure labels, and \(\mathcal E_0\) is the analyst's null exposure-map class.  The structural object is a pair \((G,e)\), where \(G\) extends \(\mathcal L\) by edges in \(\mathcal C\) while respecting \(\bar d\), and \(e_i:\{0,1\}^{n-1}\to\{0,\ldots,K-1\}\) is measurable with respect to \(i\)'s neighbors in \(G\).  Each structural explanation also carries Bernoulli response probabilities \(\mu_i(a,k)\in[0,1]\) with \(Y_I\mid(I=i,A,e)\sim\mathrm{Bernoulli}(\mu_i(A_i,e_i(A_{-i})))\).  The target \(\theta_{\mathrm{DI}}\in\mathbb R^{K+K(K-1)}\) stacks all fixed-label average direct effects \(D_k\) and ordered average indirect effects \(I_{k\ell}\), computed from \(\mu\), with unlabelled exposure partitions represented by all admissible label permutations.  The restrictions \(\mathcal R_{\mathrm{sparse}\ K\mathrm{-support,test}}\) are finite population, known randomized assignment, Bernoulli outcomes, consistency in the Bernoulli response probabilities, sparse-network compatibility, exposure sufficiency through \((A_i,e_i(A_{-i}))\), local positivity for active labels, the support-cardinality bound, primitive exposure relevance for positive-branch alternatives, and a null-vs-alternative decomposition \(\mathcal E_0\) against \(\mathcal E_{1,K}\), the sparse \(K\)-support alternatives outside \(\mathcal E_0\).  The bounding functional \(\Lambda_K(P;\mathcal E_0)\) is the proposed \(K\)-sparse exposure-collision modulus: a finite total-variation separation value computed from the full Bernoulli observable-law fibers induced by \(\mathcal E_0\) and exposure-relevant \(\mathcal E_{1,K}\) alternatives.  It is independent of any test's rejection rule and is used to define the sharp testability frontier.

\begin{abstract}
\citet{GaoHarshawSavjeWang2026} show that exposure-map specification tests have a severe worst-case impossibility: without further restrictions, no test uniformly beats random rejection against larger exposure-map alternatives.  This proposal asks whether the impossibility remains sharp when alternatives are sparse-network-compatible, have exposure image cardinality at most \(K\), and satisfy a primitive exposure-relevance contrast.  The proposed kernel is a finite collision frontier: a named modulus \(\Lambda_K(P;\mathcal E_0)\) is conjectured to be positive exactly when exposure-relevant sparse \(K\)-support alternatives are observationally separated from the null exposure class, and zero exactly when the \citet{LeCam1986}/Gao indistinguishability argument can be carried inside the sparse class.  Conjecture~\ref{conj:frontier} is the flagship statement; it is positioned against the classical total-variation testing frontier of \citet[Chapter~6]{LeCam1986}, the exposure-map impossibility of \citet{GaoHarshawSavjeWang2026}, and informed by \citet{Savje2024}'s definition-vs-assumption distinction and \citet{WeinsteinNevo2026}'s network-equivalence discussion.  If resolved, the result would tell applied network analysts when to test an exposure mapping and, at pointwise collisions, when to abandon testing and report the sharp random-set direct/indirect region instead.
\end{abstract}

\section{Introduction}
Exposure mappings make interference estimands finite-dimensional, but they also create a specification problem.  In many network experiments the analyst can plausibly bound exposure complexity: interference is local, the hidden network is sparse, and the number of distinct exposure labels is small.  Current impossibility theory is deliberately broad, so it does not say whether these sparse finite-support restrictions create a real escape hatch or merely disguise the same indistinguishability.  The methodological question is therefore a partial-identification question before it is an inference question: are the observable-law fibers of the null exposure class and the sparse \(K\)-support alternatives disjoint, or do they collide?

The main proposed finding is Conjecture~\ref{conj:frontier}.  It states that the independently defined \(K\)-sparse exposure-collision modulus \(\Lambda_K(P;\mathcal E_0)\) gives an if-and-only-if frontier.  When \(\Lambda_K>0\), a finite linear-separation statistic distinguishes the null class \(\mathcal E_0\) from sparse \(K\)-support alternatives with primitive exposure relevance and asymptotic power one under repeated experiments.  When \(\Lambda_K=0\), the null and exposure-relevant alternative fibers contain observationally colliding or arbitrarily close laws, so Lemma~\ref{lem:overlap-impossibility} applies the standard Le Cam/Gao indistinguishability machinery inside the restricted sparse class.  Conjecture~\ref{conj:noncorner} proposes a concrete noncorner class where \(\Lambda_2\ge 1/24\), so the frontier is not vacuous.

What is new is the sparse exposure-collision quotient, not the classical fact that total-variation separation is equivalent to testability.  \citet[Chapter~6]{LeCam1986} supplies the decision-theoretic TV lower bound, \citet[abstract and main result]{GaoHarshawSavjeWang2026} prove that broad exposure-map alternatives defeat any specification test, and \citet[Section~4, Proposition~4.1 and Theorem~4.2]{GaoHarshawSavjeWang2026} give a positive no-interference versus network-linear-in-means case.  \citet[Sections~4--5]{WeinsteinNevo2026} show that correct network structures may form equivalence classes and propose robust estimators over candidate networks.  This proposal's epsilon-gap is the finite algebraic frontier between these claims and the randomization-test literature of \citet[Sections~2--3]{HoshinoYanagi2023}, \citet[Sections~2--3]{BasseFellerToulis2019}, \citet[Sections~2--4]{PuelzBasseFellerToulis2022}, and \citet[Sections~2--4]{AtheyEcklesImbens2018}: \(\Lambda_K\) is a computable LP-dual support/fiber separation over sparse network-map equivalence classes, with one certificate family per edge of \(\mathcal Q_K(\mathcal E_0)\), and the conjecture says that this causal quotient exactly decides whether sparse bounded-cardinality exposure misspecification is testable or must be handled by sharp partial identification.

The proposal lives in the partial-identification and network-interference cluster.  It uses direct/indirect estimands from \citet{HudgensHalloran2008} and \citet{AronowSamii2017}, misspecified-exposure estimands from \citet{Savje2024}, exposure-map sensitivity from \citet{SchroderOprescuFeuerriegelKallus2026}, and random-set/fiber support ideas from \citet{BeresteanuMolchanovMolinari2011}.  It is not a causal-discovery proposal: networks and exposure maps are candidate structural explanations for the same observable law, and the theorem concerns the sharp boundary between testable separation and partial-ID collision.

The concrete downstream consumer is the exposure-mapping sensitivity workflow in \citet{SchroderOprescuFeuerriegelKallus2026}.  If the frontier resolves favorably, a sensitivity report should first compute or bound \(\Lambda_K(P;\mathcal E_0)\); positive values justify a specification check, while zero values direct the analyst to check pointwise membership in \(\operatorname{Col}_{K}^{X(P),\tau_{\min}}\) and then report either \(\mathsf C_K(P)\) or the nearest-colliding-fiber closure without claiming a specification test can choose the mapping.

The research-practice takeaway is that sparse finite-support exposure maps should not be tested by default: analysts should test only after an explicit collision-modulus calculation shows separation, and otherwise report partial-ID bounds over the sparse exposure class.

\section{Related work}
\citet{GaoHarshawSavjeWang2026} is the closest testing comparator.  They prove that tests of an exposure mapping against a larger exposure-map model have worst-case Type I and Type II errors summing to one, and they motivate the need for additional restrictions on alternatives.
\citet[Chapter~6]{LeCam1986} is the classical decision-theoretic comparator for Conjecture~\ref{conj:frontier}.  It supplies the total-variation lower-bound logic, while the present proposal's new object is the sparse exposure-collision quotient and its finite LP-dual certificate family.
\citet[Sections~2--3]{HoshinoYanagi2023} develops a randomization test for specification of the interference structure using hierarchical relationships among exposure specifications.  It is directly relevant as a specification-test comparator, but it conditions on null exposure specifications and constructed statistics rather than characterizing the null-vs-sparse-alternative total-variation collision frontier.
\citet[Sections~2--3]{BasseFellerToulis2019} formalizes conditioning mechanisms for valid and powerful randomization tests under interference.  The paper is a procedure comparator for conditional randomization testing, not a misspecified-exposure-map frontier; the present proposal asks when any test can separate the null exposure class from sparse \(K\)-support alternatives.
\citet[Sections~2--4]{PuelzBasseFellerToulis2022} represents interference null hypotheses as bipartite graphs and searches for bicliques that make conditional randomization tests sharp.  Their framework supplies finite-sample tests for chosen null hypotheses; it does not give a support-function or TV-distance certificate deciding whether an unknown sparse exposure map is observationally separated from the null.
\citet[Sections~2--4]{AtheyEcklesImbens2018} develops exact \(p\)-values for nonsharp null hypotheses under network interference by constructing artificial experiments that make the null sharp.  It is a direct randomization-inference comparator because it covers distance-based interference, network sparsification, and peer-effect heterogeneity hypotheses, but it does not solve the sparse \(K\)-support null-versus-alternative collision problem.
\citet{Savje2024} separates exposure mappings as estimand definitions from assumptions that the mapping fully captures interference.  That distinction is central here: \(\mathcal E_0\) is a null estimand-definition class, while \(\mathcal E_{1,K}\) contains sparse structural alternatives that may imply the same observed law.
\citet{WeinsteinNevo2026} shows that network misspecification and mapping misspecification are distinct, that correct networks need not be unique, and that multiple candidate networks can be used for robust estimation.  This proposal turns their equivalence-class phenomenon into a sharp observable-fiber object.
\citet{YuAiroldiBorgsChayes2022} studies total treatment-effect estimation when the network driving interference is unknown.  The present proposal targets direct and indirect exposure-specific components and asks whether the map can be distinguished at all, rather than estimating only a total effect.

\citet{SchroderOprescuFeuerriegelKallus2026} develops sharp partial-identification bounds for direct and spillover effects under misspecified exposure mappings in fixed canonical settings.  Their framework is the intended consumer when \(\Lambda_K=0\): one reports bounds instead of relying on a specification test.
\citet{HudgensHalloran2008} define direct, indirect, total, and overall effects under partial interference.  Their effect taxonomy fixes the coordinates of \(\theta_{\mathrm{DI}}\).
\citet{AronowSamii2017} formalize exposure mappings and design-based estimands under general interference.  Their known-map framework is the null corner from which this proposal builds collision alternatives.
\citet{HoshinoYanagi2024} studies noncompliance and unknown interference with exposure mappings of instruments, showing that meaningful causal parameters can persist under misspecification.

\citet{BeresteanuMolchanovMolinari2011} characterize sharp identification regions in incomplete econometric models through Aumann expectations of random sets.  The current proposal uses the same incomplete-model posture, but the novelty is a finite collision modulus for sparse network-compatible exposure classes.
\citet{Manski2013} studies partial identification of treatment response with social interactions under weak restrictions.  The present proposal is narrower in response restrictions but sharper about sparse-network exposure support.
\citet{SavjeAronowHudgens2021} show that average effects can be meaningful under unknown but limited interference while confidence statements may fail.  Their result motivates the fallback to partial identification when exposure-map tests collide.
\citet{Leung2022} provides sparse-network asymptotic theory under approximate neighborhood interference.  This proposal is finite-population at the identification frontier, with repeated-experiment testability used only as a consequence of observable-law separation.

Comparator roles are separated as follows.  \citet{LeCam1986} gives the generic TV testing frontier; \citet{AtheyEcklesImbens2018}, \citet{BasseFellerToulis2019}, \citet{PuelzBasseFellerToulis2022}, and \citet{HoshinoYanagi2023} give randomization-testing procedures for specified null structures; \citet{GaoHarshawSavjeWang2026} gives the broad impossibility and a positive network-linear-in-means special case; \citet{WeinsteinNevo2026} motivates equivalence classes of networks under misspecification; \citet{BeresteanuMolchanovMolinari2011} and \citet{SchroderOprescuFeuerriegelKallus2026} supply the random-set partial-ID reporting substrate.  Conjecture~\ref{conj:frontier} is positioned only against the missing causal frontier between the first three rows: a finite sparse \(K\)-support collision quotient whose LP-dual edge certificates decide when procedure-level randomization tests can be justified at all.

In-repository prior art does not duplicate the kernel.  The relevant \texttt{doc/API.md} section is ``ExactID / PartialID catalogues'', where PartialID entries are still mainly nonparametric Manski-style bound wrappers rather than network exposure-map testability frontiers.  The closest banked proposal is \texttt{pid\_network\_exposure/v1}, which studies shared-completion LP bounds and finite endpoint certificates for network ADEs; it does not define a null-vs-alternative collision modulus or a Gao-style testing dichotomy.  The adjacent accepted angles for \texttt{pid\_network\_random\_set/v1} treated random-set envelopes, nonrectangularity, and finite endpoint certificates; the current pivot is structurally different because its headline is a specification-testing frontier.

\section{Formal setup}
There are \(n<\infty\) units.  The observed finite-experiment law is
\[
P=P_{I,A,Y;\pi,\mathcal L,\mathcal C,\bar d,K,\mathcal E_0},
\]
where \(I\sim\mathrm{Unif}\{1,\ldots,n\}\), the randomized assignment law \(\pi\) is known, \(Y_I\in\{0,1\}\), \(\mathcal L\) is the observed undirected network, \(\mathcal C\) is a finite hidden-edge candidate set, \(\bar d_i\) is the hidden-degree cap for unit \(i\), \(K\ge2\) is the exposure-support bound, and \(\mathcal E_0\) is a finite null class of analyst-specified exposure systems.  Let \(\mathfrak G(\mathcal L,\mathcal C,\bar d)\) be the finite class of graphs containing \(\mathcal L\), using only hidden edges from \(\mathcal C\), and satisfying all degree caps.

A sparse \(K\)-support exposure system is \((G,e)\) with \(G\in\mathfrak G(\mathcal L,\mathcal C,\bar d)\) and maps \(e_i:\{0,1\}^{n-1}\to\{0,\ldots,K-1\}\) that depend only on treatments of \(i\)'s neighbors in \(G\) and have image size at most \(K\).  Exposure labels are fixed primitives of \((G,e)\).  If an analyst begins from an unlabelled exposure partition, its fiber is expanded over all admissible injections and permutations into \(\{0,\ldots,K-1\}\) before any \(B(G,e)\), \(M(G,e)\), or \(\Lambda_K\) object is formed.  The alternative class is
\[
\mathcal E_{1,K}=\{(G,e): (G,e)\text{ is sparse }K\text{-support and }(G,e)\notin\mathcal E_0\}.
\]
For a labelled exposure system, write \(\rho_{ik}(G,e)=\Pr_\pi(e_i(A_{-i})=k)\).  Bernoulli response probabilities are \(\mu_i(a,k)\in[0,1]\), and consistency means
\[
Y_I\mid I=i,A=\alpha,(G,e,\mu)\sim
\mathrm{Bernoulli}\{\mu_i(\alpha_i,e_i(\alpha_{-i}))\}.
\]
Because all unlabelled systems have already been expanded over label permutations, \(B(G,e)\) and \(M(G,e)\) below are fixed finite maps rather than maps chosen after observing the realized law \(P\).

For an exposure class \(\mathcal E\subseteq \mathcal E_0\cup\mathcal E_{1,K}\), define its observable-law fiber
\[
\mathfrak P(\mathcal E)=
\left\{
Q_{I,A,Y}: \exists (G,e)\in\mathcal E,\ \exists \mu(\cdot)\in[0,1]\text{ satisfying Bernoulli consistency and inducing }Q
\right\}.
\]
The direct/indirect vector \(\theta_{\mathrm{DI}}\in\mathbb R^{K+K(K-1)}\) stacks
\[
D_k=\frac{1}{N_k}\sum_{i:\rho_{ik}>0}\{\mu_i(1,k)-\mu_i(0,k)\},\qquad
I_{k\ell}=\frac{1}{2N_{k\ell}}\sum_{a\in\{0,1\}}\sum_{i:\rho_{ik}\rho_{i\ell}>0}\{\mu_i(a,\ell)-\mu_i(a,k)\},
\]
with inactive components set to zero.  The sharp random-set fallback is
\[
\mathsf C_K(P)=\overline{\operatorname{co}}\{\theta_{\mathrm{DI}}(G,e,\mu):(G,e,\mu)\text{ induces }P,\ (G,e)\in\mathcal E_0\cup\mathcal E_{1,K}\}.
\]

For each \((G,e)\), let \(B(G,e)\) be the finite exposure-incidence matrix whose rows are observed \((i,\alpha)\) cells and whose columns are fixed labels, with entry \(B_{(i,\alpha),k}(G,e)=\one\{e_i(\alpha_{-i})=k\}\).  Let \(M(G,e)\) be the finite affine map taking Bernoulli response probabilities \(\mu\) to the full observable law vector on \((I,A,Y)\):
\[
Q(i,\alpha,1)=n^{-1}\pi(\alpha)\mu_i(\alpha_i,e_i(\alpha_{-i})),\qquad
Q(i,\alpha,0)=n^{-1}\pi(\alpha)\{1-\mu_i(\alpha_i,e_i(\alpha_{-i}))\}.
\]
For a response-probability array \(\mu\), define the exposure-relevance contrast
\[
\Delta(G,e,\mu)=
\max_{i,a,k,\ell:\rho_{ik}\rho_{i\ell}>0}
\left|\mu_i(a,k)-\mu_i(a,\ell)\right|,
\]
with \(\Delta(G,e,\mu)=0\) if a unit has no two active labels.  For a fixed experiment \(X=(\pi,\mathcal L,\mathcal C,\bar d,K,\mathcal E_0)\), define
\[
\mathfrak P_{X}(G,e;\tau)=
\{Q_{I,A,Y}:Q\text{ is induced by }(G,e,\mu),\ Q_{I,A}= \text{Unif}(I)\pi(A),\
Y\in\{0,1\},\ 0\le\mu\le1,\ \Delta(G,e,\mu)\ge\tau\}.
\]
For a class \(\mathcal E\), write \(\mathfrak P_X(\mathcal E;\tau)=\bigcup_{(G,e)\in\mathcal E}\mathfrak P_X(G,e;\tau)\).  For two exposure classes \(\mathcal E,\mathcal E'\), define the collision set
\[
\operatorname{Col}(\mathcal E,\mathcal E')=
\{Q:Q\in\mathfrak P(\mathcal E)\cap\mathfrak P(\mathcal E')\}.
\]
For the fixed experiment \(X\) and relevance threshold \(\tau\), define the pointwise sparse-relevant collision set
\[
\operatorname{Col}_{K}^{X,\tau}(\mathcal E_0,\mathcal E_{1,K})=
\mathfrak P_X(\mathcal E_0;0)\cap \mathfrak P_X(\mathcal E_{1,K};\tau).
\]
This set records realized observable laws that are simultaneously generated by a null exposure system and by an exposure-relevant sparse \(K\)-support alternative; a zero model-class distance \(\Lambda_K=0\) does not by itself assert that the observed \(P\) lies in this pointwise collision set.
The \(K\)-sparse collision quotient \(\mathcal Q_K(\mathcal E_0)\) is the finite bipartite graph with left nodes \((G,e)\in\mathcal E_0\), right nodes \((G',e')\in\mathcal E_{1,K}\), and an edge when the two induced Bernoulli-law images \(M(G,e)[0,1]^m\) and \(M(G',e')[0,1]^m\) intersect.

The focal object is the independently defined collision modulus
\[
\Lambda_K(P;\mathcal E_0)=
\min_{(G,e)\in\mathcal E_0,\ (G',e')\in\mathcal E_{1,K}}
\operatorname{dist}_{\mathrm{TV}}\!\left(
\mathfrak P_{X(P)}(G,e;0),\mathfrak P_{X(P)}(G',e';\tau_{\min})
\right),
\]
where \(X(P)=(\pi,\mathcal L,\mathcal C,\bar d,K,\mathcal E_0)\) is the finite experiment carried by \(P\).
Thus \(\mathfrak P_X(G,e;0)\) is the full Bernoulli observable-law image for the fixed experiment, while \(\mathfrak P_X(G',e';\tau_{\min})\) is the exposure-relevant alternative image.  The definition is a model-class distance for the finite experiment, not a moment-restricted slice matching only the observed conditional means of \(P\).  Empty images are allowed; \(\operatorname{dist}_{\mathrm{TV}}(\varnothing,B)=\operatorname{dist}_{\mathrm{TV}}(A,\varnothing)=+\infty\), and an all-empty alternative class makes the positive branch vacuous rather than testable.  Equivalently for finite support, \(\Lambda_K\) is the optimum of a finite linear program minimizing total variation distance between two induced Bernoulli laws on \((I,A,Y)\), subject to the two exposure-incidence systems and the primitive contrast constraint.  It is not defined as a test error rate or as the smallest value for which a test works.

For a margin \(0<\varepsilon\le \lambda_{\min}(P)\), where \(\lambda_{\min}(P)\) is the smallest positive singular value among the nonzero exposure-incidence difference matrices \(B(G,e)-B(G',e')\) appearing in \(\mathcal Q_K(\mathcal E_0)\), define the separated alternative class
\[
\mathcal E_{1,K}(\varepsilon)=
\{(G',e')\in\mathcal E_{1,K}:\operatorname{dist}_{\mathrm{TV}}(\mathfrak P_{X(P)}(\mathcal E_0;0),\mathfrak P_{X(P)}(G',e';\tau_{\min}))\ge\varepsilon\}.
\]
The bound by \(\lambda_{\min}(P)\) fixes the free-margin scale in all testability statements.

\begin{quote}
\small
Locked parameters, reproduced: qid \(=\texttt{pid\_network\_random\_set}\), specialization \(=\texttt{v1}\), observable distribution \(P=P_{I,A,Y;\pi,\mathcal L,\mathcal C,\bar d,K,\mathcal E_0}\), parameter \(\theta=\theta_{\mathrm{DI}}\), identifying restrictions \(\mathcal R_{\mathrm{sparse}\ K\mathrm{-support,test}}\), and bounding functional \(\Lambda_K(P;\mathcal E_0)\), the finite collision modulus between null exposure-map fibers and sparse \(K\)-support alternative fibers.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite randomized network experiment]\label{ass:finite}
The finite population size \(n\), randomized design \(\pi\), observed network \(\mathcal L\), candidate hidden-edge set \(\mathcal C\), degree caps \(\bar d\), support bound \(K\), and null class \(\mathcal E_0\) are fixed and known.  The observed outcome satisfies \(Y_I\in\{0,1\}\).
\end{assumption}

\begin{assumption}[Sparse \(K\)-support alternatives]\label{ass:sparse-k}
Every alternative exposure system belongs to \(\mathcal E_{1,K}\): it is generated by a graph in \(\mathfrak G(\mathcal L,\mathcal C,\bar d)\), each unit's exposure depends only on its neighbors in that graph, and each unit has at most \(K\) active exposure labels under \(\pi\).
\end{assumption}

\begin{assumption}[Consistency and exposure sufficiency]\label{ass:consistency}
For every exposure system under consideration, there are Bernoulli response probabilities \(\mu_i(a,k)\in[0,1]\) in the fixed label coordinates of that system, and \(Y_I\mid I=i,A=\alpha,(G,e,\mu)\) is Bernoulli with success probability \(\mu_i(\alpha_i,e_i(\alpha_{-i}))\).
\end{assumption}

\begin{assumption}[Fixed labels and local positivity]\label{ass:labels}
Exposure labels are fixed as part of each candidate exposure system, and any unlabelled exposure partition is represented by the finite union over admissible label permutations described in Section~6.  Any direct or indirect component reported in \(\theta_{\mathrm{DI}}\) has positive assignment probability for the relevant own-treatment and exposure-label events; inactive components are set to zero.
\end{assumption}

\begin{assumption}[Finite observable-law fibers]\label{ass:fibers}
For each candidate exposure system \((G,e)\), the induced observable-law fiber \(\mathfrak P_X(G,e;\tau)\) is represented by the finite Bernoulli-law affine image \(M(G,e)[0,1]^m\), intersected with the linear inequalities defining \(\Delta(G,e,\mu)\ge\tau\), over the assignment support of \(\pi\).  The collision quotient \(\mathcal Q_K(\mathcal E_0)\) is finite.
\end{assumption}

\begin{assumption}[Separation scale]\label{ass:scale}
All positive-margin testability claims use a margin \(0<\varepsilon\le\lambda_{\min}(P)\), where \(\lambda_{\min}(P)\) is the smallest positive singular value of the nonzero exposure-incidence difference matrices in \(\mathcal Q_K(\mathcal E_0)\).  If no such positive singular value exists, positive-margin claims are void and only the collision case is asserted.
\end{assumption}

\begin{assumption}[Primitive exposure relevance]\label{ass:relevance}
The positive branch compares the null class only to alternative response surfaces with \(\Delta(G,e,\mu)\ge\tau_{\min}\), where \(0<\tau_{\min}\le\min\{1/16,\lambda_{\min}(P)/4\}\).  Alternative exposure systems with \(\Delta(G,e,\mu)=0\) are classified as null-equivalent collisions and belong to the zero-modulus fallback, not to the separated testing alternative.
\end{assumption}

\begin{assumption}[Repeated-experiment consequence]\label{ass:repeated}
When a statistical testing consequence is stated, the finite experiment is independently repeated \(m\to\infty\) times with the same \((\pi,\mathcal L,\mathcal C,\bar d,K,\mathcal E_0)\), and the test observes the empirical law of \((I,A,Y)\).  The identification frontier itself is finite-population and does not depend on this asymptotic device.
\end{assumption}

\begin{assumption}[Noncorner witness class]\label{ass:noncorner}
For generic witness claims, all assignment probabilities, active exposure propensities, and Bernoulli response probabilities used by the finite fiber program are bounded away from \(0\) and \(1\) by at least \(1/12\).  Open neighborhoods are measured in the finite-dimensional Euclidean topology on these probabilities.
\end{assumption}

\section{Main results}
\begin{lemma}[Known Lemma: fiber-overlap impossibility]\label{lem:overlap-impossibility}
Under Assumptions~\ref{ass:finite}--\ref{ass:fibers}, if
\[
\operatorname{Col}(\mathcal E_0,\mathcal E_{1,K})\ne\emptyset,
\]
then no test based only on the observable law of \((I,A,Y)\) can uniformly distinguish \(\mathcal E_0\) from \(\mathcal E_{1,K}\) over the colliding fiber.  In particular, for any test \(\varphi\), there exist \(Q_0\in\mathfrak P(\mathcal E_0)\) and \(Q_1\in\mathfrak P(\mathcal E_{1,K})\) with \(Q_0=Q_1\) such that the Type I error at \(Q_0\) plus the Type II error at \(Q_1\) is at least one.
\end{lemma}
\paragraph{Why this is new and worth studying.}
(a) This is not claimed as novel; it is the standard indistinguishable-law lemma used by \citet[Chapter~6]{LeCam1986} and \citet{GaoHarshawSavjeWang2026}.  Its role here is only to state the known zero-modulus branch that Conjecture~\ref{conj:frontier} must reduce to.  (b) The consumer is \citet{SchroderOprescuFeuerriegelKallus2026}: when a reported exposure-map sensitivity analysis sits on a colliding fiber, the analyst should report \(\mathsf C_K(P)\) rather than a specification-test verdict.

\begin{conjecture}[Conjecture 1: sparse exposure-collision frontier]\label{conj:frontier}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:repeated}, the collision modulus \(\Lambda_K(P;\mathcal E_0)\) is an exact frontier for sparse \(K\)-support exposure-map testability:
\[
\Lambda_K(P;\mathcal E_0)>0
\quad\Longleftrightarrow\quad
\text{there exists a finite linear-separation test with asymptotic size }0
\text{ and power }1
\]
against every alternative in \(\mathcal E_{1,K}(\varepsilon)\), for every \(0<\varepsilon\le\min\{\Lambda_K(P;\mathcal E_0),\lambda_{\min}(P)\}\).  If \(\Lambda_K(P;\mathcal E_0)=0\), then for every sequence of tests there are null and sparse \(K\)-support alternative laws with total variation distance tending to zero and with Type I plus Type II errors tending to at least one.  The finite test in the positive branch rejects when the empirical total-variation distance from the finite null class \(\mathfrak P_X(\mathcal E_0;0)\) exceeds \(\varepsilon/2\); equivalently, its critical statistic is the minimum over the finite family of pairwise LP-dual separating certificates indexed by edges of the sparse exposure-collision quotient \(\mathcal Q_K(\mathcal E_0)\).  The focal mathematical object is the collision quotient \(\mathcal Q_K(\mathcal E_0)\) together with its modulus \(\Lambda_K\), a causal compression of the classical \citet{LeCam1986} TV frontier to sparse exposure-map equivalence classes, not a particular estimator.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Chapter~6]{LeCam1986} already implies that positive TV distance is the right generic testing scale, and \citet[abstract and main theorem]{GaoHarshawSavjeWang2026} gives broad impossibility for larger exposure-map alternatives.  The proposed epsilon-gap is therefore not generic finite-model separation; it is the causal quotient that reduces exponentially many sparse network/exposure explanations to the finite edge set of \(\mathcal Q_K(\mathcal E_0)\) and returns an LP-dual certificate family for the null-vs-\(K\)-support exposure frontier.  \citet[Sections~2--3]{HoshinoYanagi2023}, \citet[Sections~2--3]{BasseFellerToulis2019}, \citet[Sections~2--4]{PuelzBasseFellerToulis2022}, and \citet[Sections~2--4]{AtheyEcklesImbens2018} give randomization/specification-test procedures for selected interference or exposure structures, while \citet[Sections~4--5]{WeinsteinNevo2026} shows that candidate networks may form equivalence classes and proposes robust estimation when one candidate is correct.  None of these papers identifies the sparse \(K\)-support collision quotient as the exact support-function object deciding when the Gao/Le Cam impossibility remains active.  (b) Resolving the conjecture would directly answer the open problem in the Stage -1.1 gaps payload about whether bounded-cardinality sparse exposure support makes misspecification statistically testable despite broad impossibility results.

\begin{conjecture}[Conjecture 2: noncorner exposure-relevant sparse-support escape from broad impossibility]\label{conj:noncorner}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:noncorner}, there exists an open set of \(K=2\), \(n=5\) sparse-network experiments for which \(\mathcal E_0\) is the no-interference exposure class, \(\mathcal E_{1,2}\) is the class of threshold neighborhood exposures on graphs in \(\mathfrak G(\mathcal L,\mathcal C,\bar d)\), and
\[
\Lambda_2(P;\mathcal E_0)\ge \frac{1}{24}.
\]
For every \(P\) in this open set, alternatives satisfy the primitive relevance condition \(\Delta(G,e,\mu)\ge\tau_{\min}\), the distance-to-null statistic is certified by a finite LP-dual contrast of two assignment cells that differ only in neighbors of the sampled unit, and the separator remains valid after all Bernoulli response probabilities are perturbed by at most \(1/96\).  Thus sparse \(K\)-support restrictions can produce a genuine positive branch of Conjecture~\ref{conj:frontier}, even though null-equivalent threshold maps with exposure-invariant response surfaces remain subject to the impossibility result of \citet{GaoHarshawSavjeWang2026}.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Section~4, Proposition~4.1 and Theorem~4.2]{GaoHarshawSavjeWang2026} include a positive special case for no-interference versus a network-linear-in-means model, but this conjecture is different: it asks for a finite partial-ID fiber separator over threshold exposure maps with unknown sparse network support and bounded label cardinality.  The \(1/24\) lower bound is tied to the structural scale in Assumption~\ref{ass:scale}, so it is not a free epsilon.  (b) The consumer is the testing workflow discussed in \citet[Discussion, Section~8]{WeinsteinNevo2026}: rather than enumerating \(O(2^{n^2})\) augmented networks or relying on heuristic aggregation, the analyst would look for a finite collision separator.

\begin{conjecture}[Conjecture 3: collision-zero implies sharp convex-hull reporting]\label{conj:sharp-fallback}
(NOT YET PROVED.)  Under Assumptions~\ref{ass:finite}--\ref{ass:relevance}, if the realized law satisfies
\[
P\in\operatorname{Col}_{K}^{X(P),\tau_{\min}}(\mathcal E_0,\mathcal E_{1,K}),
\]
then \(\mathsf C_K(P)\) is the smallest closed convex direct/indirect report invariant to all observationally colliding null and sparse \(K\)-support alternative exposure systems at \(P\).  More precisely, any convex set \(R(P)\subsetneq \mathsf C_K(P)\) that excludes a point generated by a colliding alternative fiber fails invariance: there exist \(Q_0\in\mathfrak P_{X(P)}(\mathcal E_0;0)\) and \(Q_1\in\mathfrak P_{X(P)}(\mathcal E_{1,K};\tau_{\min})\) with \(Q_0=Q_1=P\) but \(R(Q_0)\) and \(R(Q_1)\) cannot both contain the induced \(\theta_{\mathrm{DI}}\) vectors.  Conversely, every closed convex report containing \(\mathsf C_K(P)\) is invariant but weakly less informative.  The report \(\mathsf C_K(P)\), by construction, contains every colliding direct/indirect vector and is the sharp convex hull of those vectors.  If \(\Lambda_K(P;\mathcal E_0)=0\) but \(P\notin\operatorname{Col}_{K}^{X(P),\tau_{\min}}(\mathcal E_0,\mathcal E_{1,K})\), the conjectured fallback is instead the nearest-colliding-fiber report obtained by replacing \(P\) with the set of TV-limit points in \(\overline{\operatorname{Col}_{K}^{X(P),\tau_{\min}}(\mathcal E_0,\mathcal E_{1,K})}\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Theorems~2.1--2.2]{BeresteanuMolchanovMolinari2011} gives random-set sharp regions for incomplete models, and \citet{SchroderOprescuFeuerriegelKallus2026} gives fixed-canonical exposure bounds; neither states a testing-to-reporting frontier saying that a realized sparse exposure collision forces the sharp sparse random-set region as the minimal informative invariant report.  The pointwise condition \(P\in\operatorname{Col}_{K}^{X(P),\tau_{\min}}\) is the gap relative to Conjecture~\ref{conj:frontier}'s model-class distance: \(\Lambda_K=0\) alone is not enough for this report.  (b) Resolving this conjecture would give \citet{Savje2024}'s definition-vs-assumption distinction an operational rule: when the mapping assumption is not testably separable at the observed law, report the exposure-effect set defined by all sparse compatible mappings.

\section{Sanity-check corollaries}
\begin{corollary}[Broad-alternative collapse to Gao-Harshaw-Savje-Wang]\label{cor:gao}
If Assumptions~\ref{ass:finite}--\ref{ass:fibers} hold but \(\mathcal E_{1,K}\) is enlarged to the unrestricted larger exposure-map class used by \citet{GaoHarshawSavjeWang2026} and the primitive relevance restriction in Assumption~\ref{ass:relevance} is removed, then the collision quotient contains zero-distance pairs and the unrestricted collision modulus is zero.
\end{corollary}
Under the enlargement, the alternative class can reproduce the null observable law by choosing an exposure map and Bernoulli response-probability surface that collapses to the null induced law.  This is exactly the fiber-overlap condition in Lemma~\ref{lem:overlap-impossibility}, so the proposed frontier reduces to the published impossibility corner once exposure relevance is not imposed.

\begin{corollary}[Known full-rank exposure-map corner]\label{cor:known-map}
If the candidate class contains a single known exposure system \((G,e)\), all active exposure cells have positive design probability, and the exposure-incidence map has full column rank on the Bernoulli response-probability coordinates used by \(P\), then \(\mathcal Q_K(\mathcal E_0)\) has no right node and \(\mathsf C_K(P)\) reduces to the fixed-map direct/indirect finite LP region.
\end{corollary}
The reduction is algebraic: with no sparse alternative fiber, the collision modulus test is vacuous, and observed-law matching under the known exposure system is a finite set of linear equations in Bernoulli response probabilities as in the \citet{AronowSamii2017} known-map corner.

\begin{example}[Concrete noncorner witness target]\label{ex:witness}
Let \(n=5\), let \(\pi\) assign treatments independently with probability \(1/2\), let the observed network be empty, let \(\mathcal C=\{\{1,2\},\{2,3\},\{3,4\},\{4,5\}\}\), and let \(\bar d=(1,2,2,2,1)\).  The null class \(\mathcal E_0\) is no-interference, so all units have a single exposure label.  The alternative class \(\mathcal E_{1,2}\) contains threshold exposure maps \(e_i(A_{-i})=\one\{\text{at least one path-neighbor of }i\text{ is treated}\}\) for graphs supported on \(\mathcal C\).  For \(h=\max\{z_L,z_R\}\), consider Bernoulli outcomes with threshold-compatible conditional means
\[
\mu_i(a,h)=0.36+0.10a+0.11h+0.04ah+\eta_i,
\]
where missing neighbors have \(z=0\), \(h=0\) iff no path-neighbor is treated, and \((\eta_1,\eta_2,\eta_3,\eta_4,\eta_5)=(0.00,0.02,0.04,0.03,0.01)\).  Every assignment cell has probability \(1/32\), every displayed conditional mean lies between \(0.36\) and \(0.65\), and the primitive exposure-relevance contrast is at least \(0.11\) on active neighbor-label cells.  The response surface is exposure-sufficient for the binary threshold label: assignments with \((z_L,z_R)=(1,0)\) and \((0,1)\) have the same \(h=1\) mean for a fixed unit and own treatment.  The proposed separator contrasts assignment cells with \(h=0\) and \(h=1\) while holding own treatment fixed.  Conjecture~\ref{conj:noncorner} predicts that this class contains an open neighborhood with \(\Lambda_2(P;\mathcal E_0)\ge1/24\).
\end{example}
This is not a Gaussian or collapsed-treatment corner.  The explicit verification route is finite enumeration of the \(2^4\) candidate path subgraphs and the threshold label maps, followed by solving the pairwise total-variation LPs that define \(\Lambda_2\).

\section{Proof-sketch route}
Lemma~\ref{lem:overlap-impossibility} is the standard indistinguishable-distributions argument: if the null and alternative fibers share an observable law, any rejection probability at that law is simultaneously the Type I rejection probability and one minus the Type II acceptance probability.  For Conjecture~\ref{conj:frontier}, the finite-support proof route is to express every candidate exposure system as a Bernoulli-law affine image \(M(G,e)[0,1]^m\), impose the primitive exposure-relevance inequality \(\Delta(G,e,\mu)\ge\tau_{\min}\) on alternatives, then compute pairwise total-variation distances between null and sparse alternative law images by linear programming.  The positive branch should use the distance-to-null-class statistic \(T_m=\operatorname{dist}_{\mathrm{TV}}(\widehat Q_m,\mathfrak P_X(\mathcal E_0;0))\), where \(\widehat Q_m\) is the empirical law under the repeated-experiment device; because \(\mathfrak P_X(\mathcal E_0;0)\) is a finite union of polytopes, \(T_m\) is computed by a finite family of LPs or, equivalently, finite pairwise dual certificates indexed by \(\mathcal Q_K(\mathcal E_0)\).  Uniform consistency over \(\mathcal E_{1,K}(\varepsilon)\) should follow by rejecting when \(T_m>\varepsilon/2\), applying a finite-dimensional law of large numbers, and using the definition of \(\mathcal E_{1,K}(\varepsilon)\) to separate every alternative in the finite union, not only the closest pair attaining \(\Lambda_K\).  The zero branch should follow by constructing a sequence of null/alternative fiber pairs whose total variation distance tends to zero and applying the same Le Cam lower bound as in Lemma~\ref{lem:overlap-impossibility}.  For Conjecture~\ref{conj:noncorner}, the calculation is finite: enumerate the path-subgraph threshold maps, build the no-interference and threshold-exposure incidence matrices over the fixed label-permutation-expanded systems, enforce the \(0.11\)-or-larger threshold exposure contrast in Example~\ref{ex:witness}, and verify the distance-to-null LP has slack at least \(1/24\) after perturbations of size \(1/96\).  Conjecture~\ref{conj:sharp-fallback} then reduces to a support-function separation argument for the closed convex hull of all direct/indirect vectors generated by colliding fibers at observed laws \(P\in\operatorname{Col}_{K}^{X(P),\tau_{\min}}\); if \(\Lambda_K=0\) only through a limiting sequence, the proof route switches to the closure of that pointwise collision set.

\section{Honest scope flags}
Lemma~\ref{lem:overlap-impossibility} is routine and is not the flagship claim.  Conjectures~\ref{conj:frontier}, \ref{conj:noncorner}, and \ref{conj:sharp-fallback} are not yet proved.  The proposal is identification-first: the repeated-experiment testing consequence is included only to interpret positive fiber separation.  The concrete \(1/24\) witness margin in Example~\ref{ex:witness} is a conjectured finite LP slack, not a verified computation.  The collision modulus is a model-class distance for finite candidate graph and exposure classes with Bernoulli observable laws and a primitive exposure-relevance restriction; it is not a moment-matching slice through the realized conditional means of \(P\).  Null-equivalent threshold maps with exposure-invariant response surfaces are intentionally assigned to the zero-modulus fallback.  Conjecture~\ref{conj:sharp-fallback} now requires the realized law \(P\) to lie in the pointwise sparse-relevant collision set; if only the model classes have zero distance, the draft claims only the nearest-colliding-fiber closure rule.  Continuous network uncertainty, growing \(K\), non-Bernoulli outcomes, and asymptotic sparse graph limits are outside scope.  The sharp fallback \(\mathsf C_K(P)\) is convexified for linear direct/indirect reporting; the raw union over deterministic exposure systems may be nonconvex and is not characterized here.  This pivot deliberately leaves the already accepted random-set envelope, nonrectangularity, and endpoint-certificate angles aside.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial pivot draft for angle 3, centered on a sparse exposure-collision modulus \(\Lambda_K(P;\mathcal E_0)\) that separates testable bounded-cardinality exposure alternatives from Gao-style indistinguishability; prior verdict: none.
\item v2 (revise) -- downgraded the indistinguishable-law statement to known supporting machinery, made \(\mathfrak P_{X(P)}(G,e;\tau)\) a finite model-class image with empty-slice conventions, and added primitive exposure relevance to exclude null-equivalent threshold alternatives from the noncorner witness; prior verdict: REVISE.
\item v3 (revise) -- added direct randomization/specification-test comparators, anchored Gao-Harshaw-Savje-Wang's positive special case by section/proposition/theorem, fixed label-permutation algebra, and replaced the single-dual-witness route with a distance-to-null finite-union separator; prior verdict: REVISE.
\item v4 (revise) -- fixed the observable-law convention to Bernoulli full-law TV fibers, corrected randomization-test comparator descriptions and anchors, added Athey-Eckles-Imbens as a direct comparator, and rewrote \(\mathsf C_K(P)\) as the smallest sharp convex invariant report; prior verdict: REVISE.
\item v5 (revise) -- positioned Conjecture~\ref{conj:frontier} against the classical Le Cam TV frontier, replaced the noncorner witness with a binary-threshold-sufficient response surface, and restricted Conjecture~\ref{conj:sharp-fallback} to pointwise sparse-relevant collisions at the realized law; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Aronow and Samii(2017)]{AronowSamii2017}
Aronow, P. M. and Samii, C. (2017).
Estimating average causal effects under general interference, with application to a social network experiment.
\emph{Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem[Athey, Eckles, and Imbens(2018)]{AtheyEcklesImbens2018}
Athey, S., Eckles, D., and Imbens, G. W. (2018).
Exact \(p\)-values for network interference.
\emph{Journal of the American Statistical Association} 113(521), 230--240.
doi:10.1080/01621459.2016.1241178.

\bibitem[Beresteanu, Molchanov, and Molinari(2011)]{BeresteanuMolchanovMolinari2011}
Beresteanu, A., Molchanov, I., and Molinari, F. (2011).
Sharp identification regions in models with convex moment predictions.
\emph{Econometrica} 79(6), 1785--1821.
doi:10.3982/ECTA8680.

\bibitem[Basse, Feller, and Toulis(2019)]{BasseFellerToulis2019}
Basse, G. W., Feller, A., and Toulis, P. (2019).
Randomization tests of causal effects under interference.
\emph{Biometrika} 106(2), 487--494.
doi:10.1093/biomet/asy072.

\bibitem[Gao, Harshaw, Savje, and Wang(2026)]{GaoHarshawSavjeWang2026}
Gao, C., Harshaw, C., Savje, F., and Wang, Y. (2026).
On the impossibility of specification testing of interference models based on exposure mappings.
\emph{arXiv preprint}.
doi:10.48550/arXiv.2605.09726.

\bibitem[Hoshino and Yanagi(2023)]{HoshinoYanagi2023}
Hoshino, T. and Yanagi, T. (2023).
Randomization test for the specification of interference structure.
\emph{arXiv preprint}.
arXiv:2301.05580.

\bibitem[Hoshino and Yanagi(2024)]{HoshinoYanagi2024}
Hoshino, T. and Yanagi, T. (2024).
Causal inference with noncompliance and unknown interference.
\emph{Journal of the American Statistical Association}.
doi:10.1080/01621459.2023.2284413.

\bibitem[Hudgens and Halloran(2008)]{HudgensHalloran2008}
Hudgens, M. G. and Halloran, M. E. (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.
doi:10.1198/016214508000000292.

\bibitem[Leung(2022)]{Leung2022}
Leung, M. P. (2022).
Causal inference under approximate neighborhood interference.
\emph{Econometrica} 90(1), 267--293.
doi:10.3982/ECTA17841.

\bibitem[Le Cam(1986)]{LeCam1986}
Le Cam, L. (1986).
\emph{Asymptotic Methods in Statistical Decision Theory}.
Springer.

\bibitem[Manski(2013)]{Manski2013}
Manski, C. F. (2013).
Identification of treatment response with social interactions.
\emph{The Econometrics Journal} 16(1), S1--S23.
doi:10.1111/j.1368-423X.2012.00368.x.

\bibitem[Puelz, Basse, Feller, and Toulis(2022)]{PuelzBasseFellerToulis2022}
Puelz, D., Basse, G., Feller, A., and Toulis, P. (2022).
A graph-theoretic approach to randomization tests of causal effects under general interference.
\emph{Journal of the Royal Statistical Society: Series B} 84(1), 174--204.
doi:10.1111/rssb.12478.

\bibitem[Savje(2024)]{Savje2024}
Savje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions and assumptions.
\emph{Biometrika} 111(1), 1--15.
doi:10.1093/biomet/asad019.

\bibitem[Savje, Aronow, and Hudgens(2021)]{SavjeAronowHudgens2021}
Savje, F., Aronow, P. M., and Hudgens, M. G. (2021).
Average treatment effects in the presence of unknown interference.
\emph{Annals of Statistics} 49(2), 673--701.
doi:10.1214/20-AOS1973.

\bibitem[Schroder, Oprescu, Feuerriegel, and Kallus(2026)]{SchroderOprescuFeuerriegelKallus2026}
Schroder, M., Oprescu, M., Feuerriegel, S., and Kallus, N. (2026).
Causal inference on networks under misspecified exposure mappings: A partial identification framework.
\emph{arXiv preprint}.
doi:10.48550/arXiv.2602.03459.

\bibitem[Weinstein and Nevo(2026)]{WeinsteinNevo2026}
Weinstein, B. and Nevo, D. (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.
doi:10.1093/biomtc/ujag023.

\bibitem[Yu, Airoldi, Borgs, and Chayes(2022)]{YuAiroldiBorgsChayes2022}
Yu, C. L., Airoldi, E. M., Borgs, C., and Chayes, J. T. (2022).
Estimating total treatment effect in randomized experiments with unknown network structure.
\emph{Proceedings of the National Academy of Sciences} 119(44), e2208975119.
doi:10.1073/pnas.2208975119.
\end{thebibliography}

\end{document}
