% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_network\_random\_set, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_network\_random\_set} / \texttt{v1}%
  \\ \large\textit{Policy-decomposition compatibility sets for latent finite-support network exposures}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Partial-identification anchor.  The convention is
\[
(\texttt{qid},\texttt{specialization},P,\theta,\mathcal R_K,h_K)
=
(\texttt{pid\_network\_random\_set},\texttt{v1},P,\theta^{DI},
\mathcal R_K(P;t),h_K(\cdot;P,t)).
\]
Here \(P\) is the coarsened observable law used for identification in a finite
network experiment: \(R\in\{0,1\}\) indexes two Bernoulli assignment policies
\(p_0<p_1\), \(A_i\in\{0,1\}\) is the unit's own treatment, and
\(\mu_{iar}(P)=\E_P[Y_i\mid A_i=a,R=r]\) is observed for
\((i,a,r)\in\{1,\ldots,n\}\times\{0,1\}^2\).  The full counterfactual response
to every neighbor assignment is not observed.
The unobserved parameter is the direct--indirect decomposition
\(\theta^{DI}=(\theta_D,\theta_I)\in\mathbb{R}^2\) of a fixed total policy
contrast \(t\).  The identifying restrictions are: finite population
consistency, randomized assignment with known \(p_0,p_1\), bounded outcomes,
latent undirected sparse networks \(G\in\mathcal G_d\) with maximum degree at
most \(d\), and deterministic unit exposure maps \(m_i(G,\cdot)\) whose image
has cardinality at most \(K\).  The true identified set \(\Theta_K(P;t)\) is the
set of all direct--indirect pairs generated by complete data-generating laws
satisfying these restrictions and producing the coarsened observable law \(P\).
The computable compatibility set \(\mathcal R_K(P;t)\) is the finite selection
set defined below from the marginal matching equations.  The bounding functional
is the support function
\[
h_K(v;P,t)=\sup_{\theta\in\mathcal R_K(P;t)} v^\transpose\theta,\qquad
v\in\mathbb{S}^1,
\]
which is an outer support value for \(\Theta_K(P;t)\) unless the sharpness
conjecture holds.

\begin{abstract}
Network-interference papers now distinguish direct, indirect, total, and
policy effects, but existing decompositions assume either a known exposure
mapping or a fixed misspecification class.  This proposal asks for the sharp
partial-identification region for the direct--indirect pair when the exposure
labels themselves are latent finite-support objects and only the total policy
contrast is fixed.  The flagship kernel is the conjecture that the
\emph{policy-decomposition compatibility set} \(\mathcal R_K(P;t)\) has a
random-set support-function representation over sparse \(K\)-valued exposure
maps, and that this representation is sharp rather than merely an outer bound.
The proposal also conjectures a concrete five-unit witness in which the
componentwise direct and indirect intervals both contain the truth but no
single latent exposure map attains their endpoint pair.  If resolved, the
result would turn the Hu--Li--Wager total-effect decomposition into a robust
partial-identification object for network experiments with unknown exposure
support.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Applied network experiments often report a total policy effect even when the
scientific question asks whether the effect travels through a treated unit
itself or through its neighbors.  That decomposition is fragile when the
researcher does not know the exposure mapping: a latent label can be renamed,
merged, or reassigned across sparse candidate networks while leaving the same
observable assignment--outcome law.  The methodological stake is whether a
total policy effect can be decomposed into direct and indirect components
without pretending that a single known exposure summary is correct.

\paragraph{The main finding (proposed).}
Theorem~\ref{thm:finite-random-set-outer} records the finite random-set outer
representation that follows by enumerating sparse \(K\)-support completions.
Conjecture~\ref{conj:pdc-sharp-support} is the headline claim: after imposing
the total-policy identity \(\theta_D+\theta_I=t\), the same object is the sharp
identified set and its support function is exactly the value of a finite
selection program over latent exposure maps.  Conjecture~\ref{conj:five-unit-witness}
adds a non-corner witness showing that componentwise sharp direct and indirect
intervals need not form a sharp rectangle once both components must be
generated by one latent map.

\paragraph{What is new.}
The novelty kernel is the named object
\(\mathcal R_K(P;t)\), the policy-decomposition compatibility set.  Hu, Li, and
Wager~\citep{HuLiWager2022} prove that their average direct and indirect
effects add to an infinitesimal Bernoulli policy effect when the relevant
potential-outcome contrasts are well defined.  Schroder, Oprescu, Feuerriegel,
and Kallus~\citep{SchroderOprescuFeuerriegelKallus2026} give sharp bounds for
direct and spillover effects under misspecified but fixed canonical exposure
settings.  This proposal targets the gap between them: the direct and indirect
objects are bounded jointly, conditional on a total policy contrast, while the
exposure labels and sparse network support are latent rather than fixed.

\paragraph{How it positions in the literature.}
The proposal is a partial-identification question in the network-interference
subcluster.  It uses the direct/indirect/total taxonomy of
\citet{HudgensHalloran2008}, the known-exposure randomization framework of
\citet{AronowSamii2017}, the unknown-interference motivation of
\citet{HoshinoYanagi2024} and \citet{Savje2024}, and the random-set sharpness
machinery of \citet{BeresteanuMolchanovMolinari2011}.  It is not an SCM or
do-calculus proposal; the theorem substrate is the partial-ID identified-set
geometry induced by latent exposure labels.

\paragraph{Implications for the community.}
The concrete downstream consumer is \citet{HuLiWager2022}: their policy-effect
decomposition would gain a robustness diagnostic reporting all direct--indirect
pairs compatible with an identified total effect under bounded exposure-support
uncertainty.  A reader who accepts the conclusion should report
\(\mathcal R_K(P;t)\), or at least its directional support values, before
interpreting a network total policy effect as mainly direct or mainly indirect.

\section{Related work}
\citet{HudgensHalloran2008} formalize direct, indirect, total, and overall
effects under partial interference; their definitions motivate the
decomposition target but rely on group-level regimes rather than latent
finite-support exposure maps.  \citet{HuLiWager2022} define average direct and
indirect effects under interference and prove a decomposition theorem linking
their sum to an infinitesimal Bernoulli policy effect; this is the closest
published comparator for the total-policy identity.  \citet{AronowSamii2017}
provide the design/exposure-map/estimand framework under arbitrary but known
interference, which supplies the known-map corner case of this proposal.
\citet{Savje2024} argues that exposure mappings can define effects without
being assumed to fully capture interference, motivating a misspecified-exposure
analysis but not giving a sharp direct--indirect decomposition set.
\citet{HoshinoYanagi2024} treats noncompliance with unknown interference and
explicitly considers exposure-mapping misspecification, but their target is
identification and estimation under instrument exposure mappings rather than a
random-set region over latent treatment exposures.  \citet{SchroderOprescuFeuerriegelKallus2026}
derive sharp direct and spillover bounds under exposure-mapping misspecification
for fixed canonical exposure settings; the proposed \(\mathcal R_K(P;t)\)
differs by making the exposure labels latent \(K\)-support objects and requiring
joint compatibility with a total policy contrast.  \citet{BeresteanuMolchanovMolinari2011}
characterize sharp regions through Aumann expectations of random sets; their
machinery is the methodological template, while the new question is the
network-exposure selection set and decomposition constraint.  \citet{Manski2013}
studies partial identification of treatment response with social interactions,
providing the broad weak-restriction background for network partial ID.
\citet{YuAiroldiBorgsChayes2022} study total treatment effects when the network
is unknown; their result is adjacent because it concerns unknown networks, but
it does not identify direct and indirect components jointly.

The in-repository CausalSmith catalogue has no substantive
\texttt{pid\_network\_random\_set}/\texttt{v1} proposal before this draft.
The closest prior is \texttt{pid\_network\_exposure}/\texttt{v1}, an accepted
field-tier proposal for shared-completion LP bounds for network average direct
effects under locally known interference.  That proposal's Section 8 focuses on
cellwise nonsharpness and capacitated certificates for ADE endpoints; it does
not condition on a total policy effect or construct a joint direct--indirect
compatibility region.  The \texttt{doc/API.md} PartialID catalogue notes that
new \texttt{pid\_*} questions are recorded as partial-ID theorem-substrate
entries, which is the cluster used here.

\section{Formal setup}
There are \(n\) units.  The observed law \(P\) consists of the known assignment
design and the own-treatment marginal means
\[
\mu_{iar}(P)=\E_P[Y_i\mid A_i=a,R=r],
\qquad i\le n,\ a,r\in\{0,1\}.
\]
The policy indicator \(R\in\{0,1\}\) selects a known Bernoulli assignment
policy, \(A_j\mid R=r\) is assigned independently with probability
\(p_r\in(0,1)\), \(p_0<p_1\), and \(Y_i\in[\underline y,\overline y]\).  The
researcher observes the realized network experiment through these marginal
policy cells, not through a repeated experiment at every full assignment vector
\(a\in\{0,1\}^n\).  Let \(\mathcal G_d\) be the finite class of undirected
networks on \(\{1,\ldots,n\}\) with maximum degree at most \(d\).
For \(G\in\mathcal G_d\), let \(\mathcal M_K(G)\) be the set of deterministic
unit exposure maps \(m=(m_1,\ldots,m_n)\) such that
\(m_i(G,\cdot):\{0,1\}^n\to\{0,\ldots,K-1\}\), depends only on \(A_i\) and the
treatments of \(i\)'s neighbors in \(G\), and has image cardinality at most
\(K\).  A completion is a triple \((G,m,y)\), with \(G\in\mathcal G_d\),
\(m\in\mathcal M_K(G)\), and bounded response table
\[
y_i(a,e)\in[\underline y,\overline y],\qquad
i\le n,\ a\in\{0,1\},\ e\in\{0,\ldots,K-1\}.
\]
It matches \(P\) when
\[
\mu_{iar}(P)=
\E_{A_{-i}\sim p_r}\!\left[y_i(a,m_i(G,(a,A_{-i})))\right]
\]
for every \(i\le n\) and \(a,r\in\{0,1\}\).  The latent table entries
\(y_i(a,e)\) are therefore constrained by marginal exposure mixtures, not by
full-assignment cell means.

For a completion, define the high-policy direct component
\[
\theta_D(G,m,y)=\frac1n\sum_{i=1}^n
\E_{A_{-i}\sim p_1}\!\left[
y_i(1,m_i(G,(1,A_{-i})))-y_i(0,m_i(G,(0,A_{-i})))
\right],
\]
and the control-status indirect component
\[
\theta_I(G,m,y)=\frac1n\sum_{i=1}^n
\left\{
\E_{A_{-i}\sim p_1}y_i(0,m_i(G,(0,A_{-i})))-
\E_{A_{-i}\sim p_0}y_i(0,m_i(G,(0,A_{-i})))
\right\}.
\]
Let \(t\) be the total-policy contrast being decomposed.  The
policy-decomposition compatibility set is
\[
\mathcal R_K(P;t)=
\left\{(\theta_D(G,m,y),\theta_I(G,m,y)):
(G,m,y)\text{ matches }P,\ \theta_D(G,m,y)+\theta_I(G,m,y)=t
\right\},
\]
and its bounding functional is \(h_K(v;P,t)=\sup_{\theta\in\mathcal R_K(P;t)}
v^\transpose\theta\).  The true sharp identified set \(\Theta_K(P;t)\) is
defined semantically as all direct--indirect pairs compatible with some full
finite-population data-generating process satisfying
Assumptions~\ref{ass:finite-design}--\ref{ass:total-normalization} and inducing
the same coarsened law \(P\).

\begin{verbatim}
Locked parameters:
qid = pid_network_random_set
specialization = v1
observable distribution P = design plus mu_iar(P)=E[Y_i | A_i=a,R=r]
parameter theta = theta^{DI} = (theta_D, theta_I)
identifying restrictions = randomized assignment, bounded outcomes,
  sparse G in G_d, K-support deterministic exposure maps m_i(G,.)
bounding functional = h_K(v;P,t), the support function of R_K(P;t)
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite randomized two-policy design]\label{ass:finite-design}
The number of units \(n\), policy probabilities \(0<p_0<p_1<1\), and assignment
law \(P(A=a\mid R=r)=p_r^{\sum_i a_i}(1-p_r)^{n-\sum_i a_i}\) are known, and
the own-treatment cells \((A_i=a,R=r)\) all have positive probability.
\end{assumption}

\begin{assumption}[Bounded response tables]\label{ass:bounded-response}
For every admissible completion, \(y_i(a,e)\in[\underline y,\overline y]\) for
known finite constants \(\underline y<\overline y\).
\end{assumption}

\begin{assumption}[Sparse \(K\)-support exposure locality]\label{ass:sparse-k}
The true network belongs to \(\mathcal G_d\), and each unit exposure map belongs
to \(\mathcal M_K(G)\): it depends only on the unit's own treatment and neighbor
treatments in \(G\), and its image has cardinality at most \(K\).
\end{assumption}

\begin{assumption}[Finite-population consistency]\label{ass:consistency}
Observed outcomes satisfy
\(Y_i=y_i(A_i,m_i(G,A))\) for the true completion \((G,m,y)\), and the observed
own-treatment means in \(P\) are the corresponding marginal mixtures over
\(A_{-i}\).
\end{assumption}

\begin{assumption}[Total contrast normalization]\label{ass:total-normalization}
The scalar \(t\) is fixed in advance as the total policy contrast to be
decomposed, and admissible decompositions must satisfy
\(\theta_D+\theta_I=t\).  In applications \(t\) may be the Hu--Li--Wager
infinitesimal Bernoulli policy effect or a two-policy total contrast already
identified from the experimental design.
\end{assumption}

\begin{assumption}[Nondegenerate five-unit witness class]\label{ass:witness-class}
For the strict-separation claim only, \(n=5\), \(K=2\), \(d=2\),
\(\underline y=0\), \(\overline y=1\), and \(p_0,p_1\in(0,1)\) are bounded away
from \(0\) and \(1\).  The witness law has at least two observed assignment
cells for each value of \(R\), nonconstant cell means, and two sparse candidate
networks that agree on all observed cells but induce different indirect labels
for unit \(5\) under the high policy.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite random-set outer representation]\label{thm:finite-random-set-outer}
Under Assumptions~\ref{ass:finite-design}--\ref{ass:total-normalization}, the
true identified set \(\Theta_K(P;t)\) is contained in \(\mathcal R_K(P;t)\), the
finite union of polytopes obtained
by fixing \((G,m)\in\{(G,m):G\in\mathcal G_d,\ m\in\mathcal M_K(G)\}\), imposing
the linear marginal-mixture matching equalities from \(P\), the bounds
\(\underline y\le y_i(a,e)\le\overline y\), and the single linear constraint
\(\theta_D+\theta_I=t\).  Consequently \(h_K(v;P,t)\) is bounded above by the
maximum, over this finite family, of a linear program in the response table
\(y\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is not the flagship novelty: it is the bookkeeping theorem that makes
the proposal well posed.  It differs from \citet{SchroderOprescuFeuerriegelKallus2026}
because their sharp bounds are built for fixed canonical misspecification
settings, while this theorem enumerates latent \(K\)-support maps and imposes a
joint total-decomposition constraint.  (b) The concrete consumer is
\citet{HuLiWager2022}: the theorem supplies the finite program that would let
their total-effect decomposition be audited under bounded unknown exposure
support.

\begin{conjecture}[Conjecture 1: sharp policy-decomposition support function (NOT YET PROVED)]\label{conj:pdc-sharp-support}
Under Assumptions~\ref{ass:finite-design}--\ref{ass:total-normalization}, the
outer representation in Theorem~\ref{thm:finite-random-set-outer} is sharp,
\(\Theta_K(P;t)=\mathcal R_K(P;t)\).  Therefore, for every direction
\(v\in\mathbb{S}^1\), the sharp identified-set support value equals
\[
\sup_{\theta\in\Theta_K(P;t)}v^\transpose\theta
=
\max_{\substack{G\in\mathcal G_d,\ m\in\mathcal M_K(G),\\
y\in[\underline y,\overline y]^{2Kn}}}
\left\{
v_D\theta_D(G,m,y)+v_I\theta_I(G,m,y):
(G,m,y)\text{ matches }P,\ \theta_D(G,m,y)+\theta_I(G,m,y)=t
\right\}.
\]
Equivalently, every exposed point of the support-function envelope is generated
by a single sparse \(K\)-support exposure completion, not by pasting direct and
indirect endpoints from incompatible latent maps.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest comparator chain is \citet{BeresteanuMolchanovMolinari2011} for
Aumann-expectation sharp regions, \citet{HuLiWager2022} for the direct plus
indirect policy-effect identity, and
\citet{SchroderOprescuFeuerriegelKallus2026} for sharp bounds under fixed
canonical exposure misspecification.  The epsilon-gap is the additional
compatibility restriction \(\theta_D+\theta_I=t\) over latent sparse
\(K\)-support labels: none of those papers gives a support function for the
joint direct--indirect decomposition set when the exposure labels themselves are
unobserved.  (b) Resolving this gives network-experiment analysts using the
Hu--Li--Wager decomposition a computable robustness region rather than two
separate component intervals whose endpoint pair may be impossible.

\begin{conjecture}[Conjecture 2: five-unit decomposition incompatibility witness (NOT YET PROVED)]\label{conj:five-unit-witness}
There exists a law \(P^\star\) satisfying
Assumptions~\ref{ass:finite-design}--\ref{ass:witness-class} and a total
contrast \(t^\star\) such that the componentwise projections of
\(\Theta_2(P^\star;t^\star)\) are nondegenerate intervals, but
\[
\Theta_2(P^\star;t^\star)\subsetneq
\operatorname{proj}_D\{\Theta_2(P^\star;t^\star)\}\times
\operatorname{proj}_I\{\Theta_2(P^\star;t^\star)\}
\cap\{(\theta_D,\theta_I):\theta_D+\theta_I=t^\star\}.
\]
The strict containment persists for all laws in an open neighborhood of
\(P^\star\) with the same observed support.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) This refines the prior CausalSmith \texttt{pid\_network\_exposure}/\texttt{v1}
cellwise-nonsharpness gap: that proposal concerns ADE endpoints under shared
hidden-edge compatibility, whereas this conjecture targets the direct--indirect
allocation of a total policy contrast.  It also differs from \citet{HudgensHalloran2008}
and \citet{HuLiWager2022}, which define decompositions but do not study
componentwise sharpness failure under latent exposure labels.  (b) The concrete
consumer is \citet{HoshinoYanagi2024}: when exposure mappings are unknown, their
instrument-exposure style analyses would gain a diagnostic warning that
separately bounded direct and indirect effects can overstate the feasible
decomposition of a policy contrast.

\section{Sanity-check corollaries}
\begin{corollary}[Known exposure-map corner]\label{cor:known-map}
If \(\mathcal G_d=\{G_0\}\) and \(\mathcal M_K(G_0)=\{m_0\}\), then
\(\Theta_K(P;t)=\mathcal R_K(P;t)\) reduces to the usual bounded-response linear identified
set for \((\theta_D,\theta_I)\) under the known exposure map \((G_0,m_0)\).  In
the additional point-identified case where every response table entry used by
\(\theta_D\) and \(\theta_I\) is observed, Conjecture~\ref{conj:pdc-sharp-support}
collapses to the Hu--Li--Wager decomposition identity
\(\theta_D+\theta_I=t\).
\end{corollary}

\begin{example}[Concrete non-corner witness route]\label{ex:five-unit-route}
For Conjecture~\ref{conj:five-unit-witness}, take five units with candidate
edges \((1,5)\), \((2,5)\), \((3,5)\), and \((4,5)\), degree cap \(d=2\), and
two \(K=2\) exposure maps that both match the observed low-policy cells but
assign unit \(5\)'s high-policy untreated exposure to different labels.  Set
observed cell means so that the direct upper endpoint requires edges
\((1,5),(2,5)\), while the indirect upper endpoint requires
\((3,5),(4,5)\).  Since one graph cannot realize all four incident edges under
\(d=2\), the endpoint pair is ruled out even though each component endpoint is
separately attainable.
\end{example}

\section{Proof-sketch route}
Theorem~\ref{thm:finite-random-set-outer} is finite partial-identification
algebra: fix \((G,m)\), translate every observed conditional mean into a linear
mixture equality in the bounded response table \(y\), add the total constraint, and
optimize a linear functional.  Conjecture~\ref{conj:pdc-sharp-support} should be
verified by a random-set selection argument: show that the finite union over
\((G,m)\) admits measurable selections cell-by-cell, that the total constraint
is preserved under the selection, and that no additional cross-cell consistency
condition is introduced beyond the shared \((G,m)\) already in the program.
The hard boundary case is label switching: two completions that differ only by
renaming latent exposure labels must generate the same support value, while two
completions that require incompatible sparse graphs must not be convexified
together.  Conjecture~\ref{conj:five-unit-witness} should be attacked by
enumerating the degree-\(2\) edge subsets in Example~\ref{ex:five-unit-route},
computing the four endpoint programs, and perturbing the cell means to prove
strict containment on an open neighborhood.

\section{Honest scope flags}
Theorem~\ref{thm:finite-random-set-outer} is labelled as a theorem because it
is routine finite LP containment, not because this proposal supplies a proof.
Conjectures~\ref{conj:pdc-sharp-support} and \ref{conj:five-unit-witness} are
the novel kernels and are not yet proved.  The proposal does not claim
asymptotic inference, efficient estimation, or specification testing.  The
largest modelling choice is the normalization of \(t\): Stage 0 may instantiate
it as the Hu--Li--Wager infinitesimal policy effect or as a two-policy total
contrast, but the direct--indirect compatibility geometry should be checked for
both conventions.  This pivot intentionally withdraws the prior angles on a
generic random-set envelope, generic nonrectangularity, finite certificates, and
exposure-map testability.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) --- initial draft for angle 4, selecting the total-policy
decomposition seed after angles 0--3 were exhausted; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Aronow and Samii(2017)]{AronowSamii2017}
Aronow, P. M. and C. Samii (2017).
Estimating average causal effects under general interference, with application
to a social network experiment.
\emph{Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem[Beresteanu, Molchanov, and Molinari(2011)]{BeresteanuMolchanovMolinari2011}
Beresteanu, A., I. Molchanov, and F. Molinari (2011).
Sharp identification regions in models with convex moment predictions.
\emph{Econometrica} 79(6), 1785--1821.

\bibitem[Hoshino and Yanagi(2024)]{HoshinoYanagi2024}
Hoshino, T. and T. Yanagi (2024).
Causal inference with noncompliance and unknown interference.
\emph{Journal of the American Statistical Association} 119(548), 2869--2880.

\bibitem[Hu, Li, and Wager(2022)]{HuLiWager2022}
Hu, Y., S. Li, and S. Wager (2022).
Average direct and indirect causal effects under interference.
\emph{Biometrika} 109(4), 1165--1172.

\bibitem[Hudgens and Halloran(2008)]{HudgensHalloran2008}
Hudgens, M. G. and M. E. Halloran (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.

\bibitem[Manski(2013)]{Manski2013}
Manski, C. F. (2013).
Identification of treatment response with social interactions.
\emph{The Econometrics Journal} 16(1), S1--S23.

\bibitem[Savje(2024)]{Savje2024}
Savje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions
and assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem[Schroder, Oprescu, Feuerriegel, and Kallus(2026)]{SchroderOprescuFeuerriegelKallus2026}
Schroder, M., M. Oprescu, S. Feuerriegel, and N. Kallus (2026).
Causal inference on networks under misspecified exposure mappings: a partial
identification framework.
\emph{arXiv:2602.03459}.

\bibitem[Yu, Airoldi, Borgs, and Chayes(2022)]{YuAiroldiBorgsChayes2022}
Yu, C. L., E. M. Airoldi, C. Borgs, and J. T. Chayes (2022).
Estimating the total treatment effect in randomized experiments with unknown
network structure.
\emph{Proceedings of the National Academy of Sciences} 119(44), e2208975119.
\end{thebibliography}

\end{document}
