\begin{proof}[Proof of \cref{obj:thm:cut-corner-exactness}]
\begin{enumerate}
\item
By the two-block homophily assumption, \(m\ge2\), \(0<b<a\). Hence
\[
q=2(m-1)>0,\qquad a-b>0,\qquad a+b>0,\qquad 2b>0 .
\]
Set
\[
A=2b(a+b)\left(1-\frac{\kappa}{a-b}\right),
\qquad
B=2b(2m-2b-\kappa).
\]
From \(r<\max\{0,\min(A,B)\}\) and \(0\le r\), we first get
\[
r<\min(A,B).
\]
Indeed, if \(\min(A,B)\le0\), then the outer maximum is \(0\), contradicting
\(0\le r<0\). Otherwise the outer maximum is \(\min(A,B)\). Thus
\[
r<A,\qquad r<B .
\]
% lean: cut_corner_exactness

\item
We now convert these two inequalities into the coefficient separations needed at the cut vertex.
From \(r<A\), division by the positive number \(2b(a+b)\) gives
\[
\frac{r}{2b(a+b)}
<
1-\frac{\kappa}{a-b}.
\]
Multiplying by \(a-b>0\) and rearranging gives
\[
\kappa
<
(a-b)\left(1-\frac{r}{2b(a+b)}\right).
\]
Using
\[
(a+b)+\frac{r}{a+b}
-\left(2b+\frac{r}{2b}+\kappa\right)
=
(a-b)\left(1-\frac{r}{2b(a+b)}\right)-\kappa
\]
and \(c_x/q=(a+b)+r/(a+b)\), \(c_y=2b+r/(2b)\), we obtain
\[
\frac{c_x}{q}>c_y+\kappa .
\]
Similarly, from \(r<B\), division by \(2b>0\) gives
\[
\frac{r}{2b}<2m-2b-\kappa,
\]
and hence
\[
2b+\frac{r}{2b}+\kappa<2m.
\]
Since \(c_z=2m\), this is
\[
c_z>c_y+\kappa .
\]
% lean: cut_corner_exactness

\item
The hypotheses of the cut-vertex certificate \cref{obj:lem:cut-vertex-certificate} are therefore satisfied: \(q>0\), \(\kappa\ge0\), and the two coefficient separations above hold. Hence
\[
(0,2m,0)\in T_m,
\]
and every other point of \(T_m\) has strictly larger reduced objective value.

By the spectral-coordinate \cref{obj:lem:block-spectral-coordinates}, the cut covariance is
\[
X_{\mathrm{cut}}=X(1,-1),
\]
and its spectral coordinates are
\[
(1-1,\;1+(m-1)\cdot1-m(-1),\;1+(m-1)\cdot1+m(-1))
=(0,2m,0).
\]
Thus \(X_{\mathrm{cut}}\in\mathcal E_m^{\mathrm{blk}}\), and
\[
F_{r,\kappa}(X_{\mathrm{cut}})
=
\phi_{r,\kappa}(0,2m,0).
\]
% lean: cut_vertex_certificate

\item
Let \(X\in\mathcal E_m^{\mathrm{blk}}\) and suppose \(X\ne X_{\mathrm{cut}}\). Write \(X=X(u,v)\). By \cref{obj:lem:block-spectral-coordinates}, the associated coordinates
\[
x=1-u,\qquad
y=1+(m-1)u-mv,\qquad
z_{\mathrm{sp}}=1+(m-1)u+mv
\]
belong to \(T_m\), and
\[
F_{r,\kappa}(X)=\phi_{r,\kappa}(x,y,z_{\mathrm{sp}}).
\]
These coordinates cannot equal \((0,2m,0)\): if \(x=0\), then \(u=1\), and if also
\(z_{\mathrm{sp}}=0\), then
\[
m(1+v)=0,
\]
so \(v=-1\) since \(m>0\), giving \(X=X_{\mathrm{cut}}\), a contradiction. The strict part of \cref{obj:lem:cut-vertex-certificate} therefore gives
\[
F_{r,\kappa}(X_{\mathrm{cut}})
=
\phi_{r,\kappa}(0,2m,0)
<
\phi_{r,\kappa}(x,y,z_{\mathrm{sp}})
=
F_{r,\kappa}(X).
\]
Thus \(X_{\mathrm{cut}}\) is the unique minimizer over \(\mathcal E_m^{\mathrm{blk}}\).
% lean: block_spectral_coordinates

\item
The cut design is the two-point cut law, so
\[
P_{\mathrm{cut}}\in\mathcal P_m^{\mathrm{sym}},
\qquad
X(P_{\mathrm{cut}})=X_{\mathrm{cut}}.
\]
Consequently \(X_{\mathrm{cut}}\in\mathcal C_m^{\pm}\). Moreover, every
\(X\in\mathcal C_m^{\pm}\) is obtained from a block-exchangeable design. Its second moment is block-symmetric, say \(X=X(u,v)\), and the forward reduced-slice characterization places its spectral coordinates in the same reduced triangle \(T_m\). By \cref{obj:lem:block-spectral-coordinates}, this implies
\[
\mathcal C_m^{\pm}\subseteq \mathcal E_m^{\mathrm{blk}}.
\]
Therefore, if \(X\in\mathcal C_m^{\pm}\) and \(X\ne X_{\mathrm{cut}}\), the strict relaxed optimality already proved yields
\[
F_{r,\kappa}(X_{\mathrm{cut}})<F_{r,\kappa}(X).
\]
Thus \(X_{\mathrm{cut}}\) is also the unique minimizer over \(\mathcal C_m^{\pm}\).
% lean: cutDesign_eq_cutVDesign

\item
It remains to identify the gap. From the strict inequalities above, with equality allowed only at
\(X_{\mathrm{cut}}\), we have the non-strict minimizing inequalities
\[
F_{r,\kappa}(X_{\mathrm{cut}})\le F_{r,\kappa}(X)
\quad\text{for all }X\in\mathcal E_m^{\mathrm{blk}},
\]
and
\[
F_{r,\kappa}(X_{\mathrm{cut}})\le F_{r,\kappa}(X)
\quad\text{for all }X\in\mathcal C_m^{\pm}.
\]
Since \(X_{\mathrm{cut}}\) belongs to both feasible classes, the infimum of each corresponding objective image is exactly \(F_{r,\kappa}(X_{\mathrm{cut}})\). Hence, by the definition of the implementability gap \cref{obj:def:implementability-gap},
\[
\Delta_m^{\pm}(r,\kappa)
=
F_{r,\kappa}(X_{\mathrm{cut}})
-
F_{r,\kappa}(X_{\mathrm{cut}})
=0.
\]
This proves all asserted conclusions.
% lean: sInf_image_eq_of_minimizer
\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:robust-corner-exactness}]
\begin{enumerate}
\item We first prove the finite-weight equivalence.  Write
\[
q=2(m-1),\qquad
c_x=q\left((a+b)+\frac r{a+b}\right),\qquad
c_y=2b+\frac r{2b},\qquad
c_z=2m .
\]
Suppose that some \(\kappa\ge 0\) makes \(I_n\) a relaxed minimizer over
\(\mathcal E_m^{\mathrm{blk}}\).  For an arbitrary
\((x,y,z_{\mathrm{sp}})\in T_m\), set
\[
u=1-x,\qquad v=\frac{z_{\mathrm{sp}}-y}{2m}.
\]
Using \cref{obj:lem:block-spectral-coordinates}, this inverse change of variables sends
\((x,y,z_{\mathrm{sp}})\) to a feasible block matrix \(X(u,v)\), and the matrix
objective equals the reduced objective at \((x,y,z_{\mathrm{sp}})\).  Since
\(I_n=X(0,0)\) corresponds to \((1,1,1)\), the assumed matrix minimality says that
\((1,1,1)\) minimizes
\[
c_xx+c_yy+c_zz_{\mathrm{sp}}
+\kappa\sqrt{q x^2+y^2+z_{\mathrm{sp}}^2}
\]
on \(T_m\).  The certificate-necessity part of
\cref{obj:lem:frobenius-center-certificate} therefore gives
\[
\frac{c_x}{q}=c_y,\qquad c_y=c_z .
\]
The first equality is
\[
a+b+\frac r{a+b}=2b+\frac r{2b},
\]
hence
\[
(a-b)\left(1-\frac{r}{2b(a+b)}\right)=0.
\]
By two-block homophily, \(a>b>0\), so
\[
r=2b(a+b).
\]
Substituting this into \(c_y=c_z\) gives
\[
2b+\frac{2b(a+b)}{2b}=2m,
\]
that is \(a+3b=2m\).  Thus the affine-balanced locus holds.  Conversely, if
\[
a+3b=2m,\qquad r=2b(a+b),
\]
then the same algebra gives \(c_x/q=c_y=c_z\).  Taking \(\kappa=1\), the strict
optimality part of \cref{obj:lem:frobenius-center-certificate}, transported through
\cref{obj:lem:block-spectral-coordinates}, gives \(I_n\in\mathcal E_m^{\mathrm{blk}}\)
and strict optimality against every \(X\ne I_n\).  For \(X=I_n\) the desired inequality
is equality, while for \(X\ne I_n\) it follows from strict optimality.  Hence a finite
nonnegative robustness weight exists exactly on the stated locus. % lean: robust_corner_exactness

\item On the affine-balanced locus, let \(\kappa>0\).  As above,
\[
\frac{c_x}{q}=c_y=c_z .
\]
The point \(I_n=X(0,0)\) has reduced coordinates \((1,1,1)\) by
\cref{obj:lem:block-spectral-coordinates}.  The Frobenius-center certificate
\cref{obj:lem:frobenius-center-certificate} gives strict reduced optimality of
\((1,1,1)\) on \(T_m\).  Translating back by
\cref{obj:lem:block-spectral-coordinates}, \(I_n\in\mathcal E_m^{\mathrm{blk}}\), and
for any \(X=X(u,v)\in\mathcal E_m^{\mathrm{blk}}\) with \(X\ne I_n\), the associated
reduced coordinates are not \((1,1,1)\); otherwise \(u=0\) and \(v=0\), hence
\(X=I_n\).  Therefore
\[
F_{r,\kappa}(I_n)<F_{r,\kappa}(X).
\] % lean: identity_strict_relaxed_min_of_locus

\item The iid law is invariant under sign flip, within-block permutations, and block
swap, so
\[
P_{\mathrm{iid}}\in\mathcal P_m^{\mathrm{sym}}.
\]
Its second moments are diagonal: the diagonal entries equal \(1\), and for \(i\ne j\)
the involution that flips the \(i\)-th sign pairs every assignment with one contributing
the negative product.  Thus all off-diagonal moments vanish and
\[
X(P_{\mathrm{iid}})=I_n .
\] % lean: iidDesign_mem_blockExchangeable, iidDesign_secondMoment

\item Now assume the affine-balanced locus fails.  If for some \(\kappa>0\) the matrix
\(I_n\) were a relaxed minimizer, then the same center-coefficient necessity argument
from the first step would give
\[
\frac{c_x}{q}=c_y,\qquad c_y=c_z,
\]
and the same algebra would force
\[
a+3b=2m,\qquad r=2b(a+b),
\]
contradicting the assumption.  Hence \(I_n\) is not a relaxed minimizer at any positive
finite robustness weight off the locus. % lean: robust_corner_exactness

\item Finally, let \((X_\kappa)_{\kappa\in\mathbb R}\) be any family of relaxed
minimizers for positive \(\kappa\).  Since \(r\ge0\) and \(a>b>0\), the reduced linear
coefficients \(c_x,c_y,c_z\) are nonnegative.  Comparing each minimizer with the feasible
point \(I_n\) gives
\[
F_{r,\kappa}(X_\kappa)\le F_{r,\kappa}(I_n).
\]
Writing \(X_\kappa=X(u_\kappa,v_\kappa)\), the reduced squared norm decomposes as
\[
q(1-u_\kappa)^2+
\bigl(1+(m-1)u_\kappa-mv_\kappa\bigr)^2+
\bigl(1+(m-1)u_\kappa+mv_\kappa\bigr)^2
=
q+2+N_{\mathrm{same}}u_\kappa^2+N_{\mathrm{cross}}v_\kappa^2,
\]
with positive constants \(N_{\mathrm{same}}\) and \(N_{\mathrm{cross}}\).  If a
same-block off-diagonal entry stayed at distance at least \(\varepsilon>0\) from zero
for arbitrarily large \(\kappa\), then \(|u_\kappa|\ge\varepsilon\), so the robustness
norm would exceed its value at \(I_n\) by a fixed amount \(\delta>0\).  The nonnegative
linear part then yields
\[
\kappa\bigl(\|I_n\|+\delta\bigr)\le F_{r,\kappa}(X_\kappa)
\le F_{r,\kappa}(I_n)=L+\kappa\|I_n\|,
\]
forcing \(\kappa\delta\le L\), impossible for all sufficiently large \(\kappa\).  The
same argument with \(N_{\mathrm{cross}}\) shows that the across-block parameter
\(v_\kappa\to0\).  Diagonal entries are identically \(1\), while off-diagonal entries
are either \(u_\kappa\) or \(v_\kappa\).  Hence every entry of \(X_\kappa\) converges to
the corresponding entry of \(I_n\) as \(\kappa\to\infty\). % lean: robust_minimizers_tendsto_identity_entries
\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:gap-window}]
1.  \Cref{obj:ass:two-block-homophily} gives \(m\ge2\), \(b<a\), and \(b>0\). Hence
\[
q=2(m-1)>0,\qquad \sqrt q>0,\qquad a+b>0,\qquad a-b>0.
\]
\cref{obj:ass:low-scale-two-block} gives
\[
2m-a-3b>0.
\]
These inequalities are the standing sign facts used below for division and multiplication by positive quantities.  % lean: gap_window

2.  Assume now that \cref{obj:ass:odd-community-size} holds, and fix
\[
0\le \kappa<\kappa_{\mathrm{gap}}(m,a,b).
\]
Unfolding the definition of \(\kappa_{\mathrm{gap}}\) and multiplying by the positive factor
\((a+b)/((a-b)\sqrt q)\), we get
\[
\frac{\kappa(a+b)}{(a-b)\sqrt q}<2m-a-3b.
\]
Therefore
\[
R_x^+-R_x^-
=(a+b)\left((2m-a-3b)-\frac{\kappa(a+b)}{(a-b)\sqrt q}\right)>0.
\]
Thus \(R_x^-<R_x^+=r_{\mathrm{gap}}^+\), and since
\[
r_{\mathrm{gap}}^-=\frac{R_x^-+R_x^+}{2},
\]
we have
\[
R_x^-<r_{\mathrm{gap}}^-<r_{\mathrm{gap}}^+.
\]
Also \(R_x^-\ge0\), and
\[
2b(a+b)\left(1-\frac{\kappa}{a-b}\right)\le R_x^-,
\]
so
\[
r_{\mathrm{cut,gap}}(m,a,b,\kappa)
=\max\left\{0,\;2b(a+b)\left(1-\frac{\kappa}{a-b}\right)\right\}
\le R_x^-.
\]
Combining these inequalities yields
\[
r_{\mathrm{cut,gap}}(m,a,b,\kappa)
<
r_{\mathrm{gap}}^-(m,a,b,\kappa)
<
r_{\mathrm{gap}}^+(m,a,b,\kappa).
\]  % lean: gap_window

3.  Let \(r_{\mathrm{gap}}^-<r<r_{\mathrm{gap}}^+\). From the preceding step,
\[
R_x^-<r.
\]
After division by \(2b(a+b)>0\), this says
\[
1+\frac{\kappa}{(a-b)\sqrt q}<\frac{r}{2b(a+b)}.
\]
Multiplying by \(a-b>0\) gives
\[
\frac{\kappa}{\sqrt q}
<
(a-b)\left(\frac{r}{2b(a+b)}-1\right).
\]
Using the identity
\[
2b+\frac r{2b}-\left(a+b+\frac r{a+b}\right)
=
(a-b)\left(\frac{r}{2b(a+b)}-1\right),
\]
and \(c_x/q=a+b+r/(a+b)\), this proves
\[
c_y>\frac{c_x}{q}+\frac{\kappa}{\sqrt q}.
\]
Similarly, the upper bound \(r<r_{\mathrm{gap}}^+=R_x^+\) gives
\[
\frac r{a+b}<2m-a-b-\frac{\kappa}{\sqrt q},
\]
hence, since \(c_z=2m\) and \(c_x/q=a+b+r/(a+b)\),
\[
c_z>\frac{c_x}{q}+\frac{\kappa}{\sqrt q}.
\]
By the spread-vertex certificate, \cref{obj:lem:spread-vertex-certificate}, the point
\[
\left(\frac{2m}{q},0,0\right)=\left(\frac{m}{m-1},0,0\right)
\]
belongs to \(T_m\) and is the strict unique minimizer of the reduced objective on \(T_m\).  % lean: spread_vertex_certificate

4.  The spread covariance is \(X(-1/(m-1),0)\), whose spectral coordinates are
\[
x=1-\left(-\frac1{m-1}\right)=\frac{2m}{q},\qquad
y=0,\qquad z_{\mathrm{sp}}=0.
\]
By \cref{obj:lem:block-spectral-coordinates}, the membership of this triple in \(T_m\) gives
\[
X_{\mathrm{spread}}\in\mathcal E_m^{\mathrm{blk}},
\]
and the value of \(F_{r,\kappa}\) at \(X_{\mathrm{spread}}\) is the reduced objective at
\((2m/q,0,0)\). If \(X\in\mathcal E_m^{\mathrm{blk}}\), write \(X=X(u,v)\). \Cref{obj:lem:block-spectral-coordinates} sends it to a point of \(T_m\) and identifies \(F_{r,\kappa}(X)\) with the reduced objective there. If this reduced point equals \((2m/q,0,0)\), then \(y=z_{\mathrm{sp}}=0\) forces \(v=0\) and \(u=-1/(m-1)\), hence \(X=X_{\mathrm{spread}}\). Therefore every \(X\ne X_{\mathrm{spread}}\) corresponds to a different point of \(T_m\), and the strict reduced optimality from Step 3 gives
\[
F_{r,\kappa}(X_{\mathrm{spread}})<F_{r,\kappa}(X).
\]  % lean: spread_certificate_relaxed_minimizer_and_gap

5.  Since \(m\) is odd, \cref{obj:lem:pm-reduced-slice-characterization} imposes the implementability condition
\[
y+z_{\mathrm{sp}}\ge \frac2m.
\]
The spread point has \(y+z_{\mathrm{sp}}=0\), so
\[
X_{\mathrm{spread}}\notin\mathcal C_m^{\pm}.
\]
For the loss, pass from \((x,y,z_{\mathrm{sp}})\) to simplex variables
\[
t=(qx,y,z_{\mathrm{sp}}),\qquad t_x+t_y+t_z=2m,
\]
with weights \(\beta=(1/q,1,1)\) and coefficients
\[
\alpha=\left(\frac{c_x}{q},c_y,c_z\right).
\]
The relaxed minimizer is \(t^{\mathrm{rel}}=(2m,0,0)\), and it violates the odd parity constraint \(t_y+t_z\ge2/m\). \Cref{obj:lem:weighted-simplex-truncation} gives a minimizer on the truncated simplex, hence an implementable reduced minimizer. Since the relaxed minimizer is unique and lies outside the truncated slice, that implementable minimizer has strictly larger reduced objective value. Finally \cref{obj:lem:rounding-gap-reduction} identifies
\[
\Delta_m^{\pm}(r,\kappa)
\]
with the truncated reduced infimum minus the relaxed reduced infimum, so
\[
\Delta_m^{\pm}(r,\kappa)>0.
\]  % lean: spread_certificate_relaxed_minimizer_and_gap

6.  It remains to prove the even case. Assume \(m\) is even and let \(X\in\mathcal E_m^{\mathrm{blk}}\). Write \(X=X(u,v)\), and let \((x,y,z_{\mathrm{sp}})\) be its spectral coordinates. By \cref{obj:lem:block-spectral-coordinates}, this point lies in \(T_m\), so \(y,z_{\mathrm{sp}}\ge0\). For even \(m\), the parity threshold in \cref{obj:lem:pm-reduced-slice-characterization} is \(0\), and hence \(y+z_{\mathrm{sp}}\ge0\) automatically. The same lemma therefore gives \(X\in\mathcal C_m^{\pm}\). Thus
\[
\mathcal E_m^{\mathrm{blk}}\subseteq\mathcal C_m^{\pm}.
\]  % lean: blockElliptope_subset_implementable_of_even
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:sharp-rho-star}]
\textbf{1. Equality and range.}
By definition, \(\rho_\star(m,a,b,r,\kappa)\) is the difference between the implementable reduced value and the relaxed reduced value.  The reduced gap identity \cref{obj:lem:rounding-gap-reduction} identifies this same difference with \(\Delta_m^{\pm}(r,\kappa)\).  Hence
\[
\rho_\star(m,a,b,r,\kappa)=\Delta_m^{\pm}(r,\kappa).
\]
The nonnegativity of \(\rho_\star\) is the constrained-infimum comparison for the reduced problem: the implementable feasible set is the parity-truncated subset of \(T_m\), while the relaxed feasible set is all of \(T_m\).  The objective is bounded below using \(r\ge0\), \(\kappa\ge0\), the nonnegative reduced coordinates, and \(a>b>0\).  Applying the same reduced identity gives the nonnegativity of \(\Delta_m^{\pm}(r,\kappa)\). % lean: hGapEq, roundingLossCertificate_nonneg, implementabilityGap_nonneg

\textbf{2. Zero loss.}
Again using the definition of \(\rho_\star\) together with \cref{obj:lem:rounding-gap-reduction}, zero rounding loss is exactly zero reduced implementability gap.  The zero-gap criterion says that this happens precisely when some relaxed minimizer over \(T_m\) also belongs to the parity-truncated slice, namely when there is
\((x,y,z_{\mathrm{sp}})\in T_m\) minimizing \(\phi_{r,\kappa}\) over all of \(T_m\) and satisfying
\[
d_m\le y+z_{\mathrm{sp}}.
\]
This is the stated zero-loss equivalence. % lean: sharp_roundingLoss_zero_iff_argmin_meets_slice

\textbf{3. Strict robustness.}
Assume \(\kappa>0\).  Since \(m\ge2\) under \cref{obj:ass:two-block-homophily}, we have \(q=2(m-1)>0\).  Under the change of variables
\[
t=(qx,y,z_{\mathrm{sp}}),
\qquad
\alpha^\sharp=\Bigl(\frac{c_x}{q},c_y,c_z\Bigr),
\qquad
\beta^\sharp=\Bigl(\frac1q,1,1\Bigr),
\]
the reduced triangle \(T_m\) is the simplex of total mass \(2m\), and \(\phi_{r,\kappa}\) becomes the weighted-simplex objective.  The positive-robustness part of \cref{obj:lem:weighted-simplex-active-set} gives a unique weighted-simplex minimizer, hence a unique relaxed minimizer of \(\phi_{r,\kappa}\) on \(T_m\).  With uniqueness in hand, the zero-gap criterion from Step 2 is equivalent to saying that every relaxed minimizer satisfies \(d_m\le y+z_{\mathrm{sp}}\). % lean: sharp_reduced_active_set_and_unique, sharp_roundingLoss_zero_iff_unique_argmin_subset_slice

\textbf{4. Linear case.}
Assume \(\kappa=0\), and fix \((x,y,z_{\mathrm{sp}})\in T_m\).  Passing to \(t=(qx,y,z_{\mathrm{sp}})\), the reduced objective is the linear weighted-simplex objective with coefficients \(\alpha^\sharp\).  The zero-robustness part of \cref{obj:lem:weighted-simplex-active-set} identifies the minimizers with the exposed face supported only on coordinates whose \(\alpha^\sharp\)-coefficient is minimal.  Translating this exposed-face condition back to \((x,y,z_{\mathrm{sp}})\) gives exactly the three displayed implications:
positive \(x\)-mass requires \(c_x/q\le c_y,c_z\), positive \(y\)-mass requires \(c_y\le c_x/q,c_z\), and positive \(z_{\mathrm{sp}}\)-mass requires \(c_z\le c_x/q,c_y\). % lean: sharp_kappa_zero_reduced_min_iff

\textbf{5. Active-set formula.}
Assume \(\kappa>0\).  The same active-set construction from Step 3 supplies an admissible support \(S\subseteq\{x,y,z_{\mathrm{sp}}\}\) and multiplier \(\lambda\) for \(\alpha^\sharp,\beta^\sharp,\kappa\).  The corresponding simplex point \(t^{S,\lambda}\) has mass \(2m\); therefore
\[
\Bigl(\frac{t_x^{S,\lambda}}{q},t_y^{S,\lambda},t_z^{S,\lambda}\Bigr)\in T_m .
\]
The weighted-simplex strict minimizer property transfers back through \(t=(qx,y,z_{\mathrm{sp}})\), so this reduced point minimizes \(\phi_{r,\kappa}\) over \(T_m\).  The value formula in \cref{obj:lem:weighted-simplex-active-set} gives the relaxed reduced value \(2m\,\lambda\). % lean: sharp_reduced_active_set_and_unique

\textbf{6. Truncation correction.}
Suppose no relaxed minimizer in \(T_m\) satisfies \(d_m\le y+z_{\mathrm{sp}}\).  Choose a relaxed minimizer and pass to \(t=(qx,y,z_{\mathrm{sp}})\).  Its weighted-simplex coordinates minimize the unconstrained simplex problem but fail the truncated condition \(t_y+t_z\ge d_m\).  The truncation \cref{obj:lem:weighted-simplex-truncation} then puts the constrained minimizer on the boundary segment
\[
H_{d_m}=\{(2m-d_m,s,d_m-s):0\le s\le d_m\}
\]
at
\[
s_\star=\operatorname{truncSelector}(2m,d_m,\alpha^\sharp,\beta^\sharp,\kappa).
\]
Converting the resulting constrained weighted-simplex optimum back to the reduced notation gives
\[
\operatorname{val}_{\mathrm{impl}}(m,a,b,r,\kappa)
=
\Phi_{\alpha^\sharp,\beta^\sharp,\kappa}
(2m-d_m,s_\star,d_m-s_\star).
\]
 % lean: sharp_truncation_value_of_no_reduced_argmin_in_slice

\textbf{7. Even block size.}
If \(m\) is even, then \(d_m=0\).  A relaxed minimizer exists, and every point of \(T_m\) has \(y,z_{\mathrm{sp}}\ge0\), hence \(0=d_m\le y+z_{\mathrm{sp}}\).  The zero-loss criterion from Step 2 therefore gives
\[
\rho_\star(m,a,b,r,\kappa)=0 .
\]
 % lean: sharp_roundingLoss_zero_of_even
\end{proof}
