\begin{proof}[Proof of \cref{obj:thm:sharp-ppml-forbidden-sign}]
Write \(W_{gt}=\widetilde W_{gt}(\delta)\) and
\[
\mathcal E=\sum_{g\in\mathcal C}\sum_{t=1}^T
q_{gt}\mu^\star_{gt}(\delta)W_{gt}^2 .
\]
\begin{enumerate}
\item First, \(\mathcal E>0\). Each summand is nonnegative, since \(q_{gt}>0\), \(\mu^\star_{gt}(\delta)>0\), and \(W_{gt}^2\ge0\). If \(\mathcal E\) were not positive, then \(\mathcal E=0\), and every summand would have to vanish. Positivity of \(q_{gt}\mu^\star_{gt}(\delta)\) then gives \(W_{gt}=0\) for every supported cohort-period cell. Let \(\rho^\star(\delta)\) be the weighted nuisance projection coefficient used to define the FWL residual, and set the collapsed parameter
\[
a=(-\rho^\star(\delta),1).
\]
Its treatment coordinate is one, so \(a\ne0\). The coefficient form of the FWL residual gives, for every supported cell,
\[
r_{gt}'a
=
D_{gt}-\sum_j X_{gt,j}\rho^\star_j(\delta)
=
W_{gt}
=
0.
\]
Hence
\[
\sum_{g\in\mathcal C}\sum_{t=1}^T q_{gt}(r_{gt}'a)^2=0,
\]
contradicting the full-rank condition in \cref{obj:ass:collapsed-design-rank}. Thus \(\mathcal E>0\).

\item The scalar multiplying \(W_{ks}\) in the displayed derivative is strictly positive:
\[
c
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})}{\mathcal E}
>0.
\]
Indeed \(q_{ks}>0\), \(B_{ks}>0\), \(\exp(\delta_{ks})>0\), and the previous step gives \(\mathcal E>0\).

\item Consider the path that replaces only \(\delta_{ks}\) by \(x\). Since \(D_{ks}=1\), this changes the collapsed observed mean only in cell \((k,s)\), where it is \(B_{ks}\exp(x)\), and leaves all other collapsed means unchanged. The collapsed criterion is rewritten as a finite Poisson objective on the supported cohort-period table, with positive masses, positive means, and design map \(\theta\mapsto(r_{gt}'\theta)_{g,t}\). The rank condition makes this design map injective: if two parameters have the same fitted index in every supported cell, their difference violates \cref{obj:ass:collapsed-design-rank} unless it is zero.

\item The derivative of the selected treatment coordinate is identified from the corresponding linearized score. For any solution \(v\) of that linearized score, let \(v_\beta\) be its treatment coordinate. Normalize the weights \(q_{gt}\mu^\star_{gt}(\delta)\) by their positive total \(Z\), let \(Y\) be the one-cell source divided by \(\mu^\star\), and let the nuisance part of \(v\) lie in the fixed-effect nuisance span. The linearized score gives orthogonality of \(Y-v_\beta D-\alpha\) both to \(D\) and to every nuisance direction. Since \(\langle W,W\rangle>0\), the scalar FWL identity yields
\[
v_\beta
=
\frac{\langle W,Y\rangle}{\langle W,W\rangle}.
\]
The one-cell source gives
\[
\langle W,Y\rangle
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})W_{ks}}{Z},
\qquad
\langle W,W\rangle
=
\frac{\mathcal E}{Z},
\]
so
\[
v_\beta
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})W_{ks}}{\mathcal E}.
\]


\item The one-cell finite-Poisson derivative calculation therefore gives
\[
\frac{d}{dx}\,
\beta^\star\!\bigl(\delta \text{ with } \delta_{ks}\text{ replaced by }x\bigr)
\Big|_{x=\delta_{ks}}
=
\frac{q_{ks}B_{ks}\exp(\delta_{ks})W_{ks}}{\mathcal E}.
\]
This proves differentiability at \(x=\delta_{ks}\) and the displayed derivative formula.

\item Since the derivative is \(cW_{ks}\) with \(c>0\),
\[
cW_{ks}<0 \iff W_{ks}<0.
\]
The forward implication follows because \(W_{ks}\ge0\) would imply \(cW_{ks}\ge0\); the reverse implication is multiplication by a positive scalar.

\item Again using \(c>0\), hence \(c\ne0\),
\[
cW_{ks}=0 \iff W_{ks}=0.
\]


\item Finally, multiplication by the same positive scalar gives
\[
0<cW_{ks} \iff 0<W_{ks}.
\]
Substituting \(W_{ks}=\widetilde W_{ks}(\delta)\) gives the three asserted sign equivalences.
\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:prop:homogeneous-effect-reduction}]
\begin{enumerate}
\item Let \(\infty\) denote the never-treated reference cohort, and define the candidate collapsed parameter
\(\theta^0=(a^0,\delta_0)\) as follows: the intercept coordinate is
\(\log \bar b_\infty\); the cohort-dummy coordinate for a supported finite cohort
\(c\) is
\[
\log \bar b_c-\log \bar b_\infty;
\]
and the non-base-period time-dummy coordinate for period \(u\) is
\(\gamma_{u0}\). \Cref{obj:ass:unit-untreated-exponential-mean} gives the normalization \(\gamma_{10}=0\). Hence the time-dummy contribution equals \(\gamma_{t0}\): if \(t\) is the base period all time dummies vanish and \(\gamma_{t0}=0\), while if \(t\) is not the base period exactly its own dummy contributes. Likewise, the cohort-dummy contribution is \(0\) for \(g=\infty\), and is \(\log\bar b_g-\log\bar b_\infty\) for \(g\neq\infty\).

\item Therefore, for every supported cohort \(g\in\mathcal C\) and every period \(t\), the collapsed linear index at \(\theta^0\) is
\[
\eta_{gt}(\theta^0)
=
\log \bar b_g+\gamma_{t0}+D_{gt}\delta_0 .
\]
This is checked by the two cohort cases \(g=\infty\) and \(g\neq\infty\), using the preceding dummy-sum identities.

\item The homogeneous-effect hypothesis implies
\[
D_{gt}\delta_{gt}=D_{gt}\delta_0
\]
for every \(g\in\mathcal C\) and \(t\). Indeed, if \(D_{gt}=1\), the common treated-cell effect assumption gives \(\delta_{gt}=\delta_0\); if \(D_{gt}=0\), both products are zero.

\item Combining the previous two displays with \(B_{gt}=\bar b_g\exp(\gamma_{t0})\), the observed collapsed mean satisfies
\[
m_{gt}(\delta)
=
B_{gt}\exp(D_{gt}\delta_{gt})
=
\exp\{\eta_{gt}(\theta^0)\}.
\]
In particular \(m_{gt}(\delta)>0\), and
\[
\log m_{gt}(\delta)=\eta_{gt}(\theta^0).
\]


\item For any \(m>0\) and any real \(\eta\),
\[
m\eta-\exp(\eta)
\le
m\log m-\exp(\log m),
\]
with strict inequality when \(\eta\neq\log m\). This follows from \(1+x\le \exp(x)\), and from its strict form when \(x\neq0\), applied to \(x=\eta-\log m\) and then rearranged after multiplying by \(m>0\).

\item The cell masses are strictly positive. The rank condition in \cref{obj:ass:collapsed-design-rank} first rules out \(T=0\): the direction with zero nuisance coordinates and treatment coordinate one would otherwise have zero weighted squared index, contradicting collapsed full rank. Thus \(T>0\), and since \(\pi_g\in(0,1)\),
\[
q_{gt}=\frac{\pi_g}{T}>0 .
\]


\item For any collapsed parameter \(\theta\), write
\[
L(\theta;\delta)
=
\sum_{g\in\mathcal C}\sum_t
q_{gt}\{m_{gt}(\delta)\eta_{gt}(\theta)-\exp(\eta_{gt}(\theta))\}.
\]
Using \(\log m_{gt}(\delta)=\eta_{gt}(\theta^0)\) cell by cell and the weak scalar inequality above gives
\[
L(\theta;\delta)\le L(\theta^0;\delta).
\]
Thus \(\theta^0\) is a global maximizer of the limiting collapsed criterion.

\item This maximizer is unique. Suppose \(L(\theta;\delta)=L(\theta^0;\delta)\). If \(\theta\neq\theta^0\), then \(\theta-\theta^0\neq0\), so \cref{obj:ass:collapsed-design-rank} gives a positive weighted sum of squared index differences. Hence some supported cell \((g_0,t_0)\) must have
\[
\eta_{g_0t_0}(\theta)\neq \eta_{g_0t_0}(\theta^0);
\]
otherwise linearity of the index under subtraction would make every squared term zero. At this cell the strict scalar inequality applies, while all other cells satisfy the weak inequality. Since \(q_{g_0t_0}>0\), summing yields
\[
L(\theta;\delta)<L(\theta^0;\delta),
\]
contradicting the assumed equality. Therefore \(\theta=\theta^0\).

\item Consequently, the selected limiting collapsed projection in \cref{obj:def:collapsed-population-projection} is exactly
\[
\theta^\star(\delta)=\theta^0,
\]
because \(\theta^0\) exists as the unique global maximizer.

\item The treatment coordinate of \(\theta^0\) is \(\delta_0\), so
\[
\beta^\star(\delta)=\delta_0.
\]
For every \(g\in\mathcal C\) and every \(t\),
\[
\mu^\star_{gt}(\delta)
=
\exp\{\eta_{gt}(\theta^\star(\delta))\}
=
\exp\{\log\bar b_g+\gamma_{t0}+D_{gt}\delta_0\}
=
B_{gt}\exp(D_{gt}\delta_0).
\]

\end{enumerate}
\end{proof}

\begin{proof}[Proof of \cref{obj:thm:primitive-global-frontier}]
Write \(q_{gt}=\pi_g/T\), and write
\[
Z=\sum_{(g,t)\in H}q_{gt}B^{obs}_{gt}.
\]
The proof proceeds by the same reductions used in the collapsed frontier calculation.

\begin{enumerate}
\item Since \(T\ge 4\), in particular \(T>0\). The frontier sign calculation applies because the never-treated cohort is in \(\mathcal C\) and the collapsed rank condition holds. At the frontier fit with treatment coefficient set to zero, the nuisance scores vanish and the treatment score is
\[
\frac{\Phi}{T M}.
\]
The denominator is strictly positive: \(T>0\) and \(M\) is a sum of strictly positive primitive cell masses. Therefore the sign, zero, and positive sign of \(\beta^\star(\delta)\) agree exactly with those of \(\Phi\). This gives
\[
\beta^\star(\delta)<0\iff \Phi<0,\qquad
\beta^\star(\delta)=0\iff \Phi=0,\qquad
0<\beta^\star(\delta)\iff 0<\Phi .
\]

\item For every supported cohort \(g\), the first-period treatment indicator is zero. If \(g=\infty\), this is the never-treated path. If \(g\) is finite, support excludes adoption in the first period; hence treatment in the first period would force the adoption date to be the first period, a contradiction. Also \(D_{\infty t}=0\) for every \(t\), and \cref{obj:ass:unit-untreated-exponential-mean} gives the first-period normalization \(\gamma_{10}=0\). Thus, for every \(g\in\mathcal C\) and every \(t\),
\[
B^{obs}_{gt}
=
\frac{m_{g1}m_{\infty t}}{m_{\infty 1}}
=
\frac{\bar b_g e^{\gamma_{10}}\bar b_\infty e^{\gamma_{t0}}}
{\bar b_\infty e^{\gamma_{10}}}
=
\bar b_g e^{\gamma_{t0}}
=
B_{gt}.
\]

\item \cref{obj:ass:multicohort-frontier-scope} supplies a supported finite cohort adopting in the second paper period; in that period its treatment indicator equals one. Hence \(H\) is nonempty. For every \((g,t)\in H\), both \(q_{gt}\) and \(B^{obs}_{gt}=B_{gt}\) are positive. Consequently every summand in \(Z\) is nonnegative and at least one is strictly positive, so
\[
Z>0.
\]

\item We next identify membership in \(\mathcal R_T\). If the induced primitive tuple belongs to \(\mathcal R_T\), then \cref{obj:def:global-sign-reversal-region} includes negativity of the primitive treatment coefficient. The restricted primitive coefficient is exactly \(\beta^\star(\delta)\), so Step 1 gives \(\Phi<0\).

Conversely suppose \(\Phi<0\). The horizon, support, and frontier-scope clauses are the assumptions of the theorem. The share simplex clause follows from the cohort-share limit and array support, which imply \(\sum_{g\in\mathcal C}\pi_g=1\). The baseline clause is witnessed by \(g\mapsto \bar b_g\), since the primitive untreated coordinate is \(\bar b_g e^{\gamma_{t0}}\). The positive-effect clause is \cref{obj:ass:strict-positive-effects}. The rank clause is \cref{obj:ass:collapsed-design-rank}, after rewriting the supported-cell sum as the corresponding sum over \(g\in\mathcal C\) and \(t\). Finally Step 1 gives \(\beta^\star(\delta)<0\), and the restricted primitive coefficient equals \(\beta^\star(\delta)\). Thus the induced primitive tuple is in \(\mathcal R_T\).

\item In the four-period support \(\{2,3,4,\infty\}\), expand \cref{obj:def:frontier-elimination-handle} with equal shares, unit limiting baselines, zero untreated time effects, multiplier \(x\) on every treated cell except \((2,4)\), and multiplier \(y\) at \((2,4)\). Since \(x>1\) and \(y>1\), \(\exp(\log x)=x\) and \(\exp(\log y)=y\). Direct summation of the four row margins, four column margins, treated total, and grand total gives
\[
\Phi=\frac{5x^2+12x-2y-15}{16}.
\]

\item The displayed numerical identity is then ordinary rational arithmetic:
\[
\frac{5(101/100)^2+12(101/100)-15}{2}
=\frac{4441}{4000}.
\]

\item For the witness \(W_4\) of \cref{obj:def:four-cohort-witness}, the effect vector is the preceding four-period family with \(x=101/100\) and \(y=4\). Substituting these values in Step 5 gives
\[
\Phi
=
\frac{5(101/100)^2+12(101/100)-2\cdot 4-15}{16}
=
-\frac{11559}{32000}.
\]

\item Let \((g,t)\in H\). Then \(D_{gt}=1\). Step 2 gives \(B^{obs}_{gt}=B_{gt}\). Moreover
\[
\tau_{gt}
=
\frac{m_{gt}}{B^{obs}_{gt}}-1
=
\frac{B_{gt}\exp(\delta_{gt})}{B_{gt}}-1
=
\exp(\delta_{gt})-1,
\]
using \(B_{gt}>0\). Also
\[
\omega_{gt}=\frac{q_{gt}B^{obs}_{gt}}{Z}>0
\]
because \(q_{gt}>0\), \(B^{obs}_{gt}>0\), and \(Z>0\).

\item The weights sum to one by the definition of \(Z\):
\[
\sum_{(g,t)\in H}\omega_{gt}
=
\sum_{(g,t)\in H}\frac{q_{gt}B^{obs}_{gt}}{Z}
=
\frac{Z}{Z}
=
1,
\]
again using \(Z>0\).

\item Expanding the definition of the counterfactual-share target and using \(B^{obs}_{gt}>0\),
\[
PTT
=
\sum_{(g,t)\in H}\frac{q_{gt}B^{obs}_{gt}}{Z}
\left(\frac{m_{gt}}{B^{obs}_{gt}}-1\right)
=
\frac{\sum_{(g,t)\in H}q_{gt}m_{gt}}{Z}
-\frac{\sum_{(g,t)\in H}q_{gt}B^{obs}_{gt}}{Z}.
\]
The second fraction is \(1\), so
\[
PTT
=
\frac{\sum_{(g,t)\in H}q_{gt}m_{gt}}
{\sum_{(g,t)\in H}q_{gt}B^{obs}_{gt}}
-1.
\]

\item Finally suppose \(\Phi<0\). Step 1 gives \(\beta^\star(\delta)<0\). For \(PTT\), every treated cell has \(\omega_{gt}>0\), and \cref{obj:ass:strict-positive-effects} gives \(\delta_{gt}>0\), hence \(\exp(\delta_{gt})>1\) and \(\tau_{gt}>0\). Since \(H\) is nonempty, the finite sum defining \(PTT\) contains at least one strictly positive term and no negative terms. Therefore \(PTT>0\). Hence
\[
\Phi<0\quad\Longrightarrow\quad \beta^\star(\delta)<0<PTT .
\]
\end{enumerate}
\end{proof}

\begin{proof}[Proof of Four-Cohort Sign Reversal]
\begin{enumerate}
\item The defining conditions of the region in \cref{obj:def:global-sign-reversal-region} are checked directly for the displayed primitive.  The horizon condition is \(4\le 4\).  The support contains the never-treated cohort and the finite cohorts \(2,3,4\), all dated after period \(1\), and these four cohorts give the required four-cohort frontier scope.  The shares sum to
\[
\sum_{g\in\mathcal C}\pi_g=4\cdot \frac14=1,
\]
and, since \(\bar b_g=1\) and \(\gamma_{t0}=0\), the untreated mean representation is \(1=1\cdot \exp(0)\) in every supported cell.

For rank, let \(a\) be a collapsed parameter whose weighted quadratic design norm is zero.  Each summand is nonnegative and each supported cell mass is nonzero, so every collapsed index \(r_{gt}'a\) is zero.  Evaluating these zero equations first at the never-treated cohort in period \(1\) gives the intercept equal to zero; evaluating finite cohorts in period \(1\) gives all cohort dummy coordinates equal to zero; evaluating the never-treated cohort across periods gives all time dummy coordinates equal to zero; and evaluating the cohort \(2\), period \(2\), treated cell then gives the treatment coordinate equal to zero.  Hence \(a=0\), proving the collapsed design rank condition.

The sign condition is obtained from the primitive sign index \(\Phi\) in \cref{obj:def:frontier-elimination-handle}.  In the multiplier subfamily with common treated multiplier \(x\) off cell \((2,4)\) and multiplier \(y\) at \((2,4)\),
\[
\Phi=\frac{5x^2+12x-2y-15}{16}.
\]
Substituting \(x=101/100\) and \(y=4\) gives
\[
\Phi=-\frac{11559}{32000}<0.
\]
The sign characterization of the frontier index gives \(\beta^\star(\delta)<0\), and the restricted primitive has the same primitive treatment coordinate.  Together with the strict positivity of the treated effects verified in the next step, all clauses of \cref{obj:def:global-sign-reversal-region} hold.

\item If \(D_{gt}=1\), then the specified effect is either \(\log 4\) or \(\log(101/100)\).  Both are strictly positive because \(4>1\) and \(101/100>1\).

\item For the designated cell \((2,4)\), treatment is on and the effect is \(\delta_{2,4}=\log 4\).  For every other treated supported cell, the effect is \(\log(101/100)\).  Since \(101/100<4\) and the logarithm is strictly increasing on positive numbers,
\[
\log(101/100)<\log 4=\delta_{2,4}.
\]


\item At the zero-effect vector, the fitted mean is \(1\) in every supported cell by \cref{obj:prop:homogeneous-effect-reduction}.  Hence the mean weights in \cref{obj:def:weighted-fwl-residual} are all \(1/16\).  The displayed candidate residual table has row sums and column sums all equal to zero.  Moreover, treatment minus this table equals
\[
-\frac38+c_g+s_t,
\]
with
\[
(c_2,c_3,c_4,c_\infty)=\Bigl(\frac34,\frac12,\frac14,0\Bigr),
\qquad
(s_1,s_2,s_3,s_4)=\Bigl(0,\frac14,\frac12,\frac34\Bigr),
\]
so treatment minus the table lies in the nuisance fixed-effect space.  The zero row and column sums make the table orthogonal, under the constant weights \(1/16\), to every nuisance regressor and therefore to the whole nuisance space.  Thus the weighted projection of treatment onto the nuisance space is treatment minus the table, and the residual is the table.  This gives exactly
\[
\widetilde W_{gt}
=
\frac{1}{8}
\begin{pmatrix}
-3 & 3 & 1 & -1\\
-1 & -3 & 3 & 1\\
1 & -1 & -3 & 3\\
3 & 1 & -1 & -3
\end{pmatrix}_{gt}.
\]


\item Evaluating the residual table at the designated cell gives
\[
\widetilde W_{2,4}(0)=-\frac18.
\]


\item The residual energy at zero effects is
\[
\sum_{g,t} q_{gt}\,\mu^\star_{gt}(0)\,\widetilde W_{gt}(0)^2
=
\frac1{16}\sum_{g,t}\widetilde W_{gt}(0)^2
=
\frac1{16}\cdot\frac{80}{64}
=
\frac5{64}.
\]
\cref{obj:thm:sharp-ppml-forbidden-sign}, applied to the treated cell \((2,4)\), gives
\[
\left.\frac{d}{dx}\beta^\star(\delta_{2,4}=x,\delta_{gt}=0\text{ otherwise})\right|_{x=0}
=
\frac{q_{2,4}\,B_{2,4}\,\exp(0)\,\widetilde W_{2,4}(0)}
{5/64}.
\]
Here \(q_{2,4}=1/16\), \(B_{2,4}=1\), and \(\widetilde W_{2,4}(0)=-1/8\).  Therefore the derivative is
\[
\frac{(1/16)\cdot 1\cdot 1\cdot(-1/8)}{5/64}
=
-\frac{1}{10}.
\]


\item By continuity of the weighted FWL residual in the effect vector, \(\widetilde W_{2,4}(\delta)\) is continuous at the zero-effect vector.  Since \(\widetilde W_{2,4}(0)=-1/8<0\), the inverse image of \(( -\infty,0)\) is a neighborhood of zero.  Choose a finite coordinate neighborhood contained in that inverse image, choose a positive radius for each coordinate neighborhood, and let \(\varepsilon\) be the minimum of those radii, or \(1\) if the finite coordinate set is empty.

Now take any \(\delta'\) such that \(|\delta'_{gt}|<\varepsilon\) on every supported cell and \(\delta'_{gt}>0\) on every treated supported cell.  Define the supported truncation \(\delta^s\) by \(\delta^s_{gt}=\delta'_{gt}\) on \(g\in\mathcal C\) and \(\delta^s_{gt}=0\) outside the support.  The choice of \(\varepsilon\) puts \(\delta^s\) in the coordinate neighborhood, hence \(\widetilde W_{2,4}(\delta^s)<0\).  Changing effects outside supported cohorts leaves the limiting criterion, fitted means, and weighted FWL residuals unchanged, so \(\widetilde W_{2,4}(\delta')=\widetilde W_{2,4}(\delta^s)<0\).  Applying \cref{obj:thm:sharp-ppml-forbidden-sign} again at the treated cell \((2,4)\), the derivative of \(x\mapsto\beta^\star\) with the \((2,4)\) coordinate of \(\delta'\) replaced by \(x\), evaluated at \(x=\delta'_{2,4}\), has the same sign as \(\widetilde W_{2,4}(\delta')\), because the denominator and multiplicative prefactor are strictly positive.  Thus this derivative is strictly negative for every such strictly positive \(\delta'\).

\item The seven conclusions above are assembled in the order stated: region membership, positivity of treated effects, uniqueness of the largest treated effect at \((2,4)\), the full weighted FWL residual table, the late-cell residual \(-1/8\), the exact late-cell derivative at zero, and the local negative derivative statement under strict positivity of treated supported effects.
\end{enumerate}
\end{proof}
