\begin{abstract}
This paper studies the population treatment coefficient from pooling a staggered-adoption panel in a unit-and-time fixed-effect Poisson pseudo-likelihood. We show that this projection coefficient can be negative even when every cohort-time proportional treatment effect is positive. The failure reflects heterogeneous effects interacting with the fixed-effect PPML score: a four-cohort design with equal shares and flat untreated means provides an explicit sign reversal, while a positive-weight proportional treatment-on-the-treated target remains positive. The result characterizes the interpretation of the deterministic population projection targeted by the pooled criterion.
\end{abstract}

\section{Introduction}

Poisson pseudo-maximum likelihood with high-dimensional fixed effects is a standard way to estimate multiplicative mean models. It is especially common in gravity and other settings where the conditional mean is naturally proportional, zeros are empirically important, and fixed effects absorb large parts of the untreated outcome structure \citep{SantosSilvaTenreyro2006,SantosSilvaTenreyro2011,CorreiaGuimaraesZylkin2020}. At the same time, many policy applications have staggered adoption: some units are treated early, others later, and some never. In linear difference-in-differences, it is now well understood that a pooled two-way fixed-effect coefficient can fail to aggregate heterogeneous effects with interpretable positive weights \citep{GoodmanBacon2021,deChaisemartinDHaultfoeuille2020TWFE,CallawaySantAnna2021,SunAbraham2021,BorusyakJaravelSpiess2024}. This paper studies the corresponding issue for a different object: the treatment coordinate of a pooled fixed-effect PPML population projection when treatment effects are proportional rather than additive.

The object of interest is deliberately narrow. Consider a finite cohort-time staggered-adoption design with positive limiting cohort shares, an exponential untreated mean with unit and time components, within-cohort baseline limits, proportional cohort-time treatment effects, and a full-rank collapsed fixed-effect design. The paper defines \(\beta^\star(\delta)\) in \cref{obj:def:collapsed-population-projection} as the treatment coordinate of the limiting collapsed Poisson pseudo-likelihood projection. This is the population analogue of the coefficient an applied pooled unit-and-time fixed-effect PPML regression is trying to summarize. Its projection definition permits signed comparison weights and distinguishes it from causal average treatment effects built as convex aggregates of granular proportional effects.

The central question is whether the sign of this pooled PPML coefficient must agree with the signs of the underlying proportional effects. Sign reversal is possible. For any supported design satisfying the horizon, no-first-period-adopter, rank, and maintained population restrictions and whose cohort support contains \(\{2,3,4,\infty\}\), \cref{obj:thm:primitive-global-frontier} gives a primitive sign index \(\Phi\). Its sign is exactly the sign of \(\beta^\star(\delta)\). The theorem's closed-form polynomial calculation is a separate specialization to the exact four-cohort support \(\{2,3,4,\infty\}\). The general sign equivalence also shows that \(\Phi<0\) implies
\[
\beta^\star(\delta)<0<PTT,
\]
where \(PTT\) is the counterfactual-share proportional treatment-on-the-treated target. Thus the pooled fixed-effect PPML coefficient can have the opposite sign from every granular proportional effect while a positive-weight proportional target remains positive.

The mechanism is local as well as global. \Cref{obj:thm:sharp-ppml-forbidden-sign} shows that, under collapsed rank, the derivative of \(\beta^\star(\delta)\) with respect to a treated cell's log multiplier has the sign of the treatment indicator residual after projecting treatment on the fixed effects with weights \(q_{gt}\mu^\star_{gt}(\delta)\). These weights are generated by the fitted PPML mean through the pseudo-likelihood score and its curvature, producing a comparison geometry distinct from linear least squares. A treated cell with a negative weighted fixed-effect residual pushes the pooled coefficient downward when its proportional effect is increased. This is the multiplicative PPML analogue of a forbidden-comparison concern.

The paper also records the benchmark in which the pooled coefficient is well behaved. Under the same exponential untreated mean and collapsed rank conditions, if every treated cohort-time cell has the same log proportional effect \(\delta_0\), \cref{obj:prop:homogeneous-effect-reduction} shows that \(\beta^\star(\delta)=\delta_0\) and that the fitted collapsed mean equals the true collapsed mean in every cell. This calibration locates the sign problem in the interaction between heterogeneous proportional effects and their compression into one pooled treatment coordinate in a staggered-adoption design.

The explicit witness is intentionally simple. \Cref{obj:def:four-cohort-witness} considers four periods and four cohorts, \(\{2,3,4,\infty\}\), with equal cohort shares, flat untreated means, and strictly positive treated-cell log effects. All treated cells have multiplier \(101/100\) except cell \((2,4)\), which has multiplier \(4\). \Cref{obj:prop:four-cohort-sign-reversal} shows that this primitive belongs to the sign-reversal region in \cref{obj:def:global-sign-reversal-region}. The special four-cohort calculation in \cref{obj:thm:primitive-global-frontier} gives
\[
\Phi=\frac{5x^2+12x-2y-15}{16},
\]
and the witness has \(\Phi=-11559/32000\). Hence the negative coefficient occurs with equal shares, strictly positive effects, and flat untreated time components.

The distinction between the pooled coefficient and a positive proportional target is important for interpretation. Counterfactual-share proportional treatment-on-the-treated targets, such as those studied by \citet{MoreauKastler2025PTT}, aggregate granular proportional effects using positive exposure-based weights. Under strictly positive granular effects, those targets preserve the positive sign. The pooled fixed-effect PPML coefficient studied here is different: it is a pseudo-true projection coefficient in the sense of misspecified likelihood theory \citep{White1982MisspecifiedML,GourierouxMonfortTrognon1984Theory,GourierouxMonfortTrognon1984Poisson}. Its sign is governed by the fixed-effect fit and the induced score equation, not by positive aggregation weights.

The contribution is a sharp population diagnostic. It characterizes the deterministic projection target, derives its local and global sign formulas, and proves that under stated staggered-adoption and multiplicative-mean restrictions its sign can oppose every underlying proportional effect. These results identify the interpretation problem that granular-effect estimation and sampling inference must address in subsequent work.

The rest of the paper proceeds as follows. Section 2 relates the result to linear and nonlinear DiD, proportional treatment-on-the-treated targets, misspecified likelihood, and PPML applications. Section 3 defines the finite-array and collapsed population projections and the sign-reversal region. Section 4 gives the local derivative result, the homogeneous benchmark, the primitive sign frontier, and the four-cohort witness. Section 5 discusses interpretation and extensions. The appendix contains the collapse lemma, the pseudo-true projection lemma, proofs of the main results, and the verification note.
