% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_cic\_cl\_quantile\_nonequiv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_cic\_cl\_quantile\_nonequiv} / \texttt{v1}%
  \\ \large\textit{Curvature-timing sign reversal for staggered CIC and Callaway--Li QTT}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a free-form ExactID / staggered distributional DID proposal with tuple
\[
\begin{array}{ll}
\text{qid} & = \texttt{eid\_cic\_cl\_quantile\_nonequiv},\\
\text{specialization} & = \texttt{v1},\\
\text{graph / SWIG} & = \text{finite-cohort staggered adoption SWIG with cohorts }G\in\mathcal G,\\
\text{treatment} & = D_{it}=\one\{t\ge G_i\}\text{ and absorbing adoption time }G_i,\\
\text{target estimand} & =
  \Delta_h(\tau)=\sum_{g,t:g\le t}\omega_{gt}
  \left[Q_{h(Y_{it}(g)),g,t}(\tau)-Q^{0,\mathrm{CL}}_{h,g,t}(\tau)\right],\\
\text{identifying assumptions} & =
  \text{consistency, no anticipation, overlap, distributional DID,}\\
& \text{and the restrictions stated in Assumptions 1--7.}
\end{array}
\]
The comparator \(\Delta^{\mathrm{CIC}}_h(\tau)\) is the same aggregate except that
the untreated counterfactual quantile is built by the Athey--Imbens changes-in-changes
transport map before cohort aggregation.  The focal operational quantities are the
signed affine-invariant curvature-timing derivative \(S_h(P;\tau)\) and its
magnitude \(K_h(P;\tau)=|S_h(P;\tau)|\) in
Definition~\ref{def:curvature-timing}, both observable Gateaux derivative
functionals of the cohort-time marginal distributions and timing weights.

\begin{abstract}
This proposal asks when monotone transformations preserve the sign of staggered
quantile treatment effects on the treated computed by changes-in-changes and by
Callaway--Li-style group-time QTT formulas.  The kernel conjecture is that, even
when each cohort-time primitive satisfies the usual distributional DID and copula
conditions, staggered timing aggregation creates a signed affine-invariant
curvature-timing derivative \(S_h(P;\tau)\) whose opposition to the level-scale
margin can reverse the asymptotic sign of the transformed aggregate QTT.  This is a different pivot from an
equality frontier between CIC and Callaway--Li maps: it targets the transformation
class under which the sign and ordering of the resulting QTT reports are invariant.
The proposal also records a calibration theorem: under timing homogeneity, the
signed index vanishes and both routes recover the same joint point-identified group-time
QTT family after every increasing transformation.  Resolving the conjecture would
give applied staggered-QTT studies a concrete diagnostic for when reporting only
one outcome scale is misleading.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Distributional DID and QTT methods are used precisely when mean DID hides
heterogeneous distributional movements.  In that setting, the outcome scale is not
a cosmetic choice: an increasing transformation preserves ranks, but it need not
preserve differences between transformed quantiles after cohort-time aggregation.
The scientific question is therefore whether a staggered-QTT sign is a property of
the causal distribution or an artifact of combining timing weights, nonlinear
counterfactual recovery, and the chosen outcome scale.

\paragraph{The main finding (proposed).}
Conjecture~\ref{conj:curvature-frontier} proposes a sharp local transformation
frontier: on an open finite-support class, the transformed aggregate QTT keeps
the level-scale sign exactly when the independently computed signed derivative
\(S_r(P;\tau)\) does not oppose the level-scale margin strongly enough to cross
zero.  Conjecture~\ref{conj:witness} specializes this to a three-cohort,
three-period witness in which \(-\eta S_{y^2}(P;1/2)\) exceeds the margin and the
CIC and Callaway--Li aggregate reports have opposite asymptotic signs.

\paragraph{What is new.}
\citet[pp.~738--741 and Proposition~1]{RothSantAnna2023} characterize
functional-form sensitivity for mean DID parallel trends, while
\citet{AtheyImbens2006} motivate changes-in-changes by
scale-invariant nonlinear DID structure.  The proposed epsilon-gap is the
staggered-QTT signed curvature-timing derivative \(S_h(P;\tau)\): it is neither the
Athey--Imbens rank transport map nor the Roth--Sant'Anna mean-DID density
diagnostic, and it is visible only after cohort timing weights enter before
quantile subtraction.  \citet[Section~2 and the discussion of time-invariance
copula challenges]{LiLin2024} and \citet[Assumption~3 and Theorem~1]{CallawayLi2019}
supply the copula-based QTT route, but they do not classify which transformations
preserve or reverse staggered aggregate QTT signs.

\paragraph{How it positions in the literature.}
The proposal is an ExactID / distributional-DID proposal, not a linear panel
projection theorem.  It consumes the staggered group-time architecture of
\citet{CallawaySantAnna2021}, the nonlinear distributional recovery of
\citet{AtheyImbens2006}, and the QTT copula route of \citet{CallawayLi2019} and
\citet[Section~2]{LiLin2024}.  Its closest sensitivity comparator is
\citet[Proposition~1]{RothSantAnna2023}, but the target here is a quantile functional after
staggered timing aggregation rather than a mean parallel-trends condition.

\paragraph{Implications for the community.}
The concrete downstream consumer is the staggered-adoption QTT workflow of
\citet{LiLin2024}: a resolved curvature-timing theorem would tell users when their
group-invariance-copula QTT sign is stable to outcome transformations and when a
second scale must be reported.

\paragraph{How research benefits from the conclusion.}
Research practice changes as follows: staggered distributional-DID papers should
report \(S_h(P;\tau)\), \(K_h(P;\tau)\), or a certified zero-index condition
before interpreting the sign of an aggregate QTT as scale-robust.

\section{Related work}
\citet{AtheyImbens2006} is the CIC anchor: it identifies full counterfactual
distributions in a nonlinear DID model and emphasizes invariance of its assumptions
to outcome scaling.  \citet{CallawayLi2019} is the panel-QTT anchor: it combines
distributional DID with a time-invariance copula restriction for quantile treatment
effects.  \citet{CallawayLiOka2018} gives the two-period CQTT predecessor and
shows why a copula condition, not marginal distributional DID alone, is doing
identifying work for quantiles.  \citet[Section~2]{LiLin2024} is the closest staggered-QTT
paper: it generalizes QTT identification to staggered adoption under distributional
DID and group-invariance copulas and explicitly notes difficulties for the
Callaway--Li time-invariance copula route.  \citet{CallawaySantAnna2021} supplies
the group-time staggered-DID notation and aggregation logic that this proposal
uses for distributional objects.  \citet[pp.~738--741 and Proposition~1]{RothSantAnna2023} is the nearest
functional-form comparator because it proves that mean-DID parallel-trends
conclusions can depend on the outcome transformation; it does not study CIC/QTT
signs after quantile inversion and timing aggregation.  \citet{FernandezValMeierVanVuurenVella2024}
is adjacent distributional DID work connecting distributional effects with
doubly robust DID-style estimation; it is not a staggered CIC/Callaway--Li
non-equivalence theorem.  \citet{FanYu2012} gives a partial-ID
fallback for distributional and quantile DID when stronger restrictions fail,
which matters because a sign-reversal theorem should not be confused with a
failure of point identification.

In the project catalogue, \texttt{doc/API.md} reports no active ExactID or
PartialID entry duplicating a staggered-QTT transformation frontier.  The closest
banked in-repo prior attempt is \texttt{eid\_dist\_synth\_control\_v1}, whose
reviewer flagged that an Athey--Imbens / Callaway--Li comparison was only a
taxonomy and lacked a computable equality or separation test.  The current
proposal differs by making \(S_h(P;\tau)\), a transformation-specific operational
quantity, the focal separation object.  The banked
\texttt{pid\_qte\_marginal\_sensitivity\_v1} proposal is adjacent on quantile
partial identification, but its kernel is finite-tail CQTE certification under
marginal sensitivity rather than exact identification and transformation
invariance under staggered adoption.

\section{Formal setup}
There are finite adoption cohorts \(G\in\mathcal G\subset\{2,\ldots,T\}\), an
optional never-treated cohort \(G=\infty\), and absorbing treatment
\(D_{it}=\one\{t\ge G_i\}\).  For each cohort \(g\) and calendar time \(t\), let
\(Y_{it}(g)\) denote the potential outcome under adoption at \(g\), and
\(Y_{it}(\infty)\) the untreated potential outcome.  The observed law is \(P\)
over \((Y_{i1},\ldots,Y_{iT},G_i)\), with known cohort shares
\(\pi_g=\Pr(G=g)\) and aggregation weights \(\omega_{gt}\ge0\) summing to one
over treated cohort-time cells \(g\le t\).

For a strictly increasing twice continuously differentiable transformation \(h\),
write \(F^0_{h,g,t}\) for the counterfactual CDF of \(h(Y_{it}(\infty))\) for
cohort \(g\) at time \(t\), \(Q^0_{h,g,t}(\tau)=\inf\{y:F^0_{h,g,t}(y)\ge\tau\}\),
and \(Q_{h(Y),g,t}(\tau)=\inf\{y:\Pr(h(Y_{it})\le y\mid G=g)\ge\tau\}\).
The Callaway--Li route \(F^{0,\mathrm{CL}}_{h,g,t}\) uses distributional DID plus
the cohort-copula restriction in Assumption~\ref{ass:copula}; the CIC route
\(F^{0,\mathrm{CIC}}_{h,g,t}\) uses the Athey--Imbens monotone transport from
baseline to follow-up untreated distributions.  The aggregate QTT reports are
\[
\Delta^{m}_h(\tau)=\sum_{g,t:g\le t}\omega_{gt}
\{Q_{h(Y_{it}),g,t}(\tau)-Q^{0,m}_{h,g,t}(\tau)\},
\qquad m\in\{\mathrm{CL},\mathrm{CIC}\}.
\]
Let \(q_{gt}(\tau)=Q^0_{\mathrm{id},g,t}(\tau)\), let
\(Q_{Y,g,t}(\tau)=Q_{\mathrm{id}(Y),g,t}(\tau)\), let
\(s_{gt}(\tau)=Q_{Y,g,t}(\tau)-Q^0_{\mathrm{id},g,t}(\tau)\), and define the
group-time QTT \(QTT_{h,g,t}(\tau)=Q_{h(Y),g,t}(\tau)-Q^0_{h,g,t}(\tau)\) and the
signed level-scale margin
\[
M(P;\tau)=\left|\sum_{g,t}\omega_{gt}s_{gt}(\tau)\right|.
\]

\begin{definition}[Signed affine-invariant curvature-timing derivative]\label{def:curvature-timing}
For a local transformation path \(h_\eta(y)=y+\eta r(y)\) with \(r'\!>-1/\eta\),
let \(r^\perp\) be the residual after subtracting the unique affine function that
agrees with \(r\) at the two endpoints of the convex hull of
\(\{q_{gt}(\tau),Q_{Y,g,t}(\tau):\omega_{gt}>0\}\).  Define
\[
S_r(P;\tau)=
\sum_{g,t}\omega_{gt}
\left\{r^\perp(Q_{Y,g,t}(\tau))-r^\perp(q_{gt}(\tau))\right\}
-\sum_t\bar\omega_t
\left\{r^\perp(Q_{Y,\bar G,t}(\tau))-r^\perp(q_{\bar Gt}(\tau))\right\},
\qquad
K_r(P;\tau)=|S_r(P;\tau)|,
\]
where \(\bar\omega_t=\sum_g\omega_{gt}\), and \(Q_{Y,\bar G,t}(\tau)\) and
\(q_{\bar Gt}(\tau)\) are the observed and untreated counterfactual quantiles in
the timing-homogeneous mixture obtained by replacing
\(\Pr(G=g\mid t,g\le t)\) with the baseline cohort share \(\pi_g\).  For a fixed
\(h\), \(S_h(P;\tau)\) and \(K_h(P;\tau)\) denote the same expressions with
\(r=h-\mathrm{id}\).  Thus every affine transformation has \(S_h=K_h=0\) by
construction.
\end{definition}

\begin{verbatim}
qid = eid_cic_cl_quantile_nonequiv
specialization = v1
graph / SWIG = finite-cohort staggered adoption SWIG with absorbing D_it=1{t>=G_i}
treatment = adoption time G_i and group-time treated cells (g,t), g<=t
target estimand = Delta_h(tau), the omega-weighted staggered QTT aggregate
identifying assumptions = consistency, no anticipation, overlap,
  distributional DID, cohort-copula stability, and timing homogeneity when invoked
bounding functional = none; this is exact identification, with signed S_h(P;tau)
  and magnitude K_h(P;tau) as operational diagnostics
\end{verbatim}

\section{Assumptions}
\begin{assumption}[Finite staggered support]\label{ass:finite}
\(\mathcal G\) and \(T\) are finite, \(\Pr(G=g)>0\) for each cohort used in the
aggregate, and every treated cell \((g,t)\) with \(\omega_{gt}>0\) has an
available comparison risk set with positive probability.
\end{assumption}

\begin{assumption}[Consistency and no anticipation]\label{ass:consistency}
The observed outcome equals the potential outcome generated by the realized
adoption time, and for \(t<g\), \(Y_{it}(g)=Y_{it}(\infty)\).
\end{assumption}

\begin{assumption}[Distributional DID]\label{ass:ddid}
For each \((g,t)\) entering the aggregate, the untreated counterfactual marginal
distribution for cohort \(g\) at \(t\) is identified by the distributional DID
restriction relative to the comparison risk set specified in the locked design.
\end{assumption}

\begin{assumption}[Cohort-copula stability]\label{ass:copula}
The copula linking baseline untreated ranks and follow-up untreated ranks is
stable across the comparison risk set used to identify \(F^{0,\mathrm{CL}}_{h,g,t}\).
\end{assumption}

\begin{assumption}[Regular quantiles and transformations]\label{ass:regular}
All CDFs used in the proposal are continuous and strictly increasing in a
neighborhood of the \(\tau\)-quantiles, with densities bounded away from zero
there.  The transformation \(h\) is strictly increasing and twice continuously
differentiable on the convex hull of the relevant quantile support.
\end{assumption}

\begin{assumption}[Timing homogeneity]\label{ass:timing-homogeneity}
For every calendar time \(t\), the distribution of untreated rank evolution and
the transformed treated-minus-counterfactual quantile increment do not depend on
the adoption cohort \(g\) among cohorts at risk at \(t\).  In primitive terms,
the baseline-to-\(t\) untreated rank-transition law and the treated quantile
increment \(s_{gt}(\tau)\) are functions of \(t\) and \(\tau\) only, not of \(g\).
\end{assumption}

\begin{assumption}[Margin-normalized local path]\label{ass:margin}
For the flagship local-transformation statement, the path \(h_\eta(y)=y+\eta r(y)\)
satisfies \(0<\eta\le \eta_{\max}(r,P)\), where \(\eta_{\max}(r,P)\) is the
largest value preserving strict monotonicity on the support of \(P\).  The
level-scale margin satisfies \(M(P;\tau)>0\), and the active path is restricted
to \(\eta K_r(P;\tau)\le 2M(P;\tau)\).  The sign-frontier claim additionally
requires the opposition condition
\[
\operatorname{sign}\!\left(\sum_{g,t}\omega_{gt}s_{gt}(\tau)\right)S_r(P;\tau)<0,
\]
so magnitude \(K_r\) is never used without the signed derivative \(S_r\).
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: timing-homogeneous joint QTT recovery]\label{thm:timing-homogeneous}
Under Assumptions~\ref{ass:finite}--\ref{ass:regular} and
Assumption~\ref{ass:timing-homogeneity}, for every strictly increasing \(h\) and
every regular \(\tau\), \(F^{0,\mathrm{CL}}_{h,g,t}=F^{0,\mathrm{CIC}}_{h,g,t}\)
for all treated cells \((g,t)\), \(S_h(P;\tau)=K_h(P;\tau)=0\), and the joint family
\(\{QTT_{h,g,t}(\tau):g\le t\}\) is point identified by either route.
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) \citet{AtheyImbens2006} and \citet{CallawayLi2019} identify counterfactual
distributions under different nonlinear restrictions, and \citet{LiLin2024}
studies staggered QTT under group-invariance copulas; none states the
timing-homogeneous corner as a joint equality of the CIC and Callaway--Li
group-time QTT families after arbitrary increasing transformations.  The gap is
the explicit zero-index calibration needed before the sign-reversal conjecture is
well posed.  (b) The consumer is \citet{LiLin2024}: this theorem would provide the
clean diagnostic case in which their staggered QTT reports are scale-stable rather
than merely point identified.

\begin{conjecture}[Conjecture 1: curvature-timing sign frontier (NOT YET PROVED)]\label{conj:curvature-frontier}
Under Assumptions~\ref{ass:finite}--\ref{ass:margin}, there is an open
finite-support class \(\mathcal P_{\mathrm{ct}}\) such that, for each
\(P\in\mathcal P_{\mathrm{ct}}\), each local path \(h_\eta(y)=y+\eta r(y)\), and
each fixed \(0<\eta\le\eta_{\max}(r,P)\),
\[
\operatorname{sign}\Delta^{\mathrm{CL}}_{h_\eta}(\tau)
=\operatorname{sign}\Delta^{\mathrm{CL}}_{\mathrm{id}}(\tau)
\]
if and only if
\[
\left|\sum_{g,t}\omega_{gt}s_{gt}(\tau)+\eta S_r(P;\tau)\right|>0
\quad\text{and this sum has the original level-scale sign.}
\]
Equivalently, under the opposition condition in Assumption~\ref{ass:margin},
sign reversal occurs exactly when \(\eta K_r(P;\tau)>M(P;\tau)\).  Every
group-time counterfactual CDF remains point identified on both sides of the
frontier.
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest paper is \citet{RothSantAnna2023}, which gives a functional-form
sensitivity diagnostic for mean DID parallel trends.  The epsilon-gap is that
Conjecture~\ref{conj:curvature-frontier} concerns the sign of an identified
staggered quantile aggregate and names the independent operational quantity
\(S_r(P;\tau)\), whose magnitude \(K_r(P;\tau)\) combines transformation
curvature with timing weights before quantile subtraction.  \citet{AtheyImbens2006} supplies scale-invariant CIC
motivation, but not a staggered aggregation sign frontier.  (b) The consumer is
the \texttt{didFF} / Roth--Sant'Anna functional-form workflow: resolving the
conjecture would give the analogous diagnostic target for staggered QTT studies,
with \(S_r(P;\tau)\) and \(K_r(P;\tau)\) replacing a mean-trend density check.

\begin{conjecture}[Conjecture 2: three-cohort CIC/CL opposite-sign witness (NOT YET PROVED)]\label{conj:witness}
There exists a concrete three-period, three-cohort finite-support law satisfying
Assumptions~\ref{ass:finite}--\ref{ass:regular} but not
Assumption~\ref{ass:timing-homogeneity}, with support points
\(\{0,1,3,4,8\}\), treated-cell weights
\(\omega_{22}=\omega_{33}=1/4\) and \(\omega_{23}=1/2\), and transformation
\(h_\eta(y)=y+\eta y^2\) at \(\eta=1/10\), such that
\[
\Delta^{\mathrm{CIC}}_{h_\eta}(\tau)>0
\quad\text{and}\quad
\Delta^{\mathrm{CL}}_{h_\eta}(\tau)<0
\]
at \(\tau=1/2\).  The inequalities persist under all sufficiently small
perturbations of the displayed atom probabilities that preserve the cohort-time
rank ordering and the sign condition \(\eta K_{y^2}(P;1/2)>M(P;1/2)\) with
\(\operatorname{sign}(\sum\omega s)S_{y^2}(P;1/2)<0\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) \citet[Section~2, final paragraph]{LiLin2024} flags the staggered
Callaway--Li copula route as delicate,
and the banked \texttt{eid\_dist\_synth\_control\_v1} review noted that prior
CausalSmith text only asserted an Athey--Imbens / Callaway--Li comparison without
a computable separation test.  The epsilon-gap here is a non-degenerate
finite-support witness with named moments \(S_{y^2}(P;1/2)\) and
\(K_{y^2}(P;1/2)\) that produce
opposite signs, rather than another taxonomy of assumptions.  (b) The consumer is
\citet[abstract and identification section]{MillerGalvao2026}: a doubly robust staggered-QTT estimator needs to know
whether its target sign is invariant to outcome scale or can flip across two
published identification maps.

\section{Sanity-check corollaries}
\begin{corollary}[Two-period no-staggering reduction]\label{cor:two-period}
When \(|\mathcal G|=1\), \(T=2\), and Assumption~\ref{ass:timing-homogeneity}
holds, \(S_h(P;\tau)=K_h(P;\tau)=0\) and the proposal reduces to the standard
Athey--Imbens / Callaway--Li two-period counterfactual quantile equality whenever
their respective rank and copula restrictions coincide.
\end{corollary}

\begin{corollary}[Affine transformations]\label{cor:affine}
If \(h(y)=a+by\) with \(b>0\), then \(S_h(P;\tau)=K_h(P;\tau)=0\) and the sign of every
aggregate QTT report is preserved: \(\operatorname{sign}\Delta^m_h(\tau)=
\operatorname{sign}\Delta^m_{\mathrm{id}}(\tau)\) for
\(m\in\{\mathrm{CL},\mathrm{CIC}\}\).
\end{corollary}

\begin{example}[Concrete non-corner witness target]\label{ex:three-cohort-witness}
The finite-support witness in Conjecture~\ref{conj:witness} should be checked on
the following explicit median cells.  Conditional on each treated cell, the
untreated counterfactual law \(P^0_{gt}\) and observed treated law \(P^Y_{gt}\)
on support \((0,1,3,4,8)\) are
\[
\begin{array}{c|cc|cc}
(g,t) & P^0_{gt}(0,1,3,4,8) & P^Y_{gt}(0,1,3,4,8) & q_{gt}(1/2) & Q_{Y,g,t}(1/2)\\
\hline
(2,2) & (.10,.46,.34,.06,.04) & (.10,.20,.40,.20,.10) & 1 & 3\\
(2,3) & (.08,.18,.22,.01,.51) & (.10,.45,.25,.10,.10) & 8 & 1\\
(3,3) & (.12,.44,.32,.08,.04) & (.10,.20,.42,.18,.10) & 1 & 3
\end{array}
\]
with the timing-homogeneous barred medians fixed at
\((q_{\bar G2},Q_{Y,\bar G,2})=(1,3)\) and
\((q_{\bar G3},Q_{Y,\bar G,3})=(3,4)\).  These displayed probabilities are not
a proof of attainability by the full latent rank process; they are the concrete
non-corner target for the witness construction.  Direct median arithmetic gives
\[
\Delta^{\mathrm{CL}}_{\mathrm{id}}(1/2)=1/4,\qquad
S_{y^2}(P;1/2)=-7,\qquad
K_{y^2}(P;1/2)=7,
\]
so at \(\eta=1/10\), \(\eta K_{y^2}=.7>M=.25\) and the signed derivative points
against the level-scale margin.  The CIC side of the witness is required to
produce \(\Delta^{\mathrm{CIC}}_{h_\eta}(1/2)>0\) from the same observed law by
the Athey--Imbens transport map, giving the promised CIC/CL opposite-sign
separation.
\end{example}

\section{Proof-sketch route}
The mathematical route is to write both counterfactual CDF constructions as
monotone transport maps and then apply the ordinary quantile transformation rule
\(Q_{h(Y)}(\tau)=h(Q_Y(\tau))\) cell by cell.  Theorem~\ref{thm:timing-homogeneous}
should follow by showing that timing homogeneity makes the cohort-time transport
maps identical before aggregation, so the barred and unbarred terms in
Definition~\ref{def:curvature-timing} cancel.  For
Conjecture~\ref{conj:curvature-frontier}, expand
\(\Delta^{\mathrm{CL}}_{h_\eta}(\tau)\) around \(\eta=0\); the derivative is the
signed curvature-timing functional \(S_r(P;\tau)\), while \(K_r(P;\tau)\) records
only its magnitude.  Under the opposition condition, the boundary is the first
point at which \(\eta K_r(P;\tau)\) dominates the independently defined
level-scale margin \(M(P;\tau)\).  For Conjecture~\ref{conj:witness}, enumerate
the three-cohort finite support in Example~\ref{ex:three-cohort-witness}, compute
the CIC and Callaway--Li counterfactual median maps explicitly, and verify the
strict inequalities; openness then follows from continuity of regular quantiles
and strict inequalities under small probability perturbations.

\section{Honest scope flags}
Theorem~\ref{thm:timing-homogeneous} is intended as routine algebra once the
published CIC and Callaway--Li restrictions are specialized to timing
homogeneity.  Conjectures~\ref{conj:curvature-frontier} and \ref{conj:witness}
are not yet proved and are the novel kernel.  The largest risk is that
\(S_r(P;\tau)\) as defined above captures only the first-order local
transformation path, so the full ``for all \(0<\eta\le\eta_{\max}\)'' frontier
may need to be narrowed to sufficiently small \(\eta\).  A second risk is whether
the proposed three-cohort support \(\{0,1,3,4,8\}\) is the cleanest concrete
witness; the proposal only commits to a non-degenerate finite-support witness
with open perturbations, not to this atom set being minimal.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (pivot) -- initial draft for the structurally different
functional-form / curvature-timing angle; prior verdict: none.
\item v2 (revise) -- replaced unsigned \(K_r\) with signed affine-invariant
\(S_r\), added location anchors and a concrete finite-support witness target,
fixed the affine sanity check and citation metadata; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Athey and Imbens(2006)]{AtheyImbens2006}
Athey, S. and G. W. Imbens (2006).
Identification and inference in nonlinear difference-in-differences models.
\emph{Econometrica} 74(2), 431--497.

\bibitem[Callaway and Li(2019)]{CallawayLi2019}
Callaway, B. and T. Li (2019).
Quantile treatment effects in difference in differences models with panel data.
\emph{Quantitative Economics} 10(4), 1579--1618.

\bibitem[Callaway, Li, and Oka(2018)]{CallawayLiOka2018}
Callaway, B., T. Li, and T. Oka (2018).
Quantile treatment effects in difference in differences models under dependence
restrictions and with only two time periods.
\emph{Journal of Econometrics} 206(2), 395--413.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and P. H. C. Sant'Anna (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics} 225(2), 200--230.

\bibitem[Fernandez-Val, Meier, van Vuuren, and Vella(2024)]{FernandezValMeierVanVuurenVella2024}
Fernandez-Val, I., A. Meier, A. van Vuuren, and F. Vella (2024).
Doubly robust difference-in-differences estimators for distributional treatment
effects.
Working paper.

\bibitem[Fan and Yu(2012)]{FanYu2012}
Fan, Y. and Z. Yu (2012).
Partial identification of distributional and quantile treatment effects in
difference-in-differences models.
\emph{Economics Letters} 115(3), 511--515.

\bibitem[Li and Lin(2024)]{LiLin2024}
Li, X. and L. Lin (2024).
Identification of quantile treatment effects in difference-in-differences
settings with staggered adoption.
\emph{Economics Letters} 241, 111792.

\bibitem[Miller and Galvao(2026)]{MillerGalvao2026}
Miller, B. and A. F. Galvao (2026).
Doubly-robust quantile treatment effects with staggered interventions.
SSRN working paper.

\bibitem[Roth and Sant'Anna(2023)]{RothSantAnna2023}
Roth, J. and P. H. C. Sant'Anna (2023).
When is parallel trends sensitive to functional form?
\emph{Econometrica} 91(2), 737--747.
\end{thebibliography}

\end{document}
