% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=eid\_cic\_cl\_quantile\_nonequiv, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` -- the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{eid\_cic\_cl\_quantile\_nonequiv} / \texttt{v1}%
  \\ \large\textit{Sharp CIC--Callaway--Li non-equivalence for staggered group-time QTT via a timing-skew moment}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form exact-identification anchor with tuple
\[
(\texttt{qid},\texttt{specialization},\text{SWIG},\text{treatment},\text{target estimand},\text{identifying assumptions}).
\]
Here \(\texttt{qid}=\texttt{eid\_cic\_cl\_quantile\_nonequiv}\) and \(\texttt{specialization}=\texttt{v1}\). The SWIG is the staggered-adoption panel SWIG generated by first treatment time \(G\in\mathcal G\cup\{\infty\}\), absorbing treatment path \(D_{it}=\one\{t\geq G_i\}\), and potential outcomes \(\{Y_{it}(g):g\in\mathcal G\cup\{\infty\},t=0,\ldots,T\}\). The treatment is adoption at cohort \(g\) evaluated at post-adoption calendar time \(t\geq g\). The target estimands are the group-time counterfactual CDF \(F^0_{g,t}\), the group-time quantile treatment contrast \(QTT_{g,t}(\tau)=Q_{Y_t(g)\mid G=g}(\tau)-Q_{Y_t(\infty)\mid G=g}(\tau)\), and the paired plug-in signs \(S^{CIC}_{g,t}(\tau)=\operatorname{sgn}\{Q_{Y_t(g)\mid G=g}(\tau)-Q^{CIC,0}_{g,t}(\tau)\}\) and \(S^{CL}_{g,t}(\tau)=\operatorname{sgn}\{Q_{Y_t(g)\mid G=g}(\tau)-Q^{CL,0}_{g,t}(\tau)\}\). The baseline identifying assumptions are finite support, overlap of the risk-set controls, continuity and strict monotonicity of all CDFs at \(\tau\), stable-rank changes-in-changes for the CIC counterfactual, and conditional copula stability for the Callaway--Li counterfactual; timing homogeneity is imposed only for the recovery corollary, not for the non-equivalence conjectures. The focal operational quantities are the independently defined timing-skew moment \(\mathfrak M_{g,t,\tau}(P)\) in Definition~\ref{def:timing-skew} and the independently defined copula-transport imbalance \(\mathfrak C^{\Pi}_{g,t,\tau}(P)\) in Definition~\ref{def:copula-imbalance}, not thresholds or residuals defined by agreement of the two estimators.

\begin{abstract}
This proposal asks when the Athey--Imbens changes-in-changes counterfactual and the Callaway--Li panel quantile DID counterfactual agree for group-time QTT in staggered adoption. The proposed kernel is a necessary-and-sufficient finite-support equivalence conjecture: the two counterfactual quantiles agree for every cohort-time cell exactly when a named timing-skew moment and an independently defined local copula-transport imbalance both vanish. The same pair of operational quantities is conjectured to generate an open class of non-degenerate observable laws on which the CIC and Callaway--Li plug-in QTT signs are opposite at a fixed quantile. If true, the result would turn Li--Lin's abstract and concluding warning about staggered Callaway--Li copula extensions into a computable diagnostic and would give joint point identification of group-time and aggregate QTT under timing homogeneity. The proposal is honest about status: the two-period reduction is a routine theorem, while the finite-support iff and open-set sign-reversal statements remain conjectures.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Distributional DID methods are now used when the mean ATT is too coarse, but the staggered-adoption QTT literature has two incompatible-looking primitives. \citet{AtheyImbens2006} identifies counterfactual distributions through rank-stable nonlinear changes, while \citet{CallawayLi2019} identifies panel QTT through a copula restriction on untreated outcome changes. \citet{LiLin2024} explicitly flags that carrying the Callaway--Li copula route into staggered timing is delicate, and applied users need to know whether the CIC-style counterfactual and the panel-copula counterfactual are interchangeable or can reverse the sign of a group-time QTT.

\paragraph{The main finding (proposed).}
The headline conjecture is that, on finite support with continuous interpolation, CIC and Callaway--Li identify the same \(QTT_{g,t}(\tau)\) for all supported \((g,t,\tau)\) if and only if the timing-skew moment \(\mathfrak M_{g,t,\tau}(P)\) and the local copula-transport imbalance \(\mathfrak C^{\Pi}_{g,t,\tau}(P)\) both vanish. When \(\mathfrak M_{g,t,\tau}(P)+\mathfrak C^{\Pi}_{g,t,\tau}(P)\) has the opposite sign to the local quantile slope and is bounded away from zero by the curvature constant in Assumption~\ref{ass:margin}, the two plug-in QTT signs are conjectured to be opposite on an open set of observable laws.

\paragraph{What is new.}
The novelty is not another sufficient assumption for staggered QTT. The proposed object is a comparator frontier between two named published identification workflows: the CIC rank-map of \citet[Sections 2--3, especially the counterfactual-distribution construction around their equations (2.4)--(2.6)]{AtheyImbens2006} and the panel-copula QTT map of \citet[Sections 2--3, especially the copula/time-invariance restrictions defining their counterfactual change distribution]{CallawayLi2019}, in the staggered setting highlighted by \citet[abstract and concluding discussion]{LiLin2024}. The epsilon-gap is the pair \((\mathfrak M_{g,t,\tau}(P),\mathfrak C^{\Pi}_{g,t,\tau}(P))\): existing papers either impose a single treatment time, impose a copula restriction within a two-period architecture, or define staggered group-time QTT under a stronger group-invariance route, but none gives a necessary-and-sufficient equality test or an open-class sign reversal between the CIC and Callaway--Li counterfactual quantiles.

\paragraph{How it positions in the literature.}
This is an exact-identification proposal with panel-DID primitives. It is adjacent to the group-time architecture of \citet{CallawaySantAnna2021} and the staggered-estimator diagnostic tradition of \citet{GoodmanBacon2021}, \citet{SunAbraham2021}, and \citet{deChaisemartinDHaultfoeuille2020}, but its estimand is distributional rather than a linear mean contrast. It also touches partial-ID work by \citet{FanYu2012}, because failure of both rank and copula restrictions should move the problem to bounds; here the question is sharper, asking for the exact boundary at which two point-ID restrictions collapse to the same QTT.

\paragraph{Implications for the community.}
The direct consumer is \citet{LiLin2024}: their staggered QTT framework would gain a computable test for when the Callaway--Li time-invariance route can be treated as equivalent to CIC, and when it can instead flip the sign of a group-time QTT. A secondary consumer is applied minimum-wage or policy-adoption work using the Callaway--Sant'Anna group-time architecture, because the result would say which timing moment must be reported before interpreting a staggered QTT sign.

\paragraph{How research benefits from the conclusion.}
Researchers should report \(\mathfrak M_{g,t,\tau}(P)\) and \(\mathfrak C^{\Pi}_{g,t,\tau}(P)\) before treating CIC and panel-copula QTT estimates as concordant evidence.

\section{Related work}
\citet{AtheyImbens2006} is the CIC anchor: Sections 2--3 define a nonlinear DID counterfactual distribution from stable ranks and monotone outcome transformations. \citet{CallawayLi2019} is the panel-QTT anchor: Sections 2--3 combine distributional DID with a time-invariance copula restriction to recover the untreated change distribution and identify QTT. \citet{CallawayLiOka2018} identifies conditional QTT in a two-period setting using distributional DID plus a dependence restriction, making it the closest two-period copula predecessor. \citet{LiLin2024} is the staggered-adoption trigger: its abstract and concluding discussion extend QTT identification to staggered timing under distributional DID and group-invariance copula restrictions while noting difficulty with the Callaway--Li time-invariance route. \citet{FanYu2012} gives partial-identification bounds for distributional and quantile DID when point-ID dependence restrictions are not maintained, which is the fallback regime if the equivalence frontier fails. \citet{CallawaySantAnna2021} supplies the group-time DID estimand architecture used to index \(QTT_{g,t}(\tau)\). \citet{GoodmanBacon2021}, \citet{SunAbraham2021}, and \citet{deChaisemartinDHaultfoeuille2020} show that staggered timing and heterogeneity can contaminate linear mean DID estimators; this proposal uses them only as a diagnostic analogy and anchors the nonlinear QTT sign wedge to the Athey--Imbens, Callaway--Li, and Li--Lin counterfactual workflows. \citet{RothSantAnna2023} shows that DID conclusions can be sensitive to functional form, which is relevant because CIC is transformation-aware while QTT signs after timing aggregation need not be.

In-repo prior art is thin for this exact kernel. The Stage -1.1 catalogue scan reports no active proposal text for \texttt{eid\_cic\_cl\_quantile\_nonequiv}. The closest failed quantile proposal is \texttt{eid\_dist\_synth\_control\_v1}, whose reviewer record cited \citet{AtheyImbens2006}, \citet{CallawayLi2019}, and \citet{FanYu2012} but found only a taxonomy and a plug-in threshold diagnostic, not a computable equality or separation theorem. The closest panel non-equivalence catalogue entries are \texttt{q\_did\_drdid\_ipwdid\_frontier\_v1} and \texttt{panel\_sdid\_mc\_id\_v1}; their kernels concern mean DID or synthetic DID estimator frontiers, not nonlinear counterfactual CDFs or group-time QTT.

\section{Formal setup}
Let \(i=1,\ldots,n\), \(t=0,\ldots,T\), and \(G_i\in\mathcal G\cup\{\infty\}\) denote first treatment time, with absorbing treatment \(D_{it}=\one\{t\geq G_i\}\). For each \(g\in\mathcal G\) and \(t\geq g\), let \(Y_{it}(g)\) be the potential outcome under adoption at \(g\), and let \(Y_{it}(\infty)\) be the never-treated potential outcome. Observed outcomes satisfy \(Y_{it}=Y_{it}(G_i)\). The observable law \(P\) consists of the joint distribution of \((Y_0,\ldots,Y_T,G,X)\), with \(X\) omitted from notation except when conditioning is needed.

For a cohort \(g\), post time \(t\), and quantile index \(\tau\in(0,1)\), define
\[
F^1_{g,t}(y)=\Pr(Y_t\leq y\mid G=g),\qquad
F^0_{g,t}(y)=\Pr(Y_t(\infty)\leq y\mid G=g),
\]
and \(Q^a_{g,t}(\tau)=\inf\{y:F^a_{g,t}(y)\geq\tau\}\). The target contrast is
\[
QTT_{g,t}(\tau)=Q^1_{g,t}(\tau)-Q^0_{g,t}(\tau).
\]
Let \(\mathcal R_{g,t}=\{h\in\mathcal G\cup\{\infty\}:h>t\}\) be the not-yet-treated risk set for the \((g,t)\) comparison, with weights \(\omega_{h\mid g,t}=\Pr(G=h\mid G\in\mathcal R_{g,t})\).
For any supported cohort \(h\), let \(F_{h,s}\) and \(Q_{h,s}\) denote the observed CDF and quantile function of \(Y_s\mid G=h\), and let \(Q_{\mathcal R,s}\) denote the quantile function of the risk-set mixture \(F_{\mathcal R,s}\). The baseline timing weights \(\omega^0_{h\mid g,t}\) are the same risk-set probabilities computed in the pre-period comparison population at time \(g-1\). The cohort, calendar, and overall aggregate QTTs are fixed-weight averages of \(QTT_{g,t}(\tau)\) over supported \((g,t)\) cells, with weights equal to observable cohort shares among treated observations; these are denoted \(QTT_g(\tau)\), \(QTT_t(\tau)\), and \(QTT^{agg}(\tau)\).

The CIC counterfactual CDF for \((g,t)\) is
\[
F^{CIC,0}_{g,t}(y)
  = F_{g,g-1}\!\left(F^{-1}_{\mathcal R,g-1}\!\left(F_{\mathcal R,t}(y)\right)\right),
\]
where \(F_{\mathcal R,s}=\sum_{h\in\mathcal R_{g,t}}\omega_{h\mid g,t}F_{h,s}\). The Callaway--Li counterfactual quantile map \(Q^{CL,0}_{g,t}(\tau)\) is the \(\tau\)-quantile generated by the untreated-change distribution for cohort \(g\) recovered from the conditional copula of \((Y_{g-1}(\infty),Y_t(\infty)-Y_{g-1}(\infty))\) over the risk set. Its induced CDF is denoted \(F^{CL,0}_{g,t}\).

Define the local CIC rank transport at \((g,t,\tau)\) by
\[
T^{CIC}_{g,t,\tau}(u)=F_{g,g-1}\!\left(F^{-1}_{\mathcal R,g-1}(u)\right)
\quad\text{for }u\text{ in a neighborhood }I_\tau\text{ of the target rank.}
\]
Let \(\Pi^{CL}_{g,t}\) be the Callaway--Li conditional copula law of baseline rank and untreated-change rank for the risk set, and let \(\Pi^{rank}_{g,t}\) be the rank-preserving copula law induced by the CIC transport. Let \(\psi_{g,t,\tau}\) be the local inverse-CDF derivative weight fixed by Assumption~\ref{ass:regularity}. The local copula-transport imbalance is
\[
\mathfrak C^{\Pi}_{g,t,\tau}(P)
  =
  \int_{I_\tau}\psi_{g,t,\tau}(u)\,d\{\Pi^{CL}_{g,t}-\Pi^{rank}_{g,t}\}(u).
\]
This is a primitive functional of the two local copula laws and the quantile-density weight; it is not defined using \(Q^{CL,0}_{g,t}(\tau)-Q^{CIC,0}_{g,t}(\tau)\).

\begin{definition}[Timing-skew moment]\label{def:timing-skew}
For a fixed \((g,t,\tau)\), define the timing-skew moment
\[
\mathfrak M_{g,t,\tau}(P)
  =
  \sum_{h\in\mathcal R_{g,t}}\omega_{h\mid g,t}
  \left[
    \{Q_{h,t}(\tau)-Q_{h,g-1}(\tau)\}
    -
    \{Q_{\mathcal R,t}(\tau)-Q_{\mathcal R,g-1}(\tau)\}
  \right]
  \left(\omega_{h\mid g,t}-\omega^0_{h\mid g,t}\right),
\]
where \(\omega^0_{h\mid g,t}\) is the baseline risk-set weight at \(g-1\). This quantity is computed from risk-set marginal quantiles and timing weights; it is not defined by equality or inequality of the CIC and Callaway--Li estimators.
\end{definition}

Locked-parameter reproduction:
\[
\begin{gathered}
\texttt{qid}=\texttt{eid\_cic\_cl\_quantile\_nonequiv},\quad
\texttt{specialization}=\texttt{v1},\\
\text{SWIG}=(G,D_{0:T},Y_{0:T}(g),Y_{0:T}(\infty)),\quad
\text{treatment}=G=g,\ t\geq g,\\
\text{target estimand}=(F^0_{g,t},QTT_{g,t}(\tau),S^{CIC}_{g,t}(\tau),S^{CL}_{g,t}(\tau)),\\
\text{baseline identifying assumptions}=\text{Assumptions \ref{ass:finite-support}--\ref{ass:cl-copula};}\\
\text{frontier/sign restrictions}=\text{Assumptions \ref{ass:copula-balance}, \ref{ass:margin};}\quad
\text{recovery restriction}=\text{Assumption \ref{ass:timing-homogeneity}.}
\end{gathered}
\]

\section{Assumptions}
\begin{assumption}[Finite support and overlap]\label{ass:finite-support}
\(\mathcal G\) and the support of each \(Y_s\mid G=h\) are finite before interpolation, \(\Pr(G=g)>0\), \(\Pr(G\in\mathcal R_{g,t})>0\), and every risk-set cohort used in the maps has positive probability in the relevant support cells.
\end{assumption}

\begin{assumption}[Continuity and local quantile regularity]\label{ass:regularity}
After the standard linear interpolation of finite-support CDFs, all CDFs used in \(F^{CIC,0}_{g,t}\), \(F^{CL,0}_{g,t}\), and \(QTT_{g,t}(\tau)\) are continuous and strictly increasing on a neighborhood of their \(\tau\)-quantiles.
\end{assumption}

\begin{assumption}[Stable-rank CIC restriction]\label{ass:cic}
For each \((g,t)\), the untreated potential outcomes obey the Athey--Imbens stable-rank transformation restriction relative to the not-yet-treated risk set, so \(F^{CIC,0}_{g,t}\) is the valid CIC counterfactual CDF whenever the risk-set mixture is treated as the comparison group.
\end{assumption}

\begin{assumption}[Conditional copula stability]\label{ass:cl-copula}
For each \((g,t)\), the conditional copula of \((Y_{g-1}(\infty),Y_t(\infty)-Y_{g-1}(\infty))\) for cohort \(g\) equals the corresponding risk-set copula after conditioning on the observable comparison sigma-field; hence \(F^{CL,0}_{g,t}\) is the valid Callaway--Li panel counterfactual CDF.
\end{assumption}

\begin{assumption}[Timing homogeneity]\label{ass:timing-homogeneity}
The risk-set timing weights are baseline-stable, \(\omega_{h\mid g,t}=\omega^0_{h\mid g,t}\) for all \(h\in\mathcal R_{g,t}\), and the risk-set untreated quantile-change functions \(Q_{h,t}(u)-Q_{h,g-1}(u)\) are equal across \(h\) on a neighborhood of \(u=\tau\).
\end{assumption}

\begin{definition}[Local copula-transport imbalance]\label{def:copula-imbalance}
The local copula-transport imbalance \(\mathfrak C^{\Pi}_{g,t,\tau}(P)\) is the signed functional of \(\Pi^{CL}_{g,t}-\Pi^{rank}_{g,t}\) displayed in Section 3. It is independently computable from the local copula cells and the quantile-density weight \(\psi_{g,t,\tau}\); it is not a residual obtained after subtracting \(\mathfrak M_{g,t,\tau}(P)\) from the CIC--Callaway--Li quantile gap.
\end{definition}

\begin{assumption}[Copula-balance frontier]\label{ass:copula-balance}
\(\mathfrak C^{\Pi}_{g,t,\tau}(P)=0\) if and only if the conditional copula-stability map and the CIC rank map induce the same local rank transport \(T^{CIC}_{g,t,\tau}\) on \(I_\tau\).
\end{assumption}

\begin{assumption}[Non-degenerate sign margin]\label{ass:margin}
There is a curvature constant \(c_{g,t,\tau}(P)>0\), defined as the minimum local quantile-density slope over the CIC and Callaway--Li counterfactual quantiles, and a margin parameter \(\varepsilon_{g,t,\tau}\) satisfying \(0<\varepsilon_{g,t,\tau}\leq c_{g,t,\tau}(P)/4\), such that \(|\mathfrak M_{g,t,\tau}(P)+\mathfrak C^{\Pi}_{g,t,\tau}(P)|\geq 4\varepsilon_{g,t,\tau}\) and the observed treated quantile lies within \(\varepsilon_{g,t,\tau}\) of exactly one of the two counterfactual quantiles.
\end{assumption}

\section{Main results}
\begin{theorem}[Two-period agreement under common timing]\label{thm:two-period}
For \(T=1\) with a single treated cohort \(g=1\), under Assumptions~\ref{ass:finite-support}--\ref{ass:cl-copula} and the timing-homogeneity restriction specialized to the unique comparison group, \(F^{CIC,0}_{1,1}=F^{CL,0}_{1,1}\) at every continuity point whenever \(T^{CIC}_{1,1,\tau}\) and the Callaway--Li copula transport generated by \(\Pi^{CL}_{1,1}\) coincide on \(I_\tau\).
\end{theorem}
\paragraph{Why this is new and worth studying.}
(a) This is the sanity bridge between \citet[Sections 2--3]{AtheyImbens2006} and \citet[Sections 2--3]{CallawayLi2019}: each paper supplies one counterfactual map, but neither states the equality condition between the two local transports. (b) It gives \citet{LiLin2024} the required corner case for any staggered equivalence theorem: the proposed timing-skew object must collapse to zero in the canonical non-staggered design.

\begin{conjecture}[Finite-support CIC--Callaway--Li equivalence frontier (NOT YET PROVED)]\label{conj:frontier}
Fix \((g,t,\tau)\). Under Assumptions~\ref{ass:finite-support}, \ref{ass:regularity}, \ref{ass:cic}, \ref{ass:cl-copula}, and \ref{ass:copula-balance}, the following are equivalent:
\[
Q^{CIC,0}_{g,t}(\tau)=Q^{CL,0}_{g,t}(\tau)
\quad\Longleftrightarrow\quad
\mathfrak M_{g,t,\tau}(P)=0\ \text{ and }\ \mathfrak C^{\Pi}_{g,t,\tau}(P)=0.
\]
Moreover, if this equivalence holds for every supported \((g,t,\tau)\), then the same primitive counterfactual distribution \(F^0_{g,t}\) jointly point-identifies \(QTT_{g,t}(\tau)\), cohort-aggregated \(QTT_g(\tau)\), calendar-aggregated \(QTT_t(\tau)\), and risk-set weighted aggregate \(QTT^{agg}(\tau)\).
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest published results are \citet[Sections 2--3, counterfactual CDF construction]{AtheyImbens2006}, \citet[Sections 2--3, time-invariance copula construction]{CallawayLi2019}, and \citet[abstract and concluding discussion on the staggered copula difficulty]{LiLin2024}; the gap is an iff frontier between their counterfactual maps in staggered timing, with the operational quantities \(\mathfrak M_{g,t,\tau}(P)\) and \(\mathfrak C^{\Pi}_{g,t,\tau}(P)\) stated separately. (b) Resolving it would directly unblock the Callaway--Li route flagged by \citet{LiLin2024} by saying exactly when staggered group-time, cohort-aggregate, and calendar-aggregate QTT are jointly point-identified from one counterfactual object.

\begin{conjecture}[Open-class opposite-sign wedge (NOT YET PROVED)]\label{conj:sign}
Under Assumptions~\ref{ass:finite-support}, \ref{ass:regularity}, \ref{ass:cic}, \ref{ass:cl-copula}, \ref{ass:copula-balance}, and \ref{ass:margin}, there exists a total-variation open neighborhood \(\mathcal O_{g,t,\tau}\) of observable laws around any finite-support law with \(|\mathfrak M_{g,t,\tau}(P)+\mathfrak C^{\Pi}_{g,t,\tau}(P)|\geq 4\varepsilon_{g,t,\tau}\) and the treated quantile strictly between \(Q^{CIC,0}_{g,t}(\tau)\) and \(Q^{CL,0}_{g,t}(\tau)\), such that every \(P'\in\mathcal O_{g,t,\tau}\) satisfies
\[
S^{CIC}_{g,t}(\tau)=-S^{CL}_{g,t}(\tau).
\]
\end{conjecture}
\paragraph{Why this is new and worth studying.}
(a) The closest nonlinear targets are \citet[Sections 2--3]{AtheyImbens2006}, \citet[Sections 2--3]{CallawayLi2019}, and the staggered QTT workflow of \citet[abstract and concluding discussion]{LiLin2024}; the closest diagnostic analogues, \citet{GoodmanBacon2021}, \citet{SunAbraham2021}, and \citet{deChaisemartinDHaultfoeuille2020}, are linear mean estimands and do not cover nonlinear counterfactual CDF construction followed by quantile inversion. (b) The consumer is a Li--Lin-style staggered-QTT implementation that tries both a CIC-style rank counterfactual and a Callaway--Li time-invariance copula counterfactual: a sign reversal theorem would warn that the two plug-in signs are not interchangeable when \(\mathfrak M_{g,t,\tau}(P)+\mathfrak C^{\Pi}_{g,t,\tau}(P)\) is separated from zero.

\section{Sanity-check corollaries}
\begin{corollary}[Timing-homogeneous joint point identification]\label{cor:homogeneous}
Under Assumptions~\ref{ass:finite-support}, \ref{ass:regularity}, and \ref{ass:timing-homogeneity}, \(\mathfrak M_{g,t,\tau}(P)=0\). If Assumption~\ref{ass:copula-balance} also gives \(\mathfrak C^{\Pi}_{g,t,\tau}(P)=0\), Conjecture~\ref{conj:frontier} reduces to \(Q^{CIC,0}_{g,t}(\tau)=Q^{CL,0}_{g,t}(\tau)\), so all group-time and aggregate QTT functionals named in Conjecture~\ref{conj:frontier} are point-identified by the common counterfactual quantile.
\end{corollary}

\begin{example}[Concrete non-corner witness]\label{ex:witness}
Take \(T=3\), cohorts \(G\in\{1,3,\infty\}\), target cell \((g,t,\tau)=(1,2,1/2)\), and valid not-yet-treated risk set \(\mathcal R_{1,2}=\{3,\infty\}\). Set baseline risk-set weights \((\omega^0_{3\mid1,2},\omega^0_{\infty\mid1,2})=(1/2,1/2)\). Let untreated median changes for the risk-set cohorts be \(+a\) and \(-a\), with current risk-set weights \((1/2+\eta,1/2-\eta)\), where \(a>0\) and \(0<|\eta|<1/4\), and take a rank-preserving local copula so \(\mathfrak C^{\Pi}_{1,2,1/2}(P)=0\). Then \(\mathfrak M_{1,2,1/2}(P)=2a\eta\). Choosing the treated median strictly between the two counterfactual medians and \(2|a\eta|\geq4\varepsilon_{1,2,1/2}\) gives the explicit finite-support route for Conjecture~\ref{conj:sign}; small perturbations of \(a\), \(\eta\), and the surrounding support probabilities preserve the sign wedge.
\end{example}

\section{Proof-sketch route}
The proof route is finite-dimensional. First, write both \(F^{CIC,0}_{g,t}\) and \(F^{CL,0}_{g,t}\) as maps from the same vector of risk-set marginal CDF values, cohort timing weights, and local copula cells. Second, linearize the two maps at the \(\tau\)-quantile using the inverse-CDF derivative; this should isolate the independently defined timing-skew moment \(\mathfrak M_{g,t,\tau}(P)\) and the primitive copula-transport imbalance \(\mathfrak C^{\Pi}_{g,t,\tau}(P)\). Third, prove sufficiency by substituting \(\mathfrak M=\mathfrak C^{\Pi}=0\), and prove necessity by perturbing one timing weight or one local copula cell while holding the observed marginals fixed. The open-class sign result should follow from strict monotonicity of inverse CDFs, the margin bound in Assumption~\ref{ass:margin}, and continuity of all finite-support cell probabilities; the explicit \(T=3\) witness in Example~\ref{ex:witness} is the smallest boundary case that needs hand algebra.

\section{Honest scope flags}
The two-period bridge is labelled as a theorem because it is a routine equality check once both counterfactual maps are specialized to the same transport. The finite-support iff frontier and open-class sign reversal are conjectures: the hard part is proving the necessity direction from the primitive copula functional \(\mathfrak C^{\Pi}\), not from a residual definition, and proving that the witness remains non-degenerate on an open neighborhood. The proposal assumes continuous interpolation of finite-support CDFs; a later version may need a separate left/right quantile convention for atoms. Version 2 withdraws the v1 formulation in which timing homogeneity was inadvertently included among the non-equivalence assumptions and replaces the v1 residual \(\mathfrak C\) with the primitive copula-transport imbalance \(\mathfrak C^{\Pi}\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft from Stage -1.1 gap 1; prior verdict: none.
\item v2 (revise) -- patched location-level anchors, defined the CIC and Callaway--Li local transports, removed timing homogeneity from the non-equivalence conjectures, replaced the tautological residual with \(\mathfrak C^{\Pi}\), and fixed the risk-set witness; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Athey and Imbens(2006)]{AtheyImbens2006}
Athey, S. and G. W. Imbens (2006).
Identification and inference in nonlinear difference-in-differences models.
\emph{Econometrica} 74(2), 431--497.

\bibitem[Callaway and Li(2019)]{CallawayLi2019}
Callaway, B. and T. Li (2019).
Quantile treatment effects in difference in differences models with panel data.
\emph{Quantitative Economics} 10(4), 1579--1618.

\bibitem[Callaway, Li, and Oka(2018)]{CallawayLiOka2018}
Callaway, B., T. Li, and T. Oka (2018).
Quantile treatment effects in difference in differences models under dependence restrictions and with only two time periods.
\emph{Journal of Econometrics} 206(2), 395--413.

\bibitem[Li and Lin(2024)]{LiLin2024}
Li, X. and L. Lin (2024).
Identification of quantile treatment effects in difference-in-differences settings with staggered adoption.
\emph{Economics Letters} 241, 111789.

\bibitem[Fan and Yu(2012)]{FanYu2012}
Fan, Y. and Z. Yu (2012).
Partial identification of distributional and quantile treatment effects in difference-in-differences models.
\emph{Economics Letters} 115(3), 511--515.

\bibitem[Callaway and Sant'Anna(2021)]{CallawaySantAnna2021}
Callaway, B. and P. H. C. Sant'Anna (2021).
Difference-in-differences with multiple time periods.
\emph{Journal of Econometrics} 225(2), 200--230.

\bibitem[Goodman-Bacon(2021)]{GoodmanBacon2021}
Goodman-Bacon, A. (2021).
Difference-in-differences with variation in treatment timing.
\emph{Journal of Econometrics} 225(2), 254--277.

\bibitem[Sun and Abraham(2021)]{SunAbraham2021}
Sun, L. and S. Abraham (2021).
Estimating dynamic treatment effects in event studies with heterogeneous treatment effects.
\emph{Journal of Econometrics} 225(2), 175--199.

\bibitem[de Chaisemartin and D'Haultfoeuille(2020)]{deChaisemartinDHaultfoeuille2020}
de Chaisemartin, C. and X. D'Haultfoeuille (2020).
Two-way fixed effects estimators with heterogeneous treatment effects.
\emph{American Economic Review} 110(9), 2964--2996.

\bibitem[Roth and Sant'Anna(2023)]{RothSantAnna2023}
Roth, J. and P. H. C. Sant'Anna (2023).
When is parallel trends sensitive to functional form?
\emph{Econometrica} 91(2), 737--747.
\end{thebibliography}

\end{document}
