\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\section*{eid_score_order_minimax_gap_v1 (score_variance_gap_exponent)}

\paragraph{TL;DR.} Nonlinear additive-Gaussian ANMs are population-identifiable away from the reversible linear-Gaussian limit, where the causal-direction functional is deliberately undefined. An exchange-symmetric two-node experiment maps SCORE's score-Jacobian variance gap to Chernoff information, the fixed-alternative likelihood frontier, and an exact pointwise local minimax elbow. Conditional on maintained ass:jacobian-estimability for common hypothesis-independent training maps, the newly defined cross-fitted score-contrast template is sign-consistent in the supercritical regime n C_m(delta_n)->infinity when r_n=o(sqrt(C_m(delta_n))). Tilted change-of-measure algebra and a deterministic common-map rare-event construction on the faster diagnostic subsequence n C_star(delta_n)/log log(n+e)->infinity show why this weak training-random L4 premise does not itself deliver an exponent; primitive verification for a concrete training procedure remains oeq:primitive-tilted-attainability.

\section{Project justification}

\paragraph{Gap.} SCORE has a population leaf identity and Zhu, Locatello, and Cevher provide a sufficient finite-sample correctness bound. ScoreSort, DAS, and AdaScore establish distinct score-based ordering or graph-identification conditions, but none gives the mirror-path map from SCORE's diagonal-Jacobian gap to Chernoff information or its pointwise local minimax elbow.

\paragraph{Niche.} The Gaussian linear submodel is an explicit observational-equivalence boundary shared by the two causal directions. Defining the direction functional only off that boundary yields a pointwise local modulus of structure identification and separates sign consistency of a new template from exponent control without attributing any limitation to a published SCORE workflow.

\paragraph{Fill.} An exchange-symmetric ANM subexperiment puts the score gap, tangent likelihood separation, Chernoff information, and minimax causal-order risk in one formal experiment. It derives the mirror likelihood frontier and elbow and, conditional on common hypothesis-independent nuisance maps, the centered-variance sign-consistency target for a cross-fitted score-contrast template in the supercritical regime. The tilted-loss algebra and deterministic common-map rare-event construction on a faster diagnostic subsequence are diagnostics; primitive, verifiable exponent attainability by a concrete trainer remains open.

\section{Related work}

Rolland et al. (rolland2022score) establish the diagonal score-Jacobian leaf characterization on which the population functional rests; they do not map that variance to likelihood information at a reversible boundary. Zhu, Locatello, and Cevher (zhu2023sample, Section 3 and Theorem 2) turn SCORE into a sufficient finite-sample curvature-margin guarantee, but do not give the mirror C_m(delta)-to-Chernoff map or the local minimax elbow. Hoyer et al. (hoyer2008nonlinear) and Peters et al. (peters2014anm) establish qualitative ANM directional asymmetry and exceptional reversibility, rather than a pointwise local testing modulus. Kpotufe, Sgouritsa, Janzing, and Schölkopf (kpotufe2014, Sections 1.2 and 5) prove residual-independence ANM direction consistency without a general finite-sample rate, so their result does not yield this score-gap/Chernoff calibration. Montagna, Noceti, Rosasco, Zhang, and Locatello (montagna2023das, Sections 3--3.3 and Conclusion) use score-Jacobian derivatives for nonlinear additive-Gaussian graph recovery and scalable pruning; DAS does not analyze a mirror two-simple-hypothesis likelihood experiment. Montagna, Noceti, Rosasco, and Locatello (montagna2023shortcuts, Sections 3.1 and 4) characterize score-sortability and ScoreSort through score-component variances, a different statistic that supplies no diagonal-Jacobian-gap Chernoff map near reversibility. Montagna, Faller, Bloebaum, Kirschbaum, and Locatello (montagna2025roof, Sections 4.1--4.3 and Appendix E.3) give score-based identification and AdaScore across linear, nonlinear, and latent settings, not a local likelihood efficiency analysis of this template. Montagna et al. (montagna2023nogam) document Gaussian-score inversions under non-Gaussian noise and motivate a separate generic-noise frontier; it informs but is not compared against this Gaussian mirror result. Chernoff (chernoff1952measure) supplies the fixed-simple-hypothesis product-measure exponent, not the ANM geometry that indexes it by C_m(delta). Koehler, Heckett, and Risteski (koehler2023efficiency) show that score matching can lose information relative to likelihood for density parameters; they motivate but are not refuted by the template-specific search for a concrete trainer that controls the tilted mistake losses.

\section{Setup}

Target (estimand / structural parameter): omega(P_{h,delta})=h, for h in {+,-} and 0<|delta|<delta_0.
Identifying functional / recovery map: omega(P_{h,delta})=+ iff V_y(P_{h,delta})=0<V_x(P_{h,delta}), and omega(P_{h,delta})=- iff V_x(P_{h,delta})=0<V_y(P_{h,delta}), for 0<|delta|<delta_0.
\begin{itemize}
  \item $P$ --- probability law; R^2; generic law used to define the score functional $:= a positive twice continuously differentiable observational law with density p$
  \item $p$ --- density; R^2 -> R_+; generic observational density $:= the Lebesgue density of the generic law P$
  \item $(X,Y)$ --- random vector; R^2; observed variable pair $:= a draw from the law currently indexed by the surrounding expression$
  \item $h$ --- index; {+,-}; opposite-arrow hypothesis index
  \item $j$ --- index; {x,y}; coordinate index
  \item $n$ --- integer; {1,2,...}; sample size
  \item $i$ --- index; {1,...,n}; observation index
  \item $ell$ --- index; {1,...,n}; within-fold averaging index
  \item $k$ --- index; {1,2}; cross-fitting fold index
  \item $I_{n,k}$ --- set; power set of {1,...,n}; evaluation fold in the two-fold split
  \item $delta_0$ --- scalar; (0,infinity); radius of the local ANM path
  \item $eta$ --- scalar; (0,infinity); exponential-envelope constant
  \item $alpha$ --- scalar; (0,1); linear correlation parameter
  \item $b$ --- scalar; (0,1); innovation variance $:= b = 1 - alpha^2$
  \item $Z$ --- random variable; R; exogenous parent at the reversible center $:= Z ~ N(0,1)$
  \item $E$ --- random variable; R; structural innovation $:= E ~ N(0,b), independent of Z$
  \item $g$ --- function; R -> R; centered nonlinear perturbation
  \item $delta$ --- scalar; (-delta_0,delta_0); local curvature index
  \item $delta_n$ --- sequence; (0,delta_0)^N; moving local alternative in the score-contrast question $:= an arbitrary positive local-curvature sequence indexed by n$
  \item $r_n$ --- nonnegative sequence; [0,infinity)^N; uniform L4 estimability rate for diagonal score-Jacobian functionals
  \item $rho$ --- scalar; [0,infinity); local effective-information limit
  \item $q_n$ --- positive sequence; (0,1)^N; rare-event probability in the adversarial nuisance perturbation
  \item $M_n$ --- positive sequence; (0,infinity)^N; amplitude in the adversarial nuisance perturbation
  \item $M$ --- scalar; (0,infinity); fixed tail threshold in the training-random L4 characterization
  \item $U$ --- random variable; L^2(P); generic centered-variance input
  \item $e$ --- random variable; L^2(P); generic nuisance error in a centered-variance comparison
  \item $f_delta$ --- function; R -> R; forward structural mechanism $:= f_delta(z) = alpha z + delta g(z)$
  \item $P_0$ --- probability law; R^2; linear-Gaussian direction-unidentifiable center $:= Law(Z, alpha Z + E)$
  \item $P_{+,delta}$ --- probability law; R^2; forward-arrow local law
  \item $P_{-,delta}$ --- probability law; R^2; reverse-arrow local law
  \item $P_{h,delta}$ --- indexed probability law; R^2; generic member of the two-arrow mirror experiment $:= P_{h,delta}=P_{+,delta} when h=+ and P_{h,delta}=P_{-,delta} when h=-$
  \item $omega$ --- causal-direction functional; {P_{h,delta}: h in {+,-}, 0<|delta|<delta_0} -> {+,-}; observational-law target on the identified portion of the mirror path $:= omega(P_{h,delta})=h for h in {+,-} and 0<|delta|<delta_0; omega is undefined at the common limit P_0$
  \item $W_delta$ --- random variable; R; non-leaf score-Jacobian fluctuation along the forward path $:= W_delta=b^(-1)[-2 alpha g'(X)+(Y-f_delta(X))g''(X)-delta g'(X)^2] under P_{+,delta}$
  \item $p_{h,delta}$ --- density; R^2 -> R_+; likelihood for the binary experiment $:= Lebesgue density of P_{h,delta}, h in {+,-}$
  \item $s_P$ --- function; R^2 -> R^2; observational score $:= s_P(x,y) = grad_(x,y) log p(x,y) for a positive C^2 density p of P$
  \item $J_j(P)$ --- random variable; R; diagonal score-Jacobian entry $:= J_j(P) = partial_j s_{P,j}(X,Y) for (X,Y) ~ P and j in {x,y}$
  \item $V_j(P)$ --- scalar; R_+; population SCORE leaf statistic $:= V_j(P) = Var_P[J_j(P)] for j in {x,y}$
  \item $C_m(delta)$ --- scalar; R_+; two-node minimum non-leaf score-Jacobian variance gap $:= C_m(delta) = min_(h in {+,-}) max_(j in {x,y}) V_j(P_{h,delta})$
  \item $v_h$ --- function; R^2 -> R; local likelihood tangent $:= v_h = partial_delta log p_{h,delta}|_(delta=0), h in {+,-}$
  \item $c_1$ --- scalar; R; leading score-gap coefficient $:= c_1 = b^(-2) Var[2 alpha g'(Z) - E g''(Z)]$
  \item $c_2$ --- scalar; R; squared tangent separation $:= c_2 = E_{P_0}[(v_+(X,Y)-v_-(X,Y))^2]$
  \item $Phi$ --- function; R -> (0,1); local Gaussian decision-limit distribution function $:= the standard normal distribution function$
  \item $C_star(delta)$ --- scalar; R_+; Chernoff information $:= C_star(delta) = -log inf_(t in [0,1]) integral_(R^2) p_{+,delta}(x,y)^t p_{-,delta}(x,y)^(1-t) dx dy$
  \item $A_n$ --- scalar; (0,1]; Hellinger affinity along the moving mirror experiment $:= A_n = integral_(R^2) sqrt(p_{+,delta_n}(x,y)p_{-,delta_n}(x,y)) dx dy = exp(-C_star(delta_n))$
  \item $m_n$ --- density; R^2 -> R_+; Hellinger-tilted one-observation density $:= m_n(x,y)=A_n^(-1)sqrt(p_{+,delta_n}(x,y)p_{-,delta_n}(x,y))$
  \item $ell_delta$ --- function; R^2 -> R; one-observation log-likelihood ratio $:= ell_delta(x,y)=log[p_{+,delta}(x,y)/p_{-,delta}(x,y)]$
  \item $L_n$ --- random variable; R; sample log-likelihood ratio $:= L_n=sum_(i=1)^n ell_{delta_n}(X_i,Y_i)$
  \item $T_n$ --- class; {+,-}^{(R^2)^n}; measurable order rules at sample size n
  \item $pi$ --- measurable map; T_n; candidate order rule
  \item $mathsf S_n$ --- Borel involution; (R^2)^n -> (R^2)^n; coordinate-swap symmetry of the mirror experiment $:= mathsf S_n((x_i,y_i)_{i=1}^n)=((y_i,x_i)_{i=1}^n)$
  \item $a_n$ --- Borel map; (R^2)^n -> {+,-}; antisymmetric likelihood-ratio tie breaker $:= a Borel tie breaker satisfying a_n(mathsf S_n w)=-a_n(w) whenever mathsf S_n w != w$
  \item $pi_{n,delta}^LR$ --- measurable map; T_n; delta-indexed equalizer rule for the mirror binary experiment $:= the antisymmetrically tie-broken likelihood-ratio rule for the pair (P_{+,delta}^n,P_{-,delta}^n) in def:mirror-equalizer-rule$
  \item $R_n(delta)$ --- scalar; [0,1]; local minimax order-error risk $:= R_n(delta) = inf_(pi in T_n) max_(h in {+,-}) P_{h,delta}^n{pi != h}$
  \item $D_n$ --- constructed object; T_n; cross-fitted score-contrast template output $:= a score-contrast order rule returned by an instantiation of def:crossfitted-score-contrast-template$
  \item $widehat J_{j,k}$ --- estimated function; R^2 -> R; cross-fitted nuisance estimate $:= a diagonal score-Jacobian estimate trained on observations outside I_{n,k}$
  \item $A_{n,k}$ --- Borel event; sigma((X_i,Y_i):i notin I_{n,k}); rare training-sample event
  \item $tilde J_{j,k}$ --- estimated function; R^2 -> R; adversarial admissible nuisance estimate $:= rare-event perturbed diagonal score-Jacobian estimate in def:rare-event-nuisance-perturbation$
  \item $widehat V_{j,k}$ --- scalar; R_+; foldwise empirical variance of widehat J_{j,k}
  \item $widehat Delta_n$ --- scalar; R; cross-fitted signed non-leaf-minus-leaf variance contrast
  \item $K_{+,n}$ --- scalar; [0,infinity); plus tilted mistake loss $:= K_{+,n}=E_{m_n^n}[exp(L_n/2)1{widehat Delta_n<0}]$
  \item $K_{-,n}$ --- scalar; [0,infinity); minus tilted mistake loss $:= K_{-,n}=E_{m_n^n}[exp(-L_n/2)1{widehat Delta_n>=0}]$
  \item $G_n$ --- sigma-field; sigma-field on the full data and training randomness; conditioning sigma-field for a randomized template instantiation $:= G_n is the joint returned-function sigma-field generated by the two fitted functions returned by the cross-fitted template$
  \item $widehat sigma_n$ --- scalar; R_+; empirical standard deviation of the foldwise variance contrast
  \item $widehat Z_n$ --- scalar; R; studentized signed score-variance contrast
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:linear-center]\label{ass:linear-center}
0 < alpha < 1.
\par\smallskip\noindent\emph{Novel.} A nondegenerate correlated Gaussian center is the intersection of the two arrow orientations; standardizing both marginals makes swapping X and Y an exact symmetry.
\end{assumption}

\begin{assumption}[ass:smooth-mechanism]\label{ass:smooth-mechanism}
g belongs to C^3(R).
\par\smallskip\noindent\emph{Standard} (three-times continuously differentiable mechanism, \cite{hoyer2008nonlinear}).
\end{assumption}

\begin{assumption}[ass:hermite-centering]\label{ass:hermite-centering}
Proj_(span{1,z}) g = 0 in L^2(N(0,1)).
\par\smallskip\noindent\emph{Novel.} Removing constant and linear components isolates departure from the linear-Gaussian reversible submodel; polynomial and smooth bounded nonlinear mechanisms can always be reparameterized in this way.
\end{assumption}

\begin{assumption}[ass:nonlinear-curvature]\label{ass:nonlinear-curvature}
E[g''(Z)^2] > 0.
\par\smallskip\noindent\emph{Novel.} The condition excludes affine links and permits smooth quadratic, spline, and sigmoid mechanisms on the Gaussian design; it is the substantive directional-asymmetry restriction, not a condition on a testing distance.
\end{assumption}

\begin{assumption}[ass:exponential-envelope]\label{ass:exponential-envelope}
There exists eta > 0 such that E exp(eta(|g(Z)|+|g'(Z)|+|g''(Z)|)) < infinity.
\par\smallskip\noindent\emph{Novel.} This explicit envelope holds for bounded smooth links and for polynomial links of degree at most two when eta is sufficiently small under the Gaussian parent; it supplies a verifiable local tail class without treating a testing conclusion as an assumption.
\end{assumption}

\begin{assumption}[ass:jacobian-estimability]\label{ass:jacobian-estimability}
For every n>=2, k in {1,2}, and j in {x,y}, the same single data-measurable map of the observations outside I_{n,k}, independent of h and of the unknown observational law P, returns widehat J_{j,k}; its L4(P_{h,delta_n}) error for J_j(P_{h,delta_n}) is O_{P_{h,delta_n}^n}(r_n), uniformly over (h,j,k) in {+,-} x {x,y} x {1,2}.
\end{assumption}

\section{Definitions}

\begin{definition}[def:mirror-anm-paths]\label{def:mirror-anm-paths}
$mirror-symmetric ANM paths := (P_{+,delta},P_{-,delta})=(Law(Z,f_delta(Z)+E),Law(f_delta(Z)+E,Z)) for every delta in (-delta_0,delta_0).$ \quad (\text{inputs: } Z, E, f_delta, delta_0)
\end{definition}

\begin{definition}[def:order-rules]\label{def:order-rules}
$order-rule collection := T_n={pi:(R^2)^n -> {+,-}: pi is Borel measurable} for every n in {1,2,...}.$ \quad (\text{inputs: } n)
\end{definition}

\begin{definition}[def:mirror-equalizer-rule]\label{def:mirror-equalizer-rule}
$antisymmetric likelihood-ratio equalizer := For w=((x_i,y_i))_{i=1}^n, let mathsf S_n w=((y_i,x_i))_{i=1}^n and choose a Borel a_n with a_n(mathsf S_n w)=-a_n(w) off the fixed-point set. For every (n,delta) in {1,2,...} x (-delta_0,delta_0), set pi_{n,delta}^LR(w)=+ if product_{i=1}^n p_{+,delta}(x_i,y_i)>product_{i=1}^n p_{-,delta}(x_i,y_i), set pi_{n,delta}^LR(w)=- if the inequality is reversed, and set pi_{n,delta}^LR(w)=a_n(w) on equality.$ \quad (\text{inputs: } mathsf S_n, a_n, pi_{n,delta}^LR, p_{+,delta}, p_{-,delta}, n, delta)
\end{definition}

\begin{definition}[def:score-variance]\label{def:score-variance}
$score-Jacobian variance map := (s_P,J_j(P),V_j(P))=(grad log p,partial_j s_{P,j}(X,Y),Var_P[J_j(P)]) for every positive C^2 law P on R^2 and j in {x,y}.$ \quad (\text{inputs: } P, p, j)
\end{definition}

\begin{definition}[def:local-tangents]\label{def:local-tangents}
$ANM tangent pair := (v_+(x,y),v_-(x,y))=((y-alpha x)g(x)/b,(x-alpha y)g(y)/b).$ \quad (\text{inputs: } alpha, b, g)
\end{definition}

\begin{definition}[def:chernoff-experiment]\label{def:chernoff-experiment}
$local order-testing experiment := R_n(delta)=inf_{pi in T_n} max_{h in {+,-}} P_{h,delta}^n{pi((X_i,Y_i)_{i=1}^n) != h} for every (n,delta) in {1,2,...} x (-delta_0,delta_0).$ \quad (\text{inputs: } P_{+,delta}, P_{-,delta}, T_n, n, delta)
\end{definition}

\begin{definition}[def:crossfitted-score-contrast-template]\label{def:crossfitted-score-contrast-template}
$cross-fitted score-contrast template := For n>=2 and any two-fold cross-fitted L4 rate realizers widehat J_{j,k} returned by the same h/P-independent data-measurable training mappings in ass:jacobian-estimability, let I_{n,1}={1,...,floor(n/2)} and I_{n,2}={floor(n/2)+1,...,n}. For each k in {1,2}, train widehat J_{j,k} on the observations outside I_{n,k}; set widehat V_{j,k}=|I_{n,k}|^{-1} sum_{i in I_{n,k}}[widehat J_{j,k}(X_i,Y_i)-|I_{n,k}|^{-1}sum_{ell in I_{n,k}}widehat J_{j,k}(X_ell,Y_ell)]^2, widehat Delta_n=2^{-1}sum_{k=1}^2(widehat V_{x,k}-widehat V_{y,k}), widehat sigma_n^2=2^{-1}sum_{k=1}^2|I_{n,k}|^{-1}sum_{i in I_{n,k}}( [widehat J_{x,k}(X_i,Y_i)-|I_{n,k}|^{-1}sum_{ell in I_{n,k}}widehat J_{x,k}(X_ell,Y_ell)]^2-[widehat J_{y,k}(X_i,Y_i)-|I_{n,k}|^{-1}sum_{ell in I_{n,k}}widehat J_{y,k}(X_ell,Y_ell)]^2-widehat Delta_n)^2, widehat Z_n=sqrt(n)widehat Delta_n/(widehat sigma_n vee n^{-1}), and D_n=+ if widehat Z_n>=0 and D_n=- otherwise.$ \quad (\text{inputs: } I_{n,k}, i, ell, j, k, (X,Y), widehat J_{j,k}, widehat V_{j,k}, widehat Delta_n, widehat sigma_n, widehat Z_n, D_n, n)
\end{definition}

\begin{definition}[def:score-contrast-exponent-handle]\label{def:score-contrast-exponent-handle}
$tilted score-contrast mistake losses := For every admissible delta_n downarrow 0 with n C_m(delta_n)->infinity, set A_n=integral sqrt(p_{+,delta_n}p_{-,delta_n})=exp(-C_star(delta_n)), m_n=A_n^(-1)sqrt(p_{+,delta_n}p_{-,delta_n}), ell_delta=log(p_{+,delta}/p_{-,delta}), L_n=sum_(i=1)^n ell_{delta_n}(X_i,Y_i), K_{+,n}=E_{m_n^n}[exp(L_n/2)1{widehat Delta_n<0}], and K_{-,n}=E_{m_n^n}[exp(-L_n/2)1{widehat Delta_n>=0}]. Handle: search for primitive, verifiable conditions on a concrete nuisance-training procedure that make log max(K_{+,n},K_{-,n})=o(n C_star(delta_n)), using the returned-function sigma-field G_n rather than an evaluation-independent training field.$ \quad (\text{inputs: } A_n, m_n, ell_delta, L_n, K_{+,n}, K_{-,n}, G_n, widehat J_{j,k}, widehat V_{j,k}, widehat Delta_n, C_star(delta), delta_n, n)
\end{definition}

\begin{definition}[def:rare-event-nuisance-perturbation]\label{def:rare-event-nuisance-perturbation}
$rare-event nuisance perturbation := For an admissible delta_n downarrow 0 satisfying n C_star(delta_n)/log log(n+e)->infinity, set q_n=1/log(n+e) and fix a positive deterministic amplitude schedule M_n up-arrow infinity; both schedules are independent of h, delta_n, and the unknown law P. For each k in {1,2}, select one distinct observation i(k) outside I_{n,k} and set A_{n,k}={X_{i(k)}>Phi^{-1}(1-q_n)}. The A_{n,k} are independent under P_{+,delta_n} and each has probability q_n; under P_{-,delta_n}, each probability tends to zero by uniform local tightness and the diverging threshold. Starting from any common h/P-independent data-measurable rate-realizing maps widehat J_{j,k}, set tilde J_{x,k}=widehat J_{x,k} and tilde J_{y,k}=widehat J_{y,k} off A_{n,k}; on A_{n,k}, set tilde J_{x,k}=0 and tilde J_{y,k}=M_n x. The perturbed maps are the same common h/P-independent data-measurable mappings under both hypotheses. Insert (tilde J_{x,k},tilde J_{y,k}) into def:crossfitted-score-contrast-template.$ \quad (\text{inputs: } widehat J_{j,k}, tilde J_{j,k}, A_{n,k}, q_n, M_n, C_star(delta), delta_n, n)
\end{definition}

\section{Main results}

\begin{theorem}[thm:local-geometry]\label{thm:local-geometry}
For every sufficiently small delta != 0, P_{+,delta} is the nonlinear additive-Gaussian ANM X->Y, P_{-,delta} is the nonlinear additive-Gaussian ANM Y->X, V_y(P_{+,delta})=V_x(P_{-,delta})=0, and V_x(P_{+,delta})=V_y(P_{-,delta})=C_m(delta)>0. As delta -> 0, C_m(delta)=c_1 delta^2+o(delta^2), c_1>0, and C_star(delta)=(c_2/8)delta^2+o(delta^2)=(c_2/(8c_1))C_m(delta)+o(C_m(delta)), with c_2>0.
\end{theorem}
\begin{proof}
Let \(\phi\) and \(\phi_b\) denote the \(N(0,1)\) and \(N(0,b)\) densities. By def:mirror-anm-paths,\n\[p_{+,\delta}(x,y)=\phi(x)\phi_b\{y-\alpha x-\delta g(x)\},\qquad p_{-,\delta}(x,y)=p_{+,\delta}(y,x).\tag{1}\]\nAss:linear-center gives \(b=1-\alpha^2>0\), so these are positive \(C^2\) densities on all of \(\mathbb R^2\). At \(\delta=0\), (1) is the standardized bivariate Gaussian density with correlation \(\alpha\), hence both paths meet at \(P_0\). For \(\delta\ne0\), the plus structural equations are \(X=Z\) and \(Y=\alpha Z+\delta g(Z)+E\), with \(E\perp Z\) and \(E\sim N(0,b)\); coordinate exchange gives the minus equations with \(Y\) as parent. Since \(g''\) is continuous and \(E[g''(Z)^2]>0\), it is not identically zero. Therefore \(f_\delta''=\delta g''\) is not identically zero for \(\delta\ne0\), so these are nonlinear additive-Gaussian ANMs in the asserted directions.\n\nPut \(r_\delta(x,y)=y-\alpha x-\delta g(x)\). Direct differentiation of (1) gives\n\[J_y(P_{+,\delta})=-b^{-1},\qquad J_x(P_{+,\delta})=-1-b^{-1}(\alpha+\delta g'(x))^2+b^{-1}\delta r_\delta(x,y)g''(x).\tag{2}\]\nUnder \(P_{+,\delta}\), \((X,Y)=(Z,\alpha Z+\delta g(Z)+E)\), so \(r_\delta(X,Y)=E\). Since \(b+\alpha^2=1\), (2) becomes\n\[J_x(P_{+,\delta})=-b^{-1}+\delta W_\delta,\qquad W_\delta=b^{-1}\{-2\alpha g'(Z)+E g''(Z)-\delta g'(Z)^2\}.\tag{3}\]\nCoordinate exchange gives \(J_x(P_{-,\delta})=-b^{-1}\), while \(J_y(P_{-,\delta})\) has the distribution of the right side of (3). Consequently\n\[V_y(P_{+,\delta})=V_x(P_{-,\delta})=0,\qquad V_x(P_{+,\delta})=V_y(P_{-,\delta})=\delta^2\operatorname{Var}(W_\delta).\tag{4}\]\nThus both maxima in the definition of \(C_m\) are equal and \(C_m(\delta)=\delta^2\operatorname{Var}(W_\delta)\). Ass:exponential-envelope supplies every polynomial moment of \(g'\) and \(g''\), in particular the fourth moment of \(g'\); independence and Gaussianity of \(E\) therefore imply \(W_\delta\to W_0\) in \(L^2\). Continuity of variance in \(L^2\) gives\n\[C_m(\delta)=c_1\delta^2+o(\delta^2),\qquad c_1=\operatorname{Var}(W_0)=b^{-2}\operatorname{Var}\{2\alpha g'(Z)-E g''(Z)\}.\tag{5}\]\nThe conditional-variance identity yields\n\[b^2c_1=E\{\operatorname{Var}(2\alpha g'(Z)-E g''(Z)\mid Z)\}+\operatorname{Var}\{E(2\alpha g'(Z)-E g''(Z)\mid Z)\}\n=bE[g''(Z)^2]+4\alpha^2\operatorname{Var}(g'(Z))>0.\tag{6}\]\nHence \(c_1>0\), and continuity of \(\operatorname{Var}(W_\delta)\) makes \(C_m(\delta)>0\) for every sufficiently small \(\delta\ne0\). All variances are finite by ass:exponential-envelope and every displayed division is valid because \(b>0\).\n\nIt remains to calculate the likelihood scale. Relative to \(P_0\), direct cancellation of the Gaussian densities gives the exact identities\n\[L_{+,\delta}:=\frac{p_{+,\delta}}{p_0}=\exp\left\{\delta v_+-\frac{\delta^2g(X)^2}{2b}\right\},\qquad L_{-,\delta}:=\frac{p_{-,\delta}}{p_0}=\exp\left\{\delta v_--\frac{\delta^2g(Y)^2}{2b}\right\}.\tag{7}\]\nTo verify quadratic-mean differentiability of the plus path, condition under \(P_0\) on \(X=x\), put \(W=(Y-\alpha X)/\sqrt b\sim N(0,1)\), and let \(u=\delta g(x)/\sqrt b\). Then \(\sqrt{L_{+,\delta}}=q_u(W):=\exp(uW/2-u^2/4)\). If \(F(u)=E[(q_u(W)-1-uW/2)^2]\), Gaussian integration gives\n\[F(u)=2+u^2/4-2(1+u^2/4)e^{-u^2/8}=O(u^4),\tag{8}\]\nand the elementary square inequality also gives\n\[F(u)\le2E(q_u-1)^2+2E(uW/2)^2=4(1-e^{-u^2/8})+u^2/2\le u^2.\tag{9}\]\nTherefore \(F(u)/u^2\to0\) and \(\delta^{-2}F(\delta g(x)/\sqrt b)\le g(x)^2/b\), whose right side is integrable by ass:exponential-envelope. Dominated convergence proves\n\[\sqrt{L_{+,\delta}}=1+\frac{\delta}{2}v_++o_{L^2(P_0)}(\delta).\tag{10}\]\nConditioning on \(Y\) proves the analogous formula with \(v_-\). Direct conditional expectation gives \(E_0v_+=E_0v_-=0\); the envelope gives square integrability, so \(c_2<\infty\).\n\nFor \(t\in[0,1]\), set \(H_\delta(t)=\int p_{+,\delta}^t p_{-,\delta}^{1-t}\). Coordinate exchange gives \(H_\delta(t)=H_\delta(1-t)\), and Holder's inequality makes \(\log H_\delta\) convex. Its minimum is therefore at \(t=1/2\). Using (10),\n\[1-\inf_tH_\delta(t)=1-\int\sqrt{p_{+,\delta}p_{-,\delta}}=\frac12\|\sqrt{L_{+,\delta}}-\sqrt{L_{-,\delta}}\|_{L^2(P_0)}^2=\frac{c_2}{8}\delta^2+o(\delta^2).\tag{11}\]\nBecause \(-\log(1-u)=u+o(u)\), def:chernoff-experiment gives\n\[C_\star(\delta)=\frac{c_2}{8}\delta^2+o(\delta^2).\tag{12}\]\nTo show strict separation, suppose \(c_2=0\). The continuous function \(v_+-v_-\) is then zero \(P_0\)-almost surely; since \(P_0\) has an everywhere-positive density, it vanishes everywhere. Thus\n\[(y-\alpha x)g(x)=(x-\alpha y)g(y)\quad\text{for every }(x,y)\in\mathbb R^2.\tag{13}\]\nPutting \(y=\alpha x\) gives \(bxg(\alpha x)=0\) for all \(x\). Since \(b>0\), \(\alpha>0\), and \(g\) is continuous, this forces \(g\equiv0\), contradicting ass:nonlinear-curvature. Hence \(c_2>0\). Finally, (5) implies \(\delta^2=C_m(\delta)/c_1+o(C_m(\delta))\); substituting into (12) gives \(C_\star(\delta)=(c_2/(8c_1))C_m(\delta)+o(C_m(\delta))\). No additional support, rank, positivity, overlap, or boundary condition is needed.
\end{proof}
\par\smallskip\noindent \textit{Justification.} This theorem derives the observational information scale from SCORE's native population gap rather than assuming a testing separation. \textit{Gap.} Zhu et al. relate a curvature margin to a sufficient SCORE guarantee, while Hoyer et al. and Peters et al. give qualitative directional asymmetry. Montagna et al.'s ScoreSort studies bivariate score-component-variance ordering on its score-sortable subclass, and Montagna et al.'s broader score framework gives population identifiability conditions; neither relates SCORE's diagonal score-Jacobian variance C_m(delta) to Chernoff information at the linear-Gaussian boundary. \textit{Consumer.} It calibrates the likelihood frontier, the local-minimax elbow, and the cross-fitted score-contrast template against Zhu, Locatello, and Cevher's curvature-margin SCORE guarantee on the same mirror experiment.

\begin{theorem}[thm:local-minimax-frontier]\label{thm:local-minimax-frontier}
For each fixed sufficiently small delta != 0, R_n(delta)=exp{-n[C_star(delta)+o_n(1)]} as n -> infinity. Consequently, lim_(delta downarrow 0) lim_(n -> infinity) [-log R_n(delta)]/[n C_m(delta)] = c_2/(8c_1), so the optimal binary order-testing exponent in the mirror experiment is linear in C_m(delta).
\end{theorem}
\begin{proof}
Fix a sufficiently small \(\delta\ne0\), abbreviate \(p=p_{+,\delta}\) and \(q=p_{-,\delta}\), and let \(S\) exchange the two coordinates. The mirror construction gives \(q(w)=p(Sw)\). By the symmetry and log-convexity calculation in thm:local-geometry,\n\[A:=e^{-C_\star(\delta)}=\int_{\mathbb R^2}\sqrt{pq}<1.\tag{1}\]\nDefine \(m=A^{-1}\sqrt{pq}\) and \(\ell=\log(p/q)\). Positivity of the Gaussian densities makes both well defined. Coordinate exchange leaves \(m\) invariant and sends \(\ell\) to \(-\ell\). Moreover \(E_m\ell^2<\infty\): with \(u=p/q\), the boundedness of \(\sqrt u(\log u)^2/(1+u)\) on \((0,\infty)\) gives \(E_m\ell^2\le2K/A\). Thus \(E_m\ell=0\); write \(\sigma^2=E_m\ell^2\).\n\nLet \(B_n=\frac12\int\min(p^n,q^n)\), the equal-prior Bayes error, and let \(S_n=\sum_{i=1}^n\ell(X_i,Y_i)\) under \(m^n\). Since \(p=Ame^{\ell/2}\) and \(q=Ame^{-\ell/2}\),\n\[B_n=\frac{A^n}{2}E_{m^n}e^{-|S_n|/2}.\tag{2}\]\nThe expectation is at most one. If \(\sigma>0\), Chebyshev's inequality gives \(m^n\{|S_n|\le2\sigma\sqrt n\}\ge3/4\); if \(\sigma=0\), then \(S_n=0\) almost surely. Hence in either case\n\[\frac38A^ne^{-\sigma\sqrt n}\le B_n\le\frac12A^n,\qquad -n^{-1}\log B_n\longrightarrow C_\star(\delta).\tag{3}\]\n\nMirror symmetry makes this Bayes error exactly minimax. Take the likelihood-ratio rule, choosing \(+\) on \(p^n>q^n\), \(-\) on \(p^n<q^n\), and on equality use any Borel label antisymmetric under \(S\) off the fixed-point set. Such a label is obtained by inspecting the first sample coordinate with \(x_i\ne y_i\); the fixed-point set \(x_i=y_i\) for every \(i\) is Lebesgue-null. Changing variables by \(S\) shows that the rule's two errors are equal. Their average is \(B_n\), so its maximum error is \(B_n\). Conversely, every rule's maximum error is at least its equal-prior average error, and that average is at least \(B_n\). Therefore \(R_n(\delta)=B_n\). Combining this identity with (3) proves\n\[R_n(\delta)=\exp\{-n[C_\star(\delta)+o_n(1)]\}.\tag{4}\]\nFor fixed \(\delta\ne0\), \(C_m(\delta)>0\) by thm:local-geometry, so\n\[\lim_{n\to\infty}\frac{-\log R_n(\delta)}{nC_m(\delta)}=\frac{C_\star(\delta)}{C_m(\delta)}.\]\nTaking the outer limit \(\delta\downarrow0\) and invoking thm:local-geometry yields \(c_2/(8c_1)\). This is the stated iterated, pointwise mirror-path limit.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The local geometry becomes operational only after the binary-testing risk is shown to inherit its Chernoff scale. \textit{Gap.} Chernoff characterizes generic simple-versus-simple product testing, while Zhu et al.'s Theorem 2 analyzes a score-estimation upper guarantee. Montagna et al. analyze score-sortability and score-based identifiability rather than the product-measure risk of this opposite-order Gaussian-ANM pair; neither result states a likelihood frontier indexed by SCORE's C_m(delta). \textit{Consumer.} It is the likelihood benchmark for the local-minimax elbow and for the score-contrast template, and it calibrates Zhu, Locatello, and Cevher's sufficient curvature-margin guarantee on the same mirror experiment.

\begin{theorem}[thm:local-minimax-elbow]\label{thm:local-minimax-elbow}
For every (n,delta), the antisymmetrically tie-broken likelihood-ratio rule pi_{n,delta}^LR satisfies R_n(delta)=P_{+,delta}^n{pi_{n,delta}^LR != +}=P_{-,delta}^n{pi_{n,delta}^LR != -}. Along every delta_n downarrow 0, E_{m_n}[ell_{delta_n}(X,Y)^2]=O(delta_n^2). If n C_m(delta_n)->rho in [0,infinity), then R_n(delta_n)->Phi(-0.5 sqrt(rho c_2/c_1)); if n C_m(delta_n)->infinity, then [-log R_n(delta_n)]/[n C_star(delta_n)]->1 and [-log R_n(delta_n)]/[n C_m(delta_n)]->c_2/(8c_1). Both limits are pointwise for the fixed admissible mirror path.
\end{theorem}
\begin{proof}
Write \(S(x,y)=(y,x)\) and extend \(S\) coordinatewise to \(n\) observations. The mirror construction gives, pointwise,\n\[p_{-,\delta}(x,y)=p_{+,\delta}(S(x,y)),\qquad \ell_\delta(S(x,y))=-\ell_\delta(x,y).\tag{1}\]\nAll densities are positive because \(b=1-\alpha^2>0\). The likelihood-ratio rule is therefore Borel. Away from the likelihood tie set it is antisymmetric under \(S\), and on the tie set def:mirror-equalizer-rule makes it antisymmetric except on \(F_n=\{x_i=y_i\text{ for every }i\}\). The set \(F_n\) is Lebesgue-null and hence \(P_{h,\delta}^n\)-null. A change of variables by the measure-preserving involution \(S\) yields\n\[P_{+,\delta}^n\{\pi_{n,\delta}^{LR}=-\}=P_{-,\delta}^n\{\pi_{n,\delta}^{LR}=+\}.\tag{2}\]\nSet\n\[B_n(\delta)=\frac12\inf_{\pi\in T_n}\left[P_{+,\delta}^n\{\pi=-\}+P_{-,\delta}^n\{\pi=+\}\right]=\frac12\int\min(p_{+,\delta}^n,p_{-,\delta}^n).\tag{3}\]\nThe likelihood-ratio rule attains the pointwise minimum in (3), including on ties. By (2), each of its errors equals their average \(B_n(\delta)\). The maximum error of any rule is at least its average error, which is at least \(B_n(\delta)\). Therefore, for every \((n,\delta)\),\n\[R_n(\delta)=B_n(\delta)=P_{+,\delta}^n\{\pi_{n,\delta}^{LR}\ne+\}=P_{-,\delta}^n\{\pi_{n,\delta}^{LR}\ne-\}.\tag{4}\]\nThis includes \(\delta=0\): the laws coincide, and antisymmetric tie breaking splits their swap-invariant common law equally outside the null fixed-point set.\n\nWe next derive the local tilted moments. Relative to \(P_0\), thm:local-geometry established the exact identities\n\[L_{+,\delta}=\frac{p_{+,\delta}}{p_0}=\exp\left\{\delta v_+-\frac{\delta^2g(X)^2}{2b}\right\},\qquad L_{-,\delta}=\frac{p_{-,\delta}}{p_0}=\exp\left\{\delta v_--\frac{\delta^2g(Y)^2}{2b}\right\}.\tag{5}\]\nPut\n\[d=v_+-v_-,\qquad q=\frac{g(Y)^2-g(X)^2}{2b}.\tag{6}\]\nThen the one-observation log likelihood ratio has the exact expansion\n\[\ell_\delta=\delta d+\delta^2q.\tag{7}\]\nLet \(A_\delta=\int\sqrt{p_{+,\delta}p_{-,\delta}}\) and \(M_\delta=A_\delta^{-1}\sqrt{L_{+,\delta}L_{-,\delta}}\), so \(M_\delta=dm_\delta/dP_0\). Mirror symmetry makes \(m_\delta\) invariant under \(S\), while (1) makes \(\ell_\delta\) antisymmetric. Hence\n\[E_{m_\delta}\ell_\delta=0.\tag{8}\]\nThe integrability behind this identity and the following limits is explicit. Under \(P_0\), let \(a=Y-\alpha X\) and \(c=X-\alpha Y\). Completing squares in (5) gives\n\[\sqrt{L_{+,\delta}L_{-,\delta}}=\exp\left\{\frac{\delta a g(X)+\delta c g(Y)}{2b}-\frac{\delta^2(g(X)^2+g(Y)^2)}{4b}\right\}\le\exp\left\{\frac{a^2+c^2}{4b}\right\}=:H.\tag{9}\]\nThe Gaussian vector \((a,c)\) has covariance \(b\begin{pmatrix}1&-\alpha\\-\alpha&1\end{pmatrix}\), whose largest eigenvalue is \(b(1+\alpha)\). Therefore \(E_0H^r<\infty\) for every \(1<r<2/(1+\alpha)\), a nonempty interval because \(0<\alpha<1\). Ass:exponential-envelope gives all polynomial moments of \(g(X),g(Y)\), and Gaussianity gives all polynomial moments of \(a,c\). Holder's inequality with such an \(r>1\) consequently gives some \(\kappa\in(0,1]\) for which\n\[E_0\left[H\{ |d|+\delta_0|q|\}^{2+\kappa}\right]<\infty.\tag{10}\]\nThm:local-geometry gives \(A_\delta=e^{-C_\star(\delta)}\to1\). Equations (7), (9), and (10), followed by dominated convergence, imply\n\[E_{m_\delta}\ell_\delta^2=\delta^2E_0\left[M_\delta(d+\delta q)^2\right]=\delta^2\{E_0d^2+o(1)\}=c_2\delta^2+o(\delta^2),\tag{11}\]\nand also\n\[\sup_{0<|\delta|<\delta_1}E_{m_\delta}|\ell_\delta/\delta|^{2+\kappa}<\infty\tag{12}\]\nfor some \(\delta_1>0\). Thus, along every \(\delta_n\downarrow0\), \(E_{m_n}\ell_{\delta_n}^2=O(\delta_n^2)\), as asserted.\n\nThe exact minimax risk may now be written under the tilted law. Symmetry places the Chernoff minimum at \(1/2\), so \(A_\delta=e^{-C_\star(\delta)}\). With \(L_n=\sum_{i=1}^n\ell_{\delta_n}(X_i,Y_i)\), the identities \(p_{+,\delta_n}=A_nm_ne^{\ell_{\delta_n}/2}\) and \(p_{-,\delta_n}=A_nm_ne^{-\ell_{\delta_n}/2}\), together with (3)-(4), give\n\[R_n(\delta_n)=\frac{A_n^n}{2}E_{m_n^n}e^{-|L_n|/2}=\frac{e^{-nC_\star(\delta_n)}}2E_{m_n^n}e^{-|L_n|/2}.\tag{13}\]\n\nSuppose first that \(nC_m(\delta_n)\to\rho\in[0,\infty)\). By thm:local-geometry,\n\[n\delta_n^2\longrightarrow\lambda:=\rho/c_1,\qquad nC_\star(\delta_n)\longrightarrow\tau^2/8,\qquad \tau^2:=c_2\lambda=\rho c_2/c_1.\tag{14}\]\nIf \(\rho>0\), (8), (11), and (12) give \(L_n\Rightarrow N(0,\tau^2)\) under \(m_n^n\). To see this without invoking an undeclared limit theorem, for fixed \(t\) use \(|e^{iu}-1-iu+u^2/2|\le K_\kappa|u|^{2+\kappa}\) with (8) and (12):\n\[E_{m_n}e^{it\ell_{\delta_n}}=1-\frac{t^2}{2}E_{m_n}\ell_{\delta_n}^2+O(\delta_n^{2+\kappa}).\tag{15}\]\nHere \(n\delta_n^{2+\kappa}\to0\), while (11) and (14) give \(nE_{m_n}\ell_{\delta_n}^2\to\tau^2\); taking the \(n\)-th power in (15) proves the Gaussian convergence. Since \(z\mapsto e^{-|z|/2}\) is bounded and continuous, (13)-(14) imply, for \(G\sim N(0,\tau^2)\),\n\[R_n(\delta_n)\longrightarrow\frac{e^{-\tau^2/8}}2E e^{-|G|/2}=e^{-\tau^2/8}E[e^{G/2}1\{G<0\}]=\Phi(-\tau/2).\tag{16}\]\nThe last equality follows by completing the square in the normal density. If \(\rho=0\), (11) gives \(E_{m_n^n}L_n^2=nE_{m_n}\ell_{\delta_n}^2\to0\), so \(L_n\to0\) in probability, while (14) gives \(nC_\star(\delta_n)\to0\). Equation (13) then gives \(R_n(\delta_n)\to1/2=\Phi(0)\). Therefore\n\[R_n(\delta_n)\longrightarrow\Phi\left(-\frac12\sqrt{\rho c_2/c_1}\right).\tag{17}\]\n\nFinally suppose \(nC_m(\delta_n)\to\infty\). Thm:local-geometry implies \(N_n:=nC_\star(\delta_n)\to\infty\), \(N_n\asymp n\delta_n^2\), and \(C_\star(\delta_n)/C_m(\delta_n)\to c_2/(8c_1)\). By (8) and (11),\n\[\operatorname{Var}_{m_n^n}(L_n)=nE_{m_n}\ell_{\delta_n}^2=O(N_n).\tag{18}\]\nTake \(a_n=N_n^{3/4}\). Chebyshev's inequality gives \(m_n^n\{|L_n|\le a_n\}=1-o(1)\). Equation (13) therefore yields\n\[\frac{e^{-N_n}}2e^{-a_n/2}\{1-o(1)\}\le R_n(\delta_n)\le\frac{e^{-N_n}}2.\tag{19}\]\nBecause \(a_n=o(N_n)\), taking negative logarithms proves\n\[\frac{-\log R_n(\delta_n)}{nC_\star(\delta_n)}\longrightarrow1.\tag{20}\]\nMultiplying (20) by \(C_\star(\delta_n)/C_m(\delta_n)\to c_2/(8c_1)\) gives\n\[\frac{-\log R_n(\delta_n)}{nC_m(\delta_n)}\longrightarrow\frac{c_2}{8c_1}.\tag{21}\]\nAll constants belong to the one fixed mirror path. No uniform lower envelope over a global nonlinear-ANM class is asserted.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The elbow gives the nondegenerate local decision limit and the supercritical error exponent between the unrecoverable center and exponentially recoverable regime. \textit{Gap.} Chernoff supplies a fixed-alternative exponent, while Hoyer et al. and Peters et al. identify the reversible boundary only qualitatively. Neither provides the equalizer-based moving-alternative risk limit indexed by SCORE's C_m(delta) for this mirror ANM path. \textit{Consumer.} It converts a reported score-gap scale into the exact pointwise local power boundary and supercritical likelihood benchmark for choosing between the two causal orders.

\begin{proposition}[prop:linear-reduction]\label{prop:linear-reduction}
At delta=0, P_{+,0}=P_{-,0}=P_0 and R_n(0)=1/2 for every n.
\end{proposition}
\begin{proof}
Fix any integer $n\ge 1$. By $0<\alpha<1$ in ass:linear-center, $b=1-\alpha^2>0$. At $\delta=0$, $f_0(z)=\alpha z$, so def:mirror-anm-paths gives $P_{+,0}=\operatorname{Law}(Z,\alpha Z+E)=P_0$. The density of this law is\n\[p_{+,0}(x,y)=\frac{1}{2\pi\sqrt b}\exp\left\{-\frac{x^2}{2}-\frac{(y-\alpha x)^2}{2b}\right\}.\]\nThe reverse construction gives $P_{-,0}=\operatorname{Law}(\alpha Z+E,Z)$, whose density is\n\[p_{-,0}(x,y)=\frac{1}{2\pi\sqrt b}\exp\left\{-\frac{y^2}{2}-\frac{(x-\alpha y)^2}{2b}\right\}.\]\nSince $b=1-\alpha^2$, direct expansion yields\n\[b x^2+(y-\alpha x)^2=x^2+y^2-2\alpha xy=b y^2+(x-\alpha y)^2.\]\nConsequently $p_{+,0}(x,y)=p_{-,0}(x,y)$ for every $(x,y)$, and hence $P_{+,0}=P_{-,0}=P_0$.\n\nIt remains to evaluate the minimax risk in def:chernoff-experiment. For any $\pi\in T_n$, put $q=P_0^n\{\pi=+\}$. Because the two hypotheses induce the same sample law,\n\[P_{+,0}^n\{\pi\ne +\}=1-q,\qquad P_{-,0}^n\{\pi\ne -\}=q.\]\nThus $\max\{1-q,q\}\ge 1/2$, and taking the infimum over $\pi$ shows $R_n(0)\ge 1/2$. For the reverse inequality, define the Borel rule $\pi^*((x_i,y_i)_{i=1}^n)=+$ when $x_1\ge0$ and $\pi^*=-$ when $x_1<0$. Under $P_0^n$, $X_1=Z_1\sim N(0,1)$, so $P_0^n\{\pi^*=+\}=P_0^n\{\pi^*=-\}=1/2$. Therefore both error probabilities of $\pi^*$ equal $1/2$, giving $R_n(0)\le1/2$. Combining the bounds proves $R_n(0)=1/2$ for every $n$.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The proposed local frontier must collapse to the known linear-Gaussian observational equivalence case. \textit{Gap.} Hoyer et al. identify linear-Gaussian models as reversible, but do not quantify how the finite-sample directional error leaves that boundary. \textit{Consumer.} It verifies that the local lower bound is anchored at a genuine nonidentification point rather than at a poorly conditioned but identified model.

\begin{proposition}[prop:score-contrast-template]\label{prop:score-contrast-template}
Under ass:jacobian-estimability, the following conditional score-contrast result holds. Under P_{+,delta}, J_y(P_{+,delta})=-b^(-1) and J_x(P_{+,delta})=-b^(-1)+delta W_delta; under P_{-,delta} the two identities are swapped. For every U,e in L^2(P), |Var_P(U+e)-Var_P(U)| <= 2 sqrt(Var_P(U) Var_P(e))+Var_P(e). Hence, conditionally on each training fold, an L4 nuisance error e with ||e||_{L4(P_{h,delta_n})}=O_P(r_n) changes the non-leaf centered variance by O_P(|delta_n|r_n+r_n^2) and the leaf centered variance by O_P(r_n^2). For every instantiation D_n of def:crossfitted-score-contrast-template using the common rate realizers in ass:jacobian-estimability, if delta_n downarrow 0, n C_m(delta_n)->infinity, and r_n=o(sqrt(C_m(delta_n))), then max_{h in {+,-}}P_{h,delta_n}^n{D_n != h}->0.
\end{proposition}
\begin{proof}
Fix a sequence \(\delta_n\downarrow0\) satisfying \(nC_m(\delta_n)\to\infty\), and write \(P_{h,n}=P_{h,\delta_n}\). All claims are pointwise along this mirror path. The differentiation in thm:local-geometry gives, under \(P_{+,\delta}\),\n\[J_y(P_{+,\delta})=-b^{-1},\qquad J_x(P_{+,\delta})=-b^{-1}+\delta W_\delta,\tag{1}\]\nwhere \(W_\delta=b^{-1}[-2\alpha g'(Z)+E g''(Z)-\delta g'(Z)^2]\). Under \(P_{-,\delta}\), coordinate exchange gives \(J_x=-b^{-1}\) and \(J_y=-b^{-1}+\delta W_\delta^-\), where \(W_\delta^-(x,y)=W_\delta(y,x)\) has the same law as \(W_\delta\). In particular, the leaf entry is constant and the non-leaf entry has variance\n\[\delta^2\operatorname{Var}(W_\delta)=C_m(\delta).\tag{2}\]\n\nFor arbitrary \(U,e\in L^2(P)\), let \(U^\circ=U-E_PU\) and \(e^\circ=e-E_Pe\). Expanding the centered square gives\n\[\operatorname{Var}_P(U+e)-\operatorname{Var}_P(U)=2E_P(U^\circ e^\circ)+E_P[(e^\circ)^2].\tag{3}\]\nCauchy-Schwarz proves\n\[|\operatorname{Var}_P(U+e)-\operatorname{Var}_P(U)|\le2\sqrt{\operatorname{Var}_P(U)\operatorname{Var}_P(e)}+\operatorname{Var}_P(e).\tag{4}\]\nCondition on the training observations for a fixed fold. The fitted error \(e=\widehat J-J\) is then a fixed measurable function of an independent evaluation draw. Ass:jacobian-estimability gives \(\|e\|_{L^4(P_{h,n})}=O_P(r_n)\), hence\n\[\operatorname{Var}_{P_{h,n}}(e)\le\|e\|_{L^2(P_{h,n})}^2\le\|e\|_{L^4(P_{h,n})}^2=O_P(r_n^2).\tag{5}\]\nFor a non-leaf entry, (2) and thm:local-geometry give \(\sqrt{\operatorname{Var}(U)}=\sqrt{C_m(\delta_n)}=O(|\delta_n|)\), so (4)-(5) give a conditional centered-variance change \(O_P(|\delta_n|r_n+r_n^2)\). For a leaf entry, \(U\) is constant and (3) reduces to \(\operatorname{Var}(U+e)=\operatorname{Var}(e)=O_P(r_n^2)\). This proves the population perturbation assertions.\n\nIt remains to control the empirical fold variances. Let \(N_{n,k}=|I_{n,k}|\); both tend to infinity. For numbers \(a_1,\ldots,a_N\), write \(\mathbb V_N(a)=N^{-1}\sum_i(a_i-\bar a)^2\). The sample analogue of (4) is the deterministic inequality\n\[|\mathbb V_N(u+e)-\mathbb V_N(u)|\le2\{\mathbb V_N(u)\mathbb V_N(e)\}^{1/2}+\mathbb V_N(e).\tag{6}\]\nAss:exponential-envelope and the exact formula for \(W_\delta\) give \(\sup_{|\delta|\le\delta_1}E|W_\delta|^4<\infty\). Hence the triangular weak law, applied to \(W_{\delta_n}\) and \(W_{\delta_n}^2\), yields on each evaluation fold\n\[\mathbb V_{N_{n,k}}(W_{\delta_n})=\operatorname{Var}(W_{\delta_n})+o_P(1).\tag{7}\]\nIndeed, the variance of each empirical first or second moment is uniformly \(O(N_{n,k}^{-1})\), so Chebyshev's inequality applies. Thus the oracle empirical leaf variance is zero and the oracle empirical non-leaf variance is\n\[\delta_n^2\mathbb V_{N_{n,k}}(W_{\delta_n})=C_m(\delta_n)+o_P(\delta_n^2)=C_m(\delta_n)+o_P(C_m(\delta_n)).\tag{8}\]\nFor the empirical nuisance term, conditional on training,\n\[E\left[N_{n,k}^{-1}\sum_{i\in I_{n,k}}e(X_i,Y_i)^2\mid\text{training}\right]=\|e\|_{L^2(P_{h,n})}^2.\tag{9}\]\nTo make the training-random order explicit, for every \(\varepsilon>0\) choose \(C<\infty\) so that \(P\{\|e\|_4>Cr_n\}<\varepsilon\) eventually. On the complementary event, conditional Markov inequality bounds the probability that the average in (9) exceeds \(LC^2r_n^2\) by \(L^{-1}\). Letting \(L\) be large shows\n\[\mathbb V_{N_{n,k}}(e)\le N_{n,k}^{-1}\sum_{i\in I_{n,k}}e(X_i,Y_i)^2=O_P(r_n^2).\tag{10}\]\nSubstitution of (7) and (10) into (6) proves, simultaneously over the two coordinates and two folds, that fitting changes a non-leaf empirical variance by \(O_P(|\delta_n|r_n+r_n^2)\) and a leaf empirical variance by \(O_P(r_n^2)\). Reciprocal two-fold cross-fitting causes no problem: each marginal fold argument conditions only on that fold's fitted functions, which are independent of its evaluation observations, and a union bound joins the four cases.\n\nBy thm:local-geometry, \(C_m(\delta_n)=c_1\delta_n^2+o(\delta_n^2)\) with \(c_1>0\). Thus \(r_n=o(\sqrt{C_m(\delta_n)})\) is equivalent along this path to \(r_n=o(|\delta_n|)\), and therefore\n\[|\delta_n|r_n+r_n^2=o(C_m(\delta_n)).\tag{11}\]\nEquations (8)-(11), averaged over the two folds as in def:crossfitted-score-contrast-template, give\n\[\frac{\widehat\Delta_n}{C_m(\delta_n)}\xrightarrow[P_{+,n}^n]{P}1,\qquad \frac{\widehat\Delta_n}{C_m(\delta_n)}\xrightarrow[P_{-,n}^n]{P}-1.\tag{12}\]\nThe denominator \(\widehat\sigma_n\vee n^{-1}\) is strictly positive, so \(\widehat Z_n\) and \(\widehat\Delta_n\) have the same sign. The template declares \(D_n=+\) exactly when \(\widehat Z_n\ge0\). Since \(C_m(\delta_n)>0\) eventually, (12) proves\n\[P_{+,\delta_n}^n(D_n\ne+)\to0,\qquad P_{-,\delta_n}^n(D_n\ne-)\to0.\]\nTaking the maximum proves the proposition in the declared supercritical regime \(nC_m(\delta_n)\to\infty\). Thm:local-minimax-frontier is used only to locate this sign-consistency result relative to the likelihood benchmark; no likelihood exponent for the template is claimed.
\end{proof}
\par\smallskip\noindent \textit{Justification.} Conditional on maintained ass:jacobian-estimability for common hypothesis-independent training maps, centering annihilates the constant leaf baseline, so the displayed L4 scale gives a sharp supercritical sign-consistency condition for the newly defined template. \textit{Gap.} Zhu et al. provide a sufficient score-estimation guarantee, but neither their workflow nor any cited result analyzes this new cross-fitted diagonal-Jacobian contrast with the centered-variance calculation. \textit{Consumer.} Conditional on maintained ass:jacobian-estimability for common training maps, n C_m(delta_n)->infinity, and r_n=o(sqrt(C_m(delta_n))), it supplies a concrete sufficient scale for consistent directional decisions by this template; primitive verification remains oeq:primitive-tilted-attainability, and no likelihood exponent is claimed for published SCORE implementations.

\begin{openendedquestion}[oeq:primitive-tilted-attainability]\label{oeq:primitive-tilted-attainability}
Which primitive, verifiable conditions on a concrete two-fold nuisance-training procedure imply log max(K_{+,n},K_{-,n})=o(n C_star(delta_n)) along an admissible sequence delta_n downarrow 0 with n C_m(delta_n)->infinity?
\end{openendedquestion}
The four frozen results are proved without closing this question. In particular, prop:score-contrast-template shows that r_n=o(sqrt(C_m(delta_n))) gives pointwise sign consistency. For the unresolved exponent step, the exact bookkeeping identities are P_{+,delta_n}^n{D_n=-}=exp{-n C_star(delta_n)}K_{+,n} and P_{-,delta_n}^n{D_n=+}=exp{-n C_star(delta_n)}K_{-,n}. The rare-event diagnostic on n C_star(delta_n)/log log(n+e)->infinity yields P_{+,delta_n}^n{D_n=-}>=q_n^2 and hence log K_{+,n}>=n C_star(delta_n)-2 log log(n+e), proving only that ass:jacobian-estimability by itself cannot deliver the desired tilted-loss conclusion. Primitive sufficient conditions for a concrete training method remain open.
\par\smallskip\noindent \textit{Justification.} The tilted representation supplies a precise diagnostic, but a practitioner needs checkable training conditions that control it. \textit{Gap.} No cited score-based causal-order result translates a concrete nuisance-training algorithm into the tilted mistake-loss requirement for this mirror experiment. \textit{Consumer.} It supplies a route from the mirror likelihood benchmark to an implementable score-based order detector whose exponent can be certified.

\section*{Technical internal limitation (diagnostic only)}

For the newly defined template only, def:rare-event-nuisance-perturbation provides an explicit diagnostic on local sequences satisfying n C_star(delta_n)/log log(n+e)->infinity, equivalently n C_m(delta_n)/log log(n+e)->infinity by thm:local-geometry. The preliminary bookkeeping identities are P_{+,delta_n}^n{D_n=-}=exp(-n C_star(delta_n)) K_{+,n} and P_{-,delta_n}^n{D_n=+}=exp(-n C_star(delta_n)) K_{-,n}. Its deterministic schedules are q_n=1/log(n+e) and M_n, both independent of h, delta_n, and the unknown law P; the distinct-fold triggers are independent under P_{+,delta_n} with probability q_n, while under P_{-,delta_n} their probabilities tend to zero by uniform local tightness and the diverging threshold. The perturbed maps remain the same common h/P-independent data-measurable mappings under both hypotheses. The training-random L4 containment is Pr{||tilde J_{j,k}-J_j(P_{h,delta_n})||_4>M r_n} <= Pr(A_{n,k})+Pr{||widehat J_{j,k}-J_j(P_{h,delta_n})||_4>M r_n}, and it remains O_P because Pr(A_{n,k})->0 under both hypotheses. The construction has P_{+,delta_n}^n{D_n=-}>=q_n^2, so 0<=-log P_{+,delta_n}^n{D_n=-}/[n C_star(delta_n)]<=2 log log(n+e)/[n C_star(delta_n)]->0 and log K_{+,n}>=n C_star(delta_n)-2 log log(n+e). Thus L4 O_P control does not logically imply a positive exponent fraction uniformly over admissible instantiations of this new template, as an explicit counterexample on this faster admissible subsequence. This is not a theorem contribution, an impossibility claim for SCORE, or a claim about any published estimator.

\section{Honest scope}

The likelihood frontier and elbow are pointwise for the explicitly defined two-node mirror Gaussian-ANM path. The causal-direction functional is defined only for 0<|delta|<delta_0; P_0 is solely the common limiting law. Conditional on maintained ass:jacobian-estimability for the same hypothesis-independent training maps under both laws, the newly defined score-contrast template has sign consistency only along sequences with n C_m(delta_n)->infinity and r_n=o(sqrt(C_m(delta_n))). Its training-random L4 nuisance control does not by itself determine an exponent: the technical internal limitation gives a deterministic common-map counterexample only on the faster diagnostic subsequence n C_star(delta_n)/log log(n+e)->infinity, equivalently n C_m(delta_n)/log log(n+e)->infinity. Primitive verification remains oeq:primitive-tilted-attainability: primitive, verifiable conditions for a concrete training procedure to control the tilted losses remain open. No global uniform nonlinear-ANM constant is claimed because c_1 and c_2 have no lower envelopes over the admissible mechanisms. The result is not a score-sortability theorem for score-component variances, a broad latent-variable score-identification theorem, or a neural-score implementation result. The construction permits affine components of g; ass:nonlinear-curvature is the condition that supplies directional asymmetry. OPEN (maintained condition ass:jacobian-estimability): oeq:primitive-tilted-attainability: primitive, verifiable conditions on a concrete two-fold nuisance-training procedure that control the tilted mistake losses remain open.

\begin{thebibliography}{99}

  \bibitem{zhu2023sample} Zhu, Z., Locatello, F., and Cevher, V. (2023). Sample Complexity Bounds for Score-Matching: Causal Discovery and Generative Modeling. NeurIPS 36.

  \bibitem{rolland2022score} Rolland, P., Cevher, V., Kleindessner, M., Russell, C., Schölkopf, B., Janzing, D., and Locatello, F. (2022). Score Matching Enables Causal Discovery of Nonlinear Additive Noise Models. ICML, PMLR 162.

  \bibitem{chernoff1952measure} Chernoff, H. (1952). A Measure of Asymptotic Efficiency for Tests of a Hypothesis Based on the Sum of Observations. Annals of Mathematical Statistics 23, 493-507.

  \bibitem{hoyer2008nonlinear} Hoyer, P. O., Janzing, D., Mooij, J. M., Peters, J., and Schölkopf, B. (2008). Nonlinear Causal Discovery with Additive Noise Models. NeurIPS 21.

  \bibitem{peters2014anm} Peters, J., Mooij, J. M., Janzing, D., and Schölkopf, B. (2014). Causal Discovery with Continuous Additive Noise Models. Journal of Machine Learning Research 15, 2009-2053.

  \bibitem{koehler2023efficiency} Koehler, F., Heckett, A., and Risteski, A. (2023). Statistical Efficiency of Score Matching: The View from Isoperimetry. ICLR.

  \bibitem{montagna2023nogam} Montagna, F., Noceti, N., Rosasco, L., Zhang, K., and Locatello, F. (2023). Causal Discovery with Score Matching on Additive Models with Arbitrary Noise. CLeaR.

  \bibitem{montagna2023das} Montagna, F., Noceti, N., Rosasco, L., Zhang, K., and Locatello, F. (2023). Scalable Causal Discovery with Score Matching. Proceedings of the Second Conference on Causal Learning and Reasoning, PMLR 213, 752-771.

  \bibitem{montagna2023shortcuts} Montagna, F., Noceti, N., Rosasco, L., and Locatello, F. (2023). Shortcuts for Causal Discovery of Nonlinear Models by Score Matching. arXiv:2310.14246.

  \bibitem{montagna2025roof} Montagna, F., Faller, P. M., Blobaum, P., Kirschbaum, E., and Locatello, F. (2025). Score Matching through the Roof: Linear, Nonlinear, and Latent Variables Causal Discovery. Proceedings of the Fourth Conference on Causal Learning and Reasoning, PMLR 275, 552-605.

  \bibitem{kpotufe2014} Kpotufe, S., Sgouritsa, E., Janzing, D., and Schölkopf, B. (2014). Consistency of Causal Inference under the Additive Noise Model. ICML, PMLR 32(2), 478-486.

\end{thebibliography}

\end{document}