% =====================================================================
%  ThmSmith Stage -1 proposal skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_synth\_control\_factor\_misspec, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage_neg1_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to a Q1..Q6 pool-mode,
%    reproduce that block verbatim from
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    If it is a free-form `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_synth\_control\_factor\_misspec} / \texttt{v1}%
  \\ \large\textit{Sharp partial-identification intervals for synthetic-control effects under bounded interactive-factor misspecification}}
\author{ThmSmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
Free-form PartialID convention:
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization})=
(\texttt{pid\_synth\_control\_factor\_misspec},\texttt{v1}),\\
P=\text{the finite observed panel law for one treated unit, }J\text{ donor units,}
\ T_0\text{ pre-periods, and a fixed post-period }s,\\
\theta_s=Y^{\mathrm{obs}}_{1s}-Y_{1s}(0),\\
\text{identifying restrictions}=
\text{fixed synthetic weights }w\in\Delta_J\text{ and a bounded}
\ r\text{-factor approximation error }|u_t(w)|\le \rho,\\
\text{bounding functional}=
[Y^{\mathrm{obs}}_{1s}-S_s(w)-U_s(P,\rho),
Y^{\mathrm{obs}}_{1s}-S_s(w)-L_s(P,\rho)].
\end{gathered}
\]
Here \(S_t(w)=\sum_{j=1}^J w_jY_{j+1,t}\), \(g_t=Y^{\mathrm{obs}}_{1t}-S_t(w)\) for \(t\le T_0\), \(\rho=(1+\|w\|_1)\eta\), and
\[
[L_s(P,\rho),U_s(P,\rho)]
=\operatorname{cl}\{\lambda_s^\transpose b+u_s:
\|\Lambda_0b-g\|_\infty\le\rho,\ |u_s|\le\rho\}.
\]
The oracle version treats \(\Lambda=(\lambda_1,\ldots,\lambda_{T_0},\lambda_s)\) as the locked factor-loading bridge. The latent-dictionary conjecture replaces this fixed \(\Lambda\) by the union over all donor-panel \(r\)-factor dictionaries within sup-norm error \(\eta\).

\begin{abstract}
Synthetic control is point-identified in the Abadie--Diamond--Hainmueller factor-model argument when pre-period fit certifies exact factor balance. Empirical applications rarely have exact factor fit, and existing robustness tools often convert imperfect fit into conservative sensitivity bands rather than the sharp identified set implied by a stated misspecification budget. This proposal asks for the sharp interval of a post-treatment synthetic-control effect when the treated-minus-synthetic untreated gap is generated by an interactive-factor bridge plus a bounded sup-norm approximation error. The kernel claim is that the sharp interval is the projection of a Chebyshev-feasible factor-imbalance set, with an explicit row-span formula and a hidden-factor phase transition: post-period loadings outside the pre-period row span are not disciplined by pre-period balance unless an additional imbalance bound is imposed. Resolving the latent-dictionary conjecture would turn synthetic-control sensitivity analysis into a finite optimization problem that recovers ADH point identification when the misspecification budget is zero.
\end{abstract}

\section{Introduction}
\paragraph{Why the problem is important.}
Synthetic-control analyses often report a small pre-treatment donor--treated gap as evidence that the post-treatment synthetic counterfactual is credible. The ADH argument formalizes this when the untreated outcomes obey an exact latent factor model and the synthetic weights balance the treated unit's factor loadings \citep{AbadieDiamondHainmueller2010,Abadie2021}. The methodological question here is what remains identified when exact factor fit is replaced by a researcher-stated sup-norm error budget.

\paragraph{The main finding (proposed).}
The proposed flagship result is Conjecture~\ref{conj:latent-dictionary}: the sharp effect interval under bounded interactive-factor misspecification is obtained by taking the oracle Chebyshev interval in Theorem~\ref{thm:oracle-sharp} over every donor-panel factor dictionary compatible with the same misspecification budget. The oracle theorem already gives a concrete research object: the pre-period gap \(g\) restricts the factor imbalance \(b\) through \(\|\Lambda_0b-g\|_\infty\le \rho\), and the post-period counterfactual gap is the support function of this feasible set plus one post-period error allowance.

\paragraph{What is new.}
Closest synthetic-control sensitivity papers bound error through pre-fit diagnostics, conformal tests, augmented estimators, or matrix-completion risk controls \citep{FermanPinto2021,FirpoPossebom2018,ChernozhukovWuthrichZhu2021,BenMichaelFellerRothstein2021,AtheyBayatiDoudchenkoImbensKhosravi2021,NazaretShiBlei2024}. The novelty kernel is sharper and more structural: the proposal conditions on the full observed pre-period donor--treated gap and a sup-norm factor misspecification budget, then asks for the exact projection interval for the missing treated untreated outcome. The row-span boundary in Conjecture~\ref{conj:row-span} separates regimes where pre-period fit is informative from regimes where an unobserved post-period factor direction makes the interval unbounded without a separate imbalance cap.

\paragraph{How it positions in the literature.}
This is a partial-identification proposal, not a new exact-identification or panel-regression estimator. It follows the Manski tradition of reporting the set of counterfactual values compatible with observables and restrictions \citep{Manski1990}, but the restrictions are the latent-factor balance assumptions that motivate synthetic control \citep{AbadieDiamondHainmueller2010,Abadie2021} and generalized synthetic control \citep{Xu2017}. It is adjacent to robust synthetic-control inference and sensitivity analysis, yet the target is the sharp identified interval rather than a confidence set for a point estimand.

\paragraph{Implications for the community.}
If the kernel resolves favorably, applied researchers using ADH-style weights in settings like the California tobacco application of \citet{AbadieDiamondHainmueller2010} can report the exact treatment-effect interval implied by a declared factor-misspecification budget instead of a placebo-calibrated or ad hoc robustness range.

\paragraph{How research benefits from the conclusion.}
A researcher should report whether the post-period factor bridge is in the pre-period row span and should replace ``good pre-fit implies point credibility'' by the sharp interval \(Y^{\mathrm{obs}}_{1s}-S_s(w)-[L_s,U_s]\) under the chosen error budget.

\section{Related work}
\citet{AbadieDiamondHainmueller2010} is the closest foundational anchor: it justifies synthetic-control point identification under an exact factor model and exact balance, while this proposal asks for the sharp interval when the factor model is only approximately true. \citet{Abadie2021} clarifies feasibility and data requirements for synthetic controls; the row-span condition below formalizes one such feasibility boundary for bounded misspecification. \citet{AbadieGardeazabal2003} is the original applied synthetic-control template, motivating why a transparent interval for the missing untreated path matters in single-treated-unit designs. \citet{FermanPinto2021} studies imperfect pre-treatment fit and inference; the present proposal differs by conditioning on the full pre-gap vector and deriving the sharp set implied by a deterministic factor-error budget. \citet{FirpoPossebom2018} develops sensitivity analysis for synthetic controls; this proposal replaces sensitivity parameters calibrated to departures from assumptions by a sharp partial-ID functional. \citet{BenMichaelFellerRothstein2021} shows how augmentation reduces bias under imperfect fit, whereas the present interval treats the remaining factor approximation error as part of the identifying restriction. \citet{DoudchenkoImbens2016} connects synthetic control, regression, and balancing weights; the fixed-weight convention here can be read as a partial-ID analysis of any such chosen weight vector. \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} studies matrix-completion estimators for causal panels; the latent-dictionary conjecture asks for the sharp missing-entry set under a sup-norm low-rank approximation rather than an estimator risk bound. \citet{Xu2017} fits interactive fixed effects in comparative case studies, providing the factor-model thread whose misspecification is made explicit here. \citet{ArkhangelskyAtheyHirshbergImbensWager2021} combines synthetic-control and DID ideas; it is relevant because it regularizes imperfect balance but does not characterize the sharp counterfactual interval. \citet{ChernozhukovWuthrichZhu2021} gives conformal inference for synthetic controls; that is an inferential wrapper around prediction errors, not a deterministic identified-set characterization. \citet{NazaretShiBlei2024} gives theoretical bounds for misspecification of the linear synthetic-control assumption and proposes estimators to reduce it; the present proposal isolates the deterministic partial-ID geometry left by a declared error budget.

The in-repository ThmSmith catalogue, summarized in \texttt{ThmSmith/doc/API.md}, contains rich panel-regression proposals such as Q1 minimal-basis, Q1 sign-flip, and Q1 spectral-threshold results, but it records no PartialID synthetic-control entry. The ExactID and PartialID catalogue sections are seed-time empty, so the closest in-catalogue prior art is only structural: panel results about regression contamination rather than sharp partial identification of a missing synthetic-control counterfactual.

\section{Formal setup}
There is one treated unit \(i=1\), \(J\) donor units \(i=2,\ldots,J+1\), pre-periods \(t=1,\ldots,T_0\), and a post-period \(s>T_0\). The observable law \(P\) is the finite panel consisting of all donor outcomes in periods \(1,\ldots,T_0,s\), treated outcomes in periods \(1,\ldots,T_0\), and the treated observed post-treatment outcome \(Y^{\mathrm{obs}}_{1s}\). The unobserved scalar is \(Y_{1s}(0)\), and the parameter is \(\theta_s=Y^{\mathrm{obs}}_{1s}-Y_{1s}(0)\).

Fix synthetic weights \(w\in\Delta_J\) and define \(S_t(w)=\sum_{j=1}^Jw_jY_{j+1,t}\). The observed pre-gap is \(g=(g_1,\ldots,g_{T_0})^\transpose\), where \(g_t=Y^{\mathrm{obs}}_{1t}-S_t(w)\). The unobserved post-gap is \(h_s=Y_{1s}(0)-S_s(w)\). For a factor dimension \(r\), let \(\lambda_t\in\R^r\), let \(\Lambda_0\in\R^{T_0\times r}\) have rows \(\lambda_t^\transpose\), and let \(b\in\R^r\) denote the treated-minus-synthetic factor loading imbalance. The oracle misspecification restriction is
\[
g=\Lambda_0b+u_0,\qquad h_s=\lambda_s^\transpose b+u_s,\qquad
\|u_0\|_\infty\le\rho,\quad |u_s|\le\rho,
\]
where \(\rho=(1+\|w\|_1)\eta\) is the induced treated-minus-synthetic gap budget when each unit-level factor approximation error is bounded by \(\eta\). The identified set for \(h_s\) is \([L_s(P,\rho),U_s(P,\rho)]\), and the identified set for \(\theta_s\) is
\[
\Theta_I(P)=
[Y^{\mathrm{obs}}_{1s}-S_s(w)-U_s(P,\rho),
Y^{\mathrm{obs}}_{1s}-S_s(w)-L_s(P,\rho)].
\]

\begin{quote}
\begin{verbatim}
Free-form PartialID convention:
(qid, specialization) =
(pid_synth_control_factor_misspec, v1).
P = finite observed synthetic-control panel law with one treated unit,
    J donors, T0 pre-periods, and a fixed post-period s.
theta_s = Yobs_1s - Y_1s(0).
Identifying restrictions = fixed weights w in Delta_J and bounded
    r-factor approximation error |u_t(w)| <= rho, rho=(1+||w||_1) eta.
Bounding functional =
    [Yobs_1s - S_s(w) - U_s(P,rho),
     Yobs_1s - S_s(w) - L_s(P,rho)].
\end{verbatim}
\end{quote}

\section{Assumptions}
\begin{assumption}[Observed synthetic-control panel]\label{ass:panel}
The observed law \(P\) contains the donor panel \(Y_{j+1,t}\) for \(j=1,\ldots,J\) and \(t\in\{1,\ldots,T_0,s\}\), the treated pre-period untreated outcomes \(Y^{\mathrm{obs}}_{1t}=Y_{1t}(0)\) for \(t\le T_0\), and the treated post-treatment outcome \(Y^{\mathrm{obs}}_{1s}\).
\end{assumption}

\begin{assumption}[Fixed synthetic weights]\label{ass:weights}
The weights \(w\in\Delta_J\) are fixed as part of the design being evaluated, and \(S_t(w)=\sum_{j=1}^Jw_jY_{j+1,t}\) is observed for every \(t\in\{1,\ldots,T_0,s\}\).
\end{assumption}

\begin{assumption}[Oracle bounded factor-bridge misspecification]\label{ass:oracle-budget}
For known factor loadings \(\Lambda_0\in\R^{T_0\times r}\) and \(\lambda_s\in\R^r\), there exist \(b\in\R^r\), \(u_0\in\R^{T_0}\), and \(u_s\in\R\) such that \(g=\Lambda_0b+u_0\), \(h_s=\lambda_s^\transpose b+u_s\), \(\|u_0\|_\infty\le\rho\), and \(|u_s|\le\rho\).
\end{assumption}

\begin{assumption}[Pre-period compatibility]\label{ass:compat}
The Chebyshev feasible set \(B(P,\rho)=\{b\in\R^r:\|\Lambda_0b-g\|_\infty\le\rho\}\) is nonempty.
\end{assumption}

\begin{assumption}[Row-span post bridge]\label{ass:rowspan}
There exists \(a_s\in\R^{T_0}\) such that \(\lambda_s^\transpose=a_s^\transpose\Lambda_0\).
\end{assumption}

\begin{assumption}[Bounded imbalance cap]\label{ass:imbalance-cap}
When the row-span bridge is not imposed, the sensitivity model may additionally impose \(\|b\|_\infty\le B\) for a declared finite \(B\).
\end{assumption}

\begin{assumption}[Latent donor-dictionary feasibility]\label{ass:latent-dictionary}
The loading dictionary \(\Lambda\) is not fixed ex ante. It ranges over the set \(\mathcal{D}_r(P,\eta)\) of tuples \((\delta_t,\lambda_t,\mu_i,e_{it})\) with \(\lambda_t,\mu_i\in\R^r\), observed donor equations \(Y_{j+1,t}=\delta_t+\lambda_t^\transpose\mu_{j+1}+e_{j+1,t}\) for \(j=1,\ldots,J\) and \(t\in\{1,\ldots,T_0,s\}\), treated pre-period equations \(Y^{\mathrm{obs}}_{1t}=\delta_t+\lambda_t^\transpose\mu_1+e_{1t}\) for \(t\le T_0\), and \(|e_{it}|\le\eta\) on every observed equation. For each tuple, \(b=\mu_1-\sum_{j=1}^Jw_j\mu_{j+1}\) and the induced treated-minus-synthetic gap budget is \(\rho=(1+\|w\|_1)\eta\).
\end{assumption}

\begin{assumption}[Exact ADH corner]\label{ass:adh-corner}
The misspecification budget is \(\eta=0\), the pre-period synthetic gap is \(g=0\), and Assumption~\ref{ass:rowspan} holds for the post-period loading.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: oracle sharp Chebyshev interval]\label{thm:oracle-sharp}
Under Assumptions~\ref{ass:panel}--\ref{ass:compat}, the sharp identified set for the post-period untreated synthetic gap is
\[
[L_s(P,\rho),U_s(P,\rho)]
=\operatorname{cl}\{\lambda_s^\transpose b+u_s:
b\in B(P,\rho),\ |u_s|\le\rho\}.
\]
Equivalently,
\[
L_s(P,\rho)=\inf_{b:\|\Lambda_0b-g\|_\infty\le\rho}\lambda_s^\transpose b-\rho,
\quad
U_s(P,\rho)=\sup_{b:\|\Lambda_0b-g\|_\infty\le\rho}\lambda_s^\transpose b+\rho.
\]
The sharp identified set for \(\theta_s\) is
\[
\Theta_I(P)=
[Y^{\mathrm{obs}}_{1s}-S_s(w)-U_s(P,\rho),
Y^{\mathrm{obs}}_{1s}-S_s(w)-L_s(P,\rho)].
\]
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) \citet{FermanPinto2021}, \citet{FirpoPossebom2018}, and \citet{ChernozhukovWuthrichZhu2021} use imperfect fit for inference or sensitivity, while Theorem~\ref{thm:oracle-sharp} states the deterministic sharp set implied by a factor-error budget and the full pre-gap vector. \citet{NazaretShiBlei2024} bounds misspecification of the linear synthetic-control assumption, but does not give this Chebyshev projection interval as the target parameter. (b) Resolving and formalizing this theorem gives applied ADH-style analyses, including \citet{AbadieDiamondHainmueller2010}, a directly reportable interval for any declared \(\eta\).

\begin{conjecture}[Conjecture 1: row-span formula and hidden-factor phase transition (NOT YET PROVED)]\label{conj:row-span}
Under Assumptions~\ref{ass:panel}--\ref{ass:compat}, if Assumption~\ref{ass:rowspan} holds with \(a_s^\transpose\Lambda_0=\lambda_s^\transpose\), then the oracle interval in Theorem~\ref{thm:oracle-sharp} collapses to the closed form
\[
[L_s(P,\rho),U_s(P,\rho)]
=
[a_s^\transpose g-\rho(1+\|a_s\|_1),
a_s^\transpose g+\rho(1+\|a_s\|_1)].
\]
If Assumption~\ref{ass:rowspan} fails and no Assumption~\ref{ass:imbalance-cap} is imposed, the interval is unbounded in at least one direction whenever \(B(P,\rho)\) has nonempty relative interior. With Assumption~\ref{ass:imbalance-cap}, the finite endpoints are obtained by adding the support function of \(B(P,\rho)\cap[-B,B]^r\) in the direction \(\lambda_s\).
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{Abadie2021} emphasizes feasibility and pre-treatment fit, but the proposed phase transition pinpoints a sharper algebraic boundary: the post-period loading must be representable by pre-period loadings for pre-fit to control the post gap without an imbalance cap. This differs from augmented and matrix-completion work \citep{BenMichaelFellerRothstein2021,AtheyBayatiDoudchenkoImbensKhosravi2021}, which regularizes prediction rather than describing when the identified set becomes unbounded. (b) The concrete consumer is robustness reporting for ADH-style applications: the analyst learns whether an interval is finite because of pre-period evidence or only because an extra cap \(B\) was imposed.

\begin{conjecture}[Conjecture 2: latent-dictionary sharpness (NOT YET PROVED)]\label{conj:latent-dictionary}
Under Assumptions~\ref{ass:panel}, \ref{ass:weights}, and \ref{ass:latent-dictionary}, the sharp identified set for \(h_s\) is the closure of the union of the oracle intervals from Theorem~\ref{thm:oracle-sharp} over all donor-panel \(r\)-factor dictionaries satisfying the same sup-norm error budget. Equivalently, the endpoints are the optimal values of the rank-constrained Chebyshev completion programs obtained by optimizing \(Y_{1s}(0)-S_s(w)\) over all completed untreated panels within sup-norm distance \(\eta\) of an \(r\)-factor interactive fixed-effect matrix.
\end{conjecture}

\paragraph{Why this is new and worth studying.}
(a) \citet{Xu2017} and \citet{AtheyBayatiDoudchenkoImbensKhosravi2021} estimate latent factor or low-rank counterfactuals, and \citet{NazaretShiBlei2024} studies misspecification of the linear synthetic-control assumption, but none states the exact union-over-dictionaries sharp identified set for a bounded sup-norm low-rank approximation. (b) The named downstream consumer is the misspecification-bounds program of \citet{NazaretShiBlei2024}: the conjecture supplies the deterministic target set that such bounds should cover.

\begin{theorem}[Theorem 2: exact ADH point-identification corner]\label{thm:adh-corner}
Under Assumptions~\ref{ass:panel}--\ref{ass:compat} and \ref{ass:adh-corner}, the interval in Theorem~\ref{thm:oracle-sharp} is \([0,0]\). Hence \(\Theta_I(P)=\{Y^{\mathrm{obs}}_{1s}-S_s(w)\}\), the usual synthetic-control point estimate.
\end{theorem}

\paragraph{Why this is new and worth studying.}
(a) This is not a new claim relative to \citet{AbadieDiamondHainmueller2010}; it is the required sharpness check showing that the partial-ID proposal nests the exact ADH factor-balance argument. (b) It benefits users of \citet{AbadieDiamondHainmueller2010} by making the reported interval continuous with the standard point estimate as \(\eta\downarrow0\).

\section{Sanity-check corollaries}
\begin{corollary}[Exact pre-fit reduction]\label{cor:exact-prefit}
Under Assumptions~\ref{ass:panel}--\ref{ass:rowspan}, if \(g=0\), then Conjecture~\ref{conj:row-span} reduces to
\[
[L_s(P,\rho),U_s(P,\rho)]
=[-\rho(1+\|a_s\|_1),\rho(1+\|a_s\|_1)].
\]
In particular, Assumption~\ref{ass:adh-corner} sends this interval to \([0,0]\).
\end{corollary}

\begin{corollary}[Single-factor two-pre-period bridge]\label{cor:single-factor}
Under Assumptions~\ref{ass:panel}--\ref{ass:rowspan} with \(r=1\), \(T_0=1\), and \(\lambda_1\ne0\), the row-span coefficient is \(a_s=\lambda_s/\lambda_1\), so the proposed interval is centered at \((\lambda_s/\lambda_1)g_1\) with radius \(\rho(1+|\lambda_s/\lambda_1|)\).
\end{corollary}

\section{Proof-sketch route}
The oracle theorem is a projection argument: write the model restrictions as a finite-dimensional feasible set in \((b,u_0,u_s)\), eliminate \(u_0\) to obtain the Chebyshev slab \(\|\Lambda_0b-g\|_\infty\le\rho\), and optimize the linear functional \(\lambda_s^\transpose b+u_s\). The row-span formula follows from \(a_s^\transpose\Lambda_0b=a_s^\transpose(g-u_0)\) and the dual norm identity \(\sup_{\|u_0\|_\infty\le\rho}a_s^\transpose u_0=\rho\|a_s\|_1\); the failure of row-span is checked by moving \(b\) along a null direction of \(\Lambda_0\) with nonzero \(\lambda_s^\transpose b\). The latent-dictionary conjecture needs a rank-constrained Chebyshev completion argument: show that every feasible completed panel induces an oracle dictionary interval and, conversely, every oracle endpoint can be embedded in a donor-panel factorization without adding hidden cross-period restrictions. Boundary cases to compute explicitly are \(T_0=r\) with invertible \(\Lambda_0\), \(r=1,T_0=1\), and the \(\eta=0,g=0\) ADH corner.

\section{Honest scope flags}
The oracle interval and exact ADH corner are stated as theorems because they reduce to finite-dimensional optimization and algebra. The row-span phase transition is labelled a conjecture because the final version must specify the exact topological condition on \(B(P,\rho)\) for unboundedness and handle empty-interior slabs cleanly. The latent-dictionary union is the main open kernel: it may require an additional normalization of factor dictionaries or a compactness assumption to avoid pathological rank-factor representations. This v1 does not claim sampling inference, estimator consistency, or a data-driven rule for choosing \(\eta\), \(r\), \(w\), or \(\Lambda\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Abadie and Gardeazabal(2003)]{AbadieGardeazabal2003}
Abadie, A. and Gardeazabal, J. (2003).
The economic costs of conflict: A case study of the Basque Country.
\emph{American Economic Review} 93(1), 113--132.

\bibitem[Abadie, Diamond, and Hainmueller(2010)]{AbadieDiamondHainmueller2010}
Abadie, A., Diamond, A., and Hainmueller, J. (2010).
Synthetic control methods for comparative case studies: Estimating the effect of California's tobacco control program.
\emph{Journal of the American Statistical Association} 105(490), 493--505.

\bibitem[Abadie(2021)]{Abadie2021}
Abadie, A. (2021).
Using synthetic controls: Feasibility, data requirements, and methodological aspects.
\emph{Journal of Economic Literature} 59(2), 391--425.

\bibitem[Arkhangelsky et~al.(2021)]{ArkhangelskyAtheyHirshbergImbensWager2021}
Arkhangelsky, D., Athey, S., Hirshberg, D. A., Imbens, G. W., and Wager, S. (2021).
Synthetic difference-in-differences.
\emph{American Economic Review} 111(12), 4088--4118.

\bibitem[Athey et~al.(2021)]{AtheyBayatiDoudchenkoImbensKhosravi2021}
Athey, S., Bayati, M., Doudchenko, N., Imbens, G., and Khosravi, K. (2021).
Matrix completion methods for causal panel data models.
\emph{Journal of the American Statistical Association} 116(536), 1716--1730.

\bibitem[Ben-Michael, Feller, and Rothstein(2021)]{BenMichaelFellerRothstein2021}
Ben-Michael, E., Feller, A., and Rothstein, J. (2021).
The augmented synthetic control method.
\emph{Journal of the American Statistical Association} 116(536), 1789--1803.

\bibitem[Chernozhukov, Wuthrich, and Zhu(2021)]{ChernozhukovWuthrichZhu2021}
Chernozhukov, V., Wuthrich, K., and Zhu, Y. (2021).
An exact and robust conformal inference method for counterfactual and synthetic controls.
\emph{Journal of the American Statistical Association} 116(536), 1849--1864.

\bibitem[Doudchenko and Imbens(2016)]{DoudchenkoImbens2016}
Doudchenko, N. and Imbens, G. W. (2016).
Balancing, regression, difference-in-differences and synthetic control methods: A synthesis.
NBER Working Paper 22791.

\bibitem[Ferman and Pinto(2021)]{FermanPinto2021}
Ferman, B. and Pinto, C. (2021).
Synthetic controls with imperfect pre-treatment fit.
\emph{Quantitative Economics} 12(4), 1197--1221.

\bibitem[Firpo and Possebom(2018)]{FirpoPossebom2018}
Firpo, S. and Possebom, V. (2018).
Synthetic control method: Inference, sensitivity analysis and confidence sets.
\emph{Journal of Causal Inference} 6(2).

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Nazaret, Shi, and Blei(2024)]{NazaretShiBlei2024}
Nazaret, A. O. R., Shi, C., and Blei, D. M. (2024).
On the misspecification of linear assumptions in synthetic controls.
\emph{Proceedings of The 27th International Conference on Artificial Intelligence and Statistics}, PMLR 238, 3790--3798.

\bibitem[Xu(2017)]{Xu2017}
Xu, Y. (2017).
Generalized synthetic control method: Causal inference with interactive fixed effects models.
\emph{Political Analysis} 25(1), 57--76.
\end{thebibliography}

\end{document}
