% =====================================================================
%  ThmSmith Stage 0 derivation skeleton.
%  Written automatically by the ThmSmith TS pipeline before Stage 0 runs.
%  Locked parameters: qid=pid\_synth\_control\_factor\_misspec, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; downstream stages (0.5 reviewer,
%    Stage 1, Stage 4d) grep for these section titles and macros.
%  - Each section contains exactly one `% TODO(stage0 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `ThmSmith/tools/src/prompts/stage0_outputFormat.txt`.
%  - The `\paragraph{Locked parameters.}` block inside Formal setup must
%    pin the convention precisely. For Panel anchors mapped to a Q1..Q6
%    pool-mode, fill it VERBATIM from the question-specific block of
%    `ThmSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`.
%    For free-form panel / ExactID / PartialID anchors, reproduce the
%    locked-parameter block from the Stage -1 proposal verbatim. Do not
%    rephrase locked parameters; Stage 1 quotes them.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage 0 derivation: \texttt{pid\_synth\_control\_factor\_misspec} / \texttt{v1}%
  \\ \large\textit{Sharp Chebyshev bounds for synthetic control under bounded factor misspecification}}
\author{ThmSmith Stage 0 solver}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\begin{abstract}
This note studies partial identification of the one-period synthetic-control
counterfactual \(\theta=Y_{0s}(0)\) when a fixed donor-weight vector leaves a
signed pre-period gap \(g\) and the linear-factor approximation error is bounded
in sup norm.  The estimand-defining functional is the Chebyshev support interval
\[
\theta_L(P)=y_s^w+\inf_{\|g-X\Delta\|_\infty\le\rho}b^\transpose\Delta-\rho,
\qquad
\theta_U(P)=y_s^w+\sup_{\|g-X\Delta\|_\infty\le\rho}b^\transpose\Delta+\rho,
\]
where \(\rho=(1+\|w\|_1)\eta\).  A support-function proposition proves that this
interval is the sharp identified set for \(\theta\), with finite attained
endpoints exactly when the post bridge \(b\) is visible in the row span of \(X\).
The field-level result is a primitive active-basis scalar nonsharpness theorem:
on any open LP cell where the active pre-period constraints form a nonsingular
basis with strict complementarity, the sharp support endpoint is an affine
function of the signed pre-gap vector.  If the resulting bridge weight is not
collinear with the gradient of a scalar pre-fit report, exact same-scalar
perturbations change the sharp endpoint to first order.  Thus RMSPE-level
reporting workflows can remain useful diagnostics, but deterministic sharp
factor-misspecification reporting must carry the signed vector information
encoded by the centered support endpoint map \(H^c(P)\).
\end{abstract}

\section{Introduction}
Synthetic control asks whether a donor-weighted untreated path can stand in for
the missing untreated outcome of a treated unit.  Exact pre-treatment fit is the
cleanest case, but applied work usually has a nonzero pre-period gap, and the
causal question then becomes a partial-identification question: which untreated
post-period values remain compatible with the signed pre-gap vector and a
declared factor-model misspecification budget?

The usual scalar summaries of imperfect fit, especially RMSPE and post/pre
RMSPE ratios, are useful diagnostics for reporting and placebo-style inference.
They do not, by themselves, record the direction in which the pre-gap points
relative to the post-period factor bridge.  In a linear-factor model this
direction matters, because only components of the latent imbalance that are
visible through the pre-period dictionary can be transported to the post-period
counterfactual.

This note first proves the exact finite-dimensional partial-identification
formula.  The feasible latent imbalances form a Chebyshev tube
\[
K(P)=\{\Delta\in\R^r:\|g-X\Delta\|_\infty\le\rho\},
\]
and the sharp counterfactual interval is obtained by minimizing and maximizing
the bridge \(b^\transpose\Delta\) over that tube and then adding the remaining
post-period error budget.  This projection formula is standard convex geometry;
its role here is to define the deterministic object whose scalar compressions
are being tested.

The new contribution is the scalarization obstruction on primitive open LP
cells.  Suppose a set \(A\) of \(r\) active pre-period bounds has nonsingular
row matrix \(X_A\), active signs \(\sigma_A\in\{-1,1\}^A\), strict slack on the
inactive bounds, and strict complementarity
\(\sigma_i\beta_i>0\) for
\(\beta_A=X_A^{-\transpose}b\).  Then throughout the same open cell,
\[
h_+(g)=\beta_A^\transpose(g_A+\rho\sigma_A),
\]
so the endpoint sensitivity is derived directly from the primitive active
basis rather than assumed as an anisotropic derivative.  If the extended bridge
weight \(\beta_0\) is not collinear with the gradient of an RMSPE-level
statistic, there are exact same-scalar perturbations of the signed pre-gap
vector that change the sharp endpoint to first order.  The result is useful for
theory and formula design because it separates three objects that are often
conflated: the causal target \(\theta=Y_{0s}(0)\), the observable post gap
\(d\), and the deterministic support interval implied by the signed pre-gap
vector.

\paragraph{Motivating conjecture(s).}
Conjecture 1: fixed scalar pre-fit reporting is generically nonsharp for deterministic factor misspecification (NOT YET PROVED)
Fix \(q\in\mathcal Q\). Under Assumptions~\ref{ass:fixed-weights}, \ref{ass:bounded-factor}, \ref{ass:nonempty}, \ref{ass:bridge-visible}, \ref{ass:scalar-class}, and \ref{ass:anisotropic}, there is an \(\varepsilon_0>0\) such that for every sufficiently small \(0<\varepsilon<\varepsilon_0\) one can find two observable laws \(P_\varepsilon^+\) and \(P_\varepsilon^-\) in the same open design class with \(q(g_\varepsilon^+)=q(g_\varepsilon^-)\) but
\[
\left|\sup_{\Delta\in K(P_\varepsilon^+)}b^\transpose\Delta
-\sup_{\Delta\in K(P_\varepsilon^-)}b^\transpose\Delta\right|
\ge c\varepsilon
\]
for some \(c>0\) determined by the directional LP slopes. Hence no \(q\)-scalar pre-fit calibration \(I_{\psi,q}(P)\) is both valid and sharp on that open class; at least one of the two laws receives deterministic centered-endpoint excess of order \(\varepsilon\). The witness pair is constructible by moving along the \(q\)-level tangent direction \(v\) and solving the two endpoint LPs.

Conjecture 2: support-function calibration is minimally sharp (NOT YET PROVED)
Under Assumptions~\ref{ass:fixed-weights}, \ref{ass:bounded-factor}, \ref{ass:nonempty}, \ref{ass:bridge-visible}, and \ref{ass:endpoint-sufficient}, let \(\mathcal U\) be any open class on which the sharp centered interval for \(\theta-y_s^w\) is finite. If an interval rule depending on a statistic \(S(P)\) is valid and sharp for \(\theta-y_s^w\) for every \(P\in\mathcal U\), then \(S\) must be centered-endpoint-sufficient on \(\mathcal U\): for every \(P,P'\in\mathcal U\),
\[
S(P)=S(P')\quad\Longrightarrow\quad H^c(P)=H^c(P').
\]
Equivalently, the sharp centered endpoint map \(H^c\) factors through \(S\) on \(\mathcal U\). For uncentered intervals for \(\theta\), the necessary statistic is \((y_s^w,H^c(P))\) or any equivalent statistic that fixes the \(y_s^w\) shift as well. In particular, a scalar norm \(q(g)\) can be sharp only on classes where \(H^c(P)\) is constant along the \(q\)-level sets after fixing \(y_s^w\).

\section{Related work and positioning}
\cite{AbadieGardeazabal2003} introduced the synthetic-control case-study design
and motivates the single treated-unit counterfactual target used here.
\cite{AbadieDiamondHainmueller2010} gave the canonical linear-factor
justification for synthetic control under exact or sufficiently good pre-fit;
the support-form proposition below recovers its exact-fit point-identification
corner but treats imperfect pre-fit as a deterministic partial-identification
problem.
\cite{Abadie2021} surveys feasibility conditions, placebo inference, and
post/pre RMSPE reporting.  \cite{FirpoPossebom2018} develops RMSPE-based
inference, sensitivity analysis, and confidence sets, including modified RMSPE
weighting.  Those papers motivate the scalar \(q_{\mathrm{rms}}\) used in the
comparison, but they are not treated as making a deterministic sharp
partial-identification claim.  The negative result below targets the broader
mathematical class of deterministic interval rules that retain the signed
pre-gap \(g\) only through \(q(g)\); the published RMSPE workflows are examples
of why that scalar is a natural diagnostic to examine, not the object being
refuted.
\cite{FermanPinto2021} studies how imperfect pre-treatment fit changes the
properties of synthetic-control estimators, while this note characterizes the
set of counterfactual values compatible with a fixed misspecification budget.

\cite{CattaneoFengTitiunik2021} and \cite{ChernozhukovWuthrichZhu2021}
construct prediction and conformal inference procedures for synthetic controls;
those are sampling or prediction-coverage objects, whereas this note isolates
the deterministic identified set before sampling uncertainty is layered on.
\cite{BenMichaelFellerRothstein2021},
\cite{ArkhangelskyAtheyHirshbergImbensWager2021}, and
\cite{AtheyBayatiDoudchenkoImbensKhosravi2021} give augmented, regularized, and
matrix-completion approaches to latent-factor panel prediction; those methods
stabilize estimation but do not replace the support calculation for a declared
misspecification class.

\cite{NazaretShiBlei2024} analyzes misspecification of linear assumptions in
synthetic controls and provides related bounds on misspecification error; the
distinctive feature here is sharp compatibility with the observed signed
pre-gap vector.  \cite{ZeitlerVlontzosGilliganLee2023} studies nonparametric
identifiability and sensitivity analysis for synthetic-control models under
invariant mechanisms; the present note instead fixes a finite-dimensional
factor dictionary and computes the support of its Chebyshev compatibility tube.
\cite{Manski1990} and \cite{BalkePearl1997} are the classical
partial-identification comparators: both show that sharp bounds are projections
of feasible latent structures, and the Chebyshev interval below is the analogous
projection for bounded factor misspecification.  The novelty beyond that
standard support calculation is the active-basis scalarization theorem.  It
derives endpoint sensitivity from rank, strict-slack, strict-complementarity,
and noncollinearity conditions on \((X,b,\rho,q,g_0)\), rather than assuming the
endpoint derivative or the anisotropic conclusion.  The Stage -1 proposal for
this qid supplies the locked tuple and the two conjectures above; this Stage 0
note confirms Conjecture 1 on primitive active-basis open cells and confirms
Conjecture 2 as a necessary-statistic proposition rather than as the
field-level contribution.

\section{Formal setup}
There is one treated unit \(0\), donor units \(j=1,\ldots,J\), pre-periods
\(t=1,\ldots,T_0\), and one post-period \(s\).  The donor weights
\(w=(w_1,\ldots,w_J)\in\R^J\) are fixed before the bound is evaluated.  The
observable map takes the treated and donor outcomes, the fixed weights, the
factor dictionary, and the error budget to
\[
P=(g,d,y_s^w,w,X,b,\eta),
\]
where
\[
g_t=Y_{0t}^{\mathrm{obs}}-\sum_{j=1}^Jw_jY_{jt}^{\mathrm{obs}},
\qquad
y_s^w=\sum_{j=1}^Jw_jY_{js}^{\mathrm{obs}},
\qquad
d=Y_{0s}^{\mathrm{obs}}-y_s^w.
\]
The matrix \(X\in\R^{T_0\times r}\) has row \(X_t^\transpose\) at pre-period
\(t\), \(b\in\R^r\) is the post-period factor bridge, and \(\eta\ge0\) is the
unit-level sup-norm approximation-error budget.  The locked parameter
\[
\rho=(1+\|w\|_1)\eta
\]
is the induced treated-minus-synthetic gap budget, because a treated error and
the weighted donor errors can accumulate by at most \((1+\|w\|_1)\eta\).

The unobserved scalar parameter is the untreated post-period counterfactual
\(\theta=Y_{0s}(0)\).  A candidate completion is a latent imbalance
\(\Delta\in\R^r\), a pre-period error vector \(e_{\mathrm{pre}}\in\R^{T_0}\),
and a post-period error \(e_s\in\R\) satisfying
\[
g=X\Delta+e_{\mathrm{pre}},\qquad
\|e_{\mathrm{pre}}\|_\infty\le\rho,\qquad
\theta-y_s^w=b^\transpose\Delta+e_s,\qquad
|e_s|\le\rho.
\]
Thus the maintained restrictions carve out the identified set
\[
\Theta_I(P)=
\{\theta\in\R:\exists \Delta\in\R^r,\ \|g-X\Delta\|_\infty\le\rho,\ 
|\theta-y_s^w-b^\transpose\Delta|\le\rho\}.
\]
Write
\[
K(P)=\{\Delta\in\R^r:\|g-X\Delta\|_\infty\le\rho\}
\]
for the Chebyshev compatibility tube.  Boundary conventions are standard:
when \(K(P)=\emptyset\), the maintained restrictions are inconsistent and
\(\Theta_I(P)=\emptyset\); under the nonempty-tube assumption below, endpoints
are understood in the extended real line unless bridge visibility is imposed.

\paragraph{Locked parameters.}
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization})
  =(\texttt{pid\_synth\_control\_factor\_misspec},\texttt{v1}),\\
P=(g,d,y_s^w,w,X,b,\eta),\qquad
\theta=Y_{0s}(0),\\
\text{identifying restrictions: fixed synthetic-control weights }w,\;
\rho=(1+\|w\|_1)\eta,\;\exists \Delta\in\R^r
\text{ such that }\|g-X\Delta\|_\infty\le \rho,\\
\text{and } |\theta-y_s^w-b^\transpose \Delta|\le \rho,\\
\text{bounding functional: }
\Theta_I(P)=y_s^w+
\left[
\inf_{\|g-X\Delta\|_\infty\le\rho}b^\transpose\Delta-\rho,\;
\sup_{\|g-X\Delta\|_\infty\le\rho}b^\transpose\Delta+\rho
\right].
\end{gathered}
\]

\section{Assumptions}
\begin{assumption}[Fixed weights and observed gap]\label{ass:fixed-weights}
The weight vector \(w\in\R^J\), pre-gap vector \(g\in\R^{T_0}\), post synthetic
outcome \(y_s^w\), observed post gap \(d\), dictionary
\((X,b)\in\R^{T_0\times r}\times\R^r\), and error budget \(\eta\ge0\) are fixed
components of the observable law \(P\).  All displayed vectors and matrices are
finite-dimensional real objects.
\end{assumption}

\begin{assumption}[Bounded factor approximation]\label{ass:bounded-factor}
There are latent factor loadings \(\mu_i\in\R^r\) and untreated approximation
errors \(u_{it}\) with \(|u_{it}|\le\eta\) such that the treated-minus-synthetic
untreated gaps satisfy \(g=X\Delta+e_{\mathrm{pre}}\) and
\(\theta-y_s^w=b^\transpose\Delta+e_s\), where
\(\Delta=\mu_0-\sum_jw_j\mu_j\), \(\|e_{\mathrm{pre}}\|_\infty\le\rho\),
\(|e_s|\le\rho\), and \(\rho=(1+\|w\|_1)\eta\).
\end{assumption}

\begin{assumption}[Nonempty compatibility tube]\label{ass:nonempty}
The Chebyshev tube \(K(P)=\{\Delta\in\R^r:\|g-X\Delta\|_\infty\le\rho\}\) is
nonempty.
\end{assumption}

\begin{assumption}[Finite bridge visibility]\label{ass:bridge-visible}
The post bridge \(b\) lies in the row span of \(X\).  Equivalently,
\(b^\transpose v=0\) for every \(v\in\ker(X)\), so the linear functional
\(\Delta\mapsto b^\transpose\Delta\) is bounded above and below on every
nonempty tube \(K(P)\).
\end{assumption}

\begin{assumption}[Exact-fit ADH corner]\label{ass:exact-corner}
The approximation budget is \(\eta=0\), the pre-fit is exact \(g=0\), and
\(b\in\operatorname{rowspan}(X)\).
\end{assumption}

\begin{assumption}[Scalar-calibration class]\label{ass:scalar-class}
Let
\[
 \mathcal Q=\{q_2,q_\infty,q_{\mathrm{rms}}\},\qquad
 q_2(g)=\|g\|_2,\quad q_\infty(g)=\|g\|_\infty,\quad
 q_{\mathrm{rms}}(g)=T_0^{-1/2}\|g\|_2 .
\]
For a fixed \(q\in\mathcal Q\), a \(q\)-scalar pre-fit calibration is any
interval rule \(I_{\psi,q}(P)\) whose non-exact-fit component depends on \(g\)
only through \(q(g)\), together with \((X,b,w,\eta)\), and is required to
contain the sharp interval for every \(g\) in an open neighbourhood of the
observable law under study.  The statistic \(q_{\mathrm{rms}}\) is the
pre-period RMSPE component of the post/pre RMSPE statistic surveyed in
\cite{Abadie2021} and of the modified RMSPE statistic in
\cite{FirpoPossebom2018}.  These references name a widely used scalar
diagnostic; the negative target is the mathematical class of deterministic
\(q(g)\)-only interval rules, not the placebo or inference procedures in those
papers and not a claim that those papers assert sharp deterministic
factor-misspecification identification from that scalar.
\end{assumption}

\begin{assumption}[Primitive active-basis \(q\)-anisotropic bridge]\label{ass:anisotropic}
For the fixed statistic \(q\in\mathcal Q\) in
Assumption~\ref{ass:scalar-class}, there are a pre-gap vector
\(g_0\in\R^{T_0}\), fixed primitives \((X,b,\rho)\) with \(\rho\ge0\), an index
set \(A\subseteq\{1,\ldots,T_0\}\) of size \(r\), and signs
\(\sigma_A\in\{-1,1\}^A\) satisfying the following conditions.  The active row
matrix \(X_A\in\R^{r\times r}\) is nonsingular.  Define
\[
\Delta_0=X_A^{-1}(g_{0,A}+\rho\sigma_A),\qquad
\beta_A=X_A^{-\transpose}b,
\]
where the coordinates of \(\beta_A\) are indexed by \(A\).  Extend
\(\beta_A\) to \(\beta_0\in\R^{T_0}\) by setting
\((\beta_0)_i=(\beta_A)_i\) for \(i\in A\) and \((\beta_0)_i=0\) for
\(i\notin A\).  The inactive inequalities have strict slack,
\[
|g_{0,i}-X_i^\transpose\Delta_0|<\rho\qquad(i\notin A),
\]
and the active multipliers have strict complementary signs,
\[
\sigma_i(\beta_0)_i>0\qquad(i\in A).
\]
The scalar \(q\) is differentiable at \(g_0\): for \(q_2\) and
\(q_{\mathrm{rms}}\) this means \(g_0\ne0\), while for \(q_\infty\) it means
that a unique signed coordinate attains \(\|g_0\|_\infty\).  Finally, the
primitive active-basis bridge weight is not collinear with the scalar gradient:
\[
\beta_0\notin\operatorname{span}\{\nabla q(g_0)\}.
\]
These are rank, strict-inequality, sign, and noncollinearity conditions on
\((X,b,\rho,q,g_0)\).  They do not assume the endpoint derivative
\(Dh_+(g_0)\), local-dual regularity, or scalar-level endpoint anisotropy; those
facts are derived from the active basis in the proof.
\end{assumption}

\begin{assumption}[Nondegenerate two-dimensional anisotropic witness]\label{ass:two-dimensional-witness}
Take \(T_0=r=2\), \(X=I_2\), \(b=(1,0)^\transpose\), any \(\rho>0\), and any
\(a>0\).  Let \(g^{(1)}=(a,0)^\transpose\) and \(g^{(2)}=(0,a)^\transpose\).
Then \(q_2(g^{(1)})=q_2(g^{(2)})=a\),
\(q_\infty(g^{(1)})=q_\infty(g^{(2)})=a\), and
\(q_{\mathrm{rms}}(g^{(1)})=q_{\mathrm{rms}}(g^{(2)})=a/\sqrt2\).  The tubes
are \(K(g^{(k)})=g^{(k)}+[-\rho,\rho]^2\), so
\[
\sup_{\Delta\in K(g^{(1)})}b^\transpose\Delta=a+\rho,\qquad
\sup_{\Delta\in K(g^{(2)})}b^\transpose\Delta=\rho,
\]
and likewise the lower endpoints are \(a-\rho\) and \(-\rho\).  Thus the same
observable scalar pre-fit value gives different sharp support endpoints for
each \(q\in\mathcal Q\), and the witness is nondegenerate because the strict
endpoint gap \(a\) persists under small perturbations that preserve the
displayed scalar equality within the corresponding level surface.
\end{assumption}

\begin{assumption}[Centered endpoint-sufficient statistic]\label{ass:endpoint-sufficient}
For an open class \(\mathcal U\) of observable laws with fixed
\((X,b,w,\eta)\), define the centered endpoint map for the interval of
\(\theta-y_s^w\),
\[
H^c(P)=\left(
\inf_{\Delta\in K(P)}b^\transpose\Delta-\rho,\;
\sup_{\Delta\in K(P)}b^\transpose\Delta+\rho
\right).
\]
Write these two components as \(H^c_-(P)\) and \(H^c_+(P)\).  A statistic
\(S(P)\) is centered-endpoint-sufficient on \(\mathcal U\) if
\(S(P)=S(P')\) implies \(H^c(P)=H^c(P')\) for all
\(P,P'\in\mathcal U\).  For the uncentered \(\theta\)-interval, the
corresponding endpoint statistic is \((y_s^w,H^c(P))\).
\end{assumption}

\section{Estimand-defining functional}
The PartialID functional is the support interval of the bridge over the
Chebyshev tube.  Define
\[
h_-(P)=\inf_{\Delta\in K(P)}b^\transpose\Delta,\qquad
h_+(P)=\sup_{\Delta\in K(P)}b^\transpose\Delta,
\]
and
\[
\theta_L(P)=y_s^w+h_-(P)-\rho,\qquad
\theta_U(P)=y_s^w+h_+(P)+\rho.
\]
Equivalently, the centered endpoint map is
\[
H^c(P)=(h_-(P)-\rho,\ h_+(P)+\rho).
\]
The proposition below proves the sharp statement
\[
\Theta_I(P)=[\theta_L(P),\theta_U(P)]
\]
under Assumptions~\ref{ass:fixed-weights}, \ref{ass:bounded-factor}, and
\ref{ass:nonempty}, with endpoints interpreted as extended real values if
bridge visibility is not imposed.  Under Assumption~\ref{ass:bridge-visible},
the interval is finite and the endpoint optimizers are attained.  Thus the
functional is not merely an outer bound; it is sharp for the declared
factor-misspecification model.

\section{Target causal estimand}
The target causal estimand is the scalar untreated post-period counterfactual
\[
\theta=Y_{0s}(0).
\]
It is not defined to equal the synthetic outcome \(y_s^w\) and it is not
identified by the observed post gap alone.  The observed treated-minus-synthetic
post gap is
\[
d=Y_{0s}^{\mathrm{obs}}-y_s^w,
\]
so the post-period treatment effect for the treated unit is
\[
\tau_s=Y_{0s}^{\mathrm{obs}}-\theta
      =d-(\theta-y_s^w).
\]
Therefore a sharp interval for \(\theta-y_s^w\) immediately yields the
reversed and shifted treatment-effect interval, but the causal target remains
\(\theta\) until the partial-identification result is applied.

\section{Main theorems}
\begin{proposition}[Support-form sharp Chebyshev interval]\label{thm:sharp-chebyshev}
Under Assumptions~\ref{ass:fixed-weights}, \ref{ass:bounded-factor}, and
\ref{ass:nonempty}, the identified set for \(\theta=Y_{0s}(0)\) is
\[
\Theta_I(P)=
y_s^w+
\left[
\inf_{\Delta\in K(P)} b^\transpose\Delta-\rho,\;
\sup_{\Delta\in K(P)} b^\transpose\Delta+\rho
\right].
\]
If Assumption~\ref{ass:bridge-visible} also holds, both endpoints are finite
and attained.  The corresponding treatment-effect interval is
\[
\tau_s\in
\left[
d-\sup_{\Delta\in K(P)} b^\transpose\Delta-\rho,\;
d-\inf_{\Delta\in K(P)} b^\transpose\Delta+\rho
\right].
\]
\end{proposition}
This proposition is the required sharp partial-identification object.  It is
not the field-level novelty by itself: mathematically it is the usual projection
of a feasible latent set through a linear functional.  Its role is to fix the
deterministic target that later scalar rules must equal if they claim sharpness.
Compared with exact-factor synthetic-control identification in
\cite{AbadieDiamondHainmueller2010}, the object is the support function of the
signed pre-gap tube rather than a point equality.  Compared with
Manski--Balke--Pearl bounds, the latent feasible set is not a response-type
polytope but a Chebyshev tube over factor imbalances.

\begin{proposition}[Scalar RMSPE-level lower-bound witness]\label{thm:scalar-lower-bound}
Under Assumptions~\ref{ass:fixed-weights}, \ref{ass:bounded-factor},
\ref{ass:nonempty}, \ref{ass:bridge-visible}, \ref{ass:scalar-class}, and
\ref{ass:two-dimensional-witness}, fix any \(q\in\mathcal Q\) and consider the
two observable laws \(P_1,P_2\) generated by \(g^{(1)}=(a,0)^\transpose\) and
\(g^{(2)}=(0,a)^\transpose\) with the same \((X,b,w,\eta,y_s^w)\).  Any valid
interval rule \(I_{\psi,q}\) whose endpoints are identical whenever \(q(g)\) is
identical must be nonsharp for at least one of \(P_1,P_2\).  Quantitatively,
because the sharp \(\theta-y_s^w\) intervals are
\[
[a-2\rho,a+2\rho]\quad\text{and}\quad[-2\rho,2\rho],
\]
validity for both displayed laws forces the common scalar interval to have
upper endpoint excess at least \(a\) at \(P_2\) and lower endpoint excess at
least \(a\) at \(P_1\).
\end{proposition}
This proposition gives a concrete lower-bound witness for information loss from
scalarizing the signed pre-gap vector.  It is not the final novelty claim
because it uses two displayed laws and does not target a published sharpness
claim.  Its role is to show the finite mechanism that the open-cell theorem
promotes: a \(q(g)\)-only deterministic rule must over-cover when the same
scalar pre-fit value points in different bridge directions.

\begin{theorem}[Primitive active-basis scalar nonsharpness]\label{thm:generic-scalar}
Conjecture 1 is confirmed on primitive active-basis open cells.  Fix
\(q\in\mathcal Q\).  Under
Assumptions~\ref{ass:fixed-weights}, \ref{ass:bounded-factor},
\ref{ass:nonempty}, \ref{ass:bridge-visible}, \ref{ass:scalar-class}, and
\ref{ass:anisotropic}, there are \(\varepsilon_0>0\), \(c>0\), and, for every
\(0<\varepsilon<\varepsilon_0\), two observable laws \(P_\varepsilon^+\) and
\(P_\varepsilon^-\) in the same open design class with
\(q(g_\varepsilon^+)=q(g_\varepsilon^-)\) but
\[
\left|h_+(P_\varepsilon^+)-h_+(P_\varepsilon^-)\right|\ge c\varepsilon .
\]
Consequently, no \(q\)-scalar pre-fit calibration can be both valid and sharp
on that class; at least one of the two laws receives deterministic
centered-endpoint excess of order \(\varepsilon\).
\end{theorem}
This is the theorem-level contribution.  Endpoint derivative and local-dual
regularity conditions are not assumed; endpoint movement is derived from a
nonsingular active constraint basis, strict slack, strict complementarity, and
the primitive noncollinearity
\(\beta_0\notin\operatorname{span}\{\nabla q(g_0)\}\).  Thus the result gives
an open design-class obstruction to deterministic \(q(g)\)-only sharp
calibration, while leaving published RMSPE placebo, prediction, and sensitivity
uses intact.

\begin{proposition}[Endpoint sufficiency is necessary for sharp calibration]\label{thm:endpoint-sufficiency}
Conjecture 2 is confirmed.  Under Assumptions~\ref{ass:fixed-weights},
\ref{ass:bounded-factor}, \ref{ass:nonempty}, \ref{ass:bridge-visible}, and
\ref{ass:endpoint-sufficient}, let \(\mathcal U\) be any open class on which
the sharp centered interval for \(\theta-y_s^w\) is finite.  If an interval
rule depending on a statistic \(S(P)\) is valid and sharp for
\(\theta-y_s^w\) for every \(P\in\mathcal U\), then \(S\) must be
centered-endpoint-sufficient on \(\mathcal U\):
\[
S(P)=S(P')\quad\Longrightarrow\quad H^c(P)=H^c(P') .
\]
For uncentered intervals for \(\theta\), the statistic must also determine the
shift \(y_s^w\), equivalently it must determine \((y_s^w,H^c(P))\).
\end{proposition}
This proposition records the minimality logic behind the support-function
functional.  It is a necessary-statistic argument, not an independent
field-level theorem.  Any coarser statistic can be sharp only on classes where
the centered endpoint map is constant on its level sets.

\section{Interpretation}
Proposition~\ref{thm:sharp-chebyshev} says that bounded factor misspecification
does not produce a single corrected synthetic-control counterfactual.  It
produces all post-period bridge values \(b^\transpose\Delta\) that are
compatible with the signed pre-gap \(g\), plus the remaining post-period error
budget.  The restriction doing the tightening work is the joint condition
\(\|g-X\Delta\|_\infty\le\rho\) together with bridge visibility
\(b\in\operatorname{rowspan}(X)\).  The former uses the observed signed
pre-gap to restrict latent imbalance; the latter rules out hidden post-period
factor directions that never appear in the pre-period dictionary.

The bound collapses to point identification when \(\rho=0\) and the bridge is
zero on all compatible imbalances.  In particular, exact pre-fit \(g=0\) plus
\(b\in\operatorname{rowspan}(X)\) gives \(\theta=y_s^w\).  The bound widens to
the natural no-restriction bound when the factor-tube restriction is removed:
under the locked real-valued setup with no external bounded outcome support,
that natural bound is all of \(\R\); if an additional outcome support
\([L,U]\) were externally supplied, the analogous vacuous Manski-style bound
would be \([L,U]\).  If bridge visibility is dropped, the interval can again be
unbounded even when the pre-gap tube is nonempty.

The scalar nonsharpness results explain why two designs with the same RMSPE can
have different deterministic identified sets.  In the active-basis theorem,
the deciding object is the bridge-weight vector \(\beta_0\) obtained from the
nonsingular active rows \(X_A\) through \(X_A^\transpose\beta_A=b\) and
extended by zeros off \(A\).  Perturbations tangent to the scalar level but not
orthogonal to this \(\beta_0\) change the support endpoint to first order.
Thus RMSPE remains useful as a fit summary, but the deterministic partial-ID
report must include the vector-sensitive support interval or an equivalent
endpoint-sufficient statistic.

\section{Step-by-step proof}
\begin{lemma}[Bridge support over the tube]\label{lem:bridge-support}
Under Assumptions~\ref{ass:fixed-weights}, \ref{ass:nonempty}, and
\ref{ass:bridge-visible}, \(h_-(P)\) and \(h_+(P)\) are finite and attained.
\end{lemma}

\begin{proof}
By Assumption~\ref{ass:nonempty}, \(K(P)\) is nonempty.  By
Assumption~\ref{ass:bridge-visible}, there is a vector
\(\lambda\in\R^{T_0}\) with \(b=X^\transpose\lambda\).  For every
\(\Delta\in K(P)\),
\[
g-\rho\one\le X\Delta\le g+\rho\one
\]
componentwise, so \(z=X\Delta\) lies in the compact box
\([g-\rho\one,g+\rho\one]\subset\R^{T_0}\).  Also
\[
b^\transpose\Delta=\lambda^\transpose X\Delta=\lambda^\transpose z.
\]
The feasible set for \(z\), namely
\(\{X\Delta:\Delta\in K(P)\}\), is the intersection of the column space of
\(X\) with that compact box, hence it is compact and nonempty.  The continuous
linear map \(z\mapsto\lambda^\transpose z\) therefore attains its minimum and
maximum, proving the claim.
\end{proof}

\begin{lemma}[Dual bridge representation]\label{lem:dual-bridge}
Under Assumptions~\ref{ass:fixed-weights}, \ref{ass:nonempty}, and
\ref{ass:bridge-visible}, define
\(\mathcal B(X,b)=\{\beta\in\R^{T_0}:X^\transpose\beta=b\}\).  The upper
endpoint has the dual form
\[
h_+(g)=\min_{\beta\in\mathcal B(X,b)}
\{g^\transpose\beta+\rho\|\beta\|_1\}.
\]
\end{lemma}

\begin{proof}
Write the tube constraints as
\[
X\Delta\le g+\rho\one,\qquad -X\Delta\le -g+\rho\one .
\]
The primal problem defining \(h_+(g)\) is the feasible finite-valued linear
program
\[
\sup_{\Delta\in\R^r}\ b^\transpose\Delta
\quad\text{subject to}\quad
X\Delta\le g+\rho\one,\quad -X\Delta\le -g+\rho\one .
\]
Feasibility is Assumption~\ref{ass:nonempty}; finite value follows from
Assumption~\ref{ass:bridge-visible} and Lemma~\ref{lem:bridge-support}.  Its
linear-program dual is
\[
\inf_{\lambda^+,\lambda^-\ge0}
(g+\rho\one)^\transpose\lambda^+
{}+
(-g+\rho\one)^\transpose\lambda^-
\quad\text{subject to}\quad
X^\transpose(\lambda^+-\lambda^-)=b .
\]
Strong duality applies because this is a feasible finite-dimensional LP with
finite value.  Set \(\beta=\lambda^+-\lambda^-\).  For a fixed feasible
\(\beta\), the minimum of \(\one^\transpose(\lambda^++\lambda^-)\) over
nonnegative decompositions \(\beta=\lambda^+-\lambda^-\) is
\(\|\beta\|_1\), attained coordinatewise by the positive and negative parts of
\(\beta\).  Substituting gives exactly
\[
\min_{\beta:X^\transpose\beta=b}
g^\transpose\beta+\rho\|\beta\|_1 .
\]
\end{proof}

\begin{lemma}[Active-basis regularity gives scalar-level endpoint movement]\label{lem:primitive-anisotropy}
Under Assumption~\ref{ass:anisotropic}, there is a direction \(v\in\R^{T_0}\)
and a constant \(c_0>0\) such that, for all sufficiently small
\(\varepsilon>0\),
\[
q(g_0+\varepsilon v)=q(g_0-\varepsilon v)
\]
and
\[
\left|h_+(g_0+\varepsilon v)-h_+(g_0-\varepsilon v)\right|
\ge c_0\varepsilon .
\]
\end{lemma}

\begin{proof}
First derive the endpoint formula from the primitive active basis.  For \(g\)
near \(g_0\), set
\[
\Delta_A(g)=X_A^{-1}(g_A+\rho\sigma_A).
\]
The strict inactive slack in Assumption~\ref{ass:anisotropic} is open, so after
shrinking the neighbourhood of \(g_0\),
\[
|g_i-X_i^\transpose\Delta_A(g)|<\rho\qquad(i\notin A).
\]
The active coordinates satisfy
\[
X_A\Delta_A(g)=g_A+\rho\sigma_A,
\]
so \(\Delta_A(g)\in K(g)\).  For any \(\Delta\in K(g)\), the active constraints
give
\[
(\beta_0)_i X_i^\transpose\Delta
\le
(\beta_0)_i(g_i+\rho\sigma_i)\qquad(i\in A),
\]
because \(\sigma_i(\beta_0)_i>0\): upper-bound active constraints have positive
multiplier and lower-bound active constraints have negative multiplier.
Summing over \(A\) and using \(X_A^\transpose\beta_A=b\) yields
\[
b^\transpose\Delta
\le
\beta_A^\transpose(g_A+\rho\sigma_A)
=b^\transpose\Delta_A(g).
\]
Thus \(\Delta_A(g)\) attains the upper support endpoint and
\[
h_+(g)=\beta_A^\transpose(g_A+\rho\sigma_A)
       =\beta_0^\transpose g+\rho\|\beta_0\|_1
\]
throughout the active-basis cell.

Because \(\beta_0\notin\operatorname{span}\{\nabla q(g_0)\}\), there is
\(v\) in the tangent space of the scalar level at \(g_0\) with
\[
\nabla q(g_0)^\transpose v=0,\qquad \beta_0^\transpose v\ne0.
\]
For \(q_2\) and \(q_{\mathrm{rms}}\), this tangent condition is
\(g_0^\transpose v=0\), and therefore
\[
\|g_0+\varepsilon v\|_2^2=\|g_0-\varepsilon v\|_2^2
\]
for every \(\varepsilon\).  Hence \(q_2\) and \(q_{\mathrm{rms}}\) agree exactly
on the two symmetric perturbations.  For \(q_\infty\), differentiability means a
unique signed coordinate \(k\) attains \(\|g_0\|_\infty\).  The tangent
condition sets \(v_k=0\); after shrinking the neighbourhood, the same coordinate
remains uniquely active, so the two sup norms are again exactly equal.

The affine endpoint formula gives the exact difference
\[
h_+(g_0+\varepsilon v)-h_+(g_0-\varepsilon v)
=2\varepsilon\,\beta_0^\transpose v
\]
whenever both perturbed gaps remain in the active-basis cell.  Since
\(\beta_0^\transpose v\ne0\), choose
\(c_0=|\beta_0^\transpose v|\) and shrink the neighbourhood so that the
absolute difference is at least \(c_0\varepsilon\).
\end{proof}

\begin{proof}[Proof of Proposition~\ref{thm:sharp-chebyshev}]
The proof is a finite-dimensional projection argument, the same support-set
logic used in classical sharp partial-identification bounds.

First prove containment.  If \(\theta\in\Theta_I(P)\), the definition of
\(\Theta_I(P)\) and Assumption~\ref{ass:bounded-factor} give some
\(\Delta\in\R^r\) and \(e_s\in[-\rho,\rho]\) with
\[
\|g-X\Delta\|_\infty\le\rho,\qquad
\theta-y_s^w=b^\transpose\Delta+e_s .
\]
The first display says \(\Delta\in K(P)\).  Hence
\[
h_-(P)\le b^\transpose\Delta\le h_+(P)
\]
by the definitions of \(h_-\) and \(h_+\), and adding
\(e_s\in[-\rho,\rho]\) yields
\[
y_s^w+h_-(P)-\rho
\le \theta \le
y_s^w+h_+(P)+\rho .
\]
Thus
\[
\Theta_I(P)\subseteq [\theta_L(P),\theta_U(P)].
\]

Now prove sharpness.  The tube \(K(P)\) is convex because it is the inverse
image of a box under an affine map.  Therefore the image
\(\{b^\transpose\Delta:\Delta\in K(P)\}\) is an interval in \(\R\), with
endpoints \(h_-(P)\) and \(h_+(P)\) in the extended sense.  Under
Assumption~\ref{ass:bridge-visible}, Lemma~\ref{lem:bridge-support} gives
finite attained endpoints; without bridge visibility the same argument gives
the corresponding extended interval.  For any
\[
u\in[h_-(P)-\rho,\ h_+(P)+\rho],
\]
choose \(m\in[h_-(P),h_+(P)]\) and \(e_s\in[-\rho,\rho]\) such that
\(u=m+e_s\), which is possible because the Minkowski sum of intervals is an
interval:
\[
[h_-(P),h_+(P)]+[-\rho,\rho]
=[h_-(P)-\rho,h_+(P)+\rho].
\]
By convexity of \(K(P)\), there is \(\Delta\in K(P)\) with
\(b^\transpose\Delta=m\).  Set \(\theta=y_s^w+u\).  Then
\[
|\theta-y_s^w-b^\transpose\Delta|=|e_s|\le\rho,
\]
so \(\theta\in\Theta_I(P)\).  This proves
\[
\Theta_I(P)=[\theta_L(P),\theta_U(P)].
\]
The finite-attainment statement is Lemma~\ref{lem:bridge-support}.

Finally, for treatment effects use the identity from Section 8,
\(\tau_s=d-(\theta-y_s^w)\).  Since
\[
\theta-y_s^w\in[h_-(P)-\rho,h_+(P)+\rho],
\]
subtracting reverses endpoints and gives
\[
\tau_s\in[d-h_+(P)-\rho,\ d-h_-(P)+\rho].
\]
\end{proof}

\begin{proof}[Proof of Proposition~\ref{thm:scalar-lower-bound}]
Under Assumption~\ref{ass:two-dimensional-witness}, \(X=I_2\), \(b=e_1\), and
\[
K(g^{(k)})=\{\Delta:\|g^{(k)}-\Delta\|_\infty\le\rho\}
          =g^{(k)}+[-\rho,\rho]^2 .
\]
For \(g^{(1)}=(a,0)^\transpose\),
\[
h_-(P_1)=a-\rho,\qquad h_+(P_1)=a+\rho,
\]
so Proposition~\ref{thm:sharp-chebyshev} gives the centered sharp interval
\[
H^c(P_1)=[a-2\rho,\ a+2\rho].
\]
For \(g^{(2)}=(0,a)^\transpose\),
\[
h_-(P_2)=-\rho,\qquad h_+(P_2)=\rho,
\]
so
\[
H^c(P_2)=[-2\rho,\ 2\rho].
\]
The same assumption gives
\[
q(g^{(1)})=q(g^{(2)})
\]
for \(q_2\), \(q_\infty\), and \(q_{\mathrm{rms}}\).  A scalar rule whose
endpoints are identical whenever \(q(g)\) is identical must therefore assign a
common interval, say \([L,U]\), to both laws.  Validity for \(P_1\) and \(P_2\)
requires
\[
L\le -2\rho,\qquad U\ge a+2\rho.
\]
At \(P_2\), the sharp upper endpoint is \(2\rho\), so the common interval has
upper excess at least \((a+2\rho)-2\rho=a\).  At \(P_1\), the sharp lower
endpoint is \(a-2\rho\), so the common interval has lower excess at least
\((a-2\rho)-(-2\rho)=a\).  Hence the scalar rule cannot be sharp for both laws.
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:generic-scalar}]
Lemma~\ref{lem:primitive-anisotropy} supplies a direction \(v\), a constant
\(c_0>0\), and an \(\varepsilon_0>0\) such that the symmetric perturbations
\[
g_\varepsilon^+=g_0+\varepsilon v,\qquad
g_\varepsilon^-=g_0-\varepsilon v
\]
remain in the open design class, have identical scalar pre-fit values, and
satisfy
\[
\left|h_+(g_\varepsilon^+)-h_+(g_\varepsilon^-)\right|
\ge c_0\varepsilon
\]
for all \(0<\varepsilon<\varepsilon_0\).  Let \(P_\varepsilon^+\) and
\(P_\varepsilon^-\) be the observable laws with these two pre-gap vectors and
the same \((X,b,w,\eta,y_s^w,d)\).  Take \(c=c_0\).  Since
\(q(g_\varepsilon^+)=q(g_\varepsilon^-)\), any \(q\)-scalar calibration assigns
the same interval to both laws.  Proposition~\ref{thm:sharp-chebyshev} says the
sharp centered upper endpoints differ by at least \(c\varepsilon\).  A common
valid interval must contain the larger upper endpoint and therefore has
centered-endpoint excess at least \(c\varepsilon\) for the law with the smaller
upper endpoint.  Hence the scalar rule cannot be both valid and sharp on that
open class.
\end{proof}

\begin{proof}[Proof of Proposition~\ref{thm:endpoint-sufficiency}]
Let the interval rule depending on \(S\) be denoted \(I_S\).  Suppose
\(S(P)=S(P')\) for \(P,P'\in\mathcal U\).  Because the rule depends on the law
only through \(S\), it assigns the same centered interval:
\[
I_S(P)=I_S(P').
\]
Sharpness for \(\theta-y_s^w\), using Proposition~\ref{thm:sharp-chebyshev}, means
\[
I_S(P)=H^c(P),\qquad I_S(P')=H^c(P').
\]
Combining the last two displays gives \(H^c(P)=H^c(P')\).  This is exactly
centered-endpoint sufficiency on \(\mathcal U\).  For uncentered intervals for
\(\theta\), the sharp interval is \(y_s^w+H^c(P)\), so equality of the rule for
two laws also requires equality of the shift \(y_s^w\), or an equivalent
statistic that determines it.
\end{proof}

\section{Sanity checks}
\begin{corollary}[Zero-budget exact pre-fit]\label{cor:zero-budget}
Under Assumption~\ref{ass:exact-corner}, Proposition~\ref{thm:sharp-chebyshev}
reduces to the exact-factor point-identification corner:
\[
\Theta_I(P)=\{y_s^w\},\qquad \tau_s=d.
\]
\end{corollary}

\begin{proof}
If \(\eta=0\), then \(\rho=0\).  If \(g=0\), then
\[
K(P)=\{\Delta:X\Delta=0\}=\ker(X).
\]
Since \(b\in\operatorname{rowspan}(X)\), \(b^\transpose\Delta=0\) for every
\(\Delta\in\ker(X)\).  Hence \(h_-(P)=h_+(P)=0\), and
Proposition~\ref{thm:sharp-chebyshev} gives
\(\Theta_I(P)=\{y_s^w\}\).  The treatment-effect identity gives
\(\tau_s=d\).
\end{proof}

\paragraph{Vacuous no-restriction corner.}
If the factor-tube restriction is removed from the locked real-valued setup,
then \(\theta-y_s^w\) can be any real number, so the natural no-restriction
Manski-style bound is \(\R\).  If an external bounded support
\(\theta\in[L,U]\) were added, the corresponding vacuous bound would be
\([L,U]\); no such bounded outcome support is part of the locked parameters.

\paragraph{Finite but non-point interval.}
If \(b\in\operatorname{rowspan}(X)\) and \(\rho>0\), the endpoints are finite,
but the post-period error budget alone contributes width at least \(2\rho\).
Thus bridge visibility makes the interval finite; it does not by itself give
point identification.

\paragraph{Scalar witness corner.}
The two-dimensional construction in
Assumption~\ref{ass:two-dimensional-witness} gives the simplest check that the
formula depends on the signed vector \(g\), not only on \(\|g\|\).  With
\(X=I_2\) and \(b=e_1\), moving a gap of size \(a\) from the first coordinate to
the second changes the sharp centered interval from
\([a-2\rho,a+2\rho]\) to \([-2\rho,2\rho]\) while preserving the listed scalar
pre-fit values.

\section{Counterexample or minimality check}
Bridge visibility is the minimal condition for finite deterministic endpoints.
Take \(T_0=1\), \(r=2\), \(X=(1\ 0)\), \(g=0\), \(\rho=0\), and
\(b=(0,1)^\transpose\).  Then
\[
K(P)=\{(0,t)^\transpose:t\in\R\},
\]
but
\[
b^\transpose(0,t)^\transpose=t.
\]
Thus \(h_-(P)=-\infty\) and \(h_+(P)=+\infty\).  The pre-period fit is exact,
yet the post bridge points entirely in a hidden factor direction, so the
counterfactual is unbounded.  The nearest correct finite statement is exactly
Proposition~\ref{thm:sharp-chebyshev} with Assumption~\ref{ass:bridge-visible}
added for finite attained endpoints.

The scalar-reporting lower bound is also minimal in the relevant sense.  The
witness in Assumption~\ref{ass:two-dimensional-witness} keeps
\((X,b,w,\eta,y_s^w)\) fixed and changes only the direction of \(g\) along a
common scalar level.  Therefore no weakening that keeps only \(q(g)\) can
recover sharpness on that two-law class.  The nearest correct replacement for a
scalar RMSPE-level interval is the endpoint-sufficient statistic
\((y_s^w,H^c(P))\), or any statistic through which that pair factors.

The active-basis noncollinearity condition in
Theorem~\ref{thm:generic-scalar} is also close to necessary for a local
first-order scalar obstruction on a fixed LP cell.  If the active-basis bridge
weight \(\beta_0\) is collinear with \(\nabla q(g_0)\), then every tangent
direction to the scalar level has zero first-order endpoint slope on that cell,
so the theorem cannot produce a same-scalar first-order separation at that
point.  In such locally radial cases, scalar reporting may be
endpoint-sufficient on a restricted class; the theorem deliberately targets the
open complement where the post bridge has a component invisible to the scalar
gradient.

\section{Formalization checklist}
\paragraph{Deterministic objects.}
\begin{itemize}[leftmargin=*]
\item Finite dimensions: \(J,T_0,r\in\mathbb N\), with vectors
\(w\in\R^J\), \(g\in\R^{T_0}\), \(b\in\R^r\), matrix
\(X\in\R^{T_0\times r}\), scalars \(d,y_s^w,\eta,\rho,\theta\in\R\), and
\(\rho=(1+\|w\|_1)\eta\).
\item Chebyshev tube:
\[
K(P)=\{\Delta\in\R^r:\|g-X\Delta\|_\infty\le\rho\}.
\]
Role: feasible latent imbalances.
\item Bridge support endpoints:
\[
h_-(P)=\inf_{\Delta\in K(P)}b^\transpose\Delta,\qquad
h_+(P)=\sup_{\Delta\in K(P)}b^\transpose\Delta.
\]
Role: deterministic projection of the feasible tube onto the post bridge.
\item Dual bridge objects:
\[
\mathcal B(X,b)=\{\beta\in\R^{T_0}:X^\transpose\beta=b\},\qquad
D_g(\beta)=g^\transpose\beta+\rho\|\beta\|_1.
\]
Role: primitive LP-dual representation of the upper support endpoint.
\item Centered endpoint map:
\[
H^c(P)=(h_-(P)-\rho,\ h_+(P)+\rho).
\]
Role: sharp interval for \(\theta-y_s^w\).
\item Uncentered counterfactual endpoints:
\[
\theta_L(P)=y_s^w+H^c_-(P),\qquad
\theta_U(P)=y_s^w+H^c_+(P).
\]
Role: sharp interval for \(\theta\).
\item Treatment-effect endpoint identity:
\[
\tau_s=d-(\theta-y_s^w).
\]
Role: reverses the centered counterfactual interval and shifts by \(d\).
\end{itemize}

\paragraph{Assumptions as mathematical predicates.}
\begin{itemize}[leftmargin=*]
\item Fixed-data predicate: all components of \(P\) are finite-dimensional real
objects, and \(w\), \(X\), \(b\), \(\eta\) are held fixed for the support
calculation.
\item Bounded-factor predicate: existence of \(\Delta\), \(e_{\mathrm{pre}}\),
and \(e_s\) satisfying \(g=X\Delta+e_{\mathrm{pre}}\),
\(\|e_{\mathrm{pre}}\|_\infty\le\rho\), and
\(\theta-y_s^w=b^\transpose\Delta+e_s\), \(|e_s|\le\rho\).
\item Nonempty-tube predicate: \(K(P)\ne\emptyset\).
\item Bridge-visibility predicate:
\[
b\in\operatorname{rowspan}(X)
\quad\Longleftrightarrow\quad
b^\transpose v=0\ \text{for all }v\in\ker(X).
\]
Role: finite attained support endpoints.
\item Scalar-calibration predicate: an interval rule depends on \(g\) only
through \(q(g)\) and fixed \((X,b,w,\eta)\).
\item Primitive active-basis anisotropic predicate: there exist active indices
\(A\), signs \(\sigma_A\), a nonsingular active row matrix \(X_A\), strict
inactive slack, strict complementary signs
\(\sigma_i(\beta_0)_i>0\), differentiability of \(q\) at \(g_0\), and
\(\beta_0\notin\operatorname{span}\{\nabla q(g_0)\}\), where
\(\beta_A=X_A^{-\transpose}b\) and \(\beta_0\) extends \(\beta_A\) by zeros.
\item Endpoint-sufficiency predicate:
\[
S(P)=S(P')\Rightarrow H^c(P)=H^c(P')
\]
on the design class.
\end{itemize}

\paragraph{Deterministic identities and lemmas.}
\begin{itemize}[leftmargin=*]
\item Convexity identity: \(K(P)\) is a closed convex polyhedron because it is
defined by finitely many affine inequalities
\(-\rho\one\le g-X\Delta\le\rho\one\).
\item Image identity: the image of a convex set under a linear functional is an
interval.
\item Minkowski interval identity:
\[
[h_-,h_+]+[-\rho,\rho]=[h_--\rho,h_++\rho].
\]
\item Row-span finite-support lemma: if \(b=X^\transpose\lambda\), then
\(b^\transpose\Delta=\lambda^\transpose X\Delta\), and \(X\Delta\) is confined
to the compact box \([g-\rho\one,g+\rho\one]\).
\item LP-dual endpoint identity:
\[
h_+(g)=\min_{\beta:X^\transpose\beta=b}
\{g^\transpose\beta+\rho\|\beta\|_1\}.
\]
Role: converts the Chebyshev support problem into a primitive bridge-weight
calculation.
\item Active-basis endpoint identity: if
\(\Delta_A(g)=X_A^{-1}(g_A+\rho\sigma_A)\) remains feasible on the open cell
and \(\sigma_i(\beta_0)_i>0\) on \(A\), then
\[
h_+(g)=\beta_A^\transpose(g_A+\rho\sigma_A)
      =\beta_0^\transpose g+\rho\|\beta_0\|_1.
\]
Role: derives endpoint anisotropy from rank and sign conditions rather than
assuming \(Dh_+\) variation.
\item Two-dimensional witness calculation: for \(X=I_2\), \(b=e_1\), and
\(g^{(1)}=(a,0)\), \(g^{(2)}=(0,a)\), compute the exact centered intervals
\([a-2\rho,a+2\rho]\) and \([-2\rho,2\rho]\).
\item Norm-level equalities: \(q_2(g^{(1)})=q_2(g^{(2)})\),
\(q_\infty(g^{(1)})=q_\infty(g^{(2)})\), and
\(q_{\mathrm{rms}}(g^{(1)})=q_{\mathrm{rms}}(g^{(2)})\).
\item Local scalar-level construction: noncollinearity of \(\beta_0\) and
\(\nabla q(g_0)\) gives a tangent direction \(v\) with
\(\beta_0^\transpose v\ne0\); for \(q_2\) and \(q_{\mathrm{rms}}\),
\(g_0^\transpose v=0\) implies equal norms for \(g_0\pm\varepsilon v\); for
smooth \(q_\infty\), a unique active coordinate with zero perturbation keeps
the sup norm fixed for small \(\varepsilon\).
\item Sufficiency contradiction identity: if a sharp interval rule depends only
on \(S\), then \(S(P)=S(P')\) forces equality of the sharp endpoint maps.
\end{itemize}

\paragraph{Probabilistic content.}
There is no sampling-limit, positivity, or exchangeability argument in this
note.  The only causal content is the interpretation of
\(\theta=Y_{0s}(0)\) as the missing untreated counterfactual and the bounded
factor approximation restriction that defines the feasible completions.

\section{Conclusion and references}
The support-form proposition gives the sharp deterministic identified set for
synthetic control under bounded factor misspecification.  The tightening
restriction is the Chebyshev compatibility condition
\(\|g-X\Delta\|_\infty\le\rho\), and finite endpoints require the post bridge to
be visible in the row span of the pre-period dictionary.  The interval is
vacuous when the factor restriction or bridge visibility leaves the post bridge
unrestricted, and it becomes point-identifying in the exact-fit zero-budget
corner.  The theorem-level contribution is the primitive active-basis scalar
nonsharpness result: when a nonsingular active constraint basis has strict slack
and strict complementarity, and its bridge weight \(\beta_0\) is not collinear
with the RMSPE-level scalar gradient, same-scalar perturbations change the
sharp endpoint to first order.  Thus RMSPE-level reporting cannot replace the
signed-vector support interval on those primitive bridge-nondegenerate classes;
sharp deterministic reporting must carry \(H^c(P)\), together with the
\(y_s^w\) shift for the uncentered counterfactual.

\subsection*{References}
\begin{thebibliography}{99}
\bibitem{AbadieGardeazabal2003}
Abadie, A. and Gardeazabal, J. (2003).
The economic costs of conflict: A case study of the Basque Country.
\emph{American Economic Review}, 93(1):113--132.

\bibitem{AbadieDiamondHainmueller2010}
Abadie, A., Diamond, A., and Hainmueller, J. (2010).
Synthetic control methods for comparative case studies: Estimating the effect
of California's tobacco control program.
\emph{Journal of the American Statistical Association}, 105(490):493--505.

\bibitem{Abadie2021}
Abadie, A. (2021).
Using synthetic controls: Feasibility, data requirements, and methodological
aspects.
\emph{Journal of Economic Literature}, 59(2):391--425.

\bibitem{ArkhangelskyAtheyHirshbergImbensWager2021}
Arkhangelsky, D., Athey, S., Hirshberg, D. A., Imbens, G. W., and Wager, S.
(2021).
Synthetic difference-in-differences.
\emph{American Economic Review}, 111(12):4088--4118.

\bibitem{AtheyBayatiDoudchenkoImbensKhosravi2021}
Athey, S., Bayati, M., Doudchenko, N., Imbens, G. W., and Khosravi, K. (2021).
Matrix completion methods for causal panel data models.
\emph{Journal of the American Statistical Association}, 116(536):1716--1730.

\bibitem{BalkePearl1997}
Balke, A. and Pearl, J. (1997).
Bounds on treatment effects from studies with imperfect compliance.
\emph{Journal of the American Statistical Association}, 92(439):1171--1176.

\bibitem{BenMichaelFellerRothstein2021}
Ben-Michael, E., Feller, A., and Rothstein, J. (2021).
The augmented synthetic control method.
\emph{Journal of the American Statistical Association}, 116(536):1789--1803.

\bibitem{CattaneoFengTitiunik2021}
Cattaneo, M. D., Feng, Y., and Titiunik, R. (2021).
Prediction intervals for synthetic control methods.
\emph{Journal of the American Statistical Association}, 116(536):1865--1880.

\bibitem{ChernozhukovWuthrichZhu2021}
Chernozhukov, V., Wuthrich, K., and Zhu, Y. (2021).
An exact and robust conformal inference method for counterfactual and synthetic
controls.
\emph{Journal of the American Statistical Association}, 116(536):1849--1864.

\bibitem{FermanPinto2021}
Ferman, B. and Pinto, C. (2021).
Synthetic controls with imperfect pre-treatment fit.
\emph{Quantitative Economics}, 12(4):1197--1221.

\bibitem{FirpoPossebom2018}
Firpo, S. and Possebom, V. (2018).
Synthetic control method: Inference, sensitivity analysis and confidence sets.
\emph{Journal of Causal Inference}, 6(2):20160026.

\bibitem{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review}, 80(2):319--323.

\bibitem{NazaretShiBlei2024}
Nazaret, A. O. R., Shi, C., and Blei, D. M. (2024).
On the misspecification of linear assumptions in synthetic controls.
\emph{Proceedings of the 27th International Conference on Artificial
Intelligence and Statistics}, PMLR 238:3790--3798.

\bibitem{ZeitlerVlontzosGilliganLee2023}
Zeitler, J., Vlontzos, A., and Gilligan-Lee, C. M. (2023).
Non-parametric identifiability and sensitivity analysis of synthetic control
models.
\emph{Proceedings of the Second Conference on Causal Learning and Reasoning},
PMLR 213:850--865.
\url{https://proceedings.mlr.press/v213/zeitler23a.html}.
\end{thebibliography}

\end{document}
