\paragraph{\S9-fragment-statement: Refutation note for the labelled solve target \texttt{law-sharp}.}\label{prop:law-sharp-refuted}
\textbf{Conjecture restated verbatim (Conjecture~\ref{conj:law-sharp}).} Under Assumptions~\ref{ass:grid-bounds}--\ref{ass:completion}, the algebraic
envelope in Theorem~\ref{thm:joint-envelope} is law-sharp:
\[
  [L_h(L;P),U_h(L;P)]
  =
  \{\operatorname{ACRT}(d_h;Q):Q \text{ is a finite bounded latent law
  preserving } P \text{ and Assumptions } \ref{ass:consistency-noanticip}
  \text{--}\ref{ass:regularity}\}.
\]
In particular, no endpoint is an outer-bound artifact caused by an
unrealizable cross-dose ATT array.

\textbf{Verdict.} Refuted: in the three-dose binary bounded law with \(d_0=0,d_1=1,d_2=2\), target \(h=1\), stencil \(q_{\cdot 1}=(0,-1,1)\), \(\underline y=0\), \(\overline y=1\), and observed cells \(D=0:(Y_0,Y_1)=(0,0)\), \(D=1:(Y_0,Y_1)=(1,1)\), \(D=2:(Y_0,Y_1)=(0,1)\), the algebraic LP has \(U_1(1;P)=1\) attained by \(\alpha^\dagger_{21}=1\), but every finite bounded latent law preserving \(P\) and Assumptions~\ref{ass:consistency-noanticip}--\ref{ass:regularity} has \(\alpha_{21}=0\) and hence \(\operatorname{ACRT}(d_1;Q)=0\); the endpoint \(1\) is an outer-bound artifact.

\paragraph{\S13-refutation-attempt and counterexample.}
\textbf{Primitive executed.} I used the first prescribed partial-identification refutation primitive: a finite response-type LP on the smallest nontrivial support that can contain a cross-dose ACRT coordinate.  The support has three doses
\[
  \mathcal D=\{d_0,d_1,d_2\}=\{0,1,2\},
\]
binary bounded post-period potential outcomes \(Y_1(d_j)\in\{0,1\}\), and three deterministic observed treatment cells, each with probability \(1/3\):
\[
\begin{array}{c|ccc}
  D & d_0 & d_1 & d_2\\ \hline
  (Y_0,Y_1) & (0,0) & (1,1) & (0,1).
\end{array}
\]
Thus \(m_0(P)=0\), \(m_1(P)=0\), \(m_2(P)=1\), so the CGS inputs are
\[
  \tau_0(P)=0,\qquad \tau_1(P)=0,\qquad \tau_2(P)=1.
\]
The target is \(h=1\), and the locked finite-difference stencil is
\[
  q_{\cdot 1}=(q_{01},q_{11},q_{21})=(0,-1,1),
\]
which satisfies \(\sum_j q_{j1}=0\) and
\(\sum_j q_{j1}(d_j-d_1)=1\).  Hence
\[
  \theta_1(\alpha)=\operatorname{ACRT}(d_1;\alpha)
  =\alpha_{21}-\alpha_{11}=\alpha_{21},
\]
because \(\alpha_{11}=\tau_1(P)=0\).

\textbf{Algebraic vertex search.} In the Lipschitz version fix \(L=1\) and take
\(\bar L\ge 1\).  The algebraic array
\[
  \alpha^\dagger=
  \begin{pmatrix}
    0&0&0\\
    0&0&0\\
    1&1&1
  \end{pmatrix},
  \qquad
  \text{rows indexed by }j,\text{ columns indexed by conditioning dose }h,
\]
is feasible for \(\mathcal A_1(P)\).  The first row is the definitional
baseline row, the diagonal entries are
\(\alpha^\dagger_{00}=0\), \(\alpha^\dagger_{11}=0\), and
\(\alpha^\dagger_{22}=1\), matching \(b_{\mathrm{CGS}}(P)\), every entry lies
in \([0,1]\), and each treatment row is \(1\)-Lipschitz in the conditioning
dose.  At this algebraic vertex,
\[
  \theta_1(\alpha^\dagger)
  =\alpha^\dagger_{21}-\alpha^\dagger_{11}=1.
\]
Because \(\alpha_{21}\le 1\) for every \(\alpha\in\mathcal A_1(P)\), this also
shows \(U_1(1;P)=1\).  Theorem~\ref{thm:joint-envelope} correctly records this
as an endpoint of the algebraic support-function envelope; the question is
whether the endpoint is observationally equivalent to any latent law, in the
sense emphasized by Molinari's partial-identification survey
\cite{Molinari2020}.

\textbf{Latent response-type LP.} Now impose law-level preservation of the
same observable \(P\).  Conditional on \(D=d_1\), consistency gives
\[
  Y_1(d_1)=Y_1=1 \quad\text{almost surely}.
\]
The CGS diagonal input \(\alpha_{11}=\tau_1(P)=0\) requires
\[
  0=\alpha_{11}
  =\E[Y_1(d_1)-Y_1(d_0)\mid D=d_1]
  =1-\E[Y_1(d_0)\mid D=d_1].
\]
Since the bounded latent law has \(0\le Y_1(d_0)\le 1\), this equality forces
\[
  Y_1(d_0)=1 \quad\text{almost surely conditional on }D=d_1.
\]
For the cross-dose coordinate in the ACRT target,
\[
  \alpha_{21}
  =\E[Y_1(d_2)-Y_1(d_0)\mid D=d_1]
  =\E[Y_1(d_2)\mid D=d_1]-1
  \le 0,
\]
again because \(Y_1(d_2)\le 1\).  On the other hand, Assumption~\ref{ass:regularity}
with \(L=1\), \(d_2-d_1=1\), and the diagonal input \(\alpha_{22}=1\) implies
\[
  |\alpha_{21}-\alpha_{22}|\le 1
  \quad\Longrightarrow\quad
  \alpha_{21}\ge 0.
\]
Therefore every finite bounded latent law preserving \(P\) and satisfying the
Lipschitz regularity restriction has
\[
  \alpha_{21}=0,
  \qquad
  \operatorname{ACRT}(d_1;Q)=\alpha_{21}-\alpha_{11}=0.
\]
The response-type LP is thus bounded by the law-level equality and boundary
face \(Y_1(d_0)=Y_1(d_1)=1\) in the \(D=d_1\) stratum.  It cannot reach the
algebraic vertex \(\alpha^\dagger_{21}=1\).

\textbf{Nonempty law-level feasible set.} The refutation is not driven by an
empty identified set.  A finite latent completion satisfying the same \(P\)
and \(L=1\) is obtained by assigning, deterministically within each treatment
cell,
\[
\begin{array}{c|ccc}
  D & Y_1(d_0) & Y_1(d_1) & Y_1(d_2)\\ \hline
  d_0 & 0&0&1\\
  d_1 & 1&1&1\\
  d_2 & 0&0&1.
\end{array}
\]
This completion preserves the observed \(Y_1=Y_1(D)\), preserves the displayed
observable \(Y_0\) distribution by adjoining \(Y_0=0,1,0\) in the three cells,
and induces
\[
  \alpha=
  \begin{pmatrix}
    0&0&0\\
    0&0&0\\
    1&0&1
  \end{pmatrix}.
\]
The row \(h\mapsto\alpha_{2h}\) is \(1\)-Lipschitz on the grid
\(\{0,1,2\}\), all entries are in the bounded effect interval \([0,1]\), and
the diagonal inputs are the CGS values \((0,0,1)\).  Hence the law-level set is
nonempty, but its ACRT value at \(d_1\) is \(0\), not the algebraic endpoint
\(1\).

This contradicts Conjecture~\ref{conj:law-sharp} because
\[
  1=U_1(1;P)\in [L_1(1;P),U_1(1;P)]
  \quad\text{but}\quad
  1\notin
  \{\operatorname{ACRT}(d_1;Q):Q \text{ preserves }P
  \text{ and the maintained restrictions}\}.
\]
The obstruction is a missing mean-completion constraint.  For any bounded
latent law, consistency and the diagonal input imply the necessary condition
\[
  \underline y
  \le
  \E[Y_1\mid D=d_h]-\tau_h(P)+\alpha_{jh}
  \le
  \overline y
  \qquad\text{for every }j,h,
\]
because the middle term is
\(\E[Y_1(d_j)\mid D=d_h]\).  The algebraic set
\(\mathcal A_L(P)\) used in Theorem~\ref{thm:joint-envelope} omits this
law-level completion inequality.  In the witness above it permits
\(\E[Y_1(d_2)\mid D=d_1]=1-0+1=2\), outside the allowed support \([0,1]\).
The nearest correct law-sharp statement would have to intersect the algebraic
polytope with these coordinate-mean feasibility inequalities, and then prove
a finite product-support completion for the reduced polytope.
