\paragraph{Conjecture 2 (phase) -- verbatim statement from Proposal \S8.}
Under Assumptions~\ref{ass:randomization}--\ref{ass:phase-neighborhood}, the symmetric K=3 witness has a non-PI strict-containment phase exactly for \(\Gamma>1\).  In that cell,
\[
  \Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma)
  =\frac{\Gamma+2}{3(\Gamma+1)(2\Gamma+1)}>0,
\]
and the active-basis identities imply
\[
  T_{\mathrm{pair}}(\Gamma)-T_{\mathrm{mid}}(\Gamma)
  =
  \Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma).
\]
Thus the incident pairwise endpoint is separated from the coherent common-law endpoint by a primitive slack computed from the K=3 cell, not by a phase variable defined as the endpoint difference.  The conjectural extension is that the same active basis remains valid on a relative-open neighborhood of the symmetric witness inside the margin-compatible parameter space.

\begin{proposition}[Phase threshold and primitive slack]\label{prop:phase-threshold}
Under Assumptions~\ref{ass:randomization}--\ref{ass:phase-neighborhood}, the symmetric \(K=3\) witness has a non-PI strict-containment phase exactly on the finite positive-sensitivity regime \(\Gamma>1\).  In that cell,
\[
  T_{\mathrm{mid}}(\Gamma)=\frac{4\Gamma-1}{3(2\Gamma+1)},\qquad
  T_{\mathrm{pair}}(\Gamma)=\frac{2\Gamma+1}{3(\Gamma+1)},
\]
and hence
\[
  T_{\mathrm{pair}}(\Gamma)-T_{\mathrm{mid}}(\Gamma)
  =
  \frac{\Gamma+2}{3(\Gamma+1)(2\Gamma+1)}
  =
  \Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma)>0 .
\]
The same coherent and pairwise active bases persist on a sufficiently small relative-open neighborhood of the symmetric witness inside the margin-compatible parameter space.  The statement is a structural refinement of the parent sharp interval in Theorem~\ref{thm:parent-reduction}: it identifies the primitive K=3 middle-cell slack that separates the coherent common-law endpoint from the incident pairwise relaxation endpoint.
\end{proposition}

\paragraph{Refutation attempt before proof.}
The prescribed refutation primitive is vertex enumeration of the smallest nontrivial partial-identification cell.  Work in the witness cell of Assumption~\ref{ass:witness-cell}.  Write
\[
  x_h=q_h^1,\qquad r_h=q_h^0,\qquad h\in\{a,b,c\}.
\]
Because \(\Pr(Y=1\mid Z=z,S=k,X=x_0)=1/2\) and \(w_a=w_b=w_c=1/3\), the calibration equations reduce to
\[
  x_h+r_h=\frac23,\qquad h\in\{a,b,c\},
\]
while the two outcome-specific simplex equations reduce to
\[
  x_a+x_b+x_c=1,\qquad r_a+r_b+r_c=1.
\]
Equal baseline weights make the adjacent odds-ratio restrictions linear:
\[
  \Gamma^{-1}x_\ell\le x_h\le \Gamma x_\ell,\qquad
  \Gamma^{-1}r_\ell\le r_h\le \Gamma r_\ell
\]
for the two adjacent pairs \(a\sim_z b\) and \(b\sim_z c\).  Hence the refutation search is a six-variable finite polytope; every possible violation of the claimed coherent endpoint must appear at a vertex.

Let \(x=x_b\).  The common-law constraints imply \(r_b=2/3-x\) and \(r_a+r_c=1/3+x\).  The two incident lower-outcome upper-ratio constraints give
\[
  r_a\le \Gamma r_b,\qquad r_c\le \Gamma r_b.
\]
Summing them gives the universal vertex-enumeration bound
\[
  \frac13+x=r_a+r_c\le 2\Gamma\left(\frac23-x\right),
\]
or equivalently
\[
  x\le \frac{4\Gamma-1}{3(2\Gamma+1)}=T_{\mathrm{mid}}(\Gamma).
\]
Thus there is no common-law vertex with \(q_b^1>T_{\mathrm{mid}}(\Gamma)\).  The candidate active vertex
\[
  r_b=\frac{1}{2\Gamma+1},\qquad
  r_a=r_c=\frac{\Gamma}{2\Gamma+1},\qquad
  x_b=\frac{4\Gamma-1}{3(2\Gamma+1)},\qquad
  x_a=x_c=\frac{\Gamma+2}{3(2\Gamma+1)}
\]
satisfies simplex, calibration, nonnegativity, and all adjacent ratio inequalities; the remaining upper-outcome inequalities reduce to
\[
  \frac{4\Gamma-1}{3(2\Gamma+1)}
  \le
  \Gamma\frac{\Gamma+2}{3(2\Gamma+1)}
\]
and its reverse-direction companion, both valid for \(\Gamma>1\).  The attempted coherent-endpoint refutation therefore fails.

For the incident pairwise relaxation, keep only one lower-outcome incident edge, say \(a\sim_z b\), and leave the opposite coordinate \(c\) subject only to nonnegativity and calibration.  The active pairwise candidate has
\[
  r_b=\frac{1}{3(\Gamma+1)},\qquad
  r_a=\frac{\Gamma}{3(\Gamma+1)},\qquad
  r_c=\frac23,
\]
so
\[
  x_b=\frac{2\Gamma+1}{3(\Gamma+1)}=T_{\mathrm{pair}}(\Gamma),\qquad
  x_a=\frac{\Gamma+2}{3(\Gamma+1)},\qquad
  x_c=0.
\]
It satisfies the retained edge constraints and is therefore a feasible pairwise-relaxation vertex.  It is not a coherent common-law vertex because the dropped incident lower-outcome constraint \(r_c\le \Gamma r_b\) would require
\[
  \frac23\le \frac{\Gamma}{3(\Gamma+1)},
\]
which fails for every finite \(\Gamma\ge 1\).  The refutation search therefore finds no witness against the conjecture; it instead isolates the dropped constraint as the source of strict containment.

\paragraph{Interpretation.}
The result says that the ordinal \(K=3\) common law is doing real work.  The pairwise relaxation can optimize along the \(a\sim_z b\) edge by pushing the opposite lower-outcome coordinate \(r_c\) to its calibration boundary \(2/3\).  The coherent ordinal problem cannot do this, because the same middle coordinate \(b\) must satisfy both incident adjacent odds-ratio restrictions.  The shared-middle constraint converts two edgewise feasible moves into one incompatible common-law move.

The slack is not defined after the fact as an endpoint difference.  It is the primitive algebraic slack obtained by comparing the two active bases:
\[
  \Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma)
  =
  \frac{\Gamma+2}{3(\Gamma+1)(2\Gamma+1)}.
\]
For every \(\Gamma>1\) in Assumption~\ref{ass:witness-cell}, this number is strictly positive, so the incident pairwise endpoint lies outside the coherent common-law endpoint.  By Assumption~\ref{ass:phase-neighborhood}, the same active constraints remain nondegenerate under sufficiently small relative perturbations of the witness margins, so the strict-containment phase is not a knife-edge equality of the exactly symmetric cell.

\paragraph{Proof.}
The proof is a finite-dimensional linear-programming active-basis calculation, the same extreme-point logic used in classical partial-identification programs such as Manski (1990) and Balke and Pearl (1997).  Randomization and consistency from Assumption~\ref{ass:randomization} justify reading the posterior coordinates as latent principal-stratum posterior weights in the observed cell, while Assumptions~\ref{ass:positivity}--\ref{ass:divergence} give the finite feasible polytope.  Assumption~\ref{ass:witness-cell} specializes that polytope to three adjacent strata, two outcome values, equal baseline weights, and \(1<\Gamma<\infty\).

In the symmetric witness cell, define \(x_h=q_h^1\) and \(r_h=q_h^0\).  Calibration gives \(x_h+r_h=2/3\) for each \(h\), and the two simplex equations give \(x_a+x_b+x_c=1\) and \(r_a+r_b+r_c=1\).  For the endpoint coordinate \(x=x_b\), these identities imply
\[
  r_b=\frac23-x,\qquad r_a+r_c=1-r_b=\frac13+x.
\]
The two lower-outcome incident edge restrictions from Assumption~\ref{ass:divergence} are
\[
  r_a\le \Gamma r_b,\qquad r_c\le \Gamma r_b.
\]
Adding the two inequalities yields
\[
  \frac13+x\le 2\Gamma\left(\frac23-x\right).
\]
Solving this inequality gives
\[
  (2\Gamma+1)x\le \frac{4\Gamma-1}{3},
  \qquad
  x\le \frac{4\Gamma-1}{3(2\Gamma+1)}
  =
  T_{\mathrm{mid}}(\Gamma).
\]
Thus \(T_{\mathrm{mid}}(\Gamma)\) is an upper bound for the coherent common-law endpoint.

The bound is attained by the candidate vertex
\[
  r_b=\frac{1}{2\Gamma+1},\quad
  r_a=r_c=\frac{\Gamma}{2\Gamma+1},\quad
  x_b=\frac{4\Gamma-1}{3(2\Gamma+1)},\quad
  x_a=x_c=\frac{\Gamma+2}{3(2\Gamma+1)}.
\]
Calibration is immediate because \(x_h+r_h=2/3\) for \(h=a,b,c\), and the two simplex equations follow by summing the displayed coordinates.  The lower-outcome constraints \(r_a=\Gamma r_b\) and \(r_c=\Gamma r_b\) are active.  For the upper-outcome constraints,
\[
  x_b\le \Gamma x_a
  \quad\Longleftrightarrow\quad
  4\Gamma-1\le \Gamma(\Gamma+2)
  \quad\Longleftrightarrow\quad
  0\le(\Gamma-1)^2,
\]
and
\[
  x_a\le \Gamma x_b
  \quad\Longleftrightarrow\quad
  \Gamma+2\le \Gamma(4\Gamma-1),
\]
which holds for \(\Gamma>1\).  The same check applies to \(c\) by symmetry.  Hence the coherent endpoint is exactly
\[
  T_{\mathrm{mid}}(\Gamma)=\frac{4\Gamma-1}{3(2\Gamma+1)}.
\]

For the incident pairwise relaxation, retain only one lower-outcome incident edge and the same calibration equations.  The active candidate is
\[
  r_b=\frac{1}{3(\Gamma+1)},\quad
  r_a=\frac{\Gamma}{3(\Gamma+1)},\quad
  r_c=\frac23,
\]
and therefore
\[
  x_b=\frac{2\Gamma+1}{3(\Gamma+1)},\quad
  x_a=\frac{\Gamma+2}{3(\Gamma+1)},\quad
  x_c=0.
\]
The retained lower-outcome edge \(a\sim_z b\) is active because \(r_a=\Gamma r_b\).  The retained upper-outcome edge satisfies
\[
  x_b\le \Gamma x_a
  \quad\Longleftrightarrow\quad
  2\Gamma+1\le \Gamma(\Gamma+2),
\]
which is true for \(\Gamma\ge 1\), and \(x_a\le \Gamma x_b\), which is true for \(\Gamma>1\).  Calibration and simplex hold by direct summation.  Thus the pairwise endpoint is
\[
  T_{\mathrm{pair}}(\Gamma)=\frac{2\Gamma+1}{3(\Gamma+1)}.
\]

Subtracting the coherent endpoint from the pairwise endpoint gives
\[
\begin{aligned}
  T_{\mathrm{pair}}(\Gamma)-T_{\mathrm{mid}}(\Gamma)
  &=
  \frac{2\Gamma+1}{3(\Gamma+1)}
  -
  \frac{4\Gamma-1}{3(2\Gamma+1)}
  \\
  &=
  \frac{(2\Gamma+1)^2-(4\Gamma-1)(\Gamma+1)}
       {3(\Gamma+1)(2\Gamma+1)}
  \\
  &=
  \frac{\Gamma+2}{3(\Gamma+1)(2\Gamma+1)}
  =
  \Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma).
\end{aligned}
\]
Because \(\Gamma>1\), the numerator and denominator are positive, so the slack is strictly positive.  The pairwise endpoint is therefore separated from the coherent common-law endpoint by the primitive K=3 cell slack.  Finally, Assumption~\ref{ass:phase-neighborhood} states the needed basis nondegeneracy: all constraints not active in the coherent and pairwise candidate bases have strict slack and the active bases persist under sufficiently small relative perturbations.  The displayed rational endpoint formulas are the symmetric-cell values of those bases, and the active-basis representation remains valid on the asserted relative-open neighborhood.  This proves Proposition~\ref{prop:phase-threshold}.

\paragraph{Sanity check.}
As \(\Gamma\to\infty\), the coherent endpoint tends to
\[
  \lim_{\Gamma\to\infty}T_{\mathrm{mid}}(\Gamma)=\frac23,
\]
which is the natural calibration ceiling \(x_b\le 2/3\) coming from \(r_b=2/3-x_b\ge0\).  The pairwise endpoint has the same limit,
\[
  \lim_{\Gamma\to\infty}T_{\mathrm{pair}}(\Gamma)=\frac23,
\]
and the primitive slack vanishes,
\[
  \lim_{\Gamma\to\infty}\Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma)=0.
\]
Thus when the sensitivity restriction becomes vacuous, the ordinal compatibility gain disappears, matching the no-restriction partial-identification intuition.  At any finite \(\Gamma>1\), the lower-outcome incident constraints are still active and the slack remains positive.

\paragraph{Counterexample or minimality check.}
Dropping the second incident lower-outcome edge \(b\sim_z c\) destroys the coherent endpoint.  The pairwise-relaxation vertex
\[
  r_b=\frac{1}{3(\Gamma+1)},\qquad
  r_a=\frac{\Gamma}{3(\Gamma+1)},\qquad
  r_c=\frac23,
\]
with the corresponding calibrated upper-outcome coordinates
\[
  x_b=\frac{2\Gamma+1}{3(\Gamma+1)},\qquad
  x_a=\frac{\Gamma+2}{3(\Gamma+1)},\qquad
  x_c=0
\]
satisfies simplex, calibration, nonnegativity, and the retained \(a\sim_z b\) adjacent odds-ratio constraints.  It violates the omitted coherent constraint \(r_c\le\Gamma r_b\), since
\[
  r_c-\Gamma r_b
  =
  \frac23-\frac{\Gamma}{3(\Gamma+1)}
  =
  \frac{\Gamma+2}{3(\Gamma+1)}
  >0.
\]
At this vertex,
\[
  x_b-T_{\mathrm{mid}}(\Gamma)
  =
  T_{\mathrm{pair}}(\Gamma)-T_{\mathrm{mid}}(\Gamma)
  =
  \Delta_{\mathrm{mid}}^{\mathrm{sym}}(\Gamma)>0.
\]
This is the minimality witness: the second incident adjacent-edge restriction is the condition that prevents the pairwise optimizer from being a coherent common-law optimizer.
