% =====================================================================
%  causalsmith Stage -1 proposal skeleton.
%  Written automatically by the causalsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_datafusion\_exact\_compatibility, specialization=v1
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_core.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. For free-form
%    `(qid, specialization)`, define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{causalsmith Stage -1 proposal: \texttt{pid\_datafusion\_exact\_compatibility} / \texttt{v1}%
  \\ \large\textit{No-cancellation compatibility for joint data-fusion sensitivity}}
\author{causalsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
The observed law is $P$ of $(X,S,A,Y)$, where $S\in\{0,1\}$ indexes an observational study and a trial, $A\in\{0,1\}$, and $Y\in[a,b]$ with $0<a<b$.  The target is the compatibility set $\mathcal K(P)=\{(\rho,\gamma):C_P(\rho,\gamma)=0\}$ for simultaneous relative NUC and study-exchangeability sensitivity.  The headline kernel is Conjecture~\ref{conj:exact}: an observed-law iff characterization for one support-respecting causal extension.

\begin{abstract}
Lanners, Rudin, Volfovsky, and Parikh formulate pointwise interval restrictions for joint data-fusion sensitivity and use a signed expectation as a practical compatibility proxy.  This proposal studies the no-cancellation functional $C_P$ obtained after support clipping and the observational-mixture identity.  Proposition~\ref{prop:infeasible} proves that $C_P>0$ rules out every compatible latent extension, and Proposition~\ref{prop:cancel} gives a two-stratum example in which the signed proxy accepts by cancellation.  Conjecture~\ref{conj:exact} asks whether $C_P=0$ is also sufficient for a single common extension.  A second open question concerns tie-inclusive, learned-nuisance inference for the resulting frontier.
\end{abstract}

\section{Introduction}
The joint failure of ignorability in an observational study and exchangeability across studies makes a sensitivity pair meaningful only when both restrictions hold in one latent causal law.

Lanners et al.~\citep{LannersRudinVolfovskyParikh2025}, Section~4 through Remark~1, give pointwise population interval inequalities.  Their Appendix~D/E.3 signed expectation $G_t^{\mathrm{LRVP}}$ is an operational proxy, not an exact common-extension theorem.  The question is whether support clipping and the mixture identity turn the pointwise requirements into an observed-law iff frontier.

The immediate consumer is a compatibility map for Project STAR-style fusion: a positive $C_P$ can certify that a plotted sensitivity pair has no causal interpretation.  The cancellation witness tells an empirical user not to accept a pair merely because signed overlap averages to zero.

\begin{itemize}[leftmargin=*]
\item Proposition~1: $C_P(\theta)>0$ implies no compatible extension.  Gap: the proxy in \citep{LannersRudinVolfovskyParikh2025} may cancel.  Consumer: incompatibility certification.
\item Conjecture~1: $C_P(\theta)=0$ is sufficient for a common extension.  Gap: a measurable joint extension is not supplied by pointwise intervals alone.  Consumer: exact sensitivity regions.
\item Proposition~2: a valid two-stratum law has $G_0^{\mathrm{LRVP}}=0$ but $C_P=6/5$.  Gap: a finite cancellation witness is absent from the proxy analysis.  Consumer: stress testing.
\item Open-ended Question~2: can numerical-delta contact inference cover the frontier with ties and learned nuisances?  Gap: existing components do not deliver this combination.  Consumer: outer confidence regions.
\end{itemize}

\section{Related work}
Lanners et al.~\citep{LannersRudinVolfovskyParikh2025} are the flagship comparator: their pointwise restrictions motivate the extension question and their signed proxy motivates Proposition~2.  Parikh et al.~\citep{ParikhMorucciOrlandiRoyRudinVolfovsky2023} isolate the attribution problem without a simultaneous-extension characterization.  Chernozhukov, Lee, and Rosen~\citep{ChernozhukovLeeRosen2013} provide contact selection; Masten and Poirier~\citep{MastenPoirier2020} provide frontier inversion; Fang and Santos~\citep{FangSantos2019} provide directional inference; and Hong and Li~\citep{HongLi2018} provide the numerical delta method.  Chernozhukov et al.~\citep{ChernozhukovEtAl2018DML} supply cross-fitting, while Luedtke and van der Laan~\citep{LuedtkeVanderLaan2016} explain why positive-mass ties are nonregular.

\section{Formal setup}
Let $e_t(x,s)=P(A=t\mid X=x,S=s)$ and $\mu_{st}(x)=E_P[Y\mid X=x,S=s,A=t]$.  Define $V_t^- =\max\{a,\mu_{1t}/(1+\gamma)\}$, $V_t^+=\min\{b,(1+\gamma)\mu_{1t}\}$, $C_t^-=\max\{a,\mu_{0t}/(1+\rho)\}$, $C_t^+=\min\{b,(1+\rho)\mu_{0t}\}$, and $W_t^\pm=e_t(\cdot,0)\mu_{0t}+e_{1-t}(\cdot,0)C_t^\pm$.  Then
\[
C_P(\theta)=\max_t\E\left[\left(\max\{V_t^-,W_t^-\}-\min\{V_t^+,W_t^+\}\right)_+\right],\qquad \mathcal K(P)=\{\theta:C_P(\theta)=0\}.
\]
The class $\mathcal M(P,\rho,\gamma)$ contains laws $Q$ on $(X,S,A,Y(0),Y(1))$ whose pushforward $(X,S,A,Y(A))$ equals $P$, which satisfy trial randomization and the two stated sensitivity restrictions.

\section{Assumptions}
\begin{assumption}[Latent-law restrictions]\label{ass:latent}
The covariate space is standard Borel; $Y(t)\in[a,b]$; $\operatorname{Law}_Q(X,S,A,Y(A))=P$; $Y(t)\perp A\mid(X,S=1)$; and all study and treatment propensities are uniformly positive.  The missing-arm mean belongs to $[\mu_{0t}/(1+\rho),(1+\rho)\mu_{0t}]\cap[a,b]$, and $E_Q[Y(t)\mid X,S=0]$ belongs to $[\mu_{1t}/(1+\gamma),(1+\gamma)\mu_{1t}]\cap[a,b]$.
\end{assumption}

\begin{assumption}[Primitive inference class]\label{ass:primitive}
For inference, $X$ has compact support and density bounded above and away from zero, and $\pi,e_t,\mu_{st}$ belong to fixed Hölder balls with smoothness $\beta>d/2$.
\end{assumption}

\section{Main results}
\begin{lemma}[Observational mixture identity]\label{lem:mixture}
Every $Q$ satisfying the pushforward condition obeys $q_{t0}=e_t(\cdot,0)\mu_{0t}+e_{1-t}(\cdot,0)c_t$ almost surely.
\end{lemma}
\begin{proposition}[Positive violation implies infeasibility]\label{prop:infeasible}
Under Assumption~\ref{ass:latent}, $C_P(\theta)>0$ implies $\mathcal M(P,\rho,\gamma)=\varnothing$.
\end{proposition}
\begin{conjecture}[Exact common-latent extension (NOT YET PROVED)]\label{conj:exact}
Under Assumption~\ref{ass:latent}, $\mathcal M(P,\rho,\gamma)\ne\varnothing$ if and only if $C_P(\theta)=0$.
\end{conjecture}
\begin{proposition}[Two-stratum cancellation]\label{prop:cancel}
For the law with $P(X=x_1)=3/5$, $e_t=1/2$, $(\mu_{00},\mu_{10})(x_1)=(4,1/2)$, $(\mu_{00},\mu_{10})(x_2)=(4,4)$, and $\mu_{01}=\mu_{11}=1$, at $a=1/4$, $b=8$, and $\rho=\gamma=1$, one has $G_0^{\mathrm{LRVP}}=0$, $G_1^{\mathrm{LRVP}}=3/4$, $C_P=6/5$, and $\mathcal M(P,1,1)=\varnothing$.
\end{proposition}
\paragraph{Open-ended Question 2.} Under Assumption~\ref{ass:primitive}, can cross-fitted numerical-delta contact inference deliver uniform outer coverage and local power at positive-mass endpoint and arm ties?

\section{Sanity-check corollaries}
At $(\rho,\gamma)=(0,0)$, $C_P=0$ if and only if $\mu_{0t}(X)=\mu_{1t}(X)$ almost surely for both treatment states.  Thus the frontier reduces algebraically to conditional mean exchangeability at the no-violation origin.

\section{Proof-sketch route}
The proved direction conditions the latent mean on assignment, applies Lemma~\ref{lem:mixture}, maps the missing-arm interval into $[W_t^-,W_t^+]$, and intersects it with $[V_t^-,V_t^+]$.  The conjectured converse uses a measurable midpoint selector, recovers $c_t$, copies observed trial kernels for both potential outcomes, uses endpoint two-point kernels for missing observational potential outcomes, and conditionally independently couples the two missing potential outcomes.  For inference, spline learners are cross-fitted, face scores are linearized, active ties are retained, and the Hong--Li finite difference is combined with Fang--Santos directional analysis and contact selection.

\section{Honest scope flags}
The positive-violation implication and the cancellation arithmetic are supporting results.  The converse extension construction is Conjecture~\ref{conj:exact}, not a theorem.  Tie-inclusive coverage, level, separation rates, and local power remain open; the primitive model class does not assume a margin, Gaussian approximation, or bootstrap validity.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item Version 1 fixed the published model, support clipping, and the cancellation witness.
\item Version 2 made the observational mixture an identity rather than an assumption.
\item Version 3 distinguished pointwise feasibility inequalities from the signed operational proxy.
\item Version 4 repaired the latent-law pushforward, promoted the iff claim to an unproved conjecture, and added Hong--Li numerical-delta positioning.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem{LannersRudinVolfovskyParikh2025} Q. Lanners, C. Rudin, A. Volfovsky, and H. Parikh. Data Fusion for Partial Identification of Causal Effects. \emph{NeurIPS}, 2025.
\bibitem{ParikhMorucciOrlandiRoyRudinVolfovsky2023} H. Parikh et al. A Double Machine Learning Approach for Combining Experimental and Observational Studies. arXiv:2307.01449, 2023.
\bibitem{ChernozhukovLeeRosen2013} V. Chernozhukov, S. Lee, and A. M. Rosen. Intersection Bounds: Estimation and Inference. \emph{Econometrica}, 2013.
\bibitem{MastenPoirier2020} M. A. Masten and A. Poirier. Inference on Breakdown Frontiers. \emph{Quantitative Economics}, 2020.
\bibitem{FangSantos2019} Z. Fang and A. Santos. Inference on Directionally Differentiable Functions. \emph{Review of Economic Studies}, 2019.
\bibitem{HongLi2018} H. Hong and J. Li. The Numerical Delta Method. \emph{Journal of Econometrics}, 206:379--394, 2018.
\bibitem{ChernozhukovEtAl2018DML} V. Chernozhukov et al. Double/Debiased Machine Learning for Treatment and Causal Parameters. \emph{Econometrics Journal}, 2018.
\bibitem{LuedtkeVanderLaan2016} A. R. Luedtke and M. J. van der Laan. Statistical Inference for the Mean Outcome under a Possibly Non-Unique Optimal Treatment Strategy. \emph{Annals of Statistics}, 2016.
\end{thebibliography}

\end{document}
