\documentclass{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{mathrsfs,bm,bbm}
\usepackage{graphicx,booktabs,array,multirow,tabularx,longtable}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{algorithm,algpseudocode}
\usepackage{subcaption,tikz}
\usepackage{siunitx,cancel,accents}
\usepackage{microtype}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{cleveref}
\setlength{\emergencystretch}{2em}
\newtheorem{assumption}{Assumption}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{openendedquestion}{Open-ended Question}
\newtheorem{conjecture}{Conjecture}
\newcommand{\coreref}[1]{\ref{#1}}

\begin{document}

\sloppy

\section*{pid\_\allowbreak{}datafusion\_\allowbreak{}exact\_\allowbreak{}compatibility}

\noindent\textit{Specialization:} v1\par

\paragraph{TL;DR.} The exact observed-law compatibility region for simultaneous relative-NUC and study-exchangeability sensitivity is proved to be the computable zero set \(\mathcal K(P)=\{\theta:C_P(\theta)=0\}\), equivalently the set of sensitivity pairs admitting one support-respecting common latent causal law. The Lanners-compatible linear endpoints use the factors \(1-\rho\), \(1+\rho\), \(1-\gamma\), and \(1+\gamma\), with clipping to the known support \([a,b]\). This exact criterion differs from the signed-average proxy: in the verified two-stratum law with weights \(4/5\) and \(1/5\), \(G_0^{\mathrm{LRVP}}(1,1)=0\) but \(C_{P^{\mathrm{can}}}(1,1)=9/10\), so cancellation masks incompatibility. For inference, the proved positive-mass-tie subexperiment has sharp separation rate \(n^{-2\beta/(4\beta+d)}\), whereas fixed constant paths have the regular \(n^{-1/2}\) Gaussian boundary. Only uniform coverage and uniform level for the proposed cross-fitted numerical directional-delta procedure remain open.

\section{Project justification}

\paragraph{Gap.} Lanners et al. provide pointwise linear interval restrictions and use a signed expectation as a practical compatibility proxy, with resampling that holds fitted nuisance functions fixed. Those results do not characterize when the support-clipped restrictions are jointly realizable by one latent causal law, and they do not establish tie-inclusive uniform coverage or level after nuisance learning.

\paragraph{Niche.} The paper isolates the exact no-cancellation compatibility frontier for simultaneous relative-NUC and study-exchangeability sensitivity. It retains the Lanners-compatible linear \((1\pm\rho)\) and \((1\pm\gamma)\) forms, clips them to \([a,b]\), and distinguishes regular pointwise directions from the harder uniform geometry created by positive-mass ties. It does not claim to originate two-parameter sensitivity analysis or randomized--observational data fusion.

\paragraph{Fill.} The paper proves \(\mathcal M(P,\rho,\gamma)\ne\varnothing\Longleftrightarrow C_P(\rho,\gamma)=0\), verifies the two-stratum cancellation witness with weights \(4/5\) and \(1/5\) and exact violation \(9/10\), and proves a sharp \(n^{-2\beta/(4\beta+d)}\) minimax separation boundary in a tie subexperiment together with the contrasting root-\(n\) Gaussian constant-path power formula. Uniform coverage and uniform level of the specified numerical directional-delta procedure are the only remaining inference questions.

\section{Related work}

Lanners, Rudin, Volfovsky, and Parikh (NeurIPS 2025), including their Project STAR analysis, derive pointwise population interval requirements for simultaneous sensitivity and use \(G_t^{\mathrm{LRVP}}\), a signed expectation, as a practical proxy while holding fitted nuisances fixed in resampling. The present theorem retains their linear \((1\pm\rho)\) and \((1\pm\gamma)\) endpoint forms but enforces the known support \([a,b]\) by clipping and asks the different logical question of existence of one support-respecting common latent causal extension. The nonnegative functional \(C_P\) forbids cross-stratum cancellation: the explicit witness assigns weights \(4/5\) and \(1/5\), has signed proxy zero for arm zero, and has exact violation \(9/10\). Yu et al. combine randomized and non-randomized studies with triplet matching and two internal/external-bias sensitivity parameters, but do not give this support-clipped common-extension characterization. Parikh et al. study attribution between external-validity and ignorability failures rather than simultaneous latent-law feasibility. Hong--Li numerical differentiation, Fang--Santos directional inference, Chernozhukov--Lee--Rosen contact selection, and cross-fitting motivate the proposed inference construction; none is claimed here to establish its uniform tie-inclusive coverage or level. The proved minimax subexperiment instead shows why a uniform root-\(n\) local-power claim cannot accompany such validity over the frozen primitive class.

\section{Setup}

Target (estimand / structural parameter): \(\mathcal K(P)\).
Identifying functional / recovery map: \(\mathcal K(P)=\{\theta\in[0,1]^2:C_P(\theta)=0\}\), where \(C_P(\theta)=\max_{t\in\mathcal T}E_{P_X}[(\max\{V_t^-,W_t^-\}-\min\{V_t^+,W_t^+\})_+]\)..
\begin{itemize}
  \item \(n\) --- \texttt{integer}; \(\mathbb N\); \texttt{index}
  \par\smallskip\noindent\emph{Definition.} \texttt{Sample-\allowbreak{}size index.}
  \item \(d\) --- \texttt{integer}; \(\mathbb N\); \texttt{dimension}
  \par\smallskip\noindent\emph{Definition.} \texttt{Covariate dimension.}
  \item \(\mathcal X\) --- \texttt{set}; \(\mathbb R^d\); \texttt{support}
  \par\smallskip\noindent\emph{Definition.} \texttt{Covariate support.}
  \item \(\mathcal T\) --- \texttt{set}; \(\{0,1\}\); \texttt{index set}
  \par\smallskip\noindent\emph{Definition.} \texttt{Treatment-\allowbreak{}state set.}
  \item \(t,s,k\) --- \texttt{indices}; \(t,k\in\mathcal T,\ s\in\{0,1\}\); \texttt{indices}
  \par\smallskip\noindent\emph{Definition.} \texttt{Treatment and study indices.}
  \item \(a,b\) --- \texttt{constants}; \(0<a<b<\infty\); \texttt{support endpoints}
  \par\smallskip\noindent\emph{Definition.} \texttt{Known outcome-\allowbreak{}support endpoints.}
  \item \(\theta=(\rho,\gamma)\) --- \texttt{vector}; \(\Theta=[0,1]^2\); \texttt{index}
  \par\smallskip\noindent\emph{Definition.} \texttt{Sensitivity pair for unmeasured confounding and study exchangeability.}
  \item \(\varepsilon,\alpha\) --- \texttt{constants}; \(\varepsilon\in(0,1/2),\ \alpha\in(0,1)\); \texttt{constants}
  \par\smallskip\noindent\emph{Definition.} \texttt{Positivity and noncoverage constants.}
  \item \(O_i=(X_i,S_i,A_i,Y_i)\) --- \texttt{random vector}; \(\mathcal X\times\{0,1\}\times\mathcal T\times[a,b]\); \texttt{observation}
  \par\smallskip\noindent\emph{Definition.} \texttt{Observed unit.}
  \item \(P,P_X,f_X\) --- \texttt{probability laws and density}; \(P\in\mathcal P(\mathcal X\times\{0,1\}\times\mathcal T\times[a,b])\); \texttt{observed law}
  \par\smallskip\noindent\emph{Definition.} \texttt{Observed law,\allowbreak{} its covariate marginal,\allowbreak{} and its Lebesgue density when it exists.}
  \item \(Q\) --- \texttt{probability law}; \(\mathcal P(\mathcal X\times\{0,1\}\times\mathcal T\times[a,b]^2)\); \texttt{latent law}
  \par\smallskip\noindent\emph{Definition.} Latent causal law on \(X,S,A,Y(0),Y(1)\); the realized outcome is \(Y(A)\).
  \item \(\pi,e_t,\mu_{st}\) --- \texttt{functions}; \(\pi:\mathcal X\to[0,1],\ e_t:\mathcal X\times\{0,1\}\to[0,1],\ \mu_{st}:\mathcal X\to[a,b]\); \texttt{nuisances}
  \par\smallskip\noindent\emph{Definition.} Observed nuisances \(\pi(x)=P(S=1\mid X=x)\), \(e_t(x,s)=P(A=t\mid X=x,S=s)\), and \(\mu_{st}(x)=E_P[Y\mid X=x,S=s,A=t]\).
  \item \(c_t,q_{t0}\) --- \texttt{functions}; \(\mathcal X\to[a,b]\); \texttt{latent means}
  \par\smallskip\noindent\emph{Definition.} Latent means \(c_t(x)=E_Q[Y(t)\mid X=x,S=0,A=1-t]\) and \(q_{t0}(x)=E_Q[Y(t)\mid X=x,S=0]\).
  \item \(v_t^\pm,w_t^\pm,H_t^{\mathrm{LRVP}},G_t^{\mathrm{LRVP}}\) --- \texttt{functions}; \(\mathcal X\times\Theta\to\mathbb R\); \texttt{comparator functionals}
  \par\smallskip\noindent\emph{Definition.} \texttt{Published un-\allowbreak{}clipped envelopes,\allowbreak{} signed overlap,\allowbreak{} and practical proxy.}
  \item \(C_t^\pm,V_t^\pm,W_t^\pm\) --- \texttt{functions}; \(\mathcal X\times\Theta\to[a,b]\); \texttt{exact envelopes}
  \par\smallskip\noindent\emph{Definition.} \texttt{Support-\allowbreak{}clipped missing-\allowbreak{}arm,\allowbreak{} trial,\allowbreak{} and observational-\allowbreak{}mixture envelopes.}
  \item \(C_P,\mathcal K(P),\mathcal M(P,\rho,\gamma)\) --- \texttt{functional and sets}; \(C_P:\Theta\to[0,\infty)\); \texttt{identified objects}
  \par\smallskip\noindent\emph{Definition.} \texttt{Observed compatibility functional,\allowbreak{} its zero set,\allowbreak{} and the compatible latent-\allowbreak{}law class.}
  \item \(m,\nu_m,q_t^\star,c_t^\star\) --- \texttt{scalar,\allowbreak{} law,\allowbreak{} and functions}; \(m\in[a,b],\ \nu_m\in\mathcal P([a,b])\); \texttt{extension construction}
  \par\smallskip\noindent\emph{Definition.} \texttt{Endpoint outcome kernel and measurable selector route for a latent extension.}
  \item \(P^{\mathrm{can}}\) --- \texttt{probability law}; \(\mathcal P(\mathcal X\times\{0,1\}\times\mathcal T\times[a,b])\); \texttt{counterexample}
  \par\smallskip\noindent\emph{Definition.} \texttt{Two-\allowbreak{}stratum cancellation witness.}
  \item \(\beta,B,\mathcal H_B^\beta,\underline f,\bar f,\overline{\mathcal P}\) --- \texttt{regularity objects}; \(\beta>d/2,\ B>0,\ 0<\underline f<\bar f<\infty\); \texttt{inference model}
  \par\smallskip\noindent\emph{Definition.} \texttt{Hölder regularity,\allowbreak{} density bounds,\allowbreak{} and primitive observed-\allowbreak{}law class.}
  \item \(J,\mathcal I_j,p_K,K_n\) --- \texttt{folds and basis}; \(J\ge2,\ K=K_n\); \texttt{learner construction}
  \par\smallskip\noindent\emph{Definition.} \texttt{Cross-\allowbreak{}fitting partition and normalized tensor-\allowbreak{}product spline or wavelet basis.}
  \item \(\widehat\eta^{(-j)},\widehat\pi^{(-j)},\widehat e_t^{(-j)},\widehat\mu_{st}^{(-j)}\) --- \texttt{functions}; \(\widehat\eta^{(-j)}=(\widehat\pi^{(-j)},\widehat e^{(-j)},\widehat\mu^{(-j)})\); \texttt{learners}
  \par\smallskip\noindent\emph{Definition.} \texttt{Foldwise truncated series-\allowbreak{}logit and bounded least-\allowbreak{}squares nuisance fits.}
  \item \(h,\widehat\eta_n,\mathfrak F,r_{\pi,n},r_{e,n},r_{\mu,n},F,q,v,A_0,P_n\) --- \texttt{face,\allowbreak{} fitted vector,\allowbreak{} map,\allowbreak{} rates,\allowbreak{} constants,\allowbreak{} and law sequence}; \(h\in\{V_t^-,V_t^+,W_t^-,W_t^+\},\ q>4,\ P_n\in\overline{\mathcal P}\); \texttt{performance notation}
  \par\smallskip\noindent\emph{Definition.} \texttt{A face functional,\allowbreak{} its cross-\allowbreak{}fitted vector,\allowbreak{} the nested functional map,\allowbreak{} error-\allowbreak{}rate labels,\allowbreak{} entropy-\allowbreak{}envelope constants,\allowbreak{} and a law sequence used only by the inference construction or question.}
  \item \(p_s,R^\mu_{sk},R^e_{sk},\psi_h,\mathcal S_n^{\mathrm{act}}\) --- \texttt{scores}; \(\mathcal S_n^{\mathrm{act}}\subset L_2(P)\); \texttt{orthogonal-\allowbreak{}score construction}
  \par\smallskip\noindent\emph{Definition.} \texttt{Study probabilities,\allowbreak{} residual representers,\allowbreak{} face scores,\allowbreak{} and tie-\allowbreak{}retaining active-\allowbreak{}score collection.}
  \item \(\xi_i,\mathbb G_n^\xi,\delta_n,\Theta_n,h_n\) --- \texttt{multipliers,\allowbreak{} process,\allowbreak{} and sequences}; \(E[\xi_i]=0,\ E[\xi_i^2]=1,\ \delta_n\downarrow0,\ h_n\downarrow0\); \texttt{bootstrap construction}
  \par\smallskip\noindent\emph{Definition.} \texttt{Multiplier process,\allowbreak{} numerical-\allowbreak{}delta step,\allowbreak{} deterministic sensitivity grid,\allowbreak{} and mesh.}
  \item \(\widehat C_n,\widehat C_n^\xi,\widehat c_{1-\alpha},\widehat{\mathcal K}_{n,1-\alpha}\) --- \texttt{processes and random set}; \(\ell^\infty(\Theta)\times\ell^\infty(\Theta)\times\mathbb R\times\mathcal P(\Theta)\); \texttt{inference objects}
  \par\smallskip\noindent\emph{Definition.} \texttt{Estimated functional,\allowbreak{} numerical-\allowbreak{}delta bootstrap process,\allowbreak{} critical value,\allowbreak{} and inverted outer confidence region.}
\end{itemize}

\section{Assumptions}

\begin{assumption}[ass:iid]\label{ass:iid}
\(O_1,\ldots,O_n\stackrel{\mathrm{iid}}{\sim}P\).
\par\smallskip\noindent\emph{Standard} (independent sampling, \cite{ChernozhukovEtAl2018DML}).
\end{assumption}

\begin{assumption}[ass:pushforward]\label{ass:pushforward}
\(\operatorname{Law}_Q(X,S,A,Y(A))=P\).
\par\smallskip\noindent\emph{Standard} (observed-data pushforward, \cite{Kallenberg2002}).
\end{assumption}

\begin{assumption}[ass:trial-randomization]\label{ass:trial-randomization}
\((Y(0),Y(1))\perp_Q A\mid(X,S=1)\).
\par\smallskip\noindent\emph{Standard} (joint conditional trial randomization, \cite{LannersRudinVolfovskyParikh2025}).
\end{assumption}

\begin{assumption}[ass:relative-nuc]\label{ass:relative-nuc}
\(c_t(X)\in[C_t^-(X;\rho),C_t^+(X;\rho)]\) \(P_X\)-almost surely for every \(t\in\mathcal T\).
\par\smallskip\noindent\emph{Standard} (linear relative unmeasured-confounding sensitivity model, \cite{LannersRudinVolfovskyParikh2025}).
\end{assumption}

\begin{assumption}[ass:study-exchangeability]\label{ass:study-exchangeability}
\(q_{t0}(X)\in[V_t^-(X;\gamma),V_t^+(X;\gamma)]\) \(P_X\)-almost surely for every \(t\in\mathcal T\).
\par\smallskip\noindent\emph{Standard} (linear study-exchangeability sensitivity model, \cite{LannersRudinVolfovskyParikh2025}).
\end{assumption}

\begin{assumption}[ass:uniform-study-positivity]\label{ass:uniform-study-positivity}
\(\varepsilon\le\pi(X)\le1-\varepsilon\) \(P\)-almost surely.
\par\smallskip\noindent\emph{Standard} (uniform study positivity, \cite{LannersRudinVolfovskyParikh2025}).
\end{assumption}

\begin{assumption}[ass:uniform-treatment-positivity]\label{ass:uniform-treatment-positivity}
\(\varepsilon\le e_t(X,s)\le1-\varepsilon\) \(P\)-almost surely for every \(t\in\mathcal T\) and \(s\in\{0,1\}\).
\par\smallskip\noindent\emph{Standard} (uniform treatment positivity, \cite{LannersRudinVolfovskyParikh2025}).
\end{assumption}

\begin{assumption}[ass:compact-support]\label{ass:compact-support}
\(\mathcal X\subset\mathbb R^d\) is compact.
\par\smallskip\noindent\emph{Standard} (compact covariate support, \cite{ChernozhukovEtAl2018DML}).
\end{assumption}

\begin{assumption}[ass:density-bounds]\label{ass:density-bounds}
\(\underline f\le f_X(x)\le\bar f\) for Lebesgue-almost every \(x\in\mathcal X\).
\par\smallskip\noindent\emph{Standard} (density bounded above and away from zero, \cite{ChernozhukovEtAl2018DML}).
\end{assumption}

\begin{assumption}[ass:holder-nuisances]\label{ass:holder-nuisances}
\(\pi\in\mathcal H_B^\beta(\mathcal X)\), \(e_t(\cdot,s)\in\mathcal H_B^\beta(\mathcal X)\), and \(\mu_{st}\in\mathcal H_B^\beta(\mathcal X)\) for every \(t\in\mathcal T\) and \(s\in\{0,1\}\).
\par\smallskip\noindent\emph{Standard} (uniform Hölder nuisance balls, \cite{Newey1997}).
\end{assumption}

\section{Definitions}

\begin{definition}[def:published-endpoints]\label{def:published-endpoints}
\par\smallskip\noindent\emph{Defined object.} \(v_t^\pm,w_t^\pm,H_t^{\mathrm{LRVP}},G_t^{\mathrm{LRVP}}\)
\par\smallskip\noindent\emph{Construction.} \(v_t^-(x;\gamma)=(1-\gamma)\mu_{1t}(x)\), \(v_t^+(x;\gamma)=(1+\gamma)\mu_{1t}(x)\), \(w_t^-(x;\rho)=e_t(x,0)\mu_{0t}(x)+e_{1-t}(x,0)(1-\rho)\mu_{0t}(x)\), \(w_t^+(x;\rho)=e_t(x,0)\mu_{0t}(x)+e_{1-t}(x,0)(1+\rho)\mu_{0t}(x)\), \(H_t^{\mathrm{LRVP}}(x;\theta)=\min\{v_t^+,w_t^+\}-\max\{v_t^-,w_t^-\}\), and \(G_t^{\mathrm{LRVP}}(\theta)=E_{P_X}[H_t^{\mathrm{LRVP}}(X;\theta)]\), for \(x\in\mathcal X\) and \(t\in\mathcal T\).
\par\smallskip\noindent\emph{Inputs.} \(\pi,e_t,\mu_{st}\); \(P,P_X,f_X\); \(\theta=(\rho,\gamma)\); \(t,s,k\).
\end{definition}

\begin{definition}[def:exact-endpoints]\label{def:exact-endpoints}
\par\smallskip\noindent\emph{Defined object.} \(C_t^\pm,V_t^\pm,W_t^\pm\)
\par\smallskip\noindent\emph{Construction.} \(C_t^-(x;\rho)=\max\{a,(1-\rho)\mu_{0t}(x)\}\), \(C_t^+(x;\rho)=\min\{b,(1+\rho)\mu_{0t}(x)\}\), \(V_t^-(x;\gamma)=\max\{a,(1-\gamma)\mu_{1t}(x)\}\), \(V_t^+(x;\gamma)=\min\{b,(1+\gamma)\mu_{1t}(x)\}\), and \(W_t^\pm(x;\rho)=e_t(x,0)\mu_{0t}(x)+e_{1-t}(x,0)C_t^\pm(x;\rho)\), for \(x\in\mathcal X\), \(t\in\mathcal T\), and \(\theta\in[0,1]^2\).
\par\smallskip\noindent\emph{Inputs.} \(a,b\); \(\pi,e_t,\mu_{st}\); \(\theta=(\rho,\gamma)\); \(t,s,k\).
\end{definition}

\begin{definition}[def:compatibility-functional]\label{def:compatibility-functional}
\par\smallskip\noindent\emph{Defined object.} \(C_P,\mathcal K(P)\)
\par\smallskip\noindent\emph{Construction.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle C_P(\theta)=\max_{t\in\mathcal T}E_{P_X}[(\max\{V_t^-(X;\gamma),W_t^-(X;\rho)\}-\min\{V_t^+(X;\gamma),W_t^+(X;\rho)\})_+]\)}}\par\noindent and \(\mathcal K(P)=\{\theta\in\Theta:C_P(\theta)=0\}\).
\par\smallskip\noindent\emph{Inputs.} \(P,P_X,f_X\); \(C_t^\pm,V_t^\pm,W_t^\pm\); \(\mathcal T\); \(\theta=(\rho,\gamma)\).
\end{definition}

\begin{definition}[def:endpoint-kernel]\label{def:endpoint-kernel}
\par\smallskip\noindent\emph{Defined object.} \(\nu_m\)
\par\smallskip\noindent\emph{Construction.} \(\nu_m=((b-m)/(b-a))\delta_a+((m-a)/(b-a))\delta_b\) for every \(m\in[a,b]\).
\par\smallskip\noindent\emph{Inputs.} \(m,\nu_m,q_t^\star,c_t^\star\); \(a,b\).
\end{definition}

\begin{definition}[def:selector-extension-handle]\label{def:selector-extension-handle}
\par\smallskip\noindent\emph{Defined object.} \(q_t^\star,c_t^\star\)
\par\smallskip\noindent\emph{Construction.} For each \(t\in\mathcal T\), set \(q_t^\star(x;\theta)=[\max\{V_t^-(x;\gamma),W_t^-(x;\rho)\}+\min\{V_t^+(x;\gamma),W_t^+(x;\rho)\}]/2\) and \(c_t^\star(x;\theta)=[q_t^\star(x;\theta)-e_t(x,0)\mu_{0t}(x)]/e_{1-t}(x,0)\). The construction route copies the observed trial arm-\(t\) outcome kernel to \(Y(t)\) under both trial assignments and, in study zero, uses \(\nu_{c_t^\star(X)}\) for each missing potential outcome, conditionally independently given \(X,S,A\).
\par\smallskip\noindent\emph{Inputs.} \(C_t^\pm,V_t^\pm,W_t^\pm\); \(\pi,e_t,\mu_{st}\); \(m,\nu_m,q_t^\star,c_t^\star\); \(\theta=(\rho,\gamma)\); \(t,s,k\).
\end{definition}

\begin{definition}[def:latent-class]\label{def:latent-class}
\par\smallskip\noindent\emph{Defined object.} \(\mathcal M(P,\rho,\gamma)\)
\par\smallskip\noindent\emph{Construction.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \mathcal M(P,\rho,\gamma)=\{Q\in\mathcal P(\mathcal X\times\{0,1\}\times\mathcal T\times[a,b]^2):\textup{ass:pushforward}\wedge\textup{ass:trial-randomization}\wedge\textup{ass:relative-nuc}\wedge\textup{ass:study-exchangeability}\}\)}}\par\noindent.
\par\smallskip\noindent\emph{Member properties.} \texttt{ass:\allowbreak{}pushforward}; \texttt{ass:\allowbreak{}trial-\allowbreak{}randomization}; \texttt{ass:\allowbreak{}relative-\allowbreak{}nuc}; \texttt{ass:\allowbreak{}study-\allowbreak{}exchangeability}.
\end{definition}

\begin{definition}[def:two-stratum-witness]\label{def:two-stratum-witness}
\par\smallskip\noindent\emph{Defined object.} \(P^{\mathrm{can}}\)
\par\smallskip\noindent\emph{Construction.} Let \(\mathcal X=\{x_1,x_2\}\), \(P^{\mathrm{can}}(X=x_1)=4/5\), \(P^{\mathrm{can}}(X=x_2)=1/5\), and \(P^{\mathrm{can}}(S=s,A=t\mid X=x_j)=1/4\). Set \(a=1/4\), \(b=8\), \(\theta=(1,1)\), \(\mu_{00}(x_1)=\mu_{00}(x_2)=4\), \(\mu_{10}(x_1)=1/2\), \(\mu_{10}(x_2)=4\), and \(\mu_{01}(x_j)=\mu_{11}(x_j)=1\). For every \(j\in\{1,2\}\), \(s\in\{0,1\}\), and \(t\in\mathcal T\), let \(Y\mid X=x_j,S=s,A=t\sim\nu_{\mu_{st}(x_j)}\).
\par\smallskip\noindent\emph{Inputs.} \(P^{\mathrm{can}}\); \(a,b\); \(\pi,e_t,\mu_{st}\); \(m,\nu_m,q_t^\star,c_t^\star\); \(\theta=(\rho,\gamma)\).
\end{definition}

\begin{definition}[def:holder-ball]\label{def:holder-ball}
\par\smallskip\noindent\emph{Defined object.} \(\mathcal H_B^\beta(\mathcal X)\)
\par\smallskip\noindent\emph{Construction.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \mathcal H_B^\beta(\mathcal X)=\{g:\mathcal X\to\mathbb R:\lVert g\rVert_{C^\beta(\mathcal X)}\le B\}\)}}\par\noindent.
\par\smallskip\noindent\emph{Inputs.} \(\mathcal X\); \(\beta,B,\mathcal H_B^\beta,\underline f,\bar f,\overline{\mathcal P}\).
\end{definition}

\begin{definition}[def:primitive-class]\label{def:primitive-class}
\par\smallskip\noindent\emph{Defined object.} \(\overline{\mathcal P}\)
\par\smallskip\noindent\emph{Construction.} \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \overline{\mathcal P}=\{P\in\mathcal P(\mathcal X\times\{0,1\}\times\mathcal T\times[a,b]):\textup{ass:compact-support}\wedge\textup{ass:density-bounds}\wedge\textup{ass:uniform-study-positivity}\wedge\textup{ass:uniform-treatment-positivity}\wedge\textup{ass:holder-nuisances}\}\)}}\par\noindent.
\par\smallskip\noindent\emph{Member properties.} \texttt{ass:\allowbreak{}compact-\allowbreak{}support}; \texttt{ass:\allowbreak{}density-\allowbreak{}bounds}; \texttt{ass:\allowbreak{}uniform-\allowbreak{}study-\allowbreak{}positivity}; \texttt{ass:\allowbreak{}uniform-\allowbreak{}treatment-\allowbreak{}positivity}; \texttt{ass:\allowbreak{}holder-\allowbreak{}nuisances}.
\end{definition}

\begin{definition}[def:inference-handle]\label{def:inference-handle}
\par\smallskip\noindent\emph{Defined object.} \(\widehat C_n,\widehat C_n^\xi,\widehat c_{1-\alpha},\widehat{\mathcal K}_{n,1-\alpha}\)
\par\smallskip\noindent\emph{Construction.} Use a normalized tensor-product spline or compactly supported wavelet basis \(p_K(x)\) of order at least \(\lceil\beta\rceil\), with \(K=K_n\), and fixed \(J\)-folds. On training complements fit truncated series logits \(\widehat\pi^{(-j)},\widehat e_k^{(-j)}\) and bounded series least squares \(\widehat\mu_{sk}^{(-j)}\). Require for this construction \(K_n\log n/n=o(1)\), \(K_n^{-\beta/d}=o(n^{-1/4})\), foldwise uniform errors \(r_{\pi,n},r_{e,n},r_{\mu,n}\), and \(r_{\mu,n}(r_{e,n}+r_{\pi,n})=o(n^{-1/2})\). Put \(p_s(x)=\pi(x)^s[1-\pi(x)]^{1-s}\), \(R^\mu_{sk}=1\{S=s,A=k\}[Y-\mu_{sk}(X)]/[p_s(X)e_k(X,s)]\), and \(R^e_{sk}=1\{S=s\}[1\{A=k\}-e_k(X,s)]/p_s(X)\). For any face \(h\in\{V_t^-,V_t^+,W_t^-,W_t^+\}\), define \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \psi_h(O;\theta)=h(X;\theta)-E_Ph(X;\theta)+\sum_{s,k}\partial_{\mu_{sk}}h(X;\theta)R^\mu_{sk}+\sum_{s,k}\partial_{e_k(\cdot,s)}h(X;\theta)R^e_{sk}\)}}\par\noindent, with branchwise directional derivatives of the displayed clipped formula; the \(\pi\)-derivative is zero. Let \(\mathcal S_n^{\mathrm{act}}\) collect centered face scores attaining a lower maximum, upper minimum, positive-part contact, or outer arm maximum at every \(\theta\in\Theta_n\), retaining all ties. Its sufficient performance conditions are an envelope \(F\) with \(\sup_{P\in\overline{\mathcal P}}E_PF^q<\infty\) for some \(q>4\), \(\log N(\eta,\mathcal S_n^{\mathrm{act}},L_2(P))\le v\log(A_0/\eta)\) uniformly in \(P\) and \(0<\eta\le1\), and a fixed studentization floor for nonzero-variance scores; zero-variance scores are deterministically zero. Let \(\widehat C_n(\theta)\) be the cross-fitted empirical face vector passed through the lower-max, upper-min, positive-part, expectation, and outer-max map \(\mathfrak F\). With independent mean-zero unit-variance multipliers, put \(\mathbb G_n^\xi=n^{-1/2}\sum_i\xi_i\widehat\psi_i\), choose \(\delta_n\downarrow0\) with \(n^{-1/2}/\delta_n\to0\) and \((r_{\pi,n}+r_{e,n}+r_{\mu,n})/\delta_n\to0\), and set \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \widehat C_n^\xi=[\mathfrak F(\widehat\eta_n+\delta_n\mathbb G_n^\xi)-\mathfrak F(\widehat\eta_n)]/\delta_n\)}}\par\noindent. Take deterministic \(\Theta_n\subset[0,1]^2\) with mesh \(h_n\to0\) and interpolation error \(o(n^{-1/2})\). Let \(\widehat c_{1-\alpha}\) be the conditional \((1-\alpha)\)-quantile of \(\sup_{\theta\in\Theta_n}\widehat C_n^\xi(\theta)\), and define \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \widehat{\mathcal K}_{n,1-\alpha}=\{\theta\in\Theta_n:\sqrt n\widehat C_n(\theta)\le\widehat c_{1-\alpha}\}\)}}\par\noindent, enlarged by measurable closed grid cells in \(\Theta\). Hong--Li supplies the finite-difference derivative, Fang--Santos the directional map, Chernozhukov--Lee--Rosen contact selection, and cross-fitting nuisance linearization.
\par\smallskip\noindent\emph{Inputs.} \(O_i=(X_i,S_i,A_i,Y_i)\); \(J,\mathcal I_j,p_K,K_n\); \(\widehat\eta^{(-j)},\widehat\pi^{(-j)},\widehat e_t^{(-j)},\widehat\mu_{st}^{(-j)}\); \(p_s,R^\mu_{sk},R^e_{sk},\psi_h,\mathcal S_n^{\mathrm{act}}\); \(\xi_i,\mathbb G_n^\xi,\delta_n,\Theta_n,h_n\); \(\varepsilon,\alpha\).
\end{definition}

\section{Main results}

\begin{lemma}[lem:observational-mixture-identity]\label{lem:observational-mixture-identity}
Every \(Q\) satisfying \(\textup{ass:pushforward}\) obeys the weighted observational-mixture identity\[(1-\pi(X))\bigl[q_{t0}(X)-e_t(X,0)\mu_{0t}(X)-e_{1-t}(X,0)c_t(X)\bigr]=0\]\(P_X\)-almost surely for each \(t\in\mathcal T\). Consequently, the unweighted identity holds \(P_X\)-almost surely on \(\{x:\pi(x)<1\}\).
\end{lemma}
\begin{proof}
Fix \(t\in\mathcal T\), and define the conditional discrepancy\[D_t(x)=q_{t0}(x)-e_t(x,0)\mu_{0t}(x)-e_{1-t}(x,0)c_t(x).\]All conditional expectations may be represented by arbitrary measurable versions. Multiplication by the observational-study probability makes the asserted equality invariant to the values of those versions outside the support of \(X\mid S=0\). By conditional iterated expectation under \(Q\), and because \(A\in\{t,1-t\}\),\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle \begin{aligned}q_{t0}(X)&=E_Q[Y(t)\mid X,S=0]\\&=Q(A=t\mid X,S=0)E_Q[Y(t)\mid X,S=0,A=t]\\&\quad+Q(A=1-t\mid X,S=0)E_Q[Y(t)\mid X,S=0,A=1-t]\end{aligned}\)}}\par\noindent}}
\]almost surely on \(\{S=0\}\). Assumption \(\textup{ass:pushforward}\) identifies the two conditional assignment probabilities with \(e_t(X,0)\) and \(e_{1-t}(X,0)\), respectively. On \(\{S=0,A=t\}\), consistency of the realized outcome gives \(Y(t)=Y(A)\), and the same pushforward assumption identifies the corresponding conditional mean with \(\mu_{0t}(X)\). The other conditional mean is \(c_t(X)\) by definition. Hence \(D_t(X)=0\) \(Q\)-almost surely on \(\{S=0\}\). The pushforward also gives \(Q(S=0\mid X)=P(S=0\mid X)=1-\pi(X)\). Therefore\[E_{P_X}[(1-\pi(X))|D_t(X)|]=E_Q[1\{S=0\}|D_t(X)|]=0.\]The integrand is nonnegative, so \((1-\pi(X))D_t(X)=0\) \(P_X\)-almost surely. On \(\{x:\pi(x)<1\}\), the factor \(1-\pi(x)\) is strictly positive, and division yields \(D_t(x)=0\) \(P_X\)-almost surely there. Since \(t\) was arbitrary and \(\mathcal T\) is finite, the asserted conclusion holds for every \(t\in\mathcal T\).
\end{proof}
\par\smallskip\noindent \textit{Justification.} The mixture equality follows from the observed-data pushforward and conditional iterated expectation; it is not an additional causal restriction. \textit{Gap.} A law-level bridge is needed to translate the missing-arm mean restriction into an interval for the observational-study potential-outcome mean. \textit{Consumer.} The positive-violation proposition uses the bridge to map \(c_t\in[C_t^-,C_t^+]\) into \(q_{t0}\in[W_t^-,W_t^+]\).

\begin{proposition}[prop:positive-violation-infeasibility]\label{prop:positive-violation-infeasibility}
Under \(\textup{ass:uniform-study-positivity}\) and \(\textup{ass:uniform-treatment-positivity}\), \(C_P(\theta)>0\) implies \(\mathcal M(P,\rho,\gamma)=\varnothing\). Indeed, for any \(Q\in\mathcal M(P,\rho,\gamma)\), the weighted observational-mixture identity may be divided by \(1-\pi(X)\ge\varepsilon\). Since \(c_t\in[C_t^-,C_t^+]\), it follows that \(q_{t0}\in[W_t^-,W_t^+]\), while study exchangeability gives \(q_{t0}\in[V_t^-,V_t^+]\). Thus every nonnegative conditional violation is zero almost surely, contradicting \(C_P(\theta)>0\).
\end{proposition}
\begin{proof}
Suppose, toward a contradiction, that \(C_P(\theta)>0\) and that some \(Q\in\mathcal M(P,\rho,\gamma)\) exists. By \(\textup{def:latent-class}\), this law satisfies \(\textup{ass:pushforward}\), \(\textup{ass:relative-nuc}\), and \(\textup{ass:study-exchangeability}\). By \(\textup{lem:observational-mixture-identity}\), for each \(t\in\mathcal T\),\[(1-\pi(X))\{q_{t0}(X)-e_t(X,0)\mu_{0t}(X)-e_{1-t}(X,0)c_t(X)\}=0\]almost surely. Assumption \(\textup{ass:uniform-study-positivity}\) gives \(1-\pi(X)\ge\varepsilon>0\), so division yields\[q_{t0}(X)=e_t(X,0)\mu_{0t}(X)+e_{1-t}(X,0)c_t(X)\qquad P_X\text{-almost surely}.\]Moreover, \(\textup{ass:uniform-study-positivity}\) and \(\textup{ass:uniform-treatment-positivity}\) imply\[P(S=0,A=k\mid X)=(1-\pi(X))e_k(X,0)\ge\varepsilon^2\]for every \(k\in\mathcal T\), so the arm-specific conditional means are defined on the relevant \(P_X\)-support. The binary-treatment probabilities are nonnegative and sum to one. Assumption \(\textup{ass:relative-nuc}\), together with \(\textup{def:exact-endpoints}\), therefore implies endpoint by endpoint that\[W_t^-(X;\rho)\le q_{t0}(X)\le W_t^+(X;\rho)\qquad P_X\text{-almost surely}.\]Assumption \(\textup{ass:study-exchangeability}\) simultaneously gives\[V_t^-(X;\gamma)\le q_{t0}(X)\le V_t^+(X;\gamma)\qquad P_X\text{-almost surely}.\]Define the proof intermediates\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle L_t(X;\theta)=\max\{V_t^-(X;\gamma),W_t^-(X;\rho)\},\qquad U_t(X;\theta)=\min\{V_t^+(X;\gamma),W_t^+(X;\rho)\}.\)}}\par\noindent}}
\]The two interval inclusions give \(L_t(X;\theta)\le q_{t0}(X)\le U_t(X;\theta)\) almost surely. Consequently, \((L_t-U_t)_+=0\) almost surely and \(E_{P_X}[(L_t-U_t)_+]=0\) for both treatment arms. Definition \(\textup{def:compatibility-functional}\) now gives \(C_P(\theta)=0\), contradicting \(C_P(\theta)>0\). Hence \(\mathcal M(P,\rho,\gamma)=\varnothing\).
\end{proof}
\par\smallskip\noindent \textit{Justification.} This necessity result turns any positive no-cancellation gap into an observed-law certificate that no common latent extension exists. \textit{Gap.} It establishes infeasibility without appealing to a signed average and isolates the converse construction as a separate theorem-level task. \textit{Consumer.} It certifies the emptiness of the latent class in the two-stratum witness and supports practical rejection of incompatible sensitivity pairs.

\begin{proposition}[prop:two-stratum-cancellation]\label{prop:two-stratum-cancellation}
For \(P^{\mathrm{can}}\) at \(\theta=(1,1)\), all means lie in \([1/4,8]\), \(\pi(x_j)=e_t(x_j,s)=1/2\), and all observed kernels are valid. For arm \(0\), the published un-clipped intervals are \([0,1]\) and \([2,6]\) at \(x_1\), giving \(H_0^{\mathrm{LRVP}}(x_1)=-1\), and \([0,8]\) and \([2,6]\) at \(x_2\), giving \(H_0^{\mathrm{LRVP}}(x_2)=4\). Hence \(G_0^{\mathrm{LRVP}}=(4/5)(-1)+(1/5)4=0\). For arm \(1\), the published intervals are \([0,2]\) and \([1/2,3/2]\) at both strata, so \(H_1^{\mathrm{LRVP}}=G_1^{\mathrm{LRVP}}=1\). The support-clipped arm-zero intervals are \(V_0=[1/4,1]\), \(C_0=[1/4,8]\), and \(W_0=[17/8,6]\) at \(x_1\), and \(V_0=[1/4,8]\), \(C_0=[1/4,8]\), and \(W_0=[17/8,6]\) at \(x_2\). For arm \(1\), they are \(V_1=[1/4,2]\), \(C_1=[1/4,2]\), and \(W_1=[5/8,3/2]\) at both strata. Thus the only conditional violation is \(9/8\) at \(x_1\) for arm \(0\), so \(C_{P^{\mathrm{can}}}(1,1)=9/10\) and \(\mathcal M(P^{\mathrm{can}},1,1)=\varnothing\) by Proposition 1.
\end{proposition}
\begin{proof}
Under \(P^{\mathrm{can}}\), every listed mean belongs to \([1/4,8]\). For \(m\in[1/4,8]\), \(\textup{def:endpoint-kernel}\) gives \(\nu_m\) nonnegative weights summing to one, support contained in \(\{1/4,8\}\), and mean \(m\); hence every displayed observed outcome kernel is valid. Moreover,\[\pi(x_j)=\sum_{t\in\mathcal T}P^{\mathrm{can}}(S=1,A=t\mid X=x_j)=\frac12,\]and, for every \(s,t,j\),\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle e_t(x_j,s)=\frac{P^{\mathrm{can}}(S=s,A=t\mid X=x_j)}{P^{\mathrm{can}}(S=s\mid X=x_j)}=\frac{1/4}{1/2}=\frac12.\)}}\par\noindent}}
\]At \(\rho=\gamma=1\), the published endpoints in \(\textup{def:published-endpoints}\) reduce to\[v_t^-=0,\qquad v_t^+=2\mu_{1t},\qquad w_t^-=\frac12\mu_{0t},\qquad w_t^+=\frac32\mu_{0t}.\]For arm \(0\), the trial and observational intervals at \(x_1\) are therefore \([0,1]\) and \([2,6]\), so\[H_0^{\mathrm{LRVP}}(x_1;(1,1))=\min\{1,6\}-\max\{0,2\}=-1.\]At \(x_2\) they are \([0,8]\) and \([2,6]\), so \(H_0^{\mathrm{LRVP}}(x_2;(1,1))=6-2=4\). It follows that\[G_0^{\mathrm{LRVP}}(1,1)=\frac45(-1)+\frac15(4)=0.\]For arm \(1\), both strata have published intervals \([0,2]\) and \([1/2,3/2]\), whence \(H_1^{\mathrm{LRVP}}=1\) pointwise and \(G_1^{\mathrm{LRVP}}(1,1)=1\). For the support-clipped endpoints in \(\textup{def:exact-endpoints}\), the equalities \(1-\rho=1-\gamma=0\) give \(C_t^-=V_t^-=1/4\), whereas \(C_t^+=\min\{8,2\mu_{0t}\}\) and \(V_t^+=\min\{8,2\mu_{1t}\}\). Thus, for arm \(0\),\[V_0(x_1)=[1/4,1],\qquad V_0(x_2)=[1/4,8],\qquad C_0(x_j)=[1/4,8].\]Since \(e_0=e_1=1/2\) and \(\mu_{00}=4\), both strata have\[W_0(x_j)=\left[\frac12(4)+\frac12\left(\frac14\right),\frac12(4)+\frac12(8)\right]=[17/8,6].\]For arm \(1\), both \(\mu_{01}\) and \(\mu_{11}\) equal one, and hence\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle V_1(x_j)=C_1(x_j)=[1/4,2],\qquad W_1(x_j)=\left[\frac12(1)+\frac12\left(\frac14\right),\frac12(1)+\frac12(2)\right]=[5/8,3/2].\)}}\par\noindent}}
\]The positive gap between the maximum lower endpoint and the minimum upper endpoint is therefore \(17/8-1=9/8\) for arm \(0\) at \(x_1\), zero for arm \(0\) at \(x_2\), and zero for arm \(1\) at either stratum. Definition \(\textup{def:compatibility-functional}\) yields\[C_{P^{\mathrm{can}}}(1,1)=\max\left\{\frac45\frac98+\frac15(0),0\right\}=\frac9{10}.\]Finally, since \(\varepsilon<1/2\), the equalities \(\pi=e_t=1/2\) satisfy both uniform positivity assumptions. Proposition \(\textup{prop:positive-violation-infeasibility}\) therefore applies and gives \(\mathcal M(P^{\mathrm{can}},1,1)=\varnothing\), even though the published arm-zero signed average equals zero.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The completely specified observed law verifies numerically that signed covariate-stratum cancellation can mask exact incompatibility. \textit{Gap.} A concrete witness is needed to show that the distinction between the published proxy and the exact functional is substantive rather than terminological. \textit{Consumer.} Applied readers can use the witness as a diagnostic warning: \(G_0^{\mathrm{LRVP}}=0\) can coexist with \(C_P=9/10\) and an empty compatible class.

\begin{openendedquestion}[oeq:uniform-contact-inference]\label{oeq:uniform-contact-inference}
Under \(P\in\overline{\mathcal P}\), \(\textup{ass:iid}\), and the construction-performance conditions in \(\textup{def:inference-handle}\), can the numerical directional-delta contact-set multiplier procedure attain \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \liminf_{n\to\infty}\inf_{P\in\overline{\mathcal P}}P(\mathcal K(P)\subseteq\widehat{\mathcal K}_{n,1-\alpha})\ge1-\alpha\)}}\par\noindent and yield uniformly level-\(\alpha\) tests of \(C_P(\theta)=0\), including positive-\(P_X\)-mass endpoint and arm ties?
\end{openendedquestion}
The proved \(\textup{thm:tie-local-separation-obstruction}\) shows that, in the canonical positive-mass endpoint-and-arm-tie subexperiment, the sharp uniform separation order is \(n^{-2\beta/(4\beta+d)}\), while \(\textup{lem:regular-constant-path-power}\) gives the pointwise \(n^{-1/2}\) Gaussian boundary along fixed constant directions. Thus no uniformly level procedure can have a nontrivial worst-case power curve indexed only by \(\sqrt n C_P(\theta)\) over the full tie-inclusive class. The additional \(\textup{lem:scalar-face-tangent-nonfactorization}\) proves that the displayed scalar multiplier input is insufficient to determine the tie derivative: two paths with identical integrated face derivatives have compatibility derivatives \(0\) and \(1/4\). Uniform coverage and uniform null level remain logically possible only after a selector-complete function-valued procedure and its missing uniform approximation and inversion arguments are supplied.
\par\smallskip\noindent \textit{Justification.} After the negative local-separation resolution, the honest residual question is uniform coverage and test level for the specific tie-retaining numerical directional-delta multiplier procedure. \textit{Gap.} No current theorem in the core supplies the tie-uniform bootstrap approximation and inversion argument required for those guarantees. \textit{Consumer.} Resolving this question would determine whether the computable population frontier is accompanied by a uniformly valid confidence region and null test.

\begin{lemma}[lem:standard-borel-conditional-kernel]\label{lem:standard-borel-conditional-kernel}
Let \(Z\) and \(W\) be random elements, with \(W\) taking values in a standard-Borel space. There exists a probability kernel \(z\mapsto\kappa(z,\cdot)\) that is a regular conditional law of \(W\) given \(Z=z\), and it is unique for \(\operatorname{Law}(Z)\)-almost every \(z\).
\end{lemma}

\begin{lemma}[lem:tie-subexperiment-minimax-boundary]\label{lem:tie-subexperiment-minimax-boundary}
The primitive conditions admit the following specialization for every \(d\ge1\) and \(\beta>d/2\): take \(\mathcal X=[0,1]^d\), \(X\) uniform, \(S\) and \(A\) independent fair Bernoulli variables, and an interior baseline mean \(m_0=(a+b)/2\), with \(B\) and the density bounds chosen to contain this submodel. Put \(Z=(Y-a)/(b-a)\). For a function \(u:[0,1]^d\to[-1/4,1/4]\), let \(P_u\) have \(Z\) Bernoulli with conditional success probability \(1/2+u(X)\) when \(S=1,A=0\), and success probability \(1/2\) in every other study-arm cell. Restrict \(u\) to a fixed bounded \(C^\beta\)-ball small enough that the resulting outcome regressions lie in \(\mathcal H_B^\beta(\mathcal X)\). Then\[C_{P_u}(0,0)=(b-a)\lVert u\rVert_{L_1([0,1]^d)}.\]Let \(r_n=n^{-2\beta/(4\beta+d)}\). For every \(\eta>0\), there is \(c_\eta>0\) such that every test \(\varphi_n\) with \(E_{P_0}\varphi_n\le\alpha+o(1)\) has, for some \(P_{u_n}\),\[C_{P_{u_n}}(0,0)\asymp c_\eta r_n,\qquad E_{P_{u_n}}\varphi_n\le\alpha+\eta+o(1).\]There likewise exist alternatives with \(C_{P_{u_n}}(0,0)\asymp n^{-1/2}\) and power at most \(\alpha+o(1)\). Conversely, let \(p_1,\ldots,p_K\) be an orthonormal piecewise-polynomial basis of order at least \(\lceil\beta\rceil\), put \(K\asymp n^{2d/(4\beta+d)}\), define \[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle R_i=4\{1\{S_i=1,A_i=0\}-1\{S_i=0,A_i=0\}\}Z_i,\qquad \widehat Q_K=\frac{1}{n(n-1)}\sum_{i\ne j}R_iR_j\sum_{k=1}^Kp_k(X_i)p_k(X_j),\)}}\par\noindent}}
\]and reject for \(\widehat Q_K>L_\alpha\sqrt K/n\), where \(L_\alpha\) is a sufficiently large constant. This test has level at most \(\alpha\) under \(P_0\) and power tending to one uniformly over the displayed Hölder submodel whenever \(C_{P_u}(0,0)/r_n\to\infty\). Thus \(r_n\) is the sharp minimax separation order in this positive-mass arm-and-endpoint-tie subexperiment.
\end{lemma}
\begin{proof}
We first verify membership and compute the target. The chosen study and treatment probabilities equal \(1/2\), so both positivity assumptions hold for every \(\varepsilon<1/2\). The covariate density is one. The endpoint law of \(Y\) is \(\nu_m\) with \(m=m_0+(b-a)u(x)\) in the cell \(S=1,A=0\) and \(m=m_0\) elsewhere. Choosing the radius of the \(C^\beta\)-ball for \(u\) sufficiently small keeps every mean in \([a,b]\) and every nuisance in the prescribed Hölder ball. Thus these laws form an admissible specialization of \(\overline{\mathcal P}\).

At \(\rho=\gamma=0\), support clipping is inactive because every conditional mean belongs to \([a,b]\), and the binary-treatment identity \(e_0(x,s)+e_1(x,s)=1\) gives\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle C_t^-(x;0)=C_t^+(x;0)=\mu_{0t}(x),\quad V_t^-(x;0)=V_t^+(x;0)=\mu_{1t}(x),\quad W_t^-(x;0)=W_t^+(x;0)=\mu_{0t}(x).\)}}\par\noindent}}
\]Consequently, the conditional violation for arm \(t\) is \(\lvert\mu_{1t}(x)-\mu_{0t}(x)\rvert\). Only arm zero differs in the submodel, whence\[C_{P_u}(0,0)=(b-a)\int_{[0,1]^d}|u(x)|\,dx.\]All four faces and the positive part tie on the whole covariate support at \(u=0\), so the tie has positive, indeed unit, \(P_X\)-mass.

We next prove the lower bound by an explicit mixture. Choose a nonzero nonnegative \(C^\infty\) function \(\psi\), supported in the interior of \([0,1]^d\), with \(\lVert\psi\rVert_\infty\le1\). For a small bandwidth \(h\), pack \(M\asymp h^{-d}\) disjoint cubes of side \(h\) into \([0,1]^d\), with lower corners \(x_1,\ldots,x_M\). For \(\omega=(\omega_1,\ldots,\omega_M)\in\{-1,1\}^M\), set\[u_\omega(x)=c h^\beta\sum_{j=1}^M\omega_j\psi\!\left(\frac{x-x_j}{h}\right).\]The supports are disjoint. The scaling identity for derivatives and the Hölder remainder show directly that \(\lVert u_\omega\rVert_{C^\beta}\le C_\psi c\), uniformly in \(h\) and \(\omega\). Taking \(c\) small therefore places every alternative in the submodel and in \([-1/4,1/4]\). Moreover,\[\lVert u_\omega\rVert_1=c h^\beta M h^d\int|\psi(z)|\,dz\asymp c h^\beta.\]

Let \(L_\omega=dP_{u_\omega}/dP_0\) for one observation. Conditional on \(G=1\{S=1,A=0\}\), the Bernoulli likelihood ratio is \(1+2(2Z-1)u_\omega(X)\), and it is one when \(G=0\). Since \(P_0(G=1)=1/4\), \(E_{P_0}(2Z-1)=0\), and \((2Z-1)^2=1\), direct multiplication gives\[E_{P_0}[L_\omega L_{\omega'}]=1+\langle u_\omega,u_{\omega'}\rangle_2.\]Let \(\overline P_n=2^{-M}\sum_\omega P_{u_\omega}^{\otimes n}\). Orthogonality of the disjoint bumps gives, for a constant \(\lambda=c^2\int\psi^2\),\[\langle u_\omega,u_{\omega'}\rangle_2=\lambda h^{2\beta+d}\sum_{j=1}^M\omega_j\omega_j'.\]Using \((1+x)^n\le e^{nx}\), averaging independently over \(\omega\) and \(\omega'\), and using \(\log\cosh z\le z^2/2\), we obtain\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle 1+\chi^2(\overline P_n,P_0^{\otimes n})\le\left\{\cosh\bigl(n\lambda h^{2\beta+d}\bigr)\right\}^M\le\exp\left(\frac{M n^2\lambda^2h^{4\beta+2d}}2\right)\le\exp(Cc^4n^2h^{4\beta+d}).\)}}\par\noindent}}
\]Take \(h\asymp n^{-2/(4\beta+d)}\). Then the last exponent is bounded by a constant multiple of \(c^4\), while every alternative has \(C_{P_{u_\omega}}(0,0)\asymp c(b-a)r_n\). By choosing \(c=c_\eta\) sufficiently small, the total-variation inequality \par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \lVert\overline P_n-P_0^{\otimes n}\rVert_{\mathrm{TV}}\le\sqrt{\chi^2(\overline P_n,P_0^{\otimes n})}/2\)}}\par\noindent makes this distance at most \(\eta+o(1)\). Therefore\[2^{-M}\sum_\omega E_{P_{u_\omega}}\varphi_n\le E_{P_0}\varphi_n+\eta+o(1)\le\alpha+\eta+o(1),\]so at least one mixture component has the asserted low power. If instead \(h\asymp n^{-1/(2\beta)}\), then the signal is of order \(n^{-1/2}\) and \(n^2h^{4\beta+d}=n^{-d/(2\beta)}\to0\). The same calculation gives total variation tending to zero and hence power at most \(\alpha+o(1)\) for at least one root-\(n\) alternative.

It remains to prove attainability of the rate. Define the projection kernel \(K_K(x,x')=\sum_{k=1}^Kp_k(x)p_k(x')\). The inverse-cell weight in \(R_i\) gives\[E_{P_u}[R_i\mid X_i=x]=4\left\{\frac14\left(\frac12+u(x)\right)-\frac14\left(\frac12\right)\right\}=u(x).\]Independence of two distinct observations therefore yields\[E_{P_u}[\widehat Q_K]=\sum_{k=1}^K\langle u,p_k\rangle_2^2=\lVert\Pi_Ku\rVert_2^2.\]A piecewise Taylor polynomial of degree \(\lfloor\beta\rfloor\) on cubes of side proportional to \(K^{-1/d}\) has pointwise remainder at most \(C K^{-\beta/d}\) by the defining Hölder inequality. Since the orthogonal projection is the best \(L_2\) approximation,\[\lVert u-\Pi_Ku\rVert_2\le C K^{-\beta/d}.\]Also \(|R_i|\le4\). Writing the order-two statistic as its first projection plus a degenerate remainder and expanding the variance gives\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle \operatorname{Var}_{P_u}(\widehat Q_K)\le C\left\{\frac{\lVert\Pi_Ku\rVert_2^2}{n}+\frac{E[K_K(X_1,X_2)^2]}{n^2}\right\}=C\left\{\frac{\lVert\Pi_Ku\rVert_2^2}{n}+\frac K{n^2}\right\}.\)}}\par\noindent}}
\]The equality uses orthonormality twice: \(E[K_K(X_1,X_2)^2]=K\). Under \(u=0\), Chebyshev's inequality thus makes the rejection probability at most \(C/L_\alpha^2\), so a fixed sufficiently large \(L_\alpha\) gives level at most \(\alpha\). On a unit-volume cube, \(\lVert u\rVert_2\ge\lVert u\rVert_1\). With \(K\asymp n^{2d/(4\beta+d)}\),\[K^{-\beta/d}\asymp r_n,\qquad \frac{\sqrt K}{n}\asymp r_n^2.\]Hence \(\lVert u\rVert_1/r_n\to\infty\) implies \(E\widehat Q_K/(\sqrt K/n)\to\infty\), and the displayed variance bound plus Chebyshev's inequality gives rejection probability tending to one uniformly. This proves the matching upper bound and the lemma.
\end{proof}

\begin{lemma}[lem:regular-constant-path-power]\label{lem:regular-constant-path-power}
In the canonical subexperiment of \(\textup{lem:tie-subexperiment-minimax-boundary}\), fix \(\kappa\in\mathbb R\) and take \(u_n(x)=\kappa/[(b-a)\sqrt n]\). Then \(C_{P_{u_n}}(0,0)=|\kappa|/\sqrt n\). Define\[D_i=4(b-a)\{1\{S_i=1,A_i=0\}-1\{S_i=0,A_i=0\}\}\left(Z_i-\frac12\right),\qquad \sigma^2=2(b-a)^2.\]Under \(P_{u_n}\), \(\sqrt n\,n^{-1}\sum_iD_i/\sigma\) converges to \(N(\kappa/\sigma,1)\). If \(\Phi\) is the standard-normal distribution function and \(z_p=\Phi^{-1}(p)\), the two-sided level-\(\alpha\) test rejecting when the absolute standardized statistic exceeds \(z_{1-\alpha/2}\) has limiting power\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle 1-\Phi\!\left(z_{1-\alpha/2}-\frac{\kappa}{\sigma}\right)+\Phi\!\left(-z_{1-\alpha/2}-\frac{\kappa}{\sigma}\right).\)}}\par\noindent}}
\]Thus fixed regular directions have the pointwise \(n^{-1/2}\) boundary even though the uniform tie-inclusive boundary in \(\textup{lem:tie-subexperiment-minimax-boundary}\) is slower.
\end{lemma}
\begin{proof}
The target calculation in \(\textup{lem:tie-subexperiment-minimax-boundary}\) gives\[C_{P_{u_n}}(0,0)=(b-a)|u_n|=\frac{|\kappa|}{\sqrt n}.\]Let \(G_1=1\{S=1,A=0\}\) and \(G_0=1\{S=0,A=0\}\). Since both cells have probability \(1/4\),\[E_{P_{u_n}}D_i=4(b-a)\left\{\frac14u_n-\frac14\cdot0\right\}=\frac{\kappa}{\sqrt n}.\]Because \(Z_i\in\{0,1\}\), \((Z_i-1/2)^2=1/4\) identically. The cells are disjoint and have total probability \(1/2\), so\[E_{P_{u_n}}D_i^2=16(b-a)^2\cdot\frac12\cdot\frac14=2(b-a)^2=\sigma^2.\]Thus \(\operatorname{Var}_{P_{u_n}}(D_i)\to\sigma^2\), and \(|D_i|\le2(b-a)\). For completeness, write \(X_{ni}=(D_i-E D_i)/(\sigma\sqrt n)\). Uniform boundedness gives \(\max_i|X_{ni}|\to0\), while \(\sum_iE X_{ni}^2\to1\). Taylor expansion \(E e^{itX_{ni}}=1-t^2E[X_{ni}^2]/2+o(E[X_{ni}^2])\), uniformly in \(i\), and multiplication over the independent observations show that the characteristic function of \(\sum_iX_{ni}\) converges to \(e^{-t^2/2}\). Therefore\[\frac{\sqrt n}{\sigma}\left(\frac1n\sum_{i=1}^nD_i-\frac{\kappa}{\sqrt n}\right)\rightsquigarrow N(0,1),\]which is the asserted shifted-normal limit. Taking the probability of the event \(|Z+\kappa/\sigma|>z_{1-\alpha/2}\) for \(Z\sim N(0,1)\) yields the displayed power formula.
\end{proof}

\begin{theorem}[thm:tie-local-separation-obstruction]\label{thm:tie-local-separation-obstruction}
The frozen assumptions do not imply a uniform root-\(n\) local-power conclusion over positive-mass ties. More precisely, they admit the canonical tie subexperiment in \(\textup{lem:tie-subexperiment-minimax-boundary}\), on which, with \(r_n=n^{-2\beta/(4\beta+d)}\), every sequence of tests \(\varphi_n\) satisfying \[\sup_{P:C_P(0,0)=0}E_P[\varphi_n]\le\alpha+o(1)\]has worst-case power at most \(\alpha+\eta+o(1)\) against some alternatives with \(C_P(0,0)\asymp r_n\), for every \(\eta>0\). There are also alternatives with \(C_P(0,0)\asymp n^{-1/2}\) for which the power is at most \(\alpha+o(1)\). The rate \(r_n\) is sharp in that subexperiment: the explicit quadratic projection test in \(\textup{lem:tie-subexperiment-minimax-boundary}\) is consistent whenever \(C_P(0,0)/r_n\to\infty\). By contrast, on the fixed constant-shift paths of \(\textup{lem:regular-constant-path-power}\), root-\(n\) separation is regular and the two-sided local power is \[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle 1-\Phi\!\left(z_{1-\alpha/2}-\frac{\kappa}{\sqrt{2}(b-a)}\right)+\Phi\!\left(-z_{1-\alpha/2}-\frac{\kappa}{\sqrt{2}(b-a)}\right).\)}}\par\noindent}}
\]Consequently, no uniformly valid test, including an inversion of the frozen numerical directional-delta procedure if it has the claimed level, can have a nontrivial worst-case power curve indexed only by \(\sqrt n C_P(\theta)\) over the tie-inclusive primitive class. The frozen conditions therefore answer the local-power part negatively: the regular pointwise boundary is \(n^{-1/2}\), whereas the uniform positive-mass-tie boundary can be \(n^{-2\beta/(4\beta+d)}\). This theorem neither proves nor refutes the coverage claim for \(\widehat{\mathcal K}_{n,1-\alpha}\); it proves that coverage and level, if established, cannot be supplemented by the requested uniform root-\(n\) local-power assertion without restricting the geometry of the alternatives.
\end{theorem}
\begin{proof}
The specialization constructed in \(\textup{lem:tie-subexperiment-minimax-boundary}\) is contained in \(\overline{\mathcal P}\), and \(P_0\) satisfies \(C_{P_0}(0,0)=0\). Hence any sequence of tests obeying\[\sup_{P:C_P(0,0)=0}E_P[\varphi_n]\le\alpha+o(1)\]also obeys \(E_{P_0}[\varphi_n]\le\alpha+o(1)\). Applying the lower-bound part of \(\textup{lem:tie-subexperiment-minimax-boundary}\), for every \(\eta>0\) there is an alternative \(P_{u_n}\) in that subexperiment such that\[C_{P_{u_n}}(0,0)\asymp c_\eta n^{-2\beta/(4\beta+d)},\qquad E_{P_{u_n}}[\varphi_n]\le\alpha+\eta+o(1).\]The same lemma's second mixture choice produces alternatives satisfying \(C_{P_{u_n}}(0,0)\asymp n^{-1/2}\) and \(E_{P_{u_n}}[\varphi_n]\le\alpha+o(1)\). Thus a positive-mass tie admits root-\(n\) alternatives asymptotically indistinguishable from the null in worst case. Its matching upper-bound calculation shows, within this canonical subexperiment, that the explicit quadratic projection test is consistent whenever\[\frac{C_{P_u}(0,0)}{n^{-2\beta/(4\beta+d)}}\longrightarrow\infty.\]This establishes the asserted sharp boundary only for the stated subexperiment.

For the contrasting constant directions, \(\textup{lem:regular-constant-path-power}\) gives \(C_{P_{u_n}}(0,0)=|\kappa|/\sqrt n\) and a standardized limiting distribution \(N(\kappa/\sigma,1)\), where \(\sigma=\sqrt2(b-a)\). Substituting this value of \(\sigma\) into that lemma's two-sided Gaussian rejection probability gives exactly\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle 1-\Phi\!\left(z_{1-\alpha/2}-\frac{\kappa}{\sqrt2(b-a)}\right)+\Phi\!\left(-z_{1-\alpha/2}-\frac{\kappa}{\sqrt2(b-a)}\right).\)}}\par\noindent}}
\]Hence root-\(n\) separation is regular along these fixed one-dimensional directions even though it fails uniformly over localized positive-mass-tie directions.

If a uniformly valid test had a nontrivial worst-case power curve determined only by \(\sqrt n\,C_P(\theta)\), the root-\(n\) alternatives from the first paragraph would force that curve to exceed its null level at a fixed positive local separation. Their power is instead at most \(\alpha+o(1)\), which is a contradiction. This argument applies to any inversion of the numerical directional-delta procedure only conditionally on that inversion having the claimed uniform level. Nothing in either supporting lemma establishes multiplier critical-value validity, confidence-region coverage, or uniform level for that procedure. The coverage and level questions therefore remain undecided, exactly as stated.
\end{proof}

\begin{theorem}[thm:exact-compatibility-characterization]\label{thm:exact-compatibility-characterization}
Suppose \(\textup{ass:uniform-study-positivity}\) and \(\textup{ass:uniform-treatment-positivity}\) hold. Then, for every \(\theta=(\rho,\gamma)\in[0,1]^2\),\[\mathcal M(P,\rho,\gamma)\ne\varnothing \quad\Longleftrightarrow\quad C_P(\theta)=0.\]Consequently, the exact observed-law compatibility region is the computable zero set\[\mathcal K(P)=\{\theta\in[0,1]^2:\mathcal M(P,\rho,\gamma)\ne\varnothing\}.\]The equivalence allows arbitrary positive-\(P_X\)-mass ties among the clipped lower and upper faces.
\end{theorem}
\begin{proof}
Fix \(\theta=(\rho,\gamma)\). We prove necessity and sufficiency separately.

\emph{Necessity.} Let \(Q\in\mathcal M(P,\rho,\gamma)\). By the pushforward restriction, on an observational arm with positive conditional probability,\[E_Q\{Y(t)\mid X,S=0,A=t\}=E_P\{Y\mid X,S=0,A=t\}=\mu_{0t}(X).\]By definition,\[E_Q\{Y(t)\mid X,S=0,A=1-t\}=c_t(X).\]Conditioning first on \(A\) therefore gives\[q_{t0}(X)=e_t(X,0)\mu_{0t}(X)+e_{1-t}(X,0)c_t(X)\qquad P_{X\mid S=0}\text{-almost surely}.\]The study-positivity inequality \(1-\pi(X)\ge\varepsilon\) makes \(P_{X\mid S=0}\) and \(P_X\) equivalent. Hence the last display holds \(P_X\)-almost surely. This argument also shows explicitly why division by observational-study mass is required.

The relative-NUC restriction and the nonnegativity of the treatment probabilities imply\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle \begin{aligned}e_t(X,0)\mu_{0t}(X)+e_{1-t}(X,0)C_t^-(X;\rho)&\le q_{t0}(X)\\&\le e_t(X,0)\mu_{0t}(X)+e_{1-t}(X,0)C_t^+(X;\rho).\end{aligned}\)}}\par\noindent}}
\]By the definition of the exact endpoints, this is\[q_{t0}(X)\in[W_t^-(X;\rho),W_t^+(X;\rho)]\qquad P_X\text{-almost surely}.\]Study exchangeability also gives\[q_{t0}(X)\in[V_t^-(X;\gamma),V_t^+(X;\gamma)]\qquad P_X\text{-almost surely}.\]Thus the two closed intervals intersect almost surely, so\[\max\{V_t^-(X;\gamma),W_t^-(X;\rho)\}\le\min\{V_t^+(X;\gamma),W_t^+(X;\rho)\}\]for each \(t\). Every positive-part violation is zero almost surely, and therefore \(C_P(\theta)=0\).

\emph{Sufficiency.} Suppose \(C_P(\theta)=0\), and put\[\ell_t(x)=\max\{V_t^-(x;\gamma),W_t^-(x;\rho)\},\qquad u_t(x)=\min\{V_t^+(x;\gamma),W_t^+(x;\rho)\}.\]For \(D_t(X)=(\ell_t(X)-u_t(X))_+\), the definition of \(C_P\) yields \(E_{P_X}D_t=0\) for every \(t\), because all of these expectations are nonnegative and their finite maximum is zero. Hence \(D_t=0\) almost surely. On the resulting common full-measure set, define\[q_t^*(x)=\frac{\ell_t(x)+u_t(x)}2.\]Then\[q_t^*(x)\in[V_t^-(x;\gamma),V_t^+(x;\gamma)]\cap[W_t^-(x;\rho),W_t^+(x;\rho)].\]Since \(e_{1-t}(x,0)\ge\varepsilon\), set\[c_t^*(x)=\frac{q_t^*(x)-e_t(x,0)\mu_{0t}(x)}{e_{1-t}(x,0)}.\]Membership of \(q_t^*\) in the \(W_t\)-interval and division by the positive coefficient \(e_{1-t}(x,0)\) give\[C_t^-(x;\rho)\le c_t^*(x)\le C_t^+(x;\rho).\]In particular, \(c_t^*(x)\in[a,b]\). All displayed selectors are measurable because they are obtained from measurable nuisance versions by finitely many maxima, minima, sums, and division by a function bounded away from zero. Modify them on the exceptional \(P_X\)-null set, if necessary, to take values in \([a,b]\).

It remains to construct one common latent law rather than merely compatible conditional means. By Lemma \(\textup{lem:standard-borel-conditional-kernel}\), choose measurable kernels \(\kappa_{st}(x,dy)\) that are versions of the conditional law of \(Y\) given \(X=x,S=s,A=t\). Positivity ensures\[\int y\,\kappa_{st}(x,dy)=\mu_{st}(x)\qquad P_X\text{-almost surely}.\]Write \(p_1(x)=\pi(x)\) and \(p_0(x)=1-\pi(x)\). The observed law then has the disintegration\[P(dx,\{s\},\{k\},dy)=P_X(dx)p_s(x)e_k(x,s)\kappa_{sk}(x,dy).\]

For \(m\in[a,b]\), the endpoint kernel satisfies\[\int y\,\nu_m(dy)=a\frac{b-m}{b-a}+b\frac{m-a}{b-a}=m.\]Moreover, \(m\mapsto\nu_m(B)\) is Borel measurable for every Borel \(B\subseteq[a,b]\), so it is a probability kernel. Define conditional laws of the potential-outcome pair by\[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle \begin{aligned}\Lambda_{1k}(x,dy_0,dy_1)&=\kappa_{10}(x,dy_0)\kappa_{11}(x,dy_1),\qquad k\in\{0,1\},\\\Lambda_{00}(x,dy_0,dy_1)&=\kappa_{00}(x,dy_0)\nu_{c_1^*(x)}(dy_1),\\\Lambda_{01}(x,dy_0,dy_1)&=\nu_{c_0^*(x)}(dy_0)\kappa_{01}(x,dy_1).\end{aligned}\)}}\par\noindent}}
\]These are measurable probability kernels. Now define \(Q^*\) on \((X,S,A,Y(0),Y(1))\) by\[Q^*(dx,\{s\},\{k\},dy_0,dy_1)=P_X(dx)p_s(x)e_k(x,s)\Lambda_{sk}(x,dy_0,dy_1).\]

For every \(s,k\), the \(k\)-th marginal of \(\Lambda_{sk}\) is \(\kappa_{sk}\). Consequently, the law of \((X,S,A,Y(A))\) under \(Q^*\) is exactly \(P\), proving the pushforward restriction. In study one, \(\Lambda_{1k}=\kappa_{10}\otimes\kappa_{11}\) does not depend on \(k\); hence\[(Y(0),Y(1))\perp_{Q^*}A\mid(X,S=1).\]In study zero, treatment positivity and the mean identity for \(\nu_m\) give\[E_{Q^*}\{Y(t)\mid X,S=0,A=1-t\}=c_t^*(X).\]Thus relative NUC holds. A direct conditioning calculation gives\[\begin{aligned}E_{Q^*}\{Y(t)\mid X,S=0\}&=e_t(X,0)\mu_{0t}(X)+e_{1-t}(X,0)c_t^*(X)\\&=q_t^*(X),\end{aligned}\]and membership of \(q_t^*\) in the \(V_t\)-interval proves study exchangeability. Hence \(Q^*\in\mathcal M(P,\rho,\gamma)\), establishing sufficiency.

The two directions prove the equivalence. The displayed equality for \(\mathcal K(P)\) follows from its definition as the zero set of \(C_P\). At no step was a unique active face required, so endpoint ties, lower-maximum ties, upper-minimum ties, and outer-arm ties are all included.
\end{proof}
\par\smallskip\noindent \textit{Justification.} The theorem upgrades the nonnegative violation functional from a one-sided incompatibility certificate to an exact, computable characterization by constructing a common latent extension whenever every clipped interval intersects. \textit{Gap.} Necessity alone would leave open whether pointwise interval intersection can be realized jointly by measurable potential-outcome kernels. \textit{Consumer.} It identifies the population compatibility frontier as the zero set \(\mathcal K(P)=\{\theta:C_P(\theta)=0\}\), including positive-mass ties.

\begin{lemma}[lem:scalar-face-tangent-nonfactorization]\label{lem:scalar-face-tangent-nonfactorization}
In the canonical positive-mass-tie subexperiment of \(\textup{lem:tie-subexperiment-minimax-boundary}\), let \(P_{\tau,r}\) agree with \(P_0\) except that \(\mu_{10,\tau}(x)=m_0+\tau r(x)\), where \(r\) is bounded and belongs to the admitted \(C^\beta\)-ball. For all sufficiently small \(|\tau|\), \[C_{P_{\tau,r}}(0,0)=|\tau|\int_{[0,1]^d}|r(x)|\,dx.\] Nevertheless, the two directions \(r_0(x)=0\) and \(r_1(x)=x_1-1/2\) have the same zero derivative at \(\tau=0\) for every integrated exact-face coordinate \(E[V_t^-]\), \(E[V_t^+]\), \(E[W_t^-]\), and \(E[W_t^+]\), whereas \[
\makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\par\noindent \makebox[\linewidth][c]{\resizebox{0.98\linewidth}{!}{\(\displaystyle \displaystyle \left.\frac{d}{d\tau}C_{P_{\tau,r_0}}(0,0)\right|_{\tau=0+}=0,\qquad \left.\frac{d}{d\tau}C_{P_{\tau,r_1}}(0,0)\right|_{\tau=0+}=\frac14.\)}}\par\noindent}}
\] Hence the directional derivative of the compatibility functional at this positive-mass tie does not factor through the vector of integrated face derivatives. In particular, the scalar face-score multiplier vector displayed in \(\textup{def:inference-handle}\) does not by itself specify the selector-complete, covariate-indexed tangent needed to differentiate the pointwise max--min and positive-part operations before integration.
\end{lemma}
\begin{proof}
Let \(P_0\) be the null law in the canonical subexperiment and fix \(\theta_0=(0,0)\). The baseline mean \(m_0=(a+b)/2\) is in the interior of the outcome support. Both \(r_0\) and \(r_1\) are bounded smooth functions, with \(|r_1|\le 1/2\). Therefore, for all sufficiently small \(|\tau|\), the perturbed mean \(m_0+\tau r_j(x)\) remains in \([a,b]\), the corresponding endpoint outcome kernel is valid, and the perturbed regression remains in the fixed Hölder submodel admitted by \(\textup{lem:tie-subexperiment-minimax-boundary}\). Thus \(P_{\tau,r_j}\in\overline{\mathcal P}\).

Write \(u_{\tau,r}(x)=\tau r(x)/(b-a)\). This is exactly the parametrization of the trial cell \(S=1,A=0\) used in \(\textup{lem:tie-subexperiment-minimax-boundary}\), since its conditional outcome mean is
\[m_0+(b-a)u_{\tau,r}(x)=m_0+\tau r(x).\]
The target identity proved in that lemma therefore gives
\[C_{P_{\tau,r}}(0,0)=(b-a)\lVert u_{\tau,r}\rVert_1=|\tau|\int_{[0,1]^d}|r(x)|\,dx.\]
Taking the right derivative at zero yields
\[\dot C_0(r):=\left.\frac{d}{d\tau}C_{P_{\tau,r}}(0,0)\right|_{\tau=0+}=\int_{[0,1]^d}|r(x)|\,dx.\]
Consequently \(\dot C_0(r_0)=0\). Since \(X\) is uniform on \([0,1]^d\), Fubini's identity gives
\[\dot C_0(r_1)=\int_0^1|z-1/2|\,dz=2\int_0^{1/2}(1/2-z)\,dz=\frac14.\]

It remains to compare the information retained by the integrated face coordinates. At \(\rho=\gamma=0\), clipping is inactive in this interior submodel, and \(\textup{def:exact-endpoints}\) gives
\[V_t^-=V_t^+=\mu_{1t},\qquad W_t^-=W_t^+=\mu_{0t}.\]
Along \(P_{\tau,r}\), only \(\mu_{10}\) changes. Hence the only possibly nonzero integrated face derivatives are those of \(E[V_0^-]\) and \(E[V_0^+]\), and both equal
\[\left.\frac{d}{d\tau}E_{P_X}[m_0+\tau r(X)]\right|_{\tau=0}=E_{P_X}[r(X)].\]
For \(r_0\) this expectation is zero. For \(r_1(x)=x_1-1/2\), it is also zero because \(X_1\) is uniform on \([0,1]\). Every other integrated face derivative is identically zero along both paths. Thus the two paths have the same integrated face-derivative vector but distinct compatibility derivatives. No map whose argument is only that vector can represent \(\dot C_0\).

Finally, \(\textup{def:inference-handle}\) defines each \(\psi_h(O;\theta)\) as a scalar score and \(\mathbb G_n^\xi=n^{-1/2}\sum_i\xi_i\widehat\psi_i\) as the resulting scalar vector over faces and sensitivity indices. The preceding non-factorization shows algebraically that this vector alone omits the covariate-indexed direction on which the pointwise positive part depends. Retaining all scalar face ties does not restore the lost function \(x\mapsto r(x)\). This proves the lemma.
\end{proof}

\section{Interpretation}

For each treatment arm, \(C_P(\theta)\) averages the nonnegative amount by which the larger support-clipped lower face exceeds the smaller support-clipped upper face and then takes the maximum across arms. Thus \(C_P(\theta)=0\) is equivalent to almost-sure conditional interval intersection, not merely nonnegative average signed overlap. The measurable-selector construction turns those intersections into one common latent law, so \(\mathcal K(P)\) is an exact compatibility region rather than an outer bound. In the cancellation witness, the stratum weights \(4/5\) and \(1/5\) cancel the signed arm-zero overlaps but leave \(C_{P^{\mathrm{can}}}(1,1)=9/10\). The inference conclusion has two scales: fixed smooth directions are regular at \(n^{-1/2}\), while uniformly varying positive-mass-tie directions can require \(n^{-2\beta/(4\beta+d)}\). This proved separation result does not certify the proposed bootstrap's coverage or level.

\section*{Technical internal limitation (diagnostic only)}

The exact compatibility characterization assumes two studies, binary treatment, a known strictly positive bounded outcome support, and uniform study and treatment positivity. Its sensitivity endpoints are specifically the support-clipped Lanners-compatible linear \((1\pm\rho)\) and \((1\pm\gamma)\) forms. The minimax rate is sharp for the displayed canonical Hölder tie subexperiment; it yields an obstruction to a primitive-class-wide root-\(n\) power curve, not a complete minimax theory at every point of the two-parameter frontier. A proof of uniform tie-inclusive coverage and uniform level for the frozen numerical directional-delta construction is still absent.

\section{Honest scope}

The proved results are the observational mixture identity, positive-violation infeasibility, exact common-latent compatibility characterization, the explicit two-stratum cancellation calculation with weights \(4/5\) and \(1/5\) and \(C_{P^{\mathrm{can}}}(1,1)=9/10\), the sharp tie-subexperiment separation rate \(n^{-2\beta/(4\beta+d)}\), and the regular constant-path Gaussian power formula. The paper does not claim that the proposed cross-fitted numerical directional-delta confidence region has uniform coverage or that its inverted tests have uniform level; those questions remain open. It makes no general optimality claim outside the stated tie subexperiment and no claim beyond the frozen binary-treatment, two-study sensitivity model.

\begin{thebibliography}{99}

  \bibitem{YuKarmakarVandeleestSchwarz2024} R. Yu, B. Karmakar, J. Vandeleest, and E. B. Schwarz. \textquotedblleft Using a Two-Parameter Sensitivity Analysis Framework to Efficiently Combine Randomized and Non-randomized Studies.\textquotedblright arXiv:2412.03731, 2024.

  \bibitem{LannersRudinVolfovskyParikh2025} Q. Lanners, C. Rudin, A. Volfovsky, and H. Parikh. ``Data Fusion for Partial Identification of Causal Effects.'' \emph{Advances in Neural Information Processing Systems}, 38:150638--150702, 2025. arXiv:2505.24296.

  \bibitem{ParikhMorucciOrlandiRoyRudinVolfovsky2023} H. Parikh, M. Morucci, V. Orlandi, S. Roy, C. Rudin, and A. Volfovsky. ``A Double Machine Learning Approach for Combining Experimental and Observational Studies.'' arXiv:2307.01449, 2023.

  \bibitem{ChernozhukovLeeRosen2013} V. Chernozhukov, S. Lee, and A. M. Rosen. ``Intersection Bounds: Estimation and Inference.'' \emph{Econometrica}, 81(2):667--737, 2013.

  \bibitem{MastenPoirier2020} M. A. Masten and A. Poirier. ``Inference on Breakdown Frontiers.'' \emph{Quantitative Economics}, 11(1):41--111, 2020.

  \bibitem{FangSantos2019} Z. Fang and A. Santos. ``Inference on Directionally Differentiable Functions.'' \emph{Review of Economic Studies}, 86(1):377--412, 2019.

  \bibitem{HongLi2018} H. Hong and J. Li. ``The Numerical Delta Method.'' \emph{Journal of Econometrics}, 206(2):379--394, 2018.

  \bibitem{ChernozhukovEtAl2018DML} V. Chernozhukov, D. Chetverikov, M. Demirer, E. Duflo, C. Hansen, W. Newey, and J. Robins. ``Double/Debiased Machine Learning for Treatment and Causal Parameters.'' \emph{Econometrics Journal}, 21(1):C1--C68, 2018.

  \bibitem{LuedtkeVanderLaan2016} A. R. Luedtke and M. J. van der Laan. ``Statistical Inference for the Mean Outcome under a Possibly Non-Unique Optimal Treatment Strategy.'' \emph{Annals of Statistics}, 44(2):713--742, 2016.

  \bibitem{Kallenberg2002} O. Kallenberg. \emph{Foundations of Modern Probability}. Springer, 2002.

  \bibitem{Newey1997} W. K. Newey. ``Convergence Rates and Asymptotic Normality for Series Estimators.'' \emph{Journal of Econometrics}, 79(1):147--168, 1997.

\end{thebibliography}

\end{document}