% =====================================================================
%  thmsmith Stage -1 proposal skeleton.
%  Written automatically by the thmsmith TS pipeline before Stage -1 runs.
%  Locked parameters: qid=pid\_network\_iv\_exposure, specialization=v3
%
%  HOW TO USE THIS FILE
%  --------------------
%  - The preamble (everything above the `% --- BEGIN CONTENT ---` marker)
%    and the `\section{...}` headers below are fixed by the pipeline.
%    Do NOT rewrite or rename them; the Step 3 reviewer subagent and the
%    downstream Stage 0 / Stage 1 prompts grep for these section titles.
%  - Each section contains exactly one `% TODO(stage-1 ...): ...`
%    placeholder. Replace each TODO with the content described for that
%    section in `CausalSmith/tools/src/discovery/prompts/stage_neg1_2_draft.txt`
%    ("REQUIRED OUTPUT FORMAT (Stage -1 proposal .tex)").
%  - The `\paragraph{Locked parameters.}` block in the metadata block
%    must pin the chosen `(qid, specialization, p, assignment, target,
%    regression)` precisely. If the proposal maps to the Q1 pool-mode,
%    reproduce that block verbatim from
%    `CausalSmith/doc/panel_formula_question_generator_note_with_common_prompts.tex`
%    (Q2..Q6 templates have been retired). Otherwise (free-form
%    `(qid, specialization)` — the default), define each parameter
%    explicitly here (no implicit conventions). Stage 0 quotes this block;
%    do not rephrase it after locking.
%  - Removing a section header, renaming a macro, or rewriting the
%    preamble is a regression: the file must still match this skeleton
%    after you finish.
% =====================================================================

\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{thmsmith Stage -1 proposal: \texttt{pid\_network\_iv\_exposure} / \texttt{v3}%
  \\ \large\textit{Sharp complier direct and spillover bounds from one shared network completion under dual exposure-map misspecification}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---  (everything above is fixed by the pipeline)

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode. The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_network\_iv\_exposure},\texttt{v3},
  P_{I,Z,D,S,W,Y;\,\pi,\varphi,\psi,\mathcal L},\
  \theta^{c}_{\mathcal F}(s,w),\
  \mathcal R_{\mathrm{shared\ completion+IV\ monotonicity}},\
  [\underline\theta^{c}_{\mathcal F}(P),\overline\theta^{c}_{\mathcal F}(P)]) .
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population, \(Z=(Z_1,\ldots,Z_n)\in\{0,1\}^n\) is the randomized encouragement vector drawn from a known design \(\pi\), \(D=(D_1,\ldots,D_n)\in\{0,1\}^n\) is realized treatment take-up, \(\mathcal L\) is the observed local graph, \(\varphi_i(D,\mathcal L)=S_i\) is the researcher-specified treatment-exposure mapping, and \(\psi_i(Z,\mathcal L)=W_i\) is the researcher-specified instrumental-exposure mapping. The true hidden graph is an undirected completion \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\), shared by both exposure channels. It induces hidden treatment exposure \(R_i^D(G,D)\in\{0,1\}\) and hidden instrument exposure \(R_i^Z(G,Z)\in\{0,1\}\). The target \(\theta^{c}_{\mathcal F}(s,w)\) is the family of complier direct and spillover effects at analyst labels \((s,w)\), where compliance is defined from the latent take-up table \(D_i(z_i,w,r)\) under own encouragement \(z_i\), observed instrumental label \(w\), and hidden instrumental exposure \(r\). The restrictions \(\mathcal R_{\mathrm{shared\ completion+IV\ monotonicity}}\) are finite support, bounded outcomes, consistency, one shared graph completion, exposure sufficiency for outcomes through \((D_i,S_i,R_i^D)\), exposure sufficiency for take-up through \((Z_i,W_i,R_i^Z)\), exclusion of \(Z\) from \(Y\) conditional on realized treatment exposures, and own-instrument monotonicity \(D_i(1,w,r)\ge D_i(0,w,r)\). The bounding functional is the sharp finite projection of one joint completion-principal-strata feasibility set, not a product of separate treatment-exposure, instrument-exposure, and compliance relaxations.

\begin{abstract}
The banked parent \texttt{pid\_network\_exposure/v1} gives sharp finite-network bounds for average direct effects when the treatment exposure mapping may be misspecified but treatment equals assignment. This proposal asks whether the same shared-completion logic survives when treatment take-up is endogenous, interference enters both the treatment and instrument channels, and both analyst exposure mappings may be wrong. The routine theorem is a finite sharpness statement: under bounded outcomes, exclusion, and exposure-indexed monotonicity, the identified set for a family of complier direct and spillover effects is the projection of one joint completion-principal-strata polytope. The flagship conjecture is that the natural product relaxation, which varies treatment-exposure kernels, instrumental-exposure kernels, and compliance kernels independently, is generically too wide on finite networks because one hidden edge constrains take-up and outcome exposures simultaneously. A second conjecture states that the same polytope jointly sharp-identifies the direct and spillover complier family, whereas coordinatewise endpoint stitching is nonsharp. If resolved, the result would connect the exposure-mapping robustness frontier to IV-with-interference models through a computable finite bound rather than an informal robustness warning.
\end{abstract}

\section{Introduction}
The parent theorem fixes the treatment-equals-assignment corner. The question here is whether finite-network shared-completion sharpness survives once treatment take-up is endogenous and interference enters both the outcome and take-up channels. The headline claim is that one can still formulate a sharp finite identified set for complier direct and spillover effects by projecting a single completion-principal-strata polytope, and that the obvious product relaxation is generally nonsharp because one hidden edge simultaneously allocates treatment exposure and instrumental exposure.

The upgrade delta relative to \texttt{pid\_network\_exposure/v1} is a strict widening of the maintained structure: the parent has one hidden exposure channel and no latent compliance types, while the present kernel adds an endogenous take-up table and a second misspecified exposure mapping but retains the same shared hidden graph. The closest published comparators are \citet[Abstract]{hoshino_yanagi_2024_noncompliance_unknown_interference}, which says ``We investigate identification conditions'' for complier effects under unknown interference, and \citet[Abstract]{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid}, which says ``we derive sharp upper and lower bounds'' under misspecified exposure mappings. The gap is that the first paper does not give finite-network sharp bounds under dual misspecification, and the second has no IV compliance layer. The kernel lives in partial identification for network interference with IV noncompliance.

The immediate consumer is the open problem isolated in the Stage \(-1.1\) gap payload: sharp finite-network bounds for complier direct and spillover effects when both the treatment and instrumental exposure mappings may be misspecified. A second consumer is the two-person encouragement literature of \citet{acerenza_martinez_iriarte_sanchez_becerra_spini_2025_household_bounds}, because a many-peer finite-network polytope would reveal whether those household sharp bounds are a low-dimensional corner rather than a separate phenomenon. A reader who accepts the conclusion would stop reporting separate robustness analyses for exposure misspecification and IV noncompliance when both are generated by one latent network.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the family of complier direct and spillover effects is the projection of a finite joint completion-principal-strata polytope. Gap: \citet{hoshino_yanagi_2024_noncompliance_unknown_interference} identifies and estimates; \citet{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid} gives misspecified-exposure bounds without noncompliance. Consumer: the Stage \(-1.1\) dual-misspecification open problem.
\item Conjecture 1: the product relaxation over treatment-exposure, instrument-exposure, and compliance kernels strictly overstates the sharp bound on an open set of finite experiments. Gap: extends the parent nonsharpness mechanism to the IV-interference setting and has no published analogue in \citet{savje_2024_misspecified_exposure_mappings} or \citet{vazquez_bare_2023_iv_spillovers}. Consumer: finite-network sensitivity analysis for encouraged network experiments.
\item Conjecture 2: the same polytope jointly sharp-identifies the direct and spillover complier family, while coordinatewise endpoint stitching is nonsharp. Gap: \citet{imai_jiang_malani_2021_interference_noncompliance} identifies named complier effects under stratified interference, but not a joint sharp family under dual mapping misspecification. Consumer: \citet{nibbering_oosterveen_2025_iv_interference_policy} and related policy-weighted linear combinations.
\end{itemize}

\section{Related work}
\citet{Manski1990} is the bounded-outcome partial-identification anchor [reused from parent], because every bound in this note still projects latent bounded response surfaces onto an observable law. \citet{AronowSamii2017} is the exposure-mapping benchmark [reused from parent], because it fixes how analyst labels \(S_i\) and \(W_i\) summarize interference when the mapping is correct.

\citet{savje_2024_misspecified_exposure_mappings} is the direct treatment-exposure misspecification comparator [new anchor to the upgrade], because the abstract states that exposure definitions and identifying assumptions should be separated and that ``Some important questions remain open.'' The present note takes one of those open questions into an IV setting and asks what sharp finite restriction replaces a correct mapping when both outcome and take-up channels are misspecified.

\citet{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid} is the closest partial-identification comparator [reused parent anchor, re-verified], because it derives sharp bounds under misspecified treatment exposure mappings and develops orthogonal estimators. The proposal differs by replacing their known-network, no-compliance-type environment with one shared completion that drives both treatment and instrument exposures and with latent monotone take-up tables.

\citet{hoshino_yanagi_2024_noncompliance_unknown_interference} is the closest IV-with-interference comparator [new anchor], because the abstract says ``We investigate identification conditions for the intention-to-treat effects and the average treatment effects for compliers'' under unknown interference and misspecified exposure mapping. The gap is finite-network sharpness: the paper works through identification and IPW estimation rather than a completion-constrained identified set.

\citet{imai_jiang_malani_2021_interference_noncompliance} is the two-stage randomization anchor [new anchor], because it identifies complier direct and spillover effects under stratified interference and noncompliance. The present kernel keeps the complier target but drops the known-strata exposure structure and replaces it with partial identification over a finite network-completion class.

\citet{vazquez_bare_2023_iv_spillovers} is the compliance-type frontier comparator [new anchor], because it shows that ordinary IV ratios generally aggregate several direct and spillover effects when spillovers enter treatment take-up and outcomes. The proposal sharpens that point by asking how much of the aggregation ambiguity survives after imposing one shared latent network and finite misspecification neighborhoods.

\citet{acerenza_martinez_iriarte_sanchez_becerra_spini_2025_household_bounds} is the closest sharp-bound encouragement design comparator [new anchor], because it gives sharp bounds for two-person encouragement designs with interference and strategic interaction. The proposal differs by moving from a household latent-type enumeration to a many-peer finite-network completion problem with analyst exposure mappings.

\citet{nibbering_oosterveen_2025_iv_interference_policy} is the policy-relevance frontier [new anchor], because it partially identifies policy-relevant direct and spillover effects with IVs under interference. A joint sharp family for exposure-indexed complier effects would supply the finite-network object needed to assess when exposure-robust bounds imply policy-robust bounds.

In the repository, the parent \texttt{pid\_network\_exposure/v1} is the load-bearing prior art: its headline statement is sharp ADE bounds from one shared hidden-graph completion under treatment-exposure misspecification. The only directly relevant catalogue entry in \texttt{doc/API.md}, Section 3, still describes \texttt{CausalSmith/PartialID/} as a seed area rather than a populated network-IV theorem family. The closest non-network banked prior art is \texttt{pid\_dynamic\_iv\_compliance\_v2}, whose headline kernel is assignment-memory sharpness for dynamic IV bounds; it contributes finite latent-response logic but not shared graph-completion geometry.

\section{Formal setup}
There are \(n<\infty\) units. The encouragement vector \(Z\in\{0,1\}^n\) is drawn from a known design \(\pi\) with finite support. The analyst observes realized take-up \(D\in\{0,1\}^n\), outcomes \(Y_i\in[0,1]\), a local undirected graph \(\mathcal L\), and two analyst exposure labels,
\[
S_i=\varphi_i(D,\mathcal L)\in\mathcal S,
\qquad
W_i=\psi_i(Z,\mathcal L)\in\mathcal W .
\]
The candidate hidden-edge set is \(\mathcal C\subseteq\{\{i,j\}:i<j\}\), disjoint from \(\mathcal L\). A feasible true graph \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\) contains all edges in \(\mathcal L\), may contain hidden edges from \(\mathcal C\), and satisfies degree caps \(K_i\).

The same \(G\) induces two hidden exposures,
\[
R_i^D(G,D)=\one\{\exists j:\{i,j\}\in G\setminus\mathcal L,\ D_j=1\}\in\{0,1\},
\qquad
R_i^Z(G,Z)=\one\{\exists j:\{i,j\}\in G\setminus\mathcal L,\ Z_j=1\}\in\{0,1\}.
\]
Take-up is generated by a latent table \(D_i(z,w,r)\in\{0,1\}\), where \(z\) is own encouragement, \(w\) is the observed instrumental label, and \(r\) is the hidden instrumental exposure. Potential outcomes are \(Y_i(d,s,r_D)\in[0,1]\), where \(d\) is own take-up, \(s\) is the observed treatment label, and \(r_D\) is the hidden treatment exposure.

For each \((w,r)\in\mathcal W\times\{0,1\}\), define the exposure-indexed complier indicator
\[
C_i(w,r)=\one\{D_i(1,w,r)=1,\ D_i(0,w,r)=0\}.
\]
For fixed analyst labels \((s,w)\), the direct complier effect and spillover complier effect are linear functionals of the same latent array:
\[
\theta_{\mathrm{dir}}^{c}(s,w;G)
=
\frac{\sum_i \sum_{r_D,r_Z} \omega_{i,s,w,r_D,r_Z}(G)\,C_i(w,r_Z)\,
\{Y_i(1,s,r_D)-Y_i(0,s,r_D)\}}
{\sum_i \sum_{r_Z} \eta_{i,w,r_Z}(G)\,C_i(w,r_Z)},
\]
\[
\theta_{\mathrm{spill}}^{c}(d,s_1,s_0,w;G)
=
\frac{\sum_i \sum_{r_D,r_Z} \omega'_{i,d,s_1,s_0,w,r_D,r_Z}(G)\,C_i(w,r_Z)\,
\{Y_i(d,s_1,r_D)-Y_i(d,s_0,r_D)\}}
{\sum_i \sum_{r_Z} \eta_{i,w,r_Z}(G)\,C_i(w,r_Z)}.
\]
Here \(\omega,\omega',\eta\) are design-induced weights computed from \(\pi\), \(\varphi\), \(\psi\), and \(G\). The family \(\theta^{c}_{\mathcal F}(s,w)\) collects these direct and spillover functionals for a locked finite list \(\mathcal F\).

The observable law is
\[
P_{I,Z,D,S,W,Y;\,\pi,\varphi,\psi,\mathcal L},
\]
with \(I\) a uniformly sampled unit. The identified set \(\Theta^{c}_{\mathcal F}(P)\) contains all values of \(\theta^{c}_{\mathcal F}(s,w)\) generated by latent arrays \((G,D_i(\cdot),Y_i(\cdot))\) consistent with the observed conditional moments
\[
m_{i,z,d,s,w}(P)=\E_P(Y_I\mid I=i,Z_i=z,D_i=d,S_i=s,W_i=w),
\]
the observed take-up probabilities
\[
t_{i,z,w}(P)=\Pr_P(D_i=1\mid I=i,Z_i=z,W_i=w),
\]
and the maintained restrictions below. The bounding functionals are
\[
\underline\theta^{c}_{\mathcal F}(P)=\inf \Theta^{c}_{\mathcal F}(P),
\qquad
\overline\theta^{c}_{\mathcal F}(P)=\sup \Theta^{c}_{\mathcal F}(P).
\]

\begin{quote}\small
This is a partial-identification anchor, not a panel pool-mode. The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
  \text{bounding functional})\\
=
(\texttt{pid\_network\_iv\_exposure},\texttt{v3},
  P_{I,Z,D,S,W,Y;\,\pi,\varphi,\psi,\mathcal L},\
  \theta^{c}_{\mathcal F}(s,w),\
  \mathcal R_{\mathrm{shared\ completion+IV\ monotonicity}},\
  [\underline\theta^{c}_{\mathcal F}(P),\overline\theta^{c}_{\mathcal F}(P)]) .
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population, \(Z=(Z_1,\ldots,Z_n)\in\{0,1\}^n\) is the randomized encouragement vector drawn from a known design \(\pi\), \(D=(D_1,\ldots,D_n)\in\{0,1\}^n\) is realized treatment take-up, \(\mathcal L\) is the observed local graph, \(\varphi_i(D,\mathcal L)=S_i\) is the researcher-specified treatment-exposure mapping, and \(\psi_i(Z,\mathcal L)=W_i\) is the researcher-specified instrumental-exposure mapping. The true hidden graph is an undirected completion \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\), shared by both exposure channels. It induces hidden treatment exposure \(R_i^D(G,D)\in\{0,1\}\) and hidden instrument exposure \(R_i^Z(G,Z)\in\{0,1\}\). The target \(\theta^{c}_{\mathcal F}(s,w)\) is the family of complier direct and spillover effects at analyst labels \((s,w)\), where compliance is defined from the latent take-up table \(D_i(z_i,w,r)\) under own encouragement \(z_i\), observed instrumental label \(w\), and hidden instrumental exposure \(r\). The restrictions \(\mathcal R_{\mathrm{shared\ completion+IV\ monotonicity}}\) are finite support, bounded outcomes, consistency, one shared graph completion, exposure sufficiency for outcomes through \((D_i,S_i,R_i^D)\), exposure sufficiency for take-up through \((Z_i,W_i,R_i^Z)\), exclusion of \(Z\) from \(Y\) conditional on realized treatment exposures, and own-instrument monotonicity \(D_i(1,w,r)\ge D_i(0,w,r)\). The bounding functional is the sharp finite projection of one joint completion-principal-strata feasibility set, not a product of separate treatment-exposure, instrument-exposure, and compliance relaxations.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite randomized encouragement design]\label{ass:finite-design}
The population has \(n<\infty\) units. The support of \(Z\) under \(\pi\), the observed local graph \(\mathcal L\), the candidate hidden-edge set \(\mathcal C\), the degree caps \(K_i\), and the analyst mappings \(\varphi_i,\psi_i\) are finite and known.
\end{assumption}

\begin{assumption}[One shared hidden completion]\label{ass:shared-completion}
There exists one undirected graph \(G\in\mathfrak G(\mathcal L,\mathcal C,K)\) that determines both \(R_i^D(G,D)\) and \(R_i^Z(G,Z)\) for all units and all realizations. Hidden-edge choices are not channel-specific nuisance variables.
\end{assumption}

\begin{assumption}[Exposure sufficiency and exclusion]\label{ass:exposure-exclusion}
Observed outcomes satisfy \(Y_i=Y_i(D_i,S_i,R_i^D(G,D))\). Conditional on \((D_i,S_i,R_i^D(G,D))\), encouragement affects \(Y_i\) only through take-up and exposure labels. Take-up satisfies \(D_i=D_i(Z_i,W_i,R_i^Z(G,Z))\).
\end{assumption}

\begin{assumption}[Own-instrument monotonicity]\label{ass:monotonicity}
For every unit \(i\), observed instrumental label \(w\), and hidden instrumental exposure \(r\), \(D_i(1,w,r)\ge D_i(0,w,r)\).
\end{assumption}

\begin{assumption}[Bounded latent response surfaces]\label{ass:bounded}
For every unit \(i\), \(0\le Y_i(d,s,r_D)\le 1\) for all \((d,s,r_D)\), and \(D_i(z,w,r)\in\{0,1\}\) for all \((z,w,r)\).
\end{assumption}

\begin{assumption}[Observed moment matching]\label{ass:moment-matching}
A feasible latent structure \((G,D_i(\cdot),Y_i(\cdot))\) must reproduce the observed take-up moments \(t_{i,z,w}(P)\) and outcome moments \(m_{i,z,d,s,w}(P)\) for every cell with positive probability.
\end{assumption}

\begin{assumption}[Target-cell positivity]\label{ass:positivity}
Every analyst cell \((s,w)\) used in \(\mathcal F\) has positive design probability under both \(Z_i=0\) and \(Z_i=1\), and the denominator \(\sum_i\sum_{r_Z}\eta_{i,w,r_Z}(G)C_i(w,r_Z)\) is positive for each feasible latent structure used in \(\Theta^{c}_{\mathcal F}(P)\).
\end{assumption}

\begin{assumption}[Product relaxation comparator]\label{ass:product-relaxation}
The comparator set \(\Theta^{c}_{\mathrm{prod}}(P)\) keeps Assumptions~\ref{ass:finite-design}, \ref{ass:bounded}, \ref{ass:moment-matching}, and \ref{ass:positivity}, but replaces Assumptions~\ref{ass:shared-completion}--\ref{ass:monotonicity} by three independent nuisance layers: unitwise treatment-exposure kernels \(Q_i^D\), unitwise instrumental-exposure kernels \(Q_i^Z\), and unitwise monotone take-up tables \(\widetilde D_i(z,w,r)\). No single graph \(G\) is required to generate these objects jointly.
\end{assumption}

\begin{assumption}[Parent corner]\label{ass:parent-corner}
For the reduction to the parent, \(D_i=Z_i\) almost surely, \(W_i\) is correctly specified by \(\psi_i(Z,\mathcal L)\), and the direct-effect target in \(\mathcal F\) is evaluated at a fixed instrumental label \(w\) that carries no additional variation.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite sharp completion-principal-strata projection]\label{thm:joint-polytope}
Under Assumptions~\ref{ass:finite-design}--\ref{ass:positivity}, there exists a finite polytope
\[
\mathcal P_{\mathrm{jc}}(P)
\subseteq
\{0,1\}^{|\mathcal C|}\times
\{0,1\}^{4n|\mathcal W|}\times
[0,1]^{2n|\mathcal S|}
\]
in the hidden-edge variables, monotone take-up tables, and bounded outcome surfaces such that
\[
\Theta^{c}_{\mathcal F}(P)

=
\left\{
\theta^{c}_{\mathcal F}(s,w;G,D(\cdot),Y(\cdot)):
(G,D(\cdot),Y(\cdot))\in\mathcal P_{\mathrm{jc}}(P)
\right\}.
\]
Consequently, each endpoint \(\underline\theta^{c}_{\mathcal F}(P)\) and \(\overline\theta^{c}_{\mathcal F}(P)\) is obtained by optimizing a linear-fractional functional over a finite union of linear programs, or equivalently a single Charnes-Cooper transformed linear program after conditioning on each feasible hidden-edge vector.
\end{theorem}
The proof route is routine finite-dimensional algebra once the latent table is fixed: enumerate monotone take-up rows, impose the observed moment equations, and project the resulting compact feasible set.

\begin{conjecture}[Conjecture 1: dual product relaxation is strictly nonsharp]\label{conj:strict-gap}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite-design}--\ref{ass:positivity} and with \(\Theta^{c}_{\mathrm{prod}}(P)\) defined by Assumption~\ref{ass:product-relaxation}, there exists an open set of finite encouraged-network experiments such that
\[
\Theta^{c}_{\mathcal F}(P)\subsetneq \Theta^{c}_{\mathrm{prod}}(P).
\]
The strict gap occurs because one hidden edge changes both the instrumental exposure entering the compliance table and the treatment exposure entering the outcome table, so a cellwise feasible triple \((Q_i^D,Q_i^Z,\widetilde D_i)\) need not be realizable by any single \(G\).
\end{conjecture}

\begin{conjecture}[Conjecture 2: one polytope jointly identifies the complier family]\label{conj:joint-family}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite-design}--\ref{ass:positivity}, the same polytope \(\mathcal P_{\mathrm{jc}}(P)\) sharp-identifies the vector
\[
\Bigl(
\theta_{\mathrm{dir}}^{c}(s,w),
\theta_{\mathrm{spill}}^{c}(d,s_1,s_0,w),
\lambda\,\theta_{\mathrm{dir}}^{c}(s,w)+(1-\lambda)\theta_{\mathrm{spill}}^{c}(d,s_1,s_0,w)
\Bigr)
\]
for every fixed \(\lambda\in[0,1]\), and there exists an open set of observable laws for which the coordinatewise stitched interval
\[
[\underline\theta_{\mathrm{dir}}^{c}(P),\overline\theta_{\mathrm{dir}}^{c}(P)]
\times
[\underline\theta_{\mathrm{spill}}^{c}(P),\overline\theta_{\mathrm{spill}}^{c}(P)]
\]
strictly contains the true joint identified region.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Reduction to the parent]\label{cor:parent}
Under Assumptions~\ref{ass:finite-design}--\ref{ass:positivity} and Assumption~\ref{ass:parent-corner}, \(\mathcal P_{\mathrm{jc}}(P)\) collapses to the parent shared-completion feasible set of \texttt{pid\_network\_exposure/v1}, and the direct complier effect equals the parent's ADE target:
\[
\Theta^{c}_{\mathcal F}(P)=\Theta_{\mathrm{parent}}(P).
\]
\end{corollary}
Under \(D_i=Z_i\), the latent take-up table has one admissible row and \(R_i^Z(G,Z)\) becomes a nuisance label that no longer changes compliance status. The only remaining latent object is the shared completion governing treatment exposure, so the finite program is exactly the parent's graph-completion program.

\begin{corollary}[Known-mapping IV corner]\label{cor:known-mapping}
Under Assumptions~\ref{ass:finite-design}--\ref{ass:positivity}, if \(G\) is known and \((\varphi,\psi)\) are correctly specified, then \(\Theta^{c}_{\mathcal F}(P)\) reduces to the finite principal-strata identified set induced by the observed design weights and the monotone take-up table.
\end{corollary}
Once \(G\) is fixed, all hidden-exposure weights become observable design functionals. The only remaining ambiguity is the standard monotone principal-strata mixture.

\begin{example}[Exhibit 9.1: four-unit hub witness for the focal polytope]\label{ex:hub}
Take units \(1,2,3,4\), observed graph \(\mathcal L=\emptyset\), candidate hidden edges \(\mathcal C=\{\{1,4\},\{2,4\}\}\), and caps \(K_1=K_2=K_3=1\), \(K_4=1\). Let \(\psi_i(Z,\mathcal L)=0\) and \(\varphi_i(D,\mathcal L)=s\) for all target cells, so all analyst labels are constant and only hidden exposure matters. Let the design support assign \(Z_4=1\), \(Z_3=0\), and randomize \((Z_1,Z_2)\) independently with positive probability on each pair. For leaves \(i\in\{1,2\}\), set
\[
D_i(1,0,0)=1,\quad D_i(0,0,0)=0,\quad
D_i(1,0,1)=D_i(0,0,1)=0,
\]
so \(C_i(0,0)=1\) and \(C_i(0,1)=0\). Let \(Y_i(1,s,0)-Y_i(0,s,0)=1\) and \(Y_i(1,s,1)-Y_i(0,s,1)=0\), with outcomes for units \(3,4\) normalized to zero.

The internal-consistency check is immediate: monotonicity holds coordinatewise, every displayed take-up value is binary, no denominator is zero because each leaf is a complier when \(r_Z=0\), and the edge system is feasible because \(K_4=1\) allows exactly the three hidden-edge vectors \((0,0)\), \((1,0)\), and \((0,1)\). In the product relaxation, both leaves can be assigned the favorable hidden instrument state \(r_Z=0\) in the direct-effect numerator, so the upper endpoint equals \(1\). Under one shared completion, at most one leaf can avoid the hub-generated hidden instrument exposure when \(Z_4=1\), so the sharp joint upper endpoint is \(1/2\). Thus the worked object \(\mathcal P_{\mathrm{jc}}(P)\) produces a numerically distinct bound from the product relaxation, and the difference is not a normalization artifact because both endpoints are computed on the same target scale.
\end{example}

\section{Proof-sketch route}
Theorem~\ref{thm:joint-polytope} follows the chain
\[
\text{headline}
\leftarrow
\text{unfold }\theta^{c}_{\mathcal F}
\leftarrow
\text{substitute Assumptions~\ref{ass:shared-completion}--\ref{ass:moment-matching}}
\leftarrow
\text{enumerate monotone take-up rows}
\leftarrow
\text{encode shared-edge incidence constraints for }R^D,R^Z
\leftarrow
\text{linearize the fractional target by Charnes--Cooper}
\leftarrow
\text{compact-polytope attainment}.
\]
For Theorem~\ref{thm:joint-polytope}, the substantive non-definitional steps are \(k=4\): finite monotone-table enumeration, simultaneous treatment/instrument exposure incidence encoding, linear-fractional reduction, and endpoint-attainment on the projected feasible set. Conjecture~\ref{conj:strict-gap} should reduce to the four-unit witness in Exhibit~\ref{ex:hub} plus an openness argument showing that the strict endpoint gap persists under small perturbations of the observed moments; this adds a fifth substantive step, namely promotion from one worked instance to an open class. Conjecture~\ref{conj:joint-family} should then follow by projecting the same feasible set onto a vector of linear functionals and comparing the joint image with the rectangle formed by separate endpoint optimizations.

\section{Honest scope flags}
The sharp finite projection theorem is routine conditional on the precise choice of observed moments in Section~6, and I regard it as theorem-level. The two flagship statements are conjectural: the strict-gap claim requires a fully checked open-set witness in the IV setting, and the joint-family statement requires a careful projection argument to rule out accidental rectangularity. I deliberately withdrew a stronger claim that the joint polytope admits a simple universal list of matching or cover inequalities; the parent reviews already showed that this overstates what the polyhedral side can currently support. The most delicate modeling choice is the exposure-indexed monotonicity convention \(D_i(1,w,r)\ge D_i(0,w,r)\): it is stronger than allowing defiers only on some hidden-exposure states, and a later revision may need a sensitivity version rather than a hard monotonicity restriction.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial upgrade draft from \texttt{pid\_network\_exposure/v1} to dual exposure-misspecification with IV noncompliance via one joint completion-principal-strata polytope; prior verdict: none.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}
\bibitem[Aronow and Samii(2017)]{AronowSamii2017}
Aronow, P. M. and Samii, C. (2017).
Estimating average causal effects under general interference, with application to a social network experiment.
\emph{The Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem[Acerenza, Martinez-Iriarte, Sanchez-Becerra, and Spini(2025)]{acerenza_martinez_iriarte_sanchez_becerra_spini_2025_household_bounds}
Acerenza, S., Martinez-Iriarte, J., Sanchez-Becerra, A., and Spini, P. E. (2025).
Bounds for within-household encouragement designs with interference.
arXiv:2503.14314.

\bibitem[Hoshino and Yanagi(2024)]{hoshino_yanagi_2024_noncompliance_unknown_interference}
Hoshino, T. and Yanagi, T. (2024).
Causal inference with noncompliance and unknown interference.
\emph{Journal of the American Statistical Association} 119(548), 2869--2880.

\bibitem[Imai, Jiang, and Malani(2021)]{imai_jiang_malani_2021_interference_noncompliance}
Imai, K., Jiang, Z., and Malani, A. (2021).
Causal inference with interference and noncompliance in two-stage randomized experiments.
\emph{Journal of the American Statistical Association} 116(534), 632--644.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Nibbering and Oosterveen(2025)]{nibbering_oosterveen_2025_iv_interference_policy}
Nibbering, D. and Oosterveen, M. (2025).
Policy-relevant causal effect estimation using instrumental variables with interference.
arXiv:2509.12538.

\bibitem[S\"avje(2024)]{savje_2024_misspecified_exposure_mappings}
S\"avje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions and assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem[Schr\"oder, Oprescu, Feuerriegel, and Kallus(2026)]{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid}
Schr\"oder, M., Oprescu, M., Feuerriegel, S., and Kallus, N. (2026).
Causal inference on networks under misspecified exposure mappings: A partial identification framework.
arXiv:2602.03459.

\bibitem[Vazquez-Bare(2023)]{vazquez_bare_2023_iv_spillovers}
Vazquez-Bare, G. (2023).
Causal spillover effects using instrumental variables.
\emph{Journal of the American Statistical Association} 118(543), 1911--1922.
\end{thebibliography}

\end{document}
