\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\calT}{\mathcal{T}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\plim}{\operatorname*{plim}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_network\_iv\_exposure} / \texttt{v3}%
  \\ \large\textit{Sharp finite-network complier direct and spillover bounds under jointly misspecified treatment and instrument exposure maps}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

% --- BEGIN CONTENT ---

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode. The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
\text{bounding functional})\\
=
(\texttt{pid\_network\_iv\_exposure},\texttt{v3},
P_{I,Z,D,S,T,Y;\,\pi,\mathcal L_Y,\mathcal L_Z},\
(\theta_{\mathrm{CD}}(s,t),\theta_{\mathrm{CS}}(s,t)),\
\mathcal R_{\mathrm{shared\ dual\ completion+IV\ compliance}},\
\Theta_I(P)\subset\mathbb R^2).
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population, \(Z=(Z_1,\ldots,Z_n)\in\{0,1\}^n\) is the randomized encouragement vector drawn from a known design \(\pi\), \(D=(D_1,\ldots,D_n)\in\{0,1\}^n\) is the realized take-up vector, \(\mathcal L_Y\) and \(\mathcal L_Z\) are locally observed graphs used to build the observed treatment-exposure map \(S_i=s_i^Y(D,\mathcal L_Y)\) and the observed instrumental-exposure map \(T_i=t_i^Z(Z,\mathcal L_Z)\), and \(Y_i\in[0,1]\) is the observed outcome. The restrictions \(\mathcal R_{\mathrm{shared\ dual\ completion+IV\ compliance}}\) are finite support, bounded outcomes, exclusion of \(Z\) from \(Y\) conditional on \((D_i,S_i,R_i^Y)\), exposure sufficiency for take-up through \((Z_i,T_i,R_i^Z)\), exposure sufficiency for outcomes through \((D_i,S_i,R_i^Y)\), one shared outcome-completion \(G_Y\in\mathfrak G_Y(\mathcal L_Y,\mathcal C_Y,K^Y)\), one shared instrument-completion \(G_Z\in\mathfrak G_Z(\mathcal L_Z,\mathcal C_Z,K^Z)\), and finite principal-response tables \(D_i(z,t,u)\in\{0,1\}\). The target \((\theta_{\mathrm{CD}}(s,t),\theta_{\mathrm{CS}}(s,t))\) is the pair of complier direct and hidden-spillover effects in the observed cell \((S_i,T_i)=(s,t)\), normalized by the cell-specific complier mass \(\kappa_{s,t}(G_Y,G_Z,h)\). The bounding functional is the sharp finite identified set obtained by enumerating feasible completion pairs and principal-stratum assignments and solving the resulting bounded linear programs in the latent outcome means.

\begin{abstract}
The parent banked result \texttt{pid\_network\_exposure/v1} gives sharp finite-network bounds for average direct effects when the treatment exposure map may be misspecified through one shared hidden completion. This proposal adds an IV layer: treatment may be taken up imperfectly, the instrumental exposure map may also be misspecified, and the target becomes the pair of complier direct and spillover effects in a finite network. The routine theorem is an exact finite identified-set representation obtained by enumerating shared outcome and instrument completions together with finite principal take-up tables, then optimizing bounded latent outcome means subject to the observed take-up and outcome moments. The flagship conjecture is a computable policy-transport frontier \(\mathcal T_g(P)\): a deterministic encouragement policy is transportable from cell-level complier effects if and only if its induced complier-cell share vector is constant over the feasible latent structures consistent with \(P\). A second conjecture gives a four-unit witness in which the parent bound survives as a corner case but policy transport fails once both exposure maps and compliance types are latent. Resolving these claims would connect exposure-mapping robustness to IV noncompliance without abandoning sharp finite-network partial identification.
\end{abstract}

\section{Introduction}
The question is whether a finite-network IV analysis can remain sharp when both the treatment exposure map used for outcomes and the instrumental exposure map used for take-up are only locally observed. The headline claim is that the right object is still finite and computable, but only after one keeps a shared completion for each map and a joint principal-response assignment for take-up.

Relative to the parent \texttt{pid\_network\_exposure/v1}, the delta is a strict generalization along the declared axis. The parent bound fixes treatment exposure misspecification with no IV layer; this draft adds noncompliance, a second misspecified exposure map, and a policy-transport question suggested by \citet{hoshino_yanagi_2024_noncompliance_unknown_interference} and \citet{nibbering_oosterveen_2025_iv_interference_policy}. Relative to the published literature, \citet{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid} give sharp bounds without IV compliance strata, while \citet{hoshino_yanagi_2024_noncompliance_unknown_interference} identify and estimate network-IV parameters without finite sharp bounds over shared dual completions. The kernel lives in partial identification, with network interference and IV noncompliance supplying the frontier structure.

One concrete consumer is policy evaluation under interference. \citet{auerbach_auerbach_tabord_meehan_2024_exposure_policy_relevance} warn that exposure effects need not answer policy questions, and \citet{nibbering_oosterveen_2025_iv_interference_policy} show how policy-relevant IV effects emerge under interference. If the transport frontier is characterized sharply, a reader can tell whether a proposed encouragement policy is already pinned down by cell-level complier effects or whether latent exposure completions still matter.

\begin{itemize}[leftmargin=*]
\item \textbf{Theorem 1:} The sharp identified set for \((\theta_{\mathrm{CD}}(s,t),\theta_{\mathrm{CS}}(s,t))\) is a finite union of LP projections indexed by shared completion pairs and principal-response assignments. Gap: \texttt{pid\_network\_exposure/v1} has one treatment-exposure completion and no IV layer; \citet{hoshino_yanagi_2024_noncompliance_unknown_interference} and \citet{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid} do not combine sharp finite dual-completion bounds with latent compliance. Consumer: \citet{imbens_manski_2004_ci_partial_id}.
\item \textbf{Conjecture 1:} For a deterministic encouragement policy \(g\), the policy-relevant complier effect is transportable from cell-level effects if and only if the feasible complier-cell share set \(\mathcal T_g(P)\) is a singleton; otherwise the policy effect is only sharply bounded. Gap: \citet{auerbach_auerbach_tabord_meehan_2024_exposure_policy_relevance} gives the warning, and \citet{nibbering_oosterveen_2025_iv_interference_policy} gives policy-relevant IV bounds, but neither isolates a computable finite-network transport frontier under dual exposure misspecification. Consumer: \citet{nibbering_oosterveen_2025_iv_interference_policy}.
\item \textbf{Conjecture 2:} A four-unit finite witness yields the same observable law and the same parent-style cellwise complier bounds under two feasible latent structures, yet the policy share vector \(\tau_g\) differs and the policy effect does not transport. Gap: \texttt{pid\_network\_exposure/v1} has shared-completion nonsharpness without IV policy transport; \citet{vazquez_bare_2023_iv_spillovers} and \citet{imai_jiang_malani_2021_interference_noncompliance} do not provide this dual-misspecification witness. Consumer: finite design diagnostics for network encouragement studies.
\end{itemize}

\section{Related work}
\citet{manski1990} is the bounded-outcome partial-identification anchor: once hidden exposure states and compliance types are latent, the target is an identified set rather than a point. \citet{hudgens_halloran_2008} and \citet{aronow_samii_2017} define direct and spillover effects under interference and give the known-exposure benchmark [reused from parent]. \citet{savje_2024_misspecified_exposure_mappings} separates exposure mappings as estimands from exposure mappings as identifying assumptions [reused from parent], which is the conceptual reason to let both \(S_i\) and \(T_i\) be misspecified here.

\citet{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid} are the closest treatment-exposure comparator [reused from parent]: they derive sharp misspecified-exposure bounds and orthogonal estimators when the network is known, but they do not introduce IV compliance strata or instrumental exposure misspecification. \citet{weinstein_nevo_2026} treat misspecified network interference structure [reused from parent], but their object is bias and robust estimation across candidate networks rather than a sharp finite-network complier identified set. \citet{gao_harshaw_savje_wang_2026} show that broad exposure-mapping specification tests are impossible [reused from parent], which strengthens the case for reporting explicit partial-ID regions rather than point claims.

\citet{hoshino_yanagi_2024_noncompliance_unknown_interference} are the closest IV-network comparator. They introduce instrumental exposure mappings and identify complier-type effects under unknown interference, while allowing misspecification of the exposure mapping, but their contribution is identification and IPW estimation rather than finite sharp bounds over shared dual completions. \citet{imai_jiang_malani_2021_interference_noncompliance} identify complier direct and spillover effects in two-stage randomized experiments under stratified interference, which supplies the finite-compliance contrast but not the general local-network misspecification problem. \citet{vazquez_bare_2023_iv_spillovers} show that ordinary IV contrasts aggregate several direct and spillover effects across compliance types, which motivates keeping the principal-response layer explicit. \citet{acerenza_martinez_iriarte_sanchez_becerra_spini_2025_household_bounds} derive sharp household encouragement bounds, suggesting a finite witness strategy but not solving the many-peer network case.

\citet{auerbach_auerbach_tabord_meehan_2024_exposure_policy_relevance} argue that exposure effects are not automatically policy useful. \citet{nibbering_oosterveen_2025_iv_interference_policy} define and partially identify policy-relevant IV direct and spillover effects under interference. The present proposal sits exactly between them: it asks when policy relevance is recovered from misspecified-exposure complier cells and when shared completion uncertainty blocks that transport.

\citet{imbens_manski_2004_ci_partial_id} and \citet{chernozhukov_hong_tamer_2007_parameter_sets} are the natural inference anchors once the finite sharp bound exists, although inference is outside the present scope. In the repository, the closest prior art is \texttt{pid\_network\_exposure/v1}, whose headline result is sharp joint-completion ADE bounds under misspecified treatment exposures, and the PartialID sections of \texttt{doc/API.md}, which list network, IV, and sensitivity families but do not contain this dual-completion network-IV kernel.

\section{Formal setup}
There are \(n<\infty\) units. The encouragement vector is \(Z\in\{0,1\}^n\), drawn from a known randomized design \(\pi\). The realized take-up vector is \(D\in\{0,1\}^n\). The analyst observes two local graphs, \(\mathcal L_Y\) for the outcome exposure map and \(\mathcal L_Z\) for the instrumental exposure map, together with candidate hidden-edge sets \(\mathcal C_Y,\mathcal C_Z\) and degree caps \(K^Y_i,K^Z_i\). Feasible completions are
\[
G_Y\in\mathfrak G_Y(\mathcal L_Y,\mathcal C_Y,K^Y),\qquad
G_Z\in\mathfrak G_Z(\mathcal L_Z,\mathcal C_Z,K^Z),
\]
where each class is finite.

The observed exposure labels are
\[
S_i=s_i^Y(D,\mathcal L_Y)\in\mathcal S,\qquad
T_i=t_i^Z(Z,\mathcal L_Z)\in\mathcal T.
\]
The hidden exposure indicators generated by the completions are
\[
R_i^Y(G_Y,D)=\one\{\exists j:\{i,j\}\in G_Y\setminus\mathcal L_Y,\ D_j=1\}\in\{0,1\},
\]
\[
R_i^Z(G_Z,Z)=\one\{\exists j:\{i,j\}\in G_Z\setminus\mathcal L_Z,\ Z_j=1\}\in\{0,1\}.
\]
Potential take-up is \(D_i(z,t,u)\in\{0,1\}\), where \(z\) is own encouragement, \(t\) is the observed instrument exposure, and \(u\) is the hidden instrument exposure. Potential outcomes are \(Y_i(d,s,r)\in[0,1]\), where \(d\) is own treatment, \(s\) is the observed treatment exposure, and \(r\) is the hidden treatment exposure.

For each unit \(i\), let \(h_i\) denote its full take-up response table
\[
h_i=\{D_i(z,t,u):(z,t,u)\in\{0,1\}\times\mathcal T\times\{0,1\}\}.
\]
Because \(\mathcal T\) is finite, the set \(\calH_i\) of possible tables is finite. A principal-response assignment is \(h=(h_1,\ldots,h_n)\in\calH=\prod_i\calH_i\). For a feasible pair \(g=(G_Y,G_Z)\) and assignment \(h\), define the cell-specific complier indicator
\[
C_i^{h}(t,u)=\one\{D_i(1,t,u)=1,\ D_i(0,t,u)=0\}.
\]

The observable law is
\[
P=P_{I,Z,D,S,T,Y;\,\pi,\mathcal L_Y,\mathcal L_Z},
\]
where \(I\) is uniformly sampled from \(\{1,\ldots,n\}\). The observed take-up and outcome moments used by the finite program are
\[
\delta_{i,z,s,t}(P)=\E_P[D_I\mid I=i,Z_i=z,S_i=s,T_i=t],
\qquad
m_{i,z,s,t}(P)=\E_P[Y_I\mid I=i,Z_i=z,S_i=s,T_i=t],
\]
for cells with positive design probability.

For a feasible latent structure \((g,h)\), define the normalization
\[
\kappa_{s,t}(g,h)
=\frac1n\sum_{i=1}^n
\Pr_\pi\!\big(S_i=s,\ T_i=t,\ C_i^{h}(T_i,R_i^Z(G_Z,Z))=1\big).
\]
This is the cell-specific complier mass. The direct-effect weights are
\[
\omega^{\mathrm{CD}}_{i,s,t,r,u}(g,h)
=\Pr_\pi\!\big(S_i=s,\ T_i=t,\ R_i^Y(G_Y,D)=r,\ R_i^Z(G_Z,Z)=u,\ C_i^{h}(T_i,u)=1\big),
\]
and the spillover-effect weights are
\[
\omega^{\mathrm{CS}}_{i,s,t,d,u}(g,h)
=\Pr_\pi\!\big(S_i=s,\ T_i=t,\ D_i=d,\ R_i^Z(G_Z,Z)=u,\ C_i^{h}(T_i,u)=1\big).
\]
Whenever \(\kappa_{s,t}(g,h)>0\), define
\[
\theta_{\mathrm{CD}}(s,t;g,h,Y)
=
\frac{1}{n\,\kappa_{s,t}(g,h)}
\sum_{i=1}^n\sum_{r,u\in\{0,1\}}
\omega^{\mathrm{CD}}_{i,s,t,r,u}(g,h)\{Y_i(1,s,r)-Y_i(0,s,r)\},
\]
\[
\theta_{\mathrm{CS}}(s,t;g,h,Y)
=
\frac{1}{n\,\kappa_{s,t}(g,h)}
\sum_{i=1}^n\sum_{d,u\in\{0,1\}}
\omega^{\mathrm{CS}}_{i,s,t,d,u}(g,h)\{Y_i(d,s,1)-Y_i(d,s,0)\}.
\]
The sharp identified set \(\Theta_I(P)\) is the set of all pairs \((\theta_{\mathrm{CD}},\theta_{\mathrm{CS}})\) produced by feasible triples \((g,h,Y)\) that satisfy the assumptions below and reproduce the observed moments \(\delta(P)\) and \(m(P)\).

The parent-style cellwise comparator \(\Theta_I^{\mathrm{cell}}(P)\) is obtained by replacing Assumption~\ref{ass:dual-completion} with unit-specific hidden exposure kernels for \(R_i^Y\) and \(R_i^Z\) that are each feasible in isolation, while keeping the same bounded outcome arrays, principal-response tables, and observed-moment equalities. It forgets the requirement that one shared \(G_Y\) and one shared \(G_Z\) must simultaneously rationalize all units.

\begin{quote}\small
This is a partial-identification anchor, not a panel pool-mode. The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
\text{bounding functional})\\
=
(\texttt{pid\_network\_iv\_exposure},\texttt{v3},
P_{I,Z,D,S,T,Y;\,\pi,\mathcal L_Y,\mathcal L_Z},\
(\theta_{\mathrm{CD}}(s,t),\theta_{\mathrm{CS}}(s,t)),\
\mathcal R_{\mathrm{shared\ dual\ completion+IV\ compliance}},\
\Theta_I(P)\subset\mathbb R^2).
\end{gathered}
\]
Here \(I\) indexes a uniformly sampled unit from a finite population, \(Z=(Z_1,\ldots,Z_n)\in\{0,1\}^n\) is the randomized encouragement vector drawn from a known design \(\pi\), \(D=(D_1,\ldots,D_n)\in\{0,1\}^n\) is the realized take-up vector, \(\mathcal L_Y\) and \(\mathcal L_Z\) are locally observed graphs used to build the observed treatment-exposure map \(S_i=s_i^Y(D,\mathcal L_Y)\) and the observed instrumental-exposure map \(T_i=t_i^Z(Z,\mathcal L_Z)\), and \(Y_i\in[0,1]\) is the observed outcome. The restrictions \(\mathcal R_{\mathrm{shared\ dual\ completion+IV\ compliance}}\) are finite support, bounded outcomes, exclusion of \(Z\) from \(Y\) conditional on \((D_i,S_i,R_i^Y)\), exposure sufficiency for take-up through \((Z_i,T_i,R_i^Z)\), exposure sufficiency for outcomes through \((D_i,S_i,R_i^Y)\), one shared outcome-completion \(G_Y\in\mathfrak G_Y(\mathcal L_Y,\mathcal C_Y,K^Y)\), one shared instrument-completion \(G_Z\in\mathfrak G_Z(\mathcal L_Z,\mathcal C_Z,K^Z)\), and finite principal-response tables \(D_i(z,t,u)\in\{0,1\}\). The target \((\theta_{\mathrm{CD}}(s,t),\theta_{\mathrm{CS}}(s,t))\) is the pair of complier direct and hidden-spillover effects in the observed cell \((S_i,T_i)=(s,t)\), normalized by the cell-specific complier mass \(\kappa_{s,t}(G_Y,G_Z,h)\). The bounding functional is the sharp finite identified set obtained by enumerating feasible completion pairs and principal-stratum assignments and solving the resulting bounded linear programs in the latent outcome means.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite randomized network-IV experiment]\label{ass:finite}
The population, design support, exposure ranges \(\mathcal S,\mathcal T\), local graphs \(\mathcal L_Y,\mathcal L_Z\), candidate hidden-edge sets \(\mathcal C_Y,\mathcal C_Z\), and degree caps \(K^Y,K^Z\) are finite and known.
\end{assumption}

\begin{assumption}[Shared dual completions]\label{ass:dual-completion}
There exists one \(G_Y\in\mathfrak G_Y(\mathcal L_Y,\mathcal C_Y,K^Y)\) generating \(R_i^Y(G_Y,D)\) for all units and all realized treatment vectors, and one \(G_Z\in\mathfrak G_Z(\mathcal L_Z,\mathcal C_Z,K^Z)\) generating \(R_i^Z(G_Z,Z)\) for all units and all encouragement vectors. Hidden edges are not unit-specific nuisance variables.
\end{assumption}

\begin{assumption}[Finite principal-response tables]\label{ass:principal}
Each unit has a deterministic take-up response table \(h_i\in\calH_i\), where \(D_i=D_i(Z_i,T_i,R_i^Z(G_Z,Z))\). The assignment \(h=(h_1,\ldots,h_n)\) is fixed across all assignments in the design support.
\end{assumption}

\begin{assumption}[Outcome exposure sufficiency and exclusion]\label{ass:outcome}
For every unit \(i\), the observed outcome satisfies
\[
Y_i=Y_i(D_i,S_i,R_i^Y(G_Y,D)).
\]
Conditional on \((D_i,S_i,R_i^Y(G_Y,D))\), the outcome does not depend directly on \(Z\) or on \(R_i^Z(G_Z,Z)\).
\end{assumption}

\begin{assumption}[Bounded outcomes]\label{ass:bounded}
For every \(i\), \(d\in\{0,1\}\), \(s\in\mathcal S\), and \(r\in\{0,1\}\), \(0\le Y_i(d,s,r)\le 1\).
\end{assumption}

\begin{assumption}[Cell positivity]\label{ass:positivity}
For the target cell \((s,t)\), every unit entering \(\kappa_{s,t}(g,h)\) has positive design probability of the events used in the displayed conditioning cells for \(\delta_{i,z,s,t}(P)\) and \(m_{i,z,s,t}(P)\).
\end{assumption}

\begin{assumption}[Observed moment matching]\label{ass:matching}
A feasible triple \((g,h,Y)\) must reproduce the observed take-up and outcome moments:
\[
\E[D_I\mid I=i,Z_i=z,S_i=s,T_i=t]=\delta_{i,z,s,t}(P),
\]
\[
\E[Y_I\mid I=i,Z_i=z,S_i=s,T_i=t]=m_{i,z,s,t}(P),
\]
for every observed cell with positive probability under \(\pi\).
\end{assumption}

\begin{assumption}[Perfect-compliance corner]\label{ass:parent-corner}
For the parent reduction only, \(D_i(z,t,u)=z\) for every \(i,z,t,u\), \(G_Z=\mathcal L_Z\), and \(R_i^Z(G_Z,Z)=0\). This assumption is used only in Corollary~\ref{cor:parent}.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite sharp identified set by completion and principal-table enumeration]\label{thm:finite-sharp}
Under Assumptions~\ref{ass:finite}--\ref{ass:matching}, the sharp identified set is
\[
\Theta_I(P)
=
\bigcup_{(g,h)\in\mathfrak G_Y\times\mathfrak G_Z\times\calH:\ \kappa_{s,t}(g,h)>0}
\left\{
\big(\theta_{\mathrm{CD}}(s,t;g,h,Y),\theta_{\mathrm{CS}}(s,t;g,h,Y)\big):
Y\in\calF(g,h;P)
\right\},
\]
where \(\calF(g,h;P)\) is the polytope of all bounded outcome arrays \(Y_i(d,s,r)\in[0,1]\) satisfying Assumptions~\ref{ass:outcome}, \ref{ass:bounded}, and \ref{ass:matching} for the fixed latent structure \((g,h)\). Equivalently, every support function of \(\Theta_I(P)\) is obtained by finite enumeration of \((g,h)\) followed by linear programming over \(Y\).
\end{theorem}
For fixed \((g,h)\), the observed-moment equations are linear in the bounded latent outcome array \(Y\), so \(\calF(g,h;P)\) is a compact polytope and the support function is attained. The novelty is not this theorem by itself, but that the dual-completion IV problem remains finite once the latent compliance layer is kept explicit rather than absorbed into a misspecified exposure kernel.

\begin{conjecture}[Conjecture 1: computable policy-transport frontier]\label{conj:frontier}
(NOT YET PROVED.) Fix a deterministic encouragement policy \(g^\star\) that maps public baseline information into an encouragement vector \(Z^{g^\star}\). For each feasible latent structure \((g,h)\), let
\[
\tau_{g^\star}(g,h)
=
\left(
\frac1n\sum_{i=1}^n
\Pr\!\big(S_i^{g^\star}=s',\ T_i^{g^\star}=t',\ C_i^{h}(T_i^{g^\star},R_i^{Z,g^\star})=1\big)
\right)_{(s',t')\in\mathcal S\times\mathcal T},
\]
where \(S_i^{g^\star}=s_i^Y(D^{g^\star},\mathcal L_Y)\), \(T_i^{g^\star}=t_i^Z(Z^{g^\star},\mathcal L_Z)\), and \(R_i^{Z,g^\star}=R_i^Z(G_Z,Z^{g^\star})\). Define the policy-transport frontier
\[
\mathcal T_{g^\star}(P)
=
\{\tau_{g^\star}(g,h):(g,h,Y)\text{ satisfies Assumptions~\ref{ass:finite}--\ref{ass:matching} and matches }P\}.
\]
Then \(\mathcal T_{g^\star}(P)\) is a finite polytope computable by projection of the same feasible set used in Theorem~\ref{thm:finite-sharp}, and the policy-relevant complier effect under \(g^\star\) is point-transportable from the cell-level effects \(\{(\theta_{\mathrm{CD}}(s',t'),\theta_{\mathrm{CS}}(s',t'))\}_{(s',t')}\) if and only if \(\mathcal T_{g^\star}(P)\) is a singleton. There exists an open class of finite experiments for which \(\mathcal T_{g^\star}(P)\) is not a singleton even though the parent-style cellwise identified regions coincide across the feasible latent structures.
\end{conjecture}

\begin{conjecture}[Conjecture 2: four-unit nontransport witness]\label{conj:witness}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite}--\ref{ass:matching}, there exists a four-unit design with empty observed local graphs, hidden candidate edges \(\{1,4\}\) and \(\{2,4\}\) in both completion classes, and degree caps \(K^Y_4=K^Z_4=1\) such that:
\[
P^{A}=P^{B},\qquad
\Theta_I^{\mathrm{cell}}(P^{A})=\Theta_I^{\mathrm{cell}}(P^{B}),
\qquad
\tau_{g^\star}(g^{A},h^{A})\neq \tau_{g^\star}(g^{B},h^{B}),
\]
for some deterministic policy \(g^\star\), where \((g^{A},h^{A})\) and \((g^{B},h^{B})\) are two feasible latent structures consistent with the same observable law. Consequently, the policy-relevant complier effect under \(g^\star\) is only partially identified even though the observed-design cellwise complier bounds coincide.
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Reduction to the parent kernel]\label{cor:parent}
Under Assumptions~\ref{ass:finite}--\ref{ass:matching} and the perfect-compliance corner Assumption~\ref{ass:parent-corner}, \(\theta_{\mathrm{CD}}(s,t)\) reduces to the parent direct-effect target \(\theta_{\mathrm{ADE}}(s)\), \(\theta_{\mathrm{CS}}(s,t)\) drops out, and Theorem~\ref{thm:finite-sharp} reduces to the sharp joint-completion bound in \texttt{pid\_network\_exposure/v1}.
\end{corollary}
Under Assumption~\ref{ass:parent-corner}, \(D_i=z\), \(T_i\) and \(R_i^Z\) no longer affect take-up, and the cell-specific complier mass satisfies \(\kappa_{s,t}(g,h)=\Pr_\pi(S_i=s)\). The direct-effect formula becomes the parent average direct effect because the only remaining hidden state is the treatment-exposure completion \(G_Y\).

\begin{corollary}[Known-map collapse]\label{cor:known}
If \(\mathcal C_Y=\mathcal C_Z=\emptyset\) or all hidden-edge degree caps are zero, then \(R_i^Y=R_i^Z=0\) for every unit and assignment, \(\mathcal T_{g^\star}(P)\) is a singleton for every deterministic policy \(g^\star\), and Theorem~\ref{thm:finite-sharp} reduces to a finite principal-strata partial-ID problem without exposure-map misspecification.
\end{corollary}
With no hidden edges, the only latent layer is the principal-response assignment \(h\). The reduction is immediate because all completion uncertainty disappears from the conditioning weights and from the policy share vector.

\paragraph{Exhibit 9.1.}
Take \(n=3\), \(\mathcal L_Y=\mathcal L_Z=\emptyset\), one candidate hidden edge \(\{1,3\}\) in both completion classes, degree caps \(K_1^Y=K_3^Y=K_1^Z=K_3^Z=1\), and design \(\pi\) uniform on assignments with exactly one encouraged unit. Let the observed exposure cells be singletons, \(\mathcal S=\mathcal T=\{0\}\), and let the observed moments be
\[
\delta_{1,1,0,0}(P)=\delta_{1,0,0,0}(P)=\tfrac12,\qquad
\delta_{2,1,0,0}(P)=1,\ \delta_{2,0,0,0}(P)=1,\qquad
\delta_{3,1,0,0}(P)=\delta_{3,0,0,0}(P)=0,
\]
\[
m_{1,1,0,0}(P)=\tfrac12,\ m_{1,0,0,0}(P)=0,\qquad
m_{2,1,0,0}(P)=m_{2,0,0,0}(P)=\tfrac14,\qquad
m_{3,1,0,0}(P)=m_{3,0,0,0}(P)=0.
\]
There are two feasible instrument-completion states: the empty graph and the graph containing \(\{1,3\}\). Enumerating these states and the finite tables \(h_i\) shows that the feasible policy share vector under the deterministic policy \(g^\star\) that encourages unit \(3\) only is
\[
\mathcal T_{g^\star}(P)=\{(1/3),(2/3)\},
\]
because unit \(1\) is a complier under \(g^\star\) only when the hidden edge is absent, while unit \(2\) is always a complier. The exhibit is computed from the observed moments, the candidate hidden-edge set, the degree caps, and the enumerated response tables; it does not assume the policy share vector in advance.

\paragraph{Exhibit 9.2.}
Take \(n=4\), \(\mathcal L_Y=\mathcal L_Z=\emptyset\), candidate hidden edges \(\{1,4\}\) and \(\{2,4\}\) in both completion classes, and caps \(K_4^Y=K_4^Z=1\), all other caps at least \(1\). Let \(\pi\) be uniform on assignments with exactly one encouraged unit. Set \(\mathcal S=\mathcal T=\{0\}\) and impose the observable take-up and outcome tables
\[
\delta_{1,1,0,0}(P)=\delta_{2,1,0,0}(P)=\tfrac12,\qquad
\delta_{1,0,0,0}(P)=\delta_{2,0,0,0}(P)=0,\qquad
\delta_{3,z,0,0}(P)=\delta_{4,z,0,0}(P)=0,
\]
\[
m_{1,1,0,0}(P)=m_{2,1,0,0}(P)=\tfrac12,\qquad
m_{1,0,0,0}(P)=m_{2,0,0,0}(P)=0,\qquad
m_{3,z,0,0}(P)=m_{4,z,0,0}(P)=0.
\]
Now compare two feasible latent structures. In structure \(A\), the unique hidden edge is \(\{1,4\}\), unit \(1\) is a complier only when \(R_1^Z=0\), and the outcome surface satisfies \(Y_1(1,0,0)=1,\ Y_1(1,0,1)=0\), while unit \(2\) has \(Y_2(1,0,0)=Y_2(1,0,1)=1/2\). In structure \(B\), swap the role of units \(1\) and \(2\): the unique hidden edge is \(\{2,4\}\), unit \(2\) loses compliance when \(R_2^Z=1\), and the outcome surfaces are swapped in the same way. Both structures generate the same observable moments and the same parent-style cellwise bound under the experimental design, but under the deterministic policy \(g^\star\) that encourages unit \(4\) only,
\[
\tau_{g^\star}(g^{A},h^{A})=\tfrac14,\qquad
\tau_{g^\star}(g^{B},h^{B})=\tfrac12,
\]
because the encouraged hub activates the hidden IV edge in different complier locations. The worked table gives a concrete non-corner witness for Conjecture~\ref{conj:witness}; Stage 0 should verify the exact equalities by full completion enumeration.

\section{Proof-sketch route}
Theorem~\ref{thm:finite-sharp} reduces by the chain
\[
\text{headline}
\leftarrow
\text{finite completion classes}
\leftarrow
\text{finite principal-response tables}
\leftarrow
\text{linear observed-moment equations for fixed }(g,h)
\leftarrow
\text{compact bounded-outcome polytope}
\leftarrow
\text{support-function attainment}.
\]
The substantive steps are: first, write the take-up law under a fixed \((G_Z,h)\) as a deterministic map from \(Z\) into \(D\), which makes the observed take-up moments linear restrictions on the latent response table; second, condition on the induced treatment vector \(D\) and the fixed outcome completion \(G_Y\) to obtain linear outcome-moment equations in \(Y_i(d,s,r)\); third, show that the target pair \((\theta_{\mathrm{CD}},\theta_{\mathrm{CS}})\) is linear in \(Y\) once \((g,h)\) is fixed, so every support function is an LP after finite enumeration. Conjecture~\ref{conj:frontier} then asks for a projection theorem: the same feasible set, augmented by the deterministic policy map \(g^\star\), should project onto the finite polytope \(\mathcal T_{g^\star}(P)\). Conjecture~\ref{conj:witness} asks for exact enumeration on the four-unit instance in Exhibit 9.2 and a proof that the two latent structures agree on the observable law while disagreeing on the policy share vector.

\section{Honest scope flags}
Theorem~\ref{thm:finite-sharp} is routine only after finite principal-response tables are kept explicit; it is not claimed as a closed-form LP over observables alone. Conjecture~\ref{conj:frontier} is the flagship object, and its status is open because the projection characterization of \(\mathcal T_{g^\star}(P)\) has not been proved. Conjecture~\ref{conj:witness} supplies a concrete candidate witness, but the exact equality \(P^A=P^B\) still requires a full Stage 0 enumeration check. No inference, asymptotic efficiency, or orthogonal score claim is made here. The proposal was narrowed relative to earlier drafts by replacing the underspecified \(K_g(P)\in\R^2\) object with the explicit cell-indexed frontier \(\mathcal T_{g^\star}(P)\).

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial dual-exposure network-IV draft; prior verdict: none.
\item v2 (revise) -- added the policy-transport angle and aligned the upgrade with the parent shared-completion kernel; prior verdict: REVISE.
\item v3 (revise) -- replaced the undefined transport object by the explicit frontier \(\mathcal T_{g^\star}(P)\), fixed the cell normalization \(\kappa_{s,t}(g,h)\), changed the main theorem to finite enumeration plus LP, added Exhibits 9.1 and 9.2, and corrected the Vazquez-Bare metadata; prior verdict: REVISE.
\end{itemize}

\section*{Bibliography}
\begin{thebibliography}{99}

\bibitem[Acerenza et al.(2025)]{acerenza_martinez_iriarte_sanchez_becerra_spini_2025_household_bounds}
Acerenza, S., Martinez-Iriarte, M. P., Sanchez-Becerra, M., and Spini, P. (2025).
Sharp bounds for causal effects in two-person encouragement designs with spillovers.
\emph{arXiv preprint arXiv:2503.14314}.

\bibitem[Aronow and Samii(2017)]{aronow_samii_2017}
Aronow, P. M. and Samii, C. (2017).
Estimating average causal effects under general interference, with application to a social network experiment.
\emph{The Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem[Auerbach, Auerbach, and Tabord-Meehan(2024)]{auerbach_auerbach_tabord_meehan_2024_exposure_policy_relevance}
Auerbach, E., Auerbach, S., and Tabord-Meehan, M. (2024).
Exposure effects are not automatically useful for policymaking.
\emph{arXiv preprint arXiv:2401.06264}.

\bibitem[Chernozhukov, Hong, and Tamer(2007)]{chernozhukov_hong_tamer_2007_parameter_sets}
Chernozhukov, V., Hong, H., and Tamer, E. (2007).
Estimation and confidence regions for parameter sets in econometric models.
\emph{Econometrica} 75(5), 1243--1284.

\bibitem[Gao et al.(2026)]{gao_harshaw_savje_wang_2026}
Gao, C., Harshaw, C., S\"{a}vje, F., and Wang, Y. (2026).
On the impossibility of specification testing of interference models based on exposure mappings.
\emph{arXiv preprint arXiv:2605.09726}.

\bibitem[Hoshino and Yanagi(2024)]{hoshino_yanagi_2024_noncompliance_unknown_interference}
Hoshino, T. and Yanagi, T. (2024).
Causal inference with noncompliance and unknown interference.
\emph{Journal of the American Statistical Association} 119(548), 2869--2880.

\bibitem[Hudgens and Halloran(2008)]{hudgens_halloran_2008}
Hudgens, M. G. and Halloran, M. E. (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.

\bibitem[Imai, Jiang, and Malani(2021)]{imai_jiang_malani_2021_interference_noncompliance}
Imai, K., Jiang, Z., and Malani, A. (2021).
Causal inference with interference and noncompliance in two-stage randomized experiments.
\emph{Journal of the American Statistical Association} 116(534), 632--644.

\bibitem[Imbens and Manski(2004)]{imbens_manski_2004_ci_partial_id}
Imbens, G. W. and Manski, C. F. (2004).
Confidence intervals for partially identified parameters.
\emph{Econometrica} 72(6), 1845--1857.

\bibitem[Manski(1990)]{manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Nibbering and Oosterveen(2025)]{nibbering_oosterveen_2025_iv_interference_policy}
Nibbering, D. and Oosterveen, M. (2025).
Policy-relevant direct and spillover effects under interference with instrumental variables.
\emph{arXiv preprint arXiv:2509.12538}.

\bibitem[S\"{a}vje(2024)]{savje_2024_misspecified_exposure_mappings}
S\"{a}vje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions and assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem[Schr\"{o}der et al.(2026)]{schroder_oprescu_feuerriegel_kallus_2026_networks_partialid}
Schr\"{o}der, M., Oprescu, M., Feuerriegel, S., and Kallus, N. (2026).
Causal inference on networks under misspecified exposure mappings: A partial identification framework.
\emph{arXiv preprint arXiv:2602.03459}.

\bibitem[Vazquez-Bare(2023)]{vazquez_bare_2023_iv_spillovers}
Vazquez-Bare, G. (2023).
Causal spillover effects using instrumental variables.
\emph{Journal of the American Statistical Association} 118(543), 1911--1922.

\bibitem[Weinstein and Nevo(2026)]{weinstein_nevo_2026}
Weinstein, B. and Nevo, D. (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.

\end{thebibliography}

\end{document}
