\documentclass[11pt]{article}

\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\Pr}{\mathbb{P}}
\newcommand{\one}{\mathbf{1}}
\newcommand{\transpose}{\mathsf{T}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calR}{\mathcal{R}}
\newcommand{\calK}{\mathcal{K}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calA}{\mathcal{A}}
\newcommand{\PsiObs}{\Psi}
\newcommand{\R}{\mathbb{R}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{assumption}{Assumption}
\newtheorem{example}{Example}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\title{ThmSmith Stage -1 proposal: \texttt{pid\_network\_iv\_exposure} / \texttt{v3}%
  \\ \large\textit{Sharp finite-network complier bounds under dual exposure-map misspecification}}
\author{thmsmith Stage -1 proposer}
\date{\today}

\begin{document}
\maketitle

\paragraph{Locked parameters.}
This is a partial-identification anchor, not a panel pool-mode. The locked tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
\text{bounding functional}) \\
=
(\texttt{pid\_network\_iv\_exposure},\texttt{v3},
\PsiObs(P),\ \theta_{\mathrm{C}}(s,t),\
\mathcal{R}_{\mathrm{shared\ completion+monotone\ takeup+dual\ maps}},\
[\underline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs),
\overline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs)]) .
\end{gathered}
\]
Here \(\PsiObs(P)\) is the observable unit-level summary
\[
\PsiObs(P)=
\{p_{i,z,d,s,t},m_{i,z,d,s,t}: p_{i,z,d,s,t}>0,\ i\le n,\ z,d,s,t\},
\]
where \(p_{i,z,d,s,t}=\Pr(I=i,Z_i=z,D_i=d,S_i=s,T_i=t)\) and
\(m_{i,z,d,s,t}=\E(Y\mid I=i,Z_i=z,D_i=d,S_i=s,T_i=t)\). The observed
instrument is \(Z\), the observed take-up is \(D\), the observed treatment
exposure is \(S_i=s_i(D,\mathcal L)\), and the observed instrumental exposure
is \(T_i=t_i(Z,\mathcal L)\). The target
\(\theta_{\mathrm{C}}(s,t)\) is the complier direct effect at treatment
exposure \(s\) and instrumental exposure \(t\), averaging over hidden
treatment-side exposure \(R_i^D(G,D)\), hidden instrument-side exposure
\(R_i^Z(G,Z)\), and monotone take-up types induced by one shared graph
completion \(G\). The identifying restrictions are finite support, bounded
outcomes, shared graph completion, exclusion of instrument-side hidden exposure
from outcomes conditional on treatment-side exposure, monotone own take-up with
respect to the own instrument given total instrument exposure, and exact
matching of \(\PsiObs(P)\). The bounding functional is the sharp finite LP
projection over shared completion variables, monotone response-type masses, and
latent mean outcomes. It is not the product of independently chosen unitwise
dual-exposure kernels.

\begin{abstract}
This draft upgrades the banked parent \texttt{pid\_network\_exposure/v1} from
one misspecified treatment exposure map to IV noncompliance with misspecified
treatment and instrumental exposure maps. The routine part is a sharpness
theorem for the summary \(\PsiObs(P)\): the complier direct-effect identified
set is a finite union of linear-fractional LP projections, one for each shared
graph completion, over monotone take-up types and bounded latent mean outcomes. The open
kernel is whether the corresponding product relaxation that chooses each unit's
dual exposure errors in isolation is strictly nonsharp once one graph must
jointly govern both take-up spillovers and outcome spillovers. A positive
answer would bridge the exposure-mapping robustness literature
\citep{Savje2024,SchroderOprescuFeuerriegelKallus2026} with the network-IV
noncompliance literature \citep{HoshinoYanagi2024,ImaiJiangMalani2021}. It
would also produce a computable finite-network bound and a worked witness that
pin down exactly where cellwise robustness loses sharpness.
\end{abstract}

\section{Introduction}
The question is whether complier direct and spillover effects remain sharply
partially identified when both the treatment exposure map used in outcomes and
the instrumental exposure map used in take-up may be wrong. The headline claim
is that, after fixing a finite hidden-edge completion class, the correct object
is a finite union of shared-completion LPs for a coarsened observable summary
\(\PsiObs(P)\), not an independent product of unitwise misspecification
neighborhoods.

Relative to the parent proposal \texttt{pid\_network\_exposure/v1}, the upgrade
axis is a strict generalization: the parent handled one misspecified treatment
exposure map for an ADE, while the present draft adds IV noncompliance, a
second misspecified exposure map on the instrument side, and a complier target.
The closest published comparators are \citet[§3.2.2]{HoshinoYanagi2024}, who
identify local average direct effects with instrumental exposure mappings, and
\citet[Abstract]{SchroderOprescuFeuerriegelKallus2026}, who derive sharp bounds
under misspecified treatment exposure mappings without compliance types. The
gap is the absence of a sharp finite-network bound that lets both maps be
wrong while forcing one completion to govern both hidden channels. The kernel
lives in partial identification, with a bridge to network IV.

The downstream consumer is the policy-relevant IV-with-interference frontier.
\citet[Abstract]{NibberingOosterveen2025} partially identify policy-relevant IV
effects with interference, and \citet[Abstract]{VazquezBare2023} show that
ordinary IV contrasts aggregate multiple direct and spillover effects once
compliance types interact with spillovers. A sharp finite-network complier
interval gives a benchmark object before policy aggregation. A reader would use
this result differently by reporting a bound generated by one feasible network
completion rather than a cellwise interval that ignores shared hidden edges.

\begin{itemize}[leftmargin=*]
\item Theorem 1: the identified set for \(\theta_{\mathrm{C}}(s,t)\) is the
finite union of shared-completion LP projections indexed by \(\PsiObs(P)\). Gap:
\texttt{pid\_network\_exposure/v1} had no IV noncompliance, while
\citet{HoshinoYanagi2024} and \citet{SchroderOprescuFeuerriegelKallus2026} do
not combine dual misspecification with finite-network sharpness. Consumer:
\citet{NibberingOosterveen2025}.
\item Conjecture 1: the product comparator
\(\Theta_{\mathrm{C}}^{\mathrm{prod}}(\PsiObs)\) is strictly nonsharp on an
open class. Gap:
\citet{SchroderOprescuFeuerriegelKallus2026} allow independent exposure errors,
whereas one hidden edge here constrains take-up and outcome channels together.
Consumer: \citet{Savje2024}.
\item Conjecture 2: a four-unit hub-cap witness and its separating inequality
compute a positive compatibility gap from primitives. Gap:
\citet{ImaiJiangMalani2021} identify under stratified interference and
\citet{AcerenzaMartinezIriarteSanchezBecerraSpini2025} bound two-person
encouragement designs, but neither produces a finite-network dual-map witness.
Consumer: \citet{NibberingOosterveen2025}, where policy-relevant IV bounds need
an admissibility screen for finite-network encouragement paths.
\end{itemize}

\section{Related work}
\citet[reused from parent]{Manski1990} supplies the bounded-outcome
partial-identification logic: the present object is a finite identified set and
its endpoint interval, not a point-identified estimand. \citet[reused from
parent]{HudgensHalloran2008} and \citet[reused from parent]{AronowSamii2017}
fix the direct/spillover terminology and the exposure-mapping benchmark under a
known mapping. \citet[reused from parent]{Savje2024} is the key
misspecification anchor. Its relevance is the distinction between exposure
mappings as estimand definitions and as structural assumptions, which creates
room for explicit robustness objects rather than all-or-nothing correctness.

\citet{HoshinoYanagi2024} is the closest IV comparator. The paper introduces
instrumental exposure mappings and studies identification and IPW estimation of
complier direct and spillover parameters under unknown interference, including
possible exposure-map misspecification, but it does not derive sharp finite
bounds from one shared hidden completion. \citet{ImaiJiangMalani2021} identify
complier direct and spillover effects in two-stage randomized experiments under
stratified interference and noncompliance, which is the point-identified corner
against which the present draft measures the finite-network loss from
misspecification.

\citet{SchroderOprescuFeuerriegelKallus2026} is the closest partial-ID
comparator on the misspecified-exposure axis. Their contribution is sharp
treatment and spillover bounds under misspecified treatment exposure mappings,
plus orthogonal estimation, but the network is taken as known and there is no
latent compliance geometry. \citet{WeinsteinNevo2026} is the closest
network-misspecification comparator. The paper separates network
misspecification from exposure-map misspecification and develops robust
estimation across candidate networks, but it does not compute sharp complier
bounds over a local completion class.

\citet{VazquezBare2023} clarifies why the upgrade is nontrivial: standard IV
rescaling can aggregate direct and spillover effects across compliance types
once spillovers enter both treatment take-up and outcomes. \citet{AcerenzaMartinezIriarteSanchezBecerraSpini2025}
show that sharp bounds are attainable in a two-person encouragement design with
interference, which motivates but does not solve the many-peer finite-network
case. \citet{NibberingOosterveen2025} is the new frontier anchor for this
revision. It studies policy-relevant IV effects with interference under mild
assumptions, so the present draft supplies a sharper finite-network benchmark
before one moves to policy aggregation.

In-repository prior art is limited and distinct. The relevant catalogue summary
in \texttt{CausalSmith/doc/API.md} records PartialID as a live cluster for IV,
sensitivity, and bounds statements, but not a network-IV theorem matching this
kernel. The closest catalogue artifact is the banked parent
\texttt{pid\_network\_exposure/v1}, which derives sharp ADE bounds under one
misspecified treatment exposure map using shared completion logic. The present
draft reuses that shared-completion geometry and adds dual exposure maps,
monotone take-up types, and a complier target. No other catalogue entry
coincides with that upgrade.

\section{Formal setup}
There are \(n<\infty\) units indexed by \(i\in N=\{1,\ldots,n\}\). The
instrument assignment vector is \(Z\in\{0,1\}^n\), drawn from a known design
\(\pi_Z\) with finite support. The observed take-up vector is
\(D\in\{0,1\}^n\). The analyst observes a local undirected graph
\(\mathcal L\), a finite hidden-edge candidate set
\(\mathcal C\subseteq\{\{i,j\}:i<j\}\) disjoint from \(\mathcal L\), and degree
caps \(K_i\). A feasible completion \(G\in\calG(\mathcal L,\mathcal C,K)\)
contains all edges in \(\mathcal L\), selects binary hidden-edge variables
\(x_e\in\{0,1\}\) for \(e\in\mathcal C\), and satisfies
\[
\sum_{e\in\mathcal C} B_{ie}x_e\le K_i,\qquad
B_{ie}=\one\{i\in e\}.
\]

The observed treatment exposure and observed instrumental exposure are
\[
S_i=s_i(D,\mathcal L)\in\mathcal S,\qquad
T_i=t_i(Z,\mathcal L)\in\mathcal T.
\]
For a completion \(G\), the hidden treatment-side exposure and hidden
instrument-side exposure are
\[
R_i^D(G,D)=
\one\{\exists j:\{i,j\}\in G\setminus\mathcal L,\ D_j=1\},
\qquad
R_i^Z(G,Z)=
\one\{\exists j:\{i,j\}\in G\setminus\mathcal L,\ Z_j=1\}.
\]
The total instrument exposure argument entering own take-up is
\(U_i(G,Z)=T_i\vee R_i^Z(G,Z)\in\{0,1\}\).

Let \(\Gamma^{\mathrm{mon}}\) be the finite class of isotone response rules
\(\gamma:\{0,1\}^2\to\{0,1\}\) satisfying
\(\gamma(1,u)\ge \gamma(0,u)\) for each \(u\in\{0,1\}\). Unit \(i\) has latent
type \(\gamma_i\in\Gamma^{\mathrm{mon}}\) with masses
\(\lambda_{i\gamma}\ge0\), \(\sum_{\gamma}\lambda_{i\gamma}=1\), and take-up
equation
\[
D_i=\gamma_i(Z_i,U_i(G,Z)).
\]
Throughout, the latent-type law is the product law induced by the unit-specific
marginals \(\lambda_i=(\lambda_{i\gamma})_{\gamma\in\Gamma^{\mathrm{mon}}}\):
conditional on \((G,Z)\), the vector \((\gamma_1,\ldots,\gamma_n)\) is drawn
independently with probabilities \(\Pr(\gamma_i=\gamma)=\lambda_{i\gamma}\).
All probabilities below involving \((D,R^D,R^Z,\gamma_i)\) are therefore
computed under the joint law \(\Pr^{G,\lambda}_{\pi_Z}=\pi_Z\otimes
\bigotimes_i\lambda_i\).
For a fixed \(u\in\{0,1\}\), define the complier subset
\[
\Gamma_{\mathrm{C}}(u)=
\{\gamma\in\Gamma^{\mathrm{mon}}:\gamma(1,u)-\gamma(0,u)=1\}.
\]

Outcomes satisfy exclusion of instrument-side hidden exposure after treatment
exposure is fixed. The latent mean surface is
\[
\mu_i(d,s,r_D)\in[0,1],\qquad
Y_i(d,s,r_D)=\mu_i(d,s,r_D),
\]
so \(R_i^Z\) affects outcomes only through its effect on \(D\) and hence on the
treatment-side state \((d,s,r_D)\).

For a unit \(i\) and an observed cell \((z,d,s,t)\), define the design- and
type-induced latent table
\[
\omega^G_{i,z,d,s,t,r_D,r_Z,\gamma}(\lambda)
 =
\Pr_{\pi_Z,\lambda}\!\left(
\begin{array}{l}
Z_i=z,\ D_i=d,\ S_i=s,\ T_i=t,\\
R_i^D(G,D)=r_D,\ R_i^Z(G,Z)=r_Z,\ \gamma_i=\gamma
\end{array}
\Bigm|\, I=i\right).
\]
The observable summary used throughout this proposal is
\[
\PsiObs(P)=\{p_{i,z,d,s,t},m_{i,z,d,s,t}\},
\]
with
\[
p_{i,z,d,s,t}=\Pr(I=i,Z_i=z,D_i=d,S_i=s,T_i=t),
\qquad
m_{i,z,d,s,t}=\E(Y\mid I=i,Z_i=z,D_i=d,S_i=s,T_i=t).
\]
The matching equations are
\[
p_{i,z,d,s,t}
=
\sum_{r_D,r_Z,\gamma}
\omega^G_{i,z,d,s,t,r_D,r_Z,\gamma}(\lambda),
\]
and
\[
p_{i,z,d,s,t}m_{i,z,d,s,t}
=
\sum_{r_D,r_Z,\gamma}
\omega^G_{i,z,d,s,t,r_D,r_Z,\gamma}(\lambda)\,
\mu_i(d,s,r_D).
\]

For a target cell \((s,t)\), define the control-arm reference weights
\[
q^G_{i,s,t,r_D,r_Z,\gamma}(\lambda)
=
\Pr^{G,\lambda}_{\pi_Z}
\bigl(
R_i^D(G,D)=r_D,\ R_i^Z(G,Z)=r_Z,\ \gamma_i=\gamma
\mid I=i,Z_i=0,S_i=s,T_i=t
\bigr),
\]
the complier numerator
\[
N_{\mathrm{C}}(s,t;G,\lambda,\mu)
=
\sum_i\sum_{r_D,r_Z}\sum_{\gamma\in\Gamma_{\mathrm{C}}(t\vee r_Z)}
q^G_{i,s,t,r_D,r_Z,\gamma}(\lambda)
\{\mu_i(1,s,r_D)-\mu_i(0,s,r_D)\},
\]
the complier denominator
\[
W_{\mathrm{C}}(s,t;G,\lambda)
=
\sum_i\sum_{r_D,r_Z}\sum_{\gamma\in\Gamma_{\mathrm{C}}(t\vee r_Z)}
q^G_{i,s,t,r_D,r_Z,\gamma}(\lambda),
\]
and the complier direct effect
\[
\theta_{\mathrm{C}}(s,t;G,\lambda,\mu)
=
\frac{N_{\mathrm{C}}(s,t;G,\lambda,\mu)}
{W_{\mathrm{C}}(s,t;G,\lambda)}.
\]
The identified set
\(\Theta_{\mathrm{C}}^{\mathrm{joint}}(\PsiObs)\) is the set of all such values
over feasible \((G,\lambda,\mu)\) satisfying the matching equations above.

The product comparator is explicit. For each unit \(i\), let \(\calA_i\) be the
finite set of isolated-unit atoms generated by feasible star completions around
\(i\) that respect \(K_i\) but ignore cross-unit sharing of hidden edges. Each
atom \(a\in\calA_i\) carries finite tables
\[
Q^{Z,a}_{i}(r_Z\mid z,t),\qquad
Q^{D,a}_{i}(d\mid z,t,r_Z),\qquad
\Lambda^{a}_{i}(\gamma),\qquad
Q^{R,a}_{i}(r_D\mid d,s).
\]
The comparator chooses weights \(\eta_{ia}\ge0\), \(\sum_a\eta_{ia}=1\), and
aggregates
\[
Q^Z_i=\sum_a\eta_{ia}Q^{Z,a}_{i},\quad
Q^D_i=\sum_a\eta_{ia}Q^{D,a}_{i},\quad
\Lambda_i=\sum_a\eta_{ia}\Lambda^{a}_{i},\quad
Q^R_i=\sum_a\eta_{ia}Q^{R,a}_{i}.
\]
Its observable matching constraints are
\[
p_{i,z,d,s,t}
=
\sum_{r_D,r_Z,\gamma}
\bar{\omega}_{i,z,d,s,t,r_D,r_Z,\gamma},
\]
\[
p_{i,z,d,s,t}m_{i,z,d,s,t}
=
\sum_{r_D,r_Z,\gamma}
\bar{\omega}_{i,z,d,s,t,r_D,r_Z,\gamma}\,
\mu_i(d,s,r_D),
\]
with factorization
\[
\bar{\omega}_{i,z,d,s,t,r_D,r_Z,\gamma}
=
p_{i,z,s,t}\,
Q^Z_i(r_Z\mid z,t)\,
Q^D_i(d\mid z,t,r_Z)\,
Q^R_i(r_D\mid d,s)\,
\Lambda_i(\gamma).
\]
The product identified set \(\Theta_{\mathrm{C}}^{\mathrm{prod}}(\PsiObs)\) is
the projection of this finite system onto the same target functional
\(\theta_{\mathrm{C}}(s,t)\).

\begin{quote}\small
This is a partial-identification anchor, not a panel pool-mode. The locked
tuple is
\[
\begin{gathered}
(\texttt{qid},\texttt{specialization},P,\theta,\text{identifying restrictions},
\text{bounding functional}) \\
=
(\texttt{pid\_network\_iv\_exposure},\texttt{v3},
\PsiObs(P),\ \theta_{\mathrm{C}}(s,t),\
\mathcal{R}_{\mathrm{shared\ completion+monotone\ takeup+dual\ maps}},\
[\underline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs),
\overline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs)]) .
\end{gathered}
\]
Here \(\PsiObs(P)\) is the observable unit-level summary
\[
\PsiObs(P)=
\{p_{i,z,d,s,t},m_{i,z,d,s,t}: p_{i,z,d,s,t}>0,\ i\le n,\ z,d,s,t\},
\]
where \(p_{i,z,d,s,t}=\Pr(I=i,Z_i=z,D_i=d,S_i=s,T_i=t)\) and
\(m_{i,z,d,s,t}=\E(Y\mid I=i,Z_i=z,D_i=d,S_i=s,T_i=t)\). The observed
instrument is \(Z\), the observed take-up is \(D\), the observed treatment
exposure is \(S_i=s_i(D,\mathcal L)\), and the observed instrumental exposure
is \(T_i=t_i(Z,\mathcal L)\). The target
\(\theta_{\mathrm{C}}(s,t)\) is the complier direct effect at treatment
exposure \(s\) and instrumental exposure \(t\), averaging over hidden
treatment-side exposure \(R_i^D(G,D)\), hidden instrument-side exposure
\(R_i^Z(G,Z)\), and monotone take-up types induced by one shared graph
completion \(G\). The identifying restrictions are finite support, bounded
outcomes, shared graph completion, exclusion of instrument-side hidden exposure
from outcomes conditional on treatment-side exposure, monotone own take-up with
respect to the own instrument given total instrument exposure, and exact
matching of \(\PsiObs(P)\). The bounding functional is the sharp finite LP
projection over shared completion variables, monotone response-type masses, and
latent mean outcomes. It is not the product of independently chosen unitwise
dual-exposure kernels.
\end{quote}

\section{Assumptions}
\begin{assumption}[Finite randomized network-IV experiment]\label{ass:finite}
The population is finite, \(Z\) is assigned by a known design \(\pi_Z\), the
observed local graph \(\mathcal L\), candidate hidden-edge set \(\mathcal C\),
degree caps \(K_i\), and exposure maps \(s_i,t_i\) are finite and known, and
all conditioning cells used in \(\PsiObs(P)\) have positive probability.
\end{assumption}

\begin{assumption}[Shared completion]\label{ass:shared}
There exists one graph completion \(G\in\calG(\mathcal L,\mathcal C,K)\) that
determines \(R_i^D(G,D)\) and \(R_i^Z(G,Z)\) for all units and all instrument
assignments. Hidden edges are not unit-specific nuisance variables.
\end{assumption}

\begin{assumption}[Monotone take-up types]\label{ass:mono}
For each unit \(i\), own take-up is generated by a latent type
\(\gamma_i\in\Gamma^{\mathrm{mon}}\) through
\(D_i=\gamma_i(Z_i,U_i(G,Z))\), with type masses
\(\lambda_{i\gamma}\ge0\) summing to one.
\end{assumption}

\begin{assumption}[Product latent-type law]\label{ass:product-law}
Conditional on \((G,Z)\), the latent type vector
\((\gamma_1,\ldots,\gamma_n)\) is independent across units with marginals
\(\lambda_i\). Equivalently, every probability defining \(\omega^G\),
\(q^G\), \(N_{\mathrm{C}}\), and \(W_{\mathrm{C}}\) is computed under
\(\Pr^{G,\lambda}_{\pi_Z}=\pi_Z\otimes\bigotimes_i\lambda_i\).
\end{assumption}

\begin{assumption}[Outcome exclusion and boundedness]\label{ass:outcome}
For every unit \(i\), treatment state \(d\), observed treatment exposure \(s\),
and hidden treatment-side exposure \(r_D\), the mean outcome
\(\mu_i(d,s,r_D)\) lies in \([0,1]\). Conditional on \((d,s,r_D)\), the hidden
instrument-side exposure \(r_Z\) has no direct effect on the outcome.
\end{assumption}

\begin{assumption}[Observable-summary matching]\label{ass:matching}
A feasible joint model \((G,\lambda,\mu)\) matches the observed summary
\(\PsiObs(P)\) through the probability and mean equations in Section 6. The
proposal is sharp for \(\PsiObs(P)\), not for an unmodeled richer law.
\end{assumption}

\begin{assumption}[Target positivity]\label{ass:positivity}
For the target cell \((s,t)\), the denominator of
\(\theta_{\mathrm{C}}(s,t;G,\lambda,\mu)\) is strictly positive for every
feasible joint model considered in Section 8.
\end{assumption}

\begin{assumption}[Explicit product comparator]\label{ass:prod}
For each unit \(i\), the product comparator chooses weights
\(\eta_{ia}\) on the finite isolated-unit atom set \(\calA_i\) and uses the
aggregated kernels \(Q_i^Z,Q_i^D,Q_i^R,\Lambda_i\) defined in Section 6. The
factorized latent cell array \(\bar{\omega}\) must satisfy the displayed
probability and mean equations. No shared graph completion links unit \(i\) to
unit \(j\) inside \(\Theta_{\mathrm{C}}^{\mathrm{prod}}(\PsiObs)\).
\end{assumption}

\begin{assumption}[Parent corner]\label{ass:parent-corner}
The parent reduction imposes \(D=Z\) almost surely,
\(T_i=t_i(Z,\mathcal L)=s_i(Z,\mathcal L)\),
\(R_i^Z(G,Z)=R_i^D(G,Z)\), and a degenerate type distribution supported on the
identity rule \(\gamma(z,u)=z\). This assumption is used only in
Corollary~\ref{cor:parent}.
\end{assumption}

\section{Main results}
\begin{theorem}[Theorem 1: finite shared-completion sharpness for \(\PsiObs\)]\label{thm:sharp}
Under Assumptions~\ref{ass:finite}--\ref{ass:positivity}, fix a completion
\(G\in\calG(\mathcal L,\mathcal C,K)\). For that fixed \(G\), the feasible set
of tuples
\[
\{\lambda_{i\gamma}\}_{i,\gamma\in\Gamma^{\mathrm{mon}}},\qquad
\{\mu_i(d,s,r_D)\}_{i,d,s,r_D},\qquad
\{\omega^G_{i,z,d,s,t,r_D,r_Z,\gamma}\},\qquad
N_{\mathrm{C}},W_{\mathrm{C}}
\]
is a polytope cut out by linear constraints: the completion constraints
\(G\in\calG(\mathcal L,\mathcal C,K)\) are already resolved by fixing the
completion, so the remaining simplex constraints on \(\lambda\), box
constraints \(0\le \mu_i(d,s,r_D)\le 1\), exact matching equations for
\(\PsiObs(P)\), and linear definitions of \(N_{\mathrm{C}}\) and
\(W_{\mathrm{C}}\) from Section 6 define a polytope. Hence, for fixed \(G\), the set of feasible
ratios \(N_{\mathrm{C}}/W_{\mathrm{C}}\) is the image of a linear-fractional LP
projection, and its endpoint problems reduce by a Charnes--Cooper transform to
ordinary linear programs because Assumption~\ref{ass:positivity} imposes
\(W_{\mathrm{C}}>0\).

Consequently, the full identified set is the finite union
\[
\Theta_{\mathrm{C}}^{\mathrm{joint}}(\PsiObs)
=
\bigcup_{G\in\calG(\mathcal L,\mathcal C,K)}
\left\{
\frac{N_{\mathrm{C}}}{W_{\mathrm{C}}}:
(G,\lambda,\mu,\omega^G,N_{\mathrm{C}},W_{\mathrm{C}})
\text{ satisfies the fixed-}G\text{ constraints}
\right\},
\]
and therefore
\[
\underline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs)
=
\inf \Theta_{\mathrm{C}}^{\mathrm{joint}}(\PsiObs),\qquad
\overline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs)
=
\sup \Theta_{\mathrm{C}}^{\mathrm{joint}}(\PsiObs)
\]
are obtained by a finite collection of LPs, one for each completion \(G\).
\end{theorem}
The proof route is routine finite-dimensional sharpness. One conditions on a
completion, writes the observable-summary constraints as linear equalities
under the product latent-type law, linearizes the ratio by Charnes--Cooper, and
then takes the finite union over completions.

\begin{conjecture}[Conjecture 1: strict product nonsharpness under dual-map sharing]\label{conj:gap}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite}--\ref{ass:prod}, there is
an open class of finite experiments for which
\[
\Theta_{\mathrm{C}}^{\mathrm{joint}}(\PsiObs)
\subsetneq
\Theta_{\mathrm{C}}^{\mathrm{prod}}(\PsiObs).
\]
The strictness comes from a shared hidden edge entering both \(R_i^Z\) in the
take-up equation and \(R_i^D\) in the outcome equation, so a unitwise feasible
choice of dual kernels need not be jointly realizable by one completion. In
the worked family of Conjecture~\ref{conj:witness}, the upper-endpoint gap
\[
\Delta_{\mathrm{C}}(\PsiObs)
=
\overline{\theta}^{\,\mathrm{prod}}_{\mathrm{C}}(\PsiObs)
-
\overline{\theta}^{\,\mathrm{joint}}_{\mathrm{C}}(\PsiObs)
\]
is strictly positive.
\end{conjecture}

\begin{conjecture}[Conjecture 2: four-unit hub-cap witness and certificate]\label{conj:witness}
(NOT YET PROVED.) Under Assumptions~\ref{ass:finite}--\ref{ass:prod}, there is
a four-unit finite witness family with hidden candidates
\(\{1,4\},\{2,4\},\{3,4\}\), hub cap \(K_4=1\), and target cell
\((s^\star,t^\star)\) such that the product upper endpoint requires all three
focal units \(1,2,3\) to load on the same hub through both
\(R^Z\) and \(R^D\), while every shared completion can satisfy at most one of
those demands. In that family, a valid inequality of the projected
capacitated-incidence polytope separates the product endpoint demand vector
from the shared-completion feasible set, and the resulting separation computes a
strictly positive lower bound on \(\Delta_{\mathrm{C}}(\PsiObs)\).
\end{conjecture}

\section{Sanity-check corollaries}
\begin{corollary}[Parent reduction]\label{cor:parent}
Under Assumptions~\ref{ass:finite}--\ref{ass:positivity} and the parent-corner
Assumption~\ref{ass:parent-corner}, Theorem~\ref{thm:sharp} reduces to the
banked parent \texttt{pid\_network\_exposure/v1}. In particular,
\[
\theta_{\mathrm{C}}(s,t;G,\lambda,\mu)
=
\theta_{\mathrm{ADE}}(s;G,\mu),
\]
and the parent control-arm weights are recovered as
\[
q_{i,s,r}(G)
=
\sum_{r_Z\in\{0,1\}}
q^G_{i,s,s,r,r_Z,\gamma^{\mathrm{id}}}(\lambda),
\]
where \(\gamma^{\mathrm{id}}(z,u)=z\) is the unique type with positive mass.
\end{corollary}
Under Assumption~\ref{ass:parent-corner}, there is no compliance uncertainty,
the two exposure maps coincide, and the hidden instrument channel is merely a
copy of the hidden treatment channel. The denominator in
\(\theta_{\mathrm{C}}(s,t)\) becomes the parent target set, so the upgrade
collapses to the parent theorem.

\begin{corollary}[Known-exposure collapse]\label{cor:known}
If \(\mathcal C=\emptyset\) or \(K_i=0\) for all \(i\), then
\(R_i^D(G,D)=R_i^Z(G,Z)=0\) for every \(i\) and every completion. The
identified set in Theorem~\ref{thm:sharp} collapses to the standard finite
network-IV complier effect with known exposure maps.
\end{corollary}
The collapse is immediate because the hidden-state coordinates disappear from
the matching equations and from the target weights.

\paragraph{Exhibit 9.1 (worked hub-cap witness).}
Take \(n=4\), \(\mathcal L=\emptyset\),
\(\mathcal C=\{\{1,4\},\{2,4\},\{3,4\}\}\), and degree caps
\((K_1,K_2,K_3,K_4)=(1,1,1,1)\). Let \(\pi_Z\) put mass \(1/2\) on
\(Z_4=0\) and \(1/2\) on \(Z_4=1\), independently of
\(Z_1=Z_2=Z_3=0\). The observed maps are \(s_i=t_i\equiv 0\). For each focal
unit \(i\in\{1,2,3\}\), use the monotone gate type
\(\gamma^{g}(0,0)=\gamma^{g}(1,0)=\gamma^{g}(0,1)=0\),
\(\gamma^{g}(1,1)=1\), and the never-taker \(\gamma^{n}\equiv 0\), with
product-comparator masses
\(\Lambda_i(\gamma^{g})=\Lambda_i(\gamma^{n})=1/2\). Let unit \(4\) satisfy
\(D_4=Z_4\). Set focal latent means
\[
\mu_i(1,0,1)=1,\qquad
\mu_i(0,0,1)=0,\qquad
\mu_i(1,0,0)=\mu_i(0,0,0)=0,
\qquad i=1,2,3.
\]
Then the unit-level observable summary generated by one isolated star
completion at focal unit \(i\) is
\[
p_{i,0,0,0,0}=1,\qquad m_{i,0,0,0,0}=0,
\]
and, at the target cell \((s^\star,t^\star)=(0,0)\),
\[
q_{i,0,0,1,1,\gamma^{g}}^{\mathrm{prod}}=1/2,\qquad
q_{i,0,0,r_D,r_Z,\gamma}^{\mathrm{prod}}=0
\text{ otherwise on }\Gamma_{\mathrm C}(1).
\]
Hence each focal unit contributes numerator \(1/2\) and denominator \(1/2\),
so the product endpoint is
\[
\overline{\theta}^{\,\mathrm{prod}}_{\mathrm C}(\PsiObs)=
\frac{3\cdot (1/2)}{3\cdot (1/2)}=1.
\]
Under a shared completion, at most one hub edge can be active because
\[
x_{14}+x_{24}+x_{34}\le K_4=1.
\]
Therefore at most one focal unit can have
\((R_i^Z,R_i^D)=(1,1)\), so every shared-completion feasible point satisfies
\[
N_{\mathrm C}\le 1/2,\qquad W_{\mathrm C}=3/2,
\qquad
\overline{\theta}^{\,\mathrm{joint}}_{\mathrm C}(\PsiObs)\le \frac{1}{3}.
\]
The induced compatibility gap is therefore
\[
\Delta_{\mathrm C}(\PsiObs)\ge 1-\frac13=\frac23.
\]
The separating inequality is exactly the hub-cap inequality
\(x_{14}+x_{24}+x_{34}\le 1\): the product endpoint demand vector
\((1,1,1)\) violates it, while every shared completion satisfies it. This
exhibits the focal object promised in Conjecture~\ref{conj:witness}; what
remains open is to upgrade this worked family into a full sharpness proof for
an open observable neighborhood.

\section{Proof-sketch route}
Theorem~\ref{thm:sharp} reduces through four substantive steps. First, fix a
completion \(G\) and use Assumption~\ref{ass:product-law} to compute the latent
cell array \(\omega^G\) under the product law
\(\Pr^{G,\lambda}_{\pi_Z}\). Second, rewrite the observable summary
\(\PsiObs(P)\) and the numerator-denominator pair
\((N_{\mathrm C},W_{\mathrm C})\) as linear equations in
\((\lambda,\mu,\omega^G)\). Third, apply a Charnes--Cooper transform to convert
the endpoint problems for \(N_{\mathrm C}/W_{\mathrm C}\) into ordinary LPs for
each fixed completion. Fourth, take the finite union over the completion class
\(\calG(\mathcal L,\mathcal C,K)\). Conjecture~\ref{conj:gap} then asks for a
strict comparison between that shared-completion projection and the factorized
comparator in Assumption~\ref{ass:prod}. Conjecture~\ref{conj:witness} should
be attacked by upgrading Exhibit 9.1 from a worked demand calculation to a full
observable-neighborhood sharpness argument and then separating the infeasible
demand vector by a valid inequality of the projected capacitated-incidence
polytope.

\section{Honest scope flags}
Theorem~\ref{thm:sharp} is labelled a theorem because it is a routine finite
union-of-LPs sharpness statement once \(\PsiObs(P)\), the product latent law,
and the latent tables are fixed. The
novel upgrade delta is conjectural and lives in
Conjectures~\ref{conj:gap}--\ref{conj:witness}. The draft does not claim
statistical inference, orthogonal estimation, or policy aggregation. It also
does not claim the smallest possible witness network. What changed in this
revision is the observable convention and the product comparator: the proposal
is now explicitly sharp for \(\PsiObs(P)\), the latent law used to define
\(\omega^G\) is pinned down, and Exhibit 9.1 computes the candidate gap from
Section 6 primitives rather than leaving the witness verbal.

\section{Iteration trail}
\begin{itemize}[leftmargin=*]
\item v1 (cold-start) -- initial draft upgrading the shared-completion network-exposure result to IV noncompliance with dual exposure maps; prior verdict: none.
\item v2 (revise) -- added stronger published comparators and clarified the dual-map complier target; prior verdict: REVISE.
\item v3 (revise) -- added the shared-completion versus product-relaxation comparison and a parent-corner reduction; prior verdict: REVISE.
\item v4 (revise) -- relocked the observable object to \(\PsiObs(P)\), replaced the informal product relaxation with an explicit finite comparator polytope, and made the parent-weight reduction formula explicit; prior verdict: REVISE.
\item v5 (revise) -- pinned down the product latent-type law, rewrote Theorem~\ref{thm:sharp} as a finite union of LPs with linear-fractional endpoint reduction, removed the false containment-to-endpoint equivalence, and replaced Exhibit 9.1 with a numeric hub-cap witness tied to \citet{NibberingOosterveen2025}; prior verdict: REVISE.
\end{itemize}

\section{Bibliography}
\begin{thebibliography}{99}
\bibitem[Acerenza et al.(2025)]{AcerenzaMartinezIriarteSanchezBecerraSpini2025}
Acerenza, S., Martinez-Iriarte, M., Sanchez-Becerra, J., and Spini, N. (2025).
Sharp bounds on direct and spillover effects in two-person encouragement
designs with strategic interaction.
arXiv:2503.14314.

\bibitem[Aronow and Samii(2017)]{AronowSamii2017}
Aronow, P. M. and Samii, C. (2017).
Estimating average causal effects under general interference, with application
to a social network experiment.
\emph{The Annals of Applied Statistics} 11(4), 1912--1947.

\bibitem[Hoshino and Yanagi(2024)]{HoshinoYanagi2024}
Hoshino, T. and Yanagi, T. (2024).
Causal inference with noncompliance and unknown interference.
\emph{Journal of the American Statistical Association} 119(548), 2869--2880.

\bibitem[Hudgens and Halloran(2008)]{HudgensHalloran2008}
Hudgens, M. G. and Halloran, M. E. (2008).
Toward causal inference with interference.
\emph{Journal of the American Statistical Association} 103(482), 832--842.

\bibitem[Imai, Jiang, and Malani(2021)]{ImaiJiangMalani2021}
Imai, K., Jiang, Z., and Malani, A. (2021).
Causal inference with interference and noncompliance in two-stage randomized
experiments.
\emph{Journal of the American Statistical Association} 116(534), 632--644.

\bibitem[Manski(1990)]{Manski1990}
Manski, C. F. (1990).
Nonparametric bounds on treatment effects.
\emph{American Economic Review} 80(2), 319--323.

\bibitem[Nibbering and Oosterveen(2025)]{NibberingOosterveen2025}
Nibbering, D. and Oosterveen, M. (2025).
Policy-relevant causal effect estimation using instrumental variables with
interference.
arXiv:2509.12538.

\bibitem[S\"avje(2024)]{Savje2024}
S\"avje, F. (2024).
Causal inference with misspecified exposure mappings: separating definitions and
assumptions.
\emph{Biometrika} 111(1), 1--15.

\bibitem[Schr\"oder et al.(2026)]{SchroderOprescuFeuerriegelKallus2026}
Schr\"oder, M., Oprescu, M., Feuerriegel, S., and Kallus, N. (2026).
Causal inference on networks under misspecified exposure mappings: a partial
identification framework.
arXiv:2602.03459.

\bibitem[Vazquez-Bare(2023)]{VazquezBare2023}
Vazquez-Bare, G. (2023).
Identification and estimation of spillover effects in randomized experiments
with noncompliance.
\emph{Journal of the American Statistical Association} 118(543), 1508--1520.

\bibitem[Weinstein and Nevo(2026)]{WeinsteinNevo2026}
Weinstein, B. and Nevo, D. (2026).
Causal inference with misspecified network interference structure.
\emph{Biometrics} 82(1), ujag023.
\end{thebibliography}

\end{document}
